%\documentclass{amsart}



%\usepackage[applemac]{inputenc}
%\addtolength{\hoffset}{-12mm}
%\addtolength{\textwidth}{22mm}
%\addtolength{\voffset}{-10mm}
%\addtolength{\textheight}{20mm}

%\def\uuu{_}

%\def\vvv{-}

%\begin{document}


\centerline{\bf\large{An automorphism on product measures}}

\bigskip


\noindent
{\bf{Introduction.}}
The  results is   expose material from
the article 
[Beurling]. Before  the   measure theoretic study starts 
we
insert comments from [Beurling] about 
the  significance of the main theorem in 0.¤¤ below.

\medskip


\noindent
{\bf{Schršdinger equations.}}
The article
\emph{ThŽorie relativiste de l'electron et l'interprŽtation
de la mŽcanique quantique} was published 1932. Here
Schršdinger raised a new and unorthodox question concerning Brownian motions
leading to new mathematical problems of considerable interest.
More precisely, consider a Brownian motion which takes place in a bounded
region $\Omega$ of some euclidian space
${\bf{R}}^d$ for some $d\geq 2$.
At time $t=0$
the densities of particles 
under observation is given by some
non\vvv negative function $f\uuu 0(x)$ 
defined on $\Omega$.
Classically the density at a later time $t>0$
is equal to
a function
$x\mapsto u(x,t)$ where
$u(x,t)$ solves the heat equation
\[
\frac{\partial u}{\partial t}= \Delta(u)
\] 
with boundary conditions 
\[
u(x,0)=f\uuu 0(x)\quad\text{and}\quad
\frac{\partial u}{\partial {\bf{n}}}(x,t)= 0
\quad\text{when }\quad x\in \partial\Omega\quad\text{and}\quad t>0\tag{1}
\]
Schršdinger took into the account
the reality of quantum physics which
means that in an  actual experiment
the observed density of particles at a time
$t\uuu 1>0$ does not coincide with $u(x,t\uuu 1)$.
He posed the problem to find the most probable development during the time
interval $[0,t\uuu 1)$ which leads to the state at time
$t\uuu 1$.
He concluded  that
the the requested density
function   which
substitutes the heat\vvv solution $u(x,t)$
should belong to a non\vvv linear class of functions formed by
products
\[ 
w(x,t)= u\uuu 0(x,t)\cdot u\uuu 1(x,t)\tag{*}
\]
where $u\uuu 0$ is a solution to (1) 
while $u\uuu 1(x,t)$ is a solution to an adjoint equation
\[
\frac{\partial u\uuu 1}{\partial t}= \vvv\Delta(u)
\quad\colon\quad
\frac{\partial u\uuu 1}{\partial {\bf{n}}}(x,t)= 0
\quad\text{on}\quad \partial\Omega\tag{2}
\] 
defined when $t<t\uuu 1$.
This leads to a new type of Cauchy problems
where one asks if there exists a  $w$\vvv function given by (*)
satisfying
\[ 
w(x,0)= f\uuu 0(x)\quad\colon\quad w(x,t\uuu 1)=f\uuu 1(x)
\]
where $f\uuu 0,f\uuu 1$ are non\vvv negative functions
such that
\[
\int\uuu\Omega\, f\uuu 0\cdot dx=
\int\uuu\Omega\, f\uuu 1\cdot dx
\]
\medskip

\noindent
The solvability of this non\vvv linear boundary value problem was left open
by Schršdinger and the search for  solutions has remained as an active field
in mathematical physics.
When $\Omega$ is a bounded set
and has a smooth boundary
one can use the Poisson\vvv Greens function for the
classical equation (*)  and 
rewrite Schršdinger's equation  to 
a system of non\vvv linear integral equations.
The interested reader should consult the talk by I.N. Bernstein a the IMU\vvv congress at ZŸrich 1932 for a first account about mathematical solutions to
Schršdinger equations.
Examples occur already  on the product
of two copies of the real line where Schršdinger's equations lead to
certain non\vvv linear equation for measures which goes as follows:
Consider the Gaussian density function


\[
g(x)=\frac{1}{\sqrt{2\pi}}\cdot e^{\vvv x^2/2}
\]

\medskip

\noindent
Next, consider the family $\mathcal S\uuu g^*$
of all non\vvv negative product measures
$\gamma\uuu 1\times\gamma\uuu 2 $ for which
\[
\iint g(x\uuu 1\vvv x\uuu 2)\cdot d\gamma\uuu 1(x\uuu 1)
\cdot d\gamma\uuu 2(x\uuu 2)=1\tag{i}
\]
The product measure gives another product measure 
\[
\mathcal T\uuu g(\gamma\uuu 1\times\gamma\uuu 2)=
\mu\uuu 1\times\mu\uuu 2
\]
where
\[
\mu\uuu 1(E\uuu 1)\cdot \mu\uuu 2(E\uuu 2)=
\iint \uuu {E\uuu 1\times E\uuu 2}\,
g(x\uuu 1\vvv x\uuu 2)\cdot d\gamma\uuu 1(x\uuu 1)
\cdot d\gamma\uuu 2(x\uuu 2)
\] 
hold for all pairs of bounded Borel sets.
Notice that $\mu\uuu 1\times \mu\uuu 2$
becomes a probability measure since (i) above holds.
With these notations one has

\medskip

\noindent
{\bf{0.1 Theorem.}}
\emph{For every product measure
$\mu\uuu1\times\mu\uuu2$ which in addition is a probability measure there exists
a unique $\gamma\uuu 1\times\gamma\uuu 2$ in $S^*\uuu g$
such that}
\[
\mathcal T\uuu g(\gamma\uuu 1\times\gamma\uuu 2)=\mu\uuu1\times\mu\uuu2
\]
\medskip


\noindent
In [Beurling]
a more general result is established
where the  $g$\vvv function can be replaced by
an arbitrary  non\vvv negative and bounded function $k(x\uuu 1,x\uuu 2)$
such that
\[
\iint\uuu{{\bf{R}}^2}\,\log \, k\cdot dx\uuu 1dx\uuu 2>\vvv \infty
\]
\bigskip
  

\centerline{\bf{1. The $\mathcal T$\vvv operator and
product measures}}

\bigskip


\noindent
Let $n\geq 2$ and consider an $n$\vvv tuple of
sample spaces $\{X\uuu\nu=(\Omega\uuu\nu,\mathcal B\uuu\nu)\}$.
We get the product space
\[ 
Y=\prod X\uuu\nu
\]
whose sample space is the set\vvv theoretic product
$\prod\,\Omega\uuu\nu$ and   Boolean $\sigma$\vvv algebra 
$\mathcal B$ generated by
$\{\mathcal  B\uuu \nu\}$.
\medskip


\noindent
{\bf{0.1 Product measures.}}
Let $\{\gamma\uuu\nu\}$ be an $n$\vvv tuple of signed measures on
$X\uuu 1,\ldots,X\uuu n$ where  each $\gamma\uuu\nu$
has a finite total variation. There exists a unique measure $\gamma^*$
on $Y$ such that
\[ 
\gamma^*(
E\uuu 1\times\ldots\times E\uuu n)=
\prod\,\gamma\uuu\nu(E\uuu\nu)
\]
hold for every $n$\vvv tuple of $\{\mathcal B\uuu\nu\}$\vvv measurable sets.
We refer to $\gamma^*$ as the product measure. It is
uniquely determined  because $\mathcal B$ is generated
by
product sets $E\uuu 1\times\ldots\times E\uuu n)$
with each $E\uuu\nu\in\mathcal B\uuu\nu$.
When no confusion is possible we put
\[
 \gamma^*=\prod\,\gamma\uuu\nu
\]

\noindent
The family of all such product measures is denoted by $\text{prod}(\mathcal M\uuu B)$.

\medskip

\noindent
{\bf{0.2 Remark.}}
The set of product measures is a proper non\vvv linear subset of the space
$\mathcal M\uuu B$ of all signed measures on $Y$.
This is already seen when $n=2$ with two discrete sample spaces, i.e.
$X\uuu 1$ and $X\uuu 2$  consists of $N$
points for some integer $N$. A
Every $N\times n$\vvv matrix with 
non\vvv negative elements $\{a\uuu{jk}\}$
give a probability measure $\mu$ on
$X\uuu 1\times X\uuu 2$
when the double sum $\sum\sum\, a\uuu{jk}=1$
The condition that $\mu$ is a product measure is tha there exist
$N$\vvv tuples $\{\alpha\uuu j$ and $\{\beta\uuu k\}$
such that $\sum\,\alpha\uuu \nu=\sum\,\beta\uuu k=1$
and 
$a\uuu{jk}=\alpha\uuu j\cdot \beta\uuu k$.
\bigskip

\noindent
{\bf{0.3 The space $\mathcal A$}}.
We have the linear space 
of functions on $Y$
whose elements are of the form
\[
a=g\uuu 1^*+\ldots+g\uuu n^*\tag{i}
\] 
where  $\{g\uuu\nu\} $  are functions on the separate
product factors
$\{X\uuu\nu\}$. It is clear that a pait of product measures
$\gamma$ and $\mu$ on $Y$ are equal if and only if
\[
\int\uuu Y\, a\cdot d\gamma=
\int\uuu Y\, a\cdot d\mu
\] 
hold for every $a\in\mathcal A$.
\medskip


\noindent
{\bf{0.4 The measure $e^a\cdot \gamma^*$}}
Let $a=\sum\, g^*\uuu\nu$ be as above.
Then we get the exponential function
\[
e^a=\prod \, e^{g^*\uuu\nu}
\]
If $\gamma^*=\prod\,\gamma\uuu\nu$ is some product measure
we get a new product measure defined by

\[
e^a\cdot \gamma\uuu *= \prod\, e^{g\uuu\nu}\cdot \gamma\uuu\nu
\]


\noindent
{\bf{0.5 The $\mathcal T$\vvv operators.}}
To every bounded
$\mathcal B$\vvv measurable function $k$ we shall construct a map $\mathcal T\uuu k$
from the space of product measures into itself.
First, let 
$1\leq\nu\leq n$ be given and  $g\uuu\nu $ is some
$\mathcal B\uuu\nu$\vvv measurable function. 
Then there exists the function $g\uuu\nu^*$
on the product space $Y$ defined by
\[
g\uuu\nu ^*(x\uuu 1,\ldots,x\uuu n)=g\uuu\nu (x\uuu \nu)
\]
Let us now consider a product measure
$\gamma$.  If $1\leq\nu\leq n$ we find a unique measure on $X\uuu \nu$
denoted by $(k\cdot\gamma)\uuu\nu$ such that
\[
\int\uuu Y\, g^*\uuu\nu\cdot k\cdot d\gamma=
\int\uuu{X\uuu\nu}\, g\uuu\nu\cdot d(k\cdot\gamma)\uuu\nu
\]
hold for every bounded
$\mathcal B\uuu\nu$\vvv measurable function $g\uuu\nu$ on $X\uuu\nu$.
Now we get
the product measure
\[ 
\mathcal T\uuu k(\gamma)=\prod\, (k\gamma)\uuu\nu\tag{*}
\]

\medskip

\noindent
{\bf{Remark.}}
In the the case when  
\[
k(x\uuu 1,\ldots,x\uuu n)=g^*\uuu 1\cdots g^*\uuu n
\]
we see that 
\[ 
\mathcal T\uuu k(\gamma)= \prod\, g\uuu\nu\cdot \gamma\nu
\]
\medskip

\noindent
{\bf{Exercise.}}
Consider the case $n=2$ where $X\uuu 1$ and $X\uuu 2$ both consist of two points, say
$a\uuu 1,a\uuu 2$ and $b\uuu 1,b\uuu 2$ respectively.
A measure $\gamma\in S^*\uuu 1$
is given by $\gamma\uuu 1\times\gamma\uuu 2$ and we can identify
this product measure by a $2\times 2$\vvv matrix
\[
XXX
\]
where $\alpha\uuu i\cdot \beta\uuu \nu$ is the mass of $\gamma$ at
the point $(a\uuu i,b\uuu \nu)$. Next, let $k$ be a positive function on
the product space which means that we assign four positive numbers
\[
k\uuu{i,\nu}=
k(a\uuu i,b\uuu\nu)
\]
Find the measure $\mathcal T\uuu k(\gamma)$ and
express it as above by a $2\times 2$\vvv matrix.



\bigskip





\noindent
Now we are prepared to announce the main result in
this section.
Consider a positive $\mathcal B$\vvv measurable function $k$
such that  $k$ and $k^{\vvv 1}$
both are bounded functions.
Denote by $\mathcal S^*\uuu k$ the family of non\vvv negative product measures
$\gamma$ on $Y$ such that
\[
\int\uuu Y\, k\cdot d\gamma=1
\]
We have also the set $\mathcal S^*\uuu 1$ 
of product measures $\mu$ which are non\vvv negative and have
total mass one, i.e.
\[
\int\uuu Y\, d\mu=1
\]


\noindent
It is easily seen   that $\mathcal T\uuu k$ yields
an injective
map from  $S^*\uuu k$ into $S^*\uuu 1$. It turns out that the map also
is surjective, i.e. the following hold:




\medskip

\noindent
{\bf{Main Theorem.}}
\emph{$\mathcal T\uuu k$ yields a homeomorphism between $S^*\uuu k$ and $S^*\uuu 1$}.

\bigskip

\noindent
{\bf{0.6 Remark.}}
Above we refer to  the norm topology on the space of measure, i.e.
if $\gamma\uuu 1$ and $\gamma\uuu 2$ are two  measures on
$Y$ then
the norm $||\gamma\uuu 1\vvv \gamma\uuu 2||$ is the total variation of
the signed measure $\gamma\uuu 1\vvv\gamma\uuu 2$.
The reader may verify that
$S^*\uuu k$ and $S^*\uuu 1$
both appear as closed subsets in the
normed space of all signed measures on $Y$.
Recall also from XX that the space of measures on $Y$
is complete under this norm.
In particular, let $\{\mu\uuu \nu\}$
be a Cauchy sequence with respect to the norm where
each $\mu\uuu\nu\in \mathcal S^*\uuu 1$. Then there exists a strong limit
$\mu^*$ where $\mu^*$ again belongs to $\mathcal S^*\uuu 1$
and
\[
||\mu\uuu\nu\vvv \mu^*||\to 0
\]
This completeness property will
be used in the subsequent proof.
We shall also need some inequalities
which are announced below.

\medskip

\noindent
{\bf{0.7 Some useful inequalities.}}
Let $\gamma\uuu 1$ and $\gamma\uuu 2$
be a pair of product measures 
such that
\[ 
\bigl|\int\uuu Y\, g^*\uuu \nu\cdot d\gamma\uuu 1\vvv
\int\uuu Y\, g^*\uuu \nu\cdot d\gamma\uuu 2\bigr |\leq\epsilon
\quad\colon\quad 1\leq\nu\leq n
\] 
hold for 
some $\epsilon>0$
and every function $g\uuu\nu$ on $X\uuu\nu$ with maximum norm
$\leq 1$. Then the norm
\[ 
||\gamma\uuu 1\vvv \gamma\uuu 2||\leq n\cdot \epsilon\tag{i}
\]


\noindent
The proof of (i) is  left to the reader
where the hint is to 
make repeated  use of  Fubini's theorem.
More generally, let
$k$ be a bounded measurable function on $Y$
and $\gamma,\mu$ is a pair of product measures.
Denote by $\mathcal A\uuu *$ the set of
$\mathcal A$\vvv functions $a$ with maximum norm
$\leq 1$. Then there exists a constant $C$ which only depends on $k$ and
$n$ such that




\[
||\mathcal T\uuu k(\mu)\vvv \gamma||\leq
\max\uuu {a\in A\uuu *}\, \bigl|\int\uuu Y\, a(kd\mu\vvv d\gamma)\,\bigr|\tag{*}
\]

\noindent
Again we leave the proof as an exercise.
\medskip










\noindent
{\bf{0.8 A variational problem.}}
Since we already have observed that
$\mathcal T\uuu k$ is injective there remains to
prove surjectivity.
For this we shall study a
a variational
problem which we begin to describe  before the proof is finished in 0.¤¤ X below.
We are given the function $k$ on $Y$ where both $k$ and $k^{\vvv 1}$
are bounded and the space
$\mathcal A$ was defined in 0.3.
For every pair  $\gamma\in \mathcal S^*\uuu 1$ and
$a\in \mathcal A$  we set
\[ 
W(a,\gamma)=\int\uuu Y\, (e^ak\vvv a)\cdot d\gamma 
\quad\text{and}\quad W\uuu *(\gamma)=
 \min\uuu{a\in\mathcal A}\,W(a,\gamma)
\]




\medskip

\noindent
{\bf{0.9 Proposition.}} \emph{Let $\{a\uuu \nu\}$ be a sequence in
$\mathcal A$ such that}
\[
\lim W(a\uuu\nu,\gamma)= W\uuu*(\gamma)
\]
\emph{Then the sequence  $\{e^{a\uuu \nu}\cdot \gamma\}$
converges to a   measure
$\mu\in S^*\uuu 1$ such that $\mathcal T\uuu k(\gamma)=\mu$.}




\medskip

\noindent
Before we enter the proof we insert a preliminary result which will
be used later on.
\medskip

\noindent
{\bf{0.10. Lemma.}} 
\emph{Let $\epsilon>0$ and $a\in\mathcal A$ be such that
$W(a)\leq W\uuu *(\gamma)+\epsilon$. Then it follows that}

\[
\int\, e^a\cdot k\cdot \gamma\leq 
\frac{1+\epsilon}{1\vvv e^{\vvv 1}}
\]

\noindent
\emph{Proof.}
For every real number $s$   the function $a\vvv s$
again belongs to $\mathcal A$ and by the hypothesis 
$W(a\vvv s)\geq W(a)\vvv \epsilon$. This entails that

\[
\int\, e^a k\cdot d\gamma\leq
\int\uuu Y\, e^{a\vvv s}\cdot kd\gamma+s\int\, k\cdot d\gamma+\epsilon
\implies
\]
\[
\int (1\vvv e^{\vvv s})\cdot e^a\cdot kd\gamma\leq s+\epsilon
\]
Lemma 0.10 follows if we take $s=1$.






\bigskip


\noindent
\emph{Proof of Proposition 0.9} Keeping $\gamma$ fixed we set
$W(a)= W(a,\gamma)$.
Let $0<\epsilon<1$ and consider a pair $a,b$ in $\mathcal A$ such that
$W(a)$ and $W(b)$ both are $\leq W\uuu *(\gamma)+ \epsilon$.
Since  $\frac{1}{2}(a+b)$
belongs to $\mathcal A$  we get
\[
2\cdot W(\frac{1}{2}(a+b))\geq 2\cdot W\uuu *(\gamma)
\geq W(a)+W(b)\vvv 2\epsilon\tag{i}
\]
Notice that
\[
W(a)+W(b)\vvv
2\cdot W(\frac{1}{2}(a+b))=
\int\uuu Y\, [e^a+e^b\vvv 2\cdot e^{\frac{1}{2}(a+b))}]\cdot kd\gamma\tag{ii}
\]
Next,  we have  the algebraic identity
\[
e^a+e^b\vvv 2\cdot e^{\frac{1}{2}(a+b))}]=(e^{a/2}\vvv e^{b/2})^2
\]
It follows from (i\vvv ii) that
\[
\int\uuu Y\, (e^{a/2}\vvv e^{b/2})^2\cdot k\cdot d\gamma \leq 2\epsilon\tag{iii}
\]
Next, the identity
$|e^a\vvv e^b)|=
(e^{a/2}+e^{b/2})\cdot |e^{a/2}\vvv e^{b/2}|$
and the Cauchy\vvv Schwarz inequality give:

\[
\bigl[\int\uuu Y\, |e^a\vvv e^b|\cdot k\cdot d\gamma\,\bigr ]^2\leq
2\epsilon\cdot \int\uuu Y\, (e^{a/2}+e^{b/2})\cdot k\cdot d\gamma\tag{iv}
\]
By Lemma 0.6  the last factor is bounded by
a fixed constant and hence (iv) gives a constant $C$ such that
\[
\int\uuu Y\, |e^a\vvv e^b|\cdot k\cdot d\gamma
\leq C\cdot \sqrt{\epsilon}\tag{v}
\]
Next, let $k\uuu *$ be the minimum value taken by
$k$ on $Y$ which by assumption is positive since
$k^{\vvv 1}$ is bounded.
Replacing $C$ by $C/k\uuu *$ where 
we get
\[
\int\uuu Y\, |e^a\vvv e^b|\cdot d\gamma
\leq C\cdot \sqrt{\epsilon}\tag{vi}
\] 


\noindent
Now (v) applies to pairs in the sequence $\{a\uuu\nu\}$
and shows that
$\{e^a\cdot d\gamma\}$ is a Cauchy sequence with respect 
to the norm of measures on $Y$. So from Remark 0.6
there exists a non\vvv negative measure $\mu$ such that
\[
\lim\uuu{\nu\to \infty}\, ||e^{a\uuu\nu}\cdot\gamma\vvv \mu||=0\tag{vii}
\]

\medskip


\noindent
\emph {The equality $\mathcal T\uuu k(\mu)=\gamma$}.
Consider the 
$a$\vvv functions in the minimizing sequence.
If $\rho\in \mathcal A$ is arbitrary we have
\[ 
W(a\uuu\nu+\rho)\geq W(a\uuu\nu)\vvv \epsilon\uuu\nu
\] 
where $\epsilon\uuu\nu\to 0$.
This gives
\[
\int\uuu Y\, [ke^{a\uuu\nu}(1\vvv e^\rho)+\rho]\cdot d\gamma\leq \epsilon\uuu\nu\tag{1}
\]
When the maximum norm
$|\rho|\uuu Y\leq 1$ we can write
\[
e^\rho=1+\rho+\rho\uuu 1\quad\text{where}\quad
 0\leq \rho\uuu 1\leq \rho^2\tag{2}
\]
Then we see that (1) gives
\[
\int\uuu Y\,(\rho\vvv ke^{a\uuu\nu}\cdot \rho)\cdot d\gamma\leq
\epsilon\uuu\nu +\int\,\rho\uuu 1\cdot \gamma\leq
\epsilon+||\rho||\uuu Y^2\tag{3}
\]
where the last inequality follows since
$\gamma$ is a probability measure and the inequality in (2) above.
The same inequality holds with $\rho$ replaced by $\vvv \rho$
which entails that
\[
\bigl|\int\uuu Y\,(ke^{a\uuu\nu}\vvv 1)\cdot \rho\cdot d\gamma\bigr|
\leq\epsilon\uuu\nu+||\rho||\uuu Y^2
\]

\noindent
Notice that Lemma 0.10 entails that
the sequence of functions
$\{ke^{a\uuu\nu}\}$ are uniformly bounded.
Now we apply the inequality (*) from 0.7
while we use
$\rho$\vvv functions in $\mathcal A$ of norm $\leq\sqrt{\epsilon\uuu\nu}$.
It follows
that there exists a constant $C$ which is independent of $\nu$
such that
the  following inequality for the total variation:
\[
||\mathcal T\uuu k(e^{a\uuu\nu}\cdot\gamma)\vvv \gamma||\leq C\cdot n
\cdot \frac{1}{\sqrt{\epsilon}}\cdot
(\epsilon\uuu\nu+\epsilon\uuu\nu)= 2\cdot Cn\cdot \sqrt{\epsilon\uuu\nu}
\]
Passing to the limit it follows from (vii) that we have
the equality
\[ 
\mathcal T\uuu k(\mu)=\gamma
\]

\noindent
Since $\gamma\in S^*\uuu1$ was arbitrary
we have proved that
the $\mathcal T\uuu k$ yields a surjective map from
$S^*\uuu k$ to $S^*\uuu 1$
which finishes the proof of the
Main Theorem.







\bigskip


\centerline {\bf{  0.11 The  singular case.}}
\bigskip

\noindent
We restrict to the case $n=2$ where
$k(x\uuu 1,x\uuu 2)$ is a bounded and strictly positive 
continuous function on
$Y= X\uuu 1\times X\uuu 2$. Let $\gamma\in S^*\uuu 1$ satisfy:
\[
\int\uuu Y\, \log k\cdot d\gamma>\vvv \infty\tag{1}
\]
Under this integrability condition the following hold:

\medskip

\noindent
{\bf{2. Theorem.}}
\emph{There exists a unique non\vvv negative 
product measure
$\mu$ on $Y$ such that
$\mathcal T\uuu k(\mu)=\gamma$.}
\medskip

\noindent
{\bf{Remark.}}
In general the measure $\mu$ need not have finite mass
but the proof shows that
$k$ belongs to $L^1(\mu)$, i.e.
\[
\int\uuu Y\, k\cdot d\mu<\infty
\]


\noindent
As pointed out by Beurling  Theorem 0.12
can be applied to the case $X\uuu 1=X\uuu 2={\bf{R}}$
both are copies of the real line and
\[
k(x\uuu1,x\uuu 2)=g(x\uuu 1\vvv x\uuu 2)
\] where $g$ is the density of a Gaussian distribution which after  a
normalisation  of
the variance is taken to be
\[
\frac{1}{\sqrt{2\pi}}\cdot e^{\vvv t^2/2}
\]
So the integrability condition for $\mu$  becomes

\[
\iint\, (x\uuu 1\vvv x\uuu 2)^2\cdot d\mu(x\uuu 1,x\uuu 2)<\infty
\] 
\medskip

\noindent
A proof of Theorem 0.12  is given on page 218\vvv 220
in [loc.cit] and relies upon similar but technically more involved
methods as in the Main Theorem.
Concerning higher dimensional cases,  i.e.
singular versions of the Main Theorem when
$n\geq 3$, 
Beurling gives the
following comments at the end of [ibid]
where the citation below has changed numbering of
the theorems as compared to [ibid]:
\medskip

\noindent
\emph{The proof of the Main Theorem 
relies heavily on the condition that $k\geq a$ for some
$a>0$.
If this lower bound condition is dropped
the individual equation $\mathcal K(\gamma)=\mu$ may still
be meaningful, but serious complications will
arise concerning the global uniqueness if $n\geq 3$
and the proof of Theorem 0.12  for the case $n\geq 3$ cannot be duplicated.}






















%\end{document}

