\documentclass{amsart}
\usepackage[applemac]{inputenc}


\addtolength{\hoffset}{-12 mm}
\addtolength{\textwidth}{22 mm}
\addtolength{\voffset}{-10 mm}
\addtolength{\textheight}{20 mm}


 
\begin{document}



\centerline
{\bf{Fšrslag till Sparrerska priset}}
\bigskip


\noindent
Johan Alm inledde hšgskolestudier vid Uppsala Universitet 2004
dŠr han fšrutom matematik ocksŒ studerade  fysik i fem terminer.
Alm  antogs till forskarutbildning i matematik vid Stockholms Universitet
i augusti 2009 med Sergei Merkulov som huvudhandledare och  Torsten Ekedahl som bitrŠdande
handledare.
FrŒn  Alms studier i   Uppsala 
ingick  flera rŠtt avancerade  kurser
som Modules and Homologcal algebra (2007-12-18) samt
Analysis on Manifolds (2009-04-17).
Vidare skrev Alm ett imponerade examensarbete
som redan i ett tidigt skede 
vittnar om mycket goda  insikter och fšrmŒga  
att arbeta med avancerad differentialgeometri.
\medskip


\noindent
Hšsten 2009 inledde Alm
ett  forskningsprojekt
som  gavs  av hans handledare Merkulov vilket 
ledde till
ett  arbete  vars resultat 
vida švertrŠffar vad som normalt kan fšrvŠntas hos en
nybliven forskarstuderande.
Alms presenterade sin licentiatavhandling [A:1] 30 maj 2011.
DŠr infšrs bland annat 
tvŒ helt nya konfigurationsoperader i ¤ 1.3.14 i [A:1] och
Alm hŠrleder egenskaper hos dessa fšr att efterŒt
uvidga och skŠrpa tidigare resultat av bland andra Kontsevich och Duflo.
Jag vill  gŠrna tillŠgga att Alms  inledning  till
licentiatavhandlingen
visar prov pŒ en 
mognad som vore den skriven av en redan
eminent
matematiker med mŒngŒrig erfarenhet.
Fšrutom
nya vŠrdefulla resultat i [A:1]
visar  arbetet prov pŒ
bredd och djup hos dŠr
metoder frŒn en rad olika ŠmnesomtŒden som differentialgeometri,
topologi och  algebra ingŒr pŒ ett vis
man ytterst sŠllan mšter hos en ung forskarstuderande.
\medskip


\noindent
Artikeln [A:2]
Šr skrivet med Merkulov som medfšrfattare. HŠr 
unyttjas dels resultat frŒn [A:1]  samt
tidigare
arbeten av Merkulov, bland annat om Exotic automorphisms of
Shouten algebras and deformation quantization polyvectorfields.
Huvudresultatet i [A:2] ger nya och 
vŠrdefulla inblickar om Poissonstrukturer pŒ mŒngfalder dŠr de 
rent matematiska upptŠckterna har anknytning till
fysik, bland annat kring Feymanngrafer.
\medskip

\noindent
Alm har sedan hšsten 2012
arbetat med nya problemstŠllningar  dŠr
man torde kunna fšrvŠnta sig nya starka resultat som bland annat
kan komma att knyta an till kvantfŠltsteori  dŠr det 
finns mŒnga fundamentala och Šnnu olšsta problem fšr sŒvŠl teoretiska fysiker om
matematiker.
\medskip

\noindent
Avslutningsvis  instŠmmer jag till fullo med  de lovord som
Sergei  Merkulov 
framfšr i sitt rekommendationsbrev om Johan Alm.
\bigskip
\[
\text{Stockholm 21 december 2012}
\]

\[
\text{Jan-Erik Bjšrk}
\]

\[ 
\text{Emeritus professor vid matematiska institutionen SU}
\]












\newpage





\noindent
Hšrmander presenterade Atiyah  och Singer insatser 
nŠr de fick Abelpriset  fšr  
deras gemensamma artikel The index of elliptic operators.
Han har sjŠlv  ocksŒ
publicerat en uppsats  med anknytning till
indexteoremet
Se ref 42 i hans bšcker om PDE:
Elliptische Differentialgleichungen Akademie Verlag Berlin 1971.
BetrŠffande originalbeviset av Atiyah och Singer
fordrade den rent analytiska delen av beviset
inte  allmŠnna resultat
om pseudodifferentialoperatorer. Deras bevis 
utnyttjade  resultat om singulŠra operatorer,
frŠmst via  arbeten av Calderon frŒn mitten av 1950-talet.
Henri  Cartans presentationsfšredrag frŒn IMU i Moskava 1966
om Atiyahs Fieldspris  
tydliggšr detta.
\medskip

\noindent
DŠremot lyfter  J.J Kohn i sitt 30-minutersfšredrag med titeln
Differential  Complexes fram 
ett dŒ aktuellt arbete av Hšrmander:
Pseudo-Differential operators  and non-elliptic  boundary value
problems (Ann. of Math. 83 (1966).
Bland annat skriver Kohn:
\medskip

\noindent
In a joint paper  (Annals  of Math, 1965) with 
{Hugo Rossi we   study 
the problem of extending
holomorphic forms from the boundary of  manifold.
This suggested
the investigation of an induced $\bar\partial$-operator 
on real submanifolds of a complex manifold
which provide 
examples of non-elliptic boundary value complexes on
compact manifolds with
good regularity properties and finite cohomology.
Lars Hšrmander has studied a much more general
class of such problems, and recently Sweeney has extended
earlier work about 
Spencer resolutions where he
has applied general facts from Hšrmander's cited artiicle.}
\medskip



\noindent
{\bf{Integralrepresentationer  av  
lšsningar till  PDE-system med konstanta koefficienter.}}
I Notes till kapitel  XV: Analytic function theory  and differential equations frŒn vol.2 i Hšrmanders PDE-bšcker
visas att Šven deriverbara  lšsningar
kan representeras
via
absoluta konvergenta integraler tagna šver 
exponentiallšsningar.
Det tekniska
problemet som Hšrmander lšser i detta kapitel handlar om
att vissa $L^2$-estimat med bounds
gŠller trots att viktfunktionerna inte Šr šverallt
plurisubharmoniska. Se
Notes s. 360 fšr en detaljerad kommentar
och notera att Hšrmander i denna Not till Kapitel XV
lyfter fram originalarbeten av Morrey och J.J- Kohn som
var de som fšrst  anvŠnde $L^2$-olikheter fšr att
studera speciella šverbestŠmda system 
via Cauchy-Riemann ekvationer i flera komplex variabler.
\medskip


\noindent
{\bf{Hypoelliptiska operatorer.}}
Ett av huvudresultaten i Hšrmanders doktorsavhandling
handlar om att karakterisera hypoelliptiska operatorer.
Under hans Œr som professor vid SU
utvecklade och generaliserade han resultat frŒn avhandlingen dŠr man
kan nŠmna artikeln
xxxx (Arkiv fšr matematik vol. xx 1957).

















\newpage


\centerline{\bf{Lech's theorem on  zeros of a polynomial ideal.}}
\bigskip


\noindent
We  expose a proof of a theorem by Christer Lech from the  article [Le]. His result  
answered  a  question raised by
by Lars Hšrmander  concerned with
over-determined systems of hypoelliptic
PDE-equations. Here is the situation.
Let $n\geq 3$ and $\mathfrak{p}$ is a prime ideal in
${\bf{C}}[z_1,\ldots,z_n]$ whose locus $\mathfrak{p}^{-1}(0)= V$
yields  an irreducible algebraic set. We assume that
$\dim(V)=d$ where
$d\leq n-2$ and put
$p=n-d$. 
A \emph{Lech polynomial with respect to $V$} is a
polynomial $p(z)$
which is zero on $V$, and in addition there exists a constant $C$ such that
the following inequality hold for each
$x\in {\bf{R}}^n$
\[ 
\text{dist}(x,V)\leq C\cdot 
\text{dist}(x,f^{-1}(0))
\] 
where $\text{dist}$ refers to the euclidian length.
\medskip


\noindent
We shall prove that there exists a Lech polynomial
with respect to every algebraic set $V$ in ${\bf{C}}^n$.
To begin with it suffices to prove
this existence when
$V$ is irreducible.  Namely, in general
$V= V_1\sup\ldots\cup V_m$
where $\{V_j\}$ are irreducible.
If $\{f_j\}$  are Lech polynomials asociated to
these irreducible sets, then
it is trivial to check that the product $f_1\cdots f_m$
is a Lech polynomial with respect to $V$.
\medskip

\noindent
Let us now consider a prime ideal  $\mathfrak{p}$ whose locus is
an irreducible algebraic set $V$ where
$d=\dim(V)\leq n-2$  and put $p=n-d$.





\medskip

\noindent










To find a  polynomial $L(z)$
such that (*) holds we shall use
a classic  result  due to Max Noether.
Namely, let $V^*$ be the algwebraic cone
of $V$, i.e. the common zeros of
the leading forms of polynomials from
$\mathfrak{p}$.
It is wellknown that
$\dim(V^*)= \dim(V)$
and now we consider elements $\Pi$ in the Grassmanian
$\mathcal G(p-1)$ of
which conaists of $(p-1)$-dimensional complex subspaces of
${\bf{C}}^n$.
Such a subspace $\Pi$ is said to be $V$-transversal if
\[
\Pi\cap \, V^*=\{0\}
\]
where the right hand side is the origin in
${\bf{C}}^n$.
Via algwbraic elimintion one shows easily that
for every $V$-transversal $\Pi$, 
the set-theoretic sum $\pi+V$ is an algebraic hypersurface
given by the zeros of an irreducible  polynomial $N_\Pi(z)$ whose 
degree is equal to the muliplicity of the given algewbraic set $V$.
This unifor  bound of the degree yields a finite dimensional comŒlexsubpsace
$\mathcal N$ of ${\bf{C}}[z]$ generte by these
$N_\pi$-polynimals as $\pi$ varies over
$V$-transversal elements in
$\mathcal G(p-1)$.
\medskip

\noindent
We refer to $\mathcal N$  as the Noether space asociated to $V$ and now we announce the
major result from   [Lech].
\medskip


\noindent
Tjoerem xxx
\medskip


\noindent
The proof requires several steps.



























Consider a  finite family  
$g_1,\ldots,g_m$  in
$\mathfrak {p}$ whose set of common zeros is $V$.
To each polynomial $p(z)=\sum\, c_\alpha z^\alpha$
we can take complex conjugates of the coefficients
and get the polynomial $\widehat{ p}(z)= \sum\,\bar c_\alpha\cdot z^\alpha$.
In particular we get the polynomial 
\[
g_*(z) =\sum_{j=1}^{j=m}\, \widehat{ g_j}(z)\cdot g_j(z)\tag{0.1}
\]
If $x=(x_1,\ldots,x_n)$ is a real point in
${\bf{C}}^n$ we have 
\[
g_*(x)= \sum |g_j(x)|^2\implies
{\bf{R}}^n\cap V={\bf{R}}^n\cap g_*^{-1}(0)
\]
Thus, $g_*\in\mathfrak{p}$ and it has the same set of real zeros as  $V$.
Less obvious is the following:
\medskip

\noindent
{\bf{Lech's Theorem.}}
\emph{There exists a finite set $f_1,\ldots,f_m$ in
$\mathfrak{p}$ and a constant $C$ such that
the following inequality hold for each
$x\in {\bf{R}}^n$:}
\[ 
\text{dist}(x,V)\leq C\cdot 
\text{dist}(x,f_*^{-1}(0))
\] 

\bigskip


\noindent
A polynomial $f$ for which there exists a constant $C$ as above is called a Lech
polynomial attached to $\mathfrak{p}$.
The construction of a Lech polynomial relies upon material 
in algebraic geometry which appears in 
AndrŽ Weil's book \emph{Foundations of Algebraic Geometry.} 
But let us first
describe the construction of a Lech polynomial using
the classic normalization theorem by
Max Noether.
Given the prime ideal $\mathfrak{p}$ as above we 
denote by 
$\mathfrak{p}^*$
the ideal in ${\bf{C}}[z_1,\ldots,z_n]$
generated by the leading forms of polynomials
in $\mathfrak{p}$. This yields the algebraic set
 $V^*$ of 
common
zeros of the homogeneous polynomials in $\mathfrak{p}^*$.
It is wellknown that $V^*$ has the same dimension as 
 $V$. So  the codimension of $V^*$ is $p=n-d$.
 Denote by $\mathcal G$ 
 the Grassmanian  of $(p-1)$-dimensional subspaces of
${\bf{C}}^n$.
A subspace $\Pi\in  \mathcal G$
is transversal to $V$ if the intersection $V^*\,\cap \Pi$ is reduced to
the origin in ${\bf{C}}^n$.
It  is wellknown that
that for every  transversal $\Pi$, the set-theoretic sum
\[
V+\Pi=\{ z+w\colon\, z\in V\,\quad\&\quad w\in\Pi
\]
is an algebraic hypersurface $P_\Pi^{-1}(0)$
where the degree of  $P_\Pi$ is majorized by  
the multiplicity $e(V)$ of the given
algebraic set.
It follows that the family $\{P_\Pi\}$
generates a finite dimensional complex vector space
in ${\bf{C}}[z]$  denoted by $\mathcal N(\mathfrak{p})$.
Let $f_1,\ldots,f_m$ be a basis of $\mathcal N(\mathfrak{p})$
and put 
\[
f_*(z)=\sum\, \widehat{f}_\nu(z)\cdot f_\nu(z)\tag{i}
\]
It turns out that $f_*$ is a Lech polynomial attached to
$\mathfrak{p}$.
The proof relies upon 
Lech's inequality  in ¤ 0 expressed by Theorem 0.1.
The proof is then finished 
using 
the Zariski-Weil theory about generic points.
This is exposed in ¤ 1 and the final part of the proof
appears in  ¤ 2.




\newpage



\centerline {\bf{¤ 0.  Lech's inequality.}}
\medskip


\noindent
Let $\phi(z_1,\ldots,z_n)$ be a polynomial of $n$ variables
which is not reduced to a constant,  i.e. its degree is $>0$.
If $\alpha\in {\bf{C}}^n\setminus \phi^{-1}(0)$ we put
\[ 
\text{dist}(\alpha,  \phi^{-1}(0))=
\min_{z\in \phi^{-1}(0)}\, |z-\alpha|
\]
where $|z-\alpha|$
is the euclidian distance. Next, let 
$\Theta=(\theta_1,\ldots,\theta_n)$ be a complex vector of unit length, i.e.
$|\theta_1|^2+\ldots+|\theta_n|^2=1$. This gives a polynomial
\[
t\mapsto  \phi(\alpha+t\cdot \Theta)
\]
and a
Taylor expansion
yields 
\[
\phi(\alpha+t\cdot \Theta)=
\phi(\alpha)+\sum_{k=1}^{k=m}\, D_k(\alpha;\Theta)\cdot t^k
\]
where $m$ is the degree of $\phi$   and
$\{D_k(\alpha;\Theta)\}$ is an $m$-tuple of complex numbers.
For each $1\leq  k\leq m$ we set 
\[
\mathcal D_k^*(\phi;\alpha)= \max_{\Theta}\, |D_k(\alpha;\Theta)|
\]
\medskip

\noindent
{\bf{Definition}}.\emph{
The Lech number of $\phi$ at the point $\alpha$ is defined by}
\[
\mathcal L(\phi;\alpha)= \max_{1\leq k\leq m}\,
\bigl[\frac{|\phi(\alpha)|}{\mathcal D_k^*(\phi;\alpha)}\,\bigr]^{\frac{1}{k}}
\]
\medskip

\noindent
{\bf{0.1 Theorem}}.
\emph{For every positive integer $m$ and
each polynomial $\phi$  of degree $m$
the following inequality holds
when 
$\alpha$ is outside the zero-set of $\phi$:}
\[
\frac{1}{2}\leq 
\frac{\text{dist}(\alpha, \phi^{-1}(0))} {\mathcal L(\phi;\alpha)}\leq m\tag{*}
\]



\medskip

\noindent
\emph{Proof}
Replacing $\phi$ by $c\cdot \phi$ for some constant
we may assume that
$\mathcal L(\phi;\alpha)=1$ which means that
\[
|\phi(\alpha)|=\max_{k,\Theta}\ D_k(\alpha;\Theta)\tag{1}
\]
with the maximum taken over 
pairs $(k,\Theta)$ where
$1\leq k\leq m$ and
$\Theta$ are complex $n$-vectors of unit length.
Every unit vector  $\Theta$
gives the $\zeta$-polynomial 
\[ 
\phi(\alpha+\Theta\cdot \zeta)= \phi(\alpha)+\sum
D_k(\alpha;\Theta)\cdot \zeta^k\tag{2}
\]
If the absolute calue $|\zeta|<1/2$
the triangle inequality gives:
\[
|\phi(\alpha+\Theta\cdot \zeta)|\geq |\phi(\alpha)| -
\sum_{k=1}^{k=m}\, |\zeta|^k\cdot |D_k(\alpha,\Theta)|
\]
Now (1) entails that the
right hand side above majorises
\[
|\phi(\alpha)|\cdot (1-\sum_{k=1}^{k=m}\, |\zeta|^k)
\]
Since $|\zeta|<1/2$ the last factor above is $>0$
and hence
$\zeta\mapsto \phi(\alpha+\Theta\cdot \eta)$ is zero-free
in the disc
$\{|\zeta|<1/2$ for every unit vector
$\Theta$.
Hence $\text{dist}(\alpha,\phi^{-1}(0))\geq 1/2$
which proves  the lower bound
in (*) from Theorem 0.1.
To get the  upper bound
we choose 
a pair $k_*,\Theta_*$ such that
\[
|\phi(\alpha)|= D_{k_*}(\alpha;\Theta_*)
\]
and consider the polynomial
\[ 
g(\zeta)= \zeta^m\cdot \phi(\alpha+\Theta_*\cdot \zeta^{-1})\tag{3}
\]
Write
\[
g(\zeta)=c_m \zeta^m+\ldots+ c_0
\]
Now (1) implies that the absolute values of $c_m$ and 
$c_{m-k}$ are equal.
Let $\beta_1,\ldots,\beta_m$ be the zeros of $g$ where
eventual multiple zeros are repeated.
The symmetric  polynomial of order $m-k$ 
of  this $m$-tuple  is a sum of
monomials in the roots of degree $k$ and equal to
\[
(-1)^{m-k}\cdot \frac{c_{m-k}}{c_m}
\]
whose absolute value is 1.
If  all the zeros have absolute value $\leq 1/m$
the absolute value of the symmetric sum above is majorised by
\[
m^{-k}\binom{m}{k}
\]
Since this term is $<1$ we conclude that
$g$ must have a zero of absolute value $>1/m$ which
by (3) implies that
the right hand side in (*) is $\leq m$.

 
 
  
 
 



\bigskip

\noindent
{\bf{An application.}}
For each finite family of polynomials  $\{\phi_1,\ldots,\phi_k\}$ and every real point $a$
we set
\[
\text{dist}(a,\phi^{-1}_\bullet(0))=\min_\nu\,\text{dist}(a,\phi_\nu^{-1}(0))
\]


\medskip

\noindent{\bf{0.2 Lech's Lemma}}
\emph{
Let  $\mathcal {M}$ be a finite dimensional subspace of 
${\bf{C}}[z_1,\ldots,z_n]$
and 
$f_1,\dots,f_m$ some basis of $\mathcal{M}$.
Then, if 
$\{g_1,\ldots,g_m\}$ is another basis   in
$\mathcal{M}$ there exists a constant $c>0$ such that
the inequality below holds for every real point $a$:}
\[
\text{dist}(a,f_*^{-1}(0))\geq c\cdot 
\text{dist}(a,g_\bullet^{-1}(0))
\]
\emph{where $f_*=\sum\, \bar f_\nu\cdot f_\nu$}.
\medskip


\noindent
\emph{Proof.}
Applying Lech's inequality to the 
the $g$-functions and $f_*$ we can   reformulate
Lech's Lemma as follows: 
There exists a constant $C$ which is independent of the real point $a$
such that the following hold:
If
\[
|g_\nu(\alpha)\geq A^k \cdot D_k(g_\nu)(\alpha)\tag{1}
\] 
hold for all $k\geq 1$ and all $\nu$ and some constant $A$, then 
\[
|f_*(\alpha)\geq (CA)^k \cdot D_k(f_*)(\alpha)\tag{2}
\] 



\noindent
To get (2) we proceed as follows. First, since 
$f_1,\ldots,f_m$ is a $k$-basis in $\mathcal M$
there exists 
a constant $C_0$ which is independent of $\alpha$ and
\[
|g_\nu(\alpha)\leq C_0\cdot \sum_{k=1}^{k=m}\ |f_k(\alpha)|\quad\colon\, 1\leq\nu\leq m
\]
Conversly, since
the $g$-polynomials also is  a basis of
$\mathcal M$ it is clear that
(1) gives a constant $C_1>0$ which again is independent of $\alpha$
such that
\[
C_1\cdot \max_\nu\, |f_\nu(\alpha)|\geq 
A^k\cdot \sum_{\nu=1}^{\nu=m}\, D_k(f_\nu;\alpha) \tag{3}
\]


\noindent
Next, since
$\alpha$Êis real we have
\[ 
f_*(\alpha)= \sum |f_\nu(\alpha)|^2\implies
C_1\cdot \sqrt{f_*(\alpha)}\geq 
A^k\cdot \sum_{\nu=1}^{\nu=m}\, D_k(f_\nu;\alpha) \tag{4}
\]

\noindent
Put
\[ 
D_k^*(\alpha) =\sum_{\nu=1}^{\nu=N}
\,D_k(f_\nu;\alpha)\tag{5}
\]


\noindent
Notice that when $f_\nu$ is replaced by $\bar f_\nu$
one has 
\[
D_k(f_\nu;\alpha)= D_k(\bar f_\nu;\alpha)\quad\colon\, k=1,2,\ldots
\] 
These
Taylor expansions give  the inequality
\[
D_k(f_*;\alpha)\leq N(k+1)\max_{i+j=k}\,
D^*_i(\alpha)\cdot D^*_j(\alpha)\tag{6}
\]


\noindent
Finally, with $k=i+j$ it is clear that 
(4) gives
\[ 
A^k\cdot D^*_i(\alpha)\cdot D^*_j(\alpha)\leq C_1^2|f_*(\alpha)|\tag{7}
\]
Then (6-7) give
\[
A^k\cdot D_k(f_*;\alpha)\leq N(k+1)\cdot C_1^2\cdot f_*(\alpha)|\tag{8}
\]
Since this hold for each $k$ we get the requested 
positive constant $C$ in (2) above.














\newpage


\centerline {\bf{¤ 1. Specialisations and linear systems.}}

\bigskip


\noindent
We shall use     specialisations 
which appear in the Zariski-Weil theory.
The reader is expected to know about the fundamental constructions from their theory which 
is the starting point for everything dealing with algebraic geometry, i.e. a first and invaluable lesson for beginners 
 is to
learn about
constructions due to these two  meters
who have contributed so much in
algebra and geometry.
Their approach
has the merit
that various 
geometric questions  are carried over to algebraic
calculations 
which are not  easily found in an  intuitive fashion.
We shall  only employ
the Zariski-Weil theory in characteristic
zero and apply results from  
Weil's  book
\emph{Foundations of algebraic geometry} published in 1943.
Personally I think the material in this outstanding
text-book   
should  be 
introduced at an early stage to   students   interested
in systems of algebraic equations. I
have never understood   the point in putting so much 
emphasis
upon   trivial   sheaf theory and
the subsequent  yoga about schemes  which
tend to hide 
relevant calculations.
See  Weil's  critical comments about these matters in 
the reprinted version of his text-book from 1962.


\bigskip

\centerline{\bf{The Zariski-Weil linear system.}}

\bigskip

\noindent
Let $k$ be a
subfield of ${\bf{C}}$ which is finitely generated
over $Q$ and
$\mathfrak{p}$  
a prime ideal in the polynomial ring
$k[t_1,\ldots,t_n]$ where 
$n\geq 2$.
Generic specialisations of $\mathfrak{p}$
consist of points
\[
\xi=(\xi_1,\ldots,\xi_n) \in {\bf{C}}^n
\]
with the property that
a polynomial $f(t)$ in $k[t]$ belongs to
$\mathfrak{p}$ if and only if
$f(\xi)=0$. This means
that
one simply evaluates
$f$ at the point $\xi\in{\bf{C}}^n$.
The existence of generic specialisations is not difficult to prove
and is explained in Chapter 1 in [Weil].
An invariant of $\mathfrak{p}$
is  the degree of 
trancendency of the field extension $k(\xi)$ over $k$, i.e. this degree does not depend upon
the chosen generic specialisation.
Moreover, if $d$ is the dimension of the algebraic set
$V=\mathfrak{p}^{-1}(0)$ in ${\bf{C}}^n$
then the degree of transcendency of $k(\xi)$ over $k$ is equal to
$d$. Put $p=n-d$
where we assume that 
\[
2\leq p\leq n-1
\]
Next, introduce $n$-vectors  
\[
 \bar \tau_k= (\tau^1_k\,\ldots,\tau_k^n)\quad\colon\, 1\leq k\leq p-1
\]
where
the doubly indexed family $\{\tau_\nu^i\}$
gives  $n(p-1)$ algebraically independent elements over $k(\xi)$.
Consider also a  $(p-1)$-tuple
$\lambda_1,\dots,\lambda_{p-1}$ 
where 
$\{\tau_\nu^i\}$ and $\{\lambda_\nu\}$ together give
$(n+1)(p-1)$ algebraically independent elements over $k$.
Now we find $n$-vectors $\zeta$ defined by
 \[ 
\zeta_i= \xi_i+ \sum_{k=1}^{k=p-1}\, \lambda_k\cdot \tau^i_k
\quad\colon\quad 1\leq i\leq n\tag{1}
\]
Denote by $K$  the field extension of $k$
generated
by the $n$-tuple $\{\xi_\nu\}$, the
$(p-1)$-tuple $\{\lambda_j\}$ and
the $n(p-1)$-tuple $\{\tau_\nu^i\}$.
Notice that $K$ 
contains the subfield $k(\zeta,\bar\tau)$
generated
by $\zeta_1,\ldots,\zeta_n$ and
$\bar\tau=\{\tau_\nu^i\}$. With these notations one has the result below whose detailed proof 
appears in
[Weil:Chapter 1]:

\medskip

\noindent
{\bf{1.2 Theorem.}}
\emph{The field $K$ is algebraic over the subfield $k(\zeta,\bar\tau)$
and the degree of trancendency of the last field over $k$
is equal to $np-1$.}

\bigskip



\noindent
With $n$ variables $\{z_\nu\}$
and arranging the $n(p-1)$ many trancendental 
$\tau$-variables as
$t=(t_1,\dots,t_{np-n})$,
Theorem 1.2. gives  an irreducible polynomial
$F(z,t)$ in $k[z,t]$
such that 
\[
F(\zeta,\bar\tau)=0
\]
We can express $F$ in the form:
\[ 
F(z,t)= \sum_{\nu=1}^{\nu=m}\, f_\nu(z)\cdot \phi_\nu(t)\tag{i}
\]
where $m$ is some positive integer, and
$\{f_\nu(z)\}$ are $k$-linearly independent in $k[z]$
while $\{\phi_\nu(t)\}$ are $k$-linearly inependent in the polynomial ring of
the  $n(p-1)$  many $t$-variables.
The  polar decomposition is not unique.
However,  the vector space
over $k$ generated by the $f$-polynomials in $k[z]$ does not depend upon the chosen 
polar representation of $F$. It is denoted by
$\mathcal W(\mathfrak{p})$ and called 
 the Weil-space attached to the prime ideal  $\mathfrak{p}$.
We also get  the complex vector space
\[
\widehat{\mathcal W}(\mathfrak{p})
={\bf{C}}\otimes_k\, \mathcal W(\mathfrak{p})
\]
Returning to the polynomialÊ$F(z,t)$ of
the $np$-many variables $(z,t)$
the constructions above
give the following.
When the $t$-vector is freezed to  a point   $t^*\in {\bf{C}}^{np-n}$
then the $\lambda$-polynomial
\[
\lambda\mapsto F(\xi+\lambda\cdot t^*,t^*)\tag{1.3}
\]
is identically zero, where $\lambda\cdot t^*$ is the
complex $n$-vector with components
\[
(\lambda\cdot t^*)_i=\lambda_1\cdot t_i+\lambda_2\cdot t_{i+n}+\ldots+\lambda_{p-1}\cdot t_{i+n(p-2)}
\]
With $t^*$ given while $\lambda$ varies over complex $(p-1)$-tuples
we get a subspace denoted by $\mathcal L(t^*)$ in ${\bf{C}}^n$
which consists of points $z=(z_1,\ldots,z_n)$ of the form
\[ 
z=(\lambda\cdot t^*)\quad\colon\quad \lambda\in {\bf{C}}^{p-1}
\]
With these notations
the vanishing of the $\lambda$-polynomial in (i) and
the fact that $\xi$ was a generic point, entails that
the polynomial
\[
z\mapsto F(z,t^*)
\]
is zero on the set-theoretic  sum
\[
V+\mathcal L(t^*)
\]
In other words,
\[
F(z+\lambda\cdot t^*)=0\quad\colon\quad z\in V\,\&\, \lambda\in {\bf{C}}^{p-1}\tag{1.4}
\]
Expressing $F$ by (i)
we have by (1.4)
\[
\sum_{\nu=1}^{\nu=m}\, \phi_\nu(t^*)\cdot f_\nu(z+\lambda\cdot t^*)=0
\quad\colon\quad z\in V\,\&\, \lambda\in {\bf{C}}^{p-1}\tag{1.5}
\]
In particular we can take $\lambda=0$ and hence
\[
\sum_{\nu=1}^{\nu=m}\, \phi_\nu(t^*)\cdot f_\nu(z)=0
\quad\colon\quad z\in V
\]
Above $t^*$ is arbitrary in
${\bf{C}}^{(n-1)p}$
and since the $\phi$-polynomials constructed via the polarization in (i) are linearly independent
ver $k$ his entails that $f_\nu(\xi)=0$
for every $\nu$, i.e. the $f$-polynomials belong to $\mathfrak{p}$.
We are going  to show that
the polynomial
$f_*(z)$ constructed in ¤ 0 
yields the requested Lech polynomial in the Main Theorem.





\newpage











\centerline{\bf{¤ 2. Proof of the Main Theorem}}
\bigskip

\noindent
From ¤ 1
we have the $m$-tuple $f_1,\ldots,f_m$ in $k[z]$  and construct the polynomial
$f_*$ as in (0.1). If it fails to be a Lech polynomial there exists a real sequence
$\{a_\mu\}$ in ${\bf{R}}^n$
which stays outside $V$ while
\[ 
\lim_{\mu\to \infty}\,
\frac{\text{dist}(\alpha_\mu, f_*^{-1}(0))}{
\text{dist}(\alpha_\mu, V)}=0\tag{2.0}
\]
We shall prove that this leads to a contradiction.
First. passing to a subsequence if necessary we may assume that
there exist the limits:
\[
d_\nu= \lim_{\mu\to \infty}\,
\frac{f_\nu(\alpha_\mu)}{\sqrt{f_*(\alpha_\mu)}}\tag{2.1}
\]
where we notice that the limit is taken over complex $m$-vectors of length one. So above
\[ 
|d_1|^2+\ldots+|d_m|^2=1
\]
From ¤ 1 we have the
polynomial $F(z,t)$  with  
its polar decomposition and put
\[
\phi_*(t)= \sum\, d_\nu\cdot \phi_\nu(t)\tag{i}
\]
Here $\phi_*(t) $ is not identically zero since
$\{\phi_\nu(t)\}$ are linearly independent and the $d$-vectors.
More precisely, there exists an $m$-tuple of freezed
vectors $t^*[k]$
such that the determinant of the $m\times m$-matrix with elements 
$\{\,\phi_\nu(t^*[k])\}$  is non-zero, and in addition
\[
\phi_*(t^*(k[)\neq 0\quad\colon\, 1\leq k\leq m \tag{ii}
\]
We get the polynomials
\[ 
g_k(z)= F(z,t^*[k])\quad\colon\, 1\leq k\leq m \tag{iii}
\]
Since
\[ 
\text{det}(\{\,\phi_\nu(t^*[k])\}\neq 0 
\]
It follows that the $g$-polynomials is a basis in the Weil space from ¤ xx.
At this stage we shall use Lech's Lemma from (0.2).
Namely, when (2.0) holds we find some $1\leq k\leq m$ such that
\[
\liminf_{\mu\to \infty}\,
\frac{\text{dist}(\alpha_\mu, g_k^{-1}(0)}{\text{dist}(\alpha_\mu,V)}=0\tag{*}
\]
Passing to a subsequence of the $\alpha$-sequence we may assume that
(*) holds as an unrestricted limit as $\mu\to \infty$
and there remains only to prove that this gives a contradiction
to get  Main Theorem.
To achieve this we consider the subspace $\mathcal L(t^*[k]$
and recall, from ¤ 1 that
$g_k(z)$ is zero on
\[
V+\mathcal L(t^*[k])
\]
Hence  
\[ 
\text{dist}(\alpha_\mu, g_k^{-1}(0))\geq 
\min_{z,\zeta}\, || \alpha_\mu-z-\zeta||\tag{2.2}
\]
where the minimum is taken over pairs $z\in V$ and $\zeta\in\mathcal L$.
Since $\text{dist}(\alpha_\mu,V))\leq |\alpha_\mu-z|$ for every $z\in V$, the
quotient in (*) therefore majorizes
\[
\min_{z,\zeta}\,\frac{||\alpha_\mu-z-\zeta||}{||\alpha_\mu-z||} \tag{2.3}
\]
Since $\mathcal L$ is a subspace the minimum is the same
as
\[
\min_{z,\zeta}\,||\frac{\alpha_\mu-z}{||\alpha_\mu-z||}-\zeta||\tag{2.4}
\]
Above we measure distances of unit vectors
$\frac{\alpha_\mu-z}{||\alpha_\mu-z||}$ to the subspace $\mathcal L$
and by the unrestricted limit in (*) it follows that (2.4) tends to zero when
$\mu\to \infty$.
Given $\epsilon>A$ we can therefore find
subspace $\mathcal L(\tau_\mu)$ in the Grassmanian $\mathcal G$
with distance $\epsilon$ from $\mathcal L(t^*[k]$ for large $\mu$, and points $z_\mu\in V$
such that 
\[
\frac{\alpha_\mu-z}{||\alpha_\mu-z_\mu||}\in \mathcal L(\tau_\mu)\implies
\alpha_\mu\in V+\mathcal L(\tau_\mu)
\]
The last inclusion gives
\[
0=F(\alpha_\mu,\tau_\mu)= \sum\, f_\nu(\alpha_\mu)\cdot \phi_\nu(\tau_\mu)\tag{2.5}
\]
We can divide the last sum by
$\sqrt{f_*(\alpha_\mu)}$. So with
\[
d_\nu(\mu)=\frac{f_\nu(\alpha_\mu)}{\sqrt{f_*(\alpha_\mu)}}
\]
it follows that
\[ 
\sum\, d_\nu(\mu)\cdot \phi_\nu(\tau_\mu)=0\tag{2.6}
\]
Here
\[ 
d_\nu(\mu)\to d_\nu\quad\&\quad
\tau_\mu\to t^*[k]
\]
as $\mu\to \infty$.
By continuity this implies that (2.6) contradicts there non-vanishing
expression from
(Ii)  which finishes our proof of the Main Theorem.











\end{document}




\newpage






\centerline{\bf{Appendix. Prime ideals and specialisations.}}

\bigskip

\noindent
Let us give a brief account of material from the cited text-book by Weil.
Denote by $\mathcal K$
the family of all 
subfields  of
${\bf{C}}$. Notice that
every such field contains
the rational number field
$Q$.
To each $k\in\mathcal K$
one has the  $k$-algebra
$k[t_1,\ldots,t_n]$ in $n$ variables.
Prime ideals in this commutative algebra
can be constructed as follows:
Let $\xi=(\xi_1,\ldots,\xi_n)$ be a point in ${\bf{C}}^n$.
Now  
we can evaluate polynomials
$p(t)\in k[t]$  at $\xi$ and the map 
\[ 
p(t)\to p(\xi)\tag{i}
\] 
is called a specialisation. Its kernel is obviously a prime
ideal in $k[t]$ which we denote
$\mathfrak{p}_\xi$.
If
$\mathfrak{p}_\xi=\mathfrak{p}_\eta$.
for a pair of distinct complex $n$-vectors $\xi$ and $\eta$
one says that
$\xi$ and $\eta$ are $k$-equivalent.
\medskip



\noindent
{\bf{A warning.}}
A polynomial $p(t)$ in $k[t_1,\dots,t_n]$ can be irreducible 
and yet
$p$ may be factorised in polynomial rings
over larger fields than $k$.
A first example occurs  when
$n=1$ and $k=Q$ where
the polynomial $p(t)= t^2+1$
is irreducible in
$Q[t]$
but if we take the field $k=Q(i)$ where
the imaginary unit is adjoined, then
$p(t)= (t-i)(t+i)$ has a factorisation in
$k[t]$. 
On the other hand, if $n=2$ 
then the polynomial
$p(t_1,t_2)= t_1\cdot t_2+1$
is  \emph{absolutely irreducible polynomial} 
which means that it stays irreducible in
$k[t_1,t_2]$ for every subfield $k$ of ${\bf{C}}$, i.e. $p$ is  even
irreducible
in 
${\bf{C}}[t_1,t_2]$. 
\medskip


\centerline{\bf{The existence of specialisations.}}
\medskip

\noindent
If $k$ is a field and $n\geq 1$ we denote by
$\text{Spec}(k;n)$ the family of all prime ideals in
$k[t_1,\ldots,t_n]$.
Each prime ideal $\mathfrak{p}$ in this spectral set
is equal to $\mathfrak{p}_\xi$ for some
$\xi\in{\bf{C}}^n$.
The proof relies upon Gauss' theorem which asserts that
the polynomial ring in $n$ variables over $k$
is a unique factorisation domain.
Since this  is  an essential result we
expose details and start with:
\medskip

\noindent
{\bf{The case of principal ideals.}}
Let $n\geq 2$ and $p(t)$ is an irreducible
polynomial in
$k[t_1,\ldots,t_n]$.
Gauss' theorem entails that
the principal  ideal generated by $p$ is a prime ideal.
If $p$ has some degree $m$ we  perform
a $k$-linear transformation on the vector space
$k^n$
which yields an obvious $k$-algebra isomorphism on
$k[t]$ and assume that
$p(t)$ is of the form
\[ 
p(t)= t_n^m+q_1(t')t_n^{m1}+\ldots+q_m(t')\tag{1}
\]
where the $q$-polynomials depend on $t'=(t_1,\dots,t_{n-1})$ and
$\deg q_j\leq j$ hold for each $j$.
To $p$ we associate the polynomial
\[
\frac{\partial p}{\partial t_n}= m\cdot t_n^{m-1}+\ldots
+q_{m-1}(t')
\]
Let $K=k(t_1,\ldots,t_{n-1})$ be the field of rational functions in
the $t'$-variables.
Gauss' theorem
entails that
$p$ regarded as an element in thr polynomial ring
$K[t_n]$ is irreducible and 
therefore the ideal in $K[t_n]$
generated
by
$p$ and its partial derivative
above is equal to $K([t_n]$. This gives
an equation
\[
S(t_n)\cdot p(t',t_n)+ R(t_n)\cdot \frac{\partial p}{\partial t_n}=1
\]
where $S(t_n)$ is a polynomial in $K[t_n]$ of degree
$\leq m-2$ and $R$ has degree $\leq m-1$.
Taking the product of denominators in the
$k[t']$-coefficients of $S$ and $R$ we find a non-zero polynomial
$\delta(t')\in k[t_1,\ldots,t_{n-1}]$
such that

\[ 
\delta(t')=
A(t_n)\cdot p(t',t_n)+ B(t_n)\cdot \frac{\partial p}{\partial t_n}\tag{i}
\] 
where $A$ and $B$  are polynomials in
the the $n$ many $t$-variables.
Let us then consider a point $\xi^*=(\xi_1,\ldots,\xi_{n-1})$
in
${\bf{C}}^{n-1}$ 
where  
$\xi_1,\ldots,\xi_{n-1}$ are \emph{algebraically independent} over
$k$.
This implies that 
$\delta(\xi^*)\neq 0$.
With $\xi^*$ chosen  we
consider the polynomial
$p(\xi^*,t_n)$ which  has degree $m$ in the variable $t_n$
with complex coefficients. The  fundamental theorem
of algebra
gives a factorisation
\[ 
p(\xi^*,t_n)=  \prod_{\nu=1}^{\nu=m}\, (t_n-\alpha_j)
\]
The equation (i) gives for each $\alpha$-root

\[
 \delta(\xi^*)=
 B(\xi^*, \alpha_j)\cdot \frac{\partial p}{\partial t_n}(\xi^*,\alpha_j)\tag{ii}
\]
Hence the $t_n$-derivative of $p(\xi^*,t)$ is $\neq 0$ at all these roots which
means that
they are simple, i.e. the complex numbers
$\alpha_1,\dots,\alpha_m$ are distinct.
Let us choose one of these simple roots, say $\alpha_1$
and put
\[ 
\xi=(\xi^*,\alpha_1)
\]

\medskip

\noindent
{\bf{Exercise.}}
Show that the
prime ideal $\mathfrak{p}_\xi$
in $k[t_1,\ldots,t_n]$ is equal to the principal
ideal generated
by $p$.
\bigskip

\noindent
\emph{Specialisations of arbitrary prime ideals.}
Let $\mathfrak{p}$ be non-zero in 
$\text{Spec}(k;n)$
where $n\geq 2$.
Let $m_*$ be the smallest integer such that
 $\mathfrak{p}$ contains a polynomial of degree $m_*$. 
 The case $m_*=0$ is excluded for then
 $\mathfrak{p}$ is the whole polynomial ring.
After a $k$-linear transformations we get an irreducible
polynomial
$p(t)\in\mathfrak{p}$ as above.
Now we consider the intersection
\[
k[t_1,\ldots,t_{n-1}]\,\cap \mathfrak{p}
\]
This is obviously zero or a prime ideal
in the polynomial ring with $n-1$ many variables.
Let $K$ be a field which contains $k$.
To each $\mathfrak p\in \text{Spec}(K:n)$ we put
\[
\mathfrak p\cap k[t_1,\ldots,t_n]
\] 
is prime ideal in the polynomial ring over $k$. Hence there
exists a map
\[
\text{Spec}(K:n)\to \text{Spec}(k:n)
\]
\medskip

\noindent
{\bf{Specialisations}}.
Following  [ibid: page 27]  a pair of
points $\xi$ and $\eta$ in ${\bf{C}}^n$
are generic
specialisations of each other with respect to a field
$k\in\mathcal K$ when their prime ideals are equal.
Next,
if
$\mathfrak{p}_\xi\subset\mathfrak{p}_\eta$
one says that $\eta$ is a specialisation of $\xi$ and write
\[ 
 \eta\leq_k \xi
\]
where the subscript indicates that the given field $k$ is taken into the account.

\medskip

\noindent
{\bf{1.1 The  linear system.}}
Let $\mathfrak{p}$ be a prime ideal in $k[t]$ and choose 
$\xi$  so that $\mathfrak{p}= \mathfrak{p}_\xi$.
Next, let $\lambda_1,\dots,\lambda_{p-1}$ and
$\{ \bar \tau= (\bar \tau_1\,\ldots,\bar \tau_{p-1}\,\colon 1\leq j\leq n \}$ 
be variables over $k$, i.e. the field generated by
these points has degree of trancendency $(n+1)(p-1)$ over $k$.
Above
$\bar \tau_k=(\tau_k^1,\ldots,\tau_k^n)$ are $n$-vectors for each 
$1\leq k\leq p-1$.
To each $1\leq i\leq n$ we set
\[ 
\zeta_i= \xi_i+ \sum_{k=1}^{k=p-1}\, \lambda_k\cdot \tau^i_k\tag{1}
\]
Witb $N=n+n(p-1)=np$  we obtain variable points
$(\zeta,\bar \tau)\in {\bf{C}}^N$
where we denote the coordinates by
$(\zeta,\tau )= (\zeta_1,\dots,\zeta _n, t_1,\ldots,t_{n(p-1})$
as coordinates.
\medskip

\noindent
{\bf{1.2 Theorem.}}
\emph{The prime ideal $\mathfrak{p}_{(\zeta,\tau)}$
in the polynomial ring
$k[\zeta,\tau]$
 is  principal. Moreover,
$\{\xi_j\}$and $\{\lambda_k\}$ belong to the algebraic closure 
of the field generated by
$k$ and 
$(\zeta,\tau)$.} 
In the sequely we prefer to use 
$z_\nu=\zeta_\nu$ and the $t$-letter for the $\tau$-variables.

\medskip

\noindent
{\bf{Remark.}} 
A detailed proof appears in Weil's text-book.
In the sequel we prefer to use 
$z_\nu=\zeta_\nu$ and the $t$-letter for the $\tau$-variables.
Theorem 1.2
gives  the irreducible polynomial
$F(z,t)$ of $N$-variables in the polynomial ring
$k[z,t]$ such that
$F(\zeta,\bar\tau)=0$
We can express $F$ in as  a sum
\[ 
F(z,t)= \sum_{\nu=1}^{\nu=m}\, f_\nu(z)\cdot \phi_\nu(t)\tag{i}
\]
where $\{f_\nu(z)\}$ are $k$-linearly independentin $k[z_1,\ldots,z_n]$
and $\{\phi_\nu(t)\}$ are $k$-linearly inependent in the polynomial ring of
the  $n(p-1)$  many $t$-variables.
The  polar decomposition is not unique.
However,  the vector space
over $k$ generated by the $f$-polynomials in $k[z]$ does not depend upon the chosen 
polar representation of $F$. It is denoted by
$\mathcal M$ and called 
 the Weil-space attached to the prime ideal  $\mathfrak{p}$.
Since $\xi$ is algebraic
of the field generated by $(\zeta,\tau)$ it follows that
\[ 
F(\xi,t)=\sum\, f_\nu(\xi)\cdot \phi_\nu(t)=0\quad\colon
\forall t\in {\bf{C}}^{N-n}\tag{*}
\] 
Since $\{\phi_\nu(t)\}$ are $k$-linearly independent it follows that 
$f_\nu(\xi)=0$ for each $\nu$, i.e. these  polynomials belong to $\mathfrak{p}$.




\medskip



\noindent
{\bf{An example.}}
The first non-trivial case arises when
$n=3$ and $\mathfrak{p}^{-1}(0)=S$ is a  curve.
An example is the non-singular curve
$S$ defined by 
\[
 S=\{(t,t^2,i\cdot t^3\}
\]
where $t$ moves in the complex field.
Norice that $S$ is defined by the equations
\[
z_2=z_1^2\quad\&\quad z_3=iz_1^3
\]
The distances between real points and $S$
behave in a rather irregular fashion.
For example, let $R$ be a large positive real number
and take the point $a=(0,0,R) $.
Now we seek a complex number $t$ so that
\[
\text{dist}(a:S)^2=
\min_t\, |t|^2+|t|^4+|R+it^3|^2\tag{i}
\]
It is clear that one should choose
$t$ so that $it^3$ is real and negative
which does not affect the first two terms, i.e. (i) becomes
\[
\min_x\, x^2+x^4+(R-x^3)^2\tag{ii}
\]
where $x$ are real and positive.
The reader may check that
the minimum behaves like  $R^{\frac{4}{3}}$.
One can continue to analyze
different directions as $a$ are real and get large
euclidian distances from the origin
in
${\bf{R}}^3$.
With this kept in mind it is not  obvious how to
prove that there exists a Lech polynomial $f_*$ in the ideal generated
by
$z_1-z_2^2$ and $z_3-iz_1^3$ which satisfies (*) in the Main Theorem.
The reader is invited to carry out  computations and 
find $f_*$  using the subsequent material
where a candidate to $f_*$ is obtained via
a certain polarization and the Weil-space attached to the prime ideal
generated by these two polynomials.




\bigskip


\noindent
{\bf{The local analytic case.}}
It is an open question if Lech's  result is valid
in
the local analytic case. Here  one starts with a prime ideal 
$\mathfrak{p}$ in
the local ring
$\mathcal O_n$ of germs of holomorphic functions at the origin in
${\bf{C}}^n$.
In a small polydisc $D^n$ we get the analytic set $V= \mathfrak{p}^{-1}(0)$
and one asks if there exists a pair 
$f\in\mathcal O(D^n)$ which vanishes on $V$
and a  constant $C$ as in the Main Theorem.







\end{document}