
\documentclass{amsart}
\usepackage[applemac]{inputenc}


\addtolength{\hoffset}{-12mm}
\addtolength{\textwidth}{22mm}
\addtolength{\voffset}{-10mm}
\addtolength{\textheight}{20mm}

\def\uuu{_}


\def\vvv{-}

\begin{document}



\centerline{\bf{Glimpses from work by Carleman}}


\bigskip


\centerline{\emph{Contents}}

\bigskip


\noindent
\emph{Introduction.}
\medskip


\noindent
{\emph{Appendix}}

\medskip

\noindent
\emph{A. Linear operators and spectral theory.}

\medskip


\noindent
\emph{B. Bounded normal operators on Hilbert spaces.}
\medskip


\noindent
\emph{C. Symmetric operators.}

\medskip


\noindent
\emph{D. Proof of Theorem 0.}
\medskip


\noindent
\emph{§ E. Fundamental solutions to second order
Elliptic operators.}


\newpage




\centerline
{\bf{Self-adjoint operators on Hilbert spaces.}}



\bigskip


\noindent
{\bf{Introduction.}}
The theory about
unbounded   self-adjoint operators on separable Hilbert spaces
was   developed by Carleman 
in the
monograph \emph{Sur les équations singulières à noyau
reèl et symmétrique} [Uppsala University. 1923].
Actually this work goes further since 
families of spectral functions
are constructed from a densely defined
and hermitian operator on a separable Hilbert space.
This general construction is for example used to study non-determined moment problems
where Carleman established several conclusive results. See § x below for further comments.
Apart from thr moment problem, special attention in [ibid]
is given
to 
operators on $L^2$-spaces defined by kernel functions.
As pointed out by Carleman  in the  introduction to [ibid], the solution to the 
Dirichlet problem for a double layer potential
where the boundary is not smooth leads to
singular operators where the earlier theory by Fredholm does not apply.
It goes without saying that Carleman was inspired by earlier work, foremost by 
Fredholm and Hilbert.
The need for extending the specteal theorem for bounded self-adjoint operators
was put forward at an early stage by Schmidt and Weyl.
Several results in [ibid]
treat extensions of results by the authors above.
In addition to the "pute operator theory", the whole analysis in
[ibid] also contains instructive facts in measure theory.
An example is the notion of absolutely continous linear operators on
$L^2[0,1]$ which was introduced by Hilbert
via certain measure theoretic assumptions on the integral kernel.
As we explain in § xx this
can be interpreated via the specteral theorem for unbounded self-adjoint operators
where the conclusive result relates Hilbert's conditions with
properties of their spectra.







\medskip

\noindent
{\bf{The
abstract version of the spectral theorem}}.
Here one starts with a restricted class of 
unbounded hermitian operators
which enjoy
the self-adjoint property.
Using 
Hilbert's spectral theorem for bounded self-adjoint 
operators and the classic 
calculus of resolvent operators 
by Carl Neumann, one easily gets the spectral 
theorem for
unbounded self-adjoint operators. A proof is given in my notes
devoted to functional analysis. 
A merit in the abstract  proof is that
it works on non-separable Hilbert spaces.
But in  most applications to PDE-theory one is content to dispose the 
spectral theorem for separable Hilbert spaces, and here the constructive 
ingredients in Carleman's work are helpful when one 
tries to decide if a given densely defined hermitian operator
is self-adjoint or not.
Every  separable Hilbert space is 
isomorphic to $\ell^2$ whose vectors are complex
sequences $\{c_p\}$ indexed by positive integers and
$\sum\, |c_p|^2<\infty$. Moreover,
up to unitary equivalence
every densely defined and hermitian operator $A$ on
$\ell^2$ is represented by an infinite matrix with elements $\{a_{pq}\}$
such that $a_{qp}= \overline{a_{pq}}$ and
\[
\sum_{q=1}^\infty\,| a_{pq}|^2<\infty\tag{i}
\]
hold for each $p$. 
The Cauchy-Schwarz inequality implies that if
$x\in \ell^2$ then the series
\[
\sum_{q=1}^\infty\,a_{pq}\cdot x_q
\] 
is absolutely convergent for each $p$
and if $y_p$ is the  sum 
we obtain a vector
$y=(y_1,y_2,\ldots)$.
However, (i) need not imply that
$y$ belongs to $\ell^2$.
So in general we find a densely defined but unbounded operator
$A$ whose domain of definition consists of vectors
$x\in\ell^2$ such that
\[
\sum_{p=1}^\infty\,|\sum_{q=1}^\infty\,a_{pq}\cdot x_q|^2<\infty
\]
The favourable self-adjoint case occurs if the equations
\[
Ax=i\cdot x\quad\colon\, Ax=-i\cdot x\tag{ii}
\]
have no non-zero solutions.
Under this hypothesis there exists a spectral resolution of $A$
with similar properties as for bounded self-adjoint operators.
In Carleman's work one refers to $A$ as a Class I-operator when
(ii) have no non-zero solutions.
Let us remark that one does not know a general criterion in order that
a Hermitian matrix $A$ satisfying (i) is of Class I.
It appears to be a very difficult problem and
I suspect that no general necessary and sufficient condition is available.
The difficulty can already be explained via the moment problem by Stieltjes,
as well as the extension by Hamburger.
Here one considers a pair of real sequences $\{a_p\}$ and
$\{b_p\}$ where each  $b_p>0$ and the matrix
is given by
\[ 
A= xxxx
\]
A major result in Carleman's  theory is that
this symmetric matrix gives a Class I-operaotre if and only if
the associated  moment problem is determined.
We refer to § xx for an account about th moment problem and here we only mention that
a sufficient condition for $A$ to be self-adjoint is that
\[
\sum_{p=1}^\infty\, \frac{1}{b_p}=+\infty
\]
However, examples show that
the series may converge and while $A$ still is self-adjoint.
So conditions for a matrix in (x) to be self-adjoint
relies upon subtle arithmetic condtions during exansions into
continued fractions where we recal,that 
a major theorem due to Stieltjes assets that the moment problem is 
determined if and only if
the expansion in continued fractions is convergent.
But in spite of this elegant fact, it is in practice not easy to
decide  this convergence.
\medskip

\noindent
Passing to PDE-operators
the spectral theorem is very useful.
Again one encounters an initial problem, i.e. to decide when
a densely defined PDE-operator is self-adjoint or not.
An example is the Bohr-Schrödinger operator
\[
P= \delta+c(x)
\] 
where $\Delta$ is the Laplce operator in
${\bf{R}}^3$
and $c(x)$ a real-valued and locally square integrable function.
To begin with $P$ is defined on test-functions and 
here the symmtriy holds by Green's equation, i.e.
\[
\int\, P(f)\cdot \overline{g}\, dx=
\int\, f\cdot \overline{P(g)}\, dx
\] 
for every  pair of test-functions.
The question arises when $P$ extends to a densely defined 
self-adjoint operator.
The following sufficiency result was proved by Carleman in 
his lectures at Sorbonne 1930 and appears to
be the sharpest known result up to the present date:
\medskip

\noindent
{\bf{Theorem.}}
\emph{$P$ has a self-adjoint extension if there exists a constant $M$ such that}
\[ 
\limsup_{|x|\to \infty}\ c(x)\leq M
\]

\newpage


\centerline{\bf{The construction of spectral functions.}}

\medskip


\noindent
We shall expose material from Chapter I in [ibid].
Here various measure theoretic considerations appear.
Sime readers may prefer an "abstract theory" but in reality the
condtrucutve ingredients below are useful when one wants to apply
the general theory to
special integral operators which for example appear in double layer
potentials where irregular boundaries occur.
To make the presentstion more teransparent we shall
restrict the atrnetion to a case
where
certain "ugly nullsets" are given in a rather concrete way.
Let us recall  that every separable Hilbert space
is isomorphic to $L^2[0,1)$ whose vectors are complex-valued and square
integrable functions on the unit interval. To avoid too many notations we consider
real and symmetric kernels below and remark only that
the whole analysis can be carried out in a similar fashion for hermitian kernels.
To begin with
we have the class of symmetric Hilbert-Schmidt operators
which arise as follows.
Let $G(x,y)$ be a real-valued and   Lebesgue measurable function on
$[0,1]^2$ such that
\[
G(y,x)=G(x,y)\quad \colon
\iint\, |G(x,y)^2\, dxdy<\infty\tag{i}
\]
When (i) holds it follows from basic Lebesgue theory
that
$G(x,y)$ yields a bounded  linear operator
$\mathcal G$ defined on
$L^2[0,1)$ by
\[
\mathcal G(f)(x)=\int_0^1\, G(x,y)\cdot f(y)\, dy
\]
More precisely, the Cauchy-Schwarz inequality entails that
the operator norm of
$\mathcal G$ is bounded above by
\[
\sqrt{\iint\, G(x,y)^2\, dxdy}
\]
Moreover, there exists a sequence of eigenfunctions
$\{\phi_\nu(x)\}$ 
which are pairwise  orthogonal and normalised with $L^2$-norms equal to one
and
\[
\phi_\nu=\lambda_\nu\cdot \mathcal G(\phi_\nu)
\]
Baic Lebesgue theory shows that
each eigenfuntion is continuos on $[0,1]$.
The symmetry of $G$ implies that
$\{\lambda_\nu\}$ are non-zero real numbers
which may be $>0$ or $<0$. Moreover, it is wellknown that
$\mathcal G$ is a compact operator which implies that
the set of eigenvalues  over each bounded interval $[-\ell,\ell]$
is finite.
The spectral function associated to $\mathcal G$ is defined 
for pairs $x,y$ in $[0,1]^2$ and
each real $\lambda$ by:
\[
\theta(x,y;\lambda)=\sum_{0<\lambda_\nu<\lambda}
\phi_\nu(x)\phi_\nu(y)\quad\colon \lambda>0
\]
\[
\theta(x,y;\lambda)=-\sum_{\lambda <\lambda_\nu<0}
\phi_\nu(x)\phi_\nu(y)\quad\colon \lambda<0
\]
Keeping $x$ and $y$ fixed
we have the function
\[
\lambda\mapsto \theta(x,y;\lambda)
\]
It has jump discontinuites  at the spectral values
but we can control it total variation in a uniform way.
For let $(-\ell,\ell)$ be a bounded open interval.
The total variation of
(i) over this interval becomes
\[
\sum_{-\ell<\lambda<\ell}\, |\phi_\nu(x)\phi_\nu(y)|=
\sum_{-\ell<\lambda<\ell}\, |\lambda_\nu|^2
\sqrt{\int_0^1\,G(x,s)\phi_\nu(s)\, ds}\cdot 
\sqrt{\int_0^1\,G(y.s)\phi_\nu(s)\, ds}
\]
Above  $\lambda_|nu^2\leq \ell^2$ hold for each $\nu$. Moreover,
since the eigenfun ctons are orthonormal, Bessel's inequality gives
\[
\sum_{-\ell<\lambda<\ell}\,
\sqrt{\int_0^1\,G(x,s)\phi_\nu(s)\, ds}\leq  
\sqrt{\int_0^1\,G(x,s)^2\, ds}
\] 
and similary with $x$ replaced by $y$.
Hence the total variation of (*) over $(-\ell,\ell)$ 
is majorised by
\[
\ell^2\cdot 
\sqrt{\int_0^1\,G(x,s)^2\, ds}\cdot 
\sqrt{\int_0^1\,G(y,s)^2\, ds}
\]
\medskip

\noindent
{\bf{Unbounded symmetric kernels.}}
Let $K(x,y)$ be a real-valued Lebegue measurable function on
$[0,1]^2$ which is symmetric and 
\[
\int_0^1\, K(x,y)^2\, dy<\infty\tag{ii}
\]
hold for all $x$ outside a nullset $\mathcal N$.
Notice that (ii) implies that
if $g\in L^2[0,1]$ then the integrals
\[
\int_0^1\, K(x,y)\cdot g(y)\, dy
\]
converge absolutely for all $x$ outside $\mathcal N$.
Indeed, this is clear from the Cauchy-Schwarz inequality.
So (ii) yield an almost everywhere defined function
denoted by $\mathcal K(\phi)$.
We shall restrict the attention to the case when
$\mathcal N$ is a denumerable set $\{\xi_k\}$
whose number of cluster points in $[0,1]$ is finite.
In addition we assume that there exists a finite subset
$\eta_1,\ldots,\eta_m$ of these $\xi$-numbers such that
for every $|delta>0$
it holds that
\[
J(\delta)=\iint_\delta  K(x,y)^2\, dxdy<\infty
\]
where the integration takes place over
the product of $0\leq x\leq 1$ and the
part of the unit $y$-interval for which
$|y-\eta_k|\geq\delta$ hold for every $k$.
But no uniform bound is imposed on these integrals, i.e.
$J(\delta)$ may increase to $+\infty$ when $\delta\to 0$.
Denote by $I_*(\delta)$ the part of $[0,1]$ where
$\delta$-intervals around $\eta_1,\ldots,\eta_m$ have been removed.
define the kernel function $K_\delta(x,y)$
which is zero
outside $I_*(\delta)\times I_*(\delta)$ and equal to
$K(x,y)$ on this product set.
Then it is clear that
$K_\delta(x,y)$ is a Hilbert-Schmidt kernel
and we get its associated spectral function
to be denoted by $\theta_\delta(x,y;\lambda)$.
\medskip

\noindent
{\bf{Spectral functions of $K$.}}
In the $[0,1]^2$ we remove the
union of the lines $\{x=\xi_\nu\}$ and 
 $\{y=\xi_\nu\}$ and 
obtain a subset denoted by $D$.
Since the $\xi$-points only have a finite set of cluster points
 there exists a finite family of open and disjoint rectangles
 which together with their boundaries cover $[0,1]^2$
 and inside each rectangle the number
of removed lines is locally finite.
Using this one get the following:

\medskip

\noindent
{\bf{Proposition.}} 
\emph{
Let $D_*$ be a  compact subset of $D$ and $\ell>0$.
Then there exists some $\delta_*>0$
such that  family $\{\theta_\delta(x,y;\lambda)\,\colon\, 0<\delta\leq \delta_*
\,\colon -\ell<\lambda<\ell\}$
restrict to an equicontinuous family of  functions on
$D_*$.
Moreover, the total variations of}
\[
\lambda\mapsto \theta_\delta(x,y;\lambda)
\]
over $(-\ell,\ell)$
are bounded by a constant $M$ which is independent of the points
$(x,y)\in D_*$ and $\delta\in (0,\delta_*)$.
\bigskip


\noindent
{\bf{Exercise.}} Prove this  via the previous results. If necessary, consult
page 27-29 in [ibid] for details.
Next, using the Arzela-Ascolli theorem for equicontoinuous families 
it follows from the above that there exist
sequences $\{\delta_\nu\}$ which tends to zero
and 
a limit function $\theta(x,y:\lambda)$ where
\[
\lim\, \theta_{\delta_\nu}(x,y;\lambda)=\theta(x,y:\lambda)
\]
holds when $(x,y)\in D$ and every real $|lambda$. 
Moreover, this convergence holds uniformly over
compact subsets of $D$  while $\lambda$ stays in a bounded interval.
The limit funftion 
$\theta(x,y:\lambda)$ in $D$ is symmetric in $x$ and $y$ and 
\[
\lambda\mapsto \theta(x,y:\lambda
\] 
has bounded variation over each finite $\lambda$-interval.
\medskip

\noindent
A limit function $\theta(x,y;\lambda)$
found as above is called a specteal function associated to $K$.
We remark that in general there exists several spectral functions 
which  arise from different
$\delta$-sequences which tend to zero.
However, it turns out that every spectral function
can be used to recover action by the unbounded kernel $K$.
\medskip

\noindent
{\bf{Properties of spectral functions.}}
A number of results appear in [ibid: page 28-51] which
can be seen as generalisations of the Hilbert-Schmidt theory.
To begin eith we notice that
while we stsy with Hilbert-Schmidt kernels then
\[
|\int_0^1\, \theta_\delta(x,s;\lambda)
\theta_\delta(s,y;\lambda)|, ds\,|=
| \theta_\delta(x,y;\lambda)|
\]
Wirh $x=y$ it follows that
\[
\int_0^1\, \theta_\delta(x,s;\lambda)^2\, ds\leq | \theta_\delta(x,y;\lambda)|
\leq |\lambda|^2\cdot K^*(x)^2
\]
Since thi hold for every $\delta>0$ it follows after a passag to thr,omit that
each spectral function satisfies
\[
\int_0^1\, \theta(x,y;\lambda)^2\, dy\leq | \theta(x,x;\lambda)|
\leq |\lambda|^2\cdot K^*(x)^2
\]
Hence the function
$y\mapsto   \theta(x,y;\lambda)$ is square integrable with respect to $y$ for
every $x$ outside the denumerable set of $\xi$-points.




 
 
 
 











Now one gets the subspace
of $L^2[0,1]$ for which 
$\mathcal K(\phi)$ is square integrable.
It is denoted by $\mathcal D(\mathcal K)$
and a crucial fact is that it is dense in the Hilbert space
$L^2[0,1]$.
To see this we define for each positive integer  $N$ the set
\[
E_N=\{ x\,\colon\, \int_0^1\, K(x,y)^2\, dy\leq N
\]
They increase with $N$ and their union is
$[0.1]\setminus\mathcal N$.
For each $N\geq 1$ we obtain a Hilbert-Schmidt kernel
$G_N(x,y)$ which is zero if $x$ or $y$ is outside $E_N$ while
\[
G_N(x,y)=K(x,y)\quad\colon\, (x,y)\in E\times E
\]
Notice that $\{G_N\}$ converge weakly  to $K$ in the sense that
\[
\lim_{N\to\infty}\, \int_0^1\, [G_N(x,y)-K(x,y))^2=0
\quad\colon x\in [0,1]\setminus\mathcal N
\]





Let us  resume how this goes before we discuss further material in
[ibid].
Let 
$\mathcal H$ be a complex Hilbert space
and $A\colon \mathcal H\to \mathcal H$
is densely defined and hermitian. It  means that
\[
\langle Ax,y\rangle=
\langle x,Ay\rangle\tag{i}
\] 
hold for each pair of vectors in
$\mathcal D(A)$.
Now $A$ has a graph
\[
\Gamma(A)=\{(x,Ax)\,\colon\, x\in \mathcal D(A)\}
\]
Using (i) one easily verifes that if
the graph is not closed, then
we one construct an extended operator $B$
whose graph is the closure of
$\Gamma(A)$ and $b$ satsifies (i).
Replacing $A$ by $B$ if necessary we restrict
the attentiont to densely defined hermitian operators with a closed graph.
Guven a vector $x\in\mathcal H$ we consider the equation
\[
Ay=i\cdot y+x\tag{ii}
\]
where $i$ is the imaginary unit.
It turns out that (ii) has at least one solution
given by a vector $y\in\mathcal D(A)$ and Bessel's inequality gives
\[
||y||\leq ||x||
\]
for every such $y$.
In § xx we give an example of an operator $A$ for which
the equation
\[
Ay=i\cdot y
\]
has a non-zero solution.
When this occurs there exist seveeral different spectral functions associated to $A$
and the whole study becomes quite involved. For the moment we ignore this and
assume that
(ii) has a unique solution for every $x$.
Then (xx) gives a bounded linear operator $R$
such that
$Rx=y$. It means that the range of $R$ is equal to
$\mathcal D(A)$ and the composed operator
\[
R\circ(A-iE)(y)= y\quad\colon\, y\in \mathcal D(A)
\]
We also notice that
\[
(A-iE)\circ R(x)= x \quad\colon\, x\in \mathcal H
\]
Next, we can consider the equation
\[
Ay=-i\cdot y
\]
It it has no non-zero solution we find as above a bounded linear operator
$S$ such that
\[
S\circ(A+iE)(y)= y\quad\colon\, y\in \mathcal D(A)
\]
\[
(A+iE)\circ S(x)= x \quad\colon\, x\in \mathcal H
\]
From these equations one easily derives that
the adjoint $R^*$ is equal to $S$. Moreover, by Neumann's calculus
for resolvent opertors it follows that $R$ and $R^*$ commute, i.e.
$R$ is a normal operator.
Moreover, one shows via general results from § xx that
the spectrum of $A$ is confined to the real line while
$|sigma(R)$ is contined in the circle
\[
\mathcal C=\{\lambda\,\colon\, |\lambda+i/2|= 1/2\}
\]
At this stage we apply Hilbert's spectral theorem for bounded normal operators.
It gives a  map
\[
\mu\colon \mathcal H\times\mathcal H\to \mathfrak{M}(\mathcal C)
\]
where 
$\mathfrak{M}(\mathcal C)$ is the space of complex-valued Riesz measures on
the compact set  $\mathcal C$.
So to each pair $x,y$ in $\mathcal H$ one assigns a measure
$\mu_{x,y}$.
Moreover, Neumann's operational calculus 
gives for each bounded Borel function $g$ on $\mathcal C$
a bounded linear operator $G$ on $\mathcal H$ such that
\[
\langle Gx,y\rangle=\int_{\mathcal C}\, g(\lambda)\, 
\mu_{x,y}(\lambda)
\]
Moreover, the spectrum $\sigma(G)$ is contained in the closure of the range of $g$.
In particular we consider a closed Borel set $e$ in $\mathcal C$
which does not contain
$\lambda=0$.
Now
\[
g(\lambda)=\chi_e(\lambda)\cdot\frac{1-i\lambda}{\lambda} 
\]
is a bounded Borel function which yields 
a bounded opertor
$G$ as above.
With $\lambda= -i/2+\zeta$ 
where the absolute value $|\zeta|=1/2$
we get
\[
\frac{1-i\lambda}{\lambda}=
\frac{1/2-i\zeta}{ -i/2+\zeta}=\frac{(1/2-i\zeta)(i/2+\bar\zeta)}
{|\zeta-i/2|^2}=\frac{\mathfrak{Re}(\zeta)}{|\zeta-i/2|^2}
\]
Since $e$ deos not contsin zero we see that
(x) gives a bounded and real-valued function which via Neumann's operational calculus
correspnids to a normal and bounded operator $G$ whose spectrum is real.
Since a normal operatoer with real spectrum is self-adjoint, it follows
that $G$ is self-adjoint.























Let us first remark that every separable Hilbert space
is isomorphic to $L^2[0,1)$ whose vectors are complex-valued and square
integrable functions on the unit interval.
The starting point in [ibid]
was Hilbert's earlier studies of
Hermitian and bounded operators on
$L^2[0,1)$.
Among these occur the class of Hilbert-Schmidt operators which arise when
$G(x,y)$ is a Lebesgue measurable function on
$[0,1]^2$ such that
\[
G(y,x)=\overline{G(x,y)}\quad \colon
\iint\, |G(x,y)|^2\, dxdy<\infty\tag{i}
\]
A special case occurs when
$G$ us real-valued and then
the first equation above means that this kernel is symmetric, i.e.
$G(y,x)=G(x,y)$.
When (i) holds it follows from basic Lebesgue theory
that
$G(x,y)$ yields a bounded  linear operator
$\mathcal G$ defined on
$L^2[0,1)$ by
\[
\mathcal G(f)(x)=\int_0^1\, G(x,y)\cdot f(y)\, dy
\]
More precisely, the Cauchy-Schwarz inequality entails that
the operator norm of
$\mathcal G$ is bounded above by
\[
\sqrt{\iint\, |G(x,y)|^2\, dxdy}
\]
More generally, let $K(x,y)$ be a real-valued Lebegue measurable function on
$[0,1]^2$ which is symmetric and 
\[
\int_0^1\, K(x,y)^2\, dy<\infty\tag{ii}
\]
hold for all $x$ outside a nullset $\mathcal N$.
Notice that (ii) implies that
if $g\in L^2[0,1]$ then the integrals
\[
\int_0^1\, K(x,y)\cdot g(y)\, dy
\]
converge absolutely for all $x$ outside $\mathcal N$.
Indeed, this is clear from the Cauchy-Schwarz inequality.
So (ii) yield an almost everywhere defined function
denoted by $\mathcal K(\phi)$.
Now one gets the subspace
of $L^2[0,1]$ for which 
$\mathcal K(\phi)$ is square integrable.
It is denoted by $\mathcal D(\mathcal K)$
and a crucial fact is that it is dense in the Hilbert space
$L^2[0,1]$.
To see this we define for each positive integer  $N$ the set
\[
E_N=\{ x\,\colon\, \int_0^1\, K(x,y)^2\, dy\leq N
\]
They increase with $N$ and their union is
$[0.1]\setminus\mathcal N$.
For each $N\geq 1$ we obtain a Hilbert-Schmidt kernel
$G_N(x,y)$ which is zero if $x$ or $y$ is outside $E_N$ while
\[
G_N(x,y)=K(x,y)\quad\colon\, (x,y)\in E\times E
\]
Notice that $\{G_N\}$ converge weakly  to $K$ in the sense that
\[
\lim_{N\to\infty}\, \int_0^1\, [G_N(x,y)-K(x,y))^2=0
\quad\colon x\in [0,1]\setminus\mathcal N
\]
\medskip

\noindent
Next, for each fixed $N$ the Hilbert-Schmidt theory
entails
that $\mathcal G_N$ is a compact operator whose spectrum is
real and discrete outside $\lambda=0$.
More precisely,
there exists a sequence of  real numbers
$\{\mu^{(N)}_\nu\}$ arranged with non-decreasing absolute values
and a sequence of pairwise orthonormal  
and real-valued functions
$\{\phi_\nu^{(N)}\}$ in $L^2[0,1]$ such that
\[
\mathcal G_N(\phi_\nu^{(N)})=\frac{1}{\mu^{(N)}_\nu}\cdot \phi^{(N)}_\nu
\]
Here $|\mu^{(N)}_\nu|\to +\infty$ as $\nu$ increases.
Following Hilbert one introduces
spectral kernels for bounded intervals as follows:
If $0<a<b$ we set
\[
\theta_N(a,b;x.y)=
\sum_{a\leq \mu^{(N)}_\nu<b}\,
 \phi^{(N)}_\nu(x) \phi^{(N)}_\nu(y)
 \]
Similarly, if $0<c<d$ then
\[
\theta_N(-c,-d;x.y)= 
\sum_{-d\leq \mu^{(N)}_\nu<-c}\,
 \phi^{(N)}_\nu(x) \phi^{(N)}_\nu(y)
\]
Keeping an interval $[a,b]$ fixed with $0<a<b$
we get a linear  operator which sends
$h\in L^2[0,1]$ to
\[
E_N[a,b](h)= \int_0^1\, \theta_N(a,b;x.y)\cdot h(y)\, dy
\]
This operator s bounded because $h$ can be written
as
\[
h(y)= \sum_{a\leq \mu^{(N)}_\nu<b}\,a_\nu\cdot
\phi^{(N)}_\nu(y)+h^*(y)
\]
where
$h^*(y)$ is $\perp$ to the linear space $\Pi_N$
generated
by the  finite set of eigenfunctions
$\{\phi^{(N)}_\nu\,\colon a\leq \mu^{(N)}_\nu<b\}$
while
\[
a_\nu=\int_0^1\, \,\phi^{(N)}_\nu(y)\cdot h(y)\, dy
\]
Bessel's inequality entails that the operator in (x) has norm $\leq 1$.
Notice also that $E_N[a,b]$ is the self-adjoint projection
operator from
$L^2[0,1]$ onto $\Pi_N$.
The question arises if these $E$-operators converge.
More precisely, keeping $[a,b]$ fixed
we ask if there exists a bounded linear operator $E_*[a,b]$ such that
\[
\lim_{N\to\infty}\, E_N[a,b](h)=E_*[a,b](h)
\] 
hold for each $h\in L^2[0,1]$, where the limit is 
taken in the weak sense, i.e.
\[
\lim_{N\to\infty}\,\int_0^1\,E_N[a,b](h)(y)\cdot g(y)\, dy=
\int_0^1\,E_*[a,b](h)(y)\cdot g(y)\, dy
\] 
hold for each pair of $L^2$-functions.
A similar limit can be impoed when we 
instead consider intervals $[-d,-c]$.
\medskip

\noindent
{\bf{Class I kernels.}}
Returing to the kerenl $K(x,y)$ one considers the integral equation
\[
\int_0^1\, K(x,y)\cdot \phi(y)\,dy= i\cdot \phi(x)
\]
where $i$ is the imaginry unit.
If it has no non-zero solution $\phi$ one says that
$K(x,y)$  is of Class I.
A major result in Carlemans work goes as follows
\medskip


\noindent
{\bf{Theorem.}} \emph{If $K(x,y)$ is of class I then
the opertor valued seences $\{E_N[a,b]\}$ and
$\{E_N[-d,-c]\}$ converge weakly for all bounded
intervals. Moreover, for each
$h\in\mathcal D(\mathcal K)$ one has
the integral formula}
\[
\mathcal K(h)=
\lim_{\delta\to 0}\, \bigl[\int _{-1/\delta}^{-\delta}\, \lambda^{-1}\cdot \frac{d}{d\lambda}(E_*(h)+
\lim\int _{\delta}^{1/\delta}\,  \lambda^{-1}\cdot \frac{d}{d\lambda}(E_*(h)\,\bigr]
\]
\medskip


\noindent
{\bf{Remark.}}
Above appears Stieltjes' integrals. For example,
\[
\int _{\delta}^{1/\delta}\, \frac{d}{d\lambda}(E_*(h)=
\lim\, \sum_{\nu=0}^{\nu=M}\, E_*[s_\nu,s_{\nu+1})](h)
\]
where the limit is taken over sequences
\[
\delta=s_0<s_1<\ldots<s_M=1/\delta\quad\colon 
\max(s_{\nu+1}-s_\nu)\to 0
\]
The domain of definition for $\mathcal K$ is also fully described by
the spectral resolution defined by the $E_*$-operators.
More precisely, an $L^2$-function $h$ belongs to
$\mathcal D(\mathcal K)$ if and only if there exists a constant
$C$ such that

\[
\sum_{\nu=0}^{\nu=M}\,\bigl[\,  ||E_*[-s_{\nu+1},-s_\nu)](h)||+
\sum_{\nu=0}^{\nu=M}\, ||E_*[s_\nu,s_{\nu+1})](h)||\,\bigr]\leq C
\]
hold for every finite sequence $0<s_<s_1<\ldots s_M$, where the norms are taken in 
$L^2[0,1]$. So the integrals which appear in the right hnd sid in
Theorem xx are absolutely convergent with respect to the norm in
$L^2[0,1]$.
\medskip


\noindent
{\bf{The closure property.}}
Let $K(x,y)$ be of class I. For each $h\in L^2[0,1]$
we putconsider the integrals
\[
h_\delta=
\int _{-1/\delta}^{-\delta}\, \frac{d}{d\lambda}(E_*(h)=+
\int _{\delta}^{1/\delta}\, \frac{d}{d\lambda}(E_*(h)
\]
The question arises if 
\[
\lim_{\delta\to 0}\, h_\delta=h
\]
Here one may refer to a weak limit in
$L^2[0,1]$ or impose the stronger condition that
the $L^2$-norms
$||h_\delta-h||\to 0$.
One says that $K$ has the closure property when
(xx) holds.
In most applicstions one encounters
Class i operators which enjoy the closure property. But
in specific situations  one is obliged to check if (x) is valid or not.
\medskip


\noindent
{\bf{Further results.}}
A central issue is to determine when
a given symmetric kernel $K$ is of Class I.
No general necessary and sufficient condition exists, and it is unlikely
that such a  criterion exists.
But is is of interest to search for sufficient conditions.
several results which give sufficient  conditions appear in Carleman's work.
Among these occur criteria via iterated kernels.
Given $K$ we set
\[
K^{(2)}(x,y)= \int_0^1\, K(x,s)K(s,y)\,ds
\]
Since $K$ is symmetric this is the same as
\[
\int_0^1\, K(x,s)K(y,s)\,ds
\]
and we notice that the Cauchy-Schwarz inequality entails that
this integral taken with respect to $s$
is absolutely convergent when both $x$ and $y$ are 
outside the nullset $\mathcal N$.
For a further study of these iterated kernels and how they
are used to determine when $K$ is of Class I we refer to § xx.
























 









Further examples which emerge from
this work appears in  his
lecture from [Comptes rendus du $VI^e$  Congrés des
Mathématiques Scandinavies. Copenhagen 1925].
 
\medskip


\noindent
After Carleman's pioneering work,
hundreds of  text-books and thousands of articles
have treated 
spectral theory for unbounded
self-adjoint operators.
But the basic material is  covered in [ibid]
and to this 
I would like to add a personal comment. Even though
"abstract methods" in mathematics 
often are  useful, one only becomes truly familiar
with the "source" of a subject
after  executing 
explicit computations. From this point of view [ibid]
appears as an outstanding text about
unbounded linear operators on Hilbert spaces which in addition to
 theoretic results
contain several 
concrete applications   exposed with  
detailed and   very  elegant  proofs.
At the same time specific situations illustrate how to perform the 
pasage to limits which are taken in various weak topologies.
We shall   
describe some of the major results from [ibid] and begin with
a specific case which
illiustrates the flavour of the general theory.

\bigskip


\noindent
{\bf{Propagation of sound}}.
With $(x,y,z)$ as space variables in
${\bf{R}}^3$ and a time variable $t$, the 
propagation of sound
in the infinite  open complement $U={\bf{R}}^3\setminus \overline{\Omega}$
of a bounded open subset $\Omega$ is governed by
 solutions $u(x,y,z,t)$ to the wave equation
 \[ 
 \frac{\partial^2 u}{\partial t^2}= \Delta u\tag{1}
 \] 
 where 
 $\Delta$ is the Laplace operator in $x,y,z$.
So here (1) holds when
$p=(x,y,z)\in U$
and $t>  0$. We  assume that
$\partial\Omega$ is of class $C^1$, i.e. given as  a union of pairwise disjoint
closed surfaces of class $C^1$ along which normal vectors are defined.
We seek solutions 
such that
$p\mapsto u(p,t)$ belong to $L^2(U)$ for each $t$,
and the outer normal derivatives
taken along $\partial\Omega$ are zero,  i.e. for every $t>0$ 
\[
\frac{\partial u}{\partial n}(p,t)=0\quad\colon p\in \partial \Omega\tag{2}
\]
In addition
to this $u$ satisfies initial conditions
expressed 
by  a pair of $C^2$-functions
$f_1x,y,z)$ and $f_2(x,y,z)$ defined in $U$ such that the four functions
$f_1,f_2,\Delta(f_1,\Delta(f_2)$  belong to $L^2(U)$,
and the outer normal derivatives of $f_1$ and $f_2$ are
zero.
\medskip


\noindent
{\bf{Theorem.}}
\emph{To each pair $f_1,f_2$ satisfyinfg the conditions above
there exists a unique solution $u$ which satisfies
(1-2) and the initial conditions
$u(p,0)= f_0(p)$ and $\frac{\partial u}{\partial t}(p,0)= f_1(p)$.}
\medskip


\noindent
This theorem is proved  in [ibid: page 174-185].
Apart from the conclusive result the
methods in the proof are very instructive and relies upon
the construction of a spectral function to a certain densely defined and
self-adjoint operator
$A$ acting on the Hilbert space $L^2(U)$.
In this way the proof 
boils down to solve the ordinary Dirchlet problem in
the exterior domain
$U$ and after $A$ is found via a kernel given by a Greens function.
In § xx we explain in detail that the unique solution $u$ for a given pair $f_1,f_2$ is
is given by
\[
u=\int_0^\infty\, \cos(\sqrt{\lambda}\cdot t)
\cdot \frac{d}{d\lambda}\Theta(\lambda)(f_1)+
\int_0^\infty\, \frac{\sin(\sqrt{\lambda}\cdot t)}{\sqrt{\lambda}}
\cdot \frac{d}{d\lambda}\Theta(\lambda)(f_2)\tag{*}
\]
where $\Theta(\lambda)$ is the spectral function
of $A$.
In addition to this, Carleman proved that
the spectral function is absolutely continuous with respect to
the parameter $\lambda$ andused this to prove that the first order partial derivatives 
of $u$ with respect to the space variables $x,y,z$, tend to zero
as $t\to +\infty$.
This was already  expected by physical reasoning. But the confirmation
via the theorem above
is of course satisfactory.
So Carleman's pioneering work
pointed out the usefulness of spectral theory for unbounded
self-adjoint operators on Hilbert spaces.
More precisely, the merit is that one often
can attain integral formulas for solutions
and 
properties of the spectral function
can in favourable cases be reduced to
specific problems which are setrled by ordinary calculus.
For example, the absolute continuity of the spectral function above
is established in [ibid] by a result which goes as follows
\medskip

\noindent
Let $\{a\leq s\leq b\}$ be a 
compact interval on the real $s$-line and
$s\mapsto G_s$ is  a function with values in the Hilbert space
$L^2(U)$ which  is 
continuous in the sense that 
\[
\lim_{s\to s_0}\, ||G_s-G_{s_0}||_2=0\tag{i}
\]
hold for each $s_0$, where we  introduced the $L^2$-norms
in $L^2(U)$.
In addition we assume that
there exists a constant $M$ such that
\[
\sum_{\nu=0}^{\nu=N-1}\, ||G_{s_{\nu+1}}-G_{s_\nu}||_2\leq M\tag{ii}
\] 
hold for every partition $a=s_0<s_1<\ldots<s_N=b$.
Using (ii)
one  construct Stieltjes integrals
and 
for every subinterval $[\alpha,\beta]$
there exists
the $L^2$-function in $U$ 
\[
\Phi_{[\alpha,\beta]}= \int_\alpha^\beta\, s\cdot \frac{dG_s}{ds}
\]
which arise via limits of Steiltjes' sums:
\[
\sum_{\nu=0}^{\nu=N-1}\, s_\nu(G_{s_{\nu+1}}-G_{s_\nu})
\]
where the limit exists as $\max(s_{\nu+1}-s_\nu)\to 0$.
We impose the extra conditions that the normal deriviatives
$ \frac{\partial G_s}{\partial n}$ exist  and vanish 
$\partial\Omega$ for every $a\leq s\leq b$
and the following differential equation
holds for
every sub-interval $[\alpha,\beta]$ of $[a,b]$:
\[
\Delta(G_\beta-G_\alpha)+\Phi_{[\alpha,\beta]}=0
\] 
\medskip

\noindent
{\bf{2.1.1 Theorem.}}
\emph{The equations  above imply that
$s\mapsto G_s$ is absolutely continuous.}
\medskip

\noindent
{\bf{Remark.}}
The absolute continuity of 
$s\mapsto G_s$ means that 
whenever $\{\ell_1,\ldots,\ell_M\}$ a finite family of disjoint
intervals in $[a,b]$ where the sum of their lengths is $<\delta$,
then the sum of
the total variations over these intervals is
bounded by $\rho(\delta)$ where
$\rho$ is a function of $\delta$ which tends to zero as $\delta\to 0$.
We refer to § xx for an account of the proof of this result.

\newpage









\medskip


\centerline {\bf{0.0. Densely defined hermitian operators.}}

\medskip

\noindent
Let $A$ be a linear operator on a separable Hilbert space
$\mathcal H$ whose domain of definition $\mathcal D(A)$ is
dense and satisfies the hermitian equation:
\[
\langle Ax,y\rangle=
\langle x,Ay\rangle
\] 
for each pair $x,y$
in
$\mathcal D(A)$.
When thid holds we first notice that if
$\{x_n\}$ is a sequence in $\mathcal D(A)$
which converges  the zero vector, i.e. the norms
$||x_n||$ tend to zero, then
$\{A(x_n)\}$ cannot converge to a non-zero vector $y$ in
$mathcal H$. To see this we take some
$\xi\in\mathcal D(A)$ and since
$||x_n||\to 0$ we get

\[
0=\lim_{n\to \infty}\, \langle A(\xi),x_n\rangle
\]
Since $A$ is hermitian this entails that
\[
0=\lim_{n\to \infty}\, \langle \xi,A(x_n)\rangle
\langle \xi,y\rangle
\]
where the last equality holds since $||A(x_n)-y||\to 0$ was assumed.
But then $y$ is $\perp$ to the dense subspace
$\mathcal D(A)$ and must be zero.
From this observation it follows that
$A$ can be extended to an operator whose graph is closed
and the reader can check that this alos yields a hermitian oeprator.
So from now on it sufficies to consider densey defined and closed
hermitain operators.
\medskip

\noindent
{\bf{0.1 An inhomogenous equation.}}
A first result from Chapter 1 in [ibid]
asserts  that the inhomogeneous equation
\[
x=\lambda\cdot A(x)+\xi\tag{*}
\]
has at least one solution $x\in\mathcal D(A)$ for every vector $\xi\in\mathcal H$
and non-real complex number $\lambda$.
To prove this  Carleman  used weak approximations of $A$ by
hermitian Hilbert-Schmidt operators. Moreover,
Bessel's inequality entails 
that
every solution in (*) satisfies
\[
||x||\leq |\mathfrak{Im}(\lambda)|^{-1}\cdot ||\xi||\tag{**}
\]
\medskip


\noindent
{\bf{0.2 Class I operators.}}
If the equations (*) have unique solutions for every
non-real $\lambda$, then e say that 
$A$ is of Class I.
A notsable fact which is proved in [ibdi] asserts that if
(*) has a uniquw solution for some fixed
$\lambda^*$ in the upper hlf-plane, then
the same uniquness hold for all $\lambda$ with positive real part.
A siumilar conclusion hold for complex numbers in the lower
half-plane.
So in order to check when $A$ is of class 1 or not, it suffices to
consider the inhomogeneous equations in (*) when
$\lambda$ is $i$ or $-i$.

\newpage

\noindent
{\bf{0.3. The spectral function.}}
Let $A$ be  of Class I.
a densely defined self-adjoint operator on a separable Hilbert space
$\mathcal H$. 




Then 
there exists an operator valued function
\[
\lambda\mapsto \Theta_+(\lambda)\tag{i}
\]
of finite total variation with respect to the operator norms on
the Banach space of bounded linear operators on $\mathcal H$ 
defined when $0<\lambda<+\infty$, and another
 operator valued function
 \[
\lambda\mapsto \Theta_-(\lambda)\tag{ii}
\]
defined when $-\infty <\lambda<0$, 
These $\Theta$-operators enjoy similar properties as those 
in Hilbert's spectral resolution of bounded self-adjoint operators.
More precisely, for  the $\Theta_+$-operators the following hold:
For each interval $[a,b]$ with $0<a<b$ the
operator
\[
E_+[a,b]=
\Theta_+(b)\Theta_+(a)
\]
is a self-adjoint projection, i.e. 
its range is a closed subspace in $\mathcal H$ while the kernel of
$E[a,b]$ is the orthogonal complement and finally $E[a,b]^2=E(a,b]$.
Moreover, if $[a,b]$ and $[c,d]$ is a pair of disjoint intervals in
$(0,+\infty)$ then
$E[a,b]\circ E[c,d]=0$, which means that the subspaces
$E[a,b](\mathcal H)$ and
$E[c,d](\mathcal H)$ are orthogonal.
In addition, for each pair of vector $x,y$ in $\mathcal H$
the complex-valued function
\[
\langle \Theta_+(\lambda)(x),y\rangle
\]
is continuous on $(0,+\infty)$.
\medskip

\noindent
From the above there exist Stieltjes' integrals, i.e. if
$g(\lambda)\in C^0[a,b]$ for some 
bounded and closed interval $[a,b]$ in $(0.+\infty)$
and $x$ is a vector in $\mathcal H$, then
there exists a vector
\[
\int_a^b\, g(\lambda)\cdot \frac{d}{d\lambda}( \Theta(\lambda)(x))
\]
found as the limit of Stieltjes' sums
\[
\sum_{\nu=1}^{\nu=N-1}\,g(\lambda_\nu) \cdot  
E_+(\lambda_\nu,\lambda_{\nu-1})(x))
\]
where  $\delta=\lambda_0<\lambda_1<\ldots<\lambda_N=1/\delta$ is
a partition of the interval $[a,b]$
and the limit is taken
as
$\max(\lambda_\nu-\lambda_{\nu-1})\to 0$.
Keeping $[a,b]$ and $g$ fixed
this yields a bounded linear operator $\mathcal G[a,b]$
whose operator norm is bounded
by the maximum norm of $g$ over
$[a,b]$.
\medskip

\noindent
Similar properties as above hold for the
$\Theta_-$-operators, and here
\[
E_+[a,b]\circ E_-[-d,-c]=0
\]
for all pairs of intervals when
$0<a<b$ and $0<c<d$.
\medskip

\noindent
{\bf{0.4 Representation of $A$.}}
For each   vector  $x\in\mathcal H$ and  $\delta>0$ we have the 
non-negative integral
\[
 \int_{-1/\delta}^{-\delta}\,
|\lambda|^{-1}\cdot ||\frac{d}{d\lambda}( \Theta(\lambda)(x))||+
 \int_{\delta}^{1/\delta}\,
|\lambda|^{-1}\cdot ||\frac{d}{d\lambda}( \Theta(\lambda)(x))||
\tag{1}
\]
Above the  integrals are  taken in the sense of Stieltjes.
For example, the 
the last integral in (1)  is given by
\[
\max\, \sum_{\nu=1}^{\nu=N-1}\,\lambda_\nu^{-1} \cdot  
||\Theta(\lambda_\nu)(x))- ||\Theta(\lambda_{\nu-1})(x))||\tag{2}
\]
taken over every partition
 $\delta=\lambda_0<\lambda_1<\ldots \lambda_N=1/\delta$ of
the interval $[\delta,1/\delta]$.
\medskip

\noindent
With these notations, Carleman proved that
a vector $x$ belongs to $\mathcal D(A)$ if and only
(1) is bounded by a constant $C$ which may depend on 
the given vector $x$  but not upon
$\delta$.
Moreover, 
\[
A(x)=
\lim_{\delta\to 0}\bigl[
\, \int_{-1/\delta}^{-\delta}\,
\lambda^{-1}\cdot \frac{d}{d\lambda}(\Theta_-(\lambda)(x))
+\, \int_{\delta}^{1/\delta}\,
\lambda^{-1}\cdot \frac{d}{d\lambda}(\Theta_+(\lambda)(x))\,\bigr]
\tag{***}
\] 
where the  integrals as usual are
taken in the sense of Stieltjes and from the above they converge absolutely
when
$x$ belongs to $\mathcal D(A)$.


\medskip

\noindent
{\bf{0.4.1 Remark.}}
From the above it follows that
if $0<a<b$, then the self-adjoint projection $E[a,b]$ 
has a range contained in $\mathcal D(A)$ and
\[
A\circ E_+[a,b](x)=
\, \int_a^b\,
\lambda^{-1}\cdot \frac{d}{d\lambda}(\Theta_+(\lambda)(x))
\]
hold for every $x\in\mathcal H$.
Moreover, this yields  a bounded linear operator
$A[a,b]$ whose kernel is the orthogonal
$E[a,b](\mathcal H)$, while
\[
A[a,b](x)=
\, \int_a^b\,
\lambda^{-1}\cdot \frac{d}{d\lambda}(\Theta_+(\lambda)(x))\quad\colon
x\in E[a,b](\mathcal H)
\]
Similar bounded operators
$A[-d,-c]$ arise when $0<c<d$.



\medskip




\noindent
{\bf{0.4.2 The closure property.}}
For every vector $x\in\mathcal H$
there exists a limit vector
\[
x_*=\lim_{\delta\to 0}\, \bigl[
\, \int_{-1/\delta}^{-\delta}\,\frac{d}{d\lambda}(\Theta_-(x))+
\, \int_{\delta}^{1/\delta}\,\frac{d}{d\lambda}(\Theta_+(x))\,\bigr]\tag{xx}
\]
Following [ibid. page 136] one says that $A$ has the 
closure property when $x=x_*$ for every $x\in\mathcal H$.
In [ibid: Chapire 4]
it is proved  that $A$ has the closure property
if
it is is injective, i.e. $Ax\neq 0$ for every non-zero vector in
$\mathcal D(A)$.
We shall refrain from  a more
subtle study about the closure property which appears
in 
[ibid:page 138-142] where the closure property is derived from
the existence of certain weak approximations of
$A$.
\bigskip





\noindent
{\bf{0.5 Unitary groups.}}
Given a spectral resolution of a Class I operator $A$ which hjas the closure property
there exists  a unitary group
$\{U_t\}$ indexed by real numbers where
\[
U_t(x)=i\cdot \int_{-\infty}^\infty\, e^{i\frac{t}{\lambda}}\cdot
\frac{d}{d\lambda}(\Theta(\lambda)(x))\quad\colon\, x\in\mathcal H
\]
To be precise, one verifies easily that
each $U_t$ is a unitary operator on $\mathcal H$
where the closure property entails that
$U_0$ is the identity.
From calculus one has the limit   formula
\[
i\cdot \lim_{t\to 0}\, t^{-1}(e^{i\frac{t}{\lambda}}-1)=
\lambda^{-1}\quad\colon\,\lambda\neq 0
\] 
In § xx we explain that this implies
that 
$A$ is the infinitesmal generator  of
$\{U_t\}$ to be defined in § xx.
The  converse also holds and is proved
in the section devoted to the
Hille-Phillips-Yosida theorem.
The conclusion is that there
exists
a
1-1 corespondence between  the family of strongly continuous
unitary groups and
the family of Ckass I operators with the closure property.
\medskip



\noindent
{\bf{0.5.1 Example.}}
In ${\bf{R}}^3$
the Laplace operator $\Delta$ yields a 
densely defined linear operstor on
the Hilbert space $\mathcal H=L^2({\bf{R}}^3)$.
Introducing the Fourier transform, Parseval's equality gives
the unitary group
$\{U_t\}$
where each $f\in \mathcal H$ is sent to
\[ 
U_t(f)(x)=
i\cdot (2\pi)^{-3}\cdot \int_{{\bf{R}}^3}
e^{i\langle  x,\xi\rangle}
\cdot  e^{\frac{it}{|\xi|^2}} \cdot\widehat{f}(\xi)\, d\xi
\]
When $f$ is such that
$\widehat{f}(\xi)\in C_0^\infty({\bf{R}}^3)$ we have
\[
\lim_{t\to 0}\,\frac{U_t(f)-f}{t}=
 -(2\pi)^{-3}\cdot \int_{{\bf{R}}^3} \,|\xi|^{-2}\cdot
 e^{i\langle  x,\xi\rangle}\cdot \widehat{f} (\xi)\, d\xi
=\Delta(f)(x)
 \]



\noindent
It follows that the infinitesmal generator of
$\{U_t\}$ is the densely defined and hermitian operator $A$
where $\mathcal D(A)$
consists of $L^2$-functions $f$ for which
$\Delta(f)$ taken in the sense of distribution theory is square integrable.
As explained
in § xx,
the densely defined operator  $A$
has a spectrum in Neumann's sense.  Fourier's inversion formula
entails that $\sigma(A)=(-\infty,0])$, and the
resolvents are given by
the bounded operators
\[
R_A(\lambda)(f)(x)=
-(2\pi)^{-3}\cdot \int_{{\bf{R}}^3}\,
\frac{e^{i\langle  x,\xi\rangle}}{\lambda+|\xi|^2}\cdot
\widehat{f}(\xi)\, d\xi
\]
when $\lambda$ is outside
${\bf{C}}\setminus (-\infty,0]$.





\medskip

\noindent
{\bf{0.5.2 The closure property.}}
To check this we use that
$\Delta$ is an elliptic PDE-operator and there reamins to show
that
if $H$ is a harmonic funtion in
${\bf{R}}^3$ which is square integrable, then $H=0$.
We leave this proof as an exercsie to the reader. See also
§ xx for a further study of closure properties related to the Laplace operator
in ${\bf{R}}^3$.




 




\bigskip

\noindent
{\bf{0.6 The case of integral operators.}}
Here one starts with a real-valued function $K(x,y)$ defined in
a product $\Omega\times\Omega$ where
$\Omega$ is an open set in
${\bf{R}}^n$ for some $n\geq 1$.
Assume the symmetry  $K(x,y)= K(y,x)$ and that there exists a nullset
$\mathcal N$ in $\Omega$ such that
\[
\int_\Omega\, K(x,y)^2\, dy<\infty
\quad\colon x\in \Omega\setminus \mathcal N\tag{0.6.1}
\]
Let $f(x)$ is a continuous  and square integrable function
in $\Omega$. Now there exist  the non-empty family of
$L^2$-functions $\phi$ which satisfy
\[
\phi(x)=\lambda\cdot  \int_\Omega\, K(x,y)\cdot \phi(y)\, dy+f(x)\tag{0.6.2}
\]
To begin with
this equality hold for almost every 
$x\in \Omega$, i.e. outside a null-set
which in general  contains
$\mathcal N$.
Suppose that $E$ is a compact subset of
$\Omega\setminus \mathcal N$
such that
\[
\max_{|x_1|-x_2|\leq\delta}\, \int_\Omega\, (K(x_1,y)-K(x_2,y))^2\,dy
\]
tends to zero as $\delta\to 0$ while $x_1,x_2$ stay in  $E$.
Then it is easily seen that
each $\phi$-function is continuous on $E$ and one is led to introduce the sets
\[
\mathcal D(x:\lambda)= \bigcup\, \phi(x)
\]
with the union taken over all solutions to (3.1).
Properties of these sets are studied in [ibid] and 
in the section devoted to the moment problem we shall
give some precise results.
Returning to (0.6-1) one has a densely defined
and symmetric operator.
In  specific situations 
one is led to determine when this gives a Class I operator
which in many applications is a major
issue.






\bigskip



\noindent
{\bf{0.7. An ugly example.}}
Following [Carleman -  page 62-66]
we  give  examples which show that
the existence of self-adjoint extensions
of  densely defined symmetric operator
is not automatic.
Every separable Hilbert space can be
identified with $L^2[0,1]$ whose vectors are complex-valued square integrable functions.
Let us then consider a real-valued
Lebegue measurable function $K(x,y)$ defined on the square
$\{0\leq x\leq 1\}\times\{0\leq y\leq 1\}$ which is symmetric, i.e.
$K(y,x)= K(x,y)$.
Assume that there exists a null set $\mathcal N$ such that
\[
\int_0^1\, K(x,y)^2\, dy<\infty\quad\colon x\in [0,1]\setminus\mathcal N\tag{1}
\]
If $f\in L^2[0,1]$
the Cauchy-Schwarz inequality entails that
$y\mapsto K(x,y)\cdot f(y)$
is absolutely integrable when $x$ is outside $\mathcal N$.
Hence there exists the almost everywhere defined function
\[
\mathcal K(f)(x)=\int_0^1\, K(x,y)\cdot f(y)\, dy\tag{2}
\]
However,
(1) does not imply that
$\mathcal K(f)$ is square integrable.
So we  consider the subspace
$\mathcal D$ of $L^2[0.1]$
where $f\in \mathcal D$ gives
$\mathcal K(f)$ in
$L^2[0.1]$.
To analyze this subspace
we consider
positive integers $N$ and denote by $E_N$
the subset 
of the unit $x$-interval such that
\[
\int_0^1\, K(x,y)^2\, dy\leq N\quad\colon x\in E_N\tag{3}
\]
If $f\in L^2[0,1]$ is supported by $E_N$
and $g$ is another $L^2$-function, the symmetry of $K$ and Fubini's theorem give
\[
\int_0^1\, g(x)\mathcal K(f)(x)\, dx=
\int_0^1\, g(x)\cdot (\int\, K(x,y)f(y)\, dy)\, dx=
\int_0^1\, f(x)\cdot (\int\, K(x,y)g(y)\, dy)\, dx
\]
The Cauchy-Schwartz inequality and (3) entail that
the absolute value of the last term is majorised by
\[
\sqrt{N}\cdot ||g||_2\cdot \int_{E_N}\, |f(x)|\,dx\leq
\sqrt{N}\cdot ||g||_2\cdot ||f||_2
 \]
Since this hold for every $L^2$-function $g$, 
a wellknown fact from integration theory implies
that
$\mathcal K(f)$ is square integrable and its $L^2$-norm is majorised by
$\sqrt{N}\cdot ||f||_2$.
Hence $\mathcal D$ contains every $L^2$-function supported by
$E_N$. Since $\cup\, E_N=[0,1]\setminus\mathcal N$
it follows that $\mathcal D$ is a dense subspace.
The question arises if there exists some
complex-valued function $\phi\in\mathcal D$ 
which satisfies the eigenvalue equation
\[
\phi=i\cdot \mathcal K(\phi)\tag{*}
\]
When
$\mathcal K$ is a bounded linear operator on
the Hilbert space
$L^2[0,1]$ such non-zero solutions do not exist. In
fact, this
follows from Hilbert's theorem for
bounded symmetric operators.
So if a non-trivial solution to (*) exists, then
$\mathcal K$ must be unbounded.
To exhibit examples of such
"ugly operators", Carleman introduced the
an orthonormal basis for
$L^2[0,1]$ given by a sequence $\{\psi_n\}$ where
$\psi_0(x)=1$ and 
$\psi_1(x)= -1$ on $(0,1/2)$ and +1 on $(1/2,1)$. 
Finally, for each $n\geq 2$ we set
\[
\psi_n(x)=-2^{\frac{n-1}[{2}} \,\colon\,
1-2^{-n+1}\leq x< 1-2^{-n}
\quad\text{and}\quad
\psi_n(x)=2^{\frac{n-1}{2}}\,\colon\, 1-2^{-n}<x<1
\]
while
\[
\psi_n(x)=0\quad\colon\, 0<x<1-2^{-n+1}
\]
It is easily seen that this gives an orthonormal basis.
Next, for every
sequece $\{a_p\}$  of real numbers we define
the kernel
function  on $[0,1)\times [0,1)$
by
\[
K(x,y)=\sum\, a_p\cdot \psi_p(x)\psi_q(x)\tag{i}
\]
To this symetric function
we associate
the  operator 
\[
\mathcal K(u)(x)=\int_0^1\, K(x,y)u(y)\, dy
\]
The construction of the $\psi$-functions
show that $\mathcal D$ contains
$L^2$-functions $u$ supported by
$0\leq x\leq x_*$ for every   $x_*<1$. In § xx we shall prove the following:

\medskip

\noindent
{\bf{Theorem.}}
\emph{The equation (*) has a non-trivial $L^2$-solution if and only if}
\[
\sum_{p=0}^\infty \, \frac{2^p}{1+a_p^2}<\infty
\]






\bigskip



\centerline {\bf{1. The case of non-separable Hilbert spaces.}}
\bigskip


\noindent
Carleman's studies 
were restricted to
separable Hilbert spaces.
Using the Cayley transform and Hilbert's spectral theorem for bounded
normal operators which is valid for non-separble Hilbert spaces
one gets a rather short proof
of 
the spectral theorem for
densely defined self-adjoint operators on non-separable 
Hilbert spaces.
This was carried out in
J. von Neumann's  article  \emph{Allgemeine Eigenwerttheorie Hermitscher
Funktionaloperatoren} [Math. Annalen, vol. 102 (1929)].
See § 9 in my notes on functional analysis
for details.
During  the search of self-adjoint extensions of
densely defined hermitian  operators, 
the notion of hypermaximality   introduced by Schmidt
is useful. It
stems
from Schmidt's 
early contributions in  the article \emph{Auflösing der allgemeinen linearen Integralgleichung}
[Math. Annalen, vol. 64 (1907].  
\medskip

\noindent
Non-separable Hilbert spaces arise in many situations. An example
is the Hilbert space of square integrable functions on
the compact Bohr group which by definition is the dual of
the discrete abelian group of real numbers.
The theory   of almost periodic functions was created by Harald Bohr
(brother to the  phycisist  Niels Bohr) and   presented in the articles
\emph{Zur Theorie  der fastperiodischen Funktionen I-III } [ Acta. Math. vol
45-47 (1925-26]. This led  in
a natural way to  consider  of operators
on
non-separable Hilbert spaces and   motivated a
more
"abstract account"  where unbounded operators
are not  described via infinite matrices indexed by pairs of integers.
Other examples emerge  from quantum mechanics. 
The uncertainty principle led to 
questions concerned with
actions by pairs of non-commutating densely defined
operators on a Hilbert space.
In 1928 this was   reformulated by Weyl to
specific problems about non-commuting families   of unitary groups.
See §  for further details where we present 
von Neumann's proof  of a 
result
which settled  original problems posed by
de Broigle, Heisenberg and Schrödinger.


\bigskip




\centerline{\bf{1.2 The Cayley transform.}}

\medskip


\noindent
Recall a classic result about
matrices
which goes back to work by
Cayley and Hamilton.
If $N\geq 2$ is an integer we have the family
$\mathfrak{h}(N)$
of Hermitian  $N\times N$-matrices.
Next, a
matrix $R$ is normal if it commutes
with
the  adjoint matrix $R^*$.
The Cayley transform sends
a Hermitian matrix
$A$ to the normal matrix   
\[
R_A=(iE_N-A)^{-1}
\]
where $E_N$ is the identity matrix in $M_N({\bf{C}})$.
If   $\{\alpha_\nu\}$ is the real spectrum of $A$
it is readily seen that
\[ 
\sigma(R_A)=\{\frac{1}{i-\alpha_\nu}\}
\]
Next, when $a$ is a real number we notice that
\[
\frac{1}{i-a}+\frac{i}{2}=\frac{1}{2(i-a)}(2+i^2-ia)=\frac{1-ai}{2i(1+ai)}
\]
The last quotient  is a complex number with absolute value 1/2. Hence
$\sigma(R_A)$ is contained in the circle
\[
\mathcal C=\{|\lambda+\frac{i}{2}|= \frac{1}{2}\}
\]
Conversely, let  $R$ be a normal operator such that
$\sigma(R)$ is contained in
$\mathcal C$ and does not contain
the origin. Now  there exists the inverse operator $R^{-1}$
and 
\[ 
A=iE_N-R^{-1}\tag{i}
\]
is a normal operator whose spectrum
$\sigma(A)$ is real,  and since $A$  also is normal it follows that it is
Hermitian. Notice also that $R=R_A$ in (i).
\emph{Summing up},  the Cayley transform gives
a bijective map between
Hermitian matrices and the family of invertible
normal operators
whose spectra are contained in $\mathcal C$.

\medskip

\noindent
{\bf{1.3 The passage to Hilbert spaces.}}
Consider a complex Hilbert space
$\mathcal H$ and denote by  $\mathcal N$  the family of bounded
normal operators $R$ with the property that
$\sigma(R)$ is contained in the circle $\mathcal C$, and in addition 
$R$ is injective and has a dense range.
To each such $R$ we find a densely defined operator
$S_R$ on $\mathcal H$
which for each $y=R(x)$ in the dense range 
assigns the vector $x$,  i.e. the composed operator
$S_R\circ R=E$, where $E$ is the identity on $\mathcal H$.
Now there also exists the densely defined operator
\[
A= iE-S_R\tag{*}
\] 
We shall learn that the densely operator $A$
is self-adjoint, and 
conversely every
densely defined and self-adjoint operator $A$
is of the form (*)  for
a unique
$R$ in $\mathcal C$.
So this gives
1-1 correspondence which extends the previous result for matrices.
Let us remark that 
bounded self-adjoint operators appear
in (*)  when the normal operator $R$ is    invertible.


\bigskip


\bigskip


\centerline{\bf{2. Two examples from PDE-theory.}}

\medskip


\noindent
The study of unbounded self-adjoint
operators is especially relevant while one regards PDE-operators.
We present  two examples below.
\medskip


\noindent
{\bf{2.1. Propagation of sound}}.
With $(x,y,z)$ as space variables in
${\bf{R}}^3$ and a time variable $t$, the 
propagation of sound
in the infinite  open complement $U={\bf{R}}^3\setminus \overline{\Omega}$
of a bounded open subset $\Omega$ is governed by
 solutions $u(x,y,z,t)$ to the wave equation
 \[ 
 \frac{\partial^2 u}{\partial t^2}= \Delta u\tag{1}
 \] 
 where 
 $\Delta$ is the Laplace operator in $x,y,z$.
So here (1) holds when
$p=(x,y,z)\in U$
and $t\geq  0$. We  assume that
$\partial\Omega$ is of class $C^1$, i.e. given as  a union of pairwise disjoint
closed surfaces of class $C^1$ along which normal vectors are defined.
A well-posed Cauchy problem arises when we seek solutions 
such that
$p\mapsto u(p,t)$ belong to $L^2(U)$ for each $t$,
and the outer normal derivatives
taken along $\partial\Omega$ are zero,  i.e. for every $t$ 
\[
\frac{\partial u}{\partial n}(p,t)=0\quad\colon p\in \partial \Omega\tag{2}
\]
Initial conditions are expressed by  a pair of $C^2$-functions
$f_1x,y,z)$ and $f_2(x,y,z)$ defined in $U$ such that
$f_1,f_2$  together with
$\Delta(f_1$ and $\Delta(f_2)$ belong to $L^2(U)$,
and their outer normal derivatives along $\partial\Omega$ are zero.
Then there exists a unique solution $u$ which satisfies
(1-2) and the initial conditions
$u(p,0)= f_0(p)$ and $\frac{\partial u}{\partial t}(p,0)= f_1(p)$.
A proof of  existence and uniqueness relies upon the construction
of a 
time-independent self-adjoint operator $A$ acting on 
$L^2(U)$ whose kernel is
expressed via a Green's function
which is found by Neumann's standard elliptic boundary value problem
in the domain $U$.
After this has been done one
gets
an integral representation of the solution $u$ 
expressed via the pair $f_0,f_1$ and the spectral function associated to $A$.
For physical  reaons one expects that
if $u$ is a solution, then the first order partial derivatives of
$u(p,t)$ with respect to the space variables tend to zero as
$t\to+\infty$.
In [Carleman 1923] this is proved by analyzing the spectral function
associated with $A$
where the crucial point is that its associated spectral function is
absolutely continuous with respect to
the $\lambda$-parameter.
In §§ we show
that this absolute continuity is derived from  a
general result which goes as follows:

\medskip

\noindent
Let $\{a\leq s\leq b\}$ be a 
compact interval on the real $s$-line and
$s\mapsto G_s$ is  a function with values in the Hilbert space
$L^2(U)$ which  is 
continuous in the sense that 
\[
\lim_{s\to s_0}\, ||G_s-G_{s_0}||_2=0
\]
hold for each $s_0$, where we  introduced the $L^2$-norms.
The function has a finite total variation if 
there exists a constant $M$ such that
\[
\sum\, ||G_{s_{\nu+1}}-G_{s_\nu}||_2\leq M
\] 
hold for every partition $a=s_0<s_1<\ldots<s_M=b$.
When this holds one  construct Stieltjes integrals
and 
for every subinterval $[\alpha,\beta]$
there exists
the $L^2$-function in $U$ 
\[
\Phi_{[\alpha,\beta]}= \int_\alpha^\beta\, s\cdot \frac{dG_s}{ds}
\]
We impose the extra conditions that the normal deriviatives
$ \frac{\partial G_s}{\partial n}$ exist  and vanish 
$\partial\Omega$ for every $a\leq s\leq b$
and the following differential equation
holds for
every sub-interval $[\alpha,\beta]$ of $[a,b]$:
\[
\Delta(G_\beta-G_\alpha)+\Phi_{[\alpha,\beta]}=0
\] 
\medskip

\noindent
{\bf{2.1.1 Theorem.}}
\emph{The equations  above imply that
$s\mapsto G_s$ is absolutely continuous.}
\medskip

\noindent
{\bf{Remark.}}
The absolute continuity of 
$s\mapsto G_s$ means that 
whenever $\{\ell_1,\ldots,\ell_M\}$ a finite family of disjoint
intervals in $[a,b]$ where the sum of their lengths is $<\delta$,
then the sum of
the total variations over these intervals is
bounded by $\rho(\delta)$ where
$\rho$ is a function of $\delta$ which tends to zero as $\delta\to 0$.
We refer to § xx for an account of the proof of this result.

\bigskip







\centerline
{\bf{2.2 The Bohr-Schrödinger  equation.}}
\bigskip




\noindent
In 1923 quantum mechanics had not yet appeared so
the studies in  [Carleman: 1923] were 
concerned with singular  integral equations, foremost 
inspired from  previous work by Fredholm, Hilbert,
Weyl  and Volterra.
The creation of quantum mechanics gave new challenges for the
mathematical community,.
The interested reader should   consult the
lecture held  by Niels Bohr at the Scandianavian congress in mathematics
in Copenhagen 1925 where he
speaks  about  the   interplay between
the new physics and 
mathematics. 
Bohr's  lecture  presumably inspired Carleman when he
some years later resumed 
work from [Car 1923].
Recall that the fundamental point in Schrödinger's theory
is the hypothesis on energy levels which correspond to 
orbits in Bohr's theory of atoms. For an account about
the physical background
the reader may consult
Bohr's
plenary talk when 
he received the Nobel Prize in physics 1923.
Mathematically the Bohr-Schrödinger theory
leads to the  equation
\[ 
\Delta\phi+2m\cdot\bigl( E-U\bigr)\bigl(\frac{2\pi}{h}\bigr)^2\cdot \phi=0\tag{*}
\] 
Here $\Delta$ is the Laplace operator in the 3-dimensional $(x,y,z)$-space,
$m$ the mass of a particle and $h$  Planck's constant
while   $U(x,y,z)$ is a potential function.
Finally $E$ is a parameter and one seeks values on $E$
such that (*) has a solution $\phi$
which belongs to $L^2({\bf{R}}^3)$.
Let us   cite an excerpt   from Carlemans  lectures in Paris at 
Institut Henri Poincaré held in 1930:
\medskip

\noindent
\emph{Dans ces dernières années l'ínteret de la question qui nous
occupe a considérablement augmenté.
C'est en effet
un instrument mathématique 
indispensable pour development de la mechanique moderne crée par
M.M. de Brogile, Heisenberg et Schrödinger. Etude de l'équation
integrale:}
\[ 
\phi(x)= \lambda\cdot \int_a^b\, K(x,y)\phi(y)dy+f(x)
\quad\colon\lambda\in {\bf{C}}\setminus {\bf{R}}
\]
\medskip

\noindent
The theory from [Carleman:1923] applies  to the following
PDE-equations attached to a second order differential operator
\[ 
L=\Delta+c(x,y,z)\quad\colon
\Delta=\partial_x^2+\partial_y^2+\partial_z^2\tag{**}
\]
where $c(x,y,z)$ is a real-valued function.
The $L$-operator is  densely defined and  symmetric on the
subspace of
test-functions  in
${\bf{R}}^3$. The problem is to find conditions on
the $c$-function in order that $L$ is self-adjoint on
the Hilbert space $L^2({\bf{R}}^3)$
with a real spectrum confined to $[a,+\infty)$ for some real number $a$.
The following
sufficiency result was presented by
Carleman's  
during  his lectures at Sorbonne
in the spring 1930:
\medskip

\noindent
{\bf{Theorem }}
\emph{Let $c(x,y,z)$ be a continuous and real-valued function
such that there is a constant $M$ for which}
\[
\limsup \uuu{x^2+y^2+z^2\to \infty}\, c(x,y,z)\leq M
\]
\emph{Then $\Delta+c(x,y,z)$ is self-adjoint.}
\medskip

\medskip

\noindent{{\bf{Example.}}
The result applies when $c$ is given
by a potential function:
\[ 
W(p)=\sum\,\frac{\alpha_k}{|p-q_k|}+\beta
\] 
where $\{q_k\}$ is a finite subset of
${\bf{R}}^3$ and the $\alpha$-numbers and $\beta$ are real and positive.
Here the requested self-adjointness is  easy to prove
and solutions
to the Bohr-Schrödinger equation
are found
via  robust limit formulas.
See §§ xx for details.

\bigskip


\noindent
{\bf{Further comments.}} The literature about
the Schrödinger equation and  other
equations which emerge from quantum mechanics is 
extensive. 
For the 
source of quantum mechanics
the reader should first of all consult 
the plenary talks by Heisenberg, Dirac and Shrödinger
when they received the Nobel prize in
physics. 
Apart from physical considerations the reader
will find
expositions where explanations
are given in a mathematical framework.
Actually Heisenberg was
sole winner 1931 while Dirac and Schrödinger shared the
prize in 1932. But they visited Stockholm together in
December 1932.
\medskip

\noindent
For  mathematician who wants to become acquainted with
quantum physics the eminent text-books by Lev Landau
are recommended. Especially 
\emph{Quantum mechanics: Non-relativistic theory}
in Vol. 3.
Here Landau exposes
Heisenberg's matrix representation and
Dirac's  equations are used to study radiation phenomena.
In the introduction to
[ibid: Volume 3]
Landau inserts the following remark:
\emph{It is of interest to note
that the complete mathematical formalisim
of quantum mechanics was constructed by W. Heisenberg
and E. Schrödinger in 1925-26, before the discovery
of the uncertainty principle which revealed the physical
contents of this formalism.}

\bigskip



\bigskip

\noindent
{\bf{Introduction.}}
The material is foremost  is devoted to 
spectral properties of second order elliptic PDE-operators.
To illustrate the
methods we are content to treat   a special case while 
elliptic operators with variable coefficients 
are  treated in separate notes
devoted to mathematics by 
Carleman.
However,  § E in the appendix  contains
a construction of fundamental solutions
to elliptic
second order operators in
${\bf{R}}^3$ based upon  Carleman's lectures
 at Institute Mittag Leffler in 1935
which might be of interest to some readers even though it will
not be covered during my lecture.
As background  the  appendix  contains a section
which explains
Gustav Neumann's fundamental 
construction from 1879
of resolvents to densely defined 
linear operators,  and at the end of § A we also
recall
Hilbert's spectral theorem for bounded
normal operators on Hilbert spaces.
\medskip


\noindent
Let us now announce a major result which will
be exposed in the lecture.
In
${\bf{R}}^3$ we 
consider a bounded Dirichlet regular domain
$\Omega$, i.e. every $f\in C^0(\partial\Omega)$
has a harmonic extension to $\Omega$.
A wellknown  
fact
established by
G. Neumann and H. Poincaré
during the years 1879-1895
gives the following: First there
exists the Greens' function
\[
G(p,q)= \log\,\frac{1}{|p-q|}+H(p,q)
\]
where $H(p,q)= H(q,p)$ is continuous in
the product set
$\overline{\Omega}\times\overline{\Omega}$ with the property that
the operator $\mathcal G$ defined on $L^2(\Omega)$ by
\[
f\mapsto \mathcal G_f(p)= \frac{1}{2\pi}\dot \iint\, G(p,q)f(q)\,dq
\]
satisfies
\[ 
\Delta\circ \mathcal G_f=-f\quad\colon f\in L^2(\Omega)
\]
Moreover,  $\mathcal G$ is a compact operator on
the Hilbert space $L^2(\Omega)$ and there 
exists a sequence $\{f_n\}$ in $L^2(\Omega$ such that
$\{\phi_n=\mathcal G_{f_n}\}$
is an orthonormal basis in $L^2(\Omega$ and
\[ 
\Delta(\phi_n)=-\lambda_n\cdot \phi_n\quad\colon\, n=1,2,\ldots
\] 
where
$0<\lambda_1\leq \lambda_2\leq \ldots\}$.
When  eigenspaces have  dimension $\geq 2$, the 
eigenvalues are repeated by their multiplicity.
The result below  was presented by Carleman at the
Scandinavian Congress in mathematics held in Stockholm 1934:
\medskip

\noindent
{\bf{0. Theorem. }}\emph{For every Dirichlet regular domain
$\Omega$ and each $p\in\Omega$ one has the limit formula}
\[ 
\lim_{N\to\infty}\, \lambda_N^{-1}\cdot \sum_{n=1}^{n=N}\, \phi_n(p)^2= \frac{1}{4\pi}
\]
\medskip

\noindent
{\bf{Remark.}}
The strategy in the proof is to consider the function of a complex variable $s$
defined by
\[
\Phi(s)=\sum_{n=1}^\infty \frac{\phi_n(p)^2}{\lambda_n^s}
\]
and show that it
is a meromorphic function in the whole complex $s$-plane with
a simple pole at $s=1$ whose residue is $\frac{1}{4\pi}$.
The proof is given in § xx.
\medskip


\noindent
{\bf{0.1 Self-adjoint extensions of $\Delta+c(p)$.}}
Here we consider ${\bf{R}}^3$ with points $p=(x,y,z)$
and $\Delta$ is the Laplace operator, 
while $c(p)$ is a real-valued and locally square integrable function.
The linear operator
\[
u\mapsto L(u)= \Delta(u)+ c\cdot u
\]
is defined on test-functions and hence densely defined on the Hilbert space
$L^2({\bf{R}}^3)$.
In the monograph 
\emph{Sur les équations singulières
à noyaux réel et
symmetrique} [Uppsala University 1923],
Carleman established
spectral resolutions for unbounded
self-adjoint
operators on a Hilbert space together with  conditions 
that densely defined symmetric operators have self-adjoint extensions,
The lecture will 
describe the  major steps of a result due to
 Carleman  which asserts that
the operator $L$ has a self-adjoint extension under the condition that
\[
 \limsup_{p\to \infty}\, c(p)\leq M\tag{*}
 \] 
hold for some constant $M$.
A special  case occurs when
$c(p)$ is a Newtonian potential
\[
c(p)= \sum\, \frac{\alpha_\nu}{|p-q_\nu|}+\beta\tag{**}
\] 
where
$\{q_\nu\}$
is a finite set of points in
${\bf{R}}^2$ while $\{\alpha_\nu\}$ and $\beta$ are positive real numbers.
So here one encounters the Bohr-Schrödinger equation which
stems from quantum mechanics.
With $c$ as in (**)
the requested self-adjoint extension is  
easily verified while the existence of a self-adjoint extension
when (*) holds requires a rather involved proof.
\medskip

\noindent
{\bf{0.3 An asymptotic expansion.}}
Consider the Schrödinger equation
\[
i\cdot \frac{\partial u}{\partial t}= \Delta(u)+ c\cdot u
\]
where we assume
that
$L^\Delta+c$ has a 
self-adjoint extension.
One seeks solutions $u(x,t)$ defined when
$t\geq 0$ and $x\in{\bf{R}}^3$
with an initial  condition $u(x,0)= f(x)$ for some
$f\in L^2({\bf{R}}^3)$.
The solution is given  via the spectral function associated
with
the $L$-operator. 
So the main issue is to
get formulas for the spectral function of $\Delta +c$.
In Carleman's  cited lecture from 1934 
an  asymptotic expansion is given for this spectral function
which merits further study since
one nowadays can
investigate approximative solutions numerically by computers.




\bigskip




\noindent
{\bf{0.4 Asymptotic formula for eigenvalues.}}
Let $n=3$ and consider a PDE-operator
\[
L=
\sum_{p=1}^{p=3}\sum_{q=1}^{q=3}\, a_{pq}(x)\cdot \frac{\partial ^2}{\partial x_p\partial x_q}+
\sum_{p=1}^{p=3}\, a_p(x)
\frac{\partial }{\partial x_p}+a_0(x)
\]
The $a$-functions are real-valued and
defined in a neighborhood of the closure of a bounded
domain
$\Omega$ with a $C^1$-boundary.
Here one has the symmetry $a_{pq}=a_{qp}$, and 
$\{a_{pq}\}$ are
of class $C^2$, $\{a_p\}$  of class $C^1$ and $a_0$ is continuous.
The elliptic property of
 $L$ means that
for
every $x\in\Omega$ the eigenvalues of the symmetric
matrix
$A(x)$ with elements $\{a_{pq}(x)\}$
are positive.
Under these conditions, a  result which goes back to work by 
Neumann and Poincaré,
gives
a positive constant
$\kappa_0$ such that
if $\kappa\geq \kappa_0$ then
the inhomogeneous equation
\[
L(u)-\kappa^2\cdot u=f\quad\colon f\in L^2(\Omega)
\]
has a unique solution $u$ which is a $C^2$.-function 
in
$\Omega$ and  extends to the closure where it is zero on
$\partial\Omega$.
Moreover, there exists some $\kappa_0$
and for each $\kappa\geq \kappa_0$ a
Green's function
$G(x,y;\kappa)$ such that
\[
(L-\kappa^2)(\frac{1}{4\pi}\cdot \int_\Omega\, 
G(x,y;\kappa)\, f(y)\, dy )= -f(x)\quad\colon f\in L^2(\Omega)\tag{i}
\]
This  means  that the bounded linear operator on
$L^2(\Omega$ defined by
\[
f\mapsto 
-\frac{1}{4\pi}\cdot \int_\Omega\, 
G(x,y;\kappa)\, f(y)\, dy\tag{ii}
\]
is Neumann's resolvent
to the densely defined operator
$L-\kappa^2$ on the 
Hilbert space $L^2(\Omega)$.
After a detailed study of these $G$-functions, Carleman established
an asymptotic formula for
the discrete sequence of eigenvalues $\{\lambda_n\}$. In general they
are complex but arranged so that
the absolute values increase. To begin with one proves rather easily that they
are "almost real" in the sense that there exist positive constants
$C$ and $c$ such that
\[
|\mathfrak{Im}(\lambda_n)|\leq
C\cdot(\mathfrak{Re}(\lambda_n)+c)
\] 
hold for every $n$.
Next, the elliptic
hypothesis means that
the determinant function
\[
D(x)=\det(a_{p,q}(x))
\]
is positive in $\Omega$. With these notations one has

\medskip



\noindent
{\bf{ Theorem.}}
\emph{The following limit formula holds:}
\[
\lim_{n\to\infty}\, \frac{\mathfrak{Re}(\lambda_n)}{n^{\frac{2}{3}}}
=\frac{1}{6\pi^2}\cdot \int_\Omega\, 
\frac{1}{\sqrt{D(x)}}\, dx\tag{*}
\]
\medskip

\noindent
{\bf{Remark.}}
The formula above is due to Courant and Weyl  when
$P$ is symmetric and was extended to
non-symmetric operators during 
Carleman 's lectures at Institute Mittag-Leffler in  1935.
Weyl and Courant used calculus of variation
in the symmetric case 
while Carleman employed  different methods which
have the merit that the passage to the non-symmetric case
does not cause any  trouble. 
As pointed out by
Carleman the methods in the  proof  
give similar asymptotic formulas 
in   other boundary value problems such as
those considered by Neumann where one imposes boundary value conditions on
outer normals, and so on.
A crucial step during the  proof of the theorem above
is to
construct a fundamental solution $\Phi(x,\xi;\kappa)$
to the PDE-operators
$L-\kappa^2$ which is exposed in § E.


\newpage


\centerline{\bf{§ D. Proof of Theorem 0.}}
\bigskip

\noindent
Let
$\Omega$ be a bounded and Dirichlet regular domain.
Let $p\in\Omega$
be kept fixed
and consider the continuous function on
$\partial\Omega$ defined by
\[ 
q\mapsto  \log \frac{1}{|p-q|}
\]
We find the harmonic function
$u_p(q)$ in $\Omega$ such that
$u_p(q)=\log \frac{1}{|p-q|}\,\colon\, q\in\partial\Omega$.
Green's function is defined for pairs $p\neq q$ in
$\Omega\times\Omega$ 
by
\[ 
G(p,q)= \log\,\frac{1}{|p-q|}-u_p(q)\tag{1}
\]
Keeping
if $p\in\Omega$  fixed, the function
$q\mapsto G(p,q)$ extends to the 
closure of $\Omega$ where it vanishes if
$q\in\partial\Omega$.
If  $f\in L^2(\Omega$
we set
\[ 
\mathcal G_f(p)=\frac{1}{2\pi}\cdot \int_\Omega\, G(p,q)\cdot f(q)\, dq\tag{2}
\]
where $q=(x,y)$ so that $dq=dxdy$ when the double integral is evaluated.
From (1) we see that
\[
 \iint_{\Omega\times \Omega}\, |G(p,q)|^2\, dpdq<\infty
\]
Hence
$\mathcal G$ is of the Hilbert-Schmidt type and
therefore a compact operator on 
$L^2(\Omega)$.
Next,  recall that
$\frac{1}{2\pi}\cdot \log\sqrt{x^2+y^2}$ is
a fundamental solution to the Laplace operator.
From this one can deduce the following:

\medskip

\noindent{\bf{D.1 Theorem.}}
\emph{For each $f\in L^2(\Omega)$
the Lapacian of $\mathcal G_f$
taken in the distribution sense belongs to
$L^2(\Omega)$ and one has the equality}
\[ 
\Delta(\mathcal G_f)=-f\tag{*}
\] 
\medskip


\noindent
The equation (*) means that
the composed operator
$\Delta\circ \mathcal G$ is minus the identity on
$L^2(\Omega)$.
We are  led
to introduce the 
linear operator $S$ on $L^2(\Omega)$ 
defined by $\Delta$, where  
$\mathcal D(S)$ is
the range of $\mathcal G$.
If $g\in C^2_0(\Omega)$, i.e. twice differentiable and with
compact support, it follows via Greens' formula that
\[
\frac{1}{2\pi}\cdot \int_\Omega\, G(p,q)\cdot \Delta(g)(q)\, dq=-g(p)
\]
In particular $C_0^2(\Omega)\subset\mathcal D(S)$
which  implies that
$S$ is densely defined and we  leave it to the reader to verify that
\[
\mathcal G(\Delta(f))=-f\quad\colon f\in\mathcal D(S)
\]


\medskip
\noindent
{\bf{Remark.}}
By the construction of resolvent operators in § 1 this means that
$-\mathcal G$ is Neumann's inverse  of 
$S$.
\medskip

\noindent
{\bf{Exercise.}} Show that $S$ has a closed range and in addition it
is self-adjoint, i.e. $S=S^*$.
\medskip

\noindent
{\bf{The spectrum of $S$.}}
A wellknown  result 
asserts that there exists an orthonormal basis $\{\phi_n\}$ in $L^2(\Omega)$
where each $\phi_n\in\mathcal D(S)$ is an eigenfunction. More preciesely
there is a non-decreasing sequence of positive real numbers
$\{\lambda_n\}$ and
\[ 
\Delta(\phi_n)+\lambda_n\cdot \phi_n=0\quad\colon n=1,2,\ldots\tag{i}
\]
Let us remark that (i) means that
\[
\mathcal G(\phi_n)= \frac{1}{\lambda_n}\, \cdot \phi_n\tag{ii}
\]
So above
$\{\lambda_n^{-1}\}$
are  eigenvalues of the compact operator $\mathcal G$ whose sole cluster
point is $\lambda=0$.
Eigenvalues whose eigenspaces have
dimension $e>1$ are repeated $e$ times.



\medskip

\noindent
Now we begin the proof of Theorem 0, i.e. we will  show that
the following hold
for each point $p\in\Omega$:
\[
\lim_{n\to \infty}\, \frac{1}{\lambda_n}\cdot
\sum_{k=1}^{k=n}\, \phi_k(p)^2=
 \frac{1}{4\pi}\tag{*}
 \]
 \medskip
 
 
 \noindent
To prove (*) we  consider the Dirichlet series
for each fixed $p\in\Omega$:
\[ 
\Phi_p(s)=\sum _{n=1}^\infty \, \frac{\phi_n(p)^2}{\lambda_n^s}\tag{**}
\]
It is easily seen that
$\Phi_p(s)$ is analytic in a half-space
$\mathfrak{Re} s>b$ for a large $b$.
Less trivial is the following:

\medskip

\noindent
{\bf{D.2 Theorem.}}
\emph{There exists an entire function
$\Psi_p(s)$ such that}
\[
\Phi_p(s)=\Psi_p(s)+\frac{1}{4\pi(s-1)}
\]
\medskip

\noindent
Let us first remark that Theorem D.2  gives (*) via
a result  due to Wiener in the article
\emph{Tauberian theorem} [Annals of Math.1932].
Wiener's theorem 
asserts that if $\{\lambda_n\}$ is a non-decreasing sequence of
positive numbers which tends to infinity and
$\{a_n\}$ are non-negative real numbers such that
there exists the limit
\[ 
\lim_{s\to 1}\,(s-1)\cdot \sum\, \frac{a_n}{\lambda_n^s}=A
\] 
then it follows that
\[
\lim_{n\to \infty}\,\lambda_n^{-1}\cdot
\sum_{k=1}^{k=n}\, a_k=A
\]
\medskip

\centerline{\emph{Proof of Theorem D.2}}

\bigskip

\noindent
Since $\mathcal G$ is a Hilbert-Schmidt operator a wellknown result due to Schur
gives
\[
\sum\, \lambda_n^{-2}<\infty \tag{i}
\]
This convergence entails that various constructions below are defined.
For each $\lambda$ outside $\{\lambda_n\}$ we set
\[
G(p,q;\lambda)=
G(p,q)+
2\pi\lambda\cdot \sum_{n=1}^\infty\,
\frac{\phi_n(p)\phi_n(q)}{\lambda_n(\lambda-\lambda_n)}\tag{ii}
\]
This gives the integral operator
$\mathcal G_\lambda$ defined on $L^2(\Omega)$ by
 \[ 
 \mathcal G_\lambda(f)(p)
 =\frac{1}{2\pi}\cdot \iint_\Omega\, G(p,q;\lambda )\cdot f(q)\, dq\tag{iii}
\]

\medskip

\noindent
{\bf{A. Exercise.}} Use that the eigenfunctions $\{\phi_n\}$ is an orthonormal basis in
$L^2(\Omega)$ to show that
\[
(\Delta+\lambda)\cdot \mathcal G_\lambda=-E
\]


\noindent{\bf{B. The function $F(p,\lambda)$}}.
Set
\[ 
F(p,q,\lambda)= G(p,q;\lambda)- G(p,q)
\]
Keeping $p$ fixed we see that (ii) gives
\[
\lim_{q\to p}\, F(p,q,\lambda)=
2\pi\lambda\cdot \sum_{n=1}^\infty\,
\frac{\phi_n(p)^2}{\lambda_n(\lambda-\lambda_n)}\tag{B.1}
\]
Set
\[
F(p,\lambda)=
\lim_{q\to p}\, F(p,q,\lambda)
\]
From (i) and (B.1) it follows that it is a meromorphic function in
the complex $\lambda$-plane with at most simple poles
at $\{\lambda_n\}$.
\medskip

\noindent{\bf{C. Exercise.}}
Let $0<a<\lambda_1$. Show via residue calculus that
one has the equality below in a half-space
$\mathfrak{Re}\, s>2$:
\[ 
\Phi(s)=
\frac{1}{4\pi^2 \cdot i}\cdot \int_{a-i\infty}^{a+i\infty}\, 
F(p,\lambda)\cdot \lambda^{-s}\, d\lambda\tag{C.1}
\]
where the line integral  is taken on the vertical  line
$\mathfrak{Re}\,\lambda=a$.

\medskip

\noindent
{\bf{D. Change of contour integrals.}}
At this stage we employ a device which goes to
Riemann and
move the integration into the half-space
$\mathfrak{Re}(\lambda)<a$.
Consider  the curve $\gamma_+$
defined as the union of the
negative real interval $(-\infty,a]$ followed by
the upper
half-circle $\{\lambda= ae^{i\theta}\,\colon 0\leq\theta\leq \pi \}$
and the 
half-line $\{\lambda= a+it\,\colon t\geq 0\}$.
Cauchy's theorem entails that 
\[ 
\int_{\gamma_+}\, F(p,\lambda)\cdot \lambda^{-s}\, d\lambda=0
\]
We leave it to the reader to contruct the
similar
curve
$\gamma_-=\bar \gamma_+$. Using 
the vanishing of these line integrals and taking the branches of the 
multi-valued function
$\lambda^s$ into the account the reader should verify the following:

\medskip


\noindent
{\bf{E. Lemma.}}
\emph{One has the equality}
\[ 
\Phi(s)=\frac{a^{s-1}}{4\pi}\cdot \int_{-\pi}^\pi\,
F(ae^{i\theta})\cdot e^{(i(1-s)\theta}\,d\theta
+
\frac{\sin \pi s}{2\pi^2}\cdot \int_a^\infty\, F(p,-x)\cdot x^{-s}\,dx\tag{E.1}
\]
\medskip

\noindent
The first term in the sum of the right hand side of (E.1)
is obviously an entire function of $s$. So there remains to
prove that
\[
 s\mapsto  \frac{\sin \pi s}{2\pi^2}\cdot \
 \int_a^\infty\, F(p,-x)\cdot x^{-s}\,dx\tag{E.2}
\]
is meromorphic with
a single pole at $s=1$ whose residue is $\frac{1}{4\pi}$.
To attain this we  express $F(p,-x)$ when $x$ are real and positive in another way.
\medskip

\noindent
{\bf{F.  The $K$-function.}}
In the half-space $\mathfrak{Re}\,z>0$ there exists the analytic function
\[
K(z)= \int_1^\infty\, \frac{e^{-zt}}{\sqrt{t^2-1}}\,dt
\]
\medskip

\noindent
{\bf{Exercise.}}
Show that $K$ extends to a multi-valued analytic function outside
$\{z=0\}$ given by
\[
K(z)=-I_0(z)\cdot \log z+ I_1(z)\tag{F.1}
\] 
where $I_0$ and $I_1$ are entire functions
with series expansions
\[
I_0(z)=\sum_{m=0}^\infty\, \frac{2^{-2m}}{(m!)^2}\cdot
z^{2m}\tag{i}
\]
\[ 
I_1(z)= \sum_{m=0}^\infty\, \rho(m)\cdot
\frac{2^{-2m}} {(m!)^2} \cdot z^{2m}\quad
\colon \rho(m)=1+\frac{1}{2}+\ldots+\frac{1}{m}-\gamma\tag{ii}
\]
where $\gamma$ is the usual Euler constant.

\bigskip


\noindent
With  $p$ kept fixed and $\kappa>0$ 
we solve the Dirichlet problem and find
a  function $q\mapsto H(p,q;\kappa)$ which satisfies  the
equation
\[
 \Delta(H)-\kappa\cdot H=0\tag{F.2}
\] 
in $\Omega$ with boundary values
\[ 
H(p,q;\kappa)=K(\sqrt{\kappa}|p-q|)\quad\colon q\in \partial\Omega
\]


\noindent
{\bf{G. Exercise.}}
Verify the equation
\[ 
G(p,q;-\kappa)=K(\sqrt{\kappa}\cdot |p-q|)- H(q;\kappa)\quad\colon \kappa>0
\]



\noindent
Next,   the construction of $G(p,q)$ gives
\[
 F(p,-\kappa)=
 \lim_{q\to p}\,
 [K(\sqrt{\kappa}\cdot |p-q|)+\log\,|p-q|]+
 \lim_{q\to p}\,[u_p(q)+ H(p,q,\kappa)]\tag{G.1}
\]
The last term above has the  "nice limit" 
$u_p(p)+H(p,p,\kappa)$ and from  (F.1)  the reader can  verify the limit formula:
\[
 \lim_{q\to p}\,
 [K(\sqrt{\kappa}\cdot |p-q|)+\log\,|p-q|]=
 -\frac{1}{2}\cdot \log \kappa +\log 2-\gamma\tag{G.2}
\]
where $\gamma$ is  Euler's constant.

\bigskip

\noindent
{\bf{H. Final part of the proof.}}.
Set $A=  +\log 2-\gamma+u_p(p)$. Then (G.1) and (G.2)
give
\[
F(p,-\kappa)= -\frac{1}{2}\cdot \log \kappa +A+H(p,p;-\kappa)
\]
With $x=\kappa$ in (E.2 ) we  proceed  as follows.
To  begin with it is clear that
\[
s\mapsto A\cdot 
\frac{\sin \pi s}{2\pi^2}\cdot \int_a^\infty\,  x^{-s}\,dx
\]
is an entire function of $s$.
Next,  consider the function
\[ 
\rho(s)=
 -\frac{1}{2}\cdot 
\frac{\sin \pi s}{2\pi^2}\cdot \int_a^\infty\,  \log x\cdot x^{-s}\,dx
\]
Notice that the complex derivative
\[
\frac{d}{ds}\,  \int_a^\infty\,  x^{-s}\,dx=
- \int_a^\infty\,  \log x\cdot x^{-s}\,dx
\]

\medskip
\noindent
{\bf{H.1 Exercise.}}
Use the  above to show that
\[
\rho(s)-\frac{1}{4\pi(s-1)}
 \]
is an entire function.
\medskip


\noindent
From the above we see that Theorem D.2  follows if we have proved
\medskip

\noindent
 {\bf{H.2 Lemma.}}
\emph{The following function  is entire}:
\[
s\mapsto \frac{\sin\,\pi s}{2\pi^2}\cdot
\int_a^\infty\, H(p,p,\kappa)\cdot  \kappa^{-s}\,d\kappa
\]
\medskip

\noindent
\emph{Proof.}
When $\kappa>0$
the equation (F.1) shows that $q\mapsto H(p,q;\kappa)$
is subharmonic  in $\Omega$ and the maximum principle gives
\[
0\leq  H(p,q;\kappa)\leq \max_{q\in\partial\Omega}\,K(\kappa|p-q|)\tag{i}
\]
With  $p\in\Omega$ fixed there is 
a positive number
$\delta$ such that
$|p-q|\geq\delta\,\colon q\in \partial\Omega$ which  
gives
positive constants
$B$ and  $\alpha$  such that
\[
H(p,p;\kappa)\leq e^{-\alpha\kappa}\quad\colon \kappa>0\tag{ii}
\]
The reader may now check that this
exponential decay gives Lemma H.2.

\newpage



\centerline {\bf{§ E. Fundamental solutions to second order
Elliptic operators.}}
\bigskip


\noindent
In
${\bf{R}}^3$ with coordinates $x=(x_1,x_2,x_3)$ we consider 
 a second order PDE-operator
\[
L=
\sum_{p=1}^{p=3}\sum_{q=1}^{q=3}\, a_{pq}(x)\cdot \frac{\partial ^2}{\partial x_p\partial x_q}+
\sum_{p=1}^{p=3}\, a_p(x)
\frac{\partial }{\partial x_p}+a_0(x)
\]
where 
$a$-functions are real-valued and
one has the symmetry $a_{pq}=a_{qp}$.
To ensure existence of a globally defined fundamental solutions we
suppose the the following limit formulas hold
as $(x,y,z)\to \infty$:
\[
\lim a_\nu(x,y,z)=0 \colon 0\leq p\leq 3\quad\colon\,
\lim a_{pq}(x,y,z)= \text{Kronecker's delta function}
\]
Thus, $L$ approaches the Laplace operator as $(x,y,z)$ tends to
infinity. Moreover
$L$ is elliptic which means that
the eigenvalues of the symmetric
matrix with elements $\{a_{pq}(x)\}$
are positive for every $x$.
Recall the  notion of  fundamental solutions.
First we consider
the adjoint
operator:
\[ 
L^*(x,\partial _x)=P-2\cdot \bigl(
\sum_{p=1}^{p=3}\, \bigl(\sum_{q=1}^{q=3}\, 
\frac{\partial a_{pq}}{\partial x_q}\bigr)\cdot \frac{\partial}{\partial x\uuu p}
-\sum_{p=1}^{p=3}\, \frac{\partial a_p}{\partial x_p}
+2\cdot \sum\sum\, \frac{\partial^2 a_{pq}}{\partial x_p\partial x_q}\tag{0.1}
\]
Partial integration gives  the equation  below for every pair of
$C^2$-functions $\phi,\psi $ in ${\bf{R}}^3$ with compact support:
\[
\int\, L(\phi)\cdot \psi\, dx=
\int\, \phi\cdot L^*(\psi)\, dx\tag{0.2}
\] 
where
the volume integrals are taken over
${\bf{R}}^3$.
A locally integrable function $\Phi(x)$ in ${\bf{R}}^3$
is  a fundamental solution to $L(x,\partial _x)$
if
\[
\psi(0)=\int\, \Phi\cdot L^*(\psi)\, dx\tag{0.3}
\] 
hold for every $C^2$-function  $\psi$ with compact support.
Next, to each 
positive number
$\kappa$ we  get  the PDE-operator $L-\kappa^2$ and a
function $x\mapsto \Phi(x;\kappa)$ is a fundamental solution to $L-\kappa^2$
if
\[
\psi(0)=\int\, \Phi(x:\kappa)\cdot (L^*-\kappa^2)(\psi(x))\, dx\tag{0.4}
\] 
hold for compactly supported $C^2$-functions $\psi$.
Next, the  origin can  replaced by a variable point $\xi$ in
${\bf{R}}^3$ and then one seeks
a function
$\Phi^*(x,\xi;\kappa)$ with the property that
\[
\psi(\xi)=\int\, \Phi(x,\xi;\kappa)\cdot (L^*(x,\partial_x)-\kappa^2)(\psi(x))\, dx\tag{*}
\] 
hold for all  $\xi\in{\bf{R}}^3$
and every $C^2$-function $\psi$ with compact support.
Keeping $\kappa$ fixed this means that  
$\Phi(x,\xi;\kappa)$ is a function of six variables  defined in 
${\bf{R}}^3\times {\bf{R}}^3$.
Theorem 1.9 below 
gives
sharp estimate for  fundamental
solutions. 
The subsequent constructions 
are 
based upon a
classic formula due to Newton and  specific solutions to
integral equations
found by a convergent Neumann series.


\bigskip


\centerline {\bf{1. The construction of $\Phi(x,\xi;\kappa)$.}}
\medskip



\noindent
When $L$ has
constant coefficients 
the construction of   fundamental solutions was given by
Newton in his famous
text-books from 1666.
We have the
positive  and symmetric $3\times 3$-matrix
$A= \{a_{pq}\}$. Let
$\{b_{pq}\}$ be the elements of the inverse matrix and 
put
\[
\alpha=\sqrt{\kappa^2+\frac{1}{2}\, \sum_{p,q}\, b_{pq} a_pa_q
-a_0}
\]
where $\kappa$ is chosen so large that
the term under the square-root is $>0$.
Define the quadratic form
 \[ 
 B(x)= \sum_{p,q}\, b_{pq} a_px_q
\]

\noindent
With these notations Newton's fundamental solution taken
at $x=0$ becomes
\[
H(x;\kappa)= \frac{1}{4\pi\cdot \sqrt{\Delta\cdot B(x)}}
\cdot e^{-\alpha \sqrt{B(x)}-
\frac{1}{2}\sum_{p,q}b_{pq} a_p\cdot x_q}\tag{1.1} 
\]


\medskip




\noindent
{\bf{Exercise.}} Verify by Stokes  formula
that $H(x;\kappa)$ indeed yields  a fundamental solution
to the PDE-operator $L(\partial_x)-\kappa^2$.



\bigskip



\noindent{\emph{1.2 The case with variable coefficients.}}
For each $\xi\in{\bf{R}}^3$ the elements of the inverse matrix
to $\{a_{pq}(\xi)$
are denoted by $\{b_{pq}(\xi)\}$.
Choose $\kappa_0>0$ such that
\[
\kappa_0^2+\frac{1}{2}\, \sum_{p,q}\, b_{pq}(\xi) a_p(\xi)a_q(\xi)
-b(\xi)>0\quad\text{hold for all}\quad  \xi\in{\bf{R}}^3
\] 
and for every $\kappa\geq \kappa_0$ we set
\[
\alpha_\kappa(\xi)=
\sqrt{\kappa^2+\frac{1}{2}\, \sum_{p,q}\, b_{pq}(\xi) a_p(\xi)a_q(\xi)
-b(\xi)}\tag{i}
\]
Following Newton's construction in (1.1) we
put:
\[
H(x,\xi;\kappa)=\frac{1}{4\pi}\cdot
 \frac{\sqrt{\Delta(\xi)}^{-\frac{1}{2}}}{
\sqrt{ \sum_{p,q}\, b_{pq}(\xi)\cdot x_px_q}}
\cdot e^{-\alpha_\kappa(\xi) \sqrt{B(x)}-
\frac{1}{2}\sum_{p,q}b_{pq}(\xi) a_p(\xi)\cdot x_q} \tag{ii}
\]

\noindent
When $\xi$ is kept fixed this  function of
$x$ is real analytic  outside the origin and we also notice
that $x\to H(x,\xi;\kappa)$ is locally integrable
as a function of $x$ in a neighborhood of the origin.
We are going to find a fundamental solution
which takes the form
\[
\Phi(x,\xi;\kappa)=
H(x-\xi,\xi;\kappa)+\int_{{\bf{R}}^3}\, 
H(x-y,\xi;\kappa)\cdot\Psi(y,\xi;\kappa)\, dy\tag{iii}
\]
where the $\Psi$-function is the solution to an integral equation
which we construct in (1.5).

\medskip

\noindent
{\bf{1.3 The function $F(x,\xi;\kappa)$.}}
For every fixed $\xi$ we consider the  differential operator in the
$x$-space:
\[ 
L_*(x,\partial_x,\xi;\kappa)=
\]
\[\sum_{p=1}^{p=3}\sum_{q=1}^{q=3}\, (a\uuu{pq}(x)-
(a\uuu{pq}(\xi))\cdot 
\frac{\partial^2}{\partial x_p\partial x_q}+
\sum_{p=1}^{p=3}\,
(a_p(x)-a_p(\xi))\frac{\partial}{\partial x_p}+ (b(x)-b(\xi))
\]

\medskip

\noindent
With $\xi$ fixed we apply $L_*$ to the function
$x\mapsto H(x-\xi,\xi;\kappa)$
and put
\[ 
F(x,\xi;\kappa)=\frac{1}{4\pi}\cdot L_*(x,\partial_x,\xi;\kappa)(H(x-\xi,\xi,\kappa)) \tag{1.3.1}
\]

\medskip

\noindent
{\bf{1.4 Two  estimates.}}
The limit conditions  in (0.0)     give  positive constants
$C,C_1$ and $k$ such that the following hold when $\kappa\geq\kappa_0$:
\[
|H(x-\xi,\xi;\kappa)|\leq C\cdot \frac{e^{-k\kappa|x-\xi|}}{|x-\xi|}
\quad\colon\,
[F(x,\xi;\kappa)|\leq C_1\cdot 
\frac{e^{-k\kappa|x-\xi|}}{|x-\xi|^2}
\tag{1.4.1}
\]


\noindent
The verification of (1.4.1) is left as an exercise.



\bigskip





\noindent
{\bf{1.5 An integral equation.}}
We  seek
$\Psi(x,\xi;\kappa)$ which satisfies the equation:
\[ 
\Psi(x,\xi;\kappa)= \int_{{\bf{R}}^3}\,  F(x,y;\kappa)\cdot \Psi(y,\xi;\kappa)\,dy+F(x,\xi;\kappa)\tag{1.5.1}
\]
To solve (1.5.1 )
we construct the Neumann series of $F$.
Thus, starting with $F^{(1)}=F$ we set
\[
F^{(k)}(x,\xi;\kappa)=\int_{{\bf{R}}^3}\, F(x,y;\kappa)\cdot
F^{(k-1)}(y,\xi;\kappa)\, dy\quad\colon\quad k\geq 2\tag{1.5.2}
\]
Then (1.4.1 ) gives  the inequality
\[
|F^{(2)}(x,\xi;\kappa)|
\leq C_1^2\iiint
\frac{e^{-k\kappa|\xi-y|}}{|x-y|^2\cdot |\xi-y|^2}\cdot dy\tag{i}
\]


\noindent
To estimate (i) we  notice that the triple integral after
the substitution $y-\xi\to u$
becomes
\[
C_1^2\iiint
\frac{e^{-k\kappa|u|^2}}{|x-u-\xi|^2\cdot |u|^2}\cdot du\tag{ii}
\]


\noindent
In  (ii)  the volume integral can be integrated in polar
coordinates
and becomes
\[
C_1^2\cdot \int_0^\infty\int_{S^2}\, 
\frac{e^{-k\kappa r^2}}{|x-r\cdot w-\xi|^2}\cdot dwdr\tag{iii}
\]
where $S^2$ is the unit sphere and $dw$ the area measure on
$S^2$ and we see that (iii) becomes
\[
2\pi C_1^2\cdot
\int_0^\infty\int_0^\pi\, 
\frac{e^{-k\kappa r}}{(x-\xi)^2+r^2-
2r\cdot |x-\xi|\cdot \sin\theta}\cdot d\theta dr=
\]
\[
\frac{2\pi C_1^2}{|x-\xi|}\cdot\int_0^\infty\, e^{-k\kappa |x-\xi|t}\cdot
\log\, |\frac{1+t}{1-t}|\cdot \frac{dt}{t}\tag{iv}
\]
where the last equality follows by a straightforward computation.

\medskip


\noindent
{\bf{1.6 Exercise.}}
Show that (iv) gives the estimate
\[
|F^{(2)}(x,\xi;\kappa)|\leq \frac{2\pi\cdot  C_1^2\cdot C_1^*}{\kappa\cdot |x-\xi|^2}
\]
where $C_1^*$ is a fixed positive constant
which is independent of $x$ and $\xi$ and 
show by an induction over $n$
that one has:
\[
|F^{(n)}(x,\xi;\kappa)|\leq\frac{C_1}{|x-\xi|^2}\cdot 
\bigl[\frac{2\pi C_1^2\cdot C_1^*}{\kappa}\bigr]^{n-1}
\quad\text{hold for every}\quad  n\geq 2\tag{*}
\]
\medskip

\noindent
{\bf{1.6 Conclusion.}}
With $\kappa_0^*$ so large that
$2\pi C_1^2\cdot C_1^*<\kappa_0^*$
it follows from (*) that
the Neumann series
\[
\sum_{n=1}^\infty F^{(n)}(x,\xi;\kappa)
\]
converges when 
$\kappa\geq \kappa_0^*$ 
and
gives the requested solution $\Psi(x,\xi;\kappa)$ in (1.5.1).
\bigskip


\noindent
{\bf{1.7 Exercise.}}
Above we  have found 
$\Psi$ which satisfies the integral equation in § 1.5.1
Use  Green's formula to show
that the function
$\Phi(x,\xi;\kappa)$ defined in (1.2.1) gives  a fundamental solution
of $L(x,\partial_x)-\kappa^2$.

\medskip


\noindent{\bf {1.8 A final estimate.}}
The  constructions above show that
the  functions
\[
x\mapsto \Phi(x,\xi;\kappa)\quad\text{and}\quad 
x\mapsto H(x-\xi,\xi;\kappa)
\]


\noindent
have the same  singularities at $x=\xi$.
Consider the difference
\[
G(x,\xi;\kappa)=\Phi(x,\xi;\kappa)-
H(x-\xi,\xi;\kappa)\tag{1.8.1}
\]
\medskip


\noindent
{\bf{1.8.2 Exercise.}}
Use the previous constructions to show
that for every $0<\gamma\leq 2$
there is a constant $C_\gamma$
such that
\[
\bigl |G(x,\xi;\kappa)\,\bigr|\leq \frac{C_\gamma}{(\kappa|x-\xi|)^{\gamma}}
\]
hold for every pair $(x,\xi)$ and every $\kappa\geq \kappa_0$.
Together with the  the inequality for the
$H$-function in (1.4.1)
this gives
an estimate for the fundamental solution $\Phi$.
More precisely we have proved:

\medskip

\noindent
{\bf{1.9 Theorem.}} \emph{With $\kappa_0^*$ as above
there exist positive constants $C$ and $k$ and
for each $0<\gamma\leq 2$ a constant $C_\gamma$ such that}
\[
|\Phi(x,\xi;\kappa)|\leq
C\cdot \frac{e^{-k\kappa|x-\xi|}}{|x-\xi|}+
 \frac{C_\gamma}{(\kappa|x-\xi|)^{\gamma}}
\]
\emph{hold for all pairs $(x,\xi)$ in ${\bf{R}}^3$ and every
$\kappa\geq \kappa_0^*$.}


\medskip

\noindent
{\bf{Remark.}}
Above $C$ and $k$ are independent of
$\kappa$ as soon as $\kappa_0^*$ has been chosen as above.
The size of these constant  depend on
the $C^2$-norms of the functions $\{a_{pq}(x)\}$ and 
as well as the $C^1$-norms of $\{a_1,a_2,a-3\}$ and the maximum norm of $a_0$.
Notice that the whole construction is "canonical", i.e.
the resulting fundaemtnal ssolutions
$\{\Phi(x,\xi;\kappa)\}$ are uniquely determined.
We remark that simiular constructions can be made for
ellptic operators
of even degree $2m$ with $m\geq 2$. Here
Newton's solution for constant  coefficients is replaced by those
 of
Fritz John which arise via the wave deompostion of the Dirac measure.
It would be interesting tanalyze the resulting version of Theorem 1.9.
Of course, one  can also extend
everything to
elliptic operators of $n$ variables were $n\geq 4$
in which case the
denominator $|x-\xi|^{-1}$ is replaced by
$|x-\xi|^{-n+2}$.










\newpage































\newpage



















The proof of Theorem 1 relies upon the
construction
of fundamental  solutions which is given in § 1 below.
After this  has been achieved,
the asymptotic formula (*)  in Theorem 2 is derived
via  Tauberian theorems for Dirichlet
series which  goes as follows:
Let $\{a_\nu\}$ and  $\lambda_\nu\}$ be two sequences
of positive numbers where
$\lambda_\nu\to +\infty$ and  the series
\[ 
f(x)= \sum_{\nu=1}^\infty\, \frac{a_\nu}{\lambda_\nu+x}
\]
converges when $x>x_*$ for some positive number $x_*$.
Next, for every $x>0$ we
define the function
\[
\mathcal A(x)= \sum_{\{\lambda_\nu<x\}}\, a_\nu
\]
In other words, with $x>0$ we find the largest integer $\nu(x)$
such that $\lambda-{\nu(x)}<x$ and
then $\mathcal A(x)$ is the sum over the $a$-numbers up to
this index. With these notations the following implication holds
for every pair 
$A>0 $ and $0<\alpha<1$


\medskip

\noindent
{\bf{3.  Theorem.}}
\emph{Suppose there exists a constant $A>0$ and some
$0<\alpha<1$ such that}
\[
\lim_{x\to\infty}\,
x^\alpha\cdot f(x)=A\implies
\lim_{x\to\infty}\, \mathcal A(x)=
\frac{A}{\pi}\cdot \frac{\sin\, \pi\alpha}{1-\alpha}\cdot x^{1-\alpha}
\]

\medskip












\centerline {\bf{0 Preliminary constructions.}}
\medskip


\noindent
We are given an ellipitic operator $L$
as above
and assume that the coefficients are defined in
the whole space
${\bf{R}}^3$.
To ensure convergence of volume integrals  taken over
the whole of ${\bf{R}}^3$
we add the conditions that
\[ 
\lim_{|x|\to \infty}\ a_{pp}(x)= 1\quad\colon\quad 1\leq p\leq 3
\]
while  $\{a_{pq}\}$ for $p\neq q$ and 
$a_1,a_2,a_3,b$ tend to zero as $|x|\to +\infty$.
This  means that $P$ approaches the Laplace operator when
$|x|$ is large.
Let us 
recall the  notion of a fundamental solution 
which prior to the general notion of distributions
introduced by L. Schwartz, 
was referred to as a 
\emph{Grundlösung}.
First,
the regularity  of the
coefficients of a PDE-operator $P$ 
enable us to construct 
the adjoint
operator:
\[ 
P^*(x,\partial _x)=P-2\cdot \bigl(
\sum_{p=1}^{p=3}\, \bigl(\sum_{q=1}^{q=3}\, 
\frac{\partial a_{pq}}{\partial x_q}\bigr)\cdot \frac{\partial}{\partial x\uuu p}
-\sum_{p=1}^{p=3}\, \frac{\partial a_p}{\partial x_p}
+2\cdot \sum\sum\, \frac{\partial^2 a_{pq}}{\partial x_p\partial x_q}
\]
Partial integration gives  the equation  below for every pair of
$C^2$-functions $\phi,\psi $ in ${\bf{R}}^3$ with compact support:
\[
\int\, P(\phi)\cdot \psi\, dx=
\int\, \phi\cdot P^*(\psi)\, dx
\] 
where
the volume integrals are taken over
${\bf{R}}^3$.
A locally integrable function $\Phi(x)$ in ${\bf{R}}^3$
is  a fundamental solution to $P(x,\partial _x)$
if
\[
\psi(0)=\int\, \Phi\cdot P^*(\psi)\, dx
\] 
hold for every $C^2$-function  $\psi$ with compact support.
Next, to each 
positive number
$\kappa$ we  get  the PDE-operator $P-\kappa^2$ and a
function $\Phi(x;\kappa)$ is a fundamental solution to $P-\kappa^2$
if
\[
\psi(0)=\int\, \Phi(x:\kappa)\cdot (P^*-\kappa^2)(\psi(x))\, dx\tag{1}
\] 
hold for compactly supported $C^2$-functions $\psi$.
Above $\kappa$ appears as an index of $\Phi$, i.e. for each fixed
$\kappa$ we have the locally integrable function
$x\mapsto \Phi(x:\kappa)$.
Next, the  origin can  replaced by a variable point $\xi$ in
${\bf{R}}^3$ and then one seeks
a function
$\Phi^*(x,\xi;\kappa)$ with the property that
\[
\psi(\xi)=\int\, \Phi(x,\xi:\kappa)\cdot (P^*-\kappa^2)(\psi(x))\, dx\tag{*}
\] 
hold for all  $\xi\in{\bf{R}}^3$
and every $C^2$-function $\psi$ with compact support.
Keeping $\kappa$ fixed this means that  
$\Phi(x,\xi;\kappa)$ is a function of six variables  defined in 
${\bf{R}}^3\times {\bf{R}}^3$.
Fundamental solutions are in general not unique. However, when
$P$ is an elliptic operator as above
we shall
give an explicit construction of
fundamental solutions
$\Phi(x,\xi;\kappa)$ for all sufficiently large $\kappa$ in § 1.


\bigskip


\centerline {\bf{1. The construction of $\Phi(x,\xi;\kappa)$.}}
\medskip


\medskip

\noindent
\emph{1.1 The case when $P$ has constant coefficients.}
Here the   fundamental solution is given by a 
formula  which goes back to Newton's work
in his classic text-books from 1666.
We have the
positive  and symmetric $3\times 3$-matrix
$A= \{a_{pq}\}$. Let
$\{b_{pq}\}$ be the elements of the inverse matrix and recall 
that they are found via Cramér's rule:
\[ 
b_{pq}= \frac{A_{pq}}{\Delta}
\]
where $\Delta=\det(A)$ and $\{A_{pq}\}$  are the cofactor
minors of the $A$-matrix. Put
\[
\alpha=\sqrt{\kappa^2+\frac{1}{2}\, \sum_{p,q}\, b_{pq} a_pa_q
-b}
\]
where $\kappa$ is chosen so large that
the term under the square-root is $>0$.
Next, define the quadratic form
 \[ 
 B(x)= \sum_{p,q}\, b_{pq} a_px_q
\]

\noindent
With these notations Newton's fundamental solution taken
at $x=0$ becomes
\[
H(x;\kappa)= \frac{1}{\sqrt{\Delta\cdot B(x)}}
\cdot e^{-\alpha \sqrt{B(x)}-
\frac{1}{2}\sum_{p,q}b_{pq} a_p\cdot x_q}\tag{*} 
\]


\medskip




\noindent
{\bf{Exercise.}} Verify by Stokes  formula
that $H(x;\kappa)$ indeed yields  a fundamental solution
to the PDE-operator $P(\partial_x)-\kappa^2$.



\bigskip



\centerline{\emph{1.2 The case with variable coefficients.}}
\medskip


\noindent
Choose $\kappa_0>0$ such that
\[
\kappa_0^2+\frac{1}{2}\, \sum_{p,q}\, b_{pq}(\xi) a_p(\xi)a_q(\xi)
-b(\xi)>0\quad\text{hold for all}\quad  \xi\in{\bf{R}}^3
\] 
and for every $\kappa\geq \kappa_0$ we set
\[
\alpha_\kappa(\xi)=
\sqrt{\kappa^2+\frac{1}{2}\, \sum_{p,q}\, b_{pq}(\xi) a_p(\xi)a_q(\xi)
-b(\xi)}\tag{i}
\]
Following Newton's construction for the case of constant
coefficients we put:
\[
H(x,\xi;\kappa)=
 \frac{\sqrt{\Delta(\xi)}^{-\frac{1}{2}}}{
\sqrt{ \sum_{p,q}\, b_{pq}(\xi)\cdot x_px_q}}
\cdot e^{-\alpha_\kappa(\xi) \sqrt{B(x)}-
\frac{1}{2}\sum_{p,q}b_{pq}(\xi) a_p(\xi)\cdot x_q} \tag{ii}
\]





\noindent
When $\xi$ is kept fixed this  function of
$x$ is real analytic  outside the origin and the
singularity at $x=0$
is of Newton's type. In particular
$x\to H(x,\xi;\kappa)$ is locally integrable
as a function of $x$ in a neighborhood of the origin.
Next, for every fixed $\xi$ we consider the  differential operator in the
$x$-space:
\[ 
L_*(x,\partial_x,\xi;\kappa)=
\]
\[\sum_{p=1}^{p=3}\sum_{q=1}^{q=3}\, (a\uuu{pq}(x)-
(a\uuu{pq}(\xi))\cdot 
\frac{\partial^2}{\partial x_p\partial x_q}+
\sum_{p=1}^{p=3}\,
(a_p(x)-a_p(\xi))\frac{\partial}{\partial x_p}+ (b(x)-b(\xi))
\]

\medskip

\noindent
For each fixed $\xi$ 
there exists the function
$x\mapsto H(x-\xi,\xi;\kappa)$
and we  apply the $L_*$-operator on  this $x$-dependent function and put:
\[ 
F(x,\xi;\kappa)=\frac{1}{4\pi}\cdot L_*(x,\partial_x,\xi;\kappa)(H(x-\xi,\xi,\kappa) \tag{iii}
\]

\medskip

\noindent
{\bf{1.3 Two  estimates.}}
The hypothesis that $\{a_{pq}(x)\}$ are of class $C^2$ and$\{a_p(x)\}$ of class $C^1$, together with
the limit conditions (*) in § XX   give the existence of positive constants
$C,C_1$ and $k$ such that the following hold when $\kappa\geq\kappa_0$:
\[
|H(x-\xi,\xi;\kappa)|\leq C\cdot \frac{e^{-k\kappa|x-\xi|}}{|x-\xi|}
\tag{1.3.1}
\]
\[
[F(x,\xi;\kappa)|\leq C_1\cdot 
\frac{e^{-k\kappa|x-\xi|^2}}{|x-\xi|^2}
\tag{1.3.2}
\]


\noindent
The verification is left as an exercise.



\bigskip





\noindent
{\bf{1.4 An integral equation.}}
We  seek
$\Phi(x,\xi;\kappa)$ which solves the equation:
\[ 
\Phi(x,\xi;\kappa)= \iiint\, F(x,y;\kappa)\cdot \Phi(y,\xi;\kappa)\,dy+F(x,\xi;\kappa)\tag{1}
\]
where the integral is taken over ${\bf{R}}^3$.
To solve (1)
we construct the Neumann series of $F$.
Thus, starting with $F^{(1)}=F$ we set
\[
F^{(k)}(x,\xi;\kappa)=\int_{{\bf{R}}^3}\, F(x,y;\kappa)\cdot
F^{(k-1)}(y,\xi;\kappa)\, dy\quad\colon\quad k\geq 2\tag{1.4.1}
\]
Then (1.3.2 ) gives  the inequality
\[
|F^{(2)}(x,\xi;\kappa)|
\leq C_1^2\iiint
\frac{e^{-k\kappa|\xi-y|^2}}{|x-y|^2\cdot |\xi-y|^2}\cdot dy\tag{i}
\]


\noindent
To estimate (i) we first notice that the triple integral after
the substitution $y-\xi\to u$
becomes
\[
C_1^2\iiint
\frac{e^{-k\kappa|u|^2}}{|x-u-\xi|^2\cdot |u|^2}\cdot du\tag{ii}
\]


\noindent
In  (ii)  the volume integral is integrated in polar
coordinates
and becomes
\[
C_1^2\cdot \int_0^\infty\int_{S^2}\, 
\frac{e^{-k\kappa r^2}}{|x-r\cdot w-\xi|^2}\cdot dwdr\tag{iii}
\]
where $S^2$ is the unit sphere and $dw$ the area measure on
$S^2$ and we see that (iii) becomes
\[
2\pi C_1^2\cdot
\int_0^\infty\int_0^\pi\, 
\frac{e^{-k\kappa r^2}}{(x-\xi)^2+r^2-
2r\cdot |x-\xi|\cdot \sin\theta}\cdot d\theta dr=
\]
\[
\frac{2\pi C_1^2}{|x-\xi|}\cdot\int_0^\infty\, e^{-k\kappa |x-\xi|t}\cdot
\log\, |\frac{1+t}{1-t}|\cdot \frac{dt}{t}\tag{iv}
\]
where the last equality follows by a straightforward computation.

\medskip


\noindent
{\bf{1.5 Exercise.}}
Show that (iv) gives the estimate
\[
|F^{(2)}(x,\xi;\kappa)|\leq \frac{2\pi C_1^2\cdot C_1^*}{\kappa\cdot |x-\xi|^2}
\]
where $C_1^*$ is a fixed positive constant
which is independent of $x$ and $\xi$ and 
show by an induction over $n$
that one has:
\[
|F^{(n)}(x,\xi;\kappa)|\leq\frac{C_1}{|x-\xi|^2}\cdot 
\bigl[\frac{2\pi C_1^2\cdot C_1^*}{\kappa}\bigr]^{n-1}
\quad\text{hold for every}\quad  n\geq 2\tag{*}
\]
\medskip

\noindent
{\bf{1.6 Conclusion.}}
With $\kappa$ so large that
$2\pi C_1^2\cdot C_1^*<\kappa$
it follows form (*) that
the series
\[
\sum_{n=1}^\infty F^{(n)}(x,\xi;\kappa)
\]
converges when $x\neq\xi$ and
this Neumann series
gives the requested solution $\Phi(x,\xi;\kappa)$.
Moreover, $\Phi(x,\xi;\kappa)$ satisfies a similar estimate as in (1.3.2) above
with another  constant than $C_2$ instead of $C_1$.
\medskip


\noindent
{\bf{1.7 Exercise.}}
Above we  have found 
$\Phi$ which satisfies the integral equation in § 1.4
Use  Green's formula to show
that 
$\Phi(x,\xi;\kappa)$ gives  a fundamental solution
of $P(x,\partial_x)-\kappa^2$ with a pole at $\xi$.

\medskip


\noindent{\bf {1.8 Some final estimates.}}
The  constructions above show that
the  functions
\[
x\mapsto \Phi(x,\xi;\kappa)\quad\text{and}\quad 
x\mapsto H(x-\xi,\xi;\kappa)
\]


\noindent
have the same  singularities at $x=\xi$.
Consider the difference
\[
\Psi(x,\xi;\kappa)=\Phi(x,\xi;\kappa)-
H(x-\xi,\xi;\kappa)\tag{1.8.1}
\]
\medskip


\noindent
{\bf{1.8.2 Exercise.}}
Use the previous constructions to show
that for every $0<\gamma\leq 2$
there is a constant $C_\gamma$
such that
\[
\bigl |\Psi(x,\xi;\kappa)\,\bigr|\leq \frac{C_\gamma}{(\kappa|x-\xi|)^{\gamma}}
\]
hold for every pair $(x,\xi)$ and every $\kappa\geq \kappa_0$.
Together with  (1.3.1)  this gives
an estimate for the fundamental solution $\Phi$.




\bigskip

\centerline {\bf{2. Green's functions.}}
\bigskip


\noindent
Let $\Omega$ be a bounded domain in
${\bf{R}}^3$.
A Green's function $G(x,y;\kappa)$ attached to this domain
and the PDE-operator $P(x,\partial_x;\kappa)$
is a function which for fixed $\kappa$ is a function in 
$\Omega\times\Omega$
with the following properties:
\[ 
G(x,y;\kappa)=0\quad\text{when}\quad x\in\partial \Omega\quad \text{and}\quad
y\in\Omega\tag{*}
\]
\[
\psi(y)=\int_\Omega\, (P^*(x,\partial_x)-\kappa^2)
(\psi(x))\cdot G(x,y;\kappa)\, dx\quad\colon\quad y\in\Omega\tag{**}
\]


\noindent
hold for all $C^2$-functions $\psi$ with compact support in
$\Omega$.
To find $G$ we 
solve  Dirchlet problems.
With
$\xi\in\Omega$ kept fixed one has the continuous function on
$\partial\Omega$:
\[ 
x\mapsto \Phi^*(x,\xi;\kappa)
\]



\noindent
Solving Dirchlet's problem gives  a unique $C^2$-function
$w(x)$ which satisfies:
\[ 
P(x,\partial_x)(w)+\kappa^2\cdot w=0 \quad\text{holds  in}\quad \Omega
\quad\text{and}\quad w(x)= \Phi(x,\xi;\kappa)\quad\colon x\in\partial\Omega=0
\]

\medskip

\noindent
From the above it is clear that
this gives the requested $G$-function, i.e. one has:

\medskip

\noindent
{\bf{2.1 Proposition.}} \emph{The 
the function }
\[ 
G(x,\xi;\kappa)=
\Phi(x,\xi;\kappa)-w(x)
\quad \text{satisfies}\quad (*-**)
\]


 
\noindent
Using the estimates for the $\phi$-function from § 1
we get
estimates for the $G$-function above.
Start with  a sufficiently large
$\kappa_0$ so  that 
$\Phi^*(x,\xi;\kappa_0)$ is a positive function of
$(x,\xi)$. Then the following hold:
\medskip


\noindent
{\bf{2.2 Theorem.}}
\emph{One has}
\[ 
G(x,\xi;\kappa_0)=
\frac{1}{\sqrt{\Delta(x)}\cdot\sqrt{\Phi(x,\xi;\kappa_0)}}
+R(x,\xi)
\]

\noindent
\emph{where the remainder function satisfies the following for all pairs
$(x,\xi)$ in $\Omega$:}
\[ 
|R(x,\xi)|\leq C\cdot |x-\xi|^{-\frac{1}{4}}
\]


\noindent
\emph{and the   constant $C$ only  depends on the  domain 
$\Omega$ and
the PDE-operator $P$.}
\medskip

\noindent
{\bf{Remark.}}
Above the negative power  of 
$|x-\xi|$ is  a fourth-root which means that  the remainder term $R$ 
is more regular  compared
to the first term which behaves like $|x-\xi|^{-1}$ on the diagonal $x=\xi$.

\medskip

\noindent
{\bf{2.3 Exercise.}} Prove Theorem 2.3 
If necessary, consult [Carleman: page xx-xx9 for details.

\medskip

\centerline {\bf{2.4 The integral operator
$\mathcal J$}}. 
\medskip


\noindent
With $\kappa_0$ chosen as above
we
consider the integral operator
which sends a function
$u$ in $\Omega$ to 
\[
\mathcal J_u(x)=\int_\Omega\, G(x,\xi;\kappa_0)\cdot u(\xi)\, d\xi
\]


\noindent
The construction of the Green's function gives:
\[
(P-\kappa_0^2)(\mathcal J_u)(x)=u(x)\quad\colon\quad x\in\Omega\tag{2.4.1}
\] 
In other words, if $E$ denotes the identity we have
the operator equality

\[
P(x,\partial_x)\circ \mathcal J_u=\kappa_0^2\cdot  \mathcal J+E\tag{2.4.2}
\]



\noindent
Consider pairs $(u,\gamma)$ such that 
\[
u(x)+ \gamma\cdot \mathcal J_u(x)=0\quad\colon\quad x\in\Omega\tag{2.4.3}
\] 
The vanishing from (*) for the $G$-function 
implies that $J_u(x)=0$ on $\partial\Omega$. Hence  every
$u$-function which satisfies
in (2.4.3) for some  constant $\gamma$
vanishes   on $\partial\Omega$.
Next, apply $P$ to (2.4.3) and then
the operator formula (2.4.2) gives

\[
0=P(u)+\gamma \kappa_0^2\cdot \mathcal J_u+\gamma\cdot u\implies
P(u)+(\gamma-\kappa_0^2)u=0
\]
\medskip

\noindent
{\emph{2.4.4 Conclusion.}}
Hence the boundary value problem (*) from 0.B
is equivalent to find eigenfunctions of 
$\mathcal J$ via (2.4.3) above.

\medskip

\noindent
\centerline {\bf{3. Almost reality of eigenvalues.}}
\medskip

\noindent
Consider the set of eigenvalues $\lambda$ to (*) in (0.B).
Then we have:

\medskip

\noindent
{\bf{3.1 Proposition.}}
\emph{There exist positive constants $C_*$ and $c_*$ such that
every eigenvalue  $\lambda$ to  (*) in (0.B) satisfies}

\[
|\mathfrak{Im}\,\lambda|^2\leq C_*(\mathfrak{Re}\,\lambda)+c_*)
\]
\medskip

\noindent
\emph{Proof.}
Let $u$ be an eigenfunction where
$P(u)+\lambda\cdot u=0$.
Stokes theorem and the vanishing of $u|\partial\Omega$
give:
\[
0=\int_\Omega\, \bar u\cdot (P+\lambda)(u)\,dx
=-\int_\Omega \, \sum_{p,q}\, a_{pq}(x)\cdot \frac{\partial u}{\partial x_p}
\frac {\partial \bar u}{\partial x_q}\, dx+
\int_\Omega\, \bar u\cdot( \sum \, a_p(x)
\frac{\partial u}{\partial x_p}\,)\, dx+
\] 
\[
\int_\Omega\, |u(x)|^2\cdot b(x)\, dx+
\lambda\cdot \int\, |u(x)|^2\, dx
\]
\medskip


\noindent
Write $\lambda=\xi+i\eta$.
Separating real and imaginary parts we find the two equations:
\[
\xi\int\, |u|^2\, dx=
\int\, \sum_{p,q} a_{p,q}(x)\,\frac{\partial u}{\partial x_p}\cdot 
\frac{\partial \bar u}{\partial x_q}\, dx+
\int\, \bigl(\frac{1}{2}\cdot \sum\, \frac{\partial a_p}{\partial x_p}- b\,\bigr )
\cdot |u|^2\, dx\tag{i}
\]
\[
\eta\int\, |u|^2\, dx=\frac{1}{2i}\int \sum\, a_p\bigl(
u\frac{\partial \bar u}{\partial x_p}-
\bar u \frac{\partial u}{\partial x_p}\,\bigl )\, dx\tag{ii}
\]


\noindent
Set
\[ A= \int\, |u|^2\,dx\quad\colon\quad
B= \int\, |\nabla(u)|^2\,dx
\]
Since $P$ is elliptic there exists a positive constant $k$ such that
\[
\sum_{p,q} a_{p,q}(x)\,\frac{\partial u}{\partial x_p}>
k\cdot |\nabla(u)|^2
\]
From this we see that (i-ii) gives positive constants $c_1,c_2,c_3$ such that
\[
A\xi>c_1B-c_2B\quad\colon\quad A|\eta|<c_3\cdot \sqrt{AB}\tag{iii}
\]
\medskip

\noindent
Here (iii) implies that $\xi>-c_2$ and the reader can also confirm that
\[ 
B<\frac{A}{c-1}(\xi+c-2)\quad\colon\quad
A|\eta|< A\cdot c_2\cdot \sqrt{\frac{\xi+c_2}{c_1}}\quad\colon\quad
|\eta|< c_3\cdot \sqrt{\frac{\xi+c_2}{c_1}}\tag{iv}
\]


\noindent Finally it is obvious that (iv) above gives the requested
inequality in Proposition 3.1.

\bigskip

\centerline{\bf{4. The asymptotic  formula.}}
\bigskip


\noindent
Using the results above
where we have found  a good control of the integral operator
$\mathcal J$ and the identification of eigenvalues to $\mathcal j$ and those from (*) in (0.B), one can proceed and apply Tauberian theorems to derive
the asymptotic formula  in Theorem 1 using 
similar methods as described in § XX where we treated
the Laplace operator. 
For details the reader may consult [Carleman:p age xx-xx].









\end{document}





\newpage


























