\documentclass{amsart}

\usepackage[applemac]{inputenc}

\addtolength{\hoffset}{-12mm}
\addtolength{\textwidth}{22mm}
\addtolength{\voffset}{-10mm}
\addtolength{\textheight}{20mm}

\def\uuu{_}

\def\vvv{-}

\begin{document}


\medskip

\noindent
{\bf{A.4.4 An example.}}
One is often confronted with severe 
difficulties in specific cases
because the Hahn Banach theorem is not constructive.
Consider for example a positive integer 
$N$ and let $\mathcal P_N$ denote  the $(N+1)$-dimensional
real vector space of polynomials  $P(t)$ of degree $\leq N$.
Define a linear functional  $\lambda_0$ on $\mathcal P_N$
by
\[
\lambda_0(P)=\sum_{\nu=1}^{\nu=M} \, c_\nu\cdot P(t_\nu)\tag{i}
\]
where $\{t_\nu\}$ and
$\{c_\nu\}$ are real numbers.
We can identify $\mathcal P_N$ with a subspace of
$X=C^0[0,1]$ where
$C^0[0,1]$ is the vector space of real-valued and continuous functions on
the unit interval $\{0\leq t\leq 1\}$.
On $X$ we get a $\rho$-function via the maximum norm, i.e.
\[ 
\rho(f)= \max_{0\leq x\leq 1}\, |f(x)|
\]
Next, there exists a unique smallest constant $C>0$ such that
\[
|\lambda_0(P)|\leq C\cdot \rho(P)\quad\colon P\in  \mathcal P_N
\]
Notice that $C$ exists even in the case when some
of the $t$-points in (i) are outside $[0,1]$.
By the result above we can extend $\lambda_0$ to a linear functional
$\lambda$ on $X$ and  the Riesz representation theorem  gives
a real-valued Riesz measure $\mu$ on $[0,1]$ such that
\[
\lambda_0(P)=\int_0^1\, P(t)\cdot d\mu(t)
\quad\colon P\in \mathcal P_N
\]
and at the same time the total variation of $\mu$ 
is equal to the constant $C$ above.
However, to determine $C$ and to find
$\mu$ requires a further analysis which leads to a
rather delicate problem in optimization thoery.
Already a case when
$M=1$ and we take $t_1=2$ and $c_1=1$
is highly non-trivial. Here we find a constant $C_N$ for each
$N\geq 2$ such that
\[ 
|P(2)|\leq C_N\cdot \rho(P)\quad
\quad\colon P\in \mathcal P_N
\]
I do not know how to determine $C_N$ and how to find
a Riesz measure $\mu_N$ whose total variation is $C_N$ while
\[
P(2)=\int_0^1\, P(t)\cdot d\mu_N(t)\quad\colon P\in \mathcal P_N
\]


\newpage



For every $p\geq 1$ one has the Banach space $\ell^p$ whose
vectors are sequences $x_1,x_2,\ldots$
of complex numbers for which
\[
\sum\, |x_\nu|^p<\infty
\]
A vector $x$ is said to be elementsry if every $x_\nu$ has abosluter value one and
only finitely many $x:\nu\neq 0$. 
Dnote by $\beta(x)$ the number of non-zero
components of an elementary vector. It is clear that
the $\ell^p$ norm is equal to the $p$:th root of $\beta(x)$.
Next, let $\mathcal M$ be a finite
family of elementary vectors $m_1,\ldots m_K$.
The integer $K$ is denoted by
${\bf{c}} (\mathcal M)$ and called the rank of $\mathcal M$.
If $T$ is a linear operator on $\ell^p$
its trace with respect to $\mathcal M$ is defined by
\[
\text{Trace}(T;\mathcal M)=\frac{1}{{\bf{c}} (\mathcal M)}\cdot
\sum_{k=1}^{k=K}\,
\beta(m_k)^{-1}\cdot \langle T(m_k),m_k\rangle
\]

\noindent
Next, following Enflo we consider
an infinite  family $\mathcal F=\{m_\nu\}$ of elementary vectors
which sre pairwise orthogonoal under the inner prduct from
(xx) above.
Let $B$ be the closed subspace of
$\ell^p$ generated by the vectors in $\mathcal F$.
With these notations one has:

\medskip

\noindent
{\bf{Proposition.}}
\emph{If $T\colon B\to B$ is a continous linear operator
with finite rank, i.e. $\dim T(B)<\infty$,
then}
\[
\lim_{{\bf{c}} (\mathcal M)\to+\infty}
\,\text{Trace}(T;\mathcal M)=0
\]
\emph{hold for finite subfamiles in $\mathcal F$ with increaing rank.}
\medskip

\noindent
The easy proof of Pripostion xx is left to the reader.
To get a Banach space nd compact operator which cannot be approximated eith
perstors of finite rank, Enflo  condtructed a  family
$\mathcal F$ with special properties. 
More precisely, he found
such a family and a sequence $\{\mathcal M_\nu\}$ if pairwise disjoint
finite subfamiles whhere
\[
\lim\,  {\bf{c}} (\mathcal M_\nu)=+\infty
\]
In additin there is a sequence of positive numers $\{\lambda_\nu\}$
where the series $\sum\,\lambda_\nu<\infty$, and a compact set $K$ in the Banach space
$B$
sich that

\[
\bigl|\text{Trace}(T;\mathcal M_{nu+1})-\text{Trace}(T;\mathcal M_\nu)\bigr|
\leq \lambda_\nu\cdot \max_{x\in K}\, ||Tx||
\]
hod for every $\nu\geq $ and every
bounded oinear oeprator $T$ on $B$.





\newpage







\centerline{\bf{Topics in functional analysis}}



\bigskip


\centerline {\bf{Contents}}
\bigskip



\noindent
\emph{1. Normed spaces}

\medskip

\noindent
\emph{2. Banach spaces}

\medskip

\noindent
\emph{3. Bounded linear operators}

\medskip

\noindent
\emph{4. A: Three basic priciples}



\medskip

\noindent
\emph{4. B: Weak topologies}



\medskip

\noindent
\emph{5. Dual vector spaces.}
 
\medskip

\noindent
\emph{6. Fredholm theory}

\medskip

\noindent
\emph{7. Calculus on Banach spaces}
 

\medskip

\noindent
\emph{8. Locally convex vector spaces}



\medskip

\noindent
\emph{9. Neumann's resolvent operators.}


\medskip

\noindent


\medskip

\noindent
\emph{11. Commutative Banach algebras.}






Results  from  topology, such as Baire's category theorem and
Tychonoff's theorem about products of compact spaces
are used in many situations.
Even if  basic results in functional analysis 
are established  in a rather straightforward manner their
merit is the generality. 
Let me also add  that much inspiration stems from
the text-books by Dunford and Schwartz about Linear Operators.
In fact, several proofs below are taken from this
impressive source  where the reader  finds
an extensive list of exercises and  instructive examples of
normed linear spaces which  are helpful to grasp
the general theory.



\medskip

\centerline {\bf{Advanced results.}}
\medskip

\noindent
The  reader who has mastered the basic theory is able to pursue proofs of 
results such as the 
Hille-Phillips-Yosida theorem sbout infinitesmal generators of
strongly continuous semi-groups in ¤ xx,  and Schauder's fixed point theorem in
¤ xx. Of course  many essential results  are not covered in 
these notes.
Non-linear maps between topological vector spaces is
for exampe   an extensive subject, as well as 
results deal about 
topological groups
which in general need not be commutative.
Here is an example of a result due to G. Birkhoff and Kakutani:
\medskip

\noindent
\emph{Let $G$ be a topological group
whose topology is metrizable, i.e. there exists some distance function
whose metric is equivalent to the given topology.
Then there exists a left invariant metric $d$, i.e.}
\[ 
d(gx,gy)= d(x,y)
\] 
\emph{hold for every triple $g,x,y$Êin $G$.}
\medskip

\noindent
A  notable point above is that the existence of $d$ is valid under the sole hypotheis that
the topology is metrizable, i.e. $G$ need not be a locally compact.                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                 Here are two results    about  continuous functions on the real line
whose proofs require methods beyond standard functional analysis, i.e. the general theory is not
"the end of the story".
\medskip











\noindent
{\bf{The Carleman-Weierstrass approximation theorem.}}
It asserts that if $f(x)$ is a continuous complex-valued function on
the real $x$-line then it can be uniformly approxmated by restrictions of
entire functions in the complex $z$-plane with $z=x+iy$. In other words, for
every $\epsilon>0$ there exists an entire function $G(z)$ such that
\[ 
\max_x\, |G(x)-f(x)|<\epsilon
\]
The proof appears in my notes devoted to the matheramtics by Carleman.
Notice that the result above goes beyond the ordinary result by Weierstrass since we 
obtain a uniform approximation on the whole real line.








\medskip



\noindent
{\bf{Beurling's closure theorem.}}
On the real $t$-line we
have the space of bounded and complex-valued  bounded 
and uniformly continuous functions $\psi$. It means that
to each $\epsilon<0$ there
exists $\delta>0$ such that
\[
\max\, |\psi(x)-\psi(x')|<\epsilon
\]
with the maximum taken over pairs of real numbers such that
$|x-x'|<\delta$.
Denote this space by  $C_*({\bf{R}})$.
If $\mu$ is a Riesz measure on the real $\xi$-line we define the
function
\[
\mathcal F_\mu(x)= \int\, e^{x\xi}\, d\mu(\xi)
\]
It is easily seen that   $\mathcal F\uuu\mu\in C_*({\bf{R}})$.
Denote by 
$\mathcal A$ be  subspace of $C_*({\bf{R}})$
given by $\mathcal F\uuu\mu$-functions as $\mu $ varies over 
all Riesz measures as above.
Before we announce Beurling's result  below we define  the notion
of weak\vvv star limits in $\mathfrak{M}$.
Let $\{\mu\uuu n\}$ be a bounded sequence of Riesz measures, i.e. 
there exists a constant such that
\[ 
||\mu\uuu n||\leq M
\]
hold for all $n$.
The sequence $\{\mu\uuu n\}$
converges in the weak-star sense
to zero if
\[
\lim\uuu{n\to\infty}\,\int\, e^{ix\xi}\cdot d\mu\uuu n(x)=0
\] 
holds pointwise for every $\xi$.
\medskip

\noindent
{\bf{Theorem.}} \emph{A function $\psi\in C\uuu *$ belongs to the closure of
$\mathcal A$ if and only if}
\[
\lim\uuu{n\to\infty}\,\int\, \psi(x)\cdot d\mu\uuu n(x)=0\tag{*}
\] 
\emph{whenever $\{\mu\uuu n\}$ is a sequence in $\mathfrak{M}$
which converges weakly to zero.}
\medskip


\noindent
{\bf{Remark.}}
Beurling's proof relies upon a certain non-linear
variational problem which
requires a quite deliate analysis and is exposed in
my notes entitled  \emph{Mathematics by Beurling.}




\bigskip


\noindent
{\bf{Introduction.}}
The   general theory about normed vector spaces, and more generally locally convex
spaces,
owes much to pioneering work by Banach, Krein and Smulian.
The beginner should pay  attentions to notion of dual
topological vector spaces since  
duality arguments often are used to prove existence theorems.
The determination of the dual space $X^*$ of a given normed vector space $X$
is therefore an important issue. 
Familarity with measure theory is assumed.
The reader may consult my notes on this topic as background
for the present chapter.



\medskip

\noindent
\emph{Remarks about general topology.}
The notion of compact topological spaces is
essential.
Here certain phenomena  can arise which
differ from wellknown facts   in euclidian spaces.
For example, start with the set ${\bf{N}}$ of non-negative
integers.
There exists the commutative Banach algebra $B$ whose vectors are bounded
complex valued functions on  ${\bf{N}}$ to be denoted by $\ell^\infty$.
Now there exists the maximal ideal space $\mathfrak{M}_B$ of
$B$ whose construction is given in ¤ xx. One  refers to
$\mathfrak{M}_B$  as the Gelfand space of $B$.
It is equipped with the Gelfand topology
which is constructed in such a way that
the space of continuous and complex-valued functions on
$\mathfrak{M}_B$
can be identfied with
$B$. Moreover,
it is a compact Hausdorff space where
${\bf{N}}$ appears as a dense and discrete subset.
In spite of the compactness
$\mathfrak{M}(B)$ 
fails to be \emph{sequentially compact}.
In fact, from  the countable subset
${\bf{N}}$ one \emph{cannot}  find a subsequence of integers
$1\leq n_1<n_2<\ldots$ which converges to a limit point 
$\xi\in\mathfrak{M}(B)$. To see this we construct the bounded function on
$f$ on ${\bf{N}}$ where $f(n_k)= (-1)^k$
while $f=0$ at integers outside the subsequence.
If $\{n_k\}$
converges to a point $\xi\in\mathfrak{M}(B)$ we must have
\[
\lim_{k\to\infty}\, f(n_k)= f(\xi)
\]
But this cannot  hold since $f$ changes  signs along to the subsequence.
In the opposite  direction
we mention that
there exist topological spaces $X$
which are non-compact while 
every countable subset contains at least one convergent subsequence.
Thus, $X$ is   \emph{sequentially  compact but not compact}.
See ¤ xx for an example.
This   shows that one often must
be careful about the notion of compactness.
\medskip

\noindent
Examples of such "ugly compact topological spaces"
illustrate that
certain "positive results" due to Eberlein and Smulian 
are highly non-trivial. In ¤ xxx we prove that 
if
$X$ is a Banach space and $X$ is equipped with the weak topology, then
every weakly compact subset is
sequentially compact, and conversely, if we start from
a subset $A$ in $X$ with the property
that every countable 
sequence of vectors in $A$ has a subsequence which converges in the weak topology to a limit vector in $X$, then
the closure of $A$ taken in the 
weak topology is compact.

\bigskip

\noindent
\emph {Compact metric spaces.}
To avoid possible confusion we
recall the notion of  compactness on a metric space
which goes back to Heine and Bolzano.
Let $S$ be a metric  space where $d$ is the distance function.
A closed subset $K$ is totally bounded in  Heine's sense
if there to every $\epsilon>0$ exists
a finite subset
$\{x_1,\ldots,x_N\}$ in $K$ such that
$K$ is covered by the union of the open balls
$B_\epsilon(x_k)= \{ x\colon\, d(x,x_k)<\epsilon\}$.
A wellknown fact  whose verification is left
to the reader asserts that a
closed subset $K$ is totally bounded
if and only if it is compact in the sense of Bolzano, i.e.
every sequence $\{x_n\}$ in $K$ contains at least one convergent subsequence.












\newpage



\centerline{\bf{Summary of the contents.}}
\bigskip


\noindent
Hilbert spaces are treated in a special chapter.
One reason is that
the geometry in Hilbert spaces leads to  results which have no 
counterpart in general normed spaces,  and at the same time
the material in the present chapter is
often trivial when one regards Hilbert spaces.
¤ 1  studies normed vector spaces
over the complex field
${\bf{C}}$ or the real field
${\bf{R}}$. 
We
explain how each norm  is defined
by a convex subset of $V$ with 
special properties.
If  $X$ is a normed vector space
such that every
Cauchy sequence with respect to the norm $||\cdot||$
converges to some vector in $X$ one
says that the norm is complete and refer to
the pair $(X,||\cdot||)$ as a Banach space. 

\medskip





\noindent 
{\bf Dual spaces.}
When
$X$ is a normed linear space one constructs the  linear
space $X^*$ whose elements are continuous linear functionals
on $X$.
The Hahn-Banach Theorem 
identifies norms of vectors in
$X$ via evaluations by $X^*$-elements. More precisely, denote by
$S^*$ the unit sphere in
$X^*$, i.e. 
linear functionals
$x^*$  of unit norm.
Then
one has the equality
\[
 ||x||=\max_{x^*\in S^*}\, |x^*(x)|\quad \,\text{for all}\,\, x\in X\,.\tag{i}
\]
The dual space $X^*$ is used to construct the 
\emph{weak topology} on $X$.
The detailed construction appears in ¤ xx.
In ¤ 5.5.4 we show that when $X$ has infinite dimension, then the norm topology is strictly
stronger than the weak topology.
However, for convex sets a special result hold.
Using a  separation theorems for convex sets it follows that 
a convex subset in $X$ is weakly closed if and only if it is closed in
the norm topology.
In  ¤¤
we prove a result due to Eberlien and Smulian about
weakly compact sets in $X$.
An important consequence 
of Theorem ¤ xxx is that if $A$ is a subset of
$X$ which is compact in the weak topology, then
the closure of its convex hull, taken in the weak topology is also compact.
\medskip


\noindent
Next, on the dual space $X^*$ there exists the
\emph{weak-star topology}
where Thychonoff's theorem is used to prove that
the unit ball in $X^*$ is compact with respect to the weak-star topology.
In ¤ xxx we prove a  theorem  due to
Krein and Smulian about the 
\emph{bounded weak-star topology} where the major result is
that when $X^*$ is equipped with this topology, then its dual
can be identfied with the given Banach space $X$.


 \medskip

\noindent{\bf{Reflexive spaces.}}
Starting from a normed  space $X$ we get 
the Banach space $X^*$ 
whose  dual 
is  denoted by $X^{**}$ and called the bi-dual of $X$.
There is  a natural injective map 
\[
\mathfrak{i}_X\colon X\to X^{**}
\]
and (i) above shows that it  is an isometry, i.e.
the norms $||x||$ and $||\mathfrak{i}_X(x)||$ are equal.
But in general the bi-dual embedding map
is nor surjective.
If it is surjective   one says that $X$ is reflexive.
It is of course intructive  to
learn about examples, both of reflexive as well as non-reflexive
Banach spaces.
An example which was put forward by Stefan Banach is to take
$X={\bf{c}}_0$ whose vectors are 
sequences of complex numbers
$\{c_\nu\}$ which tend to zero as $\nu\to+\infty$
and the norm is defined to be the supremum of thier absolute values.
It turns out that the dual $X^*=\ell^1$ whose vectors are
absolutely oonvergent sequences, while the bi-dual
becomes $\ell^\infty$ where arbitary bounded
sequences of complex numbers yield vectors.

\medskip

\noindent{\bf{Compact operators.}}
Let $X$ and $Y$ be a pair of Banach spaces.
A bounded linear operator $T\colon X\to Y$
is compact if the image of the unit ball $B(X)$  in $X$ is relatively compact in
$Y$.
In applications one often encounters compact operators
and several facts about these operators occur in ¤ 6
where the crucial results deal with Fredholm operators
and culminate with Fredholm's index theorem.
When the target space $Y= C^0(S)$
a classic result due to
Arzela and Vitali asserts that $T(B(X))$ is relatively compact if and only
if this family is equi-continuous, i.e. to each $\epsilon>0$ there
exists $\delta>0$ such that
\[
\max_{x\in B(X)}\,\omega_{Tx}(\delta)\leq\epsilon
\]
where we introduced the modulus of continuity, i.e if
$f\in C^0(S)$ and $\delta>0$ then
\[
\omega_f(\delta)=\max\, |f(y_1)-f(y_2)|\quad \colon
\, d(y_1,y_2)<\epsilon
\]
In ¤ xx we prove a result due to Schauder
which asserts that  if $T\colon X\to Y$
is a compact operator between a pair of Banach spaces, then
its adjoint $T^*\colon X^*\to Y^*$ is also compact.
The  proof relies upon
the Krein and Smulian theorem in ¤ xx.
Smulian proved this result in 1940
but it was not until 1972
that a perspective upon this result was fully understood
when Enflo constructed a
pair $(X,T)$ where $X$ is a separable Banach space and
$T\colon X\to X$ is a compact operator, and yet $T$ cannot be approximated
in the operator norm by linear operators with finite dimesnsional range.
Enflo's work [Acta 1972] is one of the greatest achievements about 
geometry on topological
vector spaces and has created a veritable industry where
one seeks to determine when a given Banach space has the approximation property in
the sense that every compact operator can be approximated by finite range
operators.
Let us remark that
Enflo constructed Banach spaces $B$ for which the approximation property
fails, where $B$ can be taken as a closed subspace of
$\ell^p$ for every $p>2$, and scrutinizing Enflo's
construction one can conclude that 
the approximation property fails for  "generic subspaces" of 
$\ell^p$.
But fortunately most Banach spaces which appear in applicstions
have the approximation property
and as a consequence also posses a  Schauder basis.

















\medskip

\noindent
{\bf Calculus on Banach spaces.}
Let $X$ and $Y$ be two Banach spaces.
In ¤ 7  we define
the differential of a $C^1$-map $g\colon\,X\to Y$ where
$g$ in general is non-linear.
Here the 
differential of $g$ at a  point
$x_0\in X$ is a bounded linear operator from
$X$ into $Y$. This extends the construction of
the Jacobian  for a $C^1$-map from
${\bf{R}}^n$ into ${\bf{R}}^m$
expressed by an $m\times n$-matrix.
More generally one constructs higher order differentials and 
refer to $C^\infty$-maps from one Banach space into another.
We shall review this 
in ¤ 7.  Let us  remark that 
Baire's category theorem together with the Hahn-Banach theorem
show that if $S$ is an arbitrary  compact metric  space and
$\phi$ is a continuous function on $S$ with values
in a normed space
$X$, then $\phi$ is \emph{uniformly continuous}, i.e. to
every
$\epsilon>0$ there exists $\delta>0$ such that
\[
d_K(p,q)\leq\delta\implies
||\phi(p)-\phi(q)||\leq\epsilon
\]
where $d_S$ is the distance function on
the metric space $S$
and in 
the right hand side we have taken the norm in $X$.
Next,  there exists  a distinguished class
of differentiable Banach spaces.
By definition a Banach space $X$ is differentiable at a point $x$
if there exists a linear functional $\mathcal D\uuu x$ on $X$
such that
\[
\mathcal D\uuu x(y)=
||x+\zeta\cdot y||\vvv ||x||=\mathfrak{Re}\, (\zeta\cdot
\mathcal D\uuu x(y))+\text{small ordo}(|\zeta|)\tag{*}
\]
hold for every $y\in X$ where the limit is taken over complex
$\zeta$ which tend to zero.
One says that $X$ is differentiable if $\mathcal D\uuu x$ exist
for every $x\in X$. This notion was introduced by Clarkson in 1936.
In ¤ XX  
we expose a theorem  due to Beurling and Lorch
concerned with certain non-linear duality maps
on uniformly  convex and differentiable Banach spaces.





\bigskip

\noindent
{\bf{Borel-Stieltjes integrals.}}
Let  $\mu$
be  a Riesz measure on the unit interval $[0,1]$ and  consider
an $X$-valued function, which to every
$0\leq t\leq 1$ assigns a vector $f(t)$ in $X$. Assume that  
there exists a constant $M$ where
\[
 \max_{0\leq t\leq 1}\,||f(t)||=M
\]
i.e the function is bounded with respect to the norm on $X$.
In addition we assume that the 
the complex-valued functions
$t\mapsto x^*(f(t))$ are Borel functions on $[0,1]$ 
for every $x^*$ in the dual space $X^*$.
Measure theory teaches that there exist the Borel-Stieltjes integral
\[ 
J(x^*)= \int_0^1\, x^*(f(t))\, d\mu(t)
\] 
for every $x^*$.
The boundedness of $f$ implies that
\[
x^*\mapsto J(x^*)
\]
is a continuous linear functional on
$X^*$. This  gives
a vector $\xi(f)$ in the bi-dual $X^{**}$
such that
\[
\xi(f)(x^*)= J(x^*)\quad\colon\quad x^*\in X^*\tag{1}
\]
Notice that (1) is found for every nomed space $x$, i.e. above $X$ need not be
a Banach space. In the special case when 
 $X$ is a reflexive Banach space 
the  $f$-integrals yields a vector in $x=x(\mu,f)\in X$
which computes (1), i.e.
\[
x^*(x(\mu,f)))= \int_0^1\, x^*(f(t))\,d\mu(t) \quad\colon
x^*\in X
\]
The map
\[
(\mu,f)\mapsto x(\mu,f)
\]
is bi-additive.
The family of $X$-valued functions $f(t)$ for which
(*) hold and in addition $t\mapsto x^*(f(t)$ are Borel functions for
every $x^*\in X^*$ are called bounded Borel funcction with vlues in $X^*$.
The fact that one can assign integrals above is used in many applications.
Of course,  avove one could have replaced the unit
interval $[0,1]$
by other topological spaces on which 
the notion of Riesz meaaures exists. For example,
$[0,1]$ could be replaced by an arbitrary compact metric space.






\bigskip








\noindent
{\bf Analytic functions.} Let $X$ be a Banach space
and 
consider a power series with coefficients in $X$:
\[ 
f(z)=\sum_{\nu=0}^\infty\, b_\nu\cdot z^\nu\quad\, b_0,b_1,\ldots
\,\,\text{is a sequence in}\,\,  X\,.\tag{i}
\]
Let $R>0$ and suppose there exists
a constant $C$ such that
\[ 
||b_\nu||\leq C\cdot R^\nu\quad\colon\,\nu=0,1,\ldots\tag{ii}
\]
Then the series (i) converges when $|z|<R$ and 
$f(z)$ is called an $X$-valued analytic function in the open disc
$|z|<R$.
More generally, let $\Omega$ be an open set in
${\bf{C}}$. An $X$-valued function $f(z)$
is analytic if there to every
$z_0\in\Omega$
exists an open disc $D$ centered at $z_0$ 
such that the restriction of $f$ to $D$ is represented by
a convergent power series
\[ 
f(z)=\sum\, b_\nu(z-z_0)^\nu
\] 
Using the dual space
$X^*$
results about ordinary analytic functions
extend to $X$-valued analytic functions.
Namely, for each fixed
$x^*\in X^*$
the complex valued function
\[ 
z\mapsto x^*(f(z))
\]
is analytic in $\Omega$.
From this one recovers the Cauchy formula.
For example, let $\Omega$ be a domain in the class
$\mathcal D(C^1)$ and  $f(z)$  is an analytic $X$-valued function in
$\Omega$ which extends to a continuous $X$-valued function on
$\bar\Omega$.
If $z_0\in\Omega$ there exists the complex line integral
\[ \int_{\partial\Omega}\, \frac{f(z)dz}{z-z_0}
\]
It is evaluated by  sums just as for a  Riemann integral
of  complex-valued functions. One simply 
replaces  absolute
values of complex valued functions by
the norm on $X$  in  approximating sums which converge to the
Riemann integral. This gives  Cauchy's integral 
formula, extended to $X$-valued analytic functions:
\[
f(z_0)= \int_{\partial\Omega}\, \frac{f(z)dz}{z-z_0}\,.
\]


\bigskip


\noindent
{\bf Operational calculus}.
Commutative Banach algebras are  defined and studied in 
¤ 10.
If $B$ is a commutstive Banach algebra with a unit element $e$
and
$x\in B$, then we shgall prove that the spectrum
$\sigma(x)$ is  a non-empty  compact subset of
${\bf{C}}$ and  there exists 
the  resolvent map:
\[
\lambda\mapsto R_x(\lambda)= (\lambda\cdot e-x)^{-1}\quad\colon\quad
\lambda\in{\bf{C}}\setminus\sigma(x)\tag{i}
\]
If
$\lambda_0\in {\bf{C}}\setminus\sigma(x)$
one contructs  the local Neumann series which
represents $R_x(\lambda)$
when $\lambda$ stays in the open disc of
radius $\text{dist}(\lambda_0,\sigma(x))$.
It follows that $R_x(\lambda)$ is a $B$-valued
analytic function of the complex variable $\lambda$ defined in the open 
complement of
$\sigma(x)$.
Starting from this, Cauchy's formula gives
vectors  in $B$ for every   analytic function
$f(\lambda)$  defined in some open neighborhood of
$\sigma(x)$.
More precisely, denote by
$\mathcal O(\sigma(x))$ the algebra of 
germs of analytic functions on the compact set
$\sigma(x)$.
It turns out that
there exists
an algebra homomorphism
from $\mathcal O(\sigma(x))$ into $X$ which sends
$f\in \mathcal O(\sigma(x))$ into an element $f(x)\in X$.
Moreover,
the \emph{Gelfand transform} of $f(x)$
is related to that of $x$ by the formula
\[
\widehat f(x)(\xi)= f(\widehat x(\xi))\quad\colon\quad
\xi\in\mathfrak{M}_B\tag{*}
\]
These  general results   are  used in many applications. An example is
when $B$
is the Banach algebra generated 
by a single bounded linear operator on a Banach space.
\medskip

\noindent
{\bf{Neumann's resolvents.}}
A special section is devoted to the powerful and extremely important
study of densely defined
linear operators on a Banach space which need not be 
bounded.
It turns out that for such an operator $T$
there exists a well-defined closed spectral set $\sigma(T)$
and in its open complement one find
an analytic function oif a complex parameter $\lambda$
which gives inverses to $\lambda\cdot E-T$ in
the sense of Carl Neumann, where $E$ denotes the identity operator on
$X$.
The constructions in ¤ 10 dealing with commutative Banach algebras is
a special case of the Neumann calculus.
Spectral theory about - in general unbounded - linear oeprators
is a major topics where functional analysis 
finds useful applications.
It is here the reader will encounter challenging problems and
remarkable results.
The material about semi-groups in ¤ xx is an example where
we prove a theorem due to Hille, Phillips and Yosida
where unbounded operators appear
whose spectral and Neumann resolvents have
special properties.







\newpage

\centerline {\bf 1. Normed spaces.}

\bigskip

\noindent
A norm on  a complex vector space
$X$  is 
a map
from $X$ into ${\bf{R}}^+$ satisfying:
\[
||x+y||\leq
||x||+||y||\quad\text{and}\quad 
||\lambda\cdot x||=|\lambda|\cdot
||x||\quad\colon\quad x,y\in X\quad\colon\,\,\lambda\in{\bf{C}}\tag{*}
\]
Moreover  $||x||>0$ holds for every $x\neq 0$.
A norm gives a topology on $X$ defined by the distance function
\[ d(x,y)=||x-y||\tag{**}
\]


\noindent
{\bf 1.1 Real versus complex  norms.}
The field of real numbers is a subfield of
${\bf{C}}$. Hence every complex vector space
has an underlying structure as a vector space over
${\bf{R}}$.
A norm on a  real vector space
$Y$
is a function $y\mapsto ||y||$
where (*)
holds for real numbers $\lambda$.
Next, let  $X$ be a complex vector space
with a norm $||\cdot ||$.
Since we can take $\lambda\in{\bf{R}}$ in (*)
the complex norm induces a
real norm on the underlying
real vector space of $X$.
Complex norms are  more special than real norms.
For example, consider the 1-dimensional complex vector space
${\bf{C}}$.  When the point 1 has norm one 
the norm of a complex vector $z=a+ib$ is its
absolute value. On the other hand we can define
many norms on
the underlying real $(x,y)$-space. For example, we may
take the norm defined by
\[ 
||(x,y)||=|x|+|y|\tag{i}
\]
It fails to satisfy
(*) under complex multiplication. For example,
with
$\lambda=e^{\pi i/4}$ we send $(1,0)$ to
$p=(\frac{1}{\sqrt{2}},
\frac{1}{\sqrt{2}})$ whose norm from (i) becomes
$\sqrt 2$
while it should remain with norm one if
(*) holds.



\medskip

\noindent
{\bf 1.2 Norms defined via convex sets.} Consider 
a real vector space $Y$.
A subset $K$  is convex if
the line segment formed by a pair of points in $K$
stay in $K$, i.e.
\[ 
y_1,y_2\in K\implies s\cdot y_2+(1-s)\cdot y_1\in K\quad\colon\quad
0\leq s\leq 1\tag{i}
\]
Let ${\bf{o}}$ denote the origin in $Y$.
Let $K$ be a convex set which
contains ${\bf{o}}$  and is symmetric with respect to
${\bf{o}}$:
\[ 
y\in K\implies -y\in K
\]
We say that $K$ is called  \emph{absorbing} if there to every
$y\in Y$ exists some $t>0$ such that $ty\in K$.
Suppose that $K$ is symmetric and absorbing.
To every $s>0$ we set
\[ 
sK=\{ sx\,\colon\,\, x\in K\}
\]
Since ${\bf{o}}\in K$ and $K$ is convex  these
sets increase with $s$ and since
$K$ is absorbing we  have:
\[
\bigcup_{s>0}\, sK=Y\tag{ii}
\]
Next,  impose also  the condition that $K$ does not contain
any 1-dimensional subspace, i.e. whenever
$y\neq 0$ is a non-zero vector
there exists  some large $t^*$ such that $t^*\cdot y$ does not
belong to $K$. The condition is equivalent with
\[ 
\bigcap_{s>0}\, 
s\cdot K={\bf{o}} \tag{iii}
\]



\noindent {\bf 1.3 The norm $\rho_K$.}
Let $K$ be convex and 
symmetric and   (ii-iii) hold. To each $y\neq 0$
we set
\[
\rho_K(y)=\min_{s>0}\, y\in s\cdot K\tag{*}
\]
If $y\in K$ then
$s=1$ is competing when we seek the minimum and hence
$\rho_K(y)\leq 1$. On the other hand, if $y$ is "far away" from $K$
we need large $s$-values to get $y\in s\cdot K$
and therefore
$\rho_K(y)$ is large. It is  clear that
\[
\rho_K(ay)=a\cdot\rho_K(y)\quad\colon\ a\,\,\text{real and positive}\tag{i}
\]
Morover, since $K$ is symmetric we have $\rho_K(y)=\rho_K(-y)$  and hence (i) gives
\[
\rho_K(ay)=|a|\cdot\rho_K(y)\quad\colon\ a\,\,\text{any real number}\tag{ii}
\]

\medskip


\noindent
Next, the convexity of $K$ gives the inclusion
\[
s\cdot K+t\cdot K\subset (s+t)\cdot K
\]
for every pair of positive numbers.
Indeed, with $x$ and $y$ in $K$ one has 
\[
\frac{sx}{s+t}+ \frac{ty}{s+t}\in K
\] 
and (iii) follows.
The reader can check that the  construction of $\rho_K$
gives the triangle inequality
\[ 
\rho_K(y_1+y_2)\leq \rho_K(y_1)+\rho_K(y_2)\tag{iii}
\]
We conclude that $\rho_K$ yields a norm on $Y$.

\medskip

\noindent
{\bf 1.4 A converse result.} If $||\cdot||$ is  a norm
on $Y$ we get the  convex set
\[ 
K^*=\{ y\in Y\quad\colon\,||y|\leq 1\}
\]
It is clear that $\rho_{K^*}(y)=||y||$ holds, i.e. the given
norm is recaptured by the norm defined by $K^*$.
We can also regard the set
\[
K_*=y\in Y\quad\colon\,||y|< 1\}
\]
Here $K_*\subset K^*$
but the reader should notice
the equality
\[
\rho_{K_*}(y)=\rho_{K^*}(y)
\]
Thus, the two convex sets define the same norm
even if the set-theoretic inclusion
$K_*\subset K^*$ may be strict.
In general, a pair of convex sets $K_1,K_2$
satisfying (ii-iii) in ¤ 1.2  are said to be 
equivalent if they define the same norm.
Starting from this norm we get $K_*$ and $K^*$ and then
the reader may verify that
\[
K_*\subset K_\nu\subset K^*\quad\colon \nu=1,2
\]


\noindent
\emph{Summing up} we have described all norms
on $Y$ and   they are in a 1-1 correspondence with
equivalence classes in the family
$\mathcal K$  of  convex
sets which are symmetric and satisfy (ii-iii) from ¤ 1.2.
\bigskip

\noindent
{\bf 1.5 Equivalent norms.}
Two norms $||\cdot||_1$ and $||\cdot||_2$ are equivalent if there
exists a constant $C\geq 1$ such that
\[
\frac{1}{C}\cdot ||y||_1\leq ||y||_2\leq C\cdot ||y||_1\quad\colon\quad\tag{1.5.1}
y\in Y
\]
Notice that if the norms are defined by convex
sets $K_1$ and $K_2$ respectively, then 
(0.6) means that there exists some $0<t<1$ such that
\[ 
tK_1\subset K_2\subset t^{-1}K_1
\]
\medskip


\noindent{\bf 1.6 The case $Y={\bf{R}}^n$}.
If $Y$ is finite dimensional all norms are equivalent. To
see this we consider  the euclidian basis $e_1,\ldots, e_n$.
To begin with we have  the \emph{euclidian norm}
which  measures the euclidian length
from a vector $y$ to the origin:
\[
||y||_e=\sqrt{\,\sum_{\nu=1}^{\nu=n}\,|a_\nu|^2}\quad\colon\quad
y=a_1e_1+\ldots+a_ne_n\tag{i}
\]
The reader should verify that (i)
satisfies the triangle inequality
\[
||y_1+y_2||_e\leq ||y_1||_e+||y_2||_e
\]
which  amounts to verify the Cauchy-Schwartz inequality.
We have also  the norm $||\cdot ||^*$ defined by
\[ 
||y||^*=\sum_{\nu=1}^{\nu=n}\,|a_\nu|\quad\colon\quad
y=a_1e_1+\ldots+a_ne_n\tag{ii}
\]
This norm is equivalent to the euclidian norm. More precisely
the reader may verify the inequality
\[
\frac{1}{\sqrt{n}}\cdot ||y||_e\leq
||y||^*\leq\sqrt{n}\cdot ||y||_e\tag{iii}
\]
\medskip

\noindent
Next, let 
$||\cdot||$ be some arbitrary norm. Put
\[ 
C=\max_{1\leq \nu\leq n}\, ||e_\nu||\tag{iv}
\]
Then (ii) and the triangle inequality for the norm
$||\cdot||$ gives
\[ 
||y||\leq C\cdot ||y||^*\tag{v}
\]
\medskip

\noindent
By the equivalence (iii) the norm topology defined by
$||\cdot||^*$ is the same as the usual euclidian topology in
$Y={\bf{R}}^n$.
Next, notice  that (v) implies that the sets
\[ 
U_N=\{ y\in Y\quad\colon\quad ||y||<\frac{1}{N}\}\quad\colon\quad
N=1,2,\ldots
\]
are \emph{open} sets when  $Y$ is equipped with its usual euclidian topology.
Now $\{U_N\}$ is an increasing sequence of open sets
and their union is obviously equal t o$Y$.
in particular this union covers the compact
unit sphere $S^{n-1}$. This gives an integer $N$ such that
\[ 
S^{n-1}\subset U_N
\]
This inclusion gives
\[ 
||y||_e\leq N\cdot ||y||
\]
Together with (iii) and (v) we conclude that
$||\cdot||$is equivalent with $||\cdot||_e$.
Hence we have proved
\medskip

\noindent 
{\bf 1.7 Theorem.}
\emph{On a finite dimensional vector space all norms
are equivalent.}

\bigskip

\noindent{\bf 1.8 The complex case.}
If $X$ is a complex vector space
we obtain complex norms via
convex
sets $K$ which not only are symmetric with
respect to scalar multiplication with
real numbers, but is also invariant under multiplication
with complex numbers
$e^{i\theta}$ which  entails that
\[ 
\rho_K(\lambda\cdot x)= \lambda\cdot \rho_K(x)
\] 
hold for every complex number
$\lambda$, i.e. we get a norm on the complex vector space.
 \bigskip
 
 


\centerline {\bf 2. Banach spaces.}
\medskip


\noindent
Let $X$ be a normed space over ${\bf{C}}$ or over
${\bf{R}}$.
A sequence of vectors
$\{x_n\}$
is called a Cauchy sequence if
\[ 
\lim_{n,m\to\infty}\, ||x_n-x_m||=0\tag{*}
\]
We obtain a vector space
$\widehat X$ whose vectors are defined as equivalence classes of Cauchy sequences.
The norm of a Cauchy sequence $\{x_n\}$ is defined by
\[
\{x_n\}=\lim_{n\to\infty}\,||x_n||
\]


\noindent
One says that the  norm on $X$
is complete if every
Cauchy sequence converges, or equivalently $X=\widehat X$.
A complete normed space is  called a \emph{Banach space}
as an  attribution to Stefan Banach whose
article [Ban] introduced the general concept of
normed vector spaces.

\bigskip

\noindent
{\bf 2.1 Separable Banach spaces.}
A Banach space $X$ 
which contain a denumerable and dense subset $\{x_n\}$
is called separable.
If this holds we get for each
$n$ the finite dimensional subapce
$X_n$ generated by
$x_1,\ldots,x_n$ and 
one constructs  a basis in each $X_n$ which gives the existence 
of 
a denumarable sequence of linearly independent vectors
$e_1,e_2,\ldots$ such that the increasing sequence 
$\{X_n\}$ are all  contained in
the vector space
\[
X_*= \oplus \,{\bf{R}}\cdot e_n\tag{i}
\]
By this construction    $X_*$ is a dense subspace of $X$.
There are many ways to construct a denumerable
sequence of linearly independent vectors which 
give a dense subspace of $X$ and 
one may ask if it is possible to choose
a sequence $\{e_n\}$  such that
every $x\in X$ can be expanded  as follows:
\medskip


\noindent
{\bf {2.2 Definition.}}
\emph{A denumerable sequence $\{e_n\}$
of ${\bf{C}}$-linearly independent vectors
in a complex vector space $X$
is called a Schauder basis 
if there to each $x\in X$
exists a unique sequence of complex  numbers
$c_1(x),c_2(x),\ldots$ such that}
\[
\lim_{N\to \infty}\,
||x-\sum_{n=1}^{n=N}\, c_\nu(x)\cdot e_\nu||=0
\]
\medskip

\noindent
{\bf 2.3 Enflo's example.}
The existence of a Schauder basis in every separable Banach space
appears to be natural and 
Schauder constructed such a basis in 
the Banach space
${\bf{C}}^0[0,1]$ of continuous functions on the closed unit interval 
equipped with the maximum norm.
For several decades the question of existence of a Schauder basis in
every separable Banach space was open until
Per Enflo at seminars in Stockholm University
during  the autumn in   1972 presented an
example where a Schauder basis does not exist.
For the  construction
we refer to the   article [Enflo-Acta Mathematica]. 
After  [Enflo]
it became a veritable industry to
verify that various concrete Banach spaces $Y$
do have a Schauder basis and perhaps more important, also enjoy the
approximation property , i.e. that 
the class of linear operators on $Y$ with
finite dimensional range is dense in the linear
space of all compact
operators on $Y$. Fortunately most Banach spaces 
do have a Schauder basis. But the construction of a specific Schauder basis
is 
often non-trivial. It requires for example considerable work to exhibit a 
Schauder basis in the disc algebra 
$A(D)$ of continuous functions on the closed unit disc which
are analytic in the interior.





\newpage

\centerline {\bf 3. Linear operators.}
\medskip

\noindent
Let $X$ and $Y$ be two normed spaces and 
$T\colon\,X\to Y$  a linear operator. We say that
$T$ is continuous if there exists a constant $C$ such that
\[ 
||T(x)||\leq C\cdot ||x||
\]
where the norms on $X$ respectively $Y$ appear.
The least constant $C$ for which this holds is denoted by
$||T||$ and called the operator norm of $T$.
Denote by $\mathcal{L}(X,Y)$ the set of all continuous linear operators
from $X$ into $Y$. From the above it is
equipped with the norm
\[
||T||=\max_{||x||=1}\, ||T(x)||\quad\colon\,
\tag{*}
\]
Above  $X$ and $Y$ are not necessarily Banach spaces.
But one verifies easily that if
$\widehat X$ and $\widehat Y$ are their completitions, then
every $T\in\mathcal{L}(X,Y)$ extends in a unique way
to a continuous linear operator
$\hat T$ from $\hat X$ into $\hat Y$. Moreover, if $Y$ from the start is a Banach space
and $T\in\mathcal L(X,Y)$ then it extends in a unique way to a
bounded 
linear operator from
$\widehat X$ into $ Y$.
Finally the reader may verify the following:

\medskip

\noindent
{\bf 3.1 Proposition.}
\emph{If $Y$ is a Banach space then
the  norm on
$\mathcal {L}(X,Y)$ is complete, i.e. this
normed vector space is a Banach space.}
\medskip

\noindent
{\bf {3.2 Null spaces and the range.}}
Let $X$ and $Y$ be two Banach spaces and
$T\in\mathcal{L}(X,Y)$. In $X$ we get the subspace
\[
\mathcal{N}(T)=\{ x\colon\, T(x)=0\}
\]
Since $T$ is continuous 
the kernel is a closed subspace of $X$ and we
get the quotient space
\[
\bar X=\frac{X}{\mathcal{N}(T)}
\]
It is clear  that $T$ yields a linear operator
$\bar T$ from $\bar X$ into $Y$ which by the construction of
the quotient norm on $\bar X$ has the same norm as
$T$.
Next, consider the range  $T(X)$ and notice the equality
\[ 
T(X)=\bar T(\bar X)\tag {i}
\]
One says that $T$ has  \emph{closed range} if the linear subspace
$T(X)$ of $Y$ is closed. When this holds
the complete norm on $Y$ induces a complete
norm on  $T(X)$. In ¤4   we prove the \emph{Open Mapping Theorem}
which shows that if $T$ has closed range then there exists
a constant $C$
such that for every vector $y\in T(X)$ there exists $x\in X$ with
$y=Tx$ and
\[
||x||\leq C\cdot ||y||\tag{3.2.1}
\]
 
\newpage    



delete   xxxxxxxx

\noindent
{\bf 3.3 The closed graph theorem }
Let $X$ and $Y$ be Banach spaces and  $T$  a linear
operator from $X$ into $Y$. For the moment we do not assume that it is bounded.
In the product space $X\times Y$ we get the graph
\[
\Gamma_T=\{(x,T(x))\quad\colon\, x\in X\}
\]

\noindent
{\bf 3.4 Theorem.}
\emph{Let $T$ be a linear operator from one Banach space $X$ into another 
Banach space $Y$
with a closed graph $\Gamma_T$. Then $T$ is continuous.}
\medskip


\noindent
\emph{Proof.}
We have the surjective map
\[ x\mapsto (x,Tx)
\] 
from $X$ onto the graph.
By assumption $\Gamma_T$ is a closed subspace of
the Banach space $X\oplus Y$ equipped with the norm
\[
||(x,Tx)||= ||x||+ ||Tx||
\]
The Open Mapping Theoren gives a constant $C$ such that
 \[
||x||+ ||Tx||\leq C||x||\implies ||Tx||\leq (C-1)||x||
 \]
and
hence $T$ is bounded.



\newpage

\centerline {\bf 3.5 Densely defined and closed operators.}
\medskip

\noindent
Let $X_*\subset X$ be a dense subspace and
$T\colon\, X_*\to Y$
a linear operator where  $Y$ is a Banach space. As above we construct the graph
\[
\Gamma_T=\{(x,y)\colon\quad x\in X_*\,\colon\, y=T(x)\}
\]
If $\Gamma_T$ is a closed subspace of $X\times Y$
we say that the densely defined operator
$T$   is  closed. 
\medskip

\noindent
{\bf 3.6 Example.}
Let $X=C^0_*[0,1]$
be Banach space whose elements are continuous functions
$f(x)$ on the closed interval $[0,1]$ with $f(0)=0$.
The space $X_*=C^1_*[0,1]$ of continuously differentiable functions
appears as a dense subspace of $X$.
Let $Y=L^1[0,1]$ which gives
a linear map $T\colon\, X_*\to Y$ defined by
\[ 
T(f)=f'\quad\colon\quad f\in C^1_*[0,1]\tag{i}
\]
Now $T$ has a graph
\[ 
\Gamma(T)=\{ (f,f')\quad\colon\, f\in C^1_*[0,1]\}
\tag{ii}
\]
\medskip

\noindent
Let $\overline{\Gamma(T)}$ denote the closure taken in the Banach space
$X\times Y$.
By definition a pair $(f,g)$ belongs to $\overline{\Gamma(T)}$
if and only if
\[
\exists \,\, \{f_n\}\in C^1_*[0,1]\quad\colon
\max_{0\leq x\leq 1}\, |f(x)-f_n(x)|\to 0\quad\colon \int_0^1\, |f'_n(t)-g(t)|\cdot dt=0
\]
The last limit means that
the derivatives
$f'_n$ converge to an $L^1$-function $g$.
Since $f_n(0)=0$ hold for each $n$
we have
\[
f_n(x)=\int_0^x\, f'_n(t\cdot dt\to \int_0^x\, g(t)\cdot dt
\]
Hence the  limit function $f$ is a
primitive integral
\[ 
f(x)=\int_0^x\, g(t)\cdot dt\tag{iii}
\]
\medskip

\noindent
{\bf Conclusion}. The linear space $\overline{\Gamma(T)}$
consists of pairs
$(f,g)$ with $g\in L^1[0,T)$ and $f$ is the $g$-primitive defined by
(iii).
In this way we obtain a linear operator $\widehat{T}$ with a closed graph.
More precisely, $\mathcal D(\widehat{T})$ 
consists of  functions $f(x)$
which are primitives of $L^1$-functions. 
Lebesgue theory this means  that that the domain of definition of
$\widehat{T}$ consists of \emph{absolutely continuous functions}.
Thus, by enlarging the domain of definition the 
linear operator $T$ is extended to a densely defined and closed
linear operator.



\medskip

\noindent
{\bf{3.7 Remark.}}
The example above is typical for many constructions where one starts
with some densely defined linear operator $T$
and finds an extension $\widehat{T}$ whose graph is the
closure of $\Gamma(T)$.
The reader should  notice that the choice of the target space
$Y$ affects the construction of closed extensions.
For example, replace above
$L^1[0,1]$ with the Banach space
$L^2[0,1]$
of square integrable functions on $[0,1]$.
In this case we find a closed graph extension
$S$ whose  domain of definition  consists of
continuous functions $f(x)$ which are primitives of
$L^2$-functions.
Since the inclusion $L^1[0,1]\subset L^2[0,1]$
is strict the domain of definition for
$S$  is a proper subspace of the linear space of all
absolutely continuous functions. 
In
PDE-theory  one  starts from a
differential operator
\[
P(x,\partial)=\sum\, p_\alpha(x)\cdot\partial^\alpha\tag{*}
\]
where  $x=(x_1,\ldots,x_n)$
are coordinates in ${\bf{R}}^n$
and $\partial^\alpha$ denote the higher order differential operators
expressed by products of 
the first order operators
$\{\partial_\nu=\partial/\partial x_\nu\}$.
The coefficients $p_\alpha(x)$ are in general only 
continuous functions defined in some open subset
$\Omega$ of ${\bf{R}}^n$, though the case when
$p_\alpha$ are $C^\infty$-functions is the most frequent.
Depending upon the situation one
takes various target spaces $Y$.
For example we let $Y$ be the 
Hilbert space $L^2(\Omega)$.
To begin with
one restricts $P(x,\partial)$ to the
linear space $C_0^\infty(\Omega)$ of test-functions in
$\Omega$ and constructs the corresponding graph.
With $Y=L^2(\Omega)$
we construct a closed extension as bove.
This device is often used in PDE-theory.

















\centerline{\bf{¤ 4  Three basic principles.}}


\bigskip

\noindent
A   result    due to Baire  goes as follows:
Let
$X$ be a metric space whose metric $d$ is complete, i.e.
every Cauchy sequence with respect to the distance function
$d$ converges. 
\medskip

\noindent
{\bf A.1  Theorem.}
\emph{Let $\{F_n\}$ is an increasing  sequence of
closed subsets of $X$ where each $F_n$ has empty interior. Then
the union $F^*=\cup\, F_n$ is meager, i.e.
$F^*$ does not contain any open
set.}


\medskip

\noindent
\emph{Proof.} To say that $F^*$ is meager means that if
$x_0\in X$ and $\epsilon>0$ then 
\[
B_\epsilon(x_0)\cap (X\setminus F^*)\neq \emptyset\tag{i}
\]
To show this we first use that $F_1$ has empty interior which gives
some $x_1\in B_{\epsilon/2}(x_0)\setminus F_1$
and  choose $\delta_1<\epsilon/3$ so that
\[
B_{\delta_1}(x_1)\cap F_1=\emptyset\tag{ii}
\]
Now $B_{\delta_1/3}(x_1)$ is not contained in
$F_2$ which gives  a pair $x_2$ and $\delta_2<\delta_1/3$
such that
\[
B_{\delta_2}(x_2)\cap F_2=\emptyset\tag{ii}
\]
We can continue in this way and to every $n$ find a pair $(x_n,\delta_n)$ such that
\[
B_{\delta_n}(x_n)\cap F_n=\emptyset
\quad\colon\quad x_n\in B_{\delta_{n-1}}(x_{n-1})\quad\colon\quad
\delta_n<\delta_{n-1}/3\tag{iii}
\]
For each pair $M>N\geq 1$ the triangle inequality gives
\[
d(x_M,x_N)\leq \delta_{N+1}+\ldots+\delta_M\leq 
\delta_N(3^{-1}+\ldots 3^{-M+1})\leq\frac{2}{3}\delta_N\tag{iv}
\]
At the same time we notice that
\[
\frac{2}{3}\delta_N\leq 3^{-N+1}\cdot \frac{2}{3}\epsilon\tag{v}
\]
Hence  $\delta_N\to 0$ and (iv) entails that 
$\{x_n\}$ is a Cauchy sequence. Since the metric is complete
there exists a limit point $x_*$ where 
\[
\lim_{M\to \infty}\, d(x_M,x_*)=0
\]
To each $N\geq 1$ we apply (iv) for arbitrary large $M$ and obtain
\[
d(x_*,x_N)\leq \frac{2}{3}\delta_N\implies
x_*\in B_{\delta_N}(x_N)\subset X\setminus F_N
\]
At the same time the the last inequality in (iv) applied with arbitrary large $N$ gives
\[
d(x_*,x_0)\leq \frac{2}{3}\epsilon\implies x_*\in B_\epsilon(x_0)
\]
So $x_*$ gives the requested point which
produces a non-empty set in (i).



\bigskip

\noindent
\centerline{\bf{A.2 The Banach-Steinhaus Theorem.}}
\medskip

\noindent
Let $X$ be a vector space equipped with a complete norm
$||\cdot||$. Hence $X$  is a complete metric spacce
with the distance function
\[ 
d(x,y)= ||x-y||
\]
Let  $||\cdot ||_*$ be   another  norm on $X$, not necessarily complete.
To each positive number $a$ we  set
\[
F_a=\overline{\{x\,\colon\, ||x||_*\leq a\}}
\]
where the closure is taken with respect to the given complete norm.
The triangle inequality 
give the inclusion
\[
F_a+F_b\subset F_{a+b}
\] 
for each pair of positive real numbers.
Next,
since every vector in $X$ has a finite norm
$||x||_*$ it follows that the union of
these $F$-sets taken as 
$a$ varies over the set of positive integers is equal to $X$.
Baire's theorem applied to the complete metric space
$(X,d)$ gives an integer $N$ such that $F_N$ has a non-empty interior.
Thus, we find $x_0\in X$ and $\epsilon>0$ such that
\[
B_\epsilon(x_0)\in F_N
\]
Here $||x_0||_*<M$ for some integer $M$ and the triangle inequality gives
\[
B_\epsilon(0)\subset F_{N+M}
\]
If $k$ is a positive integer such that
$k^{-1}\leq \epsilon$ and $K=(N+M)k$ it follows after  scaling that
the open unit ball
\[
B_1\subset F_K\tag{*}
\]
and since $F_K$ is closed in the given norm-topology
it follows that (*) also holds when we replace $B_1$ with the closed unit ball.
Hence, fšr  every $x\in X$ with
$||x||\leq 1$ there exists  a sequence
$\{x_\nu\}$ where $||x_\nu||^*\leq K$ for every $\nu$ and
\[
\lim\, ||x_\nu-x||=0
\]
and by scaling we conclude that
\[ 
||x||_*\leq K\cdot ||x||\quad\colon\quad x\in X\tag{**}
\]
If 
the norm 
$||\cdot ||_*$ also is complete we can reverse the role and find
a constant $K^*$ such that
\[
d(x,y)\leq K^*\cdot d_*(x,y)\tag{***}
\]
From this we conclude the following:




\medskip

\noindent
{\bf{A.2.1 Theorem.}}
\emph{A pair of complete norms $||\cdot ||$ and $||\cdot ||_*$
on a vector space are always equivalent, i.e there exists a constant $C\geq 1 $ such that}
\[
C^{-1}||x||_*\leq
||x||\leq
C||x||_*
\]





\bigskip


\centerline{\bf{A.3 The Open Mapping theorem.}}
\medskip

\noindent
Let $T\colon X\to Y$ be a  linear operator
where $X$ and $Y$  are  Banach spaces.
Assume that $T$ is surjective  and bounded, i.e. there exists a constant 
$C$ such that
\[
||Tx||\leq C\cdot ||x||\quad\&\quad T(X)=Y
\tag{i}
\]
Let $\{B_N(X))\,\colon\, N=1,2,\ldots\}$
be the closed balls of norm $N$ in $X$.
Since $T$ is sirjective we have
\[
Y=\cup\, \overline{T(B_N(X))}
\]
Baires Category Theorem can be  applied exactly as in
(A.2) and gives an integer $N$ such that
\[
B_1(Y)\subset \overline{T(B_N(X))}\tag{i}
\]
Let us then take some $y\in Y$ of norm $\leq 1/2$.
Then (i) gives $x_1$ of norm
$\leq N/2$ such that
\[
||y-T(x_1)|\leq 1/4
\]
Then we find $x_2$ of norm
$\leq N/4$ such that
\[
||y-T(x_1)+T(x_2)|\leq 1/8
\] 
We can continue in this way and since
both $X$ and $Y$ are Banach spaces the reader can chek that one gets the inclusion
\[
B_{1/2}(Y)\subset T(B_N(X))
\]
This means that $T$ yields an open mapping from $X$ onto $Y$, i.r. after a scaling
the inclusion (xx) entails that for every
$\epsilon>0$ the image $T(B_\epsilon(X))$ contains
a small open ball centered at $y=0$.












\bigskip

\centerline {\bf{A.4 The Hahn-Banach theorem.}}
\bigskip

\noindent
Let $E$ be a real vector space.
A function $\rho\colon E\to {\bf{R}}^+$ is
subadditive and positively homogeneous
if the following hold for
each pair $x_1,x_2$ in $X$ and every non-negative real number $s$:
\[
\rho(x_1+x_2)\leq 
\rho(x_1)+
\rho(x_2)\quad\colon \rho(sx_1)= s\cdot \rho(x_1)\tag{A.4.1}
\] 
Let  $E_0\subset E$ be  a subspace and
$\lambda_0\colon  E_0\to {\bf{R}}$ 
a linear functional  such that
\[
\lambda_0(x_0)\leq \rho(x_0)\quad\colon x_0\in E_0
\] 
Then there exists a 
linear functional
$\lambda$ on $X$ which extends $\lambda_0$ and
\[
\lambda(x)\leq \rho(x)\quad\colon x\in X\tag{A.4.2}
\] 
\medskip

\noindent
To prove this we use Zorn's Lemma. Namely, consider the 
partially ordered family of pairs $(V,\mu)$
where $V$ is a subspace of $E$ which contains $E_0$ and
$\mu\colon  V\to {\bf{R}}$
a linear map which extends $\lambda_0$ and
satisfies.
\[
\mu(x)\leq \rho(x)\quad\colon x\in V\tag{i}
\] 
Zorn's Lemma gives a maximal pair
in this family and there remains to prove that $V=E$.
If  $V\neq E$ we pick a vector $y\in E\setminus V$
and get a contradiction if we can extend $\mu$ to a linear map $\mu^*$
on
$W= V+{\bf{R}}y$ which  satisfies (A.4.1) when $x\in W$.
To see that this is possible we set
\[
\alpha=\min_{x\in V}\, \rho(x+y)-\mu(x)
\]
\[
\beta=\max_{\xi\in V}\, \mu(\xi)-\rho(\xi-y)
\]
Now we show that
\[
\alpha\geq \beta\tag{i}
\]
To get (i)  we consider a pair of vectors $x$ and $\xi$ in $V$ and then
\[
 \rho(x+y)-\mu(x) -(\mu(\xi)-\rho(\xi-y))=
 \rho(x+y)+\rho(\xi-y))-\mu(x+\xi)
\]
The triangle inequality fo the $\rho$-function gives
\[
\rho(x+\xi)=\rho((x+y)+(\xi-y))\leq  \rho(x+y)+\rho(\xi-y))-\
 \]
At the same time the vector $x+\xi$ belongs to $V$ and hence
\[
\mu(x+\xi)\leq \rho(x+\xi)
 \]
 This proves (i) and now we pick a real number $a$ such that
 $\beta\leq a\leq\alpha$. At this stage the reader can check that
 if we define $\mu^*$ by
 \[
 \mu^*(x+sy)= \mu(x)+ sa
\]
for every real nuymber $s$, then
$\mu^*$ is a linear map on $W$ for which (A.4.2) holds.

\medskip

\noindent
{\bf{The case of complex vector spaces.}}
Consider a complex vector space
$X$ equipped with a norm $||\cdot ||$.
Let $X_0\subset X$ be a complex subspace and
$\mu$ a ${\bf{C}}$-linear map on $X_0$ such that
\[
|\mu(x)|\leq ||x||
\]
hold for every $x\in X_0$.
Taking real and imaginary parts of
the complex numbers
under $\mu$ we get a pair of real-valued and 
${\bf{R}}$-linear maps $f_1,f_2$  on $X_0$
such that
\[ 
\mu(x)=f_1(x)+if_2(x)
\]
Since $\mu$ is ${\bf{C}}$-linear we have
\[
i(f_1(x)+if_2(x))= i\mu(x)= \mu(ix)=
f_1(ix)+if_2(ix)
\]
Identifying the real parts we see that
\[
f_2(x)=-f_1(ix)\tag{i}
\]
Next, with $x\in X_0$ we have
\[
f_1(x)\leq |f_1(x)-if_1(ix)|\leq ||x||
\]
The real version of the Hahn Banach theorem
gives an 
${\bf{R}}$-linear map $F\colon X\to {\bf{R}}$ which extends 
$f_1$ and satisfies 
\[
F_1(x)\leq ||x||\quad\colon x\in X\tag{ii}
\]
Now we get a ${\bf{C}}$-linear map
$\mu^*$ on $X$ defined by
\[
\mu^*(x)=F_1(x)-iF_1(ix)
\]
From the above $\mu^*$ extends $\mu$ and there remains to prove that
\[
|\mu^*(x)|=|F_1(x)-iF_1(ix)|\leq ||x||\tag{*}
\] 
hold for all $x\in X$.
To prove this we apply (ii) to  vectors
$e^{i\theta}x= \cos \theta \cdot x+\sin \theta \cdot ix$ which   gives
\[
\cos \theta \cdot F_1(x)+\sin \theta \cdot F(ix)\leq ||e^{i\theta}x||= ||x||\tag{iii}
\]
This hold for all $0\leq \theta\leq 2\pi$ and  choose $\theta$ so that
\[
\cos\,\theta=\frac{ F_1(x)}{|F_1(x)-iF_1(ix)|}\quad\colon\,
\sin\,\theta=\frac{ F_2(x)}{|F_1(x)-iF_1(ix)|}
\]
Then the left hand side in (iii) becomes
$|F_1(x)-iF_1(ix)|$ and (*) follows.

\bigskip

\centerline{\bf{A.4.3 Separating hyperplanes.}}
\medskip

\noindent
Consider  a  convex
set $K$  in a real normed vector space $X$ which contains the origin.
With $\delta>0$ we put
\[
K_\delta=K+B(\delta)= \{ x+\xi\,\colon x\in K\, ||x||<\delta\}
\]
As explained in ¤ xx we get a function $\rho$ defined by
\[ 
\rho(x)= \inf_{s>0}\, x\in s\cdot K_\delta
\]
where $\rho$ satisfies (A.4.0).
Let $x_0$ be a vector such that
\[
\min_{x\in K}\, ||x-x_0||=\delta
\]
This entails that
\[
\rho(x)=1
\]
On the 1-dimensional real  subspace of $X$ generated by $x_0$ we define
the linear functional
$\lambda_0$ where $\lambda_0(x)=1$.
Now the real version of the Hahn Banach theorem gives
an extension $\lambda$ to $X$ such that
\[
\lambda(x)\leq \rho(x)
\]
hold for all $x\in X$.
In particular we take vectors in the open ball $B(\delta)$
for these vectors  the inclusion  $B(\delta)\subset K_\delta$
gives $\rho(x)\leq 1$.
After scaling we conclude that
\[
|\lambda(x)|\leq  \delta^{-1}\cdot ||x||
\]
hold for all vectors in $X$
which means that the
linear functional $\lambda$ is continuous.
Next, since $\rho(x)\leq 1$ for all vectors $x\in K_\delta$
we have
\[
\lambda(k)+\lambda(\xi)=
\lambda(k+\xi)\leq 1
\] 
for pairs $k\in K$ and $\xi\in B(\delta)$.
Here  $\xi$ can be chosen so that
\[
\lambda(\xi)=-\delta \cdot ||\lambda||
\]
We conclude that
\[ 
\max_{k\in K}\, \lambda(k)\leq 1-\delta \cdot ||\lambda||
\]
At the same time $\lambda(x)=1$
which means that the half-space 
\[ 
\{\lambda\leq 1-\delta \cdot ||\lambda||\}
\] 
contains $K$ while $x$ has distance
$\geq \delta \cdot ||\lambda||$ to this half-space.
\bigskip







\noindent
{\bf{A.5 A special construction.}}
Let $X$ be a vector space of  infinite dimension
equipped with a norm
and
consider an infinite sequence
$\{x_1,x_2,\ldots\}$
of linearly independent vectors in $X$.
To each $n\geq 1$ we get the $n$-dimensional subspaces
\[
 E_n=\{x_1,\ldots,x_n\}
 \]
generated by the first $n$ vectors.
 For a fixed $n$ 
and every vector  $y\in X\setminus E_n$ we set
 \[
 d(y;E_n)= \min_{x\in E_n}\, ||y-x||
 \]
 

\noindent
{\bf{A.5.1  Exercise.}}
Show that
there exists at least one vector $x_*\in E_n$ such that
\[
d(y;E_n)= ||y-x_*||
\]
Next, construct via an induction over
$n$ a sequence of vectors $\{y_n\}$ where
each
$||y_n||=1$ with the following properties. For every
$n$ one has
\[
E_n=\{y_1,\ldots,y_n\}\quad\colon\,
d(y_{n+1},E_n)= 1
\]
In particular $||y_n-y_m||=1$ when $n\neq m$ which entails that
the 
sequence $\{y_n\}$ cannot contain a convergent subsequence and
hence the unit ball in $X$ is non-compact.
Thus, only finite dimensional normed spaces have a unit ball which is compact with
respect to the metric defined by the norm.
\medskip

\noindent
{\bf{A.5.2 A direct sum decomposition.}}
Let $X$ be a normed space and $V$ some finite dimensional subspace
of dimension $n$. Choose a basis $v_1,\ldots,v_n$ in $V$ and
via the Hahn-Banach theorem we find an $n$-tuple $x_1^*,\ldots,x_n^*$
such that
$x_j^*(v_k)$ is Kronecker's delta-function.
Set
\[ 
W=\{x\in X\,\colon x_\nu^*(x)=0\, \colon\,1\leq\nu\leq n\}
\]
Then $W$ is a closed subspace of $X$ and we have a direct sum decompotion
\[
X=W\oplus\, V
\]
Thus, every finite dimensional subspace of a normed space $X$ has 
a closed complement.
On the other hand, examples show that  a  closed infinite dimensional subspace
$X_0$ has in general not  closed complement.





\bigskip



\centerline{\bf{A.6   Frechet spaces.}}

\bigskip


\noindent
A pseudo-norm on a complex vector space $X$ is  a map $\rho$ from $X$ into
the non-negative real numbers
with the properties
\[
\rho(\alpha\cdot x)= |\alpha|\cdot \rho(x)
\quad\colon
\rho(x_1+x_2)\leq \rho(x_1)+\rho(x_2)\tag{A.6.1}
\]
where $x,x_1,x_2$ are vectors in
$X$ and $\alpha\in {\bf{C}}$. 
Notice that (A.7.1) entails that
the kernel of  $\rho$
 is a subspace of $X$ denoted by  $\text{Ker}(\rho)$.
 If it is reduced  to  the zero vector one says that 
$\rho$ is a  norm.


\medskip

\noindent
Suppose now that 
 $\{\rho_n\}$ is a denumerable sequence of pseudo-norms and put
\[ 
d (x,y)=\sum_{n=1}^\infty\, 2^{-n}\cdot 
\frac{\rho_n(x-y)}{1+\rho_n(x-y)}\tag{*}
\]
Assume that the intersection
\[
\cap\,\, \text{ker}(\rho_n)= \{0\}
\]
Then 
$d$
is a metric. If the resulning metric space $(X,d)$
is complete, i.e. if
every Cauchy-sequence with respect to $d $ converges to a vector in
$X$ one refers to   
$X$ as a Frechet space 
\medskip

\noindent
{\bf{The class $\mathcal K_X$.}}
It consists of closed and convex subsets $K$ which contrain the origin and are absorbing in the sense
that for every vector $x\in X$ there exists some $a>0$ such that
$ax\in K$. If $N$ is a positive  integer we set
\[
NK=\{ Nx\,\colon x\in K\}
\]
\medskip


\noindent
{\bf{A.6.2 Theorem.}}
\emph{Let $(X,d)$ be a Frechet space. 
Then every 
$K\in \mathcal K_X$
contains an open neighborhood of the origin.}
\medskip

\noindent
\emph{Proof.}
To each integer $N\geq 1$ we have the closed set
$F_N= N\cdot K$.
Since $K$ is absorbing
the union of these $F$-sets is equal to $X$.
Baire's theorem applied to the complete metric space
$(X,d)$ yields some $N$ and $\epsilon>0$ such
that $F_N$ contains
an open ball of radius $\epsilon$ centered at some
$x_0\in F_N$. If $d(x)<\epsilon$ we write
\[ 
x=\frac{x_0+x}{2}-\frac{x_0-x}{2}
\]
Now $F_N$ contains $x_0+x$ and $x_0-x$. By symmetry it also contains
$-(x_0-x)$ and the convexity entails that
$x\in F_N$.
Hence one has  the implication
\[
d(x,0)<\epsilon\implies x\in N\cdot K
\]
Now the $d$-metric is defined by 
a sequence of pseudo-norms
$\{\rho_n\}$. Choose an integer $M$ where $2^{-M}<\epsilon/2$.
The construction of $d$  shows that
if
$\rho_n(x)<\frac{\epsilon}{2M}$ hold for $1\leq n\leq M$, then
$d_\rho(x)<\epsilon$. Hence (i) gives
\[ 
\max_{1\leq n\leq M}\, \rho_n(x)<
\frac{\epsilon}{2M}\implies x\in N\cdot K
\]
After a  scaling one has
\[
\max_{1\leq n\leq M}\, \rho_n(x)<
\frac{\epsilon}{2M N}\implies x\in K
\]
The reader can check that there exists $\epsilon_*>0$ such that
\[
d(x,0)<\epsilon_*\implies
\max_{1\leq n\leq M}\, \rho_n(x)<
\frac{\epsilon}{2M N}
\]
and conclude that  $K$ contains an
open neighborhood of  the origin.


\medskip

\noindent
{\bf{A.6.3 The open mapping theorem.}}
\emph{Consider  a pair of
Frechet spaces $X$ and $Y$ and let}
\[
u\colon X\to Y
\]
\emph{be  a continuous linear and surjective map.
Then $u$ is an open mapping, i.e.
for every $\epsilon>0$
the $u$-image of the $\epsilon$-ball with respect to
the Frechet metric on $X$ contains
an open neighborhood of the origin in $Y$.}
\medskip

\noindent
The proof is left as an exercise to the reader
where the hint is to employ Baire's theorem
and similar arguments as in the proof of the open mapping theoren for
Banach spaces.

\medskip


\noindent
{\bf{A.6.4 Closed Graph Theorem.}}
\emph{Let $X$ and $Y$ be Frechet spaces and 
$u\colon X\to Y$ is 
a linear map. Put}
\[ 
\Gamma(u)=\{ (x,u(x)\}
\]
\emph{and suppose it is a closed subspace of the Frechet space $X\times Y$.
Then the linear operator 
$u$ is continuous.}
\bigskip

\noindent
{\bf{  Exercise.}}
Prove this theorem.
A hint is that
one has  a bijective linear map
from  $\Gamma(u)$ onto $X$
defined by
\[
(x,u(x))\mapsto x\tag{i}
\]
Since $\Gamma(u)$ is closed in
$X\times Y$ it is a Frechet.
Moreover, it is clear that (i) is a continuous linear map
and hence it is open by (A.6.3) which entails that
it is a homeomorphism between metric spaces.
From this one easily checks 
that $u$ is continuous.












\newpage


\centerline {\bf{ ¤ 5 Dual vector spaces}}
\medskip

\noindent
Let $X$ be a normed space over the complex field. A continuous linear form on
$X$ is a ${\bf{C}}$-linear map $\gamma$ from $X$ into ${\bf{C}}$
such that there exists a constant $C$ with:
\[
\max_{||x||=1}\,|\gamma(x)|\leq C
\]
The smallest constant $C$ above is 
the norm of $\gamma$. In this way
the  continuous linear forms give vectors in a normed
vector space denoted by
$X^*$.
Since Cauchy-sequences of complex numbers
converge it follows  that
$X^*$ is a Banach space.  Notice that this holds  even
if $X$ from the start is not complete. The reader may verify that of
$\widehat{X}$ is the completition of a normed space $X$, then
its
 dual is equal to that of $X$, i.e. one has
\[ 
X^*= \widehat{X}^*
\]
Next, let $Y$ be a subspace of $X$.
Every $\gamma\in X^*$ can be restricted to $Y$ and gives
an element of $Y^*$, i.e. there exist a  restriction map
\[ 
\mathfrak{res}_Y\colon X^*\to Y^*\tag{i}
\]
A restricted linear form cannot increase the norm  which gives
the  inequality
\[ 
|| \mathfrak{res}_Y(\gamma)||\leq ||\gamma||\quad\colon\quad
\gamma\in X^*
\]


\noindent
{\bf{5.1 The kernel  of
$\mathfrak{res}_Y$}}.
The kernel is by definition the set of
$X^*$-elements which are zero on $Y$. This
gives a subspace of $X^*$ denoted by $Y^\perp$.
It can 
be identfied with the dual of
a new normed space. Namely,  consider the 
quotient space
\[
Z= \frac{X}{Y}
\]
Vectors  in $Z$ are images of vectors $x\in X$ where  a pair of 
$x_1$ and $x_2$ give the same vector in $Z$ if and only if
$x_2-x_1\in Y$.
Let $\pi_Y(x)$ denote the image of $x\in X$. Now $Z$ is 
is equipped with a norm defined by
\[
||z||=
\min_x\,||x||\quad\colon\quad z=\pi_Y(x)
\]
From the constructions above the reader can verify
that one has  a canonical isomorphism
\[
Z^*\simeq \text{Ker}(\mathfrak{res}_y)=Y^\perp
\]
\bigskip


\noindent
{\bf{5.2 An exact sequence}}.
Let $Y\subset X$  be a closed subspace and put
$Z=\frac{X}{Y}$.
By the Hahn-Banch Theorem
every continuous linear form $\gamma$
on $Y$
has a \emph{norm preserving extension}
to a linear form on $X$.
Thus, if $\gamma$  has some norm $C$,  there
exists $\gamma^*\in X$ with norm $C$ such that
\[ 
\mathfrak{res}_Y(\gamma^*)=\gamma
\]
One refers to $\gamma^*$ as a norm-preserving extension of
$\gamma$.
Identifying 
$Z^*$ with $Y^\perp$ as in (5.1)
gives
an exact sequence
\[
0\to Z^*\to X
^*\to Y^*\to 0\tag{5.2.1}
\]
where the restriction map $X^*\to Y^*$
sends the unit ball in $X^*$ onto the unit ball of 
$Y^*$.
\bigskip


\centerline{\bf 5.3 The weak star topology}

\bigskip

\noindent
Let $X$ be a normed space. On the dual $X^*$ 
there is a
topology where 
a fundamental system of open neighborhood of
the origin in the vector space $X^*$ consista of sets
\[
U(x_1,\ldots,x_N;\epsilon)=\{\gamma\in X^*\quad\colon\, |\gamma(x_\nu)|<\epsilon\quad\colon
x_1,\ldots,x_N\,\,\,\text{finite set}\}\tag{5.4.1}
\]
\medskip

\noindent
Let  $Y$ be the finite dimensional subspace of
$X$ generated by $x_1,\ldots,x_n$. It is clear that the kernel of
$\mathfrak{res}_Y$ is contained in the $U$-set above.
If  $k$ is  the dimension of $Y$, then
linear algebra entails that 
the kernel of $\mathfrak{res}_Y$ has codimension $k$ in $X$.
So the $U$-set in (5.4.1) contains a subspace of $X^*$ of
finite codimension. Thus, weak-star open neighborhoods of the origin in
$X^*$ contain subspaces with a finite codimension which for an infinite dimensional space
 means  that the weak-star topology is  rather coarse.
However, thanks to the Hahn-Banach theorem it yields   a
Hausdorff topology.
Next, let $S^*$ be the unit ball in $X^*$, i.e. the set of
linear functionals on $X$ with norm $\leq 1$.
Using Tychonoff's theorem in general toplogy the reader should confirm :
\medskip

\noindent
{\bf{5.4.2 Theorem.}}
\emph{The unit ball $S^*$ is compact in the weak star topology.}



\medskip

\noindent
{\bf {The case when
$X$ is separable.}}
This means that there exists a denumerable dense
set
$x_1,x_2,\ldots $ in $X$.
On $S^*$
we define a metric by
\medskip

\[ d(\gamma_1,\gamma_2)= \sum_{n=1}^\infty\,
2^{-n}\cdot 
\frac{\bigl|\gamma_1(x_n)-\gamma_2(x_n)\bigr|}
{1+\bigl|\gamma_1(x_n)-\gamma_2(x_n)\bigr|}
\tag{5.4.3}
\]
\medskip


\noindent
{\bf{Exercise.}} Verify that the weak-star topology on
$S^*$  is equal to the
topology defined by the metric above.
So when $X$ is separable, then
$S^*$ is a compact metric space in the weak topology.
Notice also that 
the topology defined by the metric in
(5.4.3) does not depend upon the chosen dense subsequence in $X$.


\medskip

\noindent
{\bf {A warning.}}
If $X$ is not separable the weak star topology can
be  "nasty".
More precisely, we can find
a non-separable Banach space $X$ such that
$S^*$ contains a denumerable sequence $\{x_n^*\}$ which 
does not contain any convergent subsequence.
In other words, $S^*$ is not sequentially compact.
To get such an example one employs a wellknown  construction in general topology
which produces a compact Hausdorff space $Z$
containing a denumerable sequence of points
$\{z_n^*\}$  which has no convergent subsequence.
Let  $X$ be the Banach space of bounded complex-valued 
functions on
$Z$. The dual $X^*$ is the space of Riesz measures on $Z$.
In $S^*$ we find the sequence of unit point masses
$\{\delta(z_n)\}$.
\medskip

\noindent
{\bf {5.4.4 Exercise.}}
Use the fact from topology which assers that
a compact Hausdorrf space is normal to show that
if
$\{z_n\}$ is a sequence of points in $Z$ such that
\[
\lim_{n\to\infty}|, f(z_n)= \int_Z\, f\, d\mu
\]
hold for a Riesz measure $\mu$ and all $f\in C^0(Z)$, then
$\{z_n\}$ must converge to a point $z_*$ in $Z$ and
$\mu=\delta(z_*)$.
So with an "ugly compact space" $Z$ as above we get an example of
a Banach space $X$ for which $S^*$ is not sequentially compact.

\bigskip


\bigskip

\noindent
{\bf 5.4.5 Weak hulls in $X^*$.}
Assume now that  $X$  is
separable and choose a denumerable and dense subset
$\{x_n\}$. Examples show that in general the dual space
$X^*$ is no longer separable in its norm topology.
However,  there always exists a denumerable sequences
$\{\gamma_k\}$ in $X^*$ which is dense in the weak-star  topology.
This is proved in the next exercise.
\medskip

\noindent
{\bf{5.4.6 Exercise.}}
For every $N\geq 1$ we let  $V_N$
be the finite dimensional space generated by
$x_1,\ldots,x_N$.
It has dimension $N$ at most.
Applying the Hahn-Banch theorem
the reader should construct
a sequence $\gamma_1,\gamma_2,\ldots$
in $X^*$ such that for every $N$ the restricted linear
forms
\[
\gamma_\nu|V_N\quad 1\leq \nu\leq N
\]
generate the dual vector space $V_N^*$.
Next, let $Q$ be the field of rational numbers.
Show  that if $\Gamma$ is the subset of $X^*$ formed
by all finite $Q$-linear combinations 
of the sequence $\{\gamma_\nu\}$
then this denumerable set is dense in $X^*$ with respect to the
weak-star  topology.

\medskip


\noindent
{\bf 5.4.7 Another exercise.}
Let $X$ be a separable Banach space and let $E$ be a subspace of
$X^*$. We say that
$E$ point separating if 
there to every $0\neq x\in X$ exists some
$e\in E$ such that
$e(x)\neq 0$. Show first that every such point-separating subspace of
$X^*$ is dense with respect to the weak topology.
This is the easy part of the exercise. The second part is
less obvious. Namely, put
\[ 
B(E)=B(X^*)\cap E
\] 
Prove now that $B(E)$ is a dense   $B(X^*)$.
Thus, if $\gamma\in B(X^*)$ then there exists a sequence
$\{e_k\}$ in $B(E)$ such that
\[
\lim_{k\to\infty}\, e_k(x)=\gamma(x)
\] 
hold for all $x\in X$.


\medskip

\noindent
{\bf 5.4.8 An example from integration theory.}
An example of a separable Banach space is
$X=L^1({\bf{R}})$ whose elements are
Lebesgue measurable functions
$f(x)$ for which the $L^1$-norm
\[ 
\int_{-\infty}^\infty\, |f(x)|\cdot dx<\infty
\]
If $g(x)$ is a bounded continuous functions on
${\bf{R}}$, i.e. there is a constant
$M$ such that
$|g(x)|\leq M$ for all $x$, then we get a linear
functional on $X$ defined by
\[ 
g^*(f)=\int_{-\infty}^\infty\, g(x)\cdot f(x)\cdot dx<\infty
\]
Let $E$ be the
linear space of all bounded
and continuous functions. By the previous exercise it
is a dense subspace of $X^*$ with respect to the weak topology.
Moreover, by the second part of the exercise
it follows
that if $\gamma\in X^*$ has norm one, then there exists a sequence 
of continuous functions
$\{g_n\}$ of norm one at most such that
$g_\nu\to\gamma$ holds weakly.
Let us now find   $\gamma$.
For this purpose we define the functions
\[
G_n(x)=\int_0^x\, g_n(t)\cdot dt\quad\colon\quad x\geq 0\tag{i}
\]
These primitive functions are continuous and enjoy
a further property. Namely, since the maximum norm of every
$g$-function is $\leq 1$ we see that
\[ 
|G_n(x)-G_n(x')|\leq |x-x'|\quad\colon\quad x,x'\geq 0\tag{ii}
\]
This is means that whenever $a>0$ is fixed, then the
sequence $\{G_n\}$ restricts to an
\emph{equi-continuous} family of functions on the compact
interval $[0,a]$.
Moreover, for each $0<x\leq a$
since we can take $f\in L^1({\bf{R}})$ to be
the characteristic function on the interval $[0,x]$, the
weak convergence of the $g$-sequence implies that
there exists the limit
\[
\lim_{n\to\infty}\, G_n(x)=G_*(x)\tag{iii}
\]
Next, the equi-continuity in (ii) enable us to apply the classic result due to
C. ArzŽla in his paper
\emph{Intorno alla continua della somma di infinite
funzioni contionue}
from 1883 and conclude that the point-wise limit in
(iii) is uniform. Hence   the limit function
$G_*(x)$ is continuous on $[0,a]$ and it is clear
that
$G_*$ also satisfies (ii), i.e. it is Lipschitz continuous of norm
$\leq 1$. Since the passae to the limit can be carried out 
for every $a>0$ we conclude that $G_*$ is defined on $[0,+\infty>)$.
In the same way we find
$G_*$ on $(-\infty,0]$.
Next, 
by the result in [XX-measure] there exists
the Radon-Nikodym derivative
$G_*(x)$ which is  a bounded measurable function
$g_*(x)$ whose maximum norm is   $\leq 1$.
So then
\[ G_*(x)=
\int_0^x\,g_*(t)\cdot dt=
\lim_{n\to\infty}\, G_n(x)=
\lim_{n\to\infty}\, \int_0^x\, g_n(t)\cdot dt
\]
holds for all $x$. 
Since finite ${\bf{C}}$-linear sums of characteristic functions
is dense in $L^1({\bf{R}})$ we conclude that
the limit functional $\gamma$ is determined by
the $L^\infty$-function $g_*$.
So this shows the equality
\[
L^1({\bf{R}})^*=L^\infty({\bf{R}})
\]

\medskip

\noindent
{\bf Remark.}
The result above is of course wellknown. But it is interesting to see how the
last duality formula is derived  from  studies of 
the Lebesgue integral.

\newpage








\centerline {\bf{5.5 The weak topology on $X$}}.
\medskip


\noindent
Let $X$  be a  Banach space. The weak topology on $X$ 
has by definition
a fundamental system of open neighborhoods of
the origin  of sets 
\[
U(x^*_1,\ldots,x^*_N;\epsilon)=
\{x\in X \,\colon\, |x^*_\nu(x)|<\epsilon\}
\]
where
$\{x_\nu^*\}$ are finite subsets of $X^*$.

\medskip

\noindent
{\bf{5.5.1 Weakly convergent sequences.}}
A sequence $\{x_k\}$ in $X$ converges weakly to a limit vector $x$
if
\[ 
\lim_{k\to\infty}\,
x^*(x_k)= x^*(x)\quad\text{hold for all}\,\, x^*\in X^*
\]


\noindent
{\bf{5.5.2 Exercise.}}
Apply Baire's theorem and
show that a weakly convergent
sequence  $\{x_k\}$ is 
bounded, i.e. there exists a constant $C$ such that
\[ 
||x_k||\leq C
\quad\colon\, k=1,2,\ldots
\]

\medskip

\noindent
{\bf{Weak versus strong convergence.}}
A weakly convergent sequence need not be strongly convergent.
An example is when
$X=C^0[0,1]$ is the Banach space of continuous
functions on the closed unit interval.
By the Riesz representation theorem the dual space
$X^*$ consists of Riesz measures.
A sequence $\{x_n(t)\}$ of continuous functions
converge weakly to zero if
\[ 
\lim_{n\to\infty}\, \int_0^1\, x_n(t)\cdot d\mu(t)=0
\quad\text{hold for every Riesz measure}\quad  \mu\tag{5.5.3}
\]


\noindent
By a  result from [Measure] (5.5.3) holds  if and only if
the maximum norms of the $x$-functions are uniformly bounded
and
the sequence converges pointwise to zero.
One can construct many such pointwise convergent sequences 
of continous functions which
fail to converge in the maximum norm.
\medskip

\noindent
{\bf{5.5.4  Exercie.}}
Let  $X$ be  an 
infinite dimensional Banach space. Then the
norm-topology is always strictly stronger
than the weak topology. A hint to 
prove this goes  as follows.
By the construction  of the weak topology on $X$ its equality
with the norm topology gives
a finite subset $x^*_1,\ldots,x^*_N$ of $X^*$ 
and a constant $C$ such that
one has the implication
\[ 
\max_\nu |x_\nu^*(x)|<C\implies ||x||<1
\quad\colon  x\in X
\] 
But then the
Hahn-Banach theorem implies that the complex vector space
$X^*$  is
generated by the $n$-tuple $x^*_1,\ldots,x^*_N$ which entails that
$X$ has dimension $N$ at most and  contradicts the assumption that
$X$ has infinite dimension.







\bigskip



\centerline {\bf{5.6 The bidual  $X^{**}$ and reflexive spaces.}} 
\medskip


\noindent
Let $X$ be a normed space. The dual of $X^*$ is denoted by
$X^{**}$ and called the bidual of $X$.
Each $x\in X$ yields a bounded linear functional on $X^*$ by
\[
\widehat{x}(x^*)= x^*(x)
\]
The Hahn Banach theorem implies that
when $x$ is given, then there exists
$x^*\in X* $ such that $x^*(x)=||x||$. This implies that
the norm of $\widehat{x}$ taken in $X^{**}$ is equal to $x$.
We can express this by saying that
the bidual embedding
$x\mapsto \widehat{x}$ is norm preserving and the image of $X$ in 
$X^{**}$ is denoted by
$\mathfrak{i}(X)$.
If
$\mathfrak{i}$ is surjective one says that
$X$ is reflexive. Recall that dual spaces always are complete. So
every reflexive normed space must be a Banach space.
But the conveerse is not true, i.e there exists
non-reflexive Banach spaces.
An example is to take $X={\bf{c}}_0$ in which case
$X^*=\ell^1$ and $X^{**}= \ell^\infty$.
An example of a reflexive Banach space is
 $\ell^p$ where $1<p<\infty$.
 The vectors are sequences of complex numbers
 $x_1,x_2,\ldots$ for which
 \[
 ||x||_p= \bigl(\sum_{\nu=1}^\infty\, |x_\nu|^p\bigr)^{\frac{1}{p}}<\infty
 \]
Hšlder's inequality entails
 that   the dual space of $\ell^p$ is $\ell^q$ where
$q= \frac{p-1}{p}$, and
from which it is clear that
$\ell^p$ is reflexive.
\bigskip


\noindent
{\bf{5.6.1 Condition for $X$ to be reflexive.}}
Let $X$ be a normed space whose unit ball is denoted by $S$.
The bidual embedding identifies $S$ with a subset of
$S^{**}$.
We shall analyze how $S$ can deviate from $S^{**}$.
For this purpose we consider
a finite set $x_1^*,\ldots,x_n^*$ in $X^*$ and if $\gamma\in S^{**}$
we get complex numbers $\{c_i=\gamma(x_i^*)\}$.
Then, if  $\alpha_1,\ldots,\alpha_n$ is some $n$-tuple of complex numbers
we have
\[
|\sum\, \alpha_ic_i|=|\gamma(\sum\, \alpha_ix_i^*)|\leq
||\gamma||\cdot ||\sum\, \alpha_ix_i^*||\leq
||\sum\, \alpha_ix_i^*||
\] 
where the last inequality follows since
$\gamma$ has norm one at most.
The general result in ¤ xx gives for each $\epsilon>0$ some
$x\in X$ with $||x||<1+\epsilon$ and
\[
\widehat{x}(x_i^*)= x_i^*(x)= c_i=\gamma(x_i^*)
\]
Let us now assume that $S$ equipped with the weak topology is compact.
The same holds for $2S$ and taking from (x) we find a sequence
$\{x_n\}$ wih norms $||x_n||<1+1/n$. The assumed compactness gives a limit vector 
$x_*\in X$ of norm $\geq 1$ where $x_n\overset{w}\to x$.
Moreover, this weak convergence entials that
\[
\widehat{x_*}(x_i^*)=\gamma(x_i^*)
\]
hold for each $1\leq i\leq n$.
Here we started with a finite subset of $X^*$.
At this stage the reader should verify that when
$S$ is compact in the weak topology then
we can find $x\in S$ such that
$\widehat{x}=\gamma$. This proves that the bidual
embdedding is surjective, i.e. $X$ is reflexive.
Summing up we have proved:
\medskip

\noindent
{\bf{5.6.2 Theorem.}}
\emph{If $S$ is compact with respec to the weak toplogy, then
$X$ is reflexive.}




\newpage










\centerline{\bf{5.7  The Eberlein-Smulian theorem.}}

\bigskip

\noindent
Let $X$ be a Banach space.
A subset $A$ is called weakly sequentially compact 
if every countable  sequence
$\{x_n\}$ in $A$ contains at least one subsequence 
which converges weakly to a limit vector $x$.
Here it is not required that $x$ belongs to $A$.
Now we prove a  result due to Eberlein and Smulian.
\medskip

\noindent
{\bf{5.7.1 Theorem.}}
\emph{Let $A$ be a subset of
a Banach space $X$. Then $A$ is weakly sequentially compact 
if and only if its closure taken in
the weak topology is weakly compact.}


\medskip

\noindent
Before we enter the proof we notice  that the example in ¤ xx. shows that
a similar result does not hold when we regard the weak star topology on
$X^*$.
Let us also  point out that
we have  not assumed that $X$ is separable, so 
the weak topology on
$X$ need not be metrizable.
The proof of Theorem 5.7.1 requires several steps.
Assume first that
$A$ is weakly sequentally compact.
We leave it to the reader that this implies that
$A$ is bounded. So without loss of generality we can assume 
that $A$ is contained in the unit ballÊ$S$ in $X$.
Next, denote by $w(A)$ its weak closure.
To prove that $w(A)$ is compact in the weak topology on $X$ we shall
use the bidual embedding $X\mapsto X^{**}$.
By definition the weak star topology on $X^{**}$
restricts to the weak topology on the subspace $\mathfrak{i}(X)$.
Hence the bi-dual embedding is continuous  when
$X$ is equipped with the weak topology and $X^{**}$ with the weak star topology.
It follows that
\[
\mathfrak{i}(w(A))\subset \overline{\mathfrak{i}(A)}\tag{i}
\]
where the right hand side is the weak star closure of
$\mathfrak{i}(A)$ taken in $X^{**}$
Since $A\subset S$ and $\mathfrak{i}$ is norm preserving we have
\[
\overline{\mathfrak{i}(A)}\subset S^{**}\tag{ii}
\]
By Theorem xx the unit ball $S^{**}$ is compact in the weak star
topology. So
if
we have proved the inclusion
\[
\overline{\mathfrak{i}(A)}\subset \mathfrak{i}(X)\tag{iii}
\]
it  follows that
$\overline{\mathfrak{i}(A)}$ is weakly compact in $X$
and together wtih the inclusion
(i) the set $w(A)$ is weakly compact.
\medskip


\centerline{\emph{Proof of (iii)}}.
\medskip

\noindent
Let $\lambda$ be a vector in 
$\overline{\mathfrak{i}(A)}$ and set
\[
N(\lambda)= \{x^*\in X^*\, \colon\, \lambda(x^*)=0\}
\]
This is a hyperplane in $X^*$. If $N(\lambda)$ 
is closed with respect to the weak star topology on $X^*$
then the observation in ¤ xx gives a vector $x_0\in X$ such that
$\lambda={\bf{i}}(x_0)$ and (iii) follows.
So there remains to show that
$N(\lambda)$ is weak star closed in $X^*$.
To prove  this we shall use a  result which goes as follows:
\medskip

\noindent
{{\bf{ Lemma.}}
\emph{Let $Z$ be a bounded subset of $X$ 
and $\lambda$ 
a vector in
$\overline{\mathfrak{i}(Z)}$ with norm $\leq 1$. Then, if 
$y^*_0$ a  vector in 
the weak star closure of $N(\lambda)$ and 
$\epsilon >0$ there exist
sequences $\{y_\nu^*\}$   in $N(\lambda)$ 
and
$\{x_\nu\} $  in $Z$
such that the following hold for every $n\geq 1$:}
\[
|y^*_n(x_k)-\lambda(y_0^*)|<\epsilon\quad\colon\, 1\leq k\leq n\tag{1}
\]
\[
|y^*_n(x_k)|<\epsilon\quad\colon 1\leq n<k\tag{2}
\]

\noindent
{{\bf{Exercise.}}
Prove this via an inductive construction.
\medskip

\noindent
Next, apply   the Lemma    with $Z=A$.
The hypothesis on $A$ entails that $\{x_n\}$ has a 
convergent subsequence with
a limit vector $x_*$.
Passing to a subsequence we may assume that
(1-2) hold above and  that $x_n\overset{w}\to x_*$.
By the resut in ¤ xx the weak convergence entails that $x_*$ is a strong limit of convex
combinations of $\{x_\nu\}$. So with $\epsilon>0$ kept fixed
we  find a large positive integer $N$
and real non-negative numbers
$a_1,\ldots,a_N$ whose sum is one such that 
\[
|| \xi-x_*||<\epsilon
\quad\colon\, \xi= a_1x_1+\ldots+a_Nx_N\tag{iv}
\]
Now (1)  gives
\[
|\lambda(y_0^*)-y^*_N(\xi)|\leq \sum_{k=1}^{k=N}\,a_k\cdot ||\lambda(y_0^*)-y^*_N(x_k)|
<\epsilon\tag{v}
\]
Next, since $y^*_N$ has norm $\leq 1$ we have
\[
|y^*_N(\xi)-y^*_N(x_*)|\leq ||\xi-x_*||<\epsilon
\]
From (iv-v) the triangle inequality gives
\[
|\lambda(y_0^*)|<2\epsilon+|y^*_N(x_*)|\tag{vi}
\]
Funally, since $x_k\overset{w} \to x_*$  it follows that 
we can take $k>N$ so large that
\[
|y^*_N(x_*)-|y^*_N(x_k)|<\epsilon
\]
Above $k>N$ and (2) entails that
$|y^*_N(x_k)|<\epsilon$. So  another application of the triangle inequality
gives
\[
|\lambda(y_0^*)|< 2\epsilon+2\epsilon= 4\epsilon
\]
In  the lemma  we can take $\epsilon$ arbitrarily small
and conclude that
$\lambda(y_0^*=0$. Hence $y_0^*\in N(\lambda)$ and since $y^*_0$ was
an arbitrary vector in the
weak star closure of $N(\lambda)$ we have proved that this hyperplane is
weak star closed.
\medskip




\centerline{\emph{Proof of the converse.}}
\medskip

\noindent
There remains to show that if
$w(A)$ is weakly compact then
it is sequentially compact.
DO IT ...
\medskip


\noindent
{\bf{5.7.2 Applications of Theorem 5.7.1}}
Let $A$ be a subset of the Banach space $X$.
We construct its convex hull $\text{co}(A)$ and pass to its closure in the norm topology, i.e.
we get the norm-closed set
$\overline{\text{co}(A)}$. With these notations one has the 
result below which also is due to Eberlein and Smulian.
\medskip


\noindent
{\bf{5.7.3 Theorem.}}
\emph{If $A$ is weakly compact it follows that
$\overline{\text{co}(A)}$ also is weakly compact.}
\medskip


\noindent
\emph{Proof.}
By xx the norm closed convex set
$\overline{\text{co}(A)}$ 
is weakly closed and even equal to the weak closure of
$\text{co}(A)$. By  Theorem 5.7.1  
there  remains to show that
$\text{co}(A)$. is weakly sequentially compact.
So let u sconsider a suence of points $\{p_n\}$ in
$\text{co}(A)$.
Each $p_n$ is a finite convex combination of points in
$A$ denoted by $B_n$ and we set
\[
B^*=\cup\, B_n
\]
The countable set $B^*$ generates a separable closed 
subspace $X_0$ of $X$.
CONTINUE PROOF ....

























\newpage





\centerline {\bf{5.8  The Krein-Smulian theorem.}}
\bigskip


\noindent
Articles by these authors
from the years around 1940 contain
a wealth of results.
A major theorem
from their work goes as follows.
Let $X$ be a Banach space and
$X^*$ its dual. In (B.2) we constructed the weak star topology.
Next, the 
\emph{bounded weak-star topology}
is defined as follows.
Let $S^*$ be the open 
ball  of vectors in $X^*$ with norm
$<1$. If $n$ is a positive integer we get
the ball $nS^*$ of vectors with norm $<n$.
A subset $V$ of  $X^*$ is open in the bounded weak-star
topology if and only
if
the interesections $V\cap nS^*$ are weak-star open
for every positive integer $n$.
In this way we get a new topology on $X^*$
whose corresponding
topological vector space is denoted 
by
$X^*_{bw}$,  while $X^*_w$ denotes
the topological  vector space when
$X^*$ is equipped with the weak topology.
Notice that  the family of open sets in
$X^*_{bw}$
contains the open sets in
$X^*_w$, i.e. the bounded weak-star topology is stronger.
Examples show that the topologies in general are not equal.
\medskip

\noindent
Next, let 
$\lambda$ be  a linear functional on $X^*$ which is continuous with
respect to the weak-star  topology.
This gives by
definition  a finite set
$x_1,\ldots,x_M$ in $X$ such that
if $|x^*(x_\nu)|<1$ for each $\nu$, then
$\lambda(x^*)|<1$.
This  implies that the 
subspace of $X^*$ given by
the common kernels of
$\widehat{x}_1,\ldots\widehat{x}_M$
contains the $\lambda$-kernel and   linear algebra gives
an $M$-tuple of complex numbers
such that
\[
\lambda=\sum\, c_\nu\cdot \widehat{x}_\nu
\]
We can express this by saying that 
the dual space of $X^*_w$
is equal to $\widehat{X}$, i.e. every linear functional on $X^*$ which is continuous 
with respect to the
weak-star topology is of the form
$\widehat{x}$ for a unique $x\in X$.
Less obvious is the following:

\medskip

\noindent
{\bf{5.8.1. Theorem.}}
\emph{The dual of $X^*_{bw}$ is equal to $\widehat{X}$.}
\medskip

\noindent
\emph{Proof.}
For  each finite
subset $A$ of  $X$ we put
\[ 
\widehat{A}=\{x^*\,\colon\, \max_{x\in A}\,|x^*(x)|\leq 1\}
\]
Let $U$ be an open set in $X^*_{bw}$
which contains the origin
and $S^*$ is the closed unit ball in
$X^*$.
The construction of the bounded weak-star topology gives
a finite set $A_1$ in $X$ such that
\[
S^*\,\cap \widehat{A}^0\subset U\tag{i}
\]
Next, let $n\geq 1$ and suppose we have constructed
a finite set $A_n$ where
\[
nS^*\,\cap \,\widehat{A_n}\subset U\tag{ii}
\]
To each finite set $B$ of vectors 
in $X$ with norm $\leq n^{-1}$
we notice that   
\[
 \widehat{A_n\cup\, B}\subset \widehat{A_n}\tag{iii}
\]
Put
\[
 F(B)=(n+1)S^*\cap \,\widehat{A_n\cup\, B} \,\cap (X^*\setminus U)
\]
It is clear that $F(B)$  is weak-star closed
for
every finite set $B$ as above. If these sets are non-empty for all $B$,
it follows from 
the weak-star compactness of $(n+1)S^*$
 that the whole intersection is non-empty. So we find a vector
 \[
 x^*\in \bigcap_B\, F(B)
 \]
Notice that $F(B)\subset \widehat{B}$ for every finite set $B$ as above
which means that  
$|x^*(x)||leq 1$ for every  vector $x$ in 
in $X$ of norm $\leq n^{-1}$. 
Hence the norm
\[
||x^*||\leq n
\]
 But then (iii) gives the inclusion
\[
 x^*\in nS^*\,\widehat{ A_n}\bigr)\, \cap (X\setminus U)\tag{iv}
\]
This contradicts (ii) and hence we have proved that there exists a finite set
$B$ of vectors with norm
$\leq n^{-1}$ such that 
$F(B)=\emptyset$.
\medskip

\noindent
From the above it is clear that an induction over $n$ gives
a sequence of sets $\{A_n\}$ such that  (ii) hold
for each $n$ and
\[ 
A_{n+1}=A_n\,\cup B_n\tag{v}
\]
where
$B_n$ is a finite set of vectors of norm
$\leq n^{-1}$.
\bigskip

\noindent{\emph{Final part in the roof of the Krein-Smulian theorem.}}
Let $\theta$ be a linear functional on $X^*$ which is
continuous with respect to the bounded weak-star topology.
This gives an open neighborhood
$U$ in
$X^*_{bw}$ such that
\[
|\theta(x^*)\leq 1\quad\colon\,  x^*\in U\tag{i}
\]
To the set $U$
we find a sequence $\{A_n\}$ as above.
Let us enumerate the vectors in this sequence of finite sets by
$x_1,x_2,\ldots$, i.e.
start with the finite string of vectors in $A_1$, and so on.
By the inductive construction of the $A$-sets we have
$||x_n||\to 0$ as $n\to \infty$.
If $x^*$ is a vector in $X^*$ we 
associate the complex sequence
\[
\ell(x^*)= \{x^*(x_n)\}
\]
which tends to zero since
$||x_n||\to 0$ as $n\to \infty$.
Then
\[ 
x^*\mapsto \ell(x^*)
\]
is a linear map from $X^*$ into the 
Banach space ${\bf{c}}_0$.
If
\[
\max_n\, |x^*(x_n)|\leq 1
\]
we have by definition $x^*\in A_n^0$ for each $n$.
Choose  a positive integer $N$ so  that $||x^*||\leq n$. Thus entails that
\[
x^*\in NS^*\cap A_N^0
\]
From (ii) during the inductive construction of the $A$-.sets,
the last set is contained in $U$. Hence
$x^*\in U$
which by (i) gives
$\theta(x^*)|\leq 1$.
We conclude that $\theta$ yields
a linear functional on
on the image space of the $\rho$-map  with norm one at most.
The 
Hahn-Banach theoren gives
$\lambda\in{\bf{c}}_0^*$
of norm one at most such that
\[
\theta(x^*)= \lambda(\ell(x^*))
\]
Next,  by a wellknown result due to
Banach the dual of ${\bf{c}}_0$ is $\ell^1$. Hence there exists
a sequence $\{\alpha_n\}$ in $\ell^1$ such that
\[
\theta(x^*)= \sum\,\alpha_n\cdot x^*(x_n)
\]
In $X$ we find the vector $x=\sum\, \alpha_n\cdot x_n$
and conclude that
$\theta=\widehat{x}$ which proves the Krein-Smulian theorem.











\bigskip

\noindent
\centerline {\bf{5.9  A result by Pietsch }}.
\medskip

\noindent
The  result below 
illustrates the usefulness of
regarding various weak topologies.
Let $T$
be a bounded linear operator on a Banach space $X$ and
$\{p_n(z)\}$ is  a sequence of polynomials
with complex coefficients
where $p_n(1)=1$  for each $n$. We get the bounded operators
\[
 A_n=p_n(T)\quad\colon\, n=1,2,\ldots
\]
Suppose that
\[
\lim_{n\to \infty}\, A_n(x)- A_n(T(x)) \overset{w}\to 0\tag{i}
\]
hold for every $x\in X$
where the superscript $w$ mens that we regard weak convergence.
In addition to (i) we assume that
for every $x\in X$, the sequence $\{A_n(x)\}$
is relatively compact with respect to the weak topology.
Under these two assumptions  one has:
\medskip


\noindent
{\bf{5.9.1 Theorem.}}
\emph{For every $x\in X$ the sequence
$\{A_n(x)\}$ converges weakly to a limit vector
$B(x)$ where $B$ is a bounded linear operator on $X$. Moreover
$B$ is an idempotent, i.e. $B=B^2$
and one has a direct sum decomposition}
\[ 
X=\overline{(E-T)(X)}\, \oplus  \ker(E-T)
\]
\emph{where $E$ is the identity operator on $X$
and 
$\overline{(E-T)(X)}$ is the closure taken in the norm topology of
the range of $E-T$. Finally,
$\ker(E-T)$ is equal to the range $B(X)$ while
$\ker(B)=\overline{(E-T)(X)}$.}

\medskip
\noindent
The proof  in ¤ xx and gives an instructive lesson of
"duality methods" while infinite dimensional normed spaces are
considered.




\newpage

\centerline {\bf 6. Fredholm theory.}

\bigskip
\noindent
Throughout this section 
$X$ and $Y$ are Banach spaces with
dual spaces 
$X^*$ and $Y^*$.
\medskip

\noindent
{\bf 6.1 Adjoint operators.}
Let $u\colon X\to Y$
be a bounded linear operator . The adjoint $u^*$ is the linear operator
from $Y^*$ to $X^*$ defined by
\[
u^*(y^*)
\colon\, x\mapsto y^*(u(x))\quad\colon\quad y^*\in Y\quad\colon x\in X\tag{1}
\]



\noindent
{\bf{Exercise.}} Show that 
the Hahn-Banach theorem gives the equality of operator norms:
\[
||u||=||u^*||
\]






\noindent
{\bf 6.2 The operator $\bar u$.} 
The bounded linear operator $u$ has a kernel denoted by
$\mathcal N(u)$ in $X$, often called the null space of $u$. 
Since $u$ is bounded it is clear that the null space 
is  and gives 
the
Banach space
$\frac{X}{\mathcal N(u)}$. Now one gets      the
induced linear operator
\[ 
\bar u\colon\,\frac{X}{\mathcal N(u)}\to Y\tag{6.2.1}
\]


\noindent
By construction $\bar u$
is an \emph{injective} linear operator with 
the same range as $u$:
\[
 u(X)=\bar u(\frac{X}{N_u})\tag{6.2.2}
 \]
\medskip

\noindent
{\bf 6.3 The image of $u^*$}. In the dual space $X^*$ we get
the subspace
\[ 
\mathcal N(u)^\perp=\{x^*\in X^*\quad\colon\, x^*(\mathcal N(u))=0\}\tag{i}
\]


\noindent
Consider a pair 
$y^*\in Y^*$ and
$x\in \mathcal N(u)$. Then
\[
u^*(y^*)(x)= y^*(u(x))=0
\]
The proves the inclusiuon
\[
u^*(Y^*)\subset \mathcal N(u)^\perp\tag{ii}
\]

\noindent
Next, the Hahn-Banach theorem gives
the canonical isomorphism
\[
\bigl[\frac{X}{\mathcal N(u)}\bigr]^*\simeq \mathcal N(u)^\perp\tag{iii}
\]
\medskip

\noindent 
Next,  consider the linear operator $\bar u$ 
from (6.2.1).
The canonical isomorphism
(iii) gives a linear map
\[ 
\bar u^*\colon\, Y^*\mapsto \mathcal N(u)^\perp\tag{iv}
\]

\noindent
From this and (ii) we get the equality
\[
\text{Im}(\bar u^*)=\text{Im}(u^*)\tag{6.3.1}
\]
where both sides appear as subspaces of $\mathcal N(u)^\perp$.

\medskip


\centerline {\bf 6.4 The closed range property}
\medskip

\noindent
A bounded linear operator
$u\colon X\to Y$ is said to have
closed range if
$u(X)$ 
is a closed subspace of $Y$.
When this holds 
\[
\bar u\colon \frac{X}{\mathcal N(u)}\to u(X) 
\]
is  a bijective map between
Banach spaces. The Open Mapping Theorem 
implies that this is an isomorphism of Banach spaces.
We use this to prove:

\medskip

\noindent
{\bf 6.4.1 Proposition}. \emph{If  $u$ has closed range then $u^*$ has closed range
and
one has the equality}
\[ 
\text{Im}(u^*)= \mathcal N(u)^\perp
\]
\medskip


\noindent
\emph{Proof.}
Using (6.3.1) we can replace $u$ by $\bar u$ and  assume
that $u\colon X\to Y$  is injective. Then
$\mathcal NU(u)^\perp=Y^*$ and there remains to 
show
that
$u^*$ is surjective, i.e.  that 
\[ 
u^*(Y^*)=X^*\tag{i}
\]



\noindent
To prove (i) this we use the assumption that 
 $u$ has closed range which by the Open Mapping theorem gives
a constant $c>0$ such that
\[ 
||u(x)||\geq c\cdot ||x||\quad\colon\, x\in X\tag{ii}
\]
If $x^*\in X^*$ the injectivity of $u$ gives
a linear functional
$\xi$ on  $u(X)$ defined by
\[
\xi(u(x))= x^*(x)\tag{iii}
\]
Now (ii) entails that
$\xi$ belong to $u(X)^*$ with norm
$\leq c\cdot ||x^*||$.
The Hahn-Banach theorem applied to
the subspace 
$u(X)$ of $Y$ gives a
norm preserving extension $y^*\in Y^*$ where (iii) entails that
\[ 
u^*(y^*)(x)= y^*(u(x))= x^*(x)
\]
This means  that
$u^*(y^*)= x^*$ and the requested surjectivity follows.









\bigskip

\noindent
{\bf {6.4.2 A converse result.}}
Let $u\colon X\to Y$ be a bounded linear operator and
assume that $u^*$ has closed range. Then we shall prove that
$u$ has closed range. 
To begin with we reduce the proof to the case when
$u$ is injective.
For if
$X_0=\frac{X}{\ker(u)}$
we have the induced linear operator
\[
u_0\colon X_0\to Y
\]
where $u_0(X_0)= u(X)$
and at the same time
\[
u_0^*\colon Y\to X_0^*
\] 
where we recall that
\[ 
X_0^*=\ker(u)^\perp=\{x^*\in X^*\colon x^*(\ker (u))=0\}
\]
Here $u_0^*(Y^*)$ can be identified with the closed subspace $u^*(Y)$
in $X_0^*$ which entails that
we reduce the proof to the case when $u$ is injective.
From now on $u$ is injective
and consider
the image space $u(X)$
whose  closure yields a Banach space $\overline{u(X)}$. Here
\[ 
u\colon X\to \overline{u(X)}
\] 
is a linear operator whose range is dense.
Let us denote this operator with
$T$. The adjoint
\[ 
T^*\colon\, \overline{u(X)}\to X^*
\]
and we have seen that
\[
 \overline{u(X)}=\frac{Y^*}{\ker (u^*)}
 \]
In particular the $T^*$-image is equal to $u^*(Y^*)$
and hence $T^*$ has a closed range.
The requuested closedness of $u(X)$ follows if we show that
\[ 
T\colon X\to \overline{u(X)}
\] 
is surjective.
Hence, we have reduced the proof of to the following:
\medskip

\noindent
{\bf{6.4.3 Proposition.}} \emph{Let $T\colon X\to Y$ be injective
where $T(X)$
is dense in $Y$ and $T^*$ has closed range. Then $T(X)=Y$.}
\medskip

\noindent
\emph{Proof}.
Let $y$ 
be a non-zero vector in $Y$
and put
\[ 
\{y\}^\perp=\{y^*\in Y^*\colon\,y^*(y)=0\}
\]
Consider also the image space
\[
V=T^*(\{y\}^\perp)
\]
Let us first show that 
\[
V\neq X^*\tag{i}
\]
To prove (i)  we choose
$y^*$ in $Y^*$ such that $y^*(y)=1$ and get the vector
$T^*(y^*)$. If 
$V=X^*$ this gives some $\eta\in \{y\}^\perp$
such that
$T^*(y)= T^*(\eta)$. This means
that
\[
y^*(Tx)= \eta(Tx)\quad\colon x\in X
\]
The density of $T(X)$ implies that $y^*=\eta$
which is a contradiction since
$\eta(y)=0$.
\medskip

\noindent
Next we show
that
$V$ is closed in the weak-star topology on $X^*$.
By the Krein-Smulian theorem the weak-star closedness follows
if $V$ is closed in $X^*_{bw}$.
So let $S$ be the unit ball in $X$
and $\{\xi_n\}$ is  a sequence in
$V\cap S^*$ where $\xi_n\overset{w}\to  x^*$
for some
limit vector $x^*$.
The Open Mapping Theorem applies to
the operator $T^*\colon \{y\}^\perp\to X^*$
and gives 
a 
constant $C$ and a sequence $\{y_n^*\in  \{y\}^\perp\}$
such that $||y_n^*||\leq C$  and 
$T^*(y_n)=\xi_n$.
By weak-star compactness for bounded sets in $ \{y\}^\perp$ we can pass to a 
subsequence and assume that
$y_n^*$ converge in $\{y\}^\perp$
to 
a limit vector $y^*$ in the weak star topology.
In particular  we can apply this to every vector $Tx$ with
$x\in X$ and  get
\[
 y^*(Tx)=\lim y^*_n(Tx)
 \]
 This entails that
\[
T^*(y^*)(x)= y^*(Tx)=\lim y^*_n(Tx)=\lim T^*(y_n)(x)=\lim\xi_n(x)=x^*(x)
\]
Hence  $x^*=T^*(y^*)$ which proves that $V$ is weak-star closed
in $X^*$.
\medskip

\noindent
We have proved that
 $V$ is closed in the weak-star topology on $X^*$
and not equal to the whole of $X^*$.
This gives  the existence  a non-zero vector
$x\in X$ such that $\widehat{x}(V)=0$. 
So if $y^*\in Y^*$ is such that
$y^*(y)=0$ we have 
by definition $T^*(y^*)\in V$ and obtain
\[ 
y^*(Tx)=\widehat{x}(T^*(y^*))=
y^*(Tx)=0
\tag{ii}
\]
Hence we have the implication:
\[
y^*(y)=0\implies y^*(Tx)=0\tag{iii}
\]
Finally, since  $T$ is injective we have $Tx\neq 0$ and
then (iii) gives 
a complex number
$\alpha$ such that $y=\alpha\cdot T(x)$, i.e. the vector $y$ belongs toÊ$T(X)$
as requested.
 





\newpage





\centerline{\bf 6.5 Compact operators.}
\medskip

\noindent
A linear operator
$T\colon X\to Y$ is compact if
the the image under $T$ of the unit ball in
$X$ is relatively compact in $Y$.
An equivalent  condition for $T$ to be compact
is that if
$\{x_k\}$ is an arbitrary sequence in the unit ball $B(X)$ then there exists a subsequence of $\{T(x_k)\}$ which converges to some $y\in Y$.
\medskip

\noindent
{\bf{6.5.1 Exercise.}}
Let  $\{T_n\}$
be  a sequence of compact operators
which converge to another operator $T$, i.e. 
\[ 
\lim_{n\to \infty}\, ||T_n-T||=0
\]
where we employ the operator norm on the Banach space
$L(X,Y)$.
Verify that $T$ also is a compact operator.



\medskip



\noindent
{\bf 6.5.2  Theorem.} \emph{A bounded linear operator
$T$ is  compact if and only if its
adjoint $T^*$ is  compact.}

\medskip
\noindent
\emph{Proof.}
Assume first that $T$ is compact and
let $B$ be the unit ball in $X$.
From the material
in ¤ xx this entails that for each
positive integer $N$ there exists
a finite set $F_N$ in $B$
which is $N^{-1}$-dense in $T(B)$, i.e. for
each $y\in T(B)$ there exists
$x\in F_N$ and
\[
||T(x)-y||<N^{-1}\tag{i}
\]
Let us then consider a sequence $\{y_n^*\}$ in the unit ball of
$Y^*$.
By the standard diagonal procedure we find a subsequence
$\{\xi_j=y^*_{n_j}\}$
such that
\[
\lim_{j\to\infty}\, \xi_j(Tx)\quad\colon \, x\in \bigcup_{N\geq 1}\, F_N\tag{ii}
\]
Next, if $x\in B$ and $\epsilon>0$ we  choose $N$ so large
that
$N^{-1}<\epsilon/3$.
Since
(i) hold for the finite set of points in $F_N$
there exists an integer $w$ such that
\[
 |\xi_j(Tx) -\xi_i(Tx)|<\epsilon/3 \quad\colon j,i\geq w\tag{iii}
 \]
hold for each $x\in F_N$. 
Since the $\xi$-vectors have unit norm it follows from
(i) and the triangle inequality  that
(iii) hold for each $x\in B$.
Above $\epsilon>0$ is arbitrary small which entials that
 $\{\xi_j(Tx)\}$ is a Cauchy seqence of complex numbers
for every $x\in B$ and then the same hold for
each $x\in X$. Since  Cauchy sequences of complex numbers converge
there exist limits:
 \[
 \lim_{j\to\infty}\, \xi_j(Tx)\quad\colon x\in X\tag{iv}
 \]
 It is clear that these
 limits values are
 linear with respect to $x$. So by
 the construction of $T^*$
 there exist the pointwise limits
 \[
\lim_{j\to\infty}\, T^*\xi_j(x)\quad\colon x\in X\tag{v}
\]
which means that there exists
$x^*\in X^*$ such that
 \[
x^*(x)=\lim_{j\to\infty}\, T^*\xi_j(x)\quad\colon\in x\in X\tag{vi}
\]
The requested compactness of $T^*$ follows if we have proved that
the pointwise convergence in (vi) is uniformwhen $x$ stays in $B$, i.e.
that
\[
\lim_{j\to\infty}\, ||T^*\xi_j-x^*||=0\tag{vii}
\]
To prove that (vi) gives (viii)
we apply  the Arzela-Ascoli theorem which
shows that pointwise convergence on the relatively compact
set $T(B)$ of the equicontinuous family of functions
$\{\xi_j\}$
gives the uniform convergence in (vii).
\medskip

\noindent
Above we proved that if $T$ is compact, so is $T^*$.
To prove the  the opposed  implication
we employ the bi-dual space
$X^{**}$. From the above the compactness of 
$T^*$ implies that 
$T^{**}$ is compact. At this stage the reader can check
that the restriction of
 $T^{**}$ to the
 the closed subspace $j(X)$ of $X^{**}$ under the bi-dual embedding is compact
which entails  that $T$ is compact.





 

\bigskip

\noindent
{\bf{6.5.3 Operators with finite dimensional  range.}}
Suppose that the image space $u(X)$
has a  finite dimension $N$ and 
choose 
an $N$-tuple $x_1,\ldots,x_N$ in $X$ such that
$\{u(x_k)\}$ is a basis for
$u(X)$. 
In $Y^*$ we can find an $N$-tuple
$y_1^*,\ldots,y_N^*$
such that 
\[
j\neq k\implies y_j^*(u(x_k))=0\quad\text{and}\quad
y_j^*(u(x_j))=1
\]
So if $u^*$ is the adjoint operator then
\[
u^*(y_j^*)(x_k)=\text{Kronecker's delta function}
\]
If $y^*\in Y^*$ we can therefore find
an $N$-tuple of complex numbers such that
\[
u^*(y^*-\sum c_j\cdot y_j^*)(x_k)=0\quad\colon k=1,\ldots,N
\]
This entails that the vector
$y^*-\sum c_j\cdot y_j^*)$ belongs to the kernel of $u^*$ and hence 
the range of $u^*$ is the $N$-dimensional subapace of $X^*$ generated by
$\{u^*(y_j^*)\}$.
in particular the adjoint $u^*$ has finite dimensional range.









\bigskip

\centerline {\bf 6.6 Compact pertubations.}
\medskip

\noindent
We shall prove the following:


\medskip

\noindent 
{\bf 6.6.1 Theorem.}
\emph{Let $u\colon X\to Y$
be an injective operator with closed range and $T\colon\, X\to Y$
a compact operator. Then  the kernel of $u+T$ is finite dimensional
and $u+T$ has closed range.}

\medskip










\noindent
\emph{ Proof.} 
To begin with the Open Mapping Theoren gives
gives a poaitive number $c$ such that
\[
||u(x)||\geq c\cdot ||x||\tag {i}
\]
Now we show that  $\mathcal N(u+T)$ is finite dimensional.
By the  result in ¤ xx it suffices to show that the set
\[ 
V= \mathcal N(u+T)\cap\, B(X)
\]
is relatively compact in the norm topology on
$X$, where we recall that 
$B(X)$ is the closed unit ball in $X$.
Let $\{x_n\}$ be a sequence in $V$. Since
$T$ is compact there is a subsequence $\{\xi_j=x_{n_j}\}$
and some vector $y$ such that
$\lim\, T{\xi_j}= y$. Since
$u(\xi_j)=-T(\xi_j)$
it follows that $\{u(\xi_j)\}$ is a Cauchy sequence and 
(i) entails that $\{\xi_j\}$ is a Cauchy sequence and hence has a limit vector.
This proves that
$V$ is relatively compact.
\medskip

\noindent
{\emph {The closedness of $\text{Im}(u+T)$}}.
Since $\mathcal N(u+T)$ is finite dimensional the result in  ¤ xx gives
a direct sum decomposition
\[ 
X= \mathcal N(u+T)\oplus X_*
\]
Here
$(u+T)(X)= (u+T)(X_*)$ so it suffices that the last image is closed and 
we can restrict both $u$ and $T$ to $X_*$ where  
$T_*$ again is compact. Hence we may assume that
the operator $u+T$ is \emph{injective},  i.e. that
\[
\mathcal N(u+T)=\{0\}\tag{i}
\]
If a vector 
$y$ belongs to  the closure of
$\text{Im}(u+T)$ there exists  a sequence
$\{x_n\}$ in $X$ such that
\[ 
\lim\, (u+T)(x_n)=y\tag{ii}
\]
Suppose first that
the norms of $\{x_n\}$ are unbounded. Passing to a subsequence if necessary
we may assume that $||x_n||\to\infty$.
With $\xi_n=\frac{x_n}{||x_n||}$
it follows that
\[ 
\lim\, u(\xi_n)+T(\xi_n)=0\tag{iii}
\]
Now $\{\xi_n\}$ is bounded and since $T$ is compact we can pass to
another subsequence and assume that 
$T(\xi_n)\to y$ holds for some $y\in Y$. Then
(ii) entails that
$u(\xi_n)$ also has a limit and (i) implies that 
$\{\xi_n\}$   converges in $X$ to a limit vector  $\xi_*$. Here
$\xi_*\neq 0$ since
$||\xi_n||=1$ for all $n$. Moreover, (iii)
entails that
$u(\xi_*)+T(\xi_*)=0$. This gives a  contradiction since (i) was assumed.
\medskip

\noindent 
Hence $\{x_n\}$ is a bounded sequence  in (ii)
and 
since $T$ is compact we can pass to a subsequence and assume that
$T(x_n)\to \eta$ holds for some
$\eta \in Y$, and 
(ii)  entails that
\[
\lim\, u(x_n)=y-\eta \tag{iv}
\]
Finally, by assumption  $u$ is injective and has a closed range, and
then the Open Mapping Theorenm together with (iv) entail
that
$\{x_n\}$ converges to a vector 
$\xi$. 
Passing to the limit in (ii) we 
get
\[ 
u(\xi)+T(\xi )=y
\]
Hence $y$ belongs to $\text{Im}(u+T)$ and Theorem 6.6.1 is proved.











\bigskip

\centerline{\bf{6.7 Spectra and resolvents of compact operators.}}

\medskip

\noindent
Let $T\colon X\to X$ be a compact operator.
For each complex number $\lambda\neq 0$ we set
\[
\mathcal N(\lambda)= \{ x\colon Tx=\lambda\cdot x\}
\]


\noindent
{\bf{6.7.1 Theorem.}} \emph{
The set of non-zero $\lambda$ for which
$N(\lambda)$ contains a non-zero vector is discrete.}
\medskip

\noindent
{\emph{Proof.}}
Suppose that there exists a non-zero cluster point $\lambda_0\neq 0$, i.e.
a sequence $\{\lambda_n\}$ where $\lambda_n\to \lambda_0$ and for
each $n$  a non-zero vector
$x_n\in \mathcal N(\lambda_n)$.
Since the numbers $\{\lambda_n\}$ are distinct and
$T(x_n)= \lambda_n\cdot x_n$ hold one easily verifies
that the vectors 
$\{x_n\}$ are linearly independent.
By the result in ¤ xx we find
a sequence of unit vectors $\{y_n\}$ satisfying the separation in
Theorem ¤ xx and 
\[
\{x_1,\ldots,x_n\}=
\{y_1,\ldots,y_n\}
\] 
hold for each $n$.
Now 
\[
T(\lambda_n^{-1}y_n)-\lambda_m^{-1}T(y_m)=y_n-y_m\in \{y_1,\ldots,y_{n-1}\}
\quad\colon n>m\tag{i}
\]
At the same time the separation  gives
\[
||y_n-y_m||\geq 1
\quad\colon n>m\tag{ii}
\]
Since $\lambda_n$ converge to the non-zero number
$\lambda_0$ this entails that $\{\lambda_n^{-1}y_n\}$
is a bounded sequence and from
(i-ii) we see that
$\{T(\lambda_n^{-1}y_n)\}$ cannot contain a convergent subsequence.
This  contradiction  proves Theorem 6.7.1

\medskip

\noindent
{\bf{6.7.2 Theorem.}}\emph{The spectrum of a compact operator
$T$ is discrete outside the origin.}

 \medskip
 
 \noindent
\emph{Proof.}
Consider a non-zero $\lambda_0\in\sigma(T)$.
By Schauder's result in (xx) the adjoint $T^*$ is also compact.
Hence Theorem 6.7.1 applies to $T$ and  $T^*$ which  gives
 a small punctured disc $\{0<|\lambda-\lambda_0|<\delta\}$
 such that  $\lambda\cdot E-T$ and $\lambda\cdot E^*-T^*$ 
both  are injective
when $\lambda$ belongs to the punctured disc.
 Next,  
 $\lambda\cdot E-T$ has a closed range by Theorem 5.X.
 If it is a proper subspace of $X$  find a non-zero
 $x^*\in X^*$ which vanishes on this range. The construction of
 $T^*$ entails that
 $T^*(x^*)=\lambda\cdot x^*$. But this was not the case and hence
 $\lambda\cdot E-T$ is surjective which shows that
 $\lambda$ is outside $\sigma(T)$ and  finishes the proof of
 Theorem 6.7.2.
 \medskip
 
\noindent
{\bf{6.7.3 Spectral projections}}.
Let $\lambda_0$ be non-zero in
$\sigma(T)$.
By Theorem 6.7.2 it is an isolated poiunt in
$\sigma(T)$ which gives
 the spectral projection
$E_T(\lambda_0)$ where we recal, from ¤ xx that this
operator commutes with $T$.
So if Ê$V=E_T(\lambda_0)(X)$ then
$T$ restricts to a bounded linear operator on $V$
denoted by $T_V$ where we recall from ¤ xx that
the spectrum of $T_V$ is reduced to the singleton set
$\{\lambda_0\}$.
Since $\lambda_0\neq 0$ it means that
$T_V$
is an invertible and compact operator on
$V$. So by
the result in ¤ xx 
$V$ is finite dimensional. 
This finiteness and linear algebra applied to
$T_V$ gives an integer $m\geq 1$ such that
\[
(Tx-\lambda_0 x)^m=0\quad \colon x\in V\tag{6.7.3.1}
\]

\newpage

\centerline{\bf{6.8 Fredholm operators.}}
\medskip

\noindent
A bounded linear operator
 $u\colon X\to Y$ 
is called a  Fredholm operator 
if it has closed range and 
the kernel and the cokernel of $u$ are both  finite dimensional.
When $u$ is  
Fredholm  its index is defined by:
\[ 
\mathfrak{ind}(u)=
\text{dim}\, N_u-\text{dim}\bigl[\frac{Y}{u(X)}\bigr]
\]
\medskip

\noindent
{\bf 6.8.1  Theorem.} \emph{Let $u$ be of Fredholm type  and
$T\colon X\to Y$ a compact operator. Then
$u+T$ is Fredholm and one has the equality}
\[
\mathfrak{ind}(u)=
\mathfrak{ind}(u+T)
\]

\bigskip


\noindent
The proof requires several steps
where the crucial point is to regard 
the case $X=Y$ and a compact pertubation of the
identity operator. Thus we begin with:
\medskip


\noindent
{\bf 6.8.2  Theorem.} \emph{Let $T\colon X\to X$ be compact.
Then $E-T$ is Fredholm and has index zero.}

\medskip

\noindent
\emph{Proof.}
Apply (6.7.3) with $\lambda_0=1$ which gives
the decompostion
\[
X= E_T(1)(X)\oplus
(E-E_T(1))(X)\tag{i}
\]
Theorem 6.6.1 implies that
$E-T$ has closed range.
Next, from the spectral decomposition in (6.7.3)
it follows that 
 $E-T$ restricts to a bijective operator on
$(E-E_T(1))(X)$ which by (i)
entails that
the codimension of $(E-T)(X)$ is at most
the dimension of the finite dimensional vector space
$V=E_T(1)(X)$. Moreover, 
the kernel of $E-T$ is  finite dimensional by Theorem 6.6.1.
\medskip

\noindent
Hence we have proved that
$E-T$ is a Fredholm operator and there reamins to show
that its index is zero.
To obtain this we notice again that
the decomposition
(i) impies that this index is equal to that of
the restricted operator
$E-T$ to the finite dimensional vector space
$V$. Finally,  recall from linear algebra that
the index of a linear operator on a finite dimensional vector space always is zero
which
finishes the proof.
\medskip


\noindent
{\bf{6.8.3 The general case.}}
Consider first the case when the kernel of the Fredholm operstor
$u$ is zero.
Now there exists a finite dimensional subspace $W$ of $Y$ such that
\[
Y= u(X)\oplus W\tag{*}
\]
where $u\colon X\to u(X)$ is
an isomorphisn between the  Banach spaces $X$ and $u(X)$
which gives the existence of a bounded inverse operator
\[
\phi\colon u(X)\to X
\]
So here $\phi\circ u$ is the identity on $X$.
Next, given a compact operator $T$
we consider the projection operator
$\pi\colon Y\to  u(X)$ whose kernel is
$W$ and notice that $\pi\circ T$ is a compact operator.
Now we can regard the operator
\[ 
u+\pi\circ T\colon X\to u(X)
\]
From the above and Theorem 6.8.2 the reader can verify that
this Fredholm operator has index zero.
Next, we notice that
\[
\mathfrak{ind}(u)=-\dim W\tag{1}
\]
We have also the operator
\[ 
T_*=(E_Y-\pi)\circ T\colon X\to W
\]
The direct sum decomposition (*) entails that
\[
\ker(u+T)= \ker(u+\pi\circ T)\cap\, \ker T_*\quad\&\quad 
\frac{Y}{(u+T)(X)}=
\frac{Y}{(u+\pi\circ T)(X)}\oplus\frac{W}{T_*(X)}\tag{2}
\]
From (1-2) we leave it as an exercise
to show that
the index of $u+T$ is equal to that if $u$
given by (1).
\medskip

\noindent
Above we treated the case when $u$ is injective.
In general, since  $\mathcal N(u)$ is finite dimensional one has  a decompostion
\[ 
X= \mathcal N(u)\oplus X_*
\]
whewre the restricted operator $u\colon X_*\to Y$ is injective.
For a given compact operator
$T$ we can also consider the restricted compact operator
\[
T_*\colon X_*\to Y
\]
and the  previous special case gives the equality
\[
 \mathfrak{ind}(u_*+T_*)= \mathfrak{ind}(u_*)\tag{3}
\]

\noindent
Next, let  $\pi\colon X\to \mathcal N(u)$ be the projection with kernel $X_*$
which gives
\[ 
T=T_*+T\circ \pi
\] 
At this stage we leave it as an exercise to verify that
(3) gives the requested index formula 
\[
 \mathfrak{ind}(u+T)= 
 \mathfrak{ind}(u)
\]



\newpage

\centerline {\bf{7. Calculus on Banach spaces.}}

\bigskip

\noindent
Let $X$ and $Y$ be two real Banach spaces and
$g\colon\,X\to Y$ some map. Here $g$ is not assumed
to be linear. Since  
the Banach spaces are real   the dual space
$Y^*$ consists of continuous ${\bf{R}}$-linear maps from
$Y$ into ${\bf{R}}$ and 
every 
$y^*\in Y^*$ yields the real-valued function
$y^*\circ g$ on $X$.
With $x_0$ kept fixed
we can impose the condition that
there exist limits
\[
\lim_{\epsilon\to 0}\,  \frac{y^*\circ g(x_0+\epsilon\cdot x)-
y^*(g(x_0))}{\epsilon}\tag{1}
\]
for each vector $x\in X$.
These limits resemble directional derivatives in calculus and
we can impose the extra condition that
the limits above depend linearly upon $x$.
Thus, assume  that each $y^*\in Y$
yields a linear form $\chi(y^*)$ on $X$ such that
(1) is equal to 
$\chi(y^*)(x)$ for every $x\in X$.
When this holds it is clear that
\[ 
y^*\mapsto \chi(y^*)\tag{2}
\] 
is a linear mapping from $Y^*$ into $X^*$.
When both $Y$ and $X$ are finite dimensional real vector spaces
this linear operator corresponds to the usual Jacobian
in calculus.
In the infinite-dimensional case
it is not always true that
(2) is continuous with respect to the norms
on the dual spaces.
As an extra condition for differentaiblity at $x_0$ we impose the condition that
there exists a constant $C$ such that
\[
||\chi(y^*)||\leq C\cdot ||y^*||\tag{3}
\]
When (3) holds
we have a bounded linear operator $\chi\colon Y^*\to X^*$
associated to $g$ and the given point $x_0\in X$.
It may occur that $\chi$ is the adjoint of a bounded linear operator
from $X$ into $Y$ which 
means that there exists a bounded linear operator $L\colon X\to Y$
such that
\[
\lim_{\epsilon\to 0}\, 
\frac {||g(x_0+\epsilon\cdot x)-g(x_0)-\epsilon\cdot L(x)||}{\epsilon}=0\tag{*}
\]
\medskip

\noindent
Concerning the passage to the limit
the weakest condition is that it holds pointwise, i.e.
(*) holds for every vector $x$.
A stronger condition is to impose that
the limits above hold uniformly which means that
\[
\lim_{\epsilon\to 0}\, \max_{x\in B(X)}\, 
\frac {||g(x_0+\epsilon\cdot x)-g(x_0)-\epsilon\cdot L(x)||}{\epsilon}=0\tag{**}
\]
where the maximum is taken over 
$X$-vectors with norm $\leq 1$.
In applications the
the condition (**) is often taken as a definition for
$g$ to be differentiable at $x_0$ and the uniquely determined linear map 
$L$ above is denoted by $D_g(x_0)$ and called the differential of $g$ at $x_0$.
If $g$ is a map from some open subset
$\Omega$ of $X$ with values in
$Y$ we can impose the condition that
$g$ is differentiable at each $x_0\in \Omega$ and  add the 
condition that
$x\mapsto D_g(x)$ is continuous in $\Omega$ where the values are
taken in
the Banach space of continuous linear maps from $X$ into $Y$.
When this holds we get another map
$x\to D_g(x)$ from $\Omega$ into $\mathcal L(X,Y)$
and can impose the condition that it also is differentiable in the strong sense above.
This leads  to the notion of $k$-times continuosly differentiable maps from
a Banach space into another for every positive integer $k$.
\medskip

\noindent
{\bf{Remark.}} We shall not dwell upon a general study of differentiable maps between 
Banach spaces which is best illustrated by
various examples. For a concise
treatment we refer to Chapter 1 in Hšrmander's text-book
[PDE:1]
which 
contains a proof of the implicit function theorem
for
differentiable maps between Banach spaces
in its most general set-up.

\newpage

\centerline {\bf 7.1 Line integrals}
\medskip

\noindent
Let  $Y$ be a Banach space. Consider a
continuous map $g$ from  some open set
$\Omega$ in ${\bf{C}}$ with values in $Y$.
Let  $t\mapsto \gamma(t)$ be a parametrized $C^1$-curve
whose image is a compact subset of $\Omega$.
Then there exists  the $Y$-valued line integral
\[
\int_\gamma\, g\cdot dz
=\int_0^T\, g(\gamma(t))\cdot \dot\gamma(t)\cdot dt \tag{*}
\]
The evaluation is performed exactly as for ordinary
Riemann integrals, Namely, one uses the fact that
the
$Y$-valued function
\[ t\mapsto g(\gamma(t))
\] 
is uniformly continuous with respect to the norm on
$Y$, i.e. the Bolzano-Weierstrass theorem gives:
\[
\lim_{\epsilon\to 0}
\,\max_{|t-t'|\leq\epsilon}\,||g(t)-g(t')||=0
\]
Then (*) is approximated by Riemann sums and since
$Y$ is complete this gives
a unique limit vector in $ Y$.

\centerline{\bf{7.2 Uniformly convex    Banach spaces.}}
\medskip

\noindent
From now on $X$ is a  complex
Banach space.
One says that 
$X$ is uniformly  convex if there corresponds to each 
$0<\epsilon<1$ some $\delta(\epsilon)$ tending to zero with
$\epsilon$  such that

\[ 
\frac{||x+y||}{2}\geq 1-\epsilon\implies
||x-y||\leq \delta(\epsilon)\tag{7.2.1}
\]
for all pair of vectors of norm one at most.
This condition   was introduced by Clarkson
in the article [Clarkson] from
1936. 
\medskip

\noindent
{\bf{Exercise.}}
Show  that in a uniformly convex Banach space
each closed convex set contains a unique vector of minimal norm.

\medskip

\centerline{\bf{7.3 Directional derivatives.}}
\medskip

\noindent
Let 
$p\in X $  be a non-zero vector. 
If $x\neq 0$ is another vector
we get the function of a real variable $a$ defined by:
\[
a\mapsto ||p+ax||-||p||
\]
We say that a  directional $x$-derivative exists at $p$ if there exists the limit
\[
\lim_{a\to 0}\,\frac{||p+ax||- ||p||}{a}=
D_p(x)
\]
Notice that in this limit $a$ can tend to zero both from
the negative and the positive side.
The following result is due to Clarkson:




\medskip

\noindent
{\bf{7.3.1 Theorem}} \emph{Let $p$ be a non-zero vector in
$X$ such that the directional derivatives above exist for every
$x\in X$. Then $x\mapsto D_p(x)$ is ${\bf{R}}$-linear. Moreover}
\[
|D_p(x)|\leq ||x||
\]
\emph{hold for every $x$ and 
$D_p(p)=1$.}
\medskip

\noindent
{\bf{Exercise.}} Prove Clarkson's Theorem.



\medskip

\centerline {\bf{7.4 Conjugate vectors.}}
\medskip

\noindent
For brevity we say that
$X$ is differentiable if  directional derivatives  exist for all pairs $p,x$.
Let $S$ be the unit sphere in $X$ and $S^*$ the unit sphere in
$X^*$. A pair $x\in S$ and $x^*\in S^*$ are said to be conjugate if
\[ 
x^*(x)=1
\]


\noindent
{\bf{7.4.1   Theorem.}} \emph{Let $X$ be uniformly convex and 
differentiable. Then every $x\in S$ has a unique conjugate
given by $x^*=D_x(x)$ 
and  the map $x\to x^*$ from $S$ to
$S^*$ is bijective.}



\medskip

\noindent
{\bf{Exercise.}}
Prove this result.If necessary, consult
Clarkson's article or some text-book.


\newpage


\centerline{\bf{7.5. Duality maps.}}
\medskip

\noindent
Assume that 
$X$ be uniformly convex and differentiable.
As usual $S$ denotes the unit sphere in $X$.
Let  
$\phi(r)$ be   a strictly increasing and continuous function on
$r\geq 0$ where $\phi(0)=0$ and 
\[
\lim_{r\to+\infty}\, \phi(r)=+\infty
\]
Each vector in
$X$ is of the form
$r\cdot x$ with $x\in S$ while $r\geq 0$.
Clarkson'a  conjugate in Theorem 7.4.1  yields a function
$\mathcal D_\phi$ from $X$ into $X^*$ defined by
\[ 
\mathcal D_\phi (rx)= \phi(r)\cdot x^*
\quad\text{when}\quad  x\in S\quad\text{and}\quad  r\geq 0
\]
If $C$ is a closed subspace in $X$ we put:
\[ 
C^\perp=\{\xi\in X^*\, \colon\, \xi(C)=0\}
\]



\noindent
{\bf{7.5.1 Theorem.}}
\emph{For each closed 
and proper subspace $C\neq X$  the following hold:
For 
every pair of vectors $x_*\in X$ and $y^*\in X^*$
the intersection}
\[ 
\mathcal D_\phi(C+x_*)\cap \{C^\perp+y*\}
\]
\emph{is non\vvv empty and consists of a single point in $X^*$.}


\medskip

\noindent
\emph{Proof.} Introduce the function
\[ 
\Phi(r)= \int_0^r\,\phi(s)\, ds
\]
Since $\phi$ is strictly increasing,
$\Phi$ is a strictly convex function
and since $\phi(r)\to +\infty$ we have
$\frac{\Phi(r)}{r}\to +\infty$.
Consider the functional defined on $C+x_*$
by

\[ 
F(x)= \Phi(||x||)-y^*(x)
\]
If $||x||= r$ we have
\[ 
F(x)\geq \Phi(r)-r||y^*||
\]
The right hand side is a strictly convex function of $r$
which tends to $+\infty$ and is therefore bounded below. Hence
there exists  a number
\[ 
\delta =\inf_{x\in C+x_*}\, F(x)
\]
Let $\{x_n\}$ be a minimizing sequence for $F$.
The strict convexity of $\Phi$ entails that
the norms $\{||x_n||\}$ converge to some finite limit $\alpha$.
Since the set $C+x_*$ is convex we have
\[ 
F(\frac{x_n+x_m}{2})\geq \delta
\]
Next, the convexity of $\phi$ entails that
\[
0\leq \frac{1}{2}\bigl[ \Phi(||x_n||)+
\Phi(||x_m||)-\Phi(||\frac{x_n+x_m}{2}||)=
\]
\[
 \frac{1}{2}\bigl(F(x_n)+F(x_m))-
 F(\frac{x_n+x_m}{2})
 \]
Since $\{x_n\}$ is $F$-minimizing the last terms tend to zero when
$n$ and $m$ increase which gives
\[
\lim_{n,m\to \infty}\, \Phi(||\frac{x_n+x_m}{2}||)=\Phi(\alpha) \tag{1}
\]
where we recall that
\[ 
\alpha=\lim_{n\to\infty}\, ||x_n||
\]
Now (1) and the strict convexity of $\Phi$ gives
\[
\lim_{n,m\to \infty}\, ||\frac{x_n+x_m}{2}||)=\alpha 
\]
The unifom convexity entails  that
$\{x_n\}$ is a Cauchy sequence which gives  a limit
point $p$ where $F(p)= \delta $ and consequently
\[ 
F(p+tx)-F(p)\geq 0\quad\colon\quad
x\in C\tag{2}
\]
Since $p$ belongs to $C+x_*$ the existence part in Theorem
7.14 follows if we have proved the inclusion
\[
\mathcal D_\phi(p)\in C^\perp+y^*\tag{3}
\]

\medskip

\noindent
To get (3) we use that the Banach space is differentiable
and since the $\Phi$-function as a primitive of a continuous function is of class $C^1$
one has

\[
\Phi(||p+tx||)-\Phi(||p||)=
\Phi'(||p||)\cdot \mathfrak{Re}\, tD_p(x) +o(|t|)=
\phi(\alpha)\cdot \mathfrak{Re}\, tD_p(x)+o(|t|)
\]
where $t$ is a small real or complex number.
Together with (2) this gives
\[
\phi(\alpha)\cdot \mathfrak{Re}\, tD_p(x)+o(|t|)\geq
\mathfrak{Re}\, y^*(tx)\quad\colon\quad x\in C
\]
By linearity it is clear that this implies that
\[
\phi(\alpha)\cdot D_p(x)= y^*(x)
\]
This means precisely that
the linear functional $y^*-\phi(\alpha)\cdot D_p$ belongs to $C^\perp$,
or equivalently that
\[ 
\phi(||p||)\cdot D_p\in C^\perp+y^*
\] 
Finally we recall from (7.13) 
that  
\[
\mathcal D_\phi(p)=\phi(||p||)\cdot D_p(p)
\]
and  the requested inclusion (3) is proved.
\medskip

\noindent
\emph{The uniqueness part.}
Above we proved the existence of at least one point in
the intersection from Theorem 7.12. The verification that
this set is reduced to a single point is left as an exercise to the reader.

\newpage

\newpage

\centerline {\bf {¤ 8. Locally convex spaces}}
\bigskip



\noindent
{\bf{Introduction.}}
We  expose  facts about
real vector spaces  equipped with a locally convex topology.
The definition is given in ¤ 2.
A crucial result is  the Hahn-Banach theorem for lcoally convex
spaces  in  ¤ 1.
It 
has several important consequences
such as Hšrmander's result in
Theorem 3.6.


\bigskip

\centerline{\bf{¤ 1. Convex sets and their $\rho$-functions.}}
\medskip


\noindent
Let $E$ be a real vector space.
A convex  set $U$ which contains the origin is said to be
absorbing if there for  
each vector
$x\in E$  exists some
real $s>0$ such that
$s\cdot x \in U$.
It may occur that
the whole line
${\bf{R}}x$ is contained in $U$, and then  we say that
$x$ is fully absorbed by $U$.
The convexity of $U$ entails that
the set of fully absorbed vectors is a linear subspace of $E$ which we denote by
$\mathcal L_U$.
\medskip


\noindent
{\bf{1.1 The function
$\rho_U$.}}
Let $x$ be a  non-absorbed vector $x$. Then there exists a positive real number 
\[
\mu(x)=\max\{ s\,\colon sx\in U\}
\]
If $x$ is absorbed we put $\mu(x)=+\infty$ and
for every non-zero vector $x$
we set
\[ 
\rho_U(x)=\frac{1}{\mu(x)}
\]
it is clear that if $x\in U$ then
$\mu(x)\geq 1$ and hence $\rho_U(x)\leq 1$.
Notice that we also have
\[
\rho_U(x)=\min\{s\, \colon\,x\in s^{-1}U\}
\]
\medskip



\noindent
{\bf{1.2 Exercise.}}
Show that the convexity of $U$ entails that
$\rho_U$ satisfies the triangle inequlity
\[
\rho_U(x_1+x_2)\leq \rho_U(x_1)+\rho_U(x_2)\tag{1.2.1}
\]
for all pairs of vectors in $E$.
Moreover, check also that
$\rho_U(x)=0$ if and only if
$x$ belongs to
$\mathcal L_U$ and that $\rho_U$ is positively homogeneous, i.e.
the equality below holds when $a$ is real and positive:
\[
\rho_U(ax)= a\rho_U(x)\quad\colon a>0\tag{1.2.2}
\]

\noindent
{\bf{1.3 The Hahn-Banach theorem.}}
Keeping $U$ fixed we set $\rho(x)= \rho_U(x)$.
An ${\bf{R}}$-linear map
$\lambda$ from $E$ to the 1-dimensional real line
is majorised by $\rho$ if
\[
\lambda(x)\leq \rho(x)\tag{1.3.1}
\]
hold for every vector $x$.
More generally, let $E_0$ be a subspace of $E$ and
$\lambda_0\colon E_0\to {\bf{R}}$ a linear map such that
(1.3.1) hold for vectors in $E_0$.
Then there exists a linear map
$\lambda\colon E\to {\bf{R}}$ which extends 
$\lambda_0$ and is again majorised by $\rho$. This result was proved in ¤ 4.A.4.

\bigskip



\centerline {\bf{8.2 Locally convex topologies.}}
\bigskip


\noindent
Denote by $\mathcal C_E$ the family of convex sets $U$ as in ¤ 1.
Let
$\mathfrak{U}= \{U_\alpha\}$ be a family in  $\mathcal C_E$ such that
\[
\bigcap\,\mathcal L_{U_\alpha}=\{0\}
\]
i.e. the intersction is reduced to the origin.
Now there exists a topology on $E$
where a basic for open neighborhoods of the origin
consists of sets:
\[
\cap\, \{\rho_{U_{\alpha_i}}(x)<\epsilon\}\tag{1}
\] 
where $\epsilon>0$ and $\{\alpha_1,\ldots,\alpha_k\}$ is a finite set
of indices defining the  $U$-family.
If $x_0$ is a vector in $XS$, then
a basis for its open neihghborhoods
are given by
sets of the for $x_0+U$ where $U$ is a set from (1).
In general, a subset $\Omega$ in $E$ is open if
there to eah $x_0\in\Omega$ exists some
$U$ from (1) such that
$x_0+U\subset \Omega$.
it is clear that this gives a topology and (1) entaills that it is separated, i.e. a Huasdorff topology on
$E$.
Notice also that eqch set in 82) is convex. One therefore
refers to a locally con vex
topology on $E$.
\medskip
 
 \noindent
 {\bf{2.1  Remark.}}
 The locally convex topology above depends upon the family
 $\mathfrak{U}$-toplogy. Its topology  is not changed if we enlarge 
 the family to consist of all finite intersection of its
 convex subsets. When this has been done
 we notice that if $U_1,\ldots, U_n$ is a finite family in
 $\mathfrak{U}$ then the norm defined by
 $U=U_1|\cap\ldots\,\cap U_n$ is stronger than
 the individual $\rho_{U_i}$-norms. Hence
 a fundamental system of neighborhoods 
 consists of single $\rho$-balls:
  \[
 \Omega=\{\rho_U<\epsilon \}    \quad\colon U\in\mathfrak {U}
 \]
 
 \medskip
 
 \noindent
 {\bf{2.2 The dual space $E^*$}}.
Let $E$ be equipped with a locally convex $\mathfrak{U}$-topology.
As above $\mathfrak{U}$ has been enlarged so that
the balls above  give a basis for neighborhoods of the origin.
A linear functional  $\phi$ on $E$
is $\mathfrak{U}$-continuous if  there
exists some
$U\in\mathfrak{U}$ and a
constant $C$ such that
\[
|\phi(x)||\leq C\cdot \rho_U(x)
\]
\medskip


\noindent
{\bf{2.3 Closed half-spaces.}}
To each pair 
$\phi\in E^*$ and a real number $a$ one assigns the
closed half-space
\[
H=\{x\in X\,\colon\, \phi(x)\leq a\}
\]
Notice that $a<0$ can occur in which case
$H$ does not contain the origin.
\medskip

\noindent
{\bf{2.4 The separation  theorem.}}
\emph{Each closed convex set $K$ in $E$ is the intersection of closed half-spaces.}



\medskip
\noindent
{\bf{2.5 Exercise.}}
Show (2.4)  using the Hahn-Banach theorem.
\medskip


\noindent
Next, let $K_1$ and $K_2$ be a pair of closed and disjoint convex sets.
Then they can be spearated by a hyperplane. More precisley, there
exists some $\phi\in E^*$ and a positive number $\delta$ such that
\[
\max_{x\in K_1}\, \phi(x)+\delta\leq
\min_{x\in K_2}\, \phi(x)\tag{2.6}
\]
Again we leave the proof as an exercise to the reader.

\bigskip


\centerline {\bf{8.3. Support functions of convex sets.}}
\medskip


\noindent
Let $E$ be a locally convex space as above.
Vectors in $E$ are denoted by  $x$, while $y$ denote  vectors in $E^*$.
To each closed and convex subset $K$ of $E$
we define a function $\mathcal H_K$ on the dual $E^*$ by:
\[ 
\mathcal H_K(y)=\sup_{x\in K}\,y(x)
\]


\noindent
Notice that  $\mathcal H_K$
take values in $(-\infty,+\infty]$, i.e. it may be $+\infty$ 
for some vectors $y\in E^*$.
For example, let $K=\{{\bf{R}}^+x_0$ be a half-line.
Then $\mathcal H_K(y)=+\infty$ when
$y(x_0)>0$
and otherwise zero. So here the range consisists of 0 and $+\infty$.
It is clear that
\[
\mathcal H_K(sy)= s\mathcal H_K(y)
\] 
hold when $s$ is a positive real number, i.e
$\mathcal H_K$ is positively homogeneous.



\medskip

\noindent
{\bf{3.1 Exercise.}}
Show that the convexity of $K$ entails that
\[
\mathcal H_K(y_1+y_2)\leq 
\mathcal H_K(y_1)+
\mathcal H_K(y_2)
\]
for each pair of vectors in $E^*$.
\medskip




\noindent
{\bf{3.2 Upper semi-continuity.}}
For each fixed vector $x\in E$
the function 
\[ 
y\mapsto y(x)
\]
is weak-star continuous on $E^*$.
Since
the supremum function attached to
an arbitrary family of weak-star continuoes functions is upper
semi-continuous, it follows that $\mathcal H_K$ is upper semi-contiuous.
\medskip

\noindent
{\bf{3.4 Exercise.}}
Let $K$ and $K_1$ be a pair of closed convex sets such that
$\mathcal H_K=\mathcal H_{K_1}$. Show that this entails that $K=K_1$.
The hint is to use the separation theorem.
\medskip

\noindent
{\bf{3.5 The class $\mathcal S(E)$}}.
It consids of all  
all upper semi-continuous functions
$G$ on $E^*$ with values in $(-\infty,+\infty]$
which satisfy (x) and (xx).
The next result 
was proved by   Hšrmander 
in the article
\emph{Sur la fonction d'appui des ensembles convexes dans un espaces
localementt convexe} [Arkiv fšr mat. Vol 3: 1954].

\medskip

\noindent
{\bf{3.6 Theorem.}}
\emph{Each $G\in\mathcal S(E)$ is of the form
$\mathcal H_K$ for a unique closed convex subset $K$ in $E$.}
\medskip

\noindent
{\bf{Remark.}}
As pointed out by Hšrmander in [ibid] this result
is closely related to  earlier studies by
Fenchel in the article \emph{On conjugate convex functions}
Canadian Journ. of math. Vol 1 p. 73-77) 
where  Legendre transforms are
studied in infinite dimensional topological vector spaces.
The novely in Theorem 3.3 is the generality and we
remark that various separation theorems 
in text-books dealing with notions of convexity
are easy consequences of Theorem 5.C.2.


\bigskip



\noindent{\emph{Proof of Theorem 3.6 }}
Put $F=E\oplus{\bf{R}}$ which is a new vector space where
the 1-dimensional real line is added. It dual space
$F^*=E^*\oplus{\bf{R}}$.
We are given $G\in\mathcal S(E)$ and 
put
\[
G_*=\{(y,\eta)\in E^*\oplus {\bf{R}}\quad\colon\, G(y)\leq \eta\}\tag{i}
\]
Condition in (*) entails that $G_*$ is a convex cone
in $F^*$ and the semi-continuous hypothesis on $G$
implies that  $G_*$ is closed with respect to the weak-star toplogy on $F^*$.
Next, in $F$ we define the set
\[ 
G_{**}=\{(x,t)\in E\oplus{\bf{R}}^+\,\colon\, y(x)\leq \eta t\,\colon\, (y,\eta)\in G_*\}\tag{ii}
\]
This gives a set
$\widehat C$ in 
$F^*$ which consists of vectors  $(y,\eta)$ such that
\[
\max_{(x,t)\in 
G_{**}}\,y(x)- \eta t\leq 0
\]
It is clear that
$G_*\subset \widehat C$. Now we prove the equality

\[
G_*= \widehat C\tag{*}
\]
To get (*) we use Theorem 2.4.
Namely, since
the two sets in (*)  are weak-star closed a strict inequality
gives a separating
vector $(x_*,t_*)\in E$, i.e.  there exists $(y_*,\eta_*)\in \widehat C$
and a real number $\alpha$ such that 
\[
y_*(x_*)-\eta _* t_*>\alpha
\quad\text{and}\quad (y,\eta)\in D_K\implies y(x_*)-\eta t_*\leq \alpha\tag{iv}
\]
Since $G_*$ contains $(0,0$ we  have $\alpha\leq 0$.
and since it also is a cone the last implication  gives
$(x_*,t_*)\in G_{**}$. Now
the construction of $\widehat{C}$ in (iii) contradicts the strict inequality in
the left hand side of (iv).
Hence there cannot exist
a separating vector and  (*) follows.
\medskip

\noindent
Next, in  $E$ we consider  the convex set
\[
K=\{ x\,\colon (x,1)\in G_{**}\}
\]
Using (*) the reader can check that
\[
\mathcal H_K(y)=G(y)
\]
 for all $y\in E^*$ which proves that $G$ has the requested form.
 The uniqueness of $K$ follows from Exercise 3.4.
 
 

\bigskip

\noindent
{\bf{3.7  The case of normed spaces.}}
If $X$ is a normed vector space Theorem 3.6 
leads to a certain isomorphism of two families.
Denote by $\mathcal K$ the family of all convex
subsets of $E$ which are closed with respect to the norm topology.
A topology on $\mathcal K$ is defined
when we for each $K_0\in\mathcal K$ and $\epsilon>0$
declare an open neighborhod
\[ 
U_\epsilon(K_0)=\{ K\in\mathcal K\,\colon\,
\text{dist}(K,K_0)<\epsilon\}
\] 
where the norm defines the distance between
$K$ and $K_0$ in the usual way.
Denote by $\mathfrak{H}$ the family of all
functions $G$ on $E^*$ which satisfy (*) in 5.B.1 and are continuous
with respect to the norm topology on $E^*$.
A subset $M$ of $\mathfrak{H}$ is equi-continuous if there
to
each $\epsilon>0$ exists $\delta>0$ such that
\[
||y_2-y_1||<\delta \implies ||G(y_2)-G(y_1)||<\epsilon
\] 
for every $G\in M$ and 
all pairs $y_1,y_2$ in $E^*$.
The topology on $\mathfrak{H}$ is  defined
by  uniform convergence on equi-continuous subsets.

\medskip




\noindent
{\bf{3.8 Theorem.}}
\emph{If $E$ is a normed vector space
the set-theoretic bijective map $K\to \mathcal H_K$ is
a homeomorphism when
$\mathcal K$ and
$\mathfrak {H}$ are equipped with the described topologies.}
\medskip

\noindent
{\bf{3.9 Exercise.}} Deduce this  result 
from     Theorem 3.6








\newpage

\centerline{\bf{¤ 9. Fixed point theorems.}}
\bigskip



\noindent
A compact topological space $S$ has the fixed point property
if every continuous map $T\colon S\to S$
has at least one fixed point.
An example is the closed unit ball in ${\bf{R}}^n$ whose  fixed-point
property is proved in ¤ 5.xx.
More generally, consider
a locally convex vector space $X$.
In ¤ 8 we   constructed of its dual space $X^*$ whose vectors
are continuous linear functionals on $X$.
Now one equips $X$  with the weak
topology whose open sets are generated
by pairs
$x^*\in X^*$ and positive numbers
$\delta)$ of the form:
\[
B_\delta(x^*)= \{ x\in X\,\colon\, |x^*(x)|\leq \delta\}
\]
Denote by $\mathcal K(X)$   the family of
convex subsets  of $X$ which are
compact
with respect to
the $X^*$-topology. We are going to prove the following two results.

\bigskip

\noindent
{\bf{9.1 The Schauder-Tychonoff fixed point theorem.}}\emph{
Each $K$ in $\mathcal K(X)$ has the fixed point property.}

\medskip

\noindent
The merit of this result is of course that one allows
non-linear maps. The next
result is  due to Kakutani.
Here $X$ is a normed space over the field of real numbers.
By a semi-group of linear transformations
$\bf{G}$ on a real vector space $X$ we mean a family of linear maps
$g\colon X\to X$ such that composed maps $g_2\circ g_1$
again belong to ${\bf{G}}$.
\medskip

\noindent
{\bf{9.2 Kakutani's theorem.}} \emph{Let $K\in\mathcal K(X)$ be 
$\bf {G}$-invariant,  i.e. $g(K)\subset K$  for every
$g\in{\bf {G}}$. 
Assume in addition that the family of the restricted
${\bf{G}}$-maps to $K$ is equicontinuous.
Then there exists at least some
vector $k\in K$ such that $g(k)=k$ for every
$g\in{\bf{G}}$.}
\medskip

\noindent
{\bf{Remark.}}
The equi-continuous assumption means that to each pair
every $(x^*,\epsilon)$ with $x^*\in X^*$ and $\epsilon>0$ , there exists a finite
family $x^*_1,\ldots,x^*_M$ and some $\delta>0$
such
that the following hold: If
$p$ and $q$ is a pair of points in $K$ such that
$p-q$ belongs to $\cap\, B_\delta(x^*_\nu)$, then
\[
g(p)-g(q)\in B_\epsilon(x^*)
\] 
hold for all $g\in {\bf{G}}$.
\medskip

\noindent
{\bf{9.3 Haar measures.}}
Let $G$ be a compact topological group which
means that the  group is equipped with a Hausdorff topology where
the group operations are continuous, i.e the map from
$G\times G$ into $G$ which sends a pair of group elements $g,h$ to
the product $gh$ is continuous, and  the inverse map $g\mapsto g^{-1}$
is bi-continuous.
Let
$C^0(G)$ be the Banach space
of continuous real-valued functions on $G$.
Recall from basic measure theory that
the dual space
consists of Riesz measures. Denote by $P(G)$ the family of non-negative measures with
total mass one, i.e. probability measures onÊ$G$.
If $\phi\in C^0(G)$
and $g\in G$ we get the new continuous function
$S_g(\phi)$ defined by
\[ 
S_g(\phi)(h)=\phi(gh)\quad\colon h\in G
\]
Next, every   $\mu\in P(G)$ gives the probability measure
$T_g(\mu)$ for which 
\[
\int_G\, S_g(\phi)\, d\mu=\int_G\, \phi\, dT_g(\mu)
\]
In this way $G$ is identified with a group of linear maps
on $P(G)$.
Next,  $P(G)$ is equipped with the weak-star topology
where  open neighborhoods of
a given $\mu\in P(G)$ consists of
finite intersections of sets
$\{\gamma\in P(G)\,\colon |\gamma(\phi)-\mu(\phi)|<\delta\}$
for pairs $\delta>0$ and $\phi\in C^0(G)$.
The  uniform continuity of every $\phi \in C^0(G)$
entails that
that the group action on
$P(G)$ is equi-continuous 
with respect to the weak-star topology.
Kakutani's theorem  applies  and
yields
a fixed point. Hence  there is a probability measure
$\mu_*$ such that
\[
\int_G\, \phi(gh)\, d\mu_*(h)=\int_G\,\phi(h)\, d\mu_*(h)\tag{*}
\] 
hold for every pair $g\in G$ and
$\phi \in C^0(G)$.
This is expressed by sayung that
$\mu_*$ is left invariant. It turns out that 
$\mu_*$ is unique,  i.e.
only one probability measure enjoys the invariance above.
Moreover,  starting with the operators
\[ 
S^*_g(\phi)(h)=\phi(hg)\quad\colon h\in G
\]
one finds a probability measure $\mu^*$ such that
\[
\int_G\,\phi(hg)\, d\mu^*(h)=\int_G\,\phi(h)\, d\mu^*(h)\tag{**}
\] 
hold for every pair $g\in G$ and
$\phi \in C^0(G)$.
A wellknown fact about compact topological groups asserts 
$\mu^*=\mu_*$
 and this unique probability measure os called the Haar measure on $G$.


\bigskip




\centerline{\bf{Preliminary results.}}
\medskip

\noindent
Using Stokes theorem one has the  classical  result:
\medskip


\noindent
{\bf{9.4 Theorem.}}
\emph{The closed unit ball in ${\bf{R}}^n$ has the fixed point property.}


\medskip


\noindent
\emph{Proof.}
By Weierstrass approximation theorem
every continuous map from $B$ into itself can be approxiated unifomly by
a $C^\infty$-map. Together with the compactness of $B$ the reader
can check that it suffices to prove every $C^\infty$-map
$\phi\colon B\to B$  has at least one fixed point.
We are going to derive this  by  contradiction, i.e suppose that
$\phi(x)\neq x$ for all $x\in B$.
Each  $x\in B$ gives the quadratic equation  in the variable $a$
\[
1= |x+a(x-\phi(x)|^2=|x|^2+2a(1-\langle x,\phi(x)\rangle )+a^2|x-\phi(x)|^2\tag{i}
\]


\noindent
{\bf{Exercise 1.}}
Use that $\phi(x)\neq x$,
to check that
(i) has two simpe roots for
each $x\in S$, and if $a(x)$ is the larger, then
the function $x\mapsto a(x)$
belongs to $C^\infty(B)$. Moreover
\[
a(x)=0\quad\colon x\in S\tag{E.1}
\]


\medskip


\noindent
Next,  for each real number $t$ we set
\[
f(x,t)= x+ta(x)(x-\phi(x))
\]
This is a vector-valued function of the $n+1$ variables $t,x_1,\dots,x_n$
where $x$ varies in $B$.
With $f=(f_1,\ldots,f_n)$ we  set
\[
g_i(x)=a(x)(x_i-\phi_i(x)
\]
Taking partial derivatives
with respect to $x$ we get
\[
\frac{\partial f_i}{\partial x_k}= e_{ik}+t\frac{\partial g_i}{\partial x_k}\tag{ii}
\]
where $e_{ii}=1$ and $e_{ik}=0$ if $i\neq k$.
Let $D(x;t)$ be the determinant of the $n\times n$-matrix
whose elements are the partial derivatives in (ii) and put
\[ 
J(t)=\int_B\, D(x;t)\, dx\tag{iii}
\]
When $t=0$ we notice that the $n\times n$-matrix above
is the identy matrix and hence
$D(x;0)$ has constant value one so that  $J(0)$ is the volume of $B$.
Next, (i) entails that 
$x\mapsto f(x;1)$ satisfies the functional equation
\[
|f(x;1)|^2=1
\]
which implies  that $x\mapsto D(x;1)$ is identically zero
and hence $J(1)=0$.
The requested contradiction follows if 
$t\mapsto J(t)$
is  a constant function of $t$. To attain  this we shall need:
\medskip

\noindent
{\bf{2. Exercise.}}
Use Leibniz's rule and that determinants of matrices with
two equal columns are zero to conclude that
\[
\frac{d}{dt}(D(x;t)= \sum\sum\, (-1)^{j+k}\cdot
\frac{\partial g_i}{\partial x_k}\tag{E.2}
\] 
where the double sum extends over all pairs $\leq j,k\leq n$.
\medskip

\noindent
Next, for all pairs $i.k$, Stokes theorem gives
\[
\int_B\, \frac{\partial g_i}{\partial x_k}\, dx=
\int_S\, g_i\cdot {\bf{n}}_k\, d\omega\tag{iv}
\]
where $\omega$ is the area measure on the unit sphere.
From (E.1)  we have $g_i=0$ on $S$ for each $i$.
Hence (E.2) and (iv)  imply that
\[
\frac{dJ}{dt}=\int_B\, \frac{d}{dt}(D(x;t)\, dx=0
\]
So $t\mapsto J(t)$ is constant which is impossible  because
$J(0)=1$ and $J(1)=0$ which  finishes  the proof.

\bigskip

\noindent {\bf{9.5 The Hilbert cube $\mathcal H_\square$}}.
This is  the closed subset of
the Hilbert space $\ell^2$ 
which consists of vectors $x=(x_1,x_2,\ldots)$ such that
$|x_k|\leq 1/k$ for each $k$.
\medskip



\noindent
{\bf{9.5.1 Proposition.}}
\emph{Every closed and convex subset of
$\mathcal C$ has the fixed point property.}
\medskip

\noindent
{\bf{9.5.2 Exercise.}} Deduce this result from Theorem 9.4.

\bigskip

\noindent
Next, let $X$ be a locally convex vector space and $X^*$ its dual.
Denote by  $\mathcal K(X)$ the family of convex subsets 
which are compact with respect to the  weak topology on $X$. 
Let $K\in \mathcal K(X)$ and $T\colon K\to K$
a continuous map with respect to the weak topology.
For each fixed  $f\in X^*$,  it follows from our assumptions that 
the complex-valued function on $K$ defined by
\[
p\mapsto f(T(p))
\]
is uniformly contnuus with respect to the weak topology.
So for each positive integer $n$ there exists a finite set
$G_n=(x^*_1,\ldots,x^*_N)$ and some $\delta>0$
such that the following implication holds for each pair of points
$p,q$  in $K$:
\[
p-q\in\cap \, B_\delta(x^*_\nu)\implies 
|f(T(p))-f(T(q))|\leq n^{-1}\tag{i}
\]
We can attain this for each positive integer  $n$ and get a denumerable set
\[
G=\,\cup \, G_n
\]
From (i)  it is clear that if
$p,q$ is a pair in $K$ and $g(p)=g(q)$ hold for every $g\in G$, then
$x^*(T(p))=x^*(T(q)$.
We refer to $G$ as a determining set for the map $T$.
In a similar way we find a denumerable
determining set
$G^{1)}$
for $g_1$, By a standard diagonal argument the
reader may verify the following:
\medskip


\noindent
{\bf{9.6 Proposition.}}
\emph{There exists a denumerable subset
$G$ in $X^*$ which contains $f$ and  is self-determining in the sense that
it determines each of its vectors as above}.

\bigskip


\noindent
{\bf{9.7 An embedding into the Hilbert cube.}}
During the construction of the finite $G_m$-sets which
give (i), we can choose small $\delta$-numbers and
take $\{x^*_\nu\}$  such that the maximum values
\[
\max_{p\in K}\, |x^*_\nu(p)|
\] 
are small.
From this observation the reader should confirm that
in Proposition 9.6 we can construct 
the sequence
 $G=(g_1,g_2,\ldots)$  in such a way that
 \[
 \max_{p\in K}\, |g_n(p)|\leq n^{-1}
\]
hold for every $n$.
Hence each $p\in K$ gives the vector
$\xi(p)=(g_1(p),g_2(p),\ldots)$ in the Hilbert cube
and now 
\[
K_*=\{\xi(p)\,\colon\, p\in K\}
\]
yields a convex subset of $\mathcal C$.
Since $G$ is self-determininig we have
$T(p)=T(q)$ whenever $\xi(p)=\xi(q)$. Hence
there exists a  map from
$K_*$ into itself defined by
\[
T_*(\xi(p))= \xi(T(p)\tag{*}
\]
\medskip

\noindent
{\bf{Exercise.}}
Use the compact property of $K$ to show that
$K_*$ is closed in the Hibert cube and that
$T_*$ is a continuous map with respect to the induced 
strong norm topology on $K_*$ derived from the
complete norm on $\ell^2$.
\medskip

\noindent
{\bf{9.8 A consequence.}}
Suppose from the start that
we are given a pair of points $p_1,p_2$  in $K$ and some
$f\in X^*$ where $f(p_1)\neq f(p_2)$.
From the above $f$ appears in the $G$-sequence and put
\[
K_0=\{p\in K\colon\, \xi(p)=\xi (p_1)\}
\]
Then $K_0$ is a 
convex subset of $K$, and since
$f$ appears in the $G$-sequence it follows that
$p_2$ does not belong to $K_0$.
Moreover, since $G$ is self-determining with respect to $T$ it 
is clear that 
\[
T(K_0)\subset K_0
\]
Hence we have proved:

\medskip

\noindent
{\bf{9.9 Proposition.}} \emph{For each pair
$K$ and $T$  as above where $K$ is not reduced to a single point, there
exists a proper and $X^*$-closed convex subset $K_0$ of $K$ such that
$T(K_0)\subset K_0$.}
\bigskip


\centerline {\bf{9.10 Proof of the Schauder-Tychonoff theorem.}}
\bigskip

\noindent
Let $T\colon K\to K$
be a continuous map where $K$ belongs to $\mathcal K(X)$.
Consider the family  $\mathcal F$
of all closed and convex subsets
which are $T$-invariant. It is clear that
intersections of such sets enjoy the same property. So we find
the minimal set
\[
K_*= \bigcap\, K_0
\]
given by the intersection of all sets $K_0$
in
$\mathcal F$.
If $K_*$ is not reduced to a single point then Proposition  6.1
gives a proper closed subset which again belongs to
$\mathcal F$. This is contradicts the minimal property.
Hence $K_*=\{p\}$ is a singleton set and $p$ 
gives the requested fixed point for $T$.
\bigskip

\bigskip

\centerline{\bf{9.11 Proof of Kakutani's theorem.}}
\bigskip

\noindent
With the notations from the introduction we are given a semi-group
${\bf{G}}$ whose linear operators  preserve the convex set
$K$ in $\mathcal K(X)$.
Zorn's lemma gives a minimal 
closed and convex subset $K_*$ of $K$ which again is ${\bf{G}}$-invariant.
Kakutani's theorem follows if $K_*$ is a singleton set.
To prove  this we  argue by contradiction.
For  $K_*$ is not a singleton set then
\[
K_*-K_*=\{p-q\colon p,q\in K_*\}
\] 
contains a non-zero vector
and we find  
a convex open neighborhood $V$ of the origin such that
\[
(K_*-K_*)\setminus\overline{V}\neq\emptyset\tag{i}
\]
Since
${\bf{G}}$ is equicontinuous on $K$ and hence also on $K_*$ there
exists an open convex neighborhood $U$ of the origin such that
whenever $k_1,k_2$ is a pair in $K_*$
with $k_1-k_2\in U$, then  the  orbit
\[
{\bf{G}}(k_1-k_2)\subset V\tag{ii}
\]
Let
$U^*$ be the convex hull
of  ${\bf{G}}(U)$.
Since the ${\bf{G}}$-maps are linear, the set 
$U^*$ is ${\bf{G}}$-invariant and  continuity gives  the equality
\[
{\bf{G}}(\overline{U^*})=\overline{U^*}\tag{iii}
\]
We find the unique positive number $\delta$ such that
the following hold for every $\epsilon>0$:
\[
(K_*-K_*)\subset (1+\epsilon)\cdot \delta\cdot\overline{U^*}\neq\emptyset\quad
\&\quad
(K_*-K_*)\setminus (1-\epsilon)\cdot \delta\cdot\overline{U^*}\neq\emptyset\tag{iv}
\]
Next,  $\{k+\frac{\delta}{2}\cdot U\colon\, k\in K_*\}$ 
is an open covering of the compact set $K_*$ and
Heine-Borel's Lemma gives 
 a finite set 
$k_1,\ldots,k_n$ in $K_*$ such that
\[
K_*\subset\ \bigcup\, (k_\nu+\frac{\delta}{2}\cdot U^*)\tag{v}
\]
Put
\[
K_{**}= K_*\cap\, \bigcap_{k\in K_*}
(k+(1-1/4n)\delta\cdot \overline{U}^*)\tag{vi}
\]
Since
 $\overline{U}^*$ is 
${\bf{G}}$-invariant and the intersection above is taken over all $k$ in the
invariant  set $K_*$, we see that 
$K_{**}$ is  a closed convex  and ${\bf{G}}$-invariant set.
The requested contradiction follows if we prove that
$K_{**}$ is non-empty
and
strictly contained in $K_*$.
To get the  strict inclusion   we take some
$0< \epsilon<1/4n$. Then   (iv)  gives
a pair $k_1,k_2$ in $K_*$ such that
$k_1-k_2$ does not belong to
$(1-\epsilon) \delta\cdot\overline{U^*}$.
At the same time the eventual inclusion $k_1\in K_{**}$ would entail that
\[
k_1\in (k_2+(1-1/4n)\delta\cdot \overline{U}^*)
\implies k_1-k_2\in  (1-1/4n)\delta\cdot \overline{U}^*\tag{v}
\]
But this cannot hold since   $1-1/4n<1-\epsilon$
and hence $k_1\in K_*\setminus K_{**}$ which proves the requested strict inclusion.
The proof of Kakutani's theorem is therefore finished if we have shown that
\[
K_{**}\neq \emptyset\tag{vi}
\]
To see this
we take an arbitrary $k\in K_*$.
From (v) we find some $1\leq \nu\leq n$ such that
\[
k_\nu-k\in \frac{\delta}{2}\cdot U^*\tag{vii}
\]
Without loss of generality we can assume that $\nu=1$
and get  a vector $u\in U^*$ such that
\[
k_1= k+\frac{\delta}{2}\cdot u\tag {viii}
\]
It follows that
\[
\frac{k_1+\ldots+k_n}{n}=k+\frac{\delta}{2n}\cdot u+
\sum_{i=2}^{i=n}\, \frac{1}{n}(k_i-k)\tag {ix}
\]
Next, for  each $\epsilon>0$ the left hand inclusion in (iv) and the 
convexity of $U^*$ give
\[
\sum_{i=2}^{i=n}\, \frac{1}{n}(k_i-k)\subset
\frac{n-1}{n}(1+\epsilon)\cdot \delta \cdot U^*\tag{x}
\]
It follows   that
\[
\frac{\delta}{2n}\cdot u+
\sum_{i=2}^{i=n}\, \frac{1}{n}(k_i-k)\in
(\frac{\delta}{2n}+ \frac{n-1}{n}(1+\epsilon)\delta )\cdot U^*\tag{xi}
\]
Above we can choose $\epsilon $ so small that
\[
\frac{n-1}{n}(1+\epsilon)+\frac{1}{2n})<1-1/4n
\]
and then we see that the vector
\[
p=
\frac{k_1+\ldots+k_n}{n}\in k+(1-1/4n)\delta\cdot \overline{U}^*
\]
Above $k\in K_*$ was arbitrary so by (tvi)
we get  the  inclusion
$p\in K_{**}$ and hence (vi) holds which finishes the proof.






























 




















\newpage

\noindent
\centerline {\bf{¤ 10. Semi-groups and infinitesmal generators.}}
\bigskip


\noindent
We shall expose 
a result due to Hille, Phillips and Yosida.
Let $X$ be a Banach space.
A family of bounded operators $\{T_t\}$ indexed by non-negative real numbers
is a semi-group if $T_0=E$ is the identity and
\[
T_{t+s}= T_s\circ T_t
\]
for all pairs of non-negative real numbers. In particular the $T$-operators commute.
The semi-group is said to be \emph{strongly continuous}
if the vector-valued functions
\[ 
x\mapsto T_t(x)
\] 
are continuous with respect to the norm in $X$ for each
$x\in X$.
\medskip

\noindent
{\bf{1. Proposition.}}
\emph{Let $\{T_t\}$ be a strongly continuous semi-group
and set}
\[
\omega=\log| ||T_1||
\]
\emph{Then
the operator norms satisfy}
\[
||T_t||\leq e^{\omega t}\quad\colon t\geq 0
\]
\medskip

\noindent
{\bf{Exercise.}} Prove this using calculus applied to sub-multiplicative functions.
\medskip

\noindent
With $\omega$  as above
we consider the open half-plane
\[
U= \{\mathfrak{Re}(\lambda)>\omega \}
\]
Let  $\lambda\in  U$
and $x$ is a vector in $X$.
The Borel-Stieltjes  construction of
integrals with values in a Banach space gives 
the $X$-valued integral
\[
\int_0^\infty\, e^{-\lambda t}\cdot T_t(x)\, dt\tag{1.1}
\]
whose value is   denoted by
$\mathcal T(\lambda)(x)$.
It is clear that
\[ 
x\mapsto \mathcal T(\lambda)(x)
\] 
is linear and
the triangle inequality gives
\[
||\mathcal T(\lambda)(x)||\leq 
\int_0^\infty\, e^{-\mathfrak{Re}\lambda t} \cdot e^{\omega t}\, dt
\cdot ||x||=\frac{1}{\mathfrak{Re}\,\lambda -\omega}\cdot ||x||\tag{1.2}
\]

\medskip
\noindent
{\bf{2. Infinitesmal generators.}}
Let $\{T_t\}$ be a a strongly continuous semi-group.
We are going to prove
that there exists a densely defined and closed operator which is 
called its infinitesmal generator which is 
related to the semi-group as follows:
\medskip

\noindent
{\bf{2.1 Theorem.}}
\emph{There exists a dense subspace $\mathcal D$ in $X$ such that}
\[
\lim_{h\to 0}\, \frac{T_h(x)-x}{h}\tag{*}
\] 
\emph{exists for each $x\in\mathcal D$.
Moroever, if $A(x)$ is the limit value in (*) 
then $A$ is a densely defined operator
and}
\[
\sigma(A\subset \{\mathfrak{Re}\,\lambda\leq\omega\}\tag{**}
\]
\emph{and in the open half-space $U$ one has the equality}
\[
R_A(\lambda)=\mathcal T(\lambda)\tag{***}
\]
\emph{where the left  hand side are Neumann's resolvent operators of $A$.}
\bigskip

\noindent
Theorem 2.1   produces infinitesmal generators of
strongly continuous semi-groups.
It turns out that 
this   class of  densely defined and closed operators
can be described via properties of their spectra and
their  resolvent operators.
Denote by $\mathcal{HPY}$ the family of densely defined
and closed linear operators $A$ with the property that 
$\sigma(A)$ is contained in a half-space
$\{\mathfrak{Re}\,\lambda\leq a\}$Ê
for some real number $a$, and
if $a^*>a$ there exists a constant $M$ such that
\[
||R_A(\lambda)||\leq
M\cdot \frac{1}{\mathfrak{Re}\,\lambda -\omega}\quad\colon 
\mathfrak{Re}\,\lambda\geq a^*\tag{2.2}
\]
\medskip

\noindent
Such $A$-operators are called Hille-Phillips-Yosida operators.
\medskip

\noindent
{\bf{2.2 Theorem.}}
\emph{Each $A\in\mathcal{HPY}$ is the infinitesmal generator of a 
 uniquely determined strongly continuous
 semi-group.}
\medskip

\noindent
{\bf{Remark.}}
Notice that (***) in Theorem 2.1 together with
(1.2) imply that
the infinitesmal generator of a strongly 
continuous semi-group
belongs to
$\mathcal{HPY}$. 
Hence Theorem 2.2    gives 
a 1-1 correspondence between
$\mathcal{HPY}$
and infinitesmal generators  of strongly contionuous semi-groups.
\bigskip

\centerline {\bf{3. The case of bounded operators.}}
\medskip

\noindent
Before we give the proofs of the two theorems above
we shall consider special cases arising via   bounded operators. 
Every  bounded linear operator $B$ on $X$
gives the strongly continuous semi-group
where
\[
 T_t= e^{tB}= 1+\sum_{n=1}^\infty\, \frac{t^n}{n !}\cdot B^n
\]
If $h>0$ 
and $x\in X$ we have
\[
||\lim_{h\to 0}\, \frac{T_h(x)-x}{h}-B(x)||
=||\sum_{n=2}^\infty|\, \frac{h^n}{n !}\cdot B^n(x)||
\]
The triangle inequality entails that the last term is majorised by
\[
\frac{h^2}{2}\cdot e^{||B(x)||}
\]
We conclude that $B$ is the infinitesmal generator of
the semi-group  $\mathcal T= \{T_t\}$.
Next, if $\omega=||B||$
then $\sigma(B)$ is contained in the disc of radius $\omega$ and hence
in the half-plane $U=\{\mathfrak{Re}\,\lambda\leq\omega\}$.
If
$\lambda\in U$
the operator-valued integral 
\[
\int_0^\infty\, e^{-\lambda t}\cdot e^{Bt}\,dt=\frac{1}{\lambda}\cdot E+
\sum_{n=1}^\infty\, \bigl(\int_0^\infty\, e^{-\lambda t}\cdot t^n\,dt\,\bigr)\cdot \frac{B^n}{n !}
\]
Evaluating the integrals the right hand side becomes
\[
\frac{1}{\lambda}\cdot E+
\sum_{n=1}^\infty\, \frac{B^n}{\lambda^{n+1}}
\]
The last sum is equal to the Neumann series for
$R_B(\lambda)$ from ¤ xx. which gives the equation
\[ 
R_B(\lambda)= \mathcal T(\lambda)
\]
Hence Theorem 2.1 is confirmed for 
the special semi-group defined via $B$.
\medskip

\centerline {\bf{4. Uniformly
continuous semi-groups.}}
\medskip

\noindent
Let $B$  as above be a  bounded operator.
The semi-group
$\{T_t=e^{tB}\}$ has the additional property that 
\[
\lim_{t\to 0}| ||T_t-E||=0\tag{4.1}
\]
In fact, the triangle inequality gives
\[
||T_t-E||\leq \sum_{n=1}^\infty\, \frac{t^n}{n !}\cdot ||B||^n
\] 
and it is clear that the right hand side tends to zero as $t\to 0$.
This leads us to give:

\medskip

\noindent
{\bf{4.2 Definition.}}
\emph{A semi-group  $\{T_t\}$ is called uniformly continuous if}
\[
\lim_{t\to 0}| ||T_t-E||=0\tag{4.2.1}
\]
\medskip

\noindent
When (4.2.1 )
holds we find $h_*>0$ such that
\[
||T_t-E||\leq 1/2\quad\colon\, 0\leq t\leq h_*
\]
As explained in ¤ xx this gives
bounded operators 
$\{S_t\,\colon\, 0\leq t\leq h_*\}$
such that
\[ 
T_t=e^{S_t}
\]
This entails that
if $0<h\leq h_*$ then
\[
\frac{T_h-E}{h} =\frac{S_h}{h}+\sum_{n=2}^\infty\,
\frac{h^{n-1}}{n !}\cdot  S_h^n
\]

\medskip

\noindent
{\bf{4.3 Exercise.}}
Verify that the semi-group equations entail that if $N$ is a positive integer and
$h$ so small that $Nh\leq h_*$ one has  the equation
\[
\frac{S_{Nh}}{N}=S_h\tag{4.3.1}
\] 
\medskip

\noindent
Next,  for each small and positive $h<h_*$
we choose the
largest positive integer $N_h$ such that 
\[
\frac{h_*}{N_h+1}< h\leq\frac{h_*}{N_h}
\]
With this choice of $N_h$ we apply (4.3.1) and get
\[
\frac{S_h}{h}=\frac{1}{N_h\cdot h}\cdot S_{N_h\cdot h}
 \]
Passing to the limit as $h\to 0$ the reader can check 
the limit equation
\[
\lim_{h\to 0}\, \frac{S_h}{h}=
h^{-1}_*\cdot S(h_*)
\]
\medskip

\noindent
{\bf{4.4 Exercise.}}
Show from the above that
\[
\lim_{h\to 0}\, \frac{T_h-E}{h} =
h^{-1}_*\cdot S(h_*)
\]
which
means that the infinitesmal generator of
$\{T_t\}$ is given by the bounded operator
$h^{-1}_*\cdot S(h_*)$.
\medskip

\noindent
{\bf{4.5 Conclusion.}}
There exists a 1-1 correspondence between uniformly continuous 
semi-groups and bounded linear operators on $X$.
\bigskip



\centerline{\bf{5. Proof of the main theorems.}}
\bigskip

\noindent
First we prove Theorem 2.1. 
If $x\in X$ and $\delta>0$ we put
\[
x_\delta=\int_0^\delta\, T_t(x)\, dt
\]
For every  $h>0$ the semi-group equation gives
\[
\frac{T_h(x_\delta)-x_\delta}{h}=
\frac{1}{h}\cdot \int_\delta^{\delta+h}\, T_t(x)\, dt
\] 
The strong continuity entails that 
the limit in the right hand side exists as $h\to 0$ and gives a vector
$T_\delta(x)$. Hence the space $\mathcal D$ contains $x_\delta$.
The continuity of $t\mapsto T_t(x)$ at $t=0$ implies that 
$||x_\delta-x||\to 0$ which  proves that
$\mathcal D$ is dense and  the construction of the infinitesmal generator
$A$ gives for every $\delta>0$:
\[
A(x_\delta)= T_\delta(x)\tag{5.1}
\]
\medskip


\noindent
Next, consider some vector  $x\in\mathcal D(A)$. 
Now  there exists the integral which defines
$\mathcal T(\lambda)(Ax)$ when $\lambda$ belongs to the half-plane $U$.
If $\lambda$ is real  and $h>0$ a variable substitution
gives
\[
\mathcal T(\lambda)(T_h(x))=
\int_0^\infty\, e^{-\lambda t}\cdot T_{t+h}(x)\, dt=
e^{\lambda h}\cdot 
\int_h^\infty e^{-\lambda s}T_s(x)\, ds
\]
It follows that

\[
\mathcal T(\lambda)(\frac{T_h(x))-x}{h})
=
\frac{e^{\lambda h}-1}{h}\cdot 
\int_h^\infty e^{-\lambda s}T_s(x)\, ds-
\frac{1}{h}\cdot 
\int_0^h e^{-\lambda s}T_s(x)\, ds
\]
Passing to the limit as $h\to 0$ the reader can check that
the right hand side becomes
\[
\lambda\cdot\mathcal T(\lambda)(x)-x
\]
So with $x\in\mathcal D(A)$ we have the equation
\[
\mathcal T(\lambda)(A(x))=
\lambda\cdot\mathcal T(\lambda)(x)-x
\]
which can be written
as
\[
\mathcal T(\lambda)( \lambda\cdot E-A)(x)=x
\]
\medskip

\noindent
{\bf{Exercise.}}
Conclude from the above that
\[ 
\mathcal T(\lambda)= R_A(\lambda)
\]
and deduce Theorem 2.1.





\medskip

\centerline{\bf{5.2 proof of Theorem 2.2}}

\medskip

\noindent
Let $A$ belong to $\mathcal{HPY}$. So here  
$\sigma(A)$ is contained in 
$\{\mathfrak{Re}(\lambda)\leq a\}$ for some real number $a$, and
when
$\lambda$ varies  in the open half-plane $U=\{\mathfrak{Re}(\lambda)\leq a\}$
there exist the resolvents $R(\lambda)$ where the subscript $A$ is deleted while 
we consider the  operator $A$.
By assumption there
exists a constant $K$ and some $a^*\geq a$ such that
\[
 ||R(\lambda)||\leq \frac{K}{\lambda}\tag{5.2.0}
\] 
when $\mathfrak{Re}(\lambda\geq a^*$.
\medskip

\noindent
{\bf{The operators
$B_\lambda$.}}
For each  $\lambda\in U$ we set
\[ 
B_\lambda=
\lambda^2\cdot R(\lambda)-\lambda\cdot E\tag{ii}
\]
Notice  that (5.2.0) gives
\[
||B_\lambda||\leq (K+1)|\lambda|\tag{iv}
\]
Consider a vector $x\in\mathcal D(A)$.
Now
\[
B_\lambda(x)=
\lambda\cdot(\lambda R(\lambda)(x)-x)=
\lambda \cdot R(\lambda)(Ax)
\]
We have also
\[
\lambda \cdot R(\lambda)(Ax)-R(\lambda(A(x))=A(x)
\]
Hence
\[
B_\lambda(x)-A(x)=R(\lambda)(A(x))
\]
Hence (5.2.0) gives
\[
||B_\lambda(x)-A(x)||\leq \frac{K}{\lambda}\cdot ||A(x)||
\]
Hence we have  the limit
formula
\[ 
\lim_{\lambda \to \infty}\,||B_\lambda(x)-A(x)||=0
\quad\colon x\in\mathcal D(A)
\]








\medskip


\noindent
{\bf{The semi-groups
$\mathcal S_\lambda=\{ e^{tB_\lambda}\,\colon\,  t\geq 0\}$.}}
To each $t\geq 0$ and $\lambda\in U$
we set
\[
S_\lambda(t)=e^{tB_\lambda}=E+
\sum_{n=1}^\infty\,
 \frac{t^n}{n !}\cdot B_\lambda^n\tag{5.2.1}
\]
By (iv) the series converges and
with $t$ fixed
termwise differentiation with respect to $\lambda$ gives
\[
\frac{d}{d\lambda}(S_\lambda(t))=t\cdot \frac{d}{d\lambda}(B_\lambda)\cdot S_t(\lambda)
=-t\cdot S_\lambda(t)+t\cdot(\lambda\cdot R(\lambda)^2-R(\lambda))\cdot S_\lambda(t)
\]


\noindent
Keeping $t$ fixed  we get after an integration
\[
S_\mu(t)-S_\lambda(t)=
t\cdot \int_\lambda^\mu\, (\xi\cdot R(\xi)^2-R(\xi))
S_\xi(t)\, ds
\quad\colon \mu>\lambda\geq a^*\tag{5.2.2}
\]
\medskip

\noindent
Next, we notice that (5.2.0) gives
\[
\lim_{\xi\to\infty}\, ||(\xi\cdot R(\xi)^2-R(\xi)||=0\tag{5.2.3}
\]
Together with  the general differential inequality from (xx) we
conclude that if $t$ stays in a bounded interval $[0,T)$
and  $\epsilon>0$, then  there exists some
large $\xi^*$ such that for every $0\leq t \leq T$
the operator norms satisfy
\[
||S_\mu(t)-S_\lambda(t)||<\epsilon\quad\colon \mu\geq \lambda\geq \xi^*\tag{5.2.4}
\] 
\medskip


\noindent
{\bf{5.2.5 The semi-group $\{S(t)\}$.}}
Since the  bounded operators on $X$ is 
a Banach space, it follows from the above
that each $t$ gives a bounded operator
$S(t)$ given by 
\[ 
\lim_{\lambda\to +\infty}\, S_\lambda(t)= S(t)
\]
where the limit is taken in the operator norm and
the convergence holds
uniformly  when $t$ stays in a bounded interval.
Since $t\mapsto S_\lambda(t)$ is a semi-group for each large
$\lambda$, the same holds for the family $\{S(t)\}$. Moreover, the
convergence properties entail that the semi-group
$\{S(t)\}$ 
is strongly continuous.
\medskip
Neumann's differential equation from (¤ 0.x) gives
\[
\frac{d}{d\lambda}(B_\lambda)=R(\lambda)-E-\lambda\cdot R(\lambda)^2\tag{iii}
\]


\noindent
{\bf{The infinitesmal generator of $\{S(t)\}$.}}
Returning to the series (5.2.1) it is clear that 
\[
\frac{d}{dt}(S_\lambda(t)=S_\lambda(t)\cdot B_\lambda\tag{5.2.6}
\] 
An integration and the equality 
$S_\lambda(0)= E$ give for every $t>0$ and each vector $x\in X$:
\[
S_\lambda(t)(x)-x=\int_0^t\, S_\lambda(\xi)\circ B_\lambda(\xi)(x)\, d\xi\tag{5.2.7}
\]
\medskip




\noindent

\noindent
When $x\in\mathcal D(A)$ we have the limit formula (xx) and together with
the limit which produces the semi-group $\{S(t)\}$ we conclude that
\[
S(t)(x)-x=\int_0^t\, S(\xi)\circ A(x)\, d\xi\quad\colon x\in\mathcal D(A)
\]
We can take a limit as $t\to 0$
where the strong continuity of 
the semi-group $\{S(t)\}$ applies to
vectors $A(x)\,\colon x\in\mathcal D(A)\}$.
Hence 
\[
\lim_{t\to 0}\,
\frac{S(t)(x)-x}{t}=A(x)\quad\colon x\in\mathcal D(A)
 \]
 \medskip
 
\noindent
 So if $\widehat{A}$ is the infinitesmal generator of the semi-group
 $\{S(t)\}$ then its graph contains that of $A$, i.e.
 $\widehat{A}$ is an extension of 
 the densely defined and closed operator $A$.
However, we have equality because $\widehat{A}$ being  an infinitesmal generator of a 
strongly continuous semi-group
has its spectrum confined to a half-space
$\{\mathfrak{Re}(\lambda)\leq b\}$
for some real number $b$, i.e. here we used Theorem 2.1.
In particular 
there exist points outside the union of $\sigma(A)$ and $\sigma(\widehat{A})$
and 
then the equality
$A=\widehat{A}$ 
follows from the general result in ¤ xx.
Hence  $A$ is an infinitesmal generator of a semi-group
which
finishes the proof of Theorem 2.2.



 








\centerline{\bf ¤ 11. Commutative Banch algebras}
\bigskip




\noindent
Let $B$ be
a complex Banach space 
equipped with 
a commutative product whose norm
satisfies the multiplicative inequality
\[ 
||xy||\leq ||x||\cdot ||y||\quad\,\colon\, x,y\in B\tag{*}
\]
We  also assume that $B$ has a multiplicative unit element $e$
where  
$ex=xe$ hold for all $x\in B$ and   $||e||=1$. 
When this hold we refer to $B$ as a commutative Banach algebra with 
a multiplicative unit.
\medskip


\noindent
{\bf{Neumann series.}}
A non-zero element  $x$ in $B$ gives a bounded linear operator
$T(x)$ on the underlying Banach space defined by
\[
y\mapsto x\cdot y
\]
i.e. we simply employ the multiplication on $B$.
Now we  apply Carl Neumann's general
theory about resolvent operators
from ¤ xx.
To begin with we have seen that 
$T(x)$ has a non-empty compact spectrum
denoted by $\sigma(x)$
and in the open complement we put 
\[
R(\lambda)= (\lambda\cdot e-x)^{-1}
\]
Notice that the norm of the linear operstor $T(x)$ is equal to the norm of the
$B$-vector $x$.
So by the general result in ¤ xx applied with $T(x)$
the exterior Neumann series expansion  
\[
R(\lambda)=\frac{e}{\lambda}+
\sum_{n=1}^\infty\ \frac{x^n}{\lambda^{n+1}}\quad\colon\, |\lambda|>||x||
\]
converges and gives an analytic function of the complex parameter
$\lambda$ when 
\[
 |\lambda|>||x||
\]
Now there exists a unique largest
$r_*\geq 0$ such thst
$R(\lambda)$ extends to an analytic $B$-valued function in
the exterior disc $\{|\lambda|>r_*\}$.
If $r>r_*$ and $n$ a positive integer, Cauchy's residie calculus gives 
\[
x^n= \frac{1}{2\pi i}\int_{|\zeta|=r}\, \zeta^n\cdot R(\zeta)\, d\zeta
\]
Here
\[
\max_{\theta}\, ||R(re^{i\theta}||=M<\infty
\]
for some constant $M$. The triangle inequality entails that
\[
||x^n||\leq M\cdot r^n\tag{i}
\]
At this stage
we shall need the following:
\medskip

\noindent
{\bf{1. Theorem.}}
\emph{For every $x\in B$ there exists the limit}
\[
\lim_{n\to \infty}\, ||x^n||^{\frac{1}{n}}\tag{1.1}
\]
\medskip

\noindent
This follows from a general fact about sub-multiplicative sewuences.
See ¤ xxx.
Let $\rho(x)$ denote the oimit in (1.1). 
If $r>r_*$ we take roots in (i) and 
obtain
\[
||x^n||^{\frac{1}{n}}\leq M^{\frac{1}{n}}\cdot r\tag{ii}
\]
Since the $n$:th roots of $M$ converge to one
a passage to thr limit gives
\[
\rho(x)\leq r
\]
Above $r>r_*$ was arbitrsry and hence we  have proved the
inequality
\[
\rho(x)\leq r_*\tag{*}
\]
The opposite inequality  in (**) is clear. For
if $r>\rho(x)$ we find a large positive integer $n$ such that
\[
n\geq N\implies ||x^n||\leq r^n
\]
and then it is obvious that the exterior Neumann series above  converges when
$|\lambda|>r$.
Since tihs hold for every $r>\rho(x)$ we conclude that
(*) is an equality and then the  Neumann calculus from ¤ xx gives:

\medskip

\noindent
{\bf{2. The spectral radius formula.}}
\emph{For every $x\in X$ 
one has the equality}
\[
\rho(x)= \max\{|\lambda|\,\colon\,\lambda\in \sigma(x)\}\tag{2.1}
\]
\medskip

\noindent
{\bf{3. Multiplicative functionals.}}
A  ${\bf{C}}$-linear form $\lambda$ on $B$
is  multiplicative if:
\[
\lambda(xy)=\lambda(x)\cdot \lambda(y)
\quad\text{for all pairs}\quad x,y\in B\tag{3.1}
\]
When  $\lambda$ satisfies (3.1) and is not identically zero it is clear that
$\lambda(e)=1$.

\bigskip


\noindent
{\bf{3.2  Theorem.}}
\emph{Every multiplicative functional $\lambda$
on $B$ is automatically continuous, i.e.
an element in the normed dual space $B^*$ and its norm is equal to one.}
\medskip

\noindent
\emph{Proof}.
Ignoring the topology we use that
${\bf{C}}$ is a field and conclude that
the
$\lambda$-kernel is a \emph{maximal ideal} in the commutative
${\bf{C}}$-algebra $B$
which we denote by $\mathfrak{m}$.
When  $x\in B$ has norm $<1$ the  $B$-valued power series
\[
e+\sum_{n=1}^\infty\,x^n
\]
converges and  gives the inverse to $(e-x)$.
Since $\lambda$ is multiplicative with $\lambda(e)=1$
it follows that $\lambda\cdot e-x)\neq 0$,
So if 
$B_0$Êis the open unit ball in $X$ then
\[
\mathfrak{m}=\text{ker}(\lambda)\cap \{e+B_0\}=\emptyset
\]
By the remark  in ¤ xx this implies that
the hyperplane
$\mathfrak{m}$ is closed in the Banach space $B$ and therefore
a continuous linear functional. Hence there exists a constant $C$ such that
\[
|\lambda(x)|\leq C\cdot ||x||\quad\colon x\in X
\]
Finally, since $\lambda$ is multiplicative this entails that
\[
|\lambda(x)|^n\leq C\cdot ||x^n||\quad\colon x\in X
\]
Taking $n$:th rooots and passing to infinity the reader can check that this gives
\[
|\lambda(x)|\leq \rho(x)\leq ||x||
\]

\medskip


\noindent
{\bf{4. The Gelfand transform.}}
Denote by $\mathcal M(B)$ the family of sll multiplicative functionals.
Keeping  an element $x\in B$ fixed we get
the complex-valued function  on $\mathcal M(B)$ defined by:
\[ 
\lambda\mapsto \lambda(x)
\]
The resulting function is denoted by $\widehat x$ 
and  called the Gelfand transform of the $b$-element $x$.
\medskip

\noindent
{\bf{Exercise.}} Apply the specteral radius formuka to show that
\[
\max_{\lambda\in \mathcal M(B)}\, |\widehat{x}(\lambda)|= \rho(x)\tag{4.1}
\]
\medskip

\noindent 
Following a  device by Gelfand
we use that 
$\mathcal M(B)$ is a subset of 
the dual space
$B^*$ which is  equipped with the
weak-star  topology
and we know from ¤ xx that the unit ball $S^*$ in $B^*$ is compact in this topology.
The reader can check that
$\mathcal M(B)$  appears as a weak-star closed subset of $S^*$ and
hence
becomes a compact space where
every Gelfand transform
$\widehat x$ is  a continuous function.
This gives 
an algebra homomorphism
from $B$ into the commutative algebra $C^0(\mathcal M(B))$:
\[ 
x\mapsto \widehat x\tag{*}
\]
called the Gelfand transform.
The inequality in (xx) shows that the map (*) is continuous with  norm
$\leq 1$ where we employ the sup-norm on the Banach space
 $C^0(\mathcal M(B))$.
\bigskip

\noindent
{\bf{5. Semi-simple algebras.}}
The spectral radius formula shows that $\widehat x$ is the zero function if and only if
$\rho(x)=0$. One says that the Banach algebra $B$ is
\emph{semi-simple} if the Gelfand transform in 
(*)  is injective. An equivalent condition is that
\[
0\neq x\implies \rho(x)>0\tag{5.1}
\]
\medskip





\noindent
{\bf{6. Uniform algebras.}}
If $B$ is  semi-simple the Gelfand transform
identifies $B$ with a subalgebra of $C^0(\mathcal M(B))$.
In general
this subalgebra is not closed. The reason is that
there can exist $B$-elements of norm one while
the $\rho$-numbers can be arbitrarily small.
If the equality below holds for every $x\in B$:
\[
||x||=\rho(x)= |\widehat x|_{\mathcal M(B)}\tag{*}
\]
one says that $B$ is a uniform  algebra.
\bigskip

\noindent
{\bf{Remark.}}
Multiplicative functionals
on specific Banach algebras were used  by Norbert Wiener  and Arne Beurling
where
the focus was on 
Banach algebras which arise via the 
Fourier transforms.
Later  Gelfand, Shilov and Raikow established the  abstract theory which 
has the merit that it applies to  general situations such
as Banach algebras generated by   linear operators on a
normed space. Moreover,  
Shilov  applied results from the theory
of 
analytic functions in several complex
to construct
\emph{joint spectra} of several elements
in a commutative Banach algebra.
See [Ge-Raikov-Shilov] for  a
study of commutative Banach algebras which include
results about joint spectra.
One should also mention  the   work by J. Taylor who used
integral formulas in
several complex variables  to analyze the topology
of Gelfand spaces
which arise  from 
the Banach
algebra of  Riesz measures with total bounded variation on
the real line, and more generally on arbitrary locally compact abelian groups.









\newpage

SPECIAL TOPICS




\newpage






\centerline{\bf{12.2 Positive operators on $C^0(S)$}}

\bigskip

\noindent
Let $S$ be a compact Hausdorff
space and $X$  the Banach space of continuous and
complex-valued functions on $S$.
A linear operator $T$ on $X$ is  positive if
it sends every non-negative and real-valued function $f$ to another  real-valued and
non-negative function.
Denote by $\mathcal F^+$ the family of positive operators
$T$ which satisfy the following: First
\[
\lim_{n\to\infty}\, \frac{1}{n}\cdot x^*(T^nx)=0\tag{1}
\] 
hold for all pairs $x\in X$ and $x^*\in X^*$.
The second condition is that
$\sigma(T)$ is the union of a compact set in a disc
$\{|\lambda|\leq r$ for some $r<1 $, and a 
finite set of points on the unit circle. 
The  final  condition is that
$R_T(\lambda)$
is meromorphic in the exterior disc
$\{|\lambda>r\}$, i.e. it has poles at
the spectral points on the unit circle.








\medskip

\noindent
{\bf{12.2.1. Theorem.}}
\emph{If $T\in\mathcal F^+$ 
then
each spectral value $e^{i\theta}\in \sigma(T)$ is a root of unity.}

\medskip


\noindent
\emph{Proof.}
Frist we prove that $R_T(\lambda)$  has a simple pole at
each  $e^{i\theta}\in \sigma(T)$.
Replacing 
$T$ by  $e^{-i\theta}\cdot T$
it suffices to prove this when
$e^{i\theta}=1$.
If $R_T(\lambda)$ has a pole of order $\geq 2$
at $\lambda=1 $ we know from ¤ XX that there exists $x\in X$ such that
\[ 
Tx\neq  x\quad\text{and}\quad
(E-T)^2\,x=0\tag{i}
\]
This gives  $T^2+x=2Tx$ and by an induction
\[
\frac{1}{n} \cdot T^n x=\frac{1}{n}\cdot x+(E-T)x\quad\colon n=1,2,\ldots\tag{ii}
\]
Condition (1) and (ii) give for each $x^*\in X^*$:
\[ 
0=\lim_{n\to\infty}\, \frac{1}{n}\cdot x^*( T^n x)=\lim_{n\to\infty}\,
x^*(\frac{1}{n}\cdot x+(E-T)x)
\] 
It follows that $x^*(E-T)(x)=0$ and since 
$x^*$ is arbitrary we get   $Tx=x$ which contradicts (i).
Hence
the pole must be simple.
\medskip


\noindent
Next, let  $e^{i\theta}\in\sigma(T) $
which form the above gives a simple pole of 
$R_T$.
By the  result in ¤ xx there exists
some    $f\in C^0(S)$ which is not identically zero and
\[ 
T(f)=e^{i\theta}\cdot f
\]
Multiplying $f$ with a complex scalar we may assume that
its  maximum norm on $S$ is one and there exists a point $s_0\in S$ such that
\[ 
f(s_0)=1
\]
For each $n\geq 1$ we have a linear functional on
$X$ defined by $g\mapsto T^n(g)(s_0)$ which gives a
Riesz measure $\mu_n$ such that
\[
\int_S\, g\cdot d\mu_n=T^n g(s_0)\quad\colon g\in C^0(S)
\]
Since $T^n$ is positive
the integrals in the left hand side are
$\geq 0$ when $g$ are real-valued and non-negative. Hence 
$\{\mu_n\}$ are real-valued and non-negative measures.
For each $n\geq 1 $ we put
\[ 
A_n=\{x\,\colon\, e^{-in\theta}\cdot f(x)\neq 1\}
=
\{x\,\colon\, \mathfrak{Re}(e^{-in\theta}f(x))<1\}\tag{iii}
\]
where the last equality follows since the sup-norm of $f$ is one.
Now
\[
0=f(s_0)- e^{-in\theta}\cdot T^n f(s_0)
=\int_S\,[1-e^{-in\theta}f(s)]\cdot  d\mu_n(s)\tag{iv}
\]
Taking real parts we get
\[
0=\int_S\,[1-\mathfrak{Re}(e^{-in\theta}f(s))]\cdot  d\mu_n(s)\tag{v}
\]
By (iii)  the integrand in (v)
is non-negative and since the whole 
integral is zero it follows that
\[
\mu_n(A_n)= \mu_n(\{\mathfrak{Re}(e^{-in\theta}<1\}=0\tag{vi}
\]
Suppose now that
there exists a pair $n\neq m$ such that
\[
(S\setminus A_n)\cap (S_m\setminus A_m)\neq \emptyset\tag{vii}
\] 
A point $s_*$ in this non-empty intersection
gives
\[
1=e^{in\theta}f(s_*)=e^{im\theta}\cdot f(s_*)\implies
e^{in\theta}=e^{im\theta}
\] 
and hence  $e^{i\theta}$ is a root of unity.
$m-n\neq 0$.
So the proof of Theorem 6.1  is finished if we have established the following

\medskip

\noindent
\emph{Sublemma.}
\emph{The sets $\{S\setminus A_n\}$ cannot be pairwise disjoint.}
\medskip

\noindent
\emph{Proof.}
First,  $f$ has maximum norm
and by the condtrtuction of the $\mu$-measires we have
\[ 
\int_S\, f\cdot d\mu_n=e^{in\theta}\quad\colon\,n=1,2,\ldots
\]
In particular  the total mass $\mu_n(S)\geq 1$ for every $n$.
Next, 
for each $n\geq 2$ we set
\[
\pi_n=\frac{1}{n}\cdot (\mu_1+\ldots+\mu_n)
\]
Since 
$\mu_n(S)\geq 1$  for each $n$ we get 
$\pi_n(S)\geq 1$. Put
\[
\mathcal A=\bigcap\, A_n
\]
By(vi) we have
$\mu_\nu(A_\nu)=0$ for every $\nu\geq 1$ which gives
\[ 
\pi_n(\mathcal A)=0\quad\colon\, n=1,2,\ldots\tag{*}
\]
Next, when
the sets $\{S\setminus A_k\}$ 
are pairwise disjoint one has 
the inclusions
\[
S\setminus A_k\subset A_\nu\quad\forall\,\nu\neq k
\]
Keeping $k$ fixed it follows that
$\pi_\nu(S\setminus A_k)=0$ for every $\nu\geq 0$.
So when $n$ is large while $k$ is kept fixed we obtain
\[ 
\pi_n(S\setminus A_k))= \frac{1}{n}\cdot \mu_k(S\setminus A_k))\implies
\lim_{n\to\infty}\, \pi_n(S\setminus A_k))=0
\quad\colon k=1,2,\ldots\tag{**}
\]
At this stage we use  that 
$R_T(\lambda)$ in particular has  at most a simple pole at $\lambda=1$.
So with  $\epsilon>0$
the Neumann series expansion gives
\[
E+\sum_{k=1}^\infty\,
\frac {T^k}{(1+\epsilon)^k}=
R_T(1+\epsilon))
=\frac{1}{\epsilon} \cdot Q+W(1+\epsilon))
\]
where $W(\lambda)$ is an operator-valued analytic function
in an open disc centered at $\lambda=1$ while $Q$ is a bounded
linear operator on $C^0(S)$.
Keeping $\epsilon>0$ fixed we apply both sides to the identity function
$1_S$ on $S$ and the construction of
the measures $\{\mu_n\}$ gives
\[
1+
\sum_{k=1}^\infty\,
\frac {\mu_k(S)}{(1+\epsilon)^k}=\frac{1}{\epsilon} \cdot Q(1_S)(s_0)+
W(1+\epsilon))(1_S)(s_0)
\]
If $n\geq 2$ is an integer and $\epsilon=\frac{1}{n}$
one gets the inequality
\[
\sum_{k=1}^{k=n}\,
\frac {\mu_k(S)}{(1+\frac{1}{n})^k}\leq
n\cdot |Q(1_S)(s_0)|+|W(1+1/n))(1_S)(s_0)|\leq
n\dot ||Q||+ ||W(1+1/n)||\implies
\]
\[
\frac{1}{n}\cdot\sum_{k=1}^{k=n}\,\mu_k(S)\leq
(1+\frac{1}{n})^n\cdot (||Q||+\frac{ ||W(1+1/n)||}{n}
\]
Since
Neper's constant $e\geq (1+\frac{1}{n})^n$ for every $n$
we find
a constant $C$ which is
independent of $n$ such that
\[
\frac{1}{n}\cdot\sum_{k=1}^{k=n}\,\mu_k(S)\leq C\tag{***}
\]
It is clear that (***) entails that
\[
\liminf_{n\to\infty}\mu_n(S)<\infty
\]
So by weak-star compacntness  there exists a subsequence
$\{\mu_{n_k}\}$
which converges weakly to a limit measure $\mu_*$.
For this $\sigma$-additive measure the limit formula in (**) above entails that
\[ 
\mu_*(S\setminus A_k)=0\quad\colon\, k=1,2,\ldots\tag{i}
\]
Moreover, by (*) we also have
\[
\mu_*(\mathcal A)=0\tag{ii}
\]
Now
$S= \mathcal A\cup\, A_k$ so (i-ii) give:
\[ 
\mu_*(S)=0
\]
But this is impossible for at the same time
we have already seen that
$\pi_n(S)\geq 1$ for each $n$ and hence  $\mu_*(S)\geq 1$.



\newpage


\centerline{\bf{A result about compact pertubations.}}


\bigskip



\noindent 
Let $X$ be a complex Banch space
and
denote by $\mathcal F(X)$
the family of bounded liner operators  $T$ on $X$  
such that
\[ 
\lim_{n\to\infty}\, \frac{1}{n}\cdot x^*(T^nx)=0\tag{*}
\] 
hold for all pairs $x\in X$ and $x^*\in X^*$.
\medskip


\noindent
{\bf{1. Exercise.}} Apply the Banach-Steinhaus theorem to show that
if $T\in\mathcal F(X)$ then
there exists a constant $M$ such that the operator norms satisfy
\[ 
||T^n||\leq M\cdot n\quad\colon\, n=1,2,\ldots
\]


\noindent
Since the $n$:th root of $M\cdot n$ tends to one as $n\to+\infty$, 
the spectral radius formula entails that
the spectrum $\sigma(T)$ is contained in the closed unit disc
of the complex $\lambda$-plane.

\medskip



\noindent{\bf{2. The class $\mathcal F_*$}}.
It consists of those $T$ in $\mathcal F(X)$
for which there exists
some $\alpha<1$ such that
$R_T(\lambda)$ extends to a meromorphic function in
the exterior disc
$\{|\lambda|>\alpha\}$.
Since $\sigma(T)\subset
\{|\lambda|\leq 1\}$
it follows that when
$T\in\mathcal F_*$ then
the set of points in $\sigma(T)$ which belongs to the unit circle
in the complex $\lambda$-plane is empty or finite and if necessary we can
enlarge $\alpha<1$ so that 
\[ 
\sigma(T)\cap \{\alpha<|\lambda|<1\}= \emptyset\tag{2.1}
\]

\medskip

\noindent
{\bf{2.2. Proposition.}}
\emph{If $T\in \mathcal F_*$ andÊ$e^{i\theta}\in \sigma(T)$
for some $\theta$, then Neumann's resolvent
$R_T(\lambda)$ 
has a simple pole at $e^{i\theta}$.}
 \medskip

\noindent
\emph{Proof.}
Replacing
$T$ by  $e^{-i\theta}\cdot T$
it suffices to prove the result when
$e^{i\theta}=1$.
If $R_T(\lambda)$ has a pole of order $\geq 2$
at $\lambda=1 $ we know from ¤ XX that there exists $x\in X$ such that
\[ 
Tx\neq  x\quad\text{and}\quad
(E-T)^2\,x=0\tag{i}
\]
The last equation means that $T^2+x=2Tx$ and an induction
over $n$ gives
\[
\frac{1}{n} \cdot T^n x=\frac{1}{n}\cdot x+(E-T)x\tag{ii}
\]
Since $T\in\mathcal F$ we have
\[ 
\lim_{n\to\infty}\, \frac{1}{n}\cdot x^*( T^n x)=0
\quad\colon\, \forall\\, x^*\in X^*\tag{iii}
\] 
Then (ii) entails that $x^*(E-T)(x)=0$. Since
$x^*$ is arbitrary we get  $Tx=x$ which contradicts (i) and hence
the pole is simple.
\bigskip

\noindent
{\bf{2.3  Theorem.}}
\emph{Let $T\in \mathcal F(X)$ be such that   there exists a compact
operator $K$ where 
$||T+K||<1$. Then $T\in \mathcal F_*$ and
for every $e^{i\theta}\in\sigma(T)$
the eigenspace
$E_T(\theta)= \{ x\in X\,\colon\, Tx= e^{i\theta} x\}$ is finite dimensional.}

\medskip

\noindent
\emph{Proof.}
Put $S=T+K$. 
Outside $\sigma(S)$ we get
\[
R_S(\lambda)(\lambda\cdot E-T)=
E+R_S(\lambda)\cdot K\tag{i}
\]
The Neumann series for large absolute values
$|\lambda|$
applied to $R_S(\lambda)$ gives some $\rho>0$ and
\[
( E+R_S(\lambda)\cdot K)^{-1}= E+R_S(\lambda)\cdot K\dot
( E+R_S(\lambda)\cdot K)^{-1}\quad\colon\,|\lambda|>\rho\tag{ii}
\]

\noindent
When
$|\lambda|$ is large
we notice that
(i) gives
\[
R_T(\lambda)= R_S(\lambda)\cdot  ( E+R_S(\lambda)\cdot K)^{-1}\tag{ii}
\]
At the same time we have the algebraic equality
\[
( E+R_S(\lambda)\cdot K)^{-1}= E+R_S(\lambda)\cdot K\dot
( E+R_S(\lambda)\cdot K)^{-1}{iii}
\]
when $|\lambda|$ is large.
Together with (ii) we obtain
\[
R_T(\lambda)=R_S(\lambda)+ 
R_S(\lambda)\cdot 
( E+R_S(\lambda)\cdot K)^{-1}\cdot R_S(\lambda)\tag{iv}
\]
Set $\alpha=||S||$ which by assumption is $<1$.
Now
$R_S(\lambda)$ is analytic in the exterior disc
$\{\lambda|>\alpha\}$ so in this exterior disc
$R_\lambda(T)$ differs from  the analytic function $R_\lambda(S)$ by
\[
\lambda\mapsto R_S(\lambda)\cdot 
( E+R_S(\lambda)\cdot K)^{-1}\cdot R_S(\lambda)\tag{v}
\]
Here $K$ is a compact operator so 
the
result in ¤ XX entails that (v) extends to
a meromorphic function  in $\{|\lambda|>\alpha\}$.
There remains to prove that
eigenspaces at spectral points on the unit circle are finite dimensional.
Let $e^{i\theta}\in\sigma(T)$ which by  Proposition 2.2  is a simple pole
and hence gives 
a Laurent series expansion
\[
R_T(e^{i\theta}+z)= \frac{A_{-1}}{z}+ A_0+ A_1z+\ldots
\]
By the general results from ¤¤ there remains to show that 
$A_{-1}$ has finite dimensional range.
To see this we apply (iv) which gives the equation
\[
R_S(e^{i\theta}+z)+
R_S(e^{i\theta}+z)\cdot(E+
R_S(e^{i\theta}+z)\cdot K)^{-1}\cdot R_S(e^{i\theta}+z)
\]
To simplify notations we set $B(z)=R_S(e^{i\theta}+z)$
which is analytic in a neighborhood of $z=0$ since $||S||<1$.
Moreover, the operator $B(0)$ is invertible which give
\[
 \frac{A_{-1}}{z}+ A_0+ A_1z+\ldots=
 B(z)+B(z)(E+B(z)\cdot K)^{-1}B(z)
 \]
Since $B(0)$ is invertible  we also  have a Laurent series 
\[
(E+B(z)\cdot K)^{-1}= \frac{A^*_{-1}}{z}+A_0^*+A_1^*z+\ldots\tag{vi}
\]
and identifying the coefficient of $z^{-1}$ gives
\[
A_{-1}= B(0)A^*_{-1}B(0)\tag{vii}
\]
Next, from (vi) one has

\[
E=(E+B(z)\cdot K)(\frac{A^*_{-1}}{z}+A_0^*+A_1^*z+\ldots)\implies
A^*_{-1}+ B(0)\cdot K\cdot A^*_{-1}=0\tag{viii}
\]
Here $B(0)\cdot K$ is a compact operator and from (viii) and   Fredholm theory 
it follows that $A^*_{-1}$ has a finite dimensional range. Since
$B(0)$ is invertible the same is true for $A_{-1}$ by (vii) above.
This finishes the proof
of 
Theorem 2.3.









\end{document}













\newpage

\centerline{\bf ¤ 10. Hilbert spaces.}
\bigskip

\noindent
{\bf Introduction.}
Euclidian geometry teaches   that if
$A$ is some  invertible $n\times n$-matrix whose elements are real
numbers and $A$ is regarded  as a linear map from
${\bf{R}}^n$ into itself, then the image of the euclidian unit sphere
$S^{n-1}$ is an ellipsoid $\mathcal E_A$. Conversely  if
$\mathcal {E}$ is an ellipsoid   there exists an invertible matrix
$A$ such that $\mathcal{E}=\mathcal{E_A}$.
\medskip

\noindent
{\bf 4.1 The case $n=2$}. 
Let $(x,y)$ be the coordinates in
${\bf{R}}^2$ and  $A$  the linear map
\[ 
(x,y)\mapsto  (x+y,y)\tag{0.1}
\]
To get the image of the unit circle  $x^2+y^2=1$ 
we use polar coordinates and write
$x=\text{cos}\,\phi$ and $y=\text{sin}\,\phi$.
This gives the closed image curve
\[ 
\phi\mapsto (\text{cos}\phi+\text{sin}\phi\,;\,\text{sin}\phi)
\quad\colon|\quad 0\leq\phi\leq 2\pi\tag{i}
\]
It is not obvious  how to  determine the principal axes of
this ellipse. The gateway is to consider the
\emph{symmetric} $2\times 2$-matrix $B=A^*A$.
If $u,v$ is a pair of vectors in ${\bf{R}}^2$ we have
\[
\langle Bu,v\rangle=\langle Au,Av\rangle\tag{ii}
\]
It follows that $\langle Bu,u\rangle>0$ for all $u\neq 0$. By
a wellknown result in elementary geometry it means that the symmetric matrix
$B$ is positive, i.e. the eigenvalues arising from zeros of
the characteristic polynomial $\text{det}(\lambda E_2-B)$
are both positive.
Moreover, the {\emph{spectral theorem} for symmetric matrices
shows that there exists an orthonormal basis in
${\bf{R}}^2$ given by a pair of eigenvectors for $B$ denoted by
$u_*$ and $v_*$. So here

\[ 
B(u_*)=\lambda_1\cdot u_*\quad\colon\quad
B(v_*)=\lambda_2\cdot v_*
\]
Next, since $(u_*,v_*)$ is an orthonormal basis in
${\bf{R}}^2$ points on the unit circle are
of the form
\[
\xi=
\text{cos}\phi\cdot u_*+
\text{sin}\phi\cdot v_*
\]
Then we get
\[
|A(\xi)|^2=
\langle A(\xi).A(\xi)\rangle=\langle B(\xi),\xi)=
\text{cos}^2\phi\cdot \lambda_1+
\text{sin}^2\phi\cdot \lambda_2
\]
From this we see that the ellipse $\mathcal E_A$ has $u_*$ and
$v_*$ as principal axes. It is a circle if and only if
$\lambda_1=\lambda_2$. If $\lambda_1>\lambda_2$
the largest principal axis has length $2\sqrt{\lambda_1}$ 
and the smallest has length $2\sqrt{\lambda_2}$. The reader should
now compute the specific example (*) and find
$\mathcal E_A$. 
\medskip

\noindent
{\bf 4.2 A Historic Remark.}
The fact that $\mathcal E_A$ is an ellipsoid was  wellknown in
the Ancient Greek mathematics when $n=2$ and $n=3$.
 After  general matrices and their determinants were introduced,
the spectral theorem for symmetric matrices was 
established by A. Cauchy in
1810 under the assumption that the eigenvalues are different. Later
Weierstrass found the proof in the general case, and independently Gram
and Weierstrass  found a method to
produce an  
orthonormal basis of eigenvectors for
a given symmetric $n\times n$-matrix $B$. To find an  eigenvector with
largest eigenvalue one studies the extremal problem
\[ 
\max_x\,\langle Bx,x\rangle\quad\colon\quad||x||=1\tag{1}
\]
If a unit vector $x_*$ maximises
(1) then it is an eigenvector, i.e.
\[ 
Bx_*=a_1x_*
\] 
holds for a real number $a$.
In the next stage one takes the orthogonal complement $x_*^\perp$
and proceed to  the restricted extremal problem
where $x$ say in this orthogonal complement which gives  an eigenvector
whose eigenvalue $a_2\leq a_1$. After $n$ steps we obtain an
$n$-tuple of pairwise orthogonal eigenvectors to $B$.
In the orthonormal basis given by this $n$-tuple the linear operator of $B$ is
represented by a diagonal matrix.

\medskip

\noindent
{\bf{Singular values.}}
\emph{Mathematica} has implemented programs which for every
invertible $n\times n$-matrix $A$ determines the
ellipsoid $\mathcal E_A$ numerically. This is presented under the headline
\emph{singular values for matrices}. In general
the $A$-matrix  is not symmetric but  the spectral theorem
is applied to the symmetric matrix $A^*A$ 
which  determines
the ellipsoid $\mathcal E_A$ and whose principal axis
are pairwise disjoint.


\bigskip

\noindent{\bf 4.3 Rotating bodies.}
The spectral theorem in dimension $n=3$ is
best illustrated by regarding a rotating body.
Consider a bounded
3-dimensional body
$K$ in which some distribution of mass is given.
The body is placed i ${\bf{R}}^3$ where
$(x_1,x_2,x_3)$ are the coordinates and the distribution of mass
is expressed by a positive function
$\rho(x,y,z)$ defined in $K$.
The \emph{center of gravity} in $K$ is the point
$(\bar x_1,\bar x_2,\bar x_3)$ where
\[ 
\bar x_\nu=\iiint_K\,x_\nu\cdot \rho(x_1,x_2,x_3)\cdot dx_1dx_2dx_3\tag{i}
\quad\colon\, 1\leq\nu\leq 3
\]
After a translation we may assume that 
the center of mass is the
origin.
Now we imagine that  a rigid bar
which stays on a  line $\ell$ is attached to $K$ with its two endpoints 
$p$ and $q$, i.e. if $\gamma$ is the unit vector
in ${\bf{R}}^3$ which determines the line
then
\[
p= A\cdot\gamma\quad\colon\quad q=-A\cdot\gamma
\]
where $A$ is so large that
$p$ and $q$ are outside $K$.
The mechanical experiment is to rotate
around $\ell$ with some constant
angular velocity $\omega$ while
the two points $p$ and $q$ are kept fixed.
The question arises if such an imposed rotation
of $K$ around $\ell$
implies that  external forces
at $p$ and $q$ are needed to prevent these to points from moving.
It turns out that there exist
so called free axes where no such forces are needed, i.e. for certain directions of
$\ell$ the body rotates nicely around
the axis with constant angular velocity.
The free axes are found from the spectral theorem.
More precisely, one introduces the symmetric 
$3\times 3$-matrix $A$ whose elements are
\[
a_{pq}=
\bar x_\nu=\iiint_K\,x_p\cdot x_q\cdot \rho(x_1,x_2,x_3)\cdot dx_1dx_2dx_3\tag{i}
\]
Using the expression for the centrifugal force
by C. Huyghen's one has the  \emph{Law of Momentum}
which in the present case shows that
the body has a free rotation along the
lines which correspond to eigenvectors of
the symmetric matrix $A$ above.
In view of the historic importance of this example we present the proof of this
in a separate section even though 
some readers may
refer to this as a subject in classical mechanics rather
than linear algebra.
Hence   the spectral theorem becomes evident by
this mechanical experiment, i.e. just as Stokes Theorem 
the spectral theorem  for symmetric matrices
is rather a Law
of Nature than a mathematical discovery.



\bigskip
\centerline {\bf 4.4 Inner product norms}
\medskip

\noindent
Let $A$ be an invertible $n\times n$-matrix.
The ellipsoid $\mathcal{E}_A$ defines a norm on
${\bf{R}}^n$ by the general construction in XX.
This norm has a special property. For if $B=A^*A$
and $x,y$ is a pair of $n$-vectors, then
\[
||x+y||^2=\langle B(x+y),B(x+y)\rangle
=||x||^2+||y||^2+2\cdot B(x,y)\tag{i}
\]
It means that the map
\[ (x,y)\mapsto 
||x+y||^2-||x||^2-||y||^2\tag{ii}
\]
is linear both with respect to $x$ and to $y$, i.e. it is a
bilinear map given by
\[
(x,y)\mapsto 2\cdot B(x,y)\tag{iii}
\]
We leave as an exercise for the reader to prove that if
$K$ is a symmetric convex set in
${\bf{R}}^n$
defining the $\rho_K$-norm as in xx, then this norm
satisfies the bi-linearity (ii) if and only if
$K$ is an ellipsoid and therefore  equal to  $\mathcal{E}_A$
for an invertible $n\times n$-matrix $A$.
Following Hilbert we refer to a norm
defined by some bilinear form $B(x,y)$ as an
\emph{inner product norm.}
The spectral theorem asserts that there exists
an orthonormal basis in ${\bf{R}}^n$ with respect to this norm.
\medskip

\noindent
{\bf 4.5 The complex case.}
Consider a  Hermitian matrix
$A$,  i.e an $n\times n$-matrix with complex elements
satisfying
\[ 
a_{qp}=\bar a_{pq}\quad\colon\quad 1\leq p,q\leq n\tag{*}
\]
Consider the $n$-dimensional complex vector space
${\bf{C}}^n$
with the basis $e_1,\ldots,e_n$.
An inner product is defined by
\[
\langle x,y\rangle=x_1\bar y_1+\ldots+x_n\bar y_n\tag{**}
\]
where 
$x_\bullet=\sum x_\nu\cdot e_\nu$
and
$y_\bullet=\sum y_\nu\cdot e_\nu$
is a pair of complex $n$-vectors.
If $A$ as above is a Hermitian matrix we obtain
\[
\langle Ax,y\rangle=\sum \sum a_{pq}x_q\cdot \bar y_p
\sum \sum \, x_p\cdot \bar a_{qp}\bar y_q=
\langle x,Ay\rangle\tag{***}
\]
\medskip

\noindent
Let us consider the characteristic polynomial
$\text{det}(\lambda\cdot E_n-A)$. If
$\lambda$ is a root there exists a non-zero eigenvector
$x$ such that
$Ax=\lambda\cdot x$. Now (***) entails that
\[
\lambda\cdot ||x||^2=
\langle Ax,x\rangle=
\langle x, Ax\rangle=\bar \lambda\cdot ||x||^2
\]
It follows that $\lambda$ is \emph{real}, i.e. the roots of the
characteristic polynomial of a Hermitian matrix are always
real numbers.
If all  roots are $>0$ one say that
the Hermitiain matrix is \emph{positive}.
\medskip

\noindent
\emph {4.6 Unitary matrices.}
An $n\times n$-matrix $U$ is called unitary if
\[
\langle Ux,Ux\rangle=\langle x,x\rangle
\]
hold for all $x\in{\bf{C}}^n$.
The spectral theorem for Hermitian  matrices asserts that if
$A$ is Hermitian then there exists a unitary
matrix $U$ such that
\[ 
UAU^*=\Lambda
\] 
where $\Lambda$ is a diagonal matrix whose elements are real.




\bigskip

\centerline{\bf  4.7 The passage to infinite dimension.}
\medskip

\noindent
Around 1900 the need for a spectral theorem in infinite dimensions
became  urgent.
In his article \emph{Sur une nouvelle mŽthode pour la resolution
du problme de Dirichlet} from 1900,
Ivar Fredholm extended earlier construction by Volterra and
studied  
systems of linear equations in an infinite number
of variables with certain bounds.
In Fredholm's investiagations one starts
with a sequence of matrices $A_1,A_2,\ldots$ where
$A_n$ is an $n\times n$-matrix and an infinite dimensional vector space
\[ 
V=
{\bf{R}}e_1+
{\bf{R}}e_2+\ldots
\]
To each $N\geq 1$ we get the finite dimensional subspace
$V_N={\bf{R}}e_1+\ldots
{\bf{R}}e_N$.
Now $A_N$ is regarded as a linear operator on $V_N$ and we assume that
the $A$-sequence is matching , i.e. if $M>N$ then
the restriction of $A_M$ to $V_N$ is equal to $A_N$.
This means   that we take  any infinite matrix $A_\infty$ with elements 
$\{a_{ik}\}$ and here $A_N$ is the $N\times N$-matrix
which appears as an upper block with $N^2$-elements
$a_{ik}\,\colon\,1\leq i,k\leq N$.
To each $N$ 
the ellipsoid $\mathcal {E}_N=\mathcal{E}_{A_N}$ on $V_N$ where 
defines a norm.
As $N$ increases the norms are matching
and hence  $V$ is equipped with a norm
which for every $N\geq 1$ restricts to the norm defined by $\mathcal E_N$
on the finite dimensional subspace $V_N$. Notice that
the norm of any vector $\xi\in V$
is finite  since $\xi$ belongs to $V_N$ for some $N$, i.e. by
definition any vector in $V$ is a finite
${\bf{R}}$-linear combination of the basis vectors
$\{e_\nu\}$.
Moreover, the norm on $V$ satisfies the
bilinear rule from (0.3), i.e. on $V\times V$
there exists a bilinear form $B$ such that
\[ 
||x+y||^2-||x||^2-||y||^2=2B(x,y)\quad\colon\quad
x,y\in V\tag{*}
\]
\medskip

\noindent
{\bf Remark.}
Inequalities for determinants
due to Hadamard play an important role in
Fredholm's work and since the Hadamard inequalities are used
in many other situations we 
announce some of his results, leaving proofs as an exercise or
consult the literature where an  excellent source is the introduction to integral equations by
the former professor at Harvard University
Maxime Bochner [Cambridge University Press: 1914):
\medskip

\noindent
{\bf 4.8 Two inequalities.} Let
$n\geq 2$ and $A=\{a_{ij}\}$  some
$n\times n$-matrix whose elements are real numbers.
Show that if
\[ a_{i1}^2+\ldots+a_{in}^2=1\quad\colon\quad 1\leq i\leq n
\]
then the determinant of $A$ has absolute value $\leq 1$.
Next, assume that there is a constant $M$ such that the absolute values
$|a_{ij|}|\leq M$ 
hold for all pairs $i,j$. Show that this gives
\[ 
\bigl|\text{det}(A)\bigr |\leq \sqrt{n^n}\cdot M^n
\]
 



\medskip

\noindent
{\bf 4.9 The Hilbert space $\mathcal{H}_V$}.
This is the completition of the normed space $V$.
That is, exactly as when the field of rational numbers is
completed to the real number system one regards Cauchy sequences for the norm
of vectors in $V$ and in this way we get  a  normed
vector space denoted by $\mathcal{H}_V$ where the norm topology is complete.
Under this process the bi-linearity is preserved, i.e.
on $\mathcal{H}_V$ there exists  a bilinear form $B_{\mathcal{H}}$ such that
(*) above holds for pairs $x,y\in\mathcal {H}_V$.
Following Hilbert we refer to
$B_{\mathcal{H}}$ as the  \emph{inner product}
attached to the norm.
Having performed this construction starting from any
infinite matrix $A_\infty$ it is tempting to make a further abstraction. 
This is precisely
what Hilbert did, i.e. he ignored the "source" of a matrix $A_\infty$
and defined a complete normed vector space over
${\bf{R}}$ to be  a real Hilbert space if the there exists a bilinear form
$B$ on $V\times V$ such that (*) holds. 
\medskip

\noindent
{\bf {Remark.}}
If $V$ is a "abstract"  Hilbert space the restriction of the norm to
any finite dimensional subspace $W$ is determined by
an ellipsoid and  exactly as in linear algebra  one constructs an orthonormal basis
on $W$.
By the Gram-Schmidt 
construction there exists
an orthonormal sequence $\{e_n\}$ in $V$.
However, in order to be sure that it suffices to take a
\emph{denumerable} orthonormal basis it is necessary and sufficient that
the normed space $V$ is \emph{separable}.
Assuming this  every $v\in V$ has a unique
representation
\[ 
v=\sum\, c_n\cdot e_n\quad\colon\, \sum\, |c_n|^2=||v||^2\tag{i}
\]
\medskip

\noindent
The existence of this orthonormal family  means that every
separable Hilbert space is isomorphic to
the standard space $\ell^2$ whose vectors are infinite sequences
$\{c_n\}$ where the square sum $\sum\, c_n^2<\infty$.
So in order to prove general results about separable Hilbert spaces
it is  sufficient to regard
$\ell^2$. However,  the abstract notion of a Hilbert space
is useful since inner products on 
specific linear spaces
appear in many different situations. 
For example, in complex analysis  an
example occurs when  we regard the space
of analytic functions which are square 
integrable on a domain or
whose boundary values are square integrable.
Here  the inner product
is given in advance but it can be  a highly non-trivial affair to exhibit
an orthonormal basis.

\medskip

\noindent
{\bf 4.10 Linear operators on $\ell^2$.}
A bounded linear operator
$T$ from the complex Hilbert space $\ell^2$ into itself is
described by an infinite matrix
$\{a_{p,q}\}$ whose elements are complex numbers. Namely, 
for each $p\geq 1$ we set
\[ T(e_p)=\sum_{q=1}^\infty\, a_{pq}\cdot e_q\tag{i}
\]
For each fixed $p$ we get
\[
||T(e_p)||^2=\sum_{q=1}^\infty\, |a_{pq}[^2\tag{ii}
\]


\noindent
Next,
let $x=\sum\,\alpha_\nu\cdot e_\nu$
and $y=\sum\,\beta_\nu\cdot e_\nu$ be two vectors in
$\ell^2$. Then we get
\[
||x+y||^2=\sum\, |\alpha_\nu+\beta_\nu|^2\cdot e_\nu
\]
For each $\nu$ we have the pair of complex numbers
$\alpha_\nu,\beta_\nu$ and here
we have the inequality
\[
|\alpha_\nu+\beta_\nu|^2\leq  2\cdot |\alpha_\nu|^2+2\cdot |\beta_\nu|^2
\]
It follows that
\[
||x+y||^2\leq 2\cdot ||x||^2+2\cdot||y||^2\tag{iii}
\]


\noindent
In (iii) equality holds if and only if the
two vectors $x$ and $y$ are linearly dependent, i.e. if there
exists some complex number $\lambda$ such that
$y=\lambda\cdot x$.
Let us now return to the linear operator $T$.
In (ii) we get an expression for
the norm of the $T$-images of the orthonormal basis
vectors. So when $T$ is bounded with  operator norm
$M$ then the sum of the squared absolute values in each row
of the matrix $A=\{a_{p,q}\}$ is $\leq M^2$.
However, this condition along is not sufficient to
guarantee that
$T$ is a bounded linear operator. For example, suppose that
the row vectors in $T$ are all equal to a given
vector in $\ell^2$, i.e. $a_{p,q}=\alpha_q$ hold for all pairs where
$\sum,|\alpha_q|^2=1$.
Then
\[ 
T(e_1+\ldots+e_N)=N\cdot v\quad\colon\quad
v=\sum\,\alpha_q\cdot e_q
\]
The norm in the right hand side is $N$ while the norm
of $e-1+\ldots+e_n$ is $\sqrt{N}$. Since
$N>>\sqrt{N}$ when $N$ increases this shows that
$T$ cannot be bounded. So the condition on
the matrix $A$ in order that
$T$ is bounded is more subtle.
In fact, given a vector $x=\sum\,\alpha_\nu\cdot e_\nu$ as above with
$||x||=1$ we have
\[ 
||T(x)||^2=\sum_{p=1}^\infty\, 
\sum_q\sum_k\, a_{p,q}\cdot\alpha_q\cdot\bar a_{pk}\cdot\bar \alpha_k\tag{*}
\]


\noindent
So we encounter an involved triple sum.
Notice also that for each fixed $p$ we get a \emph{non-negative}
term 
\[ 
\rho_p=
\sum_q\sum_k\, a_{p,q}\cdot\alpha_q\cdot\bar a_{pk}\cdot\bar \alpha_k=
\bigl| \sum_{q=1}^\infty\, a_{pq}\cdot\alpha_q\,\bigr|^2
\]
\medskip

\noindent
{\bf Final remark.}
Thus, the description of the Banach space
$L(\ell^2,\ell^2)$ of all bounded
linear operators on
$\ell^2$ is not easy to grasp. In fact, no
"comprehensible" description exists of this space.






\bigskip

\centerline {\bf 4.11 General  results on Hilbert spaces.}
\medskip

\noindent
Let $\mathcal H$  be  a real Hilbert space.
The construction of the inner product norm entails  that
\[
||x+y||^2+||x-y||^2=
2\cdot ||x||^2+2\cdot ||y||^2\tag{*}
\]
for every pair $x,y$ in $\mathcal H$.
Using this one solves an extremal problem.
For every  closed convex subset $K$ of
$\mathcal H$ and if $\xi\in \mathcal H\setminus K$  there exists a unique
$k_*\in K$ such that
\[
\min_{k\in K}\,||\xi-k||=||\xi-k_*||\tag{**}
\]
To prove (**) 
we let
$\rho$ denote  the minimal distance.
We find a sequence $\{k_n\}$ in $K$ such that
$||\xi-k_n||\to\rho$. Now we show that 
$\{k_n\}$ is a Cauchy sequence. For let 
$\epsilon>0$ which gives some integer  $N_*$ such that
\[
||\xi-k_n||<\rho+\epsilon\quad\colon\quad n\geq N_*\tag{i}
\]
The convexity of $K$ implies that
if $n,m\geq N_*$ then $\frac{k_n+k_m}{2}\in K$. 
Hence 
\[
\rho^2\leq ||\xi-\frac{k_n+k_m}{2}||^2\implies
4\rho^2\leq ||(\xi-k_n)+(\xi-k_m]||^2\tag{ii}
\]
By the identity (*) the right hand side is
\[
2||\xi-k_n||^2+2||\xi-k_m||^2-||k_n-k_m||^2\tag{iii}
\]
It follows from (i-iii) that
\[
||k_n-k_m||^2\leq 4(\rho+\epsilon)^2-4\rho^2=
8\rho\cdot\epsilon+4\epsilon^2
\]
Since $\epsilon$ can be made arbitrary small
$\{k_n\}$ is a Cauchy sequence and hence 
there exists a limit $k_n\to k_*$ where $k_*\in K$
since $K$ is closed.
Finally, the  uniqueness of $k_*$ 
follows from the equality
\[
||\xi-k_1||^2+||\xi-k_2||^2=
2\cdot ||\xi-\frac{k_1+k_2}{2}||^2+\frac{1}{2}\cdot ||k_1-k_2||^2
\]
for every pair $k_1,k_2$ in $K$. In fact, this equality entails that if
$\epsilon>0$ and 
$k_1,k_2$ is a pair such that
\[
||\xi-k_\nu||\leq \rho^2+\epsilon\quad\colon\, \nu=1,2
\]
then we have
\[
||k_1-k_2||^2\leq 4\epsilon
\]
from which the uniquness of $k_*$ follows.

\bigskip

\noindent
{\bf 4.12 The decomposition theorem.}
Let $V$ be a closed subspace of $H$.
Its orthogonal complement is defined by
\[ 
V^\perp=\{x\in H\quad\colon\,\langle x,V\rangle=0\}\tag{i}
\]
It is obvious that $V^\perp$ is a closed subspace of $H$
and that $V\cap V^\perp=0$.
There remains to prove the equality
\[ 
H=V\oplus\, V^\perp\tag{ii}
\]
To see this we take some $\xi\in H\setminus V$. 
Now $V$ is a closed convex set so we find $v_*$ such that
\[ 
\rho=||\xi-v_*||=\min_{v\in V}\,||\xi-v||\tag{iii}
\]
If we prove that $\xi-v_*\in V^\perp$ we get (ii).
To show this we consider  some $\eta\in V$. If
$\epsilon>0$ we have
\[
\rho^2\leq ||\xi-v_*+\epsilon\cdot\eta||^2=
||\xi-v_*||^2+\epsilon^2 \cdot||\eta||^2+
\epsilon\langle \xi-v_*,\eta\rangle
\]
Since $||\xi-v_*||^2=\rho^2$ and $\epsilon>0$ it follows that
\[
\langle \xi-v_*,\eta\rangle+\epsilon \cdot||\eta||^2\geq 0
\]
here $\epsilon$ can be arbitrary small and we conclude that
$\langle \xi-v_*,\eta\rangle\geq 0$. Using 
$-\eta$ instead we get the 
opposed inequality and hence
$\langle \xi-v_*,\eta\rangle=0$ as required.

\bigskip

\noindent
{\bf 4.13 Complex Hilbert spaces.}
On a complex vector space  similar results as above hold
provided that 
we regard convex sets which
are ${\bf{C}}$-invariant. We leave details to the reader
and refer to the literature  for a more detailed account about
general properties on Hilbert spaces.
See for example the text-book [Hal] by P. Halmos - a former student to
J. von Neumann - which in addition to theoretical
results contains
many interesting exercises.






\newpage

\centerline{\bf{4:B. Eigenvalues of matrices.}}

\bigskip

\noindent
Using  the Hermitian inner product on ${\bf{C}}^n$
we study
eigenvalues of an $n\times n$-matrices $A$ with complex elements.
The  spectrum $\sigma(A)$ is the $n$-tuple of roots
$\lambda_1,\ldots,\lambda_n$ of the characteristic polynomial
$P_A(\lambda)=\text{det}(\lambda\cdot E_n-A)$,
where eventual multiple eigenvalues are
repeated.
\medskip


\noindent
{\bf{4:B.1 Polarisation.}}
Let $A$ be an arbitrary $n\times n$-matrix.
Then there exists a unitary matrix
$U$ such that the matrix 
$U^*AU$ is upper triangular. To prove this
we first use the wellknown fact that there exists
a basis
$\xi_1,\ldots,\xi_n$ in ${\bf{C}}^n$
in which $A$ is upper triangular, i.e. 
\[ 
A(\xi_k)= a_{1k}\xi_1+\ldots a_{kk}\xi_k\quad\colon\,,1\leq k\leq n
\]
The \emph{Gram-Schmidt orthogonalisation}
gives
an orthonormal basis $e_1,\ldots,e_n$ where
\[ 
\xi_k=c_{1k}\cdot e_1+\ldots c_{kk}\cdot e_k\quad\text{for each}
\quad 1\leq k\leq n
\]
Let $U$ be  the unitary matrix which sends the standard basis in
${\bf{C}}^n$ to the $\xi$-basis. Now the
reader can  verify that the linear operator 
$U^*AU$ is  represented by an upper triangular matrix in the $\xi$-basis.





\medskip


\noindent
\emph{A theorem by H. Weyl.}
Let $\{\lambda_k\}$ be the spectrum of $A$ where the $\lambda$-sequence is
chosen with non-increasing absolute values, i.e. 
$|\lambda_1|\geq \ldots\geq |\lambda_n|$. 
We  have also the Hermitian matrix $A^*A$ which is non-negative so that
$\sigma(A^*A)$ consists of non-negative real numbers
$\mu_1\geq \mu_2\geq\ldots\geq \mu_n$. 
In particular one has 
\[ 
\mu_1=\max_{|x|=1}\, \langle Ax,Ax\rangle\tag{1}
\]
\medskip



\noindent
{\bf{4:B.2 Theorem.}}
\emph{For every $1\leq p\leq n$ one has the inequality}
\[
|\lambda_1\cdots\lambda_p|\leq \sqrt{\mu_1\cdots \mu_p}
\]
\emph{where $\{\mu_k\}$ are the eigenvalues of $A^*A$}


\medskip


\noindent
First
we consider the  case $p=1$ and prove the inequality
\[ 
|\lambda_1| \leq \sqrt{\mu_1}\tag{i}
\]


\noindent
Since $\lambda_1$ is an eigenvalue there exists
a vector $x_*$ with $|x_*|=1$ so that
$A(x_*)=\lambda_1\cdot x_*$. It follows from (1) above
that
\[
\mu_1\geq \langle A(x_*),A(x_*)\rangle=|\lambda_1|^2
\]

\medskip

\noindent
{\bf{Remark.}}
The inequality is in general strict.
Consider the $2\times 2$-matrix
\[ 
A= 
\begin{pmatrix}
1& a\\ 0&b
\end{pmatrix}
\]
where $0<b<1$  and $a\neq 0$ some complex number
which gives
\[ 
A^*A= \begin{pmatrix}
1& a\\ a&a^2+b^2
\end{pmatrix}
\]
Here $\lambda\uuu 1=1$ and the eigenvector $x\uuu *=e\uuu
1$ and we see that
$\langle A(x_*),A(x_*)\rangle=1+|a|^2$.


\bigskip

\noindent
\emph{Proof when $p\geq 2$}
We employ a construction of independent interest.
Let $e_1,\ldots,e_n$ be some orthonormal basis in
${\bf{C}}^n$. For   every $p\geq 2$ we get 
the inner product space $V^{p}$ whose vectors are
\[ 
v=\sum\, c_{i_1,\ldots,i_p}\cdot e_{i_1}\wedge\ldots\wedge e_{i_p}
\]
where the sum extends over $p$-tuples $1\leq i_1<\ldots<i_p$.
This is an inner product   space of dimension $\binom{n}{p}$
where $\{e_{i_1}\wedge\ldots\wedge e_{i_p}\}$ is an orthonormal basis.
Consider a linear operator $A$ on ${\bf{C}}^n$
which in the $e$-basis is represented by a matrix
with elements
\[ 
a_{ik}=\langle Ae_i,e_k\rangle
\]
If $p\geq 1$ we define the linear operaror $A^{(p)}$
on $V^{(p)}$ by
\[ 
A^{(p)}(e_{i_1}\wedge\ldots\wedge e_{i_p})=
A(e_{i_1})\wedge\ldots\wedge A(e_{i_p})=
\sum\, a_{j_1i_1}\cdots a_{j_pi_p}\cdot
e_{j_1}\wedge\ldots\wedge e_{j_p}
\]
with the sum extended over all $1\leq j_1<\ldots<j_p$.
\medskip

\noindent
\emph{Sublemma.} \emph{The eigenvalues of $A^{(p)}$
consists of the $\binom{n}{p}$-tuple given by the products}
\[ 
\lambda_{i_1}\cdots \lambda_{i_m}\quad\colon\quad
1\leq i_1<\ldots<i_p\leq n\tag{*}
\]

\medskip

\noindent
\emph{Proof.} The eigenvalues above are independent of the chosen
orthonormal basis $e_1,\ldots,e_n$ since a change of this basis gives
another orthonormal basis in $V^{(p)}$ which does not affect
the eigenvalues of $A^{(p)}$.
Using  a   polarisation from 4:B.1 we may  assume 
from the start that
$A$ is an upper  triangular matrix and   then reader can
verify (*) in the sublemma.
\bigskip

\noindent
\emph{Final part of the proof.}
If  $p\geq 2$ it is clear that  one has the equality

\[
(A^{(p)})^*\cdot A^{(p)}=(A^*\cdot A)^{(p)}\tag{i}
\]
If $\lambda_1,\ldots\lambda_p$ is the
large $p$-tuple in Weyl's Theorem the product appears
as an eigenvalue of
$A^{(p)}$ and using the case $p=1$
one gets Weyl's inequality
since
the product $\mu_1\cdots\mu_p$
appears as an eigenvalue of
$(A^*\cdot A)^{(p)}$.

\bigskip


\centerline {\emph{4.B.3 An inequality by Pick.}}
\bigskip

\noindent
Let $C=\{c_{ik}\}$ be a skew-symmetric $n\times n$-matrix, i.e. 
$c_{ik}= -c_{ki}$ hold for all pairs $i,k$.
Denote  by $g$  the maximum of the absolute values of
the matrix  elements of $C$. 

\medskip

\noindent
{\bf{4:B.4 Theorem.}} \emph{One
has the inequality}
\[
\max_{|x|=1}\, \bigl|\langle Cx,x\rangle\bigr|
\leq g\cdot \text{cot}(\frac{\pi}{2n})\cdot 
\sqrt{n(n-1)/2}\tag{*}
\]



\noindent
\emph{Proof.}
Since $g$ is unchanged if we permute the columns of the given
$C$-matrix it suffices to prove (*) for a vector $x$ of unit length such that
\[
\mathfrak{Im}(x_k\bar x_i-x_i\bar x_k)\geq 0
\quad\colon\quad 1\leq i<k\leq n\tag{1}
\]



\noindent
Now one has
\[
\langle Cx,x\rangle=
\sum\sum\, c_{ik}x_k\bar x_i=
\sum_{i<k}\, c_{ik}x_k\bar x_i+
\sum_{i>k}\,c_{ik} x_k\bar x_i=
\sum_{i<k}\, c_{ik}(x_k\bar x_i-\bar x_k x_i)
\tag{3}
\]
where the last equality follows since
$C$ is skew-symmetric. Put
\[
\gamma_{ik}=\mathfrak{Im}\,( x_k\bar x_i-\bar x_k x_i)
\]

\noindent
Then (1) and the triangle
inequality give
\[
|\langle Cx,x\rangle|\leq \sum_{i<k}\, |c_{ik}|\cdot \gamma_{ik}
\leq g\cdot \sum_{i<k}\,  \gamma_{ik}
\]
Hence there only  remains to show that
\[
\sum_{i<k}\,  \gamma_{ik}\leq 
\text{cot}(\frac{\pi}{2n})\cdot 
\sqrt{n(n-1)/2}\tag{4}
\]
To prove this we write $x_k= \alpha_k+i\beta_k$
and the reader can verify that (4) follows from the inequality
\[
\sum_{i\neq k}\, a_kb_i\leq \text{cot}(\frac{\pi}{2n})\cdot 
\sqrt{n(n-1)/2}\tag{5}
\] 
whenever $\{a_k\}$ and $\{b_i\}$ are $n$-tuples of non-negative real numbers 
for which
$\sum_{k=1}^{k=n}\, a_k^2+b_k^2=1$.
Finally, 
(4) follows when one
applies Lagrange's multiplier for extremals of a quadratic form.





\newpage


\centerline {\emph{4.B.4 Results  by A. Brauer.}}
\bigskip

\noindent
Let $A$ be an  $n\times n$-matrix. To each
$1\leq k\leq n$ we set

\[ r_k=\text{min}\,[\,\sum_{j\neq k}\, |a_{jk}|\,\colon\,
\sum_{j\neq k}\, |a_{kj}\,\bigr]
\]

\medskip
\noindent
{\bf{4:B.5 Theorem.}}
\emph{Denote by $C_k$ the closed  disc of 
of radius $r_k$ centered at the diagonal element $a_{kk}$.
Then one has the inclusion:}
\[
\sigma(A)\subset C_1\cup\ldots\cup C_n\tag{*}
\]


\noindent 
\emph{Proof.}  Consider some eigenvalue $\lambda$ so that
$Ax=\lambda\cdot x$ for a non-zero eigenvector.
It means that
\[
\sum_{j=1}^
 {j=n}\, a_{j\nu}\cdot x_\nu=\,\lambda\cdot x_j
 \quad\colon\quad 1\leq j\leq n
 \]
Choose $k$ so that $|x_k|\geq |x_j|$ for all $j$.
Now we have
\[ 
(\lambda-a_{kk})\cdot x_k=  \sum_{j\neq k}\, a_{j\nu}\cdot x_\nu\implies
|\lambda-a_{kk}|\leq \sum_{j\neq k}\, |a_{kj}|\tag{1}
\]
At the same time the adjoint $A^*$ satisfies
$A^*(x)=\bar\lambda\cdot x$ which gives
\[
\sum_{j=1}^
 {j=n}\, \bar a_{\nu,j}\cdot x_\nu=\,\bar \lambda\cdot x_j
 \quad\colon\quad 1\leq j\leq n
\] 
Exactly as above we get
\[
|\lambda- a_{kk}|=
|\bar \lambda-\bar a_{kk}|\leq \sum_{j\neq k}\, |a_{jk}|\tag{2}
\]
Hence (1-2) give the inclusion
$\lambda\in C_k$.
\medskip


\noindent
{\bf{4:B.6 Theorem.}} \emph{Assume that the closed discs $C_1,\ldots,C_n$ are disjoint.
Then the eigenvalues of $A$ are simple and for every
$k$ there is a unique $\lambda_k\in C_k$.}
\medskip


\noindent
\emph{Proof.} 
Let $D$ be the diagonal matrix where $d_{kk}=a_{kk}$.
For ever $0<s<1$ we consider the matrix

\[ 
B_s=sA+(1-s)D
\]
Here $b_{kk}=a_{kk}$ for every $k$ and the associated discs
of the $B$-matrix are $C_1(s),\ldots,C_b(s)$ where
$C_k(s)$ is again centered at $a_{kk}$ while the radius is $s\cdot r_k$.
When $s\simeq 0$ the matrix $B\simeq D$ and then it is clear that
the previous theorem implies that
$B_s$ has simple eigenvalues $\{\lambda_k(s)\}$ where
$\lambda_k(s)\in C_k(s)$  for every $k$.
Next, since the "large discs" $C_1,\ldots,C_n$ are disjoint, it follows by
continuity that these inclusions  holds for every $s$ and with $s=1$ we get
the theorem. 
\medskip

\noindent
{\bf{Exercise.}} Assume that the elements of $A$ are all real and
the discs above are disjoint. Show that the eigenvalues of $A$ are all real.

\bigskip


\centerline {\emph{ Results  by Perron and Frobenius}}
\medskip

\noindent
Let $A=\{a_{pq}\}$ be a matrix where all elements are 
real and positive.
Denote by $\Delta^n_+$ the standard simplex of $n$-tuples
$(x_1,\ldots,x_n)$ where
$x_1+\ldots+x_n=1$ and every $x_k\geq 0$.
The following result was  established by Perron in [xx]:

\medskip

\noindent
{\bf{4:B.7  Theorem.}} \emph{There exists a unique ${\bf{x}}^*\in\Delta_+^n$
which is an eigenvector for $A$ with an eigenvalue $s^*$. Moreover.
$|\lambda|<s^*$ holds for every other eigenvalue}.
\medskip


\noindent
We leave the proof as an exercise to the reader.
In [Frob] 
the following addendum to
Theorem 4:B.7 is proved.
\medskip

\noindent
{\bf{4:B.8  Theorem.}} \emph{Let $A$ as above be a positive matrix
which gives the eigenvalue $s^*$. For every complex
$n\times n$-matrix
$B=\{b_{pq}\}$ such that $|b_{pq}|\leq a_{pq}$
hold for all pairs $p,q$, it follows that
every root of $P_B(\lambda)$ has absolute value $\leq s^*$
and equality holds if and only if $B=A$.}

\bigskip


\noindent
{\bf{4:B.9 The case of probability matrices.}}
Let $A$ have positive elements and assume that the sum in every column 
is one. In this case $s^*=1$ for with ${\bf{x}}^*=(x_1^*,\ldots,x_n^*)$ we have
\[
s^*= s^*\cdot \sum\, x^*_p= \sum\sum a_{pq}\cdot x^*_q=
\sum\, x^*_q=1
\]
\medskip

\noindent
The components of the
Perron vector ${\bf{x}}^*$
yields the probabilities to arrive at a station $q$ after many
independent motions in an associated stationary Markov chain where
the $A$-matrix defines the transition probabilities.
\medskip


\noindent
{\bf{Example.}} Let $n=2$ and 
take  $a_{11}=3/4$ and $a_{21}= 1/4$, while $a_{12}=a_{22}= 1/2$.
A computation gives $s^*=2/3$ which in probabilistic terms means that the
asymptotic probability  to arrive
at station 1 after many steps is $2/3$ while that of station 2 is $1/3$.
Here we notice that the second eigenvalue is
$s_*=1/4$ and an associated eigenvector is
$(1,-2)$.
\bigskip

\noindent
{\bf{4.B.10  Extension to infinite dimensions.}}
The Perron-Forbenius result was
extended to positive operstors on Hilbert spaces by
Pietsch in the article [1912].
We refer to ¤ xx the proof.


\newpage


\centerline{\bf ¤ 11. Commutative Banch algebras}
\bigskip




\noindent
Let $B$ be
a complex Banach space 
equipped with 
a commutative product whose norm
satisfies the multiplicative inequality
\[ 
||xy||\leq ||x||\cdot ||y||\quad\,\colon\, x,y\in B\tag{*}
\]
We  also assume that $B$ has a multiplicative unit element $e$
where  
$ex=xe$ hold for all $x\in B$ and   $||e||=1$. 
When this hold we refer to $B$ as a commutative Banach algebra with 
a multiplicative unit.
\medskip


\noindent
{\bf{Neumann series.}}
A non-zero element  $x$ in $B$ gives a bounded linear operator
$T(x)$ on the underlying Banach space defined by
\[
y\mapsto x\cdot y
\]
i.e. we simply employ the multiplication on $B$.
Now we  apply Carl Neumann's general
theory about resolvent operators
from ¤ xx.
To begin with we have seen that 
$T(x)$ has a non-empty compact spectrum
denoted by $\sigma(x)$
and in the open complement we put 
\[
R(\lambda)= (\lambda\cdot e-x)^{-1}
\]
Notice that the norm of the linear operstor $T(x)$ is equal to the norm of the
$B$-vector $x$.
So by the general result in ¤ xx applied with $T(x)$
the exterior Neumann series expansion  
\[
R(\lambda)=\frac{e}{\lambda}+
\sum_{n=1}^\infty\ \frac{x^n}{\lambda^{n+1}}\quad\colon\, |\lambda|>||x||
\]
converges and gives an analytic function of the complex parameter
$\lambda$ when 
\[
 |\lambda|>||x||
\]
Now there exists a unique largest
$r_*\geq 0$ such thst
$R(\lambda)$ extends to an analytic $B$-valued function in
the exterior disc $\{|\lambda|>r_*\}$.
If $r>r_*$ and $n$ a positive integer, Cauchy's residie calculus gives 
\[
x^n= \frac{1}{2\pi i}\int_{|\zeta|=r}\, \zeta^n\cdot R(\zeta)\, d\zeta
\]
Here
\[
\max_{\theta}\, ||R(re^{i\theta}||=M<\infty
\]
for some constant $M$. The triangle inequality entails that
\[
||x^n||\leq M\cdot r^n\tag{i}
\]
At this stage
we shall need the following:
\medskip

\noindent
{\bf{1. Theorem.}}
\emph{For every $x\in B$ there exists the limit}
\[
\lim_{n\to \infty}\, ||x^n||^{\frac{1}{n}}\tag{1.1}
\]
\medskip

\noindent
This follows from a general fact about sub-multiplicative sewuences.
See ¤ xxx.
Let $\rho(x)$ denote the oimit in (1.1). 
If $r>r_*$ we take roots in (i) and 
obtain
\[
||x^n||^{\frac{1}{n}}\leq M^{\frac{1}{n}}\cdot r\tag{ii}
\]
Since the $n$:th roots of $M$ converge to one
a passage to thr limit gives
\[
\rho(x)\leq r
\]
Above $r>r_*$ was arbitrsry and hence we  have proved the
inequality
\[
\rho(x)\leq r_*\tag{*}
\]
The opposite inequality  in (**) is clear. For
if $r>\rho(x)$ we find a large positive integer $n$ such that
\[
n\geq N\implies ||x^n||\leq r^n
\]
and then it is obvious that the exterior Neumann series above  converges when
$|\lambda|>r$.
Since tihs hold for every $r>\rho(x)$ we conclude that
(*) is an equality and then the  Neumann calculus from ¤ xx gives:

\medskip

\noindent
{\bf{2. The spectral radius formula.}}
\emph{For every $x\in X$ 
one has the equality}
\[
\rho(x)= \max\{|\lambda|\,\colon\,\lambda\in \sigma(x)\}\tag{2.1}
\]
\medskip

\noindent
{\bf{3. Multiplicative functionals.}}
A  ${\bf{C}}$-linear form $\lambda$ on $B$
is  multiplicative if:
\[
\lambda(xy)=\lambda(x)\cdot \lambda(y)
\quad\text{for all pairs}\quad x,y\in B\tag{3.1}
\]
When  $\lambda$ satisfies (3.1) and is not identically zero it is clear that
$\lambda(e)=1$.

\bigskip


\noindent
{\bf{3.2  Theorem.}}
\emph{Every multiplicative functional $\lambda$
on $B$ is automatically continuous, i.e.
an element in the normed dual space $B^*$ and its norm is equal to one.}
\medskip

\noindent
\emph{Proof}.
Ignoring the topology we use that
${\bf{C}}$ is a field and conclude that
the
$\lambda$-kernel is a \emph{maximal ideal} in the commutative
${\bf{C}}$-algebra $B$
which we denote by $\mathfrak{m}$.
When  $x\in B$ has norm $<1$ the  $B$-valued power series
\[
e+\sum_{n=1}^\infty\,x^n
\]
converges and  gives the inverse to $(e-x)$.
Since $\lambda$ is multiplicative with $\lambda(e)=1$
it follows that $\lambda\cdot e-x)\neq 0$,
So if 
$B_0$Êis the open unit ball in $X$ then
\[
\mathfrak{m}=\text{ker}(\lambda)\cap \{e+B_0\}=\emptyset
\]
By the remark  in ¤ xx this implies that
the hyperplane
$\mathfrak{m}$ is closed in the Banach space $B$ and therefore
a continuous linear functional. Hence there exists a constant $C$ such that
\[
|\lambda(x)|\leq C\cdot ||x||\quad\colon x\in X
\]
Finally, since $\lambda$ is multiplicative this entails that
\[
|\lambda(x)|^n\leq C\cdot ||x^n||\quad\colon x\in X
\]
Taking $n$:th rooots and passing to infinity the reader can check that this gives
\[
|\lambda(x)|\leq \rho(x)\leq ||x||
\]

\medskip


\noindent
{\bf{4. The Gelfand transform.}}
Denote by $\mathcal M(B)$ the family of sll multiplicative functionals.
Keeping  an element $x\in B$ fixed we get
the complex-valued function  on $\mathcal M(B)$ defined by:
\[ 
\lambda\mapsto \lambda(x)
\]
The resulting function is denoted by $\widehat x$ 
and  called the Gelfand transform of the $b$-element $x$.
\medskip

\noindent
{\bf{Exercise.}} Apply the specteral radius formuka to show that
\[
\max_{\lambda\in \mathcal M(B)}\, |\widehat{x}(\lambda)|= \rho(x)\tag{4.1}
\]
\medskip

\noindent 
Following a  device by Gelfand
we use that 
$\mathcal M(B)$ is a subset of 
the dual space
$B^*$ which is  equipped with the
weak-star  topology
and we know from ¤ xx that the unit ball $S^*$ in $B^*$ is compact in this topology.
The reader can check that
$\mathcal M(B)$  appears as a weak-star closed subset of $S^*$ and
hence
becomes a compact space where
every Gelfand transform
$\widehat x$ is  a continuous function.
This gives 
an algebra homomorphism
from $B$ into the commutative algebra $C^0(\mathcal M(B))$:
\[ 
x\mapsto \widehat x\tag{*}
\]
called the Gelfand transform.
The inequality in (xx) shows that the map (*) is continuous with  norm
$\leq 1$ where we employ the sup-norm on the Banach space
 $C^0(\mathcal M(B))$.
\bigskip

\noindent
{\bf{5. Semi-simple algebras.}}
The spectral radius formula shows that $\widehat x$ is the zero function if and only if
$\rho(x)=0$. One says that the Banach algebra $B$ is
\emph{semi-simple} if the Gelfand transform in 
(*)  is injective. An equivalent condition is that
\[
0\neq x\implies \rho(x)>0\tag{5.1}
\]
\medskip





\noindent
{\bf{6. Uniform algebras.}}
If $B$ is  semi-simple the Gelfand transform
identifies $B$ with a subalgebra of $C^0(\mathcal M(B))$.
In general
this subalgebra is not closed. The reason is that
there can exist $B$-elements of norm one while
the $\rho$-numbers can be arbitrarily small.
If the equality below holds for every $x\in B$:
\[
||x||=\rho(x)= |\widehat x|_{\mathcal M(B)}\tag{*}
\]
one says that $B$ is a uniform  algebra.
\bigskip

\noindent
{\bf{Remark.}}
Multiplicative functionals
on specific Banach algebras were used  by Norbert Wiener  and Arne Beurling
where
the focus was on 
Banach algebras which arise via the 
Fourier transforms.
Later  Gelfand, Shilov and Raikow established the  abstract theory which 
has the merit that it applies to  general situations such
as Banach algebras generated by   linear operators on a
normed space. Moreover,  
Shilov  applied results from the theory
of 
analytic functions in several complex
to construct
\emph{joint spectra} of several elements
in a commutative Banach algebra.
See [Ge-Raikov-Shilov] for  a
study of commutative Banach algebras which include
results about joint spectra.
One should also mention  the   work by J. Taylor who used
integral formulas in
several complex variables  to analyze the topology
of Gelfand spaces
which arise  from 
the Banach
algebra of  Riesz measures with total bounded variation on
the real line, and more generally on arbitrary locally compact abelian groups.




\newpage




\centerline {\bf A. Neumann series and resolvents }
\medskip


\noindent
Let $B$ be a commutative Banach algebra with the  identity element  $e$.
The set of elements $x$ whose norms have absolute value $<1$ is denoted by
$\mathfrak B$ and  called the open unit ball in $B$.

\medskip

\noindent
{\bf A.1 Neumann series.}
Let us  prove that $e-x$ is invertible for
every $x\in\mathfrak B$. We have
$||x||=\delta<1$ and the multiplicative inequality for the norm
gives:
\[ 
||x^n||\leq ||x||^n=\delta^n\quad\colon\quad n=1,2,\ldots\tag{1}
\]

\noindent
If $N\geq 1$ we set:
\[ 
S_N(x)= e+x+\ldots+ x^N\tag{2}
\]


\noindent
For each pair $M>N$  the triangle inequality for norms gives:
\[
||S_M(x)-S_N(x)||\leq ||x^{N+1}||+\ldots+||x^M||\leq \delta^{N+1}+\ldots+\delta^M\tag{3}
\]
It follows that
\[
||S_M(x)-S_N(x)||\leq \frac{\delta^{N+1}}{1-\delta}\quad\colon M>N\geq 1
\]
Hence $\{S_N(x)\}$ is a Cauchy sequence and is therefore
convergent in the Banach space. For each $N\geq 1$ we notice that
\[
(e-x)S_N(x)= e-x^{N+1}
\]
Since $x^{N+1}\to 0$ we conclude that if $S_*(x)$ is the limit of
$\{S_N(x)\}$ then
\[ 
(e-x)S_*(x)= e\tag{*}
\]
This proves that
$e-x$ is an invertible element in
$B$ whose inverse is the convergent $B$-valued series
\[ 
S_*(x)= e+\sum_{k=1}^\infty\, x^k\tag{**}
\]

\noindent
More generally, let $0\neq x\in B$
and consider some $\lambda$ such that
$|\lambda|>||x||$. Now $\lambda^{-1}\cdot x\in \mathfrak B$
and from (**) we conclude that
$\lambda\cdot e-x=\lambda(e-\lambda^{-1}\cdot x)$ is invertible
where
\[
(\lambda\cdot e-x)^{-1}=\lambda^{-1}\cdot
\bigl[\,e+\sum_{k=1}^\infty\, \lambda^{-k}\cdot x^k\,\bigr]\tag{***}
\]

\medskip

\noindent {\bf{Exercise.}}
Deduce from (***) that one has the inequality
\[
||(\lambda\cdot e-x)^{-1}||\leq
\frac{1}{|\lambda|-||x||}
\]

\medskip






\noindent
{\bf {A.2. Local Neumann series expansions}}.
To each $x\in B$ we define the set
\[ 
\gamma(x)=\{\lambda\,\colon \,e-x\quad\text{is invertible}\}
\]
Let $\lambda_0\in\gamma(x)$
and put
\[
\delta=||(\lambda_0\cdot e-x)^{-1}||\tag{1}
\]
To each complex number $\lambda$ we set
\[ 
y(\lambda) =(\lambda_0-\lambda)\cdot (\lambda_0\cdot e-x)^{-1}\tag{2}
\]

\noindent
If $|\lambda-\lambda_0|<\delta$ we see that $y(\lambda)\in\mathfrak B$
and hence $e-y(\lambda)$ is invertible with an  inverse  given by the Neumann series:
\[
(e-y(\lambda))^{-1}=
e+\sum_{\nu=1}^\infty\, (\lambda_0-\lambda)^\nu\cdot
(\lambda_0\cdot e-x)^{-\nu}\tag{3}
\]


\noindent
Next,  for each complex number $\lambda$ we notice that
\[
(\lambda\cdot e-x)\cdot (\lambda_0\cdot e-x)^{-1}=
\]
\[
\bigl[(\lambda_0\cdot e-x)+(\lambda-\lambda_0)\cdot e\bigr]
(\lambda_0\cdot e-x)^{-1}
=e-y(\lambda)\implies 
\]
\[
(\lambda\cdot e-x)=(\lambda_0\cdot e-x)^{-1}\cdot (e-y(\lambda))\tag{4}
\]

\noindent
So if $|\lambda-\lambda_0|<\delta$ it follows that
$(\lambda\cdot e-x)$ is a product of two invertible elements and hence invertible. 
Moreover,  the series expansion from (3) gives:
\[
(\lambda\cdot e-x)^{-1}= (\lambda_0\cdot e-x)\cdot [\,
e+\sum_{\nu=1}^\infty\, (\lambda_0-\lambda)^\nu\cdot
(\lambda_0\cdot e-x)^{-\nu}\,]\tag{A.2.1}
\]

 

\medskip

\noindent
We refer to (A.2.1 ) as a local Neumann series.
The triangle inequality gives the norm inequality:
\[
||(\lambda\cdot e-x)^{-1}||\leq
||(\lambda_0\cdot e-x)||\cdot \bigl[1+\sum_{\nu=1}^\infty\,
|\lambda-\lambda_0|^\nu\cdot \delta^\nu\,\bigr]=
\]
\[
||(\lambda_0\cdot e-x)||\cdot\frac{1}{
1-|\lambda-\lambda_0|\cdot \delta}\tag{A.2.2}
\]
\medskip


\noindent
{\bf A.3. The analytic function $R_x(\lambda)$}.
From the above 
$\gamma(x)$ is an open subset of
${\bf{C}}$. Put:
\[ 
R_x(\lambda)=(\lambda\cdot e-x)^{-1}\quad\colon\, \lambda\in\gamma(x)
\]
The local Neumann series (A.2.1) 
shows that
$\lambda\mapsto R_x(\lambda)$ is a $B$-valued analytic function in
the open set $\gamma(x)$. We use this analyticity to prove:
\medskip


\noindent
{\bf A.4 Theorem.}
\emph{The set 
${\bf{C}}\setminus\gamma(x)\neq\emptyset$.}
\medskip

\noindent
\emph{Proof.}
If $\gamma(x)$ is the whole complex plane the
function $R_x(\lambda)$ is entire.
When
$\lambda|>||x||$ we have seen that 
the norm of
$R_x(\lambda)$ is $\leq \frac{1}{|\lambda|-||x||}$
which tends to zero as
$\lambda\to \infty$.
So if  $\xi$ is an element in the dual space
$B^*$
then the entire function
\[ 
\lambda\mapsto \xi(R_x(\lambda))
\]
is bounded and tends to zero and hence identically zero by
the Liouville theorem for entire functions.
This would hold  for every
$\xi\in B^*$ which clearly is impossible and hence
$\gamma(x)$ cannot be the whole complex plane.
\bigskip

\noindent
{\bf{A.5 Definition}}
\emph{The  complement ${\bf{C}}\setminus \gamma(x)$ 
is denoted by $\sigma(x)$ and called the spectrum of $x$.}


\bigskip

\noindent
{\bf{A.6 Exercise.}}
Let $\lambda_*$ be a point in $\sigma_B(x)$.
Show the following inequality for each
$\lambda\in\gamma(x)$:
\[
||(\lambda\cdot e-x)^{-1}||\geq
\frac{1}{|\lambda-\lambda_*|}
\]
The hint is to use local Neumann series from A.2.

\bigskip


\centerline {\bf B. The Gelfand transform}
\bigskip

\noindent
Put
\[
\mathfrak{r}(x)=\max_{\lambda\in\sigma(x)}\,|\lambda|\tag{*}
\]


\noindent
We refer to $\mathfrak{r}(x)$ as the spectral radius of $x$. Notice
that it gives  the radius of the smallest closed disc which contains
$\sigma(x)$.
The next result shows that
the spectral radius is found via  a limit of certain norms.


\medskip


\noindent
{\bf B.1 Theorem.}
\emph{For each $x\in B$ there exists the 
limit $\lim_{n\to\infty}\, ||x^||^{\frac{1}{n}}$
and it is equal to
$\mathfrak{r}(x)$.}
\medskip

\noindent
\emph{Proof.}
Put 
\[
\xi(n)=||x^n||^{\frac{1}{n}}\quad\, n\geq 1\,.
\]
The multiplicative inequality for the norm gives
\[
\log\,\xi(n+k)\leq
\frac{n}{n+k}\cdot \log\,\xi(n)+
\frac{k}{n+k}\cdot \log\,\xi(k)\,\quad\text{for all pairs}\,\, n,k\geq 1\,.
\]
Using this convexity it is an easy exercise to verify that there exists the
limit
\[
\lim_{n\to\infty}\, \xi(n)=\xi_*\tag{i}
\]


\noindent
There remains to prove the equality
\[ 
\xi_*=\mathfrak{r}(x)\,.\tag{ii}
\]
To prove (ii) we use
the Neumann series
expansion for $R_x(\lambda)$.
With $z=\frac{1}{\lambda}$ this gives the
$B$-valued analytic function
\[
g(z)=z\cdot e+\cdot \sum_{\nu=1}^\infty\, 
z^\nu\cdot x^\nu
\]
which  is analytic in the disc $|z|<\frac{1}{\mathfrak{rad}(x)}$.
The general result about analytic functions in
a Banach space from XX therefore implies  that when
$\epsilon>0$  there exists a constant $C_0$ such that
\[ 
||x^n||\leq C_0\cdot (\mathfrak{r}(x)+\epsilon)^n\quad\, n=1,2,\ldots\implies 
\xi(n)\leq
C_0^{\frac{1}{n}}\cdot(\mathfrak{r}(x)+\epsilon))
\]
Since
$C_0^{\frac{1}{\nu}}\to 1$ we conclude that
\[
\limsup_{n\to\infty}\,
\xi(n)\leq \mathfrak{r}(x)+\epsilon)
\]
Since $\epsilon>0$ is arbitrary and the limit  (i) exists we get
\[ 
\xi_*\leq  \mathfrak{r}(x)\tag{iii}
\]


\noindent
To prove the opposite inequality we use the definition of
the spectral radius which to begin with shows that
the $B$-valued analytic function $g(z)$ above cannot converge
in a disc of radius
$>\frac {1}{\mathfrak{r}(x)}$.
Hence Hadamard's  limit formula for  power series
with values on a Banach space  in XX gives
\[ 
\limsup_{n\to\infty}\,
\xi(n)\geq\mathfrak{r}(x)-\epsilon\quad\,\text{for every}\,\,\epsilon>0\,.
\]
Since the limit in (i)  exists we conclude that
$\xi_*\geq\mathfrak{r}(x)$ and together with (iii) above we have proved 
Theorem B.1.
\newpage


\centerline
{\bf B.2 The Gelfand space $\mathcal M_B$}.

\medskip

\noindent
Let $B$  be a commutative Banach algebra with a unit element $e$.
As a commutative ring we can refer to its \emph{maximal ideals}. Thus, 
a maximal ideal
$\mathfrak{m}$ 
is  $\neq B$ and not contained in any
strictly larger ideal.
The maximality means that
every non-zero element in the quotient ring
$\frac{B}{\mathfrak{m}}$ is invertible, i.e.
this quotient ring is a \emph{commutative field}.
Since the maximal ideal $\mathfrak{m}$
cannot contain an invertible element it follows from A.1
that
\[
x\in\mathfrak{m}\implies
||e-x||\geq 1\tag{i}
\]


\noindent
Hence the closure of $\mathfrak{m}$ 
in the Banach space is 
$\neq B$. So by  maximality 
$\mathfrak{m}$ is a \emph{closed subspace} of $B$
and hence there exists 
the Banach space
$\frac{B}{\mathfrak{m}}$.
Moreover, the  multiplication on $B$ induces a product on this quotient space and in this
way
$\frac{B}{\mathfrak{m}}$ becomes a new Banach algebra.
Since
$\mathfrak{m}$ is maximal this  Banach algebra cannot contain
any non-trivial maximal ideal which
means  that when
$\xi$ is any non-zero element in
$\frac{B}{\mathfrak{m}}$ then the principal ideal generated
by $\xi$ must be equal to
$\frac{B}{\mathfrak{m}}$. In other words, every non-zero element in
$\frac{B}{\mathfrak{m}}$ is \emph{invertible}. Using this we get
the following result.

\medskip


\noindent
{\bf B.3 Theorem.} \emph{The Banach algebra $\frac{B}{\mathfrak{m}}={\bf{C}}$, i.e. it
is reduced to the complex field.}


\medskip

\noindent
\emph{Proof.}
Let $e$ denote the identity in $\frac{B}{\mathfrak{m}}$.
Let $\xi$ be an element in $\frac{B}{\mathfrak{m}}$
and suppose that

\[
\lambda\cdot e-\xi\neq 0\quad\text{ for all}\quad \lambda\in{\bf{C}}\tag{i}
\]

\noindent
Now all non-zero elements in
$\frac{B}{\mathfrak{m}}$ are invertible so (i) would entail that
the spectrum of $\xi$ is empty which contradicts
Theorem 3.1.
We conclude that for each element $\xi\in\frac{B}{\mathfrak{m}}$ 
there exists a complex number $\lambda$ such that
$\lambda\cdot e=\xi$. It is clear that $\lambda$ is unique and
that this means precisely that
$\frac{B}{\mathfrak{m}}$ is a 1-dimensional complex vector space generated by
$e$.
\bigskip

\noindent
{\bf {B.4 The continuity of multiplicative functionals.}}
Let $\lambda\colon B\to {\bf{C}}$ be a multiplicative
functional. Since ${\bf{C}}$ is a field it follows that the
$\lambda$-kerenl is a maximal ideal in $B$ and hence closed.
Recall from XX that every linear functional on
a Banach space whose kernel is a closed subspace is automatically
in the continuous dual $B^*$.
This proves that every multiplicative functional is continuous
and as a consequence its norm in $B^*$ is equal to one.



\bigskip

\noindent
{\bf B.5 The Gelfand transform.}
Denote by $\mathcal M_B$ the set of all maximal ideals in
$B$.
For each
$\mathfrak{m}\in\mathcal  M_B$ we have proved that
$\frac{B}{\mathfrak{m}}$ is reduced to the complex field.
This enable us to construct complex-valued functions on $\mathcal M_B$. 
Namely, to each element 
$x\in B$ we get a complex-valued function on
$\mathcal  M_B$ defined by:
\medskip
\[
\hat x(\mathfrak{m})=
\,\text{the unique complex number for which}\,\, 
x-\hat x(\mathfrak{m})\cdot e\in\mathfrak{m}
\]


\noindent 
One refers to $\hat x$ as the Gelfand transform
of $x$.
Now we can    equip $\mathcal M_B$ with the \emph{weakest topology} such that the functions
$\hat x$ become continuous. 
\medskip

\noindent{\bf B.6 Exercise.}
Show that with the topology  it follows
that $\mathcal M_B$ is a compact Hausdorff space.
\bigskip



\noindent {\bf B.7 Semi-simple algebras.} 
The definition of $\sigma(x)$ shows that
this compact set is equal to the range of
$\hat x$, i.e. one has the equality
\[
\sigma(x)=\hat x(\mathcal M_B)\tag{*}
\]
Hence Theorem 4.1  gives the equality:

\[
\lim_{n\to\infty}\, ||x^n||^{\frac{1}{n}}=
\max_{\mathfrak{m}}\,\hat x(\mathfrak{m})=|\hat x|_{\mathcal M_B}\tag{**}
\]


\noindent
where the right hand side is the maximum norm of the Gelfand transform.
It may occur that the spectral radius is zero which 
by (**)  means that the Gelfand transform $\hat x$ is identically zero.
This eventual possibility leads to:
\medskip

\noindent
{\bf B.8 Definition.}
\emph{A Banach algebra $B$ is called semi-simple if
$\mathfrak{r}(x)>0$ for every non-zero element.}

\bigskip

\noindent
{\bf{B.9 Remark.}} So when $B$ is semi-simple then the Gelfand map 
$x\mapsto \widehat x$
from $B$ into $C^0(\mathcal M_B)$ is injective. In this way $B$ is
identified with a subalgebra of all continuous and complex-valued functions on the compact 
Hausdorff space $\mathcal M_B$. Moreover one has the inequality
\[
|\widehat x|_{\mathcal M_B}\leq ||x||\tag{*}
\]
It is in general strict. 
When equality holds one says that
$B$ is a \emph{uniform algebra}.
In this case the Gelfand transform identifies $B$ with a closed
subalgebra of $C^0(\mathcal M_B)$.
For an extensive study of uniform algebras
we refer to the books [Gamelin] and [Wermer].


\bigskip


\centerline{\bf{C. Examples of Banach algebras.}}



\medskip

\noindent
Below we illustrate the general theory by some examples.
Let us start with:
\medskip

\noindent
{\bf{1. Operator algebras.}}
Let $B$ be a Banach space and 
$T$ is a bounded linear operator on
$B$.
Together with the identity operator  we construct the subalgebra of $\mathcal L(B)$
expressed  by polynomials in $T$ and  take the closure of this polynomial 
$T$-algebra in the Banach space $\mathcal L(B)$.
In this way
we obtain
a Banach algebra $\mathcal L(T)$
So if $S\in\mathcal L(T)$ then $||S||$ is the operator norm taken in
$\mathcal L(B)$.
Here the Gelfand space of $\mathcal L(T)$ is identified with a compact
subset of ${\bf{C}}$ which is the spectrum of $T$
denoted by $\sigma(T)$. By definition $\sigma(T)$
consists of those complex numbers
$\lambda$ such that the operator
$\lambda\cdot E-T$ fails to be invertible in $\mathcal L(T)$.

\medskip

\noindent
{\bf{1.0 Permanent spectrum.}}
Above $\sigma(T)$ refers to the spectrum in the Banach algebra $\mathcal L(T)$.
But it can occur that $\lambda\cdot e-T$ is an invertible linear operator on
$B$ even when
$\lambda\in\sigma(T)$. To see an example we let $B=C^0(T)$
be the Banach space of continuous functions on the unit circle.
Let $T$ be the linear operator on $B$ defined by the multiplication with
$z$, i.e.
when $f(\theta)$ is some $2\pi$-periodic function we set

\[ 
T(f)(\theta)= e^{i\theta}\cdot f(e^{i\theta})
\]
If $\lambda$ belongs to the open unit disc
we notice that for any polynomial $Q(\lambda)$ one has

\[
|Q(\lambda)|\leq \max_\theta\, |Q(e^{i\theta})|=||Q(T)||
\]
It follows that the spectrum of $T$ in $\mathcal L(T)$ is identified with
the closed unit disc $\{|\lambda|\leq 1\}$.
For example, $\lambda=0$ belongs to this spectrum. On the other hand
$T$ is invertible as a linear operator on $B$ where $T^{-1}$ is
the operator defined by
\[ 
T^{-1}(f)(\theta)= e^{-i\theta}\cdot f(e^{i\theta})
\]
So in this example the spectrum of $T$ taken in the
space of all continuous linear operators on $B$ is reduced to the unit circle
$\{|\lambda|=1\}$.
\medskip

\noindent
In general, let $B$ be a commutative Banach algebra which appears as a closed 
subalgebra of a larger Banach algebra $B^*$.
If $x\in B$ we have its spectrum $\sigma_B(x)$ relative $B$ and 
the spectrum $\sigma_{B^*}(x)$ relative the larger algebra.
The following inclusion is obvious:
\[
\sigma_{B^*}(x)\subset \sigma_B(x)\tag{1}
\]
The example above shows that this inclusion in general is strict.
However, one has the opposite inclusion
\[
\partial(\sigma_B(x))\subset \sigma_{B^*}(x)\tag{2}
\]
In other words, if $\lambda$ belongs to the boundary of $\sigma_B(x)$ then
$\lambda\cdot e-x$ cannot be inverted in any larger Banach algebra. It means that
$\lambda$ is a permanent spectral value for $x$.
The proof of (2) is given in XX using  Neumann series.



\bigskip






\noindent
{\bf{2.  Finitely generated Banach algebras.}}
A Banach algebra $B$ is finitely generated if there exists a finite subset
$x_1,\ldots,x_k$ such that every $B$-element can be approximated in the norm
by polynomials of this $k$-tuple.
Since every multiplicative functional 
$\lambda$ is continuous it is determined by its values on
$x_1,\ldots,x_k$. It means that we have an injective map from
$\mathcal M(B)$ into the $k$-dimensional complex vector space
${\bf{C}}^k$
defined by
\[
\lambda\mapsto (\lambda(x_1),\ldots\lambda(x_k))\tag{1}
\]
Since the Gelfand topology is compact
the image under (1) yields a compact
subset of ${\bf{C}}^k$  denoted by $\sigma(x_\bullet)$.
This construction was introduced by Shilov and one refers to
$\sigma(x_\bullet)$ as the joint spectrum of the $k$-tuple
$\{x_\nu\}$.
It turns out that such joint spectra are 
special. More precisely, they are polynomially convex subsets of
${\bf{C}}^k$.
Namely, let $z_1,\ldots,z_k$ be the complex coordinates
in
${\bf{C}}^k$. If $z_*$ is a point outside
$\sigma(x_\bullet)$ there exists for every $\epsilon>0$ some polynomial 
$Q[z_1,\ldots,z_k]$ such that $Q(z_*)=1$ while the maximum norm of
$Q$ over $\sigma(x_\bullet)$ is $\epsilon$.
To see this one argues by a contradiction, i.e. if
this fails there exists a constant $M$ such that
\[
|Q(z^*)|\leq M\cdot|Q|_{\sigma(x_\bullet)}
\]
for all polynomials $Q$.
Then the reader may verify that we obtain a multiplicative
functional $\lambda^*$ on $B$ for which
\[
\lambda^*(x_\nu)=z^*_\nu\quad\colon\, 1\leq\nu\leq k
\]
By definition this would entail that
$z^*\in\sigma(x_\bullet)$.
\medskip

\noindent
{\bf{Remark.}}
Above we encounter a topic in several complex variables.
In contrast to the case $n=1$
it is not
easy to describe conditions on a compact subset
$K$ of ${\bf{C}}^k$ in order that it is polynomially convex,
which by definition means that whenever $z^*$ is a point in
${\bf{C}}^k$ such that
\[ 
|Q(z^*)|\leq |Q|_K
\] 
then $z^*\in K$.

\bigskip


\centerline {\bf{3. Examples from harmonic analysis.}}
\medskip

\noindent
{\bf{The measure algebra $M({\bf{R}}^n)$}}.
The elements are Riesz measures in ${\bf{R}}^n$ of finite total mass and the product defined by
convolution. The identity is the Dirac measure at the origin.
Set $B= M({\bf{R}}^n)$. The Fourier transform identifies the
$n$-dimensional $\xi$-space with a subset of
$\mathcal M(B)$. In fact, this follows since
the Fourier transform of a convolution
$\mu*\nu$ is the product $\widehat\mu(\xi)\cdot \widehat\nu(\xi)$.
In this way we have an embedding of ${\bf{R}}^n_\xi$ into $\mathcal M(B)$.
However, the resulting subset is not dense in
$\mathcal M(B)$.
It means that there exist Riesz measures $\mu$ such that 
$|\widehat\mu(\xi)|\geq \delta >0$ 
hold for all $\xi$, and yet $\mu$ is not invertible in $B$.
An example of such a measure was
discovered by Wiener and Pitt and one therefore refers to
the \emph{Wiener-Pitt phenomenon} in $B$.
Further examples occur in [Gelfand et. all].
The idea is to construct Riesz measurs $\mu$ with independent powers, i.e. measures $\mu$ such that the norm of a $\mu$-polynomial
\[ 
c_0\cdot \delta_0+c_1\cdot \mu+\ldots+c_k\cdot \mu^ k
\] 
is roughly equal
to $\sum\,|c_k|$ while $||\mu||=1$.
In this way one can construct measurs $\mu$ for which
the spectrum in $B$ is the unit disc while the range of the
Fourier transform is a real interval.
Studies of $\mathcal M(B)$
occur in work by J. Taylor who established
topological properties of
$\mathcal M(B)$. The proofs rely upon several complex variables and
we shall not try to expose material from Taylor's deep work.
Let us only mention one result from Taylor's work
in the case $n=1$.
Denote by $i(B)$ the multiplicative group of invertible measures in 
$B$ where $B=\mathcal M(B)$ on the real line.
If $\nu\in B$
we  construct the exponential sum
\[
 e^\nu=\delta_0+\sum_{k=1}^\infty\, \frac{\nu^k}{k !}
\]
In this way $e^B$ appears as a subgroup of $i(B)$.
Taylor proved that the quotient group
\[
\frac{i(B)}{e^B}\simeq {\bf{Z}}
\] 
where
the right hand side is the additive group of integers.
More precisely one finds an explicit 
invertible measure $\mu_*$ which does not belong to $e^B$ and for 
any $\mu\in i(B)$ there exists a unique integer $m$ and some
$\nu\in B$ such that

\[ 
\mu=e^\nu*\mu_*^k\tag{*}
\]
The measure $\mu_*$ is given by
\[ 
\mu_*=\delta_0+f
\] 

CONTINUE...


\medskip

\noindent{\bf{3.1 Wiener algebras.}}
We can ask for  subalgebras of $M({\bf{R}}^n)$ where the Wiener-Pitt phenomenon does not occur, i.e. subalgebras $B$ where the Fourier transform gives a dense embedding of
${\bf{R}}^n_\xi$ into $\mathcal M(B)$.
A first example goes as follows:
Let $n\geq 1$ and consider the Banach space
$L^1({\bf{R}}^n)$ where convolutions of $L^1$-functions
is defined.
Adding the unit point mass $\delta_0$ at 
the origin we get the commutative Banach algebra 
\[
B={\bf{C}}\cdot \delta_0+L^1({\bf{R}}^n)
\]
Here the Fourier transform  describes $\mathcal M(B)$.
More precisely, if $\lambda$ is a multiplicative functional on $B$ whose
restriction to  $L^1({\bf{R}}^n)$ is not identically zero, then
one proves that  there exists
a unique point $\xi\in {\bf{R}}^n$ such that
\[
\lambda(f)=\widehat f(\xi)\quad\colon\quad 
f\in L^1({\bf{R}}^n)
\]
In this way the $n$-dimensional $\xi$-space is identified with a subset of
$\mathcal M(B)$. An extra point $\lambda^*$ appears in
$\mathcal M(B)$ where $\lambda^*(\delta_0)=1$ while its restriction to
$L^1({\bf{R}}^n)$ vanishes.
Hence
the compact Gelfand space $\mathcal M(B)$ 
corresponds to the  one-point compactification of
the $\xi$-space. Here the continuity of Fourier transforms of $L^1$-functions 
correspond to the  fact that their Gelfand transforms are continuous.
An important consequence
of this is that when
$f(x)\in L^1({\bf{R}}^n)$ is such that $\widehat f(\xi)\neq 1$ for every
$\xi$, then the $B$-element $\delta_0-f$ is invertible,  i.e. there
exists another $L^1$-function $g$ such that
\[
\delta_0=(\delta_0-f)*(\delta_0+g)\implies f=g-f*g
\]
The equality
\[ 
\mathcal M(B)= {\bf{R}}^n_\xi\cup\{\lambda^*\}\tag{*}
\]
was originally put forward by Wiener prior to the general theory about Banach algebras.
Another  Banach algebra 
is $M_d({\bf{R})^n}$
whose elements are discrete measures with a finite total variation.
Thus, the elements are measures

\[ 
\mu=\sum\, c_\nu\cdot \delta(p_\nu)
\]


\noindent
where $\{p_\nu\}$ is a sequence of points in ${\bf{R}}^n$
and
$\{c_\nu\}$ a sequence of complex numbers such that
$\sum\,|c_\nu|<\infty$.
Here the Gelfand space is more involved. To begin with
the Fourier transform identifies ${\bf{R}}^n_\xi$ with a subset of
$\mathcal M(B)$.
But the compact space $\mathcal M(B)$ is considerably and given
by a compact abelian group which is  called the Bohr group after
Harald Bohr whose studies of
almost periodic functions led to
the description of $\mathcal M(B)$. However one has the following result:


\medskip

\noindent
{\bf{3.2 Bohr's Theorem.}}
\emph{The subset ${\bf{R}}^n_\xi$ is dense in $\mathcal M(B)$.}
\medskip

\noindent
{\bf{Remark.}}
See XX for an account about almost periodic functions 
which proves Bohr's theorem
in the case $n=1$.

\medskip


\noindent
{\bf{3.3 Beurling's density theorem}}.
Consider  the Banach algebra $B$ generated
by
$M_d({\bf{R}}^n)$ and $L^1({\bf{R}}^n)$.
So its elements are measures of the form
\[
\mu=\mu_d+f
\] 
where $\mu_d$ is discrete and $f$ is absolutely continuous.
Here 
the Fourier transform identifies ${\bf{R}}^n_\xi$ with an open subset
of $\mathcal M(B)$. More precisely, a multiplicative
functional $\lambda$ on $B$ belongs to the open set
${\bf{R}}^n_\xi$ if and only if $\lambda(f)\neq 0$
for at least some $f\in L^1({\bf{R}}$.
The remaining part
$\mathcal M(B)\setminus{\bf{R}}^n_\xi$  is equal to the Bohr group above..
It means
that when
$\lambda$ is an arbitrary multiplicative functional on
$B$ then there exists $\lambda_*\in\mathcal M(B)$ such that
$\lambda_*$ vanishes on $L^1({\bf{R}}^n$ while $\lambda_*(\mu)=\lambda(\mu)$
for every discrete measure.
The density of ${\bf{R}}\uuu\xi^n$
follows via Bohr's theorem and the fact that
Fourier transforms of $L^1$\vvv functions
tend to zero as $|\xi|\to +\infty$.






\medskip

\noindent
{\bf{3.4  Varopoulos'  density theorem}}.
For each  linear subspace $\Pi$ of
arbitrary dimension $1\leq d\leq n$ we get the space
$L^1(\Pi)$ of absolutely continuous measures supported by
$\Pi$ and of finite total mass.
Thus, we identify $L^1(\Pi)$ with a subspace of $M({\bf{R}}^n)$.
We get the closed subalgebra of 
 $M({\bf{R}}^n)$  generated by
all these $L^1$-spaces and the discrete measures. It is denoted by
$\mathcal V({\bf{R}}^n)$ and  called the Varopoulos 
measure algebra in ${\bf{R}}^n$.
In [Var] it is proved that
the Fourier
transform identifies
${\bf{R}}^n_\xi$ with a dense subset of
$\mathcal M( \mathcal V({\bf{R}}^n))$.
\medskip

\noindent
{\bf{3.5 The extended $\mathcal V$-algebra.}}
In ${\bf{R}}^n$
semi-analytic strata  consist of locally closed
real-analytic submanifolds $S$ whose closure $\bar S$ is compact and
the relative boundary $\partial S=\bar S\setminus S$
is equal to the zero set of a real analytic function.
On each such stratum we  construct measures which are absolutely continuous with
respect to the area measure of $S$.
Here the dimension of $S$ is between 1 and $n-1$ and 
each  measure in  $L^1(S)$ is 
identified with a Riesz measure in
${\bf{R}}^n$.
One can easily prove
that every $\mu\in L^1(S)$ has a power which 
belongs to the
Varopolulos algebra. From this it follows  
that the closed subalgebra of $M({\bf{R}}^n)$
generated by the family $\{L^1(S)\}$ and
$V({\bf{R}}^n))$ yields a
Wiener algebra.
\medskip

\noindent{\bf{3.6 Olofsson's example.}}
Above real analytic strata were used to obtain $\mathcal V^*$. That real-analyticity
is essential was demonstrated  by Olofsson in [Olof]. For example, 
he found a $C^\infty$-function $\phi(x)$ on $[0,1]$ such that if
$\mu$ is the measure in ${\bf{R}}^2$ defined by
\[ 
\mu(f)=\int_0^1\, f(x,\phi(x))\cdot dx
\] 
then $\mu$ has independent powers and it cannot belong  
to any Wiener subalgebra of $M({\bf{R}}^n)$.
Actually [Olofson] constructs similar  examples 
on curves defined by
$C^\infty$-functions outside the
Carleman-Denjoy
class of quasi-anaytic functions.





















\newpage















 







POSTPONE !!


\centerline {\bf{Some specific examples.}}

\medskip




\noindent
General results in functional analysis 
are not always
sufficient for more precise conclusions.
A typical problem is to describe the range of
a bounded linear operator $T\colon X\to Y$
from a Banach space into another.
Consider as an example the Banach space $C^0[0,1]$
of complex-valued
and continuous functions on the closd unit interval and 
the bounded linear operator
 \[
 L_g(x)= \int_0^1\, \log\, \frac{1}{|x-t|}\cdot g(t)\, dt
 \]
whose  operator norm  is bounded above by
 \[
 \max_{0\leq x\leq 1}\,\int_0^1\, \log \frac{1}{|x-t|}\, dt
 \]
Lebesgue  theory teaches that
\[
\lim_{\delta\to 0}\,\max_{x_1,x_2}\,
\int_0^1\, \bigl[\log\, \frac{1}{|x_1-t|}-
 \frac{1}{|x_2-t|}\bigr| \, dt=0
 \] 
 where the maximum for each $\delta>0$ is taken over
 pairs of points in $[0,1]$ for which $|x_1-x_2|\leq\delta$.
 This entails that $L$ maps the unit ball in
 $C^0[0,1$ to 
 an equi-continuous family of functions and as a consequence
 the Arzela-Ascoli theorem implies that $L$ is
 a compact operator.
 It turns out that $L$ is injective and has a 
dense range which contains all $C^2$-functions.
See ¤ xx for the proof  which includes an inversion formula for $L$
which therefore 
describes the range of $L$.
But  this description is rather involved and
the  precise description can onoly be found via the expŒlicit inversion forula which
was established by Carleman and also trewated in work by Zeilon from
the years around 1920.

\medskip
\noindent
{\bf{The Dirichlet problem.}}
Fortunately one is not always obliged to describe the range
in detail.
Consider as an example a bounded open set $\Omega$ in
${\bf{R}}^n$ for some $n\geq 2$. We assume that
the boundary 
 $\partial \Omega$ is a finite union of pairwise disjoint and closed
$C^1$-submanifolds.
Now there exists a bounded linear operator $L$ on
$C^0(\partial\Omega)$ defined by
 \[
 L_g(p)= 
 \int_
{\partial \Omega}\, \frac{g(q)} {|p-q|^{n-2}} \, dA(q)
\]
where $dA$ is the area measure.
If $L$ has a dense reange in $C^0(\partial\Omega)$
the maximum principle for harminic functions
entails that the Dirchlet problem has a solution, i,e. each
continuous boundsry function has a unique harmonic extension to $\Omega$.
Using a result due to F. Riesz which identifiesz the
dual of  $C^0(\partial\Omega)$ with Ruesz measures supported by
$\partial\Omega$, the range of $L$ is dense if
one has proved that if $\mu$ is a Riesz measure on
$\partial\Omega$ such that
\[
 \int_
{\partial \Omega}\, \frac{d\mu(q)} {|p-q|^{n-2}} \quad\colon
p\in \partial\Omega\tag{*}
\]
then $\mu=0$.
This ilustrates the usefulness of arguments basied upon duality.
The proof that (*) gives $\mu=0$
is an easy consequence of Green's formula and
is exposed in ¤ xx.

\medskip

\noindent
{\bf{Non-linear convexity.}}
Let $f(x)$ be a real-valued function in
${\bf{R}}^n$ of class $C^2$.
To every point $x$ we assign the Hessian
$H_f(x)$ which is the symmetric matrix with elements
$\{\partial^2f/\partial x_j\partial x_k\}$.
The function is called strictly convex if $H_f(x)$ is positive for all $x$, i.e. if
the eigenvalues  are all $>0$.
Assume in addition that
\[
 \lim_{|x|\to+\infty}\, f(x)=+\infty\tag{1}
\]
Under these conditions one has the  result
below
which is due to
 Lagrange and Legendre.
 
\medskip

\noindent
{\bf{Theorem.}}
\emph{The function takes its minimum at a unique point in
${\bf{R}}^n$
and the vector valued function}
\[
x\mapsto \nabla_f(x)
\]
\emph{bijective,  i.e. $\nabla_f(p)\neq \nabla_f(q)$
hold for all pairs $p\neq q$ in ${\bf{R}}^n$.}

 \medskip
 
 \noindent
{\bf{Exercise.}}
 Prove this classical result.
 \medskip
 
 \noindent
 With $f$ as in the theorem
 we can  move origin 
 and assume that $f$ takes its mimium at $x=0$.
 Replacing $f$ by $f(x)-f(0)$  the  minimum value is zero.
 To each positive real number
  $s$ we put
 \[
 K_s=\{f\leq s\}
 \] 
 Then $\{K_s\}$ is an increasing sequence of convex
 and compact sets whose boundaries
$\{\partial K_s\}$ are  $C^1$-submanifolds in
${\bf{R}}^n$.
The reader is invited to analyze the ray functions where one for each
point $\omega$ on the unit sphere $S^{n-1}$
studies the function
\[ 
\rho_\omega (s)=r\quad\colon r\cdot \omega\in \partial K_s
\]
The reader should verify that $\rho_\omega$
is a strictly increasing function of
$s$ and it is instructive
to
plot level sets $\{f=a\}$
when $a>0$ for some different $f$-functions as above.

\bigskip

\noindent
{\bf{Cones in ${\bf{R}}^n$}}.
A subset $\Gamma$ is  a cone if 
$x\in\Gamma $ implies that the  half-ray
${\bf{R}}^+\cdot x\subset\Gamma$.
Suppose that $\Gamma$ is a closed set in
${\bf{R}}^n$. Let  $S^{n-1}$ be the 
euclidian  unit sphere and put
\[
\Gamma_*=\Gamma\cap S^{n-1}
\]
We say that $\Gamma$ is \emph{fat} if
$\Gamma_*$ has a non-empty interior in $S^{n-1}$
and
$\Gamma$ is \emph{proper} if 
\[
\Gamma_*\cap -\Gamma_*=\emptyset
\]
The reader may verify that
this is equivalent with the condition that
$\Gamma$ does not contain any 1-dimensional subspace.
We leave it to the reader to verify
that
a cone
$\Gamma$ is proper if and only if
$\widehat{\Gamma}$ is fat.
\medskip

\noindent
{\bf{Dual cones.}}
The \emph{dual cone} is defined by
\[
 \widehat\Gamma=\{x\quad\colon\langle x,\Gamma\rangle\leq 0\}
\]


\noindent
{\bf{Exercise.}} Show the biduality formula, i.e.
that $\Gamma$ is equal to the dual cone of $\widehat\Gamma$.













 

\noindent
{\bf Hilbert spaces.}
An non-degenerate inner product on a complex vector space
$\mathcal H$
is a complex valued function on
the product set
$\mathcal H\times\mathcal H$ which
sends each pair $(x,y)$
into a complex number
$\langle x,y\rangle$  satisfying the following 
three conditions:
\[
x\mapsto\langle x,y\rangle\,\,\text{is a linear form on}\,\,\mathcal H
\,\,\text{for each fixed}\,\, y\in\mathcal H\tag{1}
\]
\[
\langle y,x\rangle=\overline{\langle x,y\rangle}
\quad\colon 
x,y\in\mathcal H\tag{2}
\]
\[
\langle x,x\rangle>0\,\,\text{for all}\,\, x\neq 0\tag{3}
\]


\noindent
Here  (1-3)
imply
that
$\mathcal H$ is equipped with a norm
defined
by
$||x||=\sqrt{\langle x,x\rangle}$ and one easiy verfies that
it satisfies
\[
||x-y||^2+||x+y||^2=
2||x||^2+2||y||^2\tag{*}
\]
Conversely, if (*) holds for a norm
then
it is defined by an inner product where
\[
2\cdot \mathfrak{Re}\,\langle x,y\rangle=
||x+y||^2-||x||^2-||y||^2
\quad\colon
2\cdot \mathfrak{Im}\,\langle x,y\rangle=
||ix+y||^2-||x||^2-||y||^2
\]


\noindent
If a norm given via an inner product
is complete one says that
$\mathcal H$ is a Hilbert space.
A fundamental fact is that  Hilbert spaces are  
\emph{self-dual}. This means that if
$\gamma$ is an element in the dual $\mathcal H^*$, then there exists
a unique vector $y\in\mathcal H$ such that
\[ 
\gamma(x)=\langle x,y\rangle\,\quad\text{for all}\,\, x\in\mathcal H\,.
\]
We prove this in the section devoted to Hilbert spaces.
\bigskip


\noindent
{\bf{Orthonormal bases.}}
If $\mathcal H$ is separable, i.e. contains a denumerable dense subset, then
it is isomorphic to the  Hilbert space
$\ell^2$ whose elements are sequences of complex numbers
$\{c_0,c_1,\ldots\}$ for which
$\sum\, |c_n|^2<\infty$.
However, this does not mean that one has a clear  picture of a Hilbert space
which is given  without a specified orthonormal basis.
So even if all separable Hiolbert spaces are isomorphic one often
needs considerable work to exhibit a sequence" of pairwise
orthogonal vectors to exhibit that $\mathcal H\simeq \ell^2$.
An example occurs when $\mathcal H$ is the Hilbert space of square integrable analytic functions
in a bounded domain in ${\bf{C}}$.
Here one defines Bergman's kernel  function and for simply connected
domains an orthonormal bases given by polynomials was found
by Faber which has consequences in analytic function theory. See
¤ X in Chapter VI for an account.












\noindent
{\bf Hilbert spaces.}
An non-degenerate inner product on a complex vector space
$\mathcal H$
is a complex valued function on
the product set
$\mathcal H\times\mathcal H$ which
sends each pair $(x,y)$
into a complex number
$\langle x,y\rangle$  satisfying the following 
three conditions:
\[
x\mapsto\langle x,y\rangle\,\,\text{is a linear form on}\,\,\mathcal H
\,\,\text{for each fixed}\,\, y\in\mathcal H\tag{1}
\]
\[
\langle y,x\rangle=\overline{\langle x,y\rangle}
\quad\colon 
x,y\in\mathcal H\tag{2}
\]
\[
\langle x,x\rangle>0\,\,\text{for all}\,\, x\neq 0\tag{3}
\]


\noindent
Here  (1-3)
imply
that
$\mathcal H$ is equipped with a norm
defined
by
$||x||=\sqrt{\langle x,x\rangle}$ and one easiy verfies that
it satisfies
\[
||x-y||^2+||x+y||^2=
2||x||^2+2||y||^2\tag{*}
\]
Conversely, if (*) holds for a norm
then
it is defined by an inner product where
\[
2\cdot \mathfrak{Re}\,\langle x,y\rangle=
||x+y||^2-||x||^2-||y||^2
\quad\colon
2\cdot \mathfrak{Im}\,\langle x,y\rangle=
||ix+y||^2-||x||^2-||y||^2
\]


\noindent
If a norm given via an inner product
is complete one says that
$\mathcal H$ is a Hilbert space.
A fundamental fact is that  Hilbert spaces are  
\emph{self-dual}. This means that if
$\gamma$ is an element in the dual $\mathcal H^*$, then there exists
a unique vector $y\in\mathcal H$ such that
\[ 
\gamma(x)=\langle x,y\rangle\,\quad\text{for all}\,\, x\in\mathcal H\,.
\]
We prove this in the section devoted to Hilbert spaces.
\bigskip


\noindent
{\bf{Orthonormal bases.}}
If $\mathcal H$ is separable, i.e. contains a denumerable dense subset, then
it is isomorphic to the  Hilbert space
$\ell^2$ whose elements are sequences of complex numbers
$\{c_0,c_1,\ldots\}$ for which
$\sum\, |c_n|^2<\infty$.
However, this does not mean that one has a clear  picture of a Hilbert space
which is given  without a specified orthonormal basis.
So even if all separable Hiolbert spaces are isomorphic one often
needs considerable work to exhibit a sequence" of pairwise
orthogonal vectors to exhibit that $\mathcal H\simeq \ell^2$.
An example occurs when $\mathcal H$ is the Hilbert space of square integrable analytic functions
in a bounded domain in ${\bf{C}}$.
Here one defines Bergman's kernel  function and for simply connected
domains an orthonormal bases given by polynomials was found
by Faber which has consequences in analytic function theory. See
¤ X in Chapter VI for an account.





\noindent
The determination of
$X^*$  is  often an important issue. An example
is the dual of the normed space
$X=H^\infty(T)$ of bounded Lebesgue measurable functions on the unit circle
which are boundary values of bounded analytic functions in
the open disc $D$. A portion of its dual space
is given by the  quotient space:
\[ 
Y=\frac{L^1(T)}{H\uuu 0^1(T)}\tag{ii}
\]
where $H\uuu 0^1(T)$ is the closed subspace of
$L^1(T)$ whose functions are boundary values of analytic functions in
$D$ which vanish at $z=0$. However, the dual
$X^*$ is considerably larger. In fact, we shall learn that
$H^\infty(T)$ is an example of a commutative Banach algebra
to which we can assign the maximal ideal space
$\mathfrak{M}\uuu X$
and now $X^*$ is the space of Riesz measures on this 
compact space.
But a concrete description of
$\mathfrak{M}\uuu X$ is not known.
Via point evaluations in $D$
it is  clear that $D$ appears as a  subset
of $\mathfrak{M}\uuu X$. 
Its position in 
$\mathfrak{M}\uuu X$ was an open question for
some time, until
Carleson in an article from 1957 proved that
$D$ is a dense  subset. This result is known as the
Corona Theorem whose  proof requires
a deep  analysis 
based upon geometric constructions such as Carleson measures.




\medskip


\centerline{\bf 7.4 Resolvent operators}
\bigskip

\noindent
Let $A$ be a continuous linear operator on a
Banach space $X$.
In XX we defined the spectrum $\sigma(A)$ and proved that
the  resolvent function
\[
R_A(z)=(z\cdot E-A)^{-1}\quad\colon\quad
z\in {\bf{C}}\setminus\sigma(A)\tag{i}
\]


\noindent 
is an analytic function, i.e. the local Neumann series from XX
show that
$R_A(z)$ is an analytic function with values in the
Banach space $Y=\mathcal{L}(X,X)$.
Let us now consider a connected
bounded domain $\Omega\in\mathcal{D}^1({\bf{C}})$
whose boundary $\partial\Omega$ is a union of smooth and closed Jordan curves
$\Gamma_1,\ldots,\Gamma_p$.
Let $f(z)$ be an analytic function in
$\Omega$ which extends to a continuous function on
$\bar\Omega$.
We impose the condition
\[ 
\partial\Omega\cap\sigma(A)=\emptyset\tag{ii}
\]


\noindent
Then we can construct the line integral
\[
\int_{\partial\Omega}\,f(\zeta)\cdot 
R_A(\zeta)\cdot d\zeta\tag{*}
\]
This yields an element of $Y$ denoted by $f(A)$.
Thus, if $\mathcal A(\Omega)$ is the space of analytic functions
with continuous extension to $\bar\Omega$
then (*) gives a map
\[
T_A\colon\,\mathcal{A}(\Omega)\to Y\tag{**}
\]
Let us put
\[ 
\delta=\min\,\{|z-\zeta|\quad\colon\,
\zeta\in\partial\Omega\,\colon\, z\in\sigma(A)\}
\]
By the result in XX there is a constant $C$
which depends on $A$ only such that
the operator norms:
\[
||R_A(\zeta)||\leq \frac{C}{\delta}\quad\colon\quad \zeta\in
\partial\Omega\tag{***}
\]
\medskip

\noindent
From (***) and the construction in (*) we conclude that
the linear operators $T_A(f)$ have norms which are estimated by
\[ 
||T_A(f)||\leq  \frac{C}{\delta}\cdot\ell(\partial\Omega)\cdot
|f|_{\partial\Omega}
\]
where 
$\ell(\partial\Omega)$ is the total arc-length of the boundary.
Hence we have proved:
\medskip

\noindent
{\bf 7.5 Theorem.}
\emph{With $\Omega$ as above there exists  a continuos linear map
$f\mapsto f(A)$ from the Banach space
$\mathcal A(\Omega)$ into $Y$ and one has the norm inequality}
\[
||f(A)||\leq
\frac{C}{\delta}\cdot\ell(\partial\Omega)\cdot |f|_{\partial\Omega}
\]

\medskip

\noindent
Recall  that
the resolvent operators
$R_A(z)$ commute with $A$ in the algebra of linear
operators on $X$.
Since $f(A)$ is obtained by a Riemann sum of 
resolvent operators, it follows that
$f(A)$ commutes with $A$ for every
$f\in\mathcal A(\Omega)$.
At the same time
$\mathcal A(\Omega)$ is a \emph{commutative Banach algebra}.
It turns out that one has a multiplicative formula for 
the operator $T_A\colon f\mapsto f(A)$.
\bigskip

\noindent
{\bf 7.6 Theorem.}
\emph{$T_A$ yields an algebra homomorphism from
$\mathcal A(\Omega)$ into a commutative subalgebra of
$Y$, i.e.}
\[
T_Afg)= T_A(f)\cdot T_A(g)\quad\colon f,g\in\mathcal A(\Omega)
\]


\medskip


\noindent
\emph{Proof.}
In addition to the given domain
$\Omega$ we  construct a slightly smaller domain
$\Omega_*$ which also is bordered by
$p$ many disjoint and closed Jordan curves
$\Gamma^*_1,\ldots,\Gamma^*_p$ where each single
$\Gamma_\nu^*$
is close to
$\Gamma_\nu$ and
$\partial\Omega^*$ stays so close to
$\partial\Omega$ that 
$\bar\Omega\setminus \Omega_*$
does not intersect $\sigma(A)$.
Consider 
pair $f,g$ in $\mathcal A(\Omega)$.
The careful choice of $\Omega_*$
and Cauchy's integral formula
give the equality
\[
g(A)= \int_{\partial \Omega_*}\, g(\zeta_*)\cdot R_A(\zeta_*)\cdot d\zeta_*\tag{i}
\]
where we use $\zeta_*$ as a variable to distinguish from the subsequent integration
along $\partial\Omega$.
To compute $f(A)$ we keep integration on $\partial\Omega$
and obtain
\[
g(A)\cdot f(A)=
\int_{\partial\Omega_*}\int
_{\partial\Omega}\,g(\zeta_*)\cdot f(\zeta)\cdot
R_A(\zeta_*)\cdot R(\zeta)\cdot d\zeta_*d\zeta\tag{ii}
\]
Next we use the Nemann's  equation
\[
R_A(\zeta_*)\cdot R(\zeta)=
\frac{R(\zeta_*)-R(\zeta)}
{\zeta-\zeta_*}\tag{ii}
\]
The double integral in (ii)  becomes a sum of two integrals
\[
C_1=\int_{\partial\Omega_*}\int
_{\partial\Omega}\, g(\zeta_*)\cdot f(\zeta)
\frac{R(\zeta_*)}
{\zeta-\zeta_*}\cdot d\zeta_*d\zeta
\]
\[
C_2=-\int_{\partial\Omega_*}\int
_{\partial\Omega}\, g(\zeta_*)\cdot f(\zeta)
\frac{R(\zeta)}
{\zeta-\zeta_*}\cdot d\zeta_*d\zeta
\]
To find $C_1$ we first perform integration with
respect to
$\zeta$. Since every $\zeta_*$ from
the inner boundary
$\partial\Omega_*$ belongs 
to the domain $\Omega$
Cauchy's formula applied to the analytic function $f$ gives:
\[
f(\zeta_*)=\frac{1}{2\pi i}\int_{\partial\Omega}\,\frac{f(\zeta)d\zeta}{\zeta-\zeta_*}
\]
Inserting this in the double integral defining $C_1$ we get
\[ 
C_1=\frac{1}{2\pi i}
\int_{\partial\Omega_*}
\int_{\partial\Omega_*}\,
f(\zeta_*)g(\zeta_*)\cdot 
R(\zeta_*)\cdot d\zeta_*=T_A(fg)\tag{iii}
\]
\medskip

\noindent
To evaluate $C_2$ we first perform integration along
$\partial\Omega_*$, i.e. we regard:
\[
\int_{\partial\Omega_*}
\frac{g(\zeta_*)}{\zeta-\zeta_*}\cdot d\zeta_*
\]
Here  $\zeta$ stays \emph{outside} the domain
$\Omega_*$ and hence (iv) is zero by Cauchy's vanishing theorem.
So $C_2=0$ and  (iii) gives the equality in
Theorem 7.6.
\bigskip


\noindent
{\bf{7.7 The Banach algebra $\mathcal A$.}}
This is the closed subagebra of $Y$
generated by
$A$ and all the resolvent operators
$R_A(z)$ as $z$ moves outside $\sigma(A)$.
Let $\mathfrak{M}_A$ denote its 
Gelfand space.
\medskip

\noindent
{\bf 7.8 Proposition} \emph{The Gelfand space
$\mathfrak M_A$
can be identified with the compact set
$\sigma(A)$.}
\medskip

\noindent
\emph{Proof.} 
As explained in ¤ XX the points in
$\mathfrak{M}_A$ correspond to
multiplicative
and linear forms on
$\mathcal A$.
Let
$\gamma$ be such a multiplicative
linear functional.
If $\gamma(A)=z_*$ for some complex number
$z_*$
then the $\gamma$-values are determined on all resolvents. In
fact,
this holds since
\[
1=\gamma((\lambda\cdot E-A)R_A(\lambda))=
(\lambda-z_*)\cdot \gamma(R_A(\lambda))
\]
hold when
$\lambda\in{\bf{C}}\setminus \sigma(A)$
Notce that this also entails that
$z_*$ must belong to $\sigma(A)$.
There remains  to show that
for each point $z_*\in\sigma(A)$ there exists
some $\gamma$ such that $\gamma(A)= z_*$.
To prove this we notice that the hypothesis on $z_*$ means that
the operator $z_*\cdot E-A$ is not inverible on $X$.
If $z_*$ is outside the range of the Gelfand transform of $A$ in the
Banach algebra $\mathcal A$, then
$z_*\cdot E-A)$ would be invertible in $\mathcal A$ whuch
gives a contradiction and finishes the proof of
Proposition 7.8.



\bigskip

\noindent
{\bf 7.9 The sup-norm case.}
Suppose that 
$\mathcal A $ is a sup-norm algebra and put $K=\sigma(A)$.
Let $\Omega$
be an open set
$\Omega$ which contains  $K$.
The operational calculus 
gives
an algebra homomorphism
\[
T_A\colon\,\mathcal O(\Omega)\to \mathcal A
\]


\noindent
Let $f\in A(\Omega$.
The spectrum of the $\mathcal A$-element
$f(A) $ is
equal to $f(\sigma(A))$. 
When $\mathcal A$
is  a sup-norm
algebra it follows that
\[
\max_{z\in K}\, |f(z)|=||f(A)||\tag{*}
\]
Above  $\Omega$ is an arbitrary open neighborhood of $K$.
Since $\mathcal A$ is a Banach algebra we can therefore perform
a limit as the open sets $\Omega$ shrink to $K$
and obtain 
an algebra homomorphism  as follows:
We have the sup-norm algebra
$\mathcal H(K)$ which consists of continuous functions on
$K$ which an be uniformly approximated 
on $K$
by analytic functions defined in small open
neighborhoods.
Then (*) yields  an algebra homomorphism
\[ 
T_A\colon\, f\mapsto f(A) \quad\colon\quad f\in\mathcal A(K)
\]
Moreover it is an isometry, i.e.
\[
\max_{z\in K}\, |f(z)|= ||f(A)||
\]
In this way the Banach algebra $\mathcal A$ is identified with
the sup-norm algebra $\mathcal H(K)$.
\bigskip

\noindent
{\bf 7.10 A special  case.}
If $K$ is "thin" one has the equality
\[
\mathcal H(K)=C^0(K)\tag{*}
\]
For example,  Theorem ¤¤ in chapter XX shows that
if the 2-dimensional Lebesgue measure of $K$ is zero then
all continuous functions on $K$ can be uniformly approximated
by rational functions with poles outside $K$ and then (*) holds.
If we also assume that ${\bf{C}}\setminus K$
is connected then Runge's Theorem from ¤¤ XX
shows that
$C^0(K)$ is equal to the closure of analytic polynomials
$P(z)$. So in this case
polynomials in  $A$ generate
a dense subalgebra of $\mathcal A$.
\bigskip





\centerline{\bf{12.2 Positive operators on $C^0(S)$}}

\bigskip

\noindent
Let $S$ be a compact Hausdorff
space and $X$  the Banach space of continuous and
complex-valued functions on $S$.
A linear operator $T$ on $X$ is  positive if
it sends every non-negative and real-valued function $f$ to another  real-valued and
non-negative function.
Denote by $\mathcal F^+$ the family of positive operators
$T$ which satisfy the following: First
\[
\lim_{n\to\infty}\, \frac{1}{n}\cdot x^*(T^nx)=0\tag{1}
\] 
hold for all pairs $x\in X$ and $x^*\in X^*$.
The second condition is that
$\sigma(T)$ is the union of a compact set in a disc
$\{|\lambda|\leq r$ for some $r<1 $, and a 
finite set of points on the unit circle. 
The  final  condition is that
$R_T(\lambda)$
is meromorphic in the exterior disc
$\{|\lambda>r\}$, i.e. it has poles at
the spectral points on the unit circle.








\medskip

\noindent
{\bf{12.2.1. Theorem.}}
\emph{If $T\in\mathcal F^+$ 
then
each spectral value $e^{i\theta}\in \sigma(T)$ is a root of unity.}

\medskip


\noindent
\emph{Proof.}
Frist we prove that $R_T(\lambda)$  has a simple pole at
each  $e^{i\theta}\in \sigma(T)$.
Replacing 
$T$ by  $e^{-i\theta}\cdot T$
it suffices to prove this when
$e^{i\theta}=1$.
If $R_T(\lambda)$ has a pole of order $\geq 2$
at $\lambda=1 $ we know from ¤ XX that there exists $x\in X$ such that
\[ 
Tx\neq  x\quad\text{and}\quad
(E-T)^2\,x=0\tag{i}
\]
This gives  $T^2+x=2Tx$ and by an induction
\[
\frac{1}{n} \cdot T^n x=\frac{1}{n}\cdot x+(E-T)x\quad\colon n=1,2,\ldots\tag{ii}
\]
Condition (1) and (ii) give for each $x^*\in X^*$:
\[ 
0=\lim_{n\to\infty}\, \frac{1}{n}\cdot x^*( T^n x)=\lim_{n\to\infty}\,
x^*(\frac{1}{n}\cdot x+(E-T)x)
\] 
It follows that $x^*(E-T)(x)=0$ and since 
$x^*$ is arbitrary we get   $Tx=x$ which contradicts (i).
Hence
the pole must be simple.
\medskip


\noindent
Next, with $e^{i\theta}\in\sigma(T) $
we have seen that
$R_T$  has a simple pole.
By the general result in ¤ xx there exists
some    $f\in C^0(S)$ which is not identically zero and
\[ 
T(f)=e^{i\theta}\cdot f
\]
Multiplying $f$ with a complex scalar we may assume that
its  maximum norm on $S$ is one and there exists a point $s_0\in S$ such that
\[ 
f(s_0)=1
\]
For each $n\geq 1$ we have a linear functional on
$X$ defined by $g\mapsto T^n(g)(s_0)$ whuch gives a
Riesz measure $\mu_n$ such that
\[
\int_S\, g\cdot d\mu_n=T^n g(s_0)\quad\colon g\in C^0(S)
\]
Since $T^n$ is positive
the integrals in the left hand side are
$\geq 0$ when $g$ are real-valued and non-negative which entails that
the measures $\{\mu_n\}$ are real-valued and non-negative.
For each $n\geq 1 $ we put
\[ 
A_n=\{x\,\colon\, e^{-in\theta}\cdot f(x)\neq 1\}
\]
Since the sup-norm of $f$ is one we notice that
\[ 
A_n=
\{x\,\colon\, \mathfrak{Re}(e^{-in\theta}f(x))<1\}\tag{iii}
\]
Now
\[
0=f(s_0)- e^{-in\theta}\cdot T^n f(s_0)
=\int_S\,[1-e^{-in\theta}f(s)]\cdot  d\mu_n(s)\tag{iv}
\]
Taking real parts we get
\[
0=\int_S\,[1-\mathfrak{Re}(e^{-in\theta}f(s))]\cdot  d\mu_n(s)\tag{v}
\]
By (iii)  the integrand in (v)
is non-negative and since the whole 
integral is zero it follows that
\[
\mu_n(A_n)= \mu_n(\{\mathfrak{Re}(e^{-in\theta}<1\}=0\tag{vi}
\]
Suppose now that
there exists a pair $n\neq m$ such that
\[
(S\setminus A_n)\cap (S_m\setminus A_m)\neq \emptyset\tag{vii}
\] 
A point $s_*$ in this non-empty intersection
gives
\[
1=e^{in\theta}f(s_*)=e^{im\theta}\cdot f(s_*)\implies
e^{in\theta}=e^{im\theta}
\] 
and hence  $e^{i\theta}$ is a root of unity.
$m-n\neq 0$.
So the proof of Theorem 6.1  is finished if we have established the following

\medskip

\noindent
\emph{Sublemma.}
\emph{The sets $\{S\setminus A_n\}$ cannot be pairwise disjoint.}
\medskip

\noindent
\emph{Proof.}
First,  $f$ has maximum norm
and by the above:
\[ 
\int_S\, f\cdot d\mu_n=e^{in\theta}
\]
Hence the total mass $\mu_n(S)$ is at least one.
Next, 
for each $n\geq 2$ we set
\[
\pi_n=\frac{1}{n}\cdot (\mu_1+\ldots+\mu_n)
\]
Since 
$\mu_n(S)\geq 1$  for each $n$ we get 
$\pi_n(S)\geq 1$. Put
\[
\mathcal A=\bigcap\, A_n
\]
Above we proved that $\mu_n(A_n)=0$ hold for every $n$ which gives
\[ 
\pi_n(\mathcal A)=0\quad\colon\, n=1,2,\ldots\tag{*}
\]
Next, when
the sets $\{S\setminus A_k\}$ 
are pairwise disjoint one has 
the inclusions
\[
S\setminus A_k\subset A_\nu\quad\forall\,\nu\neq k
\]
Keeping $k$ fixed it follows that
$\pi_\nu(S\setminus A_k)=0$ for every $\nu\geq 0$.
So when $n$ is large while $k$ is kept fixed we obtain
\[ 
\pi_n(S\setminus A_k))= \frac{1}{n}\cdot \mu_k(S\setminus A_k))\implies
\lim_{n\to\infty}\, \pi_n(S\setminus A_k))=0
\quad\colon k=1,2,\ldots\tag{**}
\]
At this stage we use Lemma xx which shows that 
$R_T(\lambda)$ has at most a simple pole at $\lambda=1$.
With $\epsilon>0$
the Neumann series expansion gives
\[
E+\sum_{k=1}^\infty\,
\frac {T^k}{(1+\epsilon)^k}=
R_T(1+\epsilon))
=\frac{1}{\epsilon} \cdot Q+W(1+\epsilon))
\]
where $W(\lambda)$ is an operator-valued analytic function
in an open disc centered at $\lambda=1$ while $Q$ is a bounded
linear operator on $C^0(S)$.
Keeping $\epsilon>0$ fixed we apply both sides to the identity function
$1_S$ on $S$ and the construction of
the measures $\{\mu_n\}$ gives
\[
1+
\sum_{k=1}^\infty\,
\frac {\mu_k(S)}{(1+\epsilon)^k}=\frac{1}{\epsilon} \cdot Q(1_S)(s_0)+
W(1+\epsilon))(1_S)(s_0)
\]
If $n\geq 2$ is an integer and $\epsilon=\frac{1}{n}$
one gets the inequality
\[
\sum_{k=1}^{k=n}\,
\frac {\mu_k(S)}{(1+\frac{1}{n})^k}\leq
n\cdot |Q(1_S)(s_0)|+|W(1+1/n))(1_S)(s_0)|\leq
n\dot ||Q||+ ||W(1+1/n)||\implies
\]
\[
\frac{1}{n}\cdot\sum_{k=1}^{k=n}\,\mu_k(S)\leq
(1+\frac{1}{n})^n\cdot (||Q||+\frac{ ||W(1+1/n)||}{n}
\]
Since
Neper's constant $e\geq (1+\frac{1}{n})^n$ for every $n$
we find
a constant $C$ which is
independent of $n$ such that
\[
\frac{1}{n}\cdot\sum_{k=1}^{k=n}\,\mu_k(S)\leq C
\]
Hence the sequence $\{\pi_n(S)\}$ is  bounded
and we can pass to a subsequence
which converges weakly to a limit measure $\mu_*$.
For this $\sigma$-additive measure the limit formula in (**) above entails that
\[ 
\mu_*(S\setminus A_k)=0\quad\colon\, k=1,2,\ldots\tag{i}
\]
Moreover, by (*) we also have
\[
\pi_*(\mathcal A)=0\tag{ii}
\]
Now
$S= \mathcal A\cup\, A_k$ so (i-ii) give:
\[ 
\mu_*(S)=0
\]
But this is impossible for at the same time
we have already seen that
$\pi_n(S)\geq 1$ for each $n$ and hence also $\mu_*(S)\geq 1$.









\bigskip
Compact pertubations to finish Kakutani-Yosida !!!



\bigskip



\noindent 
In general, consider some complex Banch space
$X$ be a Banach space and
denote by $\mathcal F(X)$
the family of bounded liner operators  $T$ on $X$  
such that

\[ 
\lim_{n\to\infty}\, \frac{1}{n}\cdot x^*(T^nx)=0\tag{*}
\] 
hold for all pairs $x\in X$ and $x^*\in X^*$.
\medskip


\noindent
{\bf{1. Exercise.}} Apply the Banach-Steinhaus theorem to show that
if $T\in\mathcal F(X)$ then
there exists a constant $M$ such that the operator norms satisfy
\[ 
||T^n||\leq M\cdot n\quad\colon\, n=1,2,\ldots
\]


\noindent
Since the $n$:th root of $M\cdot n$ tends to one as $n\to+\infty$, 
the spectral radius formula entails that
the spectrum $\sigma(T)$ is contained in the closed unit disc
of the complex $\lambda$-plane.
So in the exterior disc
$\{|\lambda|>1\}$ there exists the
the resolvent 
\[ 
R_T(\lambda)= (\lambda\cdot E-T)^{-1}
\]



\noindent{\bf{2. The class $\mathcal F_*$}}.
It consists of those $T$ in $\mathcal F(X)$
for which there exists
some $\alpha<1$ such that
$R_T(\lambda)$ extends to a meromorphic function in
the exterior disc
$\{|\lambda|>\alpha\}$.
Since $\sigma(T)\subset
\{|\lambda|\leq 1\}$
it follows that when
$T\in\mathcal F_*$ then
the set of points in $\sigma(T)$ which belongs to the unit circle
in the complex $\lambda$-plane is empty or finite and
after we can always choose $\alpha<1$ such that
\[ 
\sigma(T)\cap \{\alpha<|\lambda|<1\}= \emptyset
\]

\medskip

\noindent
{\bf{3. Proposition.}}
\emph{If $T\in \mathcal F_*$ andÊ$e^{i\theta}\in \sigma(T)$
for some $\theta$, then Neumann's resolvent
$R_T(\lambda)$ 
has a simple pole at $e^{i\theta}$.}
 \medskip

\noindent
\emph{Proof.}
Replacing
$T$ by  $e^{-i\theta}\cdot T$
it suffices to prove the result when
$e^{i\theta}=1$.
If $R_T(\lambda)$ has a pole of order $\geq 2$
at $\lambda=1 $ we know from ¤ XX that there exists $x\in X$ such that
\[ 
Tx\neq  x\quad\text{and}\quad
(E-T)^2\,x=0\tag{i}
\]
The last equation means that $T^2+x=2Tx$ and an induction
over $n$ gives
\[
\frac{1}{n} \cdot T^n x=\frac{1}{n}\cdot x+(E-T)x\tag{ii}
\]
Since $T\in\mathcal F$ we have
\[ 
\lim_{n\to\infty}\, \frac{1}{n}\cdot x^*( T^n x)=0
\quad\colon\, \forall\\, x^*\in X^*\tag{iii}
\] 
Then (ii) entails that $x^*(E-T)(x)=0$. Since
$x^*$ is arbitrary we get  $Tx=x$ which contradicts (i) and hence
the pole is simple.
\medskip

\noindent
{\bf{4. Theorem.}}
\emph{Let $T\in \mathcal F(X)$ be such that   there exists a compact
operator $K$ where 
$||T+K||<1$. Then $T\in \mathcal F_*$ and
for every $e^{i\theta}\in\sigma(T)$
the eigenspace
$E_T(\theta)= \{ x\in X\,\colon\, Tx= e^{i\theta} x\}$ is finite dimensional.}

\medskip

\noindent
\emph{Proof.}
Set $S=T+K$ and for a complex number
$\lambda$ we write 
$\lambda\cdot E-T= \lambda\cdot E-T-K+K$. Outside $\sigma(S)$ we get
\[
R_S(\lambda)(\lambda\cdot E-T)=
E+R_S(\lambda)\cdot K\tag{i}
\]
The Neumann series for large absolute values
$|\lambda|$
applied to $R_S(\lambda)$ gives some $\rho>0$ and
\[
( E+R_S(\lambda)\cdot K)^{-1}= E+R_S(\lambda)\cdot K\dot
( E+R_S(\lambda)\cdot K)^{-1}\quad\colon\,|\lambda|>\rho\tag{ii}
\]

\noindent
Next, when
$|\lambda|$ is large
we notice that
(i) gives
\[
R_T(\lambda)=  ( E+R_S(\lambda)\cdot K)^{-1}\cdot R_S(\lambda)\tag{iii}
\]
Together with (ii) we obtain
\[
R_T(\lambda)=R_S(\lambda)+ 
R_S(\lambda)\cdot 
( E+R_S(\lambda)\cdot K)^{-1}\cdot R_S(\lambda)\tag{iv}
\]
Set $\alpha=||S||$ which by assumption is $<1$.
Now
$R_S(\lambda)$ is analytic in the exterior disc
$\{\lambda|>\alpha\}$ so in this exterior disc
$R_\lambda(T)$ differs from  the analytic function $R_\lambda(S)$ by
\[
\lambda\mapsto R_S(\lambda)\cdot 
( E+R_S(\lambda)\cdot K)^{-1}\cdot R_S(\lambda)\tag{v}
\]
Here $K$ is a compact operator so 
the
result in ¤ XX entails that this function extends to
be meromorphic  in $\{|\lambda|>\alpha\}$.
There remains to prove that
eigenspaces at spectral points on the unit circle are finite dimensional.
To prove this we use (iv). 
Let $e^{i\theta}\in\sigma(T)$. By Proposition 3 it is a simple pole
so we have a Laurent series expansion
\[
R_T(e^{i\theta}+z)= \frac{A_{-1}}{z}+ A_0+ A_1z+\ldots
\]
By the general results from ¤¤ there remains to show that 
$A_{-1}$ has finite dimensional range.
To see this we apply (iv) which gives the equation
\[
R_S(e^{i\theta}+z)+
R_S(e^{i\theta}+z)\cdot(E+
R_S(e^{i\theta}+z)\cdot K)^{-1}\cdot R_S(e^{i\theta}+z)
\]
To simplify notations we set $B(z)=R_S(e^{i\theta}+z)$
which by assumption is analytic in a neighborhood of $z=0$.
Moreover, the operator $B(0)$ is invertible.
So now one has
\[
 \frac{A_{-1}}{z}+ A_0+ A_1z+\ldots=
 B(z)+B(z)(E+B(z)\cdot K)^{-1}B(z)
 \]
Since $B(0)$ is invertible  we  have a Laurent series expansion
\[
(E+B(z)\cdot K)^{-1}= \frac{A^*_{-1}}{z}+A_0^*+A_1^*z+\ldots
\]
and identying the coefficient of $z^{-1}$ gives
\[
A_{-1}= B(0)A^*_{-1}B(0)
\]
Next, from (xx) one has

\[
E=(E+B(z)\cdot K)(\frac{A^*_{-1}}{z}+A_0^*+A_1^*z+\ldots)\implies
(E +B(0)\cdot K)A^*_{-1}=0
\]
Here $B(0)\cdot K$ is a compact operator and hence  Fredholm theory 
implies that $A^*_{-1}$ has a finite dimensional range. Since
$B(0)$ is invertible the same is true for $A_{-1}$ which finishes the proof
of 
Theorem 4.




\medskip

\noindent
{\bf{5. Proposition}}.
\emph{
If
$T\in\mathcal F$ is  such that
$T^N\in\mathcal F_*$ for some integer $N\geq 2$.
Then 
$T\in\mathcal F_*$.}
\medskip

\noindent
\emph{Proof.}
We have the algebraic equation
\[ 
\lambda^N\cdot E -T^N=(\lambda\cdot E-T)(
\lambda^{N-1}\cdot E+
\lambda^{N-2}\cdot T+\ldots+T^{N_1})
\]
It follows that
\[ R_T(\lambda)=
(\lambda^{N-1}\cdot E+
\lambda^{N-2}\cdot T+\ldots+T^{N_1})\cdot R_{T^N}(\lambda^N)
\]
Since $T^NB\in\mathcal F_*$ there exists
$\alpha<1$ such that
\[
\lambda\mapsto  R_{T^N}(\lambda^N)
\]
extends to be meromorphic in
$\{|\lambda|>\alpha\}$. At the same time
$(\lambda^{N-1}\cdot E+
\lambda^{N-2}\cdot T+\ldots+T^{N_1})$
is  a polynomial
and hence
$R_T(\lambda)$ also extends to be meromorphic
in this
exterior disc so that 
$T\in\mathcal F_*$.




\newpage




\centerline{\bf{12.3 Factorizations of non-symmetric kernels.}}


\bigskip

\noindent
Recall that
the Neumann-PoincarŽ kernel $K(p,q)$ of  a
plane $C^1$-curve $\mathcal C$
is given by
\[ 
K(p,q)= \frac{\langle p-q,{\bf{n}}_i(p)\rangle}{|p-q|}
\]
This kernel function gives the integral operator $\mathcal K$
defined on $C^0(\mathcal C)$ by
\[
\mathcal K_g(p)=\int_C\, K(p,q)\cdot g(q)\, ds(q)
\]
where $ds$ is the arc-length measure on $C$.
Let $M$ be a positive number which exceeds the diameter of 
$\mathcal C$
so that
$|p-q|<M\,\colon\, p,q\in\mathcal C$.
Set
\[
N(p,q)= \int_\mathcal C\, 
K(p,\xi )\cdot \log\,\frac{M}{|q-\xi|}\cdot ds(\xi)
\]



\noindent
{\bf{Exercise.}} Verify that
$N$ is symmetric, i.e. $N(p,q)= N(q,p)$
hold for all pairs $p,q$ in $\mathcal C$.
Moreover, 
\[ 
S(p,q)=\log\, \frac{M}{|p-q|}
\] 
is a symmetric and positive kernel function
and since $\mathcal C$ is of class $C^1$ the reader should verify that it gives a
Hilbert-Schmidt kernel, i.e.
\[ 
\iint_{\mathcal C\times\mathcal C}\,
S(p,q)^2\, ds(p)ds(q)<\infty
\]





















\end{document}




