









\documentclass{amsart}



\usepackage[applemac]{inputenc}
\addtolength{\hoffset}{-12mm}
\addtolength{\textwidth}{22mm}
\addtolength{\voffset}{-10mm}
\addtolength{\textheight}{20mm}

\def\uuu{_}

\def\vvv{-}

\begin{document}




A pair of $n$-tuples $(a_1,\ldots,a_n)$ and
$(b_1,\ldots,b_n)$ where $a_k<b_k$ hold for each $k$, give 
the open rectangle
\[
\square(a_\bullet,b_\bullet)=
\{x=(x_1,\ldots,x_n)\,\colon\, a_k<x_k<b_k\}
\]
Its $n$-dimensional volume is defined as
the product of the differences $\{b_k-a_k\}$, i.e.
\[
\text{vol}_n(\square(a_\bullet,b_\bullet))=
\prod\, (b_k-a_k)\tag{0.1}
\]
Starting from this, Lebegue introduced the family of 
\emph{null sets}.
By definition a subset $A$ in ${\bf{R}}^n$ is a null set of there to
every $\epsilon>0$ exists some
denumerable  family of open cubes
$\{\square_\nu\}$
whose  union contains $A$ while
\[
\sum\, \text{vol}_n(\square_\nu)<\epsilon
\]
Keeping $n$ fixed the family of null-sets in
${\bf{R}}^n$ is denoted by $\mathcal N$.
In Lebesgue theory one  identifies various object which only
differ an a null set.
For example, a pair of real-valued functions $f$ and $g$
defined in ${\bf{R}}^n$ are said to be \emph{equal almost everywhere}
if they only take distinct values on a null set.











Inspired by Lebegue's notion of null set,
a more general notion of thin sets was introduced by Hausdorff in 1907.
Given a postive number
$0<\alpha<n-1$ one says that a set $A$ in ${\bf{R}}^n$
has
Hausdorff dimension zero of or order $\alpha$
if there to every $\epsilon>0$ exists some denumerable family of open cubes
$\{\square _\nu\}$ whose union contains $A$ while
\[ 
\sum\,
\text{vol}_n(\square_\nu)^\alpha<\epsilon
\]
The family of sets $A$ for which
this holds is denoted by $\mathcal N_\alpha$.
The reader can check that
\[
0<\alpha<\beta\implies \mathcal N_\alpha\subset\mathcal N_\beta
\]
In ¤ xx we prove  Stokes Theorem for bounded open subsets 
$\Omega$ in
${\bf{R}}^n$ where the boundary  $\partial\Omega$ satiosfies 
a certain regularity  condition expressed via Hausdorff dimensions
of order $n-1$.
Further familes of "thin sets" appear 
with important applications.
Consider for example a closed subset $E$ of the unit circle $T$.
If $0<t\leq 1 $ we get the open subset $E(t)$ in $T$ whicoh
consists  of points $e^{i\theta}$ such that
\[
\min_{e^{i\alpha}\in E}\, |e^{i\theta}-e^{i\alpha}|<\delta
\]
The 1-dimensional Lebegue theory gives the function
\[
\phi_E(t)=\text{vol}_1(E(t))
\]
Now $t\mapsto \phi_E(t)$
is a continuous   function on of $t$.
Here $E$ is a null set in the sense of Lebesgue if and only if
$\phi_E(t)\to 0$ as $t\to 0$.
We can impose the stronger condition that
the integral 
\[
\int_0^1\, \frac{\phi_E(t)}{t}\, dt<\infty
\]








\newpage



\centerline{\bf{Lebesgue theory.}}
\bigskip



\noindent
The theory was  created    by Henri Lebesgue 
in his monograph
\emph{Lecons sur l'integration et la recherche
des fonctions primitives} from 1904. Let us  also 
remark
that 
Vitali and de la VallŽ Poussin
later found  some simplifications of Lebesgue's original proofs.
We shall work in   euclidian   spaces ${\bf{R}}^n$ where $n$ is some positive integer
and points are $x=(x_1,\ldots,x_n)$.
Keeping $n$ fixed we
construct partitions of ${\bf{R}}^n$ as follows:
\medskip

\noindent
{\bf{0.1 Dyadic grids.}}
For each non-negative  integer $N$
we consider the family $\mathcal D_N$  of
cubes:
\[
\square_N(k_\bullet)=
\{ x\colon\, k_\nu\cdot 2^{-N}\leq x_\nu<(k_\nu+1)\cdot 2^{-N}\}\tag{0.1.1}
\]
where $k_\bullet=(k_1,\ldots,k_n)$ are $n$-tuples of integers.
Then 
\[
\{\square_N(k_\bullet)\}\quad\colon\, k_\bullet \in {\bf{Z}}^n
\]
are pairwise disjoint subsets of
${\bf{R}}^n$ whose union taken over all 
$k_\bullet\in {\bf{Z}}^n$
is equal to ${\bf{R}}^n$.
Notice that
every
cube in $\mathcal D_N$ is the disjoint union of
$2^n$ many cubes from
$\mathcal D_{N+1}$.
\medskip

\noindent
Let us now consider a bounded open subset
$\Omega$ of ${\bf{R}}^n$, i.e $\Omega$ is open and
contained in some ballÊ$\{|x|<r\}$
of radius $r$ centered at the origin.
Denote by $\mathcal D_1(\Omega)$ the family of cubes
from
$\mathcal D_1$ which are contained in
$\Omega$.
In  the next step, $\mathcal D_2(\Omega)$
is the family  of cubes  $\square\in \mathcal D_2$ which are
disjoint from the union of cubes in $\mathcal D_1(\Omega)$.
By induction we get 
a sequence $\{\mathcal D_k(\Omega)\,\colon\, k=1,2,\ldots\}$, where
$\mathcal D_{k+1}(\Omega)$ consists of cubes in
$\mathcal D_{k+1}$ which 
are contained in $\Omega$ and  disjoint from the union of  cubes taken from
$\mathcal D_1(\Omega),\ldots,\mathcal D_k(\Omega)$.
\medskip

\noindent
Now the   union of all cubes 
from  $\{\mathcal D_k(\Omega)\,\colon\, k=1,2,\ldots\}$ is equal to
$\Omega$. 
To see this we pick a point $x\in\Omega$. 
For every $k\geq 0$ the grid of degree $N$ gives a unique
cube $\square_k(x)\in \mathcal D_N$ which contains $x$.
Next, since $\Omega$ is bounded
the reader can check that there exists a \emph{unique smallest integer} $N$ such that
\[
\square_N(x)\subset\Omega
\]
and then the construction above entails that
$\square_N(x)$ appears in the family $\mathcal D_N(\Omega)$.
For every $k\geq 0$
we denote by $\rho_k(\Omega)$  the number of cubes in the family 
$\mathcal D_k(\Omega)$.
The $n$-dimensional volume of $\Omega$ is defined by
\[
\text{vol}_n(\Omega)=\sum_{k=1}^\infty\,
\rho_k(\Omega)\cdot
2^{-kn}\tag{0.1.2}
\]
We can express the series
in another  way.
For every $m\geq 1$ we denote by 
$\rho^*_m(\Omega)$ the number of cubes in
$\mathcal D_m$ which are contained in
$\Omega$.
The reader may check that 
\[
\rho^*_m(\Omega)\cdot 2^{-mN}=\sum_{k=1}^{k=m}\,
\rho_k(\Omega)\cdot 2^{-kn}\implies
\]
\[
\text{vol}_n(\Omega)= \lim_{m\to\infty}\, \rho^*_m(\Omega)\cdot 2^{-mn}\tag{0.1.3}
\]
\medskip

\noindent
{\bf{Example.}}
A pair of $n$-tuples $(a_1,\ldots,a_n)$ and
$(b_1,\ldots,b_n)$ where $a_k<b_k$ hold for each $k$, give 
the open rectangle
\[
\square(a_\bullet,b_\bullet)=
\{x=(x_1,\ldots,x_n)\,\colon\, a_k<x_k<b_k\}
\]
Then its $n$-dimensional volume is 
given by the product
\[
\text{vol}_n(\square(a_\bullet,b_\bullet))=
\prod\, (b_k-a_k)\tag{0.1.4}
\]
To see this one uses binary expansions  of real numbers.
Given a pair $a<b$ and a positive integer $N$
chosen so large that $2^{-N}< b-a$ we find
a pair of   integers  $k_*(N)<k^*(N)$
so that
\[
(k_*(N)-1)\cdot 2^{-N}\leq a< k_*(N)\cdot 2^{-N}
\quad\colon\quad k^*(N)2^{-N}<b\leq (k^*(N)+1)2^{-N}
\]
We leave as an exercise to check that
these binary expansions of real numbers entail that
the volume of $\square(a_\bullet,b_\bullet)$ from (0.1.4) is equal to that
defined by (0.1.3)..

\bigskip


\noindent
{\bf{0.2 The Lebesgue measure of compact sets.}}
For each non-negative  integer $N$ we have  the family 
$\overline{\mathcal D}_N$
of
closed dyadic 
cubes
\[
\overline{\square}_N(k_\bullet)=
\{ x\colon\, k_\nu\cdot 2^{-N}\leq x_\nu\leq (k_\nu+1)\cdot 2^{-N}\}
\]
Let $E$ be a compact subset of ${\bf{R}}^n$.
If $N\geq 0$ we denote by
$\rho^*_N(E)$ the number of closed cubes
in
$\overline{\mathcal D}_N$ which have
\emph{a non-empty intersection} with $E$.
\medskip

\noindent
{\bf{Exercise.}}
Show that the sequence
\[
N\mapsto \rho^*_N(E)\cdot 2^{-Nn}
\]
is a non-increasing function of $N$.
Since every non-decreasing seque ce of positive real numbers have a limit
there exists the number
\[
\lim_{N\to\infty}\, 
\rho^*_N(E)\cdot 2^{-Nn}\tag{0.2.1}
\]
Following de Valle Poussin this limit is denoted by
$\text{vol}_n(E)$ and called the $n$-dimensional Lebesgue measure of
the compact  set $E$.


\medskip

\noindent
{\bf{0.3 Some limit formulas.}}
Let $\Omega$ be a bounded open set.
The positive series (0.1.2) converges so if $\epsilon>0$ we find an integer $N$ such that
\[
\text{vol}_n(\Omega)<\epsilon+ \sum_{k=1}^{k=N}\,
\rho_k(\Omega)\cdot
2^{-kn}\tag{i}
\]
Next,  each $1\leq k\leq N$ gives  the finite family
$\mathcal D_k(\Omega)$. If $0<a<1$
and $\square\in \mathcal D_k(\Omega)$
we construct the compact cube
$\overline{a\cdot \square}$ as in (xxx) above.
The union of cubes $\{\overline{a\cdot \square}\}$
taken from the families
$\mathcal D_1(\Omega),\ldots,\mathcal D_N(\Omega)$
is a compact subset of $\Omega$ denoted by $K_N(a)$,
Now one has 
\[
\text{vol}_n(K_N(a))=a^n\cdot 
\sum_{k=1}^{k=N}\,
\rho_k(\Omega)\cdot
2^{-kn}>a^n\cdot (\text{vol}_n(\Omega)-\epsilon)\tag{ii}
\]
Above $\epsilon>0$ is arbitrary and $a$ can be chosen arbitrary close to one.
From this the reader can check that 
\[
\text{vol}_n(\Omega)= \sup_{K\subset \Omega}\, \text{vol}_n(K)\tag{0.3.1}
\]
with the supremum taken over compact subets of $\Omega$.
\medskip


\noindent
{\bf{0.3.2 Exercise.}}
Deduce from the above that if
$E$ is a compact et and $\Omega$ some bounded open set which contains
$E$, then
\[
\text{vol}_n(\Omega)=\text{vol}_n(\Omega\setminus E)+\text{vol}_n(E)\tag{i}
\]
Show also that
\[
\text{vol}_n(E)=\inf_{E\subset \Omega}\,\text{vol}_n(\Omega)\tag{ii}
\]
where the infimum now is taken over open sets which contain
$E$.
In partocular, put
\[
E(\delta)= \{x\,\colon\, \text{dist}(x,E)<\delta\}\tag{iii}
\]
Then $\{E(\delta)\}$
are open sets and from (ii) the reader should check that
\[
\text{vol}_n(E)=\lim_{\delta\to 0}\, \text{vol}_n(E(\delta))\tag{iv}
\]


\newpage


\centerline{\bf{0.5 Lebesgue measurable sets.}}

\bigskip

\noindent
Let $A$ be a  bounded subset   of ${\bf{R}}^n$.
The  outer measure is defined by:
\[
|A|^*= \inf_{A\subset \Omega}\, \text{vol}_n(\Omega)
\]
where the infimum is taken over open sets containing $A$.
The inner
measure 
is defined by
\[
|A|_*= \sup_{E\subset A}\, |E|^*
\] 
where the supremum is taken over compact subsets of $A$.
\medskip

\noindent
{\bf{0.4.1  Definition.}}
\emph{A bounded set $A$ is Lebesgue measurable if}
\[
|A|_*=|A|^*
\]
\emph{and then this common number
is denoted by
$|A|_n$ and called the Lebesgue measure of $A$.}
\medskip

\noindent
{\bf{0.4.2 $\sigma$-additivity.}}
Let $\{A_\nu\}$ be a denumarable sequence of pairwise disjoint and 
measurable sets which all are contained in some ball $\{|x|<r\}$.
Then their union is measurable and one has the equality
\[
|\cup\, A_\nu|_n= \sum\, |A_\nu|_n\tag{*}
\]
To prove (*) one proceeds as follows: Let
$\epsilon>0$. For every $\nu$ we can find an open set $U_\nu$ which contains
$A_\nu$ while
\[
|U_\nu|_n< |A_\nu|_n+2^{-\nu}\cdot \epsilon
\]
Now $\Omega=\cup\, U_\nu$ is an open  set which contains
$\cup\, A_\nu$ and hence 
\[
|\cup \, A_\nu|^*\leq |\Omega |_n\leq \sum\, |U_\nu|_n<
\sum\, |A_\nu|_n+\epsilon\tag{i}
\]
Next, for each $\nu$ we find a compact subset $K_\nu$ of $A_\nu$ such that
\[
|A_\nu|_n<|K_\nu|_n+2^{-\nu}\cdot \epsilon\tag{ii}
\]
For every $N\geq 1$ 
$K_1\cup\ldots\cup K_N$ is a compact subset of
$\cup\, A_\nu$ which gives
\[
|\cup A_\nu|_*\geq \sum_{nu=1}^{\nu=N}\, |K_\nu|_n\tag{iii}
\]
where we used the additivity in (¤ xx) applied to the pairwise
disjoint compact sets $\{K_\nu\}$.
From (ii) and (iii) we see that
\[
\sum_{nu=1}^{\nu=N}\, |A_\nu|_n<|\cup A_\nu|_*+\epsilon\tag{iv}
\]
Here (iv) hold for every $N$ and hence 
\[
\sum_{nu=1}^\infty \, |A_\nu|_n<|\cup A_\nu|_*+\epsilon\tag{v}
\]
Since $\epsilon$ can be arbitrary small we conclude that 
(i) and (v)   give  (*).




\bigskip


\centerline {\bf{0.5 Lebesgue points.}}
\medskip

\noindent
Let $A$ be a bounded and measurable set.
For each $x\in A$ and every $\delta>0$ we 
put
\[
A_\delta(x)=\min_{\square}\, \frac{\text{vol}_n(A\cap \square)}{
\text{vol}_n(\square)}
\]
where the minimum is taken over all open cubes
which contain  $x$ and have  volume $\leq \delta^n$.
Keeping $x$ fixed the 
reader can check that the function 
\[
\delta\mapsto A_\delta(x)
\]
is non-decreasing. Following Lebesgue we put
\[
\mathfrak{Leb}(A)= \{ x\in A\,\colon\,
\lim_{\delta\to 0} A_\delta(x)=1\}\tag{0.5.1}
\]
A major result due to Lebesgue asserts that
\[
A\setminus\mathfrak{Leb}A)\in \mathcal N\tag{0.5.2}
\]
\medskip

\noindent
To prove (0.5.2 )
we need  a \emph{Covering Lemma} due to Vitali which goes as follows:
Let $\Omega$ be a bounded open set in
${\bf{R}}^n$ and $\mathcal V=\{\square_\alpha\}$
a family of open cubes contained in
$\Omega$. Then one constructs a sequence
of cubes form $\mathcal V$ as follows:
Put
\[
\rho_1=\max_{\square\in \mathcal V}\,\text{vol}_n(\square)
\]
and pick $\square^*_1$ so that is volume is $>2\rho_1/3$.
In the next step
\[
\rho_2=\max_{\square\in \mathcal V[1]}\,\text{vol}_n(\square)
\]
where $\mathcal V[1]$ is the family of cubes from
$\mathcal V$  which are disjoint from
the closed cube
$\overline{\square}_1$.
Pick $\square^*_2$ in this family so that
\[ 
\text{vol}_n(\square^*_2)>2/3\cdot \rho_2
\]
One continues by induction, i.e. after $k$
steps we have found
cubes $\square^*_1,\ldots,\square_k^*$ where
the closed cubes are disjoint  and
then
\[
\rho_{k+1}=\max_{\square\in \mathcal V[k]}\,\text{vol}_n(\square)
\]
where $\mathcal V[k]$ is the family of $\mathcal V$-cubes which
are contained in  open complement of
$\overline{\square}_1^*\cup\ldots\cup\,\overline{\square}^*_k$.
\medskip

\noindent
Since the $\mathcal V$-cubes stay in a fixed bounded set it is clear that
\[
\lim_{k\to \infty}\, \rho_k=0
\]
Next, for  every positive integer $N$
we put 
\[
S_N= \overline{\square}_1^*\cup\ldots\cup\overline{\square}^*_N\bigcup_{\nu>N}
3\cdot \square_\nu^*
\]
where $3\cdot \square_\nu^*$ denote the cubes with
the same center
as
$\square^*_\nu$ while the sides are three times larger.
It is clear that the sets $\{S_N\}$ decrease with $N$ and we put
\[
S_*=\cap\, S_N
\]
\medskip

\noindent
{\bf{0.5.3 Definition.}}\emph{
Let $\mathcal V$ be a family of open cubes as above.
A point $x\in\Omega$ is said to be covered by
$\mathcal V$ in the sense of Vitali if there for every
$\epsilon>0 $ exists a cube $\square\in \mathcal V$
whos  volume is $<\epsilon$ and $x\in \square$.}

\medskip

\noindent
{\bf{0.5.4 Vitali's covering theorem.}}
\emph{The set of points which are covered by
$\mathcal V$ in Vitali's sense is contained in the set $S_*$.}
\medskip

\noindent
\emph{Proof.}
Let $x$ be  covered in Vitali's sense.
We must show that $x\in S_N$ for every positive integer.
If $x$ already belongs to
$\overline{\square}_1^*\cup\ldots\cup\overline{\square}^*_N$
we are done.
If $x$ is outside this set
the assumption that it is covered in Vitali sense gives a small open
cube
$\square\in \mathcal V$ such that 
\[ 
x\in \square\quad\&\quad \square\in\mathcal V[N]
\]
Next , since the $\rho$-numbers above  tend to zero
it follows that
$\square$ cannot belong to  $\mathcal V[M]$ for every $M>N$, 
and we find the \emph{smallest} integer $M\geq N$ such that
\[
\square\in\mathcal V[M]\quad\&\quad \square\cap \square_{M+1}^*\neq\emptyset\tag{i}
\]
The first inclusion in (i) entails that
\[
|\square|_n \leq \rho_{M+1}\implies
\text{vol}_n(\square_{M+1}^*)>2/3\cdot |\square|_n\tag{ii}
\]
At the same time
we have the non-empty intersection in (i) and by drawing a figure the reader can
check that (ii) entials that
\[
\square\subset 3\cdot \square_{M+1}^*\tag{iii}
\]
The consgruction of $S_N$ means that (iii) gives
\[
\square\subset S_N
\]
and since $x$   belongs to $\square$
we have proved  the requested inclusion $x\in S_N$.

\bigskip

\centerline{\bf{0.5.5 Proof of Lebegue's theorem.}}
\bigskip

\noindent
Let $A$ be a bounded and measurable  set.
Fix some $0<\rho<1$ and for every $\delta>0$ we put
\[
S_\delta=\{x\in A\,\colon\, A_\delta(x)<\rho\}\tag{i}
\]
We leave it to the reader to show that
$S_\delta$  is a relatively open subset of $A$, i.e.
\[
S_\delta= A\cap\, U_\delta\tag{ii}
\]
hold for some open set $_\delta$.
In particular $S_\delta$ is measurable
and we also notice that these sets
decrease with $\delta$. It follows from (¤ xx) that
\[
S_*=\bigcap_{\delta>0}\, S_\delta
\]
is measurable.
We shall prove that $S_*$ is a mull set.
To obtain this we consider some
$\epsilon>0$ and find an open set $\Omega$ which contains
$S_*$ while
\[
|\Omega|_n<|S_*|_n+(1-\rho)\cdot \epsilon\tag{iii}
\]
Next, consider a point  $x\in S_*$.
We find  $\delta>0$ such that every 
open cube  which contains $x$  and has volume
$<\delta^n$  is contained in $\Omega$.
The construction of $S_\delta $ gives
therefore an open cube $\square$ which contains $x$ where
\[
\square\subset \Omega\quad\&\quad
\text{vol}_n(A\cap \square)\leq \rho\cdot |\square |_n\tag{iv}
\]
Let $\mathcal V$ be the family of such open cubes.
If $x\in S_*$
we can find $\square$-cubes as above where
$\delta0$ is arbitrary  small. Hence each 
$x\in S_*$ is covered by $\mathcal V$ in the sense of Vitali.
Vitali's Theorem gives therefore 
sequence of pairwise disjoint cubes $\{\square_\nu\}$
in $\mathcal V$ such that
\[
S_*= \overline{\square}_1^*\cup\ldots\cup\overline{\square}^*_N\bigcup_{\nu>N}\tag{v}
3\cdot \square_\nu^*
\]
hold for every $N\geq 1$.  
Since $S_*\subset A$
it   follows from  (v) and $\sigma$-additivity that
\[
|S_*|_n\leq \sum\, |\overline{\square}^*_\nu\cap A|_n
\leq \rho\cdot  \sum\, |\overline{\square}^*_\nu |_n\leq \rho\cdot |\Omega|_n\tag{vi}
\]
where the last inequality holds because the cubes
$\{\square^*_\nu\}$ are disjoint.
Togehter  (iii) and (vi) give 
\[
(1-\rho)\cdot |S_*|_n<\rho\cdot (1-\rho)\cdot \epsilon
\]
Since $\rho<1$ this entails that
\[
 |S_*|_n<\epsilon
\]
Here $\epsilon>0$ was arbitrary  which proves that 
$S_*$ is a null set.
Finally, from (i) the set $S_*$ depends on $\rho$ and let us denote it by
$S_*(\rho)$. Put
\[
S^*=\bigcup_{m\geq 2}\, S_*(1-1/m)
\]
B y ¤ xx this denumerable union is again a null set, and
at this stage the reader can check that
the previous constructions give the inclusion
\[
A\setminus S^*\subset \mathfrak {Leb}(A)
\]
and  Lebegue's Theorem follows.



\newpage







We prove (0.xx)  in ¤ xx 
and  establish also  a similar result for 
Lebesgue measurable sets, and more generally  bounded
Lebesgue measurable  functions.
A consequence of this is that 
every bounded
Lebesgue measurable function $f$ is 
the pointwise limit outside a null set of 
a sequence of Lipschitz continuous functions
defined by mean values of  $f$ over smaller and smaller cubes
centered at the point where  pointwise
convergence takes place.
In ¤ 3.xx we also show that
outside a null set an arbitrary bounded
measurable
function
$f$ differs from an everywhere defined function
$f_*$ given as the pointwise limit of
a
non-increasing sequence of upper semi-continuus functions. This 
means that $f_*$ belongs to the second Baire class of functions. So
when one agrees to identify Lebegue measurable
functions which are equal  outside a null set, then
this class is reduced to a quite  restricted family of everywhere
defined functions.
Roughly  speaking, the existence of Lebesgue points
implies
that  no "phantoms" occur in
Lebesgue theory.



\medskip

\noindent
{\bf{0.2.9 Non-measurable sets.}}
There exist
non-measurable sets.
One must apply  
the Axiom of Choice to exhibit examples.
Using this axiom there exists a subset
$E$ of  the open interval $(0,1)$ with the property
that the
sets $\{E+ q\}$ are disjoint when $q$ runs over the set 
of rational numbers ehile
\[
(0;1)\subset \bigcup_{q\in Q}\, E+q
\]
Now $E$ cannot  be measurable. 
Namely, sincr the right hand side is
a union of denumerable sets and the lebegue measure of $E+q$Êis equal to that of $E$, it would first follow that
\[
\text{vol}_1(E)>0
\]
But this gives a contradiction. Namely, 
the disjointness would entail that if $q_1,\ldots,q_N$ is a set of rational numbers
between 0 and 1 then
\[
N\cdot \text{vol}_1(E)=
\sum_{\nu=1}^{\nu=N}\,\text{vol}_1(E+q_\nu)\leq 2
\]
where the last equality holds since
every  set $E+q_\nu\subset [0,2]$.
Since $N$ can be arbitrary large we must have 
\[
\text{vol}_1(E)=0
\]
and from this we conclude that
$E$ cannot be measurable,

\ bigskip





\newpage







\noindent
{\bf{0.2.1 Unbounded open sets.}}
If $\Omega$ is an open unbounded set
we still get the unique partition 
formed by the disjoint subsets $\{D_k(\Omega)\}$.
One says that
$\Omega$ has a finite measure if
every 
$D_k(\Omega)$ is a finite union  and the series
\[
\sum\, \mu_k(\Omega)\cdot 2^{-kn}<\infty
\]

\medskip

\noindent
{\bf{Outer and inner measures.}}
Starting from the construction of $n$-dimensional measures
of  open sets one 
constructs  outer and inner measures of an
arbitrary bounded subset $A$  of ${\bf{R}}^n$.
The  outer measure is defined by:
\[
|A|^*= \min_{A\subset \Omega}\, \text{vol}_n(\Omega)
\]
In particular the outer measure 
is defined for every compact set $E$ and the inner measure of
$A$ is defined by
\[
|A|_*= \max_{E\subset A}\, |E|^*
\] 
where the maximum is taken over compact subsets of $A$.
\medskip

\noindent
{\bf{0.2.2 Definition.}}
\emph{A set $A$ in 
 ${\bf{R}}^n$ has a finite Lebesgue measure 
if
$|A|_*=|A|^*<\infty $ and this common number
is denoted by
$|A|_n$.}
\medskip

\noindent
{\bf{0.2.3 Null sets.}}
A  set is called a null set if
its outer measure is zero. The family of 
null sets is denoted
by
$\mathcal N({\bf{R}})^n$.
A property is said to hold almost everywhere if it is valid
outside a null set.
In Lebesgue theory one 
is often content to establish a result "almost everywhere", i.e.
null sets are reduntant.
Recall that a  set
$S$ is of type $G_\delta$ if it is
the intersection  of an decreasing sequence of open
sets $\{\Omega_n\}$. It is a set of type $F_\sigma$ if it is given
as the union of a decreasing familly of compact
sets.
\medskip

\noindent
{\bf{0.2.4 Exercise.}}
Show that if $A$ is  Lebesgue   measurable 
and
$\{E_\nu\}$ an increasing sequence of compact subsets such that
$|E_\nu|_n\to |A|_n$,
then $A\setminus \cup\, E_\nu$ is a null-set. Similarly, if
$\{\Omega_\nu\}$ an decreasing sequence of open sets
containing $A$ and
$|\Omega_\nu|_n\to |A|_n$ then
$\cap\, \Omega_\nu\setminus A$ is a null set.
Hence every measurable
set differs from
a set of type $F_\sigma$ by a null set, and similarly from
a set of type $G_\delta$.
\medskip

\noindent
{\bf{0.2.5 Lebesgue points.}}
Let $A$ be a  measurable set.
A point $x\in A$ has unit   density 
if
\[
\lim_{|\square|_n\to 0}\,
\frac {\text{vol}\uuu n(\square\setminus A)}{\text{vol}\uuu n(\square)}=0\tag{0.5.1}
\]
where 
the limit  is taken over
cubes which contain $x$.
It is not requested
that $x$ is the center of the cubes
and their sides need not be
parallell to the coordinate
axis.
The set  where  (0.5.1) holds is denoted by
$\mathfrak{Leb}(A)$.
A major result due to  Lebesgue 
asserts the following:
\medskip

\noindent
{\bf{0.2.6 Theorem.}}
\emph{For  every  measurable set $A$
it follows that
$A\setminus \mathfrak{Leb}(A)$ is a null set.}
\medskip

\noindent
This fundamental  result is proved in ¤ 3.
\medskip

\noindent
{\bf{0.2.7 Measurable functions.}}
Let $f(x)$ be a real-valued function defined in some open and bounded
subset
$\Omega$ of
${\bf{R}}^n$.
It is  measurable in the sense of Lebesuge if the sets
\[
A_f(a;b)= \{ x\in\Omega\colon a\leq f(x)<b\}
\]
are measurable for all pairs of real numbers $a<b$.
The function $f$ has  Lebesgue value $a$ at a point
$x_0\in\Omega$ if
\[
\lim_{|\square|_n\to 0}\, \frac{|A_f(a-\epsilon,a+\epsilon)\cap \square|_n}
{|\square|_n|}=1\tag{0.7.1}
\]
hold for every $\epsilon>0$ where the limit of cubes is taken as in (0.5.1).
It is obvious that if (0.7.1)
hold for some
real number $a<$,
then it is uniquely determined and we set
$\mathfrak{Leb} f(x_0)=a$.
In ¤ xx we show that
 the measurable function $f$ has a Lebesgue value almost everywhere.
 More preciely, there exists a
null set $W$
of
$\Omega$ such that 
 $\mathfrak{Leb} f$ is defined in
$\Omega\setminus W$ and is equal to
$f$ in this set.
So up  to null sets every measurable function
$f$
is recaptured from its Lebesgue function, i.e.
ignoring a null set
$f$ can always be chosen so that
its values coincide with its Lebesgue values.
\medskip


\noindent
{\bf{0.2.8 Fubini's theorem.}}
Let $n$ snd $m$ be a pair of positive integers and 
$A$  a bounded and measurable subset of
${\bf{R}}^{n+m}$
whose points are written as $(x,y)$ with
$x\in {\bf{R}}^n$ and $y\in {\bf{R}}^m$.
To every $x$ we get the slice
\[
A(x)= \{ y\colon (x,y)\in A\}
\]
In ¤¤ we prove that
$A(x)$ are measurable sets in
${\bf{R}}^m $ for all $x$ outside a null set and
the almost everywhere defined function
\[
x\mapsto |A(x)|_m
\]
is measurable. After we have learnt how to construct
Lebegue integrals we also prove  the equality
\[
\int_{{\bf{R}}^n}\,  |A(x)|_m\, dx= |A|_{n+m}\tag{0.8.1}
\]







\medskip

\noindent
{\bf{0.2.9 Non-measurable sets.}}
There exist
non-measurable sets but in 
practice one does not encounter these ugly sets. In fact, one must appeal to
the Axiom of Choice to exhibit examples.
Using this axiom there exists a subset
$E$ of  the open interval $(0,1)$ with the property
that the
sets $\{E+ q\}$ are disjoint when $q$ runs over the set 
of rational numbers.
This set cannot be measurable. The reason is that
the disjointness would entail that if $q_1,\ldots,q_N$ is a set of rational numbers
between 0 and 1 then
\[
N\cdot |E|_*=
\sum_{\nu=1}^{\nu=N}= |E+q_\nu|_*\leq 2
\]
where the last equality holds since
each set $E+q_\nu\subset [0,2]$.
Since $N$ can be arbitrary large we have
$|E|_*=0$.
So if $E$ is measurable we have
$|E|= |E|_*=0$, i.e $E$ is a null set. 
Since $E+q$ is  translate of $E$ they also give  null sets 
for every rational number.
But a denumerable union of null sets is a null set which
gives a contradaction since
 $\cup \, (E+q)$ with the union taken over all rational numbers
is the whole real line.







\newpage


\centerline{\bf II. Abstract measure theory}


\bigskip



\centerline {\bf{Introduction.}} 

\bigskip


\noindent
To get  some intuition we  present the theory
using concepts
from
probability theory.
A sample space
consists of a pair  $(\Omega,\mathcal B)$ where
$\Omega$ is a set and  $\mathcal B$ a
Boolean $\sigma$-algebra of subsets.
Thus, if $\{A_\nu\}$ is a  
denumarable family
of sets in $\mathcal B$ 
indexed by non-negative
integers, then  $\cap \,A_\nu$ and $\cup \,A_\nu$  stay in
$\mathcal B$.
Moreover $\Omega$ belongs to $\mathcal B$ and one  agrees that its
complementary  empty-set also belongs to the Boolean $\sigma$-algebra.


\medskip

\noindent {\bf 0.1 Measurable functions.}
A real valued function $f$  defined on $\Omega$ is measurable if
the  sets 
\[
f^{-1}(-\infty,a)\,\,\text{and}\,\,
f^{-1}(-\infty,a]\,\,\,\text{both belong to}\,\,\mathcal B\quad\colon\quad 
a\,\,\text{any real number}\tag{0.1.1}
\]
The class of such functions is denoted
by
$\mathcal M$.
\medskip

\noindent
{\bf{Exercise.}}
Use that $\mathcal B$ is a $\sigma$-algebra to show that
a real-valued function $f$ is measurable if
the sets in (0.1.1) belong to
$\mathcal B$ for every rational number $a$.
Next, let $f$ and $g$ be a pair of measurable functions and show that
$f+g$  is measurable. The hint is that for every real number
$a$ one has the set-theortetic equality:
\[
\{f+g<a\}
=\bigcup_{q\in Q}\, \{f<q\}\cap \{g<a-q\}
\]
where the union is taken over all rational numbers. In  a similar way
one proves that
$\{f+g\leq a\}$ are measurable sets for every real number $a$.
Conclude that $\mathcal M$ is a vector space of the real number field.



\medskip







\noindent 
{\bf 0.2 Probability measures.}
A probability measure $\mu$ is a $\sigma$-additive map
\[
\mu\colon\,\mathcal B\to [0,1]
\] 
which assigns a numer
$0\leq\mu(A)\leq 1$
for every set $A$ in $\mathcal B$, and
$\mu(\Omega)=1$.
The 
$\sigma$-additivity
means that
if $\{A_\nu\}$ is a sequence of pairwise
disjoint sets in $\mathcal B$, then
\[ 
\mu(\cup\,A\nu)=\sum\,\mu(A_\nu)
\] 
The family of probablility measures  is denoted by
${\bf{P}}(\mathcal B)$.




\medskip

\noindent
{\bf 0.3 Nullsets.} Let $\mu$ be a probability measure.
A subset $F$ of $\Omega$ is  a null set with respect to 
$\mu$
if there to each $\epsilon>0$ exists $A\in\mathcal B$ such that
\[ 
F\subset A\quad\&\quad \mu(A)<\epsilon
\]
The class of null-sets  is denoted by
$\mathcal N_\mu$. By
$\sigma$-additivity  
$\mathcal N_\mu$ is stable under  a denumarable 
union, i.e.
\[
\{F_\nu\}\subset\mathcal N_\mu\implies
\cup\,F_\nu\in\mathcal N_\mu
\]


\noindent
Notice that one does not require that a null-set belongs to
$\mathcal B$.
If $A_1$ and $A_2$ is a pair of sets in
$\mathcal B$ one says that they are $\mu$-equivalent if
the Boolean difference
\[
A_1\setminus A_2\cup\,
A_2\setminus A_1\in\mathcal N(\mu)
\]
When it holds we write
\[
A_2\overset\mu\simeq A_1
\]





\medskip

\noindent
{\bf {0.4 $\mu$-measurable sets.}}
Let $B\subset \Omega$ be an
arbitrary  subset. Its outer - resp. inner
$\mu$-measure are defined by
\[ 
\mu^*(B)=\min_{A\in\mathcal B}\,\mu(A)\quad\colon B\subset A\quad\colon\quad
\mu_*(B)=\max_{A\in\mathcal B}\,\mu(A)\quad\colon 
\,\, A\subset B
\]
Notice that both the maxium and the minium can be attained.
For example, let $\{A_n\}$ be a sequence
in $\mathcal B$ where
$B\subset A_n$ hold for every $n$ while
\[
\lim\, \mu(A_n)= \mu^*(B)
\]
Put
\[
A^*=\cap\, A_n
\]
By $\sigma$-additivity the reader can chek that
\[
\mu(A^*)= \mu^*(B)
\]
Here $A^*$ belongs to $\mathcal B$. It is not unique
but if $A^{**}$ is anopther set which contains
$B$ and (x) holds, then the reader can verify that 
$A^*$ and $A^{**}$  are $\mu$-equivalent.
In the same way one finds
$A_*$ where $A_*\subset B$ and
\[
\mu_*(B)= \mu(A_*)
\]
The set $B$ is called $\mu$-measurable if
\[
\mu_*(B)= \mu^*(B)
\]
and then this 
common  number is denoted by $\mu(B)$.
Let $\mathfrak{M}_\mu$
be the family if all $\mu$-measurable subsets of $\Omega$.
It is clear that we have the inclusion
\[
\mathcal B\subset\mathfrak{M}_\mu
\]



\noindent
{\bf{0.5 Exercise.}}
From the above  a set $B$ is $\mu$-measurable if and only if
there exists some  
$B_*\in \mathcal B $ such that 
the Bolean difference of $B$ and $B_*$ belongs to
$\mathcal N(\mu)$.
Conclude that
$\mathfrak {M}_\mu$ is the  Boolean $\sigma$-algebra 
of subsets of $\Omega$
generated by $\mathcal B$ and $\mathcal N_\mu$. Show also that the map
\[ 
B\mapsto \mu(B)
\]
is
$\sigma$-additive on $ \mathfrak {M}_\mu$.


\bigskip


\centerline {\bf 0.6 $\mu$-measurable functions.} 
\bigskip

\noindent
A real-valued function $f$ on $\Omega$ is 
$\mu$-measurable if
\[
f^{-1}(-\infty,a)\,\,\text{and}\,\,
f^{-1}(-\infty,a]\,\,\,\text{both belong to}\,\,\mathfrak{M}_\mu\quad\colon\quad 
a\in\bf R
\]
Denote this class by $\mathcal M_\mu$.
Since $\mathcal B\subset \mathfrak{M}_\mu$ one has the inclusion
\[
\mathcal M\subset\mathcal M_\mu\tag{0.6.1}
\]
\medskip




\noindent
{\bf{0.6.2 Teorem.}}
\emph{Let $f\in \mathcal M_\mu$. Then 
there exists a null set
$F\in\mathcal N_\mu$  and some $f_*\in \mathcal M$ such that
$f=f_*$ in $\Omega\setminus F$. Thus, after modifying a $\mu$-measurable 
function on a 
null set with respect to $\mu$ it becomes "truly measurable".}
\medskip


\noindent
\emph{Proof.}
Let 
$\{q_\nu\}_1^\infty$  enumerate  the set $Q$
of
rational numbers.
The exercise in (0.5)
gives for  each
$q_\nu$  a  pair  of disjoint sets
$F_\nu\in \mathcal B$ and $G_\nu\in\mathcal N_\mu$
such that
\[
f^{-1}(-\infty,q_\nu)=F_\nu \cup\,G_\nu
\]
We can also regard the inverse image of the singleton sets
and find for every
$q_\nu$ a disjoint pair $H_\nu\in\mathcal B$ and $S_\nu\in\mathcal N_\mu$
\[
f^{-1}(\{q_\nu\})=H_\nu \cup\,S_\nu
\]
Put
\[
G^*=\cup\, G_\nu\bigcup\, \cup S_\nu
\]
Here $G^*\in\mathcal N_\mu$ which gives
the existence
of a decreasing sequence of sets
$\{W_\nu\}$ in
$\mathcal B$ such that
\[
\mu(W_\nu)<2^{-\nu}\quad\&\quad G^*\subset \cap\, W_\nu
\]
Now  $W_*=\cap\,  W_\nu$ belons to $\mathcal B$
and  it is also a null-set for $\mu$. Finally, 
define the function
$f_*$ by
\[
f_*(\omega)=f(\omega)\quad\colon
\omega\in \Omega\setminus W_*\quad\text{and}\quad
f_*|W_*=0 
\]
By this construction $f_*\in\mathcal M_\mathcal B$ and $f_*$ 
differs from $f$ on a null set.

\bigskip


\noindent 
{\bf {0.6.3 Equivalence classes of $\mu$-measurable functions.}}
A pair $f,g$ in $\mathcal M_\mu$ are called equivalent if they
are equal outside a null set.
Theorem 0.6.2
shows that
every equivalence class can be represented by
a 
$\mathcal B$-measurable function.




\medskip

\centerline{\bf 0.7 Convergene in $\mu$-measure.}
\bigskip

\noindent
On $\mathcal M_\mu$ there exists a metric defined by
\[
d(f,g)= \sum_{k=1}^\infty\, 2^{-k}\cdot
\frac{\mu\{|f-g|\geq 2^{-k}\}}
{1+\mu\{|f-g|\geq 2^{-k}\}}\tag{0.7.1}
\]
Let $\{f_n\}$ be a sequence in  $\mathcal M_\mu$
and $g$ a 
function  in
$\mathcal M_\mu$ such that 
\[ 
\lim_{n\to\infty}\, \mu(\{|f_n-g|\geq \epsilon\}]=0
\] 
hold for every $\epsilon>0$.
The reader can check that this is equivalent to the condition that
\[
\lim\, d(f_n,g)=0\tag{0.7.2}
\]
and when this  holds we write
\[ 
f_n\overset\mu\to g\tag{0.7.3}
\]

\medskip



\noindent 
\centerline{\bf 0.8 Convergence almost everywhere.}
\medskip

\noindent
A sequence of $\mu$-measurable functions
$\{f_n\}$ is said to converge $\mu$-almost everywhere to a limit function
$g$ if there exists a null set $F\in\mathcal N_\mu$ such that
every $f_n$ is defined in $\Omega\setminus F$
and one has a pointwise limit:
\[ 
\lim_{n\to\infty}\, f_n(\omega)=g(\omega)\,\colon\,
\omega\in\Omega\setminus F\tag{0.8.1}
\]
When (0.8.1)  holds we write
\[ 
f_n\overset{a.e}\to g\tag{0.8.2}
\]
\medskip


\noindent
Almost everywhere convergence means that   pointwise 
convergence holds outside a null set $F$ for $\mu$.
So the limit function $g$ above is only defined in
$\Omega\setminus F$.
But when we regard $\mu$-measurable functions one can ignore  null sets
for $\mu$ and the following hold:

\medskip

\noindent
{\bf {0.8.3  Proposition.}}
\emph{If $g$ is an almost everywhere limit of a sequence
$\{f_\nu\}$ in $\mathcal M_\mu$ then
$g\in \mathcal M_\mu$.}


\medskip

\noindent
\emph{Proof.}
For a real number $a$ we put
\[
\{g\leq a\}= \{ w\in \Omega\setminus F\,\colon\, g(w)\leq a\}
\]
and when $N$ is a positive integer
\[
A_N(a)=
\{w\in \Omega\setminus F\colon \max_{\nu\geq N}\, f_\nu(w)\leq a\}
\]
It  is clear that
\[
A_N(\epsilon)\subset \{g\leq a\}\quad\colon\quad N=1,2,\ldots\tag{i}
\]
Conversely, if
$\delta$ is a positive number the pointwise convergence entails that
\[
 \{g\leq a\}\subset
 \bigcup_{N\geq 1}\, A_N(a+\delta)\tag{ii}
 \]
 Notice that the sets $A_N(a)$
 increase with $N$
 and let $A^*(a)$ be the union.
 Then (i-ii) give the following inclusions hold for
 every positive integer $m$:
 \[
 A^*(a)\subset \{g\leq a\}\subset A^*_N(a+1/m)
\]
This implies that
\[
 \{g\leq a\}=\bigcap_{m\geq 1}\, A^*_N(a+1/m)
\]
and the reader may verify that
the right hand side
is a $\mu$-measurable set.
Hence 
$\{g\leq a\}\in\mathcal {M}_\mu$. In a similar fashion one shows that
$\{g\geq b\}\in\mathcal {M}_\mu$
hold for every real number and
the reader can conclude that $g$ is $\mu$-measurable.




\medskip


\noindent
Examples show that
convergence  in measure need not imply convergence almost everywhere.
But  
one has the following:
\bigskip


\noindent
{\bf 0.8.4 Proposition.} \emph{Let $\{f_n\}$ be a sequence
of measurable functions which converges in $\mu$-measure to a 
$\mu$-measurable function
$g$. Then there exists a subsequence}
\[
\{g_k=f_{\nu_k}\,\,\colon\, \nu_1<\nu_2<\ldots\}
\quad\&\quad 
g_k\overset{a.e}\to  g
\]




\noindent
\emph{Proof.}
Regarding the sequence $\{f_n-g\}$ it suffices to prove the result when
$g=0$.
We first find an integer $\nu_1$ such that
\[
\nu\geq \nu_1	\implies \mu(\{|f_\nu\geq 2^{-1}\}\leq 2^{-1}
\]
Next, we find
$\nu_2>\nu_1$ such that
\[
\nu\geq \nu_2	\implies \mu(\{|f_\nu\geq 2^{-2}\}\leq 2^{-2}
\]
Inductively we get a sequence $\nu_1<\nu_2\ldots$ where
\[
\nu\geq \nu_k	\implies \mu(\{|f_\nu\geq 2^{-k}\}\leq 2^{-k}
\]
Then, the sequence  $\{g_k=f_{\nu_k}\}$ 
converges almost everywhere to the zero function.
To see this we set:
\[
g^*_k=\max_{\nu\geq k}\, |g_\nu|
\]


\noindent
The inductive construction above gives
\[
 \mu(\{g^*_k\geq 2^{-k}\}\leq
\sum_{\nu\geq k}\, 
 \mu(\{|g_\nu|\geq 2^{-k}\}\leq \sum_{\nu\geq k}\, 2^{-\nu}= 2^{-k+1}\tag{i}
 \]
Here $g^*_1\geq g^*_2\geq\ldots$ is a monotone sequence and
(i) shows that 
\[ 
g^*_k\overset{a.e}\to 0
\]
From this it is clear that
$\{g_k\}$ also converges almost everywhere to zero.






\bigskip

\noindent 
{\bf 0.8.5 Exercise}
Let $\{f_n\}$ be a sequence in $\mathcal M_\mu$
such that
\[
\lim_{n,m}\, \mu(\{|f_n-f_m|\geq\epsilon\})=0
\]  
hold for each $\epsilon>0$, where $(m,n)$ tend to $\infty$, i.e.
$\{f_n\}$ is a Cauchy sequence with respect to the metric defined in (0.7.1).
Prove by a similar method as in Proposition 0.8.4 that there
exists a subsequence $\{g_k=f_{n_k}\}$
which converges almost everywhere to a $\mu$-measurable limit function
$f_*$. Show also that $f_*$ is unique in $\mathcal M_\mu$
since the almost everywhere convergence of the subsequence entails that 
$f_n\overset\mu\to f_*$.
The conclusion is that
$\mathcal M_\mu$ is a {\emph{complete metric space} under (0.7.1).


\newpage

\centerline{\bf 1. Integrals}


\medskip


\noindent {\bf{1.1 Elementary functions.}}
As in ¤ 0 we are given
$(\Omega,\mathcal B)$.
Every set  $B\in\mathcal B$ gives the characteristic function
$\chi_B$ which is 1 on $B$ and 0 in $\Omega\setminus B$.
An elementary function is a finite linear sum 
\[ 
F=\sum\, a_k\cdot \chi_{B_k}\tag{*}
\] 
where $B_1,\ldots,B_N$ is a finite set of disjoint
sets in $\mathcal B$ whose union is $\Omega$ and
and $a_1,\ldots,a_N$ are real numbers. 
Let $E(\mathcal B)$ denote the family of all elementary functions.
This is  a 
a linear space of functions on $\Omega$. For let  
$F$ be given by (*) and
\[
G=\sum\, b_m\cdot \chi_{C_m}\tag{*}
\] 
is another elementary function..
Now the double indexed sets $\{B_k\cap C_m\}$
is a disjount partion of $\Omega$ and 
gives the elementary function
\[
\sum\, (a_k+b_m)\cdot \chi_{B_k\cap C_m}
\]
which obviously is equal to $F+G$.
In a similar fashion the product
$F\cdot G$ is the elementary  function defined by
\[
\sum\, a_k\cdot b_m\cdot \chi_{B_k\cap C_m}
\] 
Next, let $F$ be a bounded 
$\mathcal B$-measurable function i.e. 
there exists a constant $K$ such that
\[
-K\leq F(\omega)\leq K
\]
hold for all $\omega\in\Omega$.
Then $F$ can be \emph{uniformly approximated} by
elementary functions.
Namely, if $N\geq 1$ we set
\[ 
B_N(\nu)=\{ -K+K\cdot \nu\cdot 2^{-N}\leq F<
-K+K\cdot (\nu+1)\cdot 2^{-N}\} \quad\colon\,0\leq \nu\leq 2\cdot (2^N-2)
\]
\[
\text{and}\quad  B_N(2\cdot 2^N-1)=\{ K-2^{-N}\leq F\leq K\}
\]
We get the elementary function
\[ 
F_*=\sum_{\nu=0} ^{2\cdot 2^N-1}
\,(-K+\nu\cdot 2^{-2N})\cdot \chi_{B_N(\nu)}
\]
It is clear that 
\[
F_*\leq F\leq F_*+2^{-N}
\]
Since $N$ can be arbitrary large this shows that
$F$ is uniformly
approximated by elementary functions.















\bigskip

\noindent
{\bf{1.2 Integrals of elementary functions.}}
Let $\mu$ be a probability measure.
To each
elementary function
\[
F=\sum\, a_k\cdot \chi_{B_k}
\] 
we assign the $\mu$-integral
\[
 \int\, F\cdot d\mu=\sum\, a_k\cdot \mu(B_k)\tag{1.2.1}
\]
It is clear that (1.2.1 ) yields an additive map from
$E(\mathcal B)$ into the complex number where we regard
complex-valued functions.
The maximum-norm $||F||_\infty$
is the maximum of $\{|a_k|\}$. Since
$\mu$ is a probability measure the triangle inequality gives
\[
\bigl| \int\, F\cdot d\mu\,\bigr|\leq
||F||_\infty\tag{1.2.2}
\]
\medskip


\noindent
{\bf{1.3  Integrals of bounded functions.}}
If $K>0$ is a positive number we denote by
$\mathcal M_\mu(K)$ the class of $\mu$-measurable functions
$f$ such that the absolute value $|f|$ is $\leq K$
almost everywhere. So in the equivalence class we can take $f$ to be
a function in $\mathcal M_\mathcal B$ where
this everywhere defined function has maximum norm 
$K$ at most. By (1.1) 
$f$ can be uniformly approximated
by a sequence $\{F_n\}$ from $E(\mathcal B)$
with maximum norms $\leq K$.
For each pair $n,m$ the triangle inequality gives
\[
\bigl| \int\, F_n\cdot d\mu-
\int\, F_m\cdot d\mu\,\bigr|\leq
\int\,|F_n-F_m|\cdot d\mu\leq
||F_n-F_m||_\infty\tag{1.3.1}
\]
Since $||F_n-f||_\infty\to 0$ it follows that
(1.3.1) tends to zero as $n$ and $m$ increase. Hence 
the evaluated integrals $\{\int\, F_n\cdot d\mu\}$ is a 
Cauchy sequence of complex numbers and 
there exists a limit
\[ 
\lim_{n\to\infty}\, \int\, F_n\cdot d\mu\tag{1.3.2}
\]
Moreover, (1.2.1 ) implies  that this limit is intrinsic, i.e. 
independent
of the chosen  sequence $\{F_n\}$ which approximates $f$ uniformly.
The limit (2) is called the $\mu$-integral of $f$ and is denoted by
\[
\int\, f\cdot d\mu\tag{1.3.3}
\]

\medskip

\noindent
{\bf 1.4 Absolutely integrable functions.}
For each  positive real number $K$ we define the 
the  truncation operator $T_K$ from $\mathcal M_\mu$ to 
$\mathcal M_\mu(K)$ by:
\[ 
T_K(f)(x)=f(x)\,\colon\,|f(x)|\leq K\quad\text{and}\quad
 T_K(f)(x)=0\,\colon\,|f(x)|> K
\]

 
\noindent
When $f\in\mathcal M_\mu$ 
we
get bounded functions
$\{T_K(f)\,\colon\, K>0\}$.
We can also take  absolute values and notice that
\[
 K_1<K_2\implies |T_{K_1}(f)|\leq |T_{K_2}(f)|\tag{1}
\]
From (1)  the $\mu$-integrals of the
non-negative functions $\{|T_K(f)|\}$ increase with $K$, i.e. 
\[
 K_1<K_2\implies \int\, |T_{K_1}(f)|\cdot d\mu\leq
\int\, |T_{K_2}(f)|\cdot d\mu\tag{2}
\]


\noindent
We can impose the condition that the non-decreasing sequence 
(2) is bounded. This leads to 
\medskip

\noindent
\noindent 
{\bf 1.5  Definition}.
\emph{A function $f\in\mathcal M_\mu$ is said to be absolutely integrable
if there exists a
constant $C$ such that}
\[
\int\, |T_{K_1}(f)|\cdot d\mu\leq C\quad\text{for all}\quad K>0\tag{*}
\]
\emph{
The class if these functions is denoted
$L^1(\mu)$.}
\bigskip

 

 

\noindent 
{\bf {1.6 Integrals of $L^1(\mu)$-functions.}}
Let $f$ belong to $L^1(\mu)$.
From the construction of the $T$-operators it is clear that
if $K_2>K_1>0$ then
\[
\bigl|\int T_{K_2}(f)\cdot d\mu-
\int T_{K_1}(f)\cdot d\mu\bigr|\leq
\int\, |T_{K_2}(f)|\cdot d\mu-
\int\, |T_{K_1}(f)|\cdot d\mu\tag{i}
\]


\noindent
Since $f\in L^1(\mu)$
the non-decreasing sequence
$\{\int\, |T_{K_2}(f)|\cdot d\mu\}$
is bounded above and therefore convergent. Since a 
convergent sequence also is a Cauchy sequence, it follows from (i) that
\[
\lim_{K_2,K_1}\, 
\int T_{K_2}(f)\cdot d\mu-
\int T_{K_1}(f)\cdot d\mu=0
\] 
as $K_1$ and $K_2$ tend to $+\infty$.
Since  Cauchy sequences of real  numbers converge
there exists a limit
\[ 
\lim_{K\to\infty}\, 
\int T_K(f)\cdot d\mu\tag{*}
\]
This limit is denoted by $\int\, f\cdot d\mu$ and is called the
$\mu$-integral of $f$.


\medskip

\noindent 
{\bf 1.7 Exercise.} Show that the integral on $L^1(d\mu)$ is additive, i.e.
\[
\int f d\mu+
\int g d\mu=
\int (f+g) d\mu\,\quad\colon\quad f,g\in L^1(d\mu)
\]


\medskip

\noindent
{\bf 1.8 The $L^1$-norm.}
The linear space $L^1(d\mu)$ becomes a normed space when we set
\[ 
||f||_1=\int\,|f[ d\mu\quad\colon\quad
f\in L^1(d\mu
\]



\noindent
{\bf{1.9 Exercise.}}
Show that $E(\mathcal B)$ is a dense subspace of $L^1(\mu)$.
\bigskip


\noindent
{\bf{1.10 Convergence in the $L^1$-norm.}}.
By definition
a sequence $\{f_n\}$ converges in the $L^1$-norm to a limit function
$g$ in $L^1(\mu)$ when
\[
\lim_{n\to\infty}\, ||f_n-g||_1=0\tag {i}
\]
If $\epsilon>0$ we notice that
\[
\mu(\{|f_n-g|\geq\epsilon\}\leq\epsilon^{-1}\cdot ||f_n-g||_1\tag{ii}
\]
Hence (i) implies that
\[
\lim_{n\to\infty}\
\mu(\{|f_n-g|\geq\epsilon\}=0\tag{3}
\]
Here $\epsilon$ is arbitrary small
which  means that $f_n\overset\mu\to g$. Thus
$L^1$-convergence implies convergence in $\mu$-measure.
\medskip


\noindent 
{\bf{1.11 Warning.}}
The converse is not true.
For example, let $\mu$ be the Lebesgue measure on $[0,1]$. To each
$n\geq 1$ we define $f_n(x)$ to be $n$ if $0\leq x\leq \frac{1}{n}$ 
and otherwise zero. Then 
\[ 
\int_=^1\, f_n(x)\cdot dx=1
\]
hold for all $n$. At the same time $f_n(x)\to 0$ for every $x>0$, i.e. the sequence converges almost every where to zero and hence also in measure.
But if we restrict the attention to bounded functions  a converse result holds.
\medskip

\noindent
{\bf 1.12  Proposition} 
\emph{Let $K>0$ be fixed. Then a sequence $\{f_\nu\}$
in $\mathcal M_\mu(K)$ converges to a limit function $g$ in the $L^1$-norm
if and only if the sequence  converges in measure to $g$.}

\bigskip


\noindent
\emph{Proof.} Consider a pair $f,g$ in $\mathcal M_\mu(K)$.
If $\epsilon>0$ we get the measurable set
\[ 
E_\epsilon(f,g)=\{ |f-g|\geq\epsilon\}
\]
Since the maximum norm   $||f-g||_\infty\leq 2K$ 
it follows that

\[ 
||f-g||_1=
\int_{E_\epsilon(f,g)}\,|f-g|d\mu+
\int_{\Omega\setminus E_\epsilon(f,g)}\,|f-g|d\mu\leq 2K\cdot \mu(E_\epsilon(f,g))\tag{i}
+\epsilon
\]
\medskip

\noindent
If  $f_\nu\overset\mu\to g$
where $\{f_\nu\}$ in $\mathcal M_\mu(K)$ one has 
\[
\lim_{\nu\to\infty}\, \mu(E_\epsilon(f_\nu,g))=0\quad\text{hold for each}\quad
\epsilon>0\tag{ii}
\] 
Hence (i) implies that
$||f_n-g||_1||_1\to 0$.
Since we already proved that $L^1$-convergence entails convergence in measure we get
the equivalence assertion in
Proposition 1.12 follows.



\bigskip

\centerline {\bf 1.13 Dominated convergence theorem}
\medskip

\noindent 
Let 
$\{f_n\}$ be a  sequence in $L^1(\mu)$
which converges in $\mu$-measure
to a limit function
$g$. The example in 1.11  shows that
convergence need not hold
in the $L^1$-norm.
 To compensate for this we impose a certain bound so that the situation
is essentially the same as in 
Proposition 1.12
\medskip

\noindent 
{\bf 1.14 Theorem}
\emph{Let $\{f_n\}$ be a sequence in $L^1(\mu)$ where
$f_n\overset\mu\to g$ holds. Assume in addition that there exists
a non-negative $\phi\in L^1(\mu)$ such that}
\[
|f_n|\leq \phi\tag{1}
\] 
\emph{hold almost everywhere for each $n$.
Then the limit function $g$ belongs to $L^1(\mu)$ and}
\[ 
\lim_{\nu\to\infty}\,||f_n-g||_1=0\tag{2}
\] 
\bigskip

\noindent {\bf{1.15  Exercise}} Prove Theorem 1.14.
The hint is to apply  truncation operators to $\phi$
so that the $L^1$-norm of $\phi-T_K(\phi)$ are small and then
use Proposition  1.12.



\newpage

\centerline
{\bf{2.  A completeness theorem.}}
\medskip


\noindent
Let $\{f_n\}$ be  Cauchy sequence in the $L^1$-norm, i.e. 
\[
\lim_{n,m\to\infty}\,\int\,|f_n-f_m|\cdot d\mu=0\tag{*}
\]
\medskip


\noindent
{\bf{2.1 Theorem}}
\emph{When (*) holds there exists   a unique  $L^1$-function $f_*$
such that}
\[
\lim_{n,m\to\infty}\,\int\,|f_n-f_*|\cdot d\mu=0
\]
\emph{Hence  the normed space
$L^1(\mu)$ is complete, i.e. it is a Banach space.}
\medskip

\noindent
\emph{Proof.}
From (*) it follows that there exists a subsequence
$\{n_k\}$ such that if $g_k=f_{n_k}$
then
\[
||g_{k+1}-g_k||_1\leq 2^{-k}\tag{i}
\]
Since $\sum\, 2^{-k}<\infty$
the non-negative function
\[ 
G=|g_1|+\sum_{k=1}^\infty\, |g_{k+1}-g_k|
\]
is integrable.
It is clear that 
\[
|g_k|\leq G\quad\colon k=1,2,\ldots\tag{ii}
\]
Next, (i)  entails that
$\{g_k\}$ is a Cauchy sequence in $L^1(\mu)$ and hence it is also a Cauchy sequence in the complete metric space $\mathcal M_\mu$.
It  follows that there exists a $\mu$-measurable 
function $g$ where
 \[
 g_k\overset{\mu}\to g
 \]
 Next,  
(ii) enable us to apply Theorem 1.14 which gives
\[
||g_k-g||_1\to 0
\]
Above $\{g_k\}$ is a subsequence
of $\{f_n\}$ and the triangle inequality
shows that
$||f_n-g||_1\to 0$ which shows that $g$ is the 
requested limit in $L^1(\mu)$ of the given Cauchy-sequence $\{f_n\}$.








\newpage






\centerline{\bf 3. Signed measures and the  Radon-Nikodym  theorem.}

\bigskip

\noindent
Let $(\Omega,\mathcal B)$ be a sample space.
Consider an additive real-valued map $\mu\colon\mathcal B\to
\bf R$ which may take negative values and for which 
there exists a constant $C$ such that
\[
 -C\leq\mu(A)\leq C\quad\colon\,\quad A\in \mathcal B\tag{*}
\]
\medskip

\noindent
This uniform bound and additivity  imply
that
if $\{A_\nu\}$ is a sequence of disjoint sets in $\mathcal B$ then
\[
\sum\, |\mu(A_\nu)|< 2C
\]
Hence the series $\sum\,\mu(A_\nu)$ is absolutely convergent.
We say that $\mu$ is $\sigma$-additive if
\[ 
\sum\, \mu(A_\nu)=\mu(\cup\,A_\nu)
\]
hold for every sequence of disjoint sets in $\mathcal B$ and  refer to $\mu$
as a  \emph{signed} measure. 
If $\mu(A)\geq 0$ for all $A\in\mathcal B$ we say that
$\mu$ is a positive measure.
\medskip

\noindent {\bf 3.1 Definition}
\emph{Two positive measures $\mu$ and $\nu$
are mutually singular if there exist null sets  $A\in\mathcal N_\mu$
and $B\in\mathcal N_\nu$ such that}
\[
\mu(B)=\mu(\Omega)\quad\colon\quad \nu(A)=\nu(\Omega)
\] 
\emph{When this holds we write $\mu\perp\nu$.}




\bigskip

\noindent
{\bf 3.2 Hahn's Theorem}
\emph{Every  signed measure $\mu$ has a unique decomposition}
\[
\mu=\mu_+-\mu_-\quad\text{where}\,\quad
\mu_,\mu_-\,\,\text{
are both  positive and}\,\ \mu_+\perp\mu_-
\]
\medskip

\noindent \emph{Proof.}
A set $A\in\mathcal B$ is called a $\mu$-positive set  if
\[
E\subset A\quad\&\quad E\in\mathcal B \implies \mu(E)\geq 0\tag{i}
\]

\noindent
Denote this class by $P_+(\mu)$.
Obviously the union of two $\mu$-positive sets is again $\mu$-positive and by
$\sigma$-additivity there exists a $A^*\in P_+(\mu)$ such that
\[
\mu(A^*)=\max_{A\in P_+(\mu)}\,\mu(A)\tag{ii}
\]


\noindent
\emph{Sublemma.} One has  $\mu(B)\leq 0$ for each $B\subset\Omega\setminus A^*$.
\medskip

\noindent
\emph{Proof of Sublemma.} 
We argue by contradiction.
Suppose there is  some $B_0\subset\Omega\setminus A^*$ with 
$\mu(B_0)=\delta>0$.
The maximality of $\mu(A^*)$ implies that $B_0$ does not belong to
$P_+(\mu)$ which gives
some $\delta_1>0$ such that
\[ 
-\delta_1=\min_{E\subset B_0}\,\mu(E)\tag{i}
\] 
Choose $E_1\subset B_0$ with $\mu(E_1)\leq -\delta_1/2$ and set $B_1=B\setminus E_1$.
Now $\mu(B_1)\geq \delta+\delta_1/2$ and 
exactly as above
we get a negative number
\[
-\delta_2=
\min_{E\subset B_1}\,\mu(E)
\]
Choose $E_2\subset B_1$ with $\mu(E_2)\leq-\delta_2/2$.
Inductively we get a decreasing sequence of
sets
\[ 
B_\nu=B_0\setminus (E_1\cup\ldots\cup E_\nu)
\]
where $\{E_\nu\}$ are disjoint. Moreover, we have
a sequence $\{\delta_\nu\}$ of positive numbers where
\[
-\delta_\nu=
\min_{E\subset B_\nu}\,\mu(E)\quad\text{and}\quad \mu(E_{\nu+1})\leq
-\delta_\nu/2\tag{ii}
\]
Since $\mu$ is a signed measure there is  a constant $A$
such that 
\[
\mu(E_1)+\ldots+\mu(E_N)\geq -A\quad\text{for all}\quad N\geq 1\tag{iii}
\]
It follows that
\[ 
\delta_1+\ldots+\delta_N\leq 2A\quad\text{for all}\quad N\geq 1\tag{iv}
\]
Hence the positive series
$\sum\,\delta_\nu$ is convergent which gives
$\delta_\nu\to 0$ as $\nu\to+\infty$.
Put
\[
B_*=\cap \, B_\nu\tag{v}
\]
For each $\nu\geq 1$ the inclusion $B_*\subset B_N$ 
and the definition of $\delta_\nu$ from (ii)  give:
\[ 
\min_{E\subset B_*}\, \mu(E)\geq -\delta_\nu\tag{vi}
\]
This hold for every $\nu$ and since $\delta_\nu\to 0$
the minimum in (vi) is 
$\geq 0$ which means that $B_*$ belongs to 
$P_+(\mu)$.
At the same time the construction above gives

\[ 
\mu(B_\nu\geq \delta_0+\frac{1}{2}(\delta_1+\ldots+\delta_\nu)\geq \delta_0\tag{vii}
\]
for every $\nu$. By $\sigma$-additivity we have

\[ 
\mu(B_*)=\lim_{\nu\to\infty}\,\mu(B_\nu)
\] 
and then
(vii) entails that $\mu(B_*)>0$.
This contradicts the  (1) since $A^*$ and $B_*$ are disjoint
and the Sublemma is proved.

\bigskip
 
\noindent
{\emph{Final part of the proof }}. 
The Sublemma gives  positive measures
$\mu_+$ and $\mu_-$ defined 
 by
 \[ 
 \mu_+(E)=\mu(E\cap A^*)\quad\colon\quad
 \mu_-(E)=-\mu(E\cap(\Omega\setminus A^*)
\]
We see that
$\mu_+\perp\mu_-$ and $\mu=\mu_+-\mu_-$.
This proves the existence of at least one
Hahn-decompostion.
The proof of  \emph{uniqueness} of such a 
decomposition
is left to the reader. 


\bigskip

\centerline {\bf 3.3 Radon-Nikodym derivatives.} 
\bigskip

\noindent
Let $\mu$ be a positive measure and consider
a
non-negative function $f\in L^1(d\mu)$.
This gives a  positive measure defined
by the $\sigma$-additive map

\[
E\mapsto 
\int_E\, f\cdot d\mu\quad\colon\, E\in\mathcal B
\]
Denote this positive measure by $f\cdot \mu$.
If $E\in\mathcal N_\mu$  the construction of $\mu$-integrals implies that
$\int_E\, f\cdot d\mu=0$. Hence  one has the inclusion
\[ 
\mathcal N_\mu\subset
\mathcal N_{f\cdot \mu}\tag{3.1}
\]
In general, a positive measure $\nu$ is called \emph{absolutely continuous} with respect
to $\mu$ if 
\[
\mathcal N_\mu\subset
\mathcal N_\nu
\]
It turns out that such positive measures are
of the form $f\cdot\mu$ with $f\in L^1(\mu)$.

\bigskip

\noindent
{\bf 3.4 Theorem.}
\emph{Let $\mu$ be a  positive measure. Then every positive measure
$\nu$ which is absolutely continuous with respect to
$\mu$ is of the form
$f\cdot \mu$ for a unique non-negative function
$f\in L^1(d\mu)$.}
\bigskip


\noindent
\emph{Proof.} 
For each pair $(k,N)$ where  $N$ is a positive integer and $k$
a non-negative integer
we consider the following two signed measures

\[
\nu-k2^{-N}\cdot \mu\quad\text{and}\quad
(k+1)2^{-N}\cdot \mu-\nu\tag{i}
\]
The Hahn decomposition applied to
$\nu-k2^{-N}\cdot \mu$ gives a maximal set
\[
S_N(k)\in P_+( \nu-k2^{-N}\cdot \mu)\tag{ii}
\]
and similarly we find a maximal set
\[
T_N(k)\in P_+((k+1)2^{-N}\cdot \mu-\nu)\tag{iii}
\]


\medskip

\noindent
If $N$ is fixed 
the measure 
$ (\nu-k2^{-N})-(\nu-(k+1)2^{-N})= 2^{-N}\cdot \mu\geq 0$. This implies that

\[ 
S_N(k+1)\subset S_N(k)\quad\text{for all}\quad k=0,1,\ldots\tag{iv}
\]

\noindent
Moreover, since
$\nu$ is absolutely continuous with respect to $\mu$ it is clear that:
\[
\cap_{k\geq 1}\, S_N(k)=\emptyset\tag{v}
\]
Finally the reader may observe that
\[
S_N(k)\setminus S_N(k+1)= S_N(k)\cap\, T_N(k)\tag{vi}
\]


\noindent
Let us put
\[
W_N(k)= S_N(k)\cap\, T_N(k)\tag{vii}
\]
From (vi) it follows that 
$\{W_N(k)\}$ is a family of disjoint subsets of $\Omega$ and we
notice  that

\[
k2^{-N}\mu(E)\leq \nu(E)\leq (k+1)2^{-N}\mu(E)\quad\colon\,
E\subset W_N(k)\tag{viii}
\]
The reader may also verify the set-theoretic equality
\[
 W_N(k)=W_{N+1}(2k)\cup W_{N+1}(2k+1)\tag{ix}
 \]
for all pairs $k$ and $N$,
Next we construct a sequence of functions by:
\[ 
f_N=\sum_{k=1}^\infty\, k2^{-N}\cdot \chi_{W_N(k)}\quad\colon\, N=1,2\ldots \tag{x}
\]
Using (ix) the reader may verify that
$\{f_N\}$ increase with $N$ and (viii) entails that
\[ 
\int_E\, f_N\cdot d\mu\leq \nu(E)\leq
\int_E\, f_N\cdot d\mu+2^{-N}\cdot \mu(E)
\quad\colon\,
E\in\mathcal B
\tag{xi}
\]
\medskip


\noindent
Now $\{f_N\}$ is a non-decreasing sequence and
there exists
a limit function
\[ 
f_*=\text{lim}_{N\to\infty} f_N
\] 
where the convergence holds almost everywhere and it is celar that
(xi) implies that

\[
\nu(E)=\lim_{N\to\infty}\int_E\, f_n\cdot d\mu=\int _E\, f_*\cdot d\mu
\quad\colon\,
E\in\mathcal B
\]
This gives $\nu= f_*\cdot d\mu$
and Theorem 3.3, is proved.
\bigskip


\centerline {\bf{3.4 A general decomposition.}}
\bigskip

\noindent
Let $\mu$ be a positive measure.
For any other positive measure
$\nu$
there exists a unique
decomposition of $\nu$ into a sum of one measure which is singular with
respect to $\mu$, while the other term is given by an
$L^1(d\mu)$-function. More precisely one has:
\medskip

\noindent  
{\bf 3.5 Theorem} \emph{Given a positive measure $\mu$ every other
positive measure $\nu$ is of the form}
\[ 
\nu=\nu_s+fd\mu\quad\colon\quad \nu_s\perp\mu\quad\text{and}\quad 
f\in L^1(d\mu)
\]
\bigskip

\noindent 
\emph{Proof}
To find the singular part $\nu_s$ we put
\[
M=\max\,\nu(A)\quad\colon\quad A\in\mathcal N_\mu\tag{1}
\]


\noindent
By  $\sigma$-additivity there exists some   $A_*\in\mathcal N_\mu$ such that
$\nu(A_*)=M$.
Define the measure $\nu_*$ by:
\[ 
\nu_*(E)=\nu(A_*\cap\,E)\tag{2}
\]
Here  $\nu_*\perp\mu$.
Put $\gamma=\nu-\nu_\ast$. The construction of $\nu_*$ gives 
\[ 
A\in\mathcal N_\mu\implies \gamma(A)=0\tag{3}
\]
Then Theorem 3.5 gives $\gamma=f\cdot \mu$
for some
$f\in L^1(\mu)$ and Theorem 3.5 follows.
\bigskip



\centerline {\bf{3.6 The Vitali-Hahn-Saks theorem.}}
\bigskip

\noindent
Let $\Omega,\mathcal B)$ be a probability space
and $\mu$  a probability measure which gives 
the $\sigma$-algebra 
$\mathcal N(\mu)$  of null-sets.
A pair of $\mu$-measurable sets are identified when
their Boolean difference is a null-set.
If $A\in\mathcal B$
then $A_*$ denotes its equivalence class.
Let $X$ denote the space whole points are such
equivalence classes of subdsets from $\mathcal  B$.
A metric is defined on $X$
by
\[
d(A_*,B_*)=\mu(A\setminus B)+ \mu(B\setminus A)
\]
\medskip

\noindent
{\bf{3.6.1 Exercise.}}
Show that $X$ is a complete metric space. 
\medskip

\noindent
Next, an additive real-valued function $\lambda$
defined on
$\mathcal B$ is called $\mu$-continuous if
\[
\lim_{\mu(A)\to 0}\,\lambda(A)=0
\]
\medskip

\noindent
{\bf{3.6.2 Theorem.}}
\emph{Let $\{\lambda_n\}$ be a sequece of
additive $\mu$-continuous functions such that}
\[ 
\lim_{n\to\infty}\,\lambda_n(A)=\lambda_*(A) \tag{*}
\] 
\emph{exist for every $A\in\mathcal B$.
Then, for each $\epsilon>0$ there exists $\delta$ such that}
\[
\mu(A)\leq \delta\implies
\max_n\, |\lambda_n(A)|\leq \epsilon\tag{**}
\]
\medskip

\noindent
\emph{Proof.}
For each $\epsilon>0$
and every pair of integers $n,m$ we get the  closed sets in $X$:
\[
\Sigma_{n,m}=\{A\in\mathcal B\,\colon\, 
|\lambda_n(A)-\lambda_m(A)|\leq\epsilon/2\}
\]
Set
\[
 \Sigma_p^*=\bigcap_{n,m\geq p}\Sigma_{n,m}
\]
Then (*) entails that
$\cup\, \Sigma^*_p=X$. Exercise 3.6.1 and 
Baire's  category theorem gives some  $p$ and
$\delta>0$ such that
\[
\mu(A)<\delta\implies A\in \Sigma_p^*
\]
Shrinking $\delta$ if necessary 
\[
\mu(A)<\delta\implies \max_{n \leq p_*}\lambda_n(A)\leq\epsilon/2
\]
Now the reader can check that (**) holds. 
\medskip

\noindent
{\bf{3.6.3 Exercise.}}
Show that if $\lambda_*(A)$ is  the limit value in (*)
then
$\lambda_*$ is additive and $\mu$-continuous.














\newpage














\centerline{\bf\large{Measure theory}}

\bigskip

\centerline{\emph{Contents}}


\bigskip



\noindent
0. Introduction
\medskip



\noindent
0.1. The Borel-Riesz theory

\medskip
\noindent
0.2. Lebesgue theory



\medskip
\noindent
0.3. Riesz measures in ${\bf{R}}^n$.
 
\medskip
\noindent
0.4. The 1-dimensional case
 
 \medskip
\noindent
0.5. Cantor sets
 
 \medskip
\noindent
0.6. Examples from function theory

 
 \medskip
\noindent
0.7. Rational series 


 
\bigskip

\noindent
1.A Measure theory on the real line
\medskip

\noindent
1.B Derivatives of monotone functions

\medskip

\noindent
2. Abstract measure theory

\medskip
\noindent
3. The Lebesgue measure

\medskip
\noindent
4. Riesz measures

\medskip
\noindent
5.  Stokes theorem in dimension $n$



\medskip
\noindent
6. The Hardy-Littelwood maximal function

\medskip

\noindent 
7. Rademacher functions
\medskip

\noindent
8. The Brownian motion
\medskip

\noindent
8. Riesz' representation theorem 


\bigskip

Strul ...



\noindent
The    sections 0.1-0.7
give background for  topics in 
the subsequent sections ¤ 1-9.
In ¤ 0.4 we expose the  construction by 
Weierstrass 
of a continuous function 
which fails to have a derivative at every point
on the real line.
More precisely  if $0<b<1/5$ then Weierstrass proved
that the convergent cosine series
\[
f(x)= \sum_{k=1}^\infty\, b^k\cdot \cos(
\]
is a continuous function which 
fails to have a derivative at every point
as soon as
\[
k>.....
\]





\bigskip


\centerline{\bf{Introduction}}

\bigskip



\noindent
Modern integration theory started in 1894
when Stieltjes defined integrals of the form
\[
\int_a^b\, g(x)\cdot df(x)\tag{*}
\]
where $g$ is a real-valued continuous function and
$f$ is continuous and \emph{non-decreasing} on the compact interval $[a,b]$.
Stieltjes defined  (*) as the limit of sums:
\[ 
\sum\, g(x_\nu)\cdot \bigl[f(x_{\nu+1}-f(x_\nu)\bigr]\tag{**}
\]
where $a=x_0<\ldots<x_N=b$ and $\max\,(x_{\nu+1}-x_\nu)$
tends to zero. The \emph{uniform continuity} of $g$ on 
$[a,b]$  gives a limit 
exactly  as for the ordinary Riemann integral.
Namely, consider the modulus
of
continuity:
\[ 
\omega_g(\delta)=
\max_{x_1,x_2}\,|g(x_1)-g(x_2)|\quad\colon\,
\text{maximum taken over pairs}\,\,\, |x_2-x_1|\leq \delta
\]
and put $M=f(b)-f(a)$.
Let $\{x_\nu\}$ and $\{y_j\}$ be two $\delta$-partitions of $[a,b]$, i.e.
\[
\max\, x-{\nu+1}-x_\nu\leq \delta
\quad\&\quad \max\, y_{j+1}-y_j\leq \delta
\] 
hold.
The the reader cab check that the
Stieltjes' sums in (**) using the two partitions
differ in absolute value by a quantity which is
$\leq M\cdot\omega_g(\delta)$. Hence the 
the 
uniform continuity of $g$
entails that the .limit in (**) exists as $\delta\to 0$.
\medskip



\noindent
In the special case when
$f$ is a $C^1$-function, i.e.  the  derivative
$f(x)$ exists as a continuous function, the Stieltjes' integral (*)
is equal to the ordinary Riemann integral
\[
\int_a^b\, g(x)f'(x)\cdot dx
\]
To see this one uses Rolle's mean-value formnula which shows that
every sum in (**) can be expressed as
\[ 
\sum\, g(x_\nu)\cdot f'(\theta_\nu)\cdot (x_{\nu+1}-(x_\nu)
\]
where $x_\nu<\theta_\nu<x_{\nu+1}$
hold for every $\nu$.
\medskip


\noindent
Soon after Stieltjes' construction 
another method was introduced by Emile Borel. His idea was to
decompose the range of $g$.
To begin with Borel used the elementary  fact from topology that
every open subset on the real line is
the disjoint union of
at most denumerable open intervals.
If $\{(a_\nu,b_\nu)\}$
is a family of disjoint open subintervals of $(a,b)$
the variation of $f$ over their  open union $\Omega$ 
is defined by
\[
\text{Var}_f(\Omega)= \sum\, f(b_\nu)-f(a_\nu)
\]
Since $f$ is non-decreasing
the termes  of the series are non-negative and
the sum is majorised by $f(b)-f(a)$.
More generally, if $\Omega$ is an open subset of 
an open interval $(a,b)$ and
$F$ a closed subset of $(a,b)$, Borel defined the variation of
$f$ over $\Omega\cap F$ to be
\[
\text{Var}_f(\Omega)-\text{Var}_f((a,b)\setminus F)
\]
Let us then consider a continuous function $g$ on $[a,b]$.
For every pair $\xi<\eta$
the continunity of $g$ entails that the set
\[
(a,b)\cap \{\xi\leq g<\eta\}
\]
is the intersection of a closed and an open set
on which the variation of $f$ can be defined.
Choose $M>0$
so that the range of $g$
is contained in  the open interval $(-M,M)$.
For every sequence
\[
-M=\xi_0<\xi_1<\ldots<\xi_N=M
\]
one defines
\[
\sum_{\nu=0}^{\nu=N_1}\, \xi_\nu\cdot \text{Var}_f(
(a,b)\cap \{\xi_\nu\leq g<\xi_{\nu+1}\}\tag{i}
\]
\medskip

\noindent
{\bf{0.1 Exercise.}}
Show by partial summations
that (i) differs from
(*) by a quantiity which does not exceed
\[
(b-a)\cdot \max_\nu\, (\xi_{\nu+1}-\xi_\nu)
\]
\medskip

\noindent
'The merit in Borel's construction of integrals  that it enable us to define integrals
where the $g$-function no longer need to be continuous.
A first example is when
$g$ is a bounded function given as
a \emph{pointwise limit} of
continuous functions.
Thus, suppose that $\{g_n\}$ is a sequence of
uniformly bounded continuous functions on some open interval $(a,b)$ and that
\[
\lim_{n\to\infty}\, g_n(s)=g(s)\quad\colon\quad a<s<b\tag{i}
\]
With $f$ as before  there exists the Borel integral
\[
\int_a^b\, g(x)\cdot df(x)\tag{0.2}
\]
To find (0.2), Borel argued as follows.
For every $n$ we put
\[
g^*_n(x)= \max_{\nu\geq n}\, g_\nu(x)
\]
Since the $g$-functions are bounded it is clear that the sets
\[
(a,b)\cap \{g^*_n(x)<\eta\}
\]
are open for every real number $\eta$.
Exactly as above the reader can check that
that there exist $f$-variations:
\[
\text{Var}_f((a,b)\cap \,\{\xi\leq g_n^*<\eta\}
\]
for all pairs $\xi<\eta$ and from this one contructs the Borel integrals
\[
\int\, g^*_n(x)\cdot df(x)\quad\colon\, n=1,2,\ldots
\]
Now $\{g^*_n\}$ is a non-increasing sequence of functions which
converges pointwise to $g$.
It follows first that the integrals (xx)
form a non-increasing sequence of real numbers
and since $\{g_n\}$ by assumption is uniformly bounded
the sequence in (xx) converges to a limit which
Borel defined as the iintegral of the pair $g$ and $f$.
\medskip

\noindent
{\bf{The Baire  algebra 
$\mathcal B^\infty[a,b]$}}.
By transfinite induction, Baire constructed
 a space of bounded real-valued functions  on a given compact interval $[a,b]$
which is stable under poinitwise limits and contain
the space of bounded continuous functions.
This gives an algebra  
of bounded real-valued functions denoted by
$\mathcal B^\infty[a,b]$ and called the Baire algebra.
Borel proved that
for every such function $g$
the variations
\[
\text{Var}_f(\{\xi\leq g<\eta)
\]
exist when
$f$ is a  non-decreasing continuous function
on $[a,b]$ and in this
way
one defines
the Borel integrals by a limit as in Exercise 0.1 for every 
bounded Baire functions.

\medskip

\noindent
{\bf{Remark.}}
The    set-theoretic constructions which lead to Baire functions are
presented in great detail in 
Baire's original work.
Borel gave later
gave an abstract theory where measures and their integrals are
defined on sample spaces
$(\Omega,\mathcal B)$ where
$\mathcal B$ is a Boolean $\sigma$-algebra of subsets of
a set $\Omega$.
This abstract theory is exposed in ¤ 1.
The crucial point in Borel's approach is that
transfinite induction leads to the \emph{Borel algebra}
which by defitiion is the smallest Boolean $\sigma$-algebra if subsets on the real line which
contains all open intervals.
Moroever, for every continuous and non-decreasing function $f$
and every bounded Borel set $U$ one can define the variation of $f$ over $U$.



\medskip



\centerline {\bf{Lebesgue theory.}}
\medskip


\noindent
By  a null set on  the real  line one means a set $E$ such that for every
 $\epsilon>0$ there exists a family of open intervals
 $(a_\nu,b_\nu)$ whose union contains $E$  while
\[
 \sum xxx<\epsilon
\]
In his thesis from 1902, Henri
Lebesgue 
introduced a class $\mathcal L$ of sets as follows:
If $E$ is a bounded subset of ${\bf{R}}$ its outer Lebesgue meaure is defined
by
\[
|E|^*=\inf_{E\subset U}
\, |U|
\]
where $U$ are bounded open sets.
The inner measure is defined by
\[
|E|_*= \max_{K\subset E}\, |K|
\]
where $K$ are compact subsets of $E$.
When $|E|^*=|E|_*$ one says that
$E$ is measurable in the sense of Lebesgue
and the common number is called the Lebesgue measure.
Next, a bounded real-valued function $f$
defined on some compact  interval $[a,b]$ is called Lebesgue measurable if the sets
\[
[a,b]\cap\, \{a\leq f<b\}
\]
belong to $\mathcal L$ for every pair $a<b$.
By decomposing the range of a bounded Lebesgue measurable function
$f$ defined in a compact interval $[a,b]$ one defines
the Lebesgue integral
\[
\int_a^b\, f(x)\, dx
\]




\medskip

\noindent
{\bf{0.2.9 Non-measurable sets.}}
There exist
non-measurable sets but in 
practice one does not encounter these ugly sets. In fact, one must appeal to
the Axiom of Choice to exhibit examples.
Using this axiom there exists a subset
$E$ of  the open interval $(0,1)$ with the property
that the
sets $\{E+ q\}$ are disjoint when $q$ runs over the set 
of rational numbers.
This set cannot be measurable. The reason is that
the disjointness would entail that if $q_1,\ldots,q_N$ is a set of rational numbers
between 0 and 1 then
\[
N\cdot |E|_*=
\sum_{\nu=1}^{\nu=N}= |E+q_\nu|_*\leq 2
\]
where the last equality holds since
each set $E+q_\nu\subset [0,2]$.
Since $N$ can be arbitrary large we have
$|E|_*=0$.
So if $E$ is measurable we have
$|E|= |E|_*=0$, i.e $E$ is a null set. 
Since $E+q$ is  translate of $E$ they also give  null sets 
for every rational number.
But a denumerable union of null sets is a null set which
gives a contradaction since
 $\cup \, (E+q)$ with the union taken over all rational numbers
is the whole real line.

A major result in the Lebesgue theory is the
\emph{almost everywhere existence of
Lebesgue points}.
More precisely, in his thesis Lebegue proved that
when $f$ as above is bounded and Lebesgue measurable on some
open interval $(a,b)$, then
\[
\lim_{h,k}\,\frac{1}{h+k}\cdot \int_{x-k}^{x+h}\, |f(s)-f(x)|\, ds=0
\]
hold for almost evety $a<x<b$, where the limit is taken while $h$ and $k$
tend to zero.
Let $\frak{Leb}(f)$
denote the set of $x$ for which (xx) holds.
So Lebesgue proved that
$(a,b)\setminus \frak{Leb}(f)$ is a  null set.
The proof of this result is given in ¤ xx
and there we also present Lebesgue's extension to
higher dimenbsion where one regards the $n$-dimensional lebegue measure
in
${\bf{R}}^n$.

\bigskip

\noindent
{\bf{Existence of derivatives.}}
Another major result due to  Lebesgue  is the almost everywhere existence of
derivatives when $f$ is a non-decreasing function 
defined  on some interval $(a,b)$ on the real line.
To begin with
such a function $f$ may contain jumps. Namely, for evey $a<x<b$ we put
\[
f_*(x)=\lim_{\xi<x}\, f(\xi) \quad \&\quad  f^*(x)=\lim_{\eta>x} f(\eta)
\]
where the limits are taken as
$\xi\to  x$ and $\eta\to x$.
Since $f$ is non-decreasing we have
\[ 
f_*(x)\leq f(x)\leq f^*(x)
\]
for every $x$.
Moreover, the reader can check that $f$ is continuous at $x$
if and only if $f_*(x)= f^*(x)$.
If  the strict inequality $f^*(x)>f_*(x)$
occurs, the function $f$ has a jump discontinuity at $x$.
By assumption $f$ is bounded, i.e. $f(b)-f(a)$Êis finite. From
this the reader can check that
jumps can only occur at a denumerable  set of points
$\{x_\nu\}$.
For every such jump we define the function
$s_\nu(x)$ which is
zero if $x<x_\nu$ and equal to
$f^*(x_\nu)-f_*(x_\nu)$ if $x\geq x_\nu$.
Then the function
\[
s_f(x)=\sum\, s_\nu(x)
\] 
is non-decreasing and 
the reader can check that
\[
f-s_f(x)= f_0(x)
\]
is a non-negative and non-decreasing continuous function.
one refers to $s_f(x)$ as the jump-function assocaiged to $f$.
In ¤ xx we prove that there exists a null set $E$ such  that both 
$s_f$ and $f_0$ have ordinary derivatives
at every $x\in (a,b)\setminus E$, and here the
derivative of $s_f$ is zero.
\medskip

\noindent
{\bf{Remark.}}
Alreadt the case for jump-functions is quite remarkable.
More precisely, let $\{x_\nu\}$ be an arbitrary denumerable subset of
$(a,b)$ and $\{\rho_\nu\}$ a sequence of positive numbers where
$\sum\,\rho_\nu<\infty$.
Now we get the non-decreasing function
\[ 
S(x)=\sum\,\rho_\nu\cdot s_\nu(x)
\]
The fact that $S$ has an ordinary derivative which is zero outside 
a null set is not evident. In fact, this fact constitutes one of the
high points in  Lebesgue theory.
The proof is given in ¤ xx.
\medskip

\noindent
{\bf{Cantor sets and their Lebesgue functions.}}
Starting for set-theoretic consgructions  by Cantor, one
gets a quite extensive family of non-decreasing contionuous functions
which have
ordinary derivatives equal to zero outside a null-set, and yet they are not reduced to
contants.























Lebegue's theorem is proved in  ¤ xx.
An extension of this result
applies to arbitrary continous and real-valued functions
$f$ defined on open intervals $(a,b)$.
More precisely one has the
\emph{Denjoy-Young Theorem}.
Since this result illustrates the  philosopuhy in measure theory
we announce it already in this introduction.
Let $f(x)$ be a real-valued continuous function on an open interval $(a,b)$.
For each $a<x<b$ we set
\[ 
D^*(x)=\limsup\, \frac{f(x+h)\vvv f(x\vvv k)}{h+k}
\quad\&\quad
D\uuu *(x)=\liminf\, \frac{f(x+h)\vvv f(x\vvv k)}{h+k}
\]
where $h$ and $k$ are positive when we pass to the limits above.
It is clear that $f$ has a derivative in the usual sense
at a point $x$ if and only if
$D_*(x)=D^*(x)$.
The Denjoy\vvv Young result is:

\medskip

\noindent
{\bf{Theorem.}}
\emph{Outside a (possibly empty) null\vvv set $E$ of $(a,b)$
the following two possibilities occur for each
$x\in (a,b)\setminus E$: Either there exists a common finite limit
$D^*(x)= D\uuu *(x)$
or else one has}
\[
D^*(x)=+\infty\quad\text{and}\quad D\uuu *(x)=\vvv \infty
\]
\medskip

\noindent
The  material devoted to the 1-dimensional 
case in Chapter 1  is quite demanding and
often more involved compared to the general theory
which is elegant but the  proofs are often
quite straightforward and rely only upon
"clever set-theoretic constructions".
But the role of general measure theory cannot be underestimated.
For example, in functional analysis  measures are often  used to
construct
dual spaces and also perform integrals where
the integrand in general can be an operator-valued function. 
This is for example
used for such
crucial resuilts as Hilbert's spectral theorem for
self-adjoint operators on
infinite-dimensional Hilbert spaces.
A more recent
use of measure theory is due to Laurent Schwartz who introduced distributions
which has become a fundamental tool in PDE-theory.
Every distribution in an euclidian space is for example locally
a finite sum of distribution derivstives of Riesz measures.

\bigskip




\centerline{\emph{Abstract measure theory}}

\medskip

\noindent
Here one studies
$\sigma$-additive measures defined on
an abstract Bolean $\sigma$-algebra of sets.
This elegant and powerful theory is due 
to Emile Borel and was initiated in his 
thesis from 1895 and completed in 
later work. The material in ¤ 1 is based upon
the article [Borel] from 1908.
One starts from a sample space $\Omega$ and 
a Boolean $\sigma$-algebra $\mathcal B$ of subsets.
The  pair $(\Omega,\mathcal B)$ gives 
a  class of $\sigma$-additive measures and
for each specific measure $\mu$ there exists the family
$\mathcal N_\mu$ of its null sets.
One  proceeds to study 
$\mu$-measurable functions  which are identified 
when they agree outside a null set.
This leads to the construction
of integrals for every 
$\mu$-measurable function. 
Borel defined 
integrals of   a $\mu$-measurable function
$f$, using a 
a partition of  its values.
Namely, one  first regards   $\mu$-measures of 
inverse images of sets $\{a\leq f< b \}$
for all pairs of real numbers $a<b$,  and after a limit
where $\max(b-a)\to 0$
one gets the Borel integral denoted by
\[
\int f\cdot d\mu
\]
Consider as an example the case
when the $\sigma$-additive measure $\mu$ is non-negative and
has total mass one, i.e.
$\mu(\Omega)=1$.
Let  $f$ be a $\mu$-measurable function whose range is confined
to an interval $[0,A]$ with
$>0$, i.e. $f$ is non-negative and
is $\leq A$ on $\Omega$.
Now there exists a non-decreasing function 
on the real $s$\vvv line defined by
\[
\mu_f (s)= \mu\{f\leq s \}
\]
It is zero if $s<0$ and 
$\mu_f(A)=1$.
The $\sigma$-additivity of $\mu$ entails
that
the function is right continuous, i.e.
\[
\lim_{\epsilon\to 0} \mu_f(s+\epsilon)= \mu_f(s)
\] 
hold for every $s$, where $\epsilon>0$ during the passage to the limit.
In ¤ x we show the equality
\[
\int\uuu\Omega\, f\cdot d\mu=\int_0^A\,(A-\mu_f(s))\, ds\tag{*}
\]
\medskip

\noindent
The integral in the right hand side
can be computed in a 
similar fashion as  the
usual Riemann integral which we  explain  later on.
The   merit in 
Borel's construction of integrals it that they enjoy  "robust properties"
which can be seen already in the case of integrals of continuous functions on
on the real $x$-line, taken with
respect to the ordinary measure $dx$. Via Borel's ingenious idea to
perform partitions of the range
of a continuous function, the
approximations of
$\int\, f(x)\, dx$ appear with  a rate which does not dened upon the modulus of continuity of
$f$. 
It is  this improved rate of approximation which makes it possible 
to construct integrals of functions in  a far more extensive class
compared to those which appear in
Riemann integrals.


\bigskip

\noindent
{\bf{Riesz' representation theorem.}}
An important contributions was   given by F. Riesz
around 1910.
He found a  representation of 
the dual space of $C^0(S)$ when $S$ is a compact Hausdorff space.
To begin with Riesz introduced the vector space
$\mathcal E(S)$  of real-valued bounded functions on $S$ which
are ${\bf{R}}$-linear combinations of characteristic functions taken over sets of the form
$U\cap F$ where $U\subset S$ are open and $F\subset S$ are closed.
Under the maximum  norm
this gives a normed vector space and let $\mathcal R(S)$ be its
completion, i.e. vectors in
$\mathcal R(S)$ are bounded real-valued functions on $S$ which
appear as a uniform limit of a sequence in $\mathcal E(S)$.
It is easily verified that
$C^0(S)$ appears as a closed subspace of $\mathcal R(S)$.
The Hahn-Banach  theorem  yields a surjective map
\[
\mathcal R(S)^*\to C^0(S)^*\tag{i}
\]
i.e. every continuous linear functional  on
$C^0(S)$ has a norm-preserving extension
to $\mathcal R(S)$.
Next, let $\mathfrak{B}(S)$ be the Boolean algebra of subsets of
$S$ generated by open subsets.
If $L$ belongs to the dual space
$\mathcal E(S)^*$ we get
an additive measure $\mu$
defined on 
$\mathfrak{B}(S)$ by
\[
\mu(\Omega)= L(\chi_\Omega)
\]
where $\chi_\Omega$ is the characteristic  function of a set
$\Omega\in\mathfrak{B}(S)$.
Exactly as in
Borel's  constuctions there exist integrals
\[
\int_S\, f\cdot d\mu\quad\colon\, f\in C^0(S)
\]
which arise after a decomposition of the range of $f$.
The surjective map in (i)   entails  that
every $\lambda\in C^0(S)^*$ is obtained via
the integrals in the right hand side above, where
the additive measure $\mu$ on $\mathfrak{B}(S)$
is found after a norm-preserving extension of
$\lambda$.
But this norm-presering extension is not unique because
$C^0(S)$ is a proper subspace of $\mathcal E(S)$.
Riesz proved that a \emph{unique norm-preserving extension
exists}  via an additive measure $\mu$ satisfying
a certain regularity condition which goes as follows:
First, for every set $\Omega\in \mathfrak {B}(S)$
the total variation of $\mu$ over $\Omega$ is defined by
\[
|\mu|(\Omega)=\max_{A\subset \Omega}\, \mu(A)+|\mu(\Omega\setminus A)|
\]
with the maximum taken over 
$A$-sets in $\mathfrak{B}(S)$.
With this notation $\mu$ is regular in the sense of Riesz if
\[
\max_{K\subset U}\, |\mu|(U\setminus K)=0\tag{*}
\]
hold for every open set $U$, where the maximum is taken over compact subsets of
$U$.
In 1¤ xx we prove that
for every additive measure  $\mu$ as above there exists a unique regular measure
$\mu_*$ such that
\[
\int_S\, f\cdot d\mu= \int_S\, f\cdot d\mu_*\quad\colon\, f\in C^0(S)
\]
From this it follows that
$C^=(S)^*$ can be identified with the space of 
additive measures on $\mathfrak{B}(S)$ satisfying (*).
In the special case when
$S$ is a compact subset of ${\bf{R}}^n$
for some $n\geq 1$ this leads to a fairly  concrete description of
$C^0(S)^*$ which is exposed in ¤ xx.




















\bigskip


\noindent
{\bf{Lebesgue theory.}}
 In ¤ 3 we expose  results  due to Henri Lebesgue
whose pioneering work from 1902
has become a veritable cornerstone in analysis. 
Here the   notion of \emph{Lebesgue points} plays a central role. 
A major discovery  by Lebesgue 
is the \emph{almost everywhere
existence of Lebesgue points}.
We  remark  that  the gemoetry in euclidian spaces 
is needed to arrive at this result,  i.e. Lebesgue's theorem cannot be incorporated in
the abstract measure theory.
The notion of \emph{null-sets} in Lebesgue's  sense 
is explained  in ¤ 3. Here we recall that 
a subset $A$ of ${\bf{R}}^n$
is a null-set  if there to every $\epsilon>0$
is possible to cover $A$ by a family
of open balls $\{B_\nu\}$
such that
\[
\sum\,\text{vol}_(B_\nu)<\epsilon 
\]
where we refer to the ordinary $n$-dimensional
volume of every open ball.
Lebesgue proved that if 
$E$ is a compact set, then
$E\setminus \mathcal L(E)$ is a null-set.
Here a point $p\in E$ is a Lebesgue point
if
\[
\lim_{\epsilon\to 0}\, 
\frac{B_p(\epsilon)\setminus E}{\epsilon^n}=0
\]
where $B_p(\epsilon)$ denote open balls of radius $\epsilon$ centered at $p$.
The reader may notice that (*) means that the compact et $E$ is 
"fat" form a measure theoretic point of view" around $p$.
The fact that $\mathcal L(E)\setminus E$ is a null set even in the case when
$E$ has no interior points is quite remarkable.
\medskip



\noindent
{\bf{Hausdorff dimensions.}}
Inspired by Lebegue's work, Hausdorff introduced
a more extensive procedure to measure the size of
sets which in general are null sets.
Let  $\alpha>0$ be a positive  real number.
For each bounded set $E$ in 
${\bf{R}}^n$ we perform the following
condtructions: First, if $\delta>0$ we can cover $E$ by a finite family of
open balls $\{B_k\}$ where every ball has radius $\leq \delta$ and set
\[
H_{\alpha,\delta}(E)=\min\, \sum\, \text{rad}(B_k)^\alpha
\]
with the minimum taken over families of balls with radius $\leq\delta$.
These $H$-numbers increase with $\delta$ and we put
\[
H_\alpha(E)=\lim_{\delta\to 0}
H_{\alpha,\delta}(E)
\]
This number can be zero, finite or infinite.
With $\alpha0n$ one finds that
$H_n(E)=0$ ifn and only if $E$ is a null set in Lebegue's sense.
When $0<\alpha<n$ these  Hausdorff dimensions are used to
investigate  "thin sets" which are not covered by
ordinary Lebesgue theory.
In potentail theory other notions of thin sets appear.
For example, we regard compact subsets $E$ of the closed unit interval
and study integrals
\[
\int_E\, \log \frac{1}{|x-t|}\, dt
\]
which can be defined for every $0\leq x\leq 1$.


\medskip


\noindent
{\bf{Other topics.}}
In ¤ 5  we prove
Stokes Theorem for domains in
${\bf{R}}^n$
where 
irregular points on the boundary can appear.
In ¤ 6 and 7 we study 
the Hardy-Littlewood maximal function
and the Rademacher functions, and 
¤ 8 is devoted to the  construction of   the Brownian motion
where the main result is 
the almost everywhere continuity of individual
Brownian paths.




\bigskip




\newpage



\centerline{\bf{Historic comments.}}
\medskip




\noindent
A problem which
played an important role
to develop
general measure theory appeared in
the article
\emph{Sur la distribution de l'ectrecitŽ ˆ la surface
des conducteurs fermŽs et des conducteurs ouverts} from 1886
by  G. Robin. He  asked
if every
compact set
$E$ in ${\bf{C}}$ without interior points 
carries a distribution of mass whose logarithmic potential function is constant
on $E$. Robin's problem led to 
the
notion of
sets of absolute harmonic measure zero and other 
thin sets. Modern integration theory started in work by Stieltjes from 1894
in connection with moment problems. 
He  considered the class of 
non-decreasing continuous functions
$F(x)$ defined on $x\geq 0$ where 
$F(0)=0$ and $F(x)|to 1$ as $x\to +\infty$, and the integrals
\[
m_k(F)= \int_0^\infty\, x^k\cdot dF(x)<\infty
\] 
for every positive integer $k$.
If $G$ is another function  of this form and the moments
$m_k(F)=m_k(G)$ for every $k\geq 1$, the question arises if
the two functions are identical.
Stieltjes' found examples where $F\neq G$
even if they have the same moments.
This "negative answer" illustrates that the family of all
probablity measures on $x\geq 0$ is quite ample.
In ¤ xx we shall construct   examples where
Stieltjes' phenomenon appears.



\medskip


\noindent
In addition to pioneering work by Stieltjes, Borel and Lebesgue,
important contributions are also due
to Vitali, F. Riesz and Norbert Wiener.
Some  
results about convergence were established by Vitali in the article 
\emph{Sulle funzione integrali} [Atti. R. acad. Sci. di Torino: 1905]
which put  earlier results by Lebesgue
in a broader context.
Staying in an euclidian space
${\bf{R}}^n$, F. Riesz
constructed a class of  measures in
${\bf{R}}^n$ where
Borel's abstract theory is applied to the  $\sigma$-algebra
of Borel sets in ${\bf{R}}^n$, i.e. the  smallest
$\sigma$-algebra which contains all open and closed sets.
One consequence of  Riesz' theory goes as follows:
The solution of the Dirichlet problem in the unit disc yields
a 1-1 correspondence between
the class of positive  harmonic functions $H(x,y)$ in the open unit disc
$D=\{x^2+y^2<1\}$ normalised so that $H(0,0)=1$,
and the class of probability measures 
supported by the unit circle
$T=\{x^2+y^2=1\}$. 
A notable point
is that the class contains 
measures which are singular with respect to the angular Lebesgue measure on 
$T$.
A more general construction due to Wiener works for
every bounded open set $\Omega$ even if the Dirichlet problem cannot be solved for
every continuous boundary function $f$ in $C^0(\partial\Omega)$.
More precisely, for each  $z\in\Omega$, Wiener  constructed a distinguished
probability measure $\mathfrak{m}^\Omega\uuu z$
supported by $\partial \Omega$ such that
each $f\in C^0(\partial\Omega)$ produces a unique harmonic function $W\uuu f$
defined in $\Omega$ by
\[
W\uuu f(z)=
\int\uuu{\partial\Omega}\, f(\zeta)\cdot \mathfrak{m}^\Omega\uuu z(\zeta)
\]
Wiener's result is proved in the chapter about harmonic and subharmonic functions.
In Ergodic Theory
measures are used  frequently.
The literature is extensive and
current research  active but  we  shall not enter a discussion of 
this important and very extensive subject.








\medskip

\noindent
{\emph{Infinite products of measure spaces.}}
A  method to construct integrals
over infinite product spaces was carried out by  Daniell in [Dan].
It is
logically transparent but
has a disadvantage because  one cannot so easily
call upon existing theorems in Lebesgue theory from the finite
dimensional case.
To overcome this,  Norbert Wiener used \emph{binary expansions}
in order to extend 
the Lebesgue measure to an infinite  product  of
${\bf{R}}$. The crucial point  is the construction
of  
a measure preserving map
from the 
the two-dimensional unit square
$\square=\{(x,y)\colon\, 0<x,y<1\}$ onto the interval $(0,1)$
which goes as follows:
Every real number  $0<x<1$ has a  binary expansion:
\[
 x=\alpha_1/2+\alpha_2/4+\ldots\quad\,\, \alpha_k=0
 \,\,\text{or}\,\, 1
 \]
 Similarly $0<y<1$ has a binary expansion
 \[
  y=\beta_1/2+\beta_2/4+\ldots\quad\,\, \beta_k=0
 \,\,\text{or}\,\, 1
\]
These expansions are unique  when one prescribes that the expansion never terminates 
with a sequence where the number 1 appears. For example, one represents
$1/4$ by $0,1,0,,0\ldots$ while the sequence $0,0,1,1,1,\ldots$ is not allowed.
A pair of sequences as above
is  arranged
into a single sequence which  is used to
express a real number $0<t<1$ whose binary series is:
\[
 t(x,y)=
\alpha_1/2+\beta_2/4+\alpha_2/8+\beta_2/16+\ldots\tag{*}
\]
This yields a  bijective map from $\square$ onto
$(0,1)$ which 
is  \emph{measure preserving}, i.e. if
$F(x,y)$ is a continuous function of $(x,y)$ then
\[
\iint_\square\, F(x,y)\cdot dxdy=\int_0^1\, f(t)\cdot dt
\quad\text{where}\quad f(t(x,y))= F(x,y)
\]
In this way     Lebesgue theory in
dimension two can be recaptured from the one-dimensional case.
Similar measure preserving transformations from
${\bf{R}}^n$ into ${\bf{R}}$ exist for every $n\geq 2$ and once this is
achieved it is not difficult to construct a measure preserving
transformation from a denumerable product to the real $t$-line.
Details of this construction appear in the text\vvv book
[Paley\vvv Wiener].
\medskip

\noindent
Another  issue are product spaces with infinitely many factors
where one seeks to extend  the Fubini theorem.
Here a major contribution is due to Jessen in
the   work  \emph{Bidrag til intergalteorin for funktioner av uendlig mange
variabler} [Copenhagen 1930]. His article
\emph{The theory of integration  in a space of infinitely  many
variables} [Acta math. 1933]
is a veritable classic with a wide range of 
applications, foremost in probability theory.
 \medskip

\medskip


\noindent
{\bf{The Vitali-Hahn-Saks theorem.}}
During the development of  functional analysis in a broad sense
which started 
around 1930, original results by Vitali were put into 
the context of  topological vector spaces and quite
general results were established by
Saks in the article
\emph{Integration in abstract metric spaces.} [Duke  Math. J. Vol 4: 1938].
Here one regards a Boolean 
$\sigma $-algebra $\mathcal B$
of subsets of a sample space
$\Omega$ and $\mu$ is a non-negative 
$\sigma$-additive meaasure
which assigns real numbers to sets in
$\mathcal B$.
In ¤ xx we introduce the family of $\mu$-continuous additive functions
and prove a result concerned with uniform convergence which ressembles the
Banach-Steinhaus theorem in  Frechet spaces.
As expected the Baire  category theorem plays an essential role in the proofs.
 \medskip



\noindent
{\bf {Probability theory.}}
A feeling  for  measure theory
arises via probabilistic
interpretations.
For example, if $\mu$ and $\nu$ is a pair of Riesz measures on
the real oine which both are non-negstive and have mass one, then
there exists the convolution $\mu*\nu$.
If $\mu$ and $\nu$ describe probability distributions of 
two random variables, then
 $\mu*\nu$ is the probability distribution of their sum under
the condition that they are independent.
In ¤ 8 we study the Brownian motion. Here we first expose Wiener's construction
of a stochastic process in continuous time
with independent increments while the outcome at each 
time-value is a normally distributed random variable.
To analyze individual Brownian paths
one needs a sample space which by Wiener's construction is
found by a denumerable infinite product
of "ordinary" measure spaces.
The whole study culminates in Theorem 9 in from ¤ 8.1  which
is one of the major results in this chapter. In ¤ 8.2 we have also included
the construction of a parabolic PDE-system which
governs a stochastic vector-valued process in continuous time.
This has been inserted since
such equations occur in many applications, foremost in quantum  mechanics but also in
the nowadays  popular subject referred to as "matheamatics of finance".

 
\medskip


\noindent
\emph{Ohter applications of measure theory.}
The text-book [Weil] by 
Andre Weil employs 
measure theoretic   results  to establish
reciprocity theorems and 
advanced results in 
class-field theory. In the appendix devoted to functional analysis we
establish the existence of Haar measures on
locally compact groups which in general are non-commutative.
\medskip




\noindent
{\emph{Integral inequalities and distribution theory.}}
The study of various $L^p$-estimates is an extensive subject where
Fourier analysis appears
together with
various geometric constructions such as Whitney coverings.
The reader may consult a number of excellent
text-books by Elias Stein and co-authors 
which treat the theory about  singular integrals.
Here we only give a brief account
about
the Hardy-Littlewood maximal function in
¤ xx.
Passing to differentiability one is led to distribution theory.
In fact, every 
distributions in
${\bf{R}}^n$ is  locally expressed by  finite sums of distribution derivatives
of Riesz measures. So  measure theory is  essential in order to grasp
the theory of distributions.

\bigskip


\noindent
Let us finish the introduction
by describing some  
results 
expressed via  measure theoretic
concepts but the  proofs require "hard analysis".
\medskip

\noindent
{\bf Hitting probability for the Brownian motion.}
The following result is due to the late
Bjšrn Dahlberg:

\medskip


\noindent
\emph{Let $U$ be a bounded open set in
${\bf{R}}^n$ defined by $\{F(x)<0\}$ where $F(x)$ is a 
Lipschitz continuous function and $\partial U=\{F(x)=0\}$. Then 
the class of null sets in $\partial U$
for the Brownian motion which starts
at some point $x_0\in U$ is equal to the class of subsets of $\partial U$ whose $(n-1)$-dimensional Hausdorff measure are zero.}
\medskip

\noindent
Above  $E\subset\partial U$ is a null set for the Brownian motion if the
probability to hit $E$ before the Brownian 
path reaches $\partial U$ at points outside $E$
is equal to zero.
For this discovery Dahlberg was awarded  the Salem 
Prize in 197?.
\bigskip

\noindent
{\bf {Carleson' convergence theorem in $L^2$.}}
In 1965 Lennart Carleson proved the following:
\medskip

\noindent
\emph{Let $\{a_n\}$ be a sequence of complex numbers whose $\ell^2$-norm
is finite, i.e. $\sum\, |a_n|^2$ is finite.
To every $N\geq 1$
one constructs Fourier's partial sum}:
\[ 
S_N(x)=\sum_{\nu=-N}^{\nu=N}\, a_ne^{inx}
\]
\emph{Then  $\lim_{N\to\infty}\, S_N(x)$ exists for all $0\leq x\leq 2\pi$
except for a set of 
Lebesgue measure zero.}
\medskip

\noindent
This result is one of the greatest achievements ever in mathematical analysis. 
In 2006 Carleson was awarded   the Abel Prize  for this   theorem
together with   his contributions in other areas of mathematics.
Let us only remark that Carleson's theroem came as surpsie even to specialists since 
Kolmogorov had contructrd an absolutely integrable function
$f$ on the unit circle whose  partial sums of its Fourier series
are \emph{everywhere divergent}.


\newpage






\centerline{\bf{0.1 The  Borel-Riesz theory.}}
\bigskip


\noindent
Let  $\mathcal B$ be a 
Boolean algebra  of sets and
denote by ${\bf{ba}}(\mathcal B)$
the space of additive and bounded real-valued functions
on $\mathcal B$. Thus, one considers maps
\[ 
E\mapsto \mu(E)
\]
Additivity means that $\mu(\cup \,E_\nu)=\sum\, \mu(E_\nu)$
when $\{E_\nu\}$ is a finite family of disjoint sets
in $\mathcal B$, and  boundedness means that there
exists a constant $C$ such that
\[
|\mu(E)|\leq C\quad\colon E\in \mathcal B\tag{i}
\]
Define  the non-negative 
function $\mu_+$
by
\[
\mu_+(E)= \max_{A\subset E}\, \mu(A)
\]
where  we declare that
$\mu(\emptyset)=0$.
\medskip

\noindent
{\bf{Exercise.}}
Show that $\mu_+$ is additive, i.e. 
\[
\mu_+(E\cup F)=
\mu_+(E)+
\mu_+(F)\tag{0.0.1}
\] 
hold for every pair of disjoint sets in
$\mathcal B$.
\medskip


\noindent
Now $\mu_+-\mu$ is a non-negative  additive function 
denoted by $\mu_-$ and we have
\[
\mu=\mu_+-\mu_-\tag{0.0.2}
\]
Hence $\mu$ is represented as the difference of two non-negative and additive functions.
If $E\in\mathcal B$ the total variation of $\mu$ over $E$ is defined by
\[
|\mu|(E)=\mu_+(E)+\mu_-(E)
\]
The reader may verify that
(i) above gives
\[
|\mu|(E)\leq 2C
\]
for every $E\in \mathcal B$.
\bigskip

\noindent
Let us now consider a compact topological  space $S$
which in addition is Hausdorff. 
Denote by $\mathcal B_S$ the
 Boolean algebra generated by
open sets in S. The reader can check 
that
every
set in $\mathcal B_S$ is  finite union of disjoint sets of the form
$U\cap F$ where $U$ are open and $F$ are closed.
Denote by $\chi(S)$
the linear space of real-valued functions on
$S$ given by
${\bf{R}}$-linear combinations of characteristic functions of
sets in
 $\mathcal B_S$, i.e.
 functions  of the form
 \[
 \phi=\sum\, c_k\cdot \chi_{E_k}
 \]
 where $\{E_k\}$ is a finite family of disjoint subsets from
 $\mathcal B_S$ and $\{c_k\}$ are real constants.
 To each pair
 $\phi\in\chi(S)$ and $\mu\in {\bf{ba}}(\mathcal B_S)$
 one defines the integral
 \[
 \int\, \phi\cdot d\mu= \sum\, c_k\cdot \mu(E_k)
 \]
\medskip

\noindent
{\bf{Exercise.}}
Prove additivity, i.e. that 
\[
 \int\, (\phi+\psi)\cdot d\mu=
  \int\, \phi\cdot d\mu+
  \int\, \psi\cdot d\mu\quad\colon \phi,\psi\in \chi(S)
 \]
 A hint is that
one  can  represent the two functions
 in (i) with respect to a common partition of
 $S$, i.e. there exists a familly of disjoint sets 
 $\{E_k\}$ so that
 \[
 \phi=\sum\, c_k\cdot \chi_{E_k}\quad\colon 
 \psi=\sum\, d_k\cdot \chi_{E_k}
 \]
 where $\{c_k\}$ and $\{d_k\}$ are constants.
 \medskip
 
 \noindent
 {\bf{0.1.2 Borel functions and their integrals.}}
 Via the maximum norm
 $\chi(S)$ is a normed vector space.
 If $\mu\in {\bf{ba}}(\mathcal B_S)$ its total variation  is 
denoted by $||\mu||$.
The construction of integrals gives
 \[
 | \int\, \phi\cdot d\mu|\leq |\phi|_S|\cdot ||\mu||
 \]
 where
 $|\phi|_S$ is the maximum norm of
 $\phi$.
The closure of
$\chi(S)$ taken in the
normed space of bounded
real-valued functions on
$S$
yields a Banach space denoted by
$\mathfrak{B}(S)$.
For each  $f\in \mathfrak{B}(S)$ a  $\mu$-integral is defined
as follows: By definition there exists a sequence
$\{\phi_n\}$ from $\chi(S)$ such that
$|f-\phi_n|_S\to 0$. When $n,m$ are positive integers we have
\[
|\int\, \phi_n\cdot d\mu
-\int\, \phi_m\cdot d\mu|\leq |\phi_n-\phi_m|_S\cdot ||\mu||
\]
The uniform convergence $\phi_n\to f$
entails that 
$\{|\phi_n-\phi_m|_S\}$ is a Cauchy-sequence
and hence there exists 
\[
\lim_{n\to\infty}\,
\int\, \phi_n\cdot d\mu
\]
It is clear that the last limit only depends on
$f$ and not upon the particular sequence in
$\chi(S)$ which approximates $f$ uniformly.
The common limit is defined as the
$\mu$-integral of $f$, and   
\[
f\mapsto \int\, f\cdot d\mu
\]
gives a linear functional on
the normed vector space
$\mathfrak{B}(S)$. This 
identifies
${\bf{ba}}(\mathcal B_S)$ with
a
subspace of the dual space
$\mathfrak{B}(S)^*$.
Conversely, let $L$ be a continuous linear functional on
$\mathfrak{B}(S)$ which means that there exists a constant
$C$ such that
\[
|L(f)|\leq C\cdot |f|_S\quad\colon f\in
\mathfrak{B}(S)
\]
Now $L$ yields a unique  additive measure
$\mu$ where
\[
\mu(E)=L(\chi_E)\quad\colon E\in\mathcal B_S
\]
We leave it to the reader that this entails that
\[ 
L(f)=\int\, f\cdot d\mu\quad\colon f\in \mathfrak{B}(S)
\]
Hence one has an isomorphism
\[
\mathfrak{B}(S)^*\simeq {\bf{ba}}(\mathcal B_S)\tag{*}
\]








\medskip


\noindent
{\bf{0.1.3 The dual of $C^0(S)$.}}
Tbe space of continuous and real-valued functions on
the compact space $S$ is  a   subspace of
$\mathfrak{B}(S)$.
To see this we take some
$f\in C^0(S)$ and notice that for every pair of real numbers
$a<b$, the
set
\[
\{s\colon a\leq f(s)<b\}
\]
belongs to $\mathcal B_S$.
If $\epsilon>0$ we  choose an integer $N$
so that
$N^{-1}>\epsilon$ and introduce the sets
\[
E^f_k(N)=\{s\colon\frac{k}{N}\leq f(s)<\frac{k+1}{N}\}
\]
where $k$ are integers. Since the range of $f$
is compact it follows that
$E^f_k(N)\neq\emptyset$ only hold for a finite
family of integers $k$, and 
we get a function in $\chi(S)$ defined by
\[
\phi=\sum\,\frac{k}{N}\cdot \chi_{E^f_k(N)}
\]
Here the maximum norm
$|f-\phi|_S<\epsilon$ and we conclude that
$f$ belongs to
$\mathfrak{B}(S)$.
The inclusion $C^0(S)\subset\mathfrak{B}(S)$
means that each $\mu\in {\bf{ba}}(\mathcal B_S)$
restricts to a continuous linear functional on
the normed vector space
$C^0(S)$. Hence there exists    a  map
\[
{\bf{ba}}(\mathcal B_S)\to C^0(S)^*
\]


\noindent
The  Hahn-Banach Theorem  shows  that this map is surjective
which gives
an isomorphism
\[
C^0(S)^*\simeq\frac{{\bf{ba}}(\mathcal B_S)}{C^0(S)^\perp}\tag{*}
\]
where
$C^0(S)^\perp$ is the space of  $\mu\in {\bf{ba}}(\mathcal B_S)$
such that
\[
\int\, f\cdot d\mu=0\quad \colon f\in C^0(S)
\]




\bigskip 
\centerline {\bf{ Riesz' representation theorem.}}
\bigskip


\noindent
A   measure $\mu$ in
 ${\bf{ba}}(\mathcal B_S)$ is said to be regular if the following hold 
for every set $A\in\mathcal B_S$:
\[
\min|\mu|(U\setminus A)=0\quad\&\quad
\min\, |\mu|(A\setminus K)=0\tag{0.1..4}
\]
 where the minimum  is taken over  open
 sets $U$ which contain $A$, respectively compact subsets
 $K$.
The family of these  measures is denoted by
${\mathfrak{M}}(S$).


\medskip

\noindent
{\bf{0.1.5 Theorem.}}
\emph{For each  $\mu\in {\bf{ba}}(\mathcal B_S)$
there exists a unique
$\mu^*\in\mathfrak{M}(S)$
such that}
\[
\int f\cdot d\mu=
\int f\cdot d\mu^*\quad\colon\,f\in C^0(X)\tag{*}
\]
\medskip

\noindent
\emph{The uniqueness part.}
Let us first  show that if a 
regular  measure $\mu^*$ exists above then it is unique. 
This  amounts to show that if a measure
$\gamma \in\mathfrak{M}(S)$ is such that
\[
\int\, f\cdot d\gamma=0
\]
for every $f\in C^0(S)$ then
$\gamma=0$.
To show this we argue by contradiction, i.e. suppose that
$\gamma (A)\neq 0$ for some
$A\in \mathcal B_S$.
Multiplying $\gamma$ with a constant we can assume that
$\gamma(A)=1$.
Let $0<\epsilon 1/4 $ and by (0.1.4) we find
a compact subset
$F$ of $A$ and an open set $U$ which contains
$A$ such that the total variation
\[
|\gamma|(U\setminus F)<\epsilon\tag{i}
\]
Notice that (i)  and the equality $\gamma(A)=1$ give 
\[
\gamma(F)\geq 1-\epsilon\tag{ii}
\]
Next, there exists $f\in C^0(S)$
whose range is contained in
$[0,1]$ while $f=1$ on $F$ and zero on $S\setminus U$.
It follows that
\[
\int f\cdot d\gamma\geq \mu(F)-|\int_{S\setminus F}\, fd\gamma|\geq
\mu(F)-|\gamma|(U\setminus F)\geq 1-2\epsilon>1/2
\]
This contradiction proves the uniqueness part in Theorem 0.1.5.
\bigskip


\noindent
\emph{The existence part.}
We are given $\mu$ and by (0.0.2) we can write
$\mu=\mu_+-\mu_-$. By additivity it suffices to prove the
existence of regular measures $\mu_+^*$ and $\mu_-^*$
in Theorem 0.1.5. So we can assume that
$\mu$ from the start is non-negative
and let $L$ be the associated linear functional from 
(0.1.2).
For every open set $U$ we set
\[
\mu_*(U)= \max_f\, L(f)\tag{i}
\]
with the maximum taken over all continuous functions
with range in $[0,1]$ and compact support contained in
$U$.
Next, if $K$ is a pair of compact sets we define
\[
\mu_*(K)=
\min_U\, L(f)\tag{i}
\]
with the minimum taken over 
continous functions with range in $[0,1]$
and $f=1$ on $K$.
We claim that
\[
\mu_*(K)+\mu_*(X\setminus K=1
\]
for every compact set.
To see thid we take $\epsilon>0$ and 
(i) gives some $f$ with compact support in $X\setminus K$ while
\[
\mu_*(X\setminus K)< L(f)+\epsilon
\]
Now $1-f$ is identically one on $K$ and hence
$L(1-f)\geq \mu_*(K)$ which shows that (*) is majorised by
\[
L(f)+L(1-f)+\epsilon= 1+\epsilon
\]
Since $\epsilon$ was arbitrary themleft hand side in
(xx) is $\leq 1$.
Conversely, we find some $f$ which is identically one on $K$ and
\[
\mu_*(K)>L(f)-\epsilon
\]
Now  $\{f\leq 1-\epsilon\}$ is disjoint from $K¨$ and we can find
a cotinuous function $g$ with range on $[0,1]$ which is
equal to one on this set while $g=0$ on $\{f\geq 1-\epsilon/2\}$.
It follows that
$\mu(X\setminus K)\geq L(g)$ and together with
(xx) we have
\[
\mu_*(K)+\mu_*(S\setminus K)> L(f)+L(g)-\epsilon
\]
At the same time we notice that
\[
f+g\geq 1-\epsilon
\]
holds in $x$ and since $L$ was non-negative we get
\[
L(f)+L(g)? L(f+g)\geq 1\epsilon
\]
Since $\epsilon$ was arbitrary small we see that (x) and (xx) gives
the opposite inequality in (xx).
\medskip


\noindent
{\bf{Exercise.}}
Conclude via (*) that $\mu^*$ is an additive and regular measure on $S$.
\medskip


\noindent
There remains to prove the equality
\[
L(f)= \int\, f\cdot d\mu_*\tag{*}
\]
for every continuous function.
Since 
every $f\in C^0(S)$
is the difference of two non-negative functions
$f_+=\max(f,0)$ and $f_-=-\min(f,0)$,
additivity 
implies that it suffices to show
(*) when $f$ is non-negative.
For every partition
$0=a_0<a_1<\ldots <a_M$ where $a_M$ is strictly 
larger than the maximum of $f$, 
the reader should check that there
exists   a sequence
$\{\xi_k\}$ with $a_k\leq \xi_k\leq a_{k+1}$
and 
\[
L(f)= \sum\, \xi_k\cdot \mu(\{a_k\leq f<a_{k+1}\})
\]
At the same time we have
\[
\int\, f\cdot d\mu_*\leq
 \sum\, a_{k+1}\cdot \mu_*(\{a_k\leq f<a_{k+1}\})
\]
The construction of $\mu_*$ entials that
\[
\mu_*(\{a_k\leq f<a_{k+1}\})\leq \mu(\{a_k\leq f<a_{k+1}\})
\]
for every $k$.
So if $\delta=\max\, a-{k+1}-a_k$ we get
\[
\int\, f\cdot d\mu_*\leq  \delta\cdot
\sum\, \xi_k\cdot \mu(\{a_k\leq f<a_{k+1}\})
\]
and the last term is majorised by $\mu(S)$ which is a given finitei constant.
Passing to refined partions with $\delta\to 0$ we conclude that
\[
\int\, f\cdot d\mu_*\leq  L(f)
\]
\medskip

\noindent
To prove the opposite  inequality we shall employ special partitions.
We are given $f$ and say that
a real number $\beta$ is $L$-critical if
there exists a positive number $c$ such that
\[
\mu(\{\beta-\epsilon\leq f\leq \beta+\epsilon\})\geq c
\]
By additivity and the finiteness of $\mu(S)$
it is clear that
for every $c>0$ the set of
$\beta$ for which (x) hold is finite.
From this observation the reader can check that for
every $\delta>0$ there is  a partition
$\{a_\nu\}$  where $a_{k+1}-a_k\leq \delta$ hold for every $k$
and none of the $a$-numbers are $L$-critical.
Next, we notice that
\[
L(f)\leq \delta+\sum\, a_k\cdot \mu(\{a_k\leq f<a_{k+1}\})
\]
The careful choice of the $a$-numbers
gives
a sequence $\{b_k\}$ with $a_k<b_k<b_{k+1}< a_{k+1}$  
and 
\[
\sum\, a_k\cdot \mu(\{a_k\leq f<a_{k+1}\})
\leq \delta+ \sum\, a_k\cdot \mu(\{b_k\leq f\leq b_{k+1}\})\implies
\]
\[
L(f)\leq 2\cdot \delta +a_k\cdot \mu(\{b_k\leq f\leq b_{k+1}\})\tag{i}
\]
Next, for every $k$ we can find
a continuous function $g_k$ with range in $[0,1]$ which is identically one on
the compact set
$\{b_k\leq f\leq b_{k+1}\}$ and  at the same time has compact support in
$\{a_k\leq f<a_{k+1}\}$.
Now the reader can check that
the construction of $\mu_*$ entails that
\[
\int\, f\cdot d\mu_*\geq
 \sum\, a_k\cdot \mu(\{b_k\leq f\leq b_{k+1}\})\tag{ii}
\]
Together with (i) it follows that
\[
L(f)\leq 2\cdot \delta
\int\, f\cdot d\mu_*
\]
Above $\delta$ can be chosen arbitary small which proves the equality (*)
and  finishes the proof of Theorem xx.




\bigskip



\centerline {\bf{0.1.7 $\sigma$-additivity and the algebra
$\widehat{\mathcal B}_S$}}
\bigskip


\noindent
Above we started from the Bolean algebra $\mathcal B_S$
generated by open subsets of $S$.
By general set-theory there exists a unique smallest
$\sigma$-algebra $\widehat{\mathcal B_S}$
which contains
$\mathcal B_S$.
Sets in this family are called Borel sets.
Let us remark that one can construct
$\widehat{\mathcal B_S}$ by transfinite induction using
ordinal numbers. We shall not pursue this in detail but
refer to original work by Baire and Borel where
these constructions
are carried out in detail.
The reader may also consult the text-book [Kol]
by Kolmogorov for a detailed account
about the contruction of $\sigma$-algebras and
extensions of $\sigma$-additive measures.
A major fact is the following:
\medskip

\medskip

\noindent
{\bf{0.1.8 Theorem.}}
\emph{Each  $\mu\in\mathfrak{M}(S)$ extends in a unique way
to a $\sigma$-additive measure $\widehat{\mu}$
on
$\widehat{\mathcal B_S}$. Conversely, every
$\sigma$-additive measure  on
$\widehat{\mathcal B_S}$ is equal to
$\widehat{\mu}$ for a unique
Riesz measure.}

\medskip

\noindent
In ¤ 4 we  prove  this theorem in detail
when
$S={\bf{R}}^n$ for some $n\geq 1$.

\medskip


\noindent
{\bf{0.1.9 Null sets.}}
Let $\mu$ be a non-negative Riesz measure
on the compact space $S$.
A subset $G$ is a null set with respect to $\mu$ if
\[
\min_{G\subset U}\, \mu(U)=0
\]
where $U$ are open sets containing $G$.
Let $\mathcal N(\mu)$ be the family of these null sets.
Additivity entails that
a finite union of null sets again is  null set.
Less obvious is that a denumerable union of null sets
is a null set.
To show this we consider s sequence $\{G_1,G_2,\ldots\}$
in $\mathcal N(\mu)$.
Let $\epsilon>0$ and for each $n$ we find an open set
$U_n$ containing $G_n$ such that
\[
\mu(U_n)\leq 2^{-n}\epsilon
\]
Now $U^*=\cup \,U_n$ contains
$\cup\, G_n$. Since $\mu$ is regular 
there exists a compact subset
$F$ of $U^*$ such that
$\mu(U^*\setminus F)<\epsilon$.
Now $\{U_n\}$ is an open covering of $F$ and Heine-Borel's
Lemma gives
some integer $N$ such that
the union of $U_1,\ldots,U_N$ contains $F$.
It follows that
\[ 
\mu(U^*)=\mu(U^*\setminus F)+ \mu(F)\leq
\epsilon+\mu(U_1\cup\ldots\cup U_N)\leq
\epsilon+\sum_{k=1}^{k=N}|\,
\mu(U_k)\leq 2\epsilon
\]
Since $\epsilon$ is arbitrsty small we conclude that
$\cup \,G_n$ is a null set.
\medskip

\noindent
In ¤ II where  abstract measure theory is exposed,
the result above is the starting point for the
study of "almost everywhere defined 
functions"
with respect to $\mu$
which leads to the space $L^1(\mu)$ of functions which are
integrable with respect to $\mu$.
\medskip
































 


















\newpage



\centerline{\bf{0.2  Lebesgue theory.}}
\bigskip



\noindent
The theory was  created  by Henri Lebesgue 
and presented in his monograph
\emph{Lecons sur l'integration et la recherche
des fonctions primitives} from 1904. We  expose  some
basic facts from his work and remark
that 
Vitali and de la VallŽ Poussin
later gave some simplifications of Lebesgue's original proofs.
A major result in ¤ III
is the existence of
\emph{Lebesgue points} which
implies that  measurable 
functions in Lebesgue's sense are 
realized in a  concrete way. For example, a bounded
Lebesgue measurable function $f$ is 
the pointwise limit outside a null set of 
a sequence of Lipschitz continuous functions
defined by mean values of  $f$ over smaller and smaller cubes
centered at the point where  pointwise
convergence takes place.
In ¤ 3.xx we also show that
outside a null set an arbitrary bounded
measurable
function
$f$ differs from an everywhere defined function
$f_*$ given as the pointwise limit of
a
non-increasing sequence of upper semi-continuus functions which
means that $f_*$ belongs to the second Baire class of functions. So
when one agrees to identify Lebegue measurable
functions which are equal  outside a null set, then
this class is reduced to a  restricted family of everywhere
defined functions.

\medskip


\noindent
The crucial  point in Lebesgue theory is to define
the $n$-dimensional volume of a bounded open set.
To achieve this we use \emph{binary  expansions} of real numbers.
If $n\geq 1$ and
$\square$ is a cube placed in
${\bf{R}}^n$
it has $2^n$ many corner points
and its size is measured
by the  positive number $a$ where  the distance between
two adjacent corner points is $a$, and the $n$-dimensional volume
is  $a^n$.
To construct the  $n$-dimensional measure
of an  open set $\Omega$ in ${\bf{R}}^n$ we employ
binary expansions 
of real numbers $x$:
\[ 
x=[x]+\sum_{k=1}^\infty\,\epsilon_k(x)2^{-k}\tag{i}
\]
where $[x]$
is the largest integer $\leq x$ and 
each $\epsilon$ is 0 or 1. The expansion is unique 
under the rule  that
the the sequence 
$\{\epsilon_k(x)\}$ never terminates with
1 all the time. For example,  the number $x=1/8$ 
has $\epsilon_3(x)=1$ while all other $\epsilon$-numbers are zero.
So it is not permitted  to represent $1/8$ by
the geometric series
$1/16+1/32+1/64+\ldots$.
If $N=0$ we put $\xi_0(x)=[x]$ and if $N\geq 1$
we put
\[
\xi_N(x)=[x]+\sum_{k=1}^{k=N}\,\epsilon_k(x)2^{-k}
\implies
\xi_N(x)\leq x< \xi_N(x)+2^{-N}\tag{ii}
\]
Next, if $n\geq 2$ and $p=(x_1,\ldots,x_n)$ is a point in
 ${\bf{R}}^n$ one takes the binary expansion of each
 coordinate
 and set
 $\xi_N(p)=(\xi_N(x_1),\ldots,\xi_N(x_n))$.
For each non-negative integer $N$
one associates the half-open cube
\[
\square_N(p)=\xi_N(p)+\square_N^*
\quad\colon\quad 
\square_N^*=\{(x_1,\ldots,x_n)\,\colon\, 0\leq x_k< 2^{-N}\}
\]
The reader may verify that
\[
q\in 
\square_N(p)\implies\xi_N(q)=\xi_N(p)\tag{iii}
\]
and the last equality entails that
$\square_N(q)=\square_N(p)$.
Let us now consider a bounded open set
$\Omega$ in ${\bf{R}}^n$.
To each $p\in \Omega$ we find the unique smallest
non-negative integer $N_\Omega(p)$
such that
$\square_{N_\Omega(p)}\subset\Omega$.
If $k\geq 0$ we put
\[
D_k(\Omega)=\{p\in\Omega\,\colon\,N_\Omega(p)=k\}\tag{iv}
\]
Here (iii) entails that 
$\{D_k(\Omega)\}$
are disjoint subsets of
$\Omega$. Since $\Omega$ is open it is clear
that the union is equal
to $\Omega$.
Moreover (iii) entails 
that when $D_k(\Omega\neq \emptyset $
then it is 
a  union of  
pairwise disjoint half-open cubes:
\[
D_k(\Omega)=\cup\, \square_N(p_\nu)
\]
Since $\Omega$ is bounded
 every such union is finite. Denote by 
$\mu_k(\Omega)$  the number
of cubes in this disjoint union.
The $n$-dimensional measure is defined by
 \[
 \text{vol}_n(\Omega)=
\sum_{k=0}^\infty\,  \mu_k(\Omega)\cdot 2^{-kn}\tag{*}
\]
\medskip

\noindent
{\bf{0.2.1 Unbounded open sets.}}
If $\Omega$ is an open unbounded set
we still get the unique partition 
formed by the disjoint subsets $\{D_k(\Omega)\}$.
One says that
$\Omega$ has a finite measure if
every 
$D_k(\Omega)$ is a finite union  and the series
\[
\sum\, \mu_k(\Omega)\cdot 2^{-kn}<\infty
\]

\medskip

\noindent
{\bf{Outer and inner measures.}}
Starting from the construction of $n$-dimensional measures
of  open sets one 
constructs  outer and inner measures of an
arbitrary bounded subset $A$  of ${\bf{R}}^n$.
The  outer measure is defined by:
\[
|A|^*= \min_{A\subset \Omega}\, \text{vol}_n(\Omega)
\]
In particular the outer measure 
is defined for every compact set $E$ and the inner measure of
$A$ is defined by
\[
|A|_*= \max_{E\subset A}\, |E|^*
\] 
where the maximum is taken over compact subsets of $A$.
\medskip

\noindent
{\bf{0.2.2 Definition.}}
\emph{A set $A$ in 
 ${\bf{R}}^n$ has a finite Lebesgue measure 
if
$|A|_*=|A|^*<\infty $ and this common number
is denoted by
$|A|_n$.}
\medskip

\noindent
{\bf{0.2.3 Null sets.}}
A  set is called a null set if
its outer measure is zero. The family of 
null sets is denoted
by
$\mathcal N({\bf{R}})^n$.
A property is said to hold almost everywhere if it is valid
outside a null set.
In Lebesgue theory one 
is often content to establish a result "almost everywhere", i.e.
null sets are reduntant.
Recall that a  set
$S$ is of type $G_\delta$ if it is
the intersection  of an decreasing sequence of open
sets $\{\Omega_n\}$. It is a set of type $F_\sigma$ if it is given
as the union of a decreasing familly of compact
sets.
\medskip

\noindent
{\bf{0.2.4 Exercise.}}
Show that if $A$ is  Lebesgue   measurable 
and
$\{E_\nu\}$ an increasing sequence of compact subsets such that
$|E_\nu|_n\to |A|_n$,
then $A\setminus \cup\, E_\nu$ is a null-set. Similarly, if
$\{\Omega_\nu\}$ an decreasing sequence of open sets
containing $A$ and
$|\Omega_\nu|_n\to |A|_n$ then
$\cap\, \Omega_\nu\setminus A$ is a null set.
Hence every measurable
set differs from
a set of type $F_\sigma$ by a null set, and similarly from
a set of type $G_\delta$.
\medskip

\noindent
{\bf{0.2.5 Lebesgue points.}}
Let $A$ be a  measurable set.
A point $x\in A$ has unit   density 
if
\[
\lim_{|\square|_n\to 0}\,
\frac {\text{vol}\uuu n(\square\setminus A)}{\text{vol}\uuu n(\square)}=0\tag{0.5.1}
\]
where 
the limit  is taken over
cubes which contain $x$.
It is not requested
that $x$ is the center of the cubes
and their sides need not be
parallell to the coordinate
axis.
The set  where  (0.5.1) holds is denoted by
$\mathfrak{Leb}(A)$.
A major result due to  Lebesgue 
asserts the following:
\medskip

\noindent
{\bf{0.2.6 Theorem.}}
\emph{For  every  measurable set $A$
it follows that
$A\setminus \mathfrak{Leb}(A)$ is a null set.}
\medskip

\noindent
This fundamental  result is proved in ¤ 3.
\medskip

\noindent
{\bf{0.2.7 Measurable functions.}}
Let $f(x)$ be a real-valued function defined in some open and bounded
subset
$\Omega$ of
${\bf{R}}^n$.
It is  measurable in the sense of Lebesuge if the sets
\[
A_f(a;b)= \{ x\in\Omega\colon a\leq f(x)<b\}
\]
are measurable for all pairs of real numbers $a<b$.
The function $f$ has  Lebesgue value $a$ at a point
$x_0\in\Omega$ if
\[
\lim_{|\square|_n\to 0}\, \frac{|A_f(a-\epsilon,a+\epsilon)\cap \square|_n}
{|\square|_n|}=1\tag{0.7.1}
\]
hold for every $\epsilon>0$ where the limit of cubes is taken as in (0.5.1).
It is obvious that if (0.7.1)
hold for some
real number $a<$,
then it is uniquely determined and we set
$\mathfrak{Leb} f(x_0)=a$.
In ¤ xx we show that
 the measurable function $f$ has a Lebesgue value almost everywhere.
 More preciely, there exists a
null set $W$
of
$\Omega$ such that 
 $\mathfrak{Leb} f$ is defined in
$\Omega\setminus W$ and is equal to
$f$ in this set.
So up  to null sets every measurable function
$f$
is recaptured from its Lebesgue function, i.e.
ignoring a null set
$f$ can always be chosen so that
its values coincide with its Lebesgue values.
\medskip


\noindent
{\bf{0.2.8 Fubini's theorem.}}
Let $n$ snd $m$ be a pair of positive integers and 
$A$  a bounded and measurable subset of
${\bf{R}}^{n+m}$
whose points are written as $(x,y)$ with
$x\in {\bf{R}}^n$ and $y\in {\bf{R}}^m$.
To every $x$ we get the slice
\[
A(x)= \{ y\colon (x,y)\in A\}
\]
In ¤¤ we prove that
$A(x)$ are measurable sets in
${\bf{R}}^m $ for all $x$ outside a null set and
the almost everywhere defined function
\[
x\mapsto |A(x)|_m
\]
is measurable. After we have learnt how to construct
Lebegue integrals we also prove  the equality
\[
\int_{{\bf{R}}^n}\,  |A(x)|_m\, dx= |A|_{n+m}\tag{0.8.1}
\]







\medskip

\noindent
{\bf{0.2.9 Non-measurable sets.}}
There exist
non-measurable sets but in 
practice one does not encounter these ugly sets. In fact, one must appeal to
the Axiom of Choice to exhibit examples.
Using this axiom there exists a subset
$E$ of  the open interval $(0,1)$ with the property
that the
sets $\{E+ q\}$ are disjoint when $q$ runs over the set 
of rational numbers.
This set cannot be measurable. The reason is that
the disjointness would entail that if $q_1,\ldots,q_N$ is a set of rational numbers
between 0 and 1 then
\[
N\cdot |E|_*=
\sum_{\nu=1}^{\nu=N}= |E+q_\nu|_*\leq 2
\]
where the last equality holds since
each set $E+q_\nu\subset [0,2]$.
Since $N$ can be arbitrary large we have
$|E|_*=0$.
So if $E$ is measurable we have
$|E|= |E|_*=0$, i.e $E$ is a null set. 
Since $E+q$ is  translate of $E$ they also give  null sets 
for every rational number.
But a denumerable union of null sets is a null set which
gives a contradaction since
 $\cup \, (E+q)$ with the union taken over all rational numbers
is the whole real line.



\newpage



\centerline {\bf{0.3 Riesz measures in ${\bf{R}}^n$.}}
\medskip


\noindent
To each integer $N\geq 0$ 
we have the lattice
$2^{-N}\cdot {\bf{Z}}^n$
of points
$p=(p_1,\ldots,p_n)\in {\bf{R}}^n$ 
such that $2^Np_\nu$ are integers for
every
$1\leq \nu\leq n$. 
With the notstions from 0.2.4 we obtain for
each
$p\in 2^{-N}\cdot {\bf{Z}}^n$
the half-open cube
\[
\square_N(p)=p+\square_N^*
\]
Set
\[
\mathcal D_N=\{\square_N(p)\colon\, p\in 2^{-N}{\bf{Z}}^n\}\tag{0.3.1}
\]
Notice that each cube in $\mathcal D_N$ is the union of $2^n$ many disjoint cubes from
$\mathcal D_{N+1}$.
Suppose that  non-negative numbers
$\{\mu(\square_N(p))\}$ are assigned for all $N\geq 0$ and every
$p\in {\bf{Z}}^n$.
The assignement is additive if
\[
\mu(\square_N(p))=
\sum\, \mu(\square_{N+1}(q))
\]
where the sum is taken over the $2^n$ many
cubes
in $\mathcal D_{N+1}$  contained in
$\square_N(p)$.
Given  an additive assignement we obtain
a $\mu$-measure for every bounded open
set $\Omega$  as follows: To each $k\geq 0$ we have the family
$D_k(\Omega)$ from (0.2.XX)- Put
\[
 \mu_k(\Omega)=\sum\, \mu(\square_N(p))
\]
with the sum taken over the4 finite  disjoint family of cubes
in $D_k(\Omega)$.
Now we define
\[ 
\mu(\Omega)=\sum_{k=0}^\infty\, \mu_k(\Omega)
\]
Additivity  implies that
if $\{\Omega_\nu\}$
is a finite family of disjoint bounded open sets
then
\[
\mu(\cup\, \Omega_\nu)=\sum \, \mu_k(\Omega_\nu)
\]
Next, if $E$ is a compact set
we set
\[ 
\mu(E)=\min_{E\subset \Omega}\, \mu(\Omega)
\]
\medskip

\noindent
{\bf{0.3.1 The regularity condition.}}
If  $N\geq 0$ and 
$0<\delta<1$ one has the compact cube
\[
\square_N[\delta]=\{x\colon 0\leq x_k\leq \delta\cdot 2^{-N}\}
\]
To each $p\in {\bf{Z}}^n$ we get the compact cube
\[
\square_N(p)[\delta]=p+\square_N[\delta]
\]

\medskip

\noindent
{\bf{0.3.2 Definition.}}
\emph{An additive $\mu$-measures is regular if
the following hold for every $N\geq 0$ and every lattice point
$p\in {\bf{Z}}^n$:}
\[
\mu(\square_N(p))= \lim_{\delta\to 1}\, 
\mu(\square_N(p)[\delta])\tag{0.9.2}
\]

\noindent
\emph{The class of such regular  measures is
denoteb by $\mathfrak{M}({\bf{R}}^n)$
and called  Riesz measures in
${\bf{R}}^n$.}

\medskip

\noindent
It turns out that (0.3.2) and additivity enable us to
define $\mu$-measures in a similar fashion as in Lebegue's case.
For example, (0.3.2) entails that
when $\Omega$ is a bounded open set then
\[
\mu(\Omega)= \sup_{E\subset\Omega}\,
\mu(E)
\] 
where the supremum  is taken over compact subsets.
Next, if $A$ is a bounded set one defines
its outer $\mu$-measure by
\[ 
\mu^*(A)=\min _{A\subset\Omega}
\mu(\Omega)
\]
Similarly the inner measure is defined
by
\[ 
\mu_*(A)=\max _{A\subset E}
\mu(E)
\]
One says that $A$ is $\mu$-measurable if
$\mu^*(A)=\mu_*(A)$ and the common number is denoted by
$\mu(A)$.
\medskip

\noindent
{\bf{0.3.4 Remark.}}
In ¤ IV we expose the theory about Riesz measures
where $\mu$-measurable functions and their $\mu$-integrals
are constructed.
We shall learn that  there exists an extensive class of
non-negative Riesz messures whose mass 
is concentrated to null sets in Lebesgue's sense.
The construction of  Riesz measure is not easy to grasp.
One reason is that apart from the additivity the regularity 
introduces a condition which
cannot be predicted in a straightforward manner since 
one needs the axiom of choice
to
obtain the whole class of non-negative Riesz measures
which correspond to non-negative linear functionals on the space of 
real-valued and continuous functions in
${\bf{R}}^n$ having compact support.
Important examples of a geometric  origin
appear
in connection with
Stokes Theorem 
in ¤ V.

\newpage 

\centerline{\bf{0.4 1-dimensional study.}}
 \medskip


\noindent
A construction due to Weierstrass
gave considerable motivation for the development 
measure theory. 
\medskip

\noindent{\bf{0.4.1 Weierstrass example.}}
Let $0<b<1$ be a real number and $k$ a positive integer.
Define  $f(x)$ by the series
\[
f(x)=\sum_{n=1}^\infty\, b^n\cdot \cos (k^n \pi x)
\]

\medskip

\noindent
Since $b<1$  the series of cosine-functions converges
uniformly so $f$ is a continuous
and $2\pi$-periodic.
Let $b=1/5 $ and the integer $k>5 $ is so large that
\[
\frac{3\pi}{k/5-1}\leq \frac{1}{4}\tag{*}
\]



\noindent
When (*) holds we will show  that
limes superior of inifinitesmal  difference quotients of $f$
are everywhere
$+\infty$, and similarly limes inferior are everywhere
$-\infty$. 
To prove this
we proceed as follows:
To each $x>0$ and every positive integer $n$
we find   the  integer
$\{k^nx\}$
such that
\[
k^nx=\{k^nx\}+q_n\quad\text{where}\quad
-1/2\leq q_n <1/2 
\]
Fix  some $m\geq 2$ and put
\[ 
h_m=\frac{1-q_m}{k^m}\tag{1}
\]
If $n\geq m$ we obtain

\[
k^n(x+h_m)= k^{n-m}(\{k^m x\}+q_m+1-q_m)=
k^{n-m}(\{k^m x\}+1)\tag{2}
\]

\medskip

\noindent
When $\{k^m x\}$ is an odd integer we 
take $n=m$ above and get
\[
\cos (k^m \pi (x+h_m))=\cos\, \pi(\{k^m x\}+1)=1
\]
At the same time
\[
\cos (k^m \pi x)=\cos\, \pi(\{k^m x\}+q_m)=\cos\,(\pi(1+q_m))\leq 0
\] 
where the last equality follows since
the absolute value $|q_m|\leq 1/2$.
Hence
\[
\cos (k^m \pi (x+h_m))-\cos (k^m \pi x)\geq 1\tag{3}
\]


\noindent
Next, consider the partial sum difference
\[
D_{m-1}(x) =\sum_{n=1}^{n=m-1}\, b^n\cdot [
\cos (k^n \pi (x+h_m))
-\cos (k^n \pi x)]
\]
The derivative of the cosine-function is the sine-function
whose maximum norm
is $\leq 1$. Hence
Rolle's theorem gives the inequality:
\[
|\cos (k^n \pi (x+h_m))
-\cos (k^n \pi x)|\leq k^n\pi h_m\quad\text{for all}\quad 1\leq n\leq m-1\implies
\] 
\[
|D_{m-1}(x)|\leq\pi h_m\cdot 
 \sum_{n=1}^{n=m-1}\, b^n\cdot k^n=
\pi h_m\cdot \frac{(bk)^m-1}{bk-1}
\leq 
\]
\[
\pi h_m\cdot \frac{(bk)^m}{bk-1}=
\pi(1-q_m)\frac{b^m}{bk-1}\leq \frac{3\pi}{2(bk-1)}\cdot b^m\tag{4}
\]
where the last inequality follows since $|q_m|\leq 1/2$.
Next, since the maximum norm of the cosine function is
$\leq 1$ the triangle inequality gives
\[
\sum_{n=m+1}^\infty\, b^n\cdot [
\cos (k^n \pi (x+h_m))
-\cos (k^n \pi x)]\leq 2\,\sum_{n=m+1}^\infty\, b^n\cdot=
\frac{2}{1-b}\cdot b^{m+1}\tag{5}
\]


A summation over $n$ and the triangle inequality therefore give:
\[
f(x+h_m)
-fx)\geq b^m- \frac{3\pi}{2(bk-1)}\cdot b^m-
\frac{2}{1-b}\cdot b^{m+1}\tag{6}
\]
\medskip

\noindent
Here
$b=1/5$ and together eith (*) we see (6) gives
\[ 
f(x+h_m)-f(x)\geq \frac{b^m}{4}\tag{7}
\]


\noindent
Inserting $h_m$ from (1) above
we obtain
\[
\frac{f(x+h_m)-f(x)}{h_m} \geq \frac{(bk)^m}{1-q_m}\geq
\frac{1}{6}\cdot (bk)^m\tag{8}
\]

\medskip
\noindent
where $1-q_m\geq 1/2$ was used.
\medskip

\noindent
{\bf{Conclusion.}}
Since $bk>1$ the right hand side tends to $+\infty$ when $k$ increases
and at the same time
$h_m\to 0$.
Following Weierstrass we  take 
some $0<x<1$ and
get the sequence of integers $\{ k^2x\}$ as $k=1,2,\ldots$.
It is clear that we find arbitrary large integers $k$ such that
$\{ k^2x\}$ is an odd integer and  (8) entails that
\[
\limsup_{h\to 0}\, 
\frac{f(x+h)-f(x)}{h} =+\infty
\]
\medskip

\noindent
At this stage we leave it to the reader to
verify that
the limes inferior is $-\infty$ when we instead use integers $k$ such that
$\{k^2x\}$ are even integers. So Weierstrass cosine-series gives a continuous
function
which fails to have derivatives at every $x$.







\medskip


\centerline{\bf{0.4.2 Existence of derivatives.}}
\medskip

\noindent
Weierstrass' example led  to find  of sufficient conditions
in order that a function has derivatives.
Lebesgue   proved that if $f(x)$ is a continuous and
monotone function, i.e. non-increasing or
non\vvv decreasing, then $f$ has an ordinary derivative almost everywhere.
This is shown in  ¤ 1 where we also prove a  general
 result due to Denjoy and Young
which applies to an arbitrary real\vvv valued continuous function
$f(x)$ defined on some open interval $(a,b)$ and was announced in the introdution.
The specific example by Weierstrass is no accident. In fact, later work
by Dini, Mazurkiewics and Banach demonstrated
that in the family  of all continuos functions
defined on the unit interval $[0,1]$,
the generic function fails to have derivatives
at all points $0\leq x\leq 1$. 
From this point of view the discoveries by Lebesgue
were invaluable.


\medskip
\noindent
{\bf{0.4.3 Absolute continuity.}}
Let $f(x)$ be a real-valued continuous function
on $[0,1]$.
To each sequence $0=a_0<a_1<\ldots <a_N=1$
we set
\[
\text{Var}_f(a_\bullet)=
\sum\, |f(a_{\nu+1})-f(a_\nu)|
\]
Set 
\[
\rho(a_\bullet)=\max_\nu \,  a_{\nu+1}-a_\nu)
\]
One says that $f$ is absolutely continuous if
there to every $\epsilon>0$ exists $\delta>0$
such that 
the following impliction hold for all 
\[
\rho(a_\bullet)<\delta\implies
\text{Var}_f(a_\bullet)< \epsilon
\]
\medskip

\noindent
{\bf{0.4.4 Theorem.}}
\emph{If $f$ is absolutely continuous then its derivative
$f'(x)$ exists almost everywhere and the following hold:}
\[
\int_0^1\, |f'(x)|<\infty\quad\text{and}\quad
f(x)= f(0)+ \int_0^x\, f'(t)\, dt\quad\colon \quad 0<x\leq 1
\]
\medskip

\noindent
{\bf{0.4.5 Remark.}}
The theorem asserts that an absolutly continuous function
is the primitive of its almost everywhere existing derivative.
Conversely, if $\phi$ is an $L^1$-function on
$[0,1]$ in Lebegue's sense, then
\[
\Phi(x)= \int_0^x\, \phi(t)\, dt
\] 
is absolutely continuous and
for every Lebegue point of $\phi$, the
derivative $\Phi'(x)$ exists and is equal to $\phi(x)$.
The proof is given in ¤ xx after we have introduced the space
$L^1(0,1)$ of Lebesgue meausurable functions on
$[0,1]$.









\newpage



\centerline{\bf{0.5  ‚antor sets.}}
\medskip


\noindent
On the  unit interval $[0,1]$
closed Cantor sets
arise by a succesive removal of open intervals.
A general construction goes as follows:
In the first step
an open interval  $J_1=(a_1,b_1)$  is removed where
$0<a_1<b_1<1$.
In the second   step one removes an open interval 
$J_{12}=(a_{12}<b_{12})$ from $(0,a_1)$
and an open interval 
$J_{22}=(a_{22},b_{22})$ from $(b_1,1)$.
One continues and after $n$ steps 
$1+2+\ldots+2^n$ many disjoint open intervals 
have been removed
and
there remains a disjoint union of closed intervals
$\{[a_\nu^{(n)},b_\nu^{(n)}]\colon  1\leq \nu\leq 2^{n+1}\}$.
Here $a_1^{(n)}=0$ and $b_{2^n}^{(n)}=1$
while
\[
a_\nu^{(n)}<b_\nu^{(n)}<a_{\nu+1}^{(n)}
\] 
In step $n+1$ one removes
$2^{n+1}$ open subintervals from each of the 
closed intervals above.
The union of all removed open intervals gives
an open set $U$ whose closed complement is called a Cantor set.
The  Cantor  set is of null-type arises if
the sum of the lengths of the removed open intervals is 
equal to one which means that
the closed complement $\mathcal C=[0,1]\setminus U$
is a null-set in Lebesgue's sense.

\medskip

\noindent
{\bf{Lebesgue functions.}}
To every  Cantor set
of null-type Lebegue constructed
a continuous non-decreasing function
$L(x)$ where $L(0)=0$ and $L(1)=1$ while $L$ stays constant on 
the removed open intervals.
The $L$-function is found via a limit of piecewise linear functions
$\{f_n(x)\}$. Namely, after $n$ steps
we have the closed intervals 
$\{[a_\nu^{(n)},b_\nu^{(n)}\}\colon  1\leq \nu\leq 2^{n+1}$ 
above.
Now
\[ 
f_n(x)= (\nu-1)2^{-n-1}+
2^{-n-1}\cdot \frac{x-a_\nu^{(n)}}
{b_\nu^{(n)}-a_\nu^{(n)}}\quad\colon 
a_\nu^{(n)}\leq x\leq b_\nu^{(n)}
\]
while $f_n(x)$ is constant on open intervals which have been
removed up to the $n$:th step.
So each $f_n$ is a non-decreasing piecewise linear function.
From the construction it is clear that the maximum norms
\[ 
\max_x\,
|f_n(x)-f_{n-1}(x)|\leq 2^{-n}
\]
for every $n$. Hence
$\{f_n\}$ converge uniformly to a continuous function
which yields the Lebesgue function associated to the Cantor set.
Since $\mathcal C$ is a null-set the derivative of the Lebesgue function
$L(x)$ is zero almost everywhere and yet
$L$ is a non-constant function.
This leads to an example of a  singular measure.
More precisely there exists a non-negative and $\sigma$-additive measure
$\mu_\mathcal C$ on $[0,1]$ where
the mass over an interval $[a,b]$ is the ordinary Riemann integral of
$L$ taken over this interval.
So Cantor's set-theoretic constructions give
a family of Riesz measures on $[0,1]$
which carry their  mass on
a null-set.
\medskip

\noindent {\bf{0.5.1 Arithmetic properties.}}
For certain applications one seeks special Cantor sets
$\mathcal C$ whose 
associated singular measure $\mu_\mathcal C$
has special properties. One such property
is
the behaviour of its Fourier series.
In ¤xx we expose a construction by Salem which shows that for
every number $0<p<1/2$ there exists a Cantor  set
$\mathcal C$ if null-type such that $\mu_\mathcal C$ satisfies
\[
\bigl|\int_0^1\, e^{2\pi i nx}\, d\mu_F(x)\bigr|\leq C\cdot |n|^{-p}
\]
for all $n$ and a constant $C$.



\bigskip

\centerline{\bf{0.6 Examples from function theory.}}









\bigskip

\noindent
Measure theoretic assertions   tend to be
vague when   results only asserts that
some "nice property" holds almost everywhere, while the
actual null\vvv set on which the property  is not
described.
To give an example  we consider a continuous and
real\vvv valued function $u(\theta)$ on the unit circle.
Define  $v(r,\phi)$
when $0\leq r <1$ and $0\leq\phi\leq 2\pi$ by

\[
v(r,\phi)=\frac{r}{\pi}\int\uuu 0^{2\pi}
\frac {\sin(\theta\vvv \phi)\cdot u(\theta)}{1+r^2\vvv 2r\cos(\theta\vvv \phi)}\cdot
d\theta
\]
It means that  $v$ is the conjugate harmonic function in
the unit disc of the harmonic extension of
$u$.
The Brothers Riesz' Theorem
asserts that
\[ 
\lim\uuu{r\to 1}\, v(r,\phi)=v^*(\phi)\tag{*}
\] 
exists almost everywhere, i.e. for all $\phi$ outside a null\vvv
set on $[0,2\pi]$.
However, the precise description of this null\vvv set in terms of the given
continuous function $u$ cannot be attained in general.
So  one must be content with assertion that radial limits
exist
almost everywhere.

\medskip


\noindent
{\bf{0.6.1 A boundary value problem}}
Let $f(x,y)$ be a real-valued and continuously differentiable  function
defined in an open rectangle $\square=\{ 0<x<a\}\times \{-1<y<1\}$.
The first order
partial derivatives
$f'_x$ and $f'_y$ may
satisfy integrability conditions.
For a given $p\geq 1$ we impose the $L^p$-condition:
\[
\iint_\square\, \bigl(|f'_x(x,y)|^p+
|f'_y(x,y)|^p\bigr)\, dxdy<\infty\tag{i}
\]
A result due to to Hardy, Littlewood and Paley
asserts that if $p>2$ then
$f(x,y)$ extends to a continuous function on
the half-open rectangle $\{0\leq x<a\}\times\{-1<y<1\}$, i.e.
the $L^p$-condition ensures that $f$ extends to define
a continuous function on boundary line where
$x=0$.
The case when $p=2$ leads to a  more involved situation.
The condition that
$f'_x$ and $f'_y$ are square integrable does not
ensure that $f$ is a bounded function in $\square$.
 Examples arise via Riemann's conformal mapping
 theorem
 which is explained in ¤ X from Chapter VI. However, 
the $L^2$-condition in (i) implies that
 \[
 \iint_\square\, |f(x,y)|^q\,dxdy <\infty
 \quad\text{hold for all}\quad q>2 \tag{ii}
\]
There remains to study the eventual existence of limits
\[
\lim_{x\to 0}\, f(x,y)\quad\colon\quad -1<y<1\tag{iii}
\]
when (i) holds with $p=2$.
When $f$
is harmonic in $\square$ and the $L^2$-condition holds in (i)
precise limit results due to Beurling appear in 
Special Topics ¤ xx. Here advanced analytic function theory is needed to
attain precise  measure theoretic results.
\bigskip

\noindent
{\bf{0.6.2 Measures in a logarithmic scale.}}
Let $E$ be a closed null-set on the unit circle $T$.
The  complement consists of open
intervals 
$\{\omega_\nu=\{e^{i\alpha_\nu}<
e^{i\theta}<e^{i\beta_\nu}\}$
and the condition that $E$ us a null-set means that
\[
\sum\, \beta_\nu-\alpha_\nu=2\pi
\]
Next, to each $t>0$ we have the closet
set
$E(t)$ of points
$e^{i\theta}$ such that
\[
\min_{e^{is}\in E}\,
|e^{i\theta}-e^{is}|\leq t
\]
Let $\phi_E(t)$ denote the linear Lebesgue measure of
$E(t)$.
Now one can impose the condition that
\[
\int_0^1\, \frac{\phi_E(t)}{t}\, dt<\infty\tag{*}
\]
Example show that this  is a more
restrictive than the sole condition that
$E$ is a null-set.
It turns out that (*) is a crucial condition in
several situations  related to analytic function theory.
In ¤ xx we prove a result due to Carleson 
which shows that  (*)   entails that
there exist non-vanishing 
analytic functions $f(z)$ in the disc algebra $A(D)$
which
are zero on $E$
and at the same time can be made differentiable of any
order $N\geq 1$.
Conversely a result due to Beurling shows that if
(*) diverges and $f\in A(D)$
is Hšlder continuous of some order
$>0$ on $T$, then $f$ cannot be zero on $E$ unless it is identically zero.
The proofs rely upon constructions using Herglotz integral and
a  measure theoretic result
which goes as follows:
Given the null set $E$ we have the complementary open intervals
$\{\omega_\nu\}$.
Denote by  $\ell_\nu$  the length of $\omega_\nu$.

\medskip

\noindent
{\bf{0.6.3 Proposition.}}
\emph{The integral (*) converges if and only if}
\[
\sum\, \ell_\nu\cdot \log \ell_\nu<\infty\tag{**}
\]
\medskip

\noindent
\emph{Proof.}
Arrange the intervals so that
$\{\ell_1\geq \ell_2\geq \ldots\}$ and
if $N$ is a non-negative integer we
denote by
$S_N$ the number of intervals such that
$2^{-N-1}<\ell_\nu\leq 2^{-N}$.
It is easily seen that
(**) converges if and only if
\[
\sum_{n=0}^\infty\, 2^{-N}\cdot N\cdot S_N<\infty\tag{i}
\]
For each $t>0$ we set
\[
\psi(t)= \sum_{\ell_\nu\leq t}\, \ell_\nu\tag{ii}
\]
It is clear that
\[
2^{-N-1}S_N\leq \psi(2^{-N})-\psi(2^{-N-1})\leq
2^{-N}S_N\tag{iii}
\]
Hence (i) converges if and only if
\[
\sum_{n=0}^\infty\, N\cdot( \psi(2^{-N})-\psi(2^{-N-1}))\tag{iii}
\]
Abel's partial sum formula entails
that
(iii) converges if and only if
\[
\sum_{n=0}^\infty\, \psi(2^{-N})<\infty\tag{iv}
\]
Moreover, the reader can check
that
(iv) holds if an only if the integral
\[
J=\int_0^1 \frac{\psi(t)}{t}\,dt<\infty\tag{v}
\]
To finish the proof there remains to show that
the convergence of (*) and (v) are equivalent.
One direction is easy for if $t>0$ and $\ell_\nu\leq t$
then $\omega_\nu$
is contained in
$E(2t)$. It follows that
\[
\psi(t)\leq \phi_E(2t)
\]
Using the variable subsitution $t\mapsto 2t$
we conclude that the convergence of (*) entails that of (v).
To get the converse we shall majorize $\phi_E(t)$.
With $t>0$ kept fixed we take an integer $N\geq 0$
and denote by $F_N$
the union  of $\omega$-intervals such that
$2^{N}t<\ell_\nu\leq 2^{N+1}t$ which gives
\[ 
\phi_E(t)\leq \psi(t)+\sum_{N=0}^\infty\, |F_N\cap E(t)|_1\tag{vi}
\]
Notice
that $|\omega\cap E(t)|\leq t$  for
each
$\omega\in F_N$.
Hence the last sum in (vi) is majorized by
\[
t\cdot \sum_{N=0}^\infty\, \psi(2^{N+1}t)-\psi(2^Nt)
\]
The summation only extends as long as $2^N\leq 2\pi$
and 
is therefore taken over a finite set of integers
whose  sum obviously is majorized by
$(2\pi-\psi(t))t$.
We conclude that
\[ 
\phi_E(t)
\leq (1-t)\psi(t)+ 2\pi t\leq
\psi(t)+ 2\pi t
\]
and then 
the convergence in (v) entails that of (*).

\bigskip




\centerline {\bf{0.7 Rational series}}
\bigskip

\noindent
We shall consider  series of the form:
\[ 
\sum\,\frac{A_\nu}{z-a_\nu}\tag{*}
\]
\noindent
Before general measure theory was
developed such
series  were 
studied by PoincarŽ, Goursat and Pringheim who used them to 
construct functions via  lacunary expansions.
The  general theory about  the series (*)  is foremost due Emile Borel who 
introduced
a class of generalised analytic functions
by extending Cauchy's concept  \emph{de fonction monogne}.
A full account of Borel's work would lead us too far
so the interested reader may consult his
text-book [Borel] for details. 
Non-trivial situations arise when the sequence
$\{a_\nu\}$ is everywhere dense in an open subset
$\Omega$ of ${\bf{C}}$, or even in the whole complex plane.
\medskip

\noindent
{\bf{0.7.1 A special case}}.
Suppose there exists some $\gamma>1/2$ such that
\[ 
\sum\, |A\uuu\nu|\cdot \nu^\gamma <\infty\tag{1}
\]
For a given
$\ell>0$ we consider the open discs $\{D\uuu \nu\}$
of radius $\ell\cdot \nu^{\vvv \gamma}$
centered at the points $\{a\uuu\nu\}$. The 2\vvv dimensional area
of the domain given by the union of there discs
is majorized by:
\[
\pi\cdot \ell^2\cdot \sum \nu^{\vvv 2\gamma}\tag{2}
\]
Let $C\uuu\ell ={\bf{C}}\setminus\,\cup \, D\uuu \nu$
be the closed complement.
These sets increase as $\ell\to 0$ and (2)
shows that 
the complement of $\cup\, C\uuu\ell$ has planar measure zero, i.e. 
it is a null\vvv set
in the complex plane. Next,
if $z\in C\uuu\ell$ the series
(*) is absolutely  convergent since
\[
\frac{1}{|z\vvv a\uuu\nu|}\leq \ell^{\vvv 1}\cdot \nu^\gamma
\]
hold for each $\nu$ and (1) gives therefore the absolute convergence
\[
\sum\, \frac{|A\uuu\nu|}{|z\vvv a\uuu\nu|}\leq \ell^{\vvv 1}
\]
When the sequence $\{a\uuu\nu\}$ is everywhere dense 
the interior of $C\uuu\ell$ is empty so
the resulting function 
\[ 
f(z)= 
\sum\,\frac{A_\nu}{z-a_\nu}\tag{*}
\]
is defined on  every closed set $C\uuu\ell$ so it
cannot be regarded as an analytic function.
But $f$ is the limit of meromorphic functions
\[ 
f\uuu m(z)=\sum\uuu{\nu=1}^{\nu=m}\,\frac{A_\nu}{z-a_\nu}\tag{*}
\]
where the convergence  holds uniformly on $C\uuu\ell$ for every fixed $\nu$
and
one may therefore expect some analyticity properties of $f$.
Let us say that $f$ is of quasi\vvv analytic type
if it cannot vanish identically on any Jordan arc
$\gamma$ situated in $C\uuu\ell$ for some $\ell>0$.
The condition for $f$ to be quasi\vvv analytic depends on
$\{A\uuu\nu\}$. 
Even if $\{A\uuu\nu\}$ decreases quite rapidly 
there may exist
non\vvv quasi\vvv analytic series.
Examples where
\[ 
|A\uuu\nu\leq e^{\vvv n^\alpha}\quad\colon\quad 0<\alpha<1/2
\]
are given in [Denjoy 1922].
However, if $\{A\uuu\nu\}$ decreases sufficiently rapidly  then
quasi\vvv analyticity holds.
The following sufficiency result was proved by Carleman in [Carleman 1922):
\medskip

\noindent
{\bf{0.7.2  Theorem.}}
\emph{Suppose there exists
$\epsilon>0$ such that}
\[ 
|A\uuu n|\leq e^{\vvv(\gamma+\epsilon)\cdot n\cdot \log n}
\quad\colon\quad n\geq 1
\]
\emph{Then $f(z)$ is quasi\vvv analytic in $C\uuu\ell$ for every $\ell>0$.}

\medskip


\noindent
The proof 
employs analytic function theory
and is given  in ¤ XX  from Chapter III.
Carleman's  book [xxx] contains several examples including necessity conditions for
certain classes of series in (*).
The interested reader should also consult [Wolff]
where  J. Wolff
constructs series as above
when $\{a\uuu\nu\}$ is everywhere dense and
(*) converges  at every point outside this denumerable set.
\medskip


\noindent{\emph{Another  case.}}
Consider the series (*) under the condition that
\[
\sum_{\nu=1}^\infty\, \sqrt{\bigl|A_\nu\bigr|}<\infty\tag{***}
\]
\medskip


\noindent
Let us  take a dense set
$\{a_\nu\}$ in some   open set
$\Omega$ and
an analytic Jordan curve $\Gamma$
given by the image under a
bijective and real analytic function
$t\mapsto z(t)$ from the  unit interval $[0,1]$.
When all the $a$-points are outside $\Gamma$ we can define
the partial sums
\[ 
S^\Gamma _N(t)=\sum_{\nu=1}^{\nu=N}\,\frac{A_\nu}{z(t)-a_\nu}\tag{1}
\]
We say that the infinite series (*) converges uniformly on $\Gamma$
if
$\{S^\Gamma_N(t)\}_1^\infty$ converges uniformly on
$[0,1]$.
Borel   proved that  (***) implies that
this uniform convergence holds
on  \emph{almost every
closed line segment} in the complex plane. 
To be precise, if we represent a line segment by 
its two end-points $(z_0,z_1)$ then 
there exists a nullset  $\mathcal N$ in ${\bf{C}}^2$
such that  
the series
\[ 
t\mapsto \sum\, \frac{A\uuu\nu}{tz\uuu 0+(1\vvv t)z\uuu 1
\vvv a\uuu \nu}
\]
converges uniformly for $0\leq t\leq 1$ whenever
$(z\uuu 0,z\uuu 1)$ is outside $\mathcal N$.
Next, relax the condition of uniform convergence on
$[0,1]$ to the weaker condition that $\{S^\Gamma_N(t)\}$
converge pointwise for all $t$ outside a null set on
$[0,1]$. With this relaxed notion of convergence 
Borel proved the following:
\bigskip

\noindent
{\bf{0.7.3 Theorem.}} \emph{Assume that $\{A\uuu\nu\}$ satisfies}
\[
\sum_{\nu=1}^\infty\, \bigl|A_\nu\bigr|^{\frac{2}{3}}<\infty
\]


\noindent
\emph{Then the  partial sum sequence $\{S^\Gamma_N(t)\}$
converges almost every along  every real\vvv analytic
Jordan arc $\Gamma$ in ${\bf{C}}$.}

\medskip

\noindent
The results above illustrate that the study of series (*) is a rich subject 
with  wide range of applications and  
many important problems remain unsolved. See
[Borcea. et.al.] for an account.


























\newpage

\centerline {\bf\large {I.  Measure theory on the real line.}}

\bigskip





\noindent
{\bf {Introduction.}}
The modern theory of integration
started in 1894 when Stieltjes published the article
\emph{Recherches sur les fractions continues} which contains a wealth
of new ideas; among others, a new conceptual integral
which   was used
to study
\emph{moment problems}. 
Given    a sequence of non-negative real numbers
$\{ c_n\}_0^\infty$ one asks if there exists
a non decreasing  function
$f(t)$ defined on the non-negative real axis $t\geq 0$
such that
\[ 
c_n=\int_0^\infty\, t^n\cdot df(t)
\quad\text{hold for all}\,\, n=0,1,\ldots\tag{*}
\]
To analyze this problem
Stieltjes constructed  integrals of the form:
\[
\int_a^b\, g(x)\cdot df(x)\tag{**}
\]
where $f(x)$ is a continuous and non-decreasing function
and $g(x)$ is a continuous function on the closed interval $[a,b]$.
Stieltjes defined the integral (**) as the limit of sums:
\[ 
\sum\, g(x_\nu)\cdot \bigl[f(x_{\nu+1}-f(x_\nu)\bigr]\tag{***}
\]
where $a=x_0<\ldots<x_N=b$ and $\max\,(x_{\nu+1}-x_\nu)$
tends to zero. The \emph{uniform continuity} of $g$ on 
$[a,b]$  gives a limit 
exactly  as for the ordinary Riemann integral.
Namely, consider the modulus
of
continuity:
\[ 
\omega_g(\delta)=
\max_{x_1,x_2}\,|g(x_1)-g(x_2)|\quad\colon\,
\text{maximum taken over pairs}\,\,\, |x_2-x_1|\leq \delta
\]
Put $M=f(b)-f(a)$.
If   $\delta>0$ and  $x_{\nu+1}-x_\nu\leq\delta$
hold for every $\nu$ in the partition which defines
(***), then Stieltjes proved that this 
sum  differs from a limit by a quantity which is 
$\leq M\cdot\omega_g(\delta)$. Hence the 
integral (**) exists since
uniform continuity of $g$
entails that 
\[
\lim_{\delta\to 0}\, \omega_g(\delta)=0
\]


\noindent
{\bf{Remark.}}
Stieltjes's beautiful discoveries about the moment problem
will not be
treated in these notes. We remark only 
that Stieltjes found a necessary and sufficient condition on
the sequence $\{c\uuu n\}$ in order that
there exists a function $f$ such that (*) above holds
expressed by a condition on the series of continued fractions associated to
$\{c\uuu n\}$. 


\medskip



\noindent
{\bf{Exercise.}}
Let
$f$ be a $C^1$-function, i.e.  the  derivative
$f(x)$ exists as a continuous function. Show that 
(**) is equal to the ordinary Riemann integral
\[
\int_a^b\, g(x)f'(x)\cdot dx
\]
If $g$ also is a $C^1$-function
then
partial integration gives
\[
\int_a^b\, g(x)f'(x)=g(b)f(b)-g(a)f(a)\int_a^b\, f(x)g'(x)dx\tag{1}
\]
\medskip

\noindent
Verify that 
the partial integration formula (1) remains valid
for Stieltjes' integrals, i.e. if  
$f$ and $g$ are 
continuous and non-decreasing on $[a,b]$ then   partial summations
give the equality:
\[
\int_a^b\, f(x)\cdot dg(x)+
\int_a^b\, f(x)\cdot dg(x)=f(b)g(b)-f(a)g(a)
\]



\newpage

\noindent
{\bf{0.1 Functions of bounded variation.}}
A continuous function $f(x)$ on $[a,b]$ has a bounded
variation if there exists a constant $M$ such that
\[
\sum_{\nu=0}^{\nu=N-1}\, \bigl|f(x_{\nu+1})-f(x_\nu)\bigr|\leq M
\]
for all partitions $a=x_0<x_1<\ldots<x_N=b$.
The Stieltjes integrals
\[ 
\int_a^b\, g(x)\cdot df(x)
\] 
are again defined for every continuous function $g(x)$.
To prove this one uses the
following result:
\medskip

\noindent
{\bf{0.2 Decomposition Lemma.}}
\emph{Let $f$ have a bounded variation. Then there
exists a unique pair of continuous functions $(f_*,f^*)$ where
$f^*$ is non-decreasing and $f_*$ is non-increasing such that}
\[ 
f(x)=f^*(x)-f_*(x)\quad\text{where}\quad
f^*(a)=f(a)\quad \text{and}\,\, f_*(a)=0
\]
\medskip

\noindent
{\bf{Exercise.}}
Prove this result.
The hint is to define
$f^*(x)$ for every  $a\leq x\leq b$ by 
\[
f^*(x)=f(a)+\max\, \sum\, f(\xi_\nu)-f(\eta_\nu)
\]
where the maximum is taken over sequences
$0\leq\eta_1<\xi_1<\eta_2<\ldots<\eta_N<\xi_N\leq x$.


\bigskip


\centerline {\bf{0.3 Borel's construction of integrals}}.
\medskip


\noindent
Stieltjes'  integral  can be computed in another way
using
the variation of $f$ over a certain  family of subsets
of $[a,b]$. This fundamental method   was introduced by Emile Borel in 1895.
Recall
that  a  bounded and open
subset $\Omega$ of ${\bf{R}}$  is  a unique 
union of pairwise disjoint open interval $\{(a_\nu,b_\nu)\}$.
In general this family is infinite but it is at most denumerable.
Let  $f(x)$   be continuous and non-decreasing.
The variation of $f$ over $\Omega$ is defined by
\[ 
\text{Var}_f(\Omega)=
\sum_{\nu=1}^\infty\, \bigl[f(b_\nu)-f(a_\nu)\bigr]
\]
If $E$ is a closed subset of $[a,b]$
we 
put:
\[
\text{Var}_f(\Omega\cap E)=
\text{Var}_f(\Omega\cap E)-
\text{Var}_f(\Omega\setminus E)\tag{i}
\] 
Next,
consider a
continuous function $g$ on $[a,b]$.
For each $\nu$
we get the following subset of $[a,b]$:
\[
S_g[a_\nu,b_\nu)= \{ x\quad\colon\quad a_\nu\leq g(x)<b_\nu\}
\]
Since  $\{g<b_\nu\}$ is open and  $\{g\geq a_\nu\}$ is closed, it follows from
(i) that 
the variation of $f$ is defined over 
these $S_g$-sets.
Suppose that  the range $g([a,b])$ is contained in
the interval $[-A,A]$ for some $A>0$. For
every
sequence
\[
 -A\leq \xi_0<\xi_1<\ldots<\xi_N=A
 \]
we set
\[
S_*(\xi_\bullet)=\sum\,\xi_\nu\cdot\text{Var}_f(S_g[\xi_\nu,\xi_{\nu+1})
\quad\text{and}\quad
S^*(\xi_\bullet)=\sum\,\xi_{\nu+1}\cdot\text{Var}_f(S_g[\xi_\nu,\xi_{\nu+1})
\]
When $M=f(b)-f(a)$ 
we see that
\[ 
S^*(\xi_\bullet)-S_*(\xi_\bullet)\leq M\cdot 
\max_\nu\, (\xi_{\nu+1}-\xi_\nu)\tag{0.3.1}
\]
Hence there exists 
\[ 
S=\lim\, S_*(\xi_\bullet)\tag{*}
\] 
where the limit is taken over arbitrary partitions of
$[-A,A]$ such that 
\[
 \max_\nu\, \, \xi_{\nu+1}-\xi_\nu\to 0
\]
Abel's summation formula entails that the limit  (*) is equal to
the  Stieltjes' integral, i.e.:
\[
S=\int_a^b\, g(x)\cdot df(x)\tag{0.3.2}
\]
This equality paves the way  to  constructions of integrals where
the regularity  of $g$ can be relaxed.
The reason is that  Borel's limit 
is more \emph{robust} as compared with
the construction by Stieljes. For let $A>0$ and consider the class
$\mathcal C_A$ of continuous functions $g(x)$ on $[a,b]$ whose range is contained in
$[-A,A]$.  To every $\xi$-sequence
$-A=\xi_0<\xi_1<\ldots<\xi_N=A$
we set
\[ 
\delta(\xi_\bullet)=\max\uuu\nu \, \xi_{\nu+1}-\xi_\nu
\]
By (0.3.1)  the lower- resp. the over-sums
$S_*$ and $S^*$  differ from the limit $S$  in (*) by
number majorized by
$A\cdot \delta(\xi_\bullet)$.
This hold for
 all $g$-functions in $\mathcal C_A$. So  
the rate of convergence 
 depends upon $\delta(\xi_\bullet)$ and not upon the chosen
 $g$-function in $\mathcal C_A$,
 i.e. the rate of convergence in Borel's  construction 
 is \emph{independent} of the modulus of continuity of an
 individual $g$-function.
 \bigskip
 

\centerline {\bf{0.4 Borel functions.}}
\medskip

\noindent
The  robust limit  above enable us
to construct integrals
where the $g$-functions need not be
continuous.
In fact,  there exists the integral
\[ 
\int_a^b\, g(x)df(x)\tag{0.4.1}
\] 
under the sole assumption that $g$ is a \emph{bounded
and Borel measurable function}. This 
means that $g(x)$ is a  function on
$[a,b]$ with some bounded range $[-A,A]$ and 
for each pair of real numbers
$\eta<\xi$ the
set $\{\eta\leq g<\xi\}$
belongs to the Borel algebra $\mathfrak  B$
which by definition
is the 
smallest Boolean $\sigma$-algebra of subsets of ${\bf{R}}$  containing all half-open
intervals. 
To define (0.4.1) for a  bounded Borel function $g$
one  first constructs the variation of $f$ over an arbitrary Borel set.
Once this is done the existence  of limits which
give (0.4.1) follow exactly as in the case when
$g$ is a continuous function. 
\medskip



\centerline {\bf{0.5 Baire classes.}}
\medskip


\noindent
The class $\mathcal B$ of Borel measurable functions
arises from 
increasing  families of functions.
First
$\mathcal B_0$ is the family of continuous functions.
Next, a function $g$ is of the first Baire class if it
is equal to the \emph{pointwise limit} of some sequence of
continuous functions.
This gives the  class $\mathcal B_1$. Next we get the class 
$\mathcal B_2$ which consists
of pointwise limits of $\mathcal B_1$-functions. One proceeds by
an induction over positive integers and arrive at the class
\[
 \mathcal B_\infty=\cup\, B_n
\]
However, this does not stop the process via 
pointwise convergence.
The reason is that 
there exist
sequences $\{g_k\}$ of functions in $B_w$
which have a pointwise limit function which does not
belong to $B_\infty$, i.e. the limit function does not belong to
$B_w$ for a given integer $w$.
To get a family of functions which is stable under pointwise
limits one must continue and define
$\mathcal B$-classes by an induction using
\emph{ordinal numbers}.
We shall not pursue this any further but refer to the extensive literature about
Baire's  construction of all Borel functions on the real line.
See for example [XXX].


\bigskip




\centerline{\bf\ {0.6 Monotone functions and their Riesz measures}}.
\medskip

\noindent
On an interval $[a,b]$ we  consider a
non-decreasing and continuous functions $f(x)$.
We have the $\sigma$-algebra $\mathfrak{B}[a,b]$ of Borel sets in
$[a,b]$. Consider 
a denumerable family of disjoint half-open intervals $\{[a_\nu,b_\nu)\}$
on $[a,b]$.
Then
the positive series

\[ \sum\, f(b_\nu)-f(a_\nu)\tag{1}
\] 
converges.
Next, since
$\mathfrak{B}[a,b]$ is the smallest $\sigma$-algebra which contains
half-open subintervals of $[a,b]$, the convergence in (1)
and 
general set-theoretic arguments imply that
the variation of $f$ is defined over
every Borel set $S$, i.e. we obtain a $\sigma$-additive measure
$\mu_f$ on $\mathfrak{B}[a,b]$
where

\[ 
\mu_f(S)=\text{Var}_f(S)
\] 
holds for every Borel set $S$
in $[a,b]$. More precisely, 
\[ 
S\mapsto \mu_f(S)\tag{2}
\]
yields a $\sigma$-additive map.
\medskip


\noindent
{\bf{A converse result.}}
Suppose that we have a non-negative $\sigma$-additive map
\[
S\mapsto \mu(S)
\]
from
$\mathfrak{B}[a,b]$ into the set of non-negative real numbers.
Thus, if $\mu$ is normalised so that
its mass on $[a,b]$ is one, then
it is a probability measure on the sample space
formed by
$[a,b]$ and $\mathfrak{B}[a,b]$ in the sense of abstract measure theory.
To $\mu$ we associate the non-decreasing function
$f(x)$ defined by
\[
f(x)= \mu([a,x])\quad\colon a\leq x\leq b
\]


\medskip

\noindent
{\bf{Exercise}}.
Prove  the equality
\[ 
\mu=\mu_f\tag{1}
\] 
under the assumption that
$\mu$ has no \emph{discrete point masses},
i.e. that
the $\mu$-mass is zero on every singleton set. An equivalent
condition is that
\[ 
\mu(\eta,\xi)=\mu([\eta,\xi])\tag{2}
\]
hold for all pairs $\leq \eta<\xi\leq b$.
When $\mu$ satisfies this condition
one says that
$\mu$ has no atoms or refer to  an atomless measure.
Hence   we can conclude:
\medskip


\noindent
{\bf{0.6.1 Proposition.}}\emph{
 There exists  a 1-1 correspondence between
the class of non-decreasing continuous functions on
$[a,b]$ and the class of $\sigma$-additive and 
non-negative measurs on
$[a,b]$ without atoms.}
\bigskip

\noindent
{\bf{0.6.2 Discrete measures and jump functions.}}
Let $\{x_k\}$ be a sequence of points on
${\bf{R}}$  indexed by positive integers.
No special assumption is imposed. For example, the sequence may
be some enumeration of all rational numbers.
If $\{p_k\}$ is a sequence of positive numbers such that the series
$\sum\, p_k<+\infty$ then we get the jump-fuction
\[ 
s(x)=\sum\, p_k\cdot H_{x_k}(x)\tag{1}
\] 
Above we  introduced  Heaviside functions, i.e. for every
real number $x_*$ we define $H_{x_*}(x)=1$ if
$x\geq x_*$ and 0 when $x<x_*$.
To the $s$-function corresponds the discrete measure which assigns
the mass $p_k$ at every $x_k$.
\medskip

\noindent
This yields a 1-1 correspondence between non-decreasing jump functions and
non-negative discrete measures.
A non-trivial result due to Lebesgue and Vitali
goes as follows:

\medskip

\noindent{\bf{0.6.3 Theorem.}}
\emph{Every jump-function $s(x)$ has an ordinary derivative whole value is zero outside
a nullset.}
\medskip

\noindent
We prove this in ¤ 1.15 below.
Let us now consider an
arbitrary $\sigma$-additive and non-negative measure $\mu$
defined on $\mathfrak{B}[a,b]$.
It may have point masses.
Since the total mass of $\mu$ over $[a,b]$ is finite
the sum of all mass assigned to
the 
atoms is finite, i.e.
we get a discrete part given by

\[
 \mu_d=\sum\, p_k\cdot \delta_{x_k}
\]
Here $\sum\,p_k<\infty$ and $\{x_k\}$ is at most a denumerable
subset of $[a,b]$.
The difference $\mu-\mu_d$ has no atoms and corresponds 
to a non-decreasing continuos function
$f$ as above. So here $\mu-\mu_d=\mu_f$ and one refers to
$\mu_f$ as the continuous part of $\mu$. It
is clear that this decomposition of $\mu$ is unique.




\newpage


\centerline {\bf{0.7 Signed measures.}}
\bigskip

\noindent
A continuous function
$f$ on $[a,b]$ has a bounded variation if there exists a constant
$C$ such that
\[
\sum\, \bigl|f(\xi_{\nu+1})-f(\xi_\nu)\bigr|\leq C
\] 
for all partitions
$a=\xi_0<\ldots<\xi_N=b$.
The smallest number $C$ for which this holds is called the total
variation of $f$ and is denoted by
$V(f)$.
A  result  due to  Ascoli asserts the following:
\medskip

\noindent
{\bf{0.8 Theorem.}}
\emph{Let $f$ be a continuous function with bounded
variation. Then there exists a unique pair of non-decreasing functions
$g,h$ such that}
\[ 
f(x)=g(x)-h(x)
\]
\emph{where $g(a)=f(a)$ and $h(a)=0$.}
\medskip

\noindent
{\bf {Exercise.}}
Prove this. Here is the hint is to construct the $g$-function. Put
\[
\phi (x)=f(a)+
\max\, \sum_{\nu01}^{\nu=N}\, f(\xi_\nu-f(\eta_\nu)
\] 
where the maximum is taken over
all sequences 

\[
a<\eta_1<\xi_1<\eta_2<\ldots<\xi_{N-1}<\eta_N<\xi_N\leq x
\]
Intuitively, we seek  intervals in $[0,x]$ where
$f$ increases as much as possible, while eventual intervals where
$f$ decrease are omitted.
The reader should verify that
the $\phi$-function is non-decreasing and continuous and that
the function
\[
x\mapsto f(x)-\phi(x)
\]
is non-increasing.
Now 
$g=f(a)+\phi(x)$ and 
$h=f(x)-\phi(x)-f(a)$. This proves the existence in Theorem 0.8 and the
proof of uniqueness is left to the reader.
\bigskip

\noindent
{\bf{The signed measure $\mu_f$.}}
The decomposition above gives
a  signed measure $\mu_f$ defined by

\[ 
\mu_f=\mu_g-\mu_h
\]
In
this decomposition  there
exists a Borel set $S$ in $[a,b]$ such that
\[ 
\mu_g([a,b])=\mu_g(S)
\quad\text{and}\quad 
\mu_h([a,b])= 
\mu_h([a,b]\setminus S)
\]
This means that
$\mu_g$ and $\mu_h$ are 
orthogonal and one writes
\[
 \mu_g\perp\mu_h
\]


\noindent
Summing up we have the following
\medskip

\noindent
{\bf{0.9 Theorem}}.
\emph{There exists a 1-1 correspondence between the family of signed Riesz measures
$\mu$ on $[a,b]$ without atoms and the class of continuous 
functions $f(x)$ of bounded variation
normalised with $f(a)=0$.}
\medskip

\noindent
Let us remark that the results
above
are special cases
of  the general decomposition by
Hahn which is proved in  the section devoted to  abstract measure theory.
\medskip

\noindent
{\bf{0.10 Borel-Stieltjes  integrals.}}
The previous material shows that if
$f$ is a continuous function of bounded variation on
$[a,b]$ then there exists an integral
\[ 
\int_a^b\, g(x)\cdot d\mu_f(x)=
\int_a^b\, g(x)\cdot df(x)\tag{*}
\] 
for every bounded Borel function $g(x)$.
\medskip


\centerline{\bf{0.11 Weak limits of measures}}
\medskip

\noindent
Above we have seen
that every  signed Riesz measure $\mu$
on $[a,b]$ is  a unique sum of
an atomless measure $\nu_c$ and a discrete measure $\mu_d$.
It turns out that the class of discrete measures recapture all Riesz
measures after suitable passage to the limit.
Let us clarify this and begin with the case of non-negative measures.
Consider a  positive integer $N$ and some
$N$-tuple $a\leq\xi_1<\ldots<\xi_N\leq b$ and a sequence
$\{c_\nu\geq 0\}$ where $\sum\, c_\nu=1$
To this we associate the discrete measure
$\mu_N$ and obtain: 
\[
\int\, g\cdot d\mu_N=\sum\, c_\nu\cdot g(\xi_\nu)\quad\text{for every}\,\,  g\in C^0[a,b]
\] 
\medskip

\noindent
Suppose now that there exists the limits:
\[
\lim_{N\to\infty}\, 
\int\, g\cdot d\mu_N\quad\text{for all}\quad g\in C^0[a,b]\tag{*}
\]
When (*)  holds we say that $\{\mu_N\}$ is weakly convergent.
Now the following holds:
\medskip

\noindent
{\bf{0.12 Theorem}}.
\emph{Let $\{\mu_N\}$ be  weakly convergent.
Then there
exists a unique non-negative Riesz measure 
$\mu$  such that}
\[
\lim_{N\to\infty}\, 
\int\, g\cdot d\mu_N=\int_a^b\, g\cdot d\mu
\]
hold for all $g\in C^0[a,b]$.

\medskip

\noindent
\emph{Proof.}
The existence of limits
mean that we have a linear map
\[ 
g\mapsto \lim_{N\to\infty}\, 
\int\, g\cdot d\mu_N=\int_a^b\, g\cdot d\mu
\]

\noindent
on the  vector space
$C^0[a,b]$. Let us denote it by $L$.
Notice that $g\geq 0$ gives
$L(g)\geq 0$ and taking the identity function we have $L(1)=1$.
Now we   construct a non-decreasing function
$f(x)$ as follows:
To each $a<x\leq b$
we consider the family $\mathcal F_x$
of continuos functions
$g$ such that $0\leq g\leq 1$  and
there exists some $\epsilon>0$ with
$g(y)=0$ when $y\geq x-\epsilon$. In other words, $g$ has a support given by a compact subset
of the half-open interval 
$[a,x)$.
Set
\[ 
f(x)=\max_{g\in\mathcal F_x}\, L(g)
\]
Here $f(a)=0$ and it is obvious that $f$ is non-decreasing.
The reader should also verify that
$f$ is left continuous, i.e.
\[
\lim_{\epsilon\to 0}\, f(x-\epsilon)=f(x)
\] 
hold for every $a<x\leq b$.
There may exist a 
set $\{\eta_\nu\}$
where $f$ is discontinuous. Here a jump at
$\eta_\nu$ is given by a positive number
\[ 
\rho_\nu=\lim_{\epsilon\to 0}\, f(\eta_\nu+\epsilon)-f(\eta_\nu)
\]
To every such point we have the 
Heaviside function $H_\nu(x)$ and 
define the jump function
\[ 
s(x)=\sum\,\rho_\nu\cdot H_\nu(x)
\]
Then $f-s=f_*$ is continuous and we get the Riesz measure
\[ 
\mu= \mu_d+\mu_{f_*}
\] 
where the discrete part
\[
\mu_d=\sum\, \rho_\nu\cdot \delta_{\eta_\nu}
\]


\noindent
At this stage we leave it to the
reader
to verify the
equality below  for every  continuous functions $g(x)$.
\[ 
L(g)=\int_a^b\, g\cdot d\mu
\] 
Now Theorem 0.12 follows from the  Riesz representation theorem for 
non-negative and continuous linear functionals
on $C^0[a,b]$.


\medskip


\noindent
{\bf{Remark.}}
If $X^*$ denotes the dual space of the Banach space
$C^0[a,b]$ the sequence
$\{\mu_N\}$ converge in the so called weak-star
topology to $\mu$.
Conversely,
let $\mu$ be a non-negative Riesz measure on $[a,b]$ of total mass one.
We also assume that $\mu$ is continuous. So $\mu=\mu_f$ for some
non-decreasing and continuous function $f$ on $[a,b]$ with $f(a)=0$.
In this situation we can approximate
$\mu$ weakly by a sequence of discrete measures as follows:
For every positive integer $N\geq 2$
we define the discrete measure
\[ 
\mu_N=\sum_{k=1}^{k=N}\, p_k\delta_{x_k}
\]
where
\[
p_k=f(a+\frac{k(b-a)}{N})-f(a+\frac{(k-1)(b-a)}{N})
\quad\text{and}\quad  x_k=a+\frac{k(b-a)}{N})
\]
\medskip

\noindent
{\bf{Exercise.}}
Show that the sequence $\{\mu_N\}$ converges weakly to $\mu_f$.
The hint is to use uniform continuity of  the $g$-functions
in Theorem 0.12.

\bigskip

\noindent
{\bf{0.13 Cantor's function.}}
Consider the unit interval $[0,1]$.
Let $\mu_1=\frac{1}{2}[\delta_0+\delta_1]$.
Next, we get 
\[
\mu_2=\frac{1}{4}[\delta_0+\delta_{1/3}+\delta_{2/3}+\delta_1]
\]
\[
\mu_3= \frac{1}{8}\cdot 
[\delta_0+\delta_{1/9}+\delta_{2/9}+\delta_{3/9}+
[\delta_{6/9}+\delta_{7/9}+\delta_{8/9}+\delta_1]
\]
and so on where
the reader can recognize the inductive
construction.
Intuitively one removes
one third  of middle intervals at each step.
For every integer  $k\geq 4$ we get a discrete measure $\mu_k$
which assigns the point mass $2^{-k}$ at $2^k$ many points.

\medskip

\noindent
{\bf{0.14 Exercise.}}
Show
that
the sequence $\{\mu_k\}$ converges
weakly to a  limit measure  $\mu_f$ where $f$ is  continuous and
non-decreasing. The notable fact is that
$f$ is constant on
many intervals. To begin with it is constant on the middle interval $(1(3,2/3)$.
It is also constant on the intervals $(1/9,2/9)$ and $(7/9,8/9)$.
The total length on intervals where $f$ is constant becomes

\[
\frac{1}{3}+2\cdot \frac{1}{3^2}+\ldots=
\frac{1}{3}\cdot \sum_{\nu=0}^{\infty}\, (2/3)^\nu=1\tag{*}
\]

\noindent
The support of the measure $\mu_f$ is the closed complement of the removed
intervals above.
The construction is remarkable since
$f$ has a vanishing derivative in each  removed
open interval and at the same time   (*) holds while 
$f$ increases from zero to $f(1)=1$
so the function is not constant.
Hence Cantor's  function $f$ violates the fundamental theorem of calculus, i.e.
it is not recovered by an integral of its derivative.
Moreover, there is  defined intervals on the closed complement of the removed intervals above.

\medskip

\noindent
{\bf{0.15 Absolutely continuous functions.}}
Let $f$ be a non-decreasing 
and continuous function on $[0,1]$ with $f(0)=0$ and $f(1)=1$.
To each $0<\delta<1$ we consider
open  sets which consist of pairwise disjoint open intervals
$\{(a_\nu,b_\nu)\}$ where

\[
\sum\, (b_\nu-a_\nu)<\delta\tag{*}
\]

\noindent
No condition is imposed on the number of these intervals.
With $\delta$ fixed we set:
\[
V_f(\delta)= \max\, \sum\, f(b_\nu)-f(a_\nu)
\] 
where the maximum is taken over all finite families
$\{(a_\nu,b_\nu)\}$
for which (*) hold.
\bigskip


\noindent
{\bf{0.16 Definition.}}
\emph{The function $f$ is called absolutely continuous if}
\[
\lim_{\delta\to 0}\, V_f(\delta)=0
\]
\emph{The space of such functions is denoted by
$AC^0[0,1]$.}
\medskip


\noindent
It turns out that if 
$f\in AC^0[0,1]$ then it is recaptured from its derivative $f'(x)$.
This relies upon the theorem by F. Riesz in the next section which shows that
$f$ has an ordinary derivative outside a null set in the sense of Lebesgue.
After this one constructs the Lesbegue integral
of $f'$ to get a primitive function defined by

\[ 
F(x)=\int_0^x\, f'(t)\cdot dt
\]
The almost everywhere
existence of Lebesgue points implies that
the derivative of $F$ is equal to that of $f$ almost everywhere and
there remains to consider the difference
\[
g=f-F
\]
Here $g$ belongs to 
$AC^0[0,1]$  and its derivative is almost everywhere zero.
From this one can show that $g$ is identically zero and which gives
the equality
\[ 
f(x)=\int_0^x\, f'(t)\cdot dt\tag{*}
\]
In other words, every  absolutely continuous function is recovered by its derivative.
\bigskip

\noindent
{\bf{0.17 Fubini's theorem.}}
Let $\{f\uuu n\}$ be a sequence of continuous and non\vvv decreasing functions
defined on some interval $[a,b]$. We also assume that
every $f\uuu n$ is non\vvv negative and that the positive series
\[
\sum\uuu{n=1}^\infty\,f\uuu n(x)
\]
converges for every $x$. The sum yields a 
non-decreasing function $s(x)$.
As we shall explain in more detail later on, it follows that
$s(x)$ is a sum of a non\vvv decreasing function $s\uuu *(x)$
and a discrete jump\vvv function $s\uuu d(x)$.
Moreover, $s(x)$ has a derivative almost everywhere
and the same is true for each $f\uuu n$ by Lebesgue's theorem to be proved
in the next section.
Hence there exists a null\vvv set $E\uuu 0$
such that every $f\uuu n$ and $s$ have derivatives at
points outside $E\uuu 0$. In this situation Fubini proved
that the sum of derivatives converges, i.e. when
$x$ is outside $E\uuu 0$ then
\[ 
s'(x)=\lim\uuu{N\to \infty}\, \sum\uuu{n=1}^{n=N}\, 
f'\uuu n(x)
\]

\noindent
The proof of Fubini's theorem occurs at the end of the next section under the headline
Exercises and Examples.
\medskip

\centerline{\bf{0.18 Points of density.}}

\medskip

\noindent
Recall  from
Calculus  that a bounded and open set
$U$ 
is the disjoint union of intervalÊ$\{(a\uuu n, b\uuu n)\}$.
Its Lebesgue   measure is
defined by $\sum\, (b\uuu n\vvv a\uuu n)$ and denoted by $|U|$.
A subset $S$ of the real line is a null\vvv set if for every
$\epsilon>0$ there exists an open set $U$ such that
$S\subset U$ and $|U|<\epsilon$.
One shows easily that
every denumerable union of null\vvv sets again is a null\vvv set.
Next, let $E$ be a compact subset of ${\bf{R}}$. To each $\delta>0$
we get the open set
\[
E\uuu\delta=\{ x\,\colon\, \text{dist}(x,E)<\delta\}
\]


\noindent
These sets decrease with $\delta$ and the Lebesgue measure of $E$ is defined to be
\[
 |E|= \lim\uuu{\delta\to 0}\, |E\uuu\delta|\tag{i}
\]
\medskip

\noindent
{\bf{Exercise.}}
Show that a compact set $E$ is a null\vvv set if and only
if (i) above is zero. The hint is that whenever $U$ is an open set
which contains $E$, then there exists $\delta>0$ such that
$E\uuu\delta\subset U$.

\medskip

\noindent
Next, let $E$ be compact and
consider a point $x\in E$. It is called a point of density in $E$ if:
\[
\lim\uuu {h+k\to 0}\,
\frac{\bigl |E\cap [x\vvv k,x+h]\bigr|}{h+k}=0\tag{*}
\]
where $h,k$ both tend to zero under the sole assumption that
$h+k\to 0$.
\medskip

\noindent
{\bf{0.19 Theorem.}}
\emph{Almost every  $x\in E$ is a point of density.}
\medskip

\noindent
This result was established by Lebesgue. A simplification of the original proof
was later found by Vitali using a general covering lemma which
we announce below while the proof of Theorem 0.19 is postponed until
¤ 0.23.
\medskip

\noindent
{\bf{0.20 Vitali's covering theorem. }}
Let $F$ be an arbitrary bounded subset of ${\bf{R}}$.
Let $\mathcal V$ be a family of open intervals
with the properties: To every $x\in F$ and $\delta>0$ there
exists an intervalÊ$\omega\in\mathcal V$ such that
$x\in\omega$ and $|\omega|<\delta$.
In addition we assume that $\omega\subset (\vvv A,A)$ hold 
for some $A>0$ which is chosen so large that
$F$ is contained in a compact subset of $(\vvv A,A)$.
If $\omega=(a,b)$ is an interval we denote
by $3\cdot \omega$ the enlarged interval
$(a\vvv \ell,b+\ell)$ where $\ell=b\vvv a$ is the length of
$\omega$ so that $3\cdot \omega$ has length
$3\ell$. With this notation one has:
\medskip

\noindent
{\bf{0.21 Theorem.}}
\emph{There exists a sequence of pairwise disjoint intervals $\{\omega\uuu n\}$
in $\mathcal V$
which covers $F$ in Vitali's  sense which means
that for every positive integer $N$ one has
the inclusion}
\[
F\subset \bar\omega\uuu 1\cup\ldots\cup \bar \omega\uuu N\,\bigcup
\uuu{n>N}\, 3\cdot \omega\uuu n\tag{*}
\]


\noindent
\emph{Proof.}
Put
\[ 
\delta\uuu 1=
\sup\uuu{\omega\in \mathcal V}\, |\omega|
\]
Choose $\omega\uuu 1$ with $|\omega\uuu 1|>2\delta\uuu 1/3$.
Let $\mathcal V\uuu 1$ be the subfamily of intervals
$\omega\in\mathcal V$ which have empty intersection with
the closed interval $\bar\omega\uuu 1$.
Put
\[
\delta\uuu 2=
\sup\uuu{\omega\in \mathcal V\uuu 1}\, |\omega|
\]
Choose $\omega\uuu 2\in\mathcal V\uuu 1$ with
$|\omega\uuu 2|>2\delta\uuu 2/3$.
In the next step $\mathcal V\uuu 2$ is the subfamily of
intervals in $\mathcal V$ which have empty intersection with
$\bar\omega\uuu 1\cup\bar\omega\uuu 2$ and
\[
\delta\uuu 3=
\sup\uuu{\omega\in \mathcal V\uuu 2}\, |\omega|
\]
Choose $\omega\uuu 3\in\mathcal V\uuu 2$ with
$|\omega\uuu 3|>2\delta\uuu 3/3$.
We continue in this way and get a sequence $\{\omega\uuu n\}$
where the intervals by construction are pairwise disjoint.
At this stage we leave it to the reader to verify that
the sequence $\{\omega\uuu n\}$
satisfies (*) in Theorem 0.21 for every positive integer $N$.
\bigskip

\noindent {\bf{0.22 Exercise}}
Since $\{\omega\uuu \nu\}$ is a sequence of disjoint intervals which all are 
contained in a bounded
set, it follows that
\[ 
\sum\,\delta\uuu n<\infty
\]
Use
this convergence and the inclusions in (*) for every positive integer $N$
to show that the outer measure of $F$ is majorized by:
\[
|F|^*\leq \sum\,\delta\uuu n
\]

\bigskip



\noindent
\emph{0.23 Proof of Theorem 0.19.}
For each  integer $n\geq 2 $ we denote by 
$E(n)$ the subset of $E$ which consists of points
such that
\[
\liminf\uuu{h+k\to 0} \,\, \frac{ \bigl|E\cap (x\vvv k,x+h)\bigr  |}{h+k} \leq  1\vvv 
\frac{1}{n}\tag{i}
\]
Let $\mathcal L(E)$ be the set of points of density in $E$.
It is clear that 
\[
 E\setminus \mathcal L(E)=\bigcup\uuu{n\geq 2}\,
E(n)
\] 
We 
conclude that $E\setminus \mathcal L(E)$ is a null\vvv set if
$E(n)$ are null\vvv sets for every $n\geq 2$.
To prove this for a given $n$ we proceed as follows:
For  each  $\epsilon>0$ we can choose
$\delta>0$ such that
\[
|E\uuu\delta\setminus E|<\frac{\epsilon}{n}\tag{ii}
\]
If $x\in E(N)$ the definition of limes inferior means that we can choose 
arbitrary small open intervals $\omega$ which contain $x$
while $\omega\subset E\uuu\delta$ and at the same time
\[
\frac{ \bigl|E\cap \omega \bigr|}{|\omega|} \leq  1\vvv\frac{1}{n}\tag{iii}
\]
It is clear that the family of such intervals is a Vitali covering of
$E(n)$.
Hence we find a sequence $\{\omega\uuu \nu\}$
from Theorem XX and by the remark in XX the outer measure
\[ 
|E(n)|^*\leq \sum\, |\omega\uuu\nu|
\]
Next, for each fixed $\nu$ we have
\[
|\omega\uuu\nu|=
|\omega\uuu\nu\cap E|+
|\omega\uuu\nu\cap (E\uuu\delta\setminus E)|
\]
Since $\{\omega\uuu\nu\}$ are disjoint and
(iii) above hold for every $\nu$ it follows that
\[
\sum\, |\omega\uuu\nu|\leq (1\vvv \frac{1}{n})
\cdot \sum\, |\omega\uuu\nu|+|E\uuu\delta\setminus E|
\]
Hence (ii) gives
\[
\sum\, |\omega\uuu\nu|\leq \epsilon
\]
Since $\epsilon$ was arbitrary we conclude that $E(n)$ is a null\vvv set
and Lebegue's theorem is proved.
\medskip

\noindent
{\bf{0.24 Exercise.}} Use Lebegue's theorem to show that if
$F$ is a set such that there exists a constant $c<1$ for which
\[ 
\bigl| F\cap (a,b)\,\bigr|^*\leq c(b\vvv a)
\] 
hold for every interval $(a,b)$, then $F$ is a null\vvv set.













\newpage


\centerline{\bf\large {1.B. Derivatives of functions}}

\bigskip 
 

 \noindent
In the text\vvv book \emph{ThŽorie de l'intŽgration} from 1904, Lebesgue proved that
a monotone function defined in a real interval has an ordinary
derivative outside a null\vvv set.
For an arbitrary continuous function
a  more general result  was discovered by M. Young
and Denjoy which goes as follows:
Let $f(x)$ be a real\vvv valued continuous function defined on some interval $(a,b)$.
For each $a<x<b$ we set

\[ 
D^*(x)=\limsup\uuu{h+k\to 0}\, \frac{f(x+h)\vvv f(x\vvv k)}{h+k}
\]
where $h$ and $k$ are positive when we pass to the limes
superior. Similarly
\[
D\uuu *(x)=\liminf\uuu{h+k\to 0}\, \frac{f(x+h)\vvv f(x\vvv k)}{h+k}
\]

\medskip

\noindent
{\bf{1.1 Theorem.}}
\emph{Outside a (possibly empty) null\vvv set $E$ of $(a,b)$
the following two possibilities occur for each
$x\in (a,b)\setminus E$: Either there exists a common finite limit}
\[
D^*(x)= D\uuu *(x)\tag {*}
\]
Or else one has
\[
D^*(x)=+\infty\quad\text{and}\quad D\uuu *(x)=\vvv \infty
\tag{**}
\]
\medskip

\noindent 
{\bf{Remark.}}
Above the pair $h,k)$
tends to zero under the sole condition that $h+k\to 0$. We can  take
$k=0$ or $h=0$ and consider one\vvv sided limits:

\[
D^+(x)=\limsup\uuu{h\to 0}\, \frac{f(x+h)\vvv f(x)}{h}
\quad\text{and}\quad
d^+(x)=\liminf\uuu{h\to 0}\, \frac{f(x+h)\vvv f(x)}{h}\tag{i}
\]
\[
D\uuu +(x)= \limsup \uuu{k\to 0}\, \frac{f(x)\vvv f(x\vvv k)}{k}
\quad\text{and}\quad
d\uuu + (x)=\liminf\uuu{k\to 0}\, \frac{f(x)\vvv f(x\vvv k)}{k}\tag{ii}
\]
With these notations it is clear that:
\[
D\uuu *(x)\leq d^+(x)\leq D^+(x)\leq D^ *(x)
\]
So the equality $D\uuu *(x)= D^*(x)$ entails that $f$
has an ordinary right derivative. Since 
\[
D\uuu *(x)\leq d\uuu +(x)\leq D\uuu +(x)\leq D^ *(x)
\]
we conclude that if (*) holds in the theorem, then
$f$
has a ordinary derivative at $x$.
If (**) occurs at a point
$x$, then
the graph of $f$ close to $x$ is  steep but may also change sign 
in a small interval around such a point. Take for example $x=0$
and let
\[
f(x)=\sqrt{x}\quad\text{when}\quad x>0\quad\colon\quad
f(x)=\sqrt{\vvv x}\quad \text{when}\quad x<0
\]
With $k=0$ and $h>0$ we see that
$D^*(0)=+\infty$ and with $h=0$ and $k>0$ we see that
$D\uuu *(=)=\vvv \infty$. 
Next,
recall Weierstrass'
construction of
a continuous function
$f(x)$ which fails to have an ordinary
derivative at every point in the interval $(a,b)$. The Denjoy\vvv Young
theorem shows that
such a continuous function has a "turbulent" graph where
$D^*(x)=+\infty$ and $D\uuu *(x)=\vvv \infty$
both hold for all $x$ outside a null\vvv set.
\medskip

\noindent
{\bf{1.2 The case of monotone functions.}}
If the continuous function $f$ is non\vvv increasing or
non\vvv decreasing, then 
case (**) cannot occur. So   Theorem 1.1 implies that
a monotone continuous function has an ordinary derivative almost everywhere.
Concerning Theorem 1.1 its
proof relies upon 
Lebesgue's result about points of density.
The interested reader may
consult Riesz'  plenary talk at the IMU\vvv congress in ZŸrich (1932) for
a historic account about derivatives of functions on
the real line
and  the subsequent proof follows 
Riesz' presentation in [ibid] closely.
 
\medskip


\noindent
{\bf 1.3 Forward Riesz intervals.} 
Let $g(x)$ be a real-valued and continuous function  
defined on some  open   interval  $(a,b)$,
The forward Riesz set $\mathcal F_g$
consists of all points $a<x<b$ 
for which there exists some $x<y\leq b$ such that
\[
g(x)<g(y)\tag{*}
\]
If $g$ is  
non-decreasing then $\mathcal F\uuu g=\emptyset$.
Excluding this case, continuity entails that
$\mathcal F_g$
is an open subset of $(a,b)$ and hence a disjoint union of intervals
\[ 
\mathcal F_g=\cup\,(\alpha_\nu,\beta_\nu)\tag{1}
\]
Each  interval in (1)
is called a \emph{forward Riesz interval} of $g$. It may occur that
some interval is of the form $(\alpha,b)$ i.e. $b$ is a right end-point. Similarly
$a$ can be a left end-point. For example, if $g$ from the start is
strictly increasing then
$\mathcal F_g=(a,b)$.



\medskip

\noindent {\bf 1.4 Proposition} \emph{For each forward Riesz interval $(\alpha,\beta)$
one has }
\[
g(\beta)=\max_{\alpha\leq x\leq\beta}\, g(x)\tag{*}
\]
\medskip

\noindent 
\emph{Proof.}
Assume the contrary. This gives some
maximum point $\alpha\leq x^*<\beta$ for the $g$-function on the closed interval 
$[\alpha,\beta]$.
Now $x^*\in\mathcal F_g$ which means that
\[ 
\exists\, y>x^*\quad\text{and}\quad 
g(x^*)>g(y)
\]
Since $x^*$ is a maximum point over $[\alpha,\beta]$ we must have $y>\beta$. But
then $\beta\in\mathcal F_g$ which is impossible since
$\beta$ was a boundary point of the open set $\mathcal F_g$.
\bigskip

\noindent
{\bf  1.5 Backward Riesz intervals}
Put
\[
\mathcal B_+g=\{ a<x<b\colon\,\,\exists\, a<y<x\,\quad\colon\quad \, g(y)>g(x)\}
\]
Again $\mathcal B_g$ is open and hence a disjoint union of open intervals
$(c_\nu,d_\nu)$. They are  called backward Riesz intervals. By  similar
reasoning as above one shows that if $(c,d)$ is a backward Riesz interval then
\[ 
g(c)=\max_{c\leq x\leq d}\, g(x)\tag{**}
\] 





\bigskip



\centerline {\bf 1.6 A study of monotone functions.}
\bigskip

\noindent
Let $f(x)$ be a continuous and
\emph{non-decreasing} function on $[a,b]$.
To each $a<x<b$ we set 
\[ 
D^+(x)=\limsup_{h\to 0}\,
\frac{f(x+h)-f(x)}{h}\tag{1}
\] 
where  limes superior is taken as
$h>0$  decrease to zero.
The function
$x\mapsto D^+(x)$ takes values
in $[0,+\infty]$.
\medskip

\noindent 
{\bf{ 1.7 Proposition.}} \emph{For each positive number
$C$
the following set-theoretic inclusion holds:}

\[
\{ D^+(x)>C\}\subset \mathcal F_g\quad\text{where}
\quad g(x)= f(x)-Cx
\]
\medskip

\noindent 
\emph{Proof.}
Suppose that $D^+(x)>C$ for some $a<x<b$. The definition of
limes superior gives some $y>x$ such that 
\[ 
\frac{f(y)-f(x)}{y-x}>C\tag{i}
\]
Then $g(y)-g(x)= f(y)-f(x)-C(y-x)>0$ and 
hence $x\in\mathcal F_g$.


\medskip

\noindent 
{\bf 1.8 Proposition} \emph{For every $C>0$
the outer 
Lebesgue measure
of the set $\{D^+>C\}$  satisfies the inequality}
\[
\bigl|\{D^+>C\}\bigr|^*
 \leq\,\frac{f(b)-f(a)}{C}
 \]
\medskip

\noindent 
\emph{Proof.}
With $g(x)=f(x)-Cx$ as above  one has an interval decomposition
$\mathcal F_g=\cup\,(\alpha_\nu,\beta_\nu)$ and
the inclusion from Proposition 1.4 gives
\[
|\{D^+>C\}|^*\leq \sum\,(\beta_\nu-\alpha_\nu)\tag{1}
\]

\medskip

\noindent
Apply Proposition 1.4  to the forward Riesz intervals of $g$. This gives
for every $\nu$:
\[
f(\alpha_\nu)-C\cdot \alpha_\nu\leq f(\beta_\nu)-C\cdot \beta_\nu
\]
Rewriting the last inequality we get
\[
C(\beta_\nu-\alpha_\nu)\leq f(\beta_\nu)-f(\alpha_\nu)
\]
Taking the sum over all $\nu$ we obtain
\[ 
C\cdot \sum\,(\beta_\nu-\alpha_\nu)\leq\,\sum\,
f(\beta_\nu)-f(\alpha_\nu)\leq f(b)-f(a)\tag{2}
\]
where the last inequality holds since $f$ is non-decreasing.
Now (1) and (2) give the requested inequality in
Proposition 1.8.

\bigskip

\noindent
{\bf 1.9 The $d_+$-function}. To each $a<x<b$ we put
\[
d_+(x)=\liminf_{k\to 0}\,\,
\frac{f(x)-f(x-k)}{k}
\]


\noindent
Let $c>0 $ and set
\[
h(x)=f(x)-c
\]
A similar reasoning  as in Proposition 1.4 gives the inclusion
\[
\{ d_+ < c\}\subset\mathcal B_h
\]
where the right hand side is the backward Riesz set from  1.5.
\bigskip


\noindent
{\bf{1.10 Some inequalitites.}}
Consider a pair $0<c<C$ and the intersection
\[
E=\{d\uuu +<c\}\,\cap \{D^+>C\}
\]
Now (1.9) gives the inclusion
\[ 
E\subset \{D^+>C\}\,\cap \mathcal B\uuu h\tag{i}
\]
Let  $\{(\alpha\uuu \nu,\beta\uuu\nu)\}$
be the interval decomposition of the open set
$\mathcal B\uuu h$.
For each $\nu$ we  consider the restriction of $g(x)= f(x)\vvv Cx$
to the interval
$(\alpha\uuu \nu,\beta\uuu\nu)$ and Proposition 1.8 gives the inequality
\[
|\{D^+>C\}\,\cap (\alpha\uuu \nu,\beta\uuu\nu)\,|^*\leq
\frac{f(\beta\uuu \nu)\vvv f(\alpha \uuu\nu)}{C}\tag{ii}
\]
Since $(\alpha\uuu\nu,\beta\uuu\nu)$
is a backward Riesz interval of $f(x)\vvv c$ we have
$f(\beta\uuu \nu)\vvv f(\alpha \uuu\nu)\leq c(\beta\uuu\nu\vvv \alpha\uuu\nu)$.
Hence (i) gives:
\[
|\{D^+>C\}\,\cap (\alpha\uuu \nu,\beta\uuu\nu)\,|^*\leq
\frac{c}{C}\cdot (\beta\uuu \nu\vvv \alpha \uuu\nu)\tag{iii}
\]
Since the backward Riesz intervals are disjoint 
a summation over $\nu$ and the inclusion (i) give:
\[
|\{D^ +>C\}\,\cap \{d\uuu +<c\}|^*\leq \frac{c}{C}(b\vvv a)\tag{*}
\]
\medskip

\noindent
{\bf{1.11 Proof of Lebesgue's theorem.}}
The  function $f$ restricts to a non\vvv decreasing function on
an arbitrary open subinterval $(a\uuu *,b\uuu *)$ of $(a,b)$
and since both $D^+$ and $d\uuu +$ are constructed by limits close to a point we
get the same inequality as in (*) above,  i.e. one has
the inequality

\[
|\{d\uuu +<c\}\,\cap \{D^+>C\}\,\cap (a\uuu *,b\uuu *)|^*
\leq \frac{c}{C}\cdot (b\uuu *\vvv a\uuu *)
\]


\noindent
Now the criterion from ¤XX implies that
$\{d\uuu +<c\}\,\cap \{D^+>C\}$ is a null\vvv set.
Apply  this for  pairs $c=q<r=C$ where $q,r$ are rational numbers. Since
a denumerable union  of null\vvv sets  is a null\vvv set
we conclude that  the equality
\[ 
d\uuu +(x)= D^+(x)\tag{i}
\]
holds almost everywhere.
In the same way one proves that the equality
\[
d^+(x)= D\uuu +(x)\quad\text{holds almost everywhere}\tag{i}
\]

\medskip

\noindent
Finally, it is obvious that when (i\vvv ii) hold then
$f$ has an ordinary
derivative which proves Lebegue's theorem that every
monotone function
has a derivative almost everywhere.
\bigskip

\noindent
{\bf{1.12 An extension of Lebesgue's theorem.}} 
Let $f$ be a continuous function on the closed unit interval $[0,1]$.
Suppose that $E$ is a measurable subset of $(0,1)$
such that the restriction of $f$ to $E$ is non\vvv decreasing.
Removing an eventual zero set we also assume that
$E=\mathcal L(E)$, i.e. every $x\in E$ is a point of density for
$E$ as explained in ¤ XX.
Using exactly the same methods as above it follows that 
there is a (possibly empty) null\vvv set
$S\subset E$, there exists a derivative at every
$x\in E$ in the sense that
\[
\lim\uuu{h+k\to 0}\, \frac{f(x+h)\vvv f(x\vvv k)}{h+k}
= f'\uuu E(x)\tag{1}
\] 
exists for each $x\in E\setminus S$ where
the limit is restricted in the sense that $x+h$ and $x+k$ belong to $E$
during the passage to $h+k\to 0$.
But since $x$ is a point of density 
(1) holds without this restriction, i.e. $f'\uuu E(x)$ gives an ordinary
derivative of $f$.
Let us supply the details for this assertion. We may take $x=0$
and replacing $f$ by $f\vvv f'\uuu E(0)x\vvv f(0)$ we can assume that
$f'\uuu E(0)=f(0)=0$.
Next, let $0<\epsilon<1/4$ which gives some $\delta>0$ such that
if $0<x<\delta$ and $x\in E$ then
\[ 
f(x)\leq \epsilon\cdot x
\]
At the same time the density condition entails
that if $\delta$ is small enough then 
\[
|E\cap (\vvv x,x)|\geq 2x(1\vvv\epsilon)
\quad\colon\quad 0<x<\delta
\]
If we  consider some $0<x<\delta/2$ we see that
(xx) implies 
the interval $(x+4\epsilon\cdot x,x)$
must intersect $E$ and if $x^*\in E$ is in this interval we get
\[ 
f(x)\leq f(x^*)\leq \epsilon\cdot x^*\leq
\epsilon\cdot 2x
\]
Since $\epsilon>0$ this proves that $D^+(0)=0$ and in the same way the
reader can verify that the right
derivative at $x=0$ vanishes.


 



\bigskip


\centerline {\bf{1.13 Proof of Theorem 1.1}}
\bigskip

\noindent
For each non\vvv negative integer $n=0,1,2,\ldots$ and every
rational number $r\in (a,b)$ we denote by
$E\uuu{n,r}$ the set 
of all $r<x<b$ such that
\[
\frac{f(x)\vvv f(\xi)}{x\vvv \xi}>\vvv n
\quad\colon\quad r<\xi<x
\]

\medskip

\noindent
{\bf{Exercise.}}
Show the set\vvv theoretic inclusion

\[
\{D\uuu *(x)>\vvv \infty\}\subset
\bigcup E\uuu{n,r}
\]
where the union is taken over allÊ$n\geq 0$ and
every rational number $a<r<b$.
\medskip

\noindent
{\bf{1.14 Proposition.}} \emph{For each  pair $(n,r)$ the equality}
\[ 
D^*(x)= D\uuu *(x)
\] 
\emph{holds almost everywhere in the measurable set $E\uuu{n,r}$.}
\medskip

\noindent
\emph{Proof.}
Replacing the interval $(a,b)$ by $(r,b)$
and $f$ by $f(x\vvv r)+nx$ we can assume that
$r=n=0$
and now $E\uuu {0,0}\subset (0,b\vvv r)$
where the restriction of $f$ to this measurable set is
monotone, i.e.
\[
0<\xi<x\implies f(x)>f(\xi)
\]
holds for every pair $\xi<x$ in $E\uuu{0,0}$.
To simplify notations we set $E=E\uuu{0,0}$.
Let $E\uuu *$ be the set of density for $E$ as defined in 
XX and recall from XX  that $E\setminus E\uuu *$ is a null\vvv set.
Ignoring this null\vvv set we consider the 
restriction of $f$ to $E\uuu *$ which again is a 
non\vvv decreasing function. The extended version from 1.12 of
Lebegue's theorem applies and 
shows that  after removing  another null\vvv set from
$E\uuu *$ if necessary, then 
the limit below exists for each $x\in E\uuu *$:
\[
D(x)=\lim\uuu{h+k\to 0}\, \frac{f(x+h)\vvv f(x\vvv k)}{h+k}\tag{*}
\]

\noindent
In the same way one proves that if a   null\vvv set
is removed from the set
\[ D^*(x)=+\infty\}
\] 
then $f$ has an ordinary derivative so that  $D^*(x)= D\uuu *(x)$.
This finishes the proof of the Denjoy\vvv Young theorem.


\centerline{\bf{1.15 Examples and Exercises.}}
\bigskip

\noindent
Above we have studied monotone continuous functions.
There also exist non\vvv decreasing jump functions
which arise as follows: Let $\{\xi\uuu n\}$ be a
sequence of real numbers in $(0,1)$.
They are not ordered and may give a dense set. For example, we can take some
enumeration of all rational numbers in $(0,1)$.
Next, let $\{\delta\uuu n\}$ be a sequence of positive numbers such that
$\sum\,\delta\uuu n<\infty$. To each $n$ we get the jump function
$H\uuu n(x)$ where
\[
H\uuu n(x)=0\quad\colon\quad x<\xi\uuu n\quad
\text{and}\quad
H\uuu n(x)=\delta\uuu n\quad\colon\quad x\geq \xi\uuu n
\]
Now
\[ 
s(x)=\sum\, H\uuu n(x)
\]
is a non\vvv decreasing function which has jump\vvv discontinuites at
each $\xi\uuu n$.
\medskip

\noindent
{\bf{Exercise.}} Show that $s$ is pointwise continuous at every
$x$ outside the set $\{\xi\uuu n\}$, i.e. show that if
$\epsilon>0$ then there exists $\delta>0$ such that
\[
s(x+\delta)<s(x)+\epsilon
\quad\text{and}\quad
s(x\vvv \delta)>s(x)\vvv \epsilon
\]


\noindent 
Less evident is the following:

\medskip

\noindent
{\bf{1.16 Theorem.}}
\emph{$s(x)$ has an ordinary derivative which is equal to zero almost everywhere.}
\medskip

\noindent
\emph{Proof.}
Let $\alpha>0$ and denote by  $E$ be the subset of $(0,1)$ which consists of
numbers $0<x<1$ such that
\[
\limsup\uuu{h+k\to 0}\, \frac{
s(x+h)\vvv s(x\vvv k)}{h+k}> \alpha
\]
It suffices to show that $E$ is a null\vvv set.
To prove this we consider some $\epsilon>0$ and
choose $N$ so large that
\[ 
\sum\uuu{n>N}\, \delta\uuu n<\alpha\cdot \epsilon\tag{i}
\]
Set $s\uuu *(x)= s(x)\vvv (H\uuu 1(x)+\ldots+H\uuu N(x))$.
If $E\uuu *$
is the corresponding set in (x) with $s$ replaced by $s\uuu *$ then
$E$ and $E\uuu *$ only differ by the finite set $\xi\uuu 1,\ldots,\xi\uuu N$
so the measures of $e$ and $E\uuu *$ are the same.
Now we apply 
Vitali's covering theorem using $s\uuu *$ and obtain a
a sequence of disjoint intervals $\{a\uuu n,b\uuu n)\}$
which yields a Vitali covering of $E\uuu *$ and at the same time
\[
\frac{s\uuu *(b\uuu\nu)\vvv s\uuu *(a\uuu\nu)}{b\uuu\nu\vvv a\uuu\nu}
\geq \alpha
\]
It follows that
\[
s\uuu *(1)\vvv s\uuu *(0)\geq
\alpha\cdot \sum\, (b\uuu\nu\vvv a\uuu\nu)\tag{ii}
\]
At the same time (i) entails that $s\uuu *(1)\vvv s\uuu *(0)\leq
\alpha\cdot \epsilon$ and hence we have
\[
|E|^*= |E\uuu *|^*\leq \sum\, (b\uuu\nu\vvv a\uuu\nu)\leq \epsilon
\]
Since $\epsilon$ was arbitrary we get $|E|^*=0$ as requested.



\newpage


\centerline{\bf{1.17 Stieltjes' Moment problem.}}
\bigskip

\noindent
For a full account of Stieltjes'  results  we refer to
his collected work
[Stieltjes]. Here we shall give some examples to illustrate
the flavour of moment
problems. We are given
a real\vvv valued and cointinuous function $f(x)$ defined on
$x\geq 0$ whose absolute value gets so small as
$x\to+\infty$ that the integrals
\[ 
\int_0^\infty\, x^n\cdot |f(x)|\, dx<\infty
\] 
for all positive integers $n$. At first sight one may expect that
if
\[
\int_0^\infty\, x^n\cdot f(x)\, dx=0
\] 
hold for all $n$, then $f$ must be identically zero. However, this is not
true. 
We shall give examples below. But first we
insert the following

\medskip

\noindent
{\bf{Exercise.}}
Let $g(x)$ be an arbitrary continuous function on
$[0,1]$. Then the following two equalities hold:
\[
\int_0^1\, g^2(x)\, dx=
\frac{2}{\pi}
\lim_{R\to \infty}\int_0^R\,\bigl[ \int_0^1\, \cos (st)g(t)\,dt\bigr
]^2\, ds
\]
\[
\int_0^1\, g^2(x)\, dx=
\frac{2}{\pi}\lim_{R\to\infty}\int_0^R \,\bigl[ \int_0^1\, \sin (st)g(t)\,dt\bigr
]^2\, ds
\]
The hint is to apply  Parseval's formula for $L^2$-functions on
the real line as explained in ¤¤- distribution theory.
\medskip

\noindent
Next, consider a test\vvv function $\phi(s)$ supported by $[0,1]$.
Now there exists the cosine integral
\[ 
\Phi(x)=\int_0^1\, \cos(sx)\cdot \phi(s)\, ds
\]
This function satisfies the integrability condition (*). 
For example, if $m\geq 1$ we perform $2m$-many partial
integrations and find that
\[ 
x^{2m}\Phi(x)=(-1)^m\cdot \int_0^1\, \cos(sx)\cdot 
\phi^{(2m)}(s)\, ds
\]
Similarly we have the sine-transform:
\[ 
\Psi(x)=\int_0^1\, \sin(sx)\cdot \phi(s)\, ds
\]
For each positive integer $p$ a partial integration gives
\[ 
\Phi(x)+i\Psi(x)=\frac{(-1)^p}{(is)^p}\int_0^1
e^{ixs}f^{(p)}(s)\, ds
\]
\medskip


\noindent
Using this and the exercise above the reader may verify the equalities
below for every non-negative integer $p$:
\[
\frac{2}{\pi}\int_0^\infty\, x^{2p}\cdot \Phi(x)^2\,dx=
\frac{2}{\pi}\int_0^\infty\, x^{2p}\cdot \Psi(x)^2\,dx
=m_p^2
\] 
where we have put
\[ 
m_p^2=\int_0^1\, [ f^{(p)}(s)\,]^2\, ds
\]
\medskip

\noindent
Now we consider the non-decreasing functions
\[ 
G(x)=\frac{2}{\pi}\int_0^{\sqrt{x}}\, \Phi(s)^2\, ds
\quad\text{and}\quad
H(x)=\frac{2}{\pi}\int_0^{\sqrt{x}}\, \Psi(s)^2\, ds
\]
From the above we obtain

\[
m_p^2=\int_0^\infty\, x^p\cdot G(x)\, dx=
\int_0^\infty\, x^p\cdot H(x)\, dx
\]
Since $G\neq H$ this gives an example where
the moment problem has no unique solution with
$c_p= m_p^2$.
\medskip

\noindent
{\bf{Remark.}}
The reason why uniqueness fails above is that
the sequence $\{m_p\}$ increases rather rapidly. In
fact, whenever $\phi$ is a test-function which is not identically zero then
\[ 
\sum_{p=1}^\infty
\frac{1}{m_p^{\frac{1}{p}}}=+\infty
\]

\noindent
This divergence is proved by analytic function theory in
¤ XX.
Stieltjes said that a sequence
of non-negative numbers
$\{c_n\}$ yields a \emph{determined moment problem}
if there exists a unique non-decreasing and 
continuous function $f(x)$ which satisfies (*)( and (**) above.
We refer to the notes sbout functional analysis where
the moment problem is
discussed in more detail which includes conditions for the 
moment problem to be determined.




































\newpage


\centerline{\bf II. Abstract measure theory}


\bigskip



\centerline {\bf{Introduction.}} 

\bigskip


\noindent
To get  some intuition we  present the theory
using concepts
from
probability theory.
A sample space
consists of a pair  $(\Omega,\mathcal B)$ where
$\Omega$ is a set and  $\mathcal B$ a
Boolean $\sigma$-algebra of subsets.
Thus, if $\{A_\nu\}$ is a  
denumarable family
of sets in $\mathcal B$ 
indexed by non-negative
integers, then  $\cap \,A_\nu$ and $\cup \,A_\nu$  stay in
$\mathcal B$.

\medskip

\noindent {\bf 0.1 Measurable functions.}
A real valued function $f$  defined on $\Omega$ is measurable if
the inverse sets 
\[
f^{-1}(-\infty,a)\,\,\text{and}\,\,
f^{-1}(-\infty,a]\,\,\,\text{both belong to}\,\,\mathcal B\quad\colon\quad 
a\,\,\text{any real number}\tag{0.1.1}
\]
The class of such functions is denoted
by
$\mathcal M$.
\medskip

\noindent
{\bf{Exercise.}}
Use that $\mathcal B$ is a $\sigma$-algebra to show that
a real-valued function $f$ is measurable if
the sets in (0.1.1) belong to
$\mathcal b$ for every rational number $a$.
Next, let $f$ and $g$ be a pair of measurable functions.
Then $f+g$  is measurable. To see this the reader can check that
\[
\{f+g<a\}
=\cup_{q\in Q}\, \{f<q\}\cap \{g<a-q\}
\]
where the union is taken over all rational numbers, and in a similar way
one proves that
$\{f+g\leq a\}$ are measurable sets for every real number $a$.
Conclude that $\mathcal M$ is a vector space of the real number field.



\medskip







\noindent 
{\bf 0.2 Probability measures.}
A probability measure $\mu$ is a map
\[
\mu\colon\,\mathcal B\to [0,1]
\] 
which assigns a numer
$0\leq\mu(A)\leq 1$
for every set $A$ in $\mathcal B$, and
$\sigma$-additivity
means that
if $\{A_\nu\}$ is a sequence of pairwise
disjoint sets in $\mathcal B$, then
\[ 
\mu(\cup\,A\nu)=\sum\,\mu(A_\nu)
\] 
Finally, every probability measure is normalized, i.e. 
$\mu(\Omega)=1$. 
The family of probablility measures  is denoted by
$P(\Omega,\mathcal B)$.





\medskip

\noindent
{\bf 0.3 Nullsets.}
A subset $F$ of $\Omega$ is  a null set with respect to a
probability measure $\mu$
if there to each $\epsilon>0$ exists $A\in\mathcal B$ such that
\[ F\subset A\quad\text{and}\quad \mu(A)<\epsilon
\]
The class of null-sets  is denoted by
$\mathcal N_\mu$. By
$\sigma$-additivity  
$\mathcal N_\mu$ is stable under  a denumarable 
union, i.e.
\[
\{F_\nu\}\subset\mathcal N_\mu\implies
\cup\,F_\nu\in\mathcal N_\mu
\]


\noindent
Notice that one does not require that a null-set belongs to
$\mathcal B$.
\medskip

\noindent
{\bf {0.4 $\mu$-measurable sets.}}
Let $B\subset \Omega$ be an
arbitrary  subset. Its outer - resp. inner
$\mu$-measure are defined by
\[ 
\mu^*(B)=\min_{A\in\mathcal B}\,\mu(A)\quad\colon B\subset A\quad\colon\quad
\mu_*(B)=\max_{A\in\mathcal B}\,\mu(A)\quad\colon 
\,\, A\subset B
\]
If $\mu_*(B)= \mu^*(B)$
one says that
$B$ is $\mu$-measurable and
the common  number is denoted by $\mu(B)$.
Let $\mathfrak{M}_\mu$
be the family if all $\mu$-measurable subsets of $\Omega$.
It is clear that we have the inclusion
\[
\mathcal B\subset\mathfrak{M}_\mu
\]



\noindent
{\bf{0.5 Exercise.}}
Show that a set $B$ is $\mu$-measurable if and only if there exists
a set $B_*\subset B$ such that $B\setminus B_*\in\mathcal N_\mu$ 
and
$B$ belongs to $\mathcal B$. Conclude that
$\mathfrak {M}_\mu$ is a Boolean $\sigma$-algebra 
of subsets of $\Omega$
generated by $\mathcal B$ and $\mathcal N_\mu$. Show also that the map
\[ 
B\mapsto \mu(B)
\]
is
$\sigma$-additive on $ \mathfrak {M}_\mu$.


\bigskip


\noindent 
{\bf 0.6 $\mu$-measurable functions.} 
A real-valued function $f$ on $\Omega$ is 
$\mu$-measurable if
\[
f^{-1}(-\infty,a)\,\,\text{and}\,\,
f^{-1}(-\infty,a]\,\,\,\text{both belong to}\,\,\mathfrak{M}_\mu\quad\colon\quad 
a\in\bf R
\]
Denote this class by $\mathcal M_\mu$.
Since $\mathcal B\subset \mathfrak{M}_\mu$ one has the inclusion
\[
\mathcal M\subset\mathcal M_\mu
\]
\medskip




\noindent
{\bf{0.7 Teorem.}}
\emph{Let $f\in \mathcal M_\mu$. Then 
there exists a null set
$F\in\mathcal N_\mu$  and some $f_*\in \mathcal M$ such that
$f=f_*$ in $\Omega\setminus F$. Thus, after modifying a $\mu$-measurable 
function on a 
null set with respect to $\mu$ it becomes "truly measurable".}
\medskip


\noindent
\emph{Proof.}
Let 
$\{q_\nu\}_1^\infty$  enumerate  the set $Q$
of
rational numbers.
The exercise in (0.5)
to each
$q_\nu$  a  pair  of disjoint sets
$F_\nu\in \mathcal B$ and $G_\nu\in\mathcal N_\mu$
such that
\[
f^{-1}(-\infty,q_\nu)=F_\nu \cup\,G_\nu
\]
We can also regard the inverse image of the singleton sets
and find for every
$q_\nu$ a disjoint pair $H_\nu\in\mathcal B$ and $S_\nu\in\mathcal N_\mu$
\[
f^{-1}(\{q_\nu\})=H_\nu \cup\,S_\nu
\]
Set
\[
G^*=\cup\, G_\nu\bigcup\cup S_\nu
\]
Here $G^*\in\mathcal N_\mu$ which gives
the existence
of a decreasing sequence of sets
$\{W_\nu\}$ in
$\mathcal B$ such that
\[
\mu(W_\nu)<2^{-\nu}\quad\&\quad G^*\subset \cap\, W_\nu
\]
Now  $W_*=\cap W_\nu$ belons to $\mathcal B$
and  is also a null-set for $\mu$. Finally, 
define the function
$f_*$ by
\[
f_*(\omega)=f(\omega)\quad\colon
\omega\in \Omega\setminus W_*\quad\text{and}\quad
f_*|W_*=0 
\]
By this construction $f_*\in\mathcal M_\mathcal B$ and $f_*$ 
differs from $f$ on a null set.

\bigskip


\noindent 
{\bf {0.8 Equivalence classes of $\mu$-measurable functions.}}
A pair $f,g$ in $\mathcal M_\mu$ are called equivalent if they
are equal outside a null set.
Theorem 0.7
shows that
every equivalence class can be represented by
a 
$\mathcal B$-measurable function.




\medskip


\noindent
{\bf 0.9 Convergene in $\mu$-measure.}
We say that a  sequence $\{f_n\}$ in $\mathcal M_\mu$
converges in $\mu$-measure to a limit
function $g$ in
$\mathcal M_\mu$ if
\[ 
\lim_{n\to\infty}\, \mu(\{|f_n-g|\geq \epsilon\}]=0
\] 
hold for every $\epsilon>0$.
When it holds we write
\[ 
f_n\overset\mu\to g\tag{0.9.1}
\]

\medskip



\noindent 
{\bf 0.10 Convergence almost everywhere.}
A sequence of $\mu$-measurable functions
$\{f_\nu\}$ is said to converge $\mu$-almost everywhere to a limit function
$g$ if there exists a null set $F\in\mathcal N_\mu$ such that
every $f_\nu$ is defined in $\Omega\setminus F_\nu$
and one has a pointwise limit:
\[ 
\lim_{\nu\to\infty}\, f_\nu(\omega)=g(\omega)\,\colon\,
\omega\in\Omega\setminus F
\]
\emph{When it holds we write}
\[ 
f_n\overset{a.e}\to g
\]
\medskip


\noindent
{\bf 0.11 Remark.} Almost everywhere convergence means that   pointwise 
convergence holds outside a null set $F$ for $\mu$.
So the limit function $g$ above is only defined in
$\Omega\setminus F$.
But when we regard $\mu$-measurable functions one can ignore  null sets
for $\mu$ and the following hold:

\medskip

\noindent
{\bf {0.12  Proposition.}}
\emph{If $g$ is an almost everywhere limit of a sequence
$\{f_\nu\}$ in $\mathcal M_\nu$ then
$g\in \mathcal M_\mu$.}


\medskip

\noindent
\emph{Proof.}
For a real number $a$ and a positive integer $N$ we put
\[
A_N(a)=
\{w\in \Omega\setminus F\colon \max_{\nu\geq N}\, f_\nu(w)\leq a\}
\]
If $\{g\leq a\}= \{ w\in \Omega\setminus F\,\colon\, g(w)\leq a\}$
it is clear that
\[
A_N(\epsilon)\subset \{g\leq a\}
\]
hold for every $N$.
Conversely, if
$\delta$ is a positive number the pointwise convergence entails that
\[
 \{g\leq a\}\subset
 \bigcup_{n\geq 1}\, A_N(a+\delta)
 \]
 Notice that the sets $A_N(a)$
 increase with $N$
 and let $A^*(a)$ be the union.
 Then (i-ii) entail that the following inclusions hold for
 every positive integer $m$:
 \[
 A^*(a)\subset \{g\leq a\}\subset A^*_N(a+1/m)
\]
This implies that
\[
 \{g\leq a\}=\bigcap_{m\geq 1}\, A^*_N(a+1/m)
\]
and the reader may verify that
the right hand side
is a $\mu$-measurable set.
Hence 
$\{g\leq a\}\in\mathcal {M}_\mu$. In a similar fashion one shows that
$\{g\geq b\}\in\mathcal {M}_\mu$
hold for every real number and
the reader can conclude that $g$ is $\mu$-measurable.




\medskip


\noindent
{\bf{0.13  A warning }}
Convergence  in measure need not imply convergence almost everywhere.
But for suitable 
suitable subsequences one has the following:
\bigskip


\noindent
{\bf 0.14 Proposition.} \emph{Let $\{f_n\}$ be a sequence
of measurable functions which converges in $\mu$-measure to a 
function
$g$. Then there exists a subsequence}
\[
\{g_k=f_{\nu_k}\,\,\colon\, \nu_1<\nu_2<\ldots\}
\quad\&\quad 
\phi_k\overset{a.e}\to  g
\]




\noindent
\emph{Proof.}
Regarding the sequence $\{f_n-g\}$ it suffices to prove the result when
$g=0$.
We first find an integer $\nu_1$ such that
\[
\nu\geq \nu_1	\implies \mu(\{|f_\nu\geq 2^{-1}\}\leq 2^{-1}
\]
Next, we find
$\nu_2>\nu_1$ such that
\[
\nu\geq \nu_2	\implies \mu(\{|f_\nu\geq 2^{-2}\}\leq 2^{-2}
\]
Inductively we get a sequence $\nu_1<\nu_2\ldots$ where
\[
\nu\geq \nu_k	\implies \mu(\{|f_\nu\geq 2^{-k}\}\leq 2^{-k}
\]
Then, the sequence  $\{g_k=f_{\nu_k}\}$ 
converges almost everywhere to the zero function.
To see this we set:
\[
g^*_k=\text{max}_{\nu\geq k}\, |g_\nu|
\]


\noindent
The inductive construction above gives
\[
 \mu(\{g^*_k\geq 2^{-k}\}\leq
\sum_{\nu\geq k}\, 
 \mu(\{|g_\nu|\geq 2^{-k}\}\leq \sum_{\nu\geq k}\, 2^{-\nu}= 2^{-k+1}\tag{i}
 \]
Here $g^*_1\geq g^*_2\geq\ldots$ is a monotone sequence and
(i) shows that 
\[ 
g^*_k\overset{a.e}\to 0
\]
From this it is clear that
$\{g_k\}$ also converges almost everywhere to zero.






\bigskip

\noindent 
{\bf 0.15 Exercise}
Let $\{f_n\}$ be a sequence in $\mathcal M_\mu$
such that
\[
\lim_{n,m}\, \mu(\{|f_n-f_m|\geq|\epsilon\})=0
\]  
hold for each $\epsilon>0$, where $(m,n)$ ted to $\infty$, i.e.
to every $\epsilon>0$ there exists
some integer $N$ such that for every pair $n\geq N$ and $m\geq N$ one has
\[
\mu(\{|f_n-f_m|\geq|\epsilon\})<\epsilon
\] 
When this holds we say that $\{f_n\}$ is a Cauchy-sequence with 
respect to the $\mu$-measure
Prove by a similar method as in Proposition 0.14 that there
exists a subsequence $\{g_k=f_{n_K}\}$
which converges almost everywhere to a limit function
$f_*$. Show also that $f_*$ is unique in $\mathcal M_\mu$
since the almost everywhere convergence of the subsequence entails that 
$f_n\overset\mu\to f_*$.



\bigskip

\centerline{\bf 1. Integrals}


\medskip


\noindent {\bf{1.1 Elementary functions.}}
If $B\in\mathcal B$ we get the characteristic function
$\chi_B$ which is 1 on $B$ and 0 in $\Omega\setminus B$.
An elementary function is a finite linear sum 
\[ 
F=\sum\, a_k\cdot \chi_{B_k}\tag{*}
\] 
where $B_1,\ldots,B_N$ is a finite set of disjoint
sets in $\mathcal B$ whose union is $\Omega$ and
and $a_1,\ldots,a_N$ are real numbers. 
Notice that $F$ is unchanged if we take a refined partition, i.e. if every
$B_k$ is a disjoint union of some $\mathcal B$-sets
$\{C_{k\nu}\}$ then

\[
F=\sum\sum\, a_k\cdot \chi_{C_{k\nu}}
\]
Let $E(\mathcal B)$ denote the family of all elementary functions.
This is  a 
a linear space of functions on $\Omega$, and if 
$F$ and $G$ belong to $E(\mathcal B)$ we can represent both
as in (*) after a common refinement and
the product $G\cdot F$ is the elementary
function defined by
\[
G\cdot F=\sum\, b_k\cdot a_k\cdot \chi_{B_K}
\] 
where $F=a_k$ and $G=b_k$ hold on $B_k$ for every $k$.
Next, let $F$ be a bounded 
$\mathcal B$-measurable function i.e. 
there exists a constant $K$ such that
$-K\leq F(\omega)\leq K$ hold for all $\omega\in\Omega$.
Then $F$ can be \emph{uniformly approximated} by
elementary functions.
Namely, if $N\geq 1$ we set
\[ 
B_N(\nu)=\{ -K+K\cdot \nu\cdot 2^{-N}\leq F<
-K+K\cdot (\nu+1)\cdot 2^{-N}\} \quad\colon\,0\leq \nu\leq 2^{2N}-2
\]
\[
\text{and}\quad  B_N(2^{2N}-1)=\{ K-2^{-N}\leq F\leq K\}
\]
We get the elementary function
\[ 
F_*=\sum_{\nu=0} ^{2^{2N}-1}
\,(-K+\nu\cdot 2^{-2N})\cdot \chi_{B_N(\nu)}
\]
It is clear that 
\[
F_*\leq F\leq F_*+2^{-N}
\]
Since $N$ can be arbitrary large this shows that
$F$ is uniformly
approximated by elementary functions.















\bigskip

\noindent
{\bf{1.2 Integrals of elementary functions.}}
Let $\mu$ be a probability measure.
To each
elementary function
\[
F=\sum\, a_k\cdot \chi_{B_k}
\] 
we assign the $\mu$-integral
\[
 \int\, F\cdot d\mu=\sum\, a_k\cdot \mu(B_k)\tag{1.2.1}
\]
It is clear that (1.2.1 ) yields an additive map from
$E(\mathcal B)$ into the complex number where we regard
complex-valued functions.
The maximum-norm $||F||_\infty$
is the maximum of $\{|a_k|\}$. Since
$\mu$ is a probability measure we get:
\[
\bigl| \int\, F\cdot d\mu\,\bigr|\leq
||F||_\infty\tag{1.2.2}
\]
\medskip


\noindent
{\bf{1.3  Integrals of bounded functions.}}
If $K>0$ is a positive number we denote by
$\mathcal M_\mu(K)$ the class of $\mu$-measurable functions
$f$ such that the absolute value $|f|$ is $\leq K$
almost everywhere. So in the equivalence class we can take $f$ to be
a function in $\mathcal M_\mathcal B$ where
this everywhere defined function has maximum norm 
$K$ at most. By (1.1) 
$f$ can be uniformly approximated
by a sequence $\{F_n\}$ from $E(\mathcal B)$
with maximum norms $\leq K$.
For each pair $n,m$ the triangle inequality gives
\[
\bigl| \int\, F_n\cdot d\mu-
\int\, F_m\cdot d\mu\,\bigr|\leq
\int\,|F_n-F_m|\cdot d\mu\leq
||F_n-F_m||_\infty\tag{1.3.1}
\]
Since $||F_n-f||_\infty\to 0$ it follows that
(1) tends to zero as $n$ and $m$ increase. Hence 
the evaluated integrals $\{\int\, F_n\cdot d\mu\}$ is a 
Cauchy sequence of complex numbers and 
there exists a limit
\[ 
\lim_{n\to\infty}\, \int\, F_n\cdot d\mu\tag{1.3.2}
\]
Moreover, (1.2.1 ) implies  that this limit is intrinsic, i.e. 
independent
of the chosen  sequence $\{F_n\}$ which approximates $f$ uniformly.
The limit (2) is called the $\mu$-integral of $f$ and is denoted by
\[
\int\, f\cdot d\mu\tag{1.3.3}
\]

\medskip

\noindent
{\bf 1.4 Absolutely integrable functions.}
For each  positive real number $K$ we define the 
the  truncation operator $T_K$ from $\mathcal M_\mu$ to 
$\mathcal M_\mu(K)$ by:
\[ 
T_K(f)(x)=f(x)\,\colon\,|f(x)|\leq K\quad\text{and}\quad
 T_K(f)(x)=0\,\colon\,|f(x)|> K
\]

 
\noindent
When $f\in\mathcal M_\mu$ 
we
get bounded functions
$\{T_K(f)\,\colon\, K>0\}$.
We can also take  absolute values and notice that
\[
 K_1<K_2\implies |T_{K_1}(f)|\leq |T_{K_2}(f)|\tag{1}
\]
From (1)  the $\mu$-integrals of the
non-negative functions $\{|T_K(f)|\}$ increase with $K$, i.e. 
\[
 K_1<K_2\implies \int\, |T_{K_1}(f)|\cdot d\mu\leq
\int\, |T_{K_2}(f)|\cdot d\mu\tag{2}
\]


\noindent
We can impose the condition that the non-decreasing sequence 
(2) is bounded. This leads to 
\medskip

\noindent
\noindent 
{\bf 1.5  Definition}.
\emph{A function $f\in\mathcal M_\mu$ is said to be absolutely integrable
if there exists a
constant $C$ such that}
\[
\int\, |T_{K_1}(f)|\cdot d\mu\leq C\quad\text{for all}\quad K>0\tag{*}
\]
\emph{
The class if these functions is denoted
$L^1(\mu)$.}
\bigskip

 

 

\noindent 
{\bf {1.6 Integrals of $L^1(\mu)$-functions.}}
Let $f$ belong to $L^1(\mu)$.
From the construction of the $T$-operators it is clear that
if $K_2>K_1>0$ then
\[
\bigl|\int T_{K_2}(f)\cdot d\mu-
\int T_{K_1}(f)\cdot d\mu\bigr|\leq
\int\, |T_{K_2}(f)|\cdot d\mu-
\int\, |T_{K_1}(f)|\cdot d\mu\tag{i}
\]


\noindent
Since $f\in L^1(\mu)$
the non-decreasing sequence
$\{\int\, |T_{K_2}(f)|\cdot d\mu\}$
is bounded above and therefore convergent. Since a 
convergent sequence also is a Cauchy sequence, it follows from (i) that
\[
\lim_{K_2,K_1}\, 
\int T_{K_2}(f)\cdot d\mu-
\int T_{K_1}(f)\cdot d\mu=0
\] 
as $K_1$ and $K_2$ tend to $+\infty$.
Since  Cauchy sequences of complex numbers converge
there exists a limit
\[ 
\lim_{K\to\infty}\, 
\int T_K(f)\cdot d\mu\tag{*}
\]
This limit is denoted by $\int\, f\cdot d\mu$ and is called the
$\mu$-integral of $f$.


\medskip

\noindent 
{\bf 1.7 Exercise.} Show that the integral on $L^1(d\mu)$ is additive, i.e.
\[
\int f d\mu+
\int g d\mu=
\int (f+g) d\mu\,\quad\colon\quad f,g\in L^1(d\mu)
\]
Hence the $\mu$-integral yields a linear functional on the 
space of absolutely integrable functions.
Show also that if $f\in L^1(\mu)$ then the absolute value $|f|$ 
belongs to $L^1(\mu)$.


\medskip

\noindent
{\bf 1.8 The $L^1$-norm.}
The linear space $L^1(d\mu)$ becomes a normed space when we set
\[ 
||f||_1=\int\,|f[ d\mu\quad\colon\quad
f\in L^1(d\mu
\]



\noindent
{\bf{1.9 Exercise.}}
Show that $E(\mathcal B)$ is a dense subspace of $L^1(\mu)$.
\bigskip


\noindent
{\bf{1.10 Convergence in the $L^1$-norm.}}.
By definition
a sequence $\{f_n\}$ converges in the $L^1$-norm to a limit function
$g$ in $L^1(\mu)$ when
\[
\lim_{n\to\infty}\, ||f_n-g||_1=0\tag {i}
\]
If $\epsilon>0$ we notice that
\[
\mu(\{|f_n-g|\geq\epsilon\}\leq\epsilon^{-1}\cdot ||f_n-g||_1\tag{ii}
\]
Hence (i) implies that
\[
\lim_{n\to\infty}\
\mu(\{|f_n-g|\geq\epsilon\}=0\tag{3}
\]
Here $\epsilon$ is arbitrary small
which  means that $f_n\overset\mu\to g$. Thus
$L^1$-convergence implies convergence in $\mu$-measure.
\medskip


\noindent 
{\bf{1.11  Example.}}
The converse is not true.
For example, let $\mu$ be the Lebesgue measure on $[0,1]$. To each
$n\geq 1$ we define $f_n(x)$ to be $n$ if $0\leq x\leq \frac{1}{n}$ 
and otherwise zero. Then 
\[ 
\int_=^1\, f_n(x)\cdot dx=1
\]
hold for all $n$. At the same time $f_n(x)\to 0$ for every $x>0$, i.e. the sequence converges almost every where to zero and hence also in measure.
But if we restrict the attention to bounded functions  a converse result holds.
\medskip

\noindent
{\bf 1.12  Proposition} 
\emph{Let $K>0$ be fixed. Then a sequence $\{f_\nu\}$
in $\mathcal M_\mu(K)$ converges to a limit function $g$ in the $L^1$-norm
if and only if the sequence  converges in measure to $g$.}

\bigskip


\noindent
\emph{Proof.} Consider a pair $f,g$ in $\mathcal M_\mu(K)$.
If $\epsilon>0$ we get the measurable set
\[ 
E_\epsilon(f,g)=\{ |f-g|\geq\epsilon\}
\]
Since the maximum norm   $||f-g||_\infty\leq 2K$ 
it follows that

\[ 
||f-g||_1=
\int_{E_\epsilon(f,g)}\,|f-g|d\mu+
\int_{\Omega\setminus E_\epsilon(f,g)}\,|f-g|d\mu\leq 2K\cdot \mu(E_\epsilon(f,g))\tag{i}
+\epsilon
\]
\medskip

\noindent
If  $f_\nu\overset\mu\to g$
where $\{f_\nu\}$ in $\mathcal M_\mu(K)$ one has 
\[
\lim_{\nu\to\infty}\, \mu(E_\epsilon(f_\nu,g))=0\quad\text{hold for each}\quad
\epsilon>0\tag{ii}
\] 
Hence (i) implies that
$||f_n-g||_1||_1\to 0$.
Since we already proved that $L^1$-convergence entails convergence in measure we get
the equivalence assertion in
Proposition 1.12 follows.



\bigskip

\centerline {\bf 1.13 Dominated convergence theorem}
\medskip

\noindent 
Let 
$\{f_n\}$ be a  sequence in $L^1(\mu)$
which converges in $\mu$-measure
to a limit function
$g$. The example in 1.11  shows that
convergence need not hold
in the $L^1$-norm.
 To compensate for this we impose a certain bound so that the situation
is essentially the same as in 
Proposition 1.12
\medskip

\noindent 
{\bf 1.14 Theorem}
\emph{Let $\{f_n\}$ be a sequence in $L^1(\mu)$ where
$f_n\overset\mu\to g$ holds. Assume in addition that there exists
a non-negative $\phi\in L^1(\mu)$ such that}
\[
|f_n|\leq \phi\tag{1}
\] 
\emph{hold almost everywhere for each $n$.
Then the limit function $g$ belongs to $L^1(\mu)$ and}
\[ 
\lim_{\nu\to\infty}\,||f_n-g||_1=0\tag{2}
\] 
\bigskip

\noindent {\bf{1.15  Exercise}} Prove Theorem 1.14.
The hint is to apply  truncation operators to $\phi$
so that the $L^1$-norm of $\phi-T_K(\phi)$ are small and then
use Theorem 1.13.

\bigskip

\noindent
{\bf{1.16  Remark.}}
Recall that almost everywhere convergence implies convergence in measure.
So if $\{f_n\}$ is some $L^1(\mu)$-sequence 
which converges almost everywhere to
a function $g$ and 
a dominating $\phi$-function exists as above, then
$||f_n-g||_1\to 0$.


\bigskip

\centerline
{\bf{2.  A completeness theorem.}}
\medskip


\noindent
Let $\{f_n\}$ be  Cauchy sequence in the $L^1$-norm, i.e. 
\[
\lim_{n,m\to\infty}\,\int\,|f_n-f_m|\cdot d\mu=0\tag{*}
\]
\medskip


\noindent
{\bf{2.1 Theorem}}
\emph{When (*) holds there exists   a unique  $L^1$-function $f_*$
such that}
\[
\lim_{n,m\to\infty}\,\int\,|f_n-f_*|\cdot d\mu=0
\]
\emph{Hence  the normed space
$L^1(\mu)$ is complete, i.e. it is a Banach space.}
\medskip

\noindent
\emph{Proof.}
From (*) it follows that there exists a subsequence
$\{n_k\}$ such that if $g_k=f_{n_k}$
then
\[
||g_{k+1}-g_k||_1\leq 2^{-k}\tag{i}
\]
Since $\sum\, 2^{-k}<\infty$
the non-negative function
\[ 
G=|g_1|+\sum_{k=1}^\infty\, |g_{k+1}-g_k|
\]
is integrable.
It is clear that 
\[
|g_k|\leq G\quad\colon k=1,2,\ldots\tag{ii}
\]
Together with (i) this entails that
$\{g_k\}$ is a Cauchy sequence and Exercise 0.15 gives
 a  function $g$ where
 \[
 g_k\overset{\mu}\to g
 \]
 Next,  
(ii) enable us to apply Theorem 1.14 which gives
\[
||g_k-g||_1\to 0
\]
Above $\{g_k\}$ is a subsequence
of $\{f_n\}$ and the triangle inequality
shows that
$||f_n-g||_1\to 0$ which shows that $g$ is the 
requested limit in $L^1(\mu)$ of the given Cauchy-sequence $\{f_n\}$.
\medskip

\noindent
{\bf{2.2 The space $L^2(\mu)$.}}
On elementary functions we can introduce 
the $L^2$-norm, i.e.
set
\[
||f||_2=\sqrt{\, |f|^2\cdot d\mu}
\]
Passing to the closure
of elementary
functions this yields a normed
linear space denoted by $L^2(\mu)$ which
again is complete and therefore becomes a Hilbert space.
The details are left to the reader.










\newpage






\centerline{\bf 3. Signed measures and the  Radon-Nikodym  theorem.}

\bigskip

\noindent
Let $(\Omega,\mathcal B)$ be a sample space.
Consider an additive real-valued map $\mu\colon\mathcal B\to
\bf R$ which may take negative values and for which 
there exists a constant $C$ such that
\[
 -C\leq\mu(A)\leq C\quad\colon\,\quad A\in \mathcal B\tag{*}
\]
\medskip

\noindent
This uniform bound and additivity  imply
that
if $\{A_\nu\}$ is a sequence of disjoint sets in $\mathcal B$ then
\[
\sum\, |\mu(A_\nu)|< 2C
\]
Hence the series $\sum\,\mu(A_\nu)$ is absolutely convergent.
We say that $\mu$ is $\sigma$-additive if
\[ 
\sum\, \mu(A_\nu)=\mu(\cup\,A_\nu)
\]
hold for every sequence of disjoint sets in $\mathcal B$ and  refer to $\mu$
as a  \emph{signed} measure. From now on all measures are $\sigma$-additive and
bounded, i.e. (*)  holds for some constant $C=C_\mu$.
If $\mu(A)\geq 0$ for all $A\in\mathcal B$ we say that
$\mu$ is a positive measure.
\medskip

\noindent {\bf 3.1 Definition}
\emph{Two positive measures $\mu$ and $\nu$
are mutually singular if there exist nullsets  $A\in\mathcal N_\mu$
and $B\in\mathcal N_\nu$ such that}
\[
\mu(B)=\mu(\Omega)\quad\colon\quad \nu(A)=\nu(\Omega)
\] 
\emph{When this holds we write $\mu\perp\nu$.}




\bigskip

\noindent
{\bf 3.2 Hahn's Theorem}
\emph{Every  signed measure $\mu$ has a unique decomposition}
\[
\mu=\mu_+-\mu_-\quad\text{where}\,\quad
\mu_,\mu_-\,\,\text{
are both  positive and}\,\ \mu_+\perp\mu_-
\]
\medskip

\noindent \emph{Proof.}
$A\in\mathcal B$ is called a $\mu$-positive set  if
\[
E\subset A\quad\text{and}\quad E\in\mathcal B \implies \mu(E)\geq 0\tag{i}
\]

\noindent
Denote this class by $P_+(\mu)$.
Obviously the union of two $\mu$-positive sets is again $\mu$-positive and by
$\sigma$-additivity there exists a $A^*\in P_+(\mu)$ such that
\[
\mu(A^*)=\max_{A\in P_+(\mu)}\,\mu(A)\tag{ii}
\]


\noindent
\emph{Sublemma.} One has  $\mu(B)\leq 0$ for each $B\subset\Omega\setminus A^*$.
\medskip

\noindent
\emph{Proof of Sublemma.} 
We argue by contradiction.
Suppose there is  some $B_0\subset\Omega\setminus A^*$ with 
$\mu(B_0)=\delta>0$.
The maximality of $\mu(A^*)$ implies that $B_0$ does not belong to
$P_+(\mu)$ which gives
some $\delta_1>0$ such that
\[ 
-\delta_1=\min_{E\subset B_0}\,\mu(E)\tag{i}
\] 
Choose $E_1\subset B_0$ with $\mu(E_1)\leq -\delta_1/2$ and set $B_1=B\setminus E_1$.
Now $\mu(B_1)\geq \delta+\delta_1/2$ and 
exactly as above
we get a negative number
\[
-\delta_2=
\min_{E\subset B_1}\,\mu(E)
\]
Choose $E_2\subset B_1$ with $\mu(E_2)\leq-\delta_2/2$.
Inductively we get a decreasing sequence of
sets
\[ 
B_\nu=B_0\setminus (E_1\cup\ldots\cup E_\nu)
\]
where $\{E_\nu\}$ are disjoint. Moreover, we have
a sequence $\{\delta_\nu\}$ of positive numbers where
\[
-\delta_\nu=
\min_{E\subset B_\nu}\,\mu(E)\quad\text{and}\quad \mu(E_{\nu+1})\leq
-\delta_\nu/2\tag{ii}
\]
Since $\mu$ is a signed measure there is  a constant $A$
such that 
\[
\mu(E_1)+\ldots+\mu(E_N)\geq -A\quad\text{for all}\quad N\geq 1\tag{iii}
\]
It follows that
\[ 
\delta_1+\ldots+\delta_N\leq 2A\quad\text{for all}\quad N\geq 1\tag{iv}
\]
Hence the positive series
$\sum\,\delta_\nu$ is convergent which gives
$\delta_\nu\to 0$ as $\nu\to+\infty$.
Put
\[
B_*=\cap \, B_\nu\tag{v}
\]
For each $\nu\geq 1$ the inclusion $B_*\subset B_N$ 
and the definition of $\delta_\nu$ from (ii)  give:
\[ 
\min_{E\subset B_*}\, \mu(E)\geq -\delta_\nu\tag{vi}
\]
This hold for every $\nu$ and since $\delta_\nu\to 0$
the minimum in (vi) is 
$\geq 0$ which means that $B_*$ belongs to 
$P_+(\mu)$.
At the same time the construction above gives

\[ 
\mu(B_\nu\geq \delta_0+\frac{1}{2}(\delta_1+\ldots+\delta_\nu)\geq \delta_0\tag{vii}
\]
for every $\nu$. By $\sigma$-additivity we have

\[ 
\mu(B_*)=\lim_{\nu\to\infty}\,\mu(B_\nu)
\] 
and then
(vii) entails that $\mu(B_*)>0$.
This contradicts the  (1) since $A^*$ and $B_*$ are disjoint
and the Sublemma is proved.









\bigskip
 
{\emph{Final part of the proof }}. 
The Sublemma gives  positive measures
$\mu_+$ and $\mu_-$ defined 
 by
 \[ 
 \mu_+(E)=\mu(E\cap A^*)\quad\colon\quad
 \mu_-(E)=-\mu(E\cap(\Omega\setminus A^*)
\]
We see that
$\mu_+\perp\mu_-$ and $\mu=\mu_+-\mu_-$.
This proves the existence of at least one
Hahn-decompostion.
The proof of  \emph{uniqueness} of such a 
decomposition
is left to the reader. 


\bigskip

\centerline {\bf 3.3 Radon-Nikodym derivatives.} 
\bigskip

\noindent
Let $\mu$ be a positive measure and consider
a
non-negative function $f\in L^1(d\mu)$.
This gives a  positive measure defined
by the $\sigma$-additive map

\[
E\mapsto 
\int_E\, f\cdot d\mu\quad\colon\, E\in\mathcal B
\]
Denote this positive measure by $f\cdot \mu$.
If $E\in\mathcal N_\mu$  the construction of $\mu$-integrals implies that
$\int_E\, f\cdot d\mu=0$. Hence  one has the inclusion
\[ 
\mathcal N_\mu\subset
\mathcal N_{f\cdot \mu}\tag{3.1}
\]
In general, a positive measure $\nu$ is called \emph{absolutely continuous} with respect
to $\mu$ if 
\[
\mathcal N_\mu\subset
\mathcal N_\nu
\]
It turns out that such positive measures are
of the form $f\cdot\mu$ with $f\in L^1(\mu)$.

\bigskip

\noindent
{\bf 3.4 Theorem.}
\emph{Let $\mu$ be a  positive measure. Then every positive measure
$\nu$ which is absolutely continuous with respect to
$\mu$ is of the form
$f\cdot \mu$ for a unique non-negative function
$f\in L^1(d\mu)$.}
\bigskip


\noindent
\emph{Proof.} 
For each pair $(k,N)$ where  $N$ is a positive integer and $k$
a non-negative integer
we consider the following two signed measures

\[
\nu-k2^{-N}\cdot \mu\quad\text{and}\quad
(k+1)2^{-N}\cdot \mu-\nu\tag{i}
\]
The Hahn decomposition applied to
$\nu-k2^{-N}\cdot \mu$ gives a maximal set
\[
S_N(k)\in P_+( \nu-k2^{-N}\cdot \mu)\tag{ii}
\]
and similarly we find a maximal set
\[
T_N(k)\in P_+((k+1)2^{-N}\cdot \mu-\nu)\tag{iii}
\]


\medskip

\noindent
If $N$ is fixed 
the measure 
$ (\nu-k2^{-N})-(\nu-(k+1)2^{-N})= 2^{-N}\cdot \mu\geq 0$. This implies that

\[ 
S_N(k+1)\subset S_N(k)\quad\text{for all}\quad k=0,1,\ldots\tag{iv}
\]

\noindent
Moreover, since
$\nu$ is absolutely continuous with respect to $\mu$ it is clear that:
\[
\cap_{k\geq 1}\, S_N(k)=\emptyset\tag{v}
\]
Finally the reader may observe that
\[
S_N(k)\setminus S_N(k+1)= S_N(k)\cap\, T_N(k)\tag{vi}
\]


\noindent
Let us put
\[
W_N(k)= S_N(k)\cap\, T_N(k)\tag{vii}
\]
From (vi) it follows that 
$\{W_N(k)\}$ is a family of disjoint subsets of $\Omega$ and we
notice  that

\[
k2^{-N}\mu(E)\leq \nu(E)\leq (k+1)2^{-N}\mu(E)\quad\colon\,
E\subset W_N(k)\tag{viii}
\]
The reader may also verify the set-theoretic equality
\[
 W_N(k)=W_{N+1}(2k)\cup W_{N+1}(2k+1)\tag{ix}
 \]
for all pairs $k$ and $N$,
Next we construct a sequence of functions by:
\[ 
f_N=\sum_{k=1}^\infty\, k2^{-N}\cdot \chi_{W_N(k)}\quad\colon\, N=1,2\ldots \tag{x}
\]
Using (ix) the reader may verify that
$\{f_N\}$ increase with $N$ and (viii) entails that
\[ 
\int_E\, f_N\cdot d\mu\leq \nu(E)\leq
\int_E\, f_N\cdot d\mu+2^{-N}\cdot \mu(E)
\quad\colon\,
E\in\mathcal B
\tag{xi}
\]
\medskip


\noindent
Now $\{f_N\}$ is a non-decreasing sequence and
there exists
a limit function
\[ 
f_*=\text{lim}_{N\to\infty} f_N
\] 
where the convergence holds almost everywhere and it is celar that
(xi) implies that

\[
\nu(E)=\lim_{N\to\infty}\int_E\, f_n\cdot d\mu=\int _E\, f_*\cdot d\mu
\quad\colon\,
E\in\mathcal B
\]
This gives $\nu= f_*\cdot d\mu$
and Theorem 3.3, is proved.
\bigskip


\centerline {\bf{3.4 A general decomposition.}}
\bigskip

\noindent
Let $\mu$ be a positive measure.
For any other positive measure
$\nu$
there exists a unique
decomposition of $\nu$ into a sum of one measure which is singular with
respect to $\mu$, while the other term is given by an
$L^1(d\mu)$-function. More precisely one has:
\medskip

\noindent  
{\bf 3.5 Theorem} \emph{Given a positive measure $\mu$ every other
positive measure $\nu$ is of the form}
\[ 
\nu=\nu_s+fd\mu\quad\colon\quad \nu_s\perp\mu\quad\text{and}\quad 
f\in L^1(d\mu)
\]
\bigskip

\noindent 
\emph{Proof}
To find the singular part $\nu_s$ we put
\[
M=\max\,\nu(A)\quad\colon\quad A\in\mathcal N_\mu\tag{1}
\]


\noindent
By  $\sigma$-additivity there exists some   $A_*\in\mathcal N_\mu$ such that
$\nu(A_*)=M$.
Define the measure $\nu_*$ by:
\[ 
\nu_*(E)=\nu(A_*\cap\,E)\tag{2}
\]
Here  $\nu_*\perp\mu$.
Put $\gamma=\nu-\nu_\ast$. The construction of $\nu_*$ gives 
\[ 
A\in\mathcal N_\mu\implies \gamma(A)=0\tag{3}
\]
Then Theorem 3.5 gives $\gamma=f\cdot \mu$
for some
$f\in L^1(\mu)$ and Theorem 3.5 follows.
\bigskip



\centerline {\bf{3.6 The Vitali-Hahn-Saks theorem.}}
\bigskip

\noindent
Let $\Omega,\mathcal B)$ be a probability space
and $\mu$  a probability measuremwhich gives 
the $\sigma$-algebra 
$\mathcal N(\mu)$  of null-sets.
A pair of $\mu$-measurable sets are identified when
their Boolean difference is a null-set.
If $A\in\mathcal B$
then $A_*$ denotes its equivalence class.
Let $X$ denote the space whole points are such
equivalence classes of subdsets from $\mathcal  B$.
A metric is defined on $X$
by
\[
d(A_*,B_*)=\mu(A\setminus B)+ \mu(B\setminus A)
\]
\medskip

\noindent
{\bf{3.6.1 Exercise.}}
Show that $X$ is a complete metric space. 
\medskip

\noindent
Next, an additive real-valued function $\lambda$
defined on
$\mathcal B$ is called $\mu$-continuous if
\[
\lim_{\mu(A)\to 0}\,\lambda(A)=0
\]
\medskip

\noindent
{\bf{3.6.2 Theorem.}}
\emph{Let $\{\lambda_n\}$ be a sequece of
additive $\mu$-continuus functions such that}
\[ 
\lim_{n\to\infty}\,\lambda_n(A)\tag{*}
\] 
\emph{exist for every $A\in\mathcal B$.
Then, for each $\epsilon>0$ there exists $\delta$ such that}
\[
\mu(A)\leq \delta\implies
\max_n\, |\lambda_n(A)|\leq \epsilon\tag{*}
\]
\medskip

\noindent
\emph{Proof.}
For each $\epsilon>0$
and every pair of integers $n,m$ we get the  closed sets in $X$:
\[
\Sigma_{n,m}=\{A\in\mathcal B\,\colon\, 
|\lambda_n(A)-\lambda_m(A)|\leq\epsilon/2\}
\]
Set
\[
 \Sigma_p^*=\bigcap_{n,m\geq p}\Sigma_{n,m}
\]
Then (*) entails that
$\cup\, \Sigma^*_p=X$. Exercise 3.6.1 and 
Baire's  category theorem gives some  $p$ and
$\delta>0$ such that
\[
\mu(A)<\delta\implies A\in \Sigma_p^*
\]
Shrinking $\delta$ if necessary 
\[
\mu(A)<\delta\implies \max_{n \leq p_*}\lambda_n(A)\leq\epsilon/2
\]
Now the reader can check that (*) holds. 
\medskip

\noindent
{\bf{3.6.3 Exercise.}}
Show that if $\lambda_*(A)$ is  the limit value in
the theorem for each $A$, then
$\lambda_*$ is additive and $\mu$-continuous.














\newpage



\centerline{\bf\large III. Lebesgue Theory}
\bigskip


\centerline{\emph{Contents}}

\bigskip



\noindent
0.  Introduction
\medskip

\noindent
1. Dyadic grids and Lebesgue points
\medskip

\noindent
2. Measurable sets

\medskip

\noindent
3. Measurable functions and their integrals

 \medskip

\noindent
4. Fubini's theorem

\bigskip








\centerline {\bf{Introduction.}}

\medskip


\noindent
In the euclidian
space
${\bf{R}}^n$
it is natural to define the $n$-dimensional volume of a cube whose sides
have length $a$ to be $a^n$.
After this one
expects that it is possible to associate a non-negative number
to every bounded open set and  construct an
additive measure which enjoys an invariance property, i.e.
the $n$-dimensional measure of a bounded open set $\Omega$
should be  the same after a translation and also under a rotation expressed by
an orthogonal linear map.
It turns out that this can be achieved in a unique way.
But after one is confronted with a problem, i.e. how to extend the
construction of $n$-dimensional volumes to a larger family than
bounded open sets.
More generally, one would like to find a Boolean $\sigma$-algebra of subsets of
${\bf{R}}^n$ which contain all bounded open sets  on which
there exists a $\sigma$-additive measure which may 
assign  infinite volumes to "large unbounded sets".
\medskip

\noindent
The  solution to all this was achieved by Henri Lebesgue. 
His famous book
[Leb] from 1904    has
found a wide range of applications and we shall
expose the main results in  Lebesgue's  theory.
From the abstract measure theory from Section II one can 
quickly attain the requested properties of the Lebesgue measure and after
define the class of Lebesgue measurable functions and construct  their integrals.
However, the geometric picture is lost if one
proceeds directly via the  abstract notions.
Instead we  describe 
an effective procedure to construct
the $n$-dimensional Lebesgue measure of a bounded open set
$\Omega$ which will be denoted by $\text{vol}_n(\Omega)$.
The trick is to employ \emph{dyadic grids}.
To each positive integer $N$ one has the family 
$\mathcal D_N$ of open cubes whose sides have length
$2^{-N}$ and the corner points belong to the lattice
$2^{-N}\cdot {\bf{Z}}^n$.
In  ¤1 we explain how dyadic grids enable us to
construct $\text{vol}_n(F)$ where $F$ is a bounded open set or a compact set.
After one defines the \emph{inner} 
respectively the \emph{outer} measure of an arbitrary
subset $E$ as follows:

\[
\text{inner measure}(E)= \max_{K\subset E}\,\text{vol}_n(K)\tag{1}
\]
where the maximum is taken over compact subsets of $E$. Next
\[
\text{outer measure}(E)= \min_{E\subset \Omega}\,\text{vol}_n(\Omega)\tag{2}
\] 
where the minimum is taken over open sets which contain $E$.
If (1) and  (2) are equal  one says that $E$ is measurable in the sense of
Lebesgue and the common number is its measure. It may occur that
the common number is $+\infty$. But if $E$ is relatively compact then
its measure is always finite.
The class of all  measurable subsets of
${\bf{R}}^n$ is denoted by $\mathcal L({\bf{R}}^n)$.
It contain a subclass called \emph{null sets}, where  a set $E$ is 
called a null-set if its outer
measure is zero.
The family of null sets is denoted by $\mathcal N({\bf{R}}^n)$.
One says that two measurable sets $E$ and $F$ are equivalent if their Boolean difference
\[
(E\setminus F)\cup (F\setminus E)\in \mathcal N({\bf{R}}^n)\tag{3}
\]
\newpage


\noindent{\bf{0.1 Lebesgue points.}}
Let $E$ be measurable where 
$\text{vol}_n(E)>0$.
To each point $x_0\in  E$
we denote by
$\mathcal{S}_\delta(x_0)$ the family of all open cubes
$\square$ whose sides have length $\leq \delta$ and contain $x_0$.
Here  is not required that $x_0$ is the center of the cube
or that the sides are parallell to the coordinate axis.
Following Lebesgue we set
\[
\lambda ^E_\delta(x_0)=\min_{\square\in\mathcal{S}_\delta(x_0)}
\, \frac{\text{vol}_n(E\cap\square)}{\text{vol}_n(\square)}\tag{*}
\]
Since the cube-family $\{\mathcal S_\delta(x_0)\}$
decreases as $\delta\to 0$,  
$\delta\mapsto \lambda^E_\delta(x_0)$
increases as $\delta$ shrinks to zero and we obtain a limit
\[
\lambda^E(x_0)= \lim_{\delta\to 0}\, \lambda^E_\delta(x_0)\tag{**}
\]
It is clear  that this $\lambda$-number is between 0 and 1.
The set of Lebesgue points is defined by
\[
\mathcal L(E)= \{ x\in E\quad\colon\, \lambda^E(x)=1\}\tag{***}
\]
It turns out that
\[
(E\setminus \mathcal L(E))
\in\mathcal N({\bf{R}}^n)\tag{****}
\]
\medskip

\noindent
{\bf{0.2 Absence of phantoms.}}
Let us remark that (****) already  is non-trivial when
$F$ is  a closed set, i.e. here  (****) gives
the null-set
$F\setminus\mathcal L(F)$ which 
from a measure theoretic 
point means that $F$ is like an open
set   around almost
every point.
Next, let
$\Omega$ be a bounded open  set and apply (****) to its compact boundary
which gives a null-set $S$ of $\partial\Omega$ such that

\[
\lim_{\delta\to 0}\, \sup_{\square\in S_\delta(x)}
\, \frac{\text{vol}_n(\Omega\cap\square)}{\text{vol}_n(\square)}=0
\]
hold when $x\in\partial\Omega\setminus S$.
This means that
$\Omega$ is thin  around
almost every 
boundary point. 

\bigskip


\noindent
{\bf{0.3 Lebesgue measurable functions}}.
A real-valued function
$f(x)$ is measurable in the sense of Lebesgue if
the inverse image sets $f^{-1}(-\infty,a)$ and
$f^{-1}(-\infty,a]$ are measurable for every real number $a$.
Functions whose absolute values attain 
large values too often
are not so interesting, i.e. one studies 
foremost measurable functions which  are
locally integrable.
In ¤ XX we construct the Lebesgue integral which gives
the space $L^1_{\text{loc}}({\bf{R}}^n)$.
Using (****) we shall prove that a function
$f\in L^1_{\text{loc}}({\bf{R}}^n$ has almost everywhere a
Lebesgue value defined as
\[
 \mathcal L_f(x)=\lim\,
 \frac{1}{\text{vol}_n(\square)}
 \cdot\int_\square\, f(x)\cdot dx
 \]
where the limit is taken over open cubes $\square$ which contain $x$ and
 their volumes tend to zero.
Moreover, the limit value is equal to $f(x)$ almost everywhere.
Thanks to this the notion of measurable $L^1$\vvv functions
becomes   transparent.
Namely, 
when 
 $f\in L^1_{\text{loc}}({\bf{R}}^n)$ and  $\delta>0$ and set:
 \[ 
F_\delta(x)= \frac{1}{\delta^n}\cdot
 \int_{\square_\delta(x)}\, f(\xi)\cdot d\xi
\] 
where
$\square_\delta(x)$ is the  cube centered at $x$ and with sides of length $\delta$.
Lebegue's theorem implies that 
one has a pointwise convergence
\[
\lim_{\delta \to 0}
F_\delta(x)= f(x)
\]
at every Lebesgue point of $f$.
Identifying measurable functions which 
are equal almost everywhere
we can  agree that
every $L^1_{\text{loc}}$-function is equal to
its associated Lebesgue function
$\mathcal L_f$, i.e one ignores  "silly values".
Concerning the $F_\delta$-functions they are 
continuous functions.
So outside a null set a given
$L^1_{\text{loc}}$-function is the pointwise limit 
of a sequence of continuous functions.
\bigskip

\centerline{\bf{1. Dyadic grids and Lebesgue points.}}




\medskip


\noindent
If $N $ is a positive integer we obtain a family of pairwise disjoint open
cubes of the form

\[ 
\square(\nu_\bullet)=\{(x_1,\ldots,x_n)\,\colon\,
\nu_k2^{-N}< x_\nu<(\nu_k+1)2^{-N}\,\colon\, 1\leq  k\leq n\}
\]
where $\nu_\bullet=(\nu_1,\ldots,\nu_n)$
runs over all $n$-tuples of integers.
This family of cubes is denoted by $\mathcal D_N$.
Notice that each $\square\in\mathcal D_N$ contains $2^n$ many cubes in 
$\mathcal D_{N+1}$.
\medskip

\noindent {\bf 1.1 Dyadic exhaustion of open sets.}
Let $\Omega$ be a bounded open set. To each $N\geq 1$
we get the family
$\mathcal D_N(\Omega)$ of  cubes from
$\mathcal D_N$ which are contained in $\Omega$.
Let $\rho_N(\Omega)$ be the number of such cubes.
The volume of the union becomes
\[ 
w_N(\Omega)= 2^{-nN}\cdot \rho_N(\Omega)
\]
If 
$\square\in \mathcal D_N(\Omega)$, then the $2^n$ many
dyadic cubes from $\mathcal D_{N+1}$ which are contained in
$\square$ all belong to $\mathcal D_{N+1}(\Omega)$.
It follows that
\[
\rho_{N+1}(\Omega)\geq 2^n\cdot \rho_N(\Omega)
\]
From this we conclude that
$w_N(\Omega)\leq w_{N+1}(\Omega)$.
Hence $\{w_N(\Omega)\}$ is increasing.
Since $\Omega$ is bounded this sequence is bounded above. For example, if
$\Omega$ is contained in the unit cube
$\{ 0\leq x_\nu\leq 1\}$ then $w_N(\Omega)\leq 1$ for every $N$.
Since every non-decreasing sequence 
of non-negative real numbers which is bounded above
has a limit we obtain the number
\[
\text{vol}_n(\Omega)=\lim_{N\to\infty}\, w_N(\Omega)\tag{*}
\]

\medskip

\noindent
The limit number  is called
the $n$-dimensional Lebesgue measure of the bounded open set.
\medskip

\noindent
{\bf 1.2 The unique dyadic exhaustion.}
Let $\Omega$ be a bounded open set.
We first seek cubes in $\mathcal D_1(\Omega)$.
It may be empty but is otherwise a finite set of unit cubes.
Then we consider the cubes in
$\mathcal D_2(\Omega$ which are not contained in those from
$\mathcal D_1(\Omega)$. We continue in this way, i.e. if $k\geq 3$
we take only those cubes in $\mathcal D_k(\Omega$
which are outside the union of all cubes from
$\mathcal D_1(\Omega),\ldots,\mathcal D_{k-1}(\Omega)$.
Let us denote this family by $\mathcal D_k^*(\Omega)$.
In this way we obtain a \emph{uniquely determined}
sequence $\{\mathcal D^*_k(\Omega)\}$ where
each non-empty
family $\mathcal D^*_k(\Omega)$
is a finite subfamily of $\mathcal D_k$.
Let $\rho_k^*(\Omega)$
be the number of cubes in
$\mathcal D^*_k(\Omega)$.
By this construction it is clear that


\[ 
\Omega_N(\Omega)= \sum_{k=0}^{k=N}\, 2^{-nk}\cdot \rho_k^*(\Omega)
\]
hold for every $N$. Passing to the limit we obtain

\[ 
\text{vol}_n(\Omega)=\sum_{k=0}^\infty\, 
2^{-nk}\cdot \rho_k^*(\Omega)
\]




\medskip

\noindent
{\bf 1.3 Remark.}
If $\square$ is an arbitrary cube whose sides are parallell to the coordinate
axis and of common length $a$ then
its Lebesgue measure is $a^n$.
This equality is clear from the construction above if
$2^N\cdot a$ is an integer for some
$N$ and the corner points belong to the lattice
$2^{_N}\cdot {\bf{Z}}^n$.
The fact that $\text{vol}_n(\Omega)= a^n$
for an arbitrary cube follows when
the real number $a$ is approximated by
"dyadic integers" , i.e. for every $N\geq 1$ we find
an integer $q_N$so that
$q_N2^{_N}\leq a<(q_N+1)2^{-N}$
and in a similar fashion we perform small translations of the corner points.
Next, we may also consider open cubes whose sides are not parallel to
the coordinate axis. Then we still have 
$\text{vol}_n(\Omega)=a^n$ where $a$ is the common length of the sides.
To prove this one studies a general \emph{linear transformation} on
${\bf{R}}^n$.
Thus, let $A$ be a real $n\times n$-matrix whose determinant is $\neq 0$.
By $x\mapsto y=A(x)$ we get a bijective map from
${\bf{R}}^n$ onto itself. Then one has the equality
\[ 
\text{vol}_n(A(\Omega))=
\bigl|\text{det}(A)\bigr |\cdot
\text{vol}_n(\Omega)\tag{*}
\] 
for every bounded open set $\Omega$.
\medskip

\noindent
{\bf {Exercise}}. Prove (*). The hint is that
we first have the equality in the special case when
the $A$-matrix permutes the
coordinates, i.e. when
\[
A(x_1,\ldots,x_n)= (x_{\sigma(1)},\ldots,x_{\sigma(n)})
\]
where $i\to \sigma(i)$ is a permutation.
In addition to such linear maps we recall from Linear Algebra that
every matrix with a non-zero determinant is the product of
such permuting matrices and special matrices of the form
\[
A(x_1,\ldots,x_n)=(y_1,x_2,\ldots,x_n)
\]
\[
\quad\text{where}\quad y_1=a_1x_1+a_2x_2+\ldots+a_nx_n
\quad\text{and}\quad a_1\neq 0
\]
The proof that (*) holds for such linear transforms is left as an exercise.
\bigskip

\noindent{\bf 1.4 Additivity.}
Let
$\Omega_1,\ldots,\Omega_k$ be finite  family of disjoint and bounded
open sets.
Since every open cube
$\square$ is connected
an inclusion
$\square\subset\Omega_1\cup\ldots\cup \Omega_k$ implies that
$\square$ is contained in one of the cubes. From this we conclude that
\[
\rho_N(\Omega_1\cup\ldots\cup \Omega_2)=
\rho_N(\Omega_1)+\ldots+
\rho_N(\Omega_k)
\]
hold for each $N$. Passing to the limit
we get:


\[
\text{vol}_n(\cup\,\Omega_\nu)=
\sum_{\nu=1}^{\nu=k}\, \text{vol}_n(\Omega_\nu)
\]

\medskip

\noindent
More generally, let
$\{\Omega_\nu\}$ be a denumerable sequence of pairwise disjoint open sets
such that
the union is contained in a bounded set. Then we get convergent positive series and
the reader can verify that
\[
\text{vol}_n(\cup\,\Omega_\nu)=
\sum_{\nu=1}^\infty\, \text{vol}_n(\Omega_\nu)
\]
\medskip

\noindent
Thus, the volume is $\sigma$-additive on bounded open sets.

\medskip

\noindent
{\bf{1.5 Interior approximation.}}
Let $\Omega$ be a bounded open set. For each $N$ we may also consider the
family
$\mathcal D^*_N$ of \emph{closed} dyadic cubes.
Let $\bar\rho_N(\Omega)$ be the number of closed cubes
from $\mathcal D^*_N$ which 
are contained in $\Omega$.
Notice that every such closed cube appears as a \emph{compact}
subset of $\Omega$
and hence the finite union of these cubes is again  compact subset of
$\Omega$.
It is clear that the function
\[
N\mapsto 2^{-nN}\cdot \bar\rho_N(\Omega)
\]
is increasing. So the limit exists and we have

\[
\lim_{N\to\infty}\, 2^{-nN}\cdot\bar\rho_N(\Omega)\leq
\text{vol}_n(\Omega)\tag{1}
\]
It turns out that (1) is an equality.
To  prove this we notice that if $\square\in\mathcal D_N$ and $k$ is another large
positive integer, then almost every
small cube from $\mathcal D_{N+k}$ which is contained in $\square$ 
has is closure contained in
$\square$.
More precisely, the reader may verify that if $\Omega$ is a bounded open set
then the inequality below holds for
for every pair of positive numbers $N$ and $k$:


\[ 
\bar\rho_{N+k}(\Omega)\geq
2^{nk}\cdot\rho_N(\Omega)-2n\cdot 2^{(n-1)k}\cdot\rho_N(\Omega)
=2^{nk}\rho_N(\Omega)\cdot(1-2n\cdot 2^{-k})\tag{i}
\]


\noindent
The point is that we can choose large $k$-numbers at the same time let $N\to\infty$.
Namely, for each $\epsilon>0$ we first  choose $k$
such that $2n\cdot 2^{-k}<\epsilon$. Then (i)
and a passage to the limit obviously give:

\[
\lim_{N\to\infty}\, 2^{-nN}\cdot\bar\rho_N(\Omega)\geq
(1-\epsilon)\cdot \text{vol}_n(\Omega)
\]
Since $\epsilon$ is arbitrary we get equality in (1).
\medskip

\noindent
{\bf{1.6 The measure of compact sets.}}
Let $E$ be a compact subset of ${\bf{R}}^n$.
For each $N$  we denote by $\rho^*_N(E)$ the number of  cubes
$\square\in\mathcal D_N$ such that the closure $\bar\square$ 
has a non-empty intersection with
$E$.
Next, let $\Omega$ be some  bounded open set which contains
$E$.
If $\square\in\mathcal D_N$ and $\bar\square\subset\Omega$
then we either have that 
$\bar\square\cap E\neq\emptyset$ or 
$\bar\square\subset\Omega\setminus E$. This gives
the equality:

\[ 
\bar\rho_N(\Omega)= \bar\rho_N(\Omega\setminus E)+\rho_N^*(E)
\]
Passing to the limit where we apply the interior approximation from
1.5 to the open sets $\Omega$ and $\Omega\setminus E$, it follows that

\[
\lim_{N\to\infty}\, 2^{-nN}\cdot \rho^*_N(E)=
\text{vol}_n(\Omega)-
\text{vol}_n(\Omega\setminus E)
\]
In particular the limit in the left hand side exists and we use it as a definition of
$\text{vol}_n(E)$ for a compact set $E$.
The reader may also verify that
the limit exists directly. Namely, if $\square\in\mathcal D_N$ has a closure whose
closure has a non-empty intersection wit $E$ then it can only occur that some of the
smaller closed cubes from $\mathcal D_{N+1}$ which are contained $\square$ have empty intersection with
$E$. This entails that the function

\[ 
N\mapsto 2^{-nN}\cdot \rho^*_N(E)
\] 
is increasing and hence has a limit which by the above is
the measure of $E$.

\medskip


\noindent
{\bf{1.7 An outer approximation.}}
Let $E$ be a compact set. If $\delta>0$ we obtain the open set
\[
 E_\delta=\{ x\colon\,\,\text{dist}(x,E)<\delta\}
\]
With this notation one has
\[ 
\lim_{\delta\to 0}\, \text{vol}_n(E_\delta)=
\text{vol}_n(E)\tag{*}
\]
To prove this we take some $\epsilon>0$ and find $N$ so large that

\[
2^{-nN}\cdot \rho^*_N(E)<\text{vol}_n(E)+\epsilon
\]


\noindent
Next,
with $N$ fixed we notice that if
$\square\in\mathcal D_N$ is such that
$\bar\square\cap E=\emptyset$ then
$\bar\square\cap E_\delta=\emptyset$ for a sufficiently small $\delta$.
Hence with $N$ fixed we can find $\delta$ so small that
\[
E_\delta\subset\,\cup\, \bar\square\
\] 
where the union is taken over cubes in
$\mathcal D_N$ whose closures intersect $E$.
This gives
\[
\text{vol}_n(E_\delta)\leq 2^{-nN}\cdot \rho^*_N(E)<\text{vol}_n(E)+\epsilon
\]
Since $\epsilon$ is arbitrary we get  (*).

\newpage

\centerline{\bf{1.8 Lebesgue points}}
\medskip

\noindent
Let $E$ be a compact set. Examples show that $E$ may have positive
Lebesgue measure and yet its interior is empty.
Suppose this holds and let $x_0\in E$ be a given point. If
$\square$ is an open cube which contains $x_0$
then $\square\setminus E$ is non-empty so we have the strict inequality
\[ 
\text{vol}_n(E\cap \square)=
\text{vol}_n(\square)=
\text{vol}_n(\square\setminus E)
\]
In spite of this it turns out that
\[ 
\lim_{\square\to x_0}\, 
\frac{\text{vol}_n(E\cap \square)}{
\text{vol}_n(\square)}=1\tag{*}
\] 
can hold where the limit is taken over cubes
which tend to the singleton set $\{x_0\}$.
To be precise, (*) means that for every
$\epsilon>0$ there exists some
integer $M$ such that

\[
x_0\in\square\quad \text{and}\quad
\text{vol}_n(\square)<\frac{1}{M}\implies
\text{vol}_n(E\cap \square)>(1-\epsilon)\cdot 
\text{vol}_n(\square)
\]
where $\square$ are arbitrary open cubes.
Notice that we do not require that
$x_0$ is the center if $\square$ when we regard an inclusion
$x_0\in\square$.
\medskip


\noindent
{\bf{1.9 Definition.}}
\emph{A point $x\in E$ is called a Lebesgue point if (*)
holds. The set of Lebesgue points in $E$ is denoted by
$\mathcal L(E)$.}
\bigskip

\noindent
It turns out
that
$\mathcal L(E)$ is so large that the complement
$E\setminus\mathcal L(E)$ is a null set, i.e. one has:
\medskip

\noindent
{\bf{1.10 Theorem.}} \emph{Almost every point  in $E$ is a Lebesgue point}.
\medskip

\noindent
The proof relies upon a covering Lemma due to Vitali. So we first
expose this result and prove Theorem 1.10  in 1.13 below.

\bigskip


\noindent 
{\bf 1.11 Vitali coverings.}
Let $A$ be a subset of ${\bf {R}}^n$ and  $\mathcal V=\{\square_\alpha\}$  a
family of open cubes. 
It is called a
Vitali covering of $A$ if the following hold:
\medskip

\noindent 
\emph{For  each point $a\in A$  and each $\epsilon>0$
there exists some $\square_\alpha\in \mathcal V$ such that
$a\in\square_\alpha$ and $\text{vol}_n(\square_\alpha)<\epsilon$}.
\medskip

\noindent
{\bf Remark.} The $\mathcal V$ -cubes may consist 
of a non-denumarable family, i.e. the indices $\alpha$ can be taken from any set.
\bigskip


\noindent
{\bf 1.12 Vitali's Theorem}
\emph{Let $\mathcal V$ be a Vitali covering of a bounded set $A$.
Then there exists a sequence of pairwise disjoint cubes
$\square_1,\square_2,\ldots$ in $\mathcal V$ such that for every
$N$ one has the inclusion}
\[
A\subset\bar  \square_1,\cup\,\ldots,\cup\,\bar \square_N\,\bigcup_
{\nu>N}\, 3\cdot \square_\nu
\]
\emph{where $\bar \square_1,\ldots,\bar\square_N$ denote the closure of the first $N$ cubes and if
$\nu>N$ then $3\cdot\square_\nu$ is the expanded cube
whose sides are three times larger than those of $\square_\nu$.}

\bigskip

\noindent
\emph{Proof.}
Pick a cube $\square_1\in\mathcal V$ such that
\[ 
|\square_1|_n>\frac{2}{3}|\square_\alpha|_n\quad\colon\quad
\,\forall\,\,\square_\alpha\in\mathcal V
\]
Next, let $\mathcal V_1$ be the subclass of $\mathcal V$-cubes
which have empty intersection with the closed cube $\bar\square _1$.
Then we pick $\square_2\in\mathcal V_1$ such that
\[ 
|\square_2|_n>\frac{2}{3}|\square_\alpha|_n\quad\colon\quad
\,\forall\,\,\square_\alpha\in\mathcal V_1
\]
We continue in this way and obtain a sequence of pairwise disjoint 
cubes $\square_1,\square_2,\ldots$ where one for each $k\geq 2$ has
\[
|\square_{k+1}|_n>\frac{2}{3}\cdot |\square_\alpha|_n\quad\colon\quad
\,\forall\,\,\square_\alpha\in\mathcal V_k
\]
and $\mathcal V_k$ is the family of cubes which have empy
intersection with $\bar\square_1\cup\,\ldots\cup \bar\square_k$.
It remains to show that  this sequence gives the covering lemma.
First, since the $\mathcal V$-cubes all stay inside a bounded set we have
\[ 
\sum_{\nu=1}^\infty\,|\square_\nu|_n<\infty\tag{1}
\]
Next, let $a\in A$ and let $N$ be some positive integer.
If $a$ already belongs to $\bar\square_1\,\,\cup\ldots,\cup\,\,\bar\square_N$
we are done. If the inclusion  fails the Vitali covering gives some 
$\square_\alpha\in\mathcal V$ which contains $a$ and at the same time
is so small that it has empty intersection with the union of the $N$ first closed cubes.
Now $|\square_\alpha|_n>0$ and we claim that
$\square_\alpha$ cannot be disjoint from
$\bar\square_{N+1}\cup\ldots,\cup\bar\square_M$ for all $M\geq N+1$. For if
it is disjoint from such a union up to some integer , the construction entails that

\[
|\square_\alpha|_n\leq \frac{2}{3}|\square_M|_n
\]
But this cannot hold when $M$ is large since the convergence in (1)
implies that $|\square_M|_n\to 0$ as $M$ increases. 
Hence we can find a \emph{smallest} $M\geq N+1$ such that
\[
\square_\alpha\,\cap\,\bar \square_M\neq \emptyset
\]
Since $M$ is minimal  $\square_\alpha$ is disjoint from the 
closed union of the first $M-1$-cubes and  the construction
of $\square_M$
entails
\[
|\square_M|_n>\frac{2}{3}|\square_\alpha|_n
\]
This gives obviously the inclusion
$\square_\alpha\subset 3\cdot\bar\square_M$
and finishes the proof of Vitali's covering lemma.
\bigskip








\bigskip










\centerline{\bf 1.13 Proof of Lebesgue's theorem}
\medskip


\noindent

Let $\epsilon>0$ and $0<\rho<1$ be kept
fixed for a while.
When $N$ is a positive integer we define the subset
$U_N(E)$ of $E$ which consists of points $x\in E$ for which there exist
a cube $\square$  such that
\[
\frac{\text{vol}_n(\square\cap\,E)}{\text{vol}_n(\square)}<
\rho\quad\,\colon\quad\text{vol}_n(\square)< \frac{1}{N}
\]
It is obvious that $U_N(E)$ is an relatively open subset of
$E$. 
Moreover these sets decrease as $N$ increases. Put
\[ 
A=\cap_{N\geq 1}\, U_N(E)
\]
Next, by 1.5 above 
there exists $\delta>0$ such that
\[
|A_\delta\setminus A|<\epsilon
\]
Next, let $\mathcal V(\rho)$ be the family of cubes $\square$ for which
\[
\frac{\text{vol}_n(\square\cap\,E)}{\text{vol}_n(\square)}<\rho
\quad\colon\quad 3\cdot \bar \square\subset A_{\delta}
\]
It is clear that $\mathcal V(\rho)$ is a Vitali covering of $A$.
The  Covering lemma gives a sequence of
pairwise disjoint cubes $\square_1,\square_2,\ldots$.
so that 
\[ 
A\subset\,\bar\square_1\cup\ldots\cup\bar\square_N\,\bigcup
3\cdot \square_\nu\quad\colon\quad N\geq 1
\]
Next, using the obvious  the inequalities
\[
\frac{\text{vol}_n(A\cap\square_\nu)}{\text{vol}_n(\square_\nu)}
\leq \frac{\text{vol}_n(E\cap\square_\nu)}{\text{vol}_n(\square_\nu)}
<\rho\quad\colon\quad 1\leq\nu\leq N
\]
it follows that
\[
|A|_n<\rho\cdot 
\sum_{\nu=1}^{\nu=N}\,
\text{vol}_n(\square_\nu)+
3^n\cdot\sum_{\nu>N}\,\text{vol}_n(\square_\nu)
\]
Finally, since the cubes $\{\square_\nu\}$ are pairwise disjoint
the series $\sum\,\text{vol}(\square_\nu)$ converges. So if $N$ is 
sufficently large we have
\[
3^n\cdot\sum_{\nu>N}\,\text{vol}_n(\square_\nu)<\epsilon
\]
At the same time $\square_1,\ldots,\square_N$ are
all contained in $A_\delta$. Hence XX gives
\[ |A|_n<\rho\cdot |A_{\delta}|_n+\epsilon<\rho\cdot |A|_n+
\rho\epsilon+\epsilon=\leq \rho\cdot |A|_n+2\epsilon
\]
Here $\epsilon$ can be arbitrarily small and since $\rho<1$ we conclude that 
$A$ is a null set.
Its construction dependson $\rho$ so let us denote this null set with
$A(\rho)$. As $\rho\to 1$ the condition in (x) becomes more relaxed so these null sets increase. We get in particular the null set
\[
A^*=\cup_{\nu\geq 2}\, A(1-\frac{1}{\nu})
\]
At this stage the reader may verify that $E\setminus A^*$ is contained in
$\mathcal L(E)$ and  Lebesgue's theorem is proved.
\bigskip

\noindent
{\bf Remark} Above we found that $A(1-\frac{1}{\nu})$ is a so called $G_\delta$
set, i.e. the intersection of a decreasing sequence of
relatively open subsets of $E$.
So $A^*$ is the union of an increasing sequence of $G_\delta$-subsets
of $E$, i.e. it a set-theoretically "relatively nice" subset of $E$.


\noindent
{\bf 1.14  Example.}
Let $n=1$ and consider a denumerable family of open intervals
$\{(a_\nu,b_\nu)\}$  all of which are contained in $(0,1)$.
Suppose also that $\sum\,(b_\nu-a_\nu)=1/2$.
In addition these intervals can be chosen so that their union is
dense in $(0,1)$. We obtain the compact set
\[ 
E=[0,1]\setminus\cup\,(b_\nu-a_\nu)
\]
It has no interior points and its Lebesgue measure is 1/2.
Suppose that $\xi\in\mathcal L(E)$ where $0<\xi<1$.
Given a small $\delta>0$ we put
\[
\rho(\delta)=\sum_{\nu=1}^\infty\,
\,|(b_\nu-a_\nu)\cap (\xi-\delta,\xi+\delta)|_n
\]
By the definition of Lebesgue points it follows that
\[ \
\lim_{\delta\to 0}\,\frac{\rho(\delta)}{\delta}=0
\]
The fact that this hold for all $\xi\in E$ outside a null set is remarkable since the 
chosen family  of  open intervals $\{(a_\nu,b_\nu)\}$ is quite general.






\bigskip



\centerline {\bf 2. Measurable sets}
\bigskip

\noindent
Let $\Omega$ denote open sets and $E$ compact sets.
The outer - respectively the inner measure - of a set
$A$ are defined by
\medskip
\[ 
|A|^*=\min\,\text{vol}_n(\Omega)\quad\,\colon\, A\subset \Omega\quad
\colon\quad 
|A|_*=\max\,\text{vol}_n(E)\quad\colon\, E\subset A
\]
\medskip


\noindent
{\bf 2.1 Definition.} \emph{A set $A$ is measurable in the sense of Lebesgue if 
$|A|^*=|A|_*$. When it holds the common number is denoted by 
$\text{vol}_n(A) $  and  called the Lebesgue measure of $A$.
The class of measurable sets is denoted by
$\mathfrak{Leb}(\bf R^n)$.}
\bigskip

\noindent 
{\bf Remark.}
Let $A$ be measurable. The definition of  inner measure yields 
an increasing squence of compact subsets $\{F_\nu\}$
of $A$  such that
$\lim\,|F_\nu|\to |A|_*$. Since $|A|=|A|_*$ it follows that
that if $F^*=\cup\, F_\nu$, then $A\setminus F^*$ is a null set.
Similarly, using the equality $|A|=|A|^*$ we find that
that there exists a descreasing sequence of open sets
$\{\Omega_\nu\}$ containing $A$
such that if $\Omega_*=\cap\,\Omega_\nu$, then
$\Omega_*\setminus A$ is a null set.
Thus, apart from a null set every measurable set can be 
taken as a $G_\delta$-set, i.e. a denumerable intersection of
open sets, or as a denumerable union of closed sets.
In general,  a pair of measurable sets $A,B$ are called
\emph{equivalent} if the Boolean difference
\[ 
(A\setminus B)\cup\,(B\setminus A)
\] 
is a null set. This is an equivalence relation on  the class of
measurable sets and whenever needed one may choose a special measurable set from such an
equivalence class. 



\bigskip

\centerline {\bf {Lebesgue points of measurable sets}}
\medskip

\noindent
Let  $A$ be a  measurable set.
A point $x_0$ is called a
Lebesgue point for $A$ if

\[ 
\lim_{\square\to x_0}\, 
\frac{\text{vol}_n(A\cap \square)}{
\text{vol}_n(\square)}=1\tag{*}
\] 
holds where the limit is taken over cubes
which tend to the singleton set $\{x_0\}$.
The set of Lebesgue points is denoted by
$\mathcal L(A)$.
Notice that we do not require that $x_0$ belongs to $A$.
However, if $E$ is a closed set it is clear that
a Lebesgue point of $E$ must belong to $E$
which means that our definition above extends
that for closed sets in Definition 1.9. In particular we
see that
$\mathcal L(A)$ is contained in the clopsure of $A$.
If $\Omega$ is an open set it is clear that
$\mathcal L(\Omega)\subset\Omega$ and it may occur that
the boundary $\partial\Omega$ contains some Lebesgue points, i.e. the set
$\mathcal L(\Omega)\setminus \Omega$ 
can be non-empty.
\medskip


\noindent
{\bf{2.2 Theorem.}}\emph{For every measurable set $A$ the Boolean difference
of $A$ and $\mathcal L(A)$ is a null set.}
\bigskip


\noindent
\emph{Proof.}
First we prove that $A\setminus\mathcal L(A)$ is a null set.
To show this we consider
some $0<\rho<1$ and for each integer $N\geq 1$
we  get the subset $U_N(A)$ which consists of
all $x\in A$ for which there exists an open cube $\square$
such that
\[
\frac{\text{vol}_n(\square\cap\,A)}{\text{vol}_n(\square)}<
\rho\quad\,\colon\quad\text{vol}_n(\square)< \frac{1}{N}\quad\colon
x\in\square\tag{1}
\]
\medskip

\noindent
It is clear that  $U_N(A)$ is relatively open in $A$ and hence measurable. Put
\[ 
A_*(\rho)=\cap\, U_N(A)\tag{2}
\]
Then $A_*(\rho)$ is measurable
and hence equal to its outer measure.
So for
any $\epsilon>0$ there exists 
an \emph{open set} $\Omega$ which contains
$A_*(\rho)$ such that

\[
|\Omega\setminus A_*(\rho)|<\epsilon\tag{3}
\]
Next, define the family $\mathcal V(\rho)$ of open cubes for which
\[
\frac{\text{vol}_n(\square\cap\,A)}{\text{vol}_n(\square)}<\rho
\quad\text{and}\quad 3\cdot \bar \square\subset \Omega\tag{4}
\]
This yields a Vitali covering of $A_*(\rho)$ and we get a sequence of
parirwise disjoint cubes
$\square_1,\square_2,\ldots$ in $\mathcal V(\rho)$
such that
\[
 A_*(\rho)\subset\,\bar\square_1\cup\ldots\cup\bar\square_N\,\bigcup
3\cdot \square_\nu\quad\colon\quad N\geq 1
\]
From this we conclude that
\[ 
|A_*(\rho)|<\rho\sum_{\nu=1}^{\nu=N}\,\text{vol}_n(\square_\nu)
+ 3^n\cdot \sum_{\nu>N}\,\text{vol}_n(\square_\nu)
\]
As in the proof for compact sets we  choose $N$ so that
$3^n\cdot \sum_{\nu>N}\,\text{vol}_n(\square_\nu)<\epsilon$
and since each $\square_\nu\subset \Omega$ we obtain
\[ 
|A_*(\rho)|<\rho\cdot|\Omega|+\epsilon<
\rho\cdot |A_*(\rho)|+\rho\epsilon+\epsilon\leq \rho\cdot |A_*(\rho)|+2\epsilon
\] 
where we used that $|\Omega\setminus A_*(\rho)|<\epsilon$.
Hence 
\[
|A_*(\rho)|<\frac{2\epsilon}{1-\rho}
\]
Since $\epsilon>0$ can be made arbitrary small we conclude that
$A_*(\rho)$ is a null set.
Now we choose $\rho=1-\frac{1}{k}$ with $k=1,2,\ldots $  and get
the null set
\[ 
A_*=\cup\, A_*(1-\frac{1}{N})
\] 
\medskip

\noindent
Funally, from the construction of the sets
$A_*(\rho)$ it is clear that one has the inclusion:
\[ 
A\setminus A_*\subset\mathcal L(A)
\]
Hence $A\setminus\mathcal L(A)$ is contained in the null set $A_*$.
To show that $\mathcal L(A)\setminus A$ is a null set we
can work locally and consider a bounded 
and relatively open subset $B$ of ${\bf{R}}^n\setminus A$.
Now $B\setminus\mathcal L(B)$ is a null set and at the same time
it is obvious that

\[
\mathcal L(A)\cap B\subset B\subset\mathcal L(B)
\]
From this we conclude that
$\mathcal L(A)\setminus A$ also is a null set and
Theorem 2.2 follows.








\bigskip


\noindent
{\bf{2.3 Remark.}}
The result above means that we can choose
a canonical set in every equivalence class of measurable sets.
Namely, if  $A$ and $B$ are two measurable sets
whose  Boolean difference is a null set
then $\text{vol}_n(A\cap\square)=\text{vol}_n(B\cap\square)$
hold for every cube. It follows that
we have the equality 
$\mathcal L(A)=\mathcal L(B)$.
So in the given equivalence class we can choose this common set
denoted by $A_*$ where we now have the equality

\[
A_*=\mathcal L(A_*)\tag{*}
\]




\noindent
{\bf 2.4 A criterion for null sets}
Let $A$ be a measurable set.
Suppose there exists some $0<\rho<1$
such that
\[ 
|A\cap\square|_n\leq\rho\cdot|\square|_n
\]
hold for a family of open cubes which is a Vitali covering of
$A$. Then we see that $A$ cannot have 
any Lebesgue point and hence it must be a null set.
\bigskip



\centerline{\bf 3. Measurable functions and their integrals }
\bigskip

\noindent
A real-valued function  $f$ on $\bf R^n$ is measurable if the sets
\[ 
\{x\colon\, f(x)<a\}\quad\colon\,\quad
\{x\colon\, f(x)\leq a\}
\] 
are measurable for every real number $a$.
Among these occur finite $\bf R$-linear sums of characteristic functions.
That is, let $A_1,\ldots,A_m$ be a finite family of pairwise disjoint and measurable sets. Then the functions 
\[ 
\sum c_\nu\cdot\chi_{A_\nu}\quad\colon\quad\,c_1,\ldots,c_m\,\,
\text{in}\,\,\bf R
\]
are measurable where we for each set $A$ denote by $\chi_A$ its characteristic function.
Let us now study bounded and measurable functions which for 
simplicity takes values in the interval $[-1,1]$.
Given such a function $f$ we can approximate it from below and from above.
When $N\geq 1$ we get the pairwise disjoint and measurable sets
\[
A_\nu(N)=\{\nu 2^{-N}\leq f<(\nu+1)2^{-N}\}
\]
Put
\[
S_*(N)=\sum_{\nu=-2^N}^{\nu=2^N-1}
\, \nu 2^{-N}\chi_{A_\nu(N)}\quad\text{and}\quad
S^*_N= \sum_{\nu=-2^N}^{\nu=2^N-1}\, 
(\nu+1) 2^{-N}\chi_{A_\nu(N)}
\]
It follows that
\[ 
S_*(N)\leq f\leq S^*(N)\quad\colon\quad
S^*(N)-S_*(N)\leq 2^{-N}
\]
\medskip


\noindent
{\bf{Remark.}}
Notice that
$\{S_*(N)$ is an increasing sequence of functions, while
$\{S^*(N)\}$ is decreasing. Hence we can approximate 
the bounded function $f$ \emph{uniformly} by 
characteristic functions from below or from above.
\bigskip

\noindent
{\bf 3.1 The Lebesgue integral.}
Let $f$  be bounded and measurable. Consider also some bounded
measurable set $E$ which is kept fixed.
To each $N\geq 1$ we define the integrals
\[ 
\int_E\, S_*(N)(x) dx=
\sum_{\nu=-2^N}^{\nu=2^N-1}
\, \nu 2^{-N}\text{vol}_n(A_\nu(N)\cap E)
\] 
\[
\int_E\, S^*(N)(x) dx=
\sum_{\nu=-2^N}^{\nu=2^N-1}
\, (\nu +1)2^{-N}\text{vol}_n(A_\nu(N)\cap E)
\]
It is clear that their difference is $\leq(b-a)2^{-N}
\text{vol}_n(E)$ and their exists
the common limit
\[ 
\lim_{N\to\infty}\,
\int_E\, S_*(N)(x) dx=\int_E\, S^*(N)(x) dx
\]
It is denoted by $\int_E\,f(x)dx$ and called the Lebesgue integral of $f$
over the measurable set $E$.
\medskip

\noindent {\bf Exercise}
Show that the integral is approximated
by small partitions of the range of $f$. More precisely, let
$-1=a_0<a_1\ldots<a_N=1$ and put
\[ 
I(a_\bullet)=\sum\,a_\nu\cdot \chi_{\{a_\nu\leq f<a_{\nu+1}\}}
\]
Then one has the inequality
\[
|\int_E\, f(x) dx-I(a_\bullet)|\leq
\text{vol}_n(E) \cdot\max\,(a_{\nu+1}-a_\nu)
\]
Above the rate of 
convergence these  $I(a_\bullet)$-sums  to
the Lebesgue integral of $f$  is \emph{independent} of $f$ as long as its range is confined to
$[-1,1]$.
This means  that the construction of the Lebegue inegral is "robust".
\bigskip

\noindent 
{\bf Exercise} Show that the Lebesgue integral is additive in the sense that

\[ 
\int_{E_1\cup E_2}\, f(x)dx=
\int_{E_1}\, f(x)dx+
\int_{E_2}\, f(x)dx\quad\colon\, E_1,E_2 \,\,\text{disjoint  bounded measurable sets}
\]
Show also additivity with respect to $f$, i.e. that
\[
\int_{E}\, (f_1+f_2)dx=
\int_{E}\, f_1dx=
\int_{E}\, f_2 dx
\] 
for a pair of bounded and measurable functions.

\bigskip

\noindent 
{\bf 3.2 Lebesgue points.}
Let $f$ be a bounded measurable function. A point $x_0$
is called a Lebesgue point of $f$ if
\[
\lim_{\delta\to 0}\,\frac{1}{|\square|_n}\,\int_\square\, 
f(x)\cdot dx=f(x_0)\tag{*}
\]
hold where the limit it is taken over
cubes $\square$ which contain $x_0$ with measure $<\delta^n$.
Thus, if $f=\chi_A$ for some measurable set $A$, then we encounter the previous
notion of Lebesgue points for sets.
\bigskip

\noindent {\bf 3.3 Theorem}
\emph{Outside a null set a bounded measurable function has Lebesgue points}.
\bigskip

\noindent 
\emph{Proof}
To prove this we employ the functions
$S^*(N)$ and $S_*(N)$ above.
Each $S$-function is finite linear sum of characteristic functions
and by Theorem 2.2 measurable sets have Lebesgue points almost every where.
Since the union of a denumerable family of null sets is again a null set
we see that there exists a null set $F$
such that the following
hold
for every point $x_0\in{\bf{R}}^n\setminus F$ and every $N\geq 1$:

\[
\lim_{\delta\to 0}\,\frac{1}{|\square|_n}\,\int_\square\, 
S^*(N)(x)dx=S^*(N)(x_0)\quad\text{and}\quad
\lim_{\delta\to 0}\,\frac{1}{|\square|_n}\,\int_\square\, 
S_*(N)(x)dx=S_*(N)(x_0)
\]
Since $f\leq S^*(N)$ for all $N$ the first limit formula entails that
\[
\text{Lim.sup}\,_{\delta\to 0}\,\frac{1}{|\square|_n}\,\int_\square\, 
f(x)dx\leq f(x_0)
\]
Similarly, the second limit formula gives
\[
\text{Lim.inf}\,_{\delta\to 0}\,\frac{1}{|\square|_n}\,\int_\square\, 
f(x)dx\geq f(x_0)
\]
\medskip

\noindent 
Hence the equality (*) holds almost everywhere.


\bigskip




\noindent {\bf 3.4 Approximating bounded measurable functions.}
Let $f$ be a bounded
measurable function.
To each $\delta>0$ we set
\[
F_\delta(x)=
\delta^{-n}\cdot
\int_{\square_\delta(x)}\, f(x)dx
\]
where 
$\square_\delta(x)$ is the square centered at $x$ with volume $\delta^n$.
The definition of Lebesgue points give
\[ 
\lim_{\delta\to 0}\,
F_\delta(x)=f(x)\quad\colon\quad x_0\in\mathcal L(f)\tag{*}
\]
Concerning the $F_\delta$-functions one has:
\medskip

\noindent {\bf 3.5 Proposition} \emph{There exists a constant
$C_n$ which depends on $n$ only such that
when$|f|\leq 1$ and $0<\delta\leq 1 $ then}
\[ 
|F_\delta(x)-F_\delta (y)|\leq C_n\cdot \frac{|x-y|}{\delta}\colon\quad
\text{for any pair}\,\, x,y
\]
\bigskip

\noindent
{\bf 3.6 Remark} The convergence in (*) is \emph{pointwise}.
Thus, every bounded measurable function outside a null set is a
pointwise limit  of 
Lipschitz continuous functions. Identifying  measurable functions which
are equal almost everywhere we may assume from the start that
$f$ is equal to its Lebesgue value outside a  nullset $\mathcal N_f$.
Then  the pointwise limit in (*) holds at all points outside
$\mathcal N_f$.

\bigskip

\noindent
{\bf{3.7 Another approximation of measurable functions.}}
Set 
\[ 
F^*_\delta(x)=\max_{0<\rho\leq\delta} F_{\rho}(x)\tag{1}
\]
\medskip

\noindent
Here the maximum is taken over a family of Lipschitz continuous functions which implies
that $F^*_\delta$ is upper semi-continuous  for
every $\delta>0$.
As $\delta$ decreases the maximum is taken over smaller families of functions.
So
$\{F^*_\delta\}$ is a non-increasing sequence of functions
which converge pointwise to $f$ outside
$\mathcal N_f$.




\bigskip


\centerline {\bf 3.8 Egoroff's Theorem.}
\bigskip

\noindent
Let $f$  be a bounded measurable function
defined on a compact set, say the unit cube
$\square$ in ${\bf{R}}^n$. 
If $\epsilon>0$
we can choose a compact set
$E\subset \mathcal L(f)$ such that $|\square\setminus E|_n<\epsilon$.
With $\{g_n=F_{1/n}\}$ we have a sequence of continuous functions
on $E$ which converges pointwise to $f$.
Now we construct  a subset of $E$ where the pointwise convergence is uniform.
To each pair of positive integers
$\nu,N$
we set
\[ 
G_N(\nu)=\,\bigcup_{k,m>N}\,\{x\in\,E\,\colon\,
 \,|g_k(x)-g_m(x)|\geq \frac{1}{\nu}\}
\]
Since $\{g_k\}$
converges pointwise on $E$, 
the  decreasing sequence $N\mapsto G_N(\nu)$ 
tends to the empty set for each fixed $\nu$.
So if  $\epsilon>0$  there exists for every
$\nu\geq 1$ some $N(\nu)$ such that

\[
\text{vol}_n(|G_{N(\nu)}(\nu))<2^{-\nu}\cdot\epsilon
\]

\noindent
Next,
since $G_{N(\nu)}(\nu)$ is measurable we  find
an open set
$\Omega_\nu$ such that

\[ 
G_{N(\nu)}(\nu)\subset \Omega_\nu\quad\colon\,
|\Omega_\nu| <2^{-\nu}\cdot\epsilon
\]
\medskip

\noindent
Put $E_*=E\setminus\,\cup\,\Omega_\nu$.
Then $|\square\setminus E_*|<2\epsilon$ and from the construction of the 
$G$-sets we see that the sequence $\{g_k\}$ converges \emph{uniformly} on $E_*$
which implies that  the limit function $f$ 
restricts to be continuos on $E_*$. Hence we have proved:
\bigskip

\noindent
{\bf 3.9 Theorem.} \emph{To every $\epsilon>0$ there exists a compact
set $E\subset\square$ such that the measure of $\square\setminus E$
is $<\epsilon$
and the restriction of $f$ to $E$ is a continuous function.}


\bigskip

\centerline {\bf 4.  Fubini's Theorem.}
\bigskip

\noindent
We  study images of measurable sets under projections.
Let $n$ and $m$ be positive integers and denote points in
${\bf{R}}^{n+m}$ by $(x,y)$. We have the projection
$\pi(x,y)=x$ onto the $n$-dimensional $x$-space.
Let $A$ be a bounded measurable set in
${\bf{R}}^{n+m}$. To each $x$ we get the slice
\[
 A(x)=\{y\,\colon\, (x,y)\in A\}\tag{1}
\]
\medskip

\noindent
{\bf{4.1 Theorem.}}
\emph{ There exists a null set $\mathcal N$ in the $x$-space such that
the slices $A(x)$ are measurable for all $x$ outside $\mathcal N$
and the function}
\[
x\mapsto |A(x)|_m
\]
\emph{is measurable. Moreover one has the equation}
\[
|A|_{m+n}=
\int\, |A(x)|_m\, dx\tag{*}
\]
\medskip

\noindent
\emph{Proof.}
Consider first the case when $E$ is a compact set.
in ${\bf{R}}^{n+m}$. Then every slice $E(x)$ is compact and
hence measurable and 
the reader may  verify that
the function
\[ 
x\mapsto |E(x)|_m
\]
is upper semi-continouos and in particular measurable.
Next, if $\Omega$ is a bounded open set
the slices are open and
this time we get a lower semi-continuous function
\[ 
x\mapsto |\Omega(x)|_m
\]
Taking the dyadic decomposition of $\Omega$ from ¤ xx
the reader may verify that
(*) holds for bounded open sets and
expressing compact sets is complents of open subsets of large cubes
we also have (*) for compact sets.
Next, if $A$ is a bounded measurable set we
choose an increasing sequence of compact subsets
$\{E_k|\}$ where
$|A\setminus E_k|_{m+n}\to 0$.
Similarly $\{\Omega_k|\}$ is an increasing sequence of open sets
containing $A$ such that
$|\Omega_k\setminus A|_{m+n}\to 0$.
Set
\[ g_k(x)=|\Omega_k(x)|_m-|E_k(x)|_m
\]
Then $\{g_k\}$ is a non-increasing sequence of functions
and
since (*) hold for open and compact sets
while $|\Omega_k\setminus  E_k|_{m+n}\to 0$
it follows that
\[
\lim_{k\to \infty}\,
\int\, g_k(x)\, dx=0
\]
By the remark in ¤ xx this entails that
$\{g_k\}$ converge poinitwise to zero almost everywhere.
So we find a null set $\mathcal N$ in ${\bf{R}}^n$
and $g_k(x)\to 0$ hold when $x$ is outside $\mathcal N$.
For a single slice it means that
the outer and the inner measure of $A(x)$ are equal.
Moreover, the funciton defined outside $\mathcal N$ by
\[
x\mapsto |A(x)|_m
\]
is equal to the function
\[
\lim_{k\to \infty}\, |E_k(x)|_m
\]
Here (ii) is the pointwise limit of an increasing sequece of
upper semi-continuous functions and therefore measurable.
hence (i) is measurable and at this stage the reader can also verify the
equation (*) in Theorem xx.
\bigskip

\noindent
{\bf{Fubini's theorem for functions.}}
Let $f(x,y)$ be a bounded measurable function with compact support.
We agree to identify $f$ with its Lebegue function and set
\[
G_k= F^*_{1/k}\quad\colon k=1,2,\ldots
\]
here $\{G_k(x,y)\}$ are upper semi-conionuous functions and
the same hold for the functions
\[ 
g_k(x)=\int\, G_k(x,y)\, dy
\]
Now $\{g_k\}$ is a non-increasing sequence of functions
and there exists the limit
\[
\lim_{k\to\infty}\, \int g_k(x)\, dx
\]
By ¤ xx it follows that
$\{g_k\}$ converge almost everywhere, i.e.
outside a null set
$\mathcal N$
in
the $x$-space there exists  a limit function
\[
g_*(x)=\lim_{k\to\infty}\, \int g_k(x)\
\]
For each fixed $x$ outside $\mathcal N$
it follows that there exists the limit
\[
\lim_{k\to\infty}\, \int G_k(x,y)\, dy
\]
Since the sequence of functions $\{y\mapsto G_k(x,y)\}$
is non-increasing 
we get a limit function
\[
G_*(x,y)=\lim_{k\to\infty}\, \int G_k(x,y)\, dy
\]
So here $G_*$ is defined outside the sliced null set
$\mathcal N\times{\bf{R}}^m$. Using Theorem xx and approximating
$f$
unifornly by elementary functions the reader may verify the equality
\[
\iint f(x,y)|, dxdy=
\iint G_*(x,y)\, dxdy=\int\, g_*(x)\, dx
\]
\medskip

\noindent
{\bf{Remark.}}
We refer to $G_*(x,y)$ as the Fubini's slice function
under the projection $\pi(x,y)= x$.
Returning to the function $f$ which is identified eith its
Lebesgue function
we leave the following as an exercise to the reader:
\medskip

\noindent
{\bf{Exercise.}}
Show that for every $x$ outside $\mathcal N$
one has the equality
\[
G_*(x,y=f(x,y)
\]
for all $y$ such that $(x,y)$ is a Lebegue point of $f$
and this set of $y$-values 
excludes at most a null set in ${\bf{R}}^m$
which may depend upon $x$.
It means that the bounded measurable function $f(x,y)$ has an
almost everywhere defined slice fun ction
$y\mapsto f(x,y)$
for every $x$ outside the null set $\mathcal N$
which by the above can be identified with the everywhere defined
slice function $y\mapsto G_*(x,y)$.


















\newpage




\centerline{\bf\large IV. Riesz measures}


\bigskip 
\centerline{\emph{Contents}}


\medskip

\noindent
0. Introduction

\medskip

\noindent
1. Dyadic grids

\medskip

\noindent
2. Singular Riesz measures

\medskip

\noindent
3. Signed Riesz measures


\medskip

\noindent
4. $\mu$-integrals

\medskip

\noindent
5. Riesz' representation formula

\medskip

\noindent
6. Borel measurable functions


\medskip

\noindent
7. Weak convergence

\medskip

\noindent
8. Products and convolutions

\bigskip











\centerline {\bf Introduction}
\bigskip

\noindent
The Lebesgue measure  is invariant under translations as well as rotations in
${\bf{R}}^n$.
Thus, 
the volume of a cube depends only upon the length of its sides and not upon its position.
We shall   construct measures which do not enjoy this invariance.
If $f$ is a locally integrable function in
${\bf{R}}^n$ in the sense of Lebesgue then
we obtain a measure
which to every 
bounded Lebesgue measurable set $E$ assigns
the mass
\[
 \int_E\, f\cdot dx
\]
\medskip

\noindent
We say that $f\cdot dx$ is an absolutely continuous 
measure with respect to $dx$.
The new class consists of \emph{singular} Riesz measures $\mu$ whose 
mass is concentrated to a null set in the sense of
Lebesgue.
Among these occur discrete measures which attach
masses at some sequence of points.
Less evident is the description of singular Riesz measures whose
mass of every singleton set is zero.
If $n=1$ we  described such measures in ¤ I
via  non-decreasing and continuos functions
$f(x)$ on the real $x$-line whose derivative is zero outside a set with
Lebegue measure zero. 
When $n\geq 2$
we have no clear "geometric picture" of a singular Riesz measure.
They are of a more implicit character and in general  one can just say that 
a Riesz measure $\mu$ represents a continuous linear form on
the space of continuous functions.
This follows from a  result due to Friedrich Riesz
which asserts that if $K$ is a compact subset of
${\bf{R}}^n$ and $C^0(K)$ the Banach space of continuous and 
real-valued functions on $K$, then its dual space consists of singular Riesz measures 
supported by $K$.
The \emph{Riesz representation formula} will 
be established  in ¤ 5.
\medskip

\noindent
In ¤ 1 we construct 
Riesz measures 
in
${\bf{R}}^n$ using dyadic grids which is
similar to
the construction of the Lebesgue measure, except that one now
arrives at a  family of $\sigma$-additive measures which
may assign positive mass
to null sets.
In ${\bf{R}}^n$ there exists  the algebra
$\mathcal B({\bf{R}}^n)$
of \emph{Borel measurable functions.}.
Using results from the section about from abstract measure theory 
we will show that if
$f$ is a bounded Borel function and $\mu$ some compactly supported
Riesz measure then there exists an integral
\[
\int f\cdot d\mu\tag{*}
\]
Their existence and properties
constitute a major part in the theory about Riesz measures in
${\bf{R}}^n$.








\newpage

\centerline {\bf 1. Dyadic grids.}
\bigskip

\noindent
If $N\geq 0$ we obtain the family $\mathcal D_N$ of
half-open cubes where we for each $n$-tuple
$\nu_\bullet\in{\bf{Z}}^n$ assign the cube
\[ 
\square_N(\nu_\bullet)=
\{ x\colon\, \nu2^{-N}\leq x_\nu<(\nu+1)2^{-N}\}
\]
It is clear that $\{\square_N(\nu_\bullet)\}$
is a disjoint covering of ${\bf{R}}^n$
for each fixed $N$. Next, let $\Omega$ be a bounded open set.
For each $x\in\Omega$ there exists a unique smallest integer $N(x)$
such that
$x$  belongs to a cube $\square\in\mathcal D_{N(x)}$ with
$\square\subset\Omega$.
This cube is denoted by $\square(x)$. The reader may verify
the implication
\[ 
y\in\square(x)\cap\Omega\implies\square(y)=\square(x)
\]
Hence  $\Omega$  is a unique
union of disjoint half\vvv open dyadic cubes. In other words, there exists
a denumerable sequence
$\{x_\nu\}$ in $\Omega$ such that the cubes
$\{\square(x_\nu)\}$ are disjoint and
\[
\Omega=\bigcup\,\square(x_\nu)\tag{*}
\] 



\noindent
We shall use this unique decomposition of open sets
to construct a family of additive functions.
Let $\mathcal D_*$ be the family of subsets
of
${\bf{R}}^n$ given by a finite and disjoint union of cubes
$\{\square_\alpha\}$ where each
$\square_\alpha\in \mathcal D_{N(\alpha)}$ for some
integer $N(\alpha)\geq 0$.
Suppose  that
\[
 \mu\colon \mathcal D_*\mapsto {\bf{R^+}}
 \] 
 is a non-negative and  additive function which means
that
 \[
 \mu(\cup \square_\alpha)= \sum\, \mu(\square_\alpha)
 \] 
hold for every  finite and disjoint family of dyadic half-open
cubes. 
\medskip


\noindent
{\bf{1.1 The $\mu$-measure on open sets.}}
Let $\Omega$
be a  bounded
open set. The unique  decomposition (*)
defines the number:

\[ 
\mu(\Omega)=\sum\, \mu(\square(x_\nu))\tag{**}
\]
The right hand side is a positive series.
Since
$\Omega$ is bounded the series is convergent.
To see this it suffices to observe that $\Omega$ is contained in some finite 
union of $K$ many cubes from the family $\mathcal D_0$. 
Since $\mu$ is non-negative and  
additive, each finite partial sum of the series in (**) is bounded
by the sum of $\mu$-masses over this $K$-tuple of cubes
in $\mathcal D_0$.
which entails that  (**) is convergent.
Next, let
$\{\Omega_\nu\}$ be a sequence of pairwise disjoint open sets
whose union is bounded. The uniqueness of
dyadic decompositions implies that
\[
\mu(\cup\, \Omega_\nu)=\sum\, \mu(\Omega_\nu)\tag{1}
\]

\medskip


\noindent
{\bf{1.2 The $\mu$-measure on compact sets}}.
Let $E$ be a compact subset of ${\bf{R}}^n$.
If $N\geq 0$ we set
\[ 
\rho_N(E)=
\sum\, \mu(\square)\quad\colon\quad
\square\in\mathcal D_N\quad\text{and}\quad \square\cap E\neq\emptyset
\]
If $N\geq 1$ and some $\square\in\mathcal D_N$ has 
a non-empty intersection with
$E$ it may occcur that some of the half-open cubes
in $\mathcal D_{N+1}$ which are contained in
$\square$ have empty intersection with $E$.
This observation shows that 
\[ 
N\mapsto \rho_N(E)\quad\text{decreases with}\quad  N
\] 
Hence there exists the limit
\[ 
\lim_{N\to\infty}\rho_N(E)
\]
The limit is denoted by $\mu(E)$ and is called the $\mu$-measure of the compact set.
\bigskip


\noindent
{\bf{1.3 Additivity.}}
Let $E$ be a compact set and $\Omega$ some bounded open set which contains
$E$. 
Consider some cube
$\square (x_\nu)\subset\Omega$ in  the decomposition of $\Omega$.
Here two cases can occur : Either $\square(x_\nu)\cap E\neq \emptyset$ or else
$\square (x_\nu)\subset\Omega\setminus E$.
 From this we conclude that the following equality holds for
 every integer $N\geq 0$:
 
 \[
\rho_N(\Omega)=\rho_N(\Omega\setminus E)+\rho_N(E)
\] 
where we have set

\[
\rho_N(\Omega)=
\sum\, \mu(\square)\quad\colon\quad
\square\in\mathcal D_N\quad\text{and}\quad \square\subset \Omega
\]
and similarly we define
$\rho_N(\Omega\setminus E)$.
Since the positive series (**) in 1.1  is convergent for  open sets,
a passage to the limit as $N\to\infty$ gives:

\medskip

\noindent
{\bf{1.4 Proposition.}} \emph{If $E$ is a compact set and if 
$E\subset\Omega$ for some bounded open set, then}
\[
\mu(E)+\mu(\Omega\setminus E)=\mu(\Omega)
\]



\medskip


\noindent
{\bf{1.5 Exercise.}}
Let $\mathfrak B_*$ denote the Boolean algebra of subsets of
${\bf{R}}^n$  generated by 
all open and all compact subsets. Let
$\mu$ be a non-negative and additive function on $\mathcal D_*$ which has a bounded
support in the sense that $\mu(\square)\neq 0$ only occurs for a finite
set of cubes in $\mathcal D_0$.
Use the results above to show that
$\mu$ extends to an additive map on $\mathfrak B_*$, i.e for 
each finite family of disjoint sets $\{F_k\}$ in $\mathfrak B_*$ it holds that
\[
\mu(\cup F_\nu)=\sum\, \mu(F_\nu)
\] 
whenever $F$ and $G$ are disjoint and bounded sets in
$\mathfrak B_*$.
\bigskip

\noindent
\centerline {\bf {1.6 $\sigma$-additivity.}}
\medskip

\noindent
Above we found  an additive measure
defined on bounded sets in
$\mathfrak B_*$. Now there exists the $\sigma$-algebra
$\mathfrak B$ of Borel sets which by definition this is the smallest
$\sigma$-algebra  containing
$\mathfrak B_*$.
In order that $\mu$ can be
extended to a $\sigma$-additive measure defined on $\mathfrak B$
we must impose additional conditions. If 
$\square\in\mathcal D_N $ is a  half-open dyadic cube and 
$0<a<1$ we obtain the closed cube
$a\bar\square$ defined by
\[ 
\nu_k2^{-N}\leq x_k\leq (\nu_k+a)2^{_N}\quad\colon 1\leq k\leq n\}
\]
\medskip

\noindent
By the construction in ¤ 1.2 we can assign the
$\mu$-measure to each of these compact cubes
and since $\mu$ is non-negative 
the function
\[ 
a\mapsto \mu(a\cdot\bar\square)\tag{i}
\] 
is increasing.
Moreover we have
\[
\mu(a\cdot\bar\square)\leq \mu(\square)\quad\colon\text{for each}\quad a<1\tag{ii}
\]


\medskip

\noindent
Hence (i-i) suggest the following:

\medskip

\noindent
{\bf {1.7 Definition.}} \emph{We say that the additive measure $\mu$ is regular if}
\[
\lim_{a\to 1}\, \mu(a\bar\square)=\mu(\square)
\] 
\emph{holds for every half-open dyadic cube.}
\medskip

\noindent 
{\bf {1.8 Remark}}.
This regularity condition is necessary in order that
a
$\sigma$-additive extension. In fact, this follows
since one has  the empty intersection:


\[
\bigcap_{a<1}\, (\square\setminus a\cdot\bar\square)=\emptyset
\]

\medskip

\noindent
{\bf{The case when
$\mu$ is regular. }} Let $\mu$ satisfy
the condition from Definition 1.7.
If $\Omega$ is a bounded open set and
$\epsilon>0$ we  find $N$ such that


\[
\mu(\Omega)<\rho_N(\Omega)+\epsilon\tag{i}
\]
Here $\rho_N(\Omega)=\sum\, \mu(\square_\nu)$ where the sum extends over a finite
set of cubes in $\mathcal D_N$.
The regularity condition  gives some $a<1$ such that
\[
\sum\,  \mu(\square_\nu)<
 \sum\,  \mu(a\cdot\bar\square_\nu)+\epsilon\tag{ii}
 \]
With $E=\cup\, a\cdot\bar\square_\nu$ 
it follows that

 \[
\mu(\Omega)<2\epsilon+\mu(E)\tag{iii}
\]
Notice that
$E$
is a \emph{compact} subset of
 $\Omega$.
Since $\epsilon>0$ can be arbitrary small  we have therefore proved:

\medskip

\noindent
{\bf {1.9 Proposition.}}
\emph{Let $\mu$ be regular, Then}
\[ 
\mu(\Omega)=\max_K\,\mu(K)
\] 
\emph{hold for every bounded open  set $\Omega$
where the maximum is taken over compact subsets of $\Omega$.}
\medskip

\noindent
{\bf {1.10 Exercise.}} Let $\mu$  be regular and
$E$ is a compact set. If $\delta>0$ we set
$E_\delta=\{ x\colon\,\text{dist}(x,E)<\delta\}$. Show that
\[
\lim_{\delta\to 0}\, \mu(E_\delta)=\mu(E)
\]
\medskip

\noindent
{\bf {1.11 Extension to the Borel algebra}}.
Denote by $\mathfrak B$ the 
$\sigma$-algebra generated
open and compact subsets of ${\bf{R}}^n$. Let $\mu$ be a regular and bounded
measure.  Using the
results above  it follows that $\mu$ extends  n a unique fashion to
a $\sigma$-additive measure defined on
all sets in $\mathfrak  B$.
So here

\[
\mu(\cup\, F_\nu)=\sum\,\mu(F_\nu)
\] 
\medskip

\noindent
hold for every denumerable disjoint union of Borel sets.
\bigskip



\noindent
{\bf {1.12 Non-negative Riesz measures}}.
This class consists of non-negative and regular measures $\mu$ defined as above.
We have seen that the $\sigma$-additivity follows from the regularity. Moreover 
the resulting $\sigma$-additive function on bounded Borel sets
is fully determined by the values assigned to all dyadic cubes.
\[
\square_N(\nu\cdot)=
\{ x=(x_1,\ldots,x_n)\,\colon\,\nu_j2^{-N}\leq  x_j<(\nu_j+1)2^{-N}
\}\tag{*}
\]


\noindent
Let us restrict the attention to the
cube
\[
\square_*=\{0\leq x_j<1\,\colon\, 1\leq j\leq n\}
\]
Then $\mathcal D_N$ contains 
$2^{Nn}$ many pairwise disjoint 
and half-open cubes whose  union cover $\square_*$.

\medskip
\noindent
By an induction over $N$
we  assign a non-negative mass to these cubes in
$\mathcal D_N$.
The  constraint is to preserve  additivity.
First $\mathcal D_0$ is a single cube to which we assign
the unit mass. Next, in $\mathcal D_1$
we have
$2^n$ cubes and we assign a non-negative mass to each
of them so that the sum is one.
Next, let
$N\geq 1$ and suppose that a mass $m_N(\nu\cdot)$ is assigned to
every cube $\square_N(\nu\cdot)\in\mathcal D_N$.
Notice that  a given
cube
$\square_N(\nu\cdot)\in\mathcal D_N$ is the union of
$2^n$ many cubes from
$\mathcal D_{N+1}$. To each of these we assign a mass so that
the sum of these $2^n$-many masses is equal to
$m_N(\nu\cdot)$.
\medskip

\noindent
This inductive construction works  for all $N$.
Suppose we have  performed such a construction over all 
positive integers $N$.
Hence a mass $m_N(\nu\cdot )$ is assigned to
$\square_N(\nu\cdot )$ for every
$N$ and each of the $2^{Nn}$  many
$n$-tuples $ \nu\cdot =(\nu_1,\ldots,\nu_n)$.
\medskip

\noindent
{\bf {The regularity condition.}}
Above we have seen how an inductive construction
yields an additive measure $\mu$.
But it does not follow that it is regular, i.e. the condition from 
Definition 1.7 is not automatic.
So here one encounters a set-theoretic problem, i.e. to describe
conditions during  the inductive construction of the
assigned masses $\{m_N(\nu\cdot)\}$ in order that
$\mu$ is regular.
A necessary and sufficient criterium for this regularity is not
known, i.e. this would mean that there exists a 
fully \emph{constructive}
method to achieve all Riesz measures.
So the  reader should  be aware of the fact that the
space of Riesz measures quite abstract and we remark that
it contains measures whose  existence rely upon the
Axiom of Choice.

\newpage



\centerline{\bf 2. Singular Riesz measures}
\medskip

\noindent
By the Radon Nikodym theorem
every Riesz measure $\mu$ whose total mass is finite
is the unique sum of a singular part and 
an absolutely continuous measures defined as a density by  some
$L^1({\bf{ R}}^n)$-function. 
Consider for simplicity a  measure
$\mu$ supported by the unit cube, i.e.
it is constructed via the dyadic grid on
$\square$. 
The result below gives the condition in order
that  $\mu$ is singular, i.e. its total mass taken over a set
of Lebesgue measure. 

\medskip

\noindent
{\bf 2.1 Theorem}
\emph{The measure $\mu$ is singular if and only if the following hold:
For each $\epsilon>0$ there exists an integer $N$
such that
we can find a subfamily
$\mathcal F_N= \{\square_N(\nu\cdot)\}$ of $\mathcal D_N$
where the number of cubes in
$\mathcal F_N$ is $<\epsilon\cdot 2^{Nn}$
while}
\[
\sum\,
\mu(\square_N(\nu\cdot))>1-\epsilon\quad\colon\quad
\sum\,\,\text{taken over cubes}\,\,
\square_N(\nu\cdot)\in\mathcal F_N
\]
\medskip

\noindent
{\bf Exercise.} Prove this result.




\bigskip

\centerline {\bf 3. Signed measures}.
\medskip

\noindent
A signed measure $\mu$ supported by the unit cube
arises by the inductive construction above
when we  allow that some of
the numbers $m_N(\nu\cdot)$  are negative.
In addition to additivity we  impose the condition that
\[
 \sum_\nu\, |m_N(\nu\cdot)[=1
\] 
hold for each $N$. In this case $\mu$ is again a $\sigma$-additive 
measure defined on
the Borel algebra $\mathcal B$. Moreover, by the
Hahn decomposition theorem from ¤ 2: XX
we can write
$\mu$ as difference of two non-negative Riesz measures
$\nu_1,\nu_2$ which are $\perp$ to each other.







\bigskip

\centerline{\bf 4. $\mu$-integrals.}
\medskip

\noindent
Let $\mu$ be a non-negative measure on the unit cube constructed
as above. 
Let $f(x)$ be a continuous function 
defined on the compact unit cube.
Let $M=|f|_\square$ be the maximum norm
of $|f|$ over $\square$.
The integral $\int f d\mu$ is defined
as the limit of the increasing sequence
\[
\rho_N=
\sum_{\nu=0}^{\nu=2^N-1}\,
M\cdot \nu\cdot 2^{-N}\cdot\mu(\,\nu 2^{-N}\leq f<M\cdot (\nu+1) 2^{-N}\,)
\] 
The convergence of $\{\rho_N\}$ is robust exactly as in
the abstract theory from XX.
In this way we obtain
an additive map
\[ 
f\mapsto \int\, f d\mu\tag{1}
\]
\medskip

\noindent
With  the terminology of functional analysis this means that the
$\mu$-integral yields a continuous linear form on
the normed space of continuous functions on $\square$.
The \emph{converse} is fundamental, i.e. one has


\newpage


\centerline {\bf 5. Riesz' representation theorem.}
\bigskip

\noindent
Let $\mathcal L$
be a continuous linear functional  on the Banach space
$C^0(\square)$
of real-valued continuos functions on $\square$. Using a similar procedure as in
the proof of the Hahn decomposition theorem for signed measures one shows that 
$\mathcal L$ can be written in a unique way as the difference of two
non-negative linear forms. Let us then assume that
that $\mathcal L(f)\geq 0$ for
every non-negative continuous function. If 1 is the identity number we have
the positive number
$\mathcal L(1)$ and without loss of generality we assume that
$\mathcal L(1)=1$.
Now we construct a regular  measure $\mu$
as follows: Let $\square$ be a dyadic cube in $\mathcal D_N$ for some
$N\geq 1$.
To each $0<a<1$ we get the compact cube $a\cdot\square$ and set

\[
 \mu_a(\square)=\min_f\,\mathcal L(f)\colon \quad\text{where}\quad f|a\cdot\square=1\quad\text{and}\quad
 f\geq 0\tag{i}
\]
It is clear that
$a\mapsto \mu_a(\square)$ increases with $a$ and we set

\[
\mu(\square)=\lim_{a\to 1}\, \mu_a(\square)\tag{ii}
\]
If $\square_1$ and $\square_2$ are two different dyadic cubes in
$\mathcal D_N$ we notice that the compact cubes
$a\cdot \square_1$ and
$a\cdot \square_2$ are disjoint. This observation and
the possibility to construct continuous functions
in (i) which vanish outside arbitrary small open neighborhoods of
$a\cdot \square$, imply that
(i) yields an additive function on the family of all dyadic cubes.
Moreover, by the construction via (ii) it is automatically regular.
and hence $\mu$ is a Riesz measure.
Next, let 
$E$ be a closed subset of
$\square$. One says that $E$ is a null set with respect to $\mathcal L$ if

\[
\min_f\,\mathcal L(f)=0\quad\colon\quad f|E=1\quad\colon f\geq 0
\]
This makes sense because for every $\delta>0$ one constructs 
a continuous function $f$ which is 1 on $E$ and has compact support in
its $\delta$-open neighborhood $E_\delta$.
Let us now \emph{assume} that the boundaries of all dyadic cubes
are null sets for $\mathcal L$.
This hypothesis is not restrictive since we otherwise
can use a translation of
${\bf{R}}^n$ by an $n$-tuple of numbers from
the non-denumarable set of real numbers, i.e. after such a translation
we get null sets and place the dyadic grid in the corresponding unit cube to
construct measures as in 0.X.
Under this assumption
we obtain a non-negative Riesz measure by
the following procedure: 
If $N\geq 1$ and $\square_N(\nu\cdot)$ is a dyadic cube
we define:
\medskip

\[ 
\rho_N(\nu)=
\max_f\, \mathcal L(f)\quad\colon\, 0\leq f\leq 1
\,\,\text{and has compact support in}\,\, \square_N(\nu\cdot)
\]
One verifies easily that these $\rho$-numbers satisfy the
additivity during the inductive construction as $N$ increases and hence
we obtain a Riesz measure $\mu$. Moreover, it is clear
from the whole construction that
\[
\mathcal L(f)=\int\, fd\mu\quad\colon\,f\in C^0(\square)
\]
Notice that this gives a canonical procedure to find $\mu$ when
$\mathcal L$ is given.
\bigskip

\noindent
The conclusion from this is
the following result from the original work by F. Riesz:
\medskip

\noindent
{\bf Theorem.}
\emph{Let $\Omega$ be an open set in
${\bf{R}}^n$ and 
$\mathcal L$ is a linear form
on the space $C^0_0(\Omega)$ of continuous functions with
compact support in $\Omega$. Assume also that to every
compact subset
$K$ of $\Omega$ there exists a constant $C_K$ such that}
\[
|\mathcal L(f)|\leq C_K\cdot |f|_K\quad\colon\quad
\text{Supp}(f)\subset K
\]
\emph{Then there exists a unique - in general signed - Riesz measure
$\mu$ in $\Omega$ such that}
\[
\mathcal L(f)=\int\, f\cdot d\mu\quad\colon\quad 
f\in C^0_0(\Omega)
\]


\newpage

\centerline {\bf 6. Borel measurable functions.}
\bigskip

\noindent
In many  applications one needs to integrate
functions which are not necessarily continuous.
To construct  $\mu$-integrals with
discontinuous functions as integrands we
regard the unique smallest $\sigma$-algebra of subsets of
${\bf{R}}^n$
generated by open sets.
It is denoted by $\mathcal B$
and  sets in this $\sigma$-algebra are called Borel sets.
Since a Riesz measure $\mu$ is $\sigma$-additive
and hence we can assign a measure $\mu(B)$ to every
Borel set $B$.
Next, we consider $\mathcal B$-measurable functions
$f$. It means that a real-valued function
$f$ is Borel measurable if the sets
\[ 
\{x\in{\bf{R}}^n\quad\colon\,\, f(x)<t \}\in\mathcal B\quad
\colon\text{for every real number}\,\, t\tag{*}
\]


\noindent 
Using (*) one constructs integrals $\int\, f\cdot d\mu$
exactly as in the abstract theory from Section ¤ XX.






\bigskip

\centerline {\bf 7. Weak convergence.} 
\medskip

\noindent
Consider a sequence of non-negative   measures $\{\mu_\nu\}$ where each 
measure has total mass one on $\square$. 
One says that the sequence converges weakly to a limit measure
$\mu^* $ if
\[
\lim_{\nu\to\infty}\,\int f d\mu_\nu=\int fd\mu^*
\quad\colon\,\, f\in C^0(\square)\tag{*}
\]


\noindent
{\bf 7.1 Remark.}
Suppose that the standard dyadic grid is a null set for
all
measures -$\{\mu_\nu\}$
and also for the limit measure
$\mu^*$. Then
the \emph{uniform} continuity of each 
$f\in C^0(\square)$
shows that weak convergence holds if and only if
\[
\lim_{\nu\to\infty}\, \mu_\nu(\square_N(k\cdot))=
 \mu^*(\square_N(k\cdot))\quad\colon\, N\geq 1\quad\colon
\text{for every}\,\, k(\cdot)-\text{tuple}
\]


\noindent 
Thus, weak convergence means precisely that the 
mass distributions during the inductive
partition of $\square$ into smaller dyadic cubes
give convergent sequences of
the associated real $2^N$-tuples for every $N\geq 1$.
Next, recall Bolzano's
theorem, i.e. that  every infinite sequence of real numbers on a 
bounded interval has a convergent subsequence. 
Using this and the  
"diagonal procedure" the reader may verify the following fundamental fact:
\medskip

\noindent
{\bf 7.2 Theorem.} \emph{Let $\{\mu_\nu\}$ be a sequence of 
non-negative measures on
$\square$ - each with total mass one. Then there exists at least one
subsequence which converges weakly.}
\bigskip

\noindent
{\bf{7.3 Weak density of discrete measures.}}
Among Riesz measures occur finite sums of 
point-masses.
Consider a sequence
\[ \mu_j=\sum\, c_{j,k}\cdot x_k\quad\colon\,j=1,2,\ldots
\]
where $\{x_1,x_2, \ldots\}$ is a denumarable sequence of points in
the unit cube
$\square$.  At  the same time each $\mu_j$
is a probability measure, i.e.
\[ 
\sum_j\, c_{j,k}=1\quad\colon\, k=1,2,\ldots
\]
The condition for the sequence to converge weakly is now
easy to check.
Namely, to every $N\geq 1$ and every cube
$\square_N(\nu\dot)$ in $\mathcal D_N$
we have
\[ 
\mu_j(\square_N(\nu\cdot))=\sum_*\, c_{j,k}\,\quad\colon
\text{sum taken over those}\,\, k\,\,\text{with}\,\, x_k\in\square_N(\nu\cdot)
\]


\noindent
So above  weak convergence holds if and only if
these numbers have a limit as $j\to\infty$ for
every $N\geq 1$ and every cube in $\mathcal D_N$.
Expanding each $x_k$ in the binary system
one can proceed to get an understanding when
such a weak convergence takes place.
Notice that if the sequence $\{x_k\}$ is given from the start
then there may exist many doubly indexed 
$c$-sequences where we get a weak limit and moreover one may attain
different limit measures depending on the chosen
$c$-sequence.
This occurs in particular when the sequence
$\{x_k\}$ is everywhere dense. For example, if one has enumarated
points in
the unit cube whose coordinates are all rational numbers.
In this
situation every probability measure on $\square$ is the weak
limit of a sequence $\{\mu_j\}$.

\medskip


\noindent 
{\bf{7.4 Exercise.}}
Show that if $\mu$ is a Riesz measure with compact support then
it can be approximaed weakly by a sequence of discrete measures.



\bigskip



\centerline
{\bf 8. Products and convolution of Riesz measures}

\bigskip

\noindent
Let $n$ and $m$ be two positive integers and
$\mu$ and $\nu$ are Riesz measures
in ${\bf{R}}^n$ and
${\bf{R}}^m$ respectively.
The family of dyadic cubes in ${\bf{R}}^{n+m}$
is   obtained  by  products of
cubes from grids in ${\bf{R}}^n$ and ${\bf{R}}^m$.
This gives a unique 
product measure
$\mu\times\nu$ which
satisfies
\[
(\mu\times\nu)(\Omega\times U)=
\mu(\Omega)\cdot \nu(U)
\]
where $\Omega\subset{\bf{R}}^n$ and
$U\subset {\bf{R}}^n$ are open sets.
\medskip

\noindent
{\bf 8.1 Projections of measures.}
Let $\gamma$ be a measure in
${\bf{R}}^{n+m}$
where the coordinates are $(x,y)$ with
$x\in{\bf{R}}^n$ and $y\in {\bf{R}}^m$.
We have the projection from
${\bf{R}}^{n+m}$ onto ${\bf{R}}^n$ defined by
\[ 
\pi(x,y)=x
\]
Assume  that
$\gamma$ has a finite total mass which gives
a measure
$\pi_*(\gamma)$ in
${\bf{R}}^n$ defined on Borel sets $F$
by
\[
\pi_*(\gamma)(F)=\gamma(F\times{\bf{R}}^m)\tag{*}
\]


\noindent
One refers to $\gamma_*$ as the direct image measure.

\medskip

\noindent
{\bf 8.2 Convolution.} Let $\mu,\nu$ be a pair of measures in
${\bf{R}}^n$. We get the product measure
$\mu\times\nu$ in
${\bf{R}}^{2n}$ whose points are denoted by
$(x,y)$ where
we regard
$\mu$ as a measure in the $n$-dimensional $x$-space and
$\nu$ as a measure in the $y$-space.
In ${\bf{R}}^{2n}$ we  take  coordinates
$(t,s)$ where
\[ 
t_\nu=x_\nu+y_\nu\quad\colon\quad
s_\nu=x_\nu-y_\nu
\]
Now  $\mu\times\nu$ is a measure in the
$(t,s)$ space and   the projection
$\pi(t,s)=t$  gives the measure
\[
\pi_\ast(\mu\times\nu)
\]
It is denoted by $\mu*\nu$ 
and called the convolution of
$\mu$ and $\nu$.
If $f(t)$ is a continuous function with compact
support in the $t$-space the constructions of
$\pi_\ast(\mu\times\nu)$ and 
$\mu\times\nu$ give
\[
\int\, f(t)\cdot d(\mu*\nu)(t)=\iint f(x+y)d\mu(x)d\nu(y)\tag{*}
\]
\medskip

\noindent
{\bf Remark.}
The last integral is symmetric with respect to $\mu$ and $\nu$.
Hence the convolution satisfies the commutative law:
\[
 \mu*\nu=\nu*\mu
\]
\medskip

\noindent
One can  continue  and construct the convolution of
a triple of measures, and more generally the convolution of
any number of measures in ${\bf{R}}^n$.
For example, if $\mu,\nu,\gamma$ is a triple of measures
in
${\bf{R}}^n$ then
we get the measure
defined by
\[
\int_{{\bf{R}}^n}\, f(t)\cdot d(\mu*\nu*\gamma)=
\iiint\, f(x+y+z)\cdot d\mu(x)d\nu(y)d\gamma(z)
\]
\medskip

\noindent
{\bf 8.3 Exercise.}
Show that the
convolution satisfies
the associative law.
So if $M({\bf{R}}^n)$ denotes the space of Riesz
measures with finite total variation, then convolution
equips it with
a commutative product, i.e.
$M({\bf{R}}^n)$  becomes a commutative algebra. 
The multiplicative unit is the point mass at
the origin.
One has also the inequality for norms:
\[
||\mu*\nu||\leq ||\mu||\cdot ||\nu||
\]
i.e. the total mass of a convolution is at most the product of
the individual total masses.
\bigskip

\noindent
{\bf 8.4 Example.}
Let $E$ and $F$ be two compact sets
in ${\bf{R}}^n$, each with a positive Lebesgue measure.
We get the new compact set
defined by
\[
E+F=\{ x+y\quad\colon\quad x\in E\quad\colon y\in F\}
\]
Next, the two characteristic functions
$\chi_E$ and $\chi_F$ define measures where
\[
\int\, f\cdot d\chi_E=\int_E\, f\cdot dx\quad\colon\quad
\int\, f\cdot d\chi_F=\int_F\, f\cdot dx
\]
The construction of the convolution shows that
\[
\chi_E*\chi_F= \chi_{E+F}
\]
\medskip

\noindent
{\bf 8.5 Exercise.}
Let $\mu$ be the discrete measure on the real line
which has mass $1/2$ at $x=0$ and at $x=1$.
Let $N\geq 2$ be an integer and consider the
$N$-fold convolution $\mu^N$.
Show that this is a discrete measure supported by
the integers $0,1,\ldots,N$ and the mass at
$0\leq k\leq N$ is given by
$2^{-N}\cdot \binom Nk$.
\medskip

\noindent
{\bf 8.6 Exercise.}
Let $n=2$ and $\mu$
is the Riesz measure 
supported by the unit circle $\{x^2+y^2=1\}$
where it is given by the constant angular measure, i.e.
if $f(x,y)$ is a continuous function then
\[
\int\, f\cdot d\mu=\frac{1}{2\pi}\cdot \int_0^{2\pi}
f(\cos\theta,\sin\theta)\cdot d\theta
\]
Consider the convolution of $\mu$ with itself, i.e.  the Riesz measure
$\nu=\mu*\mu$.
By (8.5) the support is $T+T$, i.e. the set of points $(x,y)$ of the form
\[
x=\cos\theta+\cos\phi\quad\colon\,
y=\sin\theta+\sin\phi
\]
The reader is invited to
find the picture of this set and try to investigate the resulting
measure.
One gateway for this is to employ Fourier transforms.
First one has
\[ 
\widehat{\mu}(\xi,\eta)=
\int_0^{2\pi}\, e^{-i\xi\cos\theta-i\eta\sin\theta}\,d\theta
\]
We use polar coordinates in the $(\xi,\eta)$-space.
With $\xi=r\cos\phi$ and $\eta=r\sin\phi$
the addition formula for the cosine function shows that the
integral becomes
\[
\int_0^{2\pi}\, e^{-ir\cdot \cos(\theta-\phi)}\,d\theta\tag{i}
\]
Since the cosine function is periodic (i)  depends
on $r$ only and expressed by the function
\[
r\mapsto \int_0^{2\pi}\, e^{-ir\cdot \cos \theta}\,d\theta\tag{ii}
\]
As explained in the chapter devoted to distribution theory
the Fourier transform of $\mu*\mu$ is $\widehat{\mu}^2$
which entails that it is a function of $r$ only.
Via Fourier's inversion formula it follows that
the measure $\mu*\mu$ is invariant under rotations.
By (xx) it is supported by a disc of radius $2$ centered at the origin
and determined by the function
\[
\phi(s)=(\mu*\mu)(\{x^2+y^2\leq s^2\})\quad\colon 0\leq s\leq 2\tag{iii}
\]
The precise expression  of this $\phi$-function
is not so easy. See ¤ xx for a further account which involves
the construction of certain Bessel functions.
This iilustrates that the passage to convolutions  can  lead to quite
cumbersome computations.














\newpage

\centerline{\bf 5. Stokes Theorem}
\bigskip


\noindent 
Consider a bounded and connected open set $\Omega$ in $\bf R^n$.
Its boundary $\partial\Omega$ is  compact but we do no assume that 
$\partial\Omega$  is
connected.
A boundary point $p$ is  \emph{regular}
if there exists some open ball $B$ centered at $p$ and a real-valued
$C^1$-function $\phi$ in $B$ such that
\[
\Omega\cap\,B=\{\phi<0\}\quad\colon\,
\partial \Omega\cap\,B=\{\phi=0\}\quad\colon\nabla(\phi)\neq 0
\]
It is clear that the set of regular boundary points is a relatively open
subset of $\partial\Omega$. Denote this set by
$\mathfrak{reg}(\partial\Omega)$.
Put
\[ 
K=\partial\Omega\setminus\mathfrak{reg}(\partial\Omega)\tag{1}
\]


\noindent
We impose the condition that $K$ has Hausdorff measure zero in dimension $n-1$.
Next there exists the area measure
on $\mathfrak{reg}(\partial\Omega)$ to be denoted by 
$dS$ which  
is found locally as follows:
Let $p$ be a regular boundary point
and assume that the partial derivative
$\frac{\partial\phi}{\partial x_n}\neq 0$ at $p$.
The implicit function theorem gives
an open neighborhood $U$ of $p$ where
\[
\phi(p+x)=(x_n-a(x'))\cdot \rho(x)
\]
for a pair of real-valued $c^1$-functions $a$ and $\rho$. Here
$\rho>0$ in $U$ and
\[
\Omega\cap U=\{x_n<a(x')\}
\]
where $a$ only depends on $x'=(x_1,\ldots,x_{n-1})$ 
and $a=$ when $x'=0$.
So locally one has 
\[
\partial\Omega\cap U=\{x_n=a(x')\}\tag{i}
\]
We can choose $U$ so that
(i) holds while $x'$ varies in a small open cube $\square$
centered at the origin in
this $(n-1)$-dimensional space.
By  a wellknown result in calculus
which follows from the theorem  of Pythagoras, the $(n-1)$-dimensional area
of
$\partial\Omega\cap U$ is given by
the integral
\[ 
\int_\square\, \sqrt{1+|\nabla(a)(x')|^2}\, dx'\tag{ii}
\]
where
\[
|\nabla(a)(x')|^2=\sum_{j=1}^{j=n-1}\,
(\frac{\partial a}{\partial x_j})^2
\]
The reader may verify that
(ii) can be written as
\[ 
\int_\square\,\frac{1}{|\frac{\partial \phi}{\partial x_n}|}\cdot
|\nabla(\phi)|\, dx'\tag{xx}
\]
where the partial derivatives of $\phi$ are evaluated at
$x=(x',a(x')$ during the integration over
$\square$.
\medskip

\noindent
{\bf{5.0 Definition.}}
\emph{
The domain $\Omega$ is of Federer type
if the Hausdorff measure $|K|_{n-1}=0$ and the
the total area}
\[ 
\int_{\text{reg}(\partial\Omega)}\, dS<\infty\tag{*}
\]
\medskip


\noindent
{\bf 5.1 Theorem.} \emph{Let $\Omega$ be a domain of the Federer type
and $f(x)$  a function of class $C^1$
defined in some open neighborhood of
the
closure
$\bar \Omega$. Then }
\[ 
\int_\Omega\,\partial f/\partial x_j\cdot dx=
\int_{\text{reg}(\partial\Omega)}\, f\cdot\mathfrak n_j\cdot dS
\quad\colon\quad 1\leq j\leq n
\]
\emph{where $\mathfrak n_j$ is the $x_j$ component of 
the outer normal $\mathfrak n$.}
\bigskip

\noindent
The proof requires several steps and we begin with a
case where the "ugly set" $K$ is empty.

\medskip

\noindent
{\bf{5.2 The case of 
graphic domains}}.
Consider an open cube of the form
\[ \square=\{x\colon
-A\leq x_\nu<A\colon\, \nu=1,\ldots,n\}
\]
Put $x'=(x_1,\ldots,x_{n-1}$ and
let $\phi(x')$ be a $C^1$ function
defined on the cube 
\[
\square_*=\{ -A<x_\nu<A\colon \nu=1,\ldots,n-1\}
\]
Here $-A<\phi(x')<A$ is assumed which gives  the graphic domain
\medskip
\[
\Omega=\{(x',x_n)\colon\, -A<x_n<\phi(x')\quad\colon\tag{1}
x'\in\square_*\}
\]

\noindent
Next,
let $f(x)$ be a $C^1$-function
with compact support in
$\square$.
Then we shall prove that
\[
\int_\Omega\,\partial f/\partial x_j\, dx=
\int_{\partial\Omega)}\, f\cdot\mathfrak n_j\cdot dS
\quad\colon\quad 1\leq j\leq n\tag{*}
\]
\medskip

\noindent
If $j=n$  the volume integral is 
equal to the repeated integral
\[ 
\int_{\square_*}\bigl [\int_{-A}^{\phi(x')}\, \partial f(x',x_n)/
\partial x_n\cdot dx_n\bigr ]\, dx'=
\int_{\square_*}\,f(x',\phi(x')\,dx'\tag{1}
\]

\noindent
Now $dx'=\mathfrak{n_n}\cdot dS$  on
the part of $\partial\Omega$ defined by $x_n=\phi(x')$.
Moreover, since $f$ has compact support in
$\square$ it vanishes on the remaining boundary of
$\partial\Omega$ where at least some $|x_j|=A$.
From this it is clear that (*) holds if $j=n$
\medskip

\noindent
{\bf{The case $1\leq j\leq n-1$}}. We may assume that
 $j=1$ to simplify  the notations. Set
\[
\psi(x')=\int_{-A}^{\phi(x')}\, f(x',s) ds
\]
Partial integration with respect to $x_1$ gives
\[
\partial \psi/\partial x_1(x')=
f(x',\phi(x'))\cdot\partial \phi/\partial x_1(x')+
\int_{-A}^{\phi(x')}\, \partial f/\partial x_1(x',s) \,ds\tag{i}
\]
Now we integrate over $\square_*$. Since
the $\psi$-function is zero when $|x_1|=A$ we have trivially
\[
\int_{\square_*}\, \partial\psi/\partial x_1(x')dx'=0\tag{ii}
\]
In the right hand side of (i)
the second term
yields the repeated integral
\[
\int_{\square_*}\,\bigl [\int_{-A}^{\phi(x')}\, 
\partial f/\partial x_1(x',s) \cdot ds\bigr ]\,\cdot dx'=\int_\Omega\, 
\partial f/\partial x_1(x)\,dx
\]
So the vanisihing of (ii) entails that  this volume integral is equal to
\[
-\int_{\square_*}\,
f(x',\phi(x'))\cdot\partial \phi/\partial x_1(x')\cdot dx'
\]


\noindent 
Next, on the part of $\partial\Omega$ defined by $\{x_n-\phi(x')=0\}$
one has the equality
\[
\mathfrak{n_1}\cdot dS=-
\partial \phi/\partial x_1(x')\cdot dx'
\] 
Hence  (*) holds
with $j=1$ and the case
$2\leq j\leq n-1$ is treated in the same way
which  finishes the proof of (*).


\bigskip

\noindent
{\bf 5.3. Using partition of the unity}
Consider the situation in Theorem 1 and   impose the extra 
assumption that $f=0$ in an open  neighborhood $U$
of the ugly set $K$.
In this case the result in  5.2  gives Theorem 5.1 after a  partition of the unity.
Namely, the compact set
$W=\partial\Omega\setminus U$ is contained in
$\mathfrak{reg}(\partial\Omega)$ and 
for each  $p\in W$ there exists a cube
$\square$ centered at $p$
such that $\square\cap\Omega$ is a graphic domain.
By Heine-Borel's Lemma we can cover $W$ by a finite set of such cubes, say
$\square_1,\ldots,\square_M$.
Finally we can cover the compact set
$\Omega\setminus U\cup\square_1\cup\ldots\cup\square_M$
by a finite set of cubes $\square_{M+1},\ldots,\square_{M+N}$
where the closure of these cubes are contained in $\Omega$.
Then we construct a $C^\infty$-partition of the unity, i.e. we find
a family $\{\phi_\nu\in C_0^\infty(\square_\nu)\}$
so that $\sum\,\phi_\nu=1$ holds in a neighborhood of
the support of $f$.
Now  Stokes formula from (1.2)  hold for every function
$f\cdot \phi_\nu$ and by adding the result we get
Stokes formula for $f$ in Theorem 5.1.
\newpage


\centerline {\bf 5.4 How to avoid $K$}
\medskip

\noindent
Consider the general case with  no assumption on  the support of  $f$.
To prove the integral  formula in Theorem 5.1 for each $x_j$
we can 
without loss of generality  take $j=n$.
Let
$\pi(x',x_n)=x'$ be the projection to the
$n-1$-dimensional $x'$-space. The assumption that $|K|_{n-1}=0$
entails that 
the image set $\pi(K)$ is  a null set in  the $(n-1)$-dimensional $x'$-space.
Let  $\phi_1(x'),\phi_2(x'),\ldots$
be a sequence of test-functions in ${\bf{R}}^{n-1}$
which converge almost everywhere to 1 outside
$\pi(K)$, while  each of them has compact 
support in ${\bf{R}}^{n-1}\setminus K$ and 
$0\leq\phi_\nu\leq1 $ hold for every $\nu$.
\medskip

\noindent
By (5.3)  Stokes Formula holds for every function 
$\phi_\nu f$. Since the functions $\{\phi_\nu(x')\} $ are independent of $x_n$
we get
\[
\int_\Omega\, \phi_\nu\cdot\partial_n(f)\cdot dx=
\int_{\mathfrak{reg}(\partial\Omega)}\, \phi_\nu\cdot f\cdot \mathfrak{n}_n\cdot dS\tag{5.4.1}
\]
\medskip

\noindent
Since $\phi_\nu\to 1$ holds almost everywhere in
the $x'$-space, Lebesgue's dominated convergence
theorem implies that the left hand side in (5.4.1) tends to the volume
integral of $\partial_n(f)$.
There remains to prove that the right hand side tends
to the integral of $f\cdot\mathfrak{n}_n$ 
taken over the  regular boundary.
Since $f$  is a bounded function and the total area is finite
the requested limit  this follows if
we have proved:
\[
\lim_{\nu\to\infty}\,
\int_{\mathfrak{reg}\partial\Omega)}\, (1-\phi_\nu)\cdot  \mathfrak{n}_n\cdot dS=0\tag{5.4.2}
\]


\noindent
To prove (5.4.2) we let $\epsilon>0$ and put
\[ 
\Gamma_\epsilon=
\{|\mathfrak{n}_n|\geq\epsilon\}\,\cap\, \mathfrak{reg}(\partial\Omega)
\]


\noindent
Set  $M=\text{Area}\,[\mathfrak{reg}(\partial\Omega)]$. Without loss of generality we
can assume that the maximum norm of $f$ is $\leq 1$.
Then (5.4.2) is majorized by
\[
M\cdot\epsilon+
\int_{\Gamma_\epsilon}\, (1-\phi_\nu)\cdot  \mathfrak{n}_n\cdot dS=0\tag{5.4.3}
\]




\noindent
Next, on $\Gamma_\epsilon$ the area measure
$dS$ is majorized by
$\frac{1}{\epsilon}\cdot dx'$.
Hence  the sequence $\{g_\nu=1-\phi_\nu\}$ regarded as functions on
the measure space
$(\Gamma_\epsilon\,;\,dS)$ converge almost everywhere to zero which gives
\[
\lim_{\nu\to\infty}\, \int_{\Gamma_\epsilon}\, (1-\phi_\nu)\cdot  \mathfrak{n}_n\cdot dS=0\tag{5.4.4}
\]
\medskip

\noindent
In particular we can take $\nu$ so large that (5.4.4) is $<\epsilon$. Since
$\epsilon$ was arbitrary  the limit formula (5.4.2) holds
and the proof of Theorem 5.1 is finished.
\medskip


\noindent
{\bf{5.5 Remarks about   Federer domains.}}
Suppose that $f$ is a non-negative $C^2$-function and
the bounded domain $\Omega$ is defined by
$\{f<a\}$ for a pair of real constants $a>0$.
To each $1\leq j\leq n$ we set $\partial_j(f)=
\frac{\partial f}{\partial x_j}$.
On the regular part of $\partial\Omega$
the outer normal
\[ 
{\bf{n}}_j=\frac{\partial_j(f)}{|\nabla(f)|}
\]
Let us assume that
$\nabla(f)\neq 0$ in $\Omega$.
So for ech $1\leq j\leq n$
there exists the $C^1$-function in $\Omega$ defined by
\[ 
g_j=\frac{\partial_j(f)}{|\nabla(f)|}
\]
If $\delta>0$ is small we have the domain
$\Omega(\delta)= \{f<a-\delta\}$ 
and  Stokes theorem gives
\[
\int_{\Omega(\delta)}\, \partial_j(g_j)\,dx=
\int_{\partial \Omega(\delta)}\, g_j\cdot {\bf{n}}_j\cdot dS
\quad\colon \,1\leq j\leq n
\]
By (xx) it follows that
\[
\sum_{j=1]}^{j=n}
\int_{\Omega(\delta)}\, \partial_j(g_j)\,dx=
\, \int_{\partial \Omega(\delta)}\, dS
\]
If $\Omega$ is a Federer domain one expects that
there is a limit formula
\[
\lim_{\delta\to 0}\,  \int_{\partial \Omega(\delta)}\, dS=
 \int_{\text{reg}(\partial \Omega)}\, dS
\]
\medskip

\noindent
The passage to the limit can be
understood via distribution theory.
For each $\delta>0$ we denote by $\chi_\delta$ the characteristic function of
the open det
$\Omega(\delta)$.
At the same time
$\{g_j\}$ are bounded funtions in
$\Omega$ and the defintion of distribution derivatives entail
that
\[
\frac{\partial \chi_\delta}{\partial x_j}(g_j)=
-\int_{\Omega(\delta)}\, \partial_j(g_j)\,dx
\]
So (xx) means that
\[
\sum\, \frac{\partial \chi_\delta}{\partial x_j}(g_j)=\text{vol}_{n-1}(\partial \Omega(\delta))
\]
At the same time the distributions $\{\chi_\delta\}$
converge
to the distribution defined by the characteristic function of
$\Omega$. Indeed,  this is so because the $n$-dimensional Lebesgue measure of
$\Omega\setminus \Omega(\delta)$ tends to zero.
Passing to distribution derivatives it follows that
\[
\lim_{\delta\to 0}\,
\frac{\partial \chi_\delta}{\partial x_j}=
\frac{\partial \chi_\Omega}{\partial x_j}
\]
But this weak limit in the space of distributions
need not impliy that evaluations on
the bounded $g$-functions give a limit since they
need not
extend so nicely to the closure of $\Omega$
where the gradient vector of $f$ may vanish at some points.
This illustrates  why the conditions in Theorem 5.2 are essential.
\medskip

\noindent
{\bf{The polynomial case.}}
A case of special interest occurs when 
$f(x)$ is a real-valued polynomial. By Sard's Lemma the
set of critical values is sparse
and situations as above arise when we in addition assume that
the polynomial is hyper-elliptic, i.e when
\[ 
\lim_{|x|\to+\infty}\, |f(x)|=+\infty
\]
In this situation the boundsries
of $\{f<a\}$ are smooth excpet for a finite set of positive numbers
and it turnd out that
they become Federer domains.
However, this cannot be deduced by pure measure theoretic arguments.
One must
use a more refined analysis to
profit upon the hypothesis that $f$ is a polynomial. It would lead us too 
far to discuss this in more detail.
Let us only mention that
the assertion that
we get Federer domains rely upon
the study of semi-algebraic sets, i.e. here one empoys
the Seidenberg-Tarski theorem and also certain straitfications and
a geometric integration theory developed in Whitney's very interesting text-book
\emph{Geometric integration theory}.
So even if Theorem 5.1 is quite general the reader should be aware of the fact
that
extra work often is needed to verify that a 
specific domain is of the Federer type.
More generally domains arising as real-analytic polyhedra
satisfy the Federer condition and
this leads to general Stokes formulas while
currents are integrated on so called semi-analytic sets in arbitrary
real-analytic manifolds.
Here inequalities due to Lojasievicz are used. But it would bring us to
far to
discuss this in more detail.


























\newpage



\centerline {\bf {6. The Hardy-Littlewood maximal function}}.
\bigskip

\noindent
Let $f$ be a non-negative  $L^1$-function on the real line
supported by $x\geq 0$.
Its forward maximal function is defined by


\noindent
\[
f^*(x)=\max_{h>0}\,\frac{1}{h}\int_x^{x+h}\, f(t) dt
\]


\noindent 
Above it  suffices to
seek the maximum when $h$ runs over  positive rational numbers
which we enumerate as $\{q_\nu\}$. For a fixed $\nu$ we have a continuous
function
\[
g_\nu(x)=\frac{1}{q_\nu}\int_x^{x+q_\nu}\, f(t) dt
\] 
Hence  $f^*(x)$ is the maximum of 
$\{g_\nu\}$ which implies that
$f^*$
is 
\emph{lower semi-continuous}.
So if  $\lambda>0$ we get the open set:
\medskip

\noindent
\[
E(\lambda)=\{x\,\colon\, f^*(x)>\lambda\}
\]


\noindent
{\bf 6.1. Theorem}
\emph{One has the inequality}
\[ 
\text{meas}\,E(\lambda)\leq
\frac{1}{\lambda}\cdot\int_{E(\lambda)}\, f(x)dx
\]

\medskip

\noindent \emph{Proof.}
With  $g(x)=\frac{f(x)}{\lambda}$ we put
$E_g=\{ g^*>1\}$ and there remains to 
show that :
\[
\text{meas}(E_g)\leq\int_{E_g}\, g(x)dx
\tag{1}
\]
To get (1)  we consider the primitive function
\[ 
G(x)=\int_0^x\,g(t)dt\tag {2}
\]
It is non-decreasing and continuous. Let $\{(a_\nu,b_\nu)\}$
be the disjoint intervals of $E_g$. 
\medskip

\noindent
\emph{Sublemma.} For each $\nu$ one has
\[
 G(b_\nu)-G(a_\nu)\geq b_\nu-a_\nu
\]
\medskip

\noindent \emph{Proof.}
Suppose strict inequality holds. By continuity we find
$x>a_\nu$ with $x-a_\nu$ small so that
\[ 
G(b_\nu)-G(x)<b_\nu-x
\]
Next, since $x\in E_g$ there exists $\xi>x$ such that
\[ 
G(\xi)-G(x)>\xi-x
\]
Then $b_\nu<\xi$ must hold. On the other hand, since
$b_\nu$ is a boundary point of $E_g$ we also have
\[ 
G(\xi)-G(b_\nu)\leq\xi-b_\nu
\]
Now we get a contradiction since it would follows that
\[ 
G(\xi)-G(x)= G(\xi)-G(b_\nu)+G(b_\nu)-G(x)
<\xi-b_\nu+b_\nu-x=\xi-x
\]
\medskip

\noindent
\emph{Proof continued.}
Since the intervals $(a_\nu,b_\nu)$ are disjoint we get

\[ 
\int _{E_g}\,g dt=
\sum\int_{a_\nu}^{b_\nu}\,g dt=
\sum\, G(b_\nu)-G(a_\nu)
\]
By the Sublemma the last sum is $\geq\sum(b_\nu-a_\nu)$
which is equal to $\text{meas}(E_g)$ and Theorem 6.1 is proved.




\medskip


\noindent
{\bf  {An $L^2$-inequality}}. 
If $x$ is a Lebesgue point of $f$ we have
the inequality
$f^*(x)\geq f(x)$. Using Theorem 1 we shall now
establish an inequality for $L^2$-norms. 
\medskip

\noindent 
{\bf 6.2. Theorem} \emph{For every square integrable function
$f(x)$ supported  $x\geq 0$
one has the inequality}
\[ 
||f^*||_2\leq 2\cdot ||f||_2
\]
\emph{where $||\cdot||_2$ denotes the $L^2$-norm.}
\bigskip

\noindent
\emph{Proof.}
Since we claim an a priori inequality it suffices to prove the
result when $f(x)$ is bounded and has compact support.
Let $N$ be a positive integer which  eventually will be very large.
Keeping $N$ fixed we set
\[ 
E(\nu)=\{\frac{\nu}{N}\leq f^*<\frac{\nu+1}{N}\}
\quad\colon\quad\nu=0,1,\ldots
\]
Set
\[ 
f_-^*=\sum\,\frac{\nu}{N}\cdot\chi_{E(\nu)}\quad\colon\quad
f_+^*=\sum\,\frac{\nu+1}{N}\cdot\chi_{E(\nu)}
\]

\noindent 
\emph{Sublemma} For each $N\geq 1$ we have
\[
\int_0^\infty\, (f_-^*(x))^2dx\leq 2\cdot \int_0^\infty\, f_+^*(x)\cdot f(x)\,dx
\]
\medskip

\noindent
\emph{Proof of Sublemma}
Set $E_\nu=\{ f^*>\frac{\nu}{N}\}$.
The left hand side is equal to
\[ 
\sum_{\nu\geq 0}\,
\frac{\nu^2}{N^2}\cdot(\,|E_\nu|-|E_{\nu+1}|\,)=
\sum_{\nu\geq 0}\,
\frac{1}{N^2}\cdot\,|E_\nu|\cdot(\nu^2-(\nu-1)^2)\leq
\sum_{\nu\geq 0}\frac{2\nu}{N^2}\cdot |E_\nu|
\]
\medskip

\noindent
By Theorem 6.1 the last sum is majorized by
\[
\sum_{\nu\geq 0}\,\frac{2}{N}\int_{E_\nu} f dt=
\sum_{\nu\geq 0}\,\frac{2(\nu+1)}{N}\int_{E(\nu)}\, fdt
\]
By the construction of $f^*_+$ the last sum is
$2\int\, f^*_+(x)\cdot f dx$ and the Sublemma is proved.
\bigskip

\noindent
\emph{Proof continued.}
The Cauchy-Schwarz inequality for $L^2$-norms gives:
\[
\int\, f^*_+(x)\cdot f \,dx\leq ||f^*_+||_2\cdot ||f||_2
\]
Hence the Sublemma gives
\[
||f^*_-||^2_2\leq 2\cdot
 ||f^*_+||_2\cdot ||f||_2
\]
Theorem 1 follows since the $L^2$-norms of $f^*_+$ and $f^*_-$
both tend to $||f^*||_2$ when $N$ increases.
\bigskip

\noindent {\bf Remark.}
The proof of the $L^2$-inequality  extends easily  to 
$L^p$ inequalities when $1<p<1$ where
the constant $2$ is replaced by
$\frac{p}{p-1}$.
In Theorem 1 we regarded the
forward maximum function. One can  also 
define the backward maximum function and 
without any restriction on the support of an $L^2$-function 
$f$ on the $x$-line its full maximal function 
\[
f^{**}(x)=\text{max}_{\xi,\eta}\,\,
\frac{1}{\xi+\eta}\int_{x-\eta}^{x+\xi}\, f(t) dt
\]
with the maximum taken over all pairs of positive numbers
$\xi,\eta$. Then
Theorem 6.2 gives:
\[
||f^{**}||_2\leq 4\cdot ||f||_2
\]



\newpage














\centerline
{\bf {7. Rademacher functions} }

\bigskip

\noindent
For each positive integer $N$
the  interval $[0,1)$ can be 
decomposed into half-open intervals
\[
\Delta_N(\nu)=[\nu2^{-N},\nu+1)2^{-N})\quad\colon\quad 0\leq
\nu\leq 2^N-1
\]
Define the function $R_N(x)$ by
\[ 
R_N(x)=(-1)^\nu\quad\colon\quad x\in \Delta_N(\nu)
\]
This construction applies to each $N\geq 1$ and it is clear that
\[
\int_{\Delta_N(\nu)}\, R_M(x)dx=0\quad\colon\quad
0\leq\nu<2^N-1\quad\colon\, M>N
\]
It follows easily that
\[ 
\int_0^1\, R_N(x)\cdot R_M(x)dx=0\quad\colon\quad M\neq N
\]
Next, let $\{\alpha_\nu\}$ be a sequence in $\ell^2$, i.e.
$\sum\,|\alpha_\nu|^2<\infty$ and
consider the partial sum functions
\[ 
S_N(x)=\sum_{\nu=1}^{\nu=N}\, \alpha_\nu\cdot R_\nu(x)
\]
We shall analyze the limit  as $N\to\infty$ using
expansions of real numbers in the binary system.
That is, when $0<x<1$ we have a series expansion
\[
x=\epsilon_1(x) 2^{-1}+\epsilon_2(x) 2^{-2}+\ldots\quad\colon\quad
\epsilon_\nu(x)=1\,\,\text{or}\,\, 0.
\]
The expansion is unique unless $2^Nx$ is an integer for some $N$.
Ignoring this denumerable set we define for each $x$ the partial sum
of its binary expansion
\[ 
\xi_N(x)=\sum_{\nu=1}^{\nu=N}\,\epsilon_\nu(x)\cdot 2^{-\nu}
\]
So here $\xi_N(x)\leq x<\xi_N(x)+2^{-N}$ and
with these notations  the following hold for the given
$\ell^2$-sequence above:
'\medskip

\noindent {\bf 7.1. Proposition} \emph{For each $x$ and $N\geq 1$ one has
the equality}
\[ 
S_N(x)=\sum_{\nu=1}^{\nu=N}\, (2\epsilon_\nu(x)-1)\cdot\alpha_\nu
\]


\noindent
The straightforward proof is left to the reader. Now we announce
\medskip

\noindent {\bf 7.2. Theorem}
\emph{For each sequence $\{\alpha_\nu\}$ in $\ell^2$ there exists a null set $E$
in $\{0\leq x\leq 1\}$
such that one has a
pointwise limit when $x$ is outside $E$:}
\[
\lim_{N\to\infty}\,
S_N(x)=\sum_{\nu=1}^\infty\,(2\cdot \epsilon_\nu(x)-1)\cdot\alpha_\nu
\]
\medskip

\noindent 
\emph{Proof.}
Since the $R$-functions is an orthonormal family in
$L^2[0,1]$ we have
\[
\int_0^1 S_N(x)^2dx=\sum_{\nu=1}^{\nu=N}
\,\alpha_\nu^2\quad\colon\quad N\geq 1
\]
It follows that $\{S_N\}$ is a Cauchy sequence in $L^2[0,1]$ and 
hence it converges in the $L^2$-norm to a limit function $S(x)$.
Let $\mathcal L(S)$ be the set of Lebesgue points for $S$.
If $x\in\mathcal L(x)$ we have
\[
S(x)=\lim_{N\to\infty}\,
\int_{\xi_N(x)}^{\xi_N(x)+2^{-N}}\, S(t) dt
\]
From the construction of the partial sum functions it follows that
$\lim\, S_N(x)=S(x)$, i.e.  the  pointwise limit exists
at each Lebesgue point of $S$. Theorem 7.2. follows
since $(0,1)\setminus\mathcal L(S)$ is a null set.



\newpage

\centerline{\bf\large 8. The Brownian motion}

\bigskip


\noindent
{\bf Introduction.} Inspired by P.J. Daniell's work  [DA] which fascilated previous
results about  infinite products of measure spaces, 
Norbert Wiener gave a rigorous  construction of
a stochastic process $\mathcal W$ in continuous time 
with the following properties: For each
$t>0$ one has a normally distributed random variable $W_t$ whose variance is $t$
and  $\{W_t\}$
have independent increments, i.e if $s<t$ then the random variables
$W_t-W_s$ and $W_s$ are independent. Wiener employed 
Fourier series to construct such a process
whose
sample space is a
\emph{denumerable} product of ${\bf{R}}$. 
The book
[Pa-Wi]   contains
an interesting historic account about the role of the
Browninan motion outside the
"abstract world of mathematics".
Here we add some further comments.
\medskip

\noindent
Albert Einstein's  first scientific paper was published in december 1900.
It
contains a statistical analysis of experimental data from phenomenon
of capillarity and shows that Einstein    already during the early
period
of his career  was familiar 
with  statistical arguments.
Five years later it led to his articles [XX] which
justified the existence of atoms
and made it possible to determine the Avogrado number.
After Einstein's work  many skilled experimental
scientists used stochastic analysis
based upon the Brownian motion. Among those who 
applied Einstein's recipe was
Theo Svedberg  who received
the Nobel Prize in chemistry in 1925 (6 ?).
The interested reader may  consult the 
book \emph{Atoms} by Jean Perrin [Per]
which gives a fascinating description of the nature of
Brownian motion and describes   experiments
which predict that individual paths
are non-differentiable.


\medskip

\noindent
{\bf{8.0 Wiener's construction.}}
The first rigouros proof that
almost every Brownian path is continuous and even
has a certain Hšlder continuity is due to Wiener who
used random Fourier series expansions of sine-functions.
In general, let
$\{a_k\}$ be sequence of real numbers
such that $\sum\, a_k^2<\infty$.
Next, $\{\rho_1,\rho_2,\ldots\}$
is a sequence of independent normally distributed variables, i.e. each
$\rho_k$ has mean-value zero and variance one.
With $t$   regarded as a time parameter
we get a stochastic process:
\[
t\mapsto W(t)=
\sum_{k=1}^\infty\, 
a_k\cdot \sin kt\cdot \rho_k\quad\colon 0\leq t\leq \pi/2\tag{i}
\]
It is obvious that the mean value of 
each $W(t)$
is zero and the variance becomes
\[
\sum_{k=1}^\infty\, 
a_k^2\cdot \sin^2 kt\tag{ii}
\]
Next, for a pair  $0<s,t\leq \pi/2$ 
the mean value
\[
 E(W(t)\cdot W(s))=
 \sum_{k=1}^\infty\, 
a_k^2\cdot \sin kt\cdot \sin ks=
\frac{1}{2} \sum_{k=1}^\infty\, 
a_k^2\cdot (\cos k(t+s)-
\cos k(t-s))\tag{iii}
\]
At this stage Winer employed a special $a$-sequence.
Expand the continuous function
$t$ on $[0,\pi]$  in a cosine series
\[
t=
\sum\, b_k\cdot \cos (kt)\tag{iv}
\]
Here
\[
\frac{\pi}{2}\cdot b_k=\int_0^\pi\, t\cdot
\cos kt \, dt=\frac{1}{k}\cdot \int_0^\pi\, \sin kt\, dt
\]
The right hand side
is $\frac{2}{k^2}$ if $k$ is odd and otherwise zero. So if $k$ is odd one has
\[
b_k=\frac{4}{\pi\cdot k^2}
\]
Set
\[
a_{2k+1}=\sqrt{b_{2k+1}}\quad\colon\, k=0,2,\ldots\tag{v}
\]
Then (iii-iv) entail that

\[
E(W_\epsilon(t)\cdot W_\epsilon(s))=\frac{1}{2}(t+s-|t-s|)=
\min\, (t,s)\tag{*}
\]
Recall from basic probability theory that
a pair of non-correlated normal distributions are independent.
From (*) it follows that
the stochastic process $\{W(t)\}$ has independent increment, i.e.
if $0<s<t\leq \pi$ then
$W(s)$ and
$W(t)-
W(s)$ are independent normally distributed variables with variance $s$ and $t-s$.
This means that
$\{W(t)\}$ yields a Brownian motion.
\medskip


\noindent
By  Wiener's construction the sample space for
the whole stochastic process in the continuous time parameter is
given   by a denumerable  product of independent 
normal distributions on the real line.
Starting from the construction above, Wiener also analyzed
the continuity of individual paths.
For a given sequence of values of the indepedent
$\rho$-variables
we have a function of $t$ with the sine-series expansion
(i).
From the above
\[
a_k=\frac{2}{\sqrt{\pi}\cdot k}
\]
when $k$ is odd while $a_k=0$ when $k$ is even.
Since the series
$\sum\, k^{-1}$ diverges we do not get an absolutely convergent
series even if
the set of $\rho$-values is bounded. So the
continuity of
$W(t)$ is not
automatic.  The reader can consult
[Paley-Wiener page xx-xx]
for a  proof that if $\delta>0$ then 
$W_\epsilon(t)$ is Hšlder continuous of order
$1/2-\delta$ for almost every outcome of the
$\rho$-sequence.
In ¤ 8.1 we give another construction of
the Brownian motion and establish a precise result about
the continuity for individual
Browninan paths.
\medskip


\noindent
{\bf{Parabolic PDE-equations.}}
Einstein's work  has shown that
a {probabilistic interpretation} to solutions of partial differential equations
which appear in diffusion processes of colloidal material
is very useful.
This inspired  later work dealing with the
Brownian motion and the heat-equation such as in the joint article
[KKP] by Khintchine, Kolmogorv and Petrowsky  from 1930.
Here one finds 
precise results about 
continuity properties of individual Brownian paths based upon
studies 
of boundary value problems
for the heat equation.
Later Paul Levy found   a more direct proof
of the continuity properties of
individual Brownian paths which we give in ¤ 8.2.
From a historic point of view considerable
credit must be given to Fourier and Laplace.
Even though  the  interplay between 
PDE-equations of parabolic type for heat conduction 
and probability theory was not fully explicit in
Laplace's pioneeringt work in probability theory from 1820,
the
mathematical frame was  paved via Fourier-Laplace transforms.
In ¤ 8.2 we follow Fourier and Laplace to 
construct parabolic PDE-equations associated to
stochastic processes in continuous time
with independent increments.

 
 
\medskip

\noindent
{\bf {Bachelier's work.}}
 To the  historic account one must add the pioneering
work by X.X Bachelier whose  article \emph{La Bourse}
from 1900 calculates
probability densities attached to the 
Brownian motion
with barriers.
For example, given some $a>0$
we can ask for  the  time when a Brownian
first hits  the barrier
$x=a$. This yields a probability distribution
which depends on $a$ and was determined 
explicitly by Bachelier.
His  
text-book on probability theory 
from  1910 is the first modern account dealing with stochastic processes
on an advanced level.
The Brownian motion can be
used to investigate
various   probability distributions, apart from the
"hitting probability" on a given arc on the boundary of a domain
in ${\bf{C}}$ which correspond to a
harmonic measure. At several occasions in these notes
we expose this "tautology" 
between  probabilistic interpretations 
via the Brownian motion and
solutions to the heat equation and other boundary
value problems which
are obtained via solutions to the Dirichlet problem.







\bigskip














\medskip

\noindent
\centerline {\bf 8.1 The Levy-Lšf  construction.} 
\medskip

\noindent

The subsequent material  is inspired from 
notes by Anders Martin-Lšf who attributes the main
constructions  to P. Levy.
We seek a stochastic process $\{X(t)\colon\, t\geq 0\}$
such that for every pair $0\leq s<t$, 
$X(t)-X(s)$
is a normally distributed 
random variable with variance $t-s$ and  independent of
$X(s)$. In particular each  $X(t)$ is normally distributed
with variance $t$.
Recall that two normally distributed variables are independent if and only if
they are uncorrelated. Hence, if $E$ denotes expected value, 
the condition that the process has
independent increments is 
equivalent  to the condition that
\[
E(X(t)\cdot X(s))=\text{min}(s,t)\quad\colon\text{for every pair}\,\ s,t
\]
Before we give the construction of a stochastic process satisfying the conditions above
we  make some observations  if such a process is given.
\medskip

\noindent {\bf 1. Conditioned mean-values.} Let $s<t<u$ and
consider the  mean value of $X(t)$ when $X(u)$ and $X(s)$ 
are given, i.e. we seek
\[ 
E((X(t)\,|\, X(s),X(u)
\]
Since the  stochastic variables $X(s),X(t),X(u)$ are normally distributed
it is wellknown  that this conditioned mean value is a linear function
of $X(s)$ and $X(u)$, i.e. there exists a pair of real numbers $(a,b)$
such that:

\[
\bar X(t)=E((X(t)\,| X(s),X(u))=a\cdot X(s)+b\cdot X(u))
\] 
Since we  are assuming independent increments, 
$X(t)-\bar X(t)$ is independent of both $X(s)$ and $X(u)$. A calculation
which is left to the reader gives
\[
a=\frac{u-t}{u-s}\quad\colon\quad b=\frac{t-s}{u-s}\tag{*}
\]
If $t-s\to 0$ while $u$ stays fixed, then
$a\to 1$ which reflects that the conditioned mean value
is close to $X(s)$.
Inserting the values of $a,b$ we now have a linear function

\[
\bar X(t)=\frac{(u-s)X(s)+(t-s)X(u)}{u-s}\quad\colon\quad s<t<u
\]
which coincides with $X(s)$, respectively $X(u)$ at the end points of
the interval $[s,u]$.
\medskip

\noindent {\bf 2. The conditioned variance.}
With $a$ and $b$ chosen as in (*) we get:
\[ 
V(t) =E((X(t)-\bar X(t))^2\,|\, X(s),X(u))=
\] 
\[
E[(a(X(t)-X(s))+b(X(t)-X(u))^2]=a^2(t-s)+b^2(u-t)=
\frac{(u-s)(t-s)}{u-s}
\]


\noindent
Hence the graph of $V(t)$ is a parabola whose values at
the end points $s$ and $u$ are zero. The maximum is attained at
the mid-point which reflects that we obtain a maximal variance
when random values taken by $X(s)$ and $X(u)$ affect $X(t)$ in equal parts.
\bigskip

\noindent
{\bf 3. An  inductive construction.}
We shall construct the Brownian motion over the unit interval $0\leq t\leq 1$.
After one can of course continue to any time interval.
Let $N\geq 1$ and put 
\[
t_\nu(N)=\nu\cdot 2^{-N}\quad\colon\quad 0\leq\nu\leq 2^N
\]


\noindent 
From  previous remarks we obtain a stochastic process
as follows:
Let $\chi_1,\ldots,\chi_{2^N}$
be independent and normally distributed variables, each
with mean value zero and variance
$2^{-N}$.
Consider a time value
\[ t=k2^{-N}+\delta\quad\colon\quad 
0\leq k\leq 2^N-1\quad\colon\,0\leq\delta\leq 2^{-N}
\]


\noindent At this moment of time
we define the random variable
\[ 
X_N(t)=\sum_{\nu=0}^{\nu=k-1}\,\chi_\nu+(1-\delta)\chi_k+
\delta\chi_{k+1}\tag{i}
\]
\medskip

\noindent
With a sample space of dimension  $2^N$ over the real line,
the outcome consists of   values  taken by the independent 
and normally distributed
$\chi$-variables. This
sample  
determines $X_t$ for every time value $0\leq t\leq 1$.
Hence the  outcome of each sample point consists of 
a piecewise linear curve
$t\mapsto \gamma(t)$
defined on $[0,1]$ with eventual corner points at
when $t=k2^{-N}$, where $\gamma(k2^{-N})$ is the sum of the
first $k$ many $\chi$-variables.
\bigskip

\noindent
{\bf 4. Passage to the limit.}
We have constructed a  process
$\{X_N(t)\}$
whose sample space is of dimension $2^N$.
For the inductive construction we pass from stage $N$ to 
$N+1$  allowing "white noise" during   time intervals 
$[k2^{-N},(k+1)2^{-N}]$. This means that we introduce $2^N$ many
new random variables $g_1,\dots,g_{2^N}$ which
are independent of those which were used to get
$\{X_N(t)\}$.
 Moreover, every $g_k$ is normally distributed 
with variance $2^{-N-1}$.
Thus, at stage $N+1$ we have a process $t\mapsto X_{N+1}(t)$
where

\[ 
X_{N+1}(k2^{-N}+\delta 2^{-N-1})=X_N(k2^{-N})+ \delta g_k
\colon\, 0\leq\delta\leq 1
\] 
\[
X_{N+1}((k+1/2)2^{-N}+\delta 2^{-N-1})=
X_N(k2^{-N})+  g_k+
\delta g_{k+1}
\colon\, 0\leq\delta\leq 1
\]
\bigskip

\noindent
Inductively we get a sequence of processes
$\{X_N(t)\}_{N\geq 1}$ whose  sample spaces increase.
Thus, at each stage "white noise" appears, expressed  by a  block of $2^N$
many $g$-variables.
The whole  sample space is  a
denumerable product of the real line on which we define the
usual product of the Lebesgue measure.
The outcome from a sample point is  a sequence of polygons
$\gamma_1,\gamma_2,\ldots$. At a dyadic time value 
$t=k2^{-N}$ the polygons
$\{\gamma_\nu\}$ pass the same point, 
There remains to investigate   when the  sequence of these polygons
converge to a continuous limit curve. It turns out that the convergence
holds for
almost every sample point which by the above
is taken from the denumerable product of copies of the real line
${\bf{R}}$.
\bigskip


\noindent
{\bf 5. Continuity of Brownian paths.}
We shall study the effect of white noise 
during the passage from  stage $N-1$ to the stage $N$.
For this purpose we consider a family
$\chi_1,\ldots,\chi_{2^N}$
of independent normally distributed with mean value zero and variance one.
Define for each $\alpha>0$:
\medskip
\noindent
\[
\Pi_N(\alpha)=
\text{Prob}\{ \text{max}\,\colon\,  2^{-N/2}|\chi_k|\geq\alpha\,\colon
1\leq k\leq 2^N\}
\]

\noindent
Thus, if $g_k=2^{-N/2}\chi_k$ are the random 
variables which cause white noise,
then
$\Pi_N(\alpha)$ is the probability that at least some $g_k$
has absolute value $\geq\alpha$.
By the previous discussion this means that we measure 
the probability for the \emph{maximal distance} between the curves 
$\gamma_{N-1}$ and $\gamma_N$
over the whole time interval.
So  we want are upper bounds for
the $\Pi$-numbers with $\alpha$ small as $N$ increases.
Here is the crucial inequality:





\medskip

\noindent
{\bf 6. Proposition.}
\emph{For all pairs $N,\alpha$ one  has the inequality}

\[ 
\Pi_N(\alpha)\leq \sqrt{\frac{2}{\pi}}\cdot 
\frac{2^{N/2}}{\alpha}\cdot
e^{-2^{_N}\cdot\alpha^2/2}
\]
\bigskip

\noindent
\emph{Proof.}
Consider first a single normal distribution
with variance one.
If $A>0$ we have the tail
probability
\[ 
\frac{1}{\sqrt{2\pi}}
\int_A^\infty\,e^{-x^2/2}dx\leq
\frac{1}{\sqrt{2\pi}}\int_A^\infty\,\frac{x}{A}\cdot e^{-x^2/2}dx=
\frac{1}{\sqrt{2\pi}}\cdot \frac{e^{-A^2/2}}{A}
\]


\noindent
Put
\[
 A=2^{N/2}\cdot \alpha\quad\colon\quad \xi=
 \sqrt{\frac {2}{\pi}}\cdot
 \frac{1}{A} \cdot e^{-A^2/2}
 \]
 
 
 \noindent
Notice that $1-\Pi_N(\alpha)$
is the probability that $|\chi_k|\leq A$ for every $k$.
The tail inequality applied to every $\chi_k$ gives
\[ 
\text{Prob}\{|\chi_k|\geq A\}\geq
 \sqrt{\frac {2}{\pi}}\cdot
 \frac{1}{A} \cdot e^{-A^2/2}=\xi
 \]
The elementary
inequality $(1-t)^M\leq Mt$ for every $0<t<1$
therefore gives
\[ 
\Pi_N(\alpha)\leq
(1-\xi)^{2^N}\leq 2^N\cdot\xi=2^N\cdot \sqrt{\frac {2}{\pi}}\cdot
 \frac{1}{A} \cdot e^{-A^2/2}
\]
Since $A=2^{N/2}\alpha$ the last inequality proves Proposition 6.
 \medskip
 
 \noindent {\bf 7. Specific choice of
 $\alpha$}.
With $\alpha=2^{-N/2}\beta$
we have
\[ 
\Pi_N(\alpha)\leq\sqrt{\frac {2}{\pi}}\cdot
2^N\cdot\frac{1}{\beta}
\cdot e^{-\beta^2/2}=\sqrt{\frac {2}{\pi}}\cdot
\frac{1}{\beta}\cdot e^{\,\text{Log}(2)\cdot N-\beta^2/2}\tag{7}
\]
\medskip

\noindent
Let us choose
\[
\beta=[2 N\cdot \log 2\,]^{\frac{1}{2}}\quad\colon\quad\theta>1
\]
\medskip

\noindent
Then the last term in (7) becomes
\[
\frac{1}{\sqrt{\pi\cdot\log 2}}\cdot
2^{N(1-\theta^2)}
\]
\medskip

\noindent
So with this specific choice of $\alpha$ we have established
the inequality
\[
\Pi_N(\alpha)\leq
\frac{1}{\sqrt{\pi\cdot\log 2}}\cdot
2^{N(1-\theta^2)}\quad\colon\quad
\alpha=
[2 N\text{Log}(2)\,]^{\frac{1}{2}}\cdot 2^{-N/2}\tag{8}
\]
\bigskip

\noindent
{\bf 8. Remark.}
Keeping $\theta>1$ fixed
and choosing $\alpha(N)=
[2 N\text{Log}(2)\,]^{\frac{1}{2}}\cdot 2^{-N/2}$
for each $N$, we get the convergence of the series
\[
\sum_{N=1}^\infty
\Pi_N(\alpha(N))\tag{9}
\]
\medskip

\noindent
In the construction of the Brownian motion the
"white noise" as we pass from period $N$ to $N+1$
arises from  $2^N$ many independent normally
distributed variables, each with variance $2^{-N}$.
So $\Pi_N(\alpha(N))$ measures the maximal deviation 
over the whole time interval $[0,1]$
from
a polygon at period $N$ to the new polygon at period $N+1$.
\medskip


\noindent
The convergent series (9)
implies that a single Brownian path is almost surely continuous and the choice of
$\{\alpha(N)\}$
entails that 
the resulting limit curves are almost surely 
Hšlder continuous of order $\sqrt{t}|\cdot\text{Log}(\frac{1}{t})$.
Summing up
we have established the following:
\bigskip

\noindent {\bf 9. Theorem.}
\emph{A  Brownian path is almost surely Hšlder continuous of order
$\sqrt{t}\cdot\log (\frac{1}{t})$.}
\bigskip

\noindent
{\bf{10. A result by Khintchine.}}
Theorem  9
asserts
that
almost every Brownian path is Hšlder continuous of
order
$\sqrt{t}\cdot\text{Log}(\frac{1}{t})$ for \emph{every} 
value of $t$.
A relaxed condition would be request
that  Hšlder continuity which
holds for almost all time values.
This leads to a result due to Khintchine
which asserts that almost every Brownian path
is Hšlder continuous of order
\[
\sqrt{t}\cdot\text{Log}(\text{Log}(\frac{1}{t}))\tag{*}
\]
for almost every time value. Notice that since we have taken a double Log-function 
we come closer to Hšlder continuity of order $\frac{1}{2}$
in (*). The proof of (*) uses Khintchine's \emph{Law of the iterated logarithm}.
For the proof of (*) we refer to [Khi] and the interested reader may also
consult his excellent text-book on statistical mechanics in
[Khi] which offers a good introduction for students of mathematics
without
prerequisite knowledge about physical laws.



\bigskip


\centerline{\bf{8.2 Parabolic PDE-equations and
stochastic  processes.}}
\medskip


\noindent
Following original work by Laplace and Fourier we
derive the parabolic PDE-equation
which is used to express   the joint probability distribution of
a vector-valued stochastic process in continuous time.
Let $n\geq 1$ and consider
a process 
$X(t)=(X_1(t),\ldots X_n(t)$ 
which is governed by infinitesmal  deterministic  drift
together with  a Brownian motion:
\[ 
dX_k(t)= b_k(X(t),t)\cdot dt+ \sigma_k(X(t),t)\cdot dW_k(t)
\quad\colon 1\leq k\leq n\tag{*}
\]
Above $\{b_k(x_1,\ldots,x_n,t)\}$ and
$\{\sigma _k(x_1,\ldots,x_n,t)\}$ are
real-valued functions defined for $x\in{\bf{R}}^n$ and  $t\geq 0$
and
$W(t)=(W_1(t),\ldots,W_n(t)$
is  a vector-valued Gaussian distribution
expressed by a density function $g(\omega_1,\ldots,\omega_n;t)$
where   no drift  occurs, i.e.
\[
\int_{{\bf{R}}^n}\, \omega_k\cdot g(\omega;t)\, d\omega=0
\quad\colon 1\leq k\leq n\tag{i}
\]
We have also  covariance functions
\[
B_{jk}(t)=
\int_{{\bf{R}}^n}\, \omega_j \omega_k\cdot g(\omega;t)\, d\omega
\quad\colon 1\leq j,k\leq n\tag{ii}
\]
At time $t=0$ the random variable
$X(0)$ has a joint density distribution
$f_0(x)= f_0(x_1,\ldots,x_n)$. If $t>0$ we denote by
$f(x;t)$  the density of $X(t)$ and
$\{\partial_j=\frac{\partial}{\partial x_j}\}$
are   derivation operators with respect to the $x$-variables.

\medskip

\noindent
{\bf{8.2.1. Theorem.}}
\emph{The function $f(x,t)$ satisfies the
PDE-equation:}
\[
\frac{\partial f}{\partial t}=
\sum_{k=1}^{k=n}\, \partial_k(b_k\cdot f)+
\frac{1}{2}\sum\sum B_{j,k}(t)\cdot
\partial_j\partial_k(\sigma_j\sigma_k\cdot f)\tag{8.2.1}
\]
\medskip

\noindent
\emph{Proof.}
Introduce the characteristic function
\[
\phi(\xi;t)=  \int_{{\bf{R}}^n}\,
e^{i\langle \xi,x\rangle}\, f(x;t)\, dx
\]
By definition (*) means that
if $\Delta$ is a small positive number then
\[
\phi(\xi;t+\Delta)=
\iint_{{\bf{R}}^n\times
{\bf{R}}^n}\,
\exp\bigl[ \sum_{k=1}^{k=n}\,
i\xi_k(x_k+b_k(x;t)\cdot \Delta+\sigma_k(x;t)\omega_k\cdot \sqrt{\Delta}\bigr]
\cdot
f(x;t)g(\omega;t) \, dxd\omega
\]
Then (i) and (ii) together with  a Taylor expansion up to order two gives:
\[
\lim_{\Delta\to 0}\,
\frac{\phi(\xi;t+\Delta)-\phi(x;t)}{\Delta}=
\]
\[
\sum_{k=1}^{k=n}\, i\xi_k\cdot 
\int_{{\bf{R}}^n}\, e^{i\langle\xi,x\rangle}
b_k(x,t)\cdot f(x;t)\,dx-
\frac{1}{2}\sum\sum B_{j,k}(t)\cdot
\xi_j\xi_k\cdot 
\int_{{\bf{R}}^n} \, e^{i\langle\xi,x\rangle}
\sigma_j(x,t)\cdot\sigma_k(x,t) \cdot f(x;t)\,dx
\]
\medskip

\noindent
Now (8.2.1) follows from Fourier's inversion formula.
\medskip

\noindent
{\bf{8.2.2 Remark.}}
In order that Fourier's inversion formula applies
one should assume that the functions $\{b_k\}$ are
in $L^1$Êand  the $\sigma$-functions are in $L^2$.
In practice more regularity is imposed, i.e. the $\sigma$-functions are of class
$C^2$ and the $b$-functions of class $C^1$ in which case
the parabolic
PDE-equation (8.2.1) is expressed
without
distribution
derivatives.
One refers to (8.2.1) as a diffusion equation
and in the context of PDE-theory 
the equation in Theorem 8.2.1 is said to be
parabolic.
Some 
text-books
prove Theorem 8.2.1 via 
the "Ito Calculus". Personally 
I prefer the original 
proof by Laplace and Fourier above where
the  parabolic PDE-equation is established  under
relaxed conditions on
the $b$- and the $\sigma$-functions. Moreover, 
Parseval's equation gives
a precise
insight about $L^2$-properties.
\medskip


\noindent
{\bf{8.2.3 Uniqueness results.}}
Already the case $n=1$ leads to subtle problems. In fact, it was discovered by
Gevrey and Hadamard that solutions to the basic heat equation
\[
\frac{\partial f}{\partial t}(x,t)=f''_{xx}(x,t)
\]
in general are not unique, i.e. non-trvial solutions can exist even if
$x\mapsto f(x,t_0)$ vanishes identically for some time value $t_0$.
It is ony in the analytic case where  
solutions expressed are 
expressed by 
the integral formula
\[
f(x,t)=\frac{1}{\pi\cdot \sqrt{t}}\int_{-\infty}^\infty\, e^{(x-\xi)^2/4t}\,
f(\xi,0)\, d\xi
\]
However, this integral formula is not valid
if $x\mapsto f(x,0)$ increases too fast.
Here an  involved
analysis is needed 
which goes   beyond    elementary studies 
of stochastic PDE-equations.
For results concerned with the non-analytic case
we
refer to work by Beurling and  Holmgren,
which is exposed in ¤ xx.













\newpage





\centerline{\bf{9. Riesz' representation theorem.}}
\bigskip

\noindent
Let $S$ be a compact Hausdorff  space
and $\mathcal B_*(S)$ the Boooelan algebra generated by closed sets.
Let $\mu$ be a non-negative and additive function on  $\mathcal B_*(S)$.
So in particular $\mu(S)$ is finite. Moreover, the additivity entails that
\[
\bigl|\sum\, a\uuu k\cdot \mu(E\uuu k)\bigr|\leq \max\{  |a\uuu k|\}\cdot \mu(S)\tag{1}
\]
for every finite family of disjoint sets $\{Ek\}$ and real $a$\vvv numbers.
Next, define  a function
$\mu^*$ 
on  $\mathcal B_*(S)$ by
\[ 
\mu^*(A)=\min_{A\subset U}\, \mu(U)\tag{2}
\]
where the mimium is taken over open sets $U$ which contain $A$.
\medskip

\noindent
{\bf{9.1 Exercise.}}
Show that $\mu^*$ is additive. The hint is  that
$\mu^*(U)=\mu(U)$ for open sets and  in the next step one verifies that
$\mu(F_1\cup F_2)+\mu(F_1)+\mu(F_2)$
hold for each pair of disjoint closed sets.
\medskip

\noindent
{\bf{9.2. Riesz' equality. }}
As already explained in ¤ 0.1 from the introduction the two additive
measures $\mu$ and $\mu^*$
yield integrals with respect to continuos functions on $S$.
Now we show the equality below for every
$f\in C^0(S)$:
\[
\int\, f\cdot d\mu^*=
\int\, f\cdot d\mu\tag{9.2.1}
\]
\medskip

\noindent
\emph{Proof.}
Since every continuous function
is the difference of two non-negative functions it suffices to prove (*) when 
$f\geq 0$ and after scaling that
$0\leq f\leq 1$. We may also assume that
$\mu(S)=1$.
Given a positive integer $N$
we set for each $0\leq k\leq N-1$:
\[
 a_k=\max_{k/N\leq x\leq (k+1)/N}\,f(x)
\,\colon\,  b_k=\min_{k/N\leq x\leq (k+2)/N}\,f(x)
\]
\[
A_k=\{k/N<f\leq (k+1)/N\}
\]
Since $\mu^*$ is non-negative one has
\[
\int\, f\cdot d\mu^*\leq \sum\, a_k\cdot \mu^*(A_k)\tag{i}
\]
Next, if $\epsilon>0$ the construction of
$\mu^*$ gives an $N$-tuple of
open sets $\{U_k\}$ where $U_k$  contains
$A_k$ and 
\[ 
\mu^*(A_k)>\mu(U_k)-\epsilon/N\tag{ii}
\]
Above we can  shrink $U_k$ and  assume that
\[
U_k\subset \{k/N<f(x)<(k+2)/N\}\tag{iii}
\]
From (ii) a summation gives
\[
\epsilon+\int\, f\cdot d\mu^*\leq \sum\, a_k\cdot \mu(U_k)\tag{iv}
\]
Set
\[
\omega_f(N)= \max\{ a_k-b_k\}
\]
The normalisation $\mu(S)=1$ gives
\[
\omega_f(N)+\epsilon+\int\, f\cdot d\mu^*\leq \sum\, b_k\cdot \mu(U_k)\tag{v}
\]
Next, let  $\{\chi_k\}$ be a partition of the unity with respect to
$\{U_k\}$, i.e. the $\chi$\vvv functions are continuous and
each $\chi\uuu k$ has compact support in
$U\uuu k$ while their sum is identically one on $S$.
The definition of the $b$-numbers entail that
$f\geq \sum b_k\cdot \chi_{U_k}$ and 
(v) gives
\[
\omega_f(N)+\epsilon+\int\, f\cdot d\mu^*\leq \int\, f\cdot d\mu\tag{vi}
\]
Above  $N$ is arbitrary large and by the uniform
continuity of $f$ we have
$\omega_f(N)\to 0$ as $N\to\infty$.
Since
$\epsilon$ can be arbitrary small
we conclude that
\[
\int\, f\cdot d\mu^*\leq \int\, f\cdot d\mu
\]
In the same way we get
\[
\int\, (1-f)\cdot d\mu^*\leq \int\,(1- f)\cdot d\mu
\]
Since  
$\mu^*(S)=\mu(S)$ 
we conclude that
(9.2.1) holds.
\bigskip



 \centerline {\bf{9.3 The $\sigma$-additivity of $\mu^*$.}}
\bigskip


\noindent
To simplify notations we set $\mu^*=\mu$.
If  $A\in \mathcal B\uuu *(S)$  the construction from (2)
applied to its  complement gives 
\[
\mu(A)=\max_{F\subset A}\, \mu(F)\tag{9.3.1}
\]
with the maximum taken over closed subsets.
Let us then take a denumerable sequence $\{A_n\}$ of pairwise disjoint sets
in $\mathcal B_*(S)$ and set $A^*=\cup\, A\uuu n$.
Define the  outer measure by
\[
\widehat{\mu}(A^*)=\min_{A^*\subset U}\,\mu(U)
\]
with the minimum taken over open sets which contain $A^*$.
Given $\epsilon>0$ we 
choose $U$ so that
\[
\mu(U)< \widehat{\mu}(A^*)+\epsilon
\]
Next, apply (9.3.1)
to $A_n$ which gives  an closed set
$F_n\subset A_n$ such that
\[
\mu(A_n)\leq \mu(F_n)+\epsilon\cdot 2^{-n}
\]
Since $\mu$ is non-negative we have
\[
\sum_{n=1}^{n=N}\,\mu(F_n)\leq \mu(U)
\]
This hold for every $N$ and since $\epsilon>0$ was arbitrary we conclude that
\[
\sum\,\mu(A_n)\leq  \widehat{\mu}(A^*)+\epsilon
\]
Above $\epsilon$ was arbitrary and hence
\[
\sum\,\mu(A_n)\leq  \widehat{\mu}(A^*)\tag{*}
\]
To prove that equality holds in (*)
we use  (2)
and 
find open sets $ \{U_n\}$ with
$A_n\subset U\uuu n$ such that
\[
\mu(U_n)\leq \mu(A_n)+\epsilon\cdot 2^{-n}\tag{i}
\]
Since  $\cup \,U_n$ is an open set which
contains $A^*$  we have
\[
\widehat{\mu}(A^*)\leq \,\mu(\cup \,U_n)\tag{ii}
\]
Next, apply (9.4.1) to 
$\cup\,U_n$ which gives   a compact subset
$F$ such that
\[
\mu(\cup\,  U_n)\leq\epsilon+\mu(F)\tag{iii}
\]
Heine-Borel's Lemma gives an integer $N$ such that
$F$ is contained in the finite union $U_1\cup\ldots\cup\,U_N$.
Hence (i-iii) give
\[
\widehat{\mu}(A^*)\leq \epsilon+\sum_{n=1}^{n=N}\, \mu(U_n)\tag{iv}
\]
Finally, by (i) the last term is majorized by
$\epsilon+\mu(A_1)+\ldots+\mu(A_n)$ which entails that
\[
\widehat{\mu}(A^*)\leq 2\epsilon+ \sum\,\mu(A_n)
\]
Hence equality holds in (*).
One can continue by an induction in the
transfinite construction of Borel's $\sigma$-algebra and
conclude that $\mu$ has a unique extension to a $\sigma$-additive
measure to the Borel algebra  $\mathfrak{B}(S)$.

\medskip

\noindent
{\bf{Remark.}}
The  reader may consult
[Kolmogorov] for a further account
about
consistency during the construction of $\sigma$-additive measures.
\bigskip


\centerline {\bf{9.4 The case of signed measures.}}
\medskip

\noindent
In general, let $\mu$ be a signed measure, i.e. an additvie function on
$\mathcal B\uuu *(S)$ where its is assumed that there exists a constant $C$ such that
$|\mu(A)|\leq C$ for ever $A\in \mathcal B\uuu *(S)$.
Set
\[ 
\mu\uuu +(A)= \max\uuu {F\subset A}\,\mu(F)
\]
where the maximum is taken over subsets of $A$ in
$\mathcal B\uuu *(S)$. The reader can check that $\mu\uuu +$ is additive.
We also define
\[
\mu\uuu (A)= \min\uuu {F\subset A}\,\mu(F)
\]
This yields another additive function  and the reader can  verify the equality
\[
\mu(A)=\mu\uuu +(A)+\mu\uuu (A)
\]
From the construction $\mu\uuu +$ is non\vvv negative
and we get $\mu\uuu +^*$.
Similarly, $\mu\uuu\vvv $ is non\vvv negative and 
we get the non\vvv negative measure
$(\vvv\mu\uuu\vvv)^*$. Set
\[ 
\mu^*= \mu\uuu +^*\vvv(\vvv\mu\uuu\vvv)^*\tag{xxx}
\]
So this is the difference of two non\vvv negative and measures which both
extend to  $\sigma$\vvv additive measures on $\mathfrak{B}(S)$.
\medskip

\noindent
{\bf{9.4.1 Exercise}}.
Show that
\[
\int\, f\cdot d\mu^*=
\int\, f\cdot d\mu
\]
hold for continuous functions.
Moreover, show that
(xxx) corresponds to the Hahn\vvv decomposition of the signed $\sigma$\vvv additive 
measure $\mu^*$as in ¤ xx.






\newpage


\noindent
{\bf {Riesz representation formula.}}
Let $S$ be a compact topolgical space. We assume that is is Hausdorff and recall
from a general result in topology that $S$ is normal, i.e.
for each pair of disjoint closed sets $F$ and $G$ there exists
a continuous function $f$ whose range is the closed unit interval 
while $f=1$ on $F$ and zero on $G$.
Now there exists the Banach space $C^0(S)$ of real\vvv valued 
continuous functions equipped with
the maximum norm.
Next, we have the Boolean algebra $\mathcal B\uuu *(S)$
generated by closed
subsets of $S$.
By set\vvv theory one constructs the unique smallest
$\sigma$\vvv algebra which contains
$\mathcal B\uuu *(S)$. It is denoted by
$\mathcal B(S)$ and called the Borel algebra of subsets in $S$.
We remark that it can be found via a certain transfinite induction which
was carried out in great detail by Baire.
Now there exists the algebra
$\mathfrak{B}^\infty (S)$ of bounded real\vvv valued Borel functions.
Such a function $f$ has a bounded range and for every pair of real numbers 
$a<b$, the set 
$\{a\leq f<b\}$ belongs to 
$\mathcal B(S)$.
Under the maxium norm it is clear that
$\mathfrak{B}^\infty (S)$ is a Banach space. Since uniformly 
convergent sequences of continuous functions have a continuous limit, it follows that
$C^0(S)$ is a closed subspace of 
$\mathfrak{B}^\infty (S)$.
Next, consider the dual space of 
$\mathfrak{B}^\infty (S)$. Let $\mu$ be a continuous linear functional.
To each Borel set $E$  in $S$ we associate 
the characteristic function $\chi\uuu E$ and get the real number
\[
\mu(E)=\mu(\chi\uuu E)
\]
It is clear that 
\[ 
E\mapsto \mu(E)
\] 
is an additive map on 
$\mathcal B(S)$.
Moreover, if $||\mu||$ is the norm of the functional $\mu$ one has
the inequality
\[
\bigl|\sum\, a\uuu k\cdot \mu(E\uuu k)\bigr|\leq \max \, |a\uuu k|\tag{*}
\]
for every finite and disjoint family of Borel sets and 
real $a$\vvv numbers.
Conversely, the reader may verify that
if $\mu$ is an additive function on
$\mathcal B (S)$ for which (*) holds, then
it gives a continuous linear functional on
$\mathfrak{B}^\infty (S)$. Thus, the dual space of 
$\mathfrak{B}^\infty (S)$ can be identified with additive
$\mu$\vvv functions satisfying (*).
 Next, for each such  $\mu$,  
Borel's construction give  integrals
\[
\int\uuu S\, f\dot d\mu\tag{1}
\]
when $f\in C^0(S)$. 
This corresponds to the restriction map
from
the dual of $\mathfrak{B}^\infty(S)$ to the dual of $C^0(S)$. 
The Hahn\vvv Banach theorem shows that this map is surjective and hence
every vector $\gamma\in C^0(S)^*$ is represented by some $\mu$ as above.
\medskip

\noindent
\emph {The Riesz' Theorem.}
The inclusion
 $ C^0(S)\subset\mathfrak{B}^\infty (S)$
is strict so via the Hahn\vvv Banach theorem there exist
certain $\mu$ for which the integrals in (1) are zero for
every continuous  function $f$.
So if we start with a vector $\gamma\in C^0(S)^*$ the question arises if
there exists a specific $\mu$
which represents $\gamma$ in the sense that
\[
\gamma(f)=
\int\uuu S\, f\cdot d\mu\tag{2}
\]
hold for every continuous function.
Riesz proved that when $\gamma$ is given, then there exists a unique $\mu$
such that (2) holds, where $\mu$ in addition is
$\sigma$\vvv additive. This condition can be expressed by saying that
\[
\lim\uuu {n\to\infty}\, \mu(E\uuu n)=0\tag{3}
\] 
for every decreasing sequence $\{E\uuu n\}$ in
$\mathcal B(S)$ 
for which $\cap\, E\uuu n=\emptyset$.
The class of those $\mu$ for which both (*) and (3) hold
are called Riesz measures on $S$, and from the above this class is isomorphic to the dual 
of $C^0(S)$.
We shall give a more detailed exposition of this important result in ¤ 9 
after we have become familiar with the
material in ¤ 1.
The  case when $S$ is replaced by an euclidian  space 
is treated in ¤ 4 where the constructions are self\vvv contained since one can profit upon the geometry in
${\bf{R}}^n$.







\end{document}











 
 
 
 










































