\documentclass{amsart}
\usepackage[applemac]{inputenc}


\addtolength{\hoffset}{-12mm}
\addtolength{\textwidth}{22mm}
\addtolength{\voffset}{-10mm}
\addtolength{\textheight}{20mm}

\def\uuu{_}


\def\vvv{-}

\begin{document}


\newpage

\centerline{\bf{Mathematics by Torsten Carleman (1892-1949)}}
\bigskip

\noindent
{\bf{Introduction.}}
Carleman's  collected work 
covers  fifty  articles of   high standard together with several monographs.
He became  professor at Stockholm University in 1924 when 
he replaced the chair held by Helge von Koch.
From 1927  he also served  director at  Institute Mittag-Leffler
where he delivered frequent    seminars during the years   1928-1938.
His text-book 
\emph{LŠrobok i differential och integralkalkyl
jŠmte geometeriska och mekaniska tillŠmpningar}
for undergraduate mathematics was published in 1928
and used for several decades in Sweden.
Personally I find it outstanding
as a beginner's text.  
A good example is the 
material in probability theory [ibid: p. 275-296]
which contains an elegant 
proof of the central limit theorem 
for sums of independent binomial 
distributions.with
sharp remainder terms.
His last major publication  was \emph{Sur un problŽme d'unicitŽ pour les systmes
d'Žquations aux dŽrivees partielles ˆ deux variables
indŽpendantes} [Arkiv fšr matematik 1938] concerned with a
uniqueness theorem for  elliptic PDE-systems 
where the variable coefficients of the PDE-operators  
are
non-analytic which 
extended an earlier   result by  Erik Holmgren
when the coefficients are real-analytic.
Let us recall  that Holmgren served as supervisor while Carleman prepared
his thesis entitled \emph{†ber das Neumann-PoincarŽsche
Problem fŸr ein Gebiet mit Ecken}, presented 
at Uppsala University in 1916 when he was 23 years old.
Here appears a  studies of double layer
potentials
which  extended earlier work by PoincarŽ to the case when
the boundary in Neumann's boundary value problem no longer is smooth.
Many results, foremost precise
inequalities in this thesis certainly merit a study up
to the present date. Let me  remark  that already in |ibid]
appears naturally defined
bounded linear operators whose spectra consist of
compact sets with interior points which at that time was a new feature
in operator theory.



\medskip

\noindent
After  World War I, Carleman  visited several universities
in Europe, such as
ZŸrich, Gšttingen, Oxford and Paris.
As pointed out in Fritz Carlson's
memorial article [Acta Mathematica 1950], 
Paris was always Carleman's favourite  place where he 
got inspiration from  prominent mathematicians such as
Borel, Denjoy and Picard.
On several occasions
Carleman delivered  lecture
series at Sorbonne.
For example, in the spring 1930
he  lectured about singular integral operators
and spectral theory for unbounded self-adjoint operators
on Hilbert spaces, and in 1937
lectures were devoted to Boltzmann's kinetic gaz theory.






\medskip

\noindent
Carleman was   aware of the interplay between
"pure mathematics" and experimental sciences which inspired his own  research.
In 1920-21
he studied  at an engineering school
in Paris. 
An outcome of this
is
the article entitled \emph{ Sur les Žquations diffŽrentielles
de la mecanique d'avion} published in
[La Technique AŽronautique, vol. 10  1921), inspired by  Lanchester's pioneering work 
\emph{Le vol aŽrien}
which played a significant role while airplanes were
designed
at an early stage.
Carleman's article ends with
the following conclusion
after an investigation of integral curves
to a certain non-linear differential system:
\emph{Quelle que soit la vitesse initiale, l'avion, aprs avoir
ŽxecutŽ s'il y lieu, un nombre fini des loopings, prend un mouvement
qui s'approche indŽfinement du rŽgime de descente
rectiligne et uniforme.}

\medskip

\noindent
Carleman's   lecture
held 1944 at the Academy of Science in Sweden entitled
\emph{Sur l'action  rŽciproque entre les mathŽmatiques
et les sciences expŽrimentales exactes}
underlines his   concern for applications of mathematics.

\medskip

\noindent
During his  last years in
life Carleman  suffered from health problems which caused his decease on
January 11 1949 at the age of 56 years.
A memorial article about his  scientific achievement
appears in [Acta. Math. 1950] by
Fritz Carlson
who was Carleman's collegue at 
the department of mathematics at Stockholm
university for several decades.
See also his collected work
published by Institute Mittag-Leffler in 1960
and the posthumous work
\emph{ProblŽmes mathŽmatiques
dans la thŽorie cinŽtique des gaz}
which was printed in 1957
by Institute Mittag Leffler and 
contains
previously unpublished material about
the Boltzmann  equation.
Let us now describe some contributions by
Carleman
in mathematical physics.

\newpage





\centerline{\bf{Results about the Bohr-Schršdinger equation.}}

\bigskip

\noindent
Carleman's
most valuable work
is the monograph
 \emph{Sur les Žquations singulires
ˆ noyaux rŽel et
symmetrique} [Uppsala University 1923].
Further applications of this theory
than those treated  by 
Carleman in 1923, were
proposed in a
lecture by Niels Bohr at the 6:th Scandianvian congress
 in mathematics held at Copenhagen 1925 devoted
 to 
 the "new-born"  quantum mechanics.
Recall that one of the  fundamental points
is the hypothesis on energy levels which correspond to 
orbits in Bohr's theory of atoms. For an account about
the physical background
the reader may consult
Bohr's
plenary talk when 
he received the Nobel Prize in physics 1923.
Mathematically the Bohr-Schršdinger equation is given by:
\[ 
\Delta\phi+2m\cdot\bigl( E-U\bigr)\bigl(\frac{2\pi}{h}\bigr)^2\cdot \phi=0\tag{*}
\] 
where $\Delta$ is the Laplace operator in the 3-dimensional $(x,y,z)$-space,
$m$ the mass of a particle and $h$  Planck's constant
while   $U(x,y,z)$ is a potential function.
Finally $E$ is a parameter and one seeks values on $E$
such that (*) has a solution $\phi$
which belongs to $L^2({\bf{R}}^3)$.
Let us   cite an excerpt   from Carlemans  lectures in Paris at 
Institut Henri PoincarŽ held in 1930 where he
treated (*) and its associated
equation (**) below when a time variable enters.
\medskip

\noindent
\emph{Dans ces dernires annŽes l'’nteret de la question qui nous
occupe a considŽrablement augmentŽ.
C'est en effet
un instrument mathŽmatique 
indispensable pour development de la mechanique moderne crŽe par
M.M. de Brogile, Heisenberg et Schršdinger. Etude de l'Žquation
integrale:}
\[ 
\phi(x)= \lambda\cdot \int_a^b\, K(x,y)\phi(y)dy+f(x)
\quad\colon\lambda\in {\bf{C}}\setminus {\bf{R}}
\]
\medskip

\noindent
So a basic equation which emerges from quantum mechanics is
to find solutions $u(p,t)$ defined in
${\bf{R}}^3\times {\bf{R}}^+$
where $t$ 
is a time variable and $p=(x,y,z)$
which satisfies the PDE-equation
\[ 
i\cdot\frac{\partial u}{\partial t}=\Delta(u)(p,t)- c(p)\cdot u(p,t)= 0 \quad t>0\tag{**}
\]
and the initial condition
\[ 
u(p,0)= f(p)
\]
Here $f(p)$ belongs to $L^2({\bf{R}}^3)$
and $c(p)$  is a real-valued and locally square integrable function.
Carleman proved that the symmetric and densely defined operator
$\Delta+c$ has a self-adjoint extension in $L^2({\bf{R}}^3)$ if
\[
\limsup_{p\to \infty}\, c(p)\leq M\tag{***}
\]
When (***) holds
the spectrum of the densely defined sefl-adjoint 
operator $\Delta-c$ on
the Hilbert space
$L^2({\bf{R}}^3)$ is confined to an interval 
$[\lambda_1,+\infty)$ on the positive real line, i.e. 
$\lambda_1>0$.
Applied to the equation (**)
Carleman proved that the solution $u$ is given
by an equation
\[ 
u(p,t)=\int_{{\bf{R}}^3}\, [
\int_{\lambda_1}^\infty\, 
e^{i\lambda t}\cdot d\theta(p,q,\lambda)\,\bigr]\cdot f(q)\, dq
\]
where
$\lambda\mapsto  \theta(p,q,\lambda)$ is the  non-decreasing 
spectral function associated to $\Delta+c$.
Moreover, he found
an  asymptotic expansion which recaptures
the $\theta$-function.

\medskip

\noindent
Later hundreds of text-books and many thousands of articles
have treated similar equations as above, Various
methods for solutions have been employed, one is to
associate the diffusion process to
$\Delta+c$  and 
state results by  probabilistic  terminology.
But personally I think  Carleman's original proofs 
give the best insight,  and 
the  condition (***) has not been improved in more recent
work, i.e.
it appears as an "almost necessary condition" in order that
$\Delta+c$Êis self-adjoint.
Concerning the special equation (*) the proof 
is much simpler and is for exampe decribed in a few lines 
during Carleman's plenary tak at the IMU-congrss held at
ZŸrich 1932.

\newpage



\centerline {\bf{ A wave equation.}}
\medskip

\noindent
Let $\Omega$ be a bounded cdomain in
${\bf{R}}^3$ with a $C^1$-boundary $\partial\Omega$.
We seek functions $u(x,t)$
where
$x=(x_1,y_2,x_3)$ defined in
${\bf{R}}^3\setminus \Omega\times \{t\geq 0\}$
where $t$ is a time variable
satisfying the wave equation
\[
\frac{\partial^2u}{\partial t^2}=  \Delta(u)
\]
when $t>0$ and
$x\in{\bf{R}}^3\setminus \overline{\Omega}$.
The initial conditions when
$t=0$ is that
\[
u(x,0)=f_1(x)\quad\colon \frac{\partial u}{\partial t}(x,0)=f_2(x)\tag{i}
\]
where $f_1,f_2$ are $C^2$-functions in
${\bf{R}}^3\setminus \Omega$
and  $\Delta(f_1)$ and $\Delta(f_2)$
are square integrable, i.e.
\[ 
\iiint_{{\bf{R}}^3\setminus \Omega}\,
|\Delta(f_\nu|^2\, dx<\infty
\]
Finally the normal derivatives along
$\partial\Omega$ satisfy
\[
\frac{\partial f_\nu}{\partial n}=0\quad\colon\nu=1,2
\]
Given such a pair $f_1,f_2$ there exists
a unique solution $u(x,t)$ which satisfies the wave equation above
and the two initial conditions (i) together with the boundary value equation
\[
\frac{\partial u}{\partial n}(x,t)=0
\] 
for
every $x\in\partial\Omega$ and each $t\geq 0$.
Carleman's cited monograph gives an expression of the solution by 
an integral formula using the
spectral measure 
of a certain from a densely defined and self-adjoint operator on
the Hilbert space
$L^2({\bf{R}}^3\setminus \Omega)$.
A crucial result during this construction is that the spectral measure is
absolutely continuous which Carleman used to consolidate the physcially evident
fact that
\[
\lim_{x\to \infty}\, \nabla(u)(x)=0
\]













\bigskip


\centerline{\bf{A final comment.}}

\bigskip

\noindent
Personally I find   few mathematical texts (if any)  which superseed
the fundamental   approach to state and solve problems
in Carleman's work.
Several of his 
articles 
merit a study  up to the present date.
My personal favourite is the differential inequality exposed in
 ¤ 6 from chapter 1 which can be regarded as a truly classic result in
real analysis.
In these notes we  refrain from 
exposing  his  work 
devoted to  quasi-analytic functions and 
Bolzmann's kinetic gaz theory. The second chapter  
is devoted to Carlemans studies of
densely defined self-adjoint opeartors on separable Hilbert spaces
with special emphasis on the moment problem of Stieltjes and Hamburger.
The chapter devoted to 
PDE-equations  contains  material which is a bit more
"sophisticated compared to the contents under the headline
\emph{Results from the world of analysis}.
The reader will recognize that
the focus is upon
inequalities rather than
general theoretical results.
To this I would like to add a personal remark.
While entering "higher studies" in mathematics
my opinion
is that it is more valuable to pursue details of 
proofs rather than
digesting "general concepts".
Let me finish the introduction by a  result in this spirit. The theorem  below
 is elementary and yet the proof
requires some
rather
involved steps.

\medskip


\centerline {\bf{A result about Cesaro limits.}}
\medskip


\noindent
Consider a sequence of real numbers
$a_0,a_1,\ldots$ whose associated  power series
\[
 f(x)= \sum_{n=0}^\infty\, a_nx^n\tag{i}
\]
converges when $0<x<1$. Thus, for every $\delta>0$ there exists a constant
$C_\delta$ such that
\[
 |a_n|\leq C_\delta(1+\delta)^n
\]
Suppose that
\[
 \lim_{x\to 1}\, f(x)=0\tag{ii}
\]
This condition need not imply that
the partial sums
\[ 
s_n=a_0+a_1+\ldots+a_n
\]
converge to zero as $n\to \infty$.
An example is to take $a_n=(-1)^n\,\colon n=1,2,\ldots$
while $a_0=1/2$.
A sufficient condition
in order that (ii) implies that $s_n\to 0$
was proved by Abel in 1824. Namely, if
$n\cdot a_n\to 0$ then (ii) entails that $s_n\to 0$.
In a joint article from 1913, Hardy and Littelwood extended Abel's theorem and
proved that if (ii) holds and there exists a constant $C$ such that
\[
\frac{a_n}{n}\leq C\quad\colon\, n=1,2,\ldots \tag{iii}
\] 
then
$s_n\to 0$.
Notice that one only requires an upper bound in
(iii) while the sequence $\{a_n\}$ in general can contain negative terms
for which no constraint  has been imposed.
The proof of the Hardy-Littlewood theorem is 
given in Chapter 1 from my notes on analytic function theory.
Next, with $f(x)$ given in (i) and 
 $r\geq 1$ one can write
\[ 
f(x)= 
\frac{(1-x)^{r+1}}{\Gamma(r+1)}\cdot
\sum_{n=0}^\infty\, s_n^{(r)}\cdot n^r\cdot x^n
\]
The sequence $\{s_n^{(r)}\}$
is determined by a recursion formula from
$\{a_n\}$ and one  refers to $\{s_n^{(r)}\}$ as the arithemetic means of order $r$.
With $r=0$ we notice that
\[
s_n^{(0)}= a_0+\ldots+a_n
\]


\medskip

\noindent
{\bf{ Theorem.}}
\emph{Assume  (ii) and that there exists some $r\geq 1$ such that}
\[
\lim_{n\to\infty}\,s_n^{(r)}=0
\] 
\emph{Then it follows that
$s_n\to 0$}.
\medskip


\noindent
This result appears in Carleman's article
\emph{Some theorems concerning the convergence of power-series
on the circle
of convergence} [Arkiv fšr matematik, astronomi och fysik. Vol 16].
Theorem 0.1
is  closely related to 
the summation procedure introduced by
Cesaro in 1880, and the reader may compare Theorem 0.1  
with
results from Chapter 2 in Landau's text-book \emph{xxxx}
which  contains a proof that
Cesaro's summability in any order is equivalent to
that of Hšlder of the same order.
\bigskip


\noindent
\emph{Proof of Theorem 0.1}. 
With $r\geq 1$ kept fixed
we set
\[ 
g_m(x)=
\frac{(1-x)^{r+1}}{\Gamma(r+1)}\cdot
\sum_{n=m}^\infty\, s_n^{(r)}\cdot n^r\cdot x^n
\]
for each $m\geq 1$.
A classic result which goes back to work by Riemann shows that
(ii) entails that $s_n\to 0$ if there to each $\epsilon>0$ exists
a positive integers $n_0$ such that
\[
\bigl|\int_0^1\, \frac{\sin \, 2p\pi x}{1-x}\cdot
g_{n_0}(x)\ dx\,\bigr|\leq \epsilon
\quad\colon \,\, p\geq n_o\tag{*}
\]
To 
analyze when Riemann's condition  holds
we first notice that  the triangle inequality
implies that the left hand side in (*) is majorised by
\[
\sum_{n=n_0}^\infty\, 
|s_n^{(r)}|\cdot \frac{n^r}{\Gamma(r+1)} \cdot 
\bigl|\int_0^1\, \sin ( 2p\pi x)\cdot x^n (1-x)^r\, dx\, \bigr|
\]
Let $\epsilon>0$ be given.
To find  $n_0)$ such that  (*) holds we consider
the integrals
\[
J(p,n)=\int_0^1\, \sin ( 2p\pi x)\cdot x^r(1-x)^n\, dx
\]
Since the sine function is periodic one has
\[
|J(p,n)|=\bigl|\int_0^1\, \sin ( 2p\pi x)\cdot x^n (1-x)^r\, dx\, \bigr|
\]

\medskip

\noindent{{\bf{Exercise.}}
Verify that
\[
|J(p,n)|\leq 2\pi\cdot \Gamma(r+2)\cdot \frac{p}{n^{r+2}}\tag{1}
\]
and that there exists a constant $C(r)$ which depends on $r$ only such that
\[
|J(p,n)|\leq \frac{C(r)}{p\cdot n^r}\tag{2}
\]
Above (1) will be used when
$n\geq p$ while (2) is used if $n<p$.
Next, if  $n_0\geq 1$ the 
left hand side in (*) is majorised by
\[
\frac{1}{\Gamma(r+1)}\cdot 
\sum_{n=n_0}^\infty\, |s_n^{(r)}|\cdot n^r\cdot |J(p,n)|\tag{3}
\]
Put
\[
\delta(n_0)= \max_{n\geq n_0}\,|s_n^{(r)}|
\]
By hypothesis $\delta(n_0)\to 0$ as $n_0$ increases.
At the same time we  use (1-2) from the exercise and estimate
\[
\sum_{n=n_0}^\infty\,  n^r\cdot |J(p,n)|
\]
for every $p\geq n_0$.
First (2) entails that a summation with $n\leq p$ is majorised by
the constant $C(r)$.
Next,  (1) gives
\[
\sum_{n=p+1}^\infty\,  n^r\cdot |J(p,n)\leq
2\pi\cdot \Gamma(r+2)\cdot p\cdot \sum_{n=p+1}^\infty n^{-2}\leq
2\pi\cdot \Gamma(r+2)
\]
We conclude that there exists a constant $C^*(r)$ which only depends 
on $r$ such that
(3) is majorised by
$C^*(r)\cdot \delta(n_0)$ and now we choose $n_0$ so large that
\[
\delta(n_0)\leq C^*(r)^{-1}\cdot \epsilon
\] 
which gives (*).




\newpage



\centerline{\bf{Results from the world of analysis}}




\bigskip
\noindent
In ¤ 0-xx we expose results from Carleman's collected work.
Tbe proofs are essentially self-contained but some
results  in analytic function theory of one complex variable,
basic Fourier analysis and measure theory are 
taken for granted.
Relevant background is covered in my notes [Bjšrk].
As said in the introduction the main
reward for the reader is to pursue details in the proofs, i.e. the methods which are used
tend to have greater value than the actual results.
For the reader's convenicence we have inserted an appendix
dealing with entire functions of exponential type and
some Tauberian theorems  due to  Beurling and Wiener.


\newpage

\centerline{\bf{¤ 0. Two problems in the calculus of variation.}}

\bigskip

\noindent
We shall consider two problems with a geometric content
which
are classic in the sense that they were alreadt treated by
Steiner and Weierstrass at an early stage.
\bigskip



\centerline{\bf{¤ 0.1 An
isoperimetric inequality}}
\bigskip

\noindent
Recall that
a planar domain whose boundary
curve has  prescribed length
has a maximal   area when it it is a disc.  
It turns out that discs solve a more extensive class
of extremal problems.
Consider a function
$f(r)$ defined for
$r>0$ which is continuous and increasing with
$f(0)=0$. 
If $p$ and $q$ are two points in ${\bf{R}}^2$ their euclidian distance is denoted by
$|p-q|$.
When $U$ is a bounded open domain we set
 \[
J(U)=\iint_{U\times U}\, f(|p-q|)\cdot dA_p\cdot dA_q
 \]
where $dA_p$ and $dA_q$ denote   area measures.
Given a positive number $\mathcal A$ one seeks
to maximize the $J$-functional  in the
family of domains with  prescribed area  $\mathcal A$. 
The $J$-number is  unchanged under a
translation  or a rotation
of a  domain and the family of discs is
stable under these operations. So
the following result makes sense:
\medskip

\noindent
{\bf{1.Theorem.}}
\emph{The $J$-functional 
takes its maximum on discs $D$
of radius $r$ with $\pi r^2=\mathcal A$.
Moreover, for every domain $U$ with area $\mathcal A$
which is not a disc one has a strict inequality}
\[ 
J(U)<J(D)
\] 
\medskip

\noindent
When $f(r)$ is a strictly convex function 
Theorem 1  was established by Blaschke. 
For a general $f$-function which need not be convex the
theorem   was proved by Carleman in [Car]
using 
the symmetrisation process   by
W. Gros from  the article (Monatshefte math.physik 1917).
In ¤ xx we explain why
Theorem 1 leads to another property of discs.

\medskip

\noindent
{\bf{2.Theorem.}}
\emph{Let $\Omega$ be a domain in the family $\mathcal D(C^1)$
and denote by $ds$ the arc\vvv length measure on its boundary.
Then, if the
function}

\[
 p\mapsto \int\uuu{\partial\Omega}\, f(|p\vvv q|)\cdot ds(q)
 \] 
\emph{is constant as $p$ varies in $\partial\Omega$ it follows that
$\Omega$ is a disc.}
 


\medskip

\noindent
{\bf{Remark.}} 
Theorem 1  can be extended to 
any dimension $n\geq 3$ using
successive symmetrisations of domains
taken in different directions converge to the unit
ball in ${\bf{R}}^n$. Here discs are replaced by
$n-1$-dimensional spheres.
\medskip




\bigskip

\centerline {\bf{2. A variational   inequality}}
\medskip

\noindent
We first establish some inequalties which will
be used
in ¤ 3 to finish the proof of 
Theorem 1.
Let $M>0$  and on
the    vertical lines $\{x=0\}$ and $\{x=M\}$
we consider 
two subsets $G_*$ and $G^*$ which both consist of a finite union of closed intervals.
Let $\{[a_\nu,b_\nu]\}$ be the $G_*$-intervals taken in the $y$\vvv coordinates
and  
$\{[c_j,d_j]\}$ are the $G^*$-intervals.
Here $a_\nu<b_\nu<a_{\nu+1}$ holds, and similarly
the $G^*$-intervals are ordered with increasing $y$-coordinates.
The number of intervals of the two sets are arbitrary and 
need not be the same.
Given  $f(r) $ as in the Theorem 1 we set

\[ 
I(G_*,G^*)=
\sum_\nu\sum_j\, \int_{a_\nu}^{b_\nu}\int_{c_j}^{d_j}\,f(|y-y'|)\cdot dydy'
\]
Consider the variational problem where we seek to minimize these $I$-integrals
for  pairs $(G_*,G^*)$ as above under the
constraints:
  
\[
\sum\,(b_\nu-a_\nu)=\ell_*\quad\text{and}\quad  \sum\,(d_j-c_j)=\ell^*
\]
\medskip

\noindent
That is, the sum of the lengths of the intervals are prescribed on $G_*$ and $G^*$.

\medskip

\noindent
{\bf{2.1 Proposition.}} \emph
{For every  pair $(\ell_*,\ell^*)$ the $I$-integral is minimized when
both $G_*$ and $G^*$ 
consist of a single interval and the mid-points of
the two intervals have equal $y$-coordinate.}
\medskip

\noindent
{\bf{Proof.}} 
First we prove the
result when both $G_*=(a,b)$ and $G^*=(c,d)$ both are intervals.
We must prove that the $I$-integral is a minimum when
\[
\frac{a+b}{2}=\frac{c+d}{2}\tag{i}
\]
Suppose that inequality holds. Since the $I$-integral is symmetric with respect to the pair 
of intervals, we may assume that
\[
\frac{c+d}{2}=s+\frac{a+b}{2}\quad\text{where}\quad  s>0
\]
Now $I(G_*,G^*)$ is unchanged 
when we translate the two intervals, i.e. if we for some
number
$\xi$ take
$(a+\xi,b+\xi)$ and $(c+\xi,d+\xi)$.
By such a translation we can assume that $a=-b$
so  the mid-point of
$G_*$ becomes $y=0$ and we have:


\[
I=\int_{-b}^b\int _c^d\, f(\sqrt{M^2+(y-y')^2})\cdot dydy'
\]
Using  the variable substitutions
$u=y'-y$ and $v=y'+y$ we see that
\[
-b+c\leq u\leq d+b
\]
and obtain
\[
I=2b\int_{-b+c}^{d+b}\, f(\sqrt{M^2+v^2})\cdot dv
\]
With
\[ 
s=d-\frac{d+c}{2}= \frac{d-c}{2}
\]
we can write
\[ 
I=2b\cdot \int_{w-s}^{w+s} f(\sqrt{M^2+u^2})\cdot dv\quad\colon
w=b+\frac{d+c}{2}
\]
The last integral is a function of $s$, i.e. for every $s\geq 0$ we set

\[
\Phi(s)=2b\cdot \int_{w-s}^{w+s} f(\sqrt{M^2+u^2})\cdot dv\quad\colon
w=b+\frac{d+c}{2}
\]
The derivative of $s$ becomes

\[ 
\Phi'(s)= f(\sqrt{M^2+(w+s)^2})- 
 f(\sqrt{M^2+(w-s)^2})
 \] 
Since $f(r)$ was increasing the derivative is 
$>0$ when $s>0$.  Hence the minimum is achieved when $s=0$
which means that $G_*$ and $G^*$ have a common mid-point and
Proposition 2.1 is proved for the case of an interval pair.
\medskip


\noindent
\emph{The general case.}
If $G_*=\{(a_\nu,b_\nu)\}$ and $G^*=\{(c_k,d_k)\}$
we make an induction over the total number of intervals which appear in the 
two families.
Let 
\[
\xi^*=\frac{c^*+d^*}{2}
\]
be the largest mid-point from the $G^*$-family
which means that $k$ is maximal,
In the $G_*$-family
we also get the largest mid-point
is
\[
\eta^*= \frac{a^*+b^*}{2}
\]
If $\xi^*>\eta^*$ the previous 
case shows that the double sum representing $I$ decreases as long as
when the interval $(c^*,d^*)$ is lowered.
In this process two cases can occur:
First, suppose that
the lowered $(c^*,d^*)$-interval hits $(c_{k\vvv 1},d_{k\vvv 1})$ before
the mid-point equality appears. To be precise, this occurs if
\[
c^*-d_{k\vvv 1}<\xi^*-\eta^*
\]
In this case we replace $G^*$ by a union of intervals where
the number of intervals therefore has decreased by one and
we lower $(c^*,d^*)$ until
$\xi^*=\eta^*$.
After this we lower the two top-intervals at the same time
until
one of them hits
the second largest $G$-interval and in this way the total number of intervals is
decreased while the double sum for $I$ is not enlarged.
This gives the requested induction step and the proof of
Proposition 2.1 is finished.






 
 
 










\bigskip

\centerline {\bf{3. Proof of Theorem 1.}}
\medskip

\noindent
Consider a  domain $U$ 
defined by
\[ 
g_1(x)\leq y\leq g_2(x)\quad\colon\quad a\leq x\leq b\tag{1}
\]
where $g_1(a)=g_2(a)$ and $g_1(b)=g_2(b)$.
To $U$ we associate the symmetric domain $U^*$
defined by 
\[
- \frac{1}{2}\bigl[ g_2(x)-g_1(x)\bigr]\leq y\leq
 \frac{1}{2}\bigl[ g_2(x)-g_1(x)\bigr]\quad\colon\quad a\leq x\leq b\tag{2}
\]
\medskip


\noindent
Notice that $U$ and $U^*$ have the same area.
Set

\[ J=\iint_{U\times U}\,
f\bigl(\sqrt{(x-x')^2+(y-y')^2}\bigr)\cdot dxdx'dydy'
\]

\[ J^*=\iint_{U^*\times U^*}\,
f\bigl(\sqrt{(x-x')^2+(y-y')^2}\bigr)\cdot dxdx'dydy'
\]
\medskip

\noindent
{\bf{Lemma 3.1.}} \emph{One has the inequality}
$J\leq J^*$.
\medskip

\noindent 
\emph{Proof.} Set 
$h(x)=\frac{1}{2}[g_2(x)-g_1(x)]$
and 
introduce the  function
\medskip

\[ 
H^*(x,x')=\int_{y=-h(x)}^{h(x)}
\int_{y'=-h(x')}^{h(x')}
\,\rho\bigl(\sqrt{(x-x')^2+(y-y')^2}\bigr)\cdot dydy'
\]
We have also the function
\[
H(x,x')=\int_{y=g_1(x)}^{g_2(x)}
\int_{y'=g_1(x')}^{g_2(x')}
f\,\bigl(\sqrt{(x-x')^2+(y-y')^2}\bigr)\cdot dydy'
\]
It is clear that

\[ J=\int_a^b\int_a^b\, H(x,x')dxdx'\quad\text{and}\quad
J^*=\int_a^b\int_a^b\, H^*(x,x')dxdx'
\]

\noindent
Lemma 3.1 follows if we have proved the inequality 
\[
H(x,x')\leq H^*(x,x')\tag{*}
\]
for all pairs $x,x'$ in $[a,b]$.
But this follows via Fubini's theorem
when Proposition 2.1 applied in the special case where
$G_*$ and $G^*$ both consist of a single interval.

\bigskip

\noindent
{\bf{3.2 Variation of convex sets.}}
Let $\mathcal A$ be the prescribed area in Theorem 1 and consider
a convex domain $U$ whose area is $\mathcal A$.
By elementary geometry we see that after a translation and a rotation the convex
domain
$U$
can be represented as in(1)  above.
We construct 
$U_*$ as above and notice that
it is a new convex domain. Moreover, 
Proposition 2.1 gives  $J(U_*)\leq J(U)$.
In the next step
we perform a symmetrisation of $U_*$ 
along some other line which cuts $U_*$ to get 
a new domain
$U_{**}$ where we now have
$J(U_{**})\leq J(U_*)\leq J(U)$.
Finally we use the  geometric result
due to Steiner for  convex domains which
asserts   that when
symmetrisations as above are repeated infinitely often while 
the angles of the directions to the
$x$-axis  change with some
irrational multiple of $2\pi$, then
the resulting sequence of convex domains converge to a disc.
This  proves that the $J$-functional on a disc is $\leq J(U)$ for every convex domain.
 
\medskip


\noindent
{\bf{3.3 The non-convex case}}
Here we  use 
the symmetrisation process by
Gros.
Let $U$ be a domain. Its symmetrisation in the $x$-direction
is defined  as follows: To every $x$ we get the open
set
\[
\ell_U(x)=\{y\,\colon\,(x,y)\in U\}\tag{1}
\]
Let
$\{(a_\nu,b_\nu)\}$ be the  disjoint intervals of $\ell\uuu U(x)$
and put 
\[
 d(x)=\frac{1}{2}\cdot
 \sum\, (b_\nu-a_\nu)
\]
 
\noindent
We get  the domain $U^*$ which is symmetric with respect to the $x$-axis where
\[ 
\ell_{U^*}(x)=(-d(x),d(x))
\]
Notice that $U$ and $U^*$ have equal  area.
Proposition 2.1 applies and gives
the inequality
\[
J(U)\leq J(U^*)\tag{2}
\]
Now Theorem 1 follows when we start from a non-convex domain $U$.
Namely, by the  result proved in  [Gros], it holds
that after inifinitely many symmetrizations as above using
different directions, the sequence of
$U$-sets converge to a disc.










\bigskip





\centerline {\bf{¤ 0.2 On minimal surfaces.}}
\medskip



\noindent 
We shall  consider 
an  isoperimetric problem with a fixed boundary curve. 
More involved situations
arise  when the  minimal surfaces are bordered by
closed Jordan curves which  are free to move on
prescribed manifolds. This leads to 
problems by Plateau and Douglas and for
an account about this general case we refer to Courant's article
\emph{The existence of minimal surfaces of given toplogical structure
under prescribed boundary conditions}. (Acta. Math. Vol 72 1940]) where the reader
also finds an extensive references to relevant literature.
\medskip

\noindent
From now on we discuss the restricted 
problem when a boundary curve is fixed in
${\bf{R}}^3$ with coordinates
$(x,y,z)$.
Consider a rectifiable   closed Jordan curve
$C$ and denote by $\mathcal S(C)$ the family of surfaces 
which are bordered by $C$.
A surface $M$ in this family is minimal if
it has smallest possible area.
To find such a minimal surface
corresponds to a problem in the calculus of variation and  was 
studied by Weierstrass in a series of articles
starting from \emph{Untersuchungen Ÿber die FlŠchen
deren mittlere KrŸmmung Ÿberall gleich null ist}  from 1866.
A revised version written by Weierstrass  himself appears in volume I of 
his collected work.
He proved
that
if $M$ is a minimal surface in $\mathcal S(C)$ then
its mean curvature vanishes identically. Moreover,
$M$ has no singular points and is simply connected.
More precisely, the exists a homeomorphic
parametrization
of $M$ above an open disc in the complex $u$-plane which can be
achieved via complex analytic functions, or as expressed by
Weierstrass in the introduction to [Wei]:
\medskip


\noindent
\emph{Ich habe mich mit der Theorie die FlŠchen, deren mittlere
KrŸmmung Ÿberall gleich null ist, besonders auf dem grunde eingehender beschŠftigt, weil
sie, wie ich zeigen werde, auf das Innigste mit der Theorie der analytischen funktionen
einer komplexen Argumentz zusammenhhŠngt.}
Or shortly phrased: 
\emph{The theory about minimal surfaces
is closely linked to the theory of  analytic functions in one complex variable.}
\medskip


\noindent
{\bf{The isoperimetric inequality.}}
Using Weierstrass'  description of minimal surfaces 
the following was proved
by
Carleman in the article
\emph{Zur Theorie der MinimalflŠchen} in 1920:

\bigskip

\noindent
{\bf{Theorem.}}
\emph{For every rectifiable simple closed curve
$C$ the area $A$ of the minimal surface
in $\mathcal S(C)$ satisfies the inequality}
\[ 
A\leq \frac {\ell(C)^2}{4\pi}
\]
where $\ell(C)$ is the arc-length of $C$.
\medskip

\noindent
{\bf{Remark.}}
For historic reasons one may wonder why this result was not already
discovered by Weierstrass. The reason might be that certain facts
in analytic function theory was not yet enough developed. 
Carleaman's proof relies upon 
the Jensen-Blascke factorisation
of analytic functions which was not know prior to 1900.
Another obstacle was the discovery by Hermann Schwarz that
the minimal surface in the family $\mathcal S(C)$
is not
determined by vanishing mean curvarute alone. See
Volume II, page 264 and  151-167 in the collected work
of Hermann Schwarz for this "ugly phenomenon" which was one reason
why Weierstrass  paid much attention to existence problems in
the calculus of variation.
As remarked by Carleman at the end of his article, an
alternative (and simpler) proof was given
by Blaschke  after the publication of 
[Carleman]. However, this proof
is restricted to
a special class of minimal surfaces where the "ugly phenomena" do not occur
so here we rely upon Weierstrass' original parametristions which
lead
to a proof the the theorem above.
\medskip

\noindent
{\bf{The case when $C$ is piecewise linear}}.
Suppose that the boundary curve
consists of
$n$ many line segements $L_1,\ldots ,L_n$. Following
Weierstrass  it means that  one regards the  problem:
\emph{Es soll ein einfach zusamenhŠngenden MinimalflŠchenstŸck
$M$ analytish bestimmt werden, dessen vorgeschiebenen
begrenzung $C$
aus $n$ geradlinigen strecken  bestecht, welche eine einfache,
geschlossene, nicht verknotete Linie bilden.}
\medskip

\noindent
In  [Weierstrass] appears a  far reaching study of this problem. 
The main result shows that
$M$ is determined via
a  pair of analytic functions $G(u)$ and $H(u)$ defined in
the lower half-plane $\mathfrak{Im}u<0$
for which the three functions defined by
\[
\phi_1(u)=\text{det}\,
\begin{pmatrix} G(u)&H'(u)\\
G'(u)&H'(u)\end{pmatrix}
\]
\[
\phi_2(u)= \text{det}\,
\begin{pmatrix} G(u)&H'(u)\\
G''(u)&H''(u)\end{pmatrix}
\]
\[
\phi_3(u)= \text{det}\,
\begin{pmatrix} G'(u)&H'(u)\\
G''(u)&H''(u)\end{pmatrix}
\]
become rational functions of $u$.
Moreover, [ibid]  exhibits 
second order differential equations of the Fuchsian type 
satisfied by the rational $\phi$-functions  and the position of their
poles are described in terms of the 
geometric configuration
of $C$. It would lead us too far to
enter
the  material in [Weierstrass] so its rich contents is left
to the interested reader for further  studies.
\medskip


\noindent
{\bf{The planar case.}}
If $C$ is a simple closed curve in the complex $z$-plane
the isoperimetric inequality follows easily via analytic function theory.
Namely, let $M$ be the Jordan domain bordered by $C$.
By Riemann's theorem there exists 
a conformal mapping $\phi\colon\, D\to M$ and we have
\[ 
\ell(C)= 
\int_0^{2\pi}\ |\phi'(e^{i\theta})|\, d\theta
\quad \colon\quad
\text{area}(M)=
\iint_D\, |\phi'(z)|^2\, dxdy
\]
Hence the isoperimetric
inequality for planar domains boils down to show that
\[
4\pi\cdot \iint_D\, |\phi'(z)|^2\, dxdy\leq 
\bigl(\int_0^{2\pi}\ |\phi'(e^{i\theta})|\, d\theta\,\bigr)^2\tag{i}
\]
To prove (i) we use that
the derivative $\phi'(z)$ is zero-free
and hence it has a suingle-valued square root
$f=\sqrt{\phi}$.
We have a series expansion
\[ 
f(z)= a_1z+a_2z^2+\ldots
\]
The right hand side in (i) becomes
\[
4\pi^2\cdot \bigl(\int_0^{2\pi}\ |\sum\, a_\nu e^{i\nu\theta}|^2\, d\theta\,\bigr)^2
= 4\pi^2\cdot( \sum\, |a_\nu|^2)^2
\]
The left hand side becomes
\[
4\pi\cdot \iint_D\, (\sum\, |a_\nu z^\nu|)^4\, dxdy
\]
Set
\[ 
b_m= \sum_{\nu=1}^{\nu=m}\, a_\nu\cdot a_{m-\nu}
\quad\colon\, m\geq 2
\]
Then (xx) becomes
\[
4\pi\cdot \iint_D\,\sum\, |b_m z^m|)^2\, dxdy=
4\pi\sum\, |b_m|^2\cdot 2\pi\cdot \iint_D\, r^{2m+1}\,dr
=
8\pi^2\cdot \sum\, \frac{|b_m|^2}{2m+2}
\]
Hence (i) follows if
\[
\sum_{m=2}^\infty \, \frac{|b_m|^2}{m+1}\leq 
\sum_{\nu=1}^\infty\, |a_\nu|^2)^2\tag{ii}
\]
\medskip

\noindent
At this stage we leave it to the reader to verify
the planar isoperimetric
inequality in
Theorem 1 and that equality holds if and only 
$\phi(z)$ is such that
the complex derivative takes the form 
\[ 
\phi'(z)=\frac{a}{(1-qz)^2}
\] 
for a pair of constants $a,b$. This means that $\phi$ is
is a Mšbius transform and hence $C$ must be a circle, i.e.
equality in Theorem 1 for a planar curve holds
if and only if $C$ borders a disc,








\bigskip

\centerline{\emph{B. Proof of Theorem 1.}}
\medskip




\noindent
The crucial step in the proof relies upon the following
result which is due to Weierstrass:
\medskip

\noindent
{\bf{B.1 Proposition.}}
\emph{Let $M$ be a minimal surface in $\mathcal S(C)$.
Then there exists an analytic function $F(u)$ in the open 
unit disc such that
points $(x,y,z)\in M$ are given by the equations:}
\[ 
x=\mathfrak{Re} \int\, (1-u^2) F(u)\,du
\quad\colon\quad
y=\mathfrak{Re}\int \, i(1+u^2)F(u)\,du\quad\colon\quad
z=\mathfrak{Re}\int \, 2F(u)\, du
\]
\medskip

\noindent
The proof of this result
occupies
five pages in [Weierstrass].
We remark that he employed
Riemann's mapping theoren for simply connected
domains
during the proof. Let us indicate some
details.
To begin with Weierstrass proved that there exists
a planar domain
$\Sigma$ with real coordinates
$(p,q)$ and a diffeomorphism
between
$M$ and $\Sigma$ which is conformal, i.e. 
$M$ is defined by the equations
\[ 
x=x(p,q)\quad\colon
y=y(p,q)\quad\colon z=z(p,q)\tag{i}
\]
where the 
vectors $(\frac{\partial x}{\partial p}, 
(\frac{\partial y}{\partial p}, (\frac{\partial x}{\partial p},)$
and
$(\frac{\partial x}{\partial q}, (\frac{\partial y}{\partial q}, (\frac{\partial z}{\partial q})$
are pairwise orthoginal unit vectors.
Moreover, when $M$ is minimal
the mean curvature of $M$ vanishes
which means that  the three functions in (1) are harmonic, i.e.
\[
\Delta(x)= \frac{\partial^2 x}{\partial p^2}+\frac{\partial ^2x}{\partial q^2}=0\tag{ii}
\]
and similarly for $y$ and $z$.
Next,
the harmonic functions above are real parts of analytic functions
which yields a triple $f,g,h$ in $\mathcal O(\Sigma)$
such that
\[ 
x= \mathfrak {Re}\, f(u)
\]
The orthogonality
of
the vectors ${\bf{v}}$ and ${\bf{w}}$ above entails via the
Cauchy Riemann equations that
\[
(f'(u))^2+(g'(u))^2+(h'(u))^2=0
\]


\medskip

\noindent
Starting from this, Weierstrass
used  sterographic projections and Riemann's conformal mapping theorem
to construct
an analytic function
$F(u)$ which gives the equations in Proposition B.1.
Admitting Weierstrass' result
the following hold:

\medskip

\noindent
{\bf{B.2 Propostion.}} \emph{
When the minimal surface $M$ is parametrized as in
Proposition B.1
one has the equations}
\[
\text{area}(M)=
\iint_D\, (1+|u|^2)^2\cdot |F(u)|^2\, d\xi d\eta\quad\colon\quad 
\ell(C)=2\cdot \int_0^{2\pi}\,  |F(e^{i\theta})|\, d\theta
\]
\medskip

\noindent
\emph{Proof.}
With $u=\alpha+i\beta$ this amounts to show that
\[ 
dx^2+dy^2+dz^2=
(1+|u|^2)|F(u)|^2\cdot (d\alpha^2+d\beta^2)\tag{i}
\]

\noindent
To prove  (i) we consider some point $u\in D$.
Set $F(u)= |F(u)|\cdot e^{i\theta}$
and $u= se^{i\alpha}$. With
$du=d\alpha$ real we have
\[
dx=\mathfrak{Re}(1-u^2)F(u))\cdot d\alpha=
|F(u)|\cdot  \bigl
(\cos\theta-|u|^2\cos\theta\cdot \cos 2\alpha
-|u|^2\sin\theta\cdot \sin 2\alpha\bigr)\cdot d\alpha
\]
Trigonometric formulas give
\[ 
(dx)^2=|F(u)|\cdot \bigl[\cos^2\theta+|u|^4\cos^2(2\alpha-\theta)-
2|u|^2\cos\theta\cdot \cos(2\alpha-\theta)\,\bigr]\cdot (d\alpha)^2\tag{i}
\]
\[
(dy)^2 =|F(u)|^2 \cdot  \bigl[\sin^2 \theta+|u|^4\sin^2(2\alpha-\theta)+
2|u|^2\sin\theta\cdot \sin(2\alpha-\theta)\bigr]\cdot d\alpha\tag{ii}
\]
\[ 
(dz)^2=4|F(u)|^2\cdot |u|^2\bigl(\cos^2(\theta-\alpha)]\cdot
(d\alpha)^2\tag{iii}
\]
\medskip

\noindent
Adding (i-ii) we get
\[
(dx)^2+(dy)^2= |F(u)|^2\cdot \bigl[1+|u|^4-
2\cdot|u|^2\cos(2\theta-2\alpha)\bigr]\cdot (d\alpha)^2
\]
Finally, the trigonometric formula
\[
4 \cos^2\phi=2-2\cos\,2\phi
\]
and (iii) entail that
\[
(dx)^2+(dy)^2+(dz)^2 = |F(u)|^2\cdot (1+|u|^2)^2\cdot (d\alpha)^2\tag{iv}
\]
\medskip

\noindent
The same infinitesmal equality as in (iv) 
is proved when
$u=id\beta$ for some small real $\beta$
and then we can read off 
Proposition B.2.





\bigskip



\centerline{ \emph{Final part of the proof}}
\medskip


\noindent
Put
$f_1(u) =F(u)u^2$ and
$f_2(u)=F(u)$. Proposition B.2 gives 
\[
\text{area}(M)=
\iint_D\,\bigl(\,|f_1(u)|^2+|f_2(u)|^2\,\bigr)\, d\xi d\eta+
2\cdot \iint_D\,|f_1(u)|\cdot |f_2(u)|\, d\xi d\eta\tag{i}
\]
Since $|f_1|=|f_2|= |F|$ holds on the unit circle we also get
\[
\ell(C)^2=
\bigl[ \int_0^{2\pi}\, |f_1(e^{i\theta})|\, d\theta\bigr ]^2+
\bigl[ \int_0^{2\pi}\, |f_2(e^{i\theta})|\, d\theta\bigr ]^2+
2\cdot  \int_0^{2\pi}\, |f_1(e^{i\theta})|\, d\theta\cdot
\int_0^{2\pi}\, |f_2(e^{i\theta})|\, d\theta\tag{ii}
\]
\medskip


\noindent
Using (i-ii) Carleman derived the isoperimetric  inequality
from the following:

\medskip

\noindent
{\bf {B.3 Lemma.}} \emph{For each pair of analytic functions $g,h$ in the unit disc
one has}
\[
\iint_D\,\bigl[g(u)|\cdot |h(u)|\, d\xi d\eta\leq
\frac{1}{4\pi}\cdot 
\int_0^{2\pi}\, |g(e^{i\theta})|\, d\theta\cdot 
\int_0^{2\pi}\, |h(e^{i\theta})|\, d\theta
\]
\medskip

\noindent
Let us first notice that  Lemma B.3 applied to the pairs $g=h=f_1$,
$g=h=f_2$ and the pair $g=f_1$ and $h=f_2$
together with (i-ii) give Theorem 1.
So there remains  to prove Lemma B.3.
We can write
\[ 
g=B_1\cdot g^*\quad\colon\quad h= B_2\cdot h^*
\]


\noindent
where $B_1,B_2$ are Blaschke products and the analytic functions
$g^*$ and $h^*$ are zero free in the unit disc.
Since
$|B_1|= |B_2|=1$ hold on the unit circle it suffices to prove
Lemma B.2 for the pair $g^*,h^*$,  i.e. we may assume that both $g$ and $h$
are zero-free.
Then they posses square roots so we
can find analytic functions $G,H$ in the unit disc where
\[
g=G^2\quad\colon\quad h=H^2
\]
Consider the Taylor series
\[
G(z)= \sum\, a_ku^k\quad\colon\quad H(z)= \sum\, b_ku^k
\]
Now $GH= \sum c_ku^k$
where
\[ 
c_k= a_0b_k+\ldots+a_kb_0\tag{i}
\]


\noindent
Using polar coordintes to perform double integrals it follows that

\[
\iint_D\,|G^2(u)|\cdot |H^2(u)|\, d\xi d\eta=
\pi\cdot \sum_{k=0}^\infty\, \frac{|c_k|^2}{k+1}
\]
At the same time one has
\[
\int_0^{2\pi}\, |G^2(e^{i\theta})|\, d\theta= 2\pi\cdot
\sum _{k=0}^\infty\, 
|a_k|^2
\]
with a similar formula for the integral of $H^2$.
Hence Lemma B.2 follows if we have proved the inequality
\[
\sum_{k=0}^\infty\, \frac{|c_k|^2}{k+1}\leq 
\sum _{k=0}^\infty\, 
|a_k|^2\cdot 
\sum _{k=0}^\infty\, 
|b_k|^2\tag{ii}
\]
To get (ii) we use (i) which for every $k$ gives:
\[
|c_k|^2\leq (|a_0||b_k|+\ldots+|a_k||b_0|)^2\leq
(k+1)\cdot (|a_0|^2|b_k|^2+\ldots+|a_k|^2|b_0|^2)
\]
Finally, a  summation over $k$ entails (ii) and Lemma B.3 is proved.












\newpage






\centerline {\bf{¤ 1. An inversion formula.}}

\bigskip

\noindent
A fundamental  result due to Abel gives an inversion formula for
the potential function
$U(x)$
in a conservative field of forces.
More precisely, let $U(x)$ be an even function of
$x$ with $U(0)=0$ and $x\to U(x)$ is stricitly increasing and convex
on $x\geq 0$.
A particle of unit mass which moves on
the real $x$-line satisfies Newton's equation
\[
\ddot x(t)=-U'(x(t))
\] 
where the initial conditions are $x(0)=0$ and $\dot x(0)= v>0$.
It follows that
\[
\frac{\dot x(t)^2}{2}+U(x(t))= \frac{v^2}{2}\implies
\dot x(t)=\sqrt{v^2-2U(x(t))}\tag{1}
\]
Here (1) holds
during a time interval $[0,T]$ where $\dot  x(t)>0$
when $0\leq t<T$ and
$\dot  x(T)=0$.
From (1) we get the equation
\[
T=\int_0^{x(T)}\, \frac{dx}{\sqrt{v^2-2U(x)}}\quad\colon\, 2\cdot U(x(T))=v^2
\]
With $U$ given this means that $T=T(v)$ is a function of $v$.
In a work from 1824, Abel established an inversion formula which
recaptures $U$ when the function
$v\mapsto T(v)$ is known.
The reader should consult the literature for this famous and
very
important result.
\medskip

\noindent
In the article \emph{Abelsche Intergalgleichung mot konstanten
Integralgrenzen}
[Mathematische Zeitschrift 1922], Carleman established
inversion formulas in Abel's spirit where one
example is as follows:
For every fixed real $0\leq x\leq 1$ 
\[ 
t\mapsto \log\,|x-t|
\]
is integrable on the unit interval $[0,1]$ and 
yields a bounded linear operator 
on the  Banach space $C^0[0,1]$
sending
every
$g\in C^0[0,1]$ to 
\[ 
T_g(x)= \int_0^1\, \log\,|x-t|\cdot g(t)\, dt
\]
It is not difficult to show that $T_g$ is injective.
less obvious is the
inversion formula below
which
at the same time gives
a description of the range of $T$.
\medskip

\noindent
{\bf{0.1 Theorem.}}
\emph{With $f=T_g$
one has the inversion formula}
\[
\sqrt{x(1-x)}\cdot g(x)= \frac{1}{\pi^2}\cdot
\int_0^1\, 
\frac{f'(t)\cdot \sqrt{t(1-t)}}{x-t}\,dt+\frac{1}{\pi}\cdot \int_0^1\,g(t)\, dt\tag{*}
\]
\medskip

\noindent
{\bf{Remark.}}
In (*) the first order derivative $f'(t)$ appears in an integral where we 
have taken a principal value.
The  inversion formula therefore shows that 
a function 
$f$ in the range of $T$ must satisfy certain regularity properties.





\medskip

\noindent
\emph{Proof of Theorem 0.1}.
For each $0\leq t\leq 1$. 
the
complex log-function 
\[
z\mapsto \log\, (z-t)
\]
is defined when
$z\in {\bf{C}}\setminus (-\infty,1]$ where
single-valued branches are chosen so that
the argument of these  log-functions stay in $(-\pi,\pi)$
and  $\log x-t$ is real if $x>t$. It follows that
\[
\lim_{\epsilon\to 0}\, \log (x+i\epsilon-t)=
 \log |x-t|+ \pi i\quad\colon x<t\tag{1}
 \]
where  the limit is taken as $\epsilon>0$ decrease to zero.
Let $g(t)$ be a continuous function on $[0,1]$ and
put
\[
 G(z)= \int_0^1\, \log(z-t)\cdot g(t)\, dt\tag{2}
\]
\medskip

\noindent
{\bf{A. Exercise.}} Show that  (1) gives:
\[
G(x+i0)=T_g(x)+\pi i\cdot \int_x^1\, g(t)\,dt \quad\colon 0< x<1\tag{i}
\]
where $G(x+i0)$ is the limit as $z=x+i\epsilon$ and $\epsilon>0$
decrease to zero.
Show in a similar way that
\[
G(x-i0)=T_g(x)-\pi i\cdot \int_x^1\, g(t)\,dt \quad\colon 0< x<1\tag{ii}
\]
\medskip

\noindent
Next, outside $[0,1]$
the complex derivative of $G$ becomes
\[ 
G'(z)=
\int_0^1\, \frac{g(t)}{z-t}\, dt
\]
Then (i-ii) give
\[
G'(x+i0)+G'(x-i0)= 2\cdot \frac{dT_g(x)}{dx}
\quad\colon
\quad
G'(x+i0)-G'(x-i0)=-2\pi \cdot g(x)\tag{iii}
\]
\medskip


\noindent
{\bf{B. The $\Phi$-function.}}
In ${\bf{C}}\setminus [0,1]$ we have
the analytic function $h(z)=\sqrt{z(z-1)}$
whose branch is chosen so that it is real and positive when
$z=x>1$. It follows that
\[
h(x+i0)=i\cdot \sqrt{x(1-x)}\quad\colon\quad
h(x-i0)=i\cdot \sqrt{x(1-x)}\quad\colon 0< x< 1 \tag{b.1}
\]
Consider the analytic function
\[
\Phi(z)=\sqrt{z(z-1)}\cdot G'(z)
\]
With $f=T_g$ we see
that (iii-iv) give the two equations

\[
\Phi(x+i0)+\Phi(x-i0)=2\pi\cdot \sqrt{x(1-x)}\cdot g(x)\tag{b.2}
\]
\[
\Phi(x+i0)-\Phi(x-i0)=2i\cdot f'(x)\cdot \sqrt{x(1-x)}\tag{b.3}
\]

\noindent
{\bf{C. The $\Psi$-function.}}
Set
\[
\Psi(z)=\int_0^1\, \frac{1}{z-t}\cdot
f'(t)\cdot \sqrt{t(1-t)}\,dt\tag{c.1}
\]
The equation (b.3)  and the general formula from ¤ XX give
\[
\Phi(x+i0)-\Phi(x-i0)=\Psi(x+i0)-\Psi(x-i0)\quad\colon\, 0<x<1\tag{c.2}
\]


\noindent
{\bf{D. Exercise.}}
Deduce from (c.2) that
\[ 
\Phi(z)= \Psi(z)+\int_0^1\,g(t)\, dt
\]
where the equality holds when
$z\in{\bf{C}}\setminus (-\infty,1]$ and
conclude from
the above that 
\[
2\pi\cdot \sqrt{x(1-x)}\cdot g(x)=\Psi(x+i0)+\Psi(x-i0)+2\cdot \int_0^1\,g(t)\, dt\tag{d.1}
\]


\noindent
Next,  (c.1 ) and the general formula in ¤ XX give
\[
\Psi(x+i0)+\Psi(x-i0)=\frac{2}{\pi}\cdot 
\int_0^1\, 
\frac{f'(t)\cdot \sqrt{t(1-t)}}{x-t}\,dt\tag{d.2}
\]
where the last integral is taken as a principal value.
Together  (d.1-2)  give (*) in  Theorem 0.1.


The proof will  show
that one also has the equation
\[
\int_0^1\,g(t)\, dt=-\frac{1}{2\pi\cdot \log 2}\cdot
\int_0^1\, \frac{f(x)}{\sqrt{(1-x)x}}\, dx\tag{**}
\]
\medskip







\newpage



\centerline{\bf{2. An extension of Weierstrass' approximation theorem.}}
\bigskip


\noindent
The result below was proved in
the article \emph{Sur un thŽorme de Weierstrass}
[Arkiv fšr mathematik och fysik. vol 20 (1927]:
\medskip

\noindent
{\bf{Theorem.}}
\emph{Let $f$ be a continuous and complex valued function on
the real $x$-line. To each $\epsilon>0$ there exists an
entire function $\phi(z)= \phi(x+iy)$
such that}
\[ 
\max_{x\in{\bf{R}}}\, |f(x)-\phi(x)|<\epsilon
\]



\medskip

\noindent
Carleman gave an 
elementary proof using Cauchys integral formula.
But his  constructions can be extended to 
cover a more general situation which goes as follows.
Let $K$ be an unbounded  closed null\vvv set in ${\bf{C}}$.
If $0<R<R^*$ we put
\[
K[R,R^*]= K\cap \{ R\leq |z|\leq R^*\}
\]
and if  $R>0$ 
we put
$K\uuu R= K\cap \bar D\uuu R$ where
$\bar D\uuu R=\{|z|\leq R\}$.

\medskip

\noindent
{\bf{2.1 Theorem.}}
\emph{Suppose  there exists a strictly increasing sequence $\{R\uuu\nu\}$
where $R\uuu\nu\to +\infty$ such that 
${\bf{C}}\setminus K\uuu{R\uuu 1}$ and the sets}
\[ 
\Omega\uuu\nu={\bf{C}}\setminus \bar D\uuu {R\uuu \nu}\,\cup K[R\uuu\nu,
R\uuu{\nu+1}]
\] 
\emph{are connected for each $\nu\geq 1$.
Then every continuous function on $K$ can be uniformly approximated by entire functions.}
\bigskip


\noindent
To prove this result we first establish the following.

\medskip

\noindent {\bf{2.2 Lemma.}}
\emph{Consider some $\nu\geq 1$
a continuous function
$\psi$  on 
$S= \bar D\uuu{R\uuu n}\cup\, K[R\uuu \nu,R\uuu{\nu+1}]$
where $\psi$ is analytic in the open disc $D\uuu{R\uuu\nu}$.
Then $\psi$ can be uniformly approximated on $S$ by polynomials in $z$.}

\medskip

\noindent 
\emph{Proof}.
If 
we have found a sequence of polynomials
$\{p\uuu k\}$ which approximate $\psi$ uniformly on
$S\uuu *=\{|z|=R\uuu\nu\}\cup K[R\uuu \nu,R\uuu{\nu+1}]$
then this sequence approximates $\psi$ on $S$. In fact, this follows since
$\psi$ is analytic in the disc $D\uuu{R\uuu \nu}$
so by the maximum principle for analytic functions in a disc
we have
\[
||p\uuu k\vvv\psi||\uuu S=
||p\uuu k\vvv\psi||\uuu {S\uuu *}
\] 
for each $k$.
Next, if uniform approximation on $S\uuu *$ fails
there exists a Riesz\vvv measure $\mu$ supported by
$S\uuu *$ which is $\perp$ to all analytic polynomials while
\[
\int\, \psi\cdot d\mu\neq 0\tag{1}
\]
To see that this cannot occur we consider the Cauchy transform
\[
\mathcal C(z)=\int\, \frac{d\mu(\zeta)}{z\vvv\zeta}
\]
Since $\int\, \zeta^n\cdot d\mu(\zeta)=0$ for every $n\geq 0$
we see that $\mathcal C(z)=0$ in the exterior disc
$|z|> R\uuu{\nu+1}$.
The connectivity hypothesis implies that
$\mathcal C(z)=0$ in the whole open complement of $S$.
Now $K$ was a null set which means that the
$L^1\uuu{\text{loc}}$\vvv function 
$\mathcal C(z)$ is zero in the exterior disc
$|z|>R\uuu\nu$ and hence its distribution derivative
$\bar\partial(\mathcal C\uuu\nu)$ also vanishes in this exterior disc.
At the same time we have the equality
\[ \bar\partial(C\uuu\nu)= \mu
\]
We conclude that the support of $\mu$ is confined to the circle
$\{|z|=R\uuu\nu\}$.
But then (1) cannot hold since
the restriction of $\psi$ to
this circle by assumption extends to be analytic in the disc
$D\uuu {R\uuu\nu}$ and therefore can be uniformly approximated by
polynomials on the circle.

\medskip

\noindent
\emph{Proof of Theorem 2.1.}
Let $\epsilon>0$ and
$\{\alpha\uuu \nu\}$ is a sequence of positive numbers such that
$\sum\,\alpha\uuu\nu<\epsilon$.
Consider some $f\in C^0(K)$. Starting with the set
$K\uuu{R\uuu 1}$
we use the assumption that its complement is connected
and using   Cauchy transforms as in  Lemma A.3
one shows that the restriction of $f$ to this compact set
can be uniformly approximated by polynomials. So we find
$P\uuu 1(z)$ such that
\[
||P\uuu 1\vvv f||\uuu {K\uuu{R\uuu 1}}<\alpha\uuu 1\tag{i}
\]
From (i) one easily construct a continuous function
$\psi$ on $\bar D\uuu{R\uuu 1}\cup K[R\uuu 1,R\uuu 2]$
such that
$\psi=P\uuu1 $ holds in the disc
$\bar D\uuu{R\uuu 1}$ and
the maximum norm
\[
||\psi\vvv f||\uuu { K[R\uuu 1,R\uuu 2]}\leq \alpha\uuu 1
\]
Lemma A.3 gives a polynomial $P\uuu 2$ such that
\[
||P\uuu 2\vvv P\uuu 1||\uuu {D\uuu{R\uuu 1}}<\alpha\uuu 2
\quad\text{and}\quad 
||P\uuu 2\vvv f||\uuu {K[R\uuu 1,R\uuu 2]}\leq
\alpha\uuu 1+\alpha\uuu 2
\]
Repeat the construction where Lemma A.3 is used as $\nu$ increases.
This gives
a sequence of polynomials $\{P\uuu\nu\}$
such that
\[
||P\uuu \nu \vvv P\uuu {\nu\vvv 1}||\uuu {D\uuu{R\uuu \nu }}<\alpha\uuu \nu
\quad\text{and}\quad 
||P\uuu\nu\vvv f||\uuu {K[R\uuu {\nu\vvv 1},R\uuu \nu]}<
\alpha\uuu 1+\ldots+\alpha\uuu\nu
\]
hold for all $\nu$.
From this it is easily seen that we obtain an entire function
\[ 
P^*(z)= P\uuu 1(z)+\sum\uuu{\nu=1}^\infty
P\uuu{\nu+1}(z)\vvv P\uuu\nu(z)
\]
Finally the reader can check that the inequalities above imply that
the maximum norm
\[
 ||P^*\vvv f||\uuu K\leq \alpha\uuu 1+ \sum\uuu{\nu=1}^\infty\,\alpha\uuu\nu
\]
Since the last sum is $\leq 2\epsilon$ and $\epsilon>0$ was arbitrary
we have proved Theorem A.3.

 
\bigskip




\noindent
{\bf 2.3 Exercise.}
Use similar methods as above to show that if
$f(z)$ is analytic in the upper half plane
$U^+=\mathfrak{Im}(z)>0$
and has continuous boundary values on the real line, then
$f$ can be uniformly approximated by an entire function, i.e. to
every $\epsilon>0$ there exists an entire function
$F(z)$ such that
\[
\max_{z\in U^+}\, |F(z)-f(z)|\leq\epsilon
\]

\newpage


\centerline {\bf{3. An inequality for differentiable functions.}}
\bigskip

\noindent
The result below 
was proved  in 
the article \emph{Sur un thŽorme de M. Denjoy}
[C.R. Acad. Sci. Paris 1922]

\medskip

\noindent
{\bf{3.1 Theorem.}}
\emph{There exists an absolute constant $\mathcal C$
such that the inequality below holds
for every pair $(f,n)$, where $n$ is a positive integer
and $f$
a non-negative real-valued $C^\infty$- function 
defined on  the closed unit interval $[0,1]$
whose  derivatives up to order $n$ vanish at the
two end points.}
\[
\sum_{\nu=1}^{\nu=n}\,
\,\frac{1}{[\beta_\nu]^{\frac{1}{\nu}}}\leq
\mathcal C\cdot\int_0^1\,f(x)dx\quad\colon\quad
\beta_\nu=\sqrt{\int_0^1\, [f^{(\nu)}(x)]^2\cdot dx}\tag{*}
\]

\noindent
{\bf{Remark.}}
The proof below shows that one can take
\[ 
C\leq 2e\pi\cdot  (1+
\frac{1}{4\pi^2 e^2-1})\tag{*}
\]
The best constant $\mathcal C_*$ which would give
\[
\sum_{p=1}^{p=n}\,
\frac{1}{\beta_p(f)}\leq\mathcal C^*\tag{i}
\]
for all pairs $(f,n)$  is not known.
Let us also remark that 
the inequality (*)
is sharp in the sense that there exists a constant $C_*$
such that  for every $n\geq 2$ there exists a 
function $f_n(x)$ as above so that 
the opposed inequality
(*) holds with $C_*$. Hence
(*) 
demonstrates
that the standard cut-off  functions which are used
in  many applications 
to keep maximum norms of derivatives small up to
order $n$ small, are optimal up to a constant.
So the theoretical result in (*)
plays 
a role in numerical analysis where one often uses smoothing
methods.
The  proof  of (*) 
employs
estimates for harmonic measures
applied to the subharmonic Log-function of the absolute value of the
Laplace transform of $f$, i.e. via a "detour into the complex domain"
which in 1922 appeared as a  "revolutionary method".

\bigskip
 
\centerline{\emph{Proof of Theorem 3.1}.}
\medskip


\noindent
Let $n\geq 1$ and 
keeping $f$ fixed we put $\beta_p=\beta_p(f)$
to simplify notations. 
Using partial integrations and the Cauchy-Schwarz inequality 
one shows that the
$\beta$-numbers are non-decreasing. i.e. 
\[ 
1=\beta_0\leq\beta_1\leq \ldots\leq \beta_{n+1}\tag{*}
\]
Define the complex Laplace transform
\[ 
\Phi(z)=\int_0^1\, e^{-zt}f(t) dt
\]
Since $f$ by assumption is $n$-flat at the end-ponts, 
integration by parts $p$ times  gives:
\[
 \Phi(z)=z^{-p}\int_0^1\, e^{-zt}\cdot \partial^p(f^2)(t) dt\quad\colon\quad 1\leq p\leq n+1
\]
where
$\partial^p(f^2)$ is the derivative of order $p$ of $f^2$.
We have
\[
\partial^p(f^2)=\sum_{\nu=0}^{\nu=p}\, \binom  {p}{\nu}\cdot
f^{(\nu)}\cdot f^{(p-\nu)}\quad\colon\,
1\leq p\leq n+1 \tag{1}
\]
Now we  study the absolute value of $\Phi$ on the vertical
line $\mathfrak{Re}(z)=-1$. 
Since $|e^{t-iyt}|= e^t$
for all $y$, the triangle inequality gives
\[ 
|-1+iy|^p\cdot |\Phi(-1+iy)|\leq
\sum_{\nu=0}^{\nu=p}\, \binom  {p}{\nu}\cdot
\int_0^1\, e^t\cdot |f^{(\nu)}(t)|\cdot |f^{(p-\nu)}(t)|\cdot dt\tag{2}
\]
Since  $e^t\leq e$ on $[0,1]$, the 
Cauchy-Schwarz inequality and 
the definition of the $\beta$-numbers give:
\[
|-1+iy|^p\cdot |\Phi(-1+iy)|\leq e\cdot 
\sum_{\nu=0}^{\nu=p}\, \binom  {p}{\nu}\cdot
\beta_\nu^\nu\cdot \beta_{p-\nu}^{p-\nu}\tag{3}
\]
From (*) it follows that
$\beta_\nu^\nu\cdot \beta_{p-\nu}^{p-\nu}\leq \beta_p^p$
for each $\nu$ and since
$\sum_{\nu=0}^{\nu=p}\, \binom  {p}{\nu}=2^p$ we obtain
\[
|-1+iy|^p\cdot |\Phi(-1+iy)|\leq e\cdot 2^p\cdot \beta_p^p\tag{4}
\]
Passing to the logarithm we get
\[
\log\, |\Phi(-1+iy)|\leq 1+p\cdot \log\,\frac{2\beta_p}{|-1+iy|}\tag{5}
\]
Here (5) holds when $1\leq p\leq n+1$ and 
the assumption that $\beta_0=1$ also gives
\[
\log\, |\Phi(-1+iy)|\leq 1\tag{6}
\]

\noindent
{\bf{The $\omega$-function}}.
To each $1\leq p\leq n+1$
we find a positve number $y_p$ such that
\[
|-1+iy_p|=2e\beta_p
\]
Now we define a function $\omega(y)$ where
$\omega(y)=0$ when $y<y_1$ and
\[
\omega(y)=p\quad\colon\quad y_p\leq y<y_{p+1}
\]
and finally $\omega(y)=n+1$ when $y\geq y_{n+1}$.
Then (5-6) give
the inequality
\[
\log\,|\phi(-1+iy)|\leq 1-\omega(y)
\quad\colon\,-\infty<y<+\infty
\tag{7}
\]

\medskip

\noindent
\emph { A harmonic majorisation.}
With $1-\omega(y)$ as boundary function in the half-plane
$\mathfrak{Re}(z)>-1$
we construct the harmonic extension $H(z)$
which by
Poisson's formula is given by:
\[ 
H(0)=
\frac{1}{\pi}\int_{-\infty}^\infty\, \frac{1-\omega(y)}{1+y^2}\cdot dy
\]
Now  $\log\,|\Phi(z)|$ is subharmonic in this half-plane and hence
(7) gives:
\[
0=\log|\Phi(0)|\leq H(0)
\]
We conclude that
\[
\int_{-\infty}^\infty\, \frac{\omega(y)}{1+y^2}\cdot dy
\leq \pi\tag{8}
\]
Since  $\omega(y)=0$ when $y\leq y_1$ we see that
(8) gives the inequality
\[
\int_{y_1}^\infty\, \frac{\omega(y)}{y^2}\cdot dy
\leq \frac{y_1^2}{1+y_1^2}\cdot \pi\tag{9}
\]
The construction of the $\omega$-function gives the equation 
\[
\int_{y_1}^\infty\, \frac{\omega(y)}{y^2}\cdot dy
=\frac{1}{y_1}+\ldots+\frac{1}{y_{n+1}}\tag{10}
\]
\medskip

\noindent
Next, the construction of the $y_p$-numbers entail that
$y_p\leq 2e\beta_p$ so (9-10) 
give
\[
\frac{1}{\beta_1}+\ldots+\frac{1}{\beta_{n+1}}\leq
2e\pi\cdot  
\frac{1}{1+\frac{1}{y_1^2}}\tag{11}
\]

\noindent
Finally, we have $1+y_1^2=4e^2\beta_1^2$ and 
recall that Writinger's inequality
implies that $\beta_1\geq \pi$. Hence
\[
\frac{1}{1+\frac{1}{y_1^2}}\leq
1+\frac{1}{4\pi^2e^2-1}\tag{12}
\]
and then (11-12) give the requested inequality in Theorem 2.1.
\bigskip












\newpage

\centerline {\bf {4. An inequality for
inverse Fourier transforms in $ L^2({\bf{R^+}})$.}}
\medskip

\noindent 
By Parsevel's theorem the Fourier transform sends $L^2$-functions 
on the $\xi$-line to $L^2$-functions on the $x$-line.
Consider
the class of non-negative $L^2$-functions $\phi(x)$
such that there exists
an $L^2$-function $F(\xi)$ supported by the half-line  $\xi\geq 0$ and
\[ 
\phi(x)=\bigl|\,\int_0^ \infty\,
e^{ix\xi}\cdot F(\xi)\cdot d\xi\bigr|\tag{*}
\]


\noindent
The theorem  below was proved in [Carleman:xx] which 
apart from  applications  to 
quasi-analytic functions    has several
other consequences which are put forward by
Paley and Wiener in their text-book
[Pa-Wi]. The 
proof  
employs a detour in the complex domain
where   Jensen's formula plays a crucial role.

\bigskip



\noindent
{\bf 4.1 Theorem. } \emph{An $L^2$-function $\phi(x)$
satisfies (*) if and only if}
\[
\int_{-\infty}^\infty\, \log^+\bigl [\,\frac{1}{\phi(x)}\,\bigr ]
\cdot \frac{dx}{1+x^2}<\infty\tag{i}
\]
\emph{Moreover, when (*) holds and
$F(\xi)$ satisfies the 
weighted mean-value equality}
\[ 
\int_0^\infty\, F(\xi)\cdot e^{-\xi}\ d\xi=1\tag{ii}
\]
then 
\[
\int_{-\infty}^\infty\, \log^+\bigl [\,\frac{1}{\phi(x)}\,\bigr ]
\cdot \frac{dx}{1+x^2}\leq 
\int_{-\infty}^\infty\, \frac{\phi(x)^2}{1+x^2}\cdot dx\tag{iii}
\]
\medskip

\noindent
\emph{Proof.}
First we prove the suffiency.
Let  $\phi(x)$ be  a non-negative  $L^2$-function where the  integral  
(i)  is finite.
The harmonic extension of
$\log\,\phi(x)$ to the upper half-plane is given by:
\[
\lambda(x+iy)=\frac{y}{\pi}\cdot 
\int_{-\infty}^\infty\, \frac{\log\,\,\phi(t)}{(x-t)^2+y^2}\cdot dt
\quad\colon\, y>0\tag{1}
\]


\noindent Let $\mu(z)$ be the conjugate harmonic function of
$\lambda$ and set
\[
h(z)=e^{\lambda(z)+i\mu(z)}\tag{2}
\]


\noindent
Fatou's theorem gives  for almost every $x$ 
a limit
\[
\lim_{y\to 0}\,\lambda(x+iy)=\log\,\,\phi(x)\tag{3}
\]
Or, equivalently
\[
\lim_{y\to 0}\,|h(x+iy)|=\phi(x)\tag{4}
\]


\noindent
From (1) and the fact that the geometric mean value of positive numbers
cannot exceed their arithmetic mean value, one has
\[
\bigl |h(x+iy)\,\bigr |= e^{\lambda(x+iy)}\leq\frac{y}{\pi}\cdot
\int_{-\infty}^\infty\, \frac{\phi(t)}{(x-t)^2+y^2}\cdot dt
\quad\colon\, y>0\tag{5}
\]


\noindent
Then (5) the Schwarz inequality give:
\[
\int_{-\infty}^\infty\, \bigl |h(x+iy)\,\bigr |^2\,dx\leq
\int_{-\infty}^\infty\, \bigl |\phi(x)\,\bigr |^2\,dx\quad\colon\, y>0\tag{6}
\]
Here  $h(z)$ is analytic in the upper half-plane
so that (6) and Cauchy's formula entail that
if $\xi<0$, then the integrals
\[
 J(y)=
\int_{-\infty}^\infty\, h(x+iy)\cdot e^{-ix\xi+y\xi}\cdot dx\quad\colon\ y>0\tag{7}
\]
are independent of $y$. Passing to the limit as $y\to\infty$ and 
using the uniform upper bounds on the $L^2$-norms of 
the functions $h_y(x)\mapsto h(x+iy)$,
it follows that $J(y)$ vanishes identically.
So the Fourier transforms of
$h_y(x)$ are supported by $\xi\geq 0$ for all $y>0$.
Passing to the limit as $y\to 0$ the same holds for
the Fourier transform of $h(x)$. Finally (4) gives
\[
\phi(x)=|h(x)|\tag{8}
\]
By Parseval's theorem
$\widehat h(\xi)$ is an $L^2$-function and hence
$\phi(x)$ has  the requested form (*).


\medskip







\noindent
{\emph{Necessity.}
Since $F$ is in $L^2$ there exists the Plancherel limit
\[ 
\psi(x)=\lim_{N\to\infty}
\,\frac{1}{2\pi}\cdot\int_0^N\,
e^{ix\xi}\cdot F(\xi)\, d\xi\,\tag{9}
\]
and in
the upper half plane we  get the analytic function
\[ 
\psi(x+iy)=
\,\frac{1}{2\pi}\cdot\int_0^\infty\,
e^{ix\xi -y\xi}\cdot F(\xi)\, d\xi\tag{10}
\]



\noindent
Suppose that  $F(\xi)$ satisfies (ii) in the  Theorem which gives
\[ 
\psi(i)=1
\]
Consider the conformal map from the upper half-plane into the unit disc where
\[ 
w=\frac{z-i}{z+i}
\]
Here  $\psi(x)$ corresponds to a function
$\Phi(e^{is})$ on the unit circe $|w|=1$ and:
\[ 
\int_{-\pi}^\pi\, |\Phi(e^{is})|^2 \, ds=
2\cdot\int_{-\infty}^\infty\,\frac{|\phi(x)|^2}{1+x^2}\, dx\tag{11}
\]


\noindent
Similarly let $\Psi(w)$ be the analytic function in
$|w|<1$ which corresponds to $\psi(z)$. From (10-11)  it follows that
$\Psi(w)$ is the Poisson extension of $\Phi$, i.e.
\[ 
\Psi(w)=
\frac{1}{2\pi}\
\int_{-\pi}^\pi\, \,\frac{1-|w|^2}{
|e^{is}-w|^2}\cdot \Phi(e^{is})\cdot ds\tag{12}
\]
If $0<r<1$ it follows that
\[
\frac{1}{2\pi}\
\int_{-\pi}^\pi\, \log^+\,|\Psi(re^{is}|\cdot ds\leq
\frac{1}{2\pi}\
\int_{-\pi}^\pi\, \bigl |\Psi(re^{is}\bigr |^2\cdot ds\leq
\frac{1}{2\pi}\
\int_{-\pi}^\pi\, \Phi(e^{is}|^2\cdot ds\tag{13}
\]


\noindent 
Now  (12) gives:
\[
\lim_{r\to 1}\,\Psi(re^{is})=\Phi(e^{is})\quad\colon\,
\text{almost everywhere}\quad 0\leq s\leq 2\pi\tag{14}
\]


\noindent 
Next, since
$\psi(i)=1$ we have  $\Psi(0)=1$ which
gives the inequality
\[
\int_{-\pi}^\pi\, \log^+\frac{1}{\,|\Psi(re^{is}|}\cdot ds\leq
\int_{-\pi}^\pi\, \log^+\,|\Psi(re^{is}|\cdot ds\quad\colon 0<r<1\tag{15}
\]


\noindent
By (13-15) a passage to the limit as $r\to 1$ gives
\[
\int_{-\pi}^\pi\, \log^+\frac{1}{\,|\Phi(e^{is}|}\cdot ds\leq
\int_{-\pi}^\pi\, \bigl |\,\Phi(e^{is}\bigr |^2\cdot ds\tag{16}
\]
\medskip

\noindent
Returning to the real $x$-line  the inequality (iii) follows 
which at the same time finishes the proof of the theorem.







\newpage


\centerline {\bf{5. The Bergman kernel.}}
\medskip

\noindent
Let $\Omega$ be a bounded and simply
connected domain in ${\bf{C}}$.
If $a\in\Omega$ a  result due to Stefan Bergman
gives  the conformal mapping
function $f_a\colon \Omega\to D$
via the kernel function of the Hilbert space
$H^2(\Omega)$.
\medskip

\noindent
{\bf{5.1 Bergman's  Theorem.}}
\emph{The conformal map $f_a$ is given by}
\[ 
f_a(z)= \sqrt{\frac{\pi}{K(a,a)}}
\cdot \int_a^z\, K(z,a)\, dz
\]

\medskip

\noindent
{\bf{Remark.}}
Recall that Bergman's kernel function
$K(z,\zeta)$ satisfies
\[
f(z)= \int_\Omega\, K(z,\zeta)\cdot f(\zeta)\, d\xi d\eta
\]
for every square integrable analytic function $f$ in
$\Omega$.
This is a Hilbert space denoted by
$H^2(\Omega)$.



\medskip

\noindent
The  Gram-Schmidt construction gives
an orthonormal basis $\{P_n(z)\}$
in $H^2(\Omega)$
where  $P_n(z)$ is a polynomial of
degree $n$ and
\[ 
\iint_\Omega \, P_k\cdot \bar P_m\cdot dxdy=
\text{Kronecker's delta function}
\]
It follows that
\[
K(z,\zeta)=\sum\, P_n(z)\cdot \overline{P_n(\zeta)}
\]

\noindent
Bergman's result  indicates
that the polynomials above are related to
a conformal mapping.
We shall consider the case
when
$\Omega$ is a Jordan domain whose boundary
curve
$\Gamma$ is \emph{real-analytic}.
Let $\phi$
be the conformal map
from the \emph{exterior domain}
$\Omega^*=\Sigma\setminus\bar\Omega$ onto
the exterior disc $|z|>1$.
Here $\phi$ is normalised so that it maps the point at infinity
into itself.
The inverse conformal mapping function
$\psi$   is defined in $|z|>1$ and has a series expansion
\[ 
\psi(z)=\tau\cdot z+ \tau_0+\sum_{\nu=1}^\infty\, \tau_\nu\cdot
\frac{1}{z^\nu}\tag{*}
\]
where $\tau$ is a positive real number.
The assumption that $\Gamma$ is real-analytic gives
some $\rho_1<1$ such that
$\psi$ extends to a conformal map from the
exterior disc $|z|>\rho_1$ onto a domain whose compact
complement is contained in $\Omega$.
\medskip

\noindent
Inspired by Faber's article \emph{†ber Tschebyscheffsche
Polynome} [Crelle. J. 1920], Carleman
proved an asymptotic result  in
the article \emph{†ber die approximation analytischer funktionen
durch linearen aggregaten von vorgegebenen potenzen} [Arkiv fšr matematik och fysik. 1920].
\bigskip

\noindent
{\bf{5.2 Theorem.}}
\emph{There exists a constant $C$ which depends upon $\Omega$ only
such that to every
$n\geq 1$ there is an analytic  function $\omega_n(z)$ defined in
$\Omega^*$ and}
\[
 P_n(z)=
 \sqrt{\frac{n+1}{\pi}}
 \cdot \phi'(z)\cdot \phi(z)^n\cdot
 \bigl(1+\omega_n(z)\bigr)
 \quad\colon z\in \partial \Omega
 \]
\emph{where }
\[ 
\max_{z\in\partial \Omega}\,\, |\omega_n(z)|\leq
C\cdot \sqrt{n}\cdot \rho_1^n\quad\colon\quad n=1,2,\ldots
\]

\medskip



\centerline {\emph{Proof.}}
\medskip


\noindent
For each $n\geq 2$ we denote by $\mathcal M_n$ the space of monic polynomials
of degree $n$:
\[ 
Q(z)= z^n+b_{n-1}z^{n-1}+\ldots +b_0
\]
Put 
\[ 
I(Q)=  \iint_ \Omega\, |Q(z)|^2\,  dxdy
\]
and with $n$ kept fixed we set 
\[ 
I_ *(n)=\min_{Q\in \mathcal M_n} \,I(Q)
\]
To each $Q$ we introduce the
primitive polynomial 
\[ 
\widehat{Q}(z)=\frac{z^{n+1}}{n+1}+ \frac{b_ {n-1}}{n}z^n+\ldots+b_0z
\]
\medskip

\noindent
{\bf{1. Exercise.}} Use Green's formula to show that
\[
I(Q)=\frac{1}{4}\int_ {\partial \Omega}\, |\partial_ n(\widehat{Q})|^2\, ds
\] 
where $ds$ is the arc-length measure on $\partial\Omega$
and we have taken the outer normal derivative of
$\widehat{Q}$.
Next,  take the inverse conformal  map $\psi(\zeta)$ in (*) and set
\[ 
F(\zeta)= \widehat{Q}(\psi(\zeta))
\]
Then $F$ is analytic in the exterior disc $|\zeta|>1$
and by (*) above,
$F$ has a series expansion
\[
F(\zeta)=\tau^{n+1}\bigl[ \frac{\zeta^{n+1}}{n+1}+
A_n\zeta^n+\ldots+A_ 1\zeta+A_ 0+
\sum_{\nu=1}^\infty\, \alpha_\nu\cdot \zeta^{-\nu}\bigr]\tag{1.1}
\]


\noindent
{\bf{2. Exercise.}}
Use a variable substitution via $\psi$ to show that
\[
I(Q)= \int_ {|\zeta|= 1}\, \frac{d}{dr}( |F(e^{i\theta})|^2)\, d\theta
\]
Show also that  the series expansion (1.1) identifies 
the right hand side with
\[ 
\pi\cdot \tau^{2n+2}\cdot [\frac{1}{n+1}+ \sum_{k=1}^{k=n}\,
k\cdot |A_k|^2-
\sum_{\\nu=1}^\infty\, \nu\cdot |\alpha_\nu|^2\,\bigr]\tag{2.1}
\]
\medskip

\noindent
{\bf{3. An upper bound for $I_ *(n)$}}.
In (2.1) the coefficients $A_ 1,\ldots,A_ n$ are determined via $Q$
and
the reader may verify that there exists  $Q\in\mathcal M_n$
such that
$A_ 1=\ldots=A_ n=0$.
It follows that
\[
I_ *(n)\leq \pi\cdot \tau^{2n+2}\cdot [\frac{1}{n+1}
-
\sum_{\nu=1}^\infty\, \nu\cdot |\alpha_\nu|^2\,\bigr]
\leq \pi\cdot \tau^{2n+2}\cdot \frac{1}{n+1}\tag{3.1}
\]


\noindent
{\bf{4. A lower bound for $I_ *$}}.
The upper bound (3.1) did not use that
$\partial\Omega$ is real- analytic, i.e. (3.1)  is valid for
every Jordan domain whose boundary curve is of class $C^1$.
To get a lower bound we use the constant $\rho-1<1$ from the above
and choose  $\rho_ 1<\rho<1$. Now
$\psi$
maps the exterior disc
$|\zeta|>\rho$ conformally to an exterior domain
$U^*=\Sigma\setminus \bar U$ where $U$  is a relatively compact
Jordan  domain inside $\Omega$.
Choose  $Q_n\in\mathcal M_n$
so that
\[
I(Q_n)=I_ *(n)
\]
Since  $\Omega\setminus \bar U\subset \Omega$  we have
\[
I_*> \iint_{\Omega\setminus \bar U}\,|Q_n(z)|^2\, dxdx\tag{4.1}
\]


\noindent
{\bf{5. Exercise.}}
Show that (4.1)  is equal to
\[
\int_ {|\zeta|= 1}\, \frac{d}{dr}( |F(e^{i\theta})|^2\cdot d\theta
-
\int_ {|\zeta|= \rho}\, \frac{d}{dr}( |F(e^{i\theta})|^2\cdot \rho\cdot d\theta=
\]
\[
\pi\cdot \tau^{2n+2}\cdot 
[\frac{1- \rho^{2n+2}}{n+1}+ 
\sum_{k=1}^{k=n}\,
k\cdot |A_ k|^2\cdot (1- \rho^{2\nu})+
\sum_{\\nu=1}^\infty\, \nu\cdot |\alpha_\nu|^2
\cdot (\frac{1}{\rho^{2\nu}}-1)\,\bigr]
\]
\medskip

\noindent
and conclude that
one has the
lower bound
\[ 
I_ *(n)\geq\frac{\pi}{n+1}\cdot \tau^{2n+2}\cdot (1- \rho^{2n+2})
\tag{5.1}
\]
\medskip

\noindent
Together (4.1) and (5.1)
give the inequality
\[
\sum_ {k=1}^{k=n}\,
k\cdot |A_ k|^2\cdot (1- \rho^{2\nu})+
\sum_{\nu=1}^\infty\, \nu\cdot |\alpha_\nu|^2
\cdot (\frac{1}{\rho^{2\nu}}- 1)\,\leq \frac{\pi}{n+1}\cdot \rho^{2n+2}\tag{5.2}
\]
Since $1- \rho^2\leq 1- \rho^{2\nu}$ for every $\nu\geq 1$
it follows that
\[
\sum_{k=1}^{k=n}\,
k\cdot |A_ k|^2+
\sum_{\nu=1}^\infty\, \nu\cdot |\alpha_\nu|^2\leq
\frac{\pi}{(1-\rho^2)\cdot n+1}\cdot \rho^{2n+2}\tag{5.3}
\]
\medskip

\noindent
{\bf{6. Conclusion.}}
Recall that $F(\zeta)= \widehat{Q_n}(\psi(\zeta)$.
So after a derivation 
we get
\[ 
F'(\zeta)= \psi'(\zeta)\cdot Q_n(\psi(\zeta))
\]
Hence the series expansion  of $F(\zeta)$ gives
\[
Q_n(\psi(\zeta))=
\frac{\tau^{n+1}}{\psi'(\zeta)}\cdot \bigl[
\zeta^n+
\sum_ {k=1}^{k=n}\, k\cdot A_ k\zeta^{k- 1}
+\sum_{\nu=1}^\infty \, \nu\cdot \alpha_\nu \cdot \zeta^{- \nu- 1}\,\bigr]\tag{6.1}
\]
where the equality holds for $|\zeta|>\rho$.
Put

\[
\omega^*(\zeta)=
\sum_{k=1}^{k=n}\, k\cdot A_ k\zeta^{k- 1}
+\sum_ {\nu=1}^\infty \, \nu\cdot \alpha_\nu \cdot \zeta^{-\nu- 1}
\]
When $|\zeta|=1$ the triangle inequality gives
\[
|\omega^*(\zeta)|\leq
\sum_{k=1}^{k=n}\, k\cdot |A_ k|
+\sum_{\nu=1}^\infty \, \nu\cdot |\alpha_\nu| \tag{6.2}
\]
\medskip

\noindent
{\bf{7. Exercise.}}
Notice  that (5.3) holds for every $ \rho>\rho_ 1$
and use this together with suitable Cauchy-Schwarz inequalities to show that
(6.1)  gives a constant $C$ which is independent of $n$ such that
\[
|\omega^*(\zeta)|\leq C\cdot  \sqrt{n}\cdot \rho_ 1^{n+1}\tag{7.1}
\]

\medskip

\noindent
\emph{Final part of the proof.}
Since $\psi$ is the inverse of $\phi$ we have
\[
\psi'(\phi(z))\cdot Q_n(\psi(\phi(z)= \frac{Q_n(z)}{\phi'(z)}
\]
Define the function  on $\partial\Omega$ by
 \[
\omega_ n(z)=\frac{\omega^*(\phi(z))}{\phi'(z)}\tag{i}
\]
Then (6.2) gives
\[
Q_n(z)= \tau^{n+1}\cdot \phi'(z)\cdot [\phi(z)^n+\omega_n(z)\,\bigr]\tag{ii}
\]
where Exercise 7 shows that $|\omega_ n(z)|$ satisfies the estimate in
Theorem 2.
Finally, the polynomial $Q_n$ minimized the $L^2$-norm
under the constraint  that the leading term is $z^n$ and for this variational problem
the upper and the lower bounds in (4.1-5.1) imply that
\[ 
|I_ *(n)-\frac{\pi}{n+1}\cdot \tau^{2n+2}|\leq 
\frac{\pi}{n+1}\cdot \tau^{2n+2}\cdot \rho^{2n+2}
\]
If we normalise $Q_n$ so that its $L^2$-norm is one gets a
polynomial $P_ n(z)$ where 
the factor $\tau^{n+1}$
is replaced by
$\frac{\sqrt{n+1}}{\sqrt{\pi}}$ which finishes the proof of
Theorem B.









\newpage


\centerline {\bf{6. Partial sums of Fourier series.}}
\bigskip

\noindent
Let $f(x)$ be a continuous function on
$0\leq x\leq 2\pi$ with $f(0)= f(2\pi)$  and consider the 
Fourier series
\[ 
f(x)=\frac{a_ 0}{2}+ \sum\, a_ k\cdot \cos kx+\sum\, b_ k\cdot \sin kx
\]
Gibbs gave examples which  show that
the partial sums 
\[ 
s_n(x)=\frac{a_ 0}{2}+ \sum_{k=1}^{k=n}\, a_ k\cdot \cos kx+\sum\, b_ k\cdot \sin kx
\]
can fail to converge to $f(x)$ for certain
$x$-values.
To analyze the situation
we introduce
the maximum norms
\[ 
\rho_f(n)= \max_{0\leq x\leq 2\pi}\, |s_n(x)-f(x)|\quad\colon n=1,2,\ldots
\]
In general they behave in an  irregular fashion as $n\to+\infty$ and 
Hardy constructed examples of continuous functions
$f$ such that
\[
\limsup_{n\to \infty}\, \rho_f(n)=+\infty
\]
This led Carleman to study
the behaviour in the mean. For each $n\geq 1$ we set
\[
\mathcal C_n(f)= \sqrt{\frac{1}{n+1}\cdot
\sum_{\nu=0}^{\nu=n}\, \rho_f(\nu)^2}
\]
Next, put
\[ 
\omega_f(\delta)= \max_{x,y}\, |f(x)-f(y)|\,\colon |x-y|\leq \delta
\]
Since $f$ is uniformly continuous 
$\omega_f(\delta)\to 0$ as $\delta\to 0$.
The following result is proved in the article 
\emph{A theorem concerninig Fourier series}
[London math.soc. 1923]:
\medskip

\noindent
{\bf{6.1 Theorem}}. \emph{There exists an absolute constant $K$
such that the following hold for every
continuous function $f$ with maximum norm
$\leq 1$:}
\[ 
\mathcal D_n(f)\leq K\cdot \bigl[ \frac{1}{\sqrt{n}}+\omega_f(\frac{1}{n})\bigr]
\quad\colon\, n=1,2,\ldots
\]
\medskip


\noindent
{\bf{Remark.}}
This result   shows that
Gibbs'  phenomenon for a given continuous function
$f$ only arises for a sparse sequence of $n$-values.
In a  joint article \emph{Fourier's series and analytic functions}
[Proc. of the Royal Soc. 1923] 
with Hardy,  pointwise convergence was
studied where the limit is unrestricted as $n\to \infty$.
However, these results were  incomplete and it was not until
1965 when Lennart Carleson proved that
for every continuous function $f(x)$ there exists
a null set $\mathcal N$ in $[0,2\pi]$ such that
\[
\lim_{n\to \infty}\, s_n(x)=f(x) \quad\colon\, x\in [0,2\pi]\setminus
\mathcal N\tag{*}
\]
Carleson's  result  constitutes one of the greatest achievements ever in
mathematical analysis  and we shall not try to
enter details of the proof.
Recall that Carleson also proved
the almost everywhere convergence
when $f\in L^2[0,2\pi]$.
When    pointwise convergence holds 
in  (*)  is  obvious that
\[
\lim_{n\to \infty}  \sqrt{\frac{1}{n+1}\cdot
\sum_{\nu=0}^{\nu=n}\, |s_n(x)-f(x)|^2}=0\tag{**}
\]
Here (**) is much  weaker than (*). On the other hand, the null-set
which appears in (*) for a given $L^2$-function $f$ 
is in general strictly larger than
the set of Lebesgue points for $f$, i.e. those $x$ for which
\[
f(x)=\lim_{\delta\to 0}\,
\frac{1}{2\delta}\cdot  \int_{x-\delta}^{x+\delta}\,
|f(s)-f(x)|\, ds=0
\]
In the cited article from 1922, Carleman   proved that
 (**) holds for
every Lebesgue point of the $L^2$-functionÊ$f$
which for "ugly Lebegue points" which belong  to 
$\mathcal N$ gives an averaged substitute to Carleson's
result.

\medskip


\noindent
{\bf{6.2 A convergence result for
$L^2$-functions.}}
Let $f(x)$ be a real\vvv valued and square integrable function
on $(\vvv \pi,\pi)$, i.e.
\[
\int\uuu{\vvv\pi}^\pi\, |f(x)|^2\, dx<\infty
\]
We say that
$f$ has a determined value $A=f(0)$ at $x=0$ if the following two conditions hold:
\[
\lim\uuu{\delta\to 0}
\frac{1}{\delta}\cdot \,\int\uuu 0^\delta\,
|f(x)+f(\vvv x)\vvv 2A|\, dx=0\tag{i}
\]
\[
\int\uuu 0^\delta\,
|f(x)+f(\vvv x)\vvv 2A|^2\, dx\leq C\cdot \delta
\quad
\text{holds for some constant} \quad C\tag{ii}
\]


\noindent
{\bf{Remark.}}
In the same way we can impose this  condition at  every point
$\vvv \pi<x\uuu 0<\pi$. To simplify the subsequent notations
we take $x=0$. 
If  $x=0$ is a Lebesgue point for $f$
and $A$  the  Lebesgue value we have (i).
Hence Lebesgue's Theorem entails  that (i)
holds almost everywhere when 
$x=0$ is replaced by other points $x\uuu 0$.
We leave it to the reader to show
that the second condition also is valid almost everywhere
when $f$ is square integrable.
Next,  expand $f$ in a Fourier series
\[ 
f(x)=\frac{a\uuu 0}{2}+ \sum\, a\uuu k\cdot \cos kx+\sum\, b\uuu k\cdot \sin kx
\]
and with $x=0$ we consider the partial sums
\[ 
s\uuu n(0)= \frac{a\uuu 0}{2}+ a\uuu 1 +\ldots+a\uuu n+
b\uuu 1+\ldots+b\uuu n
\]
The result below is proved 
in Carleman's cited article.


\medskip

\noindent
{\bf{6.3 Theorem.}}
\emph{Assume that $f$ has a determined value $A$ at $x=0$.
Then the following hold for every positive integer $k$}
\[
\lim\uuu{n\to\infty}\, 
\frac{1}{n+1}\cdot
\sum\uuu{\nu=0}^{\nu=n}\, |s\uuu\nu\vvv A|^k=0\tag{*}
\]

\noindent
\emph{Proof.}
Set $A=f(0)$ and $s_n=s_n(0)$. Introduce the function:
$\phi(x)= f(x)+f(\vvv x)\vvv 2A$. It follows that
\[
s\uuu n\vvv A=
\int\uuu 0^\pi\, \frac{\sin (n+1/2)x}{\sin\, x/2}\cdot \phi(x)\cdot dx\tag{0}
\]
where Dini's kernel was used.
Trigonometric formulas  express (0)
as a sum of 
three terms for each
$0<\delta<\pi$:
\[
\alpha\uuu n=\frac{1}{\pi}\cdot \int\uuu 0^\delta\, 
\sin nx\cdot\cot x/2\cdot
\phi(x)\cdot dx\tag{1}
\]
\[ 
\beta\uuu n= 
\frac{1}{\pi}\cdot\int\uuu \delta ^\pi\, \sin nx\cdot\cot x/2\cdot
\phi(x)\cdot dx\tag{2}
\]
\[
\gamma\uuu n=\frac{1}{\pi}\cdot\int\uuu 0^\pi\, \cos nx\cdot \phi(x)\cdot dx\tag{3}
\]
\medskip

\noindent
By Hšlder's inequality it suffices to show Theorem 6.3  if
$k=2p$ is an even integer and Minkowski's inequality gives
\[
\bigl[\,\sum\uuu{\nu=0}^{\nu=n} |s\uuu\nu\vvv A|^{2p}\,\bigr]^{1/2p}\leq
\bigl[\,\sum\uuu{\nu=0}^{\nu=n}|\alpha\uuu \nu|^{2p}\,\bigr]^{1/2p}+
\bigl[\,\sum\uuu{\nu=0}^{\nu=n}|\beta\uuu \nu|^{2p}\,\bigr]^{1/2p}+
\bigl[\,\sum\uuu{\nu=0}^{\nu=n}|\gamma\uuu \nu|^{2p}\,\bigr]^{1/2p}\tag{4}
\]
\medskip

\noindent
Denote by $o(\delta)$ small ordo and $O(\delta)$ is big ordo.
When $\delta\to 0$
we shall establish the following:
\[
\bigl[\,\sum\uuu{\nu=0}^{\nu=n}|\alpha\uuu \nu|^{2p}\,\bigr]^{1/2p}=
n^{1+1/2p)}\cdot o(\delta)\tag{i}
\]
\[
\bigl[\,\sum\uuu{\nu=0}^{\nu=n}|\beta\uuu \nu|^{2p}\,\bigr]^{1/2p}\leq K\cdot p\cdot
\delta^{\vvv 1/2p}\tag{ii}
\]
\[
\bigl[\,\sum\uuu{\nu=0}^{\nu=n}|\gamma\uuu \nu|^{2p}\,\bigr]^{1/2p}\leq K
\tag{iii}
\]
\medskip

\noindent
In (ii-iii) $K$ is an absolute constant which is independent of
$p,n$ and $\delta$.
Let us first see why (i\vvv iii) give Theorem 6.3.
Write $o(\delta)= \epsilon(\delta)\cdot \delta$
where $\epsilon(\delta)\to 0$.
With these notations (4) gives:
\[
\bigl[\,\sum\uuu{\nu=0}^{\nu=n} |s\uuu\nu\vvv A|^{2p}\,\bigr]^{1/2p}\leq
n^{1+1/2p} \cdot \delta\cdot \epsilon(\delta)
+Kp\cdot \delta^{\vvv 1/2p}+K\tag{5}
\]


\noindent
Next, let  $\rho >0$ and choose $b$ so large that
\[
pKb^{\vvv 1/2p}<\rho/3
\]
Take $\delta=b/n$ and with $n$ large it follows that
$\epsilon(\delta)$ is so small that
\[ 
b\cdot \epsilon(b/n)<\rho/3
\]
Then right hand side in (5) is majorized by
\[
\frac{2\rho}{3}\cdot n^{1/2p}+ K
\]
When $n$ is large we also have
\[
K\leq \frac{\rho}{3}\cdot n^{1/2p}
\]



\noindent 
Hence the left hand side in (*) is majorized by
$\rho\cdot n^{1/2p}$ for all sufficiently large $n$.
Since $\rho>0$ was arbitrary  Theorem 6.3 follows  when  the power 
is raised by $2p$.


\bigskip

\centerline{\emph{Proof of (i\vvv iii)}}
\bigskip

\noindent
To obtain (i) we use the triangle inequality
which gives the following for every integer $\nu\geq 1$:
\[ 
|a_\nu|\leq \frac{2}{\pi}\cdot \max_{0\leq x\leq\delta} 
|\sin \nu x\cdot\cot x/2|\cdot\int_0^\delta\, |\phi(x)|\, dx
=\nu\cdot o(\delta)
\]
where the small ordo  $\delta$-term comes from the hypothesis expressed by (*)
in the introduction. Hence
the left hand side above  is majorized by
\[
\bigl[\sum_{\nu=1}^{\nu=n}\, \nu^{2p}\,\bigr]^{\frac{1}{2p}}
 \cdot o(\delta)=
n^{1+1/2p}\cdot o(\delta)
\]
which was requested to get  (i).
To prove (iii) we  notice  that
\[
\gamma_0^2+2\cdot \sum _{\nu=1}^\infty
\gamma_\nu^2=\frac{1}{\pi}\int_0^\pi\, |\phi(x)|^2\, dx
\]
Next, we have
\[
\sum_{\nu=1}^\infty \, |\gamma_\nu|^{2p}\leq
\bigl[\, \sum_{\nu=1}^\infty \, |\gamma_\nu|^2\, \bigr ]^{1/2p}\leq K
\]
where $K$
exists since
$\phi$ is square-intergable on $[0,\pi]$ and (iii) follows.
\medskip


\noindent
\emph{Proof of (ii)}.
Here several steps are required.
For each $0<s<\pi$
we define the  function $\phi\uuu s(x)$
by
\[
\phi\uuu s(x)=\phi(x)\quad\colon\quad 0<x<s
\] 
and extend it to an odd function, i.e. $\phi\uuu s(\vvv x)=\vvv \phi\uuu s(x)$
while  $\phi\uuu s(x)=0$ when $|x|>s$.
This odd function has a sine series
\[
\phi\uuu s(x)=\sum\uuu{\nu=1}^\infty
c\uuu\nu(s)\cdot \sin x\tag{A}
\]
Let us also introduce the functions
\[
\rho(s)=\int\uuu 0^s\, |\phi(x)|\cdot dx\quad\text{and}\quad
\Theta (s)=\int\uuu 0^s\, |\phi(x)|^2\cdot dx\tag{B}
\]


\noindent
The crucial step   towards the proof of (ii)
is the following:
\medskip

\noindent
{\bf{Sublemma.}} \emph{One has the inequality}
\[
\sum\uuu{|nu=1}^\infty\, |c\uuu\nu(s)|^{2p}\leq
(\frac{2}{\pi})^{2p\vvv 1}\cdot \Theta(s)\cdot \rho(s)^{2p\vvv 2}
\]


\noindent
\emph{Proof.}
We  employ convolutions and define inductively a sequence
of functions $\{\phi\uuu{n,s}(x)\}$
where
$\phi\uuu{1,s}(x)= \phi\uuu s(x)$ and 
\[ 
\phi\uuu{n+1,s}(x)=\frac{1}{\pi}
\int\uuu {\vvv \pi}^\pi\, 
\phi\uuu{n,s}(y)\phi\uuu s(x+y)\cdot dy
\]
Since convolution yield products of the Fourier coefficients
and $2p$Êis an even integer we  have the
standard formula:
\[
\sum\uuu{\nu=1}^\infty \, c\uuu n(s)^{2p}
=\phi\uuu{2p,s}(0)\tag{1}
\]
Next, using the Cauchy\vvv Schwarz inequality the reader may verify that

\[
|\phi\uuu{2,s}(x)|\leq \frac{2}{\pi}\cdot \Theta(x)
\]
This entails that
\[
\phi\uuu{3,s}(x)\leq
\frac{1}{\pi}
\int\uuu{\vvv \pi}^\pi\,
|\phi\uuu{2,s}(y)|\cdot |\phi\uuu s(x+y)|\cdot dy
\leq 
\frac{2}{\pi^2}\cdot \Theta(s)\cdot 
\int\uuu{\vvv \pi}^\pi\,
|\phi\uuu s(x+y)|\cdot dy=(\frac{2}{\pi})^2\cdot
 \Theta(s)\cdot \rho(s)
\]
Proceeding in this way it follows by an induction that
\[
\phi\uuu{2p,s}(x)\leq (\frac{2}{\pi})^{2p\vvv 1}
 \cdot \Theta(s)\cdot (\rho(s))^{2p\vvv 2}
\]
This holds in particular when $x=0$ and then (1) above gives the sublemma.
\bigskip

\noindent
{\emph{Proof continued.}
We have by definition

\[
\beta\uuu\nu=\frac{2}{\pi}\int\uuu{\delta}^\pi\,\sin\,\nu x\cdot
\frac{1}{2}\cot (\frac{x}{2})\cdot \phi(x)\cdot dx
\]
An  integration by parts and the construction of the Fourier coefficients
$\{c\uuu\nu(s)\}$ which applies with $s=\delta$
give:
\[
\beta\uuu\nu=
\vvv \frac{1}{2}
\cdot \,\cot \delta/2\cdot c\uuu\nu(\delta)+
+\frac{1}{4}
\int \uuu\delta^\pi\, 
c\uuu\nu(x)\cdot
\text{cosec}^2 (\frac{x}{2})\cdot dx\tag{C}
\]
Now we  profit upon Minkowski's inequality.
Let $q$ be the conjugate of $2p$, i.e $\frac{1}{q}+\frac{1}{2p}=1$
and choose  $\{\xi\uuu\nu\}$ to be the   sequence in $\ell^q$
of unit norm such that
\[
|\sum \xi\uuu\nu\cdot \beta\uuu\nu|=||\beta\uuu\bullet||\uuu{2p}
\]
where the last term is the left hand side in (ii).
At the same time (*) above and the triangle inequality give
\[
||\beta\uuu\bullet||\uuu{2p}\leq 
\vvv \frac{1}{2}
\cdot \,\cot (\delta/2)\cdot \sum\, |c\uuu\nu(\delta)|\cdot |\xi\uuu\nu|+
\frac{1}{4}\int \uuu\delta^\pi\, 
\text{cosec}^2 (\frac{x}{2})\cdot \sum\,|
c\uuu\nu(x)\cdot\xi\uuu\nu|\cdot dx\leq
\]
\[
 \frac{1}{2}
\cdot \,\cot (\delta/2)\cdot ||c\uuu\bullet(\delta)||\uuu{2p}
+\frac{1}{4}\int \uuu\delta^\pi\, 
\text{cosec}^2 (\frac{x}{2})\cdot 
||c\uuu\bullet(x)||\uuu{2p}\cdot dx\tag{D}
\]
\medskip

\noindent
At this stage we apply the sublemma  and the assumption which 
give a constant $K$ such that
\[
\Theta(s)\leq K\quad\text{and}\quad \rho(s)\leq K\cdot s\tag{E}
\]

\medskip

\noindent
The last estimate actually is weaker than the hypothesis
but it will be  sufficient to get the requested
estimate of the $\ell^{2p}$\vvv norm  in (ii). Namely,
the sublemma  gives a constant $K\uuu 1$ such that
\[
||c\uuu\bullet(\delta)||\uuu{2p}\leq K\uuu 1\cdot \delta^{1\vvv 1/p}
\]
At the same time we have a constant
$K\uuu 2$ such that
\[
\cot (\delta/2)\leq \frac{K\uuu 2}{\delta}
\]
The product in the first term from (D) is therefore majorized by
$K\uuu 1K\uuu 2\cdot \delta^{\vvv 1/2p}$ as requested in (ii).
For the second term we use again the sublemma
which first gives
\[
||c\uuu\bullet(x)||\uuu p\leq K\cdot x^{\vvv 1/2p}
\]
At this stage we leave it to the reader to verify that
we get a constant $K$ so that
\[
\int \uuu\delta^\pi\, 
x^{\vvv 1/2p}\cdot 
\text{cosec}^2 (\frac{x}{2})\cdot dx\leq K\cdot \delta^{\vvv 1/2p}
\] 
which finishes the proof of (ii).
\bigskip

\noindent{\bf{The case when
$f$ is continuous.}}
Under the normalisation that
the $L^2$-integral of $f$ is $\leq 1$
the inequalities (ii-iii) hold for an absolute constant $K$.
In (i) we notice that
the construction of
$\phi$ and the definition of $\omega_f$
give the estimates
\[ 
|a_\nu|\leq \nu\cdot \delta\cdot \omega_f(\delta)
\]
With $p=2$ the proof of Theorem 5.3  entails 
that (i)  is majorised by
\[
n^{1+1/2}\cdot \delta\cdot \omega_f(\delta)
\]
This holds for every $0\leq x\leq 2\pi$ and from the previous proof we conclude that
the following hold for each
$n\geq 2$ and every $0<\delta<\pi$:
\[ 
\mathcal D_n(f)\leq\frac{1}{\sqrt{n+1}}\cdot
[n^{1+1/2}\cdot \delta\cdot \omega_f(\delta)+2K\delta^{-1/2}+K]\tag{i}
\]
With $n\geq 2$ we take $\delta=n^{-1}$ and see that
(i) gives a requested constnt in Theorem 5.1


\newpage




\centerline{\bf\large{7. The Denjoy conjecture}}

\bigskip

\noindent {\bf Introduction.}
Let $\rho$ be a positive integer and 
$f(z)$  is an entire function such that there exists some
$0<\epsilon<1/2 $  and a constant $A_\epsilon$ such that
\[
|f(z)|\leq A_\epsilon\cdot e^{|z|^{\rho+\epsilon}}\tag{0.1}
\]


\noindent
hold for every $z$. Then we say that 
$f$ has integral order $\leq\rho$.
Next, the entire function $f$ has an asymptotic value $a$
if there exists a Jordan curve
$\Gamma$ parametrized
by
$t\mapsto\gamma(t)$ for $t\geq 0$ such that
$|\gamma(t)|\to \infty$ as $t\to+\infty$ and
\[
\lim_{t\to+\infty}\, f(\gamma(t))=a\tag{0.2}
\]


\noindent
In 1920 Denjoy raised the conjecture that
(0.1) implies that the entire function $f$ has at most
$2\rho$ many different asymptotic values. Examples show that
this upper bound is sharp.
The Denjoy conjecture was proved in 1930 by  Ahlfors in [Ahl].
A few years later T. Carleman found an alternative  proof based
upon a certain differential inequality.
Theorem A.3 below 
has  applications beyond the proof of
the Denjoy conjecture
for estimates of
harmonic measures. See [Ga-Marsh].

\bigskip

\centerline{\bf A. The  differential inequality.}
\bigskip


\noindent
Let $\Omega$ be a connected open set in ${\bf{C}}$ whose
intersection $S\uuu x$ between
a  vertical line  $\{\mathfrak{Re}\, z=x\}$
is a bounded set
on the real $y$-line for every $x$.
When $S_x\neq\emptyset $ it is the disjoint union
of open
intervals $\{(a_\nu,b_\nu)\}$ and we set
\[ 
\ell(x)=\max\uuu \nu \,(b_\nu-a_\nu)\tag{*}
\]

\medskip


\noindent
Next, let
$u(x,y)$ be a positive harmonic   function
in $\Omega$ which 
extends to a continuous function on
the closure $\bar\Omega$  with the boundary values identical to zero.
Define the function $\phi$ by:
\[ 
\phi(x)=\int_{S_x}\,u^2(x,y)\cdot dy\tag{1}
\]
The Federer-Stokes theorem gives
the following  formula for the derivatives of $\phi$:
\[ 
\phi'(x)=2\int_{S_x}\,u_x\cdot u(x,y) dy\tag{2}
\]
\[
\phi''(x)=2\int_{S_x}\,u_{xx}\cdot u(x,y) dy+
2\int_{S_x}\,u^2_x\cdot dy\tag{3}
\]


\noindent
Since $\Delta(u)=0$ when $u>0$ we have
\[
2\int_{S_x}\,u_{xx}\cdot u(x,y) dy=-
2\int_{S_x}\,u_{yy}\cdot u(x,y) dy=
2\int u_y^2 dy\tag{4}
\]
The Cauchy-Schwarz inequality applied in (2) gives
\[
\phi'(x)^2\leq 4\cdot \int_{S_x}\,u^2_x\cdot\int_{S_x} u^2(x,y) dy
=4 \cdot \phi(x)\cdot \int_{S_x}u_x^2dy\tag{5}
\]
Hence (4) and (5) give:
\[ 
\phi''(x)\geq 2\int\uuu{S\uuu x} \,u^2_y(x,y)\cdot dy+\frac{1}{2}\cdot \frac{\phi'^2(x)}{\phi(x)}\tag{6}
\]
Next, since $u(x,y)=0$ at the end-points of all intervals of $S_x$,
\emph{Wirtinger's 
inequality}
and the definition of $\ell(x)$ give:
\[
\int\uuu{S\uuu x} u^2_y(x,y)\cdot dy\geq \frac{\pi^2}{\ell(x)^2}\cdot\phi(x)\tag{7}
\]


\noindent
Inserting (7) in (6) we have  proved
\medskip

\noindent
{\bf A.1 Proposition} \emph{The $\phi$-function satisfies the differential inequality}
\[
\phi''(x)\geq \frac{2\pi^2}{\ell(x)^2}\cdot\phi(x)+\frac{\phi'^2(x)}{2\phi(x)}
\]


\noindent
\emph{Proof continued.}
The maximum
principle for harmonic functions implies that the $\phi(x)>0$
when $x>0$ and hence there exists
a $\psi$-function where
$\phi(x)= e^{\psi(x)}$. It follows that

\[ 
\phi'=\psi' e^\psi\quad\text{and}\quad\,\phi''=
\psi''e^\psi+\psi'^2e^\psi
\]

\noindent
Now  Proposition A.1 gives
\[
 \psi''+\frac{\psi'^2}{2}\geq \frac{2\pi^2}{\ell(x)^2}\tag{*}
\]
\medskip


\noindent
{\bf {A.2 An integral inequality.}}
From (*) we obtain
\[
\frac{2\pi}{\ell(x)}\leq\sqrt{\psi'(x)^2+2\psi''(x)}\,\leq
\psi'(x)+\frac{\psi''(x)}{\psi'(x)}
\]
\medskip

\noindent
Taking the integral we get
\[ 
2\pi\cdot\int_0^x\,\frac{dt}{\ell(t)}\leq \psi(x)+\log\,\psi'(x)+O(1)
\leq \psi(x)+,\psi'(x)+O(1)\tag{**}
\]
where $O(1)$ is a remainder 
term which is bounded  independent of $x$. Taking the integral once more we 
obtain:
\medskip

\noindent
{\bf {A.3 Theorem.}}
\emph{The following inequality holds:}


\[
2\pi\cdot\int_0^x\, \frac{x-s}{\ell(s)}\cdot ds\leq
\int_0^x\,\psi(s)\cdot ds+\psi(x)+O(x)
\]
\emph{where the remainder term $O(x)$ is bounded by $Cx$ for 
a fixed constant.}

\bigskip


\centerline {\bf B. Solution to the Denjoy conjecture}
\bigskip

\noindent
{\bf B.1 Theorem.}
\emph{Let $f(z)$ be entire of some integral order
$\rho\geq 1$. Then $f$ has at most $2\rho$ many different asymptotic values.}
\bigskip

\noindent
\emph{Proof.}
Suppose $f$ has $n$ different asymptotic values
$a_1,\ldots,a_n$.
To each  $a_\nu$ there exists a Jordan arc $\Gamma_\nu$ as described in the introduction.
Since the $a$-values are different the $n$-tuple of
$\Gamma$-arcs are separated from each other when
$|z|$ is large.
So we can find some $R$ such that
the arcs are disjoint in the exterior disc
$|z|>R$. We may also consider the tail of each arc, i.e. starting from
the last point on $\Gamma_\nu$ which intersects the circle
$|z|=R$. So now we have an $n$-tuple of disjoint Jordan
curves in $|z|\geq R$ where each curve intersects $|z|=R$ at some point $p_\nu$ and after the curves moves to the point at infinity. See figure.
Next, we take one of these curves, say $\Gamma_1$. Let
$D_R^*$ be the exterior disc $|\zeta |>R$.
In the domain
$\Omega={\bf{C}}\setminus \Gamma_1\cup\,D_R^*$ we can choose a single-valued
branch of $\log \zeta$ and with $z=\log\,\zeta $
the image of $\Omega$ is a simply connected domain 
$\Omega^*$
where
$S_x$ for each $x$ has length strictly less than
$2\pi$
The images of the $\Gamma$-curves
separate $\Omega^*$
into $n$ many disjoint connected
domains
denoted by $D_1,\ldots,D_n$ where
each $D_\nu$ is bordered by a pair of images of $\Gamma$-curves
and a portion of the vertical line $x=\log \,R$.

\medskip

\noindent
Let $\zeta=\xi+i\eta$ be the complex coordinate
in $\Omega^*$.
Here we get the analytic function
$F(\zeta)$ where
\[ F(\text{log}(z))= f(z)
\]
We notice that $F$ may have more growth than $f$. Indeed, we get
\[
|F(\xi+i\eta)|\leq \text{exp}\bigl(e^{(\rho+\epsilon)\xi}\bigr)\tag{1}
\]

\medskip

\noindent
With $u=\text{Log}^+\,|F|$ it follows that
\[ 
u(\xi,\eta)\leq e^{(\rho+\epsilon)\xi}\tag{2}
\]


\noindent
Hence the $\phi$-function constructed
during the proof of Theorem A.3  satisfies
\[
\phi(\xi)\leq e^{2(\rho+\epsilon)\xi}
\]
It follows that the $\psi$-function satisfies


\[ 
\psi(\xi)=2\cdot (\rho+\epsilon)\xi+O(1)\tag{3}
\]


\noindent Now we  apply Theorem A.3  in each region $D_\nu$
where we have a function
$\ell_\nu(\xi)$ constructed by (0) in section A. 
This gives the inequality
\[
2\pi\cdot \int_R^\xi\, \frac{\xi-s}{\ell_\nu(s)}\cdot ds\leq
\int_R^\xi\, (\rho+\epsilon)s\cdot ds+(\rho+\epsilon)\xi+O(1)\quad\colon\quad
1\leq \nu\leq n\tag{4}
\]
\medskip

\noindent
Next, recall the elementary inequality which asserts that if $a\uuu 1,\ldots,a\uuu n$
is an arbitrary $n$\vvv tuple of positive numbers then
\[
\sum\,a\uuu \nu\cdot \sum\, \frac{1}{a_\nu}\geq n^2
\tag{5}
\]
For each $s$ we apply this to the $n$\vvv tuple
$\{\ell\uuu \nu(s)\}$ where we also have
\[ 
\sum\,\ell\uuu \nu(s)\leq 2\pi
\] 
\noindent
So  a summation in (4) over $1\leq \nu\leq n$ gives
\[
n\cdot  \int_R^\xi\, (\xi-s)\cdot ds\leq
\int_R^\xi\, (\rho+\epsilon)s\cdot ds+(\rho+\epsilon)\xi+O(1)\tag{6}
\]
Another integration gives:
\[ 
n\cdot\frac{\xi^2}{2}\leq (\rho+\epsilon)\cdot \xi^2+O(\xi)\tag{7}
\]
\medskip

\noindent
This inequality can only hold for large $\xi$ if
$n\leq 2(\rho+\epsilon)$ and since  $\epsilon<1/2$ is assumed
it follows that 
$n\leq 2\rho$ which finishes the proof of the Denjoy conjecture.



\newpage




\centerline{\bf {8. Lindelšf functions.}}

\bigskip

\noindent
{\bf{Introduction.}}
For each real number $0<a\leq 1$
there exists the entire  function
\[ 
Ea_(z)=\sum_{n=0}^\infty\,\frac{z^n}{\Gamma(1+na)}
\]
Growth properties of the $E$-functions were investigated
in a series of articles by
Mittag-Leffler between 1900-1904 using 
integral formulas  for the entire function
$\frac{1}{\Gamma}$.
This inspired
PhragmŽn
to study 
entire functions $f(z)$ such that
there are constants $C$ and $0<a<1$ with:
\[
\log|f(re^{i\theta})| \leq C\cdot (1+|r|)^a)\quad\colon
-\alpha<\theta<\alpha
\] 
for some $0<\alpha<\pi/2$ while
$f(z)|\leq C$ for all $z\in{\bf{C}}\setminus S$.
When this holds  we get the entire function
\[ 
g(z)=\int_0^\infty\, f(sz)\cdot e^{-s}\cdot ds
\]
If $z$ is outside the sector $S$ it is clear that
$|g(z)|$ is bounded by $C\cdot \int_0^\infty e^{-s}ds=C$.
When $z=re^{i\theta}$ is in the sector we 
still
get a  bound from (1) since $0<a<1$
and conclude that the entire function $g$ is bounded and hence a constant.
Since the Taylor coefficients of
$f$
are recaptured from $g$ it follows that
$f$ must be  constant.
More general  results of this kind were obtained in
the joint article [PL] by PhragmŽn and Lindelšf from 1908
and led to  the PhragmŽn-Linedlšf principle.
A continuation of [PL]
appears in  Lindelšf's  article
\emph{Remarques sur la croissance
de la fonction $\zeta(s)$}  (Bull. des scienes mathŽmatiques 1908]
devoted to 
the growth of Riemann's $\zeta$-function along vertical lines 
in the strip $0<\mathfrak{Re}(z)<1$.
This  leads to the study of  various  indicator functions
attached to analytic functions
and we shall expose
material from Care,an's article
\emph{Sur la fonction $\mu(\sigma)$ de M. Lindelšf}
which was published in 1930
and attributed toi A. Wiman,. 
Here is the  set-up:
Consider a strip domain
in the complex $s$-plane:
\[
\Omega=\{ s=\sigma+it\quad
\colon t>0\quad\text{and}\quad 0\leq a<\sigma<b\}
\]

\medskip

\noindent
An analytic function
$f(z)$ in $\Omega$ is of
\emph{finite type} if
there exists some
integer $k$, a constant  $C$ and some $t_0>0$ such that
\[ 
|f(\sigma+it)|\leq C\cdot t^k\quad\text{hold for}\quad t\geq t_0
\] 
To every such $f$ we define the Lindelšf function
\[
\mu_f(\sigma)
=
\limsup_{t\to\infty}\,
\frac{\text{Log}\, |f(\sigma+it)|}{\text{Log}\, t}\tag{*}
\]
Lindelšf and PhragmŽn proved  that $\mu_f$ is a continuous and convex
function on $(a,b)$. No further restrictions
occur on the $\mu$-function because one has:
\bigskip

\noindent
{\bf{1. Theorem.}} \emph{For every convex and continuous function
$\mu(\sigma)$ defined in $[a,b]$
there exists an analytic function $f(z)$ without zeros in
$\Omega$ such that
$\mu_f=\mu$.}
\medskip

\noindent
{\bf{2. Exercise.}} Prove this result using the
$\Gamma$-function. First, to a pair of real numbers
$(\rho,\alpha)$ we set
\[
 f(s)=e^{-\frac{\pi i\cdot\rho s}{2}}\cdot\Gamma (\rho(s-a)+\frac{1}{2})\tag{i}
 \]
Use properties of the $\Gamma$-function to show that
$f$ has finite type in
$\Omega$ and its indicator function becomes 
a linear function:
\[ 
\mu_f(\sigma)= \rho\cdot (\sigma-a)
\]

\noindent
More generally one gets a function  $f$ where
$\mu_f$Êis piecewise linear by:
\[ 
f= \sum_{k=1}^{k=m}\, c_ke^{-\frac{\pi i\cdot\rho_\nu s}{2}} \Gamma(\rho_k(s-a_k)+
\frac{1}{2})\tag{ii}
\]
where $\{c_k\}$, $\{\rho_k\}$ and $\{a_k\}$ are $m$-tuples of real numbers.
Finally, starting from
an arbitrary
convex curve we can 
choose  some dense and  enumerable set of enveloping tangents to
this curve. Then
an infinite series of the form above gives an analytic function
$f(s)$ such that
\[
 \sigma\mapsto\mu_f(\sigma)
\] 
yields an arbitrarily
given convex $\mu$-function on $(a,b)$.

\medskip


\centerline{\bf{1. A construction of   harmonic functions.}}
\medskip

\noindent
Let $U(x,y)$ be a bounded harmonic function in the strip domain
$\Omega$
and $V$  its harmonic conjugate. Set
\[
 f(s)=\text{exp}\,\bigl[\text{(log}(s)-\frac{\pi i}{2})(U(s)+iV(s))\bigr]\tag{*}
 \]


\noindent
It is easily see that
$f(z)$ has finite type in
$\Omega$.
With $s=\sigma+it$ we have
\[
|f(\sigma+it)|= 
\]
\[
\text{exp}(\frac{1}{2}\log(\sigma^2+t^2)\cdot U(\sigma+it)\cdot
\text{exp}(-(\frac{\pi}{2}- \text{arg}(\sigma+it))\cdot V(\sigma+it))
\]
It follows that 
\[ 
\frac{ \log\, |f(\sigma+it)|}{t}=
 \frac{\log\, \sqrt{\sigma^2+t^2}\cdot U(\sigma+it)]}{\log t}
+\frac {(\text{arg}(\sigma+it)-\frac{\pi i}{2})\cdot V(\sigma+it)}{t}
\]
 
 

\noindent{\bf{1.1 Exercise.}}
With $\sigma$ kept fixed one has
\[
\text{arg}(\sigma+it)=\tan\,\frac{t}{s}
\] 
which tends to $\pi/2$ as $t\to +\infty$.
Next,  $V(\sigma+it)$ is for large $t>0$
up to a constant the primitive of 
\[
\int\uuu 1^t\, \frac{\partial V}{\partial u}(\sigma+iu)\cdot du
\]
Here the partial derivative of $V$ is equal to the partial derivative
$\partial U/\partial\sigma(\sigma,u)$ taken along
$\mathfrak{Re}\, s=\sigma$.
Since $U$ is bounded in the strip domain
it follows from
Harnack's inequalities that
this partial derivative stays bounded when $1\leq u\leq t$
by a constant which is independent of $t$.
Putting this together the reader can verify that
\[ 
\lim_{t\to +\infty}\, 
\frac {(\text{arg}(\sigma+it)-\frac{\pi i}{2})\cdot 
V(\sigma+it)}{t}=0\tag{1.2}
\]

\bigskip

\noindent
From (1.2 )   we obtain the equality
\[
\mu\uuu f(\sigma)=\limsup_{t\to\infty}\, U(\sigma+it)\tag{*}
\]
This suggests a further study of 
growth properties of bounded harmonic functions in strip domains.


\bigskip


\centerline {\bf{2. The $M$ and the $m$-functions.}}

\medskip

\noindent
To a bounded harmonic function $U$ in
$\Omega$  we associate the maximum and the minimum
functions:
\[ 
M(\sigma)=\limsup_{t\to\infty}
\, U(\sigma+it)
\quad\text{and}\quad\liminf_{t\to\infty}
\,U(\sigma+it)
\]


\noindent
{\bf{2.1 Proposition.}}
\emph{$M(\sigma)$ is a convex function while
$m(\sigma)$ is concave.}
\medskip

\noindent
We prove the convexity of $M(\sigma)$. The concavity of $m$
follows when we replace $U$ by $\vvv U$.
Consider a pair $\alpha,\beta$ with $a<\alpha<\beta<b$.
Replacing $U$ by $U+ A+\cdot Bx$ for suitable constants
$A$ and $B$ we may assume that
$M(\alpha)=M(\beta)=0$
and the requested convexity follows if we can show that
\[ 
M(\sigma)\leq 0\quad\colon\quad \alpha<\sigma<\beta
\]
To see this we consider
rectangles 
\[
\mathcal R[T\uuu *,T^*]
=\{\sigma+it\quad \alpha \leq \sigma\leq \beta
\quad\text{and}\quad  T\uuu *\leq t\leq T^*\}
\]
Let $\epsilon>0$ and start with
a large $T\uuu *$ so that
\[
t\geq T\uuu *\implies
U(\alpha+it)\leq \epsilon\tag{i}
\] 
and similarly with $\alpha$ replaced by $\beta$.
Next, we have a constant $M$ such that
$|U|\uuu\Omega\leq M$.
If $z=\sigma+it$ is an interior point of the rectangle above
it follows by harmonic majorisation that

\[
U(\sigma+it)\leq \epsilon+ M\cdot \mathfrak m\uuu z(J\uuu *\cup J^*)
\]
where the last term  is the harmonic measure at $z$
which evaluates the harmonic function in
the rectangle at $z$ with boundary values zero on the two verical lines
of the rectangle which it is equal to 1 on the horizontal intervals 
$J^*=(\alpha,\beta)+iT^*$ and 
$J\uuu *=(\alpha,\beta)+iT\uuu *$
\medskip

\noindent
{\bf{Exercise.}}
Show (via the aid of figure that with $T^*=2T\uuu *$
one has
\[
\lim\uuu{T\uuu *\to +\infty}\,
\mathfrak m\uuu {\sigma+3i T\uuu */2}(J\uuu *\cup J^*)=0
\] 
where this limit is uniform when $\alpha\leq \sigma\leq \beta$.
Since $\epsilon>0$ is arbitrary in (i) the reader can  conclude that
$M(\sigma)\leq 0$ for every $\sigma\in(\alpha,\beta)$.
\bigskip

\noindent
{\bf{A special case.}}
Suppose that we have the equalities
\[
m(\alpha)=M(\alpha)\quad\text{and}\quad
m(\beta)=M(\beta)\tag{1}
\]
Using rectangles as above and harmonic majorization the
reader can verify that this implies that
\[
m(\sigma)=M(\sigma)\quad\colon\quad \alpha<\sigma<\beta
\]
Let us remark that
this result was originally proved by
Hardy and Littlewood in [H\vvv L].




\bigskip

\noindent
{\bf{The case when $M(\sigma)-m(\sigma)$ has
a tangential zero}}.
Put $\phi(\sigma)=M(\sigma)-m(\sigma)$ and suppose that this non\vvv 
negative
function in $(a,b)$
has a zero at some $a<\sigma\uuu 0<b$
whose graph has a tangent at $\sigma_0$.
This means that if:
\[ 
h(r)=\max_{-r\leq|\sigma\vvv \sigma\uuu 0|\leq r}\, \phi(\sigma)
\] 
then
\[
\lim_{r\to 0}\, \frac{h(r)}{r}=0\tag{*}
\]


\noindent
Under this hypothesis the following result is proved in
[Carleman].
\medskip


\noindent
{\bf{2.2 Theorem.}} \emph{When (*) holds we have}
\[ 
m(\sigma)=M(\sigma)\quad\colon\,
a<\sigma<b
\]

\medskip

\noindent
The subsequent proof from [Carleman]
was given
at 
a lecture by Carleman  in Copenhagen 1931 which
has the merit that a similar reasoning 
can be applied in dimension $\geq 3$.
Adding some linear function to $U$ we may assume that
$M(\sigma_0)=m(\sigma_0)=0$ which means that
\[
\limsup_{t\to\infty}\,
U(\sigma_0,t)=0\tag{1}
\]

\noindent
Next,
consider the function
\[ 
\phi\colon t\mapsto \partial U/\partial \sigma(\sigma_0,t)\tag{1}
\]
The assumption (*) and the result in XXX gives:
\[
\lim\uuu{t\to\infty}\,
\partial U/\partial \sigma(\sigma_0,t)=0\tag{2}
\]


\noindent
Next, consider some 
$a<\sigma<b$ and let $\epsilon>0$.
By the  result from XX there exist
finite tuples of constants $\{a_1,\ldots,a_N\}$ and
$\{b_1,\ldots,b_N\}$ and 
some $N$-tuple $\{\tau_\nu\}$ which
stays in a $[0,1]$ such that
\[
\bigl| U(\sigma,t)-\sum\, a_\nu\cdot U(\sigma_0, t_\nu+t)
-\sum\, b_\nu\cdot \partial U/\partial\sigma(\sigma_0, t_\nu+t)\bigr|<\epsilon\quad
\text{hold for all}
\quad t\geq 1\tag{5}
\]
Since $\epsilon$ is arbitrary it follows from (1\vvv 2)  
that
\[
\lim_{t\to\infty}\, U(\sigma,t)=0\tag{5}
\]
for every $a<\sigma<b$ which obviously gives
the requested equality
in
Theorem 2.2.



\bigskip

\noindent
\centerline {\bf{2.3. Integral  indicator funtions.}}
\medskip

\noindent
Let $f(s)$   be an analytic function of finite order
in the strip domain $\Omega$ and fix some $t_0>0$ which does not affect
the subsequent constructions.
For a 
pair  $(\sigma,p)$ where
$a<\sigma<b$ and $p>0$
we  associate the set of
of positive numbers $\chi$ such that the integral
\[ 
\int_{t_0}^\infty\, \frac{|f(\sigma+it)\bigl|^p}{t^\chi}\cdot dt<\infty\tag{*}
\]



\noindent
We get a critical smallest non-negative number  
$\chi_*(\sigma,p)$ such that (*) converges when
$\chi>\chi_*(\sigma,p)$.
In the case $p=1$ 
a  result due to Landau
asserts that 
$\chi(\sigma,1)$ determines the half-plane of the complex $z$-plane where
the function
\[ 
\gamma(z)=\int_{t_0}^\infty\, \frac{f(\sigma+it)}{t^z}\cdot dt
\] 
is  analytic and
$\sigma\mapsto \chi(\sigma,1)$
is a convex function on  $(a,b)$.
A more general  convexity
result holds when $p$  also varies.
\medskip

\noindent
{\bf{2.4 Theorem.}} \emph{Define the $\omega$-function by}:
\[ 
\omega(\sigma,\eta)= \eta\cdot \chi(\sigma,\frac{1}{\eta})\quad\colon
a<\sigma<b\quad\colon \eta>0
\]
\emph{Then $\omega$ is a continuous and convex function of the 
two variables $(\sigma,\eta)$
in the product set $(a,b)\times {\bf{R}}^+$.}
\medskip

\noindent
{\bf{2.5 Remark.}}
Theorem 2.4 is proved using 
Hšlder inequalities and
factorisations of analytic functions which
reduces the proof to the case when
$f$ has no zeros.
The reader is invited to supply details of the proof or 
consult [Carleman].


\bigskip




\centerline{\bf {3.  Lindelšf estimates in the unit disc.}}

\bigskip

\noindent
Let $f(z)$ be analytic in the open unit disc given by a power series

\[ f(z)=\sum a_n\cdot z^n
\]
We assume that the sequence $\{a_n\}$ has temperate growth, i.e. there exists
some integer $N\geq 0$ and a constant $K$ such that
\[ 
|a_n|\leq K\cdot n^N\quad\colon\quad n=1,2,\ldots
\]
In addition we assume that the sequence
$\{a_n\}$ is not too small in the sense that
\[ 
\sum_{n=1}^\infty\, |a_n|^2\cdot n^{s}=+\infty\quad\colon
\quad\,\forall\, s>0\tag{*}
\]
Now there exists  the smallest number $s_*\geq 0$ such that
the Dirichlet series

\[ 
\sum_{n=1}^\infty\, |a_n|^2\cdot \frac{1}{n^s}<\infty,\quad
\text{for all}\,\, s>s_*
\]
\medskip

\noindent
To each
$0\leq\theta\leq 2\pi$ we set
\[ 
\chi(\theta)=\min_s\, \int_0^1\, \bigl|f(re^{i\theta})\bigr|\cdot(1-r)^{s-1}\cdot dr<\infty\tag{1}
\]
\[
\mu(\theta) =\text{Lim.sup}_{r\to 1}\,
\frac{\text{Log}\, |f(re^{i\theta})|}{ \text{Log}\,\frac{1}{1-r}}
\tag{2}
\]
\medskip

\noindent
We shall study the two functions $\chi$ and $\mu$.
The first result is left as an exercise.

\medskip


\noindent
{\bf {3.1. Theorem.}} \emph{The inequality}
\[
\chi(\theta)\leq\frac{s^*}{2}
\] 
\emph{holds almost everywhere, i.e. for all $0\leq\theta\leq 2\pi$ outside a null set on
$[0,2\pi]$.}

\medskip

\noindent
\emph{Hint.} Use the formula

\[ 
\frac{1}{2\pi}\cdot \int_=^{2\pi}\, |f(re^{i\theta})|^2\cdot d\theta=
\sum\, |a_n|^2
\]


\bigskip

\noindent 
For the $\mu$-function a corresponding result holds:



\medskip
\noindent
{\bf {3.2. Theorem.}} \emph{The inequality below holds almost everywhere.}
\[
\mu(\theta)\leq\frac{s^*}{2}
\] 


\noindent
\emph{Proof.}
Let $\epsilon>0$ and introduce the function
\[ 
\Phi(z)=\sum\, a_n\cdot \frac{\Gamma(n+1)}{\Gamma(n+1+\frac{s^*}{2}+\epsilon)}
\cdot z^n=\sum\, c_n\cdot z^n
\]


\noindent
It is clear that
the construction of
$s^*$ entails
\[ 
\sum\, |c_n|^2<\infty
\]


\noindent
Next, set $\Phi_0=\Phi$ and define inductively the sequence
$\Phi_0,\Phi_1,\ldots$ by
\[ \Phi_\nu(z)=
z^{\nu-1}\cdot \frac{d}{dz}\bigl[ z^\nu\cdot \Phi_{\nu-1}(z)\bigr)
\quad\colon\quad \nu=1,2,\ldots
\]


\noindent
{\bf 3.3 Exercise.} Show that for almost every
$0\leq\theta\leq2\pi$ there exists a constant
$K=K(\theta)$ such that
\[
|\Phi_\nu(re^{i\theta})|\leq K(\theta)\cdot \frac{1}{1-r)^\nu}\quad\colon
0<r<1
\]


\noindent
Next, with  $s^*$ and $\epsilon$ given we
define
the integers $\nu$ and $\rho$:
\medskip
\[ 
\nu=\bigl[\,\frac{s^*}{2}+\epsilon\,\bigr]+1\quad\colon\quad
\rho=\frac{s^*}{2}+\epsilon- \bigl[\,\frac{s^*}{2}+\epsilon\,\bigr]
\]
where the bracket term is the usual notation for the
smallest integer $\geq \frac{s^*}{2}+1$.
\medskip

\noindent
{\bf Exercise} Show that with
$\nu$ and $\rho$ chosen  as above one has
\[\Phi_\nu(z)=\sum\, a_n\cdot \frac{\Gamma(n+1+\nu)}{\Gamma(n+1+\rho-1)}
\cdot z^n
\]

\noindent
and use  this to show the inversion formula
\[ 
f(z)=\frac{1}{z^\nu\cdot\Gamma(1-\rho)}\cdot
\int_0^z\, (z-\zeta)^{-\rho}\dot \zeta^{\nu+\rho-1}\cdot
\Phi_\nu(\zeta)\cdot d\zeta\tag{*}
\]

\medskip

\noindent
{\bf 3.4 Exercise.} Deduce from the above that for almost every
$\theta$ there exists a constant $K(\theta)$ such that
\[
|f(re^{i\theta})|\leq K(\theta)\cdot\frac{1}{ (1-r)^{\nu+\rho-1}}\tag{**}
\]
\medskip

\noindent
{\bf Conclusion.}
From (**) and the construction of
$\nu$ and $\rho$ the reader can confirm
Theorem  3. 2.

\bigskip

\noindent
{\bf 3.5 Example.} Consider the function
\[ 
f(z)=\sum_{n=1}^\infty\, z^{n^2}
\]
Show that $s^*=\frac{1}{2}$ holds in  this case. Hence
Theorem  B.2 shows that for each $\epsilon>0$ one has 
\[
\max_r\, (1-r)^{\frac{1}{4}+\epsilon}\cdot |f(re^{i\theta}|<\infty\tag{E}
\]
for almost every $\theta$. 
\medskip

\noindent
{\bf 3.6 Exercise.}
Use the inequality above to show the following:
For a complex number
$x+iy$ with $y>0$ we set
\[
q= e^{\pi ix-\pi y}
\]
Define the function
\[
\Theta(x+iy)= 1+q+q^2+\ldots
\]
Show that when $\epsilon>0$
then there exists a constant $K=K(\epsilon,x)$ for almost all
$x$ such that
\[
y^{\frac{1}{4}+\epsilon}\cdot |\theta(x+iy)|\leq K\quad\colon\quad y>0
\]


\newpage






\centerline{\bf {9. Approximation theorems in complex domains}}
\bigskip

\noindent 
\emph{0. Introduction.}

\medskip


\noindent
\emph{B. Polynomial approximation with bounds}

\bigskip


\noindent
\emph{C. Approximation by fractional powers}


\bigskip


\noindent
\emph{D. Theorem of MŸntz}




\bigskip


\noindent
\centerline {\bf 0. Introduction.}
\medskip


\noindent
This chapter is devoted to results  concerned with
approximation by analytic functions
due to Carleman, Lindelšf and MŸntz.





\bigskip



\centerline{\bf B. Polynomial approximation with bounds}

\medskip

\noindent
{\bf Introduction.} We  begin with a  result
due to Lindelšf.
Let $U$ be a Jordan domain and set $\Gamma=\partial U$.
For each  $f(z)\in\mathcal O(U)$,  
Runge's theorem
gives a 
sequence of polynomials $\{Q_\nu(z)\}$ which approximates $f$ uniformly over
each compact subset of $U$.
If we impose some bound on $f$ one may ask
if 
an approximation exists  where the
$Q$-polynomials satisfy a similar bound as $f$.
Lindelšf proved that  bounds exist
for many different  norms on
the given function $f$ 
in the
article 
\emph{Sur un principe gŽneral de l'analyse et ses applications
ˆ la theorie de la reprŽsentation conforme}
from 1915.
Let us  announce  two results from [Lindelšf]
of this nature.
Let  $p>0$ and consider the $H^p$-space
of analytic functions in $U$ for which
\[ 
||g||_p=\iint_U\,|g(z)|^p\cdot dxdy<\infty
\tag{1}
\]


\noindent
{\bf B.1 Theorem } \emph{Let $p>0$ and suppose that
$f(z)$ has a finite $H^p$-norm. Then there exists a sequence of polynomials
$\{Q_n(z)\}$ which converge uniformly to
$f$ in compact subsets of $U$ while}
\[ 
||Q_n||_p\leq ||f||_p\quad\colon\quad n=1,2,\ldots
\] 
\medskip

\noindent
A similar approximation holds when
the $H^p$-norm is replaced by the maximum norm.
Thus, if $f$ is a bounded analytic function
in $U$ there exists a sequence of polynomials
$\{Q_n\}$ which converge to $f$ in every relatively
compact subset of $U$ and at the same time
the maximum norms satisfy:
\[
||Q_n||_U\leq ||f||_U\quad\colon\quad n=1,2,\ldots
\]


\noindent
To prove Theorem B.1 one constructs for each
$n\geq 1$ a Jordan curve $\Gamma_n$
which surrounds $\bar U$, i.e. its interior Jordan domain
$U_n$ contains
$\bar U$ and for every point  $p\in\Gamma_n$ the
distance of $p$ to $\Gamma$ is $<1/n$.
It is trivial to see that such a family of Jordan curves
exist where the domains
$U_1,U_2,\ldots$ decrease.
Next, fix a point $z_0\in U$. There exists the unique  conformal map
$\psi_n$ from $U_n$ onto $U$ such that
\[ 
\psi_n(z_0)=z_0\quad\colon\quad
\psi'_n(z_0)\,\,\text{is real and positive}
\]
With these notations Lindelšf used the following lemma whose proof
is  left as
an exercise:
\medskip

\noindent
{\bf B.2. Lemma}
\emph{For each compact subset
$K$ of $U$ the
maximum norms
$|\psi_n(z)-z|_K$ tend to zero as $n\to\infty$. Moreover,
the complex derivatives $\psi'_n(z_0)\to 1$.}
\medskip

\noindent
\emph{Proof of Theorem B.1.}
To each $n$ we set
\[
F_n(z)=f(\psi_n(z))\cdot\psi'_n(z)^{\frac{2}{p}}
\]


\noindent
By Lemma B.2 the sequence $\{F_n\}$ converges uniformly to
$f$ on compact subsets of $U$. Moreover, each
$F_n\in\mathcal O(U_n)$ and it is clear that

\[
\iint_U\,|f(z)|^p\cdot dxdy=
\iint_{U_n}\,|F_n(z)|^p\cdot dxdy
\]
hold for every $n$.
To get the required  polynomials $\{Q_n\}$
in Theorem B.1 for $H^p$-spaces it suffices to apply Runge's theorem for
each single $F_n$. This  detail of the proof is left to the reader.
For maximum norms we use the functions
\[
F_n(z)=f(\psi_n(z))
\]
and after apply Runge's theorem in the domains $\{U_n\}$.

\bigskip

\noindent{\bf B.3 Remark.}
More delicate
approximations by polynomials where
other norms such as the 
modulus  of continuity,  were 
established later by Lindelšf and  De VallŽ-Poussin.
We shall not pursue this any further.
The reader can
consult
articles by  De VallŽ-Poussin which contain
many interesting results
concerned with approximation theorems.



\bigskip


\centerline{\bf C. Approximation by fractional powers }

\bigskip

\noindent 
Here is the set-up in
the article \emph{†ber die approximation analytischer funktionen}
by Carleman from 1922.  
Let $0<\lambda_1<\lambda_2<\ldots$ 
be a sequence of positive real numbers and
$\Omega$ is a simply connected
domain contained in
the right half-space
$\mathfrak{Re}(z)>0$.
The functions 
$\{q_\nu(z)= z^{\lambda_\nu}\}$
are analytic in the half-plane,  i.e. with
$z=re^{i\theta}$ and $-\pi/2<\theta<\pi/2$ we have:
\[ 
q_\nu(z)=r^{\lambda_\nu}\cdot e^{i\lambda_\nu\cdot\theta}
\]


\noindent
{\bf C.1 Definition.}
\emph{The sequence $\Lambda=\{\lambda_\nu\}$
is said to be dense for approximation if there for each
$f\in\mathcal O(\Omega)$ exists a sequence of
functions of the form}
\[ 
Q_N(z)=\sum_{\nu=1}^N
\, c_\nu(N)\cdot q_\nu(z)\quad\colon\quad N=1,2,\ldots
\]
\emph{which converges uniformly to $f$ on compact subsets of $\Omega$.}

\bigskip

\noindent
{\bf C.2 Theorem.}
\emph{A sequence $\Lambda$ is dense if }
\[
\limsup_{R\to\infty}\,
\frac{\sum_R\,\frac{1}{\lambda_\nu}}{\text{Log}\,R}>0\tag{*}
\]
\emph{where $\sum_R$ means that we take the sum over
all $\lambda_\nu<R$.}
\medskip

\noindent
{\bf Remark.}
Above condition (*)  is the same for every
simply connected  
domain $\Omega$. Theorem C.2 gives
a \emph{sufficient} condition for an   approximation.
To get  necessary condition one must specify the domain
$\Omega$ and we shall not try to discuss this
more involved problem.
The proof of Theorem C.2 requires several steps, the crucial
is the 
uniqueness theorem in C.4 while the proof of Theorem C.2 is
postponed until C.5.
\medskip


\centerline {\bf C.3 A uniqueness theorem.}
\medskip

\noindent
Consider a closed Jordan curve
$\Gamma$ of class $C^1$  contained in
$\mathfrak{Re}\, z>0$.
When $z=re^{i\theta}$ stays in the right
half-plane  we get an entire function of the complex 
variable $\lambda$ defined by:
\[ 
\lambda\mapsto z^\lambda= r^\lambda \cdot e^{i\theta\cdot\lambda}
\] 
We conclude that
a real-valued 
and continuous function $g$ on $\Gamma$ gives
an entire function of $\lambda$ defined by:
\[
 G(\lambda)=\int_\Gamma\, g(z)\cdot z^\lambda\cdot \bigl|dz\bigr|_\Gamma
 \]
where $|dz|_\Gamma$  is the arc-length on $\Gamma$.
With these notations one has
\bigskip

\noindent
{\bf C.4 Theorem.}
\emph{Assume that $\Lambda$ satisfies the condition in
Theorem C.2. Then, if $G(\lambda_\nu)=0$ for every
$\nu$ it follows that 
the $g$-function is  identically zero.}

 


\medskip

\noindent
\emph{Proof.} 
We leave as an exercise to the reader to verify that if
the $G$-function is identically zero then 
$g=0$.  There remains to show that if
$G(\lambda_\nu)=0$ for every $\nu$ then
$G=0$. To oprove this we assume the contrary, i.e. that
$G$ is not identically  zero.
We leave it to the reader to verify that
there exist constants $A,K$ and $0<a<\frac{\pi}{2}$
such that:
\[ 
|G(\lambda)|\leq K\cdot e^{|\lambda|}\quad\text{and}\quad
|G(is)|\leq K\cdot e^{|s|\cdot a}\quad\colon\,\lambda\in{\bf{C}}\,\,
\colon s\in{\bf{R}}\tag{i}
\]


\noindent
Set
\[ 
U(r,\phi)=\log\,\bigl |G(re^{i\phi})\bigr |\tag{ii}
\]


\noindent
and let  $\{ r_\nu e^{i\phi_\nu}\}$
be the zeros of $G$ in $\mathfrak{Re}(z)>0$. 
Carleman's integral formula
from ¤ xx formula gives the following for each
$R>1$:
\[
\sum_{1<r_\nu<R}\,
\bigl[\frac{1}{r_\nu}-\frac{r_\nu}{R^2}\bigr]\cdot\text{cos}\,\theta_\nu=
\frac{1}{\pi R}\cdot\int_{-\pi/2}^{\pi/2}\,
U(R,\phi)\cdot\text{cos}\,\phi\cdot d\phi+
\]
\[
\frac{1}{2\pi R}\cdot\int_1^R\, \bigl(\frac{1}{r^2}-\frac{1}{R^2}\bigr)
\cdot\bigr[\, U(r,\pi/2)+U(r,-\pi/2)\,\bigr]\cdot dr+
c_*(R)\tag{iii}
\]
where the remainder term $c_*(R)$
satisfies
\[
|c_*(R)|\leq K
\]
for a  constant which is independent of
$R$.
It follows easily from (i) that there exists a consntat $K^*$ such that
the right hand side is $\leq K^*$ for all $R>1$.
Next,
since $\{\lambda_\nu\}$ occur in the zeros of $G$, the left hand side in
(iii) majorizes
\[
\sum_{1<\lambda _\nu<R}\,
\bigl[\frac{1}{\lambda_\nu}-\frac{\lambda_\nu}{R^2}\bigr]\tag{iv}
\]
Now we get a contradiction because the reader can easily verify that
(*) entails that (iv) cannot be $\leq K^*$ for a constant as $R\to\|infty$.



\bigskip

\centerline{\bf Proof of Theorem C.2}

\bigskip
\noindent
Denote by $\mathcal O^*(\Lambda)$ the linear space of analytic functions
in the right half-plane given by finite ${\bf{C}}$-linear combinations of the fractional
powers $\{z^{\lambda_\nu}\}$.
To obtain uniform approximations over relatively compact
subsets when 
$\Omega$ is a simply connected  domain in $\mathfrak{Re}(z)>0$,
it suffices to regard a 
closed Jordan arc
$\Gamma$ 
which borders a Jordan domain $U$ where
$U$ is a relatively compact subset of
$\Omega$. In particular $\Gamma$ has a positive distance to
the imaginary axis and there remains  to show
that when (*) holds in Theorem C.2, then
an arbitrary analytic function $f(z)$ defined in some open
neighborhood of $\bar U$ can be uniformly approximated
by $\mathcal O^*(\Lambda)$-functions over a relatively compact subset
$U_*$ of $U$.
To achieve this 
we shall use a trick which
reduces the proof of uniform approximation
to a problem concerned with $L^2$-approximation on
$\Gamma$.
To begin with
we have
\medskip

\noindent
{\bf C.5 Lemma.}
\emph{The uniqueness in Theorem C.4 implies that
if $V$ is a real-valued function on
$\Gamma$ then there exists a sequence 
$\{Q_n\}$ from the family $\mathcal O(\Lambda)$
 such that}
\[
\lim_{n\to\infty}\, \int_\Gamma\,\bigl|Q_n-V|^2\cdot |dz|=0
\]
\medskip

\noindent 
The proof  is left as an exercise.

\medskip

\noindent
{\bf C.6 A tricky construction.}
Let $f(z)$ be analytic in a neighborhood of the closed
Jordan domain $\bar U$ bordered by
$\Gamma$. Define a new analytic function
\[ 
F(z)=\int_{z_*}^z\,\frac{f(\zeta)}{\zeta}\cdot d\zeta\tag{1}
\]
where $z_*$ is some point in $\bar U$ whose specific  choice
does not affect the
subsequent discussion.
We can write $F=V+iW$ where $V=\mathfrak{Re}(F)$.
Lemma C.5 gives a sequence $\{Q_n\}$ which approximates
$V$ in the $L^2$-norm on $\Gamma$.
Using this $L^2$-approximation we get
\medskip

\noindent
{\bf Lemma C.7}
\emph{Let $U_0$ be relatively compact in $U$.
Then there exists a sequence of real numbers
$\{\gamma_n\}$ such that}
\[
\lim_{n\to\infty}\, \bigl|| Q_n(z)-i\cdot\gamma_n-F(z)\bigl|_{U_0}=0
\]
\medskip

\noindent
Again we leave out the proof as an exercise.
Next, taking complex derivatives  Lemma C.7  implies that
if $U_*$ is even smaller, i.e. taken to be a relatively compact in
$U_0$, then there exists a  uniform approximation of derivatives:

\[
Q'_n(z)\to F'(z)=\frac{f(z)}{z}
\]
This implies  that
\[
 z\cdot Q'_n\to f(z)
\]
holds uniformly in
$U_*$. Next, notice that  
\[
z\cdot \frac{d}{dz}(z^{\lambda_\nu})
=\lambda_\nu\cdot z^{\lambda_\nu}
\]
hold for each $\nu$. Hence
$\{z\cdot Q'_n(z)\}$  again belong to  the $\mathcal O(\Lambda)$-family.
So we achieve the required uniform approximation of
the given $f$ function on $U_*$ which
completes the proof of
Theorem C.2.




\bigskip



\centerline{\bf D. Theorem of MŸntz}
\bigskip



\noindent
Theorem D.1   below
is due to MŸntz in the   article
\emph{†ber den Approximationssatz von
Weierstrass} from 1914. The simplified version of the original proof below
is given in [Car].
Here is the set up: Let
$0<\lambda_1<\lambda_2<\ldots$. To
each $\nu$ we get the function $x^{\lambda_\nu}$
defined on the real unit interval $0\leq x\leq 1$.
We say that the sequence $\Lambda=\{\lambda_\nu\}$
is $L^2$-dense if the family
$\{x^{\lambda_\nu}\}$
generate a dense linear subspace of the Hilbert space of
square integrable functions on $[0,1]$.
\medskip

\noindent
{\bf D.1 Theorem.} \emph{The necessary and sufficient condition for
$\Lambda$ to be $L^2$-dense is that
$\sum\,\frac{1}{\lambda_\nu}$ is convergent.}
\bigskip

\noindent
\emph{D.2 Proof of necessity.} 
If
$\Lambda$ is not $L^2$-dense there
exists some $h(x)\in L^2[0,1]$
which is not identically zero while
\[ 
\int_0^1\, h(x)\cdot x^{\lambda_\nu}\cdot dx=0
\quad\colon\quad\nu=1,2,\ldots\tag{1}
\]
Now 
consider the function
\[ 
\Phi(\lambda)= 
\int_0^1\, h(x)\cdot x^{\vvv i\lambda}\cdot dx\tag{2}
\]
It is clear that
$\Phi$ is analytic in
the right half plane
$\mathfrak{Im}\,\lambda>0$.
If $\lambda=s+it$ with $t>0$ we have
\[ 
|x^\lambda|= x^t\leq 1
\]
for all $0\leq x\leq 1$. 
From this and the Cauchy\vvv Schwarz inequality we
see that
\[
|\Phi(\lambda)|\leq ||h||_2\quad\colon \lambda\in U_+\tag{3}
\]


\noindent 
Hence $\Phi$ is a bounded analytic function in
the upper half-plane. At the same time
(1) means that the zero set of
$\Phi$ contains the sequence 
$\{\lambda\uuu\nu\cdot i\}$.
By the  integral formula formula we have seen in XX that this entails that
\[
\sum\,\frac{1}{\lambda_\nu}<\infty\tag{*}
\]
which proves the necessity.

\medskip

\noindent
\emph{Proof of sufficiency.}
There remains to show that ifwe have the convergence in 
(*) above then
there exists a non-zero
$h$-function i $L^2[0,1]$ such that
(1) above holds. 
To find $h$ we first construct an analytic function
$\Phi$ by
\[
\Phi(z)= \frac{\prod_{\nu=1}^\infty\,
\bigl(1-\frac{z}{\lambda_\nu}\bigr)}
{ \prod_{\nu=1}^\infty\,\bigl(1+\frac{z}{\lambda_\nu}\bigr)}\cdot
\frac{1}{(1+z)^2}\quad\colon\quad \mathfrak{Re}\, z>0\tag{i}
\]
Notice that $\Phi(z)$ is defined in the right half-plane
since 
the series (*) is convergent. 
When $\mathfrak{Re}(z)\geq 0$ we notice that
each quotient
\[
\frac{1-\frac{z}{\lambda_\nu}}
{1+\frac{z}{\lambda_\nu}}
\]
has absolute value $\leq 1$.
It follows that
\[ 
|\Phi(x+iy)|\leq\frac{1}{1+x+iy|^2}=\frac{1}{(1+x)^2+y^2}\tag{ii}
\]
In particular the function $y\mapsto \Phi(iy)$
belongs to  $L^2$ on the real $y$\vvv line.
Now we set
\[
f(t)=
\frac{1}{2\pi}
\int_{-\infty}^\infty\, e^{ity}\cdot
\Phi(iy)\cdot dy\tag{ii}
\]
using the inequality (ii)
If $t<0$
we can move the line integral of $e^{tz}\cdot \Phi(z)$ from
the imaginary axis to a line $\mathfrak{Re}(z)= a$
for every $a>0$ and it is clear that

\[
\lim\uuu{a\to +\infty}\, 
\int_{-\infty}^\infty\, e^{\vvv at+ity}\cdot
\Phi(a+iy)\cdot dy=0
\]
We conclude that $f(t)=0$ when $t<0$.
Next, since $y\mapsto \Phi(iy)$ is an $L^2$\vvv function it follows by
Parseval's equality that

\[
\int\uuu 0^\infty\, |f(t)|^2\cdot dt<\infty
\]
Moreover, for a fixed $\lambda\uuu \nu$ we have
\[
\int_0^\infty\, f(t) e^{-\lambda_\nu t}\cdot dt=
\frac{1}{2\pi}\cdot \int\uuu 0^\infty\,[
\int_{-\infty}^\infty\, e^{ity}\cdot
\Phi(iy)\cdot dy\,]\cdot e^{\vvv \lambda\nu t}\cdot dt=
\]
\[
\int_{-\infty}^\infty\, \frac{1}{iy\vvv \lambda\uuu\nu}\cdot 
\Phi(iy)\cdot dy
\]
where the last equality follows when the repeated integral is reversed.
By construction $\Phi(z)$ has a zero at $\lambda\uuu\nu$
and therefore (xx) above remains true with
$\Phi$ replaced by
$\frac{\Phi(z)}{z\vvv \lambda\uuu\nu}$ which entails that

\[
\int\uuu 0^\infty\, f(t)\cdot e^{\vvv \lambda\uuu\nu t}\cdot dt=0
\]

\noindent
At this stage we obtain the requested
$h$\vvv function. Namely, since $t\mapsto e^{\vvv t}$ identifies
$(0,+\infty)$ with $(0,1)$ we get a function $h(x)$ on $(0,1)$
such that
\[ 
h(e^{\vvv t})= e^{t/2}\cdot f(t)
\]
The reader may verify
that
\[
\int\uuu 0^1\, |h(x)|^2\cdot dx=\int\uuu 0^\infty\, |f(t)|^2\cdot dt
\]
and hence $h$ belongs to $L^2(0,1)$.
Moreover, one verifies that the vanishing in (xx) above entails that
\[
\int\uuu 0^1\,  h(x)\cdot x^{\lambda\uuu\nu}\cdot dx=0
\]
Since this holds for every $\nu$ we have proved the
sufficiency which therefore finishes the proof of Theorem D.1.

















\newpage

\centerline {\bf{D.2 Another density result}}
\bigskip

\noindent
Density results using exponential functions appear in many 
applications. For example, 
in the
the \emph{Sampling Theorem} by Shanning
used in telecommunication engineering.
Expressed in analytic function theory
it 
can be formulated as follows:
\medskip

\noindent {\bf {D.3  Theorem.}}
\emph{Let $T>0$ and $g(t)$ is an $L^2$-function on the interval $[0,T]$
which is not identically zero and suppose that
$a>0$ is such that}
\[
\int_0^T\, e^{inat}\cdot g(t)\cdot dt=0
\quad\colon\quad n\in{\bf{Z}}
\]
\emph{Then we must have}
\[ 
a\geq\frac{2\pi}{T}
\]
\medskip

\noindent
{\bf Remark} This result  is due to Fritz Carlson in his article
[xx] from 1914.
Carlson's result was later improved by Titchmarsh
and goes as follows:

\bigskip

\noindent
{\bf{D.4 Theorem.}}
\emph{Let $0<m\uuu 1<m\uuu 2<\ldots$
be an increasing sequence of positive real numbers such that}
\[
\limsup\uuu{n\to\infty}\, \frac{n}{m\uuu n}>1\tag{*}
\]
\emph{Then if $f(x)\in L^2(0,1)$ and}
\[
\int\uuu 0^1\, e^{im\uuu n x}\cdot f(x)\cdot dx=
\int\uuu 0^1\, e^{-im\uuu n x}\cdot f(x)\cdot dx=0\tag{**}
\]
\emph{hold for each $n$, it follows that $f=0$.}
\medskip

\noindent
\emph{Proof.}
Notice that
(**) implies that we also have vanishing integrals using
$f(\vvv x)$.
Replacing $f$ by $f(x)+f(\vvv x)$ or by $f(x)\vvv f)\vvv x)$,
it suffices to prove the result when $f$ is even or odd.
Let us show that there cannot exist an even
$L^2$\vvv function $f$ such that the integrals (**) vanish while
\[
\int\uuu 0^1\, f(x)\cdot dx=1\tag{i}
\]
We leave it to the reader to verify that
this gives Theorem D.4.
Put
\[
\phi(z)= \int\uuu{\vvv \pi}^\pi\, e^{izt}\cdot f(t)\cdot dt\tag{ii}
\]
Now  the entire function $\phi$ is even and (i) means that
$\phi(0)=1$.
Moreover, $\phi$  is an entire function of exponential type
and Cauchy\vvv Schwarz inequality gives
\[
|\phi(x+iy)|\leq ||f||\uuu 2\cdot e^{\pi|y|}\tag{iii}
\]
for all $z=x+iy$.
Moreover, Parseval's equality shows that
the restriction of $\phi$ to the real $x$\vvv line belongs to
$L^2$ which by the result in ¤ X
implies
that $\phi$ belong to the Carleman class $\mathcal N$.
So Theorem ¤ XX  gives the existence of a limit
\[
\lim\uuu{R\to \infty}\,
\frac{N\uuu\phi(R)}{R}= A\tag{iv}
\]
where $N\uuu\phi(R)$ is the counting function of zeros of $\phi$.
The inequality (iiii) and the result in XXX entails that
\[
A\leq 2\tag{v}
\]

\noindent
Next, since 
the zeros of $\phi$ contains the even sequence $\{-m\uuu\nu\}\,\cup\, \{m\uuu\nu\}$
we have the inequality
\[
N\uuu\phi(m\uuu n)\geq 2n\tag{vi}
\]
At the same time the limi formula (iv) gives:
\[ 
A=\lim\uuu{n\to \infty}\,
\frac{N\uuu\phi(m\uuu n)}{m\uuu n}\tag{vii}
\]
Finally, (vi) and the hypothesis (*) in the Theorem give
\[
\limsup\uuu{n\to \infty}
\frac{N\uuu\phi(m\uuu n)}{m\uuu n}\geq
2\cdot \limsup\uuu{n\to \infty}\frac{n}{m\uuu n}>2\tag{viii}
\]
This contradicts (v) and we conclude that the 
non\vvv zero function  $\phi$ 
cannot exist. Finally from (ii) and Fourier's inversion formula
the vanishing of $\phi$ entails that
$f=0$ which finishes the proof.




\newpage

\centerline{\bf {10. Convergence under substitution.}}
\bigskip

\noindent
{\bf{Introduction.}}
Let $\{a_k\}$ be a sequence of complex numbers where the additive series
$\sum\, a_k$ is convergent. This gives an analytic function
$f(z)$ defined in the open disc by
\[
f(z)=\sum\, a\uuu n\cdot z^n\tag{1}
\]
If $0<b <1$
we can expand $f$ around $b$ and obtain another series
\[
f(b+z)=\sum\, c\uuu n\cdot z^n\tag{2}
\]
From the   convergence of $\sum\, a\uuu k$
one  expects 
that the series
\[
\sum\, c\uuu n\cdot (1\vvv b)^n\tag{3}
\]
also is convergent. This is indeed true and was proved by Hardy and Littlewood
in (H\vvv L]. A more general result was established in [Carleman]
and we are going to expose results from Carleman's article.
In general, consider a
power series
\[ 
\phi(z)=\sum\, b_\nu\cdot z^\nu\tag{1}
\]
which 
represents an analytic function
$D$ where
$|\phi(z)|<1$ hold when $|z|<1$. There exists  the
composed analytic function 
\[ 
f(\phi(z))= \sum_{k=0}^\infty\ c_k\cdot z^k\tag{*}
\]
We seek conditions on $\phi$ in order that  the convergence of
$\{a\uuu k\}$ entails that
the series
\[
 \sum\, c\uuu k\quad\text{also converges}\tag{**}
\] 

\medskip

\noindent
First we consider the special case when
the $b$\vvv coefficients are real and non\vvv negative.
\medskip


\noindent
{\bf{8.1. Theorem.}} \emph{Assume that $\{b\uuu \nu\geq 0\}$
and that $\sum\, b\uuu \nu=1$. Then  (**) converges and the sum is equal to 
$\sum\, a\uuu k$.}



\bigskip


\noindent
\emph{Proof.}
Since  $\{b\uuu\nu\}$ are real and non\vvv negative
the Taylor series for $\phi^k$ also has non\vvv negative
real coefficients for every  $k\geq 2$. Put
\[ 
\phi^k(z)=\sum \, B\uuu{k\nu}\cdot z^ \nu
\]
and for  each pair of integers $k,p$ we set
\[
\Omega\uuu{k,p}=\sum\uuu{\nu=0}^{\nu=p} \, B\uuu{k\nu}\
\]
If $k\geq 2$ we notice that
\[
B_{kj}=\sum_{\nu=0}^j\, b_{j-\nu}\cdot B_{k-1,\nu}
\]
Since $\{b_\nu\}$ are non.-begstive with sum equal to one
the reader can easiy verify that the following hold:
\[ 
\lim_{N\to\infty}\, \Omega_{N,p}=0
\quad\text{for every}\quad p\tag{i}
\]
\[ 
k\mapsto \Omega_{k,p}
\quad\text{decreases for every }\quad p\tag{ii}
\]
\[
\sum\uuu {\nu=0}^\infty\, B\uuu{k\nu}=1
\quad\text{hold for   every }\quad k\tag{iii}
\]
\medskip

\noindent
Next, the  Taylor series of  
$f(\phi(z))$ is given by
\[
\sum a\uuu k\cdot \phi^k(z)
=\sum\uuu{\nu=0}^\infty\,\bigl[\sum\uuu {k=0}^\infty\, a\uuu k\cdot B\uuu{k\nu}\bigr ]\cdot z^\nu
\]

\noindent
For  each positive integer $n^*$ we set
\[ 
\sigma_p[n^*]=
\sum_{\nu=0}^{\nu=p}\, \,\bigl[\,\sum_{k=0}^{k=n^*}\, a_k\cdot B_{k,\nu}\bigr]\tag{1}
\]
\[
\sigma_p(n^*)= \sum_{\nu=0}^{\nu=p}\, \,\bigl[\,\sum_{k=n^*+1}^\infty\, a_k\cdot B_{k,\nu}\,\bigr]=\sum\uuu{k=n^*+1}^\infty\,a\uuu k \cdot \Omega\uuu{k,p}
\tag{2}
\]
Notice that 
\[
\sigma_p[n^*]+
\sigma_p(n^*)=\sum\uuu {k=0}^{k=p}c\uuu k\quad\text{hold for each}\quad p
\]
Our aim is to show that the last partial sums converge to 1 as  
$p\to\infty$.
To obtain  this we
study the $\sigma$\vvv terms   separately. Introduce the partial sums
\[
s\uuu n=\sum\uuu{k=0}^{k=n}\, a\uuu k
\]
By assumption  there exists a limit $s\uuu n\to S$ 
where $S=1$.
This   entails that
the sequence $\{s\uuu k\}$ is bounded and so is
the sequence $\{a\uuu k=s\uuu k\vvv s\uuu{k\vvv 1}\}$.
By (i) above it follows that
the last term in (2) tends to zero when $n^*$ increases. So if $\epsilon>0$
we find
$n*$ such that
\[
n\geq n^*\implies |\sigma\uuu p(n)|
\leq \epsilon\tag{3}
\]



\noindent

\noindent
\emph{A study of $\sigma_p[n^*]$}.
Keeping $n^*$ and $\epsilon$ fixed we apply (iii) for each $0\leq k\leq n^*$
and find an integer $p^*$ such that
\[
1\vvv \sum_{\nu=0}^{\nu=p} B_{k,\nu}\leq \frac{\epsilon}{n^*+1}
\quad\text {for all pairs }\quad p\geq p^*\,\colon\, 0\leq k\leq n^*
\]

\noindent
The   triangle inequality gives
\[
|\sigma_p(n^*)-s_{n^*}|\leq \frac{\epsilon}{n^*+1}\cdot \sum\uuu{k=0}^{k=n^*}\, |a\uuu k|
\quad\text {for  all  }\quad p\geq p^*\tag{4}
\]

\noindent
Since  $\sum\, a\uuu k$ converges the sequence
$\{a\uuu k\}$ is bounded, i.e. we have
a constant $M$ such that
$|a\uuu k|\leq M$ for all $k$.
Hence (4) gives
\[
|\sigma_p(n^*)-S|\leq \epsilon+\epsilon\cdot M
\quad\colon\quad p\geq p^*\tag{5}
\]
Together with (3) this entails that
\[
n\geq n^*\implies |\sum\uuu{k=0}^{n^*}\,  |c\uuu k\vvv s|\leq 
2\epsilon+ M\cdot \epsilon
\]
Since we can chose $\epsilon$ arbitrary small we conclude that 
$\sum c\uuu k$ converges and the limit is equal to $S$ which 
finishes the proof of Theorem 8.1.

\bigskip







\bigskip

\noindent
{\bf{8.2 A general case.}}
Now we  relax the condition that $\{b\uuu\nu\}$ are real and non-negative
but  impose extra conditions on $\phi$.
First we assume that $\phi(z)$ extends to a continuous function on
the closed disc, i.e. $\phi$ belongs to the disc\vvv algebra.
Moreover, we assume that 
$\phi(1)=1$ while $|\phi(z)|<1$ 
for all $z\in\bar D\setminus \{1\}$ which means that
$z=1$ is a peak point for $\phi$.
Consider   also  the function
$\theta\mapsto \phi(e^{i\theta})$ where $\theta$ is close to zero.
The final condition on $\phi$ is
that there exists some positive real number
$\beta$ and a constant $C$ such that
\[ 
|\phi(e^{i\theta})\vvv 1\vvv i\beta|\leq C\cdot \theta^2\tag{8.2.1}
\]
holds in some interval $\vvv \ell\leq \theta\geq\ell$.
This implies that for every integer $n\geq 2$
we get another constant $C\uuu n$ so that
\[ 
|\phi^n(e^{i\theta})\vvv 1\vvv in\beta|\leq C\uuu n\cdot \theta^2\tag{8.2.2}
\]
Hence the following integrals exist for all pairs
of integers $p\geq 0$ and $n\geq 1$:
\[
J(n,p)= \int\uuu{\vvv\ell}^\ell\,
\frac{\phi(e^{i\theta})^n\cdot (1\vvv \phi(e^{i\theta})}{
e^{ip\theta}\cdot (1\vvv e^{i\theta})}\cdot d\theta\tag{8.2.3}
\]
With these notations one has
\medskip

\noindent{\bf{8.2 Theorem.}}
\emph{Let $\phi$ satisfy the conditions above.
Then, if 
there exists a constant $C$ such that}
\[ 
\sum\uuu {k=0}^\infty\, |J(k,p)|\leq C\quad\text{for all}\quad p\geq 0\tag{*}
\] 
\emph{it follows that
the series (**) from the introduction
converges  and the   sum is equal to $\sum\, a\uuu k$.}
\bigskip







\noindent
{\emph {Proof}
With similar   notations as in  the previous proof 
we introduce the $\Omega$\vvv numbers by:
\[
\Omega\uuu{k,p}=\sum\uuu{\nu=0}^{\nu=k}\, B\uuu{k\nu}
\]
Repeating the proof of Theorem 8.1 the reader may
verify that
the series $\sum c\uuu k$ converges and has the limit $S$
if the following two conditions hold:
\[
\lim\uuu{N\to\infty}\, \Omega\uuu{N,p}=0
\quad \text{holds for every} \quad p\tag{i}
\]  
\[
\sum \uuu{k=0}^{\infty}\, 
\bigl|\Omega\uuu{k+1,p}\vvv \Omega\uuu{k,p}\bigr|\leq C
\quad\text{for  a constant}\quad C
\tag{ii}
\] 
where $C$ is
is independent of $p$.
Here (i) is clear since 
$\{g\uuu N(z)= \phi^N(z)\}$ converge uniformly to zero in
compact subsets of the unit disc and therefore
their Taylor coefficients  tend to zero with $N$.
To get   (ii)  we use residue calculus which gives:
\[
\Omega_{k+1,p}-\Omega_{k,p}=
\frac{1}{2\pi i}
\int_{|z|=1}\frac{\phi^k(z)}{z^{p+1}}\cdot \frac{1-\phi(z)}{1-z}\cdot dz\tag{iii}
\]
\medskip

\noindent
Let $\ell$ be a small positive number
and    $T_\ell$ denotes  the portion of the
unit circle where
$\ell \leq \theta\leq 2\pi\vvv \ell$. 
Since 1 is a peak \vvv point for $\phi$ there exists
some $\mu<1$ such that
\[ 
\max\uuu{z\in T\uuu\ell}\,|\phi(z)|\leq \mu
\]
This gives
\[
\frac{1}{2\pi}\cdot \bigl|\int_{z\in T\uuu\ell }\frac{\phi^k(z)}{z^{p+1}}\cdot \frac{1-\phi(z)}{1-z}\cdot dz
\bigl|\leq \mu^k\cdot \frac{2}{|e^{i\ell}\vvv 1}\bigr |\tag{iv}
\]
Since the geometric series $\sum\,\mu^k$ converges
it follows from (iii) and the construction of the $J$-integrals
in (3)
that (ii) above holds precisely when 
\[ 
\sum\uuu{k=0}^\infty\, |J\uuu \ell (k,p]|\leq C
\]
for a constant $C$ which is independent of $p$. This   finishes the
the proof of Theorem 8.2.

\bigskip

\noindent
{\bf{8.3. Oscillatory integrals.}}
Condition  (*) in Theorem 8.2.1  is   implicit. 
We shall therefore find
a sufficient condition in order that
the $J$\vvv integrals satisfy (*) which is  expressed by
local conditions on the 
$\phi$\vvv function close to
$z=1$. To begin with (8.2.1)
enable us to write
\[ 
\phi(e^{i\theta})= e^{i\beta \theta+\rho(\theta)}\tag{i}
\]
when  $\theta\simeq 0$  and
\[
\rho(\theta)= O(\theta^2)\tag{ii}
\]
The next result gives  the requested
convergence of the composed series
expressed  by an additional   condition on the $\rho$\vvv function 
in (i) above.

\bigskip

\noindent{\bf{8.4. Theorem.}}
\emph{Assume that $\rho(\theta)$ is a $C^2$-function on some interval 
$\vvv\ell <\theta<\ell$ and that the second derivative
$\rho''(0)$ is real and negative.
Then (*) in Theorem 8.2 holds.}
\bigskip


\noindent
{\bf{Remark.}}
The proof is left as  a (hard) exercise to the reader. If necessary, consult
Carleman's article [Car] for   a detailed proof.






\bigskip

\centerline{\bf 11. The series $\sum\, \bigl [a_1\cdots a_\nu\bigr ]^{\frac{1}{\nu}}$}
\bigskip

\noindent
{\bf{Introduction.}}
We shall prove a result from [Carleman:xx. Note V page 112-115].
Let $\{a_\nu\}$ be a sequence of positive real numbers
such that $\sum\, a_\nu<\infty$ and 
$e$ denotes Neper's constant. 

\medskip

\noindent
{\bf 9.1 Theorem.} \emph{Assume that the series $\sum\, a_\nu$  is 
convergent and let $S$ be the sum.
Then one has the strict inequality}
\[
\sum_{\nu=1}^\infty\, 
\bigl [a_1\cdots a_\nu\bigr ]^{\frac{1}{\nu}}<e\cdot S\tag{*}
\]



\noindent
{\bf Remark.}
The result is sharp in the sense that $e$ cannot be replaced by a smaller constant.
To see this we
consider a large positive integer $N$ and take the finite series
$\{a_\nu=\frac{1}{\nu}\quad\colon 1\leq \nu\leq N\}$.
Stirling's limit formula gives:
\[
\bigl [a_1\cdots a_\nu\bigr ]^{\frac{1}{\nu}}\simeq\frac {e}{\nu}\quad\colon\,\nu>>1
\] 
Since the harmonic series
$\sum\,\frac{1}{\nu}$ is divergent we conclude that
for every $\epsilon>0$ there exists some large integer $N$ such that
$\{a_\nu=\frac{1}{\nu}\}$ gives
\[
\sum_{\nu=1}^{\nu=N}\, 
\bigl [a_1\cdots a_\nu\bigr ]^{\frac{1}{\nu}} >
(e-\epsilon)\cdot \sum_{\nu=1}^{\nu=N}\, \frac{1}{\nu}
\]



\noindent
There remains to prove the strict upper bound (*)
when $\sum\, a_\nu$ is a convergent positive series.
To attain this we  first establish  inequalities for finite series.
Given a positive integer $m$ we consider the variational problem
\[
\max_{a_1,\ldots,a_m}\, 
\sum_{\nu=1}^{\nu=m}\, 
\bigl [a_1\cdots a_\nu\bigr ]^{\frac{1}{\nu}} \quad
\text{when}\quad a_1+\ldots+a_m=1\tag{1}
\]
\medskip

\noindent
Let $a^*_1,\ldots,a^*_m$ give a maximum and set
$a_\nu^*=e^{-x_\nu}$.
The Lagrange multiplier theorem gives a number
$\lambda^*(m)$ such that if
\[ 
y_\nu=\frac{x_\nu+\ldots+x_m}{\nu}
\]
then
\[
\lambda^*(m)\cdot e^{-x_\nu}=\frac{1}{\nu}\cdot e^{-y_\nu}+\ldots+
\frac{1}{m}\cdot e^{-y_m}\quad \colon\quad 1\leq\nu\leq m\tag{2}
\]
A summation over all $\nu$  gives
\[ 
\lambda^*(m)=e^{-y_1}+\ldots+e^{-y_m}=
\sum_{\nu=1}^{\nu=m}\, 
\bigl [a^*_1\cdots a^*_\nu\bigr ]^{\frac{1}{\nu}}
\]
Hence $\lambda^*(m)$ gives
the maximum for the variational problem which is
no surprise since $\lambda^*(m)$ is 
Lagrange's multiplier.
Now we shall
prove  the strict inequality
\[ 
\lambda^*(m)<e\tag{3}
\]
We prove (3) by  contradiction.
To begin with, subtracting the successive equalities in (2) we get
the following equations:
\[
\lambda^*(m)\cdot [e^{-x_\nu}-e^{-x_{\nu+1}}]=
\frac{1}{\nu} \cdot e^{-y_\nu}\quad
\colon\quad 1\leq\nu\leq m-1\tag{4}
\]
\[
m\cdot \lambda^*(m)=e^{x_m-y_m}\tag{5}
\]
Next, set
\[ 
\omega_\nu=\nu(1-\frac{a_{\nu+1}}{a_\nu})\colon\quad 1\leq\nu\leq m-1\tag{6}
\]
With these notations it is clear that (4) gives
\[
\lambda^*(m)\cdot\omega_\nu=
e^{x_\nu-y_\nu}\quad \colon\quad 1\leq\nu\leq m-1\tag{7}
\]
It is clear that (7) gives:
\[
\bigl(\lambda^*(m)\cdot\omega_\nu\bigr)^\nu=
e^{\nu(x_\nu-y_\nu)}=
\frac{a_1\cdots a_{\nu-1}}{a_\nu^{\nu-1}}\tag{8}
\]
By an induction over $\nu$ which is left to the reader it follows
the $\omega$-sequence satisfies the recurrence equations:
\medskip
\[
\omega_\nu^\nu=\frac{1}{\lambda^*(m)}\cdot
\bigl(
\frac{\omega_{\nu-1}}{1-\frac{\omega_{\nu-1}}{\nu-1}}\bigr)^{\nu-1}
\quad \colon\quad 1\leq\nu\leq m-1\tag{9}
\]
Notice that we also have
\[
\omega_1=\frac{1}{\lambda^*(m)}\tag{10}
\]


\noindent
{\bf{A special construction.}}
With $\lambda$ as a parameter
we define a sequence $\{\mu_\nu(\lambda)\}$
by the recursion formula:
\[ 
\mu_1(\lambda)=\frac{1}{\lambda}\quad\text{and}\quad
[\mu_\nu(\lambda)]^\nu=\frac{1}{\lambda}\cdot
\bigl[
\frac{\mu_{\nu-1}(\lambda)}{1-\frac{\mu_{\nu-1}(\lambda)}{\nu-1}}\bigr]^{\nu-1}
\quad \colon\quad \nu\geq 2\tag{**}
\]


\noindent
From (5) and (9) 
it is clear that 
$\lambda=\lambda^*(m)$ gives
the equality
\[
\mu_m(\lambda^*(m))=m\tag{***}
\]
Now we come to the key point during the whole proof.

\medskip

\noindent
{\bf{Lemma}}
\emph{If $\lambda\geq e$ then
the $\mu(\lambda)$ -sequence satisfies}
\[
\mu_\nu(\lambda)<\frac{\nu}{\nu+1}\quad \colon\quad \nu=1,2,\ldots
\]


\noindent
\emph{Proof.}
We use an induction over $\nu$. With $\lambda\geq e$ we have
$\frac{1}{\lambda}<\frac{1}{2}$ so the case $\nu=1$ is okay.
If $\nu\geq 1$ and the lemma  holds for $\nu-1$, then
the recursion formula (**) and the hypothesis $\lambda\geq e$ give:
\[
[\mu_\nu(\lambda)]^\nu=\frac{1}{\lambda}\cdot
\bigl[
\frac{\mu_{\nu-1}(\lambda)}{1-\frac{\mu_{\nu-1}(\lambda)}{\nu-1}}\bigr]^{\nu-1}<
\frac{1}{e}\cdot
\bigl[
\frac{\frac{\nu-1}{\nu}}{1-\frac{\nu-1}{\nu(\nu-1)}}\bigr]^{\nu-1}
\]
Notice that the last factor  is 1 and hence:
\[
[\mu_\nu(\lambda)]^\nu<e<\bigl(1+\frac{1}{\nu})^{-\nu}
\]
where the last inequality follows from the wellknown
limit  of Neper's constant.
Taking the $\nu$:th root we get
$\mu_\nu(\lambda)<\frac{\nu}{\nu+1}$ which finishes the induction.
\medskip

\noindent
{\bf{Conclusion.}}
If $\lambda^*(m)\geq e$ then  the lemma  above and the
equality (***)  would entail that
\[ 
m=\mu(\lambda^*(m))<\frac{m}{m+1}
\] 
This is impossible when $m$ is a positive integer and hence 
we must have proved the  strict inequality
$\lambda^*(m)<e$.


\medskip


\noindent
{\bf{The strict inequality for an infinite series.}}
It remains to prove that the strict inequality holds for
a convergent series with an infinite number of terms.
So assume that we have an equality
\[
\sum_{\nu=1}^\infty\, 
\bigl [a_1\cdots a_\nu\bigr ]^{\frac{1}{\nu}}=e\cdot \sum_{\nu=1}^\infty\, a_\nu\tag{i}
\]
Put as as above
\[ 
\omega_n=n(1-\frac{a_{n+1}}{a_n})\tag{ii}
\]
Since we already know that the left hand side  is at least equal to  the right hand side
one can apply  Lagrange multipliers and we leave it to the reader to verify that
the  equality (i) gives  the recursion formulas
\[
\omega^n_n=\frac{1}{e} \cdot \bigl[
\frac{\omega_{n-1}}{1-\frac{\omega_{n-1}}{n-1}}\bigr]^{n-1}\tag{iii}
\]
Repeating the proof of the Lemma  above it follows that
\[
 \omega_n<\frac{n}{n+1}\implies
\frac{a_{n+1}}{a_n}>\frac{n}{n+1}\tag{iv}
\]
where (ii) gives the implication.
So with
$N\geq 2$ one has:
\[ 
\frac{a_{N+1}}{a_1}>
\frac{1\cdots N}{1\cdots N(N+1)}=\frac{1}{N+1}
\]
Now $a_1>0$ and since the harmonic series $\sum\,\frac{1}{N}$ is 
divergent it would follows that
$\sum\, a_n$ is divergent.
This contradiction
shows that a strict inequality must hold
in Theorem 9.1.












\newpage


\centerline{\bf{Appendix}}.

\bigskip





\centerline{\bf{A.  Entire functions of exponential type}}

\bigskip


\noindent
The class $\mathcal E$ of entire functions of exponential type is defined as follows:
\medskip

\noindent
{\bf{A.0 Definition.}} \emph{An entire function $f$ belongs to
$\mathcal E$ if and only if there exists constants
$A$ andÊ$C$ such that}
\[
 |f(z)|\leq C\cdot e^{A|z|}\quad\colon\,\, z\in{\bf{C}}\tag{*}
\] 

\medskip

\noindent
The results in Sections A\vvv B are  due to Hadamard and Lindelšf.
The  class $\mathcal N$ which appears in Section 3
was introduced by Carleman
who used it to prove certain approximation theorems related to moment problems.
The main results
deal with
Tauberian theorems which is treated in section D and
based upon Chapter V in [Paley\vvv Wiener].
Let us present some  of the results to be proved in ¤ D
while we refer to ¤ A-B for
more elementary material about the class $\mathcal E$.
Consider a non\vvv decreasing sequence $\{\lambda\uuu\nu\}$
of positive real numbers such that the series
\[ 
\sum\, \lambda\uuu \nu^{\vvv 2}<\infty\tag{1}
\]
When this holds there exists the entire function
given by a product series:

\[ 
H(z)=\prod\, (1\vvv \frac{z^2}{\lambda\nu^2})
\]
Notice that $H(z)$ is  positive on the imaginary
axis. We get  the function defined for real $y>0$:
\[
y\mapsto \frac{\log H(iy)}{y}=
\frac{1}{y}\, \sum \log\, (1+ \frac{y^2}{\lambda\nu^2})
\]
At the same time we  consider the intergals
\[ 
J(R)=\int\uuu{\vvv R}^R\, \frac {\log |H(x)|\cdot dx}{x^2}
\]

\medskip
\noindent
{\bf{0.1 Theorem.}} \emph{The existence of a constant $A$ such that}
\[
\lim\uuu{y\to \infty}\, \frac{\log H(iy)}{y}= \pi A \tag{i}
\] 
\emph{and}
\[
\lim\uuu{R\to \infty} J(R)=\vvv \pi^2A\tag{ii}
\]
\emph{are completely equivalent}
\medskip

\noindent
{\bf{Remark.}}
Of special interest is the case when
the limit in (ii) is automatic via an integrability condition, i.e. when
\[
\int\uuu{\vvv\infty}^\infty\,\frac {\bigl|\log |H(x)|\,\bigr |\cdot dx}{x^2}\tag{*}
<\infty
\]
In this case the $J$\vvv integrals converge and as a consequence 
there is a limit in (i) for some $A\geq 0$.
It turns out that further conclusions can be made.
namely, the convergence of (*) implies that
the
sequence $\{\lambda\uuu\nu\}$
also has a regular growth in the sense that if $N(r)$ is the counting function
which for every $r>0$ counts the number of $\lambda\nu\leq r$, then
there exists the limit
\[ 
\lim\uuu{R\to\infty}\,
\frac{N(R)}{R}=A
\]
with $A$ determined via Theorem 0.1.
We shall prove this in Section D and remark that the integrability condition
(*) is related to the study of the Carleman class in
Section C.















\newpage



\centerline{\bf{Growth of entire functions.}}


\bigskip

\noindent
Each entire function  $f(z)$ can be written in the form
\[ 
f(z)=az^m\cdot f_*(z)
\] 
where $f_*$ is entire and $f_*(0)=1$.
The  case when $f(0)=1$ is therefore not so special and
several formulas below take a simpler form when this holds.





\medskip

\noindent
{\bf{A.1 The functions $T_f(R)$ and $m_f(R)$}}.
They are defined for every $R>0$ by
\[ 
T_f(R)=\frac{1}{2\pi}\cdot   \int_0^{2\pi}\,
\log^+\,\bigl  |f(R(e^{i\theta})\bigr |\, d\theta\tag{i}
\]
\[
m_f(R)=\frac{1}{2\pi}\cdot \int_0^{2\pi}\,
\log^+\bigl[\frac{1}{\,\bigl  |f(R(e^{i\theta})\bigr |}\bigr]
\, d\theta\tag{ii}
\]
\medskip

\noindent
{\bf{A.2 The maximum modulus function.}} It is defined by
\[ M_f(R)= \max_
{0\leq \theta\leq 2\pi}\, |f(Re^{i\theta})|
\]
\medskip

\noindent
{\bf{A.3  The counting function $N_f(R)$}}.
To each $R>0$ we count the number of zeros of
$f$ in the punctured disc $0<|z|<R$. This integer is denoted by
$N_f(R)$, where
multiple zeros are counted according to their
multiplicities.
Jensen's formula shows that if
$f(0)=1$ then
\[
\int_0^R\, \frac{N_f(s)}{s}\cdot ds
=\frac{1}{2\pi}\cdot \int_0^{2\pi}\,
\log\,\bigl  |f(R(e^{i\theta})\bigr |\cdot d\theta=
T_f(R)-m_f(R)\tag{A.3.1}
\]
\medskip

\noindent
Since the left hand side always is
$\geq 0$, the inequality below holds under the hypothesis that
$f(0)=1$:
\[ 
m_f(R)\leq T_f(R)\tag{A.3.2}
\]
Next, since $N_f(R)$ is increasing we get
\[
\log 2\cdot N_f(R)\leq \int_R^{2R}\, \frac{N_f(s)}{s}\cdot ds
\leq T_f(2R)\implies
\]
\[
 N_f(R)\leq\frac{T_f(2R)}{\log 2}\tag{A.3.3}
 \]





\medskip

\noindent
{\bf{A.4 Harnack's inequality.}}
The function $\log^+|f|$ is subharmonic
which implies that whenever $0<r<R$ then
one has
\[
\log^+|f(re^{i\alpha})|\leq
\frac{1}{2\pi}\cdot \int_0^{2\pi}\,
\frac{R+r}{R-r}\cdot 
\log^+\,\bigl  |f(R(e^{i\theta})\bigr |\cdot d\theta
\]


\noindent
It follows that
\[
M_f(r)\leq \frac{R+r}{R-r}\cdot T_f(R)
\]
In particular we can take $R=2r$ and conclude that
\[
M_f(r)\leq 3\cdot T_f(2r)\quad\text{hold for every}\quad  r>0
\]
The last inequality gives:
\medskip

\noindent
{\bf{A.5 Theorem.}}
\emph{An entire function $f$ belongs to $\mathcal E$ if and only if there
exists a constant $A$ such that}
\[ 
T_f(R)\leq A\cdot R
\]
\emph{holds for every $R$.}
\bigskip

\noindent
{\bf{A.6 A division theorem.}}
Let $f$ and $g$ be in $\mathcal E$ and assume that
$h=\frac{f}{g}$ is entire. Now
\[ 
\log^+|h|\leq \log^+|f|+\log^+|g|\tag{i}
\]
In the case when $g(0)=1$ we apply (**) in A.3 and conclude that
\[ 
T_h(R)\leq T_f(R)+T_g(R)
\]
Hence Theorem A.5 implies that
$h$ belongs to $\mathcal E$.
We leave it to the reader to verify that this conclusion holds
in general, i.e. without any assumption on
$g(0)$.




\bigskip



\medskip

\noindent {\bf{A.7 Hadamard products.}}
Let $\{\alpha_\nu\}$ be a sequence of complex numbers
arranged so that the absolute values are non-decreasing.
The counting function of the sequence is 
denoted by $N_{\alpha(\bullet)}(R)$. Suppose that the counting function
satisfies:
\[
N_{\alpha(\bullet)}(R)\leq A\cdot R\quad\text{for all}\quad R\geq 1\tag{*}
\]

\medskip

\noindent 
{\bf{A.8 Theorem}}
\emph{When (*) holds the infinite product}
\[
\prod\, (1-\frac{z}{\alpha_\nu})\cdot e^{\frac{z}{\alpha_\nu}}
\]
\emph{converges for every $z$ and gives an entire function to be denoted by
$H_{\alpha(\bullet)}$ and  called the Hadamard product of the
$\alpha$-sequence.}

\medskip

\noindent
{\bf{A.9 Exercise.}}
Prove this theorem and show also
that there exists a constant $C$ which is independent of $A$ such that
the Hadamard product satisfies the growth condition:
\[
\bigl|H_{\alpha(\bullet)}(z)\bigr| \leq
C\cdot e^{A\cdot |z|\cdot \log\,|z|}\quad
\text{for all}\quad |z|\geq e
\]
\medskip


\noindent{\bf{A.10 Lindelšf's condition.}}
For a sequence $\{\alpha\uuu\nu\}$ we define the Lindelšf function
\[ 
L(R)= \sum_{|\alpha_\nu|<R}\, \frac{1}{\alpha_\nu}
\]

\noindent
We say that $\{\alpha\uuu\nu\}$
is of Lindelšf type  if there there exists a constant $L^*$ such that
\[
\bigl|L(R)\bigr|\leq L^*\quad\text{hold  for all}\quad  R.
\tag{A.10.1}
\]




\bigskip

\noindent
{\bf{A.11 Theorem.}}
\emph{If the $\alpha$-sequence satisfies (*) above  A.8 and is of the Lindelšf type,
then
there exists a constant $C$ such that the maximum modulos function of
$H\uuu {\alpha(\bullet)}$ satisfies}
\[
M_{H_{\alpha(\bullet)}}(R)\leq C\cdot e^{AR}
\]
\emph{and hence the entire function
$H\uuu {\alpha(\bullet)}(z)$
belongs to $\mathcal E$.}

\medskip

\noindent
{\bf{A.12 Exercise.}}
Prove this result.
A hint is to study the products
\[
\prod_{|\alpha_\nu|<2R}\,(1-\frac{z}{\alpha_\nu})e^{\frac{z}{\alpha_\nu}}
\quad\text{and}\quad 
\prod_{|\alpha_\nu|\geq 2R}\,(1-\frac{z}{\alpha\uuu\nu})e^{\frac{z}{\alpha_\nu}}
\] 
separately for every $R\geq 1$. Try also to find an upper bound for 
$C$ expressed by  $A$ and $L^*$.

\bigskip

\noindent
{\bf{A converse result.}}
Let $f$ belong to $\mathcal E$. Then the set of zeros 
$\{\alpha_\nu\}$
satisfies the
Lindelšf condition, i.e.
(**) in A.10 holds for a constant $L^*$.
To prove this we shall use:
\medskip


\noindent
{\bf{A.13 An integral formula.}}
With $R>0$ we put
$g(z)=\frac{1}{z}-\frac{\bar z}{R^2}$.
This is a is harmonic function in $\{0<|z|>R\}$ and 
$g=0$ on  $|z|=R$.
Let $f(z)$ be an entire function
with $f(0)=1$
and consider a pair $0<\epsilon<R$ where
$f$ has not zeros in
$|z|\leq\epsilon$.
Applying  Green's formula to $g$ and $\log\,|f|$
on an annulus $\{\epsilon<|z|<R\}$ we get:
\[
\sum_{|\alpha_\nu|<R}\, \,\bigl[ \frac{1}{\alpha_\nu}-
\frac{\bar\alpha_\nu}{R^2}\bigr]
= \frac{1}{\pi\cdot R}\cdot \int_0^{2\pi}\,
\log\,|f(Re^{i\theta})|  \cdot e^{-i\theta}\cdot d\theta-f'(0)
\tag{A.13.1}
\]
where the sum is taken over zeros of $f$ repeated with multiplicities in
the disc $\{|z|<R\}$.
\bigskip

\noindent
{\bf{A.14 The case $f\in\mathcal E$}}.
From (A.3.3) it follows that
the counting function $N\uuu f(R)$ is bounded by
$C\cdot R$ for some constant $C$.
With $f(0)=1$ and $R>0$ one has
\[
\bigl|\sum_{|\alpha_\nu|<R}\, 
\frac{\bar\alpha_\nu}{R^2}\bigr|\leq
\int_0^R\, s\cdot dN(s)\leq R\cdot N(R)
\]
Hence
\[ 
R\mapsto R^ {-2}\cdot \sum_{|\alpha_\nu|<R}\, 
\frac{\bar\alpha_\nu}{R^2}
\] 
is a bounded function. By (A.13.1) we conclude that
the Lindelšf functionof its zeros satisfies
(A.10.1) if
\[
R\mapsto \frac{1}{\pi\cdot R}\cdot \int_0^{2\pi}\,
\log\,|f(Re^{i\theta})|  \cdot e^{-i\theta}\cdot d\theta
\] 
is bounded and this follows from Theorem A.5 and the inequality (A.3.2).






 
\bigskip


\centerline {\bf{B. The factorisation theorem for  $\mathcal E$}}

\bigskip

\noindent
Consider some 
$f\in\mathcal E$. 
If $f$ has a  zero at
the origin we can write
\[ 
f(z)= az^m\cdot f_*(z)\quad\text{where}\quad f_*(0)=1
\]
It is clear that $f_*$ again belongs to $\mathcal E$ and in this way
we essentially reduce the study of $\mathcal E$-functions
$f$ to the case when $f(0)=1$. 
Above we proved that the set of zeros satisfies Lindelšf's condition
and therefore the Hadamard product

\[ 
H_f(z)=\prod\,(1-\frac{z}{\alpha_\nu})\cdot e^{\frac{z}{\alpha_\nu}}
\] 
taken over all zeros of $f$ outside the origin belongs to $\mathcal E$.
Now the quotient $f/H\uuu f$ is entire and we shall prove:


\medskip




\noindent{\bf{B.1 Theorem}}
\emph{Let $f\in\mathcal E$ where $f(0)=1$. Then
there exists a complex number $b$ such that}
\[ 
f(z)=e^{bz}\cdot H_f(z)
\]
\medskip

\noindent
\emph{Proof}.
The division
in
A.6 shows that the function
\[ 
G=\frac{f}{H_f}
\] 
is entire and belongs to $\mathcal E$.
By construction $G$ is zero\vvv free
which gives
the entire
function
$g=\log G$ for we have 
the inequality

\[ 
|g(z)|\leq 1+\log^+|G(z)|\leq 1+C|z|
\]
Since $G\in\mathcal E$ we see that 
$|g|$ increases at most like a linear function so by Liouvile's
theorem it is a polynomial of degree 1. 
Since $f(0)=1$  we have  $g(0)=0$ and hence $g(z)=bz$ for a complex number $b$
and the 
formula in Theorem B.1 follows.




\bigskip



\centerline{\bf\large C. The Carleman class $\mathcal N$}

\medskip

\noindent 
Let $f\in\mathcal E$. On the real $x$-axis we have the non-negative function
$\log^+\,|f(x)|$. If the integral
\[
\int_{-\infty}^\infty\, \frac{\log^+\,|f(x)| \cdot dx}{1+x^2}<\infty\tag{*}
\]



\noindent 
we say that $f$ belongs to the Carleman class 
denoted by $\mathcal N$. To study
$\mathcal N$ the following integral formula
plays an important role.

\medskip

\noindent 
{\bf C.1 Integral formula in a half-plane.}
Let $g(z)$ be analytic in the half plane $\mathfrak{Im}(z)>0$ which
extends continuously to the boundary $y=0$, i.e. to the real $x$-axis
and that $g(0)=1$. For each   pair $0<\ell<R$
we consider the domain
\[
\Omega_{\ell,R}=\{\ell^2<x^2+y^2<R^2\}\cap\,\{y>0\}
\]


\noindent
With $z=re^{i\theta}$
we have the harmonic function
\[
v(r,\theta)=(\frac{1}{r}-\frac{r}{R^2})\sin\,\theta=\frac{y}{x^2+y^2}-\frac{y}{R^2}
\]
Here $v=0$ on the upper half circle where $ |z|=R$ and $y>0$
and 
the outer normal derivative along the $x$-axis becomes
\[ 
\partial_n(v)=-\partial_y(v)=-\frac{1}{x^2}+\frac{1}{R^2}\quad\colon\,\quad x\neq 0
\]
Let $\{\alpha_\nu\}$ be the zeros of $g$ counted with multiplicites 
in the upper half-plane.
\medskip

\noindent
{\bf{C.2 Proposition.}} \emph{One has the equation}

\[ 
2\pi\cdot\sum\,\frac {\mathfrak{Im}\,\alpha\uuu\nu}{|\alpha_\nu|^2}\vvv
\frac{\mathfrak{Im}\, \alpha_\nu}{R^2}
=
\]
\[
\int_\ell^R\,\,\bigl(\frac{1}{R^2}-\frac{1}{x^2}\bigr)\cdot
\log\,|g(x)\cdot g(-x)|
\,dx
\vvv\frac{2}{R}\int_0^\pi\, \text{sin}(\theta)\cdot 
\log\,|g(Re^{i\theta})|\, d\theta+\chi(\ell)\tag{C.2.1}
\]
where $\chi(\ell)$ is a contribution from line integrals along
the half circle $|z|=\ell$ with $y>0$.

\bigskip



\noindent
{\bf {C.3 Exercise}}
Prove  this equation using
Green's theorem.
Above the 
term $\chi(\ell)$ is independent of $R$ so (*)
can be used to study  the asymptotic behaviour as $R\to+\infty$.
\medskip

\noindent
Next, the family of analytic functions $g(z)$ in the upper half\vvv plane
is identified with $\mathcal O(D)$
using a conformal map, i.e. with a given $g$ we get $g\uuu *\in \mathcal O(D)$
where
\[
g\uuu *(\frac{z\vvv i}{z+i})= g(z)
\] 
holds when $\mathfrak{Im}(z)>0$.
When $g$ extends to a continuous function on
the real $x$\vvv axis the reader can verify 
the equality
\[
\int\uuu 0^{2\pi}\, \log^+|g\uuu *(e^{i\theta})|\, d\theta=
2\cdot \int_{-\infty}^\infty\, \frac{\log^+|g(x)| }{1+x^2}\, dx\tag{i}
\]
This means that the last integral is finite if and only if
$g\uuu *$ belongs to the Jensen\vvv Nevanlinna class
and in XX we proved that this entails that
\[
\int\uuu 0^{2\pi}\, \log^+\frac{1}{|g\uuu *(e^{i\theta})|}\cdot d\theta<\infty\tag{ii}
\]
In particular we conclude that if an entire function $f$
satisfies (*) above then it follows that
\[
\int_{-\infty}^\infty\, \log^+\frac{1}{|f(x)|} \cdot 
\frac{dx}{1+x^2}\tag{iii}
\]
Since the absolute value of
$\log\,|f(x)|$ is equal to the sum
\[
 \log^+\frac{1}{|f(x)|}+\log^+|f(x)|
\]
we conclude from (iii) above that
(*) entails that the absolute value of
$\log\,|f(x)|$ is integrable with respect to
the density $\frac{1}{1+x^2}$.
Using this we can prove:



\bigskip

 \noindent {\bf C.4  Theorem} \emph{Let $f\in\mathcal N$. Then}
\[
\sum^*\,\mathfrak{Im}\frac{1}{\alpha_\nu}<\infty
\]
\emph{where the sum is taken over all zeros of $f$ 
which belong to the  upper half-plane.}
\bigskip


\noindent
\emph{Proof.}
Since $f\in\mathcal E$
there exists a constant $C$ such that $N\uuu f(R)\leq C\cdot R$.
If $R\geq 1$ it follows that
\[ 
\bigl|
R^{\vvv 2}\sum\,\bar\alpha_\nu|\leq R^{\vvv 2}\cdot R\cdot N\uuu f(R)\leq C
\]
where  the sum is taken over zeros in $\Omega\uuu{\ell,R}$.
Next, since $\mathfrak{Im}\,\alpha\uuu\nu>0$ in this open set
it follows that 
\[
\frac{\mathfrak{Im}\,\alpha_\nu}{|\alpha\uuu \nu|^2}>0
\]
 for every zero in the upper half\vvv plane. In particular this holds for the
 zeros in 
$\Omega\uuu{\ell,R}$ and 
passing to the limit as $R\to \infty$
it suffices to establish an upper bound in the right hand side of
Proposition C.2 with $g=f$.
The integral taken over the half\vvv circle where $|z|=R$
is uniformly  bounded with respect to $R$
since $f\in \mathcal E$
and we have the inequality XX from A.XX.
For the integral on the $x$\vvv axis we therefore only need an upper bound.
Since $R^{\vvv 2}\vvv x^{\vvv 2}\leq 0$
during the integration it suffices to find a constant $C$ such that
\[
\int_\ell^R\,\,\bigl(\frac{1}{x^2}-\frac{1}{R^2}\bigr)\cdot
\log^+\frac{1}{\,|f(x)\cdot f(-x)|}
\cdot dx\leq C\quad\text{hold for all}\quad R\geq 1
\]
The reader may verify that such a constant $C$ since (iii) above 
Theorem C.4 holds.


















\bigskip



\centerline{\bf{D. A Tauberian Theorem}}


\bigskip

\noindent
Let $\Lambda$
be a non-decreasing and discrete sequence 
of positive real numbers  $\{t_\nu\}$
whose counting function satisfies
$\mathcal N_\Lambda(R)\leq C\cdot R$  for some constant.
We get the entire function
\[
f(z)=
\prod\,(1-\frac{z^2}{t_\nu^2})
\]
which by the results in ¤ A belongs to $\mathcal E$.
If $R>0$ we set:
\[
 J_1(R)=\frac{\text{log}\, f(iR)}{R}
\quad\text{and}\quad 
J_2(R)=\int_{-R}^R\, \frac{\text{Log}\,| f(x)|}{x^2}\cdot dx\tag{*}
\]



\noindent
{\bf{D.1 Theorem.}}
\emph{There exists a limit }
\[ 
\lim\uuu {R\to\infty}\, \frac{N\uuu f(R)}{R}=2A
\]
\emph{if and only if at least one of the $J$\vvv functions has
a limit as $R\to\infty$. Moreover, when this holds
one has the equalities:}

\[
\lim_{R\to\infty} J_1(R)=\frac{\pi\cdot A}{2}\quad\text{and}\quad
\lim_{R\to\infty} J_2(R)=\vvv \frac{\pi^2\cdot A}{2}
\]
\bigskip

\noindent
The proof reauires seveeral steps.
First 
we introduce the following:
\medskip


\noindent
{\bf{D.2 The $W$\vvv functions.}}
On the positive real $t$-line we define the following functions:
\[ 
W_0(t)=\frac{1}{t}\quad\colon \,\,t\geq 1\quad
\text{and}\quad W_0(t)=0\quad\text{when}\,\,\, t<1\tag{1}
\]
\[
W_1(t)=\frac{\log(1+t^2)}{t}\tag{2}
\]
\[
W_2(t)=
\int_0^t
\frac{\log\,|1-x^2|}{x^2}\cdot dx\tag{3}
\]

\noindent
Next, 
the
real   sequence
$\Lambda=\{t_\nu\}$   gives a discrete measure
on the positive real axis where one  assigns a unit point mass at
every $t_\nu$. If repetitions occur, i.e. if some
$t$-numbers are equal we
add these unit point-masses.
Let $\rho$ denote  the resulting  discrete measure. 
The constructions of the $J$\vvv functions obviously give:
\[
J_k(R)=
\int_0^\infty\,W_k\bigl(\frac{R}{t}\bigr)\cdot\frac{d\rho(t)}{t}
\quad\colon\, k=1,2\tag{4}
 \]
Moreover, the reader can verify that
\[ 
\frac{\mathcal N_\Lambda (R)}{R}=
2\cdot \int_0^\infty\, W_0(R/t)\cdot \frac{d\rho(t)}{t}\tag{5}
\]
\medskip

\noindent{\bf{D.3 Exercise.}}
Show that under the assumption that
the function $\frac{\mathcal N_\Lambda (R)}{R}$ is bounded, it follows
the three $\mathcal W$-functions belong to
the $\mathcal {BW}$-algebra defined by the measure $\rho$
as explained in ¤ XXX.


\bigskip
\noindent
{\bf  D.4 Fourier transforms.} Recall that on $\{t>0\}$ we have the Haar
measure 
$\frac{dt}{t}$. 
We leave it to the reader to verify that all  the $W$-functions above  belong to $L^1({\bf{R}}^+)$, i.e. 
\[ 
\int_0^\infty\, \bigl|W_k(t)\bigr|\cdot \frac{dt}{t}<\infty\quad\colon
k=0,1,2
\tag{i}
\]
The Fourier
transforms  are defined by
\[ 
\widehat W_k(s)=
\int_0^\infty\,  W_k(t)\cdot t^{-(is+1)}\cdot dt\tag{ii}
\]
We shall prefer to use the functions with reversed sign on $s$, i.e. set
\[
\mathcal F\,W_k(s)=\int_0^\infty\,  W_k(t)\cdot t^{is-1}\cdot dt\tag{iii}
\]

\medskip

\noindent
{\bf{D.5 Proposition}} \emph{One has the formulas}
\[
\mathcal F\,W_0(s)=\frac{1}{1-is}\tag{i}
\]
\[
\mathcal F\,W_1(s)= 
\frac {\pi \cdot e^{\vvv \pi s/2}}{(1\vvv is)\cdot (1+e^{\vvv \pi s})}
\]
\[
\mathcal F\,W_2(s)=\frac{1}{is}\cdot\bigl[
\frac{i\pi}{1-is}+
\frac{2\pi}{(i+s)\cdot (e^{\pi s/2}+e^{-\pi s/2})}\,\bigr]\tag{iii}
\]


\bigskip

\noindent
\emph{Proof.}
Equation (i) is easily verified and left to the reader.
To prove (ii) we use a partial integration which gives
\[
\mathcal F\,W_1(s)=\frac{1}{is\vvv 1}\cdot
\int\uuu 0^\infty\,\frac{2\cdot t^{is}\cdot dt}{1+t^2}
\]
To compute this integral we employ residue calculus where
we shall use
the function
\[ 
\phi(z)=\frac{z^{is}}{1+z^2}
\]
We perform  line integrals over 
large half\vvv circles where $z=Re^{i\theta}$ and $0\leq \theta\leq \pi$.
A residue occurs at $z=i$. Notice also that if $t>0$ then
\[
 (\vvv t)^{is}= t^{is}\cdot e^{\vvv \pi s}
 \]
This gives
\[
 \mathcal FW\uuu 1(s)=
 \frac{1}{1\vvv is)\cdot (1+e^{\vvv \pi s})}
 \cdot
 \lim\uuu {R\to\infty}\, \int\uuu{\vvv R}^R\, \phi(t)\cdot dt
\]
Here $\phi$ has a simple pole at $z=1$
so by residue calculus the last integral becomes
\[
\vvv 2\pi i\cdot (i)^{is}\cdot  \frac{1}{2i}
 =\vvv \pi\cdot e^{\vvv \pi s/2}
\]
Taking the minus sign into the account we conclude that

\[
 \mathcal FW\uuu 1(s)=
 \frac {\pi \cdot e^{\vvv \pi s/2}}{(1\vvv is)\cdot (1+e^{\vvv \pi s})}
\]
 


\noindent
For (iii) a partial integration gives
\[
\mathcal F\,W_2(s)=\vvv \frac{1}{is}\cdot
\int\uuu 0^\infty\, \log|1\vvv t^2|\cdot t^{is\vvv 2}\cdot dt
\]
Here we computed the right hand side in
[Residue Calculus] which gives  (iii).
\bigskip




\centerline {\emph{ D.6  Proof of Theorem D.1}}
\medskip

\noindent
The formulas for the Fourier transforms in Proposition D.5  show that each
of them is $\neq 0$ on the  real $s$-line.
Hence we can apply the general result in XX
to the discrete measure $\rho$ since
the
$\mathcal W$-functions belong to
the $\mathcal {BW}$-algebra from ¤ XXX. 
This implies that if one of the three
limits in Theorem D.1   exists, so do the other.
To get the relation between the limit values we 
only have to evaluate the Fourier transform at $s=0$.
From Proposition D.5 we see that
\[
\mathcal FW_0(0)=1\quad\,\colon\quad 
F\mathcal W_1(0)=\frac{\pi}{2}
\]
Finally, (iii) in (D.4) and a computation which is left to the reader
gives
\[
F\mathcal W_2(0)=-\frac{\pi^2}{2}\tag{**}
\]

\noindent 
This gives the formulas
in
Theorem D.3 by the general result for $\mathcal{BW}$\vvv algebras in XXX.
\bigskip

\noindent{\bf {D.7 An application}}.
Using Theorem D.1 we can prove the following: 
\bigskip

\noindent
{\bf D.8  Theorem} \emph{For each $f\in\mathcal N$ there exists the limit:}
\[ 
\lim_{R\to\infty}\,\frac{N_f(R)}{R}
\]


\noindent 
\emph{Proof.}
The product $f(z)\cdot f(\vvv z)$ also 
belongs to $\mathcal N$ and for this even function
the counting function is twice that of $f$. So it suffices to prove
Theorem D.8  when $f$ is even.
We may also assume that $f(0)=1$ and since
$f\in\mathcal E$ it is given by a Hadamard product
\[
f(z)=\prod^*\, (1-\frac{z^2}{\alpha_\nu^2})\tag{1}
\]
where $\prod^*$ indicates the we  take the product of zeros whose
real part is $>0$ and if they are purely imaginary 
they are of the form $b\cdot i$ with $b>0$.
We can  replace the zeros by their absolute values and construct
\[
f_*(z)=\prod^*\, (1-\frac{z^2}{|\alpha_\nu|^2})\tag{2}
\]


\noindent
If $x$ is real we see that 
\[
|f_*[x)|\leq |f(x)|\tag{3}
\]
We conclude that if $f$ belongs to
$\mathcal N$ so does $f_*$.
At the same time their counting functions of zeros are equal.
This reduces the proof  to the special case when
$f$ is even and the zeros  are real and at this stage it is clear that
Theorem D.1 gives
existence of the limit  in Theorem D.8.


\medskip












\bigskip


\centerline{\bf{E. Application to measures with compact support.}}
\bigskip

\noindent
Le $\mu$ be a Riesz measure on the real $t$\vvv line with
compact support in an interval $[\vvv a,a]$ where
we assume that both end\vvv points belong to the support.
The measure is in general complex\vvv valued.
Now we get the entire function

\[
f(z)= \int\uuu{\vvv a}^a\, e^{\vvv izt}\cdot d\mu(t)
\]
Here $f$ restricts to a bounded function on the real $x$\vvv axis with
maximum norm $\leq ||\mu||$.
Hence $f$ belongs to $\mathcal N$ which means that
Theorem D.8 holds and the reader may now verify the following:
\medskip

\noindent
{\bf{E.1 Theorem.}}
\emph{One has the equality}
\[
\lim\uuu{R\to \infty}\,\frac{N\uuu f(R)}{R}=\frac{a}{\pi}
\]


\bigskip



















\centerline{\bf {F. Tauberian theorems with a remainder term}}
\medskip

\noindent
An extension of
Theorem D.1 which  contains remainder terms were
established by Beurling in 1936.
An example of Beurling's results  goes as follows:
Let
\[ 
f(z)=\prod\,(1\vvv \frac{z^2}{t\uuu\nu^2})
\]
be an even and entire function of exponential type with real zeros
as in section D. 

\medskip

\noindent
{\bf{F.1 Theorem.}}
\emph{Let $A>0$ and $0<a<1$ and assume that there 
exists a constant $C\uuu 0$ such that}
\[
\bigl|\vvv \frac{1}{\pi^2}\cdot \int\uuu 0^R\,
 \frac{\log |f(x)|}{x^2}\cdot dx\vvv A\,\bigr|\leq
 C\uuu 0\cdot R^{\vvv a}
 \]
\emph{hold for all $R\geq 1$.
Then there is another constant $C$ such that}
\[
\bigl|\, N\uuu f(R)\vvv R\bigr|\leq C\uuu 1\cdot R^{1\vvv a/2}
\]
\medskip

\noindent
{\bf{Remark.}}
Beurling's original manuscript which contains a proof of
Theorem F.1 as well as other 
results dealing with remainder terms    has remained
unpublished. It
was   resumed with details of proofs
in  a Master's Thesis at 
Stockholm University 
by F. GŸlkan in 1994.
The interested reader should also consult articles by
Beurlings former Ph.d student
S. Lyttkens which prove various Tauberian theorems with
remainder terms. See also work by T. Ganelius 
for closely related material.



\newpage








\centerline{\bf {XVI.. Beurling-Wiener  algebras}}

\bigskip

\noindent
\centerline{\emph{Contents}}
\bigskip

\noindent


\medskip

\noindent
\emph{A: Beurling-Wiener algebras on the real line.}

\medskip

\noindent
\emph{B: A Tauberian theorem}


\medskip

\noindent
\emph{C: Ikehara's theorem}

\medskip
\noindent
\emph{D: The Gelfand space of $L^1({\bf{R}}^+)$.}

\bigskip

\centerline {\bf{Introduction.}}

\bigskip

\noindent
The cornerstone in this section is Wiener's general Tauberian Theorem.
It will be 
applied
to the   class of 
Beurling\vvv Wiener algebras where the ordinary convolution algebra
$L^1({\bf{R}}) $ is replaced by  weight algebras
introduced by Beurling in the article [Beurling: 1938].
Here follows the set\vvv up in this section.
Consider
the Banach space $L^1({\bf{R}})$
of 
Lebesgue measurable and absolutely integrable functions whose
product is defined by  convolutions:
\[ 
f*g(x)=\int\, f(x-y)g(y)\, dy
\]

\medskip




\noindent {\bf A.1 The space $\mathcal F_0^\infty$.}
On the $\xi$-line we have the space $C_0^\infty$ 
of infintely differentiable functions with compact support.
Each $g(\xi)\in C_0^\infty$ yields an $L^1$-function on the real 
$x$-line defined by
\[ 
\mathcal F(g)(x)=\frac{1}{2\pi}\int\, e^{ix\xi}\, g(\xi)\,d\xi\tag{*}
\]
The resulting subspace of $L^1$ is denoted by
$\mathcal F_0^\infty$.

\medskip


\noindent {\bf A.2  Beurling-Wiener algebras.}
A subalgebra B of $L^1$
is called a Beurling-Wiener algebra - for short a 
$\mathcal B\mathcal W$-algebra - if the
following two conditions hold:
\medskip

\noindent
\emph{Condition 1.}
$B$ is
equipped with a complete norm
denoted by $||\cdot  ||_B$ such that 
\[
||f*g||_B\leq ||f||_B\cdot ||g||_B\quad\colon\quad f,g\in B\quad\text{and}\quad
||f||_1\leq ||f||_B
\]
\medskip

\noindent
\emph{ Condition 2.}
$\mathcal F_0^\infty$ is  a dense subalgebra of
$B$. 
\bigskip


\noindent {\bf A.3 Theorem} \emph{Let $B$ be a $\mathcal B\mathcal W$-algebra.
For each multiplicative and continuous functional $\lambda$ on $B$ 
which is not identically zero
there exists a unique $\xi\in\bf R$ such that}
\[
 \lambda(f)=\widehat f(\xi)\quad\colon\quad f\in B
\]

\medskip

\noindent 
\emph{Proof.}
First we prove uniqueness.
For
suppose  there exists some $\xi$ such that
\[
\lambda(f)=0
 \implies  \widehat f(\xi)=0\tag{i}
\]
This means that the linear
form $f\mapsto \widehat f(\xi)$
has the same kernel as $\lambda$ and hence there exists some
constant $c$ such that
\[
\lambda(f)=c\cdot \hat f(\xi)\quad\text{for all}\,\, f\in B\,.\tag{ii}
\]
Since  $\lambda$  is multiplicative it follows that
$c=c^n$ for every positive integer $n$ which gives
$c=1$.
Next, since
$B$ contains $\mathcal F_0^\infty$ and test-functions on
the $\xi$-line separate points, it is clear that
$\xi$  is uniquely determined.
There remains to prove the existence
of some $\xi$ for which (i) holds.
To prove (i) we use the
density of $\mathcal F_0^\infty$ in $B$ which by the continuity of
$\lambda$ gives
some
$g\in\mathcal F_0^\infty$ such  that $\lambda(g)\neq 0$.
Let $K$ be the compact support of
the test-function $\widehat g(\xi)$ and
suppose that  
(i)  fails for each point  $\xi\in K$.
The density of
$\mathcal F_0^\infty$ gives for each
 $\xi\in K$
some $f_\xi \in\mathcal F_0^\infty$ such that
\[ 
 \widehat f_\xi(\xi)\neq 0\,\quad \text{and}\,\, \lambda(f)=0\tag{iii}
\]

\noindent
Heine-Borel's Lemma yields
a finite set of points $\xi_1,\ldots,\xi_N$ in $K$ such
that
$\{ \widehat f_{\xi_k}\}$ have no common zero on $K$.
To simplify notations we set
$f_k=f_{\xi_k}$.
The complex conjugates 
of $\{\widehat f_k\}$ are again  test-functions. So for each $k$
we find
$h_k\in B$ such that $\widehat h_k$ is the is complex conjugate
of  $\widehat f_k$.
Set
\[ 
\phi (\xi)=
\sum_{k=1}^{k=N}\,\widehat h_k(\xi)\cdot \widehat f_k(\xi)
\]


\noindent
This test-function is $>0$ on the support of $\widehat g$ and hence there exists
the test-function
\[
Q(\xi)=\frac{\widehat g}{\phi}\tag{iv}
\]
By Condition 2, Q is  the Fourier transform of some $B$-element
$q$. Since $L^1({\bf{R}})$-functions are uniquely determined by their
Fourier transforms, it follows from (iv) that 
\[
\sum_{k=1}^{k=N}\, q*h_k*f_k=g\tag{v}
\]

\noindent
Now we get a contradiction since $\lambda(f_k)=0$ for each  $k$
while $\lambda(g)\neq 0$. 








\bigskip



\centerline {\bf  A.4 The algebra $B_a$.}
\medskip


\noindent 
Let $a>0$ be a positive real number.
Given a Beurling-Wiener algebra $ B$
we set
\[ 
J_a=\{ f\in B\quad\colon\, \widehat f(\xi)=0\,\,\text{for all}\,\,
-a\leq \xi\leq a\}
\]


\noindent
Condition 1 and the continuity of the Fourier transform on
$L^1$-functions imply
that $J_a$ is a closed ideal in $ B$. 
Hence we get the Banach algebra $\frac{B}{J_a}$ which we denote by
$B_a$. Let   $g\in \mathcal F_0^\infty$ be such that
$\widehat g(\xi)=1$ on $[-a,a]$. For every
$f\in B$ it  follows that
$g*f-f$ belongs to $J_a$ which  means that
the image of $f$ in $B_a$ is equal to the image of $g*f$. We conclude that
the $g$-image yields an identity in the algebra $B_a$ and  hence $B_a$
is a Banach algebra with a unit element.
\medskip

\noindent
{\bf A.5 Theorem.} \emph{The Gelfand space of
$B_a$ is equal to the compact interval $[-a,a]$.}
\medskip

\noindent
{\bf{A.6 Exercise.}} Prove this using Theorem A.3


\bigskip

\centerline{\bf {A.7. Examples of $\mathcal BW$-algebras}}
\medskip

\noindent
Let $B$ be the space of all continuous functions $f(x)$ 
on the real $x$-line such that the positive series:
\[
\sum_{-\infty}^{\infty}\,||f||_{[\nu,\nu+1]}<\infty \tag{*}
\]


\noindent 
where
$||f||_{[\nu,\nu+1]}$ is the maximum norm of $f$ on the closed interval 
$[\nu.\nu+1]$ and the sum extends over all integers. The norm on $B$-elements
is defined by the sum of the series above.
It is obvious that this norm dominates the $L^1$-norm.
Moreover, one easily verifies that
\[
||f*g||_B\leq ||f|||\cdot ||g||_B\tag{i}
\]
for pairs in $B$.
Hence $B$ satisfies Condition 1 from B.
\medskip

\noindent
{\bf{Exercise.}}
Show that 
the Schwartz space $\mathcal S$
of rapidly decreasing functions
on the real $x$-line
is a dense subalgebra
of $B$.

\medskip

\noindent
Next, since  $\mathcal F_0^\infty\subset \mathcal S$ we have the inclusion
\[ 
\mathcal F_0^\infty\subset B\tag{ii}
\]
There remains to see why
$\mathcal F_0^\infty$ is dense in
$B$. To prove this we construct some special functions
on the $x$-line whose Fourier transforms have compact support.
If $b>0$
we set
\[ 
f_b(x)=\frac{1}{2\pi}
\int_{-b}^b\,e^{ix\xi}\cdot (1-\frac{|\xi|}{b})\cdot d\xi
\]
By Fourier's inversion formula this means that
\[ 
\widehat f_b(\xi)=1-\frac{|\xi|}{b}\quad\,-b\leq\xi\leq b\quad
\text{and zero if}\,\,|\xi|>b
\]
A computation which is left to the reader gives
\[
f_b(x)=\frac{1}{\pi}\cdot \frac{1-\text{cos}\, bx}{bx^2}
\]
From this expression it is clear that
$f_b(x)$ belongs to $B$ and we leave it to the reader to verify that
\[ 
\lim_{b\to+\infty}\, ||f_b*g-g||_B=0
\quad\text{for all}\,\, g\in B\tag{iii}
\]
\medskip

\noindent
Next,  the functions
$\widehat f_b(\xi)$ have compact support but they are not smooth, i.e.
they do not belong to $\mathcal F_0^\infty$.
However, we can perform a smoothing of these functions as follows:
Let $\phi(\xi)$  be an even and non-negative
$C_0^\infty$-function with support in
$-1\leq\xi\leq 1$  such that the integral
\[
\int\, \phi(\xi)\cdot d\xi=1
\]


\noindent
With $\delta>0$ we set
$\phi_\delta(\xi)= \frac{1}{\delta}\cdot \phi(\xi/\delta)$ and 
for each
pair $\delta,b$ we get the test-function on the $\xi$-line
defined by
\[
\psi_{\delta,b}(\xi)=
\int_{-b}^b\, \phi_\delta(\xi-\eta)\cdot (1-\frac{|\eta|}{b})\cdot d\eta
\]
The inverse Fourier transforms
\[ 
f_{\delta,b}(x)=\frac{1}{2\pi}\int
e^{ix\xi}\cdot \psi_{\delta,b}(\xi)\cdot d\xi
\]
yield functions in $\mathcal F_0^\infty$ for all pairs $\delta,b$.
Next, if $g\in B$ then 
the Fourier transform of the $B$-element $f_{\delta,b}*g$ is equal to the
\emph{convolution} of
$\phi_\delta(\xi)$ and the Fourier transform of
$f_b*g$.
This implies that
\[ 
f_{\delta,b}* g\in \mathcal F_0^\infty\,.
\]
At this stage we leave it to the reader to verify that
\[
\lim_{(\delta,b)\to (0,0)}\, f_{\delta,b}*g=g
\]
holds for every $g\in B$. Hence the required density of
$\mathcal F_0^\infty$ is proved and $B$ is a Beurling-Winer algebra.



\centerline{\bf A.8 Adding discrete measures}
\medskip

\noindent
Let $M_d({\bf{R}})$ be the Banach algebra of discrete measures
of finite total variation, i.e. measures of the form
\[ 
\mu=\sum\, c_\nu\cdot\delta_{x_\nu}\quad\colon\,
||\mu||=\sum\,|c_\nu|<\infty
\]
\medskip

\noindent
As explained in XX the Gelfand 
space is the compact
Bohr group $\mathfrak{B}$, where the real $\xi$-line via the Fourier
transform
appears as a dense subset.
Now we  adjoin some $\mathcal{BW}$\vvv algebra
$B$ and 
obtain a Banach algebra $B\uuu d$ which 
consists of measures of the form
\[ 
f+\mu\quad\colon\quad f\in B \,\,\text{and}\,\, \mu\in
M_d({\bf{R}})
\]
where the norm of $f+\mu$ is the sum of the $B$-norm of $f$
and the total variation of  $\mu$. Since $B$ is a subspace of
$L^1$ one easuly checks that this yields a complete norm.
next, by condition (2) in A.2 it follows that if
$f\in b$ and
$\mu\in M_d({\bf{R}})$ then the convolution
$f*\mu$ belongs to $B$.
This means that
$B$ appears as a closed ideal in $B\uuu d$.
\medskip

\noindent
{\bf A.9 The Gelfand space
$\mathcal M_{B\uuu d}$}.
Let  $\lambda$ is a multiplicative functional on
$B\uuu d$ which is not identically zero on
$B$. Theorem A.3 gives
a unique
$\xi$ such that
\[
\lambda(f)= \widehat f(\xi)\quad\,\colon\quad 
f\in B\tag{i}
\]
If $a$ is a real number then $\delta_a*f$ has the
Fourier transform
becomes $e^{ia\xi}\cdot \widehat f(\xi)$. It follows that
\[
\lambda(\delta_a)\cdot \widehat f(\xi)=
\lambda(\delta_a*f)= e^{-ia\xi}\cdot \widehat f(\xi)\tag{ii}
\]


\noindent
We conclude that $\lambda(\delta_a)=e^{-ia\xi}$ and hence  the restriction of
$\lambda$ 
is the evaluation of the Fourier transform  at $\xi$ on the whole algebra $B\uuu d$.
In this way the real $\xi$-line is embedded in
$\mathcal M_B$ where a point $\lambda\in\mathcal M_B$
belongs to this subset if and only if
$\lambda(f)\neq 0$ for some
$f\in B$.
The construction of the Gelfand 
topology shows  that
this copy of the real $\xi$-line appears as an \emph{open} subset of
$\mathcal M_{B\uuu d}$  denoted by
${\bf{R}}_\xi$.
\medskip

\noindent
{\bf A.10 The set $\mathcal M_{B\uuu d}\setminus {\bf{R}}_\xi$}.
If $\lambda$ belongs to this closed subset it is identically zero on
the ideal $B$ and its restriction to 
$M_d({\bf{R}})$ 
corresponds to a point $\gamma$ 
in the Bohr group
$\mathfrak{B}$. 
Conversely, every point in  $\mathfrak{B}$
yields a $\lambda\in
\mathcal M_{B\uuu d}\setminus {\bf{R}}_\xi$ 
since the quotient algebra
\[
\frac{B\uuu d}{B}\simeq
 M_d({\bf{R}})
\]
Hence we have the set\vvv theoretic equality
\[
\mathcal M\uuu{B\uuu d}= {\bf{R}}\uuu\xi
\cup\,\mathfrak{B}\tag{*}
\]




\medskip


\noindent
{\bf A.11  Proposition.} \emph{The open subset
${\bf{R}}_\xi$ is dense in $\mathcal M_B$.}
\medskip

\noindent\emph{Proof.}
Let $\lambda$ be a point in 
$\mathcal M_{B\uuu d}\setminus {\bf{R}}_\xi$ which therefore
corresponds to a point $\gamma\in\mathfrak{B}$.
By the result in XX we know that
for every finite set $\mu_1,\ldots,\mu_N$
of discrete measures, there exists a sequence $\{\xi_\nu\}$
such that
\[
\lim_{\nu\to\infty}
\widehat \mu_i(\xi_\nu)=\gamma(\mu_i)\quad\text{and}\,\,
|\xi_\nu|\to \infty
\]

\medskip

\noindent
At the same time
the Riemann-Lebesgue Lemma entails that

\[
\lim_{\nu\to\infty}\, \widehat f(\xi_\nu)=0
\]
for every
$f\in B$. Hence
the construction of the Gelfand topology on
$\mathcal M_{B\uuu d}$ gives the requested density
in Proposition A.11



\medskip

\noindent
{\bf A.12  An inversion formula.}
Let $f\in B $  and $\mu$ is some discrete measure.
Suppose that there exists $\delta>0$ such that
the Fourier transform of $f+\mu$ has absolute value 
$\geq\delta$ for all $\xi$.
Proposition A.11  implies that its Gelfand transform has no zeros and hence
this $B\uuu d$-element is invertible, i.e. there exist
$g\in B$ and a discrete measure $\gamma$ such that
\[
\delta_0=(f+\mu)*(g+\gamma)\tag{i}
\]
Notice  that the right hand side becomes
\[
f*g+ f*\gamma+g*\mu+\mu*\gamma
\]
Here $f*g+ f*\gamma+g*\mu$ belongs to $B$
while
$\mu*\gamma$ is a discrete measure. So (i) implies that
$\gamma$ must be the inverse of $\mu$ in
$M_d({\bf{R}})$
and hence (i) also gives the equality:
\[
f*g+f*\mu^{-1}+g*\mu=0\tag{ii}
\]
\bigskip














\noindent
\centerline {\bf B.  A Tauberian Theorem.}
\medskip

\noindent
Consider the Banach algebra $B$ in (A.7).
The dual space $B^*$ consists of  Riesz measures
$\mu$ on the real line for which there exists a constant $A$ such that
\[ 
\int_\nu^{\nu+1}\, |d\mu(x)|\leq A\quad\text{for all integers}\,\,\nu\,.
\] 

\noindent
The smallest $A$ above is  the norm of $\mu$ in $B^*$ and 
duality is expressed by:
\[ 
\mu(f)=\int\, f(x)\cdot d\mu(x)\,\quad\colon\quad f\in B\,\,\text{and}\,\, \mu\in B^*
\]
\noindent 
Let $f\in B$ be such that  $\widehat f(\xi)\neq 0$ for all
$\xi$. For each $a>0$ it follows from
Theorem A.5 that the $f$-image in $B_a$ generates the whole algebra.
Since this hold for every $a>0$
it follows that each
$\phi\in\mathcal F_0^\infty$
belongs to the principal ideal generated by $f$ in $B$, i.e. there exists some
$g\in B$ such that
\[
 \phi=g*f\tag{*}
\]
Since $\mathcal F_0^\infty$ is dense in $B$ we conclude that
$B\cdot f$ is dense in $B$.
Using this density we have:


\bigskip

\noindent 
{\bf B.1  Theorem} \emph{Let 
$\mu\in B^*$ be such that}
\[
\lim_{y\to+\infty}\, \int\, f(y-x)\cdot d\mu(x)=A\,\,\, \text{exists}.
\]
\emph{Then, for each $g\in B$ it follows that}
\[
\lim_{y\to+\infty}\, \int\, g(y-x)\cdot d\mu(x)=B
\quad\text{where}\quad B=A\cdot \frac{ \hat g(0)}{\hat f(0)}
\]

\medskip

\noindent \emph{Proof.} 
Let $g\in B$. If $\epsilon>0$ we find
$h_\epsilon\in B$ such that 
$||g-f*h_\epsilon||_B<\epsilon$. When  $y>0$ we get:
\[
\int\, (f*h_\epsilon)(y-x)\cdot d\mu(x)=\tag{i}
\]
\[
\int\, \bigl[f(y-s-x)h_\epsilon(s)\cdot ds\,\bigr] \cdot  d\mu(x)=
\int\, h_\epsilon(s)\cdot\bigl[\int \,f(y-s-x)\mu(x)\,\bigr]\cdot ds
\]
By the hypothesis the inner integral converges to $A$ when
$y\to+\infty$
every fixed $s$. Since
$h$ belongs to $B$ it follows easily that
the limit of (i) when $y\to+\infty$ is equal to
\[ 
A\cdot \int\, h_\epsilon(s)\cdot ds=A\cdot \widehat h_\epsilon(0)\tag{ii}
\]


\noindent
Next, since the $B$-norm is stronger than the $L^1$-norm it follows that
\[ 
|\widehat g(0)-\hat h_\epsilon(0)\cdot \widehat f(0)|<\epsilon\tag{iii}
\]
Moreover, since the $B$-norm is invariant under translations
we have
\[
\bigr |
 \int\, g(y-x)d\mu(x)-\int\, (f*h_\epsilon)(y-x)\cdot d\mu(x)\bigl|\leq
 \epsilon\cdot ||\mu||\quad\text{for all}\,\,y\tag{iv}
\]
where $||\mu||$ is the norm of $\mu$ in the dual space $B^*$.
Notice also that   (iii) gives:

\[
\lim_{\epsilon\to }\, \hat h_\epsilon(0)=\frac{\hat g(0)}{\hat f(0)}
\]
Finally, since $\epsilon>0$ is arbitrary we see that the limit formula for (i) when
$y\to+\infty$ expressed by
(ii)  and (iv) above together imply that


\[
\lim_{y\to+\infty}\, 
\int\, g(y-x)d\mu(x)=A\cdot \frac{\hat g(0)}{\hat f(0)}
\]
This finishes the proof of 
Theorem A.9

\bigskip




\centerline
{\bf B.2  The multiplicative version}
\medskip



\noindent 
Let ${\bf{ R}}^+$ be the multiplicative group of positive real numbers.
To each function $f(t)$ on ${\bf{R}}^+$
we get the function $E_f(x)= f(e^x)$ on the real $x$-line.
Since $dt=e^xdx$ under the exponential map we have
\[
\int_0^\infty\, f(t)\frac{dt}{t}=
\int_{-\infty}^\infty\, E_f(x)dx
\]
provided that $f$ is integrable.
On $\bf R^+$ we get the convolution algebra $L^1(\bf R^+)$ where
\[ 
f*g(t)=\int_0^\infty\, f(\frac{t}{s})\cdot g(s)\cdot \frac{ds}{s}
\]
This convolution commutes with the $E$ map from
$L^1({\bf {R}}^+$ into $L^1({\bf {R}}^1)$, i.e. 
\[
E_{f*g}= E_f*E_g
\]
Next, recall that the Fourier transform on $L^1({\bf{ R}}^+)$
is defined by
\[ 
\widehat f(\xi)=\int_0^\infty\,t^{-i\xi} \cdot f(t)\cdot \frac{dt}{t}
\]
\medskip









\noindent
{\bf B.3  The Banach algebra $B_m$.} The companion to $B$ on
${\bf {R}}^+$ consists of continuous functions $f(t)$ for which
\[ 
\sum\, ||f||_{[2^\nu,2^{\nu+1}]}<\infty
\]
where the is taken over all integers. Notice  that
with $\nu<0$ one takes small intervals approaching $t=0$.
Just as in Theorem A.9  we obtain a Tauberian Theorem for functions
$f\in B_m$ whose Fourier transform is everywhere $\neq 0$.
Here we  the dual space $B\uuu m^*$
consists of Riesz measures $\mu$ on ${\bf{R}}^+$
for which there exists a constant $C$ such that

\[
\int\uuu{2^m}^{2^{m+1}}\, |d\mu(t)|\leq C
\] 
for all integers $m$.



\bigskip



\bigskip


\centerline{\bf C. Ikehara's theorem.}
\bigskip


\noindent
Let
$\nu$ be a non-negative Riesz measure supported on
$[1,+\infty)$ which satisfies
\[
\int_1^\infty x^{-1-\delta}\cdot d\nu(x)<\infty\quad
\text{for all}\,\, \delta>0
\]
This gives
an analytic function
$f(s)$ defined in
the  half plane
$\mathfrak{Re}(s)>1$ by
\[ 
f(s)=\int_1^\infty x^{-s}\cdot d\nu(x)
\]


\noindent
{\bf D.1 Theorem.}
\emph{Assume that there exists a constant
$A$ and a continuous function
$G(u)$ defined on the real $u$-line such that}
\[
\lim_{\epsilon\to 0}\, \bigl[f(1+\epsilon+iu)-\frac{A}{1+\epsilon+iu}\,\bigr]=G(u)\tag{*}
\]
\emph{where the limit holds uniformly   on  every
bounded interval $-b\leq u\leq b$.
Then}
\[ 
\lim_{x\to+\infty}\,\frac{1}{x}\int_1^x\,d\nu(t)=A\tag{**}
\]
\medskip

\noindent
We shall prove a sharper version 
of
Ikehara's result 
where
the assumption on $G(u)$ is relaxed.
Namely, replace  (*)
by the weaker assumption that there
exists a locally integrable function $G(u)$ such that
\[
\lim_{\epsilon\to 0}\, \int_{-b}^b\, \bigl|
f(1+\epsilon+iu)-\frac{A}{1+\epsilon+iu}-G(u)\bigr|\cdot du=0\quad
\text{holds for each}\,\, b>0\tag{***}
\]
\medskip



\noindent
{\emph{Proof that (***) gives (**)}}.
The variable substitution  $x\mapsto e^\xi$ gives
\[ 
f(s)=\int_0^\infty\, e^{-\xi s}\cdot d\nu(e^\xi)
\]



\noindent
Define the  measure $\mu$ on the non-negative real $\xi$-line by
\[
d\mu(\xi)= e^{-\xi}\cdot d\nu(e^\xi)-A\cdot d\xi\,\quad\colon\,\,\xi\geq 0\tag{1}
\]
Then we see that
\[ 
f(s)-\frac{A}{s-1}=\int_0^\infty e^{(1-s)\xi}d\mu(\xi)\tag{2}
\]
It is clear that  (**) holds in Theorem D.1 if and only if
\[
 \lim_{\eta\to\infty}\int_0^\eta\, e^{-\eta+\xi}\cdot d\mu(\xi)=0\tag{3}
\]


\noindent
\emph{A reformulation of Ikehara's theorem.}
From the equations  above we
can restate the sharp version of Ikehara's theorem as follows.
Let
$\nu^*$ be a non-negative measure on $0\leq\xi<+\infty$
such that 
\[ \int_0^\infty\, e^{-\delta\cdot \xi}\cdot d\nu^*(\xi)<\infty
\quad\text{for all}\,\,\delta>0\tag{4}
\]
Next, let $A>0$ be some positive constant
and put $d\mu(\xi)=d\nu^*(\xi)-A\cdot d\xi$.
Then (1) gives
the analytic function
$g(s)$ defined in $\mathfrak{Re}(s)>0$ by
\[
g(s)=\int_0^\infty\, e^{-s\cdot\xi}\cdot d\mu(\xi)\tag{5}
\]
\medskip

\noindent
{\bf D.2. Definition.}
\emph{We say that the  measure $\mu$ is of the
Ikehara type if there exists a locally integrable function
$G(u)$ defined on the real $u$-line such that}
\[
\lim_{\epsilon\to 0}\, \int_{-b}^b\, \bigl|
g(\epsilon+iu)-G(u)\bigr|\cdot du=0\,\quad
\text{holds for each}\,\, b>0
\]
\medskip

\noindent
{\bf D.3. The space $\mathcal W$.}
Let $\mathcal W$ be the space of continuous functions
$\rho(\xi)$ defined on $\xi\geq 0$ which satisfy:
\[
\sum_{n\geq 0}\,||\rho||_n<\infty\,
\quad\text{where}\,\,||\rho||_n=\max_{n\leq u\leq n+1}\, |\rho(u)|
\]
The dual space
$\mathcal W^*$ consists of Riesz measures
$\gamma$ on $[0,+\infty)$ such that
\[ 
\max_{n\geq 0}\,\int_n^{n+1}\, |d\gamma(\xi)|<\infty
\]
With these notations we have
\bigskip

\noindent
{\bf D.4. Theorem.}
\emph{Let $\nu^*$ be a non-negative meausure
on $[0,+\infty)$ and $A\geq 0$ some constant
such that the measure $\mu=\nu^*-A\cdot d\xi$
is of Ikehara type.
Then $\mu\in \mathcal W^*$
and for every
function $\rho\in\mathcal W$ one has}
\[
\lim_{\eta\to+\infty}\, \int_0^\eta
\rho(\eta-\xi)\cdot d\mu(\xi)=0
\]
\medskip

\noindent
{\bf {Exercise.}} 
Use the previous observations  to show that
Theorem D. 4 gives  the sharp
version of Ikehara's theorem.
The  hint is to apply Theorem D.4 to the
$\mathcal W$-function
$\rho(s)=e^{-s}$ 

\bigskip

\centerline {\emph{Proof of Theorem D.4.}}
\bigskip

\noindent
Let $b>0$ and define the function $\omega(u)$ by
\[
\omega(u)= 1-\frac{|u|}{b}\,,\quad
-b\leq u\leq b\,\,\quad\text{and}\,\,
\omega(u)=0\,\,\text{outside this interval}\tag{i}
\]


\noindent
Set
\[ J_b(\epsilon,\eta)=
\int_{-b}^b\, e^{i\eta u}\cdot g(\epsilon+iu)\cdot \omega(u)\cdot du\tag{ii}
\]
From Definition D.2 we have the $L^1_{\text{loc}}$-function $G(u)$
and since $\omega(u)$ is a continuous function on the compact
interval $[-b,b]$
it follows that 
\[ 
\lim_{\epsilon\to 0}\, J_b(\epsilon,\eta)=J_b(0,\eta)=
\int_{-b}^b\, e^{i\eta u}\cdot G(u)\cdot \omega(u)\cdot du\tag{iii}
\]
With $b$ kept fixed  the right
hand side
is a Fourier transform of an
$L^1$-function and the Riemann-Lebesgue theorem gives:
\[
\lim_{\eta\to+\infty}\, J_b(0,\eta)=0\tag{iv}
\]
Moreover, the triangle inequality gives the inequality:
\[
|J_b(0,\eta)|\leq 
\int_{-b}^b\,\bigl| G(u)\bigr|\cdot du\tag{v}
\]
\medskip


\noindent{\bf Some integral formulas.}
From the above
it  is clear that
\[ J_b(\epsilon,\eta)=
\int_0^\infty\,
\bigl[\int_{-b}^b\, e^{i\eta u-i\xi u}\cdot \omega(u)\cdot du\bigr]
\cdot e^{-\epsilon\cdot\xi}\cdot d\mu(\xi)\tag{1}
\]


\noindent
Next, notice that
\[
\int_{-b}^b\, e^{i\eta u-i\xi u}\cdot \omega(u)\cdot du=
2\cdot\frac{1-\text{cos}\,b(\eta-\xi)}{b(\eta-\xi)^2}\tag{2}
\]
Hence we obtain
\[ J_b(\epsilon,\eta)=
2\cdot\int_0^\infty\, 
\frac{1-\text{cos}\,b(\eta-\xi)}{b(\eta-\xi)^2}\cdot e^{-\epsilon\xi}
\cdot d\mu(\xi)\tag{3}
\]

\noindent
From (iii) above it follows that  (3)
has a limit as $\epsilon\to 0$ which is equal to 
the integral in the right hand side in (iii) which is
denoted by $J_b(0,\eta)$. Next, it is 
easily seen that there exists the limit

\[
\lim_{\epsilon\to 0}\, 
2\cdot\int_0^\infty\, 
\frac{1-\text{cos}\,b(\eta-\xi)}{b(\eta-\xi)^2}\cdot e^{-\epsilon\xi}
\cdot Ad\xi=2\pi\cdot A\tag{4}
\]
\medskip

\noindent
Hence (3-4) imply that there exists the limit
\[
\lim_{\epsilon\to 0}\, 
2\cdot\int_0^\infty\, 
\frac{1-\text{cos}\,b(\eta-\xi)}{b(\eta-\xi)^2}\cdot e^{-\epsilon\xi}
\cdot d\nu^*(\xi)=J_b(0,\eta)+2\pi\cdot A\tag{5}
\]
\medskip

\noindent
Next, the measure  $\nu^*\geq 0$ and the function
$\frac{1-\text{cos}\,b(\eta-\xi)}{b(\eta-\xi)^2}\geq 0$
for all $\xi$. So the existence of a finite limit in (5) entails that there exists
the convergent integral 
\[
\int_0^\infty\, 
\frac{1-\text{cos}\,b(\eta-\xi)}{b(\eta-\xi)^2}
\cdot d\nu^*(\xi)=J_b(0,\eta)+2\pi\cdot A\tag{6}
\]



\medskip


\noindent
{\bf Proof that
$\mu\in\mathcal W^*$.}
Let $\mathcal W^*$ be the dual of the Banach space
$\mathcal W$ from D.3.
Since $A\cdot d\xi$ obviously belongs to
$\mathcal W^*$ it suffices to show that
$\nu^*\in\mathcal W^*$.
To prove this we consider some integer $n\geq 0$ and with $b=1$
it is clear that
(6) gives
\[
\bigl|\int_n^{n+1}\, 
\frac{1-\text{cos}\,(\eta-\xi)}{(\eta-\xi)^2}
\cdot d\nu^*(\xi)\bigr|\leq |J_1(0,\eta)|+2\pi=
\int_{-1}^1\, |G(u)|\cdot du+2\pi\cdot A
\]
Apply this with
$\eta=n+1+\pi/2$ and notice that

\[
\frac{1-\text{cos}\,(n+1+\pi/2-\xi)}{(n+1+\pi/2-\xi)^2}
\geq a\quad\,\text{for all}\,\, n\leq\xi\leq n+1
\]
This gives a constant $K$ such that
\[
\int_n^{n+1}\, d\nu^*(\xi)\leq K\quad\, n=0,1,\ldots
\]
\medskip

\noindent
{\emph {Final part of the proof.}}
We have proved that
$\mu\in \mathcal W^*$. Moreover, 
(iv) and the integral formula (6) give
\[
\lim_{\eta\to+\infty}\, \int_0^\infty
\frac{1-\text{cos}\,b(\eta-\xi)}{b(\eta-\xi)^2}\cdot d\mu(\xi)=0
\quad\,\text{for all}\,\, b>0\tag{*}
\]
Next, for each fixed 
$b>0$ we notice that the function
\[
\rho_b(\xi)=2\cdot \frac{1-\text{cos}\,(b\xi)}{b\cdot \xi^2}
\]
belongs to $\mathcal W$ and its
Fourier is  $\omega_b(u)$.
Here $\omega_b(u)\neq 0$ when
$-b<u<b$.
So the family of these $\omega$-functions have no common
zero on the real $u$-line. By the Remark in XX this entails  that
the linear subspace of
$\mathcal W$ generated by
the translates of all $\rho_b$ -functions with
arbitrary large
$b$ is dense in $\mathcal W$. 
Hence (*) above implies
that
we get a zero limit as $\eta\to+\infty$ for every function
$\rho\in\mathcal W$. But this is precisely the
assertion in
Theorem D.4.


\bigskip


\centerline{\bf E. The algebra $L^1({\bf{R}}^+)$}

\bigskip

\noindent
Consider the  family
of $L^1$-functions on the real $x$-line 
supported by the half-line $x\geq 0$.
This yields a closed subalgebra of $L^1({\bf{R}})$
denoted by
$L^1({\bf{R}}^+)$. 
Adding the unit point mass $\delta_0$ we obtain the commutative
Banach algebra
\[ 
B={\bf{C}}\cdot \delta_0+L^1({\bf{R}}^+)
\]


\noindent
{\bf E. 1. The Gelfand space
$\mathfrak{M}_B$}.
For each
$f(x)\in L^1({\bf{R}}^+)$
we set:
\[
\widehat f(\zeta)=\int_0^\infty\, e^{i\zeta x}\cdot f(x)\cdot dx,\quad\text{where}
\quad \mathfrak{Im}(\zeta)\geq 0
\]
With $\zeta=\xi+i\eta$ we get
\[
|\widehat f(\xi+i\eta)|\leq 
\int_0^\infty\, |e^{i\xi x-\eta x} |\cdot|f(x)|\cdot dx=
\int_0^\infty\, |e^{-\eta x}\cdot |f(x)|\cdot dx\leq ||f||_1
\]
We conclude that
for every point $\zeta=\xi+i\eta$ in the closed upper half-plane 
corresponds to a point
in $\zeta^*\in \mathfrak{M}_B$
defined by
\[ 
\zeta^*(f)=
\widehat f(\zeta)\,\quad\text{and}\quad \,\zeta^*(\delta_0)=1
\]
In addition to this 
 $L^1({\bf{R}}^+)$ is a maximal ideal in
 $B$ whioch gives a   point
 $\zeta^\infty\in \mathfrak{M}_B$ such that
 \[ 
 \zeta^\infty (f)=0\quad\text{for all}\,\, f\in
L^1({\bf{R}}^+ )
\]
\medskip

\noindent
{\bf E.2. Theorem.} \emph{The Gelfand space
$\mathfrak{M}_B$ can be identified with
the union  of $\zeta^\infty $ and the closed upper half-plane.}
\medskip

\noindent
{\bf Remark.}
The theorem asserts that every multiplicative
functional on $B$ is either
$\zeta^\infty $ 
or determined by a point
$\zeta=\xi+i\eta$ where
$\eta\geq 0$.
Concerning the topological identification
$\zeta^\infty $ corresponds to the 
one point compactification of the closed
upper half-plane. Thus, whenever
$\{\zeta_\nu\}$ is a sequence in
$\mathfrak{Im}(\zeta)\geq 0$ such that
$|\zeta_\nu|\to\infty$ then $\{\zeta_\nu^*\}$
converges to $\zeta^*$ in
$\mathfrak{M}_B$.
In fact, this follows via the Riemann-Lebegue Lemma which gives
\[ 
\lim_{|\zeta|\to\infty}\, \widehat f(\zeta)=0
\quad\text{for all}\,\, f\in L^1({\bf{R}}^+)
\]
\medskip

\noindent
The general result in XX gives 
Theorem 2   if we have
proved if   the following:

\medskip

\noindent
{\bf E.3. Proposition.}
\emph{Let $\{g_\nu=\alpha_\nu\cdot\delta_0+f_\nu\}_1^k$
be a finite family in $B$ such that
the $k$-tuple $\{\hat g_\nu\}$
has no common zero in
$\bar U_+\cup\{\infty\}$.
Then the ideal in $B$ generated by this $k$-tuple is equal to
$B$.}

\medskip

\noindent
The proof requires some preliminary constructions.
We  use the conformal map from
the upper half-plane onto the unit disc defined by

\[
w=\frac{\zeta-i}{\zeta+i}
\]
So here $w$ is the complex coordinate in $D$.
Next, consider the disc algebra $A(D)$.
Via  the conformal map
each transform $\widehat f(\zeta)$ of a
function $f\in L^1(\bf{R}^+)$
yields an element of $A(D)$ defined by:

\[ 
F(w)=\widehat f(\frac{i+iw}{1-w})
\]
It is clear that
$F(w)\in A(D)$. Moreover, we notice that
\[
w\to 1\implies\, 
|\frac{i+iw)}{1-w}|\to\infty
\]
It follows that the $A(D)$-function $F(w)$ is zero at
$w=1$ and we can conlcude:
\medskip

\noindent
{\bf E.4. Lemma.} \emph{By 
$f\mapsto F$ we have an algebra homomorphism
from $L^1({\bf{R}}^+)$ to functions in
$A(D)$ which are
zero at $w=1$.}
\medskip

\noindent
Next, let  $\mathcal H$ denote the algebra homomorphism in Lemma 4
and 
consider the function $1-w$ in $A(D)$.
We claim this it belongs to the image under $\mathcal H$.
To see this we consider the function
\[
f(x)= e^{-x}\quad\,x\geq 0\,\quad\text{and}\,\, f(x)=0
\quad\text{when}\,\, x<0
\]
Then we see that
\[
\hat f(\zeta)=\int_0^\infty \, e^{i\zeta x}\cdot e^{-x}\cdot dx=
\frac{1}{1-i\zeta}
\]
It follows that
\[ 
F(w)=\frac{1}{1-i(\frac{iw+i}{1-w})}=\frac{1-w}{1-w+w+1}=
\frac{1-w}{2}
\]
Using $2f$ we conclude that
$1-w$ belongs to the $\mathcal H$-image.
Next, the identity element $\delta_0$ is mapped to the constant function
on $D$. So via $\mathcal H$ we have an algebra homomorphism
from $B$ into a subalgebra of $A(D)$ which contains
$1-w$ and the identity function and hence all $w$-polynomials.
Returning to the special $B$-element $f$ we notice that the convolution

\[ 
f*f(x)= x\cdot e^{-x}
\]
We can continue and conclude that the subalgebra of $B$ 
generated by $f$ and $\delta_0$ contains 
$L^1$-functions of the form $p(x)\cdot e^{-x}$ where $p(x)$ are polynomials.
\medskip


\noindent
{\bf{E.5. Exercise.}}
Prove that the linear space ${\bf{C}}[x]\cdot e^{-x}$
is a dense subspace of $L^1({\bf{R}}^+)$.
\medskip

\noindent
From the result in  the exercise it follows that
the polynomial algebra ${\bf{C}}[w]$ appears as a dense subalgebra
of $\mathcal H(B)$ when it is equipped with the $B$-norm.
At this stage we are prepared to give:

\bigskip

\noindent
{\bf{Proof of Proposition E.3.}}
In $A(D)$ we have the functions $\{G_\nu=\mathcal H(g_\nu)\}$.
By assumption $\{G_\nu\}$ have no common zero in the closed disc $D$.
Since $D$ is the maximal ideal space of the disc algebra and
${\bf{C}}[w]$  a dense subalgebra, it follows that
for every $\epsilon>0$ there exist
polynomials $\{p_\nu(w)\}$ such that
the maximum norm
\[
|p_1\cdot G_1+\ldots+p_k\cdot G_k-1|_D<\epsilon|\tag{1}
\]
where 1 is the identity function.
Now $p_\nu=\mathcal H(\phi_\nu)$ for $B$-elements $\{\phi_\nu\}$.
So in $B$ we get the element
\[
\psi=\phi_1g_1+\ldots+\phi_k\cdot g_k\tag{2}
\] 
Moreover we have $|\mathcal H(\psi)-1|_D<\epsilon$ and here we can choose
$\epsilon<1/4$ and by the previous identifications it follows that
\[ 
|\widehat \psi(\xi)|\geq 1/4\quad\text{for all}\quad -\infty<\xi<\infty\tag{3}
\]
The proof of Proposition E.3 is finished if we can show that (3) entails that
the $B$-element $\psi$ is invertible.
Multiplying $\psi$ with a non-zero scalar we may assume that
\[ 
\psi=\delta_0-g\quad\colon\quad g\in L^1({\bf{R}}^+)
\]
and  the Fourier transform $\widehat\psi(\xi)$
satisfies
\[
|\widehat\psi(\xi)-1|\leq 1/2
\]
for all $\xi$.
It means that $|\widehat g(\xi)|\leq 1/2$.
The spectral radius formula applied to $L^1$-functions shows that if
$N$ is a sufficiently large integer then
\[
||g^{(N)}||_1\leq (3/4)^N\tag{4}
\]
where $g^{(N)}$ is the $N$-fold convolution of $g$.
Now we have
\[
(1+g+\ldots+g^{N_1})\cdot \psi= 1-g^{(N)}\tag{5}
\]
By (4)  the norm of the $B$-element $g^{(N)}$ is strictly less than one
and hence the right hand side is invertible where the inverse is given
by a Neumann series, i.e. with $g_*=g^{(N)}$  the inverse is

\[ 
\delta_0+\sum_{\nu=1}^\infty\, g_*^\nu
\]
Since convolutions of $L^1({\bf{R}}^+)$-functions still are supported by
$x\geq 0$, it follows from the above that $\psi$ is invertible in $B$ and
Proposition E.3 is proved.

\newpage






\centerline{\bf{0.2 Results about a Schršdinger equation.}}

\bigskip

\noindent
Carleman's
most valuable work
is the monograph
 \emph{Sur les Žquations singulires
ˆ noyaux rŽel et
symmetrique} [Uppsala University 1923].
Here  the main results give conditions in order that densely defined
symmetric operators on Hilbert spaces
have self-adjoint extensions, together 
with the construction
of 
spectral resolutions for unbounded
and self-adjoint
operators. 
A basic equation which emerges from quantum mechanics is
to find solutions $u(p,t)$ defined in
${\bf{R}}^3\times {\bf{R}}^+$
where $t$ 
is a time variable and $p=(x,y,z)$
which satisfies the PDE-equation
\[ 
i\cdot\frac{\partial u}{\partial t}=\Delta(u)(p,t)- c(p)\cdot u(p,t)= 0 \quad t>0
\]
and the initial condition
\[ 
u(p,0)= f(p)
\]
Here $f(p)$ belongs to $L^2({\bf{R}}^3)$
and $c(p)$  is a real-valued and locally square integrable function.
Carleman proved that the symmetric and densely defined operator
$\Delta+c$ has a self-adjoint extension in $L^2({\bf{R}}^3)$ if
\[
\limsup_{p\to \infty}\, c(p)\leq M\tag{*}
\]
holds for some constant $M$
As far as I know the sufficiency condition (*) for the existence of a self-adjoint
extension
remains as the "best possible result".
Returning to Schršdinger's equation
we assume (*) and that
the spectrum of the densely defined sefl-adjoint 
operator $\Delta-c$ on
the Hilbert space
$L^2({\bf{R}}^3)$ is confined to an interval 
$[\lambda_1,+\infty)$ on the positive real line, i.e. 
$\lambda_1>0$.
When this holds,   the solution $u$ is given
by an equation
\[ 
u(p,t)=\int_{{\bf{R}}^3}\, [
\int_{\lambda_1}^\infty\, 
e^{i\lambda t}\cdot d\theta(p,q,\lambda)\,\bigr]\cdot f(q)\, dq
\]
where
$\lambda\mapsto  \theta(p,q,\lambda)$ is a non-decreasing function on
$[\lambda_1,+\infty)$ for each fixed pair $p.q$.
Moreover, Carleman found
an  asymptotic expansion which recaptures
the $\theta$-function.
For details we refer to the article [Carleman XX].
\medskip



\centerline {\bf{0.3 A wave equation.}}
\medskip

\noindent
Let $\Omega$ be a bounded cdomain in
${\bf{R}}^3$ with a $C^1$-boundary $\partial\Omega$.
We seek functions $u(x,t)$
where
$x=(x_1,y_2,x_3)$ defined in
${\bf{R}}^3\setminus \Omega\times \{t\geq 0\}$
where $t$ is a time variable
satisfying the wave equation
\[
\frac{\partial^2u}{\partial t^2}=  \Delta(u)
\]
when $t>0$ and
$x\in{\bf{R}}^3\setminus \overline{\Omega}$.
The initial conditions when
$t=0$ is that
\[
u(x,0)=f_1(x)\quad\colon \frac{\partial u}{\partial t}(x,0)=f_2(x)\tag{i}
\]
where $f_1,f_2$ are $C^2$-functions in
${\bf{R}}^3\setminus \Omega$
and  $\Delta(f_1)$ and $\Delta(f_2)$
are square integrable, i.e.
\[ 
\iiint_{{\bf{R}}^3\setminus \Omega}\,
|\Delta(f_\nu|^2\, dx<\infty
\]
Finally the normal derivatives along
$\partial\Omega$ satisfy
\[
\frac{\partial f_\nu}{\partial n}=0\quad\colon\nu=1,2
\]
Given such a pair $f_1,f_2$ there exists
a unique solution $u(x,t)$ which satisfies the wave equation above
and the two initial conditions (i) together with the boundary value equation
\[
\frac{\partial u}{\partial n}(x,t)=0
\] 
for
every $x\in\partial\Omega$ and each $t\geq 0$.
Carleman's cited monograph gives an expression of the solution by 
an integral formula using the
spectral measure 
of a certain from a densely defined and self-adjoint operator on
the Hilbert space
$L^2({\bf{R}}^3\setminus \Omega)$.
This is used to
prove that
\[
\lim_{x\to \infty}\, \nabla(u)(x)=0
\]
In other words, the first order derivatives
of $u$ tend to zero as
$x\to \infty$.
Let us remark
that
similar spectral functions were  employed by 
Friedrich's in an article from 1944
which
proved the existence and uniqueness for solutions to symmetric hyperbolic systems,
where Maxwell's equations for electro-magnetic fields
is an example.






\newpage



\centerline {\bf{0.4 Fredholm's resolvent.}}
\medskip


\noindent
In the   article \emph{Sur le genre
du denominateur $D(\lambda)$
de Fredholm} [Arkiv fšr matematik 1917], Carleman considered
a continuous function
$K(x,y)$ defined on the square
$\{0\leq x,y\leq 1\}$ which yields the
integral operator
\[
f\mapsto \mathcal K_f(x)= \int_0^1\, K(x,y)f(y)\, dy
\]
There  exists the discrete 
sequence of spectral values  $\{\lambda_\nu\}$ 
for which $E-\lambda_\nu \cdot \mathcal K_f$
are not invertible where
$E$ is the identity operator on the Hilbert space
$L^2[0,1]$.
Here $\{0< |\lambda_1|\leq |\lambda_2|\leq\ldots  \}$
are arranged with non-decreasing absolute values and
eventual
eigenspaces of dimension $e\geq 1$ means that the corresponding
$\lambda$-value is repated $e$ times in the sequence.
Carleman proved that the infinte product
\[ 
\mathcal D(\lambda)=
e^{a\lambda}\cdot \prod_{\nu=1}^\infty\, 
\bigl(1-\frac{\lambda}{\lambda_\nu}\bigr)\tag{*}
\]
yields an entire of  function of exponential type.
Here $\mathcal D(\lambda)$ is the Fredholm resolvent defined for
each complex $\lambda$ by
the series
\[
1+\sum_{n=1}^\infty\, \frac{(-1)^n}{n\, !}\cdot
\int_{[0,1]^n}\,
\text{det}(K_n(s_1,\dots,s_n))\, ds_1\cdots  ds_n
\]
where $K_n(s_1,\dots,s_n)$ is the $n\times n$-matrix with
elements
$\{K(s_i,s_k)\,\colon 1\leq i,k\leq n\}$.
Notice that one does not assume that
the kernel  function $K(x,y)$ is    symmetric,
Carleman's  proof is presented
in ¤ xx and
offers 
an excellent lesson about spectral properties of linear
operators. Let us remark that
the main  ingredients in the proof rely upon
analytic function theory
where 
a result  due to Arne Wiman plays a crucial role.
Recall that Wiman also was
professor at Uppsala during this time.
So Carleman's career started at Uppsala University
in an "optimal enviroment"
guided by Holmgren and Wiman.
Let us also remark  that
in a later work Carleman extended 
the result above to kernels $K(x,y)$ of the Hibert-Schmidt type, i.e.
here 
\[
 \iint_0^1\, |K(x,y)|^2\, dxdy<\infty
 \]

\bigskip


\noindent
{\bf{ Carleman's inequality.}}
The cited article above also contains
an  inequaliy for norms
of
resolvents to matrices which goes as follows:
Recall first that
the Hilbert-Schmidt norm of 
an  
$n\times n$-matrix $A=\{a_{ik}\}$  is defined by:
\[
||A||= \sqrt{ \sum\sum\, |a_{ik}|^2}
\]


\noindent
where the double sum extends over all pairs
$1\leq i,k\leq n$.
Next, 
for a linear operator $S$
on ${\bf{C}}^n$
its \emph{operator norm} is defined by
\[
||S||=
\max_x\, ||S(x)||\quad\text{with the maximum taken over unit vectors.}
\] 

\noindent
{\bf{Theorem.}}
\emph{Let $\lambda_1,\ldots,\lambda_n$ be the roots of 
$P_A(\lambda)$ and  $\lambda\neq 0$ is outside $\sigma(A)$. Then
one has the inequality:}
\[ 
\bigl|\prod_{i=1}^{i=n}\, 
\bigl[1-\frac{\lambda_i}{\lambda}\bigr ]
e^{\lambda_i/\lambda}\bigr|\cdot 
||(\lambda\cdot E_n-A)^{-1}||
\leq |\lambda|\cdot \text{exp}
\bigl(\frac{1}{2}+ \frac{||A||^2}{2\cdot |\lambda|^2}\bigr)
\]
\medskip


\noindent
Te proof is given in chapoter 1 from my notes on analytic function theory.
It gives
an instructive lesson for the calculus with
matrices and we remark
that the inequality in the theorem above
can be applied to
Hilbert-Schmidt operators in the infinite dimensional case and
therefore plays a crucial role 
for expansions via eigen-functions of
such operators.



















\end{document}







