


\documentclass{amsart}
\usepackage[applemac]{inputenc}


\addtolength{\hoffset}{-12mm}
\addtolength{\textwidth}{22mm}
\addtolength{\voffset}{-10mm}
\addtolength{\textheight}{20mm}

\def\uuu{_}


\def\vvv{-}

\begin{document}





\centerline{\bf{¤ 1 The construction of fundamental solutions.}}
\bigskip

\noindent
In
${\bf{R}}^3$ with coordinates $x=(x_1,x_2,x_3)$ we consider 
 a second order PDE-operator
\[
L=
\sum_{p=1}^{p=3}\sum_{q=1}^{q=3}\, a_{pq}(x)\cdot \frac{\partial ^2}{\partial x_p\partial x_q}+
\sum_{p=1}^{p=3}\, a_p(x)
\frac{\partial }{\partial x_p}+a_0(x)
\]
where 
$a$-functions are real-valued and
one has the symmetry $a_{pq}=a_{qp}$.
In addition th doubly indexed $a$-functions are of class $C^2$ while $\{a_\nu\}$
are of class $C^1$.
To ensure existence of a globally defined fundamental solutions we
also suppose that the following limit formulas hold
as $(x,y,z)\to \infty$:
\[
\lim a_\nu(x,y,z)=0 \colon 0\leq p\leq 3\quad\&\,
\lim a_{pq}(x,y,z)= \text{Kronecker's delta function}
\]
Thus, $L$ approaches the Laplace operator as $(x,y,z)$ tends to
infinity. Moreover we assume that 
$L$ is elliptic. It means that
the eigenvalues of the symmetric
matrix with elements $\{a_{pq}(x)\}$
are positive for every $x$.
The adjoint
operator is defined by:
\[ 
L^*(x,\partial _x)=P-2\cdot \bigl(
\sum_{p=1}^{p=3}\, \bigl(\sum_{q=1}^{q=3}\, 
\frac{\partial a_{pq}}{\partial x_q}\bigr)\cdot \frac{\partial}{\partial x\uuu p}
-\sum_{p=1}^{p=3}\, \frac{\partial a_p}{\partial x_p}
+2\cdot \sum\sum\, \frac{\partial^2 a_{pq}}{\partial x_p\partial x_q}\tag{0.1}
\]
Partial integration gives  the equation  below for every pair of
$C^2$-functions $\phi,\psi $ in ${\bf{R}}^3$ with compact support:
\[
\int\, L(\phi)\cdot \psi\, dx=
\int\, \phi\cdot L^*(\psi)\, dx\tag{0.2}
\] 
where
the volume integrals are taken over
${\bf{R}}^3$.
A locally integrable function $\Phi(x)$ in ${\bf{R}}^3$
is  a fundamental solution to $L(x,\partial _x)$
if
\[
\psi(0)=\int\, \Phi\cdot L^*(\psi)\, dx\tag{0.3}
\] 
hold for every $C^2$-function  $\psi$ with compact support.
Next, to each 
positive number
$\kappa$ we  get  the PDE-operator $L-\kappa^2$ and a
function $x\mapsto \Phi(x;\kappa)$ is a fundamental solution to $L-\kappa^2$
if
\[
\psi(0)=\int\, \Phi(x:\kappa)\cdot (L^*-\kappa^2)(\psi(x))\, dx\tag{0.4}
\] 
hold for compactly supported $C^2$-functions $\psi$.
Next, the  origin can  replaced by a variable point $\xi$ in
${\bf{R}}^3$ and then one seeks
a function
$\Phi^*(x,\xi;\kappa)$ with the property that
\[
\psi(\xi)=\int\, \Phi(x,\xi;\kappa)\cdot (L^*(x,\partial_x)-\kappa^2)(\psi(x))\, dx\tag{*}
\] 
hold for all  $\xi\in{\bf{R}}^3$
and every $C^2$-function $\psi$ with compact support.
Keeping $\kappa$ fixed this means that  
$\Phi(x,\xi;\kappa)$ is a function of six variables  defined in 
${\bf{R}}^3\times {\bf{R}}^3$.
With these notations we announce the main result:


\bigskip

\noindent
{\bf{Main Theorem.}} \emph{There exist  three constants
$C,k,\kappa_*$ such that for every $\kappa\geq\kappa_*$ one can find a fundamental 
solution
$\Phi(x,\xi;\kappa)$ which is locally integrable
in the 6-dimensional $(x,\xi)$-space.
Moreover,
for each $0<\gamma\leq 2$ a constant $C_\gamma$ such that}
\[
|\Phi(x,\xi;\kappa)|\leq
C\cdot \frac{e^{-k\kappa|x-\xi|}}{|x-\xi|}+
 \frac{C_\gamma}{(\kappa|x-\xi|)^{\gamma}}
\]

\bigskip



\noindent
To prove this result we
first consider the case when
$L$ has
constant coefficients. Here  
the construction of   fundamental solutions was (at least essentially)
given by
Newton in his famous
text-books from 1666 and goes as follows:
Consider a 
positive  and symmetric $3\times 3$-matrix
$A= \{a_{pq}\}$. Let
$\{b_{pq}\}$ be the elements of the inverse matrix which gives 
the quadratic form

\[ 
 B(x)= \sum_{p,q}\, b_{pq} a_px_q
\]
Put
\[
\alpha=\sqrt{\kappa^2+\frac{1}{2}\, \sum_{p,q}\, b_{pq} a_pa_q
-a_0}
\]
where $\kappa$ is chosen so large that
the term under the square-root is $>0$. Finally, put
\[
\Delta=\det(A)
\]
With these notations we get a function:
\[
H(x;\kappa)= \frac{1}{4\pi\cdot \sqrt{\Delta\cdot B(x)}}
\cdot e^{-\alpha \sqrt{B(x)}-
\frac{1}{2}\sum_{p,q}b_{pq} a_p\cdot x_q}\tag{1.1} 
\]


\medskip




\noindent
{\bf{1.1 Exercise.}} Verify by Stokes  formula
that $H(x;\kappa)$  yields  a fundamental solution
to the PDE-operator $L(\partial_x)-\kappa^2$ where the single indexed $a$-numbers are arbitrary real numbers.

\medskip



\noindent
{\bf{1.2 The case with variable coefficients.}}
Now $L$ has variable coefficients.
For each $\xi\in{\bf{R}}^3$ the elements of the inverse matrix
to $\{a_{pq}(\xi)$
are denoted by $\{b_{pq}(\xi)\}$.
Choose $\kappa_0>0$ such that
\[
\kappa_0^2+\frac{1}{2}\, \sum_{p,q}\, b_{pq}(\xi) a_p(\xi)a_q(\xi)
-b(\xi)>0\quad\text{hold for all}\quad  \xi\in{\bf{R}}^3
\] 
and for every $\kappa\geq \kappa_0$ we set
\[
\alpha_\kappa(\xi)=
\sqrt{\kappa^2+\frac{1}{2}\, \sum_{p,q}\, b_{pq}(\xi) a_p(\xi)a_q(\xi)
-b(\xi)}\tag{i}
\]
Following Newton's  we
put:
\[
H(x,\xi;\kappa)=\frac{1}{4\pi}\cdot
 \frac{\sqrt{\Delta(\xi)}^{-\frac{1}{2}}}{
\sqrt{ \sum_{p,q}\, b_{pq}(\xi)\cdot x_px_q}}
\cdot e^{-\alpha_\kappa(\xi) \sqrt{B(x)}-
\frac{1}{2}\sum_{p,q}b_{pq}(\xi) a_p(\xi)\cdot x_q} \tag{ii}
\]

\noindent
When $\xi$ is kept fixed this  function of
$x$ is real analytic  outside the origin and 
$x\to H(x,\xi;\kappa)$ is locally integrable
as a function of $x$ in a neighborhood of the origin.
We are going to construct  a fundamental solution
which takes the form
\[
\Phi(x,\xi;\kappa)=
H(x-\xi,\xi;\kappa)+\int_{{\bf{R}}^3}\, 
H(x-y,\xi;\kappa)\cdot\Psi(y,\xi;\kappa)\, dy\tag{iii}
\]
where the $\Psi$-function is the solution to an integral equation
which we construct in (1.5). But first we need another construction.

\medskip

\noindent
{\bf{1.3 The function $F(x,\xi;\kappa)$.}}
For every fixed $\xi$ we get  the  differential operator in the
$x$-space:
\[ 
L_*(x,\partial_x,\xi;\kappa)=
\]
\[\sum_{p=1}^{p=3}\sum_{q=1}^{q=3}\, (a\uuu{pq}(x)-
(a\uuu{pq}(\xi))\cdot 
\frac{\partial^2}{\partial x_p\partial x_q}+
\sum_{p=1}^{p=3}\,
(a_p(x)-a_p(\xi))\frac{\partial}{\partial x_p}+ (b(x)-b(\xi))
\]

\medskip

\noindent
Apply $L_*$ to the function
$x\mapsto H(x-\xi,\xi;\kappa)$
and put
\[ 
F(x,\xi;\kappa)=\frac{1}{4\pi}\cdot L_*(x,\partial_x,\xi;\kappa)(H(x-\xi,\xi,\kappa)) \tag{1.3.1}
\]

\medskip

\noindent
{\bf{1.4 Two  estimates.}}
The limit conditions  in (0.0)     give  positive constants
$C,C_1$ and $k$ such that the following hold when $\kappa\geq\kappa_0$:
\[
|H(x-\xi,\xi;\kappa)|\leq C\cdot \frac{e^{-k\kappa|x-\xi|}}{|x-\xi|}
\quad\colon\,
[F(x,\xi;\kappa)|\leq C_1\cdot 
\frac{e^{-k\kappa|x-\xi|}}{|x-\xi|^2}
\tag{1.4.1}
\]


\noindent
The verification of (1.4.1) is left as an exercise.



\newpage





\noindent
{\bf{1.5 An integral equation.}}
We  seek
$\Psi(x,\xi;\kappa)$ which satisfies the equation:
\[ 
\Psi(x,\xi;\kappa)= \int_{{\bf{R}}^3}\,  F(x,y;\kappa)\cdot \Psi(y,\xi;\kappa)\,dy+F(x,\xi;\kappa)\tag{1.5.1}
\]
To solve (1.5.1 )
we construct the Neumann series of $F$.
Thus, starting with $F^{(1)}=F$ we set
\[
F^{(k)}(x,\xi;\kappa)=\int_{{\bf{R}}^3}\, F(x,y;\kappa)\cdot
F^{(k-1)}(y,\xi;\kappa)\, dy\quad\colon\quad k\geq 2\tag{1.5.2}
\]
Then (1.4.1 ) gives  the inequality
\[
|F^{(2)}(x,\xi;\kappa)|
\leq C_1^2\iiint
\frac{e^{-k\kappa|\xi-y|}}{|x-y|^2\cdot |\xi-y|^2}\cdot dy\tag{i}
\]


\noindent
To estimate (i) we  notice that the triple integral after
the substitution $y-\xi\to u$
becomes
\[
C_1^2\iiint
\frac{e^{-k\kappa|u|^2}}{|x-u-\xi|^2\cdot |u|^2}\cdot du\tag{ii}
\]


\noindent
In  (ii)  the volume integral can be integrated in polar
coordinates
and becomes
\[
C_1^2\cdot \int_0^\infty\int_{S^2}\, 
\frac{e^{-k\kappa r^2}}{|x-r\cdot w-\xi|^2}\cdot dwdr\tag{iii}
\]
where $S^2$ is the unit sphere and $dw$ the area measure on
$S^2$. It follows that
(iii) becomes
\[
2\pi C_1^2\cdot
\int_0^\infty\int_0^\pi\, 
\frac{e^{-k\kappa r}}{(x-\xi)^2+r^2-
2r\cdot |x-\xi|\cdot \sin\theta}\cdot d\theta dr=
\]
\[
\frac{2\pi C_1^2}{|x-\xi|}\cdot\int_0^\infty\, e^{-k\kappa |x-\xi|t}\cdot
\log\, |\frac{1+t}{1-t}|\cdot \frac{dt}{t}\tag{iv}
\]
where the last equality follows by a straightforward computation.

\medskip


\noindent
{\bf{1.6 Exercise.}}
Show that (iv) gives the estimate
\[
|F^{(2)}(x,\xi;\kappa)|\leq \frac{2\pi\cdot  C_1^2\cdot C_1^*}{\kappa\cdot |x-\xi|^2}
\]
where $C_1^*$ is a fixed positive constant
which is independent of $x$ and $\xi$ and 
show by an induction over $n$
that one has:
\[
|F^{(n)}(x,\xi;\kappa)|\leq\frac{C_1}{|x-\xi|^2}\cdot 
\bigl[\frac{2\pi C_1^2\cdot C_1^*}{\kappa}\bigr]^{n-1}
\quad\text{for every}\quad  n\geq 2\tag{*}
\]
\medskip

\noindent
{\bf{1.6 Conclusion.}}
Choose  $\kappa_0^*$ so large that
\[
2\pi C_1^2\cdot C_1^*<\kappa_0^*\tag{1.6.1}
\]
Then (*) implies that 
the Neumann series
\[
\sum_{n=1}^\infty F^{(n)}(x,\xi;\kappa)
\]
converges when 
$\kappa\geq \kappa_0^*$ 
and
gives the requested solution $\Psi(x,\xi;\kappa)$ in (1.5.1).
\bigskip


\noindent
{\bf{1.7 Exercise.}}
We  have found 
$\Psi$ which satisfies the integral equation in ¤ 1.5.1.
Next, since the $H$-function in (ii) from ¤ 1.2 is everywhere positive
the integral equation (iii)in ¤ 1.2 has a unique solution
$\Phi(x,\xi;\kappa)$. Using Green's formula the reader can check that
$\Phi(x,\xi;\kappa)$ yields   a fundamental solution
of $L(x,\partial_x)-\kappa^2$.

\medskip


\noindent{\bf {1.8 Some estimates.}}
The  constructions above show that
the  functions
\[
x\mapsto \Phi(x,\xi;\kappa)\quad\text{and}\quad 
x\mapsto H(x-\xi,\xi;\kappa)
\]


\noindent
have the same  singularities at $x=\xi$.
Consider the difference
\[
Q(x,\xi;\kappa)=\Phi(x,\xi;\kappa)-
H(x-\xi,\xi;\kappa)\tag{1.8.1}
\]
\medskip


\noindent
{\bf{1.8.2 Exercise.}}
Use the previous constructions to show
that for every $0<\gamma\leq 2$
there is a constant $C_\gamma$
such that
\[
\bigl |Q(x,\xi;\kappa)\,\bigr|\leq \frac{C_\gamma}{(\kappa|x-\xi|)^{\gamma}}
\]
hold for every pair $(x,\xi)$ and every $\kappa\geq \kappa_0$.
Finally, the reader can apply 
the inequality for the
$H$-function in (1.4.1) to conclude the results in the Main Theorem.



\newpage

\centerline {\bf{¤ 2. Green's functions.}}
\bigskip


\noindent
Let $\Omega$ be a bounded domain in
${\bf{R}}^3$, and $L$ an elliptic differential operator as in ¤ xx.
Let $\kappa>0$ and suppose we have found a function
$G(x,y;\kappa)$ defined when $(x,y)\in \Omega\times\Omega$
with the property that
$G(x,y)=0$   if $x\in\partial\Omega$ and  $y\in\Omega$.
Moreover
\[
(L(x,\partial_x)-\kappa^2)(G(x,y;\kappa))=\delta(x-y)
\]
With $G$ as  kernel we get the integral operator
\[
\mathcal G(f)(x)=
\int_\Omega\, 
G(x,y;\kappa)\, f(y)\, dy 
\]
Then $\mathcal G(f)(x)=0$ on $\partial\Omega$
and the composed operator 
\[
(L(x,\partial_x)-\kappa^2)\circ \mathcal G=E
\]
To construct $G$ we use the fundamental solution
$\Phi(x,y;\kappa)$ from ¤ xx which satisfies
\[
(L(x,\partial_x)-\kappa^2)(\Phi(x,y;\kappa))=\delta(x-y)
\]
With $y\in\Omega$ kept fixed we have the 
continuous boundary functon
\[
x\mapsto \Phi(x,y;\kappa)
\]
Solving the Dirchlet problem we find
$w(x)$ such that
$w(x)= \Phi(x,y;\kappa)$ on the boundary while
$ (L(x,\partial_x)-\kappa^2)(w)=0$ holds in $\Omega$.
Then we can take
\[
G(x,y;\kappa)=\Phi(x,y;\kappa)-w(x)
\]


\noindent
Using the estimates for the $\Phi$-function from ¤ 1
we get
estimates for the $G$-function above.
We choose    a sufficiently large
$\kappa_0$ so  that 
$\Phi(x,\xi;\kappa_0)$ is a positive function of
$(x,\xi)$. Then the following hold:
\medskip


\noindent
{\bf{2.1 Theorem.}}
\emph{One has}
\[ 
G(x,\xi;\kappa_0)=
\frac{1}{\sqrt{\Delta(x)}\cdot\sqrt{\Phi(x,\xi;\kappa_0)}}
+R(x,\xi)
\]

\noindent
\emph{where the remainder function satisfies the following for all pairs
$(x,\xi)$ in $\Omega$:}
\[ 
|R(x,\xi)|\leq C\cdot |x-\xi|^{-\frac{1}{4}}
\]


\noindent
\emph{and the   constant $C$ only  depends on the  domain 
$\Omega$ and
the PDE-operator $L$.}
\medskip

\noindent
{\bf{Remark.}}
Above the negative power  of 
$|x-\xi|$ is  a fourth-root which means that  the remainder term $R$ 
is more regular  compared
to the first term which behaves like $|x-\xi|^{-1}$ on the diagonal $x=\xi$.

\bigskip

\noindent
{\bf{2.2 Exercise.}} Prove Theorem 2.1 
If necessary, consult [Carleman: page xx-xx9 for details.

\bigskip

\medskip

\noindent
\centerline {\bf{2.3. Almost reality of eigenvalues.}}
\medskip

\noindent
Consider the set of eigenvalues $\lambda$ for which there exists a function $u$
in $\Omega$ which is zero on
$\partial\Omega$ while
\[
L(u)+\lambda\cdot u=0
\]
holds in $\Omega$.


\medskip

\noindent
{\bf{2.3.1  Proposition.}}
\emph{There exist positive constants $C_*$ and $c_*$ such that
every eigenvalue  $\lambda$ above   satisfies}
\[
|\mathfrak{Im}\,\lambda|^2\leq C_*(\mathfrak{Re}\,\lambda)+c_*)
\]
\medskip

\noindent
\emph{Proof.}
Let $u$ be an eigenfunction where
$L(u)+\lambda\cdot u=0$.
Stokes theorem and the vanishing of $u|\partial\Omega$
give:
\[
0=\int_\Omega\, \bar u\cdot (L+\lambda)(u)\,dx
=-\int_\Omega \, \sum_{p,q}\, a_{pq}(x)\cdot \frac{\partial u}{\partial x_p}
\frac {\partial \bar u}{\partial x_q}\, dx+
\int_\Omega\, \bar u\cdot( \sum \, a_p(x)
\frac{\partial u}{\partial x_p}\,)\, dx+
\] 
\[
\int_\Omega\, |u(x)|^2\cdot b(x)\, dx+
\lambda\cdot \int\, |u(x)|^2\, dx
\]
\medskip


\noindent
Write $\lambda=\xi+i\eta$.
Separating real and imaginary parts we find the two equations:
\[
\xi\int\, |u|^2\, dx=
\int\, \sum_{p,q} a_{p,q}(x)\,\frac{\partial u}{\partial x_p}\cdot 
\frac{\partial \bar u}{\partial x_q}\, dx+
\int\, \bigl(\frac{1}{2}\cdot \sum\, \frac{\partial a_p}{\partial x_p}- b\,\bigr )
\cdot |u|^2\, dx\tag{i}
\]
\[
\eta\int\, |u|^2\, dx=\frac{1}{2i}\int \sum\, a_p\bigl(
u\frac{\partial \bar u}{\partial x_p}-
\bar u \frac{\partial u}{\partial x_p}\,\bigl )\, dx\tag{ii}
\]


\noindent
Set
\[ A= \int\, |u|^2\,dx\quad\colon\quad
B= \int\, |\nabla(u)|^2\,dx
\]
Since $L$ is elliptic there exists a positive constant $k$ such that
\[
\sum_{p,q} a_{p,q}(x)\,\frac{\partial u}{\partial x_p}>
k\cdot |\nabla(u)|^2
\]
From this we see that (i-ii) gives positive constants $c_1,c_2,c_3$ such that
\[
A\xi>c_1B-c_2B\quad\colon\quad A|\eta|<c_3\cdot \sqrt{AB}\tag{iii}
\]
\medskip

\noindent
Here (iii) implies that $\xi>-c_2$ and the reader can also confirm that
\[ 
B<\frac{A}{c-1}(\xi+c-2)\quad\colon\quad
A|\eta|< A\cdot c_2\cdot \sqrt{\frac{\xi+c_2}{c_1}}\quad\colon\quad
|\eta|< c_3\cdot \sqrt{\frac{\xi+c_2}{c_1}}\tag{iv}
\]


\noindent Finally it is obvious that (iv) above gives the requested
inequality in Proposition 2.3.1.

\bigskip



\newpage




\centerline{ \bf{¤ XX. Carleman's work in PDE-theory.}}


\bigskip


\noindent
{\bf{Introduction.}}
Early contributions by
Weyl and  Carleman  laid foundations for much of
later work on partial diffferential equations.
The sections in this chapter expose material from
articles by Carleman during the period 1917 until 1938.
The most remarkable result is the uniqueness theorem in
¤ 6 where the methods of the proof has inspired later work.
See for example [Hšrmander ??].
The  boundary value problem for the wave equation 
in ¤ 7 is  nowadays
standard. But the strategy to construct a spectral function 
was revolutionary in 1922  and has after become a basic
tool. A merit is that this makes it possbile to
achieve various limit properties  for the actual solutions
by deriving properties of the spectral function.
A typical example is Theorem 0.1 in ¤ 7.
Another remarkable result appears in
¤ 3 which not only gives asymptotic formulas for eigenvalues but also
for values taken by the eigenfunctions.
The method to treat a non-linear boundary  value problem in ¤ xx also merits
attention.
It goes without saying that many of the results which are
established in dimension 2 or 3 can be extended to higher dimensions.
But to avoid technicalities we are content to deal with
"classical situations".
Let us remark that we have not
discussed Carleman's work in kinetic gaz theory
which contains far-reaching studies of non-linear equations of
the Bolzmann type.
For  this the reader may consult the monograph [Carleman].
\medskip

\noindent
Let us remark that the use ofdistributions is not needed in the subsequent
sections since fundamental solutions and other weak type equations are
expressed in a direct way via integrals.
in ¤ 1 we expose Carelan's construction of fundamental  solutions to
an elliptic second order differential operor in
${\bf{R}}^3$. I think this gives a very good lesson for
beginners in the subject since
the result is that one gets a fundamental  solution in a unique way via
rather straightforward calcuations whose sole analytic tool  is to
solve  integral equations via Neumann series for resolvents.
A reward is that one gets a fundamental
solution with good regularity
properties
and the reader may notice that we do not assume that the differential 
operators is self-adjoint.
Of course, many important topics are not overed by
the subsequent sections, and we remakr that fgor
cetain problems it is better to adopt the methods by Weyl
via variational methods and a more extensive use of
Hilbert space methods where higher order derivatives occur
and various Sobolev inequalities are used.
Examples where this becomes crucial occurs for symmetric hyperbolic systems
where a quite conclusive theorem was established by
Friedrichs
in 1946.
In ¤ xx we give an account about this which  can be read
independently  of the sections devoted to Carleman's work.





  

\newpage





\centerline {\bf{¤ 0. Fundamental solutions to second order
Elliptic operators.}}
\bigskip


\noindent
{\bf{Introduction.}}
To avoid  cumbersome technical points we shall
restrict the attention to second order elliptic operators
in dimension 2 or 3.
But it goes without saying that the subsequent results can be
extended after suitable changes of constants which appear
in the theorems.
Elliptic partial differential operators appear frequently and in order to solve 
inhomogeneous equations one often employs a fundamental  solution.
To attain this one seeks  fundamental solutions with
best possible regularity conditions.
For PDE-operators with constant coefficients one can
employ Fouriers' inversion fourmula
and we  refer to Chapter X in vol.2 in Hšrmander's text-book series on linear 
partial differential operators for a detailed account
about constructions of fundamental  solutions with optimal regularity
in the case of constant coefficients.
Passing to the case of variable coefficients we expose a construction by 
Carleman in ¤ 2 which give
fundamental  solutions to second order elliptic operators in
a canonical fashion. They 
are found
by solutions to integral equations.
Let us  remark that there is no need
for distribution
theory since we construct 
fundamental solutions which are locally integrable and 
in such situations
the
notion of fundamental solutions were well understood at an early stage after pioneering work by
Weyl and Zeilon prior to 1925. In his article Carleman refers to
\emph{Grundlšsungen}.
 

\medskip


\noindent
{\bf{Remark.}}
We have restricted the study to ${\bf{R}}^3$ and  remark only that
similar constructions can be performed when $n\geq 4$ starting from
Newton's potential 
$|x-\xi|^{-n+2}$. Here it would be  interesting to clarify the
precise estimates  when $n\geq 4$ and
establish similar inequalities as in the Main Theorem
One can also try to extend the  constructions in ¤ 1 to elliptic operators of
order $\geq 3$.
In the case of even order $2m$ one can 
employ the canonical fundamental solutions for
elliptic operators of even order with constant coefficents 
given by F. John. So here  replaces Newton's fundamental
solutions which appear in ¤ 1 below by those of John and after 
it is tempting to perform  
similar constructions as those by 
Carleman. This appears to be a "profitable research problem" for 
ph.d-students.
Let us also remark that
one does not assume that the elliptic operators are symmetric, i.e.
both the constructions as well as estimates for the fundamental solutions do
not rely upon symmetry conditions.

\medskip


\noindent
{\bf{An asymptotic formula for the spectrum.}}
Let $n=3$ and consider a second order PDE-operator
\[
L=
\sum_{p=1}^{p=3}\sum_{q=1}^{q=3}\, a_{pq}(x)\cdot \frac{\partial ^2}{\partial x_p\partial x_q}+
\sum_{p=1}^{p=3}\, a_p(x)
\frac{\partial }{\partial x_p}+a_0(x)
\]
The $a$-functions are real-valued and
defined in a neighborhood of the closure of a bounded
domain
$\Omega$ in ${\bf{R}}^3$
with a $C^1$-boundary.
Here one has the symmetry $a_{pq}=a_{qp}$, and 
$\{a_{pq}\}$ are
of class $C^2$, $\{a_p\}$  of class $C^1$ and $a_0$ is continuous.
The elliptic property of
 $L$ means that
for
every $x\in\Omega$ the eigenvalues of the symmetric
matrix
$A(x)$ with elements $\{a_{pq}(x)\}$
are positive.
Under these conditions, a  result which goes back to work by 
Neumann and PoincarŽ,
gives
a positive constant
$\kappa_0$ such that
if $\kappa\geq \kappa_0$ then
the inhomogeneous equation
\[
L(u)-\kappa^2\cdot u=f\quad\colon f\in L^2(\Omega)
\]
has a unique solution $u$ which is a $C^2$-function 
in
$\Omega$ and  extends to the closure where it is zero on
$\partial\Omega$.
Moreover, there exists some $\kappa_0$
and for each $\kappa\geq \kappa_0$ a
Green's function
$G(x,y;\kappa)$ such that
\[
(L-\kappa^2)(\frac{1}{4\pi}\cdot \int_\Omega\, 
G(x,y;\kappa)\, f(y)\, dy )= -f(x)\quad\colon f\in L^2(\Omega)\tag{i}
\]
This  means  that the bounded linear operator on
$L^2(\Omega$ defined by
\[
f\mapsto 
-\frac{1}{4\pi}\cdot \int_\Omega\, 
G(x,y;\kappa)\, f(y)\, dy\tag{ii}
\]
is Neumann's resolvent
to the densely defined operator
$L-\kappa^2$ on the 
Hilbert space $L^2(\Omega)$. 
Next, one seeks pairs $(u_n,\lambda_n)$
where $u_n$ are $L2$-functions in $\Omega$ which 
extend to be zero on
$\partial\Omega$ and satisfy
\[ 
L(u_n)+\lambda_n\cdot u_n=0
\]
It turns out that the set of eigenvalues is discrete and
moreover their real parts tend to $+\infty$.
They are arranged with non-decreasing absolute values and in ¤ xx we prove
that there exist positive constants
$C$ and $c$ such that
\[
|\mathfrak{Im}(\lambda_n)|\leq
C\cdot(\mathfrak{Re}(\lambda_n)+c)
\] 
hold for every $n$.
Next, the elliptic
hypothesis means that
the determinant function
\[
D(x)=\det(a_{p,q}(x))
\]
is positive in $\Omega$. With these notations one has


\medskip



\noindent
{\bf{ Theorem.}}
\emph{The following limit formula holds:}
\[
\lim_{n\to\infty}\, \frac{\mathfrak{Re}(\lambda_n)}{n^{\frac{2}{3}}}
=\frac{1}{6\pi^2}\cdot \int_\Omega\, 
\frac{1}{\sqrt{D(x)}}\, dx\tag{*}
\]
\medskip

\noindent
{\bf{Remark.}}
The formula above is due to Courant and Weyl  when
$P$ is symmetric and  extended to
non-symmetric operators during 
Carleman 's lectures at Institute Mittag-Leffler in  1935.
Weyl and Courant used calculus of variation
in the symmetric case 
while Carleman employed  different methods which
have the merit that the passage to the non-symmetric case
does not cause any  trouble. 
A crucial step during the  proof of the theorem above
is to
construct a fundamental solution $\Phi(x,\xi;\kappa)$
to the PDE-operators
$L-\kappa^2$ which done in ¤ 1 while ¤ 2 treats the asymptotic formula above.
As pointed out by
Carleman the methods in the  proof  
give similar asymptotic formulas 
in   other boundary value problems such as
those considered by Neumann where one imposes boundary value conditions on
outer normals.
As an example we consider an elliptic
operator
of the form
\[
L=\Delta+
\sum_{p=1}^{p=3}\, a_p(x)
\frac{\partial }{\partial x_p}+a_0(x)
\]
where $\Delta$ is the Laplace operator.
Given a positive real-valued continuous function
$\rho(x)$ on $\partial\Omega$
we obtain the Neumann-PoincarŽ operator
$\mathcal{NP}$ which sends each $u\in C^0(\partial\Omega)$ to
\[
\mathcal{NP}(u)=
\frac{\partial u^*}{\partial{\bf{n}}_i}-\rho\cdot u
\]
Here $u^*$ is the Dirichlet extension of $u$ to $\Omega$ which
is equal to $u$ on $\partial\Omega$ and satisfies $L(u)=0$ in
$\Omega$, while
$\frac{\partial u^*}{\partial{\bf{n}}_i}$ is the inner normal along the boundary.
In the special case when
$L=\Delta$ this  boundary value problem has unique solutions, i.e.
for every
$f\in C^0(\partial\Omega)$ there exists a unique $u$ such that
\[
\mathcal{NP}(u)=f
\]
This was proved
by PoincarŽ in 1897 for
domains in ${\bf{R}}^3$ whose boundaries are of class
$C^2$ and the extension to domains with a $C^1$-boundary
is also classic.
Passing to general operators $L$ as above which are not neccesarily symmetric
one encounters spectral problems, i.e. above
$\mathcal{NP}$ regared as a linear operator on the
Banach space $C^0(\partial\Omega)$ is densely defined and
one seeks its spectrum, i.e,  compex numbers
$\lambda$ for which there exists a non-zero
$u$ such that
\[
\mathcal{NP}(u)+\lambda\cdot u=0
\]
I do not
know if there exists
an  analytic formula for these eigenvalues. Notice that a new feauture is that
the $\rho$-function affects the spectrum.










\newpage 



\centerline{\bf{¤ 1 The construction of fundamental solutions.}}
\bigskip

\noindent
In
${\bf{R}}^3$ with coordinates $x=(x_1,x_2,x_3)$ we consider 
 a second order PDE-operator
\[
L=
\sum_{p=1}^{p=3}\sum_{q=1}^{q=3}\, a_{pq}(x)\cdot \frac{\partial ^2}{\partial x_p\partial x_q}+
\sum_{p=1}^{p=3}\, a_p(x)
\frac{\partial }{\partial x_p}+a_0(x)
\]
where 
$a$-functions are real-valued and
one has the symmetry $a_{pq}=a_{qp}$.
To ensure existence of a globally defined fundamental solutions we
suppose the the following limit formulas hold
as $(x,y,z)\to \infty$:
\[
\lim a_\nu(x,y,z)=0 \colon 0\leq p\leq 3\quad\colon\,
\lim a_{pq}(x,y,z)= \text{Kronecker's delta function}
\]
Thus, $L$ approaches the Laplace operator as $(x,y,z)$ tends to
infinity. Moreover
$L$ is elliptic which means that
the eigenvalues of the symmetric
matrix with elements $\{a_{pq}(x)\}$
are positive for every $x$.
Recall the  notion of  fundamental solutions.
Consider
the adjoint
operator:
\[ 
L^*(x,\partial _x)=P-2\cdot \bigl(
\sum_{p=1}^{p=3}\, \bigl(\sum_{q=1}^{q=3}\, 
\frac{\partial a_{pq}}{\partial x_q}\bigr)\cdot \frac{\partial}{\partial x\uuu p}
-\sum_{p=1}^{p=3}\, \frac{\partial a_p}{\partial x_p}
+2\cdot \sum\sum\, \frac{\partial^2 a_{pq}}{\partial x_p\partial x_q}\tag{0.1}
\]
Partial integration gives  the equation  below for every pair of
$C^2$-functions $\phi,\psi $ in ${\bf{R}}^3$ with compact support:
\[
\int\, L(\phi)\cdot \psi\, dx=
\int\, \phi\cdot L^*(\psi)\, dx\tag{0.2}
\] 
where
the volume integrals are taken over
${\bf{R}}^3$.
A locally integrable function $\Phi(x)$ in ${\bf{R}}^3$
is  a fundamental solution to $L(x,\partial _x)$
if
\[
\psi(0)=\int\, \Phi\cdot L^*(\psi)\, dx\tag{0.3}
\] 
hold for every $C^2$-function  $\psi$ with compact support.
Next, to each 
positive number
$\kappa$ we  get  the PDE-operator $L-\kappa^2$ and a
function $x\mapsto \Phi(x;\kappa)$ is a fundamental solution to $L-\kappa^2$
if
\[
\psi(0)=\int\, \Phi(x:\kappa)\cdot (L^*-\kappa^2)(\psi(x))\, dx\tag{0.4}
\] 
hold for compactly supported $C^2$-functions $\psi$.
Next, the  origin can  replaced by a variable point $\xi$ in
${\bf{R}}^3$ and then one seeks
a function
$\Phi^*(x,\xi;\kappa)$ with the property that
\[
\psi(\xi)=\int\, \Phi(x,\xi;\kappa)\cdot (L^*(x,\partial_x)-\kappa^2)(\psi(x))\, dx\tag{*}
\] 
hold for all  $\xi\in{\bf{R}}^3$
and every $C^2$-function $\psi$ with compact support.
Keeping $\kappa$ fixed this means that  
$\Phi(x,\xi;\kappa)$ is a function of six variables  defined in 
${\bf{R}}^3\times {\bf{R}}^3$.
With these notations we announce the main result:


\bigskip

\noindent
{\bf{Main Theorem.}} \emph{There exists a  constant
$\kappa_*$ such that for every $\kappa\geq\kappa_*$ one can find a fundaemtal
solution
$\Phi(x,\xi;\kappa)$ which is locally integrable
in the 6-dimensional $(x,\xi)$-space.
Moreover,
there exist positive constants $C$ and $k$ and
for each $0<\gamma\leq 2$ a constant $C_\gamma$ such that}
\[
|\Phi(x,\xi;\kappa)|\leq
C\cdot \frac{e^{-k\kappa|x-\xi|}}{|x-\xi|}+
 \frac{C_\gamma}{(\kappa|x-\xi|)^{\gamma}}
\]
\emph{hold for all pairs $(x,\xi)$ in ${\bf{R}}^3$ and every
where the constants $k$ and $C$ do not depend upon $\kappa$.}

\bigskip



\centerline {\bf{1. The construction of $\Phi(x,\xi;\kappa)$.}}
\medskip



\noindent
When $L$ has
constant coefficients 
the construction of   fundamental solutions was (at least essentially)
given by
Newton in his famous
text-books from 1666 and goes as follows:
Consider a 
positive  and symmetric $3\times 3$-matrix
$A= \{a_{pq}\}$. Let
$\{b_{pq}\}$ be the elements of the inverse matrix which gives 
the quadratic form

\[ 
 B(x)= \sum_{p,q}\, b_{pq} a_px_q
\]
Put
\[
\alpha=\sqrt{\kappa^2+\frac{1}{2}\, \sum_{p,q}\, b_{pq} a_pa_q
-a_0}
\]
where $\kappa$ is chosen so large that
the term under the square-root is $>0$. Finally, put
\[
\Delta=\det(A)
\]
With these notations we get a function:
\[
H(x;\kappa)= \frac{1}{4\pi\cdot \sqrt{\Delta\cdot B(x)}}
\cdot e^{-\alpha \sqrt{B(x)}-
\frac{1}{2}\sum_{p,q}b_{pq} a_p\cdot x_q}\tag{1.1} 
\]


\medskip




\noindent
{\bf{Exercise.}} Verify by Stokes  formula
that $H(x;\kappa)$  yields  a fundamental solution
to the PDE-operator $L(\partial_x)-\kappa^2$.



\bigskip



\noindent
{\bf{1.2 The case with variable coefficients.}}
Now $L$ has variable coefficients.
For each $\xi\in{\bf{R}}^3$ the elements of the inverse matrix
to $\{a_{pq}(\xi)$
are denoted by $\{b_{pq}(\xi)\}$.
Choose $\kappa_0>0$ such that
\[
\kappa_0^2+\frac{1}{2}\, \sum_{p,q}\, b_{pq}(\xi) a_p(\xi)a_q(\xi)
-b(\xi)>0\quad\text{hold for all}\quad  \xi\in{\bf{R}}^3
\] 
and for every $\kappa\geq \kappa_0$ we set
\[
\alpha_\kappa(\xi)=
\sqrt{\kappa^2+\frac{1}{2}\, \sum_{p,q}\, b_{pq}(\xi) a_p(\xi)a_q(\xi)
-b(\xi)}\tag{i}
\]
Following Newton's construction in (1.1) we
put:
\[
H(x,\xi;\kappa)=\frac{1}{4\pi}\cdot
 \frac{\sqrt{\Delta(\xi)}^{-\frac{1}{2}}}{
\sqrt{ \sum_{p,q}\, b_{pq}(\xi)\cdot x_px_q}}
\cdot e^{-\alpha_\kappa(\xi) \sqrt{B(x)}-
\frac{1}{2}\sum_{p,q}b_{pq}(\xi) a_p(\xi)\cdot x_q} \tag{ii}
\]

\noindent
When $\xi$ is kept fixed this  function of
$x$ is real analytic  outside the origin and 
$x\to H(x,\xi;\kappa)$ is locally integrable
as a function of $x$ in a neighborhood of the origin.
We are going to construct  a fundamental solution
which takes the form
\[
\Phi(x,\xi;\kappa)=
H(x-\xi,\xi;\kappa)+\int_{{\bf{R}}^3}\, 
H(x-y,\xi;\kappa)\cdot\Psi(y,\xi;\kappa)\, dy\tag{iii}
\]
where the $\Psi$-function is the solution to an integral equation
which we construct in (1.5). But first we need another construction.

\medskip

\noindent
{\bf{1.3 The function $F(x,\xi;\kappa)$.}}
For every fixed $\xi$ we get  the  differential operator in the
$x$-space:
\[ 
L_*(x,\partial_x,\xi;\kappa)=
\]
\[\sum_{p=1}^{p=3}\sum_{q=1}^{q=3}\, (a\uuu{pq}(x)-
(a\uuu{pq}(\xi))\cdot 
\frac{\partial^2}{\partial x_p\partial x_q}+
\sum_{p=1}^{p=3}\,
(a_p(x)-a_p(\xi))\frac{\partial}{\partial x_p}+ (b(x)-b(\xi))
\]

\medskip

\noindent
Apply $L_*$ to the function
$x\mapsto H(x-\xi,\xi;\kappa)$
and put
\[ 
F(x,\xi;\kappa)=\frac{1}{4\pi}\cdot L_*(x,\partial_x,\xi;\kappa)(H(x-\xi,\xi,\kappa)) \tag{1.3.1}
\]

\medskip

\noindent
{\bf{1.4 Two  estimates.}}
The limit conditions  in (0.0)     give  positive constants
$C,C_1$ and $k$ such that the following hold when $\kappa\geq\kappa_0$:
\[
|H(x-\xi,\xi;\kappa)|\leq C\cdot \frac{e^{-k\kappa|x-\xi|}}{|x-\xi|}
\quad\colon\,
[F(x,\xi;\kappa)|\leq C_1\cdot 
\frac{e^{-k\kappa|x-\xi|}}{|x-\xi|^2}
\tag{1.4.1}
\]


\noindent
The verification of (1.4.1) is left as an exercise.



\bigskip





\noindent
{\bf{1.5 An integral equation.}}
We  seek
$\Psi(x,\xi;\kappa)$ which satisfies the equation:
\[ 
\Psi(x,\xi;\kappa)= \int_{{\bf{R}}^3}\,  F(x,y;\kappa)\cdot \Psi(y,\xi;\kappa)\,dy+F(x,\xi;\kappa)\tag{1.5.1}
\]
To solve (1.5.1 )
we construct the Neumann series of $F$.
Thus, starting with $F^{(1)}=F$ we set
\[
F^{(k)}(x,\xi;\kappa)=\int_{{\bf{R}}^3}\, F(x,y;\kappa)\cdot
F^{(k-1)}(y,\xi;\kappa)\, dy\quad\colon\quad k\geq 2\tag{1.5.2}
\]
Then (1.4.1 ) gives  the inequality
\[
|F^{(2)}(x,\xi;\kappa)|
\leq C_1^2\iiint
\frac{e^{-k\kappa|\xi-y|}}{|x-y|^2\cdot |\xi-y|^2}\cdot dy\tag{i}
\]


\noindent
To estimate (i) we  notice that the triple integral after
the substitution $y-\xi\to u$
becomes
\[
C_1^2\iiint
\frac{e^{-k\kappa|u|^2}}{|x-u-\xi|^2\cdot |u|^2}\cdot du\tag{ii}
\]


\noindent
In  (ii)  the volume integral can be integrated in polar
coordinates
and becomes
\[
C_1^2\cdot \int_0^\infty\int_{S^2}\, 
\frac{e^{-k\kappa r^2}}{|x-r\cdot w-\xi|^2}\cdot dwdr\tag{iii}
\]
where $S^2$ is the unit sphere and $dw$ the area measure on
$S^2$. It follows that
(iii) becomes
\[
2\pi C_1^2\cdot
\int_0^\infty\int_0^\pi\, 
\frac{e^{-k\kappa r}}{(x-\xi)^2+r^2-
2r\cdot |x-\xi|\cdot \sin\theta}\cdot d\theta dr=
\]
\[
\frac{2\pi C_1^2}{|x-\xi|}\cdot\int_0^\infty\, e^{-k\kappa |x-\xi|t}\cdot
\log\, |\frac{1+t}{1-t}|\cdot \frac{dt}{t}\tag{iv}
\]
where the last equality follows by a straightforward computation.

\medskip


\noindent
{\bf{1.6 Exercise.}}
Show that (iv) gives the estimate
\[
|F^{(2)}(x,\xi;\kappa)|\leq \frac{2\pi\cdot  C_1^2\cdot C_1^*}{\kappa\cdot |x-\xi|^2}
\]
where $C_1^*$ is a fixed positive constant
which is independent of $x$ and $\xi$ and 
show by an induction over $n$
that one has:
\[
|F^{(n)}(x,\xi;\kappa)|\leq\frac{C_1}{|x-\xi|^2}\cdot 
\bigl[\frac{2\pi C_1^2\cdot C_1^*}{\kappa}\bigr]^{n-1}
\quad\text{for every}\quad  n\geq 2\tag{*}
\]
\medskip

\noindent
{\bf{1.6 Conclusion.}}
Choose  $\kappa_0^*$ so large that
\[
2\pi C_1^2\cdot C_1^*<\kappa_0^*\tag{1.6.1}
\]
Then (*) implies that 
the Neumann series
\[
\sum_{n=1}^\infty F^{(n)}(x,\xi;\kappa)
\]
converges when 
$\kappa\geq \kappa_0^*$ 
and
gives the requested solution $\Psi(x,\xi;\kappa)$ in (1.5.1).
\bigskip


\noindent
{\bf{1.7 Exercise.}}
We  have found 
$\Psi$ which satisfies the integral equation in ¤ 1.5.1.
Next, since the $H$-function in (ii) from ¤ 1.2 is everywhere positive
the integral equation (iii)in ¤ 1.2 has a unique solution
$\Phi(x,\xi;\kappa)$. Using Green's formula the reader can check that
$\Phi(x,\xi;\kappa)$ yields   a fundamental solution
of $L(x,\partial_x)-\kappa^2$.

\medskip


\noindent{\bf {1.8 Some estimates.}}
The  constructions above show that
the  functions
\[
x\mapsto \Phi(x,\xi;\kappa)\quad\text{and}\quad 
x\mapsto H(x-\xi,\xi;\kappa)
\]


\noindent
have the same  singularities at $x=\xi$.
Consider the difference
\[
Q(x,\xi;\kappa)=\Phi(x,\xi;\kappa)-
H(x-\xi,\xi;\kappa)\tag{1.8.1}
\]
\medskip


\noindent
{\bf{1.8.2 Exercise.}}
Use the previous constructions to show
that for every $0<\gamma\leq 2$
there is a constant $C_\gamma$
such that
\[
\bigl |Q(x,\xi;\kappa)\,\bigr|\leq \frac{C_\gamma}{(\kappa|x-\xi|)^{\gamma}}
\]
hold for every pair $(x,\xi)$ and every $\kappa\geq \kappa_0$.
Finally, the reader can apply 
the inequality for the
$H$-function in (1.4.1) to conclude the results in the Main Theorem.



\newpage

\centerline {\bf{¤ 2. Green's functions.}}
\bigskip


\noindent
Let $\Omega$ be a bounded domain in
${\bf{R}}^3$, and $L$ an elliptic differential operator as in ¤ xx.
Let $\kappa>0$ and suppose we have found a function
$G(x,y;\kappa)$ defined when $(x,y)\in \Omega\times\Omega$
with the property that
$G(x,y)=0$   if $x\in\partial\Omega$ and  $y\in\Omega$.
Moreover
\[
(L(x,\partial_x)-\kappa^2)(G(x,y;\kappa))=\delta(x-y)
\]
With $G$ as  kernel we get the integral operator
\[
\mathcal G(f)(x)=
\int_\Omega\, 
G(x,y;\kappa)\, f(y)\, dy 
\]
Then $\mathcal G(f)(x)=0$ on $\partial\Omega$
and the composed operator 
\[
(L(x,\partial_x)-\kappa^2)\circ \mathcal G=E
\]
To construct $G$ we use the fundamental solution
$\Phi(x,y;\kappa)$ from ¤ xx which satisfies
\[
(L(x,\partial_x)-\kappa^2)(\Phi(x,y;\kappa))=\delta(x-y)
\]
With $y\in\Omega$ kept fixed we have the 
continuous boundary functon
\[
x\mapsto \Phi(x,y;\kappa)
\]
Solving the Dirchlet problem we find
$w(x)$ such that
$w(x)= \Phi(x,y;\kappa)$ on the boundary while
$ (L(x,\partial_x)-\kappa^2)(w)=0$ holds in $\Omega$.
Then we can take
\[
G(x,y;\kappa)=\Phi(x,y;\kappa)-w(x)
\]


\noindent
Using the estimates for the $\Phi$-function from ¤ 1
we get
estimates for the $G$-function above.
We choose    a sufficiently large
$\kappa_0$ so  that 
$\Phi(x,\xi;\kappa_0)$ is a positive function of
$(x,\xi)$. Then the following hold:
\medskip


\noindent
{\bf{2.1 Theorem.}}
\emph{One has}
\[ 
G(x,\xi;\kappa_0)=
\frac{1}{\sqrt{\Delta(x)}\cdot\sqrt{\Phi(x,\xi;\kappa_0)}}
+R(x,\xi)
\]

\noindent
\emph{where the remainder function satisfies the following for all pairs
$(x,\xi)$ in $\Omega$:}
\[ 
|R(x,\xi)|\leq C\cdot |x-\xi|^{-\frac{1}{4}}
\]


\noindent
\emph{and the   constant $C$ only  depends on the  domain 
$\Omega$ and
the PDE-operator $L$.}
\medskip

\noindent
{\bf{Remark.}}
Above the negative power  of 
$|x-\xi|$ is  a fourth-root which means that  the remainder term $R$ 
is more regular  compared
to the first term which behaves like $|x-\xi|^{-1}$ on the diagonal $x=\xi$.

\bigskip

\noindent
{\bf{2.2 Exercise.}} Prove Theorem 2.1 
If necessary, consult [Carleman: page xx-xx9 for details.

\bigskip

\medskip

\noindent
\centerline {\bf{2.3. Almost reality of eigenvalues.}}
\medskip

\noindent
Consider the set of eigenvalues $\lambda$ for which there exists a function $u$
in $\Omega$ which is zero on
$\partial\Omega$ while
\[
L(u)+\lambda\cdot u=0
\]
holds in $\Omega$.


\medskip

\noindent
{\bf{2.3.1  Proposition.}}
\emph{There exist positive constants $C_*$ and $c_*$ such that
every eigenvalue  $\lambda$ above   satisfies}
\[
|\mathfrak{Im}\,\lambda|^2\leq C_*(\mathfrak{Re}\,\lambda)+c_*)
\]
\medskip

\noindent
\emph{Proof.}
Let $u$ be an eigenfunction where
$L(u)+\lambda\cdot u=0$.
Stokes theorem and the vanishing of $u|\partial\Omega$
give:
\[
0=\int_\Omega\, \bar u\cdot (L+\lambda)(u)\,dx
=-\int_\Omega \, \sum_{p,q}\, a_{pq}(x)\cdot \frac{\partial u}{\partial x_p}
\frac {\partial \bar u}{\partial x_q}\, dx+
\int_\Omega\, \bar u\cdot( \sum \, a_p(x)
\frac{\partial u}{\partial x_p}\,)\, dx+
\] 
\[
\int_\Omega\, |u(x)|^2\cdot b(x)\, dx+
\lambda\cdot \int\, |u(x)|^2\, dx
\]
\medskip


\noindent
Write $\lambda=\xi+i\eta$.
Separating real and imaginary parts we find the two equations:
\[
\xi\int\, |u|^2\, dx=
\int\, \sum_{p,q} a_{p,q}(x)\,\frac{\partial u}{\partial x_p}\cdot 
\frac{\partial \bar u}{\partial x_q}\, dx+
\int\, \bigl(\frac{1}{2}\cdot \sum\, \frac{\partial a_p}{\partial x_p}- b\,\bigr )
\cdot |u|^2\, dx\tag{i}
\]
\[
\eta\int\, |u|^2\, dx=\frac{1}{2i}\int \sum\, a_p\bigl(
u\frac{\partial \bar u}{\partial x_p}-
\bar u \frac{\partial u}{\partial x_p}\,\bigl )\, dx\tag{ii}
\]


\noindent
Set
\[ A= \int\, |u|^2\,dx\quad\colon\quad
B= \int\, |\nabla(u)|^2\,dx
\]
Since $L$ is elliptic there exists a positive constant $k$ such that
\[
\sum_{p,q} a_{p,q}(x)\,\frac{\partial u}{\partial x_p}>
k\cdot |\nabla(u)|^2
\]
From this we see that (i-ii) gives positive constants $c_1,c_2,c_3$ such that
\[
A\xi>c_1B-c_2B\quad\colon\quad A|\eta|<c_3\cdot \sqrt{AB}\tag{iii}
\]
\medskip

\noindent
Here (iii) implies that $\xi>-c_2$ and the reader can also confirm that
\[ 
B<\frac{A}{c-1}(\xi+c-2)\quad\colon\quad
A|\eta|< A\cdot c_2\cdot \sqrt{\frac{\xi+c_2}{c_1}}\quad\colon\quad
|\eta|< c_3\cdot \sqrt{\frac{\xi+c_2}{c_1}}\tag{iv}
\]


\noindent Finally it is obvious that (iv) above gives the requested
inequality in Proposition 2.3.1.

\bigskip

\centerline{\bf{2.4. Asymptotic  formula for eigenvalues}}
\bigskip


\noindent
Consider a function $f$ which satisfies
\[
\mathcal G(f)=-\frac{1}{\lambda}\cdot f
\]
for some non-zero complex number $\lambda$.
With $u=\mathcal G(f)$ it follows from (xx) that
\[
(L-\kappa^2)(u)=f=-\lambda\cdot u
\]
Hence
\[
L(u)+(\lambda-\kappa^2)u=0
\]
\medskip


\noindent
{\bf{About the proof of Theorem xx.}}
From  the above the asymptotic formula in Theorem xx 
can be derived from asymptotic properties of eigenvalues to
the integral operator $|mathcal G$.
Using Theorem 2.1 and the estimates for the fundsemtnal solution
$\Phi$ in ¤ 1, one can proceed as in the
the next section where a Tauberian theorem is employed to
finish the proof of Theorem xx.
The  reader may try to supply details or  consult 
[Carleman: page xx-xx] for details.














\newpage














\newpage

\centerline{\bf{¤ 3. A study of $\Delta(\phi)+\lambda\cdot \phi$.}}
\bigskip


\noindent
{\bf{Introduction.}}
We expose material from Carleman's article \emph{xxx}
whose contents were presented at the Scandinavian Congress in Stockholm 1934.
In
${\bf{R}}^2$ we 
consider a bounded Dirichlet regular domain
$\Omega$, i.e. every $f\in C^0(\partial\Omega)$
has a harmonic extension to $\Omega$.
A wellknown  
fact
established by
G. Neumann and H. PoincarŽ
during the years 1879-1895
gives the following: First there
exists the Greens' function
\[
G(p,q)= \log\,\frac{1}{|p-q|}+H(p,q)
\]
where $H(p,q)= H(q,p)$ is continuous in
the product set
$\overline{\Omega}\times\overline{\Omega}$ with the property that
the operator $\mathcal G$ defined on $L^2(\Omega)$ by
\[
f\mapsto \mathcal G_f(p)= \frac{1}{2\pi}\dot \iint\, G(p,q)f(q)\,dq
\]
satisfies
\[ 
\Delta\circ \mathcal G_f=-f\quad\colon f\in L^2(\Omega)
\]
Moreover,  $\mathcal G$ is a compact operator on
the Hilbert space $L^2(\Omega)$ and there 
exists a sequence $\{f_n\}$ in $L^2(\Omega$ such that
$\{\phi_n=\mathcal G_{f_n}\}$
is an orthonormal basis in $L^2(\Omega$ and
\[ 
\Delta(\phi_n)=-\lambda_n\cdot \phi_n\quad\colon\, n=1,2,\ldots
\] 
where
$0<\lambda_1\leq \lambda_2\leq \ldots\}$.
When  eigenspaces have  dimension $\geq 2$, the 
eigenvalues are repeated by their multiplicity.
\medskip

\noindent
{\bf{Main Theorem. }}\emph{For every Dirichlet regular domain
$\Omega$ and each $p\in\Omega$Êone has the limit formula}
\[ 
\lim_{N\to\infty}\, \lambda_N^{-1}\cdot \sum_{n=1}^{n=N}\, \phi_n(p)^2= \frac{1}{4\pi}
\]
\medskip

\noindent
The strategy in the proof is to consider the function of a complex variable $s$
defined by
\[
\Phi(s)=\sum_{n=1}^\infty \frac{\phi_n(p)^2}{\lambda_n^s}
\]
and show that it
is a meromorphic function in the whole complex $s$-plane with
a simple pole at $s=1$ whose residue is $\frac{1}{4\pi}$.
More precisely we shall prove:
\medskip


\noindent
{\bf{0.1 Theorem.}}
\emph{There exists an entire function
$\Psi_p(s)$ such that}
\[
\Phi_p(s)=\Psi_p(s)+\frac{1}{4\pi(s-1)}
\]
\medskip

\noindent
Let us first remark that Theorem 0.1   gives ther main theorem 
by a result  due to Wiener in the article
\emph{Tauberian theorem} [Annals of Math.1932].
Wiener's theorem 
asserts that if $\{\lambda_n\}$ is a non-decreasing sequence of
positive numbers which tends to infinity and
$\{a_n\}$ are non-negative real numbers such that
there exists the limit
\[ 
\lim_{s\to 1}\,(s-1)\cdot \sum\, \frac{a_n}{\lambda_n^s}=A
\] 
then it follows that
\[
\lim_{n\to \infty}\,\lambda_n^{-1}\cdot
\sum_{k=1}^{k=n}\, a_k=A
\]
\medskip

\noindent
{\bf{Exercise.}}
Derive the main theorem from Wiener's result and Theorem 0.1.
\medskip

\noindent
{\bf{About Wiener's result.}}
It is a version of
an famous  Tauberian  theorem proved by
Hardy and Littlewood in 1913 which goes as follows:
\medskip

\noindent
{\bf{0.2 The Hardy-Littelwood theorem.}}
\emph{Let $\{a_n\}$ be a sequence of non-negative real numbers
such that}
\[ 
A=
\lim_{r\to 1}\, (1-r)\cdot \sum\,a_nr^n\tag{*}
\]
\emph{exists. Then  there also exists the limit}
\[
A=\lim_{N\to \infty}\, \frac{a_1+\ldots+a_N}{N}\tag{**}
\]
\medskip

\noindent
Notice that no growth condition is imposed on  the sequence 
$\{a_n\}$, i.e. the sole assumption
is the existing limit (*). The proof is quite demanding and does not follow by
"abstract nonsense"from functional analysis.
For the reader's convenience we include details of the proof in a 
separate appendix since
courses devoted to series rarely appear in contemporary
education.



\bigskip









\centerline{\bf{¤ 1. Proof of Theorem 0.}}
\bigskip

\noindent
Let
$\Omega$ be a bounded and Dirichlet regular domain.
For ech fixed point  $p\in\Omega$
we 
get  the continuous function on
$\partial\Omega$ defined by
\[ 
q\mapsto  \log \frac{1}{|p-q|}
\]
We find the harmonic function
$u_p(q)$ in $\Omega$ such that
$u_p(q)=\log \frac{1}{|p-q|}\,\colon\, q\in\partial\Omega$.
Green's function is defined for pairs $p\neq q$ in
$\Omega\times\Omega$ 
by
\[ 
G(p,q)= \log\,\frac{1}{|p-q|}-u_p(q)\tag{1}
\]
Keeping
if $p\in\Omega$  fixed, the function
$q\mapsto G(p,q)$ extends to the 
closure of $\Omega$ where it vanishes if
$q\in\partial\Omega$.
If  $f\in L^2(\Omega$
we set
\[ 
\mathcal G_f(p)=\frac{1}{2\pi}\cdot \int_\Omega\, G(p,q)\cdot f(q)\, dq\tag{2}
\]
where $q=(x,y)$ so that $dq=dxdy$ when the double integral is evaluated.
From (1) we see that
\[
 \iint_{\Omega\times \Omega}\, |G(p,q)|^2\, dpdq<\infty
\]
Hence
$\mathcal G$ is of the Hilbert-Schmidt type and
therefore a compact operator on 
$L^2(\Omega)$.
Next,  recall that
$\frac{1}{2\pi}\cdot \log\sqrt{x^2+y^2}$ is
a fundamental solution to the Laplace operator.
From this the reader can   deduce the following:

\medskip

\noindent{\bf{1.1 Theorem.}}
\emph{For each $f\in L^2(\Omega)$
the Lapacian of $\mathcal G_f$
taken in the distribution sense belongs to
$L^2(\Omega)$ and one has the equality}
\[ 
\Delta(\mathcal G_f)=-f\tag{*}
\] 
\medskip


\noindent
The equation (*) means that
the composed operator
$\Delta\circ \mathcal G$ is minus the identity on
$L^2(\Omega)$.
We are  led
to introduce the 
linear operator $S$ on $L^2(\Omega)$ 
defined by $\Delta$, where  
$\mathcal D(S)$ is
the range of $\mathcal G$.
If $g\in C^2_0(\Omega)$, i.e. twice differentiable and with
compact support, it follows via Greens' formula that
\[
\frac{1}{2\pi}\cdot \int_\Omega\, G(p,q)\cdot \Delta(g)(q)\, dq=-g(p)
\]
In particular $C_0^2(\Omega)\subset\mathcal D(S)$
which  implies that
$S$ is densely defined and we  leave it to the reader to verify that
\[
\mathcal G(\Delta(f))=-f\quad\colon f\in\mathcal D(S)
\]


\medskip
\noindent
{\bf{Remark.}}
By Carl Neumann's classic construction of
resolvent operators from 1879, the result above   means that
$-\mathcal G$ is Neumann's inverse  of 
$S$. Since
$-\mathcal G$ is compact it follows by Neumann's formula for spectra that
$S$ has a discrete spectrum,and we recall the following wellknown fact which
goes back to work by PoincarŽ: 
\medskip

\noindent
{\bf{1.2 Proposition.}}\emph{
There exists an orthonormal basis $\{\phi_n\}$ in $L^2(\Omega)$
where each $\phi_n\in\mathcal D(S)$ is an eigenfunction, and
a non-decreasing sequence of positive real numbers
$\{\lambda_n\}$ such that}
\[ 
\Delta(\phi_n)+\lambda_n\cdot \phi_n=0\quad\colon n=1,2,\ldots\tag{1.2.1}
\]
\medskip

\noindent
{\bf{Remark. }} Above (1.2.1) means 
that
\[
\mathcal G(\phi_n)= \frac{1}{\lambda_n}\, \cdot \phi_n
\]
This, 
$\{\lambda_n^{-1}\}$
are  eigenvalues of the compact operator $\mathcal G$ whose sole cluster
point is $\lambda=0$.
As usual eigenvalues whose eigenspaces have
dimension $e>1$ are repeated $e$ times.



\medskip

\noindent
After these preliminaries we embark upon the proof
of Theorem 0.1. 
First, since $\mathcal G$ is a Hilbert-Schmidt operator a wellknown result due to Schur
gives
\[
\sum\, \lambda_n^{-2}<\infty \tag{i}
\]
This convergence entails that various constructions below are defined.
For each complex number $\lambda$ outside $\{\lambda_n\}$ we set
\[
G(p,q;\lambda)=
G(p,q)+
2\pi\lambda\cdot \sum_{n=1}^\infty\,
\frac{\phi_n(p)\phi_n(q)}{\lambda_n(\lambda-\lambda_n)}\tag{ii}
\]
This gives the integral operator
$\mathcal G_\lambda$ defined on $L^2(\Omega)$ by
 \[ 
 \mathcal G_\lambda(f)(p)
 =\frac{1}{2\pi}\cdot \iint_\Omega\, G(p,q;\lambda )\cdot f(q)\, dq\tag{iii}
\]

\medskip

\noindent
{\bf{A. Exercise.}} Use that the eigenfunctions $\{\phi_n\}$ is an orthonormal basis in
$L^2(\Omega)$ to show that
\[
(\Delta+\lambda)\cdot \mathcal G_\lambda=-E
\]


\noindent{\bf{B. The function $F(p,\lambda)$}}.
Set
\[ 
F(p,q,\lambda)= G(p,q;\lambda)- G(p,q)
\]
Keeping $p$ fixed we see that (ii) gives
\[
\lim_{q\to p}\, F(p,q,\lambda)=
2\pi\lambda\cdot \sum_{n=1}^\infty\,
\frac{\phi_n(p)^2}{\lambda_n(\lambda-\lambda_n)}\tag{B.1}
\]
Set
\[
F(p,\lambda)=
\lim_{q\to p}\, F(p,q,\lambda)
\]
From (i) and (B.1) it follows that it is a meromorphic function in
the complex $\lambda$-plane with at most simple poles
at $\{\lambda_n\}$.
\medskip

\noindent{\bf{C. Exercise.}}
Let $0<a<\lambda_1$. Show via residue calculus that
one has the equality below in a half-space
$\mathfrak{Re}\, s>2$:
\[ 
\Phi(s)=
\frac{1}{4\pi^2 \cdot i}\cdot \int_{a-i\infty}^{a+i\infty}\, 
F(p,\lambda)\cdot \lambda^{-s}\, d\lambda\tag{C.1}
\]
where the line integral  is taken on the vertical  line
$\mathfrak{Re}\,\lambda=a$.

\medskip

\noindent
{\bf{D. Change of contour integrals.}}
At this stage we employ a device which goes to
Riemann and
move the integration into the half-space
$\mathfrak{Re}(\lambda)<a$.
Consider  the curve $\gamma_+$
defined as the union of the
negative real interval $(-\infty,a]$ followed by
the upper
half-circle $\{\lambda= ae^{i\theta}\,\colon 0\leq\theta\leq \pi \}$
and the 
half-line $\{\lambda= a+it\,\colon t\geq 0\}$.
Cauchy's theorem entails that 
\[ 
\int_{\gamma_+}\, F(p,\lambda)\cdot \lambda^{-s}\, d\lambda=0
\]
We leave it to the reader to contruct the
similar
curve
$\gamma_-=\bar \gamma_+$. Using 
the vanishing of these line integrals and taking the branches of the 
multi-valued function
$\lambda^s$ into the account the reader should verify the following:

\medskip


\noindent
{\bf{E. Lemma.}}
\emph{One has the equality}
\[ 
\Phi(s)=\frac{a^{s-1}}{4\pi}\cdot \int_{-\pi}^\pi\,
F(ae^{i\theta})\cdot e^{(i(1-s)\theta}\,d\theta
+
\frac{\sin \pi s}{2\pi^2}\cdot \int_a^\infty\, F(p,-x)\cdot x^{-s}\,dx\tag{E.1}
\]
\medskip

\noindent
The first term in the sum of the right hand side of (E.1)
is obviously an entire function of $s$. So there remains to
prove that
\[
 s\mapsto  \frac{\sin \pi s}{2\pi^2}\cdot \
 \int_a^\infty\, F(p,-x)\cdot x^{-s}\,dx\tag{E.2}
\]
is meromorphic with
a single pole at $s=1$ whose residue is $\frac{1}{4\pi}$.
To attain this we  express $F(p,-x)$ when $x$ are real and positive in another way.
\medskip

\noindent
{\bf{F.  The $K$-function.}}
In the half-space $\mathfrak{Re}\,z>0$ there exists the analytic function
\[
K(z)= \int_1^\infty\, \frac{e^{-zt}}{\sqrt{t^2-1}}\,dt
\]
\medskip

\noindent
{\bf{Exercise.}}
Show that $K$ extends to a multi-valued analytic function outside
$\{z=0\}$ given by
\[
K(z)=-I_0(z)\cdot \log z+ I_1(z)\tag{F.1}
\] 
where $I_0$ and $I_1$ are entire functions
with series expansions
\[
I_0(z)=\sum_{m=0}^\infty\, \frac{2^{-2m}}{(m!)^2}\cdot
z^{2m}\tag{i}
\]
\[ 
I_1(z)= \sum_{m=0}^\infty\, \rho(m)\cdot
\frac{2^{-2m}} {(m!)^2} \cdot z^{2m}\quad
\colon \rho(m)=1+\frac{1}{2}+\ldots+\frac{1}{m}-\gamma\tag{ii}
\]
where $\gamma$ is the usual Euler constant.

\bigskip


\noindent
With  $p$ kept fixed and $\kappa>0$ 
we solve the Dirichlet problem and find
a  function $q\mapsto H(p,q;\kappa)$ which satisfies  the
equation
\[
 \Delta(H)-\kappa\cdot H=0\tag{F.2}
\] 
in $\Omega$ with boundary values
\[ 
H(p,q;\kappa)=K(\sqrt{\kappa}|p-q|)\quad\colon q\in \partial\Omega
\]


\noindent
{\bf{G. Exercise.}}
Verify the equation
\[ 
G(p,q;-\kappa)=K(\sqrt{\kappa}\cdot |p-q|)- H(q;\kappa)\quad\colon \kappa>0
\]



\noindent
Next,   the construction of $G(p,q)$ gives
\[
 F(p,-\kappa)=
 \lim_{q\to p}\,
 [K(\sqrt{\kappa}\cdot |p-q|)+\log\,|p-q|]+
 \lim_{q\to p}\,[u_p(q)+ H(p,q,\kappa)]\tag{G.1}
\]
The last term above has the  "nice limit" 
$u_p(p)+H(p,p,\kappa)$ and from  (F.1)  the reader can  verify the limit formula:
\[
 \lim_{q\to p}\,
 [K(\sqrt{\kappa}\cdot |p-q|)+\log\,|p-q|]=
 -\frac{1}{2}\cdot \log \kappa +\log 2-\gamma\tag{G.2}
\]
where $\gamma$ is  Euler's constant.

\bigskip

\noindent
{\bf{H. Final part of the proof.}}.
Set $A=  +\log 2-\gamma+u_p(p)$. Then (G.1) and (G.2)
give
\[
F(p,-\kappa)= -\frac{1}{2}\cdot \log \kappa +A+H(p,p;-\kappa)
\]
With $x=\kappa$ in (E.2 ) we  proceed  as follows.
To  begin with it is clear that
\[
s\mapsto A\cdot 
\frac{\sin \pi s}{2\pi^2}\cdot \int_a^\infty\,  x^{-s}\,dx
\]
is an entire function of $s$.
Next,  consider the function
\[ 
\rho(s)=
 -\frac{1}{2}\cdot 
\frac{\sin \pi s}{2\pi^2}\cdot \int_a^\infty\,  \log x\cdot x^{-s}\,dx
\]
Notice that the complex derivative
\[
\frac{d}{ds}\,  \int_a^\infty\,  x^{-s}\,dx=
- \int_a^\infty\,  \log x\cdot x^{-s}\,dx
\]

\medskip
\noindent
{\bf{H.1 Exercise.}}
Use the  above to show that
\[
\rho(s)-\frac{1}{4\pi(s-1)}
 \]
is an entire function.
\medskip


\noindent
From the above we see that Theorem 0.1  follows if we have proved
\medskip

\noindent
 {\bf{H.2 Lemma.}}
\emph{The following function  is entire}:
\[
s\mapsto \frac{\sin\,\pi s}{2\pi^2}\cdot
\int_a^\infty\, H(p,p,\kappa)\cdot  \kappa^{-s}\,d\kappa
\]
\medskip

\noindent
\emph{Proof.}
When $\kappa>0$
the equation (F.1) shows that $q\mapsto H(p,q;\kappa)$
is subharmonic  in $\Omega$ and the maximum principle gives
\[
0\leq  H(p,q;\kappa)\leq \max_{q\in\partial\Omega}\,K(\kappa|p-q|)\tag{i}
\]
With  $p\in\Omega$ fixed there is 
a positive number
$\delta$ such that
$|p-q|\geq\delta\,\colon q\in \partial\Omega$ which  
gives
positive constants
$B$ and  $\alpha$  such that
\[
H(p,p;\kappa)\leq e^{-\alpha\kappa}\quad\colon \kappa>0\tag{ii}
\]
The reader may now check that this
exponential decay gives Lemma H.2.

\newpage



\centerline{\bf {Appendix. Theorems by Abel, Tauber, Hardy and Littlewood}}
\bigskip


\noindent
{\bf Introduction.}
Consider a power series
$f(z)=\sum\, a_nz^n$ whose radius of convergence is one.
If $r<1$ and $0\leq\theta\leq 2\pi$
we are sure that the series
\[ 
f(re^{i\theta})= 
\sum\, a_nr^ne^{in\theta}
\]
is convergent. In fact, it is even absolutely convergent since
the assumption implies that
\[\sum\, |a_n|\cdot r^n<\infty\quad\text{for all}\quad r<1
\]
Passing to $r=1$ it is in general not true that the series
$\sum\, a_ne^{in\theta}$ is convergent. An example arises if we consider
the geometric series
\[ 
\frac{1}{1-z}= 1+z+z^2+\ldots
\] 
This leads to the following  problem where we without loss of
generality can take 
$\theta=0$.
Consider as above a
convergent power series and assume that there exists the limit
\[
\lim_{r\to 1}\, \sum\, a_nr^n\tag{*}
\]
When can we conclude that the series
$\sum\, a_n$ also is convergent and that
one has the equality
\[
 \sum\, a_n=
\lim_{r\to 1}\, \sum\, a_n r^n\tag{**}
\]
The first result in this direction was established by Abel in a work from 1823:
\medskip

\noindent
{\bf{A. Theorem}} \emph{Let $\{a_n\}$ be a sequence such that
$\frac{a_n}{n}\to 0$
as $n\to \infty$
and there exists}
\[
A=\lim_{r\to 1}\, \sum\, a_nr^n
\] 
\emph{Then  
$\sum\, a_n$ is convergent and the  sum is $A$.}

\medskip

\noindent
An extension of Abel's result was
established by  Tauber in 
1897. 
\medskip

\noindent
{\bf B. Theorem.}
\emph{Let $\{a_n\}$ be a sequence of real numbers such that
there exists the limit}
\[
A=\lim_{r\to 1}\, \sum\, a_nr^n
\]
Set
\[ 
\omega_n=a_1+2a_2+\ldots+na_n\quad\colon\, n\geq 1
\]
\emph{If $\lim_{n\to\infty}\,\omega_n=0$ it follows that
the series $\sum\, a_n$ is convergent and the sum is $A$.}


\bigskip

\noindent
{\bf C. Results by 
Hardy and Littlewood.}
In their joint article \emph{xxx} from 1913
the following extension of Abel's  result was proved by Hardy and Littlewood:

\medskip

\noindent
{\bf {C. Theorem.}}
\emph{Let $\{a_n\}$ be a sequence of real numbers such that there 
exists a constant $C$ so that
$\frac{a_n}{n}\leq C$ for all $n\geq 1$. Assume also that the
power series $\sum\, a_nz^n$ converges when
$|z|<1$. Then the same conclusion as in Abel's theorem holds.}
\medskip

\noindent
{\bf {Remark.}}
In addition to this they proved
a result about
positive series from the cited article which has independent interest.

\medskip

\noindent
{\bf {D. Theorem.}}
\emph{Assume that
each $a_n\geq 0$ and that there exists the limit:}
\[ 
A=
\lim_{r\to 1}\, (1-r)\cdot \sum\,a_nr^n\tag{*}
\]
\emph{Then  there exists the limit}
\[
A=\lim_{N\to \infty}\, \frac{a_1+\ldots+a_N}{N}\tag{**}
\]
\medskip

\medskip

\noindent
{\bf{Remark.}} The proofs of Abel's and Tauber's results are  easy
while C and D require more effort and rely upon 
results from calculus in one variable.
So before we enter the proofs of the  theorems above insert
some  preliminaries.
\newpage

\centerline{\bf{1. Results from calculus}}

\medskip

\noindent
Below $g(x)$ is a real-valued function defined on $(0,1)$ and
of class $C^2$ at least.
\medskip


\noindent
{\bf 1.1 Lemma } \emph{Assume that there exists a constant $C>0$ such that}
\[
g''(x)\leq C(1-x)^{-2}\quad\colon\, 0<x<1\quad\text{and}\quad
\lim_{x\to 1}\, g(x)=0
\] 
\emph{Then one  has the limit formula}:
\[
\lim_{x\to 1}\, (1-x)\cdot g'(x)=0
\]

\medskip

\noindent
{\bf 1.2 Lemma } \emph{Assume that the second order derivative
$g''(x)>0$.
Then the following implication holds for each $\alpha>0$:}

\[
\lim_{x\to 1}\, (1-x)^\alpha\cdot g(x)=1\implies
\lim_{x\to 1}\, (1-x)^{\alpha+1}\cdot g'(x)=\alpha
\]




\noindent
{\bf{Remark.}}
If $g(x)$ has higher order derivatives
which all are
$>0$ on $(0,1)$
we can iterate the conclusion in Lemma 1.2 where 
we take $\alpha$ to be positive integers.
More precisely, by an induction over
$\nu$ the reader may verify that if
\[
\lim_{x\to 1}\, (1-x)\cdot g(x)=1
\]
exists and  if 
$\{g^{(\nu)}(x)>0\}$ for all 
every $\nu\geq 2$ then 
\[
\lim_{x\to 1}\, (1-x)^{\nu+1}\cdot g^{(\nu)}(x)=\nu\,!
\quad\colon\, \nu\geq 2\tag{*}
\]



\bigskip

\noindent
Next, to each integer $\nu\geq 1$ we denote by $[\nu-\nu^{2/3}]$
the largest integer $\leq\,(\nu-\nu^{2/3}).$ Set
\[
J_*(\nu)=\sum_{n\leq [\nu-\nu^{2/3}]}\,
n^\nu e^{-\nu}
\quad\colon\quad J^*(\nu)=\sum_{n\geq [\nu+\nu^{2/3}]}\,
n^\nu e^{-\nu}
\]

\medskip

\noindent
{\bf 1.3 Lemma }
\emph{There exists a constant $C$
such that}
\[
\frac{J^*(\nu)+J_*(\nu)}{\nu\,!}\leq \delta(\nu)\quad\colon\quad
\delta(\nu)=C\cdot \text{exp}\, \bigl(-\frac{1}{2}\cdot \nu^{\frac{1}{{3}}}\bigr )
\quad\colon\,\nu=1,2,\ldots
\]

\medskip

\centerline{\emph{Proofs}}

\bigskip

\noindent
We prove only  Lemma 1.1 which is a bit tricky 
while the proofs of Lemma 1.2 and 1.3 are
left as  exercises to the reader.
Fix $0<\theta<1$. Let
$0<x<1$ and set
\[
x_1=x+(1-x)\theta
\]
The mean-value theorem in calculus gives
\[ 
g(x_1)-g(x)=\theta(1-x)g'(x)+\frac{\theta^2}{2}(1-x)^2\cdot g''(\xi)\quad
\text{for some}\quad \, x<\xi<x_1\tag{i}
\]
By the hypothesis
\[
g''(\xi)\leq C(1-\xi)^{-2}\leq C)1-x_1)^{-2}
\]
Hence (i) gives
\[
(1-x)g'(x)\geq
\frac{1}{\theta}(g(x_1)-g(x))-
C\cdot \frac{\theta}{2}\frac{(1-x)^2}{1-x_1)^2}=
\]
\[
\frac{1}{\theta}(g(x_1)-g(x))-
\frac{C\cdot \theta}{2(1-\theta)^2}
\]
Keeping $\theta$ fixed we have by assumption
\[
\lim_{x\to 1}\, g(x)=0
\]
Notice also that $x\to 1\implies x_1\to 1$. It follows that



\[
\liminf_{x\to 1}\,\,
(1-x)g'(x)\geq -\frac{C\cdot \theta}{2(1-\theta)^2}
\]
Above  $0<\theta<1$ is arbitrary, i.e. we can choose 
small $\theta>0$ and hence we have proved that
\[
\liminf_{x\to 1}\,
(1-x)g'(x)\geq 0\tag{*}
\]
\medskip

\noindent
Next we  prove the opposed inequality

\[
\limsup_{x\to 1}\,
(1-x)g'(x)\leq 0\tag{**}
\]
To get (**) we apply the mean value theorem in the form
\[
g(x_1)-g(x)=\theta(1-x)g'(x_1)-\frac{\theta^2}{2}(1-x)^2\cdot g''(\eta)\quad
\colon\, x<\eta<x_1\tag{ii}
\]
Since $(1-x_1)=\theta(1-x)(1-\theta)$ we get
\[ 
(1-x_1)g'(x_1)=\frac{1-\theta}{\theta}\cdot (g(x_1)-g(x))+
\frac{(1-\theta)\theta}{2}\cdot(1-x)^2g''(\eta)\tag{iii}
\]
Now $g''(\eta)\leq C(1-\eta)^{-2}\leq C(1-x_1)^{-2}$ so
the right hand side in (iii) is majorized by
\[
\frac{1-\theta}{\theta}\cdot (g(x_1)-g(x))+
C\cdot \frac{(1-\theta)\theta}{2}\cdot(1-x)^2(1-x_1)^2=
\]
 \[
\frac{1-\theta}{\theta}\cdot (g(x_1)-g(x))+
C\cdot \frac{\theta}{2(1-\theta}\tag{iv}
\]
Keeping $\theta$ fixed while $x\to 1$ we obtain:
\[
\liminf_{x\to 1}\, (1-x)g'(x)\leq 
C\cdot \frac{\theta}{2(1-\theta}
\]
Again we can choose arbitrary small $\theta$ and hence (**) 
holds which finishes the proof of 
Lemma 1.1.













\bigskip


\centerline{\bf{2. Proof of Abel's theorem.}}

\medskip

\noindent
Without loss of generality we can assume that
$a_0=0$ and set  $S_N=a_1+\ldots+a_N$.
Given $0<r<1$ we let $f(r)=\sum\, a_nr^n$. For every positive integer $N$
the triangle inequality gives:
\[
\bigl| S_N-f(r)\bigr|\leq
\sum_{n=1}^{n=N}\, |a_n|(1-r^n)+
\sum_{n\geq N+1}\, |a_n|r^n
\]
Set $\delta(N)=\max_{n\geq N}\,\frac{|a_n|}{n}$.
Since  $1-r^n)=(1-r)(1+\ldots+r^{n-1}\leq (1-r)n$
the last sum is majorised by
\[
(1-r)\cdot \sum_{n=1}^{n=N}\, n\cdot |a_n|
+
\delta(N+1)\cdot
 \sum_{n\geq N+1}\, \frac{r^n}{n}
\]
Next, the obvious inequality 
$\sum_{n\geq N+1}\, \frac{r^n}{n}\leq\frac{1}{N+1}\cdot \frac{1}{1-r}$
gives the new majorisation
\[
(1-r)\cdot \sum_{n=1}^{n=N}\, \frac{|a_n|}{n}
+\frac{\delta(N+1)}{N+1}\cdot  \frac{1}{1-r}\tag{1}
\]
This hold for all pairs $N$ and $r$.
To each $N\geq 2$ we take $r=1-\frac{1}{N}$
and hence the right hand side in (1)
is majorised by

\[
\frac{1}{N}\cdot \sum_{n=1}^{n=N}\, \frac{|a_n|}{n}
+\delta(N+1)\cdot \frac{N}{N+1}
\]
Here both terms tend to zero as $N\to\infty$. Indeed, Abel's condition 
$\frac{a_n}{n}\to 0$   implies that
$\frac{1}{N}\cdot \sum_{n=1}^{n=N}\, \frac{|a_n|}{n}$ 
tends to zero as $N\to \infty$. Hence
we have proved the limit formula:
\[ 
\lim_{N\to\infty}\,\bigl |s_N-f(1-\frac{1}{N})\bigr|=0\tag{*}
\]
Finally it is clear that (*)  gives Abel's result.

\bigskip

\centerline{\bf{3. Proof of Tauber's theorem.}}
\medskip

\noindent
We may assume that $a_0=0$. Notice that
\[
a_n=\frac{\omega_n-\omega_{n-1}}{n}\quad\colon\, n\geq 1
\]
It follows that
\[ 
f(r)=\sum\, \frac{\omega_n-\omega_{n-1}}{n}\cdot r^n
=\sum\,\omega_n\bigl(\frac{r^n}{n}-\frac{r^{n+1}}{n+1}\bigr )
\]
Using  the equality
$\frac{1}{n}=
\frac{1}{n+1}=
\frac{1}{n(n+1)}$ we can  rewrite the right hand side as follows:
\[
\sum\,\omega_n\bigl(\frac{r^n-r^{n+1}}{n+1}+\frac{r^n}{n(n+1)}\bigr )
\]
Set
\[ g_1(r)=\sum\,\omega_n\cdot\frac{r^n-r^{n+1}}{n+1}
=(1-r)\cdot \sum\, \frac{\omega_n}{n+1}\cdot r^n
\]
By the hypothesis 
$\lim_{n\to\infty}\,  \frac{\omega_n}{n+1}=0$ and then it is
clear that we get
\[
\lim_{r\to 1}\, g_1(r)=0
\]
Since we also have $f(r)\to 0$ as $r\to 1$ we conclude that
\[
\lim_{r\to 1} \sum\, \frac{\omega_n}{n(n+1)}\cdot r^n=0\tag{1}
\]
Next, with
$b_n= \frac{\omega_n}{n(n+1)}$ we have
$nb_n= \frac{\omega_n}{n+1}\to 0$.
Hence Abel's theorem applies so (1) gives  convergent series
\[
\sum\, \frac{\omega_n}{n(n+1)}=0\tag{2}
\]
If $N\geq 1$ we have the partial sum
\[
S_N=\sum_{n=1}^{n=N} 
\, \frac{\omega_n}{n(n+1)}=
\sum_{n=1}^{n=N}, \omega_n\cdot\bigl(\frac{1}{n}-\frac{1}{n+1}\bigr)
\]
The last term becomes
\[
\sum_{n=1}^{n=N}\,\frac{1}{n}(\omega_n-\omega_{n-1})-
\frac{\omega_N}{N+1}=
\sum_{n=1}^{n=N}\,a_n-\frac{\omega_N}{N+1}
\]
Again, since
$\frac{\omega_N}{N+1}\to 0$ as $N\to\infty$ we conclude that the convergent series
from (2) implies that the series
$\sum\, a_n$ also is converges and has sum equal to zero.
This finishes the proof of Tauber's result.
\bigskip

\centerline{\bf{4. Proof of Theorem D. }}
\medskip

\noindent
Set $f(x)=\sum\, a_nx^n$ which is defined when $0<x<1$.
Notice that 
\[
(1-x)f(x)=\sum\, s_nx^n\quad\text{where}\quad s_n=a_1+\ldots+a_n
\]
Set $g(x)= \sum\, s_nx^n$ which is defined when
$0<x<1$.
Since $s_n\geq 0$ for all $n$  all the higher order derivatives
\[
g^{(p)}(x)= \sum_{n=p}^\infty\, n(n-1)\cdots (n-p+1)a_nx^{n-p}>0
\]
when $0<x<1$.
The hypothesis that
$\lim_{x\to 1}\, g(x)=A$ and Lemma 1.1 and the inductive result in the
remark after Lemma 1.2 give:
\[
\lim_{x\to 1}\, (1-x)^{\nu+2}\cdot
\sum\, s_n\cdot n^\nu x^n=(\nu+1)!\quad\colon\,\nu\geq 1\tag{1}
\]
We shall use the substitution $e^{-t}=x$ where $t>0$.
Since $t\simeq 1-x$ when
$x\to 1$ we see that
(1) gives
\[
\lim_{t\to 0}\, t^{\nu+2}\cdot 
\sum\, s_n\cdot n^\nu e^{-nt}=(\nu+1)!\quad\colon\,\nu\geq 1\tag{2}
\]
Let us put
\[ J_*(\nu,t)=\frac{t^{\nu+2}}{(\nu+1)!}\cdot 
\sum_{n=1}^\infty\, s_n\cdot n^\nu e^{-nt}
\]
So for each fixed $\nu$ one has 
\[
\lim_{t\to 0}\, J_*(\nu,t)=1\tag{3}
\]

\medskip

\noindent
Next, for each pair $\nu\geq 2$ and $0<t<1$ we define the integer
\[ 
N=\bigl[\frac{\nu-\nu^{2/3}}{t}\bigr]\tag{*}
\]
Since the sequence $\{s_n\}$ is non-decreasing we get
\[
s_N\cdot\sum_{n\geq N}\, n^\nu e^{-nt}\leq
\sum_{n\geq N}\, s_n\cdot n^\nu e^{-nt}\leq\frac{(\nu+1)!\cdot J_*(\nu,t)}{t^{\nu+2}}
\tag{i}
\]
Next,  the construction of $N$ and Lemma 1.3 give:

\[
\sum_{n\geq N}\, n^\nu e^{-nt}\geq \frac{\nu !}{t^{\nu+1}}\cdot (1-\delta(\nu))\tag{ii}
\]
where the $\delta$ function is independent of $\nu$ and
tends to zero as $\nu\to\infty$. Hence (i-ii) give
\[
s_N\leq \frac{(\nu+1)}{t}\cdot \frac{1}{1-\delta(\nu)}\cdot
J_*(\nu,t)\tag{iii}
\]
Next, by the construction of $N$ one has
\[ 
N+1\geq \frac{\nu-\nu^{2/3}}{t}=\frac{\nu}{t}\cdot(1-\nu^{-1/3})
\]
It follows that (iii) gives
\[
\frac{s_N}{N+1}\leq 
\frac{\nu+1}{\nu}
\cdot\frac{1}{1-\nu^{-1/3}}\cdot\frac{1}{1-\delta(\nu)}\cdot 
J_*(\nu,t)\tag{iv}
\]
Since $\delta(\nu)\to 0$
it follows that for any $\epsilon>0$ there exists some
$\nu_*$ such that
\[
\frac{\nu_*+1}{\nu_*}
\cdot\frac{1}{1-\nu_*^{-1/3}}\cdot\frac{1}{1-\delta(\nu_*)}<1+\epsilon \tag{v}
\]
\medskip

\noindent
Keeping $\nu_*$ fixed we now consider pairs $t_n,N$ such that
(*) above hold with $\nu=\nu_*$.
Notice that
\[
 N\to+\infty\implies t_N\to 0\tag{vi}
\]

\medskip
\noindent
It follows from (iv) and (v) that we have:
\[
\frac{s_N}{N+1}<(1+\epsilon)\cdot J_*(\nu_*,t_N)\quad\colon\, N\geq 2\tag{vii}
\]
Now (vi) and the limit in (3) which applies with
$\nu_*$ while $t_N\to 0$
entail that
\[
\lim_{N\to \infty}\, J(\nu_*,t_N)=1
\]
We have also that
$\frac{N}{N+1}\to 1$ and since $\epsilon>0$ was arbitrary
we see that (vii) proves  the inequality
\[ 
\limsup_{N\to\infty}\, 
\frac{s_N}{N}\leq 1\tag{1}
\]
So Theorem 2 follows if we also prove that
\[
\liminf_{N\to\infty}\, 
\frac{s_N}{N}\geq 1\tag{2}
\]
The proof of (II) is similar where we now define the integers $N$ by:
\[ 
N=\bigl[\frac{\nu+\nu^{2/3}}{t}\bigr]
\]
Then we have
\[ 
S_N\cdot\sum_{n\leq N}\, n^\nu e^{-nt}\geq
\frac{(\nu+1)!\cdot J_*(\nu,t)}{t^{\nu+2}}-
\sum_{n> N}\,s_n\cdot n^\nu e^{-nt}
\]
Here the last term can be estimated above since the Lim.sup
inequality (I) gives a constant $C$ such that
$s_n\leq Cn$ for all $n$ and then
\[
\sum_{n> N}\,s_n\cdot n^\nu e^{-nt}
\leq C\cdot \sum_{n> N}\,n^{\nu+1} e^{-nt}
\leq C\cdot \delta^*(\nu)\cdot 
\frac{(\nu+1)!}{t^{\nu+2}}
\]
where Lemma 1.3  entails that
$\delta^*(\nu)\to 0$ as $\nu$ increases. At the same time Lemma 1.3 also gives
\[
\sum_{n\leq N}\, n^\nu \cdot e^{-nt}=
\frac{\nu !}{t^{\nu+1}}\cdot (1-\delta_*(\nu)
\] 
where $\delta(\nu_*)\to 0$. At this stage the reader can verify that (2) 
by  similar methods as in the proof of (I).


\bigskip
\centerline{\bf{5. Proof of Theorem C}}
\medskip

\noindent
Set $f(x)=\sum\, a_nx^n$. Notice that it suffices to prove
Theorem C when
the limit value
\[
\lim_{x\to 1}\, \sum\,a_nx^n=0
\]
Next,
the assumption that $a_n\leq\frac{c}{n}$ for a constant $c$ gives
\[
f''(x)=\sum\, n(n-1)a_nx^{n-2}\leq c\sum\, (n-1)x^{n-2}=\frac{c}{1-x)^2}
\]
The hypothesis $\lim_{x\to 1}\, f(x)=0$ and Lemma xx therefore gives
\[
\lim_{x\to 1}\, (1-x)f'(x)=0\tag{i}
\]
Next, notice the equality
\[
\sum_{n=1}^\infty\, \frac{na_n}{c} x^n=
\frac{x}{c}\cdot f'(x)\tag{ii}
\]
At the same time
$\sum_{n=1}^\infty\,x^n=\frac{x}{1-x}$
and hence (i-ii)  together give:

\[
\lim_{x\to 1}\, (1-x)\cdot\sum\, (1-\frac{na_n}{c} )\cdot x^n=1
\]
Here $1-\frac{na-n}{c}\geq 0$ so Theorem 2 gives
\[
\lim_{N\to \infty}\,
\frac{1}{N} \sum_{n=1}^{n=N}\, (1-\frac{na_n}{c})=1
\]
It follows that
\[
\lim_{N\to \infty}\,\frac{1}{N} \cdot \sum_{n=1}^{n=N}\, na_n=0
\]
This means precisely that the condition in Tauber's Theorem holds and hence 
$\sum\, a_n$ converges and has series sum
equal to 0 which finishes the proof of Theorem C.











\newpage









\centerline{\bf{¤ 4. The Neumann-PoincarŽ  boundary value problem}}

\bigskip

\noindent
{\bf{Introduction.}}
Several fundamental  results were
achieved by Carl  Neumann in the article
emph{xxx} from 1877 which in particular 
solved  boundary
valued problems where  double-layer potentials occur.
The results were carried out in dimension 3 which for
physical reasons is the most relevant part. Here we 
expose 
Neumann's  theory in dimension two and give some remarks 
about the 3-dimensional case in
¤ xx.
The crucial steategy is to use Neumann's
analytic series expansions which reduces 
the proof of existence to show
 that
certain poles are absent while
meromorphic extensions of  Neumann series are constructed.
We remark that Neumann's existence results were confined to convex
domains
where
certain majorizations become straighforward since this gives rise to
positive integral kernels. The
extension of Neumann's results to general domains was
achieved by PoincarŽ in the article \emph{xxx} from 1897
where some ingenoius new methods were introduced to overcome
the failure of positivity for the
non-symmetric kernel defining the double-layer potential.
\medskip

\noindent
The smoothness of boundaries
was  relaxed in later work.
Existence results for planar domains where
isolated corner points are allowed were 
established by Zarmela in 1904.
Further studies 
of Neumann's  problem for planar domains with non-regular boundary
appear 
in Carleman's thesis from 1916.
A novelty in this work is that solutions to the Neumann's
boundary value problem also are exhibited for functions which only 
are  integrable on the boundary.
This leads to new phenomena for the spectrum of
•ntegral operators, i.e the spectrum 
is not always  confined to discrete subsets of the
complex $\lambda$-plane.  It will take us too far to
go into  details, especially in the delicate analysis from Part 3 in
[ibid]. The interested reader can also consult  the expositary
article
\emph{xxxx} by Holmgen which describes how non-discrete spectral can occur 
for integral kernels associated to the Neumann problem
which in those days  was a  new phenomenon in operator theory.
Let us now expose the methods introduced by Neumann and PoincarŽ.

\bigskip

\noindent
{\bf{Preliminaries.}}
Let $\mathcal C$ be a closed Jordan curve of class $C^2$ whose 
arc-lengt measure is denoted by $\sigma$.
If  $g$ is a continuous function on
$\mathcal C$ the logarithmic  potential
\[
U_g(z)=
\frac{1}{\pi}\int_{\mathcal C}\, \log\,\frac{1}{|z-q|} \cdot g(q)\, d\sigma(q)
\]
yields a harmonic function
in open the complement of  $\mathcal C$. 
Since $\log\,|z|$ is locally integrable in
${\bf{C}}$ and  $U_g(z)$  the convolution of
this log-function and the compactly supported Riesz measure
$g\cdot \sigma$. By elementary measure theory
this implies
that $U_g$ extends to a continuous function.
In particular  the pair of harmonic functions in the 
inner respectively outer component of $\mathcal C$ are equal
on $\mathcal C$.
Moreover,  
the  Laplacian of $U_g$ taken in the distribution sense is equal to
the measure $g\cdot\sigma$.
Now we consider partial derivatives of $U$
and  study the inner normal derivative as $z$ approaches points
$p\in\mathcal C$ from the inside.
Let ${\bf{n}}_*$ denote the inner normal derivative
along $\mathcal C$ which gives
the function  on $\mathcal C$ defined by:
\[
p\mapsto \frac{\partial U_g}{\partial {\bf{n}}_*}(p)
\]
With  $p\neq q$ we have
the vector $p-q$. We  take its inner product with
the unit vector
${\bf{n}}_*(q)$ and set
set
\[ 
K(p,q)=
\frac{\langle p-q,{\bf{n}}_*(q)}{|p-q|^2}\tag{*}
\]
\medskip


\noindent
Let  analyze the behaviour of $K$ close to a point on
the diagonal.
Working in local coordinates we can take $p=q=(0,0)$ and close 
the this boundary point 
the $C^2$-curve $\mathcal C$ is locally defined by a function
\[ 
y=f(x)
\] 
where $\phi(x)$ is a $C^1$-function and 
the $(x,y)$ belong to the bounded Jordan domain when
$y>f(x)$.
By drawing a figure the reader can verify that
\[
{\bf{n}}_*(x,f(x))\cdot d\sigma=(-f'(x), 1)\dot dx
\]
So with $p=(t,f(t))$ and $q=(x,f(x))$ we have

\[
K(p,q)\cdot d\sigma(q)=
\frac{f(t)-f(x)- f'(x)(t-x)}{(t-x)^2+(f(t)-f(x))^2}\cdot dx
\]
By hypothesis $f$ is of class $C^2$ which implies that
the right hand side stays bounded as $y$ and $x$ independently
of each other approach zero.
This eanble us to construct
integrals and  Green's formula yields:

\medskip

\noindent
{\bf{0.1 Theorem.}}
\emph{For each $p\in\mathcal C$ one has }

\[
\frac{\partial U_g}{\partial {\bf{n}}_*}(p)=
 g(p)+\int_{\mathcal C}\, K(p,q)\cdot g(q)\,d\sigma(q)
 \]
 \medskip
 
 \noindent
 {\bf{Exercise.}} Prove this equality.
A hint is by additivity it suffices to take $g$-functions with 
supports confined to small sub-intervals of $\mathcal C$ and profit upon
local coordinates and  parametrizations as above for 
$\mathcal C$ close to the support of $g$.


\bigskip


\centerline {\bf{1. Neumann's boundary value problem.}}
\bigskip

\noindent
Let $\Omega$ be a bounded domain
where $\partial\Omega$ consists of a finite set of closed Jordan
curves of class $C^2$. 
Let $h$ and $f$
be a pair of real-valued continuous functions on
$\partial\Omega$ where  $h$ is positive.
We seek a function $U$ which is harmonic in $\Omega$
and on the boundary satisfies
\[
\frac{\partial U}{\partial {\bf{n}}_*}(p)=
 h(p)U(p)+ f(p)\tag{*}
\]
\medskip

\noindent
{\bf{1.1 Theorem.}}
\emph{The boundary value problem
above has a unique solution $U$.}

\medskip

\noindent
The uniqueness amounts to show that if $V$ is harmonic in $\Omega$ and
\[
\frac{\partial V}{\partial {\bf{n}}_*}(p)=
 h(p)V(p)
 \] 
 holds on $\partial\Omega$, then $V=0$.
Since 
$h$ is  positive 
this follows from  ¤ XX: Chapter V.
\medskip

\noindent 
\emph{Proof of existence.}
For each $g\in C^0(\partial \Omega)$ we construct 
$U_g$
which by Theorem 0.1 solves (*)  if
the $g$  satisfies the integral equation
\[
g(p)+\int_{\mathcal C}\, K(p,q)\cdot g(q)\,d\sigma(q)=
h(p)\cdot \frac{1}{\pi}\cdot\int_{\partial\Omega}\, \log\,\frac{1}{|p-q|}\cdot g(q)\,d\sigma(q)
+f(p)\tag{1}
\]
With $h$ kept fixed we introduce the kernel
\[ 
K_h(p,q)=h(p)\cdot \frac{1}{\pi}\cdot\log\, \frac{1}{|p-q|}- K(p.q)
\]
and  (1) reduces to the equation
\[
g(p)-\int_{\partial\Omega}\,K_h(p,q) g(q)\,d\sigma(q)= f(p)\tag{2}
\]
\medskip
Define the linear operator on
the Banach space $C^0(\partial\Omega)$
defined by
\[ 
\mathcal K_h(g)=\int_{\partial\Omega}\,K_h(p,q) g(q)\,d\sigma(q)
\quad\colon\quad
g\in C^0(\partial\Omega)\tag{3}
\]
With this notation a $g$-function satisfies (2) if
\[
(E-\mathcal K_h)(g)=f\tag{4}
\] 
where $E$ is the identity operator on
$C^0(\partial\Omega)$.
Next, from the general result in ¤¤ 
$\mathcal K_h$ is a compact linear operator.
By  
another general result from ¤ xx it follows that each 
$f\in C^0(\partial\Omega)$
yields a meromorphic function of the complex parameter
$\lambda$ given  by
\[ 
N_f(\lambda)=
f+\sum_{n=1}^\infty\, \lambda^n\cdot \mathcal K_h^n(f)
\]
If $\delta>0$ is so small that
$||\mathcal K_h||<\delta^{-1}$ it is clear that
\[
(E-\lambda \mathcal K_h)(N_f(\lambda))=f\tag{5}
\]
By analyticity (5) reamins valied when $\lambda$ stays outside the
poles of   $N_f(\lambda)$.
In particular,  if  no pole occurs at $\lambda=1$ we have the equation
\[
(E-\mathcal K_h)(N_f(1)=f
\] 
This  means that $g=N_f(1)$
solves (4) and the existence part  in Theorem 1.1 follows.
So there remains only to show:
\medskip

\noindent
\emph {The absence of a pole at $\lambda=1$.}
If $N_f(\lambda)$ has a pole at $\lambda=1$
there is a positive integer $m$ such that 
\[ 
N_f(\lambda)=
\sum_{k=1} ^{k=m}\, \frac{a_k}{(1-\lambda)^k}+ b(\lambda)
\] 
hold when $|\lambda-1|$ is small where $a_m\neq 0$ in 
$C^0(\partial\Omega)$
and $b(\lambda)$ is analytic in some disc centered at $\lambda=1$.
It follows that
\[
(1-\lambda)^m N_f(\lambda)=a_m+(1-\lambda)\beta(\lambda)
\] 
where 
$\beta(\lambda)$ again is an analytic $C^0(\partial\Omega)$-valued function
close to 1.
Apply $E-\lambda \mathcal K_h$ on both sides which gives
\[
(1-\lambda)^m (E- \lambda\mathcal K_h)(N_f(\lambda))
=(E-\lambda \mathcal K_h)(a_m)+(1-\lambda)
(E-\lambda \mathcal K_h)(\beta(\lambda))
\]
By (5) the left hand side is equal to $(1-\lambda)^m f$. So 
with $\lambda=1$  we get
\[
(E-\mathcal K_h)(a_m)=0\implies
a_m=\mathcal K_h(a_m)
\]
This  contradicts  the uniqueness part which already has been proved.



\bigskip

\centerline{\bf{2. The case when
$\mathcal C$ has corner points.}}

\bigskip


\noindent
In the preceeding section we  found a unique solution to 
Neumann's boundary problem where
the inner normal derivative of $U$
along $\partial\Omega$ is a continuous function.
If corner points appear 
this will no longer be true. But 
stated in an appropriate way we can extend
Theorem 1.1.
Let us analyze the specific case when
the boundary curves are piecewise linear, i.e. each
closed Jordan curve in
$\partial\Omega$
is a simple polygon with a finite number of corner points.
Given one of these we begin to study the
$K$-function.
Let $\xi_1,\ldots,\xi_N$ be the corner points on
$\mathcal C$.
On the linear interval $\ell_i$ which joints two succescive
corner
points $\xi_i$ and $\xi_{i+1}$ we notice that
${\bf{n}}_*$ is constant and it is even true that
\[ 
K(p,q)=0\quad\colon\quad p,q\in \ell_i
\]
Indeed, this is obvious for if $p$ and $q$ both belong to$\ell_i$ then
the vector $p-q$ is parallell to $\ell_i$ and hence $\perp$ to
the normal of this line.
Next, keeping $q$ fixed on the open interval $\ell_i$
while $p$ varies on $\mathcal C\setminus \ell_i$
the behaviour of the function
\[ 
p\mapsto \langle p-q,{\bf{n}}_*(q)\rangle
\] 
is can be understood via a picture and it is
clear that (x) is a continuous function.
By a picture the reader should discover the different behaviour in the case
when $\mathcal C$ is convex or not.
For example, in the non-convex case it is in general not true 
that $\mathcal C\setminus \ell_i$
stays in the half-space bordered by the line passing $\ell_i$ and then
(*) can change sign, i.e. take both positive and negative values.
In the special case when
$\mathcal C$ is a convex polygon the reader should confirm that
(x) is a positive function of $p$ because we have taken the
\emph{inner} normal 
${\bf{n}}_*(q)$.
\medskip


\noindent
{\bf{2.1 Local behaviour at a corner point.}}
After a linear change of coordinates
we take a corner point $\xi_*$ placed at the origin
and one $\ell$-line is defined by
the equation $\{y=0\}$ to the left of $\xi_*$ where
$x<0$ while $y=Ax$ hold to the right for some $A\neq 0$.
If $A>0$ it means that
the angle $\alpha$ at the corner point is detemined by
\[ 
\alpha=\pi-\text{arctg}(A)
\]
If $A<0$ the inner angle is between 0 and $\pi/2$
which the reader should illustrate by a picture.
Next, consider
a pair of points $p=(-x,0)$ and $q=(t,At)$
where $x,t>0$. So $p$ and $q$ belong to opposite sides of the
corner point.
To be specific, suppose that $A>0$ which entails that
\[ 
{\bf{n}}_*(q)=\frac{(-A,1)}{\sqrt{1+A^2}}\implies
\]
\[
K(p,q)\cdot d\sigma(q)=  \frac{Ax+t}{(x+t)^2+A^2t^2}
\]
When $x$ and $t$ decrease to the origin the order of magnitude 
is
$\frac{1}{x+t}$ so the kernel function is unbounded
and the order of magnitude is $\frac{1}{x+t}$.
If $\ell_+$ denotes the boundsry interval to the right of the origin
where $q$ are placed we conclude that
\[
\int_{\ell_+}\, K(p,q)\cdot d\sigma(p)\simeq
\int_0^1\, \frac{dt}{x+t}\simeq \log\,\frac{1}{x}
\]
The last function is integrable with respect to $x$. This local computation shows
that the kernel function $K$ is not too large in 
the average. In particular
\[
\iint_{\mathcal C\times\mathcal C}\,
|K(p,q)|\cdot d\sigma(p)d\sigma(q)<\infty
\]
But
the
growth of $K$ near corner points prevail 
a finite $L^2$-integral, i.e. the reader may verify that
\[
\iint_{\mathcal C\times\mathcal C}\,
|K(p,q)|^2\cdot d\sigma(p)d\sigma(q)=+\infty
\]
\medskip


\noindent
{\bf{2.2 The integral operator $\mathcal K_h$}}.
Let $h$ be a positive continuous function on
$\partial\Omega$.
Now we define the kernel function $K_h(p,q)$ exactly as in
¤ xx and obtain the corresponding
linear operator
\[ 
g\mapsto\int_{\partial\Omega}\, K_h(p,q)g(q)d\sigma(q)
\]
It has a natural domain of definition.
Namely,  introduce the space
$L^1_*$ which consists of functions on $g$
on $\partial\Omega$ for which
\[
\iint\, \log\frac {R}{|p-q|}\cdot |g(p)|\cdot d\sigma(q)d\sigma(p)<\infty\tag{*}
\] 
where  $R>0$ is so large that
$\frac{R}{|p-q|}>1$  hold for  pairs $p,q$ on $\partial\Omega$.
Return to the local situation in
(xx) and consider a $g$-function in  $L^1_*$. Locally 
we encounter an integral of the form
\[
\iint_{\square_+}\, \frac{1}{x+t}\cdot |g(t,At))|\, dt
\]
where $0\leq x,t\leq 1$ hold in
$\square_+$.
In this double integral we first perform integration with respect to $x$
which is finite since the inclusion $g\in L^1_*$ entails that
\[
\int_0^1\,\log\,\frac{1}{t}\cdot |g(t,At)|\, dt<\infty
\]


\noindent
From the above we obtain the following:

\medskip

\noindent
{\bf{2.3 Theorem.}}
\emph{The kernel function $K_h$ yields a continuous linear operator from
$L^1_*$ into $L^1(\partial\Omega)$, i.e. there exists a constant
$C$ such that}
\[
\int_{\partial \Omega} |\mathcal K_h(g)|\cdot d\sigma
\leq C\cdot 
\iint
_{\partial \Omega\times \partial \Omega} 
\, \log\frac {R}{|p-q|}\cdot |g(p)|\cdot d\sigma(q)d\sigma(p)
\]
\bigskip

\noindent
Armed with Theorem 2.3 
we can solve Neumann's boundary value problem for domains 
whose boundary curves are polygons.

\medskip
\noindent
{\bf{2.4 Theorem.}}
\emph{For each $f\in L^1(\partial\Omega$
there exists
a unique harmonic function $U$ in $\Omega$ such that}
\[
\frac{\partial U}{\partial {\bf{n}}_*}(p)=
 h(p)U(p)+ f(p)
\]
holds on $\partial \Omega$. Moreover, $U=U_g$ where
$g\in L^1_*$ solves the integral equation
\[
g-\mathcal K_h(g)=f
\]



\noindent
\emph{The uniquenss part.}
At corner points the inner normal of $U$ has no limit and
to establish the uniqueness part we use  instead
an integral formula:


\medskip

\noindent{\bf{2.5 Proposition.}}
\emph{For each $g\in L^1_*$ the potential function $U=U_g$ satisfies}

\[
\iint_\Omega\ [
(\frac{\partial U}{\partial x})^2
+(\frac{\partial U}{\partial y})^2]\, dxdy+
\int_{\partial\Omega}\, U\cdot 
\frac{\partial U}{\partial {\bf{n}}_*}\,
d\sigma=0
\]
\medskip


\noindent
{\bf{Exercise.}} Prove this result.

\medskip 

\noindent
The requested uniqueness follows. For if
$\frac{\partial U}{\partial {\bf{n}}_*}= h\cdot U$
holds on the boundary we get 

\[
0=\iint_\Omega\ [
(\frac{\partial U}{\partial x})^2
+(\frac{\partial U}{\partial y})^2]\, dxdy=\int_{\partial\Omega}\, 
h\cdot U^2\,
d\sigma\implies g=0
\] 
\medskip

\centerline
{\emph{2.6 Proof of existence.}}
\medskip

\noindent
It  is carried out by the same mehod as in
¤ X. The crucial  point is  that
the kernel function $K_h$ is sufficiently well-behaved in order that
every $f\in L^1(\Omega)$
yields a meromorphic function $N_f(\lambda$
where $\mathcal K_h$-powers are applied to $f$ exactly as in XX.
\medskip


\noindent
{\bf{Exercise.}} Supply details which prove that
$N_f(\lambda)$ is meromorphic.
\medskip


\noindent
{\bf{Remark.}}
In [Carleman: Part 3] it is proved that
the unique solution $g$ to the integral equation
is represented in a canonical fashion using a certain orthonormal family of functions with 
respect to the $L^2$-function $\log\,\frac{1}{|p-q|}$ 
wtih respect to the product measure $\sigma\times\sigma$. Moreover, there exists
a representation formula expressed by convergent series for the inhomogenous
equation
\[ 
g+\lambda\cdot \mathcal K_h(g)=f
\] 
where poles of $N_f(\lambda)$ are taken into the account.



BRA


\newpage


\centerline{\bf{¤ 5. A Non-Linear PDE-equation}}

\bigskip

\noindent
{\bf{Introduction.}}
In the  article
\emph{†ber eine nichtlineare Randwertaufgabe bei der Gleichung $\Delta u=0$}
(Mathematisches Zeitschrift vol. 9 (1921),
Carleman considered
the following 
equation: Let
$\Omega$ be a bounded domain in ${\bf{R}}^3$
with $C^1$-boundary and
${\bf{R}}^+$ the non-negative real line where  $t$ is the coordinate.
Let $F(t,p)$
be a real-valued and continuous function
defined on  ${\bf{R}}^+\times\partial\Omega$.
Assume that 
\[
t\mapsto F(t,p)\tag{0.1}
\]
is strictly increasing  for every $p\in\partial\Omega$
and that $F(0,p)\geq 0$. Moreover,  
\[
\lim_{u\to\infty} F(t,p)=+\infty\tag{0.2}
\] 
holds uniformly with respect to $p$.
For a given point $q_*\in\Omega$ we seek a function $u(x)$
which is harmonic in $\Omega\setminus\{q_*\}$
and at $q_*$ it is locally $\frac{1}{|x-q_*|}$ plus a harmonic function.
Moreover, it is requested that
$u$
extends to a continuous function on
$\partial\Omega$ and that $u\geq 0$ in $\overline{\Omega}$.
Finally, along  the boundary
the  inner normal derivative $\partial u/\partial n$ satisfies the 
equation
\[
\frac{\partial u}{\partial n}(p)= F(u(p),p)\quad \colon p\in\partial\Omega\tag{*}
\]

\medskip

\noindent 
{\bf{Remark.}}
The case when $F(t,p)= kt^4$ for some positive constant $k$
means that we regard the Stefan-Boltzmann equation whose
physical 
interpretation 
ensures that
(*) has a unique non-negative solution $u$.


\medskip

\noindent {\bf {Theorem.}}
\emph{For each $F$  satisfying (0.1-0.2)
 the boundary value problem has a unique solution $u$.}
\medskip

\noindent
The strategy in the  proof is to consider
a family of boundary value problems where 
one for each
$0\leq h\leq 1$ seeks $u\uuu h$ to satisfy
\[
\frac{\partial u\uuu h}{\partial n}(p)=(1\vvv h)u\uuu h+ h\cdot  F(u\uuu h(p),p)\quad \colon p\in\partial\Omega\tag{*}
\]
and $u\uuu h$ has the same pole as $u$ above.
Let us begin  with
\medskip

\noindent
{\bf{0.1 The case $h=0$}}.
Here we seek $u_0$ so that
\[
\frac{\partial u_0}{\partial n}(p)=u_0\tag{i}
\]
If $G(p)$ is  the Greens' function with a pole at
$q_*$ we seek a harmonic
function $h$ in
$\Omega$ such that
\[ 
u_0=G-h\tag{ii}
\] 
Since $G(p)=0$ on  $\partial\Omega$, the equation (i) holds if
\[
\frac{\partial h}{\partial n}(p)=h(p)+
\frac{\partial G}{\partial n}(p)\quad\colon\, p\in \partial\Omega\tag{iii}
\]
This is a classic linear boundary value problem which
has a unique solution $h$. See ¤ xx for further details.
\medskip


\noindent
{\bf{0.2 Properties of $u_0$.}}
The construction in (ii) entails
that  $u_0$ is superharmonic in $\Omega$ and therefore attains its
minimum on the boundary.
Say that
\[ 
u_0(p_*)=\min_{p\in\overline{\Omega}}\, u_0(p)
\]
It follows that
$\frac{\partial u_0}{\partial n}(p_*)\geq 0$
and the equation
(i) gives
\[
u_0(p_*)\geq 0
\]
Hnece our  unique  solution $u_0$ is non-negative.
We can say more. For consider the harmonic function
$h$ in (ii) which takes a maxium  at some $p^*\in\partial\Omega$.
Then
$\frac{\partial h}{\partial n}(p^*)\leq 0$ so that (iii) gives
\[
h(p^*)+\frac{\partial G}{\partial n}(p^*)\leq 0
\]
Hence
\[ 
\max_{p\in\partial\Omega}\, h(p)\leq
-\frac{\partial G}{\partial n}(p^*)
\]
which entails that
\[
\min_{p\in\partial \Omega}\, u(p)=
-\max_{p\in\partial\Omega}\, h(p)\geq
\frac{\partial G}{\partial n}(p^*)\tag{0.2.1}
\]
Here the function
\[
p\mapsto \frac{\partial G}{\partial n}(p)
\] 
is continuous and positive on
$\partial\Omega$ and if $\gamma_*$ is the minimum value we conclude that
\[
\min_{p\in\partial \Omega}\, u(p)\geq \gamma_*\tag{0.2.2}
\]
Next, let $h$ attain its minimum at some $p_*\in\partial\Omega$
which entails that
$\frac{\partial h}{\partial n}(p_*)\geq 0$ and then (iii) gives
\[
h(p_*)+\frac{\partial G}{\partial n}(p^*)\geq 0
\]
It follows that
\[
\max_{p\in\partial \Omega}\, u_0(p)=
\min_{p\in\partial \Omega}\, h(p)=-h(p_*)\leq 
\frac{\partial G}{\partial n}(p^*)\leq\gamma^*\tag{0.2.3}
\]
where
\[
\gamma^*=\max_{p\in\partial \Omega}\,
\frac{\partial G}{\partial n}(p)\tag{0.2.4}
\]
So the unique solution $u_0$ in (i) satisfies
\[
\gamma_*\leq u(p)\leq \gamma^*
\quad\colon p\in\partial\Omega\tag{0.2.5}
\]
where the  positive constants $\gamma_*$ and $\gamma^*$ depend on
the  point $q_*\in\Omega$ and the given domain $\Omega$.


\bigskip


\noindent
{\bf{The homotopy method.}}
To proceed from $h=0$ to $h=1$
the idea is to use a "homotopy argument"
which can be   handled via 
precise estimates of solutions to Neumann's linear
boundary value problem
which are presented in ¤ B.
Thanks to this and some uniquness properties in ¤ A below, 
the reduction to the case when
$F$ is real-analytic
is relatively easy. The ciucial steps during the  proof appear
in ¤ C where we
carry out a  "homotoy method" to
get solutions in (*) as $h$ increases from zero to one.



\bigskip


\centerline {\bf{A.0. Proof of uniqueness.}}
\medskip

\noindent
Suppose that $u_1$ and $u_2$ are two solutions to the equation in the main theorem.
Notice that  $u_2-u_1$.
is harmonic in
$\Omega$.
If $u\uuu 1\neq u\uuu 2$ we may
without loss of generality we may assume that
the maximum of $u\uuu 2\vvv u\uuu 1$ is $>0$.
The maximum is attained at some $p\uuu *\in\partial\Omega$
and  the strict maximum principle for harmonic functions gives:
\[
u\uuu 2(x)\vvv u\uuu 1(x)<
u\uuu 2(p\uuu *)\vvv u\uuu 1(p\uuu *)\tag{i}
\] 
for all $x\in\Omega$.With $v=u\uuu 2\vvv u\uuu 1$
we have
\[
\frac{\partial v}{\partial n}(p)=F(u_2(p),p)-F(u_1(p),p)
\]
Here (0.1) entails that
$\frac{\partial v}{\partial n}(p\uuu *)>0$
and since we have an inner normal derivative this violates
(i) which proves the uniqueness.


\medskip



\centerline {\bf{A.1 Montonic properties.}}
\medskip


\noindent
Let $F_1$ and $F_2$ be two functions which both satisfy
(0.1) and (0.2) where  
\[ 
F_1(u,p)\leq F_2(u,p)
\]
hold for all $(u,p)\in{\bf{R}}^+\times\partial\Omega$.
If $u_1$, respectively $u_2$ solve (*) for $F_1$ and $F_2$
it follows that
$u_2(q)\leq u_1(q)$ for all $q\in\Omega$.
To see this we set $v=u_2-u_1$ which is harmonic in
$\Omega$.
If $p\in\partial\Omega$ we get
\[
\frac{\partial v}{\partial n}(p)=F_2(u_2(p),p)-F_1(u_1(p),p)\geq 0\tag{i}
\]
Suppose that the maximum of $v$ is $>0$ and let the maximum be attained at some 
point $p_*$. Since (i) is an inner normal it follows that we must have
$0=\frac{\partial v}{\partial n}(p)$ which would entail that

\[ 
F_2(u_2(p_*)p_*)>F_2(u_1(p_*),p_*)\geq F_1(u_1(p_*),p_*)\implies
\]
and this contradicts the strict inequality
$u\uuu 2(p\uuu *)>
u\uuu 1(p\uuu *)$
since we have an increasing function in (0.1).





\medskip


\noindent
{\bf{A.2. A bound for the maximum norm.}}
Let $G$ be the Green's function which has a pole
at $q_*$ while $G=0$ on $\partial\Omega$. Then
\[ 
p\mapsto
\frac{\partial G}{\partial n}(p)
\]
is a continuous and positive function on
$\partial\Omega$.
Set
\[
m_*=\min_{p\in\partial\Omega}\, \frac{\partial G}{\partial n}(p)
\quad\colon
m^*=\max_{p\in\partial\Omega}\, \frac{\partial G}{\partial n}(p)
\]
Next, let $0\leq h\leq 1$ and suppose that
$u_h$ is  a solution to (*). Put

\[
m(h)= \min_{p\in\partial\Omega} u_h(p)
\quad\colon
M(h)= \max_{p\in\partial\Omega} u_h(p)\tag{*}
\]
To estimate these numbers
we proceed as follows.
Choose
$p^*\in\partial\Omega$
such that
\[
 u_h(p^*)=M(h)\tag{1}
\]
Now the function 
\[
H=u-G-M(h)
\] 
is  harmonic function in
$\Omega$ and non-negative on the boundary.
Hence $H$ is positive in $\Omega$ and since $H(p^*)=0$
we have
\[ 
\frac{\partial H}{\partial n}(p^*)\leq 0\implies
\] 
which via the equation (*) give
\[
(1-h)M(h)+h\cdot F(M(h),p^*)\leq
\frac{\partial G}{\partial n}(p^*)\leq \gamma^*\tag{2}
\]
Next, the hypothesis on $F$ entails that
\[
t\mapsto (1-h)t+h\cdot F(t,p^*)\tag{3}
\]
is a strictly increasing function for each
fixed $0\leq h\leq 1$
and the hypothesis (0.2) together with the
inequality (2) above, give
a positive constant
$A^*$ which is independent of $h$ such that
\[
M(h)\leq A^*\quad\colon 0\leq h\leq 1\tag{3}
\]

\medskip


\noindent
Next, let $m(h)$ be the minimum of $u_h$ on $\partial\Omega$ and
this time we consider the harmonic function
\[
H=u-m(h)-G
\]
Here $H\geq 0$ on $\partial\Omega$
and if $u_h(p_*)=m(h)$ we have $H(p_*)=0$
$p_*$ is a minimum for $H$.
It follows that
\[ 
\frac{\partial H}{\partial n}(p_*)\geq 0\implies
F(u(p_*),p)=\frac{\partial u}{\partial n}(p_*)\geq 
\frac{\partial G}{\partial n}(p_*)
\]
So with
\[
\gamma_*=\min_{p\in\partial\Omega}\,\, \frac{\partial G}{\partial n}(p)
\]
one has the inequality
\[
F(m(h),p^*)\geq \gamma_*\tag{4}
\]
Above $\gamma^*$ is the constant from (xx) and the properties of $F$
give a positive constant $A_*$ such that
\[
m(h)\geq A_*
\]





\noindent
{\bf{Conclusion.}} Above $0<A_*<A^*$ are  constants which are independent of $h$.
Hence the maxima and the minima of
$u_h$ stay in a fixed interval $[A_*,A^*]$ as soon as 
$u_h$ exists.



\bigskip


\noindent
\centerline {\bf{B. The  linear equation.}}

\medskip


\noindent
Let $f(p)$ and $W(p)$
be a pair of continuous functions on the boundary
$\partial \Omega$ where  $W$ is positive, i.e. $W(p)>0$ for every
boundary point.
Set
\[
w_*=\min_p \, W(p)
\]
So by the assumption on  $W$ we have
$w_*>0$. 
The classical Neumann
theorem
asserts  that there exists a unique function $U$ which is harmonic in
$\Omega$, extends to a continuous function on
the closed domain and its inner normal  derivative satisfies:
\[ 
\partial U/\partial n(p)=
W(p)\cdot U(p)+f(p)\quad p\in\partial\Omega\tag{1}
\] 
For the unique   solution in (1)  some  estimates hold.
Namely, set 
\[
M^*=\max_p\, U(p)\quad\text{and}\quad
m_*=\min_p\, U(p)
\] 

\medskip

\noindent
Since $U$ is harmonic in $\Omega$ 
the  maximum and the minimum are both taken on the boundary.
If $U(p^*)= M^*$ for some $p^*\in\partial \Omega$
we have $\partial U/\partial n(p^*)\leq 0$ which together with
(1) entails that
\[
M^*\cdot W(p^*)+f(p^*)\leq 0\implies
M^*\leq  \frac{|f|_{\partial\Omega}}{w_*}
\]
where
$|f|_{\partial\Omega}$ is the maximum norm of $f$ on the boundary.
In the same way one verifies that
\[
m_U\geq -\frac{|f|_{\partial\Omega}}{w_*}
\]
Hence  the following inequality holds for the
 the maximum norm  $|U|_{\partial\Omega}$ :
\[
|U|_{\partial\Omega}\leq
\frac{|f|_{\partial\Omega}}{w_*}\tag{B.0}
\]
Notoice that
(B.0) and the equation (1)
entails that
Suppose that $W\in C^0(\partial\Omega)$ satisfies
\[ 
w_*\leq W(p)\leq w^*
\]
for a pair of positive constants.
If $|f|_{\partial\Omega}$ is the maximum norm of
$f$ it follows from (B.0) that
\[
\bigl|W(p)\cdot U(p)+f(p)\bigr|\leq (1+\frac{w^*}{w_*})\cdot
|f|_{\partial\Omega}
\]
Hence the equation (1) gives
\[ 
\max_{p\in\partial\Omega}\,|\frac{\partial U}{\partial n}(p)|
\leq (1+\frac{w^*}{w_*})\cdot |f|_{\partial\Omega}
\tag{B.1}
\]


\noindent
{\bf{B.2 An estimate for first order derivatives.}}
Let $p\in\partial \Omega$ and denote by $N$
the inner normal at $p$. Since $\partial\Omega$ is of class $C^1$
a sufficiently small line segment from $p$ along
$N$ stays in $\Omega$. So for small positive $\ell$ we have
points $q=p+\ell \cdot N$ in $\Omega$ and 
take the directional derivative of $U$ along $N_p$.
This gives  a function
\[
 \ell\mapsto \partial U/\partial N(p+\ell\cdot N)
\]
Since the boundary is $C^1$
these functions are defined on a fixed interval $0\leq\ell\leq \ell^*$ for all 
boundsry points $p$.
A classic result which appears in 
\emph{Der zweite 
Randwertaufgabe}  gives  a constant
$B$ such
that 
\[
\bigl|\partial U/\partial N(p+\ell\cdot N)\bigr|\leq B\cdot 
\max_{p\in\partial\Omega}\,|\frac{\partial U}{\partial n}(p)|
\]
hold for all
$p\in\partial\Omega$ and
$0\leq \ell\leq \ell^*$.

\bigskip


\centerline {\bf{C. Proof of Theorem when $t\mapsto F(t,p)$ is analytic.}} 

\medskip

\noindent
Assume that $t\mapsto F(t,p)$ is a real-analytic function on
the positive real axis for each $p\in\partial\Omega$
where local power series converge uniformly with respect to $p$.
In this situation we shall  prove
the
\emph{existence} of  a solution $u$ in the Theorem.
To attain this
we  proceed as follows.
To each real number $0\leq h\leq 1$ we seek a solution $u_h$ where
\[
 \frac{\partial u_h}{\partial n}(p)= h\cdot F(u_h,p)+(1-h)\cdot u_h(p)\tag{1}
\]
When  $h=0$ we found the solution $u_0$ in ¤ xx.
Next, suppose that $0\leq h_0<1$ and that we have found the 
solution $u_{h_0}$ to (1).
By
the result in ¤ B there exists
 a pair of positive constants $A_*<A^*$ such that
\[
 A_*\leq u_{h_0}(p)\leq A^*\tag{*}
 \]
 which are independent of $h_0$ and of $p$.
\medskip

\noindent
Set $u_0=u_{h_0}$
and
with $h=h_0+\alpha$ for some small $\alpha>0$
we shall find  $u_h$ by a series
\[
u_h= u_{h_0}+\sum_{\nu=1}^\infty\, \alpha^\nu\cdot u_\nu\tag{2}
 \]

 
\noindent
The pole at $q_*$  occurs already in $u_0$. So 
$u_1,u_2,\ldots$ is   a sequence of 
harmonic functions in  $\Omega$ and  there remains to find them
so that
$u_h$  solves (1). We will  show that this can
be achieved when $\alpha $ is sufficiently small.
Keeping $h_0$ fixed we set
\[
 u_0=u_{h_0}
\]
The analyticity of $F$ with respect to $t$ gives 
for every $p\in\partial\Omega$ a series expansion
\[
 F(u_0(p)+\alpha,p)=
F(u_0(p),p)+\sum_{k=1}^\infty\, c_k(p)\cdot \alpha^\nu
 \tag{3}
 \]


\noindent
where $\{c_k(p)\}$ are continuous functions on
 $\partial\Omega$.
Here (*) and  
the hypothesis on $F$ entail that
the radius of convergence has a uniform bound below, i.e.
there exists $\rho>0$ which is independent of $p\in\partial\Omega$
and a constant $K$ such that
\[
\sum_{k=1}^\infty\, |c_k(p)|\cdot \rho^k\leq K\tag{4}
\] 
Now
the equation (1) can be  solved 
via a system of equations where the  harmonic functions
$\{u_\nu\}$ are determined inductively
while $\alpha$-powers are identified.
The linear
$\alpha$-term gives  the equation
\[
\frac{\partial u_1}{\partial n}=F(u_0(p),p)-u_0(p)+
(1-h_0)u_1+h_0\cdot c_1(p)\cdot u_1(p)\tag{i}
\]
\medskip


\noindent
For $u_2$ we find that
\[
\frac{\partial u_2}{\partial n}=(1-h_0)u_2-u_1+h_0c_1(p)u_2+
c_1(p)u_1+c_2(p)u_1^2\tag{ii}
\]
\medskip

\noindent
In general we have
\[
\frac{\partial u_\nu}{\partial n}=(1-h_0+h_0\cdot c_1(p))\cdot u_\nu+
R_\nu(u_0,\ldots,u_{\nu-1},p)\quad\colon\, \nu\geq 1
\tag{iii}
\] 
where $\{R_\nu\}$ are polynomials in the preeceding $u$-functions
whose coefficients are
continuous functions obtained from
the
$c$-functions.
The function $c_1(p)$ is given by

\[ 
c_1(p)= \frac{\partial F}{\partial t}(u_0(p),p)
\]
which by  the hypothesis on $F$ is a
positive continuous function on $\partial\Omega$.
It follows that the function
\[ 
W(p)= (1-h_0)+h_0\cdot c_1(p)\tag{iv}
\] 
also is positive on $\partial\Omega$ and 
in the recursion above we have
\[
\frac{\partial u_\nu}{\partial n}=W(p)\cdot
u_\nu(p)+
R_\nu(u_0,\ldots,u_{\nu-1},p)\quad\colon\, \nu=1,2,\ldots
\tag{v}
\]

\medskip

\noindent
Above we encounter linear equations exactly as in (B.0) where the
the $f$-functions are  the $R$-polynomials.
Put

\[ 
w_*=\min_{p\in\partial\Omega}\, W(p)
\]
From ¤ B.XX we get

\[
|u_\nu|_{\partial\Omega}\leq w_*^{-1}\cdot 
|R_\nu(u_0,\ldots,u_{\nu-1},p)|_{\partial\Omega}\tag{vi}
\]
\medskip

\noindent
Finally,   (vi) and a majorising  positive
series expressing maximum norms imply 
that if $\alpha$ is sufficiently small then the
series (2)  converges and gives the requested solution for
(1). Moreover,   $\alpha$ 
can be taken  \emph{independently} of $h_0$.
Together with the established
uniqueness of solutions $u_h$ whenever they exist, it follows
that we can move from $h=0$ until $h=1$ and arrive
at the requested solution 
in Theorem 1.

\medskip

\noindent
{\bf{Remark.}} 
The reader may consult page 106 in [Carleman]
where the existence of a uniform constant $\alpha>0$ for which the series
(2) converge for every $h$ is
demonstrated by an
explicit majorant series.





\newpage









\centerline{\bf { ¤ 6. A uniqueness theorem for 
an elliptic boundary value problem}}

\bigskip

\noindent
{\bf Introduction.}
We shall work in  ${\bf{R}}^2$ with  coordinates
$(x,y)$.
Let
$n=2m$ be an even positive integer and consider two $n\times n$-matrices
$\mathcal A=\{A_{pq}\}$ and $\mathcal B=\{B_{pq}\}$
whose elements are real-valued functions of $x$ and $y$
where
the $B$-functions are continuous and the
$A$-functions  of class $C^2$. 
Eigenvalues of the
$\mathcal A$-matrix 
when $(x,y)$-varies give an
$n$-tuple of  roots
$\lambda_1(x,y),\ldots,\lambda_n(x,y)$ which solve
\[
\text{det}\,\bigl(\lambda\cdot E_n-\mathcal A(x,y)\bigr)=0\tag{1}
\]



\noindent
Next, we have
a system of first order
PDE-equations whose solutions are 
vector valued functions $(f_1,\ldots,f_n)$
defined in a half-disc
\[
D_+(\rho)=\{ x^2+y^2<\rho^2\quad\colon\, x>0\}
\]
where the $f$-functions satisfy the system:
\[ 
\frac{\partial f_p}{\partial x}+
\sum_{q=1}^{q=n}\,
A_{pq}(x,y)\cdot
\frac {\partial f_p}{\partial y}+
\sum_{q=1}^{q=n}\,
B_{pq}(x,y)\cdot f_q(x,y)=0\tag{*}
\]


\noindent
together with the boundary conditions:
\[
f_p(0,y)=0\quad\text{for all}\quad 1\leq p\leq n\tag{**}
\]

\medskip


\noindent
If the $\lambda$-roots are non-real in (1)
we say that (*)  is an elliptic system. When this holds
one exocets that the vanishing Cauchy data in  (**) entails
that the   solution
$f$  is identically zero.
This uniqueness  was proved by
Erik Holmgren in the  article [Holmgren]
under the assumption that the $A$-functions and the
$B$-functions are real analytic.
The question remained if the uniqueness still holds under less
regularity on the coefficient functions. 
An affirmative answer was proved
by  Carleman in the article \emph{xxx}.
\bigskip 

\noindent
{\bf 1. Theorem.} \emph{Assume that the
$\lambda$-roots are all simple and non-real as 
$(x,y)$ varies in the open half-disc. Then every solution $f$ to (**) 
with vanishing Cauchy-data  is identically zero}.
\medskip

\noindent
The proof requires several steps and 
the methods which occur below
have inspired more recent work where   Carleman estimates 
are used to handle  boundary value problems
in PDE-theory.
\bigskip



\centerline {\bf {A. First part of the proof}}
\medskip

\noindent
The system  in (*) is equivalent to a system of
$m$-many equations where one  seeks
complex-valued functions
$g_1,\ldots,g_m$   satisfying:
\[ 
\frac{\partial g_p}{\partial x}+
\sum_{q=1}^{q=m}\,
\lambda_p(x,y)\cdot
\frac {\partial g_p}{\partial y}=
\]
\[
\sum_{q=1}^{q=m}\,
a_{pq}(x,y)\cdot g_q(x,y)+
b_{pq}(x,y)\cdot \bar g_q(x,y)=0\,\,\colon\,1\leq p\leq m\tag{**}
\]
Above $\{a\uuu{pq}\}$ and $\{b\uuu{pq}\}$
are complex\vvv valued,and by the elliptic hyptheis the
complex-valued $\lambda$-functions can be chosen so that
their  imaginary parts are  positive functions of $(x,y)$.
The  reduction  of the originalsystem to
to this complex family of equations
is left to the reader. From  now
on we study the system (**) and Theorem 1 amounts
to prove that
if the $g$-functions satisfy (**) 
in a half-disc
$D_+(\rho)$
and
\[
g_p(0,y)=0\quad\colon\quad 1\leq p\leq m
\]
then there exists some $0<\rho_*\leq \rho$ such that the $g$-functions
are identically zero in 
$D_+(\rho_*)$. To attain this we
introduce domains as follows:
For a pair  $\alpha>0$ and 
$\ell>0$ we put
\[ 
D_\ell(\alpha)=\{
x+y^2-\alpha x^2<\ell^2\}\cap\{ x>0\}\tag{1}
\]


\noindent
Notice that the boundary
\[ 
\partial D_\ell(\alpha)=\{0\}
\times[-\ell,\ell]\,\cup \,
\{x+y^2-\alpha x^2=\ell^2\}
\]




\noindent
Above $\alpha$ and $\ell$ are small so the the $g$-functions satisfy (**)
in $D_\ell(\alpha)$.
For  each  $t>0$
we define  the  $m$-tuple of functions
by
\[
\phi_p(x,y)= g_p(x,y)\cdot e^{-t(x+y^2-\alpha x^2)}\tag{2}
\]
Since the $g$-functions satisfy   (**)
one verifies easily that
the $\phi$-functions
satisfy the system
\[
\frac{\partial \phi_p}{\partial x}+
\frac {\partial}{\partial y}\bigl(\lambda_p\cdot\phi_p)+
t(1-2\alpha x+2y\lambda_p\bigl)\cdot\phi_p=H_p(\phi)\tag{3}
\]
where 
\[
H_p(\phi)=\sum_{q=1}^{q=n}\,
a_{pq}(x,y)\cdot \phi_q(x,y)+
b_{pq}(x,y)\cdot \bar \phi_q(x,y)=0\,\,\colon\,1\leq p\leq m
\]

\noindent
Next, we set
\[ 
\Phi(x,y)=\sum_{p=1}^{p=m}\, |\phi_p(x,y)|\tag{4}
\]


\noindent
The crucial step in the proof
of Theorem 1
is to establish the following inequality.
\medskip

\noindent
{\bf A.1 Proposition.} \emph{Provided that $\alpha$ from the start is sufficiently large
there exists some $0<\ell_*\leq\ell$ and a constant $C$
which is independent of $t$  such that}
\[
\iint_{D_{\ell_*}}\, \Phi(x,y)\cdot dxdy \leq
C\cdot \int_{T_{\ell_*}}\, \sum_{p=1}^{p=n}\,|\phi_p|\cdot
 |dy-\lambda_p\cdot dx|
\]
\medskip

\noindent
\emph{How to deduce  Theorem 1.}
Let us show why Proposition A.1 gives Teorem 1.
In addition to
$\ell_*$ we fix some
$0<\ell_{**}<\ell_*$.
In  (2) above we have used the function
\[
w(x,y)= e^{-t(x+y^2-\alpha x^2)}\implies
\]
\[ w(x,y)= e^{-t\ell_*^2}\quad\colon\quad \{x+y^2-\alpha x^2=\ell_*^2\}
\quad\colon\quad
w(x,y)\geq e^{-t\ell_{**}^2}\quad\colon\quad (x,y)\in D_{\ell_{**}}\tag{i}
\]

\medskip

\noindent
Next, we have
$|\phi_p|= |g_p|\cdot w$ for each $p$. Replacing the left hand side in Proposition
A.1 by the area integral over the smaller
domain
$D_{\ell_{**}}$
we obtain the inequality;
\[
\iint_{D_{\ell_{**}}}\,
\sum_{p=1}^{p=m}\,| g_p(x,y)|\cdot dxdy\leq
C\cdot  e^{t(\ell_{**}^2-\ell_*^2)}\cdot 
\int_{T_{\ell_*}}\, \sum_{p=1}^{p=n}\,|g_p|\cdot
 |dy-\lambda_p\cdot dx|\tag{ii}
\]
\medskip

\noindent
Here (ii)  holds for every $t>0$. When
$t\to+\infty$ we have 
$ e^{t(\ell_{**}^2-\ell_*^2)}\to 0$
and  conclude that
\[
\iint_{D_{\ell_{**}}}\,
\sum_{p=1}^{p=m}\,| g_p(x,y)|\cdot dxdy=0
\]

\noindent
This means  that the $g$-functions are all zero in
$D_{\ell_{**}}$ and Theorem 1 follows.


\bigskip

\centerline{\bf B. Proof of Proposition A.1}
\medskip

\noindent
The proof  relies upon the
construction of certain $\psi$-functions.
More precisely, when
$t>0$ and  a point $(x_*,y_*)\in D_\ell$ are given we shall construct
an $m$-tuple of $\psi$-functions satisfying
the following:

 \bigskip

\noindent
{\bf Condition 1.} Each
$\psi_p$ is defined in
the punctured domain
$D_\ell\setminus\{(x_*,y_*)\}$
where $\psi_p$ for a given $1\leq p\leq m$
satisfies the equation
\[
\frac{\partial\psi}{\partial x}+
\lambda_p\cdot\frac{\partial\psi}{\partial y}-
t(1-2\alpha x+2y\lambda_p)\psi_p=0\tag{i}
\]





\noindent
{\bf Condition 2}. For each $p$ the
singularity of $\psi_p$ at $(x_*,y_*)$
is such that the line integrals below have a limit:
\[
\lim_{\epsilon\to 0}\,
\int_{[z-z_*|=\epsilon}\,\psi_p\cdot (dx-\lambda_p\cdot dy)=2\pi\tag{ii}
\]


\noindent
{\bf Condition 3.} There exists a constant $K$
which is independent both of
$(x_*,y_*)$ and of $t$ such that
\[
|\psi_p(z)|\leq\frac{K}{|z-z_*|}\tag{iii}
\]
Notice that the $\psi$-functions depend on the parameter
$t$, i.e. they are found for each $t$ but the constant $K$ in (3) is independent of
$t$.
\bigskip

\centerline {\emph{ The deduction of Proposition A.1}}
\bigskip

\noindent
Before the $\psi$-functions are  constructed in Section C
we show how  they  give
Proposition A.1.
Consider a point  $z_*\in D_+(\ell)$.
We get the associated $\psi$-functions from ¤ B
at this particular point.
Remove a small disc
$\gamma_\epsilon$ centered at $z_*$ and
consider some fixed
$1\leq p\leq m$.
Now $\phi_p$ satisfies the differential equation (3) from section A and 
$\psi_p$ satisfies (i) in Condition 1 above.
Stokes theorem gives:
\[
\int_{T_\ell}\phi_p\cdot\psi_p\cdot \bigl(dy-\lambda_p\cdot dx\bigr)
=\iint_{D_\ell\setminus\gamma_\epsilon}\,
H_p(\phi)\cdot \psi_p\cdot dxdy+
\int_{|z-z_*|=\epsilon}
\, \phi_p\cdot\psi_p\cdot \bigl(dy-\lambda_p\cdot dx\bigr)
\]
\medskip


\noindent
Passing to the limit as $\epsilon\to 0$, Condition 2 gives
\[
\phi_p(x_*,y_*)=\frac{1}{2\pi}
\int_{T_\ell}\phi_p\cdot\psi_p\cdot \bigl(dy-\lambda_p\cdot dx\bigr)
-\frac{1}{2\pi}\cdot \iint_{D_\ell}\,
H_p(\phi)\cdot \psi_p\cdot dxdy\tag{1}
\]


\noindent
Let $L$ be the maximum over $D_\ell$ of the 
coefficient functions  of $\phi$ and $\bar\phi$
which appear in  $H_p(\phi)$
from (3) i ¤ A. We have also the constant $K$ from
Condition 3 for $\psi_p$. The
triangle inequality gives:


\[
\bigl|\phi_p(x_*,y_*)\bigr|\leq
\frac{K}{2\pi}
\int_{T_\ell}\frac{|\phi_p|\cdot |dy-\lambda_p\cdot dx|}{z-z_*|}
+\frac{LK}{\pi}\cdot \sum_{q=1}^{q=m}\,
\iint_{D_\ell}\,
\frac{|\phi_q|}{|z-z_*|}\cdot dxdy\tag{*}
\]
\medskip

\noindent
Next, we use the elementary  inequality

\[ \iint_\Omega\, \frac{dxdy}{\sqrt{x-a)^2+(y-b)^2}}
\leq 2\cdot\sqrt{\pi}\cdot \sqrt{\text{Area}(\Omega)}\tag{**}
\]
where $\Omega$ is an arbitrary  bounded domain
and $(a,b)\in\Omega$.
Apply (**)  with
$\Omega=D_\ell$ and set
$S=\text{area}(D_\ell)$.
Integrating both sides in (*) over $D_\ell$
for every
$p$ and taking the sum we get
\[
\iiint_{D_\ell}\, \Phi\cdot dxdy\leq
\]
\[
K\cdot\sqrt{\frac{S}{\pi}}\cdot \int_{T_\ell}\,
\sum_{p=1}^{p=m}\, |\phi_p|\cdot |dy-\lambda_p\cdot dx|
+2\pi m LK\cdot \sqrt{\frac{S}{\pi}}\iint_{D_\ell}\,
\Phi\cdot dxdy
\]
\medskip

\noindent
This inequality hold for all small $\ell$.  Choose
$\ell$ so small that
\[
2\pi m LK\cdot \sqrt{\frac{S}{\pi}}\leq\frac{1}{2}
\]
Then the inequality above gives
\[
\iiint_{D_\ell}\, \Phi\cdot dxdy\leq
2\cdot 
K\cdot\sqrt{\frac{S}{\pi}}\cdot \int_{T_\ell}\,
\sum_{p=1}^{p=m}\, |\phi_p|\cdot |dy-\lambda_p\cdot dx|\tag{***}
\]


\noindent
Finally, consider some relatively compact
domain
$\Delta$ in $D_\ell$. Then there exists
$0<\ell_*<\ell$ such that
\[
\Delta\subset D_{\ell_*}
\]
Now we notice that

\[ 
|\phi_p(z)|\geq e^{-t\ell_*^2}\cdot |u_p(z)|
\quad\colon\quad z\in \Delta\quad\colon\quad
|\phi_p(z)|\geq e^{-t\ell^2}\cdot |u_p(z)|
\quad\colon\quad z\in T_\ell
\]


\noindent
We conclude that
\[
e^{-t\ell_*^2}
\,\iiint_\Delta\, \sum_{p=1}^{p=m}\, |u_p(z)|\cdot dxdy\leq
e^{-t\ell^2}\cdot 2\cdot 
K\cdot\sqrt{\frac{S}{\pi}}\cdot \int_{T_\ell}\,
\sum_{p=1}^{p=m}\, |u_p|\cdot |dy-\lambda_p\cdot dx|\tag{****}
\]
\medskip

\noindent Here (****) hold for every $t>0$. Passing to the limit
as
$t\to+\infty$ it follows that

\[
\cdot \iiint_\Delta\, \sum_{p=1}^{p=m}\, |u_p(z)|\cdot dxdy\leq
\]
Since $\Delta$ was any relatively compact subset of
$D_\ell$, we conclude  that the $u$-functions are zero in
$D_\ell$ and Theorem 1   follows.







\bigskip

\centerline{\bf {C. Construction of the $\psi$-functions.}}

\bigskip


\noindent
Before we embark upon specific constructions
we investigate the whole family of solutions to
a first order differential operators  of the form
\[
Q=\partial_x+\lambda(x,y)\cdot\partial_y\tag{*}
\] 
where $\lambda(x,y)$ is a complex 
valued $C^2$-function whose
imaginary part is $>0$. 
Set
\[ 
\lambda(x,y)=\mu(x,y)+i\cdot\tau(x,y)\quad\colon\, \tau(x,y)>0
\]


\noindent
Now we look for
solutions 
$h(x,y)$ to the equation $Q(h)=0$.
With
$h(x,y)=\xi(x,y)+i\cdot\eta(x,y)$
where $\xi$ and $\eta$ are real-valued $C^2$-functions this gives
the differential system:
\[
\frac{\partial\xi}{\partial x}+\mu_p\cdot
\frac{\partial\xi}{\partial y}-
\tau_p\cdot \frac{\partial\eta}{\partial y}=0
\]
\[
\frac{\partial\eta}{\partial x}+\mu_p\cdot
\frac{\partial\eta}{\partial y}+
\tau_p\cdot \frac{\partial\xi}{\partial y}=0
\]

\medskip

\noindent
Suppose we have found one solution 
 $h=\xi+i\cdot\eta$ where the 
Jacobian 
$\xi_x\eta_y-\xi_y\eta_x$
is $\neq 0$ at the origin. 
Then $(x,y)\mapsto (\xi,\eta)$ is a local $C^2$-diffeomorphism.
With  $\zeta=\xi+i\eta$ 
we have the usual Cauchy\vvv Riemann operator.
\[ 
\frac{1}{2}(\frac{\partial}{\partial\xi}+
i\cdot \frac{\partial}{\partial\eta})
\]

\noindent
Let $g(\xi+i\eta)$ be  a holomorphic function
in the complex $\zeta$-space with $\zeta=\xi+i\eta$ and put
\[ 
g_*(x,y)=g(\xi(x,y)+i\eta(x,y))
\] 
Then one easily verifies that $Q(g\uuu*)=0$
and conversely, every solution
to this equation is expressed by 
a $g\vvv*$function derived from an
analytic function in the complex $\zeta$space.satisfies  $Q(g_*)$.
\medskip

\noindent
{\bf{Conclusion.}} \emph{If a non-degenerate solution $h=\xi+i\eta$ has been found
then the homogenous solutions to $Q$ is in a 1-1 correspondence to
analytic functions in the $\zeta$-variable.}
\medskip

\noindent
{\bf{Remark.}} The effect
of a coordinate transformation
as above is that
the $Q$-operator 
is transported to the
Cauchy-Riemann operator in
the complex $\zeta$-space where $\zeta=\xi+i\eta$.
Later we   employ such  $(\xi,\eta)$-transformations
to
construct  
solutions to an inhomogeneous equation of the form
\[ 
Q(\psi)=(t-\alpha x+2y\lambda(x,y))\cdot \psi(t,x,y)
\]
where $t$Êis a positive parameter and the
$\psi$-functions 
will have certain specified properties.
Notice that it suffices to construct
the
$\psi$-functions separately, 
i.e. we no longer have to bother about
a differential system. With a fixed
$p$ fixed   $\lambda_p(x,y)=\mu_p+\tau_p$ and
from now on we may drop the index $p$ and explain how to obain
$\psi$-functions satisfying
the three conditions from ¤ B.
So we consider
the first order differential operator
\[
Q=\frac{\partial}{\partial x}+(\mu(x,y)+i\tau(x,y))\cdot
\frac{\partial}{\partial y}\tag{1}
\]
where 
$\tau(x,y)>0$.
\bigskip



\noindent
{\bf C.1 A class of $(\xi,\eta)$-functions.}
Let $V(x,y)$ and $W(x,y)$
be two quadratic forms, i.e. both are homogeneous polynomials of
degree two. Given a point $(x_*,y_*)$ 
and with $z=x+iy$
we seek  a coordinate transformation $(x,y)\mapsto(\xi,\eta)$
of the form:

\[ 
\xi(z)= \tau_p(z_*)\cdot (x-x_*)+V(x-x_*,y-y_*)+\gamma_1(z)
\cdot|z-z_*|^2
\]
\medskip
\[ 
\eta(z)= (y-y_*)-\mu_p(z_*)\cdot (x-x_*)+W(x-x_*,y-y_*)+
\gamma_2(z)\cdot|z-z_*|^2
\]
\medskip

\noindent{\bf Lemma.}
\emph{There exists  a pair of quadratic forms
$V$ and $W$ whose coefficients depend on
$(x_*,y_*)$ and a pair of
$\gamma$-functions which both vanish at
$(x_*,y_*)$ up to order one such that the complex\vvv valued function
$\xi+i\eta$ solves the homogeneous equation $Q(\xi+i\eta)=0$.}
\medskip

\noindent
A solution above
gives
a change of variables
so that
$Q$ is expressed in new real coordinates
$(\xi,\eta)$ by the operator
\[
\frac{\partial}{\partial \xi}+i\cdot \frac{\partial}{\partial\eta}\tag{2}
\]
There exist many coordinate transforms
$(x,y)\to(\xi,\eta)$
which change $Q$ into (2).
This \emph{flexible choice} of coordinate transforms
is used to  construct  the required
$\psi$-functions. Notice  that
Condition (2) in ¤ B is of a pointwise character, i.e. 
it suffices to find a $\psi$-function for a given point
$z_*=x_*+iy_*$. With this in mind
the required construction in ¤ B boils down to perform
a suitable coordinate transformation
adapated to $z_*$,
and after use the existence of
a $\psi$-function which to begin with  is expressed in the
$(\xi,\eta)$-variables where  the $Q$-operator is replaced by
the Cauchy-Riemann operator. In this special case
the required $\psi$-function is easy to find, i.e. see 
the remark in ¤ B.0.
So all that remains is to exhibit suitable coordinate transformations
which send $Q$ to the $\bar\partial$-operator. We leave it to the reader to
carry out such coordinate transformations. If
necessary, consult
Carleman's article where
a very detailed construction appears.







\newpage







\centerline{\bf{¤ 7. Propagation of sound}}

\bigskip


\noindent
With $(x,y,z)$ as space variables in
${\bf{R}}^3$ and a time variable $t$, the 
propagation of sound
in the infinite  open complement $U={\bf{R}}^3\setminus \overline{\Omega}$
of a bounded open subset $\Omega$ is governed by
 solutions $u(x,y,z,t)$ to the wave equation
 \[ 
 \frac{\partial^2 u}{\partial t^2}= \Delta u\tag{1}
 \] 
 where 
 $\Delta$ is the Laplace operator in $x,y,z$.
So here (1) holds when
$p=(x,y,z)\in U$
and $t\geq  0$. We  assume that
$\partial\Omega$ is of class $C^1$, i.e. given as  a union of pairwise disjoint
closed surfaces of class $C^1$ along which normal vectors are defined.
We seek solutions 
such that
$p\mapsto u(p,t)$ belong to $L^2(U)$ for each $t$,
and the outer normal derivatives
taken along $\partial\Omega$ are zero,  i.e. for every $t$ 
\[
\frac{\partial u}{\partial n}(p,t)=0\quad\colon p\in \partial \Omega\tag{2}
\]
Initial conditions are expressed by  a pair of $C^2$-functions
$f_1x,y,z)$ and $f_2(x,y,z)$ defined in $U$ such that
$f_1,f_2$  together with
$\Delta(f_1$ and $\Delta(f_2)$ belong to $L^2(U)$,
and their outer normal derivatives along $\partial\Omega$ are zero.
So here
$u(p,0)= f_0(p)$Êand $\frac{\partial u}{\partial t}(p,0)= f_1(p)$
hold for each $p\in U$.
\medskip

\noindent
Following materail in [carleman]
we shall prove the existence and uniqueness  using a
spectral function $\theta$ attached to a Class I operator
$A$ constructed via solutions to the Dirichlet problem
where no time variable appears.
A merit of this proof is that it enable us
to confirm 
the physically expected result expressed by:
\[
\lim_{t\to \infty}\, (\frac{\partial u}{\partial x})^2(p,t)+
(\frac{\partial u}{\partial y})^2(p,t)+(\frac{\partial u}{\partial z})^2(p,t)=0\tag{*}
\]
with uniform convergence when $p$ stays in a relatively compact subset of
$U$.
More precisely, Carleman proved (*) by proving
that the  spectral function of $A$ 
is \emph{absolutely continuous} with respect to
the $\lambda$-parameter. Since this result has independent interest
we announce it here in the introduction while the proof is given in ¤ xx.


\medskip

\noindent
Let $\{a\leq s\leq b\}$ be a 
compact interval on the real $s$-line and
$s\mapsto G_s$ is  a function with values in the Hilbert space
$L^2(U)$ which  is 
continuous in the sense that 
\[
\lim_{s\to s_0}\, ||G_s-G_{s_0}||_2=0
\]
hold for each $s_0$, where we  introduced the $L^2$-norms.
The function has a finite total variation if 
there exists a constant $M$ such that
\[
\sum\, ||G_{s_{\nu+1}}-G_{s_\nu}||_2\leq M
\] 
hold for every partition $a=s_0<s_1<\ldots<s_M=b$.
When this holds one  construct Stieltjes integrals
and 
for every subinterval $[\alpha,\beta]$
there exists
the $L^2$-function in $U$ 
\[
\Phi_{[\alpha,\beta]}= \int_\alpha^\beta\, s\cdot \frac{dG_s}{ds}
\]
Impose the extra conditions that the normal deriviatives
$ \frac{\partial G_s}{\partial n}$ vanish on
$\partial\Omega$ for every $a\leq s\leq b$
and the following differential equation
holds for
every sub-interval $[\alpha,\beta]$ of $[a,b]$:
\[
\Delta(G_\beta-G_\alpha)+\Phi_{[\alpha,\beta]}=0
\] 
\medskip

\noindent
{\bf{0.1 Theorem.}}
\emph{The equations  above imply that
$s\mapsto G_s$ is absolutely continuous which means that 
whenever $\{\ell_1,\ldots,\ell_M\}$ a finite family of disjoint
intervals in $[a,b]$ where the sum of their lengths is $<\delta$,
then the sum of
the total variations over these intervals is
bounded by $\rho(\delta)$ where
$\rho$ is a function of $\delta$ which tends to zero as $\delta\to 0$.}

\newpage



\centerline{\bf{¤ 1. Preliminary  results.}}
\medskip

\noindent
Let $U$ be as above and suppose that $u$ is a real-valued $C^2$-function in this domain
such that both $u$ and $\Delta(u)$ belong to $L^2(/U)$. In addition
we assume that the normal derivative of $u$ along $\partial U$
exists
as a continuous function. Set
\[
D^2(u)=
 \frac{\partial u}{\partial x}^2+
\frac{\partial u}{\partial y}^2+\frac{\partial u}{\partial z}^2
\]
We shall prove that 
\[
\int_U\,D^2(u)\, dxdydz<\infty\tag{i}
\]
\medskip

\noindent
To prove (ii) we consider  large $R$ such that
$\Omega$ is contained in the ball $B(R)$ of radius $R$ centered at the origin.
Set $U(R)= U\cap B(R)$. Then Greens' formula gives the equation
\[
\int_{U(R)}\, u\Delta(u)+
D^2(u)+\int_{\partial U}\, u\frac{\partial u}{\partial n}\, dA=
\int_{\partial B(R)}\, u\frac{\partial u}{\partial n}\, dA\tag{i}
\]
The Cauchy-Schwarz inequality and the hypothesis  that 
$u$ and $\Delta(u)$ belong to $L^2(U)$ imply that the first term above is bounded
as a function of $R$. 
We conclude that (i) holds if there exists a sequence
$\{r_k\}$ which tends to $+\infty$ such that
\[
\lim\, \int_{\partial B(r_k)}\, u\frac{\partial u}{\partial n}\, dA=0
\tag{ii}
\]
To prove (i) we introduce the function
\[
\psi(R)=\int_{U(R)}\, u^2
\]
It follows that
\[
\psi'(R)=\int_{\partial B(R)}\, u^2\, dA
\]
and the reader can verify that the second order derivative becomes
\[
\psi''(R)=\frac{2}{R}\psi'(R)+2\int_{\partial B(R)}\, u\frac{\partial u}{\partial n}\, dA
\]
Hence
\[
\int_{\partial B(R)}\, u\frac{\partial u}{\partial n}\, dA=
\frac{\psi''(R)}{2)}-\frac{\psi'(R)}{R}
\]
Next, since $u$ is in $L^2(U)$ the increasing function
$\psi(R)$ is bounded and converges to a finite limit
as $R\to\infty$ which  entails that the positive function
$\psi'(R)$ cannot stay $\geq a$ for a positive constant $a$.
Now two possible cases can occur. The first is that 
$R\mapsto \psi'(R)$ decreases in a monotone fashion to
zero. Then Rolle's mean-value theorem implies
that there exists a sequence
$\{r_k\}$ such that
$\psi''(r_k)\to 0$ and (ii) follows.
\medskip

\noindent
The second case is that
there exists a sequence 
$\{r_k\}$ where $\psi'(r_k)$ takes a local minimum which gives
$\psi''(r_k)=0$ and since
the quotients
$\frac{\psi'(r_k)}{r_k}$ also tend to zero 
we get (i) in this case also.

\bigskip

\noindent
{\bf{1.1 Exercise.}}
Let $u$ be a complex-valued function where $u$ and
$\delta(u)$ both belong to $L^2(U)$ and
the normal  derivative along $\partial U$ is zero.
Show that the result above gives
the equation
\[
\int \Delta(u)\bar u+\int |D(u)|^2=0
\]
where we have put
\[
|D(u)|^2
 |\frac{\partial u}{\partial x}|^2+
|\frac{\partial u}{\partial y}|^2+|\frac{\partial u}{\partial z}|^2
\]






\bigskip

\noindent
{\bf{1.2 Application.}}
Suppose that $u$ is 
a function $u$ in $L^2(U)$ such that
\[
\Delta(u)+\lambda u=0
\]
hold for some complex  number $\lambda$
and the normal derivative is zero along $\partial U$.
The exercise gives
the equality
\[
-\lambda\cdot \int_U\, |u|^2+\int_U\, D(u)^2=0
\]
This  entails that
$\lambda$ must be real and positive. The next result requires
more effort to prove.

\bigskip

\noindent
{\bf{1.3 Theorem.}} \emph{Let $u$ 
satisfy the equation in the exercise for some positive real number
$\lambda$. Then $u$ is identically sero.}
\bigskip





\noindent
\emph{Proof.}
We shall work with polar coordinates, i.e. employ the Euler's  angular variables
$\phi$ and $\theta$ where
\[
0<\theta\quad\colon\, 0<\phi<2\pi
\]
The wellknown expression of $\Delta$Êin the variables $r,\theta,\phi$ 
shows that the equation (*) corresponds to
\[
xxxxx+xxxx=0 page 132 \tag{i}
\]
Let $n\geq 1$ and $Y_n(\theta,\phi)$ some spherical function of
degree $n$ with a normalised $L^2$-integral  equal to one.
For each $r$ where $B(r)$ contains $\overline{\Omega}$
we set
\[
 Z(r)=\int_0^{2\pi}\int_0^\pi\, 
 Y_n(\theta,\phi)\cdot f(r,\theta,\phi)\, \sin(\theta)\, d\theta d\phi\tag{ii}
\]
The Cauchy-Schwarz inequality gives
\[
 Z(r)^2\leq \int_0^{2\pi}\int_0^\pi\, 
Y^2_n\cdot  \sin(\theta)\, d\theta d\phi\cdot 
\int_0^{2\pi}\int_0^\pi\, 
f^2(r,\theta,\phi)\cdot  \sin(\theta)\, d\theta d\phi
\]
Since the $L^2$-integral if $Y_n$ is normalised
the last product is reduced to
\[
J(r)=\int_0^{2\pi}\int_0^\pi\, 
f^2(r,\theta,\phi)\cdot  \sin(\theta)\, d\theta d\phi
\]
Now
\[
\int_{r_*}^\infty\, r^2\cdot J(r)\, dr
\]
is equal to the finite $L^2$-integral of $f$ in the exterior domain
taken outside a ball $B(r_*)$.
From (ii) we conclude that
\[
\int_{r_*}^\infty\, r^2\cdot Z(r)^2\, dr<\infty\tag{iii}
\]
\medskip


\noindent
{\bf{A differential equation.}}
Recall that a spherical function of degree $n$ satisfies
\[
\frac{1}{\sin \theta}
\frac{d}{d \theta}\bigl(\sin \theta\cdot
\frac{\partial Y_n}{\partial \theta}\bigr)+
\frac{1}{\sin^2 \theta}\frac{\partial^2 Y_n}{\partial \phi^2}+
(n+1)n\cdot Y_n=0
\tag{iv}
\]
\medskip

\noindent
{\bf{Exercise.}}
Show via suitable partial integrations that (i) and (iv) imply that
$Z(r)$ satisfies the differential equation
\[
\frac{1}{r^2}\cdot
\frac{d}{dr}(r^2\cdot \frac{dZ}{dr})+
(\lambda-\frac{n(n+1)}{r^2})Z=0\tag{v}
\]
\medskip

\noindent
The second order differential equation
has two linearly independent solutions of the form
\[
Z_1=\cos(\sqrt{\lambda} r)\cdot \bigl[\frac{1}{r}+
\frac{a_2}{r^2}+\ldots\bigr]
\]
\[
Z_2=\sin(\sqrt{\lambda} r)\cdot \bigl[\frac{1}{r}+
\frac{b_2}{r^2}+\ldots\bigr]
\]
It follows that there exist a pair of constants $c_1,c_2$ such that

\[
Z=c_1Z_1+c_2Z_2=\frac{c_1\cdot  \cos(\sqrt{\lambda} r)+
c_2\cdot  \sin(\sqrt{\lambda} r)}{r}+
\frac{B(r)}{r^2}\tag{vi}
\]
where $r\mapsto B(r)$ stays bounded as $r\to+\infty$.
\medskip

\noindent
{\bf{Exercise.}}
Show that the finite integral in (iii) and (vi) give 
$c_1=c_2=0$ and hence $Z(r)$
identically zero for large $r$.
Since this  hold for all spherical functions we conclude that 
$f$ is identically zero outside 
the closed ballÊ$B(r_*)$.
Finally, by assumption $U$Êis connected and the elliptic equation
(*) implies that $f$ is a real-analytic function in
$U$, So the vanishing outside a large ball entails that $f$ is identically zero in $U$
which finishes the proof of Theorem 1.3.
\bigskip

\noindent
\centerline {\bf{¤ 2. Proof of Theorem 0.1}}
\medskip

\noindent
Using similar methods as in the proof of Theorem xxx 
one reduces the proof to study
functions 
$g(r;\mu)$ where $r\mapsto g(r;\mu)$ is 
a $C^2$-function and square integrable on
the interval $[r_*,+\infty)$ for a given $r_*>0$
while $\mu$ as above varies in $[a,b]$.
Moreover one has 
\[ 
\max_\mu\, \int_{r_*}^\infty\, g(r;\mu)\,  dr<\infty
\] 
Next, for each sub-interval
$\ell=[\alpha,\beta]$ we set
\[
\delta_\ell(g(r,\mu)=g(r,\beta)-g(r,\alpha)
\]
With these notations we say that
$g(r;\mu)$ is absolutely continuous with respect to $\mu$
if there to each $\epsilon>0$ exists
$\delta>0$Êsuch that
\[
\sum\, \int_{r_*}\, |\delta_{\ell_\nu}((g(r,\mu)\bigr|^2\cdot r^2\,dr<\epsilon
\]
for every finite family of sub-intervals
$\{\ell_\nu\}$ when  the sum of their lengths is
$<\delta$.
\medskip

\noindent
{\bf{2.1 Theorem.}}
\emph{Assume in addition to the above that
the  equation below holds for each 
sub-interval $\ell$} 
\[
\frac{1}{r^2}
\frac{d}{dr} \bigl[\, r^2\frac{d}{dr}(\delta_\ell(g(r,\mu) \bigr]-
\frac{n(n+1)}{r^2}\cdot \delta_\ell(g(r,\mu)+
\int_\ell\, \mu\cdot \frac{d}{d\mu}(g(r,\mu)=0
\]
\emph{Then 
$g(r,\mu)$ is absolutely continuous with respect to $\mu$.}

\newpage
\centerline{\bf{¤ 3. Solution of the wave equation.}}

\bigskip

\noindent
The result in ¤ 1.2 imples that the symmetric and densely defined operator
on $L^2(U)$ expressed by the Green's function for
the Laplace operator in $U$
gives a spectral  function $\Theta(p,q;\lambda)$ defined for
$\lambda\geq 0$ with the property that when
$f$ is a function in $U$ such that both $f$ and
$\Delta(f)$ are square integrable and
the normal derivative is zero on the boundary, then
\[
f=\int_0^\infty\, \frac{d\Theta}{d\lambda}(f)
\]
where the integral is absolutely convergent
a s explained in ¤ xx.
Moreover, one has
\[
\Delta(f)=\int_0^\infty\, \lambda\cdot \frac{d\Theta}{d\lambda}(f)
\]
The solution $u(x,t)$ from the introduction with the prescribed
initial
conditions when $t=0$ is therefore given by
\[
u=\int_0^\infty\,\cos\,\sqrt{t\lambda}\cdot \frac{d\Theta}{d\lambda}(f_0)
+\int_0^\infty\,\frac{\sin\,\sqrt{t\lambda}}{\sqrt{\lambda}}\cdot 
\frac{d\Theta}{d\lambda}(f_1)
\]
This entails for example that
\[
\frac{\partial u}{\partial x}
=\int_0^\infty\,\cos\,\sqrt{t\lambda}\cdot \frac{d\Theta}{d\lambda}
(\frac{\partial f_0}{\partial x})
+\int_0^\infty\,\frac{\sin\,\sqrt{t\lambda}}{\sqrt{\lambda}}\cdot 
\frac{d\Theta}{d\lambda}(\frac{\partial f_1}{\partial x})
\]
Next, Theorem 0.1 entails that the 
spectral function is absolutely contoinuous with respect to
$\lambda$, and then the Riemann-Lebesgue Theorem applies and proves
the limit formula (*) from the introduction.



































\newpage





\centerline{\bf{A hyperbolic boundary value equation,.}}

\bigskip


\noindent
{\bf{Introduction.}}
Let $x,s$ be coordinates in
${\bf{R}}^2$ and consider the rectangle
\[
\square=\{(x,y)\colon\, 0\leq x\leq \pi\colon\, 0\leq s\leq s^*\}
\]
for some  $s^*>0$.
A continuous and real-valued function $g(x,s)$ in $\square$ is $x$-periodic if
\[
g(0,s)=g(\pi,s)\quad\colon 0\leq s\leq s^*\
\]
More generally, if $k\geq 1$ and $g(x,s)$ 
belongs to $C^k(\square)$ then
it is $x$-periodic if
\[
\partial_x^\nu(g(0,s))=
\partial_x^\nu(g(\pi,s)\quad\colon 0\leq\nu\leq k \tag{i}
\] 
In particular we can consider real-valued $C^\infty$-functions on
$\square$ for which (i) hold for every $\nu\geq 0$.
Let $a(x,s)$ and $b(x,s)$ be a pair real-valued $C^\infty$-functions on
$\square$ which are periodic in $x$. They give
the PDE-operator
\[ 
P=\partial_s-a\cdot \partial_x-b\tag{*}
\]
\medskip

\noindent
{\bf{0.1 A boundary value problem.}}
Let $p\geq 1$
and $f(x)$ is a periodic function on
$[0,\pi]$ which is $p$-times continuously differentiable.
Now we seek $F(x,s)\in C^p(\square)$
which is $x$-periodic and satisfies
$P(F)=0$ in $\square$ and the 
initial condition
\[ 
F(x,0)= f(x)
\]



\noindent
We are going to prove that this
boundary value equation has a unique solution.
The proof  requires several steps and is not finished until
¤ 4.
We shall use  Hilbert space methods.
If $k\geq 2$ there exists the Hilbert space
$\mathcal H^{(k)}$
which arises via the completetion of $C^k(\square)$
with respect to the sum of $L^2$-norms
of derivatives up to order $k$ of $x$-periodic
$C^\infty$-functions in $\square$.
Sobolev's inquality gives
\[
\mathcal H^{(k)}\subset C^{k-2}(\square)\quad\colon\, k\geq 2
\]
Staying in the interval $\{0\leq x\leq \pi\}$
we also have  the Hilbert space $H^k[0,\pi]$
which is the  completion of periodic $C^\infty$-functions $f(x)$.
For a fixed $k\geq 2$
we denote by $\mathcal D_k(P)$ the set of
$f\in H^k[0,\pi]$ such that
there exists $F\in\mathcal H^{[k)}$ where
$P(F)=0$ and $F(x,0)=f(x)$ on $[0,\pi]$.
\medskip

\noindent
In 1¤ xx we prove the
following Hilbert space version
of the boundary problem.
\medskip


\noindent
{\bf{0.2 Theorem.}}
\emph{For each $k\geq 2$  the equality
$\mathcal D_k(P)=H^k[0,\pi]$ holds and the map $f\to F$ 
from $H^k[0,\pi]$  to
$\mathcal H^{(k)}$ is bijective.}
\medskip


\noindent
\emph{About the proof.} The material in ¤ 1 is
used to
show that if
$\mathcal D_k(P)$ is a dense subspace of
$H^k[0,\pi]$, then equality holds.
To   prove the density
we consider the the linear operator $S_k$
which
for each $f\in\mathcal D_k(P)$ associates the periodic function
$x\mapsto F(x,s^*)$ on $[0,\pi]$.
So  here the domain of definition
$\mathcal D(S_k)=\mathcal D(P_k)$.
Again  material in ¤ 1 is used to prove that $S_k$ is a bounded operator, i.e.
there exists a constant $C$ such that
\[ 
||S_k(f)||_k\leq C\cdot ||f||_k\quad\colon f\in\mathcal D(S_k)
\]
In ¤ xx we prove that
the density of $\mathcal D_k(P)$
follows from
the following:
\medskip

\noindent
{\bf{0.2.1 Proposition.}}
\emph{For each $k\geq 2$ there exists
a positive number
$\alpha(k)$ such that
the range of 
$E-\alpha\cdot S_k$
contains all periodic $C^\infty$-functions on $[0,\pi]$ when
$\alpha<\alpha(k)$.}
\bigskip


\noindent
{\bf{0.3 A periodic equation.}}
To prove of Proposition 0.2.1  
we
consider doubly periodic functions
$g(x,s)$ defined in $\{0\leq x\leq \pi\}\times
\{0\leq s\leq 2\pi\}$.
When $k\geq 2$ we get the Hilbert space
$\mathcal H^{(k)}$
after the completion of doubly periodic $C^\infty$-functions with 
$L^2$-norms of derivatives up to order $k$.
This time we consider a  differential operator
\[
P=\partial _s-a(x,s)\partial_x-b(x,s)
\]
where $a$ and $b$ are doubly periodic $C^\infty$-functions.
Set
\[ 
\mathcal D_k(P)= \{ g\in \mathcal H^{(k)}\,\colon
P(g)\in \mathcal H^{(k)}\}
\]
In the product
space
$\mathcal H^{(k)}\times \mathcal H^{(k)}$
we have the graphic set
\[
\gamma_k=\{(g,P(g)\,\colon\, g\in C^\infty\}
\] 
where we always refer to doubly periodic $C^\infty$-functions as 
above.
The closure of $\gamma_k$
is the graph of a closed and densely defined 
linear operator  on
$\mathcal H^{(k)}$ denoted by $T_k$.
With these notations the following holds,  which apart from
its use during the proof of Theorem 0.2  has independent interest:

\medskip

\noindent
{\bf{0.3.1 Theorem.}}
\emph{There exists a positive number
$\lambda(k)$ such that}
\[
 \lambda\cdot E-T_k\colon\,\mathcal D(T_k)\to \mathcal H^{(k)}
\] 
\emph{are surjective fo every $\lambda>\lambda(k)$.}
\medskip

\noindent
To prove this theorem  we shall 
consider the  closed and densely defined operator
$\mathcal T_k$
on
$\mathcal H^{(k)}$ where  
\[
\Gamma(\mathcal T_k)=\{(g,P(g)\,\colon\, g\in \mathcal D_k(P)\}
\]
Since doubly periodic $C^\infty$-functions belong to
$\mathcal D_k(P)$ we have 
$\Gamma(T_k)\subset
\Gamma(\mathcal T_k)$, i.e. 
$\mathcal T_k$ is an extension
of
$T_k$.
Since $T_k$  is densely defined this entails that the adjoint operators
$T_k^*$ and $\mathcal T_k^*$ are equal.
A crucial step in the proof of
Theorem 0.3.1
is the following:

\medskip

\noindent
{\bf{0.3.2 Theorem.}}
\emph{One has the equality  $\mathcal D(P)=\mathcal D(T_k^*)$
and there exists a desnely defined self-adjoint operator $B_k$ such that}
\[
T_k^*= -\mathcal T_k+B_k
\]
\medskip

\noindent
{\bf{Remark.}}
As described above 
general facts about densely defined and closed linear operators on
Hilbert spaces play an essential role.
The subsequent proofs therefore offer an instructive lesson hos
they are applied to "concrete" PDE-equations.
In ¤ xx we expose a result in higher dimension for symmetric hyperbolic 
systems where the proofs are verbatim the same, except for additional 
technical details.



























 











\newpage

\centerline{\bf{¤ 1. Differential inequalities
and energy integrals.}}

\bigskip

\noindent
Let $M(s)$ be a non-negative real-valued continuous function
on a closed interval $[0,s^*]$.
To each $0\leq s<s^*$
we set
\[
d_M^+(s)=\limsup_{\Delta s\to 0}\, \frac{M(s+\Delta s)-M(s)}{\Delta s}
\]
where $\Delta s$ are positive during the limit.
\medskip

\noindent
{\bf{1.1 Proposition.}} \emph{Let $B$ be a real number such that
$d_M^+(s)\leq B\cdot M(s)$ holds in $[0,s^*)$. Then }
\[ 
M(s)\leq M(0)\cdot e^{Bs}\quad\colon 0<s\leq s^*
\]
\medskip

\noindent
The proof of this result is left as an exercise.
The hint is to consider the function $N(s)= M(s)e^{-Bs}$
and show that $d^+_N(s)\leq 0$ for all $s$.
Notice that $B$ is an arbitrary real number, i.e. it may also be $<0$.
More generally, let $k(s)$ be a  non-decreasing continuous function
with $k(0)=0$ and 
suppose that
\[
d^+_M(s)\leq B\cdot M(s)+k(s)\quad \colon 0\leq s<s^*
\]
Now the reader may verify that
\[
M(s)\leq M(0)\cdot e^{Bs}+\int_0^s\, k(t)\, dt\tag{1.1.1}
\]


\medskip


\noindent
Next, consider
the  set
$\square=[0,\pi]\times [0,s^*]$ as above.
A $C^1$-function
$g$ is  
periodic  with respect to $x$ if
$g$  and the partial derivatives
$\partial_s(g)$,$\partial_x(g)$  are  periodic in
$x$, i.e.
\[ 
g(0,s)= g(\pi,s)\quad\colon 0\leq s\leq s^*
\]
and similarly  for $\partial_x(g)$ and $\partial_s(g)$.



\medskip

\noindent
{\bf{1.2 Theorem.}}
\emph{Let $g$ be a periodic $C^1$-function which satisfies the PDE-equation}
\[
\partial_s(g)= a\cdot \partial_x(g)+ b\cdot g\tag{*}
\]
\emph{in $\square$ where $a$ and $b$ are 
$x$-periodic real-valued continuous functions
on $\square$. Set}
\[
M_g(s)= \max_x\, |g(x,s)|\quad\colon \,B=\max_{x,s}\, |b(x,s)|
\]
\emph{Then one has the inequality}
\[
M_g(s)\leq M_g(0)\cdot e^{Bs}
\]
\medskip


\noindent
\emph{Proof.}
Consider some $0<s<s^*$ and let $\epsilon>0$.
Put
\[ 
m^*(s)=\{ x\,\colon\, g(x,s)= M_g(s)\}
\]
The  continuity of $g$
entials that the function $M(s)$ is continuous and
the sets $m^*(s)$ are compact.
If $x^*\in m^*(s)$ the periodicity of
the
$C^1$-function $x\mapsto g(x,s)$
entails that
$\partial_x(x^*,s)=0$ and (*) gives
\[
\partial_s(g)(x,s)=b(x,s)g(x,s)\quad\colon x\in m^*(s)
\]
Next, let $\epsilon>0$. We find an open neighborhood $U$
of $m^*(s)$
such that
\[
|\partial_x(g)(x,s)|\leq \epsilon\quad\colon x\in U
\]
Now there exists
$\delta>0$ such that
\[
|g(x,s)|\leq M(s)-2\delta\quad\colon x\in [0,\pi]\setminus U
\]
Continuity gives  some
$\rho>0$ such that
if $0<\Delta s<\rho$ then  the inequalities below hold:
\[
|g(x,s+\Delta s)|\leq M(s)-\delta\quad\colon x\in [0,\pi]\setminus U
\quad\colon\,M(s+\Delta s)>M(s)-\delta\tag{i}
\]
\[
M(s+\Delta s)\leq M(s)+\epsilon\quad \colon\,
|\partial_x(g)(x,s+\Delta s)|\leq 2\epsilon \quad\colon x\in m^*(s)\tag{ii}
\]

\noindent
If $0<\Delta s<\rho$ we see that (i) gives
$x\in m^*(s+\Delta s)\subset U$
and for such $x$-values 
Rolle's mean-value theorem and the PDE-equation give
\[
M_g(x,s+\Delta s)- g(x,s)=\Delta s\cdot \partial_s(g(x,s+\theta\cdot \Delta s)=
\] 
\[
\Delta s\cdot \bigl[a(x,s+\Delta s)\cdot
\partial_x(g)(x+\theta\cdot \Delta s)+
b(x,s+\Delta s)\cdot
g(x,s+\theta\cdot \Delta s)\bigr]\tag{iii}
\]
Let  $A$ be the maximum norm of $|a(x,s)|$ taken over
$\square$.
Since $|g(x,s)|\leq M(s)$
the triangle inequality and (iii) give
\[ 
M(s+\Delta s)\leq M(s)+\Delta s[\cdot A\cdot 2\epsilon+
B\cdot M(s+\theta\cdot \Delta s)]
\]
Since the function $s\mapsto M(s)$ is continuous
it follows that
\[
\limsup_{\Delta s\to 0}\,
\frac{M(s+\Delta s)-M(s)}{\Delta s}\leq
A\cdot 2\epsilon+ BM(s)
\]
Above $\epsilon$ can be arbitrary small
and hence
\[ d^+(s)\leq B\cdot M(s)
\]
Then Proposition 1.1 gives (*) in the theorem.


\medskip

\noindent
{\bf{1.3 $L^2$-inequalities.}}
Let $g(x,s)$ be a $C^1$-function satisfying (*)
in
Theorem 1.2.
Set
\[ 
J_g(s)=\int_0^\pi\, g^2(x,s)\, dx
\]
Taking the $s$-derivative we obtain
 with respect to $s$ and (*) give
\[
\frac{dJ_g}{ds}= 2\cdot \int_0^\pi\, g\cdot \partial_s(g)\,ds=
2\cdot \int_0^\pi\, (a\partial_x(g)\cdot \partial g+ b\cdot g)\,dx
\]
The periodicity of $g$ with respect to $x$ gives
$\int_0^\pi\, \partial_x(ag^2)\, dx=0$. This
entails that the right hand side becomes
\[
\int_0^\pi\, (-\partial_x(a)+b)\cdot g^2\, dx
\]
So if $K$ is the maximum norm of
$-\partial_x(a)+b$ over $\square$ it follows that
\[
\frac{dJ_g}{ds}(s)\leq K\cdot J_g(s)
\]
Hence Theorem 1.2 gives
\[
\int_0^\pi\, g^2(x,s)\, dx\leq e^{Ks}\cdot
\int_0^\pi\, g^2(x,0)\, dx\quad\colon 0<s\leq s^*\tag{1.3.1}
\]
Integration with respect to $s$ entails that
\[ 
\iint_\square\, g^2(x,s)\, dxds\leq
\int_0^{s^*}\, e^{Ks}\,ds\cdot
\int_0^\pi\, g^2(x,0)\, dx\tag{1.3.2}
\]
Thus, the $L^2$-integral of $x\to g(x,0)$
majorizes both the area integral and each slice integral when
$0<s\leq s^*$.


\bigskip

\centerline{\bf{¤ 2. A boundary value equation}}
\bigskip

\noindent
Let $a(x,s)$ and $b(x,s)$ be real-valued $C^\infty$-functions on
$\square$ which are periodic in $x$ and consider the PDE-operator
\[ 
P=\partial_s-a\cdot \partial_x-b
\]
\medskip

\noindent
{\bf{2.1 Theorem.}}
\emph{For every positive integer $p$ and each
periodic $f\in C^p[0,\pi]$
there exists a unique periodic $g\in C^p(\square)$ 
where $P(g)=0$ and $g(x,0)= f(x)$.}

\bigskip

\noindent
The uniqueness follows from the results in ¤ 1.
For if $g$ and $h$ are solutions in Theorem 2.1
then $\phi=g-h$   satisfies $P(\phi)=0$. Here
$\phi(x,0)=0$ which gives $\phi=0$ in $\square$
via
(1.3.2).
The proof of existence requires several steps and 
employs Hilbert space methods. So first we
introduce
certain Hilbert spaces.

\medskip

\noindent
{\bf{2.2 The space $\mathcal H^{(k)}$}}.
To each  integer $k\geq 2 $ 
the complex Hilbert space
$\mathcal H^{(k)}$ is the
completion  
of complex-valued
$C^k$-functions on 
$\square$ which are periodic with respect to $x$.
A trivial Sobolev  inequality  entails that 
every function in
$\mathcal H^{(2)}$ is continuous, and more generally
\[
\mathcal H^{(k)}\subset C^{k-2}(\square)\quad\colon k\geq 3
\]
and it  clear that the  first order PDE-operator $P$ maps
$\mathcal H^{(k+1)}$ into
$\mathcal H^{(k)}$.
Next,
on the periodic $x$-interval $[0,\pi]$ we have  the Hilbert spaces
$H^k[0,\pi]$ for each $k\geq 2$.
\medskip

\noindent
{\bf{2.3 Definition.}}
\emph{For each integer $k\geq 2$ we denote by 
$\mathcal D_k(P)$   the  family of all
$f(x)\in H^k[0,\pi]$ for which 
there exists some
$F(x,s)\in\mathcal H^{(k)}$ such that}
\[
P(F)=0\quad\colon\, F(x,0)=f(x)\tag{*}
\]
The results in ¤ 1 show that $F$ is uniquely determined by (*). Moreover,
there exists a constant $C_k$ which only depends upon the
$C^\infty$-functions $a$ and $b$ and the given integer $k$
such that
\[
||F||_k\leq C_k\cdot ||f||_k\tag{2.3.1}
\]
where we have taken norms in
$\mathcal H^{(k)}$ and 
$H^k[0,\pi]$ respectively.
Next, the last inequality in (1.3.2)
shows that
$C_k$ can be chosen such that 
\[
||f^*||_k\leq C_k\cdot ||f||_k\tag{2.3.3}
\]
where $f^*(x)= F(x,s^*)$ belongs to $H^k[0,\pi]$.


\medskip

\noindent
{\bf{2.4 A density principle}}
Above we introduced the space
$\mathcal D_k(P)$. Now the following hold:
\medskip


\noindent
{\bf{2.4.1 Proposition.}}
\emph{If $\mathcal D_k(P)$ is dense in 
$\mathcal H^k[0,\pi]$, then one has the equality}
\[
\mathcal D_k(P)=\mathcal H^k[0,\pi]\tag{2.4.1}
\]

\medskip

\noindent
\emph{Proof.}
Suppose that
$\mathcal D_k(P)$ is dense.
So if $f\in\mathcal H^k[0,\pi]$ there exists a sequence
$\{f_n\}$ in 
$\mathcal D_k(P)$ where $||f_n-g||_k\to 0$.
By (2.2.2)   we have
\[ 
||F_n-F_m||_k\leq C||f_n-f_m||_k
\]
Hence $\{F_n\}$ is a Cauchy sequence in
the Hilbert space $\mathcal H^{(k)}$
and converges to a limit $F$.
Since each $P(F_n)=0$ it follows that
$P(F)=0$
and it is clear that the continuous boundary value function
$F(x,0)$Êis equal to
$f(x)$ which entails that
$f$ belongs to 
$\mathcal D_k(P)$.
\medskip

\noindent
{\bf{2.5 The operators $S_k$.}}
Each $f\in \mathcal D_k(P)$ gives the function  $f^*(x)= F(x,s^*)$
in $\mathcal H^k[0,\pi]$ and  set
\[ 
S_k(f)=f^*(x)
\]
So  the domain of definition of $S_k$ is equal to
$\mathcal D_k(P)$ and  (2.3.3) gives  a constant
$M_k$ such that
\[
||S_k(f)||\leq M_k\cdot ||f||_k\quad\colon f\in  \mathcal D_k(P)
\]
where $M_k$ only  depends on the integer $k$ and the given
PDE-operator $P$. The next result constitutes  a crucial point
to attain Theorem 2.1.




\bigskip

\noindent
{\bf{2.6 Proposition.}}
\emph{For each $k\geq 2 $ there exists some
$\alpha(k)<0$ such that for every $0<\alpha<\alpha(k)$
the range of the operator $E-\alpha\cdot S_k$ contains
all periodic $C^\infty$-functions on
$[0,\pi]$.}
\bigskip

\noindent
{\bf{2.7 The density of $\mathcal D_k(P)$.}}
We prove Proposition 2.6 in ¤ xx  and proceed to show 
that it gives the density of
$\mathcal D_k(P)$.
For if $\mathcal D_k(P)$ fails to be dense there exists
a non-zero $f_0\in\mathcal D_k(P)$ which is
$\perp$ to $\mathcal D_k(P)$.
In Proposition 2.6 we choose $0<\alpha\leq \alpha(k)$ so small that
\[
\alpha<M_k/2\tag{i}
\]
Since periodic $C^\infty$-functions are dense in
$\mathcal H^k[0,\pi]$,
 Proposition 2.6 gives  a sequence
$\{h_n\}$ in $\mathcal D_k(P)$
such that
\[ 
\lim_{n\to \infty}\, ||h_n-\alpha\cdot S_k(h_n)-f_0||_k\to 0\tag{ii}
\]
It follows that
\[
\langle f_0,f_0\rangle=1=\lim\, 
\langle f_0,h_n-\alpha\cdot S_k(h_n)\rangle=
-\alpha\cdot \lim\, \langle f_0,S_k(h_n)\rangle\tag{iii}
\]
Next, the triangle inequality and (ii) give
\[
||h_n||_k\leq 1+\alpha\cdot ||(S_k(h_n)||
\leq 1+1/2\cdot||h_n||\implies
||h_n||_k\leq 2\tag{iv}
\]
Finally, by the Cauchy-Schwarz inequality the absolute value in
the right hand side of (iii) is majorized by
\[
\alpha\cdot M_K\cdot 2<1
\] 
which contradicts (iii).
Hence the orthogonal complement of $\mathcal D_k(P)$ is zero
which proves the requested density.
\medskip


\noindent
Together with Propostion 2.4.1  we get
the following conclusive result:
\medskip

\noindent
{\bf{2.8 Theorem.}}
\emph{For each  $k\geq 2$
and $f(x)\in \mathcal H^k[0,\pi]$
there exists a unique function
$F(x,s)\in \mathcal H^{(k)}$ such that (*) holds in
Definition 2.3.}
\medskip


\noindent
{\bf{2.9 Remark.}}
The result above soplves the requested boundsry valued problem in
$\mathcal H^{(k)}$ -spaces.
Using Sobolev  inequalities
oner easily derives Theorem  2.1.





\newpage

\centerline{\bf{¤ 3. A doubly periodic class of inhomogeneous PDE-equations.}}


\medskip

\noindent
Before Theorem 3.2 is announced we introduce some notations.
Put
\[ 
\square =\{ 0\leq x\leq \pi\}\times
\{0\leq s\leq 2\pi\}
\]
In this section we  shall consider doubly periodic functions
$g(x,s)$ on $\square$, i.e. 
\[
g(\pi,s)= g(0,s)\quad\colon g(x,0)= g(x,2\pi)
\]
For each non-negative integer
$k$
we denote by $C^k(\square)$ the space of $k$-times
doubly periodic continuously differentiable functions. 
If 
$g\in C^k(\square)$
we set
\[ 
||g||^2_{(k)}= \sum_{j,\nu}\, \int_\square
\bigl|\frac{\partial^{j+\nu}g}{\partial x^j\partial s^\nu}(x,s)\bigr|^2\, dxds
\]
with the double sum extended  pairs  $j+\nu\leq k$.
This gives the complex Hilbert space $\mathcal H^{(k)}$
after a completion of $C^k(\square)$ with respect
to the norm  above.
Recall  that a Sobolev inequality entails that 
a function $g\in\mathcal H^{(2)}$
is automatically continuous and doubly periodic  on
the closed square.
More generally, if $k\geq 3$ 
each
$g\in\mathcal H^{(k)}$ has continuous and doubly periodic derivatives
up to order $k-2$.
Next, consider a first order PDE-operator
\[
P=\partial_s-a(x,s)\partial_x-b(x,s)\tag{3.1}
\]
where $a$ andÊ$b$ are real-valued doubly 
periodic $C^\infty$-functions.
It is clear that
$P$ maps
$\mathcal H^{(k)}$ into $\mathcal H^{(k+1)}$
for every $k\geq 2$.
Keeping $k\geq 2$ fixed we set

\[
\mathcal D_k(P)=\{g\in\mathcal H^{(k)}\,\colon\,
P(g)\in\mathcal H^{(k)}\}
\]
Since $C^\infty(\square)$
is dense in
$\mathcal H^{(k)}$ this yields  a densely defined operator
\[
P\colon \mathcal D_k(P)\to \mathcal H^{(k)}\tag{i}
\]
In
$\mathcal H^{(k)}\times \mathcal H^{(k)}$ we get the graph
\[
\Gamma_k=\{(g,P(g)\colon\, g\in\mathcal D_k(P)\}
\]
Since $P$ is a differential operator we know from  general results 
that
$\Gamma_k$ is a closed subspace. Hence there exists
a densely defined linear operator
and closed operator on $\mathcal H^{(k)}$ which we 
denote by $\mathcal T_k$.
So here   $\mathcal D(\mathcal T_k)= \mathcal D_k$. Set
\[
\gamma_k=\{(g,P(g)\colon\, g\in C^\infty(\square)\}\tag{ii}
\]
This is a subspace of
$\Gamma_k$ and 
denote by
$\overline{\gamma}_k$
its closure taken in  $\mathcal H^{(k)}\times \mathcal H^{(k)}$.
Since $\Gamma_k$ is closed we have
\[
\overline{\gamma}_k\subset\Gamma_k
\]
We get
the densely defined linear operator
$T_k$ whose graph is
$\overline{\gamma}_k$. By this construction
$\mathcal T_k$ is an extension of
$T_k$ which in particular gives
the
inclusion
\[
\mathcal D(T_k)\subset\mathcal D(\mathcal T_k)\tag{iii}
\] 
Next, let $E$ be the identity operator
on
$\mathcal H^{(k)}$.
 With these notations we shall prove:

\bigskip

\noindent 
{\bf{3.2  Theorem.}}
\emph{For each integer $k\geq 2$ there exists
a positive real number $\rho(k)$ such that
the map}
\[
T_k-\lambda\cdot E\colon\mathcal H^{(k)} \to  \mathcal H^{(k)}  
\] 
\emph{is 
bijective
for every $\lambda>\rho(k)$.}
\medskip



\noindent
The proof requires several steps and is not finished until
¤ 3.x. First we shall study the adjoint operator $T_k^*$
and establish the following:
\medskip

\noindent
{\bf{3.3  Proposition.}}
\emph{One has the equality $\mathcal D(T_k^*)= \mathcal D_k(P)$
and there exists a bounded self-adjoint operator
$B_k$ on
 $\mathcal H^{(k)}$ such that}
 \[
 T_k^*=-\mathcal T_k+B_k
 \]
 

\medskip




\noindent{\emph{Proof of Proposition 3.3}}
Keeping $k\geq 2$ fixed we set $\mathcal H=\mathcal H^{(k)}$.
For each pair $g,f$ in $\mathcal H$
their inner product is defined by
\[
\langle f,g\rangle=
 \sum\, \int_\square
\frac{\partial^{j+\nu}f}{\partial x^j\partial s^\nu}(x,s)
\cdot
\overline{\frac{\partial^{j+\nu}g} {\partial x^j\partial s^\nu}}(x,s)
\, dxds
\]
where the sum is taken when
$j+\nu\leq k$.
Introduce the differential operator
\[
\Gamma= \sum_{j+\nu\leq  k}\, (-1)^{j+\nu}\cdot \partial_x^{2j}\cdot \partial_s^{2\nu}
\]
Partial integration gives
\[
\langle f,g\rangle=\int_\square\, f\cdot \Gamma(\bar g)\, dxds=
\int_\square\, \Gamma(f)\cdot\bar g\, dxds
\quad\colon\, f,g\in C^\infty
\tag{i}
\]
Now we consider the operator
$P=\partial_s-a\cdot\partial_x-b$ and 
get 
\[
\langle P(f),g\rangle=\int_\square\, P(f)\cdot \Gamma(\bar g)\,dxds\tag{ii}
\]
Partial integration identifies (ii) with
\[
-\int_\square\, f\cdot \bigl(\partial_s-\partial_x(a)-a\cdot\partial_x-b)\circ\Gamma(\bar g)\,dxds\tag{iii}
\]


\noindent
{\bf{1.1 Exercise.}}
In (iii)  appears the composed differential operator
\[
\partial_s-\partial_x(a)-a\cdot\partial_x-b)\circ\Gamma
\]
Show that in the ring of differential operators with
$C^\infty$-coefficients this differential operator can be written
in the form
\[
\Gamma\circ(\partial_s-a\cdot\partial _x-b)+Q(x,s,\partial_x,\partial_s)
\]
where $Q$ is a differential of order $\leq 2k$ 
with coefficients in $C^\infty(\square)$.
Conclude from the above that
\[
\langle Pf,g\rangle=-
\langle f,Pg\rangle+\int_\square\ f\cdot Q(\bar g)\,dxds\tag{1.1.1}
\]
\medskip

\noindent
{\bf{1.2 Exercise.}}
With $Q$ as above we have a bilinear form which sends a pair
$f,g$ in $C^\infty(\square)$ to 
\[
\int_\square\ f\cdot Q(\bar g)\,dxds\tag{1.2.1}
\]
Use partial integration and
the
Cauchy-Schwarz inequelity to show that
there exists a conatant $C$ which depends on $Q$ only such that
the absolute value of (1.2.1) is majorized by
$C_Q\cdot ||f||_k\cdot ||g||_k$.
Conclude that
there exists a bounded linear operator 
$B_k$ on $\mathcal H$ such that
\[
\langle f,B_k(g)\rangle=\int_\square\ f\cdot Q(\bar g)\,dxds\tag{1.2.2}
\]

\medskip

\noindent
{\bf{1.3 Proof that $B_k$ is self-adjoint}}
From the above we have
\[
\langle Pf,g\rangle=
-\langle f,Pg\rangle+
\langle f,B_k(g)\rangle\tag{1.3.1}
\]

\noindent
Keeping $f$ in $C^\infty(\square)$ we notice that
$\langle f,B_k(g)\rangle$ is defined for every
$g\in\mathcal H$.
From this the reader can check that (1.3.1) remains valid when
$g$ belongs to $\mathcal D(\mathcal T_k)$
which means that
\[
\langle Pf,g\rangle=
-\langle f,\mathcal T_kg\rangle+
\langle f,B_k(g)\rangle\quad\colon f\in C^\infty(\square)\tag{1.3.2}
\]

\medskip

\noindent
Moreover, when both $f$ and $g$ belong to $C^\infty(\square)$
we can
reverse their positions in (*) which gives
\[
\langle Pg,f\rangle=
-\langle g,Pf\rangle+
\langle g,B_k(f)\rangle\tag{1.3.3}
\]
Since $a$ and $b$ are real-valued it is clear that
\[
\langle Pg,f\rangle=-\langle f,Pg\rangle\tag{1.3.4}
\]
It follows that
\[
\langle f,B_k(g)=\langle g,B_k(f)\quad\colon f,g\in C^\infty(\square)\tag{1.3.5}
\]
Since this hold for all pairs of $C^\infty$-functions and
$B_k$ is a bounded linear operator on
$\mathcal H$ the density of $C^\infty(\square)$ entails that
$B_k$ is a bounded self-adjoint operator
on $\mathcal H$.



\medskip

\noindent
{\bf{ 1.4  The equality 
$\mathcal D(T_k^*)=
\mathcal D_k(P)$.}}
The density of $C^\infty(\square)$ in $\mathcal H$
entails that  a function $g\in \mathcal H$ belongs to $\mathcal D(T_k^*)$  
if and only if there exists a constant $C$ such that
\[
|\langle Pf,g\rangle|\leq C\cdot ||f||\quad\colon f\in C^\infty(\square)\tag{1.4.1}
\]
Since $B_k$ is a bounded operator,
(1.3.2) gives the inclusion
\[
\mathcal D_k(P)\subset
\mathcal D(T_k^*)\tag{1.4.2}
\]
To prove the opposite inclusion we use that
the $\Gamma$-operator is elliptic.
If $g\in \mathcal D(T_k^*)$
we have from (i) in ¤ 1.1:
\[
\langle Pf,g\rangle=\langle f,T_k^*g\rangle=
\int\, \Gamma(f)\cdot \overline{T_k^*(g)}\, dxds
\quad\colon f\in C^\infty(\square)
\]
Similarly
\[
\langle f,B_k(g)\rangle=
\int\, \Gamma(f)\cdot \overline{B_k(g)}\, dxds
\]
Treating $\mathcal T_k(g)$ as a distribution the equation
(1.3.2)  entails that
the elliptic operator $\Gamma$ annihilates
$T^*_k(g)-\mathcal T_k(g)+B_k(g)$.
Since both
$T^*_k(g)$ and $B_k(g)$ belong to $\mathcal H$
this implies by the general result in ¤ xx that
$\mathcal T_k(g)$  belongs to $\mathcal H$
which proves the 
requested equality (1.4) and at the same time the operator equation
\[
T_k^*=-\mathcal T_k(g)+B_k\tag{1.4.3}
\] 

\bigskip


\centerline {\bf{3.4  An inequality.}}
\medskip

\noindent
Let $f\in C^\infty(\square)$
and $\lambda$ is a positive real number.
Then
\[
||\mathcal T_k(f)-\frac{1}{2}B_k(f)-\lambda\cdot f||^2=
\]
\[
||\mathcal T_k(f)-\frac{1}{2}B_k(f)||^2+\lambda^2\cdot ||f||^2-
\lambda\bigl(\langle \mathcal T_k(f)-\frac{1}{2}B_k(f),f\rangle+
\langle f, \mathcal T_k(f)-\frac{1}{2}B_k(f)\rangle\bigr)
\]
The last term is $\lambda$ times
\[
\langle \mathcal T_k(f),f\rangle+
\langle f,\mathcal T_k(f)\rangle-\langle f,B_kf\rangle\tag{i}
\]
where we used that $B_k$ is symmetric.
Now $T_k=\mathcal T_k$ holds
on $C^\infty(\square)$ and the definition of adjoint
operators give
\[
\langle \mathcal T_k(f),f\rangle=
\langle f,T_k^*\rangle\tag{ii}
\]
Then (1.4.3) implies that (i) is zero and hence we have
proved 
\[
||T_k(f)-\frac{1}{2}B_k(f)-\lambda\cdot f||^2=
\lambda^2\cdot ||f||^2+||T_k(f)-\frac{1}{2}B_k(f)||^2\geq \lambda^2\cdot ||f||^2\tag{iii}
\]
From (iii)  and the triangle inequality for norms we obtain
\[
||T_k(f)-\lambda\cdot f||\geq \lambda\cdot ||f||-
\frac{1}{2}||B_k(f)||\tag{iv}
\]
Now $B_k$ has a finite operator norm and if
$\lambda\geq ||B_k||$ we see that 
\[
||T_k(f)-\lambda\cdot f||\geq
\frac{\lambda}{2}\cdot ||f||\tag{v}
\]


\noindent
Finally, since $C^\infty(\square)$ is dense in $\mathcal D(T_k)$
it is clear that (v) gives
\medskip


\noindent
{\bf{3.41 Proposition.}}
\emph{One has the inequality}
\[
||T_k(f)-\lambda\cdot f||\geq
\frac{\lambda}{2}\cdot ||f||\quad\colon f\in\mathcal D(T_k)\tag{3.4.1}
\]
\medskip

\centerline{\emph{¤ 3.5. Proof of Theorem 3.2}}
\bigskip

\noindent
Suppose we have found some
$\lambda^*\geq \frac{1}{2}\cdot ||B||$
such that
$T_k-\lambda$  has a dense range in $\mathcal H$
for every $\lambda\geq \lambda^*$.
If this is so we fix $\lambda\geq \lambda^*$
 and take some
$g\in \mathcal H$. The hypothesis gives a
sequence $\{f_n\in \mathcal D(T_k)\}$ such that
\[
\lim_{n\to\infty}\,||T_k(f_n)-\lambda\cdot f_n-g||=0
\]
In particular $\{T_k(f_n)-\lambda\cdot f_n\}$ is a Cauchy sequence 
in $\mathcal H$
and (1.5.x )  implies that $\{f_n\}$ is a Cauchy sequence 
in the Hilbert space $\mathcal H$
and hence converges to
a limit $f_*$. Since the operator $T_k$ is closed we conclude that
$f_*\in\mathcal D(T_k)$ and we get  the equality
\[
T_k(f_*)-\lambda\cdot f_*=g
\]
Since $g\in\mathcal H$ was arbitrary we have proved Theorem 3.2.

\bigskip

\noindent{\bf{3.5.1 Density of the range.}}
There remains to find $\lambda^*$ as above.
By the construction of adjoint operators, the range of $T_k-\lambda\cdot E$
fails to be dense
if and ony if
$T_k^*-\lambda$ has a non-zero kernel.
So assume that
\[ 
T_k^*(f)-\lambda\cdot f=0
\]
for some $f\in\mathcal D(T_k^*)$ which is not identically zero.
Notice that $T_k$ sends real-valued functions into real-valued
functions. So above we can assume that
$f$ is real-valued and 
normalised so that
\[
\int_\square f^2(x,s)\, dxds=1\tag{i}
\]
From (i) and Proposition 3.3 we have
\[
\mathcal T_k(f)+\lambda\cdot f-B(f)=0\tag{ii}
\]
Let us  consider
the function
\[ 
V(s)= \int_0^\pi\, f^2(x,s)\, dx
\]
Since $k\geq 2$ is assumed we recall  that
the $\mathcal H$-function $f$ is of class
$C^1$ at least. The $s$-derivative of $V(s)$ becomes:
\[ 
\frac{1}{2}\cdot V'(s)=  \int_0^\pi\, f\cdot \frac{\partial f}{\partial s}\, dx\tag{iii}
\]
By (ii) we have
\[
 \frac{\partial f}{\partial s}-
a(x)\frac{\partial f}{\partial x}-b\cdot f=B(f)-\lambda\cdot f
\]
\medskip

\noindent
Hence the right hand side in (iii) becomes
\[
-\lambda\cdot V(s)+ \int_0^\pi\, f(x,s)\cdot B(f)(x,s)\,dx
+ \int_0^\pi\,a(x,s)\cdot f(x,s)\cdot \frac{\partial f}{\partial x}(x,s)\,dx
\]
By partial integration the last term is equal to
\[
-\frac{1}{2}\int_0^\pi\, \partial_x(a)(x,s)\cdot f^2(x,s)\,dx\tag{iv}
\]
Set
\[
M=\frac{1}{2}\cdot \max_{(x,s )\in\square}\,|\partial_x(a)(x,s)|
\]
From the above  we get the inequality
\[
\frac{1}{2}\cdot V'(s)\leq
(M-\lambda)\cdot V(s)+\int_0^\pi\, f(x,s)\cdot B(f)(x,s)\,dx\tag{v}
\]
Set
\[
 \Phi(s)=\int_0^\pi\, |f(x,s)|\cdot |B(f)(x,s)|\,dx
\]
Since the $L^2$-norm of $f$ is one
the Cauchy-Schwarz inequality 
gives
\[
\int_{-\pi}^\pi \Phi(s)\,ds \leq
\sqrt{\int_\square\,  |B(f)(x,s)|^2\, dx ds}\leq ||B(f)||
\]
where the last equality follows since
the  squared integral of $B(f)$ is majorized by its squared
norm in $\mathcal H$.
When $\lambda>M$ it follows from  (v) that
\[
(\lambda-M)\cdot V(s)+
\frac{1}{2}\cdot V'(s)\leq\Phi(s)\tag{vi}
\]
Next, since $f$ is double periodic we have  $V(-\pi)= V(\pi)$
so after an integration (vi) gives
\[
(\lambda-M)\cdot \int_\pi^\pi V(s)\, ds=\int_{-\pi}^\pi \Phi(s)\,ds \leq ||B(f)||\tag{vii}
\]
Finally, thr normalisation (i) gives
$\int_\pi^\pi V(s)\, ds=1$ and then (vii) cannot hold
if
\[
\lambda>M+||B(f)||
\]

\medskip


\noindent
{\bf{Remark.}}
Set
\[ 
\tau=\min_f\,||B(f)||
\] 
with the minimum taken over
funtions $f\in\mathcal D(T_0^*)$ whose $L^2-$integral is normalised by
(i) above.  The proof has shown that
the kernel of $T_0^*-\lambda$ is zero for all $\lambda>M+\tau$.

\newpage


\centerline{\bf{A special solution.}}
\bigskip


\noindent
Let $f(x)$ be a periodic $C^\infty$-function 
on $[0,\pi]$.
Put
\[ 
Q= a(x,s)\cdot \frac{\partial}{\partial x}+ b(x,s)
\]
Let  $\eta(s)$ be a $C^\infty$-function of $s$ and 
$m$ some  positive integer
If $\lambda>0 $ is a real number.
we set
\[ 
g_\lambda(x,s)=\eta(s)\cdot f+\eta(s)\cdot\sum_{j=1}^{j=m}\,
\frac{(s-\pi)^j}{j!}\cdot (Q-\lambda)^j(f)\quad\colon 0\leq s\leq \pi\tag{i}
\]
We choose $\eta$ to be a real-valued $C^\infty$-function
such that
$\eta(s)=0$ when $s\leq 1/4$ and -1 if $s\geq 1/2$.
Hence $g_\lambda(x,s)=0$ in (i) when
$0\leq  s\leq 1/4$
and we extend the function to $[-\pi\leq s\leq \pi$ where
$g_\lambda(x,-s)= g_\lambda(x,s)$ if $0\leq s\leq \pi$.
So now $g_\lambda$ is $\pi$-periodic with respect to $s$
and  vanishes when
$|s|\leq 1/4$.
\medskip

\noindent
{\bf{Exercise.}}
If $1/2\leq s\leq \pi$ we have $\eta(s)=1$. Use (i) to show that 
\[
(P+\lambda)(g_\lambda)=
\frac{\partial g_\lambda}{\partial s}
-(Q-\lambda)(g_\lambda)=\frac{(s-\pi)^m}{m!}\cdot (Q-\lambda)^{m+1}(f)
\]
hold when
$1/2\leq s\leq \pi$.
At the same time
$g_\lambda(s)=0$ when $0\leq s\leq 1/4$.
So $(P+\lambda)(g)$
is a function whose derivatives
with respect to $s$ vasnish up to order
$m$ at $s=0$ and $s=\pi$ and is therefore
doubly periodic of class $C^m$ in
$\square$.
Now Theorem 2.2  applies. For a given $k\geq 2$
we choose a sufficently large $m$
and find $h(x,s)$ so that  
\[ 
P(h)+\lambda\cdot h=(P+\lambda)( g_\lambda)(x,s)
\]
where $h$ is $s$-periodic, i.e.
\[ 
h(x,0)= h(x,\pi)
\]
Notice also that
$g_\lambda(x,0)=0$ while $g_\lambda(x,\pi)= f(x)$.
Set
\[ 
g_*(x)=h-g_\lambda
\]
Then  $P(g_*)+\lambda\cdot g_*=0$
and 
\[ 
g_*(x,0)-g_*(x,\pi)=f(x)
\]
\medskip

\noindent
Above we started with the $C^\infty$-function.
Given $k\geq 2$
we can take
$m$ sufficiently large during the constructions above
so that $g_*$ belongs to
$\mathcal H^{(k)}(\square)$.




















\newpage

\centerline{\bf{The Schršdinger equation.}}

\bigskip


\noindent
We work in ${\bf{R}}^3$ with the coordinates
$(x,y,z)$. Let $c(x,y,z)$ be a real-valued function in 
$L^2_{\text{loc}}({\bf{R}}^3$.
In order that the subsequent
formulas can be stated in a precise manner we also assume that
$c$is almost everywhere continuous which of course is a rather weak condition and
in any case satisfied in applications.
Next, let $\Delta$ be the Laplace operator and
define the operator $L$ by

\[ 
L(u)=\Delta(u)+c\cdot u\tag{*}
\]
Denote by $E_L({\bf{R}}^3)$
the set of functions $u$ such that both
$u$ and $L(u)$ belong to $L^2({\bf{R}}^3)$. Given a
pair $(f,\lambda)$ where
$f\in L^2({\bf{R}}^3$
and $\lambda$ is a complex number
we seek solutions $u\in E_L({\bf{R}}^3)$ such that

\[ 
L(u)+\lambda\cdot u=f\tag{**}
\]
\medskip

\noindent
{\bf{The case $\mathfrak{Im}(\lambda\neq 0$.}}
By
a classic result about solutions to the Neumann
boundary value problem  in
open balls in ${\bf{R}}^3$ one proves that
(1) has at least one solution $u$ whenever $\lambda$ is not real.
The remains to investigate the uniqueness, i.e, when one has the implication


\[
\mathfrak{Im}(\lambda\neq 0\quad\text{and}\quad 
L(u)+\lambda\cdot u=0\implies u=0\tag{***}
\]
\medskip


\noindent
This uniqueness property depends on the $c$-function.
A sufficient  condition is the following:


\medskip

\
\medskip

\noindent
{\bf{Theorem.}} \emph{Assume that there exists a constant $M$
and some $r_*>0$ such that}
\[ 
c(x,y,z)\leq M
\quad\text{when}\quad x^2+y^2+z^2\geq r_*^2
\]
Then (***) above holds.


\bigskip


\noindent
{\bf{The spectral $\theta$-function.}}
When (***)  holds it was proved in
[Carleman] that
classical solutions to the Neumanns boundary value problem in
open balls yield a $\theta$-function
which enable us to describe  solutions to 
(*) for real $\lambda$-values.
More precisely, there exists two increasing sequence of positive real numbers
$\{\lambda^*(\nu)\}$ and $\lambda_*(\nu)\}$
and two sequence of pairwise orthogonal functions
$\{\phi_\nu(p))\}$ and $\{\psi_\nu(p)\}$ in $L^({\bf{R}})^3$
where all these functions have $L^2$-norm equal to one such that
the following hold. First, set 


\[
\theta(p.q,\lambda)= \sum_{0<\lambda^*(\nu)\leq\lambda}\, \phi_\nu(p)\cdot\phi_\nu(q)
\quad\colon\quad \lambda>0
\]

\[
\theta(p.q,\lambda)= -\sum_{\lambda\leq \lambda_*(\nu)\leq<0}
\, \psi_\nu(p)\cdot\psi_\nu(q)
\quad\colon\quad \lambda<0
\]
such that the following hold:
\bigskip

\[
v(p)=\lim_{R\to \infty}\, \sum_{[\lambda_\nu<R}\, 
\theta(p,q,\lambda)\cdot v(q)\cdot dq\quad\text{for all}
\quad v\in L^2({\bf{R}}^3)\tag{1}
\]

\[
v\in E_L({\bf{R})^3}\quad\text{if and only if}\quad
xxxx\tag{2}
\]

\[
L(v)(p)=
\lim_{R\to \infty}\, \sum_{[\lambda_\nu<R}\, 
\lambda\cdot [
\int_{{\bf{R}}^3}
\theta(p,q,\lambda)\cdot v(q)\cdot dq]\cdot d\lambda\quad\text{for all}\quad
v\in E_L({\bf{R}}^3)\tag{3}
\]
Here the equaliy holds in $L^2$, i.e, in the sense of a Plancherel's limit.
\medskip


\noindent
{\bf{Remark.}}
Here the equaliy holds in $L^2$, i.e, in the sense of a Plancherel's limit.


\medskip

\noindent
{\bf{Construction of the $\phi$-functions. }}
For each finite $r$ we have the ball $B_r$ and consider the space $E_L(B_r)$ of 
functions 
$u$ in $B_r$ such that both $u$
and $L(u)$ also belong to $L^2(B_r)$.
By a classical result in the Fredholm theory that
exist discrete sequences of real numbers
$\{\lambda*(\nu)$ and $\lambda_*(\nu)$ as above
and two families of orthonormal functions
$\{\phi^{(r)}_\nu\}$ and $\{\psi^{(r)}_\nu\}$
satisfying (xx) 

and here a classical result shows that the real eigenvalues 
to the equation $L(u)+\lambda\cdot u=0$
xxx

\[ 
xxx
\]


\noindent
The proofs of the assertions above rely on a systematic use of Green's formula.
To begin with we recall how to
express solutions to an inhomogeneous
the Laplace equation by an integral formula.
\medskip


\noindent
{\bf{A. The equation $\Delta(u)=\phi$}}.
let $D$ be a domain in
${\bf{R}}^3$ and $\phi$
a function in $L^2(D)$.
Then a function $u$ for which both $u$ and $\Delta(u)$ belong to
$L^2(D)$ gives $\Delta(u)=\phi$ if and only if
the following hold for every $p\in D$ and every 
$\rho<\text{dist}(p,\partial D)$:

\[
u(p)=
\frac{1}{2\pi \rho^2}\cdot \int_{B_p(\rho)}\,
\frac{1}{|p-q|}\cdot u(q)\cdot dq+
\frac{1}{4\pi \rho^2}\cdot \int_{B_p(\rho)}\,
A(p,q)\cdot \phi(q)\cdot dq\tag{i}
\]
where we have put

\[ 
A(p,q)= \frac{2}{\rho}-\frac{1}{|p-q|}-\frac{|p-q|}{\rho^2}\tag{ii}
\]
\medskip

\noindent
{\bf{Exercise.}} Prove this result.The hint is to apply Green's formula
while $\phi$ is replaced by $\Delta(u)$ in the last integral.
\medskip

\noindent
{\bf{Remark.}}
Let us also recall
also that when $\Delta(u)$ is in $L^2$, then $u$ is automatically
a continuous function in $D$.
\medskip


\noindent
{\bf{The class $\mathfrak{Neu}(B_r)$}}.
Let $B_r$ be the open ball of radius $r$ centered at the origin.
The class of functions $u$  which are continuous on the closed ball
and whose interior normal derivative
$\frac{\partial u}{\partial{\bf{n}}}$ is continuous on the boundary
$S^2[r]$ is denoted by
$\mathfrak{Neu}(B_r)$. 
\medskip


\noindent
{\bf{The Neumann equation.}}
Let $c(x,y,z)$ be a function in $L^2({\bf{R}}$
and consider also a pair $a,H$ where
$a$ be a continuous function on
$S^2[r]$ and 
$H(p,q)$ a continuous hermitian function on
$S^2[r]\times S^2[r]$, i.e.  $H(q,p)=\bar H(p,q)$ hold for all pairs 
of point $p,q$ on
the sphere $S^2[r]$.
With these notations the following hold:


\bigskip


\noindent
{\bf{Theorem}} For each $f\in L^2(B_r)$ and every
non-real complex number $\lambda$ there exists a unique $u\in 
\mathfrak{Neu}(B_r)$
such that $u$ satisfies the two equations:


\[ 
L(u+\lambda\cdot u=f\quad\text{holds in}\quad B_r
\] 

\[
\partial u/\partial {\bf{n}}(p)=xx
\]
Moreover, one has the $L^2$-estimate

\[
\int_{B_r}\, |u|^2\cdot dxdydz\leq
\bigl|\frac{1}{\mathfrak{Im}(\lambda)}\bigr|\leq
\int_{B_r}\, |f|^2\cdot dxdydz
\]












\newpage




Classic result: $R>0$ we have unit ball $B_R$ and unit sphere $S_R$.
Let $\mathfrak{Neu}(R)$
set uf $u$ -functions where $\Delta(u)$ in $L^2$, continuous on closed ball
and limit of interior derivative as a continuous funtion.
Given $c\in L^2(B_R)$ define

\[
L(u)= \delta(u)+c\cdot u
\]
\medskip


\noindent
{\bf{Theorem}} For each pair $(a,H)$ in (*) there exists a unique
$u\in \mathfrak{Neu}(R)$ such that
\[ 
L(u+\lambda\cdot u=f\quad\text{holds in}\quad B_R
\] 
and $u$ saisfies th boundsry condition

\[
\partial u/\partial {\bf{n}}(p)=xx
\]

from that $L^2$-esteimate as well.

\bigskip

Do if for $R=m$ running over positive integers.
Catch up sequence with $L^2$-convergence bounded uniformly.
$u_m\to u_*$ weak sense and see tha $u_*$ is a solution to (*) on al over space.

Second point about eventual uniquenss. Class I type. Euquialent condition-
















In an article from 1920 Carleman constructed an "ugly  example" of a doubly
indexed sequence
$\{c_{pq}\}$ of real  numbers
satisfying (1) and the symmetry condition
$c_{pq}=c_{qp}$, and yet there exists a non-zero complex vector
$\{x_p=a_p+ib_p\}$ in $\ell^2$ such that
\[ 
S(x)= ix\tag{4}
\]
This should be compared with
the finite dimensional case where
the spectral theorem due to Cauchy and Weierstrass asserts that
if
$A$ is a real and symmetric $N\times N$-matrix for some
positive integer $N$, then there exists an orthogonal
$N\times N$-matrix $U$ such that
$UAU^*$ is a diagonal matrix with real elements.
Carleman  extended this finite dimensional result 
to infinite Hermitian matrices 
for which the densely defined linear operator $S$ has no eigenvectors with
eigenvalue $i$ or $-i$.
More precisely, one says that
the densely defined operator $S$ is of Class  I
if the equations
\[
S(z)= iz\quad\colon S(\zeta)= -i\zeta\tag{*}
 \] 
 do not have non-zero solutions with complex vectors
 $z$ or $\zeta$ in $\ell^2$.
 The major result in the cited monograph is as follows:
 \medskip
 
 
 \noindent
 {\bf{0.0.1 Theorem.}}
\emph{Each densely Hermitian operator $S$ of Class I has  a unique
adapted resolution of the identity.}
\medskip



\noindent 
{\bf{0.0.2 Resolutions of the identity.}}
In order to digest Theorem 0.0.1
we recall the notion of spectral resolutions.
To begin with, a resolution  of the identity on
$\ell^2$ consists of a 
family $\{E(\lambda)\}$
of self-adjoint projections, indexed by real numbers
$\lambda$  which satisfies  (A-C) below.

\medskip

\noindent
{\bf{A}}. Each $E(\lambda)$ 
is an orthogonal projection from
$\ell^2$ onto the range $E(\lambda)(\ell^2)$ and 
these operators commute pairwise, i.e.
\[
E(\lambda)\cdot E(\mu)=
E(\mu)\cdot E(\lambda)\tag{i}
\]
hold for pairs of real numbers. 

\noindent {\bf{B}}.
To each pair of real numbers
$a<b$ we set
\[ 
E_{a,b}= E(b)-E(a)
\]
Then
\[
E_{a,b}\cdot
E_{c,d}=0\tag{iii}
\] 
for each pair of disjoint interval
$[a,b]$ and $[b,c]$.

\medskip

\noindent {\bf{C}}.
For each $x\in\ell^2$  the real-valued function 
\[ 
\lambda\mapsto\langle E(\lambda)(x),x\rangle\tag{c}
\] 
is  a non-decreasing and 
right continuous function.
\medskip



\noindent{\bf{0.0.3 $S$-adapted resolutions.}}
Let $S$ be a densely defined and hermitian linear operator on
$\ell^2$.
A spectral resolution  $\{E(\lambda)\}$ of the identity
is $S$-adapted if the following  three conditions hold:
\medskip

\noindent
{\bf{A.1}} For each interval bounded $[a,b]$ the range of
$E_{a,b}$ from (B) above
is contained in $\mathcal D(S)$
 and 
\[
E_{a,b}(Sx)=S\circ E_{a,b}(x)
\quad\colon x\in\mathcal D(S)
\]
\medskip

\noindent
{\bf{B.1 }} By (C)  each  $x\in\ell^2$
gives the non-decreasing function
$\lambda\mapsto\langle E(\lambda)(x),x\rangle$ on the  real line.
Together with the right continuity in (c) there exist
Stieltjes' integrals
\[
\int_a^b\, \lambda\cdot \langle dE(\lambda)(x),x\rangle
\] 
for each bounded interval.
Carleman's  second condition for 
$\{E(\lambda)\}$  to be $S$-adapted is that
a vector $x$ belongs to $\mathcal D(S)$ if and only if
\[
\int_{-\infty}^\infty \, |\lambda|\cdot \langle dE(\lambda)(x),x\rangle<\infty\tag{b.1}
\] 


\noindent
{\bf{C.1}} The last  condition is that
\[
\langle Sx,y\rangle=
\int_{-\infty}^\infty \, \lambda\cdot \langle dE(\lambda)(x),y\rangle
\quad\colon x,y\in\mathcal D(S)\tag{c.1}
\]
where (b.1) and the Cauchy-Schwarz inequality
entail that the Stieltjes' integral in (c.1) is absolutely convergent.
\bigskip


\end{document}








