%\documentclass{amsart}
%\usepackage[applemac]{inputenc}


%\addtolength{\hoffset}{-12mm}
%\addtolength{\textwidth}{22mm}
%\addtolength{\voffset}{-10mm}
%\addtolength{\textheight}{20mm}
%\def\uuu{_}


%\def\vvv{-}

%\begin{document}

\centerline{\bf\large{IV. Nevanlinna-Pick theory}}




\bigskip
\centerline{\emph{Contents}}


\bigskip

\noindent
\emph{0. The Nevanlinna-Pick Interpolation}

\bigskip

\noindent
\emph{1. The Lindelšf-Pick principle
with an application}

\bigskip

\noindent
\emph{2. A result by Julia}
\bigskip

\noindent
\emph{3. Geometric results by Lšwner}

\bigskip

\centerline{\bf{Introduction.}}

\bigskip

\noindent
In the unit  disc $D$ there exists the a metric defined by
\[ 
\frac{|dz|}{1-|z|^2}
\]
In a joint article from 1916, Lindelšf and Pick discovered that
if $f(z)\in\mathcal O(D)$ has maximum norm $\leq 1$, then
the map $z\to f(z)$ does not increase the metric (*).
This result turns out to be very useful and
is applied in  ¤ 2
to give a proof of a theorem due  Julia.
In ¤ 3 we prove some results due to Lšwner about
geometric properties of analytic mappings.
Section 0
is devoted to an
interpolation theorem
due to  Nevanlinna and Pick.
We give a detailed proof since the result has
a wide range of applications beyond analytic function theory
in various optimization problems.






\bigskip

\bigskip



\centerline{\bf 0. The Nevanlinna-Pick Interpolation Theorem}
\bigskip

\noindent
Let $D$ be the open unit disc.
Given an  $n$-tuple  of distinct points
$z_1,\ldots,z_n$ in $D$ and some $n$-tuple
$w_1,\ldots,w_n$ of complex numbers we put:
\[
\rho(z(\cdot),w(\cdot))= \min_{f\in\mathcal O(D)}\,
\,|f|_D\quad\colon\quad f(z_\nu)=w_\nu\quad\colon\, 1\leq\nu\leq n\tag{*}
\]
Thus we seek to interpolate preassigned values
at the points $\{z\uuu k\}$
with an analytic
function $f(z)$ whose maximum norm is minimal.
The case $n=1$ is trivial for then it is obvious that
the constant function $f(z)=w_1$ minimizes (*) so $\rho(z_1,w_1)=|w_1|$
hold for all $\alpha_1\in D$. If $n\geq 2$
there exists
at least some $f\in\mathcal O(D)$ which gives a minimum.
For let $\{f_\nu\}$
be a sequence of  functions which solve the interpolation
while their  maximum norms tend
to
$\rho(\alpha(\cdot),w(\cdot))$. This is a normal family
and hence we
extract a subsequence which
converges to a limit function $f_*$ whose maximum norm
is equal to $\rho(z(\cdot),w(\cdot))$.
It turns out
that the minimizing $f$ is unique and of a special form.
Before Theorem 1 is announced  we 
introduce the class
$\mathfrak{B}_{n\vvv 1}$ which consists of functions of the form:
\[ 
f(z)=e^{i\theta}\cdot \prod_{\nu=1}^{\nu=n\vvv 1}
\,\frac{z-\alpha_\nu}{1-\bar \alpha_\nu\cdot z}\tag{**}
\]
where  $0\leq\theta\leq 2\pi$ and $(\alpha_1,\ldots,\alpha_{n\vvv 1})$ is some 
$(n\vvv 1)$-tuple of  points in $D$ which are not necessarily distinct.


\bigskip

\noindent {\bf 0.1. Theorem}  \emph{For each pair of $n$-tuples $z(\cdot)$
and $w(\cdot)$
there exists a unique $f_*\in\mathfrak{B}_{n\vvv 1}$ 
and a positive real number $\rho$ such that
the  $\rho\cdot f_*(z)$
minimizes the interpolation (*).}
\bigskip


\noindent
{\bf{Remark.}}
With $\rho=\rho(z(\cdot),w(\cdot))$  the uniquenss
means that if $g\in\mathcal O(D)$ is an arbitrary
interpolating function which is $\neq f_*$ then
$|g|_D>\rho$.



\bigskip

\noindent
The proof of Theorem 0.1 requires several steps. 
First we shall establish a result about Blaschke products.






\medskip

\noindent
{\bf{0.3 Proposition.}}
\emph{Let $f$ be a function in
$\mathfrak{B}\uuu n$. For every 
$k(z)\in \mathcal O(D)$ with  maximum norm $|k|\uuu D= 1$
such that $f\vvv k$ has at least $n$ zeros counted with multiplicity in
$D$, it follows that $f=k$.}


\medskip



\noindent
\emph{Proof.}
We argue by a contradiction. If $k\neq f$
we
denote by $N(f-k:r)$ the number of
zeros of $f-k$ in $|z|<r$ counted with multiplicities.
The hypothesis gives some   $r_*<1$ such that
\[
N(k-f,r_*)\geq n\tag{ii}
\]
Next, to each 0$<r<1$ we set
\[
\mathfrak{m}(r)= \min\uuu\theta\, |f(re^{i\theta})\vvv k(re^{i\theta})|
\]
The hypothesis gives a sequence $\{r\uuu\nu\}$ such hat
$r\uuu\nu\to 1$ and every $\mathfrak{m}(r\uuu\nu)>0$.
Consider some $r\uuu\nu>r\uuu *$
and the analytic function

\[
h_\nu=\epsilon_\nu f+\frac{1}{2}(f-k)\quad\text{where}\quad
\epsilon_\nu=\frac{1}{4}\mathfrak{m}(r_\nu)\tag{iii}
\]
Since $|\frac{1}{2}(f-k)|>\epsilon_\nu \cdot |f|$ holds 
on the circle $|z|=r\uuu\nu$ it follows from
(i) and Rouche's theorem that we have:
\[ 
N(h_\nu : r_\nu)=N(f-k:r_\nu)\geq n\tag{iv}
\]
At the same time we can write
\[
h_\nu=(1+\epsilon_\nu)f-\frac{1}{2}(k+f)\tag{v}
\]
By assumption   $|k|_D=|f|_D=1$  and since $f$ is a finite
Blaschke product
its absolute value tends uniformly to zero as $|z|\to 1$. So
if $r\uuu\nu$ is sufficiently close to 1 we get:
\[ 
(1+\epsilon_\nu)\cdot |f(z)|>\frac{1}{2}|k(z)+f(z)|\quad\colon\quad |z|= r\uuu\nu\tag{vi}
\]
Then
another application of
Rouche's theorem gives:
\[
N(h_\nu : r)=N(f : r)\leq n-1\tag{vii}
\]
where the last inequality follows since
$f\in\mathfrak B_n$.
Now (vii) contradicts (iv) and hence we must have $k=f$
as requested.

\bigskip

\noindent
{\bf{A consequence.}}
Let $z(\cdot)$ and $w(\cdot)$ be some  pair of $n$\vvv tuples
and suppose there exists some $f\uuu *\in\mathfrak{B}\uuu {n\vvv 1}$
and some $\rho>0$
such that $\rho\cdot f\uuu *(z\uuu k)=w\uuu k$
hold for each $k$.
Then the function $f=\rho\cdot f\uuu *$ not only interpolates but it
has also the minimal maximum norm, i.e. we have the equality
$\rho=\rho(z(\cdot),w(\cdot))$.
For suppose we have strict inequality
$\rho(z(\cdot),w(\cdot))<\rho$ which gives an interpolating function $k(z)$
with maximum norm $|k|\uuu D<\rho$.
Since $|\rho\cdot f|=\rho$ holds on $|z|=1$ it follows by Rouche's theorem
that
$f$ and $f\vvv k$ has the same number of zeros i $D$.
Now $f\vvv k$ has at least $n$ zeros while $f$ has at most $n\vvv 1$
many zeros. This  contradiction and proves that
$f$ is minimizing and Proposition 0.2 entails also that
$f$ is uniquely determined in $\mathfrak{B}\uuu{n\vvv 1}$.
\medskip

\noindent
The results   above show that
there remains to establish an \emph{existence result}. Namely, there remains to prove
that for every given 
$n$\vvv tuple 
$z(\cdot)$ in $D$ and  an  arbitrary
$n$\vvv tuple 
$w(\cdot)$ of complex numbers,  there exists a pair  $f\uuu *\in\mathfrak{B}\uuu n$
and  $\rho>0$
such that $\rho\cdot f\uuu *$ solves the interpolation. Moreover, if the pair has been
found
then we have the equality
$\rho= \rho(z(\cdot),w(\cdot))$.
\medskip

\noindent
{\bf{0.4 Induction over $n$}}.
We shall prove the existence above by an induction over
$n$. First we establish a result where Mšbius transformations intervene.
To each  $n$\vvv tuple $(z\uuu 1,\ldots,z\uuu n)$
we denote   for every   $\rho>0$  the family  $I\uuu \rho(z(\cdot))$
of all $n$\vvv tuples $w(\cdot)$
such that $\rho(z(\cdot),w(\cdot))=\rho$.
\newpage


\noindent
{\bf{0.5 Exercise.}}
For each point $a\in D$ we have the Mšbius transformation
\[ 
M_a(z)=\frac{z-a}{1-\bar a z}
\]
If $f(z)\in \mathcal O(D)$
we get the new analytic function $f\circ M\uuu a$
which  has the same maximum norm as $f$. Use this to show that
\[ 
I\uuu \rho(z(\cdot ))=
I\uuu\rho(M\uuu a(z(\cdot)))
\]
hold for every $n$\vvv tuple $z(\cdot)$.
Thus, we can change the $z$\vvv points via a Mšbius transformation
without affecting the
$I\uuu\rho$\vvv sets.
\medskip

\noindent
{\bf{0.6 The induction step.}}
If $g\in\mathfrak {B}\uuu{n\vvv 1}$
and $|a|<1$  then the composed function $g\circ M\uuu a$
again belongs to
$\mathfrak {B}\uuu{n\vvv 1}$.
So by  Exercise 0.5 it suffices to establish the existence of
an interpolation $f\in\mathfrak{B}\uuu{n\vvv 1}$
when $z\uuu 1=0$.
So assume this and consider first the case $w\uuu 1=0$.
Then we seek $f$ of the form
\[ 
f(z)= z\cdot g(z)\tag{1}
\]
where $g$ satisfies $g(z\uuu k)=\frac{w\uuu k}{z\uuu k}$
when $2\leq k\leq n\vvv 1$. By an an induction over
$n$
we can find $g=\rho\cdot g\uuu *$ for some
$g\uuu *\in \mathfrak{B}\uuu{n\vvv 2}$ and 
(1) entails that
\[
f=\rho\cdot z\cdot g\uuu *
\] 
where $z\cdot g\uuu *$ belongs to
$\mathfrak{B}\uuu{n\vvv 1}$ which gives  the requested interpolating function. 
\medskip

\noindent
{\bf{The case $w\uuu 1\neq 0$ }}.
To begin with we find
$f\in\mathcal O(D)$ with the maximum norm
$\rho=\rho(z(\cdot),w(\cdot))$
such that $f(0)=w\uuu 1$ and $f(z\uuu k)=w\uuu k$
when $2\leq k\leq n$. Put
\[ 
\mu\uuu k=\frac{w\uuu k\vvv w\uuu 1}{1\vvv
\rho^{\vvv 2}\cdot \bar w\uuu 1\cdot w\uuu k}\tag{1}
\]
We have also the analytic function
\[ 
g(z)= \frac{f(z)\vvv w\uuu 1}{1\vvv
\rho^{\vvv 2}\cdot \bar w\uuu 1\cdot f(z)}
\]
Since $|f|\uuu D=\rho$ we also have $|g|\uuu D=\rho$ where
$g(z\uuu k)=\mu\uuu k$ for each $k\geq 2$ while $g(0)=0$.
In particular 
\[
(0,\mu\uuu 2,\ldots,\mu\uuu n)\in
I\uuu\gamma(0,z\uuu 2,\ldots,z\uuu n)\quad\text{where}\quad \gamma\leq\rho
\]
By the induction over $n$ and the previous special case we find
$f\uuu *\in\mathfrak{B}\uuu{n\vvv 2}$ such that the function
\[
g\uuu *=\gamma \cdot z\cdot f\uuu *
\]
takes the interpolating values
$(0,\mu\uuu 2,\ldots,\mu\uuu n)$.
Next,  there exists the analytic function
\[ 
\phi(z)=\frac{g\uuu *(z)+w\uuu 1}{1+\rho^{\vvv 2}\cdot \bar w\uuu 1\cdot g\uuu *(z)}
\]
If $\gamma<\rho$
we see that
the maximum norm
$|\phi|\uuu D<\rho$.
At the same time
(1) entails that $\phi(0)=w\uuu 1$ and
$\phi(z\uuu k)= w\uuu k$ for $k\geq 2$.
Since $\rho$ was the interpolation norm
for the pair $(0,z\uuu 2,\ldots,z\uuu n)$ and the $n$\vvv tuple
$w(\cdot)$ we have  contradiction. Hence  
$\gamma=\rho$ holds and from the above it follows that

\[
\rho\cdot \frac{zf\uuu *(z)+w\uuu 1}{1\vvv \rho^{\vvv 2}
\bar w\uuu 1 z f\uuu *(z)}
\]
takes the requested interpolation values
$(w\uuu 1,\ldots,w\uuu n)$ which
gives the induction step over $n$.
\bigskip
















\medskip

\noindent
{\bf{Remark.}}
Consider the case $n=2$ in Theorem 0.1 where we assume that
$w_1\neq w_2$.
Theorem 1 shows  that
there exists a unique triple
\[
(a,\theta,\rho)\quad
\text{where}\quad  a\in D\quad\colon 0\leq\theta\leq 2\pi\quad\colon\rho>0
\]
such that  function
\[
 f(z)=\rho\cdot e^{i\theta}\cdot \frac{z-a}{1-\bar a\cdot z}
\]
solves the interpolation problem.
\medskip

\noindent
{\bf{0.7 Exercise.}}
With $n=2$ and $z\uuu 1=0$ while $z\uuu  2\neq 0$
is kept fixed
we solve the interpolation for a given pair $(w\uuu 1,w\uuu 2)$,
The minimizing interpolation function is of the form
\[
f(z)=\zeta\cdot \frac{z+\frac{w\uuu 1}{\zeta}}{
1+\frac{\bar w\uuu 1\cdot  z}{\bar\zeta}}
\] 
for some $\zeta\neq 0$.
So here $\zeta$ satisfies the equation
\[
z\uuu 2\cdot\zeta+w\uuu 1=
w\uuu 2+w\uuu 2 \bar w\uuu 1\cdot z\uuu 2\cdot \frac{1}{\bar\zeta}
\]
Writing $w\uuu 2= w\uuu 1+\gamma$
this amounts to solve the equation
\[
z\uuu 2\cdot |\zeta|^2=\gamma\cdot \bar\zeta+|w\uuu 1|^2\cdot z\uuu 2+
\gamma\cdot \bar w\uuu 1\cdot z\uuu 2\tag{*}
\]
We assume that $w\uuu 2\neq w\uuu 1$ which means that
$\gamma\neq 0$ and that the minimizing function
$f$ is not reduced to a constant. Hence   its maximum norm
$|\zeta|$ must be $|w\uuu 1|$,
Theorem 1 implies that under these conditions
(*) has a unique solution $\zeta$ with absolute value 
$>|w\uuu 1|$.
It is interesting to
analyze how $|\zeta|$ depends on the triple $z\uuu 2,w\uuu 1w\uuu 2$.
Dividing (*) with $z\uuu 2$ and regarding
$\lambda=\gamma/z\uuu 2$ as a parameter which varies
we are led to  the equation
\[
|\zeta|^2\vvv \lambda\cdot \bar\zeta=  
|w\uuu 1|^2+\gamma\cdot \bar w\uuu 1
\]


\noindent
The reader is invited to analyze the behaviour of $|\zeta|$
with a special attention  to the case when
$z\uuu 2$ is close to the origin while
$\gamma$ stays fixed, So here 
the interpolating function $f$ takes quite distinct  values at 
the origin while   $z\uuu 2$. So  one expects that its maximum norm
increases. Here is

\medskip

\noindent {\bf{0.8 A specific example.}}
Let $\gamma=1$ and $z\uuu 2=\epsilon$ for some small positive 
$\epsilon$ while $w\uuu 1=a$ is real and positive.
So the equation becomes
\[ 
|\zeta|^2\vvv \frac{\bar\zeta}{\epsilon}
= a^2+a
\]
The solution $\zeta$ is therefore real
and we are led to the algebraic equation

\[
s^2\vvv \frac{s}{\epsilon}=a^2+a
\]
Notice that we require that $|\zeta|>|w\uuu 1|=a$
so we seek the unique root $s$ for which $s>a$ and it is given by
\[ 
s=\frac{1}{2\epsilon}+
\sqrt{a+a^2+
4^{\vvv 1}\epsilon^{\vvv 2}}
\]
With $a$ kept fixed we obtain 
$|\zeta|\simeq \frac{1}{\epsilon}$ as $\epsilon\to 0$
which illustrates that 
the maximum norm of
the
interpolating function increases when $\epsilon\to 0$.

\bigskip


\noindent{\bf{0.9 Interpolation constants.}}
Let $E=(z\uuu 1,\ldots,z\uuu n)$
be given. Each $f\in\mathfrak{B}\uuu{n\vvv1}$
has $n\vvv 1$ many roots counted
with multiplicities in
$D$. In particular $f$ cannot vanish identically on
$E$, i.e the maximum norm
\[ 
|f|\uuu E= \max\, |f(z\uuu k)|>0
\] 
This leads us to define the number
\[
\tau(E)=\min\uuu {f\in\mathfrak{B}\uuu {n\vvv 1}} \, |f|\uuu E
\]
We have also the interpolation number:
\[ 
\mathfrak{int}(E)= \max\uuu {w(\cdot)}\, \rho(z(\cdot),w(\cdot))
\]
with the maximum taken over all $w$\vvv sequences with
$|w\uuu k|\leq 1$ for every $k$.
With these notations one has the following result which is due to Beurling:


\newpage

\noindent
{\bf{0.9 Theorem.}} \emph{For every finite set $E$ one has the equality}
\[
\tau(E)=\frac{1}{\mathfrak{int}(E)}\tag{*}
\]


\noindent
\emph{Moreover,  a function $f\in\mathcal B\uuu {n\vvv 1}$
which gives $|f|\uuu E= \tau(E)$ is unique up to a constant
and for such an extremal $f$ one has $|f(\alpha\uuu k)|=\tau(E)$
for every $1\leq k\leq n$.}


\bigskip

\noindent
\emph{Proof.}
With $n$ kept fixed
the family of $\mathcal B\uuu{n\vvv 1}$
enjoys normal properties in the sense of Montel so it
follows  that there exists at least some
extremal $f\in\mathcal B\uuu{n\vvv 1}$ such that
$|f|\uuu E= \tau(E)$.
Now we prove that
$|f(\alpha\uuu k)|= \tau(E)$ for each $k$.
For suppose strict inequality holds at some
$\alpha$\vvv point which we can take to be
$\alpha\uuu 1$.
Consider the Blaschke product
\[ 
B(z)=\prod\uuu {k=2}^{k=n}
\,\frac{z\vvv \alpha\uuu k}{1\vvv \bar\alpha\uuu k\cdot z}
\]
Rouche's theorem gives some $\delta>0$ such that
if $|\zeta|<\delta$ then the analytic function
$f(z)+\zeta\cdot B(z)$ has $n\vvv 1$ zeros in $D$
and we can therefore write
\[
f(z)+\zeta\cdot B(z)=\rho(\zeta)\cdot \psi\uuu\zeta(z)\tag{1}
\]
where the $\zeta$\vvv indexed $\psi$\vvv functions 
belong to $\mathcal B\uuu {n\vvv 1}$
and $\rho(\zeta)$ are complex numbers.
Notice that
\[
f(\alpha\uuu k)= \rho(\zeta)\cdot \psi\uuu\zeta(\alpha\uuu k)\tag{2}
\] 
hold when $2\leq k\leq n$.
Moreover, since
$|f(\alpha\uuu 1)|<\tau(E)$
it is clear by continuity that
if $\delta$ is sufficiently small then
$|\psi\uuu\zeta(\alpha\uuu 1)|<\tau(E)$
when $|\zeta|<\delta$.
Since $f$ is extremal we conclude from
(2) that there exists $\delta>0$ such that
\[
 |\zeta|<\delta\implies |\rho(\zeta)|\geq 1\tag{3}
\]
This gives a contradiction
since the absolute value of the $\rho$\vvv function
cannot have a relative minimum at $\zeta=0$
by the local complex expansion
of this $\rho$\vvv function  in Chapter III:XX.
\medskip


\noindent
\emph{Uniqueness.}
Let $f$ and $g$ be two extremal functions
so that $|f|\uuu E= |g|\uuu E= \tau(E)$ and suppose they are not identical.
For each $\zeta$ where $|\zeta|<\delta$ for a sufficiently small $\delta$
we can write
\[
1\vvv \zeta)\cdot f+\zeta\cdot g= \rho(\zeta)\cdot \psi\uuu\zeta(z)
\]
with $\psi\uuu\zeta\in \mathcal B\uuu{n\vvv 1}$.
The triangle inequality gives
\[
|1\vvv \zeta)\cdot f(\alpha\uuu k)+\zeta\cdot g(\alpha\uuu k)|\leq
\tau(E)
\]
for every $k$ and since $|\psi\uuu \zeta|\geq \tau(E)$ we get as above
that $|\rho(\zeta(\geq 1$
whenever $\zeta$ is sufficiently close to zero.
This contradicts again the complex expansion of this
$\rho$\vvv function from Chapter III.
\medskip

\noindent
{\bf{The equality $\mathfrak{int}(E)= \frac{1}{\tau(E)}$.}}
To begin with, let $f$ be the unique  extremal   above which gives
an $n$\vvv tuple of points on the unit circle so that
\[ 
f(\alpha\uuu k)= \tau(E)\cdot e^{i\theta\uuu k}
\]
The Nevanlinna\vvv Pick theorem shows that
$\frac{f((z)}{\tau(E)}$
has smallest maximum norm over $D$ when 
the $n$\vvv tuple $\{w\uuu k= e^{i\theta\uuu k}\}$.
This implies that
\[
\mathfrak{int}(E)\geq \frac{1}{\tau(E)}
\]
To prove the opposite inequality
we consider some $n$\vvv tuple
$\{w\uuu \bullet\}$ for which the interpolating function
$g(z)$ has the maximum norm $|g|\uuu D=\mathfrak{int}(E)$.
Theorem 0.1 gives
\[
 g=\mathfrak{int}(E)\cdot f\quad\text{where}\quad f\in\mathcal B\uuu{n\vvv 1}
\]
This entails that
\[ 
\tau(E)\leq |f|\uuu E\leq
\frac{1}{\mathfrak{int}(E)}
\]
and the requested equality (*) in Theorem 0.9 follows.
 
 







\newpage











\

\centerline{\bf 1. The Lindelšf-Pick principle.}

\bigskip


\noindent {\bf Introduction.}
The non-euclidian metric on $D$
is defined by
\[ 
\frac{|dz|}{1-|z|^2}\quad\colon\, |z|<1\tag{0.1}
\]
When $D$ is equipped with this metric
one gets  a model of
hyperbolic geometry  in the sense of Bolyai and 
Lobatschevsky which led to an  intense geometric study
around 1890, foremost  by F. Klein and
H. PoincarŽ. We shall not enter a detailed discussion about
the geometry
since
our main concern  is to apply the  metric (0.1) to derive
inequalities for 
analytic functions.
In a work from 1916, Lindelšf and Pick
discovered that
very analytic function $\phi(z)$ in the unit disc with maximum norm
one at most decreases the
metric (0.1).
This result is called the Lindelšf-Pick principle
and is proved in Theorem XX below.
In section XX it is used to
prove a result by
Caratheodory and Julia concerned with the boundary behaviour
of analytic functions.

\bigskip












\noindent
{\bf{1. Schwarz' inequality}}
The non-euclidian distance between
two point  $z_1$ and $z_2$  in $D$
will be  denoted by
\[
 \mathfrak{h}(z_1,z_2)\tag{1.1}
\]


\noindent
To grasp this distance function we first notice the equality:
\[ 
\mathfrak{h}(0,z)=\frac{1}{2}\cdot
 \text{Log}\,\frac{1+|z|}{1-|z|}\tag{*}
\]
Indeed, (*) follows  since it is obvious from
(0.1) that the geodesic curve from the origin to a point  
 $z\in D$ is  the ray from 0 to $z$. So   with $|z|=r$
one computes
 \[ 
 \int_0^r\,\frac{ds}{1-s^2}
 \]
which after integration gives
(*).
Next, with $a\in D$ we consider a Mšbius transformation:
\[ 
w=\frac{z-a}{1-\bar a\cdot z}\implies
\frac{dw}{dz}= \frac{1-|a|^2}{(1-\bar a \cdot z)^2}
\]
At the same time we notice that
\[ 
1-|w|^2= \frac{|1-\bar a z|^2-|z-a|^2}{|1-\bar a \cdot z|^2}=
(1-|a|^2)\cdot\frac{1-|z|^2}{|1-\bar a \cdot z|^2}
\]
From this the reader may deduce that
the Mšbius transform preserves the $\mathfrak h$-metric.
\medskip

\noindent
{\bf 1.1 Example.} 
Take $z_1=1/2$ and $z_2=e^{i\theta}/2$
with some $0<\theta<\pi$.
Now
\[ z\mapsto \frac{z-1/2}{1-z/4}
\]
sends $z_1$ to the origin. It follows that
\[
\mathfrak{h}(1/2,e^{i\theta}/2)=
\frac{1}{2}\cdot
 \text{Log}\,\frac{1+r}{1-r}\quad\colon\, 
r=\frac{2\cdot |e^{i\theta}-1|}{|2-e^{i\theta}|}
\]


\noindent
The following
consequence of Schwarz inequality was discovered by
G. Pick in 1915. 


\medskip


\noindent 
{\bf 1.2 Theorem.}
\emph{Let $\phi\colon\,D\to\Omega$
be a conformal map from the unit disc onto a simply
connected domain contained in $|w|<1$. Then
the non-euclidian metric decreases.}
\medskip



\noindent \emph {Proof.}
Let $z_0\in D$ and set
$w_0=\phi(z_0)$. The quotient
\[ 
G(z)= \frac{\phi(z)-w_0}{1-\bar w_0\phi(z)} \, \colon\,
\frac{z-z_0}{1-\bar z_0z} 
\]
Since

\[ \lim\, \frac{|z-z_0|}{|1-\bar z_0z|}=1\quad\text{as}\quad |z|\to 1
\] 
we see that
$|G(z)|\leq 1$ holds for all $z\in D$. With $z=z_0$ we have
\[ 
G(z_0)= \phi'(z_0)\cdot \frac{1-|z_0|^2}{1-|\phi(z_0)^2|}
\]
Since $z_0\in D$ was arbitrary we get the
differential inequality
\[ 
\frac{|d\phi(z)|}{|1-\phi(z)|^2}\leq \frac{|dz|}{1-|z|^2}
\]
and this is precisely the assertion in Pick's theorem.

\medskip

\noindent
{\bf{The Lindelšf-Pick principle.}}
Above $\phi$ was a  conformal mapping.
Since the $\mathfrak{h}$-metric  is
defined locally the inequality in Pick's theorem extends to analytic functions
in $D$ of absolute value $<1$ and leads to the following general
result:
\bigskip

\noindent
{\bf 1.3 Theorem}
\emph{Let $\phi(z)\in\mathcal O(D)$ have maximum norm
$\leq 1$. Then $\phi$ decreases the $\mathfrak{h}$-metric.}
\medskip

\noindent
{\bf{Remark.}}
Thus, if we set $w=\phi(z)$ and
$z_1,z_2$ is a pair in the unit disc $D_z$ one has
\[ 
\mathfrak{h}(\phi(z_1),\phi(z_2))\leq
\mathfrak{h}(z_1),z_2)\tag{*}
\]
\medskip

\noindent 
{\bf 1.4 The $\mathfrak{h}$-metric in half-spaces.}
Passing to the right half-plane $U_+$ where
$\mathfrak{Re}(w)>0$,
the non-euclidian metric  is obtained via the conformal map
\[
z\mapsto w=\frac{1+z}{1-z}
\]
From this it follows that
\[ 
\frac{|dz|}{1-|z|^2}\mapsto
2\cdot\frac{|w+1|^4\cdot |dw|}{|w+1|^2-|w-1|^2}
\]
So with  $w=\xi+i\eta$ the non-euclidian metric in the right half-plane becomes
\[
\frac{|w+1|^4\cdot |dw|}{2\xi}\tag{*}
\]




\medskip

\noindent 
Next, 
the Lindelšf-Pick principle applies after
a conformal mapping from $D$ onto any other simply connected
domain $\Omega$ where one then
regards analytic functions $g\in\mathcal O(\Omega)$ such that
$g(\Omega)\subset\Omega$.
\medskip

{\noindent
{\bf 1.5 Example.}
Let 
$\Phi(z)=u(x,y)+iv(x,y)\in\mathcal O(U^+)$
be such that its real part $u$ is positive in $U_+$.
The Lindelšf-Pick principle applies to
$\Phi$ and using (*) in (1.4) one has the following result:

\medskip

\noindent
{\bf 1.6 Proposition.} \emph{To every $k>0$ there exists another
constant $k^*$ such that
the following inequality holds for
every pair of points $z_0=x_0+iy_0$ and $z_1=x_1+iy_1$ in $U_+$:}
\[
|\Phi(x_1+iy_1)|\leq |v(x_0+iy_0)|+k^*\cdot \frac{x_1\cdot u(x_0,y_0)}{x_0}
\quad\colon\, |y_1|<k\cdot x_1
\]


\noindent 
{\bf 1.7 Exercise.}
Try to prove this result. If necessary, consult
the text-book   [Nevanlinna: page 59-61]
for a proof where it is also shown
that for each $k>0$
one can take
\[
k^*=3+2(k+1)^2\quad\colon\,\,
\text{provided that}\,\, x_1>x_0\quad\text{and}\quad
x_1>|y_0|\tag{*}
\]

\newpage








\noindent
\centerline {\bf{2. A result by  Julia.}} 


\medskip

\noindent
Let $\phi\in\mathcal O(D)$
be such that $|\phi(z)|<1$ when $z\in D$ and 
consider the boundary point $z=1$.
\medskip

\noindent {\bf 2.1 Theorem.} \emph{For every $e^{i\theta}$
there exists the limit}
\[ 
c(\theta)=\lim_{z\to 1}\, \frac{|e^{i\theta}-\phi(z)|}
{|1-z|}\quad\colon 0\leq c(\theta)\leq +\infty\tag{1}
\]


\noindent
\emph{where the limit $z\to 1$ is taken in any Fatou sector at 1. Moreover,
if $\theta$ is such that the limit
$0<c(\theta)<\infty$ then 
there exist the Fatou limits}:
\[
\phi'(z)\to c(\theta)\cdot e^{i\theta}\quad\colon\,
\text{arg}\,\frac{e^{i\theta}-\phi(z)}{1-z}\to \theta\tag{2}
\]
\emph{and the following inequality holds}
\[ 
\frac{1-|\phi(z)|^2}{|e^{i\theta}-\phi(z)|^2}\geq
\frac{1}{c}\cdot \frac{ 1+|z|}{1-|z|}\quad\colon\, z\in D\tag{3}
\]
\medskip

\noindent
{\bf Remark.}
Of course, only the  case when
$c(\theta)<\infty$  is of  interest. Notice that this 
finiteness only can occur for at most one
$\theta$-value.
The
theorem  above was the starting point for an  extensive study of
boundary values of analytic functions in Julia's work
[Ju] and has  later led to a far-reaching study about 
Julia sets in  complex dynamics. See [Carleson-Garnett] for this more recent and
advanced theory in function theory.
The reader may also consult Chapter IV in [Caratheodory]
for an account of Julia's original theorem
where some geometric interpretations appear.

\bigskip



\centerline{\emph{Proof of Theorem 2.1}}
\medskip

\noindent
Applying the two  conformal mappings
\[
z\mapsto\frac{1+z}{1-z}\quad\colon\,w\mapsto
\frac{e^{i\theta}+w}{e^{i\theta}-w}
\]
we can work in the right
half plane where $z=1$  has been mapped into
the point at infinity and $\phi$ has become an analytic function
\[ 
\Phi(x+iy)=u(x+iy)+iv(x+iy)\quad\colon u(x,y)>0
\,\,\text{for all}\,\, (x,y)\in U_+
\]


\medskip


\noindent
The crucial step in the proof  is
to show the result below:
\medskip

\noindent 
\emph{Let $\Phi=u+iv$ be an arbitrary
analytic map from $U_+$ to $U_+$ and assume that}
\[ 
\min_{x+iy\in U_+}\, \frac{u(x+iy)}{x}=0\tag{*}
\]
\emph{Then it follows that}
\[ \lim_{x\to+\infty}\, 
\frac{u(x+iy)}{x}=0\quad\colon\, \text{holds uniformly
inside any  Fatou sector}
\,\,|y|<kx\quad\colon\, k>0
\]
\medskip

\noindent
To prove
this we take some
$k>0$ and for each  $\epsilon>0$
the hypothesis (*) gives a point
$z_0=x_0+iy_0$ in $U_+$ such that
\[ 
\frac{u(x_0,y_0)}{x_0}<\epsilon\tag{1}
\]
Next, if $z=x+iy$  stays in the Fatou sector
$|y|<k|x|$ and $x_1$ is large then   Proposition 1.6 gives:
\[
|\Phi(x+iy)|\leq
|v(x_0+iy_0)|+k^*\cdot \frac{x\cdot u(x_0+iy_0)}{x_0}
<|v(x_0+iy_0)|+\epsilon\cdot k^*\cdot x
\]
\medskip

\noindent
In particular we have
\[
\frac{u(x+iy)}{x}<\frac{|v(x_0+iy_0)|}{x}+\epsilon\cdot k^*
\]
Since $\epsilon>0$ can be chosen arbitrary small the conclusion after (*) follows.


\medskip

\noindent
\emph{Proof continued.}
Next, suppose that
\[ 
c=\min_{x+iy\in U_+}\, \frac{u(x+iy)}{x}>0\tag {1}
\]
is positive. The result above applies
to $\Phi(z)-cz$
and hence $\frac{\Phi(z)}{z}\to c$
holds uniformly  as $|z|\to\infty$ inside any Fatou sector
$|y|<k|x|$. Moreover, this
gives:

\[ 
\liminf_{x\to\infty}\,
\frac{u(x,y)}{x}=c\tag{2}
\]
\medskip

\noindent
Let us no consider the complex derivative of $\Phi$
assuming that (1) above holds for some
$c>0$.
\bigskip




\noindent
\emph{Sublemma}
\emph{One has}
\[
 \lim_{z\to\infty}\, \Phi'(z)=c
\]
\emph{where this limit holds uniformly while
$z$ stays in any given
Fatou sector.}
\medskip

\noindent
\emph{Proof.} Replacing $\Phi$ by $\Psi(z)=\Phi(z)-cz$
it suffices to show that
\medskip
\[ 
\lim_z\, \Psi'(z)=c\quad\colon\text{uniformly when the limit is in a Fatou sector}\tag{i}
\]


\noindent To show (i) we proceed as follows. Consider some
$0<p<1$ and choose also some $q$ so that
$p<q<1$.
For every $r>0$
we consider the disc 
\[
\Delta_r=\{|z-r|<q \cdot r\}
\]
Since $q<1$ this disc stays in
a fixed Fatou sector for all large $r$ and 
Cauchy's inequality gives
\medskip
\[ 
|\Psi'(z)|
\leq \frac{qr}{2\pi}\,\int_0^{2\pi}\,
\frac{|\Psi(r+qre^{i\theta})|}{
|r+qre^{i\theta}-z|^2}\cdot d\theta
\quad\colon\quad
z\in\Delta_r\tag{ii}
\]
\medskip

\noindent
Next, if $\epsilon>0$  Propostion 1.6 gives
some large $r^*$ such that 
\[
|\frac{\Psi(\zeta)}{\zeta}|<\epsilon\quad\colon 
|\zeta-r|= qr\quad\colon\, r\geq r^*\tag{iii}
\]
Hence, if $|z-r|\leq pr$, the Cauchy inequality from (ii)
and a  computation which is left to the reader
gives:
\[
|\Psi'(z)|\leq
\epsilon\cdot\frac{q(1+q)}{(q-p)^2}\tag{iii}
\]
\medskip

\noindent
This proves that
$\Psi'(z)\to 0$ holds uniformly when  $z$ stays in the sector
\[
|\text{arg}\, z|< \text{arc.sin}(p)
\]
Above $p<1$ is arbitrary
which therefore gives
the Caratheodory-Julia theorem after   we have  returned to
the unit disc  via a conformal map between  $D$ and 
$U_+$. 






\newpage

\centerline{\bf\large 3. Some geometric results}


\bigskip



\noindent
{\bf 3.1 A study of convex domains.}}
Let $\Omega$ be a bounded convex domain and  $p\in\Omega$ 
an interior point. The convexity implies that
if we start at some boundary  point $q_0\in\partial\Omega$ where
$q_0-p$ is real and positive, then we obtain a function
\[ 
\phi\mapsto q(\phi)\quad\colon\,
\text{arg}\,[q(\phi)-p\,]=\phi\quad\colon q(\phi)\in \partial\Omega\tag{*}
\]
where $q(2\pi)=q_0$ holds after one turn. The $q$-function is continuous and
1-1, i.e. a homeomorphism between the unit circle and
$\partial\Omega$. 
Let $g(\phi)$ be a
non-negative continuous function on $T$, i.e   here
$g(2\pi)=g(0)$. We get $g^*\in C^0(\partial\Omega)$ satisfying
\[ 
g^*(q(\phi))=g(\phi)
\]
Starting from $g^*$ we solve the Dirichlet problem and find the
harmonic function $G^*$ in $\Omega$ which extends $g^*$.
With these notations we have
\medskip


\noindent
{\bf Theorem 3.2} \emph{One has the inequality}
\[ 
G^*(p)\leq\frac{1}{\pi}\,\int_0^{2\pi}\, g(\phi)d\phi
\]


\noindent{\bf Remark.}
The inequality is of special interest when $p$ approaches the boundary.
Before Theorem 3.2 is proved we consider
a general situation.
Let $W$ be any bounded Jordan domain and $p\in W$
an interior point. Let $a,b$ be two points  on $\partial W$.
Denote by $\gamma$ the Jordan subarc of $\partial W$ 
which joins $a$ and $b$.
Let $L$ be the line passing through these two points.
Suppose that the two infinite half lines from $a$ and $b$ 
are outside $W$, i.e. $W\cap L$ is contained in
the line segment $(a,b)$.
Now $L$ cuts $W$ into two halfs. Let $W^*$ be one of these.
Given a point $p\in W^*$ we shall find an upper bound
for the harmonic measure
$\mathfrak{m}_W(p;\gamma)$.
After a rotation and a translation we may
assume that $a=m$ and $b=-m$ for some $m>0$, i.e. 
$[a,b]$ is an interval on the real axis and that $W^*$
is contained in the upper half plane $U^+=\mathfrak{Im}(z)>0$.
Now $W\subset U$ and Carleman's principle from XX
gives:

\[
\mathfrak{m}_W(p;\gamma)\leq
\mathfrak{m}_{W^*}(p:[a.b])\leq
\mathfrak{m}_U^+(p:[a.b])\tag {1}
\]


\noindent
By the result in XXX the last term is equal to $\frac{1}{\pi}\cdot\alpha$
where $\alpha$ is the angle formed by $a-p$ and $b-p$.
\bigskip



\noindent 
\emph{Proof of Theorem 3.2.}
Consider a small arc $\gamma\subset\partial\Omega$ 
which by the parametrisation (*) above is defined by some $\phi$-interval 
$\phi_*\leq\phi\leq\phi^*$.
Let $\mathfrak{m}_\Omega(p:\gamma)$ be the harmonic measure at
$p$ with respect to this boundary arc.
We can apply the  inequality (1)  and conclude that
\[
\mathfrak{m}_\Omega(p:\gamma)\leq \phi^*-\phi_*
\]
Now the Theorem  3.2 follows after an  integration over $0\leq\phi\leq 2\pi$
where we  use that $G^*(p)$ is evaluated by
the integral of $g^*$ over $\partial\Omega$
with respect to the positive measure on
$\partial\Omega$ defined by the harmonic measure at $p$.


\bigskip


\centerline {\bf 3.3. On the range of analytic functions}
\bigskip

\noindent
Consider a domain $\Omega\in \mathcal D(C^1)$.
Let $\phi\in\mathcal O(\Omega)$ and assume it  extends to
$C^0(\bar\Omega)$.
The $\phi$-function is not supposed to be 1-1.
We get the domain
\[
 W=\phi(\Omega)
\]
Now
the following may occur: There exists a subset
$\Gamma$ of $\partial\Omega$ given as a finite union of
arcs
$\{\gamma_\alpha\}$
such that the image set $\phi(\Gamma)$
gives the boundary $\partial A$ of a domain $A\subset W$, i.e. here 
$A$ is a relatively compact subset of the connected open set
$W$.
Put
\[
\Omega_*=
\{z\in\Omega\quad\colon\,\phi(z)\in W\setminus A\}
\]


\noindent
Here $A\subset\partial (W\setminus A)$
and  we construct a harmonic measures as follows: If
$z\in\Omega_*$ we have $\phi(z)\in W\setminus A$ and get
the function
\[ 
z\mapsto\mathfrak{m}_{W\setminus A}\,(\phi(z);\partial A)
\quad\colon\, z\in\Omega_*
\]
Since $w\mapsto\mathfrak{m}_{W\setminus A}(w;\partial A)$
is a harmonic function in $W\setminus A$ it follows that the function above is harmonic in
$\Omega_*$.
Let us analyze its boundary values on $\partial \Omega_*$.
If $z\in\Omega_*$ approaches $\Gamma$, then
$\phi(z)\to A$ and hence
\[ 
\lim_{z\to\Gamma}\,
\mathfrak{m}_{W\setminus A}\,(\phi(z);\partial A)=1
\]


\noindent
Let us now regard the harmonic measure function
\[ z\mapsto \mathfrak{m}_{\Omega_*}(z:\Gamma)
\]
By definition it has boundary value 1 along $\Gamma$ and otherwise it is zero. 
Hence the maximum principle for harmonic functions gives:

\bigskip
\noindent {\bf 3.4 Theorem.} \emph{In the situation above one has
the
inequality:}
\[
\mathfrak{m}_{\Omega_*}(z:\Gamma)\leq
\lim_{z\to\Gamma}\,
\mathfrak{m}_{W\setminus A}\,(\phi(z);\partial A)\quad\colon\quad 
z\in \Omega_*
\]


\noindent 
{\bf Application.}
Using Theorem 3.4 we  prove a result due to  Lšwner.
Let $w(z)\in\mathcal O(D)$ where $w(0)=0$ and
$|w(z)|<1$. Suppose there exists an arc $\gamma$ on the unit circle
such that $w(z)$ extends continuously up to $\gamma$ and that
\[ 
|\gamma(e^{i\theta})|= 1\quad\colon\quad e^{i\theta}\in\gamma
\]
Consider the image $w(\gamma)$ which 
is an another arc on the unit cicle.
With these notations  Theorem 3.4 gives
\medskip

\noindent 
{\bf 3.5 Lšwner's inequality.}
\emph{The length of $w(\gamma)$ is $\geq$ the length of $\gamma$
and equality can only hold if $w(z)$ from the start is
$e^{i\alpha}z$ for some $\alpha$.}
\bigskip

\noindent
{\bf 3.6 Remark.} Actually Lšwner proved a more precise 
result. Before it is announced  we insert a preliminary remark. 
Given $w(z)$ and an arc $\gamma\subset T$ where $|w(z)|=1$
one should expect that $|w(z)|$ must tend to 1 rather quick
as $z\in D$ approaches $\gamma$.
To put this in a precise form, Lšwner proceeds as follows:
Up to a rotation we may take
\medskip
\[ \gamma=\{ e^{i\theta}\quad\colon
-a<\theta<a\}\quad\colon\, 0<a<\pi/2
\]
Now we consider the family of 
circles $K_\lambda$ passing the two end-points
$e^{ia}$ and $e^{-ia}$ where $\lambda>0$
expresses
the angle of intersection beteen
$K_\lambda$ and the unit circle $T$.
\medskip

\noindent
The reader should  draw a picture to see the situation where
the constraint  that the $\lambda$-numbers are chosen
so that  obtain a simple connected domain $\Omega_\lambda\subset D$
bordered by $\gamma$ and a portion of $K_\lambda$.
Next,   regard the image set $w(\Omega_\lambda)$.
On its boundary we find the arc $w(\gamma)$ which by the
hypothesis that $|w|=1$ on $\gamma$, is a sub-arc
of $T$.
At the same time we 
can start with the arc
$w(\gamma)$ and take the circle $K^*_\lambda$
which passes the end-points of $w(\gamma)$. This
gives a domain $\Omega^*_\lambda$ bordered by
$w(\gamma)$ and a subarc of the circle
$K^*_\lambda$.
With these notations the precise  result by Lšwner goes as follows:
\medskip

\noindent {\bf 3.7 Theorem.}
\emph{For each $\lambda$ as above one has the inclusion}
\[ 
w(\Omega_\lambda)\subset \Omega^*_\lambda
\]
\medskip

\noindent
{\bf {3.8 Exercise.}}
Deduce  Theorem 3.7 from
Theorem 3.5. The strategy is that if 
$w(z)$ is \emph{outside} the set $\Omega_\lambda$
while $z\in \Omega^*_\lambda$, then
the inequality for harmonic measures is violated.
We leave it to the reader to discover this contradiction which gives
Lšwner's theorem.
See also his article [Lš:1]:\emph{Untersuchungen Ÿber
schlichte
konforme Abildungen} for details and further results.



\newpage








%\end{document}



