
%\documentclass{amsart}
%\usepackage[applemac]{inputenc}
%\addtolength{\voffset}{-10mm}
%\addtolength{\textheight}{20mm}
%\def\uuu{_}
%\def\vvv{-}
%\begin{document}



\centerline{\bf\large{14. Sets of harmonic measure zero }}
\bigskip



\noindent
{\emph{0. Introduction}}
\bigskip




\noindent
{\emph{A. Myhrberg's theorem}}
\bigskip


\noindent
{\emph{B. Equilibrium distributions
and Robin's constant.}}
\bigskip


\noindent
\emph {C. Cartan's theorem}





\bigskip
\noindent
\emph {D. Cantor sets.}


\bigskip



\centerline {\bf Introduction.} 

\bigskip

\noindent
The study of harmonic measures
and other areas in potential theory goes back to
a problem raised by G. Robin in the article [Rob]
from 1886 which had  
physical background in electric engineering.
The problem is: \emph{Let $E$ be a compact set in
${\bf{C}}$. Find a probability
measure $\mu$ on $E$ such that the function}
\[ 
U_\mu(z)=
\int_E\,\log\,\frac{1}{[z-\zeta|}\,\cdot d\mu(\zeta)\quad
\colon\, z\in{\bf{C}}\setminus E\tag{*}
\]
\emph{takes  constant boundary values on $E$.}
For every 
probability measure $\mu$ on $E$, i.e. a non\vvv negative
Riesz measure of unit  mass  supported by $E$, 
the integral (*) is defined for points in $E$
where the value can be finite or infinite.
To be precise, if $z\uuu *\in E$ is fixed and $n$ is a positive integer
we put $E\uuu n= E\setminus \{|z\vvv z\uuu *|\geq 1/n\}$. Since
$\log\,\frac{1}{|z\uuu *-\zeta|}\geq 0$ when $|\zeta\vvv z\uuu *|\leq 1$
it follows 
\[
n\mapsto \int_{E\uuu n}\,\log\,\frac{1}{|z\uuu *-\zeta|}\,\cdot d\mu(\zeta)
\]
is increasing and by  definition the integral (*) taken
on $E$ with $z=z\uuu *$ is equal to
the limit if (1) which therefore is  finite or $+\infty$.
Using the  limits above to compute
$U\uuu\mu(z)$ at points in $E$ it follows  that
the function
\[ 
z\mapsto U\uuu\mu(z)
\] 
is superharmonic function and 
always is harmonic in the open complement of $E$.
One refers to $U\uuu\mu(z)$ as the logarithmic potential of
$\mu$. 
\medskip


\noindent
{\bf{Energy integrals.}}
We can  integrate $U\uuu\mu$ with respect to
$\mu$, i.e. there exists a well defined Borel integral:
\[ 
J(\mu)=\int\, U\uuu\mu(z)\cdot d\mu(z)
\]
We refer to $J(\mu)$ as the energy integral of $\mu$. Notice that
the energy also is expressed  by a double integral:
\[
J(\mu)=\iiint \,\log,\frac{1}{|z-\zeta|}\,\cdot d\mu(\zeta)\cdot d\mu(z)
\]
\medskip

\noindent
We shall foremost study the case when $E$ is 
compact and
totally disconnected.  
So Perron's
criterium for a solution to the Dirichlet problem fails.
But it is still meaningful to speak about harmonic functions defined in
open complementary sets to $E$.
Notice also that if $z\uuu *\in E$ then we can construct arbitrary small Jordan
domains $U$ which where $z\uuu *$ is an interior point while the
closed Jordan curve $\partial U$ has empty intersection with $E$.
This leads to the following:

\medskip

\noindent{\bf{0.1 Definition.}}
\emph{A compact and totally disconnected set $E$
is a removable singularity for bounded harmonic functions if every bounded
harmonic function $H$ in $U\setminus E$ for a pair $(z\uuu *,U)$ as above
extends to a harmonic function in the whole Jordan domain $U$.}
\medskip

\noindent
{\bf{Remark.}}
This is a local condition at each point in $E$ and
the extensions  should hold at all points in $E$. 
The following result is due to Myhrberg.

\medskip

\noindent
{\bf{0.2 Theorem.}} \emph{A compact and totally disconnected set $E$
is a removable singularity for bounded harmonic functions if and only if
there exists a probability measure $\mu$ on $E$ such that
$U\uuu \mu(z)=+\infty$ for every $z\in E$.}

\medskip



\noindent
We prove this result in § A.
When the two equivalent conditions hold in Theorem 0.2  we say that
$E$ is a  harmonic null\vvv set.
Denote by $\mathcal N_{\text{harm}}$
the family  of totally 
disconnected sets   harmonic null\vvv sets.
One may ask for metric conditions in order that
a given compact and totally disconnected set $E$ belongs to
$\mathcal N_{\text{harm}}$. 
To analyze this we introduce  $h$-measures
where $h(r)$ is a continuous and non-decreasing function
defined for $r>0$ and $h(0)=0$.  If $F$ is a compact set
we  consider open coverings of $F$ by discs and
define its outer $h$-measure by
\[ 
h^*(F)=\min\, \sum h(r_\nu)
\] 
where the minimum is taken over
coverings of $F$ by open discs
$\{D_\nu\}$ of radius  $\{r_\nu\}$. 
The family of
compact sets whose outer $h$-measure is zero
is denoted by
$\mathcal N(h)$.
The case $h(r)=r^2$  means precisely that
$F$ has planar Lebesgue measure zero.
If $h(r)$ tends more slowly to zero as $r\to 0$
we get a more restrictive class, i.e. then
$\mathcal N(h)$ consists of sets which are more thin than sets
with 
planar Lebesgue measure zero.
In the case when
\[
h(r)=\frac{1}{\log\,\frac{1}{r}}
\] 
we say that a compact set in $\mathcal N(h)$
has
logarithmic capacity
zero .
The first major result
about harmonic null\vvv sets
was proved by 
Lindeberg in 1918 and goes as follows:

\medskip

\noindent
{\bf{0.3 Theorem.}} \emph{Let $E$ be a compact set whose logarithmic measure zero.
Then $E$ has harmonic measure zero.}


\medskip







\noindent
A  result
which
gives a necessary metric condition 
for a set $E$ to be a  harmonic null\vvv set
was proved by
Henri Cartan in [Cartan]. First we give:
\medskip

\noindent
{\bf 0.4 Definition}
\emph{Let $\mathfrak{H}_*$ denote
the class of 
non-decreasing and continuous function
$h(r)$ satisfying}
\[
 \int_0^1\,\frac{h(r)}{r}\cdot dr<\infty
\]


\bigskip

\noindent
{\bf 0.5 Theorem.} \emph{For every
$E\in\mathcal N_{\text{harm}}$
it follows that}
\[
E\in\mathcal N(h)=0\quad\colon\,\forall\,\, h\in \mathfrak{H}_*
\]





\noindent
{\bf 0.6 Remark.} 
Cartan's result   is
close to Lindeberg's sufficiency result.
Namely,  if $\eta>0$ we set
\[ 
h(r)=\frac{1}{
\bigl[\text{Log}\,\frac{1}{r}]^{1+\eta}}
\]
It is clear that
$h\in\mathfrak{H}_*$
and hence
$h^*(E)=0$ for every   $E\in\mathcal N_{\text{harm}}$.
With $\eta$ small this comes close to say
that the logarithmic capacity of $E$ is zero.
However, Cartan's Theorem 
does not give sufficient  conditions in order that a compact
and totally disconnected  set
$E$ has harmonic measure zero.
The search for other  metric conditions which
are either necessary or sufficient in  order that a compact set
has harmonic measure zero is unclear
and one should perhaps not  expect too much.
The text-book on \emph{Exceptional Sets} by
Carleson contains examples which illustrate the difficulty to get 
definite answers. However, 
a metric criterion for harmonic null\vvv sets exists
if 
$E$ is a Cantor set on a line. See XXX below.

\bigskip

\noindent
{\bf{0.7 Transfinite diameters and  the logarithmic capacity.}}
Let $E$ be a compact set which is assumed to be infinite.
Here we do not assume that $E$ is totally disconnected.
To each $n$\vvv tuple of distinct points
$z\uuu 1,\ldots,z\uuu n$ we put:
\[ 
L\uuu n(z\uuu\bullet)=\frac{1}{n(n\vvv 1)}\cdot
\sum\uuu {k\neq j}\,
\log\,\frac{1}{|z\uuu j\vvv z\uuu k|}
\]
Then we define the number
\[ 
\mathcal L\uuu n(E)=\min \, L\uuu n(z\uuu\bullet)
\]
where the minimum is taken over all $n$\vvv tuples in $E$.
Since $\log\,\frac{1}{r}$ is large when $r\simeq 0$ this means intuitively that
we tryo to choose separated $n$\vvv tuples in order to
minimize the $L\uuu n$\vvv function.
Notice for example that when $n=2$ then
the minium is achieved for a pair of points in $E$ whose
distance is maximal, i.e. $\mathcal L\uuu 2$ is the diameter of $E$.
As $n$ increases one has

\medskip

\noindent
{\bf{0.8 Proposition.}}
\emph{The sequence $\{\mathcal L\uuu n\}$ is non\vvv decreasing.}

\medskip

\noindent
\emph{Proof.}
Let $z\uuu1,\ldots,z\uuu{n+1}$ minimize  the $L\uuu{n+1}$\vvv
function which gives
\[
\mathcal L\uuu{n+1}(E)=\frac{1}{n(n+1)}\cdot
\sum^{(1)}\uuu {k\neq j}\, \log\,\frac{1}{|z\uuu j\vvv z\uuu k|}
+\frac{2}{n(n+1)}\cdot\sum\uuu{k=2}^{k=n+1}\log\,\frac{1}{z\uuu 1\vvv z\uuu k|}
\]
where $(1)$ above the sum above means that we only consider pairs
$k,j$ which both are $\geq 2$.
Since $z\uuu 2,\ldots,z\uuu {n+1}$ is an $n$\vvv tuple we get the inequality
\[ 
\mathcal L\uuu{n+1}(E)\geq 
\frac{1}{n(n+1)}\cdot  n(n\vvv1)\cdot \mathcal L\uuu n(E)
+\frac{2}{n(n+1)}\cdot\sum\uuu{k=2}^{k=n+1}\log\,\frac{1}{z\uuu 1\vvv z\uuu k|}
\]
The same inequaliiy holds when when we instead of $z\uuu 1$ delete some
$z\uuu j$ for $2\leq j\leq n+1$
and taking the sum of the resulting inequalities we obtain
\[
(n+1)\mathcal L\uuu{n+1}(E)\geq 
\frac{1}{n}\cdot n(n\vvv1)\cdot \mathcal L\uuu n(E)+
\frac{2}{n(n+1)}\cdot\sum\uuu{k\neq j}\log\,\frac{1}{|z\uuu j\vvv z\uuu k|}
\]
The last term is $2\cdot \mathcal L\uuu{n+1}$ which gives:
\[
(n\vvv 1)\cdot \mathcal L\uuu{n+1}(E)\geq 
\frac{1}{n}\cdot n(n\vvv1)\cdot \mathcal L\uuu n(E)=(n\vvv 1)\mathcal L\uuu n(E)
\]
A division by $n\vvv 1$ gives the requested inequality.
\medskip

\noindent
{\bf{0.8 Definition.}}
\emph{Put}
\[
\mathfrak{D}(E)=
\lim\uuu{n\to\infty}\, e^{\vvv \mathcal L\uuu n(E)}
\]
\emph{This non\vvv negative number is called the transfinite diameter of $E$.}
\medskip

\noindent
{\bf{Remark.}} The definition means that
$\mathfrak D(E)=0$ if and only if
$\mathcal L\uuu n(E)$ tends to $+\infty$ as $n$ increases.
Intuitively this means that we are not able to choose  large tuples in $E$ separated
enough to keep  the sum of the $\log$\vvv terms bounded.
Another number is associated to $E$ is defined by:
\[
\mathcal J\uuu *(E)= \min\uuu\mu\, J(\mu)
\] 
where the minimum is taken over all probability measures in
$E$. 

\medskip

\noindent
{\bf{0.9 Definition.}}
\emph{The  
logarithmic capacity of $E$ is defined by:}
\[
\text{Cap}(E)=e^{\vvv J\uuu *(E)}
\]



\noindent
{\bf{0.10 Theorem.}}\emph{ For each compact set $E$ one has the equality}
\[
\text{Cap}(E)=\mathfrak D(E)
\]


\noindent
\emph{Proof.}
First, let $n\geq 2$ and $z^*\uuu 1,\ldots,z^*\uuu n$
is some $n$\vvv tuple where $L\uuu n(z\uuu\bullet)= \mathcal L\uuu n(E)$.
Now we have the probability measure
\[ 
\mu= \frac{1}{n}\cdot \sum\uuu{k=1}^{k=n}\,\delta\uuu{z\uuu k}
\]
It is clear that
the energy
\[ 
J(\mu)= \frac{n(n\vvv 1)}{n^2}\cdot L\uuu n(z\uuu\bullet)
\]
Hence we have the inequality
\[ 
\mathcal J\uuu *(E)\leq  \frac{n(n\vvv 1)}{n^2}\cdot\mathcal L\uuu n(E)
\]
Since $\frac{n(n\vvv 1)}{n^2}$ tends to one as $n\to\infty$
a passage to the limit gives:
\[
\mathcal J\uuu *(E)\leq \lim\uuu{n\to\infty}\, \mathcal L\uuu n(E)
\]
Taking exponentials and recalling the negative signs in Definition x and x 
we conclude that
\[
\mathfrak{D}(E)\leq\text{Cap}(E)\tag{i}
\]
The opposite inequality follows since
we can approximate probability measures on $E$
by discrete measures.
Leave this as a TRIVIAL EXERCISE, 
\bigskip










\centerline{\bf{A. Proof of Myhrberg's theorem}}

\bigskip

\noindent
When $E$ is totally disconnected
we can  surrender $E$ by
open sets $\Omega$ such that
Dirichlet's problem has a solution in
the exterior domain
${\bf{C}}\setminus\bar\Omega$.
After a suitable passage to the limit as these domains shrink to $E$
we obtain a
special measure supported by $E$. To obtain this we employ
a construction which was introduced in the present context
by
De Vallé Poussin.
\medskip

\noindent
{\bf{A.1 Nested coverings }}
Let $E$ as above be a totally disconnected
and compact set and consider  some  $z\uuu *\in E$.
Choose a small Jordan domain $U$ which contains $z\uuu *$
while $\partial U\cap E=\emptyset$.
In particular can take $U$ to be contained in the disc
of radius 1/2 centered at $z\uuu *$ which  gives 
\[
|z\uuu 1\vvv z\uuu 2|<1
\] 
for each pair $z\uuu 1,z\uuu 2$ in $E\cap U$.
To compensate for the failure of solving Dirichlet's problem
we construct 
a sequence of open sets $\{V_N\}$ as follows.
For each positive integer $N$ one has  the dyadic grid
$\mathcal D_N$
of open squares whose sides are $2^{-N}$.
We get the finite family
$\mathcal D_N(E)$ of  dyadic squares in $\mathcal D_N$
which have a non-empty intersection with
$E$. The union of this finite 
family of open squares gives an open neighborhood $V_N$ of $E$. 
We consider only large $N$ so that
$2^{-N}$ is strictly larger than the distance of $E$ to $\partial U$.
Let $\Omega^*_N$ be the exterior connected component of
$D\setminus \bar V_N$ whose closure contains $\partial U$.
\medskip

\noindent
{\bf{A.2 Exercise.}}
Show by a figure
that
$\Omega^*\uuu N$
is a doubly connected domain whose boundary is the disjoint union of
$\partial U$ and a closed Jordan curve $\Gamma\uuu N$
formed by line segments from squares in the dyadic grid.
Notice also that
$\{\Omega^*\uuu N\}$ form an increasing sequence of
open sets where $\Gamma\uuu N$ appears as a compact subset
of $\Omega^*\uuu{N+1}$ for each $N$ and conclude that
\[
 \cup\,\, \Omega_N^*=D\setminus E
\]
\medskip



\noindent
Next, fix some point $z_0\in D\setminus E$ and  from now on $N$ are so large that
$z\uuu 0\in \Omega^*\uuu N$ hold.
The Dirichlet problem has a solution in
each domain $\Omega^*\uuu N$.
This gives a unique pair of non\vvv negative measures
$\mu\uuu N,\gamma\uuu N$
where $\mu \uuu N$ is supported by $\Gamma\uuu N$ and $\rho \uuu N$
by $\partial U$ such that
\[
h(z_0)=
\int_{\Gamma \uuu N}
\, h(\zeta)\cdot d\mu_N(\zeta)+
\int_{\partial U}\,h(\zeta)\cdot d\rho_N(\zeta)\tag{*}
\] 
hold for every $h$-function which
is harmonic
in $\Omega^*_N$ with continuous boundary values.
In particular we let $h$ be the harmonic measure function
$\mathfrak m\uuu N$
with respect to
$\Gamma\uuu N$, i.e. it is 1 on $\Gamma\uuu N$ and zero on
$\partial U$.
Then
\[ 
\mathfrak{m}\uuu N(z\uuu 0)=
\int_{\Gamma \uuu N}
\, d\mu_N(\zeta)=||\mu\uuu N||\tag{**}
\]
Since $\Gamma\uuu N\subset \Omega^*\uuu {N+1}$
we have $\mathfrak{m}\uuu {N+1}\leq
\mathfrak{m}\uuu N$ in $\Omega^*\uuu N$
which implies that
\[
||\mu\uuu {N+1}||\leq ||\mu\uuu N||
\]
for each $N$. Hence there exists the limit
\[
\alpha=\lim\uuu{N\to\infty}\, ||\mu\uuu N||\tag{***}
\]










\medskip


\noindent
{\bf{A.3 The case $\alpha=0$.}}
When this holds the mass of $\rho\uuu N$ tends to one and
since (*) in particular hold for $h$\vvv functions which are harmonic in
the whole set $U$ with continuous boundary values on $\partial U$
the reader may verify:

\medskip

\noindent
{\bf{A.4 Proposition.}}
\emph{If $\alpha=0$
the sequence  $\{\rho\uuu N\}$ converges weakly to
the representing measure $m(z\uuu 0)$ for which}
\[ 
H(z\uuu 0)= \int\uuu{\partial U}\, H(\zeta)\cdot dm(z\uuu 0,\zeta)
\]
\emph{when $H$ is harmonic in $U$ and continuous on $\bar U$.}
\medskip

\noindent
Keeping the case A.3 we can apply the result in
Exercise A.4 and obtain the following crucial result.

\medskip

\noindent
{\bf{A.5 Proposition.}}
\emph{When A.3 holds there exists a pair of positive numbers
$0<a<A$ such that}

\[
a\leq 
\int_{\Gamma \uuu N}
\, \log\,\frac{1}{|\zeta\vvv w|}
\cdot d\mu_N(\zeta)\leq A
\]
\emph{hold for all $w\in E$ and every $N$.}
\medskip

\noindent
{\bf{A.6 Exercise.}} Prove this result. Here is a hint in the  case when
$U$ is the unit disc so that $\partial U=T$ is the unit circle.
If $w\in E$ we have 

\[ 
|e^{i\theta}\vvv w|= |1\vvv \bar w\cdot e^{i\theta}|
\]
This gives the equality
\[
\int_T
\, \log\,\frac{1}{|\zeta\vvv w|}\cdot d\rho\uuu N(\zeta)=
\int_T
\, \log\,\frac{1}{|1\vvv \bar w\zeta|}\cdot
d\rho\uuu N(\zeta)\tag{i}
\]
Next, in $D$ we have
the harmonic function $H(z)=
\log\,\frac{1}{|1\vvv \bar w z|}$ in $D$ and Exercise A.4 
together with (i) give

\[
\log\,\frac{1}{|1\vvv \bar w z\uuu 0|}=
\lim\uuu{N\to\infty}\, 
\int_T
\, \log\,\frac{1}{|\zeta\vvv w|}\cdot d\rho\uuu N(\zeta)\tag{ii}
\]
At the same time
(**)  applied with $h(z)= \log\,\frac{1}{|z\vvv w|}$
gives

\[
 \log\,\frac{1}{|z\uuu 0\vvv w|}=
\int_{\Gamma\uuu N}
\, \log\,\frac{1}{|\zeta\vvv w|}\cdot d\mu\uuu N(\zeta)+
\int_T
\, \log\,\frac{1}{|\zeta\vvv w|}\cdot d\rho\uuu N(\zeta)\tag{iii}
\]
 By (ii) the last integral converges to
 $\log\,\frac{1}{1\vvv \bar wz\uuu 0|}$
which entails that
\[
\lim\uuu{N\to \infty}\, \int_{\Gamma\uuu N}
\, \log\,\frac{1}{|\zeta\vvv w|}\cdot d\mu\uuu N(\zeta)
= \log\frac{1\vvv \bar wz\uuu 0|}{|z\uuu 0\vvv w|}
\]
Since $|z\uuu 0|<1$ and there is some $r<1$ such that
$|w|\leq r$ for every $w\in E$
the last term is between $a$ and $A$ for a pair of positive numbers
which proves Proposition A.5 in the case when $U=D$. For a general Jordan
domain the reader can deduce the requested result using a conformal map or
suitable Green's functions in $U$ adapted to the point $z\uuu 0$.
\medskip

\noindent
{\bf{A.7 The limit measure $\mu\uuu *$.}}
Keeping A.3 we have the probability measures
\[ 
\nu\uuu N=\frac{1}{||\mu\uuu N||}\cdot \mu\uuu N
\]
We can extract a subsequence which converges weakly to a probability measure
$\mu$ which by (xx) is supported by $E$.
For this limit measure the following holds:

\medskip

\noindent
{\bf{A.8 Proposition.}}
\emph{The potential function $U\uuu\mu$ is $+\infty$ on $E$ 
except possible at a finite set of points.}
\bigskip

\noindent
\emph{Proof.}
GIVE IT is easy ...


\bigskip


\noindent
{\emph{A.9 Final part of the proof of
Theorem 0.2.}}
Suppose first that $E$ is a removable singularity for bounded
harmonic functions.
Working locally as above around  
some $z\uuu *\in E$ and a Jordan domain $U$,
we obtain for each $N$ the harmonic measure function
$\mathfrak m\uuu N$ in $\Omega^*\uuu N$.
They take values in $(0,1)$ and passing to a subsequence we obtain
a bounded harmonic limit function $\mathfrak m\uuu *$
defined in $U\setminus E$.
By construction $\mathfrak m\uuu *=0$ on $\partial U$
so if it extends to a harmonic function in $U$ it must be identically zero. This entails that
\[
\lim\uuu{N\to\infty}\, 
\mathfrak m\uuu N(z\uuu 0)=0
\]
Now we recall that
$\mathfrak m\uuu N(z\uuu 0)=||\mu\uuu N||$ and conclude that
A.3 holds which by Theorem XX gives the existence of
a probability measure  $\mu$ on $E$ such that
$U\uuu \mu(w)=+\infty$ for all $w\in E\cap\,U$.
\medskip

\noindent
\emph{The converse.}
Assume that there exists $\mu$ on $E$ for which
$U\uuu \mu(w)=+\infty$ for all $w\in E$.
Given a large positive constant we consider the open subset of $U$ defined by
\[
\{z\in U\quad\colon\quad U\uuu\mu(z)>C\}
\]
By the hypothesis this is an open neighborhood of $E\cap U$
so when $N$ is large we have $U\uuu\mu\geq C$ on $\Gamma\uuu N$.
Next,  $U\uuu\mu$ restricts to a continuous function on
$\partial U$ and we find its harmonic extension $H(z)$ to the whole Jordan domain $U$.
Now $U\uuu\mu\vvv H$ is harmonic in $\Omega^*\uuu N$
and if $C\uuu *$ is the maximum of $H$ on $\Gamma\uuu N$
it follows that $U\uuu\mu\vvv H\geq C\vvv C\uuu *$ on
$\Gamma\uuu n$. This gives the inequality
\[
\mathfrak m\uuu N(z\uuu 0)\leq
\frac{1}{C\vvv C\uuu *}\cdot 
[U\uuu\mu(z\uuu 0)\vvv H(z\uuu 0)]
\]
Here we can start with arbitrary
large $C$ and get (xx) for sufficiently large $N$ which entails that
\[
\lim\uuu{N\to\infty}\, \mathfrak m\uuu N(z\uuu 0)=0
\] 
The conclusion is valid for any starting point 
$z\uuu 0\in U\setminus E$ and
let us  consider a bounded harmonic function $h$ in $U\setminus E$
with continuous boundary values on $\partial U$.
It can be restricted to $\Omega^*\uuu N$ for every $N$. In
A.2 we could have started with an arbitrary point $z\uuu 0\in
U\setminus E$ and 
by (*) from A.2 we have
\[ 
h(z\uuu 0)=
\]
Passing to the limit as $N\to\infty$ it follows from (x) and
the discussion in (xx) that
\[
h(z\uuu 0)= \int\uuu{\partial U}\, 
h(\zeta)\cdot dm(z\uuu 0,\zeta)
\] 
Since this hold for every $z\uuu 0$ in $U\setminus E$ we get the requested
harmonic extension $H$ given by
\[
H(z)= \int\uuu{\partial U}\, 
h(\zeta)\cdot dm(z,\zeta)\quad\colon\quad z\in U
\]

\bigskip

\centerline{\bf{B. Equilibrium distributions
and Robin's constant.}}
\bigskip


\noindent
Let $E$ be a compact set in ${\bf{C}}$.
To each probability measure $\mu$ supported by $E$ we get the potential function

\[
U\uuu \mu(z)= \int\,\log\,\frac{1}{|z\vvv \zeta|}\cdot d\mu(\zeta)
\]
We are going to construct a special $\mu$ for which
$U\uuu \mu$ either is identically $+\infty$ or else 
takes a constant value almost everywhere 
on $E$ with respect to $\mu$.
First we carry out the construction in the special case when
$E$ is a finite union of pairwise disjoint 
and closed Jordan domains
$U\uuu 1,\ldots,U\uuu m$ for some $m\geq 1$.
We also assume that each Jordan curve
$\partial U\uuu k$ is of class $C^1$.
When this holds we get the connected exterior domain

\[
 \Omega^*={\bf{C}}\cup \{\infty\}\setminus
 \cup \,\, \bar U\uuu k
\]
Here we can solve Dirichlet's problem. in particular we obtain the
unique probability measure $\mu$ on $\partial \omega^*$ such that
\[
H(\infty)=\int\, H\cdot d\mu
\]
for every harmonic function $H$ in $\Omega^*$ with continuous boundary
values.
If $z\uuu 1$ and $z\uuu 2$ are two points in
$/cup \,U\uuu k$ which may or may not belong to the same Jordan
domain then we notice that the function
\[
H(z)=\log |z\vvv z\uuu 1|\vvv\log |z\vvv z\uuu 2|
\] 
is harmonic i $\Omega^*$.
Moreover, as $|z|\to \infty$ we notice that
\[
H(z)=\log |1\vvv \frac{z\uuu 1}{z}|\vvv 
\log |1\vvv \frac{z\uuu 2}{z}|
\]
and in the limit we have $H(\infty)=0$.
Since $\log r=\vvv \log\,\frac{1}{r}$ for each $r>0$
 it follows that
\[ 
U\uuu \mu(z\uuu 1)= U\uuu \mu(z\uuu 2)
\]
Hence the function $z\mapsto U\uuu \mu(z)$ is constant in
the interior of $E$
Since the boundary curves $\{\partial U\uuu k\}$ are $C^1$ it follows that
$U\uuu\mu$ extends to a continuous function
with constant value on the whole set $E$.
Of course, $U\uuu\mu$ is also continuous outside $E$ where it is
harmonic.
In fact, we conclude that $U\uuu\mu$ is a globally defined and continuous super\vvv harmonic function in
${\bf{C}}$.
The measure $\mu$ is called the equilibrium distribution
of $E$.
\medskip

\noindent
{\bf{Remark.}} If $E$ is contained in the unit disc
it is clear that the constant value of $U\uuu\mu$ is positive.
On the other hand, let $R>1$ and $E$ is the disc $|z\leq R$.
here $\mu$ is the measure $\frac{1}{\pi}\cdot d\theta$ on
the circle of radius $R$ and we find that the constant value is 
$\vvv
\log \,R$.
 \medskip
 
 \noindent
{\bf{Notation.}}
If $a$ is the constant value of $U\uuu\mu$ we set

\[
 \text{cap}(E)= e^{\vvv a}
\]
and refer to this as the capacity of $E$.
For example, if $E$ is the disc $|z|\leq r$ where $r$ is small we see that
the capacity becomes $r$.
\bigskip

\noindent
{\bf{The general case.}}
Now $E$ is an arbitrary compact set.
To construct a special probability
measure $\mu\uuu E$
we use a similar construction as in section A.
Thus, for $N\geq 1$ we get the family of cubes in $\mathcal D\uuu N$
which have a non\vvv empty intersection with $E$
and then we construct the outer boundary curves of thus set
which borders a connected exterior domain $\Omega^*\uuu N$
whose boundary now
will be a union of closed and piecewise linear Jordan  curves
where two of these may interest at corner points.
We solve the Dirichlet problem and exactly as above we find 
the equilibrium measure $\mu\uuu N$ supported by
$\partial\Omega^*\uuu N$.

 









\bigskip









\centerline {\bf C. Cartan's theorem}
\bigskip

\noindent
We shall 
actually establish
an inequality in
Theorem C.1  below which
has independent interest since
it applies to compact sets $E$ which are not necessarily
harmonic null sets. 
Consider a pair $(h,\mu)$ where
$\mu$ is a probability  measure with compact support
in a compact  set  $E$ of ${\bf{C}}$
with planar Lebesgue measure zero
while 
$h\in \mathfrak{H}_*$.
To each point $a\in E$
and every $r>0$ we have the open disc $D_r(a)$ centered at
$a$ and can regard its $\mu$-mass. This   gives anon\vvv decreasing
function
\[ 
r\mapsto \mu(D_r(a))\quad\colon\, r>0
\]
Put
\[ 
\mathcal U^*=\{ a\in E\quad\colon\,\exists\,\,r>0
\quad\colon\,
\mu(D_r(a))>h(r)\}\tag{1}
\]


\noindent
We assume that the pair $(h,\mu)$ is such that
this set is non\vvv empty.
Since $\mu$ is a Riesz measure one has the limit formula
\[
\lim_{\rho\to r}\,\mu(D_\rho(a)=\mu(D_r(a)
\]
for each $r>0$ where the limit is taken as $\rho$ increases to $r$.
From this it is obvious that $\mathcal U^*$ is a relatively open
subset of $E$ and 
in the closed complement we have
\[ 
a\in E\setminus\mathcal U^*\,\implies\,
\mu(D_r(a))\leq h(r)\quad\colon\,\,\forall\,\, r>0\tag{2}
\]

\noindent
Now the size of $\mathcal U^*$ is
controlled as  follows:
\bigskip

\noindent {\bf C.1 Cartan's Covering Lemma.}
\emph{There  exists a sequence $\{a_\nu\}$
in $E$ and a sequence of positive numbers
$\{r_\nu\}$ such that the following hold:}
\[
\mathcal U^*\subset\,\cup\,\bar D_{r_\nu}(a_\nu)
\quad\text{and}\quad
\sum\, h(r_\nu)\leq 6
\]
\emph{Moreover, for each $z\in{\bf{C}}$
at most five discs from the family
$\{D_{r_\nu}(a_\nu)\}$ contains $z$.}
\bigskip


\noindent \emph{Proof} We may assume that
$\mathcal U^*\neq\emptyset$. Set
\[
\lambda_1^*(r)=
\max_{a\in E}\, \mu(D_r(a))\tag{1}
\]
Since the functions $r\mapsto \mu(D_r(a))$ are lower semi-continuous for
each $a$, it follows that the maximum function
$\lambda_1^*(r)$ also is lower semi-continuous.
Hence the set 
$\{r\colon\, \lambda_1^*(r)>h(r)\}$ is open
and we find
its least upper bound
$r_1^*$. Thus,
\[
\lambda_1^*(r_1^*)=h(r_1^*)\quad\colon\,
\lambda_1^*(r)<h(r)\,\,\,\text{for all}\,\, \, r>r_1^*\tag{2}
\]
Pick $a_1\in E$ so that
\medskip
\[
\lambda_1^*(r_1^*)<\mu(D_{r^*_1}(a_1))+1/2\tag{3}
\]
Next, set $E_1=E\setminus D_{r^*_1}(a_1)$ and define
\[
\lambda_2^*(r)=
\max_{a\in E_1}\, \mu(D_r(a))
\]
If $\lambda_2^*(r)\leq h(r)$ for every $r$ we stop the process.
Otherwise we find the unique largest $r_2^*$ such that
\[
\lambda_2^*(r^*_2)=h(r_2^*)
\]
Notice that $r_2^*\leq r_1^*$
holds since
$h$ is non-decreasing while it is obvious that
$\lambda_2^*\leq\lambda_1^*$.
This time we pick $a_2\in E$ so that
\[
\lambda_2^*(r_2^*)<\mu(D_{r^*_2}(a_2))+2^{-2}
\]
Put $E_2=E_1\setminus D_{r^*_2}$ and continue as above, i.e.
inductively
we get  $E_n$ and set
\[ 
\lambda_{n+1}(r)=\max_{a\in E_n}\,\mu(D_r(a))
\] 
The process continues if we have found $r^*_{n+1}$
so that
$\lambda_{n+1}(r^*_{n+1})=h(r^*_{n+1})$, then we pick 
$a_{n+1}\in E_n$ where
\[
\lambda_{n+1}(r^*_{n+1})\leq \mu(D_{r^*_{n+1}}(a_{n+1}))+ 2^{-n-1}\tag{4}
\]


\noindent
In this way we get the sequence $r_1^*\geq r_2^*\geq\ldots$
and a family of discs $\{ D_{r_\nu^*}(a_\nu)\}$.
To simplify notations we set
\[
D^*_\nu=D_{r_\nu^*}(a_\nu)
\]


\noindent \emph{Sublemma}\emph{ Every point $a\in E$ belongs to at most five
many $D^*$-discs.}
\medskip

\noindent 
\emph{Proof.}
If some $a$ belongs to six discs then elementary geometry gives
a pair $a_k,a_\nu$
such that the angle between the lines $[a,a_k]$ and $[a.a_\nu]$ is $<\pi/3$.
Suppose that for example that $|a-a_k|\geq [a-a_\nu|$.
Euclidian geometry gives
\[ 
|a_k-a_\nu|<|a-a_k|
\]
But this is impossible. For say that $k<\nu$.
Now the disc $D^*_k$ was removed and $a_\nu$ is picked from
the subset $E_\nu$ of $E_k$ while $E_k\cap\Delta_k=\emptyset$.
\medskip

\noindent
\emph{Proof continued.}
The Sublemma implies that
\[ 
\sum\,\mu(D^*_\nu)\leq 5\cdot \mu(E)= 5\tag{5}
\]
The convergence of (5) and (4) imply that
$\lim_{\nu\to\infty} r^*_\nu= 0$. From this it follows that
\[
\mathcal U^*\subset\,\cup\,\bar D_{r_\nu}(a_\nu)\tag{6}
\]

\noindent
Finally we have
\[ 
\sum h(r^*_\nu)= \sum\,\lambda^*_\nu(r_\nu^*)\leq
\sum\,[ \mu(D^*_\nu)+ 2^{-\nu}]\leq
5\cdot \mu(E)+\sum\, 2^{-\nu}=6\tag{7}
\]


\noindent
This completes the proof of Cartan' s Covering Lemma.





\bigskip


\noindent
{\bf{The family $\mathcal G\uuu h$}}.
Let $g(r)$ be a positive   function defined on $(0,+\infty)$
which satisfies:
\[ 
\lim_{r\to 0}\,g(r)=+\infty
\]
In this family we get those $g$\vvv functions for which
\[ 
\int_0^1\, g(r)\cdot dh(r)<\infty\tag{*}
\]
This family is denoted by $\mathcal G\uuu h$.
With this notation we have:
\bigskip

\noindent
{\bf C.2 Lemma}
\emph{For each $g\in\mathcal G\uuu h$
and every point $a\in E\setminus \mathcal U^*$
one has}
\[ 
\int_E\,
g(|z-a|)d\mu(z)\leq\int_0^\rho\, g(r)dh(r)\quad\text{where}\,\,\,h(\rho)=1
\]

\medskip

\noindent
\emph{Proof.} Since $a$ is outside $\mathcal U^*$
we have
\[
\mu(D\uuu r(a))\leq h(r)
\]
for every $r>0$.
Moreover, we recall that $\mu$ has total mass one
and now the reader can verify the inequality in Lemma C.2 b
using a partial integration.




\bigskip

\noindent
{\bf C.3 A special choice of $g$.}
Let us take
\[ 
g(r)=\text{Log}\,\frac{1}{r}\,\quad\colon\, 0<r<1\quad\colon\quad
g(r)=0\quad\colon\,r\geq 1
\]
\medskip

\noindent
This $g$-function belongs to $\mathcal G\uuu h$
by the  
condition on  $h$-functions in Cartan's theorem.
Next, for every  $\lambda>1$ we get the function
$h_\lambda=\lambda\cdot h$ in $\mathfrak{H}_*$ and set:
\[ 
E\setminus\mathcal U^*(\lambda)=\{
a\in E\quad\colon\,\mu(D_r(a))\leq\lambda\cdot h(r)\,\,\colon\, 
\forall\,\, r>0\}
\]


\noindent
Proposition XX(measure general)  applied with $h_\lambda$
gives:
\[ 
\int_E\,
g(|z-a|)d\mu(z)\leq\lambda\cdot \int_0^{\rho/\lambda}\, g(r)dh(r)
\quad\colon\, a\in E\setminus\mathcal U^*(\lambda)\tag{1}
\]

\medskip

\noindent
A partial integration shows that the right hand side in (1)  becomes
\[
g(\rho)+\lambda\cdot \int_0^{\rho}\, \frac{h(r)dr}{r}
\]


\noindent
Hence we have the inequality
\[
\int\,g(|z-a|)\cdot d\mu(z)\leq g(\rho)+\lambda\cdot \int_0^{\rho}\, \frac{h(r)dr}{r}
\quad\colon\quad a\in E\setminus\mathcal U^*(\lambda)\tag{2}
\]


\noindent
In addition to this,  the Covering Lemma gives
an  inclusion
\[
\mathcal U^*(\lambda)\subset \,\cup\,\, D_{r_\nu}(a_\nu)\quad\text{where}\, \sum
\,\,\, h_\lambda(r_\nu)<6\tag{3}
\]
Since $h_\lambda=\lambda\cdot h$
this means that the outer $h$-measure
\[
h^*(\mathcal U^*(\lambda))\leq \frac{6}{\lambda}\tag{4}
\]


\noindent
Hence we have proved the following
where we  recall that
$g(r)=\text{Log}\,\frac{1}{r}$:

\medskip

\noindent
{\bf C.4 Theorem.}
\emph{For
every  triple $(E,\mu,h)$, where $\mu$ is a probability measure supported by
$E$ and $h\in \mathfrak{H}_*$, and any $\lambda>1$
there exists a relatively open
subset $\mathcal U^*(\lambda)\subset E$ such that
the following two inequalities hold:}
\[
\int_E\,\log\,\frac{1}{|z-a|}\cdot d\mu(z)\leq \log\,\frac{1}{\rho}
+
\lambda\cdot \int_0^{\rho}\, \frac{h(r)dr}{r}
\quad\colon\quad a\in E\setminus\mathcal U_*(\lambda)\tag{i}
\]
\[
h^*(U_*(\lambda))<\frac{6}{\lambda}\tag{ii}
\]


\noindent
{\bf {C.11 Proof of Theorem 0.5}}.
Let $E\in\mathcal N_{\text{harm}}$ which by
Theorem 0.2  gives
a probability measure
$\mu$ supported by $E$ such that that the left hand side in (i) 
is $+\infty$ for every $a\in E$.
It follows that the set
$E\setminus \mathcal U^*(\lambda)$ is empty for
every $\lambda>1$. With a fixed $\lambda$ we apply
Cartan's covering Lemma and since
$E=\mathcal U^*(\lambda)$ it follows that
\[
h^*(E)\leq \frac{6}{\lambda}
\]
Here  $\lambda>1 $ is
arbitrary  which gives 
$h^*(E)=0$ as required and 
of Cartan's theorem follows.











\bigskip

\centerline{\bf D. Cantor sets.}

\bigskip
\noindent
We construct  
a  family of 
closed subsets of  $[0,1]$ as follows.
Let $1<p_1<p_2<\ldots$ be some  strictly increasing sequence
of real numbers such that the products
$\{p_1\cdots p_n\}$ tend to $+\infty$ as $n$ increases.
Then we can construct  a
decreasing sequence
of closed sets $E_1,E_2,\ldots$
where each $E_n$ is the union of $2^n$-many closed intervals
with equal
length
\[ 
\ell_n= 2^{-n}\cdot\frac{1}{p_1\cdots p_n}
\]


\noindent
{\bf D.1 The construction.}
First $E_1$ is any closed interval $[a_1,b_1]$
with 
\[ 
b_1-a_1=\frac{1}{2p_1}
\]
Inside this closed interval we 
pick two pairwise disjoint closed interval both of length
$\ell_2$ and  let $E_2$ be  their union.
In the next step we pick a pair of closed intervals both of length
$\ell_3$ from each of the two intervals in $E_2$. Their union gives the set $E_3$
and we continue in the same way for every $n$ and arrive at
a closed set
\[ 
\mathcal E=
\,\cap\, E_n
\]

\noindent
We refer to $\mathcal E$ as a Cantor set.
The construction  is  flexible since
we do not impose any condition on specific positions while we at
stage $n$ pick pairs of intervals of length
$\ell_{n+1}$ from each of the $2^n$ many intervals of $E_n$.
Thus, for a given $p$-sequence we obtain a whole family of
Cantor sets denoted by $\text{Cantor}(p_\bullet)$.
The next result gives a condition for such  Cantor sets
to have
harmonic measure zero.
\bigskip

\noindent
{\bf D.2 Theorem.} \emph{The following are equivalent
for an arbitrary  sequence $p_\bullet$ as above}:
\[ 
\text{Cantor}(p_\bullet)\subset
\mathcal N_{\text{harm}}
\,\,\text{holds if and only if}\,\,\,
\sum_{\nu=1}^\infty\,
\frac{\text{Log}\,p_\nu}{2^\nu}=+\infty
\]
\bigskip

\noindent
The proof 
uses  the explicit formulas for 
Robin constants  of  intervals on the real line. For the detailed proof
we refer to page xx-xx in [Nevanlinna].



\end{document}

\centerline {\bf{E. Further remarks and examples.}}







\centerline {\bf{A. The Robin constant}}.

\medskip


\noindent
First we consider a finite union
of pairwise disjoint Jordan domains $U_1,\ldots U_p$
and get the compact boundary
$\Gamma=\,\cup\,\partial U_\nu$.
The closed Jordan curves $\{\partial U_\nu\}$ are in general disjoint but
we may also allow that a pair intersect at some finite set of points.
We also impose the condition that
the open complement 
\[
\Omega={\bf{C}}\setminus\,\cup \bar U_\nu
\]
is connected.
We  add the point at infinity to
$\Omega$ where
$w=1/z$ is a new coordinate.
A harmonic function $H(z)$ defined in $\Omega$
becomes harmonic at infinity if $w\mapsto H(1/w)$
extends to a harmonic function in a whole disc centered at $w=0$.
\medskip

\noindent
{\bf{A.1 A basic construction}}
In the exterior domain  $\Omega^*=\Omega\cup\{\infty\}$ 
the Dirichlet problem is well posed. 
Hence there exists  a unique probability measure
$\mu$ on $\partial\Omega^*$  such that
\[ 
H(\infty)= \int\, H(\zeta)\cdot d\mu(\zeta)\tag{*}
\]
holds for every harmonic function $H$ in
$\Omega^*$. Notice that
$\partial\Omega^*$ is equal to the union of the closed
Jordan curves $\{\partial U\uuu\nu\}$.
Let us then consider two points
$a$ and $b$ in
in $\cup\,U_\nu$.
It may occur that they belong to a common Jordan
domain or in two different $U$-domains.
In any case we get a harmonic function in $\Omega^*$
defined by:
\[
 H(z)=\text{Log}\, |z-a|-\text{Log}\, |z-b|
\] 
Here
$H$  is harmonic at the point at infinity. For if
$w=1/z$  we have 
\[
H(w)= \text{Log}\, |1-aw|-\text{Log}\, |1-bw|
\] 
which is harmonic
in a disc $|w|<\delta$ and  zero if $w=0$, i.e. 
$H(\infty)=0$.
Since the pair $a,b$ above was arbitrary we conclude that the function
\[ 
a\mapsto \int  \text{Log}\,\frac{1}{ |\zeta-a|}\cdot d\mu(\zeta)\tag{**}
\] 
is constant as $a$ varies in
$\cup\,U_\nu$. Here $\mu$ is supported by the union of the Jordan curves
$\{\partial U_\nu\}$
Since every point on  a single Jordan curve
can be approximated from the inside by
$a$-points in $U_\nu$, it follows by continuity that
the potential function (**) is constant
on $\partial\Omega^*$. So when $E$ is the union of the closed
Jordan curves $\{\partial U_\nu\}$
we conclude that $\mu$ is
a probability measure which settles Robin's problem, i.e. $U\uuu\mu(z)$
is constant on the compact set $E=\cup\,\,\partial U\uuu\nu$.


\medskip


\noindent
{\bf{A.2 An inequality.}}
Consider a pair of
open sets $\Omega$ and $\Omega_1$ which both consist of a finite union of Jordan domains as above and
$\Omega$ is a relatively compact
subset of  $\Omega_1$, i.e. the closure of each Jordan domain in
$\Omega$ is a compact subset of
$\Omega_1$.
Pick some point $a\in\Omega$. In the exterior domain
$\Omega^*$ we find the harmonic function $H\uuu a(z)$
whose boundary values on $\partial\Omega^*$ is equal to the continuous function $z\mapsto \log\,|z\vvv a|$.
Set
\[ 
g\uuu a(z)= \log |z\vvv a|\vvv H\uuu a(z)\tag{1}
\]
This gives a super\vvv harmonic function in
$\Omega^*$
with a singularity at $\infty$ while $g\uuu a=0$ on
the boundary.
It follows from the minimum principle for super\vvv harmonic
functions that 
\[
g\uuu a(z)>0\tag{2}
\]
for all $z\in\Omega^*$.
Next, replacing $\Omega$ by $\Omega\uuu 1$
we find the harmonic function $H\uuu a^1(z)$
which equals $\log|z\vvv a|$ on $\partial \Omega^*\uuu 1$
and  the super\vvv harmonic function
\[
g^1 \uuu a(z)= \log |z\vvv a|\vvv H^1\uuu a(z)\tag{3}
\]
Now $\partial\Omega_1$ is contained in $\Omega^*$ so
$g_a$ restricts to a non-negative function on
$\partial\Omega_1$. 
At $\infty$ the two $g$\vvv functions have the same
logarithmic singularity and hence  $G\uuu a=g_a-g^1_a$ is harmonic in $\Omega_1^*$.
Now $\partial\Omega^*_1$ is contained in $\Omega^*$ and (2) entails that
$G\uuu a>0$ on $\partial\Omega\uuu 1^*$.
We conclude that
$G_a(\infty)\geq 0$.
At the same time we notice that
\[
G_a(\infty)=H\uuu a^1(\infty)\vvv H\uuu a(\infty)
\]
It follows that
\[
H\uuu a ^1(\infty)\geq H\uuu a(\infty)\tag{4}
\]


\noindent
The monotonic property expressed by (4) above
will be used to study the case when
$E$ is a
totally  disconnected and compact
subset of
${\bf{C}}$.
Let  $\Omega^*$ be the exterior domain of $E$, i.e. the union of
$\infty$ and  
${\bf{C}}\setminus E$. 
Since $E$ is totally disconnected the 
boundary points $a\in\partial\Omega^*$ fail to satisfy the
Perron condition for  Dirichlet's problem.
However, we shall   define Robin's constant for
$E$ by a limit process
and    find  a probability measure $\mu$ on $E$ 
such that the potential

\[
z\mapsto 
\int_E\,\text{Log}\,|1-\frac{\zeta}{z}|\,\cdot \mu(\zeta)\tag{*}
\]
is constant as $z$ varies in $E$. But in contrast to the case 
case when $E$ is a union of Jordan arcs,  it may occur that the "constant value" is 
$+\infty$.  
To attain this
we  use a construction which goes back to De 
Vallé\vvv Poussin.
\medskip








\noindent
{\bf{A.2 Nested coverings }}
Let $E$ be a totally disconnected
and compact set.
Without essential loss of generality we
may  assume that $E$ is a compact subset
of the open unit disc $D$.
We
construct a sequence of open sets $\{V_N\}$ as follows.
For each positive integer $N$ one has  the dyadic grid
$\mathcal D_N$
of open squares whose sides are $2^{-N}$.
We get the finite family
$\mathcal D_N(E)$ of  dyadic squares in $\mathcal D_N$
which have a non-empty intersection with
$E$. The union of this finite 
family of open squares gives an open neighborhood $V_N$ of $E$. 
If necessary one starts with a large $N$ so that
$2^{-N}$ is strictly larger than the distance of $E$ to the unit
circle $T$ which entails that the closure of $V_N$ is a compact subset
of $D$.
Let $\Omega^*_N$ be the exterior connected component of
$D\setminus \bar V_N$ whose closure contains the unit circle.
So here
$\Omega^*_N$  contains an annulus $r<|z|<1$ 
for some $0<r<1$
and $\partial \Omega_N$
is the union of $T$ and a closed subset $\Gamma_N$
of $\partial V_N$
which is a finite union of line segments with a finite set of corner
points.
During this construction it is clear that the open sets $\{\Omega_N^*\}$
increase and since $D\setminus E$ is connected we have
\[
 \cup\, \Omega_N^*=D\setminus E
\]


\noindent
Next, fix some point $z_0\in D\setminus E$
which is chosen relatively close to $T$.
For all sufficiently large $N$ we have $z_0\in\Omega^*_N$
and get the unique   probability measure $\mathfrak{m}_N$ which is supported
by $\partial\Omega_N$ and satisfies:
\[ 
g(z_0)=\int_T\, g(e^{i\theta})\cdot d\mathfrak{m}_N(\theta)+
\int_{\Gamma_N}\, g(\zeta)\cdot d\mathfrak{m}_N(\zeta)
\] 
for every $g$-function which
is harmonic
in $\Omega^*_N$ with continuous boundary values.
Since $\{\Omega^*_N\}$ is a nested sequence
it follows that the masses
\[ 
\rho_N=\int_{\Gamma_N}\, d\mathfrak{m}_N(\zeta)
\] 
is a decreasing sequence of positive real numbers.
Hence there exists the limit
\[ 
\rho_*=\lim_{N\to\infty}\,\rho_N\tag{*}
\]
Above two cases may occur. Either $\rho_*>0$ or it is zero.
The condition that $\rho_*=0$ is intrinsic since Harnack's inequality
shows that 
the choice of $z_0$ in $D\setminus E$
is irrelevant. 

\medskip


\noindent
{\bf{A.3 The case $\rho_*=0$.}}
If $a\in E$ is kept fixed then
$g(z)=\text{Log}\frac{1-\bar az|}{|z-a|}$ is a harmonic function
in the domain $\Omega^*_N$ for every integer $N$ which is
identically zero on the unit circle. Hence
\[ 
g(z_0)=\int_{\Gamma_N}\, g(\zeta)\cdot d\mathfrak{m}_N(\zeta)\tag{1}
\]
Consider the probability measure
$\mu_N=\frac{1}{\rho_N}\cdot \mathfrak{m}_N$ which gives:
\[
\frac{1}{\rho_N}\cdot g(z_0)=
\int_{\Gamma_N}\, \log\, \frac{1}{|\zeta-a|}\cdot d\mu_N(\zeta)
+\int_{\Gamma_N}\, \log\,|1-\bar a\zeta | \cdot d\mu_N(\zeta)\tag{2}
\]
\medskip

\noindent
Next, from $\{\mu_N\}$
we  can extract a subsequence which
converges weakly to a Riesz measure $\mu_*$. It is clear that 
$\mu\uuu *$ is supported by $E$ and
the weak convergence gives:
\[
\lim_{N\to\infty}\, 
\int_{\Gamma_N}\, \log\,|1-\bar a\zeta | \cdot d\mu_N(\zeta)=
\int\, \log\,|1-\bar a\zeta | \cdot d\mu_*(\zeta)\tag{3}
\]
Indeed, this holds since
the integrand
$\text{Log}\,|1-\bar a\zeta z|$ is continuous on $E$.
Next, when $\rho_N\to 0$ is assumed
it follows from (2) that
\[ 
\lim_{N\to\infty}\, 
\int_{\Gamma_N}\, \log\, \frac{1}{|\zeta-a|}\cdot d\mu_N(\zeta)=+\infty\tag{4}
\]
\medskip

\noindent
{\bf{A.4 Exercise.}} 
Show 
that (4) together with  the weak convergence of  $\{\mu_N\}$ to $\mu_*$ imply that
\[
\int_E\log\, \frac{1}{|\zeta-a|}\cdot d\mu_*(\zeta)=+\infty
\]

\noindent
This holds for an arbitrary $a$ in $E$ and hence we have proved:

\medskip


\noindent
{\bf{A.5 Theorem.}} \emph{Let $E$ be a 
totally disconnected and compact set where $\rho_*=0$.
Then there exists 
at least one  probability measure
$\mu$ supported by $E$ such that}
\[ 
\int_E\,\log\, \frac{1}{|a-\zeta|}\cdot d\mu(\zeta)=+\infty
\quad\text{for all}\quad a\in E
\]






\bigskip

\centerline {\bf{B. Removable singularities}}.
\medskip

\noindent
Let $E$ be a totally disconnected and compact subset of some open domain
$\Omega$. 
We say that $E$ is a removable singularity if
every 
bounded harmonic function in $\Omega\setminus E$
extends to be harmonic in the whole domain $\Omega$.
Now we shall use Theorem A.5 to prove Myrberg's result.



\noindent
\emph{Proof.} XXXX










%\end{document}




















