\documentclass{amsart}
\usepackage[applemac]{inputenc}

\addtolength{\hoffset}{-12mm}
\addtolength{\textwidth}{22mm}
\addtolength{\voffset}{-10mm}
\addtolength{\textheight}{20mm}


\def\uuu{_}


\def\vvv{-}

 
\begin{document}

\centerline{\bf\large{Homogeneous distributions and the Mellin transform}}

\bigskip

\centerline{\emph{Contents}}

\bigskip

\noindent
\emph {A. Polar distributions}
\bigskip

\noindent
\emph {B. Homogeneous distributions}
\bigskip


\noindent
\emph{C. The Radon transform}



\bigskip

\noindent
\emph{D. The Mellin transform}

\bigskip

\noindent
\emph {E. The family $P_+(x,y)^\lambda$}
\bigskip

\noindent
{\bf{Introduction.}}
We establish some results where analytic function theory
is used in connection with distributions and
asymptotic expansions.
Special attention in the first sections is given to
homogeneous distributions in
${\bf{R}}^2$.
while the last section exposes a famous result due to Mellin in [Mellin]
which has a wide range of applications.
A separate section is devoted to the Radon transform where
the inversion formula has a wide range of applications but we shall not pursue
the discussion any further. The reader may consult Helgason's
text-book [Helgason] for the theory about radon transforms
which include the case of higher dimension.
In ¤ 4 we 
establish an important result due to Mellin in [Mellin]
and ¤ 5 contains more advanced material which relies upon
$\mathcal D$-modue theory. So  the  presentation is
expositary in this section.





\bigskip


\centerline{\bf  {A. Polar distributions}}

\bigskip

\noindent
In the $(x,y)$-plane we can take polar coordinates where
$x=r\cdot\text{cos}\,\theta$ and
$y=r\cdot\text{sin}\,\theta$.
If $\phi(x,y)$ belongs to the Schwartz space $\mathcal S$
of rapidly decreasing $C^\infty$-functions  we  restrict $\phi$ to the
circle of radius $r$ which after a dilation is identified
with  unit circle $T$ and
obtain the $\theta$-periodic function
\[ 
\theta\mapsto \phi_r(\theta)= \phi(r\cdot\text{cos}\,\theta,r\cdot\text{sin}\,\theta)\tag{0.1}
\]


\noindent
Let $\nu$ be a distribution on $T$.
For each $r>0$ we
can evaluate $\nu$ on the
$C^\infty(T)$-function $\phi_r$ which yields a function:
\[ 
r\mapsto \nu(\phi_r)\quad\colon\, r>0\tag{0.2}
\]

\medskip

\noindent
{\bf{A.0 Exercise.}}
Show that (2) gives a $C^\infty$-function defined on
$\{r>0\}$. More precisely,verify that the first order derivative becomes:


\[
\frac{d}{dr}(\nu(\phi_r))=
\nu(\text{cos}\,\theta\cdot\partial_x(\phi)(r\cdot\text{cos}\,\theta,r\cdot\text{sin}\,\theta)+
\text{sin}\,\theta\cdot\partial_y(\phi)(r\cdot\text{cos}\,\theta,r\cdot\text{sin}\,\theta))
\]
\medskip

\noindent
More generally, show that for each $m\geq 2$ the derivative of order $m$ becomes:
\[
\frac{d^m}{dr^m}(\nu(\phi_r))=\sum_{j=0}^{j=m}\,
\binom{m}{j}\,
\nu\bigl(\text{cos}^j\,\theta\cdot \text{sin}^{m-j}\,\theta\cdot
\partial^j_x\partial_y^{m-j}(\phi)_r\bigr)\tag{*}
\]
\medskip


\noindent
Show also that the function in (0.2) decreases 
rapidly as $r\to+\infty$. More precisely, for
each positive integer $N$ one has
\[
\lim_{r\to\infty} r^N\cdot\nu(\phi_r)=0\tag{**}
 \]
 
\medskip



\noindent
{\bf{A.1 The function $V_\lambda$.}}
Using (**) above it follows that
if $\lambda$ is a complex number with
$\mathfrak{Re}(\lambda)>-2$, then  there exists  the absolutely convergent integral
\[ 
V_\lambda(\phi)=
\int_0^\infty\,
r^{\lambda+1}\cdot \nu(\phi_r)\cdot dr\tag{1}
\]


\medskip

\noindent
{\bf{A.2 Exercise }}
Show that $V_\lambda$
is an analytic function of
$\lambda$ in the open half-plane
$\mathfrak{Re}(\lambda)>-2$ and
use a partial integration with respect to $r$ to show that:
\[
(\lambda+2)V_\lambda(\phi)=-\int_0^\infty
r^{\lambda+2}\cdot \frac{d}{dr}[\nu(\phi_r)]\cdot dr
\]
Continue this procedure and show that for every
$N\geq 1$ one has:
\[
(\lambda+2)\cdots(\lambda+2+N)\cdot V_\lambda(\phi)=
(-1)^{N+1}\int_0^\infty
r^{\lambda+2+N}\cdot \frac{d^N}{dr^N}[\nu(\phi_r)]\cdot dr\tag{*}
\]




\noindent
Together with  (*) in Exercis A.0 
we can conclude that following:


\medskip

\noindent
{\bf{A.3 Proposition.}} \emph{For each
$\phi\in \mathcal S$
it follows that   $V_\lambda(\phi)$ 
extends to a meromorphic
function in the whole complex
$\lambda$-plane with at most simple poles at
the integers $-2,-3,\ldots$.}



\bigskip


\noindent{\bf{A.4 Polar distributions.}}
As $\phi$ varies in $\mathcal S$ 
we obtain a
distribution-valued function
$V_\lambda$.
If $\delta>0$ and 
$\phi(x,y)\in\mathcal S$ is identically zero in the
disc $\{x^2+y^2<\delta^2\}$, then we only integrate
(1) in A.1 when $r\geq\delta$ and we notice that the function
\[
 \lambda\mapsto \int_\delta^\infty\,
r^{\lambda+1}\cdot \nu(\phi_r)\cdot dr
\]
is an entire function of $\lambda$ whose complex derivative is given by
\[
 \lambda\mapsto \int_\delta^\infty\,
\log r\cdot r^{\lambda+1}\cdot \nu(\phi_r)\cdot dr
\]

\medskip

\noindent
Regarding the distribution-valued function $V_\lambda$
this means that 
eventual poles  consist of Dirac distributions at the origin.
Let us first study if   a pole can occur  at $-2$.
With $\lambda=-2+\zeta$ we have
\[
\zeta\cdot V_{-2+\zeta}(\phi)=-
\int_0^\infty\, r^\zeta\cdot 
\frac{d}{dr}[\nu(\phi_r)]\cdot dr\tag{i}
\]
Since $r^\zeta\to 1$ holds for each $r>0$ as
$\zeta\to 0$, the right hand side has the limit
\[
\int_0^\infty\, 
\frac{d}{dr}[\nu(\phi_r)]\cdot dr=\nu(\phi_0)=
\nu(1_T)\cdot \phi(0)\tag{ii}
\]
where $1_T$ is the identity function on $T$ on which $\nu$ is evaluated.
Hence $V_\lambda$ has a pole at $\lambda=-2$ if and only if
$\nu(1_T)\neq 0$ and in this case the polar distribution is
$\nu(1_T)$ times the Dirac distribution $\delta_0$.

\medskip

\noindent
{\bf{A.5 Exercise}}
Use the functional equation formula (*)
in A.2 to show the following:

\bigskip


\noindent
{\bf{A.6 Proposition }}
\emph{For each $N\geq 1$ the polar distribution at
$\lambda=-N-2$ is zero if and only if }

\[ 
\nu(\text{cos}^j\,\theta\cdot \text{sin}^k\,\theta)=0
\]
\emph{hold for all pairs of non-negative integers $j,k$ with
$j+k=N$.}
\medskip

\noindent
{\bf{Remark.}} Thus, no pole occurs 
at $\lambda=-N-2$
if and only if $\nu$ vanishes on the
$N+1$-dimensional subspace of $C^\infty(T)$
spanned by
$\{\text{cos}^j\,\theta\cdot \text{sin}^{N-j}\,\theta)\quad\colon
0\leq j\leq N\}$.
Next, if a pole occurs we have a Laurent series:
\[
V_{-N-2+z}=
\frac{\gamma_N}{\zeta}+ V_{-N-2}+\sum_{n=1}^\infty
\rho_j\cdot \zeta^j
\]
where $\gamma_N$ is the polar distribution.
\medskip

\noindent
{\bf{A.7 Exercise,}}
Show that if a pole occurs then
$\gamma_N$ is the Dirac distribution given by:
\[ 
\gamma_N(\phi)=\frac{1}{N\,!}\cdot
\sum_{j=0}^{N}\,
\nu((\text{cos}^j\,\theta\cdot \text{sin}^{N-j}\,\theta)\cdot
\partial_x^j\partial_y^{N-j}(\phi)(0)\tag{*}
\]
\newpage







\centerline
{\bf{B. Homogeneous distributions.}}
\medskip


\noindent
A distribution $\mu$ defined outside the origin in
${\bf{R}}^2$ is homogeneous of degree $\lambda$ if
\[ 
\mathcal E(\mu)=\lambda\cdot \mu\tag{*}
\] 
where $\mathcal E=x\partial_x+y\partial_y$ is the radial vector field.
Denote by $\mathcal S^*(\lambda)$ the family of all
$\lambda$-homogeneous distribution in
${\bf{R}}^2\setminus\{0\}$.
\bigskip

\noindent
{\bf{B.1 Proposition.}}
\emph{$\mathcal S^*(\lambda)$ is in a 1-1 correspondence with
$\mathfrak{Db}(T)$ when  we for every distribution $\nu$ on $T$
consider the restriction of $V_\lambda$ to
${\bf{R}}^2\setminus\{0\}$.}
\medskip

\noindent
{\bf{B.2 Exercise.}}
Prove this result. The hint is to verify that
one has the equality

\[ 
\mathcal E(V_\lambda)=\lambda\cdot V_\lambda
\] 
when one  starts from an arbitrary distribution $\nu$ on $T$.
\bigskip


\noindent
{\bf{B.3 The space $\mathcal S^*[\lambda]$}}.
This the space of tempered distributions on
${\bf{R}}^2$ which are everywhere homogeneous. So a tempered
distribution $\mu$ belongs to
$ \mathcal S^*[\lambda]$ 
if and only if
\[ 
\mathcal E(\mu)=\lambda\cdot\mu
\]
where the equality holds in $\mathcal S^*$.
\medskip


\noindent
{\bf{B.4 Example of distributions in
$\mathcal S^*[\lambda]$}}.
Let $\nu$ be  a distribution on $T$ and
construct the meromorphic function $V_\lambda$. It is clear that

\[
 \mathcal E(V_\lambda)=\lambda\cdot V_\lambda
 \quad\text{holds when}\quad \,\mathfrak{Re}(\lambda)>-2\tag{i}
 \]
 
 \medskip
 
\noindent
Let 
$\lambda_*$ be a complex number such that
$V_\lambda$ has no pole at 
$\lambda_*$. By analyticity it follows from (i) that the constant term
$V_{\lambda_*}$ satisfies
\[
\mathcal E(V_{\lambda_*})=\lambda_*\cdot V_{\lambda_*}\tag{ii}
\]
Hence $V_{\lambda_*}$ belongs to $\mathcal S^*[\lambda_*]$.
By Proposition A.3 no poles occur 
when
$\lambda_*$ is outside the set
$\{-2,-3,\ldots\}$ which  gives the following:


\medskip

\noindent
{\bf{B.5 Proposition.}}
\emph{For each $\lambda_*$ outside
the set $\{-2,-3,\ldots\}$ there exists a bijective map}
\[
\nu\mapsto V_{\lambda_*}
\] 
\emph{from $\mathfrak{Db}(T)$ into $\mathcal S^*[\lambda_*]$.}
\bigskip





\noindent
{\bf{B.6 The action  by $\mathcal E$
on
Dirac distributions.}}
Using Dirac distributions at the origin we shall construct
homogeneous distributions which do not arises
via distributions from $T$ as above.
To begin with
the complex vector space of all Dirac distributions
is a direct sum of the subspaces
\[
\text{Dirac}[m]=
\oplus\,{\bf{C}}\cdot \partial_x^k\partial_y^j(\delta_0)
\quad\colon\, j+k=m\tag{1}
\]
where $m$ are non-negative integers.
Next, in the ring
$\mathcal D$ of differential operators we
have the identity
\[ 
\mathcal E=\partial_x\cdot x+\partial_y\cdot y-2
\]
Since $x\cdot \delta_0=y\cdot \delta_0=0$ it follows that
\[ 
\mathcal E(\delta_0)=-2\cdot \delta_0
\]


\medskip

\noindent
In general the reader may verify by an induction over $m$ that

\[ 
\mathcal E(\gamma)= -(m+2)\cdot\gamma
\quad\text{hold for all}\quad \gamma\in\text{Dirac}[m]\tag{2}
\]
\medskip

\noindent
Hence $\text{Dirac}[-m-2]$ is a subspace of
$S^*[-m-2]$ which has dimension $m+1$. In particular
$S^*[-2]$ contains  the 1-dimensional vector space generated
by $\delta_0$.




\bigskip


\centerline {\bf{B.7 The description of $\mathcal S^*[-2-N]$}}.
\medskip

\noindent
Let $m$ be a non-negative integer. 
Denote by $\mathfrak{Db}(T)[m+2]$
the set of distributions
$\nu$  on
$T$ such that $V_\lambda$ has no pole at
$-2-m$. From B.4 it follows that one has an injective map

\[
\mathfrak{Db}(T)[m+2]\mapsto S^*[-2-m]\tag{*}
\]
\medskip

\noindent
{\bf{B.8 Exercise.}}
Show that
\[
S^*[-2-m]=\mathfrak{Db}(T)[m+2]\oplus \text{Dirac}[m]
\] 
hold for every integer $m\geq 0$.

\medskip


\noindent
{\bf{B.9 A converse to (*)}}.
Let $m$ be a non-negative integer and
consider a distribution $\nu$ on $T$.
At $\lambda=-m-2$ we have the constant term $V_{-m-2}$ of the Laurent expansion of $V_\lambda$. We have seen
that the distribution $V_{-m-2}$ is homogeneous of order
$-m-2$ if no pole occurs.
It turns out that the absence of a pole also is necessary in order
that
$V_{-2-m}$ belongs to $S^*[-2-m]$.
To show this 
we suppose that a pole is present which gives the Laurent series

\[ 
V_{-2-m+\zeta}= \frac{\gamma}{\zeta}+ V_{-2-m}+
\sum_{j=1}^\infty \gamma_j\cdot \zeta^j
\]
where $\gamma$ now is a non-zero Dirac distribution
which belongs to $\text{Dirac}[-2-m]$. Now we have


\[
\mathcal E(\frac{\gamma}{\zeta}+V_{-m-2}+\sum\rho_j\zeta^j)=
(-m-2+\zeta)\cdot V_{-m-2+\zeta}=
\]
\[ 
(-m-2)\cdot\frac{\gamma}{\zeta}+
\gamma+(-m-2)V_{-m-2}+\zeta\cdot V_{-2-m}+(-m-2+\zeta)\cdot \sum\rho_j\zeta^j
\] 
Identifying the constant term we get

\[
\mathcal E(V_{-m-2})=\gamma-(m+2)V_{-2-m}\tag{2}
\]
Hence the distribution $V_{-m-2}$ fails to be homogeneous.

\bigskip

\noindent
{\bf{B.10 Example.}}
Let $\nu=1_T$ be the  identity density on $T$.
So here
\[ 
V_\lambda(\phi)=\int_0^\infty\, [\int_0^{2\pi}\, \phi(r,\theta)\, d\theta\,]\, 
r^{\lambda+1}dr
\]
Outside the origin we see that the distribution $V_{-2}$
is given by the density function
\[ 
f=\frac{1}{x^2+y^2}
\]
Moreover, it is clear that
$V_\lambda$ has a pole when
$\lambda=-2$ and whose polar distribution is $\delta_0$.
The conclusion is that the distribution $V_{-2}$ is not homogeneous.
Notice that we encounter another obstacle since
the function $f$ above is not locally integrable at
the origin so it is not clear how
to define the distribution $V_{-2}$.
If a test-function $\phi$ is zero at the origin, then
the integral
\[
\iint _{{\bf{R^2}}}\, \frac{\phi(x,y)}{x^2+y^2} \cdot dxdy
\] 
is defined.
So the action by $V_{-2}$
is determined on a the hyperplane of all test-functions which
are zero at the origin.
There remains to evaluate $V_{-2}(\phi)$ when
$\phi(0,0)\neq 0$.






\newpage

\centerline {\bf{B.12 Fourier transforms.}}
\medskip

\noindent
The Fourier transform maps tempered distributions in the $(x,y)$-space 
to tempered distribution the $(\xi,\eta)$-space.
By the laws from XX we 
the radial field $\mathcal E=x\partial_x+y\partial_y$
is sent into the first order differential operator 

\[
(i\partial_\xi)\cdot i\xi+(i\partial_\eta)\cdot i\eta=
-\partial_\xi\cdot \xi-\partial_\eta\cdot \eta=-\xi\partial_\xi-1-
-\eta\partial_\eta-1=-\mathcal E^*-2
\]

\noindent
where $\mathcal E^*$ is the Euler field in the 
$(\xi,\eta)$-space. So if $\mu\in S^*[\lambda]$ is a
homogeneous distribution in
the $(x,y)$-space the
equality $\mathcal E(\mu)= \lambda\cdot \mu$
entails that
\[
-(\mathcal E^*+2)(\widehat\mu)= \lambda\cdot \widehat\mu\implies
\mathcal E^(\widehat\mu)=-(2+\lambda)\widehat\mu
\]
Hence the Fourier transform gives a bijective map between
$S^*[\lambda]$ and the space
šf hiomogeneous distributions in the
$(\xi,\eta)$-space of degree $-2-\lambda$.
\medskip


\noindent
{\bf{Example.}}
The Dirac measure
$\delta_0$ is homogenoues of degree $-2$ so here
$\widehat\delta_0$ should be in $S^*[0]$ and this is indeed the
fact since
it is given by the constant density in the $(x,\xi)$-space.
Notice also that the Fourier transform sends
$S^*[-1]$ into itself.
\bigskip

\noindent
{\bf{B.13 The $\lambda$-maps on $\mathfrak{Db}(T)$.}}
Let $\lambda$ be a complex umber outside the set
$\{-2,-3,\ldots\}$. 
To each $\nu\in\mathfrak{Db}(T)$
we get the distribution $V_\lambda$ which belongs to
$S^*[\lambda)$.
It follows that the Fourier transform
$\widehat V_\lambda$ belongs to $S^*[-\lambda-2]$ and
this gives a unique distribution
$\nu^*$ on $T$
such that
\[
\widehat V_\lambda=V^*_{-\lambda-2}\tag{*}
\]
Keeping $\lambda$ fixed this means that we get a bijective map from
$\mathfrak{Db}(T)$ to itself defined by
\[ 
\nu\mapsto \nu^*
\]
where the rule is that (*) holds.
We denote this map by
$\mathcal H_\lambda$ and refer to this as Fourier's
$\lambda$-map on $\mathfrak{Db}(T)$.
\bigskip


\noindent
{\bf{Exercise.}}
Assume that $\lambda$ is outside
$\{-2,-3,\ldots\}$.
Let $m$ be a posiotove integer and $P_m(\xi,\eta)$
is a homogenous polynomial of degree $m$.
Now we get a homogenous distribution
in the $(x,\xi)$-space
of degree $m+\lambda$ defined outside the origin by the density 
\[
P_m(\xi,\eta)\cdot (\xi^2+\eta^2)^{\frac{\lambda}{2}}\tag{1}
\]


\noindent
We seek a homogeneous distribution $\mu_\lambda$ in the $(x,y)$-space
such that $\widehat\mu_\lambda$ is equal to (1).
In the $(x,y)$-space we first consider the distribution
\[ 
\gamma= (x^2+y^2)^{-\frac{\lambda}{2}-1}
\] 
and notice that $\widehat\gamma$ is equal to the
distribution 
$(\xi^2+\eta^2)^{\frac{\lambda}{2}}$.
Fourier's inversion formula entails that
(1) is equal to
\[
i^{-m}\cdot P_m(\partial_x,\partial_y)(\gamma)\tag{2}
\]
\medskip

\noindent
{\bf{Example.}}
Take $m=1$ and $P_1(\xi,\eta)=\xi$.

















\newpage





\centerline{\bf  C. The Radon transform}

\bigskip

\noindent
In the article  [Radon] from 1917
Johann Radon 
established  an inversion formula which recaptures 
a  test-function $f(x,y)$ in ${\bf{R}}^2$
via   integrals over  affine lines
in the
$(x,y)$-plane. This family 
is parametrized by pairs $(p,\alpha)$,
where  $p\in{\bf{R}}$ and $0\leq \alpha<\pi$
give  the line
$\ell(p,\alpha)$:
\[
 t\mapsto 
 \bigl(p\cdot \text{cos}\,\alpha-
 t\cdot \text{sin}\,\alpha\, , \,p\cdot \text{sin}\,\alpha+
 t\cdot \text{cos}\,\alpha\bigr)
 \]


\noindent
The Radon  transform of $f$ is a function of the pairs $(\alpha,p)$
defined by:
\[
R_\alpha(p)=\int_{\ell(p,\alpha)}\,f\cdot dt=
\int_{-\infty}^\infty\, 
f\bigl(p\cdot \text{cos}\,\alpha-
t\cdot \text{sin}\,\alpha\, , \,p\cdot \text{sin}\,\alpha+
 t\cdot \text{cos}\,\alpha\bigr)
\cdot dt\tag{*}
 \]
Thus, for a given $\alpha$ we  take the mean value of $f$ over an affine line
which is $\perp$ to the vector $(\cos\alpha,\sin\alpha)$ and 
whose distance to the origin is $|p|$.
We give
an inversion formula which recaptures $f$ from the Radon transform.
To achieve this
we construct the partial  Fourier transform
of $R$ with respect to $p$, i.e. set
\[
 \widehat R_\alpha( \tau)=\int e^{-i\tau p}\cdot R_\alpha(p)\cdot dp\tag{1}
 \]
Consider the linear map
$(p,\tau)\mapsto (x,y)$ where
\[
x= p\cdot \text{cos}\,\alpha-
t\cdot  \text{sin}\,\alpha\quad\text{and}\quad
y=p\cdot \text{sin}\,\alpha+t\cdot \text{cos}\,\alpha\implies
\]
\[
p=\text{cos}(\alpha)\cdot x+
\text{sin}(\alpha)\cdot y\tag{2}
\]
Since  
$ \text{cos}^2\,\alpha+\text{sin}^2\,\alpha=1$ this substitution gives
$dpdt=dxdy$ and hence
(2) entails that
\[
 \widehat R_\alpha(\tau)=
\int\, e^{-i\tau(x\cdot \text{cos}\,\alpha+
y\cdot \text{sin}\,\alpha)}
\cdot f(x,y)\cdot dxdy=
\widehat f(\tau\cdot \text{cos}\,\alpha\,,\,
\tau\cdot \text{sin}\,\alpha)\tag{3}
\]

\noindent
Next, Fourier's inversion formula applied to $f$ gives:
\[
f(x,y)=\frac{1}{(2\pi)^2}\cdot
\int\, e^{i(x\xi+y\eta)}\cdot
\widehat f(\xi,\eta)\cdot d\xi d\eta
\]
Now we use the substitution
$(\tau,\alpha)\mapsto (\xi,\eta)$ where
\[ 
\xi=\text{cos}(\alpha)\cdot \tau\quad\text{and}\quad
\eta=\text{sin}(\alpha)\cdot \tau
\]
Here $d\xi d\eta=|\tau|\cdot d\tau d\alpha$ and then
(3) gives
the equality
\[
f(x,y)=
\frac{1}{(2\pi)^2}\int_0^\pi\,\bigl[
\int_{-\infty}^\infty\,
e^{i\tau(x\cdot \text{cos}\,\alpha+
y\cdot \text{sin}\,\alpha)}
\cdot \widehat R_\alpha(\tau)\cdot |\tau|\cdot d\tau\bigr]\cdot d\alpha\tag{*}
\]


\noindent
To get an inversion formula  where 
the partial Fourier transform
$\widehat R_f(\alpha,\tau)$
does not appear we  apply the Fouriers inversion formula in
dimension one. Namely, for each $A>0$ we set
\[ 
K_A(u)=
\frac{1}{2\pi}
\int_{-A}^A\,
e^{i\tau u}\cdot |\tau|\cdot d\tau\tag{4}
\]
This function admits a alternative
description since we have
\[
K_A(u)=
\frac{1}{\pi}
\int_0^A\,
\tau\cdot \text{cos}(\tau u)\cdot d\tau=
\frac{1}{\pi}\cdot \frac{d}{du}\bigl(
\int_0^A\,
\text{sin}(\tau u) \cdot d\tau\bigr)=
\]
\[
\frac{1}{\pi}\cdot \frac{d}{du}\bigl(
\frac{1-\text{cos}(Au)}{u}\bigr)=
\frac{1}{\pi}\cdot [A\cdot \frac{\sin Au}{u}-\frac{1-\text{cos}(Au)}{u^2}]\tag{5}
\]


\noindent
Next, 
by the convolution formula for Fourier transforms
the right hand side in (*) becomes
\[
\lim_{A\to\infty}\,
\frac{1}{2\pi}\int_0^\pi\,\bigl[
\int_{-\infty}^\infty\,
R_\alpha(
x\cdot \text{cos}\,\alpha+
y\cdot \text{sin}\,\alpha-u)\cdot K_A(u) du\,\bigr]
\cdot d\alpha\tag{6}
\]






\noindent
After the substitution
$u\to \frac{s}{A}$ and applying (5) 
the limit in (*) becomes
\[ 
\lim_{A\to\infty}\,
\int_0^\pi\,\bigl[\int_{-\infty}^\infty\, R_\alpha(
x\cdot \text{cos}\,\alpha+
y\cdot \text{sin}\,\alpha-\frac{s}{A})
\cdot \bigl(
A\cdot \frac{\sin s}{s}-
A\cdot \frac{1-\cos s}{s^2}\bigr)\cdot ds\,\bigr ] \cdot d\alpha\tag{**}
\]


\newpage


\centerline{\bf  D. The Mellin transform}

\bigskip

\noindent
In many situations one encounters a
function $J(\epsilon)$ which is defined for $\epsilon>0$
and has an asymptotic expansion as $\epsilon\to 0$ by
fractional powers which  means  that there
exists a strictly increasing sequence of real numbers
$0<q_1<q_2\ldots$with $q_N\to +\infty$
and constants $c_1,c_2,\ldots$
such that for every $N$ there exists some $\delta>0$ 
which in general depends upon $N$ and:
\[
\lim_{\epsilon\to 0}\,
\frac{J(\epsilon)-(c_1e^{q_1}+\ldots +c_Ne^{q_N})}
{\epsilon^{q_N+\delta}}= 0\tag{*}
\] 

\noindent
It is clear that the constants $\{c_k\}$ are uniquely determined 
by $J$ and the $q$-numbers if (*) holds.
We are only concerned with the behavior of $J$ for small $\epsilon$
and may therefore assume that $J(\epsilon)=0$ when $\epsilon>1$.

\medskip

\noindent{\bf{The Mellin transform.}}
Let  $J(\epsilon)$ be some bounded and continuous function on
$[0,1]$  and zero if $\epsilon\geq 1$ and  the integral
\[ 
\int_0^1\, |J(\epsilon)|\cdot \frac{d\epsilon}{\epsilon}<\infty\tag{1}
\]
When $\mathfrak{Re}(\lambda)>0$ we set
\[
 M(\lambda)=\lambda\cdot \int_0^1\, J(\epsilon)\cdot \epsilon^{\lambda-1}\cdot d\epsilon\tag{2}
\]

\noindent
It is clear that $M(\lambda)$ is an analytic function in the right
half-plane $\mathfrak{Re}(\lambda)>0$ which by (1) extends to a continuous function
on the closed half\vvv plane. Moreover, if we assume that
$j$ has an asymptotic expansion (*) it follows
that
$ M(\lambda)$ extends to a meromorphic function in the whole complex
$\lambda$-plane whose  poles are contained in the set
$\{-q_k\}$. In fact, this follows easily via (*) since
\[
\lambda\int_0^1\, \epsilon^q\cdot  \epsilon^{\lambda-1}\epsilon=
\frac{1}{\lambda+q}\quad\text{for every}\quad q>0
\] \medskip

\noindent
Along the imaginary axis  we have
\[
M(is)=is\int_0^1\, J(\epsilon)\cdot \epsilon^{is}\cdot 
\frac{d\epsilon}{\epsilon}\tag{3}
\]
Apart from the factor $i$ this is the Fourier transform of 
$J$ on  the multiplicative line ${\bf{R}}^+$.
So by XXX one has  the inversion formula
\[ 
J(\epsilon)=\lim_{R\to\infty}\, J_R(\epsilon)=
\,\int_R^R\epsilon^{-is}\cdot
\frac{ M(is)}{is}\cdot ds\tag{4}
\]
\medskip




\noindent
Mellin discovered
a reverse process  where one from the start  only assumes that
(1) holds after   an asymptotic expansion (*) is derived when
$M(\lambda)$ extends to a meromorphic function with simple poles confined to a set
$\{\vvv q\uuu k\}$ of strictly negative real numbers
which in addition satisfies certain growth conditions which
we give below.

\medskip

\noindent
{\bf{The Mellin conditions.}}
Let $M(\lambda)$
be a meromorphic function
in the complex $\lambda$-plane with simple poles at a
strictly decreasing sequence of negative  numbers
$\{-q_\nu\}$ where
$0<q_1<q_2<\ldots$.
We say that the meromorphic function satisfies
the Mellin conditions when the following hold:

\medskip
\noindent
\emph{For every
positive integer $N$ there exists some  $q_N<A<q_{N+1}$
such that the follwing two limit formulas hold:}
\[
\lim_{R\to\infty}\,
\frac{1}{R}\cdot
\int_{-R}^R\,  \bigl|M(-A+is)\bigr|\cdot ds=0\tag{i}
\]
\[
\lim_{R\to\infty}\,\int_0^{-A}\, 
\bigl[\epsilon^{-t-iR}\cdot \frac{M(t+iR)}{t+iR}-
[\epsilon^{-t+iR}\cdot \frac{M(t-iR}{t-iR}\bigr]\cdot dt=0\tag{ii}
\]
\medskip



\noindent
{\bf{3. Theorem.}}\emph{If the meromorphic function
$M(\lambda)$ satisfies the Mellin conditions it follows that
the $J$-function defined by}
\[
J(\epsilon) =\lim_{R\to\infty}\, \int_{-R}^R\,
\epsilon^{-is}\cdot \frac{M(is)}{is}\, ds
\]
has an asymptotic expansion where the constants
$\{c_k\}$ whis appear in (*) are given by:
\[ 
c_k=\mathfrak{res}(M:q_k)\quad\colon\quad k=1,2,\ldots
\]



\noindent
\emph{Proof.}
With $\lambda=t+is$ we consider  line integrals over rectangles
\[
\square_{R,A}=\{-A<t<0\}\cap\, \{-R<s<R\}\tag{5}
\]
where one for  an  arbitrary positive integer $N$  choose
$A$ so that 
\[
q_N<A<q_{N+1} \tag{6}
\]
With $\epsilon>0$
kept fixed we have the analytic function in
$\square_{R,A}$  defined by
\[ 
\lambda\mapsto \epsilon^{-\lambda}\cdot \frac{M(\lambda)}{\lambda}\tag{6}
\]





\noindent
Cauchy's residue formula gives the equality:
\[
2\pi i\cdot J_R(\epsilon)=
2\pi i\cdot \sum_{k=1}^{k=N}\,q_k^{-1}\cdot 
\mathfrak{res}(M(\lambda):q_k)\cdot \epsilon^{q_k}
+I_1(R,A)+I_2(R,A)\tag{i}
\]
where 
\[
I_1(R)=\int_0^{-A}\, 
\bigl[\epsilon^{-t-iR}\cdot \frac{M(t+iR)}{t+iR}-
[\epsilon^{-t+iR}\cdot \frac{M(t-iR}{t-iR}\bigr]\cdot dt\tag{ii}
\]
\[
I_2(R)=-\int_{-R}^R\,  \epsilon^{A-is}\cdot 
\frac{M(-A+is)}{-A+is}\cdot ds\tag{iii}
\]


\noindent
The triangle inequality gives

\[
|I_2(R)|\leq  \epsilon^A\cdot 
\int_{-R}^R\,  \bigl|\frac{M(-A+is)}{-A+iRs}\bigr|\cdot ds
\leq\epsilon^A\cdot\frac{1}{R}\cdot
\int_{-R}^R\,  \bigl|M(-A+is)\bigr|\cdot ds\tag{3.1}
\]





\noindent
Above we have  $A>q_N$ and hence $\epsilon^A$
gives an admissable error for an asymptotic expansion
up to order $N$
and Theorem ¤ XX follows.





\bigskip

\noindent
{\bf{4. The case of
multiple roots.}}
Keeping Meelin's   conditions one
can relax the hypothesis that the poles of
$M(\lambda)$ are simple and obtain
an asymptotic expansion of the $J$-function where 
the terms $\{c_k\epsilon^{q_k}\}$ in  (*)
are replaced by finite sums of the form
\[ 
\sum_{\nu=0}^{m_k-1}\, c_{k,\nu}\cdot (\log \epsilon)^\nu\cdot \epsilon^{q_k}\tag{1}
\]
where $m_k$ is the multiplicity of the pole of $M(\lambda)$ at $q_k$.
To see this we notice that while 
Cauchy's residue formula was applied during the proof above
the terms
$2\pi i\cdot q_k^{-1}\mathfrak{res}(M(\lambda):q_k)$
are replaced by
\[
2\pi i\cdot \mathfrak{res}(\epsilon^{-\lambda}M(\lambda):q_k)\tag{2}
\]
For a given $k$ we set $\lambda=-q_k+\zeta$
and here  the residue is found via  
the expansion
\[
\epsilon ^{q_k+\zeta}=\epsilon^{q_k}\cdot
\bigl [1+\sum_{\nu=1}^\infty
\,(\log \epsilon)^\nu\cdot\zeta^\nu\bigr]
\]

\newpage


\noindent
{\bf{Example.}}
Suppose that $M(\lambda)$ has a double pole at $-q_k$
with a local Laurent expansion
\[
M(-q_k+\zeta)= \frac{c_k}{\zeta^2}+a_0+a_1\zeta+\ldots
\]
In this case the residue in (2) becomes
\[
\mathfrak{res}(\epsilon^{-\lambda}M(\lambda):q_k)=
c_k\cdot \epsilon ^{q_k}\cdot \log\epsilon\tag{3}
\]
\medskip


\noindent
{\bf{Remark.}}
To appreciate Mellin's result one should consider various examples where
the point is that other kind of methods to begin with prove that
the $M$\vvv function has a "nice" meromorphic extension as above.
Quite extensive classes of situations where this applies are derived via
$\mathcal D$\vvv module theory.
The reader may also consult the  article [Barlet\vvv Maire]
where Mellin's result is extended to give complex
expansions, i.e here a $J$\vvv function is defined in a punctured complex disc
where asymptotic expansions appear
when a complex variable $\zeta$ tends to zero instead of 
taking limits as in (*) over positive real $\epsilon$.
\medskip

\noindent
Let us also point out that
one can consider aymptotic expansions of
distribution-valued functions.
Consider for example a real-valued polynomial $P(x,y)$ of two variables.
By Sard's  Lemma there exists some $s_*>0$ such that
$P$ has non-critical  values in $(0,s_*)$, i.e.
for every
$0<s<s_*$ the real hypersurface
$\{P=s\}$ is a non-singular.
It consists in general of a union of a (possibly empty) finite 
family of closed
bounded curves and   some union of simple curves which
are unbounded. The reader should contemplate upon 
examples such as $P(y,x)= y^2-x^3-2x$.
In addition to "naive  geometric pictures"
one can study distribution-valued functions.
Namely, for each $\phi(x,y)$ in the Schwartz class
we set
\[
J_\phi(s)= \int_{\{P=s\}}\, \phi\cdot dx
\]
where one has taken a sum of line integrals over
the family of  curves which constitute
$\{P=s\}$ and they  have been  oriented in a natural fashion.
Now one attains an asymptotic expnasion which
gives a far more
detailed description of the "naive geometric pictures".
Namely, one finds that
the $\mathcal S^*$-valued $J$-function has an asymptoptic expansion
(*) whose  coefficients  are
tempered distributions.
That such asymptotic expansions exist
was shown  
by Marcel Ruesz in special cases and used to construct fundamenntal solutions.
See also
the text-book series [Gelfand-et.al].
In a more general set-up where
$P(x,y)$ is an arbitrary polynomial and
even can depend upon more than two variables, the
existence of an aymptotic expnbasion was
established by Nils Nilsson in the impressive article [Nilsson].
Later work has employed Hironka's desingularisation which
and far-rechaing studies of asymptotic expansions as above
occur in
$\mathcal D$-module theory where one foremost should mention
contributions by Barlet.
Here it would bring us to far to
expose this theory in detail. For a general account about
$\mathcal D$-module theory and how it is used to
construct asymptotic expansions I refer to my  article [Bjšrk] in [Abel Legacy].













 

\bigskip

\centerline{\bf  {E. The family $\int\,P_+^{2\lambda}$}}

\bigskip

\noindent
Let $P(x,y)$ be a real-valued polynomial 
in ${\bf{R}}^2$.
When $\mathfrak{Re}(\lambda)>0$
it is clear that we obtain a tempered distribution defined by
\[
\phi\mapsto \int_{\{P>0\}}\, P(x,y)^{2\lambda}\cdot\phi(x,y)\cdot dxdy\tag{*}
\]
Moreover,  this gives a distribution-valued holomorphic
function in the right half-plane.
More generally we can
consider 
a connected component $\Omega$ of the set $\{P>0\}$
and obtain the $\mathcal S^*$-valued function defined by:
\[
\phi\mapsto \int_\Omega\, P(x,y)^{2\lambda}\cdot\phi(x,y)\cdot dxdy\tag{**}
\]
\medskip

\noindent
It turns out that both (*) and (**) extend to meromorphic
distribution valued functions in the whole complex
$\lambda$-plane and there exists a 
finite set of positive rational numbers
$\{ q_\nu\}$
such that the poles are contained in the set
\[ 
\cup_{k=1}^m\, \mathcal A_k=\{-q_k-n\quad\colon n=0,1,2\ldots\}
\]
\medskip


\noindent
Moreover, these meromorphic extensions satisfy the 
Mellin condtiions which
can be used to recover the asymptotic expansions which were
described in ¤ XX.
\bigskip


\noindent
{\bf{The  functional equation.}}
Using algebraic properties of  the Weyl algebra 
of differential operators with polynomial coefficients, Joseph Bernstein gave
a  remarble simple proof 
of the mere existence of the meromorphic
extension of the  distribution-valued function
in (*) above which we denote
by $\mathcal P_+^\lambda$.
More precisely,  
the meromorphic
extension is   achieved by a functional equation. Namely, 
the meromorphic extension in
(*) follows from the existence of a non-zero polynomial $b(\lambda)$ in
${\bf{C}}[\lambda]$ such that

\[
b(\lambda)\cdot\int_{\{P>0\}}\,P(x,y)^{2\lambda}\cdot\phi(x,y)\cdot dxdy
=
\] 
\[
\sum\,\lambda^k
\cdot\int _{\{P>0\}}\, P(x,y)^{2\lambda+1}\cdot Q_k(\phi)(x,y)\cdot dxdy\tag{*}
\]
hold for every $\phi$ in $\mathcal S({\bf{R}}^2)$
where $\{Q_k\}$ is a finite set of differential operators 
indexed by non-negative integers
which  belong 
to the Weyl algebra $A_2$, i.e., they are globally definied
differential operators wirh polynomial coefficients.
Above one can choose $b(\lambda)$ of smallest possible degree and it is then
referred
to as the \emph{Bernstein-Sato polynomial} of $P$.
We remark that the tribute to M. Sato stems from his early
discoveries of  functional equations as above.
The fact that the 
roots of the $b$-function always are strictly negative rational numbers was
established by Masaki Kashiwarin in the article [Kashiwara] from 1975.
In addition to (*), Kashiwara also estalnished a second functional equation
which implies that Mellin's two conditions are valid.
More precisely, given the polynomial $P$ as above, it is proved in
[loc.cit] that there exists a positive integer $m$ and
a finite set
$\{Q_0,\ldots,Q_{m-1}\}$ in
$A_2$ such that
\[
\lambda^m\cdot \mathcal P_\lambda(\phi)=
\sum_{k=0}^{m-1}\, \,\lambda^k
\cdot\int _{\{P>0\}}\, P(x,y)^{2\lambda}\cdot Q_k(\phi)(x,y)\cdot dxdy\tag{**}
\]





















\end{document}











 




 




