


\documentclass{amsart}
\usepackage[applemac]{inputenc}
\addtolength{\hoffset}{-12mm}
\addtolength{\textwidth}{22mm}
\addtolength{\voffset}{-10mm}
\addtolength{\textheight}{20mm}

\begin{document}




\bigskip


\centerline{\bf{Course in advanced analysis}}




\[
\emph{Special topics: Subharmonic and plurisubharmonic
functions in the complex domain.}
\]

\bigskip


\noindent
{\bf{Time and location.}}
The first lecture takes place January 20 : $10^{15}-12^{00}$ in
Lecture room 306 at the department of mathematics SU.
\[
\text{Welcome}
\]
\[
\text{Jan-Erik Björk}
\]










 \bigskip

\noindent
{\bf{Contents.}}
The course is foremost adressed to Phd-students interested in
complex analysis.
A proposed   examination procedure
is that
participants deliver
a lecture about a selected topic.
The headline \emph{Lectures 4-9}
describe  the general spirit (or level)  of the lectures.
Much  attention is given to harmonic and subharmonic functions
where probabilistic considerations also appear.
Here is an  example:
Denote by 
$\Pi$ the family of  open and
simply connected
domains
in ${\bf{C}}$ which contain the origin and
have area $\pi$.
Let $\Omega$ be in this family and suppose that
$\ell$ is an open interval of the vertical line
$\mathfrak{Re}( z) =\rho$
for some $\rho>0$.
Then there exists the harmonic measure
$\mathfrak{m}_ 0^\Omega(\ell)$.
which is the probability that
a Brownian motion 
hits a point in $\ell$
at the first moment 
when it has reached $\partial\Omega$. Or equivalently,
$\mathfrak{m}_ 0^\Omega(\ell)$
is the value at $z=0$ of the harmonic function in
$\Omega$ with boundary value 1 on $\ell$ and
zero on
$\partial\Omega\setminus\ell$.
\medskip

\noindent
{\bf{Theorem.}}
\emph{For every simply connected domain
$\Omega\in\Pi $ and each pair $\rho$ and $\ell$ as above
one has the inequality}
\[
\mathfrak{m}_ 0^\Omega(\ell)\leq \frac{2}{\pi}\cdot \text{arcsin} e^{-\rho^2}
\]
\medskip

\noindent
{\bf{Remark.}}
This theorem is due to
Otto Frostman   and appears in his  thesis  devoted to 
equilibrium measures in potential theory, together with a
description  of a simply connected domain
$\Omega_\rho$  which together with  an interval $\ell$
give the
equality 
above.
Personally I find a result of this kind  both striking and
elegant, especially since
it is not "intuitively clear"
how to choose an extremal domain
$\Omega_\rho$ in spite of  the probabilistic
interpretation.
A proof will
be given  during a session 
devoted to
Dirichlet integrals 
based upon an article by Beurling
where more general  results appear which
can be used to
establish upper bounds for harmonic measures and therefore has independent interest
in probability theory - such as   the "pop-subject"  mathematics
of finance
where evaluations of barrier options rely upon
formulas for harmonic measures.
In any case, the lectures during the course are 
adressed to those who are interested to learn
about results as above
where complex analysis 
plays a central role.

\medskip

\noindent
{\bf{Functional analysis.}}
Some general facts will be used without hesitation from
basic measure theory and
functional analysis.
In complex analysis
one encounters various Frechet spaces
and Theorem 1.1 below  is often used.
Recall  that
a Frechet space $E$
is a complex vector space equipped with
a sequence of semi-norms
$\{||\cdot ||_n\colon n=1,2,\ldots\}$ which become
stronger with $n$, i.e. $||x||_n\leq ||x||_{n+1}$
hold for every $n$.
Frechet's condition is that
these semi-norms give
a complete metric defined by
the distance function
\[ 
d(x,y)= \sum_{n=1}^\infty\, \frac{||x-y||_n}{1+||x-y||_n}
\]
A subset $W$ of $E$ is bounded if there to each $n$ exists
a constant $C(n)$ such that
\[ 
\max_{x\in W}\, ||x||_n\leq C(n)
\]
A linear operator $T\colon E_1\to E_2$ from one Frechet space to another
is compact if it maps every bounded subset in
$E_1$ to a relatively compact
set in the metric space $E_2$.
\medskip

\noindent
{\bf{1.1 Theorem.}}
\emph{Let $S\colon E_1\to E_1$ be a bounded and surjective linear
operator.  Then $S+T$ has a closed range with finite codimension for
every compact operator
$T\colon E_1\to E_2$.}

\medskip

\noindent
A variant 
goes as follows:
Let $E_1,E_2,F$ be three Frechet spaces
and consider a pair of linear operators
\[
 S_1\colon E_1\to F\quad\colon S_2\colon E_2\to F
\]
where $S_1$ is continuous and $S_2$ compact
and suppose that the map
\[ 
(e_1,e_2)\mapsto S_1(e_1)+ S_2(e_2)
\]
is surjective.
Then the quotient space
$\frac{F}{S_1(E_1)}$ is finite dimensional.
\medskip

\noindent
{\bf{Exercise.}}
Prove the results above, The hint is to apply
Baire's category theorem for complete metric spaces.

\medskip


\noindent
{\bf{Spectral theory for linear operators.}}
Tbe pioneering work by Gustav Neumann 
from 1879
about solutions ot the Dirichlet problem,
followed by some further studies  by
Poincaré,  leads to the extension of matrix calculus
where matrices with complex elements are replaced by general densely defined
linear operators acting on a
complex Banach space $X$.
More precisely, the spectrum $\sigma(T)$
of a densely defined
linear operator $T\colon X\to X$
is by definition the closed complement of the open
set
of ${\bf{C}}$ which consists of complex numbers
$\lambda$ for which Neumann's resolvent operator $R_T(\lambda)$ exists.
Here $R_T(\lambda)$ is a uniquely
determined  bounded linear operator on $X$ which satisfies
\[
R_T(\lambda)(\lambda\cdot E-T)(x)= x\quad\colon x\in \mathcal D(T)
\]
Moreover,  the range of $R_T(\lambda)$ is equal to $\mathcal D(T)$ and
\[
(\lambda\cdot E-T)(R_TR(\lambda)(x)= x\quad\colon x\in X
\]
Above $\mathcal D(T)$ is the domain of definition of $T$ and $E$ the identity operator on
$X$.
A major result, which stems from
Neumann's equation for resolvents, is
the operational calculus which is proved by Cauchy's integral formula.
For the reader's convenience
we have inserted an  appendix about Neumann's 
classic theory
since
text-books devoted to functional analysis have tendency to "delay" 
Neumann's theory until
a late stage. My personal  opinion is that this theory
should be exposed immediately 
after one has introduced the notion of norms on vector spaces
in order to
illustrate the power of complex analysis.














\newpage




\centerline{\emph{Contents.}}

\bigskip
\noindent
Below follows an outline of the contents during
the first 9 lectures which are divided in 3 separate parts.
Lecture 1-3 deals with Riemnan surfaces and Lectures 4-5 with
the Laplace operator in the complex domain,
while Lecture 5-9
are devoted to subharmonic functions of one complex variable.
The later part of the course
treats several complex variables with special attention about
currents and plurisubharmonic functions.
We give a rather  detailed account about Riemann surfaces,
but begin with a survey about material in
lecture 4-9.

\bigskip


\noindent
\emph{Lecture 4: The Laplace operator in the complex domain.}

\medskip

\noindent
\emph{Lecture 5: The heat equation}

\bigskip
\noindent
\emph{Lecture 6-9}

\medskip
\noindent
\emph{A. A result by Nevanlinna}



\medskip
\noindent
\emph{B. Subharmonic configurations}


\medskip

\noindent
\emph{C. Zero sets of subharmonic functions}



\medskip
\noindent
\emph{D. The Riemann-Schwarz inequality}




\bigskip

\noindent
\emph{E. Special topics about subharmonic functions.}


\medskip
\noindent
\emph{1. Largest subharmonic minorants}

\medskip

\noindent
\emph{2. Dirichlet integrals}
\medskip

\noindent
\emph{3. Carleman's differential inequality}
\medskip

\noindent
\emph{4. Weighted Runge approximations}
\bigskip

\noindent
\emph{Appendix: Spectral thory for linear operators.}


\bigskip

\noindent{\bf{2nd part.}}
A more detailed account about 
material related to Riemann surfaces appears
at the end of these notes
which include
proofs of the Behnke-Stein theorem and the uniformisation
of open Riemann surfaces.
Material about compact Riemann surfaces
appear in separate notes starting with
an  account about doubly period meromorphic functions
in the complex plane which serves as an introduction. Here the
results about
elliptic curves
appear which go back to work
by  Abel, Jacobi and Weierstrass.





\newpage

\centerline {\bf{Lectures 4-5}}.
\bigskip

\noindent
Here is the set-up for
Lecture 4.
Let
$\Omega$ be a bounded and connected domain in
${\bf{C}}$
whose boundary consists of a finite number of
pairwise disjoint and differentiable closed Jordan curves.
With $p\in\Omega$
kept fixed we
consider the continuous function on
$\partial\Omega$ defined by
\[ 
q\mapsto  \log \frac{1}{|p-q|}
\]
Solving
the Dirichlet problem
we get the harmonic function
$u_p(q)$ in $\Omega$ where
\[
u_p(q)=\log \frac{1}{|p-q|}\,\colon\, q\in\partial\Omega
\]
Greens' function is defined for pairs $p\neq q$ in
$\Omega\times\Omega$ 
by
\[ 
G(p,q)= \log\,\frac{1}{|p-q|}-u_p(q)\tag{1}
\]
It is wellknown that $G$ is non-negative in
$\Omega\times\Omega$ and symmetric, i.e.
$G(p,q)=G(q,p)$.
Next, let $f\in L^2(\Omega)$, i.e  $f$ is complex-valued and square integrable over
$\Omega$. Set
\[ 
\mathcal G_f(p)=\frac{1}{2\pi}\cdot \int_\Omega\, G(p,q)\cdot f(q)\, dq\tag{2}
\]
Since
\[
 \iint_{\Omega\times \Omega}\, |G(p,q)|^2\, dpdq<\infty
\]
the linear operator  
$f\mapsto \mathcal G_f$ is 
of the Hilbert-Schmidt type and
therefore  compact  on the Hilbert space
$L^2(\Omega)$. Moreover,
since 
$\frac{1}{2\pi}\cdot \log\sqrt{x^2+y^2}$ is
a fundamental solution to the Laplace operator one has:

\medskip

\noindent{\bf{A.1  Theorem.}}
\emph{For each $f\in L^2(\Omega)$
the Laplacian of $\mathcal G_f$
taken in the distribution sense belongs to
$L^2(\Omega)$ and one has the equality}
\[ 
\Delta(\mathcal G_f)=-f\tag{*}
\] 


\noindent
Using this one proves that
there
exists an orthonormal basis $\{\phi_n\}$ in $L^2(\Omega)$ and a
non-decreasing sequence of positive real numbers
$\{\lambda_n\}$ such that
\[ 
\Delta(\phi_n)+\lambda_n\cdot \phi_n=0\quad\colon n=1,2,\ldots\tag{i}
\]
holds in $\Omega$ where each $\phi_n$
extends to a continuous function on the closure with
boundary value zero on $\partial\Omega$.
Let us  remark that (i) means that
\[
\mathcal G(\phi_n)= \frac{1}{\lambda_n}\, \cdot \phi_n\tag{ii}
\]
So
$\{\lambda_n^{-1}\}$
are  the eigenvalues of the compact operator $\mathcal G$ whose sole cluster
point is $\lambda=0$.
Eigenvalues whose eigenspaces have
dimension $e>1$ are repeated $e$ times.
With these notations the result below 
was proved by Carleman in a lecture during the Scandinavian Congress at
Stockholm in 1934:
\medskip

\noindent
{\bf{A.2 Theorem.}}
\emph{For each point $p\in\Omega$ one has the limit formula}
\[
\lim_{n\to \infty}\, \frac{1}{\lambda_n}\cdot
\sum_{k=1}^{k=n}\, \phi_k(p)^2=
 \frac{1}{4\pi}\tag{*}
 \]
 \medskip
 
 
 \noindent
{\bf{Remark}}. Notice that (*)
holds for
every domain $\Omega$ as above, i.e. independent if its
degree  of   connectivity.
Similar asymptotic formulas hold for
derivatives of the $\phi$-functions. One has for example
\[
\lim_{n\to \infty}\, \frac{1}{\lambda_n}\cdot
\sum_{k=1}^{k=n}\, \frac{\partial \phi_k}{\partial x}(p)^2=
 \frac{1}{16\pi^2}\tag{**}
 \]
 The proof relies heavily upon analytic function theory
 where one  
 considers the Dirichlet series:
\[ 
\Phi_p(s)=\sum _{n=1}^\infty \, \frac{\phi_n(p)^2}{\lambda_n^s}\tag{0.4.3}
\]
The major result to be proved in  Lecture 4 goes as follows:
\medskip

\noindent
{\bf{A.3 Theorem.}}
\emph{There exists an entire function
$\Psi_p(s)$ such that}
\[
\Phi_p(s)=\Psi_p(s)+\frac{1}{4\pi(s-1)}
\]
\medskip

\noindent
Carleman's   proof of Theorem A.3 is very instructive.
It relies upon a change of complex contour integrals
similar to those employed  by Riemann in his  studies about
the $\zeta$-function, 
together with a  sharp 
asymptotic estimates
of 
Greens' kernel functions  $G(x;y;-\kappa)$ when $\kappa\to +\infty $.
The fact that
Theorem A.3  gives Theorem A.2  follows via 
a result  from  N. Wiener's   article
\emph{Tauberian theorem} [Annals of Math.1932
which asserts that if $\{\lambda_n\}$ is a non-decreasing sequence of
positive numbers  tending to infinity, and
$\{a_n\}$ are non-negative real numbers such that
there exists the limit
\[ 
\lim_{s\to 1}\,(s-1)\cdot \sum\, \frac{a_n}{\lambda_n^s}=A
\] 
then 
\[
\lim_{n\to \infty}\,\lambda_n^{-1}\cdot
\sum_{k=1}^{k=n}\, a_k=A
\]
Time will prevent me from giving detailed proofs of
this Tauberian theorem but details appear in
my notes devoted to analytic function theory
and Wiener's result could be an example for an
"examination lecture".

\bigskip

\centerline{\emph{Lecture 5: The heat equation.}}

\medskip


\noindent
In probability theory  one considers stochastic processes in
continuous time of the Markov type. The time dependent distributions 
densitites appear as solutions to
parabolic PDE-equations.
An example is the diffusion process expressed by the stochastic differential equation
\[ 
dX_t=b(X(t),t)\cdot dW
\]
where $dW$ is a "white noise"
which for small $dt$ is a normally distributed variable with
variance
$\sqrt{dt}$ and independent of the present stage $X(t)$,
i.e. one has independent increments.
It means that
the random variabe $X(t+dt)$ is infinitesmally equal to the sum of $X(t)$ and
$b(X(t),t)\cdot W(\sqrt{dt})$ where $X(t)$ and $W(\sqrt{dt})$ are independent 
random variables.
Taking the Fourier transform of  the distribution function
$f(x,t)$ of $X(t)$ we get
\[
\widehat{f}(\xi;t+dt)=\frac{1}{\sqrt{2\pi}\cdot \sqrt{dt}}
\cdot \iint\, e^{-i\xi(x+b(x,t)u})
\cdot f(x;t)\cdot e^{-u^2/2dt}\, dxdu+o(dt)
\]
where the remainder is small ordo of $dt$.
The variable substitution $u\mapsto \sqrt{dt}\cdot s$
identifies the double integral above with
\[
\frac{1}{\sqrt{2\pi}}
\cdot \iint\, e^{-i\xi(x+b(x,t)\sqrt{dt}\cdot s})
\cdot f(x;t)\cdot e^{-s^2/2}\, dxds
\]
A Taylor expansion of the complex exponential function
$\zeta\to e^{i\zeta}$ at $\zeta=0$ gives
\[
\lim_{dt\to 0}\,
\frac{\widehat{f}(\xi;t+dt). \widehat{f}(\xi,t)}{dt}=
-b(x,t)^2/2\cdot 
\int\, \xi^2\cdot \widehat{f}(\xi;t)\, d\xi
\]
Fourier's inversion formula entails that
$f(x,t)$ satisfies the PDE
\[
\frac{\partial f}{\partial t}=\frac{
b(x,t)^2}{2}\cdot \partial_x^2(f)\tag{*}
\]
At time $t=0$ we suppose that $X_0$ has a given distribution function
$f_0(x)$ which therefore gives
the initial condition
\[ 
f(x;0)= f_0(x)
\]
where one from  assumes that
$X_0$ has a finite variance, i.e.
\[ 
\int\, x^2\cdot f_0(x)\ dx<\infty
\]



\noindent
The PDE in (*) is 
parabolic and basic results for such
equations 
were established by Gevrey, Hadamard and Holmgren
around 1900. 
The prototype  is the equation
\[
\frac{\partial u}{\partial y}=
\frac{\partial^2 u}{\partial x^2}
\]
defined in a strip domain
$B=\{-\infty < x<\infty\}\times \{-A<y<A\}$.
The favourable  case occurs if
there exists a constant $C$ such that
\[ 
|u(x,y)|\leq C\cdot e^{x^2}\tag{**}
\]
Then $u(x,y)$ is determined by
its
restriction $x\mapsto u(x,a)$ for every
fixed
$-A<a<A$ by the integral formula
\[ 
u(x,y)=
\frac{1}{2\sqrt{\pi (y-a)}}\int_{-\infty}^\infty\,
u(\xi,a)\cdot U(x-\xi,y-a)\, d\xi\quad\colon a<y<A\tag{i}
\]
where $U(x,y)$ is the function which is zero when $y\leq 0$ and 
\[
U(x,y)= e^{-x^2/4y}\,\colon\, y>0
\]
When (**) fails one cannot represent $u$ in the trivial fashion above
but the question remains if uniqueness hold under a less restrictive condition than
(**). A positive answer was given
by
Erik Holmgren in the 
article \emph{Sur les solution quasi-analytique d l'équation de chaleur}
[Arkiv för matematik. 1924] where he proved
that the solution $u$ is uniquely determined by
a restriction to some $\{y=a\}$ if there exists a constant $k\geq 0$
such that
\[
|u(x,y]|\leq e^{kx^2\cdot \log(e+|x|)}\quad\colon\, (x,y)\in B\tag{***}
\]

\medskip

\noindent
Leter work by Täcklund demonstrated that
Holmgren's uniqueness theorem is essentially sharp.
A
suggestion for an "examination lecture"
is to expose 
constructions by Beurling who considered
solutions satisfying
\[
u(x,y)|\leq e^{\epsilon(|x|)\cdot x^2\cdot \log(e+|x|)}\tag{****}
\]
where    $\epsilon(r)$  tends to zero as
$r\to+\infty$. 
When (****) holds
Beurling  found   an integral kernel $U^*$
which serves as a substitute for the standard kernel $U$  in (i).
The  construction of $U_*$ gives
an
instructive  lesson 
about the role of analytic functions
in PDE-theory.


\bigskip




\centerline
{\bf{B. Lecture 6-9}}


\medskip


\noindent

\noindent
The logarithmic potentials and
the Cauchy transform play a
central role.  Here
"pure analysis" intervenes with more geometric constructions
while harmonic and subharmonic functions
are studied. Let us begin with    a typical result which will
be covered during lecture 6-9:
\bigskip


\noindent
\centerline {\emph{A. A  theorem by Nevanlinna}}. 
\medskip


\noindent
Let $\Omega$ be a connected and bounded
domain in ${\bf{C}}$
whose boundary consists of $p$ many pairwise disjoint and closed
Jordan curves
$\Gamma_1,\ldots,\Gamma_p$.
On each $\Gamma_\nu$
we consider a function $\phi_\nu$
which takes the value +1 on a finite
union of intervals and  zero on the complementary intervals.
So unless $\phi$ happens to be constant on a single
curve  $\Gamma_\nu$
we get jumps 
at common boundary points of  intervals where $\phi_\nu$ is constant.
The number of such points is  an even integer denoted by $2\cdot k_\nu$
where
$k_\nu=0$ means that
$\phi_\nu$ is identically 1 or 0 on $\Gamma_\nu$.
Solving  Dirichlet's problem we get a harmonic function $\omega(z)$
whose boundary function is  $\phi$ and in $\Omega$ there exists the analytic function
\[ 
g(z)= \frac{\partial \omega}{\partial x}
-i\cdot \frac{\partial \omega}{\partial y}
\]

\medskip

\noindent
{\bf{Theorem.}} \emph{The number of zeros of $g$ counted
with multiplicities is equal to}
\[
k_1+\ldots+k_p+p-2
\]
Nevanlinna's  proof gives an instructive lesson how
the argument principle intervenes with level sets
of harmonic functions.


\medskip


\centerline{\emph{B. Subharmonic configurations}}

\medskip


\noindent
Let $\mu$ be a Riesz measure
in ${\bf{C}}$ supported 
by a compact null set. Assume that
its Cauchy transform
\[
\widehat{\mu}(z)= \int \frac{d\mu(\zeta)}{z-\zeta}
\]
satisfies an algebraic equation
$p_m(z)\cdot \widehat{\mu}^m(z)+\ldots
p_1(z)\cdot \widehat{\mu}(z)+p_0(z)=0$
in
${\bf{C}}\setminus \text{Supp}(\mu)$
where $\{p_\nu(z)\}$ are polynomials.
In a joint article by
J. Borcea, R. Bögvad and myself, it is proved
that the support of $\mu$ is a finite union of
real-analytic compact Jordan arcs.
The proof relies upon a study
of piecewise harmonic subharmonic functions.
For example, given a finite family of harmonic functions
$h_1,\ldots,h_k$
in some open connected domain $\Omega$
there exists the  subharmonic function
$u$ defined as the maximum of this $k$-tuple.
Conversely, suppose that $u$ is subharmonic in 
$\Omega$ where its 
Riesz measure is supported by some  null-set while
the restriction of $u$ to every connected component of
$\Omega\setminus \text{Supp}(\Delta(u)$
is equal to one of the given $h$-functions.
An example discovered by Borcea and Bögvad
shows that this in general need not imply that
$u=\max(h_1,\ldots,h_k)$.
However, one can prove
that this equality holds under the condition
that the $k$-tuple of gradient vectors of
the $h$-functions are extreme points in the convex
set they generate in
${\bf{C}}$.
When this holds
one  says that
$h_1,\ldots,h_k$ admit a unique subharmonic configuration.
Without this condition on the gradient vectors
one seeks the family of all subharmonic configurations, i.e.
the set of all subharmonic functions $u$ in
$\Omega$ for which
$\text{Supp}(\Delta u)$ is a null set and
the restriction of $u$ to every
connected component of
$\Omega\setminus \text{Supp}(\Delta u)$ 
is equal to one of the given harmonic $h$-functions.
This leads to some open and problems and it is
also natural to try to extend this study to
higher dimensions where
one
instead consider
finite families of pluirsubharmonic functions and
seek there plurisubharminic configurations.
This will
be a topic during the second half of the course.







\bigskip








\centerline {\emph{C.  Zero sets of subharmonic functions.}}

\medskip

\noindent
Some of the topics  
are described in
§ B-E below where
logarithmic potentials and
the Cauchy transform play a
central role.  Here
"pure analysis" intervenes with more geometric constructions
while harmonic and subharmonic functions
are studied. Let us describe   a typical result which will
be covered during lecture 6-9:
\medskip


\noindent
{\bf{A  theorem by Nevanlinna}}. 
Let $\Omega$ be a connected and bounded
domain in ${\bf{C}}$
whose boundary consists of $p$ many pairwise disjoint and closed
Jordan curves
$\Gamma_1,\ldots,\Gamma_p$.
On each $\Gamma_\nu$
we consider a function $\phi_\nu$
which takes the value +1 on a finite
union of intervals and  zero on the complementary intervals.
So unless $\phi$ happens to be constant on a single
curve  $\Gamma_\nu$
we get jumps 
at common boundary points of  intervals where $\phi_\nu$ is constant.
The number of such points is  an even integer denoted by $2\cdot k_\nu$
where
$k_\nu=0$ means that
$\phi_\nu$ is identically 1 or 0 on $\Gamma_\nu$.
Solving  Dirichlet's problem we get a harmonic function $\omega(z)$
whose boundary function is  $\phi$ and in $\Omega$ there exists the analytic function
\[ 
g(z)= \frac{\partial \omega}{\partial x}
-i\cdot \frac{\partial \omega}{\partial y}
\]

\medskip

\noindent
{\bf{Theorem.}} \emph{The number of zeros of $g$ counted
with multiplicities is equal to}
\[
k_1+\ldots+k_p+p-2
\]
Nevanlinna's  proof gives an instructive lesson how
the argument principle intervenes with level sets
of harmonic functions.

\bigskip




\noindent
Let  $\Omega$ in ${\bf{C}}$ be a bounded open set and
denote by
$\text{SH}_0(\Omega)$
the set of  subharmonic functions in   $\Omega$
whose Laplacian is a Riesz measure supported by a 
compact null set. Every such function $u$ is locally the sum of a harmonic function
and a
logarithmic potential 
\[
u(z)=\frac{1}{2\pi}\cdot \int\,\log|z-\zeta|\cdot d\mu(\zeta)
\]
where $\mu$ is a non-negative Riesz measure with compact support.
This entails
that 
the distribution derivatives  $\partial u/\partial x$
and
$\partial u/\partial y$  belong to
$L^1_{\text{loc}}(\Omega)$.
Before 
the theorem below is announced
we need  a geometric construction.
If $U$ is a bounded  open subset of $\Omega$ and 
$\zeta\in U$ we denote by 
$s(\zeta)>0$ the largest positive number such that
the line segment
\[
\ell_\zeta=
\{ \zeta+x\,\colon \, 0\leq x<s(\zeta)\}\subset \Omega
\]
Put 
\[ 
\mathfrak{s}(U)=\bigcup_{\zeta\in U}\, 
\ell_\zeta\tag{*}
\]
This yields an open  set called
the
forward star domain of $U$.
\bigskip

\noindent{\bf{Theorem.}}
\emph{Let 
$g\in\text{SH}_0(\Omega)$ and put
$K=\text{Supp}(\Delta(g))$. Let  $U$ be an open subset of
$\Omega\setminus K$  with the property that
$g=0$ in  $U$  and}
\[
\partial g/\partial x(z)<0,\quad\colon
z\in \Omega
\setminus (K\cup U)
\]
\emph{Then $g=0$ in $\mathfrak{s}(U)$.}
\medskip

\noindent
This result is a slight extension of a theorem  which appears in
a joint article by T. Bergquist and H. Rullgård
where it was  used
to prove that if $Q(z)$ is a monic polynomial of
some
degeee
$n$, then there exists a unique compact and connected
null-set   $\Gamma$ in
${\bf{C}}$ which contains the zeros of $Q$
and 
the extended complex plane minus $\Gamma$ is connected.
Moreover, and this is the crucial point, 
there exists a probability  measure $\mu$ supported by
$\Gamma$
such that
the Cauchy transform
\[
\widehat{\mu}(z)=
\int \, \frac{d\mu(\zeta)}{z-\zeta}
\]
satisfies the equation
\[ 
\widehat{\mu}(z)^n=
Q(z)^{-1}\quad\colon z\in {\bf{C}}\setminus |\Gamma
\]



\noindent
{\emph{Another Example.}}
Consider an algebraic equation
\[
 y^2=\frac{p(x)}{q(x)}\tag{1.1.4}
\]
where $q$ is a monic polynomial 
with simple zeros of some
degree $m+2$ and $p$ is monic with degree $m$
and the polynomials $p$ and $q$ have no common zero.
On the attached compact Riemann surface $X$
we get a local branch of $y$ at a point $p^*$ above $x=\infty$ whose series
expansion starts with $x^{-1}$. 
\medskip

\noindent
{\emph{ Conjecture}}
\emph{There exists a unique tree $\Gamma$ in the complex $z$-plane
such that the 
single-valued branch of $\sqrt{\frac{p}{q}}$
in ${\bf{P}}^1\setminus\Gamma$
with the Laurent expansion as above   at $z=\infty$
is equal to the Cauchy transform of a probability measure
supported by $\Gamma$}.
\medskip

\noindent
{\emph{Remark.}}
Affirmative answers to this conjecture 
have been established in special cases
by J. Borcea and
B. Shapiro and applied to  study
asymptotic distributions of roots to Lamé equations.
To settle
the conjecture 
amounts to contruct a specific
branch-cut on the associated hyperelliptic curve. For an eventual  proof is its tempting
to  employ potential-theoretic methods
where  results by Beurling might be
useful, i.e.
employ  subharmonic principles to settle a free boundary value problem
where one  minimizes certain energy integrals.
To achieve eventual  solutions may be "too hard" but at least 
one may settle 
specific cases which might be a reasonable and attractive subject
for   Phd-students interested in this kind of analysis.
Let us remark that
the proposed problem amounts to construct special triangulations on
compact Riemann surfaces $X$ whose
(eventual) solutions rely upon interesting  variational problems
where the Riesz mass of certain subharmonic functions
are minimized.




\bigskip


\centerline{\emph{D. The Riemann-Schwarz inequality.}}
\medskip

\noindent
Let $X$ be a non-compact   1-dimensional complex manifold
and $\sigma$ a
hyperbolic metric, i.e. in a local chart
$(U,z)$ the metric is
$e^{w(z)}\cdot d|z|$ where
$w$ is subharmonic in $U$.
To each pair of points $p,q$ in $X$
one has the  family $\mathcal C(p,q)$ of
rectifiable curves in $X$ with end-points at $p$ and $q$.
The Riemann-Schwarz inequality asserts that
for every pair
$\gamma_1,\gamma_2$ in 
$\mathcal C(p,q)$ and
each point $\xi\in\gamma_1$
there exists a curve 
$\alpha\in\mathcal C(p,q)$ and a curve $\beta$ with
end-points at $\xi$ and some point $\eta\in\gamma_2$ such that
\[
\sigma(\alpha)^2+\sigma (\beta )^2\leq
\frac{1}{2}\bigr (\sigma(\gamma_1)^2+\sigma(\gamma_2)^2\,\bigl )\tag{*}
\]
Moreover, the inequality (*) is strict with the exception for
a special rhombic situation when $X$ is the unit disc.
This inequality   gives
the existence of unique geodesic  curves
on $X$ with respect to the $\sigma$-metric.
The proof 
relies upon the uniformisation theorem for
Riemann surfaces and   calculations based 
upon  geometric properties  of Möbius transforms in the unit disc.

\bigskip

\centerline{\bf{E. Special topics about subharmonic functions.}}

\bigskip





\noindent {\emph{E.1. Largest subharmonic minorants.}}
Let $F$ be a real-valued function with values in
$[1,+\infty]$  defined in a bounded  open set
$\Omega$ in ${\bf{C}}$.
The function is assumed to be
upper semi-continuous, i.e. the sets $\{F<a\}$ are open for
every $1\leq a\leq +\infty$. Notice that
$F(z)=+\infty$ is allowed
on some non-empty and closed subset
of
$\Omega$.
One associates Sjöberg's minorant function
\[
\mathcal S_F(z)= \max_u\, u(z)
\] 
where
the maximum is taken over all subharmonic functions 
$u$ in $\Omega$ which are everywhere $\leq F$.
In general 
$\mathcal S_F(z)$ fails
to be subharmonic but a result due to Beurling
gives the following sufficient condition in order
that
$\mathcal S_F$ is subharmonic. Namely, 
subharmonicity holds if there
to every relatively compact set $\Omega_0$ of
$\Omega$ exists some $\epsilon>0$ such that
\[
\iint _{\Omega_0}\,[\log F(z)]^{1+\epsilon}\, dxdy<\infty
\]
\medskip

\noindent 
Beurling's  proof teaches a good lesson about
estimates of mass distributions of
$\Delta(u)$ for subharmonic functions which
also will appear 
in the second half of the lectures when 
plurisubharmonic functions are studied.
\medskip

\noindent 
{\emph{E.2. Dirichlet
integrals.}}
Let $h(z)$ be a harmonic function in
the open unit disc
$D=\{|z|<1\}$ with a finite Dirichlet integral
\[
D(h)=\sqrt{\iint_D\, (h_x^2+h_y^2)\, dxdy}
\]
Using polar coordinates $(r,\theta)$ 
we set
\[
M_h(r e^{i\theta})= \int_0^r\, |\frac{\partial h(se^{i\theta})}{\partial s}|\, ds
\quad\colon 
M_h^*(\theta)=
\lim_{r\to 1}\, M_h(r e^{i\theta})
\]
Let $h^*$ be the harmonic extension to $D$ of the boundary value function 
$M^*_h$. With these notations a result due to Beurling
asserts that
\[
D(h^*)\leq D(h)
\]
Just as in E.1, Beurling's ingenious  proof   
offers  an instructive
lesson about
subharmonic functions.


\bigskip


\noindent{\emph{E.3 Carleman's differential inequality.}}
Let $\Omega$ be a connected open set in ${\bf{C}}$ 
with the property that for
every
$x>0$
the
intersection $S_ x$ between
$\Omega$ and a  vertical line  $\{\mathfrak{Re}\, z=x\}$
is a non-empty
bounded set
on the real $y$-line.
Each $S_x$  is the disjoint union
of open
intervals $\{(a_\nu,b_\nu)\}$ and we set
\[ 
\ell(x)=\max_ \nu \,(b_\nu-a_\nu)\tag{*}
\]

\medskip


\noindent
Next, let
$u(x,y)$ be an arbitrary  positive harmonic   function
in $\Omega$ which 
extends to a continuous function on
the closure $\bar\Omega$  where $u=0$ on $\partial\Omega$. 
Notice that this class can be non-empty since
$\Omega$ is unbounded.
A typical case is that $\Omega$
is a sector bordered by a pair of disjoint simple curves
which both issue from the origin and tend to inifinity.
Set
\[ 
\psi(x)=\log\, (\int_{S_x}\,u^2(x,y)\cdot dy)\tag{1}
\]



\noindent
With these notations the following result was proved by Carleman in 1933.
\medskip


\noindent
{\bf {Theorem.}}
\emph{Given a pair $\Omega$ and $u$ as above there exists a constant
$C\geq 0$ such that}
\[
2\pi\cdot\int_0^x\, \frac{x-s}{\ell(s)}\cdot ds\leq
\int_0^x\,\psi(s)\cdot ds+\psi(x)+Cx\quad\colon x>0
\]

\medskip


\noindent
The proof is instructive since it teaches how to use
subharmonic majorisations and
suitable $L^2$-inequalities of Wirtinger.


\bigskip


\noindent
\emph{E.4 Weighted Runge approximations.}
Put  $z=x+iy$ and 
$\square=\{-a<x<a\}\times \{-b<y<b\}$.
This rectangle  contains
$\square_+= \{-a<x<a\}\times \{0<y<b\}$ and  the lower part
$\square_-=\square\cap \{y<0\}$.
Let 
$\phi(z)$ be an analytic function
in $\square_+$ which extends continuously to its closure.
A classic result, known as Runge's theorem,
entails that for every $\delta>0$ there exists
a sequence of polynomials $\{P_n(z)$
such that the maximum norms $|P_n-\phi|_{\square_+}$ tend to zero
and at the same time
the maximum norms of $|P_n|$ taken over
the rectangle
$\square(-\delta)=\{-a<x<a\}\times \{-b<y<-\delta\}$ tend to zero.
While such an approximation takes place
the maximum norms
of $\{P_n\}$ taken over $\square$ cannot remain uniformly bounded
when $\delta\to 0$.
For if this  holds, another classic  result, known as Montel's theorem,
implies that there exists
a sequence of polynomials which converge
to an analytic function $g$ in $\square$, where this convergence is
uniform over compact subsets of $\square$.
Here $g$ is   zero in
$\square(-\delta)$ which by analyticity entails that
$g$ is identically zero in $\square$. At the same time
$g=\phi$ in $\square_+$
which contradicts the assumption that
$\phi$ is not identically zero.

\medskip

\noindent
To compensate for this one   introduces the
family
$\mathcal W$
of real-valued continuous
functions $\omega(y)$
which are
even  and positive $y\neq 0$, and 
decrease to zero  as $y$ approaches zero
through positive or negative values.
An example is $\omega(y)=y^2$ and
another is 
$\omega(y)= e^{-1/y^2}$
which decreases quite rapidly to zero with
$y$.
With $\phi(z)$ given as above
and $\omega\in\mathcal W$ we say that
a weighted Runge approximation holds if there
exists a sequence of polynomials $\{P_n(z)\}$
such that
\[
\lim_{n\to\infty}\,
||\omega(y)(P_n(z)-\phi(z)||_{\square_+}+
||\omega(y)(P_n(z)||_{\square_-}=0\tag{*}
\]
It turns out that
such a weighted approximation exists
if
$\omega(y)$ tends to zero sufficiently fast.
The following
was established  by
Beurling
ín the article  \emph{Analytic continuations along a linear boundary:
Acta mathematica 1953}.

\medskip

\noindent
{\bf{E.4.1 Theorem}}
\emph{The weighted Runge approximation (*) exists
if and only if}
\[
\int_0^b\, \log\log \frac{1}{\omega(y)}\, dy=+\infty\tag{*}
\]
The proof gives an instructive lesson how to employ
subharmonic estimates.

\bigskip


\centerline{\bf{Several complex variables.}}


\bigskip

\noindent
Complex analysis in several variables is  more 
involved  compared with the 1-dimensional case.
However, it is tempting to try to extend 1-dimensinal results to
higher dimensions.
A basic result of this nature 
due to Deval and Sibony goes as follows:
\medskip

\noindent
{\emph{Jensen's formula in dimension $n\geq 2$}.
Let $\Omega$
be  a bounded and  strictly pseudo-convex domain
in ${\bf{C}}^n$ with smooth boundary.
When  $z_0 \in\Omega$ a probability measure
$\mu$ supported by $\partial\Omega$ is called a Poisson-Jensen measure
with respect to $z_0$  if
\[ 
f(z_ 0)=\int_{\partial\Omega}\, f(z)\cdot d\mu(z)
\] 
hold for all analytic functions $f$ in $\Omega$ which extend to be continuous 
on the closure  $\bar\Omega$.
Given the pair $(z_ 0,\mu)$ 
the \emph{defect of value} taken at $z_ 0$ by 
pluri-subharmonic functions $u(z)$ of class $C^2$
is expressed by the difference
\[ 
\text{def}(u)=\int_{\partial\Omega}\, u(z)\cdot d\mu(z)- u( z_0)
\]
In dimension one
this  defect is  an integral of $\Delta(u)$ times 
the positive density in $\Omega$ given by   Green's function of
the domain. If $n\geq 2$ the result by Deval and Sibony
goes as follows:

\medskip

\noindent
{\bf{Theorem.}}
\emph{To each pair $(z_0,\mu)$ 
there exists
 a current
$T_\Omega$ of bi-degree $(n- 1,n-1)$ 
such that}
\[ 
\text{def}(u)=\int_\Omega\, T_\Omega\wedge \bar\partial\partial(u)\tag{*}
\] 
\emph{hold for every pluri-subharmonic function
$u$ of class $C^2$ where  
the right hand side  in (*) is  the integral of the volume form
$T_\Omega\wedge \bar\partial\partial(u)$.}

\bigskip


\noindent
\emph {Currents in ${\bf{C}}^n$.}
This is  a major issue during the second half  of the course.
A typical result goes as follows:
Let $V$ be a complex analytic set in
a complex manifold $X$ with positive
codimesion and $T$ a current of
bi-degree $(p,p)$ defined in
$X\setminus V$ where $1\leq p\leq \dim(X)=-1$.
If  $T$ in addition is positive. closed and has locally finite
Hausdorff mass of degree $2p$
in neighborhoods of $V$, it follows that
$T$  extends to a positive and closed current in $X$.
During the lectures    basic facts about analytic sets in 
complex manifolds of dimension 
$\geq 2$ with emphasis upon their  metric properties 
will be recalled, including
special results 
for algebraic sets.
As an example I will
expose  a  beautiful  theorem  due to Christer Lech
which asserts that if $V$ is an algebraic set in
${\bf{C}}^n$ for some $n\geq 2$, then
there exists a polynomial $P(z)$ which is 
zero on $V$ and a constant $C$ such that
\[
\text{dist}(x,V)\leq C\cdot \text{dist}(x,P^{-1}(0)
\quad\colon x\in {\bf{R}}^n
\]
where one measures ordinary euclidian distances and
${\bf{R}}^n$ is the set of points in
${\bf{C}}^n$ with real coordinates.
The lectures  will also cover
results from work by
Y.T. Siu
which 
lead to the existence of
Lelong numbers attached to plurisubharmonic functions.
Siu's theorem is exposed in Chapter 2 from
Hörmander's text-book in several complex variables 
and  gives  an
example of a proposed  "examination lecture".



































\newpage


\centerline {\bf{Riemann surfaces}}.
\medskip

\noindent
The first three  lectures  are devoted to the study of
both open and closed Riemann surfaces, 
i.e connected 1-dimensional complex manifolds.
In contrast to later lectures
this  subject is more oriented towards algebra and
the requested complex analysis is "soft".
The esssential  result is the 
Pompieu formula 
which gives solutions to inhomogeneous $\bar\partial$-equations
together with  two 
residue formulas which are as follows.
Let  $z=x+iy$ be the complex coordinate
in ${\bf{C}}$, and $k$ a positive integer.
Then the  following two limit formulas hold when
$g(z)$ is a test-function of the real  variables $(x,y)$:
\[
\lim_{\epsilon\to 0}\int_{|z|=\epsilon}\, \frac{g(z)}{z^k}\, d\bar z=0\tag{i}
\]
\[
\lim_{\epsilon\to 0}\int_{|z|=\epsilon}\, \frac{g(z)}{z^k}\, dz=
2\pi i\cdot (-1)^{k-1}\cdot \frac{\partial^{k-1}(g)(0)}{(k-1)!}\tag{ii}
\]
where 
\[
\partial(g)= \frac{1}{2}(\frac{\partial g}{\partial x}-
i\cdot \frac{\partial g}{\partial y})
\]
and if $k\geq 2$ we have taken the
$\partial$-derivative of order $k-1$ in (ii).
A proof of  (i-ii) occurs 
in a separate appendix A:xx.
Calculus 
based upon currents 
plays a crucial  role 
during the study of Riemann surfaces.
In appendix § Xx we expose the theory about doubly periodic meromorphic functions
which can be seen as a modest introduction to the general theory. Here
no manifolds appear, i.e. everything relies upon 
analytic function theory. 
On the other hand one does not really grasp this special material until
general facts about Riemann surfaces have
been
developed.
\medskip

\noindent
{\bf{Example.}}
Denote by $\mathcal P$ the class of meromorphic functions
$f(z)$ in ${\bf{C}}$ which are doubly periodic in the sense that
\[
 f(z)= f(z+1)=f(z+i)
\]
Let $\mathcal G$ be the set of Gaussian integers, i.e.
complex numbers $a+ib$ where $a,b$ are integers,
A result due to Abel asserts that for 
every pair of complex numbers
$\{z_\nu=x_\nu+iy_\nu\}$  where
$0<x_\nu<1$ and $0<y_\nu<1$
both hold, there
exists $f\in\mathcal P$
with a double pole at $z=0$ and holomorphic outside
the Gaussian integers while $f$ has simple zeros of
$z_1$ and $z_2$ if and only if the sum
$z_1+z_2$ is a Gaussian integer.
Even though it is possible to write down an explicit series for the
requested meromorphic function when
$z_1+z_2\in\mathcal G$, the full contents  of Abel's result which
in addition asserts that this condition also is necessary, is
not fully understood until one has developed a calculus which involves
line integrals of holomorphic 1-forms.
Abel's theorem on compact Riemann surfaces
which expresses a necesssary and sufficient condition in order that
a divisor is principal is a veritable high-light in the whole theory and
we shall give a proof which foremost is based upon
the calculus with currents on complex manifolds.











\medskip


\centerline{\bf{Comments about Lecture 1-3.}}

\bigskip


\noindent
A gateway to understand the concept of Riemann surfaces
is Weierstrass' construction of
multi-valued analytic functions.
Let  $\Omega$ be
a connected open subset of
${\bf{C}}\setminus \{0,1\}$ and
$z_0$  a  point in
$\Omega$. 
Denote by $M_\Omega(z_ 0)$ the family 
of germs of analytic functions $f(z)$ at $z_ 0$
which
extend analytically  along every curve in $\Omega$ with
$z_ 0$ as initial point while its end-point in
$\Omega$ can be arbitrary.
If $f_0\in  M_\Omega(z_ 0)$ and $z\in\Omega$
we put
\[
\widehat{f(z)}=\{ T_\gamma(f)(z)\quad\colon
\gamma\in\mathcal C(z_0,z)\}
\]
Thus, one considers the values at $z$ attained by all
analytic continuations of the given germ $f_0$.
Now $M_\Omega(z_ 0)$
contains a subfamily
$M^*_\Omega(z_ 0)$ characterized by the property that 
\[
 \widehat{f(z_1)}\cap
 \widehat{f(z_2)}=\emptyset
 \]
for each pair of distinct points in $\Omega$.
\medskip

\noindent
{\bf{Theorem.}} \emph{There exists a unique
$f_0\in M^*_\Omega(z_ 0)$ whose 
complex derivative $f'_0(z_0)$ is real and positive and}
\[ 
\bigcup_{z\in\Omega} \widehat{f(z)}= D\tag{*}
\] 
\emph{where $D$ is the open  unit disc.}
\medskip

\noindent
{\bf{Remark.}}. A consequence  is that
the universal covering space of
$\Omega$ is biholomorphic with the open  unit disc. This is a special case
of the uniformisation  theorem
for open Riemann surfaces.
We remarr that this  theorem can be proved without the passage to manifolds, i.e. one employs
similar methods as 
for simply connected domains. 
Details are presented in
my notes on analytic function thery in a chapter
devoted to Riemann's mapping theorem.


 
\medskip

\noindent
{\bf{Currents and sheaves.}}
Some
relevant background material appears in § 0-4 below.
Let us remark that  
sheaf theory 
finds
excellent illustrations within  complex analysis.
The first relevant sheaf
was introduced by
Weiertrass, namely the total sheaf space
$\widehat{\mathcal O}$ whose points are pairs
$(p,f)$ where
$p\in {\bf{C}}$ and $f$
is a germ of an analytic function at $p$.
One has the projection $\pi(p,f)=p$ from
$\widehat{\mathcal O}$ onto ${\bf{C}}$ which is a local homemorphism
and equips  
$\widehat{\mathcal O}$
with a structure
as a complex manifold of dimension one.
If $\Omega$ is a conected
subset of
${\bf{C}}$
one has a 1-1 correspondence between
open and connected
subsets of
$\widehat{\mathcal O}$ 
whose $\pi$-image is $\Omega$ and the familly of multi-valued analytic functions in
$\Omega$.
So every connected component in
$\widehat{\mathcal O}$ is an  open  Riemann surface.













\medskip

\noindent
{\bf{Counting zeros of analytic functions.}}
Here is an example which illustrates how
one can use  measure theory to grasp results on manifolds.
Let $f$ be a holomorphic function on
a Riemann surface $X$ and assume it has a finite
number of zeros $p_1,\ldots,p_k$ with multiplicities
$e_1,\ldots,e_k$.
Stokes theorem entails that
\[
2\pi i\cdot \sum\, e_\nu g(p_\nu)=
\int_X\, \log |f|^2\cdot \bar\partial(\partial(g)\tag{*}
\] 
for every $g\in C_0^\infty(X)$.
This integral formula serves as a  substitute  for the  argument principle which
counts zeros of analytic functions in the complex plane.
Suppose in  addition that
there exists some $\delta>0$ such that
the set $\{|f|\leq\delta\}$ is a compact subset of $X$
and fix $g\in C_0^\infty$ so that $g=1$ on this compact set.
For each complex number $a$ with $|a|<\delta$
we  apply (*) to  $f-a$
and conclude that
\[
2\pi i\cdot \sum\, E(a) =
\int_X\, \log |f-a|^2\cdot \bar\partial(\partial(g)
\]
where $E(a)$ is the number of zeros of $f-a$ counted with multiplicity.
At the same time
Lebesgue theory shows that the right hand side is a continuous function of
$a$
and since $a\to E(a)$ is integer-valued 
this $E$-function is constant while $|a|<\delta$.
This ressembles Rouche's theorem in the planar case and illustrates
the efficiency to employ currents.
So one major aim in the lectures is to
bring distribution theory together with complex analysis.


\bigskip


\centerline{\bf{Open Riemann surfsces.}}

\medskip

\noindent
A  result
due to 
Behnke and Stein 
asserts that 
if $X$ is   a non-compact Riemann surface 
then
every differential $(0,1)$-form
is $\bar\partial$-exact, i.e.
the inhomogeneous $\bar\partial$-equation
\[
\omega^{0,1}= \bar\partial(g)\tag{*}
\]
has a solution $g\in C^\infty(X)$ for every  globally defined and smooth
differential form $\omega$ of bi-degree $(0,1)$.
After this has been proved, we  show that
if $X$ is an open Riemann surface where
every globally defined holomorphic 1-form is
$\partial$-exact, then $X$ is biholomorphic with the open unit disc or the complex plane.
This is  the uniformisation theorem for open Riemann surfaces.

\medskip

\noindent
\emph{About the proof of (*)}.
To begin with,   Pompieu's formula 
in analytic function theory   implies that
(*) holds for 
planar domains where
open subsets of
${\bf{C}}$ are regarded as  open Riemann surfaces.
Starting from this,  the next step is to prove
that (*) also holds for relatively compact open subsets of an open
Riemann surfaces and finally an extended version of Runge's theorem
gives the Behnke-Stein  result above.
\medskip

\noindent
The  steps during the whole proof are instructive
and teaches the  lesson  that systematic use of currents is very useful.
Concerning the uniformisation theorem it is deduced via (*) and
solutions to the Dirichlet problems where the
existence of solutions is proved just as for planar
domains using Perron's method.







\medskip

\noindent
{\bf{Subharmonic functions.}}
A crucial fact is  that
the class of subharmonic functions on a Riemann surface $X$
is defined.
More precisely, if $u$ is a real-valud function of class 
$C^2$ on
$X$ there exists the
2-current $\bar\partial\partial(u)$
which by defintion is a linear functional on the Frechet space
of  $C^\infty$-functions $g$ on $X$ defined by
\[ 
g\mapsto \int_X\, g\cdot \bar\partial\partial(u)\tag{i}
\]
In a chart $\Delta$ with local coordinate
$z=x+iy$
we have
\[
\bar\partial\partial(u)=\frac{1}{2}\cdot \bar\partial((u'_x-iu'_y)\cdot dz)
=\frac{1}{4}\cdot (u''_{xx}+ u''_{yy})\cdot d\bar z\,\wedge dz
\]
Recall that
\[
d\bar z\,\wedge dz=2i\cdot dx\wedge dy
\]
So if $g$ is a test-function with compact support in the chart
the right hand side in (i) becomes
\[
\frac{i}{2}\int_\Delta\, g\cdot \Delta(u)\, dxdy
\]
where
$\Delta(u)=u''_{xx}+ u''_{yy}$. The planar condition for
$u$ to be subharmonic is that
$\Delta(u)$ is a non-negative function.
This leads to

\medskip

\noindent
{\bf{Definition.}}
\emph{A real-valued $C^2$-function $u$ on $X$ is subharmonic if}
\[
\mathfrak{Im}\,  \int_X\, g\cdot \bar\partial\partial(u)\geq 0
\] 
\emph{for every real-valued and non-negative $g$-function.}
\medskip

\noindent
{\bf{Remark.}}
A two-fold application of  Stokes Theorem gives
\[
\int_X\, g\cdot \bar\partial\partial(u)=
-\int_X\, \bar\partial(g)\,\wedge \partial(u)=
\int_X\, \partial(u)\,\wedge \bar\partial(g)=
\]
\[
-\int_X\, u\cdot \partial\bar\partial(g)=
\int_X\, u\cdot \bar\partial\partial(g)
\]
This leads to an extension of the class of subharmonic function just as in
the planar  case.
More precisely, a real-valued and locally integrable function $u$
is subharmonic if
\[
 \mathfrak{Im}\, \int_X\, u\cdot \bar\partial\partial(g)\geq 0\tag{*}
\]
for every non-negative and real-valued test-function $g$.




\newpage







\centerline {\bf{Compact Riemann surfaces}}.
\medskip


\noindent
If $X$ is a compact Riemann surface it is not difficult to show
that
\[
\frac{\mathcal E^{0,1}(X)}{\bar\partial(\mathcal E(X))}\tag{i}
\]
is a finite dimensional vector space
whose  dual space consists of globally
defined holomorphic 1-form, i.e. the space
$\Omega(X)$.
Set
\[
k(X)= \text{dim}_{\bf{C}}\,\Omega(X)\tag{ii}
\]
A fundamental result for compact Riemann surfaces asserts that
$k(X)$ is equal to the topological genus number
$g$, i.e.
when $X$ is identified with a sphere where
a finite number of handles is attached, then
this number
is equal to $k(X)$.
This result goes back to original work 
by Riemann.
The proof which employs 
currents 
has the merit that no specific triangulations or constructions of
a canonical basis for the homology of $X$ are neeeded. Instead 
one disposes of 
a "two-line proof" using
general facts due to Leray and Dolbeault which 
also are used
to study complex manifolds in dimension $\geq 2$.
So in the lectures we  prove  the equality $k(X)=g$
using
the Dolbeault-Leray methods.
Let us now describe two major results about compact Riemann surfaces
which go back to work by Abel and Weierstrass.

\medskip


\centerline {\emph{Abel's theorem.}}
\medskip

\noindent
On a compact Riemann surface
$X$ the zeros and  the poles of a meromorphic function
$f$ cannot be assigned in an arbitrary fashion.
First $f$ can be   identified with a holomorphic map from
$X$ onto ${\bf{P}}^1$. This entails 
that
the number of zeros counted with multiplicities  is equal to the number
of poles counted with their orders.
Conversely, let $\{q_1,\ldots,q_s\}$ and
$\{p_1,\ldots p_r\}$ be two finite and disjoint sets in $X$.
To the $q$-points we assign positive integers $m_1,\ldots,m_s$ and 
to the $p$-points negative integers $-k_1,\ldots,-k_r$ where
\[
m_1+\ldots+m_s= k_1+\ldots+ k_r
\]
One seeks conditions in order that
there exists
$f\in\mathfrak{M}(X)$
whose associated principal divisor is
given by the pair above.
To analyze this we introduce the family
$\mathcal C$ of all currents $\gamma\in \mathfrak{c}^{0,1}$
with the property that
\[
\gamma(\partial(g))=2\pi i\cdot \bigl[
\sum m_\nu g(q_\nu)-
\sum k_\nu g(p_\nu)\,\bigr]\quad\colon g\in C^\infty(X)\tag{*}
\]
With these notations one has:
\medskip

\noindent
{\bf{Theorem.}}
\emph{A pair $\{q_\nu;m_\nu\}$ and $\{p_\nu;-k_\nu\}$
as above is a principal divisor
of a meromorphic function $f$
if and only if there exists some
$\gamma\in\mathcal C$ such that}
\[
\gamma(\omega)=0\quad \colon \, \omega\in
\Omega(X)\tag{*}
\]
\medskip

\noindent
{\bf{Remark.}}
In one direction the result follows from
residue calculus  For suppose that
$f\in\mathfrak{M}(X)$ is given.
Now $\log\, |f|^2$ is a locally 
integrable function on
$X$ and therefore defines a distribution. Hence there exists
the current
\[
\gamma=\bar\partial(\log\, |f|^2)
\]
If $g\in C^\infty(X)$ it follows that
\[
\gamma(\partial g)=-\int_X\, \log|f|^2\cdot
\bar\partial\partial(g)
\]
and residue calculus shows that
the current $\gamma$ belongs to $\mathcal C$
associated to the principal divisor of $f$.
At the same time
$\gamma(\omega)=0$
hold for each
$\Omega\in\Omega(X)$
since these holomorphic forms are $\bar\partial$-closed.
The non-trivial part  is therefore the converse,
i.e. if
$\mathcal C$ contains some
$\gamma$ such that
the vanishing (*) holds in
the theorem above,  then
the divisor  expressed as
\[
\sum\, m_\nu\cdot \delta(q_\nu)-\sum\, k_\nu\cdot \delta(p_\nu)
\]
is the principal divisor of a meromorphic function.

\bigskip


\centerline {\emph{Weierstrass points.}}
\bigskip

\noindent
Let $X$ be a compact Riemann surface and 
consider a point $p\in X$.
Now one seeks meromorphic functions
$f$ on $X$ which are holomorphic in
$X\setminus\{p\}$.
As we shall  see later on there exists such 
$f$ if we allow a sufficiently high order
of the pole at $p$. To analyze the polar part at $p$
of such meromorphic functions we choose a chart
$\Delta$ around $p$
with
a local coordinate $z$ where $p$ correspoinds to $z=0$ in the $z$-disc.
For small $\epsilon>0$
we get the open complement
\[ 
X_\epsilon= X\setminus\{|z|\geq \epsilon\}
\]
If $\omega\in \Omega(X)$
then Stokes Theorem  applied to the open domain 
$X_\epsilon$ gives
\[
\int_{|z|=\epsilon}\, f\cdot \omega=0\tag{1}
\]
In the chart we can write
\[
f(z)=f_*(z)+ c_1 z^{-1}+\ldots+c_kz^{-k}\tag{2}
\] 
where $f_*$ is holomorphic in
$\Delta$ and $\{c_\nu\}$ are complex numbers
where $c_k\neq 0$ and $k$ is the order of the ple at $p$.
At the same time one has a  series expansion
\[
\omega|\Delta= \sum_{\nu=0}^\infty \, a_\nu(\omega)\cdot z^\nu\cdot dz\tag{3}
\]
By residue calculus (1) implies that 
\[
\sum_{\nu=1}^{\nu=k}\, a_{\nu-1}(\omega)\cdot c_\nu=0\tag{*}
\]
In § xx we prove the following converse:

\medskip

\noindent
{\bf{Theorem.}}
\emph{Let $c_1,\ldots,c_k$ be  complex numbers
such that (*) holds for every $\omega\in \Omega(X)$.
Then there exists
$f\in\mathfrak{M}(X)$
which is holomorphic in
$X\setminus \{p\}$
and its negative Laurent series in (2) is given by
the $c$-sequence.}
\medskip

\noindent
{\bf{Conclusion.}}
Suppose that the genus number
$g$ of $X$ is $\geq 2$ and
$\omega_1,\ldots,\omega_g$ is a basis in
the complex vector space
$\Omega(X)$.
This  yield a $g\times g$-matrix
$W_p$ with elements
\[
\xi_{j,\nu}= 
a_{j-1}(\omega_\nu)\colon 1\leq j,\nu\leq g
\]
If $\det(W_p)=0$ we can solve the homogenous system of linear equations
in (*) and together with the theorem it follows that
there exists a meromorphic function $f$
whose negative Laurent series at $p$ is of the form
$c_1z^{-1}+\ldots +c_kz^{-k}$ for some
$k\leq g$ which means that the order of the pole at
$p$ is at most $g$.
To analyze this more closely  we shall construct 
determinant functions in charts.




\medskip

\noindent
{\bf {The divisor $\mathfrak{w}$}}.
Let $\Delta$ be a chart in $X$ with local coordinate
$z$.
For each $1\leq \nu\leq g$ we can write
\[
\omega_\nu|\Delta=h_\nu(z)\cdot dz
\quad\colon h_\nu\in\mathcal O(\Delta)
\]
In the chart we also have the holomorphic
differential operator
$\partial_z$ and get new holomorphic functions
\[
\rho_{j,\nu}(z)=\frac{1}{(j-1)\, !}\cdot
\partial_z^{j-1}(h_\nu)\quad \colon  1\leq j,\nu\leq g
\]
where we have put $0 \, !=1$.
Since $h_1,\ldots ,h_g$ are ${\bf{C}}$-linearly independent,
the holomorphic function
\[ 
\mathcal W(z)= \det(\{\rho_{j,\nu}(z)\})
\] 
is not identically zero in
$\Delta$.
We refer to $\mathcal W(z)$ as Weierstrass determinant function in
the  chart.
\medskip

\noindent
Next, let  $\zeta$ be a
local coordinate
in another  chart $\Delta^*$ where 
 $\Delta^*\,\cap \,\Delta\neq \emptyset$.
Now
\[ 
d\zeta= \frac{d\zeta}{dz}\cdot dz
\]
where
$\frac{d\zeta}{dz}$ is holomorphic and zero-free in
$\Delta^*\,\cap \,\Delta$.
In $\Delta^*$ we have the holomorphic
determinant function
$\mathcal W(\zeta)$ and matrix calculus gives
\[
\mathcal W(\zeta)=(\frac{d\zeta}{dz})^{g(g+1)/2}\cdot \mathcal W(z)\tag{i}
\]
\medskip

\noindent
The transition formula (i)  implies that
the zeros counted with multiplicities
of the locally defined Weierstrass determinants are
intrinsic, i.e. we obtain  a non-negative divisor
denoted by $\mathfrak{w}$ which is 
called the  Weierstrass divisor  on $X$.
Its degree is the sum of zeros counted
with multiplicities and  denoted
by
$\text{deg}(\mathfrak{w})$.
The support, i.e. points where
Weierstrass determinants are zero is the set of Weierstrass points.
The question arises if this set is non-empty and
if it holds we would also like to determine the number
of points.
Details are given in § xx after we have established 
the Riemann-Roch theorem in § x and a conclusive fact
which goes back to work by Weierstrass asserts the following:
\medskip

\noindent
{\bf{Theorem.}} \emph{For every compact Riemann surface
$X$ with genus number $g\geq 2$
one has the equation}
\[
\text{deg}(\mathfrak{w})=g(g+1)(g-1)
\]
In particular the support is non-empty if
$g\geq 2$
which gives
at least one
point $p\in X$ and $f\in\mathfrak{M}(X)$
with a pole of  order $\leq g$ at $p$ and otherwise it is holomorphic.
Moreover, $f$
yields a map from $X$ onto ${\bf{P}}^1$ which is generically
$k$ sheeted for some $k\leq g$.



\newpage


\centerline {\bf{Algebraic function fields}}
\bigskip

\noindent
A result due to Weyl
shows
that every compact Riemann surface
$X$ is algebraic, i.e. equal to
the family of valuation rings of an algebraic function field  $K$ in one
variable, which means that 
$K$ is a finitely generated field extension of
${\bf{C}}$ whose degree of trancendency is one.
Riemann 
started with
$K$ and  constructed 
$X$ so that
$K=\mathfrak{M}(X)$
where
$\mathfrak{M}(X)$ is the field of meromorphic functions on
$X$.
The construction  of local charts in $X$
relies upon a result due to Puiseux from 1854  which goes as follows:
Let $\Delta$ be an open disc centered at
$\{z=0\}$ and consider a  $y$-polynomial
\[ 
\phi(z,y)= y^m+q_{m-1}(z)y^{m-1}+\ldots +q_1(z)y+q_0(z)\tag{1}
\]
where $\{q_\nu(z)\}$
are holomorphic in an open
disc $\Delta$ of some radius $r$ centered at the origin
and 
$q_\nu(0)=0$ for every $\nu$.
Assume in addition that
$\phi$ is irreducible
in the polynomial ring
$\mathcal O(\Delta)[y]$.
Then there exists a holomorphic function
$A(\zeta)$ in a disc
$D^*=\{|\zeta|<r^{1/m}\}$
such that
\[
\phi(\zeta^m,A(\zeta))=0
\quad\colon \zeta\in D^*
\]
We  give the proof in the lectures
and 
explain how it is used to contruct local coordinates
on
the Riemann surface attached to a given algebraic function field.
More precisely, one starts wtih an
irreducible polynomial $P(x,y)$
and in ${\bf{C}}^2$ we get the affine algebraic curve
$S=\{P=0\}$.
Singukar  points on $S$ occur when
the gradient
vector $(P'_x,P'_y)=(0,0)$
and then
one employs the local Puiseux condtruction to
obtain local analytic coordinates on the associated Riemann surface
$X$.
An example is
the cusp curve
$\{y^2=x^3\}$, i.e $P(x,y)= y^2-x^3$.
Here $t\mapsto (t^2,t^3)$ yields a bijective map from
the complex $t$-plane to $S$. One refers to $S$ as a monomial curve
and $t$ serves as a gobal analytic coordinate
on
$S$.
In general the construction of local coordinastes on $X$ is a 
bit more involved, especially when
one encounters singular points on $S$ where
the
germ of $P$ is not irreducible. An example is the curve
defined by the equation
\[ 
y^8-(y^2-x^3)y^3-x^4)=0
\]
It is singular at the origin and here
one must emplly two different Puiseux charts
around
the origin which entails that
the map $X\to S$ no longer is bijective. 







\bigskip


\centerline {\bf{§ 0 Intersection numbers.}}
\medskip

\noindent
Let
$P(x,y)$ and $Q(x,y)$ be a distinct pair of irreducible polynomials in
${\bf{C}}[x,y]$. The common zero set  $\{P=Q=0\}$
in ${\bf{C}}^2$ is  finite  and one seeks  the number of
intersection points counted with multiplicities which gives
an integer
$\mathfrak{i}(P,Q)$ called the intersection number.
Under the hypothesis that
\[
\lim_{|x|+|y|\to +\infty}\,|P(x,y)|+|Q(x,y]|=+\infty\tag{i}
\]
one obtains
$\mathfrak{i}(P,Q)$ in a "robust manner".
To illustrate
the computations  we suppose that
\[
P(x,y)= \prod_{\nu=1}^{\nu=N}\, (y-\alpha_\nu x)+ P_*(x,y)
\quad \colon \text{deg}(P_*)\leq N-1\tag{ii}
\]
where $\{\alpha_1,\ldots,\alpha_N\}$ are distinct complex numbers.
Let $X$ be the compact Riemann surface attached to $\{P=0\}$.
We shall learn that (ii) entails that if
$x$ is considered as a meromorphic function on
$X$, then it has $N$ simple poles
which appear after we have taken the projective closure of the
affine curve
$\{P=0\}$ in
${\bf{C}}^2$. More precisely, in the coordinates
of
${\bf{P}}^2$ these simple poles appear at
the points $\{p_\nu=(1,\alpha_\nu,0)\}$.
Next, the  polynomial $Q(x,y)$ is identified with
a
meromorphic function on $X$
and we shall  learn that
$\mathfrak{i}(P,Q)$
is equal to the number of zeros of $Q$
in $X$  counted with
multiplicities.
Moreover, this integer  is equal to the number of poles
counted with their orders which often
is easier to
find.
Suppose for example that
\[
Q(x,y)= \prod_{j=1}^{j=M}\, (y-\beta_j x)+ Q_*(x,y)
\quad \colon \text{deg}(Q_*)\leq M-1\tag{ii}
\]
for some integer $M\geq 2$
where $\beta_1,\ldots,\beta_M$ are distinct.
If $\alpha_\nu\neq \beta_j$ hold for all pairs, then
one easily verifies that
$Q$ has a pole of order $M$ at each point $p_\nu$ above.
This entials that the intersection number is $NM$.
If some equality occurs, say that
$\beta_1=\alpha_1$,
then the order of the pole of $Q$ at
$p_1$ is at most $M-1$.
In the case when
 the polynomial
 \[ 
 x\mapsto
 P_*(x,\alpha_1x)
\] 
has degree $N-1$
while $\text{deg}(Q_*)\leq M-2$, an
easy computation 
shows that
$Q$ has a pole of order $M-1$ at $p_1$
which entails  that the "generic intersection number"
$N\cdot M$ has decreased with one unit. 
One can pursue these calculations at "points at inifinity" to
recover
intersection numbers  in quite general situations.
\medskip

\noindent
Next,  Stokes Theorem implies  that
the intersectioin number is robust. When
(i) holds it turns out that
\[
\mathfrak{i}(P,Q)=
\mathfrak{i}(P-a,Q-b)
\] 
for every pair of complex numbers $a,b$.
Moreover, this common number can be computed via multi-residue calculus, i.e. 
\[
\mathfrak{i}(P,Q)=\lim_{(\epsilon,\delta)\to (0,0)}
\, \int_{\{|P|= \epsilon\,\cap
\, Q|= \delta\}}\, \frac{\partial P}{P}\wedge  \frac{\partial Q}{Q}
\]
\medskip



\centerline {\bf{0.1 The curve $y^2=q(x)$.}}
\medskip


\noindent
Let $q(x)$ be a polynomial of odd degree
$2k+1$ with simple zeros
$\alpha_1,\ldots,\alpha_{2k+1}$.
Suppose also that $q(0)\neq 0$.
Now $P(x,y)= y^2-q(x)$ is an irreducible polynomial and let
$X$ be the attached Riemann surface.
The local Puiseux constructions show that
$x$ viewed as a meromorphic function on $X$ has  simple zeros
at the poinits $(0,\sqrt{q(0)})$ and
$(0,-\sqrt{q(0)})$. Hence
the meromorphic function $x$ on $X$ yields a holomorphic map from
$X$ onto ${\bf{P}}^ 1$
which is generically two-sheeted and $x$ has a double pole above
the point at infinity in
${\bf{P}}^ 1$ which  corresponds to the point $p_\infty=(1,0,0)$
in ${\bf{P}}^2\}$ where
$X$ is imbedded.
The meromorphic function $y$
has simple zeros at the points
$\{(\alpha_\nu,0,1)$
and a pole of order $k+1$ at $(1,0,0)$.
Now one  determines the topological genus number  $g$ of the compact manifold $X$.
It turns out that
\[ 
g=k\tag{*}
\]
To prove this by a "direct vizualisation" is not so easy.
Instead it can be established via
the equation (ii) above which means that we only have to
determine the dimension of the complex vector space 
$\Omega(X)$.
The crucial
point is that  the differential 1-form $dx$
has simple zeros at
the points $\{\alpha_\nu,0,1)\}$
which entails that
\[
\omega_0= \frac{dx}{y}
\]
is a holomorphic 1-form outside the point $p_\infty$. 
Now 
$x$ has a pole of order two at this point and hence
$dx$ has a pole of order
3 while
$\frac{1}{y}$ has a zero of multiplicitiy $2k+1\geq 3$.
It follows that
$\omega_0\in \Omega(X)$ and if $k\geq 2$ we see that 
\[
\omega_\nu = \frac{x^\nu\cdot dx}{y}\quad\colon 1\leq \nu\leq k-1
\]
also are holomorphic at $p_\infty$.
Another rather easy computation shows that
this  $k$-tuple $\{\omega_\nu\}$
is a basis for the complex vector space
$\Omega(X)$
and  (*) follows.

\medskip


\centerline{\bf{0.2 The curve $y^k=x^k+1$.}}
\medskip

\noindent
Let $k=2m+1$ be  odd  which gives
the irreducible polynomial
$P=y^k-x^k-1$ and  $X$ is the associated compact Riemann surface.
When $x$ is regarded as a meromorphic function on
$X$ it has simple poles at the points
$\{p_\nu=(1, e^{2\pi i\nu/ k},0)\, \colon 0\leq \nu\leq 2m\}$.
Next, one verifies by Puiseux that
$x$ has a zero of multiplicity
$k$
at the points $\{q_\nu=(e^{2\pi i\nu/ k},0,1)\}$
This entails that $dx$ vanishes up to order $k-1$ at these 
$k$ many points. Hence
the sheaf $\Omega_X$ of holomorphic
1-forms is equal to 
\[ 
\mathcal O_D\cdot dx
\] 
where
$\mathcal O_D$ is the sheaf of meromorphic functions on
$X$ whose sections have 
poles up to order $k-1$ at 
the points $\{q_\nu\}$
and zeros of multiplicity $\geq 2$ at $\{p_\nu\}$.
It means that the divisor $D$ has degree
\[
(k-1)k-2k= (k-3)k
\]
In § xx we show that the genus number $g$ of $X$ therefore is given by
the equation
\[
2g-2=(k-3)k\implies g=1+(2m+1)(m-1)
\]
With $k=3$ one has $g=1$ which means that
$X$ is a torus while the Riemann surface attached to
$y^5=x^5+1$ has genus two.
\medskip

\noindent
{\bf{Remark.}}
The results above illustrate the flavour in the  calculus on
compact Riemann surfaces where   results
related to sheaves such as $\Omega_X$ play
a central role.


\bigskip


\centerline {\bf{§ 1 Work by Niels Henrik Abel (1802-1829)}}


\bigskip

\noindent
In 1826
Abel presented the  article  
\emph{Remarques sur quelques propriétes génerales
d'une classe de fonctions trancendentes}.
In addition to a wealth of  results, this ingeniuos work
paved the way to
the contemporary theory about Riemann surfaces.
Before we give comments
about this
we
recall that Abel's
first major contribution to  mathematics was the proof that
the general equation of degree 5 cannot be solved by roots and radicals.
His  proof  from 1823 was  published in
the first volume of Crelle's journal. In addition to the actual result
this article includes   
foundational results about
algebraic field extensions.
Abel studied the symmetric group with
120 elements and constructed
an over-determined
system of linear 
equations 
which in general fails to have solutions
and explains why the general algebraic equation of degree 5
cannot be solved by roots and radicals. An example is 
\[
x^5+x+1=0
\]
For an exposition of Abel's  proof the reader can consult
the book \emph{The  Abel Legacy} 
published at  the innaguration of the  Abel Prize in Oslo.
Two years after Abel's decease in 1829, 
Galois discovered that
systematic  use of group theory
leads to criteria for
non-solvability.
Let us also remark that Abel's original proof has
the merit that today's use of computers can be applied
to analyze extensive  linear systems and in this way
one can decide when an specific algebraic equation has
solutions by roots and radicals in situations where the
its associated Galois group is not easy to handle.
\medskip


\noindent
{\bf{Abelian differentials and their integrals.}}
Now we discuss integrals on Riemann surfaces from
the cited article above.
We are given an affine curve
$\{F(x,y)=0\}$
and let $G(x,y)$ be a polynomial of some degree $n$
whose coefficients depend upon  indepenent parameters
$a_1,\ldots,a_s$.
To be specific
\[
G(x,y;a)=
\sum_{j,k}\, c_{j,k}(a_1,\ldots,a_s)\cdot x^jy^k
\]
where $\{c_{j,k}\}$ are polynomials in the $a$-variables for each
pair $(j,k)$ with $j+k\leq n$.
Suppose that $F$ has some degree $m$ wehich implies that the generic
intersection $\{F(x,y=G(x,y;a)=0\}$ consists of
$n\cdot m$ many simple points on
the Riemann surface attached to
$F$.
These points depend on
$a$
and consists of an unordered $mn$-tuple
$\{p_\nu(a)\}$ on $\{F=0\}$.
With a fixed point $p_*\in \{F=0\}$
we construct $nm$ many simple curves $\{\gamma_\nu\}$
where $\gamma_\nu$ has end-points at $p_*$ and $p_\nu(a)$.
If $\omega$ is a holomorphic 1-form on the Riemann surface of
$\{F=0\}$
we consider the
function
\[ 
J(a_1,\ldots,a_s)= \sum\int_{\gamma_\nu}\, \omega
\]
The crucial point is that the right hand side
is symmetric in the $a$-variables.
At the same time
we can consider small variations of the $a$-parameters and
find that
$J$ is locally holomorphic as a function of
the $a$-variables and since
the $J$-function is bounded while
$a_1,\ldots,a_s$ varies in
${\bf{C}}^s$
it must be reduced to a constant function.
This was Abel's first observation and
he also considered
more general cases where
one
integrates a meromorphic 1-form
$\omega$ while the $a$-parameters initially are chosen so that
the points of intersection above do not
meet poles of
$\omega$.
In this case the $J-$function need not be constant but takes a special form
form a general result by Abel which we describe below.
Let us first remark that
with the language used in "contempoary mathematics"
Abel's  result  asserts
that if $T\subset{\bf{C}}^n$
is a hypersurface with $k$ irreducible components defined by
irreducible polynomials $P_1,\dots,P_k$ in
${\bf{C}}[z_1,\dots,z_n]$,
then
the integral cohomology of order one over the  open
set
${\bf{C}}^N\setminus T$ is a free abelian group
generated by
the $k$-tuple of $\partial$-closed 1-forms
$\{\frac{\partial P_\nu}{P_\nu}\}$.
\medskip


\noindent
{\bf{The case $n=2$}}.
Here is a result whose proof is left as an exercise.
Consider a pair 
$R(x,y)$ and $Q(x,y)$  of
rational functions in two variables
such that
the differential 1-form
 $R dx+ Qdy$
 is closed  which means that
 \[
\frac{\partial R}{\partial y}=
 \frac{\partial Q}{\partial x}
\]
Since the polynomial ring ${\bf{C}}[x,y]$ 
is a unique factorisation domain
each rational funtion is the quotient of two polynomials with no common factor.
Suppose that the denominators of $R$ and $Q$ are non-zero at the origin in
${\bf{C}}^2$ and
set 
\[
\Phi(x,y) =
 \int_0^x\,R(\zeta,y)\,d\zeta+
 \int_0^y\,Q(x,\eta)\,d\eta
 \] 
 which is defined when $(x,y)$ stays close to the origin.
 \medskip
 
 
 \noindent
 {\bf{Theorem}}
\emph{There exists a unique pair $F,P$ where
$P$ is a polynomial with $P(0,0)=1$ and
$F$ a rational function such that the following hold
in a neighborhood of the origin in ${\bf{C}}^2$:}
\[
\Phi(x,y)= F(x,y)+\log P(x,y)
\]







\medskip

\noindent
Abel's original work  is presented in
a truly "modern way" and therefore  gives
an "up-to-date account of
the whole theory.
Of course the reader may consult other text-books
such as
\emph{Théorie functions algébriques et leurs intégrales} by P. Appel 
E. Goursat (2nd. edition 1929).
Here the reader will
find
several different proofs of Abel's results 
where algebraic, geometric or analytic
considerations are put forward,  together with many instructive examples.
\medskip


\noindent
{\bf{Work by Jacobi.}}
Abel's original work was  continued by Jacobi 
where one should mention  his famous article
\emph{Mémoire sur les fonctions quadruplement périodiques
de deux variables} (Creelle. J. vol 13).
Here the issue is to find inversion formulas for hyperelliptic integrals
which
in his work were restricted to
the case of genus 2. Jacobi's inversion formulas were later
extended to every genus number by Weierstrass 
in the articles \emph{Zur Theorie
der Abelschen Funktionen}
(Crelle vol. 47 and vol. 52]












\medskip



\centerline {\bf{Elliptic integrals.}}
\medskip


\noindent
Let us  discuss  a specific example in  Abel's  work.
Consider the equation 
\[ 
y^2=x(x-1)(x-\beta)\tag{*}
\] 
where the complex number
$\beta$ differs from 0 and 1.
This yields a Riemann surface
$X$
whose genus number  $g=1$, i.e.  an elliptic curve where
a global holomorphic 1-form is given
by
\[ 
\omega=\frac{dx}{y}
\]
Let $\gamma^*_1,\gamma^*_2$ be a canonical basis for the homology 
on $X$ which gives the two period numbers
\[
w_k=\int_{\gamma^*_k}\,\frac{dx}{y}
\]


\noindent
Next,
consider a  complex line $\ell$ in
the 2-dimensional complex $(x,y)$ space
defined by some equation
\[ 
\alpha x+\beta y+\gamma=0
\]
where   $\beta\neq 0$.
It is clear
that $X\cap \ell$ consists of
three points whose $x$-coordinates
are roots of the cubic equation
\[
x(x-1)(x-\beta)=\frac{1}{\beta^2}(\alpha x+\gamma)^2\tag{1}
\]
One can solve this equation by Cardano's formula. Abel invented
another point of view to describe the three intersection points.
Suppose the line is chosen so that (1) has
three simple roots $\{x_\nu\}$ which
determine
three points $p_1,p_2,p_3$ on $X$ where
\[ 
p_\nu=(x_\nu,-\frac{1}{\beta}(\alpha x_\nu+\gamma)
\]
Next, starting at the point 
$p_*=(0,0)$ on $X$ we
choose simple curves
$\{\gamma_\nu\}$ which join  $p_*$ with $\{p_\nu\}$
and integrate $\omega$ along each such $\gamma$-curve.
With these notations, Abel proved the following:

\medskip

\noindent
{\bf{Theorem.}}
\emph{There exists a constant $C$ which depends on $X$ only such that
for every line $\ell$ as above one has an equation}
\[
\sum_{\nu=1}^{\nu=3}\int_{\gamma_\nu}\, \frac{dx}{dy}= C+m_1\cdot w_1+m_2\cdot m_2
\tag{*}
\]
\emph{where $m_1,m_2$ is a pair of integers.}
\medskip

\noindent
{\bf{Remark.}}
One refers to this as an addition theorem and $C$ is called the Abel 
constant of the given curve, i.e.
here the teo period numbers $\omega_1,\omega_2$ together weith
$C$ are invariants of the given curve.
A notable fact is
that the equation (*) implies that
two intersection points determine the third.
Let us for example explain  why
$p_3$ is determined by $p_1$ and $p_2$.
Choose the line $\ell^*$ which 
passes through $p_1$ and $p_2$ and let $p_3^*$ be the third point
in $\ell^*\cap X$.
The equation applied to $\ell^*$ gives
a  pair of integers $m'_1,m'_2$
and an equation
\[
\sum_{\nu=1}^{\nu=2}\int_{\gamma_\nu}\, \frac{dx}{dy}
+\int_{\gamma}\,  \frac{dx}{dy}=C+m'_1+m'_2
\] 
where $\gamma$ is a curve from $(0,0)$ to $p^*_3$.
The composed curve
$\gamma_3^{-1}\circ \gamma$ joins $p_3$ with $p^*_3$
and subtracting the equations for the two lines
the constant $C$ disappears and we get
\[
\int_{p_3}^{p_3^*}\,  \frac{dx}{dy}=(m'_1-m_1)w_1+
(m'_2-m_2)w_2
\]
In § xx we explain that this
implies that $p_3^*=p_3$
which shows that two of the intersection points determine the third
via Abel's addition theorem.
Moreover, Abel proved 
that
the equation (*) is
not only is necessary, but  gives also a \emph{sufficient} condition in order
that three given points on the elliptic curve stay on a line.
This can
be
established by
algebraic computations  based upon Cardano's formula,
but Abel's method has a wider range since it
applies to  
intersection points of the 
elliptic curve above  with algebraic curves of arbitrary high degree.
For example, Abel's general theory
gives the following remarkable result:


\medskip


\noindent
{\bf{Abel's  addition theorem.}}
\emph{Let $s\geq 3$ and 
$p_1,\dots,p_{3s}$ are $3s$  distinct points on the elliptic curve from (*).
Then they all belong to an algebraic curve of degree
$s$ if and only if there exists a pair of integers $m_1,m_2$ such that}
\[
\sum_{\nu=1}^{\nu=3s}\int_{\gamma_\nu}\, \frac{dx}{dy}= 
C\cdot s+m_1\cdot w_1+m_2\cdot m_2
\tag{*}
\]
\emph{Where $\{\gamma_\nu\}$ are curves on $X$ 
which join $(0,0)$ to
$\{p_\nu\}$ and $C$ the constant of the preceeding theorem.}
\bigskip

\noindent
{\bf{A result about hyperelliptic curves.}}
Let $g\geq 1$ and consider a  Riemann surface $X$ defined by
\[
 y^2=p(x)
 \] 
where $p(x)$ is a monic polynomial of
degree $2g+2$
with simple zeros $\{c_\nu\}$.
As we shall explain later, 
$X$ has genus $g$ and 
a basis for $\Omega(X)$ consists of   the 1-forms
\[ 
\frac{x^kdx}{y}\quad\colon\quad 0\leq k\leq g-1
\]


\noindent
Let us now consider polynomials $Q(x)$ of the form
\[ 
Q(x)=x^{g+1}+ a_gx^g+\ldots+a_1x+a_0
\]
where $\{a_\nu\}$ is an arbitary $(g+1)$-tuple of complex numbers.
As will be explained in § x the number of intersection of the two curves
$\{Q=0\}$ and $\{u^2-p(x)=0\}$ when $x$ is finite 
consists of $2g+1$ points on $X$ counted with multiplicity.
Next, let $\{\xi_\nu=(x_\nu,y_\nu)\}$
be some  $g+1$-tuple of points on
$X$ where the $x$-coordinates are finite. Above 
we dispose $g+1$ many $a$-parameters. They   can be choosen so that
the intersection above contains $\xi_1,\ldots,\xi_{g+1}$
together with another $p$-tuple of points $\{\xi_{g+2},\ldots,\xi_{2g+1}\}$ on $X$.
For the generic choice of the
first $(g+1)$-tuple of $\xi$-points the
$a$-tuple is unique  and the last
$g$-tuple
depends only upon  the assigned  $(g+1)$-tuple. Set
\[ 
\eta_j= \xi^*_{g+1+j}\quad\colon\quad 1\leq j\leq g
\] 
where the *-sign means that when
$\xi_{g+1+j}= (x,u)$ in ${\bf{C}}^2$ then
we take the *-marked point changes $u$ to $-u$, i.e.
the $\eta-$-point becomes $(x,-u)$.
With these notations Abel proved the following:

\medskip

\noindent
{\bf{Theorem.}}
\emph{There exists a constant $C$ such that the following hold for
each $\omega\in\Omega(X)$ and every
tuple
$(\xi_1,\ldots,\xi_{g+1})$} 
\[
\sum_{k=1}^{k=g+1}\,\int _{\xi_*}^{\xi_\nu}\, 
\omega=C+ \sum_{j=1}^{j=g}\int_{\xi_*}^{\eta_j}\omega
\]
\medskip

\noindent
{\bf{Remark.}}
As explained above
the $\eta$-points are algebraic functions of
$\xi_1,\ldots,\xi_{g+1}$.
Since we have taken a sum of integrals in the right hand side,
it is determined by the unordered $g$-tuple of $\eta$-points on $X$.
The theorem  constitutes an addition formula since it asserts 
that the sum of line integrals over a family of $g+1$ curves is equal to
a sum over
 $g$ curves.
When $g=1$  
the theorem above corresponds to an equation which  was
established by Euler and presumably inspired Abel while he
developed the theory of general hyperelliptic equations.
The case $g=2$ can solved
rather explicitly and the  reader may consult
[Appel-Goursat: page 423-425] for detailed formulas 
expressing Abel's addition theorem  for hyper-elliptic curves.

\bigskip



\medskip


\centerline
{\bf{§ 2 Root functions and Cauchy transforms.}}
\medskip

\noindent
Tbe theory about Riemann surfaces is 
quite exploited.
However, many open questions 
related to roots of algebraic functions remain. Here is an example
which  leads to a proposed "research problem":
Let $P(y)= y^n+c_{n-1}y^{n-1}+\ldots+c_2y^2+y$
be a polynomial without constant term 
where $n\geq 3$.
Outside a finite set $\Sigma$
in the complex $z$-plane which contains $\{z=0\}$
the roots of the equation
\[ 
P(y)= \frac{1}{z}\tag{i}
\]
are simple. Let $\Gamma$ be a tree which contains
$\Sigma$. It means that
$\Gamma$ is a connected compact set given as the union of a finite number
of
real-analytic Jordan arcs and
the open complement $\Omega={\bf{P}}^1\setminus \Gamma$ is simply connected.
Now there exists a distinguished single-valued root
function $\alpha(z)$ 
to the equation (i) which is
holomorphic in
$\Omega$ and has a simple zero at the point at infinity, i.e.
\[
\alpha(z)\simeq \frac{1}{z}\tag{ii}
\]
when the absolute value $|z|$ is large.
Since $\Gamma$ has planar 
Lebegue measure zero we can identify $\alpha$ with a locally integrable function in
${\bf{C}}$ and take its $\bar\partial$-derivative. 
This gives
a complex-valued Riesz measure $\mu_\Gamma$ supported by
$\Gamma$ such that
\[
\alpha(z)= \int\, \frac{d\mu_\Gamma(\zeta)}{z-\zeta}
\]
where (ii)
entails that
$ \int\, d\mu_\Gamma (\zeta)=1$.
\medskip


\noindent
{\bf{Question.}}
Does there exists a unique tree $\Gamma$
such that $\mu_\Gamma$ is real-valued and non-negative.
Let us  remark that this is related to
asymptotic properties of roots of eigen-polynomials to ODE-equations
after one has taken the Bergquist-scaling into the account.
So numerical experiments from
the Phd-thesis by T. Bergquist 
indicate that the answer  is affirmative.
However, no proof - or an eventual counter example - is known.
The search for $\Gamma$ relies on a
variational problem, i.e.  
the issue is to find extremals where
free boundaries expressed by trees appear.
So this is an example of an open problem where the course does not
provide an answer but at least will
give background and   tools 
related to the problem.






\newpage


\centerline {\bf{§ 0. Sheaf theory.}}
\medskip

\noindent
We  restrict the study to sheaves
whose sections over open sets are complex vector spaces
and assume the reader is familiar with the axiomatic definition 
of sheaves which can be digested during a  short coffee-break.
However, the general notion of sheaves is extremely useful. 
Especially when it is combined with
constructions of  cohomology
which in the general context is due to Leray  from his
pioneering work 
during the years 1943-1949.
For the student in complex analysis basic familarity with
sheaves and constructions of various cohomology groups should
be considered as equally basic as integral formulas related
to Stokes theorem.
The generality in Leray's theory makes many
proofs trivial, while the applications often are
quite remarkable. We give examples of this in § 0.1.
In our applications we consider 
a paracompact manifold $X$ of some real dimension $n\geq 1$.
It means that every open covering has a locally finite subcovering,
and whenever $\{U_\alpha\}$ is a locally finite covering of
$X$ there exists a family
$\{\phi_\alpha\in C_0^\infty(U_\alpha)\}$ such that
$\sum\, \phi_\alpha=1$   on $X$.
Next, if $\mathcal F$ is a sheaf one constructs the Cech complex
\[
0\to C^0(\mathfrak{U},\mathcal F)\overset{\delta^0}\to
C^1(\mathfrak{U},\mathcal F)\overset{\delta^1}\to \ldots\tag{i}
\]
To each $p\geq 1 $ we set
\[
Z^p(\mathfrak{U},\mathcal F)=\text{Ker}(\delta^p)
\]
which are called Cech cocycles.
The cohomology groups
\[
H^p(\mathfrak {U},\mathcal F)=\frac{Z^p(\mathfrak{U},\mathcal F)}{
\delta^{p-1}(C^{p-1}(\mathfrak{U},\mathcal F))}
\]
are 
called  Cech cohomology groups with values in the sheaf
$\mathcal F$.
\medskip


\noindent
{\bf{Soft resolutions.}}
In  the applications during the lectures
these cohomology groups can
be obtained via soft resolutions. It means that
if $\mathcal E_X$ is the sheaf of complex-valued $C^\infty$-functions
then there exists a
sheaf resolution
\[
0\to \mathcal F\to \mathcal J^0\to \mathcal J^1\to \ldots\tag{ii}
\]
where $\{\mathcal J^\nu\}$ are sheaves of
$\mathcal E_X$-modules.
Using $C^\infty$-partitions
of the unity
one proves that
\[
H^p(X,\mathcal J)=0
\]
hold for every $p\geq 1$ and every
sheaf of $C^\infty$-modules.
Moreover, when we stsrt from an arbitrary sheaf
$\mathcal F$ and takes
a soft resolution (ii), then
one  verifies by  "diagram chasing" that
the cohomology of the complex
\[
0\to \mathcal J^0(X)\to \mathcal J^1(X)\to \ldots\tag{iii}
\]
depend on the sheaf $\mathcal F$ only, i.e. not upon the particular choice
of a resolution in (ii).
These intrinsically defined cohomology groups are denoted by
$\{H^p(X,\mathcal F)\,\colon\, p=0,1,\ldots \}$. More generally one can restrict
$\mathcal F$ to an open subset $Y$ and consider a soft resolution 
over $Y$ which  give  intrinsically defined
cohomology groups  $\{H^p(Y,\mathcal F)\}$.
\medskip


\noindent
{\bf{Exercise.}}
The restriction of a  sheaf $\mathcal J$ of $C^\infty$-modules
to an open subset of $Y$ of $X$ is again
a sheaf of $C^\infty$-modules.
Use this to explain how one gets natural complex linear maps
\[ 
H^p(X,\mathcal F)\to H^p(Y;\mathcal F)
\]
 for every $p\geq 1$.
Find also examples where such maps fail to be injective or surjective.






\medskip

\noindent
{\bf{0.0 An Edge Map}}.
Assume that $\mathcal F$ has a soft resolution 
and let $\mathfrak {U}=\{U_\alpha\}$ be a finite family of open sets.
Put
$Y= \cup\,  U_\alpha$.
Leray's  construction of spectral sequences
gives 
an exact sequence of complex vector spaces
\[
0\to H^1(\mathfrak{U},\mathcal F)\to H^1(Y,\mathcal F)\to \Gamma\to 0\tag{0.0.1}
\]
where $\Gamma$ is a direct sum of vector spaces
\[
\bigoplus_\alpha\, \text{Ker}\bigl[ H^1(U_\alpha,\mathcal F)
\to H^2(\mathfrak{U},\mathcal F)\bigr ]\tag{0.0.2}
\]
Hence one has
the isomorphism
\[
H^1(\mathfrak{U},\mathcal F)\simeq  H^1(Y,\mathcal F)\tag{0.0.3}
\] 
under the condition that
$H^1(U_\alpha,\mathcal F)=0$ for each $\alpha$.
One refers to this as Leray's acyclicity theorem.
\medskip


\centerline {\bf{0.1 Construction of meromorphic functions.}}
\medskip

\noindent
Let $X$ be a Riemann surface
and
consider the sheaf
$\mathcal O$ whose sections are holomorphic functions.
Suppose that an open subset
$Y$ of $X$ is such that
$H^1(Y,\mathcal O)$  is finite dimensional.
Fix a point $p\in Y$ and 
$\Delta$ is a chart centered at $p$ with
local coordinate $z$ and consider
the open covering $\mathfrak{U}= (\Delta, Y\setminus \{p\}$.
Here  $C^1(\mathfrak{U})$ is reduced to
$\mathcal O(\Delta\setminus \{p\})$
and since $\mathfrak{U}$ only consists of two sets
we have
$C^2(\mathfrak{U},\mathcal O)=0$.
It follows that
\[ 
H^1(\mathfrak{U},\mathcal O)=
\frac{\mathcal O((\Delta\setminus \{p\}}{\text{Im}(\delta^0)}
\]
It means that if $\phi$ is a holomorphic function in
the punctured disc
$\Delta\setminus \{p\}$ then its cohomology class is zero if and only if
there exists a pair $f\in\mathcal O(\Delta)$ and
$g\in\mathcal O(Y\setminus \{p\})$ such that
\[ 
\phi= g-f
\]
Let $M$ the dimension of the complex vector space
$H^1(Y,\mathcal O)$.
To each  $1\leq n\leq M+1$
we have the function 
$z^{-n}\in O(\Delta, Y\setminus \{p\})$.
By (0.0.1) the map  $H^1(\mathfrak{U},\mathcal O)\to H^1(Y,\mathcal O)$
is injective. It follows from the above
that
 there exists complex numbers
$c_1,\ldots,c_{N+1}$ which are not all identically zero such that
\[
c_1z^{-1}+\ldots+ c_{N+1}z^{-N-1}= g-f
\]
From this it is clear that $g$ extends to a meromorphic function in
$Y$ with a pole of order $N+1$ at most at $p$,  while
$g$ is holomorphic in
$Y\setminus\{p\}$.
This shows how Leray's injective map in 
(0.0.1) can be used to construct non-trivial meromorphic functions
provided 
one has a finite dimensional cohomology group as above.
\medskip

\noindent{\bf{0.1.1 Exercise.}}
Use the fact that if $Y\subset X$
is a relatively compact open set in $X$ then its compact 
closure can be covered by a finite
family of charts and apply the construction above to
show that
this gives the existence of a holomorphic function $f$ defined in some
open neighborhood of
$\overline{Y}$
which does not vanish identically in any non-empty open subset
of $Y$. 








\bigskip


\centerline {\bf{0.2 Surjective cohomology maps.}}
\medskip

\noindent
Now $X$ is an arbitrary paracompact manifold and
$\mathcal F$ is  a sheaf on $X$.
An open set $U$ in $X$ is  
said to be fully
$\mathcal F$-acyclic if
$H^p(U\, \cap \Omega,\mathcal F)=0$ for every
open set $\Omega$ in $X$ and each $p\geq 1$.
If $\mathfrak U=\{U_\alpha\}$ is a finite family of open and
fully  $\mathcal F$-acyclic sets
then Leray's acyclicity result  in (0.0.3) gives
\[
H^1(\cup \,U_\alpha,\mathcal F)=
H^1(\mathfrak{U},\mathcal F)
\]
More generally, if
$Y_0$ is an open subset of $Y=\cup\, U_\alpha$ we have
the open covering
$\mathfrak{U}_0= \{ Y_0\cap U_\alpha\}$ and the isomorphism
\[
H^1(Y_0,\mathcal F)=
H^1(\mathfrak{U}_0,\mathcal F)
\]

\noindent
{\bf{0.2.1. Theorem.}}
\emph{With  $\mathfrak U=\{U_\alpha\}$ and $\mathcal F$ as above
the restriction map}
\[
 \text{res}\colon\, H^1(Y,\mathcal F)\to H^1(Y_0,\mathcal F)
 \]
 \emph{is surjective for every open subset
 $Y_0$ of $Y$.}
\medskip

\noindent
\emph{Proof.}
Let $N$ be the number of sets in
$\mathfrak{U}$ which can be indexed with
open sets $U_1,\ldots,U_N$.
To each $1\leq k\leq N$ we put
\[ 
Y_k= Y_0\bigcup_{1\leq\nu\leq k}\, U_\nu
\]
It suffices to show that
\[
 \text{res}\colon\, H^1(Y_k,\mathcal F)\to H^1(Y_{k-1},\mathcal F)\tag{i}
\]
are surjective for each $1\leq k\leq N$.
Here $\mathfrak {U}^*=\{U_1\cap Y_{k-1},\ldots U_N\cap Y_{k-1},U_k)\}$
is an open covering of $Y_k$
while
$\mathfrak {U}_*=\{U_1\cap Y_{k-1},\ldots U_N\cap Y_{k-1}\}$
is an open covering of $Y_{k-1}$
and by Leray's theorem
\[
H^1(\mathfrak{U}^*,\mathcal F)=
H^1(Y_k,\mathcal F)\quad\colon\,
H^1(\mathfrak{U}_*,\mathcal F)=
H^1(Y_{k-1},\mathcal F)
\]
Notice that
\[
(U_\nu\cap Y_{k-1})\cap U_k=
(U_\nu\cap Y_{k-1})\cap 
(U_k\cap Y_{k-1})\quad\colon 1\leq \nu\leq N
\]
This entails that
\[
C^1(\mathfrak{U}^*,\mathcal F)=
C^1(\mathfrak{U}_*,\mathcal F)
\]
from  which the surjectivity in (i) is obvious.
\bigskip


\centerline{\bf{Applications to Riemann surfaces.}}
\bigskip



\noindent
Let $X$ be a Riemann surface.
Pompieu's theorem for planar domains implies that
every open set in $X$ which is biholomorphic to a  planar open
set is
fully $\mathcal O$-acylic.
This basic result is used to analyze
cohomology over
open subsets of $X$.
Let
$Y\subset X$ be  a relatively compact open subset and consider in addition
a relatively compact subset $Y_0$ of $Y$.
By Heine-Borel's Lemma we can cover
the compact closure $\overline{Y}$ with a finite  family of open
charts
$\{\Delta_\alpha\}$, i.e. each $\Delta_\alpha$ is biholomorphic with
the open unit disc.
If $0<a<1$ is sufficiently close to one, 
the discs
$\{a\cdot \Delta_\alpha\}$ is a covering of
$Y_0$. Put
\[
U^*_\alpha= Y\cap \, \Delta_\alpha\, \colon\, U_\alpha= Y_0\cap \,a\cdot \Delta_\alpha
\]
It is clear that
$V_\alpha$ is a relatively compact subset of $U_\alpha$ for each
$\alpha$ and the reader can also check that
each non-empty intersection
$V_\alpha\,\cap V_\beta$ is
relatively compact in $U_\alpha\,\cap U_\beta$.
Montel's theorem entails that the restriction map
\[
\text{res}\colon 
Z^1(\mathfrak{U}^*,\mathcal O)\to 
Z^1(\mathfrak{U},\mathcal O)\tag{i}
\]
is a compact operator, where
we 
the Frechet toplogy on
$\mathcal O(\Omega)$ for each open set in $X$
equips the two Cech cocylce spaces above with
a Frechet space topology.
Recall from the above
that
every open set in $X$ which is biholomorphic to a planar open
set is
fully $\mathcal O$-acylic.
Theorem 0.2.1 and Leray's acyclicity theorem applied to $Y$ and $Y_0$
imply  that the map
\[
C^0(\mathfrak{U},\mathcal O)\oplus  
 Z^1(\mathfrak{U}^*,\mathcal O)\overset{\delta^0+\text{res}}\to \,\,
Z^1(\mathfrak{U},\mathcal O)\tag{ii}
\]
is surjective.
Now one applies the result in functional analysis from
the introduction and conclude that
the range of $\delta^0$ is finite dimensional which means that
\[
H^1(Y_0,\mathcal O)\simeq
\frac{Z^1(\mathfrak{U},\mathcal O)}{\delta^0(C^0(\mathfrak{U},\mathcal O))}\tag{iii}
\] 
is finite dimensional.
\medskip

\noindent
Starting with a relatively compact open set $Y$ in $X$ we can always
construct another relatively compact open set $Y^*$ which contains the compact closure
of $Y$ and hence
$H^1(Y,\mathcal O)$ is  finite dimensional.

\medskip




\noindent
{\bf{0.2.1 A vanishing result.}}
Let $\mathcal F$ be a  sheaf of $\mathcal O$-modules
with the property that
every open chart $\Delta$ in $X$ is fully $\mathcal F$-acyclic.
Let $Y\subset X $ be relatively compact, i.e. the closure is a compact subset of $X$
By (0.1.1) there  exists
a holomorphic function $f$ defined in a neighborhood of the compact closure
$\bar Y$ which is not constant on any
connected component of the open set $Y$.
We shall use this function to prove the following:
\medskip

\noindent
{\bf{0.2.2 Theorem.}}
\emph{If $Y_0\subset Y$ is  such that $H^1(Y_0,\mathcal F)$
is finite dimensional, then this cohomology group is zero.}

\medskip

\noindent
\emph {Proof.}
Suppose that $H^1(Y_0,\mathcal F)$
has some dimension $M$.  Theorem 0.2.1 give vectors
$\xi_1,\ldots,\xi_M$  in
$H^1(Y,\mathcal F)$ such that
$\{\text{res}(\xi_k)\}$
is a basis for $H^1(Y_0,\mathcal F)$.
Since $\mathcal F$ is a sheaf of $\mathcal O$-modules,
$H^1(Y,\mathcal F)$ is a module over the ring
$\mathcal O(Y)$ which gives
an $M\times M$-matrix $B=\{b_{jk}\}$ with complex elements
such that
\[
\text{res}(f\cdot \xi_k)= \sum_{j=1}^{j=M} \, b_{jk}\cdot
\text{res}( \xi_k)\tag{ii}
\]
Set
\[ 
F=\text{det}(f\cdot E_M-B)
\]
Next,   (ii) and the Cayley-Hamilton theorem in matrix calculus entail that
\[
\text{res}(F\cdot \xi_k)=0\quad\colon k=1,\ldots,M\tag{iii}
\]
Moreover,  $F$ is a holomorphic function of the form
\[ 
F=f^M+c_{M-1}f^ {M-1}+\ldots +c_1f+c_0
\]
and by  analyticity  the condition on $f$ implies that
$F$ is not identically zero on
any
connected component of $Y$.
Now $\overline{ Y}$ can be covered by a finite family 
$\{\Delta_\alpha\}$ of open charts.
It is clear that the condition on $F$
implies that there exists  a finite family 
such that if
$\mathfrak {U}=\{U_\alpha=\Delta_\alpha\, \cap Y\}$,
then the restriction of $F$ to each non-empty intersection
$U_\alpha\cap U_\beta$ is zero-free.
Now
the assumption on $\mathcal F$ and leray's acyclicity result gives
\[
H^1(Y,\mathcal F)=H^1(\mathfrak{U},\mathcal F)
\]
Consider a Cech cocycle 
\[
\xi=\{\xi_{\alpha\beta}\}\in Z^1(\mathfrak{U},\mathcal F)
\]
Since $F$ is zero-free on $U_\alpha\,\cap U_\beta$
and $\mathcal F(U_\alpha\,\cap U_\beta)$
is a module over $\mathcal O(U_\alpha\,\cap U_\beta)$, 
there exists the 1-cocycle
\[
\eta=\{F^{-1}\cdot \xi_{\alpha\beta}\}
\]
Now (iii) gives $\text{res}(F\cdot \eta)=0$
and at the same time
\[ 
\xi= F\cdot \eta
\]
Hence $\text{res}(\xi)=0$
and together with the surjectivity in (0.2.1) we get
Theorem 0.2.2.
\medskip

\noindent
{\bf{0.2.3 Remark.}}
When
$\mathcal F$ is the sheaf
$\mathcal O$ of holomorphic functions on a Riemann surface
we have seen that the finiteness assumption in Theorem 0.2.1 holds
and hence we get:
\medskip

\noindent
{\bf{0.2.4 Proposition.}} \emph{For every relatively compact open
set $Y$ in a Riemann surface it follows that
$H^1(Y,\mathcal O)=0$.}
\medskip

\noindent
Starting from this result we shall relax the condition that
$Y$ is relatively compact and establish the Behnke-Stein theorem in § xx.








\bigskip


\centerline{\bf{§ 1. Residue formulas.}}

\bigskip


\noindent
Let $k$ be a positive integer and
$g(z)$ is a $C^\infty$-function of $(x,y)$ defined in an
open neighborhood of the origin in
the complex $z$-plane.
To each $\epsilon>0$ we consider the line integral
\[
\int_{|z|=\epsilon}\, \frac{g(z)}{z^k}\, d\bar z\tag{i}
\]
In polar coordinates it takes the form
\[
i\cdot \epsilon^{-k+1}\cdot \int_0^{2\pi}\, g(\epsilon\cdot e^{i\theta})
e^{-i(k+1)\theta}\, d\theta
\]
Now $g$ has a Taylor expansion where
$(x,y)$-polynomials are expressed in $z$ and $\bar z$.
In particular we get
\[ 
g(z)=\sum_{j+m\leq k}\, c_{j,m}\cdot z^j\cdot \bar z^m+\rho(z)\tag{ii}
\]
where the absolute value $|\rho(z)|\leq C\cdot \epsilon^{k+1}$
for a constant $C$.
Now
\[
 \int_0^{2\pi}\, e^{i(j-m-k+1)\theta}\, d\theta=0
 \quad\colon j+m\leq k
 \]
From this the reader discovers that
 there exists a constant $C$ such that
 the absolute value of (i) is majorized by
 $C\cdot |z|^2$. in particular the limit is zero as
 $z\to 0$.
 \medskip
 
 \noindent
 {\bf{1.1 Exercise.}}
 Use (ii) and show that
 \[
 \lim_{z\to 0}, 
 \int_{|z|=\epsilon}\, \frac{g(z)}{z^k}\, d z= 2\pi i\cdot c_{k-1,0}
\]

 
 









\bigskip






\centerline {\bf{§ 2. Pompieu's formula.}}
\medskip

\noindent
Let $\Omega$ be a connectd open set
in ${\bf{C}}$ whose boundary
$\partial\Omega$ is a union of pairwise disjoint and 
differentiable closed Jordan
curves, and 
$f(z)$ is
a continuously differentable  function defined on the closure of $\Omega$.
With $z\in\Omega$
we put
\[ 
g(z)=\frac{1}{\pi}\cdot \iint _\Omega\, 
\frac{\frac{\partial f}{\partial \bar \zeta}(\zeta)}{\zeta-z}
\,d\xi d\eta-
\frac{1}{2\pi i}\cdot \int _{\partial \Omega}\, \frac{f(\zeta)\, d\zeta}{\zeta-z}\tag{i}
\]
With $d\zeta= d\xi+id\eta$ and
$d\bar \zeta= d\xi-id\eta$ one has
\[
d\xi d\eta=\frac{1}{2i}\cdot d\bar \zeta\wedge d\zeta\tag{ii}
\]
If $\epsilon>0$ is small we set
$\Omega_\epsilon=\Omega\setminus \{|\zeta-z|\leq \epsilon\}$.
Since the function $\zeta\mapsto \frac{1}{z-\zeta}$
is integrable over $\Omega$ one has
\[
\frac{1}{\pi}\cdot \iint _\Omega\, 
\frac{\frac{\partial f}{\partial \bar \zeta}(\zeta)}{\zeta-z}
\,d\xi d\eta=
\lim_{\epsilon\to 0}\,
\frac{1}{\pi}\cdot \iint _{\Omega_\epsilon}
\, \frac{\frac{\partial f}{\partial \bar \zeta}(\zeta)}{\zeta-z}
\,d\xi d\eta\tag{iii}
\]
When $\epsilon>0$ the equality (ii) identifies the right hand side in
(iii) with
\[
\frac{1}{2\pi i}\cdot \iint _{\Omega_\epsilon}
\, \frac{\frac{\partial f}{\partial \bar \zeta}(\zeta)}{\zeta-z}
\,d\bar\zeta\wedge d\zeta=
\frac{1}{2\pi i}\cdot \iint _{\Omega_\epsilon}
\bar\partial(\frac{f(\zeta)}{\zeta-z})\wedge d\zeta\tag{iv}
\]
Stokes Theorem identifies (iv) with
\[
\frac{1}{2\pi i}\cdot \int _{\partial \Omega}\, \frac{f(\zeta)\, d\zeta}{\zeta-z}-
\frac{1}{2\pi i}\cdot \int _{\{|\zeta-z|=\epsilon\}}
 \frac{f(\zeta)\, d\zeta}{\zeta-z}\tag{v}
 \]
 where the last line integral is taken in
 the positive sense and with the aid of a figure which keeps trace of orientations 
 the reader should 
 verify the  minus sign in (v).
 Next, one has the residue formula
 \[
 \lim_{\epsilon\to 0}\, 
\frac{1}{2\pi i}\cdot \int _{\{|\zeta-z|=\epsilon\}}
 \frac{f(\zeta)\, d\zeta}{z-\zeta}= f(z)\tag{vi}
 \]
 
\noindent
{\bf{2.1 Conclusion.}} With $f$ as  above one has the equation
\[ 
f(z)=\frac{1}{2\pi i}\cdot \int _{\partial \Omega}\, \frac{f(\zeta)\, d\zeta}{\zeta-z}-
\frac{1}{\pi}\cdot \iint _\Omega\, 
\frac{\frac{\partial f}{\partial \bar \zeta}(\zeta)}{\zeta-z}
\,d\xi d\eta\tag{*}
\]
In the  case when
$f$ is holomorphic in
$\Omega$ this recovers Cauchy's integral formula.
\medskip


\noindent
{\bf{2.2 An inhomogeneous equation.}}
Let $\phi$ be a continuous function with compact support in
$\Omega$ and put
\[
g(z)= \frac{1}{\pi}\cdot \iint _\Omega\, 
\frac{\phi(\zeta)}{z-\zeta}\, d\xi d\eta\tag{**}
\]
If $f$ is a test-function with compact support in
$\Omega$ we get
\[
\iint_\Omega\, g(z)\cdot \frac{\partial f}{\partial\bar z}(\zeta)\, dx dy
=\iint_\Omega\, \bigl[\frac{1}{\pi}\cdot \iint_\Omega\,
\frac{\frac{\partial f}{\partial\bar z}(\zeta)}{z-\zeta}\, dxdy\bigr]
\, \phi(\zeta)\, d\xi d\eta=-\iint_\Omega\, f(\zeta ) \cdot \phi(\zeta )\, d\xi d\eta
\]
The construction of distribution derivatives entails  that
\[
\frac{\partial g}{\partial \bar z}(z)=\phi(z)
\]
Hence the $g$-function in (**)  solves the inhomogenous $\bar\partial$-equation.


\medskip

\noindent
{\bf{Remark.}}
The equations above  were established  by Pompieu
around 1820.
Starting from (*) where the $\phi$-function has compact support one
can go further and the following resuklt is proved in
my notes in analytic function theory.
\medskip

\noindent
{\bf{2.3 Theorem.}}
\emph{For every open set $\Omega$ in ${\bf{C}}$ and each
$\phi\in C^0(\Omega)$ there exists a $C^1$-function $g$ in
$\Omega$ such that}
\[
\frac{\partial g}{\partial \bar z}(z)=\phi(z)
\]

\newpage

\centerline{\bf{§ 3. Analysis on compact Riemann surfaces.}}
\medskip


\noindent
A compact Riemann surface $X$ has an
underlying real-analytic structure which is   an oriented compact real manifold
of dimension two.
For a while we ignore
the complex analytic structure.
There exists the sheaf
$\mathcal E$ whose sections are complex-valued
$C^\infty$-functions and 
the sheaf $\mathcal E^1$ of differential 1-forms with
$C^\infty$-coefficients. For brevity we refer to smooth 1-forms.
Finally there is the sheaf $\mathcal E^2$ of smooth 2-forms.
Since $X$ is oriented and  compact, every  smooth 2-form
$\sigma$ can be integrated
over $X$ and we write
\[ 
\int_X\, \sigma
\] 
If $\alpha$ is a smooth 1-form its exterior differential $d\alpha$ belongs to
$\mathcal E^2(X)$ and Stokes Theorem gives
\[
\int_X d\alpha=0
\] 
It  means that the integral of an
exact 2-form over $X$ is zero.
A non-trivial fact is the converse
whose proof is given in § 3.10 below.

\medskip


\noindent
{\bf{3.0.Theorem.}} \emph{A smooth 2-form is exact 
if and only if its integral over $X$ is zero.}
\bigskip


\noindent
{\bf{3.1 Currents.}}
A current of degree zero is a continuous linear form on
the Frechet space $\mathcal E^2(X)$ and we
set
\[
\mathfrak{c}^0(X)=
\mathcal E^2(X)^*
\]
Let us remark that $\mathfrak{c}^0(X)$ corresponds to the space of 
distributions on $X$, i.e. 
\[
\mathfrak{c}^0(X)=\mathfrak{Db}(X)
\]


\noindent
The dual  $\mathcal E^1(X)^*$
is denoted by $\mathfrak{c}^1(X)$ 
and its  elements are
called 1-currents. Finally, the dual of $\mathcal E(X)$ is denoted by
$\mathfrak{c}^2(X)$ and its elements are called
2-currents.
\medskip

\noindent
{\bf{ Example.}}
A function $f\in \mathcal E(X)$   defines a zero-current
via the linear form
\[ 
\sigma\mapsto \int_X f\cdot \sigma
\quad\colon\quad \sigma\in \mathcal E ^2(X)
\]
In this way $\mathcal E(X)$ appears as a subspace of $\mathfrak{c}^0(X)$ and such currents 
are called smooth.
In the same way we get an inclusion $\mathcal E^1(X)\subset\mathfrak{c}^1(X)$
where $\phi\in\mathcal E^1(X)$ yields a continuous linear functional on
$\mathcal E^1(X)$ defined by
\[
w\mapsto \int_X \phi\wedge w
\quad\colon\quad w\in \mathcal E ^1(X)
\]
Exterior differential maps on smooth forms
 extend  to currents. If $w\in\mathcal E^1(X)$
is a smooth 1-current then
$dw$ is the 2-current defined by
\[
f\mapsto \int_X\ f\cdot dw\quad\colon\quad f\in \mathcal E (X)
\]
Stokes theorem gives:
\[
0=\int_X\, d(fw)=\int_X f\cdot dw+
\int_X\ df\wedge  w
\]
Since $df\wedge w=-w\wedge df$ we get
\[
\int_X\ f\cdot dw=\int_X\ w\wedge  df
\]

\medskip
\noindent
This leads to the construction of 
exterior differentials of 1-currents. Namely, if
$\gamma\in\mathfrak{c}^1(X)$
then the  2-current $d\gamma$ is 
defined by
\[
f\mapsto \gamma(df)\quad\colon\quad f\in \mathcal E (X)
\]
By the above 
it follows that
if $w\in \mathcal E^1(X)$ is regarded as a smooth
1-current then its current differential $dw$ is the smooth 2-current
expressed by the differential 2-form $dw$.
Thus, the exterior differentials on smooth forms extend to
currents and one has a complex
\[
0\to \mathfrak{c}^0(X)\overset{d}\to 
 \mathfrak{c}^1(X)\overset{d}\to  \mathfrak{c}^2(X)\to 0\tag{3.1.1}
\]

\medskip


\noindent
{\bf{3.1.2 Remark about Stokes theorem.}}
Let $\Omega$ be an open set in $X$.
The characteristic function $\chi_\Omega$ is a 0-current
and we get the 1-current $d\chi_\Omega$
which is supported by $\partial\Omega$.
In the favourable case when
$\partial\Omega$ is a piecewise differentiable curve
the current 
$d\chi_\Omega)$
 has order zero, i.e. in local charts it is expressed by
a Riesz measure given by a bounded functions times
a locally constructed arc-length measure of the boundary curve.
Recall also that the boundary curve is oriented by the rule of thumbs
 and therefore one can integrate differential 1-forms along
 $\partial\Omega$ in an intrinsic fashion without specifying
 local coordinates.
 
\medskip
 
 
 


\noindent
{\bf{3.2. $d$-closed zero currents.}}
A 
current $\gamma$ of order zero is $d$-closed if and only if
\[
d\gamma(w)= \gamma(dw)=0\quad\colon\quad w\in \mathcal E^1 (X)\tag{3.2.1}
\]
To grasp this condition we consider a chart $U$ in $X$ 
taken as an open disc in the  $(x,y)$-plane.
If $f(x,y)\in C_0^\infty(U)$
we have the 1-form $f\cdot dx$ and get $d(fdx)= f'_y\cdot dy\wedge dx$.
Hence
(2.i) means that
\[ 
\gamma(f'_y\cdot dy\wedge dx)= 0\quad\colon\quad f\in C_0^\infty(U)\tag{3.2.2}
\]
The restriction of $\gamma$ to $U$
 is a distribution in the sense of § X and
(i)
means that the distribution derivative $\frac{\partial\gamma}{\partial y}$
vanishes in $U$.
Similarly, if we start with a 1-form $gdx$ where $g\in C_0^\infty(U)$
we find that
$\frac{\partial\gamma}{\partial x}=0$
in $U$. It follows that the distribution $\gamma$ 
restricts to a constant density
function in $U$.
The conclusion is that the $d$-kernel on
$ \mathfrak{c}^0(X)$ is reduced to constant functions, i.e.
\[ 
\text{ker}_d( \mathfrak{c}^0(X))={\bf{C}}\tag{3.2.3}
\]
\medskip

\noindent
{\bf{3.3  Inverse and direct images under mappings.}}
Let $X,Y$ be a 
pair of oriented compact two-dimensional manifolds and $F\colon X\to Y$
a real-analytic map. Assume that $F$ is surjective, i.e.
$F(X)=Y$ and that the mapping is finite which means  that
there exists an integer $n$
such that the inverse fiber
$F^{-1}(\{y\}$ contains at most $n$ points in $X$ for 
every $y\in Y$. Now
we  construct inverse images of smooth forms on $Y$.
First, if $g\in \mathcal E(Y)$ the composed function $g\circ F$ belongs to $\mathcal E(X)$.
Next, let $w$ be a smooth 1-form on $Y$. Using local coordinates
one verifies that
there exists a pull-back denoted by $F^*(w)$ which yields a smooth
1-form on $X$.
More precisely, let $p\in X$ be a given point and
$U$ is some chart around $p$ while $V$ is a chart around
$F(p)$.
Let $(\xi,\eta)$ be local coordinates in the chart $V$ and
$(x,y)$ are local coordinates in $U$.
Then
\[ 
w|V= g\cdot d\xi+ h\cdot d\eta
\quad\colon\quad g,h\in \mathcal E (V)\tag{i}
\]
In $U$ we get the $C^\infty$-functions
$\xi\circ F$ and $\eta\circ F$
whose exterior differentials give smooth 1-forms in $U$
denoted by $F^*(\xi)$ and $F^*(d\eta)$.
Now
\[
F^*(w)=g\circ F\cdot F^*(d\xi)+ h\circ F\cdot F^*(d\eta)
\]
\medskip

\noindent
{\bf{3.3.1 Exercise.}} Verify that
the 1-form $F^*(w)$  does not depend upon the chosen local coordinates
in the two charts. Conclude that
if $w\in \mathcal E^1(Y)$ then there exists a smooth
1-form
$F^*(w)$ on $X$ obtained in local charts as above. Hence there exists a pull-back map:
\[ 
w\mapsto F^*(w)
\]
In the same way one constructs the pull-back of each smooth 2-form on $Y$.
A notable fact is that
these pull-back mappings commute with
exterior differentials.
One has for example
\[ 
d(F^*(w))= F^*(dw) \quad\colon\quad w\in \mathcal E^1 (Y)
\]


\noindent We leave out the detailed verifications which are exposed in text-books
devoted to differential geometry.

\bigskip

\noindent
{\bf{3.4. Direct images of currents.}}
The construction of inverse images of smooth forms
give by duality  $F_*$-mappings on currents.
More precisely, let $\gamma\in \mathfrak{c}^\nu(X)$ for some
$0\leq\nu\leq 2$.
The direct image current
$F_*(\gamma)$ is defined by
\[
F_*(\gamma)(w)=
\gamma(F^*(w))\quad\colon\quad w\in \mathcal E^\nu (Y)
\]
By this construction  the passage to direct images of currents 
commute with exterior differentials. For example, let
$\gamma$ be a 1-current on $X$. Then
\[
d_Y(F_*(\gamma))= F_*(d_X(\gamma))
\]
where we for convenience introduced a sub-index to indicate on which
manifold one has performed an exterior differential.
In particular $F_*$ sends $d$-closed currents on $X$ to $d$-closed currents on $Y$.
\medskip





\noindent
{\bf{3.5. Integration chains and 1-currents.}}
Let $c$ be an oriented $C ^1$-curve on $X$
which means that $c$ is defined via
a $C^1$-mapping $t\to x(t)$
from
a closed $t$-interval $[0,T]$ into $X$.
Each smooth 1-form
$\gamma$ in $X$ can  be integrated along $c$
and the map
\[
\gamma\mapsto \int_c\,\gamma
\] 
yields a 1-current
denoted by $\int_c$.
More generally we can take a finite sum of such integration currents, i.e.
every chain $c$ of class $C^1$
gives
a current
$\int_c$ which belongs to $\mathfrak{c}^1(X)$.
By definition the exterior differential $d\int_c$ is the 2-current defined by
\[
g\mapsto  \int_c\, dg\quad\colon\quad g\in \mathcal E (X)
\]
The resulting current is denoted by $\partial c$. In simplicial topology one
refers to $\partial c$ as the boundary of the 1-chain $c$.
Here it has been given an operative definition.
If $c$ is an elementary chain defined by a single 
oriented $C^1$-curve with end-points
$a$ and $b$, then
the 2-current
$\partial c$ is a  current
supported by the end-points $a$ and $b$.
In general $\partial c$ is a sum of Dirac measures assigned at a finite set of points, i.e.
\[
d\int_c= \sum\, k_\nu\cdot \delta(x_\nu)
\] 
where  $\{k_\nu\}$ are integers
and $\sum\, k_\nu=0$.
\medskip

\noindent
{\bf{3.6. Critical values of a map $F$.}}
Let $F\colon X\to Y$ be a surjective mapping with finite fibers.
One says that $F$ is smooth at a point $p\in X$
if the following hold when
a pair of local charts $U$ and $V$ have been chosen as in § XX:
The 1-forms $F^*(d\xi)$ and $F^*(d\eta)$ are non-zero and 
${\bf{R}}$-linearly independent.
Next, a point $q\in Y$
non-critical if $F$ is smooth at each $p\in F^{-1}(\{q\})$.
The complement is denoted by $\text{Crit}(F)$
and is called the set of the critical values.
A welknown fact - called Sard's Lemma - asserts that
the set of $F$-critical values is a (possibly empty) finite subset of $Y$.
Since $X$ and $Y$ both are connected
it follows that when $q\in Y\setminus \text{Crit}(F)$
then the number of points in
the inverse fiber
$F^{-1}(\{q\})$ does not depend upon $q$. This integer $n$ is called the degree of the 
mapping $F$ and  denoted by $\text{deg}(F)$.
Put $X_*= X\setminus F^{-1}(\text{Crit}(F)$. In topology one says that the
restricted mapping
\[ 
F\colon X_*\to Y\setminus \text{Crit}(F)
\]
is an unbranched covering map of degree $n$.
If $\Omega\subset Y\setminus \text{Crit}(F)$ is open and simply connected one proves that
the inverse image $F^{-1}(\Omega)$ consists of pairwise disjoint open subsets 
$U_1,\ldots,U_n$ and
$F\colon U_k\to \Omega$
is a diffeomorphism  for each $k$. One refers to
$\{U_k\}$ as the sheets above $\Omega$.
\bigskip

\noindent
{\bf{3.7. Direct images of integration currents.}}
Let $F$ be as above and consider a 1-current $\int_c$ on $X$ given by an
oriented 1-chain $c$.
Now there exists the direct image current $F_*(\int_c)$.
To describe this 1-current on $Y$
we proceed as follows.
To begin with $c$ is a sum of small 1-chains $\{c_k\}$ where
each $c_k$ is a single $C ^1$-curve
and we can also choose  $c_k$ so that
its parametrized curve
$t\to x(t)$  stays in a small
subset of $X$. So $a=x(0)$ and $b=x(T)$ are close to each other and
the whole curve $c_k$ stays inside a chart  $U$ in $X$ where
$a$ is the origin in $U$ and we may also assume that
$F(U)$ stays in a chart $V$ around $F(a)$.
\medskip

\noindent
Let $(\xi,\eta)$ be local coordinates in
$F(U)$.
If $g(\xi,\eta)\in C_0^\infty(F(U))$
we get the differential 1-form
$g\cdot d\xi$
whose  pull-back
can be integrated on the chain $c_k$.
This gives a linear functional
\[
 g\mapsto \int_{c_k}\,F^*(g\cdot \xi)
\]
A similar linear functional arises when
we instead use the 1-form $d\eta$.
\medskip

\noindent
{\bf{3.8 Exercise.}}
Conclude from the above that there exists the direct image current
$F_*(\int_{c_k})$
which has a compact support in
$F(U)$ and is given by
a 1-current of the form
\[ 
\mu_1\cdot d\xi+\mu_2\cdot d\eta
\]
where $\mu_1,\mu_2$ are two
Riesz measures with compact support in
$U$.
It means that the direct image current has order zero.
But unless $F\colon U\to F(U)$ is a diffeomorphism the direct image current
is in general not given by integration along a 1-chain.
Funally, by additivity one has
\[ 
F_*(\int_c)=\sum\, 
F_*(\int_{c_k})
\]
\bigskip


\noindent
{\bf{3.9. Further results.}}
Let $F\colon X\to Y$ be as above.
A special current on $X$ is the 2-current $\square_X$
 defined by
 \[ 
 \omega^2\mapsto \int_X\,\omega^2
 \]
i.e. one integrates 2-forms over $X$.
If $\phi$ is a bounded Borel function on $X$, or more generally
an $L^1$-function on $x$ in Lebegue's sense, then
there exists the 2-current defined by
\[ 
 \omega^2\mapsto \int_X\,\phi \cdot \omega^2
\]
It is denoted by $\phi \cdot \square_X$.
\bigskip


\noindent
{\bf{3.9.1 Exercise.}}
Let $F\colon X\to Y$ where
$F(X)=Y$ and $F$ is finite but may have some critical values.
Show that there exists a Borel function $\phi$ on $Y$ such that
\[
F_*(\square_X)= \phi\cdot \square_Y
\]
and  describe the $\phi$-function via some sort of Jacobian of $F$.
The case when $X$ is a compact Riemann  surface and $Y={\bf{P}}^1$
while $F$ is a meromorphic function on $X$ is of special interest.
\bigskip

\centerline{\bf{3.10 Cohomology and duality.}}

\medskip

\noindent
Let $X$  be a compact Riemann surface.
The constant sheaf ${\bf{C}}_X$ has a soft resolution
\[
0\to {\bf{C}}_X\to 
\mathcal E\overset{d}\to \mathcal E^1\overset{d}\to \mathcal E^2\to 0
\]
It follows that the ordinary cohomology groups
$\{ H^p(X,{\bf{C}})\}$
are equal to the cohomology of the complex
\[
0\to  \mathcal E(X)\to \mathcal E^1(X)\to \mathcal E^2(X)\to 0\tag{3.10.1}
\]
Now (3.1.1) is the dual complex. So we have for example that
\[
H^2(X,{\bf{C}})^*\simeq
\text{ker}_d(\mathfrak{c}^0(X))
\]
By 3.2.3 the last space is 1-dimensional and hence
$H^2(X,{\bf{C}})$ is also 1-dimensional.
Using this the reader can give a proof of Theorem 3.1.
Concerning the cohomology group
$H^1(X,{\bf{C}})$ its dual space
is given by
\[
\frac{\text{ker}_d(\mathfrak{c}^1(X))}{d(\mathfrak{c}^0(X)}\tag{3.10.2}
\]
Among $d$-closed 1-currents we have those which arise as
integration cycles along closed and oriented $C^1$-curves
$\gamma$.
A  major result due to Riemann asserts that this family is amply enough to
generate
the quotient space (3.10.2) and the conclusive result is
\medskip

\noindent
{\bf{3.10.3 Theorem.}}
\emph{Let $X$ be a compact Riemann surface which is not biholomorphic with
${\bf{P}}^1$. Then there exists a positive integer $g$
such that
$H^1(X,{\bf{C}})$  is a $2g$-dimensional complex vector space.
Moreover, there exist closed
1-chains $\gamma_1,\ldots,\gamma_{2g}$
whose images in (3.10.2) is a basis
and there exist closed 1-forms  $\omega_1,\ldots,\omega_{2g}$
such that}
\[
 \int_{\gamma_k}\, \omega_j= \text{Kronecker's delta-function}
\]
\medskip

\noindent
{\bf{3.10.4 Remark.}}
Theorem 3.10.3 is discussed further in a separate chapter
devoted to compact Riemann surfaces.
A notable fact is that the complex analytyic structure leads to
a decomposition of $d$-closed 1-forms
which represent
the cohomology via 
(3.10.1).
\bigskip


\centerline{\bf{3.11 Further results.}}
\bigskip

\noindent 
On a  compact Riemann surface $X$
the complex analytic structure gives a
decomposition:
\[ 
\mathcal E^1(X)= \mathcal E^{1,0}(X)\oplus
\mathcal E^{0,1}(X)
\]
The exterior differential on $X$  is decomposed into
a sum $d=\partial+\bar\partial $ and when
$f\in\mathcal E(X)$ one gets  the 1-forms
\[
\partial f\in \mathcal E^{1,0}(X) \quad\text{and}\quad\bar\partial f \in 
\mathcal E^{0,1}(X)
\]
This gives  two complexes
\[
0\to \mathcal E(X)\overset{\partial}\to
\mathcal E^{1,0}(X)\overset{\bar \partial}\to
\mathcal E^{1,1}(X)\to 0
\]
\[
0\to \mathcal E(X)\overset{\bar \partial}\to
\mathcal E^{0,1}(X)\overset{\partial}\to
\mathcal E^{1,1}(X)\to 0
\]
\medskip

\noindent
where we remark that
$\mathcal E^{1,1}(X)= \mathcal E^2(X)$.
Since $\bar\partial$ is elliptic a current 
$\gamma\in \mathfrak {c}^0(X)$ is $\bar\partial$-closed if
it is a holomorphic function, i.e. 
\[
\text{Ker}_{\bar\partial}( \mathfrak {c}^0(X))=\mathcal O(X)={\bf{C}}
\] 
where the last equality follows since holomorphic functions on
the compact Riemann surface are  constant.

\medskip

\noindent
{\bf{3.11.1 Application.}}
On $X$ one has the exact sheaf sequence
\[
0\to \Omega\to \mathcal E^{1,0}\overset{\bar\partial}\to \mathcal E^{1,1}\to 0\tag{i}
\]
This is a soft resolution of the sheaf
$\Omega$ and entails that
\[
H^1(X,\Omega)=\frac{\mathcal E^{1,1}(X)}
{\bar\partial(\mathcal E^{1,0}(X))}\tag{ii}
\]
It follows that
\[
 \bigl[H^1(X,\Omega)\bigr]^*\simeq
 \text{ker}_{\bar\partial} (\mathfrak{c}^0(X))
 \]
 Since $\bar\partial$ is elliptic the last space is
 $\mathcal O(X)$ and this is a 1-dimensional complex vector space
 becuause $X$ is compact and connected. We eonclude that
 $H^1(X,\Omega)$ is a 1-dimensional complex vector space.
 
 

\bigskip




\noindent
{\bf{3.12 Principal value distributions.}}
Let $f\in\mathfrak {M}(X)$.
It defines a distribution  $\text{VP}(f)$ as follows: When
$\sigma$ is a smooth 2-form on $X$ we avoid poles of $f$
and consider the limit integrals:
\[ 
\lim_{\epsilon\to 0}\, \int_{X_f(\epsilon)}\,f\cdot\sigma\tag{*}
\]
where $X_f(\epsilon)$ is the open complement of
small removed $\epsilon$-discs centered at the finite set of poles of $f$.
The existence of this limit was explained in §§,  i.e. in local coordinates
it amounts to show that there exist limits
\[
\int_{|z|>\epsilon},\frac{\phi(x,y)dxdy}{z^k}
\] 
for every positive integer $k$ and 
each test-function $\phi(x,y)$ in ${\bf{C}}$.
Next,  construct the current
\[
R_f=\bar\partial(\text{VP}(f))
\]
It is called the residue current of the meromorphic function $f$.
Since $f$ is holomorphic outside the poles
the (0,1)-current $R_f$
is supported by the discrete set of poles. In fact, Stokes Theorem gives
\[ 
R_f(\gamma)=
\lim_{\epsilon\to 0}\, \int_{X_f[\epsilon]}\,f\cdot\gamma\tag{**}
\]
where $X_f[\epsilon]$
consists of disjoint small circles centered at the poles
$p_1,\dots,p_k$ of $f$.

\medskip



\noindent
{\bf{3.13 The current $\frac{\partial f}{f}$}}.
Let $f\in\mathfrak {M}(X)$. 
Now 
$\frac{\partial f}{f}$ is a $(1,0)$-current.
Let  $U$ be  a chart around a zero $q$ of $f$ of some order $e$
so that $f= z^e\phi(z)$ where $\phi\neq 0$ holds in the chart.
Then 
\[
\frac{\partial f}{f}|U=\frac{\partial \phi}{\phi}+
e\cdot \frac{dz}{z}
\]
If $V$ instead is a chart around a pole
of some order $e$ we have $f= z^{-e}\phi(z)$ and obtain
\[
\frac{\partial f}{f}|V=\frac{\partial \phi}{\phi}-
e\cdot \frac{dz}{z}
\]


\medskip

\noindent
{\bf{3.14 Exercise.}}
Show that
if $g\in\mathcal E(X)$ then
\[
\frac{\partial f}{f}(dg)=2\pi i\cdot \bigl[\sum e_k\cdot g(p_k)- \sum\ e_j\cdot g(q_j)\,\bigr]
\]
where $\{p_k\}$ are the poles and $\{q_k\}$ the zeros of $f$
and $\{e_k\}$ the order of poles, respectively 
the multiplicities at the zeros of $f$.
\bigskip

\noindent
{\bf{3.15 A special  direct images.}}
Let $w\in \Omega(X)$ be an abelian differential.
It yields a smooth
current
and there exists the dirct image current
$F_*(\omega)$.
Since the passage to direct images commute with differentials we have
\[ 
\bar\partial_y(F_*(\omega))=0
\]
Hence  the direct image current belongs to
$\Omega(Y)$.
If $Y={\bf{P}}^1$ 
there are no non-zero holomorphic forms so when 
$f\colon X\to {\bf{P}}^1$ is
given via some $f\in\mathfrak{M}(X)$ then
$f_*(\omega)=0$.
The vanishing of this direct image current means that
for every  $\beta\in\mathcal E^{0,1}({\bf{P}}^1)$ one has

\[
\int_X\, w\wedge f^*(\beta)=0\tag{4.4.1}
\]
\medskip


\centerline
{\bf{3.16 Divisors and adapated currents.}}
\medskip

\noindent
A divisor $D$ on the compact Riemann surfaces
consists of a finite set of pairs $(p_\nu,k_\nu)$ whrere
$\{p_\nu\}$ are points in $X$ and
$\{k_\nu\}$ are integers which may be positive or negative.
Around each $p_\nu$ we choose a small chart
$\Delta_\nu$ with local coordinate $z_\nu$
and construct
a function
\[ 
f_\nu(z_\nu)= z_\nu^{k_\nu}\cdot \psi_\nu(z_\nu)\tag{3.16.0}
\]
By a $C^\infty$-partition of the 
unity we get
a function $f$ in $X$ which is zero-free and $C^\infty$ in
$X\setminus\{p_\nu\}$
and in each   chart    above it has the form (3.16.0).
If $k_\nu<0$ for some $p_\nu$ 
the construction of principal value distributions entails that
$f$ restricts to a distribution in
$\Delta_\nu$. The conclusion is that
$f$
is a well-defined distribution in $X$, i.e. a zero-current in
$X$.
\medskip

\noindent
{\bf{3.16. The 1-current
$\frac{df}{f}$.}}
Outside
the finite set
$\{p_\nu\}$ this is a smooth 1-current.
If $k_\nu>0$ then $df$ is smooth in
the chart $\Delta_\nu$ and can therefore be multiplied with
the principal value distribution defined by $f$. If $k_\nu<0$
then $f$ restricts to  a $C^\infty$-function in
$\delta_\nu$ which can be multiplied with
the current
$df$, i.e. here we use that
the exterior differential $d$ sends zero-currents to 1-currents.
\medskip

\noindent
{\bf{Exercise.}}
In a chart where
$f=z_\nu^{k_\nu}\cdot \psi$
the reader should verfy that
\[
\frac{df}{f}=k_\nu\cdot \frac{dz_\nu}{z_\nu}+
\frac{d\psi }{\psi}\tag{3.16.1}
\]
Decompising this 1-current the part of bi-degree (0,1) becomes
\[
\frac{\bar \partial\psi}{\psi}
\] 
which is smooth since $\psi$ is zero-free.
Conclude from the above that there exists a smooth
differential  form $\rho_f$ if bi-degree $(0,1)$ such that
\[
\frac{df}{f}(\alpha^{1,0})=\int_X\, \rho_f
\,\wedge \alpha^{1,0}
\] 
for every test-form of bi-degree $(1,0)$.
\medskip

\noindent
{\bf{3.17 The case when
$\rho_f$ is $\bar\partial$-exact.}}.
Suppoose that
\[
\rho_f=\bar\partial (g)\tag{i}
\]
for some
$C^\infty$-function $g$.
In the open set $X\setminus \{p_\nu\}$
it is celar that (3.,16.1) entails that
\[
\rho_f=f^{-1}\cdot \bar\partial(f)\tag{ii}
\]
Together (i-ii) give
\[
\bar\partial(e^{-g}f)=0
\]
in 
$X\setminus \{p_\nu\}$.
Hence $\phi=e^{-g}\cdot f$ is holomorphic in
the complement of $\{p_\nu\}$
and (3.16.0) entails that it extends to a meromorphic
function
in $X$.
Moreover, since
$e^{-g}$ is zero-free it is clear that
the principal divisor
$\text{Div}(\phi)$
via (3.16.0) coincides with the given divisor $D$.

\medskip

\noindent
{\bf{3.18 A general construction.}}
Let $D$ be a divisor as above.
Then there exists the familly $\mathfrak{c}^1(X;D)$ of 
1-currents $\gamma$ on $X$ such that
\[ 
\gamma(dg)=\sum \, k_\nu\cdot g(p_\nu)
\quad\colon
g\in C^\infty(X)
\]
In the case when
the divisor
$D$ has degree zero, i.e. $\sum\, k_\nu=0$ holds, then
we can construct a subfamily using integration chains
as in (3.5).
For eample, fix a piint $p_*$ in $X$ and let
$\{\gamma_\nu\}$
be simple and oriented curves
where $\gamma_\nu$ has end-points at $p_*$ and $p_\nu$.
Then
\[
\int_{\gamma_\nu}\, dg=g(p_\nu)-g(p_*)
\]
Since $\sum\, k_\nu=0$ it follows that
the 1-current
\[ 
\gamma=
\sum\, k_\nu\cdot \int_{\gamma_\nu}
\]
belongs to 
$\mathfrak{c}^1(X;D)$.
Moroever, each single $\gamma_\nu$ can be
exrpoessed as a sum of integration currents
taken over the all curves
parametrised  by
$t\mapsto \gamma_\nu(t)\colon\, t_j\leq t\leq t_{j+1}$
where $0=t_0<t-1<\ldots<t_N=1$
is a partiton of $[0,1]$.
\medskip

\noindent
{\bf{3.18.1 Exercise.}}
Use the last partitions above and the fact that
closed and smooth 1-forms in a chart are $d$-exact to
to prove that
when
$\gamma$ is given as above then
there
exists $f$ in (3.16.0) such that
\[ 
\gamma(\alpha)=
\sum\, k_\nu\cdot  \int_{\gamma_\nu} \,\alpha=
\frac{1}{2\pi i} \cdot \frac{df}{f}(\alpha)=\frac{1}{2\pi i} \cdot \int_X\,
\frac{df}{f}\wedge\, \alpha
\]
for every closed and smooth 1-form
$\alpha$ on $X$.






































\newpage















\centerline{\bf{§ 4. Topological results.}}
\bigskip


\noindent
We restrict the attention to topological spaces
$X$ which are Hausdorff.
One says that
the Hausdorff space $X$ has a countable topology if there
exista a denumerable family $\mathfrak{U}$
of open subsets
$\{U_n\}$ such that every
open set in $X$ is the union of 
sets from $\mathfrak{U}$.
Next, the Hausdorff space $X$ is arc-wise connected
if there to every pair of points $p,q$ in $X$ exists a continuous map
$\gamma\colon [0,1]\to X$
such that $\gamma(0)=p$ and $\gamma(1)= q$.
The following remarkable result is due to Poincaré and Volterra:


\medskip

\noindent
{\bf{4.1 Theorem.}} \emph{Let 
$X$ be arc-wise  connected and Hausdorff which in addition is locally compact.
Suppose there exists a continuous map
$f\colon X\to Y$
where
$Y$ is a Hausdorff  space with countable topology
and the fibers
$f^{-1}(y)$ are discrete subsets of $X$ for every $y\in Y$. Then
$X$ has countable topology.}
\medskip

\noindent
\emph{Proof.}
Denote by $\mathfrak{B}$ the family of open sets
$V$ in $X$ which satisfy the following:
\[
\text{$V$ has a countable topology}\tag {i} 
\]
\[
\text{$V$ is a connected component of $f^{-1}(U)$ for some
open set $U$ in $Y$}\tag{ii}
\]
Theorem 4.1 follows if we prove that
$\mathfrak{B}$ is a countable family and
every open set in $X$ is a union of
$\mathfrak{B}$-sets.
\medskip

\noindent
\emph{Proof that $\mathfrak{B}$ is countable.}
Let $V_0$ be a set in $\mathfrak{B}$ and
consider an open set $U$ in $Y$.
The connected components of
$f^{-1}(U)$ are disjoint by (i)
$V_0$ has countable topology.
It follows
that
at most countably many
of the connected components of $f^{-1}(U)$
have a non-empty
intersection with $V$.
Next, since every
$V\in \mathfrak{B}$ is of the form $f^{-1}(U)$ for an open
set in $Y$ and $Y$ has a countable topology we
conclude that
\[
V_0\cap V\neq\emptyset\tag{iii}
\]
only  can hold for
countably many $V$ in $\mathfrak{B}$.
Next, fix $V_*\in\mathfrak{B}$ and set
\[ 
\mathfrak{B}_0=\{ V\colon V_*\cap V\neq\emptyset\}
\]
By (iii) this is a countable set in $\mathfrak{B}$.
If $n\geq 1$ we define inductively
\[
\mathfrak{B}_n= \{V\colon \exists\, W\in\mathfrak{B}_{n-1}\, \colon
 W\cap V\neq\emptyset\}
\]
An induction over $n$ entails
that each
$\mathfrak{B}_n$ is countable and since
$X$ is connected it is clear that
their union is equal to $\mathfrak{B}$
which therefore is a countable family.
\medskip

\noindent
\emph{Proof that
$\mathfrak{B}$ is a basis of the topology.}
Let $\Omega\subset X$ be open and take some
$x\in\Omega$. We must prove that there exists
$V\in\mathfrak{B}$ such that
\[
x\in V\subset\Omega
\]
To show this we consider the discrete fiber
$f^{-1}(f(x))$. Since $X$ is Hausdorff and locally compact
there exists 
a small open and relatively compact neighborhood $W$ of $x$ such that 
$W\subset \Omega$ and
$\partial W\cap f^{-1}(f(x))=\emptyset$.
Now $f(\partial W)$ is a compact set in $Y$
which does not contain
$f(x)$ which gives $U\in\mathfrak{U}$ such that
\[
f(x)\in U\quad\colon f(\partial W)\cap U= \emptyset
\]
Let $V$ be the connected component of $f^{-1}(U)$ which contains
$x$.
From the above $V\cap \partial W=\emptyset$ and
we conclude that 
\[
x\in V\subset W\subset\Omega
\]
which finishes the proof.
\bigskip

\centerline {\bf{4.2  Covering spaces.}}
\bigskip


\noindent
Let $X$ be arc-wise connected and Hausdorff.
A pair $(Y,\rho)$ is a covering of $X$ 
if $\rho\colon Y\to X$ is a continuous map and
for each point $p\in X$ there exists some open neighborhood $U$
such that
\[ \rho^{-1}(U)= \cup \, V_\alpha
\]
where the right hand side is a disjoint union of open sets in
$Y$ and $\rho\colon V_\alpha\to U$ are homeomorphisms for
each $\alpha$.
\medskip

\noindent
{\bf{4.2.1 Exercise.}}
Let $\gamma\colon  [0,1]\to X$ be a continuous map
and let $y_0\in Y$ be a point such that
\[
\rho(y_0)= x_0=\gamma(0)
\]
Show that there exists a unique continuous map
$\gamma^*\colon  [0,1]\to Y$ such that
$y_0=\gamma^*(0)$ and
\[
\rho(\gamma^*(t))= \gamma(t)\,\colon\, 0\leq t\leq 1\tag{i}
\]
which means that
there exist unique liftings of curves. 
\bigskip

\noindent
Next, let $\pi_1(X)$ be the fundamental  group of $X$.
Since $X$ is arc-wise connected it can be identified with homotoy classes
of closed curves $\gamma$ which have a given
$x_0\in X$ as a common initial and terminal point.
Let us also fix a point $y_0$ in the fiber
$\rho^{-1}(x_0)$.
To each closed $\gamma$-curve as above the exercise gives
a unique lifted curve
$\gamma^*$  where  (i) entials that
\[
\rho(\gamma(1))\in
\rho^{-1}(x_0)\tag{ii}
\]

\medskip

\noindent
{\bf{4.2.2 Exercise.}}
Show that the end-point
$\gamma(1)$ in  (ii)
only  depends upon the homotopy class of
$\gamma$ and conclude that
one has a map
\[
\rho_*\colon \pi_1(X)\to \rho^{-1}(x_0)\tag{*}
\]
Show also that $\rho_*$ is surjective
if $Y$ is connected.
\medskip

\noindent
{\bf{4.2.3 The universal covering property.}}
A covering $\phi \colon Z\to X$ has a universal property if the
following holds: For every covering
$\rho\colon Y\to X$
and each pair of points $z_0\in \phi^{-1}(x_0)$ and
$y_0\in \rho^{-1}(x_0)$ there exists a unique fiber preserving continuous map
$f\colon Z\to Y$ with $f(z_0)=y_0$ and 
\[ 
\rho\circ f=\phi\tag{**}
\]
Notice that (**) means that $f$ is fiber preserving.
\medskip

\noindent
{\bf{4.2.4 Exercise.}}
Show that a covering with the universal property is unique in
the sense that if $(Z_1,\phi_1)$ and $Z_2,\phi_2)$ is such a pair then
there exists a homeomorphism $g\colon Z_1\to Z_2$
with
\[
\phi_1= \phi_2\circ g
\]
\medskip

\noindent
{\bf{4.2.5 Existence.}}
Show that an arc-wise connected  Hausdorff space
$X$ has a universal covering $\widehat{X}$ and that
the fundamental  group
$\pi_1(\widehat{X})=0$.
\medskip

\noindent
{\bf{4.2.6 The Galois property.}}
A covering $\rho\colon Y\to X$
where $Y$ is connected has the Galois property if there
to each
$p\in  X$ and every pair
of points $y_1,y_2$ in $\rho^{-1}(p)$ exista a fiber presering
homeomorphism $f\colon Y\to Y$
with
$f(y_1)= y_2$.
\medskip

\noindent
{\bf{4.2.7 Exercise.}}
Verify that the universal covering $\widehat{X}$
has the Galois property.


\bigskip
\centerline {\bf{4.3 Runge sets on Riemann surfaces.}}

\bigskip


\noindent
If $K$ is a compact subset of the Riemann surface $X$
we get the conncted components $\{\Omega_\alpha\}$
of the open complement $X\setminus K$.
Since $X$ is connected we notice that
\[ 
\partial\Omega_\alpha\subset K\tag{i}
\] 
hold for every connected component in $X\setminus K$.
Next,
choose an open set $U$ which contains $K$ where $\overline{U}$
is compact.
This is of course possible since
$K$  can be covered by a finite number of charts
where each chart has a compact closure in $X$.
If a component 
$\Omega_\alpha$ is such that
\[ 
\partial U\cap \Omega_\alpha= \emptyset\tag {ii}
\] 
the connectivity
of $X$ and (i) entail that
\[
\Omega_\alpha\subset U\tag{iii}
\]
Next,  the Heine-Borel Lemma
a finite
family of $\Omega_{\alpha_1},\ldots,\Omega_{\alpha_N}$
whose union cover the compact set $\partial U$.
Among these occur a finite family of non-compact
sets, say
$\Omega_{\alpha_1},\ldots,\Omega_{\alpha_k}$ where $1\leq k\leq N$.
Set
\[ 
\mathfrak{h}(K)= K\, \cup\, \bigcup_*\, \Omega_\alpha\tag{iv}
\]
 where the *-marked union is taken over
 all components for which (iii) hold together with  the finite family of relatively compact
 components which intersect $\partial U$, or equivalently
 \[
 \mathfrak{h}(K)=X\setminus \Omega_{\alpha_1}\,\cup\ldots \cup\, \Omega_{\alpha_k}
\]

 
 \noindent
 {\bf{4.3.1 Exercise.}}
 Verify that $\mathfrak{h}(K)$ is compact and that
 \[ 
 \mathfrak{h}(\mathfrak{h}(K))=\mathfrak{h}(K)
 \]
 
 
 \noindent
{\bf{4.3.2 Open Runge sets.}}
An open subset $Y$ in $X$ is Runge if
\[ 
K\subset Y\implies \mathfrak{h}(K)\subset Y
\]
hold for every compact set $K$, i.e. the Runge hull of a compact
subset of $Y$ stays in $Y$.
 \medskip
 
 \noindent
{\bf{4.3.3 Proposition.}}
\emph{Let $K$ be a compact Runge set
in $X$ with a non-empty interior.
Let $\Delta_1,\ldots,\Delta_N$
be a finite number of open  discs whose union cover
$\partial K$.  Then the open set below is Runge:}
\[
Y=K\setminus \,\cup\, \overline{\Delta}_\nu
\]  

 \noindent
The easy proof is left as an exercise.







\newpage

\centerline{\bf{§ 5. Runge's theorem.}}
\medskip


\noindent
Let $Y$ be a relatively  compact open set in the non-compact Riemann surface
$X$ and $K\subset Y$ is  a compact subset such that
$K=\mathfrak{h}(K)$.
Let $\mathcal O(K)$
be the space of germ of analytic functions on $K$.
Each $f\in \mathcal O(K)$ has a restriction to $K$
which yields a continuous function $f_*\in C^0(K)$.

\medskip

\noindent
{\bf{5.1 Proposition.}}
\emph{Let $Y,K$ be a pair as above.
Then, for each  
 $f\in\mathcal O(K)$ 
there exists a sequence $\{g_n\}$ in $\mathcal O(Y^*)$ such that
the maximum norms
$|g_n-f_*|_K\to 0$.}

\medskip

\noindent
\emph{Proof.}
Since
$Y$ is relatively compact we have 
$H^1(Y,\mathcal O)=0$ by Proposition  0.2.4.
By Dolbeault's isomorphism it follows that
if
$\omega\in \mathcal E^{0,1}(X)$ then there exists
$g\in\mathcal E(Y)$ 
such that
\[ 
\omega|Y=\bar\partial(g)\tag{i}
\]
Next, let
$\mu$ be a Riesz measure with compact support contained
in
$K$
such that
\[ 
\int\, f\cdot d\mu=0\quad\colon f\in\mathcal O(Y)\tag{ii}
\]
For a given $\omega$ in (i) the $g$-function is unique up to
$\mathcal O(Y)$ and hence (ii) entails that
\[
\int\, g\cdot d\mu
\]
only depends on $\omega$.
This gives a current $S$ of bi-degree
(1,0) acting on
smooth (0,1)-forms $\omega$ via the rule above.
Next, consider
an 
open chart $\Delta$ contained in $X\setminus \text{supp}(\mu)$.
If $g\in C_0^\infty(X)$ has compact support in
$\Delta$ we take $\omega^{0,1}= \bar\partial(g)$
and since $g=0$ on the support of $\mu$  one has 
\[
S(\bar\partial(g))=0\tag{iii}
\]
Since this hold for every pair $(\Delta, g)$ as above we conclude that 
$S$ is $\bar\partial$-closed in $X\setminus \text{supp}(\mu)$ and
the elliptic property of
$\bar\partial$ gives a holomorphic 1-form
$\sigma$ in $X\setminus \text{supp}(\mu)$ such that
\[
S(\omega^{0,1})=\int\, \omega^{0,1}\wedge \sigma\tag{iv}
\]
holds when $\omega^{0,1}$ has compact support in
$X\setminus \text{supp}(\mu)$.
\medskip

\noindent
Consider a
point $p\in X\setminus K$.
Since $K=\mathfrak{h}(K)$
there exists 
a non-compact
open and connected subset $\Omega$ 
of $X\setminus\ K$
which contains $p$. 
Now the 
current $S$ has a compact support which implies that
\[
\Omega\setminus \text{Supp}(S)\neq \emptyset\tag{v}
\]
Let $q$ be a point in this set and 
choose a small open chart
$\Delta$ centered
at $q$
which stays in $\Omega$ and is disjoint from
the support of $S$. Then
\[
\int\, \omega^{0,1}\wedge \sigma=0
\] 
for every test-form
$\omega^{0,1}$ with compact support in
$\Delta$. Hence the restriction of $\sigma$
to $\Delta$ is zero. Since
$\sigma$ is a 
holomorphic 1-form
and  $\Omega$ is connected, 
analyticity
gives 
$\sigma|\Omega=0$. In particular $\sigma=0$ holds in a neighborhood of
$p$ which  proves the inclusion
\[
 \text{Supp}(S) \subset
K\tag{vi}
\]
Finally, 
let
$f\in\mathcal O(K)$ which by defintion means that it
is a holomorphic function defined in some open neighborhood $U$ of $K$.
There exist  
a test-function $g$ with compact support in
$Y$ such that
$g=f$ 
holds in a neighborhood of $K$.
Then $\bar\partial(g)$ vanishes in a neighborhood of
$K$ so (vi) and the construction of $S$ entail that
\[ 
0=S(\bar\partial g)=\int_K\,g\cdot d\mu=
\int_K\,f\cdot d\mu\tag{vii}
\] 
Since $\mu$ was an arbitrary Riesz meausure for which (ii) holds
and we have proved that (ii) implies (vii) for every
$f\in\mathcal O(K)$, we get Proposition 5.1 from the Hahn-Banach theorem.
\medskip

\noindent
{\bf{Remark.}} Above we have followed a proof given by
Malgrange.








\bigskip





\centerline{\bf{6. Proof of the Behnke-Stein theorem.}}

\medskip


\noindent
By  § xx  we can  exhaust the open Riemann surface
$X$ by an increasing sequence of Runge domains
$\{Y_n\}$  where the closure of $Y_n$
is a compact subset of $Y_{n+1}$ 
for each $n$.
Consider
some $\phi\in \mathcal E^{0,1}(X)$.
By Theorem 1.3 the restriction of $\phi$ to $Y_n$ is
$\bar\partial$-exact for every $n$.
Hence there exists
$f_n\in \mathcal E(Y_n)$
such that 
\[
 \bar\partial f_n=\phi|Y_n\tag{6.1}
\]
It follows that
the restriction to $Y_n$ of $f_{n+1}-f_n$ is holomorphic
and since $Y_n$ is Runge and $\overline{Y}_{n-1}$ is a compact subset,
Proposition 5.1  entails that $f_{n+1}-f_n$
can be uniformly approximated on
$Y_{n-1}$ by functions from $\mathcal O(Y_{n+1})$.
Hence there
exists 
$g_{n+1}\in \mathcal O(Y_{n+1})$
such that the maximum norm
\[
||g_{n+1}+f_{n+1}-f_n||_{Y_{n-1}}<2^{-n}
\]
With $f^*_{n+1}= f_{n+1}+g_{n+1}$
we still have
\[
\bar\partial f^*_{n+1}=\phi|Y_{n+1}
\]
Perfoming
these modifications inductively with increasing $n$ we obtain a 
sequence $\{f^*_n\}$ such that   (6.1) hold for every $n$
and 
\[
||f^*_{n+1}-f^*_n||_{Y_{n-1}}<2^{-n}
\quad\colon \, n=1,2,\ldots\tag{6.2}
\]
It follows that $\{f_n^*\}$ converge uniformly on $X$ to a continuous function
$F$ which 
entails that
the distributions
$\{\bar\partial f_n^*\}$ converge to the distribution derivative
$\bar\partial (F)$. Moreover, since (6.2) hold for every
$n$
it is clear that
\[ 
\bar\partial(F)=\phi\tag{6.3}
\]
holds everywhere in $X$.
Finally, $\phi$ is a smooth form so  the elliptic property of
$\bar\partial$ implies that
$F$ is a $C^\infty$-function. Hence the mapping
$\bar\partial\colon \mathcal E(X)\to \mathcal E^{(0,1)}(X)$
is surjective which proves the Behnke-Stein theorem.



\newpage

\centerline{\bf{§ 7. Further results on non-compact Riemann surfaces.}}
\bigskip


\noindent
A locally free sheaf of $\mathcal O$-modules with rank one is called
a
holomorphic line bundle.
Let $\mathcal L$ be such a sheaf.
By definition it has local trivialisations, i.e. we can find
a locally finite covering $\mathfrak{U}$
by charts such that
the restricted sheaf
$\mathcal L|U_\alpha\simeq \mathcal O$.
In each non-empty intersection
$U_\alpha\cap U_\beta$ we find
a zero free function 
$g_{\alpha\beta}\in\mathcal O^*(U_\alpha\cap U_\beta)$
so that the space $\mathcal L(V)$ of sections over
an open subset $V$ in $X$
consists of a family $\{\xi_\alpha\in \mathcal O(U_\alpha\cap V)\}$
satisfying th glueing conditions
\[
\xi_\alpha|U_\alpha\cap U_\beta\cap V=
g_{\alpha\beta}\cdot
\xi_\beta|U_\alpha\cap U_\beta\cap V\tag{1}
\]
\medskip

\noindent
Now one can repeat the methods which were used in the previius sections
and extend the Behnke-Stein theorem as follows:

\medskip

\noindent
{\bf{7.1 Theorem.}}
\emph{For every holomorphic line bundle
$\mathcal L$ one has $H^1(X,\mathcal L)=0$.}
\medskip


\noindent
{\bf{Example.}}
Notice that the 
sheaf $\Omega$ of holomorphic 1-forms is a holomorphic line bundle.
Another example is the sheaf
$\Theta_X$ whose sections are holomiorphic vector fields.
here we notice that
\[ 
\Omega=Hom_{\mathcal O}(\Theta_X,\mathcal O)
\]
is the  dual line bundle.
So Theorem 7.1 entails that
\[
H^1(X, \Omega)=H^1(X,\Theta_X)=0\tag{7.2}
\]



 \medskip
 
 
 \centerline{\bf{7.3 
Weierstrass'  Theorem}}

\bigskip


\noindent
Let $D$ be a divisor on $X$
which means that integers $\{k_\nu\}$ are assigned to
a discrete sequence of points $\{p_\nu\}$.
We shall  prove that there exists a globally deefined meromorphic function $\psi$
whose principal divisor is $D$.
To begin with one has:

\medskip

\noindent
{\bf{7.3.1 Exercise.}}
Use a
$C^\infty$-partition of the unity
to find a function $\phi$ which is zero-free and 
$C^\infty$ in the open complement of
the discrete set $\{p_\nu\}$, and for each
$p_\nu$ there is a small open  chart
$\Delta_\nu$ centered at $p_\nu$ with a local coordinate
$z_\nu$ where 
\[
\phi|\Delta_\nu= z_\nu^{k_\nu}
\]


\noindent
Next, we find a locally finite covering
$\mathfrak{U}=\{U_\alpha\}$ of  charts in
$X$ which contains
the discs
$\{\Delta_\nu\}$
while each $U_\alpha$ which differs from these discs 
does not contain points in $\{p_\nu\}$.
For
each
$U_\alpha$ which does not contain any point in
$\{p_\nu\}$ we take $f_\alpha=1$ while
$f_\alpha= z_\nu^{k_\nu}$ when
$U_\alpha=\Delta_\nu$.
Then we can write 
\[
\phi|U_\alpha= f_\alpha\cdot \psi_\alpha
\quad\colon\,\psi_\alpha\in C^\infty(U_\alpha)
\tag{i}
\] 
Since $\phi$ is zero-free outside
$\{p_\nu\}$ we see that
every $\psi$-function is zero-free. Next, since  every chart
$U_\alpha$ is simply connected there exist
$\{\rho_\alpha\in C^\infty(U_\alpha)\}$ such that
\[
 \psi_\alpha= e^{\rho_\alpha}\tag{ii}
\]
In each non-empty intersection $U_\alpha\cap U_\beta$  
it follows that
\[
e^{\rho_\alpha-\rho_\beta}=\frac{f_\beta}{f_\alpha}\tag{iii}
\]
Each quotient
$\frac{f_\beta}{f_\alpha}\in \mathcal O^*(U_\alpha\cap U_\beta)$
and then 
(iii) entails that
the restricted differences
\[
\rho_\alpha-\rho_\beta|U_\alpha\cap U_\beta)\in 
\mathcal O(U_\alpha\cap U_\beta)
\]
So with $g_{\alpha\beta}=\rho_\alpha-\rho_\beta|U_\alpha\cap U_\beta)$
we get a Cech-cocycle in $H^1(\mathfrak{U},\mathcal O)$.
The Behnke-Stein theorem entails that it is a $\delta$-coboundary which
give $\{g_\alpha\in \mathcal O(U_\alpha)\}$ such that
\[
\rho_\alpha-\rho_\beta|U_\alpha\cap U_\beta)=g_\alpha-g_\beta\tag{iv}
\]
Taking exponentials in (iv) and using (iii) it follows that
the following hold
in $U_\alpha\cap U_\beta$:
\[
e^{g_\alpha}\cdot f_\alpha=
e^{g_\beta}\cdot f_\beta\tag{v}
\] 
This gives
a globally defined meromorphic
function
$\psi $ such that
\[ 
\psi|U_\alpha=e^{g_\alpha}\cdot f_\alpha\tag{vi}
\]
Finally,  the construction of the $f$-functions  implies  that 
the principal divisor $D(\psi)$ is equal to the given divisor $D$
which finishes the proof of Weierstrass' theorem.
\bigskip


\noindent
{\bf{7.3.2 The construction of a non-vanishing holomorphic form.}}
Take a non-zero global section $\omega$ in $\Omega(X)$.
If $(\Delta,z)$ is a chart we have
\[
\omega|\Delta=g(z)\cdot dz
\]
where $g\in\mathcal O(\Delta)$ is non-constant and hence has
a discrete set of zeros.
The locally defined divisors of these $g$-functions
match each other and yield a globally defined
divisor
$D=\{(p_\nu;k_\nu)\}$ in $X$.
Notice that
$D$ is positive, i.e.
 the integers $k_\nu>0$.
Weierstrass's theoren gives
$\psi\in\mathcal O(X)$ with $D(\psi)=D$.
Then it is clear that
\[ 
\omega^*=\psi^{-1}\cdot \omega
\]
yields a holomorphic 1-form whose associated $g$-functions in local charts
are zero-free.

\bigskip

 




\centerline{\bf{§ 8. The uniformisation  theorem}}

\bigskip


\noindent
Consider a  non-compact Riemann surface
$X$ where  every holomorphic 1-form is $\partial$-exact.
By (7.3.2)  there exists $\omega\in \Omega(X)$ which is everywhere 
non-zero.
So if $Y$ is an open set in $X$
and $\mu\in\Omega(Y)$
 there exists $g\in\mathcal O(Y)$ such that
 \[ 
 \mu= g\cdot \omega_Y\tag{i}
\] 
where $\omega_Y$ is the restriction of $\Omega$ to $Y$.
We use this to prove

\medskip

\noindent
{\bf{8.1 Proposition.}} \emph{If 
$Y$ is  an open Runge set in $X$ one has}
\[
\Omega(Y)=\partial(\mathcal O(Y))\tag{8.1.1}
\]

\noindent
\emph{Proof.}
Let  $\mu$ be as in (i).
Consider a point $y_0\in Y$ and a closed curve
$\gamma$ in $Y$ which has $y_0$ as initial 
and terminal point.
Since $Y$ is Runge, Theorem § XX   gives  a sequence
$\{g_n\}$ in $\mathcal O(X)$ and 
the maximum norms $|g_n-g|_\gamma\to 0$.
It follows that
\[
\int_\gamma\, \mu=\lim_{n\to\infty}\, \int_\gamma\, g_n\cdot \omega
\]
Here $\gamma$ is a closed curve in $X$ and since
each $g_n\cdot \omega$ belong to $\Omega(X)$ the 
hypothesis on $X$ implies
that the integrals in
the right hand side above are all zero. Hence
the line integrals of $\mu$ are zero for all closed curves
at $y_0$ and then  § xx shows  that it is $\partial$-exact in $Y$
which finishes the proof.

\medskip

\noindent
{\bf{8.2 Semi-local conformal mappings.}}
Let $Y$ be a relatively compact open subset of $X$ which is 
Runge and Dirichlet regular.
Let $y_0\in Y$ and by
§§ there exists
$g\in\mathcal O(X)$ with  a simple zero at $y_0$ and  zero-free
in $X\setminus\{y_0\}$.
Now $\mathfrak{Re}(g)$ restricts to a continuous function
on $\partial Y$ and we find a harmonic function
$u$ in $Y$ whose boundary value function is
$\log |g|$.
The equality (5.1.1) and the remark in § xx  entail that
$u$ has a harmonic conjugate $v$ in $Y$
which gives $u+iv\in\mathcal O(Y)$. Set
\[
f=g\cdot e^{-(u+iv)}
\]
On $\partial Y$ it follows that
\[ 
|f|=|g|\cdot e^{-\log|g|}=1
\]
At the same time $f$ has a simple zero at $y_0$ and is zero-free in
$Y\setminus \{y_0\}$.
The result in § xx shows  that
$f\colon Y\to D$ is biholomorphic.
Around $y_0$ we choose a small chart
$(\Delta,z)$ and get the non-zero complex derivative 
$f'(0)$
of $f$ at $z=0$.
With
\[
f^*=\frac{1}{f'(0)}\cdot f\tag{8.2.1}
\] 
we have a 
biholomorphic mapping from $Y$ into the open disc of radius
$|f'(0)|$
and  the $f^*$-derivative at $z=0$ is one.




\medskip

\noindent
{\bf{8.3 A global construction.}}
By § xx we can exhaust $X$ with an increasing sequence of
relatively compact open subsets
$\{Y_n\}$ which are Runge and Dirichlet regular.
Fix a point $p\in Y_0$
and a local chart $(\Delta,z)$ as above.
For each $n\geq 0$  (8.2.1) gives some $r_n>0$ and a biholomorphic map
\[
f_n\colon Y_n\to D(r_n)
\]
where $f_n(p)=0$ and $f'_n(0)=1$.
The inverse mapping $f_n^{-1}$
is holomorphic in the open disc $D(r_n)$
and we notice that the complex derivative
\[
(f_n^{-1})'(0)=1\tag{i}
\]
Next, to each $n\geq 0$ we have the  composed function
\[
h_n= f_{n+1}\circ f_n^{-1}
\]
which maps $D(r_n)$ into $D(r_{n+1})$
where $h_n(0)=0$ and (i) gives
$h'_n(0)=1$. Schwarz'  inequality implies that 
\[
r_n\leq r_{n+1}
\]
Set
\[ 
R= \lim_{n\to\infty}\, r_n
\]
We shall construct a biholomorphic map
$f^*\colon X\to D(R)$  where the case $R=+\infty$ means that
$D(+\infty)={\bf{C}}$.
To find $f^*$ we shall pass to certain subsequences of 
$\{f_n\}$.
Consider first the composed functions
\[
g_n= \frac{1}{r_0}\cdot f_n\circ f_0^{-1}(r_0z)
\]
which by the choice of $r_0$ and the inclusion $Y_0\subset Y_n$ are
holomorphic in the open unit disc $D$ of the complex $z$-plane.
It is clear that
we have
\[
g_n(0)=0\quad\colon g'_n(0)=1
\]
Moreover, $g_n$ is a biholomorphic map from
$D$ onto the
open set $r_0^{-1}\cdot f_n(Y_0)$.
By the  result from § xx  $\{g_n\}$ is a normal family in the sense lof
Montel. Hence we can extract a subsequence
$\{g_{n_k}\}$ which converges uniformly on compact subsets
of $D$.
\medskip

\noindent
{\bf{Exercise.}}
Verify that
the convergence of $\{g_{n_k}\}$  above entails that
$\{f_{n_k}\}$  converges uniformly over compact subsets of $Y_0$
to a limit function $f^*_0\in\mathcal O(Y)$.
Moreover, since
each restriction $f_{n_k}|Y_0$
is biholomorphic and the derivatives
$f'_{n_k}$ at $p$ all are equal to one, 
it follows from
the result in § xx that
$f^*_0\colon Y_0\to f_0^*(Y_0)$ is biholomorphic.
\bigskip

\noindent
Next, starting with the sequence 
\[
g_k= r_1^{-1}\cdot f_{n_k}\circ f_1^{-1}
\]
we repeat the arguments above and find
a subsequence $\{\phi_{k_j}\}$ which conveges uniformly  in the unit disc
and
returning  to the $f$-sequence,  its corresponding  subsequence
converges uniformly on $Y_1$ to a limit function
$f^*_1$ which yields a biholomorphic map from
$Y_1$ onto $f^*_1(Y_1)$.
We  continue  
by an induction over $n$ and 
obtain  biholomorphic maps $\{f^*_n\colon Y_n\to f^*_n(Y_n)\}$ 
and after the passage to a  diagonal subsequence we find
a subsequence $\{f_{n_k}\}$ which converges uniformly on compact subsets of
$x$ to a limit function $f^*$ which gives the requested biholomorphic map
from $X$ onto $D(R)$.



\newpage


\centerline{\bf{Representations of fundamental groups.}}
\medskip


\noindent
Let $X$ be an open Riemann surface which is not simply connected, i.e.
the fundamental
group $\pi_1(X)\neq 0$.
Recall that it  can be identfied with homotopy classes of closred and differentiable curves
which start and terminte at a given point $p_*\in X$.
Let $f$ be a globally defined and zero-free holomorphic function.
Then there exists the holomorphic 1-form $f^{-1}\partial f$
which can be integrated along every closed curve
$\gamma$ above.
The monodromy theorem shows that
\[
 \int_\gamma\, f^{-1}\partial f\tag{1}
\]
only depends on the homotopy class of $\gamma$.
Moreover, locally $f=e^g$ where $g$ is determined up to an integer
multiple of $2\pi $.
Covering $\gamma$ by a finite sequence of charts
it follows that (1) is an integer times
$2\pi i$.
So if $\{\gamma\}$ is the homotopy class we get a
map
\[
\{\gamma\}\mapsto \frac{1}{2\pi i}\cdot
 \int_\gamma\, f^{-1}\partial f\tag{2}
\]
from $\pi_1(X)$ into the additive group of integers.
\medskip

\noindent
{\bf{Theorem.}} \emph{Every  group homomorphism from
$\pi_1(X)$ into ${\bf{Z}}$ is given by (2) for a zero-free holomorphic function
$f$.}
\medskip

\noindent
The proof follows from  the Behnke-Stein theorem.
To begin with one regards the
universal covering space
of $X$ which gives 
a 1-1 correspondence between
additive group homeomorphisms of $\pi_1(X)$ and the cohomology group
$H^1(X;{\bf{Z}}_X$. Next, one has the exact sheaf sequence

\[
0\to {\bf{Z}}_X\to \mathcal O\overset{\text{exp}}\to \mathcal O^*\to 0
\]
Since $H^1(X,\mathcal O)=0$ it follows that
\[
H^1(X;{\bf{Z}}_X)\simeq \frac{\mathcal O^*(X)}{\text{exp}(\mathcal O(X))}
\]
The theorem follows from the observation that
a zero-free holomorphic function $f$ on $X$ is of the form
$e^g$ with $g\in\mathcal O(X)$ if and only if
the integrals in (ii) are zero for all closed curves $\gamma$.
Here one direction is clear, i.e. if $f=e^g$
we have
\[ 
f^{-1}\partial f= \partial  g
\]
and use that line integrals of exact 1-forms taken along a closed curve are zero.
Conversely, if (2) is zero for all $\gamma$ there
exists a holomorphic function $g$ on $X$ defined
by
\[ 
g(x)= \int_{p_*}^ x\, f^{-1}\partial f
\]
where the integral is taken ovar
a curve starting at $p_*$ and terminating at $x$
and itis clear that
$\partial g= f^{-1}\partial f$ which finishes the proof.






\newpage

\centerline{\bf{Appendix. Linear operators and spectral theory.}}

\bigskip



\noindent
{\bf{Introduction.}}
We shall expose basic facts about spectra of densely defined linear operators on
Banach spaces. Let us remark
that the special case of bounded linear operators is
incorporated in Neumann's general theory as a special case.
The major result is Theorem A.6.3 which extends thr
calculus  for matrices with complex elements where
the spectrum is finite and resolvent operators
are expressed via 
Cayley-Hamilton equations. 
In addition to the basic 
material in § A.2-A.7 below we include a result about
an inequality for resolvent operators in § A.8. 
In contrast to the previous material the
proof is
more involved but has been inserted to give a glimpse of more
advanced
results in spectral theory.
At the same time Carleman's proof offers  a very instructive lesson.

\medskip

\noindent
{\bf{The finite dimensional case.}}
Let 
$T\colon V\to V$ be a linear operator on
a finite dimensional complex vector space
$V$ of  some dimension $N\geq 2$.
Let $E$ be the identity operator and with a complex number
$\lambda$ there exists the determinant polynomial
\[
P_T(\lambda) =\text{det}(\lambda\cdot E-T)
\]
This is a monic polynomial in $\lambda$ of degree 
$N$ 
which we write as
\[
\lambda^N+c_{N-1}\lambda^{N-1}+\ldots +c_1\lambda+c_0\tag{1}
\]
A fundamental fact in matrix calculus  is  Hamilton's  equation
\[
T^N+c_{N-1}\cdot T^{N-1}+\ldots +c_1\cdot T+c_0\cdot E=0\tag{*}
\]
The zeros of the determinant  polynomial
is the spectrum $\sigma)T)$.
If $\mu $ is outside the spectrum there exists the 
inverse linear operator
\[ 
R_T(\mu)=(\mu\cdot E-T)^{-1}
\]
A crucial  point  is that
\[
\mu\mapsto R_T(\mu)\tag{2}
\] 
is an analytic matrix-valued function in
${\bf{C}}\setminus \sigma(T)$.
The analyticity is expressed by saying that the $N^2$ many elements of
$R_T(\mu)$ are complex-valued analytic functions of
$\mu$.
\medskip

\noindent
{\bf{Cayley's equation.}}
If $\mu$ is outside the spectrum we have the polynomial
\[ 
\lambda\mapsto 
\text{det}((\lambda-\mu)\cdot E-T)=P_T(\lambda-\mu)
\]
which via (1) is of the form
\[
\lambda^N+c_{N-1}(\mu)\cdot (\lambda^{N-1}+\ldots +c_1(\mu)\cdot
\lambda+c_0(\mu)\tag{iii}
\]
where $\{c_k(\mu)\}$ are polynomials in $\mu$.
Here
\[
c_0(\mu)= (-1)^N\cdot \text{det}(\mu\cdot E-T)\neq 0
\]
and the Hamilton equation gives
\[
(\mu\cdot E-T)^N+c_{N-1}\cdot (\mu\cdot E-T)^{N-1}+\ldots +
c_1\cdot (\mu\cdot E-T)+c_0\cdot E=0\tag{**}
\]
This entails that
\[
R_T(\mu)=\frac{(-1)^{N+1}}{c_0(\mu)}\cdot
\bigl[(\mu\cdot E-T)^{N-1}+c_{N-1}(\mu)\cdot (\mu\cdot E-T)^{N-2}+\ldots +
c_1(\mu)\cdot E\,  \bigr]\tag{***}
\]
One refers to the right hand side as Cayley's equation for the resolvent
$R_T(\mu)$ which exibits  the function in (2)
as a polynomial of degree $N-1$ in $T$ whose coefficients 
are rational functons of $\mu$ with
poles confined to $\sigma(T)$.
\medskip


\noindent
{\bf{A.0 Densely defined operators.}}
The Cayley-Hamilton calculus extends  verbatim
to
a quite general case using Neumann's definition of  resolvent operators
in A.1 below.
Let $X$ be a Banach space and
$T\colon X\to X$
a linear and densely defined operator whose 
domain of definition 
is  denoted by $\mathcal D(T)$.
In general $T$ is unbounded:
\[
\max_{x\in \mathcal D_*(T)}\, ||T(x)||=+\infty
\]
where the maximum is taken over
unit vectors in
$\mathcal D(T)$.




\medskip

\noindent
{\bf{A.1 Inverse operators.}}
A densely defined operator $T$ has a bounded inverse
if the range $T(\mathcal D(T))$ is equal to $X$
and there
exists a positive constant $c$ such that
\[
||T(x)||\geq c\cdot ||x||\quad\colon x\in\mathcal D(T)\tag{i}
\]
Since
$T(\mathcal D(T))=X$, (i) gives
for each
$x\in X$ a unique vector $R(x)\in\mathcal D(T)$
such that
\[
T\circ R(x)= x\tag{ii}
\]
Moreover, the inequality (i) gives
\[
||R(x)||\leq c^{-1}\cdot ||x||\quad\colon x\in X\tag{iii}
\]
and when  $R$ is applied to the left on both sides in (ii), it follows that
\[ 
R\circ T(x)=x\quad\colon x\in\mathcal D(T)\tag{iv}
\]


\noindent{\bf{A.2 The spectrum $\sigma(T)$}}.
Let
$E$ be the identity operator on $X$. Each complex number
$\lambda$ gives  the densely defined
operator $\lambda\cdot E-T$.
If it fails to be invertible one   says that
$\lambda$ is a spectral  point of $T$ and denote this set
by
$\sigma(T)$.
If $\lambda\in{\bf{C}}\setminus \sigma(T)$
the  inverse  to
$\lambda\cdot E-T$ is denoted by $R_T(\lambda)$
and called a Neumann resolvent to $T$.
By the construction in (A.1)
the range of every Neumann resolvent 
is equal to $\mathcal D(T)$
and one has the  equation:
\[
T\circ R_T(\lambda)(x)= 
R_T(\lambda)\circ T (x)\quad\colon x\in \mathcal D(T)\tag{A.2.1}
\]




\medskip

\noindent
{\bf{Example.}}
Let $X$ be the Hilbert space $\ell^2$ whose vectors are  complex sequences
$\{c_1,c_2,\ldots\}$ for which $\sum\ |c_n|^2<\infty$.
We have  the dense subspace $\ell^2_*$ vectors such that
$c_n\neq 0$ only occurs for finitely many integers $n$.
If $\{\xi_n\}$ is an arbitrary sequence of complex numbers
there exists the densely defined operator $T$ on $\ell^2$
which
sends every sequence  vector $\{c_n\}\in \ell_*^2$ to
the vector $\{\xi_n\cdot c_n\}$.
If $\lambda$ is a complex number 
the reader may check that
(i) holds in (A.1) if and only if
there exists a  constant $C$ such that
\[
|\lambda-\xi_n|\geq C\quad\colon n=1,2,\ldots\tag{i}
\]
Thus, $\lambda\cdot E-T$ has a bounded  inverse if and ony if
$\lambda$ belongs to the open complement of the closure of the
set
$\{\xi_n\}$ taken in the complex plane.
Moreover,   if (i) holds then
$R_T(\lambda)$ is the bounded
linear operator on $\ell^2$
which sends $\{c_n\}$ to 
$\{\frac{1}{\lambda-\xi_n}\cdot c_n\}$.
Since
every closed subset of ${\bf{C}}$
is equal to the closure of a denumerable set of points our
construction  shows that the spectrum of a 
densely defined
operator $\sigma(T)$ can be an arbitrary closed set in
${\bf{C}}$. The  equation   below is due to G. Neumann:


\medskip


\noindent
{\bf{A.3 Neumann's equation.}}
\emph{Assume that
$\sigma(T)$ is not the whole complex plane.
For each pair 
$\lambda\neq\mu$   outside $\sigma(T)$ the operators 
$R_T(\lambda)$ and $R_T(\mu)$ commute
and}
\[
R_T(\mu)R_T(\lambda)=\frac{R_T(\mu)-R_T(\lambda)}{\lambda-\mu}\tag{*}
\]


\noindent
\emph{Proof.}
Notice that
\[
(\mu\cdot E-T)\cdot \frac{R_T(\mu)-R_T(\lambda)} {\lambda-\mu}
=
\]
\[
\frac{E}{\lambda-\mu}-(\mu-\lambda)\cdot\frac{R_T(\lambda)}{\lambda-\mu}-
(\lambda\cdot E-T)\cdot \frac{R_T(\lambda)}{\lambda-\mu}=R_T(\lambda)\tag{i}
\]
Multiplying to the left by
$R_T(\mu)$
gives (*) which  at the same time this shows 
that the resolvent operators commute.
\medskip

\noindent
{\bf{A.4 The position of $\sigma(T)$.}}
Assume that ${\bf{C}}\setminus \sigma(T)$ is non-empty.
We can  write (*) in the form
\[
R_T(\lambda)(E+(\lambda-\mu)R_T(\mu))= R_T(\mu)\tag{1}
\]
Keeping $\mu$ fixed we conclude that
$R_T(\lambda)$ exists if and only if
$E+(\lambda-\mu)R_T(\mu))$ is invertible
which implies that
\[
 \sigma(T)= \{\lambda\,\colon \frac{1}{\mu-\lambda}\in
\sigma(R_T(\mu))\} \tag{A.4.1}
 \]

 
 \noindent
Hence one  recovers $\sigma(T)$ via the spectrum of
any given  resolvent operator. Notice that (A.4.1) holds  even
when
the open component
of $\sigma(T)$ has several connected components.


\medskip

\noindent
{\bf{A.4.2 Example.}}
Suppose that $\mu=i$ and that 
$\sigma(R_T(i))$ is contained in a circle
$\{|\lambda+i/2|=1/2\}$.
If $\lambda\in\sigma(T)$ the inclusion (A.4.1) gives some
$0\leq\theta\leq 2\pi$ such that 
\[
\frac{1}{i-\lambda}=-i/2+ 1/2\cdot e^{i\theta}\implies
1-i\cdot e^{i\theta}=\lambda(e^{i\theta}-i)\implies
\]
\[
\lambda=\frac{2\cdot \cos \theta}{|e^{i\theta}-i|^2}\in {\bf{R}}
\]

\bigskip

\noindent
{\bf{A.4.3 Neumann series.}}
Let     $\lambda_0$  be outside $|sigma(T)$  and
construct the operator valued series
\[
S(\zeta)= R_T(\lambda_0)+ \sum_{n=1}^\infty
(-1)^n\cdot \zeta^n\cdot R_T(\lambda_0)^{n+1}\tag{1}
\]
It is clear that (1)
converges in the Banach space of bounded linear operators when
\[
|\zeta|<\frac{1}{||R_T(\lambda_0)||}\tag{2}
\]
Moreover,  the series expansion (1) gives
\[ 
(\lambda_0+\zeta-T)\cdot S(\zeta)=
(\lambda_0-T)\cdot S(\zeta)+\zeta S(\zeta)=E\tag{23}
\]
Hence
$S(\zeta)=R_T(\lambda_0+\zeta)$ and 
the  locally defined
series in (1) entail the complement of $\sigma(T)$ is open
where $\lambda\mapsto R_T(\lambda)$ is an 
analytic operator-valued  function.
Finally  (*)
in (A.3) and a passage to the limit
as $\mu\to\lambda$ shows that  this analytic function
satisfies the differential equation
\[
\frac{d}{d\lambda}(R_T(\lambda)=-R^2_T(\lambda)\tag{**}
\]








\medskip


\centerline {\bf{A.5. Operators with closed graph.}}
\medskip

\noindent
Let $T$ be a densely defined operator. In the product $X\times X$
we get the graph:
\[ 
\Gamma(T)=\{(x,Tx)\quad\colon x\in\mathcal D(T)\}\tag{A.5.1}
\]
If $\Gamma(T)$  is a closed subspace of $X\times X$ we say that
$T$ is closed.

\medskip

\noindent
{\bf{A.5.1 Exercise.}}
Let $T$ be densely defined and assume
that 
$\sigma(T)$ is not the whole complex plane.
Show that  $T$ is automatically closed.
\medskip

\noindent
In the study of spectra we shall foremost
restrict the attention to 
closed operators.
Assume  that $T$ is densely defined and closed.
Let $\lambda$ be a 
complex number  
such that (i) holds in (A.1) for some
constant $c$ and 
the range of
$\lambda\cdot E-T$ is dense. 
\medskip

\noindent
{\bf{A.5.2 Exercise.}}
Show that the closedness of
$T$ implies that  
the range of $\lambda\cdot E-T$ is equal to $X$ so that 
$R_T(\lambda)$ exists.
A hint is that  if $y\in X$, then the  density gives
a sequence $\{x_n\}$ in $\mathcal D(T)$ such that
$\xi_n=\lambda\cdot x_n-T(x_n)\to y$.
In particular $\{\xi_n\}$ is a Cauchy- sequence
By (i) in
(A.1) we have
\[
||x_n-x_m||\leq c^{-1}\cdot ||\xi_n-\xi_m||
\]
Hence $\{x_n\}$ is a Cauchy sequence and
since
$X$ is a Banach space
there exists $x\in S$ such that $x_n\to x$.
But then $\{(x_n,T(x_n))=
(x_n,\lambda\cdot x_n-\xi_n)$
converges to $(x,\lambda\cdot x-y)$
and since
$T$ is closed it follows that $(x,\lambda\cdot x-y)\in \Gamma(T)$
which gives the requested surjectivity since
\[
T(x)=\lambda\cdot x-y\implies y=(\lambda\cdot E-T)(x)
\]
\medskip


\noindent
{\bf{A.5.3 Adjoints.}}
Let $T$ be densely defined
but not necessarily closed.
In the dual space $X^*$ we get  the subspace
of  vectors $y$ for which   there exists a constant
$C(y)$ such that
\[
|y(Tx)|\leq C(y)\cdot ||x||\quad\colon x\in\mathcal D(T)\tag{i}
\]
When (i) holds the density of $\mathcal D(T)$
gives  a unique vector 
$T^*(y)$ in $X^*$ 
such that
\[
y(Tx)= T^*(y)(x)\quad\colon x\in\mathcal D(T)\tag{ii}
\]
One refers to $T^*$ as the adjoint operator of $T$ whose
domain of definition is denoted by
$\mathcal D(T^*)$.
\medskip

\noindent
{\bf{Exercise.}}
Show that $T^*$ has a closed graph.

\medskip

\noindent
{\bf{A.5.4 Closed extensions.}}
Let $T$ be densely defined
but not closed.
The question arises when
the closure of $\Gamma(T)$ is the graph of a linear operator
$\widehat{T}$ and then 
we refer to
$\widehat{T}$ as a closed extension of $T$.
A sufficient condition for the existence of a close extension goes as follows:

\medskip

\noindent
{\bf{A.5.5 Theorem.}}
\emph{If 
$\mathcal D(T^*)$ is    dense in  $X^*$ then $T$ has a closed extension.}
\medskip

\noindent
\emph{Proof.}
Consider the graph 
 $\Gamma(T)$
and let 
$\{x_n\}$ and $\{\xi_n\}$
be two sequences in $\mathcal D(T)$ which both converge to a point
$p\in X$ while 
$T(x_n)\to y_1$ and $T(\xi_n)\to y_2$ hold 
for some pair $y_1,y_2$. We must rove that $y_1=y_2$.
To achieve this we take some
$x^*\in \mathcal D(T^*)$ which gives
\[
x^*(y_1)= \lim \,x^*(Tx_n)= \lim\,T^*(x^*)(x_n)= T^*(x^*)(p)
\]
In the same way we get $x^*(y_2)=T^*(x^*)(p)$. 
Now the density of $\mathcal D(T^*)$ gives $y_1=y_2$
which proves that
the closure of $\Gamma(T)$ is a graphic subset of $X\times X$
and gives the closed   operator $\widehat{T}$
with 
\[
\Gamma(\widehat{T})=
\overline{\Gamma(T)}
\]


\noindent
{\bf{A.5.6 Exercise.}}
Let $T$ be closed and densely defined.
There may exist several  closed operators $S$
with the property that
\[
\Gamma(T)\subset \Gamma(S)
\]
Show the equaity
\[ 
T^*= S^*
\]
for every closed extension  $S$.
\bigskip

\noindent
{\bf{A.5.7 The case when
$X$ is reflexive.}}
Recall that a Banach space is reflexive if the bi-dual $X^{**}=X$.
Suppose this holds and let $T$ 
be a linear operator where both $\mathcal D(T)$
and  $\mathcal D(T^*)$ are dense.
If $x\in \mathcal D(T)$ it yields $x^{**}|in X^{**}$
and by defintion
\[
x^{**}(T^*(y))=y(Tx)\quad\colon y\in \mathcal D(T^*)
\]
It follows that
$x^{**}\in \mathcal D(T^{**}$ and we conclude that
$T^{**}$ extends $T$ in the sense that
$\Gamma(T)\subset\Gamma(T^{**})$ and from the above $T^{**}$ 
yields a closed extension of $T$,.

 





\bigskip




\centerline{\bf{A.6 Operational calculus.}}
\medskip


\noindent
Let $T$ be densely defined and closed.
To each pair $(\gamma,f)$, where
$\gamma$ is a rectifiable Jordan
arc contained in
${\bf{C}}\setminus \sigma(T)$
and $f\in C^0(\gamma)$, there exists the bounded linear operator
\[ 
T_{(\gamma,f)}=\int_\gamma\, f(z)R_T(z)\, dz\tag{A.6.1}
\]
The integrand has values in the Banach space of bounded
linear operators on $X$ and (A.6.1)  is calculated
by Riemann sums. Next, 
Neumann's equation  (A.3)
entails that
$R_T(z_1)$ and $R_T(z_2)$
commute for all pairs $z_1,z_2$ on $\gamma$.
From this it is clear that
if
$g$ is another function in
 $C^0(\gamma)$,
then  the operators
$T_{f,\gamma}$
and $T_{g,\gamma}$
commute. Moreover, for each $f\in C^0(\gamma)$
the reader may verify that
the closedeness of $T$
implies that
the range of
$T_{f,\gamma}$ is contained in
$\mathcal D(T)$ and 
\[
T_{f,\gamma}\circ T(x)= T\circ T_{f,\gamma}(x)
\quad\colon x\in \mathcal D(T)
\]


 

\medskip

\noindent
Next, let $\Omega$ be an open set of class $\mathcal D(C^1)$, i.e.
$\partial\Omega$ is a finite union of
closed differentiable Jordan curves. 
When
$\partial\Omega\,\cap \sigma(T)=\emptyset$
we construct the line integrals  (A.6.1)
for continuous functions on
the boundary.
Consider the algebra $\mathcal A(\Omega)$
of analytic functions in
$\Omega$ which extend to be continuous on the closure.
Each $f\in \mathcal A(\Omega)$
gives the operator
\[ 
T_f=
\int_{\partial\Omega}\, f(z)R_T(z)\, dz\tag{A.6.2}
\]
\medskip

\noindent
{\bf{A.6.3 Theorem.}}
\emph{The map $f\mapsto T_f$ is an algebra homomorphism from
$\mathcal A(\Omega)$ into a commutative algebra of bounded
linear operators on $X$ whose  image is  a commutative algebra of 
bounded linear operators
denoted by $T(\Omega)$.}

\medskip

\noindent
{\emph{Proof.}}
Let $f,g$ be a pair in $\mathcal A(\Omega)$. We must show the equality
\[
T_{gf}= T_f\circ T_g\tag{*}
\]
To attain this 
we choose  a slightly  smaller open
set $\Omega_*\subset\Omega$ which again is of class $\mathcal D(C^1)$
and each of it  bounding Jordan curve is close to one 
boundary curve in
$\partial\Omega$ and $\Omega\setminus \Omega_*$ does not
intersect $\sigma(T)$.
By Cauchy's theorem we can shift the integration to
$\partial\Omega_*$ and get
\[
T_g=
\int_{\partial\Omega_*}\, g(z)R_T(z_*)\, dz_*\tag{i}
\]
where we use  $z_*$ to indicate that integration takes place
along
$\partial\Omega_*$. Now
\[
T_f\circ T_g=
\iint_{\partial\Omega_*\times\partial\Omega}\, f(z)g(z_*)R_T(z)\circ
R_T(z_*)\, dz_*dz\tag{ii}
\]
Neumann's equation
(*) from  (A.3) entails that  the right hand side in
(ii) becomes
\[
\iint_{\partial\Omega_*\times\partial\Omega}\, \frac{f(z)g(z_*)R_T(z_*)}{z-z_*}
\, dz_*dz+
\iint_{\partial\Omega_*\times\partial\Omega}\, \frac{f(z)g(z_*)R_T(z)}{z-z_*}
\, dz_*dz=A+B
\tag{iii}
\]
\medskip

\noindent
Here $A$ is  evaluated
by first integrating with respect to $z$ and 
Cauchy's theorem gives
\[
f(z_*)=\frac{1}{2\pi i}\cdot 
\iint_{\partial\Omega }\frac{f(z)}{z-z_*}\quad\colon z_*\in\partial\Omega_*
\, dz
\]
It follows that
\[ 
A=\frac{1}{2\pi i}\cdot
\iint_{\partial\Omega_*\times\partial\Omega}\, f(z_*)g(z_*)R_T(z_*)\, dz_*
=T_{fg}
\]
Next, $B$ is evaluated when we first integrate with respect to $z_*$. Here
\[
\iint_{\partial\Omega}\frac{g(z_*)}{z-z_*}\quad\colon z\in\partial\Omega
\]
which entails that $B=0$ and the theorem  follows.
\medskip


\centerline {\bf{A.7 Spectral gap sets.}}
\medskip

\noindent
Let
$K$ be a compact subset
of $\sigma(T)$ 
such that
$\sigma(T)\setminus K$ is a closed
set in ${\bf{C}}$.
This implies that if $V$ is an open  neighborhood of $K$, then
there exists a relatively compact subdomain
$U\in \mathcal D(C^1)$ which contains
$K$ as a compact subset while $\partial U\cap \sigma(T)= \emptyset$.
To every such domain $U$ we can apply Theorem A.6.3.
If $U_*\subset U$ for a pair of such domains
we can restrict functions in
$\mathcal A(U)$ to $U_*$. This
yields an algebra homomorphism
\[
\mathcal T(U)\to \mathcal T(U_*)
\]
Next, denote by
$\mathcal O(K)$ the algebra of germs of analytic functions
on $K$.
So each $f\in \mathcal O(K)$ 
comes from
some analytic function in a domain $U$ as above.
The resulting operator $T_U(f)$ depends on the germ $f$ only.
In fact, this follows because if
$f\in \mathcal A(U)$ and
$U_*\subset U$ is a similar 
$\mathcal D(C^1)$-domain which again contains
$K$, then
Cauchy's vanishing theorem in analytic function theory
applies
to $f(z)R_T(z)$ in $U\setminus \bar U_*$ and entails that
\[
\int_{\partial U_*}\, f(z)R_T(z)\, dz=
\int_{\partial U}\, f(z)R_T(z)\, dz
\]
Hence there exists an algebra homorphism
from $\mathcal O(K)$ into a commutative algebra
of bounded linear operators on $X$
denoted by $\mathcal T(K)$.
The identity in $\mathcal T(K)$
is denoted
by $E_K$ and called 
the spectral projection operator
attached to the compact set $K$ in
$\sigma(T)$. By this construction one has
\[
E_K=\frac{1}{2\pi i}\cdot \int_{\partial U}\, R_T(z)\, dz
\] 
for every open domain $U$ surrounding
$K$ as above.


\medskip

\noindent
{\bf{A.7.1 The operator $T_K$.}} When $K$ is a compact spectral gap set of $T$
we set
\[
 T_K=TE_K
\]
This  is a  bounded linear operator  given
by
\[
\frac{1}{2\pi i}\cdot \int_{\partial U}\, z\cdot R_T(z)\, dz
\] 
where $U$ is a domain as above which contains  $K$.
\medskip

\noindent
{\bf{A.7.2 Theorem.}} \emph{Identify
$T_K$ with a linear  operator on
the subspace $E_K(X)$. Then one has the equality}
\[
\sigma(T_K)=K
\]
\emph{Proof.}
If $\lambda_0$ is outside $K$ we can choose
$U$ so that $\lambda_0$ is outside $\bar U$
and construct the operator
\[
S=\frac{1}{2\pi i}\cdot \int_{\partial U}\, \frac{1}{\lambda_0-z}\cdot R_T(z)\, dz
\]
The operational calculus gives
\[
S(\lambda_0 E_K-T)= E_K
\]
here $E_K$ is the identity operator on
$E_K(X)$ which shows that
$\sigma(T_K)\subset K$.


\bigskip


\noindent
{\bf{A.7.3  Discrete spectra.}}
Consider 
a spectral set  reduced to a singleton set
$\{\lambda_0\}$, i.e.
$\lambda_0$ is an isolated point in
$\sigma(T)$. The associated spectral projection is denoted by
$E_T(\lambda_0)$ and
given by
\[
E_T(\lambda_0)=
\frac{1}{2\pi i}\cdot \int_{|\lambda-\lambda_0|=\epsilon}\,
R_T(\lambda)\, d\lambda
\]
for all sufficiently small $\epsilon$.
Now
$R_T(\lambda)$ is an analytic function defined
in some punctured disc
$\{0<\lambda-\lambda_0|<\delta\}$
with  a Laurent expansion
\[
R_T(\lambda)=\sum_{-\infty}^\infty\, 
(\lambda-\lambda_0)^k\cdot B_k
\]
where $\{B_k\}$ are bounded linear operators
obtained  by residue formulas:
\[
B_k= \frac{1}{2\pi i}\cdot
\int_{|\lambda|=\epsilon}\,  
\frac{R_T(\lambda)}{(\lambda-\lambda_0)^{k+1}}\, d\lambda
\quad\colon\,\epsilon<\delta
\]


\noindent
{\bf{Exercise.}}
Show that
$R_T(\lambda)$ is meromorphic, i.e. 
$B_k=0$ hold when $k<<0$,
if and only if there
exists a constant $C$ and some integer $M\geq 0$ such that
the operator norms satisfy
\[
||R_T(\lambda)||\leq C\cdot |\lambda-\lambda_0)^{-M}
\]
\medskip


\noindent
Suppose now that 
$R_T$ has a pole of some order $M\geq 1$ at $\lambda_0$
which gives a series expansion
\[
R_T(\lambda)=\sum_1^M\,
\frac{B_{-k}}{(\lambda-\lambda_0)^k}+
\sum_0^\infty\, 
(\lambda-\lambda_0)^k\cdot B_k\tag{i}
\]
Residue calculus gives
\[
B_{-1}=E_T(\lambda_0)\tag{ii}
\]
\medskip

\noindent
{\bf{The case of a simple  pole.}}
Suppose that $M=1$. Then it is clear that
Operational calculus gives
\[
\lim_{\epsilon\to 0}
\frac{1}{2\pi i}\cdot \int_{|\lambda-\lambda_0|=\epsilon}\,
(\lambda-\lambda_0)R(\lambda)\, d\lambda=0\tag{iii}
\]
This vanishing and operational calculus entail that
\[
(\lambda_0E-T)E_T(\lambda_0)=0
\]
which means that the ragne of the projection operator
$E_T(\lambda_0)$ is equal to the kernel of
$\lambda_0\cdot E-T$, i.e. the set of eigenvectors $x$ for which
\[
 Tx=\lambda_0\cdot x
\]
\medskip

\noindent
{\bf{The case $M\geq 2$}}.
To begin with residue calculus 
identifies (iii) with $B_2$ and at the same time operational calculus
which aftera reversed sign gives
\[
(\lambda_0E-T)E_T(\lambda_0)=-B_2
\]
Since $E_T(\lambda_0)$ is a projection which commutes with
$T$ it follows that
\[
E_T(\lambda_0)\cdot B_2= B_2\cdot E_T(\lambda_0)=B_2
\]
\medskip

\noindent
{\bf{Exercise.}}
Show that if $M\geq 3$ then
\[
(\lambda_0E-T)^k\cdot E_T(\lambda_0)=(-1)^k\cdot B_{k+1}
\quad\colon 2\leq k\leq M
\]
Consider also the subspaces
\[
\mathcal N_k(\lambda_0)= 
\{ x\colon (\lambda_0E-T)^k(x)=0\}
\quad\colon 1\leq k\leq M
\]
and show that they are non-decreasing and
for every  $k>M$ one has
\[
\mathcal N_M(\lambda_0)=\{ x\colon (\lambda_0E-T)^k(x)=0\}
\]



\medskip

\noindent
{\bf{A.7.4 The case when
$E_T(\lambda_0)$ has a finite dimensional range.}}
Here  the operator $T(\lambda_0)= TE_T(\lambda_0)$
acts on this finite dimensional vector space
which entails that
the nullspaces $\{\mathcal N_k(\lambda_0)\}$ above are
finite dimensional and if $M$ is the order of the pole
one has
\[
(T(\lambda_0)-\lambda_0)^M=0
\]
So $\lambda_0$ is the sole eigenvalue of $T(\lambda_0)$.
Moreover, the finite dimensional range of $E_T(\lambda_0)$
has dimension equal to that of $\mathcal N_M(\lambda_0)$.
\medskip


\noindent
{\bf{Exercise.}}
Recall l that finite dimensional subspaces appear as
direct sum compoinetns. So if
$E_T(\lambda_0)$ is finite dimensional there exists a direct sum decomposition
\[
X=E_T(\lambda_0)(X)\oplus E-E_T(\lambda_0)
\]
where  $V=E-E_T(\lambda_0)$ is a closed subspace of $X$.
Show that $V$ is $T$-invariant 
and  that there exists
some $c>0$ such that
\[
||\lambda_0x-Tx||\geq ||x||\quad x\in V\cap \mathcal D(T)
\]

\bigskip


\centerline {\bf{A.8  Carleman's inequality.}}
\bigskip

\noindent
In many applications one is interested to estimate the operator norm
of resolvent operators.
In this connection a useful result was
proved by 
Carleman in the article
\emph{Zur theorie der linearen Integralgleuchungen}[
Mathematische Zeitschrift. 1921].
Let us remark that the finite dimensional case 
in the theorem below
easily extends to
analogue results
for
operators on infinite-dimensional Hilbert spaces.
See Chapter XI
in [Dunford-Schwartz] for an account and applications of
Carleman's
inequality in   Theorem A.8.1 below. First we recall:
\medskip

\noindent
{\bf{The Hilbert-Schmidt norm.}} 
Let $n$ be a positive integer
and $A=\{a_{ik}\}$ some
$n\times n$-matrix 
whose elements are complex numbers.
Set
\[
||A||= \sqrt{ \sum\sum\, |a_{ik}|^2}
\]


\noindent
where the double sum extends over all pairs
$1\leq i,k\leq n$.
Next, 
for a linear operator $S$
on ${\bf{C}}^n$
its \emph{operator norm} is defined by
\[
\text{Norm}[S]=
\max_x\, ||S(x)||\quad\text{with the maximum taken over unit vectors.}
\] 
Identifying a matrix $A$ with a linear operator on
the Hermitian vector space
${\bf{C}}^n$, it is clear that
\[
\text{Norm}[A]\leq ||A||
\]
Examples show that the inequality in general is strict.
Let
$\lambda_1\ldots,\lambda_n$
be  the unordered $n$-tuple of roots of
$\text{det}(\lambda\cdot E_n-A)$
with  eventual multiple  zeros  repeated.
The union of these roots give the spectrum
$\sigma(A)$.

\bigskip


\noindent
{\bf{A.8.1 Theorem.}}
\emph{For each
non-zero 
 $\lambda$
outside $\sigma(A)$ 
one has the inequality:}
\[ 
\bigl|\prod_{i=1}^{i=n}\, 
\bigl(1-\frac{\lambda_i}{\lambda}\bigr )
e^{\lambda_i/\lambda}\bigr|\cdot \text{Norm}\bigl[R_A(\lambda)\bigr]
\leq |\lambda|\cdot \text{exp}
\bigl(\frac{1}{2}+ \frac{||A||^2}{2\cdot |\lambda|^2}\bigr)
\]
\medskip

\noindent
The proof requires some preliminary results.
First we  recall a wellknown  inequality due to  Hadamard which
goes as follows:
\medskip

\noindent
{\bf {1. Hadamard's inequality.}}
\emph{For every matrix $A$ with a non-zero determinant one has the inequality}
\[
\bigl|\text{det}(A)\bigr|\cdot \text{Norm}(A^{-1})\leq
\frac{||A||^{n-1}}{(n-1)^{n-1)/2}}
\]



\medskip

\noindent
{\bf{2. Traceless matrices.}}
The trace 
of the $n\times n$-matrix $A$ is given
by
\[
\text{Tr}(A)= b_{11}+\ldots+b_{nn}\tag{i}
\]
Recall  that 
$\text{Tr}(A)$ is
equal to the sum of the roots of the characterstic polynomial
$\text{det}(\lambda\cdot E-n-A)$.
In particular the trace of two equivalent matrices are equal.
Carleman used this 
to prove the rewsult below
where we follow a   simplified proof which  was
found later by  Schur.

\medskip

\noindent
{\bf{3. Lemma.}}
\emph{Let $A$ be an $n\times n$-matrix whose trace is zero. Then there
exists a unitary matrix
$U$ such that  the diagonal elements of $U^*AU$ all are zero.}
\medskip


\noindent
\emph{Proof}. Consider
first consider the case $n=2$. 
Since  $A$ can be transformed to an upper tringular matrix
via a unitary transformation
in
${\bf{C}}^2$, 
it suffices to consider the case when the 
traceless $2\times 2$-matrix $A$
has the form
\[ 
A=
\bigl(\,\begin{matrix} a&b\\0&-a
\end{matrix}\,\bigr)
\]
where $a,b$ is a pair of complex numbers.
If $a=0$ the diagonal elements are zero and we can take $U=E_2$ to be the identity.
If $a\neq 0$ we consider a vector $\phi=(1,z)$ in ${\bf{C}}^2$.
Then $A(\phi)$ is the vector $(a+bz,-az)$ and  the inner product becomes:
\[
\langle A(\phi),\phi\rangle=a+bz-a|z|^2\tag{i}
\]
We can write
\[
\frac{b}{a}= re^{i\theta}
\]
where $r>0$ and then (i) is zero if
\[
|z|^2=1+se^{i\theta}\cdot z\tag{ii}
\]
With $z=se^{-i\theta}$
it amounts to find a positive real number $s$ such that
$s^2=1+s$ which clearly exists.
Now we get the vector
\[ 
\phi_*=\frac{1}{1+s^2}(1,se^{-i\theta})
\]
which has unit length and 
\[
\langle A(\phi_*),\phi_*\rangle=0\tag{ii}
\]
Now we can find another unit vector $\psi_*$ so that
$\phi_*,\psi_*$ is an orthonormal base in
${\bf{C}}^2$ and hence there exists a unitary matrix
$U$ such that $U(e_1)=\phi_*$ and $U(e_2)= \psi_*$.
If $B=U^*AB$ the vanishing in (ii) gives $b_{11}=0$. At the same time
the trace is unchanged, i.e. $\text{tr}(B)=0$ holds and hence
we also get
$b_{22}=0$. This means  that  the diagonal elements of $U^*AU$ 
are both zero as required.
\medskip

\noindent{\bf{The case $n\geq 3$}}.
For the
induction
the following is needed:
\medskip

\noindent
\emph{Sublemma.} \emph{For each  $n\geq 3$
there exists some
non-zero vector $\phi\in{\bf{C}}^n$ such that}
\[
\langle A(\phi),\phi\rangle=0\tag{*}
\]

\noindent
\emph{Proof.}
If (*) does not hold we
get the positive number
\[
m_*=\min_\phi\, \bigl|\langle A(\phi),\phi\rangle\bigr|
\]
where the minimum is taken over unit vectors in
${\bf{C}}^n$.
The minimum is achieved by some unit vector $\phi_*$. Let
$\phi_*^\perp$ be its orthonormal complement
and $E$ is the self-adjoint projection from
${\bf{C}}^n$ onto $\phi_*^\perp$.
On the $(n-1)$-dimensional inner product space
$\phi_*^\perp$ we get the linear operator
$B=E A$, i.e. 
\[ 
B(\xi)= E (A(\xi))\quad\colon\quad \xi\in \phi_*^\perp\tag{i}
\]
If $\psi_1,\ldots,\psi_{n-1}$ is an orthonormal basis in
$\phi_*^\perp$ then the $n$-tuple $\phi_*,\psi_1,\ldots,\psi_{n-1}$
is an orthonormal basis in ${\bf{C}}^n$ and since the trace of $A$ is zero we get
\[
0=\langle A(\phi_*),\phi_*\rangle+
\sum_{\nu=1}^{\nu=n-1}\, \langle A(\psi_\nu),\psi_\nu\rangle=
m+\sum_{\nu=1}^{\nu=n-1}\, \langle B(\psi_\nu),\psi_\nu\rangle\tag{ii}
\]
where we used that $E(\psi_\nu)=\psi_\nu$ for each $\nu$
and that $E$ is self-adjoint so that

\[
\langle A(\psi_\nu),\psi_\nu\rangle=
\langle A(\psi_\nu),E(\psi_\nu)\rangle=\langle E(A(\psi_\nu)),\psi_\nu\rangle
=\langle B(\psi_\nu),\psi_\nu\rangle
\]
Now (ii)  gives
\[ 
\text{Tr}(B)=-m
\]
Hence the $(n-1)\times(n-1)$-matrix which represents
$B+\frac{m}{n-1}\cdot E$
has trace zero. By an induction over $n$ we find a unit vector
$\psi\in \phi_*^\perp$
such that
\[
\langle B(\psi_*),\psi_*\rangle=-\frac{m}{n-1}
\]
Finally, since $E$ is self-adjoint we have already seen that
\[
\langle A(\psi_*),\psi_*\rangle=\langle B(\psi_*),\psi_*\rangle\implies
\bigl|\langle A(\psi_*),\psi_*\rangle\bigr |=\bigl|\frac{m}{n-1}\bigr |=
\frac{m_*}{n-1}
\]
Since $n\geq 3$ the last number is $<m_*$ which contradicts the minimal choice 
of $m_*$.
Hence we must have $m_*=0$ which proves lemma 6.5
\bigskip

\noindent
{\emph{Final part of the proof.}
Let $n\geq 3$. The Sublemma  gives unit vector $\phi$
such that
$\langle A(\phi),\phi\rangle=0$.
Consider the hyperplane
$\phi^\perp$ and the operator $B$ from the Sublemma  which now has trace
zero on this $(n-1)$-dimensional space. So by an induction over
$n$
there exists an orthonormal basis $\psi_1,\ldots,\psi_{n-1}$ in
$\phi^\perp$ such that
$\langle B(\psi_\nu),\psi_nu\rangle=0$ for every $\nu$.
Now $\phi,\psi_1,\ldots,\psi_{n-1}$
is an orthonormal basis in ${\bf{C}}^n$ and if $U$
is the unitary matrix which has this $n$-tuple as column vectors
it follows that the diagonal elements of $U^*AU$ all vanish.
This finishes the proof of Lemma 3.


 
\bigskip

\centerline{\bf{Proof Theorem A.8.1}}.



\noindent
Set $B=\lambda^{-1}A$ so that $\sigma(B)=\{ \lambda_i/\lambda\}$ and
$\text{Tr}(B)=\sum\,\frac{\lambda_i}{\lambda}$.
We also have 

\[
||B||^2=\frac{||A||^2||}{|\lambda|^2}\quad\text{and}\quad
\bigl |\lambda\bigr |\cdot \text{Norm}[R_A(\lambda)]=\text{Norm}[(E-B)^{-1}]
\]


\noindent Hence Theorem A.8.1 follows if we prove the inequality
\[
\bigl |e^{\text{Tr}(B)}\bigr|\cdot
\bigl|\prod_{i=1}^{i=n}\, 
\bigl[1-\frac{\lambda}{\lambda_i}\bigr ]
\cdot \text{Norm}
\bigl [E-B)^{-1}\bigr]
\leq \text{exp}\bigl[\frac{1+ ||B||^2}{2}\bigr]\tag{*}
\]


\noindent
To prove (*) we choose an arbitrary integer $N$ such that
$N>\bigl |\text{Tr}(B)\bigr|$ and for each such $N$ we define the linear operator
$B_N$ on the $n+N$-dimensional complex space with points 
denoted by $(x,y)$ with  $y\in{\bf{C}}^N$
as follows:
\[
B_N(x,y)= (Bx\, , \, -\frac{\text{Tr}(B)}{N}\cdot y)\tag{**}
\]


\noindent
The
eigenvalues of the linear operator $E-B_N$ is the union of the $n$-tuple 
$\{1-\frac{\lambda_i}{\lambda}\}$ and 
the $N$-tuple of equal eigenvalues given by 
$1+\frac{\text{Tr}(B)}{N}$.
This gives the determinant formula
\[
\text{det}(E-B_N)=
\bigl(1+\frac{\text{Tr}(B)}{N}\bigr)^N
\cdot \prod_{i=1}^{i=n}\, (1-\frac{\lambda_i}{\lambda}\bigr)\tag{1}
\]
The choice of $N$ implies that (1) is $\neq 0$ so 
the inverse $(E-B_N)^{-1}$ exists.
Moreover, the construction of $B_N$ gives
for any pair $(x,y)$ in ${\bf{C}}^{N+n}$:
\medskip
\[
(E-B_N)^{-1}(x,y)=
\bigl (E-B)^{-1}(x), \frac{y}{
1+\frac{1}{N}\cdot \text{Tr}(B)}\bigr)
\]


\noindent
It follows that 
\[
\text{Norm}\bigl[(E-B)^{-1})\bigr]\leq
\text{Norm}\bigl[
(E-B_N)^{-1}\bigr]\implies
\]
\[
\bigl|\text{det}(E-B_N)\bigr|\cdot \text{Norm}\bigl[(E-B)^{-1})\bigr]\leq
\bigl|\text{det}(E-B_N)\bigr|\cdot
\text{Norm}\bigl[
(E-B_N)^{-1}\bigr]\tag{2}
\]


\noindent 
Hadarmard's inequality
estimates the
hand side in (2) by:
\[
\frac{||E-B_N||^{N+n-1}}{(N+n-1)^{N+n-1)/2}}\tag{3}
\]
\medskip

\noindent
Next, the construction of $B_N$ implies that its trace is zero.
So  by Lemma 3 we can find
an orthonormal basis $\xi_1,\ldots,\xi_{n+N}$
in ${\bf{C}}^{n+N}$ such that
\[ 
\langle B_N(\xi_k),\xi_k\rangle=0\quad\colon 1\leq k\leq n+N
\]


\noindent
Relative to this basis the matrix of $E-B_N$ 
has 1 along the diagonal and the negative of the
elements of $B_N$ elsewhere. It follows that the Hilbert-Schmidt norm
satisfies the equality:
\[
||E-B_N||^2=
N+n+||B_N||^2=N+n+||B||^2+ N^{-1}\cdot
|\text{Tr}(B)|^2\tag{4}
\]

\medskip

\noindent Hence, (1) and the inequalities from (2-3) give:
\medskip

\[
\bigl(1+\frac{\text{Tr}(B)}{N}\bigr)^N
\cdot \prod_{i=1}^{i=n}\, (1-\frac{\lambda_i}{\lambda}\bigr)\cdot
\text{Norm}\bigl[
(E-B)^{-1}\bigr]\leq
\] 

\[
\frac{\bigl(N+n+||B||^2+
N^{-1}\cdot
|\text{Tr}(B)|^2\bigr)^{(N+n-1)(2}}{
\bigl(N+n-1\bigr)^{N+n-1/2}}=
\frac{\bigl(1+\frac{||B||^2}{N+n}+
\frac{|\text{Tr}(B)|^2}{N(N+n)}\bigr)^{(N+n-1)/2}}{
(1-\frac{1}{N+n}\bigr)^{N+n-1/2}}
\]
\bigskip

\noindent
This inequality holds for
arbitrary large $N$.
Passing to the limit as $N\to\infty$  the definition of Neper's constant $e$
give

\[
\lim_{N\to\infty}\, \bigl(1+\frac{\text{Tr}(B)}{N}\bigr)^N=
e^{\text{Tr}(B)}
\]
and the reader may also verify that
the limit of the last term above is equal to
$\text{exp}\bigl[\frac{1+ ||B||^2}{2}\bigr]$ which finishes the proof of
(*) above and hence also of Theorem A.8.1.




\end{document}








\newpage



\centerline{\bf{Hermitian integral operators.}}

\medskip

\noindent
Let us  describe some contructions from Carleman's cited monograph.
Here is the set-up:
Consider the compact set 
$\square=\{(x,y)\colon a\leq x,y\leq b\}$
in ${\bf{R}}^2$.
A Lebesgue measurable   and complex-valued function $K(x,y)$
is Hermitian if
\[
 K(y,x)= \overline{K(x,y)}
\]
We impose the condition that there exists a null set
$\mathcal N$ in $[a,b]$ such that
\[ 
\int_a^b\, |K(x,y)|^2 \, dy<\infty\quad\colon\,  x\in[a,b]\setminus \mathcal N
\]
Lebesgue theory gives
a non-decreasing sequence of
closed subsets $\{E_n\}$ of $[a,b]$ such that
\[
\int_{E_n}\, |K(x,y)|^2 \, dy\leq n\quad\colon x\in E_n\tag{1}
\]
To each $n$ we define the truncated kernel $K_n(x,y)$ which is equal to
$K$ on $E_n\times E_n$ and otherwise zero.
It follows that
\[
\int_a^b\, |K_n(x,y)|^2 \, dy\leq n\quad\colon a\leq x\leq b
\]
which  entails that
\[
\iint_\square\, |K_n(x,y)|^2\, dxdy <\infty\tag{2}
\]
Hence each $K_n$ yields a Hilbert-Schmidt operator on
the Hilbert space
$L^2[a,b]$ and is therefore compact.
Since $K_n$ also is Hermitian the eigenvalues are real.
Keeping $n$ fixed
one seeks all real numbers
$\lambda\neq 0$ for which there exists a non-zero
$\phi\in L^2[a,b]$ such that
\[
\phi(x)=\lambda\cdot \int_a^b\, K_n(x,y)\cdot \phi(y)\, dy\tag{3}
\]
At each eigenvalue
which can be  positive or negative,
the eigenspace may have 
dimension  $e\geq 2$, but it is always finite dimensional.
The Gram-Schmidt construction gives
an orthonormal family of eigenfunctions
$\{\phi_{\lambda_k}\}$ with  eigenvalues
$\{\lambda_k\}$, where  eigenspaces of
dimension $e\geq 2$ means that $\lambda_k$ is repeated $e$ times.
Expanding an arbitrary
function $h\in L^2[a,b]$
with respect to the orthormal eigenfunctions
and an eventual term which is $\perp$ to all
eigenfunctions with non-zero eigenvalues, 
Bessel's inequality gives
\[
\sum\,
\bigl|\iint_\square\, \phi_{\lambda_k}(x)\cdot h(x)\, dx \bigr|^2
\leq \int_a^b\, |h(x)|^2\, dx\tag{4}
\]
Following Hilbert one associates a spectral function
defined for $\lambda> 0$  by
\[
\theta_n(x,y;\lambda)=\sum_{0<\lambda_k<\lambda} \, \phi_{\lambda_k}(x)\cdot \overline{\phi_{\lambda_k}(y)}
\]
\[
\theta_n(x,y;-\lambda)=\sum_{-\lambda <\lambda_k<0} \, \phi_{\lambda_k}(x)\cdot \overline{\phi_{\lambda_k}(y)}
\] 
and finally 
$\theta_n(x,y;0)=0$.
Next, each $h\in L^2[a,b]$ has  an expansion
\[
h=\sum c_k\cdot \phi_{\lambda_k}
\]
With $\lambda>0$ one has 
\[
\iint_\square\, \theta_n(x,y;\lambda)\cdot h(x)\cdot
 \overline{h(y)}\, dxdy=\sum_{0<\lambda_k<\lambda}\, |c_k|^2
\]
\[
\iint_\square\, \theta_n(x,y;\lambda)\cdot h(x)\cdot
 \overline{h(y)}\, dxdy=\sum_{-\lambda <\lambda_k<0}\, |c_k|^2
\]
Moreover, keeping $h$ fixed,
weak star convergence applied to a conutable dense set
of $h$-functions gives  a subsequence $n_1<n_2<\ldots$ 
such that
there exists a limit 
\[ 
\lim_{k\to \infty}\, \iint_\square\, \theta_{n_k}(x,y;\lambda)\cdot h(x)\cdot
 \overline{h(y)}\, dxdy\tag{5}
 \]
 for each $h\in L^2[a,b]$ and every real $\lambda$.
Next, the construction of the truncated kernels give
a limit function defined on $E_*\times E_*$ by
\[
 \theta(x,y;\lambda)=\lim_{k\to \infty}\, \theta_{n_k}(x,y;\lambda)\tag{6}
\]
\medskip

\noindent
{\bf{When is 
$\theta(x,y;\lambda)$ a spectral function for $K$.}}
So far the constructions were  straighforward.
There remains to analyze if
the $\theta$-function in (6)
yields an adapted spectral resolution of
the densely defined
integral operator attached to $K(x,y)$ where  the limit in (5) is unconstrained.
The following sufficiency
criterion for this to be true goes as follows:
\medskip

\noindent
{\bf{Theorem.}}
\emph{The limit in (5) exists   as $n\to +\infty$ and
the $\theta$-function yields a spectral resolution of
the densely defined $K$-operator  under the condition that
the two equations below do not have non-zero $L^2$-solutions:}
\[
\phi(x)=
 i\cdot \int_a^b\, K(x,y)\phi(y)\, dy
\quad \colon \psi(x)=
 i\cdot \int_a^b\, K(y,x)\psi(y)\, dy\tag{*}
\] 
\medskip

\noindent
{\bf{Remark.}}
More generally, Carleman proved the existence of an adapted
spectral resolution if
the two equations in (*)  both give finite dimensional spaces with
equal dimension.
We refrain  from giving   details of the proof but
refer to
[Carleman] and 
the expositary 
article 
\emph{La theorie des equations intégrales singuliérs} [
Ann. l'Institut Poincaré Vol. 1 (1931)].
In § xx we establish an "abstract version" of the theorem which
therefore includes a proof of the sufficiency result above.























\end{document}




\newpage



\centerline {\bf{Lectures 4-9}}.
\bigskip

\noindent
Some of the topics  
are described in
§ B-E below where
logarithmic potentials and
the Cauchy transform play a
central role.  Here
"pure analysis" intervenes with more geometric constructions
while harmonic and subharmonic functions
are studied. Let us describe   a typical result which will
be covered during lecture 6-9:
\medskip


\noindent
{\bf{A  theorem by Nevanlinna}}. 
Let $\Omega$ be a connected and bounded
domain in ${\bf{C}}$
whose boundary consists of $p$ many pairwise disjoint and closed
Jordan curves
$\Gamma_1,\ldots,\Gamma_p$.
On each $\Gamma_\nu$
we consider a function $\phi_\nu$
which takes the value +1 on a finite
union of intervals and  zero on the complementary intervals.
So unless $\phi$ happens to be constant on a single
curve  $\Gamma_\nu$
we get jumps 
at common boundary points of  intervals where $\phi_\nu$ is constant.
The number of such points is  an even integer denoted by $2\cdot k_\nu$
where
$k_\nu=0$ means that
$\phi_\nu$ is identically 1 or 0 on $\Gamma_\nu$.
Solving  Dirichlet's problem we get a harmonic function $\omega(z)$
whose boundary function is  $\phi$ and in $\Omega$ there exists the analytic function
\[ 
g(z)= \frac{\partial \omega}{\partial x}
-i\cdot \frac{\partial \omega}{\partial y}
\]

\medskip

\noindent
{\bf{Theorem.}} \emph{The number of zeros of $g$ counted
with multiplicities is equal to}
\[
k_1+\ldots+k_p+p-2
\]
Nevanlinna's  proof gives an instructive lesson how
the argument principle intervenes with level sets
of harmonic functions.

\bigskip




\centerline{\emph{A. The Laplace operator and Greens functions.}}

\bigskip


\noindent
Here is the set-up for
Lecture 4.
Let
$\Omega$ be a bounded and connected domain in
${\bf{C}}$
whose boundary consists of a finite number of
pairwise disjoint and differentiable closed Jordan curves.
With $p\in\Omega$
kept fixed we
consider the continuous function on
$\partial\Omega$ defined by
\[ 
q\mapsto  \log \frac{1}{|p-q|}
\]
Solving
the Dirichlet problem
we get the harmonic function
$u_p(q)$ in $\Omega$ where
\[
u_p(q)=\log \frac{1}{|p-q|}\,\colon\, q\in\partial\Omega
\]
Greens' function is defined for pairs $p\neq q$ in
$\Omega\times\Omega$ 
by
\[ 
G(p,q)= \log\,\frac{1}{|p-q|}-u_p(q)\tag{1}
\]
It is wellknown that $G$ is non-negative in
$\Omega\times\Omega$ and symmetric, i.e.
$G(p,q)=G(q,p)$.
Next, let $f\in L^2(\Omega)$, i.e  $f$ is complex-valued and square integrable over
$\Omega$. Set
\[ 
\mathcal G_f(p)=\frac{1}{2\pi}\cdot \int_\Omega\, G(p,q)\cdot f(q)\, dq\tag{2}
\]
Since
\[
 \iint_{\Omega\times \Omega}\, |G(p,q)|^2\, dpdq<\infty
\]
the linear operator  
$f\mapsto \mathcal G_f$ is 
of the Hilbert-Schmidt type and
therefore  compact  on the Hilbert space
$L^2(\Omega)$. Moreover,
since 
$\frac{1}{2\pi}\cdot \log\sqrt{x^2+y^2}$ is
a fundamental solution to the Laplace operator one has:

\medskip

\noindent{\bf{A.1  Theorem.}}
\emph{For each $f\in L^2(\Omega)$
the Laplacian of $\mathcal G_f$
taken in the distribution sense belongs to
$L^2(\Omega)$ and one has the equality}
\[ 
\Delta(\mathcal G_f)=-f\tag{*}
\] 


\noindent
Using this one proves that
there
exists an orthonormal basis $\{\phi_n\}$ in $L^2(\Omega)$ and a
non-decreasing sequence of positive real numbers
$\{\lambda_n\}$ such that
\[ 
\Delta(\phi_n)+\lambda_n\cdot \phi_n=0\quad\colon n=1,2,\ldots\tag{i}
\]
holds in $\Omega$ where each $\phi_n$
extends to a continuous function on the closure with
boundary value zero on $\partial\Omega$.
Let us  remark that (i) means that
\[
\mathcal G(\phi_n)= \frac{1}{\lambda_n}\, \cdot \phi_n\tag{ii}
\]
So
$\{\lambda_n^{-1}\}$
are  the eigenvalues of the compact operator $\mathcal G$ whose sole cluster
point is $\lambda=0$.
Eigenvalues whose eigenspaces have
dimension $e>1$ are repeated $e$ times.
With these notations the result below 
was proved by Carleman in a lecture during the Scandinavian Congress at
Stockholm in 1934:
\medskip

\noindent
{\bf{A.2 Theorem.}}
\emph{For each point $p\in\Omega$ one has the limit formula}
\[
\lim_{n\to \infty}\, \frac{1}{\lambda_n}\cdot
\sum_{k=1}^{k=n}\, \phi_k(p)^2=
 \frac{1}{4\pi}\tag{*}
 \]
 \medskip
 
 
 \noindent
{\bf{Remark}}. Notice that (*)
holds for
every domain $\Omega$ as above, i.e. independent if its
degree  of   connectivity.
Similar asymptotic formulas hold for
derivatives of the $\phi$-functions. One has for example
\[
\lim_{n\to \infty}\, \frac{1}{\lambda_n}\cdot
\sum_{k=1}^{k=n}\, \frac{\partial \phi_k}{\partial x}(p)^2=
 \frac{1}{16\pi^2}\tag{**}
 \]
 The proof relies heavily upon analytic function theory
 where one  
 considers the Dirichlet series:
\[ 
\Phi_p(s)=\sum _{n=1}^\infty \, \frac{\phi_n(p)^2}{\lambda_n^s}\tag{0.4.3}
\]
The major result to be proved in  Lecture 4 goes as follows:
\medskip

\noindent
{\bf{A.3 Theorem.}}
\emph{There exists an entire function
$\Psi_p(s)$ such that}
\[
\Phi_p(s)=\Psi_p(s)+\frac{1}{4\pi(s-1)}
\]
\medskip

\noindent
Carleman's   proof of Theorem A.3 is very instructive.
It relies upon a change of complex contour integrals
similar to those employed  by Riemann in his  studies about
the $\zeta$-function, 
together with a  sharp 
asymptotic estimates
of 
Greens' kernel functions  $G(x;y;-\kappa)$ when $\kappa\to +\infty $.
The fact that
Theorem A.3  gives Theorem A.2  follows via 
a result  from  N. Wiener's   article
\emph{Tauberian theorem} [Annals of Math.1932
which asserts that if $\{\lambda_n\}$ is a non-decreasing sequence of
positive numbers  tending to infinity, and
$\{a_n\}$ are non-negative real numbers such that
there exists the limit
\[ 
\lim_{s\to 1}\,(s-1)\cdot \sum\, \frac{a_n}{\lambda_n^s}=A
\] 
then 
\[
\lim_{n\to \infty}\,\lambda_n^{-1}\cdot
\sum_{k=1}^{k=n}\, a_k=A
\]
Time will prevent me from giving detailed proofs of
this Tauberian theorem but details appear in
my notes devoted to analytic function theory
and Wiener's result could be an example for an
"examination lecture".




















\newpage

\centerline{\emph{ A.4 . The heat equation.}}

\medskip


\noindent
In probability theory  one considers stochastic processes in
continuous time of the Markov type. The time dependent distributions 
densitites appear as solutions to
parabolic PDE-equations.
An example is the diffusion process expressed by the stochastic differential equation
\[ 
dX_t=b(X(t),t)\cdot dW
\]
where $dW$ is a "white noise"
which for small $dt$ is a normally distributed variable with
variance
$\sqrt{dt}$ and independent of the present stage $X(t)$,
i.e. one has independent increments.
It means that
the random variabe $X(t+dt)$ is infinitesmally equal to the sum of $X(t)$ and
$b(X(t),t)\cdot W(\sqrt{dt})$ where $X(t)$ and $W(\sqrt{dt})$ are independent 
random variables.
Taking the Fourier transform of  the distribution function
$f(x,t)$ of $X(t)$ we get
\[
\widehat{f}(\xi;t+dt)=\frac{1}{\sqrt{2\pi}\cdot \sqrt{dt}}
\cdot \iint\, e^{-i\xi(x+b(x,t)u})
\cdot f(x;t)\cdot e^{-u^2/2dt}\, dxdu+o(dt)
\]
where the remainder is small ordo of $dt$.
The variable substitution $u\mapsto \sqrt{dt}\cdot s$
identifies the double integral above with
\[
\frac{1}{\sqrt{2\pi}}
\cdot \iint\, e^{-i\xi(x+b(x,t)\sqrt{dt}\cdot s})
\cdot f(x;t)\cdot e^{-s^2/2}\, dxds
\]
A Taylor expansion of the complex exponential function
$\zeta\to e^{i\zeta}$ at $\zeta=0$ gives
\[
\lim_{dt\to 0}\,
\frac{\widehat{f}(\xi;t+dt). \widehat{f}(\xi,t)}{dt}=
-b(x,t)^2/2\cdot 
\int\, \xi^2\cdot \widehat{f}(\xi;t)\, d\xi
\]
Fourier's inversion formula entails that
$f(x,t)$ satisfies the PDE
\[
\frac{\partial f}{\partial t}=\frac{
b(x,t)^2}{2}\cdot \partial_x^2(f)\tag{*}
\]
At time $t=0$ we suppose that $X_0$ has a given distribution function
$f_0(x)$ which therefore gives
the initial condition
\[ 
f(x;0)= f_0(x)
\]
where one from  assumes that
$X_0$ has a finite variance, i.e.
\[ 
\int\, x^2\cdot f_0(x)\ dx<\infty
\]



\noindent
The PDE in (*) is 
parabolic and basic results for such
equations 
were established by Gevrey, Hadamard and Holmgren
around 1900. 
The prototype  is the equation
\[
\frac{\partial u}{\partial y}=
\frac{\partial^2 u}{\partial x^2}
\]
defined in a strip domain
$B=\{-\infty < x<\infty\}\times \{-A<y<A\}$.
The favourable  case occurs if
there exists a constant $C$ such that
\[ 
|u(x,y)|\leq C\cdot e^{x^2}\tag{**}
\]
Then $u(x,y)$ is determined by
its
restriction $x\mapsto u(x,a)$ for every
fixed
$-A<a<A$ by the integral formula
\[ 
u(x,y)=
\frac{1}{2\sqrt{\pi (y-a)}}\int_{-\infty}^\infty\,
u(\xi,a)\cdot U(x-\xi,y-a)\, d\xi\quad\colon a<y<A\tag{i}
\]
where $U(x,y)$ is the function which is zero when $y\leq 0$ and 
\[
U(x,y)= e^{-x^2/4y}\,\colon\, y>0
\]
When (**) fails one cannot represent $u$ in the trivial fashion above
but the question remains if uniqueness hold under a less restrictive condition than
(**). A positive answer was given
by
Erik Holmgren in the 
article \emph{Sur les solution quasi-analytique d l'équation de chaleur}
[Arkiv för matematik. 1924] where he proved
that the solution $u$ is uniquely determined by
a restriction to some $\{y=a\}$ if there exists a constant $k\geq 0$
such that
\[
|u(x,y]|\leq e^{kx^2\cdot \log(e+|x|)}\quad\colon\, (x,y)\in B\tag{***}
\]

\medskip

\noindent
Leter work by Täcklund demonstrated that
Holmgren's uniqueness theorem is essentially sharp.
A
suggestion for an "examination lecture"
is to expose 
constructions by Beurling who considered
solutions satisfying
\[
u(x,y)|\leq e^{\epsilon(|x|)\cdot x^2\cdot \log(e+|x|)}\tag{****}
\]
where    $\epsilon(r)$  tends to zero as
$r\to+\infty$. 
When (****) holds
Beurling  found   an integral kernel $U^*$
which serves as a substitute for the standard kernel $U$  in (i).
The  construction of $U_*$ gives
an
instructive  lesson 
about the role of analytic functions
in PDE-theory.


\bigskip




\centerline
{\emph{B. Subharmonic configurations }}
\medskip


\noindent
Let $\mu$ be a Riesz measure
in ${\bf{C}}$ supported 
by a compact null set. Assume that
its Cauchy transform
\[
\widehat{\mu}(z)= \int \frac{d\mu(\zeta)}{z-\zeta}
\]
satisfies an algebraic equation
$p_m(z)\cdot \widehat{\mu}^m(z)+\ldots
p_1(z)\cdot \widehat{\mu}(z)+p_0(z)=0$
in
${\bf{C}}\setminus \text{Supp}(\mu)$
where $\{p_\nu(z)\}$ are polynomials.
In a joint article by
J. Borcea, R. Bögvad and myself, it is proved
that the support of $\mu$ is a finite union of
real-analytic compact Jordan arcs.
The proof relies upon a study
of piecewise harmonic subharmonic functions.
For example, given a finite family of harmonic functions
$h_1,\ldots,h_k$
in some open connected domain $\Omega$
there exists the  subharmonic function
$u$ defined as the maximum of this $k$-tuple.
Conversely, suppose that $u$ is subharmonic in 
$\Omega$ where its 
Riesz measure is supported by some  null-set while
the restriction of $u$ to every connected component of
$\Omega\setminus \text{Supp}(\Delta(u)$
is equal to one of the given $h$-functions.
An example discovered by Borcea and Bögvad
shows that this in general need not imply that
$u=\max(h_1,\ldots,h_k)$.
However, one can prove
that this equality holds under the condition
that the $k$-tuple of gradient vectors of
the $h$-functions are extreme points in the convex
set they generate in
${\bf{C}}$.
When this holds
one  says that
$h_1,\ldots,h_k$ admit a unique subharmonic configuration.
Without this condition on the gradient vectors
one seeks the family of all subharmonic configurations, i.e.
the set of all subharmonic functions $u$ in
$\Omega$ for which
$\text{Supp}(\Delta u)$ is a null set and
the restriction of $u$ to every
connected component of
$\Omega\setminus \text{Supp}(\Delta u)$ 
is equal to one of the given harmonic $h$-functions.
This leads to some open and problems and it is
also natural to try to extend this study to
higher dimensions where
one
instead consider
finite families of pluirsubharmonic functions and
seek there plurisubharminic configurations.
This will
be a topic during the second half of the course.







\bigskip








\centerline {\emph{C.  Zero sets of subharmonic functions.}}

\medskip


\noindent
Let  $\Omega$ in ${\bf{C}}$ be a bounded open set and
denote by
$\text{SH}_0(\Omega)$
the set of  subharmonic functions in   $\Omega$
whose Laplacian is a Riesz measure supported by a 
compact null set. Every such function $u$ is locally the sum of a harmonic function
and a
logarithmic potential 
\[
u(z)=\frac{1}{2\pi}\cdot \int\,\log|z-\zeta|\cdot d\mu(\zeta)
\]
where $\mu$ is a non-negative Riesz measure with compact support.
This entails
that 
the distribution derivatives  $\partial u/\partial x$
and
$\partial u/\partial y$  belong to
$L^1_{\text{loc}}(\Omega)$.
Before 
the theorem below is announced
we need  a geometric construction.
If $U$ is a bounded  open subset of $\Omega$ and 
$\zeta\in U$ we denote by 
$s(\zeta)>0$ the largest positive number such that
the line segment
\[
\ell_\zeta=
\{ \zeta+x\,\colon \, 0\leq x<s(\zeta)\}\subset \Omega
\]
Put 
\[ 
\mathfrak{s}(U)=\bigcup_{\zeta\in U}\, 
\ell_\zeta\tag{*}
\]
This yields an open  set called
the
forward star domain of $U$.
\bigskip

\noindent{\bf{Theorem.}}
\emph{Let 
$g\in\text{SH}_0(\Omega)$ and put
$K=\text{Supp}(\Delta(g))$. Let  $U$ be an open subset of
$\Omega\setminus K$  with the property that
$g=0$ in  $U$  and}
\[
\partial g/\partial x(z)<0,\quad\colon
z\in \Omega
\setminus (K\cup U)
\]
\emph{Then $g=0$ in $\mathfrak{s}(U)$.}
\medskip

\noindent
This result is a slight extension of a theorem  which appears in
a joint article by T. Bergquist and H. Rullgård
where it was  used
to prove that if $Q(z)$ is a monic polynomial of
some
degeee
$n$, then there exists a unique compact and connected
null-set   $\Gamma$ in
${\bf{C}}$ which contains the zeros of $Q$
and 
the extended complex plane minus $\Gamma$ is connected.
Moreover, and this is the crucial point, 
there exists a probability  measure $\mu$ supported by
$\Gamma$
such that
the Cauchy transform
\[
\widehat{\mu}(z)=
\int \, \frac{d\mu(\zeta)}{z-\zeta}
\]
satisfies the equation
\[ 
\widehat{\mu}(z)^n=
Q(z)^{-1}\quad\colon z\in {\bf{C}}\setminus |\Gamma
\]



\noindent
{\emph{Another Example.}}
Consider an algebraic equation
\[
 y^2=\frac{p(x)}{q(x)}\tag{1.1.4}
\]
where $q$ is a monic polynomial 
with simple zeros of some
degree $m+2$ and $p$ is monic with degree $m$
and the polynomials $p$ and $q$ have no common zero.
On the attached compact Riemann surface $X$
we get a local branch of $y$ at a point $p^*$ above $x=\infty$ whose series
expansion starts with $x^{-1}$. 
\medskip

\noindent
{\emph{ Conjecture}}
\emph{There exists a unique tree $\Gamma$ in the complex $z$-plane
such that the 
single-valued branch of $\sqrt{\frac{p}{q}}$
in ${\bf{P}}^1\setminus\Gamma$
with the Laurent expansion as above   at $z=\infty$
is equal to the Cauchy transform of a probability measure
supported by $\Gamma$}.
\medskip

\noindent
{\emph{Remark.}}
Affirmative answers to this conjecture 
have been established in special cases
by J. Borcea and
B. Shapiro and applied to  study
asymptotic distributions of roots to Lamé equations.
To settle
the conjecture 
amounts to contruct a specific
branch-cut on the associated hyperelliptic curve. For an eventual  proof is its tempting
to  employ potential-theoretic methods
where  results by Beurling might be
useful, i.e.
employ  subharmonic principles to settle a free boundary value problem
where one  minimizes certain energy integrals.
To achieve eventual  solutions may be "too hard" but at least 
one may settle 
specific cases which might be a reasonable and attractive subject
for   Phd-students interested in this kind of analysis.
Let us remark that
the proposed problem amounts to construct special triangulations on
compact Riemann surfaces $X$ whose
(eventual) solutions rely upon interesting  variational problems
where the Riesz mass of certain subharmonic functions
are minimized.




\bigskip


\centerline{\emph{D. The Riemann-Schwarz inequality.}}
\medskip

\noindent
Let $X$ be a non-compact   1-dimensional complex manifold
and $\sigma$ a
hyperbolic metric, i.e. in a local chart
$(U,z)$ the metric is
$e^{w(z)}\cdot d|z|$ where
$w$ is subharmonic in $U$.
To each pair of points $p,q$ in $X$
one has the  family $\mathcal C(p,q)$ of
rectifiable curves in $X$ with end-points at $p$ and $q$.
The Riemann-Schwarz inequality asserts that
for every pair
$\gamma_1,\gamma_2$ in 
$\mathcal C(p,q)$ and
each point $\xi\in\gamma_1$
there exists a curve 
$\alpha\in\mathcal C(p,q)$ and a curve $\beta$ with
end-points at $\xi$ and some point $\eta\in\gamma_2$ such that
\[
\sigma(\alpha)^2+\sigma (\beta )^2\leq
\frac{1}{2}\bigr (\sigma(\gamma_1)^2+\sigma(\gamma_2)^2\,\bigl )\tag{*}
\]
Moreover, the inequality (*) is strict with the exception for
a special rhombic situation when $X$ is the unit disc.
This inequality   gives
the existence of unique geodesic  curves
on $X$ with respect to the $\sigma$-metric.
The proof 
relies upon the uniformisation theorem for
Riemann surfaces and   calculations based 
upon  geometric properties  of Möbius transforms in the unit disc.

\newpage

\centerline{\emph{E. Special topics about subharmonic functions.}}

\bigskip





\noindent {\emph{E.1. Largest subharmonic minorants.}}
Let $F$ be a real-valued function with values in
$[1,+\infty]$  defined in a bounded  open set
$\Omega$ in ${\bf{C}}$.
The function is assumed to be
upper semi-continuous, i.e. the sets $\{F<a\}$ are open for
every $1\leq a\leq +\infty$. Notice that
$F(z)=+\infty$ is allowed
on some non-empty and closed subset
of
$\Omega$.
One associates Sjöberg's minorant function
\[
\mathcal S_F(z)= \max_u\, u(z)
\] 
where
the maximum is taken over all subharmonic functions 
$u$ in $\Omega$ which are everywhere $\leq F$.
In general 
$\mathcal S_F(z)$ fails
to be subharmonic but a result due to Beurling
gives the following sufficient condition in order
that
$\mathcal S_F$ is subharmonic. Namely, 
subharmonicity holds if there
to every relatively compact set $\Omega_0$ of
$\Omega$ exists some $\epsilon>0$ such that
\[
\iint _{\Omega_0}\,[\log F(z)]^{1+\epsilon}\, dxdy<\infty
\]
\medskip

\noindent 
Beurling's  proof teaches a good lesson about
estimates of mass distributions of
$\Delta(u)$ for subharmonic functions which
also will appear 
in the second half of the lectures when 
plurisubharmonic functions are studied.
\medskip

\noindent 
{\emph{E.2. Dirichlet
integrals.}}
Let $h(z)$ be a harmonic function in
the open unit disc
$D=\{|z|<1\}$ with a finite Dirichlet integral
\[
D(h)=\sqrt{\iint_D\, (h_x^2+h_y^2)\, dxdy}
\]
Using polar coordinates $(r,\theta)$ 
we set
\[
M_h(r e^{i\theta})= \int_0^r\, |\frac{\partial h(se^{i\theta})}{\partial s}|\, ds
\quad\colon 
M_h^*(\theta)=
\lim_{r\to 1}\, M_h(r e^{i\theta})
\]
Let $h^*$ be the harmonic extension to $D$ of the boundary value function 
$M^*_h$. With these notations a result due to Beurling
asserts that
\[
D(h^*)\leq D(h)
\]
Just as in E.1, Beurling's ingenious  proof   
offers  an instructive
lesson about
subharmonic functions.


\bigskip


\noindent{\emph{E.3 Carleman's differential inequality.}}
Let $\Omega$ be a connected open set in ${\bf{C}}$ 
with the property that for
every
$x>0$
the
intersection $S_ x$ between
$\Omega$ and a  vertical line  $\{\mathfrak{Re}\, z=x\}$
is a non-empty
bounded set
on the real $y$-line.
Each $S_x$  is the disjoint union
of open
intervals $\{(a_\nu,b_\nu)\}$ and we set
\[ 
\ell(x)=\max_ \nu \,(b_\nu-a_\nu)\tag{*}
\]

\medskip


\noindent
Next, let
$u(x,y)$ be an arbitrary  positive harmonic   function
in $\Omega$ which 
extends to a continuous function on
the closure $\bar\Omega$  where $u=0$ on $\partial\Omega$. 
Notice that this class can be non-empty since
$\Omega$ is unbounded.
A typical case is that $\Omega$
is a sector bordered by a pair of disjoint simple curves
which both issue from the origin and tend to inifinity.
Set
\[ 
\psi(x)=\log\, (\int_{S_x}\,u^2(x,y)\cdot dy)\tag{1}
\]



\noindent
With these notations the following result was proved by Carleman in 1933.
\medskip


\noindent
{\bf {Theorem.}}
\emph{Given a pair $\Omega$ and $u$ as above there exists a constant
$C\geq 0$ such that}
\[
2\pi\cdot\int_0^x\, \frac{x-s}{\ell(s)}\cdot ds\leq
\int_0^x\,\psi(s)\cdot ds+\psi(x)+Cx\quad\colon x>0
\]

\medskip


\noindent
The proof is instructive since it teaches how to use
subharmonic majorisations and
suitable $L^2$-inequalities of Wirtinger.


\bigskip


\noindent
\emph{E.4 Weighted Runge approximations.}
Put  $z=x+iy$ and 
$\square=\{-a<x<a\}\times \{-b<y<b\}$.
This rectangle  contains
$\square_+= \{-a<x<a\}\times \{0<y<b\}$ and  the lower part
$\square_-=\square\cap \{y<0\}$.
Let 
$\phi(z)$ be an analytic function
in $\square_+$ which extends continuously to its closure.
A classic result, known as Runge's theorem,
entails that for every $\delta>0$ there exists
a sequence of polynomials $\{P_n(z)$
such that the maximum norms $|P_n-\phi|_{\square_+}$ tend to zero
and at the same time
the maximum norms of $|P_n|$ taken over
the rectangle
$\square(-\delta)=\{-a<x<a\}\times \{-b<y<-\delta\}$ tend to zero.
While such an approximation takes place
the maximum norms
of $\{P_n\}$ taken over $\square$ cannot remain uniformly bounded
when $\delta\to 0$.
For if this  holds, another classic  result, known as Montel's theorem,
implies that there exists
a sequence of polynomials which converge
to an analytic function $g$ in $\square$, where this convergence is
uniform over compact subsets of $\square$.
Here $g$ is   zero in
$\square(-\delta)$ which by analyticity entails that
$g$ is identically zero in $\square$. At the same time
$g=\phi$ in $\square_+$
which contradicts the assumption that
$\phi$ is not identically zero.

\medskip

\noindent
To compensate for this one   introduces the
family
$\mathcal W$
of real-valued continuous
functions $\omega(y)$
which are
even  and positive $y\neq 0$, and 
decrease to zero  as $y$ approaches zero
through positive or negative values.
An example is $\omega(y)=y^2$ and
another is 
$\omega(y)= e^{-1/y^2}$
which decreases quite rapidly to zero with
$y$.
With $\phi(z)$ given as above
and $\omega\in\mathcal W$ we say that
a weighted Runge approximation holds if there
exists a sequence of polynomials $\{P_n(z)\}$
such that
\[
\lim_{n\to\infty}\,
||\omega(y)(P_n(z)-\phi(z)||_{\square_+}+
||\omega(y)(P_n(z)||_{\square_-}=0\tag{*}
\]
It turns out that
such a weighted approximation exists
if
$\omega(y)$ tends to zero sufficiently fast.
The following
was established  by
Beurling
ín the article  \emph{Analytic continuations along a linear boundary:
Acta mathematica 1953}.

\medskip

\noindent
{\bf{E.4.1 Theorem}}
\emph{The weighted Runge approximation (*) exists
if and only if}
\[
\int_0^b\, \log\log \frac{1}{\omega(y)}\, dy=+\infty\tag{*}
\]
The proof gives an instructive lesson how to employ
subharmonic estimates.

\bigskip


\centerline{\bf{Several complex variables.}}


\bigskip

\noindent
Complex analysis in several variables is  more 
involved  compared with the 1-dimensional case.
However, it is tempting to try to extend 1-dimensinal results to
higher dimensions.
A basic result of this nature 
due to Deval and Sibony goes as follows:
\medskip

\noindent
{\emph{Jensen's formula in dimension $n\geq 2$}.
Let $\Omega$
be  a bounded and  strictly pseudo-convex domain
in ${\bf{C}}^n$ with smooth boundary.
When  $z_0 \in\Omega$ a probability measure
$\mu$ supported by $\partial\Omega$ is called a Poisson-Jensen measure
with respect to $z_0$  if
\[ 
f(z_ 0)=\int_{\partial\Omega}\, f(z)\cdot d\mu(z)
\] 
hold for all analytic functions $f$ in $\Omega$ which extend to be continuous 
on the closure  $\bar\Omega$.
Given the pair $(z_ 0,\mu)$ 
the \emph{defect of value} taken at $z_ 0$ by 
pluri-subharmonic functions $u(z)$ of class $C^2$
is expressed by the difference
\[ 
\text{def}(u)=\int_{\partial\Omega}\, u(z)\cdot d\mu(z)- u( z_0)
\]
In dimension one
this  defect is  an integral of $\Delta(u)$ times 
the positive density in $\Omega$ given by   Green's function of
the domain. If $n\geq 2$ the result by Deval and Sibony
goes as follows:

\medskip

\noindent
{\bf{Theorem.}}
\emph{To each pair $(z_0,\mu)$ 
there exists
 a current
$T_\Omega$ of bi-degree $(n- 1,n-1)$ 
such that}
\[ 
\text{def}(u)=\int_\Omega\, T_\Omega\wedge \bar\partial\partial(u)\tag{*}
\] 
\emph{hold for every pluri-subharmonic function
$u$ of class $C^2$ where  
the right hand side  in (*) is  the integral of the volume form
$T_\Omega\wedge \bar\partial\partial(u)$.}

\bigskip


\noindent
\emph {Currents in ${\bf{C}}^n$.}
This is  a major issue during the second half  of the course.
A typical result goes as follows:
Let $V$ be a complex analytic set in
a complex manifold $X$ with positive
codimesion and $T$ a current of
bi-degree $(p,p)$ defined in
$X\setminus V$ where $1\leq p\leq \dim(X)=-1$.
If  $T$ in addition is positive. closed and has locally finite
Hausdorff mass of degree $2p$
in neighborhoods of $V$, it follows that
$T$  extends to a positive and closed current in $X$.
During the lectures    basic facts about analytic sets in 
complex manifolds of dimension 
$\geq 2$ with emphasis upon their  metric properties 
will be recalled, including
special results 
for algebraic sets.
As an example I will
expose  a  beautiful  theorem  due to Christer Lech
which asserts that if $V$ is an algebraic set in
${\bf{C}}^n$ for some $n\geq 2$, then
there exists a polynomial $P(z)$ which is 
zero on $V$ and a constant $C$ such that
\[
\text{dist}(x,V)\leq C\cdot \text{dist}(x,P^{-1}(0)
\quad\colon x\in {\bf{R}}^n
\]
where one measures ordinary euclidian distances and
${\bf{R}}^n$ is the set of points in
${\bf{C}}^n$ with real coordinates.
The lectures  will also cover
results from work by
Y.T. Siu
which 
lead to the existence of
Lelong numbers attached to plurisubharmonic functions.
Siu's theorem is exposed in Chapter 2 from
Hörmander's text-book in several complex variables 
and  gives  an
example of a proposed  "examination lecture".


\end{document}




























\bigskip

\centerline{\emph{ D. An inequality for harmonic functions
and the heat equation.}}
\medskip


\noindent
Denote by $U_+$ the upper half-plane $\{\mathfrak{Im}\, z>0\}$
and for 
each positive harmonic  function $u(x,y)$  in $U_+$
we put
\[
E_u=\{ x+iy\in U_+\quad\colon\, u(x,y)\geq y\}
\]
With these notation the following result
is due to Beurling:



\medskip
\noindent
{\bf{Theorem.}}
\emph{For every $u$ as above
one has the implication}
\[
U_+\setminus E_u\neq\emptyset\implies
\int_{E_u}\,\frac{dxdy}{1+x^2+y^2}<\infty\tag{*}
\]
\medskip


\noindent
\emph{Remark.}
This result  is  used it to
study  
solutions to the heat equation  where the standard growth condition does not hold, i.e.
when we take a solution
$u(x,y)$ to the heat equation
\[
\frac{\partial u}{\partial y}=
\frac{\partial^2 u}{\partial x^2}
\]
defined in a strip domain
$B=\{-\infty < x<\infty\}\times \{-A<y<A\}$,
The favourable analytic case occurs if
there exists a constant $C$ such that
\[ |
u(x,y)|\leq C\cdot e^{x^2}\tag{*}
\]
Then $u(x,y)$ is found
via an
integral
equation from its
restriction $x\mapsto u(x,a)$ where
$-A<a<A$ is fixed. 
If $a<x<A$ one has for example
\[ 
u(x,y)=
\frac{1}{2\sqrt{\pi (y-a)}}\int_{-\infty}^\infty\,
u(\xi,a)\cdot U(x-\xi,y-a)\, d\xi\quad\colon a<y<A\tag{ii}
\]
where $U(x,y)$ is the function which is zero when $y\leq 0$ and 
\[
U(x,y)= e^{-x^2/4y}\,\colon\, y>0
\]
When (*) does not hold
some growth condition is
needed to
ensure that
a solution $u$ is determined by
its restriction to $\{y=a\}$.
A famous
result in PDE-theory is
Erik Holmgren's uniqueness theorem
from
the article \emph{Sur les solution quasi-analytique d l'équation de chaleur}
[Arkiv för matematik. 1924] which asserts that
the solution $u$ is uniquely determined by
a restriction to some $\{y=a\}$ if there exists a constant $k\geq 0$
such that
\[
|u(x,y]|\leq e^{kx^2\cdot \log(e+|x|)}\quad\colon\, (x,y)\in B\tag{**}
\]


\centerline{\emph{A. The logarithmic potential.}}
\medskip


\noindent
Let $\gamma$ be a piecewise smooth
and closed Jordan arc with a finite number of corner points 
which borders a Jordan domain
$\Omega$.
Denote by $C_*(\partial\Omega)$ the class of
real-valued functions $f$ on
$\partial\Omega$ which
are continuous outside the corner points and absolutely integrable with
respect to
the arc-length measure on the boundary curves.
For each $f$ in this class we set
\[
 F(z)=\int_{\partial\Omega}\, 
\log\, \frac{1}{|z-p|}\, f(p)\, ds(p)
\]
where $ds$ is the arc-length measure.
Then Green's formula holds for
every $f\in C_*(\partial\Omega)$:
\[
F(z)=\frac{1}{2\pi}\int_{\partial\Omega}\,
\frac{d}{d{\bf{n}}}\log \, \frac{1}{|z-p|}(p)
\cdot F(p)\, ds(p)-
\int_{\partial\Omega}\, 
 \frac{d}{d{\bf{n}}}(F(p))
\cdot 
\log\, \frac{1}{|z-p|}\, ds(p)\tag{*}
\]
Moreover, the Dirichlet integral
\[
\iint_\Omega\, (F_x^2(z)+ F_y^2(z))\, dxdy<\infty
\]
and for each pair $f,g$ in $C_*(\partial\Omega)$ one has
\[
\iint_\Omega\, (F_x\cdot G_x+ F_y\cdot G_y)\, dxdy+
\int_{\partial\Omega}\,  \frac{d}{d{\bf{n}}} (F(p))\cdot G(p)\, ds(p)=0\tag{**}
\]
The equations  (*-**) are fundamental
and   used to
study
the double layer potential 
defined outside the diagonal 
of $\partial\Omega\times\Omega$ and all corner points by
\[
K(p,q)=\frac{\langle p-q,{\bf{n}}(q)\rangle} {\pi\cdot |p-q|^2}
\]
A crucial point is to
exhibit
properties of $K(p,q)$ when
$(p,q)$ both approach a corner.
Using parametrization of the arc-length and   partitions of the unity,
an integral equation 
emerges from a kernel  function $g(s,t)$ defined
on a square
$\{0\leq s,t,\leq 1\}$
which is zero when $s$ and $t$ have equal signs
and if $st<0$ it holds that
\[ 
g(s,t)=\frac{|s|}{s^2+t^2-2\cdot |s||t|\cdot\cos \alpha}
\] 
for some $0<\alpha\leq \pi/2$.
For such a $g$-function
one regards the integral equation below with a complex parameter $\lambda$:
\[
\phi(s)-\lambda\cdot \int_0^1\, g(s,t)\phi(t)\, dt= f(s)
\]
where $f(s)$ is a  function
for which
$|f(s)|\leq C\cdot s^{-\kappa}$ holds for some
$0<\kappa<1$.
For small absolute values of $\lambda$ the solution $\phi$ is found
via a Neumann series.
It goes without saying that the whole analysis
requires several steps,  but  it gives an instructive 
lesson about
integral operators of the Fredholm type and their spectral properties.



\medskip

\noindent
{\bf{Remark.}}
A deep  investigation of the uniqueness problem for the heat equation  was
carried out by Täcklund
in [Täcklund]. A suggestion for an "examination lecture"
is to expose
constructions by Beurling
where one studies solutions satisfying
\[
u(x,y)|\leq e^{\epsilon(|x|)\cdot x^2\cdot \log(e+|x|)}\tag{***}
\]
Here   $\epsilon(r)$  tends to zero as
$r\to+\infty$. This is a more restricted estimate compared to
Holmgren's theorem and hence 
uniqueness holds.  
Beurling  found  an integral kernel $U^*$
which serves as a substitute for the standard kernel $U$  above and
gives an
expression of $u(x,y)$ in  $B$ via
an integral where the restricted function
$x\mapsto u(x,a)$ appears. Beulring's  construction is
exposed in my notes and 
offers an
instructive  lesson 
about the role of analytic functions
in PDE-theory.


\medskip

\bigskip


\centerline {\emph{K. Currents in ${\bf{C}}^n$}}

\medskip

\noindent
This will be a major issue at the end of the course.
A typical result goes as follows:
Let $V$ be a complex analytic set in
a complex manifold $X$ with positive
codimesion and $T$ a current of
bi-degree $(p,p)$ defined in
$X\setminus V$ where $1\leq p\leq \dim(X)=-1$.
If  $T$ in addition is positive. closed and has locally finite
mass in neighborhoods of $V$, it follows that
$T$  extends to a positive and closed current in $X$.
To pursue 
the proof  I will recall   basic facts about analytic sets in 
complex manifolds of dimension 
$\geq 2$ with emphasis upon  local metric
properties.
Another topic
is
Siu's theorem whiuch gives 
the existence of
Lelong numbers attached to plurisubharmonic functions
which will be covered in the course based upon material in
Chapter 2 from Hörmander's text-book in several complex variables.










 










\medskip



\centerline{\emph{A first  example}}.
\medskip

\noindent
Neumann's boundary value problem will
be exposed during the course.
The  result in (1) below
extends the classic theorem  due to G. Neumann from 1877
for convex domains with $C^2$-boundary where
the double layer potential is continuous and positive.
Using this  "nice geometric situation"  
Neumann  solved boundary value problems by 
resolvents of
associated kernels. So his  pioneering work
contains    the first appearance of 
operational calculus for linear operators.
Relaxing  regularity and without convexity assumptions
we consider a closed Jordan curve
$\Gamma$
which is piecewise of class $C^1$, i.e. the image of a 
1-1 map from the unit circle 
$e^{i\theta}\mapsto  \alpha(\theta)$
with a finite number of corner points
$\{s_k=\alpha(e^{i\theta_k})\}$
where  the restriction of $\alpha$ to
each closed interval $\theta_k\leq \theta \leq \theta_{k+1}$ is
continuously differentiable. So the derivative
$\frac{d\alpha}{d\theta}$ has a finite number of
jump discontinuities on the $2\pi$-periodic $\theta$-interval.
Let $f$ be a real-valued function
on $\Gamma$ which is continuous on the open intervals
covering $\Gamma$ minus the set of corner points.
Suppose also that there
exists $0<\kappa<1$ and a constant $C$ such that
\[
|f(\alpha(\theta)|\leq |\alpha(\theta)-s_k|^{-\kappa}
\]
hold for each corner point $s_k$ while
$0<|\theta-\theta_k|<\epsilon$ for some small $\epsilon$.
The arc-length measure on $\Gamma$ 
is denoted by $ds$. 
Set
\[
V_f(z)=\int_\Gamma\, 
\log\, \frac{1}{|z-p|}\, f(p)\, ds(p)
\]
This gives a harmonic function in the open complement of
$\Gamma$.  Less obvious is the fact that  if
$\square$ is a  compact square in the complex $z$-plane which contains
$\Gamma$, then
there exists a constant $C$ such that
\[
|V_f(p)-V_f(q)|\leq C\cdot \log\,\frac{1}{|p-q|} \cdot |p-q|^{1-\kappa}\tag{*}
\]
hold for all pairs of points $p,q$ in $\square$ with distance $\leq 2^{-1}$.
 Those who  will take  interest and 
attend the seminars should try to verify, and in any case  \emph{appreciate}
the   result   in (*).
\medskip


\noindent
Next we discuss Neumann's boundary value problem.
Let $\Gamma$ be as above.
If $h\in C^0(\Gamma)$ and $f$ is a
measurable function on
$\Gamma$ which is integrable with respect to the arc-length
measure $ds$
there exists a unique harmonic function $U$ in
$\Omega$ satisfying Neumann's boundary equation:
\[
\frac{\partial U}{\partial{\bf{n}}} (p)=
h(p)\cdot U(p)+ f(p)\tag{1}
\] 
where equality holds almost everywhere with respect to $ds$.
In Carleman's thesis
the  solution $U$ is found as follows: Choose
$R>0$ such that $R>\max\,|p-q|\colon p.q\in\Gamma$.
Introduce the double layer potential defined outside the union
of  corner points
and the diagonal in 
$\Gamma\times\Gamma$ by
\[
K(p,q)= \frac{\langle p-q,{\bf{n}}(q)\rangle}{|p-q|^2}
\]
Via a careful analysis of the $K$-function, Carleman  proved that
the integral equation
\[ 
\mu(p)=f(p)+\int_\Gamma\, K(p,q)\mu(q)\,ds(q)-
\frac{h(p)}{\pi}\cdot \int_\Gamma\, \log\,\frac{R}{[p-q|}\cdot \mu(q)\, ds(q)
\]
has a unique solution and   the requested $U$-function
in (1) is given by
\[
U(p)=\int_\Gamma\, \log\,\frac{R}{|p-q|}\cdot \mu(q)\, ds(q)
\]
\medskip

\noindent
{\bf{Non-linear boundary values.}}
Let
$\Phi(p,x)$ be  a continuous function defined on
the product $\Gamma\times{\bf{R}}^+$ with the properties that
$\Phi(p,0)=0$ and 
$x\mapsto  \Phi(p,x)$ is strictly increasing on $[0,+\infty)$
and tends uniformly to $+\infty$ with respect to $p$ as $x$ increases.
Using  powerful technique from Carleman's work on non-linear boundary value problems
for domains with $C^1$-boundaries 
together with the solutions to the linear boundary
value problem (1),
it is likely that Neumann's  problem has a unique solution
$U$ satisfying the  boundary equation:
\[
\frac{\partial U}{\partial{\bf{n}}} (p)=
\Phi(p,U(p))+ f(p)
\] 
\medskip


\noindent
{\bf{Remark.}} I do not know if a result as above is covered
in the literature and will
therefore be very grateful if somebody
can supply information about this.
Notice  that
it is not required that
$\Phi$  is convex with respect to $x$. Passing to dimension 3
a similar result is likely to hold
where the logarithmic potential is replaced by
Newton's. Here the geometry for bounded
domains $\partial\Omega$
bordered by non-smooth surfaces is more involved.
But under similar conditions as for plane curves, i.e. under  certain restrictions 
on the singularites of $\partial\Omega$, it is proved in
Chapter 2  from Carleman's thesis that
Neumann's problem has a solution with  linear
boundary equations. Let me  also recall 
that Carleman  in 
an article from 1920,
proved that 
 the non-linear boundary value problem above
 has a unique solution
when
the boundary is of class $C^1$.










\end{document}




