\documentclass{amsart}
\usepackage[applemac]{inputenc}


\addtolength{\hoffset}{-12mm}
\addtolength{\textwidth}{22mm}
\addtolength{\voffset}{-10mm}
\addtolength{\textheight}{20mm}
\def\uuu{_}

\def\vvv{-}

 
\begin{document}




\centerline{\bf{I. Open Riemann surfaces}}



\bigskip


\noindent
{\bf{Introduction.}}
A Riemann surface is a 1-dimensional and connected complex manifold $X$.
We  shall consider open  surfaces, i.e.  the topological space $X$ is non-compact.
Proofs of the announced results below rely
upon analytic function theory in one complex variable, i.e.
complex analysis on open Riemann surfaces is based  upon
the study of analytic functions on
planar domains.
For example, the complex analytic structure on
an open Rieann surface $X$ yields  an intrinsic notion of
harmonic, respectively subharmonic functions om
$X$. This will
be explained in ¤ xx and will be used to extend
solutions to the Dirichlet prolelm for planar domains 
to $X$ where one regards relatively  compact open sets $Y$
for which the boundary $\partial Y$
locally satisfies  similar conditions as in the planar case,  to ensure
that evety
continouos boundary function $f\in C^0(\partial Y)$ has a harmonic
extension to $Y$.
\medskip

\noindent
We shall use  sheaf-theory 
without hesitation.
Let us  remark that  original work
by Riemann and Weierstrass
gave the first exanples about sheaves. So
various sheaves on Riemann surfaces provide
excellent examples which illustrate and has motivated
general sheaf theory.
We also employ differential calculus.
An open Rieann surface $X$ is in particular
an oriented $C^\infty$-manifold 
whose real dimension is two.
The complex analytic structure yields a direct sum decompostiion
\[
\mathcal E^1(X)=
\mathcal E^{1,0}(X)\oplus 
\mathcal E^{0,1}(X)
\]
where the left hand siude is the space of globally defined
differentia1-forms, while
$\mathcal E^{1,0}(X)$ are 1-forms of bidegree $(1,0)$,
and .... 
If $(U,z)$ is a chart in $X$ then
the restriction of a (1,0)-form to $U$ is
given by
$\phi(z)\cdot dz$ where
$\phi\in C^\infty(U)$.
Similarly a $(0.1)$-form restricts in the chart to
$\psi(z)\cdot dz$ where
$\psi\in C^\infty(U)$.
The $\bar\partial$-operator sends
$f\in C^\infty(X)$ to the $(1,0)$-form
$\bar\partial(f)$.
\medskip


\noindent
In analytic function theory  a classic result due to Ponpieu from 1810
asserts that if $U$ is an open subset of
${\bf{C}}$ and $w\in \mathcal E^{0,1}(U)$, then
there exist $f\in \mathcal C^\infty(U)$ such that
\[
\bar\partial(f)=w\tag{*}
\]
Thus, the inhomogenous $\bar\partial$-equation is solvable on
planar domains.
It turns out that this $\bar\partial$-equation is solvable on
every open Riemann surface !
The proof   requires several steps and is given in ¤ xx.
A first step is to establish the existence of
non-constant meromorphic functions.
Let us already in this introductiuon
describe a special construction which
is the starting point towards more general results.
Conisder a poiunt $p\in X$ and choose a chart
$\Delta$ arond $p$, i.e. $\Delta$ is biholomorphiuc with
the open unit disc where $p$ corresponds to the origin.
Now $X$ is covered by the open sets
$U_0=\Delta$ and $U_1=X\setminus\{p\}$.
Notice that the intersection
$U_0\cap U_1$ is a punctured open disc where
we let $z$ denote the complex coordinate.
With $\mathfrak{U}= (U_0,U_1$ one construct 
the Cech complex
\[
0\to C^0(\mathfrak U, \mathcal OX)
\]
By definition the Cech cohomology of order one is
the quoitent
\[
\frac{C^1(\mathfrak U, \mathcal OX)}{\partial(C^0(\mathfrak U, \mathcal O_X)}
\]
and since the covering only consists of two sets we notice that
\[
C^1(\mathfrak U, \mathcal O_X=\mathcal O(\Delta^*)
\]
Next, let $Y$ be a relatively compact open subset of
$X$.
If $0<a<1$ we consider rhe disc $a\cdot \Delta$ of radius $a$
centered at the origin.
Put
\[
V_0=Y\cap a\cdot \Delta\,\quad\&\quad
V_1=Y\setminus  a/2\cdot \overline{\Delta}
\]
Now $\mathfrak{V}=(V_0,V_1)$ is an open covering of $Y$
and we get the ceh complex
$C^\bullet(\mathfrak V, \mathcal OX)$.
Since $\overline{V_i}$ is a compact subsrt of $U_i$ for
evety $i$, it follows from
\emph{Montels theorem} in analytic function theory that
the resriction maps
\[
C^k(\mathfrak{U},\mathcal O_X)\to
\]
are compact for every $k$.
Hence a wellkonown   result from the Fredholm theoryentails that
the induced map
\[
\rho\colon\, H^1(\mathfrak{U}\to 
\]
has a finite dimensional range.
Let $N$ be the dimenson of the $\rho$-image.
Now we consider thr holomorphic functions $1,z^{-1},\ldots z^{-N}$
in
the punctured disc $\Delta^*$ and conclude that
there exist complex numbers $c_0,c-1,\ldots c_{N-1}$ such that
\[
\rho(z^{-N}= 
\]
This menas that if
\[
g= z^{-N}- (c_0+c_1z+\ldots+c_{N-1}z^{N-1})
\]
then the restrcition of $g$ to $V_0\cap V_1$
has a zero iimage in the cohomology space
(xx) above, and hence there exist
holomorphic funvtions $f_i\in\mathcal O(V_i)$ such that
\[
f_1-f_0= g
\]
holds in $V_0\cap V_1$.
This impkies thst there exists
a meromorphic function $\phi$ in $Y$ with a pole of
order $N$ at $p$, while $\phi$ is holomorphic in
$Y\setminus\{p\}$.



\medskip



\centerline{\bf{0.1 The Behnke.Stein theory.}}
\medskip


\noindent
Major result about open Riemann surfaces
were established by
Behnke and Stein  in their 
article \emph{Entwicklungen analytischer Funktionen
auf Riemannschen FlŠchen} [Math. Ann. 120 (1948)].
They proved that 
if $\mathcal O_X$ is the sheaf of holomorphic 
functions on an open Riemann surface, then
the cohomology group
\[
H^1(X,\mathcal O_X)=0\tag{0.1.1}
\]
More generally, in [ibid] it is also proved that
\[
H^1(X,\mathcal L)=0\tag{0.1.2}
\]
hold for every holomorphic line bundle.
We establish  this in ¤ xx, and
also expose classic results 
due to Riemann and Weierstrass.
In ¤ xx we prove a theorem due to Weierstrass 
which goes as follows:
\medskip

\noindent
On an open Riemann surface $X$ the space   $\mathfrak{M}(X)$ of globally defined
meromorphic functions is ample in the following sense.
Let $\{p_k\}$ be a discrete set of points in $X$
and to every $p_k$ we assign an non-zero integer $\mu_k$ which can be
positive or negative.
Then there exists $f\in\mathfrak{M}(X)$
which is holomorphic and zero-free in $X\setminus \{p_k\}$, and
for every $k$  it has a pole of order
$-\mu_k$ if $\mu_k<0$, and a zero of multiplicity $\mu_k$ if
$\mu_k>0$.
\medskip


\noindent
{\bf{0.2 Additive representations of $\pi_1(X)$.}}
An open Riemann surface
$X$
has  a fundamental group $\pi_1(X)$ and we consider the family 
$\mathcal F$ of group homomorphisms
\[
\rho\colon \pi_1(X)\to {\bf{Z}}
\]
where ${\bf{Z}}$ is the abelian group of integers.
Identify $\pi_1(X)$ with homotopy classes of closed curves
which start and terminate at some point $p\in X$.
Denote by $\mathcal O^*(X)$
the family of globally defined and zero-free holomorphic functions on $X$.
\medskip

\noindent
{\bf{0.2.1 Theorem.}}
\emph{For each $\rho\in\mathcal F$ there
exists $\phi\in \mathcal O^*(X)$
such that}
\[
\rho(\{\gamma\})=\frac{1}{2\pi i}\cdot \int_\gamma\, \frac{\partial\phi}{\phi}
\quad\colon \, \{\gamma\}\in \pi_1(X)
\]
\emph{where $\{\gamma\}$ is the homotopy class of a closed curve.}
\medskip

\noindent
The proof of Theorem 0.2.1   relies upon the exact sheaf sequence
\[
0\to {\bf{Z}}_X\to \mathcal O_X\overset{\text{exp}}\to \mathcal O_X^*\to 0
\]
where
${\bf{Z}}_X$ is the sheaf whose sections are ocally constant integer-valued functions
and 
we have used the exponential map which 
sends  holomorphic function $f$ defined in  open
subsets $U$ of $X$  to  
$e^{2\pi i f}$ which  are   sections of the multiplicative sheaf
$\mathcal O^*$ of  zero-free holomorphic functions.
Passing to the long exact sequence of cohomology one gets an exact sequence
\[ 
0\to {\bf{Z}}\to
\mathcal O(X)\overset {\text{exp}}\to \mathcal O^*(X)\to
H^1(X,{\bf{Z}})\to
H^1(X,\mathcal O)\to\ldots 
\]
Admitting
the vanishing theorem by
Behnke and Stein in (0.1) this entails that
\[
H^1(X,{\bf{Z}})\simeq \frac{\mathcal O^*(X)}{
\text{exp}(\mathcal O(X))}\tag{i}
\]
Next, we have the sheaf
$\Omega_X$ whose sections are holomorphic 1-forms
and an  exact sheaf sequence
\[
0\to {\bf{C}}_X\to \mathcal O_X
\overset{\partial} \to \Omega_X\to 0
\]
where ${\bf{C}}_X$ is the sheaf whose sections are locally constant
complex-valued functions.
Here the Behnke-Stein theorem gives
the isomorphism
\[
H^1(X,{\bf{C}})\simeq \frac{\Omega(X)}{\partial(\mathcal O(X))}\tag{ii}
\]
Next, if $g\in \mathcal O^*(X)$ one easily verifies that
the holomorphic
1-form
$\frac{\partial g}{g}$ is $\partial$-exact if and only if
$g= e^{2\pi if}$ for some $f\in\mathcal O(X)$.
Hence  (i-ii)  give a canonically defined and injective map
\[ 
H^1(X,{\bf{Z}})\to H^1(X,{\bf{C}})\tag{iii}
\]

\noindent
From this we shall deduce   Theorem 0.1.1
via a  representation for the family 
$\mathcal F_{{\bf{C}}}$
of group homomorphisms from $\pi_1(X)$ into  the additive group
of complex numbers.
More precisely, to each $\rho\in \mathcal F_{{\bf{C}}}$
we shall prove that there exists
$\omega\in \Omega(X)$ such that
\[
\rho(\{\gamma\})=\frac{1}{2\pi i}\cdot \int_\gamma\, \omega\tag{iv}
\]
Here $\omega$ is unique up to a $\partial$-exact holomorphic 1-form
and it turns out that
$\omega$ can be represented as the logarithmic differential of a zero-free
holomorphic function if and only if the
$\rho$-function  is integer-valued.










\medskip

\noindent
{\bf{0.3 The uniformisation theorem.}}
In ¤ xx we construct the universal covering space
$\widehat{X}$ of a given open Riemann surface
and show first that this yields another open Riemann surface.
It is special  since
it is \emph{simply connected}
which means that every closed curve on $\widehat{X}$
is homotopic to a constant curve.
In ¤ xx we prove that
every simply connected open Riemann surface is
bihololomorphic to the open unit disc $D$  or the complex plane
${\bf{C}}$.
\medskip

\noindent
{\bf{0.4 The Riemann-Schwarz  inequality for hyperbolic distances.}}
The uniformisation theorem has
several consequences.
Let $X$ be an open Riemann surface.
Conider a  hyperbolic metri $\sigma$ on $X$
which means
that
$\sigma $ has  
a negative curvature.
An equivaent condition is that in each open chart
$(U,z)$ of $X$
where $U$ is identified with an open subset of
the complex $z$-plane, there exists a subharmonic function $u(z)$ such that
the $\sigma$-distance  in $U$ is defined by
\[
e^{u(z)}\cdot |dz|
\]
where
$|dz|$ the ordinary euclidan length.
Assume that $\sigma$ is hyperbolic and consider a
pair of points $p,q$ in $X$. Denote by 
$\mathcal C(p,q)$ the family of
curves in $X$ with end-points at $p$ and $q$.
\medskip

\noindent
{\bf{0.4.1 Theorem.}}
\emph{For every pair
$\gamma_1,\gamma_2$ in  $\mathcal C(p,q)$
and
each point $\xi\in\gamma_1$,
there exist  a pair of curves $\alpha,\beta$, where
$\alpha\in\mathcal C(p,q)$ while $\beta$ has end-points
at $\xi$ and some point $\eta\in \gamma_2$ such that}
\[
\ell(\alpha)^2+\ell(\beta)^2\leq
\frac{1}{2}\bigr (\ell(\gamma_1)^2+\ell(\gamma_2)^2\,\bigl )\tag{*}
\]
\emph{where $\ell(\gamma)$ denotes the $\sigma$-length of a curve in $X$.
Moreover, the inequality (*) is strict with the exception for
special rhombic configurations.}
\medskip

\noindent
{\bf{Remark.}}
Theorem 0.4.1 gives in particular  existence of unique geodesic  curves
on $X$ which join a pair of points.
The proof relies upon the
uniformisation theorem 
which
reduces the 
proof to show the following: 
\medskip

\noindent
 \emph{Let
$D$ be the unit disc and $0<\theta<\pi/2$ and consider   the unique
circle $C_\theta$ which
contains
$e^{i\theta}$
and $e^{-i\theta}$ and intersects the unit circle at right angles at these points.
Let $\alpha$ denote the circular subarc of $C_\theta$  contained in
$D$.
Then the following inequality holds for
every subharmonic function $u$ in $D$:}
\[
\bigl(\int_{-1}^1\, e^{u(x)}\, dx\bigr)^2+
\bigl(\int_\alpha\, e^{u(z)}\, |dz|\bigr)^2\leq
\frac{1}{4}\cdot\bigl( \int_0^{2\pi}\, e^{u(e^{i\phi})}\,d\phi\bigr)^2\tag{0.4.2}
\] 
\bigskip

\noindent
We prove this result in ¤ xx and
how one derives Theorem 0.4.1.


\newpage


delete .....









Next, let ${\bf{C}}_X$ be the sheaf
whose sections are locally constant complex-valued functions
and consider
the cohomology group
$H^1(X,{\bf{C}}_X)$.
If it vanishes we shall prove
that the open Riemann surface is biholomorphic with
the open unit disc $D$ or the complex plane
${\bf{C}}$.
One refers to this fact  as the \emph{Uniformisation Theorem} for open
Riemann surfaces.
The proof is given 
in ¤ 5.
\medskip

\noindent
A crucial result which is used to prove (*) is the Pompieu theorem which
asserts thst the $\bar\partial$-operator is sirjhective on planar domains, i.e.
if $\Omega$is an open subset of
${\bf{C}}$ and $\phi$ is a complex-valued $C^\infty$-function on $\Omega$
then
there exists $g\in C^\infty(\Omega)$ such that
\[
\bar\partial g/\partial \bar z=\phi
\]









\medskip

\noindent
The uniformisation theorem has
several consequences.
An example is 
\emph{The Riemann-Schwarz inequality} when an open Riemann surface
$X$ is equipped with a hyperbolic metric,
This result goes
as followss:
Let $\sigma$
be 
a hyperbolic metric. This  means
that
$\sigma $ has  
a negative curvature.
An equivaent condition is that in each open chart
$(U,z)$ of $X$
where $U$ is identified with an open subset of
the complex $z$-plane, there exists a subharmnic function $u(z)$ such that
the $\sigma$-distance  in $U$ is defined by
\[
e^{u(z)}\cdot |dz|
\]
where
$|dz|$ the ordinary euclidan length.
Assume that $\sigma$ is hyperbolic and consider a
pair of points $p,q$ in $X$. Denote by 
$\mathcal C(p,q)$ the family of
curves in $X$ with end-points at $p$ and $q$.
\medskip

\noindent
{\bf{0.1 Theorem.}}
\emph{For every pair
$\gamma_1,\gamma_2$ in  $\mathcal C(p,q)$
and
each point $\xi\in\gamma_1$,
there exist  a pair of curves $\alpha,\beta$, where
$\alpha\in\mathcal C(p,q)$ while $\beta$ has end-points
at $\xi$ and some point $\eta\in \gamma_2$ such that}
\[
\ell(\alpha)^2+\ell(\beta)^2\leq
\frac{1}{2}\bigr (\ell(\gamma_1)^2+\ell(\gamma_2)^2\,\bigl )\tag{*}
\]
\emph{where $\ell(\gamma)$ denotes the $\sigma$-length of a curve in $X$.
Moreover, the inequality (*) is strict with the exception for
special rhombic configurations.}
\medskip

\noindent
{\bf{Remark.}}
The theorem gives in particular  existence of unique geodesic  curves
on $X$ which join a pair of points.
The proof relies upon the
uniformisation theorem 
which
reduces the 
proof to show the following: 
\medskip

\noindent
{\bf{0.2}} \emph{Let
$D$ be the unit disc and $0<\theta<\pi/2$ and consider   the unique
circle $C_\theta$ which
contains
$e^{i\theta}$
and $e^{-i\theta}$ and intersects the unit circle at right angles at these points.
Let $\alpha$ denote the circular subarc of $C_\theta$  contained in
$D$.
Then the following inequality holds for
every subharmonic function $u$ in $D$:}
\[
\bigl(\int_{-1}^1\, e^{u(x)}\, dx\bigr)^2+
\bigl(\int_\alpha\, e^{u(z)}\, |dz|\bigr)^2\leq
\frac{1}{4}\cdot\bigl( \int_0^{2\pi}\, e^{u(e^{i\phi})}\,d\phi\bigr)^2
\] 
\bigskip

\noindent
We prove this result in ¤ xx and
how one derives Theorem 0.1 from (0.2).


\medskip

\noindent
{\bf{A comment}}.
Basic facts about sheaves and  calculus on 2-dimensional manifolds
will
be used without hesitation.
Let us  remark that the study of open Riemann surfaces
gives
an excellent illustration to  general theory
related to analysis on manifolds.
For example, sheaf theory has emerged from Weierstrass' constructions of
analytic continuations where the "total sheaf space" $\widehat{O}$ in
¤ x below is an instructive example of a sheaf.
During our whole study
the $\bar\partial$-operator plays a crucial role. On
a Riemann surface it assigns to every
complex valued $C^\infty$-function $f$ the
differential form
$\bar\partial(f)$ of bi-degree $(0,1)$.
The Cauchy-Riemann equations
show that
$\bar\partial(f)=0$ if and only if $f$ is holomorphic. 
The \emph{Pompieu Theorem} for planar domains
is crucial. This classic result asserts that if 
$\Omega$ is an open subset of
${\bf{C}}$ and $f\in C^\infty(\Omega)$ then
there exists
$g\in C^\infty(\Omega)$  such that
\[
\frac{\partial g}{\partial\bar z}=f\tag{0.3.1}
\]
Passing to an open Riemann surface
$X$ we shall prove that 
a similar result holds, i.e. if
$\phi\in \mathcal E^{0,1}(X)$ is a 
smooth differential form of bi-degree $(0,1)$, then
there exists
$f\in C^\infty(X)$  such that
\[
\bar\partial(f)= \phi\tag{0.3.2}
\]
One can express this by saying that every smooth
differential form of bi-degree $(0,1)$ is
$\bar\partial$-exact on an open Riemann surface.
A result due to Dolbeault
implies that the solvability in (0.3.2) for every $\phi$
is equivalent to
the Behnke-Stein Theorem in (*) from the introduction.
A notsble factis that
the inhomogeneus equation (0.3.2) can be solved for
non-smooth $\phi$-froms of bi-degree $(0,1)$.
For example, given a smooth form
$\phi$ as in (0.3.2)  we also take a 
bounded Lebesgue measurable function $\rho$ on $X$
and get the current $\rho\cdot \phi$
of bi-degree $(0,19$ on $X$.
Then it turnd out that there exists
a continuous function $f$ on $X$ such that
\[
\bar\partial(f)= \rho\cdot \phi\tag{0.3.4}
\]
where the left hand side is
the
$(0,1)$-current founf via charts where
distribution derivatives of $f$ appear.








\medskip

\noindent
{\bf{0.4 The Dirichlet problem.}}
A   result due to Rado asserts that
every open Riemann surface has a countable topology.
The proof relies upon
a theorem due to PoincarŽ and Volterra from the appendix about topology,
 together with
solutions to Dirichlet problems.
Here one profits upon Perron's solution 
for planar domains which has the merit that it extends verbatim
to open Riemann surfaces, using the observation
that the complex analytic structure on a
Riemann surface $X$ leads to an intrinsic  notion of
subharmonic functions.
From this we shall describe how to
solve the Dirichlet problem
exactly  as in the planar case.
More precisely, let $\Omega$ be a relatively compact
 open set in
$X$.
A point  $p\in\partial\Omega$Êis regular in the sense of Perron if
there exists
some open chart $D$ in $X$ which contains $p$
and a continuous subharmonic function $u$ in $D$ 
such that 
\[
u(x)<0\,\colon\, x\in U\cap D\quad\colon u(p)=0
\]
\medskip

\noindent
{\bf{0.4.1 Theorem.}}
\emph{If $\Omega$ is a  relatively compact open set
and each boundary point is Perron regular, then
the Dirchlet problem has a solution for
every
$g\in C^0(\partial \Omega)$, i.e. there exists 
a harmonic function $G$ in $\Omega$ with 
continuous boundary values equal to $g$.}
\medskip

\noindent
Let us  finish this introduction by
with some  preliminary considerations
which illustrate the general theory.
\medskip

\noindent
{\bf{0.5. Additive
representations
of fundamental groups in the planar case.}}
Each open and connected set $U$ in ${\bf{C}}$ yields
an open  Riemann surface.
A special case is to take $U={ \bf{C}}\setminus (a_1,\ldots,a_k)$ where
$a_1,\ldots,a_k$ is a finite set of points which have been
removed
from the complex plane. Residue calculus
can be used to describe some topological
properties of $U$.
For each $1\leq\nu\leq k$
the zero-free holomorphic function
$\phi_\nu(z)= z-a_\nu$ in $U$ has a
logarithmic differential 
\[
\frac{\partial\phi_\nu}{\phi_\nu}= \frac{dz}{z-a_\nu}
\]
This  yields a holomorphic 1-form on $U$  which is not
$\partial$-exact, i.e. we cannot find
$g\in\mathcal O(U)$ such that
$\partial(g)= g'(z)dz= \frac{dz}{z-a_\nu}$.
The obstruction stems from the multi-valued behaviour of
$\log (z-a_\nu)$ and  can  also be seen by
residue calculus. Namely, choose a closed
Jordan curve $\gamma$ which surrounds $a_\nu$, i.e. its winding number
is +1 as explained in ¤ xx. Then
\[
\int_\gamma\, \frac{dz}{z-a_\nu}=2\pi i
\] 
On the other hand the closedness of $\gamma$ implies that
\[
\int_\gamma\,\partial g=0\quad\colon g\in\mathcal O(U)
\]
Next,  the fundamental group $\pi_1(U)$
can be identified with homotopy classes of closed curves
with a common intial and terminal point $p\in U$.
Topology teaches that
$\pi_1(U)$ is a free group of rank $k$
with
generators
$\gamma_1,\ldots,\gamma_k$ where
each $\gamma_\nu$ is a closed Jordan curve whose winding
number
with respec to $a_\nu$ is +1 while its winding number
with respect to other $a$-points
are  zero.
Consider
the
family of group homomorphisms
\[
 \rho\colon \pi_1(U)\to {\bf{Z}}\tag{1}
\] 
where
${\bf{Z}}$ is the additive group of integers.
Denote by $\mathcal O^*(U)$
the family of zero-free holomorphic functions in $U$.
If $\gamma$ is a closed curve
at $p$
and
$\phi\in\mathcal O^*(U)$
residue calculus entails that
the line integral
\[
\frac{1}{2\pi i}\cdot \int_\gamma\, \frac{\partial\phi}{\phi}
\] 
is an integer.
Recall that elementary
integration theory from
Chapter II implies that this  line integral only depends upon the
homotopy class of $\gamma$, i.e. 
upon the image $\{\gamma\}$ in $\pi_1(X)$.
Keeping $\phi$ fixed
it follows that
\[
\{\gamma\}\mapsto 
\frac{1}{2\pi i}\cdot \int_\gamma\, \frac{\partial\phi}{\phi}\tag{2}
\] 
is a group homomorphism from
$\pi_1(X)$ into ${\bf{Z}}$.
It turns out that
every such group  homomorphism is
realised by a zero-free $\phi$.
To see this we take the free
basis
$\{\gamma_1\},\ldots,\{\gamma_k\}$
in $\pi_1(U)$
and then every 
$\rho$ in (1) is determined by
a $k$-tuple of integers $e_\nu=\rho(\{\gamma_\nu\})$.
With 
\[ 
\phi(z)= \prod\, (z-a_\nu)^{e_\nu}
\]
we see that $\rho$ is equal to the
group homomorphis  given by (2).
\medskip

\noindent
{\bf{0.6 Line integrals of multi-valued functions.}}
Before  the passage to calculus on Reimann surfaces where one 
contructs
complex line integrals, an intermediate step is to
evaluate complex line integrals of multi-valued functions.
Consider as an example
some complex number
$\alpha$ which is not an integer and
the function $f=z^\alpha$
which is multi-valued in outside the origin.
A local branch  at $z=1$ is chosen so that
$f(1)=1$.
If $g(z)$ is an analytic function defined in
a neighbrhood of the closed unit disc
$\{|z|\leq 1 \}$
we seek the line integral
\[
\int_T\, g(z)\cdot z^\alpha\, dz\tag{1}
\] 
where $T$ is the unit circle oriented in the positive sense, i.e. integration moves 
counter clockwise.
It means that (1) is equal to
\[
i\cdot \int_0^{2\pi}\, g(e^{i\theta}) e^{i\alpha\theta}\, e^{i\theta}\, d\theta
\]
Here $g$ has a series expnasion $\sum\,c_nz^n$
which converges when
$|z|\leq 1$
and for each non-negative integer one has
\[
i\cdot \int_0^{2\pi}\, e^{in\theta} e^{i\alpha\theta}\, e^{i\theta}\, d\theta
=\frac{i}{n+1+\alpha}\cdot (e^{2\pi i\alpha}-1)
\]
Taking a sum over $n$ we evaluate (1).
Wirh $g=1$ we have for example
\[
\int_T\,  z^\alpha\, dz=\frac{i}{1+\alpha}\cdot (e^{2\pi i\alpha}-1)\tag{2}
\] 
If $0<r<1$ and we instead integrate along
the circle $T(r)= \{|z|=r\}$ in the counter clockwise sense,
the reader can verify that
\[
\int_{T(r)}\,  z^\alpha\, dz=\frac{i\cdot r^{1+\alpha}}{1+\alpha}\cdot (e^{2\pi i\alpha}-1)\tag{3}
\] 
Notice that (2) and (3) differ even though the closed sucrves
$T$ and $T(r)$ are homotopic in the punctured complex plane.
So the usual invariance for line integrals of single-valued analytic functions
fails.
Following original contructions by Riemann one can
explain this by regarding the universl covering space of
$\widehat{X}= {\bf{C}}\setminus \{0\}$
where $z^\alpha$ becomes a single valued holomorŒphic functions
but when the closed curves
$T$ and $T(r)$ are lifted to $\widehat{X}$ they are no longer
closed and have different end-points on
$\widehat{X}$ 
where $z^\alpha$ takes distinict values and this
explains why $(2)\neq (3)$.
\medskip


\noindent
{\bf{0.7 An extension to Riemann surfaces.}}
An open Riemann surface
$X$
has  a fundamental group $\pi_1(X)$ and we consider the family 
$\mathcal F$ of group homomorphisms
$\rho\colon \pi_1(X)\to {\bf{Z}}$.
Identify $\pi_1(X)$ with homotopy classes of closed curves
which start and terminate at some point $p\in X$.
Denote by $\mathcal O^*(X)$
the family of globally defined and zero-free holomorphic functions on $X$.
\medskip

\noindent
{\bf{0.7.1 Theorem.}}
\emph{For each $\rho\in\mathcal F$ there
exists $\phi\in \mathcal O^*(X)$
such that}
\[
\rho(\{\gamma\})=\frac{1}{2\pi i}\cdot \int_\gamma\, \frac{\partial\phi}{\phi}
\quad\colon \, \{\gamma\}\in \pi_1(X)\tag{*}
\]
\emph{where $\{\gamma\}$ is the homotopy class of a closed curve.}
\medskip

\noindent
{\bf{Remark.}}
The proof of Theorem 0.7.1   relies upon the exact sheaf sequence
\[
0\to {\bf{Z}}_X\to \mathcal O\overset{\text{exp}}\to \mathcal O^*\to 0
\]
where
${\bf{Z}}_X$ is the sheaf whose sections are ocally constant integer-valued functions
and 
we have used the exponential map which 
sends  holomorphic function $f$ defined in  open
subsets $U$ of $X$  to  
$e^{2\pi i f}$ which  are   sections of the multiplicative sheaf
$\mathcal O^*$ of  zero-free holomorphic functions.
Passing to the long exact sequence of cohomology one gets an exact sequence
\[ 
0\to {\bf{Z}}\to
\mathcal O(X)\overset {\text{exp}}\to \mathcal O^*(X)\to
H^1(X,{\bf{Z}})\to
H^1(X,\mathcal O)\to\ldots 
\]
Admitting
the vanishing theorem by
Behnke and Stein this entails that
\[
H^1(X,{\bf{Z}})\simeq \frac{\mathcal O^*(X)}{
\text{exp}(\mathcal O(X))}\tag{i}
\]
Next, we have the sheaf
$\Omega$ whose sections are holomorphic 1-forms
and an  exact sheaf sequence
\[
0\to {\bf{C}}_X\to \mathcal O
\overset{\partial} \to \Omega\to 0
\]
where ${\bf{C}}_X$ is the sheaf whose sections are locally constant
complex-valued functions.
Here the Behnke-Stein theorem gives
the isomorphism
\[
H^1(X,{\bf{C}})\simeq \frac{\Omega(X)}{\partial(\mathcal O(X)}\tag{ii}
\]
Next, if $g\in \mathcal O^*(X)$ one easily verifies that
the holomorphic
1-form
$\frac{\partial g}{g}$ is $\partial$-exact if and only if
$g= e^{2\pi if}$ for some $f\in\mathcal O(X)$.
Hence  (i-ii)  give a canonically defined and injective map
\[ 
H^1(X,{\bf{Z}})\to H^1(X,{\bf{C}})\tag{iii}
\]

\noindent
From this one  gets  Theorem 0.7.1
via a similar representation for the family 
$\mathcal F_{{\bf{C}}}$
of group homomorphisms from $\pi_1(X)$ into  the additive group
of complex numbers.
More precisely, to each $\rho\in \mathcal F_{{\bf{C}}}$
we shall prove that there exists
$\omega\in \Omega(X)$ such that
\[
\rho(\{\gamma\})=\frac{1}{2\pi i}\cdot \int_\gamma\, \omega
\]
Here $\omega$ is unique up to a $\partial$-exact holomorphic 1-form
and it turns out that
$\omega$ can be represented as the logarithmic differential of a zero-free
holomorphic function if and only if the
$\rho$-function in (*) is integer-valued.


\newpage

\centerline{\bf{¤ 1. Summary of some major constructions and results.}}

\bigskip


\noindent {\bf{1.1 The sheaf  $\widehat{\mathcal O}$.}}
An  extensive family   of open Riemann surfaces
arises via a construction due to Weierstrass.
For each point $z\in{\bf{C}}$
one has the 
space $\mathcal O(z)$ of germs of analytic functions at $z$.
Weierstrass total sheaf space is defined  by
\[
\widehat{\mathcal O} =\bigcup_{z\in {\bf{C}}} \,
\mathcal O(z)
\]
One has the projection $\pi\colon \widehat{\mathcal O}\to  {\bf{C}}$
with inverse fibers
$\pi^{-1}(z)=\mathcal O(z)$.
Now $\widehat{\mathcal O}$ becomes a complex manifold
where $\pi$ is locally biholomorphic.
Charts consist  of  pairs $(\Delta,f)$ where
$\Delta$ is an open disc in
${\bf{C}}$ and $f\in \mathcal O(\Delta)$
whose corresponding
open  set in
$\widehat{\mathcal O}$ are the
points $\{(z,f_z)\colon z\in \Delta\}$
where $f_z\in\mathcal O(z)$ denotes the germ determined by $f$
at a point $z\in\Delta$.
\medskip

\noindent
Every
open and connected subset of $\widehat{\mathcal O}$
gives an open  Riemann surface.
As an example one has the Riemann surface
attached to the multi-valued function $\log z$.
At $z=1$ we start with the local branch of $\log z$.
whose value is zero.
Now $\log z$ extends to a multi-valued function in
${\bf{C}}\setminus \{0\}$
and in $\widehat{\mathcal O}$ we get the connected
open set
$\mathcal L$ whose points are pairs $(p,f)$ where
$p\in {\bf{C}}\setminus \{0\}$ and $f$ is a local branch of $\log z$
at $p$.
Here $\pi\colon \mathcal L\to {\bf{C}}\setminus \{0\}$
is surjective where  each inverse fiber is a copy of the set of integers which reflects
the property that
local branches of the  log-function 
differ by integer-multiples of $2\pi$.
\medskip

\noindent
{\bf{Exercise.}}
Show that $\log z$ yields a single-valued holomorphic function
$\widehat{\log}$ on the open Riemann surface
$\mathcal L$ and the map
\[
p\to \widehat{\log}(p)
\] 
from $\mathcal L$ into the complex plane ${\bf{C}}$  is biholomorphic.
In topology it means that $\mathcal L$ can be taken as the
universal covering space of the punctured complex plane and
(*) gives a first example
of the uniformisation theorem applied to the simply connected
Riemann surface $\mathcal L$.









\medskip

\noindent
{\bf{1.1.1 The space $M_\Omega(z_0)$}}.
Let $\Omega$ be a  open and connected
subset of
${\bf{C}}$ and consider a point $z_0\in \Omega$. In ¤ xx
we introduced the family of germs 
$M_\Omega(z_0)$ which can
be extended in the sense of Weierstrass along every curve 
$\gamma$ in $\Omega$
with initial point at $z_0$ and some terminal point $z$.
For a pair $(f,\gamma)$ with
$f\in M_\Omega(z_0)$, the analytic continuation along
$\gamma$ gives the germ
the germ $T_\gamma(f)\in \mathcal O(z)$
wihch by definition is a point in $\widehat{\mathcal O}$.
The 
union of these points 
as $\gamma$ varies yields  a connected
open subset of
$\widehat{O}$ denoted by
$\widehat{X}_f$ and called 
the associated Riemann surface of $f$.
Here $\pi\colon \widehat{X}_f\to \Omega$ is surjective
and  the construction gives  a 
\emph{single-valued} holomorphic function
$\widehat{f}$ on $\widehat{X}_f$ where
\[
\widehat{f}(T_\gamma(f))=T_\gamma(f)(z)
\]
when $\gamma$ is a curve with terminal point at $z$.
\medskip


\noindent
{\bf{Example}}.
Remove 0 and 2 from the complex plane
and in $\Omega={\bf{C}}\setminus \{0,2\}$ we have
the multi-valued function
\[
f(z)= \sqrt{z}+ \sqrt{2-z}
\] 
where one starts with the germ at $z=1$ for which
$\sqrt{1}= \sqrt{2-1}=1$.
Under analytic continuation the
germs of the square root functions can change sign
and from this the reader may verify that
$\pi\colon \widehat{X}_f\to \Omega$
is a four-sheeted covering map, i.e. the inverse fibers consist of four points.
\medskip

\centerline{\bf{1.2 The $\bar\partial$-operator.}}
\medskip


\noindent
The complex analytic structure
on a Riemann surface  arises via charts
$(\Delta,z)$ where
$\Delta$ are open discs in a complex $z$-plane and 
equips also 
$X$ with a structure as an oriented $C^\infty$-manifold whose real dimension is two.
Denote by $\mathcal E(X)$
the space of complex-valued $C^\infty$-functions on $X$ and
$\mathcal E^1(X)$ is the space of smooth differential 1-forms.
The exterior differential
$d\colon \mathcal E(X)\mapsto \mathcal E^1(X)$
is a sum
$\partial+\bar\partial$. More precisely, one has 
a direct
sum decomposition
\[
\mathcal E^1(X)=\mathcal E^{1,0}(X)\oplus \mathcal E^{0,1}(X)
\]
and the two differentials:
\[
 \partial \colon \mathcal E(X)\mapsto \mathcal E^{1,0}(X)
\quad\colon\,
 \bar \partial \colon \mathcal E(X)\mapsto \mathcal E^{0,1}(X)
\]
Here   a differential 1-form
$\phi$ has bi-degree $(1,0)$ if its restriction
to a chart
$(\Delta,z)$ is  $a(z)dz$ with
$a\in C^\infty(\Delta)$. Similarly, a 1-form
$\psi$ has bi-degree $(0,1)$ if
$\psi|\Delta= b(z) d\bar z$ with 
$b\in C^\infty(\Delta)$. The
Cauchy-Riemann equations entail that
the $\bar\partial$-kernel on
$\mathcal E(X)$ consists of holomorphic functions.
If $U$ is an open subset of $X$ we denote by
$\mathcal O(U)$ the set of holomorphic functions in
$U$ and by
$U\mapsto \mathcal O(U)$ one gets the sheaf 
$\mathcal O$.
As already announced in the introduction
a  major result about non-compact Riemann surfaces
is the following:

\medskip

\noindent
{\bf{1.2.1 Theorem.}}
\emph{Every $(0,1)$-form on $X$ is $\bar\partial$-exact.}
\medskip


\centerline {\bf{Runge's theorem.}}
\medskip

\noindent
Let $Y$ be an open subset of $X$.
For each compact subset
$K$ of $Y$ we get  connected open components
of $X\setminus K$ and put
\[
\mathcal C^*(K)= \cup\,\Omega_\alpha
\] 
where the union is taken over all components
$\Omega_\alpha$
which are not relatively compact, i.e. the closure $\overline{\Omega}_\alpha$
is not a compact set in $X$.
One says that $K$ is a compact   Runge set in $Y$
if 
\[
\mathfrak{h}(K)=X\setminus \mathcal C^*(K)
\] 
is a compact subset of $Y$.
\medskip

\noindent
{\bf{1.2.2 Theorem.}}
\emph{For every pair $(Y,K)$ where
$K$ is a compact Runge set in $Y$
and each $f\in\mathcal O(Y)$ there exists a sequence
$\{g_n\}$ in $\mathcal O(X)$ such that}
\[
\lim_{n\to \infty}|g_n-f|_K=0
\]
\emph{where we have taken maximum norms over $K$.}

\medskip

\noindent
The two theorems above are proved in ¤ xx and   give rise to 
further results
which we describe below.
\medskip

\noindent
{\bf{Weierstrass' Theorem.}}
A divisor on $X$ consists of a discrete sequence
of points $\{p_\nu\}$ to which one assigns
integers $\{k_\nu\}$  which may be positive or negative.
A globally defined and non-constant meromorphic function
$g$ gives the  principal divisor $D(g)$ where
one assigns
a positive integer at each zero 
of $g$ given  by its multiplicity. Similarly one assigns
negative integers  at poles given by  their orders.
\medskip

\noindent
{\bf{1.2.3  Theorem.}}
\emph{Every divisor on a non-compact Riemann surface is principal.}

\medskip


\noindent
{\bf{The Mittag-Leffler Theorem.}}
On the Riemann surface
$X$ one has the sheaf $\mathcal O$ of holomorphic functions and
the sheaf $\mathfrak{M}$ whose sections are meromorphic functions.
Now there exists the quotient sheaf
\[
\mathcal M= \frac{\mathfrak{M}}{\mathcal O}
\]
Sections in $\mathcal M$ are special since
one only gets contributions at the set of poles of
a meromorphic function which over an open subset in $X$
is discrete.
Theorem 0.2.1 and the long exact sequence of cohomology entails that
one has an exact sequence
\[
0\to \mathcal O(X)\to \mathfrak{M}(X)\to
\mathcal M(X)\to 0\tag{1.2.4}
\]
This  surjective maps means that one
can assign a  Mittag-Leffler distribution
in an arbitrary fashion on disrete subsets of $X$ which
extends the classic result for planar domains.


\bigskip



\centerline{\bf{1.3 Harmonic functions and the Dirichlet problem.}}
\bigskip


\noindent
A real-valued function $u$ on $X$ is harmonic if its restriction to
every chart satisfies the Laplace equation.
An equivalent condition is that
the $(1,0)$-form
$\partial(u)$ is $\bar\partial$-closed, i.e. a holomorphic 1-form.
The space  of harmonic functions on $X$ 
is denoted by $\mathfrak{h}(X)$.
We have also the sheaf
$\mathfrak{h}_X$ whose sections over
open sets $U$ is
$\mathfrak{h}(U)$.
Let us then consider an   open
subset $Y$ of $X$ whose  boundary
$\partial Y$ is compact.
For each $h\in C^0(\partial Y)$ one seeks 
a continuous function $H$ on $\overline{Y}$ where
$H$ is harmonic in $Y$ and equal to $h$ on
the boundary.
To find $H$ one proceeds exactly as in the planar case
using Perron's method. This 
gives a sufficiency for solutions to the Dirichlet problem
for arbitrary continuous boundary value functions. More precisely, a point
$p\in\partial Y$ satisfies the Perron condition if
we can find a pair $(\Delta,u)$
where
$\Delta$ is a chart with the origin at $p$ and
$u$ is a continuous function in
$\overline{Y}\cap \Delta$ with the property that
$u$ is subharmonic in
$Y\cap \Delta$ where it takes strictly negative values, while $u(p)=0$.



\medskip

\noindent
{\bf{1.3.1 Theorem.}}
\emph{Let $Y$ be an open set in $X$ such that every $p\in\partial Y$
is Perron regular. Then the Dirichlet problem has a solution for
every
$h\in C^0(\partial Y)$.}

\medskip

\noindent
{\bf{1.3.2 Remark.}}
For brevity we say that
$Y$ is Dirichlet regular when  the Dirichlet problem has a solution.
The proof of Theorem 1.3.1 is verbatim to the planer case  and
left as an exercise to the reader.
\bigskip


\centerline{\bf{1.4 The uniformisation  theorem.}}
\medskip

\noindent
Denote by $\Omega(X)$ the space of globally defined holomorphic 1-forms.
We can impose the condition that
\[ 
\partial(\mathcal O(X))= \Omega(X)\tag{1.4.1}
\]

\medskip

\noindent
{\bf{1.4.2  Theorem.}}
\emph{Let $X$ be a non-compact Riemann surface for which (1.4.1) holds.
Then $X$
is biholomorphic with the unit disc $D$ or the complex plane
${\bf{C}}$.}
\bigskip


\noindent
{\bf{Remark.}}
In the special case when
$X$ is a planar domain the result above is
Riemann's ordinary mapping theorem for simply connected
domains.
The extension to an arbitrary
open Riemann surface 
requires extra work which is given  in ¤ 5.

\bigskip






\centerline{\bf{1.5 Further results.}}
\medskip

\noindent
The Behnke-Stein theorem
extends to the case when
$\mathcal O$ is replaced by
a holomorphic line bundle $\mathcal L$ which by definition
is a locally free sheaf of $\mathcal O$-modules with rank one.
Thus
\[ 
H^1(X,\mathcal L)=0\tag{1.5.1}
\]
There also  exists  the multiplicative sheaf
$\mathcal O^*$ whose sectios are zero-free holomorphic functions.
The exponential map yields an exact sequence of sheaves
\[
0\to {\bf{Z}}_X\to \mathcal O\overset{\text{exp}}\to  \mathcal O^*\to 0
\]
In ¤ x we prove that
$H^1(X,\mathcal O^*)=0$ 
and  the long exact sequence of cohomology  gives
\[ 
H^2(X,{\bf{Z}}_X)=0\tag{1.5.2}
\]


\noindent
Next, let $\Omega $ be the sheaf of holomorphic 1-forms
which gives the exact sheaf sequence
\[
0\to {\bf{C}}_X\to \mathcal O\overset{\partial }\to  \Omega\to 0
\]
The vanishing of $H^1(X,\mathcal O)$
gives the exact sequence
\[
0\to {\bf{C}}_X
\to \mathcal O(X)\overset{\partial }\to  \Omega(X)\to 
H^1(X,{\bf{C}}_X)\to 0\tag{1.5.3}
\]
Hence one has the isomorphism
\[
H^1(X,{\bf{C}}_X)\simeq\frac  {\Omega(X)}{\partial(\mathcal O(X)}\tag{*}
\]
When (1.4.1) fails 
one is led to analyze when a  globally defined holomorphic
1-form
$\omega$ is $\partial$-exact, i.e. equal to
 $\partial(f)$ for some
$f\in\mathcal O(X)$.
To analyze   when this holds we fix a point $x_0\in X$ and denote by
$\mathcal F$ the family of closed and differentiable curves
$\gamma$ with common start and terminal points at $x_0$.
If $\omega=\partial(f)$ it is clear that
\[
\int_\gamma\,\omega=0\quad\colon
\gamma\in\mathcal F\tag{i}
\]
Conversely, assume that
(i) holds for some
 $\omega\in\Omega(X)$.
 If $x$ is a point in $X$ we find a differentiable curve
 $\gamma(x)$ which starts at $x_0$ and has $x$ as terminal point.
 Now (i) entails that
 \[
 \int_{\gamma(x)}\,\omega\tag{ii}
 \] 
 only depends on $x$ and not on the specific choice of 
 $\gamma(x)$. This gives
 $f\in\mathcal O(X)$ such that
$f(x)$ equals (ii) for every $x$ and 
$\omega=\partial(f)$.
So the vanishing in (i) is a necessary and sufficient condition in order
that
$\omega$ is $\partial$-exact.
\medskip

\noindent {\bf{1.5.4 Additive representations of $\pi_1(X)$.}}
Recall that the fundamental group of the manifold $X$ can be identified with
homotopy classes of closed curves in the family $\mathcal F$.
Exactly as in the planar case one verifies that
the integrals in (i)  only depend upon the homotopy
classes.
So if $\omega$ is kept fixed we get a group homomorphism
from $\pi_1(X)$ into the abelian group 
${\bf{C}}$ defined by
\[
\{\gamma\}\mapsto \int_\gamma\,\omega\tag{i}
\]
Conversely one applies (1.5.3)  to show that
\emph{every} group homomorphism
$\rho\colon \pi_1(X)\to {\bf{C}}$
is given by (i) for some
holomorphic 1-form $\omega$.

\bigskip

\centerline
{\bf{¤ 1.6. About the proofs.}}
\medskip

\noindent
Theorem 1.3.1 plays a crucial role where  Perron's solution  for planar domains
can be carried out directly on a manifold by repeating the proof for planar domains.
To begin with  Theorem 1.3.1 is used to prove that
the topology of $X$ is 
countable which means that 
there exists  denumerable increasing sequence of compact subsets
$\{K_n\}$ where
$K_n$ is contained in the interior of $K_{n+1}$ for every $n$.
The proof is given
in
tbe Appendix  where the  crucial  point 
is to apply Theorem 1.3.1  when
$Y$ is the open complement in $X$   when
one has removed
a pair of closed discs in separate charts.
\medskip

\noindent
Another very useful fact
is  Montel's theorem for planar domains.
Namely, let 
$V$ and $U$ be  two open sets in
${\bf{C}}$ where
$V$ is relatively compact in
$U$, i.e $\overline{V}$ is a compact subset
of $U$. Then the restriction operator from
$\mathcal O(U)$ into $\mathcal O(V)$ is compact
where both are Frechet spaces under uniform convergence over compact subsets of 
$V$ and $U$
respectively.
In ¤ xx we show that this 
compactness and Pompieu's theorem for planar domains
give:

\medskip

\noindent
{\bf{1.6.1 Dolbeault's Lemma.}}
\emph{Let $Y$
be a relatively compact open subset of $X$.
Then, for every open set $Y^*$ which contains $\overline{Y}$
and
each $\phi\in\mathcal E^{0,1}(Y^*)$, the restriction of
$\phi$ to $Y$ is  $\bar\partial$-exact, i.e. one has the inclusion}
\[
 \phi|Y\in \bar\partial(\mathcal E(Y))
\]

\noindent
{\bf{Remark.}}
We shall see that this result
constitutes the
essential step to get   the Behnke-Stein theorem where
the relative compactness is relaxed.
\medskip


\noindent
{\bf{1.6.2 The elliptic
property
of $\bar\partial$.}}
Recall that if $\mu$ is a distribution   in some open
subset $U$ of ${\bf{C}}$ such that
$\partial(\mu)=0$ then it
is a holomorphic density.
Passing to a Riemann surface $X$
we consider a current $S$ of bi-degree
$(1,0)$, i.e  a continuous linear form on
test-forms of bi-degree $(0,1)$.
The current $S$ is $\bar\partial$-closed in an open subset
$U$ of $X$ if
\[
S(\bar\partial(g))=0\quad \colon g\in C_0^\infty(U)\tag{i}
\]
The planar result entails that (i) gives
a holomorphic 1-form
$\sigma$ in $U$ such that
\[
S(\phi^{0,1})=\int\, \phi\wedge \sigma\tag{ii}
\]
for every $\phi\in \mathcal E^{0,1}(X)$ having compact support in
$U$.
That $(i)\implies (ii)$ plays a crucial role in
the proof of Theorem 1.2.2.


\medskip


\noindent
{\bf{1.6.3 Counting zeros.}}
A substitute for the argument principle in
the complex plane to count zeros of analytic functions
exists on Riemann surfaces.
Let $f$ be holomorphic in an open subset $Y$ of $X$
and suppose that the   zeros in $Y$ is a finite set
$p_1,\ldots,p_k$, where each $p_\nu $ is  zero of some multiplicity
$e_\nu$.
Now $\log |f|^2$ is locally integrable in 
$Y$
which gives a current
defined on test-forms
$\omega$ of bi-degree $(1,1)$ with compact support in $Y$
which is defined by 
\[
\int_Y\, \log|f|^2\cdot \omega^{1,1}\tag{i}
\]
To evaluate (i)
we apply the calculus with currents.
To begin with
we get the current
\[
\partial(\log |f|^2)= \frac{\partial  f}{f}\tag{ii}
\]
whiuch  is a holomorphic density outside the zeros and if
$(|Delta,z)$ is a chart around a zero $p_\nu$ of multiplicity
$e_\nu$ then the 
current in (ii) restricted to this chart
is
$e_\nu\cdot \frac{dz}{z}$.
Now we can apply $\bar\partial$  and residue calculus shows that
the (1,1)-current
\[
\bar\partial \partial(\log |f|^2)= 2\pi i\cdot \sum\, e_\nu\cdot \delta(p_\nu)
\]
where $\{\delta(p_\nu)\}$
are Dirac measures. 
More precisely, for every test-function $g\in C_0^\infty(Y)$
one has the equality
\[
2\pi i\cdot \sum\, e_\nu\cdot g(p_\nu)
\int_Y\, \log |f|^2\cdot  \bar\partial\partial (g)\tag{iii}
\]
\medskip

\noindent
{\bf{1.6.4 A continuity principle.}}
Let $f\in\mathcal O(Y)$
and suppose  it extends to a continuous function on
$\overline{Y}$ and  there is some $\delta>0$ such that 
$|f(p)|\geq \delta$ hold for each $p\in\partial Y$.
For each complex number
$a$ with $|a|<\delta$ it follows
that $f-a$ has a finite number of zeros in $Y$. Denote by 
$e_f(a)$ be the number of zeros counted with multiplicity.
Exactly as above we get
\[
 2\pi i\cdot e(a)=\int\,  \log |f-a|^2\cdot \bar\partial\partial(g)\tag{1}
\]
when $g$ is a test-function in $Y$ which take values one at
the zeros of $f-a$.
Let $0<\delta_0<\delta$ so that
the set
$\{|f|\leq \delta_0\}$ is compact in $Y$
and fix $g\in C_0^\infty(Y)$ so that
$g=1$ over this compact set.
Now we get ther integer-valued function $a\mapsto e(a)$
which for each $a$ is evaluated via (1).
At the same time we have the $L^1$-functions
$\{\log\, |f-a|\}$ and elementary measure theory
shows that
$a\mapsto \log |f-a|$
is continuous with values in $L^1(Y)$.
Passing to their distribution derivatives
give a weak-star  continuous
current-valued function
$a\mapsto\bar\partial\partial(\log |f-a|)$
which entails that
(1) is a continuous integer-valued function defined in the disc
$\{|a|<\delta\}$.
Hence this function is constant, i.e. the number of
$a$-values taken by $f$ and counted with multiplicities is
constant.
\medskip

\noindent
{\bf{Remark.}}
It is possible to prove
the result above by regarding
proper maps with
finite fibers from one manifold into another. However, the proof given above
has the merit that it can be extended to
considerably  more general situations
since we only used the fact that passage to higher order derivatives of distributions is a
weak-star continuous process.



\newpage


\centerline{\bf{Appendix: Topological results.}}
\bigskip


\noindent
We restrict the attention to topological spaces
$X$ which are Hausdorff.
A Hausdorff space $X$ is arc-wise connected
if there to every pair of points $p,q$ in $X$ exists a continuous map
$\gamma\colon [0,1]\to X$
such that $\gamma(0)=p$ and $\gamma(1)= q$.
Next, one says that
the Hausdorff space $X$ has a countable topology if there
exista a denumerable family $\mathfrak{U}$
of open subsets
$\{U_n\}$ such that every
open set in $X$ is the union of 
sets from $\mathfrak{U}$.
The following remarkable result is due to PoincarŽ and Volterra:


\medskip

\noindent
{\bf{A.1 Theorem.}} \emph{Let 
$X$ be arc-wise  connected and Hausdorff which in addition is locally compact.
Suppose there exists a continuous map
$f\colon X\to Y$
where
$Y$ is a Hausdorff  space with countable topology
and the fibers
$f^{-1}(y)$ are discrete subsets of $X$ for every $y\in Y$. Then
$X$ has countable topology.}
\medskip

\noindent
\emph{Proof.}
Denote by $\mathfrak{B}$ the family of open sets
$V$ in $X$ which satisfy the following:
\[
\text{$V$ has a countable topology}\tag {i} 
\]
\[
\text{$V$ is a connected component of $f^{-1}(U)$ for some
open set $U$ in $Y$}\tag{ii}
\]
Theorem A.1 follows if we prove that
$\mathfrak{B}$ is a countable family and
every open set in $X$ is a union of
$\mathfrak{B}$-sets.
\medskip

\noindent
\emph{Proof that $\mathfrak{B}$Êis countable.}
Let $V_0$ be a set in $\mathfrak{B}$ and
consider an open set $U$ in $Y$.
The connected components of
$f^{-1}(U)$ are disjoint by (i)
$V_0$ has countable topology.
It follows
that
at most countably many
of the connected components of $f^{-1}(U)$
have a non-empty
intersection with $V$.
Next, since every
$V\in \mathfrak{B}$ is of the form $f^{-1}(U)$ for an open
set in $Y$ and $Y$ has a countable topology we
conclude that
\[
V_0\cap V\neq\emptyset\tag{iii}
\]
only  can hold for
countably many $V$ in $\mathfrak{B}$.
Next, fix $V_*\in\mathfrak{B}$ and set
\[ 
\mathfrak{B}_0=\{ V\colon V_*\cap V\neq\emptyset\}
\]
By (iii) this is a countable set in $\mathfrak{B}$.
If $n\geq 1$ we define inductively
\[
\mathfrak{B}_n= \{V\colon \exists\, W\in\mathfrak{B}_{n-1}\, \colon
 W\cap V\neq\emptyset\}
\]
An induction over $n$ entails
that each
$\mathfrak{B}_n$ is countable and since
$X$ is connected it is clear that
their union is equal to $\mathfrak{B}$
which therefore is a countable family.
\medskip

\noindent
\emph{Proof that
$\mathfrak{B}$ is a basis of the topology.}
Let $\Omega\subset X$ be open and take some
$x\in\Omega$. We must prove that there exists
$V\in\mathfrak{B}$ such that
\[
x\in V\subset\Omega
\]
To show this we consider the discrete fiber
$f^{-1}(f(x))$. Since $X$ is Hausdorff and locally compact
there exists 
a small open and relatively compact neighborhood $W$ of $x$ such that 
$W\subset \Omega$ and
$\partial W\cap f^{-1}(f(x))=\emptyset$.
Now $f(\partial W)$ is a compact set in $Y$
which does not contain
$f(x)$ which gives $U\in\mathfrak{U}$ such that
\[
f(x)\in U\quad\colon f(\partial W)\cap U= \emptyset
\]
Let $V$ be the connected component of $f^{-1}(U)$ which contains
$x$.
From the above $V\cap \partial W=\emptyset$ and
we conclude that 
\[
x\in V\subset W\subset\Omega
\]
which finishes the proof.
\bigskip

\centerline {\bf{A.2  Covering spaces.}}
\bigskip


\noindent
Let $X$ be arc-wise connected and Hausdorff.
A pair $(Y,\rho)$ is a covering of $X$ 
if $\rho\colon Y\to X$ is a continuous map and
for each point $p\in X$ there exists some open neighborhood $U$
such that
\[ \rho^{-1}(U)= \cup \, V_\alpha
\]
where the right hand side is a disjoint union of open sets in
$Y$ and $\rho\colon V_\alpha\to U$ are homeomorphisms for
each $\alpha$.
\medskip

\noindent
{\bf{A.2.1 Exercise.}}
Let $\gamma\colon  [0,1]\to X$ be a continuous map
and let $y_0\in Y$ be a point such that
\[
\rho(y_0)= x_0=\gamma(0)
\]
Show that there exists a unique continuous map
$\gamma^*\colon  [0,1]\to Y$ such that
$y_0=\gamma^*(0)$ and
\[
\rho(\gamma^*(t))= \gamma(t)\,\colon\, 0\leq t\leq 1\tag{i}
\]
which means that
there exist unique liftings of curves. 
\bigskip

\noindent
Next, let $\pi_1(X)$ be the fundamental  group of $X$.
Since $X$ is arc-wise connected it can be identified with homotoy classes
of closed curves $\gamma$ which have a given
$x_0\in X$ as a common initial and terminal point.
Let us also fix a point $y_0$Êin the fiber
$\rho^{-1}(x_0)$.
To each closed $\gamma$-curve as above the exercise gives
a unique lifted curve
$\gamma^*$  where  (i) entials that
\[
\rho(\gamma(1))\in
\rho^{-1}(x_0)\tag{ii}
\]

\medskip

\noindent
{\bf{A.2.2 Exercise.}}
Show that the end-point
$\gamma(1)$ in  (ii)
only  depends upon the homotopy class of
$\gamma$ and conclude that
one has a map
\[
\rho_*\colon \pi_1(X)\to \rho^{-1}(x_0)\tag{*}
\]
Show also that $\rho_*$ is surjective
if $Y$ is connected.
\medskip

\noindent
{\bf{A.2.3 The universal covering property.}}
A covering $\phi \colon Z\to X$ has a universal property if the
following holds: For every covering
$\rho\colon Y\to X$
and each pair of points $z_0\in \phi^{-1}(x_0)$ and
$y_0\in \rho^{-1}(x_0)$ there exists a unique fiber preserving continuous map
$f\colon Z\to Y$ with $f(z_0)=y_0$ and 
\[ 
\rho\circ f=\phi\tag{**}
\]
Notice that (**) means that $f$ is fiber preserving.
\medskip

\noindent
{\bf{A.2.4 Exercise.}}
Show that a covering with the universal property is unique in
the sense that if $(Z_1,\phi_1)$ and $Z_2,\phi_2)$ is such a pair then
there exists a homeomorphism $g\colon Z_1\to Z_2$
with
\[
\phi_1= \phi_2\circ g
\]
\medskip

\noindent
{\bf{A.2.5 Existence.}}
Show that an arc-wise connected  Hausdorff space
$X$ has a universal covering $\widehat{X}$ and that
the fundamental  group
$\pi_1(\widehat{X})=0$.
\medskip

\noindent
{\bf{A.2.6 The Galois property.}}
A covering $\rho\colon Y\to X$
where $Y$ is connected has the Galois property if there
to each
$p\in  X$ and every pair
of points $y_1,y_2$ in $\rho^{-1}(p)$ exista a fiber presering
homeomorphism $f\colon Y\to Y$
with
$f(y_1)= y_2$.
\medskip

\noindent
{\bf{A.2.7 Exercise.}}
Verify that the universal covering $\widehat{X}$
has the Galois property.


\bigskip
\centerline {\bf{A.3 Runge sets on Riemann surfaces.}}

\bigskip


\noindent
If $K$ is a compact subset of the Riemann surface $X$
we get the conncted components $\{\Omega_\alpha\}$
of the open complement $X\setminus K$.
Since $X$ is connected we notice that
\[ 
\partial\Omega_\alpha\subset K\tag{i}
\] 
hold for every connected component in $X\setminus K$.
Next,
choose an open set $U$ which contains $K$ where $\overline{U}$
is compact.
This is of course possible since
$K$  can be covered by a finite number of charts
where each chart has a compact closure in $X$.
If a component 
$\Omega_\alpha$ is such that
\[ 
\partial U\cap \Omega_\alpha= \emptyset\tag {ii}
\] 
the connectivity
of $X$ and (i) entail that
\[
\Omega_\alpha\subset U\tag{iii}
\]
Next,  the Heine-Borel Lemma
a finite
family of $\Omega_{\alpha_1},\ldots,\Omega_{\alpha_N}$
whose union cover the compact set $\partial U$.
Among these occur a finite family of non-compact
sets, say
$\Omega_{\alpha_1},\ldots,\Omega_{\alpha_k}$ where $1\leq k\leq N$.
Set
\[ 
\mathfrak{h}(K)= K\, \cup\, \bigcup_*\, \Omega_\alpha\tag{iv}
\]
 where the *-marked union is taken over
 all components for which (iii) hold together with  the finite family of relatively compact
 components which intersect $\partial U$, or equivalently
 \[
 \mathfrak{h}(K)=X\setminus \Omega_{\alpha_1}\,\cup\ldotsÊ\cup\, \Omega_{\alpha_k}
\]

 
 \noindent
 {\bf{A.3.1 Exercise.}}
 Verify that $\mathfrak{h}(K)$ is compact and that
 \[ 
 \mathfrak{h}(\mathfrak{h}(K))=\mathfrak{h}(K)
 \]
 
 
 \noindent
{\bf{A.3.2 Open Runge sets.}}
An open subset $Y$ in $X$ is Runge if
\[ 
K\subset Y\implies \mathfrak{h}(K)\subset Y
\]
hold for every compact set $K$, i.e. the Runge hull of a compact
subset of $Y$ stays in $Y$.
 \medskip
 
 \noindent
{\bf{A.3.3 Proposition.}}
\emph{Let $K$ be a compact Runge set
in $X$ with a non-empty interior.
Let $\Delta_1,\ldots,\Delta_N$
be a finite number of open  discs whose union cover
$\partial K$.  Then the open set below is Runge:}
\[
Y=K\setminus \,\cup\, \overline{\Delta}_\nu
\]  

 \noindent
The easy proof is left as an exercise.



\newpage




\centerline{\bf{¤ 1. Proofs of the main results.}}
\bigskip

\noindent
Preliminary results are established in ¤ 2
where Dolbeaulit's Lemma from ¤ xx is crucial.
Here the proof requires several steps which starts by a certain finiteness
result in Propostion 2.3.2 and after one derives Dolbeault's Lemma via a 
"tricky construction" which 
is due to Cauchy and based upon 
the general fact that if
$A\colon V|to V$ is a linear operator on a finite dimensional vector space
of some dimension $N$
and
\[ 
\text{det}(\lambda\cdot E_V-A)=
\lambda^N+
c_{N-1}\lambda^{N-1}+\ldots +c_0
\]
then the linear operator
\[
A^N+
c_{N--1}A^{N-1}+\ldots +c_0E_V
\] 
is identically zero.
In ¤ 3 we first establish an approximation result
where calculis with currents are used. The crucial point is the
elliptic property of $\bar\partial$ 
which implies that if $S$ is a current of bi-degree
(1,0) in some open set $U$ of $X$
which is $\bar\partial$-closed, then
there exists a holomorphic 1-form $\sigma$ in $U$ such that
\[
S(\omega^{0,1})=\int_U\, \omega^{0,1}\wedge \sigma
\]
for every test-form $\omega^{0,1}$ of bi-degree 
$(0,1)$ having compact support in $U$.
At the end of ¤ 3 we deduce the Behnke-Stein theorem from the previous results.
In ¤ 4 we derive further results  such as
Weierstrass' theorem 
which asserts that
every divisor on an open Riemann surface is principal.
Another crucial  fact is the existence of
a globally defined holomorphic 1-form which never is zero.
\medskip

\noindent
Armed with previous results we prove the uniformisation theorem in
¤ 5 which is based upon repeated solutions to certain Dirchlet problems
in an exhaustion of the simply connected Riemann surface
$X$ by relatively compact Perron regular
Runge domains.
A crucial point during the proof  is that
the hypothesis 
\[
\Omega(X)=\partial(\mathcal O(X))
\]
entails that the same holds for every
open Runge set in $X$.










\newpage




\centerline{\bf{¤ 2. Dolbeault's Lemma.}}

\bigskip


\noindent
Let $X$ be an open Riemann surface
and $Y$  a
relatively  compact open subset.
Heine-Borel's Lemma gives a finite covering of
$\overline{Y}$ by open charts
$\{\Delta_\alpha\}$ and hence   a finite open covering 
$\mathfrak{U}= \{U_\alpha\}$ 
of $Y$ where
\[
U_\alpha=\Delta_\alpha\cap Y
\]
Construct  the Cech complex
\[
C^0(\mathfrak {U},\mathcal O)
\overset{\delta}\to\,
C^1(\mathfrak {U},\mathcal O)
\overset{\delta}\to\,
C^2(\mathfrak {U},\mathcal O)
\overset{\delta}\to\ldots
\]
and consider  the cohomology group
\[ 
H^1(\mathfrak {U},\mathcal O)=
\frac{Z^1(\mathfrak {U},\mathcal O)}{
\delta(C^0(\mathfrak {U},\mathcal O)}\tag{2.1}
\]
Pompieu's  theorem and Leray's acyclicity theorem
for sheaf cohomology entail that
(2.1) is 
independent of the chosen 
covering  and equal to the cohomology group
$H^1(Y;\mathcal O_X)$. Moreover,   the Dolbeault isomorphism from ¤ XX gives:
\[
H^1(\mathfrak {U},\mathcal O_X))\simeq
\frac{\mathcal E^{0,1}(Y)}{\bar\partial(\mathcal E(Y))}\tag{2.2}
\]

\medskip

\noindent
{\bf{2.3 A finiteness result.}}
Let $Y$ and $Y^*$ be a pair of relatively
compact subsets of
$X$ where  $\overline{Y}$ is a compact subset of
$Y^*$.
Let $\{\Delta_\alpha\}$ be a finite covering of 
$\overline{Y^*}$
by  charts and set
$U_\alpha=\Delta_\alpha\cap Y^*$ so that
$\mathfrak {U}^*=\{U_\alpha\}$
is a finite 
covering of 
$Y^*$.
Since $\overline{Y}$ is compact in
$Y^*$ 
there exists some
$0<a<1$ such that
$\{a\cdot \Delta_\alpha\}$ cover
$\overline{Y}$ and  give a covering $\mathfrak{U}_*$
of $Y$ where
\[ 
V_\alpha=
a\cdot \Delta_\alpha\cap Y
\]
It is clear that
$V_\alpha$ is a compact subset of $U_\alpha$ for every
$\alpha$.
Montel's theorem entails that the restriction operators
\[
C^p(\mathfrak{U},\mathcal O)\to 
C^p(\mathfrak{U}_*,\mathcal O)
\]
are compact for each $p$.
These restrictions  commute with the Cech coboundary mappings
and give a  ${\bf{C}}$-linear operator
\[
H^1(\mathfrak U,\mathcal O)\to 
H^1(\mathfrak{U}_*,\mathcal O)\tag{2.3.1}
\]
 A general result in functional analysis about
 compact operators between Frechet spaces entails that the range of
 (2.3.1) is finite dimensional.
 By (2.2) it follows that 
 the restriction map
 \[
 H^1(Y^*,\mathcal O)\to 
  H^1(Y,\mathcal O)\tag{2.3.2}
 \] 
 has a finite dimensional range.
Above $Y^*$ was relatively compact. More generally, let
$U\subset X$ be open where
$\overline{Y}$Êis a compact subset of $U$.
We can find $Y^*$ as above where
$Y\subset Y^*\subset U$.
Let $N$ be the dimension of the range from (2.3.2). It means that
there exists an $N$-tuple $\{\phi_\nu\}$ in $\mathcal E^{1,0}(Y^*)$
and for every other $\phi\in \mathcal E^{1,0}(Y^*)$ there
exist complex numbers $\{c_k\}$ such that
\[
\phi|Y-\sum\, c_k\cdot \phi_k|Y\in \bar\partial \mathcal E(Y)
\]
This applies  when we start from some
$\psi\in \mathcal E^{1,0}(U)$
and take the restriction $\phi=\psi |Y^*$. Hence
the range of the map 
\[ 
H^1(U,\mathcal O)\to H^1(Y,\mathcal O)
\] 
is contained in the
$N$-dimensional complex vector space
generated
by the images of $\{\phi_k|Y\}$ in
Dolbeault's quotient space from (2.2) which defines
$H^1(Y,\mathcal O)$. Summing up 
we have proved

\medskip

\noindent
{\bf{2.3.3 Proposition.}}
\emph {Let $Y$ be a relatively compact open set in
$X$. Then the range of}
\[ 
H^1(U,\mathcal O)\to H^1(Y,\mathcal O)
\] 
\emph{is finite dimensional for every open set
$U$ which contains $\overline{Y}$.}
\bigskip


\noindent
{\bf{2.4 Another finiteness result.}}
Consider some finite open covering $\mathfrak{U}=\{U_\alpha\}$ of $X$.
No assumption is imposed on the open sets $U_\alpha$.
Let $Y$ be a relatively compact subset of $X$ and
$\mathfrak{U}_*=\{V_\alpha\}$ a finite open covering of $Y$ such that
$\overline{V}_\alpha$ is a compact subset of $U_\alpha$ for every
$\alpha$.
Restrictions give a 
morphism from the Cech complex $C^\bullet(\mathfrak U,\mathcal O)$
to
$C^\bullet(\mathfrak{U}_* ,\mathcal O)$, and exactly as above  Montel's theorem implies that
the  map
\[
H^1(\mathfrak U;\mathcal O)\to 
H^1(\mathfrak{U}_*;\mathcal O)\tag{2.4.1}
\] 
has a finite dimensional range.
\bigskip


\noindent
{\bf{2.4.2 A special case.}}
Let $p$ be a point in $X$ and $Y$ a relatively compact subset.
Here $p$ may or may not belong to $Y$.
Choose a chart $\Delta$ centered at $p$.
Now  $U_0=X\setminus\{p\}$ and $U_1=\Delta$ is an open covering 
$X$.
Let $0<a<1$ and put
\[
V_0=Y\setminus \frac{a}{2}\cdot \overline{\Delta}
\quad\colon V_1=Y\cap a\cdot \Delta
\]
where
$ \frac{a}{2}\cdot \overline{\Delta}$ is the closed disc of radius $a/2$.
Here  $V_0,V_1$ cover $Y$
and from the above the
restriction map
\[ 
\rho\colon H^1(U_0,U_1;\mathcal O)\to
H^1(V_0,V_1;\mathcal O)\tag{2.4.3}
\] 
has a finite dimensional range.
Notice that
\[ 
C^1(U_0,U_1;\mathcal O)=\mathcal O(\Delta^*)
\] 
where $\Delta^*$ is the punctured
disc wih $z=0$ removed.
To each non-negative integer we have
$z^{-j}\in \mathcal O(\Delta^*)$. Since 
$C^2(U_0,U_1;\mathcal O)=0$  each
of these holomorphic functions in
the punctured disc yields a vector in
$H^1(U_0,U_1;\mathcal O)$ and
we apply $\rho$ to get
\[ 
\rho(z^{-j})\in  H^1(V_0,V_1;\mathcal O)
\]
If $N$ is the dimension of the range of $\rho$ we find
complex numbers
$c_0,\ldots,c_{N-1}$ such that
\[
\rho(z^{-N})= \sum\, c_j\cdot \rho (z^{-j})
\]
This means that there exists a pair $f_0\in\mathcal O(V_0)$ and
$f_1\in\mathcal O(V_1)$ such that
\[
f_1=
f_0+ \sum\, c_j\cdot z^{-j}-z^{-N}
\quad\colon  z\in V_0\cap V_1\cap Y\tag{2.4.4}
\]
Hence $f_1$ and $g_0=f_0+ \sum\, c_j\cdot z^{-j}-z^{-N}$
are glued in $V_0\cap V_1$ and give together a meromorphic function
$g$ in $Y$ which is holomorphic in $Y\setminus \{p\}$ and has a pole of order
$N$ at $p$  when
$p\in Y$.

\bigskip


\noindent
{\bf{2.5 Exercise.}}
Use the above to show that
when $Y$ is relatively  compact
then there exists an open neighborhood $U$ of $\overline{Y}$ and some
$f\in\mathcal O(U)$
whose restriction to every connected component of $Y$ is
non-constant.
In particular the number of its zeros is finite
and the reader should verify that
the same holds if we take
\[ F= f^N+c_{N-1}f^{N_1}+\ldots+c_1f+c_0
\]
where $N\geq 1$ and $\{c_k\}$ are complex numbers.



\bigskip



\centerline {\bf{2.6 Proof of Dolbeault's Lemma.}}
\bigskip


\noindent
Let $Y\subset X$ be relatively compact and
$Y^*$  another relatively compact set which contains
$\overline{Y}$ as a compact subset. Choose coverings as in ¤ xx to
get the restriction map
\[
\rho\colon H^1(Y^*,\mathcal O\to 
 H^1(Y,\mathcal O)\tag{2.6.1}
 \]
We are going to prove that the $\rho$-image is zero.
To get this we argue by a contradiction. If the image is $\neq 0$ we already know 
that it has a finite dimension $N$.
Choose
$\xi_1,\ldots,\xi_N$ in $C^1(\mathfrak {U},\mathcal O)$
such that $\{\rho(\xi_k)\}$ is a basis of the $\rho$-image.
Here we employ Dolbeault's respresentation of
cohomology so that each $\xi_k\in \mathcal E^{0,1}(Y^*)$.
Next,  Exercise 2.5 applied with $Y^*$  gives
$f\in \mathcal O(Y^*)$.
Now  $f\cdot \xi_k$ belongs to
$\mathcal E^{0,1}(Y^*)$ for each $k$
and since   
$\{\rho(\xi_k)\}$ was a basis
we find  for each fixed $k$ complex numbers 
$\{b_{kj}\}$
such that
\[
f\cdot \xi_k-\sum_{j=1}^{j=N}\, b_{kj}\cdot \xi_k\, \bigl|Y\in
\bar\partial (\mathcal E(Y))
\tag{2.6.2 }
\]
Here $B=\{b_{kj}\}$ is an $N\times N$-matrix
and we construct  the holomorphic function $F$ in $Y^*$
\[
F=\det(f\cdot E_N-B)
\]
The Cayley-Hamilton  theorem from  linear algebra gives
\[
F\cdot \xi_k|Y\in\bar\partial (\mathcal E(Y))
\quad\colon k=1,\ldots,N\tag{2.6.3}
\]
Since $\{\rho(\xi_k)\}$ spans the $\rho$-image it follows that
\[
\rho(F\cdot \eta)=0\tag{2.6.4}
\]
for every cohomology class $\eta\in H^1(Y^*;\mathcal O)$.
Next,  $f$ is non-constant
on connected components in $Y^*$ and we notice  that 
the same holds for $F$. Recall  also that $f$ even is holomorphic in
a neighborhood of $Y^*$ which implies  that
the zeros of $F$ in $Y^*$ is a finite set at most.
Then   it is clear that there exists
a finite covering
$\mathfrak U$ via charts in $Y^*$ such
that $F$ has no zeros in every non-empty intersection of $\mathfrak U$-sets.
Let us now  consider an arbitrary
cohomology class
$\eta\in H^1(Y^*,\mathcal O)$
represented by a Cech cocycle $\{\phi_{\alpha \beta}\}$.
Since $F$ has no zeros in non-empty intersections 
$U_\alpha\cap U_\beta$ we get another Cech cocycle
\[ 
\psi_{\alpha\beta}=\frac{\phi_{\alpha\beta}}{F}
\]
Let $\eta^*$ be its cohomology class. Now $\eta= F\cdot \eta^*$
and (2.6.4) applied with
$\eta^*$ entails  that
$\rho(\eta)=0$. Since $\eta$ was arbitrary 
the restriction map from 
$H^1(Y^*;\mathcal O)$ into
$H^1(Y;\mathcal O)$ is zero.
\bigskip


\centerline{\bf{¤ 3. Proofs of Theorem 0.2.1-0.2.2}}
\bigskip


\noindent
Let us first consider
a pair $(Y,K)$ from Theorem  0.2.2
and  $Y^*$ is  another relatively compact subset of
$X$ such that  $\overline{Y}$ is compact in $Y^*$.
First we establish 
a
weaker variant of  Theorem
0.2.2 where   the subsequent proof is attributed to Malgrange.

\medskip

\noindent
{\bf{3.1 Proposition.}}
\emph{When 
 $f\in\mathcal O(Y)$ 
there exists a sequence $\{g_n\}$ in $\mathcal O(Y^*)$ such that
$|g_n-f|_K\to 0$.}

\medskip

\noindent
\emph{Proof.}
Let $\mu$ be a Riesz measure
supported by $K$ such that
\[ 
\int\, \phi\cdot d\mu=0\quad\colon \phi\in\mathcal O(Y^*)\tag{i}
\]
The Hahn-Banach  theorem gives Proposition 3.1 if we show that (i)
entails that
\[ 
\int\, f\cdot d\mu=0\quad\colon f\in\mathcal O(Y)\tag{ii}
\]
To prove this
we  construct a current
$S$ on $X$ as follows: Apply Dolbeault's Lemma
to the relatively compact set
$Y^*$. It follows
that  for each 
$\omega^{0,1}\in \mathcal E^{0,1}(X)$ 
there exists  
$g\in \mathcal E(Y^*)$ such that
\[
\omega|Y^*= \bar\partial(g)\tag{iii}
\]
Here $g$ is unique up to $\mathcal O(Y^*)$ so by (i)
the  integral 
$\int\, g\cdot d\mu$
only depends upon $\omega$. Hence there exists a
current $S$ on $X$ 
defined by
\[ 
S(\omega^{0,1})=\int\, g\cdot d\mu\tag{iv}
\]
with $g$ determined via (iii).
Next, consider
an 
open chart $\Delta$ contained in $X\setminus K$.
If $g\in C_0^\infty(X)$ has compact support in
$\Delta$ we take $\omega^{0,1}= \bar\partial(g)$
and since $g=0$ on $K$ one has 
\[
S(\bar\partial(g))=0
\]
Since this hold for every pair $(\Delta, g)$ as above,
$S$ is $\bar\partial$-closed in $X\setminus K$ and
the elliptic property of
$\bar\partial$ gives a holomorphic 1-form
$\sigma$ in $X\setminus K$ such that
\[
S(\omega^{0,1})=\int\, \omega^{0,1}\wedge \sigma\tag{v}
\]
holds when $\omega^{0,1}$ has compact support in
$X\setminus K$.
Let us now consider a point $p\in X\setminus \mathfrak{h}(K)$.
By the construction of $\mathfrak{h}(K)$ this gives a non-compact
open and connected subset $\Omega$ 
of $X\setminus\mathfrak{h}(K)$
which contains $p$. Since the current $S$ has compact support
it follows that 
\[
\Omega\setminus \text{Supp}(S)\cup K)\neq \emptyset\tag{vi}
\]
Let $q$ be a point in this set and 
choose a small open chart
$\Delta$ centered
at $q$
which stays in $\Omega$ and is disjoint from
the support of $S$. Then
\[
\int\, \omega^{0,1}\wedge \sigma=0
\] 
for every test-form
$\omega^{0,1}$ with compact support in
$\Delta$. Hence the restriction of $\sigma$
to $\Delta$ is zero. Since
$\sigma$ is a 
holomorphic 1-form
and  $\Omega$ is connected, 
analyticity
gives 
$\sigma|\Omega=0$. In particular $\sigma=0$ holds in a neighborhood of
$p$ which  proves the inclusion
\[
 \text{Supp}(S) \subset
\mathfrak{h}(K)\tag{vii}
\]
Finally, by  assumption $\mathfrak{h}(K)$ is a compact subset of $Y$. 
So if  $f\in\mathcal O(Y)$ we can find
a test-function $g$ with compact support in
$Y$ such that
$g=f$ 
holds in a neighborhood of $\mathfrak{h}(K)$.
Then $\bar\partial(g)$ vanishes in a neighborhood of
$\mathfrak{h}(K)$ so (vii) and the construction of $S$ entail that
\[ 
0=S(\bar\partial g)=\int_K\,g\cdot d\mu=
\int_K\,f\cdot d\mu\tag{viii}
\] 
which proves Proposition 3.1.




\bigskip





\centerline{\bf{3.2 Proof of Theorem 0.2.1}}
\medskip


\noindent
By  ¤ xx  we can  exhaust $X$ by an increasing sequence of Runge domains
$\{Y_n\}$  where the closure of $Y_n$
is a compact subset of $Y_{n+1}$ 
for each $n$.
Consider
some $\phi\in \mathcal E^{0,1}(X)$.
Dolbeault's Lemma applies to each pair
$Y_n, Y_{n+1}$ and the restriction of
$\phi$ to $Y_{n+1}$.
Hence there exists
$f_n\in \mathcal E(Y_n)$
such that 
\[
 \bar\partial f_n=\phi|Y_n\tag{3.2.1}
\]
It follows that
the restriction to $Y_n$ of $f_{n+1}-f_n$ is holomorphic
and since $Y_n$ is Runge and $\overline{Y}_{n-1}$ is a compact subset,
Proposition 2.4 entails that $f_{n+1}-f_n$
can be uniformly approximated on
$Y_{n-1}$ by functions from $\mathcal O(Y_{n+1})$.
Hence there
exists 
$g_{n+1}\in \mathcal O(Y_{n+1})$
such that the maximum norm
\[
||f_{n+1}+g_{n+1}-f_n||_{Y_{n-1}}<2^{-n}
\]
With $f^*_{n+1}= f_{n+1}+g_{n+1}$
we still have
\[
\bar\partial f^*_{n+1}=\phi|Y_{n+1}
\]
Perfoming
these modifications inductively with increasing $n$ we obtain a 
sequence $\{f^*_n\}$ such that   (3.2.1) hold for every $n$
and 
\[
||f^*_{n+1}-f^*_n||_{Y_{n-1}}<2^{-n}
\quad\colon \, n=1,2,\ldots\tag{3.2.2}
\]
It follows that $\{f_n^*\}$ converge uniformly on $X$ to a continuous function
$F$ which 
entails that
the distributions
$\{\bar\partial f_n^*\}$ converge to the distribution derivative
$\bar\partial (F)$. Moreover, since (3.2.1) hold for every
$n$
it is clear that
\[ 
\bar\partial(F)=\phi\tag{3.2.3}
\]
holds everywhere in $X$.
Finally, $\phi$ is a smooth form so  the elliptic property of
$\bar\partial$ implies that
$F$ is a $C^\infty$-function. Hence the mapping
$\bar\partial\colon \mathcal E(X)\to \mathcal E^{(0,1)}(X)$
is surjective which proves Theorem 0.2.1.


\bigskip





\centerline{\bf{3.3 Proof of Theorem 0.2.2}}
\medskip
 TO BE GIVEN


\newpage

\centerline{\bf{¤ 4. Further results.}}
\bigskip


\noindent
A locally free sheaf of $\mathcal O$-modules of rank one is called
a
holomorphic line bundle.
Let $\mathcal L$ be such a sheaf.
By definition it has local trivialisations, i.e. we can find
a locally finite covering $\mathfrak{U}$
by charts such that
the restricted sheaf
$\mathcal L|U_\alpha\simeq \mathcal O$.
In each non-empty intersection
$U_\alpha\cap U_\beta$ we find
a zero free function 
$g_{\alpha\beta}\in\mathcal O^*(U_\alpha\cap U_\beta)$
so that the space $\mathcal L(V)$ of sections over
an open subset $V$ in $X$
consists of a family $\{\xi_\alpha\in \mathcal O(U_\alpha\cap V)\}$
satisfying the glueing conditions
\[
\xi_\alpha|U_\alpha\cap U_\beta\cap V=
g_{\alpha\beta}\cdot
\xi_\beta|U_\alpha\cap U_\beta\cap V\tag{*}
\]
\medskip

\noindent
Repeating  the methods which were used to prove
Theorem 0.2.1  one has the result below whose detailed verification is left
as an exercise to the reader.

\medskip

\noindent
{\bf{4.1 Theorem.}}
\emph{For every holomorphic line bundle
$\mathcal L$ one has $H^1(X,\mathcal L)=0$.}
\bigskip


\noindent
{\bf{4.2 Example.}}
The 
sheaf $\Omega$ of holomorphic 1-forms is an example of a  holomorphic line bundle.
Another example is the sheaf
$\Theta_X$ whose sections are holomorphic vector fields.
Notice that
\[ 
\Omega=Hom_{\mathcal O}(\Theta_X,\mathcal O)
\]
is the  dual line bundle.
Theorem 4.1 entails that
\[
H^1(X, \Omega)=H^1(X,\Theta_X)=0\tag{4.2.1}
\]



 \medskip
 
 
 \centerline{\bf{4.3 Proof of 
Weierstrass'  Theorem}}

\bigskip


\noindent
Let $D$ be a divisor on $X$
which means that integers $\{k_\nu\}$ are assigned to
a discrete sequence of points $\{p_\nu\}$.
We must prove that there exists a globally deefined meromorphic function $\psi$
whose principal divisor is $D$.
To begin with one has:

\medskip

\noindent
{\bf{4.3.1 Exercise.}}
Use a
$C^\infty$-partition of the unity
to find a function $\phi$ which is zero-free and 
$C^\infty$ in the open complement of
the discrete set $\{p_\nu\}$, and for each
$p_\nu$ there is a small open  chart
$\Delta_\nu$ centered at $p_\nu$ with a local coordinate
$z_\nu$ where 
\[
\phi|\Delta_\nu= z_\nu^{k_\nu}
\]
\medskip

\noindent
Next, we find a locally finite covering
$\mathfrak{U}=\{U_\alpha\}$ of  charts in
$X$ which contains
the discs
$\{\Delta_\nu\}$
while each $U_\alpha$ which differs from these discs 
does not contain points in $\{p_\nu\}$.
For
each
$U_\alpha$ which does not contain any point in
$\{p_\nu\}$ we take $f_\alpha=1$ while
$f_\alpha= z_\nu^{k_\nu}$ when
$U_\alpha=\Delta_\nu$.
Then we can write 
\[
\phi|U_\alpha= f_\alpha\cdot \psi_\alpha
\quad\colon\,\psi_\alpha\in C^\infty(U_\alpha)
\tag{i}
\] 
Since $\phi$ is zero-free outside
$\{p_\nu\}$ we see that
every $\psi$-function is zero-free. Since  every chart
$U_\alpha$ is simply connected there exist
$\{\rho_\alpha\in C^\infty(U_\alpha)\}$ such that
\[
 \psi_\alpha= e^{\rho_\alpha}\tag{ii}
\]
In each non-empty intersection $U_\alpha\cap U_\beta$  
it follows that
\[
e^{\rho_\alpha-\rho_\beta}=\frac{f_\beta}{f_\alpha}\tag{iii}
\]
Here 
each quotient
$\frac{f_\beta}{f_\alpha}\in \mathcal O^*(U_\alpha\cap U_\beta)$
and 
(iii) entails that
the restricted differences
\[
\rho_\alpha-\rho_\beta|U_\alpha\cap U_\beta)\in 
\mathcal O(U_\alpha\cap U_\beta)
\]
So with $g_{\alpha\beta}=\rho_\alpha-\rho_\beta|U_\alpha\cap U_\beta)$
we get a Cech-cocycle in $H^1(\mathfrak{U},\mathcal O)$.
The Behnke-Stein theorem entails that it is a $\delta$-coboundary. Hence
there exist $\{g_\alpha\in \mathcal O(U_\alpha)\}$ such that
\[
\rho_\alpha-\rho_\beta|U_\alpha\cap U_\beta)=g_\alpha-g_\beta\tag{iv}
\]
Taking exponentials in (iv) and using (iii) it follows that
\[
e^{g_\alpha}\cdot f_\alpha=
e^{g_\beta}\cdot f_\beta\tag{v}
\] 
hold in $U_\alpha\cap U_\beta$.
This gives
a globally defined meromorphic
function
$\psi $ such that
\[ 
\psi|U_\alpha=e^{g_\alpha}\cdot f_\alpha\tag{vi}
\]
Finally,  the construction of the $f$-functions  implies  that 
the principal divisor $D(\psi)$ is equal to the given divisor $D$
which finishes the proof of Weierstrass' theorem.
\bigskip


\noindent
{\bf{4.4 The construction of a non-vanishing holomorphic form.}}
By ¤ xx there exists a non-zero global section $\omega$ in $\Omega(X)$.
If $(\Delta,z)$ is a chart we have
\[
\omega|\Delta=g(z)\cdot dz
\]
where $g\in\mathcal O(\Delta)$ is non-constant and hence has
a discrete set of zeros.
The locally defined divsors of these $g$-functions
match each other and yield a globally defined
divisor
$D=\{(p_\nu;k_\nu)\}$ in $X$.
Notice that
$D$ is positive, i.e.
 the integers $k_\nu>0$.
Weierstrass's theoren gives
$\psi\in\mathcal O(X)$ with $D(\psi)=D$.
Then it is clear that
\[ 
\omega^*=\psi^{-1}\cdot \omega
\]
yields a holomorphic 1-form whose associated $g$-functions in local charts
are zero-free.

\bigskip


\centerline{\bf{4.5 The Mittag-Leffler theorem.}}
\bigskip


\noindent
Announce and Prove !
 
\newpage




\centerline{\bf{¤ 5. The uniformisation  theorem}}

\bigskip


\noindent
Consider a  non-compact Riemann surface
$X$ where  every holomorphic 1-form is $\partial$-exact.
By ¤ xx there exists $\omega\in \Omega(X)$ which is everywhere 
non-zero.
So if $Y$ is an open set in $X$
and $\mu\in\Omega(Y)$
 there exists $g\in\mathcal O(Y)$ such that
 \[ 
 \mu= g\cdot \omega_Y\tag{i}
\] 
where $\omega_Y$ is the restriction of $\omega$ to $Y$.
We use this to prove

\medskip

\noindent
{\bf{5.1 Proposition.}} \emph{If 
$Y$ is  an open Runge set in $X$ one has}
\[
\Omega(Y)=\partial(\mathcal O(Y))\tag{5.1.1}
\]

\noindent
\emph{Proof.}
Let  $\mu$ be as in (i).
Consider a point $y_0\in Y$ and a closed curve
$\gamma$ in $Y$ which has $y_0$ as initial 
and terminal point.
Since $Y$ is Runge, Theorem 0.2.2  gives  a sequence
$\{g_n\}$ in $\mathcal O(X)$ and 
the maximum norms $|g_n-g|_\gamma\to 0$.
It follows that
\[
\int_\gamma\, \mu=\lim_{n\to\infty}\, \int_\gamma\, g_n\cdot \omega
\]
Here $\gamma$ is a closed curve in $X$ and since
each $g_n\cdot \omega$ belong to $\Omega(X)$ the 
hypothesis on $X$ implies
that the integrals in
the right hand side above are all zero. Hence
the line integrals of $\mu$ are zero for all closed curves
at $y_0$ and then  ¤ xx shows  that it is $\partial$-exact in $Y$
which finishes the proof.

\medskip

\noindent
{\bf{5.2 Semi-local conformal mappings.}}
Let $Y$ be a relatively compact open subset of $X$ which is 
Runge and Dirichlet regular.
Let $y_0\in Y$ and by
¤¤ there exists
$g\in\mathcal O(X)$ with  a simple zero at $y_0$ and  zero-free
in $X\setminus\{y_0\}$.
Now $\mathfrak{Re}(g)$ restricts to a continuous function
on $\partial Y$ and we find a harmonic function
$u$ in $Y$ whose boundary value function is
$\log |g|$.
The equality (5.1.1) and the remark in ¤ xx  entail that
$u$ has a harmonic conjugate $v$ in $Y$
which gives $u+iv\in\mathcal O(Y)$. Set
\[
f=g\cdot e^{-(u+iv)}
\]
On $\partial Y$ it follows that
\[ 
|f|=|g|\cdot e^{-\log|g|}=1
\]
At the same time $f$ has a simple zero at $y_0$ and is zero-free in
$Y\setminus \{y_0\}$.
The result in ¤ xx shows  that
$f\colon Y\to D$ is biholomorphic.
Around $y_0$ we choose a small chart
$(\Delta,z)$ and get the non-zero complex derivative 
$f'(0)$
of $f$ at $z=0$.
With
\[
f^*=\frac{1}{f'(0)}\cdot f\tag{4.2.1}
\] 
we have a 
biholomorphic mapping from $Y$ into the open disc of radius
$|f'(0)|$
and  the $f^*$-derivative at $z=0$ is one.




\medskip

\noindent
{\bf{5.3 A global construction.}}
By ¤ xx we can exhaust $X$ with an increasing sequence of
relatively compact open subsets
$\{Y_n\}$ which are Runge and Dirichlet regular.
Fix a point $p\in Y_0$
and a local chart $(\Delta,z)$ as above.
For each $n\geq 0$  (5.2.1) gives some $r_n>0$ and a biholomorphic map
\[
f_n\colon Y_n\to D(r_n)
\]
where $f_n(p)=0$ and $f'_n(0)=1$.
The inverse mapping $f_n^{-1}$
is holomorphic in the open disc $D(r_n)$
and we notice that the complex derivative
\[
(f_n^{-1})'(0)=1\tag{i}
\]
Next, to each $n\geq 0$ we have the  composed function
\[
h_n= f_{n+1}\circ f_n^{-1}
\]
which maps $D(r_n)$ into $D(r_{n+1})$
where $h_n(0)=0$ and (i) gives
$h'_n(0)=1$. Schwarz'  inequality implies that 
\[
r_n\leq r_{n+1}
\]
Set
\[ 
R= \lim_{n\to\infty}\, r_n
\]
We shall construct a biholomorphic map
$f^*\colon X\to D(R)$  where the case $R=+\infty$ means that
$D(+\infty)={\bf{C}}$.
To find $f^*$ we shall pass to certain subsequences of 
$\{f_n\}$.
Consider first the composed functions
\[
g_n= \frac{1}{r_0}\cdot f_n\circ f_0^{-1}(r_0z)
\]
which by the choice of $r_0$ and the inclusion $Y_0\subset Y_n$ are
holomorphic in the open unit disc $D$ of the complex $z$-plane.
It is clear that
we have
\[
g_n(0)=0\quad\colon g'_n(0)=1
\]
Moreover, $g_n$ is a biholomorphic map from
$D$ onto the
open set $r_0^{-1}\cdot f_n(Y_0)$.
By the  result from ¤ xx  $\{g_n\}$ is a normal family in the sense lof
Montel. Hence we can extract a subsequence
$\{g_{n_k}\}$ which converges uniformly on compact subsets
of $D$.
\medskip

\noindent
{\bf{5.4 Exercise.}}
Verify that
the convergence of $\{g_{n_k}\}$  above entails that
$\{f_{n_k}\}$  converges uniformly over compact subsets of $Y_0$
to a limit function $f^*_0\in\mathcal O(Y)$.
Moreover, since
each restriction $f_{n_k}|Y_0$
is biholomorphic and the derivatives
$f'_{n_k}$ at $p$ all are equal to one, 
it follows from
the result in ¤ xx that
$f^*_0\colon Y_0\to f_0^*(Y_0)$ is biholomorphic.
\bigskip

\noindent
Next, starting with the sequence 
\[
g_k= r_1^{-1}\cdot f_{n_k}\circ f_1^{-1}
\]
we repeat the arguments above and find
a subsequence $\{\phi_{k_j}\}$ which conveges uniformly  in the unit disc
and
returning  to the $f$-sequence,  its corresponding  subsequence
converges uniformly on $Y_1$ to a limit function
$f^*_1$ which yields a biholomorphic map from
$Y_1$ onto $f^*_1(Y_1)$.
We  continue  
by an induction over $n$ and 
obtain  biholomorphic maps $\{f^*_n\colon Y_n\to f^*_n(Y_n)\}$ 
and after the passage to a  "diagonal subsequence" we find
a subsequen ce $\{f_{n_k}\}$ which converges uniformly on compact subsets of
$x$ to a limit function $f^*$ which gives the requested biholomorphic map
from $X$ onto $D(R)$.

 
\end{document}
























 




















 








  
  
 



































\newpage







































Sheaves and currents will be used in the subsequent proofs.
The crucial result in this chapter are  the following vanishing theorems.

\medskip

\noindent
{\bf{0.1 Theorem.}}
\emph{For every non-compact Remann surface one
has
 $H^1(X,\mathcal O)=0$.}
\bigskip

\noindent
Next, let $\mathcal O^*$ be the multiplicative sheaf whose sections
are zero-free holomorphic functions.

\medskip


\noindent
{\bf{0.2 Theorem.}}
\emph{The cohomology group $H^1(X,\mathcal O^*)=0$.}
\medskip

\noindent
A locally free sheaf of $\mathcal O$-modules of rank one is called
a holomorphic line bundle
As explained in ¤ xx the family of holomorphic line bundles
correspond to elements in
$H^1(X,\mathcal O^*)=0$. So Theorem 0.2 means that
every holomorphic line bundle $\mathcal L$
is holomorphically trivial
and as a sheaf  therefore isomorphic to
$\mathcal O$ which by Theorem 0.1 entails that
\[
H^1(X;\mathcal L)=0\tag{*}
\]


\noindent
However, to  prove Theorem 0.2 we shall  need 
(*) and we shall later on explain how
(*) can be established in a similar way as in the special case
$\mathcal L=\mathcal O$.
\medskip

\noindent
{\bf{0.3 Some  cohomology groups.}}
The sheaf $\Omega$ is a locally free sheaf of $\mathcal O$-modules of rank one
and there is  the exact sequence of sheaves:
\[ 
0\to {\bf{C}}_X\to \mathcal O\overset\partial\to \Omega\to 0
\]
Passing the the long exact sequence of cohomology
the vanishing in
(*)  entails that
\[ 
H^2(X,{\bf{C}}_X)=0
\]
From this
it follows trivially - see ¤ xx - that
if the complex field ${\bf{C}}$ is replaced by the field of rational numbers
then
\[
H^2(X,Q_X)=0\tag{i}
\]
Next,   the exponential map
which sends a holomorphic function $f$ to
the zero-free function $e^{2\pi i f}$
gives an exact sequence of sheaves:
\[
0\to {\bf{Z}}_X\to \mathcal O\overset{\text{exp}}\to \mathcal O^*\to 0
\]
Passing to the long exact sequence of cohomology  we get
\[
H^1(X,\mathcal O^*)\simeq
H^2(X,{\bf{Z}}_X
\]
So Theorem 0.2 anounts to show that
the last cohomology group is zero.
We have already  (i) so 
Theroem 0.2 is
"almost" derived from 
(*).
However, extra arguments will be needed to 
get Theorem 0.2 which we begin to explain.
Let  $\mathcal L$
ibea holomorphic line bundle.
By definton it is trivial, i.e. isomorphic to $\mathcal O$ if and only if it
has a global generating section.
Suppose to begin with that one has found
a non-constant global section $\xi\in \mathcal L$.
The zeros of $\xi$ is some (possibly empty) discrete set in $xX$.
Let $\{q_\nu\}$ be these zeros and $\xi$ vanishes of some
order $k_\nu$ at $q_\nu$.
Suppose we have
found
a meromorphic function $g$ in $X$
with poles of order $k_\nu$ at every
 $q_\nu$ while $g$ is a zero-free holomorphic function outside this
 discrete set.
 Then $g\cdot \xi\in\mathcal L(X)$ is 
 a global section which gives the requested
trivialisation so that
 $\mathcal L\simeq \mathcal O$.
 So in order to get Theorem 0.2 we need to 
 prove the existence of globally defined meromorphic functions
 with prescribed
 poles on  discrete subsets  of  $X$.
The whole discussion has shown that Theorem 0.2 follows if we in addition to
Theorem 01 and its extension in  (*) have established the following:
\medskip

\noindent
{\bf{0.4 Theorem.}}
\emph{Every divisor $D$ on $X$ is principal, i.e.
equal to $D(f)$ for some
$f\in\mathfrak {M}(X)$.}

 
 
\bigskip


\noindent
{\bf{0.5 Runge's theorem.}}
Recall from ¤ xx that an open subset $Y$ in $X$ is a Runge domain if
every connectd component of the closed complemnet $X\setminus y$
is non-compact. The following result will
be used to prove Theorem 0.1 and  has also independent interest:

\medskip

\noindent
{\bf{0.6 Theorem.}}
\emph{Let $Y\subset X$ be a Runge domain.
Then
the restriction map $\mathcal O(X)\to \mathcal O(Y)$ has a dense image.}
\bigskip

\noindent
The results above constitute the
major facts in this section.
To prove Theorem 0.1  we first establish  seeemingly weaker results
and after 
finish the proofs of the the other  results.
\medskip

\centerline{\bf{¤ 1. A finiteness result.}}

\medskip

\noindent
Consider
an connected open subset $Y$ 
which is relatively compact in
$X$. The boundary
$\partial Y$
is  compact but in general it need not be connected.
It can for example consist of a finite number of pairwise disjoint
and closed Jordan curves
together with some Jordan arcs and
some isolated points, like an annulus where
a finite set of points in the open annulus have been
removed.
If $\partial Y$
is "nice", for example piecewise analytic
then
tthe cohomology group
$H^1(Y,{\bf{C}})$ is a finite dimensional complex vector space.
Recall also from ¤ xx that one has
the isomorphism
\[
\frac{\mathcal E^1(Y)}{d(\mathcal E(Y))} \simeq
H^1(Y,{\bf{C}})
\]
and
as explained in ¤ xx there exists   an injective map
\[
\frac{\mathcal E^{0,1}Y)}{\bar\partial(\mathcal E(Y))}\to
H^1(Y,{\bf{C}})
\]
Moreover, Dolbeault's Theorem   identifies
right hand side with
$H^1(Y,\mathcal O)$ and hence
this cohomology group is finite dimensional
for every $Y$ as above with a nice compact boundary.
The finite-dimensionality
enable us to construct non-constant meromorphic functions on
$Y$.
Namely, if $p\in Y$ is fixed we
take a positive integer $N$ and
the sheaf $\mathcal O_D$ where $D$ is the divisor
$N\cdot p$ which means that one allows a pole of order
$\leq N$ at $p$.
Exactly as in the compact case from ¤ xx one has an exact sequence
\[ 
0\to \mathcal O(Y)\to \mathcal O_D(Y)
\to {\bf{C}}^N\to H^1(Y,\mathcal O)\to H^1(Y,\mathcal O_D)\to
0
\]
If $N$ is strictly larger than
the dimension of
$H^1(Y,\mathcal O)$ we  get a non-zero
section of  $\mathcal O_D$, i.e. a meromorphic
function
in $Y$
with a pole of order
$\leq N$ at $p$ and otherwise  holomorphic.


\bigskip


\centerline{\bf{ ¤ 2. A vanishing lemma.}}
\medskip

\noindent
Consider a pair  $Y\subset Y_1$ 
where $Y$ is relatively compact in $Y_1$.
As explained in ¤ xx one has  the restriction map

\[
\mathcal L\colon H^1(Y_1,\mathcal O)\to 
H^1(Y,\mathcal O)\tag{2.1}
\]
\medskip

\noindent
{\bf{2.2 Proposition.}}
\emph{If $H^1(Y;\mathcal O)$ is finite dimensional
the $\mathcal L$-image in (2.1) is zero}
\medskip

\noindent
\emph{Proof.}
Choose $\xi_1,\ldots,\xi_K$ in  
$H^1(Y_1,\mathcal O)$ such that
$\{\mathcal L(\xi_k)\}$
gives a basis for the  $\mathcal L$-image
in the finite dimensional vector space
$H^1(Y;\mathcal O)$.
Next, we can find
a 
relatively compact set
$Y_2$ in $X$ where $Y_1<< Y_2$
and $\partial Y_2$ is "nice" so that
$H^1(Y_2,\mathcal O)$ is finite dimensional.
Fix a point $p\in Y_2\setminus Y_1$ and from ¤ 1 we 
find
a meromorphic function
$f$
in $Y_2$ 
which restricts to a holomorphic funtion in
$Y_1$
which is not constant  on the connected components of this set.
Now we get the vectors
$\{f\cdot \xi_k\}$  in $H^1(Y_1,\mathcal O)$
and take  their $\mathcal L$-images.
Since we have chosen a basis above 
there is an $N\times n$-matrix $B$ with complex
elements such that

\[ 
\mathcal L(f\cdot \xi_k)=\sum_{j=1}^{j=N}\,
b_{kj}\cdot \mathcal L(\xi_j)\tag{i}
\]
Let us now consider
the holomorphic function in $Y_1$ defined by 
\[ 
F=\det(f\cdot E_N-B)
\]
Then (i) and Cramer's rule entail that
\[
\mathcal L(F\cdot \xi_k)=0\quad\colon\, 1\leq k\leq N\tag{ii}
\] 
Above $F$ is meromorphic in $Y_2$ with no poles
in the relatively compact subset $Y_1$.
We can therefore cover $Y_1$ with a finite number of charts
$\mathfrak{U}= \{U_\alpha\}$
such that
$F$ has no zeros in
non-empty intersections $U_\alpha\cap U_\beta$ when
$\alpha\neq \beta$.
Let us then take some $\eta\in H^1(Y_1,\mathcal O)$ which by 
Lerays theorem is represented by a cocycle
$\{\phi_{\alpha,\beta}\}$
in $Z^1(\mathfrak{U},\mathcal O)$.
Since $F\neq 0$ on each non-empty intersection we get  the cocycle
$\{\psi_{\alpha,\beta}= F^{-1}\cdot \phi_{\alpha,\beta}\}$
which represents a vector in $H^1(Y_1,\mathcal O)$ denoted by
$\eta^*$.
From  these  constructions we get
\[ 
\mathcal L(\eta)=\mathcal L(F\cdot \eta^*)
\] 
By (ii) the last term is zero and since
$\eta\in H^1(Y_1,\mathcal O)$ was arbitrary Proposition 2.2 is proved.

\medskip

\noindent
{\bf{2.3 A $\bar\partial$-equation.}}
Consider a pair $Y<< Y_1$ as above.
Dolbeault's theorem and Proposition 2.2  imply
that every  $\phi\in \mathcal E^{0,1}(Y_1)$
restricts to a $\bar\partial$-exact form on $Y$, i.e.
there exsits $g\in \mathcal E(Y)$ such that
\[ 
\bar\partial g=\phi|Y\tag{2.3.1}
\]
\medskip

\noindent
Now we can establish  a density result:

\medskip

\noindent
{\bf{2.4 Proposition.}}
\emph{Let $Y$ be 
a relatively compact
Runge domain in $X$. Then, for every $Y_1$
sich that $Y< Y_1$ and $H^1(Y_1,\mathcal O)$ is finite dimensional
it follows that  the restriction map from 
$\mathcal O(Y_1)$ to $\mathcal O(Y)$ has a dense image.}
\bigskip


\noindent
\emph{Proof.}
By the Hahn-Banach Theorem it suffices to show that 
for every (1,1)-current $\gamma$ with  some compact support $K$  in $Y$
one has the implication
\[ 
\gamma(f|Y)=0\quad\forall \,\, f\in \mathcal O(Y_1)\implies
\gamma|\,\mathcal O(Y)=0\tag{i}
\]
Consider a current $\gamma$ as above which vanishes on
each restricition of $f\in\mathcal O(Y_1)$
to $Y$ and let  $k$ be its compact support in $Y$.
Next,  choose an open set $Y_2$
where $Y_1<< Y_2$ and (2.3.1)
holds for this pair. So when
$\phi\in \mathcal E^{0,1}(X)$
there exists
$g\in \mathcal E(Y_1)$ such that
\[
\bar\partial g=\phi|Y_1
\]
Above $g$ is unique up to a
function in $\mathcal O(Y_1)$ and since
$\gamma$  vanishes on
$\mathcal O(Y_1)|Y$ 
the evaluation $\gamma(g)$ only depends upon $\phi$.
Hence there exists a current $S$ on $X$
defined by
the process above, i.e.
\[
S(\phi)= \gamma(g|Y)\quad\colon\,\bar\partial g=\phi|Y_1
\]
If $h\in C_0^\infty(X\setminus K)$
we get the $(0,1)$-form
$\bar\partial(h)$ and by the constructions above
\[ 
S(\bar\partial h)= \gamma(h|Y)=0
\] 
where the last equality follows since
$\gamma$Êis supported by $K$.
This means that the current $S$ is $\bar\partial$-closed in
$X\setminus K$ and since $\bar\partial$ is elliptic
the restricttion of $S$
 to $X\setminus K$ is expressed by a holomorphic 1-form
$\sigma\in \Omega(X\setminus K)$.
So far we have not used the assumption that $Y$ is Runge.
To profit upon this we consider
the compact hull
$\mathfrak{h}(K)$ from ¤ XX.
If
$y\in Y\setminus \mathfrak{H}(K)$  
the connected component $V$
in
$X\setminus  K$ which contains $y$ is non-compact.
Since the current $S$ has  compact support it follows that
\[ 
V\setminus \bigl(\text{Supp}(S)\cup K\bigr)\neq \emptyset\tag{ii}
\]
Now $\sigma$ respresents $S$ outside $K$
and  therefore it must vanishes in
the open set (ii).
By analyticity $\sigma$ vanishes in the whole connected
set $V$ and hence in a neighborhood of $y$.
Since $y$ was arbitrary we conclude that 
$\sigma$ vanishes identically in
$Y\setminus \mathfrak{h}(K)$.
Let us now consider some
$f\in \mathcal O(Y)$ and 
take
$g\in C_0^\infty(Y)$ where
$g=f$  in an open neighborhood of
$\mathfrak{h}(K)$.
It follows that
\[ 
S(\bar\partial(g))=\gamma(g|Y)= \gamma(f)
\] 
where the last equality holds since
$K$ is the support of $\gamma$.
Finally, since
$f$ is holomorphic we have $\bar\partial g=0$ in a neighborhood of
$\mathfrak{H}(k)$
and since $\sigma$ is supported by $\mathfrak{h}(K)$ it follows that
$S(\bar\partial(g))=0$. Hence 
$\gamma(f)=0$ for every $f\in \mathcal O(Y)$
which proves the requested implication (i)
above and hence the density in
Proposition 2.4.



\medskip

\noindent
{\bf{Remark.}}
 The
 proof above
 is attributed to Malgrange and  we  followed
 the presentation in  [Forster: page xx-xx].
 \bigskip
 
\noindent
{\bf{2.5 The case of locally free $\mathcal O$-modules.}}
If $\mathcal L$ is 
a locally free sheaf of $\mathcal O$-modules with rank one
similar results as above hold. Theproofs are more or less verbatim.
More precisely we first have some locally finite covering
$\mathfrak{U}=\{U_\alpha\}$ by simply connected charts
and $\mathcal L|U_\alpha$ are trvial for every $\alpha$, i.e.
there exists a section $\rho_\alpha\in\mathcal L(U_\alpha)$
such that the restricted sheaf
$\mathcal L|U_\alpha$ is the free
$\mathcal O_{U_\alpha}$-module 
generated by $\rho_\alpha$.
Shrinking $\mathfrak{U}$ if necessary we may assume that
the transistion functions which give
\[
\rho_\beta= \phi_{\beta\alpha}\cdot \rho_\alpha
\]
 in each non-empty intersection $U_\beta\cap U_\alpha$ yiled bounded
 holomrphic functions, i.e. the maximum norms
 \[
 || \phi_{\beta\alpha}||_{U_\beta\cap U_\alpha}<\infty
\]
When
this holds it is meaningful to speak about convergence for $\mathcal L$-valued sections.
More precisely, let 
$Y<< Y_1$ and $\{\rho_\nu\in\mathcal (Y_1)\}$
be given. If $\rho_*\in \mathcal L(Y)$ and $K$ is a compact subset
of
$Y$ we leave it to the reader to
clarify the condition that $\{\rho_\nu|K$ converges in a uniform way to
$\rho|K$, i.e. u
Thus, in Propostion 22and 2.4 we can replace $\mathcal O$ by
any $\mathcal L$. Concerning (2,3,1) we ntocie that
there exists the sheaf
\[
 \mathcal E_\mathcal L= 
 \mathcal O_\mathcal L\otimes_\mathcal O\,\mathcal E
\]
and
a well  defined map
\[
\bar\partial\colon\mathcal E_\mathcal L\to \mathcal E^{(0,1)}_\mathcal L
\]
So now (2,3,1) means that if $\phi\in \mathcal E^{(0,1)}_\mathcal L(Y_1)$
then there exists
$g\in \mathcal E_\mathcal L(Y)$ such that
\[
\bar\partial(g)=\phi|Y
\]





\centerline{\bf{2.5 Proof of Theorem 0.1}}
\medskip

\noindent
By  ¤ XX we  exhaust $X$ by an increasing sequence of Runge domains
$\{Y_n\}$
where $Y_n<<Y_{n+1}$ and $\{H^1(Y_n,\mathcal O)\}$ are finite dimensional.
Consider
some $\phi\in \mathcal E^{0,1}(X)$. Now (2.3.1) applies to each
piar $Y_n<< Y_{n+1}$ and since $\phi$ restricts to 
$\mathcal E^{(0,1)}(Y_{n+1}$
there exists
$f_n\in \mathcal E(Y_n)$
such that 
\[
 \bar\partial f_n=\phi|Y_n
\]
It follows that
the restriction to $Y_n$ of $f_{n+1}-f_n$ is holomorphic.
Now $Y_{n-1}<< Y_n$ and
Proposition 2.4 entails that
this restricted holomorphic function can be uniformly approximated on
$Y_{n-1}$ by functions from $\mathcal O(Y_{n+1}$.
In particular we find
$g_{n+1}\in \mathcal O(Y_{n+1})$
such that the maximum norm
\[
||f_{n+1}+g_{n+1}-f_n||_{Y_{n-1}}<2^{-n}
\]
With $f^*_{n+1}= f_{n+1}+g_{n+1}$
we still have
\[
\bar\partial f^*_{n+1}=\phi|Y_{n+1}
\]
Pwerforibng these modfifications inductively we get
anew sequence $\{f^*_n\}$ where  (xx) hold for every $n$
while
\[
||f^*_{n+1}-f^*_n||_{Y_{n-1}}<2^{-n}
\quad\colon \, n=1,2,\ldots
\]
It follows that $\{f_n^*\}$ converge uniformly on $X$ to a continuous function
$F$.
This entials that
the distributuons
$\\bar\partial f_n^*\}$ converge to the distribution derivative
$\bar\partial (F)$ and by (xx) it is clear that
the following hold on the whole of $X$:
\[ 
\bar\partial(F)=\phi
\]
Now $\phi$ is a smooth form and the elliptic property of
$\bar\partial$ implies that
$F$ is a $C^\infty$-function. Hence the mapping
\[ 
\bar\partial\colon \mathcal E(X)\to \mathcal E^{(0,1)}(X)
\]
is surjective.
Dolbeaualt's theorem gives  $H^1(X,\mathcal O)=0$
and Theorem 0.1 is proved.
\medskip

\noindent
{\bf{2.7 Exercise.}}
Use the remarks from ¤ 25.5
and repeat the methods above to show that
\[
H^1(X,\mathcal L)=0
\] 
for every locally free sheaf of $\mathcal O$-modules with rank one.



\newpage




\newpage





Weierstrass product formula asserts that
 every divisor on $X$ is principal-
 

By a differentalble 1-chain in $X$ we mean a map 
$t\to c(t)$ from the unit interval $[0,1]$ with values in $X$ which
has a continuous derivative. The 1-chain is denoted by
${\bf{c}}$. 
The end points $q=c(0)$ and $p=c(1)$ can be either equal or
different and it is not assumed that
the map $t\to c(t)$ is 1-1, i.e. the  image curve
can   have several "self-intersections".
If $\omega$ belongs to $\mathcal E^1(X)$, i.e. a smoooth 
differential 1-form, then  we take its pull-back to $[0,1]$ and
obtain the integral
\[ 
\int_{{\bf{c}}}\, \omega\tag{1}
\]
Notice that
(1) yields a 1- current of since
$\omega\mapsto \int_{{\bf{c}}}\, \omega$ is a continuous linear form
and the current is supported by the compact image under the $c$-map.
We can construct other compactly supported 2-currents
as follows:
Let $p_1,\ldots,p_k$ be a finite set of points in $X$
and $U$ some relalitively  compact open  subset which contains
this $k$-tuple.
Now we consider a global section $\psi$of the sheaf
$\mathfrak {M}\otimes_\mathcal O\, \mathcal E$
with the following properties:
First $\psi$ is a zero-free $C^\infty$-function in
$X\setminus \{p_1,\ldots,p_k\}$ and it is identically one
in $X\setminus U_*$ where $\overline{U_*}$ is a compact subset of $U$.
Finally, if $(\Delta,z)$ is a small chart centered at some $p_\nu$ then
\[
 \psi|\Delta= z^{e_\nu}\cdot \psi_\nu(z)
\]
where $e_\nu$ is
some integer and $\psi_\nu$ a zero-free $C^\infty$-function in $\Delta$.
Here $e_\nu$ can be positive or negative.
Now there exists the current
\[ 
\gamma= \frac{\partial \psi}{\psi}
\]
Since $\psi=1$ in $X\setminus U$
the support of this current is contained in the compact set
$\overline{U_*}$. By defintion
\[ 
\gamma(\omega)=
 \omega\wedge \frac{\partial \psi}{\psi}
\] 
for every smooth 1-foirm $\omega$.
In the case when 
there exists $g\in\mathcal E(U)$ such that 
$\omega=d g$ holds in $U$ we have:
\[
\gamma(\omega)=\int \,dg\wedge \frac{\partial \psi}{\psi}=
\int \,\bar\partial(g) \wedge \frac{\partial \psi}{\psi}
\]
where the last equality follows since
$dg=\partial g+\bar\partial g$ and
the exterior product
$\partial(g) \wedge \frac{\partial \psi}{\psi}=0$.

\medskip

\noindent
{\bf{0.6.7 Exercise.}} Apply Stokes Theorem and show that (x) is equal to
\[ 
-2\pi i\cdot \sum\, e_\nu\cdot g(p_\nu)
\]
So in the special case when
the 1-current $\gamma$ satisfies
\[
\int_{\bf{c}}\, dg=
\gamma(dg)\quad\colon g\in \mathcal E(X)\tag{0.6.7}
\]
it follows that
$\{p_\nu\}$ is reduced to the pair $q,p$ where
$e_q=1$ and $e_p=-1$.
In ¤ xx w shall prove that
when ${\bf{C}}$ is given as above then
there existd
a $\psi$-.function such that 
(0.6.7) holds and this turns out to be the key point in  the
proof of
Weierstrass' result in (0.3).







\newpage

































\centerline{\bf{I. Non-compact Riemann surfaces}}



\bigskip


\noindent
{\bf{Introduction.}}
A Riemann surface is a 1-dimensional and connected complex manifold $X$.
Here we  shall consider open  surfaces, i.e.  the topological space $X$ is non-compact.
The major result about open Riemann surfaces
is a vanishing theorem due to Behnke and Stein 
from their article in the article  \emph{Entwicklungen analytischer Funktionen
auf Riemannschen FlŠchen} [Math. Ann. 120 (1948)].
It asserts that
if $\mathcal O_X$ is the sheaf of holomorphic 
functions on an open Riemann surface, then
the cohomology group
\[
H^1(X,\mathcal O_X)=0\tag{*}
\]
Next, let ${\bf{C}}_X$ be the sheaf
whose sections are locally constant complex-valued functions
and consider
the cohomology group
$H^1(X,{\bf{C}}_X)$.
If it vanishes we shall prove
that the open Riemann surface is biholomorphic with
the open unit disc $D$ or the complex plane
${\bf{C}}$.
One refers to this fact  as the \emph{Uniformisation Theorem} for open
Riemann surfaces.
The proof is given 
in ¤ 5.
\medskip

\noindent
A crucial result which is used to prove (*) is the Pompieu theorem which
asserts thst the $\bar\partial$-operator is sirjhective on planar domains, i.e.
if $\Omega$is an open subset of
${\bf{C}}$ and $\phi$ is a complex-valued $C^\infty$-function on $\Omega$
then
there exists $g\in C^\infty(\Omega)$ such that
\[
\bar\partial g/\partial \bar z=\phi
\]









\medskip

\noindent
The uniformisation theorem has
several consequences.
An example is 
\emph{The Riemann-Schwarz inequality} when an open Riemann surface
$X$ is equipped with a hyperbolic metric,
This result goes
as followss:
Let $\sigma$
be 
a hyperbolic metric. This  means
that
$\sigma $ has  
a negative curvature.
An equivaent condition is that in each open chart
$(U,z)$ of $X$
where $U$ is identified with an open subset of
the complex $z$-plane, there exists a subharmnic function $u(z)$ such that
the $\sigma$-distance  in $U$ is defined by
\[
e^{u(z)}\cdot |dz|
\]
where
$|dz|$ the ordinary euclidan length.
Assume that $\sigma$ is hyperbolic and consider a
pair of points $p,q$ in $X$. Denote by 
$\mathcal C(p,q)$ the family of
curves in $X$ with end-points at $p$ and $q$.
\medskip

\noindent
{\bf{0.1 Theorem.}}
\emph{For every pair
$\gamma_1,\gamma_2$ in  $\mathcal C(p,q)$
and
each point $\xi\in\gamma_1$,
there exist  a pair of curves $\alpha,\beta$, where
$\alpha\in\mathcal C(p,q)$ while $\beta$ has end-points
at $\xi$ and some point $\eta\in \gamma_2$ such that}
\[
\ell(\alpha)^2+\ell(\beta)^2\leq
\frac{1}{2}\bigr (\ell(\gamma_1)^2+\ell(\gamma_2)^2\,\bigl )\tag{*}
\]
\emph{where $\ell(\gamma)$ denotes the $\sigma$-length of a curve in $X$.
Moreover, the inequality (*) is strict with the exception for
special rhombic configurations.}
\medskip

\noindent
{\bf{Remark.}}
The theorem gives in particular  existence of unique geodesic  curves
on $X$ which join a pair of points.
The proof relies upon the
uniformisation theorem 
which
reduces the 
proof to show the following: 
\medskip

\noindent
{\bf{0.2}} \emph{Let
$D$ be the unit disc and $0<\theta<\pi/2$ and consider   the unique
circle $C_\theta$ which
contains
$e^{i\theta}$
and $e^{-i\theta}$ and intersects the unit circle at right angles at these points.
Let $\alpha$ denote the circular subarc of $C_\theta$  contained in
$D$.
Then the following inequality holds for
every subharmonic function $u$ in $D$:}
\[
\bigl(\int_{-1}^1\, e^{u(x)}\, dx\bigr)^2+
\bigl(\int_\alpha\, e^{u(z)}\, |dz|\bigr)^2\leq
\frac{1}{4}\cdot\bigl( \int_0^{2\pi}\, e^{u(e^{i\phi})}\,d\phi\bigr)^2
\] 
\bigskip

\noindent
We prove this result in ¤ xx and
how one derives Theorem 0.1 from (0.2).


\medskip

\noindent
{\bf{A comment}}.
Basic facts about sheaves and  calculus on 2-dimensional manifolds
will
be used without hesitation.
Let us  remark that the study of open Riemann surfaces
gives
an excellent illustration to  general theory
related to analysis on manifolds.
For example, sheaf theory has emerged from Weierstrass' constructions of
analytic continuations where the "total sheaf space" $\widehat{O}$ in
¤ x below is an instructive example of a sheaf.
During our whole study
the $\bar\partial$-operator plays a crucial role. On
a Riemann surface it assigns to every
complex valued $C^\infty$-function $f$ the
differential form
$\bar\partial(f)$ of bi-degree $(0,1)$.
The Cauchy-Riemann equations
show that
$\bar\partial(f)=0$ if and only if $f$ is holomorphic. 
The \emph{Pompieu Theorem} for planar domains
is crucial. This classic result asserts that if 
$\Omega$ is an open subset of
${\bf{C}}$ and $f\in C^\infty(\Omega)$ then
there exists
$g\in C^\infty(\Omega)$  such that
\[
\frac{\partial g}{\partial\bar z}=f\tag{0.3.1}
\]
Passing to an open Riemann surface
$X$ we shall prove that 
a similar result holds, i.e. if
$\phi\in \mathcal E^{0,1}(X)$ is a 
smooth differential form of bi-degree $(0,1)$, then
there exists
$f\in C^\infty(X)$  such that
\[
\bar\partial(f)= \phi\tag{0.3.2}
\]
One can express this by saying that every smooth
differential form of bi-degree $(0,1)$ is
$\bar\partial$-exact on an open Riemann surface.
A result due to Dolbeault
implies that the solvability in (0.3.2) for every $\phi$
is equivalent to
the Behnke-Stein Theorem in (*) from the introduction.
A notsble factis that
the inhomogeneus equation (0.3.2) can be solved for
non-smooth $\phi$-froms of bi-degree $(0,1)$.
For example, given a smooth form
$\phi$ as in (0.3.2)  we also take a 
bounded Lebesgue measurable function $\rho$ on $X$
and get the current $\rho\cdot \phi$
of bi-degree $(0,19$ on $X$.
Then it turnd out that there exists
a continuous function $f$ on $X$ such that
\[
\bar\partial(f)= \rho\cdot \phi\tag{0.3.4}
\]
where the left hand side is
the
$(0,1)$-current founf via charts where
distribution derivatives of $f$ appear.








\medskip

\noindent
{\bf{0.4 The Dirichlet problem.}}
A   result due to Rado asserts that
every open Riemann surface has a countable topology.
The proof relies upon
a theorem due to PoincarŽ and Volterra from the appendix about topology,
 together with
solutions to Dirichlet problems.
Here one profits upon Perron's solution 
for planar domains which has the merit that it extends verbatim
to open Riemann surfaces, using the observation
that the complex analytic structure on a
Riemann surface $X$ leads to an intrinsic  notion of
subharmonic functions.
From this we shall describe how to
solve the Dirichlet problem
exactly  as in the planar case.
More precisely, let $\Omega$ be a relatively compact
 open set in
$X$.
A point  $p\in\partial\Omega$Êis regular in the sense of Perron if
there exists
some open chart $D$ in $X$ which contains $p$
and a continuous subharmonic function $u$ in $D$ 
such that 
\[
u(x)<0\,\colon\, x\in U\cap D\quad\colon u(p)=0
\]
\medskip

\noindent
{\bf{0.4.1 Theorem.}}
\emph{If $\Omega$ is a  relatively compact open set
and each boundary point is Perron regular, then
the Dirchlet problem has a solution for
every
$g\in C^0(\partial \Omega)$, i.e. there exists 
a harmonic function $G$ in $\Omega$ with 
continuous boundary values equal to $g$.}
\medskip

\noindent
Let us  finish this introduction by
with some  preliminary considerations
which illustrate the general theory.
\medskip

\noindent
{\bf{0.5. Additive
representations
of fundamental groups in the planar case.}}
Each open and connected set $U$ in ${\bf{C}}$ yields
an open  Riemann surface.
A special case is to take $U={ \bf{C}}\setminus (a_1,\ldots,a_k)$ where
$a_1,\ldots,a_k$ is a finite set of points which have been
removed
from the complex plane. Residue calculus
can be used to describe some topological
properties of $U$.
For each $1\leq\nu\leq k$
the zero-free holomorphic function
$\phi_\nu(z)= z-a_\nu$ in $U$ has a
logarithmic differential 
\[
\frac{\partial\phi_\nu}{\phi_\nu}= \frac{dz}{z-a_\nu}
\]
This  yields a holomorphic 1-form on $U$  which is not
$\partial$-exact, i.e. we cannot find
$g\in\mathcal O(U)$ such that
$\partial(g)= g'(z)dz= \frac{dz}{z-a_\nu}$.
The obstruction stems from the multi-valued behaviour of
$\log (z-a_\nu)$ and  can  also be seen by
residue calculus. Namely, choose a closed
Jordan curve $\gamma$ which surrounds $a_\nu$, i.e. its winding number
is +1 as explained in ¤ xx. Then
\[
\int_\gamma\, \frac{dz}{z-a_\nu}=2\pi i
\] 
On the other hand the closedness of $\gamma$ implies that
\[
\int_\gamma\,\partial g=0\quad\colon g\in\mathcal O(U)
\]
Next,  the fundamental group $\pi_1(U)$
can be identified with homotopy classes of closed curves
with a common intial and terminal point $p\in U$.
Topology teaches that
$\pi_1(U)$ is a free group of rank $k$
with
generators
$\gamma_1,\ldots,\gamma_k$ where
each $\gamma_\nu$ is a closed Jordan curve whose winding
number
with respec to $a_\nu$ is +1 while its winding number
with respect to other $a$-points
are  zero.
Consider
the
family of group homomorphisms
\[
 \rho\colon \pi_1(U)\to {\bf{Z}}\tag{1}
\] 
where
${\bf{Z}}$ is the additive group of integers.
Denote by $\mathcal O^*(U)$
the family of zero-free holomorphic functions in $U$.
If $\gamma$ is a closed curve
at $p$
and
$\phi\in\mathcal O^*(U)$
residue calculus entails that
the line integral
\[
\frac{1}{2\pi i}\cdot \int_\gamma\, \frac{\partial\phi}{\phi}
\] 
is an integer.
Recall that elementary
integration theory from
Chapter II implies that this  line integral only depends upon the
homotopy class of $\gamma$, i.e. 
upon the image $\{\gamma\}$ in $\pi_1(X)$.
Keeping $\phi$ fixed
it follows that
\[
\{\gamma\}\mapsto 
\frac{1}{2\pi i}\cdot \int_\gamma\, \frac{\partial\phi}{\phi}\tag{2}
\] 
is a group homomorphism from
$\pi_1(X)$ into ${\bf{Z}}$.
It turns out that
every such group  homomorphism is
realised by a zero-free $\phi$.
To see this we take the free
basis
$\{\gamma_1\},\ldots,\{\gamma_k\}$
in $\pi_1(U)$
and then every 
$\rho$ in (1) is determined by
a $k$-tuple of integers $e_\nu=\rho(\{\gamma_\nu\})$.
With 
\[ 
\phi(z)= \prod\, (z-a_\nu)^{e_\nu}
\]
we see that $\rho$ is equal to the
group homomorphis  given by (2).
\medskip

\noindent
{\bf{0.6 Line integrals of multi-valued functions.}}
Before  the passage to calculus on Reimann surfaces where one 
contructs
complex line integrals, an intermediate step is to
evaluate complex line integrals of multi-valued functions.
Consider as an example
some complex number
$\alpha$ which is not an integer and
the function $f=z^\alpha$
which is multi-valued in outside the origin.
A local branch  at $z=1$ is chosen so that
$f(1)=1$.
If $g(z)$ is an analytic function defined in
a neighbrhood of the closed unit disc
$\{|z|\leq 1 \}$
we seek the line integral
\[
\int_T\, g(z)\cdot z^\alpha\, dz\tag{1}
\] 
where $T$ is the unit circle oriented in the positive sense, i.e. integration moves 
counter clockwise.
It means that (1) is equal to
\[
i\cdot \int_0^{2\pi}\, g(e^{i\theta}) e^{i\alpha\theta}\, e^{i\theta}\, d\theta
\]
Here $g$ has a series expnasion $\sum\,c_nz^n$
which converges when
$|z|\leq 1$
and for each non-negative integer one has
\[
i\cdot \int_0^{2\pi}\, e^{in\theta} e^{i\alpha\theta}\, e^{i\theta}\, d\theta
=\frac{i}{n+1+\alpha}\cdot (e^{2\pi i\alpha}-1)
\]
Taking a sum over $n$ we evaluate (1).
Wirh $g=1$ we have for example
\[
\int_T\,  z^\alpha\, dz=\frac{i}{1+\alpha}\cdot (e^{2\pi i\alpha}-1)\tag{2}
\] 
If $0<r<1$ and we instead integrate along
the circle $T(r)= \{|z|=r\}$ in the counter clockwise sense,
the reader can verify that
\[
\int_{T(r)}\,  z^\alpha\, dz=\frac{i\cdot r^{1+\alpha}}{1+\alpha}\cdot (e^{2\pi i\alpha}-1)\tag{3}
\] 
Notice that (2) and (3) differ even though the closed sucrves
$T$ and $T(r)$ are homotopic in the punctured complex plane.
So the usual invariance for line integrals of single-valued analytic functions
fails.
Following original contructions by Riemann one can
explain this by regarding the universl covering space of
$\widehat{X}= {\bf{C}}\setminus \{0\}$
where $z^\alpha$ becomes a single valued holomorŒphic functions
but when the closed curves
$T$ and $T(r)$ are lifted to $\widehat{X}$ they are no longer
closed and have different end-points on
$\widehat{X}$ 
where $z^\alpha$ takes distinict values and this
explains why $(2)\neq (3)$.
\medskip


\noindent
{\bf{0.7 An extension to Riemann surfaces.}}
An open Riemann surface
$X$
has  a fundamental group $\pi_1(X)$ and we consider the family 
$\mathcal F$ of group homomorphisms
$\rho\colon \pi_1(X)\to {\bf{Z}}$.
Identify $\pi_1(X)$ with homotopy classes of closed curves
which start and terminate at some point $p\in X$.
Denote by $\mathcal O^*(X)$
the family of globally defined and zero-free holomorphic functions on $X$.
\medskip

\noindent
{\bf{0.7.1 Theorem.}}
\emph{For each $\rho\in\mathcal F$ there
exists $\phi\in \mathcal O^*(X)$
such that}
\[
\rho(\{\gamma\})=\frac{1}{2\pi i}\cdot \int_\gamma\, \frac{\partial\phi}{\phi}
\quad\colon \, \{\gamma\}\in \pi_1(X)\tag{*}
\]
\emph{where $\{\gamma\}$ is the homotopy class of a closed curve.}
\medskip

\noindent
{\bf{Remark.}}
The proof of Theorem 0.7.1   relies upon the exact sheaf sequence
\[
0\to {\bf{Z}}_X\to \mathcal O\overset{\text{exp}}\to \mathcal O^*\to 0
\]
where
${\bf{Z}}_X$ is the sheaf whose sections are ocally constant integer-valued functions
and 
we have used the exponential map which 
sends  holomorphic function $f$ defined in  open
subsets $U$ of $X$  to  
$e^{2\pi i f}$ which  are   sections of the multiplicative sheaf
$\mathcal O^*$ of  zero-free holomorphic functions.
Passing to the long exact sequence of cohomology one gets an exact sequence
\[ 
0\to {\bf{Z}}\to
\mathcal O(X)\overset {\text{exp}}\to \mathcal O^*(X)\to
H^1(X,{\bf{Z}})\to
H^1(X,\mathcal O)\to\ldots 
\]
Admitting
the vanishing theorem by
Behnke and Stein this entails that
\[
H^1(X,{\bf{Z}})\simeq \frac{\mathcal O^*(X)}{
\text{exp}(\mathcal O(X))}\tag{i}
\]
Next, we have the sheaf
$\Omega$ whose sections are holomorphic 1-forms
and an  exact sheaf sequence
\[
0\to {\bf{C}}_X\to \mathcal O
\overset{\partial} \to \Omega\to 0
\]
where ${\bf{C}}_X$ is the sheaf whose sections are locally constant
complex-valued functions.
Here the Behnke-Stein theorem gives
the isomorphism
\[
H^1(X,{\bf{C}})\simeq \frac{\Omega(X)}{\partial(\mathcal O(X)}\tag{ii}
\]
Next, if $g\in \mathcal O^*(X)$ one easily verifies that
the holomorphic
1-form
$\frac{\partial g}{g}$ is $\partial$-exact if and only if
$g= e^{2\pi if}$ for some $f\in\mathcal O(X)$.
Hence  (i-ii)  give a canonically defined and injective map
\[ 
H^1(X,{\bf{Z}})\to H^1(X,{\bf{C}})\tag{iii}
\]

\noindent
From this one  gets  Theorem 0.7.1
via a similar representation for the family 
$\mathcal F_{{\bf{C}}}$
of group homomorphisms from $\pi_1(X)$ into  the additive group
of complex numbers.
More precisely, to each $\rho\in \mathcal F_{{\bf{C}}}$
we shall prove that there exists
$\omega\in \Omega(X)$ such that
\[
\rho(\{\gamma\})=\frac{1}{2\pi i}\cdot \int_\gamma\, \omega
\]
Here $\omega$ is unique up to a $\partial$-exact holomorphic 1-form
and it turns out that
$\omega$ can be represented as the logarithmic differential of a zero-free
holomorphic function if and only if the
$\rho$-function in (*) is integer-valued.


\newpage

\centerline{\bf{¤ 1. Summary of some major constructions and results.}}

\bigskip


\noindent {\bf{1.1 The sheaf  $\widehat{\mathcal O}$.}}
An  extensive family   of open Riemann surfaces
arises via a construction due to Weierstrass.
For each point $z\in{\bf{C}}$
one has the 
space $\mathcal O(z)$ of germs of analytic functions at $z$.
Weierstrass total sheaf space is defined  by
\[
\widehat{\mathcal O} =\bigcup_{z\in {\bf{C}}} \,
\mathcal O(z)
\]
One has the projection $\pi\colon \widehat{\mathcal O}\to  {\bf{C}}$
with inverse fibers
$\pi^{-1}(z)=\mathcal O(z)$.
Now $\widehat{\mathcal O}$ becomes a complex manifold
where $\pi$ is locally biholomorphic.
Charts consist  of  pairs $(\Delta,f)$ where
$\Delta$ is an open disc in
${\bf{C}}$ and $f\in \mathcal O(\Delta)$
whose corresponding
open  set in
$\widehat{\mathcal O}$ are the
points $\{(z,f_z)\colon z\in \Delta\}$
where $f_z\in\mathcal O(z)$ denotes the germ determined by $f$
at a point $z\in\Delta$.
\medskip

\noindent
Every
open and connected subset of $\widehat{\mathcal O}$
gives an open  Riemann surface.
As an example one has the Riemann surface
attached to the multi-valued function $\log z$.
At $z=1$ we start with the local branch of $\log z$.
whose value is zero.
Now $\log z$ extends to a multi-valued function in
${\bf{C}}\setminus \{0\}$
and in $\widehat{\mathcal O}$ we get the connected
open set
$\mathcal L$ whose points are pairs $(p,f)$ where
$p\in {\bf{C}}\setminus \{0\}$ and $f$ is a local branch of $\log z$
at $p$.
Here $\pi\colon \mathcal L\to {\bf{C}}\setminus \{0\}$
is surjective where  each inverse fiber is a copy of the set of integers which reflects
the property that
local branches of the  log-function 
differ by integer-multiples of $2\pi$.
\medskip

\noindent
{\bf{Exercise.}}
Show that $\log z$ yields a single-valued holomorphic function
$\widehat{\log}$ on the open Riemann surface
$\mathcal L$ and the map
\[
p\to \widehat{\log}(p)
\] 
from $\mathcal L$ into the complex plane ${\bf{C}}$  is biholomorphic.
In topology it means that $\mathcal L$ can be taken as the
universal covering space of the punctured complex plane and
(*) gives a first example
of the uniformisation theorem applied to the simply connected
Riemann surface $\mathcal L$.









\medskip

\noindent
{\bf{1.1.1 The space $M_\Omega(z_0)$}}.
Let $\Omega$ be a  open and connected
subset of
${\bf{C}}$ and consider a point $z_0\in \Omega$. In ¤ xx
we introduced the family of germs 
$M_\Omega(z_0)$ which can
be extended in the sense of Weierstrass along every curve 
$\gamma$ in $\Omega$
with initial point at $z_0$ and some terminal point $z$.
For a pair $(f,\gamma)$ with
$f\in M_\Omega(z_0)$, the analytic continuation along
$\gamma$ gives the germ
the germ $T_\gamma(f)\in \mathcal O(z)$
wihch by definition is a point in $\widehat{\mathcal O}$.
The 
union of these points 
as $\gamma$ varies yields  a connected
open subset of
$\widehat{O}$ denoted by
$\widehat{X}_f$ and called 
the associated Riemann surface of $f$.
Here $\pi\colon \widehat{X}_f\to \Omega$ is surjective
and  the construction gives  a 
\emph{single-valued} holomorphic function
$\widehat{f}$ on $\widehat{X}_f$ where
\[
\widehat{f}(T_\gamma(f))=T_\gamma(f)(z)
\]
when $\gamma$ is a curve with terminal point at $z$.
\medskip


\noindent
{\bf{Example}}.
Remove 0 and 2 from the complex plane
and in $\Omega={\bf{C}}\setminus \{0,2\}$ we have
the multi-valued function
\[
f(z)= \sqrt{z}+ \sqrt{2-z}
\] 
where one starts with the germ at $z=1$ for which
$\sqrt{1}= \sqrt{2-1}=1$.
Under analytic continuation the
germs of the square root functions can change sign
and from this the reader may verify that
$\pi\colon \widehat{X}_f\to \Omega$
is a four-sheeted covering map, i.e. the inverse fibers consist of four points.
\medskip

\centerline{\bf{1.2 The $\bar\partial$-operator.}}
\medskip


\noindent
The complex analytic structure
on a Riemann surface  arises via charts
$(\Delta,z)$ where
$\Delta$ are open discs in a complex $z$-plane and 
equips also 
$X$ with a structure as an oriented $C^\infty$-manifold whose real dimension is two.
Denote by $\mathcal E(X)$
the space of complex-valued $C^\infty$-functions on $X$ and
$\mathcal E^1(X)$ is the space of smooth differential 1-forms.
The exterior differential
$d\colon \mathcal E(X)\mapsto \mathcal E^1(X)$
is a sum
$\partial+\bar\partial$. More precisely, one has 
a direct
sum decomposition
\[
\mathcal E^1(X)=\mathcal E^{1,0}(X)\oplus \mathcal E^{0,1}(X)
\]
and the two differentials:
\[
 \partial \colon \mathcal E(X)\mapsto \mathcal E^{1,0}(X)
\quad\colon\,
 \bar \partial \colon \mathcal E(X)\mapsto \mathcal E^{0,1}(X)
\]
Here   a differential 1-form
$\phi$ has bi-degree $(1,0)$ if its restriction
to a chart
$(\Delta,z)$ is  $a(z)dz$ with
$a\in C^\infty(\Delta)$. Similarly, a 1-form
$\psi$ has bi-degree $(0,1)$ if
$\psi|\Delta= b(z) d\bar z$ with 
$b\in C^\infty(\Delta)$. The
Cauchy-Riemann equations entail that
the $\bar\partial$-kernel on
$\mathcal E(X)$ consists of holomorphic functions.
If $U$ is an open subset of $X$ we denote by
$\mathcal O(U)$ the set of holomorphic functions in
$U$ and by
$U\mapsto \mathcal O(U)$ one gets the sheaf 
$\mathcal O$.
As already announced in the introduction
a  major result about non-compact Riemann surfaces
is the following:

\medskip

\noindent
{\bf{1.2.1 Theorem.}}
\emph{Every $(0,1)$-form on $X$ is $\bar\partial$-exact.}
\medskip


\centerline {\bf{Runge's theorem.}}
\medskip

\noindent
Let $Y$ be an open subset of $X$.
For each compact subset
$K$ of $Y$ we get  connected open components
of $X\setminus K$ and put
\[
\mathcal C^*(K)= \cup\,\Omega_\alpha
\] 
where the union is taken over all components
$\Omega_\alpha$
which are not relatively compact, i.e. the closure $\overline{\Omega}_\alpha$
is not a compact set in $X$.
One says that $K$ is a compact   Runge set in $Y$
if 
\[
\mathfrak{h}(K)=X\setminus \mathcal C^*(K)
\] 
is a compact subset of $Y$.
\medskip

\noindent
{\bf{1.2.2 Theorem.}}
\emph{For every pair $(Y,K)$ where
$K$ is a compact Runge set in $Y$
and each $f\in\mathcal O(Y)$ there exists a sequence
$\{g_n\}$ in $\mathcal O(X)$ such that}
\[
\lim_{n\to \infty}|g_n-f|_K=0
\]
\emph{where we have taken maximum norms over $K$.}

\medskip

\noindent
The two theorems above are proved in ¤ xx and   give rise to 
further results
which we describe below.
\medskip

\noindent
{\bf{Weierstrass' Theorem.}}
A divisor on $X$ consists of a discrete sequence
of points $\{p_\nu\}$ to which one assigns
integers $\{k_\nu\}$  which may be positive or negative.
A globally defined and non-constant meromorphic function
$g$ gives the  principal divisor $D(g)$ where
one assigns
a positive integer at each zero 
of $g$ given  by its multiplicity. Similarly one assigns
negative integers  at poles given by  their orders.
\medskip

\noindent
{\bf{1.2.3  Theorem.}}
\emph{Every divisor on a non-compact Riemann surface is principal.}

\medskip


\noindent
{\bf{The Mittag-Leffler Theorem.}}
On the Riemann surface
$X$ one has the sheaf $\mathcal O$ of holomorphic functions and
the sheaf $\mathfrak{M}$ whose sections are meromorphic functions.
Now there exists the quotient sheaf
\[
\mathcal M= \frac{\mathfrak{M}}{\mathcal O}
\]
Sections in $\mathcal M$ are special since
one only gets contributions at the set of poles of
a meromorphic function which over an open subset in $X$
is discrete.
Theorem 0.2.1 and the long exact sequence of cohomology entails that
one has an exact sequence
\[
0\to \mathcal O(X)\to \mathfrak{M}(X)\to
\mathcal M(X)\to 0\tag{1.2.4}
\]
This  surjective maps means that one
can assign a  Mittag-Leffler distribution
in an arbitrary fashion on disrete subsets of $X$ which
extends the classic result for planar domains.


\bigskip



\centerline{\bf{1.3 Harmonic functions and the Dirichlet problem.}}
\bigskip


\noindent
A real-valued function $u$ on $X$ is harmonic if its restriction to
every chart satisfies the Laplace equation.
An equivalent condition is that
the $(1,0)$-form
$\partial(u)$ is $\bar\partial$-closed, i.e. a holomorphic 1-form.
The space  of harmonic functions on $X$ 
is denoted by $\mathfrak{h}(X)$.
We have also the sheaf
$\mathfrak{h}_X$ whose sections over
open sets $U$ is
$\mathfrak{h}(U)$.
Let us then consider an   open
subset $Y$ of $X$ whose  boundary
$\partial Y$ is compact.
For each $h\in C^0(\partial Y)$ one seeks 
a continuous function $H$ on $\overline{Y}$ where
$H$ is harmonic in $Y$ and equal to $h$ on
the boundary.
To find $H$ one proceeds exactly as in the planar case
using Perron's method. This 
gives a sufficiency for solutions to the Dirichlet problem
for arbitrary continuous boundary value functions. More precisely, a point
$p\in\partial Y$ satisfies the Perron condition if
we can find a pair $(\Delta,u)$
where
$\Delta$ is a chart with the origin at $p$ and
$u$ is a continuous function in
$\overline{Y}\cap \Delta$ with the property that
$u$ is subharmonic in
$Y\cap \Delta$ where it takes strictly negative values, while $u(p)=0$.



\medskip

\noindent
{\bf{1.3.1 Theorem.}}
\emph{Let $Y$ be an open set in $X$ such that every $p\in\partial Y$
is Perron regular. Then the Dirichlet problem has a solution for
every
$h\in C^0(\partial Y)$.}

\medskip

\noindent
{\bf{1.3.2 Remark.}}
For brevity we say that
$Y$ is Dirichlet regular when  the Dirichlet problem has a solution.
The proof of Theorem 1.3.1 is verbatim to the planer case  and
left as an exercise to the reader.
\bigskip


\centerline{\bf{1.4 The uniformisation  theorem.}}
\medskip

\noindent
Denote by $\Omega(X)$ the space of globally defined holomorphic 1-forms.
We can impose the condition that
\[ 
\partial(\mathcal O(X))= \Omega(X)\tag{1.4.1}
\]

\medskip

\noindent
{\bf{1.4.2  Theorem.}}
\emph{Let $X$ be a non-compact Riemann surface for which (1.4.1) holds.
Then $X$
is biholomorphic with the unit disc $D$ or the complex plane
${\bf{C}}$.}
\bigskip


\noindent
{\bf{Remark.}}
In the special case when
$X$ is a planar domain the result above is
Riemann's ordinary mapping theorem for simply connected
domains.
The extension to an arbitrary
open Riemann surface 
requires extra work which is given  in ¤ 5.

\bigskip






\centerline{\bf{1.5 Further results.}}
\medskip

\noindent
The Behnke-Stein theorem
extends to the case when
$\mathcal O$ is replaced by
a holomorphic line bundle $\mathcal L$ which by definition
is a locally free sheaf of $\mathcal O$-modules with rank one.
Thus
\[ 
H^1(X,\mathcal L)=0\tag{1.5.1}
\]
There also  exists  the multiplicative sheaf
$\mathcal O^*$ whose sectios are zero-free holomorphic functions.
The exponential map yields an exact sequence of sheaves
\[
0\to {\bf{Z}}_X\to \mathcal O\overset{\text{exp}}\to  \mathcal O^*\to 0
\]
In ¤ x we prove that
$H^1(X,\mathcal O^*)=0$ 
and  the long exact sequence of cohomology  gives
\[ 
H^2(X,{\bf{Z}}_X)=0\tag{1.5.2}
\]


\noindent
Next, let $\Omega $ be the sheaf of holomorphic 1-forms
which gives the exact sheaf sequence
\[
0\to {\bf{C}}_X\to \mathcal O\overset{\partial }\to  \Omega\to 0
\]
The vanishing of $H^1(X,\mathcal O)$
gives the exact sequence
\[
0\to {\bf{C}}_X
\to \mathcal O(X)\overset{\partial }\to  \Omega(X)\to 
H^1(X,{\bf{C}}_X)\to 0\tag{1.5.3}
\]
Hence one has the isomorphism
\[
H^1(X,{\bf{C}}_X)\simeq\frac  {\Omega(X)}{\partial(\mathcal O(X)}\tag{*}
\]
When (1.4.1) fails 
one is led to analyze when a  globally defined holomorphic
1-form
$\omega$ is $\partial$-exact, i.e. equal to
 $\partial(f)$ for some
$f\in\mathcal O(X)$.
To analyze   when this holds we fix a point $x_0\in X$ and denote by
$\mathcal F$ the family of closed and differentiable curves
$\gamma$ with common start and terminal points at $x_0$.
If $\omega=\partial(f)$ it is clear that
\[
\int_\gamma\,\omega=0\quad\colon
\gamma\in\mathcal F\tag{i}
\]
Conversely, assume that
(i) holds for some
 $\omega\in\Omega(X)$.
 If $x$ is a point in $X$ we find a differentiable curve
 $\gamma(x)$ which starts at $x_0$ and has $x$ as terminal point.
 Now (i) entails that
 \[
 \int_{\gamma(x)}\,\omega\tag{ii}
 \] 
 only depends on $x$ and not on the specific choice of 
 $\gamma(x)$. This gives
 $f\in\mathcal O(X)$ such that
$f(x)$ equals (ii) for every $x$ and 
$\omega=\partial(f)$.
So the vanishing in (i) is a necessary and sufficient condition in order
that
$\omega$ is $\partial$-exact.
\medskip

\noindent {\bf{1.5.4 Additive representations of $\pi_1(X)$.}}
Recall that the fundamental group of the manifold $X$ can be identified with
homotopy classes of closed curves in the family $\mathcal F$.
Exactly as in the planar case one verifies that
the integrals in (i)  only depend upon the homotopy
classes.
So if $\omega$ is kept fixed we get a group homomorphism
from $\pi_1(X)$ into the abelian group 
${\bf{C}}$ defined by
\[
\{\gamma\}\mapsto \int_\gamma\,\omega\tag{i}
\]
Conversely one applies (1.5.3)  to show that
\emph{every} group homomorphism
$\rho\colon \pi_1(X)\to {\bf{C}}$
is given by (i) for some
holomorphic 1-form $\omega$.

\bigskip

\centerline
{\bf{¤ 1.6. About the proofs.}}
\medskip

\noindent
Theorem 1.3.1 plays a crucial role where  Perron's solution  for planar domains
can be carried out directly on a manifold by repeating the proof for planar domains.
To begin with  Theorem 1.3.1 is used to prove that
the topology of $X$ is 
countable which means that 
there exists  denumerable increasing sequence of compact subsets
$\{K_n\}$ where
$K_n$ is contained in the interior of $K_{n+1}$ for every $n$.
The proof is given
in
tbe Appendix  where the  crucial  point 
is to apply Theorem 1.3.1  when
$Y$ is the open complement in $X$   when
one has removed
a pair of closed discs in separate charts.
\medskip

\noindent
Another very useful fact
is  Montel's theorem for planar domains.
Namely, let 
$V$ and $U$ be  two open sets in
${\bf{C}}$ where
$V$ is relatively compact in
$U$, i.e $\overline{V}$ is a compact subset
of $U$. Then the restriction operator from
$\mathcal O(U)$ into $\mathcal O(V)$ is compact
where both are Frechet spaces under uniform convergence over compact subsets of 
$V$ and $U$
respectively.
In ¤ xx we show that this 
compactness and Pompieu's theorem for planar domains
give:

\medskip

\noindent
{\bf{1.6.1 Dolbeault's Lemma.}}
\emph{Let $Y$
be a relatively compact open subset of $X$.
Then, for every open set $Y^*$ which contains $\overline{Y}$
and
each $\phi\in\mathcal E^{0,1}(Y^*)$, the restriction of
$\phi$ to $Y$ is  $\bar\partial$-exact, i.e. one has the inclusion}
\[
 \phi|Y\in \bar\partial(\mathcal E(Y))
\]

\noindent
{\bf{Remark.}}
We shall see that this result
constitutes the
essential step to get   the Behnke-Stein theorem where
the relative compactness is relaxed.
\medskip


\noindent
{\bf{1.6.2 The elliptic
property
of $\bar\partial$.}}
Recall that if $\mu$ is a distribution   in some open
subset $U$ of ${\bf{C}}$ such that
$\partial(\mu)=0$ then it
is a holomorphic density.
Passing to a Riemann surface $X$
we consider a current $S$ of bi-degree
$(1,0)$, i.e  a continuous linear form on
test-forms of bi-degree $(0,1)$.
The current $S$ is $\bar\partial$-closed in an open subset
$U$ of $X$ if
\[
S(\bar\partial(g))=0\quad \colon g\in C_0^\infty(U)\tag{i}
\]
The planar result entails that (i) gives
a holomorphic 1-form
$\sigma$ in $U$ such that
\[
S(\phi^{0,1})=\int\, \phi\wedge \sigma\tag{ii}
\]
for every $\phi\in \mathcal E^{0,1}(X)$ having compact support in
$U$.
That $(i)\implies (ii)$ plays a crucial role in
the proof of Theorem 1.2.2.


\medskip


\noindent
{\bf{1.6.3 Counting zeros.}}
A substitute for the argument principle in
the complex plane to count zeros of analytic functions
exists on Riemann surfaces.
Let $f$ be holomorphic in an open subset $Y$ of $X$
and suppose that the   zeros in $Y$ is a finite set
$p_1,\ldots,p_k$, where each $p_\nu $ is  zero of some multiplicity
$e_\nu$.
Now $\log |f|^2$ is locally integrable in 
$Y$
which gives a current
defined on test-forms
$\omega$ of bi-degree $(1,1)$ with compact support in $Y$
which is defined by 
\[
\int_Y\, \log|f|^2\cdot \omega^{1,1}\tag{i}
\]
To evaluate (i)
we apply the calculus with currents.
To begin with
we get the current
\[
\partial(\log |f|^2)= \frac{\partial  f}{f}\tag{ii}
\]
whiuch  is a holomorphic density outside the zeros and if
$(|Delta,z)$ is a chart around a zero $p_\nu$ of multiplicity
$e_\nu$ then the 
current in (ii) restricted to this chart
is
$e_\nu\cdot \frac{dz}{z}$.
Now we can apply $\bar\partial$  and residue calculus shows that
the (1,1)-current
\[
\bar\partial \partial(\log |f|^2)= 2\pi i\cdot \sum\, e_\nu\cdot \delta(p_\nu)
\]
where $\{\delta(p_\nu)\}$
are Dirac measures. 
More precisely, for every test-function $g\in C_0^\infty(Y)$
one has the equality
\[
2\pi i\cdot \sum\, e_\nu\cdot g(p_\nu)
\int_Y\, \log |f|^2\cdot  \bar\partial\partial (g)\tag{iii}
\]
\medskip

\noindent
{\bf{1.6.4 A continuity principle.}}
Let $f\in\mathcal O(Y)$
and suppose  it extends to a continuous function on
$\overline{Y}$ and  there is some $\delta>0$ such that 
$|f(p)|\geq \delta$ hold for each $p\in\partial Y$.
For each complex number
$a$ with $|a|<\delta$ it follows
that $f-a$ has a finite number of zeros in $Y$. Denote by 
$e_f(a)$ be the number of zeros counted with multiplicity.
Exactly as above we get
\[
 2\pi i\cdot e(a)=\int\,  \log |f-a|^2\cdot \bar\partial\partial(g)\tag{1}
\]
when $g$ is a test-function in $Y$ which take values one at
the zeros of $f-a$.
Let $0<\delta_0<\delta$ so that
the set
$\{|f|\leq \delta_0\}$ is compact in $Y$
and fix $g\in C_0^\infty(Y)$ so that
$g=1$ over this compact set.
Now we get ther integer-valued function $a\mapsto e(a)$
which for each $a$ is evaluated via (1).
At the same time we have the $L^1$-functions
$\{\log\, |f-a|\}$ and elementary measure theory
shows that
$a\mapsto \log |f-a|$
is continuous with values in $L^1(Y)$.
Passing to their distribution derivatives
give a weak-star  continuous
current-valued function
$a\mapsto\bar\partial\partial(\log |f-a|)$
which entails that
(1) is a continuous integer-valued function defined in the disc
$\{|a|<\delta\}$.
Hence this function is constant, i.e. the number of
$a$-values taken by $f$ and counted with multiplicities is
constant.
\medskip

\noindent
{\bf{Remark.}}
It is possible to prove
the result above by regarding
proper maps with
finite fibers from one manifold into another. However, the proof given above
has the merit that it can be extended to
considerably  more general situations
since we only used the fact that passage to higher order derivatives of distributions is a
weak-star continuous process.



\newpage


\centerline{\bf{Appendix: Topological results.}}
\bigskip


\noindent
We restrict the attention to topological spaces
$X$ which are Hausdorff.
A Hausdorff space $X$ is arc-wise connected
if there to every pair of points $p,q$ in $X$ exists a continuous map
$\gamma\colon [0,1]\to X$
such that $\gamma(0)=p$ and $\gamma(1)= q$.
Next, one says that
the Hausdorff space $X$ has a countable topology if there
exista a denumerable family $\mathfrak{U}$
of open subsets
$\{U_n\}$ such that every
open set in $X$ is the union of 
sets from $\mathfrak{U}$.
The following remarkable result is due to PoincarŽ and Volterra:


\medskip

\noindent
{\bf{A.1 Theorem.}} \emph{Let 
$X$ be arc-wise  connected and Hausdorff which in addition is locally compact.
Suppose there exists a continuous map
$f\colon X\to Y$
where
$Y$ is a Hausdorff  space with countable topology
and the fibers
$f^{-1}(y)$ are discrete subsets of $X$ for every $y\in Y$. Then
$X$ has countable topology.}
\medskip

\noindent
\emph{Proof.}
Denote by $\mathfrak{B}$ the family of open sets
$V$ in $X$ which satisfy the following:
\[
\text{$V$ has a countable topology}\tag {i} 
\]
\[
\text{$V$ is a connected component of $f^{-1}(U)$ for some
open set $U$ in $Y$}\tag{ii}
\]
Theorem A.1 follows if we prove that
$\mathfrak{B}$ is a countable family and
every open set in $X$ is a union of
$\mathfrak{B}$-sets.
\medskip

\noindent
\emph{Proof that $\mathfrak{B}$Êis countable.}
Let $V_0$ be a set in $\mathfrak{B}$ and
consider an open set $U$ in $Y$.
The connected components of
$f^{-1}(U)$ are disjoint by (i)
$V_0$ has countable topology.
It follows
that
at most countably many
of the connected components of $f^{-1}(U)$
have a non-empty
intersection with $V$.
Next, since every
$V\in \mathfrak{B}$ is of the form $f^{-1}(U)$ for an open
set in $Y$ and $Y$ has a countable topology we
conclude that
\[
V_0\cap V\neq\emptyset\tag{iii}
\]
only  can hold for
countably many $V$ in $\mathfrak{B}$.
Next, fix $V_*\in\mathfrak{B}$ and set
\[ 
\mathfrak{B}_0=\{ V\colon V_*\cap V\neq\emptyset\}
\]
By (iii) this is a countable set in $\mathfrak{B}$.
If $n\geq 1$ we define inductively
\[
\mathfrak{B}_n= \{V\colon \exists\, W\in\mathfrak{B}_{n-1}\, \colon
 W\cap V\neq\emptyset\}
\]
An induction over $n$ entails
that each
$\mathfrak{B}_n$ is countable and since
$X$ is connected it is clear that
their union is equal to $\mathfrak{B}$
which therefore is a countable family.
\medskip

\noindent
\emph{Proof that
$\mathfrak{B}$ is a basis of the topology.}
Let $\Omega\subset X$ be open and take some
$x\in\Omega$. We must prove that there exists
$V\in\mathfrak{B}$ such that
\[
x\in V\subset\Omega
\]
To show this we consider the discrete fiber
$f^{-1}(f(x))$. Since $X$ is Hausdorff and locally compact
there exists 
a small open and relatively compact neighborhood $W$ of $x$ such that 
$W\subset \Omega$ and
$\partial W\cap f^{-1}(f(x))=\emptyset$.
Now $f(\partial W)$ is a compact set in $Y$
which does not contain
$f(x)$ which gives $U\in\mathfrak{U}$ such that
\[
f(x)\in U\quad\colon f(\partial W)\cap U= \emptyset
\]
Let $V$ be the connected component of $f^{-1}(U)$ which contains
$x$.
From the above $V\cap \partial W=\emptyset$ and
we conclude that 
\[
x\in V\subset W\subset\Omega
\]
which finishes the proof.
\bigskip

\centerline {\bf{A.2  Covering spaces.}}
\bigskip


\noindent
Let $X$ be arc-wise connected and Hausdorff.
A pair $(Y,\rho)$ is a covering of $X$ 
if $\rho\colon Y\to X$ is a continuous map and
for each point $p\in X$ there exists some open neighborhood $U$
such that
\[ \rho^{-1}(U)= \cup \, V_\alpha
\]
where the right hand side is a disjoint union of open sets in
$Y$ and $\rho\colon V_\alpha\to U$ are homeomorphisms for
each $\alpha$.
\medskip

\noindent
{\bf{A.2.1 Exercise.}}
Let $\gamma\colon  [0,1]\to X$ be a continuous map
and let $y_0\in Y$ be a point such that
\[
\rho(y_0)= x_0=\gamma(0)
\]
Show that there exists a unique continuous map
$\gamma^*\colon  [0,1]\to Y$ such that
$y_0=\gamma^*(0)$ and
\[
\rho(\gamma^*(t))= \gamma(t)\,\colon\, 0\leq t\leq 1\tag{i}
\]
which means that
there exist unique liftings of curves. 
\bigskip

\noindent
Next, let $\pi_1(X)$ be the fundamental  group of $X$.
Since $X$ is arc-wise connected it can be identified with homotoy classes
of closed curves $\gamma$ which have a given
$x_0\in X$ as a common initial and terminal point.
Let us also fix a point $y_0$Êin the fiber
$\rho^{-1}(x_0)$.
To each closed $\gamma$-curve as above the exercise gives
a unique lifted curve
$\gamma^*$  where  (i) entials that
\[
\rho(\gamma(1))\in
\rho^{-1}(x_0)\tag{ii}
\]

\medskip

\noindent
{\bf{A.2.2 Exercise.}}
Show that the end-point
$\gamma(1)$ in  (ii)
only  depends upon the homotopy class of
$\gamma$ and conclude that
one has a map
\[
\rho_*\colon \pi_1(X)\to \rho^{-1}(x_0)\tag{*}
\]
Show also that $\rho_*$ is surjective
if $Y$ is connected.
\medskip

\noindent
{\bf{A.2.3 The universal covering property.}}
A covering $\phi \colon Z\to X$ has a universal property if the
following holds: For every covering
$\rho\colon Y\to X$
and each pair of points $z_0\in \phi^{-1}(x_0)$ and
$y_0\in \rho^{-1}(x_0)$ there exists a unique fiber preserving continuous map
$f\colon Z\to Y$ with $f(z_0)=y_0$ and 
\[ 
\rho\circ f=\phi\tag{**}
\]
Notice that (**) means that $f$ is fiber preserving.
\medskip

\noindent
{\bf{A.2.4 Exercise.}}
Show that a covering with the universal property is unique in
the sense that if $(Z_1,\phi_1)$ and $Z_2,\phi_2)$ is such a pair then
there exists a homeomorphism $g\colon Z_1\to Z_2$
with
\[
\phi_1= \phi_2\circ g
\]
\medskip

\noindent
{\bf{A.2.5 Existence.}}
Show that an arc-wise connected  Hausdorff space
$X$ has a universal covering $\widehat{X}$ and that
the fundamental  group
$\pi_1(\widehat{X})=0$.
\medskip

\noindent
{\bf{A.2.6 The Galois property.}}
A covering $\rho\colon Y\to X$
where $Y$ is connected has the Galois property if there
to each
$p\in  X$ and every pair
of points $y_1,y_2$ in $\rho^{-1}(p)$ exista a fiber presering
homeomorphism $f\colon Y\to Y$
with
$f(y_1)= y_2$.
\medskip

\noindent
{\bf{A.2.7 Exercise.}}
Verify that the universal covering $\widehat{X}$
has the Galois property.


\bigskip
\centerline {\bf{A.3 Runge sets on Riemann surfaces.}}

\bigskip


\noindent
If $K$ is a compact subset of the Riemann surface $X$
we get the conncted components $\{\Omega_\alpha\}$
of the open complement $X\setminus K$.
Since $X$ is connected we notice that
\[ 
\partial\Omega_\alpha\subset K\tag{i}
\] 
hold for every connected component in $X\setminus K$.
Next,
choose an open set $U$ which contains $K$ where $\overline{U}$
is compact.
This is of course possible since
$K$  can be covered by a finite number of charts
where each chart has a compact closure in $X$.
If a component 
$\Omega_\alpha$ is such that
\[ 
\partial U\cap \Omega_\alpha= \emptyset\tag {ii}
\] 
the connectivity
of $X$ and (i) entail that
\[
\Omega_\alpha\subset U\tag{iii}
\]
Next,  the Heine-Borel Lemma
a finite
family of $\Omega_{\alpha_1},\ldots,\Omega_{\alpha_N}$
whose union cover the compact set $\partial U$.
Among these occur a finite family of non-compact
sets, say
$\Omega_{\alpha_1},\ldots,\Omega_{\alpha_k}$ where $1\leq k\leq N$.
Set
\[ 
\mathfrak{h}(K)= K\, \cup\, \bigcup_*\, \Omega_\alpha\tag{iv}
\]
 where the *-marked union is taken over
 all components for which (iii) hold together with  the finite family of relatively compact
 components which intersect $\partial U$, or equivalently
 \[
 \mathfrak{h}(K)=X\setminus \Omega_{\alpha_1}\,\cup\ldotsÊ\cup\, \Omega_{\alpha_k}
\]

 
 \noindent
 {\bf{A.3.1 Exercise.}}
 Verify that $\mathfrak{h}(K)$ is compact and that
 \[ 
 \mathfrak{h}(\mathfrak{h}(K))=\mathfrak{h}(K)
 \]
 
 
 \noindent
{\bf{A.3.2 Open Runge sets.}}
An open subset $Y$ in $X$ is Runge if
\[ 
K\subset Y\implies \mathfrak{h}(K)\subset Y
\]
hold for every compact set $K$, i.e. the Runge hull of a compact
subset of $Y$ stays in $Y$.
 \medskip
 
 \noindent
{\bf{A.3.3 Proposition.}}
\emph{Let $K$ be a compact Runge set
in $X$ with a non-empty interior.
Let $\Delta_1,\ldots,\Delta_N$
be a finite number of open  discs whose union cover
$\partial K$.  Then the open set below is Runge:}
\[
Y=K\setminus \,\cup\, \overline{\Delta}_\nu
\]  

 \noindent
The easy proof is left as an exercise.



\newpage




\centerline{\bf{¤ 1. Proofs of the main results.}}
\bigskip

\noindent
Preliminary results are established in ¤ 2
where Dolbeaulit's Lemma from ¤ xx is crucial.
Here the proof requires several steps which starts by a certain finiteness
result in Propostion 2.3.2 and after one derives Dolbeault's Lemma via a 
"tricky construction" which 
is due to Cauchy and based upon 
the general fact that if
$A\colon V|to V$ is a linear operator on a finite dimensional vector space
of some dimension $N$
and
\[ 
\text{det}(\lambda\cdot E_V-A)=
\lambda^N+
c_{N-1}\lambda^{N-1}+\ldots +c_0
\]
then the linear operator
\[
A^N+
c_{N--1}A^{N-1}+\ldots +c_0E_V
\] 
is identically zero.
In ¤ 3 we first establish an approximation result
where calculis with currents are used. The crucial point is the
elliptic property of $\bar\partial$ 
which implies that if $S$ is a current of bi-degree
(1,0) in some open set $U$ of $X$
which is $\bar\partial$-closed, then
there exists a holomorphic 1-form $\sigma$ in $U$ such that
\[
S(\omega^{0,1})=\int_U\, \omega^{0,1}\wedge \sigma
\]
for every test-form $\omega^{0,1}$ of bi-degree 
$(0,1)$ having compact support in $U$.
At the end of ¤ 3 we deduce the Behnke-Stein theorem from the previous results.
In ¤ 4 we derive further results  such as
Weierstrass' theorem 
which asserts that
every divisor on an open Riemann surface is principal.
Another crucial  fact is the existence of
a globally defined holomorphic 1-form which never is zero.
\medskip

\noindent
Armed with previous results we prove the uniformisation theorem in
¤ 5 which is based upon repeated solutions to certain Dirchlet problems
in an exhaustion of the simply connected Riemann surface
$X$ by relatively compact Perron regular
Runge domains.
A crucial point during the proof  is that
the hypothesis 
\[
\Omega(X)=\partial(\mathcal O(X))
\]
entails that the same holds for every
open Runge set in $X$.










\newpage




\centerline{\bf{¤ 2. Dolbeault's Lemma.}}

\bigskip


\noindent
Let $X$ be an open Riemann surface
and $Y$  a
relatively  compact open subset.
Heine-Borel's Lemma gives a finite covering of
$\overline{Y}$ by open charts
$\{\Delta_\alpha\}$ and hence   a finite open covering 
$\mathfrak{U}= \{U_\alpha\}$ 
of $Y$ where
\[
U_\alpha=\Delta_\alpha\cap Y
\]
Construct  the Cech complex
\[
C^0(\mathfrak {U},\mathcal O)
\overset{\delta}\to\,
C^1(\mathfrak {U},\mathcal O)
\overset{\delta}\to\,
C^2(\mathfrak {U},\mathcal O)
\overset{\delta}\to\ldots
\]
and consider  the cohomology group
\[ 
H^1(\mathfrak {U},\mathcal O)=
\frac{Z^1(\mathfrak {U},\mathcal O)}{
\delta(C^0(\mathfrak {U},\mathcal O)}\tag{2.1}
\]
Pompieu's  theorem and Leray's acyclicity theorem
for sheaf cohomology entail that
(2.1) is 
independent of the chosen 
covering  and equal to the cohomology group
$H^1(Y;\mathcal O_X)$. Moreover,   the Dolbeault isomorphism from ¤ XX gives:
\[
H^1(\mathfrak {U},\mathcal O_X))\simeq
\frac{\mathcal E^{0,1}(Y)}{\bar\partial(\mathcal E(Y))}\tag{2.2}
\]

\medskip

\noindent
{\bf{2.3 A finiteness result.}}
Let $Y$ and $Y^*$ be a pair of relatively
compact subsets of
$X$ where  $\overline{Y}$ is a compact subset of
$Y^*$.
Let $\{\Delta_\alpha\}$ be a finite covering of 
$\overline{Y^*}$
by  charts and set
$U_\alpha=\Delta_\alpha\cap Y^*$ so that
$\mathfrak {U}^*=\{U_\alpha\}$
is a finite 
covering of 
$Y^*$.
Since $\overline{Y}$ is compact in
$Y^*$ 
there exists some
$0<a<1$ such that
$\{a\cdot \Delta_\alpha\}$ cover
$\overline{Y}$ and  give a covering $\mathfrak{U}_*$
of $Y$ where
\[ 
V_\alpha=
a\cdot \Delta_\alpha\cap Y
\]
It is clear that
$V_\alpha$ is a compact subset of $U_\alpha$ for every
$\alpha$.
Montel's theorem entails that the restriction operators
\[
C^p(\mathfrak{U},\mathcal O)\to 
C^p(\mathfrak{U}_*,\mathcal O)
\]
are compact for each $p$.
These restrictions  commute with the Cech coboundary mappings
and give a  ${\bf{C}}$-linear operator
\[
H^1(\mathfrak U,\mathcal O)\to 
H^1(\mathfrak{U}_*,\mathcal O)\tag{2.3.1}
\]
 A general result in functional analysis about
 compact operators between Frechet spaces entails that the range of
 (2.3.1) is finite dimensional.
 By (2.2) it follows that 
 the restriction map
 \[
 H^1(Y^*,\mathcal O)\to 
  H^1(Y,\mathcal O)\tag{2.3.2}
 \] 
 has a finite dimensional range.
Above $Y^*$ was relatively compact. More generally, let
$U\subset X$ be open where
$\overline{Y}$Êis a compact subset of $U$.
We can find $Y^*$ as above where
$Y\subset Y^*\subset U$.
Let $N$ be the dimension of the range from (2.3.2). It means that
there exists an $N$-tuple $\{\phi_\nu\}$ in $\mathcal E^{1,0}(Y^*)$
and for every other $\phi\in \mathcal E^{1,0}(Y^*)$ there
exist complex numbers $\{c_k\}$ such that
\[
\phi|Y-\sum\, c_k\cdot \phi_k|Y\in \bar\partial \mathcal E(Y)
\]
This applies  when we start from some
$\psi\in \mathcal E^{1,0}(U)$
and take the restriction $\phi=\psi |Y^*$. Hence
the range of the map 
\[ 
H^1(U,\mathcal O)\to H^1(Y,\mathcal O)
\] 
is contained in the
$N$-dimensional complex vector space
generated
by the images of $\{\phi_k|Y\}$ in
Dolbeault's quotient space from (2.2) which defines
$H^1(Y,\mathcal O)$. Summing up 
we have proved

\medskip

\noindent
{\bf{2.3.3 Proposition.}}
\emph {Let $Y$ be a relatively compact open set in
$X$. Then the range of}
\[ 
H^1(U,\mathcal O)\to H^1(Y,\mathcal O)
\] 
\emph{is finite dimensional for every open set
$U$ which contains $\overline{Y}$.}
\bigskip


\noindent
{\bf{2.4 Another finiteness result.}}
Consider some finite open covering $\mathfrak{U}=\{U_\alpha\}$ of $X$.
No assumption is imposed on the open sets $U_\alpha$.
Let $Y$ be a relatively compact subset of $X$ and
$\mathfrak{U}_*=\{V_\alpha\}$ a finite open covering of $Y$ such that
$\overline{V}_\alpha$ is a compact subset of $U_\alpha$ for every
$\alpha$.
Restrictions give a 
morphism from the Cech complex $C^\bullet(\mathfrak U,\mathcal O)$
to
$C^\bullet(\mathfrak{U}_* ,\mathcal O)$, and exactly as above  Montel's theorem implies that
the  map
\[
H^1(\mathfrak U;\mathcal O)\to 
H^1(\mathfrak{U}_*;\mathcal O)\tag{2.4.1}
\] 
has a finite dimensional range.
\bigskip


\noindent
{\bf{2.4.2 A special case.}}
Let $p$ be a point in $X$ and $Y$ a relatively compact subset.
Here $p$ may or may not belong to $Y$.
Choose a chart $\Delta$ centered at $p$.
Now  $U_0=X\setminus\{p\}$ and $U_1=\Delta$ is an open covering 
$X$.
Let $0<a<1$ and put
\[
V_0=Y\setminus \frac{a}{2}\cdot \overline{\Delta}
\quad\colon V_1=Y\cap a\cdot \Delta
\]
where
$ \frac{a}{2}\cdot \overline{\Delta}$ is the closed disc of radius $a/2$.
Here  $V_0,V_1$ cover $Y$
and from the above the
restriction map
\[ 
\rho\colon H^1(U_0,U_1;\mathcal O)\to
H^1(V_0,V_1;\mathcal O)\tag{2.4.3}
\] 
has a finite dimensional range.
Notice that
\[ 
C^1(U_0,U_1;\mathcal O)=\mathcal O(\Delta^*)
\] 
where $\Delta^*$ is the punctured
disc wih $z=0$ removed.
To each non-negative integer we have
$z^{-j}\in \mathcal O(\Delta^*)$. Since 
$C^2(U_0,U_1;\mathcal O)=0$  each
of these holomorphic functions in
the punctured disc yields a vector in
$H^1(U_0,U_1;\mathcal O)$ and
we apply $\rho$ to get
\[ 
\rho(z^{-j})\in  H^1(V_0,V_1;\mathcal O)
\]
If $N$ is the dimension of the range of $\rho$ we find
complex numbers
$c_0,\ldots,c_{N-1}$ such that
\[
\rho(z^{-N})= \sum\, c_j\cdot \rho (z^{-j})
\]
This means that there exists a pair $f_0\in\mathcal O(V_0)$ and
$f_1\in\mathcal O(V_1)$ such that
\[
f_1=
f_0+ \sum\, c_j\cdot z^{-j}-z^{-N}
\quad\colon  z\in V_0\cap V_1\cap Y\tag{2.4.4}
\]
Hence $f_1$ and $g_0=f_0+ \sum\, c_j\cdot z^{-j}-z^{-N}$
are glued in $V_0\cap V_1$ and give together a meromorphic function
$g$ in $Y$ which is holomorphic in $Y\setminus \{p\}$ and has a pole of order
$N$ at $p$  when
$p\in Y$.

\bigskip


\noindent
{\bf{2.5 Exercise.}}
Use the above to show that
when $Y$ is relatively  compact
then there exists an open neighborhood $U$ of $\overline{Y}$ and some
$f\in\mathcal O(U)$
whose restriction to every connected component of $Y$ is
non-constant.
In particular the number of its zeros is finite
and the reader should verify that
the same holds if we take
\[ F= f^N+c_{N-1}f^{N_1}+\ldots+c_1f+c_0
\]
where $N\geq 1$ and $\{c_k\}$ are complex numbers.



\bigskip



\centerline {\bf{2.6 Proof of Dolbeault's Lemma.}}
\bigskip


\noindent
Let $Y\subset X$ be relatively compact and
$Y^*$  another relatively compact set which contains
$\overline{Y}$ as a compact subset. Choose coverings as in ¤ xx to
get the restriction map
\[
\rho\colon H^1(Y^*,\mathcal O\to 
 H^1(Y,\mathcal O)\tag{2.6.1}
 \]
We are going to prove that the $\rho$-image is zero.
To get this we argue by a contradiction. If the image is $\neq 0$ we already know 
that it has a finite dimension $N$.
Choose
$\xi_1,\ldots,\xi_N$ in $C^1(\mathfrak {U},\mathcal O)$
such that $\{\rho(\xi_k)\}$ is a basis of the $\rho$-image.
Here we employ Dolbeault's respresentation of
cohomology so that each $\xi_k\in \mathcal E^{0,1}(Y^*)$.
Next,  Exercise 2.5 applied with $Y^*$  gives
$f\in \mathcal O(Y^*)$.
Now  $f\cdot \xi_k$ belongs to
$\mathcal E^{0,1}(Y^*)$ for each $k$
and since   
$\{\rho(\xi_k)\}$ was a basis
we find  for each fixed $k$ complex numbers 
$\{b_{kj}\}$
such that
\[
f\cdot \xi_k-\sum_{j=1}^{j=N}\, b_{kj}\cdot \xi_k\, \bigl|Y\in
\bar\partial (\mathcal E(Y))
\tag{2.6.2 }
\]
Here $B=\{b_{kj}\}$ is an $N\times N$-matrix
and we construct  the holomorphic function $F$ in $Y^*$
\[
F=\det(f\cdot E_N-B)
\]
The Cayley-Hamilton  theorem from  linear algebra gives
\[
F\cdot \xi_k|Y\in\bar\partial (\mathcal E(Y))
\quad\colon k=1,\ldots,N\tag{2.6.3}
\]
Since $\{\rho(\xi_k)\}$ spans the $\rho$-image it follows that
\[
\rho(F\cdot \eta)=0\tag{2.6.4}
\]
for every cohomology class $\eta\in H^1(Y^*;\mathcal O)$.
Next,  $f$ is non-constant
on connected components in $Y^*$ and we notice  that 
the same holds for $F$. Recall  also that $f$ even is holomorphic in
a neighborhood of $Y^*$ which implies  that
the zeros of $F$ in $Y^*$ is a finite set at most.
Then   it is clear that there exists
a finite covering
$\mathfrak U$ via charts in $Y^*$ such
that $F$ has no zeros in every non-empty intersection of $\mathfrak U$-sets.
Let us now  consider an arbitrary
cohomology class
$\eta\in H^1(Y^*,\mathcal O)$
represented by a Cech cocycle $\{\phi_{\alpha \beta}\}$.
Since $F$ has no zeros in non-empty intersections 
$U_\alpha\cap U_\beta$ we get another Cech cocycle
\[ 
\psi_{\alpha\beta}=\frac{\phi_{\alpha\beta}}{F}
\]
Let $\eta^*$ be its cohomology class. Now $\eta= F\cdot \eta^*$
and (2.6.4) applied with
$\eta^*$ entails  that
$\rho(\eta)=0$. Since $\eta$ was arbitrary 
the restriction map from 
$H^1(Y^*;\mathcal O)$ into
$H^1(Y;\mathcal O)$ is zero.
\bigskip


\centerline{\bf{¤ 3. Proofs of Theorem 0.2.1-0.2.2}}
\bigskip


\noindent
Let us first consider
a pair $(Y,K)$ from Theorem  0.2.2
and  $Y^*$ is  another relatively compact subset of
$X$ such that  $\overline{Y}$ is compact in $Y^*$.
First we establish 
a
weaker variant of  Theorem
0.2.2 where   the subsequent proof is attributed to Malgrange.

\medskip

\noindent
{\bf{3.1 Proposition.}}
\emph{When 
 $f\in\mathcal O(Y)$ 
there exists a sequence $\{g_n\}$ in $\mathcal O(Y^*)$ such that
$|g_n-f|_K\to 0$.}

\medskip

\noindent
\emph{Proof.}
Let $\mu$ be a Riesz measure
supported by $K$ such that
\[ 
\int\, \phi\cdot d\mu=0\quad\colon \phi\in\mathcal O(Y^*)\tag{i}
\]
The Hahn-Banach  theorem gives Proposition 3.1 if we show that (i)
entails that
\[ 
\int\, f\cdot d\mu=0\quad\colon f\in\mathcal O(Y)\tag{ii}
\]
To prove this
we  construct a current
$S$ on $X$ as follows: Apply Dolbeault's Lemma
to the relatively compact set
$Y^*$. It follows
that  for each 
$\omega^{0,1}\in \mathcal E^{0,1}(X)$ 
there exists  
$g\in \mathcal E(Y^*)$ such that
\[
\omega|Y^*= \bar\partial(g)\tag{iii}
\]
Here $g$ is unique up to $\mathcal O(Y^*)$ so by (i)
the  integral 
$\int\, g\cdot d\mu$
only depends upon $\omega$. Hence there exists a
current $S$ on $X$ 
defined by
\[ 
S(\omega^{0,1})=\int\, g\cdot d\mu\tag{iv}
\]
with $g$ determined via (iii).
Next, consider
an 
open chart $\Delta$ contained in $X\setminus K$.
If $g\in C_0^\infty(X)$ has compact support in
$\Delta$ we take $\omega^{0,1}= \bar\partial(g)$
and since $g=0$ on $K$ one has 
\[
S(\bar\partial(g))=0
\]
Since this hold for every pair $(\Delta, g)$ as above,
$S$ is $\bar\partial$-closed in $X\setminus K$ and
the elliptic property of
$\bar\partial$ gives a holomorphic 1-form
$\sigma$ in $X\setminus K$ such that
\[
S(\omega^{0,1})=\int\, \omega^{0,1}\wedge \sigma\tag{v}
\]
holds when $\omega^{0,1}$ has compact support in
$X\setminus K$.
Let us now consider a point $p\in X\setminus \mathfrak{h}(K)$.
By the construction of $\mathfrak{h}(K)$ this gives a non-compact
open and connected subset $\Omega$ 
of $X\setminus\mathfrak{h}(K)$
which contains $p$. Since the current $S$ has compact support
it follows that 
\[
\Omega\setminus \text{Supp}(S)\cup K)\neq \emptyset\tag{vi}
\]
Let $q$ be a point in this set and 
choose a small open chart
$\Delta$ centered
at $q$
which stays in $\Omega$ and is disjoint from
the support of $S$. Then
\[
\int\, \omega^{0,1}\wedge \sigma=0
\] 
for every test-form
$\omega^{0,1}$ with compact support in
$\Delta$. Hence the restriction of $\sigma$
to $\Delta$ is zero. Since
$\sigma$ is a 
holomorphic 1-form
and  $\Omega$ is connected, 
analyticity
gives 
$\sigma|\Omega=0$. In particular $\sigma=0$ holds in a neighborhood of
$p$ which  proves the inclusion
\[
 \text{Supp}(S) \subset
\mathfrak{h}(K)\tag{vii}
\]
Finally, by  assumption $\mathfrak{h}(K)$ is a compact subset of $Y$. 
So if  $f\in\mathcal O(Y)$ we can find
a test-function $g$ with compact support in
$Y$ such that
$g=f$ 
holds in a neighborhood of $\mathfrak{h}(K)$.
Then $\bar\partial(g)$ vanishes in a neighborhood of
$\mathfrak{h}(K)$ so (vii) and the construction of $S$ entail that
\[ 
0=S(\bar\partial g)=\int_K\,g\cdot d\mu=
\int_K\,f\cdot d\mu\tag{viii}
\] 
which proves Proposition 3.1.




\bigskip





\centerline{\bf{3.2 Proof of Theorem 0.2.1}}
\medskip


\noindent
By  ¤ xx  we can  exhaust $X$ by an increasing sequence of Runge domains
$\{Y_n\}$  where the closure of $Y_n$
is a compact subset of $Y_{n+1}$ 
for each $n$.
Consider
some $\phi\in \mathcal E^{0,1}(X)$.
Dolbeault's Lemma applies to each pair
$Y_n, Y_{n+1}$ and the restriction of
$\phi$ to $Y_{n+1}$.
Hence there exists
$f_n\in \mathcal E(Y_n)$
such that 
\[
 \bar\partial f_n=\phi|Y_n\tag{3.2.1}
\]
It follows that
the restriction to $Y_n$ of $f_{n+1}-f_n$ is holomorphic
and since $Y_n$ is Runge and $\overline{Y}_{n-1}$ is a compact subset,
Proposition 2.4 entails that $f_{n+1}-f_n$
can be uniformly approximated on
$Y_{n-1}$ by functions from $\mathcal O(Y_{n+1})$.
Hence there
exists 
$g_{n+1}\in \mathcal O(Y_{n+1})$
such that the maximum norm
\[
||f_{n+1}+g_{n+1}-f_n||_{Y_{n-1}}<2^{-n}
\]
With $f^*_{n+1}= f_{n+1}+g_{n+1}$
we still have
\[
\bar\partial f^*_{n+1}=\phi|Y_{n+1}
\]
Perfoming
these modifications inductively with increasing $n$ we obtain a 
sequence $\{f^*_n\}$ such that   (3.2.1) hold for every $n$
and 
\[
||f^*_{n+1}-f^*_n||_{Y_{n-1}}<2^{-n}
\quad\colon \, n=1,2,\ldots\tag{3.2.2}
\]
It follows that $\{f_n^*\}$ converge uniformly on $X$ to a continuous function
$F$ which 
entails that
the distributions
$\{\bar\partial f_n^*\}$ converge to the distribution derivative
$\bar\partial (F)$. Moreover, since (3.2.1) hold for every
$n$
it is clear that
\[ 
\bar\partial(F)=\phi\tag{3.2.3}
\]
holds everywhere in $X$.
Finally, $\phi$ is a smooth form so  the elliptic property of
$\bar\partial$ implies that
$F$ is a $C^\infty$-function. Hence the mapping
$\bar\partial\colon \mathcal E(X)\to \mathcal E^{(0,1)}(X)$
is surjective which proves Theorem 0.2.1.


\bigskip





\centerline{\bf{3.3 Proof of Theorem 0.2.2}}
\medskip
 TO BE GIVEN


\newpage

\centerline{\bf{¤ 4. Further results.}}
\bigskip


\noindent
A locally free sheaf of $\mathcal O$-modules of rank one is called
a
holomorphic line bundle.
Let $\mathcal L$ be such a sheaf.
By definition it has local trivialisations, i.e. we can find
a locally finite covering $\mathfrak{U}$
by charts such that
the restricted sheaf
$\mathcal L|U_\alpha\simeq \mathcal O$.
In each non-empty intersection
$U_\alpha\cap U_\beta$ we find
a zero free function 
$g_{\alpha\beta}\in\mathcal O^*(U_\alpha\cap U_\beta)$
so that the space $\mathcal L(V)$ of sections over
an open subset $V$ in $X$
consists of a family $\{\xi_\alpha\in \mathcal O(U_\alpha\cap V)\}$
satisfying the glueing conditions
\[
\xi_\alpha|U_\alpha\cap U_\beta\cap V=
g_{\alpha\beta}\cdot
\xi_\beta|U_\alpha\cap U_\beta\cap V\tag{*}
\]
\medskip

\noindent
Repeating  the methods which were used to prove
Theorem 0.2.1  one has the result below whose detailed verification is left
as an exercise to the reader.

\medskip

\noindent
{\bf{4.1 Theorem.}}
\emph{For every holomorphic line bundle
$\mathcal L$ one has $H^1(X,\mathcal L)=0$.}
\bigskip


\noindent
{\bf{4.2 Example.}}
The 
sheaf $\Omega$ of holomorphic 1-forms is an example of a  holomorphic line bundle.
Another example is the sheaf
$\Theta_X$ whose sections are holomorphic vector fields.
Notice that
\[ 
\Omega=Hom_{\mathcal O}(\Theta_X,\mathcal O)
\]
is the  dual line bundle.
Theorem 4.1 entails that
\[
H^1(X, \Omega)=H^1(X,\Theta_X)=0\tag{4.2.1}
\]



 \medskip
 
 
 \centerline{\bf{4.3 Proof of 
Weierstrass'  Theorem}}

\bigskip


\noindent
Let $D$ be a divisor on $X$
which means that integers $\{k_\nu\}$ are assigned to
a discrete sequence of points $\{p_\nu\}$.
We must prove that there exists a globally deefined meromorphic function $\psi$
whose principal divisor is $D$.
To begin with one has:

\medskip

\noindent
{\bf{4.3.1 Exercise.}}
Use a
$C^\infty$-partition of the unity
to find a function $\phi$ which is zero-free and 
$C^\infty$ in the open complement of
the discrete set $\{p_\nu\}$, and for each
$p_\nu$ there is a small open  chart
$\Delta_\nu$ centered at $p_\nu$ with a local coordinate
$z_\nu$ where 
\[
\phi|\Delta_\nu= z_\nu^{k_\nu}
\]
\medskip

\noindent
Next, we find a locally finite covering
$\mathfrak{U}=\{U_\alpha\}$ of  charts in
$X$ which contains
the discs
$\{\Delta_\nu\}$
while each $U_\alpha$ which differs from these discs 
does not contain points in $\{p_\nu\}$.
For
each
$U_\alpha$ which does not contain any point in
$\{p_\nu\}$ we take $f_\alpha=1$ while
$f_\alpha= z_\nu^{k_\nu}$ when
$U_\alpha=\Delta_\nu$.
Then we can write 
\[
\phi|U_\alpha= f_\alpha\cdot \psi_\alpha
\quad\colon\,\psi_\alpha\in C^\infty(U_\alpha)
\tag{i}
\] 
Since $\phi$ is zero-free outside
$\{p_\nu\}$ we see that
every $\psi$-function is zero-free. Since  every chart
$U_\alpha$ is simply connected there exist
$\{\rho_\alpha\in C^\infty(U_\alpha)\}$ such that
\[
 \psi_\alpha= e^{\rho_\alpha}\tag{ii}
\]
In each non-empty intersection $U_\alpha\cap U_\beta$  
it follows that
\[
e^{\rho_\alpha-\rho_\beta}=\frac{f_\beta}{f_\alpha}\tag{iii}
\]
Here 
each quotient
$\frac{f_\beta}{f_\alpha}\in \mathcal O^*(U_\alpha\cap U_\beta)$
and 
(iii) entails that
the restricted differences
\[
\rho_\alpha-\rho_\beta|U_\alpha\cap U_\beta)\in 
\mathcal O(U_\alpha\cap U_\beta)
\]
So with $g_{\alpha\beta}=\rho_\alpha-\rho_\beta|U_\alpha\cap U_\beta)$
we get a Cech-cocycle in $H^1(\mathfrak{U},\mathcal O)$.
The Behnke-Stein theorem entails that it is a $\delta$-coboundary. Hence
there exist $\{g_\alpha\in \mathcal O(U_\alpha)\}$ such that
\[
\rho_\alpha-\rho_\beta|U_\alpha\cap U_\beta)=g_\alpha-g_\beta\tag{iv}
\]
Taking exponentials in (iv) and using (iii) it follows that
\[
e^{g_\alpha}\cdot f_\alpha=
e^{g_\beta}\cdot f_\beta\tag{v}
\] 
hold in $U_\alpha\cap U_\beta$.
This gives
a globally defined meromorphic
function
$\psi $ such that
\[ 
\psi|U_\alpha=e^{g_\alpha}\cdot f_\alpha\tag{vi}
\]
Finally,  the construction of the $f$-functions  implies  that 
the principal divisor $D(\psi)$ is equal to the given divisor $D$
which finishes the proof of Weierstrass' theorem.
\bigskip


\noindent
{\bf{4.4 The construction of a non-vanishing holomorphic form.}}
By ¤ xx there exists a non-zero global section $\omega$ in $\Omega(X)$.
If $(\Delta,z)$ is a chart we have
\[
\omega|\Delta=g(z)\cdot dz
\]
where $g\in\mathcal O(\Delta)$ is non-constant and hence has
a discrete set of zeros.
The locally defined divsors of these $g$-functions
match each other and yield a globally defined
divisor
$D=\{(p_\nu;k_\nu)\}$ in $X$.
Notice that
$D$ is positive, i.e.
 the integers $k_\nu>0$.
Weierstrass's theoren gives
$\psi\in\mathcal O(X)$ with $D(\psi)=D$.
Then it is clear that
\[ 
\omega^*=\psi^{-1}\cdot \omega
\]
yields a holomorphic 1-form whose associated $g$-functions in local charts
are zero-free.

\bigskip


\centerline{\bf{4.5 The Mittag-Leffler theorem.}}
\bigskip


\noindent
Announce and Prove !
 
\newpage




\centerline{\bf{¤ 5. The uniformisation  theorem}}

\bigskip


\noindent
Consider a  non-compact Riemann surface
$X$ where  every holomorphic 1-form is $\partial$-exact.
By ¤ xx there exists $\omega\in \Omega(X)$ which is everywhere 
non-zero.
So if $Y$ is an open set in $X$
and $\mu\in\Omega(Y)$
 there exists $g\in\mathcal O(Y)$ such that
 \[ 
 \mu= g\cdot \omega_Y\tag{i}
\] 
where $\omega_Y$ is the restriction of $\omega$ to $Y$.
We use this to prove

\medskip

\noindent
{\bf{5.1 Proposition.}} \emph{If 
$Y$ is  an open Runge set in $X$ one has}
\[
\Omega(Y)=\partial(\mathcal O(Y))\tag{5.1.1}
\]

\noindent
\emph{Proof.}
Let  $\mu$ be as in (i).
Consider a point $y_0\in Y$ and a closed curve
$\gamma$ in $Y$ which has $y_0$ as initial 
and terminal point.
Since $Y$ is Runge, Theorem 0.2.2  gives  a sequence
$\{g_n\}$ in $\mathcal O(X)$ and 
the maximum norms $|g_n-g|_\gamma\to 0$.
It follows that
\[
\int_\gamma\, \mu=\lim_{n\to\infty}\, \int_\gamma\, g_n\cdot \omega
\]
Here $\gamma$ is a closed curve in $X$ and since
each $g_n\cdot \omega$ belong to $\Omega(X)$ the 
hypothesis on $X$ implies
that the integrals in
the right hand side above are all zero. Hence
the line integrals of $\mu$ are zero for all closed curves
at $y_0$ and then  ¤ xx shows  that it is $\partial$-exact in $Y$
which finishes the proof.

\medskip

\noindent
{\bf{5.2 Semi-local conformal mappings.}}
Let $Y$ be a relatively compact open subset of $X$ which is 
Runge and Dirichlet regular.
Let $y_0\in Y$ and by
¤¤ there exists
$g\in\mathcal O(X)$ with  a simple zero at $y_0$ and  zero-free
in $X\setminus\{y_0\}$.
Now $\mathfrak{Re}(g)$ restricts to a continuous function
on $\partial Y$ and we find a harmonic function
$u$ in $Y$ whose boundary value function is
$\log |g|$.
The equality (5.1.1) and the remark in ¤ xx  entail that
$u$ has a harmonic conjugate $v$ in $Y$
which gives $u+iv\in\mathcal O(Y)$. Set
\[
f=g\cdot e^{-(u+iv)}
\]
On $\partial Y$ it follows that
\[ 
|f|=|g|\cdot e^{-\log|g|}=1
\]
At the same time $f$ has a simple zero at $y_0$ and is zero-free in
$Y\setminus \{y_0\}$.
The result in ¤ xx shows  that
$f\colon Y\to D$ is biholomorphic.
Around $y_0$ we choose a small chart
$(\Delta,z)$ and get the non-zero complex derivative 
$f'(0)$
of $f$ at $z=0$.
With
\[
f^*=\frac{1}{f'(0)}\cdot f\tag{4.2.1}
\] 
we have a 
biholomorphic mapping from $Y$ into the open disc of radius
$|f'(0)|$
and  the $f^*$-derivative at $z=0$ is one.




\medskip

\noindent
{\bf{5.3 A global construction.}}
By ¤ xx we can exhaust $X$ with an increasing sequence of
relatively compact open subsets
$\{Y_n\}$ which are Runge and Dirichlet regular.
Fix a point $p\in Y_0$
and a local chart $(\Delta,z)$ as above.
For each $n\geq 0$  (5.2.1) gives some $r_n>0$ and a biholomorphic map
\[
f_n\colon Y_n\to D(r_n)
\]
where $f_n(p)=0$ and $f'_n(0)=1$.
The inverse mapping $f_n^{-1}$
is holomorphic in the open disc $D(r_n)$
and we notice that the complex derivative
\[
(f_n^{-1})'(0)=1\tag{i}
\]
Next, to each $n\geq 0$ we have the  composed function
\[
h_n= f_{n+1}\circ f_n^{-1}
\]
which maps $D(r_n)$ into $D(r_{n+1})$
where $h_n(0)=0$ and (i) gives
$h'_n(0)=1$. Schwarz'  inequality implies that 
\[
r_n\leq r_{n+1}
\]
Set
\[ 
R= \lim_{n\to\infty}\, r_n
\]
We shall construct a biholomorphic map
$f^*\colon X\to D(R)$  where the case $R=+\infty$ means that
$D(+\infty)={\bf{C}}$.
To find $f^*$ we shall pass to certain subsequences of 
$\{f_n\}$.
Consider first the composed functions
\[
g_n= \frac{1}{r_0}\cdot f_n\circ f_0^{-1}(r_0z)
\]
which by the choice of $r_0$ and the inclusion $Y_0\subset Y_n$ are
holomorphic in the open unit disc $D$ of the complex $z$-plane.
It is clear that
we have
\[
g_n(0)=0\quad\colon g'_n(0)=1
\]
Moreover, $g_n$ is a biholomorphic map from
$D$ onto the
open set $r_0^{-1}\cdot f_n(Y_0)$.
By the  result from ¤ xx  $\{g_n\}$ is a normal family in the sense lof
Montel. Hence we can extract a subsequence
$\{g_{n_k}\}$ which converges uniformly on compact subsets
of $D$.
\medskip

\noindent
{\bf{5.4 Exercise.}}
Verify that
the convergence of $\{g_{n_k}\}$  above entails that
$\{f_{n_k}\}$  converges uniformly over compact subsets of $Y_0$
to a limit function $f^*_0\in\mathcal O(Y)$.
Moreover, since
each restriction $f_{n_k}|Y_0$
is biholomorphic and the derivatives
$f'_{n_k}$ at $p$ all are equal to one, 
it follows from
the result in ¤ xx that
$f^*_0\colon Y_0\to f_0^*(Y_0)$ is biholomorphic.
\bigskip

\noindent
Next, starting with the sequence 
\[
g_k= r_1^{-1}\cdot f_{n_k}\circ f_1^{-1}
\]
we repeat the arguments above and find
a subsequence $\{\phi_{k_j}\}$ which conveges uniformly  in the unit disc
and
returning  to the $f$-sequence,  its corresponding  subsequence
converges uniformly on $Y_1$ to a limit function
$f^*_1$ which yields a biholomorphic map from
$Y_1$ onto $f^*_1(Y_1)$.
We  continue  
by an induction over $n$ and 
obtain  biholomorphic maps $\{f^*_n\colon Y_n\to f^*_n(Y_n)\}$ 
and after the passage to a  "diagonal subsequence" we find
a subsequen ce $\{f_{n_k}\}$ which converges uniformly on compact subsets of
$x$ to a limit function $f^*$ which gives the requested biholomorphic map
from $X$ onto $D(R)$.

 
\end{document}
























 




















 








  
  
 



































\newpage







































Sheaves and currents will be used in the subsequent proofs.
The crucial result in this chapter are  the following vanishing theorems.

\medskip

\noindent
{\bf{0.1 Theorem.}}
\emph{For every non-compact Remann surface one
has
 $H^1(X,\mathcal O)=0$.}
\bigskip

\noindent
Next, let $\mathcal O^*$ be the multiplicative sheaf whose sections
are zero-free holomorphic functions.

\medskip


\noindent
{\bf{0.2 Theorem.}}
\emph{The cohomology group $H^1(X,\mathcal O^*)=0$.}
\medskip

\noindent
A locally free sheaf of $\mathcal O$-modules of rank one is called
a holomorphic line bundle
As explained in ¤ xx the family of holomorphic line bundles
correspond to elements in
$H^1(X,\mathcal O^*)=0$. So Theorem 0.2 means that
every holomorphic line bundle $\mathcal L$
is holomorphically trivial
and as a sheaf  therefore isomorphic to
$\mathcal O$ which by Theorem 0.1 entails that
\[
H^1(X;\mathcal L)=0\tag{*}
\]


\noindent
However, to  prove Theorem 0.2 we shall  need 
(*) and we shall later on explain how
(*) can be established in a similar way as in the special case
$\mathcal L=\mathcal O$.
\medskip

\noindent
{\bf{0.3 Some  cohomology groups.}}
The sheaf $\Omega$ is a locally free sheaf of $\mathcal O$-modules of rank one
and there is  the exact sequence of sheaves:
\[ 
0\to {\bf{C}}_X\to \mathcal O\overset\partial\to \Omega\to 0
\]
Passing the the long exact sequence of cohomology
the vanishing in
(*)  entails that
\[ 
H^2(X,{\bf{C}}_X)=0
\]
From this
it follows trivially - see ¤ xx - that
if the complex field ${\bf{C}}$ is replaced by the field of rational numbers
then
\[
H^2(X,Q_X)=0\tag{i}
\]
Next,   the exponential map
which sends a holomorphic function $f$ to
the zero-free function $e^{2\pi i f}$
gives an exact sequence of sheaves:
\[
0\to {\bf{Z}}_X\to \mathcal O\overset{\text{exp}}\to \mathcal O^*\to 0
\]
Passing to the long exact sequence of cohomology  we get
\[
H^1(X,\mathcal O^*)\simeq
H^2(X,{\bf{Z}}_X
\]
So Theorem 0.2 anounts to show that
the last cohomology group is zero.
We have already  (i) so 
Theroem 0.2 is
"almost" derived from 
(*).
However, extra arguments will be needed to 
get Theorem 0.2 which we begin to explain.
Let  $\mathcal L$
ibea holomorphic line bundle.
By definton it is trivial, i.e. isomorphic to $\mathcal O$ if and only if it
has a global generating section.
Suppose to begin with that one has found
a non-constant global section $\xi\in \mathcal L$.
The zeros of $\xi$ is some (possibly empty) discrete set in $xX$.
Let $\{q_\nu\}$ be these zeros and $\xi$ vanishes of some
order $k_\nu$ at $q_\nu$.
Suppose we have
found
a meromorphic function $g$ in $X$
with poles of order $k_\nu$ at every
 $q_\nu$ while $g$ is a zero-free holomorphic function outside this
 discrete set.
 Then $g\cdot \xi\in\mathcal L(X)$ is 
 a global section which gives the requested
trivialisation so that
 $\mathcal L\simeq \mathcal O$.
 So in order to get Theorem 0.2 we need to 
 prove the existence of globally defined meromorphic functions
 with prescribed
 poles on  discrete subsets  of  $X$.
The whole discussion has shown that Theorem 0.2 follows if we in addition to
Theorem 01 and its extension in  (*) have established the following:
\medskip

\noindent
{\bf{0.4 Theorem.}}
\emph{Every divisor $D$ on $X$ is principal, i.e.
equal to $D(f)$ for some
$f\in\mathfrak {M}(X)$.}

 
 
\bigskip


\noindent
{\bf{0.5 Runge's theorem.}}
Recall from ¤ xx that an open subset $Y$ in $X$ is a Runge domain if
every connectd component of the closed complemnet $X\setminus y$
is non-compact. The following result will
be used to prove Theorem 0.1 and  has also independent interest:

\medskip

\noindent
{\bf{0.6 Theorem.}}
\emph{Let $Y\subset X$ be a Runge domain.
Then
the restriction map $\mathcal O(X)\to \mathcal O(Y)$ has a dense image.}
\bigskip

\noindent
The results above constitute the
major facts in this section.
To prove Theorem 0.1  we first establish  seeemingly weaker results
and after 
finish the proofs of the the other  results.
\medskip

\centerline{\bf{¤ 1. A finiteness result.}}

\medskip

\noindent
Consider
an connected open subset $Y$ 
which is relatively compact in
$X$. The boundary
$\partial Y$
is  compact but in general it need not be connected.
It can for example consist of a finite number of pairwise disjoint
and closed Jordan curves
together with some Jordan arcs and
some isolated points, like an annulus where
a finite set of points in the open annulus have been
removed.
If $\partial Y$
is "nice", for example piecewise analytic
then
tthe cohomology group
$H^1(Y,{\bf{C}})$ is a finite dimensional complex vector space.
Recall also from ¤ xx that one has
the isomorphism
\[
\frac{\mathcal E^1(Y)}{d(\mathcal E(Y))} \simeq
H^1(Y,{\bf{C}})
\]
and
as explained in ¤ xx there exists   an injective map
\[
\frac{\mathcal E^{0,1}Y)}{\bar\partial(\mathcal E(Y))}\to
H^1(Y,{\bf{C}})
\]
Moreover, Dolbeault's Theorem   identifies
right hand side with
$H^1(Y,\mathcal O)$ and hence
this cohomology group is finite dimensional
for every $Y$ as above with a nice compact boundary.
The finite-dimensionality
enable us to construct non-constant meromorphic functions on
$Y$.
Namely, if $p\in Y$ is fixed we
take a positive integer $N$ and
the sheaf $\mathcal O_D$ where $D$ is the divisor
$N\cdot p$ which means that one allows a pole of order
$\leq N$ at $p$.
Exactly as in the compact case from ¤ xx one has an exact sequence
\[ 
0\to \mathcal O(Y)\to \mathcal O_D(Y)
\to {\bf{C}}^N\to H^1(Y,\mathcal O)\to H^1(Y,\mathcal O_D)\to
0
\]
If $N$ is strictly larger than
the dimension of
$H^1(Y,\mathcal O)$ we  get a non-zero
section of  $\mathcal O_D$, i.e. a meromorphic
function
in $Y$
with a pole of order
$\leq N$ at $p$ and otherwise  holomorphic.


\bigskip


\centerline{\bf{ ¤ 2. A vanishing lemma.}}
\medskip

\noindent
Consider a pair  $Y\subset Y_1$ 
where $Y$ is relatively compact in $Y_1$.
As explained in ¤ xx one has  the restriction map

\[
\mathcal L\colon H^1(Y_1,\mathcal O)\to 
H^1(Y,\mathcal O)\tag{2.1}
\]
\medskip

\noindent
{\bf{2.2 Proposition.}}
\emph{If $H^1(Y;\mathcal O)$ is finite dimensional
the $\mathcal L$-image in (2.1) is zero}
\medskip

\noindent
\emph{Proof.}
Choose $\xi_1,\ldots,\xi_K$ in  
$H^1(Y_1,\mathcal O)$ such that
$\{\mathcal L(\xi_k)\}$
gives a basis for the  $\mathcal L$-image
in the finite dimensional vector space
$H^1(Y;\mathcal O)$.
Next, we can find
a 
relatively compact set
$Y_2$ in $X$ where $Y_1<< Y_2$
and $\partial Y_2$ is "nice" so that
$H^1(Y_2,\mathcal O)$ is finite dimensional.
Fix a point $p\in Y_2\setminus Y_1$ and from ¤ 1 we 
find
a meromorphic function
$f$
in $Y_2$ 
which restricts to a holomorphic funtion in
$Y_1$
which is not constant  on the connected components of this set.
Now we get the vectors
$\{f\cdot \xi_k\}$  in $H^1(Y_1,\mathcal O)$
and take  their $\mathcal L$-images.
Since we have chosen a basis above 
there is an $N\times n$-matrix $B$ with complex
elements such that

\[ 
\mathcal L(f\cdot \xi_k)=\sum_{j=1}^{j=N}\,
b_{kj}\cdot \mathcal L(\xi_j)\tag{i}
\]
Let us now consider
the holomorphic function in $Y_1$ defined by 
\[ 
F=\det(f\cdot E_N-B)
\]
Then (i) and Cramer's rule entail that
\[
\mathcal L(F\cdot \xi_k)=0\quad\colon\, 1\leq k\leq N\tag{ii}
\] 
Above $F$ is meromorphic in $Y_2$ with no poles
in the relatively compact subset $Y_1$.
We can therefore cover $Y_1$ with a finite number of charts
$\mathfrak{U}= \{U_\alpha\}$
such that
$F$ has no zeros in
non-empty intersections $U_\alpha\cap U_\beta$ when
$\alpha\neq \beta$.
Let us then take some $\eta\in H^1(Y_1,\mathcal O)$ which by 
Lerays theorem is represented by a cocycle
$\{\phi_{\alpha,\beta}\}$
in $Z^1(\mathfrak{U},\mathcal O)$.
Since $F\neq 0$ on each non-empty intersection we get  the cocycle
$\{\psi_{\alpha,\beta}= F^{-1}\cdot \phi_{\alpha,\beta}\}$
which represents a vector in $H^1(Y_1,\mathcal O)$ denoted by
$\eta^*$.
From  these  constructions we get
\[ 
\mathcal L(\eta)=\mathcal L(F\cdot \eta^*)
\] 
By (ii) the last term is zero and since
$\eta\in H^1(Y_1,\mathcal O)$ was arbitrary Proposition 2.2 is proved.

\medskip

\noindent
{\bf{2.3 A $\bar\partial$-equation.}}
Consider a pair $Y<< Y_1$ as above.
Dolbeault's theorem and Proposition 2.2  imply
that every  $\phi\in \mathcal E^{0,1}(Y_1)$
restricts to a $\bar\partial$-exact form on $Y$, i.e.
there exsits $g\in \mathcal E(Y)$ such that
\[ 
\bar\partial g=\phi|Y\tag{2.3.1}
\]
\medskip

\noindent
Now we can establish  a density result:

\medskip

\noindent
{\bf{2.4 Proposition.}}
\emph{Let $Y$ be 
a relatively compact
Runge domain in $X$. Then, for every $Y_1$
sich that $Y< Y_1$ and $H^1(Y_1,\mathcal O)$ is finite dimensional
it follows that  the restriction map from 
$\mathcal O(Y_1)$ to $\mathcal O(Y)$ has a dense image.}
\bigskip


\noindent
\emph{Proof.}
By the Hahn-Banach Theorem it suffices to show that 
for every (1,1)-current $\gamma$ with  some compact support $K$  in $Y$
one has the implication
\[ 
\gamma(f|Y)=0\quad\forall \,\, f\in \mathcal O(Y_1)\implies
\gamma|\,\mathcal O(Y)=0\tag{i}
\]
Consider a current $\gamma$ as above which vanishes on
each restricition of $f\in\mathcal O(Y_1)$
to $Y$ and let  $k$ be its compact support in $Y$.
Next,  choose an open set $Y_2$
where $Y_1<< Y_2$ and (2.3.1)
holds for this pair. So when
$\phi\in \mathcal E^{0,1}(X)$
there exists
$g\in \mathcal E(Y_1)$ such that
\[
\bar\partial g=\phi|Y_1
\]
Above $g$ is unique up to a
function in $\mathcal O(Y_1)$ and since
$\gamma$  vanishes on
$\mathcal O(Y_1)|Y$ 
the evaluation $\gamma(g)$ only depends upon $\phi$.
Hence there exists a current $S$ on $X$
defined by
the process above, i.e.
\[
S(\phi)= \gamma(g|Y)\quad\colon\,\bar\partial g=\phi|Y_1
\]
If $h\in C_0^\infty(X\setminus K)$
we get the $(0,1)$-form
$\bar\partial(h)$ and by the constructions above
\[ 
S(\bar\partial h)= \gamma(h|Y)=0
\] 
where the last equality follows since
$\gamma$Êis supported by $K$.
This means that the current $S$ is $\bar\partial$-closed in
$X\setminus K$ and since $\bar\partial$ is elliptic
the restricttion of $S$
 to $X\setminus K$ is expressed by a holomorphic 1-form
$\sigma\in \Omega(X\setminus K)$.
So far we have not used the assumption that $Y$ is Runge.
To profit upon this we consider
the compact hull
$\mathfrak{h}(K)$ from ¤ XX.
If
$y\in Y\setminus \mathfrak{H}(K)$  
the connected component $V$
in
$X\setminus  K$ which contains $y$ is non-compact.
Since the current $S$ has  compact support it follows that
\[ 
V\setminus \bigl(\text{Supp}(S)\cup K\bigr)\neq \emptyset\tag{ii}
\]
Now $\sigma$ respresents $S$ outside $K$
and  therefore it must vanishes in
the open set (ii).
By analyticity $\sigma$ vanishes in the whole connected
set $V$ and hence in a neighborhood of $y$.
Since $y$ was arbitrary we conclude that 
$\sigma$ vanishes identically in
$Y\setminus \mathfrak{h}(K)$.
Let us now consider some
$f\in \mathcal O(Y)$ and 
take
$g\in C_0^\infty(Y)$ where
$g=f$  in an open neighborhood of
$\mathfrak{h}(K)$.
It follows that
\[ 
S(\bar\partial(g))=\gamma(g|Y)= \gamma(f)
\] 
where the last equality holds since
$K$ is the support of $\gamma$.
Finally, since
$f$ is holomorphic we have $\bar\partial g=0$ in a neighborhood of
$\mathfrak{H}(k)$
and since $\sigma$ is supported by $\mathfrak{h}(K)$ it follows that
$S(\bar\partial(g))=0$. Hence 
$\gamma(f)=0$ for every $f\in \mathcal O(Y)$
which proves the requested implication (i)
above and hence the density in
Proposition 2.4.



\medskip

\noindent
{\bf{Remark.}}
 The
 proof above
 is attributed to Malgrange and  we  followed
 the presentation in  [Forster: page xx-xx].
 \bigskip
 
\noindent
{\bf{2.5 The case of locally free $\mathcal O$-modules.}}
If $\mathcal L$ is 
a locally free sheaf of $\mathcal O$-modules with rank one
similar results as above hold. Theproofs are more or less verbatim.
More precisely we first have some locally finite covering
$\mathfrak{U}=\{U_\alpha\}$ by simply connected charts
and $\mathcal L|U_\alpha$ are trvial for every $\alpha$, i.e.
there exists a section $\rho_\alpha\in\mathcal L(U_\alpha)$
such that the restricted sheaf
$\mathcal L|U_\alpha$ is the free
$\mathcal O_{U_\alpha}$-module 
generated by $\rho_\alpha$.
Shrinking $\mathfrak{U}$ if necessary we may assume that
the transistion functions which give
\[
\rho_\beta= \phi_{\beta\alpha}\cdot \rho_\alpha
\]
 in each non-empty intersection $U_\beta\cap U_\alpha$ yiled bounded
 holomrphic functions, i.e. the maximum norms
 \[
 || \phi_{\beta\alpha}||_{U_\beta\cap U_\alpha}<\infty
\]
When
this holds it is meaningful to speak about convergence for $\mathcal L$-valued sections.
More precisely, let 
$Y<< Y_1$ and $\{\rho_\nu\in\mathcal (Y_1)\}$
be given. If $\rho_*\in \mathcal L(Y)$ and $K$ is a compact subset
of
$Y$ we leave it to the reader to
clarify the condition that $\{\rho_\nu|K$ converges in a uniform way to
$\rho|K$, i.e. u
Thus, in Propostion 22and 2.4 we can replace $\mathcal O$ by
any $\mathcal L$. Concerning (2,3,1) we ntocie that
there exists the sheaf
\[
 \mathcal E_\mathcal L= 
 \mathcal O_\mathcal L\otimes_\mathcal O\,\mathcal E
\]
and
a well  defined map
\[
\bar\partial\colon\mathcal E_\mathcal L\to \mathcal E^{(0,1)}_\mathcal L
\]
So now (2,3,1) means that if $\phi\in \mathcal E^{(0,1)}_\mathcal L(Y_1)$
then there exists
$g\in \mathcal E_\mathcal L(Y)$ such that
\[
\bar\partial(g)=\phi|Y
\]





\centerline{\bf{2.5 Proof of Theorem 0.1}}
\medskip

\noindent
By  ¤ XX we  exhaust $X$ by an increasing sequence of Runge domains
$\{Y_n\}$
where $Y_n<<Y_{n+1}$ and $\{H^1(Y_n,\mathcal O)\}$ are finite dimensional.
Consider
some $\phi\in \mathcal E^{0,1}(X)$. Now (2.3.1) applies to each
piar $Y_n<< Y_{n+1}$ and since $\phi$ restricts to 
$\mathcal E^{(0,1)}(Y_{n+1}$
there exists
$f_n\in \mathcal E(Y_n)$
such that 
\[
 \bar\partial f_n=\phi|Y_n
\]
It follows that
the restriction to $Y_n$ of $f_{n+1}-f_n$ is holomorphic.
Now $Y_{n-1}<< Y_n$ and
Proposition 2.4 entails that
this restricted holomorphic function can be uniformly approximated on
$Y_{n-1}$ by functions from $\mathcal O(Y_{n+1}$.
In particular we find
$g_{n+1}\in \mathcal O(Y_{n+1})$
such that the maximum norm
\[
||f_{n+1}+g_{n+1}-f_n||_{Y_{n-1}}<2^{-n}
\]
With $f^*_{n+1}= f_{n+1}+g_{n+1}$
we still have
\[
\bar\partial f^*_{n+1}=\phi|Y_{n+1}
\]
Pwerforibng these modfifications inductively we get
anew sequence $\{f^*_n\}$ where  (xx) hold for every $n$
while
\[
||f^*_{n+1}-f^*_n||_{Y_{n-1}}<2^{-n}
\quad\colon \, n=1,2,\ldots
\]
It follows that $\{f_n^*\}$ converge uniformly on $X$ to a continuous function
$F$.
This entials that
the distributuons
$\\bar\partial f_n^*\}$ converge to the distribution derivative
$\bar\partial (F)$ and by (xx) it is clear that
the following hold on the whole of $X$:
\[ 
\bar\partial(F)=\phi
\]
Now $\phi$ is a smooth form and the elliptic property of
$\bar\partial$ implies that
$F$ is a $C^\infty$-function. Hence the mapping
\[ 
\bar\partial\colon \mathcal E(X)\to \mathcal E^{(0,1)}(X)
\]
is surjective.
Dolbeaualt's theorem gives  $H^1(X,\mathcal O)=0$
and Theorem 0.1 is proved.
\medskip

\noindent
{\bf{2.7 Exercise.}}
Use the remarks from ¤ 25.5
and repeat the methods above to show that
\[
H^1(X,\mathcal L)=0
\] 
for every locally free sheaf of $\mathcal O$-modules with rank one.



\newpage




\newpage





Weierstrass product formula asserts that
 every divisor on $X$ is principal-
 

By a differentalble 1-chain in $X$ we mean a map 
$t\to c(t)$ from the unit interval $[0,1]$ with values in $X$ which
has a continuous derivative. The 1-chain is denoted by
${\bf{c}}$. 
The end points $q=c(0)$ and $p=c(1)$ can be either equal or
different and it is not assumed that
the map $t\to c(t)$ is 1-1, i.e. the  image curve
can   have several "self-intersections".
If $\omega$ belongs to $\mathcal E^1(X)$, i.e. a smoooth 
differential 1-form, then  we take its pull-back to $[0,1]$ and
obtain the integral
\[ 
\int_{{\bf{c}}}\, \omega\tag{1}
\]
Notice that
(1) yields a 1- current of since
$\omega\mapsto \int_{{\bf{c}}}\, \omega$ is a continuous linear form
and the current is supported by the compact image under the $c$-map.
We can construct other compactly supported 2-currents
as follows:
Let $p_1,\ldots,p_k$ be a finite set of points in $X$
and $U$ some relalitively  compact open  subset which contains
this $k$-tuple.
Now we consider a global section $\psi$of the sheaf
$\mathfrak {M}\otimes_\mathcal O\, \mathcal E$
with the following properties:
First $\psi$ is a zero-free $C^\infty$-function in
$X\setminus \{p_1,\ldots,p_k\}$ and it is identically one
in $X\setminus U_*$ where $\overline{U_*}$ is a compact subset of $U$.
Finally, if $(\Delta,z)$ is a small chart centered at some $p_\nu$ then
\[
 \psi|\Delta= z^{e_\nu}\cdot \psi_\nu(z)
\]
where $e_\nu$ is
some integer and $\psi_\nu$ a zero-free $C^\infty$-function in $\Delta$.
Here $e_\nu$ can be positive or negative.
Now there exists the current
\[ 
\gamma= \frac{\partial \psi}{\psi}
\]
Since $\psi=1$ in $X\setminus U$
the support of this current is contained in the compact set
$\overline{U_*}$. By defintion
\[ 
\gamma(\omega)=
 \omega\wedge \frac{\partial \psi}{\psi}
\] 
for every smooth 1-foirm $\omega$.
In the case when 
there exists $g\in\mathcal E(U)$ such that 
$\omega=d g$ holds in $U$ we have:
\[
\gamma(\omega)=\int \,dg\wedge \frac{\partial \psi}{\psi}=
\int \,\bar\partial(g) \wedge \frac{\partial \psi}{\psi}
\]
where the last equality follows since
$dg=\partial g+\bar\partial g$ and
the exterior product
$\partial(g) \wedge \frac{\partial \psi}{\psi}=0$.

\medskip

\noindent
{\bf{0.6.7 Exercise.}} Apply Stokes Theorem and show that (x) is equal to
\[ 
-2\pi i\cdot \sum\, e_\nu\cdot g(p_\nu)
\]
So in the special case when
the 1-current $\gamma$ satisfies
\[
\int_{\bf{c}}\, dg=
\gamma(dg)\quad\colon g\in \mathcal E(X)\tag{0.6.7}
\]
it follows that
$\{p_\nu\}$ is reduced to the pair $q,p$ where
$e_q=1$ and $e_p=-1$.
In ¤ xx w shall prove that
when ${\bf{C}}$ is given as above then
there existd
a $\psi$-.function such that 
(0.6.7) holds and this turns out to be the key point in  the
proof of
Weierstrass' result in (0.3).



































\end{document}

 




 


