
\documentclass{amsart}

\usepackage[applemac]{inputenc}


\addtolength{\hoffset}{-12mm}
\addtolength{\textwidth}{22mm}
\addtolength{\voffset}{-10mm}
\addtolength{\textheight}{20mm}

\def\uuu{_}

\def\vvv{-}


 \begin{document}


\centerline{\bf{¤ 6. The Riemann-Schwarz inequality.}}

\bigskip


\noindent
By the uniformisation theorem for Riemann surfaces it
suffices to prove the result in ¤¤ when $X=D$ and
$u$ is a continuous and subharmonic function in $D$
where 
$\lambda(z)= e^{u(z)}$ which yields a metric.
Consider a pair of points $a,b$ in $D$ and a pair of rectifiable 
Jordan arcs
$\gamma_1,\gamma_2$ in $\mathcal C(a,b)$.
Suppose for the moment that
the intersection of
the $\gamma$-curves only contains the end-points $a$ and $b$.
Their union gives
a closed Jordan curve
$\Gamma$ which borders a Jordan domain
$\Omega$.
The inequality (*) in  Theorem XX follows 
if there to each
point $p\in\gamma_1$ exist
a Jordan arc
$\beta$ in $\Omega$ which joins $p$ with some 
$q\in\gamma_2$ and a
Jordan arc $\alpha$ in $\Omega$ which joins $a$ and $b$ such that
\[
\bigl(\int_\alpha\, \lambda(z)\, |dz|\bigr)^2+
\bigl(\int_\beta\, \lambda(z)\, |dz|\bigr)^2\leq
\frac{1}{2}\cdot\bigl[\,
\bigl(\int_{\gamma_1}\, \lambda(z)\, |dz|\bigr)^2+
\bigl(\int_{\gamma_2}\, \lambda(z)\, |dz|\bigr)^2\bigr ]\tag{1}
\]
To prove (1) we employ a conformal mapping
$\psi\colon D\to \Omega$ where $D$ is another unit disc with
the complex coordinate $w$. Recall that the  Koebe-Lindelšf theorem
entails 
that $\psi$ extends to a homeomorphism from $D$ onto the closed Jordan 
domain $\bar\Omega$ where the inverse images of  $\gamma_1$ and $\gamma_2$
is a pair of closed intervals on the unit circle $|w|=1$
which
instersect  at two points. Now
$\log\,\lambda\circ \psi$
is subharmonic in $D$ and 
if $\gamma$ is a rectifiable  arc in $\Omega$ one has the equation:
\[
\int_\gamma\, \lambda(z)\cdot  |dz|
=\int_{\psi(\gamma)}\, \lambda\circ \psi(w)\cdot\frac{|dw|}{|\psi'(w)|}
\]
Set
\[ 
\lambda^*(w)=\frac{1}{|\psi'(w)|}\cdot \lambda\circ \psi(w)
\]
Then
\[ 
\log \lambda^*=-\log |\psi'(w)| +\log  \lambda\circ \psi
\] 
Here 
$\log |\psi'(w)|$ is the real part of the analytic function $\log \psi'(w)$
in $D$ and hence harmonic  which entails that
$\log\lambda^*$ is subharmonic.
The proof of (1) is now reduced to the case when
$\Omega$ is replaced by the unit $w$-disc where
$\lambda$ is replaced by $\lambda^*$.
Moreover, the Cauchy-Schwarz inequality gives
\[
\bigl(\int_{\gamma_1}\, \lambda^*(w)\, |dw|\bigr)^2+
\bigl(\int_{\gamma_2}\, \lambda^*(w)\, |dw|\bigr)^2\geq
\frac{1}{2}\cdot  \bigl(\int_{|w|=1}\, \lambda^*(w)\, |dw|\bigr)^2
\]
where we used that  
$\gamma_1\cup\gamma_2$ is equal to the whole unit circle $|w|=1$.
There remains only to find
a pair of curves $\alpha^*$ and $\beta^*$
in the $w$-disc where
$\alpha^*$ joins
the two points $\{e^{i\theta_\nu}\}$
on the unit circle where
the boundary  arcs $\psi^{-1}(\gamma_1)$ and $\psi^{-1}(\gamma_2)$ intersect
and the
$\beta^*$-curve
joins some point
$p\in \psi^{-1}(\gamma_1)$  with a point  $q\in  \psi^{-1}(\gamma_2)$. 
\medskip


\noindent
{\bf{The choice of
$\alpha^*$ and $\beta^*$.}}
Let  $\alpha^*$ be the circular arc
with end-points at $e^{i\theta_1}$ and $e^{i\theta_2}$
which intersects $\{|w|=1\}$ at right angles.
Next, given a point $p\in\psi^{-1}(\gamma_1)$ there exists the unique circular arc
$\beta^*$ which  intersects both
$\alpha^*$ and  $\{|w|=1\}$ at right angles. See figure ¤ XX.
With this choice there remains to prove
the inequality
\[
\bigl(\int_{\alpha^*}\, \lambda^*(w)\cdot  |dw|\,\bigr)^2+
\bigl(\,\int_{\beta^*}\, \lambda^*(w)\cdot  |dw|\,\bigr)^2\leq
\frac{1}{4}\cdot \bigl(\int_{|w|= 1\}}
\, \lambda^*(w)\, |dw|\,\bigr)^2\tag{2}
\]

\medskip


\noindent
To prove
(2) we shall use a symmetrisation of $\lambda^*$.
Namely,
there
exists a Mšbius transformation $T_1$
on the unit disc which is a reflection of $\alpha^*$, i.e.
it restricts to 
the identity map on $\alpha^*$ and the composed map
$T_1^2$ is the identity in $D$. Similarly we find the reflection $T_2$
of $\beta^*$. One easily verifies that
$T_2\circ T_1=T_1\circ T_2$.
Let $S_0(w)=w$ be the identity while 
$S_1=T_1$, $S_2=T_2$
and $S_3= T_2\circ T_1$. Set
\[ 
\lambda^{**}(w)=
\frac{1}{4}\cdot 
\sum_{\nu=0}^{\nu=3}
\, \lambda(S_\nu(w))\cdot |\frac{dS_\nu(w)}{dw}|\tag{3}
\]
Now $T_1$ maps $\alpha^*$ into itself, and similarly
$T_2$ maps $\beta^*$ into itself while the composed Mšbius transformation 
$S_3=T_2\circ T_1$ interchanges the two curves. Hence 
the left hand side in (2) is majorised  when 
$\lambda^*$ is replaced by  $\lambda^{**}$ and
the right hand side is  unchanged 
since the  $S$-transformations 
map $\{|w|=1\}$ onto itself.
Hence it suffices to prove (2)  when
$\lambda^*$ from the start is invariant with respect to the 
$S$-transformations. In this case
we solve the Dirichlet problem
using the boundary value function $\log\lambda^*$ on $\{|w|\}$ so that
\[ 
\log \lambda^*=u+H
\]
where $H$ is harmonic
in $D$ while  $u$ is subharmonic and zero on
$\{|w|\}$.
The maximum principle entails that
$u\leq 0$ in $D$ which gives 
\[ 
\lambda^*= e^u\cdot e^H\leq e^H\tag{4}
\]
Since $u=0$ the right hand side in (2) is does not change  while the left 
hand side is majorised when 
$\lambda^*$ is replaced by $e^H$.
The $S$-invariance of $\lambda^*$ implies that
$H$ also is $S$-invariant and
there exists an analytic function $g(w)$ in $D$ such that
\[
 e^{H(w)}= |g'(w)|
\]
where 
the map $w\mapsto g(w)$
sends $\alpha^*$ to a real interval $[-A,A]$ and $\beta^*$
to an imaginary interval $[-iB,iB]$. Hence (4) implies that
the left  hand side in (2) is majorized by
\[ 
\bigl(\int_\alpha\, |g'(w)|\ |dw|)^2+
\bigl(\int_\beta\, |g'(w)|\ |dw|\,\bigr)^2=
4A^2+4B^2\tag{5}
\]
Next, since
$\lambda^*=|g'|$ holds on $\{|w|\}$
the right hand side in (2) becomes
\[
\frac{1}{4}\cdot\bigl(
\int_{|w|= 1}\,
|g'(w)|\, |dw|\,\bigr)^2\tag{6}
\]
The $S$-symmetry of $g$ entails thst
$\int_{|w|= 1}\,
|g'(w)|\, |dw|$ is four times
the
integral taken along
a subarc of $T$ which joins
consequtive points where $\alpha^*$ and $\beta^*$ intersect
and every suvh integral is the euclidian length of
the image curvr under $g$ which by the above joins
the real point $A$ with $iB$. So its euclidian length is
$\geq \sqrt{A^2+B^2}$, i.e. we have used that the shortest
distance between a pair of points is a straight line and then applied
Pythagoras' theorem.
Hence (6)  majorizes 
\[ 
\frac{1}{4}\cdot \bigl (4\cdot \sqrt{A^2+B^2}\bigr)^2=4(A^2+B^2)\tag{7}
\]
Then (5) and (7) give the
requested inequality (2).









\newpage




\centerline{\bf{Abel's theorem.}}





\bigskip


\noindent
A divisor $D$ on $X$ consists of
an assignement of integers $\{\mu_\nu\}$ to a finite set of points $\{p_\nu\}$
in $X$. One writes
\[
D= \sum\, \mu_\nu\cdot \delta(p_\nu)
\]
The $\mu$-integers may be positive or negative.
The degree is defined by
\[
\deg D= \sum\,\mu_\nu
\] 
while the finite set $\{p_\nu\}$ is called the support of $D$.
Next we construct a class of 1-currents.
In general, let $\gamma\colon [0,1]\to X$
be an $X$valued function on the closed unit interval
We assume that $\gamma$ is continuous and has a
finite total variation. The last condition means that
there exists a constant $C$ such that
\[
\sum_{\nu=0}^{\nu=N-1}\, d(\gamma(t_{\nu+1},\gamma(t_\nu)\leq C
\]
for all sequences $0=t_0<t-1<\ldots<t_N=1$
Here $d$ is some  distance function 
on $X$ regarded as a metric space which in charts
is equivsoent to
the euclidian distance.
Every such $\gamma$ gives a current of degree one
acting on $\mathcal E^1(X)$ by 
\[
\alpha\mapsto \int_\gamma \,\alpha\tag{*}
\]
\medskip

\noindent
{\bf{Exercise.}} Explain how the classical Borel-Stieltjes integrals for functions
with bounded variation
defines the integral in the right hand side.
Show also that
\[
\int_\gamma\, dg= g(\gamma(1))-g(\gamma(0))
\]
hold for every $g\in\mathcal E()$.
One refers to (*) as an integration current of degree one.
More generally we can take a finite sum of such
currents and get the integration current
$\Gamma$ defined by
\[
\Gamma(\alpha)= \sum\, \int_{\gamma_j}\,\alpha
\]
Let $D=\sum\,\mu_\nu\cdot \delta(p_\nu)$ be a divisor of
degreee zero.
An integration current $\Gamma$ is said to be associated with
$D$ if the equality below hold for every
$g\in\mathcal E(X)$:
\[
\Gamma(dg)= \sum\, \mu_\nu\cdot g(p_\nu)
\]
\medskip

\noindent
{\bf{F.1 Principal divisors.}}
Let $f$ be a non-constant meromorphic function.
Now we have the finite set of poles $\{p_\nu\}$ and the finite set of zeros
$\{q_j\}$.
We associate the divisor
\[
\text{div}(f)= \sum\, \mu_k\cdot \delta(p_k)-\sum\, \mu_j\cdot \delta(q_j)
\]
Here $\mu_k$ is the order of the pole of $f$ at every $p_\nu$, while
$\mu_j$ is the order of a zero at $q_j$.
By the result in ¤ xx this divisor has degree zero.
A divisor $D$ of degree zero is called principal if
it is equal to $\text{div}(f)$ for some
$f\in\mathcal M(X)$.
Notice that if $f$ and $g$ is a pair of non-constant meromorphic functions such that
$\text{div}(f)= \text{div}(g)$, then
$f/g$ is a holomorphic function on $X$ and hence reduced to a non-zero constant.
Introducing the multiplicative group
$\mathcal M(X)^*$ of non-constant meromorphic functions
this means that one has an injective map
\[
\frac{\mathcal M(X)^*}{{\bf{C}}^*}\to\mathcal D_0
\]
where $\mathcal D_0$ is the additive group of divisors whose degree are zero.
The  theorem below describes the range of this map.

\medskip

\noindent
{\bf{F.2 Theorem.}}
\emph{A divisor $D$ of degree zero
is principal if and only if there
exists an integration current $\Gamma$ associated with
$D$  such that}
\[
\Gamma(\omega)=0\quad\colon \,\,\gamma\in \Omega(X)
\]
\medskip

\noindent
The proof requires several steps.
First we shall show the "if part", i.e. if 
$\Gamma$ exists so that (*) holds then
the divisor $D$ is principal.
To achieve this we first
perform a local construction in the complex plane.
\medskip

\noindent
{\bf{F.3 A class of currents in ${\bf{C}}$.}}
In the complex $z$-plane we consider
a point $z_0$ where 
\[
0<|z_0|<r<1
\]
holds for some $0<r<1$.
It is easily seen that there exists
a $C^\infty$-function $a(z)$  in ${\bf{C}}$
which never is zero and the function
\[
\phi(z)= \frac{z}{z-z_0}\cdot a(z)
\]
is identically one when
$|z|\geq r$.
Now $z\mapsto \frac{1}{z-z_0}$ is locally integrable around
$z_0$ and hence $\phi$ belongs to 
$L^1_{\text{loc}} ({\bf{C}})$ and is therefore a distribution.
\medskip

\noindent
Cauchy's residue formula can be expressed by saying
the $\bar\partial$-image of the $\frac{1}{z}$
is equal to the $(0,1)$-current
$2\pi i\cdot \delta(0)d\bar z$ where $\delta(0)$ is the Diraqc distribution
at the origin.
Using this the reader can check that
\[
\bar\partial(\phi)=
 \frac{z}{z-z_0}\cdot \bar\partial(a)+z_0a(z_0)\cdot \delta(z_0)d\bar z\tag{i}
 \]
 from (i) the reader should also check that
 \[
 \phi^{-1}\cdot \bar\partial(\phi)= a^{-1}\cdot \bar\partial(a)\tag{ii}
 \]
 \medskip
 
 \noindent
 {\bf{F.4 The current $\phi^{-1}\cdot \partial(\phi)$.}}
 To begin we one has
 \[
 \partial(\phi)=\frac{a(z)}{z-z_0}\cdot dz-
 \frac{za}{(z-z_0)^2)}\cdot dz+\frac{z}{z-z_0}\cdot \partial a\tag{F.4.1}
 \]
 Above $(z-z_0)^{-2}$ is the principal value distribution
 defined as in ¤ xx.
 \medskip
 
 \noindent
 {\bf{ Exercise.}}
 Use (F.4.1) to establish the equation
 \[
 \phi^{-1}\cdot \partial(\phi)=z^{-1}\cdot dz-(z-z_0)^{-1}\cdot dz+
 a^{-1}\cdot \partial(a)\tag{F.4.2}
 \]
 \medskip
 
 \noindent
 {\bf{Exercise.}}
 Use Stokes Theorenm and Cauchy's residue fornula to
 prove that when the 1-current
 \[
 \phi^{-1}\cdot d\phi=  \phi^{-1}\cdot \partial(\phi)+ \phi^{-1}\cdot \bar \partial(\phi)
 \] 
 is applied to $dg$ for some
 $g\in C_0^\infty({\bf{C}}$, then
 \[
 \phi^{-1}\cdot d\phi<dg>\, = 2\pi i\cdot (g(0)-g(z_0)\tag{F.4.3}
 \]
\medskip


\noindent
 Let us now consider an integration current
 $\Gamma$ given by a finite sum
 $\sum\,\gamma_j$ where each $\gamma_j$ has compact support in
 a chart
 $(U_j,z_j)$ in $X$ and the end-points of
 $\gamma_j$ are $z_j=0$ and $z_j=z_j^*$
 with $0<|z_j^*|<r<1$ and $U_j$ is a chart defined by
 $\{|z_j|<1|]$.
In $X$ the point $z_j=0$ is denoted by $q_j$ while $z_j^*$ corresponds to a
point $p_j$.
It follows that 
 \[
 \int_\Gamma \, dg=\sum_{j=1}^{j=N}\, g(p_j)-g(q_j)\tag{F.5}
 \]
for every $g\in \mathcal E(X)$.
 Next, for each $j$ we apply the local contruction the chart
 and find a function
 $\phi_j$ in $X$ which is identically one
 in $X\setminus \{|z_j|\leq r\}$ such that 
 \[
 \phi_j^{-1}\cdot d\phi_j<dg>=2\pi i\cdot \int_{\gamma_j}\, dg\quad\colon\, g\in \mathcal E(X)
 \]
 More generally, since
 $d$-closed 1-forms in the chart $U_j$ are $d$-exact the re4ader should check that
 (F.5) implies that
 \[
 \phi_j^{-1}\cdot d\phi_j<\alpha>=2\pi i\cdot \int_{\gamma_j}\,\alpha\tag{F.6}
 \]
 hold for every $d$-closed differential 1-form $\alpha$.
 Let us now consider the function
 \[
 \Phi= \prod_{j=1}^{j=N}\, \phi_j
 \]
 \medskip
 
 \noindent
 {\bf{F.7 Exercise.}}
 From the above the
 reader should check  that
 the construction of the $\phi$-functions imply that
 $\Phi$ is a zero-free
 $C^\infty$-function
 in $X\setminus \{q_j,p_j\}$, i.e. in the open complement of
 the finite set
  which is the union of these   $q$  and  $p$ points.
Moreover,  additivity for logarithmic derivatives and 
(F.6) above gives
\[
\Phi^{-1}\cdot d\Phi<\alpha>=
\int_\Gamma\, \alpha\tag{F.7.1}
\]
for every $d$-closed 1-form
$\alpha$. Finally, show that
\[
\Phi^{-1}\cdot \bar\partial(\Phi)=
\sum\, a_j^{-1}\cdot \bar\partial(a_j)\tag{F.7.2}
\]
where the right hand side is a smooth $(0,1)$-form.
\medskip

\noindent
{\bf{F.8 A special case.}}
Suppose that $\Gamma$ is such that
\[
\int_\Gamma\, \omega=0\quad\colon\quad \omega\in\Omega(X)\tag{F.8.1}
\]
The equality in (F.7.1) applied to  $d$-closed holomorphic 1-forms
and
Theorem ¤ xx  entail  that
the smooth $(0,1)$-form
$\Phi^{-1}\cdot \bar\partial(\Phi)$ from (F.7.2) is $\bar\partial$-exact.
Thus, we can find $G\in \mathcal E(X)$ such that
\[
\bar\partial(G)= \Phi^{-1}\cdot \bar\partial(\Phi)\tag{F.8.2}
\]
\medskip


\noindent
{\bf{Exercise.}}
Put
\[
\Psi=e^{-G}\cdot \Phi
\]
deduce from the above  that
$\bar\partial(\Psi)=0$ holds in
$X\setminus \{q_j,p_j\}$ and hence $\Psi$ is holomorphic in
this open subset of $X$
Show also  that the local constructions of the
$\phi$-functions inside the charts
$\{U_jz_j\}$ entail  that
$\psi$ extends to a mermorphic function in
$X$ whose princial divisor is equal to
\[
\sum\, \delta(q_j)-\sum \delta(p_j)
\]
Funally the reader should confirm that the constructions above
prove the "if part" in Theorem F.2.
\medskip


\centerline{\emph{F.9 Proof of the "only if part"}}
\medskip

\noindent 
Here we are given a non-constant meromorphic funvtion
$f$.
We shall condtruct an integration chain $\Gamma$ as follows:
Frst $f\colon X\to {\bf{P}}^1$ is a holomorphic map.
With $s=f(x)$
we recall from (xx) that the number critical $s$-points in
the complex $s$-plane is finite.
In ${bf[P})^1$ we choose a simple
curve $\gamma_*$ with intial point at $s=0$ and end-point at
$s=|nfty$, while
$\gamma_*$ avoids the critical points $s\neq 0$ in
${\bf{C}}$.
of course, while this is done we can choose
$\gamma_*$ so that it is a smooth curve
on the $C^\infty$-manifold ${\bf{P}}^1$.
\medskip

\noindent
{\bf{The inverse image $f^{-1}(\gamma_*)$.}}
Let $N=\deg(f)$.
Since $\gamma_*$ avoids $f$-cirtical points we see that
\[
f^{-1}(\gamma_*\setminus \{0,\infty\})= \gamma_1\cup\ldots\cup\,\gamma_N
\]
where $\{\gamma_j\}$ are disjoint  curves in
$X$, each of which is oriented via
$\gamma_*$ which from the start moves from
$s=0$ to $s=\infty$.
\medskip

\noindent
{\bf{Exercise.}}
Show that the closure $\bar\gamma_j$ yields a rectifiable  curve
whose initial point is zero of $f$ and the end-point a pole.
Put
\[
\Gamma=\sum\, \bar\gamma_j
\]
and conclude from the above that
$\Gamma$ is associated to the principal divisor of $f$.
The proof of the "onmy if part" is therefore finished if we show that
\[
\int_\Gamma\,\omega=0\quad\colon\quad \omega\in \Omega(X)\tag{*}
\]
To prove (*) we shall  use
a certain trace map.
First, a holomorphic 1-form
$\omega$ on $X$ is regared as a $\bar\partial$-closed current with
bi-degree $(0,1)$.
Since the amp $f\colon X\to {\bf{P}}^1$ is proper
there exists the direct image current
$f_*(\Omega$ and we recal from general facts that
the passage to direct image currents commute with
the $\bar\partial$-operator.
hence $\bar\partial(f_*(\Omega))==$ and since
$\bar\partial$ is elliptic it follows that
$f_*(\omega)$ is a holomorphic 1-form on
${\bf{P}}^1$.
By the result in Exercise xx there does not exist non-zero globally defined
holomorphic 1-forms on the projective line.
hence
\[ 
f_*(\omega)=0\tag{**}
\]
In partocuar we have
\[
\int_{\gamma_*(\epsilon)}\, f_*(\omega)=0
\]
where $\gamma_*(\epsilon)$ is the closed 
curve given by $\gamma$ intersected with
$\{\epsilon\leq |s| \leq \epsilon^{-1}\}$
for a small $\epsilon>0$.
\medskip

\noindent
{\bf{Exercise.}}
Put $\Gamma(\epsilon)= f^{-1}(\gamma(\epsilon)$
and dediuce from (xx) that
\[
\int_{\Gamma(\epsilon)}\, \omega=0
\]
Finally, pass to the limit as $\epsilon\to 0$ and conclude that (*) holds which finishes the proof of
the "only if part".



 


\centerline{\bf{Holomorphic differential operators}}


\bigskip


\noindent
With $\partial=\partial/\partial z$
a holomorphic differential operator
$Q$ defined in a connected open subset of
${\bf{C}}$ can be written in a unique way as
\[
Q(z,\partial)= \sum_{\nu=0}^{\nu=k}\, q_\nu(z)\cdot \partial^\nu\tag{*}
\]
where $\{q_\nu(z)\}$ are holomorphic functions in
$\Omega$.
The largest integer $k$ for which $q_k\neq 0$ is called the order
of the differential operator $Q$, and the set of
all holomorphic differential operators in $\Omega$ is denoted by
$\mathcal D(\Omega)$.
A basic result  in analytic $\mathcal D$-module theory
is the following:

\medskip

\noindent
{\bf{1. Theorem.}}
\emph{Let $\Omega$ be a connected open set
in the complex $z$-plane which contains the origin
and let $f_1,\ldots,f_k$ be ${\bf{C}}$-linearly independent  in
the complex vector space $\mathcal O(\Omega)$.
Then there exists $Q\in\mathcal D(\Omega)$ of order $k$
such that}
\[
Q(f_\nu)=0\quad\colon\quad 1\leq \nu\leq k\tag{1.1}
\]
\emph{Moreover, we can always choose $Q$ as in (*) where
the holomrphic $q$-functions have no common zero in
$\Omega$, and 
when $Q_1$ and $Q_2$ are two such differential operators 
which both satisfy (1.1) we have}
\[
Q_2= \phi(z)\cdot Q_1
\]
\emph{where $\phi$ is a zero-free holomorphic function in
$\Omega$.}
\medskip

\noindent
{\bf{Remark.}}
When $Q=\sum\, q_\nu(z)\cdot \partial^\nu$ satisfies
(1.1)  and the $q$-functions have no common zeros, the
uniquenss in the theorem entails that
the zero divisor of $q_k(z)$ 
is uniquely determined. In the special case when
$q_k(z)$ only has a finite number of zeros, we find a
\emph{unique} $Q$ satisfying (1.1)  of the form
\[
Q(z,\partial)= \sum_{\nu=0}^{\nu=k-1}\, q_\nu(z)\cdot \partial^m\nu+
q_m(z)\cdot \partial^m
\]
where $q_m(z)$ is a monic polynomial
\[
q_m(z)=\rho\, (z-z_\nu)^{\mu_\nu}
\]
Here  $\{z-\nu\}$ is a finite set of points in
$\Omega$ snd $\{\mu_\nu\}$ are positive integers, while
eventual common zeors of $q_0,\ldots,q_{k-1}\}$
do not contain the zeros of $q_m(z)$.
In $\mathcal D$-module theory one  refers to this unique differential
operator as the minimal annihilator of the $k$-tuple 
$\{f_\nu\}$  in $\mathcal O(\Omega)$.
One has also a duality whch means that
if $g\in\mathcal O(\Omega$ satisfies 
$Q(g)=0$,  then $g$ belongs to the $k$-dimensionsl 
vector space generated by $f_1,\ldots,f_k$.
\medskip


\noindent
A proof of this result  appears in chapter 1 from 
my book \emph{Analytic $\mathcal D$-modules.}
Via analyticity it suffices to prove a local version where one regards
the local ring
$\mathcal O={\bf{C}}\{z\}$ of germs of holomorphic functions
at the origin.
If $f_1,\ldots,f_k$ sre ${\bf{C}}$-linearly independent, the local version
of the theorem above assert that there exists a unique 
differential operator
\[
Q()z,\partial)= z^m\partial^k+\sum\,
\]
where $m\geq 0$ snd $\{q_\nu(z)\}$
is a $k$-tupe in $\mathcal O$ such thst
$q_\nu(0)\neq 0$ hold for at least some
$0\leq\nu\leq k-1$.
An example where $m\geq 1$ already occurs with $k=1$. Namely, let 
$f_1(z)= z^2$. Now the attached
minimal $Q$-operator is
given by
\[
z\partial-\frac{1}{2}
\]
A special family of local minimal $Q$-operators 
appears when the leading $q$-function $q_k(z)$ 
satisfies $q_k(0)\neq 0$.
Namely,let $k\geq 1$ and consider a differential operator
\[
Q(z,\partial)= \partial^k+ 
\]
where $\{q_\nu\}$ is an arbitrary $k$-tuple in
$\mathcal O$.
Cauch'ys classic result for analytic ODE:s
asserts that
the $Q$-kernel on $\mathcal O$ is
$k$-dimensional. Moreover, we csn choose
soluyions $f-1,\ldots,f_k$ whose derivatives at the origin satisfy
\[
\partial^\nu(f_j= \text{Kronecker's delta}\quad\colon
0\leq j,\nu\leq k-1
\]
\medskip

\noindent
The case when $q_k(0)=$ leads to a more involved analysis which
was carried out by Fuchs and Picard around 1880.
To begin with, if $Q$ is the minimal  operstor to some
$k$-dimensional subspace of $\mathcal O$, then
it turns out that $m\leq k$ and we can write
\[
z^{k-m}\cdot Q(z,\partial)=
\nabla^m+\sum\, p_\nu(z)\cdot \nabla^\nu
\]
where $\nabla=z\partial$ is called the  Fuchsian operator.
One refers to the right hand side as a Fuchsian operstor of
order $k$.
The $p$-functions are not arbitrary if
the $Q$-kernel on $\mathcal O$ is $k$-dimensional
To see this we notice thsa if $j$ is a positive integer then
\[
Q(z^j)= (j^m+p_{m-1}(0)j^{m-1}+\cdots+p_0(0)\cdot z^j+
z^{j+1}\cdot \phi_j(z)
\]
where $\phi_j(z)\in \mathcal O$.
Using this one can prove that
the $Q$-kernel on $\mathcal O$ is $k$-dimensional if and only if
the zeros of the polynomial
\[
\rho_Q(\lambda)= \lambda^m+\sum\, p_\nu(0)\cdot \lambda^\nu
\]
consists of a $k$-tuple of distinct non-negstive integers.
\medskip


\noindent
{\bf{An example.}}
Consider the differential operator
\[
Q=z\partial^2 +\partial
\implies z\cdot Q= z^2\partial^2+\nabla= \nabla^2
\]
So here $\rho_Q(\lambda)= \lambda^2$ which has a double zero
at $\lambda=0$.
The constant function $f(z)=1$ is a solution to
$Q(f)=$ and generates the 1-dimensional $Q$-kernel on
$\mathcal O$.
Outside the origin  the multi-valued function
$\log z$ satisfies
\[ 
(z\partial^2+\partial)(\log z)=
z\partial(1/z)+1/z=0
\]
In gneral Fuchs studied arbitrary
differentisl operators expressed via the right hand side in
(xx). When the $p$-functions are holomorphic in some disc
$\{|z|<\delta\}$, we can regard the action by $Q$ on
germs of holomorphic functions at points in the punctured disc
$\dot D=\{0<|z|<\delta\}$.
Cauchy's  theorem applies and gives a $k$-dimensional $Q$-kernel
in $\mathcal O(z_0)$ for every $z_0\in \dot D$.
A major result due to Fuchs is that these
locally  defined germs in the punctured disc are local branches of
multi-valued analytic functions of a special form.
Let us explain this in more detail.
                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                      
                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                      
                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                      
                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                      
                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                      


 
\newpage




\centerline{\bf{Analytic function theory.}}

\bigskip

\noindent
The Cauchy-Riemann equations in
${\bf{C}}$ are expressed by
\[
u_x= v_y\quad\&\quad u_y=-v_x\tag{0.1}
\]
for a pair of real-valued functions $u(x,y)$ snd $v(x,y)$, and (0.1)
means
that the complex-valued function $f(z)= u(x,y)+iv(x,y)$
is holomorphic.
More generally one can consider
elliptic first  order systems. With
$n\geq 2$ one seeks an
$n$-tuple of real-valued functions $u_1,\ldots,u_n$
which satisfy the system
\[
\frac{\partial u_p}{\partial x}+ \sum_{q=1}^{q=n}\,
A_{p,q}(x,y)\cdot \frac{\partial u_q}{\partial q}+
\sum_{q=1}^{q=n}\,B_{p,q}(x,y)\cdot\, u_q=0\quad\colon\quad 1\leq p\leq n
\tag{*}
\]
where $\{A_{p,q}\}$
and $\{B_{p,q}\}$
are real-valued functions of $(x,y)$ which  give elements 
in $n\times$-matrices  $\mathcal A(x,y)$ and
$\mathcal B(x,y)$. 
The system is called elliptic  if the determinant  polynomial 
\[
\lambda\mapsto \det(\mathcal A(x,y)-\lambda\cdot E_n)
\]
has no real roots for every point $(x,y)$.
Notice  that $n=2m$
must be an even integer when the system is elliptic.
Such general elliptic systems will
not be treated here.
Let us only remark that 
a deep 
result was proved by  Carleman  in 1937
which yields a uniquness theorem for solutions  to
the elliptic system above. More precisely, he  proved
that a $u$-solution to (*) where 
$y\mapsto u_k(0,y)=0$
hold for every $k$. must vanish identically in
a an open neighborhood of
the line 
$\{x=0\}$.
The  non-trivial fact is that
this uniqueness holds under the sole condition that
the
$A$-function are of class $C^2$ and the $B$-functions are continuous.
Prior to Carleman's work, the uniqueness was proved  by 
Erik Holmgren  when the $A$- and the $B$-functions are
real-analytic. Holmgren's proof from
an  article published in 1901 by
the Royal Scademy of Sweden is very elegant and
and offers
an instructive lesson for readers who enter studies of
PDE-equations, and 
Carleman's proof of
uniqueness in the non-analytic case
gives a new perspective upon the Cauchy-Riemann equations
and has 
inspired more recent more recent work devoted to  linear elliptic PDE-systems
in a wider context which foremost has been put forward by 
Lars Hšrmander.



\medskip


\noindent
The subsequent material deals foremost with
analysis on compact Riemann surfacas
and expose clasic facts 
due to Abel and Riemann. More recent 
work by  Weierstrass, PoincarŽ. Koebe and
Weyl give  certain simplifications of the original discoveries 
by Abel and Riemann.
We shall work in the complex $z$-plane and write
$z=x+iy$ which identifies 
the complex $z$-plane with
${\bf{R}}^2$.
Now
\[
z^{-1}=\frac{1}{x+iy}\tag{i}
\]
is locally integrable with respect to  planar Lebesgue measure.
Let us  compute  some   distribution derivatives 
of (i). 
Consider the first order differential operator
\[
\bar\partial=\frac{1}{2}\cdot (\partial_x+i\partial_y)
\]
With these notations one has the equality
\[
\bar\partial(z^{-1})= \pi\cdot \delta_0\tag{*}
\]
where $\delta_0$ is the Dirac  measure at the origin.
To prove (*) we consider for each
$\epsilon>0$ the $C^\infty$-function
\[
f_\epsilon(z)= \frac{\bar z}{|z|^2+\epsilon}
\]
The reader can  check that
\[
\bar\partial(f_\epsilon)(z)= \frac{\epsilon}{(|z|^2+\epsilon)^2}
\]
The function in the right hand side tends to zero
outside the origin as $\epsilon\to 0$.
At the same time
\[
\iint\, f_\epsilon(z)\, dxdy=\epsilon\cdot 2\pi\cdot \int_0^\infty\,
\frac{rdr}{(r^2+\epsilon)^2}=\pi
\]
and now the reader can check the equation 
(*).
\medskip

\noindent
{\bf{Pompieu's formula.}}
Let $f(x,y)$ be a test-function in ${\bf{R}}^2$.
There exists the convolution
\[
\phi(z)= \iint\, f(\zeta)\cdot \frac{1}{\zeta-z}\, d\xi d\eta\tag{i}
\]
where we have put
$\zeta=\xi+i\eta$.
Notice that the double integral is equal to
\[
\iint\, f(\zeta+z)\cdot \frac{1}{\zeta}\, d\xi d\eta\tag{ii}
\]
From this we see thst
$\phi$ is a $C^\infty$-function and  the reader can check that 
\[
\bar\partial(\phi)(z)=
\iint\, \bar\partial(f)(\zeta)\cdot \frac{1}{\zeta-z}\, d\xi d\eta\tag{ii}
\]
At the same time, using (*) and (i) the reader can check that
\[
\bar\partial(\phi)(z)=-\pi\cdot f(z)\tag{iii}
\]
Hence we obtain the formula
\[
f(z)=\frac{1}{\pi}\cdot 
\iint\, \bar\partial(f)(\zeta)\cdot \frac{1}{z-\zeta}\, d\xi d\eta\tag{iv}
\]
Next, in the complex $\zeta$-plane one has
the differential 1-forms
\[
d\zeta=d\xi+id\eta\quad\&\quad 
d\bar \zeta=d\xi-id\eta
\]
From this the reader can conclude that
\[
-2i\cdot d\xi d\eta= d\zeta\wedge d\bar\zeta
\]
Since $i^2=-1$ it follows that 
(iv) gives
\[
f(z)=\frac{1}{2\pi i}\cdot 
\iint\, \bar\partial(f)(\zeta)\cdot \frac{1}{z-\zeta}\, d\zeta\wedge d\bar\zeta\tag{**}
\]
Notice also that (iv)  can be expressed by the equation
\[
f=\frac{1}{\pi}\cdot \bar\partial(z^{-1}*f)\tag{***}
\]
where * denoted the convolution of functions in
${\bf{R}}^2$.
This means that the  $\bar\partial$-equation
\[
\bar\partial(u)=f
\]
has a solution $u$ for every test-function $f$ obtained from 
the  formula in (***).
\bigskip


\noindent
{\bf{1.  A passage to distributions.}}
Let $\mu$ be a diistribution
with compact support. 
Then there
exists a distribution $\gamma$ such that
\[
\bar\partial(\gamma)=\mu
\]
To prove this we shall define
$z^{-1}*\mu$.
Since $\mu$ in general is a sum of distribution derivatives of
measures, it is not obvious how to
construct this convolution.
However, it is schieved via the Fourier transform.
Namely, let $\widehat{\mu}$ be the Fourier transofrm of
$\mu$, i.e. it is for every $(\xi,\eta)$ found by evaluating 
$\mu$ on the $C^\infty$-function
\[
(x,y)\mapsto e^{-i(x\xi+y\eta)}
\]
When $\mu$ has compact support we know  that
$\widehat{\mu}$ is a real-analytic function on
the $(\xi,\eta)$-space.
So  in this space there exists
the locally integrable function
\[
\frac{\widehat{\mu}}{\xi+i\eta}\tag{i}
\]
Fourier's inversion formula for tempered distributions
implies  that
(i) is the Fourier transform of a tempered distribution
$\rho$ in the $(x,y)$-space.
Rules for the Fourier transform  give 
\[
\widehat{\bar\partial(\rho)}=
\frac{i}{2}\cdot (\xi+i\eta)\cdot \widehat{\rho}=
\frac{i}{2}\cdot \widehat{\mu}
\]

So 
\[
\gamma=\frac{2}{i}\cdot \rho
\implies \bar\partial(\gamma)= \mu\tag{1.1}
\]
\medskip

\noindent
{\bf{1.2 A convolution formula.}}
Consider the distribution.
$z^{-1}$. It is tempered and has therefore a Fourier transform.
It turns out that there exists as constant $c_0$ such that
\[
\widehat{z^{-1}}= c_0\cdot \frac{1}{\xi+i\eta}\tag{i}
\]
To prove (i)  we use that the product 
\[
\frac{i}{2}\cdot (\xi+i\eta)\cdot 
\widehat{z^{-1}}
\]
is equal to the Fourier transform of
$\bar\partial(z^{-1})$.
Next, since 
the Fouier transform of the Dirac distribution
$\delta_0$ is the identity function in
the $(\xi,\eta)$-space, it follows from (*) above
that (i) holds with
\[
c_0=\frac{2\pi}{i}
\]

\medskip

\noindent
{\bf{Exercise.}} Use the results above to
extend Pompieu's formula to distributions with
a compact support,  i.e. one has
\[
\mu=\frac{1}{\pi}\cdot z^{-1}*\bar\partial(\mu)
\]
\medskip

\noindent
{\bf{The elliptic property of $\bar\partial$.}}
In general, let $\mu$ be a distribution with
a compact support $K$ and consider the distribution
\[
\gamma = z^{-1}*\mu
\]
If $z$ is outside $K$, then
\[
\zeta\mapsto \frac{1}{z-\zeta}
\]
restricts to a $C^\infty-$function on $K$ 
and we can evaluate $\mu$ on this funtion.
The construction of the convolution gives
\[
\gamma(z)=\mu<\frac{1}{z-\zeta}>
\]
In the special case when
$\mu$ has order zero, i.e. given by
a measure with compact support one has
\[
\gamma(z)=\int\,\frac{d\mu(\zeta)}{z-\zeta}
\]
and it is clear  that the right hand side is a holomorphic
function of $z$ outside $K$.
In general 
$\mu$ is expressed as a finite sum of
derivatives of mesures supported by $K$ 
Suppose for example that
$\mu=\partial_x(\rho)$ where
$\rho$ is a measure with compact support confined to $K$.
In this case the construction of distribution derivatives give
\[
\gamma(z)=\int\,\frac{d\rho(\zeta)}{(z-\zeta)^2}
\]
From this we see that
$\gamma$ again is holomorphic outside $K$ and
in general we conclude that 
(xx) gives a holomorphic $\gamma$-function in the open complement of
$K$. Thus, a distribution $\mu$ which satisfies
$\bar\partial(\mu)=0$ in an open set is
"truly holomorphic".


\newpage





\centerline{\bf{Analysis on a compact Riemann surface.}}

\bigskip


\noindent
Let $X$ be a compact Riemann surface.
Regarding its   underlying structure as a real manifold
we  introduce certain $\mathcal E$-spaces. By
$\mathcal E(X)$ we denote  the space of complex-valued $C^\infty$-functions and
$\mathcal E^1(X)$ the space of differential 1-forms
woth
$C^\infty$-coefficients,
If $(U,z)$ is an analytic  chart  in
$X$ and $w\in \mathcal E^1(X)$, its restriction to
$U$ is  expressed by
a sum:
\[
w|U= f\cdot dz+g\cdot d\bar z\quad\colon\quad f,g\in C^\infty(U)
\]
In this way $w$ is a sum of two 
globally defined differential 1-forms
denoted by
$w^{1,0}$ and $w^{0,1}$, and in a chart as above
\[
w^{1,0}|U= f\cdot dz\quad\&\quad w^{0,1}=
g\cdot d\bar z
\]
It means that there is a decomposition
\[
\mathcal E^1(X)= \mathcal E^{1,0}(X)\oplus\mathcal E^{0,1}(X)
\]
We refer to
$\mathcal E^{1,0}$ as the space of differential 1-forms of bi-degree
$(1,0)$, and 
$\mathcal E^{0,1}$ is  the space of differential 1-forms of bi-degree
$(0,1)$, 
When $f\in \mathcal E(X)$ its usual exterior differential $df$
is dcomposed as a sum
\[
df=\partial f+\bar\partial f
\]
Here $\partial f$ is of bi-degree $(1,0)$ whose  restriction to a chart
becomes
\[
\partial f|U= \partial(f)\cdot dz
\]
where  $\partial(f)$
is the $C^\infty$-function 
\[
\partial(f)=\frac{1}{2}(f'_x-if'_y)
\]
The $(0,1)$-form
$\bar\partial f$ is found in a similar fashion.
We have also the space $\mathcal E^2(X)$ of differential
2-forms, and  the exterior differential map:
\[
d\colon  \mathcal E^1(X)\to \mathcal E^2(X)
\]
\medskip

\noindent
{\bf{1. Some cohomology spaces.}}
We can cover $X$ by s finite family of charts
$\{U_\alpha,z_\alpha)\}$.
By a zero-cochain we mean a family of complex numbers
$\{c_\alpha\}$ assigned to the open sets  $\{U_\alpha\}$.
This is a complex vector space  denoted by
$C^0(\mathfrak{U})$ whose dimension is the number of
charts in the covering.
A 1-cochain assigns complex numbers
$c_{\alpha,\beta}$ to pairs when $U_\alpha\cap U_\beta\neq \emptyset$
which is 
alternating, i.e. 
\[
c_{\beta,\alpha}= c_{\alpha,\beta}
\]
Each zero-cochain $\{c_\alpha\}$
gives the 1-cochain
\[
\delta(\{c_\alpha\})= \{c_\alpha-c_\beta\}
\]
Next, a 1-cochain is $\delta$-closed if
\[
c_{\alpha,\beta}+ c_{\beta,\gamma}+ c_{\gamma,\alpha}=0
\]
for every triple where $U_\alpha\cap U_\beta\cap U_\gamma\neq \emptyset$.
The set of $\delta$-closed 1-cochains is denoted by
$Z^1(\mathfrak{U})$.
It is clear thst
the $\delta$-image of zero-cochains yield  $\delta$-closed
1-cochains. Hence there exists the quotient space
\[
H^1(\mathfrak{U})=\frac{Z^1(\mathfrak{U})}{
\delta C^0(\mathfrak{U})}\tag{1.1}
\]
Next, we have  the quotient  space
of $d$-closed modulu $d$-exact differential 1-forms.
It turns out that there is an  isomorphism:
\[
H^1(\mathfrak{U})\simeq 
\frac{\mathcal E^1_{cl}(X)}{d\mathcal E(X)}\tag{*}
\]
To prove (*)  we  
choose a $C^\infty$-partition of the unity, i.e. 
a family
$\{\phi_\alpha\in C_0^\infty(U_\alpha)\}$
such that
$\sum\, \phi_\alpha=1$ on $X$.
Consider a 
$\delta$-closed 1-cochain  $\{c_{\alpha,\beta}\}$.
To each fixed $\alpha$ we put
\[
h_\alpha= \sum\, c_{\alpha,\beta}\cdot \phi_\beta
\]
In a non-empty intersection $U_\alpha\cap  U_\gamma$
we have 
\[
(h_\alpha-h_\gamma)|U_\alpha\cap U_\gamma=
\sum\, (c_{\alpha,\beta}-c_{\gamma,\beta})\phi_\beta=
c_{\alpha,\gamma}\cdot 
\sum \phi_\beta= c_{\alpha,\gamma}
\]
The right hand side are  a constants  and hence the differentials
$dh_\alpha$ snd $dh_\gamma$ are equal on
the intersection $U_\alpha\cap U_\gamma$. This gives
a globslly defined 1-form
$w$ such that
\[ 
w|U_\alpha=dh_\alpha
\]
hold for every chart in the covering
$\mathfrak{U}$.
Since $d^2=0$ the 1-form
$w$ is $d$-closed.
Hence we have constructed a map
\[
\rho\colon\, Z^1(\mathfrak{U})\to \mathcal E^1_{cl}(X)\tag{i}
\]
It turns out that (i) is surjective.
For let $w$ be a $d$-closed 1-form.
In every chart it is $d$-exst, i.e. we find
$h_\alpha\in C^\infty(U_\alpha)$ and
\[
w|U_\alpha=dh_\alpha
\]
Now
\[
\{c_{\alpha,\beta}= h_\alpha-h_\beta|U_\alpha\cap U_\beta\}
\in Z^1(\mathfrak{U})
\]
is a $\delta$-closed 1-cochiasn and 
the reader can check that its
its $\rho$-image 
is equal to $w$.
Next, suppose thst
$\{c_\alpha-c_\beta\}$ is a $\delta$-exact 1-cochain.
Now
\[
h_\alpha= \sum\, (c_\alpha-c_\beta)\cdot \phi_\beta
=c_\alpha-\sum\, \phi_\beta\cdot c_\beta
\]
It follows that
\[
dh_\alpha||U_\alpha=d(\sum\, c_\beta\cdot \phi_\beta)
\]
The right hand side is the $d$-image of the globally defined
$C^\infty$-function $\Phi= \sum\,c_\beta\cdot \phi_\beta$
and we get
\[
\rho(\{c_\alpha-c\beta\})= d(\Phi)
\]
 Hence  (i) induces a  map
 \[
 \bar\rho\colon\, H^1(\mathfrak{U})\to \frac{\mathcal E^1_{cl}(X)}{d\mathcal E(X)}
 \]
 From the surjectivity of $\rho$
 it follows that $\bar\rho$  is
 surjective, and we leave as an exercise to
 check that it  also is injective which proves
 the requested isomorphism in (*). Notice that this
 implies that
 $H^1(\mathfrak{U})$ is independent of the chosen covering 
 of $X$ by charts.
 This intrinsically defined complex vector space is
 denoted by $H^1(X)$ and called the cohomology 
 space over $X$ in
in degree one.
In the literature one refers to (*) as the
Dolbeault isomorphism.
\medskip


\noindent
{\bf{2. Holomorphic 1-forms.}}
They consist of differential forms of bi-degree (0,1) which 
are $\bar\partial$-closed. This
space  is denoted by $\Omega(X)$.
If $\omega$ is a holomorphic 1-form  and
$(U;z)$ a chart in $X$ we have
\[
\omega|U= f(z)dz
\]
where $\bar\partial(\omega)=0$ entails  that $f$ is holomorphic in
$U$.
Notice that every holomorphic 1-form is
$d$-closed, i.e. one has the inclusion
\[
\Omega(X)\subset \mathcal E^1_{cl}(X)
\]
Next, we show that
a holomorphic 1-fiorm
$\omega$ cannot be  $d$-exact so that (i) yields an injective map
\[
\Omega(X)\to \frac{\mathcal E^1_{cl}(X)}{d\mathcal E(X)}\tag{i}
\]
To see this we suppose that 
\[
\omega= dg
\] 
for some $g\in\mathcal E(X)$.  Since $\omega$ has bi-degree
$(1,0)$ this gives
the equality
\[
\omega=\partial g\implies
0=\bar\partial\omega= \bar\partial\partial  g
\]
As explained in ¤ xx this means that
$g$ is a harmonic function in every chart $U_\alpha$
and by the maximum principle for 
iharmonic functions it follows from the compactness of $X$ that
$g$ is a compact and hence $w=0$.
This proves that  the map
(i) is injective.
\medskip


\noindent
We can also  consider $\partial$-closed $(0,1)$-forms.
This family is denoted by $\overline{\Omega(X)}$.
If $\gamma$ is such a form its restriction to a chart becomes
\[
\gamma= g(z)\cdot d\bar z\quad\colon\quad
\partial(g)=0
\]
The last equation means that $g$ is the complex conjugate of a
holomorphic function in the chart.
Exactly as above one prove that there is sn injective map
\[
\overline{\Omega(X)}\to \frac{\mathcal E^1_{cl}(X)}{d\mathcal E(X)}
\]
\medskip

\noindent
{\bf{2.1 Exercise.}} Shiow that one also has an injective map
\[
\Omega(X)\oplus\, \overline{\Omega(X)}\to \frac{\mathcal E^1_{cl}(X)}{d\mathcal E(X)}
\]
whuch amounts  to check that a 1-form
\[
w= \omega+\gamma
\]
with $\Omega\in \Omega(X)$ and 
$\gamma\in \overline{\Omega(X)}$
cannot be $d$-exact, unless $\omega=\gamma=0$.







\medskip



\noindent
{\bf{3. Riemann's decomposition theorem.}}
It  turns out that the injective map from (2.1)   is
surjective, i,e. 
one has a direct sum:
\[
\mathcal E^1_{cl}()=d\mathcal E(X)\oplus\Omega(X)\oplus \overline{\Omega(X)}\tag{3.1}
\]
To prove (3.1) we proceed as follows.
First we have  the map
\[
w\mapsto w^{0,1}
\] 
from $\mathcal E_{cl}^1(X)$ into $\mathcal E^{0,1}(X)$.
Passing to a quotient we get a map
\[
 \rho\colon\, \mathcal E^1_{cl}(D)\to
\frac{\mathcal E^{0,1}}{\bar\partial \mathcal E(X)}
\]
Let us determine the $\rho$-kernel.
So let $w$ be a $d$-closed 1-form and suppose thst
$w^{0,1}$ is $\bar\partial$-exact:
\[
w^{0,1}=\bar\partial g\implies
w-dg=  w^{1,0}-\partial g
\]
Since $d(w-dg)=0$ we see that
the (1,0)-form
$w^{1,0}-\partial g$ is $\bar\partial$-closed and hence 
a holomorphic 1-form $\omega$,  and from the above
\[
w= dg+\omega
\]
Conversely the reader can check that
$d\mathcal E(X)\oplus\Omega(X)$
belongs to the $\rho$-kernel.
\medskip

\noindent
{\bf{3.2 Exercise.}} Deduce from the above that there is a left
exact sequence
\[
0\to\Omega(X)\to 
\frac{\mathcal E^1_{cl}(X)}{d\mathcal E(X)}
\to \frac{\mathcal E^{0,1}(X)}{\bar\partial \mathcal E(X)}
\]
and conclude  the inequality
\[
\dim\, \frac{\mathcal E^1_{cl}(X)}{d\mathcal E(X)}
\leq \dim\,\Omega(X)+\dim\,
\frac{\mathcal E^{0,1}(X)}{\bar\partial \mathcal E(X)}\tag{i}
\]
At the same time Exercise (2.1) gives the inequality
\[
2\cdot \dim\,\Omega(X)\leq
\dim\, \frac{\mathcal E^1_{cl}(X)}{d\mathcal E(X)}\tag{ii}
\]
where we  used the obvious equslity
$\dim\,\Omega(X)=\dim\overline{\Omega(X)}$.
\medskip


\noindent
From the above we see that  (3.1)
follows if we
have proved the equality
\[
\dim\,\Omega(X)=\dim\,
\frac{\mathcal E^{0,1}(X)}{\bar\partial \mathcal E(X)}\tag{3.2.1}
\]
\medskip

\noindent
{\bf{3.3 A duality formula.}}
To get (3.2.1) we  regard the dual space of
$\frac{\mathcal E^{0,1}(X)}{\bar\partial \mathcal E(X)}$.
Recall  that
$\mathcal E^{0,1}(X)$ is a Frechet space whose dual
${\bf{c}}^{1,0}(X)$ consist of currents of bi-degree (0,1).
Moreover, $\bar\partial \mathcal E(X)$ is a closed subspace of
$\mathcal E^{0,1}(X)$. The construction of
$\bar\partial$ on currents gives
\[
[\,\frac{\mathcal E^{0,1}(X)}{\bar\partial \mathcal E(X)}]^*=
\text{Ker}_{\bar\partial}({\bf{c}}^{1,0}(X))
\]
At this stage we use that
$\bar\partial$ is elliptic and by the result in
(xx) applied to charts the reader should confirm that
the equality
\[
\text{Ker}_{\bar\partial}({\bf{c}}^{1,0}(X))=\Omega(X)
\]
Hence we have  the duality formula:
\[
\Omega(X)\simeq 
[\,\frac{\mathcal E^{0,1}(X)}{\bar\partial \mathcal E(X)}]^*
\]
which gives  (3.2.1) and finishes the proof
of Riemann's decomposition theorem.









 




\bigskip


\noindent
{\bf{4. The cohomology space $H^1(\mathfrak{U},\mathcal O)$.}}
By $C^1(\mathfrak{U},\mathcal O)$ we denote the space of
families $\{g_{\alpha,\beta}\}$
where $g_{\alpha,\beta}\in \mathcal O(U_\alpha\cap U_\beta)$, and this doubly indexed family is alternating.
Exactly as before  we choose  a partition of the uniity by
$\phi$-functions,  and for each $\alpha$ we put
\[
h_\alpha= \sum\, g_{\alpha,\beta}\cdot \phi_\beta
\]
Now we construict the (0,1)-forms
$\bar\partial(h_\alpha$. Since the holomorphic
$g$-functions are annhilated by
$\bar\partial$ we get
\[
\bar\partial(h_\alpha)=
\sum\, g_{\alpha,\beta}\cdot \bar\partial(\phi_\beta)
\]
In each  non-empty intersection the reader
can check that
these  forms are matching and hence
there exists a globally defined
$(0,1)$-form $w$ with
\[
w|U_\alpha= \bar\partial(h_\alpha)
\]
So we have constructed a map
\[
\rho\colon\, Z^1(\mathfrak{U},\mathcal O)\to \mathcal E^{0,1}(X)\tag{4.1}
\]
It  turns out that $\rho$ is surjective.
For let $w$ be a globally defined $(1,0)$-form.
Pompieu's result applied to charts gives
for each $U_\alpha$ some funtion $f_\alpha$ so that
\[
w|U_\alpha= \bar\partial(f_\alpha)
\]
Then 
$\{f_\alpha-f_\beta\}$ yields a holomorphic 1-cocycle
whose  $\rho$-image is $w$.
Next, consider some
$\delta$-exact 1-cochain $\{g_\alpha-g_\beta\}$.
Now
the $h$-funtions above become
\[
h_\alpha= \sum\, (g_\alpha-g_\beta)\cdot \phi_\beta=
g_\alpha-\sum\, g_\beta\cdot \phi_\beta
\]
Since the $g$-functions are holomorphic we get
\[
\bar\partial(h_\alpha)= 
\sum\, g_\beta\cdot \bar\partial(\phi_\beta)
\]
whivh holds for every $\alpha$, while the right hand side is a globally
defined $(0,1)$-form. We conclude that 
the $\rho$-image of a $\delta$-exact 1-cochain is
$\bar\partial$-exact. Hence there exists an induced map
\[
\bar\rho\colon\, \frac{
 Z^1(\mathfrak{U},\mathcal O)}{\delta(C^0(\mathfrak{U},\mathcal O)}
 \to \frac{\mathcal E^{0,1}(X)}{\bar\partial \mathcal E(X)}\tag{4.2}
 \]
 We leave to the reader to check that this
 map is bijective. Hence there exists an isomorphism
 \[
 H^1(\mathfrak{U},\mathcal O)\simeq
 \frac{\mathcal E^{0,1}(X)}{\bar\partial \mathcal E(X)}\tag{4.3}
\] 
 
 
\bigskip
 
\noindent
{\bf{5. Passage to currents.}}
We have the map
$\bar\partial \colon {\bf{c}}(X)\to 
{\bf{c}}^{0,1}(X)$
and  shall prove that
\[
 H^1(\mathfrak{U},\mathcal O)\simeq
 \frac{{\bf{c}}^{0,1}(X)}{\bar{\bf{c}} (X)}\tag{5.1}
\] 
To get  (5.1)  we consider a (0,1)-current
$\gamma$. Pompieu's theorem for distributions applied to
charts gives for every
$U_\alpha$ some $\mu_\alpha\in {\bf{c}}(U_\alpha)$
such that
\[
\gamma|U_\alpha= \bar\partial(\mu_\alpha)
\]
Since $\bar\partial$ is elliptic it follows that
\[
\mu_\alpha-\mu_\beta|U_\alpha\cap U_\beta\in \mathcal O(
U_\alpha\cap U_\beta)
\]
and now $\{\mu_\alpha-\mu_\beta\}$ is a $\delta$-closed
1-cochain, which has an  image
in
$H^1(\mathfrak{U},\mathcal O)$.
Exactly as in ¤ 4 the reader can check that we get an
injective map
\[
\frac{{\bf{c}}^{0,1}}{\bar\partial {\bf{c}}(X)}\to
H^1(\mathfrak{U},\mathcal O)
\tag{5.1}
\]
Finally, the inclusion
$\mathcal E^{0,1}(X)\subset {\bf{c}}^{0,1}(X)$
and (4.3) entail that (5.1) is surjective. Hence 
\[
 H^1(\mathfrak{U},\mathcal O)\simeq
\frac{{\bf{c}}^{0,1}(X)}{\bar\partial {\bf{c}}(X)}\tag{5.2}
\]


\bigskip


\noindent
{\bf{6. Exercises.}}
Deduce from (4.3( and (5.1) that
\[
{\bf{c}}^{0,1}(X)=\mathcal E^{0,1}(X)+\bar\partial {\bf{c}}(X)
\] 
Thus, up to a $\bar\partial$-exact (0,1)-image, every
(0,1)-current coincides with a smooth (0,1)-current.
Moreover, the dulity from ¤ 3 extends and gives
\[
\Omega(X)=[\frac{{\bf{c}}^{0,1}}{\bar\partial {\bf{c}}(X)}]^*
\]
It can be expressed by saying that
a $(o,1)$-current $\gamma$ is $\bar\partial$-exact if and only if
its evaluation on holomorphic 1-forms is zero.




\newpage


\centerline{\bf{Meromorphic functions.}}
\bigskip


\noindent
Let $X$ be a compact Riemann surface of some genus $g\geq 1$.
For each point $p\in X$ we denote by
$\mathcal M_p(X)$ the space of meromorphic functions on
$X$ whose polar set is reduced to the single point
$p$.
It turns out that $\mathcal M_p(X)$ contains  non-constant
functions, and  we shall prove that
there exists $f\in\mathcal M_p(X)$
with a pole at $p$ of order $g+1$ at most.
To prove this we
shall consider $(0,1)$-currents supported by $\{p\}$.
Choose a chart $(U,z)$ around $p$ where $p$
corresponds to the origin in the $z$-disc $U$.
If $\Phi\in \mathcal E^{1,0}(X)$ we can consider 
its restriction to $U$ and get
\[
\Phi|U= \phi(z)\cdot dz\quad\colon\, \phi\in C^\infty(U)
\]
We can evaluate  $\phi$ at $z=0$ which gives a (1,0)-current
on $X$ denoted by $\rho_p$ defined by
\[
\rho_p(\Phi)= \phi(0)
\]
We can also regard derivstives of $\phi$ which for  each positive  integer
$k$ gives  a current $\rho_p^{(k)}$ defined by
\[
\rho_p^{(k)}(\Phi)=\partial^k\phi/\partial \bar z^k(0)
\]
Now $\{\rho_p^{(k)}\colon\, 0\leq k\leq g\}$
are $g+1$ many (0,1)-currents.
By Exercise  6  the quotient space
\[
\frac{{\bf{c}}^{0,1}(X)}{\bar\partial {\bf{c}}(X)}
\] 
is $g$-dimensionsl.
Hence there exists a $(g+1)$-tuple of complex numbers
such that the current
\[
\gamma=c_0\cdot \rho_p^{(0)}+\dots+c_g\cdot \rho_p^{(g)}
\]
is $\bar\partial$-exact, i.e 
we find a distribution $\mu$ on $X$ so that
\[
\bar\partial(\mu)= \gamma
\]
Since $\gamma=0$ in $X\setminus \{p\}$ and the
$\bar\partial$-operator is ellitpic, it follows that
$\mu|X\setminus \{p\}= f$ for some
holomorphic function $f$ in the open set
$X\setminus\{p\}$.
Working in the chart $U$ local residue formulas
entail  that $f$ extends to a globally defined meromorphic
function, i.e. it belongs to
$\mathcal M_p(X)$, and gives the
$(0,1)$-current 
\[
\bar\partial f=\gamma
\]
Moreover, lcoal residue calculus inside  the chart $U$
together with the expression of $\gamma$ above, imply that
the pole of $f$ at $p$ has order $g+1$ at most.
\medskip


\noindent
{\bf{Weierstrass' points.}}
The question arises if $\mathcal M_p(X)$
contains a non-constant meromorphic function
$f$ with a pole of order $\leq g$ at $p$.
To decide when such a meromorphic function exists
we proceed as follows.
From the above, if
a non-constant  funtion $f$ exists in
$\mathcal M_p(X)$ with a pole fo some order
$m\leq g$ at $p$, then the $(0,1)$-current
\[
\bar\partial(f)=c_0\cdot \rho_p^{(0)}+\dots+c_m\cdot \rho_p^{(m)}
\]
for some constants $\{c_\nu\}$.
So if the $g$-tuple of currents
$\{rho_p^{(k)}\,\colon 0\leq k\leq g-1\}$
are ${\bf{C}}$-linearly independent in the
$g$-dimensional quotient space from Exercise 6, then
no  $f$ as above exists.
\medskip

\noindent
A point $p\in X$ is called a Weierstrass point if
$\mathcal M_p(X)$ contains a non-constant meromorphic function with
a pole of order $\leq g$ at $p$.
Let $\mathcal W(X)$ denote this set. We shall prove
that it is a finite subset of $X$.
To achieve this we choose a basis
$\omega_1,\ldots,\omega_p$ in the $g$-dimensional vector space
$\Omega(X)$. 
Given a point $p\in X$ we choose a chart $(U,z)$
around $p$ and  get 
\[
\omega_\nu= g_\nu(z)\cdot dz
\]
where $\{g_\nu(z)\}$ sre holomorphic functions in
$U$.
Now we get the $g\times g$-matrix $A(z)$ with elements
\[
a_{k\nu}(z)= \partial^{k-1(}g_\nu)(z)
\quad\colon 1\leq k,\nu\leq g
\]
\medskip

\noindent
From Exercise 6 the reader can check that
$p$ is a Weiertrass point if and only if
\[
\det A(z)=0
\]
It turnd out thst
the set of Weierstrass points is a non-empty finite set in
$X$ as so0n as the genus is $\geq 2$.






\newpage





\centerline{\bf{Hšrmander's  $L^2$-estimate
in dimension one }}

\bigskip

\noindent
Theorem 1  below will
not be covered during my lecture 
devoted to Riemann surfaces. It  has been
inserted together with a detailed proof 
to illustrate the  flavour of some of the subsequent  seminars.
Those who 
appreciate Lsrs Hšrmander's theorem
 below may find the seminars devoted to pluricomplex analysis interesting,
while those who prefer to contemplae upon 
more abstract 
theories and algebra whree no hard analysis appears
might hesitate to attend the them..
\medskip

\noindent
Hšrmander's proof below
teaches an  instructive lesson.
Here is the situation:
Let $\Omega$ be an open  set in  ${\bf{C}}$.
A real-valued continuous and non-negative function 
$\phi$ on $\Omega$ gives
the Hilbert space 
$\mathcal H_\phi$
whose elements are complex-valued Lebesgue measurable functions $f$ in $\Omega$ such that
\[ 
\int_\Omega\, |f|^2\cdot e^{-\phi}\, dxdy<\infty\tag{1}
\]
The square root  yields norm   denoted by
$||f||_{\phi}$. Let $\psi$ be another
continuous and non-negative function 
which gives the Hilbert space 
$\mathcal H_\psi $ where the norm of an element $g$ is denoted by $||g||_{\psi}$.
We  consider the
$\bar\partial$-operator
which sends
a function $f\in \mathcal H_\phi$  to
$\bar\partial(f)=df/d \bar z$
and study the
equation
\[
\bar\partial(f)= g\quad\colon g\in H_\psi\tag{2}
\]
One  seeks  conditions for  the pair $(\phi,\psi)$ in order
that there exists a constant  $C$ such that
(2) has a solution $f$ for every $g$ where
\[
 ||f||_\phi\leq C\cdot ||g||_\psi\tag{3}
\]
Notice that  (2) does not have a unique solution since
$f$ can be replaced by $f+a(z)$ where $a$ is a holomorphic function
which belongs to
$\mathcal H_\phi$.
For example, non-uniquneness fails when
$\Omega$ is a bounded open set
and the function $e^{-\phi}$ is bounded in
$\Omega$. For then $f$ can be replaced by $f+p$ for
an arbitrary
polynomial $p(z)$.
We shall find a sufficient condition
in order that (2-3) above hold.
\medskip

\noindent
{\bf{4. Hšrmander's condition.}}
The pair  $\phi,\psi$ satisfies the Hšrmander condition if 
$\psi$ is a $C^2$-function and $\phi$ is at least a $C^1$-function,
and there  exists a
positive constant $c_0$ such that the following pointwise inequality holds in
$\Omega$:
\[ 
\Delta(\psi)\vvv 2\cdot |\nabla(\psi)|^2+
\psi\uuu x\phi\uuu x+\psi\uuu y\phi\uuu y\geq
2\cdot c_0^2\cdot e^{\psi(z)-\phi(z)}
\tag{4.0}
\]
where we have put $|\nabla(\psi)|^2=\psi\uuu x^2+\psi\uuu y^2$.
\medskip


\noindent
{\bf{4.1 Theorem.}}
\emph{If the pair $(\phi,\psi)$ satisfies (4.0) 
the equation
$\bar\partial(f)=g$ has a solution for every $g\in\mathcal H_\psi$ where}
\[
||f||_\phi\leq \frac{1}{c_0}\cdot ||q||_\psi
\]


\noindent
Before  the proof starts we recall
some facts sbout linear operators between
Hilbert spaces.
In general, let $\mathcal H_0$ and $\mathcal H_1$ be a pair of complex Hilbert spaces
and $T\colon\mathcal H_0\to \mathcal H_1$ is a densely defined linear operator.
Following Torsten Carlemsn's famous monograph about unbounded
operators on Hilbert spaces 
published by  Uppsala university in 1923, 
we recall the construction of an adjoint.
Namely, a  vector $y\in\mathcal H_1$ belongs to the domain 
of definition for the adjoint
operator $T^*$ if and only if there exists a constant $C$ such that
\[
\bigl|\langle Tx,y\rangle_1\bigr|\leq C\cdot |x|_o\quad\colon x\in\mathcal D(T)\tag{i}
\]
where $|x_|$ is the norm of the vector $x$ taken in
$\mathcal H_0$, 
and in the left hand side
we  considered the hermitiain inner product on
$\mathcal H_1$.
Since $\mathcal D(T)$ is dense and Hilbert spaces are self-dual, each
$y$ for which (i) holds yields a unique vector
$T^*(y)\in\mathcal H_0$ such that
\[
\langle Tx,y\rangle_1=\langle x,T^*y\rangle_0\tag{ii}
\]
In general $\mathcal D(T^*)$ is not a dense subspace of
$\mathcal H_1$. But let us add this as an hypothesis on $T$.
Moreover,  assume that the two densely defined operators
$T$ and $T^*$ both are closed, i.e. their graphs are
closed in the product of the two Hilbert spaces.
\medskip

\noindent
{\bf{Exercise.}}
Suppose as above that both
$T$ and $T^*$ are closed with dense domains of definition.
Assume in addition that there exists a positive constant $c$ such that
\[
|T^*y|_0\geq |y|_1\quad\colon\quad y\in \mathcal D(T^*)
\]
Show that this implies that the range
$T^*(\mathcal D(T^*))$ is
a closed subspace of $\mathcal H_0$ which is equal
to the orthogonal complement of
the nullspace $\text{Ker}(T)$
Moreover, show that for
each $y\in\mathcal H_1$
we can find
$x\in\mathcal D(T)$ such that
\[
Tx=y\quad\&\quad  |x|_0\leq c^{-1}\cdot |y|_1
\] 
\bigskip






\centerline{\bf{Proof of Theorem 4.2}}
\medskip


\noindent
Since $C_0^\infty(\Omega)$ is a dense subspace of $\mathcal H_\phi $
the linear operator $T\colon f\mapsto \bar\partial(f)$ 
from $\mathcal H_\phi$ to $\mathcal H_\psi$  is densely defined
and we leave as an exercise to the reader to check that
$T$ also is closed, i.e. this relies on a genrral fact about closedness
of operators defined by differential operators.
The reader may also check that Stokes Teorem entails that
test-functions in $\Omega$ belong to
$\mathcal D(T^*)$ and since
$C_0^\infty(\Omega)$ is dense in
the Hilbert space $\mathcal H_\psi$ the adjoint is also densely defined.
Let us then consider some
$g\in\mathcal D(T^*)$. For each $f\in C_0^\infty(\Omega)$
Stokes theorem gives
\[ 
\langle T(f),g\rangle=\int \bar\partial(f)\cdot \bar g\cdot e^{-\psi}\,dxdy=
-\int\, f\cdot 
\bigl[\bar\partial(\bar g)-\bar g\cdot \bar\partial(\psi)\bigr]\cdot
 e^{-\psi}\,dxdy\tag{i}
\]


\noindent
Since $\psi$ is real\vvv valued, 
$\bar\partial(\bar w)-\bar w\cdot \bar\partial(\psi)$
is equal to the complex conjugate of
$\partial(w)-w\cdot\partial(\psi)$. We conclude that (i) gives
\[
T^*(g)=-\bigl[\partial(g)-g\cdot\partial(\psi)\bigr]\cdot
 e^{\phi-\psi}\tag{ii}
\]
In particular $T^*$ is defined via a differential operator and has therefore
a closed graph.
Taking the squared $L^2$-norm in $\mathcal H_\phi$
we obtain
\[ 
||T^*(g)||^2_\phi=
\int\, |\partial(g)-g\cdot\partial(\psi)|^2\cdot
e^{\phi-2\psi}=
\]
\[
\int\, \bigl(|\partial(g)|^2+|g|^2\cdot|\partial(\psi)|^2\bigr)\cdot
e^{\phi-2\psi}-2\cdot\mathfrak{Re}\bigl (
\int\, \partial(g)\cdot\bar g\cdot\bar \partial(\psi)\cdot
e^{\phi-2\psi}\bigr)\tag{iii}
\]
By partial integration
the last integral in (iii) is equal to
\[
2\cdot\mathfrak{Re}\bigl(\,  \int\,g\cdot[\partial(\bar w)\cdot\bar \partial(\psi)+
\bar g\cdot \partial\bar\partial(\psi)-
2\bar w\cdot \bar \partial(\psi)\cdot \partial (\psi)+
\bar g\cdot \bar\partial(\psi)\cdot \partial(\phi)]\cdot e^{\phi-2\psi}\,\bigr)\tag{iv}
\]


\noindent
Next, the Cauchy-Schwarz inequality gives
\[
\bigl|2\cdot 
\int \, g\cdot  \partial(\bar g)\cdot \bar \partial(\psi)\cdot e^{\phi-2\psi}\,\bigr|\leq
\int\, \bigl(|\partial(g)|^2+|g|^2\cdot|\partial(\psi)|^2\bigr)\cdot
e^{\phi-2\psi}\tag{v}
\] 
Together (iii-v) give
\[
||T^*(g)||^2_\phi\geq 
2\cdot \mathfrak{Re}\,  \int\, |g|^2\cdot \bigl[\,\partial\bar\partial(\psi)\vvv
2\cdot \bar \partial(\psi)\cdot \partial (\psi)+
\bar\partial(\psi)\cdot \partial(\phi)\,\bigr ]\cdot e^{\phi-2\psi}=
\]
\[
2\cdot \mathfrak{Re}\,  \int\, |g|^2\cdot
\frac{1}{4}\bigl[\Delta(\psi)-2\cdot |\nabla(\psi)|^2+
\psi_x\phi\uuu x+\psi_y\phi_y\,\bigr]\, \cdot e^{\phi-2\psi}
\tag{vi}
\]
where the last equality follows since
$\phi$ and $\psi$ are real-valued.
Funally, since (4.1) is assumed
it follows that
\[
||T^*(g)||^2_\phi\geq c_0^2\cdot \int\, |g|^2\cdot
e^{\psi-\phi}\cdot e^{\phi-2\psi}=
c\uuu 0^2\cdot ||g||^2\uuu\psi\tag{vi}
\]
Now we aŒply the Exercise  above
and
get 
Theorem 4.2.
\medskip

\noindent
{\bf{Remark.}}
Let  $\Omega$ be  an open subset of a disc $\{|z|<r\}$ for somne $r<1$
which is centered at the origin.
We  find 
a pair
with $\phi=\psi$ satisfying (4.1) 
by:
\[
\phi(z)= \log\,( |z|^2+1)= \log\, (x^2+y^2+1)
\]
For then we see that
\[
\Delta(\psi)=\frac{4}{(x^2+y^2+1)^2}
\]
At the same time
\[
\psi_x^2+\psi_y^2= \frac{4x^2+4y^2}{(x^2+y^2+1)^2}
\]
The reader can check that one gets a constant $c_0$ so that Hšrmander's condition (4.1) holds.

\medskip

\noindent
{\bf{Final remsrk.}}
The full strength of  $L^2$-estimates
appears in dimension $n\geq 2$ where one works with
\emph{plurisubharmonic functions}  and 
impose the condition that $\Omega$ is a
strictly pesudo-convex set in ${\bf{C}}^n$ and
solve inhomogeneous $\bar\partial$-equations for 
differential forms of bi-degree $(p,q)$. 
We refer to 
Chapter 4 in Hšrmander's  cited 
text-book for details.


\newpage




\centerline{\bf{Pluricomplex analysis}}


\bigskip

\noindent
The seminars 
continue throughout the academic yesr 2011-12.
Focus is upon complex analysis of one and several variables.
They will  take place every second week, except for the first two 
lectures below.
Here are titles of these   two lectures 
with  J-E Bjšrk as  speaker.

\medskip


\noindent
{\bf{1. November 21: Riemann surfaces.}}
\medskip


\noindent
{\bf{2. November 28: Volumes and limits of analytic sets
in ${\bf{C}}^n$.}}

\medskip

\noindent
{\bf{Time and place.}}
Each lecture takes place on a Tuesday $15^{30}-17^{30}$
at room 304  in House 6 at the department  of mathematics at SU.



\newpage



\medskip

\noindent
{\bf{Remarks about the lectures.}}
Distributions, and more generally currents
play a central role during the whole analysis.
From a historic point of view
the study of Riemann surfaces,  i.e. 1-dimensional complex manifolds
has paved the way  towards  many areas
in mathematics,  such as
cohomology of sheaves and 
the determination  of cohomology on manifolds via
the de Rham complex of smooth differential forms. For example, 
duality in the sense of PoincarŽ is 
best expressed  via the de Rham complex  of
currents.
The study  of Riemann surfaces,  i.e. 
1-dimensional  complex manifolds offer
instructive lessons about  currents on
$C^\infty$-manifolds of arbitrary dimension, and the aim of
Lecure 1 is to expose
how the sydtemstic use of
currents  on a Riemann surface  - compact or non-compact -
enabe us to establish many remarkable results.
Among these we mention the Behnke-Sdtrin theorrmn whivassertd thst thr inhomogrnouus $\bar\partial$-equstion is sovsbe on
onevety non-compsvt Riesnn surface, the fsmoud reut due to Abelwhigves as necesssry nd sufficient conditio
for the podtion of es snd xerod of s meromprphic funvtion on
a compsvt riemsnn surface.








Basic facts  from calculus, foremost in dimension two
will
be used without hesitation.
Let me recall  some results expressed via
currents
We work in the complex $z$-plane with $z=x+iy$.
Consider a closed and dimle curve
$\gamma$ with vontonous tangent   i.e. a closed Jordan curve of class $C^1$. It  borders  a bounded
domain  $U$ and we recall that $\gamma$ is oriented in
a natural way vis the rule of the thumb.
If $w=A\cdot dx+B\cdot dy$
is a differential 1-form, where $A(x,y)$ andÊ$B(x,y)$ in general are
complex-vslued $C^\infty$.funvtions, we obtain
a current of degree 1 via the linear functional
\[
w\mapsto \int_\gamma\, w
\]
One refers to this as the integration current
attached to the oriented curve
$\gamma$.
Stokes theorem gives the equality
\[
\iint_U\, dw=\int_\gamma\, w
\]
It means that the distribution defined 
by the characteristic function
$\chi_U$
has a differentisl whivh is  equal to the integration current, i.e.
in the space ${\bf{c}}^1$ of current of degree one, we have
the equslity
\[
d\chi_U= \int_\gamma\tag{*}
\]
This is a convenient  way to express Stokes theorem
and we shall  learn that similar  formulas extend to
manifolds.
\medskip

\noindent
Next, in analytic function theory
the fsmous residue formula due to
Cauchy can be expressed and later on extended to
a formula related to currents.
Consider the function $z^{-1}$ which  is
meromorphic with a simple pole at the origin
If $f(x,y)$ is a complex-valued $C^\infty$-function
a Taylor expansion of $f$ at the origin gives  \[
f(0)= \frac{1}{2\pi i}\cdot 
\lim_{\epsilon\to 0}\, \int_{|z|=\epsilon}\,
\frac{f(z)}{z}\, dz
\]
This local  residue 
formula leads  to
an equality expressed via currents,
Namely, first $z^{-1}$ 
is a locally integrable function in
the $(x,y)$.space 
and gived therefore a distirbution.
By definition
$\mathfrak{Db}({\bf{C}})$
is the dual of test-form of maximal degree 2.
Thus space to be denoted by
$\mathcal E^2({\bf{C}})$
consists  of differential  2-forms
\[
\psi(x,y)\cdot dx\wedge dy
\]
where $\psi$ is a complex-valued
$C^\infty$-function with compact support.
Now $z^{-1}$ is the distribution degined by
\[
\psi\cdot dx\wedge dy\mapsto \iint\,
\frac{\psi(x,y)}{x+iy}\ dxdy
\]
Recall   that we can construct derivatives of
distributions.
In particular  we 
regard the first order differential operator
\[
\bar\partial=\frac{1}{2}\cdot (\partial_x+i\cdot \partial_y)
\]
Now there exists the 1-current
$\bar\partial(z^{-1})$ which
by defintion is a linear functional on test-forms
of degreee one, defined by
\[
\bar\partial(z^{-1})<w>=
-\iint\, \frac{\bar\partial(w)}{z}
\]
In the right hand side we have constructed
the differrential  2-form
$\bar\partial(w)$.
Te 1-form  $w= A\cdot dx+B\cdot dy$ and we
shall express it using the 1-forms $dz$ and $d\bar z$. By definition
\[
dz=dx+idy\quad\&\quad
d\bar z=dx-idy
\]
It follows thst
\[
A\cdot dx+B\cdot dy=\frac{1}{2}[
A\cdot (dz+d\bar z)-i\cdot B\cdot (dz-d\bar z)]=
\frac{1}{2}[(A-iB)\cdot dz+(A+iB)\cdot d\bar z]
\]
So in this way every differential 1-form can be expressed
via the 1-forms $dz$ and $d\bar z$, i.e. an arbitrary
1-form $w$ csn be expressed as
\[
w= A\cdot dz+B\cdot d\bar z
\]
where $A,B$ is a pair of $C^\infty$-functions.
Now the $\bar\partial$-operator  from
1-forms into 2-forms becomes
\[
\bar\partial(w)= \bar\partial(A)\cdot d\bar z\wedge dz
\]
where $dz\wedge d\bar z$
is the 2-form given by
\[
dz\wedge  d\bar z=-2i\cdot dx\wedge dy
\]
\medskip

\noindent
{\bf{Remark.}}
Denote by $\mathcal E^1$ the space of differential 1-forms in the complex 
$z$-plane.
From the aboce  one has a direct dum decompositon 
\[
\mathcal E^1=
\mathcal E^{1,0}\oplus
\mathcal E^{0,1}\quad\colon\quad
\mathcal E^{1,0}= \mathcal E\cdot dz
\,\&\, 
\mathcal E^{0,1}= \mathcal E\cdot d\bar z
\]
where $\mathcal E$ denotes complex valued $C^\infty$-functions.
With these notyions the exterior differntisl of a 1-fotm
$w$ can be found as follows:
First we decompose
$w$ as
\[
w=w^{1,0}+w^{0.1}
\]
and then
\[
dw= \bar\partial (w^{1.0})+ \partial (w^{0,1}
\]
Above we therefore find the exterior differentials 
\[
\bar\partial\colon\, \mathcal E^{1,0}\to \mathcal E^2
\]

























In both lectures attention is given
to the notion of currents on a complex analytic manifold
where  ¤ 1 treats the 1-dimensional case.
So several classic results,  such as Abel's theorrn which gives
a
necessary and sufficient condition for the positions of
poles and zeros of a non-constant  meromorphic function on a compact
Riemann surface.
Baisc fvts from anakytic funvtion theory in
dimension one eill
be used eithout hesitstion,and
in addition the resder dhould be
fsmlisir eith
basic didtributyion throty whivh for exsmple is covered
in chsoter 1-3 in Lars HšrmsnderŠs tect-book
on linesr psrtisl differentisl equstions.
Cincering the importstn  interplsy between
anslytic funvtyion theory in one complex vsrisbles snd
the sdydtesmtic ude of didtributions and currents the
bedt dource is chapter 2 in Hšrmander's fsmous text book
devoted to
seversl complex variables.
Aosrt from these sotces, I will also deliver dome
note
for the first lecture.
The sevnod lecture trestd geomrtric poperties of
complex analytic sets  in
${\bf{C}}^n$ when $n\geq 2$.
With $z=(z_1,\ldots,z_n)$ as coorfinstes
one introduced the KŠhler fotm
\[
\mathcal K= dz-1\wedge d\bar z-1+
\]
If $V\subset {\bf{C}}^n$  is an anslytic dubdet of dome pure diumendion
$1\leq k\leq n-1$
one knows thst the drt of regulsr pointd on $V$ is
a dense open subdt of $V$ snd conditutes a locsly closed
embedded
complex suybmsnifold of dimendion $k$.
lecture 1 weill
for exsmple discuss volumed of suvh srts.
Fir exsmple, if $R>0$ we can cpomute
\[
\text{Vol}_{2k}(\cap \{|z|>R\})
\] 
for every $R>0$ where $\{|z|<R\}$ id thr open bsll of rsfius $R$.
It turnd out thst thid volume is finite snd
is ewuasl to
\[
xxx\dot \int_{\text{reg}(V)\cap \{|z|<R\}}\, \mathcal K^k
\]
where we hsbe tsken the $k$-fold exterior product of the
KŠhler form whguivh yied a differentisl form of bidgree $(k,k)$ ehivh csn be integrted on
thr oritnerts manifold
$\text{reg}(V)$ whose resl fimendion is $2k$.










  $X$ will illustrste the udefulenss ofcurrents,.
On $X$ one encounters spaces such as $\mathcal E^{1,0}(X)$ and
$\mathcal E^{0,1}(X)$ of differential forms of bi-degree $(1,0)$ 
and $(0,1)$ respectively.
Both are nsturslly ewuipped eith s struvute as Frechet spaced.
The dusl spsces consisdtd of currrnts, i.e. we put
\[
\mathcal E^{1,0}(X)^*= {\bf{c}}^{1,0}(X)
\]
Moreover, the usual exterior differential $d$ from
$C^\infty$-functiond to differrntisl 1-fporms
csn be devpmosoed as $d=\partial+\bar|psrtisl $ ehrre
\[
\partial\colon C^\infty(X)\to 
\]
One has also the space of ero-ducrentd, i.e.
the spce of didtributiond on $X$ 
to be denoted by $\mathfrak{Db}(X)$.
Diring the lecture I will
exlsts  that
(*) extend to maps
\[
xxxx
\]
A crucuasl fsct is thst
$\bar\partial l$ is sn ellitic operator which 
and durting the lectyure I wiull
exlsin thst thid gived
ewuskities suvh as
\[
{\bf{c}}^{1,0}(X)=
xxx
\]
















\newpage

\centerline{\bf{About Lecture 1}}.

\bigskip

\noindent
Notes will
supplement Lecture 1 where classic facts
about Riemann surfaces are exposed.
Distributions, and more generally currents play  a central  role during the whole 
analysis.

 
 
On a Riemann surface, i.e. a 1-dimensional complex manifold,
the $\bar\partial$-operator 
maps $C^\infty$-functions  on $X$ to  
the space $\mathcal E^{0,1}(X)$
of differential forms with 
bi-degree (0,1).
Using complex analytic charts the
analysis relies upon basic results  
in the complex $z$-plane
${\bf{C}}$.
Consider for exsmple the funvtion
$z^{-1}$ ehivh i ocslly integrsble in
the real $(x,y)$-plsne where we write $z0x+iy$.
it defines s didtribution svtinig on test-funvtions
$g(x,y9$ by
\[
g\mapsto \iint \frac{g(x,y)}{x+iy}\, dxdy
\]
Now the exidt the didtribution derivdtives
of thid distribution. In psrtiaslr wee grt the didtribuyion
\[
\bar\partial(z^{-1})
\frac{1}{2}(\partial_x+i\partial_y)(z^{-1})
\]
It turnf out thst it is eual to $\pi\cdot \delta_0$ wehrre
$\delta_0$ id the dursc mesdure st the origin.
To prove this one csn use thst
\[
\lim_{\epsilon\to 0}\, \frac{\bar z}{|z|^2+\epsilon}= z^{-1}
\]
where thr limit holdd in the ususl wesk topology for distributions.
With $\epsilon>0$ the reader can check that
\[
\bar\partial(\frac{\bar z}{|z|^2+\epsilon}=
\frac{1}{|z|^2+\epsilon}-\frac{\bar z\cdot z }{((|z|^2+\epsilon)^2}=
=\frac{\epsilon}{(|z|^2+\epsilon)^2 2}
\]
The last positive function 
tends to zero outside the origin and we notice that
\[
\iint\,=\frac{\epsilon}{(|z|^2+\epsilon)^2 2}\, dxdy=
2\pi\cdot \int_0^\infty
\frac{\epsilon\cdot r }{(r^2+\epsilon)^2 2}\, dr=\pi
\]
After a passsge to thr omiit we get the equality
\[
\bar\partial(z^{-1})= \pi\cdot \delta_0
\]
\medskip


\noindent
{\bf{Another example.}}
Line integrals sre bet understood vis currents.
Consider for exsmple a psth $\gamma$ in th vompŒlex plsne
whivh srises vis c vomplex-vslued snbd vontonoud msp
\[
t\mapsto \gamma(t)\quad 0\leq t\leq 1
\]
Under the asumption thst this function is of class $C1$ we obtain s current of degree 
one. Namely, let $w=A\cdot dx+B\cdot fy$
be a tedt-form of dgree one, i.e. here $A(x,y)$ snd $B(x,y)$
sre test-functions.
With
\[
\gamma(t)= x(t)+y(t)
\]
One has
\[
\int_\gamma\ w= \int_0^1\, A(\gamma(t))\cdot x'(t)\, dt+
\int_0^1\, B(\gamma(t))\cdot y'(t)\, dt
\]
This yields a conttnuous linesr funvionsl on ther spsce of
tedt-fotmd of degrre one whch by defintion corredpoondd to
a 1-cyrrrnt. <it id denotedf by $\int_\gamma$ snd csllef the
intgrstion currrnt assocsitd tothr prrted psth $\gamma$. A
fiunddmetnsl fsvt id tht thid currrnt doed not depenf upon thr vhodrn 
psrsmetrisstion, i.e. by dfraeing an oreotned psth
weith vontonoud tdngrntd one assocsits s unioweue currrent.
Suppose thst th origin snd a point $z_0|nrw 0$ sre the end-piintd of
$\gamma$. if $w=dg$ id the ecterior differrntisl of s tst-funvtion
the resder vsn check thst
\[
\int_\gamma\, dg=g(z_0)-g(0)
\]
Now we csn condtruvt snother 1-currrnt
whivh tsked the ssme vslues on $d$-exsct 1-forms.
Nsmely, we can choose a $C^\infty$-funvtion
$a$ such that
\[
\phi(z)= a(z)\cdot \frac{z}{z-z_0}
\]
is identicslly one in an ecterior disc
$|z|>E$ weirth $R>|z_0|$
and $a(z)\ne 0$ for sll $z$.
The con dtruvtion of suvh sn $a$-funvtion is left to the resder.
Tsking distribution derivatives we get the 1-current
$d\phi$ which becomes
\[
\frac{z}{z-z_0}\cdot da+
\frac{a}{z-z-0}\cdot dz-\frac{za}{(z-z_0^2)}\cdot dz
\]
It follows that
\[
\phi^{-1}\cdot d\phi= \frac{da}{a}
+\frac{dz}{z}-\frac{dz}{z-z_0}
\]
Above $\frac{da}{a}$ is  $d$-closed, asnd uding (xx) the resder dhould verify thdt
the 1-current
$phi^{-1}\cdot d\phi$ satisfies
\[
phi^{-1}\cdot d\phi<dg>= 2\i i\cdot (g(09-g8z_0)
\]
for every testfuncion $g$.
Next, we recsl thdt rvery $d$-closed differneital 1-fotm is
$d$-exact, It gollows from the sbove thst
\[
phi^{-1}\cdot d\phi<w>=-2\i i\dot \int_\gamma \, w
\]
for evety $d$-closed 1-form.
This locsl contuction eill
be used durting the asnslyis on Riemsnn surfaces.
A cruvsi point id that the currrnt of bi-degree $(0.1)$ definef by
\[
phi^{-1}\cdot \bar\partial \phi=
a^{-1}\cdot \bar\partial a
\]
where the right hsnd side is a smooth current since
$a$ is a zero-free $C^\infty$--function.
Fir exsmple, the condtruvtion dbove is used to prove a fdmous theorrm dur to Abrl whivh
guves a necessry ssnd dufficirbt condition 
when a psir of $n$-tupled of poiints $q_1,\ldots,q_N$ and
$p_1,\ldots,p_N$ give sinple xeros, respevtivrly fimple poked of
a globdlly dgined neromotphic funvyion on s compsvt Riemsnn surfscr.
So for thr beuibnner it is esdentisl to grsps snslytic funvyion yhroty in
thr vomplex plsne via sn intersvtion eith resl anslydis snd
the dudtmstic use of  distributions and currents.
An exsmple isd the classic fornus due to Pompieu from 2810
whivh goes as follows:
lrt $\Omega$ be a bounded snd coinnected domdin
in ${\bf{C}}$ whod nounddry is the diodjoint union of s finite drt of closded
Jordsb curves, whivh all sre of class $C^1$.
Givrn s piint $z_0\in \Omega$ snd
a complex-vslued $C^1$-funvtion $f$ efined in
soimr oprn nrighborhood of $\overline{\Omega}$
one has
\[
f(z_0)=\frac{1}{2\pi i}\cdot  \int_{\partial\Omega}\, \frac{fz)\, dz}{z-z_0}+
+ \frac{1}{2\pi i}\cdot  \iint_\Omega\,
\frac{\bar\partial(f(z)}{z-z_0}\, d\bar z\wedge\,dz
\]
To prove this one regards thr differential 1-fotm
\[
w=\frac{f(z)}{z-z_0}\, dz
\]
in a punctured fomdin
$\Omega\setminus \{|z-z_0|\leq \epsilon\}$.
The exterior differential of $w$ becomes
\[
dw=\frac{\bar\partial(f(z)}{z-z_0}\, d\bar z\wedge\,dz
\]
and via Stoeks theorrm and a passsgr to thr limit as
$\epsilon\to 0$ the reader cdn vonfitm Pompieu's fornula.
As we sjal see lster on (*) is a veritable cornerdtond
during the analysis on Riemann surfaces.














A major result due to Behnke and Stein asserts that if
'$X$ is   non-compact then the
map
\[
\bar\partial\colon  C^\infty(X) \to
\mathcal E^{0.1}(X)\tag{*}
\]
is surjective.
The planar  case when
$X$ is sn open subset of ${\bf{C}}$ is  proved in 
chapter 1 from Lars Hšrmander's text-book devoted to
several complex variables.i.e. here the proof
uses elementary analytic function theory of one
complex analysis.
The general case in the Behnke-Stein Theorem is
requires a more involved proof where an essentis, ingredient is to
employ \emph{currrents}.
So a majort theme during the lefture is to
dedrbie how cslculus based upon currents  is used to
establish  results about  Riemann surfaces, both compact and non-compact.
Let jus remsrk thst the Behnke-Strin theorrm uields a
quick proof of the \emph{uniformisation theorem}  which
aserts that vrty open and simply connected Riemann 
surface is either biholomorphic with
the open unit disc or the complex plsne.
This result  was orignallly established
by Koebe in 1905, while the
contemporary  proof using currents becomes
rather strsightforward using a clever device
introduced by Malgrange after the original  proof by
Behnke and Strein  from 1948.
Since Malgrsnge's method iullustrate the uefulness of
currents we
describe his proof.
Let $X$ as above be a non-compact Riemann surface
and  $Y$ is  a relatively compact  open subset , i.e. $Y$ is open and
the closure is a compact set in $X$.
Consider also  a compact subset $K$ of $Y$
with the property that every  connected open component of
$X\setminus K$ is non-compact. We remark that
one then refers to $K$ as a compact Runge set.
Now there exists the spscve $\mathcal O(K)$
of germs of holomorphic functions  on $K$.
With these notations one proves thst
esvh $f\in\mathcal O(K)$ csn be uniformly approximated on $K$
by holomiorohiuc funvtiond on $Y$, i.e. there exidts
a sewuence $\{g_n\in\mathcal O(Y)\}$ such thdt
\[
\lim_{n\to \infty}\, ||g_n-f||_K=0
\]
To prove this approximation 
one proceeds as follows: Firrst one shows thst
the vompsctned of $\overline{Y}$ entails that
when $w\in \mathcal E^{0,1}(X)$ is a globally defined 
smooth $(0,1)$-form, then
there exits $g\in C^\infty(Y)$ suvh thst
\[
w|Y=\bar\partial(g)
\]
Since funviond in $Y$ whuvh sre dnnihllsted by
$\bar\partial$ srr jolomotphic, the $g$-funvtion is
unwiue up to adding $\mathcal O(Y)$-funvtions.
Suppoe now thst $\mu$ is a mesdure on $K$ suvh thst
\[
\int\, g\cdot d\mu=0\quad\colon\quad g\in \mathcal O(Y)
\]
Then there exidts s current $S$ of bi-degree $(1,0)$ defined by
\[
S(w)=\int\, g\cdot d\mu
\]
with $g$ chosen as in (i).
The current $S$ is supported by
the vompsvt srt $\overline{Y}$, for if
$w\in \mathcal E^{0,1}(X)$  has compsct dupport ehivh i didjoint ftom
$\overline{Y}$ we can take $g=0$ in (i) and get $S(w)=0$.
Nect, if $\phi\in C^\infty(X)$ has compact support
whivh is dodjoint from $K$ we take $w=\bar\partial(\phi)$ snd dince
$\phi|K=0$ we get
\[
S(\bar\partial(\phi))=0
\]
Thid dhows thdt the dupport of
thr current
$\bar\partial(S)$ is contained  in $K$.
At this stsge one ues thdt the
$\bar\partial$-operstor is elliptic.
If follows thst $S$ redtrictd to a holomorphic
1-form in
$X\setminus K$.
if we thrn tske s connected open compoinent
$\Omega$ in $X\setminus K$, the includion 8xx)fiordt entsils thst
the holomorphic 1-form attsched to $S$ is zero in
$\Omega\setminus \overline{Y}$ snd 
since $K$ is Ringe this set is non-empty.
Then \emph{anslyticity} entails thst
$S=0$ in thr ehole open rt $\Omega$ snd we conclude thst
$S=0$ in $X\setminus K$, i.e. the cuirrent has cmposct dupport in $K$.
Now we tdke dome $f\in \mathcal O(U)$ here $U$ is a - in genersl small- 
open neighborhood of $K$.
We csn vhoode $\rho\in C^\infty(X)$ eith 
compsvt dupport in $u$ while $\rho=1$ 
in dome opoen nighbrhood of $K$.
Then $\bar\partial(\rho g)$ has compsvt duprt ehivh id didjoint ftom
$K$ and form the sbove one has
\[
0=S(\bar\partial(\rho f))= \int_K\, \rho fd\mu=\int_Kfd\mu
\]







However, it doe not slwys supersed the classic proofs.
in pasrtoiculsr we recsallmthst hermsnn Schwarz alresfy in 1870
proved the unifomrsisstion theorem for planer domains
via a rsther natursl extendionnof Riemsnn's mapong theorrm for dimply connctd
domains.
The proof chwrz employs mulit.vslkued analytic funvyionf in
the sense of Weierstrass and here one also exhibitd domr interedting
condtnt stteched to a bounded and connectd domdin
$\Omega$ in ${\bf{C}}$.
More oprecidsely, tgivrn s pint $z_0\in\Omega 4 one regsrds ths
srt of gernms of snskytic funvyions $f8z9 st $z_0$ ehivh cn br vontonud snslyticsly slong
evety cuve in $\Omega$ whiich stsrts st $z-0$ sand has sn arbitsry end-point
in
$\Omega$.  Denote  this family of germs by $M_\Omega(z_0)$.
next, identify the fundsmets grtoup $\pi_1(\Omega)$  eith homotopy clases f closed curves whih
stdtt snd end st $z_0$.
The monofromy theorrm  by Weierdtrass assertd thst
if
$f\in M_\Omega(z_0)$ and 
$\gamma$ ius suvh a closed curvr, thrn thr germ $t_\gamma$ st $z_0$ ehivh srises vis anslytic conoinustionmony dependd upon thr homotopy class of
$\{\gamma\}$ of th givrn closed ruve. The full rsnge of $f$ st $z_0$ isd defned by
\[
f^*(z_0=\{ T_\gamma(f)z_0)\}
\]
where $\gamma$ vasry over closed curves st $z_0$.
in a similsr way on findd thr fgull range $f^*(z)$ st svety pinit $z|\in \Omega$.
Follwing Hermsnn Schwsrz we introuce the set
\[
S_\Omega(z_0=\{ f\in M_\Omega(z_0)\quad
\colon  f^*(z_1)\cap f^*(z-2)= \emptyset\,\colon z_1\neq z_2\}
\]
Next, let $S^*_\Omega)(z-0)$ be tghe dubdt of'those f
$f\in S_\Omega(z-0)$ with 
$f^*(z)\subset D$ for every
$z\in \Omega$
Folloei g Schwsrz we thrn regsrd thr poditvr number
\[
M=\max_{f\in S^*(xx9}
 \,|f'(z_0)/
 \]
RTepsting riemsnnŠs rpof nfor thr dimply connrctrd fomdin, schwsrs proved thrst there exidts a uniwue $f\in S^*_\Omega(z_0)$ suvh thst
th vomplex derivdtive $f'(z_0)=M$ and the totsl rsnge
\[
\cup_{z\in \Omega} f^*(z)=D
\]
using $f^*$ one esdily gets the uniformisstion theorrm, i.e. thr dimply connctd domdin sbove $\omega$ is thrornunit disc $D$ snd there exidts
a holomorphic map 
$\pi\colon D\to \Omega$ ehih is locslly biholomorphic sndhas discretr 
fiberd, esch of which csn bve identfied rith
$\pi_1(\Omega)$.
it goes eithout ssying thst thi an exidtence theorrn  wherr the stusl "elicit derrmindtion"bof Schwarz*s mapping funvtion is not essy to trsce, except for s few very specisl csse.




The passage to an  arbitrary  open Riemann surface is a bit technical.
Let us only remark that
the original proof by Behnke and Stein from 1948
was later simplified by Malgrange using a clever trick about
currents where the elliptic property of the $\bar\partial$-operator  is used.
So the proof of surjectivity offers a good illustration why
systematic use of cuurents
is so  valuable while one regards analysis on 
complex manifolds.
When $X$ is compact the situation  is different.
Here  
the map (*)
has a closed range and the quotient  space
\[
\frac{\mathcal E^{0.1}(X)}{\bar\partial C^\infty(X)}\tag{**}
\]
is a finite dimensional complex vector space.
This goes  back  to work by Cauchy and 
Pompieu from 1810, and 
is the starting point for the analyis 
on compact Riemann surfaces.
The essential ingredient in the proof
is an inequality which goes as follows:
Let $\{U_\alpha,z_\alpha\}$ be s finite covering of
$X$ where each $U_\alpha$ is an open set which is biholomorphic
with
tht open unit disc, and $z_\alpha$  the  complex coordinate  in $U_alpha$.
i
If $f\in C^\infty(X)$  
we find for every $\alpha$ a function
$f_\alpha\in  C^\infty(U_\alpha)$ where 
\[
\bar\partial f|U_\alpha= f_\alpha(z)\cdot d\bar z_\alpha
\]
Put
\[
||\bar\partial f||= \sum\, ||f_\alpha||_\infty
\] 
where we  take  maxium norms of the $f_\alpha$-functions over
the sets $U_\alpha$.
With these notations one has:

\medskip

\noindent
{\bf{Pompieu's inequality.}}
\emph{For each point $p\in X$ there exists a constant  $C$ such that}
\[
|f|_X\leq C\cdot ||\bar\partial f||
\]
\emph{hold when $f\in C^\infty(X)$ and $f(p)=0$.}

\medskip

\noindent 
Let us remark thst  this follows  from
the solution to the $\bar\partial$-equation in the complex $z$-plane
where we write  $z=x+iy$.
Namely, for every test-function $g(x,y) $ we put
\[
h(z)= \frac{1}{2\pi i}\cdot \iint\, \frac 
{g(\zeta)}{z-\zeta} \, d\zeta\wedge d\bar\zeta
\]
Then $h$ is a  $C^\infty$-function which satisfies
\[
\bar\partial (h)= f\cdot d\bar z
\]
This classic formula 
illustrates thsat 
 one should  learn analytic function theory  via
systematic use of
the $\bar\partial$-operator, and not restrict the  attention to
holomorphic functions, but rather let \emph{real analysis} intervene.
For exsmple, Cauchy's residue formula is best  
formulated as follows. Whenever $f(x,y)$ is a $C^1$-function
in the real $(x,y)$-plane with $z=x+iy$, one has 
\[
f(0)= \frac{1}{2\pi i}\cdot \lim_{\epsilon\to 0}\int_{|z|=\epsilon}\, \frac{f(z)}{z}\, dz
\]
\medskip


\noindent
{\bf{Duality redults.}}
To profit upon (**)    one regards the space
${\bf{c}}^{1,0}(X)$ of currents  of bi-degree $(1.0)$, i.e.
the dual of the Frechet space $\mathcal E^{0.1}(X)$.
 Now the dual of  (**) is the $\bar\partial$-kernel on
 ${\bf{c}}^{1,0}(X)$,  and since  
 $\bar\partial$ is an \emph{elliptic} operator  the kernel is  the space
 $\Omega(X)$ of holomorphic 1-forms.
 The isomorphism
 \[
 \bigl[\frac{\mathcal E^{0.1}(X)}{\bar\partial C^\infty(X)}
\bigr ]^*\simeq  \Omega(X)\tag{**}
 \]
 is cslled the duality theorem on compact Riemann surfaces
 The  genus number is defined by
 \[
 g=\dim \Omega(X)
 \]
 Starting from (**)  one easily deduces some classic facts
 due to Riemann. First 
 \[
 2g=\dim H^1(X)
 \]
 where $H^1(X)$ is the cohomology spsce over $X$.
 Next, a compact Riemann surface is in particular sn oriented and compact 
 real manifold of dinmension two.
 Using  triangulations  it was discovered in 1850  by the geometer
 Camille Jordan that
$X$ is homeomorphic to a sphere with $g$ many attached handles.
 Moreover, the complex analytic structure 
 gives rise to further results  established by Riemann around
 1855.
 Namely,   Jordan's result  gives 
 a basis for the homology expressed  by
 $2g$ many closed curves
 $\gamma_1,\ldots,\gamma_{2g}$ on $X$.
 They can be chosen  to be rectifiable so that  differential 1-forms
 can be integrated along every $\gamma$-curve.
 Hence each $\gamma$-curve is identfied 
 a 1-current via  the map
 \[
 \alpha\mapsto \int_\gamma\,\alpha\tag{i}
 \]
 where $\alpha\in\mathcal E^1(X)$.
 The currents $\{\int_\gamma\}$
 are  $d$-closed
and one has a direct sum decomposition
\[
{\bf{c}}^1(X)=d({\mathfrak{Db}}(X))\oplus \Gamma  \tag{ii}
 \]
 where $\Gamma$ is the $2g$-dimensional complex vector space 
 generated by the currents in
(i).
Another consequence of (**) together with  the fact that
$\bar\partial$ is elliptic goes as follows.
\medskip

\noindent
{\bf{0.1 Theorem.}}Ê\emph{A current $\gamma$ 
of bi-degree (0,1) 
$\bar\partial$-exact  if and only if}
\[
\gamma(\omega)=0\quad\forall\, \omega\in \Omega(X)
\]





\medskip

\noindent
{\bf{Period integrals.}}
Next, following original work  due to Abel and Riemann
one  studies various period integrals. This 
gives  rise to  remarkable
results about algebraic curves.

\medskip

\noindent
{\bf{An example.}}
Consider the algebraic equation
\[
y^2=x(x-1)(x-b)\tag{i}
\]
where $b>1$ is real.
In the 2-dimensional complex $(x,y)$-space it defines 
a non-singular  algebraic curve'$S$. Indeed,
the reader can check that if
$P(x,y)= y^2-x(x-1)(x-b)$ then the complex gradient vector
$(P_x,P_y)\neq (0,0)$ for sll points  on $S$.
In the projective
space
${\bf{P}}^2$  the metric closure of $S$ gives a  compact space $X$. It 
is clear from (i) that  $X\setminus S$ is reduced to the single  point
$(0,0,1)$, Close to this point we have local analytic coordinates
representing points $(\zeta,\eta,1)$ on the 2-dimensional projective space.
When $\zeta\neq 0$ they give points
\[
p=(1,\frac{\eta}{\zeta}, 1/\zeta)
\]
which belong to  $S$ if and only if
\[
\zeta^{-2}=\frac{\eta}{\zeta}(\frac{\eta}{\zeta}-1)(\frac{\eta}{\zeta}-b)
\implies
\zeta=\eta(\eta-\zeta)(\eta-b\zeta)
\]
The reader can check thst this corresponds to an equation
\[
\zeta=\phi(\eta)
\]
where $\phi(\eta)$  is sn analytic function with a xero of order three  at  $\eta=0$.
From this one deduces that when $y$ is identified with a globally defined
meromorphic function on $X$, then it has a triple pole at
$(0,0,1)$,  and   simple
zeros at the points
$(0,0,(1,0),(b,0)$ in $S$.
Put
\[
\omega=\frac{dx}{y}
\]
One  verifies that this is  a globally defined holomorphic
1-form on $X$ without zeros. It follows from a general result referred to as the Riemann-Hurwitz formula that the genus of $X$  is one, i.e. $X$ is a torus.
Now one can construct a pair of   closed curves
$\gamma_1$ and $\gamma_2$ which intersect transverslly at a single point on
$X$, and   following Abel one  introduces  the period numbers
\[
w_1=\int\, \omega \quad \&\quad w_2= \int \,\omega
\]
Abel posed the problem when
a triple of  points $p_1,p_2,p_3$ in $X$ stay  on a complex line in
the (x,y)-space.
For example,
when does there exist a pair of complex numbers $\alpha,\beta$ such that
each $p_\nu$ stays on a  line
$\ell$ defined by the equation
\[
y=\alpha\cdot x+\beta
\]
So with $p_\nu=(x_\nu,y_\nu)$ it means that
the $x$-coordinates satisfy the
algebraic equation
\[
(\alpha\cdot x+\beta)^2=x(x-1)(x-b)
\]
To settle this  problem
Abel considered an arbitrary  triple of $X$-points,  and for each
$1\leq \nu\leq 3$ one takes a simple  curve $\rho_\nu$ 
on $X$ which  joins $(0,0)$ with $p_\nu$. Then one regards the Abel sum:
\[
W= \sum_{\nu=1}^{\nu=3}\, \int_0^{p_\nu}\, \omega
\]
This complex number depends upon the chosen
$\rho$-curves,  but since line integrals 
of $\omega$  along a pair of  homotopic curves
are equal, the position of $W$ modulu the  period lattice
\[
\Gamma={\bf{Z}}\cdot w_1+{\bf{Z}}\cdot w_2
\]
only depends on the  given $p$-points.
With these  notations a msjor result from Abels famous work
which he
published in 1826   asserts the following:
\medskip


\noindent
{\bf{Theorem.}} \emph{There exists a constant $C$ which only depends on
the chosen $\gamma$-curves such that a triple  of points
$\{p_\nu\}$ stay on a complex line if and only if}
\[
W= C+ n_1w_1+n_2w_2
\]
\emph{for some pair of integers $n_1,n_2$}.
\medskip


\noindent
{\bf{Final  Remark.}} This finishes  our   introduction.
To digest   results such as Abel's theorem  above
illustrates  the flavour  in  the  theory about Riemann surfaces.
Let us also remark thst currents are used to
prove another remarkable  result by  Abel concerned with
the existence of meromorphic  functions on  compact Riemann surface with 
an arbitrary  genus number  $g\geq 1$.
Namely, let $N\geq 2$ and consider a pair of $N$-tuples of distinvc points
$(q_1,|\dots q_N)$ and $(p_1,\dots p_N)$ and
Now we ask when there exists a meromorphic
function $f$ on $X$ with simple  zeros at  the 
$q$-points, simple poles st the $p$-points  and 
otherwise holomorphic and zero-free.
Abel  proved that $f$ exists if and only if there exists
simple curves $\rho_1,\ldots,\rho_{2g}$ where
$\rho_\nu$ has end-points st $q_\nu$ and $p_\nu$ such thst
\[
\sum_{\nu=1}^{\nu=2g}\, \int_{\rho_\nu}\, \omega \quad\colon 
\, w\in \Omega(X)
'\]
It turns out that via systematic use of currents, thr proof boils  down to
show that on the projective line
${\bf{P}}^2$ there  does noe exist any globslly defined holomorphic
1-form, together with Theorem 0.1 above.






\newpage




 
 facts sbout compact and non-comnpsct Riemann surfsces
are exposed using the calculus with currents, i.e.
the algebraic approach to compact Riemsnn surfaces is only mentioned
briefly,  while such results such as Abel's theorem providing
a necessary and sufficient condition for
the positioon of poles and xeros of s globally defined meromorphic function
appears. For open Riemsnn surfaces I will
expose some details  from the  theorem  due to Behnke and Strin  which
asserts  thst the  inhomogeneous $\bar\partial$-equation
is solvable  on every non-compst Riemsnn surface.
The uniformisation theorem  for Riemann surfsces
is an easy consequence
of this result,  and
I will  sketch how it csn be spplied to
analyze geodesic curves when a Riemann surface  is
equipped with s hyperbolic metric. A very elegant
proof by  Arne Beurling appesrs and
illustrates that analytic function theory using subharmonic
functions is  importsnt.
Passing  to complex manifolds of dimension $\geq 2$
one encounters plurisubharmonic functions
which will play a central role 
in many subsequent lectures  of these seminars..
So it is a good occasion to first become fsmiliar methods in
the 1-dimendional case where  classic results sbout
Riemann surfaces  appear.
So this  motivates  the contents  of the first lecture in these seminars.







\newpage





\centerline{\bf{Compact Riemann surfaces.}}

\bigskip

\noindent
A compact Riemann surface
$X$ is by definition a connected and compact
complex analytic manifold of dimension one.
The maximum principle for holomorphic functions entails that
every globally defined holomorphic funtions on $X$
is a  constant.
Thus, $\mathcal O(X)$ is reduced to the complex field.
But if one allows poles we shall learn that there exist non-constant
meromorphic functions
on $X$. They give a field denoted by
$\mathcal M(X)$ whose properties will
be investigated later on.
The projective line ${\bf{P}}^1$
over the complex field is an example of a compact Riemann surface.
One starts with the complex $z$-plane and adds the point at
infinity to get ${\bf{P}}^1$. Here
$\mathcal M({\bf{P}}^1)$ is equal to 
the field of rational functions of
the single complex variable $z$.
More generally, 
one starts from
an irreducible polynomial $P(x,y)$
of two independent variables, i.e.
$P$ is irreducible in the unique factorisation domain
${\bf{C}}[x,y]$.
We  shall learn how to find the associated compact
Riemann surface $X$ where $\mathcal M(X)$
\[
\mathcal M(X)\simeq\text{quotient field of}\,\,\,
\frac{{\bf{C}}[x,y)}{(P)}
\]
and $(P)$ denotes the principal ideal generated
by $P$.
Here is  an example. Let 
\[
P(x,y)= y^3-x^3-1
\]
To get $X$ one first regards the
algebraic curve in ${\bf{C}}^2$ defined by
$\{P=0\}$.
The complex gradient
vector $(P'_x,P'_y)= (3x^2,3y^2)\neq (0,0)$ when $P(x,y)=0$. It 
means that $\{P=0\}$ is non-singular
and hence can be regarded  as an embedded one-dimensional complex manifold
in
${\bf{C}}^2$.
To get a compact complex manifold one regards the
projective curve $S$ in ${\bf{P}}^2$
with its inhomogeneous coordintes
$(\zeta,x,y)$
where $S$ is the zero set of $P^*(\zeta,x,y)= y^3-x^3-\zeta^3$.
We shall learn  that $S$  is non-singular
and therefore gives a compact Riemann surface.
Less obvious is that
$S$ regarded as a topological space is
homeomorphic to
the oriented real manifold
$T^2$, where $T^2$ denotes the 2-dimensional torus.
This will be proved in ¤ xx.


\medskip
\noindent
Originally compact Riemsnn surfsces were obtsined via the algebraic procedure above, i.e.
starting from an irreducible polynomial $P(x,y)$. The constructioin of
the assocaited compsvt Riemsnn urfsce wss givrn by Bernhard Riemann in 1855.
He  employed local charts which were found esrlier by Puiseux.
This locsl result goes as foloows:
Consider a function of the form
\[
\phi(x,y)= y^e+g_1(x)y^{e-1}+\ldots +g_e(x)
\]
where $\{g_\nu(x)\}$ are holomorphic funvtion of
the complex vsribe $x$ defined in some disc $D=\{|x|<r\}$ centered at the origin and 
$g_\nu(0)=0$ for each $\nu$.
Put $S= \{\phi=0\}$ ehicvh is an analytic curve
defined in $D\times {\bf{C}}$.
We assume thst $\phi$ is irreducible  in thr unique factorisstion domsin
${\bf{C}}\{x\}[y]$. Thjs entails thst one has a fsrorisstion
\[
\phi(x,y)= \prod_{\nu=1}^{mu=e}\, (y-\alpha-|[nu(x))
\]
where the root functions sre defiened in a small puntured disc
$0<|z|<\delta$. When $e\geq 2$ these root funvtiond sr not single-vslued.
However, Pusieux proved in 1850
thst with s new complex vsriabke $\zeta$ there exisdts
a holomorphic funvtioin
$A(\zeta)$ defined in a disc $\Delta$ centered at $\zeta=0$
suvh thst
\[
S= \{(\zeta^e, A(\zeta)\,\colon\, \zeta\in \delta\}
\]
Moreover, $A(\zeta)$ has a poer series expnasion
\[
A(\zeta)= c_1\zeta+c-2\zeta^2+\ldots
\]
with the property that for every
prime number which sppesrs ss a factor in
$e$ there exists some $\nu$ which
does not contain $p$ as a prime factor and $c_\nu\neq 0$.
Thus local result by Pusieux was thrn sdoptef by Riemsnn tyo condtruct
the associated Riemsnn surfsce sbove.
It is indtducitve. and not very difficult - to
analkyze $X$ when $P(x,y)$ is givn. Here sversl formulas sppesr
which for exemple dermine thr \emph{gniuus number} of $X$ from
propertied of th givrn polynomisl $P$.

\medskip

\noindent
The subsewuent msterisl willo
not focus so muvh upon the
aslgebrsic manipulstiond, but rsthrr
edtsblidh
fsvtd sbout compsvt riemsnn urfsced vis analyis based upon
the cslclusu eith currentd snd potntisl thoretic methods.
This approasvh wssd originslly fonr by <hermsnn <Seyl in s clsdic book from
1913 :\emph{Die Idee der Riemsnnschen FlŠchen}.
To a large ectent we folloow Weyl's book below.
Let us only remsrk tht thr noyion of didtributiond and currentd of cvoutse
wss wellknoen
at this time - st lesdt when dopted to 
1-dimendionsl complex manifolds.
So evetythiung blow 
abot compsvt <riesnn durfsve is classic. In ddition to Reimsnn msjoir contrubution sre due to Abel and
Weierstrass.
The grestest cvhslengr is to pursue dep theorrms whivh go bask to
Abel's fsmous srticle from 1826 abouyt a new class if
trasncendentsl functions.
It les for exsmple to \emph{Abel's addition theorem}
ehivh is a veritsble high-light in thr whod theory.
\medskip

\noindent
of courde, hundredd of tect-boks hsve ecposed the theotu sbnout
Riemann surfsve. Below my main indpitstion has
been thr clddic tect by Appel-Goursst sbout slgebrsic funvtiond, togethr eith
Giunning'd levture edited by <princeton Univerdity <press sround 1960.
Som fsmlisriuty eith bsic noyiond in differentisl geometry - redtrfcited to manifolds of resl dimendjion 2, and
thr mr notion of didtributions is asdumed. otherwise th
mzterisl is slef-contsine for resderd who re resonsbly well aqyzinted eith
anslytic funvyion throry.
An exszmple is the fsmoud redult due to PompŒieu from 1810
whivh assers thst the inhomogenous $\bar\partial$-ewustion is
sovsble in planar domsins.
Ststting from this one derives some funds,mrntsl theortrmd on compsvt
Riemsnn durfsces $X$ suvh sd thr Duaslity Theorrm whivh
csn be expressed by ssying thst
a differentisl form $\alpha$ of bi-degree (0,1) on $X$ is
$\bar\partial$-exsct if snd only if
\[
\int_X\, \alpha\wedge \omega=0
\] 
hold for evety globally degined holomorphic 1-form  $\omega$.






\medskip


\centerline{\bf{About methods of proofs.}}
\medskip

\noindent
Riemann surfaces offer instructive lessons in sheaf theory since
various sheaves
appear in a natural fashion. The reader is supposed to be familiar with
basic facts about sheaves and their cohomology. For less experienced readers we
add an appenbdix where
som fundamental reults from Leray's   pioneering article
\emph{xxxx} are resumed. Let us also 
remark that even if Weierstrass never
introduced the notion of sheaves, his construction of
"sheaf spaces" attached to  multi-valued analytic functions
gave the first  exampe of sheaves.
In addition to sheaf theory we employ calculus on manifolds without
hesitation.
For example. let $M$ be an oriented  real $C^\infty$-manifold of some dimension
$n\geq 2$. To say that $M$ is oriented means that
there exists a globally defined differential $n$-form
which never vanishes and choosing an  orientation
one can define integrals
\[
\int_M\, \omega\quad\colon\quad \omega\in \mathcal E^n(M)
\]
where $\mathcal E^n(M)$ is the space of 
$n$-forms with $C^\infty$-.coefficients.
More generally there exist to each
$0\leq p\leq n$ the space
$\mathcal E^p(M)$ of differential $p$-forms
with $C^\infty$-coefficients.
Under the condition that $M$ can be covered by a denumarable family of compact subsets
it follows  that
$\mathcal E^p(M)$ is equipped with a topology so that it
becomes a Frechet spaces.
There also exists the spaces
$\{\mathcal E^p_0(M)\}$
which consist of differential forms having compact support in
$M$.
The dual of
$\mathcal E^p_0(M)$ is denoted by
$\mathfrak{c}^{n-p}(M)$ and its elements are called currents of
degree $n-p$.
In particular $\mathfrak{c}^0(M)$ is the space of distributions on
$M$ and is often denoted by
$\mathfrak{Db}(M)$. Thus, by definition
\[
\mathfrak{Db}(M)\simeq \mathcal E^n_0(M)^*
\]
where * indicates that one regards the dual space.
We assume that the reader is famiiar with basic distribution theory which for
example is coveed in Hšrmander's text-book
[xx].
Even if we shall not study manifolds of dreal dimension $\geq 3$
we recall some classic facts about oriented and compact $C\infty-$manifolds
Let $M$ be a such a manifold of some dimension $n\geq 2$.
Using exterior differentials one
has a complex
\[
0\to \mathcal E^0(M)\to \mathcal E^1(M)\to\ldots\to \mathcal E^n(M)\to 0
\]
Here
\[
d\colon \mathcal E^p(M)\to \mathcal E^{p+1}(M)
\] 
are continuous for every $p$, where we recall that
every $\mathcal E^p(M)$ is a Frechet space.
A fundamental fact is that the images of the $d$-maps 
are closed and have finite codimension.
This can be proved in several ways. The most convincing proof is due to
AndrŽ Weil who  established that
every compact and oriented manifold $M$ can be triangulated
via  a finite simplicial complex.
Readers interested in algebraic topology should  consult Weil's
original proof which teaches a good lesson
dealing with
topology and triangulations of manifolds.
Next one introduces the cohomology spaces
\[
H^p(M)= \frac{\text{Ker}_d(\mathcal E^p(M))}{d\mathcal E^{p-1}(M)}\quad\colon 0\leq p\leq n
\]
In particular $H^0(M)$ is the $d$-kernel on $C^\infty(M)$ and hence the
1-dimensional space of constant functions.
One has also the complex of currents:
\[
0\to \mathfrak{c}^0(M)\to \mathfrak{c}^1(M)\to\ldots\to \mathfrak{c}^n(M)\to 0\tag{**}
\]
It is denoted by
$\mathfrak{c}^\bullet$.
For every $p$ one has the inclusion $\mathcal E^p(M)\subset\mathfrak{c}^p(M)$ 
and hence  
(*) is a subcomplex of (**).
Next, the  contruction of currents and their exterior differentials, togehter with
the closed range of the differentials in (*), 
give
a natural  duality
\[
H^p(M)^*\simeq \frac{\text{Ker}_d(\mathfrak{c}^{n-p})}{
d(\mathfrak{c}^{n-p-1}(M)}= H^{n-p}(\mathfrak{c}^\bullet)\tag{***}
\]
Since $M$ admits a triangulation one csn essdily prove tht  
the complexes (*) and (**) are quasi-isomorphic.
Hence the right hand side in (**) can be identfied with
$H^{n-p}(M)$, i.e. the dual of $H^p(M)$ is
equal to th cohomology space in degree $n-p$.
This is referred to as the \emph{PoincarŽ duality theorem} for compact
and oriented  manifolds.















\medskip

\noindent
{\bf{Examples when $n=2$.}}
Let $M$ be an oriented  $C^\infty$-manifold of dimension two.
Since $M$ can be covered by a finite family of
charts  we can equip $M$ with a distance function
$d$ whose restriction to charts is equivalent to ordinary euclidian metric.
Every pair of such distance functions
$d_1$ and $d_2$ are equivalent in the sense that
there exists a constant $C>0$ such that
\[
C^{-1}\cdot d_2(p,q)\leq d_1(p,q)\leq C\cdot d_2(p,q)
\]
hold for every pair $p,q$ in $M$.
Next, a  parametrized curve
on $M$ is a continuous map $\gamma\colon [0,1]\to M$.
Using a metric as above we can impose the
extra condition that
$\gamma$ has a bounded variation, i.e. there exists a constant $C$ such that
\[
\sum_{\nu=0}^{\nu=N-1}\, d(\gamma(t_{\nu+1}),\gamma(t_\nu)\leq C\tag{i}
\]
for all partitions
$0=t_0<t_1<\ldots<t_{N-1}<t_N=1$.
When (i) holds  there exist ordinary Borel-Stieltjes' integrals
\[
\int_\gamma\, \psi^1\tag{ii}
\] 
for every differential 1-form $\psi^1$ with $C^\infty$-coefficents.
This gives a continuous  functional on
$\mathcal E^(M)$ with compact support and hence a current of
degree 1, called 
the integration current associated with
$\gamma$. This operative construction  will
be used at many places later on.
One merit is that  "nasty geometric pictures"
when $\gamma$ for example has self-intersections
can be ignored while one
treats its associated integration current.
The case when $\gamma$ is closed, i.e. when
$\gamma(1)=\gamma(0)$ 
leads to special results. To begin with
we notice that
the equality $\gamma(0)= \gamma(1)$ entails that
\[
\int_\gamma\, dg=0\quad\colon\quad g\in \mathcal E(M)
\]
This is expressed by saying that the current
$\int_\gamma$ is $d$-closed.
A crucial result which follows from
the fact that
every distribution in ${\bf{R}}^2$ has  locally primitive distributions with
respect to the pair of euclidian coordinates in
${\bf{R}}^2$, entails that
the following complex vector spaces are isomorphic
\[
\frac{\text{Ker}_d(\mathcal E^1(M))}{d(\mathcal E^0(M)}\simeq
\frac{\text{Ker}_d(\mathfrak{c}^1(M))}{d(\mathfrak{Db}(M)}\simeq
H^1(M)
\]
where the last term is the cohomology space in degree one on $M$.
This entails that if $\gamma$ is a closed and rectifiable curve 
then there exists a $d$-closed 1-form
$\phi\in \mathcal E^1(M)$ and a distribution $\mu$ such that
\[
d(\mu)+\phi^1=\int_\gamma\tag{*}
\]
where equality holds  in
$\mathfrak{c}^1(M)$.
Here the  $d$-closed 1-form $\phi^1$ is
unique up to
an exact smooth 1-form.
With $\gamma$  regarded as a linear functional on
$\mathcal E^1(M)$ the reader should check that
(*) gives the equality
below for every $d$-closed $\psi^1\in\mathcal E^1(M)$:
\[
\gamma(\psi^1)= \int_M\, \phi^1\wedge \psi^1
\]
\medskip

\noindent
{\bf{The $d$-closed current $\int_{\partial\Omega}$.}}
Let $\Omega$ be a connected open set in $M$
whose boundary $\partial\Omega$ is regular in the sense of
Federer. It means that
there exists a (possibly empty) closed set
$\Sigma\subset\partial\Omega$ whose 1-dimensional Haussdorff measure is zero
while 
$\partial\Omega_*=\partial\Omega\setminus \Sigma$
is locally simple and rectifiable with a total finite arc-length.
The orientation  along $\partial\Omega_*$ is given by the rule of thumbs
exactly as 
in the classic version of
Stokes Theorem, which  was already well explainef
by the  genius
Archimedes.
Under these conditions one has the equality 
\[
\int_\Omega\, d\phi= \int_{\partial\Omega_*}\, \phi
\]
for each $\phi\in \mathcal E^1(M)$.
In particular the 1-current defined via the right hand side is $d$-closed.
Notice that we do not assume that
$\partial\Omega$ is connected.
\medskip

\noindent









\noindent
{\bf{Direct images of currents.}}
Let $\rho\colon M\to N$
be a $C^\infty$-map from $M$ to another oriented 
and compact 2-dimensional manifold $N$.
Elie Cartan's
construction of differential forms on manifolds give for
each $\phi\in\mathcal E^1(N)$ a pullback
$\rho^*(\phi)\in \mathcal E^1(M)$.
The map  is continuous when $\mathcal E^1(N)$ and
$\mathcal E^1(M)$ are equipped with
their standard Frechet topologies.
In particular we regard a
parametrized curve
$\gamma$ and obtain 
a 1-current
$\rho_*(\gamma)$ on $N$ defined by
\[
\rho_*(\phi)= \int_\gamma\, \rho^*(\phi)
\]
Later on we shall use  such direct images of currents at several places.
The reader  should "accept" that it is often  more profitable to
ignore "intuitive genetroic pictures" while calculations 
are performed.
A  merit is  that
while the integrals along the  $\gamma$ is computed, then
calculus teaches that one can employ
different parametrisation  along $\gamma$,  as long as they
have bounded variation and preserve the given orientation.
Notice that even if $\gamma$ from the start is a simple Jordan arc, it
may occur that $\rho_*(\gamma)$
has a more involved structure  since
the restriction of the map $\rho$ to $\gamma$ need not be
one-to-one.
\medskip


\noindent
{\bf{Intersection numbers.}}
If $\rho $ is another  closed and rectifiable curve we have a
similar decomposition
\[
\int_\rho=\psi^1+d(\nu)
\]
Stokes Theorenm implies that 
\[
\int_M\, \phi^1\wedge \psi^1\tag{*}
\]
is independent of the chosen decompostions.
So the complex number in (*) depends only upon the ordered
pair of closed curves
$(\gamma,\rho)$ and  is denoted by
$\mathfrak{i}(\gamma,\rho)$.It is called the intersection number of the closed curves.
Calculus shows
that the intersection number always in an integer,
and by continuity it follows that
if $\gamma$ and $\gamma^*$ are two homotopic closed curves
then
$\mathfrak{i}(\gamma,\rho)=
\mathfrak{i}(\gamma^*,\rho)$ for every other closed curve
$\rho$.
\medskip


\noindent
Riemann analyzed intersection numbers between 
pairs of closed and simple curves on an oriented 2-dimensional manifold
$M$. He proved thst if it has as genus $g\geq 1$
then there  exist 
simple closed curves
$\mu_1,\ldots,\mu_{2g}$ which give
a free basis for the fundamental group $\pi_1(M)$ which is free of some rank $2g$.
Moreover, he showed the the $2g$ msny closed curevd csn be srrsingrd
as a pair of $g$-tuples 
$\gamma_1,\ldots,\gamma_g$ and
$\rho_1,\ldots,\rho_g)$ , where 
\[
\mathfrak{i}(\gamma_\nu,\rho_\nu)=1\quad\colon \quad 1\leq\nu\leq g
\]
while all other intersection numbers are zero.
In topology one says  that this special family of closed curves
is a basis for the homology on $M$.
Classic tet-books,  such as Appel-Goursat
trestise about   algebrsic functions, 
offer  instructive pictures and examples which expose 
Riemann's  original work, where 
a basis of homology is achieved via triangulations of $M$.
It goes without saying that Riemann's work 
has inspired combinatorical  topology.


\newpage















\newpage


\centerline{\bf{Analysis on compact Riemann surfaces.}}
\bigskip


\noindent
Let $X$ be a compact 1-dimensional complex manifold.
Recall that its 
complex analytic structure arises via charts
$(U,z)$ where $z$ is a local coordinate on
$X$ in the open set $U$ which is biholomorphic with
the open disc $D=\{|\zeta|<1\}$ in the complex $\zeta$-plane.
Let $\rho_U\colon U\to D$ be the holomorphic map.
When a pair of charts
$U$ and $V$ overlap
their complex analytic structures are
compatible. It means that
one has a biholomorphic map
\[
\rho_{U.V}\colon \rho_U(U\cap V)\to
\rho_V(U\cap V)
\]
where 
\[
\rho_U(\zeta)=\rho_V\circ\rho_{U,V}(\zeta)\quad\colon
\zeta\in \rho_U(U\cap V)
\]
The reader should illustrate this by a suitable picture
to see how the transition functions work
in overlapping charts
Since $X$ is compact it can be covered by a finite family of charts
$\mathfrak{U}= \{U_\alpha,z_\alpha)\}$. So here $\cup \, U_\alpha=X$
and one refers to $\mathfrak{U}$ as an atlas for the complex manifold $X$.
If $U$ is an arbitrary open set
in $X$ a complex valued function $f$ in $U$ is holomorphic if
\[
f\circ \rho_\alpha^{-1}\in \mathcal O(\rho_\alpha(U\cap\, U_\alpha))
\]
hold for
every chart in the atlas.
The set of holomorphic functions in $U$ is denoted by
$\mathcal O(U)$.
Local existence of non-constant holomiorphic functions is clear since
the defintion above entails  that
if $U_\alpha$ is a chart then
$\mathcal O(U_\alpha)\simeq \mathcal O(D)$.
\medskip


\noindent
{\bf{Differential calculus  on $X$.}}
A complex analytic atlas is in particular  a
$C^\infty$-atlas on the underlying real manifold
which has real dimension two.
The space of complex-vaued $C^\infty$-functions on
$X$ is denoted by $\mathcal E(X)$.
We have also the space $\mathcal E^1(X)$
of differential 1-forms
with
$C^\infty$-coefficients.
In a chart $(U,z)$
every differential 1-form can be decomposed as
\[
a\cdot dz+b\cdot d\bar z\tag{A.0}
\]
where $a$ and $b$ are complex-valued $C^\infty$-functions.
This gives a direct sum decomposition
\[
\mathcal E^1(X)=\mathcal E^{1.0}(X)\oplus\, \mathcal E^{0,1}(X)\tag{A.1}
\]
One refers to $\mathcal E^{1,0}$ as the space of diffeential 
forms of bi-degree $(1,0)$.
Thet are characterised by the condition that
$b=0$ holds in
$(A.0)$ for every  chart.
Similarly  when $a=0$  hold we get
a differential form of bi-degree $(0,1)$.
If $g\in\mathcal E(X)$ its exterior differential $dg$
is a 1-form which has a decompostion
\[
dg=\partial g+\bar\partial g
\]
For example, one has a map
\[
\bar\partial\colon\mathcal E(X)\to \mathcal E^{0,1}(X)\tag{A.2}
\]
The Cauchy-Riemann equations applied in charts show that
the kernel in (A.2) consists of holomorphic functions and
hence the kernel is reduced to  constant functions.
\medskip

\noindent
Next, we also have differential 2-forms on $X$ which in a chart $(U,z)$
can be expressed as
\[
c(z)\cdot dz\wedge d\bar z
\]
Keeping the complex analytic structure in mind
we denote the space of differential 2-forms with
$\mathcal E^{1,1}(X)$.
The reader should
construct the  maps
\[
\bar\partial\colon \mathcal E^{1,0}(X)\to \mathcal E^{1.1}(X)\tag{A.3}
\]
\[
\partial\colon \mathcal E^{0,1}(X)\to \mathcal E^{1.1}(X)\tag{A.4}
\]
\medskip

\noindent
Next, recall that $\mathcal E(X)$ is a Frechet space
where the topology is defined via uniform convergence of
derivatives in every order.
In a similar fashion $\mathcal E^{p,q}(X)$
are Frechet spaces for every pair $0\leq p,q\leq 1$.
The reader should  check that 
the maps in (A:2-4)  are continous between these 
Frechet spaces.
Less obvious is the folloowing:
\medskip

\noindent
{\bf{A.5 Theorem.}}
\emph{Tbe range of the exterior differential maps
in (A.2-4) above are all closed.}
\bigskip




\noindent
{\bf{A.6. Remark.}}
This is the first non-trivial result
about compact Riemann surfaces.
We give the proof in (*) and remark only that it
relies upon
a classic result due to Pompieu which gives solutions to
the inhomogeneous $\bar\partial$-partial 
equation in planar
domains. More precisely, if
$U$ is an open set  in the complex $\zeta$-plane and
$g\in C^\infty(U)$ then
there exists $f\in C^\infty(U)$ such that
\[
\bar\partial(f)= g\cdot d\bar\zeta\tag{A.6.1}
\]
\bigskip

\noindent
{\bf{A.7 Currents on $X$.}}
To  begin with we have the space
$\mathfrak{Db}(X)$ of distributions which by  definition it is the 
space of continuos linear forms on the Frechet space
$\mathcal E^{1,1}(X)$, i.e.
\[
\mathfrak{Db}(X)= \mathcal E^{1,1}(X)^*
\]
Passing to differential forms
we get dual spaces
\[ 
\mathfrak{c}^{1,0}(X)=\mathcal E^{0,1}(X)^*
\quad\colon\quad
\mathfrak{c}^{0,1}(X)=\mathcal E^{1,0}(X)^*
\]
Finally, we have the space $\mathfrak{c}^{1.1}(X)$
which is the dual of $\mathcal E(X)$.
\medskip

\noindent
{\bf{B.1 The integration current $1_X$.}}
The reader should check that
the complex analytic structure on $X$ entails that its underlying
real manifold is oriented.
It  follows that if
$\gamma\in \mathcal E^{1,1}(X)$
then there exists an integral
\[
\int_X\, \gamma
\]
This defines a distribution   denoted by
$1_X$.
In general we have an inclusion
\[
\mathcal E(X)\subset\mathfrak{Db}(X)
\]
Namely, if $g$ is a $C^\infty$-function we get
a linear form on
$\mathcal E^{1,1}(X)$ defined by
\[
\gamma\mapsto \int_X\, g\cdot \gamma
\]
If
$\gamma^{1,0}$ belongs to
$\mathcal E^{1,0}(X)$
we notice that Stokes Theorem gives
\[
0=\int_X\, d(g\cdot \gamma^{1,0})
\]
Now the reader should verify that
\[
d(g\cdot \gamma^{0,1})=
\bar\partial g\wedge \gamma^{1,0}+g\cdot \bar\partial(\gamma^{1,0})
\]
Next, by definition the
$(0,1)$-current $\bar\partial g$
is defined by
\[
\bar\partial(g)\langle \gamma^{1,0}\rangle=-\int_X\, g\cdot \bar\partial(\gamma^{1,0})
\]
Keeping  signs in mind one concludes that
when $g$ from the start is identified with a distribution, then
the $(0,1)$-current $\bar\partial(g)$ is equal to the smooth
differential 1-form
of  bi-degree (0,1) arising when
$\bar\partial$ is applied to the $C^\infty$-function $g$.
\medskip

\noindent
{\bf{B.2 A  duality result.}}
We have the map
\[
\bar\partial\colon \mathcal E^{1,0}(X)\to \mathcal E^{1,1}(X)
\]
By Theorem A.5 the range is closed.
This implies that
the dual space
\[
\bigl[\, \frac{\mathcal E^{1,1}(X)}{\bar\partial \mathcal E^{1,0}(X)}\,\bigr]^*
\simeq \text{Ker}_{\bar\partial}(\mathfrak{Db}(X))\tag{B.2.1}
\]
Next, recall that  $\bar\partial$ is elliptic.Indeed, via the   classic Pompieu formula for planar
doimains  every distribution $\mu$ satisfying
the homogeneous equation $\bar\partial(\mu)=0$ is a holomorphic
function.
Since $\mathcal O(X)$ is reduced to constants the
dual space in (B.2.1)  is 1-dimensional and hence
\[
\dim_{{\bf{C}}}\, \frac{\mathcal E^{1,1}(X)}{\bar\partial \mathcal E^{1,0}(X)}=1\tag{B.2.2}
\]
Notice also that Stokes Theorem gives
\[
\int_X\, \bar\partial(\gamma^{1,0})=0\quad\colon\, \gamma^{1,0}\in \mathcal E^{,1,0}(X)
\]
from this we conclude thatif 
$\rho^{1,1}$ is a  2-form for which
$\int_X\,\rho^{1,1}\neq 0$, then
\[
\mathcal E^{1,1}(X)={\bf{C}}\cdot \rho\oplus
\bar\partial(\mathcal E^{1,1}(X))\tag{B.2.3}
\]
\medskip

\noindent{\bf{B.3 A second duality.}}
Theorem A.5 entails that
\[
\bigl[\, \frac{\mathcal E^{0,1}(X)}{\bar\partial \mathcal E(X)}\,\bigr]^*
\simeq \text{Ker}_{\bar\partial}(\mathfrak{c}^{1,0}(X))\tag{B.3.1}
\]
The right hand side is found as follows.
In a chart $(U,z)$
a current of bi-degree
$(1,0)$ is of the form
$\mu\cdot dz$ with
$\mu\in \mathfrak{Db}(U)$.
The $\bar\partial$ image of this current is
zero if and only if $\bar\partial(\mu)=0$ and as we have seen
before this implies that
$\mu$ is a holomorphic density.
Hence the right hand side in (B.3.1) consists of globally defined
\emph{holomorphic} 1-forms. This space is denoted by
$\Omega(X)$ and (B.3.1) can be expressed by
the duality formula
\[
\Omega(X)\simeq\bigl[\, \frac{\mathcal E^{0,1}(X)}{\bar\partial \mathcal E(X)}\,\bigr]^*\tag{B.3.2}
\]
\medskip

\noindent
{\bf{B.3.3 Exercise.}}
Show that (B.3.2) gives the following:
A differential form $\gamma^{0,1}$ on $X$ is $\bar\partial$-exact
if and only if
\[
\int_X\, \omega\wedge \gamma^{0,1}=0\quad\colon\, \forall\,\,
\omega\in \Omega(X)
\]
\medskip

\noindent
{\bf{B.4 Passage to currents.}}
Recall that $\mathcal E^{0,1}(X)\subset\mathfrak{c}^{0,1}$.
in ¤ xx we shall learn that
\[
\mathfrak{c}^{0,1}=\bar\partial(\mathfrak{Db}(X))+
\mathcal E^{0,1}(X)\tag {B.4.1}
\]
Moreover, a $(0.1)$-current $\rho^{0,1}$ is
$\bar\partial$-exact, i.e. of the form
$\bar\partial(\mu)$ for some
distribution $\mu$ on $X$ if and only if
\[
\rho^{1,0}(\omega)=0\quad\colon\quad \omega\in \Omega(X)\tag{B.4.2}
\]
\medskip

\noindent
{\bf{B.5 The case $X={\bf{P}}^1$.}}
Here $\Omega(X)$ is reduced to the zero space.
To see this we suppose that
$\omega$ is a globally defined holomorphic 1-form.
Now ${\bf{P}}^1\setminus \{\infty\}$ is the complex $z$-plane and here
\[
\omega= f(z)\cdot dz
\] 
where $f$ is an entire function.
At the point at infinity we have a local coordinate
$\zeta$ and
\[
\zeta= z^{-1}\quad\colon R<|z|<\infty
\]
hold for every $R>0$.
Since $\omega$ is globally holomorhpic we have
\[
\omega= g(\zeta)\cdot d\zeta
\]
when $0<|\zeta|<R^{-1}$. At the same time the reader can check that
\[
dz=-\zeta^{-2}\cdot d7zeta
\]
holds when $R<|z[<R$. Ths entails that
\[
f(z)=-z^{-2}\cdot g(1/z)\quad\colon |z|>R
\]
From this we see that
the entire function $f$ tends to zero as $|z|\to\infty$
and hence $f$ is identically zero.
So with $X={\bf{P}}^1$ one has $\Omega(X)=0$ and
then (B.4.2) entails that
\[
\mathfrak{c}^{0,1}= \bar\partial(\mathfrak{Db}(X))
\]
In other words, the inhomogeneous $\bar\partial$-equation
is always solvable.
Consider as an example a current
of the form
\[
\gamma=\mu\cdot d\bar z
\]
where $\mu$ is a measure in the complex $z$-plane with compact support.
Now there exists the Cauchy transform
\[
\widehat{\mu}(z)=\int\,\frac{d\mu(\zeta)}{z-\zeta}
\]
It is holomiorphic in
in the open set of the complex $z$-plane where
the compact set
$\text{Supp}(\mu)$ has been removed.
passing to infinity we
notice that
it extends to be holomorphic
because one has the convergent series expansion
\[
\widehat{\mu}(z)=\sum_{n=0}^\infty\,
\int\,\zeta^n|cdot d\mu(\zeta)\cdot z^{-n-1}{z-\zeta}
\]
in an exterior disc
$|z[>R$ where
the support of $\mu$ is contained in
$\{|z|\leq R\}$.
\medskip

\noindent
next, by basuc lebsgue theory one knows that
the funnction $\widehat{\mu}$ is locally integrable
in the whole complex $z$-plane and hence defines a distribution.
Finally, Cacuhy's residue formula shows that
the distribution derivative
\[
\frac{\bar\partial\widehat{\mu}}{\bar\partial\bar z}=\pi \cdot \mu
\]
So we get
\[
\bar\partial(\pi^{-1}\cdot \widehat{\mu})=\mu\cdot d\bar z
\]




















\newpage


\centerline{\bf{C. Some sheaves and their cohomology}}.
\medskip


\noindent
Let $X$ be a compact complex  analytic manifold.
Classic  facts due to Cauchy and Pompieu applied to charts in $X$ 
give  an exact sequence of sheaves
\[
0\to \mathcal O_X\to \mathcal E_X\overset{\bar\partial}\to, \mathcal E_X^{0,1}\to 0\tag{C.0}
\]
Using $C^\infty$-parotions of unity and Leray's theory about  cohomology with
values in sheaves
one gets
\[
H^1(\mathcal O_X)\simeq \frac{
\mathcal E^{0,1}(X)}{\bar\partial(\mathcal E(X)}\tag{C.1}
\]
where the left hand side is the first cohomology groups with
values in the sheaf
$\mathcal O_X$. The reader may also notice that when Leray's long exact sequence for sheaf cohomology is applied to (C.0), then it follows that
\[
H^2(\mathcal O_X)=0\tag{C.2}
\]
Next, we have also the exact sheaf sequence
\[
0\to {\bf{C}}_X\to \mathcal O_X\overset{\partial}\to \Omega_X\to 0\tag{C.3}
\]
Since $H^0({\bf{C}}_X)= H^0(\mathcal O_X)= {\bf{C}}$ and (C.2) holds
one gets the following   exact sequence of complex vector spaces:
\[
0\to \Omega(X)\to H^1({\bf{C}}_X)\to
 H^1(\mathcal O_X)\to H^1(\Omega _X)\to H^2({\bf{C}}_X)\to 0\tag{C.4}
\]
Next, we have
also the following exact sheaf sequence
\[
0\to \Omega_X\to \mathcal E^{1,0}_X\overset{\bar\partial}\to \mathcal E_X^{1,1}\to 0\tag{C.5}
\]
This gives the equality
\[
H^1(\Omega_X)\simeq\frac{\mathcal E^{1,1}(X)}{\bar\partial(\mathcal E^{1,0}(X))}\tag{C.6}
\]
The right hand side rsssembles the quotient in
(B.2.2).
Indeed, we can regard the 7emph{conjugate} analytic structure on
the underlying real manifold of $x$ where the sheaf of holomorphic functions
are compex cojugates of sections in
$\mathcal O_X$. From this the reader may conclude via (B.2.2)
that the rifht hand side in (C.5)
is a 1-dimensional vector space. Hence we have 
\[
\dim_{{\bf{C}}}\,H^1(\Omega_X)=1\tag{C.7}
\]
\medskip

\noindent
Next, recall that
$H^2({\bf{C}}_X)={\bf{C}}$. Together with (C.7) we conclude that
 (C.4) gives the
short exact sequence
\[
0\to \Omega(X)\to H^1({\bf{C}}_X)\to
 H^1(\mathcal O_X)\to 0\tag{C.8}
\]
Topology teaches that
the cohomology space
$H^1({\bf{C}}_X)$Êis finite dimensional.
Hence (C.8) implies that both
$\Omega(X)$ and $H^1(\mathcal O_X)$ are finite dimensional complex vector spaces.
Finally, (B.3.2) and (C.1) give
\[
\Omega(X)\simeq\bigl [\, H^1(\mathcal O_X)\,\bigr]^*\tag{C.9}
\]
In particular the complex vector spaces
$\Omega(X)$ and $H^1(\mathcal O_X)$ have the same dimension.
This equality and (C.8) give
\[
\dim H^1({\bf{C}}_X)= 2\cdot \dim \Omega(X)\tag{C.10}
\]
The equality (C.10) is fundamental  during the study of compact
Riemann surfaces. 
A notable point is that
the cohomology group $H^1({\bf{C}}_X)$ only depends upon the
topological space $X$ and not upon its particular complex structure.

\bigskip

\noindent
{\bf{C.10 A duality for currents.}}
In planar domains it is wellknown that the
inhomogenous $\bar\partial$-equation is locally solvable on distributions.
Since the $\bar\partial$-kernel on $\mathfrak{Db}_X$ is $\mathcal O_X$
one has an exact sequence
\[
0\to \mathcal O_X\to \mathfrak{Db}_X\overset{\bar\partial}\to
\mathfrak{c}^{0,1}_X\to 0
\]
Passing to cohomology and using 
$C^\infty$-partitions of the unity, it follows that
\[
H^1(\mathcal O_X)\simeq \frac{\mathfrak{c}^{0,1}_X}{
\bar\partial(\mathfrak{Db}(X)}\tag{C.10.1}
\]
\medskip

\noindent
{\bf{Exercise.}} Deduce from the above that
\[
\Omega(X)\simeq\bigl[\, \frac{\mathfrak{c}^{0,1}_X}{
\bar\partial(\mathfrak{Db}(X)}\,\bigr]^*\tag{C.10.2}
\]
Conclude that the implication below holds for
each 
$\gamma\in \mathfrak{c}^{0,1}$:
\[
\gamma(\omega)=0\quad\colon\,\forall\,\, \omega\in \Omega(X)
\implies \gamma\in \bar\partial(\mathfrak{Db}(X))\tag{C.10.3}
\]
\medskip

\noindent
{\bf{C.11 A decomposition theorem.}}
Since $X$ in particular is an oriented and compact real manifold
one has
\[
H^1({\bf{C}}_X)\simeq\frac{\text{Ker}_d(\mathcal E^1(X)}{d(\mathcal E(X)}\tag{C.11.1}
\]
Next, on $X$ there also exists
the anti-holomorphic differential forms of bi-degree
$(0,1)$, i.e differential forms  $\gamma\in \mathcal E^{0,1}(X)$ for which
$\partial(\gamma)=0$.
This space is denoted by $\overline{\Omega}(X)$.
Using the conjugate complex analytic structure one has another compact
complex manifold $\overline{X}$
where
$\overline{\Omega}(X)$ is the space of holomorphic 1-forms.
Since $X$ and $\overline{X}$ have the same underlying real manifold, it follows from
(C.10) that
\[
\dim H^1({\bf{C}}_X)= 2\cdot \dim \overline{\Omega}(X)\tag{C.11.2}
\]
Using  this we shall prove
\medskip

\noindent
{\bf{C.11.3 Theorem.}}
\emph{One has a direct sum decomposition}
\[
\text{Ker}_d(\mathcal E^1(X))=
d(\mathcal E(X))\oplus \Omega(X)\oplus\overline{\Omega}(X)
\]
\medskip

\noindent
\emph{Proof}
To begin with we notice that
\[
\Omega(X)\,\cap \overline{\Omega}(X)= \{0\}
\]
Counting dimensions this follows if we prove that
a 1-form $\gamma)\omega+\mu$ cannot be $d$-exact
when $\omega\in \Omega(X)$ and $\mu\in \overline{\Omega}(X)$
where at least one these froms is not identically ero.
For suppose that
$\gamma=dg$ is $d$-exact.
If $\omega$ is not identically zero there exists
the conjugate
form
$\bar\omega\in\overline{\Omega}(X)$.
Now Stokes Theorem gives
\[
0=\int_X\, dg\cdot \bar\omega)=\int_X(\omega+\mu)\wedge\bar\omega=
\int_X(\omega\wedge\bar\omega
\]
Now the reader can check that
the last integral is $\neq 0$ when $\omega$ is not identically zero.
hence $\gamma\in d(\mathcal E(X))$ implies that
$\Omega=0$ and in the same way we find that
$\mu=0$ which proves Theorem C.11.3.








\newpage


\centerline{\bf{D. Existence of meromorphic functions.}}
\bigskip


\noindent
On $X$ there exists the sheaf
$\mathcal M_X$ whose sections are meromorphic  functions.
Subsheaves arise via  constraints on  poles.
In particular, let $p\in X$ be a given point and
$m$ a positive integer.
Denote by $\mathcal O_X[* mp]$
the sheaf whose sections are meromorphic functions on
$X$ which are holomorphic in $X\setminus\{p\}$ and have
poles of order $\leq m$ at $p$.
If $(U,z)$ is a chart where $p$ corresponds to
the origin we seee that
\[
\mathcal O_X[* mp]\,|U= z^{-m}\cdot \mathcal OX|U
\]
Taking Laurent exapnsions
every section in the right hand side is of the form
\[
f+\frac{c_1}{z}+\ldots+\frac{c_m}{z^m}
\]
where $f\in \mathcal O_X$ and $\{c_\nu\}$ is an $m$-tuple of complex numbers.
Expressed by  sheaves it gives
an exact sequence
\[
0\to \mathcal O_X\to \mathcal O_X[*mp]\to S_p^m\to 0\tag{D.1}
\]
where $S_p$ is the scyscraper sheaf suppotet  by $\{p\}$
and
the stalk $S_p(p)$ is an $m$-dimensional vector space.
Passing to long exact sequence of cohomology the reader 
can verify that there is an exact sequence:
\[
0\to {\bf{C}}\to H^0(\mathcal O_X[*mp])\to
{\bf{C}}^m\to 
H^1(\mathcal O_X)\to H^0(\mathcal O_X[*mp])\to 0\tag{D.1.1}
\]
\medskip

\noindent
{\bf{D.2 Exercise.}}
Use that the vector space 
$H^1(\mathcal O_X)$ is $g$-dimensional and conclude that
\[
\dim_{{\bf{C}}}\, 
H^0(\mathcal O_X[*mp])=m-g+1+
\dim_{{\bf{C}}}\, 
H^1(\mathcal O_X[*mp])\geq m-g+1\tag{D.2.1}
\]
\medskip

\noindent
In particular the left hand side is $\geq 2$ if $m=g+1$
which means that
apart from constants, there exists at least one
constant global section in 
$\mathcal O_X[*(g+1)p]$.
Hence we have proved:

\bigskip

\noindent
{\bf{D.3 Theorem.}}
\emph{For every $p\in X$ there exists a non-constant 
meromorphic function $f$  in $X$ with no poles in
$X\setminus{p}$ while
the order of the pole at $p$ is at most $g+1$.}











\newpage



\centerline{\bf{Weierstrass' points.}}

\bigskip

\noindent
Let $X$ be a compact Riemann surface
whose genus number $g$ is $\geq 2$.
Removing  a point $p\in X$
we get  the space
$\mathcal O(X\setminus\{p\})$.
If $(U,z)$ is a chart centered at $p$
where $p$ corresponds to $z=0$, then every
$f\in\mathcal O(X\setminus\{p\})$
restricts to a holomorphic function in
the punctured disc
$0<|z|<1$
and we can regard its Laurent series:
\[
f(z)=
\sum_{\nu=1}^\infty\ c_\nu\cdot z^{-\nu}+\sum_{\nu\geq 0}\, d_\nu\cdot z^\nu
\]
The negative part of the Laurent series is denoted by $f_*(z)$.
If $f_*=0$ then $f$ is globally holomorphic and hence reduced to
a constant.
So 
\[
f\mapsto f_*(z)+ d_0
\]
yields an  injective 
map from $\mathcal O(X\setminus\{p\})$ 
into the space of
non-positive Laurent series at $z=0$.
We are going to study the range of this map.
Denote by $\mathcal L$
the space 
of all non-positive Laurent series, where we recall that a negative
series
\[
\sum_{\nu=1}^\infty\ c_\nu\cdot z^{-\nu}\in\mathcal L
\]
if and only if
\[
\sum_{\nu=1}^\infty\, |c_\nu|\cdot R^\nu<\infty
\] 
for all $R>0$.
In particular $\mathcal L$ contains the $g$-dimensional subspace
formed by Laurent series given by
finite series:
\[
\rho(z)= c_1z^{-1}+\ldots+c_g\cdot z^{-g}
\]
where $\{c_\nu\}$ is a $p$-tuple of complex numbers.
Let $\mathcal L[p]$ denote this subspace of
$\mathcal L$.
\medskip

\noindent
{\bf{E.1 Theorem.}}
\emph{Outside a finite set ${\bf{W}}$ in $X$
one has} 
\[ 
\mathcal L=\mathcal L[p]\oplus \mathfrak{Im}(\mathcal O(X\setminus\{p\})
\]
\medskip

\noindent
{\bf{E.2 Remark.}}
In ¤xx we show that
the exceptional set
${\bf{W}}$ is non-empty when $g\geq 2$,
If (*) holds above
it follows that when $m>g$
then  there exists a unique $g$-tuple $\{c_\nu\}$ such that 
\[ 
z^{-m}=c_1z^{-1}+\dots+c_gz^{-g}+ \mathfrak{Im}(\phi)
\]
where $\phi$ is holomorphic in
$X\setminus\{p\}$.
Herte the negative Laurent series of $\phi$ is finite
at $p$ which implies that
$\phi$ is a globally defined meromorphic function
with a pole of order $m$ at $p$ whose negative Laurent expnasion at $p$
is of the form
\[
z^{-m}+c_1z^{-1}+\dots+c_gz^{-g}
\]
where the $g$-tuple $\{c_\nu\}$ is uniquely determined and depends on
the chosen integer $m$.
At the same time
the direct dum in (*) entails that
there do not exist non-constant meromorphic functions
which are holomorphic in
$X\setminus\{p\}$ while the order of
the pole at $p$ is $\leq g$.
\medskip

\noindent
The proof of Theorem E.1 requires several steps.
We are given a point
$p\in X$ and let $(U,z)$ be a chart
around $p$ where $p$ corresponds to $z=0$.
Residue calculus gives
a $g$-tuple of 
currents defined by
\[
\rho_\nu=\bar\partial(z^{-\nu})\quad\colon\quad \nu=1,\ldots,g
\]
Each current is supported by the singleton set $\{p\}$
and extends to a current on $X$ supported by $p$.
If $\Psi^{1,0}\in\mathcal E^{1,0}(X)$
we can regard its restriction to $U$ and write
\[
\Psi^{1,0}|U= \psi(z)\cdot dz
\]
with $\psi\in C^\infty(U)$.
Residue calcluus teaches that
\[
\rho_1(\Psi^{1,0})= 2\pi i\cdot \psi(0)
\]
If $\nu\geq 2$ the reader may verify that
\[
\rho_\nu(\Psi^{1,0})= \frac{(-1)^{\nu-1}}{(\nu-1)!}\cdot
\partial^{\nu-1}\psi/\partial z^{\nu-1}(0)
\]
The construction of the $\rho$-currents
is not intrinsic, i.e.
the $g$-tuple  depends on the chosen chart around $p$.
But the reader can check that
the $g$-dimenbsional vector space
in $\mathfrak{c}^{0,1}(X)$
generated by
$\{\rho^\nu\,\colon 1\leq \nu\leq g\}$
does not depend on the chosen chart around $p$.
Let us denote it by $\mathcal W(p)$.
The major step towards the proof of Theorem E.1
is the following:


\medskip

\noindent
{\bf{E.3 Theorem.}} \emph{Outside a finite set
${\bf{W}}$  in $X$ one has
the direct sum decomposition}
\[
\mathfrak{c}^{0,1}(X)=\bar\partial(\mathfrak{Db}(X))\oplus\, \mathcal W(p)\tag{E.3.1}
\]
\bigskip

\noindent
\emph{Proof.}
The duality result in ¤ xx gives (E.3.1)
if
the $g$-tuple
$\{\rho^\nu\}$ restrict to 
${\bf{C}}$-linearly independent in the dual space
$\Omega(X)^*$.
To check when this holds we
consider a basis $\omega_1,\ldots,\omega_g$ in the $g$-dimensional vector space
$\Omega(X)$.
In a chart
$(U,z)$ centered at a point $p_0\in X $ we can write
\[
\omega_j= f_j(z)\cdot dz\tag{i}
\]
where Ê$\{f_j\}$ are ${\bf{C}}$-linearly 
independent in $\mathcal O(U)$.
The general result in ¤ xx  entails that 
the determinant function
\[
\mathcal F(z)= \det\bigl(\partial f_j^\nu/\partial z^\nu(z)\tag{ii}
\]
formed by the $g\times g$-matrix with
elements as above is not identically zero.
Now linear algebra shows that
$\{\rho_\nu\}$ restrict to linearly independent functionals
on $\Omega(X)$ at every $z|in U$ for ehich
$F(z)\neq 0$.
Since the zero set of $F$ in the chart $U$ is discrete
and we can cover
$X$ by a finite famliy of charts, it follows that
(E.3.1) holds outside a finite set
${\bf{W}}$.


\medskip

\noindent
{\bf{E.4 How to find ${\bf{W}}$.}}
In each  chart $(U,z)$ as above we have
the $\mathcal F$-functions from (ii).
If $(U_\alpha,z_\alpha)$ and $(U_\beta,z_\beta)$ is a pair of charts
in $X$ where $U_\alpha\cap U_\beta\neq\emptyset$
we get two $g$-tuples  of analytic functions by
\[
\omega_j|U_\alpha= f_j^\alpha\cdot dz\quad\colon\quad
\omega_j|U_\beta= f_j^\beta\cdot dz_\beta
\]
When $z_\beta=z_\beta(z_\alpha)$ is regarded as
an analytic function in $U_\alpha\cap U_\beta$ one has the equations
\[
f_j^\alpha=\frac{\partial z_\beta}{\partial z_\alpha}\cdot f_j^\beta\tag{E.4.1}
\]
for each $j$ in $U_\alpha\cap U\beta$.
\medskip

\noindent
{\bf{E.4.2 Exercise.}} Show by using
rules for calcuating determinsnts that
(E.4.1) gives
the equation
\[
\mathcal F_\alpha=\bigl(\frac{\partial z_\beta}{\partial z_\alpha}\bigr)^{g(g-1)/2}\cdot F_\beta(z)
\]
So with $N=g(g-1)/2$
the family $\{\mathcal F_\alpha\}$ which arises when
$X$ is covered by a finite number of charts, is a global section of
the $N$-fold product of the holomorphic line bundle $\Omega_X$.
By (xx) the
set of xeros counted with multiplicities  of every global section
in $\Omega_X$ is equal to $2(g-1)$.
So by the general result in ¤ xxx the
zero set of the $\mathcal F$-family counted with multiplicities is equal to
$g(g-1)^2$. Since $g\geq 2$ this is a positive integer and hence
the set ${\bf{W}}$ is non-empty.
\bigskip

\noindent
{\bf{Remark.}} In the literature one refers to
${\bf{W}}$ as the set of Weierstrass' points in $X$.
The determination of ${\bf{W}}$ for a given $X$ with genus $\geq 2$
is in general not easy.
From the above ${\bf{W}}$ contains at most
$(g-1)^2\cdot g$ many distinct points. 
In general the number of points can be
strictly smaller.
Weierstrass investigated
${\bf{W}}$ for special families of compact Riemann surfaces.
See ¤ xx for some comments.
\bigskip

\centerline {\bf{Proof of Theorem E.1}}

\bigskip

\noindent
Consider a point $p\in X$ which is outside ${\bf{W}}$ and let $(U,z)$ be a chart 
centered at $p$.
Let $U^*=U\setminus\{p\}$ be the punctured open disc.
In $X$ we also have the open set
$X\setminus\{p\}$
which can be regarded as an open Riemann surface.
The theorem by Behnke and Stein from
the chapter devoted to open Rieann surfaces
gives
$H^1(X\setminus\{p\},\mathcal O)=0$.
The cohomology in the  disc $U$ is also zero.
Hence the open covering of $X$ given by the pair
$\mathfrak{U}= (U,X\setminus\{p\})$
is acyclic with respect to the sheaf
$\mathcal O_X$. So  Leray's acyclicity theorem gives
\[
H^1(X,\mathcal O_X)\simeq \frac{\mathcal O( U^*)}{
\delta(C^0(\mathfrak{U},\mathcal O_X))}\tag{i}
\]
where
\[
\delta\colon \mathcal O(U)\oplus \mathcal O(X\setminus\{p\})\to
\mathcal O(U^*)
\] 
is the Cech coboundary map.
Next, the $g$-tuple $\{z^{-\nu}\colon \nu=1,\ldots,g\}$
are holomorphic in $U^*$
and  their images in the right hand side from (i) give
elements in
$H^1(X,\mathcal O_X)$ denoted by
$\{[z^{-\nu}]\}$.
\medskip

\noindent
{\bf{Exercise.}}
Recall  that
\[
H^1(X.\mathcal OX)= \frac{\mathfrak{c}^{0,1}}{\bar\partial(\mathfrak{Db}(X)}
\]
Since $p$ is outside ${\bf{W}}$
the last quotient is equal to $\mathcal W(p)$.
Conclude from this that
the $g$-tuple
$\{[z^{-\nu}]\}$ is a basis in the $g$-dimensional vector space
$H^1(X,\mathcal O_X)$.
\medskip

\noindent
Let us then consider some
$g\in\mathcal O(U^*)$ which has a  Laurent series
\[
g(z)= \sum_{\nu=1}^\infty\ c_\nu\cdot z^{-\nu}+
\sum_{\nu=0}^\infty\ d_\nu\cdot z^{\nu}
\]
By the Exercise  there exists
a unique $g$-tuple of complex numbers
$a_1,\ldots,a_p$
such that
the image of $g$ in
$H^1(X,\mathcal O_X)$ is equal to $\sum\, a_\nu\cdot [z^{-\nu}]$.
Hence (i) gives a pair $\phi(z)\in\mathcal O(U)$ and $f(z)\in \mathcal O(X\setminus\{p\}$
such that
\[
g(z)-\sum\,\rho_\nu\cdot z^{-\nu}=\phi(z)+f(z)
\]
where $\phi(z)\in\mathcal O(U)$ and $f(z)\in \mathcal O(X\setminus\{p\}$.
Regarding the negative Laurent series it follows that
\[
g_*(z)= \sum\, a_\nu\cdot z^{-\nu}+f_*(z)\tag{ii}
\]
Here $g$ was arbitrary in
$\mathcal O(U^*)$ and hence the proof of Theorem E.1 is finished.
















\newpage










 
 
 
 

\centerline{\bf{F. Abel's theorem.}}



\bigskip


\noindent
A divisor $D$ on $X$ consists of
an assignement of integers $\{\mu_\nu\}$ to a finite set of points $\{p_\nu\}$
in $X$. One writes
\[
D= \sum\, \mu_\nu\cdot \delta(p_\nu)
\]
The $\mu$-integers may be positive or negative.
The degree is defined by
\[
\deg D= \sum\,\mu_\nu
\] 
while the finite set $\{p_\nu\}$ is called the support of $D$.
Next we construct a class of 1-currents.
In general, let $\gamma\colon [0,1]\to X$
be an $X$valued function on the closed unit interval
We assume that $\gamma$ is continuous and has a
finite total variation. The last condition means that
there exists a constant $C$ such that
\[
\sum_{\nu=0}^{\nu=N-1}\, d(\gamma(t_{\nu+1},\gamma(t_\nu)\leq C
\]
for all sequences $0=t_0<t-1<\ldots<t_N=1$
Here $d$ is some  distance function 
on $X$ regarded as a metric space which in charts
is equivsoent to
the euclidian distance.
Every such $\gamma$ gives a current of degree one
acting on $\mathcal E^1(X)$ by 
\[
\alpha\mapsto \int_\gamma \,\alpha\tag{*}
\]
\medskip

\noindent
{\bf{Exercise.}} Explain how the classical Borel-Stieltjes integrals for functions
with bounded variation
defines the integral in the right hand side.
Show also that
\[
\int_\gamma\, dg= g(\gamma(1))-g(\gamma(0))
\]
hold for every $g\in\mathcal E()$.
One refers to (*) as an integration current of degree one.
More generally we can take a finite sum of such
currents and get the integration current
$\Gamma$ defined by
\[
\Gamma(\alpha)= \sum\, \int_{\gamma_j}\,\alpha
\]
Let $D=\sum\,\mu_\nu\cdot \delta(p_\nu)$ be a divisor of
degreee zero.
An integration current $\Gamma$ is said to be associated with
$D$ if the equality below hold for every
$g\in\mathcal E(X)$:
\[
\Gamma(dg)= \sum\, \mu_\nu\cdot g(p_\nu)
\]
\medskip

\noindent
{\bf{F.1 Principal divisors.}}
Let $f$ be a non-constant meromorphic function.
Now we have the finite set of poles $\{p_\nu\}$ and the finite set of zeros
$\{q_j\}$.
We associate the divisor
\[
\text{div}(f)= \sum\, \mu_k\cdot \delta(p_k)-\sum\, \mu_j\cdot \delta(q_j)
\]
Here $\mu_k$ is the order of the pole of $f$ at every $p_\nu$, while
$\mu_j$ is the order of a zero at $q_j$.
By the result in ¤ xx this divisor has degree zero.
A divisor $D$ of degree zero is called principal if
it is equal to $\text{div}(f)$ for some
$f\in\mathcal M(X)$.
Notice that if $f$ and $g$ is a pair of non-constant meromorphic functions such that
$\text{div}(f)= \text{div}(g)$, then
$f/g$ is a holomorphic function on $X$ and hence reduced to a non-zero constant.
Introducing the multiplicative group
$\mathcal M(X)^*$ of non-constant meromorphic functions
this means that one has an injective map
\[
\frac{\mathcal M(X)^*}{{\bf{C}}^*}\to\mathcal D_0
\]
where $\mathcal D_0$ is the additive group of divisors whose degree are zero.
The  theorem below describes the range of this map.

\medskip

\noindent
{\bf{F.2 Theorem.}}
\emph{A divisor $D$ of degree zero
is principal if and only if there
exists an integration current $\Gamma$ associated with
$D$  such that}
\[
\Gamma(\omega)=0\quad\colon \,\,\gamma\in \Omega(X)
\]
\medskip

\noindent
The proof requires several steps.
First we shall show the "if part", i.e. if 
$\Gamma$ exists so that (*) holds then
the divisor $D$ is principal.
To achieve this we first
perform a local construction in the complex plane.
\medskip

\noindent
{\bf{F.3 A class of currents in ${\bf{C}}$.}}
In the complex $z$-plane we consider
a point $z_0$ where 
\[
0<|z_0|<r<1
\]
holds for some $0<r<1$.
It is easily seen that there exists
a $C^\infty$-function $a(z)$  in ${\bf{C}}$
which never is zero and the function
\[
\phi(z)= \frac{z}{z-z_0}\cdot a(z)
\]
is identically one when
$|z|\geq r$.
Now $z\mapsto \frac{1}{z-z_0}$ is locally integrable around
$z_0$ and hence $\phi$ belongs to 
$L^1_{\text{loc}} ({\bf{C}})$ and is therefore a distribution.
\medskip

\noindent
Cauchy's residue formula can be expressed by saying
the $\bar\partial$-image of the $\frac{1}{z}$
is equal to the $(0,1)$-current
$2\pi i\cdot \delta(0)d\bar z$ where $\delta(0)$ is the Diraqc distribution
at the origin.
Using this the reader can check that
\[
\bar\partial(\phi)=
 \frac{z}{z-z_0}\cdot \bar\partial(a)+z_0a(z_0)\cdot \delta(z_0)d\bar z\tag{i}
 \]
 from (i) the reader should also check that
 \[
 \phi^{-1}\cdot \bar\partial(\phi)= a^{-1}\cdot \bar\partial(a)\tag{ii}
 \]
 \medskip
 
 \noindent
 {\bf{F.4 The current $\phi^{-1}\cdot \partial(\phi)$.}}
 To begin we one has
 \[
 \partial(\phi)=\frac{a(z)}{z-z_0}\cdot dz-
 \frac{za}{(z-z_0)^2)}\cdot dz+\frac{z}{z-z_0}\cdot \partial a\tag{F.4.1}
 \]
 Above $(z-z_0)^{-2}$ is the principal value distribution
 defined as in ¤ xx.
 \medskip
 
 \noindent
 {\bf{ Exercise.}}
 Use (F.4.1) to establish the equation
 \[
 \phi^{-1}\cdot \partial(\phi)=z^{-1}\cdot dz-(z-z_0)^{-1}\cdot dz+
 a^{-1}\cdot \partial(a)\tag{F.4.2}
 \]
 \medskip
 
 \noindent
 {\bf{Exercise.}}
 Use Stokes Theorenm and Cauchy's residue fornula to
 prove that when the 1-current
 \[
 \phi^{-1}\cdot d\phi=  \phi^{-1}\cdot \partial(\phi)+ \phi^{-1}\cdot \bar \partial(\phi)
 \] 
 is applied to $dg$ for some
 $g\in C_0^\infty({\bf{C}}$, then
 \[
 \phi^{-1}\cdot d\phi<dg>\, = 2\pi i\cdot (g(0)-g(z_0)\tag{F.4.3}
 \]
\medskip


\noindent
 Let us now consider an integration current
 $\Gamma$ given by a finite sum
 $\sum\,\gamma_j$ where each $\gamma_j$ has compact support in
 a chart
 $(U_j,z_j)$ in $X$ and the end-points of
 $\gamma_j$ are $z_j=0$ and $z_j=z_j^*$
 with $0<|z_j^*|<r<1$ and $U_j$ is a chart defined by
 $\{|z_j|<1|]$.
In $X$ the point $z_j=0$ is denoted by $q_j$ while $z_j^*$ corresponds to a
point $p_j$.
It follows that 
 \[
 \int_\Gamma \, dg=\sum_{j=1}^{j=N}\, g(p_j)-g(q_j)\tag{F.5}
 \]
for every $g\in \mathcal E(X)$.
 Next, for each $j$ we apply the local contruction the chart
 and find a function
 $\phi_j$ in $X$ which is identically one
 in $X\setminus \{|z_j|\leq r\}$ such that 
 \[
 \phi_j^{-1}\cdot d\phi_j<dg>=2\pi i\cdot \int_{\gamma_j}\, dg\quad\colon\, g\in \mathcal E(X)
 \]
 More generally, since
 $d$-closed 1-forms in the chart $U_j$ are $d$-exact the re4ader should check that
 (F.5) implies that
 \[
 \phi_j^{-1}\cdot d\phi_j<\alpha>=2\pi i\cdot \int_{\gamma_j}\,\alpha\tag{F.6}
 \]
 hold for every $d$-closed differential 1-form $\alpha$.
 Let us now consider the function
 \[
 \Phi= \prod_{j=1}^{j=N}\, \phi_j
 \]
 \medskip
 
 \noindent
 {\bf{F.7 Exercise.}}
 From the above the
 reader should check  that
 the construction of the $\phi$-functions imply that
 $\Phi$ is a zero-free
 $C^\infty$-function
 in $X\setminus \{q_j,p_j\}$, i.e. in the open complement of
 the finite set
  which is the union of these   $q$  and  $p$ points.
Moreover,  additivity for logarithmic derivatives and 
(F.6) above gives
\[
\Phi^{-1}\cdot d\Phi<\alpha>=
\int_\Gamma\, \alpha\tag{F.7.1}
\]
for every $d$-closed 1-form
$\alpha$. Finally, show that
\[
\Phi^{-1}\cdot \bar\partial(\Phi)=
\sum\, a_j^{-1}\cdot \bar\partial(a_j)\tag{F.7.2}
\]
where the right hand side is a smooth $(0,1)$-form.
\medskip

\noindent
{\bf{F.8 A special case.}}
Suppose that $\Gamma$ is such that
\[
\int_\Gamma\, \omega=0\quad\colon\quad \omega\in\Omega(X)\tag{F.8.1}
\]
The equality in (F.7.1) applied to  $d$-closed holomorphic 1-forms
and
Theorem ¤ xx  entail  that
the smooth $(0,1)$-form
$\Phi^{-1}\cdot \bar\partial(\Phi)$ from (F.7.2) is $\bar\partial$-exact.
Thus, we can find $G\in \mathcal E(X)$ such that
\[
\bar\partial(G)= \Phi^{-1}\cdot \bar\partial(\Phi)\tag{F.8.2}
\]
\medskip


\noindent
{\bf{Exercise.}}
Put
\[
\Psi=e^{-G}\cdot \Phi
\]
deduce from the above  that
$\bar\partial(\Psi)=0$ holds in
$X\setminus \{q_j,p_j\}$ and hence $\Psi$ is holomorphic in
this open subset of $X$
Show also  that the local constructions of the
$\phi$-functions inside the charts
$\{U_jz_j\}$ entail  that
$\psi$ extends to a mermorphic function in
$X$ whose princial divisor is equal to
\[
\sum\, \delta(q_j)-\sum \delta(p_j)
\]
Funally the reader should confirm that the constructions above
prove the "if part" in Theorem F.2.
\medskip


\centerline{\emph{F.9 Proof of the "only if part"}}
\medskip

\noindent 
Here we are given a non-constant meromorphic funvtion
$f$.
We shall condtruct an integration chain $\Gamma$ as follows:
Frst $f\colon X\to {\bf{P}}^1$ is a holomorphic map.
With $s=f(x)$
we recall from (xx) that the number critical $s$-points in
the complex $s$-plane is finite.
In ${bf[P})^1$ we choose a simple
curve $\gamma_*$ with intial point at $s=0$ and end-point at
$s=|nfty$, while
$\gamma_*$ avoids the critical points $s\neq 0$ in
${\bf{C}}$.
of course, while this is done we can choose
$\gamma_*$ so that it is a smooth curve
on the $C^\infty$-manifold ${\bf{P}}^1$.
\medskip

\noindent
{\bf{The inverse image $f^{-1}(\gamma_*)$.}}
Let $N=\deg(f)$.
Since $\gamma_*$ avoids $f$-cirtical points we see that
\[
f^{-1}(\gamma_*\setminus \{0,\infty\})= \gamma_1\cup\ldots\cup\,\gamma_N
\]
where $\{\gamma_j\}$ are disjoint  curves in
$X$, each of which is oriented via
$\gamma_*$ which from the start moves from
$s=0$ to $s=\infty$.
\medskip

\noindent
{\bf{Exercise.}}
Show that the closure $\bar\gamma_j$ yields a rectifiable  curve
whose initial point is zero of $f$ and the end-point a pole.
Put
\[
\Gamma=\sum\, \bar\gamma_j
\]
and conclude from the above that
$\Gamma$ is associated to the principal divisor of $f$.
The proof of the "onmy if part" is therefore finished if we show that
\[
\int_\Gamma\,\omega=0\quad\colon\quad \omega\in \Omega(X)\tag{*}
\]
To prove (*) we shall  use
a certain trace map.
First, a holomorphic 1-form
$\omega$ on $X$ is regared as a $\bar\partial$-closed current with
bi-degree $(0,1)$.
Since the amp $f\colon X\to {\bf{P}}^1$ is proper
there exists the direct image current
$f_*(\Omega$ and we recal from general facts that
the passage to direct image currents commute with
the $\bar\partial$-operator.
hence $\bar\partial(f_*(\Omega))==$ and since
$\bar\partial$ is elliptic it follows that
$f_*(\omega)$ is a holomorphic 1-form on
${\bf{P}}^1$.
By the result in Exercise xx there does not exist non-zero globally defined
holomorphic 1-forms on the projective line.
hence
\[ 
f_*(\omega)=0\tag{**}
\]
In partocuar we have
\[
\int_{\gamma_*(\epsilon)}\, f_*(\omega)=0
\]
where $\gamma_*(\epsilon)$ is the closed 
curve given by $\gamma$ intersected with
$\{\epsilon\leq |s| \leq \epsilon^{-1}\}$
for a small $\epsilon>0$.
\medskip

\noindent
{\bf{Exercise.}}
Put $\Gamma(\epsilon)= f^{-1}(\gamma(\epsilon)$
and dediuce from (xx) that
\[
\int_{\Gamma(\epsilon)}\, \omega=0
\]
Finally, pass to the limit as $\epsilon\to 0$ and conclude that (*) holds which finishes the proof of
the "only if part".



 
 
 
 \newpage
 
 \centerline{\bf{G. Holomorphic line bundles.}}
 
 
\bigskip

\noindent
There exists the multiplicative sheaf
$\mathcal O_X^*$ whose sections are zero-free
holomorphic functions.
every such function is locally $e^g$ with $g\in \mathcal O_X$
where $g$ is determined up to an integer multiple of $2\pi i$.
This gives an exact sheaf sequence
\[
0\to {\bf{Z}}_X\to \mathcal O_X\overset{\exp}\to \mathcal O^*_X\to 0
\]
where $\exp$ sends $g$ to $e^{2\pi i g}$
and ${\bf{Z}}_X$ is the sheaf of locally constant  integer-valued functions on
$X$.
Notice that global sections in
$\mathcal O_X^*$ are reduced to non-zero complex numbers
and we have the short exact sequence
\[
0\to {\bf{Z}}\to {\bf{C}}\overset{\exp}\to {\bf{C}}^*\to 0
\]
Conclude that one has an exact sequence
\[
0\to H^1({\bf{Z}}_X)\to H^1(\mathcal O_X)\to
H^1(\mathcal O_X^*)\to H^2({\bf{Z}}_X)\to 0\tag{G.1}
\]
As explained in ¤ xx
the cohomology group $H^1({\bf{Z}}_X)$
is a free abelian group of rank $2g$
while
$H^2({\bf{Z}}_X)={\bf{Z}}$.























 
 

 
 
 
 
 
 
 
 

\newpage











\centerline{\bf{Compact Riemann surfaces.}}

\bigskip

\noindent
A compact Riemann surface
$X$ is by definition a connected and compact
complex analytic manifold of dimension one.
The maximum principle for holomorphic functions entails that
every globally defined holomorphic funtions on $X$
is a  constant.
Thus, $\mathcal O(X)$ is reduced to the complex field.
But if one allows poles we shall learn that there exist non-constant
meromorphic functions
on $X$. They give a field denoted by
$\mathcal M(X)$ whose properties will
be investigated later on.
The projective line ${\bf{P}}^1$
over the complex field is an example of a compact Riemann surface.
Topologically it is homeomorphic to
a where and as a module one takes the
As a model one starts with the complex $z$-plane and adds the point at
infinity. Now $\mathcal M({\bf{\P}}^1)$
becomes the field of rational functions of
the single complex variable $z$.
Other compact Riemann urfaces
arise when one starts from
an irreducible polynomial $P(x,y)$
of two independent variables, i.e.
$P$ is irreducible in the unique factorisation domain
${\bf{C}}[x,y]$.
We shall learn how to find the associated compact
Riemann surface $X$ where $\mathcal (X)$
is isomorphic to the quotient field of the integral domain
$\frac{{\bf{C}}[x,y)}{(P)}$
where $(P)$ denotes the princial ideal generated
by $P$.
As an example we take
\[
P(x,y)= y^3-x^3-1
\]
To get $X$ one first regards the
algebraic curve in ${\bf{C}}^2$ defined by
$\{P=0\}$.
Since the complex gradient
vector $(P'_x,P'_y)= (3x^2,3y^2)\neq (0,0)$
it follows that $\{P0=\}$ is non-singular
and therefore brcomes an embedded one-dimensional complex manifold
in
${\bf{C}}^2$.
To get a copmpact complex manifold one regards the
prjective curve in ${\bf{P}}^2$
with its inhomogeneous coordintes
$(\zeta,x,y)$
where the zero set of $P^*(\zeta,x,y)= y^3-x^3-\zeta^3$
yields a projective curve $S$.
We shall learn  that $S$  is non-singular
and therefore gives a compact Riemann surface.
Less obvious is that
$S$ regarded as a topological space is
homeomorphic to
the oriented real manifold
$T^2$, where $T^2$ denotes the 2-dimensional torus.
The reason why $S\simeq T^2$ as a topoligcal space is that
$\mathcal M(S)$ contains
a meromorohiuc function $u$
which has one double pole and two simple zeros on
$S$ and is otherwise holomorphic without zeros.
An example of such a meromorphic function is
\[
u=\frac{1}{y-x}
\]
whose properties as a meromorphic function on
$S$ will
be described in ¤ xx.
\medskip
\noindent
In ¤ xxx we
expose the pioneering work
by Hermann Weyl devoted to "abstract" Riemann surfaces which
in particular prove
the existence of non-constant
meromorphic  functions. 
From this Weyl deduced that
$\mathcal M(X)$ is a so called algebraiuc functon field, i.e.
as a filed extension over
${\bf{C}}$ the degree of trancendency is one
and in addition it is finitely generated.
Using the existence of primitive elements in
finite algebraic extensions of fields in characterstic zero
it follows that $\mathcal M(X)$
is isomorphic to the quotoent field of an integral domain
\[
\frac{{\bf{C}}[x,y]}{P(x,y)}
\]
where $P(x,y)$ is an irreducible polynomial in
the unique  factorisation domain ${\bf{C}}[x,y]$.
So every compact
Riemann surface arises from an irreducible
polynomial $P(x,y)$. 
A remarkable fact is that
a compact Riemann surface $X$ is determiuned by
the field $\mathcal M(X)$.
More precisely, let $Y$ be another compact Riemann surface
and assume that there exists a ${\bf{C}}$-linear isimorohism
\[
\rho\colon \mathcal M(X)\to \mathcal M(Y)
\]
Thus, the two algebraic function fields are isomorphic.
In ¤ xx we show that
$X$ and $Y$ are isomorphic
as complex manifolds, i.e.
$\rho$ yields a \emph{biholomorphic map}
from $X$ to $Y$.
\medskip

\noindent
{\bf{Non-compact Riemann surfaces.}}
In addition to compact Riemann surfaces there  exist
open -or non-compact- Riemann surfaces $X$. It means that
$X$ is a connected but non-compact complex manifold of dimension one.
In this case it turns out
that
$\mathcal O(X)$ contains a quite extensive
 family of non-constant functions.
In ¤ xx we expose  results due to Behnke and Stein about
non-compact Riemann surfaces which
for example show that one can prescribe zeros and poles
in an arbitrary fashion and
which correspond to a globally defined meromorophic function on
$X$, i.e $\mathcal M(X)$ is so to speak "optimally ample".
In ¤ xx we also expose the \emph{Uniformisation Theorem}
where our proof follows that
of  
Behnke  and Stein. It implies for example that
every simply connected open Riemann surface is either
biholomorphic to the open unit disc or the complex plane.
The  uniformisation theorem for
connected  open
subsets $\Omega$ of the complex $z$-plane
deserve special attention.
More precisely, if $\Omega\subset{\bf{C}}$ is
open and connected and the complement contains at least two points, then
there exists a holomorphic map
\[
\phi\colon D\to \Omega
\]
where $D$ is the open unit disc, and
$\phi$ has the following two properties: First
it is surejctive, i.e. $\phi(D)=\Omega$ and moreover it is locally
conformal, i.e. the complex derivative
$\phi'(z)$ has no zeros.
In ¤ xx we shall learn that this entails that thr universal covering space of
$\Omega$ is homeomorphic to the open unit disc which is 
achieved via the  locally biholomorphic map $\phi$.
The uniformisation theorem for planar domains
is due to Hermann Schwarz who adopted Riemann's methods for
simple connected domains and is 
be exposed in ¤ xx
in connection with Riemann's ordinary conformal mapping theorem for
simply connected planar domains.
Even though Schwarz's Uniformisation Theorem can be deduced via
the general case treated by Behnke and Stein, it is instructive to pursue
his original proof which only relies upon analytic function theory.
As expected it is in general very hard to
obtain explicit formulas. 
An example is when
$\Omega$ is the open complement of
${\bf{C}}$ where one has removed
three disjoint closed intervals
$\{[a_\nu,b_\nu]\}$ where
$a_1<b_1<a_2<b_2<a_3<b_3$.
See ¤ xx for a discussion related to this case.
\bigskip



\centerline{\bf{About methods of proofs.}}
\medskip

\noindent
The study of Riemann surfaces offer instructive lessons in sheaf theory since
various sheaves
appear in a natrual fashion. The reader is supposed to be familiar with
basic facts about sheaves and their cohomology. But for less experienced readers we
add an appenbdix where
som fundamental reults from Leray's   pioneering article
\emph{xxxx} are resumed. Let us also 
remark that even if Weierstrass never
introduced the notion of sheaves, his construction of
"sheaf spaces" attached to in general multiu.valued abnalytic functions
gave the first  exampe of sheaves.
In addition to sheaf theory we employ calculus on manifolds without
hesitation.
For example. let $M$ be an oriented  real $C^\infty$-manifold of some dimension
$n\geq 2$. To say that $M$ is oriennted means that
there exists a globally defined differential $n$-form
which never vanishes and choosing the orientation
one can define integrals
\[
\int_M\, \omega\quad\colon\quad \omega\in \mathcal E^n(M)
\]
where $\mathcal E^n(M)$ is the space of 
$n$-forms with $C^\infty$-.coefficients.
More generally there exist to each
$0\leq p\leq n$ the space
$\mathcal E^p(M)$ of differential $p$-forms
with $C^\infty$-coefficients.
Under the condition that $M$ can be covered by a denumarable family of compact subsets
it follows  that
$\mathcal E^p(M)$ is equipped with a topology so that it
becomes a Frechet spaces.
There also exists the spaces
$\{\mathcal E^p_0(M)\}$
which consist of differential forms having compact support in
$M$.
The dual of
$\mathcal E^p_0(M)$ is denoted by
$\mathfrak{c}^{n-p}(M)$ and its elements are called currents of
degree $n-p$.
in particular $\mathfrak{c}^0(M)$ is the space of distributions on
$M$ and is often denoted by
$\mathfrak{Db}(M)$. Thus, by definition
\[
\mathfrak{Db}(M)\simeq \mathcal E^n_0(M)^*
\]
where (*) indicates that one regards the dual space.
We assume that the reader is famiiar with basic distribution theory which for
example is coveed in Hšrmander's text-book
[xx], where the passage to manifolds and currents 
become  trivial using charts on $C^\infty$-manifolds and $C^\infty$-partitions  of the unity.
Even if we shall not study manifolds of dreal dimension $\geq 3$
we recall some classic facts about oriented and compact $C\infty-$manifolds
Let $M$ be a such a manifold of siome dimension $n\geq 2$.
using exterior differentials one
has a complex
\[
0\to \mathcal E^0(M)\to \mathcal E^1(M)\to\ldots\to \mathcal E^n(M)\to 0
\]
Here
\[
d\colon \mathcal E^p(M)\to \mathcal E^{p+1}(M)
\] 
are continuous for every $p$, where we recall that
every $\mathcal E^p(M)$ is a Frechet space.
A fundamental fact is that the images of the $d$-maps above
are closed and have finite codimension.
Ths can be proved in several ways. The most convincing proof is due to
AndrŽ Weil who also established that
every compact and oriented manifold $M$ can be tringulated
via  a finite simplicial complex.
So readers interested in algebraic topology should  consult Weil's
original proof which teaches a good lesson
dealing with
topology and triangulations of manifolds.
Now one introduces the cohomology spaces
\[
H^p(M)= \frac{\text{Ker}_d(\mathcal E^p(M)}{d\mathcal E^{p-1}(M)}\quad\colon 0\leq p\leq n
\]
In particular $H^0(M)$ is the $d$-kernel on $C^\infty(M)$ and hence the
1-dimensional space of constant functuons.
One has also the complex of currents:
\[
0\to \mathfrak{c}^0(M)\to \mathfrak{c}^1(M)\to\ldots\to \mathfrak{c}^n(M)\to 0\tag{**}
\]
It is denoted by
$\mathfrak{c}^\bullet$.
For every $p$ one has the inclusion $\mathcal E^p(M)\subset\mathfrak{c}^p(M)$ 
and hence  Hence 
(*) above is a subcomplex of (**).
Next, the  contruction of currents and their exterior differentials, togehter eith
the closed range of the differentials in (*), 
give
a natural  duality
\[
H^p(M)^*\simeq \frac{\text{Ker}_d(\mathfrak{c}^{n-p})}{
d(\mathfrak{c}^{n-p-1}(M)}= H^{n-p}(\mathfrak{c}^\bullet)
\]
In addition to this
the fact that $M$ admits a triangulation implies that
the complexes (*) and (**) are quasi-isomorphic.
Hence the right hsnd side in (**) can be identfied with
$H^{n-p}(M)$, i.e. the dual of $H^p(M)$ is
equal to th cohomology space in degree $n-p$.
This is referred to as PoincarŽ duality theorem for compact
and oriented  manifolds.















\medskip

\noindent
{\bf{Some examples when $n=2$.}}
Let $M$ be an oriented  $C^\infty$-manifold of dimension two.
Since $M$ can be covered by a finite family of
charts  we can equip $M$ with a distance function
$d$ whose restriction to charts is equivsrnt to ordinsty euclidian metroc.
Every pair of such distance functions
$d_1$ and $d_2$ are equivalent in the sense that
there exists a constant $C>0$ such that
\[
C^{-1}|cdot d_2(p,q)\leq d_1(p,q)\leq C\cdot d_2(p,q)
\]
hold for every pair $p,q$ in $M$.
Next, a  parametrized curve
on $M$ is a map $\gamma\colon [0,1]\to M$
which is continuous.
Using a metric as above we can impose the
extra condition that
$\gamma$ has a bounded variation, i.e. there exists a constant $C$ such that
\[
\sum_{\nu=0}^{\nu=N-1}\, d(\gamma(t_{\nu+1}),\gamma(t_\nu)\leq C\tag{i}
\]
for all partitions
$0=t_0<t_1<\ldots<t_{N-1}<t_N=1$.
When (i) holds  there exist ordinary Borel-Stieltjes' integrals
\[
\int_\gamma\, \psi^1\tag{*}
\] 
for every differential 1-form $\psi^1$ with $C^\infty$-coefficents.
This gives a continuous  functional on
$\mathcal E^(M)$ with compact support and hence a current of
degree 1, called 
the integration current associated with
$\gamma$. This "operative construction" will
be used at many places later on.
One merit is that  "nasty geometric pictures"
when $\gamma$ for example has self-intersections
can be ignored while one
treats its associated integration current.
The case when $\gamma$ is closed, i.e. when
$\gamma(1)=\gamma(0)$ 
leads to special results. To begin with
we notice that
the equality $\gamma(0)= \gamma(1)$ entails that
\[
\int_\gamma\, dg=0\quad\colon\quad g\in \mathcal E(M)
\]
This is expressed by saying that the current
$\int_\gamma$ is $d$-closed.
A crucial result which follows from
the fact that
every distribution in ${\bf{R}}^2$ has  locally primitive distributuions with
respect to the pair of euclidian coordinates in
${\bf{R}}^2$, entails that
the following complex vector spaces are isomorphic
\[
\frac{\text{Ker}_d(\mathcal E^1(M)}{d(\mathcal E^0(M)}\simeq
\frac{\text{Ker}_d(\mathfrak{c}^1(M)}{d(\mathfrak{Db}(M)}\simeq
H^1(M)
\]
where the last term is the cohomology space in degree one on $M$.
This entials that if $\gamma$ is a closed and rectifiable curve 
then there exists a $d$-closed 1-form
$\phi\in \mathcal E^1(M)$ and a distribution $\mu$ such that
\[
\int_\gamma=d(\mu)+\phi^1\tag{*}
\]
where this equality takes place in
$\mathfrak{c}^1(M)$.
Moreover, the $d$-closed 1-form $\phi^1$ is
unique up to
an exact smooth 1-form.
With $\gamma$  regarded as a linear functional on
$\mathcal E^1(M)$ the reader should check that
(*) gives the equality
below for every $d$-closed $\psi^1\in\mathcal E^1(M)$:
\[
\gamma(\psi^1)= \int_M\, \phi^1\wedge \psi^1
\]
\medskip

\noindent
{\bf{The $d$-closed current $\int_{\partial\Omega}$.}}
Let $\Omega$ be a connected open set in $M$
whose boundary $\partial\Omega$ is regular in the sense of
Federer. It means that
there exists a (possibly empty) closed set
$\Sigma\subset\partial\Omega$ whose 1-dimensional Haussdorff measure is zero
while 
$\partial\Omega_*=\partial\Omega\setminus \Sigma$
is locally simple and rectifiable.
That is. for each $p\in\partial\Omega_*$ there exists
a bijective map $\gamma$ from the
closed unit intervalÊ$[0,1]$
to
a connected
subset of $\partial\Omega_*$
where $p=\gamma(1/2)$ while the distinct end-points
$\gamma(0)$ and $\gamma(1)$ stay in
$\partial\Omega_*$.
The orientation  along$\partial\Omega_*$ is given by the rule of thumbs
which appears
in the classic version of
Stokes Theorem as found already by Archimedes.
The extra the  condition is that the total variation, or equivalently the
arc-length measure of
$\partial\Omega_*$ is finite while it is evaluated with
respect to a local euclidian distance function, is finite.
Under these conditions one has
\[
\int_\Omega\, d\phi= \int_{\partial\Omega_*}\, \phi
\]
for each $\phi\in \mathcal E^1(M)$.
In particular the 1-current defined via the right hand side is $d$-closed.
Notice that we do not assume that
$\partial\Omega$ is connected.
\medskip

\noindent









\noindent
{\bf{Direct images of currents.}}
Let $\rho\colon M\to N$
be a $C^\infty$-map from $M$ to another oriented 
and compact 2-dimensional manifold $N$.
Elie Cartan's
construction of differential forms on manifolds give for
each $\phi\in\mathcal E^1(N)$ a pullback
$\rho^*(\phi)\in \mathcal E^1(M)$.
The map  is continuous when $\mathcal E^1(N)$ and
$\mathcal E^1(M)$ are equipped with
their standard Frechet topologies.
In particular we regard a
parametrized curve
$\gamma$ and obtain 
a 1-current
$\rho_*(\gamma)$ on $N$ defined by
\[
\rho_*(\phi)= \int_\gamma\, \rho^*(\phi)
\]
Later on we shall use  such direct images of currents at several places.
The reader  should "accept" that it is often  more profitable to
ignore "intuitive genetroic pictures" while calculations 
are performed.
An extra merit is  that
while the integrals along the  $\gamma$ is computed, then
calcluus teaches that one can employ
different parametrisatiin  along $\gamma$. as long as they
have bounded variation and preserve the given orientation.
Notice that even if $\gamma$ from the start is a simple Jordan arc, it
may occur that $\rho_*(\gamma)$
has a more involved structure  since
the restriction of the map $\rho$ to $\gamma$ need not be
one-to-one.
\medskip


\noindent
{\bf{Intersection numbers.}}





If $\rho $ is another  closed and rectifiabsle curve we have a
similar decomposition
\[
\int_\rho=\psi^1+d(\nu)
\]
Stokes Theorenm entials that
\[
\int_M\, \phi^1\wedge \psi^1\tag{*}
\]
is independent of the chosen decompostions.
So the complex number in (*) depends only upon the ordered
pair of closed curves
$(\gamma,\rho)$ and  is denoted by
$\mathfrak{i}(\gamma,\rho)$ and called the intersection number of the closed curves.
Elementaty calculus shows
that the intersection number always in an integer,
and by continuity it follows that
if $\gamma$ and $\gamma^*$ are two homotopic closed curves
then
$\mathfrak{i}(\gamma,\rho)=
\mathfrak{i}(\gamma^*,\rho)$ for every other closed curve
$\rho$.









Following original work by Riemann one
regards
specific simple closed curves
$\gamma_1,\ldots,\gamma_{2g}$ which give
a free basis for the fundamental group $\pi_1(M)$ which is free of some rank $2g$
where $g$ is a positive number.
Here we exlude the case when
$M\simeq S^2$, i.e $M$ is not
homoemorphic to the sphere. Instead $M$ is homeomorphic to a sphere where
$g$ handles have been attached and
with this picture  in mind one can draw $2g$-many
closed curves
on $M$ whose intersection numbers
are special. More precisely, there exists 
a pair of $g$-tuples $\gamma_1,\ldots,\gamma_g$ and
$\rho_1,\ldots,\rho_g)$ , where all these $2g$ many closed curves are simple
and
\[
\mathfrak{i}(\gamma_\nu,\rho_\nu)=1\quad\colon \quad 1\leq\nu\leq g
\]
while all other intersection numbers are zero.


\newpage















\newpage


\centerline{\bf{Analysis on compact Riemann surfaces.}}
\bigskip


\noindent
Let $X$ be a compact 1-dimensional complex manifold.
Recall that its 
complex analytic structure arises via charts
$(U,z)$ where $z$ is a local coordinate on
$X$ in the open set $U$ which is biholomorphic with
the open disc $D=\{|\zeta|<1\}$ in the complex $\zeta$-plane.
Let $\rho_U\colon U\to D$ be the holomorphic map.
When a pair of charts
$U$ and $V$ overlap
their complex analytic structures are
compatible. It means that
one has a biholomorphic map
\[
\rho_{U.V}\colon \rho_U(U\cap V)\to
\rho_V(U\cap V)
\]
where 
\[
\rho_U(\zeta)=\rho_V\circ\rho_{U,V}(\zeta)\quad\colon
\zeta\in \rho_U(U\cap V)
\]
The reader should illustrate this by a suitable picture
to see how the transition functions work
in overlapping charts
Since $X$ is compact it can be covered by a finite family of charts
$\mathfrak{U}= \{U_\alpha,z_\alpha)\}$. So here $\cup \, U_\alpha=X$
and one refers to $\mathfrak{U}$ as an atlas for the complex manifold $X$.
If $U$ is an arbitrary open set
in $X$ a complex valued function $f$ in $U$ is holomorphic if
\[
f\circ \rho_\alpha^{-1}\in \mathcal O(\rho_\alpha(U\cap\, U_\alpha))
\]
hold for
every chart in the atlas.
The set of holomorphic functions in $U$ is denoted by
$\mathcal O(U)$.
Local existence of non-constant holomiorphic functions is clear since
the defintion above entails  that
if $U_\alpha$ is a chart then
$\mathcal O(U_\alpha)\simeq \mathcal O(D)$.
\medskip


\noindent
{\bf{Differential calculus  on $X$.}}
A complex analytic atlas is in particular  a
$C^\infty$-atlas on the underlying real manifold
which has real dimension two.
The space of complex-vaued $C^\infty$-functions on
$X$ is denoted by $\mathcal E(X)$.
We have also the space $\mathcal E^1(X)$
of differential 1-forms
with
$C^\infty$-coefficients.
In a chart $(U,z)$
every differential 1-form can be decomposed as
\[
a\cdot dz+b\cdot d\bar z\tag{A.0}
\]
where $a$ and $b$ are complex-valued $C^\infty$-functions.
This gives a direct sum decomposition
\[
\mathcal E^1(X)=\mathcal E^{1.0}(X)\oplus\, \mathcal E^{0,1}(X)\tag{A.1}
\]
One refers to $\mathcal E^{1,0}$ as the space of diffeential 
forms of bi-degree $(1,0)$.
Thet are characterised by the condition that
$b=0$ holds in
$(A.0)$ for every  chart.
Similarly  when $a=0$  hold we get
a differential form of bi-degree $(0,1)$.
If $g\in\mathcal E(X)$ its exterior differential $dg$
is a 1-form which has a decompostion
\[
dg=\partial g+\bar\partial g
\]
For example, one has a map
\[
\bar\partial\colon\mathcal E(X)\to \mathcal E^{0,1}(X)\tag{A.2}
\]
The Cauchy-Riemann equations applied in charts show that
the kernel in (A.2) consists of holomorphic functions and
hence the kernel is reduced to  constant functions.
\medskip

\noindent
Next, we also have differential 2-forms on $X$ which in a chart $(U,z)$
can be expressed as
\[
c(z)\cdot dz\wedge d\bar z
\]
Keeping the complex analytic structure in mind
we denote the space of differential 2-forms with
$\mathcal E^{1,1}(X)$.
The reader should
construct the  maps
\[
\bar\partial\colon \mathcal E^{1,0}(X)\to \mathcal E^{1.1}(X)\tag{A.3}
\]
\[
\partial\colon \mathcal E^{0,1}(X)\to \mathcal E^{1.1}(X)\tag{A.4}
\]
\medskip

\noindent
Next, recall that $\mathcal E(X)$ is a Frechet space
where the topology is defined via uniform convergence of
derivatives in every order.
In a similar fashion $\mathcal E^{p,q}(X)$
are Frechet spaces for every pair $0\leq p,q\leq 1$.
The reader should  check that 
the maps in (A:2-4)  are continous between these 
Frechet spaces.
Less obvious is the folloowing:
\medskip

\noindent
{\bf{A.5 Theorem.}}
\emph{Tbe range of the exterior differential maps
in (A.2-4) above are all closed.}
\bigskip




\noindent
{\bf{A.6. Remark.}}
This is the first non-trivial result
about compact Riemann surfaces.
We give the proof in (*) and remark only that it
relies upon
a classic result due to Pompieu which gives solutions to
the inhomogeneous $\bar\partial$-partial 
equation in planar
domains. More precisely, if
$U$ is an open set  in the complex $\zeta$-plane and
$g\in C^\infty(U)$ then
there exists $f\in C^\infty(U)$ such that
\[
\bar\partial(f)= g\cdot d\bar\zeta\tag{A.6.1}
\]
\bigskip

\noindent
{\bf{A.7 Currents on $X$.}}
To  begin with we have the space
$\mathfrak{Db}(X)$ of distributions which by  definition it is the 
space of continuos linear forms on the Frechet space
$\mathcal E^{1,1}(X)$, i.e.
\[
\mathfrak{Db}(X)= \mathcal E^{1,1}(X)^*
\]
Passing to differential forms
we get dual spaces
\[ 
\mathfrak{c}^{1,0}(X)=\mathcal E^{0,1}(X)^*
\quad\colon\quad
\mathfrak{c}^{0,1}(X)=\mathcal E^{1,0}(X)^*
\]
Finally, we have the space $\mathfrak{c}^{1.1}(X)$
which is the dual of $\mathcal E(X)$.
\medskip

\noindent
{\bf{B.1 The integration current $1_X$.}}
The reader should check that
the complex analytic structure on $X$ entails that its underlying
real manifold is oriented.
It  follows that if
$\gamma\in \mathcal E^{1,1}(X)$
then there exists an integral
\[
\int_X\, \gamma
\]
This defines a distribution   denoted by
$1_X$.
In general we have an inclusion
\[
\mathcal E(X)\subset\mathfrak{Db}(X)
\]
Namely, if $g$ is a $C^\infty$-function we get
a linear form on
$\mathcal E^{1,1}(X)$ defined by
\[
\gamma\mapsto \int_X\, g\cdot \gamma
\]
If
$\gamma^{1,0}$ belongs to
$\mathcal E^{1,0}(X)$
we notice that Stokes Theorem gives
\[
0=\int_X\, d(g\cdot \gamma^{1,0})
\]
Now the reader should verify that
\[
d(g\cdot \gamma^{0,1})=
\bar\partial g\wedge \gamma^{1,0}+g\cdot \bar\partial(\gamma^{1,0})
\]
Next, by definition the
$(0,1)$-current $\bar\partial g$
is defined by
\[
\bar\partial(g)\langle \gamma^{1,0}\rangle=-\int_X\, g\cdot \bar\partial(\gamma^{1,0})
\]
Keeping  signs in mind one concludes that
when $g$ from the start is identified with a distribution, then
the $(0,1)$-current $\bar\partial(g)$ is equal to the smooth
differential 1-form
of  bi-degree (0,1) arising when
$\bar\partial$ is applied to the $C^\infty$-function $g$.
\medskip

\noindent
{\bf{B.2 A  duality result.}}
We have the map
\[
\bar\partial\colon \mathcal E^{1,0}(X)\to \mathcal E^{1,1}(X)
\]
By Theorem A.5 the range is closed.
This implies that
the dual space
\[
\bigl[\, \frac{\mathcal E^{1,1}(X)}{\bar\partial \mathcal E^{1,0}(X)}\,\bigr]^*
\simeq \text{Ker}_{\bar\partial}(\mathfrak{Db}(X))\tag{B.2.1}
\]
Next, recall that  $\bar\partial$ is elliptic.Indeed, via the   classic Pompieu formula for planar
doimains  every distribution $\mu$ satisfying
the homogeneous equation $\bar\partial(\mu)=0$ is a holomorphic
function.
Since $\mathcal O(X)$ is reduced to constants the
dual space in (B.2.1)  is 1-dimensional and hence
\[
\dim_{{\bf{C}}}\, \frac{\mathcal E^{1,1}(X)}{\bar\partial \mathcal E^{1,0}(X)}=1\tag{B.2.2}
\]
Notice also that Stokes Theorem gives
\[
\int_X\, \bar\partial(\gamma^{1,0})=0\quad\colon\, \gamma^{1,0}\in \mathcal E^{,1,0}(X)
\]
from this we conclude thatif 
$\rho^{1,1}$ is a  2-form for which
$\int_X\,\rho^{1,1}\neq 0$, then
\[
\mathcal E^{1,1}(X)={\bf{C}}\cdot \rho\oplus
\bar\partial(\mathcal E^{1,1}(X))\tag{B.2.3}
\]
\medskip

\noindent{\bf{B.3 A second duality.}}
Theorem A.5 entails that
\[
\bigl[\, \frac{\mathcal E^{0,1}(X)}{\bar\partial \mathcal E(X)}\,\bigr]^*
\simeq \text{Ker}_{\bar\partial}(\mathfrak{c}^{1,0}(X))\tag{B.3.1}
\]
The right hand side is found as follows.
In a chart $(U,z)$
a current of bi-degree
$(1,0)$ is of the form
$\mu\cdot dz$ with
$\mu\in \mathfrak{Db}(U)$.
The $\bar\partial$ image of this current is
zero if and only if $\bar\partial(\mu)=0$ and as we have seen
before this implies that
$\mu$ is a holomorphic density.
Hence the right hand side in (B.3.1) consists of globally defined
\emph{holomorphic} 1-forms. This space is denoted by
$\Omega(X)$ and (B.3.1) can be expressed by
the duality formula
\[
\Omega(X)\simeq\bigl[\, \frac{\mathcal E^{0,1}(X)}{\bar\partial \mathcal E(X)}\,\bigr]^*\tag{B.3.2}
\]
\medskip

\noindent
{\bf{B.3.3 Exercise.}}
Show that (B.3.2) gives the following:
A differential form $\gamma^{0,1}$ on $X$ is $\bar\partial$-exact
if and only if
\[
\int_X\, \omega\wedge \gamma^{0,1}=0\quad\colon\, \forall\,\,
\omega\in \Omega(X)
\]
\medskip

\noindent
{\bf{B.4 Passage to currents.}}
Recall that $\mathcal E^{0,1}(X)\subset\mathfrak{c}^{0,1}$.
in ¤ xx we shall learn that
\[
\mathfrak{c}^{0,1}=\bar\partial(\mathfrak{Db}(X))+
\mathcal E^{0,1}(X)\tag {B.4.1}
\]
Moreover, a $(0.1)$-current $\rho^{0,1}$ is
$\bar\partial$-exact, i.e. of the form
$\bar\partial(\mu)$ for some
distribution $\mu$ on $X$ if and only if
\[
\rho^{1,0}(\omega)=0\quad\colon\quad \omega\in \Omega(X)\tag{B.4.2}
\]
\medskip

\noindent
{\bf{B.5 The case $X={\bf{P}}^1$.}}
Here $\Omega(X)$ is reduced to the zero space.
To see this we suppose that
$\omega$ is a globally defined holomorphic 1-form.
Now ${\bf{P}}^1\setminus \{\infty\}$ is the complex $z$-plane and here
\[
\omega= f(z)\cdot dz
\] 
where $f$ is an entire function.
At the point at infinity we have a local coordinate
$\zeta$ and
\[
\zeta= z^{-1}\quad\colon R<|z|<\infty
\]
hold for every $R>0$.
Since $\omega$ is globally holomorhpic we have
\[
\omega= g(\zeta)\cdot d\zeta
\]
when $0<|\zeta|<R^{-1}$. At the same time the reader can check that
\[
dz=-\zeta^{-2}\cdot d7zeta
\]
holds when $R<|z[<R$. Ths entails that
\[
f(z)=-z^{-2}\cdot g(1/z)\quad\colon |z|>R
\]
From this we see that
the entire function $f$ tends to zero as $|z|\to\infty$
and hence $f$ is identically zero.
So with $X={\bf{P}}^1$ one has $\Omega(X)=0$ and
then (B.4.2) entails that
\[
\mathfrak{c}^{0,1}= \bar\partial(\mathfrak{Db}(X))
\]
In other words, the inhomogeneous $\bar\partial$-equation
is always solvable.
Consider as an example a current
of the form
\[
\gamma=\mu\cdot d\bar z
\]
where $\mu$ is a measure in the complex $z$-plane with compact support.
Now there exists the Cauchy transform
\[
\widehat{\mu}(z)=\int\,\frac{d\mu(\zeta)}{z-\zeta}
\]
It is holomiorphic in
in the open set of the complex $z$-plane where
the compact set
$\text{Supp}(\mu)$ has been removed.
passing to infinity we
notice that
it extends to be holomorphic
because one has the convergent series expansion
\[
\widehat{\mu}(z)=\sum_{n=0}^\infty\,
\int\,\zeta^n|cdot d\mu(\zeta)\cdot z^{-n-1}{z-\zeta}
\]
in an exterior disc
$|z[>R$ where
the support of $\mu$ is contained in
$\{|z|\leq R\}$.
\medskip

\noindent
next, by basuc lebsgue theory one knows that
the funnction $\widehat{\mu}$ is locally integrable
in the whole complex $z$-plane and hence defines a distribution.
Finally, Cacuhy's residue formula shows that
the distribution derivative
\[
\frac{\bar\partial\widehat{\mu}}{\bar\partial\bar z}=\pi \cdot \mu
\]
So we get
\[
\bar\partial(\pi^{-1}\cdot \widehat{\mu})=\mu\cdot d\bar z
\]




















\newpage


\centerline{\bf{C. Some sheaves and their cohomology}}.
\medskip


\noindent
Let $X$ be a compact complex  analytic manifold.
Classic  facts due to Cauchy and Pompieu applied to charts in $X$ 
give  an exact sequence of sheaves
\[
0\to \mathcal O_X\to \mathcal E_X\overset{\bar\partial}\to, \mathcal E_X^{0,1}\to 0\tag{C.0}
\]
Using $C^\infty$-parotions of unity and Leray's theory about  cohomology with
values in sheaves
one gets
\[
H^1(\mathcal O_X)\simeq \frac{
\mathcal E^{0,1}(X)}{\bar\partial(\mathcal E(X)}\tag{C.1}
\]
where the left hand side is the first cohomology groups with
values in the sheaf
$\mathcal O_X$. The reader may also notice that when Leray's long exact sequence for sheaf cohomology is applied to (C.0), then it follows that
\[
H^2(\mathcal O_X)=0\tag{C.2}
\]
Next, we have also the exact sheaf sequence
\[
0\to {\bf{C}}_X\to \mathcal O_X\overset{\partial}\to \Omega_X\to 0\tag{C.3}
\]
Since $H^0({\bf{C}}_X)= H^0(\mathcal O_X)= {\bf{C}}$ and (C.2) holds
one gets the following   exact sequence of complex vector spaces:
\[
0\to \Omega(X)\to H^1({\bf{C}}_X)\to
 H^1(\mathcal O_X)\to H^1(\Omega _X)\to H^2({\bf{C}}_X)\to 0\tag{C.4}
\]
Next, we have
also the following exact sheaf sequence
\[
0\to \Omega_X\to \mathcal E^{1,0}_X\overset{\bar\partial}\to \mathcal E_X^{1,1}\to 0\tag{C.5}
\]
This gives the equality
\[
H^1(\Omega_X)\simeq\frac{\mathcal E^{1,1}(X)}{\bar\partial(\mathcal E^{1,0}(X))}\tag{C.6}
\]
The right hand side rsssembles the quotient in
(B.2.2).
Indeed, we can regard the 7emph{conjugate} analytic structure on
the underlying real manifold of $x$ where the sheaf of holomorphic functions
are compex cojugates of sections in
$\mathcal O_X$. From this the reader may conclude via (B.2.2)
that the rifht hand side in (C.5)
is a 1-dimensional vector space. Hence we have 
\[
\dim_{{\bf{C}}}\,H^1(\Omega_X)=1\tag{C.7}
\]
\medskip

\noindent
Next, recall that
$H^2({\bf{C}}_X)={\bf{C}}$. Together with (C.7) we conclude that
 (C.4) gives the
short exact sequence
\[
0\to \Omega(X)\to H^1({\bf{C}}_X)\to
 H^1(\mathcal O_X)\to 0\tag{C.8}
\]
Topology teaches that
the cohomology space
$H^1({\bf{C}}_X)$Êis finite dimensional.
Hence (C.8) implies that both
$\Omega(X)$ and $H^1(\mathcal O_X)$ are finite dimensional complex vector spaces.
Finally, (B.3.2) and (C.1) give
\[
\Omega(X)\simeq\bigl [\, H^1(\mathcal O_X)\,\bigr]^*\tag{C.9}
\]
In particular the complex vector spaces
$\Omega(X)$ and $H^1(\mathcal O_X)$ have the same dimension.
This equality and (C.8) give
\[
\dim H^1({\bf{C}}_X)= 2\cdot \dim \Omega(X)\tag{C.10}
\]
The equality (C.10) is fundamental  during the study of compact
Riemann surfaces. 
A notable point is that
the cohomology group $H^1({\bf{C}}_X)$ only depends upon the
topological space $X$ and not upon its particular complex structure.

\bigskip

\noindent
{\bf{C.10 A duality for currents.}}
In planar domains it is wellknown that the
inhomogenous $\bar\partial$-equation is locally solvable on distributions.
Since the $\bar\partial$-kernel on $\mathfrak{Db}_X$ is $\mathcal O_X$
one has an exact sequence
\[
0\to \mathcal O_X\to \mathfrak{Db}_X\overset{\bar\partial}\to
\mathfrak{c}^{0,1}_X\to 0
\]
Passing to cohomology and using 
$C^\infty$-partitions of the unity, it follows that
\[
H^1(\mathcal O_X)\simeq \frac{\mathfrak{c}^{0,1}_X}{
\bar\partial(\mathfrak{Db}(X)}\tag{C.10.1}
\]
\medskip

\noindent
{\bf{Exercise.}} Deduce from the above that
\[
\Omega(X)\simeq\bigl[\, \frac{\mathfrak{c}^{0,1}_X}{
\bar\partial(\mathfrak{Db}(X)}\,\bigr]^*\tag{C.10.2}
\]
Conclude that the implication below holds for
each 
$\gamma\in \mathfrak{c}^{0,1}$:
\[
\gamma(\omega)=0\quad\colon\,\forall\,\, \omega\in \Omega(X)
\implies \gamma\in \bar\partial(\mathfrak{Db}(X))\tag{C.10.3}
\]
\medskip

\noindent
{\bf{C.11 A decomposition theorem.}}
Since $X$ in particular is an oriented and compact real manifold
one has
\[
H^1({\bf{C}}_X)\simeq\frac{\text{Ker}_d(\mathcal E^1(X)}{d(\mathcal E(X)}\tag{C.11.1}
\]
Next, on $X$ there also exists
the anti-holomorphic differential forms of bi-degree
$(0,1)$, i.e differential forms  $\gamma\in \mathcal E^{0,1}(X)$ for which
$\partial(\gamma)=0$.
This space is denoted by $\overline{\Omega}(X)$.
Using the conjugate complex analytic structure one has another compact
complex manifold $\overline{X}$
where
$\overline{\Omega}(X)$ is the space of holomorphic 1-forms.
Since $X$ and $\overline{X}$ have the same underlying real manifold, it follows from
(C.10) that
\[
\dim H^1({\bf{C}}_X)= 2\cdot \dim \overline{\Omega}(X)\tag{C.11.2}
\]
Using  this we shall prove
\medskip

\noindent
{\bf{C.11.3 Theorem.}}
\emph{One has a direct sum decomposition}
\[
\text{Ker}_d(\mathcal E^1(X))=
d(\mathcal E(X))\oplus \Omega(X)\oplus\overline{\Omega}(X)
\]
\medskip

\noindent
\emph{Proof}
To begin with we notice that
\[
\Omega(X)\,\cap \overline{\Omega}(X)= \{0\}
\]
Counting dimensions this follows if we prove that
a 1-form $\gamma)\omega+\mu$ cannot be $d$-exact
when $\omega\in \Omega(X)$ and $\mu\in \overline{\Omega}(X)$
where at least one these froms is not identically ero.
For suppose that
$\gamma=dg$ is $d$-exact.
If $\omega$ is not identically zero there exists
the conjugate
form
$\bar\omega\in\overline{\Omega}(X)$.
Now Stokes Theorem gives
\[
0=\int_X\, dg\cdot \bar\omega)=\int_X(\omega+\mu)\wedge\bar\omega=
\int_X(\omega\wedge\bar\omega
\]
Now the reader can check that
the last integral is $\neq 0$ when $\omega$ is not identically zero.
hence $\gamma\in d(\mathcal E(X))$ implies that
$\Omega=0$ and in the same way we find that
$\mu=0$ which proves Theorem C.11.3.








\newpage


\centerline{\bf{D. Existence of meromorphic functions.}}
\bigskip


\noindent
On $X$ there exists the sheaf
$\mathcal M_X$ whose sections are meromorphic  functions.
Subsheaves arise via  constraints on  poles.
In particular, let $p\in X$ be a given point and
$m$ a positive integer.
Denote by $\mathcal O_X[* mp]$
the sheaf whose sections are meromorphic functions on
$X$ which are holomorphic in $X\setminus\{p\}$ and have
poles of order $\leq m$ at $p$.
If $(U,z)$ is a chart where $p$ corresponds to
the origin we seee that
\[
\mathcal O_X[* mp]\,|U= z^{-m}\cdot \mathcal OX|U
\]
Taking Laurent exapnsions
every section in the right hand side is of the form
\[
f+\frac{c_1}{z}+\ldots+\frac{c_m}{z^m}
\]
where $f\in \mathcal O_X$ and $\{c_\nu\}$ is an $m$-tuple of complex numbers.
Expressed by  sheaves it gives
an exact sequence
\[
0\to \mathcal O_X\to \mathcal O_X[*mp]\to S_p^m\to 0\tag{D.1}
\]
where $S_p$ is the scyscraper sheaf suppotet  by $\{p\}$
and
the stalk $S_p(p)$ is an $m$-dimensional vector space.
Passing to long exact sequence of cohomology the reader 
can verify that there is an exact sequence:
\[
0\to {\bf{C}}\to H^0(\mathcal O_X[*mp])\to
{\bf{C}}^m\to 
H^1(\mathcal O_X)\to H^0(\mathcal O_X[*mp])\to 0\tag{D.1.1}
\]
\medskip

\noindent
{\bf{D.2 Exercise.}}
Use that the vector space 
$H^1(\mathcal O_X)$ is $g$-dimensional and conclude that
\[
\dim_{{\bf{C}}}\, 
H^0(\mathcal O_X[*mp])=m-g+1+
\dim_{{\bf{C}}}\, 
H^1(\mathcal O_X[*mp])\geq m-g+1\tag{D.2.1}
\]
\medskip

\noindent
In particular the left hand side is $\geq 2$ if $m=g+1$
which means that
apart from constants, there exists at least one
constant global section in 
$\mathcal O_X[*(g+1)p]$.
Hence we have proved:

\bigskip

\noindent
{\bf{D.3 Theorem.}}
\emph{For every $p\in X$ there exists a non-constant 
meromorphic function $f$  in $X$ with no poles in
$X\setminus{p}$ while
the order of the pole at $p$ is at most $g+1$.}











\newpage



\centerline{\bf{Weierstrass' points.}}

\bigskip

\noindent
Let $X$ be a compact Riemann surface
whose genus number $g$ is $\geq 2$.
Removing  a point $p\in X$
we get  the space
$\mathcal O(X\setminus\{p\})$.
If $(U,z)$ is a chart centered at $p$
where $p$ corresponds to $z=0$, then every
$f\in\mathcal O(X\setminus\{p\})$
restricts to a holomorphic function in
the punctured disc
$0<|z|<1$
and we can regard its Laurent series:
\[
f(z)=
\sum_{\nu=1}^\infty\ c_\nu\cdot z^{-\nu}+\sum_{\nu\geq 0}\, d_\nu\cdot z^\nu
\]
The negative part of the Laurent series is denoted by $f_*(z)$.
If $f_*=0$ then $f$ is globally holomorphic and hence reduced to
a constant.
So 
\[
f\mapsto f_*(z)+ d_0
\]
yields an  injective 
map from $\mathcal O(X\setminus\{p\})$ 
into the space of
non-positive Laurent series at $z=0$.
We are going to study the range of this map.
Denote by $\mathcal L$
the space 
of all non-positive Laurent series, where we recall that a negative
series
\[
\sum_{\nu=1}^\infty\ c_\nu\cdot z^{-\nu}\in\mathcal L
\]
if and only if
\[
\sum_{\nu=1}^\infty\, |c_\nu|\cdot R^\nu<\infty
\] 
for all $R>0$.
In particular $\mathcal L$ contains the $g$-dimensional subspace
formed by Laurent series given by
finite series:
\[
\rho(z)= c_1z^{-1}+\ldots+c_g\cdot z^{-g}
\]
where $\{c_\nu\}$ is a $p$-tuple of complex numbers.
Let $\mathcal L[p]$ denote this subspace of
$\mathcal L$.
\medskip

\noindent
{\bf{E.1 Theorem.}}
\emph{Outside a finite set ${\bf{W}}$ in $X$
one has} 
\[ 
\mathcal L=\mathcal L[p]\oplus \mathfrak{Im}(\mathcal O(X\setminus\{p\})
\]
\medskip

\noindent
{\bf{E.2 Remark.}}
In ¤xx we show that
the exceptional set
${\bf{W}}$ is non-empty when $g\geq 2$,
If (*) holds above
it follows that when $m>g$
then  there exists a unique $g$-tuple $\{c_\nu\}$ such that 
\[ 
z^{-m}=c_1z^{-1}+\dots+c_gz^{-g}+ \mathfrak{Im}(\phi)
\]
where $\phi$ is holomorphic in
$X\setminus\{p\}$.
Herte the negative Laurent series of $\phi$ is finite
at $p$ which implies that
$\phi$ is a globally defined meromorphic function
with a pole of order $m$ at $p$ whose negative Laurent expnasion at $p$
is of the form
\[
z^{-m}+c_1z^{-1}+\dots+c_gz^{-g}
\]
where the $g$-tuple $\{c_\nu\}$ is uniquely determined and depends on
the chosen integer $m$.
At the same time
the direct dum in (*) entails that
there do not exist non-constant meromorphic functions
which are holomorphic in
$X\setminus\{p\}$ while the order of
the pole at $p$ is $\leq g$.
\medskip

\noindent
The proof of Theorem E.1 requires several steps.
We are given a point
$p\in X$ and let $(U,z)$ be a chart
around $p$ where $p$ corresponds to $z=0$.
Residue calculus gives
a $g$-tuple of 
currents defined by
\[
\rho_\nu=\bar\partial(z^{-\nu})\quad\colon\quad \nu=1,\ldots,g
\]
Each current is supported by the singleton set $\{p\}$
and extends to a current on $X$ supported by $p$.
If $\Psi^{1,0}\in\mathcal E^{1,0}(X)$
we can regard its restriction to $U$ and write
\[
\Psi^{1,0}|U= \psi(z)\cdot dz
\]
with $\psi\in C^\infty(U)$.
Residue calcluus teaches that
\[
\rho_1(\Psi^{1,0})= 2\pi i\cdot \psi(0)
\]
If $\nu\geq 2$ the reader may verify that
\[
\rho_\nu(\Psi^{1,0})= \frac{(-1)^{\nu-1}}{(\nu-1)!}\cdot
\partial^{\nu-1}\psi/\partial z^{\nu-1}(0)
\]
The construction of the $\rho$-currents
is not intrinsic, i.e.
the $g$-tuple  depends on the chosen chart around $p$.
But the reader can check that
the $g$-dimenbsional vector space
in $\mathfrak{c}^{0,1}(X)$
generated by
$\{\rho^\nu\,\colon 1\leq \nu\leq g\}$
does not depend on the chosen chart around $p$.
Let us denote it by $\mathcal W(p)$.
The major step towards the proof of Theorem E.1
is the following:


\medskip

\noindent
{\bf{E.3 Theorem.}} \emph{Outside a finite set
${\bf{W}}$  in $X$ one has
the direct sum decomposition}
\[
\mathfrak{c}^{0,1}(X)=\bar\partial(\mathfrak{Db}(X))\oplus\, \mathcal W(p)\tag{E.3.1}
\]
\bigskip

\noindent
\emph{Proof.}
The duality result in ¤ xx gives (E.3.1)
if
the $g$-tuple
$\{\rho^\nu\}$ restrict to 
${\bf{C}}$-linearly independent in the dual space
$\Omega(X)^*$.
To check when this holds we
consider a basis $\omega_1,\ldots,\omega_g$ in the $g$-dimensional vector space
$\Omega(X)$.
In a chart
$(U,z)$ centered at a point $p_0\in X $ we can write
\[
\omega_j= f_j(z)\cdot dz\tag{i}
\]
where Ê$\{f_j\}$ are ${\bf{C}}$-linearly 
independent in $\mathcal O(U)$.
The general result in ¤ xx  entails that 
the determinant function
\[
\mathcal F(z)= \det\bigl(\partial f_j^\nu/\partial z^\nu(z)\tag{ii}
\]
formed by the $g\times g$-matrix with
elements as above is not identically zero.
Now linear algebra shows that
$\{\rho_\nu\}$ restrict to linearly independent functionals
on $\Omega(X)$ at every $z|in U$ for ehich
$F(z)\neq 0$.
Since the zero set of $F$ in the chart $U$ is discrete
and we can cover
$X$ by a finite famliy of charts, it follows that
(E.3.1) holds outside a finite set
${\bf{W}}$.


\medskip

\noindent
{\bf{E.4 How to find ${\bf{W}}$.}}
In each  chart $(U,z)$ as above we have
the $\mathcal F$-functions from (ii).
If $(U_\alpha,z_\alpha)$ and $(U_\beta,z_\beta)$ is a pair of charts
in $X$ where $U_\alpha\cap U_\beta\neq\emptyset$
we get two $g$-tuples  of analytic functions by
\[
\omega_j|U_\alpha= f_j^\alpha\cdot dz\quad\colon\quad
\omega_j|U_\beta= f_j^\beta\cdot dz_\beta
\]
When $z_\beta=z_\beta(z_\alpha)$ is regarded as
an analytic function in $U_\alpha\cap U_\beta$ one has the equations
\[
f_j^\alpha=\frac{\partial z_\beta}{\partial z_\alpha}\cdot f_j^\beta\tag{E.4.1}
\]
for each $j$ in $U_\alpha\cap U\beta$.
\medskip

\noindent
{\bf{E.4.2 Exercise.}} Show by using
rules for calcuating determinsnts that
(E.4.1) gives
the equation
\[
\mathcal F_\alpha=\bigl(\frac{\partial z_\beta}{\partial z_\alpha}\bigr)^{g(g-1)/2}\cdot F_\beta(z)
\]
So with $N=g(g-1)/2$
the family $\{\mathcal F_\alpha\}$ which arises when
$X$ is covered by a finite number of charts, is a global section of
the $N$-fold product of the holomorphic line bundle $\Omega_X$.
By (xx) the
set of xeros counted with multiplicities  of every global section
in $\Omega_X$ is equal to $2(g-1)$.
So by the general result in ¤ xxx the
zero set of the $\mathcal F$-family counted with multiplicities is equal to
$g(g-1)^2$. Since $g\geq 2$ this is a positive integer and hence
the set ${\bf{W}}$ is non-empty.
\bigskip

\noindent
{\bf{Remark.}} In the literature one refers to
${\bf{W}}$ as the set of Weierstrass' points in $X$.
The determination of ${\bf{W}}$ for a given $X$ with genus $\geq 2$
is in general not easy.
From the above ${\bf{W}}$ contains at most
$(g-1)^2\cdot g$ many distinct points. 
In general the number of points can be
strictly smaller.
Weierstrass investigated
${\bf{W}}$ for special families of compact Riemann surfaces.
See ¤ xx for some comments.
\bigskip

\centerline {\bf{Proof of Theorem E.1}}

\bigskip

\noindent
Consider a point $p\in X$ which is outside ${\bf{W}}$ and let $(U,z)$ be a chart 
centered at $p$.
Let $U^*=U\setminus\{p\}$ be the punctured open disc.
In $X$ we also have the open set
$X\setminus\{p\}$
which can be regarded as an open Riemann surface.
The theorem by Behnke and Stein from
the chapter devoted to open Rieann surfaces
gives
$H^1(X\setminus\{p\},\mathcal O)=0$.
The cohomology in the  disc $U$ is also zero.
Hence the open covering of $X$ given by the pair
$\mathfrak{U}= (U,X\setminus\{p\})$
is acyclic with respect to the sheaf
$\mathcal O_X$. So  Leray's acyclicity theorem gives
\[
H^1(X,\mathcal O_X)\simeq \frac{\mathcal O( U^*)}{
\delta(C^0(\mathfrak{U},\mathcal O_X))}\tag{i}
\]
where
\[
\delta\colon \mathcal O(U)\oplus \mathcal O(X\setminus\{p\})\to
\mathcal O(U^*)
\] 
is the Cech coboundary map.
Next, the $g$-tuple $\{z^{-\nu}\colon \nu=1,\ldots,g\}$
are holomorphic in $U^*$
and  their images in the right hand side from (i) give
elements in
$H^1(X,\mathcal O_X)$ denoted by
$\{[z^{-\nu}]\}$.
\medskip

\noindent
{\bf{Exercise.}}
Recall  that
\[
H^1(X.\mathcal OX)= \frac{\mathfrak{c}^{0,1}}{\bar\partial(\mathfrak{Db}(X)}
\]
Since $p$ is outside ${\bf{W}}$
the last quotient is equal to $\mathcal W(p)$.
Conclude from this that
the $g$-tuple
$\{[z^{-\nu}]\}$ is a basis in the $g$-dimensional vector space
$H^1(X,\mathcal O_X)$.
\medskip

\noindent
Let us then consider some
$g\in\mathcal O(U^*)$ which has a  Laurent series
\[
g(z)= \sum_{\nu=1}^\infty\ c_\nu\cdot z^{-\nu}+
\sum_{\nu=0}^\infty\ d_\nu\cdot z^{\nu}
\]
By the Exercise  there exists
a unique $g$-tuple of complex numbers
$a_1,\ldots,a_p$
such that
the image of $g$ in
$H^1(X,\mathcal O_X)$ is equal to $\sum\, a_\nu\cdot [z^{-\nu}]$.
Hence (i) gives a pair $\phi(z)\in\mathcal O(U)$ and $f(z)\in \mathcal O(X\setminus\{p\}$
such that
\[
g(z)-\sum\,\rho_\nu\cdot z^{-\nu}=\phi(z)+f(z)
\]
where $\phi(z)\in\mathcal O(U)$ and $f(z)\in \mathcal O(X\setminus\{p\}$.
Regarding the negative Laurent series it follows that
\[
g_*(z)= \sum\, a_\nu\cdot z^{-\nu}+f_*(z)\tag{ii}
\]
Here $g$ was arbitrary in
$\mathcal O(U^*)$ and hence the proof of Theorem E.1 is finished.
















\newpage










 
 
 
 

\centerline{\bf{F. Abel's theorem.}}



\bigskip


\noindent
A divisor $D$ on $X$ consists of
an assignement of integers $\{\mu_\nu\}$ to a finite set of points $\{p_\nu\}$
in $X$. One writes
\[
D= \sum\, \mu_\nu\cdot \delta(p_\nu)
\]
The $\mu$-integers may be positive or negative.
The degree is defined by
\[
\deg D= \sum\,\mu_\nu
\] 
while the finite set $\{p_\nu\}$ is called the support of $D$.
Next we construct a class of 1-currents.
In general, let $\gamma\colon [0,1]\to X$
be an $X$valued function on the closed unit interval
We assume that $\gamma$ is continuous and has a
finite total variation. The last condition means that
there exists a constant $C$ such that
\[
\sum_{\nu=0}^{\nu=N-1}\, d(\gamma(t_{\nu+1},\gamma(t_\nu)\leq C
\]
for all sequences $0=t_0<t-1<\ldots<t_N=1$
Here $d$ is some  distance function 
on $X$ regarded as a metric space which in charts
is equivsoent to
the euclidian distance.
Every such $\gamma$ gives a current of degree one
acting on $\mathcal E^1(X)$ by 
\[
\alpha\mapsto \int_\gamma \,\alpha\tag{*}
\]
\medskip

\noindent
{\bf{Exercise.}} Explain how the classical Borel-Stieltjes integrals for functions
with bounded variation
defines the integral in the right hand side.
Show also that
\[
\int_\gamma\, dg= g(\gamma(1))-g(\gamma(0))
\]
hold for every $g\in\mathcal E()$.
One refers to (*) as an integration current of degree one.
More generally we can take a finite sum of such
currents and get the integration current
$\Gamma$ defined by
\[
\Gamma(\alpha)= \sum\, \int_{\gamma_j}\,\alpha
\]
Let $D=\sum\,\mu_\nu\cdot \delta(p_\nu)$ be a divisor of
degreee zero.
An integration current $\Gamma$ is said to be associated with
$D$ if the equality below hold for every
$g\in\mathcal E(X)$:
\[
\Gamma(dg)= \sum\, \mu_\nu\cdot g(p_\nu)
\]
\medskip

\noindent
{\bf{F.1 Principal divisors.}}
Let $f$ be a non-constant meromorphic function.
Now we have the finite set of poles $\{p_\nu\}$ and the finite set of zeros
$\{q_j\}$.
We associate the divisor
\[
\text{div}(f)= \sum\, \mu_k\cdot \delta(p_k)-\sum\, \mu_j\cdot \delta(q_j)
\]
Here $\mu_k$ is the order of the pole of $f$ at every $p_\nu$, while
$\mu_j$ is the order of a zero at $q_j$.
By the result in ¤ xx this divisor has degree zero.
A divisor $D$ of degree zero is called principal if
it is equal to $\text{div}(f)$ for some
$f\in\mathcal M(X)$.
Notice that if $f$ and $g$ is a pair of non-constant meromorphic functions such that
$\text{div}(f)= \text{div}(g)$, then
$f/g$ is a holomorphic function on $X$ and hence reduced to a non-zero constant.
Introducing the multiplicative group
$\mathcal M(X)^*$ of non-constant meromorphic functions
this means that one has an injective map
\[
\frac{\mathcal M(X)^*}{{\bf{C}}^*}\to\mathcal D_0
\]
where $\mathcal D_0$ is the additive group of divisors whose degree are zero.
The  theorem below describes the range of this map.

\medskip

\noindent
{\bf{F.2 Theorem.}}
\emph{A divisor $D$ of degree zero
is principal if and only if there
exists an integration current $\Gamma$ associated with
$D$  such that}
\[
\Gamma(\omega)=0\quad\colon \,\,\gamma\in \Omega(X)
\]
\medskip

\noindent
The proof requires several steps.
First we shall show the "if part", i.e. if 
$\Gamma$ exists so that (*) holds then
the divisor $D$ is principal.
To achieve this we first
perform a local construction in the complex plane.
\medskip

\noindent
{\bf{F.3 A class of currents in ${\bf{C}}$.}}
In the complex $z$-plane we consider
a point $z_0$ where 
\[
0<|z_0|<r<1
\]
holds for some $0<r<1$.
It is easily seen that there exists
a $C^\infty$-function $a(z)$  in ${\bf{C}}$
which never is zero and the function
\[
\phi(z)= \frac{z}{z-z_0}\cdot a(z)
\]
is identically one when
$|z|\geq r$.
Now $z\mapsto \frac{1}{z-z_0}$ is locally integrable around
$z_0$ and hence $\phi$ belongs to 
$L^1_{\text{loc}} ({\bf{C}})$ and is therefore a distribution.
\medskip

\noindent
Cauchy's residue formula can be expressed by saying
the $\bar\partial$-image of the $\frac{1}{z}$
is equal to the $(0,1)$-current
$2\pi i\cdot \delta(0)d\bar z$ where $\delta(0)$ is the Diraqc distribution
at the origin.
Using this the reader can check that
\[
\bar\partial(\phi)=
 \frac{z}{z-z_0}\cdot \bar\partial(a)+z_0a(z_0)\cdot \delta(z_0)d\bar z\tag{i}
 \]
 from (i) the reader should also check that
 \[
 \phi^{-1}\cdot \bar\partial(\phi)= a^{-1}\cdot \bar\partial(a)\tag{ii}
 \]
 \medskip
 
 \noindent
 {\bf{F.4 The current $\phi^{-1}\cdot \partial(\phi)$.}}
 To begin we one has
 \[
 \partial(\phi)=\frac{a(z)}{z-z_0}\cdot dz-
 \frac{za}{(z-z_0)^2)}\cdot dz+\frac{z}{z-z_0}\cdot \partial a\tag{F.4.1}
 \]
 Above $(z-z_0)^{-2}$ is the principal value distribution
 defined as in ¤ xx.
 \medskip
 
 \noindent
 {\bf{ Exercise.}}
 Use (F.4.1) to establish the equation
 \[
 \phi^{-1}\cdot \partial(\phi)=z^{-1}\cdot dz-(z-z_0)^{-1}\cdot dz+
 a^{-1}\cdot \partial(a)\tag{F.4.2}
 \]
 \medskip
 
 \noindent
 {\bf{Exercise.}}
 Use Stokes Theorenm and Cauchy's residue fornula to
 prove that when the 1-current
 \[
 \phi^{-1}\cdot d\phi=  \phi^{-1}\cdot \partial(\phi)+ \phi^{-1}\cdot \bar \partial(\phi)
 \] 
 is applied to $dg$ for some
 $g\in C_0^\infty({\bf{C}}$, then
 \[
 \phi^{-1}\cdot d\phi<dg>\, = 2\pi i\cdot (g(0)-g(z_0)\tag{F.4.3}
 \]
\medskip


\noindent
 Let us now consider an integration current
 $\Gamma$ given by a finite sum
 $\sum\,\gamma_j$ where each $\gamma_j$ has compact support in
 a chart
 $(U_j,z_j)$ in $X$ and the end-points of
 $\gamma_j$ are $z_j=0$ and $z_j=z_j^*$
 with $0<|z_j^*|<r<1$ and $U_j$ is a chart defined by
 $\{|z_j|<1|]$.
In $X$ the point $z_j=0$ is denoted by $q_j$ while $z_j^*$ corresponds to a
point $p_j$.
It follows that 
 \[
 \int_\Gamma \, dg=\sum_{j=1}^{j=N}\, g(p_j)-g(q_j)\tag{F.5}
 \]
for every $g\in \mathcal E(X)$.
 Next, for each $j$ we apply the local contruction the chart
 and find a function
 $\phi_j$ in $X$ which is identically one
 in $X\setminus \{|z_j|\leq r\}$ such that 
 \[
 \phi_j^{-1}\cdot d\phi_j<dg>=2\pi i\cdot \int_{\gamma_j}\, dg\quad\colon\, g\in \mathcal E(X)
 \]
 More generally, since
 $d$-closed 1-forms in the chart $U_j$ are $d$-exact the re4ader should check that
 (F.5) implies that
 \[
 \phi_j^{-1}\cdot d\phi_j<\alpha>=2\pi i\cdot \int_{\gamma_j}\,\alpha\tag{F.6}
 \]
 hold for every $d$-closed differential 1-form $\alpha$.
 Let us now consider the function
 \[
 \Phi= \prod_{j=1}^{j=N}\, \phi_j
 \]
 \medskip
 
 \noindent
 {\bf{F.7 Exercise.}}
 From the above the
 reader should check  that
 the construction of the $\phi$-functions imply that
 $\Phi$ is a zero-free
 $C^\infty$-function
 in $X\setminus \{q_j,p_j\}$, i.e. in the open complement of
 the finite set
  which is the union of these   $q$  and  $p$ points.
Moreover,  additivity for logarithmic derivatives and 
(F.6) above gives
\[
\Phi^{-1}\cdot d\Phi<\alpha>=
\int_\Gamma\, \alpha\tag{F.7.1}
\]
for every $d$-closed 1-form
$\alpha$. Finally, show that
\[
\Phi^{-1}\cdot \bar\partial(\Phi)=
\sum\, a_j^{-1}\cdot \bar\partial(a_j)\tag{F.7.2}
\]
where the right hand side is a smooth $(0,1)$-form.
\medskip

\noindent
{\bf{F.8 A special case.}}
Suppose that $\Gamma$ is such that
\[
\int_\Gamma\, \omega=0\quad\colon\quad \omega\in\Omega(X)\tag{F.8.1}
\]
The equality in (F.7.1) applied to  $d$-closed holomorphic 1-forms
and
Theorem ¤ xx  entail  that
the smooth $(0,1)$-form
$\Phi^{-1}\cdot \bar\partial(\Phi)$ from (F.7.2) is $\bar\partial$-exact.
Thus, we can find $G\in \mathcal E(X)$ such that
\[
\bar\partial(G)= \Phi^{-1}\cdot \bar\partial(\Phi)\tag{F.8.2}
\]
\medskip


\noindent
{\bf{Exercise.}}
Put
\[
\Psi=e^{-G}\cdot \Phi
\]
deduce from the above  that
$\bar\partial(\Psi)=0$ holds in
$X\setminus \{q_j,p_j\}$ and hence $\Psi$ is holomorphic in
this open subset of $X$
Show also  that the local constructions of the
$\phi$-functions inside the charts
$\{U_jz_j\}$ entail  that
$\psi$ extends to a mermorphic function in
$X$ whose princial divisor is equal to
\[
\sum\, \delta(q_j)-\sum \delta(p_j)
\]
Funally the reader should confirm that the constructions above
prove the "if part" in Theorem F.2.
\medskip


\centerline{\emph{F.9 Proof of the "only if part"}}
\medskip

\noindent 
Here we are given a non-constant meromorphic funvtion
$f$.
We shall condtruct an integration chain $\Gamma$ as follows:
Frst $f\colon X\to {\bf{P}}^1$ is a holomorphic map.
With $s=f(x)$
we recall from (xx) that the number critical $s$-points in
the complex $s$-plane is finite.
In ${bf[P})^1$ we choose a simple
curve $\gamma_*$ with intial point at $s=0$ and end-point at
$s=|nfty$, while
$\gamma_*$ avoids the critical points $s\neq 0$ in
${\bf{C}}$.
of course, while this is done we can choose
$\gamma_*$ so that it is a smooth curve
on the $C^\infty$-manifold ${\bf{P}}^1$.
\medskip

\noindent
{\bf{The inverse image $f^{-1}(\gamma_*)$.}}
Let $N=\deg(f)$.
Since $\gamma_*$ avoids $f$-cirtical points we see that
\[
f^{-1}(\gamma_*\setminus \{0,\infty\})= \gamma_1\cup\ldots\cup\,\gamma_N
\]
where $\{\gamma_j\}$ are disjoint  curves in
$X$, each of which is oriented via
$\gamma_*$ which from the start moves from
$s=0$ to $s=\infty$.
\medskip

\noindent
{\bf{Exercise.}}
Show that the closure $\bar\gamma_j$ yields a rectifiable  curve
whose initial point is zero of $f$ and the end-point a pole.
Put
\[
\Gamma=\sum\, \bar\gamma_j
\]
and conclude from the above that
$\Gamma$ is associated to the principal divisor of $f$.
The proof of the "onmy if part" is therefore finished if we show that
\[
\int_\Gamma\,\omega=0\quad\colon\quad \omega\in \Omega(X)\tag{*}
\]
To prove (*) we shall  use
a certain trace map.
First, a holomorphic 1-form
$\omega$ on $X$ is regared as a $\bar\partial$-closed current with
bi-degree $(0,1)$.
Since the amp $f\colon X\to {\bf{P}}^1$ is proper
there exists the direct image current
$f_*(\Omega$ and we recal from general facts that
the passage to direct image currents commute with
the $\bar\partial$-operator.
hence $\bar\partial(f_*(\Omega))==$ and since
$\bar\partial$ is elliptic it follows that
$f_*(\omega)$ is a holomorphic 1-form on
${\bf{P}}^1$.
By the result in Exercise xx there does not exist non-zero globally defined
holomorphic 1-forms on the projective line.
hence
\[ 
f_*(\omega)=0\tag{**}
\]
In partocuar we have
\[
\int_{\gamma_*(\epsilon)}\, f_*(\omega)=0
\]
where $\gamma_*(\epsilon)$ is the closed 
curve given by $\gamma$ intersected with
$\{\epsilon\leq |s| \leq \epsilon^{-1}\}$
for a small $\epsilon>0$.
\medskip

\noindent
{\bf{Exercise.}}
Put $\Gamma(\epsilon)= f^{-1}(\gamma(\epsilon)$
and dediuce from (xx) that
\[
\int_{\Gamma(\epsilon)}\, \omega=0
\]
Finally, pass to the limit as $\epsilon\to 0$ and conclude that (*) holds which finishes the proof of
the "only if part".



 
 
 
 \newpage
 
 \centerline{\bf{G. Holomorphic line bundles.}}
 
 
\bigskip

\noindent
There exists the multiplicative sheaf
$\mathcal O_X^*$ whose sections are zero-free
holomorphic functions.
every such function is locally $e^g$ with $g\in \mathcal O_X$
where $g$ is determined up to an integer multiple of $2\pi i$.
This gives an exact sheaf sequence
\[
0\to {\bf{Z}}_X\to \mathcal O_X\overset{\exp}\to \mathcal O^*_X\to 0
\]
where $\exp$ sends $g$ to $e^{2\pi i g}$
and ${\bf{Z}}_X$ is the sheaf of locally constant  integer-valued functions on
$X$.
Notice that global sections in
$\mathcal O_X^*$ are reduced to non-zero complex numbers
and we have the short exact sequence
\[
0\to {\bf{Z}}\to {\bf{C}}\overset{\exp}\to {\bf{C}}^*\to 0
\]
Conclude that one has an exact sequence
\[
0\to H^1({\bf{Z}}_X)\to H^1(\mathcal O_X)\to
H^1(\mathcal O_X^*)\to H^2({\bf{Z}}_X)\to 0\tag{G.1}
\]
As explained in ¤ xx
the cohomology group $H^1({\bf{Z}}_X)$
is a free abelian group of rank $2g$
while
$H^2({\bf{Z}}_X)={\bf{Z}}$.























 
 

 
 
 
 
 
 
 
 





\end{document}





















\end{document}



\centerline{\bf{Riemann surfaces.}}

\bigskip

\noindent
A compact Riemann surface
$X$ is by definition a connected and compact
complex analytic manifold of dimension one.
The maximum principle for holomorphic functions entails that
every globally defined holomorphic funtions on $X$
is a  constant.
Thus, $\mathcal O(X)$ is reduced to the complex field.
But if one allows poles we shall learn that there exist non-constant
meromorphic functions
on $X$. They give a field denoted by
$\mathcal M(X)$ whose properties will
be investigated later on.
The projective line ${\bf{P}}^1$
over the complex field is an example of a compact Riemann surface.
One starts with the complex $z$-plane and adds the point at
infinity to get ${\bf{P}}^1$. In ¤ xx we explain that
$\mathcal M({\bf{P}}^1)$ is equal to 
the field of rational functions of
the single complex variable $z$.
More generally, compact Riemann surfaces
arise when one starts from
an irreducible polynomial $P(x,y)$
of two independent variables, i.e.
$P$ is irreducible in the unique factorisation domain
${\bf{C}}[x,y]$.
We shall learn how to find the associated compact
Riemann surface $X$ where $\mathcal M(X)$
is isomorphic to the quotient field of the integral domain
$\frac{{\bf{C}}[x,y)}{(P)}$
where $(P)$ denotes the principal ideal generated
by $P$.
Here is  an example. Let 
\[
P(x,y)= y^3-x^3-1
\]
To get $X$ one first regards the
algebraic curve in ${\bf{C}}^2$ defined by
$\{P=0\}$.
The complex gradient
vector $(P'_x,P'_y)= (3x^2,3y^2)\neq (0,0)$ when $P(x,y)=0$. It 
means that $\{P=0\}$ is non-singular
and hence can be regarded  as an embedded one-dimensional complex manifold
in
${\bf{C}}^2$.
To get a compact complex manifold one regards the
projective curve $S$ in ${\bf{P}}^2$
with its inhomogeneous coordintes
$(\zeta,x,y)$
where $S$ is the zero set of $P^*(\zeta,x,y)= y^3-x^3-\zeta^3$.
We shall learn  that $S$  is non-singular
and therefore gives a compact Riemann surface.
Less obvious is that
$S$ regarded as a topological space is
homeomorphic to
the oriented real manifold
$T^2$, where $T^2$ denotes the 2-dimensional torus.
We shall learn that  $S\simeq T^2$ as a topological space because 
$\mathcal M(S)$ contains
a meromorohiuc function $u$
which has one double pole and two simple zeros on
$S$ and is otherwise holomorphic without zeros.
An example of such a meromorphic function is
\[
u=\frac{1}{y-x}
\]
whose properties as a meromorphic function on
$S$ will
be described in ¤ xx.



\medskip
\noindent
In ¤ xxx we
expose the pioneering work
by Hermann Weyl devoted to "abstract" Riemann surfaces.
His text-book from 1913
proves
the existence of non-constant
meromorphic  functions on a given compact 1-ddiensional complex manfold $X$.
From this Weyl deduced that
$\mathcal M(X)$ is an  algebraic functon field, i.e.
as a field extension over
${\bf{C}}$ its the degree of trancendency is one
and in addition  finitely generated.
Using the existence of primitive elements in
finite algebraic extensions of fields in characterstic zero
it follows that $\mathcal M(X)$
is isomorphic to the quotoent field of an integral domain
\[
\frac{{\bf{C}}[x,y]}{P(x,y)}
\]
where $P(x,y)$ is an irreducible polynomial in
the unique  factorisation domain ${\bf{C}}[x,y]$.
So every compact
Riemann surface arises from an irreducible
polynomial $P(x,y)$. 
In ¤ xx we shall learn
that
a compact Riemann surface $X$ is determined by
the field $\mathcal M(X)$.
More precisely, let $Y$ be another compact Riemann surface
and assume that there exists a ${\bf{C}}$-linear isomorphism
\[
\rho\colon \mathcal M(X)\to \mathcal M(Y)
\]
Thus, the two algebraic function fields are isomorphic.
In ¤ xx we show that this implies that 
$X$ and $Y$ are isomorphic
as complex manifolds, i.e.
$\rho$ yields a \emph{biholomorphic map}
from $X$ to $Y$.
\medskip

\noindent
{\bf{Non-compact Riemann surfaces.}}
In addition to compact Riemann surfaces there  exist
open   Riemann surfaces $X$. It means that
$X$ is a connected but non-compact complex manifold of dimension one.
Here 
$\mathcal O(X)$ contains an  extensive
 family of non-constant functions.
In ¤ xx we expose  results due to Behnke and Stein about
open  Riemann surfaces, One major fact is 
that one can prescribe zeros and poles
in an arbitrary fashion on $X$ 
which correspond to a globally defined meromorophic function on
$X$, i.e $\mathcal M(X)$ is  "optimally ample".
The \emph{Uniformisation Theorem}
is proved in ¤ xx.
It implies for example that
every simply connected open Riemann surface is either
biholomorphic to the open unit disc or the complex plane.
The  uniformisation theorem for
connected  open
subsets $\Omega$ of the complex $z$-plane
deserve special attention.
More precisely, if $\Omega\subset{\bf{C}}$ is
open and connected and the complement contains at least two points, then
there exists a holomorphic map
\[
\phi\colon D\to \Omega
\]
where $D$ is the open unit disc, and
$\phi$ has the following two properties: 
It is surejctive, i.e. $\phi(D)=\Omega$ and locally
conformal, i.e. the complex derivative
$\phi'(z)$ has no zeros.
In ¤ xx we shall learn that this entails that thr universal covering space of
$\Omega$ is homeomorphic to the open unit disc which is 
achieved via the  locally biholomorphic map $\phi$.
The uniformisation theorem for planar domains
was proved by Hermann Schwarz around 1860. He
adopted Riemann's methods for
simple connected domains and this classic  result  
is exposed in ¤ xx
in connection with Riemann's ordinary conformal mapping theorem for
simply connected planar domains.
Even though Schwarz's Uniformisation Theorem can be deduced via
the general case  by Behnke and Stein, it is instructive to pursue
his original proof which only relies upon analytic function theory.
\bigskip



\centerline{\bf{About methods of proofs.}}
\medskip

\noindent
The study of Riemann surfaces offer instructive lessons in sheaf theory since
various sheaves
appear in a natrual fashion. The reader is supposed to be familiar with
basic facts about sheaves and their cohomology. But for less experienced readers we
add an appenbdix where
som fundamental reults from Leray's   pioneering article
\emph{xxxx} are resumed. Let us also 
remark that even if Weierstrass never
introduced the notion of sheaves, his construction of
"sheaf spaces" attached to in general multiu.valued abnalytic functions
gave the first  exampe of sheaves.
In addition to sheaf theory we employ calculus on manifolds without
hesitation.
For example. let $M$ be an oriented  real $C^\infty$-manifold of some dimension
$n\geq 2$. To say that $M$ is oriennted means that
there exists a globally defined differential $n$-form
which never vanishes and choosing the orientation
one can define integrals
\[
\int_M\, \omega\quad\colon\quad \omega\in \mathcal E^n(M)
\]
where $\mathcal E^n(M)$ is the space of 
$n$-forms with $C^\infty$-.coefficients.
More generally there exist to each
$0\leq p\leq n$ the space
$\mathcal E^p(M)$ of differential $p$-forms
with $C^\infty$-coefficients.
Under the condition that $M$ can be covered by a denumarable family of compact subsets
it follows  that
$\mathcal E^p(M)$ is equipped with a topology so that it
becomes a Frechet spaces.
There also exists the spaces
$\{\mathcal E^p_0(M)\}$
which consist of differential forms having compact support in
$M$.
The dual of
$\mathcal E^p_0(M)$ is denoted by
$\mathfrak{c}^{n-p}(M)$ and its elements are called currents of
degree $n-p$.
in particular $\mathfrak{c}^0(M)$ is the space of distributions on
$M$ and is often denoted by
$\mathfrak{Db}(M)$. Thus, by definition
\[
\mathfrak{Db}(M)\simeq \mathcal E^n_0(M)^*
\]
where (*) indicates that one regards the dual space.
We assume that the reader is famiiar with basic distribution theory which for
example is coveed in Hšrmander's text-book
[xx], where the passage to manifolds and currents 
become  trivial using charts on $C^\infty$-manifolds and $C^\infty$-partitions  of the unity.
Even if we shall not study manifolds of dreal dimension $\geq 3$
we recall some classic facts about oriented and compact $C\infty-$manifolds
Let $M$ be a such a manifold of siome dimension $n\geq 2$.
using exterior differentials one
has a complex
\[
0\to \mathcal E^0(M)\to \mathcal E^1(M)\to\ldots\to \mathcal E^n(M)\to 0
\]
Here
\[
d\colon \mathcal E^p(M)\to \mathcal E^{p+1}(M)
\] 
are continuous for every $p$, where we recall that
every $\mathcal E^p(M)$ is a Frechet space.
A fundamental fact is that the images of the $d$-maps above
are closed and have finite codimension.
Ths can be proved in several ways. The most convincing proof is due to
AndrŽ Weil who also established that
every compact and oriented manifold $M$ can be tringulated
via  a finite simplicial complex.
So readers interested in algebraic topology should  consult Weil's
original proof which teaches a good lesson
dealing with
topology and triangulations of manifolds.
Now one introduces the cohomology spaces
\[
H^p(M)= \frac{\text{Ker}_d(\mathcal E^p(M)}{d\mathcal E^{p-1}(M)}\quad\colon 0\leq p\leq n
\]
In particular $H^0(M)$ is the $d$-kernel on $C^\infty(M)$ and hence the
1-dimensional space of constant functuons.
One has also the complex of currents:
\[
0\to \mathfrak{c}^0(M)\to \mathfrak{c}^1(M)\to\ldots\to \mathfrak{c}^n(M)\to 0\tag{**}
\]
It is denoted by
$\mathfrak{c}^\bullet$.
For every $p$ one has the inclusion $\mathcal E^p(M)\subset\mathfrak{c}^p(M)$ 
and hence  Hence 
(*) above is a subcomplex of (**).
Next, the  contruction of currents and their exterior differentials, togehter eith
the closed range of the differentials in (*), 
give
a natural  duality
\[
H^p(M)^*\simeq \frac{\text{Ker}_d(\mathfrak{c}^{n-p})}{
d(\mathfrak{c}^{n-p-1}(M)}= H^{n-p}(\mathfrak{c}^\bullet)
\]
In addition to this
the fact that $M$ admits a triangulation implies that
the complexes (*) and (**) are quasi-isomorphic.
Hence the right hsnd side in (**) can be identfied with
$H^{n-p}(M)$, i.e. the dual of $H^p(M)$ is
equal to th cohomology space in degree $n-p$.
This is referred to as PoincarŽ duality theorem for compact
and oriented  manifolds.















\medskip

\noindent
{\bf{Some examples when $n=2$.}}
Let $M$ be an oriented  $C^\infty$-manifold of dimension two.
Since $M$ can be covered by a finite family of
charts  we can equip $M$ with a distance function
$d$ whose restriction to charts is equivsrnt to ordinsty euclidian metroc.
Every pair of such distance functions
$d_1$ and $d_2$ are equivalent in the sense that
there exists a constant $C>0$ such that
\[
C^{-1}|cdot d_2(p,q)\leq d_1(p,q)\leq C\cdot d_2(p,q)
\]
hold for every pair $p,q$ in $M$.
Next, a  parametrized curve
on $M$ is a map $\gamma\colon [0,1]\to M$
which is continuous.
Using a metric as above we can impose the
extra condition that
$\gamma$ has a bounded variation, i.e. there exists a constant $C$ such that
\[
\sum_{\nu=0}^{\nu=N-1}\, d(\gamma(t_{\nu+1}),\gamma(t_\nu)\leq C\tag{i}
\]
for all partitions
$0=t_0<t_1<\ldots<t_{N-1}<t_N=1$.
When (i) holds  there exist ordinary Borel-Stieltjes' integrals
\[
\int_\gamma\, \psi^1\tag{*}
\] 
for every differential 1-form $\psi^1$ with $C^\infty$-coefficents.
This gives a continuous  functional on
$\mathcal E^(M)$ with compact support and hence a current of
degree 1, called 
the integration current associated with
$\gamma$. This "operative construction" will
be used at many places later on.
One merit is that  "nasty geometric pictures"
when $\gamma$ for example has self-intersections
can be ignored while one
treats its associated integration current.
The case when $\gamma$ is closed, i.e. when
$\gamma(1)=\gamma(0)$ 
leads to special results. To begin with
we notice that
the equality $\gamma(0)= \gamma(1)$ entails that
\[
\int_\gamma\, dg=0\quad\colon\quad g\in \mathcal E(M)
\]
This is expressed by saying that the current
$\int_\gamma$ is $d$-closed.
A crucial result which follows from
the fact that
every distribution in ${\bf{R}}^2$ has  locally primitive distributuions with
respect to the pair of euclidian coordinates in
${\bf{R}}^2$, entails that
the following complex vector spaces are isomorphic
\[
\frac{\text{Ker}_d(\mathcal E^1(M)}{d(\mathcal E^0(M)}\simeq
\frac{\text{Ker}_d(\mathfrak{c}^1(M)}{d(\mathfrak{Db}(M)}\simeq
H^1(M)
\]
where the last term is the cohomology space in degree one on $M$.
This entials that if $\gamma$ is a closed and rectifiable curve 
then there exists a $d$-closed 1-form
$\phi\in \mathcal E^1(M)$ and a distribution $\mu$ such that
\[
\int_\gamma=d(\mu)+\phi^1\tag{*}
\]
where this equality takes place in
$\mathfrak{c}^1(M)$.
Moreover, the $d$-closed 1-form $\phi^1$ is
unique up to
an exact smooth 1-form.
With $\gamma$  regarded as a linear functional on
$\mathcal E^1(M)$ the reader should check that
(*) gives the equality
below for every $d$-closed $\psi^1\in\mathcal E^1(M)$:
\[
\gamma(\psi^1)= \int_M\, \phi^1\wedge \psi^1
\]
\medskip

\noindent
{\bf{The $d$-closed current $\int_{\partial\Omega}$.}}
Let $\Omega$ be a connected open set in $M$
whose boundary $\partial\Omega$ is regular in the sense of
Federer. It means that
there exists a (possibly empty) closed set
$\Sigma\subset\partial\Omega$ whose 1-dimensional Haussdorff measure is zero
while 
$\partial\Omega_*=\partial\Omega\setminus \Sigma$
is locally simple and rectifiable.
That is. for each $p\in\partial\Omega_*$ there exists
a bijective map $\gamma$ from the
closed unit intervalÊ$[0,1]$
to
a connected
subset of $\partial\Omega_*$
where $p=\gamma(1/2)$ while the distinct end-points
$\gamma(0)$ and $\gamma(1)$ stay in
$\partial\Omega_*$.
The orientation  along$\partial\Omega_*$ is given by the rule of thumbs
which appears
in the classic version of
Stokes Theorem as found already by Archimedes.
The extra the  condition is that the total variation, or equivalently the
arc-length measure of
$\partial\Omega_*$ is finite while it is evaluated with
respect to a local euclidian distance function, is finite.
Under these conditions one has
\[
\int_\Omega\, d\phi= \int_{\partial\Omega_*}\, \phi
\]
for each $\phi\in \mathcal E^1(M)$.
In particular the 1-current defined via the right hand side is $d$-closed.
Notice that we do not assume that
$\partial\Omega$ is connected.
\medskip

\noindent









\noindent
{\bf{Direct images of currents.}}
Let $\rho\colon M\to N$
be a $C^\infty$-map from $M$ to another oriented 
and compact 2-dimensional manifold $N$.
Elie Cartan's
construction of differential forms on manifolds give for
each $\phi\in\mathcal E^1(N)$ a pullback
$\rho^*(\phi)\in \mathcal E^1(M)$.
The map  is continuous when $\mathcal E^1(N)$ and
$\mathcal E^1(M)$ are equipped with
their standard Frechet topologies.
In particular we regard a
parametrized curve
$\gamma$ and obtain 
a 1-current
$\rho_*(\gamma)$ on $N$ defined by
\[
\rho_*(\phi)= \int_\gamma\, \rho^*(\phi)
\]
Later on we shall use  such direct images of currents at several places.
The reader  should "accept" that it is often  more profitable to
ignore "intuitive genetroic pictures" while calculations 
are performed.
An extra merit is  that
while the integrals along the  $\gamma$ is computed, then
calcluus teaches that one can employ
different parametrisatiin  along $\gamma$. as long as they
have bounded variation and preserve the given orientation.
Notice that even if $\gamma$ from the start is a simple Jordan arc, it
may occur that $\rho_*(\gamma)$
has a more involved structure  since
the restriction of the map $\rho$ to $\gamma$ need not be
one-to-one.
\medskip


\noindent
{\bf{Intersection numbers.}}





If $\rho $ is another  closed and rectifiabsle curve we have a
similar decomposition
\[
\int_\rho=\psi^1+d(\nu)
\]
Stokes Theorenm entials that
\[
\int_M\, \phi^1\wedge \psi^1\tag{*}
\]
is independent of the chosen decompostions.
So the complex number in (*) depends only upon the ordered
pair of closed curves
$(\gamma,\rho)$ and  is denoted by
$\mathfrak{i}(\gamma,\rho)$ and called the intersection number of the closed curves.
Elementaty calculus shows
that the intersection number always in an integer,
and by continuity it follows that
if $\gamma$ and $\gamma^*$ are two homotopic closed curves
then
$\mathfrak{i}(\gamma,\rho)=
\mathfrak{i}(\gamma^*,\rho)$ for every other closed curve
$\rho$.









Following original work by Riemann one
regards
specific simple closed curves
$\gamma_1,\ldots,\gamma_{2g}$ which give
a free basis for the fundamental group $\pi_1(M)$ which is free of some rank $2g$
where $g$ is a positive number.
Here we exlude the case when
$M\simeq S^2$, i.e $M$ is not
homoemorphic to the sphere. Instead $M$ is homeomorphic to a sphere where
$g$ handles have been attached and
with this picture  in mind one can draw $2g$-many
closed curves
on $M$ whose intersection numbers
are special. More precisely, there exists 
a pair of $g$-tuples $\gamma_1,\ldots,\gamma_g$ and
$\rho_1,\ldots,\rho_g)$ , where all these $2g$ many closed curves are simple
and
\[
\mathfrak{i}(\gamma_\nu,\rho_\nu)=1\quad\colon \quad 1\leq\nu\leq g
\]
while all other intersection numbers are zero.


\newpage















\newpage


\centerline{\bf{Analysis on compact Riemann surfaces.}}
\bigskip


\noindent
Let $X$ be a compact 1-dimensional complex manifold.
Recall that its 
complex analytic structure arises via charts
$(U,z)$ where $z$ is a local coordinate on
$X$ in the open set $U$ which is biholomorphic with
the open disc $D=\{|\zeta|<1\}$ in the complex $\zeta$-plane.
Let $\rho_U\colon U\to D$ be the holomorphic map.
When a pair of charts
$U$ and $V$ overlap
their complex analytic structures are
compatible. It means that
one has a biholomorphic map
\[
\rho_{U.V}\colon \rho_U(U\cap V)\to
\rho_V(U\cap V)
\]
where 
\[
\rho_U(\zeta)=\rho_V\circ\rho_{U,V}(\zeta)\quad\colon
\zeta\in \rho_U(U\cap V)
\]
The reader should illustrate this by a suitable picture
to see how the transition functions work
in overlapping charts
Since $X$ is compact it can be covered by a finite family of charts
$\mathfrak{U}= \{U_\alpha,z_\alpha)\}$. So here $\cup \, U_\alpha=X$
and one refers to $\mathfrak{U}$ as an atlas for the complex manifold $X$.
If $U$ is an arbitrary open set
in $X$ a complex valued function $f$ in $U$ is holomorphic if
\[
f\circ \rho_\alpha^{-1}\in \mathcal O(\rho_\alpha(U\cap\, U_\alpha))
\]
hold for
every chart in the atlas.
The set of holomorphic functions in $U$ is denoted by
$\mathcal O(U)$.
Local existence of non-constant holomiorphic functions is clear since
the defintion above entails  that
if $U_\alpha$ is a chart then
$\mathcal O(U_\alpha)\simeq \mathcal O(D)$.
\medskip


\noindent
{\bf{Differential calculus  on $X$.}}
A complex analytic atlas is in particular  a
$C^\infty$-atlas on the underlying real manifold
which has real dimension two.
The space of complex-vaued $C^\infty$-functions on
$X$ is denoted by $\mathcal E(X)$.
We have also the space $\mathcal E^1(X)$
of differential 1-forms
with
$C^\infty$-coefficients.
In a chart $(U,z)$
every differential 1-form can be decomposed as
\[
a\cdot dz+b\cdot d\bar z\tag{A.0}
\]
where $a$ and $b$ are complex-valued $C^\infty$-functions.
This gives a direct sum decomposition
\[
\mathcal E^1(X)=\mathcal E^{1.0}(X)\oplus\, \mathcal E^{0,1}(X)\tag{A.1}
\]
One refers to $\mathcal E^{1,0}$ as the space of diffeential 
forms of bi-degree $(1,0)$.
Thet are characterised by the condition that
$b=0$ holds in
$(A.0)$ for every  chart.
Similarly  when $a=0$  hold we get
a differential form of bi-degree $(0,1)$.
If $g\in\mathcal E(X)$ its exterior differential $dg$
is a 1-form which has a decompostion
\[
dg=\partial g+\bar\partial g
\]
For example, one has a map
\[
\bar\partial\colon\mathcal E(X)\to \mathcal E^{0,1}(X)\tag{A.2}
\]
The Cauchy-Riemann equations applied in charts show that
the kernel in (A.2) consists of holomorphic functions and
hence the kernel is reduced to  constant functions.
\medskip

\noindent
Next, we also have differential 2-forms on $X$ which in a chart $(U,z)$
can be expressed as
\[
c(z)\cdot dz\wedge d\bar z
\]
Keeping the complex analytic structure in mind
we denote the space of differential 2-forms with
$\mathcal E^{1,1}(X)$.
The reader should
construct the  maps
\[
\bar\partial\colon \mathcal E^{1,0}(X)\to \mathcal E^{1.1}(X)\tag{A.3}
\]
\[
\partial\colon \mathcal E^{0,1}(X)\to \mathcal E^{1.1}(X)\tag{A.4}
\]
\medskip

\noindent
Next, recall that $\mathcal E(X)$ is a Frechet space
where the topology is defined via uniform convergence of
derivatives in every order.
In a similar fashion $\mathcal E^{p,q}(X)$
are Frechet spaces for every pair $0\leq p,q\leq 1$.
The reader should  check that 
the maps in (A:2-4)  are continous between these 
Frechet spaces.
Less obvious is the folloowing:
\medskip

\noindent
{\bf{A.5 Theorem.}}
\emph{Tbe range of the exterior differential maps
in (A.2-4) above are all closed.}
\bigskip




\noindent
{\bf{A.6. Remark.}}
This is the first non-trivial result
about compact Riemann surfaces.
We give the proof in (*) and remark only that it
relies upon
a classic result due to Pompieu which gives solutions to
the inhomogeneous $\bar\partial$-partial 
equation in planar
domains. More precisely, if
$U$ is an open set  in the complex $\zeta$-plane and
$g\in C^\infty(U)$ then
there exists $f\in C^\infty(U)$ such that
\[
\bar\partial(f)= g\cdot d\bar\zeta\tag{A.6.1}
\]
\bigskip

\noindent
{\bf{A.7 Currents on $X$.}}
To  begin with we have the space
$\mathfrak{Db}(X)$ of distributions which by  definition it is the 
space of continuos linear forms on the Frechet space
$\mathcal E^{1,1}(X)$, i.e.
\[
\mathfrak{Db}(X)= \mathcal E^{1,1}(X)^*
\]
Passing to differential forms
we get dual spaces
\[ 
\mathfrak{c}^{1,0}(X)=\mathcal E^{0,1}(X)^*
\quad\colon\quad
\mathfrak{c}^{0,1}(X)=\mathcal E^{1,0}(X)^*
\]
Finally, we have the space $\mathfrak{c}^{1.1}(X)$
which is the dual of $\mathcal E(X)$.
\medskip

\noindent
{\bf{B.1 The integration current $1_X$.}}
The reader should check that
the complex analytic structure on $X$ entails that its underlying
real manifold is oriented.
It  follows that if
$\gamma\in \mathcal E^{1,1}(X)$
then there exists an integral
\[
\int_X\, \gamma
\]
This defines a distribution   denoted by
$1_X$.
In general we have an inclusion
\[
\mathcal E(X)\subset\mathfrak{Db}(X)
\]
Namely, if $g$ is a $C^\infty$-function we get
a linear form on
$\mathcal E^{1,1}(X)$ defined by
\[
\gamma\mapsto \int_X\, g\cdot \gamma
\]
If
$\gamma^{1,0}$ belongs to
$\mathcal E^{1,0}(X)$
we notice that Stokes Theorem gives
\[
0=\int_X\, d(g\cdot \gamma^{1,0})
\]
Now the reader should verify that
\[
d(g\cdot \gamma^{0,1})=
\bar\partial g\wedge \gamma^{1,0}+g\cdot \bar\partial(\gamma^{1,0})
\]
Next, by definition the
$(0,1)$-current $\bar\partial g$
is defined by
\[
\bar\partial(g)\langle \gamma^{1,0}\rangle=-\int_X\, g\cdot \bar\partial(\gamma^{1,0})
\]
Keeping  signs in mind one concludes that
when $g$ from the start is identified with a distribution, then
the $(0,1)$-current $\bar\partial(g)$ is equal to the smooth
differential 1-form
of  bi-degree (0,1) arising when
$\bar\partial$ is applied to the $C^\infty$-function $g$.
\medskip

\noindent
{\bf{B.2 A  duality result.}}
We have the map
\[
\bar\partial\colon \mathcal E^{1,0}(X)\to \mathcal E^{1,1}(X)
\]
By Theorem A.5 the range is closed.
This implies that
the dual space
\[
\bigl[\, \frac{\mathcal E^{1,1}(X)}{\bar\partial \mathcal E^{1,0}(X)}\,\bigr]^*
\simeq \text{Ker}_{\bar\partial}(\mathfrak{Db}(X))\tag{B.2.1}
\]
Next, recall that  $\bar\partial$ is elliptic.Indeed, via the   classic Pompieu formula for planar
doimains  every distribution $\mu$ satisfying
the homogeneous equation $\bar\partial(\mu)=0$ is a holomorphic
function.
Since $\mathcal O(X)$ is reduced to constants the
dual space in (B.2.1)  is 1-dimensional and hence
\[
\dim_{{\bf{C}}}\, \frac{\mathcal E^{1,1}(X)}{\bar\partial \mathcal E^{1,0}(X)}=1\tag{B.2.2}
\]
Notice also that Stokes Theorem gives
\[
\int_X\, \bar\partial(\gamma^{1,0})=0\quad\colon\, \gamma^{1,0}\in \mathcal E^{,1,0}(X)
\]
from this we conclude thatif 
$\rho^{1,1}$ is a  2-form for which
$\int_X\,\rho^{1,1}\neq 0$, then
\[
\mathcal E^{1,1}(X)={\bf{C}}\cdot \rho\oplus
\bar\partial(\mathcal E^{1,1}(X))\tag{B.2.3}
\]
\medskip

\noindent{\bf{B.3 A second duality.}}
Theorem A.5 entails that
\[
\bigl[\, \frac{\mathcal E^{0,1}(X)}{\bar\partial \mathcal E(X)}\,\bigr]^*
\simeq \text{Ker}_{\bar\partial}(\mathfrak{c}^{1,0}(X))\tag{B.3.1}
\]
The right hand side is found as follows.
In a chart $(U,z)$
a current of bi-degree
$(1,0)$ is of the form
$\mu\cdot dz$ with
$\mu\in \mathfrak{Db}(U)$.
The $\bar\partial$ image of this current is
zero if and only if $\bar\partial(\mu)=0$ and as we have seen
before this implies that
$\mu$ is a holomorphic density.
Hence the right hand side in (B.3.1) consists of globally defined
\emph{holomorphic} 1-forms. This space is denoted by
$\Omega(X)$ and (B.3.1) can be expressed by
the duality formula
\[
\Omega(X)\simeq\bigl[\, \frac{\mathcal E^{0,1}(X)}{\bar\partial \mathcal E(X)}\,\bigr]^*\tag{B.3.2}
\]
\medskip

\noindent
{\bf{B.3.3 Exercise.}}
Show that (B.3.2) gives the following:
A differential form $\gamma^{0,1}$ on $X$ is $\bar\partial$-exact
if and only if
\[
\int_X\, \omega\wedge \gamma^{0,1}=0\quad\colon\, \forall\,\,
\omega\in \Omega(X)
\]
\medskip

\noindent
{\bf{B.4 Passage to currents.}}
Recall that $\mathcal E^{0,1}(X)\subset\mathfrak{c}^{0,1}$.
in ¤ xx we shall learn that
\[
\mathfrak{c}^{0,1}=\bar\partial(\mathfrak{Db}(X))+
\mathcal E^{0,1}(X)\tag {B.4.1}
\]
Moreover, a $(0.1)$-current $\rho^{0,1}$ is
$\bar\partial$-exact, i.e. of the form
$\bar\partial(\mu)$ for some
distribution $\mu$ on $X$ if and only if
\[
\rho^{1,0}(\omega)=0\quad\colon\quad \omega\in \Omega(X)\tag{B.4.2}
\]
\medskip

\noindent
{\bf{B.5 The case $X={\bf{P}}^1$.}}
Here $\Omega(X)$ is reduced to the zero space.
To see this we suppose that
$\omega$ is a globally defined holomorphic 1-form.
Now ${\bf{P}}^1\setminus \{\infty\}$ is the complex $z$-plane and here
\[
\omega= f(z)\cdot dz
\] 
where $f$ is an entire function.
At the point at infinity we have a local coordinate
$\zeta$ and
\[
\zeta= z^{-1}\quad\colon R<|z|<\infty
\]
hold for every $R>0$.
Since $\omega$ is globally holomorhpic we have
\[
\omega= g(\zeta)\cdot d\zeta
\]
when $0<|\zeta|<R^{-1}$. At the same time the reader can check that
\[
dz=-\zeta^{-2}\cdot d7zeta
\]
holds when $R<|z[<R$. Ths entails that
\[
f(z)=-z^{-2}\cdot g(1/z)\quad\colon |z|>R
\]
From this we see that
the entire function $f$ tends to zero as $|z|\to\infty$
and hence $f$ is identically zero.
So with $X={\bf{P}}^1$ one has $\Omega(X)=0$ and
then (B.4.2) entails that
\[
\mathfrak{c}^{0,1}= \bar\partial(\mathfrak{Db}(X))
\]
In other words, the inhomogeneous $\bar\partial$-equation
is always solvable.
Consider as an example a current
of the form
\[
\gamma=\mu\cdot d\bar z
\]
where $\mu$ is a measure in the complex $z$-plane with compact support.
Now there exists the Cauchy transform
\[
\widehat{\mu}(z)=\int\,\frac{d\mu(\zeta)}{z-\zeta}
\]
It is holomiorphic in
in the open set of the complex $z$-plane where
the compact set
$\text{Supp}(\mu)$ has been removed.
passing to infinity we
notice that
it extends to be holomorphic
because one has the convergent series expansion
\[
\widehat{\mu}(z)=\sum_{n=0}^\infty\,
\int\,\zeta^n|cdot d\mu(\zeta)\cdot z^{-n-1}{z-\zeta}
\]
in an exterior disc
$|z[>R$ where
the support of $\mu$ is contained in
$\{|z|\leq R\}$.
\medskip

\noindent
next, by basuc lebsgue theory one knows that
the funnction $\widehat{\mu}$ is locally integrable
in the whole complex $z$-plane and hence defines a distribution.
Finally, Cacuhy's residue formula shows that
the distribution derivative
\[
\frac{\bar\partial\widehat{\mu}}{\bar\partial\bar z}=\pi \cdot \mu
\]
So we get
\[
\bar\partial(\pi^{-1}\cdot \widehat{\mu})=\mu\cdot d\bar z
\]




















\newpage


\centerline{\bf{C. Some sheaves and their cohomology}}.
\medskip


\noindent
Let $X$ be a compact complex  analytic manifold.
Classic  facts due to Cauchy and Pompieu applied to charts in $X$ 
give  an exact sequence of sheaves
\[
0\to \mathcal O_X\to \mathcal E_X\overset{\bar\partial}\to, \mathcal E_X^{0,1}\to 0\tag{C.0}
\]
Using $C^\infty$-parotions of unity and Leray's theory about  cohomology with
values in sheaves
one gets
\[
H^1(\mathcal O_X)\simeq \frac{
\mathcal E^{0,1}(X)}{\bar\partial(\mathcal E(X)}\tag{C.1}
\]
where the left hand side is the first cohomology groups with
values in the sheaf
$\mathcal O_X$. The reader may also notice that when Leray's long exact sequence for sheaf cohomology is applied to (C.0), then it follows that
\[
H^2(\mathcal O_X)=0\tag{C.2}
\]
Next, we have also the exact sheaf sequence
\[
0\to {\bf{C}}_X\to \mathcal O_X\overset{\partial}\to \Omega_X\to 0\tag{C.3}
\]
Since $H^0({\bf{C}}_X)= H^0(\mathcal O_X)= {\bf{C}}$ and (C.2) holds
one gets the following   exact sequence of complex vector spaces:
\[
0\to \Omega(X)\to H^1({\bf{C}}_X)\to
 H^1(\mathcal O_X)\to H^1(\Omega _X)\to H^2({\bf{C}}_X)\to 0\tag{C.4}
\]
Next, we have
also the following exact sheaf sequence
\[
0\to \Omega_X\to \mathcal E^{1,0}_X\overset{\bar\partial}\to \mathcal E_X^{1,1}\to 0\tag{C.5}
\]
This gives the equality
\[
H^1(\Omega_X)\simeq\frac{\mathcal E^{1,1}(X)}{\bar\partial(\mathcal E^{1,0}(X))}\tag{C.6}
\]
The right hand side rsssembles the quotient in
(B.2.2).
Indeed, we can regard the 7emph{conjugate} analytic structure on
the underlying real manifold of $x$ where the sheaf of holomorphic functions
are compex cojugates of sections in
$\mathcal O_X$. From this the reader may conclude via (B.2.2)
that the rifht hand side in (C.5)
is a 1-dimensional vector space. Hence we have 
\[
\dim_{{\bf{C}}}\,H^1(\Omega_X)=1\tag{C.7}
\]
\medskip

\noindent
Next, recall that
$H^2({\bf{C}}_X)={\bf{C}}$. Together with (C.7) we conclude that
 (C.4) gives the
short exact sequence
\[
0\to \Omega(X)\to H^1({\bf{C}}_X)\to
 H^1(\mathcal O_X)\to 0\tag{C.8}
\]
Topology teaches that
the cohomology space
$H^1({\bf{C}}_X)$Êis finite dimensional.
Hence (C.8) implies that both
$\Omega(X)$ and $H^1(\mathcal O_X)$ are finite dimensional complex vector spaces.
Finally, (B.3.2) and (C.1) give
\[
\Omega(X)\simeq\bigl [\, H^1(\mathcal O_X)\,\bigr]^*\tag{C.9}
\]
In particular the complex vector spaces
$\Omega(X)$ and $H^1(\mathcal O_X)$ have the same dimension.
This equality and (C.8) give
\[
\dim H^1({\bf{C}}_X)= 2\cdot \dim \Omega(X)\tag{C.10}
\]
The equality (C.10) is fundamental  during the study of compact
Riemann surfaces. 
A notable point is that
the cohomology group $H^1({\bf{C}}_X)$ only depends upon the
topological space $X$ and not upon its particular complex structure.

\bigskip

\noindent
{\bf{C.10 A duality for currents.}}
In planar domains it is wellknown that the
inhomogenous $\bar\partial$-equation is locally solvable on distributions.
Since the $\bar\partial$-kernel on $\mathfrak{Db}_X$ is $\mathcal O_X$
one has an exact sequence
\[
0\to \mathcal O_X\to \mathfrak{Db}_X\overset{\bar\partial}\to
\mathfrak{c}^{0,1}_X\to 0
\]
Passing to cohomology and using 
$C^\infty$-partitions of the unity, it follows that
\[
H^1(\mathcal O_X)\simeq \frac{\mathfrak{c}^{0,1}_X}{
\bar\partial(\mathfrak{Db}(X)}\tag{C.10.1}
\]
\medskip

\noindent
{\bf{Exercise.}} Deduce from the above that
\[
\Omega(X)\simeq\bigl[\, \frac{\mathfrak{c}^{0,1}_X}{
\bar\partial(\mathfrak{Db}(X)}\,\bigr]^*\tag{C.10.2}
\]
Conclude that the implication below holds for
each 
$\gamma\in \mathfrak{c}^{0,1}$:
\[
\gamma(\omega)=0\quad\colon\,\forall\,\, \omega\in \Omega(X)
\implies \gamma\in \bar\partial(\mathfrak{Db}(X))\tag{C.10.3}
\]
\medskip

\noindent
{\bf{C.11 A decomposition theorem.}}
Since $X$ in particular is an oriented and compact real manifold
one has
\[
H^1({\bf{C}}_X)\simeq\frac{\text{Ker}_d(\mathcal E^1(X)}{d(\mathcal E(X)}\tag{C.11.1}
\]
Next, on $X$ there also exists
the anti-holomorphic differential forms of bi-degree
$(0,1)$, i.e differential forms  $\gamma\in \mathcal E^{0,1}(X)$ for which
$\partial(\gamma)=0$.
This space is denoted by $\overline{\Omega}(X)$.
Using the conjugate complex analytic structure one has another compact
complex manifold $\overline{X}$
where
$\overline{\Omega}(X)$ is the space of holomorphic 1-forms.
Since $X$ and $\overline{X}$ have the same underlying real manifold, it follows from
(C.10) that
\[
\dim H^1({\bf{C}}_X)= 2\cdot \dim \overline{\Omega}(X)\tag{C.11.2}
\]
Using  this we shall prove
\medskip

\noindent
{\bf{C.11.3 Theorem.}}
\emph{One has a direct sum decomposition}
\[
\text{Ker}_d(\mathcal E^1(X))=
d(\mathcal E(X))\oplus \Omega(X)\oplus\overline{\Omega}(X)
\]
\medskip

\noindent
\emph{Proof}
To begin with we notice that
\[
\Omega(X)\,\cap \overline{\Omega}(X)= \{0\}
\]
Counting dimensions this follows if we prove that
a 1-form $\gamma)\omega+\mu$ cannot be $d$-exact
when $\omega\in \Omega(X)$ and $\mu\in \overline{\Omega}(X)$
where at least one these froms is not identically ero.
For suppose that
$\gamma=dg$ is $d$-exact.
If $\omega$ is not identically zero there exists
the conjugate
form
$\bar\omega\in\overline{\Omega}(X)$.
Now Stokes Theorem gives
\[
0=\int_X\, dg\cdot \bar\omega)=\int_X(\omega+\mu)\wedge\bar\omega=
\int_X(\omega\wedge\bar\omega
\]
Now the reader can check that
the last integral is $\neq 0$ when $\omega$ is not identically zero.
hence $\gamma\in d(\mathcal E(X))$ implies that
$\Omega=0$ and in the same way we find that
$\mu=0$ which proves Theorem C.11.3.








\newpage


\centerline{\bf{D. Existence of meromorphic functions.}}
\bigskip


\noindent
On $X$ there exists the sheaf
$\mathcal M_X$ whose sections are meromorphic  functions.
Subsheaves arise via  constraints on  poles.
In particular, let $p\in X$ be a given point and
$m$ a positive integer.
Denote by $\mathcal O_X[* mp]$
the sheaf whose sections are meromorphic functions on
$X$ which are holomorphic in $X\setminus\{p\}$ and have
poles of order $\leq m$ at $p$.
If $(U,z)$ is a chart where $p$ corresponds to
the origin we seee that
\[
\mathcal O_X[* mp]\,|U= z^{-m}\cdot \mathcal OX|U
\]
Taking Laurent exapnsions
every section in the right hand side is of the form
\[
f+\frac{c_1}{z}+\ldots+\frac{c_m}{z^m}
\]
where $f\in \mathcal O_X$ and $\{c_\nu\}$ is an $m$-tuple of complex numbers.
Expressed by  sheaves it gives
an exact sequence
\[
0\to \mathcal O_X\to \mathcal O_X[*mp]\to S_p^m\to 0\tag{D.1}
\]
where $S_p$ is the scyscraper sheaf suppotet  by $\{p\}$
and
the stalk $S_p(p)$ is an $m$-dimensional vector space.
Passing to long exact sequence of cohomology the reader 
can verify that there is an exact sequence:
\[
0\to {\bf{C}}\to H^0(\mathcal O_X[*mp])\to
{\bf{C}}^m\to 
H^1(\mathcal O_X)\to H^0(\mathcal O_X[*mp])\to 0\tag{D.1.1}
\]
\medskip

\noindent
{\bf{D.2 Exercise.}}
Use that the vector space 
$H^1(\mathcal O_X)$ is $g$-dimensional and conclude that
\[
\dim_{{\bf{C}}}\, 
H^0(\mathcal O_X[*mp])=m-g+1+
\dim_{{\bf{C}}}\, 
H^1(\mathcal O_X[*mp])\geq m-g+1\tag{D.2.1}
\]
\medskip

\noindent
In particular the left hand side is $\geq 2$ if $m=g+1$
which means that
apart from constants, there exists at least one
constant global section in 
$\mathcal O_X[*(g+1)p]$.
Hence we have proved:

\bigskip

\noindent
{\bf{D.3 Theorem.}}
\emph{For every $p\in X$ there exists a non-constant 
meromorphic function $f$  in $X$ with no poles in
$X\setminus{p}$ while
the order of the pole at $p$ is at most $g+1$.}











\newpage



\centerline{\bf{Weierstrass' points.}}

\bigskip

\noindent
Let $X$ be a compact Riemann surface
whose genus number $g$ is $\geq 2$.
Removing  a point $p\in X$
we get  the space
$\mathcal O(X\setminus\{p\})$.
If $(U,z)$ is a chart centered at $p$
where $p$ corresponds to $z=0$, then every
$f\in\mathcal O(X\setminus\{p\})$
restricts to a holomorphic function in
the punctured disc
$0<|z|<1$
and we can regard its Laurent series:
\[
f(z)=
\sum_{\nu=1}^\infty\ c_\nu\cdot z^{-\nu}+\sum_{\nu\geq 0}\, d_\nu\cdot z^\nu
\]
The negative part of the Laurent series is denoted by $f_*(z)$.
If $f_*=0$ then $f$ is globally holomorphic and hence reduced to
a constant.
So 
\[
f\mapsto f_*(z)+ d_0
\]
yields an  injective 
map from $\mathcal O(X\setminus\{p\})$ 
into the space of
non-positive Laurent series at $z=0$.
We are going to study the range of this map.
Denote by $\mathcal L$
the space 
of all non-positive Laurent series, where we recall that a negative
series
\[
\sum_{\nu=1}^\infty\ c_\nu\cdot z^{-\nu}\in\mathcal L
\]
if and only if
\[
\sum_{\nu=1}^\infty\, |c_\nu|\cdot R^\nu<\infty
\] 
for all $R>0$.
In particular $\mathcal L$ contains the $g$-dimensional subspace
formed by Laurent series given by
finite series:
\[
\rho(z)= c_1z^{-1}+\ldots+c_g\cdot z^{-g}
\]
where $\{c_\nu\}$ is a $p$-tuple of complex numbers.
Let $\mathcal L[p]$ denote this subspace of
$\mathcal L$.
\medskip

\noindent
{\bf{E.1 Theorem.}}
\emph{Outside a finite set ${\bf{W}}$ in $X$
one has} 
\[ 
\mathcal L=\mathcal L[p]\oplus \mathfrak{Im}(\mathcal O(X\setminus\{p\})
\]
\medskip

\noindent
{\bf{E.2 Remark.}}
In ¤xx we show that
the exceptional set
${\bf{W}}$ is non-empty when $g\geq 2$,
If (*) holds above
it follows that when $m>g$
then  there exists a unique $g$-tuple $\{c_\nu\}$ such that 
\[ 
z^{-m}=c_1z^{-1}+\dots+c_gz^{-g}+ \mathfrak{Im}(\phi)
\]
where $\phi$ is holomorphic in
$X\setminus\{p\}$.
Herte the negative Laurent series of $\phi$ is finite
at $p$ which implies that
$\phi$ is a globally defined meromorphic function
with a pole of order $m$ at $p$ whose negative Laurent expnasion at $p$
is of the form
\[
z^{-m}+c_1z^{-1}+\dots+c_gz^{-g}
\]
where the $g$-tuple $\{c_\nu\}$ is uniquely determined and depends on
the chosen integer $m$.
At the same time
the direct dum in (*) entails that
there do not exist non-constant meromorphic functions
which are holomorphic in
$X\setminus\{p\}$ while the order of
the pole at $p$ is $\leq g$.
\medskip

\noindent
The proof of Theorem E.1 requires several steps.
We are given a point
$p\in X$ and let $(U,z)$ be a chart
around $p$ where $p$ corresponds to $z=0$.
Residue calculus gives
a $g$-tuple of 
currents defined by
\[
\rho_\nu=\bar\partial(z^{-\nu})\quad\colon\quad \nu=1,\ldots,g
\]
Each current is supported by the singleton set $\{p\}$
and extends to a current on $X$ supported by $p$.
If $\Psi^{1,0}\in\mathcal E^{1,0}(X)$
we can regard its restriction to $U$ and write
\[
\Psi^{1,0}|U= \psi(z)\cdot dz
\]
with $\psi\in C^\infty(U)$.
Residue calcluus teaches that
\[
\rho_1(\Psi^{1,0})= 2\pi i\cdot \psi(0)
\]
If $\nu\geq 2$ the reader may verify that
\[
\rho_\nu(\Psi^{1,0})= \frac{(-1)^{\nu-1}}{(\nu-1)!}\cdot
\partial^{\nu-1}\psi/\partial z^{\nu-1}(0)
\]
The construction of the $\rho$-currents
is not intrinsic, i.e.
the $g$-tuple  depends on the chosen chart around $p$.
But the reader can check that
the $g$-dimenbsional vector space
in $\mathfrak{c}^{0,1}(X)$
generated by
$\{\rho^\nu\,\colon 1\leq \nu\leq g\}$
does not depend on the chosen chart around $p$.
Let us denote it by $\mathcal W(p)$.
The major step towards the proof of Theorem E.1
is the following:


\medskip

\noindent
{\bf{E.3 Theorem.}} \emph{Outside a finite set
${\bf{W}}$  in $X$ one has
the direct sum decomposition}
\[
\mathfrak{c}^{0,1}(X)=\bar\partial(\mathfrak{Db}(X))\oplus\, \mathcal W(p)\tag{E.3.1}
\]
\bigskip

\noindent
\emph{Proof.}
The duality result in ¤ xx gives (E.3.1)
if
the $g$-tuple
$\{\rho^\nu\}$ restrict to 
${\bf{C}}$-linearly independent in the dual space
$\Omega(X)^*$.
To check when this holds we
consider a basis $\omega_1,\ldots,\omega_g$ in the $g$-dimensional vector space
$\Omega(X)$.
In a chart
$(U,z)$ centered at a point $p_0\in X $ we can write
\[
\omega_j= f_j(z)\cdot dz\tag{i}
\]
where Ê$\{f_j\}$ are ${\bf{C}}$-linearly 
independent in $\mathcal O(U)$.
The general result in ¤ xx  entails that 
the determinant function
\[
\mathcal F(z)= \det\bigl(\partial f_j^\nu/\partial z^\nu(z)\tag{ii}
\]
formed by the $g\times g$-matrix with
elements as above is not identically zero.
Now linear algebra shows that
$\{\rho_\nu\}$ restrict to linearly independent functionals
on $\Omega(X)$ at every $z|in U$ for ehich
$F(z)\neq 0$.
Since the zero set of $F$ in the chart $U$ is discrete
and we can cover
$X$ by a finite famliy of charts, it follows that
(E.3.1) holds outside a finite set
${\bf{W}}$.


\medskip

\noindent
{\bf{E.4 How to find ${\bf{W}}$.}}
In each  chart $(U,z)$ as above we have
the $\mathcal F$-functions from (ii).
If $(U_\alpha,z_\alpha)$ and $(U_\beta,z_\beta)$ is a pair of charts
in $X$ where $U_\alpha\cap U_\beta\neq\emptyset$
we get two $g$-tuples  of analytic functions by
\[
\omega_j|U_\alpha= f_j^\alpha\cdot dz\quad\colon\quad
\omega_j|U_\beta= f_j^\beta\cdot dz_\beta
\]
When $z_\beta=z_\beta(z_\alpha)$ is regarded as
an analytic function in $U_\alpha\cap U_\beta$ one has the equations
\[
f_j^\alpha=\frac{\partial z_\beta}{\partial z_\alpha}\cdot f_j^\beta\tag{E.4.1}
\]
for each $j$ in $U_\alpha\cap U\beta$.
\medskip

\noindent
{\bf{E.4.2 Exercise.}} Show by using
rules for calcuating determinsnts that
(E.4.1) gives
the equation
\[
\mathcal F_\alpha=\bigl(\frac{\partial z_\beta}{\partial z_\alpha}\bigr)^{g(g-1)/2}\cdot F_\beta(z)
\]
So with $N=g(g-1)/2$
the family $\{\mathcal F_\alpha\}$ which arises when
$X$ is covered by a finite number of charts, is a global section of
the $N$-fold product of the holomorphic line bundle $\Omega_X$.
By (xx) the
set of xeros counted with multiplicities  of every global section
in $\Omega_X$ is equal to $2(g-1)$.
So by the general result in ¤ xxx the
zero set of the $\mathcal F$-family counted with multiplicities is equal to
$g(g-1)^2$. Since $g\geq 2$ this is a positive integer and hence
the set ${\bf{W}}$ is non-empty.
\bigskip

\noindent
{\bf{Remark.}} In the literature one refers to
${\bf{W}}$ as the set of Weierstrass' points in $X$.
The determination of ${\bf{W}}$ for a given $X$ with genus $\geq 2$
is in general not easy.
From the above ${\bf{W}}$ contains at most
$(g-1)^2\cdot g$ many distinct points. 
In general the number of points can be
strictly smaller.
Weierstrass investigated
${\bf{W}}$ for special families of compact Riemann surfaces.
See ¤ xx for some comments.
\bigskip

\centerline {\bf{Proof of Theorem E.1}}

\bigskip

\noindent
Consider a point $p\in X$ which is outside ${\bf{W}}$ and let $(U,z)$ be a chart 
centered at $p$.
Let $U^*=U\setminus\{p\}$ be the punctured open disc.
In $X$ we also have the open set
$X\setminus\{p\}$
which can be regarded as an open Riemann surface.
The theorem by Behnke and Stein from
the chapter devoted to open Rieann surfaces
gives
$H^1(X\setminus\{p\},\mathcal O)=0$.
The cohomology in the  disc $U$ is also zero.
Hence the open covering of $X$ given by the pair
$\mathfrak{U}= (U,X\setminus\{p\})$
is acyclic with respect to the sheaf
$\mathcal O_X$. So  Leray's acyclicity theorem gives
\[
H^1(X,\mathcal O_X)\simeq \frac{\mathcal O( U^*)}{
\delta(C^0(\mathfrak{U},\mathcal O_X))}\tag{i}
\]
where
\[
\delta\colon \mathcal O(U)\oplus \mathcal O(X\setminus\{p\})\to
\mathcal O(U^*)
\] 
is the Cech coboundary map.
Next, the $g$-tuple $\{z^{-\nu}\colon \nu=1,\ldots,g\}$
are holomorphic in $U^*$
and  their images in the right hand side from (i) give
elements in
$H^1(X,\mathcal O_X)$ denoted by
$\{[z^{-\nu}]\}$.
\medskip

\noindent
{\bf{Exercise.}}
Recall  that
\[
H^1(X.\mathcal OX)= \frac{\mathfrak{c}^{0,1}}{\bar\partial(\mathfrak{Db}(X)}
\]
Since $p$ is outside ${\bf{W}}$
the last quotient is equal to $\mathcal W(p)$.
Conclude from this that
the $g$-tuple
$\{[z^{-\nu}]\}$ is a basis in the $g$-dimensional vector space
$H^1(X,\mathcal O_X)$.
\medskip

\noindent
Let us then consider some
$g\in\mathcal O(U^*)$ which has a  Laurent series
\[
g(z)= \sum_{\nu=1}^\infty\ c_\nu\cdot z^{-\nu}+
\sum_{\nu=0}^\infty\ d_\nu\cdot z^{\nu}
\]
By the Exercise  there exists
a unique $g$-tuple of complex numbers
$a_1,\ldots,a_p$
such that
the image of $g$ in
$H^1(X,\mathcal O_X)$ is equal to $\sum\, a_\nu\cdot [z^{-\nu}]$.
Hence (i) gives a pair $\phi(z)\in\mathcal O(U)$ and $f(z)\in \mathcal O(X\setminus\{p\}$
such that
\[
g(z)-\sum\,\rho_\nu\cdot z^{-\nu}=\phi(z)+f(z)
\]
where $\phi(z)\in\mathcal O(U)$ and $f(z)\in \mathcal O(X\setminus\{p\}$.
Regarding the negative Laurent series it follows that
\[
g_*(z)= \sum\, a_\nu\cdot z^{-\nu}+f_*(z)\tag{ii}
\]
Here $g$ was arbitrary in
$\mathcal O(U^*)$ and hence the proof of Theorem E.1 is finished.
















\newpage










 
 
 
 

\centerline{\bf{F. Abel's theorem.}}



\bigskip


\noindent
A divisor $D$ on $X$ consists of
an assignement of integers $\{\mu_\nu\}$ to a finite set of points $\{p_\nu\}$
in $X$. One writes
\[
D= \sum\, \mu_\nu\cdot \delta(p_\nu)
\]
The $\mu$-integers may be positive or negative.
The degree is defined by
\[
\deg D= \sum\,\mu_\nu
\] 
while the finite set $\{p_\nu\}$ is called the support of $D$.
Next we construct a class of 1-currents.
In general, let $\gamma\colon [0,1]\to X$
be an $X$valued function on the closed unit interval
We assume that $\gamma$ is continuous and has a
finite total variation. The last condition means that
there exists a constant $C$ such that
\[
\sum_{\nu=0}^{\nu=N-1}\, d(\gamma(t_{\nu+1},\gamma(t_\nu)\leq C
\]
for all sequences $0=t_0<t-1<\ldots<t_N=1$
Here $d$ is some  distance function 
on $X$ regarded as a metric space which in charts
is equivsoent to
the euclidian distance.
Every such $\gamma$ gives a current of degree one
acting on $\mathcal E^1(X)$ by 
\[
\alpha\mapsto \int_\gamma \,\alpha\tag{*}
\]
\medskip

\noindent
{\bf{Exercise.}} Explain how the classical Borel-Stieltjes integrals for functions
with bounded variation
defines the integral in the right hand side.
Show also that
\[
\int_\gamma\, dg= g(\gamma(1))-g(\gamma(0))
\]
hold for every $g\in\mathcal E()$.
One refers to (*) as an integration current of degree one.
More generally we can take a finite sum of such
currents and get the integration current
$\Gamma$ defined by
\[
\Gamma(\alpha)= \sum\, \int_{\gamma_j}\,\alpha
\]
Let $D=\sum\,\mu_\nu\cdot \delta(p_\nu)$ be a divisor of
degreee zero.
An integration current $\Gamma$ is said to be associated with
$D$ if the equality below hold for every
$g\in\mathcal E(X)$:
\[
\Gamma(dg)= \sum\, \mu_\nu\cdot g(p_\nu)
\]
\medskip

\noindent
{\bf{F.1 Principal divisors.}}
Let $f$ be a non-constant meromorphic function.
Now we have the finite set of poles $\{p_\nu\}$ and the finite set of zeros
$\{q_j\}$.
We associate the divisor
\[
\text{div}(f)= \sum\, \mu_k\cdot \delta(p_k)-\sum\, \mu_j\cdot \delta(q_j)
\]
Here $\mu_k$ is the order of the pole of $f$ at every $p_\nu$, while
$\mu_j$ is the order of a zero at $q_j$.
By the result in ¤ xx this divisor has degree zero.
A divisor $D$ of degree zero is called principal if
it is equal to $\text{div}(f)$ for some
$f\in\mathcal M(X)$.
Notice that if $f$ and $g$ is a pair of non-constant meromorphic functions such that
$\text{div}(f)= \text{div}(g)$, then
$f/g$ is a holomorphic function on $X$ and hence reduced to a non-zero constant.
Introducing the multiplicative group
$\mathcal M(X)^*$ of non-constant meromorphic functions
this means that one has an injective map
\[
\frac{\mathcal M(X)^*}{{\bf{C}}^*}\to\mathcal D_0
\]
where $\mathcal D_0$ is the additive group of divisors whose degree are zero.
The  theorem below describes the range of this map.

\medskip

\noindent
{\bf{F.2 Theorem.}}
\emph{A divisor $D$ of degree zero
is principal if and only if there
exists an integration current $\Gamma$ associated with
$D$  such that}
\[
\Gamma(\omega)=0\quad\colon \,\,\gamma\in \Omega(X)
\]
\medskip

\noindent
The proof requires several steps.
First we shall show the "if part", i.e. if 
$\Gamma$ exists so that (*) holds then
the divisor $D$ is principal.
To achieve this we first
perform a local construction in the complex plane.
\medskip

\noindent
{\bf{F.3 A class of currents in ${\bf{C}}$.}}
In the complex $z$-plane we consider
a point $z_0$ where 
\[
0<|z_0|<r<1
\]
holds for some $0<r<1$.
It is easily seen that there exists
a $C^\infty$-function $a(z)$  in ${\bf{C}}$
which never is zero and the function
\[
\phi(z)= \frac{z}{z-z_0}\cdot a(z)
\]
is identically one when
$|z|\geq r$.
Now $z\mapsto \frac{1}{z-z_0}$ is locally integrable around
$z_0$ and hence $\phi$ belongs to 
$L^1_{\text{loc}} ({\bf{C}})$ and is therefore a distribution.
\medskip

\noindent
Cauchy's residue formula can be expressed by saying
the $\bar\partial$-image of the $\frac{1}{z}$
is equal to the $(0,1)$-current
$2\pi i\cdot \delta(0)d\bar z$ where $\delta(0)$ is the Diraqc distribution
at the origin.
Using this the reader can check that
\[
\bar\partial(\phi)=
 \frac{z}{z-z_0}\cdot \bar\partial(a)+z_0a(z_0)\cdot \delta(z_0)d\bar z\tag{i}
 \]
 from (i) the reader should also check that
 \[
 \phi^{-1}\cdot \bar\partial(\phi)= a^{-1}\cdot \bar\partial(a)\tag{ii}
 \]
 \medskip
 
 \noindent
 {\bf{F.4 The current $\phi^{-1}\cdot \partial(\phi)$.}}
 To begin we one has
 \[
 \partial(\phi)=\frac{a(z)}{z-z_0}\cdot dz-
 \frac{za}{(z-z_0)^2)}\cdot dz+\frac{z}{z-z_0}\cdot \partial a\tag{F.4.1}
 \]
 Above $(z-z_0)^{-2}$ is the principal value distribution
 defined as in ¤ xx.
 \medskip
 
 \noindent
 {\bf{ Exercise.}}
 Use (F.4.1) to establish the equation
 \[
 \phi^{-1}\cdot \partial(\phi)=z^{-1}\cdot dz-(z-z_0)^{-1}\cdot dz+
 a^{-1}\cdot \partial(a)\tag{F.4.2}
 \]
 \medskip
 
 \noindent
 {\bf{Exercise.}}
 Use Stokes Theorenm and Cauchy's residue fornula to
 prove that when the 1-current
 \[
 \phi^{-1}\cdot d\phi=  \phi^{-1}\cdot \partial(\phi)+ \phi^{-1}\cdot \bar \partial(\phi)
 \] 
 is applied to $dg$ for some
 $g\in C_0^\infty({\bf{C}}$, then
 \[
 \phi^{-1}\cdot d\phi<dg>\, = 2\pi i\cdot (g(0)-g(z_0)\tag{F.4.3}
 \]
\medskip


\noindent
 Let us now consider an integration current
 $\Gamma$ given by a finite sum
 $\sum\,\gamma_j$ where each $\gamma_j$ has compact support in
 a chart
 $(U_j,z_j)$ in $X$ and the end-points of
 $\gamma_j$ are $z_j=0$ and $z_j=z_j^*$
 with $0<|z_j^*|<r<1$ and $U_j$ is a chart defined by
 $\{|z_j|<1|]$.
In $X$ the point $z_j=0$ is denoted by $q_j$ while $z_j^*$ corresponds to a
point $p_j$.
It follows that 
 \[
 \int_\Gamma \, dg=\sum_{j=1}^{j=N}\, g(p_j)-g(q_j)\tag{F.5}
 \]
for every $g\in \mathcal E(X)$.
 Next, for each $j$ we apply the local contruction the chart
 and find a function
 $\phi_j$ in $X$ which is identically one
 in $X\setminus \{|z_j|\leq r\}$ such that 
 \[
 \phi_j^{-1}\cdot d\phi_j<dg>=2\pi i\cdot \int_{\gamma_j}\, dg\quad\colon\, g\in \mathcal E(X)
 \]
 More generally, since
 $d$-closed 1-forms in the chart $U_j$ are $d$-exact the re4ader should check that
 (F.5) implies that
 \[
 \phi_j^{-1}\cdot d\phi_j<\alpha>=2\pi i\cdot \int_{\gamma_j}\,\alpha\tag{F.6}
 \]
 hold for every $d$-closed differential 1-form $\alpha$.
 Let us now consider the function
 \[
 \Phi= \prod_{j=1}^{j=N}\, \phi_j
 \]
 \medskip
 
 \noindent
 {\bf{F.7 Exercise.}}
 From the above the
 reader should check  that
 the construction of the $\phi$-functions imply that
 $\Phi$ is a zero-free
 $C^\infty$-function
 in $X\setminus \{q_j,p_j\}$, i.e. in the open complement of
 the finite set
  which is the union of these   $q$  and  $p$ points.
Moreover,  additivity for logarithmic derivatives and 
(F.6) above gives
\[
\Phi^{-1}\cdot d\Phi<\alpha>=
\int_\Gamma\, \alpha\tag{F.7.1}
\]
for every $d$-closed 1-form
$\alpha$. Finally, show that
\[
\Phi^{-1}\cdot \bar\partial(\Phi)=
\sum\, a_j^{-1}\cdot \bar\partial(a_j)\tag{F.7.2}
\]
where the right hand side is a smooth $(0,1)$-form.
\medskip

\noindent
{\bf{F.8 A special case.}}
Suppose that $\Gamma$ is such that
\[
\int_\Gamma\, \omega=0\quad\colon\quad \omega\in\Omega(X)\tag{F.8.1}
\]
The equality in (F.7.1) applied to  $d$-closed holomorphic 1-forms
and
Theorem ¤ xx  entail  that
the smooth $(0,1)$-form
$\Phi^{-1}\cdot \bar\partial(\Phi)$ from (F.7.2) is $\bar\partial$-exact.
Thus, we can find $G\in \mathcal E(X)$ such that
\[
\bar\partial(G)= \Phi^{-1}\cdot \bar\partial(\Phi)\tag{F.8.2}
\]
\medskip


\noindent
{\bf{Exercise.}}
Put
\[
\Psi=e^{-G}\cdot \Phi
\]
deduce from the above  that
$\bar\partial(\Psi)=0$ holds in
$X\setminus \{q_j,p_j\}$ and hence $\Psi$ is holomorphic in
this open subset of $X$
Show also  that the local constructions of the
$\phi$-functions inside the charts
$\{U_jz_j\}$ entail  that
$\psi$ extends to a mermorphic function in
$X$ whose princial divisor is equal to
\[
\sum\, \delta(q_j)-\sum \delta(p_j)
\]
Funally the reader should confirm that the constructions above
prove the "if part" in Theorem F.2.
\medskip


\centerline{\emph{F.9 Proof of the "only if part"}}
\medskip

\noindent 
Here we are given a non-constant meromorphic funvtion
$f$.
We shall condtruct an integration chain $\Gamma$ as follows:
Frst $f\colon X\to {\bf{P}}^1$ is a holomorphic map.
With $s=f(x)$
we recall from (xx) that the number critical $s$-points in
the complex $s$-plane is finite.
In ${bf[P})^1$ we choose a simple
curve $\gamma_*$ with intial point at $s=0$ and end-point at
$s=|nfty$, while
$\gamma_*$ avoids the critical points $s\neq 0$ in
${\bf{C}}$.
of course, while this is done we can choose
$\gamma_*$ so that it is a smooth curve
on the $C^\infty$-manifold ${\bf{P}}^1$.
\medskip

\noindent
{\bf{The inverse image $f^{-1}(\gamma_*)$.}}
Let $N=\deg(f)$.
Since $\gamma_*$ avoids $f$-cirtical points we see that
\[
f^{-1}(\gamma_*\setminus \{0,\infty\})= \gamma_1\cup\ldots\cup\,\gamma_N
\]
where $\{\gamma_j\}$ are disjoint  curves in
$X$, each of which is oriented via
$\gamma_*$ which from the start moves from
$s=0$ to $s=\infty$.
\medskip

\noindent
{\bf{Exercise.}}
Show that the closure $\bar\gamma_j$ yields a rectifiable  curve
whose initial point is zero of $f$ and the end-point a pole.
Put
\[
\Gamma=\sum\, \bar\gamma_j
\]
and conclude from the above that
$\Gamma$ is associated to the principal divisor of $f$.
The proof of the "onmy if part" is therefore finished if we show that
\[
\int_\Gamma\,\omega=0\quad\colon\quad \omega\in \Omega(X)\tag{*}
\]
To prove (*) we shall  use
a certain trace map.
First, a holomorphic 1-form
$\omega$ on $X$ is regared as a $\bar\partial$-closed current with
bi-degree $(0,1)$.
Since the amp $f\colon X\to {\bf{P}}^1$ is proper
there exists the direct image current
$f_*(\Omega$ and we recal from general facts that
the passage to direct image currents commute with
the $\bar\partial$-operator.
hence $\bar\partial(f_*(\Omega))==$ and since
$\bar\partial$ is elliptic it follows that
$f_*(\omega)$ is a holomorphic 1-form on
${\bf{P}}^1$.
By the result in Exercise xx there does not exist non-zero globally defined
holomorphic 1-forms on the projective line.
hence
\[ 
f_*(\omega)=0\tag{**}
\]
In partocuar we have
\[
\int_{\gamma_*(\epsilon)}\, f_*(\omega)=0
\]
where $\gamma_*(\epsilon)$ is the closed 
curve given by $\gamma$ intersected with
$\{\epsilon\leq |s| \leq \epsilon^{-1}\}$
for a small $\epsilon>0$.
\medskip

\noindent
{\bf{Exercise.}}
Put $\Gamma(\epsilon)= f^{-1}(\gamma(\epsilon)$
and dediuce from (xx) that
\[
\int_{\Gamma(\epsilon)}\, \omega=0
\]
Finally, pass to the limit as $\epsilon\to 0$ and conclude that (*) holds which finishes the proof of
the "only if part".



 
 
 
 \newpage
 
 \centerline{\bf{G. Holomorphic line bundles.}}
 
 
\bigskip

\noindent
There exists the multiplicative sheaf
$\mathcal O_X^*$ whose sections are zero-free
holomorphic functions.
every such function is locally $e^g$ with $g\in \mathcal O_X$
where $g$ is determined up to an integer multiple of $2\pi i$.
This gives an exact sheaf sequence
\[
0\to {\bf{Z}}_X\to \mathcal O_X\overset{\exp}\to \mathcal O^*_X\to 0
\]
where $\exp$ sends $g$ to $e^{2\pi i g}$
and ${\bf{Z}}_X$ is the sheaf of locally constant  integer-valued functions on
$X$.
Notice that global sections in
$\mathcal O_X^*$ are reduced to non-zero complex numbers
and we have the short exact sequence
\[
0\to {\bf{Z}}\to {\bf{C}}\overset{\exp}\to {\bf{C}}^*\to 0
\]
Conclude that one has an exact sequence
\[
0\to H^1({\bf{Z}}_X)\to H^1(\mathcal O_X)\to
H^1(\mathcal O_X^*)\to H^2({\bf{Z}}_X)\to 0\tag{G.1}
\]
As explained in ¤ xx
the cohomology group $H^1({\bf{Z}}_X)$
is a free abelian group of rank $2g$
while
$H^2({\bf{Z}}_X)={\bf{Z}}$.























 
 

 
 
 
 
 
 
 
 

\newpage











\centerline{\bf{Compact Riemann surfaces.}}

\bigskip

\noindent
A compact Riemann surface
$X$ is by definition a connected and compact
complex analytic manifold of dimension one.
The maximum principle for holomorphic functions entails that
every globally defined holomorphic funtions on $X$
is a  constant.
Thus, $\mathcal O(X)$ is reduced to the complex field.
But if one allows poles we shall learn that there exist non-constant
meromorphic functions
on $X$. They give a field denoted by
$\mathcal M(X)$ whose properties will
be investigated later on.
The projective line ${\bf{P}}^1$
over the complex field is an example of a compact Riemann surface.
Topologically it is homeomorphic to
a where and as a module one takes the
As a model one starts with the complex $z$-plane and adds the point at
infinity. Now $\mathcal M({\bf{\P}}^1)$
becomes the field of rational functions of
the single complex variable $z$.
Other compact Riemann urfaces
arise when one starts from
an irreducible polynomial $P(x,y)$
of two independent variables, i.e.
$P$ is irreducible in the unique factorisation domain
${\bf{C}}[x,y]$.
We shall learn how to find the associated compact
Riemann surface $X$ where $\mathcal (X)$
is isomorphic to the quotient field of the integral domain
$\frac{{\bf{C}}[x,y)}{(P)}$
where $(P)$ denotes the princial ideal generated
by $P$.
As an example we take
\[
P(x,y)= y^3-x^3-1
\]
To get $X$ one first regards the
algebraic curve in ${\bf{C}}^2$ defined by
$\{P=0\}$.
Since the complex gradient
vector $(P'_x,P'_y)= (3x^2,3y^2)\neq (0,0)$
it follows that $\{P0=\}$ is non-singular
and therefore brcomes an embedded one-dimensional complex manifold
in
${\bf{C}}^2$.
To get a copmpact complex manifold one regards the
prjective curve in ${\bf{P}}^2$
with its inhomogeneous coordintes
$(\zeta,x,y)$
where the zero set of $P^*(\zeta,x,y)= y^3-x^3-\zeta^3$
yields a projective curve $S$.
We shall learn  that $S$  is non-singular
and therefore gives a compact Riemann surface.
Less obvious is that
$S$ regarded as a topological space is
homeomorphic to
the oriented real manifold
$T^2$, where $T^2$ denotes the 2-dimensional torus.
The reason why $S\simeq T^2$ as a topoligcal space is that
$\mathcal M(S)$ contains
a meromorohiuc function $u$
which has one double pole and two simple zeros on
$S$ and is otherwise holomorphic without zeros.
An example of such a meromorphic function is
\[
u=\frac{1}{y-x}
\]
whose properties as a meromorphic function on
$S$ will
be described in ¤ xx.
\medskip
\noindent
In ¤ xxx we
expose the pioneering work
by Hermann Weyl devoted to "abstract" Riemann surfaces which
in particular prove
the existence of non-constant
meromorphic  functions. 
From this Weyl deduced that
$\mathcal M(X)$ is a so called algebraiuc functon field, i.e.
as a filed extension over
${\bf{C}}$ the degree of trancendency is one
and in addition it is finitely generated.
Using the existence of primitive elements in
finite algebraic extensions of fields in characterstic zero
it follows that $\mathcal M(X)$
is isomorphic to the quotoent field of an integral domain
\[
\frac{{\bf{C}}[x,y]}{P(x,y)}
\]
where $P(x,y)$ is an irreducible polynomial in
the unique  factorisation domain ${\bf{C}}[x,y]$.
So every compact
Riemann surface arises from an irreducible
polynomial $P(x,y)$. 
A remarkable fact is that
a compact Riemann surface $X$ is determiuned by
the field $\mathcal M(X)$.
More precisely, let $Y$ be another compact Riemann surface
and assume that there exists a ${\bf{C}}$-linear isimorohism
\[
\rho\colon \mathcal M(X)\to \mathcal M(Y)
\]
Thus, the two algebraic function fields are isomorphic.
In ¤ xx we show that
$X$ and $Y$ are isomorphic
as complex manifolds, i.e.
$\rho$ yields a \emph{biholomorphic map}
from $X$ to $Y$.
\medskip

\noindent
{\bf{Non-compact Riemann surfaces.}}
In addition to compact Riemann surfaces there  exist
open -or non-compact- Riemann surfaces $X$. It means that
$X$ is a connected but non-compact complex manifold of dimension one.
In this case it turns out
that
$\mathcal O(X)$ contains a quite extensive
 family of non-constant functions.
In ¤ xx we expose  results due to Behnke and Stein about
non-compact Riemann surfaces which
for example show that one can prescribe zeros and poles
in an arbitrary fashion and
which correspond to a globally defined meromorophic function on
$X$, i.e $\mathcal M(X)$ is so to speak "optimally ample".
In ¤ xx we also expose the \emph{Uniformisation Theorem}
where our proof follows that
of  
Behnke  and Stein. It implies for example that
every simply connected open Riemann surface is either
biholomorphic to the open unit disc or the complex plane.
The  uniformisation theorem for
connected  open
subsets $\Omega$ of the complex $z$-plane
deserve special attention.
More precisely, if $\Omega\subset{\bf{C}}$ is
open and connected and the complement contains at least two points, then
there exists a holomorphic map
\[
\phi\colon D\to \Omega
\]
where $D$ is the open unit disc, and
$\phi$ has the following two properties: First
it is surejctive, i.e. $\phi(D)=\Omega$ and moreover it is locally
conformal, i.e. the complex derivative
$\phi'(z)$ has no zeros.
In ¤ xx we shall learn that this entails that thr universal covering space of
$\Omega$ is homeomorphic to the open unit disc which is 
achieved via the  locally biholomorphic map $\phi$.
The uniformisation theorem for planar domains
is due to Hermann Schwarz who adopted Riemann's methods for
simple connected domains and is 
be exposed in ¤ xx
in connection with Riemann's ordinary conformal mapping theorem for
simply connected planar domains.
Even though Schwarz's Uniformisation Theorem can be deduced via
the general case treated by Behnke and Stein, it is instructive to pursue
his original proof which only relies upon analytic function theory.
As expected it is in general very hard to
obtain explicit formulas. 
An example is when
$\Omega$ is the open complement of
${\bf{C}}$ where one has removed
three disjoint closed intervals
$\{[a_\nu,b_\nu]\}$ where
$a_1<b_1<a_2<b_2<a_3<b_3$.
See ¤ xx for a discussion related to this case.
\bigskip



\centerline{\bf{About methods of proofs.}}
\medskip

\noindent
The study of Riemann surfaces offer instructive lessons in sheaf theory since
various sheaves
appear in a natrual fashion. The reader is supposed to be familiar with
basic facts about sheaves and their cohomology. But for less experienced readers we
add an appenbdix where
som fundamental reults from Leray's   pioneering article
\emph{xxxx} are resumed. Let us also 
remark that even if Weierstrass never
introduced the notion of sheaves, his construction of
"sheaf spaces" attached to in general multiu.valued abnalytic functions
gave the first  exampe of sheaves.
In addition to sheaf theory we employ calculus on manifolds without
hesitation.
For example. let $M$ be an oriented  real $C^\infty$-manifold of some dimension
$n\geq 2$. To say that $M$ is oriennted means that
there exists a globally defined differential $n$-form
which never vanishes and choosing the orientation
one can define integrals
\[
\int_M\, \omega\quad\colon\quad \omega\in \mathcal E^n(M)
\]
where $\mathcal E^n(M)$ is the space of 
$n$-forms with $C^\infty$-.coefficients.
More generally there exist to each
$0\leq p\leq n$ the space
$\mathcal E^p(M)$ of differential $p$-forms
with $C^\infty$-coefficients.
Under the condition that $M$ can be covered by a denumarable family of compact subsets
it follows  that
$\mathcal E^p(M)$ is equipped with a topology so that it
becomes a Frechet spaces.
There also exists the spaces
$\{\mathcal E^p_0(M)\}$
which consist of differential forms having compact support in
$M$.
The dual of
$\mathcal E^p_0(M)$ is denoted by
$\mathfrak{c}^{n-p}(M)$ and its elements are called currents of
degree $n-p$.
in particular $\mathfrak{c}^0(M)$ is the space of distributions on
$M$ and is often denoted by
$\mathfrak{Db}(M)$. Thus, by definition
\[
\mathfrak{Db}(M)\simeq \mathcal E^n_0(M)^*
\]
where (*) indicates that one regards the dual space.
We assume that the reader is famiiar with basic distribution theory which for
example is coveed in Hšrmander's text-book
[xx], where the passage to manifolds and currents 
become  trivial using charts on $C^\infty$-manifolds and $C^\infty$-partitions  of the unity.
Even if we shall not study manifolds of dreal dimension $\geq 3$
we recall some classic facts about oriented and compact $C\infty-$manifolds
Let $M$ be a such a manifold of siome dimension $n\geq 2$.
using exterior differentials one
has a complex
\[
0\to \mathcal E^0(M)\to \mathcal E^1(M)\to\ldots\to \mathcal E^n(M)\to 0
\]
Here
\[
d\colon \mathcal E^p(M)\to \mathcal E^{p+1}(M)
\] 
are continuous for every $p$, where we recall that
every $\mathcal E^p(M)$ is a Frechet space.
A fundamental fact is that the images of the $d$-maps above
are closed and have finite codimension.
Ths can be proved in several ways. The most convincing proof is due to
AndrŽ Weil who also established that
every compact and oriented manifold $M$ can be tringulated
via  a finite simplicial complex.
So readers interested in algebraic topology should  consult Weil's
original proof which teaches a good lesson
dealing with
topology and triangulations of manifolds.
Now one introduces the cohomology spaces
\[
H^p(M)= \frac{\text{Ker}_d(\mathcal E^p(M)}{d\mathcal E^{p-1}(M)}\quad\colon 0\leq p\leq n
\]
In particular $H^0(M)$ is the $d$-kernel on $C^\infty(M)$ and hence the
1-dimensional space of constant functuons.
One has also the complex of currents:
\[
0\to \mathfrak{c}^0(M)\to \mathfrak{c}^1(M)\to\ldots\to \mathfrak{c}^n(M)\to 0\tag{**}
\]
It is denoted by
$\mathfrak{c}^\bullet$.
For every $p$ one has the inclusion $\mathcal E^p(M)\subset\mathfrak{c}^p(M)$ 
and hence  Hence 
(*) above is a subcomplex of (**).
Next, the  contruction of currents and their exterior differentials, togehter eith
the closed range of the differentials in (*), 
give
a natural  duality
\[
H^p(M)^*\simeq \frac{\text{Ker}_d(\mathfrak{c}^{n-p})}{
d(\mathfrak{c}^{n-p-1}(M)}= H^{n-p}(\mathfrak{c}^\bullet)
\]
In addition to this
the fact that $M$ admits a triangulation implies that
the complexes (*) and (**) are quasi-isomorphic.
Hence the right hsnd side in (**) can be identfied with
$H^{n-p}(M)$, i.e. the dual of $H^p(M)$ is
equal to th cohomology space in degree $n-p$.
This is referred to as PoincarŽ duality theorem for compact
and oriented  manifolds.















\medskip

\noindent
{\bf{Some examples when $n=2$.}}
Let $M$ be an oriented  $C^\infty$-manifold of dimension two.
Since $M$ can be covered by a finite family of
charts  we can equip $M$ with a distance function
$d$ whose restriction to charts is equivsrnt to ordinsty euclidian metroc.
Every pair of such distance functions
$d_1$ and $d_2$ are equivalent in the sense that
there exists a constant $C>0$ such that
\[
C^{-1}|cdot d_2(p,q)\leq d_1(p,q)\leq C\cdot d_2(p,q)
\]
hold for every pair $p,q$ in $M$.
Next, a  parametrized curve
on $M$ is a map $\gamma\colon [0,1]\to M$
which is continuous.
Using a metric as above we can impose the
extra condition that
$\gamma$ has a bounded variation, i.e. there exists a constant $C$ such that
\[
\sum_{\nu=0}^{\nu=N-1}\, d(\gamma(t_{\nu+1}),\gamma(t_\nu)\leq C\tag{i}
\]
for all partitions
$0=t_0<t_1<\ldots<t_{N-1}<t_N=1$.
When (i) holds  there exist ordinary Borel-Stieltjes' integrals
\[
\int_\gamma\, \psi^1\tag{*}
\] 
for every differential 1-form $\psi^1$ with $C^\infty$-coefficents.
This gives a continuous  functional on
$\mathcal E^(M)$ with compact support and hence a current of
degree 1, called 
the integration current associated with
$\gamma$. This "operative construction" will
be used at many places later on.
One merit is that  "nasty geometric pictures"
when $\gamma$ for example has self-intersections
can be ignored while one
treats its associated integration current.
The case when $\gamma$ is closed, i.e. when
$\gamma(1)=\gamma(0)$ 
leads to special results. To begin with
we notice that
the equality $\gamma(0)= \gamma(1)$ entails that
\[
\int_\gamma\, dg=0\quad\colon\quad g\in \mathcal E(M)
\]
This is expressed by saying that the current
$\int_\gamma$ is $d$-closed.
A crucial result which follows from
the fact that
every distribution in ${\bf{R}}^2$ has  locally primitive distributuions with
respect to the pair of euclidian coordinates in
${\bf{R}}^2$, entails that
the following complex vector spaces are isomorphic
\[
\frac{\text{Ker}_d(\mathcal E^1(M)}{d(\mathcal E^0(M)}\simeq
\frac{\text{Ker}_d(\mathfrak{c}^1(M)}{d(\mathfrak{Db}(M)}\simeq
H^1(M)
\]
where the last term is the cohomology space in degree one on $M$.
This entials that if $\gamma$ is a closed and rectifiable curve 
then there exists a $d$-closed 1-form
$\phi\in \mathcal E^1(M)$ and a distribution $\mu$ such that
\[
\int_\gamma=d(\mu)+\phi^1\tag{*}
\]
where this equality takes place in
$\mathfrak{c}^1(M)$.
Moreover, the $d$-closed 1-form $\phi^1$ is
unique up to
an exact smooth 1-form.
With $\gamma$  regarded as a linear functional on
$\mathcal E^1(M)$ the reader should check that
(*) gives the equality
below for every $d$-closed $\psi^1\in\mathcal E^1(M)$:
\[
\gamma(\psi^1)= \int_M\, \phi^1\wedge \psi^1
\]
\medskip

\noindent
{\bf{The $d$-closed current $\int_{\partial\Omega}$.}}
Let $\Omega$ be a connected open set in $M$
whose boundary $\partial\Omega$ is regular in the sense of
Federer. It means that
there exists a (possibly empty) closed set
$\Sigma\subset\partial\Omega$ whose 1-dimensional Haussdorff measure is zero
while 
$\partial\Omega_*=\partial\Omega\setminus \Sigma$
is locally simple and rectifiable.
That is. for each $p\in\partial\Omega_*$ there exists
a bijective map $\gamma$ from the
closed unit intervalÊ$[0,1]$
to
a connected
subset of $\partial\Omega_*$
where $p=\gamma(1/2)$ while the distinct end-points
$\gamma(0)$ and $\gamma(1)$ stay in
$\partial\Omega_*$.
The orientation  along$\partial\Omega_*$ is given by the rule of thumbs
which appears
in the classic version of
Stokes Theorem as found already by Archimedes.
The extra the  condition is that the total variation, or equivalently the
arc-length measure of
$\partial\Omega_*$ is finite while it is evaluated with
respect to a local euclidian distance function, is finite.
Under these conditions one has
\[
\int_\Omega\, d\phi= \int_{\partial\Omega_*}\, \phi
\]
for each $\phi\in \mathcal E^1(M)$.
In particular the 1-current defined via the right hand side is $d$-closed.
Notice that we do not assume that
$\partial\Omega$ is connected.
\medskip

\noindent









\noindent
{\bf{Direct images of currents.}}
Let $\rho\colon M\to N$
be a $C^\infty$-map from $M$ to another oriented 
and compact 2-dimensional manifold $N$.
Elie Cartan's
construction of differential forms on manifolds give for
each $\phi\in\mathcal E^1(N)$ a pullback
$\rho^*(\phi)\in \mathcal E^1(M)$.
The map  is continuous when $\mathcal E^1(N)$ and
$\mathcal E^1(M)$ are equipped with
their standard Frechet topologies.
In particular we regard a
parametrized curve
$\gamma$ and obtain 
a 1-current
$\rho_*(\gamma)$ on $N$ defined by
\[
\rho_*(\phi)= \int_\gamma\, \rho^*(\phi)
\]
Later on we shall use  such direct images of currents at several places.
The reader  should "accept" that it is often  more profitable to
ignore "intuitive genetroic pictures" while calculations 
are performed.
An extra merit is  that
while the integrals along the  $\gamma$ is computed, then
calcluus teaches that one can employ
different parametrisatiin  along $\gamma$. as long as they
have bounded variation and preserve the given orientation.
Notice that even if $\gamma$ from the start is a simple Jordan arc, it
may occur that $\rho_*(\gamma)$
has a more involved structure  since
the restriction of the map $\rho$ to $\gamma$ need not be
one-to-one.
\medskip


\noindent
{\bf{Intersection numbers.}}





If $\rho $ is another  closed and rectifiabsle curve we have a
similar decomposition
\[
\int_\rho=\psi^1+d(\nu)
\]
Stokes Theorenm entials that
\[
\int_M\, \phi^1\wedge \psi^1\tag{*}
\]
is independent of the chosen decompostions.
So the complex number in (*) depends only upon the ordered
pair of closed curves
$(\gamma,\rho)$ and  is denoted by
$\mathfrak{i}(\gamma,\rho)$ and called the intersection number of the closed curves.
Elementaty calculus shows
that the intersection number always in an integer,
and by continuity it follows that
if $\gamma$ and $\gamma^*$ are two homotopic closed curves
then
$\mathfrak{i}(\gamma,\rho)=
\mathfrak{i}(\gamma^*,\rho)$ for every other closed curve
$\rho$.









Following original work by Riemann one
regards
specific simple closed curves
$\gamma_1,\ldots,\gamma_{2g}$ which give
a free basis for the fundamental group $\pi_1(M)$ which is free of some rank $2g$
where $g$ is a positive number.
Here we exlude the case when
$M\simeq S^2$, i.e $M$ is not
homoemorphic to the sphere. Instead $M$ is homeomorphic to a sphere where
$g$ handles have been attached and
with this picture  in mind one can draw $2g$-many
closed curves
on $M$ whose intersection numbers
are special. More precisely, there exists 
a pair of $g$-tuples $\gamma_1,\ldots,\gamma_g$ and
$\rho_1,\ldots,\rho_g)$ , where all these $2g$ many closed curves are simple
and
\[
\mathfrak{i}(\gamma_\nu,\rho_\nu)=1\quad\colon \quad 1\leq\nu\leq g
\]
while all other intersection numbers are zero.


\newpage















\newpage


\centerline{\bf{Analysis on compact Riemann surfaces.}}
\bigskip


\noindent
Let $X$ be a compact 1-dimensional complex manifold.
Recall that its 
complex analytic structure arises via charts
$(U,z)$ where $z$ is a local coordinate on
$X$ in the open set $U$ which is biholomorphic with
the open disc $D=\{|\zeta|<1\}$ in the complex $\zeta$-plane.
Let $\rho_U\colon U\to D$ be the holomorphic map.
When a pair of charts
$U$ and $V$ overlap
their complex analytic structures are
compatible. It means that
one has a biholomorphic map
\[
\rho_{U.V}\colon \rho_U(U\cap V)\to
\rho_V(U\cap V)
\]
where 
\[
\rho_U(\zeta)=\rho_V\circ\rho_{U,V}(\zeta)\quad\colon
\zeta\in \rho_U(U\cap V)
\]
The reader should illustrate this by a suitable picture
to see how the transition functions work
in overlapping charts
Since $X$ is compact it can be covered by a finite family of charts
$\mathfrak{U}= \{U_\alpha,z_\alpha)\}$. So here $\cup \, U_\alpha=X$
and one refers to $\mathfrak{U}$ as an atlas for the complex manifold $X$.
If $U$ is an arbitrary open set
in $X$ a complex valued function $f$ in $U$ is holomorphic if
\[
f\circ \rho_\alpha^{-1}\in \mathcal O(\rho_\alpha(U\cap\, U_\alpha))
\]
hold for
every chart in the atlas.
The set of holomorphic functions in $U$ is denoted by
$\mathcal O(U)$.
Local existence of non-constant holomiorphic functions is clear since
the defintion above entails  that
if $U_\alpha$ is a chart then
$\mathcal O(U_\alpha)\simeq \mathcal O(D)$.
\medskip


\noindent
{\bf{Differential calculus  on $X$.}}
A complex analytic atlas is in particular  a
$C^\infty$-atlas on the underlying real manifold
which has real dimension two.
The space of complex-vaued $C^\infty$-functions on
$X$ is denoted by $\mathcal E(X)$.
We have also the space $\mathcal E^1(X)$
of differential 1-forms
with
$C^\infty$-coefficients.
In a chart $(U,z)$
every differential 1-form can be decomposed as
\[
a\cdot dz+b\cdot d\bar z\tag{A.0}
\]
where $a$ and $b$ are complex-valued $C^\infty$-functions.
This gives a direct sum decomposition
\[
\mathcal E^1(X)=\mathcal E^{1.0}(X)\oplus\, \mathcal E^{0,1}(X)\tag{A.1}
\]
One refers to $\mathcal E^{1,0}$ as the space of diffeential 
forms of bi-degree $(1,0)$.
Thet are characterised by the condition that
$b=0$ holds in
$(A.0)$ for every  chart.
Similarly  when $a=0$  hold we get
a differential form of bi-degree $(0,1)$.
If $g\in\mathcal E(X)$ its exterior differential $dg$
is a 1-form which has a decompostion
\[
dg=\partial g+\bar\partial g
\]
For example, one has a map
\[
\bar\partial\colon\mathcal E(X)\to \mathcal E^{0,1}(X)\tag{A.2}
\]
The Cauchy-Riemann equations applied in charts show that
the kernel in (A.2) consists of holomorphic functions and
hence the kernel is reduced to  constant functions.
\medskip

\noindent
Next, we also have differential 2-forms on $X$ which in a chart $(U,z)$
can be expressed as
\[
c(z)\cdot dz\wedge d\bar z
\]
Keeping the complex analytic structure in mind
we denote the space of differential 2-forms with
$\mathcal E^{1,1}(X)$.
The reader should
construct the  maps
\[
\bar\partial\colon \mathcal E^{1,0}(X)\to \mathcal E^{1.1}(X)\tag{A.3}
\]
\[
\partial\colon \mathcal E^{0,1}(X)\to \mathcal E^{1.1}(X)\tag{A.4}
\]
\medskip

\noindent
Next, recall that $\mathcal E(X)$ is a Frechet space
where the topology is defined via uniform convergence of
derivatives in every order.
In a similar fashion $\mathcal E^{p,q}(X)$
are Frechet spaces for every pair $0\leq p,q\leq 1$.
The reader should  check that 
the maps in (A:2-4)  are continous between these 
Frechet spaces.
Less obvious is the folloowing:
\medskip

\noindent
{\bf{A.5 Theorem.}}
\emph{Tbe range of the exterior differential maps
in (A.2-4) above are all closed.}
\bigskip




\noindent
{\bf{A.6. Remark.}}
This is the first non-trivial result
about compact Riemann surfaces.
We give the proof in (*) and remark only that it
relies upon
a classic result due to Pompieu which gives solutions to
the inhomogeneous $\bar\partial$-partial 
equation in planar
domains. More precisely, if
$U$ is an open set  in the complex $\zeta$-plane and
$g\in C^\infty(U)$ then
there exists $f\in C^\infty(U)$ such that
\[
\bar\partial(f)= g\cdot d\bar\zeta\tag{A.6.1}
\]
\bigskip

\noindent
{\bf{A.7 Currents on $X$.}}
To  begin with we have the space
$\mathfrak{Db}(X)$ of distributions which by  definition it is the 
space of continuos linear forms on the Frechet space
$\mathcal E^{1,1}(X)$, i.e.
\[
\mathfrak{Db}(X)= \mathcal E^{1,1}(X)^*
\]
Passing to differential forms
we get dual spaces
\[ 
\mathfrak{c}^{1,0}(X)=\mathcal E^{0,1}(X)^*
\quad\colon\quad
\mathfrak{c}^{0,1}(X)=\mathcal E^{1,0}(X)^*
\]
Finally, we have the space $\mathfrak{c}^{1.1}(X)$
which is the dual of $\mathcal E(X)$.
\medskip

\noindent
{\bf{B.1 The integration current $1_X$.}}
The reader should check that
the complex analytic structure on $X$ entails that its underlying
real manifold is oriented.
It  follows that if
$\gamma\in \mathcal E^{1,1}(X)$
then there exists an integral
\[
\int_X\, \gamma
\]
This defines a distribution   denoted by
$1_X$.
In general we have an inclusion
\[
\mathcal E(X)\subset\mathfrak{Db}(X)
\]
Namely, if $g$ is a $C^\infty$-function we get
a linear form on
$\mathcal E^{1,1}(X)$ defined by
\[
\gamma\mapsto \int_X\, g\cdot \gamma
\]
If
$\gamma^{1,0}$ belongs to
$\mathcal E^{1,0}(X)$
we notice that Stokes Theorem gives
\[
0=\int_X\, d(g\cdot \gamma^{1,0})
\]
Now the reader should verify that
\[
d(g\cdot \gamma^{0,1})=
\bar\partial g\wedge \gamma^{1,0}+g\cdot \bar\partial(\gamma^{1,0})
\]
Next, by definition the
$(0,1)$-current $\bar\partial g$
is defined by
\[
\bar\partial(g)\langle \gamma^{1,0}\rangle=-\int_X\, g\cdot \bar\partial(\gamma^{1,0})
\]
Keeping  signs in mind one concludes that
when $g$ from the start is identified with a distribution, then
the $(0,1)$-current $\bar\partial(g)$ is equal to the smooth
differential 1-form
of  bi-degree (0,1) arising when
$\bar\partial$ is applied to the $C^\infty$-function $g$.
\medskip

\noindent
{\bf{B.2 A  duality result.}}
We have the map
\[
\bar\partial\colon \mathcal E^{1,0}(X)\to \mathcal E^{1,1}(X)
\]
By Theorem A.5 the range is closed.
This implies that
the dual space
\[
\bigl[\, \frac{\mathcal E^{1,1}(X)}{\bar\partial \mathcal E^{1,0}(X)}\,\bigr]^*
\simeq \text{Ker}_{\bar\partial}(\mathfrak{Db}(X))\tag{B.2.1}
\]
Next, recall that  $\bar\partial$ is elliptic.Indeed, via the   classic Pompieu formula for planar
doimains  every distribution $\mu$ satisfying
the homogeneous equation $\bar\partial(\mu)=0$ is a holomorphic
function.
Since $\mathcal O(X)$ is reduced to constants the
dual space in (B.2.1)  is 1-dimensional and hence
\[
\dim_{{\bf{C}}}\, \frac{\mathcal E^{1,1}(X)}{\bar\partial \mathcal E^{1,0}(X)}=1\tag{B.2.2}
\]
Notice also that Stokes Theorem gives
\[
\int_X\, \bar\partial(\gamma^{1,0})=0\quad\colon\, \gamma^{1,0}\in \mathcal E^{,1,0}(X)
\]
from this we conclude thatif 
$\rho^{1,1}$ is a  2-form for which
$\int_X\,\rho^{1,1}\neq 0$, then
\[
\mathcal E^{1,1}(X)={\bf{C}}\cdot \rho\oplus
\bar\partial(\mathcal E^{1,1}(X))\tag{B.2.3}
\]
\medskip

\noindent{\bf{B.3 A second duality.}}
Theorem A.5 entails that
\[
\bigl[\, \frac{\mathcal E^{0,1}(X)}{\bar\partial \mathcal E(X)}\,\bigr]^*
\simeq \text{Ker}_{\bar\partial}(\mathfrak{c}^{1,0}(X))\tag{B.3.1}
\]
The right hand side is found as follows.
In a chart $(U,z)$
a current of bi-degree
$(1,0)$ is of the form
$\mu\cdot dz$ with
$\mu\in \mathfrak{Db}(U)$.
The $\bar\partial$ image of this current is
zero if and only if $\bar\partial(\mu)=0$ and as we have seen
before this implies that
$\mu$ is a holomorphic density.
Hence the right hand side in (B.3.1) consists of globally defined
\emph{holomorphic} 1-forms. This space is denoted by
$\Omega(X)$ and (B.3.1) can be expressed by
the duality formula
\[
\Omega(X)\simeq\bigl[\, \frac{\mathcal E^{0,1}(X)}{\bar\partial \mathcal E(X)}\,\bigr]^*\tag{B.3.2}
\]
\medskip

\noindent
{\bf{B.3.3 Exercise.}}
Show that (B.3.2) gives the following:
A differential form $\gamma^{0,1}$ on $X$ is $\bar\partial$-exact
if and only if
\[
\int_X\, \omega\wedge \gamma^{0,1}=0\quad\colon\, \forall\,\,
\omega\in \Omega(X)
\]
\medskip

\noindent
{\bf{B.4 Passage to currents.}}
Recall that $\mathcal E^{0,1}(X)\subset\mathfrak{c}^{0,1}$.
in ¤ xx we shall learn that
\[
\mathfrak{c}^{0,1}=\bar\partial(\mathfrak{Db}(X))+
\mathcal E^{0,1}(X)\tag {B.4.1}
\]
Moreover, a $(0.1)$-current $\rho^{0,1}$ is
$\bar\partial$-exact, i.e. of the form
$\bar\partial(\mu)$ for some
distribution $\mu$ on $X$ if and only if
\[
\rho^{1,0}(\omega)=0\quad\colon\quad \omega\in \Omega(X)\tag{B.4.2}
\]
\medskip

\noindent
{\bf{B.5 The case $X={\bf{P}}^1$.}}
Here $\Omega(X)$ is reduced to the zero space.
To see this we suppose that
$\omega$ is a globally defined holomorphic 1-form.
Now ${\bf{P}}^1\setminus \{\infty\}$ is the complex $z$-plane and here
\[
\omega= f(z)\cdot dz
\] 
where $f$ is an entire function.
At the point at infinity we have a local coordinate
$\zeta$ and
\[
\zeta= z^{-1}\quad\colon R<|z|<\infty
\]
hold for every $R>0$.
Since $\omega$ is globally holomorhpic we have
\[
\omega= g(\zeta)\cdot d\zeta
\]
when $0<|\zeta|<R^{-1}$. At the same time the reader can check that
\[
dz=-\zeta^{-2}\cdot d7zeta
\]
holds when $R<|z[<R$. Ths entails that
\[
f(z)=-z^{-2}\cdot g(1/z)\quad\colon |z|>R
\]
From this we see that
the entire function $f$ tends to zero as $|z|\to\infty$
and hence $f$ is identically zero.
So with $X={\bf{P}}^1$ one has $\Omega(X)=0$ and
then (B.4.2) entails that
\[
\mathfrak{c}^{0,1}= \bar\partial(\mathfrak{Db}(X))
\]
In other words, the inhomogeneous $\bar\partial$-equation
is always solvable.
Consider as an example a current
of the form
\[
\gamma=\mu\cdot d\bar z
\]
where $\mu$ is a measure in the complex $z$-plane with compact support.
Now there exists the Cauchy transform
\[
\widehat{\mu}(z)=\int\,\frac{d\mu(\zeta)}{z-\zeta}
\]
It is holomiorphic in
in the open set of the complex $z$-plane where
the compact set
$\text{Supp}(\mu)$ has been removed.
passing to infinity we
notice that
it extends to be holomorphic
because one has the convergent series expansion
\[
\widehat{\mu}(z)=\sum_{n=0}^\infty\,
\int\,\zeta^n|cdot d\mu(\zeta)\cdot z^{-n-1}{z-\zeta}
\]
in an exterior disc
$|z[>R$ where
the support of $\mu$ is contained in
$\{|z|\leq R\}$.
\medskip

\noindent
next, by basuc lebsgue theory one knows that
the funnction $\widehat{\mu}$ is locally integrable
in the whole complex $z$-plane and hence defines a distribution.
Finally, Cacuhy's residue formula shows that
the distribution derivative
\[
\frac{\bar\partial\widehat{\mu}}{\bar\partial\bar z}=\pi \cdot \mu
\]
So we get
\[
\bar\partial(\pi^{-1}\cdot \widehat{\mu})=\mu\cdot d\bar z
\]




















\newpage


\centerline{\bf{C. Some sheaves and their cohomology}}.
\medskip


\noindent
Let $X$ be a compact complex  analytic manifold.
Classic  facts due to Cauchy and Pompieu applied to charts in $X$ 
give  an exact sequence of sheaves
\[
0\to \mathcal O_X\to \mathcal E_X\overset{\bar\partial}\to, \mathcal E_X^{0,1}\to 0\tag{C.0}
\]
Using $C^\infty$-parotions of unity and Leray's theory about  cohomology with
values in sheaves
one gets
\[
H^1(\mathcal O_X)\simeq \frac{
\mathcal E^{0,1}(X)}{\bar\partial(\mathcal E(X)}\tag{C.1}
\]
where the left hand side is the first cohomology groups with
values in the sheaf
$\mathcal O_X$. The reader may also notice that when Leray's long exact sequence for sheaf cohomology is applied to (C.0), then it follows that
\[
H^2(\mathcal O_X)=0\tag{C.2}
\]
Next, we have also the exact sheaf sequence
\[
0\to {\bf{C}}_X\to \mathcal O_X\overset{\partial}\to \Omega_X\to 0\tag{C.3}
\]
Since $H^0({\bf{C}}_X)= H^0(\mathcal O_X)= {\bf{C}}$ and (C.2) holds
one gets the following   exact sequence of complex vector spaces:
\[
0\to \Omega(X)\to H^1({\bf{C}}_X)\to
 H^1(\mathcal O_X)\to H^1(\Omega _X)\to H^2({\bf{C}}_X)\to 0\tag{C.4}
\]
Next, we have
also the following exact sheaf sequence
\[
0\to \Omega_X\to \mathcal E^{1,0}_X\overset{\bar\partial}\to \mathcal E_X^{1,1}\to 0\tag{C.5}
\]
This gives the equality
\[
H^1(\Omega_X)\simeq\frac{\mathcal E^{1,1}(X)}{\bar\partial(\mathcal E^{1,0}(X))}\tag{C.6}
\]
The right hand side rsssembles the quotient in
(B.2.2).
Indeed, we can regard the 7emph{conjugate} analytic structure on
the underlying real manifold of $x$ where the sheaf of holomorphic functions
are compex cojugates of sections in
$\mathcal O_X$. From this the reader may conclude via (B.2.2)
that the rifht hand side in (C.5)
is a 1-dimensional vector space. Hence we have 
\[
\dim_{{\bf{C}}}\,H^1(\Omega_X)=1\tag{C.7}
\]
\medskip

\noindent
Next, recall that
$H^2({\bf{C}}_X)={\bf{C}}$. Together with (C.7) we conclude that
 (C.4) gives the
short exact sequence
\[
0\to \Omega(X)\to H^1({\bf{C}}_X)\to
 H^1(\mathcal O_X)\to 0\tag{C.8}
\]
Topology teaches that
the cohomology space
$H^1({\bf{C}}_X)$Êis finite dimensional.
Hence (C.8) implies that both
$\Omega(X)$ and $H^1(\mathcal O_X)$ are finite dimensional complex vector spaces.
Finally, (B.3.2) and (C.1) give
\[
\Omega(X)\simeq\bigl [\, H^1(\mathcal O_X)\,\bigr]^*\tag{C.9}
\]
In particular the complex vector spaces
$\Omega(X)$ and $H^1(\mathcal O_X)$ have the same dimension.
This equality and (C.8) give
\[
\dim H^1({\bf{C}}_X)= 2\cdot \dim \Omega(X)\tag{C.10}
\]
The equality (C.10) is fundamental  during the study of compact
Riemann surfaces. 
A notable point is that
the cohomology group $H^1({\bf{C}}_X)$ only depends upon the
topological space $X$ and not upon its particular complex structure.

\bigskip

\noindent
{\bf{C.10 A duality for currents.}}
In planar domains it is wellknown that the
inhomogenous $\bar\partial$-equation is locally solvable on distributions.
Since the $\bar\partial$-kernel on $\mathfrak{Db}_X$ is $\mathcal O_X$
one has an exact sequence
\[
0\to \mathcal O_X\to \mathfrak{Db}_X\overset{\bar\partial}\to
\mathfrak{c}^{0,1}_X\to 0
\]
Passing to cohomology and using 
$C^\infty$-partitions of the unity, it follows that
\[
H^1(\mathcal O_X)\simeq \frac{\mathfrak{c}^{0,1}_X}{
\bar\partial(\mathfrak{Db}(X)}\tag{C.10.1}
\]
\medskip

\noindent
{\bf{Exercise.}} Deduce from the above that
\[
\Omega(X)\simeq\bigl[\, \frac{\mathfrak{c}^{0,1}_X}{
\bar\partial(\mathfrak{Db}(X)}\,\bigr]^*\tag{C.10.2}
\]
Conclude that the implication below holds for
each 
$\gamma\in \mathfrak{c}^{0,1}$:
\[
\gamma(\omega)=0\quad\colon\,\forall\,\, \omega\in \Omega(X)
\implies \gamma\in \bar\partial(\mathfrak{Db}(X))\tag{C.10.3}
\]
\medskip

\noindent
{\bf{C.11 A decomposition theorem.}}
Since $X$ in particular is an oriented and compact real manifold
one has
\[
H^1({\bf{C}}_X)\simeq\frac{\text{Ker}_d(\mathcal E^1(X)}{d(\mathcal E(X)}\tag{C.11.1}
\]
Next, on $X$ there also exists
the anti-holomorphic differential forms of bi-degree
$(0,1)$, i.e differential forms  $\gamma\in \mathcal E^{0,1}(X)$ for which
$\partial(\gamma)=0$.
This space is denoted by $\overline{\Omega}(X)$.
Using the conjugate complex analytic structure one has another compact
complex manifold $\overline{X}$
where
$\overline{\Omega}(X)$ is the space of holomorphic 1-forms.
Since $X$ and $\overline{X}$ have the same underlying real manifold, it follows from
(C.10) that
\[
\dim H^1({\bf{C}}_X)= 2\cdot \dim \overline{\Omega}(X)\tag{C.11.2}
\]
Using  this we shall prove
\medskip

\noindent
{\bf{C.11.3 Theorem.}}
\emph{One has a direct sum decomposition}
\[
\text{Ker}_d(\mathcal E^1(X))=
d(\mathcal E(X))\oplus \Omega(X)\oplus\overline{\Omega}(X)
\]
\medskip

\noindent
\emph{Proof}
To begin with we notice that
\[
\Omega(X)\,\cap \overline{\Omega}(X)= \{0\}
\]
Counting dimensions this follows if we prove that
a 1-form $\gamma)\omega+\mu$ cannot be $d$-exact
when $\omega\in \Omega(X)$ and $\mu\in \overline{\Omega}(X)$
where at least one these froms is not identically ero.
For suppose that
$\gamma=dg$ is $d$-exact.
If $\omega$ is not identically zero there exists
the conjugate
form
$\bar\omega\in\overline{\Omega}(X)$.
Now Stokes Theorem gives
\[
0=\int_X\, dg\cdot \bar\omega)=\int_X(\omega+\mu)\wedge\bar\omega=
\int_X(\omega\wedge\bar\omega
\]
Now the reader can check that
the last integral is $\neq 0$ when $\omega$ is not identically zero.
hence $\gamma\in d(\mathcal E(X))$ implies that
$\Omega=0$ and in the same way we find that
$\mu=0$ which proves Theorem C.11.3.








\newpage


\centerline{\bf{D. Existence of meromorphic functions.}}
\bigskip


\noindent
On $X$ there exists the sheaf
$\mathcal M_X$ whose sections are meromorphic  functions.
Subsheaves arise via  constraints on  poles.
In particular, let $p\in X$ be a given point and
$m$ a positive integer.
Denote by $\mathcal O_X[* mp]$
the sheaf whose sections are meromorphic functions on
$X$ which are holomorphic in $X\setminus\{p\}$ and have
poles of order $\leq m$ at $p$.
If $(U,z)$ is a chart where $p$ corresponds to
the origin we seee that
\[
\mathcal O_X[* mp]\,|U= z^{-m}\cdot \mathcal OX|U
\]
Taking Laurent exapnsions
every section in the right hand side is of the form
\[
f+\frac{c_1}{z}+\ldots+\frac{c_m}{z^m}
\]
where $f\in \mathcal O_X$ and $\{c_\nu\}$ is an $m$-tuple of complex numbers.
Expressed by  sheaves it gives
an exact sequence
\[
0\to \mathcal O_X\to \mathcal O_X[*mp]\to S_p^m\to 0\tag{D.1}
\]
where $S_p$ is the scyscraper sheaf suppotet  by $\{p\}$
and
the stalk $S_p(p)$ is an $m$-dimensional vector space.
Passing to long exact sequence of cohomology the reader 
can verify that there is an exact sequence:
\[
0\to {\bf{C}}\to H^0(\mathcal O_X[*mp])\to
{\bf{C}}^m\to 
H^1(\mathcal O_X)\to H^0(\mathcal O_X[*mp])\to 0\tag{D.1.1}
\]
\medskip

\noindent
{\bf{D.2 Exercise.}}
Use that the vector space 
$H^1(\mathcal O_X)$ is $g$-dimensional and conclude that
\[
\dim_{{\bf{C}}}\, 
H^0(\mathcal O_X[*mp])=m-g+1+
\dim_{{\bf{C}}}\, 
H^1(\mathcal O_X[*mp])\geq m-g+1\tag{D.2.1}
\]
\medskip

\noindent
In particular the left hand side is $\geq 2$ if $m=g+1$
which means that
apart from constants, there exists at least one
constant global section in 
$\mathcal O_X[*(g+1)p]$.
Hence we have proved:

\bigskip

\noindent
{\bf{D.3 Theorem.}}
\emph{For every $p\in X$ there exists a non-constant 
meromorphic function $f$  in $X$ with no poles in
$X\setminus{p}$ while
the order of the pole at $p$ is at most $g+1$.}











\newpage



\centerline{\bf{Weierstrass' points.}}

\bigskip

\noindent
Let $X$ be a compact Riemann surface
whose genus number $g$ is $\geq 2$.
Removing  a point $p\in X$
we get  the space
$\mathcal O(X\setminus\{p\})$.
If $(U,z)$ is a chart centered at $p$
where $p$ corresponds to $z=0$, then every
$f\in\mathcal O(X\setminus\{p\})$
restricts to a holomorphic function in
the punctured disc
$0<|z|<1$
and we can regard its Laurent series:
\[
f(z)=
\sum_{\nu=1}^\infty\ c_\nu\cdot z^{-\nu}+\sum_{\nu\geq 0}\, d_\nu\cdot z^\nu
\]
The negative part of the Laurent series is denoted by $f_*(z)$.
If $f_*=0$ then $f$ is globally holomorphic and hence reduced to
a constant.
So 
\[
f\mapsto f_*(z)+ d_0
\]
yields an  injective 
map from $\mathcal O(X\setminus\{p\})$ 
into the space of
non-positive Laurent series at $z=0$.
We are going to study the range of this map.
Denote by $\mathcal L$
the space 
of all non-positive Laurent series, where we recall that a negative
series
\[
\sum_{\nu=1}^\infty\ c_\nu\cdot z^{-\nu}\in\mathcal L
\]
if and only if
\[
\sum_{\nu=1}^\infty\, |c_\nu|\cdot R^\nu<\infty
\] 
for all $R>0$.
In particular $\mathcal L$ contains the $g$-dimensional subspace
formed by Laurent series given by
finite series:
\[
\rho(z)= c_1z^{-1}+\ldots+c_g\cdot z^{-g}
\]
where $\{c_\nu\}$ is a $p$-tuple of complex numbers.
Let $\mathcal L[p]$ denote this subspace of
$\mathcal L$.
\medskip

\noindent
{\bf{E.1 Theorem.}}
\emph{Outside a finite set ${\bf{W}}$ in $X$
one has} 
\[ 
\mathcal L=\mathcal L[p]\oplus \mathfrak{Im}(\mathcal O(X\setminus\{p\})
\]
\medskip

\noindent
{\bf{E.2 Remark.}}
In ¤xx we show that
the exceptional set
${\bf{W}}$ is non-empty when $g\geq 2$,
If (*) holds above
it follows that when $m>g$
then  there exists a unique $g$-tuple $\{c_\nu\}$ such that 
\[ 
z^{-m}=c_1z^{-1}+\dots+c_gz^{-g}+ \mathfrak{Im}(\phi)
\]
where $\phi$ is holomorphic in
$X\setminus\{p\}$.
Herte the negative Laurent series of $\phi$ is finite
at $p$ which implies that
$\phi$ is a globally defined meromorphic function
with a pole of order $m$ at $p$ whose negative Laurent expnasion at $p$
is of the form
\[
z^{-m}+c_1z^{-1}+\dots+c_gz^{-g}
\]
where the $g$-tuple $\{c_\nu\}$ is uniquely determined and depends on
the chosen integer $m$.
At the same time
the direct dum in (*) entails that
there do not exist non-constant meromorphic functions
which are holomorphic in
$X\setminus\{p\}$ while the order of
the pole at $p$ is $\leq g$.
\medskip

\noindent
The proof of Theorem E.1 requires several steps.
We are given a point
$p\in X$ and let $(U,z)$ be a chart
around $p$ where $p$ corresponds to $z=0$.
Residue calculus gives
a $g$-tuple of 
currents defined by
\[
\rho_\nu=\bar\partial(z^{-\nu})\quad\colon\quad \nu=1,\ldots,g
\]
Each current is supported by the singleton set $\{p\}$
and extends to a current on $X$ supported by $p$.
If $\Psi^{1,0}\in\mathcal E^{1,0}(X)$
we can regard its restriction to $U$ and write
\[
\Psi^{1,0}|U= \psi(z)\cdot dz
\]
with $\psi\in C^\infty(U)$.
Residue calcluus teaches that
\[
\rho_1(\Psi^{1,0})= 2\pi i\cdot \psi(0)
\]
If $\nu\geq 2$ the reader may verify that
\[
\rho_\nu(\Psi^{1,0})= \frac{(-1)^{\nu-1}}{(\nu-1)!}\cdot
\partial^{\nu-1}\psi/\partial z^{\nu-1}(0)
\]
The construction of the $\rho$-currents
is not intrinsic, i.e.
the $g$-tuple  depends on the chosen chart around $p$.
But the reader can check that
the $g$-dimenbsional vector space
in $\mathfrak{c}^{0,1}(X)$
generated by
$\{\rho^\nu\,\colon 1\leq \nu\leq g\}$
does not depend on the chosen chart around $p$.
Let us denote it by $\mathcal W(p)$.
The major step towards the proof of Theorem E.1
is the following:


\medskip

\noindent
{\bf{E.3 Theorem.}} \emph{Outside a finite set
${\bf{W}}$  in $X$ one has
the direct sum decomposition}
\[
\mathfrak{c}^{0,1}(X)=\bar\partial(\mathfrak{Db}(X))\oplus\, \mathcal W(p)\tag{E.3.1}
\]
\bigskip

\noindent
\emph{Proof.}
The duality result in ¤ xx gives (E.3.1)
if
the $g$-tuple
$\{\rho^\nu\}$ restrict to 
${\bf{C}}$-linearly independent in the dual space
$\Omega(X)^*$.
To check when this holds we
consider a basis $\omega_1,\ldots,\omega_g$ in the $g$-dimensional vector space
$\Omega(X)$.
In a chart
$(U,z)$ centered at a point $p_0\in X $ we can write
\[
\omega_j= f_j(z)\cdot dz\tag{i}
\]
where Ê$\{f_j\}$ are ${\bf{C}}$-linearly 
independent in $\mathcal O(U)$.
The general result in ¤ xx  entails that 
the determinant function
\[
\mathcal F(z)= \det\bigl(\partial f_j^\nu/\partial z^\nu(z)\tag{ii}
\]
formed by the $g\times g$-matrix with
elements as above is not identically zero.
Now linear algebra shows that
$\{\rho_\nu\}$ restrict to linearly independent functionals
on $\Omega(X)$ at every $z|in U$ for ehich
$F(z)\neq 0$.
Since the zero set of $F$ in the chart $U$ is discrete
and we can cover
$X$ by a finite famliy of charts, it follows that
(E.3.1) holds outside a finite set
${\bf{W}}$.


\medskip

\noindent
{\bf{E.4 How to find ${\bf{W}}$.}}
In each  chart $(U,z)$ as above we have
the $\mathcal F$-functions from (ii).
If $(U_\alpha,z_\alpha)$ and $(U_\beta,z_\beta)$ is a pair of charts
in $X$ where $U_\alpha\cap U_\beta\neq\emptyset$
we get two $g$-tuples  of analytic functions by
\[
\omega_j|U_\alpha= f_j^\alpha\cdot dz\quad\colon\quad
\omega_j|U_\beta= f_j^\beta\cdot dz_\beta
\]
When $z_\beta=z_\beta(z_\alpha)$ is regarded as
an analytic function in $U_\alpha\cap U_\beta$ one has the equations
\[
f_j^\alpha=\frac{\partial z_\beta}{\partial z_\alpha}\cdot f_j^\beta\tag{E.4.1}
\]
for each $j$ in $U_\alpha\cap U\beta$.
\medskip

\noindent
{\bf{E.4.2 Exercise.}} Show by using
rules for calcuating determinsnts that
(E.4.1) gives
the equation
\[
\mathcal F_\alpha=\bigl(\frac{\partial z_\beta}{\partial z_\alpha}\bigr)^{g(g-1)/2}\cdot F_\beta(z)
\]
So with $N=g(g-1)/2$
the family $\{\mathcal F_\alpha\}$ which arises when
$X$ is covered by a finite number of charts, is a global section of
the $N$-fold product of the holomorphic line bundle $\Omega_X$.
By (xx) the
set of xeros counted with multiplicities  of every global section
in $\Omega_X$ is equal to $2(g-1)$.
So by the general result in ¤ xxx the
zero set of the $\mathcal F$-family counted with multiplicities is equal to
$g(g-1)^2$. Since $g\geq 2$ this is a positive integer and hence
the set ${\bf{W}}$ is non-empty.
\bigskip

\noindent
{\bf{Remark.}} In the literature one refers to
${\bf{W}}$ as the set of Weierstrass' points in $X$.
The determination of ${\bf{W}}$ for a given $X$ with genus $\geq 2$
is in general not easy.
From the above ${\bf{W}}$ contains at most
$(g-1)^2\cdot g$ many distinct points. 
In general the number of points can be
strictly smaller.
Weierstrass investigated
${\bf{W}}$ for special families of compact Riemann surfaces.
See ¤ xx for some comments.
\bigskip

\centerline {\bf{Proof of Theorem E.1}}

\bigskip

\noindent
Consider a point $p\in X$ which is outside ${\bf{W}}$ and let $(U,z)$ be a chart 
centered at $p$.
Let $U^*=U\setminus\{p\}$ be the punctured open disc.
In $X$ we also have the open set
$X\setminus\{p\}$
which can be regarded as an open Riemann surface.
The theorem by Behnke and Stein from
the chapter devoted to open Rieann surfaces
gives
$H^1(X\setminus\{p\},\mathcal O)=0$.
The cohomology in the  disc $U$ is also zero.
Hence the open covering of $X$ given by the pair
$\mathfrak{U}= (U,X\setminus\{p\})$
is acyclic with respect to the sheaf
$\mathcal O_X$. So  Leray's acyclicity theorem gives
\[
H^1(X,\mathcal O_X)\simeq \frac{\mathcal O( U^*)}{
\delta(C^0(\mathfrak{U},\mathcal O_X))}\tag{i}
\]
where
\[
\delta\colon \mathcal O(U)\oplus \mathcal O(X\setminus\{p\})\to
\mathcal O(U^*)
\] 
is the Cech coboundary map.
Next, the $g$-tuple $\{z^{-\nu}\colon \nu=1,\ldots,g\}$
are holomorphic in $U^*$
and  their images in the right hand side from (i) give
elements in
$H^1(X,\mathcal O_X)$ denoted by
$\{[z^{-\nu}]\}$.
\medskip

\noindent
{\bf{Exercise.}}
Recall  that
\[
H^1(X.\mathcal OX)= \frac{\mathfrak{c}^{0,1}}{\bar\partial(\mathfrak{Db}(X)}
\]
Since $p$ is outside ${\bf{W}}$
the last quotient is equal to $\mathcal W(p)$.
Conclude from this that
the $g$-tuple
$\{[z^{-\nu}]\}$ is a basis in the $g$-dimensional vector space
$H^1(X,\mathcal O_X)$.
\medskip

\noindent
Let us then consider some
$g\in\mathcal O(U^*)$ which has a  Laurent series
\[
g(z)= \sum_{\nu=1}^\infty\ c_\nu\cdot z^{-\nu}+
\sum_{\nu=0}^\infty\ d_\nu\cdot z^{\nu}
\]
By the Exercise  there exists
a unique $g$-tuple of complex numbers
$a_1,\ldots,a_p$
such that
the image of $g$ in
$H^1(X,\mathcal O_X)$ is equal to $\sum\, a_\nu\cdot [z^{-\nu}]$.
Hence (i) gives a pair $\phi(z)\in\mathcal O(U)$ and $f(z)\in \mathcal O(X\setminus\{p\}$
such that
\[
g(z)-\sum\,\rho_\nu\cdot z^{-\nu}=\phi(z)+f(z)
\]
where $\phi(z)\in\mathcal O(U)$ and $f(z)\in \mathcal O(X\setminus\{p\}$.
Regarding the negative Laurent series it follows that
\[
g_*(z)= \sum\, a_\nu\cdot z^{-\nu}+f_*(z)\tag{ii}
\]
Here $g$ was arbitrary in
$\mathcal O(U^*)$ and hence the proof of Theorem E.1 is finished.
















\newpage










 
 
 
 

\centerline{\bf{F. Abel's theorem.}}



\bigskip


\noindent
A divisor $D$ on $X$ consists of
an assignement of integers $\{\mu_\nu\}$ to a finite set of points $\{p_\nu\}$
in $X$. One writes
\[
D= \sum\, \mu_\nu\cdot \delta(p_\nu)
\]
The $\mu$-integers may be positive or negative.
The degree is defined by
\[
\deg D= \sum\,\mu_\nu
\] 
while the finite set $\{p_\nu\}$ is called the support of $D$.
Next we construct a class of 1-currents.
In general, let $\gamma\colon [0,1]\to X$
be an $X$valued function on the closed unit interval
We assume that $\gamma$ is continuous and has a
finite total variation. The last condition means that
there exists a constant $C$ such that
\[
\sum_{\nu=0}^{\nu=N-1}\, d(\gamma(t_{\nu+1},\gamma(t_\nu)\leq C
\]
for all sequences $0=t_0<t-1<\ldots<t_N=1$
Here $d$ is some  distance function 
on $X$ regarded as a metric space which in charts
is equivsoent to
the euclidian distance.
Every such $\gamma$ gives a current of degree one
acting on $\mathcal E^1(X)$ by 
\[
\alpha\mapsto \int_\gamma \,\alpha\tag{*}
\]
\medskip

\noindent
{\bf{Exercise.}} Explain how the classical Borel-Stieltjes integrals for functions
with bounded variation
defines the integral in the right hand side.
Show also that
\[
\int_\gamma\, dg= g(\gamma(1))-g(\gamma(0))
\]
hold for every $g\in\mathcal E()$.
One refers to (*) as an integration current of degree one.
More generally we can take a finite sum of such
currents and get the integration current
$\Gamma$ defined by
\[
\Gamma(\alpha)= \sum\, \int_{\gamma_j}\,\alpha
\]
Let $D=\sum\,\mu_\nu\cdot \delta(p_\nu)$ be a divisor of
degreee zero.
An integration current $\Gamma$ is said to be associated with
$D$ if the equality below hold for every
$g\in\mathcal E(X)$:
\[
\Gamma(dg)= \sum\, \mu_\nu\cdot g(p_\nu)
\]
\medskip

\noindent
{\bf{F.1 Principal divisors.}}
Let $f$ be a non-constant meromorphic function.
Now we have the finite set of poles $\{p_\nu\}$ and the finite set of zeros
$\{q_j\}$.
We associate the divisor
\[
\text{div}(f)= \sum\, \mu_k\cdot \delta(p_k)-\sum\, \mu_j\cdot \delta(q_j)
\]
Here $\mu_k$ is the order of the pole of $f$ at every $p_\nu$, while
$\mu_j$ is the order of a zero at $q_j$.
By the result in ¤ xx this divisor has degree zero.
A divisor $D$ of degree zero is called principal if
it is equal to $\text{div}(f)$ for some
$f\in\mathcal M(X)$.
Notice that if $f$ and $g$ is a pair of non-constant meromorphic functions such that
$\text{div}(f)= \text{div}(g)$, then
$f/g$ is a holomorphic function on $X$ and hence reduced to a non-zero constant.
Introducing the multiplicative group
$\mathcal M(X)^*$ of non-constant meromorphic functions
this means that one has an injective map
\[
\frac{\mathcal M(X)^*}{{\bf{C}}^*}\to\mathcal D_0
\]
where $\mathcal D_0$ is the additive group of divisors whose degree are zero.
The  theorem below describes the range of this map.

\medskip

\noindent
{\bf{F.2 Theorem.}}
\emph{A divisor $D$ of degree zero
is principal if and only if there
exists an integration current $\Gamma$ associated with
$D$  such that}
\[
\Gamma(\omega)=0\quad\colon \,\,\gamma\in \Omega(X)
\]
\medskip

\noindent
The proof requires several steps.
First we shall show the "if part", i.e. if 
$\Gamma$ exists so that (*) holds then
the divisor $D$ is principal.
To achieve this we first
perform a local construction in the complex plane.
\medskip

\noindent
{\bf{F.3 A class of currents in ${\bf{C}}$.}}
In the complex $z$-plane we consider
a point $z_0$ where 
\[
0<|z_0|<r<1
\]
holds for some $0<r<1$.
It is easily seen that there exists
a $C^\infty$-function $a(z)$  in ${\bf{C}}$
which never is zero and the function
\[
\phi(z)= \frac{z}{z-z_0}\cdot a(z)
\]
is identically one when
$|z|\geq r$.
Now $z\mapsto \frac{1}{z-z_0}$ is locally integrable around
$z_0$ and hence $\phi$ belongs to 
$L^1_{\text{loc}} ({\bf{C}})$ and is therefore a distribution.
\medskip

\noindent
Cauchy's residue formula can be expressed by saying
the $\bar\partial$-image of the $\frac{1}{z}$
is equal to the $(0,1)$-current
$2\pi i\cdot \delta(0)d\bar z$ where $\delta(0)$ is the Diraqc distribution
at the origin.
Using this the reader can check that
\[
\bar\partial(\phi)=
 \frac{z}{z-z_0}\cdot \bar\partial(a)+z_0a(z_0)\cdot \delta(z_0)d\bar z\tag{i}
 \]
 from (i) the reader should also check that
 \[
 \phi^{-1}\cdot \bar\partial(\phi)= a^{-1}\cdot \bar\partial(a)\tag{ii}
 \]
 \medskip
 
 \noindent
 {\bf{F.4 The current $\phi^{-1}\cdot \partial(\phi)$.}}
 To begin we one has
 \[
 \partial(\phi)=\frac{a(z)}{z-z_0}\cdot dz-
 \frac{za}{(z-z_0)^2)}\cdot dz+\frac{z}{z-z_0}\cdot \partial a\tag{F.4.1}
 \]
 Above $(z-z_0)^{-2}$ is the principal value distribution
 defined as in ¤ xx.
 \medskip
 
 \noindent
 {\bf{ Exercise.}}
 Use (F.4.1) to establish the equation
 \[
 \phi^{-1}\cdot \partial(\phi)=z^{-1}\cdot dz-(z-z_0)^{-1}\cdot dz+
 a^{-1}\cdot \partial(a)\tag{F.4.2}
 \]
 \medskip
 
 \noindent
 {\bf{Exercise.}}
 Use Stokes Theorenm and Cauchy's residue fornula to
 prove that when the 1-current
 \[
 \phi^{-1}\cdot d\phi=  \phi^{-1}\cdot \partial(\phi)+ \phi^{-1}\cdot \bar \partial(\phi)
 \] 
 is applied to $dg$ for some
 $g\in C_0^\infty({\bf{C}}$, then
 \[
 \phi^{-1}\cdot d\phi<dg>\, = 2\pi i\cdot (g(0)-g(z_0)\tag{F.4.3}
 \]
\medskip


\noindent
 Let us now consider an integration current
 $\Gamma$ given by a finite sum
 $\sum\,\gamma_j$ where each $\gamma_j$ has compact support in
 a chart
 $(U_j,z_j)$ in $X$ and the end-points of
 $\gamma_j$ are $z_j=0$ and $z_j=z_j^*$
 with $0<|z_j^*|<r<1$ and $U_j$ is a chart defined by
 $\{|z_j|<1|]$.
In $X$ the point $z_j=0$ is denoted by $q_j$ while $z_j^*$ corresponds to a
point $p_j$.
It follows that 
 \[
 \int_\Gamma \, dg=\sum_{j=1}^{j=N}\, g(p_j)-g(q_j)\tag{F.5}
 \]
for every $g\in \mathcal E(X)$.
 Next, for each $j$ we apply the local contruction the chart
 and find a function
 $\phi_j$ in $X$ which is identically one
 in $X\setminus \{|z_j|\leq r\}$ such that 
 \[
 \phi_j^{-1}\cdot d\phi_j<dg>=2\pi i\cdot \int_{\gamma_j}\, dg\quad\colon\, g\in \mathcal E(X)
 \]
 More generally, since
 $d$-closed 1-forms in the chart $U_j$ are $d$-exact the re4ader should check that
 (F.5) implies that
 \[
 \phi_j^{-1}\cdot d\phi_j<\alpha>=2\pi i\cdot \int_{\gamma_j}\,\alpha\tag{F.6}
 \]
 hold for every $d$-closed differential 1-form $\alpha$.
 Let us now consider the function
 \[
 \Phi= \prod_{j=1}^{j=N}\, \phi_j
 \]
 \medskip
 
 \noindent
 {\bf{F.7 Exercise.}}
 From the above the
 reader should check  that
 the construction of the $\phi$-functions imply that
 $\Phi$ is a zero-free
 $C^\infty$-function
 in $X\setminus \{q_j,p_j\}$, i.e. in the open complement of
 the finite set
  which is the union of these   $q$  and  $p$ points.
Moreover,  additivity for logarithmic derivatives and 
(F.6) above gives
\[
\Phi^{-1}\cdot d\Phi<\alpha>=
\int_\Gamma\, \alpha\tag{F.7.1}
\]
for every $d$-closed 1-form
$\alpha$. Finally, show that
\[
\Phi^{-1}\cdot \bar\partial(\Phi)=
\sum\, a_j^{-1}\cdot \bar\partial(a_j)\tag{F.7.2}
\]
where the right hand side is a smooth $(0,1)$-form.
\medskip

\noindent
{\bf{F.8 A special case.}}
Suppose that $\Gamma$ is such that
\[
\int_\Gamma\, \omega=0\quad\colon\quad \omega\in\Omega(X)\tag{F.8.1}
\]
The equality in (F.7.1) applied to  $d$-closed holomorphic 1-forms
and
Theorem ¤ xx  entail  that
the smooth $(0,1)$-form
$\Phi^{-1}\cdot \bar\partial(\Phi)$ from (F.7.2) is $\bar\partial$-exact.
Thus, we can find $G\in \mathcal E(X)$ such that
\[
\bar\partial(G)= \Phi^{-1}\cdot \bar\partial(\Phi)\tag{F.8.2}
\]
\medskip


\noindent
{\bf{Exercise.}}
Put
\[
\Psi=e^{-G}\cdot \Phi
\]
deduce from the above  that
$\bar\partial(\Psi)=0$ holds in
$X\setminus \{q_j,p_j\}$ and hence $\Psi$ is holomorphic in
this open subset of $X$
Show also  that the local constructions of the
$\phi$-functions inside the charts
$\{U_jz_j\}$ entail  that
$\psi$ extends to a mermorphic function in
$X$ whose princial divisor is equal to
\[
\sum\, \delta(q_j)-\sum \delta(p_j)
\]
Funally the reader should confirm that the constructions above
prove the "if part" in Theorem F.2.
\medskip


\centerline{\emph{F.9 Proof of the "only if part"}}
\medskip

\noindent 
Here we are given a non-constant meromorphic funvtion
$f$.
We shall condtruct an integration chain $\Gamma$ as follows:
Frst $f\colon X\to {\bf{P}}^1$ is a holomorphic map.
With $s=f(x)$
we recall from (xx) that the number critical $s$-points in
the complex $s$-plane is finite.
In ${bf[P})^1$ we choose a simple
curve $\gamma_*$ with intial point at $s=0$ and end-point at
$s=|nfty$, while
$\gamma_*$ avoids the critical points $s\neq 0$ in
${\bf{C}}$.
of course, while this is done we can choose
$\gamma_*$ so that it is a smooth curve
on the $C^\infty$-manifold ${\bf{P}}^1$.
\medskip

\noindent
{\bf{The inverse image $f^{-1}(\gamma_*)$.}}
Let $N=\deg(f)$.
Since $\gamma_*$ avoids $f$-cirtical points we see that
\[
f^{-1}(\gamma_*\setminus \{0,\infty\})= \gamma_1\cup\ldots\cup\,\gamma_N
\]
where $\{\gamma_j\}$ are disjoint  curves in
$X$, each of which is oriented via
$\gamma_*$ which from the start moves from
$s=0$ to $s=\infty$.
\medskip

\noindent
{\bf{Exercise.}}
Show that the closure $\bar\gamma_j$ yields a rectifiable  curve
whose initial point is zero of $f$ and the end-point a pole.
Put
\[
\Gamma=\sum\, \bar\gamma_j
\]
and conclude from the above that
$\Gamma$ is associated to the principal divisor of $f$.
The proof of the "onmy if part" is therefore finished if we show that
\[
\int_\Gamma\,\omega=0\quad\colon\quad \omega\in \Omega(X)\tag{*}
\]
To prove (*) we shall  use
a certain trace map.
First, a holomorphic 1-form
$\omega$ on $X$ is regared as a $\bar\partial$-closed current with
bi-degree $(0,1)$.
Since the amp $f\colon X\to {\bf{P}}^1$ is proper
there exists the direct image current
$f_*(\Omega$ and we recal from general facts that
the passage to direct image currents commute with
the $\bar\partial$-operator.
hence $\bar\partial(f_*(\Omega))==$ and since
$\bar\partial$ is elliptic it follows that
$f_*(\omega)$ is a holomorphic 1-form on
${\bf{P}}^1$.
By the result in Exercise xx there does not exist non-zero globally defined
holomorphic 1-forms on the projective line.
hence
\[ 
f_*(\omega)=0\tag{**}
\]
In partocuar we have
\[
\int_{\gamma_*(\epsilon)}\, f_*(\omega)=0
\]
where $\gamma_*(\epsilon)$ is the closed 
curve given by $\gamma$ intersected with
$\{\epsilon\leq |s| \leq \epsilon^{-1}\}$
for a small $\epsilon>0$.
\medskip

\noindent
{\bf{Exercise.}}
Put $\Gamma(\epsilon)= f^{-1}(\gamma(\epsilon)$
and dediuce from (xx) that
\[
\int_{\Gamma(\epsilon)}\, \omega=0
\]
Finally, pass to the limit as $\epsilon\to 0$ and conclude that (*) holds which finishes the proof of
the "only if part".



 
 
 
 \newpage
 
 \centerline{\bf{G. Holomorphic line bundles.}}
 
 
\bigskip

\noindent
There exists the multiplicative sheaf
$\mathcal O_X^*$ whose sections are zero-free
holomorphic functions.
every such function is locally $e^g$ with $g\in \mathcal O_X$
where $g$ is determined up to an integer multiple of $2\pi i$.
This gives an exact sheaf sequence
\[
0\to {\bf{Z}}_X\to \mathcal O_X\overset{\exp}\to \mathcal O^*_X\to 0
\]
where $\exp$ sends $g$ to $e^{2\pi i g}$
and ${\bf{Z}}_X$ is the sheaf of locally constant  integer-valued functions on
$X$.
Notice that global sections in
$\mathcal O_X^*$ are reduced to non-zero complex numbers
and we have the short exact sequence
\[
0\to {\bf{Z}}\to {\bf{C}}\overset{\exp}\to {\bf{C}}^*\to 0
\]
Conclude that one has an exact sequence
\[
0\to H^1({\bf{Z}}_X)\to H^1(\mathcal O_X)\to
H^1(\mathcal O_X^*)\to H^2({\bf{Z}}_X)\to 0\tag{G.1}
\]
As explained in ¤ xx
the cohomology group $H^1({\bf{Z}}_X)$
is a free abelian group of rank $2g$
while
$H^2({\bf{Z}}_X)={\bf{Z}}$.























 
 

 
 
 
 
 
 
 
 





\end{document}





















\newpage





\centerline{\bf{Riemann surfaces.}}

\bigskip

\noindent
A compact Riemann surface
$X$ is by definition a connected and compact
complex analytic manifold of dimension one.
The maximum principle for holomorphic functions entails that
every globally defined holomorphic funtions on $X$
is a  constant.
Thus, $\mathcal O(X)$ is reduced to the complex field.
But if one allows poles we shall learn that there exist non-constant
meromorphic functions
on $X$. They give a field denoted by
$\mathcal M(X)$ whose properties will
be investigated later on.
The projective line ${\bf{P}}^1$
over the complex field is an example of a compact Riemann surface.
One starts with the complex $z$-plane and adds the point at
infinity to get ${\bf{P}}^1$. In ¤ xx we explain that
$\mathcal M({\bf{P}}^1)$ is equal to 
the field of rational functions of
the single complex variable $z$.
More generally, compact Riemann surfaces
arise when one starts from
an irreducible polynomial $P(x,y)$
of two independent variables, i.e.
$P$ is irreducible in the unique factorisation domain
${\bf{C}}[x,y]$.
We shall learn how to find the associated compact
Riemann surface $X$ where $\mathcal M(X)$
is isomorphic to the quotient field of the integral domain
$\frac{{\bf{C}}[x,y)}{(P)}$
where $(P)$ denotes the principal ideal generated
by $P$.
Here is  an example. Let 
\[
P(x,y)= y^3-x^3-1
\]
To get $X$ one first regards the
algebraic curve in ${\bf{C}}^2$ defined by
$\{P=0\}$.
The complex gradient
vector $(P'_x,P'_y)= (3x^2,3y^2)\neq (0,0)$ when $P(x,y)=0$. It 
means that $\{P=0\}$ is non-singular
and hence can be regarded  as an embedded one-dimensional complex manifold
in
${\bf{C}}^2$.
To get a compact complex manifold one regards the
projective curve $S$ in ${\bf{P}}^2$
with its inhomogeneous coordintes
$(\zeta,x,y)$
where $S$ is the zero set of $P^*(\zeta,x,y)= y^3-x^3-\zeta^3$.
We shall learn  that $S$  is non-singular
and therefore gives a compact Riemann surface.
Less obvious is that
$S$ regarded as a topological space is
homeomorphic to
the oriented real manifold
$T^2$, where $T^2$ denotes the 2-dimensional torus.
We shall learn that  $S\simeq T^2$ as a topological space because 
$\mathcal M(S)$ contains
a meromorohiuc function $u$
which has one double pole and two simple zeros on
$S$ and is otherwise holomorphic without zeros.
An example of such a meromorphic function is
\[
u=\frac{1}{y-x}
\]
whose properties as a meromorphic function on
$S$ will
be described in ¤ xx.



\medskip
\noindent
In ¤ xxx we
expose the pioneering work
by Hermann Weyl devoted to "abstract" Riemann surfaces.
His text-book from 1913
proves
the existence of non-constant
meromorphic  functions on a given compact 1-ddiensional complex manfold $X$.
From this Weyl deduced that
$\mathcal M(X)$ is an  algebraic functon field, i.e.
as a field extension over
${\bf{C}}$ its the degree of trancendency is one
and in addition  finitely generated.
Using the existence of primitive elements in
finite algebraic extensions of fields in characterstic zero
it follows that $\mathcal M(X)$
is isomorphic to the quotoent field of an integral domain
\[
\frac{{\bf{C}}[x,y]}{P(x,y)}
\]
where $P(x,y)$ is an irreducible polynomial in
the unique  factorisation domain ${\bf{C}}[x,y]$.
So every compact
Riemann surface arises from an irreducible
polynomial $P(x,y)$. 
In ¤ xx we shall learn
that
a compact Riemann surface $X$ is determined by
the field $\mathcal M(X)$.
More precisely, let $Y$ be another compact Riemann surface
and assume that there exists a ${\bf{C}}$-linear isomorphism
\[
\rho\colon \mathcal M(X)\to \mathcal M(Y)
\]
Thus, the two algebraic function fields are isomorphic.
In ¤ xx we show that this implies that 
$X$ and $Y$ are isomorphic
as complex manifolds, i.e.
$\rho$ yields a \emph{biholomorphic map}
from $X$ to $Y$.
\medskip

\noindent
{\bf{Non-compact Riemann surfaces.}}
In addition to compact Riemann surfaces there  exist
open   Riemann surfaces $X$. It means that
$X$ is a connected but non-compact complex manifold of dimension one.
Here 
$\mathcal O(X)$ contains an  extensive
 family of non-constant functions.
In ¤ xx we expose  results due to Behnke and Stein about
open  Riemann surfaces, One major fact is 
that one can prescribe zeros and poles
in an arbitrary fashion on $X$ 
which correspond to a globally defined meromorophic function on
$X$, i.e $\mathcal M(X)$ is  "optimally ample".
The \emph{Uniformisation Theorem}
is proved in ¤ xx.
It implies for example that
every simply connected open Riemann surface is either
biholomorphic to the open unit disc or the complex plane.
The  uniformisation theorem for
connected  open
subsets $\Omega$ of the complex $z$-plane
deserve special attention.
More precisely, if $\Omega\subset{\bf{C}}$ is
open and connected and the complement contains at least two points, then
there exists a holomorphic map
\[
\phi\colon D\to \Omega
\]
where $D$ is the open unit disc, and
$\phi$ has the following two properties: 
It is surejctive, i.e. $\phi(D)=\Omega$ and locally
conformal, i.e. the complex derivative
$\phi'(z)$ has no zeros.
In ¤ xx we shall learn that this entails that thr universal covering space of
$\Omega$ is homeomorphic to the open unit disc which is 
achieved via the  locally biholomorphic map $\phi$.
The uniformisation theorem for planar domains
was proved by Hermann Schwarz around 1860. He
adopted Riemann's methods for
simple connected domains and this classic  result  
is exposed in ¤ xx
in connection with Riemann's ordinary conformal mapping theorem for
simply connected planar domains.
Even though Schwarz's Uniformisation Theorem can be deduced via
the general case  by Behnke and Stein, it is instructive to pursue
his original proof which only relies upon analytic function theory.
\bigskip



\centerline{\bf{About methods of proofs.}}
\medskip

\noindent
The study of Riemann surfaces offer instructive lessons in sheaf theory since
various sheaves
appear in a natrual fashion. The reader is supposed to be familiar with
basic facts about sheaves and their cohomology. But for less experienced readers we
add an appenbdix where
som fundamental reults from Leray's   pioneering article
\emph{xxxx} are resumed. Let us also 
remark that even if Weierstrass never
introduced the notion of sheaves, his construction of
"sheaf spaces" attached to in general multiu.valued abnalytic functions
gave the first  exampe of sheaves.
In addition to sheaf theory we employ calculus on manifolds without
hesitation.
For example. let $M$ be an oriented  real $C^\infty$-manifold of some dimension
$n\geq 2$. To say that $M$ is oriennted means that
there exists a globally defined differential $n$-form
which never vanishes and choosing the orientation
one can define integrals
\[
\int_M\, \omega\quad\colon\quad \omega\in \mathcal E^n(M)
\]
where $\mathcal E^n(M)$ is the space of 
$n$-forms with $C^\infty$-.coefficients.
More generally there exist to each
$0\leq p\leq n$ the space
$\mathcal E^p(M)$ of differential $p$-forms
with $C^\infty$-coefficients.
Under the condition that $M$ can be covered by a denumarable family of compact subsets
it follows  that
$\mathcal E^p(M)$ is equipped with a topology so that it
becomes a Frechet spaces.
There also exists the spaces
$\{\mathcal E^p_0(M)\}$
which consist of differential forms having compact support in
$M$.
The dual of
$\mathcal E^p_0(M)$ is denoted by
$\mathfrak{c}^{n-p}(M)$ and its elements are called currents of
degree $n-p$.
in particular $\mathfrak{c}^0(M)$ is the space of distributions on
$M$ and is often denoted by
$\mathfrak{Db}(M)$. Thus, by definition
\[
\mathfrak{Db}(M)\simeq \mathcal E^n_0(M)^*
\]
where (*) indicates that one regards the dual space.
We assume that the reader is famiiar with basic distribution theory which for
example is coveed in Hšrmander's text-book
[xx], where the passage to manifolds and currents 
become  trivial using charts on $C^\infty$-manifolds and $C^\infty$-partitions  of the unity.
Even if we shall not study manifolds of dreal dimension $\geq 3$
we recall some classic facts about oriented and compact $C\infty-$manifolds
Let $M$ be a such a manifold of siome dimension $n\geq 2$.
using exterior differentials one
has a complex
\[
0\to \mathcal E^0(M)\to \mathcal E^1(M)\to\ldots\to \mathcal E^n(M)\to 0
\]
Here
\[
d\colon \mathcal E^p(M)\to \mathcal E^{p+1}(M)
\] 
are continuous for every $p$, where we recall that
every $\mathcal E^p(M)$ is a Frechet space.
A fundamental fact is that the images of the $d$-maps above
are closed and have finite codimension.
Ths can be proved in several ways. The most convincing proof is due to
AndrŽ Weil who also established that
every compact and oriented manifold $M$ can be tringulated
via  a finite simplicial complex.
So readers interested in algebraic topology should  consult Weil's
original proof which teaches a good lesson
dealing with
topology and triangulations of manifolds.
Now one introduces the cohomology spaces
\[
H^p(M)= \frac{\text{Ker}_d(\mathcal E^p(M)}{d\mathcal E^{p-1}(M)}\quad\colon 0\leq p\leq n
\]
In particular $H^0(M)$ is the $d$-kernel on $C^\infty(M)$ and hence the
1-dimensional space of constant functuons.
One has also the complex of currents:
\[
0\to \mathfrak{c}^0(M)\to \mathfrak{c}^1(M)\to\ldots\to \mathfrak{c}^n(M)\to 0\tag{**}
\]
It is denoted by
$\mathfrak{c}^\bullet$.
For every $p$ one has the inclusion $\mathcal E^p(M)\subset\mathfrak{c}^p(M)$ 
and hence  Hence 
(*) above is a subcomplex of (**).
Next, the  contruction of currents and their exterior differentials, togehter eith
the closed range of the differentials in (*), 
give
a natural  duality
\[
H^p(M)^*\simeq \frac{\text{Ker}_d(\mathfrak{c}^{n-p})}{
d(\mathfrak{c}^{n-p-1}(M)}= H^{n-p}(\mathfrak{c}^\bullet)
\]
In addition to this
the fact that $M$ admits a triangulation implies that
the complexes (*) and (**) are quasi-isomorphic.
Hence the right hsnd side in (**) can be identfied with
$H^{n-p}(M)$, i.e. the dual of $H^p(M)$ is
equal to th cohomology space in degree $n-p$.
This is referred to as PoincarŽ duality theorem for compact
and oriented  manifolds.















\medskip

\noindent
{\bf{Some examples when $n=2$.}}
Let $M$ be an oriented  $C^\infty$-manifold of dimension two.
Since $M$ can be covered by a finite family of
charts  we can equip $M$ with a distance function
$d$ whose restriction to charts is equivsrnt to ordinsty euclidian metroc.
Every pair of such distance functions
$d_1$ and $d_2$ are equivalent in the sense that
there exists a constant $C>0$ such that
\[
C^{-1}|cdot d_2(p,q)\leq d_1(p,q)\leq C\cdot d_2(p,q)
\]
hold for every pair $p,q$ in $M$.
Next, a  parametrized curve
on $M$ is a map $\gamma\colon [0,1]\to M$
which is continuous.
Using a metric as above we can impose the
extra condition that
$\gamma$ has a bounded variation, i.e. there exists a constant $C$ such that
\[
\sum_{\nu=0}^{\nu=N-1}\, d(\gamma(t_{\nu+1}),\gamma(t_\nu)\leq C\tag{i}
\]
for all partitions
$0=t_0<t_1<\ldots<t_{N-1}<t_N=1$.
When (i) holds  there exist ordinary Borel-Stieltjes' integrals
\[
\int_\gamma\, \psi^1\tag{*}
\] 
for every differential 1-form $\psi^1$ with $C^\infty$-coefficents.
This gives a continuous  functional on
$\mathcal E^(M)$ with compact support and hence a current of
degree 1, called 
the integration current associated with
$\gamma$. This "operative construction" will
be used at many places later on.
One merit is that  "nasty geometric pictures"
when $\gamma$ for example has self-intersections
can be ignored while one
treats its associated integration current.
The case when $\gamma$ is closed, i.e. when
$\gamma(1)=\gamma(0)$ 
leads to special results. To begin with
we notice that
the equality $\gamma(0)= \gamma(1)$ entails that
\[
\int_\gamma\, dg=0\quad\colon\quad g\in \mathcal E(M)
\]
This is expressed by saying that the current
$\int_\gamma$ is $d$-closed.
A crucial result which follows from
the fact that
every distribution in ${\bf{R}}^2$ has  locally primitive distributuions with
respect to the pair of euclidian coordinates in
${\bf{R}}^2$, entails that
the following complex vector spaces are isomorphic
\[
\frac{\text{Ker}_d(\mathcal E^1(M)}{d(\mathcal E^0(M)}\simeq
\frac{\text{Ker}_d(\mathfrak{c}^1(M)}{d(\mathfrak{Db}(M)}\simeq
H^1(M)
\]
where the last term is the cohomology space in degree one on $M$.
This entials that if $\gamma$ is a closed and rectifiable curve 
then there exists a $d$-closed 1-form
$\phi\in \mathcal E^1(M)$ and a distribution $\mu$ such that
\[
\int_\gamma=d(\mu)+\phi^1\tag{*}
\]
where this equality takes place in
$\mathfrak{c}^1(M)$.
Moreover, the $d$-closed 1-form $\phi^1$ is
unique up to
an exact smooth 1-form.
With $\gamma$  regarded as a linear functional on
$\mathcal E^1(M)$ the reader should check that
(*) gives the equality
below for every $d$-closed $\psi^1\in\mathcal E^1(M)$:
\[
\gamma(\psi^1)= \int_M\, \phi^1\wedge \psi^1
\]
\medskip

\noindent
{\bf{The $d$-closed current $\int_{\partial\Omega}$.}}
Let $\Omega$ be a connected open set in $M$
whose boundary $\partial\Omega$ is regular in the sense of
Federer. It means that
there exists a (possibly empty) closed set
$\Sigma\subset\partial\Omega$ whose 1-dimensional Haussdorff measure is zero
while 
$\partial\Omega_*=\partial\Omega\setminus \Sigma$
is locally simple and rectifiable.
That is. for each $p\in\partial\Omega_*$ there exists
a bijective map $\gamma$ from the
closed unit intervalÊ$[0,1]$
to
a connected
subset of $\partial\Omega_*$
where $p=\gamma(1/2)$ while the distinct end-points
$\gamma(0)$ and $\gamma(1)$ stay in
$\partial\Omega_*$.
The orientation  along$\partial\Omega_*$ is given by the rule of thumbs
which appears
in the classic version of
Stokes Theorem as found already by Archimedes.
The extra the  condition is that the total variation, or equivalently the
arc-length measure of
$\partial\Omega_*$ is finite while it is evaluated with
respect to a local euclidian distance function, is finite.
Under these conditions one has
\[
\int_\Omega\, d\phi= \int_{\partial\Omega_*}\, \phi
\]
for each $\phi\in \mathcal E^1(M)$.
In particular the 1-current defined via the right hand side is $d$-closed.
Notice that we do not assume that
$\partial\Omega$ is connected.
\medskip

\noindent









\noindent
{\bf{Direct images of currents.}}
Let $\rho\colon M\to N$
be a $C^\infty$-map from $M$ to another oriented 
and compact 2-dimensional manifold $N$.
Elie Cartan's
construction of differential forms on manifolds give for
each $\phi\in\mathcal E^1(N)$ a pullback
$\rho^*(\phi)\in \mathcal E^1(M)$.
The map  is continuous when $\mathcal E^1(N)$ and
$\mathcal E^1(M)$ are equipped with
their standard Frechet topologies.
In particular we regard a
parametrized curve
$\gamma$ and obtain 
a 1-current
$\rho_*(\gamma)$ on $N$ defined by
\[
\rho_*(\phi)= \int_\gamma\, \rho^*(\phi)
\]
Later on we shall use  such direct images of currents at several places.
The reader  should "accept" that it is often  more profitable to
ignore "intuitive genetroic pictures" while calculations 
are performed.
An extra merit is  that
while the integrals along the  $\gamma$ is computed, then
calcluus teaches that one can employ
different parametrisatiin  along $\gamma$. as long as they
have bounded variation and preserve the given orientation.
Notice that even if $\gamma$ from the start is a simple Jordan arc, it
may occur that $\rho_*(\gamma)$
has a more involved structure  since
the restriction of the map $\rho$ to $\gamma$ need not be
one-to-one.
\medskip


\noindent
{\bf{Intersection numbers.}}





If $\rho $ is another  closed and rectifiabsle curve we have a
similar decomposition
\[
\int_\rho=\psi^1+d(\nu)
\]
Stokes Theorenm entials that
\[
\int_M\, \phi^1\wedge \psi^1\tag{*}
\]
is independent of the chosen decompostions.
So the complex number in (*) depends only upon the ordered
pair of closed curves
$(\gamma,\rho)$ and  is denoted by
$\mathfrak{i}(\gamma,\rho)$ and called the intersection number of the closed curves.
Elementaty calculus shows
that the intersection number always in an integer,
and by continuity it follows that
if $\gamma$ and $\gamma^*$ are two homotopic closed curves
then
$\mathfrak{i}(\gamma,\rho)=
\mathfrak{i}(\gamma^*,\rho)$ for every other closed curve
$\rho$.









Following original work by Riemann one
regards
specific simple closed curves
$\gamma_1,\ldots,\gamma_{2g}$ which give
a free basis for the fundamental group $\pi_1(M)$ which is free of some rank $2g$
where $g$ is a positive number.
Here we exlude the case when
$M\simeq S^2$, i.e $M$ is not
homoemorphic to the sphere. Instead $M$ is homeomorphic to a sphere where
$g$ handles have been attached and
with this picture  in mind one can draw $2g$-many
closed curves
on $M$ whose intersection numbers
are special. More precisely, there exists 
a pair of $g$-tuples $\gamma_1,\ldots,\gamma_g$ and
$\rho_1,\ldots,\rho_g)$ , where all these $2g$ many closed curves are simple
and
\[
\mathfrak{i}(\gamma_\nu,\rho_\nu)=1\quad\colon \quad 1\leq\nu\leq g
\]
while all other intersection numbers are zero.


\newpage















\newpage


\centerline{\bf{Analysis on compact Riemann surfaces.}}
\bigskip


\noindent
Let $X$ be a compact 1-dimensional complex manifold.
Recall that its 
complex analytic structure arises via charts
$(U,z)$ where $z$ is a local coordinate on
$X$ in the open set $U$ which is biholomorphic with
the open disc $D=\{|\zeta|<1\}$ in the complex $\zeta$-plane.
Let $\rho_U\colon U\to D$ be the holomorphic map.
When a pair of charts
$U$ and $V$ overlap
their complex analytic structures are
compatible. It means that
one has a biholomorphic map
\[
\rho_{U.V}\colon \rho_U(U\cap V)\to
\rho_V(U\cap V)
\]
where 
\[
\rho_U(\zeta)=\rho_V\circ\rho_{U,V}(\zeta)\quad\colon
\zeta\in \rho_U(U\cap V)
\]
The reader should illustrate this by a suitable picture
to see how the transition functions work
in overlapping charts
Since $X$ is compact it can be covered by a finite family of charts
$\mathfrak{U}= \{U_\alpha,z_\alpha)\}$. So here $\cup \, U_\alpha=X$
and one refers to $\mathfrak{U}$ as an atlas for the complex manifold $X$.
If $U$ is an arbitrary open set
in $X$ a complex valued function $f$ in $U$ is holomorphic if
\[
f\circ \rho_\alpha^{-1}\in \mathcal O(\rho_\alpha(U\cap\, U_\alpha))
\]
hold for
every chart in the atlas.
The set of holomorphic functions in $U$ is denoted by
$\mathcal O(U)$.
Local existence of non-constant holomiorphic functions is clear since
the defintion above entails  that
if $U_\alpha$ is a chart then
$\mathcal O(U_\alpha)\simeq \mathcal O(D)$.
\medskip


\noindent
{\bf{Differential calculus  on $X$.}}
A complex analytic atlas is in particular  a
$C^\infty$-atlas on the underlying real manifold
which has real dimension two.
The space of complex-vaued $C^\infty$-functions on
$X$ is denoted by $\mathcal E(X)$.
We have also the space $\mathcal E^1(X)$
of differential 1-forms
with
$C^\infty$-coefficients.
In a chart $(U,z)$
every differential 1-form can be decomposed as
\[
a\cdot dz+b\cdot d\bar z\tag{A.0}
\]
where $a$ and $b$ are complex-valued $C^\infty$-functions.
This gives a direct sum decomposition
\[
\mathcal E^1(X)=\mathcal E^{1.0}(X)\oplus\, \mathcal E^{0,1}(X)\tag{A.1}
\]
One refers to $\mathcal E^{1,0}$ as the space of diffeential 
forms of bi-degree $(1,0)$.
Thet are characterised by the condition that
$b=0$ holds in
$(A.0)$ for every  chart.
Similarly  when $a=0$  hold we get
a differential form of bi-degree $(0,1)$.
If $g\in\mathcal E(X)$ its exterior differential $dg$
is a 1-form which has a decompostion
\[
dg=\partial g+\bar\partial g
\]
For example, one has a map
\[
\bar\partial\colon\mathcal E(X)\to \mathcal E^{0,1}(X)\tag{A.2}
\]
The Cauchy-Riemann equations applied in charts show that
the kernel in (A.2) consists of holomorphic functions and
hence the kernel is reduced to  constant functions.
\medskip

\noindent
Next, we also have differential 2-forms on $X$ which in a chart $(U,z)$
can be expressed as
\[
c(z)\cdot dz\wedge d\bar z
\]
Keeping the complex analytic structure in mind
we denote the space of differential 2-forms with
$\mathcal E^{1,1}(X)$.
The reader should
construct the  maps
\[
\bar\partial\colon \mathcal E^{1,0}(X)\to \mathcal E^{1.1}(X)\tag{A.3}
\]
\[
\partial\colon \mathcal E^{0,1}(X)\to \mathcal E^{1.1}(X)\tag{A.4}
\]
\medskip

\noindent
Next, recall that $\mathcal E(X)$ is a Frechet space
where the topology is defined via uniform convergence of
derivatives in every order.
In a similar fashion $\mathcal E^{p,q}(X)$
are Frechet spaces for every pair $0\leq p,q\leq 1$.
The reader should  check that 
the maps in (A:2-4)  are continous between these 
Frechet spaces.
Less obvious is the folloowing:
\medskip

\noindent
{\bf{A.5 Theorem.}}
\emph{Tbe range of the exterior differential maps
in (A.2-4) above are all closed.}
\bigskip




\noindent
{\bf{A.6. Remark.}}
This is the first non-trivial result
about compact Riemann surfaces.
We give the proof in (*) and remark only that it
relies upon
a classic result due to Pompieu which gives solutions to
the inhomogeneous $\bar\partial$-partial 
equation in planar
domains. More precisely, if
$U$ is an open set  in the complex $\zeta$-plane and
$g\in C^\infty(U)$ then
there exists $f\in C^\infty(U)$ such that
\[
\bar\partial(f)= g\cdot d\bar\zeta\tag{A.6.1}
\]
\bigskip

\noindent
{\bf{A.7 Currents on $X$.}}
To  begin with we have the space
$\mathfrak{Db}(X)$ of distributions which by  definition it is the 
space of continuos linear forms on the Frechet space
$\mathcal E^{1,1}(X)$, i.e.
\[
\mathfrak{Db}(X)= \mathcal E^{1,1}(X)^*
\]
Passing to differential forms
we get dual spaces
\[ 
\mathfrak{c}^{1,0}(X)=\mathcal E^{0,1}(X)^*
\quad\colon\quad
\mathfrak{c}^{0,1}(X)=\mathcal E^{1,0}(X)^*
\]
Finally, we have the space $\mathfrak{c}^{1.1}(X)$
which is the dual of $\mathcal E(X)$.
\medskip

\noindent
{\bf{B.1 The integration current $1_X$.}}
The reader should check that
the complex analytic structure on $X$ entails that its underlying
real manifold is oriented.
It  follows that if
$\gamma\in \mathcal E^{1,1}(X)$
then there exists an integral
\[
\int_X\, \gamma
\]
This defines a distribution   denoted by
$1_X$.
In general we have an inclusion
\[
\mathcal E(X)\subset\mathfrak{Db}(X)
\]
Namely, if $g$ is a $C^\infty$-function we get
a linear form on
$\mathcal E^{1,1}(X)$ defined by
\[
\gamma\mapsto \int_X\, g\cdot \gamma
\]
If
$\gamma^{1,0}$ belongs to
$\mathcal E^{1,0}(X)$
we notice that Stokes Theorem gives
\[
0=\int_X\, d(g\cdot \gamma^{1,0})
\]
Now the reader should verify that
\[
d(g\cdot \gamma^{0,1})=
\bar\partial g\wedge \gamma^{1,0}+g\cdot \bar\partial(\gamma^{1,0})
\]
Next, by definition the
$(0,1)$-current $\bar\partial g$
is defined by
\[
\bar\partial(g)\langle \gamma^{1,0}\rangle=-\int_X\, g\cdot \bar\partial(\gamma^{1,0})
\]
Keeping  signs in mind one concludes that
when $g$ from the start is identified with a distribution, then
the $(0,1)$-current $\bar\partial(g)$ is equal to the smooth
differential 1-form
of  bi-degree (0,1) arising when
$\bar\partial$ is applied to the $C^\infty$-function $g$.
\medskip

\noindent
{\bf{B.2 A  duality result.}}
We have the map
\[
\bar\partial\colon \mathcal E^{1,0}(X)\to \mathcal E^{1,1}(X)
\]
By Theorem A.5 the range is closed.
This implies that
the dual space
\[
\bigl[\, \frac{\mathcal E^{1,1}(X)}{\bar\partial \mathcal E^{1,0}(X)}\,\bigr]^*
\simeq \text{Ker}_{\bar\partial}(\mathfrak{Db}(X))\tag{B.2.1}
\]
Next, recall that  $\bar\partial$ is elliptic.Indeed, via the   classic Pompieu formula for planar
doimains  every distribution $\mu$ satisfying
the homogeneous equation $\bar\partial(\mu)=0$ is a holomorphic
function.
Since $\mathcal O(X)$ is reduced to constants the
dual space in (B.2.1)  is 1-dimensional and hence
\[
\dim_{{\bf{C}}}\, \frac{\mathcal E^{1,1}(X)}{\bar\partial \mathcal E^{1,0}(X)}=1\tag{B.2.2}
\]
Notice also that Stokes Theorem gives
\[
\int_X\, \bar\partial(\gamma^{1,0})=0\quad\colon\, \gamma^{1,0}\in \mathcal E^{,1,0}(X)
\]
from this we conclude thatif 
$\rho^{1,1}$ is a  2-form for which
$\int_X\,\rho^{1,1}\neq 0$, then
\[
\mathcal E^{1,1}(X)={\bf{C}}\cdot \rho\oplus
\bar\partial(\mathcal E^{1,1}(X))\tag{B.2.3}
\]
\medskip

\noindent{\bf{B.3 A second duality.}}
Theorem A.5 entails that
\[
\bigl[\, \frac{\mathcal E^{0,1}(X)}{\bar\partial \mathcal E(X)}\,\bigr]^*
\simeq \text{Ker}_{\bar\partial}(\mathfrak{c}^{1,0}(X))\tag{B.3.1}
\]
The right hand side is found as follows.
In a chart $(U,z)$
a current of bi-degree
$(1,0)$ is of the form
$\mu\cdot dz$ with
$\mu\in \mathfrak{Db}(U)$.
The $\bar\partial$ image of this current is
zero if and only if $\bar\partial(\mu)=0$ and as we have seen
before this implies that
$\mu$ is a holomorphic density.
Hence the right hand side in (B.3.1) consists of globally defined
\emph{holomorphic} 1-forms. This space is denoted by
$\Omega(X)$ and (B.3.1) can be expressed by
the duality formula
\[
\Omega(X)\simeq\bigl[\, \frac{\mathcal E^{0,1}(X)}{\bar\partial \mathcal E(X)}\,\bigr]^*\tag{B.3.2}
\]
\medskip

\noindent
{\bf{B.3.3 Exercise.}}
Show that (B.3.2) gives the following:
A differential form $\gamma^{0,1}$ on $X$ is $\bar\partial$-exact
if and only if
\[
\int_X\, \omega\wedge \gamma^{0,1}=0\quad\colon\, \forall\,\,
\omega\in \Omega(X)
\]
\medskip

\noindent
{\bf{B.4 Passage to currents.}}
Recall that $\mathcal E^{0,1}(X)\subset\mathfrak{c}^{0,1}$.
in ¤ xx we shall learn that
\[
\mathfrak{c}^{0,1}=\bar\partial(\mathfrak{Db}(X))+
\mathcal E^{0,1}(X)\tag {B.4.1}
\]
Moreover, a $(0.1)$-current $\rho^{0,1}$ is
$\bar\partial$-exact, i.e. of the form
$\bar\partial(\mu)$ for some
distribution $\mu$ on $X$ if and only if
\[
\rho^{1,0}(\omega)=0\quad\colon\quad \omega\in \Omega(X)\tag{B.4.2}
\]
\medskip

\noindent
{\bf{B.5 The case $X={\bf{P}}^1$.}}
Here $\Omega(X)$ is reduced to the zero space.
To see this we suppose that
$\omega$ is a globally defined holomorphic 1-form.
Now ${\bf{P}}^1\setminus \{\infty\}$ is the complex $z$-plane and here
\[
\omega= f(z)\cdot dz
\] 
where $f$ is an entire function.
At the point at infinity we have a local coordinate
$\zeta$ and
\[
\zeta= z^{-1}\quad\colon R<|z|<\infty
\]
hold for every $R>0$.
Since $\omega$ is globally holomorhpic we have
\[
\omega= g(\zeta)\cdot d\zeta
\]
when $0<|\zeta|<R^{-1}$. At the same time the reader can check that
\[
dz=-\zeta^{-2}\cdot d7zeta
\]
holds when $R<|z[<R$. Ths entails that
\[
f(z)=-z^{-2}\cdot g(1/z)\quad\colon |z|>R
\]
From this we see that
the entire function $f$ tends to zero as $|z|\to\infty$
and hence $f$ is identically zero.
So with $X={\bf{P}}^1$ one has $\Omega(X)=0$ and
then (B.4.2) entails that
\[
\mathfrak{c}^{0,1}= \bar\partial(\mathfrak{Db}(X))
\]
In other words, the inhomogeneous $\bar\partial$-equation
is always solvable.
Consider as an example a current
of the form
\[
\gamma=\mu\cdot d\bar z
\]
where $\mu$ is a measure in the complex $z$-plane with compact support.
Now there exists the Cauchy transform
\[
\widehat{\mu}(z)=\int\,\frac{d\mu(\zeta)}{z-\zeta}
\]
It is holomiorphic in
in the open set of the complex $z$-plane where
the compact set
$\text{Supp}(\mu)$ has been removed.
passing to infinity we
notice that
it extends to be holomorphic
because one has the convergent series expansion
\[
\widehat{\mu}(z)=\sum_{n=0}^\infty\,
\int\,\zeta^n|cdot d\mu(\zeta)\cdot z^{-n-1}{z-\zeta}
\]
in an exterior disc
$|z[>R$ where
the support of $\mu$ is contained in
$\{|z|\leq R\}$.
\medskip

\noindent
next, by basuc lebsgue theory one knows that
the funnction $\widehat{\mu}$ is locally integrable
in the whole complex $z$-plane and hence defines a distribution.
Finally, Cacuhy's residue formula shows that
the distribution derivative
\[
\frac{\bar\partial\widehat{\mu}}{\bar\partial\bar z}=\pi \cdot \mu
\]
So we get
\[
\bar\partial(\pi^{-1}\cdot \widehat{\mu})=\mu\cdot d\bar z
\]




















\newpage


\centerline{\bf{C. Some sheaves and their cohomology}}.
\medskip


\noindent
Let $X$ be a compact complex  analytic manifold.
Classic  facts due to Cauchy and Pompieu applied to charts in $X$ 
give  an exact sequence of sheaves
\[
0\to \mathcal O_X\to \mathcal E_X\overset{\bar\partial}\to, \mathcal E_X^{0,1}\to 0\tag{C.0}
\]
Using $C^\infty$-parotions of unity and Leray's theory about  cohomology with
values in sheaves
one gets
\[
H^1(\mathcal O_X)\simeq \frac{
\mathcal E^{0,1}(X)}{\bar\partial(\mathcal E(X)}\tag{C.1}
\]
where the left hand side is the first cohomology groups with
values in the sheaf
$\mathcal O_X$. The reader may also notice that when Leray's long exact sequence for sheaf cohomology is applied to (C.0), then it follows that
\[
H^2(\mathcal O_X)=0\tag{C.2}
\]
Next, we have also the exact sheaf sequence
\[
0\to {\bf{C}}_X\to \mathcal O_X\overset{\partial}\to \Omega_X\to 0\tag{C.3}
\]
Since $H^0({\bf{C}}_X)= H^0(\mathcal O_X)= {\bf{C}}$ and (C.2) holds
one gets the following   exact sequence of complex vector spaces:
\[
0\to \Omega(X)\to H^1({\bf{C}}_X)\to
 H^1(\mathcal O_X)\to H^1(\Omega _X)\to H^2({\bf{C}}_X)\to 0\tag{C.4}
\]
Next, we have
also the following exact sheaf sequence
\[
0\to \Omega_X\to \mathcal E^{1,0}_X\overset{\bar\partial}\to \mathcal E_X^{1,1}\to 0\tag{C.5}
\]
This gives the equality
\[
H^1(\Omega_X)\simeq\frac{\mathcal E^{1,1}(X)}{\bar\partial(\mathcal E^{1,0}(X))}\tag{C.6}
\]
The right hand side rsssembles the quotient in
(B.2.2).
Indeed, we can regard the 7emph{conjugate} analytic structure on
the underlying real manifold of $x$ where the sheaf of holomorphic functions
are compex cojugates of sections in
$\mathcal O_X$. From this the reader may conclude via (B.2.2)
that the rifht hand side in (C.5)
is a 1-dimensional vector space. Hence we have 
\[
\dim_{{\bf{C}}}\,H^1(\Omega_X)=1\tag{C.7}
\]
\medskip

\noindent
Next, recall that
$H^2({\bf{C}}_X)={\bf{C}}$. Together with (C.7) we conclude that
 (C.4) gives the
short exact sequence
\[
0\to \Omega(X)\to H^1({\bf{C}}_X)\to
 H^1(\mathcal O_X)\to 0\tag{C.8}
\]
Topology teaches that
the cohomology space
$H^1({\bf{C}}_X)$Êis finite dimensional.
Hence (C.8) implies that both
$\Omega(X)$ and $H^1(\mathcal O_X)$ are finite dimensional complex vector spaces.
Finally, (B.3.2) and (C.1) give
\[
\Omega(X)\simeq\bigl [\, H^1(\mathcal O_X)\,\bigr]^*\tag{C.9}
\]
In particular the complex vector spaces
$\Omega(X)$ and $H^1(\mathcal O_X)$ have the same dimension.
This equality and (C.8) give
\[
\dim H^1({\bf{C}}_X)= 2\cdot \dim \Omega(X)\tag{C.10}
\]
The equality (C.10) is fundamental  during the study of compact
Riemann surfaces. 
A notable point is that
the cohomology group $H^1({\bf{C}}_X)$ only depends upon the
topological space $X$ and not upon its particular complex structure.

\bigskip

\noindent
{\bf{C.10 A duality for currents.}}
In planar domains it is wellknown that the
inhomogenous $\bar\partial$-equation is locally solvable on distributions.
Since the $\bar\partial$-kernel on $\mathfrak{Db}_X$ is $\mathcal O_X$
one has an exact sequence
\[
0\to \mathcal O_X\to \mathfrak{Db}_X\overset{\bar\partial}\to
\mathfrak{c}^{0,1}_X\to 0
\]
Passing to cohomology and using 
$C^\infty$-partitions of the unity, it follows that
\[
H^1(\mathcal O_X)\simeq \frac{\mathfrak{c}^{0,1}_X}{
\bar\partial(\mathfrak{Db}(X)}\tag{C.10.1}
\]
\medskip

\noindent
{\bf{Exercise.}} Deduce from the above that
\[
\Omega(X)\simeq\bigl[\, \frac{\mathfrak{c}^{0,1}_X}{
\bar\partial(\mathfrak{Db}(X)}\,\bigr]^*\tag{C.10.2}
\]
Conclude that the implication below holds for
each 
$\gamma\in \mathfrak{c}^{0,1}$:
\[
\gamma(\omega)=0\quad\colon\,\forall\,\, \omega\in \Omega(X)
\implies \gamma\in \bar\partial(\mathfrak{Db}(X))\tag{C.10.3}
\]
\medskip

\noindent
{\bf{C.11 A decomposition theorem.}}
Since $X$ in particular is an oriented and compact real manifold
one has
\[
H^1({\bf{C}}_X)\simeq\frac{\text{Ker}_d(\mathcal E^1(X)}{d(\mathcal E(X)}\tag{C.11.1}
\]
Next, on $X$ there also exists
the anti-holomorphic differential forms of bi-degree
$(0,1)$, i.e differential forms  $\gamma\in \mathcal E^{0,1}(X)$ for which
$\partial(\gamma)=0$.
This space is denoted by $\overline{\Omega}(X)$.
Using the conjugate complex analytic structure one has another compact
complex manifold $\overline{X}$
where
$\overline{\Omega}(X)$ is the space of holomorphic 1-forms.
Since $X$ and $\overline{X}$ have the same underlying real manifold, it follows from
(C.10) that
\[
\dim H^1({\bf{C}}_X)= 2\cdot \dim \overline{\Omega}(X)\tag{C.11.2}
\]
Using  this we shall prove
\medskip

\noindent
{\bf{C.11.3 Theorem.}}
\emph{One has a direct sum decomposition}
\[
\text{Ker}_d(\mathcal E^1(X))=
d(\mathcal E(X))\oplus \Omega(X)\oplus\overline{\Omega}(X)
\]
\medskip

\noindent
\emph{Proof}
To begin with we notice that
\[
\Omega(X)\,\cap \overline{\Omega}(X)= \{0\}
\]
Counting dimensions this follows if we prove that
a 1-form $\gamma)\omega+\mu$ cannot be $d$-exact
when $\omega\in \Omega(X)$ and $\mu\in \overline{\Omega}(X)$
where at least one these froms is not identically ero.
For suppose that
$\gamma=dg$ is $d$-exact.
If $\omega$ is not identically zero there exists
the conjugate
form
$\bar\omega\in\overline{\Omega}(X)$.
Now Stokes Theorem gives
\[
0=\int_X\, dg\cdot \bar\omega)=\int_X(\omega+\mu)\wedge\bar\omega=
\int_X(\omega\wedge\bar\omega
\]
Now the reader can check that
the last integral is $\neq 0$ when $\omega$ is not identically zero.
hence $\gamma\in d(\mathcal E(X))$ implies that
$\Omega=0$ and in the same way we find that
$\mu=0$ which proves Theorem C.11.3.








\newpage


\centerline{\bf{D. Existence of meromorphic functions.}}
\bigskip


\noindent
On $X$ there exists the sheaf
$\mathcal M_X$ whose sections are meromorphic  functions.
Subsheaves arise via  constraints on  poles.
In particular, let $p\in X$ be a given point and
$m$ a positive integer.
Denote by $\mathcal O_X[* mp]$
the sheaf whose sections are meromorphic functions on
$X$ which are holomorphic in $X\setminus\{p\}$ and have
poles of order $\leq m$ at $p$.
If $(U,z)$ is a chart where $p$ corresponds to
the origin we seee that
\[
\mathcal O_X[* mp]\,|U= z^{-m}\cdot \mathcal OX|U
\]
Taking Laurent exapnsions
every section in the right hand side is of the form
\[
f+\frac{c_1}{z}+\ldots+\frac{c_m}{z^m}
\]
where $f\in \mathcal O_X$ and $\{c_\nu\}$ is an $m$-tuple of complex numbers.
Expressed by  sheaves it gives
an exact sequence
\[
0\to \mathcal O_X\to \mathcal O_X[*mp]\to S_p^m\to 0\tag{D.1}
\]
where $S_p$ is the scyscraper sheaf suppotet  by $\{p\}$
and
the stalk $S_p(p)$ is an $m$-dimensional vector space.
Passing to long exact sequence of cohomology the reader 
can verify that there is an exact sequence:
\[
0\to {\bf{C}}\to H^0(\mathcal O_X[*mp])\to
{\bf{C}}^m\to 
H^1(\mathcal O_X)\to H^0(\mathcal O_X[*mp])\to 0\tag{D.1.1}
\]
\medskip

\noindent
{\bf{D.2 Exercise.}}
Use that the vector space 
$H^1(\mathcal O_X)$ is $g$-dimensional and conclude that
\[
\dim_{{\bf{C}}}\, 
H^0(\mathcal O_X[*mp])=m-g+1+
\dim_{{\bf{C}}}\, 
H^1(\mathcal O_X[*mp])\geq m-g+1\tag{D.2.1}
\]
\medskip

\noindent
In particular the left hand side is $\geq 2$ if $m=g+1$
which means that
apart from constants, there exists at least one
constant global section in 
$\mathcal O_X[*(g+1)p]$.
Hence we have proved:

\bigskip

\noindent
{\bf{D.3 Theorem.}}
\emph{For every $p\in X$ there exists a non-constant 
meromorphic function $f$  in $X$ with no poles in
$X\setminus{p}$ while
the order of the pole at $p$ is at most $g+1$.}











\newpage



\centerline{\bf{Weierstrass' points.}}

\bigskip

\noindent
Let $X$ be a compact Riemann surface
whose genus number $g$ is $\geq 2$.
Removing  a point $p\in X$
we get  the space
$\mathcal O(X\setminus\{p\})$.
If $(U,z)$ is a chart centered at $p$
where $p$ corresponds to $z=0$, then every
$f\in\mathcal O(X\setminus\{p\})$
restricts to a holomorphic function in
the punctured disc
$0<|z|<1$
and we can regard its Laurent series:
\[
f(z)=
\sum_{\nu=1}^\infty\ c_\nu\cdot z^{-\nu}+\sum_{\nu\geq 0}\, d_\nu\cdot z^\nu
\]
The negative part of the Laurent series is denoted by $f_*(z)$.
If $f_*=0$ then $f$ is globally holomorphic and hence reduced to
a constant.
So 
\[
f\mapsto f_*(z)+ d_0
\]
yields an  injective 
map from $\mathcal O(X\setminus\{p\})$ 
into the space of
non-positive Laurent series at $z=0$.
We are going to study the range of this map.
Denote by $\mathcal L$
the space 
of all non-positive Laurent series, where we recall that a negative
series
\[
\sum_{\nu=1}^\infty\ c_\nu\cdot z^{-\nu}\in\mathcal L
\]
if and only if
\[
\sum_{\nu=1}^\infty\, |c_\nu|\cdot R^\nu<\infty
\] 
for all $R>0$.
In particular $\mathcal L$ contains the $g$-dimensional subspace
formed by Laurent series given by
finite series:
\[
\rho(z)= c_1z^{-1}+\ldots+c_g\cdot z^{-g}
\]
where $\{c_\nu\}$ is a $p$-tuple of complex numbers.
Let $\mathcal L[p]$ denote this subspace of
$\mathcal L$.
\medskip

\noindent
{\bf{E.1 Theorem.}}
\emph{Outside a finite set ${\bf{W}}$ in $X$
one has} 
\[ 
\mathcal L=\mathcal L[p]\oplus \mathfrak{Im}(\mathcal O(X\setminus\{p\})
\]
\medskip

\noindent
{\bf{E.2 Remark.}}
In ¤xx we show that
the exceptional set
${\bf{W}}$ is non-empty when $g\geq 2$,
If (*) holds above
it follows that when $m>g$
then  there exists a unique $g$-tuple $\{c_\nu\}$ such that 
\[ 
z^{-m}=c_1z^{-1}+\dots+c_gz^{-g}+ \mathfrak{Im}(\phi)
\]
where $\phi$ is holomorphic in
$X\setminus\{p\}$.
Herte the negative Laurent series of $\phi$ is finite
at $p$ which implies that
$\phi$ is a globally defined meromorphic function
with a pole of order $m$ at $p$ whose negative Laurent expnasion at $p$
is of the form
\[
z^{-m}+c_1z^{-1}+\dots+c_gz^{-g}
\]
where the $g$-tuple $\{c_\nu\}$ is uniquely determined and depends on
the chosen integer $m$.
At the same time
the direct dum in (*) entails that
there do not exist non-constant meromorphic functions
which are holomorphic in
$X\setminus\{p\}$ while the order of
the pole at $p$ is $\leq g$.
\medskip

\noindent
The proof of Theorem E.1 requires several steps.
We are given a point
$p\in X$ and let $(U,z)$ be a chart
around $p$ where $p$ corresponds to $z=0$.
Residue calculus gives
a $g$-tuple of 
currents defined by
\[
\rho_\nu=\bar\partial(z^{-\nu})\quad\colon\quad \nu=1,\ldots,g
\]
Each current is supported by the singleton set $\{p\}$
and extends to a current on $X$ supported by $p$.
If $\Psi^{1,0}\in\mathcal E^{1,0}(X)$
we can regard its restriction to $U$ and write
\[
\Psi^{1,0}|U= \psi(z)\cdot dz
\]
with $\psi\in C^\infty(U)$.
Residue calcluus teaches that
\[
\rho_1(\Psi^{1,0})= 2\pi i\cdot \psi(0)
\]
If $\nu\geq 2$ the reader may verify that
\[
\rho_\nu(\Psi^{1,0})= \frac{(-1)^{\nu-1}}{(\nu-1)!}\cdot
\partial^{\nu-1}\psi/\partial z^{\nu-1}(0)
\]
The construction of the $\rho$-currents
is not intrinsic, i.e.
the $g$-tuple  depends on the chosen chart around $p$.
But the reader can check that
the $g$-dimenbsional vector space
in $\mathfrak{c}^{0,1}(X)$
generated by
$\{\rho^\nu\,\colon 1\leq \nu\leq g\}$
does not depend on the chosen chart around $p$.
Let us denote it by $\mathcal W(p)$.
The major step towards the proof of Theorem E.1
is the following:


\medskip

\noindent
{\bf{E.3 Theorem.}} \emph{Outside a finite set
${\bf{W}}$  in $X$ one has
the direct sum decomposition}
\[
\mathfrak{c}^{0,1}(X)=\bar\partial(\mathfrak{Db}(X))\oplus\, \mathcal W(p)\tag{E.3.1}
\]
\bigskip

\noindent
\emph{Proof.}
The duality result in ¤ xx gives (E.3.1)
if
the $g$-tuple
$\{\rho^\nu\}$ restrict to 
${\bf{C}}$-linearly independent in the dual space
$\Omega(X)^*$.
To check when this holds we
consider a basis $\omega_1,\ldots,\omega_g$ in the $g$-dimensional vector space
$\Omega(X)$.
In a chart
$(U,z)$ centered at a point $p_0\in X $ we can write
\[
\omega_j= f_j(z)\cdot dz\tag{i}
\]
where Ê$\{f_j\}$ are ${\bf{C}}$-linearly 
independent in $\mathcal O(U)$.
The general result in ¤ xx  entails that 
the determinant function
\[
\mathcal F(z)= \det\bigl(\partial f_j^\nu/\partial z^\nu(z)\tag{ii}
\]
formed by the $g\times g$-matrix with
elements as above is not identically zero.
Now linear algebra shows that
$\{\rho_\nu\}$ restrict to linearly independent functionals
on $\Omega(X)$ at every $z|in U$ for ehich
$F(z)\neq 0$.
Since the zero set of $F$ in the chart $U$ is discrete
and we can cover
$X$ by a finite famliy of charts, it follows that
(E.3.1) holds outside a finite set
${\bf{W}}$.


\medskip

\noindent
{\bf{E.4 How to find ${\bf{W}}$.}}
In each  chart $(U,z)$ as above we have
the $\mathcal F$-functions from (ii).
If $(U_\alpha,z_\alpha)$ and $(U_\beta,z_\beta)$ is a pair of charts
in $X$ where $U_\alpha\cap U_\beta\neq\emptyset$
we get two $g$-tuples  of analytic functions by
\[
\omega_j|U_\alpha= f_j^\alpha\cdot dz\quad\colon\quad
\omega_j|U_\beta= f_j^\beta\cdot dz_\beta
\]
When $z_\beta=z_\beta(z_\alpha)$ is regarded as
an analytic function in $U_\alpha\cap U_\beta$ one has the equations
\[
f_j^\alpha=\frac{\partial z_\beta}{\partial z_\alpha}\cdot f_j^\beta\tag{E.4.1}
\]
for each $j$ in $U_\alpha\cap U\beta$.
\medskip

\noindent
{\bf{E.4.2 Exercise.}} Show by using
rules for calcuating determinsnts that
(E.4.1) gives
the equation
\[
\mathcal F_\alpha=\bigl(\frac{\partial z_\beta}{\partial z_\alpha}\bigr)^{g(g-1)/2}\cdot F_\beta(z)
\]
So with $N=g(g-1)/2$
the family $\{\mathcal F_\alpha\}$ which arises when
$X$ is covered by a finite number of charts, is a global section of
the $N$-fold product of the holomorphic line bundle $\Omega_X$.
By (xx) the
set of xeros counted with multiplicities  of every global section
in $\Omega_X$ is equal to $2(g-1)$.
So by the general result in ¤ xxx the
zero set of the $\mathcal F$-family counted with multiplicities is equal to
$g(g-1)^2$. Since $g\geq 2$ this is a positive integer and hence
the set ${\bf{W}}$ is non-empty.
\bigskip

\noindent
{\bf{Remark.}} In the literature one refers to
${\bf{W}}$ as the set of Weierstrass' points in $X$.
The determination of ${\bf{W}}$ for a given $X$ with genus $\geq 2$
is in general not easy.
From the above ${\bf{W}}$ contains at most
$(g-1)^2\cdot g$ many distinct points. 
In general the number of points can be
strictly smaller.
Weierstrass investigated
${\bf{W}}$ for special families of compact Riemann surfaces.
See ¤ xx for some comments.
\bigskip

\centerline {\bf{Proof of Theorem E.1}}

\bigskip

\noindent
Consider a point $p\in X$ which is outside ${\bf{W}}$ and let $(U,z)$ be a chart 
centered at $p$.
Let $U^*=U\setminus\{p\}$ be the punctured open disc.
In $X$ we also have the open set
$X\setminus\{p\}$
which can be regarded as an open Riemann surface.
The theorem by Behnke and Stein from
the chapter devoted to open Rieann surfaces
gives
$H^1(X\setminus\{p\},\mathcal O)=0$.
The cohomology in the  disc $U$ is also zero.
Hence the open covering of $X$ given by the pair
$\mathfrak{U}= (U,X\setminus\{p\})$
is acyclic with respect to the sheaf
$\mathcal O_X$. So  Leray's acyclicity theorem gives
\[
H^1(X,\mathcal O_X)\simeq \frac{\mathcal O( U^*)}{
\delta(C^0(\mathfrak{U},\mathcal O_X))}\tag{i}
\]
where
\[
\delta\colon \mathcal O(U)\oplus \mathcal O(X\setminus\{p\})\to
\mathcal O(U^*)
\] 
is the Cech coboundary map.
Next, the $g$-tuple $\{z^{-\nu}\colon \nu=1,\ldots,g\}$
are holomorphic in $U^*$
and  their images in the right hand side from (i) give
elements in
$H^1(X,\mathcal O_X)$ denoted by
$\{[z^{-\nu}]\}$.
\medskip

\noindent
{\bf{Exercise.}}
Recall  that
\[
H^1(X.\mathcal OX)= \frac{\mathfrak{c}^{0,1}}{\bar\partial(\mathfrak{Db}(X)}
\]
Since $p$ is outside ${\bf{W}}$
the last quotient is equal to $\mathcal W(p)$.
Conclude from this that
the $g$-tuple
$\{[z^{-\nu}]\}$ is a basis in the $g$-dimensional vector space
$H^1(X,\mathcal O_X)$.
\medskip

\noindent
Let us then consider some
$g\in\mathcal O(U^*)$ which has a  Laurent series
\[
g(z)= \sum_{\nu=1}^\infty\ c_\nu\cdot z^{-\nu}+
\sum_{\nu=0}^\infty\ d_\nu\cdot z^{\nu}
\]
By the Exercise  there exists
a unique $g$-tuple of complex numbers
$a_1,\ldots,a_p$
such that
the image of $g$ in
$H^1(X,\mathcal O_X)$ is equal to $\sum\, a_\nu\cdot [z^{-\nu}]$.
Hence (i) gives a pair $\phi(z)\in\mathcal O(U)$ and $f(z)\in \mathcal O(X\setminus\{p\}$
such that
\[
g(z)-\sum\,\rho_\nu\cdot z^{-\nu}=\phi(z)+f(z)
\]
where $\phi(z)\in\mathcal O(U)$ and $f(z)\in \mathcal O(X\setminus\{p\}$.
Regarding the negative Laurent series it follows that
\[
g_*(z)= \sum\, a_\nu\cdot z^{-\nu}+f_*(z)\tag{ii}
\]
Here $g$ was arbitrary in
$\mathcal O(U^*)$ and hence the proof of Theorem E.1 is finished.
















\newpage










 
 
 
 

\centerline{\bf{F. Abel's theorem.}}



\bigskip


\noindent
A divisor $D$ on $X$ consists of
an assignement of integers $\{\mu_\nu\}$ to a finite set of points $\{p_\nu\}$
in $X$. One writes
\[
D= \sum\, \mu_\nu\cdot \delta(p_\nu)
\]
The $\mu$-integers may be positive or negative.
The degree is defined by
\[
\deg D= \sum\,\mu_\nu
\] 
while the finite set $\{p_\nu\}$ is called the support of $D$.
Next we construct a class of 1-currents.
In general, let $\gamma\colon [0,1]\to X$
be an $X$valued function on the closed unit interval
We assume that $\gamma$ is continuous and has a
finite total variation. The last condition means that
there exists a constant $C$ such that
\[
\sum_{\nu=0}^{\nu=N-1}\, d(\gamma(t_{\nu+1},\gamma(t_\nu)\leq C
\]
for all sequences $0=t_0<t-1<\ldots<t_N=1$
Here $d$ is some  distance function 
on $X$ regarded as a metric space which in charts
is equivsoent to
the euclidian distance.
Every such $\gamma$ gives a current of degree one
acting on $\mathcal E^1(X)$ by 
\[
\alpha\mapsto \int_\gamma \,\alpha\tag{*}
\]
\medskip

\noindent
{\bf{Exercise.}} Explain how the classical Borel-Stieltjes integrals for functions
with bounded variation
defines the integral in the right hand side.
Show also that
\[
\int_\gamma\, dg= g(\gamma(1))-g(\gamma(0))
\]
hold for every $g\in\mathcal E()$.
One refers to (*) as an integration current of degree one.
More generally we can take a finite sum of such
currents and get the integration current
$\Gamma$ defined by
\[
\Gamma(\alpha)= \sum\, \int_{\gamma_j}\,\alpha
\]
Let $D=\sum\,\mu_\nu\cdot \delta(p_\nu)$ be a divisor of
degreee zero.
An integration current $\Gamma$ is said to be associated with
$D$ if the equality below hold for every
$g\in\mathcal E(X)$:
\[
\Gamma(dg)= \sum\, \mu_\nu\cdot g(p_\nu)
\]
\medskip

\noindent
{\bf{F.1 Principal divisors.}}
Let $f$ be a non-constant meromorphic function.
Now we have the finite set of poles $\{p_\nu\}$ and the finite set of zeros
$\{q_j\}$.
We associate the divisor
\[
\text{div}(f)= \sum\, \mu_k\cdot \delta(p_k)-\sum\, \mu_j\cdot \delta(q_j)
\]
Here $\mu_k$ is the order of the pole of $f$ at every $p_\nu$, while
$\mu_j$ is the order of a zero at $q_j$.
By the result in ¤ xx this divisor has degree zero.
A divisor $D$ of degree zero is called principal if
it is equal to $\text{div}(f)$ for some
$f\in\mathcal M(X)$.
Notice that if $f$ and $g$ is a pair of non-constant meromorphic functions such that
$\text{div}(f)= \text{div}(g)$, then
$f/g$ is a holomorphic function on $X$ and hence reduced to a non-zero constant.
Introducing the multiplicative group
$\mathcal M(X)^*$ of non-constant meromorphic functions
this means that one has an injective map
\[
\frac{\mathcal M(X)^*}{{\bf{C}}^*}\to\mathcal D_0
\]
where $\mathcal D_0$ is the additive group of divisors whose degree are zero.
The  theorem below describes the range of this map.

\medskip

\noindent
{\bf{F.2 Theorem.}}
\emph{A divisor $D$ of degree zero
is principal if and only if there
exists an integration current $\Gamma$ associated with
$D$  such that}
\[
\Gamma(\omega)=0\quad\colon \,\,\gamma\in \Omega(X)
\]
\medskip

\noindent
The proof requires several steps.
First we shall show the "if part", i.e. if 
$\Gamma$ exists so that (*) holds then
the divisor $D$ is principal.
To achieve this we first
perform a local construction in the complex plane.
\medskip

\noindent
{\bf{F.3 A class of currents in ${\bf{C}}$.}}
In the complex $z$-plane we consider
a point $z_0$ where 
\[
0<|z_0|<r<1
\]
holds for some $0<r<1$.
It is easily seen that there exists
a $C^\infty$-function $a(z)$  in ${\bf{C}}$
which never is zero and the function
\[
\phi(z)= \frac{z}{z-z_0}\cdot a(z)
\]
is identically one when
$|z|\geq r$.
Now $z\mapsto \frac{1}{z-z_0}$ is locally integrable around
$z_0$ and hence $\phi$ belongs to 
$L^1_{\text{loc}} ({\bf{C}})$ and is therefore a distribution.
\medskip

\noindent
Cauchy's residue formula can be expressed by saying
the $\bar\partial$-image of the $\frac{1}{z}$
is equal to the $(0,1)$-current
$2\pi i\cdot \delta(0)d\bar z$ where $\delta(0)$ is the Diraqc distribution
at the origin.
Using this the reader can check that
\[
\bar\partial(\phi)=
 \frac{z}{z-z_0}\cdot \bar\partial(a)+z_0a(z_0)\cdot \delta(z_0)d\bar z\tag{i}
 \]
 from (i) the reader should also check that
 \[
 \phi^{-1}\cdot \bar\partial(\phi)= a^{-1}\cdot \bar\partial(a)\tag{ii}
 \]
 \medskip
 
 \noindent
 {\bf{F.4 The current $\phi^{-1}\cdot \partial(\phi)$.}}
 To begin we one has
 \[
 \partial(\phi)=\frac{a(z)}{z-z_0}\cdot dz-
 \frac{za}{(z-z_0)^2)}\cdot dz+\frac{z}{z-z_0}\cdot \partial a\tag{F.4.1}
 \]
 Above $(z-z_0)^{-2}$ is the principal value distribution
 defined as in ¤ xx.
 \medskip
 
 \noindent
 {\bf{ Exercise.}}
 Use (F.4.1) to establish the equation
 \[
 \phi^{-1}\cdot \partial(\phi)=z^{-1}\cdot dz-(z-z_0)^{-1}\cdot dz+
 a^{-1}\cdot \partial(a)\tag{F.4.2}
 \]
 \medskip
 
 \noindent
 {\bf{Exercise.}}
 Use Stokes Theorenm and Cauchy's residue fornula to
 prove that when the 1-current
 \[
 \phi^{-1}\cdot d\phi=  \phi^{-1}\cdot \partial(\phi)+ \phi^{-1}\cdot \bar \partial(\phi)
 \] 
 is applied to $dg$ for some
 $g\in C_0^\infty({\bf{C}}$, then
 \[
 \phi^{-1}\cdot d\phi<dg>\, = 2\pi i\cdot (g(0)-g(z_0)\tag{F.4.3}
 \]
\medskip


\noindent
 Let us now consider an integration current
 $\Gamma$ given by a finite sum
 $\sum\,\gamma_j$ where each $\gamma_j$ has compact support in
 a chart
 $(U_j,z_j)$ in $X$ and the end-points of
 $\gamma_j$ are $z_j=0$ and $z_j=z_j^*$
 with $0<|z_j^*|<r<1$ and $U_j$ is a chart defined by
 $\{|z_j|<1|]$.
In $X$ the point $z_j=0$ is denoted by $q_j$ while $z_j^*$ corresponds to a
point $p_j$.
It follows that 
 \[
 \int_\Gamma \, dg=\sum_{j=1}^{j=N}\, g(p_j)-g(q_j)\tag{F.5}
 \]
for every $g\in \mathcal E(X)$.
 Next, for each $j$ we apply the local contruction the chart
 and find a function
 $\phi_j$ in $X$ which is identically one
 in $X\setminus \{|z_j|\leq r\}$ such that 
 \[
 \phi_j^{-1}\cdot d\phi_j<dg>=2\pi i\cdot \int_{\gamma_j}\, dg\quad\colon\, g\in \mathcal E(X)
 \]
 More generally, since
 $d$-closed 1-forms in the chart $U_j$ are $d$-exact the re4ader should check that
 (F.5) implies that
 \[
 \phi_j^{-1}\cdot d\phi_j<\alpha>=2\pi i\cdot \int_{\gamma_j}\,\alpha\tag{F.6}
 \]
 hold for every $d$-closed differential 1-form $\alpha$.
 Let us now consider the function
 \[
 \Phi= \prod_{j=1}^{j=N}\, \phi_j
 \]
 \medskip
 
 \noindent
 {\bf{F.7 Exercise.}}
 From the above the
 reader should check  that
 the construction of the $\phi$-functions imply that
 $\Phi$ is a zero-free
 $C^\infty$-function
 in $X\setminus \{q_j,p_j\}$, i.e. in the open complement of
 the finite set
  which is the union of these   $q$  and  $p$ points.
Moreover,  additivity for logarithmic derivatives and 
(F.6) above gives
\[
\Phi^{-1}\cdot d\Phi<\alpha>=
\int_\Gamma\, \alpha\tag{F.7.1}
\]
for every $d$-closed 1-form
$\alpha$. Finally, show that
\[
\Phi^{-1}\cdot \bar\partial(\Phi)=
\sum\, a_j^{-1}\cdot \bar\partial(a_j)\tag{F.7.2}
\]
where the right hand side is a smooth $(0,1)$-form.
\medskip

\noindent
{\bf{F.8 A special case.}}
Suppose that $\Gamma$ is such that
\[
\int_\Gamma\, \omega=0\quad\colon\quad \omega\in\Omega(X)\tag{F.8.1}
\]
The equality in (F.7.1) applied to  $d$-closed holomorphic 1-forms
and
Theorem ¤ xx  entail  that
the smooth $(0,1)$-form
$\Phi^{-1}\cdot \bar\partial(\Phi)$ from (F.7.2) is $\bar\partial$-exact.
Thus, we can find $G\in \mathcal E(X)$ such that
\[
\bar\partial(G)= \Phi^{-1}\cdot \bar\partial(\Phi)\tag{F.8.2}
\]
\medskip


\noindent
{\bf{Exercise.}}
Put
\[
\Psi=e^{-G}\cdot \Phi
\]
deduce from the above  that
$\bar\partial(\Psi)=0$ holds in
$X\setminus \{q_j,p_j\}$ and hence $\Psi$ is holomorphic in
this open subset of $X$
Show also  that the local constructions of the
$\phi$-functions inside the charts
$\{U_jz_j\}$ entail  that
$\psi$ extends to a mermorphic function in
$X$ whose princial divisor is equal to
\[
\sum\, \delta(q_j)-\sum \delta(p_j)
\]
Funally the reader should confirm that the constructions above
prove the "if part" in Theorem F.2.
\medskip


\centerline{\emph{F.9 Proof of the "only if part"}}
\medskip

\noindent 
Here we are given a non-constant meromorphic funvtion
$f$.
We shall condtruct an integration chain $\Gamma$ as follows:
Frst $f\colon X\to {\bf{P}}^1$ is a holomorphic map.
With $s=f(x)$
we recall from (xx) that the number critical $s$-points in
the complex $s$-plane is finite.
In ${bf[P})^1$ we choose a simple
curve $\gamma_*$ with intial point at $s=0$ and end-point at
$s=|nfty$, while
$\gamma_*$ avoids the critical points $s\neq 0$ in
${\bf{C}}$.
of course, while this is done we can choose
$\gamma_*$ so that it is a smooth curve
on the $C^\infty$-manifold ${\bf{P}}^1$.
\medskip

\noindent
{\bf{The inverse image $f^{-1}(\gamma_*)$.}}
Let $N=\deg(f)$.
Since $\gamma_*$ avoids $f$-cirtical points we see that
\[
f^{-1}(\gamma_*\setminus \{0,\infty\})= \gamma_1\cup\ldots\cup\,\gamma_N
\]
where $\{\gamma_j\}$ are disjoint  curves in
$X$, each of which is oriented via
$\gamma_*$ which from the start moves from
$s=0$ to $s=\infty$.
\medskip

\noindent
{\bf{Exercise.}}
Show that the closure $\bar\gamma_j$ yields a rectifiable  curve
whose initial point is zero of $f$ and the end-point a pole.
Put
\[
\Gamma=\sum\, \bar\gamma_j
\]
and conclude from the above that
$\Gamma$ is associated to the principal divisor of $f$.
The proof of the "onmy if part" is therefore finished if we show that
\[
\int_\Gamma\,\omega=0\quad\colon\quad \omega\in \Omega(X)\tag{*}
\]
To prove (*) we shall  use
a certain trace map.
First, a holomorphic 1-form
$\omega$ on $X$ is regared as a $\bar\partial$-closed current with
bi-degree $(0,1)$.
Since the amp $f\colon X\to {\bf{P}}^1$ is proper
there exists the direct image current
$f_*(\Omega$ and we recal from general facts that
the passage to direct image currents commute with
the $\bar\partial$-operator.
hence $\bar\partial(f_*(\Omega))==$ and since
$\bar\partial$ is elliptic it follows that
$f_*(\omega)$ is a holomorphic 1-form on
${\bf{P}}^1$.
By the result in Exercise xx there does not exist non-zero globally defined
holomorphic 1-forms on the projective line.
hence
\[ 
f_*(\omega)=0\tag{**}
\]
In partocuar we have
\[
\int_{\gamma_*(\epsilon)}\, f_*(\omega)=0
\]
where $\gamma_*(\epsilon)$ is the closed 
curve given by $\gamma$ intersected with
$\{\epsilon\leq |s| \leq \epsilon^{-1}\}$
for a small $\epsilon>0$.
\medskip

\noindent
{\bf{Exercise.}}
Put $\Gamma(\epsilon)= f^{-1}(\gamma(\epsilon)$
and dediuce from (xx) that
\[
\int_{\Gamma(\epsilon)}\, \omega=0
\]
Finally, pass to the limit as $\epsilon\to 0$ and conclude that (*) holds which finishes the proof of
the "only if part".



 
 
 
 \newpage
 
 \centerline{\bf{G. Holomorphic line bundles.}}
 
 
\bigskip

\noindent
There exists the multiplicative sheaf
$\mathcal O_X^*$ whose sections are zero-free
holomorphic functions.
every such function is locally $e^g$ with $g\in \mathcal O_X$
where $g$ is determined up to an integer multiple of $2\pi i$.
This gives an exact sheaf sequence
\[
0\to {\bf{Z}}_X\to \mathcal O_X\overset{\exp}\to \mathcal O^*_X\to 0
\]
where $\exp$ sends $g$ to $e^{2\pi i g}$
and ${\bf{Z}}_X$ is the sheaf of locally constant  integer-valued functions on
$X$.
Notice that global sections in
$\mathcal O_X^*$ are reduced to non-zero complex numbers
and we have the short exact sequence
\[
0\to {\bf{Z}}\to {\bf{C}}\overset{\exp}\to {\bf{C}}^*\to 0
\]
Conclude that one has an exact sequence
\[
0\to H^1({\bf{Z}}_X)\to H^1(\mathcal O_X)\to
H^1(\mathcal O_X^*)\to H^2({\bf{Z}}_X)\to 0\tag{G.1}
\]
As explained in ¤ xx
the cohomology group $H^1({\bf{Z}}_X)$
is a free abelian group of rank $2g$
while
$H^2({\bf{Z}}_X)={\bf{Z}}$.























 
 

 
 
 
 
 
 
 
 

\newpage











\centerline{\bf{Compact Riemann surfaces.}}

\bigskip

\noindent
A compact Riemann surface
$X$ is by definition a connected and compact
complex analytic manifold of dimension one.
The maximum principle for holomorphic functions entails that
every globally defined holomorphic funtions on $X$
is a  constant.
Thus, $\mathcal O(X)$ is reduced to the complex field.
But if one allows poles we shall learn that there exist non-constant
meromorphic functions
on $X$. They give a field denoted by
$\mathcal M(X)$ whose properties will
be investigated later on.
The projective line ${\bf{P}}^1$
over the complex field is an example of a compact Riemann surface.
Topologically it is homeomorphic to
a where and as a module one takes the
As a model one starts with the complex $z$-plane and adds the point at
infinity. Now $\mathcal M({\bf{\P}}^1)$
becomes the field of rational functions of
the single complex variable $z$.
Other compact Riemann urfaces
arise when one starts from
an irreducible polynomial $P(x,y)$
of two independent variables, i.e.
$P$ is irreducible in the unique factorisation domain
${\bf{C}}[x,y]$.
We shall learn how to find the associated compact
Riemann surface $X$ where $\mathcal (X)$
is isomorphic to the quotient field of the integral domain
$\frac{{\bf{C}}[x,y)}{(P)}$
where $(P)$ denotes the princial ideal generated
by $P$.
As an example we take
\[
P(x,y)= y^3-x^3-1
\]
To get $X$ one first regards the
algebraic curve in ${\bf{C}}^2$ defined by
$\{P=0\}$.
Since the complex gradient
vector $(P'_x,P'_y)= (3x^2,3y^2)\neq (0,0)$
it follows that $\{P0=\}$ is non-singular
and therefore brcomes an embedded one-dimensional complex manifold
in
${\bf{C}}^2$.
To get a copmpact complex manifold one regards the
prjective curve in ${\bf{P}}^2$
with its inhomogeneous coordintes
$(\zeta,x,y)$
where the zero set of $P^*(\zeta,x,y)= y^3-x^3-\zeta^3$
yields a projective curve $S$.
We shall learn  that $S$  is non-singular
and therefore gives a compact Riemann surface.
Less obvious is that
$S$ regarded as a topological space is
homeomorphic to
the oriented real manifold
$T^2$, where $T^2$ denotes the 2-dimensional torus.
The reason why $S\simeq T^2$ as a topoligcal space is that
$\mathcal M(S)$ contains
a meromorohiuc function $u$
which has one double pole and two simple zeros on
$S$ and is otherwise holomorphic without zeros.
An example of such a meromorphic function is
\[
u=\frac{1}{y-x}
\]
whose properties as a meromorphic function on
$S$ will
be described in ¤ xx.
\medskip
\noindent
In ¤ xxx we
expose the pioneering work
by Hermann Weyl devoted to "abstract" Riemann surfaces which
in particular prove
the existence of non-constant
meromorphic  functions. 
From this Weyl deduced that
$\mathcal M(X)$ is a so called algebraiuc functon field, i.e.
as a filed extension over
${\bf{C}}$ the degree of trancendency is one
and in addition it is finitely generated.
Using the existence of primitive elements in
finite algebraic extensions of fields in characterstic zero
it follows that $\mathcal M(X)$
is isomorphic to the quotoent field of an integral domain
\[
\frac{{\bf{C}}[x,y]}{P(x,y)}
\]
where $P(x,y)$ is an irreducible polynomial in
the unique  factorisation domain ${\bf{C}}[x,y]$.
So every compact
Riemann surface arises from an irreducible
polynomial $P(x,y)$. 
A remarkable fact is that
a compact Riemann surface $X$ is determiuned by
the field $\mathcal M(X)$.
More precisely, let $Y$ be another compact Riemann surface
and assume that there exists a ${\bf{C}}$-linear isimorohism
\[
\rho\colon \mathcal M(X)\to \mathcal M(Y)
\]
Thus, the two algebraic function fields are isomorphic.
In ¤ xx we show that
$X$ and $Y$ are isomorphic
as complex manifolds, i.e.
$\rho$ yields a \emph{biholomorphic map}
from $X$ to $Y$.
\medskip

\noindent
{\bf{Non-compact Riemann surfaces.}}
In addition to compact Riemann surfaces there  exist
open -or non-compact- Riemann surfaces $X$. It means that
$X$ is a connected but non-compact complex manifold of dimension one.
In this case it turns out
that
$\mathcal O(X)$ contains a quite extensive
 family of non-constant functions.
In ¤ xx we expose  results due to Behnke and Stein about
non-compact Riemann surfaces which
for example show that one can prescribe zeros and poles
in an arbitrary fashion and
which correspond to a globally defined meromorophic function on
$X$, i.e $\mathcal M(X)$ is so to speak "optimally ample".
In ¤ xx we also expose the \emph{Uniformisation Theorem}
where our proof follows that
of  
Behnke  and Stein. It implies for example that
every simply connected open Riemann surface is either
biholomorphic to the open unit disc or the complex plane.
The  uniformisation theorem for
connected  open
subsets $\Omega$ of the complex $z$-plane
deserve special attention.
More precisely, if $\Omega\subset{\bf{C}}$ is
open and connected and the complement contains at least two points, then
there exists a holomorphic map
\[
\phi\colon D\to \Omega
\]
where $D$ is the open unit disc, and
$\phi$ has the following two properties: First
it is surejctive, i.e. $\phi(D)=\Omega$ and moreover it is locally
conformal, i.e. the complex derivative
$\phi'(z)$ has no zeros.
In ¤ xx we shall learn that this entails that thr universal covering space of
$\Omega$ is homeomorphic to the open unit disc which is 
achieved via the  locally biholomorphic map $\phi$.
The uniformisation theorem for planar domains
is due to Hermann Schwarz who adopted Riemann's methods for
simple connected domains and is 
be exposed in ¤ xx
in connection with Riemann's ordinary conformal mapping theorem for
simply connected planar domains.
Even though Schwarz's Uniformisation Theorem can be deduced via
the general case treated by Behnke and Stein, it is instructive to pursue
his original proof which only relies upon analytic function theory.
As expected it is in general very hard to
obtain explicit formulas. 
An example is when
$\Omega$ is the open complement of
${\bf{C}}$ where one has removed
three disjoint closed intervals
$\{[a_\nu,b_\nu]\}$ where
$a_1<b_1<a_2<b_2<a_3<b_3$.
See ¤ xx for a discussion related to this case.
\bigskip



\centerline{\bf{About methods of proofs.}}
\medskip

\noindent
The study of Riemann surfaces offer instructive lessons in sheaf theory since
various sheaves
appear in a natrual fashion. The reader is supposed to be familiar with
basic facts about sheaves and their cohomology. But for less experienced readers we
add an appenbdix where
som fundamental reults from Leray's   pioneering article
\emph{xxxx} are resumed. Let us also 
remark that even if Weierstrass never
introduced the notion of sheaves, his construction of
"sheaf spaces" attached to in general multiu.valued abnalytic functions
gave the first  exampe of sheaves.
In addition to sheaf theory we employ calculus on manifolds without
hesitation.
For example. let $M$ be an oriented  real $C^\infty$-manifold of some dimension
$n\geq 2$. To say that $M$ is oriennted means that
there exists a globally defined differential $n$-form
which never vanishes and choosing the orientation
one can define integrals
\[
\int_M\, \omega\quad\colon\quad \omega\in \mathcal E^n(M)
\]
where $\mathcal E^n(M)$ is the space of 
$n$-forms with $C^\infty$-.coefficients.
More generally there exist to each
$0\leq p\leq n$ the space
$\mathcal E^p(M)$ of differential $p$-forms
with $C^\infty$-coefficients.
Under the condition that $M$ can be covered by a denumarable family of compact subsets
it follows  that
$\mathcal E^p(M)$ is equipped with a topology so that it
becomes a Frechet spaces.
There also exists the spaces
$\{\mathcal E^p_0(M)\}$
which consist of differential forms having compact support in
$M$.
The dual of
$\mathcal E^p_0(M)$ is denoted by
$\mathfrak{c}^{n-p}(M)$ and its elements are called currents of
degree $n-p$.
in particular $\mathfrak{c}^0(M)$ is the space of distributions on
$M$ and is often denoted by
$\mathfrak{Db}(M)$. Thus, by definition
\[
\mathfrak{Db}(M)\simeq \mathcal E^n_0(M)^*
\]
where (*) indicates that one regards the dual space.
We assume that the reader is famiiar with basic distribution theory which for
example is coveed in Hšrmander's text-book
[xx], where the passage to manifolds and currents 
become  trivial using charts on $C^\infty$-manifolds and $C^\infty$-partitions  of the unity.
Even if we shall not study manifolds of dreal dimension $\geq 3$
we recall some classic facts about oriented and compact $C\infty-$manifolds
Let $M$ be a such a manifold of siome dimension $n\geq 2$.
using exterior differentials one
has a complex
\[
0\to \mathcal E^0(M)\to \mathcal E^1(M)\to\ldots\to \mathcal E^n(M)\to 0
\]
Here
\[
d\colon \mathcal E^p(M)\to \mathcal E^{p+1}(M)
\] 
are continuous for every $p$, where we recall that
every $\mathcal E^p(M)$ is a Frechet space.
A fundamental fact is that the images of the $d$-maps above
are closed and have finite codimension.
Ths can be proved in several ways. The most convincing proof is due to
AndrŽ Weil who also established that
every compact and oriented manifold $M$ can be tringulated
via  a finite simplicial complex.
So readers interested in algebraic topology should  consult Weil's
original proof which teaches a good lesson
dealing with
topology and triangulations of manifolds.
Now one introduces the cohomology spaces
\[
H^p(M)= \frac{\text{Ker}_d(\mathcal E^p(M)}{d\mathcal E^{p-1}(M)}\quad\colon 0\leq p\leq n
\]
In particular $H^0(M)$ is the $d$-kernel on $C^\infty(M)$ and hence the
1-dimensional space of constant functuons.
One has also the complex of currents:
\[
0\to \mathfrak{c}^0(M)\to \mathfrak{c}^1(M)\to\ldots\to \mathfrak{c}^n(M)\to 0\tag{**}
\]
It is denoted by
$\mathfrak{c}^\bullet$.
For every $p$ one has the inclusion $\mathcal E^p(M)\subset\mathfrak{c}^p(M)$ 
and hence  Hence 
(*) above is a subcomplex of (**).
Next, the  contruction of currents and their exterior differentials, togehter eith
the closed range of the differentials in (*), 
give
a natural  duality
\[
H^p(M)^*\simeq \frac{\text{Ker}_d(\mathfrak{c}^{n-p})}{
d(\mathfrak{c}^{n-p-1}(M)}= H^{n-p}(\mathfrak{c}^\bullet)
\]
In addition to this
the fact that $M$ admits a triangulation implies that
the complexes (*) and (**) are quasi-isomorphic.
Hence the right hsnd side in (**) can be identfied with
$H^{n-p}(M)$, i.e. the dual of $H^p(M)$ is
equal to th cohomology space in degree $n-p$.
This is referred to as PoincarŽ duality theorem for compact
and oriented  manifolds.















\medskip

\noindent
{\bf{Some examples when $n=2$.}}
Let $M$ be an oriented  $C^\infty$-manifold of dimension two.
Since $M$ can be covered by a finite family of
charts  we can equip $M$ with a distance function
$d$ whose restriction to charts is equivsrnt to ordinsty euclidian metroc.
Every pair of such distance functions
$d_1$ and $d_2$ are equivalent in the sense that
there exists a constant $C>0$ such that
\[
C^{-1}|cdot d_2(p,q)\leq d_1(p,q)\leq C\cdot d_2(p,q)
\]
hold for every pair $p,q$ in $M$.
Next, a  parametrized curve
on $M$ is a map $\gamma\colon [0,1]\to M$
which is continuous.
Using a metric as above we can impose the
extra condition that
$\gamma$ has a bounded variation, i.e. there exists a constant $C$ such that
\[
\sum_{\nu=0}^{\nu=N-1}\, d(\gamma(t_{\nu+1}),\gamma(t_\nu)\leq C\tag{i}
\]
for all partitions
$0=t_0<t_1<\ldots<t_{N-1}<t_N=1$.
When (i) holds  there exist ordinary Borel-Stieltjes' integrals
\[
\int_\gamma\, \psi^1\tag{*}
\] 
for every differential 1-form $\psi^1$ with $C^\infty$-coefficents.
This gives a continuous  functional on
$\mathcal E^(M)$ with compact support and hence a current of
degree 1, called 
the integration current associated with
$\gamma$. This "operative construction" will
be used at many places later on.
One merit is that  "nasty geometric pictures"
when $\gamma$ for example has self-intersections
can be ignored while one
treats its associated integration current.
The case when $\gamma$ is closed, i.e. when
$\gamma(1)=\gamma(0)$ 
leads to special results. To begin with
we notice that
the equality $\gamma(0)= \gamma(1)$ entails that
\[
\int_\gamma\, dg=0\quad\colon\quad g\in \mathcal E(M)
\]
This is expressed by saying that the current
$\int_\gamma$ is $d$-closed.
A crucial result which follows from
the fact that
every distribution in ${\bf{R}}^2$ has  locally primitive distributuions with
respect to the pair of euclidian coordinates in
${\bf{R}}^2$, entails that
the following complex vector spaces are isomorphic
\[
\frac{\text{Ker}_d(\mathcal E^1(M)}{d(\mathcal E^0(M)}\simeq
\frac{\text{Ker}_d(\mathfrak{c}^1(M)}{d(\mathfrak{Db}(M)}\simeq
H^1(M)
\]
where the last term is the cohomology space in degree one on $M$.
This entials that if $\gamma$ is a closed and rectifiable curve 
then there exists a $d$-closed 1-form
$\phi\in \mathcal E^1(M)$ and a distribution $\mu$ such that
\[
\int_\gamma=d(\mu)+\phi^1\tag{*}
\]
where this equality takes place in
$\mathfrak{c}^1(M)$.
Moreover, the $d$-closed 1-form $\phi^1$ is
unique up to
an exact smooth 1-form.
With $\gamma$  regarded as a linear functional on
$\mathcal E^1(M)$ the reader should check that
(*) gives the equality
below for every $d$-closed $\psi^1\in\mathcal E^1(M)$:
\[
\gamma(\psi^1)= \int_M\, \phi^1\wedge \psi^1
\]
\medskip

\noindent
{\bf{The $d$-closed current $\int_{\partial\Omega}$.}}
Let $\Omega$ be a connected open set in $M$
whose boundary $\partial\Omega$ is regular in the sense of
Federer. It means that
there exists a (possibly empty) closed set
$\Sigma\subset\partial\Omega$ whose 1-dimensional Haussdorff measure is zero
while 
$\partial\Omega_*=\partial\Omega\setminus \Sigma$
is locally simple and rectifiable.
That is. for each $p\in\partial\Omega_*$ there exists
a bijective map $\gamma$ from the
closed unit intervalÊ$[0,1]$
to
a connected
subset of $\partial\Omega_*$
where $p=\gamma(1/2)$ while the distinct end-points
$\gamma(0)$ and $\gamma(1)$ stay in
$\partial\Omega_*$.
The orientation  along$\partial\Omega_*$ is given by the rule of thumbs
which appears
in the classic version of
Stokes Theorem as found already by Archimedes.
The extra the  condition is that the total variation, or equivalently the
arc-length measure of
$\partial\Omega_*$ is finite while it is evaluated with
respect to a local euclidian distance function, is finite.
Under these conditions one has
\[
\int_\Omega\, d\phi= \int_{\partial\Omega_*}\, \phi
\]
for each $\phi\in \mathcal E^1(M)$.
In particular the 1-current defined via the right hand side is $d$-closed.
Notice that we do not assume that
$\partial\Omega$ is connected.
\medskip

\noindent









\noindent
{\bf{Direct images of currents.}}
Let $\rho\colon M\to N$
be a $C^\infty$-map from $M$ to another oriented 
and compact 2-dimensional manifold $N$.
Elie Cartan's
construction of differential forms on manifolds give for
each $\phi\in\mathcal E^1(N)$ a pullback
$\rho^*(\phi)\in \mathcal E^1(M)$.
The map  is continuous when $\mathcal E^1(N)$ and
$\mathcal E^1(M)$ are equipped with
their standard Frechet topologies.
In particular we regard a
parametrized curve
$\gamma$ and obtain 
a 1-current
$\rho_*(\gamma)$ on $N$ defined by
\[
\rho_*(\phi)= \int_\gamma\, \rho^*(\phi)
\]
Later on we shall use  such direct images of currents at several places.
The reader  should "accept" that it is often  more profitable to
ignore "intuitive genetroic pictures" while calculations 
are performed.
An extra merit is  that
while the integrals along the  $\gamma$ is computed, then
calcluus teaches that one can employ
different parametrisatiin  along $\gamma$. as long as they
have bounded variation and preserve the given orientation.
Notice that even if $\gamma$ from the start is a simple Jordan arc, it
may occur that $\rho_*(\gamma)$
has a more involved structure  since
the restriction of the map $\rho$ to $\gamma$ need not be
one-to-one.
\medskip


\noindent
{\bf{Intersection numbers.}}





If $\rho $ is another  closed and rectifiabsle curve we have a
similar decomposition
\[
\int_\rho=\psi^1+d(\nu)
\]
Stokes Theorenm entials that
\[
\int_M\, \phi^1\wedge \psi^1\tag{*}
\]
is independent of the chosen decompostions.
So the complex number in (*) depends only upon the ordered
pair of closed curves
$(\gamma,\rho)$ and  is denoted by
$\mathfrak{i}(\gamma,\rho)$ and called the intersection number of the closed curves.
Elementaty calculus shows
that the intersection number always in an integer,
and by continuity it follows that
if $\gamma$ and $\gamma^*$ are two homotopic closed curves
then
$\mathfrak{i}(\gamma,\rho)=
\mathfrak{i}(\gamma^*,\rho)$ for every other closed curve
$\rho$.









Following original work by Riemann one
regards
specific simple closed curves
$\gamma_1,\ldots,\gamma_{2g}$ which give
a free basis for the fundamental group $\pi_1(M)$ which is free of some rank $2g$
where $g$ is a positive number.
Here we exlude the case when
$M\simeq S^2$, i.e $M$ is not
homoemorphic to the sphere. Instead $M$ is homeomorphic to a sphere where
$g$ handles have been attached and
with this picture  in mind one can draw $2g$-many
closed curves
on $M$ whose intersection numbers
are special. More precisely, there exists 
a pair of $g$-tuples $\gamma_1,\ldots,\gamma_g$ and
$\rho_1,\ldots,\rho_g)$ , where all these $2g$ many closed curves are simple
and
\[
\mathfrak{i}(\gamma_\nu,\rho_\nu)=1\quad\colon \quad 1\leq\nu\leq g
\]
while all other intersection numbers are zero.


\newpage















\newpage


\centerline{\bf{Analysis on compact Riemann surfaces.}}
\bigskip


\noindent
Let $X$ be a compact 1-dimensional complex manifold.
Recall that its 
complex analytic structure arises via charts
$(U,z)$ where $z$ is a local coordinate on
$X$ in the open set $U$ which is biholomorphic with
the open disc $D=\{|\zeta|<1\}$ in the complex $\zeta$-plane.
Let $\rho_U\colon U\to D$ be the holomorphic map.
When a pair of charts
$U$ and $V$ overlap
their complex analytic structures are
compatible. It means that
one has a biholomorphic map
\[
\rho_{U.V}\colon \rho_U(U\cap V)\to
\rho_V(U\cap V)
\]
where 
\[
\rho_U(\zeta)=\rho_V\circ\rho_{U,V}(\zeta)\quad\colon
\zeta\in \rho_U(U\cap V)
\]
The reader should illustrate this by a suitable picture
to see how the transition functions work
in overlapping charts
Since $X$ is compact it can be covered by a finite family of charts
$\mathfrak{U}= \{U_\alpha,z_\alpha)\}$. So here $\cup \, U_\alpha=X$
and one refers to $\mathfrak{U}$ as an atlas for the complex manifold $X$.
If $U$ is an arbitrary open set
in $X$ a complex valued function $f$ in $U$ is holomorphic if
\[
f\circ \rho_\alpha^{-1}\in \mathcal O(\rho_\alpha(U\cap\, U_\alpha))
\]
hold for
every chart in the atlas.
The set of holomorphic functions in $U$ is denoted by
$\mathcal O(U)$.
Local existence of non-constant holomiorphic functions is clear since
the defintion above entails  that
if $U_\alpha$ is a chart then
$\mathcal O(U_\alpha)\simeq \mathcal O(D)$.
\medskip


\noindent
{\bf{Differential calculus  on $X$.}}
A complex analytic atlas is in particular  a
$C^\infty$-atlas on the underlying real manifold
which has real dimension two.
The space of complex-vaued $C^\infty$-functions on
$X$ is denoted by $\mathcal E(X)$.
We have also the space $\mathcal E^1(X)$
of differential 1-forms
with
$C^\infty$-coefficients.
In a chart $(U,z)$
every differential 1-form can be decomposed as
\[
a\cdot dz+b\cdot d\bar z\tag{A.0}
\]
where $a$ and $b$ are complex-valued $C^\infty$-functions.
This gives a direct sum decomposition
\[
\mathcal E^1(X)=\mathcal E^{1.0}(X)\oplus\, \mathcal E^{0,1}(X)\tag{A.1}
\]
One refers to $\mathcal E^{1,0}$ as the space of diffeential 
forms of bi-degree $(1,0)$.
Thet are characterised by the condition that
$b=0$ holds in
$(A.0)$ for every  chart.
Similarly  when $a=0$  hold we get
a differential form of bi-degree $(0,1)$.
If $g\in\mathcal E(X)$ its exterior differential $dg$
is a 1-form which has a decompostion
\[
dg=\partial g+\bar\partial g
\]
For example, one has a map
\[
\bar\partial\colon\mathcal E(X)\to \mathcal E^{0,1}(X)\tag{A.2}
\]
The Cauchy-Riemann equations applied in charts show that
the kernel in (A.2) consists of holomorphic functions and
hence the kernel is reduced to  constant functions.
\medskip

\noindent
Next, we also have differential 2-forms on $X$ which in a chart $(U,z)$
can be expressed as
\[
c(z)\cdot dz\wedge d\bar z
\]
Keeping the complex analytic structure in mind
we denote the space of differential 2-forms with
$\mathcal E^{1,1}(X)$.
The reader should
construct the  maps
\[
\bar\partial\colon \mathcal E^{1,0}(X)\to \mathcal E^{1.1}(X)\tag{A.3}
\]
\[
\partial\colon \mathcal E^{0,1}(X)\to \mathcal E^{1.1}(X)\tag{A.4}
\]
\medskip

\noindent
Next, recall that $\mathcal E(X)$ is a Frechet space
where the topology is defined via uniform convergence of
derivatives in every order.
In a similar fashion $\mathcal E^{p,q}(X)$
are Frechet spaces for every pair $0\leq p,q\leq 1$.
The reader should  check that 
the maps in (A:2-4)  are continous between these 
Frechet spaces.
Less obvious is the folloowing:
\medskip

\noindent
{\bf{A.5 Theorem.}}
\emph{Tbe range of the exterior differential maps
in (A.2-4) above are all closed.}
\bigskip




\noindent
{\bf{A.6. Remark.}}
This is the first non-trivial result
about compact Riemann surfaces.
We give the proof in (*) and remark only that it
relies upon
a classic result due to Pompieu which gives solutions to
the inhomogeneous $\bar\partial$-partial 
equation in planar
domains. More precisely, if
$U$ is an open set  in the complex $\zeta$-plane and
$g\in C^\infty(U)$ then
there exists $f\in C^\infty(U)$ such that
\[
\bar\partial(f)= g\cdot d\bar\zeta\tag{A.6.1}
\]
\bigskip

\noindent
{\bf{A.7 Currents on $X$.}}
To  begin with we have the space
$\mathfrak{Db}(X)$ of distributions which by  definition it is the 
space of continuos linear forms on the Frechet space
$\mathcal E^{1,1}(X)$, i.e.
\[
\mathfrak{Db}(X)= \mathcal E^{1,1}(X)^*
\]
Passing to differential forms
we get dual spaces
\[ 
\mathfrak{c}^{1,0}(X)=\mathcal E^{0,1}(X)^*
\quad\colon\quad
\mathfrak{c}^{0,1}(X)=\mathcal E^{1,0}(X)^*
\]
Finally, we have the space $\mathfrak{c}^{1.1}(X)$
which is the dual of $\mathcal E(X)$.
\medskip

\noindent
{\bf{B.1 The integration current $1_X$.}}
The reader should check that
the complex analytic structure on $X$ entails that its underlying
real manifold is oriented.
It  follows that if
$\gamma\in \mathcal E^{1,1}(X)$
then there exists an integral
\[
\int_X\, \gamma
\]
This defines a distribution   denoted by
$1_X$.
In general we have an inclusion
\[
\mathcal E(X)\subset\mathfrak{Db}(X)
\]
Namely, if $g$ is a $C^\infty$-function we get
a linear form on
$\mathcal E^{1,1}(X)$ defined by
\[
\gamma\mapsto \int_X\, g\cdot \gamma
\]
If
$\gamma^{1,0}$ belongs to
$\mathcal E^{1,0}(X)$
we notice that Stokes Theorem gives
\[
0=\int_X\, d(g\cdot \gamma^{1,0})
\]
Now the reader should verify that
\[
d(g\cdot \gamma^{0,1})=
\bar\partial g\wedge \gamma^{1,0}+g\cdot \bar\partial(\gamma^{1,0})
\]
Next, by definition the
$(0,1)$-current $\bar\partial g$
is defined by
\[
\bar\partial(g)\langle \gamma^{1,0}\rangle=-\int_X\, g\cdot \bar\partial(\gamma^{1,0})
\]
Keeping  signs in mind one concludes that
when $g$ from the start is identified with a distribution, then
the $(0,1)$-current $\bar\partial(g)$ is equal to the smooth
differential 1-form
of  bi-degree (0,1) arising when
$\bar\partial$ is applied to the $C^\infty$-function $g$.
\medskip

\noindent
{\bf{B.2 A  duality result.}}
We have the map
\[
\bar\partial\colon \mathcal E^{1,0}(X)\to \mathcal E^{1,1}(X)
\]
By Theorem A.5 the range is closed.
This implies that
the dual space
\[
\bigl[\, \frac{\mathcal E^{1,1}(X)}{\bar\partial \mathcal E^{1,0}(X)}\,\bigr]^*
\simeq \text{Ker}_{\bar\partial}(\mathfrak{Db}(X))\tag{B.2.1}
\]
Next, recall that  $\bar\partial$ is elliptic.Indeed, via the   classic Pompieu formula for planar
doimains  every distribution $\mu$ satisfying
the homogeneous equation $\bar\partial(\mu)=0$ is a holomorphic
function.
Since $\mathcal O(X)$ is reduced to constants the
dual space in (B.2.1)  is 1-dimensional and hence
\[
\dim_{{\bf{C}}}\, \frac{\mathcal E^{1,1}(X)}{\bar\partial \mathcal E^{1,0}(X)}=1\tag{B.2.2}
\]
Notice also that Stokes Theorem gives
\[
\int_X\, \bar\partial(\gamma^{1,0})=0\quad\colon\, \gamma^{1,0}\in \mathcal E^{,1,0}(X)
\]
from this we conclude thatif 
$\rho^{1,1}$ is a  2-form for which
$\int_X\,\rho^{1,1}\neq 0$, then
\[
\mathcal E^{1,1}(X)={\bf{C}}\cdot \rho\oplus
\bar\partial(\mathcal E^{1,1}(X))\tag{B.2.3}
\]
\medskip

\noindent{\bf{B.3 A second duality.}}
Theorem A.5 entails that
\[
\bigl[\, \frac{\mathcal E^{0,1}(X)}{\bar\partial \mathcal E(X)}\,\bigr]^*
\simeq \text{Ker}_{\bar\partial}(\mathfrak{c}^{1,0}(X))\tag{B.3.1}
\]
The right hand side is found as follows.
In a chart $(U,z)$
a current of bi-degree
$(1,0)$ is of the form
$\mu\cdot dz$ with
$\mu\in \mathfrak{Db}(U)$.
The $\bar\partial$ image of this current is
zero if and only if $\bar\partial(\mu)=0$ and as we have seen
before this implies that
$\mu$ is a holomorphic density.
Hence the right hand side in (B.3.1) consists of globally defined
\emph{holomorphic} 1-forms. This space is denoted by
$\Omega(X)$ and (B.3.1) can be expressed by
the duality formula
\[
\Omega(X)\simeq\bigl[\, \frac{\mathcal E^{0,1}(X)}{\bar\partial \mathcal E(X)}\,\bigr]^*\tag{B.3.2}
\]
\medskip

\noindent
{\bf{B.3.3 Exercise.}}
Show that (B.3.2) gives the following:
A differential form $\gamma^{0,1}$ on $X$ is $\bar\partial$-exact
if and only if
\[
\int_X\, \omega\wedge \gamma^{0,1}=0\quad\colon\, \forall\,\,
\omega\in \Omega(X)
\]
\medskip

\noindent
{\bf{B.4 Passage to currents.}}
Recall that $\mathcal E^{0,1}(X)\subset\mathfrak{c}^{0,1}$.
in ¤ xx we shall learn that
\[
\mathfrak{c}^{0,1}=\bar\partial(\mathfrak{Db}(X))+
\mathcal E^{0,1}(X)\tag {B.4.1}
\]
Moreover, a $(0.1)$-current $\rho^{0,1}$ is
$\bar\partial$-exact, i.e. of the form
$\bar\partial(\mu)$ for some
distribution $\mu$ on $X$ if and only if
\[
\rho^{1,0}(\omega)=0\quad\colon\quad \omega\in \Omega(X)\tag{B.4.2}
\]
\medskip

\noindent
{\bf{B.5 The case $X={\bf{P}}^1$.}}
Here $\Omega(X)$ is reduced to the zero space.
To see this we suppose that
$\omega$ is a globally defined holomorphic 1-form.
Now ${\bf{P}}^1\setminus \{\infty\}$ is the complex $z$-plane and here
\[
\omega= f(z)\cdot dz
\] 
where $f$ is an entire function.
At the point at infinity we have a local coordinate
$\zeta$ and
\[
\zeta= z^{-1}\quad\colon R<|z|<\infty
\]
hold for every $R>0$.
Since $\omega$ is globally holomorhpic we have
\[
\omega= g(\zeta)\cdot d\zeta
\]
when $0<|\zeta|<R^{-1}$. At the same time the reader can check that
\[
dz=-\zeta^{-2}\cdot d7zeta
\]
holds when $R<|z[<R$. Ths entails that
\[
f(z)=-z^{-2}\cdot g(1/z)\quad\colon |z|>R
\]
From this we see that
the entire function $f$ tends to zero as $|z|\to\infty$
and hence $f$ is identically zero.
So with $X={\bf{P}}^1$ one has $\Omega(X)=0$ and
then (B.4.2) entails that
\[
\mathfrak{c}^{0,1}= \bar\partial(\mathfrak{Db}(X))
\]
In other words, the inhomogeneous $\bar\partial$-equation
is always solvable.
Consider as an example a current
of the form
\[
\gamma=\mu\cdot d\bar z
\]
where $\mu$ is a measure in the complex $z$-plane with compact support.
Now there exists the Cauchy transform
\[
\widehat{\mu}(z)=\int\,\frac{d\mu(\zeta)}{z-\zeta}
\]
It is holomiorphic in
in the open set of the complex $z$-plane where
the compact set
$\text{Supp}(\mu)$ has been removed.
passing to infinity we
notice that
it extends to be holomorphic
because one has the convergent series expansion
\[
\widehat{\mu}(z)=\sum_{n=0}^\infty\,
\int\,\zeta^n|cdot d\mu(\zeta)\cdot z^{-n-1}{z-\zeta}
\]
in an exterior disc
$|z[>R$ where
the support of $\mu$ is contained in
$\{|z|\leq R\}$.
\medskip

\noindent
next, by basuc lebsgue theory one knows that
the funnction $\widehat{\mu}$ is locally integrable
in the whole complex $z$-plane and hence defines a distribution.
Finally, Cacuhy's residue formula shows that
the distribution derivative
\[
\frac{\bar\partial\widehat{\mu}}{\bar\partial\bar z}=\pi \cdot \mu
\]
So we get
\[
\bar\partial(\pi^{-1}\cdot \widehat{\mu})=\mu\cdot d\bar z
\]




















\newpage


\centerline{\bf{C. Some sheaves and their cohomology}}.
\medskip


\noindent
Let $X$ be a compact complex  analytic manifold.
Classic  facts due to Cauchy and Pompieu applied to charts in $X$ 
give  an exact sequence of sheaves
\[
0\to \mathcal O_X\to \mathcal E_X\overset{\bar\partial}\to, \mathcal E_X^{0,1}\to 0\tag{C.0}
\]
Using $C^\infty$-parotions of unity and Leray's theory about  cohomology with
values in sheaves
one gets
\[
H^1(\mathcal O_X)\simeq \frac{
\mathcal E^{0,1}(X)}{\bar\partial(\mathcal E(X)}\tag{C.1}
\]
where the left hand side is the first cohomology groups with
values in the sheaf
$\mathcal O_X$. The reader may also notice that when Leray's long exact sequence for sheaf cohomology is applied to (C.0), then it follows that
\[
H^2(\mathcal O_X)=0\tag{C.2}
\]
Next, we have also the exact sheaf sequence
\[
0\to {\bf{C}}_X\to \mathcal O_X\overset{\partial}\to \Omega_X\to 0\tag{C.3}
\]
Since $H^0({\bf{C}}_X)= H^0(\mathcal O_X)= {\bf{C}}$ and (C.2) holds
one gets the following   exact sequence of complex vector spaces:
\[
0\to \Omega(X)\to H^1({\bf{C}}_X)\to
 H^1(\mathcal O_X)\to H^1(\Omega _X)\to H^2({\bf{C}}_X)\to 0\tag{C.4}
\]
Next, we have
also the following exact sheaf sequence
\[
0\to \Omega_X\to \mathcal E^{1,0}_X\overset{\bar\partial}\to \mathcal E_X^{1,1}\to 0\tag{C.5}
\]
This gives the equality
\[
H^1(\Omega_X)\simeq\frac{\mathcal E^{1,1}(X)}{\bar\partial(\mathcal E^{1,0}(X))}\tag{C.6}
\]
The right hand side rsssembles the quotient in
(B.2.2).
Indeed, we can regard the 7emph{conjugate} analytic structure on
the underlying real manifold of $x$ where the sheaf of holomorphic functions
are compex cojugates of sections in
$\mathcal O_X$. From this the reader may conclude via (B.2.2)
that the rifht hand side in (C.5)
is a 1-dimensional vector space. Hence we have 
\[
\dim_{{\bf{C}}}\,H^1(\Omega_X)=1\tag{C.7}
\]
\medskip

\noindent
Next, recall that
$H^2({\bf{C}}_X)={\bf{C}}$. Together with (C.7) we conclude that
 (C.4) gives the
short exact sequence
\[
0\to \Omega(X)\to H^1({\bf{C}}_X)\to
 H^1(\mathcal O_X)\to 0\tag{C.8}
\]
Topology teaches that
the cohomology space
$H^1({\bf{C}}_X)$Êis finite dimensional.
Hence (C.8) implies that both
$\Omega(X)$ and $H^1(\mathcal O_X)$ are finite dimensional complex vector spaces.
Finally, (B.3.2) and (C.1) give
\[
\Omega(X)\simeq\bigl [\, H^1(\mathcal O_X)\,\bigr]^*\tag{C.9}
\]
In particular the complex vector spaces
$\Omega(X)$ and $H^1(\mathcal O_X)$ have the same dimension.
This equality and (C.8) give
\[
\dim H^1({\bf{C}}_X)= 2\cdot \dim \Omega(X)\tag{C.10}
\]
The equality (C.10) is fundamental  during the study of compact
Riemann surfaces. 
A notable point is that
the cohomology group $H^1({\bf{C}}_X)$ only depends upon the
topological space $X$ and not upon its particular complex structure.

\bigskip

\noindent
{\bf{C.10 A duality for currents.}}
In planar domains it is wellknown that the
inhomogenous $\bar\partial$-equation is locally solvable on distributions.
Since the $\bar\partial$-kernel on $\mathfrak{Db}_X$ is $\mathcal O_X$
one has an exact sequence
\[
0\to \mathcal O_X\to \mathfrak{Db}_X\overset{\bar\partial}\to
\mathfrak{c}^{0,1}_X\to 0
\]
Passing to cohomology and using 
$C^\infty$-partitions of the unity, it follows that
\[
H^1(\mathcal O_X)\simeq \frac{\mathfrak{c}^{0,1}_X}{
\bar\partial(\mathfrak{Db}(X)}\tag{C.10.1}
\]
\medskip

\noindent
{\bf{Exercise.}} Deduce from the above that
\[
\Omega(X)\simeq\bigl[\, \frac{\mathfrak{c}^{0,1}_X}{
\bar\partial(\mathfrak{Db}(X)}\,\bigr]^*\tag{C.10.2}
\]
Conclude that the implication below holds for
each 
$\gamma\in \mathfrak{c}^{0,1}$:
\[
\gamma(\omega)=0\quad\colon\,\forall\,\, \omega\in \Omega(X)
\implies \gamma\in \bar\partial(\mathfrak{Db}(X))\tag{C.10.3}
\]
\medskip

\noindent
{\bf{C.11 A decomposition theorem.}}
Since $X$ in particular is an oriented and compact real manifold
one has
\[
H^1({\bf{C}}_X)\simeq\frac{\text{Ker}_d(\mathcal E^1(X)}{d(\mathcal E(X)}\tag{C.11.1}
\]
Next, on $X$ there also exists
the anti-holomorphic differential forms of bi-degree
$(0,1)$, i.e differential forms  $\gamma\in \mathcal E^{0,1}(X)$ for which
$\partial(\gamma)=0$.
This space is denoted by $\overline{\Omega}(X)$.
Using the conjugate complex analytic structure one has another compact
complex manifold $\overline{X}$
where
$\overline{\Omega}(X)$ is the space of holomorphic 1-forms.
Since $X$ and $\overline{X}$ have the same underlying real manifold, it follows from
(C.10) that
\[
\dim H^1({\bf{C}}_X)= 2\cdot \dim \overline{\Omega}(X)\tag{C.11.2}
\]
Using  this we shall prove
\medskip

\noindent
{\bf{C.11.3 Theorem.}}
\emph{One has a direct sum decomposition}
\[
\text{Ker}_d(\mathcal E^1(X))=
d(\mathcal E(X))\oplus \Omega(X)\oplus\overline{\Omega}(X)
\]
\medskip

\noindent
\emph{Proof}
To begin with we notice that
\[
\Omega(X)\,\cap \overline{\Omega}(X)= \{0\}
\]
Counting dimensions this follows if we prove that
a 1-form $\gamma)\omega+\mu$ cannot be $d$-exact
when $\omega\in \Omega(X)$ and $\mu\in \overline{\Omega}(X)$
where at least one these froms is not identically ero.
For suppose that
$\gamma=dg$ is $d$-exact.
If $\omega$ is not identically zero there exists
the conjugate
form
$\bar\omega\in\overline{\Omega}(X)$.
Now Stokes Theorem gives
\[
0=\int_X\, dg\cdot \bar\omega)=\int_X(\omega+\mu)\wedge\bar\omega=
\int_X(\omega\wedge\bar\omega
\]
Now the reader can check that
the last integral is $\neq 0$ when $\omega$ is not identically zero.
hence $\gamma\in d(\mathcal E(X))$ implies that
$\Omega=0$ and in the same way we find that
$\mu=0$ which proves Theorem C.11.3.








\newpage


\centerline{\bf{D. Existence of meromorphic functions.}}
\bigskip


\noindent
On $X$ there exists the sheaf
$\mathcal M_X$ whose sections are meromorphic  functions.
Subsheaves arise via  constraints on  poles.
In particular, let $p\in X$ be a given point and
$m$ a positive integer.
Denote by $\mathcal O_X[* mp]$
the sheaf whose sections are meromorphic functions on
$X$ which are holomorphic in $X\setminus\{p\}$ and have
poles of order $\leq m$ at $p$.
If $(U,z)$ is a chart where $p$ corresponds to
the origin we seee that
\[
\mathcal O_X[* mp]\,|U= z^{-m}\cdot \mathcal OX|U
\]
Taking Laurent exapnsions
every section in the right hand side is of the form
\[
f+\frac{c_1}{z}+\ldots+\frac{c_m}{z^m}
\]
where $f\in \mathcal O_X$ and $\{c_\nu\}$ is an $m$-tuple of complex numbers.
Expressed by  sheaves it gives
an exact sequence
\[
0\to \mathcal O_X\to \mathcal O_X[*mp]\to S_p^m\to 0\tag{D.1}
\]
where $S_p$ is the scyscraper sheaf suppotet  by $\{p\}$
and
the stalk $S_p(p)$ is an $m$-dimensional vector space.
Passing to long exact sequence of cohomology the reader 
can verify that there is an exact sequence:
\[
0\to {\bf{C}}\to H^0(\mathcal O_X[*mp])\to
{\bf{C}}^m\to 
H^1(\mathcal O_X)\to H^0(\mathcal O_X[*mp])\to 0\tag{D.1.1}
\]
\medskip

\noindent
{\bf{D.2 Exercise.}}
Use that the vector space 
$H^1(\mathcal O_X)$ is $g$-dimensional and conclude that
\[
\dim_{{\bf{C}}}\, 
H^0(\mathcal O_X[*mp])=m-g+1+
\dim_{{\bf{C}}}\, 
H^1(\mathcal O_X[*mp])\geq m-g+1\tag{D.2.1}
\]
\medskip

\noindent
In particular the left hand side is $\geq 2$ if $m=g+1$
which means that
apart from constants, there exists at least one
constant global section in 
$\mathcal O_X[*(g+1)p]$.
Hence we have proved:

\bigskip

\noindent
{\bf{D.3 Theorem.}}
\emph{For every $p\in X$ there exists a non-constant 
meromorphic function $f$  in $X$ with no poles in
$X\setminus{p}$ while
the order of the pole at $p$ is at most $g+1$.}











\newpage



\centerline{\bf{Weierstrass' points.}}

\bigskip

\noindent
Let $X$ be a compact Riemann surface
whose genus number $g$ is $\geq 2$.
Removing  a point $p\in X$
we get  the space
$\mathcal O(X\setminus\{p\})$.
If $(U,z)$ is a chart centered at $p$
where $p$ corresponds to $z=0$, then every
$f\in\mathcal O(X\setminus\{p\})$
restricts to a holomorphic function in
the punctured disc
$0<|z|<1$
and we can regard its Laurent series:
\[
f(z)=
\sum_{\nu=1}^\infty\ c_\nu\cdot z^{-\nu}+\sum_{\nu\geq 0}\, d_\nu\cdot z^\nu
\]
The negative part of the Laurent series is denoted by $f_*(z)$.
If $f_*=0$ then $f$ is globally holomorphic and hence reduced to
a constant.
So 
\[
f\mapsto f_*(z)+ d_0
\]
yields an  injective 
map from $\mathcal O(X\setminus\{p\})$ 
into the space of
non-positive Laurent series at $z=0$.
We are going to study the range of this map.
Denote by $\mathcal L$
the space 
of all non-positive Laurent series, where we recall that a negative
series
\[
\sum_{\nu=1}^\infty\ c_\nu\cdot z^{-\nu}\in\mathcal L
\]
if and only if
\[
\sum_{\nu=1}^\infty\, |c_\nu|\cdot R^\nu<\infty
\] 
for all $R>0$.
In particular $\mathcal L$ contains the $g$-dimensional subspace
formed by Laurent series given by
finite series:
\[
\rho(z)= c_1z^{-1}+\ldots+c_g\cdot z^{-g}
\]
where $\{c_\nu\}$ is a $p$-tuple of complex numbers.
Let $\mathcal L[p]$ denote this subspace of
$\mathcal L$.
\medskip

\noindent
{\bf{E.1 Theorem.}}
\emph{Outside a finite set ${\bf{W}}$ in $X$
one has} 
\[ 
\mathcal L=\mathcal L[p]\oplus \mathfrak{Im}(\mathcal O(X\setminus\{p\})
\]
\medskip

\noindent
{\bf{E.2 Remark.}}
In ¤xx we show that
the exceptional set
${\bf{W}}$ is non-empty when $g\geq 2$,
If (*) holds above
it follows that when $m>g$
then  there exists a unique $g$-tuple $\{c_\nu\}$ such that 
\[ 
z^{-m}=c_1z^{-1}+\dots+c_gz^{-g}+ \mathfrak{Im}(\phi)
\]
where $\phi$ is holomorphic in
$X\setminus\{p\}$.
Herte the negative Laurent series of $\phi$ is finite
at $p$ which implies that
$\phi$ is a globally defined meromorphic function
with a pole of order $m$ at $p$ whose negative Laurent expnasion at $p$
is of the form
\[
z^{-m}+c_1z^{-1}+\dots+c_gz^{-g}
\]
where the $g$-tuple $\{c_\nu\}$ is uniquely determined and depends on
the chosen integer $m$.
At the same time
the direct dum in (*) entails that
there do not exist non-constant meromorphic functions
which are holomorphic in
$X\setminus\{p\}$ while the order of
the pole at $p$ is $\leq g$.
\medskip

\noindent
The proof of Theorem E.1 requires several steps.
We are given a point
$p\in X$ and let $(U,z)$ be a chart
around $p$ where $p$ corresponds to $z=0$.
Residue calculus gives
a $g$-tuple of 
currents defined by
\[
\rho_\nu=\bar\partial(z^{-\nu})\quad\colon\quad \nu=1,\ldots,g
\]
Each current is supported by the singleton set $\{p\}$
and extends to a current on $X$ supported by $p$.
If $\Psi^{1,0}\in\mathcal E^{1,0}(X)$
we can regard its restriction to $U$ and write
\[
\Psi^{1,0}|U= \psi(z)\cdot dz
\]
with $\psi\in C^\infty(U)$.
Residue calcluus teaches that
\[
\rho_1(\Psi^{1,0})= 2\pi i\cdot \psi(0)
\]
If $\nu\geq 2$ the reader may verify that
\[
\rho_\nu(\Psi^{1,0})= \frac{(-1)^{\nu-1}}{(\nu-1)!}\cdot
\partial^{\nu-1}\psi/\partial z^{\nu-1}(0)
\]
The construction of the $\rho$-currents
is not intrinsic, i.e.
the $g$-tuple  depends on the chosen chart around $p$.
But the reader can check that
the $g$-dimenbsional vector space
in $\mathfrak{c}^{0,1}(X)$
generated by
$\{\rho^\nu\,\colon 1\leq \nu\leq g\}$
does not depend on the chosen chart around $p$.
Let us denote it by $\mathcal W(p)$.
The major step towards the proof of Theorem E.1
is the following:


\medskip

\noindent
{\bf{E.3 Theorem.}} \emph{Outside a finite set
${\bf{W}}$  in $X$ one has
the direct sum decomposition}
\[
\mathfrak{c}^{0,1}(X)=\bar\partial(\mathfrak{Db}(X))\oplus\, \mathcal W(p)\tag{E.3.1}
\]
\bigskip

\noindent
\emph{Proof.}
The duality result in ¤ xx gives (E.3.1)
if
the $g$-tuple
$\{\rho^\nu\}$ restrict to 
${\bf{C}}$-linearly independent in the dual space
$\Omega(X)^*$.
To check when this holds we
consider a basis $\omega_1,\ldots,\omega_g$ in the $g$-dimensional vector space
$\Omega(X)$.
In a chart
$(U,z)$ centered at a point $p_0\in X $ we can write
\[
\omega_j= f_j(z)\cdot dz\tag{i}
\]
where Ê$\{f_j\}$ are ${\bf{C}}$-linearly 
independent in $\mathcal O(U)$.
The general result in ¤ xx  entails that 
the determinant function
\[
\mathcal F(z)= \det\bigl(\partial f_j^\nu/\partial z^\nu(z)\tag{ii}
\]
formed by the $g\times g$-matrix with
elements as above is not identically zero.
Now linear algebra shows that
$\{\rho_\nu\}$ restrict to linearly independent functionals
on $\Omega(X)$ at every $z|in U$ for ehich
$F(z)\neq 0$.
Since the zero set of $F$ in the chart $U$ is discrete
and we can cover
$X$ by a finite famliy of charts, it follows that
(E.3.1) holds outside a finite set
${\bf{W}}$.


\medskip

\noindent
{\bf{E.4 How to find ${\bf{W}}$.}}
In each  chart $(U,z)$ as above we have
the $\mathcal F$-functions from (ii).
If $(U_\alpha,z_\alpha)$ and $(U_\beta,z_\beta)$ is a pair of charts
in $X$ where $U_\alpha\cap U_\beta\neq\emptyset$
we get two $g$-tuples  of analytic functions by
\[
\omega_j|U_\alpha= f_j^\alpha\cdot dz\quad\colon\quad
\omega_j|U_\beta= f_j^\beta\cdot dz_\beta
\]
When $z_\beta=z_\beta(z_\alpha)$ is regarded as
an analytic function in $U_\alpha\cap U_\beta$ one has the equations
\[
f_j^\alpha=\frac{\partial z_\beta}{\partial z_\alpha}\cdot f_j^\beta\tag{E.4.1}
\]
for each $j$ in $U_\alpha\cap U\beta$.
\medskip

\noindent
{\bf{E.4.2 Exercise.}} Show by using
rules for calcuating determinsnts that
(E.4.1) gives
the equation
\[
\mathcal F_\alpha=\bigl(\frac{\partial z_\beta}{\partial z_\alpha}\bigr)^{g(g-1)/2}\cdot F_\beta(z)
\]
So with $N=g(g-1)/2$
the family $\{\mathcal F_\alpha\}$ which arises when
$X$ is covered by a finite number of charts, is a global section of
the $N$-fold product of the holomorphic line bundle $\Omega_X$.
By (xx) the
set of xeros counted with multiplicities  of every global section
in $\Omega_X$ is equal to $2(g-1)$.
So by the general result in ¤ xxx the
zero set of the $\mathcal F$-family counted with multiplicities is equal to
$g(g-1)^2$. Since $g\geq 2$ this is a positive integer and hence
the set ${\bf{W}}$ is non-empty.
\bigskip

\noindent
{\bf{Remark.}} In the literature one refers to
${\bf{W}}$ as the set of Weierstrass' points in $X$.
The determination of ${\bf{W}}$ for a given $X$ with genus $\geq 2$
is in general not easy.
From the above ${\bf{W}}$ contains at most
$(g-1)^2\cdot g$ many distinct points. 
In general the number of points can be
strictly smaller.
Weierstrass investigated
${\bf{W}}$ for special families of compact Riemann surfaces.
See ¤ xx for some comments.
\bigskip

\centerline {\bf{Proof of Theorem E.1}}

\bigskip

\noindent
Consider a point $p\in X$ which is outside ${\bf{W}}$ and let $(U,z)$ be a chart 
centered at $p$.
Let $U^*=U\setminus\{p\}$ be the punctured open disc.
In $X$ we also have the open set
$X\setminus\{p\}$
which can be regarded as an open Riemann surface.
The theorem by Behnke and Stein from
the chapter devoted to open Rieann surfaces
gives
$H^1(X\setminus\{p\},\mathcal O)=0$.
The cohomology in the  disc $U$ is also zero.
Hence the open covering of $X$ given by the pair
$\mathfrak{U}= (U,X\setminus\{p\})$
is acyclic with respect to the sheaf
$\mathcal O_X$. So  Leray's acyclicity theorem gives
\[
H^1(X,\mathcal O_X)\simeq \frac{\mathcal O( U^*)}{
\delta(C^0(\mathfrak{U},\mathcal O_X))}\tag{i}
\]
where
\[
\delta\colon \mathcal O(U)\oplus \mathcal O(X\setminus\{p\})\to
\mathcal O(U^*)
\] 
is the Cech coboundary map.
Next, the $g$-tuple $\{z^{-\nu}\colon \nu=1,\ldots,g\}$
are holomorphic in $U^*$
and  their images in the right hand side from (i) give
elements in
$H^1(X,\mathcal O_X)$ denoted by
$\{[z^{-\nu}]\}$.
\medskip

\noindent
{\bf{Exercise.}}
Recall  that
\[
H^1(X.\mathcal OX)= \frac{\mathfrak{c}^{0,1}}{\bar\partial(\mathfrak{Db}(X)}
\]
Since $p$ is outside ${\bf{W}}$
the last quotient is equal to $\mathcal W(p)$.
Conclude from this that
the $g$-tuple
$\{[z^{-\nu}]\}$ is a basis in the $g$-dimensional vector space
$H^1(X,\mathcal O_X)$.
\medskip

\noindent
Let us then consider some
$g\in\mathcal O(U^*)$ which has a  Laurent series
\[
g(z)= \sum_{\nu=1}^\infty\ c_\nu\cdot z^{-\nu}+
\sum_{\nu=0}^\infty\ d_\nu\cdot z^{\nu}
\]
By the Exercise  there exists
a unique $g$-tuple of complex numbers
$a_1,\ldots,a_p$
such that
the image of $g$ in
$H^1(X,\mathcal O_X)$ is equal to $\sum\, a_\nu\cdot [z^{-\nu}]$.
Hence (i) gives a pair $\phi(z)\in\mathcal O(U)$ and $f(z)\in \mathcal O(X\setminus\{p\}$
such that
\[
g(z)-\sum\,\rho_\nu\cdot z^{-\nu}=\phi(z)+f(z)
\]
where $\phi(z)\in\mathcal O(U)$ and $f(z)\in \mathcal O(X\setminus\{p\}$.
Regarding the negative Laurent series it follows that
\[
g_*(z)= \sum\, a_\nu\cdot z^{-\nu}+f_*(z)\tag{ii}
\]
Here $g$ was arbitrary in
$\mathcal O(U^*)$ and hence the proof of Theorem E.1 is finished.
















\newpage










 
 
 
 

\centerline{\bf{F. Abel's theorem.}}



\bigskip


\noindent
A divisor $D$ on $X$ consists of
an assignement of integers $\{\mu_\nu\}$ to a finite set of points $\{p_\nu\}$
in $X$. One writes
\[
D= \sum\, \mu_\nu\cdot \delta(p_\nu)
\]
The $\mu$-integers may be positive or negative.
The degree is defined by
\[
\deg D= \sum\,\mu_\nu
\] 
while the finite set $\{p_\nu\}$ is called the support of $D$.
Next we construct a class of 1-currents.
In general, let $\gamma\colon [0,1]\to X$
be an $X$valued function on the closed unit interval
We assume that $\gamma$ is continuous and has a
finite total variation. The last condition means that
there exists a constant $C$ such that
\[
\sum_{\nu=0}^{\nu=N-1}\, d(\gamma(t_{\nu+1},\gamma(t_\nu)\leq C
\]
for all sequences $0=t_0<t-1<\ldots<t_N=1$
Here $d$ is some  distance function 
on $X$ regarded as a metric space which in charts
is equivsoent to
the euclidian distance.
Every such $\gamma$ gives a current of degree one
acting on $\mathcal E^1(X)$ by 
\[
\alpha\mapsto \int_\gamma \,\alpha\tag{*}
\]
\medskip

\noindent
{\bf{Exercise.}} Explain how the classical Borel-Stieltjes integrals for functions
with bounded variation
defines the integral in the right hand side.
Show also that
\[
\int_\gamma\, dg= g(\gamma(1))-g(\gamma(0))
\]
hold for every $g\in\mathcal E()$.
One refers to (*) as an integration current of degree one.
More generally we can take a finite sum of such
currents and get the integration current
$\Gamma$ defined by
\[
\Gamma(\alpha)= \sum\, \int_{\gamma_j}\,\alpha
\]
Let $D=\sum\,\mu_\nu\cdot \delta(p_\nu)$ be a divisor of
degreee zero.
An integration current $\Gamma$ is said to be associated with
$D$ if the equality below hold for every
$g\in\mathcal E(X)$:
\[
\Gamma(dg)= \sum\, \mu_\nu\cdot g(p_\nu)
\]
\medskip

\noindent
{\bf{F.1 Principal divisors.}}
Let $f$ be a non-constant meromorphic function.
Now we have the finite set of poles $\{p_\nu\}$ and the finite set of zeros
$\{q_j\}$.
We associate the divisor
\[
\text{div}(f)= \sum\, \mu_k\cdot \delta(p_k)-\sum\, \mu_j\cdot \delta(q_j)
\]
Here $\mu_k$ is the order of the pole of $f$ at every $p_\nu$, while
$\mu_j$ is the order of a zero at $q_j$.
By the result in ¤ xx this divisor has degree zero.
A divisor $D$ of degree zero is called principal if
it is equal to $\text{div}(f)$ for some
$f\in\mathcal M(X)$.
Notice that if $f$ and $g$ is a pair of non-constant meromorphic functions such that
$\text{div}(f)= \text{div}(g)$, then
$f/g$ is a holomorphic function on $X$ and hence reduced to a non-zero constant.
Introducing the multiplicative group
$\mathcal M(X)^*$ of non-constant meromorphic functions
this means that one has an injective map
\[
\frac{\mathcal M(X)^*}{{\bf{C}}^*}\to\mathcal D_0
\]
where $\mathcal D_0$ is the additive group of divisors whose degree are zero.
The  theorem below describes the range of this map.

\medskip

\noindent
{\bf{F.2 Theorem.}}
\emph{A divisor $D$ of degree zero
is principal if and only if there
exists an integration current $\Gamma$ associated with
$D$  such that}
\[
\Gamma(\omega)=0\quad\colon \,\,\gamma\in \Omega(X)
\]
\medskip

\noindent
The proof requires several steps.
First we shall show the "if part", i.e. if 
$\Gamma$ exists so that (*) holds then
the divisor $D$ is principal.
To achieve this we first
perform a local construction in the complex plane.
\medskip

\noindent
{\bf{F.3 A class of currents in ${\bf{C}}$.}}
In the complex $z$-plane we consider
a point $z_0$ where 
\[
0<|z_0|<r<1
\]
holds for some $0<r<1$.
It is easily seen that there exists
a $C^\infty$-function $a(z)$  in ${\bf{C}}$
which never is zero and the function
\[
\phi(z)= \frac{z}{z-z_0}\cdot a(z)
\]
is identically one when
$|z|\geq r$.
Now $z\mapsto \frac{1}{z-z_0}$ is locally integrable around
$z_0$ and hence $\phi$ belongs to 
$L^1_{\text{loc}} ({\bf{C}})$ and is therefore a distribution.
\medskip

\noindent
Cauchy's residue formula can be expressed by saying
the $\bar\partial$-image of the $\frac{1}{z}$
is equal to the $(0,1)$-current
$2\pi i\cdot \delta(0)d\bar z$ where $\delta(0)$ is the Diraqc distribution
at the origin.
Using this the reader can check that
\[
\bar\partial(\phi)=
 \frac{z}{z-z_0}\cdot \bar\partial(a)+z_0a(z_0)\cdot \delta(z_0)d\bar z\tag{i}
 \]
 from (i) the reader should also check that
 \[
 \phi^{-1}\cdot \bar\partial(\phi)= a^{-1}\cdot \bar\partial(a)\tag{ii}
 \]
 \medskip
 
 \noindent
 {\bf{F.4 The current $\phi^{-1}\cdot \partial(\phi)$.}}
 To begin we one has
 \[
 \partial(\phi)=\frac{a(z)}{z-z_0}\cdot dz-
 \frac{za}{(z-z_0)^2)}\cdot dz+\frac{z}{z-z_0}\cdot \partial a\tag{F.4.1}
 \]
 Above $(z-z_0)^{-2}$ is the principal value distribution
 defined as in ¤ xx.
 \medskip
 
 \noindent
 {\bf{ Exercise.}}
 Use (F.4.1) to establish the equation
 \[
 \phi^{-1}\cdot \partial(\phi)=z^{-1}\cdot dz-(z-z_0)^{-1}\cdot dz+
 a^{-1}\cdot \partial(a)\tag{F.4.2}
 \]
 \medskip
 
 \noindent
 {\bf{Exercise.}}
 Use Stokes Theorenm and Cauchy's residue fornula to
 prove that when the 1-current
 \[
 \phi^{-1}\cdot d\phi=  \phi^{-1}\cdot \partial(\phi)+ \phi^{-1}\cdot \bar \partial(\phi)
 \] 
 is applied to $dg$ for some
 $g\in C_0^\infty({\bf{C}}$, then
 \[
 \phi^{-1}\cdot d\phi<dg>\, = 2\pi i\cdot (g(0)-g(z_0)\tag{F.4.3}
 \]
\medskip


\noindent
 Let us now consider an integration current
 $\Gamma$ given by a finite sum
 $\sum\,\gamma_j$ where each $\gamma_j$ has compact support in
 a chart
 $(U_j,z_j)$ in $X$ and the end-points of
 $\gamma_j$ are $z_j=0$ and $z_j=z_j^*$
 with $0<|z_j^*|<r<1$ and $U_j$ is a chart defined by
 $\{|z_j|<1|]$.
In $X$ the point $z_j=0$ is denoted by $q_j$ while $z_j^*$ corresponds to a
point $p_j$.
It follows that 
 \[
 \int_\Gamma \, dg=\sum_{j=1}^{j=N}\, g(p_j)-g(q_j)\tag{F.5}
 \]
for every $g\in \mathcal E(X)$.
 Next, for each $j$ we apply the local contruction the chart
 and find a function
 $\phi_j$ in $X$ which is identically one
 in $X\setminus \{|z_j|\leq r\}$ such that 
 \[
 \phi_j^{-1}\cdot d\phi_j<dg>=2\pi i\cdot \int_{\gamma_j}\, dg\quad\colon\, g\in \mathcal E(X)
 \]
 More generally, since
 $d$-closed 1-forms in the chart $U_j$ are $d$-exact the re4ader should check that
 (F.5) implies that
 \[
 \phi_j^{-1}\cdot d\phi_j<\alpha>=2\pi i\cdot \int_{\gamma_j}\,\alpha\tag{F.6}
 \]
 hold for every $d$-closed differential 1-form $\alpha$.
 Let us now consider the function
 \[
 \Phi= \prod_{j=1}^{j=N}\, \phi_j
 \]
 \medskip
 
 \noindent
 {\bf{F.7 Exercise.}}
 From the above the
 reader should check  that
 the construction of the $\phi$-functions imply that
 $\Phi$ is a zero-free
 $C^\infty$-function
 in $X\setminus \{q_j,p_j\}$, i.e. in the open complement of
 the finite set
  which is the union of these   $q$  and  $p$ points.
Moreover,  additivity for logarithmic derivatives and 
(F.6) above gives
\[
\Phi^{-1}\cdot d\Phi<\alpha>=
\int_\Gamma\, \alpha\tag{F.7.1}
\]
for every $d$-closed 1-form
$\alpha$. Finally, show that
\[
\Phi^{-1}\cdot \bar\partial(\Phi)=
\sum\, a_j^{-1}\cdot \bar\partial(a_j)\tag{F.7.2}
\]
where the right hand side is a smooth $(0,1)$-form.
\medskip

\noindent
{\bf{F.8 A special case.}}
Suppose that $\Gamma$ is such that
\[
\int_\Gamma\, \omega=0\quad\colon\quad \omega\in\Omega(X)\tag{F.8.1}
\]
The equality in (F.7.1) applied to  $d$-closed holomorphic 1-forms
and
Theorem ¤ xx  entail  that
the smooth $(0,1)$-form
$\Phi^{-1}\cdot \bar\partial(\Phi)$ from (F.7.2) is $\bar\partial$-exact.
Thus, we can find $G\in \mathcal E(X)$ such that
\[
\bar\partial(G)= \Phi^{-1}\cdot \bar\partial(\Phi)\tag{F.8.2}
\]
\medskip


\noindent
{\bf{Exercise.}}
Put
\[
\Psi=e^{-G}\cdot \Phi
\]
deduce from the above  that
$\bar\partial(\Psi)=0$ holds in
$X\setminus \{q_j,p_j\}$ and hence $\Psi$ is holomorphic in
this open subset of $X$
Show also  that the local constructions of the
$\phi$-functions inside the charts
$\{U_jz_j\}$ entail  that
$\psi$ extends to a mermorphic function in
$X$ whose princial divisor is equal to
\[
\sum\, \delta(q_j)-\sum \delta(p_j)
\]
Funally the reader should confirm that the constructions above
prove the "if part" in Theorem F.2.
\medskip


\centerline{\emph{F.9 Proof of the "only if part"}}
\medskip

\noindent 
Here we are given a non-constant meromorphic funvtion
$f$.
We shall condtruct an integration chain $\Gamma$ as follows:
Frst $f\colon X\to {\bf{P}}^1$ is a holomorphic map.
With $s=f(x)$
we recall from (xx) that the number critical $s$-points in
the complex $s$-plane is finite.
In ${bf[P})^1$ we choose a simple
curve $\gamma_*$ with intial point at $s=0$ and end-point at
$s=|nfty$, while
$\gamma_*$ avoids the critical points $s\neq 0$ in
${\bf{C}}$.
of course, while this is done we can choose
$\gamma_*$ so that it is a smooth curve
on the $C^\infty$-manifold ${\bf{P}}^1$.
\medskip

\noindent
{\bf{The inverse image $f^{-1}(\gamma_*)$.}}
Let $N=\deg(f)$.
Since $\gamma_*$ avoids $f$-cirtical points we see that
\[
f^{-1}(\gamma_*\setminus \{0,\infty\})= \gamma_1\cup\ldots\cup\,\gamma_N
\]
where $\{\gamma_j\}$ are disjoint  curves in
$X$, each of which is oriented via
$\gamma_*$ which from the start moves from
$s=0$ to $s=\infty$.
\medskip

\noindent
{\bf{Exercise.}}
Show that the closure $\bar\gamma_j$ yields a rectifiable  curve
whose initial point is zero of $f$ and the end-point a pole.
Put
\[
\Gamma=\sum\, \bar\gamma_j
\]
and conclude from the above that
$\Gamma$ is associated to the principal divisor of $f$.
The proof of the "onmy if part" is therefore finished if we show that
\[
\int_\Gamma\,\omega=0\quad\colon\quad \omega\in \Omega(X)\tag{*}
\]
To prove (*) we shall  use
a certain trace map.
First, a holomorphic 1-form
$\omega$ on $X$ is regared as a $\bar\partial$-closed current with
bi-degree $(0,1)$.
Since the amp $f\colon X\to {\bf{P}}^1$ is proper
there exists the direct image current
$f_*(\Omega$ and we recal from general facts that
the passage to direct image currents commute with
the $\bar\partial$-operator.
hence $\bar\partial(f_*(\Omega))==$ and since
$\bar\partial$ is elliptic it follows that
$f_*(\omega)$ is a holomorphic 1-form on
${\bf{P}}^1$.
By the result in Exercise xx there does not exist non-zero globally defined
holomorphic 1-forms on the projective line.
hence
\[ 
f_*(\omega)=0\tag{**}
\]
In partocuar we have
\[
\int_{\gamma_*(\epsilon)}\, f_*(\omega)=0
\]
where $\gamma_*(\epsilon)$ is the closed 
curve given by $\gamma$ intersected with
$\{\epsilon\leq |s| \leq \epsilon^{-1}\}$
for a small $\epsilon>0$.
\medskip

\noindent
{\bf{Exercise.}}
Put $\Gamma(\epsilon)= f^{-1}(\gamma(\epsilon)$
and dediuce from (xx) that
\[
\int_{\Gamma(\epsilon)}\, \omega=0
\]
Finally, pass to the limit as $\epsilon\to 0$ and conclude that (*) holds which finishes the proof of
the "only if part".



 
 
 
 \newpage
 
 \centerline{\bf{G. Holomorphic line bundles.}}
 
 
\bigskip

\noindent
There exists the multiplicative sheaf
$\mathcal O_X^*$ whose sections are zero-free
holomorphic functions.
every such function is locally $e^g$ with $g\in \mathcal O_X$
where $g$ is determined up to an integer multiple of $2\pi i$.
This gives an exact sheaf sequence
\[
0\to {\bf{Z}}_X\to \mathcal O_X\overset{\exp}\to \mathcal O^*_X\to 0
\]
where $\exp$ sends $g$ to $e^{2\pi i g}$
and ${\bf{Z}}_X$ is the sheaf of locally constant  integer-valued functions on
$X$.
Notice that global sections in
$\mathcal O_X^*$ are reduced to non-zero complex numbers
and we have the short exact sequence
\[
0\to {\bf{Z}}\to {\bf{C}}\overset{\exp}\to {\bf{C}}^*\to 0
\]
Conclude that one has an exact sequence
\[
0\to H^1({\bf{Z}}_X)\to H^1(\mathcal O_X)\to
H^1(\mathcal O_X^*)\to H^2({\bf{Z}}_X)\to 0\tag{G.1}
\]
As explained in ¤ xx
the cohomology group $H^1({\bf{Z}}_X)$
is a free abelian group of rank $2g$
while
$H^2({\bf{Z}}_X)={\bf{Z}}$.























 
 

 
 
 
 
 
 
 
 





\end{document}





















