\documentclass[12pt]{amsart}


\usepackage[applemac]{inputenc}



\addtolength{\hoffset}{-12mm}
\addtolength{\textwidth}{22 mm}
\addtolength{\voffset}{-10mm}
\addtolength{\textheight}{20mm}

\def\uuu{_}

\def\vvv{-}

\begin{document}

\centerline{\bf\large{Analytic function theory in one complex variable}}


\bigskip

\[ 
\text{By Jan\vvv Erik Björk}
\]

\bigskip

\[ 
\text{Department of Mathematics Stockholm University}
\]



\bigskip



\centerline{\emph{Contents}}




\bigskip

\noindent
{\bf{Chapter I:}}
\medskip

\noindent
\emph{Part A:  Complex numbers}

\medskip 

\noindent
\emph{Part B:  Series}



\medskip


\noindent
\emph{Part C:  Linear algebra}
\medskip


\noindent
\emph{Part D:  Zeros of polynomials}
\medskip


\noindent
\emph{Part E:  Fourier series}





\medskip 

\noindent{\bf{Chapter II}}
\medskip 

\noindent
\emph{Stokes Theorem and Line integrals}

\bigskip


\noindent{\bf{Chapter III.}}

\medskip

\noindent
\emph{Analytic functions}
 \bigskip

 


\noindent
{\bf{Chapter IV. }}
\medskip

\noindent
\emph{Multi-valued functions}
\bigskip

\noindent
{\bf{Chapter V. }}

\medskip

\noindent
\emph{A. Harmonic functions}
\medskip

\noindent
\emph{B. Subharmonic functions}


\bigskip

\noindent
{\bf{Chapter VI. }}
\medskip

\noindent
\emph{Conformal mappings}

\bigskip

\noindent
{\bf{Chapter VII. }}
\medskip

\noindent
\emph{Residue calculus}

\bigskip

\noindent
{\bf{Chapter VIII. }}
\medskip


\noindent
\emph{The $\Gamma$\vvv function and Riemann's $\zeta$\vvv function}

\bigskip

\noindent
{\bf{Appendix.}}
\medskip

\noindent
\emph{1: Measure theory}
\medskip

\noindent
\emph{2: Distributions and boundary values of analytic functions}
\medskip

\noindent
\emph{3: Functional analysis}

\newpage


\centerline{\emph{List of detailed contents}}

\bigskip


\centerline{\bf{I:A Complex numbers}}

\bigskip


\noindent
0. Introduction
\medskip

\noindent
1.A: Basic facts.
\medskip

\noindent
1.B: The fundamental theorem of algebra
\medskip

\noindent
1:C. Interpolation by polynomials

\medskip

\noindent
1:D Tchebysheff polynomials and transfinite diameters.
\medskip

\noindent
1:E Exercises
\medskip

\noindent
2. Möbius functions


\medskip

\noindent
3. The Laplace operator
\medskip

\noindent
4. Some complex mappings
\medskip

\noindent
5. The stereographic projection

\bigskip

\centerline{\bf\ Chapter I:B. Series}
\bigskip



\noindent
0. Introduction
\medskip

\noindent
1. Additive series
\medskip

\noindent
1:B Counting functions

\medskip

\noindent
2. Power series


\medskip



\noindent
2:B Radial limits
\medskip

\noindent
2:C A theorem by Landau

\medskip


\noindent
3. Product series
\medskip

\noindent
4. Blascke products
\medskip

\noindent
5. Estimates using the counting function
\medskip

\noindent
6. Convergence on the boundary
\medskip

\noindent
7. An example by Hardy
\medskip

\noindent
8. Convergence under substitution
\medskip

\noindent
9. The series $\sum\, (a_1\cdots a_\nu)^{\frac{1}{\nu}}$
\medskip

\noindent
10. Thorin's convexity theorem.


\medskip

\noindent
11. Cesaro and Hölder limits
\medskip

\noindent
12. Power series and arithmetic means
\medskip

\noindent
13. Taylor series and quasi\vvv analytic functions

\newpage


\centerline {\bf I:C  Complex vector spaces}

\bigskip




\noindent
0. Introduction
\medskip

\noindent
1. Wedderburn's Theorem
\medskip

\noindent
2. Resolvent marices


\medskip

\noindent
3. Jordan's theorem
\medskip

\noindent
4. Hermitian and normal operators
\medskip

\noindent
5. Fundamental solutions to ODE-equations

\medskip

\noindent
6. Carleman's  inequality for resolvents

\medskip

\noindent
7. Examples and exercises.


\bigskip

\centerline{\bf {I:D On zeros of polynomials}}
\bigskip




\noindent
A: Preliminary results
\medskip

\noindent
B: The Laguerre operators $A_\zeta^n$


\medskip

\noindent
C: Properties of Laguerre forms
\medskip

\noindent
D: Proof of Theorem 0.1
\medskip

\noindent
E: Proof of Theorem 0.2 and 0.1




\medskip

\noindent
F: Legendre polynomials


\bigskip



\centerline{\bf {I:E. Fourier series}}
\bigskip



\noindent
\emph{A: The Fejer kernel}

\medskip


\noindent
\emph{B: Legendre polynomials}



\medskip


\noindent
\emph{C. The space $\mathcal T_n$}


\medskip


\noindent
\emph{D. Tchebysheff  polynomials and transfinite diameters}
\medskip


\noindent
\emph{E. Fejer sums and Gibbs phenomenon}

\medskip


\noindent
\emph{F. Partial Fourier sums and convergence in the mean}


\bigskip

\centerline{\bf{II. Line integrals and Stokes theorem.}}


\medskip













\noindent
0. Introduction
\medskip

\noindent
0: A. Calculus in ${\bf{R}}^2$.

\medskip


\noindent
1. Some physical explanations

\medskip


\noindent
2. Stokes Theorem in ${\bf{R^2}}$
\medskip


\noindent
3. Line integrals via differentials
\medskip


\noindent
4. Green's formula and the Dirichlet problem
\medskip


\noindent
5. Exact versus closed 1-forms

\medskip
\noindent
6. An integral formula for the Laplace operator



\newpage



\centerline{\bf Chapter III. Complex analytic functions}

\bigskip


\noindent
0. Introduction
\medskip


\noindent
1. Complex line integrals
\medskip

\noindent
2. The Cauchy-Riemann equations
\medskip

\noindent
3. The $\bar\partial$-operator
\medskip


\noindent
4. The complex derivative
\medskip

\noindent
5. Theorems by Morera and Goursat
\medskip





\noindent
6. Cauchy's Formula
\medskip

\noindent
7. Complex differentials 
\medskip

\noindent
8. The Pompieu formula
\medskip


\noindent
9. Normal families
\medskip

\noindent
10. Laurent series
\medskip

\noindent
11. An area formula
\medskip



\noindent
12. A theorem by Jentsch
\medskip

\noindent
13. An inequality by Siegel 
\medskip

\noindent
14. Zeros of product series.

\bigskip



\centerline{\bf  Chapter 4: Multi-valued analytic functions}

\bigskip

\noindent
0. Introduction
\medskip

\noindent
1. Angular variation and Winding numbers
\medskip

\noindent
2. The argument principle
\medskip

\noindent
3. Multi-valued functions

\medskip


\noindent
4. The monodromy theorem
\medskip

\noindent
5. Homotopy and Covering spaces
\medskip

\noindent
6. The uniformisation theorem
\medskip


\noindent
7. The $\mathfrak{p}^*$-function


\medskip


\noindent
9. Reflections across a boundary


\medskip

\noindent
10. The elliptic modular function
\medskip


\noindent 
11. Work by Henri Poincaré



\newpage

\centerline{\bf Chapter 5.A Harmonic functions}


\bigskip


\noindent 
1. The Dirichlet problem
\medskip

\noindent 
2. The Harmonic Conjugate.
\medskip

\noindent 
3. Harmonic functions in a disc
\medskip

\noindent 
4. The mean value property
\medskip


\noindent 
5. The harmonic measure
\medskip

\noindent 
6. The Green's function


\medskip

\noindent 
7. The Neumann problem 


\medskip

\noindent 
8. Example from Hydro mechanics



\medskip

\noindent 
9. A result on harmonic majorisation

\medskip

\noindent 
10. On harmonic measure functions
\medskip

\noindent 
11. Some estimates for  harmonic  functions
\medskip

\noindent 
12.  A density result for harmonic functions

\bigskip

\centerline{\bf Chapter 5.B. Subharmonic functions }

\bigskip



\noindent 
1. The subharmonic Log-function
\medskip


\noindent 
2. Basic facts about subharmonic functions
\medskip

\noindent 
3. Riesz representation formula
\medskip

\noindent 
4. Perron families

\medskip

\noindent
5. Piecewise harmonic subharmonic functions

\medskip

\noindent
6. On zero sets of subharmonic functions.

\bigskip

\centerline{\bf{Chapter 6. Conformal mappings.}}


\bigskip


\noindent
1.A.  Riemann's mapping theorem for  simply connected domains


\medskip

\noindent
1.B.  The  mapping theorem for   connected domains
 

\medskip

\noindent
2. Boundary behaviour
\medskip

\noindent
3. Picard's theorem



\medskip

\noindent
4. Geometric results


\medskip

\noindent
5. Schwartz-Christoffell maps
\medskip

\noindent
6. Privalov's theorem
\medskip

\noindent
7. Maps between multiple connected domains
\medskip

\noindent
8. The Bergman kernel
\medskip

\noindent
9. The electric equilibrium potential
\medskip


\noindent
10. Conformal maps of circular domains
\medskip

\noindent
11. Beurling's mapping theorem



\newpage


\centerline{\bf {Chapter 7. Residue calculus.}}


\bigskip

















\noindent
\emph{0: Introduction}

\medskip


\noindent
\emph{0.A Five examples of residue calculus }

\medskip


\noindent
\emph{0:B Summation formulas}
\medskip


\noindent
\emph{0:C Asymptotic expansions}
\medskip


\noindent
\emph{0:D Ugly examples}



\medskip


\noindent
\emph{0:E Fractional decomposition}


\medskip


\noindent
\emph{0:F Computing local residues}



\medskip


\noindent
\emph{0.G Line integrals of multi-valued functions}
\medskip


\noindent
\emph{0:H Solving a differential equation}


\medskip


\noindent
\emph{0:I More involved integrals}
\medskip


\noindent
\emph{0:J  Abel integrals and equations}

\medskip


\noindent
\emph{0:K  Location of zeros of polynomials}




\bigskip













\centerline{\emph{Special integrals.}}
\bigskip

\noindent
\emph{A: The integral $e^{-x^2}$}


\medskip

\noindent
\emph{B: Integrals of rational functions}


\medskip

\noindent
\emph{C: The integral $\int_0^\infty\,\frac{dx}{P(x)}$}

\medskip

\noindent
\emph{D: The integrals $\int_{-\infty}^\infty\,\frac{e^{iax}\cdot dx}{P(x)}$}

\medskip

\noindent
\emph{E: Principal value integrals}
\medskip

\noindent
\emph{F: The integral $\int_0^\infty\,\frac{T(\sin x)}{P(x)}\cdot dx$}

\medskip

\noindent
\emph{G: Adding complex zeros to $P$}


\medskip

\noindent
\emph{H: The integral $\int_0^\infty\, \frac{x^a}{1+x^2}\cdot dx$}





\medskip

\noindent
\emph{I: The use of the log-function}



\medskip
\noindent
\emph{J: Trigonometric integrals}


\medskip

\noindent
\emph{K: Summation formulas.}

\medskip

\noindent
\emph{L:  Fourier integral}
\medskip

\noindent
\emph{M: Multi-valued Laplace integrals}

\newpage

\centerline{\bf{Chapter VIII  The Gamma function and Riemann's $\zeta$-function}}

\bigskip

\noindent
\emph{1. The Gamma function}
\medskip


\noindent
\emph{2. The $\zeta$-function}



\medskip
\noindent
\emph{3. The Riemann hypothesis}
\medskip


\noindent
\emph{4. The prime number theorem.}


\medskip

\noindent
\emph{5. A uniqueness
result for the $\zeta$\vvv function.}
\medskip

\noindent
\emph {6. A theorem on functions defined by a semi\vvv group}
\medskip

\noindent
\emph{7. Beurling's criterion for the Rieman hypothesis}








\bigskip










\centerline{\bf{Appendix A: Measure theory}}


\bigskip



\noindent
0. Introduction
\medskip



\noindent
0.1. Rational series and measure theory

\medskip


\noindent
2. Abstract measure theory

\medskip
\noindent
3. The Lebesgue measure

\medskip
\noindent
4. Riesz measures

\medskip
\noindent
5.  Stokes theorem in dimension $n$



\medskip
\noindent
6. The Hardy-Littelwood maximal function

\medskip

\noindent 
7. Rademacher functions
\medskip

\noindent
8. The Browninan motion

\bigskip


\centerline{\bf{Appendix B.  Distributions and boundary values of analytic functions}}

\bigskip




\noindent
0. Examples related to distribution theory.
\medskip





\noindent
0.A The origin of distributions
\medskip





\noindent
0.B A bird's view on distributions on the real line
\medskip





\noindent
1. Tempered distributions on the real line
\medskip

\noindent
2. Boundary values of analytic functions
\medskip

\noindent
3. Fourier-Carleman  transforms
\medskip

\noindent
4. The Paley-Wiener theorem
\medskip

\noindent
5. Runge's theorem

\medskip


\noindent
6. The generalised Fourier transform 

\medskip
\noindent
8. Carleman's inequality for differentiable functions 

\medskip
\noindent
9. Carleman's inequality for the inverse Fourier transform
in $L^2({\bf{R}}^+)$.

\medskip



\noindent
9. An integral equation.

\medskip
\noindent
10. Spectral synthesis

\medskip



\noindent
11. On  inhomogeneous $\bar\partial$-equations.



\medskip



\noindent
12. Integral equations of Planck and Laplace


\medskip



\noindent
13. The Carleman-Hardy theorem

\medskip

\noindent
14. The log-potential and Abel's inversion formula

\medskip

\noindent
15. An $L^1$\vvv inequality for inverse Fourier transforms.
\medskip

\noindent
16. On functions with a spectral gap.

\medskip

\noindent
17. A result by Beurling



\medskip

\noindent
18. Lindeberg's central limit theorem

\bigskip

\centerline{\bf{Appendix C: Functional analysis.}}

\bigskip


\noindent
\emph{0.A. Introduction}
\medskip

\noindent
\emph{0. B: Hilbert's spectral theorem}
\medskip

\noindent
\emph{0. C: Carleman's spectral theorem}




\bigskip

\noindent
\emph{1. Normed spaces}

\medskip

\noindent
\emph{2. Banach spaces}


\medskip

\noindent
\emph{3. Linear operators}

\medskip

\noindent
\emph{4. Hilbert spaces}

\medskip

\noindent
\emph{4. B: Eigenvalues of matrices}
\medskip


\noindent
\emph{5. Dual spaces}

\medskip

\noindent
\emph{6. Fredholm theory}

\medskip

\noindent
\emph{7. Calculus on Banach spaces}
\medskip

\noindent
\emph{8. Bounded self-adjoint operators}
\medskip

\noindent
\emph{9. Unbounded self-adjoint operators}

\medskip

\noindent
\emph{10. Commuative Banach algebras.}















\newpage



\centerline {\bf{Introduction.}}

\bigskip


\noindent
These notes   are foremost devoted to  analytic function theory
of one  variable but there also occur  material about measures and
Fourier analysis.
The borderline between complex and real
situations
is not strict since each profits from the other.
The level varies  where   results of  foundational character appear
together 
with more advanced material.
The less prepared reader may first  study
basic material and
for   experienced readers   the chapters  provide
background to
\emph{Special Topics}.
Most of the results in these notes 
are of a relatively  old vintage which 
is no surprise
since analytic function theory is
a  subject which has been developed for more than   two centuries.
Contributions by
Gauss, Cauchy and Abel, followed by 
Riemann, Schwarz, Weierstrass and Poincaré, 
put the subject into a level which has 
inspired later research in analytic function theory.
Let us finsh the introduction by some
examples.
The reader may of course skip this at a first instant and
move directly to the heading 
\emph{An overwiev}.
But the subsections below illustrate 
the flavour of these notes where
an ambition is to
show how analytic function theory intervenves with other subjects.






\bigskip


\centerline {\bf{The heat equation.}}
\bigskip

\noindent
An equation which appears
in many situations, including probability theory,
where it is related to the Brownian motion, is the PDE-equation
\[
\frac{\partial u}{\partial x}=
\frac{\partial^2 u}{\partial y^2}
\] 
which is satisfied in
a domain
$B=\{ -\infty<x<\infty\}\times \{0<y<A\}$.
The question arises if the vanishing of $u$ on some line 
$\{y=a\}$ with
$ 0<a<A$ implies that
$u$ is identically zero in $B$.
If
there exists a constant $k$ such that
\[
|u(x,y)|\leq e^{kx^2}\quad\colon (x,y)\in B\tag{i}
\]
the answer is affirmative. In fact, for each 
$0<a<A$ one has the integral formula
\[ 
u(x,y)=
\frac{1}{2\sqrt{\pi (y-a)}}\int_{-\infty}^\infty\,
u(\xi,a)\cdot U(x-\xi,y-a)\, d\xi\quad\colon a<y<a\tag{ii}
\]
where $U(x,y)$ is the function which is zero when $y\leq 0$ and 
\[
U(x,y)= e^{-x^2/y}\,\colon\, y>0
\]
If (i) does not hold uniqueness can fail, i.e.
without   growth conditions there exist solutions to
the heat equation in $B$ which vanish identically on
a line $\{y=a\}$.
A sufficient
and "almost necessary" condition for the uniqueness
was proved by Erik Holmgren in the article
\emph{Sur les solution quasi-analytique d l'équation de chaleur}
[Arkiv för matematik. 1924].


\medskip

\noindent
{\bf{Theorem.}}
\emph{Suppose there exists a constant $k$ such that}
\[
|u(x,y]|\leq e^{kx^2\cdot \log(e+|x|)}\quad\colon\, (x,y)\in B
\] 
\emph{Then, if $u(x,a)=0$ holds identically in $x$ for some
$0<a<A$,
it follows that
$u$ is identically zero.}
\medskip

\noindent
{\bf{Remark.}}
A complete investigation of the uniqueness problem for the heat equation  was
carried out by Täcklund
in [Täcklund] which shows that Holmgren's sufficiency theorem is quite sharp.
In § xx we expose constructions due to
Beurling devoted to  
solutions of the heat equation satisfying 
\[
u(x,y)|\leq e^{\epsilon(|x|)\cdot x^2\cdot \log(e+|x|)}\tag{iii}
\]
where  $\epsilon(r)$  tends to zero as
$r\to+\infty$. Here 
Holmgren's growth condition holds
and hence 
uniqueness holds.
Beurling constructed a
kernel $U^*$
which is used to express 
a solution $u$ satisfying (iii)  by
an integral formula like  (ii) above.
Several steps are needed to get $U^*$
where a crucial role is
played by
the analytic function
defined in
${\bf{C}}\setminus (-\infty,-e]$ by
\[
\gamma(z)=[\log(z+e)]^z= e^{z\cdot \log\,(z+e)}
\]
Here $e$ is Neper's constant and
a single-valued branch of the complex log-function
$\log\,(z+e)$ is found when
the
real interval $(-\infty,-e]$ has been removed.
\medskip

\noindent
The discussion above illustrates that
analytic function theory is needed in
refined questions from PDE-theory.
Readers who feel "an appetite" for the results  above
will hopefully find  these notes 
interesting, while those who prefer
"abstract  theories"  without involved estimates
may just as well 
refrain from studying  
these notes.







\bigskip


\centerline {\bf{Runge's theorem and Schwarz' reflection principle.}}
\bigskip


\noindent
With $z=x+iy$ we consider a rectangle
$\square=\{-a<x<a\}\times \{-b<y<b\}$.
It contains
the upper part
$\square_+= \{-a<x<a\}\times \{0<y<b\}$ and  the lower part
$\square_-=\square\cap \{y<0\}$.
Let 
$\phi(z)$ be an analytic function
in $\square_+$ which extends continuously to its closure.
A classic result, known as Runge's theorem,
entails that for every $\delta>0$ there exists
a sequence of polynomials $\{P_n(z)$
such that the maximum norms $|P_n-\phi|_{\square_+}$ tend to zero
and at the same time
the maximum norms of $|P_n|$ taken over
the rectangle
$\square(-\delta)=\{-a<x<a\}\times \{-b<y<\delta\}$ tend to zero.
While such an approximation takes place
the maximum norms
of $\{P_n\}$ taken over $\square$ cannot remain uniformly bounded
when $\delta\to 0$.
For if this  holds, another classic  result, known as Montel's theorem,
implies that there exists
a sequence of polynomials which converge
to an analytic function $g$ in $\square$, where this convergence is
uniform over compact subsets of $\square$.
Here $g$ is   zero in
$\square(-\delta)$ which by analyticity entails that
$g$ is identically zero in $\square$. At the same time
$g=\phi$ in $\square_+$
which contradicts the assumption that
$\phi$ is not identically zero.

\medskip

\noindent
To compensate for this one   introduces the
family
$\mathcal W$
of real-valued continuous
functions $\omega(y)$
which are
even  and positive $y\neq 0$, and 
decrease to zero  as $y$ approaches zero
through positive or negative values.
An example is $\omega(y)=y^2$ and
another is 
$\omega(y)= e^{-1/y^2}$
which decreases quite rapidly to zero with
$y$.
With $\phi(z)$ given as above
and $\omega\in\mathcal W$ we say that
a weighted Runge approximation holds if there
exists a sequence of polynomials $\{P_n(z)\}$
such that
\[
\lim_{n\to\infty}\,
||\omega(y)(P_n(z)-\phi(z)||_{\square_+}+
||\omega(y)(P_n(z)||_{\square_-}=0\tag{*}
\]
It turns out that
such a weighted approximation exists
if
$\omega(y)$ tends to zero sufficiently fast.
The following
necesssary and sufficient condition
was established  by
Beurling
ín the article  \emph{Analytic continuations along a linear boundary:
Acta mathematica 1953}.

\medskip

\noindent
{\bf{A. Theorem}}
\emph{The weighted Runge approximation (*) exists
if and only if}
\[
\int_0^b\, \log\log \frac{1}{\omega(y)}\, dy=+\infty\tag{*}
\]
\medskip

\noindent
Beurling's result will
be proved in § xx from the appendix about distributions.
Another
fundamental issue is about
analytic extensions across a linear boundary.
Schwarz' reflection principle in its
most wellknown version
asserts that if
$\phi$ and $\psi$ is a pair of analytic functions in 
the upper, resp. the lower rectangle 
which extend continuously to the real
interval $(-a<x <a)$
where
$\phi(x)= \psi(x)$,
then
they are analytic continuations of each other.
Relaxed conditions which entail analytic continuation across
$(-a,a)$ were
established by Carleman in lectures at the Mittag-Leffler Institute in 1935.
Here one starts with a pair $\phi,\psi$ where no
growth conditions are imposed as one approaches the real axis, i.e.
$y\mapsto |\phi(x_0+iy)|$ can
increase to $+\infty$ with no restriction upon its rate as
$y$ descreases to zero while $-a<x_0<a$ is kept fixed, and
similar increasing
slice functions of $\psi$ can be present.
However, the following sufficient condition holds:

\medskip

\noindent
{\bf{B. Theorem.}} \emph{Assume that}
\[
\lim_{y\to 0}\, \int_a^b\, \bigl |\phi(x+iy)-\psi (x-iy)\bigr |\, dx=0
\]
\emph{Then $\phi$ and $\psi$ are analytic continuations of each other.}
\medskip

\noindent
The proof is given in  § xx from the appendix about
distributions.
\medskip

\noindent
{\bf{Remark.}}
The two results above illustrate the spirit of these notes.
The proofs rely upon solutions to
the Dirichlet problem and
constructions of suitable subharmonic functions.








\bigskip


\centerline{\bf{The Dirichlet problem.}}

\bigskip

\noindent
Let
$D$ be  a bounded and simply connected domain in
${\bf{C}}$.
Given a continuous function $\phi$ on
the boundary $\partial D$ one seeks a harmonic function
$\Phi$ in $D$ whose boundary values agree with
$\phi$.
With no regularity conditions upon
$\partial D$
one cannot achive a solution. However, there
always exists a unique $\Phi$ whose generalised boundary values agree with
$\phi$. The precise assertion is due to 
Norbert Wiener and is given
in Chapter V.
Various applications and refinements of this result will appear
in more advanced sections.
Let us illustrate this by a result due to Beurling
where
geometric constructions interfere with analytic
estimates.
Here is the set-up: Let $\square=\{-a<x<a\}\times \{-b<y<b\}$
be a rectangle in the complex $z$-plane where $z=x+iy$.
Denote by $\mathcal D^*$ the family of simply connected
subdomains $D$ with the property that
if $\zeta=\xi+i\eta\in\partial D$ then
the rectangle
\[ 
P_\zeta=\{x+iy\colon |x|<|\xi,\, |y|<\eta|\}\subset D
\]
Next, denote by $\mathcal F$ the family of 
even  and real-valued functions $\omega(y)$ 
defined when $0<|y|<b$ with the property that
$y\mapsto \omega(y)$ descreases on $(0,b]$
and there is a constant $C$ such that
$\omega(y)+C\geq 0\colon\ 0<y\leq b\}$.
Moreover,  
\[
\int_0^b\,\omega(y)\,dy<\infty
\]
The last condition means roughly that $\omega$ is not too large
when $y\simeq 0$.
\medskip

\noindent
{\bf{Theorem.}}
\emph{For each  $\omega\in\mathcal F$
there exists a constant $c$ and some
$\omega_1\in\mathcal F$  with $\omega_1\geq \omega$
and a domain $D\in\mathcal D^*$
such that the generalized Dirichet
problem for $D$ with boundary function}
\[
\phi(\xi+i\eta)= e^{\omega_1(\eta)}
\]
\emph{has a solution $\Phi$ satisfying}
\[
0<\phi(x+iy)< 2e^{\omega_1(\eta)}+ c\quad\colon x+iy
\in P_\zeta\, \colon\,\zeta=\xi+i\eta \in\partial D
\]


\noindent
{\bf{Remark.}}
This result appears in the  
article  \emph{Analytic continuations along a linear boundary}
cited before and  
used to
prove Theorem A  in
the previous paragraph.
It goes without saying that the theorem above
belongs to one of the harder
results in these notes. Here
"good familarity"  with subharmonic functions is
essential  to pursue the details in Beurling's proof
which is presented 
in § xx from the appendix about distributions.

\bigskip


\centerline {\bf{The Riemann-Schwarz inequality.}}
\bigskip

\noindent
Let $\sigma$
be 
a hyperbolic metric  on  a Riemann surface $X$, i.e. 
it has  negative curvature which means that in
an open chart identified with
a 
subset of the complex $z$-plane,
the $\sigma$-distance 
is given by
$e^{u(z)}\cdot |dz|$ where
$u(z)$ is  a  subharmonic function.
To each  pair of points $p,q$ in $X$ we denote by 
$\mathcal C(p,q)$ the family of
curves in $x$ with end-points at $p$ and $q$.
\medskip

\noindent
{\bf{Theorem.}}
\emph{For every pair
$\gamma_1,\gamma_2$ in  $\mathcal C(p,q)$
and
each point $\xi\in\gamma_1$,
there exist  curves $\alpha,\beta$ with
$\alpha\in\mathcal C(p,q)$ while $\beta$ has end-points
at $\xi$ and some point $\eta\in \gamma_2$ such that}
\[
\ell(\alpha)^2+\ell(\beta)^2\leq
\frac{1}{2}\bigr (\ell(\gamma_2)^2+\ell(\gamma_3)^2\,\bigl )\tag{*}
\]
\emph{where $\ell(\gamma)$ denotes the $\sigma$-length of a curve in $X$.
Moreover, the inequality (*) is strict with the exception for
special rhombic configurations.}
\medskip

\noindent
We prove (*) in a chapter devoted to
Riemann surfaces.
The theorem  gives the  existence of unique geodesic  curves
on $X$ which join a pair of points.
The proof employs the 
uniformisation theorem for Riemann surfaces
which
reduces the 
proof to show the following: 
\medskip

\noindent
\emph{Let
$D$ be the unit disc and $0<\theta<\pi/2$ and consider   the unique
circle $C_\theta$ which
contains
$e^{i\theta}$
and $e^{-i\theta}$ and intersects the unit circle at right angles at these points.
Let $\alpha$ denote the circular subarc of $C_\theta$  contained in
$D$.
Then the following inequality holds for
every subharmonic function $u$ in $D$:}
\[
\bigl(\int_{-1}^1\, e^{u(x)}\, dx\bigr)^2+
\bigl(\int_\alpha\, e^{u(z)}\, |dz|\bigr)^2\leq
\frac{1}{4}\cdot\bigl( \int_0^{2\pi}\, e^{u(e^{i\phi})}\,d\phi\bigr)^2
\] 
\bigskip



\centerline {\bf{An inequality for Dirichlet integrals.}}
\medskip


\noindent
Let  
$\Omega$ be a bounded open set in
${\bf{R}}^2$
and $f$ a real-valued continuously differentiable function in
$\Omega$ with partial derivatives
$f_x$ and $f_y$. 
The Dirichlet integral is defined by
\[
D^2_\Omega(f)=\iint_\Omega\, (f_x^2(x,y)+f_y^2(x,y))\, dxdy\tag{*}
\]
When
$\Omega$ is the square
$\{0\leq x\leq \pi\}\times\{0\leq y\leq \pi\}$,
$D_\Omega^2(f)$ is given by a Fourier series.
More precisely, with 
\[
a_0=\frac{1}{\pi^2}\,\iint_\Omega\, f(x,y)\, dxdy\quad\colon\,
\widehat f(k,m)=\iint_\Omega \, f(x,y)\cdot
\sin kx\cdot \sin my\, dxdy
\]
it  follows that
\[
D^2_\Omega (f)=
\sum_{k=1}^\infty\sum_{m=1}^\infty\,
(k^2+m^2)\cdot\widehat{ f}(k,m)^2
\]
At the same time the $L^2$-integral
\[
\iint_\Omega \, f^2(x,y)\, dxdy=\pi^2\cdot a_0^2+
\sum_{k=1}^\infty\sum_{m=1}^\infty\,
\widehat{ f}(k,m)^2
\]
So if the mean value of $f$ over $\Omega$  vanishes, i.e. if $a_0=0$
then
\[
\iint_\Omega\, f^2(x,y)\, dxdy\leq D^2_\Omega (f)\tag{*}
\]
It turns out that (*) holds when the square
is replaced by
an arbitrary
bounded and simply connected
open set $U$.
The proof follows from the existence  
of a conformal mapping from the square above  onto $U$
and is given in
(*) where we also describe
 how (*)  can be  used to
settle the
Dirichlet problem  for simply connected domains with
smooth boundaries.



\bigskip



\centerline {\bf{Carleman-Hadamard functions.}}
\bigskip


\noindent
Let $\Omega$ be a bounded and connected 
open set in ${\bf{C}}$.
The family of analytic functions in
$\Omega$ is denoted by $\mathcal O(\Omega)$.
Each $f\in \mathcal O(\Omega)$ is 
locally represented
by convergent power series: 
\[ 
f(z)= f(z_0)+\sum_{n=1}^\infty\, 
\frac{f^{(n)}(z_0)}{n!}\cdot (z-z_0)^n
\quad\colon\, z_0\in\Omega
\tag{1}
\]
Let $d(z_0,\partial\Omega)$
be the distance of $z_0$ to the  boundary
and  $D_\Omega(z_0)$ is the open disc of radius
$d(z_0,\partial\Omega)$ centered at $z_0$
The power series in (1) 
may   converge in a larger disc
whose radius is denoted by $\rho_f(z_0)$. We exclude the
case when
$f$ is the restriction to
$\Omega$ of an analytic function $F$ defined in some large
disc containing $\Omega$ which means that
there exists a constant $M$ such that
$\rho_f(z_0)\leq M$ hold for every
$z_0\in \Omega$.
Hadamard's formula gives:
\[ 
\frac{1}{\rho_f(z_0)}=\limsup_{n\to \infty}
\bigl[\frac{|f^{(n)}(z_0)|}{n!} \,\bigr]^{\frac{1}{n}}\tag{2}
\]
Regarding a picture  one
verifies the inequality below for each
$z_0\in\Omega$:
\[
|\rho_f(z)-\rho_f(z_0)|\leq |z-z_0|\quad\colon z\in D_\Omega(z_0)
\]
It follows that
$\rho_f(z)$
is a continuous and positive function in
$\Omega$.
The  Carleman-Hadamard function is defined by
\[
\mathcal{CH}_f(z)=\log\,\frac{1}{\rho_f(z)}
\]
A crucial  fact is that this function is
subharmonic, i.e its Laplacian
taken in
the sense of distributions
yields a non-negative Riesz measure in
$\Omega$. To prove this we
take a positive integer
$N$ and set
\[ 
\gamma_N(z)=\max_{n\geq N}\,\frac{1}{n}\cdot 
\log\, \frac{|f^{(n)}(z)|}{n!}
\]
Since the  complex derivatives
$\{f^{(n)}(z)\}$ belong to $\mathcal O(\Omega)$,
$\gamma_N(z)$ is the maximum of subharmonic functions and
therefore itself subharmonic.
Now $\{\gamma_N(z)\}$ is a non-increasing sequence of functions 
which  by (2)  converge pointwise to
$\log\,\frac{1}{\rho_f}$.
The subharmonicity of the $\gamma$-functions
imply that $\{\Delta(\gamma_N)\}$
are non-negative Riesz measures in $\Omega$ and then the  pointwise
convergence implies convergence in the weak distribution sense
which implies  that 
$\Delta(\log\,\frac{1}{\rho_f})$
is a non-negative Riesz measure in
$\Omega$ and hence
$\mathcal{CH}_f$ is subharmonic.
\medskip


\noindent
{\bf{Remark.}}
The subharmonicity of
$\mathcal{CH}_f$
was put forward by Carleman in lectures at the Mittag-Leffler Institute in 1935
who used this  fact to 
construct 
boundary values of analytic functions
which
led to an extension of Fourier's inversion formula where
so called 
hyperfunctions 
extend  
the class of   distributions on real intervals.
Let us also remark that
the Carleman-Hadamard function measures 
the singularities of $f$ when one approaches the boundary.
Namely, the  condition that
$f$ does not extend analytically across in a neighborhood of
a boundary point
$p\in \partial\Omega$ means that
$\rho_f(z)\to 0$ as $z\to\partial \Omega$, or equivalently that
\[ 
\lim_{z\to p}\, \mathcal{CH}_f(z)=+\infty\quad\colon p\in \partial\Omega
\]
In addition to this the mass distribution
of non-negative Riesz measure
$\Delta(\mathcal{CH}_f)$
reflects the boundary behaviour of $f$
in a  refined way.
A special subharmonic  function arises when
we take
\[ 
u_\Omega(z)=\log\,\frac{1}{d(z,\partial\Omega)}
\]
The non-negative Riesz measure
$\Delta(u_\Omega(z))$
is  an
invariant attached to the bounded domain $\Omega$ which 
measure proportions in a logarithmic scale and 
leads us to the next topic.


\newpage


\centerline {\bf{Logarithmic capacity.}}
\bigskip

\noindent
A new era in analytic function theory
started  with  Iversen's Ph.d-thesis
\emph{Recherches sur les fonctions meromorphes}
from Helsinki University in 1914 
and led for example to  the  theory
about
value distributions of meromorphic functions
where
major results are due to R. Nevanlinna.
In these notes
attention is given to
logarithmic capacity.
A  compact
set $E$  of the unit circle
has  logarithmic capacity equal to zero
if the energy
integral
\[
\iint_{E\times E}\,
\log\, \frac{1}{|z-\zeta|}\,d\mu(z)\cdot d\mu(\zeta)=+\infty
\]
for every probability measure supported by $E$.
\emph{Special Topics} contain sections
devoted to
thin sets and  boundary values
of analytic functions.
Here is an example where  logarithmic
capacity intervenes with function theory.
Let $f(z)$ be a meromorphic function in the unit disc
with no pole at $z=0$. Put
\[
T_f(r)=\frac{1}{2\pi}\cdot \int_0^{2\pi}\,\log ^+|f(re^{i\theta})|\,d\theta
\quad\colon\, P_f(r)= \int_0^r\, \frac{n_\infty(\rho)}{\rho}\, d\rho
\] 
where
$n_\infty(\rho)$ counts  the number of poles with their orders in
the disc
$\{|z|<\rho\}$. One says that the meromorphic function
$f$ has unbounded characteristic if
\[
\lim_{r\to 1}\, T_f(r)+ P_f(r)=+\infty
\]
Next, a complex number
$\alpha$
belongs to the essential range set $R(f)$
if there exists a sequence $\{z_n\}$ in $D$ where
$|z_n|\to 1$ and  $f(z_n)= \alpha$
hold for every $n$.
With these notation
the following result was proved by Frostman in
[xxx]:
\medskip

\noindent
{\bf{Theorem.}}
\emph{If $f$ has unbounded  characteristic
then the logarithmic capacity of the set
${\bf{C}}\setminus R(f)$
is zero.}
\medskip

\noindent
Results as above
motivate why an extensive appendix devoted to
measure theory has been included.
The next
example  illustrates how complex analysis in one variable
intervenes
with measure theoretic considerations.


\bigskip


\centerline {\bf{Borel-Denjoy series.}}
\bigskip

\noindent
Let $A_1,A_2,\ldots$ be a sequence of complex numbers
which tends to zero and assume that
\[ 
\sum_{k=1}^\infty\, |A_k|\cdot \log\, \frac{1}{|A_k|}<\infty
\]
Let $\{\alpha_\nu\}$ be a sequence of complex numbers
where the sole condition is that
$\alpha_k\neq \alpha_\nu$ when
$\nu\neq k$.
An example could be
a sequence  with rational coordinates
arranged in such a way that
every point in
${\bf{C}}$ is a cluster point for the $\alpha$-sequence.
Next, let $P(t)$ 
be a polynomials with complex   coefficients. 
To each $N\geq 1$ 
we consider the function
\[ 
S_N(t)=\sum_{k=1}^{k=N}\, \frac{A_k}{P(t)-\alpha_k}
\]
As a complex-valued function of the real variable $t$
this partial sum function is defined outside a finite set of $t$-values
where $P(t)$ happens to be $\alpha_k$ for some $k\leq N$.
It means that one only has to
avoid a denumerable
set of $t$-values in order that
the partial sums are defined for every $N$.
But absolute values $|P(t)-\alpha_k|$
can be small quite often 
and the 
question arises when 
there exists a limit
\[
\lim_{N\to\infty}\,S_N(t) =S_*(t)
\]
for those  $t$-values where
$P(t)\neq \alpha_k$  for all $k$.
It turns out that convergence holds almost everywhere in
the sense of Lebesgue.
In other words, there exists a subset $\mathcal N_P$ of the real $t$-line whose
linear Lebegue measure is zero and the partial sums converge to a limit 
for all $t$ outside $\mathcal N_P$. 
How does one start the proof of this assertion?
An ambition in these notes
is 
to supply the reader with 
"enough muscles" in analytic function theory
so that
articles which settle a result as above
can be studied with relative ease.

\bigskip



\centerline {\bf{The $\Gamma$-function}}.
\medskip


\noindent
It is
defined by
\[ 
\Gamma(z)= \int_0^\infty\, t^{z-1} \cdot e^{-t}\, dt
\]
The function is  analytic in the half-space $\mathfrak{Re}\, z>0$
and partial integration gives the functional equation
\[
z\cdot \Gamma(z)=\Gamma(z+1)
\]
From this it follows that
the $\Gamma$-function
extends to a meromorphic
function in the whole complex plane with simple poles at
$0,-1,-2,\ldots$. Less obvious is that
 $\frac{1}{\Gamma(z)}$ is an entire function.
Another remarkable result
is Euler's integral formula 
which will be proved in
§ XX devoted to the $\Gamma$-function:
\[ 
\Gamma(z)=\frac{1}{z}\cdot e^{-\gamma\cdot z+
z^2\int_1^\infty
\frac{[t]}{t^2(t+z)}} \, dt\tag{*}
\]
Here  $\gamma$ is Euler's constant and
$[t]$ the integral part of $t$ which gives
\[
z^2\int_1^\infty
\frac{[t]}{t^2(t+z)} \, dt
=\sum_{n=1}^\infty\, z^2\cdot n\cdot \int_n^{n+1}\,\frac{dt}{t^2(t+z)}=
\] 
\[
\sum_{n=1}^\infty\, n\cdot
\int_n^{n+1}\,[\frac{1}{t+z}+ \frac{z-t}{t^2}]\,dt
=n\bigl[\log\,(1+\frac{1}{n+z})+\frac{z}{n(n+1)}-\log (1+\frac{1}{n})\,]
\]
Euler's clever choice of 
the constant $\gamma$
gives the equation (*). 
An example where (*) is used
appear 
during the construction of  kernels which
give solutions to the heat equation in the non-analytic case
where the usual  heat  kernel cannot be applied.
This  illustrates how analytic function theory applies to
problems about differential equations.


\newpage



\centerline {\bf{Critical values for harmonic level curves.}}
\bigskip


\noindent
Let $D$ be the unit disc and consider
a sequence of real numbers
\[ 
0<\alpha_1<\beta_1<\alpha_2<\ldots<\beta_{m-1}<\alpha_m<\beta_m<2\pi
\]
They give rise to $m$ disjoint intervals on the unit circle:
\[ 
J_\nu=\{e^{i\theta}\colon\, \alpha_\nu\leq \theta<\beta_\nu\}\quad\colon
1\leq\nu\leq m
\]
Now there exists the harmonic function
$\omega(z)$ in the unit disc whose boundary
values are one on
each $J_\nu$ and
zero on the closed complement of these $J$-intervals.
Poisson's integral formula gives
\[
\omega(z)= \frac{1}{2\pi}\cdot \sum_{\nu=1}^{\nu=m}\,
\int_{\alpha_\nu}^{\beta_\nu}\frac{1-|z|^2}{|e^{i\theta}-z|^2}\, d\theta
\]
To each $0<s<1$ we get the level set
$L(s)=\{\omega(z)=s\}$ in $D$.
When $s$ is close to one
it is easily seen that
$L(s)$ is the disjoint union of arcs
which stay close to the unit circle and join
end-points of the $J$-intervals. Similarly,  if $s\simeq 0$ then
$L(s)$ is a disjoint union of arcs which join
end-points of the complementary intervals.
When $m\geq 2$ one sees from a picture that
in between there must occur $s$-values where
the level set
$L(s)$ cannot be a union of
$m$ disjoint Jordan arcs.
It means that self-intersections occur and we shall learn that
they are caused by
zeros of the gradient vector for
$\omega$.
Here
$\omega(z)$ 
has
a harmonic conjugate $\omega^*(z)$ such that
the complex-valued function $\omega(z)+i\cdot \omega^*(z)$ is analytic given
by the Herglotz formula:
\[
\omega(z)+i\cdot \omega^*(z)=
\frac{1}{2\pi}\cdot \sum_{\nu=1}^{\nu=m}\,
\int_{\alpha_\nu}^{\beta_\nu}\frac{e^{i\theta}+z}{e^{i\theta}-z}\, d\theta\tag{*}
\]
The Cauchy-Riemann equations show  that
the gradient vector $\nabla(\omega)= (\omega_x,\omega_y)$
vanishes
at a point $z$ if and only if
the complex derivative of (*) is zero at $z$.
Taking the derivative with respect to
$z$
in (*) we get the analytic function
\[
\phi(z)=
 \frac{1}{2\pi}\cdot \sum_{\nu=1}^{\nu=m}\,
\int_{\alpha_\nu}^{\beta_\nu}\frac{2\cdot e^{i\theta}}{(e^{i\theta}-z)^2}\, d\theta
\]
For each $\nu$ 
the $\theta$-derivative of
$(e^{i\theta}-z)^{-1}$ is equal to  $-ie^{i\theta}\cdot (e^{i\theta}-z)^{-2}$
which gives
\[
\phi(z)= \frac{1}{\pi\cdot i} \cdot\bigl [
\sum_{\nu=1}^{\nu=m}\,\frac{1}{e^{i\beta_\nu}-z}-
\sum_{\nu=1}^{\nu=m}\,\frac{1}{e^{i\alpha_\nu}-z}\bigr]
\]
It turns out that
the rational function $\phi(z)$ has $m-1$ zeros counted with multiplicity
in
the unit disc.
The proof 
is very instructive and  relies upon the argument principle.
Details appear
in § XX where we treat
a  general result due to Nevanlinna which applies to level curves
of harmonic measure functions
in domains which are not necessarily simply connected.

\newpage


\centerline{\bf{Absolute values of complex polynomials.}}
\bigskip

\noindent
Let $P(z)=(z-\alpha_1)\cdots (z-\alpha_n)$
be a polynomial of degree $n$ with simple zeros which means that
$\{\alpha_k\}$ is an $n$-tuple of disctinct numbers.
To every $a>0$ we get the subset of the complex $z$-plane defined
by the level curve of $|P(z)|$:
\[
 \gamma_a=\{|P(z)|= a\}
\]
We have also the open
sets
\[
\Omega_a=\{|P(z)|< a\}
\]
If $a$ is small it is clear that
$\gamma_a$
is the disjoint union of $n$ many small simple and closed curves
around the zeros. If $a$ is very large
the term $z^n$ dominates and $\gamma_a$ is a simple closed
curve
which stays close to the circle $|z|= a^{\frac{1}{n}}$.
Hence some  changes must occur as $a$ increases from small to large values.
In particular the number of connected
components of the $\Omega$-sets
change.
Under the extra assumption that
the derivative
$P'(z)$ also has
simple zeros, say $\beta_1,\ldots,\beta_{n-1}$ and
the absolute values $\{|P(\beta_\nu)|\}$
are
all distinct  one gets the following
topological picture. Arrange the absolute values
$\{a_k=|P(\beta_k)|\}$   so that
$0<a_1<\ldots<a_{n-1}$.
In § XX we  show
that  if $a_k<a<a_{k+1}$
for some $1\leq k\leq n-2$, then
$\gamma_k$
is the union of $n-k$
simple closed curves and hence
$\Omega_k$ has $n-k$ connected components.
If $a>a_{n-1}$ then 
$\gamma_a$ is 
a simple closed curve so that  $\omega_a$ is a connected
a Jordan domain.
One can
visualize  the change of the
$\Omega$-domains as $a$ increases 
on a computer.
As a specific example one can take
the polynomial 
$P(z)= z^7-\delta\cdot z-1$ where $\delta$ is a positive real number.
 One easily verifies 
that
the conditions above hold for every
$\delta>0$.
With $\delta$  small, say
$10^{-2}$
the computer 
illustrates how the
domains
$\{|P|<a\}$
change and thanks to
contemporary programs
one 
watch the  changing configurations
like a moving film which gives intuitive feeling for
a  complex analytic
situation

\bigskip


\centerline {\bf{Ordinary differential equations.}}
\bigskip

\noindent
Let $m\geq 2$ and $p_0(x),\ldots,p_m(x)$
are polynomials which in general may have
complex coefficients.
With $\partial= \frac{\partial}{\partial x}$
one has the  differential operator
\[
P(x,\partial)= p_m(x)\partial^m+\ldots+ p_1(x)\partial +p_0(x)
\]
If the leading polynomial $p_m$ has no real zeros one says that
the elliptic case occurs. Then it is wellknown that
the homogeneous solutions to
$P$ is an $m$-dimensional vector space
formed by real-analytic functions on the $x$-line.
If $p_m$ has real zeros
the determination of all distributions
$\mu$ on the $x$-line satisfying $P(\mu)=0$
is not so obvious.
Expressing distributions via boundary values of analytic functions we
shall prove that the
$P$-kernel on the space
${\mathfrak{Db}(\bf{R}})$
is a vector space of dimension $m+k$, where
$k$
is the number of real zeros of $p_m$ counted with multiplicities.
Moreover, the $P$-kernel 
contains specific subspaces for each
real zero $a$ of $p_m$.
Namely, let 
$p_m(z)=(z-a)^e\cdot q(z)$ for some $e\geq 1$
where $q(a)\neq 0$. In §§ we prove that 
$\text{Ker}_P{\mathfrak{Db}(\bf{R}})$
contains an $e$-dimensional subspace
of distributions
supported by the half-line $[a,+\infty)$ and that
$P$ has a fundamental solution $\gamma$ supported by
this half-line, i.e.
\[ 
P(x,\partial)(\gamma)= \delta_a
\]
where $\delta_a$ is the Dirac distribution at $a$.
\medskip

\noindent
{\bf{Example.}}
Set $\nabla=(x\partial)^2=x^2\partial^2-x\partial$
and
consider Bessel's differential operator
\[
P(x,\partial)= \nabla^2+x^2-1
\]
Here one finds
an entire function $f(z)$ such that
$P(f)=0$ whose series expansion at $\{z=0\}$ starts with
$f(z)= z+c_3z^3+\ldots$.
In addition 
there exists a multi-valued solution
\[
\phi(z)= f(z)\cdot \log z+a(z)
\]
where $a(z)$ is a meromorphic function with
a simple pole at $\{z=0\}$.
Now
we get the distribution supported by $\{x\geq 0\}$
defined by
\[
\mu= f(x)\cdot (\log x)_++ a_+(x)
\]
where $(\log x)_+$ and $a_+(x)$ are  Euler's distribution extension to
$\{x\geq 0\} $ of the densities
$\log x)$ and $ a(x)$ on $\{x>0\}$ to be defined in § xx where we also
verify that
$\mu$ is  a fundamental  solution to $P$.
























 







\newpage


\centerline{\bf{An overwiew to these notes.}}
\bigskip





\noindent
The material in  § 0.1-0.10 
describes various  aspects in analytic function theory and
applications to other subjects.
The less experienced reader may prefer to
study the subsections (0.1-0.10)  at a later occasion since
rather advanced concepts sometimes appear.
The  section devoted to work by Beurling and Carleman
has been inserted both for its historic reconsiliation, and
since 
many results in these notes
are due to Beurling and Carleman.










\bigskip



\centerline{\emph{References.}}





\medskip



\noindent
Much inspiration in these notes, including  sources  for    historic accounts,
come from Ludwig Bieberbach's  text-books [Bi:1,2]
which cover  analytic function theory
up to 1925.
In several sections I  borrow proofs from these text-books 
where my presentation  is only slightly different.
An example is the Uniformisation
Theorem for multiply connected domains
in ${\bf{C}}$ 
where I have followed Bieberbach's  presentation of the elegant 
proof due to  Caratheodory. 
The text book [Cartan] by Henri Cartan 
has inspired the way I have organised the chapters devoted to analytic
functions.
Here the reader may  find
exercises which give very good illustrations to
theoretical results.
The book [Ko] by Paul Koosis
has also been a valuable source.
At several places
material  from Koosis' original text are
presented with  minor changes,
such as in the proof of Donald  Marshall's convexity theorem for inner
functions in the unit disc.
I have also profited 
upon material from
the two volumes about the logarithmic potential by Koosis which
is a good reference for further studies in analytic function theory.
Material devoted to
Runge's Theorem is inspired by
Raghavan Narasimhan's text-book [Na]
where the reader also may find
a nice introduction to  Riemann surfaces.
Basic facts about
the harmonic measure and the Lindelöf-Pick principle 
is  inspired  by R. Nevanlinna's book [xx]. 
E. Landau's book [xx] has contributed to sections
devoted to series.
Topics from   the  book [PE] by Raymond Paley
and Norbert Wiener also appear.
Apart  from the text-books above
there also occur  some problems taken 
from  [Po-Sz] by Polya and Szegö. 
An example  is a result 
due to Siegel which gives an 
upper bound for products of roots to  polynomial
in any degree expressed by the size of its coefficients. 
Siegel's  proof 
gives   a  good lesson since it teaches
how complex analysis can be used in an  unexpected
fashion. 
\medskip

\noindent
In addition to the references above I have  been inspired by
the over-all presentation  
in the text-book [Kr] by  Steven G. Krantz.
Here the reader will find 
a number of results  about
conformal maps of multiply connected domains and
their associated automorphism groups
together with a study
of the Bergman kernel  and 
constructions of
various metrics. The reader may also consult
the text\vvv book by John Conway, especially part II which contains
material  of considerable
interest. For example a chapter is devoted to De Brange's proof of the Bieberbach
conjecture
which for more than half a century was
an open problem in a analytic function theory.
Chapters devoted to harmonic and subharmonic functions
also merit attention such the exposition of the 
Fine Topology in ${\bf{C}}$  which by definition is the 
weakest topology making every subharmonic function with values in
the extended interval $\vvv \infty,\infty]$ into continuous functions.
Another recommended text-book is [Andersson] which
presents  elegant proofs  of  advanced
results such as Carleson's Corona theorem.





\bigskip

\noindent
Finally I must mention the text-books [1-2] by Lars Ahlfors.
His masterful presentation  in
[1]
is  recommended to everybody who enters  studies
devoted to complex analysis. 
Since [1] was a veritable   "bible"
for me as a graduate student, it is clear that
the text by Ahlfors has inspired much  material in
these notes, foremost in  sections devoted to
the foundations in analytic function theory.
Concerning the more advanced book [Ahl-2]
there occur references in these notes to 
the general Uniformisation Theorem.
But I have not tried to pursue this  in detail.
One reason is that these notes  do not treat
potential theory.
But hopefully these
notes may inspire  readers to study [Ahl:2].
One must also mention 
the deep studies of moduli problems  in  articles such as [Ahl-Beu]
where the authors seek
invariants to decide when
a pair of  multiple connected  domains
are conformally  equivalent
and
from  work by
Ahlfors one should  mention  his
far reaching studies of
quasi-conformal maps. His
article [Ah. Acta 1935] 
is even today
an inspiration for  contemporary
research. 
The  lyric comments 
when  Caratheodory
presented Ahlofor's contributions  at the IMU-congress in 1936
where he bacame  the first mathematician
to receive a Fields medal,
is a recommended reading even today.
Twenty years later Ahlfors discovered an explicit analytic solution
to the Beltrami equation and soon after, in collaboration with Lipman
Bers, quasiconformal variations were applied to
study Kleinian groups. 
Among
more recent topics
of  advanced nature
we mention  
complex dynamics where  Sullivan's theorem
about Julia sets is an  example. A 
proof  of this result appears in the
text-book 
[Ca-Ga] by
L. Carleson and J. Garnett.
Finally, we  already mentioned
the text-book
[Ga-Ma] by J. Garnett and Marshall devoted to  recent discoveries
about 
harmonic measure and extremal length. 



\newpage




\centerline {\emph{Remarks about the contents.}}
\bigskip



\noindent
I have tried to make the notes reasonably self-contained. For example,
a detailed proof of \emph{Stokes Theorem} is given
together with
the formulas of
Green and Gauss where  attention also is given 
to the notion of differential forms.
With $z=x+iy$ we identify the complex $z$-plane with
${\bf{R}}^2$. Consider 
a differential 1-form
$W= f\cdot dx+g\cdot dy$ where 
$f$ and $g$ is a pair  real-valued $C^1$-functions.
The 1-form $W$ is  closed when 
\[ 
dW= (-f'_y+g'_x)\cdot dx\wedge dy=0\tag{*}
\]
In  Chapter II
we establish a  result expressing the 
difference of two line integrals
of a 1-form $W$ which is not
necessarily closed, taken
over a pair of curves $\Gamma_1$ and $\Gamma_0$ 
with common end-points
and linked by a continuous family of similar curves.
The  formula  in Theorem 5.7 from  Chapter II is a
result in real 2-variable analysis which  contains  the subsequent
study of complex line integrals as a special case
when the integrands 
are complex analytic functions.
So the reader should be aware of the fact that
ordinary Calculus  provide many
tools to attain
integral formulas in analytic function theory.
However, we  shall prove results in the complex analytic set-up
for its own sake. One reason for doing this extra job
is that
complex line integrals are  nicely 
expressed by taking complex Riemann sums. Another is the special flavour which 
arises  from complex arguments. A typical case 
occurs  in § 2 from Chapter 4 where the argument principle 
counts zeros of an analytic function via its complex logarithmic derivative.


\medskip


\noindent
An example where calculus in one real variable
becomes useful in analytic function theory
is a convexity theorem 
from 1906 by
Jensen which goes as follows:
Let  
$\{\alpha_\nu\}$
be a decreasing sequence of positive real numbers
with $\alpha_1\leq 1$
and let
$\{p_\nu\}$ another sequence of positive numbers.
Assume that there exists some
$\delta>0$  such that the series
$\Phi(r)=\sum\, p_\nu\cdot r^{\alpha_\nu}$
converges when $0<r<\delta$.
Then Jensen proved  that
$\text{log}\,\Phi(r)$ is a convex
function of
$\text{log}\,r$.
This   can be used
to  prove convexity theorems
expressed by 
integrals connected to analytic functions and more
generally to subharmonic functions.
For example, Jensen's result was used when Hardy in his work 
\emph{The Mean Value of the Modulus of an Analytic function}
from 1915 proved that the function
$r\mapsto\int_0^{2\pi}\, |f(re^{i\theta})|\cdot d\theta$
is a convex function of
$\text{log}\,r$ when $f(z)$ is  analytic in some disc
centered at the origin.
Many early results such as those of Hardy were later superseeded
by the  systematic use of subharmonic functions and
Thorin's convexity theorem which is exposed in § XX.





\medskip


\centerline {\emph{A general comment.}}
\medskip

\noindent
These notes do not strive to present the theory in its most
perfect form and I often try
to give a historic perspective, perhaps a bit too  affected by my own
experience as undergraduate student at Stockholm University
in the early 60:s when I was taught function theory by
Otto Frostman in a way I appreciated very much. 
Theorems  
are often proved in a "pedestrian manner" rather than
using the full force of concepts from functional analysis.
This is not just a matter  of a "historic reconcilation". One reason is that
results
are better understood if one  can find a
constructive proof rather than to rely upon the axiom of choice
via the Hahn Banach theorem or the existence of maximal ideals which
appear
in commutative Banach algebras.
A typical case is when we start from a function $f(x)\in L^1({\bf{R}})$
and regard its Fourier transform $\hat f(\xi)$.
Suppose  that $a\leq\xi\leq b$
is an interval on the real $\xi$-line and let
$\Phi(z)$ be an analytic function defined in an open
neighborhood of the compact image set
$\hat f([a,b])$.
Then there exists $g(x)\in L^1({\bf{R}})$
whose Fourier transform
$\hat g(\xi)$ is equal to $\Phi(\hat f(\xi))$
when $a\leq\xi\leq b$.
The mere existence of $g$ follows easily 
by an abstract reasoning. However, one can
construct $g$ in a rather explicit manner
using the local power series expansions
of the analytic $\Phi$-function.
We shall give this "pedestrain proof" 
based
upon a lecture by Carleman at Institute of Mittag
Leffler in 1935
which has the merit
that it is constructive. Of course, this 
requires more effort
as compared to the "abstract proof". But I think it teaches
the student more. 

\medskip

\noindent
The reader   will  also find 
repetitions of similar
arguments which appear in slightly different contexts.
A typical case occurs  in studies of various maximal functions.
It would be possible to
concentrate all this to some few general results
in
a general context where one regards Riesz measures on metric spaces
whose distribution of mass satisfies certain conditions with respect to the given metric.
This 
would lead to short
proofs but often with less control of a priori constants.
So  we often
prefer to repeat similar arguments in  specific
situations.
For an account about
general maximal functions we refer to
the elegant article
[Smith] which becomes especially useful 
when  analytic function theory in one
complex variable is replaced by studies of  harmonic and subharmonic functions in
${\bf{R}}^d$ for $d\geq 3$.








\medskip


\noindent {\emph{ A  (nasty ?) remark.}}
Personally I do not understand the contemporary
trend in the teaching  of mathematics where subjects
tend to be isolated from each other into  small 
separate courses devoted to measures, function theory, 
Fourier series and so on. Not to
mention the unreasonable 
borderline between algebra and analysis.
To give an example. In the past
Eisenstein's famous theorem from 1852 was demonstrated to
most  students entering graduate studies.
The elegant proof of Heine from 1854 (presented in
Chapter XX)
combines  algebraic facts about
irreducible polynomials in two 
variables  
with  analytic function theory.
Recall that Eisenstein's theorem
says  that
if the power series expansion $\sum\, c_\nu(z-z_0)^\nu$
of a 
regular local branch of an algebraic function
is such that every $c_\nu$ is a rational number, then there exists a
positive integer $k$ so that $k^\nu\cdot c_\nu\in{\bf{Z}}$ for all
$\nu$.
My question to contemporary teaching is whether any
course in mathematics  for beginning graduate students
is suited to present
Eisenstein's theorem. 

\medskip


\centerline {\emph{Measure theory.}}
\medskip

\noindent
An appendix is devoted to 
Lebegue theory and  
Riesz measures.
A major result due to Lebesgue asserts that
every 
non-decreasing and continuous function on the real 
line has a classical derivative outside a null-set.
We  give a detailed proof  which  illustrates
the high standard in classical analysis
and  remark that   "abstract methods"  do not   improve Lebegue's original 
proof. In analytic function theory Lebegue's result 
was used by
Fatou to show
that if $f(z)$
is a bounded analytic function in the unit disc, then
the radial limit $\lim_{r\to 1}\, f(re^{i\theta})$
exists for almost all $\theta$. 
Fatou
used the primitive function $F$ of $f$. Here $F$
has a continuous  extension to the closed disc
and Fatou's  proved that
if the function $F(e^{i\theta})$
of the angular variable has an ordinary derivative at
a point $\theta_0$, then the radial limit 
for $f$ exists at this $\theta$-value.
Later Friedrich Riesz adopted measure theory in a
most succesful manner 
and proved  that there is a 1-1 correspondence between
the class of non-negative Riesz measures $\mu$ on the unit circle $T$ and 
the family of positive harmonic functions $u$ in the unit disc.
More precisely, every such $u$ is the Poisson extension $P_\mu$ of 
a unique non-negative Riesz measure on $T$.
This is proved in Chapter V and
for readers who are less familiar with measure theory
the result by Riesz helps  to "feel  more comfortable"
with   abstract notions of measures, especially 
the  "hidden family" 
of singular Riesz measures
which carry their  whole mass on null sets in the sense of Lebesgue.
\medskip

\noindent
Many subtle results in analytic function theory
are expressed via measures.
An example is a result due to Beurling which
goes as follows: Let $\mu$ be a non-negative Riesz measure on
the unit circle with
no atom at $\theta=0$, i.e. it has no mass at the singleton
set $\{z=1\}$. Let
\[ 
P_\mu(z)=\frac{1}{2\pi}\int\, \frac{1-|z|^2}{|e^{i\theta}-z|^2}\cdot d\mu(\theta)
\]
be Poisson's harmonic extension of $\mu$ to the unit disc.
To each real number $a$ we put
\[
E_a=\{ z\in D\,\colon\, P_\mu(z)\geq \frac{a}{|1-z|}\}
\]
Beurling proved that 
the integral
\[ 
\iint_{E_a}\, \frac{dxdy}{|1-z|}<\infty
\]
At first sight this may appear as an exercise in measure theory. But in § xx
we shall learn that
the proof requires  results
based upon harmonic measures and  estimates using
the theory of 
extremal lengths.
This illustrates that
in order to 
understand measure theory in 
"concrete situations" it is far from sufficient to 
digest some  abstract notions
which interpretate measures as representatives
of linear functionals on spaces of continuous functions.









\bigskip







\centerline {\emph{Series.}}

\medskip
\noindent
Since analytic functions are locally
represented by convergent power series the
study of series is an imporant issue.
In § 2 from Chapter I we start with 
elementary facts about series and 
proceed to  more involved  results.
An example   is a  theorem by
Hardy and Littlewood   which
asserts that if $\{a_n\}$ is a sequence of positive real numbers
such that  there exists the limit
\[
\lim_{x\to 1}\, (1-x)\cdot\sum_{n=1}^\infty\, a_n\cdot x^n=A
\]
then there exists the mean-value limit
\[
\lim_{n\to \infty}\, \frac{a_1+\ldots+a_n}{n}=A
\]


\noindent
The remarkable fact is  that no
other condition than positivity of the $a$-numbers has been imposed.
It is  very instructive to follow  the single  steps in the proof which
are put together in an ingenious fashion.
One might say that the Hardy-Littlewood theorem  
illustrates what analysis
is all about, i.e. \emph{to put small seemingly 
unrelated
threads together.} 
The proof of the  theorem above
is  "elementary" in the sense that
no functional analysis is used.
A case where  functional analysis is used appears in
\emph{Ikehara's Theorem}
which goes as follows: Let
$\mu$ be  a non-negative Riesz measure on $[1,+\infty)$
such that
the integrals 
\[
\int_1^\infty\, x^{-\delta}\cdot d\mu(x)<\infty\quad\text{for all }\quad 
\delta>1
\]
Assume also
that there exists a continuous function $G(u)$ such that
\[
\lim_{\epsilon\to 0}\,
\bigl[\,\int_0^\infty\, x^{iu-(1+\epsilon) }\cdot d\mu(x)-
\frac{A}{\epsilon+iu}\,\bigr]=G(u)
\]
holds uniformly over all bounded intervals $-b\leq u\leq b$.
Then one has the limit formula:
\[ 
\lim_{x\to\infty}\, \frac{1}{x}\int_0^x\,d\mu(t)=A
\]
Let us finish this discussion with
a result  proved by Volterra in 1913.
He considered  an $L^1$-function $K(x)$ supported
by $[0,+\infty)$ and defined the function
\[
\Phi(x)=\sum_{n=1}^\infty\,(-1)^n\cdot K^n(x)
\quad\, K^n(x)\,\, \text{is the n-fold convolution of }\,\, K(x)\,.
\]
The question arises when
$\Phi(x)$ also belongs to $L^1({\bf{R}}^+)$.
To settle this we consider the Laplace transform
\[ 
\hat K(w)=\int_0^\infty\, e^{-wx}\cdot K(x)\cdot dx\,,
\quad\,\mathfrak{Re}\,w\geq 0\,.
\]
Volterra proved that
$\Phi$ is integrable if and only if
\[
\frac{\hat K(w)}{1+\hat K(w)}\neq 0\,\quad\text{for all}\,\,
\quad\,\mathfrak{Re}\,w\geq 0\,.
\]
In 1913 the proof was quite involved.
Today, with the aid of   general results about Banach algebras,
Volterra's result is  an easy exercise
which we explain in the Chapter XX.
So  this example illustrates that  it is  profitable 
to learn    abstract theories.



\bigskip







\centerline {\emph{The use of geometry.}}
\bigskip






\noindent
It is often profitable to employ geometric considerations.
An example is \emph{Poisson's formula}
expressing the values taken by a harmonic function in the unit disc from
its boundary values.
Actually it was Hermann Schwarz,
one of the great pioneers
in function theory, who
established this formula in the context of analytic function theory.
His
geometric description of the Poisson kernel 
leads to  invariance 
properties  for the spherical, respectively
the hyperbolic metric.
An example where geometric considerations appear
in analytic function theory  is   a result due to Julia and Caratheodory
which goes as follows:
\medskip

\noindent
\emph{Let $f(z)= u(x,y)+iv(x,y)$
be an analytic function in the right
half-plane $U=\mathfrak{Re}(z)>0$
whose real part $u$ is a positive function
and satisfies:}
\[
\inf_{x+iy\in U}\, \frac{u(x+iy)}{x}=0
\]
\emph{Then it follows that}
\[
\lim_{x\to +\infty}\, \frac{f(x+iy)}{x}=0
\quad\,\, \text{\emph{uniformly every  sector}}\,\, \{y\leq N\cdot x\}
\quad\colon N=1,2,\ldots
\]
This  is remarkable   since no assumption
is imposed on the imaginary part of $f$.  As we shall see
in XX   the proof of the Julia-Caratheodory theorem
relies upon a general principle for the
spherical measure on domains in
${\bf{C}}$. The  result above was used when Julia studied
iterated maps which   leads to Julia sets and  fractals, a
subject 
which has  become  "fashion" since many
phenomena  can be illustrated
by computers. 
Deeper results arise when geometric ideas and
hard analysis are put together.
An example
is the notion \emph{Carleson measures}
which is essential  in the proofs
of two famous theorems due to 
Lennart Carleson:  The Corona problem and
the interpolation by bounded analytic functions.
These  results
are exposed  in a section from  \emph{Special Topics}
and  may be regarded as a veritable  "high-light" in these notes.

\medskip



\centerline{\emph{Hardy spaces.}}
\bigskip


\noindent
Problems 
in complex analysis has initiated  many results in measure theory
such as in 
studies of Hardy spaces
which appear in many places, foremost in
§ 2-3 from Special Topics.
A result due to
C. Fefferman and E. Stein  asserts that 
a measurable function $f(\theta)$ on the unit circle  has
bounded mean oscillation if and only if the squared length of the
gradient vector
$\nabla(H\uuu f)= (\partial H\uuu f/\partial x,\partial H\uuu f/\partial y)$
of its harmonic extension $H\uuu f(z)$ to the unit disc satisfies:
\[
\frac{1}{h}\cdot \iint\uuu{S\uuu h(\theta)}\, 
|z|\cdot \log\,\frac{1}{|z|}\cdot
\bigl |\nabla(H\uuu f)\bigr |^2\cdot dxdy\leq C
\]
for some constant $C$ and  every $0<h<1/2$, where $S\uuu h(\theta)$
is the subset of $D$ defined by
\[
S\uuu h(\theta)=\{ z=re^{i\phi}\,
\colon 1\vvv h<r<1\,\colon |\phi\vvv \theta|<h\}
\]
This result illustrates how  geometric ideas together with
analytic estimates 
are used to attain deep results.
Another  result which exhibits  the
distinction between absolutely continuous, respectively
singular measures on the unit circle $T$ appears 
in a  closure  theorem due to Beurling.
Every  non-negative 
measure $\mu$ on $T$ gives  a bounded
analytic function
$g(z)$ in the unit disc $D$ defined by
\[ 
g(z)=\exp\,\bigl[-\frac{1}{2\pi}\int_0^{2\pi}\, \frac{e^{it}+z}{e^{it}-z}\cdot d\mu(t)\bigr]
\]
The $g$ -function is quite special. It has no zeros in $D$
and $g(0)=e^{-a}$ where $a=\frac{1}{2\pi}\int_0^{2\pi}\, d\mu(t)$ is a positive constant.
At the same time
$\log|g|$ is the Poisson integral of $-\mu$ and by a result which goes back to
F. Riesz and Fatou this implies that
the radial limit
\[ 
\lim_{r\to 1}\, |g(re^{i\theta})|=1
\] 
exists for almost every $\theta$ in the sense of Lebesgue.
Next, let $H^2(T)$ be the Hardy space whose elements are square integrable functions
on $T$ which are boundary values of analytic functions in $D$.
This is a Hilbert spaces
where the exponential functions
$\{e^{in\theta}\colon n=0,1,2,\ldots\}$
is an orthonormal basis.
One might expect that
multiplication
with $g$ yields a linear operator on
$H^2(T)$ whose range is dense. But this turns out to
be false in general. Beurling proved that
$g\cdot H^2(T)$ is a closed proper subspace of
$H^2(T)$ as soon as the singular part of the  measure
$\mu$
is $\neq 0$.
On the other hand, if $\mu=\phi(t)\cdot dt$ is absolutely  continouos, i.e when
$\phi(t)$ is an $L^1$-function on $T$, then
$g_\mu\cdot H^2(T)$ is a dense subspace of $H^2(T)$.
The proof  appears in 
Section XX and gives an instructive lesson 
since  a mixture of 
measure theory, functional analysis and
analytic function theory appear in the proof.



\bigskip






\centerline {\emph{ A final comment.}}
\medskip


\noindent
My personal  opinion while entering  graduate studies in
mathematics  is that it is  rewarding to pursue  specific proofs
of a more involved nature, rather than to "swallow  
a mass of general 
concepts".
My
favourite example  is due to Carleman.
In
the article [Ca]  it is proved that
there exists an absolute constant $\mathcal C$ with the following property:
\medskip


\noindent
\emph{For every pair $(f,n)$ where $n$ is a positive integer
and $f$
a non-negative real-valued $C^\infty$- function 
defined on  the closed unit interval $[0,1]$
whose  derivatives up to order $n$ vanish at the
two end points,  one has the inequality}
\[
\sum_{\nu=1}^{\nu=n}\,
\,\frac{1}{[\beta_\nu]^{\frac{1}{\nu}}}\leq
\mathcal C\cdot\int_0^1\,f(x)dx\quad\colon\quad
\beta_\nu=\sqrt{\int_0^1\, [f^{(\nu)}(x)]^2\cdot dx}\tag{*}
\]
The remarkable fact is  that $\mathcal C$ is independent of
$n$. 
Carleman's inequality
is sharp in the sense that there exists a constant $C_*$
such that one for every $n\geq 2$ can 
find functions $f_n(x)$ as above so that 
the opposed inequality
(*) holds with $C_*$. Let us remark
that (*) 
demonstrates
that the standard cut-off  functions which
in  many applications 
are used to keep maximum norms of derivatives small up to
order $n$ small are optimal up to a constant.
So the theoretical result in (*)
plays 
a role in numerical analysis where one often uses smoothing
methods.
The ingenious proof  of (*) 
employs
certain  estimates for harmonic measures
applied to the subharmonic Log-function of the absolute value of the
Laplace transform of $f$.

\medskip


\centerline {\emph{An open problem.}}
\medskip

\noindent
Let me finish  by describing an open problem
in the spirit of these notes.
Let $n\geq 2$ and consider a  polynomial
\[
f(z)= a\uuu 0+a\uuu1\cdot  x+\ldots+a\uuu n\cdot z^n
\]
where the sole assumption is that $a\uuu 0$ and $a\uuu n$ both are
$\neq 0$. The coefficients are in general complex numbers.
To each $0<\theta<\pi$
we  count the number of zeros  in
the sector of the complex $z$\vvv plane whose points have argument
in the interval $(\vvv\theta,\theta)$. Denote this integer by $n\uuu f(\theta)$
where  multiple zeros are repeated according to their multiplicities.
By the fundamental theorem of algebra $f$ has $n$ complex zeros and if
$n$ is large one expects that in average 
\[ 
\frac{n\uuu f(\theta)}{n}\simeq \frac{\theta}{\pi}\tag{*}
\]
This "statistical result" is indeed true and goes back to work by Schur.
The search for a more
precise control of the deviation in (*) 
stimulated  further  research.
The following result was proved by
Erdös and Turan in [Annals of math. vol. 51 (1950)]
 

\medskip

\noindent
{\bf{Theorem.}}
\emph{There exists a constant $C^*$ which is independent of $n$
such that the following hold for every $0<\theta<\pi$ and
every polynomial $f$ as above:}
\[
\bigl|\frac{n\uuu f(\theta)}{n}
\vvv\frac{\theta}{\pi}\,\bigr|\leq 
C^*\cdot n^{\vvv 1/2}\cdot \log\, \frac{
|a\uuu 0|+|a\uuu 1|+\ldots+|a\uuu n|}{\sqrt{|a\uuu 0\cdot a\uuu n|}}\tag{*}
\]


\noindent
In § XX we give a proof due to Ganelius 
which
shows that one can take
\[ 
C^*=\sqrt{\frac{2\pi}{\mathcal G}}
\quad\colon\quad \mathcal G= 1+\sum\uuu{\nu=1}^\infty \, (\vvv 1)^\nu\cdot 
\frac{1}{(2\nu+1)^2}\simeq 0,916\ldots
\]
However, this upper bound is not sharp so the question remains if one
can determine the best  constant $C^*$ above, or at least
"as sharp as possible" which eventually only has to  work
for all sufficiently large $n$.
\medskip

\noindent
{\emph{A related problem about Fourier series.}}
The major step to estimate  $C^*$ from above 
stems from
a result about trigonometric polynomials which goes as follows:
Let $H$ and $K$ be  positive real numbers.
Consider all pairs
of finite sequences of real numbers $\{a\uuu k\}$ and 
$\{b\uuu k\}$ indexed by positive integers $k$
such that the following two inequalities hold
for every $0\leq \phi\leq 2\pi$:
\[
\sum\, a\uuu k\cdot \cos\,k\phi+
b\uuu k\cdot \sin\,k\phi\leq K\tag{i}
\]
\[
\sum\, k\cdot (a\uuu k\cdot \sin\,k\phi\vvv
b\uuu k\cdot \cos\,k\phi)\leq H\tag{ii}
\]
\medskip

\noindent
Set
\[
v(\phi)=\sum\, a\uuu k\cdot \sin\,k\phi\vvv
b\uuu k\cdot \cos\,k\phi
\]
\medskip

\noindent
In § XX we expose the following result which is due to T. Ganelius:

\medskip


\noindent
{\bf{B. Theorem.}} \emph
{Put $C\uuu*=2\pi^{\frac{3}{2}}\cdot \mathcal G^{\vvv 1/2}$.
Then
(i\vvv ii) entail that}
\[
\bigl|v(\beta)\vvv v(\alpha)|\leq C\uuu *\cdot \sqrt{HK}
\]
\emph{hold for all pairs $0\leq \beta<\alpha<2\pi$.}
\medskip

\noindent
However, this constant is not sharp so one can   ask for a best constant 
which would improve the choice of  $C^*$ in Ganelius' theorem.


\newpage





\newpage
 
\centerline {\emph{Work by Beurling and Carleman.}}
\medskip

\noindent
Many  results in these notes are
due to Arne Beurling and Torsten Carleman.
This reflects  my personal taste since I regard them
as two of 
the most prominent mathematicians ever in analysis.
Let me first recall  some of Carleman's contributions.
The appendix  devoted to  functional analysis treats
spectral resolutions for unbounded
self-adjoint operators on a Hilbert space
which Carleman established in 1923.
This  
result  has  a wide range of applications.
Carleman also introduced a 
method to handle non-symmetric operators
which admit suitable factorisations in order to 
reduce the spectral analysis to the case of 
symmetric kernels. We describe such a case in § 11 in the appendix devoted to 
functional analysis.
Among   contributions  prior to 1920
one can mention
Carleman's  inequality for the operator norm of resolvents which
is a veritable cornerstone in the spectral theory of linear operators.
He   also used subharmonic
functions to extend
results of the Phragmén-Lindelöf type.
Here is an example. Put $B=\{ 0<\mathfrak{Re}\, z <0\}$ which
is an open and simply connected domain in
${\bf{C}}$. Let $f(z)$ be analytic in
$B$ and for each $0<x<1$ we put
\[
m(x)= \max_y\, |f(x+iy)|\quad\text{and}\quad
\phi(x)= \int_{-\infty}^\infty\, |f(x+iy]|^2\, dy
\]
We assume that these functions  are bounded
on
all intervals $\delta\leq x\leq 1-\delta$ when $\delta>0$ are small.
Phragmén and Lindelöf proved that the function
$\phi(x)$ is convex on $(0,1)$. 
Carleman proved 
that $\phi(x)$
satisfies the differential inequality
\[
\phi''(x)\geq \frac{\phi'(x)^2+m(x)}{\phi(x)}\tag{*}
\]
which in particular gives the convexity.
In § xx we shall give the proof of (*) which employs
the subharmonic function $\log\,|f|$.
\medskip


\noindent
{\emph{Liouville's theorem}}.
Consider  arcs parametrized
by  injective and continuous
 maps $s\to \gamma(s)= x(s)+iy(s)$
from the half-open interval $[0,1)$ in ${\bf{C}}$
where $\gamma(0)=0$ is the origin and
$|\gamma(s)|\to +\infty$ as $s\to 1$.
Let
$\gamma_1,\gamma_2$ be a pair of such arcs
whose sole common point
is the origin and  together give  an unbounded
domain $\Omega$ whose boundary
is the union of the two arcs.
Suppose  that
$f(z)$ is analytic in
$\Omega$ and extends continuously to $\partial\Omega$
with a finite maximum norm
\[
m^*=\sup_{z\in \gamma_1\cup\gamma_2}\, |f(z)|
\]
Since 
we can find $\gamma$-arcs inside $\Omega$ which
tend to inifinity
one cannot
appeal to the ordinary maximum principle and conclude that
the absolute value $|f(z)|$ stays below $m^*$
for all $z\in \Omega$.
However, if the  maximum principle fails then
the function 
\[
\omega_f(\theta)= \max_r\, |f(re^{i\theta)}|\quad\colon re^{i\theta}\in\Omega
\] 
cannot stay too small. Lindelöf gave examples of 
non-constant entire functions $f$
where the $\omega_f$-functions is bounded for all
$\theta$-angles outside a null-set.
By scrutinizing  how these Lindelöf-functions increase, Carleman 
established 
the following 
in the article 
\emph{Sur l'éxtension d'un
theoréme de Liouville}:   
\emph{When the 
$\gamma$-arcs are straight half-lines so that
$\Omega=\{ \alpha<\arg z<\beta\}$
is a sector and 
the maximum principle fails, then one must have a divergent integral}:
\[
\int_\alpha^\beta\ \log\,\log^+\omega_f(\theta)\ d\theta=+\infty
\]
Above a double log-function appears so the
the divergence forces the $\omega_f$-function to be very large in
the avergage.
A proof is given in § XX and in § XX we also expose
an improved version
due to
Beurling where
the pair of $\gamma$-curves are of a more general type than straight lines.







\medskip


\centerline {\emph{Carleman's work on PDE\vvv equations.}}
\medskip

\noindent
The student in analysis is confronted with several disciplines where 
analytic function theory and Fourier analysis is one aspect, and PDE\vvv theory another.
As expected the interaction is close and many results in PDE\vvv theory use
complex methods and Fourier analysis. 
Let us  describe  one of  Carleman's results whose   proof
rely upon methods  from all these disciplines.


\medskip

\noindent
Let $\Omega$ be a bounded open domain in
${\bf{R}}^3$ with a $C^1$\vvv boundary.
We are given a symmetric $3\times 3$\vvv matrix $A(x)$ whose 
elements  $\{a\uuu{pq}(x)\}$ are real\vvv valued continuous functions on the closure
$\bar\Omega$.
Let $b\uuu 1,b\uuu 2,b\uuu 3$ and $c$ be four other real\vvv valued
continuous functions on $\bar\Omega$.
We get the differential operator $L$ acting on $C^2$\vvv functions
$u(x)$   by
\[ 
L(u)= 
\sum\uuu{p=1}^{p=3}\, 
\sum\uuu{q=1}^{q=3}\, a\uuu {pq}(x) \frac{\partial ^2 u}
{\partial x\uuu p\partial x\uuu q} + \sum\uuu{p=1}^{p=3}
\,b\uuu p(x) \frac{\partial u} {\partial x\uuu p}
+c(x)u
\]
Assume that $L$ is elliptic which means that there is a constant $\rho>0$ such that
\[
\min\uuu \xi\, |\,\sum\uuu{p=1}^{p=3}\,  
\sum\uuu{q=1}^{q=3}\, a\uuu {pq}(x)\cdot \xi\uuu p\xi \uuu q\,|
\geq \rho
\] 
where the minimum is taken over all $x\in\bar\Omega$ and every real 
$\xi$\vvv vector of unit length.
Fredholm's classical  theory about integral equations implies
that the  eigenvalues $\lambda$ for which there exists a non\vvv zero function $u$
such that
\[ 
L(u)+\lambda\cdot u=0\quad\text{and}\quad u|\partial\Omega=0
\]
is a discrete set of complex numbers.
When $L$ is symmetric these eigenvalues are real and
tend to $+\infty$ and
results about their  asymptotic distribution were established
by Weyl and Courant.
In the article [Carleman 1936] the asymptotic expansion 
was extended to cover
non\vvv symmetric elliptic operators.
The result from [ibid] goes as follows where we for each
$x\in\Omega$ introduce the non\vvv zero value of the 
determinant of $A(x)$ which  
by the elliptic condition may be taken to be everywhere positive.

\medskip

\noindent
{\bf{Theorem.}}
\emph{Let $|\lambda\uuu n|$ be the absolute value of the
$n$:th eigenvalue  ordered in a non\vvv decreasing sequence.
Then}
\[ 
|\lambda\uuu n|\simeq
 \bigl[\,\frac{1}{6\pi}\int\uuu\Omega\,
 \frac{dx}{\det A(x)}\,\bigr]^{\vvv \frac{2}{3}}\cdot n^{2/3}
\]

 
\noindent
{\bf{Remark.}}
The $\simeq$\vvv sign means that the difference of
the  terms above are of small ordo $n^{2/3}$ as $n\to +\infty$. 
Notice that   the asymptotic formula is the same as in the symmetric case, i.e.
the lower order differentials of $L$ do not affect the asymptotic 
distribution of eigenvalues.
This is no surprise since one can easily show that
even if eigenvalues can be complex, they 
are asymptotically real. More precisely, when
the elliptic operator $L$ is given, then there are positive constants
$c\uuu 1,c\uuu 2$ such that
$\mathfrak{Re}\,\lambda\geq \vvv c\uuu 1$ and
\[
\bigr |\mathfrak {Im}\,\lambda\,|\leq
c\uuu 2\cdot \sqrt{\mathfrak{Re}\,\lambda+c\uuu 1}
\] 
hold for all  eigenvalues.

\bigskip



\centerline {\emph{Work by Arne Beurling.}}
\bigskip


\noindent
Several sections  expose results   by Beurling
which not only offer striking theorems but 
have the merit that the proofs are both highly original and instructive. 
Many of Beurling's   methods 
have led to 
new areas  in analytic function theory, 
harmonic analysis and
potential theory. 
We have not 
tried to include his deepest results which for example appear
in joint articles  with Lars Ahlfors and Paul Malliavin.
For a more detailed account we refer 
to  [Beurling:Collected Works 1-2]
whose   foreword contains 
a very  informative text  written by 
Lars Ahlfors and Lennart Carleson.
A  feature in Beurling's work is the  mixture of
geometric constructions  and "hard calculus".
An example
is the notion 
of extremal distances which
Beurling  introduced in 1929
and applied in  many different situations, foremost to
estimate harmonic measures.
Below follows
a description of  some  major results in his thesis
\emph{Études sur un problème de majoration}
form Uppsala in 1933.
Personally I find Beurling's proofs in [ibid]
utmost  intstructive 
and  transparent. So 
[ibid] constitutes 
a veritable classic in
analytic function theory.
The results below speak  for themselves, though the  less experienced reader may
consider the subsequent material as a "bird's view" 
and whenever necessary 
consult Chapters for  background about  
concepts  which are used without hesitation below.

\bigskip


\centerline{\emph{A. The Milloux problem.}}



\medskip


\noindent
Consider an analytic function $f(z)$ in the unit disc
where $|f(z)|<1$ for all $z$ and suppose there exist some
$\delta>0$ such that
\[
 \min_\theta\, |f(re^{i\theta})|\leq \delta\quad\forall\,\ 0\leq r<1
\] 
\emph{Then it follows that}
\[
\max_\theta\, |f(re^{i\theta})|\leq \delta^{\frac{2}{\pi}\cdot
\arcsin\,\frac{1-r}{1+r}}
 \quad\colon\, 0<r<1 \tag {*}
\]

\noindent
Prior to this result
M.E  Schmidt had proved (*) under the constraint that
there exists a Jordan arc from the origin to the unit 
circle along which
$|f|$ is $\leq \delta$ in which case one  profits upon a suitable 
conformal mapping which in a simllar context had been used by Koebe.
To prove (*) in the general case
Beurling introduced   totally new ideas.

\newpage


\centerline{\emph{Minimum modulus of analytic functions.}}
\medskip

\noindent
Chapter XX in [ibid]
studies
the minimum modulus of an analytic function.
When $f(z)$ is analytic in a disc $\{|z|<R\}$
we set
\[
m_f(r)= \max_{|z|= r}\, |f(z)|\quad\colon\, \mu_f(r)=
 \min_{|z|= r}\, |f(z)\quad\colon 0<r<R
\]


\noindent
The following  is proved in [ibid: page 94]:

\medskip

\noindent
{\bf{Theorem.}}
\emph{Let $0<r_1<r_2<R$ and 
$\alpha>0$ satisfies 
$0<\alpha\leq m_f(r_1)$. Then}
\[
\int_{r_1}^{r_2}\, \chi(\{\mu_f\leq \alpha\} \cdot \log r\, dr \leq
\log 4+2 \int_{r_1}^{r_2} \,\log\log \frac{m_f(r)}{\alpha}\, dr\tag{**}
\]
\emph{where 
$\chi(\{\mu_f\leq \alpha\})$ is the characteristic function of the set
where $\mu_f(r)\leq\alpha$.}
\medskip


\noindent
{\bf{Remark.}}
In the article [xxx] from 1933
Nevanlinna found another proof of (*) above 
which has the merit that
it  consolidates why  (*) is sharp.
Using the constructions by Nevanlinna, Beurling
could then  demonstrate that
the inequality  (**) gets sharp when $\alpha$ tends to zero
which
is the interesting part of (**) above.
\medskip

\centerline{\emph{Upper bounds for harmonic measures}}
\medskip

\noindent
 Let
$D$ be a simply connected domain and $\gamma\subset\partial D$
a subarc.
If $z\in D$ we denote by $r(z;\partial D)$, resp. $r(z,\gamma)$ the euclidian 
distance from $z$
to the boundary and to $\gamma$ respectively.
With these notations Theorem III : page 55 in [ibid] asserts that
\[
\mathfrak{m}(D,\gamma;z)\leq
\frac{4}{\pi} \cdot \arctan\,\sqrt{\frac{r(z,\partial D)}{r(z,\gamma)}}\tag{***}
\]
where the left hand side is the harmonic measure at $z$ with respect to
$\gamma$. Examples show that
this upper bound is sharp.
Next,  an inequality, which in a slightly weaker form
was established in Beulring's thesis to 
demonstrate 
the Denjoy conjecture, 
was  refined later in the  article [xx] from 1940
and goes as follows:
Let $\Omega$ be a Jordan domain
and  $\omega\subset\partial\Omega$
a sub-arc of its boundary. Let $z_0\in\Omega$ and suppose there exists a
positive harmonic function $\psi$ in $\Omega$ satisfying:
\[
\psi(z_0)=0 
\quad\colon 
A=\iint_\Omega\, |\nabla(\psi)|^2\, dxdy<\infty
\]

\medskip

\noindent
{\bf{Theorem.}}
\emph{Set $\min_{z\in\omega}|, \psi(z)=L$. Then one has the inequality}
\[
\mathfrak{m}(\Omega;\omega)(z_0)\leq
e^{-\pi\cdot \frac{L^2}{A}}
\]


\medskip

\noindent
{\bf{Remark.}}
A detailed proof 
appears in
section §§ from Special Topics.

\bigskip


\centerline {\emph{Regular points for the Dirichlet problem.}}
\medskip

\noindent
Sections in [ibid:page 63-69]
are devoted to Dirchlet's problem. Let $\Omega$ be an open 
subset of
${\bf{C}}$.
If $f$ is a real-valued and continuous function on
$\partial\Omega$ it can be extended to some
$F\in C^0(\bar\partial\Omega)$.
Now $\Omega$ can be exhausted by an increasing sequence of subdomains
$\{\Omega_n\}$ for which the Dirichlet problem is solvable. Such exhaustions were
considered by Lebesgue
and explicit constructions
were given by de Vallé Poussin in 1910.
To each $n$ we find the harmonic function $H_n$ in $\Omega_n$
which solves the Dirichlet problem with boundary
values given by the restriction of $F$ to $\partial\Omega_n$.
In Chapter V we prove Wiener's result
that the sequence $\{H_n\}$ converges to a unique  harmonic function
$W_f$ in $\Omega$ which is independent of the chosen
exhaustion. One refers to $W_f$ as Wiener's generalised solution.
A boundary point $z_0$ is called regular if
\[
\lim_{z\to z_0} W_f(z)= f(z_0)\quad\colon\forall\, f\in C^0(\partial\Omega)
\]

A criterion for
a boundary point to be
regular was established by 
Boulignad in 1923. Namely,
a boundary point $z_0$ is regular if and only if there
exists a positive harmonic function $V$ in $\Omega$ such that
\[
\lim_{z\to z_0} V(z)=0
\]
This condition is rather implicit
so one seeks geometric properties to
decide if a boundary point is regular or not.
In [ibid] Beurling established a sufficient regularity condition which 
goes as follows:
Let $z_0\in\partial \Omega$
and for a given $R>0$ we consider the
circular projection of
the closed complement of $\Omega$ onto the real interval $0<r<R$
defined by:
\[ 
E_\Omega(0,R)=\{ 0<r< R\,\colon\,\exists
\,\, z\in \{|z-z_0|=r\}\cap {\bf{C}}\setminus \Omega\}
\]
Following Beurling one
 says that $z_0$ is logarithmically dense  (Point
frontière de
condensation logarithmique)
if the integral
\[
\int_{E_\Omega(0,R)}\, \log r\, dr=+\infty\tag{1}
\]
Beurling proved that if (1) is divergent
then $z_0$ is a regular boundary point.
The proof relies upon an inequality which has  independent interest.
Here is the situation considered in [ibid: page 64-66]:
Let $\Omega$ be an open set - not necessarily connected and
$R>0$ where $\Omega$ is general contains points of absolute value $\geq R$.
Consider a harmonic function $U$ in $\Omega$ with the following properties:
\[ 
\limsup_{z\to z_*}\, U(z)\leq 0\quad\colon \,
z_*\in \partial \Omega\cap \{|z|\leq R\}\tag{i}
\]
\[
U(z)\leq  M\quad\colon\, z\in \{|z|=R\}\,\cap D\tag{ii}
\]

\medskip
\noindent{\bf{Theorem.}}
\emph{When (i-ii) hold one has the inequality below for every
$0<r<R$}
\[
\max_{z}\, U(z)\leq 2M\cdot\, e^{-\frac{K}{2}}
\]
\emph{where the maximum in the left hand side
is taken over $\Omega\cap \{r<|z|<R\}$
and}
\[ 
K=\int_{E_\Omega(r,R)}\, \log r\, dr
\]





\bigskip





\centerline{\emph{Extremal length.}}
\medskip


\noindent
Let us first cite
Beurling
where he gives the following
attribute to original work
by Poincaré:
\emph{Rappelons que dans la 
théorie des fonctions analytiques, on a introduit
des élements géometriques non euclidiennes, invariants
par rapports a certaines transformation, et
cela surtout pour simplifier la thérie dont il s'agit}.
In his 
lecture at the Scandinavian Congress in
Copenhagen 1946, Beurling describes in more detail 
the  usefulness of
extremal
lengths.

\medskip

\noindent
\emph{In geometric function theory one often tries to
characterize or determine a certain mapping or quantity by
an extremal property. The method goes back to Riemann
who introduced variational methods in function theory in the form of
Dirichlet's principle. When you want to characterize
a function by an extremal property , then the class of competing functions
is very important. The wider you can make this class the more you can say
about the extremal function 
and the easier it becomes to find
good majorants or minorants, as the case may be.}




\medskip

\noindent
In his thesis
Beurling defined  an extremal distance between
pairs of points $z_0,z_1$ in  simply conected domains $\Omega$
with a finite area. The construction goes as follows:
First 
the interior distance 
is defined by
\[
\rho(z_0,z_1;\Omega)= \inf_\gamma\, \int_\gamma\, |dz|
\]
where the infimimum is taken over
rectifiable
Jordan arcs which
stay in $\Omega$ and join the two points.
Set
\[
\lambda_*(z_0,z_1;\Omega)=\sqrt{\frac{\pi}{\text{Area}(\Omega)}}|\cdot
\rho(z_0,z_1,\Omega)
\]
One refers to $\lambda_*$
as  the reduced distance. It is
not a conformal invariant and to  overcome this default
Beurling considered
the family of \emph{all triples} $(\Omega^*,z_0^*,z_1^*)$
which are conformally equivalent
to the given triple, i.e. 
there exists a conformal mapping $f\colon \Omega\to \Omega^*$
such that $f(z_\nu)= z_\nu^*$.
The \emph{extremal distance} is now defined by
\[
\lambda(z_0,z_1;\Omega)=
\sup\, \lambda_*(z^*_0,z^*_1;\Omega^*)
\]
with the supremum taken over all equivalent 
triples.
By this construction $\lambda$ yields a conformal invariant.
Next, consider
a 
triple $(z_0,z_1, \Omega)$
is the  Green's function $G(z_0,z_1;\Omega)$.
Recall that $G$ is a symmetric function of the pair $z_0,z_1$
and keeping $z_1$ fixed
\[ 
z\mapsto  G(z,z_1;\Omega)-\log\, \frac{1}{z-z_1|}
\]
is a harmonic function
$\Omega$ which is zero on
$\partial\Omega$.
In [ibid: Théorème 1: page 29] the following fundamental result is proved:

\medskip

\noindent
{\bf{Theorem.}}
\emph{For each triple $(z_0,z_1;\Omega)$ one has the equality}
\[ 
e^{-2G}+e^{-\lambda^2}=1\tag{*}
\]


\noindent
\emph{About the proof.}
By conformal invariance it suffices to prove the equality 
for a triple $(0,a,D)$ where $D$ is the unit disc
where  the pair of points is the origin and a real point $0<a<1$.
In this case
\[
G=\log\,\frac{1}{a}
\]
Hence the theorem amounts to prove the equality
\[ 
e^{-\lambda^2}= 1-a^2
\]
or equivalently that
\[
\lambda^2=\log\,\frac{1}{1-a^2}\tag{*}
\]
We will show (*) in § XX.
The equation  has several applications but at this monent
we refrain form
discussing more details.
 








\medskip

\centerline{\emph{General extremal metrics.}}
\medskip

\noindent
Ten years later Beurling realised the need for a
more extensive class of extremal distances which
can be applied for domains  which are not 
simply connected. The  constructions below appear in 
the section  \emph{Extremal Distance and estimates for Harmonic Mesure}
[Collected work. Vol 1. page 361-385].









\medskip

\noindent
\emph{The numbers 
$\lambda(E,K;\Omega)(z_0).$}
Let  $\Omega$ be a Jordan domain in the complex $z$-plane
and consider a pair of sets $E,K$
where
$E\subset\partial \Omega$ and $K$ is a compact subset
of $\Omega$. To a point 
$z_0\in\Omega\setminus K$
we introduce the family $\mathcal J(E,K;z_0)$ of  rectifiable Jordan
arcs $\gamma$ with the following properties:
Apart from its end-points 
$\gamma$ stays in
$\Omega\setminus K$ and  passes through  $z_0$. Moreover, the end-points
of $\gamma$ divides  the Jordan curve $\partial\Omega$
into a pair of closed intervals $\omega_1$ and
$\omega_2$ and the last constraint on $\gamma$
is that
$E$
is contained in one  of these $\omega$-intervals.
Notice that neither $K$ or $E$
are assumed to be connected.
Next, let $\mathcal A$ be the family of positive and continuous
functions $\rho$ in $\Omega$ for which the squared area integral
\[ 
\iint_\Omega\, \rho^2(x,y)\,dxdy=1
\]
To each such $\rho$-function we set
\[
L(\rho)=\inf_{\gamma\in\mathcal J}\int\,  \,\rho(z)\,|dz|\tag{*}
\]
where we for simplicity  put
$\mathcal J= \mathcal J(E,K;z_0)$.
 The extremal distance between
$E$ and $z_0$ taken in
$\Omega\setminus K$ is  defined by
\[ 
\lambda(E,K;\Omega)(z_0)= \sup_{\rho\in\mathcal A}
\,L(\rho)\tag{**}
\]


\noindent
These  $\lambda$-numbers are conformal invariants.
More precisely, let 
$(E^*,\Omega^*,K^*)$ be  another triple and 
$f\colon \Omega\setminus K\to \Omega^*\setminus K^*$
is  a conformal mapping
which extends 
continuously   to   the boundary and
gives a homeomorphism
between the closed Jordan arcs
$\partial\Omega$ and $\partial\Omega^*$ where $E^*=f(E)$.
Then one has the equality
\[
\lambda(E,K;\Omega)(z_0)=\lambda(E^*,K^*;\Omega^*)(f(z_0))
\]




\noindent
Consider  a triple $(E;\Omega,K)$ as above
and when $z_0\in\Omega\setminus K$ there exists
the harmonic measure
$\mathfrak{m}(E;\Omega,K)(z_0)$.

\medskip

\noindent
{\bf{Theorem.}}
\emph{For every  triple $E;\Omega,K)$ and each
$z_0\in\Omega\setminus K$ 
where  $\lambda(E;\Omega,K)(z_0)\geq 2$ 
one has the inequality}
\[
\mathfrak{m}(E;\Omega,K)(z_0)\leq
3\pi\cdot e^{-\pi\cdot \lambda(E;\Omega,K)(z_0)}
\]


\noindent
This result  is often used to
estimate harmonic measures. The point is
that in the right hand side we can use
$\rho$-functions which need
not maximize the
$L$-functional in (**) and since $L(\rho)\leq\lambda(E;\Omega,K)(z_0)$
one has  in particular
\[
\mathfrak{m}(E;\Omega,K)(z_0)\leq
3\pi\cdot e^{-\pi\cdot L(\rho)}
\]
Examples in § XX  demonstrate the usefulness of such
majorisations. 
\medskip

\noindent
{\bf{The simply connected case.}}
Here $\Omega$ is  a Jordan domain 
and  $K=\emptyset$. Consider
a pair of closed subsets
$E$ and $F$ in $\partial\Omega$
which both are   a finite unions of closed subintervals.
Denote by  $\mathcal J(E,F)$  the family of
Jordan arcs $\gamma$ with
one end-point in $E$ and the other in $F$
while the interior stays in $\Omega$. Set
\[
\lambda(E;F:\Omega)=
\max_\rho\min_{\gamma\in\mathcal J}\,
\,\int_\gamma \, \rho\cdot d|z|\quad\colon\,\rho\in\mathcal A
\]
This yields  a conformal invariant which can
be determined under the extra condition that the sets
$E$ and $F$ are \emph{separated} which means
that
there exists a pair of points $p,q$ in $\partial \Omega\setminus E\cup F$
which divide $\partial \Omega$ in two intervals where $E$ belongs to one
and $F$ to the other.
Under this condition one has the equality
\[
\lambda(E;F:\Omega)=\mathcal{NS}(E;F:\Omega)\tag{1}
\]
Here  $\mathcal{NS}(E;F:\Omega)$ is  the Neumann-Schwarz number associated
to the triple $(E,F;\Omega)$ which is    found as follows:
Let $u$ be the 
harmonic function in
$\Omega$ with boundary values
$u=1$ on $E$ and 
zero on $F$ while the normal derivative
$\frac{\partial\phi}{\partial n}=0$ on $\partial\Omega\setminus E\,\cup F$.
If $v$ is the harmonic conjugate
then $v$ is increases on $E$ and decreases on $F$
and when  $v$ is normalised so that
the range $v(E)$ is an interval $[0,h]$ it follows that
$f=u+iv$ is a conformal mapping from
$\Omega$ onto a rectangular slit domain:
\[ 
\{0<x<1\}\times \{ 0<y<h\}\cup S_\nu 
\] 
where $\{S_\nu\}$ are horizontal intervals directed   into the rectangle
and with end-points on one of the vertical sides
$\{x=0\}$ or $\{y=0\}$. See  § XX for a figure.
The Neumann-Schwarz number is given by
\[
\mathcal{NS}(E,F;\Omega)=\frac{1}{\sqrt{h}}
\]
In § xx we prove that it is a conformal invariant which reduces
the proof of (1) to the case when
$\Omega$ is a rectangle as above with some removed
spikes while $E$ and $F$ are the opposed vertical lines.
If  $\rho^*$ is the constant function
$\frac{1}{\sqrt{h}}$ the fact that horisontal straight lines minimize
arc-lengths when we move from $E$ to $F$ imply that
\[ 
L(\rho^*)=\frac{1}{\sqrt{h}}\tag{2}
\]
On the other hand, let $\rho\in\mathcal A$ be non-constant.
Now
\[
0<\iint_\Omega\, (\rho-\frac{1}{\sqrt{h}})^2dxdy=2-\frac{2}{\sqrt{h}}\iint_\Omega \rho\, dxdy\implies
\iint_\Omega \rho\, dxdy<\sqrt{h}
\]
It follows that
\[
\min_{0\leq y\leq h}\, \int_0^1\,\rho(x,y)\,dx<\frac{1}{\sqrt{h}}
\]
In the left hand side appear competing $\gamma$-curves and hence
\[ 
L(\rho)<\frac{1}{\sqrt{h}}
\]
This proves that $\rho^*$ maximizes the $L$-function and 
the equality (2) entails (1).

\medskip







\noindent
{\bf{Another inequality.}}
Let $\Omega$
be a bounded and connected
domain whose boundary consists of a finite family of disjoint closed Jordan
curves $\{\Gamma_\nu\}$. Consider a pair $(z_0,\gamma)$
where $z_0\in\Omega$ and $\gamma$ is a Jordan arc
starting at $z_0$ and with
an end-point $p$ on one
boundary curve, say
$\Gamma_1$.
Next, let $K$ be a compact subset of
$\Gamma_1\setminus\{p\}$.
For each point $z\in \gamma$ we get the harmonic
measure
$\mathfrak{m}_K(z)$
which is the value at $z$ of the harmonic function in
$\Omega$ whose boundary values are one on $K$ and zero in
$\partial\Omega\setminus K$.
Set
\[ 
h^*(K,\gamma;z_0)= \max_{z\in\gamma}\, \mathfrak{m}_K(z)
\]
The  interpretation
is that one seeks a point $z\in\gamma$ where the probability for
the Browninan motion which starts at $z$
and escapes at some point in $K$
before it has reached points in
$\partial\Omega\setminus K$,
is as large as possible.
An upper bound
of $h^*$ is found using the notion of extremal length. Namely,
let
$\lambda(K;\gamma)$ be the extremal length for  the family of
curves in $\Omega$
with one end-point in $K$ and the other on
$\gamma$. Then Beurling proved that
\[
h^*(K,\gamma;z_0)\leq 5\cdot e^{-\pi\cdot \lambda(K;\gamma)}\tag{*}
\]
\medskip

\noindent
{\bf{Remark.}}
In  random walks under a Brownian motion the inequality above
shows that if $K$ is a  large obstacle
and $\gamma$ small, then the $h^*$-function
can be majorised if
some lower bound for
the extremal length can be proved. This is of interest
in configurations
with "narrow channels" when one seeks
paths  out to the boundary and 
illustrates a typical  application of extremal lengths.

\bigskip






\centerline{\bf{On quasianalytic series.}}
\medskip

\noindent
Let us finish with   a  result which
illustrates
Beurling's vigour in "hard analysis". The theorem below was presented
in a lecture  at the
Scandinvian congress in Helsinki 1938.
A closed subset
$E$ of ${\bf{C}}$ has positive    perimeter if 
there exists a positive constant $c$ such that
\[
\sum\ell(\gamma_\nu)\geq c
\] 
hold for every denumerable famly of
closed and rectifiable Jordan curves
$\{\gamma_\nu\}$
which surround $E$, i.e. $E$ is contained in the union of the
associated open Jordan domains.
Let $\{\alpha_k\}$ 
be a sequences of distinct complex numbers
and $\{A_k\}$  another sequence  sequence such that
\[
\sum\, |A_k|<\infty\tag{i}
\]
 Set
\[ 
F(z)= \sum\,\frac{A_k}{z-\alpha_k}\tag{*}
\]
To each $k$ we put $r_k= |A_1|+\ldots |A_k|$ and
define  $\mathcal E_f$ by
\[
 \mathcal E_f=\{ z\in{\bf{C}} \quad\colon\,
\sum_{k=2}^\infty\, \frac{A_k}{\sqrt{r_{k-1}}} \cdot \frac{1}{|z-\alpha_k|} <\infty\}
\]
It is easily seen that (i) entails that
the complement of $\mathcal E_f$ is a null set in
${\bf{C}}$. 
One says that
(*) is quasi-analytic if $F(z)$ cannot vanish 
on a closed subset $E$ of $\mathcal E_F$ with positive perimeter.
The following was proved in [ibid];
\medskip

\noindent
{\bf{Theorem.}}
\emph{The series (*) is quasi-analytic in the sense above if}
\[
\liminf_{n\to \infty}\,r_n^{\frac{1}{n}}<1
\]
In § XX we  expose some  steps in the proof based upon
some remarkable inequalities
for 
rational functions.




\newpage



\centerline{\emph{A  final comment}}
\medskip

\noindent
Carleman and Beurling  studied
at Uppsala University, where Carleman entered in 1911 and Beurling in 1924.
Both had 
Erik  Holmgren and Anders Wiman as teachers
and to this one can add that  as young
researchers they  also met Ernst Lindelöf whose classic text-book
\emph{Théorie des Residues} from 1907
was studied at an early stage by them both.
The  major contents in Beurling's Ph.D-thesis
was  already written in 1929 and presented  on November 4 1933.
At that time
 Carleman had   served during  five years as director at
Institute Mittag-Leffler.
In the period 1933-1937 
Beurling  attended Carleman's lectures at
the Mittag-Leffler institute and  got 
considerable  inspiration from this.
One can mention Carleman's lectures about the generalised Fourier transform in
1935
and  refined versions of Ikehara's theorem and other  Tauberian results.
A few years later 
Beurling   proved Tauberian theorems with
remaineder terms.
There was never a "competetive situation" 
during the years
when  Beurling
prepared his application for the chair  at Uppsala University
replacing  Homgren after his retirement   in 1937.
On the contrary, preserved
letters between Carleman and Beurling
show that
they esteemed  each others work.
For example, in his thesis Beurling
inserted the following comments upon Carleman's
new proof from 1933 of the Denjoy conjecture 
with a sharp bound $2n$ for entire functions of order
$n$:
\emph{Plus récemmment 
M. Carleman en perfectionnant sa méthode initiale 
est arrivé au resultat $\leq 2n$ d'une manière fort élegante}.
Beurling's  proof from 1929
has like Carleman's proof the merit
that it
can be adapted to other cases than
asymptotic values.
An example is the following
remarkable result from his thesis:

\bigskip

\noindent
{\bf{Theorem}}
\emph{Let $f(z)$ be a bounded analytic function in
the half space
$\mathfrak{Re}\, z>0$. Set}
\[ 
\mu(r,f)= \min_
{-\pi/2<\theta<\pi/2}\ |f(re^{i\theta})|
\]
 
\noindent
\emph{Then
$f$ converges uniformly to zero 
in
every sector $-\pi/2+\delta\leq\theta\leq \pi/2-\delta$
under the condition that}
\[
\lim_{r\to\infty}\ \mu(r,f)=0
\]

\medskip

\noindent
Carleman's last major article
At the end of 1930:s Carleman's health became weak and from this 
time Beurling
took 
the leading role in Swedish mathematics. 
His work after 1940 contains
a wealth of new results where one may mention his ingenious idea to
relate inner functions in the unit disc with closed subspaces of the Hilbert space
$H^2(T)$ which are invariant under multiplication with $z$.
While reading articles from their  collected work
I always get fascinated by the
transparency  and 
generality while they
announce and prove deep results.
I can only hope that
the sections in these notes which expose
material from their work 
may inspire readers to continue  studies 
of articles by these  eminent mathematicians.





\newpage




\centerline{\bf{The use of computers.}}
\medskip

\noindent
Today's  student 
is confronted with another
world than in the past since
computers offer
numerical solutions
and provide
figures which 
can be illustrated in a mobile way.
This is a veritable
revolution and one may even  ask
if   traditional text-books in mathematics are out-dated.
Hopefully the answer is a compromise, i.e.
pure theory should help
to create more accurate computer programs and
conversely computers   contribute to
new theoretical discoveries.
Apart from the standard programs \emph{Matlab, Mathematica} and \emph{ Maple}
we recommend
the
excellent programs delivered by \emph{Comsol}. Here
refined numerical mathematics has been
developed during the last decade 
which in particular  are suitable for  numerical solutions to non-linear
PDE:s. 
The computer offers accurate numerical solutions to both linear and
non-linear
boundary value problems. 
An example
is the boundary value problem where one seeks a function $u(x,y)$ in the open
unit disc which satisfying  the non-linear PDE-equation
\[ 
\Delta(u)+ u(u-1)
\] 
and  a boundary condition 
\[
u(e^{i\theta})= P(\theta)
\] 
where $P$ for example is a trigonometric polynomial  
$A\cos^\theta+\sin^2\theta$ for some positive constant $A>1$.
 The solution $u$
 will
 be subharmonic in the region $\{u<1\}$ while it is super-harmonic in
 $\{u>1\}$.
To find critical points in the open disc where the gradient vector
$\nabla(u)=(0,0)$ one must rely upon the numerial solutions
based upon  the computer's efficency to solve non-linear PDE-equations by
the method of finite elements in fine grids.






\newpage









\centerline{\emph{Contents of special subsections}}

\bigskip


\noindent
\emph{0.1 The isoperimetric inequality.}

\medskip

\noindent
\emph{0.2 Neumann's boundary value problem.}\medskip

\medskip

\noindent
\emph{0.2.1  Comments by Beurling about the Helmholtz equation}

\medskip

\noindent
\emph{0.2.2  Calculus of variation.}

\medskip


\noindent
\emph {0.3 Hadamard's extension theorem.}\medskip

\noindent
\emph{0.4 The role of
inequalities.}
\medskip

\noindent
\emph{0.4.1 Distributions of zeros of polynomials.}
\medskip

\noindent
\emph{0.4.2 Infinite systems of linear equations}
\medskip

\noindent
\emph{0.4.3 The heat equation.}







\medskip

\noindent
\emph{0.5 Why one should study complex analysis}

\medskip

\noindent
\emph{0.6 Jensen's formula and logarithmic potentials.}


\medskip

\noindent
\emph{0.7 Riemann's $\zeta$-function}

\medskip

\noindent
\emph{0.8 Kepler's equation and Lagrange's problem}

\medskip

\noindent
\emph{0.9 The Dagerholm series and comments on more recent theories}

\medskip

\noindent
\emph{0.10 Mathematical physics and boundary value problems}

\medskip

\noindent
\emph{0.11 The use of computers.}

\medskip

\noindent
\emph{0.12 Acknowledgent: Work by Beurling and Carleman}



\newpage









\centerline{\emph{0.1 The isoperimetric inequality.}}
\medskip


\noindent
Many
problems which from the start are
given in a real context are solved via   complex analysis.
An example is the isoperimetric inequality which asserts that if
$C$ is a simple closed curve
in ${\bf{R}}^3$ of length $L$, then
the area of the minimal surface
bordered by $C$ is majorized by
$\frac{1}{4\pi}\cdot L^2$ and equality holds only if
$C$ is a planar circle.
The proof  relies upon  a result  established by
Weierstrass in 1861 which shows that every
minimal surface is parametrized via an  
analytic function defined on a simply connected domain.
More precisely, let $M$ be  the minimal surface bordered by $C$
and $(x,y,z)$ denote coordinates
in ${\bf{R}}^3$. After a
change of variables which includes  sterographic projection
and Riemann's  conformal mapping theorem, 
Weierstrass proved  there exists an analytic function $F(u)$ defined in the
open unit disc $D$ where $u$ is the complex coordinates
such that points $(x,y,z)$ in $M$
are given by
the equations
\[
x=\mathfrak{Re}\int_0^u\, (1-\zeta^2)F(\zeta)d\zeta\,
\colon\, 
y=\mathfrak {Re}\int_0^u\, i(1+\zeta^2) F(\zeta)d\zeta\,\colon
z=\mathfrak {Re}\int_0^u\, 2\zeta F(\zeta)d\zeta
\]
From this
the sharp isoperimetric inequality boils down to prove
the following inequality for every pair of analytic functions $f,g$ in the unit disc:
\[
\iint_D\, |f(z)|\cdot |g(z)|\, dxdy\leq
\frac{1}{4\pi}\, \int_0^{2\pi}\, |f(e^{i\theta})|\, d\theta\cdot
 \int_0^{2\pi}\, |g(e^{i\theta})|\, d\theta\tag{*}
 \]
That (*) holds was demonstrated by Carleman in an article from 1921.
One reason that Weierstrass himself did not
find the sharp isoperimetric inequality might  be
that the Blaschke-Jensen factorization was not known until 
1910.
In  § XX from Special Topics we shall learn that this 
factorisation leads to the proof of
(*).
\medskip

\noindent
Another example of an
isoperimetric inequality 
related to function theory goes as follows:
Let $r(z)= \frac{p(z)}{q(z)}$ be a rational function where 
the polynomials $p,q$ have no common root.
No hypothesis is imposed on their degrees.
Let $D=\{|z|<1\}$ be the open unit disc
and for each real number $t$
we put
\[ 
D_r(t)=\{ z\in D \,\colon\, |r(z)|<t\}
\]
The boundary of $D_r(t)$ is a union of Jordan arcs and
some  finite set of corner points. In this family occur 
subarcs of the unit circle. Denote by
$\lambda_r(t)$  the sum of their
lengths while 
$L_r(t)$ is the sum the lengths of the boundary arcs  contained
in
$D$.
With these notations one has the inequality
\[
L_r(t)\geq 2\sin\,\frac{\lambda_r(t)}{2}\tag{*}
\]
In §§ we shall prove (*) together with
other inequalities about rational functions which are due to Beurling.
Here geometry, variational inequalities and analytic function theory appear in a most fruitful manner.








\newpage


\centerline{\emph{0.2 Neumann's boundary value problem.}}
\medskip

\noindent
In the  pioneering article
\emph{Untersuchungen über das Logarithmische und Newtonsche Potential}
from 1877, Gustav Neumann  
introduced 
operator-valued meromorphic series
to
solve the
boundary value problem
\[
\frac{\partial U}{\partial {\bf{n}}_*}(p)= h(p)\cdot U(p)+f(p)\tag{1}
\]
where $\Omega$ is a bounded domain in
${\bf{R}}^3$, 
$U$ is  harmonic in $\Omega$
and (1)  hold for points $p$ on the boundary
and
$\frac{\partial U}{\partial {\bf{n}}_*}$ denotes the inner normal derivative.
Above $h$ is assumed to be a positive continuous function on
$\partial\Omega$ while $f$ is an arbitrary real-valued continuous function.
Neumann proved existence and uniqueness  for each such pair $(h,f)$
when $\Omega$ is a
bounded and strictly  convex domains with
a $C^2$-boundary.
His work was later resumed by
Poincaré whose article 
[Acta:20: 1897 ]
\emph{La méthode de Neumann et le problème de Dirichlet}
where existence and uniqueness was proved
under the solve assumption that
$\partial\Omega$ is of class $C^2$, i.e. the convexity 
assumption is not neeeded.
In § xx we shall consider neumann's boundsry value problem in dimension two
while the 3-dimensional case is treated in § xx.
\medskip


\noindent
{\bf{The inhomogeneous Laplace equation.}}
We discuss the 2-dimensional case where
$\Omega$ is a connected and bounded
bounded domain in
${\bf{R}}^2$
whose boundary
is a finite union of pairwise disjoint and differentiable
closed Jordan curves.
Under this condition the Diriclhet probelm is sovlable, i.e., for
every
$h\in C^0(\partial\Omega)$ there exists a unique harmonic function
$H$ in $\Omega$ whichextends to a continuous function on the closure and
$H=h$ on $\partial\Omega$.
This will be proved in § xx from Chapter V.
In particular we take a point $p\in\Omega$
and find the harmonic function
$H_p(q)$ in $\Omega$ such that
\[ 
H_p(q)= \log \, |p-q|\quad\colon q\in \partial\Omega
\]
The Greens' function 
is 
defined for pairs $(p,q)$ in
in $\Omega\times\Omega$ with $p\neq q$ by
\[
 G(p,q)=\log\,\frac{1}{|p-q|}- H_p(q)
\]
In § xx from Chapter V we prove that
$G$ is symmetric, i.e. $G(p,q)= G(q,p)$.
Next one gets a nintegral operator
$\mathcal G$
defined by
\[
\mathcal G_f(p)= 
\frac{1}{2\pi}\cdot \int_\Omega\,
G(p,q)\cdot f(q)\, dq
\]
So above $q=(x,y)$ and $dq=dxdy$.
For each fixed $p\in\Omega$ the function
$q\mapsto   G(p,q)$ is integrable over
$\Omega$ and from this we shall learn that
(x) is defined for fun cions
$f\in L^2(\Omega)$, i.e.
complex-valued square integrable functions in the sense of Lebesgue.
Moreover one easily verifies that 
\[
\iint_{\Omega\times\Omega}\, |G(p,q)|^2\, dp dq<\infty
\]
It means that
$\mathcal G$ is a Hilbert-Schmidt  operator and
in particular compact.
Next, we can apply the Laplce operator and a crucial resut is
that
for every $f\in L^2(\Omega)$ it holds that
$\Delta(\mathcal G_f)$ exists in the distribution sense
and is equal to $-f$ in the Hilbert space
$L^2(\Omega$, i.e. one has the operator equation
\[
\Delta\circ \mathcal G=-E
\] 
where $E$ is the identity operator on $L^2(D)$.
In §§ we shall learn that
$L^2(\Omega$ has an orthonormal basis
$\{\phi_n\}$ where
\[ 
\frac{1}{2\pi}\cdot \int_\Omega\,
G(p,q)\cdot \phi_n(q)\, dq=\lambda_n^{-1}\cdot \phi_n(p)
\]
and $\{\lambda_n\}$ is a non-decreasing sequence of positive real numbers
which tend to $+\infty$ as  $n\to\infty$.
From (x) we see that (xx) means that
\[ 
\Delta(\phi_n)+\lambda_n\cdot \phi_n=0
\] 
holds in $\Omega$. Moreover, by the construction of
$\mathcal G$ 
one verifies that
each   
$\phi_n$
extends to a contionuous function on
the closure with boundary value equal to zero.
\medskip


\noindent{\bf{Asymptotic results.}}
The resuts above are due to Neumann and Poincaré and sved as a model in
more general studies 
of integral operatoes by Fredholm
and Hilbert.
A regined study of the asymptotic
behaviour  of the eigenvalues $\{\lambda_n\}$
was later established by Weyl who proved the following limit formula
for every domain
$\Omega$ as above:
\[
 \lim_{n\to\infty}\, \frac{\lambda_n}{n}= 
\frac{4\pi}{\text{area}(\Omega)}\tag{*}
\]

\medskip

\noindent
Using some further refinements in
Weyl's proof and a general Tuaberian theorem due to Wiener
the following result was proved by Carleman:
\medskip

\noindent
{\bf{Theorem.}}
\emph{ For each $p\in\Omega$ one has}
\[
\lim_{n\to\infty}\,
\frac{1}{n}\cdot
\sum_{k=1}^{k=n}\, \phi^2_k(p)=
\frac{1}{\text{area}(\Omega)}
\]
\medskip

|noindent
The proolf of this theorem is given in § xx where
the crucial point is to study the Dirichlet series
below for each $p\in\Omega$:
\[ 
\Phi_p(s)=\sum _{n=1}^\infty \, \frac{\phi_n(p)^2}{\lambda_n^s}
\]
It is easily seen that
$\Phi_p(s)$ is analytic in a half-space
$\mathfrak{Re} s>b$ for a large $b$.
Less trivial is that
there exists an entire function
$\Psi_p(s)$ such that
\[
\Phi_p(s)=\Psi_p(s)+\frac{1}{4\pi(s-1)}
\]
Hence $\Phi_p(s)$ is meromorphic in the complex $s$-plane with a simple pole
at $s=1$.
The proof that (xx) holds is given in § xx and offers an instructive lesson
in analytic functiuon theory where
residue caluculs and changes of contioours appear.
We remark that this elegant procedure goes back to
constructions by Riemann whose original work
paved the way towards many discoveries.
Concernibngt Theorem xx we also mention that it
can be used to analyze asymptotic behaviour of heat-eqautions with
related to   vibrating membrans. See § xx for an account.












\newpage


SKIP


\bigskip







We   the proof in §  which uses 
Ikehara's Theorem. So here
"pure real analysis" and 
Dirichlet series with a complex parameter
intervene during   the proof.
By a further study of  estimates for Green's resolvents,
Carleman  proved that
the eigenfunctions and all their higher derivatives also
satisfy a limit formula. The result is that
for each pair of non-negative integers $j,m$ and every $p\in \Omega$ one has
\[ 
\lim_{n\to\infty}\,
\frac{1}{\lambda_n^{j+m+1}}\cdot
\sum_{k=1}^{k=n}\, \bigl(\frac{\partial^{j+m}\phi_k}{\partial x^j\partial y^j}
\bigr)^2(p)=
\frac{1}{\pi\cdot 2^{2m+2j+2}}\cdot
\frac{(2m)!\cdot (2j)!}{m!\cdot j!\cdot (m+j+1)!}
\]
So in particular
\[
\lim_{n\to\infty}\,
\frac{1}{n}\cdot
\sum_{k=1}^{k=n}\, \phi^2_k(p)=
\frac{1}{\text{area}(\Omega)}
\]
where a notable   point is that the limit is independent of $p$.
Background to the proofs of the results above
is covered by
material  
in the chapters where the ordinary Dirichlet problem
is solved  and
Green's functions are constructed in Chapter 5, while 
material related to harmonic analysis and  spectral theory which is 
needed to get Ikehara's theorem
is covered by an appendix devoted to functional analysis.














Poincaré solved
the boundary value problem as follows: 
Given a positive continuous function
$h$
on $\partial\Omega$ he associated
the kernel function $K_h(p,q)$ defined 
outside the diagonal  of   $\partial\Omega\times\partial\Omega$ by
\[ 
K_h(p,q)=
\frac{1}{4\pi}\cdot \frac {\langle p-q,{\bf{n}}_*(q)\rangle}{|p-q|^3}
\]
where  inner product between  the vectors $p-q$ 
and the inner normal ${\bf{n}}_*(q)$ 
appear in the denominator
while 
the third power of the
euclidian distance between points  $p,q$ in $\partial\Omega$
appear in the numerator.
With a complex parameter $\lambda$
one gets the integral equatiion
\[ 
u(p)-\lambda\cdot \int_{\partial\Omega}\, K_h(p,q)u(q)\cdot d\sigma (q)=
f(q)\tag{2}
\] 
where
$d\sigma (q)$ denotes the area measure on $\partial \Omega$.
It means that for each $f\in C^0(\partial\Omega)$ one seeks
$u\in C^0(\partial\Omega)$ such that (2) holds.
If $u$ solves (2) when
$\lambda=1$, then Green's formula shows that
the solution $U$ to (1) is found via
Newton's harmonic extension of $u$, i.e. 
\[
U(p)= \int_{\partial\Omega}\, \frac{1}{p-q|}\cdot u(q)\, d\sigma(q)
\quad\colon\quad p\in \Omega\tag{3}
\]


\noindent
The   merit in the approach  by   Neumann 
and Poincaré  is that these authors
realized the importance of
studying  
the
operator-valued function 
\[ 
\lambda\mapsto  E-\lambda\cdot \mathcal K_h
\]
where
$\mathcal K_h$ is the integral operator
defined by the kernel function $K_h(p,q)$.
For domains whose boundary is sufficiently
regular 
$\mathcal K_h$ is a bounded linear operator and to solve
(2) one considers the resolvent
\[
R_h(\lambda)=(E-\lambda\cdot \mathcal K_h)^{-1}\tag{*}
\]
Poincaré 
proved that for a domain $\Omega$ with $C^2$-boundary, this operator-valued function
extends to a meromorphic function of $\lambda$ defined in 
the whole complex plane whose poles are
real and simple. He
also demonstrated that no pole occurs when
$\lambda=1$ which
gives the requested solution $u$  to (2) given by
\[ 
u=R_h(1)(f)
\]

\medskip


\noindent
Inspired by the Neumann-Poincaré methods to handle boundary value problems,
Fredholm and Hilbert studied
the eigenvalue problem
where one seeks functions $u$ in a domain $\Omega$ as above such that
\[ 
\Delta(U)+\lambda\cdot U=0\quad\text{and}\quad U|\partial\Omega=0\tag{1}
\]
In § xx we shall treat this in the planar case where
$\partial\Omega$ consists of a finite family of disjoint and closed Jordan curves
of class $C^1$.
The first fact is that
non-trivial solutions to (1) only  occur when
$\lambda$ is real and positive and
using  general facts about integral equations, Fredholm and Hilbert demonstrated that
the eigenvalues for a discrete  sequence 
$\{0<\lambda_1\leq \lambda_2\leq \ldots\}$
where eventual eigenvalues whose eigenspace has dimension $>1$ is repated
according to this multiplicity.
The associated eigenfunctions
$\{\phi_k\}$ are real-valued and can be chosen so that 
they form an orthonormal set in the Hilbert space
$L^2(\Omega)$.
The search for  asymptotic formulas of the eigenvalues
became a natural issue and was settled by Weyl who proved the  limit
formula:
\[
 \lim_{n\to\infty}\, \frac{\lambda_n}{n}= 
\frac{4\pi}{\text{area}(\Omega)}
\]

\medskip

\noindent
We give  the proof in §  which uses 
Ikehara's Theorem. So here
"pure real analysis" and 
Dirichlet series with a complex parameter
intervene during   the proof.
By a further study of  estimates for Green's resolvents,
Carleman  proved that
the eigenfunctions and all their higher derivatives also
satisfy a limit formula. The result is that
for each pair of non-negative integers $j,m$ and every $p\in \Omega$ one has
\[ 
\lim_{n\to\infty}\,
\frac{1}{\lambda_n^{j+m+1}}\cdot
\sum_{k=1}^{k=n}\, \bigl(\frac{\partial^{j+m}\phi_k}{\partial x^j\partial y^j}
\bigr)^2(p)=
\frac{1}{\pi\cdot 2^{2m+2j+2}}\cdot
\frac{(2m)!\cdot (2j)!}{m!\cdot j!\cdot (m+j+1)!}
\]
So in particular
\[
\lim_{n\to\infty}\,
\frac{1}{n}\cdot
\sum_{k=1}^{k=n}\, \phi^2_k(p)=
\frac{1}{\text{area}(\Omega)}
\]
where a notable   point is that the limit is independent of $p$.
Background to the proofs of the results above
is covered by
material  
in the chapters where the ordinary Dirichlet problem
is solved  and
Green's functions are constructed in Chapter 5, while 
material related to harmonic analysis and  spectral theory which is 
needed to get Ikehara's theorem
is covered by an appendix devoted to functional analysis.



\newpage



\centerline {\emph{0.2.1 Comments by Beurling about  the Helmholtz equation.}}
\medskip

\noindent 
While referring to applications 
in physics
of analytic function theory 
and 
elliptic boundary value problems in
${\bf{R}}^3$ one should be  prudent. Here follows an excerpt from a lecture
by Beurling in Lund 1951 which points out some  problematic features.

\medskip

\noindent
 \emph{Hydromechanics is filled with paradoxes which begin already 
with the simplest problem; the motion of an ideal incompressible fluid in a force-free
field. In that case the velocity vector is the gradient of  a harmonic function
$\phi$ whose normal derivative vanishes on fixed walls 
which limit the fluid's expansion in space.
If we bound a certain portion of the fluid by two surfaces $A$ and $B$ 
which are orthogonal to the stream-lines, we obtain a domain 
$\mathcal R$ bounded by certain fixed wall $C$. The function $\phi$ is then a solution
to Laplace's differential equation with boundary conditions
$\phi=a$ on $A$; $\phi=b$ on $B$; $\frac{\partial\phi}{\partial n}=0$ on $C$
where $a$ and $b$ are constants.}
\medskip

\noindent
\emph{In spite of  exact mathematical solutions to the boundary value problem 
describing a potential flow, it is of limited interest both from a 
theoretical and practial point of view.
The  mathematical equations
which describe the flow is usually in poor agreement with the empirical facts
and  give rise to a variety of contradictions, i.e. d'Alemebert's paradox.
In 1868 Helmholtz introduced a new model with the objective
of fitting the theory better to physical facts.
Here the flowing fluid only fills up a
certain subdomain $\mathcal R_0$ not given in advance, while the remaining
set $\mathcal R\setminus \mathcal R_0$
is filled with fluid at rest, so called "deadwater" or "wakes".
By Bernoulli's relations the flowing fluid has constant
speed on the boundary $F$ between
$\mathcal R\setminus \mathcal R_0$ and $\mathcal R_0$
which mathematically
leads to a free boundary value problem.}
\medskip

\noindent 
\emph{However, the Helmholtz's flow problem leads to great 
difficulties and still belongs on the whole
to an unexplored region of potential theory.
Certain 2-dimensional problems  were settled by Weinstein
when polygonal boundaries
appear where  analytic function theory and
 hodographic methods can be  used, and some  other 2-dimensional problems
 have  been solved
 by
Leray using rather complicated techniques. Passing to dimension three
there is of now the lack of mathematical methods ...}
\medskip

\noindent
{\bf{Remark.}}
The reader may consult Birkhoff's 
text-book \emph{Hydromechanics, a Study in Logic,
fact and Similtude} 
(Princeton University Press 1950)  and 
articles by Weinstein, especially
\emph{Non-linear problems in the Theory of
Fluid Motion with free Boundaries} [Proc.of first symp. applied math. 1949]
for a further account.
The article \emph{On measurement of velocity by Pitot tube}
by B.J. Andersoon in [Arkiv för mat. 1955]
was inspired by Beurling's lecture and contains
a specific solution to a 2-dimensional problem with a free boundary where
analytic function theory is used to construct theoretical solutions.
This theoretical work was carried out together with empirical experiments
which showed  discrepancy between
expermintal data and the theoretical solution but within errors of a few percentages.
A  Pitot tube is well adapted
for a mathematical treatment  because it is supposed to have a long range
which makes it easy to start with a stationary fluid at a long distance before
wakes appear.
Passing to dimension three the discrepancy increases rather drastically
between experminental data and
mathematical solutions.
\medskip


\noindent
Beurling's lecture was delivered more than half a century.
Thanks to comuters one can nowadays
exhibit  numerical solutions. But from a pure theoretical 
point if view
little   
progress 
has been achieved
about equations of Helmholtz type during  more recent decades and
one may ask if it is worth efforts to
find more theoretical results for various 
linear boundsry value problems.
Well, hopefully some n
further mathematical discoveries  can  contribute to
develop a more efficient   numerical analysis.
Non-linearity caused by viscosity lead to   more
involved  equations such as a mixture of a classical Navier-Stokes equation and
free boundaries in the sense of Helmholtz and here one is more or 
less totally dependent upon numerical solutions.
This   means that
a \emph{very   important issue}  in current mathematical research
is the 
search for   improved numerical algorithms. A  typical problem is to adapt
grids in order that the computer can
start calculations to find approximative solutions
to PDE-equations.
Recall that the major difficulity in Navier-Stokes equations occur in
the physically relevant case when
the viscosity is small and here one is more or less totally dependent 
to find numerical solutions since the associated PDE-equations do not fit with
any
manageable class.

 
\bigskip


\centerline{\emph{0.2.2 Calculus of variation.}}

\bigskip


\noindent
This is a subject which would
require an extensive chapter. Optimization
problems  solved by calculus of variation  played a significant role while
analysis was developed. 
Fermat's  
early studies
led to the principle of least action and 
Huyghen's applied this to  many delicate variational problems.
Recall for  example his fundamental  discovery that
the Law of Momentum
implies that a hanging chain under gravity with
its end-points fixed on some veritcal wall, minimizes
the potential energy.
Dynamical situations
led  to the solution of the Brachistone problem and
extensive classes  of variational problems were
considered  by Euler. Here  the Euler equations
express necessary conditions for
extremals in a variational problem.
In classical mechanics the
principle of virtual work was introduced by d'Alembert 
and a 
conclusive result appears in Lagrange's  famous text-book
on \emph{Mechanique} from 1770 (?) 
which gives the equations of motion
for  every  system  
with a finite degree of freedom. Here
the external forces can be arbitrary, i.e.
non-conservative  cases can occur.
The d'Alembert-Lagrange equations have a wide range of applications,
foremost in
engineering.
The crucial role of convexity (or concavity)
in order to
ensure that a specific problem has a unique
minimum (or maximum)  was clarified by Legendre. 
Later  physical discoveries, such as the Briot-Savart Law
from 1800 led to more involved 
problems related to mathematical
physics.
From a geometric point of view
one should mention  contributions by Gauss 
who introduced the notion of curvature
in differential geometry.
A specific case is the Dirichlet problem
where we consider the following 
boundary value problem in dimension two: Let
$\Omega$ be a connected domain of
class $\mathcal D(C^1)$ which means that
$\partial\Omega$
consists of a finite union of disjoint closed 
and differentiable Jordan curves.
Let $g\in C^0(\partial\Omega)$ be
real-valued
and
$\phi(x,y)$ is a continuous function in
$\bar \Omega$ which takes positive values in the open interior.
One seeks a function $u$ such that
$u=g$ on $\partial\Omega$ while
\[ 
\Delta(u)+\phi\cdot u=0
\] 
holds in $\Omega$.
To solve this one introduces the functional
\[ 
J(u)=
\iint_\Omega\, (u_x^2+u_y^2)\, dxdy+
\iint_\Omega\, \phi\cdot u^2\, dxdy
\]
It is defined on functions $u\in C^0(\bar\Omega)$ for which
$u=g$ on $\partial\Omega$ and
its first order partial derivatives exist in $\Omega$ so that
the first integral above is finite, i.e.
$u$ has a finite Dirichlet integral.
The $J$-functional is strictly
convex in  Legendre's sense.
For if
$h\in C^1(\Omega)$  vanishes on
$\partial\Omega$ then the function of the real variable $s$
defined by
\[
s\mapsto J(u+sh)
\] 
is strictly convex. In fact, this follows because
the second order derivative at $s=0$ is equal to 
$J(h)$ which is $>0$ for every $h$ above which is not identically zero.
If $u_*$  minimizes the $J$-functional it gives a solution to
the boundary value problem. The reason is that
if $h$ is an arbitrary $C^2$-function
with compact support in $\Omega$ then
the inequality
\[ 
J(u_*+\Delta\cdot h)\geq J(u_*)
\] 
for all small $\delta$ which may be either positive or negative
entails that
\[
\iint\, (u_xh_x+u_yh_y)\, dxdy+\iint\, \phi\cdot u\cdot h\, dxdy=0
\]
Greens'  formula applied to the pair $u_*,h$
and the elliptic property of the Laplace operator imply that 
$u_*$ is a $C^2$-function in $\Omega$ where it  satisfies the
requested PDE-equation
$\Delta(u_*)+\phi\cdot u_*=0$.

\medskip


\noindent
{\bf{Remark.}}
Above the competing family of $u$-functions
are of the form $u=G+w$ where
$G$ is the ordinary solution to the Dirichlet problem, i.e. harmonic in
$\Omega$ while $G=g$ on $\partial\Omega$, while $w$ are
functions with a finite Dirichlet integral and boundary values zero.
After Hilbert's creation of general Hilbert spaces
the solution to the variational probelm above was consolidated
by Weyl who  regarded
the space of $w$-functions as above for which
$J(w)<\infty$.
Weyl
considered   
the class $C^1_0(\Omega)$
of continuously differentiable
$w$-functions 
with  compact support which
gives  a dense subspace  of a  Hilbert space
denoted by $W_0^1(\Omega)$ whose
functions have first order
derivatives in $L^2_\text{loc}(\Omega)$ in
the sense of distributions, while $J(w)<\infty$ and the inner product of a pair
$(w,v)$ is defined by
\[ 
\langle w,v\rangle=
\iint\, (w_xv_x+w_yv_y)\, dxdy+\iint\, \phi\cdot w\cdot v\, dxdy
\]
From this  the existence and uniquness of $u_*$ follows from
general facts about
strictly convex functionals on Hilbert spaces.













\newpage



\centerline{\emph {0.3 Hadamard's extension theorem.}}
\medskip


\noindent
A good example of  
"an old vintage result "
is due to Jaques Hadamard. Text\vvv books are in most cases content
to announce the
formula for
the radius of convergence of a power series
$\sum\, c\uuu nz^n$  by the equality
\[
\frac{1}{\rho}= \limsup\uuu{n\to \infty}\,
|c\uuu n|^{\frac{1}{n}}\tag{*}
\]
This is     a    minor observation
compared to   the contents  in Hadamard's thesis
\emph{Essai sur l'études des fonctions donnés par leur
développement de Taylor} 
from 1893. 
Let us recall the major result
in [ibid] since it  has a wide range of applications
and is seldom  mentioned  in contemporary text-books.
Consider a power  series   whose radius of convergence is a positive  number
$\rho$. To every pair $p\geq 1$ and $n\geq 0$
we have  the
Hankel determinants:
\[
\mathcal D\uuu n^{(p)}=
\text{det}
\begin{pmatrix}
c\uuu n&c\uuu{n+1}&\ldots&c\uuu{n+p}\\
c\uuu {n+1}&c\uuu{n+2}&\ldots&c\uuu{n+p+1}\\
\ldots&\ldots&\ldots&\ldots\\
c\uuu {n+p}&c\uuu{n+p+1}&\ldots&c\uuu{n+2p}\\
\end{pmatrix}
\]


\noindent
To each $p\geq 1$ we set
\[
\limsup\uuu {n\to\infty}\, |\mathcal D\uuu n^{(p)}|^{\frac{1}{n}}=\delta(p)
\]
From (*) it follows easily that
\[
\delta(p)\leq \rho^{\vvv p\vvv 1}
\quad\colon\,  p\geq 1\tag{1}
\]
If strict inequality holds for some positive integer in  (1) the 
following result was proved in [loc.cit] where we put $f(z)= \sum\, c\uuu nz^n$.

\medskip

\noindent
{\bf{Theorem.}}
\emph{Assume  there exists a positive integer $p$
and some
$\rho\uuu*>\rho$
such that 
$\delta(q)=\rho^{\vvv q\vvv 1}$ when $0\leq q\leq p\vvv 1$ while}
\[
\delta(p)=\rho^{\vvv p}\cdot \rho\uuu *^{\vvv 1}
\]
\emph{Then there exists a polynomial $Q(z)$ of degree
$p$  at most such that $Q(z)\cdot f(z)$ extends to an analytic function in the disc
$\{|z|<\rho^*\}$.}


\medskip

\noindent
Hadamard's proof shows also that
the coefficients of the $Q$\vvv polynomial are found
via  robust  limit formulas which arise  
from  linear systems of
equations derived  from the given
sequence $\{c\uuu n\}$.



\medskip



\centerline {\emph{A result by Jentsch.}}
\medskip


\noindent
The following result is due  Jentsch in the article
\emph{xxx} from 1917.
Let $\{a_k\}$ be a sequence of complex numbers such that 
\[ 
\lim_{k\to\infty}\,|a_k|^{\frac{1}{k}}=1\tag{1}
\]
To each positive integer $n$ we get the polynomial
\[ 
s_n(z)= a_0+a_1z+\ldots+a_nz^n
\]
Let $\{\alpha_1^{(n)},\ldots,\alpha_n^{(n)})$
be its zeros and construct the probability measure
\[ 
\mu_n= \frac{1}{n}\cdot\sum _{k=1}^{k=n}\,\delta( \alpha_n^{(n)})\tag{2}
\]
Jentsch proved that the sequence $\{\mu_n\}$ converges to the
Haar measure on the unit circle, i.e. for every
continuous function
$f$ in ${\bf{C}}$ one has the limit formula
\[ 
\lim_{n\to\infty}\, \int\, f\cdot d\mu_n=
\frac{1}{2\pi}\int_0^{2\pi}\, f(e^{i\theta})\, d\theta\tag{*}
\]
To prove (*)  Jentsch
considered the
sequece of locally integrable functions
\[
\phi_n(z)=
\frac{\log\,|s_n(z)|}{n}\tag{3}
\]
In § xx we show that
(1) entails that the sequence $\{\phi_n(z)\}$
converges in the sense of
distributions to the function $U(z)$ which is zero in
$|z|<1$ and equal to $\log\,|z|$ when $|z|\geq 1$. After this (*) follows when
one applies the Laplace operator. So here 
measure theory intervenes with analytic function theory.
The result is quite remarkable. The simplest case occurs when $a_n=1$ 
for all $n$. Here 
\[
s_n(z)= 1+z+\ldots+z^n
\] 
whose  zeros are
the roots of unity $\{e^{2\pi i\nu/(n+1)}\quad\colon \nu= 1,\dots, n\}$.
These $n$-tuples are
equi-distributed so after the normlisation with
the factor $\frac{1}{n}$ one gets  (*).
But for other sequences the limit  (*)
is not evident.
For example we can take 
$\{a_\nu= e^{\i\cdot\theta_\nu}\}$
where the sequence $\{0\leq\theta_\nu\leq 2\pi\}$ is arbitrary.








\newpage



\centerline{
\emph{0.4 The role of
inequalities.}}
\medskip


\noindent
For students aiming to learn     "big theories" 
the search for    inequalites  may appear
to be a modest or even  trivial  issue
compared to studies of
axiomatic concepts.
But the truth is that more or less all
deep
results in mathematics rely upon inequalities.
An example is the Riemann Hypothesis which is 
the utmost challenge among  open problems in the world of mathematics.
A necessary and sufficient condition
for its validity
goes as follows: For each real number $x$ we denote
by $\{x\}$ the largest integer such that
$0\leq x\vvv \{x\}<1$.
To each   positive integer $M$ we get $M$ many functions
$\{\rho\uuu j(x)\}$ defined on the open unit  interval $(0,1)$
by
\[
\rho\uuu j(x)=\frac{j}{M x}\vvv
\{\frac{j}{M x}\}\quad\colon\quad 1\leq j\leq M
\]
Set
\[ \beta(M)= \min\uuu{c\uuu\bullet}\,
\int\uuu 0^1\, \bigl(\, \sum\uuu{j=1}^{M}\,
c\uuu j\cdot \rho\uuu j(x)\vvv 1\,\bigr)^2\cdot dx\tag{1}
\]
with the minimum taken over
all $M$\vvv tuples of real numbers such that
\[
\sum\uuu{j=1}^{j=M}\, j\cdot c\uuu j=0
\]
Beurling has shown
that the Riemann Hypothesis is true  if and only if
\[
\lim\uuu{M\to\infty}\,\beta(M)=0\tag{*}
\]


\noindent
When $M$ is fixed  (1) is minimized  by a unique
$M$\vvv tuple $c\uuu\bullet$ since we are dealing with a 
positive definite quadratic form and then   $\beta(M)$ is recovered from
Lagrange's multiplier. The obstacle is that the 
$\rho$\vvv functions become  irregular   as $M$ increases and
mathematics has not yet  become enough developed
to establish  bounds of the
$\beta$\vvv numbers in order to 
decide whether  (*) holds or not.
\medskip

\noindent 
However 
we are able to exhibit many inequalities.
An example is 
a mini-max result for
polynomials
which goes as follows.
 Let $P(z)$ be a polynomial of some degree $n\geq 2$ where
$P(0)=1$.
To each pair $0<a<b<1$
we set
\[
\omega_P(a,b)= \max_{a\leq r\leq b}\, \min_\theta\, |P(re^{i\theta})|
\]
Thus, while the radius $r$ varies between
$a$ and $b$ we seek some $r$
such that the minimum modulus of $P$ on the circle
$|z|=r$ is as large as possible.
In his thesis \emph{Études sur in problème de majoration}
at Uppsala University from  1933, Beurling found
a lower bound hold for these $\omega$-functions.
More precisely, the following hold for
all pairs $0<a<b$ and each normalised  polynomial $P$ as above with degree $n$:
\[
 \omega_P(a,b)\geq \bigl(\frac{\sqrt{b}-\sqrt{a}}{\sqrt{b}+\sqrt{a}}\,\bigr)^n\tag{*}
\]
In § XX we  expose the proof
which
relies upon a study of
logarithmic potentials.
Let us  remark that (*)
gets  sharp when $n$ increases.
A result of a similar nature from [ibid: page 96]
goes as follows: Let $R>0$ and $f(z)$ is analytic in
$\{|z|<R\}$. To every
$0<r<R$ we denote by $M(r)$ the maximum 
of $|f(z)|$ taken on the circle of radius $r$.
Let $\mu>0$  and consider a pair
$0<r_1<r_2<R$ where $M(r_1)>\mu$ is holds and put
\[ 
E=\{ r_1<r<r_2\,\colon\, M(r)\leq \mu\}
\]
The integral of $r^{-1}$ over $E$ measures its logarithmic length. Set
\[
\mathcal L(r_1,r_2;\mu)=
\frac{1}{2}\cdot e^{\int_{r_1}^{r_2}\, \frac{dr}{r}}
\]
With this notation one has the inequality
\[
\frac{M(r_2)}{\mu}\geq
\bigl[ \frac{M(r_1)}{\mu}\bigr]^{\mathcal L(r_1,r_2;\mu)}\tag{**}
\]



\medskip



\centerline{\emph{0.4.1 Distributions of zeros of polynomials}}
\medskip


\noindent
Let
$n\geq 2$ and $\{e^{i\theta_k}\}$
is an $n$-tuple of points on the unit circle
where $-\pi<\theta_k<\pi$, i.e. $-1$ does not occur.
For each $0<\alpha<\pi$ we denote by $N(\alpha)$ the
number of $\theta$-points such that $-\alpha<\theta_k<\alpha$
and set
\[
J(\alpha)= \bigl|\frac{N(\alpha)}{n}-\frac{\alpha}{2\pi}|
\]
It turns out that the $J$-function is majorized
via 
a maximum norm of the polynomial
$p(z)= \prod \,(1-e^{-i\theta_\nu} z)$.
Namely, one has the inequality
\[ 
|J(\alpha)| \leq \sqrt{\frac{2\pi}{kn}}\cdot
\sqrt{\log |p|_D}
\]
where $|p|_D$ is the maximum norm of $p$ on the unit disc and
$k\simeq 0,916\ldots$ is Catalani's constant.
We prove this in Chapter 5. § 13
under the heading Ganelius' theorem.
\medskip



\centerline{\emph{0.4.2 A result by Lindwart and Polya.}}
\medskip


\noindent
The result below was proved in their joint article
\emph{Über eine Zusammenhang zwischen der Konvergenz von Polynomfolgen und der Verteilering ihrer Wurzeln}
[Palermo 1914].
Here is the situation:
Let $\{P_n(z)\}$ be a sequence of polynomials
which converges uniformly on the closed unit disc $\{|z|\leq 1\}$
to a function which is not identically zero. Suppose also that there exists some
$0<\phi<\pi/2$ and some $a>0$
such that the polynomials are zero free in the union of the
sector $\{-\phi<\arg z< \phi\}$ and the half space
$\mathfrak{Re}\, z>a$.
Under these  conditions
the sequence
$\{P_n(z)\}$ converges uniformly on compact subsets
of ${\bf{C}}$ to an entire function
$f(z)$ of order $\rho\leq 2$.
The last assertion means
that if 
$\{a_k\}$ are the coefficients
in the series expansion of $f$ then
\[ 
\liminf_{k\to \infty}\,\frac{\log\, \frac{1}{|a_k|}}
{k\cdot \log k}= \frac{1}{\rho}
\]

\medskip

\noindent
The proof contains several unexpected ingredients
and illustrates that
analytic function theory
contains a wealth of results
where individual proofs  often
require some 
ingenious  idea, i.e. the theory is not 
"stream-lined". The proof of the Lindwart-Polya theorem
is given in § XX.

\newpage


\centerline{\emph{0.4.3 An inequality by Nevanlinna.}}
\medskip

\noindent
A subject which is not covered in these notes is Nevanlinna's value distribution theory 
for meromorphic functions.
It is treated in the text-book (Nevanlinna). 
But let  us 
recall one major result
which leads to  
an extension of Picard's theorem. Let 
$f(z)$ be a meromorphic function 
in ${\bf{C}}$ and consider
Nevanlinna's reduced counting functions, i.e.
when
$a$ is a complex number then
$ N_*(r;a)$ which
counts the number of points $|z|<r$ where $f(z)=a$ irrespectively of multiplicity.
If   $a=\infty$ we count poles in the same way 
irrespectively
of the order of the poles.
Nevannlina proved that 
there exists a constant $C_f$ which depends
on the given
meromorphic function such that
the inequality below holds for all $r>0$:
\[ 
\frac{1}{2\pi}\cdot \int_0^{2\pi}\,\log^+\,|f(re^{i\theta})|\,d\theta\leq
N_*(0;r)+N_*(1;r)+ N_*(\infty;r) + C_f\cdot\log (r+2)\tag{*}
\]
\medskip



\centerline{\emph{0.4.4 An inequality for convolutions.}}
\medskip


\noindent
Let $k(x,y)$ be a complex-valued continuous function on the  square
$\{0\leq x,y\leq 1\}$. Symmetry is not assumed, 
i.e,
$k(x,y)\neq k(y,x)$ may occur
Let $f_0(x)$ be another  continuous function  on $[0,1]$
and 
assume that the maximum norms of $k$ and $f$ both are $<1$.
Inductively
we get a sequence $\{f_ n\}$ where
\[
f\uuu n(x)=\int\uuu 0^1\, k(x,y)\cdot f\uuu{n\vvv 1}(y)\cdot dy
\quad \colon\quad n\geq 1
\]


\noindent
To each $0\leq x\leq 1$ and every pair of positive integers $n,p$ 
one has the Hankel determinant:
\[
\mathcal D_n^{(p)}(x)=
\det
\begin{pmatrix}
f_{n+1}(x)
&f_{n+2}(x)
&\ldots&\ldots
& f_{n+p}(x)\\
f_{n+2}(x)
&f_{n+3}(x)
&\ldots&\ldots
& f_{n+p+1}(x)\\

\ldots &\ldots &\ldots&\ldots \\
\ldots &\ldots&\ldots&\ldots\\
f_{n+p}(x)
&f_{n+p+1}(x)
&\ldots&\ldots
& f_{n+2p-1}(x)\\
\end{pmatrix}
\]

\noindent
With these notation the inequality below
will
be proved in 
Chapter I:C : § 10:

\medskip

\noindent
{\bf{0.4.5 Theorem }} \emph{For every $p\geq 2$ and $0\leq x\leq 1$ one has
the inequality}
\[
\bigl |\,  \mathcal D\uuu n^{(p)}(x))\,\bigr|\leq 
(p\, !)^{\vvv n}\cdot \bigl( p^{\frac{p}{2}}) ^n\cdot \frac{p^p}{p\,!}\tag{*}
\]


\noindent
Using (*) and Hadamard's inequality from § 0.3
we also show
that
if $\lambda$ is a new complex variable then
the power series
\[
u\uuu\lambda(x)= \sum\uuu{n=0}^\infty\, f\uuu n(x)\cdot \lambda^n
\] 
which to begin with
converges if  $|\lambda|<1$ 
extends to a meromorphic
function in the whole complex plane whose the poles
are related to a certain compact integral operator.
Above one regards
$u_\lambda$ as a function of $\lambda$ with values in the
Banach space of continuous functions on the closed unit interval
and 
we shall see many examples where
the ordinary family of  complex-valued analytic functions
is extended to analytic functions with values in
Banach spaces.



\newpage

\centerline{\emph{0.4.6 An inequality for Fourier series.}}
\medskip


\noindent
Let $f(x)$ be a continouos and $2\pi$-periodic function.
The Fourier coefficients are defined by
\[
\widehat{f}(\nu)= 
\frac{1}{2\pi}\, \int_0^{2\pi}\,
e^{-i\nu x}\, f(x)\ dx
\]
For each integer $n$ we get the partial sum
\[ 
s_n(x)= 
\sum_{\nu=-n}^{\nu=n}\, \widehat{f}(\nu)\cdot e^{i\nu x}
\]
In general $\{s_n\}$ does not converge to $f$ pointwise convergence.
Classic examples are due
to  Gibbs. On the positive side
a  deep result  due to Carleson asserts that
\[ 
\lim_{n\to\infty}\, s_n(x)= f(x)
\]
holds almost everywhere, i.e. for every $x$ outside a null set in
Lebegue's sense.
An averaged version goes as follows:
To each $n$ we set
\[
\mathcal D_n(f)= \sqrt{\frac{1}{n+1}\cdot
\sum\uuu{\nu=0}^{\nu=n}\, ||s\uuu\nu\vvv f||^2}
\]
where $||s_\nu-f||$ is the maximum norm 
taken over $[0,2\pi]$.
The inequality below shows that
Gibb's phenomenon is sparse when 
when partial sums occur via
a random choice of $n$. For a
$2\pi$-periodic and continuous function $f$ 
we denote its maximum norm by $||f||$
and  $\omega_f$ is its
modulos of continuity. 
The result below is due to Carleman and will be proved in 
Chapter I: § XX:

\medskip



\noindent
{\bf{Theorem}}. \emph{There exists an absolute constant $K$
such that the following hold for every 
$2\pi$-periodic and continuous function $f$,
every $b\geq 1$ and every positive integer $n$:}
\[ 
\mathcal D_n(f)\leq K\cdot ||f||\cdot \bigl[\frac{1}{b}+b\cdot \omega_f(\frac{1}{n})\bigr]
\]
\medskip


\noindent
Since $\omega_f(\frac{1}{n})$ tends to zero as $n$ increases
we can take $b$ arbitrary large  and
conclude that
\[
\lim_{n\to\infty}\, \mathcal D_n(f)=0
\]
This shows that Gibb's phenomenon in the average 
only can occur
at a  sparse  set of integers.







\newpage


\centerline{\emph{0.4.7 Infinite systems of linear equations.}}



\medskip

\noindent
Let $\{a_p\}$ be a sequence of positive real numbers
such that $a_p\to +\infty$ and
associate 
the function $A(r)$ which to each $r>0$
is the number of $a$-values $<r$. We say that $\{a_p\}$ has a
positive  asymptotic density if
there exists the limit
\[ 
\lim_{r\to\infty}\, A(r)>0
\]
We do not require that the sequence is monotone, i.e 
$a_p\leq a_{p+1}$ need not always hold.
Next, let $\{b_q\}$ be another sequence of real numbers which also has
some
positive  asymptotic density which in general can be different from that of
$\{a_p\}$.
Given such a pair we take some
$\epsilon>0$ and consider the homogeneous  system of equations:
\[
 \sum_{q=1}^\infty\,\frac{x_q}{a_p-b_q-i\epsilon\cdot q}=0\tag{*}
 \]
 where $\{x_q\}$ is a complex sequence
which   belongs to  the Hilbert space $\ell^2$, i.e.
 $\sum\,|x_q|^2<\infty$. 
 In § xx we  prove that the homogeneous system only has the trivial null solution.
 The proof relies upon inequalities for
 certain fractional sums and a construction of a meromorphic function.
In the section entitled \emph{Dagerholm Series} in
 Special Topics we  prove a subtle result
 where
 $\epsilon=0$. In this situation we shall find non-trivial 
 solutions $\{x_q\}$
 but they need not 
 be in $\ell^2$.
The lesson  is that
 many problems about infinite systems of 
 linear equations, as well as many problems in functional analysis, 
 can only be
 proved 
 by analytic function theory.
 \bigskip
 


\centerline{\emph{0.4.8 Blaschke products and interpolation.}}
\medskip


\noindent
Let $n\geq 2$ and $E=\{\alpha_1,\ldots,\alpha_n\}$
is an $n$-tuple of distinct points in the open unit disc $D$.
To each $n$-tuple of complex numbers
$w_\bullet=(w_1,\ldots,w_n)$
one
seeks to minimize the maximum norm
\[
|f|_D=\max_{z\in D}\,|f(z)|
\]
in the class of functions which
solve the interpolation problem
$f(\alpha_k)= w_k$ for every $k$.
A result due to Nevanlinna and Pick
shows that there exists a unique interpolating function
$f$ with minimal norm. Moreover, 
\[ 
f(z)=\rho(w_\bullet)\cdot 
e^{i\theta}\cdot \prod_{\nu=1}^{\nu=n-1}\,
\frac{z-\beta_\nu}{1-\bar\beta_\nu\cdot z}
\]
Here
$\rho(w_\bullet)>0$ while $0\leq\theta\leq 2\pi$ and
$\{\beta_\nu\}$ is an $(n-1)$-tuple in $D$
which is not necessarily
distinct.
We  prove this result in  Special Topics § XX.
Keeping $E$ fixed we 
introduce the interpolation constant
\[
\mathfrak{int}(E)=\max \,\rho(w_\bullet)
\]
where the mximum is taken over $n$-tuples $w_\bullet$ such that
$|w_k|\leq 1$ for every $k$.
Next,  denote by $\mathcal B_{n-1}$ the class of functions of the form
\[
e^{i\theta}\cdot \prod_{\nu=1}^{\nu=n-1}\,
\frac{z-\beta_\nu}{1-\bar\beta_\nu\cdot z}
\]
where $0\leq\theta<2\pi$ and $\{\beta-\nu\}$ is an $(n-1)$-tuple of points in 
$D$ which need not be distinct. Put
\[
\tau(E)=\min_\phi\, |\phi|_E
\]
 where the minimum is taken over all 
 $\phi\in\mathcal B_{n-1}$ and
 $|\phi|_E$ is the maximum norm on $E$.
 The Nevanlinna-Pick theorem easilly entails that one has the equality
 \[
 \mathfrak{int}(E)=\frac{1}{\tau(E)}
 \]
 Less obvious is the follwing result due to Beurling:
 \medskip
 
 \noindent
{\bf{Theorem.}}\emph{
 Up to multiplication with
 $e^{i\theta}$ for some complex number, the
 minimax problem above has a unique solution $\phi_*$. Moreover}
 \[ 
 |\phi_*(\alpha_k)|=\tau(E)\quad \colon 1\leq k\leq n
 \]
\medskip
 
 
\noindent
A consequence of this result is that
when the set $E$ is given then the "worst scenario" consists of $n$-vectors $w^*_\bullet$ 
such that   $\rho(w_\bullet^*)=\mathfrak{int}(E)$ and Beurling's result shows
that   $|w^*_k|= 1$ hold for every $k$.
Moreover, this $n$-tuple of points on the unit circle is
unique up to a common rotation.
We shall prove this in Special  Topics §§
which illustrate
a typical complex
extremal problem where the given set 
$E$ determines the 
$(n-1)$-tuple of zeros of the unique $\phi$-function
in Beurling's minimax-theorem as well as the
$n$-tuple $w^*_\bullet$.
A notable fact which also is due to Beurling
shows that the extremals
$\phi_*$ and $w_\bullet^*$ can be found
by
a variational  problem  using a suitable
Hilbert spaces.
More precisely, consider the Hardy space $H^2(D)$ of analytic functions 
$F(z)$ in
the unit disc  equipped with
the norm
\[
 ||F||_2=
\sqrt{\frac{1}{2\pi}\int_0^{2\pi}\,
|F(e^{i\theta})|^2}\, d\theta
\]
Given $E=\{\alpha_k\}$
we have the Blaschke product
\[ 
B_E(z)=\prod_{k=1}^{k=n}\, \frac{z-\alpha_k}{1-\bar\alpha_k\cdot z}
\]
With these notations one
considers the variational problem
\[ 
\max_F\, \sum_{k=1}^{k=n}\, \frac{|F(\alpha_k)|^2}{|B'_E(\alpha_k)|}
\]
with the maximum taken over $F$ of unit norm in
$H^2(D)$.
Beurling has proved that
this variational problem has a unique solution $F$
normalised so that $F(0)$ is real and positive. Moreover,
the maximum above is equal to
$\mathfrak{int}(E)$
and $F(z)$ is a zero-free analytic function in $D$
where  the $\beta$-zeros of  $\phi_*$  are  determined by 
the equation
\[
\prod_{\nu=1}^{\nu=n-1}\,
(\bar \zeta-\bar\beta_\nu)(1-\bar\beta_\nu\cdot \zeta)
=\prod_{k=1}^{k=n}\,|\zeta-\alpha_k|^2\cdot
\frac{\zeta\cdot F^2(\zeta)}{F^2(0)}
\quad\colon\, |\zeta|=1
\]







 
 






























\newpage


\centerline{\emph {0.5 Why one should study complex analysis}}


\bigskip




\noindent
Apart from its intrinsic beauty which  contains  residue theory and
conformal mappings, complex analytic methods
find 
applications  many areas
of mathematics.
Let us remark that
complex analytic functions are  special.
For example, an entire function $f(z)$
is  uniquely determined
by its values in a dense subset of  an arbitrary
small open interval on the real line. On the other hand
the class of entire functions is quite ample.
In  section XX from Special Topics we prove a result due to Weierstrass 
which asserts
that if  $g(x)$ is an arbitrary  complex valued function on
the real line  and $\epsilon>0$, then there exists an entire function
$f(z)$ such that $|f(x)-g(x)|<\epsilon$ hold for all real $x$.
Notice that this is far more precise than the trivial result that
approximation holds on compact subsets of the real line.
So just as in the case of Hadamard's
radius formula this 
result from 1861
is a good  example of "old vintage". 
\medskip

\noindent
{\bf{Resolvents of linear operators.}}
An example where analytic functions play a
crucial role occurs in spectral theory for linear operators.
Consider a
Banach space
$X$  and
$T\colon X\to X$ is a linear operator
whose domain of definition is a
dense subspace
$\mathcal D(T)$ of $X$.
 But $T$ is unbounded which means that
\[
\max_{x\in \mathcal D_*(T)}\, ||Tx||=+\infty
\]
where $\mathcal D_*(T)$ is the intersection of $\mathcal D(T)$ and 
the unit ball of vectors in
$X$ with norm $\leq 1$.
In addition we assume that $T$ is closed which means that
the graph
\[ 
\Gamma(T)=\{(x,Tx)\quad\colon x\in\mathcal D(T)\}
\]
is a closed subset of $X\times X$.
Let $T$ be such a linear operaor and denoted by
$E$ the identity operator on $X$.
\medskip

\noindent
{\bf{Definition.}}
\emph{A resolvent value of $T$ is a complex number $\lambda$
such that there range of 
$\lambda\cdot E-T$  is a dense subspace of  $X$ and there exists a positive constant
$c$ such that}
\[
||\lambda\cdot x-Tx||\geq ||x||\quad\colon x\in\mathcal D(T)\tag{i}
\]
Since $T$ is closed it easily follows from (i) that the dense range
$(\lambda\cdot E-T)(X)$ is equal to $X$ and there exists
a unique bounded linear operator $R(\lambda;T)$ on $X$ which is injective and has 
range equal to 
$\mathcal D(T)$ where
\[
R(\lambda;T)\circ(\lambda\cdot E-T)(x)= x\quad\colon x\in\mathcal D(T)
\]
and the composed operator $(\lambda\cdot E-T)\circ R=E$.
One refers to $R(\lambda;T)$ as the  resolvent operator of $T$.
The construction of such resolvents appeared
for the first time
in  Neumann's   article cited in § xx.
The crucial fact is that if $\lambda$ is a resolvent value of
$T$  then the open disc of radius $||R(\lambda;T)||$
centered at $\lambda$  give resolvent values and one has
the Neumann series
\[ 
R(\lambda+\zeta;T)=
R(\lambda;T)+\sum_{n=1}^\infty\, (-1)^n\cdot \zeta^n\cdot R(\lambda;T)^n
\quad\colon|\zeta|<||R(\lambda;T)||
\]
So if $T$ has at least one resolvent value the set of all
resolvent values is an open subset of ${\bf{C}}$ whose closed complement is
denoted by $\sigma(T)$ and called the spectrum of $T$.
A neat desription of $\sigma(T)$ is available using  the Neumann equation which
asserts that if $\lambda,\mu$ is an arbitrary pair of resolvent values then
\[
R(\lambda;T)-R(\mu;T)=\frac{
R(\lambda;T)R(\mu;T)}{\mu-\lambda}
\]
In the appendix devoted to Functional analysis we shall establish
the Neumann equation and use it to show
that
if $\mu$ is an arbitrary  resolvent value of $T$, then
\[ 
\sigma(T)=\{\mu-\frac{1}{s}\,\colon \,s\in \sigma(R(\mu;T))\setminus\{0\}\}\tag{ii}
\]
\medskip

\noindent
A special case occurs when one of the resolvents
$R(\mu;T)$ is a compact operator. Neumann's equation entails that 
all resolvent operators are compact operators and
(ii) implies  that $\sigma(T)$  is a discrete subset
of ${\bf{C}}$.
Situations where the resolvent operators are compact
occur in Fredholm's studies of integral equations and was
put into a general context by Hilbert in his work
\emph{Grundzüge einer allgemeinen Theorie der linearen
Integralgleichungen}
from 1904 which 
paved the way to the the theory about spectral
resolutions of  linear operators.
When $X$ is a Hilbert space
and $T$ a densely defined but unbounded self-adjoint 
operator   conclusive results were
established by Carleman in his book \emph{xxxx} from 1923. 
The  appendix devoted to
Funtional Analysis contains proofs of 
Carleman's spectral resolution for unbounded self-adjoint operators.
Here complex methods play a crucial role and  at the same time
the result has a wide range of applications to situations which at a first glance
seem to be of a "purely real character".
An example where Carleman's theory about unbounded self-adjoint operators
applies is
the product formula for
an arbitrary  densely defined and closed linear operator $T$ on a complex Hilbert
space.
It asserts that
there is a unique pair $P,A$ where $A$ is a densely defined self-adjoint 
operator and $P$ a partial isometry such that
\[ 
T=PA
\]
One can regard this as the ultimate polar representation of
complex objects. The proof is given in the appendix devoted to functional analysis.




\medskip



  
\noindent
{\bf{Applications to probability theory.}}
A
theorem due to Harald Cramér
asserts that if $\chi_1,\ldots,\chi_N$ is a family of independent
random variables whose 
sum variable $\chi_1+\ldots+\chi_N$ is normally distributed, then
each single $\chi_\nu$  has a normal distribution. This
is a useful  fact  for applications in  statistics. Using the existence of complex log\vvv functions of
entire functions without zeros the
proof 
boils down to show
that an entire function which only increases like $|z|^2$ is a polynomial 
of degre $\leq 2$. Staying with probability theorem we also recall
a result due to   Kakutani and Yosida where 
one regards
transition probability
functions defining a Markov process. These authors  proved
that under
a rather modest condition
there exists a finite partition of the given probability space
which consists of a  dissipative
part and a finite set of ergodic kernels where
the process stays once it has arrived to such  kernel.
The main steps  in the proof use analytic function theory
and  operators with complex eigenvalues. The proof
of the Kakutani-Yosida theorem
is exposed in
§ XXX,


\medskip

\noindent
{\bf{Linear algebra and Thorin's convexity theorem.}}
Let $A$ be an
$n\times n$-matrix with real elements $\{a_{k\nu}\}$.
To get 
zeros of the characteristic
polynomial $P_A(\lambda)= \text{det}(\lambda\cdot E_n-A)$
one must include those which are complex.  Denote by
$\rho(A)$ the maximum of the  
absolute value of these zeros. Now 
$R_A(\lambda)=(\lambda\cdot E_n-A)^{-1}$ is an analytic matrix-valued function
defined outside the spectrum $\sigma(A)$. From this it follows 
that $\rho(A)$ is equal to the spectral radius  computed via an
an
\emph{arbitrary norm} on ${\bf{R}}^n$. This  invariance  property
is
for example  used to study a matrix $A$ whose elements are positive
real numbers where the spectral radius formula 
gives a quick proof of 
a theorem  due to Perron and Frobenius which    asserts
that if $A$ is  a matrix with real and positive elements
then there exists a unique  a real eigenvector
${\bf{x}}$ where each $x_k>0$ such that $\sum\, x_k=1$
and $A({\bf{x}})= \rho(A)\cdot {\bf{x}}$.
This result is a cornerstone in linear programming where
one seeks solutions which are constrained to convex sets.
Another example where complex methods are  used appears in
Thorin's convexity theorem.
Let  $A=\{c_{\nu k}\}$ be an arbitrary
$n\times n$-matrix with complex elements. To each pair of real numbers
$0<a,b<1$ we set
\[ 
M(a,b)=\max_{x,y}\, |\sum\sum c_{\nu k}
\cdot x_\nu\cdot y_k\bigr |
\quad\colon\, \sum\,|x_\nu|^{1/a}= \sum\,|y_k|^{1/b}=1
\]
Via Hadamard's maximum principle for
analytic functions defined in  strip domains, Thorin proved
that the function
\[ 
(a,b)\mapsto \log M(a,b)
\] 
is convex in the square
$0<a,b<1$.
The fundamental theorem of algebra is of course a major motivation 
why complex numbers are so useful.
The variation of the argument for a complex-valued function which is $\neq 0$ along 
some curve
is a fundamental  issue.
Here is a result which
can serve as a first challenge for the reader and
will be explained in Chapter 4.
Consider a polynomial
\[ 
P(z)= z^{2n+1}+a_{2n}z^{2n}+\ldots a_1z+a_0
\] 
with real coefficients and
assume that the function
\[
P_*(iy)=\sum_{k=0}^{n}\, a_{2k}\cdot  (iy)^{2k}
\]
is $>0$ for all real $y$.
Then, if $n$ is even it follows
that
$P(z)$ has $n$ complex zeros counted with multiplicity in
the right half-plane $\mathfrak{Re}(z)>0$, while the 
number of zeros is $n+1$ if $n$ is odd.
For example, if $n=5$ and
\[ P(z)= z^5+Az^3+Bz+1
\] 
where $A,B$ is any pair of real numbers then
$P$ has two roots in $\mathfrak{Re} z>0$.
We shall learn that this follows since the real parti of 
$P(iy)$ is identically one on the imaginary axis
which implies
that the
variation of
$\arg(Piy)$  increases from
$-\pi/2$ when $y=-\infty$ to $\pi/2$ when $y=+\infty$
while the argument changes by $5\pi$
when we follows $\arg P(z)$ along a half-circle 
$\{ z=Re^{i\theta}\colon\, -\pi/2<\theta<\pi/2\}$
and then a general result from Chapter 4 gives the assertion about
the number of zeros in
$\mathfrak{Re}\ z>0$.









\newpage


\centerline{\emph{0.6 Jensen's formula and the Jensen-Nevanlinna class}}

\medskip

\noindent
One can say that modern analytic function theory started with a  discovery
by the
Danish telephone engineer Jensen. In 1899
he   proved that if $f(z)$ is analytic in a disc
$|z|\leq R$
where $f(0)\neq 0$, then
\[ 
\frac{1}{2\pi}\cdot \int_0^{2\pi}\, \log |f(Re^{i\theta})|\cdot d\theta=
\log |f(Re^{i\theta})|+
\log\,\frac{R^n}{|a_1|\cdots |a_n|}\tag{*}
\] 
where $\{a_k\}$ are the zeros of $f$ in the disc
$\{|z|>R$ repeated with their multiplicitites.
Today's student learns this theorem with relative ease, i.e.
one uses a factorisation to get rid of the zeros by a product  of Möbius functions and
after the mean value formula for a harmonic functions is applied.
But it took almost a century
until
familarity with complex analysis reached a stage when (*)
was announced. Jensen's formula is a cornerstone in
analytic function theory
and our  historic comment illustrates that today's student 
has to learn a lot of material in order to advance in
contemporary mathematics. 
Another  essential  result  is  Herglotz'  
integral formula which
exhibits an analytic function $f(z)$ in the unit disc
by its real part. Namely, if  $h(\theta)$ is
a continuous function on the unit circle there exists
an analytic function in the unit disc defined by
\[
\mathcal H(z)= \frac{1}{2\pi}\int\uuu 0^{2\pi}\, 
\frac{e^{i\theta}+z}{e^{i\theta}\vvv z}
\cdot h(\theta)\cdot d\theta\tag{**}
\]
One  refers to (**) as the Herglotz' extension of
$h$. It is  related to the given $h$\vvv function since the real part
$\mathfrak{Re}\, \mathcal F$ is expressed by Poisson's formula
\[
\mathfrak{Re} \, \mathcal H(z)= \frac{1}{2\pi}\int\uuu 0^{2\pi}\, 
\frac{1\vvv |z|^2}{|e^{i\theta}\vvv z|^2}
\cdot h(\theta)\cdot d\theta
\]
This means that   $\mathfrak{Re}\mathcal H\uuu u$
is  the harmonic extension of
$h$
to the unit disc.
Starting from (*) and (**)   
zero\vvv free functions were
analyzed by Jensen and Nevanlinna. Here
one takes exponentials and define
\[ 
F\uuu h(z)=
e^{\mathcal H(z)}
\]
This is a zero\vvv free analytic function in $D$ whose
absolute value is given by:
\[
|F\uuu h(z)|=
e^{\mathfrak{Re}\mathcal H\uuu u(z)}
\]
On $T$ we get the equality
\[
\log \,|F_h(e^{i\theta})|= h(\theta)
\]
and at the origin we find that
\[ 
\log F_h(0)= \frac{1}{2\pi}\int\uuu 0^{2\pi} h(\theta)\cdot d\theta
\]



\noindent
A more  extensive class of analytic functions in the unit disc are found
using
Herglotz's extensions of   signed
Borel measure $\mu$ on the unit circle. Here we get
\[
\mathcal H_\mu(z)= \frac{1}{2\pi}\int\uuu 0^{2\pi}\, 
\frac{e^{i\theta}+z}{e^{i\theta}\vvv z}
\cdot d\mu(\theta)\tag{***}
\]
and as above we 
get a zero-free analytic function $F_\mu(z)=e^{\mathcal H_\mu(z)}$. Next there exist
Blaschke products where
Jensen's integral formula gives a precise condition in order that
they converge and yield analytic functions in the unit disc with
prescribed zeros.
In §§ we construct the Jensen-Nevanlinna class of 
analytic functions $f$ in
the unit disc
which are charcterised by the property that
there exists a constant $C$ so that
\[
 \int_0^{2\pi}\, \log^+\,|f(re^{i\theta})\, d\theta\leq C
\quad\colon\, 0<r<1\tag{***}
\]
\medskip

\noindent
A major result due to Jensen and Nevanlinna asserts that when
(***) holds and $f(0)=1$
and $\{\alpha_\nu\}$ are the zeros of $f$
with multiple zeros repeated according to their multiplicities, then
there exists a unique Riesz measure $\mu$ on $T$ such that
\[ 
f(z)=B(z)\cdot e^{\mathcal H_\mu(z)}\quad\colon\,
B(z)=
\prod\,\frac{z-\alpha_\nu}{1-\bar\alpha_\nu\cdot z}
\]

\medskip


\noindent
{\bf{0.6.1 A special construction.}}
Let
$0<\delta<1$ and define the function $\phi(\theta)$ on $T$ by:
\[
\phi(\theta)=\log  (\delta^2-\theta^2)\quad\colon -\delta\leq \theta\leq \delta
\]
while $\phi=0$ outside this interval on $T$.
Now we get the analytic function $\mathcal H_\phi(z)$
and if
$K$ is  a positive integer we put 
\[ 
\Phi(z)=
e^{K\cdot \mathcal H_\phi(z)}
\]
On the unit circle we have
\[ 
|\Phi(e^{i\theta})|=
(\delta^2-\theta^2)^K\quad\colon -\delta\leq \theta\leq \delta
\]
while $|\Phi(e^{i\theta})|=1$ outside this interval. 
Next, let $\mu$ be a real-valued and non-negative Riesz measure
on the unit circle supported by $T\setminus [-\delta,\delta]$
and construct the zero-free analytic function $F_\mu(z)$ as above.
Set
\[ 
f(z)=F(z)\cdot \Phi(z)
\]
Notice that $|F(e^{is})|=1$ holds  on interval $(-\delta,\delta)$.
Let us then consider the complex derivative
$f'(z)$.
Here an upper bound exists for  radial limits
as we approach points in $(-\delta,\delta)$. More precisely one has:
\medskip

\noindent
{\bf{0.6.2 Proposition.}}
\emph{There exists an absolute constant $C$ which dpends on $K$ only
such that}
\[
\limsup_{r\to 1}\, |f'(re^{i\theta})|\leq C\cdot (\delta^2-\theta^2)^{K-2}\cdot ||\mu||
\quad\colon -\delta<\theta<\delta
\]
The proof employs Herglotz formula
which gives the equation below for every $z$ in the open unit disc:
\[
f'(z)=
\frac{1}{\pi}\cdot\bigl[
\int_{-\delta}^\delta\,
\frac{\phi(s)\cdot e^{is}}{(e^{is}-z)^2}\, ds+
\int\,
\frac{d\mu(s)\cdot e^{is}}{(e^{is}-z)^2}\, ds\bigr]\cdot f(z)
\]
Starting from this we will show Proposition 0.6.2 in
§ xx from the section devoted to the disc algebra in Special Topics.
where we 
expose  results due to Carleson about sets of uniquneness for analytic functions.
Apart for a number of conclusive  results
Carleson's constructions
provide some  concrete aspects in measure theory where
more refined questions   require that one goes
beyond the  notion of null-sets
in Lebegue's sense.




\medskip









\centerline {\emph{0.6.4 Logarithmic potentials.}}
\medskip








\noindent
A central  issue in these notes
are logarithmic potentials. 
A closed subset $E$ of the unit  circle $T$ has logarithmic capacity zero
if there exists a probability measure $\mu$ on $E$ such that
\[
\lim\uuu{r\to 1}
 \int\uuu E\, \log\,\frac{1}{|e^{i\theta}\vvv r\cdot e^{i\phi}|}
\cdot d\mu(\theta)=+\infty
\quad\text{for all points }\quad e^{i\phi}\in E
\]
Conversely, $E$ has positive capacity if there exists a probability
measure $\mu$ on $E$ such that
the limit of integrals above are bounded by a fixed constant  for
all $e^{i\phi}\in E$
which amounts to say that the energy integral
\[
J(\mu)=
\int_E \int_ E\, \log\,\frac{1}{|e^{i\theta}- e^{i\phi}|}\cdot d\mu(\theta)
\cdot d\mu(\phi)<\infty\tag{1}
\]
This energy integral is
related to
Dirichlet integrals. Namely, starting from $\mu$
we obtain a harmonic function  in the unit disc
defined by
\[
U_\mu(re^{i\phi})=
 \int\uuu E\, \log\,\frac{1}{|e^{i\theta}\vvv r\cdot e^{i\phi}|}
\cdot d\mu(\theta)\tag{2}
\]
Here $U_\mu$ is the real part of the analytic function
\[ 
F_\mu(z)=
 \int\uuu E\, \log\,\frac{1}{1-e^{-i\theta}z}
\cdot d\mu(\theta)
=\sum_{n=1}^\infty\,  \frac{\widehat{\mu}(n)}{n}\cdot z^n
\quad\colon\, \,\,\widehat{\mu}(n)=
\int_E\, e^{-in\theta}\, d\mu(\theta)\tag{3}
\]
Next, to every  analytic
function $f(z)$ in the unit disc one associates the Dirichlet integral
\[
\mathcal D(f)=\frac{1}{\pi}\iint_D\, |f'(z)|^2\, dxdy
\]
If $f(z)= f(0)+\sum\, a_nz^n$
the double integral becomes
\[
\sum_{n=1}^\infty\sum_{m=1}^\infty\, n\cdot a_n\cdot m\cdot \bar a_m
\cdot \frac{1}{\pi}\int_0^1\,\int_0^{2\pi}\,
r^{n+m-1}\cdot e^{i(n-m)\theta}\, d\theta\, dr
\tag{4}
\]
Since 
$\int_0^{2\pi}\,
 e^{ik\theta}\, d\theta=0$ for every non-zero integer
 it follows that (4) is equal to
 \[ 
 \sum_{n=1}^\infty \, n\cdot |a_n|^2
 \]




\noindent
So $f$ has a finite Dirichlet integral if and only if
 the sequence $\{\sqrt{n}\cdot a_n\}$
belongs to the Hilbert space $\ell^2_+$ of complex sequences
$\{c_1,c_2,\ldots\}$ for which
$\sum\, |c_n|^2<\infty$.
Analytic functions with a finite Dirichlet integral have special interest because
$\mathcal D(f)$ measures the area of the image domain $f(D)$.
When $f=F_\mu$ with $F_\mu$ as in (3) one has
\[ 
\mathcal D(F_\mu)=\sum\, \frac{1}{n}\cdot |\widehat{\mu}(n)|^2
\]
Next, when (1) is finite one has the limit formula
\[ 
J(\mu)= \lim_{r\to 1}\,
\int_E \int_ E\, \log\,\frac{1}{|1- r\cdot e^{i\phi-\theta}|}\cdot d\mu(\theta)
\cdot d\mu(\phi)<\infty
\]
Expanding the log-function one gets the equality
\[ 
J(\mu)=\mathcal D(F_\mu)\tag{5}
\]


\noindent
Beurling used the
formulas
above  in
the article \emph{Ensembles exceptionnels}
from 1940 to  prove that
when
$f$ is an  analytic function in the unit disc with
a finite Dirichlet integral, then the radial limits
\[
\lim_{r\to 1}\, f(re^{i\theta})= f^*(\theta)
\] 
exists for all $\theta$ outside a set whose logarithmic capacity
is zero.
Beurling's theorem is  established 
in § XX from Special Topics.
\medskip



\centerline{\emph{0.6.5 Carleson's extremal functions.}}
\medskip


\noindent
The results above suggest the   study
of pairs $(f,E)$ where
$E$ is a closed set with positive logarithmic capacity while
$\mathcal D(f)$ is finite
and the boundary value function $f^*$ is zero on $E$.
Denote this family
by
 $\mathcal D_E$.
In the article \emph{Sets of uniqueness for functions regular in
the unit disc} [Acta 1952]  Carleson
studied the situation where
$\mathcal D_E$ contains non-constant functions while
$E$ has positive logarithmic capacity.
Let
$\mathcal D^*_E$
be the  subfamily
of functions
$f\in\mathcal D_E$ where
$f(0)=0$ and consider
the variational problem
\[
\inf_{f\in \mathcal D^*_E}\, D(f)
\]
Carleson proved that
there exists a unique $f\in \mathcal D^*_E$
with minimal Dirchlet integral 
with the property that the complex derivative
$f'(z)$
extends to an analytic function in
${\bf{C}}\setminus E$.
This  result is established  in  Special Topics § XX.
The
reader who can pursue the details of Carleson's proof with the aid of
material from earlier  chapters has attained
good familarity with analytic function theory.

\medskip

\noindent
{\bf{Remark.}} We inserted some   details 
at this early stage
in order to illustrate what these notes are striving at.
The
proofs  are not
"sophisticated"  
but  contain often  a   sequence of seemingly  unrelated
threads which   constitute the
innovative part where 
more delicate  results
often rely upon  innovative
constructions which
are not 
predicted in advance. A brilliant
example is
Carleson's construction  from § XX 
of a compact set on the unit interval with  positive logarithmic capacity
while it has
vanishing Hausdorff measures for all $h$-functions satisfying
\[
\int_0^1\, \frac{h(r)}{r}\ dr<\infty
\]

\noindent
The main lesson  is  therefore to
study 
details of separate proofs
and in this way become sufficiently familiar with  methods to
be able to make new discoveries.










\newpage


\centerline {\emph{0..7 Riemann's  $\zeta$-function.}} 
\bigskip

\noindent
These   notes are foremost directed to students  
who are  familiar with
undergraduate calculus and   want to encounter  more advanced 
topics in analysis.
While entering such studies it is good
to have a goal. I cannot imagine anything
more appealing  than to
learn about Riemann's  zeta-function defined by the series:
\[
\zeta(s)=\sum_{n=1}^\infty\, \frac{1}{n^s}\,,\quad\mathfrak{Re}\, s>1\,.
\]
The first result   is due to Euler and
asserts  that $\zeta(s)$  extends to a meromorphic
function defined in the whole complex $s$-plane with a simple pole at $s=1$
and
the entire function
$(1-s)\zeta(s)$
has simple zeros at all even negative integers
while  the remaining zeros belong to the strip domain
\[ 
0<\mathfrak{Re}\, s<1
\]

\noindent
In a work which dates back to 1859, Bernhard Riemann conjectured that
the zeros of the zeta-function 
belong to the line
$\mathfrak{Re}\, s=\frac{1}{2}$.
Numerical
calculations  confirm the hypothesis up to a very high degree.
So it is not  likely that one may discover an eventual  zero outside the critical line
by mere guessing.
But there  remains to \emph{prove} the hypothesis.
The study of the zeta-function has contributed to the development in
analytic function theory.
An example is the 
asymptotic formula for the zeros 
in the critical strip $0<\mathfrak{Re}(s)<1$
which was already announced by Riemann.
It asserts that there exists a constant $C_0$
such that 
if $\mathcal N(T)$ is the number of zeros counted
with multiplicities in the rectangle where
$-T<\mathfrak{Im}\,s<T$ and $0<\mathfrak{Re}\,s<1$,
then 
\[
\mathcal N(T)=\frac{1}{\pi}\cdot T\cdot\text{Log}\,T-
\frac{1+\text{Log}\,2\pi}{\pi}\cdot T+\rho(T)\cdot \text{Log}\,T\quad\text
{where}\quad 
\,|\rho(T)|\leq C_0\tag{*}
\]

\noindent
where the constant $C_0$ is indepenent of $T$.
We  prove (*) in the chapter  devoted to Riemann-s $\zeta$-function
whose content
should  be more than
sufficient to convince that analytic function theory in one complex variable
is as active as ever within the  curriculum of mathematics.
Anybody who  tries  to attack the Riemann Hypothesis
must be well aquainted  with
function theory and harmonic analysis.
This explains  why these notes
in addition to analytic function theory
contains extensive material about
the Fourier transform.
Let us illustrate  this interaction 
by the following formula 
which at first sight appears to "almost settle" the Riemann hypothesis:
Hardy 
proved the equality below when $\mathfrak{Re}\, s>1$: 
\[ 
\zeta(s)=\frac{\pi^{\frac{s}{2}}}{\Gamma(\frac{s}{2})}\cdot
\int_0^\infty \omega(x)\cdot x^{\frac{s}{2}-1}\cdot dx
\quad\colon\quad \omega(x)=\sum_{n=1}^\infty\,
e^{-n^2\pi x}\tag{**}
\]
where $\Gamma(s)$ is the Gamma-function.
The constraint $\mathfrak{Re}\, s>1$
is needed to ensure that the integral in the right hand side is defined since
one has the asymptotic formula
\[
 \omega(x)\simeq\frac{1}{\sqrt{x}}\quad\, x\to 0
\]
 A major fact 
to be proved in 
these notes
is that
$\frac{1}{\Gamma(s)}$ is an entire 
function 
of the complex variable
$s$. So (**) can be used to investigate
zeros of the zeta-function after its meromorphic continuation is
constructed via the Dirichlet integral of the $\omega$-function.
The equation (**)   was used by Hardy in [Ha] to demonstrate that a
"considerable amount" of zeros 
belong to
the critical line
$\mathfrak{Re}\, s=1/2$.
\medskip

\noindent
{\bf{Beurling's criterion.}}
A necessary and sufficient condition for the validity of the Riemann hypothesis
was presented  by Beurling in the article \emph{A closure problem related
to the Riemann zeta\vvv function} and 
goes  as follows: Denote by  $\rho(x)$  the
numerically smallest remainder term modulo 1, i.e.
$\rho(x)= x$ if $0 < x<1$ and $\rho(x+1)= \rho (x)$
for all real $x$.
Given some $N\geq 2$ and an $N$\vvv tuple of real numbers
$0<\theta\uuu\nu< 1$ and real constants
$c\uuu 1,\ldots,c\uuu N$ such that
$\sum\, c\uuu \nu\cdot \theta\uuu \nu=0$ we define a function $f(x)$ on 
the unit interval $(0,1)$ by
\[
 f(x)=\sum\uuu{\nu=1}^{\nu=N}\, c\uuu \nu\cdot \rho(\frac{\theta\uuu\nu}{x})
\]


\noindent
{\bf{Theorem.}} \emph{The Riemann hypothesis is valid if and only if for each
$\epsilon>0$ there exists some $N$ and a pair
of
$N$\vvv tuples
$\{\theta\uuu\nu\}$ and $\{c\uuu\nu\}$ as above such that}
\[
\int\uuu 0^1\, (1\vvv f(x))^2\cdot dx<\epsilon
\]
\medskip

\noindent
The sufficieny, i.e. that the existence of $f$\vvv functions which
approximate the identity function in the $L^2$\vvv norm gives the Riemann Hypothesis
is easy to prove, while 
the proof of
necessity relies upon an ingenious blend of
functional analysis and analytic function theory.
Personally I find Beurling's proof exceedingly instructive and hope that this
will be shared by the reader. For details we refer to section xx in Chapter VIII.
\medskip


\noindent
{\bf Alan Turing and the
$\zeta$-function.}
The creation of
computers 
is 
foremost due to
Turing and  von Neumann.
Less wellknown
is perhaps that Turing also was  fascinated by the
zeta-function.
His article
\emph{A method for the calculation of the zeta-function} from 1943
already suggested  his ambition  to
build an analog computer specifically intended
for calculating values of $\zeta(s)$.
A decade later his
article \emph{Some calculations of the Riemann
zeta-function} 
gave 
the first extensive calculations of zeros of $\zeta(s)$  by a computer.
This historic
reconcilation  illustrates how
problems in mathematics
has  stimulated advancement in  applied areas
of science. The 
reader  may  consult the
article by Dennis Hejhal in [Hej] for
a further account about Turing's work related to the
$\zeta$-function and up-to-date
references about the zeta-function.

\newpage




\centerline {\emph{0.8 Kepler's equation and Lagrange's problem}}
\medskip



\noindent
During  intense calculations based upon
astronomic data
in the beginning of 1600, Kepler
encountered the equation
\[ 
\zeta_a(z)=a+z\cdot \text{sin}(\zeta_a(z))\tag{*}
\]
where $a>0$ is a positive constant which
may vary.
At that time
analytic function theory did not exist and Kepler
could only manage to derive a part of the series expansion of the $\zeta_a$-function.
In 1760  Lagrange  found the whole series expansion
of $\zeta_a(z)$
and  proved that it is analytic in a disc centered at $z=0$ 
whose radius of convergence $\rho$ is
independent of $a$.
However, no exact formula for $\rho$ is known, i.e. it can only be
found numerically.
Personally I find historic examples of this kind
both instructive and exciting since
they illustrate how  
"heroic efforts"  have preceded
a "more developed theory".
In these notes the reader will learn
how basic analytic function theory
can be applied   to obtain Lagrange's  result about Kepler's 
$\zeta_a(z)$-functions.








\medskip



\noindent
\emph{A problem by Lagrange.}
Let us give another  early example where 
complex methods appear naturally.
In a  work from 1782
Lagrange studied the motion of the planets in the solar system
which by Newton's  Law of gravity amounts to solve the
$N$-body problem with
$N\geq 3$. As a first approximation
for "la longitude du périhélie de l'orbite d'une planete
au temps $t$" one needs to determine the argument of a complex-valued 
trigonometric polynomial
\[
 F(t)= a_1e^{i\lambda_1t}+\ldots+a_Ne^{i\lambda_N t}
\]
where $\lambda_1,\ldots,\lambda_N$
are distinct real numbers and
$a_1,\ldots,a_N$
some $N$-tuple  of complex numbers.
Assume that $F(t)\neq 0$ for all $t\geq 0$.
Then there exists  a continuous argument function
$\psi(t)$ of $F$ such that:
\[ 
F(t)=|F(t)| \cdot e^{i\psi(t)}\quad\colon t\geq 0\,.
\]
When $|a_N|>|a_1|+\ldots +|a_{N-1}|$
it is easily seen that
\[ 
\lim_{T\to\infty}\, \frac{\psi(T)}{T}=\lambda_N\,.\tag{*}
\]
Lagrange posed the question if there exists a limit in
the general case when no single $a$-coefficient has a dominating
absolute value. This problem  with its source in astronomy
has led to interesting results in analytic function theory.
In 1908 it was proved by Bohl that (*) always has a limit
when $N=3$. 
For $N\geq 4$ quite general results were found  by
Weyl and later work has studied
the existence of (*) for the more extensive class of
almost periodic analytic functions.
Let us also  mention that
the study of (*) is closely related to find
zeros of analytic functions in  vertical strip domains.
More precisely, given $F(t)$ as above it is the restriction 
of an entire function
$F(\zeta)$
to the
imaginary axis in the complex
$\zeta$-plane where
$\zeta=\sigma+it$.
For each real $\sigma$
it turns out that there exists the limit
\[
\phi(\sigma)= \text{Lim}_{T\to\infty}\,
\frac{1}{T}\int_0^T\,\text{log}\, |F(\sigma+it)|\cdot dt\,.
\]
A result due to B. Jessen and M. Tornehave in their joint article [Je-Torn]
from 1945 shows that  the $\phi$-function is continuous and
convex with respect to
$\sigma$ and has an ordinary derivative
outside a set which contains at most denumerable many points.
Moreover, assuming that
$\phi$ has a derivative at $\sigma=0$
one has
the equality
\[
 \text{Lim}_{T\to\infty}\,\frac{\psi(T)}{T}=\phi'(0)\,.
 \]
Finally the derivatives of the $\phi$-function 
determine the asymptotic number of zeros of
$F(z)$. More precisely, for a given
pair of real numbers
$a<b$ we denote by
$N_{a,b}(T)$ the number of zeros of
$F(\zeta)$
in the  domain $\{\zeta=\sigma+it\,\,\colon\,\,
a<\sigma<b\,\,\text{and}\,\, 0<t<T\}$.
Then
\[
\text{Lim}_{T\to\infty}\,\frac{N(T)}{T}=
\frac{\phi'(b)-\phi'(a)}{2\pi}
\]
hold when $\phi$ has a derivative at $a$ and $b$.
Results of this kind illustrate the rich interplay between
analytic function theory and
other areas of mathematics.



\bigskip

\noindent
\centerline{\emph{Conformal mappings.}}
\medskip

\noindent
In the 3-dimensional space
${\bf{R}}^3$ with coordinates
$(x,y,z)$
we  consider  a surface $S$ defined   by an equation
\[ 
z=g(x,y)
\] 
where $g$ is a real-valued 
function which
is real-analytic as a function of the two real variables
$(x,y)$.
One may imagine a  portion of such a surface which is
defined when
$(x,y)$ stays in a small square 
$\square$
centered at the origin in
${\bf{R}}^2$. Given an arbitrary   point $p=(x,y,g(x,y))$
on $S$  we  consider a pair of curves
$\gamma$  and $\rho$ passing through $p$.
They intersect at $p$ with some angle denoted by
$\langle\gamma,\rho \rangle$. Next, let
$(\xi,\eta)$ be another set of coordinates
in ${\bf{R}}^2$
and consider a map
\[ 
\phi \colon\, (x,y,g(x,y))\mapsto (\xi(x,y),\eta(x,y))
\]
Working locally we assume that the map is a diffeomorphism
and preserves orientation
which means that the Jacobian  $\xi_x\cdot\eta_y-\xi_y\cdot \eta_x>0$.
Now we can consider the $\rho$-images of a pair of curves
$\gamma,\rho$ as above and in the $(\xi,\eta)$-plane we regard
the angle between these two plane curves.
If the angle is preserved for every pair of curves passing through
arbitrary
points on $S$ one says that $\phi$ is an \emph{conformal }
representation of $S$ onto a plane. 
The first example of such a conformal map goes back to the astronomer Ptolemy
who considered the  case when
$S$ is a portion of a sphere and found the answer by 
the  
\emph{stereographic projection} which  has become a
useful  in
analytic function theory.
Recall also that
Mercator constructed another conformal map
in 1568 which  has been adopted for the construction of sea-maps.
In  1779 Lagrange classified all locally defined conformal maps
from a portion of the sphere  onto the plane and
in 1821 Gauss described the whole  family of locally defined
conformal maps from
an arbitrary surface $S$  onto a planar domain.
A turning point which led to the contemporary
analytic function theory was discovered by Riemann
in his thesis from 1851. He introduced  ideas which have been
used in later investigations  of conformal representation
and  showed that the problem itself is of fundamental
importance for analytic function  theory.
A major result  
is that every bounded and 
simply connected domain in
 ${\bf{C}}$
 is conformal with the open unit disc $D$.
This  is called  \emph{Riemann's Mapping Theorem}.
The first rigorous proof was given  in 1865
by
Hermann Schwartz.
More generally there is a
mapping theorem for an arbitrary connected 
domain $\Omega$ in ${\bf{C}}$. For topological reasons
we cannot find a conformal map from $\Omega$ onto $D$. But there exist
locally conformal maps from $\Omega$ onto $D$ expressed by
\emph{multi-valued} analytic functions on
$\Omega$ which  are  used to obtain a
holomorphic function $g(z)$ defined in
$D$ such that
the complex derivative
$g'(z)\neq 0$ for all points and
the image $g(D)=\Omega$.
This   identifies  the fundamental group of
$\Omega$ with a group of Möbius transformations 
on the unit disc $D$.
Starting from this fact, 
Poincaré began to investigate general groups of Möbius transformations.
He considered  to begin with  a discontinuous group $\mathcal F$
of Möbius transforms on $D$
without a fixed point. For such a group
there exists a
normal domain $U$
inside $D$  characterized by the property
that every orbit under
$\mathcal F$
intersects $U$ in exactly one point.
This result, proved   
in his  article \emph{Théorie des groupes
fuchsien} was published in the first volume of
Acta Mathematica in 1882.
All this may  at first glance appear as "classic old stuff". But the truth is that
the
visions by Riemann and Poincaré continue to
serve as an inspiration in contemporary mathematics.
To this one should also say that analytic function theory in one
variable already had reached a quite advanced level
more than a century ago. 
For example, a result which goes
beyond
the material in these notes is the study of
the differential equation
$\Delta(u)= e^u$
where one seeks a solution
$u$ defined on  a closed Riemann surface with
prescribed singularities.
This second order differential equation was completeley 
solved by
Poincaré in his article [Poinc]
\emph{Les fonctions fuchsiennes et l'équation
$\Delta(u)= e^u$} from 1898. 



\medskip

\centerline
{\emph{0.9 The Dagerholm series and comments on
more recent theories.}}
\medskip


\noindent
Of course, many results in these notes
are of a more recent origin. An example is
an extension of the
Riemann Mapping Theorem by
Beurling from  an article published in  1953.
A result which 
illustrates that  more
recent theorems  also are    concerned with  
"concrete problems" was published in 1968
by Karl Dagerholm who    was 
Beurling's first Ph.d student from Uppsala University in
1938, and thirty  years later Dagerholm  was finally able to prove
the following  result which had remained as an open question from his
thesis:

\bigskip

\noindent
{\bf Theorem.} \emph{Up to multiplication with a real  number
there exists a unique  sequence
$\{x_q\}$ of real  numbers which is not identically zero and solves the
infinite system of  equations}
\[ 
\sum_{q\neq p}\,\frac{x_q}{p-q}=0\quad\colon\quad p=1,2,\ldots\quad
\text{where}\,\, \sum_{q=1}^\infty\, \frac{x_q}{q}\,\,\,\,\text{is convergent}.
\]
As we shall see the proof this result
employs many   ingredients from analytic function theory.
\medskip

\noindent
{\bf{The Hayman-Wu constant}}.
To illustrate  that analytic function theory
in one complex variable  
contains many active research areas  
we mention the following  open problem:
Let
$\phi\colon D\to \Omega$ be a conformal map from the unit disc onto
a simply connected domain $\Omega$. 
Now $\mathfrak{Im}(\phi)$ is a harmonic function in
$D$ whose gradient is everywhere $\neq 0$.
As we shall explain later on this implies that
the zero set $\{\mathfrak{Im}(\phi)=0\}$
is a union of disjoint open Jordan
arcs
$\{\gamma_k\}$
where each single arc has two end-points on
the unit circle $\partial D$. 
Denote by  $\ell(\gamma_k)$  the arc-length of 
each individual Jordan arc.
In 1981 it was proved by Hayman and Wu
that there exists an absolute constant $C$ such that
\[
\sum\,\ell(\gamma_k)\leq C\tag{*}
\]
The remarkable fact is  that
$C$ is independent of the conformal map.
To find the best constant in (*) is an open
problem.
So far one knows that $C$ is strictly smaller than
$4\pi$ [Rohde 2002] and at least $\pi^2$ [Öyma 1993].

\medskip

\noindent
{\bf{Remark.}} 
The text-book [GM]
\emph{Harmonic measure} by
John B. Garnett and Donald E. Marshall
has been an inspiration for these notes. Actually
I  started to write these notes
to provide 
background for
the reader who wants to study more advanced topics in
[GM]. But as in most projects of this  sort
my original   material eventually expanded and cover
subjects in   analytic function theory
which are not within the main streamline
in [GM].
In any case, this text-book is highly recommended.
For example, Chapter V  offers a brilliant
account of  results due to Lars Ahlfors and  contains also an
introduction to the 
theory  of extremal distances which was created by
Arne Beurling during the years 1943-44 and 
presented in his article [Beurling] from 1946.
An example of a result which goes   beyond the scope of these notes
appears in  [GM;  Chapter V : Theorem 2.1]
which  gives a 
quite sharp lower bound for harmonic measures.
See also Chapter XX in R. Nevanlinna's text-book
[Nev] where
the Carleman-Milloux problem  is studied via
certain solutions which were found independently by Nevanlinna and Beurling in 1933.
In these notes we are content to establish results which provide
upper bounds for harmonic measures in various situations.

\bigskip




\centerline{\emph{0.10 Mathematical physics.}}
\medskip

\noindent
Analytic function theory  of one complex variable
is often used in mathematical physics.
An  example is the  \emph{Biot-Savart Law} which was
discovered in 1800 and 
inspired the development of analytic function theory.
In 1879 the  electric engineer Robin posed a quite general
problem which
led to the study of thin sets and various potential theoretic questions.
The special case occurs
when $\Gamma$ is a   closed
Jordan curve in the complex $z$-plane.
To determine a density function which gives
electric equilibrium on
$\Gamma$ amounts to find a
positive function
$\mu$ on $\Gamma$ such that the logarithmic potential
\[
\int_\Gamma\, \log\, \frac{1}{|q-p|}\cdot
\mu(p)\cdot ds(p)\quad\colon\quad  q\in\Gamma\tag{*}
\]
where $ds(p)$ is the arc-length along $\Gamma$ and one requirs that
(*) is 
constant as 
$q$ varies on $\Gamma$.
Riemann demonstrated the existence of such a density
by
his conformal mapping theorem. More precisely,
the equilibrium  density is  unique and equal to a constant times
$\frac{1}{|f'(z)|}$ where $f'(z)$ is the complex derivative of the
conformal map from
the \emph{exterior domain} bordered by $\Gamma$ to the
exterior disc
$|w|>1$ in the complex $w$-plane. 
We  prove this result   in the chapter
devoted to conformal mappings.
This example
is instructive since  it shows
that one should 
be aware of the point at infinity. This was
the reason why Riemann  introduced the Riemann sphere in his fundamental work
[Rie:xx] from 1857. 
Let us also remark 
that analytic function theory does not
"cover everything" as the following   example shows.
A classical result due to Helmholtz about
stationary fluid motion in the plane
asserts that if
$\Omega$ is a Jordan domain
and the function
\[ z\mapsto \iint_\Omega\,\text{log}\,\frac{1}{|z-\zeta|}\cdot d\xi d\eta\tag{i}
\]
is  constant on
$\partial\Omega$, then
$\Omega$ must be a disc.
This fact has a natural physical explanation.
Less obvious is that that $\Omega$ also must be a disc if
(i) holds when  the log-potentiao is replaced by
an integrand  of the form
$f(|z-\zeta|)$, where $f(r)$ is an arbitrary
strictly decreasing function  
defined on $r\geq 0$.
Here the proof uses calculus of variation and the
symmetrization process due to W. Gross. See § XX in special topics 
where the asserted result is proved.

\medskip

\noindent
{\bf{The use of majorant series.}}
The idea to use majorant series is due to Cauchy and
is often used to prove existence results for non-linrear
equations.
Let us give an example where Cauchy's method applies.
Let $\Omega$ be a bounded open domain
in ${\bf{R}}^3$ whose boundary $\partial\Omega$
is of class $C^1$. Let $p=(x,y,z)$ denote points in
${\bf{R}}^3$. 
The equation
which obeys the Stefan-Bolzmann law
for heat conduction  of 
Black Bodies is to find a function
$u$ which  is harmonic in
$\Omega$ outside a  point $p_*$ (the source of heat)
where $u(p)$ is locally of the form
$\frac{1}{|p-p_*|}$ plus a harmonic function.
On the boundary its   interior normal derivative satisfies:

\[ 
\partial u/\partial {\bf{n}}=k\cdot u^4\quad\colon\,\,k>0\tag{*}
\]
Green's formula  shows that  
the solution to (*) is unique if it exists.
The proof of existence
is achieved by regarding intermediate equations
where $u_h(p)$ for every $0<h<1$ 
is a solution with the pole at $p_*$ as above and
\[ 
\partial u_h/\partial {\bf{n}}=k\cdot ((1-h)u_h+ h\cdot u_h^4)\tag{**}
\]
Using the robust properties of solutions to Neumann's 
linear boundary value problem one shows that if $0\leq h_0<1$
is given and  the unique solution
$u_{h_0}$ has been found,  then 
(**) is solved for $h$-values in some interval $h_0<h<h_0+\delta$
via a series expansion $u_h=u_{h_0}+\sum_{\nu=1}^\infty\,
(h-h_0)^\nu\cdot w_\nu$. Here   $\{w_\nu\}$ are functions which
are found inductively by solving 
a system of  \emph{ linear}  boundary
value problems.
In this way the main burden to obtain a solution to the non-linear 
Stefan-Boltzmann equation is to prove that various series
admit a positive radius of convergence.
In XX we expose Carleman's methods from [Car]
to solve the more general  non-linear boundary value 
problem 
where one  seeks $u$ as above in $\Omega$ while
\[
 \partial u/\partial{\bf{n}}(p)= F(u(p),p)\quad
\colon  p\in\partial\Omega\tag{***}
\]
Here the sole condition is that
$F(u,p)$ is a on-negative continuous function defined on ${\bf{R}}^+\times
\partial\Omega$, and for each fixed
$p\in\partial\Omega$ the map 
 $u\mapsto F(u,p)$ is increasing
and tends to $+\infty$ with $u$.
  
\bigskip

\noindent
{\bf{Another boundary value problem.}}
Let  $\Omega$ be a bounded domain in
the real $(x,y)$\vvv plane of class $\mathcal D(C^1)$, i.e. the boundary
is a finite union of disjoint and closed differentiable Jordan curves.
Denote by  
$\Delta=\partial\uuu x^2+\partial\uuu y^2$  the Laplace operator.
One seeks functions
$\phi(x,y)$ which satisfy
\[ 
\Delta(\phi)+\lambda\cdot \phi=0
\] 
in $\Omega$ for some constant $\lambda$
where $\phi=0$ on the boundary
$\partial\Omega$.
This equation has solutions for a discrete sequence of eigenvalues
$\{\lambda\uuu n\}$ where
$0<\lambda\uuu 1\leq \lambda\uuu 2\leq \ldots$ and the corresponding eigenfunctions
$\{\phi\uuu n\}$ are normalised so that the integrals
\[
\iint\uuu\Omega\,  \phi\uuu n(x,y)^2\, dxdy=1
\]
Moreover, these $\phi$\vvv functions can be chosen to be
pairwise orthogonal
when we take area integrals.
This is  proved by
classical methods using 
Fredholm determinants and  hence  only  calculus in real
variables is used, while  
analytic function theory is needed to
study  asymptotic properties.
Tohe crucuial result gies as follows where
$s$ is  a complex variable and $p$ a variable point in
$\Omega$:


\medskip

\noindent
{\bf{Theorem.}} \emph{The series}
\[ 
\Phi(s)= \sum\uuu{n=1}^\infty\, \frac{\phi^2\uuu n(p)}{\lambda\uuu n^s}
\]
\emph{is a meromorphic function of $s$ defined in the whole complex $s$\vvv plane
which is independent of the point $p\in\Omega$.
Moreover, $\phi$ has a simple pole at $s=1$ whose residue is
$\frac{1}{4\pi}$ and it has zeros at all non\vvv positive integers.}
\medskip

\noindent 
Using Tauberian theorems which also are derived via analytic function theory
one gets
the following asymptotic formula:

\medskip

\noindent
{\bf{Theorem.}} \emph{Let $S$ be the area of $\Omega$. Then}
\[ 
\lim\uuu{n\to \infty}\,
\frac{1}{n}\cdot \sum\uuu{\nu=1}^{\nu=n}\, \phi^2\uuu\nu(p)= 
\frac{1}{S}
\]
\emph{hold for each $p\in \Omega$.}
\medskip

\noindent
{\bf{Remark.}} 
Results such as thoses above 
illustrate that one  attains "muscles" via 
studies in analytic function theory
in order to establish  asymptotic results for solutions to
 PDE\vvv equations.
 






  
\bigskip
  
\noindent
{\bf{Quantum mechanics.}}
Analytic function theory as well as
extensive use of Fourier integral operators occur also in
quantum mechanics while one investigates special 
equations. For example, confluent 
hypergeometric functions appear as  solutions
in a Coulomb field   and to 
continue the study of scattering in a Coulomb field
where the quantum\vvv mechanical collision problem can be solved exactly,
it is from a physical point of view important
to analyze
the asymptotic behaviour of confluent
hypergeometric functions. Here  asymptotic expansions
are
derived via 
complex line integrals where  attention must be given
to the choice of local branches of certain multi\vvv valued analytic functions.
Examples of this kind illustrate that  classical topics in analytic function theory
remain  "up\vvv to date" since they provide useful
tools in quantum mechancs.
It would lead us to far to even try to 
give a glimpse of the physical theories.
For the mathematically oriented reader 
we recommend the outstanding text\vvv books 
by L.D. Landau and his former student E.M Lifschitz.
The third edition of \emph{Non\vvv relativistic quantum mechanics}
is especially recommended.









\end{document}