                                                                                                                                                             
\documentclass{amsart}
\usepackage[applemac]{inputenc}
\addtolength{\hoffset}{-12mm}
\addtolength{\textwidth}{22mm}
\addtolength{\voffset}{-10mm}
\addtolength{\textheight}{20mm}
\def\uuu{_}

\def\vvv{-}                                                                                                                                                                                                                                                                                                                                                         


\begin{document}

\newpage

                        
\centerline {\bf{The $p^*$-function.}}
\medskip

\noindent
We  shall construct a special harmonic function which 
is  used
to get solutions of the Dirichlet problem.
Let $\Omega$ be an open and connected set in
${\bf{C}}$ and consider the connected components of
its 
closed complement.
Let $E$ be
such a connected component which is not reduced to a single point.
Let us then consider some closed and simple Jordan curve $\gamma$ 
contained in $\Omega$. For each point $a\in E$
there exists the winding number
$\mathfrak{w}_a(\gamma)$
defined by
the integer
\[
\frac{1}{2\pi i}\int_\gamma \, \frac{dz}{z-a}
\]
If $b$  is another point in the connected set 
$E$  the continuity of the integer-valued winding number
implies that 
\[
\mathfrak{w}_a(\gamma)=\mathfrak{w}_b(\gamma)\tag{*}
\]
This  equality  yields  
a single-valued analytic function
in $\Omega$ given by
the difference
\[
\text{log}\,(z-a)-\text{log}\,(z-b)
\]
Taking the exponential we find
an analytic function $\psi(z)$ in $\Omega$ such that
\[
e^{\Psi(z)}=
\frac{z-a}{z-b}
\]


\noindent
Since $a\neq b$
we see that
$\Psi(z)\neq 0$
for all $z\in\Omega$ and obtain the 
harmonic function  in 
$\Omega$
defined by
\[
p(z)=\mathfrak{Re}\bigl(\frac{1}{\Psi(z)}\bigr)=
\frac{\mathfrak{Re}(\Psi(z)}{|\Psi(z)|^2}\tag{*}
\]


\noindent
Next, we have
\[
\mathfrak{Re}(\Psi(z))=\text{Log}\, |z-a|-\text{Log}|z-b|
\]
and since
$\text{log}\, |z-a|\to-\infty$ as $z\to a$
we see from (*) that
\[
\lim_{z\to a}\, p(z)=0\tag{**}
\]


\noindent
Notice also that
$\Psi(z)$ exends to a continuous function on
$\bar\Omega\setminus (a,b)$ and we can
choose a small $\delta>0$ such that
\[ 
\text{Log}|z-a|-\text{Log}\,|z-b|<-1\quad\colon\quad
|z-a|\leq\delta\tag{ii}
\]

\noindent 
From the above we can conclude:


\medskip

\noindent {\bf 7.1 Theorem.}
\emph{Let $a\in\partial\Omega$ be such that
the connected component of ${\bf{C}}\setminus \Omega$
which contains $a$ is not reduced to the single point $a$.
Then there exists a harmonic function
$p^*(z)$
in $\Omega$
for which}
\[
\lim_{z\to a}\, p^*(z)=0
\]
\emph{and there exists $\delta>0$ such that}
\[
0<r<\delta\implies \max_{\{|z-a|=r\}\,\cap\Omega}\, p^*(z)<0\quad\colon\quad
\]
\newpage 

\centerline{\bf 1. The Dirichlet Problem.}


\bigskip

\noindent
{\bf Introduction.}
Let $\Omega$ be a bounded open set
in ${\bf{C}}$.
No connectivity assumptions are imposed, i.e. neither
$\Omega$ or $\partial\Omega$ have to be connected.
To each  
$\phi\in C^0(\partial\Omega)$
we shall construct a harmonic 
function $H_\phi$  in $\Omega$ by a contruction due to 
Perron. Denote by
$\mathcal P(\phi)$  the family of  subharmonic functions $u(z)$ in 
$\Omega$ satisfying
\[
\limsup_{z\to w}\,u(z)\leq \phi(w)
\quad\colon\, w\in\partial\Omega\tag{0.1}
\]


\noindent 
One verifies that
the
function defined for $z\in \Omega$ by 
\[
H_\phi(z)=\max_{u\in\mathcal P(\phi)}\, u(z)\tag{*}
\]


\noindent
is  harmonic in $\Omega$. A boundary point $a$ is called Dirichlet regular if
\[
\lim_{z\to a}\, H_\phi(z)=\phi(a)\quad\colon\,\phi\in C^0(\partial\Omega)\tag{**}
\]


\noindent
If (**) holds for every boundary point 
then Perron's solution extends to a continuous function
on the closure $\bar\Omega$ and 
solves the Dirichlet problem with the prescribed
boundary
function $\phi$.
We shall prove
that (**) holds under a certain  
geometric condition. 

\medskip

\noindent
{\bf 1.1 Theorem.}
\emph{Let $a\in\partial \Omega$ be such that
the connected component of $a$ in the closed complement
${\bf{C}}\setminus \Omega$
is not reduced to the singleton set $\{a\}$.
Then (**) holds for every $\phi$.}
\bigskip

\noindent
The proof involves  several steps.
First we consider
Perron's solution in the special case when
\[
\phi(z)=|z-a|
\]
which we denote  by  
$H_a(z)$. Notice that the function
\[ 
z\mapsto |z-a|
\]
is subharmonic and hence  Perron's  function $H_a(z)$
satisfies
\[ 
|z-a|\leq H_a(z)\quad\colon\quad z\in\Omega\tag{1}
\]
Now we shall prove:

\medskip


\noindent
{\bf 1.2 Boulignad's Lemma.} \emph{Let $a\in\partial\Omega$
satisfy the condition in Theorem 1.1. Then}
\[ 
\lim_{z\to a}\, H_a(z)=0
\]

\noindent
\emph{Proof.}
The assumption upon $a$ and
Theorem 0.1  
gives a harmonic   function
$p^*(z)$ in $\Omega$ such that 
\[
\lim_{z\to a}\, p^*(z)=0\quad\text{and}\quad
\, p^*(z)<0\quad\colon z\in\Omega\tag{1}
\]
Next, let $\epsilon>0$.
Since $a\in\partial\Omega$ we  find
$0<r\leq\epsilon$
such that the circle $|z-a|=r$ has a non-empty intersection 
$\Gamma$
with
$\Omega$.
Put
\[
M=\max_{z\in\Omega}\,|z-a|\tag{2}
\]
We can choose a compact subset $\Gamma_*$ of $\Gamma$ such that
\[
\ell=\text{arc-length}\,\,(\Gamma\setminus\Gamma_*)\leq \frac{\epsilon}{M}
\tag {3}
\]

\noindent
In the disc $D=\{|z-a|<r\}$
we find the harmonic function $V(z)$
whose boundary values on $|z-a|=r$ are zero outside the open set
$\Gamma\setminus\Gamma_*$
while $V=M$ holds on 
$\Gamma\setminus\Gamma_*$. 
Next, since   $\Gamma_*$ is a compact subset of $\Omega$
and $p_a^*<0$  in
$\Omega$ there exists $\delta>0$ such that
\[
p^*(z)\leq -\delta\quad\colon\quad z\in\Gamma_*\tag{4}
\]
Set
\[
B(z)= V(z)-\frac{M}{\delta}\cdot p^*(z)\tag{5}
\]



\noindent
This is a harmonic function in $\Omega\cap D$
and 
the construction of $V$ together with
(4) give
\[
B(z)\geq M\quad\colon\quad z\in\Gamma\tag{6}
\]





\noindent
Next, in  the the open set $U=\Omega\,\cap D$
we have the subharmonic  function
\[
g=H_a-B\tag{7}
\]




\noindent
Since  $|z-a|\leq\epsilon$  holds in the closed disc
in $\bar D$
we have
\[ 
\limsup_{z\to w}\, H_a(z)\leq\epsilon
\quad\colon\, w\in \bar D\cap\partial\Omega\tag{8}
\]

\noindent
and (2) implies  that
$H_a(z)\leq M$ holds in $\Omega$ which gives
\[ 
\limsup_{z\to w}\, H_a(z)\leq M
\quad\colon\, w\in \Gamma\tag{9}
\]

\noindent
At this stage we use
the set-theoretic inclusion
\[
\partial(D\cap\Omega)\subset\Gamma
\cup\, (\bar D\cap\partial\Omega)
\tag{10}
\]
Hence (6) together with
(7-8) entail that 
\[
\limsup_{z\to w}\, H_a(z)-B(z)\leq \epsilon
\quad\colon\, w\in\partial(\Omega\cap D)\tag{10}
\]


\noindent
The maximum principle applied to the subharmonic function
$H-B$ in
$\Omega\cap D$ and (10) give
\[
\limsup_{z\to a}\, H_a(z)\leq \epsilon+
\limsup_{z\to a}\, B(z)=\epsilon+ V(a)+
\limsup_{z\to a}p^*(z)=
\epsilon+ V(a)
\tag{11}
\]
where (1) gives the last equality.
Finally, 
the mean-value formula for the harmonic function
$V$ and (3) entail that
\[
V(a)=\ell\cdot M\leq\epsilon\tag{12}
\]


\noindent
Hence the limes superior in the left hand side of
(11) is $\leq 2\epsilon$ and since
$\epsilon>0$ was
arbitrary small we get 
$\limsup_{z\to a}\, H_a(z)\leq 0$ which  finishes the proof of
Boulignad's lemma.


\bigskip





\centerline{\emph{¤ 1.3 Proof of Theorem 1.1.}}
\medskip

\noindent
Let $\phi\in C^0(\partial\Omega)$
with the Perron solution $H_\phi(z)$.
If $c$ is a constant it is clear that
$H_{\phi-c}= H_\phi-c$. Replacing $\phi$ by
$\phi(z)-\phi(a)$ we may therefore assume that
$\phi(a)=0$ and it remains to show that
\[
\lim_{z\to a}\, H_\phi(z)=0\tag{1}
\]
First we consider the limes superior and show that
\[ 
\limsup_{z\to a}\, H_\phi(z)\leq 0\tag{2}
\]
To get (2) 
we take some
$\epsilon>0$ and the continuity of  $\phi$ gives 
$\delta>0$ such that
\[
\phi(z)\leq\epsilon\quad\colon\quad z\in\partial\Omega\,\cap D_a(\delta)
\]
Put $M^*=\max_{z\in\partial\Omega}\,|\phi(z)|$ and define
the harmonic function in
$\Omega$ by
\[
g^*(z)=\epsilon+\frac{M^*}{\delta}\cdot H_a(z)
\]
Since $H_a(z)\geq |z-a|$
we have:
\[ 
\liminf_{z\to b}\, g^*(z)\geq M^*\quad\colon\quad
b\in\partial\Omega\setminus D_a(\delta)
\]


\noindent
At the same time  $g^*(z)\geq\epsilon$ for every
$z\in\Omega$ so $g^*\geq \phi$ on the whole boundary
and the maximum principle for harmonic functions
gives:
\[
u\leq g^*\quad \colon \, u\in\mathcal P(\phi)
\]




\noindent
The construction of
$H_\phi$ entails that
$H_\phi\leq g^*$ holds in $\Omega$ which implies that
\[
\limsup_{z\to a}\, H_\phi(z)\leq 
\limsup_{z\to a}\, g^*(z)=\epsilon
\]
where the last equality follows from Boulignad's Lemma.
Since $\epsilon$ can be arbitrary small we get (2).
There remains to show that
\[
\liminf_{z\to a}\, H_\phi(z)\geq 0\tag{3}
\]



\noindent
To prove (3)  we put
\[ 
g_*(z)=-\epsilon-\frac{M^*}{\delta}\cdot H_a(z)
\]
It is clear that
\[
\limsup_{z\to\xi}\, g_*(z)\leq\phi(\xi)
\quad\text{for all boundary points}\,\,\xi\in\partial\Omega
\]
Hence $g_*\in\mathcal P(\phi)$
which gives
$g_*\leq H_\phi$. So now we have
\[
\liminf_{z\to a}\, H_\phi(z)\geq
\liminf_{z\to a}\, g_*(z)=-\epsilon
\]
Since $\epsilon$ can be arbitrary small we get (3) and Theorem
1.1 is proved.




\newpage





\bigskip

\centerline
{\bf{1.5 Wiener's solution.}}

\medskip

\noindent
Let $\Omega$ be a bounded open set which in general  consists
of infinitely many connected components.
There exists a family
 $\mathcal F$  of 
nested sequences of
strictly increasing relatively compact subsets $\{\Omega_n\}$
such that $\cup\,\Omega_n=\Omega$ and
Dirichlet's problem is solvable for each $\Omega_ n$. The nested property means that
$\bar\Omega_{n-1}$ appears as a compact subset of
$\Omega_n$ for every $n$.
For example, if $N\geq 1$ we consider the family
$\mathcal D\uuu N$
of dyadic cubes whose sides have length $2^{\vvv N}$.
We find the finite family $\mathcal D\uuu N(\Omega)$
of cubes in this family whose closure stay in $\Omega$.
Their closed union is relatively compact in
$\Omega$ and it is clear that Dirichlet's problem is solvable for
the open set given by the union of  interior points in this family.
With increasing $N$ this is  an example of a nested sequence 
$\mathcal F$.

\medskip

\noindent
{\bf{1.6 Theorem.}}
\emph{For each  $z\in\Omega$ and every nested sequence $\{\Omega\uuu n\}$,
the harmonic measures 
$\{\mathfrak {m}\uuu z^{ \Omega\uuu n}\}$
converge weakly to a unique probability measure $\mathfrak {m}^*\uuu z$
supported by  $\partial \Omega$, and for each 
$f\in C^0(\partial\Omega)$  the  function}
\[
W\uuu f(z)=\int\, f(\zeta)\cdot d\mathfrak {m}^*\uuu z(\zeta)
\] 
\emph{is harmonic in $\Omega$.}
\medskip

\noindent
\emph{Proof.}
Let 
$\phi$ be a continuous function $\phi$
on the closure $\overline{\Omega}$ which is subharmonic in
$\Omega$.
For every $n$ its restriction to $\partial\Omega\uuu n$
has a harmonic extension $\Phi\uuu n$ to $\Omega\uuu n$.
Next, let $z$ be a point in $\Omega$ and start 
with some $n\uuu *$ so that
$z\in \Omega\uuu{n\uuu *}$.
To each  $n\geq n\uuu *$ we get  the harmonic measure
$\mathfrak{m}\uuu z^{\Omega\uuu n}$ and obtain
\[
\Phi\uuu n(z)=
\int\uuu{\partial\Omega\uuu n}
\,\phi\cdot d\mathfrak{m}\uuu z^{\Omega\uuu n}\tag{1}
\]
Since $\phi$ is subharmonic  and $\phi=\Phi\uuu{n+1}$ holds on
$\partial \Omega\uuu{n+1}$, it follows that
$\phi\leq \Phi \uuu{n+1}$ in $\Omega\uuu{n+1}$ This holds
in particular  on $\partial\Omega\uuu n$ which entails that


\[
\Phi\uuu n(z)= \int\uuu{\partial \Omega\uuu n}
\,\phi\cdot \mathfrak{m}\uuu z^{\Omega\uuu n}\leq
\int\uuu{\partial \Omega\uuu n}
\,\Phi\uuu {n+1}\cdot \mathfrak{m}\uuu z^{\Omega\uuu n}=\Phi\uuu{n+1}(z)
\tag{2}
\]
where the last equality holds since the restriction of $\Phi\uuu{n+1}$ to
$\Omega\uuu n$ is harmonic.
Hence (1\vvv 2) entail that
\[
\int\uuu{\partial \Omega\uuu n}
\,\phi\cdot \mathfrak{m}\uuu z^{\Omega\uuu n}\leq
\int\uuu{\partial \Omega\uuu {n+1}}
\,\phi\cdot \mathfrak{m}\uuu z^{\Omega\uuu {n+1}}\quad\text{hold for every}
\quad  n\geq n\uuu *
\] 
So the integrals above give
a non-decreasing sequence of real numbers which in addition
is bounded above because the maximum norm of
$\phi$ on $\bar\Omega$ is finite.
Hence there exists the limit
\[
 L(\phi)=\lim\uuu{n\to\infty}\, 
\int\uuu{\partial \Omega\uuu n}
\,\phi\cdot \mathfrak{m}\uuu z^{\Omega\uuu n}\tag{3}
\]
In ¤ XX:B we  show
that every
$C^2$-function 
can be expressed as the difference of two
subharmonic functions and hence  the limit in (3) exists
for every $f\in C^2(\partial\Omega)$. Since $C^2(\partial \Omega)$ is dense
in
$C^0(\partial\Omega)$,
Riesz representation Theorem implies  that 
weak-star limits from subsequences of
$\{\mathfrak{m}\uuu z^{\Omega\uuu n}\}$ are
equal and hence the whole sequence has a
weak-star  limit $\mathfrak{m}\uuu z^*$.
Moreover, the  
boundaries
$\partial\Omega\uuu n$ approach $\partial\Omega$ which entails that 
$\mathfrak{m}^*_z$ is supported by $\partial\Omega$.
At this stage we leave to the reader to show
that
if $\{U\uuu n\}$ is another nested sequence then the weak star limit of
of $\{\mathfrak{m}\uuu z^{U\uuu n}\}$
is equal to 
the limit measure $\mathfrak{m}\uuu z^*$ constructed via
$\{\Omega\uuu n\}$. Finally, the constructions above show that
when $z$ varies in
$\Omega$ then 
\[ 
z\mapsto \int\uuu{\partial\Omega}
\, f\cdot \mathfrak {m}\uuu z^*
\] 
is harmonic in $\Omega$ for every continuous boundary function $f$.

\bigskip

\noindent
{\bf{1.7 Regular boundary points.}}
Consider a point $a\in\partial\Omega$.
It is called  Wiener-regular   if
\[
\lim\uuu{z\to a}\, W\uuu f(z)=f(a)\tag{1.7.1}
\]
hold for every $f\in C^0(\partial\Omega)$.
We shall find a potential-theoretic condition
in order that (1.7.1) holds.
Without loss of generality we can take $a$ as the origin
and for each  $n\geq 1$
we consider the closed annulus
\[
A\uuu n=\{2^{\vvv n}\leq |z|\leq 2^{\vvv n+1}\}
\]
For each fixed $n$
the compact set $\partial\Omega\cap A_n$ has a
capacity 
$e^{\vvv \gamma\uuu n}$ which by
¤ XX means that there exists
a probability measure $\mu\uuu n$ supported by
$\partial\Omega\cap A\uuu n$ such that the logarithmic potential
\[ 
U\uuu n(z)=\frac{1}{\gamma\uuu n}\int\,\log\,\frac{1}{|z\vvv\zeta|}\cdot d\mu\uuu n(\zeta)
=1\quad\colon
z\in \partial\Omega\cap A\uuu n
\]

\medskip

\noindent
{\bf{1.8 Theorem.}}
\emph{The boundary point $a$ is regular if and only if}
\[
\sum\uuu{n=1}^\infty\, \frac{n}{\gamma\uuu n}=+\infty\tag{*}
\]
\medskip

\noindent
\emph{Proof.}
Suppose first that
(*) is convergent and then we must
prove that (1.7.1) does not hold.
To achieve this we take
some
$0<\epsilon<1/3$ which is kept fixed from now on where the assumed
convergence in (*) gives
an integer $N\uuu *$ such that
\[
\sum\uuu{n=N\uuu *}^\infty\,
 \frac{n}{\gamma\uuu n}
\leq\epsilon\tag{i}
\]

\medskip

\noindent
Choose $F\in C^0(\partial\Omega)$
with $F(0)=1 $ and
$F=0$ on $\{|z|\geq 2^{\vvv N\uuu *+1}\cap \partial\Omega\}$
while the  whole range $F(\bar\partial\Omega)$
is contained in $[0,1]$. 
Now we shall argue by contradiction and suppose that
(1.7.1) holds for $F$. This   gives the existence of a small 
$s>0$ such that 
\[
W\uuu F(z)\geq 1\vvv \epsilon\quad\text{holds Êon}\quad
D(s)\cap \Omega\tag{ii}
\]
where $D(s)$ is the 
disc of radius $s$ centered at the origin.
Next, as  $r\to 0$ the discs $D(r)$
shrink to the singleton set $\{0\}$. So by ¤ XX
the capacities
$e^{\vvv \gamma\uuu r}$ of $D(r)\cap \Omega$.
tend to zero with $r$.
Let $\nu\uuu r$ be the
equilibrium distribution
on $D(r)\cap \partial\Omega$ and put
\[
V\uuu r(z)= \frac{1}{\gamma \uuu r}\cdot \int \log\frac{1}{|z\vvv \zeta|}
\cdot d\nu\uuu r(\zeta)\tag{iii}
\]
So here $V(z)=1$ on $D(r)\cap \partial \Omega$.
Since $\gamma_r\to +\infty$ as $r\to 0$
we can choose $r<s$ so small that
\[
\max\uuu{|z|\geq s}\, V\uuu r(z)\leq\epsilon\tag{iv}
\]
Next, let  $M>N\uuu * $ be so large that $2^{\vvv M}\leq r$ and put
\[ 
U^*\uuu M(z)=\sum\uuu{n=N\uuu *}^{n=M}\,
\frac{1}{\gamma\uuu n}\cdot U\uuu n(z)
\]
With this choice it is clear that 
\[
V(z)+U^*\uuu M(z)\geq 1\quad\text{holds on}\quad 
D(2^{\vvv N\uuu *+1})\cap \partial \Omega\tag{v}
\]
Since $0\leq F\leq 1$ and $F=0$ on
$\partial\Omega\setminus D(2^{\vvv N\uuu *+1})$
we have $F\leq V+U^*\uuu M$ on the whole boundary
of $\Omega$. The minimum principle 
for super\vvv harmonic functions
gives the inequality
\[
V+U^*\uuu M\geq W\uuu F\quad\text{in}\quad \Omega\tag{vi}
\]
Now (i) and (iv) entail that
\[ 
\min\uuu{z\in \Omega\cap D(s)}\, U^*\uuu M(z)\geq 1\vvv 2\epsilon \tag{vii}
\]
At the same time we have $2^{\vvv M}\leq s$ so the construction of
$U^*\uuu M$ entails that
$U^*\uuu M=1$ holds on
$|z|\cap \partial\Omega$. Together with (vii) we obtain
\[
\min\uuu {|z|=s}\, U^*\uuu M(z)\geq 1\vvv 2\epsilon\tag{viii}
\]


\noindent
Now $U^*\uuu M$ restricts to  a super\vvv harmonic
function on $D(s)$ 
so the minimum principle for super\vvv harmonic functions gives
\[
1\vvv 2\epsilon\leq U^*\uuu M(0)
=\sum\uuu{n=N\uuu *}^{n=M}\, 
\frac{1}{\gamma\uuu n}\int\, \cdot 
\log\,\frac{1}{|\zeta|}\cdot d\mu\uuu n(\zeta)\tag{ix}
\]
Finally, $|\zeta|\geq 2^{\vvv n}$ holds on the support of $\mu\uuu n$
and hence each integral is $\leq n\cdot \log 2$. So (ix) gives
the inequality
\[
1\vvv 2\epsilon\leq \sum\uuu{n=N\uuu *}^{n=M}\, 
\frac{n\cdot \log 2}{\gamma\uuu n}<\log 2\cdot \epsilon
\]
This cannot hold
since we have chosen
$\epsilon<1/3$. It means that  (ii) cannot hold and hence 
$a$ is not a regular boundary point.

\medskip


\centerline {\emph{Proof of sufficiency.}}
\bigskip

\noindent
Above we  proved that
if $a$ is regular then the series (*) in Theorem 1.8 must diverge.
There remains to show that  if (*) is divergent then $a$ is regular.
The proof  of this converse is left as an exercise to the reader.












\newpage



\centerline{\bf\large Chapter 5.A Harmonic functions}


\bigskip

\noindent 
\centerline{\emph{Contents}}
\medskip

\noindent 
1. The Dirichlet problem
\medskip

\noindent 
2. The Harmonic Conjugate.
\medskip

\noindent 
3. Harmonic functions in a disc
\medskip

\noindent 
4. The mean value property
\medskip


\noindent 
5. The harmonic measure
\medskip

\noindent 
6. The Green's function


\medskip

\noindent 
7. The Neumann problem 


\medskip

\noindent 
8. Example from Hydro mechanics



\medskip

\noindent 
9. A result on harmonic majorisation

\medskip

\noindent 
10. On harmonic measure functions
\medskip

\noindent 
11. Some estimates for  harmonic  functions
\medskip

\noindent 
12.  A density result for harmonic functions

\medskip

\noindent 
13.  A representation of rotation invariant harmonic functions
\medskip

\noindent 
14.  Ganelius' inequality for conjugate harmonic functions
\medskip

\noindent 
15.  Beurling's minimum principle for
harmonic functions







\bigskip



\noindent
\centerline{\bf\large{ Introduction.}}
\medskip



\noindent
Chapter V is divided in two parts, where ¤ B
treats subharmonic functions.
A  logical procedure might have started with 
subharmonic functions. However, we prefer to first study
harmonic functions even though we are obliged to appeal to
some facts from  V:B.
Hopefully the reader will accept this and
whenever needed consult results in  V:B.
A crucial fact 
is that
every positive harmonic function $u$ in the open unit disc
is the Poisson extension of a non-negative Riesz measure 
$\mu$ with finite total mass on
the unit circle, i.e. with $z=x+iy$ one has 
\[
u(x,y)=\frac{1}{2\pi}\cdot \int_0^{2\pi}\,
\frac{1-|z|^2}{|e^{i\theta}-z|^2}\cdot d\mu(\theta)
\]
Another useful result is that
every real-valued continuous function $\phi$ 
whose Laplacian in the sense of distribution theory
is of order zero, i.e. given by a signed Riesz measure, 
is the difference of two subharmonic functions.
In  particular this is true for real-valued $C^2$-functions.
Armed with these results to be  proved in 
V:B   we  solve   the
 Dirichlet problem in a quite general context where
the  major results are due to Perron and Wiener.
In fact, we shal, learn that there exist
several ways to attain solutions of 
Dirchlet's problem.
The less experienced reader
may
first consult the 
material in ¤ 3 and ¤ 4 
where we study the Poisson kernel in the unit disc
and  establish the Herglotz formula, while ¤ 4 
exhibits maximum principles for harmonic functions which
are derived from local  mean-value equalities.

\medskip

\noindent
\emph{ Comments on other sections.}
In  ¤ 5 we study harmonic measures and use these to
prove  results due to Lindelšf concerning limits
of  bounded analytic functions.
In  ¤6 we construct  Green's functions and
the Neumann problem is treated 
in ¤ 7. An  example related to hydromechanics appears in
¤ 8 and ¤ 9
presents a  proof by Carleman which uses
differential inequalities in order to
estimate harmonic functions.
Section 10 treats  a result due to Nevanlinna about
critical points for level curves of harmonic measure functions.
Sections 11-13 contain  supplementary facts about harmonic functions.
For example, the estimates in ¤ 12 will be used when Lindelšf
indicators  are studied for analytic functions in strip domains
in  Special Topics: ¤ XX.
Sections 14 -15 contain results whose proofs are more involved, especially in
¤ 15.
The  results in
¤ 8-15 
are not neeeded for the "general theory". However, the proofs
are instructive and the theorems  quite striking. So they deserve
to be studied since they teach lessons about
the usefulness of both harmonic and subharmonic  functions.
\medskip

\noindent
{\bf{Remark.}}
Many results can be exended to a more general set-up. 
One can for example replace the Laplace operator by
an elliptic second-order PDE-operator with variable coefficients and
establish solutions to boundary value problems, both in the sense of 
Dirichlet and Neumann.
So the subsequent material is rather restricted, 
but has the merit that
proofs are quite  constructive and 
the special results which occur  for  the Laplace operator are 
used in analytic function theory.





\bigskip



\centerline {\emph{The Dirichlet problem.}}

\medskip


\noindent
Consider a bounded open and connected domain
$\Omega$ in ${\bf{C}}$.
To every $f\in C^0(\partial\Omega)$ one
seeks a harmonic function $H_f$ in $\Omega$ which extends continuously to
$\bar\Omega$ and whose  boundary value function is $f$.
The maximum principle for harmonic functions entails that
$H_f$ is unique if it exists.
When $\Omega$ is of class $\mathcal D(C^1)$, i.e.
the boundary is a finite union of
pairwise disjoint closed Jordan curves of class $C^1$, then
Dirichlet's problem can be solved for every
continuous boundary function.
This  relies upon
properties of Dirchlet integrals. If
$F$ is a $C^1$-function defined in a neighborhood of
the closure of 
$\Omega$ the Dirichlet norm is defined by
\[ 
D(F)=\sqrt{\iint_\Omega\, (F_x^2+F_y^2)\, dxdy}\tag{i}
\]
If $F$ and $G$ are two $C^1$-functions which  extend to be
of class $C^1$ on the boundary, then Greens' formula entails that
\[
\iint_\Omega\,[ G\cdot \Delta F+(G_xF_x+G_yF_y)]\, dxdy
=
\int_{\partial\Omega}\, G\cdot \frac{\partial F}{\partial n}\, ds\tag{ii}
\]
\medskip

\noindent
{\bf{The case when
$F$ is harmonic}}. Then (ii) gives
\[
\iint_\Omega\,(G_xF_x+G_yF_y)\, dxdy
=
\int_{\partial\Omega}\, G\cdot \frac{\partial F}{\partial n}\, ds\tag{iii}
\]
With $F=G$ we obtain in particular 
\[
D^2(F)=\int_{\partial\Omega}\, F\cdot \frac{\partial F}{\partial n}\, ds\tag{iv}
\]

\medskip

\noindent
Next, we notice that
\[
D^2(F-G)=D^2(F)+D^2(G)-2\cdot \iint_\Omega\,(G_xF_x+G_yF_y)\, dxdy\tag{v}
\]
If $G=F$ holds on $\partial\Omega$ we see that
(iii-iv) give
\[
D^2(F-G)= D^2(G)+D^2(F)-2\cdot \int_{\partial\Omega}\,
F\cdot \frac{\partial F}{\partial n}\, ds= D^2(G)-D^2(F)
\]
Hence we have established

\medskip


\noindent
{\bf{Dirichlet's equation}}
\emph{Let $F$ be harmonic in $\Omega$. Then}
\[
D^2(G)=D^2(F)+D^2(F-G)\tag{*}
\] 
\emph{hold for every $G$ such that $G=F$ on $\partial\Omega$.}
\medskip

\noindent
{\bf{Remark.}}
This equality   suggests 
that
if $f\in C^0(\partial\Omega)$
then the solution to Dirchlet's problem amounts 
to settle a variational 
problem, i.e.  find $F$ such that
$D(F)$ is minimized while $F=f$ on the boundary.
It was  pointed out by Weierstrass  that
a variational problem of this kind
is not automatically well posed. After a rather 
refined analysis PoincarŽ demonstrated that
the variational problem indeed
leads to the solution of the Dirichlet problem  for domains of class $C^2$.
For domains with less regularity  we shall learn
that solutions to the Dirchlet problem can be found
by a Perron's method.
His  solution is
given in
¤ 5.B after we have become familiar with subharmonic functions.
\medskip

\noindent
{\bf{0.2 Wiener's generalised solution.}}
Examples  of "ugly domains" show that the Dirichlet problem in 
general cannot be solved.
However, for an arbitrary bounded open set $\Omega$
there
exists for each $\phi\in C^0(\partial\Omega)$ a unique harmonic
function $W_f$
which is 
constructed
as follows:
The domain $\Omega$ can be exhausted by a 
nested sequence of  increasing 
subdomains $\{U_n\}$ such that
$\cup \, U_n=\Omega$, and for each $n$ the boundary
$\partial U_n$ is a finite union of closed Jordan 
curves of class $C^2$. Moreover, 
\[
\lim_{n\to\infty}\, \text{dist}(\partial U_n,\partial\Omega)=0
\]
Next,  extending $\phi $ to a continuous function
$\Phi$ on $\bar \Omega$ 
we can solve the Dirichlet problem in $U_n$
which gives  a harmonic function
$H_n$ in $U_n$ whose boundary value function on 
$\partial U_n$
is  the restriction of $\Phi$.
In ¤ xx we show that the sequence $\{H_n\}$ converges uniformly over
compact subsets to a limit function  which
is harmonic in $\Omega$.
Wiener proved that this limit function does not depend upon the chosen
nested $U$-sequence, nor upon the chosen 
continuous extension of $\phi$.
The resulting function is  denoted by $W_\phi$
and called Wiener's generalised solution.
The map $\phi\to W_\phi$ is linear
and Riesz representation theorem gives  
for each point $z\in\Omega$   a unique probability measure
$\mathfrak{m}_z$ on $\partial\Omega$
such that
\[ 
W_\phi(z)=
\int\, \phi (\zeta)\cdot d\mathfrak{m}_z(\zeta)\tag{*}
\]
holds for every $\phi\in C^0(\partial\Omega)$.


\medskip

\noindent
{\bf{0.3 Regular boundary points.}}
A point $z_0\in\partial\Omega$ is called regular 
if
\[
\lim_{z\to z_0}\,  W_\phi(z)= \phi(z_0)
\]
hold for every continuous boundary function.
A criterion for
a boundary point to be
regular was established by 
Boulignad in 1923. Namely,
a boundary point $z_0$ is regular if and only if there
exists a positive harmonic function $V$ in $\Omega$ such that
\[
\lim_{z\to z_0} V(z)=0
\]
This condition is rather implicit
so one seeks geometric properties to
decide if a boundary point is regular or not.
In his Phd-thesis from 1933, Beurling established a sufficient regularity condition which 
goes as follows:
Let $z_0\in\partial \Omega$
and for a given $R>0$ we consider the
circular projection of
the closed complement of $\Omega$ onto the real interval $0<r<R$
defined by:
\[ 
E_\Omega(0,R)=\{ 0<r< R\,\colon\,\exists
\,\, z\in \{|z-z_0|=r\}\cap {\bf{C}}\setminus \Omega\}
\]
Following Beurling one
 says that $z_0$ is logarithmically dense  (Point
frontire de
condensation logarithmique)
if the integral
\[
\int_{E_\Omega(0,R)}\, \log r\, dr=+\infty\tag{1}
\]
Beurling proved that if (1) is divergent
then $z_0$ is a regular boundary point.
The proof relies upon an inequality which has  independent interest.
Here is the situation considered in [ibid: page 64-66]:
Let $\Omega$ be an open set - not necessarily connected - and
$R>0$ is such that  $\Omega$  contains points of absolute value $\geq R$.
Consider a harmonic function $h$ in $\Omega$ with the following properties:
\[ 
\limsup_{z\to z_*}\, h(z)\leq 0\quad\colon \,
z_*\in \partial \Omega\cap \{|z|\leq R\}\tag{i}
\]
\[
h(z)\leq  M\quad\colon\, z\in \{|z|=R\}\,\cap D\tag{ii}
\]

\medskip
\noindent{\bf{0.3.1 Theorem.}}
\emph{When (i-ii) hold one has the inequality below for every
$0<r<R$}
\[
\max_{z}\, h(z)\leq 2M\cdot\, e^{-\frac{K}{2}}
\]
\emph{where the maximum in the left hand side
is taken over $\Omega\cap \{r<|z|<R\}$
and}
\[ 
K=\int_{E_\Omega(r,R)}\, \log r\, dr
\]
\medskip

\noindent
In this chapter we shall not expose Beurling's result but refer to ¤ xx.
Instead we give an account about Wiener's potential-theoretic
condition for boundary points to be regular in ¤ 1.6.


\bigskip






\noindent
{\bf 0.4 Harmonic measures.}
Let $\Omega$ be
a bounded and connected domain.
By (*) in (0.2)
we find a probability measure $\mathfrak{m}_z$
 on $\partial\Omega$ for each $z\in\Omega$ and
refer to $\mathfrak{m}\uuu z$ as the harmonic measure of
$z$. 
Let
$g$ be a bounded
Borel function
defined on 
$\partial\Omega$.
Recall from   \emph{Measure Appendix}
that we can construct
integrals of Borel functions with respect to an arbitrary
Riesz measure.
If  $z\in\Omega$ we put
\[
G(z)=\int_{\partial\Omega}\,
g(\zeta)\cdot d\mathfrak{m}_z(\zeta)\quad\colon\quad
\]


\noindent
Then $G$ is a bounded harmonic function in
$\Omega$. 
In particular we  take a Borel set $E$ in $\partial\Omega$
and integrate its characteristic function which
gives  the harmonic function
\[ 
\omega_E(z)=
\int_E\, d\mathfrak{m}_z(\zeta)
\]
One refers to
$\omega_E$ as the harmonic measure function  with respect
to the $E$.
\medskip


\noindent
{\bf{Remark.}}
When $z$ varies in $\Omega$, Harnack's inequality 
for harmonic functions
shows
that the family of harmonic measures 
are absolutely continuous with respect to each other.
So with   $z\uuu *\in\Omega$ kept fixed every point $z\in\Omega$ gives
a function $\rho\uuu z\in L^\infty(\mathfrak{m}\uuu{z\uuu *})$
such that
\[
\mathfrak{m}\uuu z= \rho\uuu z\cdot \mathfrak{m}\uuu{z\uuu *}
\]



\noindent
Since $C^0(\partial\Omega)$
is a dense subspace of
$L^1(\mathfrak{m}_{z_*})$  
every
$f\in L^1(\mathfrak{m}_{z_*})$ yields a harmonic function in
$\Omega$ defined by
\[ 
f^*(z)=\int\, \rho_z(\zeta)\cdot f(\zeta)\cdot
d\mathfrak{m}_{z_*}(\zeta)
\]


\bigskip

\noindent
\centerline {\bf {0.5 Other topics.}}
\medskip

\noindent
In  ¤ 2 we construct the harmonic conjugate
of a  harmonic function.
¤ 3 is devoted to the case when
$\Omega$ is the unit disc where
we confirm the solution to
the Dirichlet problem using the Poisson kernel 
\[
P(r,\theta)=
\frac{1}{2\pi}\cdot \frac{1\vvv r^2}{1+r^2\vvv 2r\cos\theta}
\] 
where $0<r<1$ while $0\leq \theta\leq 2\pi$.
When $u(\theta)$ is a continuous function on the circle its harmonic
extension to $D$ is given by
\[
U(r,\phi)=\int\uuu 0^{2\pi}\,P(r,\theta\vvv \phi)\cdot U(\theta)\, d\theta\tag{1}
\]
One often
rewrites this  integral as:
\[
U(r,\phi)=\int\uuu 0^{2\pi}\,P(r,\theta)\cdot u(\theta+\phi)\, d\theta\tag{2}
\]


\noindent
{\bf{0.6 An estimate of derivatives.}}
Suppose that $u$ is Lipschitz continuous, i.e. there is a constant 
$C$ such that
\[
|u(\theta\uuu 2)\vvv u(\theta\uuu 1)|\leq C\cdot |\theta\uuu 1\vvv \theta\uuu 2|
 \]
Then  (2) implies that
$U$ restricts to a Lipschitz continuous function of the angular variable
$\phi$
with  norm
$\leq C$ on every circle of radius $r<1$.
Hence the angular derivatives satisfy
\[
|\frac{\partial U}{\partial\phi}(r,\phi)|\leq C\quad\colon\,\,
0<r<1
\] 
To study radial derivatives 
we use the equation
\[
\frac {\partial P(r,\theta)}{\partial r}
=\frac{1}{2\pi}\cdot \frac{2\cos\theta+2r^2\cos\theta\vvv 4r}
{(1+r^2\vvv 2r\cos\,\theta)^2}
\]
With a fixed $\phi\uuu *$ we consider the function
\[ 
r\mapsto \frac{\partial U}{\partial r}(r,\phi\uuu *)\tag{*}
\]
Now $\theta\mapsto u(\theta+\phi\uuu *)$ has the same Lipschitz norm
and we may therefore take $\phi\uuu *=0$ and since
the partial $r$\vvv derivative of $U$ is unchanged when we add a constant
we can  replace $u(\theta)$
by $u(\theta)\vvv u(0)$, i.e assume that $u(0)=0$.
This    entails that
\[
|u(\theta)|\leq C\cdot |\theta|\quad\colon\quad \vvv \pi<\theta<\pi
\]
Now (*) is majorized  in absolute value by the integral
\[
\frac{C}{2\pi}\int\uuu{\vvv\pi}^\pi\, 
\frac{\bigl|2\cos\theta+2r^2\cos\theta\vvv 4r\bigr|}
{(1+r^2\vvv 2r\cos\,\theta)^2}\cdot |\theta|\cdot d\theta
\]
\medskip

\noindent
{\bf{Exercise.}}
Show that the last integral is majorized by an absolute constant which is independent 
of $0<r<1$ and conclude  
the following:
\medskip

\noindent
{\bf{0.6.1 Theorem.}}
\emph{There exists an absolute constant $C\uuu *$ such that}
\[
\max\uuu{(r,\phi)\in D}\, 
|\frac{\partial U}{\partial r}(r,\phi)|+|\frac{\partial U}{\partial\phi}(r,\phi)|
\leq C\uuu *\cdot \frac{||u||\uuu{\text{Lip}}}{2\pi}
\] 
\emph{where the last term is the Lipschitz norm of $u$ over $T$.}
\medskip

\noindent
{\bf{Remark.}} If we remove a small disc centered at the origin
the left hand side can be replaced by
the length of the gradient vector $\nabla U=(U\uuu x,U\uuu y)$.
For example, we find an absolute constant $C^*$ such that
\[
\max\uuu{1/2\leq |z|< 1}\, ||\nabla(U)(z)||\leq C^*\cdot 
||u||\uuu{\text{Lip}}
\]
\bigskip



\bigskip


\newpage


\centerline{\bf 1. The Dirichlet Problem.}


\bigskip

\noindent
{\bf Introduction.}
Let $\Omega$ be a bounded open set
in ${\bf{C}}$.
No connectivity assumptions are imposed, i.e. neither
$\Omega$ or $\partial\Omega$ have to be connected.
To each  
$\phi\in C^0(\partial\Omega)$
we shall construct as harmonic 
function $H_\phi$  in $\Omega$ using a
procedure  introduced by
J. Perron. Denote by
$\mathcal P(\phi)$  the family of  subharmonic functions $u(z)$ in 
$\Omega$ satisfying
\[
\limsup_{z\to w}\,u(z)\leq \phi(w)
\quad\colon\, w\in\partial\Omega\tag{0.1}
\]


\noindent 
In Theorem XX  
we prove that the function defined by
\[
H_\phi(z)=\max_{u\in\mathcal P(\phi)}\, u(z)\quad\colon\, z\in\Omega\tag{*}
\]


\noindent
is  harmonic in $\Omega$. A boundary point $a$ is called Dirichlet regular if
\[
\lim_{z\to a}\, H_\phi(z)=\phi(a)\quad\colon\,\phi\in C^0(\partial\Omega)\tag{**}
\]


\noindent
If (**) holds for every boundary point 
then Perron's solution extends to a continuous function
on the closure $\bar\Omega$ and 
solves the Dirichlet problem with the prescribed
boundary
function $\phi$.
It turns out that (**) holds under a fairly mild 
geometric condition. 

\medskip

\noindent
{\bf 1.1 Theorem.}
\emph{Let $a\in\partial \Omega$ be such that
the connected component of $a$ in the closed complement
${\bf{C}}\setminus \Omega$
is not reduced to the singleton set $\{a\}$.
Then (**) holds for every $\phi$.}
\bigskip

\noindent
The idea  is to 
consider
Perron's solution when 
$\phi(z)=|z-a|$. Let us denote
it by  
$H_a(z)$. 
We remark that
outside the origin in
${\bf{C}}$ the Laplacian of the function
$|z|= \sqrt{x^2+y^2}$
is equal to $|z|^{-1}$ and hence a positive function.
After a translation it follows that
$\phi(z)= |z-a|$ is subharmionic in $\Omega$
so Perron's construction entails that
$H_a$ gives:
\[ 
|z-a|\leq H_a(z)\quad\colon\quad z\in\Omega\tag{1}
\]



\noindent
The  crucial step in the proof of Theorem 1.1 is:
\medskip


\noindent
{\bf 1.2 Boulignad's Lemma.} \emph{Let $a\in\partial\Omega$
satisfy the condition in Theorem 1.1. Then}
\[ 
\lim_{z\to a}\, H_a(z)=0
\]

\noindent
\emph{Proof.}
The assumption on $a$ and
Theorem XX from Chapter 4
gives a harmonic   function
$p^*(z)$ in $\Omega$
which satisfies:
\[
\lim_{z\to a}\, p^*(z)=0\quad\text{and}\quad
\, p^*(z)<0\quad\colon z\in\Omega\tag{1}
\]
Next, let $\epsilon>0$.
Since $a\in\partial\Omega$ we  find
$0<r\leq\epsilon$
such that the circle $|z-a|=r$ has a non-empty intersection 
$\Gamma$
with
$\Omega$.
Put
\[
M=\max_{z\in\Omega}\,|z-a|\tag{2}
\]
We can choose a compact subset $\Gamma_*$ of $\Gamma$ such that
\[
\ell=\text{arc-length}\,\,(\Gamma\setminus\Gamma_*)\leq \frac{\epsilon}{M}
\tag {3}
\]

\noindent
In the disc $D=\{|z-a|<r\}$
we find the harmonic function $V(z)$
whose boundary values on $|z-a|=r$ are zero outside the open set
$\Gamma\setminus\Gamma_*$
while $V=M$ holds on 
$\Gamma\setminus\Gamma_*$. 
Next, since   $\Gamma_*$ is a compact subset of $\Omega$
and $p_a^*<0$  in
$\Omega$ there exists $\delta>0$ such that
\[
p^*(z)\leq -\delta\quad\colon\quad z\in\Gamma_*\tag{4}
\]
Set
\[
B(z)= V(z)-\frac{M}{\delta}\cdot p^*(z)\tag{5}
\]



\noindent
This is a harmonic function in $\Omega\cap D$
and 
the construction of $V$ together with
(4) give
\[
B(z)\geq M\quad\colon\quad z\in\Gamma\tag{6}
\]





\noindent
Next, in  the the open set $U=\Omega\,\cap D$
we have the subharmonic  function
\[
g=H_a-B\tag{7}
\]




\noindent
Since  $|z-a|\leq\epsilon$  holds in the closed disc
in $\bar D$
we have
\[ 
\limsup_{z\to w}\, H_a(z)\leq\epsilon
\quad\colon\, w\in \bar D\cap\partial\Omega\tag{8}
\]

\noindent
From (2) it follows that
$H_a(z)\leq M$ holds in $\Omega$
which entails that
\[ 
\limsup_{z\to w}\, H_a(z)\leq M
\quad\colon\, w\in \Gamma\tag{9}
\]

\noindent
At this stage we use
the set-theoretic inclusion
\[
\partial(D\cap\Omega)\subset\Gamma
\cup\, (\bar D\cap\partial\Omega)
\tag{10}
\]
Hence (6) together with
(7-8) entail that 
\[
\limsup_{z\to w}\, H_a(z)-B(z)\leq \epsilon
\quad\colon\, w\in\partial(\Omega\cap D)\tag{10}
\]


\noindent
The maximum principle applied to the subharmonic function
$H-B$ in
$\Omega\cap D$ and (10) give
\[
\limsup_{z\to a}\, H_a(z)\leq \epsilon+
\limsup_{z\to a}\, B(z)=\epsilon+ V(a)+
\limsup_{z\to a}p^*(z)=
\epsilon+ V(a)
\tag{11}
\]
where (1) gives the last equality.
Finally, 
the mean-value formula for the harmonic function
$V$ and (3) entail that
\[
V(a)=\ell\cdot M\leq\epsilon\tag{12}
\]


\noindent
Hence the limes superior in the left hand side of
(11) is $\leq 2\epsilon$ and since
$\epsilon>0$ was
arbitrary small we get 
$\limsup_{z\to a}\, H_a(z)\leq 0$ which  finishes the proof of
Boulignad's lemma.


\bigskip





\centerline{\emph{¤ 1.3 Proof of Theorem 1.1.}}
\medskip

\noindent
Let $\phi\in C^0(\partial\Omega)$
with the Perron solution $H_\phi(z)$.
If $c$ is a constant it is clear that
$H_{\phi-c}= H_\phi-c$. Replacing $\phi$ by
$\phi(z)-\phi(a)$ we may therefore assume that
$\phi(a)=0$ and it remains to show that
\[
\lim_{z\to a}\, H_\phi(z)=0\tag{1}
\]
First we consider the limes superior and show that
\[ 
\limsup_{z\to a}\, H_\phi(z)\leq 0\tag{2}
\]
To get (2) 
we take some
$\epsilon>0$ and the continuity of  $\phi$ gives 
$\delta>0$ such that
\[
\phi(z)\leq\epsilon\quad\colon\quad z\in\partial\Omega\,\cap D_a(\delta)
\]
Put $M^*=\max_{z\in\partial\Omega}\,|\phi(z)|$ and define
the harmonic function in
$\Omega$ by
\[
g^*(z)=\epsilon+\frac{M^*}{\delta}\cdot H_a(z)
\]
Since $H_a(z)\geq |z-a|$
we have:
\[ 
\liminf_{z\to b}\, g^*(z)\geq M^*\quad\colon\quad
b\in\partial\Omega\setminus D_a(\delta)
\]


\noindent
At the same time  $g^*(z)\geq\epsilon$ for every
$z\in\Omega$ so $g^*\geq \phi$ on the whole boundary
and the maximum principle for harmonic functions
gives:
\[
u\leq g^*\quad \colon \, u\in\mathcal P(\phi)
\]




\noindent
The construction of
$H_\phi$ entails that
$H_\phi\leq g^*$ holds in $\Omega$ which implies that
\[
\limsup_{z\to a}\, H_\phi(z)\leq 
\limsup_{z\to a}\, g^*(z)=\epsilon
\]
where the last equality follows from Boulignad's Lemma.
Since $\epsilon$ can be arbitrary small we get (2).
There remains to show that
\[
\liminf_{z\to a}\, H_\phi(z)\geq 0\tag{3}
\]



\noindent
To prove (3)  we put
\[ 
g_*(z)=-\epsilon-\frac{M^*}{\delta}\cdot H_a(z)
\]
It is clear that
\[
\limsup_{z\to\xi}\, g_*(z)\leq\phi(\xi)
\quad\text{for all boundary points}\,\,\xi\in\partial\Omega
\]
Hence $g_*\in\mathcal P(\phi)$
which gives
$g_*\leq H_\phi$. So now we have
\[
\liminf_{z\to a}\, H_\phi(z)\geq
\liminf_{z\to a}\, g_*(z)=-\epsilon
\]
Since $\epsilon$ can be arbitrary small we get (3) and Theorem
1.1 is proved.
\bigskip

\centerline
{\bf{1.5 Wiener's solution.}}

\medskip

\noindent
Let $\Omega$ be a bounded open set which in general  consists
of infinitely many connected components.
There exists a family
 $\mathcal F$  of 
nested sequences of
strictly increasing relatively compact subsets $\{\Omega_n\}$
such that $\cup\,\Omega_n=\Omega$ and
Dirichlet's problem is solvable for each $\Omega_ n$. The nested property means that
$\bar\Omega_{n-1}$ appears as a compact subset of
$\Omega_n$ for every $n$.
For example, if $N\geq 1$ we consider the family
$\mathcal D\uuu N$
of dyadic cubes whose sides have length $2^{\vvv N}$.
We find the finite family $\mathcal D\uuu N(\Omega)$
of cubes in this family whose closure stay in $\Omega$.
Their closed union is relatively compact in
$\Omega$ and it is clear that Dirichlet's problem is solvable for
the open set given by the union of  interior points in this family.
With increasing $N$ this is  an example of a nested sequence 
$\mathcal F$.

\medskip

\noindent
{\bf{1.6 Theorem.}}
\emph{For each  $z\in\Omega$ and every nested sequence $\{\Omega\uuu n\}$,
the harmonic measures 
$\{\mathfrak {m}\uuu z^{ \Omega\uuu n}\}$
converge weakly to a unique probability measure $\mathfrak {m}^*\uuu z$
supported by  $\partial \Omega$, and for each 
$f\in C^0(\partial\Omega)$  the  function}
\[
W\uuu f(z)=\int\, f(\zeta)\cdot d\mathfrak {m}^*\uuu z(\zeta)
\] 
\emph{is harmonic in $\Omega$.}
\medskip

\noindent
\emph{Proof.}
Let 
$\phi$ be a continuous function $\phi$
on the closure $\overline{\Omega}$ which is subharmonic in
$\Omega$.
For every $n$ its restriction to $\partial\Omega\uuu n$
has a harmonic extension $\Phi\uuu n$ to $\Omega\uuu n$.
Next, let $z$ be a point in $\Omega$ and start 
with some $n\uuu *$ so that
$z\in \Omega\uuu{n\uuu *}$.
To each  $n\geq n\uuu *$ we get  the harmonic measure
$\mathfrak{m}\uuu z^{\Omega\uuu n}$ and obtain
\[
\Phi\uuu n(z)=
\int\uuu{\partial\Omega\uuu n}
\,\phi\cdot d\mathfrak{m}\uuu z^{\Omega\uuu n}\tag{1}
\]
Since $\phi$ is subharmonic  and $\phi=\Phi\uuu{n+1}$ holds on
$\partial \Omega\uuu{n+1}$, it follows that
$\phi\leq \Phi \uuu{n+1}$ in $\Omega\uuu{n+1}$ This holds
in particular  on $\partial\Omega\uuu n$ which entails that


\[
\Phi\uuu n(z)= \int\uuu{\partial \Omega\uuu n}
\,\phi\cdot \mathfrak{m}\uuu z^{\Omega\uuu n}\leq
\int\uuu{\partial \Omega\uuu n}
\,\Phi\uuu {n+1}\cdot \mathfrak{m}\uuu z^{\Omega\uuu n}=\Phi\uuu{n+1}(z)
\tag{2}
\]
where the last equality holds since the restriction of $\Phi\uuu{n+1}$ to
$\Omega\uuu n$ is harmonic.
Hence (1\vvv 2) entail that
\[
\int\uuu{\partial \Omega\uuu n}
\,\phi\cdot \mathfrak{m}\uuu z^{\Omega\uuu n}\leq
\int\uuu{\partial \Omega\uuu {n+1}}
\,\phi\cdot \mathfrak{m}\uuu z^{\Omega\uuu {n+1}}\quad\text{hold for every}
\quad  n\geq n\uuu *
\] 
So the integrals above give
a non-decreasing sequence of real numbers which in addition
is bounded above because the maximum norm of
$\phi$ on $\bar\Omega$ is finite.
Hence there exists the limit
\[
 L(\phi)=\lim\uuu{n\to\infty}\, 
\int\uuu{\partial \Omega\uuu n}
\,\phi\cdot \mathfrak{m}\uuu z^{\Omega\uuu n}\tag{3}
\]
In ¤ XX:B we  show
that every
$C^2$-function 
can be expressed as the difference of two
subharmonic functions and hence  the limit in (3) exists
for every $f\in C^2(\partial\Omega)$. Since $C^2(\partial \Omega)$ is dense
in
$C^0(\partial\Omega)$,
Riesz representation Theorem implies  that 
weak-star limits from subsequences of
$\{\mathfrak{m}\uuu z^{\Omega\uuu n}\}$ are
equal and hence the whole sequence has a
weak-star  limit $\mathfrak{m}\uuu z^*$.
Moreover, the  
boundaries
$\partial\Omega\uuu n$ approach $\partial\Omega$ which entails that 
$\mathfrak{m}^*_z$ is supported by $\partial\Omega$.
At this stage we leave to the reader to show
that
if $\{U\uuu n\}$ is another nested sequence then the weak star limit of
of $\{\mathfrak{m}\uuu z^{U\uuu n}\}$
is equal to 
the limit measure $\mathfrak{m}\uuu z^*$ constructed via
$\{\Omega\uuu n\}$. Finally, the constructions above show that
when $z$ varies in
$\Omega$ then 
\[ 
z\mapsto \int\uuu{\partial\Omega}
\, f\cdot \mathfrak {m}\uuu z^*
\] 
is harmonic in $\Omega$ for every continuous boundary function $f$.

\bigskip

\noindent
{\bf{1.7 Regular boundary points.}}
Consider a point $a\in\partial\Omega$.
It is called  Wiener-regular   if
\[
\lim\uuu{z\to a}\, W\uuu f(z)=f(a)\tag{1.7.1}
\]
hold for every $f\in C^0(\partial\Omega)$.
We shall find a potential-theoretic condition
in order that (1.7.1) holds.
Without loss of generality we can take $a$ as the origin
and for each  $n\geq 1$
we consider the closed annulus
\[
A\uuu n=\{2^{\vvv n}\leq |z|\leq 2^{\vvv n+1}\}
\]
For each fixed $n$
the compact set $\partial\Omega\cap A_n$ has a
capacity 
$e^{\vvv \gamma\uuu n}$ which by
¤ XX means that there exists
a probability measure $\mu\uuu n$ supported by
$\partial\Omega\cap A\uuu n$ such that the logarithmic potential
\[ 
U\uuu n(z)=\frac{1}{\gamma\uuu n}\int\,\log\,\frac{1}{|z\vvv\zeta|}\cdot d\mu\uuu n(\zeta)
=1\quad\colon
z\in \partial\Omega\cap A\uuu n
\]

\medskip

\noindent
{\bf{1.8 Theorem.}}
\emph{The boundary point $a$ is regular if and only if}
\[
\sum\uuu{n=1}^\infty\, \frac{n}{\gamma\uuu n}=+\infty\tag{*}
\]
\medskip

\noindent
\emph{Proof.}
Suppose first that
(*) is convergent and then we must
prove that (1.7.1) does not hold.
To achieve this we take
some
$0<\epsilon<1/3$ which is kept fixed from now on where the assumed
convergence in (*) gives
an integer $N\uuu *$ such that
\[
\sum\uuu{n=N\uuu *}^\infty\,
 \frac{n}{\gamma\uuu n}
\leq\epsilon\tag{i}
\]

\medskip

\noindent
Choose $F\in C^0(\partial\Omega)$
with $F(0)=1 $ and
$F=0$ on $\{|z|\geq 2^{\vvv N\uuu *+1}\cap \partial\Omega\}$
while the  whole range $F(\bar\partial\Omega)$
is contained in $[0,1]$. 
Now we shall argue by contradiction and suppose that
(1.7.1) holds for $F$. This   gives the existence of a small 
$s>0$ such that 
\[
W\uuu F(z)\geq 1\vvv \epsilon\quad\text{holds Êon}\quad
D(s)\cap \Omega\tag{ii}
\]
where $D(s)$ is the 
disc of radius $s$ centered at the origin.
Next, as  $r\to 0$ the discs $D(r)$
shrink to the singleton set $\{0\}$. So by ¤ XX
the capacities
$e^{\vvv \gamma\uuu r}$ of $D(r)\cap \Omega$.
tend to zero with $r$.
Let $\nu\uuu r$ be the
equilibrium distribution
on $D(r)\cap \partial\Omega$ and put
\[
V\uuu r(z)= \frac{1}{\gamma \uuu r}\cdot \int \log\frac{1}{|z\vvv \zeta|}
\cdot d\nu\uuu r(\zeta)\tag{iii}
\]
So here $V(z)=1$ on $D(r)\cap \partial \Omega$.
Since $\gamma_r\to +\infty$ as $r\to 0$
we can choose $r<s$ so small that
\[
\max\uuu{|z|\geq s}\, V\uuu r(z)\leq\epsilon\tag{iv}
\]
Next, let  $M>N\uuu * $ be so large that $2^{\vvv M}\leq r$ and put
\[ 
U^*\uuu M(z)=\sum\uuu{n=N\uuu *}^{n=M}\,
\frac{1}{\gamma\uuu n}\cdot U\uuu n(z)
\]
With this choice it is clear that 
\[
V(z)+U^*\uuu M(z)\geq 1\quad\text{holds on}\quad 
D(2^{\vvv N\uuu *+1})\cap \partial \Omega\tag{v}
\]
Since $0\leq F\leq 1$ and $F=0$ on
$\partial\Omega\setminus D(2^{\vvv N\uuu *+1})$
we have $F\leq V+U^*\uuu M$ on the whole boundary
of $\Omega$. The minimum principle 
for super\vvv harmonic functions
gives the inequality
\[
V+U^*\uuu M\geq W\uuu F\quad\text{in}\quad \Omega\tag{vi}
\]
Now (i) and (iv) entail that
\[ 
\min\uuu{z\in \Omega\cap D(s)}\, U^*\uuu M(z)\geq 1\vvv 2\epsilon \tag{vii}
\]
At the same time we have $2^{\vvv M}\leq s$ so the construction of
$U^*\uuu M$ entails that
$U^*\uuu M=1$ holds on
$|z|\cap \partial\Omega$. Together with (vii) we obtain
\[
\min\uuu {|z|=s}\, U^*\uuu M(z)\geq 1\vvv 2\epsilon\tag{viii}
\]


\noindent
Now $U^*\uuu M$ restricts to  a super\vvv harmonic
function on $D(s)$ 
so the minimum principle for super\vvv harmonic functions gives
\[
1\vvv 2\epsilon\leq U^*\uuu M(0)
=\sum\uuu{n=N\uuu *}^{n=M}\, 
\frac{1}{\gamma\uuu n}\int\, \cdot 
\log\,\frac{1}{|\zeta|}\cdot d\mu\uuu n(\zeta)\tag{ix}
\]
Finally, $|\zeta|\geq 2^{\vvv n}$ holds on the support of $\mu\uuu n$
and hence each integral is $\leq n\cdot \log 2$. So (ix) gives
the inequality
\[
1\vvv 2\epsilon\leq \sum\uuu{n=N\uuu *}^{n=M}\, 
\frac{n\cdot \log 2}{\gamma\uuu n}<\log 2\cdot \epsilon
\]
This cannot hold
since we have chosen
$\epsilon<1/3$. It means that  (ii) cannot hold and hence 
$a$ is not a regular boundary point.

\medskip


\centerline {\emph{Proof of sufficiency.}}
\bigskip

\noindent
Above we  proved that
if $a$ is regular then the series (*) in Theorem 1.8 must diverge.
There remains to show that  if (*) is divergent then $a$ is regular.
The proof  of this converse is left as an exercise to the reader.




















\newpage


\centerline {\bf  2. Harmonic conjugates}
\bigskip

\noindent
Let $H(x,y)$ be a harmonic function of class $C^2$ which means
that 
\[ 
\Delta(H)=H_{xx}+H_{yy}=0
\]
Put
\[
u=H_x\quad v=-H_y
\]
Recall from Calculus that
the mixed second order derivatives $H_{xy}$ and $H_{yx}$ 
are equal. Hence
$u_y=-v_x$. Next, we have
\[
u_x-v_y=H_{xx}+H_{yy}=0
\]
Hence $(u,v)$ is a CR-pair and we can conclude:
\medskip

\noindent {\bf 2.1 Proposition.} \emph{Let $H$ be harmonic
in a domain $\Omega$. Then} 
\[ 
f(z)=f(x+iy)=H_x-iH_y\in\mathcal O(\Omega)
\]


\noindent
{\bf 2.2 The harmonic conjugate.} Suppose that the analytic function $f(z)$
above  has a 
primitive, i.e. there exists an analytic function $F(z)=U+iV$
whose complex derivative is $f$. We get
\[
F'(z)= H_x-iH_y=U_x+iV_x=-iU_y+V_y\tag{1}
\] 
Identifying real and imaginary parts in (1)
give
\[ 
H_x=V_y\quad \text{and}\quad H_y=-V_x\tag{2}
\]
We refer to $V$ as the harmonic
conjugate of $H$ and notice that
it  is determined up to a constant. 
\emph{Conversely}, if   $H$ has a harmonic conjugate $V$
we get  analytic function $F=H+iV$ where
\[
F'=H_x+iV_x=H_x-iH_y=f(z)
\]
Hence we have proved
\medskip

\noindent 
{\bf 2.3 Theorem} \emph{A harmonic function
 $H$ has a harmonic conjugate if and only if
the analytic function $H_x-iH_y$ is the complex derivative of an analytic function.}
\medskip

\noindent 
{\bf 2.4 Existence of harmonic conjugates.} Consider a domain 
$\Omega\in\mathcal D(C^1)$.
Let $H$ be harmonic in $\Omega$ which
extends to a $C^1$-function  up to the boundary.
Put $f(z)=H_x-iH_y$. To find an (eventual)   primitive function of $f$
we fix a point $z_0\in\Omega$ and when  $z\in\Omega$ we 
choose a path $\gamma$ from $z_0$ to $z$ and take the complex line integral of $f$ along
$\gamma$. Put
\[
F_\gamma(z)=\int_\gamma\, f \,d\zeta\tag{i}
 \]
This gives
an analytic
function $F(z)$ in $\Omega$
provided
that  the integral above
does 
not depend upon the particular path $\gamma$
which joins $z_0$ and $z$.
This independence holds if and only if the integral of $f$
is zero along every \emph{closed} curve inside $\Omega$.
Now $\partial\Omega$ consists of $k$ disjoint closed curves $\Gamma_1,
\ldots,\Gamma_k$ for some $k\geq 1$.
By the \emph{topological fact} from  XX 
the $f$-intergral is zero along each closed curve in $\Omega$
if and only if
\[ 
\int_{\Gamma_i}\,f(z)\, dz=0\quad\colon\quad 1\leq i \leq k\tag{ii}
\]
So (ii) gives a necessary and sufficient condition in order
that $f$ has a primitive analytic function.
Let us  express  (ii) via 
derivatives of  the $H$-function.
We have
\[ 
f dz=(H_x-iH_y) dz= H_xdx+H_ydy+i(H_x dy-H_y dx)\tag{iii}
\]
Since $\Gamma_i$ is closed 
the 
observation from   ¤ xx in Chapter II gives:
\[ 
\int_{\Gamma_i}\,H_x \,dx+H_y \,dy =0\tag{iv}
\] 
There remains only  the line integrals
\[ 
\int_{\Gamma_i}\,H_x \,dy-H_y \,dx=
\int_{\Gamma_i}\,\bigl[H_x\cdot  {\bf{n}}_x+H_y \cdot{\bf{n}}_y\bigr]\, ds=
\int_{\Gamma_i}\, H_{{\bf{n}}} \,ds\tag{v}
\]
Hence the results above give:
\medskip

\noindent {\bf 2.5 Proposition.}
\emph{A harmonic function $H$ which extends to a $C^1$-function on $\bar\Omega$ has a
harmonic conjugate if and only if}
\[
\int_{\Gamma_i}\, H_{{\bf{n}}}\,  ds\quad\colon\, \quad 1\leq i\leq k
\]
\emph{where $H_{{\bf{n}}}$ is the  normal derivative and
$ds$ the arc-length measure.}

\medskip

\noindent
{\bf{Remark.}}
By Theorem XX from Chapter II  the line integral of $H\uuu {{\bf{n}}}$
taken along the whole boundary is always zero, i.e.
for every harmonic function $H$ one has
\[
\sum\uuu{i=1}^{i=k}\, \int_{\Gamma_i}\, H_{{\bf{n}}}\,  ds
\]
So in order to check the conditions in Proposition 2.5 it suffices to regard
$p\vvv 1$ many boundary curves.


\medskip

\noindent
{\bf 2.6 The case $k=1$.} If $\Omega$ only has one boundary curve 
$\Gamma_1$ the remark above
shows that
every harmonic function has a conjugate.
Recall  that $\Omega$ is a \emph{Jordan domain}
when its boundary consists of a single closed curve.
Thus, in every Jordan domains there exist harmonic conjugates.
If $\Omega$ is not a Jordan domain
we cannot always find harmonic conjugates.
\medskip

\noindent 
{\bf 2.7 Example.}
Consider an annulus $\Omega=\{r<|z|<R\}$. Here
we have the harmonic function $H(z)=\log\,|z|$.
On the boundary curve $|z|=R$ we notice that $H_n=\frac{1}{R}$
and since $ds=Rd\theta$ is the arc-length measure we get
\[
\int_{\{|z|=R\}}\, H_{{\bf{n}}}\, ds=\int_0^{2\pi} d\theta=2\pi
\]
So here there does not exist a harmonic conjugate which
reflects the fact that
$\log z$ is multi\vvv valued and hence prevents the analytic function
$\frac{1}{z}$ to have a primitive in the annulus.


\medskip 

\noindent
{\bf {2.8 A special construction.}}
Let $\Omega\in\mathcal D(C^1)$
where $\partial\Omega$
consists of $p$ many pairwise disjoint and closed Jordan
curves $\Gamma_1,\dots,\Gamma_p$ and 
$\Gamma_p$ is the outer curve. 
We assume that $p\geq 2$ and consider a harmonic function
$H(z)$ which extends to a $C^1$\vvv function on $\bar\Omega$.
Put
\[ 
a_j=
\int_{\Gamma_j}\,H_{{\bf{n}}}\, ds
\quad\,\, 1\leq j\leq p-1\,.
\]
Suppose
there exist integers $m_1,\ldots,m_{p-1}$ such that
\[
a_j=2\pi\cdot m_j\quad\,\, 1\leq j\leq p\tag{*}
\]
For each $1\leq j\leq p-1$
we choose a point $z_j$ in the interior of the Jordan domain
bordered by $\Gamma_j$ and set
\[
H^*(z)=H(z)-\sum_{j=1}^{j=p-1}\, m_j\cdot\text{log}\, |z-z_j|\tag{1}
\] 
Then we see that
\[
\int_{\Gamma_j}\,H^*_{{\bf{n}}}\, ds=0
\quad\,\, 1\leq j\leq p-1\,.
\]
Proposition 2.5 shows that
$H^*$ has a harmonic conjugate $V^*$ and there
exists the analytic function
\[ 
f(z)=H^*(z)+iV^*(z)\tag{2}
\]
It follows that

\[
\bigl|e^{f(z)}\bigr|=e^{H^*(z)}= e^{H(z)}\cdot
\bigl| (z-z_1)^{-m_1}\cdots (z-z_{p-1})^{-m_{p-1}}\bigr|
\]

\medskip


\noindent
Hence, with $g(z)=(z-z_1)^{m\uuu 1}\cdots [z-z_{p-1})^{m_{p-1}}\cdot e^{f(z)}$ 
we have :
\medskip

\noindent
{\bf 2.9 Theorem.}
\emph{Let $H(z)$ be a harmonic function in
$\Omega$ such that the periods $a_1,\ldots,a_{p-1}$ are integer multiples of
$2\pi$.
Then there exists a zero\vvv free  analytic function $g(z)\in\mathcal O(\Omega)$ 
such that}
\[ 
|g(z)|= e^{H(z)}
\]
\medskip

\noindent
{\bf{Exercise.}}
By the construction above the $g$\vvv function extends to a 
$C^1$\vvv function on the closure
$\bar\Omega$ and 
the reader should verify that
\[
\int_{\Gamma_j}\,H_{{\bf{n}}}\, ds
=\mathfrak{Im}\bigl[\,
\int_{\Gamma_j}\,
\frac{g'(z)dz}{g(z)-w}\,\bigr]
\]
hold for every boundary curve.
Show also  the converse to
Theorem 2.9. Thus, assume that there exists an
analytic function $g(z)$ with no zeros in $\Omega$ such that
$|g(z)|= e^{H(z)}$ holds and deduce that   the period numbers $\{a\uuu j\}$
are integers times $2\pi$.

\medskip







\noindent
{\bf 2.10 The case when
$H$ is constant on boundary curves.}
Let $H$ be as in Theorem 2.8
and suppose also that
$H(z)= c_j$ is a constant on every  boundary curve of $\Omega$.
Then  $|g(z)|= e^{c_j}$
is constant on each $\Gamma_j$.
Let $w$ be a complex number whose absolute value is
$\neq e^{c_j}$ for every $j$.
Let $\mathcal N(g:w)$ be the
number of zeros of $g(z)$ in $\Omega$
counted with multiplicity.
The  formula from
Theorem XXX in Chapter 4 gives:
\[
\mathcal N(g:w)=
\mathfrak{Im}\,\bigl[\frac{1}{2\pi}\sum_{\nu=1}^p\,
\int_{\Gamma_\nu}\,
\frac{g'(z)\,dz}{g(z)-w}\bigr]
\]


\noindent
As explained in XX each single integral
\[
\mathfrak{Im}\bigl[\frac{1}{2\pi}\cdot \int_{\Gamma_\nu}\,
\frac{g'(z)\,dz}{g(z)-w}\bigr]\tag{ii}
\]
is equal to the winding number of the
image curve
$(g(z)-w)\circ\Gamma_\nu$.
This individual winding number is zero if
$|w|> e^{c_j}$ and if
$|w|<e^{c_j}$ the stability of the winding number under
a homotopic deformation identifies (ii) with
the value when $w=0$.
Next, Theorem 2.9 gives
the equality
\[ 
g'(z)= g(z)\cdot (H_x-iH_y)
\]
So with $w=0$ it follows that
(ii) becomes
\[
\mathfrak{Im}\bigl[\frac{1}{2\pi}\cdot \int_{\Gamma_\nu}\,
(H_x-iH_y)\, dz \bigr]=
\frac{1}{2\pi}\cdot \int_{\Gamma_\nu}\,
H_x\,dy+
H_y\, dx=
\frac{1}{2\pi}\cdot \int_{\Gamma_\nu}\,
H_{\bf{n}}\,ds
\]
Hence we have proved the following:

\medskip

\noindent
{\bf 2.11 Theorem}
\emph{Let  $w$ be a complex number such that
$|w|\neq e^{c_j}$ for every
$j$ and denote by $w(*)$ the set of 
those $j$:s  for which
$|w|<e^{c_j}$. Then one has the equality}

\[
\mathcal N(g:w)=\frac{1}{2\pi}\cdot
\sum_{j\in w(*)} \, a_j
\]


\medskip


\noindent
{\bf 2.12 Example.}
Suppose that $a_p=2\pi\cdot m$
for some positive integer $m$ while $a_\nu=-2\pi\cdot $
for every $1\leq\nu\leq p-1$.
Suppose that $w$ belongs to the open image set $g(\Omega)$
which means that the sum in Theorem  2.11 is a positive integer.
Since $a_j\leq 0$
when $j\leq p-1$
it follows that the term from $a_1$ must be $>0$ and hence
$|w|<e^{c\vvv 1}$.
Thus, $g(\Omega)$ is contained in the
disc of radius $e^{c_1}$.
Moreover, there cannot exist
$2\leq j\leq p-1$ with
$e^{c_j}>e^{c-1}$
for then we can choose
$|w|>e^{c_1}$ while $|w|<e^{c_j}$
and then the right hand side in Theorem  2.11 would be a negative
integer.

\newpage

\centerline {\bf 3. Harmonic functions in a disc.} 
\bigskip

\noindent
Above we studied general  domains
$\Omega\in\mathcal D(C^1)$. 
Here we specialize to the case when
$\Omega=D$ is the unit disc
centered at the origin.
Already in Chapter 1 we  encountered
the Poisson kernel and described   how  to solve
the Dirichlet problem. Let us  resume this 
and give  alternative proofs.
If $f$ is analytic in a neighborhood of $\bar D$ we have:
\[
f(z)=\frac{1}{2\pi i}\int_{|\zeta|=1|}\, \frac{f(\zeta)\,d\zeta}{\zeta-z}=
\frac{1}{2\pi }\int_0^{2\pi}\, 
\frac{f(e^{i\theta}) \, d\theta}
{1-ze^{-i\theta}}
\]
Since   $z^nf(z)$ is analytic
for each
non-negative integer $n$ we have 
\[ 
\int_{|\zeta|=1}\,\zeta^n f(\zeta)\,d\zeta=
i\cdot \int_0^{2\pi}\, e^{i(n+1)\theta}\,f(e^{i\theta})\, d\theta=0\tag{i}
\]
Consider the geometric series
\[
\frac{\bar ze^{i\theta}}{1-\bar z e^{i\theta}}=
\sum_{n=0}^\infty \bar z^{n+1}e^{i(n+1)\theta}
\]
Since the series converges absolutely when $|z|<1$, the vanishing (i) gives
\[
\int_0^{2\pi}\, 
\frac{\bar ze^{i\theta}\cdot f(e^{i\theta})\cdot d\theta}{1-\bar z e^{i\theta}}=0\tag{*}
\]
\medskip

\noindent 
{\bf 3.1 The Poisson kernel}.
Let us add the zero term (*)  to
the Cauchy integral and put
\[
P(z,\theta)=\frac{1}{2\pi}\cdot 
\frac{1}{1-ze^{-i\theta}}+
\frac{\bar ze^{i\theta}d\theta}{1-\bar z e^{i\theta}}=
\frac{1-|z|^2}{|1- z e^{-i\theta}|^2}
\]
\medskip

\noindent
where the last equality follows since
$|1- z e^{-i\theta}|^2=(1- z e^{-i\theta})(1- \bar z e^{i\theta})$.
We refer to $P(z,\theta)$ as the \emph{Poisson kernel}. 
The results above give
\bigskip


\noindent 
{\bf 3.2 Theorem} \emph{For each analytic function $f$ in $D$ which extends
continuously to $\bar D$ one has}
\[
f(z)=
\int_0^{2\pi}\, P(z,\theta)f(e^{i\theta})\,d\theta\quad\colon\quad
z\in D
\]
\medskip

\noindent
Since the Poisson kernel is \emph{real-valued} we can decompose $f=u+iv$ into
its real and imaginary parts and obtain
\[
u(z)=\int_0^{2\pi}\, P(z,\theta)u(e^{i\theta})\,d\theta\quad\colon\quad
v(z)=\int_0^{2\pi}\, P(z,\theta)v(e^{i\theta})\,d\theta
\]
\medskip

\noindent
{\bf 3.3 Solution to Dirichlet's Problem}
Keeping $\theta$ fixed we have 
a function in $D$ defined by
$z\mapsto P(z,\theta)$.
From the construction we have
\[ 
2\pi\cdot P(z,\theta)=
\frac{1}{1-ze^{-i\theta}}+
\frac{\bar ze^{i\theta}d\theta}{1-\bar z e^{i\theta}}
\]
The first term is an analytic function of $z$ in $D$ and since both
the real and imaginary parts of an analytic function are harmonic, this complex 
valued function satisfies the Laplace equation. The second term  is
an \emph{anti-analytic function}, i.e. analytic with respect to the conjugate
complex variable. These functions also satisfy the Laplace
equation and hence the function
$z\to P(z,\theta)$ is harmonic in $D$.
Now we 
solve  the Dirichlet problem in $D$.

\newpage

\noindent {\bf 3.4 Theorem} \emph{Let $h\in C^0(T)$. Put}
\[ 
H(z)=\int_0^{2\pi} P(z,\theta)h(e^{i\theta})\, d\theta
\]
\emph{Then $H$ solves the Dirichlet problem, i.e.
it extends to  a continuous function on
$T$ where it is equal to $h$.}
\medskip

\noindent
{\bf Proof.}
We use that $h$ is uniformly continuous and define its modulus of continuity:
\[ 
\omega(\delta)=\max\,|h(\theta_1)-h(\theta_2)|\quad
\colon\quad |\theta_1-\theta_2|\leq
\delta 
\]
For each $0\leq\alpha\leq 2\pi$
we  take a difference and obtain

\[
2\pi\cdot [H(re^{i\alpha})-h(e^{i\alpha})]= 
\int_0^{2\pi}\,\frac{(1-r^2)[h(e^{i(\theta+\alpha)}- h(e^{i\alpha})]\cdot d\theta}
{1+r^2-2r\text{cos}\,\theta}
\]
By the triangle inequality and the definition of the $\omega$-function,
the absolute value of the left hand side
is majorized by
\[
\int_0^{2\pi}\,
\frac{(1-r^2)\cdot \omega(\theta)}
{1+r^2-2r\text{cos}\,\theta}\, d\theta
\]
With $\delta>0$ given we split the $\theta$-integral in two parts, where we integrate over
$-\delta<\theta<\delta$ and in the second part $|\theta|\geq\delta$.
Since the $\omega$-function is non-decreasing, i.e.
$\omega(\theta)\leq \omega(\delta)$ hold when $|\theta|\leq\delta$ we then majorize the integral above by
\[ 
\omega(\delta)+
M\cdot \int_{|\theta|\geq \delta}\,
\frac{(1-r^2)\,d\theta}
{1+r^2-2r\text{cos}\,\theta}
\]
where $M$ is the maximum norm of the $\omega$-function.
With $r=1-s$ and $0<s\leq 1$ the last integral above is majorized by
\[
2Ms\cdot 
\int_{|\theta|\geq \delta}\,\frac{d\theta}{(2-s)(1-\text{cos}\,\theta)}
\leq
2Ms\cdot 
\int_{|\theta|\geq \delta}\,\frac{d\theta}{1-\text{cos}\,\theta}
\]
where the positive contribution of $s^2$ in the denominator is
removed since this only strenghtens the inequality.
Next, since 
$(1-\text{cos}\,\theta\geq \theta^2/2$ the lat integral is majorised
by
\[
\int_{|\theta|\geq \delta}\,\frac{2d\theta}{\theta^2}=4\frac{\pi\vvv\delta}{\delta}
\leq \frac{4\pi }{\delta}
\]
Hence
(*) is majorized by
\[
\omega(\delta)+\frac{8\pi M(1\vvv r)}{\delta}
\]
The required limit as $r\to 1$ follows since the $\omega$-function tends to zero, 
i.e. given $\epsilon$ we choose $\delta$ so that $\omega(\delta)<\epsilon$
and after we choose $1\vvv r<\frac{1}{8\pi M}\delta\epsilon$ which majorizes
(*) with $2\epsilon$.
\bigskip

\noindent 
{\bf 3.5 Remark} When the boundary function $h$ has
extra continuity, say that it is of class $C^1$ one can improve the
rate of convergence.
But we shall not  to discuss detailed
estimates concerned with  the rate of convergence of 
\medskip
\[ 
r\mapsto \max_\theta\, |\,H(re^{i\theta})-h(e^{i\theta})\,|
\] 
as $r\to 1$.
One may also consider boundary functions 
for any $L^1$\vvv function
$h(\theta)$ on the
unit circle we can apply the Poisson kernel and obtain a harmonic
function $H(z)$ in the unit disc defined by
\[ 
H(z)=\int_0^{2\pi}\,P(z,\theta)\cdot  h(\theta)d\theta
\]

\noindent
The question arises if the $H$-function has \emph{radial limit values}, i.e. if
there exist limits of the form
\[ 
\lim_{r\to 1}
H(re^{i\theta})=h(\theta)\tag{*}
\]
One expects that the radial limit exists for all $\theta$ outside 
a null set, i.e.  convergence holds almost 
everywhere in the sense of Lebesgue. This is indeed true.
More precisely (*) holds at every Lebesgue point of the $L^1$\vvv function $h$.
We refer to ¤ 3.18  for  further details about  
boundary values of $H$ when we start from a Riesz measure on
$T$.


\bigskip



\centerline {\bf 3.6 Herglotz formula.}
\medskip

\noindent
Given a real-valued continuos  function $u$ on the unit circle we define
a function $U(z)$ in  $D$ by
\[
U(z)=\frac{1}{2\pi}\int_0^{2\pi}\frac{e^{i\theta}+z}
{e^{i\theta}-z}\cdot u(e^{i\theta})\cdot d\theta\tag{*}
\]
It is clear that $U(z)$ is an analytic function in $D$ since 
the
geometric series of  the denominator converges when $|z|<1$.
Next, multiply with $e^{-i\theta}-\bar z$ which is the complex conjugate of the denominator and notice that:

\[ 
(e^{-i\theta}-\bar z)(e^{i\theta}-z)=
1-|z|^2-2i\cdot \mathfrak{Im}(ze^{-i\theta})
\]
It follows that
\[
U(z)=\frac{1}{2\pi}\int_0^{2\pi}\,[\frac{1-|z|^2}{|e^{i\theta}-z|^2}
\cdot u(e^{i\theta})d\theta+
\frac{i}{2\pi}\int_0^{2\pi}\,[\frac{ \mathfrak{Im}(ze^{-i\theta})}{|e^{i\theta}-z|^2}
\cdot u(e^{i\theta})d\theta\tag{**}
\]
Hence the real part of $U$ is the Poisson integral of $u$, i.e. $\mathfrak{Re}(U)$
is the harmonic extension of $u$.
The second integral which yields the 
harmonic conjugate to
$\mathfrak{Re}(U)$.
Starting with an analytic function $f(z)=u+iv$ and choosing $h=u|T$ as a boundary function, the construction gives
\medskip

\noindent {\bf 3.7 Theorem.} 
\emph{Let $f(z)$ be analytic in $D$ with continuous boundary values. Then}
\[
f(z)=\frac{1}{2\pi}\int_0^{2\pi}\frac{e^{i\theta}+z}
{e^{i\theta}-z} \cdot \mathfrak{Re}(f(e^{i\theta}))\cdot d\theta+
i\cdot \mathfrak{Im}(f(0))\quad\colon\quad z\in D
\]
\medskip  

\noindent
Hence $f$ is represented by a boundary integral
expressed by its real part only, except for the value
of its imaginary part at the origin.
\bigskip

\noindent 
{\bf 3.8 Formula for a  harmonic conjugate}.
Start with some real-valued continuous function
$u$ on the unit circle $T$.
We find the unique analytic function $f(z)$
in $D$ whose real part is $u$ on $T$ while $f(0)$ is real.
Now $\mathfrak{Im}\, f$
is 
the harmonic conjugate of $\mathfrak{Re}\ f$
and (**) above gives:

\medskip

\[
\mathfrak{Im} f(z)=
\frac{1}{2\pi}\int_0^{2\pi}\,\frac{ \mathfrak{Im}(ze^{-i\theta})}{|e^{i\theta}-z|^2}
\cdot u(e^{i\theta})d\theta\tag{***}
\]
\medskip

\noindent
{\bf{3.9 The conjugate kernel $\mathcal C$}}.
In the product set $D\times T$
we define the function
\medskip

\[
\mathcal C(z,\theta)=
\frac{1}{2\pi}\cdot\frac{ \mathfrak{Im}(ze^{-i\theta})}{|e^{i\theta}-z|^2}
\] 
\medskip

\noindent 
The $\mathcal C$-function
is no longer positive
and the integrals with respect to $\theta$
of its absolute value increase when $|z|\to 1$.
Namely, let  $z=r=1-s$ with $0<s<1$.
Then
\[
|\mathcal C(z,\theta)|=
\frac{1-s}{2\pi}\cdot\frac{| \text{sin}\,\theta\,|}{
[\,s^2+2(1-s)(1-\text{cos}\,\theta)\,]^2}
\]
So when $s$ and $\theta$ both are close to zero  the order
of magnitude of $\mathcal C$ becomes
\[ 
|\mathcal C(s,\theta)|\simeq\frac{|\theta|}{(s^2+\theta^2)^2}\tag{1}
\]
This explains why the map which sends 
a boundary function $u(e^{i\theta}) $ into 
the boundary value function
$v(e^{i\theta}$ of the harmonic conjugate of the
harmonic extension of $u$ 
is not so well-behaved. 
However, certain estimates are available.
In particular the BMO-norm of the conjugate boundary
value function $v$ can be estimated by the maximum norm of $u$.
\bigskip

\noindent
{\bf 3.10 Theorem.}
\emph{There exists an absolute  constant $C$ such that}
\[ 
[v|_{\text{BMO}}\leq C\cdot\max_\theta\,|u(e^{i\theta})|
\]
\medskip

\noindent
The proof  
boils down to
an exercise in one variable analysis.
Namely, regard the following linear operators:
\medskip

\noindent {\bf 3.11 Definition.} \emph{To each $s>0$ we define
the  operator $T_s$ acting on real-valued functions $f(x)$ with support in
$[-1,1]$ by}
\[ 
T_s(f)(y)=
\int_{-1}^1\, \frac{x}{x^2+s^2}\cdot f(x+y)dy
\]
In the case when $f$ is an even function we notice that
$T_s(f)(0)=0$.
From the definition of functions in BMO and 
recalling that $\text{sin}\,\theta\simeq\theta$ for small $\theta$,
the reader will have no difficulty to derive Theorem 3.10  from
the following result:
\bigskip

\noindent 
{\bf 3.12 Proposition.}
\emph{There exists a constant $C$ such that the following holds when
$f$ is even and has support in $[-1,1]$:}
\medskip
\[
|\int
\frac{1}{2h}\int_{-h}^h\, T_s(f)(y)dy|\leq |f|_\infty\quad\colon
\forall \,\,\, 0< s,h<1
\]
\medskip

\noindent \emph{Proof.} By partial integration
the term above becomes
\[
\frac{1}{2h}\int\,\text{Log}\,[\frac{(\xi-h)^2+s^2}{
(\xi+h)^2+s^2}\,]\cdot f(\xi)d\xi
\]
Hence there only remains to show that there exists $C$ so that
\[
\int_{-1}^1\,
|\text{Log}\,[\,\,\frac{(\xi-h)^2+s^2}{(\xi+h)^2+s^2}]\,|d\xi\leq C\cdot h
\]
Obviously $C$ exists if there is a constant $C^*$ such that
\[ 
\int_0^1\,
\text{Log}\,|\frac{(\xi+h)^2+s^2}{\xi^2+s^2}|d\xi\leq C^*\cdot h\tag{i}
\]
Now we use that
\[
\frac{\xi+h)^2+s^2}{\xi^2+s^2}=1+\frac{2h\xi+h^2}{\xi^2+s^2}\leq
1+\frac{2h^2+\xi^2}{\xi^2}= 2+2\frac{h^2}{\xi^2}
\]
So there remains only to show
\[
\int_0^1\,
\text{Log}\,[2+2\frac{h^2}{\xi^2}\,]\cdot d\xi\leq
C^*\cdot h\quad\colon\, 0<h<1\tag{ii}
\]
With $\xi=hu$ this follows since
\[
\int_0^\infty\,
\text{Log}\,[2+2\frac{1}{u^2}]\cdot du<\infty\tag{iii}
\] 
In other words, we can take  $C^*$ as the value of this
convergent integral.
\bigskip

\centerline {\bf 3.13 A duality theorem.}
\medskip

\noindent
Theorem 3.10 shows
that the harmonic conjugation functor 
expressed via the boundary value function 
\[ 
u\mapsto \mathcal C(u)
\quad\colon\, u(e^{i\theta})\in L^\infty(T)
\]
\medskip

\noindent
is a continuous linear operator from $L^\infty(T)$ into BMO.
Next,   consider the
Hardy space $H^1(T)$ which consists of
those $f\in L^1(T)$ which are boundary values
of analytic functions in $D$, or equivalently those 
integrable functions on the unit circle for
for which
\medskip

\[ 
\int_0^{2\pi}\, e^{in\theta}\cdot f(e^{i\theta})\cdot d\theta=0
\quad\colon\, n=1,2,\ldots
\]
\medskip

\noindent
The following result is due to C. Fefferman and E. Stein in [F-S]:
\medskip

\noindent
{\bf 3.14 Theorem}
\emph{There exists an absolute constant $C$
such that}


\[
|\int_0^{2\pi}\,\phi(e^{i\theta})\cdot
f(e^{i\theta})\cdot d\theta\,|\leq C\cdot 
|\phi|_{\text{BMO}}\cdot |f|_1
\] 
\emph{hold for all pairs $f\in H^1(T)$ and $\phi$ in BMO.}
 
\bigskip

\noindent 
For the proof of Theorem 3.14 and an account about
Hardy spaces and  BMO  the reader is
referred to text-books by E. Stein. See in particular (St:xxx].
\bigskip

\centerline {\bf 3.15 The Riesz transform}
\medskip

\noindent
Let $f(\theta)\in L^1(T)$.
We get the Fourier coefficients


\[ 
\hat f(n)=
\int_0^{2\pi}\,e^{-in\theta}f(\theta)d\theta
\]
A dense subspace of $L^1(T)$ consists of trigonometric
polynomials, i.e.
those functions on $T$ with a finite Fourier series.
Denote this subspace by $\mathcal P$.
On this subspace we define the linear operator
$\mathcal R$  by
\[
\mathcal R(e^{i\nu\theta})=-e^{i\nu\theta}\,\,\colon\,\nu\leq -1\quad\colon
\mathcal R(e^{i\nu\theta})=e^{i\nu\theta}\,\,\colon\,\nu\geq 1
\quad\colon\,\mathcal R(1)=0\tag{*}
\]


\noindent
This operator is closely related to the harmonic conjugation functor.
To see this, let $n\geq 1$ and 
and put
\[
u_n(\theta)=
\frac{1}{2}[e^{in\theta}+e^{-in\theta}]
\]
Its harmonic extension to $D$ is $\mathfrak{Re}\,(z^n)$
and hence the boundary function of the harmonic conjugate is
\[ 
v(\theta)=
\frac{1}{2}[e^{in\theta}-e^{-in\theta}]\implies
\]
\[ 
\mathcal C(u)=v=\mathcal R(u)\tag{**}
\]
Taking linear sums we conclude that
$\mathcal R$ via the associated Fourier series
coincides with  the harmonic conjugation functor.
Passing to functions $f(\theta)$ which belong to $H^\infty(T)$
Theorem 3.10 therefore proves  that
$\mathcal R(f)$ has a bounded means oscillation.
In other words,
$\mathcal R$
gives a continuous linear operator from
$H^\infty(T)$ to $\text{BMO}(T)$.
We shall not continue this discussion since it is a topic
in the theory about singular integral operators.
See the text-books by E. Stein which
presents this theory from many aspects including 
higher dimensional cases.

\bigskip




\bigskip

\centerline{\bf{3.16 Poisson integrals of Riesz measures.}}
\medskip

\noindent
Let $\mu$ be a real Riesz measure on $T$.
In general it is decomposed into $\\mu\uuu c+\mu\uuu s$
where $\mu\uuu c$ is absolutely continuous and $\mu\uuu s$ is
singular. We obtain a harmonic function $H\uuu \mu(z)$ in $D$
defined by

\[
H\uuu \mu(z)= \frac{1}{2\pi}\int\,
\frac{1\vvv |z|^2}{|e^{i\theta}\vvv z|^2}\cdot d\mu(\theta)
\]

\medskip

\noindent
{\bf{Exercise.}}
Show the inequality below for each $r<1$:
\[
\int\uuu 0^{2\pi}\, |H(re^{i\phi}|\cdot d\phi\leq ||\mu||
\quad \colon\quad ||\mu\||\quad \text{is the total variation of}\quad \mu
\tag{1}
\] 
Next, let $g(\theta)$ be a continuous function on $T$ identified
with the $2\pi$\vvv periodic $\theta$\vvv interval.
Using the uniform continuity of $g$
the reader may verify the limit formula
\[
\lim\uuu{r\to 1}\, 
\int\uuu 0^{2\pi}\, g(\theta)\cdot H(re^{i\theta})=
\int\uuu 0^{2\pi}\, g(\theta)\cdot d\mu(\theta)\tag{2}
\]
Since (2) holds for every $g\in C^0(T)$ it means that
the absolutely continuous measures
$\{H(re^{i\theta})\}$ converge weakly to $\mu$ where
Riesz' representation theorem  identifies
the dual space of $C^0(T)$ with Riesz measures on $T$.
\medskip

\noindent
{\bf{A converse result.}}
Let $H(z)$ be harmonic in $D$ and assume that there is a constant
$C$ such that
\[
\int\uuu 0^{2\pi}\, |H(re^{i\theta})|\cdot d\theta\leq C
\quad \text{hold for all}\quad  r<1\tag{*}
\]

\medskip

\noindent
{\bf{3.17 Theorem.}}
\emph{When (*) holds there exists a unique Riesz measure $\mu$ on $T$
such that $H=H\uuu \mu$.}
\medskip

\noindent
\emph{Proof.}
Notice that (*) means that the family of 
absolutely continuous measures on $T$
given by the family $\{\mu\uuu r(\theta)= H(re^{i\theta})\}$
is bounded. So by the compactness in the weak topology
of measures  there exists 
an increasing sequence $\{r\uuu n\}$
where $r\uuu n\to 1$ and a Riesz measure $\mu$
such that
\[
\lim\uuu {n\to\infty}\, 
\int\uuu 0^{2\pi}\, g(\theta)\cdot H(r\uuu n e^{i\theta})d\theta=
\int\uuu 0^{2\pi}\, g(\theta)\cdot d\mu(\theta)\tag{i}
\] 
hold for every $g\in C^0(T)$.
There remains to see why this gives $H=H\uuu \mu$ in $D$.
To prove this we fix $z\in D$ and if $r\uuu n>|z|$
we have the Poisson formula
\[
H(z)= 
\int\uuu 0^{2\pi}\, \frac{r\uuu n^2\vvv |z|^2}{
r\uuu n e^{i\theta}\vvv z|^2}\cdot 
H(r\uuu n e^{i\theta})d\theta\tag{ii}
\]
Keeping $z\in D$ fixed we set 
\[
g\uuu n(\theta)=
\frac{1}{2\pi}
\cdot  \frac{r\uuu n^2\vvv |z|^2}{
|r\uuu n e^{i\theta}\vvv z|^2}\quad\text{and}\quad
g\uuu *(\theta)=\frac{1}{2\pi}
\cdot  \frac{1\vvv |z|^2}{
|e^{i\theta}\vvv z|^2}
\]
It is clear that $g\uuu n\to g\uuu *$ holds uniformly 
over $0\leq\theta\leq 2\pi$
as $n\to \infty$.
So if $\epsilon>0$ we can find $n*$ such that $n\geq n\uuu *$ entails
\[
\bigl |H(z)\vvv \int\uuu 0^{2\pi}\, g\uuu *(\theta)\cdot 
H(r\uuu n e^{i\theta})d\theta\,\bigr|<\epsilon
\]
Now
\[
H\uuu \mu(z)= \int\uuu 0^{2\pi}\,g\uuu *(\theta)\cdot d\mu(\theta)
\]
and at the same time (i) holds. So when $n\geq n*$ we see that
\[
|H(z)\vvv H\uuu\mu(z)|<2\epsilon
\] 
Finally, since $\epsilon>0$ is arbitrary we get $H=H\uuu\mu$ as required.
\medskip

\noindent{\bf{Remark.}}
Theorem 3.17 gives a 1\vvv 1 correspondence between the space of 
Riesz measures on $T$ and harmonic functions in $D$
satisfying the $L^1$\vvv condition (*).
\medskip

\noindent
{\bf{3.18 Radial limits.}}
Let $\mu$ be a Riesz measure on $T$
which gives the harmonic function $H\uuu\mu$.
it turns out that radial limits exist almost everywhere.


\medskip

\noindent
{\bf{3.19 Theorem.}}
\emph{Write $\mu=\mu\uuu c+\mu\uuu s$.
Then there exists a null set $E$ on $T$ such that}
\[
\lim\uuu{r\to 1}\, H\uuu\mu(re^{i\theta})= \mu\uuu c(e^{i\theta})
\] 
\emph{holds when $\theta\in T\setminus E$ and 
$\theta$ is a Lebesgue point of the $L^1(T)$\vvv function
$\mu\uuu c(e^{i\theta})$}
\medskip

\noindent
{\bf{Exercise.}} Prove this result.
A hint concerning the singular part $\mu\uuu s$
is as follows: Since $\mu\uuu s$ is singular we know from
XX that there exists a null set
$F$ on $T$ such that
\[
\lim\uuu {\delta\to 0}\,
\frac{1}{\delta}\cdot \int\uuu {\theta\vvv \delta}^{\theta+\delta}\, 
|d\mu\uuu s(\theta)|=0
\]
for each $\theta\in T\setminus F$.
Using the expression of the Poisson kernel the reader can verify
that this gives:
\[
\lim\uuu {r\to 1}\, H\uuu{\mu\uuu s}(re^{i\theta})=0\quad\text{
for each}\quad \theta\in T\setminus F
\]
\medskip

\noindent
{\bf{3.20 A class of analytic functions.}}
Let $\mu$ be a singular measure on $T$.
In $D$ we get the analytic function

\[
U\uuu \mu (z)=\frac{1}{2\pi}\int_0^{2\pi}\frac{e^{i\theta}+z}
{e^{i\theta}-z}\cdot d\mu(\theta)
\]
We see that $\mathfrak{Re}\, U\uuu\mu=H\uuu \mu$ and
taking the exponential  we get the analytic function

\[ 
\omega\uuu \mu(z)=e^{U\mu(z)}
\]
Here
the absolute value
\[
 |\,\omega\uuu\mu(z)|= e^{H\uuu \mu(z)}
\]
Theorem 3.19 entails that there is a null set $F$ on $T$ such that
\[
\lim\uuu {r\to 1}\, |\omega\uuu\mu(re^{i\theta})|=1
\quad\colon\quad \theta\in T\setminus F\tag{1}
\] 


\noindent
The question arises if there  exist radial limits
\[
\lim\uuu {r\to 1}\, 
\omega\uuu\mu(re^{i\theta})=\omega\uuu *(e^{i\theta})
\]
outside a null set.
This turns out to be true but the proof is more involved and relies 
upon the Brothers Riesz theorem which is established in 
Section X from Special Topics
and a further study of analytic functions of the form
$\omega\uuu \mu(z)$ for singular Riesz measures is treated in 
XX from Special Topics.









 



















\newpage



\noindent
\centerline {\bf\large  4. The mean value property}
\bigskip

\noindent
Let $H$ be a harmonic function defined in an open 
domain $\Omega$. Let $z_0\in\Omega$ and  $D$ is a disc centered at $z_0$
of some radius $R$ with $R$ chosen so that 
$\bar D\subset \Omega$. 
We already know 
the mean-value formula:

\[
H(z_0)=\frac{1}{2\pi}\int_0^{2\pi}\, H(z_0+Re^{i\theta})d\theta\tag{*}
\] 
It turns out that the converse is true. More precisely
a real-valued and continuous
function in $\Omega$
satisfying a local mean-value formula at every point in $\Omega$
is harmonic. 
Since the condition to be harmonic is local it suffices to
prove this when $\Omega$ is a disc. 
\medskip

\noindent
{\bf 4.1 Theorem} \emph{Let $\bar D$ be a closed disc of some radius $R$ centered at the origin. Let $h\in C^0(\bar D)$ and assume that to every $z_0\in D$ there exists some 
$0<r\leq\text{dist}(z_0,\partial D)$ such that $h(z_0)$ equals its mean value over 
the circle $|z-z_0|=r$. Then $h$ is harmonic in $D$.}
\medskip

\noindent 
\emph{Proof.} We  solve the Dirichlet problem and find a harmonic 
function $H$ in $D$ which extends to a continuous function 
on $\bar D$ where $H=h$ on the circle $\{|z|=R\}$.
Now we claim that $h=H$. Assume the contrary and suppose 
for example that there exists a point $z_0$ where $h(z_0)>H(z_0)$. 
Since a continuos function achieves its maximum on the compact set 
$\bar D$ we get the closed set $K$ where
$h-H$ takes its maximum. Here $K$ must be inside the open disc since
$h=H0$ on the boundary. Choose a point $z^*\in K$
such that $|z^*|\geq |z|$ for any other point $z\in K$.
By hypothesis there exists a circle of some radius $r\leq R-|z^*|$ such that
$h(z^*)$ is equal to its mean value over the circle $T=\{|z-z^*|=r\}$.
Since the harmonic function $H$ satisfies the mean value condition  everywhere, 
it follows that
\[
h(z^*)-H(z^*)=\frac{1}{2\pi}\int_0^{2\pi}\,
(h-H)(z^*+re^{i\theta}])d\theta\tag{i}
\]
But this gives a contradicton. For $H-h$
takes its maximum at
$z^*$ and by the choice of $z^*$ we can find
$\theta$ such that $z^*+re^{i\theta}$ is outside the set $K$
and then the integral in (i) cannot be equal to
$h(z^*)-H(z^*)$.
This proves that $h\leq H$ holds in the whole disc.
Since $-h$ also satisfies the local mean value condition we prove that
$h\geq H$ in the same way and Theorem 3.1 follows.

\bigskip

\noindent
{\bf 4.2 Remark} 
Notice that Theorem 4.1 implies that if $h$ is
\emph{not} harmonic then
there must exist
some point $z_0\in D$ such that
\[
h(z_0)\neq\frac{1}{2\pi}\int_0^{2\pi}\, h(z_0+re^{i\theta})d\theta
\] 
hold for all $0<r\leq R-|z_0|$.
Notice also that this inequality means that $h(z_0)$ is either 
strictly less or strictly larger
than all mean-values above.

\bigskip



\noindent
{\bf 4.3 A study of $\log\,|f|$.}
Let $\Omega\in\mathcal D(C^1)$
and $f$ is an analytic function in $\Omega$ which extends to
a continuos function on $\bar\Omega$. We also assume that
$f\neq 0$ on $\partial\Omega$ but inside $\Omega$ it has some zeros 
$a_1,\ldots,a_k$ where the multiplicity
of each zero can be any positive integer.
Outside these zeros 
$\log \,|f|$ exists as a harmonic  function.
Now one has the following  inequality:
\medskip  

\noindent
{\bf 4.4 Proposition} \emph{Let $h$ solve Dirichlet's problem for the boundary function
$\log\,|f|$. Then} 
\[
\log\,|f(z)|\leq h(z)\quad\,\colon\quad z\in
\Omega\setminus (a_1,\ldots,a_k)
\]
\medskip

\noindent
{\bf Proof.}
Let $\epsilon>0$ be small and let $\Omega_\epsilon$ be the open set 
where the closed
discs of radius $\epsilon$ around the zeros of $f$ are removed from
$\Omega$.
If $m$ is the order of a zero of $f$ at $a_\nu$ we have
\[
\log(|f|)(z-a_\nu)=
m\cdot \log\,|z-a_\nu|+\,\,\,\text{a bounded function}
\]
when $z$ is close to $a_\nu$.
So on the boundaries  of the removed discs the harmonic function
$\log \,|f|$ is negative and $\simeq$ to the negative number
$m\cdot \log (\epsilon)$. For a sufficiently small $\epsilon$ it therefore follows that
\[ 
\log |f|(z)\leq h(z)\quad\,\colon\quad z\in\cup\,\partial D_\epsilon(a_\nu)
\]
\medskip
At the same time equality holds on $\partial\Omega$. Hence the maximum principle
for harmonic functions gives  
the inequality
\[
\text{Log}(|f|)(z)\leq h(z)\quad\,\colon\quad z\in\Omega\setminus
\cup\,\bar D_\epsilon(a_\nu)
\]
Since we can take any small $\epsilon$  Proposition 2.4 follows.


\bigskip

\noindent {\bf 4.5 A specific majorisation.}
Let $f(z)$ be analytic in the  half-plane $\mathfrak{Im}\, z>0$ which
extends continuously to the real line $\{\mathfrak{Im}\,z=0\}$.
Consider a finite sequence of real numbers 
$a_0<a_1<\ldots a_N$ where some $a_\nu$ may be negative.
We get the pairwise disjoint intervals
\[
J_0=(-\infty,a_0)\quad J_\nu=(a_\nu,a_{\nu+1})\colon\,\,
0\leq\nu\leq N-1\quad J_N=(a_n,+\infty)
\]
Suppose there are constants $c_0,\ldots,c_N$ such that
\[
\text{Log}\,|f(x)|\leq c_\nu\quad\colon\quad x\in J_\nu
\quad\colon \quad 0\leq\nu\leq N
\]
In addition to this we assume that
\[
\lim_{|z|\to \infty}\,f(z)=0\tag{*}
\]
where $z$ stay in the closed upper half-plane during the limit.
In this case we can chose a specific harmonic majorant
to
$\log\,|f(x)|$. Namely, put
\[
H(z)=\sum_{\nu=0}^{\nu=N}\, c_\nu\cdot H_{J_\nu}(z)
\]
where $\{H_{J_\nu}\}$ are the harmonic measure
functions of the $J$-intervals.
Then we have
\[
\log\,|f(x)|\leq H(x)
\]
for real $x$. 

\noindent
{\bf{Exercise.}}
Show that (*)  entails the global inequality:
\[
\log\,|f(z)|\leq H(z)\quad\colon\quad z\in U
 \]



\newpage

\newpage

\centerline{\bf 5. Harmonic measures}
\bigskip

\noindent
Let $\Omega$ be a bounded connected and  open set where
Dirichlets problem can be solved.
If $z\in\Omega$
we get a linear form on $C^0(\partial\Omega)$ defined by
\[ 
\phi\mapsto H_\phi(z)\tag{1}
\]


\noindent
Thus, we evaluate the unique harmonic extension of
the boundary function $\phi$ at the point $z$.
If $\phi\geq 0$ then $H_\phi(z)\geq 0$ and when
$\phi=1$ is the identity we have $H_\phi=1$.
Riesz' Representation Formula
gives a unique probability measure
on $\partial\Omega$ denoted by $\mathfrak{m}_z$
such that
\[
H_\phi(z)=\int_{\partial\Omega}\,\phi(\zeta)\cdot
d\mathfrak{m}_z(\zeta)\tag{2}
\]


\noindent
When $z$ varies in $\Omega$ these measures are absolutely continuous with
respect to each other.
To see this we fix
some point $p$ in $\Omega$. Let $q$ be another point and suppose that
$\mathfrak{m}\uuu q$ is not absolutely continuous with respect to
$\mathfrak{m}\uuu p$ which gives 
a closed subset $E$ of $\partial\Omega$
where $\mathfrak {m}\uuu p(E)=0$ and $\mathfrak{m}\uuu q(E)=a>0$.
Now we  can  choose a sequence of continuous boundary functions
$\{\phi\uuu n\}$ such that $0\leq\phi\uuu n\leq 1$ while $\phi\uuu n=1$ on $E$ and
\[
\lim\uuu{n\to\infty}\, \int\uuu{\partial\Omega}\phi\uuu n\cdot d\mathfrak{m}\uuu p=0\tag{1}
\]
Here $\{H\uuu n=H\uuu{\phi\uuu n}\}$ is a sequence of harmonic functions
such that $0\leq H\uuu n\leq 1$ holds and $H\uuu n(p)\to 0$.
The minium principle for harmonic functions entails that $H\uuu n\to 0$
holds on uniformly on every compact subset of $\Omega$. In particular
$H\uuu n(q)\to 0$. But this  gives a contradiction since the
$\phi$\vvv functions give $H\uuu n(q)\geq a$ for all $n$.

\medskip

\noindent
{\emph{…ksendal's theorem.}}
If may occur that the boundary
$\partial\omega$ has a positive 2\vvv dimensional Lebesgue measure.
But the harmonic measures are always concentrated to null sets
with respect to the Lebesgue measure in ${\bf{R}}^2$.
Nasmely, one has

\medskip

\noindent
{\bf{5.0 Theorem.}} \emph{There exists a null\vvv set $E$ 
in $\partial\Omega$
such that
$\mathfrak m\uuu p(E)=1$ for every $p\in\Omega$.}
\medskip

\noindent
We prove this result in 5.x below after some
results concerning majorisation principles for harmonic measures have
been established.

\medskip

\noindent
{\emph{The principle of
Gebietserweiterung.}}
The inequality in (*) below is used in many situations.
Let $\Omega$ and $U$ be two domains where the Dirichlet problem is solvable for both.
Suppose that $\Omega\subset U$ and put
\[ 
\partial\Omega=\gamma\cup \gamma
\] 
where $\gamma$ is a compact subset of $\partial U$ while $\Gamma$ is a
subset of $\bar \Omega$.
Consider also a compact subset $K$ of $\partial U$ such that
$\bar\Omega\cap K=\emptyset$.
Let $z$ be a point in $\Omega$ which also may be regarded as a point in $U$.
We get the harmonic measure $\mathfrak{m}\uuu z^U(K)$, i.e.
the value at $z$ of the harmonic function $h$ in $U$ for which
$h=1$ on $K$ while $h=0$ on $\partial U\setminus K$.
At the same time we have the harmonic measure 
$\mathfrak{m}^\Omega\uuu z(\Gamma)$
which equals  $H(z)$ for the harmonic function in
$\Omega$ which is one on $\Gamma$ and zero on
$\gamma\setminus \Gamma$.
Since $0\leq h\leq 1$ holds in $U$
it follows that $h\leq H$ on $\Gamma$
and at the same time both $H$ and $h$ are zero on 
$\gamma\setminus\Gamma$.
Hence $h\leq H$ holds on $\partial\Omega$ so the maximum principle for harmonic functions entails that
\[
\mathfrak{m}\uuu z^U(K)\leq \mathfrak{m}\uuu z(\Gamma)\tag{*}
\]


\noindent
{\bf 5.1. Conformal invariance.}
Let $\Omega$ and $\Omega^*$ be two bounded and  connected
open sets which both are of class $\mathcal D(C^1)$.
Let  $g\colon\,\Omega\to\Omega^*$
be a conformal map which extends to the boundary and gives a
homeomorphism from $\bar\Omega$ to $\bar\Omega^*$.
As explained in XX the $g$-function sends
a harmonic function
$H$ in $\Omega^*$ to the harmonic function
$H\circ g$ in $\Omega$. Let $\Gamma_1,\ldots,\Gamma_p$
be the closed boundary curves to $\Omega$. Their images
$\{g(\Gamma_\nu)\}$ give the boundary curves of $\Omega^*$.
Let $E$ be some Borel set in $\partial\Omega$ which gives the
harmonic measure function
\[
H_E(z)=\int_E\, d\mathfrak{m}_z(\zeta)
\]
Similarly  we get the harmonic measure function
\[
H^*_{g(E)}(w)=
\int_{g(E)}\, d\mathfrak{m}^*_w(\zeta)
\]
where $\mathfrak{m}^*_w$ is the harmonic measure on
$\partial\Omega^*$. Now we have the equality
\[ 
H_E(z)=H^*_{g(E)}\circ g(z)\implies
\]
\[
\int_E\, d\mathfrak{m}_z(\zeta)=
\int_{g(E)}\, d\mathfrak{m}^*_{g(z)}(\zeta)
\quad\text{holds for all points }\quad z\in\Omega\tag{*}
\]
Since $g$ restricts to a homeomorphism from
$\partial\Omega$ into $\partial\Omega^*$
this gives a transformation rule for the harmonic measure.
This invariance 
is often used and we
shall meet such  applications  in the chapter about conformal mappings.
\bigskip



\medskip

\noindent
{\bf{5.2 Harmonic measures in half-discs.}}
Let $R>1$ and consider the half-disc
$D^+_R=D_R\,\cap \{y>0\}$.
which is contained in the upper half-plane
$\mathfrak{Im}(z)>0$. Here
there exists the harmonic function
\[ 
u(z)=\mathfrak{Im}(\text{Log}(z-R))-
\mathfrak{Im}(\text{Log}(z+R))=
\text{arg}(z-R)-\text{arg}(z+R)
\]
As already pointed out in XX we have
\[ 
\lim_{y\to 0}\, u(x+iy)=\pi\quad\colon\quad -R<x<R
\]
Moreover, by euclidian geometry we have
\[
u(Re^{i\theta})=\frac{\pi}{2}\quad
\colon\,0<\theta<\pi
\]
Set
\[ 
u^*(z)=\frac{2}{\pi}\cdot (u(z)-\frac{\pi}{2})\tag{*}
\]
Then $u^*(x)=1$ on the real interval $(-R,R)$ while
$u^*=0$ on the portion of $\partial D_R^+$ where
$|z|=R$.
Hence, if $0<a<R$ then the harmonic measure
of the point $ai$ with respect to
the boundary piece $(-R,R)$ is equal to $u^*(ai)$.

\medskip

\noindent
{\bf{Exercise.}}
Show that
\[ 
u^*(ai)= \frac{2}{\pi}\cdot \text{arctg}(\frac{R}{a})
\]


\noindent
We have also the harmonic measure with respect to the circular boundary
where $|z|=R$ which is given by the function $1-u^*$.
hence, the harmonic measure at $ai$ with respect to this
circular portion is equal to 
\[
1-\frac{2}{\pi}\cdot \text{arctg}(\frac{R}{a})
=\frac{2}{\pi}\cdot \int_{R/a}\, \frac{dt}{1+t^2}
\]
The last term is majorised by
\[
\frac{2}{\pi}\cdot \int_{R/a}\, \frac{dt}{t^2}=
\frac{2a}{\pi R}\tag{*}
\]
In particular this harmonic measure behaves like $O(\frac{1}{R})$ when
$R\to+\infty$ while $a$ stays in a bounded interval.


\bigskip






\centerline{\bf{5.3 Lindelšf's theorem.}}
\medskip


\noindent
Let $D^+$ be a half\vvv disc where $|z|<R$ and $\mathfrak{Im} \,z>0$.
Let $f(z)$ be a bounded analytic
function in $D^+$ with maximum norm $\leq 1$.
Consider also  a Jordan arc
$\gamma$ which belongs to $D^+$ except for the endpoint $\gamma(1)$
which is taken as the origin.
Suppose that $f$ converges to zero along $\gamma$, i.e.
\[
\lim\uuu{s\to 1}\, f(\gamma(s))=0
\]
Then Lindelšf proved that $f$ has a non\vvv tangential limit
at $z=0$. More precisely, for each $0<\alpha<\pi/2$ one has

\[
\lim\uuu {r\to 0}\, [\max\uuu {\alpha\leq \theta\leq \pi\vvv \alpha}\,
|f(re^{i\theta})|\,]=0\tag{*}
\]
\medskip

\noindent
\emph{Proof}. Consider the subharmonic function
$u(z)=\log\,|f(z)|$.
For each large  $M>0$  it follows from
(1) that there exists $s\uuu 0<1$
such that
\[
u(\gamma(s))\leq \vvv M\tag{i}
\] 
for all $s\uuu 0\leq s<1$.
Now we choose  $0<R\uuu *<R$ such that
the smallest $s$ for which $|\gamma(s)|=R\uuu *$
holds is $\geq s\uuu 0$. Denote this $s$\vvv number with
$s\uuu *$
So if $D^+\uuu *$
is the half\vvv disc where $|z|<R\uuu *$
then
\[
u(\gamma(s))\leq \vvv M\tag{ii}
\]
for all $s\uuu *\leq s<1$ and  the
half\vvv open Jordan curve
$\gamma[s\uuu *,1)$ stays in $D\uuu *$.
It follows from Jordan's theorem
that this curve divides $D^+\uuu *$
into a pair of disjoint Jordan domains
$\Omega\uuu 1$ and $\Omega\uuu 2$.
Moreover, as illustrated by a picture
the real intervals $[\vvv R\uuu *,0]$ and
$[0,R\uuu *]$  appear in the boundary of
each $\Omega$\vvv domain. We may assume that
\[
[\vvv R\uuu *,0]\subset\partial  \Omega\uuu 1
\]
In addition $\partial\Omega\uuu 1$
consists of the Jordan arc $\gamma[s\uuu *,1]$
and an arc of the circle $|z|=R\uuu*$
with end\vvv points at $\vvv R\uuu *$ and
$\gamma(s\uuu *)$.
Next, given  $0<\alpha<\pi$
we consider points $z\in\Omega\uuu 1$
such that:
\[ 
z=re^{i\theta}\quad \colon\quad
\alpha\leq \theta\leq \pi\vvv\alpha\quad\text{and}
\quad 0<r<R\uuu */2\tag{iii}
\]


\noindent
For each such point $z$ we have the harmonic measure
$\mathfrak{m}\uuu z$ on $\partial\Omega\uuu 1$.
Since $|f|\leq 1$ was assumed we have $u\leq 0$ 
and since $u$ is  subharmonic we get:
\[
u(z)\leq \vvv M\cdot 
\mathfrak{m}\uuu z(\Omega\uuu 1\cap \gamma)\tag{iv}
\]


\noindent
At this stage
we use
the principle of \emph{Gebietserweiterung}. Consider the
whole half\vvv disc $D^+\uuu *$.
Here $[0,R\uuu *]$Êis the portion of its boundary
and since
the Jordan  arc $\gamma$ separates the half disc where
$[0,R\uuu *]\subset\partial\Omega\uuu 2$
one has the inequality
\[
\mathfrak{m}\uuu z(\Omega\uuu 1\cap \gamma)
\geq \mathfrak {m}^*\uuu z([0,R\uuu *])
\] 



\noindent
where $\mathfrak{m}\uuu z^*$
is the harmonic measure for $z$ in the half disc.
It follows from (iv) that 
\[
u(z)\leq \vvv M\cdot 
\mathfrak{m}\uuu z^*(([0,R\uuu *])/tag{v}
\]
Finally, since $z$ satisfies (1) it follows that
\[
\mathfrak{m}\uuu z^*(([0,R\uuu *])\geq \rho(\alpha)\tag{vi}
\] 
where $\rho(\alpha)$ is a positive number which can
be computed via a conformal mapping. See XX for details.
So when $z$ is as in (iii) we get the estimate
\[
 u(z)\leq \vvv \rho(\alpha)\cdot M
\]
Here $\rho(\alpha)$ depends on the fixed $\alpha$\vvv value only while
$M$ can be arbitrary large while $R\uuu *$ gets small
and this obviously entails that we have the requested limit
(*) in the sector $\alpha\leq \arg(z)\leq \pi\vvv\alpha$.
Finally, we proved that the limit when $z$ stays in
$\Omega\uuu 1$. Reversing the role where one instead
works with the interval $[\vvv R\uuu *,0]$
we get again the  limit in (*) and Lindelšf's theorem is proved.
\medskip

\noindent
{\bf{Remark.}}
The original proof by Lindelšf appears in [Lindelšf].
The idea to employ harmonic measures and estimate  the subharmonic
function $\log\,|f(z)|$ was  introduced by Carleman. See
page xxxx in Nevanlinna's book [Nev] for an account about the principle
for harmonic measures under a change of domains.

\bigskip

\noindent
{\bf{5.4 Application to Laurent series.}}
Let $f(z)$ be analytic in a punctured disc $0<|z|<1$.
If $0<r<1/2$ and $|z|=r$
we find estimates for harmonic measures as follows.
To each $0<\epsilon <r$
we have the annulus $\epsilon <|z|<1/2$
and put
\[
\omega(z)=
 \frac{1}{\log\,\frac{1}{2\epsilon}}\cdot \log \frac{|z|}{\epsilon}
 \]
This yields a harmonic function  and we conclude that
\[ 
\mathfrak{m}\uuu z(T\uuu *)=
 \frac{1}{\log\,\frac{1}{2\epsilon}}\cdot \log \frac{2r}{2\epsilon}=1+
 \frac{\log 2r}{\log\,\frac{1}{2\epsilon}}
\]
where $T\uuu *$ is the circle $|z|=1/2$.
It follows that the harmonic measure with
respect to the inner circle $T\uuu \epsilon=|z|=\epsilon$
becomes
\[ 
\mathfrak{m}\uuu z(T\uuu \epsilon)=
1\vvv \mathfrak{m}\uuu z(T\uuu *)=
 \frac{\log \frac{1}{2r}}{\log\,\frac{1}{2\epsilon}}\tag{1}
\]
Suppose now that $f(z)$ is bounded in the punctured disc with a maximum norm
$M$. At the same time we consider the maximum norm
of $|f|$ on the circle $|z|=1/2$
which we denote by $M\uuu *$.
Since $\log\,|f|$ is subharmonic it follows from
(1) that we have
\[
\log\,|f(z)|\leq \log M\uuu *+
M\cdot  \frac{\log \frac{1}{2r}}{\log\,\frac{1}{2\epsilon}}\tag{2}
\]
This inequality holds for every $|epsilon>0$ and since
$\frac{1}{2\epsilon}\to+\infty$ we conclude that
$\log\,|f(z)|\leq \log M\uuu *$ which entails that
\[
|f(z)|\leq M\uuu *\tag{3}
\]
The point is that (3) does not depend upon $M$. Now we give
an application:
\medskip

\noindent
{\bf{5.5 Theorem.}}
\emph{Let $f$ be an analytic function in the punctured disc
$0<|z|<1$ where $f$ and all is derivatives $\{f^{(n)}\}$ are bounded.
Then $f$ extends
to an analytic function in the disc $|z|<1$.}
\medskip

\noindent
\emph{Proof.}
Let $M$ be the maximum norm of $f$ in $0<|z|<1$.
If $n\geq 1$ then Cauchy's inequality entails that

\[
|f^{(n)}(z)|\leq n\,!\cdot 2^n\cdot M\tag{i}
\] 
for each $|z|=1/2$.
Using (3) applied to the analytic function $f^{(n)}$ it follows that
(i) holds for all $0<|z|<1/2$.
Now we consider the series expansion
at $z=1/4$:

\[ 
f(1/4+z)= \sum\, \frac{f^{(n)}(1/4)}{n\,!}\cdot z^n\tag{ii}
\]
Since (i) hold with $z=1/4$ we see that the series (ii) has a radius of convergence which is 
at least $1/2$ which implies that $f(z)$ extends beyond $z=0$.
\bigskip

\noindent

\centerline {\emph{5.6 Proof of …ksendal's theorem.}}
\bigskip

\noindent
We shall interpretate harmonic measures
via the hitting probability
for a Browninan motion.
To begin with we consider the following situation.
Let $\delta>0$
and  start a Brownian motion a point $p$ with $|p|=\delta$.
Suppose also that there is a closed subset
$\Gamma$ on a circle $|z|=r$ for some $\delta/2\leq r<3\delta/4$
whose linear measure is $(1\vvv \epsilon)\cdot 2\pi r$
for some $0<\epsilon<1$.
This set is viewed as an obstacle and we seek the probability that the
Brownian motion reaches some point on  the circle $|z|=\delta/2$ before it
has hit $\Gamma$ which
means that a Brownian path during passages
through $|z|=r$ must stay in one of the open intervals
on this circle which form the open complement of
$\Gamma$.
With this in mind one has

\medskip

\noindent
{\bf{5.7 Proposition.}} \emph{There exists an absolute constant $C$
which is independent of both $\delta$ and $\epsilon$ such that
the survival probalility
is $\leq C\cdot\epsilon$.}
\medskip


\noindent
The result is 
intuitively clear and for a formal proof we refer to XXX.
There remains to see why Propostion 5.7 gives Theorem 5.0.
To achieve this we study Lebesgue points on the compact set
$\partial\Omega$ where we assume that its 2\vvv dimensional measure is
$>0$ since otherwise Theorem 5.0 is trivial.
With $C$ chosen as above we set
\[
\epsilon=\frac{1}{8C}\tag{1}
\]
For each positive integer $M$
we let $K\uuu M$ be the subset of $\partial\Omega$ such that
if $x\in K\uuu M$ then
\[
0<\delta\leq 2^{\vvv M}\implies
\frac{|\partial\Omega\,\cap B\uuu z(\delta)|\uuu 2}{\pi\delta^2}\geq
1\vvv \epsilon\tag{2}
\]
By Lebegue's Theorem we have
\[ 
\lim\uuu{M\to\infty}\, |\Omega\setminus K\uuu M|\uuu 2=0\tag{3}
\]
Next, fix a point $p\in \Omega$ and consider the 
measure$\mathfrak{m}\uuu p$.
We must show that this Riesz measure is singular and 
from (3) it suffices to show that its restriction to
$K\uuu M$ is singular for all $M$.
Since the sets $\{K\uuu M\}$ increase with $M$ 
it suffices to show this when we start from $M$\vvv values such that
the distance of $p$ to 
$\partial\Omega$ is strictly greater than
$2^{\vvv M}$.
By the general result in MEASURE
the restriction $\mathfrak{m}\uuu p|K\uuu M$
is singular if
\[
\lim\uuu{N\to\infty}\, 
4^N\cdot 
\mathfrak{m}\uuu p(B\uuu z(2^{\vvv N}))=0\tag{5}
\] 
for each $z\uuu *\in K\uuu M$.
To prove (5) we consider integers $N\geq M+1$
and identify
$\mathfrak{m}\uuu p(B\uuu {z\uuu *}(2^{\vvv N}))$ with the 
probability that
a Brownian path starting at $p$ reaches
the circle $|z\vvv z\uuu *|=2^{\vvv N}$
before it has hit $\partial\Omega$.
In order that such a path survives it must
pass the circles $T\uuu k=|z\vvv z\uuu *|= 2^{\vvv k}$
for every $M\leq k\leq N$.
If the path has reached a point $p\in T\uuu k$
the probability that it also reaches $T\uuu{k+1}$
can be estimated above by
Proposition 5.7. 
Namely, for a given $k$
we set

\[
\rho\uuu k=\max\uuu r\frac{1}{2\pi r}\cdot \, \text{Length of}\quad
\partial \Omega\cap T\uuu r|
\]
where the maximum is taken when
$2^{\vvv (k+1)}\leq r\leq
3\cdot 2^{\vvv k}/4$.
It follows that the area:
\[
|\Omega\cap B\uuu{z\uuu *}(2^{\vvv k}|\uuu 2\geq
(1\vvv \rho\uuu k)\pi \cdot 2^{\vvv 2k}\cdot (9/16\vvv 1/4)
\]
On the other hand, since
$z\uuu *\in K\uuu M$ we also have
\[
|\Omega\cap B\uuu{z\uuu *}(2^{\vvv k})|\uuu 2\leq
\epsilon\cdot \pi\cdot 2^{\vvv 2k}
\]
It follows that

\[
1\vvv\rho\uuu k\leq \frac{16}{5}\cdot \epsilon\implies \rho\uuu k\geq
1\vvv \frac{16}{5}\cdot \epsilon
\]
Hence we find a radius $r$ in the interval above
where the length of
$\partial \Omega\cap T\uuu r$ is at least
$(1\vvv \frac{16}{5}\cdot \epsilon)\cdot 2\pi r$.
This set is an obstacle and  Proposition  5.7
together with the general principle in 5.1 imply that
the probability to move from $p$ to a point on $T\uuu{k+1}$
without reaching  $\partial\Omega$
is majorized by
\[ 
C\cdot \frac{16}{5}\cdot \epsilon=\frac{1}{8}
\]
where (1) above gives the last inequality.
At this stage we easily get (5).
For in order to move from a point $p$ on the circle 
$|z\vvv z\uuu *|= 2^{\vvv M}$
to a point on $|z\vvv z\uuu *|= 2^{\vvv N}$
we must survive the passage for each $k$ as above, i.e. we must survive
a passage $N\vvv M\vvv 1$ many times.
By (**) the probability for this survivial is estimated above by
\[
\frac{1}{8^{N\vvv M\vvv 1}}
= 4^{\vvv N}\cdot 8^{M+1}\cdot 2^{\vvv N}
\]
It follows that

\[
4^N\cdot 
\mathfrak{m}\uuu p(B\uuu z(2^{\vvv N}))\leq  8^{M+1}\cdot 2^{\vvv N}
\]
With $M$ fixed the right hand side tends to zero with $N$ and hence (5) follows which finishes the proof of …ksendal's theorem.













\newpage





\centerline{\bf 6. Green's functions.}
\bigskip

\noindent
Let $\Omega$ be a bounded and connected set
of class $\mathcal D(C^1)$.
Let $z_*\in\Omega$ which gives 
the continuous boundary function
\[ 
\zeta\to\text{Log}\,|\zeta-z_*|\tag{1}
\]
In $\Omega$ we get the unique harmonic function
whose boundary function is (1). It depends upon $z_*$ and is denoted by
$H(z_*;z)$ where 
$z$
is the "active variable".
Keeping $z_*$ fixed
the values of $H$ inside $\Omega$ are recaptured by the harmonic measure:

\medskip

\[ 
H(z_*;z)=
\int_{\partial\Omega}\,
\log\,|\zeta-z_*|\, d\mathfrak {m}_z(\zeta)\quad\colon\,z\in\Omega\tag{2}
\]
\medskip

\noindent
Keeping $z$ fixed
the measure $\mathfrak{m}\uuu z$ can be weakly approximated by a sequence of discrete measures of the form $\rho=\sum\, p\uuu k\cdot \delta\uuu{\zeta\uuu k}$
where $\sum\, p\uuu k=1$ and $\{\zeta\uuu k\}$ is a finite subset of
$\partial\Omega$.
Since the functions
\[
 z\uuu *\mapsto \log| z\vvv z\uuu*|
\]
are harmonic in $\Omega$
for each $\zeta\in\partial\Omega$ it follows that
the functions
\[ 
\zeta\uuu *\mapsto H(z\uuu *;z)
\] 
are harmonic for every fixed $z$.
It turns out that one has  symmetry.
\bigskip

\noindent
{\bf 6.1. Theorem.}
\emph{For each pair of points $z_*,z$ in $\Omega$ one has:}
\[ 
H(z_*,z)=H(z,z_*)
\]


\noindent
\emph{Proof.}
By the construction of the $H$\vvv function we have
\[ 
H(z\uuu *,\zeta)=\log|\zeta\vvv z\uuu *|
\quad\colon\quad \zeta\in\partial\Omega\tag{1}
\]
Next,
for  each pair of distinct points
in $\Omega$ we set:
\[ 
G(z_*;z)=H(z_*;z)-\log\,|z-z_*|\quad\colon\, z_*\neq z\tag{2}
\]

\noindent
Then (1) entails that
\[ 
G(z_*;\zeta)=0\quad\colon\,\zeta\in\partial\Omega\tag{3}
\]

\noindent
At the same time
the function of $z$ defined by
\[ 
-G(z;z_*)=
\log\,|z-z_*|-H(z_*;z)
\] 
is subharmonic
in $\Omega$ and tends to $-\infty$ as $z\to z_*$.
By (3) it vanishes on $\partial\Omega$ so by the maximum principle for
subharmonic functions it is $<0$ in $\Omega\setminus z_*$ which means that
\[
G(z_*;z)>0\quad\colon\, z\in\Omega\setminus z_*\tag{4}
\]
\medskip
Next, since  $\log \,|z-z_*|$ is symmetric we have:
\[
G(z_*;z)-G(z;z_*)=H(z_*;z)-H(z;z_*)
\]

\medskip

\noindent
Keeping $z_*$ fixed (3) and (4)  show that the left hand side
is $<0$ when $z\in\partial\Omega$. Hence the maximum principle
for harmonic functions gives
\[
G(z_*;z)-G(z;z_*)\geq 0
\]
Reversing the role the reader finds the opposite inequality and
Theorem 6.1 follows.
\medskip

\noindent
{\bf 6.2 Remark.} The $G$-function is called the Green's function 
attached to the domain $\Omega$.
Theorem 6.1 implies also that Green's function  also enjoys 
symmetry,  i.e. 
\[
G(z_*,;z)= G(z;z_*)\tag{*}
\]
\medskip

\noindent
{\bf 6.3 Harmonic measure and normal derivatives of $G$.}
It turns out that $G$ recaptures harmonic measures.
Keeping $z_*$ fixed we know that
$z\to G(z_*;z)$ is positive in $\Omega$
and tends to zero as $z\to\partial\Omega$.
Now  
we can apply Green's formula starting with
an arbitrary harmonic function $u$ in $\Omega$
which extends to a $C^1$-function on the boundary.
More precisely, for a small $\epsilon>0$
we remove the disc $D\uuu\epsilon=|z\vvv z\uuu *|\leq\epsilon$
and with $\Omega\uuu\epsilon=
\Omega\setminus D\uuu\epsilon$ we apply
Green's formula  to the pair $u$ and $G(z\uuu *,\zeta)$. This gives
the equality
\[
\int_{\partial\Omega\uuu\epsilon}\,
u(\zeta)\cdot \partial G/\partial{\bf{n}}(\zeta)\cdot ds(\zeta)=
\int_{\partial D\uuu\epsilon}\,
G(z\uuu *,\zeta)\cdot \partial u/\partial {\bf{n}}(\zeta)\cdot ds(\zeta)
\]
where we used that $G(z\uuu *,\zeta)=0$
on $\partial\Omega$.
\medskip

\noindent
Notice that we have taken outer normals with respect to the domain
$\Omega\uuu\epsilon$.
A passage to the limit when  $\epsilon\to 0$
gives the equality
 \[ 
 u(z\uuu *)
 =\frac{1}{2\pi}\cdot
 \int_{\partial\Omega}\,
u(\zeta)\cdot \partial G/\partial{\bf{n\uuu *}}\cdot ds(\zeta)\tag{*}
\]
where we have taken the \emph{inner normal} of
$G(z\uuu *,\zeta)$ along $\partial\Omega$.
This choice is natural since $G>0$ in $\Omega$ so that  the inner normal is 
non\vvv negative which means that we obtain
a representation by a
non\vvv negative measure.
Hence we  get the equality
\[
d\mathfrak{m}\uuu{z\uuu *}= 
\partial G/\partial{\bf{n\uuu *}}\cdot ds\tag{**}
\] 
where $ds$ is the arc\vvv length measure on the boundary.






\medskip

\noindent
{\bf 6.5 Example.} Let $\Omega=D$ be the unit disc.
In this case we have:
\[ 
G(z,\zeta)=
\text{Log}\,\frac{|1-z\cdot \bar\zeta|}{|z-\zeta|}
\]
\medskip

\noindent
With $z_*\in D$ kept fixed
and $\zeta=e^{i\theta}$ is on the boundary circle $T$
we see  the inner  normal derivative becomes
\[
\frac{d}{dr}\bigr[(\text{Log}\,\frac{|re^{i\theta}-z_*|}
{|1-re^{-i\theta}\cdot z_*|}\bigl]
\]
where this  derivative is evaluated when $r=1$.
At the same time the arc-length measure is $d\theta$.
The reader may now verify that
the formula in (**)  corresponds to Poisson's formula
for the harmonic extension of the boundary function
$u(e^{i\theta})$.
\bigskip


\noindent
{\bf{6.6 Harmonic measures with respect to arcs.}}
Let $\Omega$  be a domain in the class $\mathcal D(C^1)$
and 
$\gamma$  a simple $C^1$\vvv curve
which appears as a compact subset of $\Omega$.
compact subset of $\Omega$.
The  Dirichlet problem has a solution for the domain
$\Omega\setminus \gamma$.
Let $H$ be harmonic in
$\Omega\setminus\gamma$ with continuous boundary
values.
Along $\gamma$  the outer normal derivative
of $H$ is taken from two sides while we apply Green's formula.
See XXX for a detailed discussion.
If $z\uuu 0\in\Omega\setminus \gamma$
we apply Green's formula to $H(\zeta)$ and $G(z\uuu 0,\zeta)$
while a small disc centered at $z\uuu 0$ is removed.
Since $G=0$ on $\partial\Omega$ we obtain 
\[
\int\uuu{\partial\Omega} H\cdot \partial G(z\uuu 0,\zeta)
/\partial{\bf{n}}\cdot ds+
\int\uuu\gamma  H\cdot \partial G(z\uuu 0,\zeta)/\partial{\bf{n}}\cdot ds
+\int\uuu{\partial D\uuu\epsilon}
H\cdot \partial G(z\uuu 0,\zeta)/\partial{\bf{n}}\cdot ds=
\]
\[
\int\uuu\gamma  G(z\uuu 0,\zeta)\cdot \partial H/\partial{\bf{n}}\cdot ds
+\int\uuu{\partial D\uuu\epsilon}
G(z\uuu 0,\zeta)\cdot \partial H/\partial{\bf{n}}\cdot ds
\]
Passing to the limit as $\epsilon\to 0$ 
we get the equality
\[
\int\uuu{\partial\Omega} H\cdot \partial G(z\uuu 0,\zeta)
/\partial{\bf{n}}\cdot ds+
\int\uuu\gamma  H\cdot \partial G(z\uuu 0,\zeta)/\partial{\bf{n}}\cdot ds
\vvv 2\pi\cdot H(z\uuu 0)
=\int\uuu\gamma  G(z\uuu 0,\zeta)\cdot \partial H/\partial{\bf{n}}\cdot ds
\tag{1}
\]
Now $\zeta\mapsto G(z\uuu 0,\zeta)$
is harmonic in a neighborhood of $\gamma$
and hence quite regular which implies that the outer normal derivatives
along the two sides of $\gamma$ cancel each other so
the second integral above vanishes and there remains
the equality
\[
\int\uuu{\partial\Omega} H\cdot \partial G(z\uuu 0,\zeta)
/\partial{\bf{n}}\cdot ds\vvv 2\pi\cdot H(z\uuu 0)
=\int\uuu\gamma  G(z\uuu 0,\zeta)\cdot \partial H/\partial{\bf{n}}\cdot ds\tag{2}
\]
In particular we can apply (*) when $H=0$ on $\partial\Omega$ and 
identically one on $\gamma$.
This means that $H(z\uuu 0)$ evaluates the harmonic measure at
$z\uuu 0=$ with respect to the compact set $\gamma$
inside the domain $\Omega$.
We set $H(z)= w\uuu\gamma(z)$
where one should consider $\Omega$ as fixed while $\gamma$
is a simple curve situated inside $\Omega$.
Since $w\uuu\gamma =0$ on $\partial\Omega$
we arrive at the formula
\[
w\uuu\gamma(z\uuu 0)=
\frac{1}{2\pi}\cdot  
\int\uuu\gamma  G(z\uuu 0,\zeta)\cdot 
\partial w\uuu\gamma /\partial{\bf{n\uuu *}}\cdot ds\tag{3}
\]
where we use the inner normal of $w\uuu\gamma$.
Denote by $\sigma_\gamma$
the non\vvv negative measure defined by
the density $\frac{1}{2\pi}\cdot
\partial w\uuu\gamma /\partial{\bf{n\uuu *}}\cdot ds$.
So we can write
\[
w\uuu\gamma(z\uuu 0)=
\int\uuu\gamma  G(z\uuu 0,\zeta)\cdot 
d\sigma\uuu\gamma(\zeta)\tag{*}
\]
\medskip

\noindent
{\bf{Remark.}}
Notice that   (*) holds for every point
$z\uuu 0\in\Omega\setminus\gamma$
while the non\vvv negative measure $\sigma\uuu\gamma$ is fixed.
\bigskip

\noindent
\centerline
{\bf{6.7  Beurling's projection theorem.}}
\bigskip

\noindent
The formula (*) in (6.6) has several  applications.
We shall give one  which is due to Beurling.
Let $\Omega$ be the unit disc $D$
and consider an arc $\gamma$ inside $D$ which does not contain the origin.
Keeping $\gamma$ fixed we set $\sigma=\sigma\uuu\gamma$.
Now we have the circular projection
\[ 
z\mapsto |z|\tag{1}
\] 
which sends $\gamma$ onto some interval $[a,b]$
on the positive $x$\vvv axis with $0<a\leq b<1$.
The exceptional equality $a=b$ holds if $\gamma$ happens 
an arc on the circle $|z|=a$.
As illustrated by a figure the map (1) is in general
not bijective.
However, there always exists the push\vvv forward measure 
denoted by $\sigma^*$ which is supported by $[a,b]$ and 
\[
\int\uuu a^b\, \phi(s)\cdot d\sigma^*(s)=
\int\uuu\gamma\, \phi(|\zeta|)\cdot d\sigma(\zeta)\tag{2}
\]
holds for every $\phi\in C^0[a,b]$.
We consider only the case $a<b$
and assume
also 
the measure $\sigma^*$ is absolutely continuous.
\medskip

\noindent
{\bf{Exercise.}}
Show that
$\sigma^*$ is absolutely continuous if
the
arc
$\gamma$ is  real\vvv
analytic.
\medskip

\noindent
Next, 
consider the function
\[ 
V(z)= \int\uuu a^b\, G(z,s)\cdot d\sigma^*(s)\tag{3}
\]
It is clear that $V(z)$ is a harmonic function in
$D\setminus\gamma$ and $V=0$ on
the unit circle $T$. 
Since $z\mapsto g(z,\zeta)$ 
are super\vvv harmonic for every $\zeta$ and $\sigma^*\geq 0$, it
follows that $V(z)$ is super\vvv harmonic in the whole disc $D$.

\medskip

\noindent
{\bf{6.7.1 Proposition.}}
\emph{For each $a\leq s\uuu *\leq b$ one has}
\[
\liminf\uuu{z\to s\uuu *}\,  V(z)\geq 1
\]
\emph{where the $\liminf$ is taken as $z\in D\setminus
[a,b]$ approach $s\uuu *$.}
\medskip

\noindent
\emph{Proof.}
We have $s\uuu *=|z\uuu *|$ for some $z\uuu *\in \gamma$
where $z\uuu *=s\uuu *\cdot e^{i\theta}$
for some $\theta$.
If $\liminf$ is taken along some sequence $\{z\uuu k$
we put $z\uuu k^*= |z\uuu k|\cdot e^{i\theta}$
which implies that $ z\uuu k^*\to z\uuu *$.
Since $w\uuu \gamma=1$ on $\gamma$
it follows that
\[
\lim \,\int\, G(z\uuu k^*,\zeta)\cdot d\sigma(\zeta)=1\tag{i}
\]
Since $\sigma\geq 0$ the inequality for $G$ in (xx)
entails that the integrals above are majorized
by
\[
\int\, G(|z\uuu k^*|,|\zeta|)\cdot d\sigma(\zeta )=
\int\, G(|z\uuu k|,s)\cdot d\sigma^*(s)
\tag{ii}
\]
where the last equality used (2) above
and the equalities $|z^*\uuu k|= z\uuu k|$
At the same time we have
\[
V(z\uuu k)=\int\uuu a^b\, G(z\uuu k,s)\cdot d\sigma^*(s)\tag{iii}
\]
Now
we have the 
limit formulas
\[ 
\lim\, z\uuu k=\lim |z\uuu k|= s\uuu *
\]
We have assumed
that $d\sigma^*(s)$ is an absolutely continuous measure
Moreover, 
it is clear the functions $s\mapsto G(z,s)$ are
$L^1$\vvv functions on $[a,b]$
for every $z\in D$ which in addition
satisfy
\[
\lim \int\uuu a^b\, |G(z,s)\vvv G(z',s)|\cdot d\sigma^*(s)=0
 \] 
 when $|z|\vvv z'|\to  0$. 
 Since $|z\uuu k\vvv |z\uuu k|\to 0$
we have
\[
\lim V(z\uuu k)= \lim V(|z\uuu k|)
\] 
Finally,  the majorization from (ii) and the limit formula
(i) give  Proposition 6.7.1.
\bigskip

\noindent
{\bf{6.7.2 An estimate for harmonic measures.}}
The inequality in Proposition 6.7.1  implies that the
$V$\vvv function majorizes 
the harmonic measure function with respect to the interval $[a,b]$.
Hence we get the inequality
\[ 
w\uuu{[a,b]}(\vvv [z|)\leq V(\vvv |z|)=\int\uuu a^b\, G(\vvv |z|,s)\cdot
d\sigma^*(s)\tag{i}
\]
for each $z\in D$.
By (2) the right hand side is equal to
\[ 
\int\uuu\gamma\, G(\vvv |z|,|\zeta|)\cdot d\sigma(\zeta)\tag{ii}
\]
Now the inequality from (xxx) shows that (ii) is majorized by
\[
\int\uuu\gamma\, G(z,\zeta)\cdot d\sigma(\zeta)=
w\uuu\gamma(z)
\tag{iii}
\]
Hence we arrive at the following
\medskip

\noindent
{\bf{6.7.3 Theorem.}}
\emph{For every $z\in D$ one has the inequality}
\[
w\uuu{[a,b]}(\vvv |z|)\leq w\uuu\gamma(z)
\]
\emph{where $[a,b]$ is the circular projection of $\gamma$.}
\bigskip

\noindent
{\bf{Remark.}}
The result above gives the starting point fora far\vvv reaching
study concerned with estimates of harmonic measures.
We refer to Section 9 in chapter III in [Garnett\vvv Marshall]
for further  results of this nature and mention that [ibid]
also contains several instructive
exercises and  references to
the literature.


























\newpage


\centerline {\bf 7. The Neumann problem.}

\bigskip

\noindent
Let $\Omega$ be a domain in
the class $\mathcal D(C^1)$
bordered by $p$ many closed Jordan curves
$\Gamma_1,\ldots,\Gamma_p$ where
$p\geq 2$.
Given a continuous function
$f$ on $\partial\Omega$
we seek a harmonic function $v$ in
$\Omega$ whose outer normal derivative satisfies
\[
\partial v/\partial{\bf{n}}(p)=f(p)\quad\colon\quad p\in\partial\Omega\tag{*}
\]
Since
\[ 
\int\uuu{\partial\Omega}\partial v/\partial{\bf{n}}\cdot ds=0
\] 
hold for every harmonic function a necessary condition in order that
(*) can  be solved is that
\[ 
\int\uuu{\partial\Omega}\,f\cdot ds=0\tag{**}
\] 



\noindent
We are going to prove that (*) has a unique solution when
$f$ satisfies (**).
Before we enter the proof we
establish a  mean-value inequality
which is due to Schwarz. Namely, 
let $v$ be harmonic in $\Omega$ and suppose it extends to a
$C^1$-function on the boundary. Let
$\gamma$ be an arc of one boundary
curve, say $\Gamma_1$, and suppose that
\[
\partial v/\partial{\bf{n}}(p) =0\,\,\text{for all}\,\,p\in\gamma\tag{i}
\]
If $a$ and $b$ are the two end-points 
of $\gamma$ we can construct
a closed Jordan curve
$J$ where $\gamma$ appears as an arc and 
$J\setminus\gamma$ is a simple Jordan curve contained in
$\Omega$. As explained by a figure we may construct
$J$ so that $a$ and $b$ are two corner points and otherwise $J$ is of class
$C^1$.
With this given one has the following result:
\medskip

\noindent
{\bf 7.1 Schwarz integral formula.}
\emph{Assume that (i) above holds. Then, for every point
$p\in\gamma$ there exists a probability measure $\mu_p$ supported by
$J\setminus\gamma$ such that}
\[
v(p)=\int_{J\setminus\gamma}\, v(z)\cdot d\mu_p(z)
\]
\medskip


\noindent
\emph{Proof.}
Riemann's mapping theorem gives
a conformal map $\phi$ from the Jordan domain bordered by
$J$ onto the upper half-disc $D^+$ where
$|w|<1$ and 
$\mathfrak{Im}(w)>0\}$, 
such that $\phi(\gamma)$ is the real interval
$(-1,1)$ while $\phi(J\setminus\gamma)$
is the half circle.
Then $V=v\circ\phi^{-1}$
is harmonic in
$D^+$ and with the complex coordinate $\zeta=\xi+i\eta$
in $D^+$ we see that
(i) means that
\[
\frac{\partial V}{\partial\eta}(\xi,0)=0\quad\colon\quad -1<\xi<1\,.\tag{ii}
\]
Let $U$ be the harmonic conjugate of $V$ and consider the analytic function
\[ 
F(\zeta)=U+iV
\]
The Cauchy-Riemann equations and (ii) give
$\frac{\partial U}{\partial\xi}(\xi,0)=0$.
Hence $U$ is a constant  on this real interval and since
we can choose this conjugate harmonic function up to a constant we
may assume that $U(\xi,0)=0$.
Hence Schwarz'  reflection principle can be applied, i.e. we find
an analytic function $\hat F(\zeta)$ defined in the unit disc
$|\zeta|<1$ with
\[
\hat F(\zeta)=\bar F(\bar\zeta)\quad\colon\quad \, \mathfrak{Im}(\zeta)<0
\]
If $-1<\xi<1$ we  represent $\hat F(\xi)$ by the Poisson integral over
$|\zeta|=1$ and since $\xi$ is real we get
\[
\hat F(\xi)=
2\cdot\int_0^\pi\, 
P(\xi,e^{i\theta})\cdot F(e^{i\theta})\cdot d\theta
\]
Taking the real part we can write
\[ 
V(\xi)= 2\cdot \int_0^\pi\, 
P(\xi,e^{i\theta})\cdot V(e^{i\theta})\cdot d\theta
\]
Here $2\cdot \int_0^\pi\, P(\xi,e^{i\theta})d\theta=1$. So 
$V(\xi)$ is a convex sum of values of $V$ taken on
the half-circle $\phi(J\setminus\gamma)$.
Returning to the $v$-function   this means that there exists a probability measure
$\mu_\xi$ supported by
$J\setminus\gamma$ such that
\[
v(\phi^{-1}(\xi))=
\int_{J\setminus\gamma}\, v(z)\cdot d\mu_\xi(z)
\]
Since  $\phi^{-1}(\xi))$ corresponds to any preassigned point on
$\gamma$ we have proved Schwarz'  integral formula. 
\medskip


\noindent
{\bf 7.2 A uniqueness result.}
Let $v$ be harmonic in
$\Omega$ and suppose that
\[
\frac{\partial v}{\partial{\bf{n}}}(p)=0\,\,\text{holds for every}
\,\,p\in\partial\Omega
\]
\medskip

\noindent
Then Schwarz'  integral formula  and 
the maximum principle for harmonic function
implies that
$v$ is a constant. In fact, let
$M$ be the maximum of $v$ over
$\partial\Omega$ and choose $p\in\partial\Omega$
where $v(p)=M$.  
If $v$ is not a constant we have seen in XX that
$v(q)<M$ for every
$q\in\Omega$. This strict inequality means that we cannot
obtain a measure $\mu_p$  in the integral formula above.
On the other hand we can find such a non-trivial formula when
$\frac{\partial v}{\partial{\bf{n}}}$ is identically zero on
$\partial\Omega$. Hence  $v$ must be  reduced to a constant.
This proves the uniqueness part for a solution to the equation (*).
Their remains to prove the existence. Before this is done
we establish another result of independent interest.

\bigskip

\noindent
{\bf 7.3 A non-singular matrix for  harmonic measure functions.}
To each boundary $\Gamma_i$
we have the harmonic function $H_i$ in
$\Omega$ with boundary value one on
$\Gamma_i$ while $H_i=0$ on the remaining
boundary curves. Let $\Gamma_p$ be the outer curve
and  consider the functions
$H_1,\ldots,H_{p-1}$. We get the
$(p-1)\times(p-1)$-matrix $A$
with elements
\[ 
a_{j,\nu}=
\int_{\Gamma_\nu}\,
\frac{\partial H_j}{\partial{\bf{n}}}\cdot ds\quad\colon\, 1\leq j,\nu\leq p-1\tag{i}
\]
\medskip

\noindent
{\bf Proposition.} \emph{7.4 The matrix $A$ is non-singular.}
\medskip

\noindent
\emph{Proof.}
 Assume the contrary. This gives some $p-1$-tuple
 $c_1,\ldots,c_{p-1}$ which are not all zero such that
 \[
 c_1\cdot a_{1,\nu}+\ldots+c_{p-1}\cdot a_{p-1,\nu}=0
 \quad\colon\quad 1\leq \nu\leq p-1\tag{ii}
 \]
Set $V=c_1H_1+\ldots+c_{p-1}H_{p-1}$.
 Then (i) and (ii) give
 \[
 \int_{\Gamma_\nu}\,
\frac{\partial V}{\partial{\bf{n}}}\cdot ds=0
\quad\colon\quad 1\leq \nu\leq p-1\tag{iii}
\]
From (xx) it follows that
$V$ has a harmonic conjugate
$U$ and we get the analytic function
$F=U+iV$.
Next, the \emph{tangential} derivative of 
a harmonic measure function $H_j$
is  identically zero on every boundary
curve.
By the Cauchy- Riemann  equations it follows that
the normal derivative of $U$ is identically zero on
every boundary curve and then the
uniqueness result in 7,2 above implies
that 
$U$ is a constant. But then $V$ would also be reduced
to a constant which obviously cannot occur when
some $c_k\neq 0$.
Hence the $A$-matrix is non-singular.


\bigskip


\noindent{{\bf{7.5 A consequence.}}
Now we consider the whole $p$-tuple $H_1,\ldots,H_p$
and the $p\times p$-matrix $B$ with elements

\[ 
b_{j\nu}=
\int_{\Gamma_\nu}\,
\frac{\partial H_j}{\partial{\bf{n}}}\cdot ds\quad\colon\, 1\leq j,\nu\leq p\tag{i}
\]
By xx we have $b_{1\nu}+\ldots+b_{n\nu }=0$ for every $\nu$
and therefore the $B$-matrix must be singular,
From Proposition xx its rank is $p-1$. More precisely, the
column vectors when $1\leq \nu\leq p-1$ are linearly independent.
Hence we can find complex numbers
$\rho_1,\ldots,\rho_{p-1}$ such that

\[
\int_{\Gamma_\nu}\,
\frac{\partial H_p}{\partial{\bf{n}}}\cdot ds=
\sum_{j=1}^{p-1}\,\rho_j\cdot 
\int_{\Gamma_\nu}\,
\frac{\partial H_j}{\partial{\bf{n}}}\cdot ds
\quad\colon\, 1\leq  \nu\leq p\tag{ii}
\]
\medskip






\centerline {\bf 7.6 Solution to the Neuman problem.}
\medskip



\noindent
Since the equation (*) is linear it suffices by additivity to show that
it has a solution when the function $f$ is identically zero on
$(p-1)$ many boundary curves and $\neq 0$ on one of them.
Consider the case when
$f=0$ on the inner curves. Notice that (**) entails that

\[
\int_{\gamma_p}\, f\cdot ds=0\tag{1}
\]
where $ds$ is the arc-length measure along $\gamma_p$.
Fix a point $z_*$ on $\gamma_p$ 
and we move in the positive direction of this oriented curve
to construct a primitive function with respect to $s$, i.e. we 
obtain a continuous function $F$ on $\gamma_p$ such that
$F(z_*)=0$ and its  derivative with respect to
$s$ is equal to $f$ on $\gamma\uuu p$.
.Next, we solve the Dirichlet problem 
and find $G$ where
$\Delta(G)=0$ in $\Omega$ while $G=F$ on $\gamma_p$ and $G=0$ 
on the inner boundary
curves.
By 7.4 we can find constants $a_1,\ldots,a_{p-1}$ such that the function
$g=G-(a_1H_1+\ldots+a_{p-1}H_{p-1})$ has a harmonic conjugate
which we denote by $v$.
Since $H_1,\ldots,H_{p-1}$  are constant functions on the boundary curves, 
the tangential $g$-derivative is equal to that of $G$ along each
boundary
curve. From the construction of $G$ this means that
the tangential $g$-derivatives are zero on all inner curves and
equal to $f$ on the outer curve.
Finally, if $v$ is the conjugate harmonic  function to $g$
it follows that
$v$ is a solution to (*).













\newpage

\centerline{\bf 8. An example from Hydro mechanics.}
\bigskip

\noindent
{\bf Introduction.}
Consider a stationary
motion of an ideal  fluid in the plane which
means that 
the velocity vector $(u,v)$ at each point
$(x,y)$ is independent of the time.
We   also 
assume that the fluid is  incompressible
which means that whenever
$\Omega $ is some domain, then
\[
\int_{\partial \Omega}\, (u\cdot {\bf{n}}_x+
v\cdot {\bf{n}}_y\bigr)\cdot ds=0
\]
Stokes theorem implies  that the area integral
\[
\iint_\Omega\, (u_x+v_y)\cdot dxdy=0
\]
Since this holds for every small domain  the
velocity vector satisfies the equation
\[
u_x+v_y=0\tag{*}
\]
This is the continuity equation for an incompressible fluid.
Next, one defines the
\emph{rotation}  by
\[
\rho=\frac{1}{2}(v_x-u_y)\tag{i}
\]
Assume that (*) holds in the whole plane which gives
a function
$\psi$ such that
\[
\frac{\partial\psi}{\partial x}=-v\quad \,\,\text{and}\,\,\quad  
\frac{\partial\psi}{\partial y}=u\,.\tag{ii}
\]

\noindent
From (i-ii) we get
\[
\Delta(\psi)+2\rho=0\tag{iii}
\]

\noindent
{\bf{An example.}}
Consider  the case when
\[
\lim_{x^2+y^2\to+\infty}\,
(u,v)=(0,0)
\]
and there exists a bounded
Jordan domain
$\Omega$ such that
\[
\rho(x,y)=A=\text{a constant when }\,\,\,\, (x,y)\in\Omega
\quad\text{and}\,\, \rho=0\,\,\text{in}\,\,{\bf{C}}\setminus\Omega
\]

\noindent
Then the $\psi$-function satisfies:
\[ \Delta(\psi)=0\,\,\text{outside}\,\,\Omega\quad\text{and}\quad
\Delta(\psi)(x,y)=-2A\,\,\colon\,\,(x,y)\in\Omega\tag{1}
\]
\[ 
\lim_{x^2+y^2\to\infty}\,
\bigr[\bigl(\frac{\partial\psi}{\partial x}\bigr)^2+
\bigl(\frac{\partial\psi}{\partial y}\bigr)^2\bigr]=0\tag{2}
\]


\noindent
The Riesz representation formula for subharmonic functions gives:

\medskip


\noindent
{\bf 8.1 Proposition.} \emph{The $\psi$-function is given by}

\[
\psi(x,y)=\frac{A}{\pi}\iint_\Omega\,
\text{log}\,\frac{1}{|z-\zeta|}\cdot dxdy+C
\]
\emph{where $C$ is some constant.}

\medskip

\noindent
Above we found a formula for the $\psi$-function. It turns out
{the domain $\Omega$ cannot be arbitrary. Namely, one has:
\medskip

\noindent
\bf 8.2 Theorem}. \emph{Under the assumptions above 
$\Omega$ is a disc.}
\medskip


\noindent
\emph{Proof.}
Since the motion is stationary
it follows from
the general physical principle
by Helmholtz that the boundary
curve
$\partial\Omega$
must be a streamline. By (ii) above this means that
the $\psi$-function is a constant $C_0$ on $\partial\Omega$, i.e. we have
\[ 
\frac{A}{\pi}\iint_\Omega\,
\text{log}\,\frac{1}{|z-\zeta|}\cdot d\xi d\eta=C_0\quad\text{for all}\,\, z\in
\partial\Omega\tag{**}
\]


\noindent
But then the  general result below
shows that
$\Omega$ is a disc. 


\newpage

\noindent
{\bf 8.3 An isoperimetric result.} Let $f(r)$ be a positive function defined on
$r>0$ which is strictly decreasing.
Next, 
for 
an arbitrary   Jordan domain $\Omega$ with a $C^1$-boundary
we define the function
\[ 
F_\Omega(z)=
\iint_\Omega\, f(|z-\zeta|)\cdot d\xi d\eta\tag{*}
\]
With these notations Theorem 8.2  is a special case of
the result below applied to the special function
\[
f(r)=\text{Log}\,\frac{1}{r}
\]
\medskip

\noindent
{\bf 8.5 Theorem.}
\emph{If $\Omega$ is a Jordan domain such that
$F_\Omega(z)$ is a constant function on
$\partial\Omega$ then
$\Omega$ is a disc.}
\medskip

\noindent
{\bf Remark.} 
We refer to
XXX for the proof of this isoperimetric result.
Notice that 
we can express Theorem 8.2 in physical terms as follows:
\medskip

\noindent
{\bf 8.6 Theorem.} \emph{Every stationary motion 
of an incompressible fluid
with constant rotational
density and a simply connected
(Querschnitt) is circular.}
\medskip


\newpage


\centerline{\bf{9. A differential inequality}}
\bigskip


\noindent
In this section we  expose a result from Carleman's  article
\emph{Sur les fonctions inverses des fonctions entires d'ordre fini}
which was published in 1920
and gave   the first example  how the principle of harmonic
majorisation can be applied in a  fruitful manner.
Here is the situation: A connected domain $\Omega$ is given. It is contained
in $\mathfrak{Re}(z)>0$ and for every $\xi>0$ we assume that the
set
\[ 
\ell(\xi)=\{ y\quad\colon\, (\xi,y)\in \Omega\}\tag{1}
\] 
is bounded. Hence $\ell(\xi)$
is some union of open intervals. We  assume that
that $\ell(\xi)\neq\emptyset$ for all $\xi$ and
the sum of the lengths of the intervals 
yields a positive function
$h(\xi)$.
Next, let $f(z)$ be an analytic function in $\Omega$ with maximum norm
$|f(z)|\uuu\Omega \leq 1$.
For every $\xi>0$ we set
\[ 
M(\xi)=\max_{z\in\ell(\xi)}\, |f(z)|\tag{2}
\]
We shall assume that $M(\xi)$ tends to $+\infty$ as $\xi$ increases.
In particular there exists some $\xi_*$ such that $M(\xi_*)>1$.
The maximum principle  $f$ shows that 
$\xi\mapsto M(\xi)$
is non-decreasing when $\xi\geq \xi_*$.
\medskip

\noindent
{\bf{9.1 Theorem.}} \emph{One has the inequality}
\[
\log \,M(\xi)\geq
 \log \,M(\xi_*)\cdot \text{exp}
 \bigl[ \frac{4}{\pi}\int_{\xi_*}^\xi\, \frac{dt}{h(t)}\bigr]\quad\text{for all}\quad
 \xi>\xi_*
 \]


\noindent
\emph{Proof.}
Let $\xi>\xi_*$ and choose  $p\in\ell(\xi)$ where
$M(\xi)=|f(p)|$ and
put
\[ 
U(x+iy)=\log\, |f(x+iy)|\tag{i}
\]
Choose some  $\xi^*>\xi$ and let
$D$  be the connected subdomain  of 
the set
\[
\Omega\cap\{0<\mathfrak{Re}\, z<\xi^*\}
\]
which
contains  $p$. In $D$ we 
have the Green's function $G$ with a
pole at $p$ while $G(z)$ is harmonic in
$D\setminus\{p\}$ and  zero on
$\partial D$. Next, in  $\partial D$ we have the portion
\[ 
L(\xi_*)=\partial D\cap \ell(\xi_*)
\]
\medskip

\noindent With these notations we apply
the general formula in XX to $G$ and
$U$ which by
¤ XX gives the  inequality

\[ 
2\pi\cdot  U(p)\leq
\int_{L(\xi_*)}\,
U\cdot \frac{\partial G}{\partial{\bf{n}}}\cdot ds\leq
\log\, M(\xi_*)\cdot 
\int_{L(\xi_*)}\,
\frac{\partial G}{\partial{\bf{n}}}\cdot ds\tag{*}
\] 
where we have used that $U\leq 0$ on
$\partial D\setminus L(\xi)$.
Now we use the principle of harmonic majorisation 
from ¤ XX. Namely,  consider the half-plane $\mathfrak{Re}\, z<\xi_*$
and let $G^*$ be the Green's function for this half-plane with a pole at
$p$. The majorisation principle from ¤ XX gives:
\[
 \frac{\partial G}{\partial{\bf{n}}}\leq
  \frac{\partial G^*}{\partial{\bf{n}}}\quad\text{on}\quad L(\xi_*)
  \] 


\noindent 
Next, with $p=(\xi,y_0)$
the explicit formula for $G^*$ gives
 \[
 \int_{L(\xi_*)}\,
\frac{\partial G^*}{\partial{\bf{n}}}\cdot ds=
\int_{L(\xi_*)}\, 
\frac{\xi_*-\xi}{
(\xi_*-\xi)^2+(y-y_0)^2}\cdot dy\tag{1}
\]
Now (1) is $\leq$ than the integral taken over
$\ell(\xi_*)$  and since $h(\xi_*)$
is the sum of the lengths of these intervals
it is clear that
(1) is majorised by
\[
\frac{2}{\pi}\cdot \text{arctg}\, \frac{h(\xi_*)}{2(\xi_*-\xi)}\tag{2}
\]
Hence we have proved the inequality
\[
 \log\, M(\xi)\leq
\frac{2}{\pi}\cdot \text{arctg}\, \frac{h(\xi_*)}{2(\xi_*-\xi)}
\cdot  \log\, M(\xi)\quad\text{for all}\quad \xi>\xi_*
\tag{3}
\]
Apply
(3) when $\xi=\xi_*+\delta$ and $\delta\to 0$ which gives:
\[
\frac{2}{\pi}\cdot \text{arctg}\, \frac{h(\xi_*)}{2\delta}=
1-\frac{4\delta}{\pi\cdot h(\xi)}+O(\delta^2)
\]
Passing to the limit as $\delta\to 0$ we get the differential inequality
\[
\frac{d}{d\xi}\,\bigr[ \log\, M(\xi)\bigl]\geq
\frac{4}{\pi\cdot h(\xi)}
\]
Finally  an integration gives the inequality in Theorem 9.1.


\newpage


\centerline{\bf{10. On harmonic measure functions.}}

\bigskip

\noindent
We  expose  material from [¤ 5: Chapter 1]
in Nevanlinna's text-book
[Nev].
Let $\Omega$ be a domain in $\mathcal D(C^1)$ with
boundary curves $\Gamma_1,\ldots,\Gamma_p$ where $\Gamma_p$ is taken as the outer
boundary curve.
On each $\Gamma_\nu$
we consider a function $\phi_\nu$
which takes the value +1 on a finite
union of intervals and  zero on the complementary intervals.
So unless $\phi$ happens to be constant on a single
curve  $\Gamma_\nu$
we get jumps 
at common boundary points of  intervals where $\phi_\nu$ is constant.
The number of such points is  an even integer denoted by $2\cdot k_\nu$
where
$k_\nu=0$ means that
$\phi_\nu$ is identically 1 or 0 on $\Gamma_\nu$.
Solving  Dirichlet's problem we get a harmonic function $\omega(z)$
whose boundary function is  $\phi$. At jump points
the boundary value is discontinuous. But in any case $\omega$ is defined
in $\Omega$  where it takes values in the open interval $(0,1)$ when we assume that
the range of the $\phi$-function contains both 1 and 0.
In fact, the strict inequality

\[ 
0<\omega(z)<1\quad\colon\,z\in \Omega
\]
follows from the maximum principle for harmonic functions.
For every  $0<\lambda<1$  the level curve
$\{\omega=\lambda\}$ is denoted by $S(\lambda)$.
Since $\partial\Omega$ is of class $C^1$ it follows 
that $S(\lambda)$ contains all jump points, i.e. if $z_*\in\Gamma_\nu$
is a jump point for some
$\nu$ then
$S(\lambda)$ contains an arc which has $z_*$ as end-point.
This is proved
using
a locally defined conformal mapping and
a straighforward local  analysis which takes place when
$\Omega$ is an open half-disc
bordered by a real segment $-r\leq x\leq r$ and the upper half-circle
$|z|=r$ where $y\geq 0$. When $\phi(x)=0$ for $-r<x< 0$
and $\phi(x)=1$ when $0<x<r$
we describe the level curves
$S(\lambda)$ in XX  below which proves
the claim above.
\medskip

\noindent
Let us introduce
the critical points for
the $\omega$-function defined by:
\[
\mathcal C_\omega=\{ z=x+iy\quad\colon \,\nabla(\omega)(x,y)=0\}
\]
where $\nabla(\omega)=(\omega_x,\omega_y)$ is the gradient vector.
Consider the analytic function
\[ 
g(z)= \omega_x-i\cdot \omega_y
\]
Then $\mathcal C\uuu \Omega$ is equal to the zeros of 
$g$ 
in
$\Omega$. 


\medskip

\noindent
{\bf{10.1 Theorem.}} \emph{The number of zeros of $g$ counted
with multiplicities is equal to}
\[
k_1+\ldots+k_p+p-2
\]
\medskip

\noindent
{\bf{10.1 Examples.}}
Consider the 
when $\Omega$ is the unit disc $D$ so that $p=1$.
So here $T=\Gamma_1$
is the sole boundar curve.
Let $k_1=1$ which means that 
$\phi=1$ on some interval $(\theta_0,\theta_1)$ and 0 on the complementary interval.
Theorem 10.1  asserts  that 
$g$ has no zeros and hence each
curve
$S(\lambda)$ is smooth. In fact, as shown by a figure $S(\lambda)$ will
be a simple  curve with end-points at 
$^{i\theta_0}$ and
 $e^{i\theta_1}$.
Next, consider the case $k_1=2$ which  means that
$\phi$ is 1 on two disjoint intervals. Suppose they
are
$\{-a<\theta<a\}$ and $\pi-b<\theta<\pi+b\}$ for some  pair 
$0<a,b<\pi/2$.
In this case there exists a unique $0<\lambda_*<1$ where the level curve
$S(\lambda_*)$
fails to be smooth.
For symmetric reason the branch point of $S(\lambda_*)$ 
belongs to  the real axis, i.e. at a point
$-1<x_*<1$  where  two pieces of $S(\lambda_*)$ intersect at a right angle 
by the general result about level curves for harmonic functions in XX.
As explained in the introduction to these notes
we have
\[ 
g(z)=
\frac{1}{e^{ia}-z}+ 
\frac{1}{e^{i\pi+b}-z}-
\frac{1}{e^{-ia}-z}-
\frac{1}{e^{i\pi-b}-z}
\]
With $B(z)=(e^{ia}-z)(e^{-ia}-z)(e^{ib}-z)(e^{-ib}-z)$
 a computation shows that
the rational function $g(z)$ is of the form
\[
g(z)= \frac{A(z)}{B(z)}
\]
whereÊ$A(z)$ is a polynomial of second degree.
Nevanlinna's result is confirmed if one employs a computer
to
find the two zeros of $a$, where one is in $D$ and the other 
belongs to the exterior disc.
\medskip

\noindent{\bf{More involved cases.}}
Keeping $\Omega=D$
while $k_1$ increases
more involved computations occur.
A computer is needed for plots while Nevanlinna's theorem  
indicates
what will occur during such  numerical investigations.

\medskip

\noindent
{\bf{The case $p=2$.}}
Let $\Omega$ be an annulus $\{1<|z|<R\}$ for some $R>1$.
Let
$\phi=0$ on $\{|z|=1\}$,
and on the outer circle we take some interval $-a<\theta<a$ where
$\phi(Re^{i\theta})=+1$ while $\phi=0$ on the remaining part of
$\{|z|=R\}$.
Here $k_1=1$ and $p=2$ so $g$ has one simple zero
which corresponds to a unique $\lambda_*$ where $S(\lambda_*$ fails to 
be smooth.
The reader is again invited to use a computer and to determine the zero of $g$ and plot
the critical level curve $S(\lambda_*)$.

\bigskip

\centerline{\bf{Proof of Theorem 10.1}}
\medskip

\noindent
Along the outer Jordan curve $\Gamma_p$ we let
$s\mapsto z(s)$ be the parametrization with respect  to the arc-length.
The function
\[ 
s\mapsto \omega(z(s))
\] 
is constant
on each of the intervals between eventual jumps.
If $J$ is such an interval we have
\[ 
0=\frac{d \omega(z(s))}{ds}=
\omega_x((z(s))\cdot \frac{dx}{ds}+
\omega_y((z(s))\cdot \frac{dy}{ds}
\]
With $\dot z(s)=\frac{dx}{ds}+i\cdot \frac{dy}{ds}$
this means that
\[
\mathfrak{Re}\bigl(\omega_x-i\omega_y)\cdot \dot z(s)\bigr)=0
\]
This entails that the argument function
\[ 
s\mapsto \arg g(z(s))+\arg z(s)
\]
is constant on the interval $J$.
So after integration over $J$ we have the equality
for the variation of the arguments
\[ 
\int_J\, \arg g\cdot ds=\int_J\, \arg z\cdot ds\tag{i}
\]
If $k_p=0$
it follows that
\[ 
\int_{\Gamma_p}\,  \arg g\cdot ds
-\int_{\Gamma_p}\,  \arg z\cdot ds=-2\pi
\] 
where the last equality follows since
$\Gamma_p$ is the outer Jordan curve.
If $k_p=m \geq 1$ we consider
the $m$ many intervals 
between jumps. Let $p_\nu$ and
$q_\nu$ be the end-points of the $\nu$:th interval.
With a small $\epsilon>0$
one constructs circular arcs
of radius $\epsilon$ centered at
the $2m$ many jumps as illustrated with Figure XX.
Denote these by $\mathcal  C(P_\nu)$ and $\mathcal C(q_\nu)$.
With $\epsilon$ small we apply (i) to the $J$-intervals and get
\[
\int_{\Gamma_p}\,  \arg g\cdot ds\simeq -2\pi+
\sum_{\nu=1}^{\nu=m}\, 
\int_{\mathcal C(p_\nu)}\,  \arg g\cdot ds+
\sum_{\nu=1}^{\nu=m}\,\int_{\mathcal C(q_\nu)}\,  \arg g\cdot ds\tag{1}
\]
\medskip

\noindent
If $p\geq 2$ a similar reasoning applies to
each inner curve. Here
one has
\[
\int_{\Gamma_j}\,  \arg z\cdot ds=-2\pi\quad\colon\, j=1,\ldots(p-1)
\]
This entails that if $1\leq k\leq p-1$ then
\[
\int_{\Gamma_j}\,  \arg g\cdot ds\simeq 2\pi+
\sum_{\nu=1}^{\nu=k_j}\, 
\int_{\mathcal C(p^j_\nu)}\,  \arg g\cdot ds+
\sum_{\nu=1}^{\nu=k_j}\,\int_{\mathcal C(q^j_\nu)}\,  \arg g\cdot ds\tag{2}
\]
where $\{p_\nu^j,q_\nu^j\}$ are thr jump points when
$k_j\geq 1$.
\medskip


\noindent
Next, by the argument principle the number of zeros of $g$
counted with multiplicities in $\Omega$ is equal to
\[
\frac{1}{2\pi}\cdot \sum_{j=1}^{j=p}\, \int_{\Gamma_j}\,  \arg g\cdot ds\tag{3}
\]
\medskip

\noindent
Adding (1) and (2)
we conclude  that Theorem 10.1 follows if the following
limit  formula holds at every jump point $\xi$
which belong to one of thr bordering curves whether it
is
the outer curve
$\Gamma_p$ or an inner curve:
\[
\lim_{\epsilon\to 0}\,\int_{\mathcal C(\xi)}\,  \arg g\cdot ds=\pi\tag{*}
\]
\bigskip

\centerline{\bf{Proof of (*)}}
\bigskip


\noindent
By local conformal mappings
of small arcs centered at $\xi$ on
the $\Gamma$-curve which contains this jump point
the reader may verify that
the proof of (*) boils dow to the
study the infinitemal variation of arguments when
we take the upper half-plane $\mathfrak{Im}\, z>0$
and consider the harmonic function $\omega(z)$ which
takes the value +1 on the negative  real $x$-axis and zero on
$x\geq 0$, or vice versa.
In the case when $\omega(x)=1$ for $x<0$
while $\omega(x)=0$ when
$x>0$ we have
\[ 
\omega(x)=\frac{1}{\pi i}\cdot \mathfrak{Im}\, \log z
\]
It follows that
\[
g(z)=\frac{1}{\pi i}\cdot \frac{1}{z}
\]
Now  $z$ moves on the half-circle of radius $\epsilon$
from $-\epsilon$ to $\epsilon$. Here
\[ g(-\epsilon)=-\frac{1}{\pi i\cdot \epsilon}\implies
\arg\, g(-\epsilon)=\frac{\pi}{2}
\]
When $z=\epsilon\cdot i$
we see that
\[ 
g(\epsilon\cdot i)=-\frac{1}{\pi\epsilon}\implies
\arg g(\epsilon\cdot i)=\pi
\]
Finally the reader can check that
\[
\arg g(\epsilon)=\frac{3\pi}{2}
\]
So the function
\[
\theta\mapsto \arg\, g(\epsilon\cdot e^{i\theta})
\]
increases from $\frac{\pi}{2}$ to $\frac{3\pi}{2}$
and hence the jump of the argument is $\pi$.
Let us  instead consider the function
\[ 
g_*(z)=-\frac{1}{\pi i}\cdot \frac{1}{z}
\]
Ths time the reader can verify that
the functon
\[
\theta\mapsto \arg\, g_*(\epsilon\cdot e^{i\theta})
\] 
increases from $-\frac{\pi}{2}$ to $\frac{pi}{2}$
so again the argument increases by $\pi$.
This gives (*) and Nevanlinna's theorem is proved.



\newpage

\centerline{\bf{11. Some estimates
for harmonic functions.}}

\bigskip


\noindent
Let $u$ be harmonic in the unit disc $D$ and 
suppose that 
\[ 
\iint\uuu D\,  \sqrt{|u(x,y)|}\cdot dxdy=1\tag{*}
\]
We seek   estimates of the maximum modulus function
\[ 
M(r)=\max\uuu \theta\, |u(r,\theta)|
\]
where $re^{i\theta}= x+iy$ are 
the polar coordinates. Put

\[ 
I(r)=\frac{1}{2\pi} \int\uuu 0^{2\pi}\,  \sqrt{|u(r,\theta)|}\cdot d\theta
\]
If $0<r<1$ we represent values of $u$ on $|z|= r^2$
by a Poisson integral over $|z|=r$
and find that

\[ 
M(r^2)\leq\frac{1+r}{1\vvv r}\cdot \frac{1}{2\pi}\int
\int\uuu 0^{2\pi}\,|u(r,\theta)|\cdot d\theta
\]
The right hand side is estimated above by
$\frac{2}{1\vvv r}\cdot \sqrt{M(r)}\cdot I(r)$ which gives  the inequality
\[
M(r^2)\leq \frac{2}{1\vvv r}\cdot \sqrt{M(r)}\cdot I(r)\implies
\] 
\[
\log\, M(r^2)\leq 
\log\, \frac{2}{1\vvv r}+
\frac{1}{2}\cdot \log M(r)+\log  I(r)\tag{i}
\]
Put
\[
\mathcal M(A)=  \int\uuu A^1\, \log\, M(s)\cdot \frac{ds}{s}
\]
The substitution $s=r^2$ gives
\[
\mathcal M(A)= 2\cdot \int\uuu {\sqrt{A}}^1\, \log\, M(r^2)\cdot \frac{dr}{r}
\]
Using (i) we obtain
\[ 
\mathcal M(A)\leq 
2\cdot \int\uuu {\sqrt{A}}^1\, \log\,\frac{2}{1\vvv r}\cdot\frac{dr}{r}
+\int\uuu {\sqrt{A)}}^1\,\log M(r)\cdot dr+
2\cdot \int\uuu {\sqrt{A}}^1\log I(r)\cdot \frac{dr}{r}\tag{ii}
\]
Put
\[
C(A)=2\cdot \int\uuu {\sqrt{A}}^1\, \log\,\frac{2}{1\vvv r}\cdot\frac{dr}{r}
\]
Then (ii) gives
\[
\int\uuu A^{\sqrt{A}}\, \log\, M(s)\cdot \frac{ds}{s}
\leq C(A)+
2\cdot \int\uuu {\sqrt{A}}^1\log I(r)\cdot \frac{dr}{r}
\]
Since $M(r)$ is increasing
the left hand side majorizes
\[
\log M(A)\cdot 
\int\uuu A^{\sqrt{A}}\,\frac{ds}{s}=
\log M(A)\cdot \frac{1}{2}\cdot
\log\,\frac{1}{A}
\]
So for each $1/2\leq A<1$ we have
\[
\log M(A)\cdot \frac{1}{2}\cdot
\log\,\frac{1}{A}\leq C(A)+
2\cdot \int\uuu {\sqrt{A}}^1\log I(r)\cdot \frac{dr}{r}\tag{iii}
\]

\medskip

\noindent
{\bf{The case $A\geq 1/2$}}.
Then
$r\geq \sqrt{A}\geq \sqrt{1/2}$ during the integration and 
the last integral in (iii) is estimated by
\[
2\sqrt{2}\cdot \int\uuu {\sqrt{A}}^1\log I(r)\cdot dr
\]
Let us also write
$\sqrt{A}=1\vvv s$ 
where we will study the situation as $s\to 0$.

\medskip

\noindent
{\bf{Exercise.}}
Show that there exists an absolute constant such that
when $A\geq 1/2$
then
\[ 
C(A)\leq C\cdot s
\]
Use also that
\[
s\mapsto \log\,\frac{1}{(1\vvv s)^2}
\] 
starts a Taylor expansion with $2s$ and conclude that
there is an absolute constant $C$ such that
\[
\log M((1\vvv s)^2)\leq 
C\bigl[1+ s^{\vvv 1}\cdot \int\uuu{1\vvv s}^1\,
\log I(r)\cdot dr\,\bigr]\tag{*}
\]






\noindent
Next, since the Log\vvv function is concave
we get the inequality
\[
\frac{1}{s}\cdot  \int\uuu {1\vvv s}^1\log I(r)\cdot dr\leq
\log\,\bigr[\,
\frac{1}{s}
 \int\uuu {1\vvv s}^1\,I(r)\cdot dr\,\bigr ]
\]
and  the normalisation (*) gives
\[ 
1=2\pi\cdot \iint\uuu 0^1\, I(r)\cdot rdr
\]
It follows that the integrals
\[
\Phi(s)= \int\uuu {1\vvv s}^1\,I(r)\cdot dr
\]
converge to zero as $s\to 0$ and with
$r=1\vvv s$
we  obtain
\[
\log M(r^2)\leq C[1+\frac{\Phi(1\vvv r)}{1\vvv r}]\tag{**}
\]
This estimate is probably not very sharp so
we are led to the following:

\medskip

\noindent
{\bf{11.1 Question.}}
What kind of upper bounds can hold for  $M(r)$ as $r\to 1$.


\bigskip

\noindent
{\bf{11.2 Interior estimates.}}
Ignoring the eventual growth of $M(r)$ as $r\to 1$
we  fix $r=1/2$ and get the inequality
\[ 
M(1/4)\leq C[1+2\Phi(1/2)]\tag{1}
\]
for an absolute constant $C$.
Moreover, the normalisation
\[
1=2\pi\cdot \int\uuu 0^1\, I(r)\cdot r\cdot dr\implies
\]
\[
\Phi(1/2)\leq 2\cdot \int\uuu{1/2}^1\, 
I(r) \cdot rdr\leq \frac{1}{\pi}
\]
Hence (1) gives another  absolute constant $C^*$ such that
\[ 
M(1/2)\leq C^*
\]
In particular we can estimate $u(0)$ and the discussion  above leads to

\medskip

\noindent
{\bf{11.3 Theorem.}}
\emph{In the family of harmonic functions $u$ where (*) holds
there is an absolute constant $C$ such that}
\[ 
|u(0)|\leq C
\]
 
 \newpage
 
 
 \centerline{\bf{12. A density result for harmonic functions.}}
  \bigskip
 
 
\noindent
Consider the interval $[\vvv a,a]$ on the real $x$\vvv line
for some $0<a<1$ which in general is small.
Let  $H(x,y)$ be harmonic in $D$  and
$H^*$ is the harmonic conjugate which gives  the analytic function
$f=h+iH^*$ whose complex derivative becomes
$f'=H\uuu x\vvv iH\uuu y$.
If both $H$ and the partial derivative $H\uuu y$
are identically zero on $[\vvv a,a]$
it follows that $f'=0$ on this interval. So by analyticity $f$ is a constant and 
it follows that
$H=0$ in $D$.
Hence, the pair of restricted functions
$H$ and $H\uuu y$ to $[\vvv a,a]$ determine $H$ in $D$.
We  use this to establish some   density theorems.
To each $\vvv a\leq x\leq a$
we have the Poisson kernel
\[
 P\uuu x(\theta)= \frac{1}{2\pi}\cdot
\frac{1\vvv x^2}{1+x^2\vvv 2x\cos\,\theta}
\]
We also introduce a partial $y$\vvv derivative and define
\[ 
\partial\uuu y(P\uuu x)(\theta)=\frac{1}{2\pi}\cdot
\frac{(1\vvv x^2)\cdot \cos\,\theta}{(1+x^2\vvv 2x\cos\,\theta)^2}
\]
It means that whenever $h(\theta)$ is a continuous function on the unit circle
and $H(z)$ its harmonic extension to $D$ then
\[
\partial\uuu y(H)(x,0)=
\int\uuu 0^{2\pi} \partial\uuu y(P\uuu x)(\theta)\cdot h(\theta)\cdot d\theta
\]
\medskip

\noindent
{\bf{12.1 Proposition.}} \emph{For each $0<a<1$ the linear space of
functions on $T$ generated by
$\{ P\uuu x\}$ and $\partial\uuu y(P\uuu x)\}$
as $\vvv a\leq x\leq a$ is dense in $L^2(T)$}.
\medskip

\noindent
\emph{Proof.}
If  $h\in L^2$ is $\perp$ to this space it follows
from the above that its harmonic extension
is identically
zero and since $h(\theta)$ is almost everywhere
equal to the  radial limit of its harmonic extension it follows that $h=0$. 
This proves the requested density.
\bigskip


\noindent
Let us now consider a point $z\in D$ which is outside the interval.
Now $\theta\mapsto P\uuu z(\theta)$ is an $L^2$\vvv function.
So to each $\epsilon>0$ there exist
finite subsets $\{\alpha\uuu\nu\}$ and $\{\beta\uuu\nu\}$
in $[\vvv a,a]$ such that an
${\bf{R}}$\vvv linear combination
\[
\sum \, c\uuu j\cdot P\uuu{\alpha \uuu j}(\theta)+
+\sum \, d\uuu k\cdot \partial\uuu y(P\uuu{\beta \uuu k}(\theta)\tag{1}
\]
has distance $\leq\epsilon$ in  the $L^2$\vvv norm to $P\uuu z$.
Applying Cauchy\vvv Schwarz inequality it follows that
for every harmonic function $H$ in the unit disc
whose boundary function $h(\theta)$  belongs to $L^2(T)$
one has 
\[
\bigl |H(p)\vvv \sum\, c\uuu j\cdot H(\alpha \uuu j)\vvv
\, \sum\, d\uuu k\cdot \partial\uuu y(H)(\beta \uuu k)\,\bigr|\leq
\sqrt{\epsilon}\cdot ||h||\uuu2\tag{*}
\]
\medskip


\noindent
{\bf{Remark.}}
The family of $L^2(T)$\vvv functions used for the density in
Proposition 12.1 is not orthogonal and it appears to be cumbersome to
exhibit an orthonormal  family in an efficient manner.
So above we have just proved a density theorem while no specific control
is given to the constants $\{c\uuu \nu\}$ or $\{d\uuu k\}$
which in addition depend on $z$ when the $\epsilon$\vvv approximation 
in
(*) is attained. But a merit is that (*) hold for all harmonic functions $H$ with
$h\in L^2(T)$.
This can for example be used to study growth properties of harmonic functions in 
strip domains. See the section \emph{Lindelšf functions} 
in Special Topics  XXX for such an application. 


\bigskip

\noindent
{\bf{12.2 On inner normal derivatives.}}
Consider the domain
\[
\Omega\uuu A=
\{ 0<x<1\}\,\cap \{ x> A|y|\}
\] 
where $A>0$.
If $A$ is small this domain is almost a half\vvv disc while it
shrinks as $A$ increases. See figure XX.
Let $u(x,y)$ be harmonic in $\Omega\uuu A$ with continuous boundary values where
$u(0,0)=0$ and $u\geq 0$ in $\bar\Omega$.
This entails that $u>0$ in $\Omega$ and in particular we get
the positive number
$u(1/2)$.
Now we  estimate $u(x,0)$ from below as $x\to 0$.

\medskip

\noindent
{\bf{Exercise.}}
Show that there exists a positive number $A\uuu *$ which depends on $A$
only such that
\[ 
u(x,0)\geq A\uuu *\cdot u(1/2,0)\cdot x
\]
hold for all $0<x<1/2$ and every harmonic function $u$ as above.
A hint is to employ the conformal map $F$
from $\Omega\uuu A$ onto the half\vvv disc $D\uuu +$
in the right half\vvv plane where 
\[
F(z)= z^{\frac{1}{A}}
\]
Then we can pass to the half\vvv disc
and seek $B\uuu *$ such that
\[
U(x^{\frac{1}{A}},0)\geq B\uuu *\cdot U(2^{\vvv\frac{1}{A}},0)\cdot
x^{\frac{1}{A}}
\]
for non\vvv negative harmonic functions in the half\vvv disc
which is achieved using a suitable version of Harnack's inequality
which is left to the reader to analyze in detail.

\medskip

\noindent
{\bf{An application.}}
Let $\Omega$ be a connected domain
where the origin is a boundary point which contain
$\Omega\uuu A$ for some $A>0$.
Prove that there again exists a constant $A\uuu{**}$ which depends on
$A$ only such that
(*) above holds for every harmonic function
$u$ in $\Omega$ which is $>0$ in $\Omega$ while $u(0,0)=0$.
This entails in particular that 
\[ 
\liminf\uuu{x\to 0}\frac{u(x)}{x}>0
\]
\medskip

\noindent
{\bf{Remark.}}
A special case occurs when $\partial\Omega$ is of class $C^1$
and working locally close to the boundary point $(0,0)$ the domain is defined by an equation
$\{x>\rho(y)\}$ where $\rho(y)$ is a real\vvv valued $C^1$\vvv function with
$\rho(0)=0$.
In that case we get (xx) above
and this strict inequality for $C^1$\vvv domains is sometimes referred to as 
Hopf's lemma who established similar inequalities in higher dimensions.
See also [Krantz\vvv Green: page 440\vvv 444] 
which describes how Hopf's Lemma is used to establish certain 
smoothness results for
conformal mappings.





\newpage

\centerline{\bf{13. Representations of rotation invariant harmonic functions.}}

\bigskip

\noindent
Let $(x,t,s)$ be the real coordinates in
${\bf{R}}^3$. A real\vvv valued $C^2$\vvv function
$u(x,t,s)$ is harmonic if it satisfies the Laplace equation.
We shall consider the subclass of harmonic 
 functions which are invariant under rotations of the
 $(t,s)$\vvv coordinates.
More precisely, suppose that $u$ is defined in
in an open set $U$ given as the product of an interval 
$(-A,A)$
on the $x$\vvv axis and
a disc $\{t^2+s^2<R^2\}$. 
The invariance
means that the function
\[
\phi\mapsto u(x,r\cos\phi.r\sin\,\phi) 
 \] 
is constant for each $x$ and $0<r<R$.
Let $\square$ be the rectangle in the
$z$\vvv plane defined by 
\[ 
\{z=x+iy\,\colon\, 
- A<x<A,\colon\, - R< y<R\}
\]
\medskip


\noindent
Let $f(z)$ be analytic in
$\square$ assume that
$f(x)$ is real-valued when
$-A<x<A$.
Then we have

\medskip

\noindent
{\bf{13.1 Theorem.}}
\emph{Define $u$ in $U$ by}
\[ 
u(x,t,s)= 
\frac{1}{\pi}\int\uuu 0^\pi\, f(x+i\sqrt{t^2+s^2}\cdot\cos\,\phi)\, d\phi
\]
\emph{Then  $u$ is  harmonic and rotation invariant in $U$}
\medskip


\noindent
\emph{Proof.}
The existence of complex derivative of $f$ give
\[
\partial\uuu x^2(u)=
\frac{1}{\pi}\int\uuu 0^\pi\, f''(x+i\sqrt{t^2+s^2}\cdot\cos\,\phi)\, d\phi\tag{i}
\]
\[ 
\partial\uuu t(u)=
\frac{1}{\pi}\int\uuu 0^\pi\, i\cos\,\phi\cdot
\frac{t}{\sqrt{t^2+s^2}}\cdot
f'(x+i\sqrt{t^2+s^2}\cdot\cos\,\phi)\, d\phi\implies
\]
\[ 
\partial\uuu t^2(u)=
\frac{1}{\pi}\int\uuu 0^\pi\, [\vvv \cos^2\,\phi\cdot
\frac{t^2}{t^2+s^2}+i\cos\,\phi\cdot\frac{s^2}{(t^2+s^2)^{3/2}}\bigr]\cdot 
f''(x+i\sqrt{t^2+s^2}\cdot\cos\,\phi)\, d\phi\tag{ii}
\]
A similar expression is found for
$\partial\uuu s^2(u)$ and adding the result we find that
\[
\Delta(u)=
\frac{1}{\pi}\int\uuu 0^\pi\, \bigl(\sin^2\phi\cdot f''+
i\cos\phi\cdot \frac{1}{\sqrt{t^2+s^2}}\cdot f'\,\bigr )\, d\phi\tag{iii}
\]
where $1\vvv \cos^2\phi=\sin^2\phi$ was used.
Next, notice that
\[
\partial\uuu\phi(f'(x+i\sqrt{t^2+s^2}\cos\phi)=
\vvv i\sqrt{t^2+s^2}\cdot \sin\phi\cdot f''(x+\sqrt{t^2+s^2}\cos\phi)\tag{iv}
\]


\noindent
BY partial integration of the
first term in (iii), the reader can check that
(iv) entails that $\Delta(u)=0$.
Next, the integral equation in the theorem shows that
$u$ is rotation invariant and 
\[ 
u(x,0,0)= f(x)
\]
Since $f(x)$ was real-valued the reader can 
confirm that $u$ is real-valued in $U$ and the proof is finished.
\medskip


\noindent
{\bf{A converse result.}}
Let $u$ be 
a rotation invariant harmonic function. Then there exists
an analytic function $f(z)$ in $\square$ such that
$u$ is represented as in the theorem.
To prove this we  use that
harmonic functions are real-analytic
and define $f$ on the real $x$-interval $(-A,A)$ by
\[
f(x)= u(x,0,0)
\]
At this stage we leave as an exercise to the reader to confirm that
$f$ extends to an analytic funcituon in
$\square$ and that $u$ is represented via $f$ as in the theorem.
A hint is to apply the general result below.
\newpage


\noindent
{\bf{13.2 Integrals expression solutions to elliptic equations.}}
Let $a(x,y),b(x,y),c(x,y)$ be real\vvv valued and
real\vvv analytic functions in a rectangle
\[
\square=\{z= x+iy\,\colon -A<x < A\,\colon\, 
\vvv B<y<B\}
\]
Denote by $\mathcal S$ the class of
real-valued functions
$u(x,y)$  which solve the elliptic equation
\[ 
\Delta(u)+ a\frac{\partial u}{\partial x}+
b\frac{\partial u}{\partial y}+c=0
\]
in $\square$.
\medskip

\noindent
{\bf{13.3 Theorem.}}
\emph{There exists a function $V(x,y,\zeta)$
where $\zeta$ is a new complex variable such that 
$V$ is complex analytic with
respect to $\zeta$, and the general solution $u$ is of the form}
\[
u(x,y)= A\cdot V(x,y,0)+
\mathfrak {Re}\, \int\uuu 0^{x+iy}\, V(x,y,\zeta)\cdot f(\zeta)\, d\zeta
\]
\emph{where $A$ is a real constant and $f$ an arbitray continous
complex analytic function.}
\medskip

\noindent
{\bf{13.4 Remark.}}
The results above appear in Carleman's article
\emph{Applications de la thŽorie des fonctions analytiques
ˆ la resolutions de certaines Žquations fonctionelles} [Acad. Italia Volta 1940].
A special case of Theorem 13.3 appears whgen we regard
solutions to the elliptic equation 
\[
\Delta(u)-k^2\cdot u=0
\] 
where $k>0$ is a constant.
Here the general $u$-solution defined in some disc centered at the origin
takes the form
\[
u(x,y)= \mathfrak{Re}\, \int_0^z\, J_0(ik\sqrt{|z|^2-\bar z\cdot \zeta})\cdot f(\zeta)\, d\zeta
\]
where $z=x+iy$ and $J_0$  the usual Bessel function.


\newpage


\centerline{\bf{14. Ganelius' inequality for conjugate harmonic functions.}}
\bigskip


\noindent
{\bf{Introduction.}}
We   prove a result due to Ganelius from the article
\emph{Sequences of analytic functions and their zeros} Arkiv fšr matematik. Vol 3 (1953).
Here is the situation: Let $u$
be a harmonic funtion 
defined in some open neighborhood
of
the closed unit disc where 
$u(0)=0$. Its harmonic conjugate $v$
is normalised so that
$v(0)$. The constants  $H,K$ are defined by:
\[ 
\max_\theta\, u(e^{i\theta})=H\quad\colon\quad
\max_\theta\, \frac{\partial v}{\partial\theta}(e^{i\theta})=K\tag{*}
\]
where the maximum is taken over
$0\leq \theta\leq 2\pi$.

\medskip

\noindent
{\bf{14.1 Theorem.}}
\emph{There exists an absolute constant $C$ such that}
\[ 
\max_{z\in D}\, |v(z)|\leq C\cdot \sqrt{HK}
\]

\bigskip

\noindent{\emph{Proof}.
For a small $\epsilon>0$ and a positive number $\lambda$ we set
\[ 
G(z)= \log\, \bigl| \frac{1+z^\lambda}{1-z^\lambda}\bigr |
\]
where $G$  is defined in the intersection of the unit disc $D$ and the
sector $S=\{z\,\colon\,|\arg z|<\frac{\pi}{2\lambda}\}$.
If $z=r\cdot e^{i\pi/2\lambda}$ we see that
$G(z)=\log \frac{/1+ir}{1-ir}\bigr |=0$
and the reader may verify that
the normal derviative
$\frac{\partial G}{\partial r}=0$ if
$z=e^{i\theta}$  when $0<|\theta|<\frac{\pi}{2\lambda}$.

\medskip

\noindent
{\bf{1. Exercise.}}
Apply  Green's formula  to domains
$S\cap \{|z-1|>\epsilon\}$ and  show that the passage to the
limit when
 $\epsilon\to 0$ gives the equation
 below for each $0\leq \phi\leq 2\pi$:
 \[
2\lambda\cdot \int_0^1
\,  \frac{u(re^{i(\phi-\frac{\pi}{2\lambda})}+
u(re^{i(\phi+\frac{\pi}{2\lambda}})}{1+r^2}\,r^{\lambda-1}\, dr-\pi u(e^{i\phi})=
\]
\[
\int_ {\frac{\pi}{2\lambda}}^{\frac{\pi}{2\lambda}}
\,\log\,\frac{\cos(\lambda\theta/2)}{
\sin(\lambda\theta/2)}\cdot 
\frac{\partial u}{\partial r}(
re^{i(\phi+\theta})\,d\theta\tag{1}
\]
\bigskip


\noindent
Next, the restriction of the harmonic conjugate
$v$ to the unit circle is written as:
\[
v^*(\theta)= v(e^{i\theta})
\]
The Cauchy-Riemann equations give
\[
\frac{\partial u}{\partial r}(
re^{i(\phi+\theta})= \frac{\partial v^*}{\partial\theta}(\phi+ \theta)
\]
Choose some
$0<\xi<\pi$
and integrate
(1) with respect to $\phi$ over $(-\xi,\xi)$.
The equality
\[
\frac{\partial v^*}{\partial\theta}(\phi+ \theta)=
\frac{\partial v^*}{\partial\phi}(\phi+ \theta)\tag{2}
\] 
implies that
the integral of the last term in (1) becomes
\[
\int_ {\frac{\pi}{2\lambda}}^{\frac{\pi}{2\lambda}}
\,\log\,\frac{\cos(\lambda\theta/2)}{
\sin(\lambda\theta/2)}\cdot  \bigl[v^*(\xi+\theta)-v^*(-\xi+\theta)\bigr ]
\,d\theta\tag{3}
\]
\medskip

\noindent
{\bf{2. Exercise.}}
Recall that $u$ is harmonic with $u(0)=0$ and by (*) we have 
$u^*(\theta)\leq H$ for all $\theta$.
Show that
\[ 
\int_a^b\, u(\theta)\,d\theta\geq  -2\pi H
\] 
hold for all intervals $(a,b)($ on the unit circle
and deduce that 
the integral of the first two terms in (1)
taken over an interval $-\xi<\phi<\xi)$ is bounded below by
$-4\pi H$ for each $0<\xi\leq \pi$.

\bigskip

\noindent
From the above
it follows that
\[
\int_ {\frac{\pi}{2\lambda}}^{\frac{\pi}{2\lambda}}
\,\log\,\frac{\cos(\lambda\theta/2)}{
\sin(\lambda\theta/2)}\cdot  
\bigl[v^*(\xi+\theta)-v^*(-\xi+\theta)\bigr ]
\,d\theta\geq -4\pi H\tag{4}
\]

\noindent
At this stage we   use the upper bound for the
$\theta$-derivative of $v^*$.
To simplify notations we set
\[ 
J_\lambda(\theta)=\log\,\frac{\cos(\lambda\theta/2)}{
\sin(\lambda\theta/2)}\tag{5}
\]
\medskip

\noindent
{\bf{3. Exercise.}}
Use the ineqality $\frac{dv^*}{d\theta}\leq K$
for the
$\theta$-periodic $v^*$-function to show that
\[
v^*(\xi+\theta)-v^*(-\xi+\theta)\leq
v^*(\xi-\frac{\pi}{2\lambda})-
v^*(-\xi+\frac{\pi}{2\lambda})+K\cdot \frac{\pi}{\lambda}
\quad\colon\quad 
 -\frac{\pi}{2\lambda}<\theta<\frac{\pi}{2\lambda}\tag{6}
\]
\medskip

\noindent
Since $J_\lambda(\theta)\geq  0$ for all $\theta$
it follows from (4-5) that we have the inequality
\[
v^*(\xi-\frac{\pi}{2\lambda})-
v^*(-\xi+\frac{\pi}{2\lambda})+K\cdot \frac{\pi}{\lambda}
\geq
- \frac{1}{I(\lambda)}\cdot  4\pi H
\quad\colon\quad I(\lambda)= 
\int_ {\frac{\pi}{2\lambda}}^{\frac{\pi}{2\lambda}}
J_\lambda\theta)\,d\theta\tag{7}
\]

\noindent
{\bf{4. Exercise.}}
Show that

\[
I(\lambda)=\frac{4}{\lambda}\int_1^\infty\, \frac{\log t}{1+t^2}\, dt
= \frac{4}{\lambda}\cdot k\quad\colon
k= 1+ \sum_{m=1}^\infty\,(-1)^m\cdot \frac{1}{(m+1)^2} \simeq
0,916\ldots
\]
\medskip

\noindent
{\bf{5. The  choice of $\lambda$.}}
The inequality (7) hold for all $\xi$ and 
and we choose $\lambda$ to minimize
\[
K\cdot \frac{\pi}{\lambda}+ \frac{4}{\lambda}\cdot k\cdot H
\]
It means that we take
$\lambda= \sqrt{\frac{Kk}{\pi H}}$ and
(7) gives the inequality
\[
v^*(\xi-\frac{\pi}{2\lambda})-
v^*(-\xi+\frac{\pi}{2\lambda})\geq
-2\pi\cdot \sqrt{\frac{\pi}{k}HK}\tag{8}
\]
\medskip

\noindent
Since  (8) hold for all $\xi$ and 
$v^*$ is $2\pi$-periodic we obtain
\[
v^*(2\kappa+\xi)-v^*( \xi)\geq
-2\pi\cdot \sqrt{\frac{\pi}{k}HK}\quad\forall\,\,
0\leq \xi,\kappa\leq 2\pi
\tag{9}
\]
Finally, since $v(0)=0$ and $v$ is harmonic
the boundary value function $v^*$ has at least one zero $\xi_0$
and we  can  choose $\kappa$ so that
\[
v^*(2\kappa+\xi_0)= \min_\theta\,V^*(\theta)
\]
 Then (9) implies that
 the minimum of $v^*$ is
 $\geq -2\pi\cdot \sqrt{\frac{\pi}{k}HK}$. In  the same way the
 reader can verify that the maximum of $v^*$ cannot exceed
 $2\pi\cdot \sqrt{\frac{\pi}{k}HK}$.
Hence (*) in Theorem 14.1 holds
with
\[
C=2\pi\cdot \sqrt{\frac{\pi}{k}}\tag{10}
\]
where $k$ is the constant from Exercise 4.


\bigskip




\centerline {\bf{14.2 Applications to zeros of polynomials.}}
\medskip




\noindent
Let $n\geq 1$ and consider a polynomial 
\[
p(z)=\prod\, (1-ze^{-i\theta_\nu})
\]
where $\{\theta_\nu\}$ is some $n$-tuple 
in the periodic  interval $[0,2\pi]$.
Let $(\alpha,\beta)$ be an interval on the unit circle.
Denote by $N(\alpha,\beta)$ the number
of $\theta_\nu$ satisfying
\[
\alpha<\theta_\nu<\beta
\]
and  $|p|_D$ is  the maximun norm of
$p$ over the unit disc.

\medskip

\noindent
{\bf{14.3 Theorem}}. \emph{With the same absolute constant as in Theorem 14.1 one has}
\[
\bigl[ \frac{N(\alpha,\beta)}{n}-\frac{\beta-\alpha}{2\pi}\bigr|\leq
C\cdot \sqrt{n\cdot \log |p|_D}
\]
\medskip


\noindent
\emph{Proof.}
Consider  the
harmonic function $u(z)$ in the unit disc defined by
\[
 u(z)=\frac{1}{\pi}\log\, |p(z)|=
 \frac{1}{\pi}\cdot \sum\, \log\,|1-ze^{-i\theta_\nu}|
\]
It follows that
the conjugate harmonic function becomes
\[ 
v(z)= \frac{1}{\pi}\cdot \sum\, \arg\,(1-z\cdot e^{-i\theta_\nu})
\]
From this the reader can verify  the inequality
\[
\frac{\partial v}{\partial\theta} (re^{i\theta})\leq
\frac{n}{2\pi}\quad\colon\, 0<r<1
\]

\noindent 
From the above  Theorem 14.1 gives
\[
 \max_\theta\, v(\theta) \leq C\sqrt{\frac{n}{2\pi}\cdot \log\, |p|_D}
 =
\sqrt{ \frac{2\pi}{k}}\cdot \sqrt{n\cdot  \log\, |p|_D}
\]
where $k$ is Catalani's constant from Exercise 4.
 
 
 \bigskip
 
 NOW DONE by generalformula !


\bigskip

\centerline {\bf{14.4 Schur's inequality.}}
\bigskip

 \noindent
 A  polynomial $P(z)$ of degree $n$ with constant term $a_0\neq 0$ can be written
as
\[ 
P(z)= a_0\cdot \prod\,(1-\frac{z}{\alpha_k})
\]
which entails that the absolute value of coefficient $a_n$ of $z^ n$ becomes
\[ 
|a_n|= \frac{|a_0|}{\prod\, |\alpha_k|}\tag{1}
\]
Put  $\alpha_k= \rho_k\cdot e^{i\theta_k}$
and set
\[ 
p(z)= \prod\, (1-e^{-i\theta_k}z)
\]
\medskip

\noindent
{\bf{14.5 Theorem.}}
\emph{One has the inequality}
\[
|p|_D\leq \frac{|P|_D}{\sqrt{|a_0a_n|}}
\]
\medskip

\noindent
\emph{Proof.}
For each $k$ one we set $|\alpha_k|= r_k$ and notice that
\[
r_k\cdot |1-\frac{e^{i\theta}}{\alpha_k}|^2=
r_k+\frac{1}{r_k}-2\cos(\theta-\theta_k)\geq 2-
2\cos(\theta-\theta_k)= |1-e^{i(\theta-\theta_k)}|^2
\]
This holds for each $\theta$
we choose $\theta$
where $|p|$ takes its maximum and conclude that
\[
|p|_D^2\leq \frac{\prod\, r_k}{|a_0|^2}\cdot |P|^2_D
\]
Taking the square root and using (1)  above we get Theorem 14.5
\bigskip


\noindent
{\bf{14.6 Carlson's formula.}}
Studies of zeros of polynomials, and more generally 
of analytic functions, in sectors
were  treated by F. Carlson in the article
\emph{Sur quelques suites de polynomes}.
We present a specific formula by Carlson.
Let $P(z)$ be a polynomial of some degree $n$
where  $P(x)\neq 0$ for every real $x\leq 0$.
The argument of each root $\alpha_\nu$ of $P$
is taken in the interval $(-\pi,\pi)$.
If $0<\phi<\pi$
we set
\[ 
J(\phi) =\sum\, (\phi-|\arg\alpha_\nu)|
\] 
where the sum is taken over roots of $P$ with their arguments in
$(-\phi,\phi)$. 

\medskip

\noindent
{\bf{14.6.1 Theorem.}}
\emph{For each $\phi$ one has the equality}

\[
J(\phi)= \frac{n\phi^2}{2\pi}+
 \frac{1}{2\pi}\int_0^\infty\,\frac{\log |P(re^{i\phi})|\cdot 
\log |P(re^{-i\phi})|}{|\log P(r)|^2}\, \frac{dr}{r}
\]
\medskip

\noindent
\emph{Proof}
By a factorisation of $P$
the proof is reduced to the case $n=1$ with
$P(z)=1-\frac{1}{\alpha}$ for some
non-zero complex number $\alpha$ and here the verification is left 
as an exercise to the reader.
\bigskip

\noindent
The formula above is  special and yet instructive.
Let us  finally mention
that 
one can study distributions of zeros for Dirichlet series and
exponential polynomials. This requires a further
analysis and will not be exposed here.
The reader may consult the cited
article by Ganelis for results about
complex zeros of
exponential polynomials.





\newpage

\centerline
{\bf{15. Beurling's  minimum principle for positive harmonic functions}}
\bigskip


\noindent
{\bf{Introduction.}}
We expose a result  from the article [Beurling:Ann.sci, Fennica].
 Let $\Omega$ be a simply connected
domain.
Let $g(z,\zeta)$ be the Green function for $\Omega$.
If
$p\in\partial\Omega$
a  Martin function with respect to $p$ 
is a positive harmonic function
$\phi$ in $\Omega$ such that
\[ 
\lim_{z\to q}\,\phi(z)=0\quad\colon\,\forall\,\, q\in\partial\Omega\setminus \{p\}
\]
The class of these Martin functions is denoted by
$\mathcal M(p)$.
Following  Beurling  we give

\medskip

\noindent
{\bf{15.0 Definition.}}
\emph{
A sequence $\mathcal S=\{ z_n\}$  in
$\Omega$ which convergs to the boundary point $p$
is an equivalence sequence 
at $p$ if the following implication
hold for every positive harmonic function $u$ in $D$,
every real $\lambda>0$ and each  $\phi\in \mathcal M(p)$}
\[
u-\lambda\cdot \phi\bigl| S\geq 0\implies u\geq \lambda\cdot \phi \quad\text{holds in the whole 
domain}\,\,\Omega
\]
\medskip



\noindent
{\bf{15.1 Theorem.}}
\emph{A sequence $\mathcal S=\{z_n\}$ which converges to $p$
is an equivalence at $p$
if and only if it constains a subsequence
$\{\xi_k= z_{n_k}\}$ such that}
\[
\sup_{k\neq j}\, g(\xi_j,\xi_k)<\infty\quad\text{and}\quad
\sum_{k=1}^\infty\, g(z,\xi_k)\cdot \phi(\xi_k)= +\infty
\quad\colon\, z\in\Omega
\]
\medskip


\noindent
{\bf{Remark.}}
The necessity in Theorem 15.1  proved rather easily. See ¤ xx below.
From now on
we treat   the non-trivial part, i.e.we prove  that the two conditions in Theorem 15.1
entail that $\mathcal S$ is an equivalence at $p$.
By Riemann's mapping theorem it suffices to prove this sufficiency
when
$\Omega$ is the unit disc $D$.
Since every positive harmonic function $u$ in $D$
is the Poisson extension of a non-negative Riesz measure on $T$,
it follows 
that every  $\phi\in \mathcal M(p)$
is 
the
Poisson extension of the unit point mass at $p$ times a positive constant
$\lambda$, i.e. of the form
\[
\phi_\lambda(z)= \frac{\lambda}{2\pi}\cdot \frac{1-|z|^2}{|1-z|^2}
\]
where the mean-value property gives $\phi_\lambda (0)=\lambda$.
Moreover, if $u$
is a positive harmonic function
given by  the Poisson extension $P_\mu$ of some 
non-negative Riesz measure $\mu$ in $D$.
then 
the inequality $P_\mu\geq \phi_\lambda $
holds everywhere in   $D$ if and only if
the measure
$\mu$ has
an atom at $z=1$ of mass $\geq \lambda $.
Up to scaling it suffices to consider the
case $\lambda=1$ and hence
$\mathcal S$ is an equivalence sequence if 
and only if the following hold for 
every
non-negative Riesz measure on $T$:
\[
P_\mu(z_n)\geq \phi_1(z_n)\quad\colon\, n=1,2,\ldots\implies
\mu(\{1\})\geq 1\tag{* }
\]

\noindent
To prove (*) we  prefer to work in
the upper half-plane  where  $p$Êis taken as $\infty$. Here we get 
Martin function $\phi(x,y)= y$ and 
Green's  function is
\[ 
g(\zeta,z)=\log\, \frac{|z-\bar\zeta|}{|z-\zeta)}
\]
When $z=re^{i\theta}$
where $r$ is large and $0<\theta<\pi$
one has
\[ 
\frac{|re^{i\theta}+i|^2}{|re^{i\theta}-i|^2}
=\frac{r^2+1+2r\sin\theta}{ r^2+1-2r\sin\theta}
\]
It follows that
\[
g(i,re^{i\theta})=
\frac{2\sin\,\theta}{r}+O(r^{-2})
\]

\noindent
in polar coordinates we write
$\{\zeta_k=r_ke^{i\theta_k}\}$ }
where $\{0<\theta_k=\arg \xi_k<\pi\}$
and from the above it is clear that
the  two conditions in Theorem 15.1 are  equivalent to
\[
\inf_{j\neq k}\, \frac{|\xi_j-\xi_k|}
{|\xi_j-\bar \xi_k|}
\quad\colon\quad 
\sum_{k=1}^\infty\, \sin^2\,\theta_k=+\infty \tag{**}
\]


\newpage


\noindent
At this stage
we need a result  which has independent interest. 
In the final part of the proof of Theorem 15.2
below we
derive the
sufficiency in
Theorem 15.1.



\medskip



\noindent
{\bf{15.2 Theorem.}}\emph{
For each positive harmonic  function $u(x,y)$  in $U_+$
we put}
\[
E_u=\{ x+iy\in U_+\quad\colon\, u(x,y)\geq y\}
\]
\emph{Then one has the implication}
\[
U_+\setminus E_u\neq\emptyset\implies
\int_{E_u}\,\frac{dxdy}{1+x^2+y^2}<\infty\tag{15.2}
\]
\medskip




\noindent{\emph{Proof}.
The impliction (15.2) is obvious
when
$u(x,y)=ay$ for some positive real number $a$, i.e.
regard the cases $a<1$ and $a\geq 1$ separately.
From now on we assume that
$u(x,y)$ is not a linear function of $y$ and the
Harnack-Hopf inequality from ¤ XX gives
the strict inequality
\[ 
\frac{\partial u}{\partial y}(x,y)<\frac{u(x,y)}{y}
\quad\colon\, (x,y)\in U_+\tag{1}
\]
\medskip

\noindent
Set $u_*=y-u$ which entails that
\[ 
\{u_*>0\}=U_+\setminus E_u\tag{2}
\]

\medskip

\noindent
\emph {3. A simply connected domain.}
Assume that the set $U_+\setminus E_u$ is non-emtpy and let
$\Omega$ be  a  connected component of this open set.
Replacing $u$ by the harmonic
function $u(x+a,y)$ for a suitable 
real $a$
we may assume that
$\Omega$ contains a point on the imaginary axis and after a scaling
that $i\in\Omega$.
Next, (1) gives
\[ 
\frac{\partial u_*}{\partial y}=1-\frac{\partial u}{\partial y}
>1-\frac{u}{y}\tag{4}
\]
Starting at a point $(x,y)\in\Omega$ it follows that
$s\mapsto u_*(x,y+is)$ increases strictly  on $\{s\geq 0\}$ and
hence the open set
$\Omega$ is placed above a graph, i.e. there exists an interval $(a,b)$
on the real $x$-axis and a non-negative 
continuous function $g(x)$ on $(a,b)$ such that
\[ 
\Omega=\{ (x,y)\,\colon a<x<b\,\,\colon\,\, y>g(x)\}\tag{5}
\]
In (5)
it  may occur that the interval $(a,b)$
is unbounded and may even be
the whole $x$-axis in which   case $\Omega$ is the sole component of
$U_+\setminus E_u$. In any case, since $i\in\Omega$
one has
$a<0<b$
and $\Omega$ contains
the the set $\{ai\colon\, a\geq 1\}$.
Next, for each $r>2$ we put
\[ 
C_r=U_+\cap \{|z+i|<r\}\tag{6}
\]
Notice that
$C_r$ contains the point $(r-1)i$
which also belongs to $\Omega$.
Denote by  $\gamma_r$ be the largest open interval on the
circle $\{|z+i|= r$ which contains 
$(r-1)i$ and at the same time is 
contained in $\partial\Omega$.
With the aid of a figure it is clear that the
set $\Omega _r= \Omega\cap C_r$ 
is simply connected where 
$\gamma_r$ is a part of
$\partial  D_r$ and   $u_*=0$ on
$\partial D_r\setminus \gamma_r$.
\medskip



\noindent{\emph{ The use of harmonic measure.}}
Let $h_r(z)$ be the harmonic function in
$\Omega_r$ which is 1 on
$\gamma_r$ and zero on the rest of the boundary.
By the above and the maximum principle for harmonic functions
we have the inequality
\[ 
u_*(i)\leq h_r(i)\cdot \max_{z\in\partial D_r} u_*(z)\leq r\tag{7}
\]
where the last inequality follows since
$u_*(x,y)\leq y\leq  r$.
To  estimate  the function $h_r(z)$ with respect to  $r$ and $z$
we  use
the harmonic function
\[
\Psi(z)= \log\, \bigl|\frac{z+i}{2i}\bigr |\implies
|\nabla(\Psi)|^2=\Psi_x^2+\Psi_y^2=\frac{1}{|z+i|^2}\tag{8}
\]
Set
\[ 
m(r)=
\frac{1}{\pi}\,  \iint_{E_u\cap C_r}\,|\nabla(\Psi)|^2\, dxdy=
\frac{1}{\pi}\,  \iint_{E_u\cap C_r}\,\frac{1}{|z+i|^2}|\, dxdy\tag{9}
\]
Notice  that
\[
\frac{1}{\pi}\,  \iint_{C_r}\,\frac{1}{|z+i|^2}|\, dxdy<\log r\tag{10}
\]
Together (9-10) give the inequality
\[
\frac{1}{\pi}\,  \iint_{\Omega_r}\,|\nabla(\Psi)|^2\, dxdy<
\log r-m(r)\tag{11}
\]


\noindent
Next, we notice that
 \[ 
 \Psi(z)= \log r-\log 2\quad\text{on}\quad \gamma_r\quad\text{and}\quad
 \Psi(i)=0\tag{12}
 \] 


\noindent
Now we can apply the general inequality from ¤ XX in [Beurling-Special Topics]
and conclude that (11-12) 
give
the inequality
 \[ 
 h_r(i)\leq e^{-\frac{\pi L^2}{A}} \quad\text{where}\quad
 L=\log r-\log 2 \tag{13}
\]


\noindent
Next, the reader may verify
that there exists a constant $C$
which is independent of $r\geq 2$ such that
\[
 \frac{\pi L^2}{A}\geq \frac{\lg r-\log 2)^2}{\log r-\log m(r)}
 \geq \log r-2\log 2+m(r)\cdot \bigl[1-\frac{C}{\log r}]\tag{14}
 \]
 \medskip
 
 \noindent
Then (13-14)
gives a constant $C_1$ such that
\[
h_r(i)\leq  e^{-\frac{\pi L^2}{A}}\leq C_1\cdot \frac{1}{r}\cdot e^{-m(r)}
\quad\colon\, r\geq 2\tag{15}
\]

\noindent
Then (7) and  (15) give
\[ 
u_*(i)\leq C_1\cdot \cdot e^{-m(r)}\tag{*}
\]

\medskip

\noindent
This inequality hold for all $r>2$ and since
$u_*(i)>0$
there must exist a finite limit
\[ 
\lim_{r\to\infty} m(r)=m^*\tag{**}
\]
The requested implication in Theorem 15.2
follows since  (9)  this means that
\[
\iint_{E_u}\, \frac{1}{|z+i|^2}\, dxdy=\lim_{r\to\infty} m(r)
\]







 





























\end{document}


