
\documentclass{amsart}


\usepackage[applemac]{inputenc}

\addtolength{\hoffset}{-12mm}
\addtolength{\textwidth}{22mm}
\addtolength{\voffset}{-10mm}
\addtolength{\textheight}{20mm}


\def\uuu{_}

\def\vvv{-}

\begin{document}


\centerline{\bf\large{Chapter VI: Conformal mappings.}}


\medskip

\noindent
0.Introduction

\medskip

\noindent
1.A.  Riemann's mapping theorem for  simply connected domains


\medskip

\noindent
1.B.  The  mapping theorem for   connected domains
 

\medskip

\noindent
2. Boundary behaviour
\medskip

\noindent
3. Picard's theorem



\medskip

\noindent
4. Geometric results


\medskip

\noindent
5. Schwartz-Christoffell maps
\medskip

\noindent
6. Privalov's theorem
\medskip

\noindent
7. Maps between multiple connected domains
\medskip

\noindent
8. The Bergman kernel
\medskip

\noindent
9. The electric equilibrium potential
\medskip


\noindent
10. Conformal maps of circular domains
\medskip

\noindent
11. Beurling's mapping theorem



\bigskip









\noindent 
\centerline {\bf Introduction.}

\bigskip


\noindent 
In his disseration from 1851,  Riemann announced 
the uniformisation theorem which applies  to
general  Riemann surfaces.
We give some comments about the general mapping theorem in ¤ 0.6.
The simplest
version 
asserts that every simply connected open
subset $\Omega$ of 
${\bf {C}}$ which is not equal to the whole complex plane is
conformal with the open unit disc $D$.
More precisely, 
for every point  $z_0\in\Omega$ there exists a unique
$f\in\mathcal O(\Omega)$ where $f(z_0)=0$ and $f'(z_0)$ is real and
positive such that 
\[
f\colon\Omega\to D\tag{*}
\]
is bijective and the complex derivative $f'(z)\neq 0$
for all $z\in\Omega$. 
Here  $f$
is the solution to a variational problem where one consider the family
$\mathcal C(\Omega,z_0) $ of  all analytic functions
$g$ in $\Omega$ for which $g(\Omega)\subset D$, $g(z_0)=0$ and
the derivative $g'(0)$ is real and non-negative.
Then one seeks
\[
\max_{g\in\mathcal C(\Omega,z_0)}\, g'(z_0)
\]

\noindent 
The extremal function   to 
this  variational problem gives the
conformal map (*). For an arbitrary
$g\in\mathcal O(\Omega)$ with  $g(\Omega)\subset D$
we can choose $\theta$ so that if
$h=e^{i\theta}\cdot g$ then $h'(0)$ is real and positive
and it turns out that it is majorized by  $\leq f'(0)$. Since
the absolute value of $g'(0)$ is equal to $h'(0)$ this means that
\[ 
|g'(z_0)|\leq f'(z_0)\tag{**}
\] 
for all $g\in\mathcal O(\Omega)$ such that
$g(\Omega)\subset D$. The uniqueness in Riemann's mapping theorem
entails  that 
equality holds in (**)  if and only if $g(z)= e^{i\theta}\cdot f(z)$ for some
$0\leq\theta\leq 2\pi$.
\medskip

\noindent
\emph{Remark.}
The mapping theorem above follows 
from the existence of conformal mappings between
special Jordan domains. Namely, 
a bounded and simply connected domain $\Omega$
can be exhausted by an increasing sequence of Jordan
domains, i.e. by  a sequence of closed Jordan
curves
$\{\Gamma_\nu\}$ which all are contained in $\Omega$
and  the Jordan domains $\{\Omega_\nu\}$
bounded by these curves
form an increasing sequence of relatively compact
regions of $\Omega$.
If  $z_0\in\Omega$
is given we can start with some $\Gamma_1$ so that 
$z_0$ lies in its interior. Suppose  we have found
Riemann's mapping function $f_\nu$
from $\Omega_\nu$
into $D$ where $f_\nu(z_0)=0$.
Now $\{f_\nu\}$ is a normal family of analytic functions
and there exists $f\in\mathcal O(\Omega)$ such that
$\{f_\nu\}$ converges uniformly to $f$ on every
compact subset of $\Omega$. It follows easily via
an application of Rouche's theorem
that $f$ is the mapping function for
$\Omega$.
So the   mapping theorem for simply connected
domains
is essentially a
result about conformal mappings from  Jordan domains to the unit disc.
Moreover, 
during the exhaustion  it  suffices to consider
Jordan curves which are piecewise linear. In this case
Schwarz and Cristoffell independently   gave
a formula for  the mapping function in  1868 which is
exposed in ¤ 5.
\medskip


\centerline {\emph{The case of unbounded domains.}}
\medskip

\noindent
If
$\Omega$ is a  simply connected domain in
${\bf{C}}$ which is not the whole plane
then the closed complement
${\bf{C}}\setminus \Omega$
contains at least two points, say $a$ and $b$. Now there exists
the multi-valued root function
\[
w(z) =\sqrt{\frac{z-a}{z-b}}
\]
Since
$\Omega$ is simply connected
there exists a single-valued branch of
$w$ in $\Omega$ and in ¤ 1:A we explain hos this gives
the existence of a conformal mapping from
$\Omega$ onto a simply connected
subset of the unit disc. In this way
Riemann's mapping theorem is  reduced to
the case when
$\Omega$ from the start is bounded.
\medskip


\noindent
\emph{Adding the point at infinity.}
Consider the
function:
\[
 f(z)= z+\frac{1}{z}
\]
which is meromorphic with a simple pole at the origin.
When $z= e^{i\theta}$ we have
\[ 
f(e^{i\theta})= 2\cdot \cos\,\theta
\]
The range as $0\leq\theta\leq 2\pi$
 is the real interval $[\vvv 2,2]$.
Introducing the point at infinity we set $\Sigma={\bf{C}}\cup \{\infty\}$
and then
$\Omega= \Sigma\setminus [\vvv 2,2]$
is a simply connected domain on the Riemann sphere.
If $z_1,z_2$ is a pair of distinct pints in
the punctured open disc
$\{0<|z|<1\}$
it is clear that
$f(z_1)\neq f(z_1)$. If
$w\in {\bf{C}}\setminus [-2,2]$
there exists a unique $z$ in this punctured disc such that
\[ 
z+\frac{1}{z}= w
\]
Indeed, $z$ is given by
\[ 
z= \frac{1}{2w}-\frac{1}{2w}\cdot \sqrt{w^2-4}
\]
where the  brancch of
$\sqrt{w^2-4}$ outside $[-2,2]$ is chosen so that it takes positive
real values when
$w$ is real and with absolute value $>2$.
Now $f$ yields a biholomorphic map between
$D$ and the simply connected
domain $\Omega$ where
$\zeta= \frac{1}{w}$ serves as local coordinate
at the point at infinity.
So here $f(0)= \infty$ and
$f$ is  a conformal mapping in Riemann's sense.
The  restriction of $f$ to $T$  yields a double cover onto
$[\vvv 2,2]$ which reflects the geometric fact that
this real segment as a boundary of the domain
$\Sigma\setminus [\vvv 2,2]$ has two sides, i.e. one can approach a point 
$\vvv 2<x<2$ from the above with $z=x+i\epsilon$ or  from below by 
$z=x\vvv i\epsilon$.
The conformal mapping $f$ is an example of
a map from $D$ onto a  parallell slit region which will be treated in ¤ 7.
The  example shows that
Riemann's mapping theorem 
applies when $D$ is replaced by other simply connected sets
which in general appear on the Riemann sphere
containing the point at infinity.



\bigskip




\noindent
{\bf 0.1 The equilibrium potential on plane curves.}
Riemann's mapping theorem for Jordan domains
was  predicted  
in electric engineering. Namely, let $\Gamma$ be a closed Jordan
curve
of class $C^1$.
Then one seeks 
a positive density function
$\mu$ on 
$\Gamma$  such that
the logarithmic potential
\[
\int_\Gamma\,\log\,\frac{1}{|z-\zeta|}\cdot
\mu(\zeta)\cdot |d\zeta|\tag{*}
\]


\noindent
is constant as $z$ varies in $\Gamma$.
The existence of  $\mu$ is
expected since
$\mu$ corresponds to 
an equilibrium density for an electric
field. It turns out that
$\mu$ is found  via the conformal mapping
function $f$ from the exterior domain bordered by
$\Gamma$ onto the exterior of the unit disc. 
In ¤ 9 we prove that:
\[
\mu(\zeta)=\frac{1}{|f'(\zeta)|}\tag{**}
\]
Moreover, the probability measure $\mu$ is unique
when one requires that
(*) is a constant on $\Gamma$.






\medskip

\noindent
{\bf{0.2 Solution by  Greens' functions}}. 
If $\Omega$ is a bounded Jordan domain
and  $z_0\in\Omega$ there
exists the unique
harmonic function $H(z)$ in $\Omega$ with  boundary function  
$\log\,|z-z_0|$.
Since $\Omega$ is simply connected  $H$ has a 
unique harmonic conjugate
$V$ in $\Omega$  normalized so that $V(z_0)=0$. Set

\[ 
f(z)=(z-z_0)e^{-(H(z)+iV(z))}
\]
Then $f$ gives the conformal mapping from $\Omega$ onto $D$.
We prove this result in Section XX.
\bigskip

\noindent
{\bf{0.3 Constructions of special conformal mappings.}}
Solving a mixed boundary value problem in
the unit disc
$D$ yield
conformal mappings  from $D$ onto
special image domains.
Namely, let $E$ and $F$ be a 
a pair of closed subsets on the unit circe $T$ where
each set is  a finite union of closed subintervals of
$T$. We also assume that
the sets are separated which
means that $T$ can be partioned into a pair of intervals
$J_1$ and $J_2$
whose intersection  is reduced to a pair of  points while $E\subset J_1$ and
$F\subset J_2$.
Now there exists the harmonic function $u$ in $D$
whose normal derivative $\frac{\partial u}{\partial n}$
vanishes on 
$T\setminus E\cup F$
while $u=1$ on $E$ and zero on $F$.
Let $v$ be the harmonic conjugate of $u$.
The Cauchy-Riemann equations entail that
the boundary function $\theta\mapsto v(e^{i\theta})$
stays constant on intervals in
$T\setminus E\cup F$ while it is strictly increasing on every
open subinterval of $E$, respectively strictly decreasing on
open subintervals of $F$.
In ¤ xx we shall learn that the analytic function
$f=u+iv$
yields a conformal mappiing from $D$ onto a domain $\mathcal R$
which consists of
 an open rectangle $\{ 0< x<1\}\times \{0<y<h\}$
from which a finite number of horisontal spikes 
have been   removed, i.e. closed vertical
line segments which
issue from one of the vertical sides and terminate at
some point in the open rectangle. See figure ¤ XX.
The positive integer $h$ depends on the pair $E,F$
and is referred to as the Neumann-Schwarz number
and denoted by $\mathcal {NS}(E,F)$.
In ¤ XX we expose Beurling's theory about extremal distances
which gives a  perspective upon these
numbers and their relation
to harmonic measures.




\medskip

\noindent
\emph{0.3.1 Comb domains.}
Let $\Omega$ be a simply connected open subset
of the half-plane
$\mathfrak{Re}\, z>0$.
It is called a comb domain if
\[
z=x+iy \in\Omega\implies
\{ tx+iy\,\colon 0<t\leq 1\}\subset \Omega\tag{1}
\]
The set $\{x=0\}\cap \partial\Omega$Êis called its base
and (1)  means that $\Omega$  is starshaped with respect to
the base which is a closed subset of
the imaginary axis and in general can
be unbounded.
In ¤ xx we   construct
conformal mappings from a  simply connected 
domain onto  comb domains with 
special properties.
So one often employs
constructions  via solutions to
mixed Neumann  boundary value problems.



 

\medskip





\noindent
{\bf{0.4 Koebe's function and the Bieberbach hypothesis.}}.
Locally conformal mappings whose range are
multiply connected domains and more generally 
Riemann surfaces leads to the uniformisation theorem
which is described in ¤ 0.6. It was proved in its full generality by
Koebe in 1907. His   proof 
employed a special conformal mapping defined by
\[ 
k(z)= \frac{z}{(1\vvv z)^2}
\]
We leave it as an exercise to show that
$k(z)$ is 1\vvv 1 in the open unit disc and hence  gives a conformal mapping
from $D$ onto a simply connected set which is unbounded since
$k(x)\to +\infty$ as $x$ is real and tends to 1.
The Taylor series of $k$ is given by:
\[ 
k(z)= z+2z^2+3z^3+\ldots
\]
Koebe's  $k$-function  led to a
conjecture  posed by Bieberbach in 1916
which goes as follows: Let
\[
 f(z)= z+\sum\uuu{n=2}^\infty\, a\uuu n\cdot z^n
\] 
give  a conformal mapping from $D$ onto some simply connected
domain. Bieberbach conjectured that
the coefficients $\{a\uuu n\}$ must satisfy
\[
|a\uuu n|\leq n\quad\colon  n=2,3,\ldots
\]
The affirmative answer to the Bieberbach conjecture was
established by de Branges in 1985.
The interested reader can consult [Bieberbach\vvv book]
for background and history how the proof was finally finished.
In addition to Bieberbach's article [Bieb:Acta] we refer to
Chapter XX in [Krantz] for a detailed  proof.
\medskip

\noindent
\emph {0.4.1 Baernstein's inequality.}
Koebe's function enjoys  other extremal properties.
The following result was proved in
[Acta:A. Baerenstein] in 1977:

\medskip

\noindent
{\bf{0.4.2 Theorem.}}
\emph{For every conformal mapping function $f(z)$ where $f(0)=0$ 
and $f'(0)=1$ one has the inequality}
\[
\int\uuu 0^{2\pi}\, |f(re^{i\theta})|\cdot d\theta\leq
\int\uuu 0^{2\pi}\, |k(re^{i\theta})|\cdot d\theta
\quad\text{for each}\quad 0<r<1
\]
\emph{where $k$ is Koebe's function.}
\medskip


\noindent
We shall not try to enter the proof  of Baerenstein's result which
requires an extensive excursion into variational techniques.
See also
the text\vvv book
\emph{Univalent functions} by P.I. Duren 
which treats extremal problems 
in connection with conformal
mappings.

\bigskip








\noindent
{\bf{0.5  Beurling's mapping theorem.}}
Equation  (**) in (0.1) suggests that if $g$ is a conformal map from
the unit disc $D$ onto a simply connected domain $\Omega$ then
there is a close interplay between the absolute
value of $|g'(z)|$  and  values of $g(z)$ when $z\to\partial D$.
A  result  about this correspondence
was proved  in  
[Beurling] where
the simply connected domain is not given in advance. Instead
one starts from  a positive
and bounded continuous  function
$\Phi(w)$ defined in the whole complex plane
such that
$\text{Log}\, \frac{1}{|\Phi|}$ is subharmonic.
Beurling proved that
there exists a unique analytic function $f$ in $D$
with $f(0)=0$
which
yields a conformal map from $D$ onto $f(D)$,
and satisfies the limit formula:
\[ 
\lim_{r\to 1}\,\, \max_{0\leq\theta\leq 2\pi}\,\,
\bigl[\bigl |f'(re^{i\theta})\bigr|-\Phi(f(re^{i\theta})\bigr]=0\tag{*}
\]
\medskip

\noindent
The proof in ¤ 11 is quite involved.
But  it is utmost   rewarding to pursue the
details which 
give  an  instructive
lessons how to  solve
problems in analytic function theory
using calculus of variation.


\bigskip




\centerline {\bf  {0.6 The uniformisation theorem.}}
\medskip


\noindent
Let $\Omega$ be a bounded and connected domain but 
not simply connected.
Then there does not exist a conformal mapping  from $\Omega$ onto $D$.
To compensate for this one considers 
\emph{multi-valued} functions on $\Omega$.
If  $z_0\in\Omega$ 
we defined the 
family $M_\Omega(\mathcal O)(z_0)$ in Chapter IV 
of germs of analytic functions at $z_0$ which
extend to multi-valued functions on $\Omega$.
When $f$ is such a germ and $z\in\Omega$ we denote by 
set $f^*(z)$  the  set of values taken by all the local
branches of $f$ at $z$.
We say that a germ
$f\in M_\Omega(\mathcal O)(z_0)$ gives a \emph{multi-valued 
and locally conformal map} from
$\Omega$ onto $D$ if the following hold:
\[ 
\widehat{f}(z_1)\cap \widehat{f}(z_2)=\emptyset
\quad\text{for all pairs}\,\, z_1\neq z_2\,\,\,\text{in}\,\,\, \Omega\tag{i}
\]
\[ \bigcup_{z\in\Omega}\, \widehat{f}(z)=D\tag{ii}
\]
In ¤ 1.B we  prove that for each point    $z_0$ in $\Omega$
there exists a unique germ 
$f$ as above which is normalised so that $f'(z_0)$ is real and positive
and $f(z_0)=0$. Moreover, 
$f$ solves an extremal problem. Namely, for 
every 
$g\in M_\Omega(\mathcal O)(z_0)$ such that
$g(0)=0$ and $\cup_{z\in\Omega}\, \widehat{g}(z)\subset D$ one has:
\[ 
|g'(z_0)|\leq f'(z_0)\tag{iii}
\]


\noindent
The uniqueness  has several consequences.
Namely  identify the fundamental
group $\pi_1(X)$
with homotopy classes of 
the family of closed curves at $z_0$.
To each  closed curve $\gamma$ in this family we perform
the analytic contonuation along $\gamma$ and
get the new germ
$T_\gamma(f)$ at $x_0$. The monodromy theorem from
Chapter IV entails that this  germ  only depends upon
the homotopy class
$\{\gamma\}$ and via the evaluation at $x_0$ one has a
map from $\pi_1(X)$
into $D$ defined by
\[
\{\gamma\}\mapsto T_\gamma(z_0)
\]
The uniqueness  above entails that
(*) is bijective which means that we 
have   identified 
$\pi_1(X)$ with a  subset of the open unit disc $D$.
Using Mšbious transformations 
we explain in ¤ xx how this identifies
$\pi_1(\Omega)$ with a group of Mšbius transforms on
$D$.
\medskip

\noindent
The existence of a multi-valued mapping
above was
established by Schwarz. But its full
 scope was
 put forward by PoincarŽ who used  the result above
 to construct 
 Fuchsian groups.
 For bounded and connected
 domains $\Omega$
 with infinitely many holes, i.e. when
 its closed complement has inifintely many connected
 components
 the
 fundamental group   is not finitely generated
 and
 the associated group of Mšbius transforms
 is therefore hard to describe.
 For nice multiple connected domains $\Omega$
 whose boundary consists of $p$ disjoint and closed Jordan¬curves for some
 $p\geq 2$ the situation is more favourable. Here
 $\pi_1(\Omega)$ is  free group 
generated by $p-1$ many closed loops and
the associated group of Mšbius transforms
is a more manageable Fuchsian group in PoincarŽ's sense.
However, in contrast to the simply connected
case
the equation about \emph{conformal equivalence} between
a pair of $p$-connected domains is a very subtle and 
leads to  \emph{moduli problems}
on
arbitrary Riemann surfaces. We refer to Chapter XX for a further account about this.




\bigskip


\centerline {\bf {0.7 Picard's theorem.}}

\medskip

\noindent
In 1879 Picard found the affirmative answer to a question
posed by Weierstrass. The result is that an entire function
$f(z)$ whose range excludes two values must be a constant.
Picard's  proof used the modular function.
A proof  which
does not use the modular function was  found by
Emile Borel in 1895. Inspired by Borel's methods,
Shottky and Landau established   
extensions of Picard's theorem.
For example, let $a_0$ and $a_1$ be two complex numbers
where $a_0$ is $\neq 0$ and $\neq 1$.
Then there exists a constant
$C(a_0,a_1)$ which depends on this pair only such that
the following hold: 
\medskip


\noindent
\emph{If
$f(z)$ is an analytic function in
some disc
$D_R$ of radius $R$ centered at the origin where
the range
$f(D_R)$ does not contain the two values 0 and 1 and the Taylor
series at $z=0$ starts with $a_0+a_1+\ldots$, i.e.
$f(0)=a_0$ and $f'(0)=a_1$, then}
\[ 
R\leq C(a_0,a_1)\,.
\]



\noindent {\bf{Remark.}} 
Using the modular function  the best possible constant
$C(a_0,a_1)$ is determined in ¤ 3.






\bigskip


\centerline
{\bf 0.8 Extension to the Boundary }
\medskip

\noindent
Let $\Omega$ be bounded and simply connected set
and 
$f$ is a conformal map from $\Omega$ onto the open unit disc
$D$. 
With no conditions on $\partial\Omega$
one cannot expect a continuous extension of
$f$.
But for those 
points $p$ on $\partial\Omega$ which  
can be reached by a Jordan arc which 
except for $p$
stays inside 
$\Omega$ there exist certain limits.
Such boundary points are called \emph{accessible} and  denote 
this set by $\mathcal A(\partial\Omega)$.
We will prove that $\mathcal A(\partial\Omega)$
is   dense in
$\partial\Omega$.
Next, for each
$p\in\mathcal A(\partial \Omega)$ we denote by
$\mathcal J(p)$ the family of Jordan arcs
$J$ where $p$ is an end-point while the
remaining part of $J$ stays in $\Omega$. 
So if $t\mapsto \gamma(t)$
defines $J$ then
$\gamma(t)\in\Omega$
when $0\leq t<1$ and $\gamma_J(1)=p$.
The image of $J\setminus \{p\}$ under $f$
is a half-open Jordan arc
in $D$  
defined by:
\[
t\mapsto \gamma^*(t)\quad\colon\quad
f(\gamma(t))=\gamma^*(t)\quad\colon 0\leq t<1\tag{i}
\]

\noindent
With these notations one has:

\medskip

\noindent
{\bf 0.8.1 Koebe's limit theorem.} \emph{For every $J\in\mathcal J(p)$
there exists the limit}
\[ 
\lim_{t\to 1}\,\gamma^*(t))
\]
\medskip

\noindent
The limit above is a point on
the unit circle which
depends on the pair $(p,J)$. It is  
denoted by $\mathcal{K}(J,p)$
and called the Koebe limit.
The second major result is due to Lindelšf.

\medskip

\noindent
{\bf 0.8.2 Lindelšf's separation theorem.}
\emph{Let $p\neq q$ be distinct points on $\partial\Omega$.
Then}
\[ \mathcal {K}(J,p)\neq\mathcal{K}(J',q)\quad\colon\quad
J\in\mathcal{J}(p)\quad\colon J'\in\mathcal{J}(q)
\]
\medskip

\noindent
Next, let $p\in\partial\Omega$
and consider some
$J\in\mathcal{J}(p)$.
Let $\{J_\nu\in\mathcal{J}(q_\nu)\}$
be a sequence of Jordan arcs with end points
$\{q_\nu\}$.
\medskip

\noindent
{\bf 0.8.3 Definition.} \emph{We say that the sequence $\{(J_\nu,q_\nu)\}$
converges to $(J,p)$Êif $q_\nu\to p$ and for every
$\epsilon>0$ there exists some
$\nu^*$ such that whenever $\nu\geq\nu^*$
there exists a Jordan
arc
$\gamma_\nu$ which is contained in the disc
$D_\epsilon(p)$ and has endpoints on $J$ and $J_\nu$.}
\medskip

\noindent
{\bf 0.8.4 Koebe's Continuity Theorem.}
\emph{If $(J_\nu,q_\nu)\to (J,p)$  it follows that}
\[ 
\lim_{\nu\to\infty}\,\mathcal{K}(J_\nu,q_\nu)=\mathcal{K}(J,p)
\]
\medskip

\noindent
Next, consider a pair
$J_1,J_2$ in $\mathcal{J}(p)$.
The  two Jordan arcs are 
\emph{asymptotically
linked} if there to every $\epsilon>0$ exists a 
Jordan arc $\gamma_\epsilon\subset D_\epsilon(p)$
whose end-points belong to $J_1$ and $J_2$ respectively.
Koebe's continuity theorem entails
\medskip

\noindent
{\bf 0.8.5 Proposition.} \emph{Let $J_1,J_2$ be a pair in
$\mathcal{J}(p)$ which are asymptotically linked.
Then one has the equality:}
\[
\mathcal{K}(J_1,p)=
\mathcal{K}(J_2,p)
\]
\bigskip

\noindent
The results above show that
if 
every pair of  Jordan arcs in $\mathcal J(p)$
are
asymptotically linked, then there exists a  Koebe
limit $\mathcal{K}\uuu f(p)$ defined as the common value of
$\mathcal{K}(J,p)$.
Let $\mathcal{A}\uuu *(\Omega)$
denote the set of such boundary points.
Together with Lindelšf's separation theorem this yields
an injective map from $\mathcal{A}\uuu *(\Omega)$ into the unit circle
$T$ defined by 
\[ 
p\mapsto\mathcal{K}\uuu f(p)\tag{*}
\]
\medskip

\noindent
\centerline{\bf 0.8.6 The case of Jordan domains.}
\medskip

\noindent
When $\Omega$ is a Jordan domain
a classic   result due to 
Camille Jordan asserts that every boundary point is accessible.
Moreover, a sharpended version of Camille Jordan's
theorem was proved by von Schoenflies in [vScH].

\medskip

\noindent
{\bf 0.8.7 Schoenflies' theorem.}
\emph{Let $\Omega$ be a Jordan domain. 
For each boundary
point $p$
the family of 
all Jordan arcs is in $\mathcal{J}(p)$
are asymptotically linked and
if 
$J\in\mathcal{J}(p)$ and  $\{(J_\nu,q_\nu)\}$
is a sequence such that
$q_\nu\to p$, then  the sequence
$(J_\nu,q_\nu)$ converges to $(J,p)$ in the sense of Definition  0.8.3.}
\bigskip

\noindent
{\bf 0.8.8 Conclusion.}
Koebe's Continuity Lemma and Schoenflies' result show that
when $\Omega$ is a Jordan domain then the Koebe-Lindelšf
map (*) above
is a continuous and bijective map from
$\partial\Omega$ into $T$.
Since both $\partial\Omega$ and $T$ are closed Jordan
curves this  implies that
$\mathcal K^*$ must be surjective.
Finally,  a continuous and bijective map between two compact sets
has a continuous inverse. Hence
the mapping function $f$  yields   a homeomorphism from
$T$ onto $\partial\Omega$ and as one easily sees $f$ 
actually  extends to
a continuous map from the closed unit disc $D$ onto the closed Jordan
domain $\bar\Omega$.
This  result for Jordan domains  is sometimes attributed to
Caratheodory but all   essential steps
in the proof rely upon the
results   above due to Jordan, von Schoenfliess,
Koebe and Lindelšf.
Caratheodory's contribution is   foremost his 
elegant proof of the uniformisation theorem for arbitrary
connected domains and certain  topological constructions
adapted
to   
the Koebe\vvv Lindelšf map (*)
for an arbitrary  simply connected domain.

\medskip

\noindent
{\bf 0.8.9 Smooth boundary points.}
Let $\Omega$ be a Jordan domain
and $f$ a conformal map from $D$ onto $\Omega$.
So now we have a homeomorphism
\[ 
e^{i\theta}\mapsto f(e^{i\theta})\quad\colon\quad
0\leq\theta\leq 2\pi
\]
The closed Jordan curve
$\partial\Omega$
has a  parametrisation
$t\mapsto\gamma(t)$ which may have  extra regularity.
A result in
the pointwise
differentiable case  was  presented by
Lindelšf  at the Scandinavian Congress of
Mathematics held at Institute Mittag-Leffler in 1916.
It goes as follows:
\medskip

\noindent
Let $p\in\partial\Omega$
and assume
that $\partial\Omega$ has a tangent line at $p$.
We can take   $p=1$  and
after a rotation in the complex $w$-plane 
also assume that the vertical line $\mathfrak{Re}(w)=1$
is tangent to $\partial\Omega$ at $p$.
This means that we can choose a parametrisation $\gamma(t)$
where we may translate $t$ and assume that
$\gamma$ is defined on some interval $[-A,A]$ with
$\gamma(-A)=\gamma(A)$ while $p=\gamma(0)$ and the differentiable
assumption  means that there exists some positive
real number $a$ such that
\[
\gamma(t)=1+iat+\text{small ordo}\,(t)\,\quad\colon\,t\to 0\tag{*}
\]
\medskip

\noindent
Let $g(z)$ be the  conformal mapping 
from  $D$ onto $\Omega$ normalised so that
$g(1)=1$.
When $\theta$ is close to zero we get a real-valued function
$\beta(\theta)$ such that
\[
g(e^{i\theta})=\gamma(\beta(\theta))\tag{**}
\]
We already  know that
the $\beta$-function is continuous.
But when (*) is added
Lindelšf proved the following result:
\medskip

\noindent {\bf{0.8.10 Theorem.}}
\emph{The $\beta$-function has an ordinary derivative at $\theta=0$.}
\medskip

\noindent
Moreover, Lindelšf  proved that
$f$ is locally conformal up to the boundary at $z=1$:
\bigskip




\noindent
{\bf 0.8.11 Theorem.}
\emph{Assume (*) above. Then there exists a positive constant
$B$ such that the following limits exist and are equal:}
\[ 
\lim_{\theta\to 0}\,
\frac{f(e^{i\theta})-1}{i\theta}=B\tag{i}
\]
\[
\lim_{s\to 0}\,\,
\frac{1-f(1-se^{i\alpha})}{s}=B\cdot e^{i\alpha}
\quad\colon\quad -\frac{\pi}{2}<
\alpha<\frac{\pi}{2}\tag{ii}
\]
\medskip

\noindent
{\bf 0.8.12 Remark.}
Caratheodory proved that  the   conformal property holds up to the boundary
in the more general case when
$p$ is a corner point, i.e. when (*) is replaced by the weaker 
assumption that the $\gamma$-function has one-sided derivatives
as $t$ decreases or increases to 0.
For a full account of various  results due to  Lindelšf and
Caratheodory we refer to Lindelšf's article in
[XX]. Here we are content to give a proof of
Theorem 0.8.10 in 
¤ XXX.
Regularity for higher order derivatives was
studied  by PainlavŽ in [Pain]  (when???) who
proved  that if
$\Omega$ is a Jordan domain
whose boundary curve
is of class $C^\infty$, then
a conformal map from $\Omega$ onto $D$ extends to a $C^\infty$-function from
the closure of $\Omega$ onto the closed unit disc.
\bigskip


\noindent
\centerline
{\bf{0.8.13 Properties of the inverse map $f^{-1}$.}}
\medskip

\noindent
Above we discussed the boundary behaviour of the conformal map from
a bounded simply connected
domain $\Omega$ onto the open unit disc.
Let us  instead consider the inverse function
$\phi=f^{-1}$, i.e. now $\phi$ is a conformal map from
$D$ onto $\Omega$. 
The
Brothers
Riesz theorem shows that $\phi$ has radial limits almost everywhere
and.  Actually the failure of radial limits is confined to a smaller set
because the area integral
\[
\iint \uuu D\, |\phi'(z)|^2\dot dxdy<\infty
\]
We can  therefore apply a result due to
Beurling from
Special Topics ¤ XX which shows that
radial limits exist outside a subset of $T$ whose outer 
logarithmic capacity is zero.
One can continue to analyze
further regularity of 
$\phi$.
First we introduce the following:

\medskip

\noindent
{\bf{0.8.14 Angular derivatives
at the boundary}}.
Consider some  $e^{i\theta}\in T$ 
where the radial limit exists:

\[
\lim_{r\to 1}\,\phi(re^{i\theta})=p\tag{1}
\] 
Results about Fatou limits for bounded
analytic functions imply 
that
$\phi$  has a limit in every Fatou sector
having $e^{i\theta}$ as a corner point.
Consider the argument of the difference quotients
\[
z\mapsto \text{arg}\bigl(\frac{\phi(e^{i\theta})-\phi(z)}{e^{i\theta}-z})\tag{2}
\]
If (2) has a limit when
$z\to 1$ in the sense of Fatou we 
say that $\phi$ is conformal at $e^{i\theta}$.
For example, if $\theta=0$ so that $e^{i\theta}=1$
we require that for every
$0<\delta<\pi/2$ there exists the limit
\[
\lim_{s\to 0}\,
\text{arg}\bigl[\,\frac{\phi(1)-\phi(1-s\cdot e^{i\alpha})}
{s\cdot e^{i\alpha}}\,]\tag{3}
\]
uniformly with respect to
$\alpha$ provided that
$\pi/2-\delta\leq\alpha\leq \pi/2-\delta$.
We can also consider the complex differences
without introducing their arguments and
say that $\phi$ has an 
\emph{angular derivative} at $e^{i\theta}$
when
\[
z\mapsto \frac{\phi(e^{i\theta})-\phi(z)}{e^{i\theta}-z}\tag{4}
\]
has a Fatou limit as $z\to e^{i\theta}$. The limit is then called the angular derivative
of
$\phi$ and  denoted by $\phi'(e^{i\theta})$.
If $\phi'(e^{i\theta})\neq 0$ it is clear that
(2) also  has a limit, i.e.
the existence of a non-zero angular derivative implies that
$\phi$  is conformal at $e^{i\theta}$.
Results
about  angular derivatives
are  due to Ostrowski in his article
[Ost] from 1937. It  
would take us to far to describe this in detail and 
instead we refer
to the  text-book
[Marshall-Garnett where  Chapter V.5
contains  a detailed account  of
Ostrowski's results.
Roughly speaking   angular 
derivatives and conformality at boundary points
are expressed via
geometric conditions of $\Omega$ and a boundary
point $p$ which to begin with can be reached 
from a radial limit (1) above.
In [loc.cit] the reader also finds
an exposition of more recent results which
give conditions for the existence of angular
derivatives
using conditions which
rely upon various
extremal metrics.
\medskip

\noindent
{\bf{Remark.}}
See also
the article 
\emph{Angular derivatives and Lipschitz majorants}
by D.E. Marshall, available on-line at
http:// math.washington.edu/- marshall/personal. html.
\bigskip





















\bigskip




\centerline {\bf 0.10 Comments on other sections.}
\bigskip


\noindent
In section 4 we prove Koebe's \emph{"One Quarter Theorem"} 
together with  the 
\emph{Area Theorem}
and Koebe's \emph{Verzerrungssatz}.
¤ 5 is devoted to the construction of conformal maps 
from the unit disc onto convex polygons. 
In ¤ 7  we construct  conformal maps between
multiple connected domains using certain harmonic functions
and  ¤ 8 is devoted to 
the \emph{Bergman kernel}.where we prove a result due to Carleman about
the asymptotic behaviour of the kernel function with a sharp
remained term for Jordan domains whose boundary curve is real\vvv analytic.
In ¤ 10
we 
prove 
a result due to Koebe
about conformal mappings between  domains which are bordered
by circles. In ¤ 11 we prove the Riemann-Schwarz inequality for
geodesic curves with respec to metrics with non-positive curvature.

\bigskip










\newpage

\centerline{\bf I:A.  Riemann's mapping theorem for  simply connected domains}
\bigskip


\noindent
The family of 
simply connected domains were described by
Schwarz  in the article  
[Schwarz]   from 1869.
\medskip

\noindent
\emph{
The following are equivalent for an open subset $\Omega$ 
of ${\bf{C}}$ }:
\medskip
\[
{\bf{C}}\setminus\Omega\,\,\,\text{has no compact connected components}\tag{1}
\]
\[
\text{For every closed curve}\,\,
\gamma\,\,\text{inside}\,\,\Omega\implies\,\mathfrak{w}_\gamma(a)=0
\quad\colon\, a\in {\bf{C}}\setminus \Omega\tag{2}
\]
\[
\text{Any}\,\, f\in\mathcal O(\Omega)\,\,\, \text{has a primitive}\tag{3}
\]
\[
\text{If}\,\, f \in\mathcal O(\Omega),\,\text{has no zeros
there exists}\,\, g\in\mathcal O(\Omega)\quad\colon\, f= e^g\tag {4}
\]
\[
\text{If}\,\, f \in\mathcal O(\Omega),\,\text{has no zeros
there exists}\,\, h\in\mathcal O(\Omega)\quad\colon\, f= h^2\tag {5}
\]
\medskip

\noindent
{\bf Remark.}
The reader should contemplate upon these conditions
and  prove they are equivalent.
See also  [Nah: page 151-153] which gives a
detailed proof of  the equivalence between (1-5).
When $\Omega$ satisfies the equivalent conditions above we say that it is
simply connected.
The case $\Omega={\bf{C}}$ is excluded. A
punctured complex plane ${\bf{C}}\setminus\{a\}$ which arises when a single point is removed is obviously not simply connected.
So when $\Omega\neq {\bf{C}}$  is simply connected then
the boundary $\partial\Omega$ contains at least two points.
This will be used below to establish 
Riemann's mapping theorem.
Let us remark that
the subsequent proof   is due to FejŽr and F. Riesz.

\medskip


\noindent
{\bf{A.1 Reduction to bounded domains.}}
Let $\Omega\neq {\bf{C}}$ be simply connected.
Above we have seen that there exists two distinct points
$a$ and $b$ in its closed complement.
Consider the function
\[
w(z)=\sqrt{\frac{z-a}{z-b}}\tag{i}
\]
From (5) in the list by Schwarz 
there exists a
\emph{single valued} branch of this root function
which we denote by $w^*(z)$, i.e. here $w^*\in\mathcal O(\Omega)$.
Let $z_0\in\Omega$ and put $w^*(z_0)=c$.
Since we have chosen a branch of the square root function
it follow that $w^*(z)$ never attains the value $-c$.
Moreover, since the complex derivative of $w^*$ is $\neq 0$
there exists an open  disc $\Delta$ centered at $c$
which is disjoint from the disc $-\delta$ centered at $-c$, and an open
neighborhood $U$ of $z_0$ such that
$w^*\colon\, U\to \delta$ is biholomorphic.
It follows that the image $w^*(\Omega)$ has empty intersection with
$-\Delta$. So if $r$ is the radius of $\Delta$ we conclude that
\[ 
|w^*(z)+c|\geq r \quad\text{for all}\quad  z\in\Omega
\]
We conclude that
$\frac{1}{w(z)-c}$ yields a conformal map from
$\Omega$ onto a bounded simply connected set $U$.
Since the composition of two conformal maps is conformal
there only  remains only to prove Riemanns Mapping Theorem for $U$.
So from now on we assume that $\Omega$ is bounded and proceed with the proof.
\medskip

\noindent
{\bf{A.2 Proof of uniqueness}}.
Let us prove
that the mapping function is \emph{unique} if it exists.
For suppose that $f$ and $g$ are two conformal mappings from
$\Omega$ onto $D$ where  $f(z_0)=g(z_0)=0$ and both $f'(z_0)$ and 
$g'(z_0)$ are real and positive.
Now there exists the inverse mapping function $g^{-1}$ from $D$ onto $\Omega$
and we set
\[ 
\phi=f\circ g^{-1}
\]
Then $\phi$ yields a conformal mapping of
$D$ onto itself where $\phi(0)=0$. As explained in XX
it follows that $\phi(z)=az$ for a constant $a$ with
$|a|=1$. Here

\[ 
a=\phi'(0)=\frac{f'(z_0)}{g'(z_0)}
\]
Since both $f'(0)$ and $g'(0)$ are real and positive we get
$a=1$. So $\phi(z)=z$ is the identity map and 
$f=g$ follows.


\newpage

\noindent
{\bf{A.3 Proof of Existence.}} Set
\[ 
\mathcal F=\{f\in\mathcal O(\Omega)\quad\colon\,f(z_0)=0\quad f(\Omega)
\subset D\quad\colon\, f\,\,\text{is 1-1}\}\tag{i}
\]
Thus, each $f\in\mathcal F$ gives a conformal map from $\Omega$ into some open 
subset of $D$. There remains to find some $f$ such that $f(\Omega)=D$.
To attain this we put
\[ 
M=\max_{f\in\mathcal F}\,|f'(z_0)|\tag{ii}
\]
Here $M$ is finite since there exists $r>0$ such that the disc
$D_r(z_0)\subset\Omega$ and   Schwarz'  inequality gives
$|f'(z_0)|\leq\frac{1}{r}$ for each $f\in\mathcal F$.
Next, by the Montel Theorem in XXX, the family
$\mathcal F$ is  \emph{normal} in
$\mathcal O(\Omega)$. Hence   we
can find
$f\in\mathcal F$ such that $|f'(z_0)|=M$.
Multiplying $f$ with some $e^{i\theta}$ we may assume that
$f'(z_0)=M$.
There remains to show that $f(\Omega)=D$. Assume the contrary, i.e. suppose
there exists $a\in D\setminus f(\Omega)$.
Put
\[ 
\phi(z)=\frac{f(z)-a}{1-\bar a f(z)}\tag{iii}
\]
Since a Mšbius transform is a conformal map on $D$, it follows that
$\phi(\Omega)\subset D$. Moreover, $\phi\neq 0$ 
and by (4) in the list by Schwarz there exists
an analytic function $F(z)$ in $\Omega$
such that
\[ 
F(z)=\text{Log}[\,\frac{f(z)-a}{1-\bar a f(z)}]\in\mathcal O(\Omega)\quad
\colon\quad\mathfrak{Re}(F(z))<0\quad z\in\Omega\tag{iv}
\]
It is clear that
$F$  yields a conformal mapping from
$\Omega$ into an open  subset of the left half-plane
$\mathfrak{Re}(w)<0$. Next, consider the function
\[
G(z)=\frac{F(z)-F(z_0)}{F(z)+\bar F(z_0)}\tag{v}
\]
Since $F(z)$ and $F(z_0)$ belong to the same half-plane
$\mathfrak{Re}(w)<0$
we see that
the absolute value of $G$ is $<1$ for every $z\in\Omega$ and
conclude that $G$ yields a conformal mapping from
$\Omega$ into $D$. Now  $G(z_0)=0$ and by the maximal property of $M$
we get a contradiction if we have proved the strict inequality:
\[
|G'(z_0)|>M\tag{vi}
\]
To prove (vi) we notice that
\[ 
G'(z_0)=\frac{F'(z_0)}{F(z_0)+\bar F(z_0)}\tag{vii}
\]
Next, the construction of the Log-function $F$ gives
\[
F(z_0)+\bar F(z_0)=2\mathfrak{Re}\,F(z_0)= 2\,\text{Log}\,|a|\tag{vii}
\]
Moreover, since $f(z_0)=0$ a derivation of the Log-function $F$ gives
\[
F'(z_0)=f'(z_0)(1-|a|^2)=M(1-|a|^2)\tag{viii}
\]
Putting this together we obtain
\[
G'(z_0)=M\cdot\frac{1-|a|^2}{2\,\log\,|a|}\implies
|G'(z_0)|=M\cdot\frac{1-|a|^2}{2\,\log\,\frac{1}{|a|}}\tag{ix}
\]
Here $|a|<1$. A trivial verification which is left to the reader shows that
\[
1-|a|^2)>2\,\log\,\frac{1}{|a|}\quad\colon 0<|a|<1
\]
Hence 
we have found $G\in\mathcal F$ with $|G'(z_0)|>M$. This is a contradiction and  hence we must have $f(\Omega)=D$
which finishes the proof of Riemann's Mapping Theorem.


\bigskip


\centerline {\bf {A.4 Other  extremal properties.}}
\medskip

\noindent
Let $\Omega$ be simply connected and assume that
$0\in\Omega\subset D$.
Let $f^*\colon\Omega\to D$
be the conformal mapping with $f^*(0)=0$ 
and its derivative at 0 is real and positive.
Then the following hold:
\medskip

\noindent
{\bf{A.5  Theorem.}}
\emph{For every point
$a\in \Omega$ one has:}
\[
[f^*(a)|=\max_f\,|f(a)|\quad\colon\,
f\in\mathcal O(\Omega)\,\quad\colon\, f(0)=0\quad\text{and}\quad
f(\Omega)\subset D\tag{*}
\]
\medskip

\noindent
To prove (*) we use the inverse map $\phi\colon\,D\to\Omega$ 
which satisfies
\[
f^*(\phi(w)=w\quad\colon\quad w\in D\tag{i}
\]


\noindent
Next, consider some  
$f\in\mathcal O(\Omega)$ as above.
Since $f(0)=0$ and $\Omega\subset D$
we get
$f\circ\phi\in\mathcal O(D)$. This analytic function in
$D$  is zero at the origin and has
maximum norm
$\leq 1$. Hence Schwarz inequality gives:
\medskip
\[
|f(\phi(w))|\leq |w|\quad\colon\,w\in D\tag{ii}
\]
With $a\in\Omega$ we pick $w\in D$ so that $\phi(w)=a$ and then (i-ii) give
\[
|f(a)|\leq |w|=|f^*(a)|
\]
Since this hold for every $f$ as above we get (*).
\medskip

\noindent
{\bf{A.6 A result for Jordan domains.}}
Assume that $\Omega$ is a Jordan domain
bordered by a rectifiable closed Jordan curve $\Gamma$.
Given $a\in \Omega$ we denote by 
$\mathcal F_a$ the family of
analytic functions $g(z)$ in $\Omega$ such that
$g(a)=0$ and the complex derivative $g'(z)$ extends to
a continuous function on $\Gamma$ and
\[ 
\int_\Gamma\ |g'(z)|\cdot |dz= 2\pi\tag{*}
\]
This means that the total length of the image curve
$g(\Gamma)$ is $2\pi$.
Now one seeks
\[
\max_g\, |g'(a)|\quad\colon\, g\in\mathcal F_a\tag{**}
\]
\medskip

\noindent
{\bf{Theorem A.7 }}
\emph{The maximum in (**) is attained by the conformal map
from $\Omega$ onto $D$ which sends $a$ to the origin.}
\medskip

\noindent
The proof is left as an exercise. The hint is to study the family
$g\circ\phi$ where $\phi$ is the conformal map from $D$ into
$\Omega$ which sends the origin to $a$.  



\bigskip

\centerline {\bf {B. The mapping theorem
for  multiply connected sets.}}
\bigskip

\noindent
Let $\Omega$ be an open   and  connected subset
of ${\bf{C}}\setminus\{0,1\}$.
For each point $z_0\in
\Omega$ we have the family
$M_\Omega\mathcal (z_0) $
of germs of analytic functions at
$z_0$ which extend to multi-valued functions in
$\Omega$. 
If 
$f\in M_\Omega\mathcal O(z_0)$
and 
$z\in \Omega$ we denote by
 $ \widehat{f(z)}$ the set of values taken by
all   local branches of $f$, i.e. with the notations from
¤ xx:
\[
 \widehat{f(z)}=\{ T_\gamma(f)(z)\,\colon \gamma\in\mathcal C(z_0,z)\}
 \]
 where 
$\mathcal C(z_0,z)$ is the family of curves with end-points at
$z_0$ and $z$. We set

\[
 \mathcal D_f= \bigcup_{z\in\Omega}\,  \widehat{f(z)}
\]
and refer to this as the total range of $f$.
Next, denote by
$M_\Omega\mathcal O(z_0)^*$ the set of all
$f\in M_\Omega\mathcal O(z_0)$ such that
$f(z_0)=0$ and
\[ 
 \widehat{f(z_1)} \cap \widehat{f(z_2)}=\emptyset\quad\colon z_1\neq z_2\tag{*}
\]


\noindent
{\bf{Remark.}}
In ¤¤ we construcuted the modular function
$\mathfrak{m}$ in ${\bf{C}}\setminus\{0,1\}$ which by construction
is multi-valued and satisfies the separation condition (*).
If $\phi$ is a conformal maping from the upper half-plane onto
$D$, then
$\phi\circ \mathfrak{m}$ has total range $D$.
Next, when $\Omega\subset{\bf{C}}\setminus\{0,1\}$
we can restrict $\mathfrak{m}$Êto $\Omega$
where it again becomes a multi-valued function
and after a suitable Mšbius transform on $D$
the reader can conclude that
the 
$M_\Omega \mathcal O((z_0)^*$ is non-empty
for every $z_0\in\Omega$.



\medskip

\noindent
{\bf{The  inverse function $W_f$}}.
Let $f$ be given in
$M_\Omega\mathcal O(z_0)^*$ and put
\[ 
\mathcal D_f=\bigcup_{z\in\Omega}\, \widehat{f(z)} 
\]
Notice that 
(*) implies that for each $w\in \mathcal D_f$ there exists
a unique point $z(w)\in\Omega$ and a local branch $T_\gamma(f)\in
\mathcal O(z(w))$ such that 
\[
T_\gamma(f)(z(w))=w\tag{i}
\]
This gives a map
\[ 
W_f\colon \mathcal D_f\to \Omega
\]
\medskip

\noindent
{\bf{B.0 Lemma.}} \emph{$W_f$ is an analytic function in
$\mathcal D_f$.}
\medskip

\noindent
\emph{Proof.}
Let $w_0\in\mathcal D_f$
which gives a pair $(z_0,\gamma)$ such that (i) holds above.
Now
$T_\gamma(f)$ is analytic function in a small open
disc
$U$ centered at $z(w_0)$.
If $z\in U$ we have  $T_\gamma(f)(z)|in\widehat{f(z)}$
and the separation condition (*)
implies that
$z\mapsto T_\gamma(f)(z)$ is 1-1 in $U$, i.e.
the germ $T_\gamma$ is locally conformal.
In particular the range $T_\gamma(U)$ is an open
set which contains $w_0$
and by the construction of $W_f$ we see that
its restriction to
$T_\gamma(U)$ is the inverse of the conformal apping
$T_\gamma\colon U\to T_\gamma(U)$ which proves Lemma B.0.

\medskip



\noindent
Now we announce the uniformisation theorem 
for $\Omega$ where
$D$ is the open disc.
\medskip



\noindent
{\bf{B.1 Theorem.}} \emph{There exists a unique $f\in M_\Omega\mathcal O(z_0)^*$
such that $f'(z_0)$ is real and positive and $\mathcal D_f=D$.
Moreover one has the inequality:}
\[ 
|g'(z_0)|\leq f'(z_0)\tag{B.1.1}
\]
\emph{for all germs $g\in M_\Omega\mathcal O(z_0)$ 
where $g(z_0)=0$ and
$\mathcal D_g\subset D$.}


\medskip

\centerline{\emph{Proof of Theorem B.1}}
\medskip

\noindent
Let us first prove the inequality (B.1.1).
First, the conditions on $f$ give map 
$W_f\colon D\to \Omega$ and by Lemma
B.0 we have $W_f\in\mathcal O(D)$.
Next, with $g$ as above the general result in ¤ xx entials that
we get an analytic function $G$ in $D$
such that
\[ 
G(w)=g(W_f(w))
\]
holds in a small disc $\{|w|<\delta\}$.
Taking the complex derivative at $w=0$ we get
\[
G'(0)=g'(z_0)\cdot W_f'(0)\tag{i}
\]
At the same time
\[ 
W_f(f(z))= z
\]
 holds in a disc
$\{|z-z_0|<\epsilon\}$ which entails that
\[
W_f'(0)=\frac{1}{f'(z_0)}\tag{ii}
\]
Next, we have $G(0)=0$ and since
$\mathcal D_g\subset D$
holds we also have the inclusion $G(D)\subset D$, i.e.
the maximum norm of $G$ in $D$ is $\leq 1$.
Schwarz's inequality applied to $G$ gives
$|G'(0)|\leq 1$ and then (i-ii) give (B.1.1).
\medskip

\noindent
\emph{The uniqueness  of $f$.}
Suppose that  $f$ and $g$ both belong to
$M_\Omega\mathcal O(z_0)^*$
and $\mathcal D_f=\mathcal D_g=D$.
Now we can apply (B.1.1) starting with $f$ or $g$
and first conclude that
\[
|g'(z_0)|= |f'(z_0)|\tag{iii}
\]
Starting with $f$ we get
from the above  the analytic function $G$
and (iii) entials that
$[G'(0)=1$ which
by Schwarz' reversed principle implies that
$G(w)= e^{i\theta}\cdot w$ for some
$\theta$. Do of both
$f'(0)$ and $g'(0)$ are real and positive we have
$G(w)=w$ which implies that
the two germs $f$ and $g$ are the same.
\medskip

\noindent
\emph{The existence  of $f$.}
The  multi-valued version of Montel's theorem
in XXX shows that  family
$M_\Omega\mathcal O(z_0)^*$
is a normal. Hence we can solve a variational problem
where the derivatives at $z_0$
are maximized and find
$f\in M_\Omega\mathcal O(x_0)$ such that
$f'(z_0)$ is real and positive and (B.1.1) holds.
There remains to prove the equality
\[
\mathcal D_f=D
\]
Assume the contrary, i.e. suppose there exists some
$a\in D\setminus \mathcal D_f$.
Next, 
multi-valued functions compete in the variational problem
and we consider
the log-function
\[ 
F(z)=\log\, \frac{f-a}{1-\bar a\cdot f}\tag{i}
\]
This germ at $z_0$ extends to a multi-valued analytic function in
$\Omega$. Moreover,  since  $\log$-functions
only add integer multiples of $2\pi i$ we have
\[
\mathfrak{Re}\, F=\log\, |\frac{f-a}{1-\bar a\cdot f}|<0
\]
where the last inequality holds since
$\mathcal D_f\subset d$.
hence the essential range f$F$ is contained in
the half-space
$\{\mathfrak{Re}\, w<0\}$. Set
Next, set
\[ 
G=\frac{F-F(z_0)}{F+\bar F(z_0)}\tag{ii}
\]
From the above  the 
essential range of $G$ is contained in
$D$ so by the extremal property of $f$ gives
\[
|G'(z_0)|\leq f'(z_0)\tag{iii}
\]
Now a
repetition of the proof in 1.1 leads to a contradiction, i.e. one
verifies (i-ii) imples that
$|G'*(x_0)|>|f'(x_0)|$ which contradicts (iii).
Hence $\mathcal D_f=D$ and which completes  the proof of existence in
Theorem B.1.




\newpage







\bigskip









\centerline{\bf\large II. Boundary behaviour}
\bigskip

\noindent
First we study arbitrary bounded analytic functions
and establish some  results due to
Lindelšf and Koebe.
Let $D$ be the open unit disc
and $T$ the unit circle.
Let
$\{\omega_\nu\}$ and 
$\{\omega^*_\nu\}$ be two sequences in $D$
which converge to  different points $p$ and $q$ on the unit circle
$T$ and $\{\gamma_\nu\}$
is
a sequence
of Jordan arcs
which are contained  in $D$
and connect 
$\omega_\nu$ with $\omega^*_\nu$ for each $\nu$.
Moreover, we assume  that:
\[
\lim_{\nu\to\infty}\,\min_{z\in\gamma_\nu}\,|z|=1\tag{*}
\]
Thus, the joining Jordan arcs  stay close to the unit circle
$T$ as $\nu$ increases.
\medskip

\noindent
{\bf 2.1 Koebe's Lemma} \emph{Let $f$ be a bounded analytic function
in
$D$ such that
the maximum norms of $f$ on
$\gamma_\nu$ tend to zero as $\nu\to\infty$. Then
$f$ must be identically zero.}

\medskip

\noindent
{\emph{Proof}}.
By continuity we may assume that
the joining arcs $\gamma_\nu$ are polygons.
After a rotation we may assume that $\omega_\nu\to 1$
and $\omega^*_\nu\to e^{i\theta^*}$
for some $0<\theta^*<\pi$.
Given $\nu$ we have 
$\omega_\nu=r_\nu e^{i\theta_\nu}$
and
$\omega^*_\nu=r^*_\nu e^{i\theta^*_\nu}$.
While drawing the Jordan arc $\gamma_\nu$ from $\omega_\nu$ to
$\omega_\nu^*$ we encounter the last point
$\xi_\nu\in\gamma_\nu$ whose argument is
$\theta_\nu$ and after the first point $\eta_\nu\in\gamma_\nu$
whose argument is $\theta^*_\nu$.
Replace the pair $\omega_\nu,\omega_\nu^*$
with $\xi_\nu,\eta_\nu$
which then are joined by a simple polygon
$\Gamma_\nu$ which except for its end-points
stay in the circular sector where
$0<\text{arg}(z)<\theta^*$.
To each $\nu$ we therefore get a domain
$U_\nu$ bordered by $\Gamma_\nu$ and the two 
rays from the origin to $\xi_\nu$ and $\eta_\nu$.
By the hypothesis the maximum norms
\[
M_\nu= \max_{z\in\Gamma_\nu}\,
|f(z)|\tag{i}
\]
tend to zero as $\nu\to\infty$.
At the same time the assumption in (*) above gives
\[
\min_{z\in\Gamma_\nu}\, =\rho_\nu
\quad\,\text{where}\,\,\rho_\nu\to 1
\]

\medskip
\noindent
Since $f$ is assumed to be bounded in $D$
and without loss of generality we may assume that
the maximum norm $|f|_D\leq 1$.
Now we will finish the proof is  using
results from XXX applied to the subharmonic function
$log\,|f|$.
Namely, we have
$\theta_\nu\to 0$ and $\theta_\nu^*\to\theta^*$ with
$0<\theta^*<\pi$ and may assume that
$\rho_nu>3/4$.
So when $\nu$ is large we get
\[ 
z_*=\frac{1}{2}\cdot e^{i\theta^*/2}\in U_\nu
\]
Next,
let $U_\nu^*$ be the circular sector bordered by the two rays
which pass through $\xi_\nu$ and $\eta_\nu$ and
put $\gamma^*_\nu= T\cap\partial U_v$. Let
$\mathfrak{m}_{\gamma_\nu^*}^*(z_*)$ be the harmonic
measure at $z_*$ with respect to the boundary arc
$\gamma_\nu^*$  of the circular sector.
Then there is a fixed constant $a>0$ such that
\[
\mathfrak{m}_{\gamma_\nu^*}^*(z_*)\geq a\quad\colon
\forall\,\nu
\]
At the same time  Carleman's  majorant principle for harmonic measures gives:
\[
\mathfrak{m}_{\gamma_\nu^*}^*(z_*)\leq
\mathfrak{m}_{\Gamma_\nu^*}^*(z_*)
\]
where the right and side is the harmonic measure at $z_*$
in the domain $U_\nu$.
Regarding the subharmonic function
$\log\,|f|$ we obtain
\[
\log\,|f(z\uuu *)|\leq a\cdot \log(M_\nu)
\]
By (i) the right hand side tends to $-\infty$ and hence
$f(z_*)=0.$ We can  achieve a similar 
vanishing for points in a small disc centered at $z_*$. So by analyticity
$f$ is identically zero in $D$ and Koebe's Lemma is proved.

\bigskip
\noindent
{\bf 2.2. Lindelšf's Theorem.} 
\emph{Let $J_1$ and $J_2$ be two Jordan arcs in $D$
with a common end-point $p\in T$.
Let  
$f\in\mathcal O(D)$ be bounded 
and assume that it
has a limit along both $J_1$ and $J_2$, Then the
two limit values are equal.  
Moreover, if two Jordan arcs
are disjoint then $f(z)$
converges to the  common limit value
when $z$ tends to  $p$  inside the domain bordered by
$J_1$ and $J_2$.}

\newpage



\centerline{\emph{ Proof of Lindelšf's theorem}}
\bigskip

\noindent
Let $a$ be the limit of $f$ along $J_1$
and $b$ the limit along $J_2$.
If the  curves $J_1$ and $J_2$ 
intersect at some sequence
of points $\{z_\nu\}$ which tends to $p$, then
we immediately get $a=b$.
So we may assume that $J_1$ and $J_2$ do not intersect in the open disc $D$,
i.e. their sole common point is $p$.
After a rotation we may take $p=1$. When $\delta>0$ we consider the line
$L$ defined by $\mathfrak{Re}(z)=1-\delta$
where $\delta>0$ is small.
On $J_1$ we find the 
last point $\xi$ which intersects $L$ and similarly the last point
$\eta$ on $J_2$.
We get the domain $G_\delta$ bordered by
the portions  $ \Lambda_1\subset  J_1$ and 
$\Lambda_2\subset J_2$ where
$\mathfrak{Re}(z)>1-\delta$
and the  line segment which joins $\eta$ and $\xi$
on $L$. Put

\[
F(z)=(f(z)-a)(f(z)-b)
\]
By the assumption on $f$
the maximum norm of $F$ tends to zero on
both $\Lambda_1$ and $\Lambda_2$.
At the same time $F$
is a bounded analytic in the whole disc $D$
and put  $M=|F|\uuu D$.
Now 
we  apply the reflection construction by Schwartz from XX
and conclude that the maximum norm
\[ 
|F|_{\partial G_\delta}\leq\sqrt{M}\cdot 
\sqrt{
|F|_{\Lambda_1}+
|F|_{\Lambda_2}}
\]
Hence $F$ converges to zero in $G_\delta$ as $\delta\to 0$.
By the construction of $F$ this means that $f$ must  tends to $a$ or
to $b$ uniformly in $G_\delta$ as $\delta\to 0$.
But then it is obvious that $a=b$ and at the same time
we have proved that
$f$ converges to this common number
in the domain bordered by $J_1$ and $J_2$
as we approach $p$. This finishes the proof of Lindelšf's theorem.
\bigskip



\centerline{\bf 2.3 Proof of Theorem 0.6.1}
\medskip

\noindent
Let $f\colon\Omega\to D$ be a conformal map. Let $p\in\partial\Omega$
and consider some Jordan arc
$J\in\mathcal J(p)$.
Put $w=f(z)$ so that $w\in D$.
Let $J$ be defined by
$t\mapsto\gamma(t)$. 
In $D$ 
we get the image arc
\[
t\mapsto f(\gamma(t))\quad\colon\quad 0\leq t<1\tag{ii}
\]
Denote it by $J^*$. We must
prove that $J^*$ tends to a  point  $e^{i\theta}\in T$, i.e. 
\[
\lim_{t\to 1}\,f(\gamma(t))=e^{i\theta}\tag{iii}
\]
Assume the contrary. Then we obtain 
two sequences  of points in $D$:
\[
q_\nu=f(\gamma(t_\nu))\quad\colon\quad
s_\nu=f(\gamma(\tau_\nu))\quad\colon\quad
t_1<\tau_1<t_2<\tau_2\ldots\tag{iii}
\] 
where $t_\nu$ and $\tau_\nu$ both tend to 1 and
a pair of \emph{distinct} points $q^*,s^*$ on $T$
such that
\[
q_\nu\to q^*\quad\colon\quad
s_\nu\to s^*\tag{iv}
\]

\noindent 
Next, to each
$\nu$ we get the image curve in $D$ given by
\[
\gamma_\nu^*=f(\gamma[t_\nu,\tau_\nu])\tag{v}
\]
which joints $q_\nu$ with $s_\nu$.
Now we regard the inverse
function $g=f^{-1}$ which is a bounded
analytic function in $D$.
Here
\[
\lim_{t\to 1}\, |g(f(\gamma(t))-p|=0\tag{vi}
\]
With $h(z)=g(z)-p$ it follows that
\[
\lim_{\nu\to\infty}\, \max_{z\in\gamma_\nu^*}\, |h(z)|=0\tag{vii}
\]
At the same time we notice that since
both $g$ and $f$ are conformal
we must have
\[
\lim_{\nu\to\infty}\,\min_{|z|}\, z\in\gamma^*_\nu=1\tag{viii}
\]
Since $q^*\neq s^*$ in (iv)  Koebe's 
Lemma applied to
$h$ would entails that
$h=0$. This is  a contradiction and
Theorem 0.6.1. follows.




\newpage

\centerline
{\bf {2.4 Proof of Theorem 0.6.2}}

\medskip


\noindent
Suppose that  $\mathcal K_{J_1}(f)=
\mathcal K_{J_2}(f)=z^*$ for some $z^*\in T$.
In $D$ we get the two Jordan arcs $\{J_\nu^*=f(J_\nu)\}$ which 
both tend to $z^*$.
If $g=f^{-1}$ is the inverse function the limit of $g(z)$ along $J_1^*$
is $p$ and the limit along $J_2^*$ is $q$.
Now $p\neq q$ was assumed which contradicts Lindelšf's 
Theorem and  Theorem 0.6.2 follows.
\bigskip

\centerline{\bf 2.5 Proof of  0.6.4-0.6.5.}
\medskip

\noindent
Both results are easy consequences of Koebe's Lemma
using the same device as in the proof of Theorem 0.6.1 above. So we leave the details
of the proofs of the announced results from
0.6.4 and  Proposition 0.6.5
as  exercises to the reader.
\medskip

\noindent
\centerline{\bf{2.6 Accessible pointsá}}
\medskip

\noindent
Let $\Omega$ be bounded and simply connected while no 
further assumptions are imposed. Let $\phi\colon\,D\mapsto \Omega$ 
be a conformal mapping where $z$ is the complex coordinate
in $D$ while $\zeta=\phi(z)$ denote  points in $\Omega$.
Consider a accessible  point  $p\in\mathcal A(\partial\Omega)$
which gives
a half-open
Jordan arc $\gamma_*$ in $D$ such that
\[
\lim _{t\to 1}\, \phi(z(t))=p\tag{1}
\] 
Lindelšf's theorem applies to the bounded analytic function
$\phi$ and  hence
(1) entails that
$\phi$ has a non-tangential limit at $p_*$. In particular there exists the radial limit
\[ 
p=\lim_{r\to 1}\,\phi(re^{i\theta})\tag{2}
\]
Conversely, let $e^{i\theta}\in T$ and assume that
$\phi$ has a radial limit 
which yields a boundary point $p\in\partial\Omega$. Then it is clear that
$p\in\mathcal A(\partial \Omega)$ and we have proved the following:

\medskip

\noindent
{\bf{2.7 Theorem.}}
\emph{Let $\mathcal R(\phi)$ be the set of points on $T$ where
$\phi$ has a radial limit. Then
$\mathcal A(\partial\Omega)$ is equal to the set of $p\in\partial\Omega$
such that}
\[ 
p=\lim_{r\to 1}\, \phi(re^{i\theta})
\quad\text{for some}\quad e^{i\theta}\in \mathcal R(\phi)
\]
\medskip


\noindent
Thus, $\mathcal A(\partial\Omega)$ is equal to the $\phi$\vvv image 
of all radial limit values.
Recall from [Measure] that the subset of $T$ where $\phi$ has 
a radial limit is dense Borel set.
By Theorem 2.7 its image is equal to
$\mathcal A(\partial\Omega)$ which to begin with implies that
$\mathcal A(\partial\Omega)$ is a Borel subset of $\partial\Omega$.
\medskip

\noindent
{\bf{2.8 Harmonic measures on $\partial\Omega$}}.
When $\Omega$ is simply connected
the condition in Theorem xx from Chapter V holds
so Dirichlet's problem has a solution.
Let $\phi\colon D\to\Omega$ be a conformal map
where we let $z$ be the variable in $D$ and set
$\zeta=\phi(z)$. Put $\zeta\uuu *=\phi(0)$
and consider the harmonic measure $\mathfrak{m}\uuu{z\uuu *}$
on $\partial\Omega$.
So when $f\in C^0(\partial\Omega)$
we have
\[
H\uuu f(\zeta\uuu*)=
\int\, f(\zeta)\cdot d\mathfrak {m}\uuu{z\uuu *}(\zeta)\tag{*}
\]
if $r<1$
the circle $|z|=r$ gives  the image curve
$\Gamma\uuu r=\phi(|z|=r)$ which appears as a closed Jordan curve in
$\Omega$.
When $r$ is close to one the Jordan domain
bounded by $\Gamma\uuu r$ contains $z\uuu *$
and we get the harmonic measure on
$\Gamma\uuu r$ with respect to $z\uuu *$.
Restricting $\phi$ to the disc $|z|\leq r$
the transformation rule for harmonic 
measures under conformal mappings gives:

\[
H\uuu f(z)=\frac{1}{2\pi}\cdot 
\int\uuu 0^{2\pi}\, H\uuu f(\phi(re^{i\theta}))\cdot d\theta
\]
Above $H\uuu f\circ\phi$
is a bounded harmonic function in $D$.
and has therefore radial limits almost everywhere which  by dominated
convergence gives:

\[
H\uuu f(\zeta\uuu *)=\frac{1}{2\pi}\cdot 
\int\uuu 0^{2\pi}\, H\uuu f(\phi(e^{i\theta}))\cdot d\theta
\]
More precisely we have integrated the almost everywhere defined function
$\theta\to H\uuu f(\phi(e^{i\theta}))$
where $\phi(e^{i\theta})$ are points on $\mathcal A(\partial\Omega)$
Hence we have the equality
\[
H\uuu f(\zeta\uuu *)=
\frac{1}{2\pi}\cdot 
\int\uuu 0^{2\pi}\, f(\phi(e^{i\theta}))\cdot d\theta\tag{**}
\]
Above $f\in C^0(\partial\Omega)$ is arbitrary
so (**) gives a
linear functional 
\[
f\mapsto \frac{1}{2\pi}\cdot 
\int\uuu 0^{2\pi}\, f(\phi(e^{i\theta}))\cdot d\theta
\] 
which evaluates 
$H\uuu f$ at $\zeta\uuu *$. The uniqueness of the harmonic measure this entails that
$\mathfrak{m}\uuu{z\uuu *}$
is the Riesz measure representing   (**).
We can interpretate  this in a direct measure theoretic sense.
Namely, let $\mathcal R(\phi)$ denote the set of points $e^{i\theta}$ where
$r\mapsto \phi(re^{i\theta})$
has a radial limit. Then we get the Borel measurable
function
from $\mathcal R(\phi)$ to $\mathcal A(\partial\Omega)$
given by
\[ 
e^{i\theta}\mapsto \phi(e^{i\theta})\tag{1}
\]
and the discussion above shows that
$\mathfrak{m}\uuu{z\uuu *}$
is the push\vvv forward of $\frac{1}{2\pi}\cdot d\theta$
\medskip

\noindent
{\bf{Remark.}}
The result above implies
$\mathcal A(\partial\Omega)$ carries all mass of
the harmonic measure, i.e.
\[
\mathfrak{m}\uuu{\zeta\uuu *}(\mathcal A(\partial\Omega))=1
\]
More generally, for every Borel subset $E$ of $\mathcal A(\partial\Omega)$
we have the equality

\[
\mathfrak{m}\uuu{\zeta\uuu *}(E)=
\frac{1}{2\pi} \int\uuu {\phi^{\vvv 1}(E)}\, d\theta
\]
where $\phi^{\vvv 1}(E)$ is a Borel set in $\mathcal R(\phi)$.
Notice also that the results by Koebe and Lindelšf imply that
the map (1) is injective.







\medskip

\noindent{\bf{2.9 A further remark.}}
If $f\in C^0(\partial\Omega)$ we consider its restriction to
$\mathcal A(\partial\Omega)$ and obtain the function $f^*$ on
$\mathcal R(\phi)$:
\[ 
f^*(e^{i\theta})= h(\phi(e^{i\theta}))\tag{1}
\]
Here $f^*$ is defined almost everywhere so via the Poisson kernel
it has a unique harmonic extension
$H^*$ to $D$. The previous material shows that

\[ 
H^*(z^*)=H\uuu f(\phi(z))
\]
hold when $z\in D$.
This gives
an injective linear
map from
$C^0(\Omega)$ to
a space of bounded harmonic functions in $D$.
The description of the resulting range 
of this linear map is unclear without further assumptions on
$\partial\Omega$.









 











\newpage















\centerline{\bf\large  3. Picard's Theorem}
\bigskip

\noindent
{\bf Introduction} In 1879 E. Picard
gave  the affirmative answer to a question posed by Weierstrass
and proved that
an entire function $f(z)$ which excludes two values must be a constant.
Picard's   proof goes as follows: 
Without loss of generality we can assume
that $f(z)$ never takes
the values 0 or 1. Consider the \emph{modular function}
$\mathfrak w(z)$ which exists as a multi-valued function
in ${ \bf{ C}}\setminus \{0,1\}$ with values in the upper half plane $U_+$.
The composed function $g(z)=\mathfrak w((f(z))$ becomes  a
multi-valued function defined in the whole of $\bf C$. Here 
$\bf C$ is simply connected and hence $g$
is
single valued. So $g$ is a entire function with values in
$U_*$. But then $g$ is a constant which
gives a contradiction, for then $f$ would also be a constant function.



\bigskip

\noindent 
\centerline {\bf 3.1 The  Landau-Schottky  Theorem}
\medskip

\noindent
In 1904 Shottky discovered a surprising consequence of the proof by
Picard which led
to a refined
version of Picard's Theorem in joint work with
E. Landau. 
First we give
\medskip

\noindent
{\bf 0.2 Definition}
\emph{Let $f(z)=a_0+a_1z+\ldots$ be an analytic function
defined in a disc $D_R$ of radius $R$ centered at the origin.
Then  $D_R$ is said to be
$(0,1)$-excluding relative $f$
if the range
$f(D_R)$ does not contain the two points 0 and 1.}
\bigskip


\noindent 
{\bf 0.3 Theorem}
\emph{To each non-zero pair $(a_0,a_1)$ there exists a constant 
$L(a_0,a_1)$ such that if $D_R$ is
$(0,1)$-excluding for some
$f\in\mathcal O(D_R)$, then
$R\leq L(a_0,a_1)$.}
\medskip

\noindent 
{\bf Remark} The point is of course that $L(a_0,a_1)$ does 
not depend on higher terms in the series expansion of $f$.
The proof below is attributed to
Caratheodory and gives  a sharp  estimate of $L(a_0,a_1)$ in (*) below.
\medskip

\noindent 
\emph{Proof of Theorem 0.3.}
Suppose that a disc $D_R$
is $(0,1)$-excluding with respect to $f$.
Let $\mathfrak{w}$ be the modular function.
As explained in ¤ XX
we get the analytic function
$g(z)=\mathfrak w(f(z))$ is  in $D_R$ where
$g(D_R)$ is contained in the upper half plane
$U$. Set

\[ 
\ell(z)=\frac{g(z)-g(0)}{g(z)-\bar g(0)}
\]
Since $\mathfrak{Im}(g(z))>0$ we see that $\ell(z)$
has absolute  value $<1$ in $D_R$.
Here $\ell(0)=0$ and  Schwarz' Lemma gives:
\[
|\ell(z)|\leq \frac {|z|}{R}\quad\colon\, z\in D_R\,.
\]
It follows that
the derivative at the origin has absolute value $\leq\frac{1}{R}$.
Here 
\[
\ell'(0)=\frac{g'(0)}{g(0)-\bar g(0))}\quad\text{which gives}\quad
|\frac{g'(0)}{g(0)-\bar g(0))}|\leq\frac{1}{R}\tag{i}
\]
Next, notice  that
\[
g'(0)=\mathfrak w'(a_0)\cdot a_1\,\quad\text{and}\quad
g(0)=\mathfrak w(a_0)\tag{ii}
\]
Hence (i-ii) give;
\[
R\leq2\cdot  |\frac{\mathfrak{Im}
(\mathfrak w(a_0)}{ \mathfrak w'(a_0)\cdot a_1}|\tag{iii}
\]


\noindent
This proves  the inequality
\[
L(a_0,a_1)\leq2\cdot  |\frac{\mathfrak{Im}
(\mathfrak w(a_0)}{ \mathfrak w'(a_0)\cdot a_1}|\tag{*}
\]
\medskip


\noindent
{\bf{Exercise.}}
Show that (*) is sharp wherte a hint is to
use the inverse modular function
$\mathfrak{w}$. 
\medskip

\noindent
{\bf 0.4. The Schottky-Landau Theorem.}
Working a bit more using the $\mathfrak{w}$-function
and various Green's functions, the
following result was  established by Landau and Schottky:
\bigskip

\noindent {\bf 0.5 Theorem}
\emph{For each pair  $(k,\theta)$ where $k>0$ and $0<\theta<1$
there exists a constant $S(k,\theta)$
such that  if   $R>0$ and the open disc $D_R$ is
$(0,1)$ excluding for some $f\in\mathcal O(D_R)$, one has}
\[ 
\max_{|z|\leq\theta R}\,
|f(z)|\leq S_1(k,\theta)\quad\colon\, \quad |f(0)|\leq k
\]


\noindent 
{\bf Remark}
This result applies locally since $R$ can be small and in contrast
to the previous case we only assume that $f$ is analytic in the disc
$D_R$. From Theorem 0.5 one can  deduce the local version of 
Picard's Theorem, i.e. that an analytic function $f(z)$ with an isolated essential singularity
at some point $z_0$ must take all values with at most one exception in arbitrary small 
punctured discs.
For details of proof we refer to paragraph 2 in Ch.V from [Bieberbach] which
contains further comments about
upper bounds of the 
$S$-function. Of special interest is the asymptotic behavior as
$k\to\infty$.
For example, at the end of ¤ 2 in [loc.cit],
the
following is proved:
\medskip

\noindent 
{\bf 0.6 Theorem} \emph{There exists an absolute constant ${\bf{B}}$
such that for any $R>0$ and any $f\in\mathcal O(D_R)$ where $D_R$ is (0,1)- excluding for $f$, one has}
\[
\max_{|z|<\theta R}\, |f(z)|\leq 
\text{exp}[\,\frac{{\bf{B}}\cdot \log \bigl(\,|a_0| +2\,\bigr)}{1-\theta}\,\quad\colon\,\quad
0<\theta<1\quad\colon\, a_0=f(0)
\]


\bigskip

\noindent
{\bf 0.7 Remark.}
Landau' text\vvv book [Landau]
contains a historic account of the
Picard's Theorem and  a
proof of Theorem 0.5 
which only uses 
elementary function theory, i.e avoiding the modular function.
Let us also mention that Theorem 0.5  leads to
certain a priori inequalities for conformal mappings.
We announce
one such result from
Chapter 7 in [Landau]:
Denote by  $\mathcal F$
the family of all  functions
\[ 
f(z)=z+a_2z^2+\ldots
\]
such that $f$ gives a conformal map from the unit
disc $D$ onto some simply connected domain. 
\medskip

\noindent
{\bf 0.8 Theorem.} \emph{To each $0<r<1$ there exist
constants $C_1(r)$ and $C_2(r)$ such that the following hold
for every $f\in\mathcal F$:}
\[ 
\max_{|z|\leq r}\, |f(z)|\leq C_1(r)
\quad\colon\,
\frac{1}{C_2(r)}\leq
\max_{|z|\leq r}\, |f'(z)|\leq C_2(r)
\]
\medskip

\noindent
Since the image domain $f(D)$ need not be bounded this
\emph{a priori} inequality is quite remarkable.

\bigskip

\centerline {\bf 1. The method by  Ahlfors.}
\medskip

\noindent
Landau's Theorem can be viewed  as a special case
of a more general problem where one starts from  some
open and connected set
$\Omega$ in the complex plane such that
${\bf{C}}\setminus\Omega$
contains at least two points.
Given $\Omega$
we consider an analytic function
$f(z)$ defined in some open disc
$D_R$ centered at the origin 
such that $f(D_R)\subset \Omega$.
At the origin we have the Taylor expansion
\[ 
f(z)=a_0+z+a_2z^2+\ldots\quad\colon\quad a_0\in\Omega
\]
For simplicity we have normalised the situation  so that
$f'(0)=1$. Landau's theorem implies
that there exists such an upper bound $R^*$ which depends on $a_0$ and
$\Omega$ only such that
the analytic function $f(z)$ only can exist 
in a disc of radius $<R^*$.
Ahlfors constructed certain
subharmonic functions in
$\Omega$ and used an extension of Schwartz inequality 
to obtain an upper bound for $R^*$ which depends
on the existence of a certain subharmonic function
in $\Omega$. We shall describe this result.
Let $w$ be the complex variable in $\Omega$.
\medskip

\noindent
{\bf 1.1 Definition.}
\emph{Let $\gamma>0$.
Denote by $\text{SH}\uuu \gamma(\Omega)$ the 
class of subharmonic $C^2$-functions
$U$ in $\Omega$ satisfying}
\[
\Delta(U)(w)\geq e^{\gamma\cdot U(w)}\quad
\colon\quad w\in\Omega
\]
\medskip

\noindent
Let us  assume that 0 and 1
stay outside $\Omega$. In this case  one can show that
the class
$\text{SH}\uuu\gamma(\Omega)$ is non-empy when
$\gamma$ is small enough.
Notice that the constraint upon $u$ is more restricted as $\gamma$ increases
and  more relaxed when the open set $\Omega$ becomes smaller.
Here follows  Ahlfors' version of the
Schwartz's inequality.
\bigskip

\noindent
{\bf 1.2 Theorem.}
\emph{Let $U\in\text{SH}\uuu \gamma(\Omega)$ and  $f\in\mathcal O(D_R)$
for some $R>0$.
Then}
\[
e^{\gamma\cdot U(f(z))}\cdot |f'(z)|^2
\leq \frac{8\cdot R^2}{(R^2-|z|^2)^2}
\quad\colon\quad z\in D_R\tag{*}
\]


\noindent
\emph{Proof.}
In $D$ we consider the function
\[
\Phi(z)=
e^{\gamma\cdot U(f(z))}\cdot |f'(z)|^2\cdot (R^2-|z|^2)^2\tag{1}
\]


\noindent
Since $\Phi=0$ on the boundary
$|z|=R$ it takes its maximum at
some $a\in D_R$, i.e.
\[
\Phi(a)=\max_{z\in D_R}\,\Phi(z)
\]
Then $\log\,\Phi=\phi$ also takes its maximum
at $a$ and since the maximum value of
$\Phi$
is positive we have
$f'(a)\neq 0$.
Now
\[ 
\phi(z)=\gamma\cdot U(f(z))+\log\,|f'(z)|^2+
2\cdot\log\, (R^2-|z|^2)\tag{2}
\]
Since $\phi$ takes a maximum at $a$ one has
$\Delta(\phi)(a)\leq 0$.
Moreover, $|f'(z)|^2$ is harmonic in a neighborhood of
$a$ which gives
\[
\gamma\cdot \Delta(U(f(z))+
2\cdot\Delta(\log\, (R^2-|z|^2))\leq 0\quad\text{at the point}\quad z=a\tag{3}
\]
\medskip

\noindent
Differential rules give:
\[
\Delta(U(f(a))= \Delta U(f(a))\cdot |f'(a)|^2\tag{4}
\]
and   an easy  computation also gives
\[
2\cdot \Delta(\log\, (R^2-|z|^2))=\vvv \frac{8 R^2}{(R^2-|z|^2)^2}
\tag{5}
\]
Hence (3-5) entail that
\[
\Delta U(f(a))\cdot |f'(a)|^2\leq \frac{8 R^2}{(R^2-|z|^2)^2}\tag{6}
\]
Since
$U\in\text{SH}\uuu\gamma(\Omega)$ we get
\[
e^{\gamma\cdot U(f(a))}\cdot |f'(a)|^2\cdot(R^2-|a|^2)^2\leq
8R^2\tag{7}
\]
Since
$\Phi(z)$ attains its maximum at $z=a$
the inequality (7) gives
(*) in Theorem 1.2.

\medskip

\noindent
{\bf 1.3 Upper bound for $R^*$}.
Let $f(z)=a_0+z+a_2z^2+\ldots$ and suppose that
$f(D_R)\subset \Omega$ holds for some $R$.
With $z=0$ in Theorem 1.2 we must have
\[
e^{\gamma\cdot U(a_0)}\leq\frac{8}{R^2}\implies
R\leq\sqrt{8}\cdot e^{-\gamma U(a_0)/2}
\]


\noindent
Thus, the existence of some $U$ function in
$\text{SH}\uuu\gamma(\Omega)$
gives
\[ R^*(a_0,\Omega)\leq
\sqrt{8}\cdot e^{-\gamma\dot  U(a_0)/2}
\]
\medskip

\noindent
{\bf 1.4 Remark.}
Theorem 1.2  illustrates the
usefulness  to construct  subharmonic functions with
certain extremal properties.
The  article [Ahlfors]
studies extremal metrics
which in addition
to analytic functions also apply
to
\emph{quasi-conformal mappings}.
In this way
Ahlfors  extended Picard's Theorem
to a set-up where quasi-conformal mappings appear.
For an account about Ahlfors' theory
the reader may  consult the 
presentation talk by Caratheodory from the
IMU congress at Oslo in 1936
when L.  Alhfors received the Fields Prize for his 
contributions.



\newpage





\centerline{\bf\large 4. Some geometric results.}
\bigskip

\noindent
We   study  geometric properties of 
maps defined by analytic functions.
Let $\Gamma$ be an interval on the circle
$|z|=r$. Suppose that $f(z)$ is analytic in some
neighborhood of $\Gamma$ and that $f'(z)\neq 0$
when $z\in\Gamma$.
So if $z_0\in\Gamma$ then
$f$ maps a small circle interval $\gamma\subset\Gamma$
centered at $z_0$
to a Jordan curve $f(\gamma)$. 
For each $z\in\gamma$ the curvature along $\gamma$
at the point $f(z)$ is denoted by $\rho(z)$.
With this notation one has:

\medskip

\noindent {\bf 4.1 Theorem} \emph{For each $z\in \gamma$ 
the following equality holds:}

\[
\frac{1}{\rho(z)}= \frac{1+\mathfrak{Re}[ z\cdot\frac{f''(z)}{f'(z)}]}
{r|f'(z)|}
\]
\bigskip

\noindent
\emph{Proof.}
The image curve  $f(\gamma)$  has the parametrisation 
$\theta\mapsto f(re^{i\theta})$ defined for some $\theta$-interval.
Let $ds$ be the arc-length measure along this curve.
By the general result in XXX we have
\[ 
\frac{ds}{d\theta}=r\cdot |f'(re^{i\theta})|\tag{i}
\]
Next, the $\theta$-parametrisation of $f(T_r)$ gives the complex tangent vector
defined by
\[
v(\theta)=\lim_{\Delta|\theta\to 0}\,
\frac{f(re^{i\theta+i\Delta\theta}-f(re^{i\theta})}{\Delta\theta}
=iz f'(z)\quad\colon\quad z=r^{i\theta}\tag{ii}
\]
Let $\alpha(\theta)=\text{arg}(v(\theta)$.  
The definition  curvature gives:
\[
\frac{1}{\rho}=\frac{d\alpha}{ds}=\frac{d\alpha}{d\theta}\cdot\frac
{d\theta}{ds}
\tag{iii}
\]
So by (i) here remains to show that
\[
\frac{d\alpha}{d\theta}=1+\mathfrak{Re}[ z\cdot\frac{f''(z)}{f'(z)}]\tag{iv}
\]
To show (iv) we notice that $z=re^{i\theta}$ gives
\[
\alpha(\theta)=\text{arg}(izf'(z))=
\pi/2+\theta+\mathfrak{Im}[\text{Log}(f'(re^{i\theta}))]
\]
It follows that
\[
\frac{d\alpha}{d\theta}=1+\mathfrak{Im}
\bigl(ire^{i\theta}\cdot\frac{f''(re^{i\theta})}{
f''(re^{i\theta})}\bigr )=1+\mathfrak{Re}
\bigl(re^{i\theta}\cdot\frac{f''(re^{i\theta})}{
f''(re^{i\theta})}\bigr )
\]
Since  $z=re^{i\theta}$ we have (iv) and Theorem 3.1 is proved.


\bigskip

\noindent 
{\bf 4.2 Convexity of image curves.}
Let 
$f(z)$ be analytic in some open neighborhood
of a circle
$T_r=\{|z|=r\}$. Notice that we do not require that $f$ extends to 
an analytic function in the disc $D_r$.
But we assume that $f$ is 1-1 on $T_r$ which gives
the closed Jordan
curve $f(T_r)$. Recall from analytic geometry that
this curve is \emph{strictly convex} if and only if the curvature
is everywhere $>0$. By Theorem 4.1   strict convexity therefore
holds if and only if
\[
\mathfrak{Re}\,z\cdot\frac{f''(z)}{f'(z)}>\vvv 1\quad\colon\quad
z\in T_r
\]
\medskip

\noindent {\bf 4.3 Example.}
Let $a$ be a real number different from 1 and -1. Consider the function
\[ 
f(z)=z+\frac{a}{z}
\]
It is analytic in a neighborhood of the unit circle $T$. We obtain
\[
z\cdot\frac{f''(z)}{f'(z)}=
\frac{2a}{a-z^2}=\frac{2a(a-z^2)}{|2a-z^2|^2}
\]
So with $z=e^{i\theta}$ the real part becomes
\[
\frac{2a^2-2a\cdot\text{cos}(\theta)}{|2a-e^{i\theta}|^2}
\]
Hence we have strict convexity if and only if
\[
2a^2+|2a-e^{2i\theta}|^2> 2a\cdot \text{cos}(\theta)\quad
\colon\quad  0\leq\theta\leq 2\pi
\]
\medskip

\noindent
{\bf Remark.}Here is a good occasion to 
use a computer and plot the Jordan curves when $a$ varies and
discover when the are convex or not via the criterion above.





\bigskip

\noindent
{\bf{A bound for convexity}}.
Let $f$ give a conformal map from the unit disc $D$ onto a simply
connected domain.
To each $0<r<1$ the image of $|z|<r$ is a Jordan domain
$\Omega\vvv [r]$. 

\medskip

\noindent{\bf{4.4 Theorem.}}
\emph{Set $r\uuu *= 2\vvv \sqrt{3}$.
Then $r\uuu *$ is the largest number such that
$\Omega\uuu f[r]$ are convex for all conformal mappings $f$.}
\medskip

\noindent
\emph{Proof.}
Given $f$ and some $z\uuu 0\in D$
we put
\[ \phi(z)= B\cdot f(\frac{z+z\uuu 0}{1+\bar z\uuu 0\cdot z})
\] 
where 
$B$ is determined so that the derivative $\phi'(0)=1$ which gives
\[
B\cdot f'(z\uuu 0)\cdot (1\vvv |z\uuu 0|^2)=1\tag{1}
\]	
Now $\phi(z)= f(z\uuu 0)+z+a\uuu 2\cdot z^2+\ldots$
is a conformal map on $D$ and Theorem XX in XXX gives
\[
|a\uuu 2|\leq 2\tag{2}
\]
At the same time a computation gives

\[ 
\phi'(z)= 
B\cdot f'(\frac{z+z\uuu 0}{1+\bar z\uuu 0\cdot z})\cdot
\frac{1\vvv |z\uuu 0|^2}{(1+\bar z\uuu 0\cdot z)^2}\implies
\]
\[
\phi''(0)=B\cdot f''(z\uuu 0)\cdot\bigl[1\vvv |z\uuu 0|^2\bigr]^2\vvv
B\cdot f'(z\uuu 0)\cdot (1\vvv|z\uuu 0|^2)\cdot 2\cdot \bar z\uuu 0=
\]
\[
\frac{f''(z\uuu 0)}{f'(z\uuu 0)}
\cdot (1\vvv |z\uuu 0|^2)\vvv 2\cdot \bar z\uuu 0\tag{3}
\]
Now (2) gives $|\phi''(0)|\leq 4$
and after a multiplication with $z\uuu 0$ we get
the inequality
\[
\bigl|z\uuu 0\cdot \frac{f''(z\uuu 0)}{f'(z\uuu 0)}
\cdot (1\vvv |z\uuu 0|^2)\vvv  2\cdot |z\uuu 0|^2\bigr |\leq 4\cdot |z\uuu 0|\tag{4}
\]
With $|z\uuu 0|= r<1$ we see that (4) gives the inequality
\[
\mathfrak{Re}\, z\uuu 0\frac{f''(z\uuu 0)}{f'(z\uuu 0)}
\geq \frac{\vvv 4r+2r^2}{1\vvv r^2}
\]
By (*) in 4.2  the image domain
$\Omega\uuu r$ is convex if the right hand side is $>\vvv 1$
Hence the critial value $R\uuu *$ is the smallest root of the
equation $r^24r+1=0$ which gives $r\uuu *=2\vvv\sqrt{3}$.
\medskip

\noindent
{\bf{Exercise.}} Show that the bound $r\uuu *$ is sharp using the Koebe map from
XX where we have the equality $|a\uuu 2|=2$
for a normalised conformal map $\phi$ with $\phi'(0)=1$.



\bigskip




\centerline
{\bf 4.5 Jensen's landscape surface.}
\bigskip

\noindent
Let $f(z)\in \mathcal O(\Omega)$ for some open  set. 
Assume that $f\neq 0$ in $\Omega$. To each 
$z\in\Omega$ we get the positive number $t=|f(z)|$.
So with $z=x+iy$ we obtain a surface in the real $(x,y,t)$-space defined by
\[ 
t=|f(x+iy)|
\]
It is denoted by $\mathcal J_f$. To each 
$z=x+iy\in \Omega$ we get the point
\[ 
p=(x,y,|f(x,y)|)\in\mathcal J_f
\]
Let $\Pi$ be the tangent plane to $\mathcal J_f$ at $p$.
Let $\gamma(p)$ be the acute angle between $\Pi$ and the $(x,y)$-plane.
So here $0<\gamma(p)<\frac{\pi}{2}$. With these notations one has;

\medskip

\[
\text{tg}(\gamma(p))=
2\cdot |f(z)|\cdot |f'(z)|
\]
\medskip

\noindent \emph{Proof.}
Let $n$ be the unit normal to Jensen's surface whose $t$-component
becomes
\[ 
n_t=
\frac{1}{(\partial_x |f|)^ 2+(\partial_y |f|)^ 2+1}
\]
By elementary geometry we have
\[ 
n_t\text{cos}(\gamma(p))=
\frac{1}{(\partial_x |f|)^ 2+(\partial_y |f|)^ 2+1}
\]
At this stage the reader can finish the proof after calculating
the partial derivatives of $|f|$ by expressing   
$f$ as $u+iv$.


\bigskip

\centerline{\bf\large Koebe's One Quarter Theorem}

\bigskip
\noindent
The result below was established by Koebe in 1907.
Let $f(z)$ be analytic in the unit disc $D$. Assume that
$f(0)=0$ and $f'(0)=1$ and that $f$ is 1-1, i.e. $f$ gives a 
\emph{conformal map} from $D$ onto a domain $\Omega$.
\medskip

\noindent {\bf 4.6 Theorem.} \emph{The image set $f(D)$ contains the open disc of radius
$\frac{1}{4}$ centered at the origin, i.e. to any $|w|<1/4$ there exists $z\in D$ so that $f(z)=w$.}
\medskip

\noindent \emph{Proof.}
To begin with $f(D)$ certainly contains some open
disc centered at the origin. This yields the existence of a positive number $d$
defined by
\[
d=\min \,|w[\quad\colon\,\quad w\in C\setminus f(D)
\]
We find some $w^*C\setminus f(D)$ such that $|w^*|=d$.
Next, since the image $f(D)=\Omega$ is \emph{simply connected}
the result in plane topology from XXX gives the existence of a simple
curve $\Gamma$ with a starting point at $w^*$, contained in
$C\setminus f(D)$ and moving to the point at infinity.
Removing $\Gamma$ we also know from XXX that
$C\setminus\Gamma$ is simply connected.
This implies that there exists a \emph{single-valued} branch of the root
function $\sqrt{w-d}$ in $C\setminus \Gamma$
such that
\[
\mathfrak{Re}(\sqrt{w-d})>0\quad\colon\quad
w\in  C\setminus\Gamma
\]
Set
\[ 
g(w)=-4d\frac{\sqrt{w-d}-i\sqrt{d}}{\sqrt{w-d}+i\sqrt{d}}
\]
Then we see that
\[ 
g'(0)=0\quad\colon\,\quad |g(w)|< 4d\quad\colon\, w\in
C\setminus\Gamma
\]
Next, consider the composed function $H=g(f(z))$ which becomes analytic in $D$. Since $f(0=0$ and $f'(0)=1$ we obtain
\[ 
H'(0)=g'(0)f'(0) =1\quad\colon\quad
|H(z)|< 4 d\quad\colon\,z\in D
\]
Since we also have $H(0)=g(0)=0$, the last estimate and Schwarzs' inequality from
XX give $|H'(0)\leq 4d$. Since we also have
$H'(0)=1$ we get $d\geq\frac{1}{4}$ as required.

\medskip

\centerline{\bf 4.7 The Area Theorem.}
\medskip

\noindent
Consider a function
\[ 
w(z)=z+\frac{a_1}{z}+\frac{a_2}{z^2}+\ldots\tag{*}
\]
where the
negative Laurent series
is convergent in the exterior disc
$|z|>1$. At the point at infinity  the
$w$-function has a simple pole since
$z$ appears in (*).
Assume that (*) yields a conformal map from
the exterior domain $D^*=\{|z|> 1\}\cup\{\infty\}$
onto a simply connected exterior domain which includes the point at
infinity
in the $w$-plane bordered by a closed Jordan arc
$\Gamma$. Thus,  the \emph{bounded} Jordan domain
bordered by $\Gamma$ is outside the image
of the map (*).
\medskip

\noindent
{\bf 4.8 Theorem.} \emph{One has the inequality}

\[ \sum_{n=1}^\infty\, n\cdot |a_n|^2\leq 1
\]
\medskip

\noindent
\emph{Proof.}
If $r>1$ we denote by $\Gamma(r)$ the closed Jordan curve
in the $w$-plane which is the image of the circle $|z|=r$.
Let $J(r)$ be the area of the bounded
Jordan domain in the
$w$-plane which is bordered by
$\Gamma(r)$.
With $w=u+iv$ we recall from (xx) that
Green's formula gives:
\medskip
\[
J(r)=\int_0^{2\pi}
u(re^{i\theta})\cdot
\frac {dv(re^{i\theta})}{d\theta}\cdot d\theta\tag{i}
\]
The Cauchy Riemann equations imply that
(i) is equal to:
\[
\int_0^{2\pi}\,
\frac{w(re^{i\theta})+\bar w(re^{i\theta})}{2}\cdot
\frac{w'(re^{i\theta})-\bar w'(re^{i\theta})}{2i}\cdot d\theta\tag{ii}
\]
Now (ii) has the series expansion

\[
\int_0^{2\pi}\,
\bigr[\,
\frac{re^{i\theta}+re^{-i\theta}}{2}+
\sum_{n=1}^\infty\, 
\frac{a_n\cdot re^{-in\theta})+\bar a_n\cdot (re^{in\theta})}{2\cdot r^n}\bigr ]\cdot
\]
\[
\bigr[\,
\frac{re^{i\theta}+re^{-i\theta}}{2}-
\sum_{n=1}^\infty\, 
\frac{na_n\cdot re^{in\theta})+n\bar a_n\cdot (re^{in\theta})}{2\cdot r^n}\bigr]\cdot 
d\theta
\] 
\medskip

\noindent
Since the integrals $\int_0^{2\pi}\, e^{ik\theta}\cdot d\theta=0$
for all integers $k\neq 0$, a computation shows that
the expression above becomes
\[
\pi r^2-\pi\cdot \sum_{n=1}^\infty\, \frac{n\cdot |a_n|^2}{r^{2n}}\tag{iii}
\]
Here (iii) holds for every $r>1$ and since
it expresses the non-negative area
$J(r)$  it is non-negative.
Passing to the limit as
$r\to 1$
we get the inequality in the theorem.
\bigskip

\noindent
{\bf{4.9 An extremal problem.}}
Consider a double connected domain
$\Omega$ where $\partial\Omega$
consists of two disjoint and closed Jordan curves
$\Gamma_*$ and $\Gamma^*$. Here $\Gamma^*$ is the outer curve which
borders the unbounded component of ${\bf{C}}\setminus \bar\Omega$.
By XXX there exists a unique number $0<\ell<1$ such that
$\Omega$ is conformally equivalent to the annulus
$\mathcal A(\ell)=\{0<\ell<|z|<1\}$
and we set $\ell=\ell(\Omega)$.
Let $\Omega^*$ be the Jordan domain bounded
by the outer curve $\Gamma^*$ and $\Omega_*$ is the Jordan domain bounded
by $\Gamma_*$. Set
\[
\rho_*=
\text{Area}(\Omega_*)\quad\text{and}\quad
\rho^*=
\text{Area}(\Omega^*)
\]
So if $\Omega$ is equal to
$\mathcal A(\ell)$ or a translate of this annulus we have
\[
\ell^2=\frac{\rho_*}{\rho^*}
\]

\medskip


\noindent
{\bf{4.10 Theorem.}}
\emph{For every doubly connected domain
$\Omega$ which is not a translate of an annulus one has  strict inequality}
\[ 
\ell(\Omega)^2>
\frac{\rho_*}{\rho^*}
\]

\medskip

\noindent
\emph{Proof.} 
Set 
$\ell=\ell(\Omega)$ and
let $F\colon\mathcal A(\ell)\to\Omega$ be a conformal map.
Now $F(z)$ has a Laurent series expansion
\[
 F(z)=\sum_{-\infty}^\infty \, c_n\cdot z^n\tag{1}
\]
We get the  area formulas
\[ 
\rho_*=
\frac{1}{\pi}\cdot 
\sum_{-\infty}^\infty \, n\cdot |c_n|^2\cdot \ell^{2n}
\quad \text{and}\quad
\rho^*=
\frac{1}{\pi}\cdot \sum_{-\infty}^\infty \, n\cdot |c_n|^2\tag{2}
\]


\noindent
Since $\ell<1$ we get :
\[
\ell^2\cdot \sum_{n=1}^\infty \, n\cdot |c_n|^2\geq
\sum_{n=1}^\infty \, n\cdot |c_n|^2\cdot \ell^{2n}=
\]
\[
\pi\cdot \rho_*-
\sum_{n-1}^{-\infty} \, n\cdot |c_n|^2\cdot \ell^{-2n}
\geq
\pi\cdot \rho_*-
\sum_{n-1}^{-\infty} \, n\cdot |c_n|^2\tag{3}
\]



\noindent
Above strict inequality holds unless
\[
c_n=0\quad\text{for all}\quad n\neq 1\tag{4}
\]
We have also the equality
\[
\sum_{n=1}^{\infty} \, n\cdot |c_n|^2=
\pi\cdot \rho^*-\sum_{n-1}^{-\infty} \, n\cdot |c_n|^2\tag{5}
\]
The inequality (3) and a division with
$\sum_{n=1}^{\infty} \, n\cdot |c_n|^2$ gives



\[\ell^2\geq 
\frac{\pi\cdot \rho_*-
\sum_{n-1}^{-\infty} \, n\cdot |c_n|^2}{\pi\cdot \rho^*-
\sum_{n-1}^{-\infty} \, n\cdot |c_n|^2}
\tag{6}
\]
\medskip

\noindent
Since $\rho^*-\rho_*>0$ it is obvious that the last term is
$\geq\frac{\rho_*}{\rho^*}$ and Theorem 4.10 follows.
\medskip

\noindent
{\bf{Remark.}} Theorem 4.10
appears
in  Carleman's  article  
\emph{†ber eine Minimalproblem der mathematischen Physik}
from 1917 where 
an application 
of Theorem 4.10 to  \emph{Zylinderkondensatoren}
is described.
























\newpage

\centerline{\bf\large 5. Schwarz-Christofell maps}
\bigskip

\noindent
{\bf Introduction.}
Following  original 
constructions by H. Schwartz and Christoffell 
we shall find
a conformal mapping from
the unit disc onto a
convex polygon $\Pi$ whose corner points are denoted by
$w_1,\ldots,w_N$ where $N\geq 3$.
Performing a translation if necessary we may assume that the origin
is an interior point of $\Pi$. Here $\Pi$
is placed in the complex
$w$-plane. The corner points $w_1,\ldots,w_N$ are arranged so that
the boundary has a positive orientation - i.e. anti-clockwise. See figure XXX.
At each corner point $w_k$ we get
the two line segments
$\ell_*(k)$ and $\ell^*(k)$
where $\ell_*(k)$ joins $w_{k-1}$ with $w_k$ and
$\ell^*(k)$ joins $w_k$ with $w_{k+1}$.
In the case $k=1$ then $\ell_*(1)$ joins $w_N$ with
$w_1$ and  $\ell^*(N)$ joins $w_N$ with $w_1$.
At each corner point we have the interior angle
$\beta_k$ where $0<\beta_k<\pi$. 
A wellknown formula from euclidian geometry
gives
\[
\sum\,\beta_k=(N-2)\pi
\]
The outer angles are defined by:
\[ 
\alpha_k=\pi-\beta_k\quad\implies\quad
\sum\,\alpha_k=2\pi
\]



\noindent
See figure XXX for an illustration.
Riemann's mapping theorem gives the unique
analytic function $f(z)$ in $D$ such that
$f(0)=0$ and $f'(0)$ is real and positive while $f$ maps $D$ conformally
onto
$\Pi$.
Moreover, since $\Pi$ is a Jordan domain we know that this
conformal mapping.
extends continuously up to the boundary and 
$f$ yields a bi-continuous map from the unit circle $T$
onto the boundary of $\Pi$.
On $T$ we get the points $z_1,\ldots,z_N$ which are mapped
to the corner points of $\Pi$. 
Performing a rotation of $\Pi$ in the $w$-plane we may assume that
$z_1=1$ and if  $2\leq k\leq N$ we 
have 

\[
z_k=e^{i\theta_k}\quad\text{where} \quad
0<\theta_2<\ldots<\theta_N<2\pi
\]

\medskip

\noindent
When $k=1$ we have $z\uuu 1=0$ so $\theta\uuu 1=0$.
Put
\[ 
a_k=\frac{\alpha_k}{\pi}\quad\colon\quad 1\leq k\leq N
\]
Hence (xx) entails that

\[ 
\sum\, a\uuu k=2
\]
To every $1\leq k\leq n $ we get the analytic function in
$D$ defined by
\[
\phi_k(\zeta)=(1-e^{-i\theta_k}\zeta)^{-a_k}\tag{1}
\]
where  single valued branches  are chosen so that
\[ 
-\pi/2<\text{arg}(\phi(\zeta))<\pi/2
\]
In particular  $\phi_k(0)=1$.
With these notations one has:
\medskip

\noindent
{\bf 5.1 Theorem.}
\emph{The conformal map
$f$ from $D$ onto $\Pi$ is given by:}


\[ 
f(z)=
c_0\cdot\int_0^z\, \frac{d\zeta}{
(1-e^{-i\theta_1}\zeta)^{\alpha_1}\cdots (1-e^{-i\theta_N}\zeta)^{\alpha_N}}
\quad\colon\, c_0>0\,\,\, \text{is a positive constant}
\]
\medskip

\noindent
To prove this we analyze
the function
\[
\theta\mapsto f(e^{i\theta})
\] 
over $\theta$\vvv intervals
which avoids the $n$\vvv tuple $\{\theta\uuu k\}$.
When $\theta\uuu k<\theta<\theta\uuu{k+1}$
holds we have
\[
f(e^{i\theta})= c_0\cdot\int_0^{e^{i\theta}}\, \frac{d\zeta}{
(1-e^{-i\theta_1}\zeta)^{a_1}\cdots (1-e^{-i\theta_N}\zeta)^{a_N}}
\]
It follows that the $\theta$\vvv derivative becomes

\[
\frac{df}{d\theta}=
c\uuu 0\cdot i\cdot e^{i\theta}
\cdot\frac{1}{\prod\,(1\vvv  e^{-i\theta_k+i\theta})^{a\uuu k}}
\]
The argument of the right hand side becomes

\[
\frac{\pi}{2}+\theta\vvv \sum a\uuu k\cdot
\text{arg}\, (1\vvv  e^{-i\theta_k+i\theta})\tag{i}
\]
As explained in XX: Chapter I we have
\[
\text{arg}\, (1\vvv  e^{-i\theta_k+i\theta})=\frac{\theta\vvv \theta\uuu k\vvv \pi}{2}
\]
for every $k$. Together with (*) above we conclude that
\[
\text{arg}\, \frac{df}{d\theta}=
\frac{\pi}{2}+\theta+ \sum a\uuu k\cdot  \frac{\theta\uuu k+\pi\vvv \theta}{2}
=\frac{3\pi}{2}+\sum a\uuu k\cdot\frac{\theta\uuu k}{2}
\]
where the last equality follows from XX.
In particular the argument remains constant which means that
$f$ maps the circular arc $\{\theta\uuu k<\theta<\theta\uuu{k+1}\}$
onto a line segment.
So this confirms that if $f$ is s conformal mapping then it sends
$D$ onto a Jordan domain bounded by
a piecewise linear boundary curve which we want to be equal to
the given convex polygon $\Pi$.




\medskip


\noindent
\emph{Proof that $f$ is a conformal mapping.} 
To show this we
investigate the conformal mapping $f\uuu *(z)$ which is 
already predicted by Riemann's mapping theorem
and we are going to show that the complex derivative of $f\uuu *$
is equal to
the complex derivative
\[ 
f'(z)= c\uuu 0\cdot \phi\uuu 1(z)\cdot \phi\uuu N(z)\tag{1}
\]

\noindent
To prove that $f'\uuu *(z)$ is equal to the function in
(1) we first
consider a circular arc:
\[ 
\gamma_k=\{ e^{i\theta}\quad\colon \theta_k<\theta<\theta_{k+1}\}\tag{1}
\]
Now $f\uuu *$ maps this arc onto
a line segment of the polygon $\Pi$.
In particular
$\text{arg}(f'_*)$ is constant on $\gamma_k$ and then
Schwarz' reflection principle 
implies that the complex derivative
$f'_*$ extends analytically across $\gamma_k$.
In fact, set
\[
\beta_k=\text{arg}\, f_*'(e^{i\theta})\quad \colon\quad e^{i\theta}\in\gamma_k\tag{2}
\]
In the exterior disc $|z|>1$ we define the analytic function
\[ 
g_k(z)= e^{2i\beta_k}\cdot \bar f'_*(\frac{1}{\bar z})\tag{3}
\]
When $e^{i\theta}\in\gamma_k$ we obtain
\[
\text{arg}\, g_k(e^{i\theta})=2\beta_k
\text{arg}\, f'_*(e^{i\theta})\tag{4}
\]
It follows that  $g_k=f'_*$ on $\gamma_k$ and hence $g_k$ 
yields the analytic extension of
$f'_*$ across $\gamma_k$ where $g\uuu k$ is analytic in the
exterior disc
$\{|z|>1\}$.
Next, for any other arc
$\gamma\uuu\ell$ we can
return to the unit disc by performing an analytic extension of
$g\uuu k$ across $\ell\uuu\nu$.
Moreover, we see that the new analytic function in
$d$ must be a constant times
$f'\uuu *$.
This process can be continued, and the conclusion is that
$f'_*$ is a single-valued branch of a multi-valued analytic function
$F$ defined in
${\bf{C}}\setminus (e^{i\theta_1},\ldots, e^{i\theta_N})$.
Moreover, by the explicit analytic continuations over the
$\gamma$-segments  the rank of the
multi-valued function $F$ is equal to one and hence
the general result in XX shows  that the single-valued
branch $f'_*$ is given in the form
\[
f'_*(z)= \prod_{k=1}^{k=N}\,
(1-e^{-i\theta_k}z)^{\rho_k}\cdot H(z)\tag{5}
\]
where 
$\rho_1,\ldots,\rho_N$ are complex numbers
and $H(z)$ is an entire function.
From (4) above the jump of 
$\text{arg}\, f_*'$   at each point $e^{i\theta_k}$,
via  the local study in
XX gives the equalities:
\[ 
\rho_k= -a_k
\]
\medskip

\noindent
There remains to prove that
the entire function $H(z)$ is constant.
To see this we consider the analytic extension of
$f_*$ across some $\gamma_k$ as  above which leads to
the analytic function $g_k$ in the exterior domain. By the
construction $g_k$ is bounded in this exterior disc and from this we see
that the entire function 
$H(z)$ is bounded and hence reduced to a constant by Liouville's theorem.
Hence we have proved that
there exists a constant $c$ such that
\[ 
f'\uuu *= c\cdot f'
\]
Since both $f$ and $f\uuu *'$ are zero at the origin we have proved that
$f$ is a constant times $f\uuu *'$ which shows that
$f$  gives the requested conformal mapping from $D$ onto $\Pi$.


\bigskip



\centerline{\bf{5.4 A local study.}}

\bigskip

\noindent
With the notations as above
we  analyze the behaviour of the mapping function
$f_*(z)$ as $z\to z_k$ for every $k$.
We already know that $f_*$  extends to a multi-valued function
in a punctured disc centered at $z_k$ and there
remains to consider  the situation locally for each
given $z_k$.
After a rotation
we may take $z_k=w_k=1$ and at the corner point $w_k$
we have some angle $\alpha$. Put

\[ 
a=\frac{\alpha}{\pi}
\]

\noindent
Consider the analytic function $g(z)$ in $D$ defined by
\[ 
\phi(z)=(z-1)^{1-a}\tag{i}
\]
When $\theta>0$ is small the complex argument
\[
\text{arg}(e^{i\theta}-1)\simeq \frac{\pi}{2} \tag{ii}
\]
At the same time, when $\theta$ is small and negative we have
\[
\text{arg}(e^{i\theta}-1)\simeq -\frac{\pi}{2}\quad\colon
\theta<0 \tag{iii}
\]
\medskip

\noindent Hence we have two limit formulas:
\[
\lim_{\theta\to 0_+}
\,\text{arg}\, \phi(e^{i\theta})=(1-\alpha)\frac{\pi}{2}\quad\colon\,
\lim_{\theta\to 0_-}
\,\text{arg}\, \phi(e^{i\theta})=(\alpha-1)\frac{\pi}{2}\tag{iv}
\]
\medskip

\noindent
From figure XX the two limit formulas reflect
the jump discontinuity of the argument for the mapping function
$f$ at the corner point.
From this we conclude that
$f(z)$ close to $z=1$ has 
a fractional series expansion
\[ 
f(z)=1+[\, c_1(x-1)+c_2(x-1)+\ldots\,]^{1-\alpha}\tag{v}
\]

\noindent
Passing to the complex derivative we get
\[ 
f'(z)=
[\, c_1(x-1)+c_2(x-1)+\ldots\,]^{-\alpha}\tag{vi}
\]
\medskip

\noindent
It follows that
\[
\frac{f''(z)}{f'(z)}=
\frac{-\alpha}{z-1}+\sum_{\nu=0}^\infty\,
d_\nu\cdot (z-1)^\nu\tag{iv}
\]
where the last sum is an analytic function in some disc centered at $z=1$.
So in (iv) above we encounter a simple pole whose residue is
determined by the angle $\alpha$.
Applying this to every corner point of the given 
polygon $\Pi$
we have proved:
\medskip

\noindent
{\bf 5.5 Lemma} \emph{Under analytic continuation of $f(z)$ it follows
that $\frac{f''(z)}{f'(z)}$ becomes a single valued meromorphic function
of the form:}
\[ 
\phi(z)=\sum\,\frac{-\alpha_\nu}{z_\nu-z}+H(z)\quad\colon\, H(z)\,\,\text{entire function}
\]
\medskip

\noindent
There remains only to see that the entire function
is zero. To show this we first notice that
the analytic continuation of $f$ is achived by
reflections in  boundary arcs of $T$ and therefore
remains bounded. In particular the entire function $H$ is bounded
and hence a constant.
Finally, this constant must be zero for otherwise
\[ 
\text{Log}\,f(z)=
-\sum\,\alpha_\nu\cdot\text{Log}\,(z_\nu-z)+ bz\quad\colon\, b\neq 0
\]
and taking the exponential we see that $f'(z)$ increases too fast.

\bigskip

\noindent
{\bf 5.2 Determination of the $z_k$-numbers.}
The  given polygon $\Pi$ 
gives the $\alpha$-numbers in the Schwarz-Christoffell formula.
There remains to determine  the points
$\{z_k=e^{i\theta_k}\}$ on the unit circle which are mapped to corner
points
of the polygon.
This amounts to compute
the integrand in Theorem 5.1  to recover the  lengths of the  sides in
$\Pi$.
The determination of the $N$-tuple $z_1,\ldots,z_N$
when $\Pi$ is prescribed is not easy. The reason is that one 
cannot solve  these $z_k$-numbers
step by step. One has to regard 
a system of $N$ many \emph{non-linear} equations where the $z_k$ appear
in a rather implicit way. 
However,
computer programs 
offer algorithms which give numerical solutions for the
$z$-numbers.
See for example [XXX].

\medskip













\newpage


\centerline{\bf 6. Privalov's theorem}


\medskip



\noindent {\bf Introduction.}
We shall prove a 
uniqueness result 
established by Privalov in 1917.
Let $f(z)\in\mathcal O(D)$ 
where no conditions are imposed on
$|f(z)|$ , i.e. it may have arbitrary growth.
There exist $f$
which is not identically zero, and yet
the radial limits are all zero,  i.e.

\[ \lim_{r\to 1}\, f(re^{i\theta})=0\quad\colon\,\forall\,0\leq\theta
\leq 2\pi
\]

\medskip

\noindent
{\bf Remark.}
For the construction of such a function $f$
we refer to Privalov's text-book [Pri].
See also  [Bi:2.page 152-154] for the construction of 
an unbounded analytic function $f$ in $D$
which \emph{never} has a radial limit.
\bigskip

\noindent
To establish a uniqueness theorem for a general unbounded
function one must
therefore allow \emph{non-tangential limits}.
Following Privalov we describe how such non-tangential limit values should be
defined.
\medskip

\noindent 
{\bf The Jordan domain $\mathfrak{M}_E$}
Let $J$ be an interval in $T$
with two end-points $\zeta_\nu=e^{i\theta_\nu}$
where 
$|\theta_1-\theta_2|<\pi$.
Then we obtain 
a curve linear triangle $\Delta_J$ constructed upon $J$
as follows: Through $\zeta_1$ we take the
straight line $\ell_1$
which has angle $\pi/4$ with $T$.
Similarly we construct the line $\ell_2$. 
The two lines intersect at a point
$q\in D$. Then $\Delta_J$ is the domain bordered
by $J$ and the two line segments along the $\ell$-lines from $\zeta_\nu$
to $q$. The reader may illustrate this by a figure.
Notice that the angle at $q$ becomes $\pi/2$.
\medskip

\noindent
Next, let $E$ be a closed subset of $T$.
Now $T\setminus E$ is a disjoint union of
open intervals $J_\nu$. To each of them we get the domain
$\Delta_\nu$. Put
\[ 
\mathfrak{W}_E=
D\setminus \,\cup\,\bar\Delta_\nu
\]
We refer to $\mathfrak{W}_E$ as \emph{Privalov's domain}
attached to $E$.
It is easily seen that it is a Jordan domain. In fact, to
each
$0\leq\theta\leq2\pi$ we consider the ray
from the origin in the $\theta$-direction
and looking a a figure the reader discovers that
there is a unique $0<r(\theta)\leq 1$
such that $re^{i\theta}\in\partial \mathfrak {W}_E$
while $re^{i\theta}\in\mathfrak {W}_E$ when
$0\leq r<r(\theta)$.
In this way we get a bi-continuous map from
the periodic $\theta$-interval onto
$\partial \mathfrak {W}_E$.
Notice also that $r(\theta)=1$ precisely when
$e^{i\theta}\in E$.
By the construction the boundary of
$\mathfrak{M}_E$ is piecewise linear inside $D$ and
where the  total arc-length is 
$\sqrt{2}\cdot \sum\, |J_k\nu|$ as one sees from the construction of the
$\Delta$-triangles.
When $E$ has positive Lebesgue measure
the remaining part of the simple and closed Jordan
$\partial \mathfrak {W}_E$ has length $|E|$. Hence
the boundary of $\mathfrak{M}_E$ is a
\emph{rectifiable} Jordan curve.
Now we can announce Privalov's uniqueness theorem.

\bigskip

\noindent
{\bf 6.1 Theorem}
\emph{Let $E\subset T$ be a closed set of positive measure.
If  $f\in\mathcal O(D)$ is such that}
\[ 
\lim_{z\to E}\, f(z)=0\quad\colon\quad z\in
\mathfrak {W}_E
\] 
\emph{Then $f$ is identically zero}.
\bigskip








\noindent
\emph{Proof .}
By assumption we have a pointwise convergence to zero
as $z\in\mathfrak{M}_E$ tends to $E$.
By \emph{Egoroff's theorem} in measure theory we 
can  therefore find a closed subset $E_*$ if $E$ such that
the limit is attained \emph{uniformly}
as $z\to E_*$ and at the same time
$E_*$ again has positive measure.
Now we notice that 
$\mathfrak{W}_{E_*}\subset\mathfrak{W}_E$ 
and we restrict $f$ to this Jordan domain.
Let $f_*$ denote this restricted function. By the uniform convergence it
follows that $f_*$ is a bounded analytic function in
$\mathfrak{W}_{E_*}$.
Next, consider a conformal map $\phi$ from $D$ 
onto 
$\mathfrak{W}_{E_*}$ and put $g=f_*\circ g$.
Then $g$ is a bounded analytic function in $D$.
Since $E_*$ has positive Lebesgue measure and
$\partial\mathfrak{W}_{E_*}$ is a rectifiable Jordan
arc, it follows that the inverse set $\phi^{-1}(E_*)$
appears as a closed subset of $T$ with positive Lebesgue measure.
Hence $g$ tends to zero on  set of positive measure and is
therefore identically zero, i.e. as a very special case of Fatou's result in XX. 
We conclude that $f=0$ and Privalov's theorem is proved. 

\newpage


\centerline{\bf 7. Maps between multiple connected domains.}

\bigskip

\noindent
{\bf Introduction.}
Let us begin  the study with a doubly connected domain $\Omega$ 
whose outer boundary
is the unit circle $T$ and the inner boundary a closed Jordan curve
$\gamma$ contained in the unit disc.
There exists the harmonic function
$\omega$ with boundary value one on $T$ and zero on
$\gamma$, i.e. $\omega$ is the harmonic measure with respect to
$T$.
Set
\[ 
b=\int_T\,\frac{\partial \omega}{\partial{\bf{n}}}\cdot ds
\]
It is clear that $b>0$
and we put:
\[ 
\alpha=\frac{2\pi}{b}
\]
The result in XXX shows that
there exists an analytic function
$f(z)$ in $\Omega$ defined by
\[
f(z)=
e^{\alpha\cdot \omega+iV}
\]
where $V$ is the locally defined harmonic conjugate of $\alpha\cdot \omega$.
Since
\[ 
|f(z)|= e^{\alpha\cdot\omega(z)}
\]
and $\omega(z)=0$ on $\gamma$ we conclude 
that $|f|=1$ on $\gamma$ while $|f|=e^\alpha$ on
$T$.
\medskip

\noindent
{\bf 7.1. Proposition.}
\emph{The function $f$ maps from
$\Omega$ conformally onto the annulus $1<|z|<e^\alpha$.}
\medskip

\noindent
\emph{Proof.}
The maximum principle for analytic functions
applied to $f$ and $\frac{1}{f}$ give
\[
1<|f(z)|<e^\alpha\quad\colon\, z\in\Omega
\]
Next, let $w$ be a complex number in the annulus, i.e.
$1<|w|<e^\alpha$. By the general result in
XX  $f$ is conformal if we prove the equality
\[
\frac {1}{2\pi i}
\int_{\partial\Omega}\,\frac{f'(z)}{f(z)-w}\cdot dz=1\tag{1}
\]
for every such $w$.
To get (1) we use that
$|f(z)|= 1<|w|$  on the inner curve
$\gamma$. So  the result in  XXX gives:
\[
\int_{\gamma}\,\frac{f'(z)}{f(z)-w}\cdot dz=0\tag{2}
\]
Next, on the unit circle $T$ 
it follows from
the general result in XX from Chapter 4 that
\[
\frac {1}{2\pi i}
\int_{\partial\Omega}\,\frac{f'(z)}{f(z)-w}\cdot dz=
\frac {1}{2\pi i}
\int_{\partial\Omega}\,\frac{f'(z)}{f(z)}\cdot dz=\tag{3}
\]
\[
\frac{1}{2\pi}\cdot \int_0^{2\pi}\,\frac{dV}{d\theta}(e^{i\theta})\cdot d\theta
\]
Here $V$ is the local harmonic conjugate to $\alpha\omega$
which means gives
\[ 
\frac{dV}{d\theta}= \alpha\cdot \frac{\partial\omega}{\partial{\bf{n}}}
\]
along $T$.
Hence the choice of $\alpha$  shows that (3) has value one and together with
(2) we conclude that (1) also has value one.










\bigskip
\centerline {\bf 7.2 General case.}
\medskip

\noindent
Consider a domain $\Omega\in\mathcal D(C^1)$
with $p$ boundary
curves $\gamma_1,\ldots,\gamma_p$ where $p\geq 3$. Let
$\gamma_p$ be the
curve which borders
the unbounded  connected component of ${\bf{C}}\setminus\Omega$.
To each $1\leq j\leq p-1$ we have the harmonic function
$\omega^j$
with boundary value 1 on $\gamma_j$ and zero on the remaining
boundary curves. This gives a $(p-1)\times(p-1)$-matrix
${\bf {B}}$ with elements
\medskip

\[
b_{\nu,j}=\int_{\gamma_\nu}\, \omega^j_{{\bf{n}}}\cdot ds
\quad\colon\, 1\leq j,\nu\leq p-1
\tag{1}
\]

\noindent
By the result in XXX
this matrix is non-singular which gives 
a unique solution
to the following system of  inhomogeneous  linear equations:
\medskip

\[
b_{11}\xi_1+\ldots+b_{1,p-1}\cdot\xi_{p-1}=-2\pi
\]
\[
b_{\nu1}\xi_1+\ldots+b_{\nu,p-1}\cdot\xi_{p-1}=0
\quad\colon 2\leq\nu\leq p-1\,.
\]

\noindent
Set
\[ 
H=\xi_1\omega_1+\ldots+\xi_{p-1}\omega_{p-1}
\]
This gives
\[ 
\int_{\gamma_1}\, H_{{\bf{n}}}\cdot ds=-2\pi\quad
\text{and}
\int_{\gamma_\nu}\, H_{{\bf{n}}}\cdot ds=0\quad\colon\, 2\leq\nu\leq p-1\,.\tag{2}
\]
Recall from XXX that
the sum of the line integrals over
all the boundary curves is zero and hence we have:
\[
\int_{\gamma_p}\, H_{{\bf{n}}}\cdot ds=2\pi\tag{*}
\]
\medskip

\noindent
Since the line integrals of
$H_{{\bf{n}}}$ are integer multiples of $2\pi$ for every 
the boundary curve
the locally defined
harmonic conjugate $V$ of $H$  is 
determined  up to integer  multiples of $2\pi$.
Hence there exists
the analytic function
$f(z)$ in $\Omega$ defined by
\[
f(z)= e^{H(z)+iV(z)}
\]
Along each inner boundary curve
$\gamma_\nu$
we get:

\[
|f(z)|= e^{H(z)}= e^{\xi_\nu}\quad\colon\, 1\leq\nu\leq p-1
\]
and along the outer curve
$\gamma_p$ we have
$|f(z)|=1$. Moreover one has:

\medskip

\noindent
{\bf{7.3 Theorem.}}
\emph{The function $f$ yields a conformal map from
$\Omega$ onto a domain  $\Omega^*$.}
\medskip

\noindent
\emph{Proof.}
The same reasoning as in the proof of Proposition 7.1 gives

\[
\frac{1}{2\pi}\cdot \int_{\gamma_\nu}\, H_{{\bf{n}}}\cdot ds=
\frac {1}{2\pi i}
\int_{\gamma\uuu\nu} \,\frac{f'(z)}{f(z)}\cdot dz
\quad\colon\quad
1\leq\nu\leq p
\]
Moreover, from (2) we have
\[
\int_{\gamma\uuu\nu} \,\frac{f'(z)}{f(z)}\cdot dz=0
\quad\colon\quad
2\leq\nu\leq p\vvv 1
\]
Since the absolute value of $f$ along a curve
$\gamma\uuu\nu$ is the constant $e^{|xi\uuu \nu}$ 
the general result in XX gives
\[ 
|w|\neq e^{\xi\uuu \nu}\implies
\int_{\gamma\uuu\nu} \,\frac{f'(z)}{f(z)\vvv w}\cdot dz=0\tag{1}
\quad\colon\quad
2\leq\nu\leq p\vvv 1
\]
We have also 
\[
\int_{\gamma\uuu p} \,\frac{f'(z)}{f(z)\vvv w}\cdot dz=2\pi
\quad\text{for each}\quad |w|<1
\tag{2}
\]
\[
\int_{\gamma\uuu 1} \,\frac{f'(z)}{f(z)\vvv w}\cdot dz=0
\quad\text{for each}\quad |w|<e^{\xi\uuu 1}
\tag{3}
\]
while (2) is zero if $|w|>1$ and similarly
(3) is zero if $|w|>e^{\xi\uuu 1}$.
Next, since $f$ is a non\vvv constant analytic function
in $\Omega$ we find  some
$w$ such that $f(z)=w$ has at least  one solution where we 
may assume that
$|w|\neq e^{\xi\uuu\nu}$ for all $\nu$ and $|w|\neq 1$.
Let $N(w)$ be the sum of zeros of $f(z)\vvv w$ counted with multiplicities
which by (1) give

\[
2\pi i\cdot N(w)= 
\int_{\gamma\uuu 1} \,\frac{f'(z)}{f(z)\vvv w}\cdot dz+
\int_{\gamma\uuu p} \,\frac{f'(z)}{f(z)\vvv w}\cdot dz
\]
From (2\vvv 3) we see that $N(w)\geq 1$
implies that $|w|<1$ and $|w|>e^{\xi\uuu 1}$ and that
the integer $N(w)$ cannot exceed one.
Hence we have proved the inequality
\[ 
e^{\xi\uuu 1}<1
\] 
and we have also proved
also that $f$ restricts to a conformal map in $\Omega$
since $w\mapsto N(w)$ is the constant one.
\bigskip

\noindent
{\bf{7.4 The image domain $f(\Omega)$.}}
Using (1\vvv 3) above one shows that
$f$ maps the outer curve
$\gamma\uuu p$ onto the unit circle $T$
and $\gamma\uuu 1$ onto the circle of radius $e^{\xi\uuu 1}$.
Next, if $2\leq\nu\leq p\vvv 1$ then
$f$ maps $\gamma\uuu \nu$ onto an interval
$\ell\uuu\nu$ of the circle $\{|z|= e^{\xi\uuu\nu}\}$.
See figure XX for an illustration of the image domain.
\bigskip

\noindent
{\bf{Exercise.}} 
Prove the
assertions in 7.4. 
See also [page xx\vvv xx] in [Ahlfors] for
a discussion and a proof of (7.4).
\bigskip

\noindent
{\bf{Parallell slit regions}} 
Let $\Omega$ as above be a domain in the class
$\mathcal D){\bf{C}}^1)$
with $p$ many boundary curves.
In Chapter V:A.6 we introduced the
function $H(z,\zeta)$ defined in $\Omega\times\Omega$
where Theorem 6.1 in [ibid] shows the symmetry
\[
H(z,\zeta)=H(\zeta,z)
\] 
for each pair of points in $\Omega$.
Moreover
\[
H(z,\zeta)= \log\, |z\vvv\zeta|
\] 
when $z\in\Omega$ and $\zeta\in\partial\Omega$.
We can use $H$ to construct special conformal mappings.
Write $\zeta=\xi+i\eta$ and notice that the function
\[ 
z\mapsto  \frac{\partial}{\partial \xi}\, H(z,\zeta\uuu 0)
\]
is a harmonic of the variable $z$ in $\Omega$.
Keeping $\zeta\uuu 0$ fixed we denote this function
by $u(z)$.
Next, to each inner boundary curve
$\gamma\uuu\nu$ we have the harmonic measure function
$\omega\uuu\nu$ and as explained in Chapter V:A:xx
we find real constants $a\uuu 1,\ldots,a\uuu {p\vvv 1}$
such that if
\[
 U= u\vvv (a\uuu 1\cdot \omega\uuu 1
+\cdots+ a\uuu{p\vvv 1}\cdot \omega\uuu {p\vvv 1})
\]
then $u$ has a single\vvv valued harmonic conjugate $V$ which gives
the analytic function $f(z)= U+iV$ in $\Omega$.
Next, from (xx) we have
the equality
\[
u(z)= \mathfrak{Re}\, \frac{1}{z\vvv \zeta\uuu 0}\quad
\colon\quad z\in\partial\Omega
\]
Let us put

\[ 
p(z)=f(z)\vvv \frac{1}{z\vvv \zeta\uuu 0}
\]
Then we see that $\mathfrak{Re}\, p$ is constant on each boundary
curve.
\bigskip

\noindent
{\bf{Theorem.}}
\emph{The analytic function $p(z)$ yields a conformal mapping from
$\Omega$ onto a  a slit region whose complement consists of
$p$ vertical segments.}
\bigskip

\noindent
{\bf{Remark.}}
Above $p$ maps $\zeta\uuu 0$ to the point at infinity.
Its residue a $\zeta\uuu 0$ is one and
by this normalisation the vertical segments
under a conformal map
as above are determined except for a parallel translation.
\medskip

\noindent
{\bf{Example.}}






 





\newpage



\centerline{\bf\large{ 8. The Bergman kernel.}}

\bigskip

\noindent
{\bf Introduction.} Let $\Omega$ be a bounded and connected
open set in ${\bf{C}}$. Denote by $A^2(\Omega)$
the family of analytic functions
$f(z)$ which are square integrable, i.e
\[
\iint_\Omega\, |f(z)|^2\cdot dxdy<\infty\tag{*}
\]
The space $A^2(\Omega)$ was introduced and studied by
Stefan Bergman whose  text-book [Bergman]
used this  Hilbert space
to 
construct  Riemann's mapping theorem via a kernel function.
A merit of Bergman's approach
is that the similar
Hilbert spaces
can be adapted in several variables, i.e. 
Bergman kernels   exist when one regards
square integrable analytic functions $f(z)$ defined in
domains of ${\bf{C}}^n$ with $n\geq 2$.
Here we only consider
the 1-dimensional case. The starting point
is the observation that if $f(z)$ is analytic in
some open disc $D_R$ of radius $R$ centered at the origin, then
the vanishing  of the integrals
\[ 
\int_0^{2\pi}\, e^{ik\theta}d\theta\quad\colon\quad k\neq 0
\]
implies that with $f(z)=\sum a_nz^n$ one has the equality:
\[
\iint_{D_R}\, |f(z)|^2\cdot dxdy=
\sum\, |a_n|^2\cdot 2\pi\cdot \int_0^R\,r^{2n+1}dr=
\sum\, |a_n|^2\cdot 2\pi\cdot \frac{\,R^{2n+2}}{2n+2}
\]
In particular
\[ |f(0)|^2=|a_0|^2\leq \frac{1}{\pi R^2}
\iint_{D_R}\, |f(z)|^2\cdot dxdy
\]
The square root of the double integral  is by  definition 
$L^2$-norm on $A^2(D_R)$. This gives:
\[
|f(0)|\leq\frac{1}{\sqrt{\pi}\cdot R}\cdot ||f||_2\tag{**}
\]

\noindent
Passing to a domain $\Omega$ we  use
that when  $z_0\in\Omega$ then the open disc of radius
$\text{dist}(z_0,\partial\Omega)$ is contained in $\Omega$.
Since the area integral of $|f|^2$ taken over
$\Omega$ is $\geq$ than that over $D_R(z_0)$
it follows that
\[ 
|f(z_0)|\leq\frac{1}{\sqrt{\pi}\cdot R}\cdot ||f||_2
\quad \colon\quad R=\text{dist}(z_0,\partial\Omega)
\tag{***}
\]
These local  inequalities show  that if
$\{f_\nu\}$ is a Cauchy sequence with respect to the
$L^2$-norm, then the maximum norms
of $|f_\nu-f_j|$ over compact subsets of
$\Omega$ tend to zero. Hence 
$\{f_\nu\}$ converges to an analytic function $f_*$ in $\Omega$ and  one
easily verifies that
$f_*\in A^2(\Omega)$ and that the $L^2$-norms of $f_\nu-f_*$ tend
to zero. This proves that  $A^2(\Omega)$ is a Hilbert space.
Next, (***) shows
that the linear functional on
$f\mapsto f(z_0)$ is continuous on
$A^2(\Omega)$ and
the representation formula for elements in the dual of a
Hilbert space gives a unique function $g(z)\in A^2(\Omega)$
such that
\[ 
f(z_0)=
\iint_\Omega\, f(z)\bar g(z)\cdot dxdy\quad\colon\quad f\in A^2(\Omega)\tag{i}
\]
To find an expression for the $g$-function we choose some orthonormal basis
in $A^2(\Omega)$, i.e. a sequence $\{\phi_\nu(z)\}$
for which
\[
\int_\Omega\, \phi_\nu(z)\bar \phi_j(z)\cdot dxdy=
\text{Kronecker's delta function}\tag{ii}
\]
Now $g(z)$ has an expansion
\[ 
g(z)=\sum\, c_k\cdot\phi_k(z)\tag{iii}
\]
Apply  (i) with $f=\phi_k$. Then   (ii) gives
\[
\phi_k(z_0)=c_k\tag{iv}
\]
\medskip

\noindent
\centerline {\bf 8.1. The kernel function.}
\medskip

\noindent
Define the function $K(\zeta,z)$ on the product space
$\Omega\times\Omega$ by
\[ 
K(\zeta,z)=\sum\,\phi_\nu(\zeta)\cdot\bar  \phi_\nu(z)\tag{1}
\]
The previous results give
\medskip

\noindent
{\bf 8.2 Theorem.} \emph{For every $f\in A^2(\Omega)$ and each
$\zeta\in\Omega$ one has}
\[ 
f(\zeta)=\iint\, f(z)\cdot K(\zeta,z)\cdot dxdy\tag{*}
\]
\medskip

\noindent
{\bf Remark.}
The kernel function $K$ is analytic in
$\zeta$ for each fixed $z$ while it is anti-analytic in
$z$ when $\zeta$ is fixed. A notable point is that
the formula (*) does not depend on the chosen orthonormal basis in
$A^ 2(\Omega)$, i.e. one has the equality

\[ 
K(\zeta,z)=\sum\,\psi_\nu(\zeta)\cdot\bar  \psi_\nu(z)\tag{*}
\]
for \emph{every} orthonormal basis
$\{\psi_\nu\}$ in
$A^2(\Omega)$.
\medskip

\noindent
{\bf 8.3 Transformation laws.}
Let $F\colon\, U\to\Omega$ be an analytic map.
That is, $F\in\mathcal O(U)$ and the image $F(U)\subset\Omega$.
For the moment we do not assume that $F$ is injective and it may occur that
its derivative is zero at some points in $U$. If $g\in\mathcal O(\Omega)$
we get $g^*=g\circ F\in\mathcal O(U)$.
Recall that the Jacobian of the $F$-map is $|F'(z)|^2$.
So if $w=u+iv$ is the complex coordinate in $\Omega$ then

\[
\iint _\Omega |g(w)|^2\cdot dudv= \iint_U\, |g^*(z)|^2\cdot |F'(z)|^2\cdot dxdy\tag{i}
\]
Hence there is  a linear map from $A^2(\Omega)$ into
$A^2(U)$ defined by:

\[
{\bf{T}}\colon\, g(w)\mapsto F'(z)\cdot g^*(z)
\]
Moreover, ${\bf{T}}$ is an isometry,  i.e.
the $L^2$-norms of $g$ and of ${\bf{T}}(g)$ are the same.
So if $\{\phi_\nu\}$ is an orthonormal basis in
$A^2(\Omega)$ then
$\{{\bf{T}}(\phi_\nu)\}$ is an orthonormal family in
$A^2(U)$. The question arises when
this orthonormal family is a basis in $A^2(U)$. From the construction of
${\bf{T}}$ via (ii) above we see that this holds if and only if
the derivative $F'(z)\neq 0$ for all points in $\Omega$ and in addition
$F$  must be 1-1, i.e. $F(z)$ is a conformal map.
Moreover,  when $F$ is conformal
the Remark  after Theorem 8.2 shows
that the kernel function
$K^*(\zeta,z)$ on $U$ becomes:

\[ 
K^*(\zeta,z)= F'(\zeta)\cdot \bar F'(z)\cdot K(F(\zeta),F(z))\tag{**}
\]
where $K$ is the kernel function on $\Omega$.
We refer to (**) as the \emph{transformation law} for Bergman's kernel function.

\medskip

\noindent
{\bf 8.4 An extremal problem.}
Let $\Omega$ as  be some bounded 
and connected domain. 
If $z_0\in\Omega$ we put
\medskip
\[
\lambda^*(z_0)=\max_g\, |g(z_0)\quad\colon\quad ||g||_2=1\tag{i}
\]


\noindent
To find $\lambda^*(z_0)$ and  a maximizing $g$-function
we choose an orthonormal basis and write
\[ 
g(z)=\sum\, c_\nu\cdot\phi_\nu(z)
\]
Now $||g||_2=1$ means that
$\sum\,|c_\nu|^2=1$ so
\[
\lambda^*(z_0)=
\max\,\bigl| \sum c_\nu\cdot\phi_\nu(z_0)\bigr |\quad\colon\, 
\sum\,|c_\nu|^2=1
\]
By the Cauchy-Schwartz inequality the right hand side is majorised by:
\medskip

\[
\sum\,|\phi_\nu(z_0)|^2\quad\colon\quad
\text{for all sequences}\,\,\{c_\nu\}\,\colon
\sum\,|c_\nu|^2=1
\]
Moreover,  equality holds  if and only if there is a complex number
$\rho$ such that
\[
c_\nu=\rho\cdot\bar\phi_\nu(z_0)\quad\colon\quad \nu=1,2,\ldots
\]
Now $\rho$ must be chosen so that
\[
1=\rho^2\sum\,|\phi(z_0)|^2=\rho^2\cdot K(z_0.z_0)\implies
\rho=\frac{1}{\sqrt{K(z_0,z_0)}}
\]
At the same time we get
\[ 
\lambda^*(z_0)=\rho\cdot K(z_0,z_0)
\]
Hence we have proved:
\medskip

\noindent
{\bf 8.5 Theorem.}
\emph{For each $z_0\in\Omega$ one has the equality}
\[ 
\lambda^*(z_0)=\sqrt{K(z_0,z_0)}
\]
\emph{Moreover, the $g$-function which 
maximizes  (i) above is given by}
\[ 
g(z)=\frac{1}{\sqrt{K(z_0,z_0)}}\cdot K(z,z_0)
\]
\medskip

\noindent
{\bf{8.6 The simply connected case.}}
Let $\Omega$ be bounded and simply
connected.
If $a\in\Omega$ we find the conformal mapping
function $f_a\colon \Omega\to D$
using the Kernel function.
The result is
\medskip

\noindent
{\bf{8.7 Theorem.}}
\emph{The conformal map $f_a$ is given by}
\[ 
f_a(z)= \sqrt{\frac{\pi}{K(a,a)}}
\cdot \int_a^z\, K(z,a)dz
\]
\medskip

\noindent
{\bf{Exercise.}} Prove this result. The hint is to 
use the various extremal properties satisfied
by the mapping function $f_a$.
\medskip

\noindent
{\bf{8.8 Orthogonal polynomials.}}
Let $\Omega$ be a bounded simply connected domain.
The Gram-Schmidt construction gives
a special orthonormal basis in $A^2(\Omega)$ given by a sequence of polynomials
$\{P_n(z)\}$ where  $P_n$ has degree $n$ and
\[ 
\iint\, P_k\cdot \bar P_m\cdot dxdy=
\text{Kronecker's delta function}
\]
One expects that these polynomials are related to
a mapping function.
We shall consider the case
when
$\Omega$ is a Jordan domain whose boundary
curve
$\Gamma$ is \emph{real-analytic}.
Let $\phi$
be the conformal map
$\phi$ from the \emph{exterior domain}
$\Omega^*=\Sigma\setminus\bar\Omega$ onto
the exterior disc $|z|>1$.
Here $\phi$ is normalised so that it maps the point at infinity
into itself.
The inverse conformal mapping function
$\psi$   is defined in $|z|>1$ and has a series expansion
\[ 
\psi(z)=\tau\cdot z+ \tau_0+\sum_{\nu=1}^\infty\, \tau_\nu\cdot
\frac{1}{z^\nu}\tag{*}
\]
where $\tau$ is a positive real number.
The assumption that $\Gamma$ is real-analytic gives
some $\rho_1<1$ such that
$\psi$ extends to a conformal map from the
exterior disc $|z|>\rho_1$ onto a domain whose compact
complement is contained in $\Omega$.
It turns out that the polynomials $\{P\uuu n\}$
are  approximated 
by functions expressed by
$\phi$ and is complex derivative
on $\partial\Omega$.

\newpage

\noindent
{\bf{8.9 Theorem.}}
\emph{There exists a constant $C$ which depends upon $\Omega$ only
such that to every
$n\geq 1$ there is a function $\omega_n(z)$ defined in
$\Omega^*$ and}
\[
 P_n(z)=
 \sqrt{\frac{n+1}{\pi}}
 \cdot \phi'(z)\cdot \phi(z)^n\cdot
 \bigl[1+\omega_n(z)\bigr]
 \quad\text{holds on }\quad \partial \Omega
 \]
\emph{Finally the $\omega$-functions satisfy}
\[ 
\max_{z\in\partial \Omega}\,\, |\omega_n(z)|\leq
C\cdot \sqrt{n}\cdot \rho_1^n\quad\colon\quad n=1,2,\ldots
\]

\medskip

\noindent
{\bf{Remark.}}
Theorem  8.10 stems
from Faber's
article 
\emph{†ber Tschebycheffsche Polynome} from 1920.
The subsequent proof is taken from  the article  
[Carleman]
\medskip

\medskip

\noindent
\emph{Proof.}
Let $n\geq 2$ and consider the set of polynomials
$Q(z)$ of degree $n$ whose highest term is $z^n$.
Keeping $n$ fixed we set
\[ 
I\uuu *(n)=\min\uuu{Q}I(Q)= \, \iint\uuu \Omega\, |Q(z)|^2\cdot dxdy
\]
Given a polynomial $Q$ as above we choose a primitive polynomial $R(z)$. So here
\[ 
R(z)=\frac{z^{n+1}}{n+1}+ b\uuu nz^n+\ldots+b\uuu 0
\]
\medskip

\noindent
{\bf{1. Exercise.}} Use Green's formula to show that

\[
I(Q)=\frac{1}{4}\int\uuu {\partial \Omega}\, \partial\uuu n(|R|^2)\cdot ds
\] 
where $ds$ is the arc\vvv length measure on $\partial\Omega$
\medskip

\noindent
Now we use the inverse conformal  map $\psi(\zeta)$ and set

\[ 
F(\zeta)= R(\psi(\zeta))
\]
Then $F$ is analytic in the exterior disc $|\zeta|>1$
and (*) above Theorem 8.9 entails that
$F$ has the series expansion

\[
F(\zeta)=\tau^{n+1}\bigl[ \frac{\zeta^{n+1}}{n+1}+
A\uuu n\zeta^n+\ldots+A\uuu 1\zeta+A\uuu 0+
\sum\uuu{\\nu=1}^\infty\, \alpha\uuu\nu\cdot \zeta^{\vvv \nu}\bigr]\tag{i}
\]
\medskip

\noindent
{\bf{2. Exercise.}}
Use a variable substitution via $\psi$ to show that the integral in Exercise 1
is equal to

\[
\int\uuu {|\zeta|= 1}\, \frac{d}{dr}( |F(e^{i\theta})|^2\cdot d\theta
\]
and use the series expansion (i) to show that this integral is equal to

\[ 
\pi\cdot \tau^{2n+2}\cdot [\frac{1}{n+1}+ \sum\uuu {k=1}^{k=n}\,
k\cdot |A\uuu k|^2\vvv
\sum\uuu{\\nu=1}^\infty\, \nu\cdot |\alpha\uuu\nu|^2\,\bigr]
\]
\medskip

\noindent
{\bf{An upper bound for $I\uuu *$}}.
The coefficients $A\uuu 1,\ldots,A\uuu n$ are determined via $Q$.
The reader may verify that there exists a polynomial $Q(z)$
with highest termÊ$z^n$ such that
$A\uuu 1=\ldots=A\uuu n=0$.
It follows that

\[
I\uuu *\leq \pi\cdot \tau^{2n+2}\cdot [\frac{1}{n+1}
\vvv
\sum\uuu{\nu=1}^\infty\, \nu\cdot |\alpha\uuu\nu|^2\,\bigr]
\leq \pi\cdot \tau^{2n+2}\cdot \frac{1}{n+1}\tag{*}
\]
\medskip

\noindent
{\bf{A lower bound for $I\uuu *$}}.
The upper bound (*) did not use that
$\partial\Omega$ is real\vvv analytic, i.e. it is valid for
every Jordan domain whose boundary curve is of class $C^1$.
To get a lower bound we choose some $\rho\uuu 1<\rho<1$
and by assumption $\psi$
maps the exterior disc
$|\zeta|>\rho$ conformally to an exterior domain
$U^*=\Sigma\setminus \bar U$ where $U$  is a relatively compact
Jordan  domain inside $\Omega$.
Let $Q$ be a polynomial for which $I(Q)=I\uuu *$.
Now $\Omega\setminus \bar U$ is contained in $\Omega$ so we have

\[
I\uuu*> \iint{\Omega\setminus \bar U}\,|Q(z)|^2\cdot dxdx\tag{i}
\]
\medskip

\noindent
{\bf{3. Exercise.}}
Show that the integral in (i) is equal to

\[
\int\uuu {|\zeta|= 1}\, \frac{d}{dr}( |F(e^{i\theta})|^2\cdot d\theta
\vvv
\int\uuu {|\zeta|= \rho}\, \frac{d}{dr}( |F(e^{i\theta})|^2\cdot \rho\cdot d\theta=
\]
\[
\pi\cdot \tau^{2n+2}\cdot 
[\frac{1\vvv \rho^{2n+2}}{n+1}+ 
\sum\uuu {k=1}^{k=n}\,
k\cdot |A\uuu k|^2\cdot (1\vvv \rho^{2\nu})+
\sum\uuu{\\nu=1}^\infty\, \nu\cdot |\alpha\uuu\nu|^2
\cdot (\frac{1}{\rho^{2\nu}}\vvv 1)\,\bigr]\tag{ii}
\]
\medskip

\noindent
The last equality gives the lower bound

\[ 
I\uuu *\geq\frac{\pi}{n+1}\cdot \tau^{2n+2}\cdot (1\vvv \rho^{2n+2})\tag{**}
\]
\medskip

\noindent
Moreover the upper bound and  (ii) give the inequality

\[
\sum\uuu {k=1}^{k=n}\,
k\cdot |A\uuu k|^2\cdot (1\vvv \rho^{2\nu})+
\sum\uuu{\\nu=1}^\infty\, \nu\cdot |\alpha\uuu\nu|^2
\cdot (\frac{1}{\rho^{2\nu}}\vvv 1)\,\leq \frac{\pi}{n+1}\cdot \rho^{2n+2}
\]
Since $1\vvv \rho^2\leq 1\vvv \rho^{2\nu}$ for every $\nu\geq 1$
it follows that

\[
\sum\uuu {k=1}^{k=n}\,
k\cdot |A\uuu k|^2+
\sum\uuu{\\nu=1}^\infty\, \nu\cdot |\alpha\uuu\nu|^2\leq
\frac{\pi}{(1\vvv\rho^2)\cdot n+1}\cdot \rho^{2n+2}\tag{***}
\]
\medskip

\noindent
{\bf{Conclusion.}}
Recall that $F(\zeta)= R(\psi(\zeta)$ and $R'=Q$. So after a derivation 
we get

\[ 
F'(\zeta)= \psi'(\zeta)\cdot Q(\psi(\zeta))
\]
Hence the series expansion  of $F(\zeta)$ gives

\[
Q(\psi(\zeta))=
\frac{\tau^{n+1}}{\psi'(\zeta)}\cdot \bigl[
\zeta^n+
\sum\uuu {k=1}^{k=n}\, k\cdot A\uuu k\zeta^{k\vvv 1}
+\sum\uuu {\nu=1}^\infty \, \nu\cdot \alpha\uuu\nu \cdot \zeta^{\vvv \nu\vvv 1}\,\bigr]\tag{i}
\]
where the equality holds for $|\zeta|>\rho$.
Put

\[
\omega^*(\zeta)=
\sum\uuu {k=1}^{k=n}\, k\cdot A\uuu k\zeta^{k\vvv 1}
+\sum\uuu {\nu=1}^\infty \, \nu\cdot \alpha\uuu\nu \cdot \zeta^{\vvv \nu\vvv 1}
\]
When $|\zeta|=1$ the triangle inequality gives
\[
|\omega^*(\zeta)|\leq
\sum\uuu {k=1}^{k=n}\, k\cdot |A\uuu k|
+\sum\uuu {\nu=1}^\infty \, \nu\cdot |\alpha\uuu\nu|\tag{ii}
\]
\medskip

\noindent
{\bf{4. Exercise.}}
Notice  that (***) holds for every $ \rho>\rho\uuu 1$
and use this together with suitable Cauchy\vvv Schwarz inequalities to show that
(i) above gives a constant $C$ which is independent of $n$ such that


\[
|\omega^*(\zeta)|\leq C\cdot  \sqrt{n}\cdot \rho\uuu 1^{n+1}
\]

\medskip

\noindent
\emph{Final part of the proof.}
Since $\psi$ is the inverse of $\phi$ we have
\[
\psi'(\phi(z))\cdot Q(\psi(\phi(z)= \frac{Q(z)}{\phi'(z)}
\]
Then (iii) in the conclusion implies that
if  we define the function  $\partial\Omega$ by
 
\[
\omega\uuu n(z)=\frac{\omega^*(\phi(z))}{\phi'(z)}
\]
then we have

\[
Q(z)= \tau^{n+1}\cdot \phi'(z)\cdot [\phi(z)^n+\omega\uuu n(z)\,\bigr]
\]
where Exercise 4 shows that $|\omega\uuu n(z)|$ satisfies the estimate in
Theorem 8.5. 
Finally, the $Q$\vvv polynomial minimized th $L^2$\vvv norm
under the constraint  that the leading term is $z^n$ and for this variational problem
he upper and the lower bounds in (*\vvv **) above show that
the minimum $I\uuu *(n)$ satisfies


\[ 
|I\uuu *(n)\vvv\frac{\pi}{n+1}\cdot \tau^{2n+2}|\leq 
\frac{\pi}{n+1}\cdot \tau^{2n+2}\cdot \rho^{2n+2}
\]
So if we normalise $Q$ so that its $L^2$\vvv norm is one and hence gives
the polynomial $P\uuu n(z)$
then the factor $\tau^{n+1}$
is replaced by
$\frac{\sqrt{n+1}}{\sqrt{\pi}}$ which finishes the proof of
Theorem 8.10.








\newpage



\centerline {\bf\large{ 9. The  electric equilibrium potential.}}
\bigskip

\noindent
{\bf Introduction.}
Let $\Gamma$ be a closed Jordan curve of class
$C^1$.
We seek a positive 
density function
$\mu(s)$ where $ds$ is the arc-length measure
on $\Gamma$ whose  the logarithmic potential 
is constant on $\Gamma$. It turns out that
$\mu$ is found from a conformal mapping.
Namely, consider the \emph{exterior domain}
$\Omega^*$ which is bounded by $\Gamma$. So 
the Jordan domain $DU$  bordered by
$\Gamma$ is the open complement of
$\bar\Omega^*$.
Adding the point at infinity we get the simply connected
set $\Omega_\infty=\Omega^*\cup\infty$. Riemann's mapping theorem
gives a conformal map $f$ from
$\Omega_\infty$ onto the exterior disc $|w|>1$ which
maps the point at infinity to the point
at infinity . This means that there is some real number $a>0$ and
$f(z)\simeq  az$ as $|z|\to\infty$.
Now we shall  prove that the function defined on
$\Gamma$ by
\[
z_*\mapsto \int_\Gamma\,\log\bigl(\,\frac{1}{|z-z_*|}\bigr)\cdot 
\frac{|dz|}{|f'(z)|}
\tag{*}
\]
is constant.
To get  this we set $w=f(z)$ and  $\phi(w)$ is the inverse function.
So here $\phi$ is analytic in
$|w|>1$ and
the conformal map gives the arc-length
formula
\[
|dw|=\frac{|dz|}{|f'(z)|}
\]
Hence (*) amounts to show that
\[
\theta_*\mapsto \int_0^{2\pi}\, 
\log \bigl(\,\frac{1}{|\phi(e^{i\theta})-\phi(e^{i\theta_*})|} \bigr)
\cdot d\theta\tag{**}
\]
is a constant function of
$\theta_*$.To prove this we use that
the image set
$\phi(T)=\Gamma$ which enable us to
define a function in $U$ by:
\[
H(z)= 
\int_0^{2\pi}\, 
\text{Log}\bigl(\,\frac{1}{|\phi(e^{i\theta})-z|}\bigr)\cdot d\theta
\]
This is a harmonic function in
$U$ given by the real part
of 
\[
z\mapsto 
\int_0^{2\pi}\, 
\text{Log}\bigl(\,\frac{1}{\phi(e^{i\theta})-z}\bigr)\cdot d\theta
\]
Passing to  the complex derivative we get
\[
H_x-iH_y=
 \int_0^{2\pi}\, 
\,\frac{d\theta }{\phi(e^{i\theta})-z}\quad\colon\quad z\in D\tag{1}
\]
With $z\in D$ kept fixed, the right hand side
can be written as a complex line integral:
\[
 \int_{|w|=1}
 \frac{1}{\phi(w)-z}\cdot \frac{dw}{iw}\tag{2}
\]
Now 
the $\phi$-image of $\{|w|>1\}$ is contained in
$\Omega^*$ so $z\in U$ stays  outside this set.
By Cauchy's theorem we can therefore shift
the integration to circle $|w|=R$ with $R>1$ and hence
(2) becomes:
\[
 \int_{|w|=R}
 \frac{1}{\phi(w)-z}\cdot \frac{dw}{iw}\tag{3}
\]
Next, we have $\phi(w)\simeq\frac{w}{a}$
when
$|w|\to\infty$.
It follows that (3) tends to zero when
$R\to+\infty$.
This proves that
(1) is identically zero as $z$ varies on $U$
and hence the harmonic function
$H(z)$ is  constant.
Finally, 
$H(z)$ extends to a continuous function on the closed
Jordan domain
$\bar U$ and we conclude that the function from
(**) is constant.



\bigskip


\centerline {\bf 9.1 A special class of curves}. 
\medskip

\noindent
Let $\Gamma$
be a closed Jordan curve
whose curvature $\rho$ is $\neq 0$ at all points.
One may ask when
the equilibrium density
$\mu_\Gamma$   is proportional to a
fractional power of $\rho$, i.e.   when
there exists some $\beta>0$ and a positive constant $k$
such that
\[
\mu_\Gamma(z)^\beta=k\cdot \rho(z)\quad\colon\quad z\in \Gamma\tag{*}
\]
\medskip

\noindent
To find such example we
consider for a given $\gamma$ the conformal mapping
$F(z)$ from the exterior disc
$|z|>1$ onto the exterior domain bounded by $\Gamma$.
The curvature formula from ¤ 4:xx  shows that if $f=F'$ is the complex derivative
then
\[ 
\frac{1}{\rho}=
\frac{1}{|f(z)|}\cdot \mathfrak {Re}\,
(z\cdot \frac{f'(z)}{f(z)}+1)\quad\colon\quad |z|=1
\]
Hence (*) holds for those $\gamma$ where the associated mapping function
$F$ satisfies
\[
\mathfrak {Re}\,
(z\cdot \frac{f'(z)}{f(z)}+1)
=k\cdot |f(z)|^\kappa
\quad\colon\quad |z|=1
\]
for some pair of positive constants $k,\kappa$. We shall find all non-trivial conformal mappings
where $\Gamma$ is not a circle.
\medskip

\noindent
{\bf{9.2 Theorem.}}
\emph{The non-trival class of   conformal mappings
for which (*) hold are those where the complex derivative is of the form}
\[ 
f(z)= k(1+\frac{a}{z^m})^{\frac{2}{m}}
\]
\emph{where $k>0$, $|a|<1$ and $m\geq 2$ is an integer.}

\medskip

\noindent
The proof has two ingredients. First we show that
every $f$ as above is the complex derivative of a mapping function
$F$ for which the requested equation (*) is satisfied for a pair $k,\beta$.
The more involved part of the proof is to show that
no other cases exist.
\medskip

\noindent
{\bf{The case $m=2$}}.
With $f$ as above the primitive function becomes
\[ 
F(z)= k(z\vvv\frac{a}{z})
\]
By a scaling we may assume that $k=a=1$ so that
\[ 
f(z)= 1\vvv \frac{1}{z^2}
\]



\noindent
{\bf{Exercise.}} Show that  $F$ yields a bijective map from
$|z|=1$ onto an ellipse $\mathcal C$ and that (xx) above holds
and determine 
the constant $\kappa$.


\medskip

\noindent
{\bf{The case $m\geq 3$.}}
We may assume that $k=1$ and $0<a<1$ is real. 
In $|z|>1$ we have the analytic function
\[
f(z)= (1+\frac{a}{z^m})^{\frac{2}{m}}
\]
It extends to be analytic at ther point at infinity
and from I:¤ XX we have the newton expansion below where
we set
$\beta=\frac{2}{m}$:
\[
f(z)= 1+\sum\uuu{k=1}^\infty
\, \binom{\beta}{ k}\cdot \frac{a^k}{z^{mk}}
\]
The primitive function becomes:
\[ 
F(z)= z\vvv\sum\uuu{k=1}^\infty\binom{\beta}{ k}\cdot 
\frac{a^k}{mk\vvv 1}\cdot \frac{1}{z^{mk+1}}
\]
\medskip

\noindent
{\bf{Proposition.}}
\emph{The function $F$ yields a conformal mapping from
$\{|z|>1\}$ onto the exterior of a Jordan domain.}
\medskip

\noindent
\emph{Proof.}
It is clear  that the complex derivative
$f\neq 0$ in $|z|>1$ and there remains to show that
$F$ is 1\vvv 1.
To show this we take a pair $z\uuu 1\neq z\uuu 2$ in
$|z|>1$
and write
\[
\frac{F(z\uuu 1)\vvv F(z\uuu 2)}{z\uuu 1\vvv z\uuu 2}=1+P(z\uuu 1,z\uuu 2)
\]


A trivial computation which is left to the reader shows that
\[
P(z\uuu 1,z\uuu 2)=\frac{1}{z\uuu 1 z\uuu 2}\cdot
\sum\uuu{k=1}^\infty 
\frac{a^k}{km-1}\cdot\binom{\beta}{k}\cdot\bigl[
\frac{1}{z_1^{km-2}} +
\frac{1}{z_1^{km-3}}
\cdot\frac{1}{z_2}+\ldots+\frac{1}{z_1}\cdot\frac{1}{z_2^{km\vvv 3}}
\frac{1}{z_2^{km-2}}
\bigl]
\]



\noindent
Since $m-1\leq km-1$ when  $k\geq 2$ and 
each $z\uuu\nu$ has abslute value $\geq 1$, 
the triangle inequality gives:
\[ 
|P(z\uuu 1,z\uuu 2)|\leq \sum\uuu{k=1}^\infty 
a^k\cdot\binom{\beta}{k}=(1+a)^\beta\vvv 1
\]
\medskip

\noindent
Finally, since $0<a<1$ 
the last term is $<1$ and hence  (i) is $\neq 0$ which means that
$F(z\uuu 1)\neq F(z\uuu 2)$ as requested.
\medskip

\noindent
{\bf{Conclusion.}}
Proposition 9.3 gives the conformal mapping $F$
and we get the Jordan curve
$\Gamma=F(T)$. We leave it as an exercise to prove that
(xx) holds for some $\kappa$ and remark only that a computation gives
\[
\kappa= XXX
\]
\bigskip

\centerline
{\emph{Proof of necessity.}}
\medskip

\noindent
There remains to show that the examples above exhaust all possible cases.
The idea is to introduce the analytic function in the disc
$D=\{|z|<1\}$ defined by
\[ 
g(z)= \bar f(\frac{1}{\bar z})\tag{i}
\]
Since $f\neq 0$ in the exterior disc, it follows that
$g$ is zero\vvv free in $D$
and we know from ¤ xx that $f$ and hence also $g$ extend to
continuous functions on
$|z|=1$ where both remain zero\vvv free.
Notice that
\[
g'(z)= \vvv \frac{1}{z^2}\cdot \bar f'(z)\quad\colon\quad |z|= 1\tag{ii}
\]
Using (ii) it is easily seen that (**) above Theorem 9.1
entails that
\[
1+\frac{z}{2}[\frac{f'(z)}{f(z)}\vvv\frac{g'(z)}{g(z)}\,]=
k\cdot f(z)^\kappa\cdot g(z)^\kappa\quad\colon\quad |z|= 1\tag{iii}
\]

\noindent
{\bf{The case $\kappa=0$}}.
Then (iii) gives
\[
\frac{f'(z)}{f(z)}\vvv\frac{g'(z)}{g(z)}= \frac{2(k\vvv 1)}{z}\quad\colon\quad |z|= 1
\]
It follows that
\[
f(z)= A\cdot g(z)\cdot z^{2(k\vvv 1)}
\]
holds for some constant $A$.
\bigskip

FINISH EASY....

\medskip

\noindent
{\bf{The case $\kappa\neq 0$}}.
Since $f$ is zero\vvv free we can consider the function
$\phi= f^{\vvv\kappa}$
and rules for derivatives show that (iii) gives the differential equality
\[
\frac{d}{dz}(\phi(z))\vvv \kappa
\bigl(\frac{2}{z}\vvv \frac{g'(z)}{g(z)}\bigr)
\cdot \phi(z)= \vvv\frac{2k\kappa}{z}\cdot g^{\vvv\kappa}(z)\tag{1}
\]
Since $g$ is zero\vvv free in $D$ i follows that
$g^{\vvv\kappa}$ also is analytic in $D$ and (1) can be regarded as a
first order Fuchsia equation where we seek $\phi$
so that
\[ 
\nabla(\phi(z))\vvv (2\kappa\vvv A(z))\phi(z)= B(z)
\]
Above we have put  $\nabla =z\partial\uuu z$ and 
\[ 
A(z)= \kappa z\cdot \frac{g'}{g}\quad\colon\quad B=
\vvv 2k\kappa\cdot g^{\vvv\kappa}(z)
\]
In particular $A(0)=0$ and provided that $m\vvv 2\kappa\neq 0$ for all positive integers
$m$, 
a formal recursion shows that 
the Fuchsian equation has a unique solution
$\phi(z)$ in $D$ where
\[ 
\phi(0)=k\cdot g(0)^{\vvv\kappa}
\]
So when $m\vvv 2\kappa\neq 0$ for all positive integers $m$, it follows that
$\phi(z)$ extends to an analytic function in $D$
which means that $f^{\vvv\kappa}$ extends 
from $|z|>1$ to an entire function.
As $z\to\infty$ we know that $f(z)$ is bounded and non\vvv zero so
the entire function $f^{\vvv\kappa}$ will
be bounded and hence reduced to a constant,  i.e. the derivative of 
the conformal mapping $F$ is reduced to a constant which entails that
$F(z)$ just is a linear function in $z$ and then
$\Gamma=f(T)$ is a circle.
 \medskip
 
 \noindent
There remains to consider the case when
$\kappa=m/2$ for some positive integer $m$.
Then the Fuchsian equation
is not directly solved by a formal recursion.
However, with $2\kappa=m$
the equation becomes
\[
xxx
\]  


FINISH easy ....






\newpage


\centerline {\bf\large{10. Conformal maps of circular domains.}}

\medskip

\noindent
{\bf Introduction.}
In 1906 Koebe proved a
result about conformal mappings between
domains bordered by a finite set of circles.
Let $p\geq 2$
and denote by $\mathcal C^*(p)$ the family of connected
bounded  domains $\Omega$ in ${\bf{C}}$ for which
 $\partial\Omega$ is the union of $p$ many disjoint circles.
\medskip

\noindent
{\bf Theorem.} \emph{Let
$f\colon\Omega\to U$
be a conformal map between two domains in
$\mathcal C^*(p)$. Then $f(z)$ is a linear function, i.e.
$f(z)=Az+B$ for some constants $A$ and $B$.}
\medskip

\noindent
Koebe's  original proof  used reflections over the boundaries and
results related  to the uniformisation theorem.
A more direct  proof was given by Carleman in [Car] which we expose
below.  It teaches how to
compute certain winding numbers in  specific situations.
\medskip

\noindent
Let $f$ be a mapping function as above.
Let $\Omega$ be
bordered by circles $C_1,\ldots,C_p$ where $C_p$ is the outer
circle. Similarly  $U$ is  bordered by
$C_1^*,\ldots,C_p^*$. Then $f$ must map $C_p$ to $C^*_p$
and the remaining discs are arranged so that
$f$ maps $C_\nu$ onto $C^*_\nu$ for $1\leq\nu\leq p-1$.
Using a linear map of the outer discs we may assume from the start that
$C_p=C_p^*=T$ where $T$ is the unit circle.
Moreover, after a suitable rotation we may also assume
that the map $f\colon T\to T$ has at least 3 fixed points.
There remains to show that when this holds, then
$f(z)=z$ must be the identity map.
To prove this we shall argue by a contradiction. Namely,
if $f(z)$ is not the identity we get the non-constant
function
\medskip

\[ 
\phi(z)=f(z)-z\tag{*}
\]
\medskip

\noindent {\bf Notations.}
To each $1\leq \nu\leq p$ we denote by $n^{(\nu)}$ the number of zeros
of $\phi$ counted with multiplicities which belong to  $C_\nu$.
We also set


\[
J_\nu=\frac{1}{2\pi i}\cdot \int_{C_\nu}\,\frac{\phi'(z)}{\phi(z)}\cdot dz\quad\colon\quad
1\leq\nu\leq p
\]
\medskip

\noindent
Now we will derive a contradiction using residue formulas to
compute these $J$-numbers. For each $1\leq\nu\leq p-1$
one encounters nine different case which are listed below:


\medskip

\centerline{\bf Separate cases.}
\medskip

\noindent
Let $1\leq\nu\leq p-1$ be given.
Then $J_\nu$ is found by the equations below
depending on the positions of the
two circles $C_\nu$ and $C^*_\nu$:
\medskip

\noindent
\emph{Case 1: $C_\nu=C_\nu^*$. } Here
\[ 
J_\nu= 1+\frac{1}{2}\sum\, n_k^{(\nu)}
\]

\noindent
\emph{Case 2}: $C_\nu$ and $C^*_\nu$ are exterior to each
other, i.e. $C_\nu^*$ is outside the closed
disc bordered by $C_\nu$. Then
\[ 
J_\nu= 0
\]

\noindent
\emph{Case 3}: $C_\nu$ inside the open disc bordered by
$C_\nu^*$ or
conversely $C_\nu^*$ inside the open
disc bordered by $C_\nu$. Then
\[
J_\nu= 1
\]

\noindent
\emph{Case 4}: $C_\nu\cap C_\nu^*$ consists of two points
$P,Q$, none of which is a zero of $\phi$. Then
\medskip

\[
J_\nu= 0,1,2\,\,\text{i.e. one of these numbers are attained}
\]

\noindent
\emph{Case 5}: $C_\nu\cap C_\nu^*$ consists of two points
$P,Q$ where one of these two points is a zero of
$\phi$ of some multiplicity $e$. Then
\medskip

\[
J_\nu= \frac{1+e}{2}\,\,\text{or equal to}\,\, \frac{3+e}{2}
\]

\noindent
\emph{Case 6}: $C_\nu\cap C_\nu^*$ consists of two points
$P,Q$ where both are zeros of $\phi$ with multiplicity
$e$ and $f$. Then
\medskip

\[
J_\nu= 1+\frac{e+f}{2}
\]
\noindent
\emph{Case 7}: $C_\nu$ and $C_\nu^*$ has a
a common tangential  point $P$ which is not a zero of
$\phi$. See Figure XX for this case. Then
\medskip


\[
J_\nu=0\,\,\text{or equal to}\,\, 1 
\]
\noindent
\emph{Case 8}: $C_\nu\cap C_\nu^*$ is reduced to a single point $P$
and are otherwise external to each other and $P$
is a zero of $\phi$ with multiplicity $e$. Then
\medskip


\[
J_\nu=\frac{1+e}{2}
\]
\noindent
\emph{Case 9}: $C_\nu\cap C_\nu^*$ is reduced to a single point $P$
and this time
$C_\nu$ is contained in the closed disc bordered
by
$C^*_\nu$ or vice versa and
$p$ is a zero of $\phi$ of 
multiplicity $e$. Then
\medskip
\[
J_\nu=\frac{k+e}{2}+ \quad\colon\quad k=1,2,3
\]
\bigskip

\noindent
{\bf {Exercise.}} Verify the nine formulas above.
A hint is that the conformal mapping $f$
restricts to bijective map from  $C_\nu$ onto $C_\nu^*$
and 
preserves orientation.
\bigskip

\noindent{\bf Conclusion.} For each $1\leq\nu\leq p$
we have found that  $J$-number is $\geq 0$.
Next, on the outer circle $T$
we have
\[
J_1=\frac{1}{2\pi i}\cdot \int_T\,\frac{\phi'(z)}{\phi(z)}\cdot dz
=1-\frac{1}{2}\cdot N_T(\phi)
\]
where $N_T(\phi)$ is the number of zeros of $\phi$ on the unit circle counted
with multiplicities.
By the hypothesis $N_T(\phi)\geq 3$
Hence $J_1\leq-\frac{1}{2}$
is strictly negative.
Now we get a contradiction. Namely, let
$\mathcal N_\Omega (\phi)$ be the number of zeros of
$\phi$ in the open domain $\phi$. Then we have  the general formula:
\medskip

\[
\mathcal N_\Omega (\phi)= J_1-(J_2+\ldots+J_p)\tag{*}
\]
But this is a contradiction,  i.e. the left hand side is a non-negative integer
and by the above the right hand side is $<0$. Hence
the $\phi$-function must be identically zero which proves
Koebe's theorem.





\newpage

\centerline{\bf{Metrics with non-positive curvature and the Riemann-Schwarz inequalitiy.}}
\bigskip


\noindent
Let $D$ be the unit disc.
Every conformal mapping of $D$ onto itself is
given by a Mšbius map
\[ 
S(z)= 
e^{i\theta}\frac{z-\alpha}{1-\bar\alpha\cdot z}\tag{1}
\]
The fact that (1) is a conformal mapping  was  demonstrated 
in Chapter 1 where one  constructs the inverse map.
Conversely, if $S$ is an arbitrary conformal map and
$S(0)=\alpha$
then
the composed map 
\[ 
z\mapsto \frac{S(z)-\alpha} {1-\bar\alpha\cdot S(z)}\tag{2}
\]
is again a conformal map which sends the origin into itself and 
Schwarz Lemma entails that (2) is 
given by $z\mapsto e^{i\theta}\cdot z$
for some
$e^{i\theta}$ which implies
that
$S$ is a 
Mšbius map.
Next, a circular arc $\alpha$ in $D$
is called a curve of symmetry
if  intersects the unit circle $T$ at  right angles.
In this family we  include diameters , i.e. line segments which
intersect $T$ at a pair $e^{i\theta}$ and $-e^{-i\theta}$.
Since every Mšbius transform is conformal it preserves the family of
curves of symmetry.
In fact, each Mšbius transformation $S$ yields a bijective map on this family.
\medskip

\noindent
{\bf{Definition.}}
\emph{A conformal rhomb in $D$ consists of 
pair of curves of symmetry $\alpha,\beta$ 
which intersect at a right angle.}
\bigskip

\noindent{\bf{0.1 Theorem.}}
\emph{For each conformal rhomb
$(\alpha,\beta)$ and every subharmonic function $u$
in $D$ which extends to be continuous on the closed unit disc
one has the inequality}

\[
\bigl(\int_\alpha\, e^{u(z)}\,|dz|\bigr)^2+
\bigl(\int_\beta\, e^{u(z)}\,|dz|\bigr)^2\leq\frac{1}{4}\cdot
\bigl(\int_T\, e^{u(z)}\,|dz|\bigr)^2\tag{*}
\]
\medskip


\noindent
Theorem 0.1 can be applied to
general connected domains
$\Omega$ in ${\bf{C}}$-equipped with a 
$\lambda$-metric where
$\lambda= e^u$ for a subharmonic and continuous function
$u$ in $\Omega$.
More precisely, for
each rectifibale curve $\gamma$
in $\Omega$ we set
\[
\ell(\gamma)= \int_\gamma\, \lambda(z)\,|dz|
\]
Let us then consider a pair of points $a,b$ in $\Omega$
and the family $\mathcal C(a,b)$
of curves which have $a,b$ as end-points.
\medskip

\noindent
{\bf{0.2 Theorem.}}
\emph{For each pair of curves
$\gamma_1,\gamma_2$ in $\mathcal C(a,b)$ and
every point $p\in\gamma_1$ there exists
a point $q\in \gamma_2$
and a pair of curves
$\alpha\in \mathcal C(a,b)$ and 
$\beta\in\mathcal C(p,q)$ such that}
\[
\ell(\alpha)^2+\ell(\beta)^2\leq
\frac{1}{2}\cdot \bigl(\ell(\gamma_1)^2+\ell(\gamma_2)^2\,\bigr)\tag{**}
\]

\medskip


\noindent
We refer to this as the Riemann-Schwrz inequality.
The proof requires several steps and is not finished until
¤ 1.8.
We begin with some special considerations.











\medskip


\centerline 
{\bf{1.1. A special class of Mšbius transformations.}}
\medskip

\noindent
Let $0<b<1$ be real and set
\[
 S(z)= \frac{b-z}{1-bz}\quad\colon\quad 0<b<1
\]
The composed map becomes
\[ 
S^2(z)=
\frac{b-\frac{b-z}{1-bz}}{1- b\cdot \frac{b-z}{1-bz}}=z
\] 
where the last equality follows by a trivial calculation.
Notice that $S$ maps the real diameter
$-1<x<1$ into itself. To be precise,
$S(-1)= 1$ and
after $x\mapsto S(x)$ is a decreasing function with
$S(1)=-1$.
Next, on the unit circle we find
a point $e^{i\theta}$ such that
\[
e^{-i\theta}= S(e^{i\theta})
\]
A computation which is left to the reader shows that
\[ 
\cos\theta=b
\]
Let $\alpha$ be the circle which passes through
$e^{i\theta}$ and $e^{-i\theta}$
and intersects $T$ with right angles at these points.
This holds when the center of the disc containing $\alpha$ 
belongs to the positive real $x$-axis and the reader
can verify that
$\alpha$ contains the real point $0<x_0<1$ which solves the
equation
\[
x_0= \frac{b-x_0}{1-bx_0}\implies x_0=\frac{1-\sqrt{1-b^2}}{b}
\]
The reader may verify that
$S$ maps the circular arc $\alpha$ into itself, i.e.
$\alpha$ is $S$-invariant.
\medskip

\noindent
{\bf{1.2 Exercise.}}
Draw some figures to illustrate how $S$ maps circular arcs
which are lines of symmetry and
intersect $T$ at a pair of points
$e^{i\phi}, e^{-i\phi}$ when
$0<\phi<\theta$.
\medskip

\noindent
{\bf{A special  inequality}}
Let $0<\theta<\pi/2$ and $\alpha$Êis the circular arc above.
Then the following hold for every
subharmonic function $u$ in $D$ which extends
to be continuous
on the closed disc:




\[
\bigl(\int_{-1}^1\, \lambda(x)\, dx\bigr)^2+
\bigl(\int_\alpha\, \lambda(z)\, |dz|\,\bigr)^2\leq
\frac{1}{4}\cdot \bigl(\int_0^{2\pi}
\lambda(e^{i\theta})\, d\theta\,\bigr)^2\tag{1.3}
\]
\medskip


\noindent
\emph{Proof.}
Put $\lambda= e^u$
so that $\log \lambda=u$ and set:
\[
 \lambda^*z)=
\frac{1}{2}\cdot \bigl( \lambda(z)+
\lambda(S(z))\cdot
|S'(z)|\,\bigr)
\]
Recall from ¤ XX that
the positive $\lambda^*$-function also is of the form
$e^U$ for a subharmonic function $U$.
Since $S$ preserves $\alpha$ we have
\[
\int_\alpha\, \lambda(z)\cdot |dz|=
\int_\alpha\, \lambda^*(z)\cdot |dz|
\] 
and  the same  equality holds when we integrate on 
the real diameter $(-1,1)$. Moreover, since
$S$ maps $T$ onto itself we also get
an equality for the integrals on $T$.
Hence it suffices to prove (1.3) when
$\lambda$ is $S$-invariant, i.e. when  $\lambda=\lambda\circ S$.
From now on $\lambda$ is $S$-invariant and
with $\lambda= e^u$
we solve the Dirichlet problem for the boundary
value function $u$
and get
\[
u= H+w
\]
where $H$ is the harmonic
extension of $u|T$. Here $w$ is subharmonic and 
vanishes on $T$ so   the maximum principle gives $w\leq 0$ in
$D$.
It follows that $\lambda\leq e^H$ and equality holds on $T$.
Hence (1.3) holds for $\lambda$ if we have proved
(1.3) using the function $e^H$. To prove this we first notice
that since $\lambda$ is  $S$-invariant the same holds  for $H$.
This entails that the normal derivatives
\[
\frac{\partial H}{\partial y}(x,0)=0\quad\colon\quad -1<x<1
\]
and similarly the normal derivative of $H$ along
$\alpha$ vanishes.
Let $V$ be the conjugate harmonic function
to $H$ chosen so that $V(x_0))=0$ where
$\alpha$ intersects the real diameter at $x_0$.
Let $\Psi$ be the primitive analytic function of $e^{H+iV}$ where $\Psi(x_0)=0$
which gives:
\[
 |\Psi'(z)|=|e^{H(z)+iV(z)}|= e^{H(z)}= \lambda(z)\tag{i}
\]
The vanishing of normal derivatives of $H$ along
$(-1,1)$ and $\alpha$ implies that 
the conjugate function $V$ is constant on
these two curves
and by the normalisation it is identically zero.
Using this the reader may verify the following
\medskip

\noindent
{\bf{1.4 Lemma.}}
\emph{The analytic function $\Psi$ maps
$(-1,1)$ onto a real line segment $(-A,A)$ and
$\alpha$ to an imaginary line segment $(-iB,iB)$.}
\medskip

\noindent
{\bf{1.5 Exercise.}} Deduce from Lemma 1.4 that one has the equations:
\[
\int_{-1}^1\, \lambda(x)\, dx=2A
\quad\colon\quad
\int_\alpha\, \lambda(z)\, |dz|=2B\tag{1.5.1}
\]
Notice also that
\[
\int_0^{2\pi}
\lambda(e^{i\theta})\, d\theta=
\int_T\, |\Psi'(z)|\, |dz|\tag{1.5.2}
\]
\medskip

\noindent
The right hand side in (1.5.2) measures the total arc-length
of
the image curve
$\theta\mapsto \Psi(e^{i\theta})$.
By the $S$-invariance this curve contains for
four subarcs which join the vertices of the 
rectangle 
with corner points at $A,iB,-A,-iB$.
Since the shortest distance between twe points is a straight line,
Pythagoras' theorem gives the inequality
\[
4\cdot \sqrt{A^2+B^2}\leq \int_T\, |\Psi'(z)|\, |dz|\tag{1.6}
\]
\medskip

\noindent
Together (i) and (1.5.1-1.5.2) therefore give
the requested inequality in (1.3).

\medskip

\noindent
{\bf{1.7 The case of a general rhomb.}}
Let us now consider a pair $\alpha,\beta$ of curves of symmetry
which intersect at a right angle and 
$\lambda= e^u$ for some subharmonic function $u$.
Up  to a rotation 
we may assume that
$\alpha$ intersects $T$ at a pair $e^{i\theta},e^{-i\theta}$
where $0<\theta<\pi/2$.
As explained in ¤ XX there exists a Mšbius transform $S$
which maps the interval $(-\theta,\theta)$
to an interval of length $\pi$
which implies that $S(\alpha)$ is a diameter.
At the same time $S(\beta)$Êis a
curve of symmetry which intersect this diameter at a right angle since
$S$ is conformal. Put
\[
\lambda^*(z)=\lambda(S^{-1}(z))\cdot |S'(z)|^{-1}
\]
Notice that $\log \lambda^*$ again is subharmonic. We have also
\[ 
\int_\alpha\, \lambda(z)\, |dz|=
\int_{S(\alpha)}\,\lambda^*(z)\, |dz|
\]
with similar equations  for integrals over
$\beta$ and the unit circle.
Now (1.3) applies to $\lambda^*$ and 
Theorem 0.1 follows.
\medskip


\noindent
{\bf{1.8 Proof of Theorem 0.2.}}
We are given a pair $\gamma_1,\gamma_2$ in
$\mathcal C(a,b)$.
Then $\gamma_2^{-1}\circ\gamma_1$
is a cklosed Jordan
curve which borders a Jordan domain
$U$ contained in
$\Omega$.
Let $\phi\colon\, D\to U$ be a conformal mapping
which by Theorem XX extends to a homeomorphism from
the closed unit disc onto $\bar U$.
In $DS$ we define the function $\lambda^*$ by
\[
 \lambda^*(z)= 
\lambda(\phi(z))\cdot |\phi'(z)|
\]
Then Theorem 0.2 follows when we 
let $\alpha$ be the Jordan arc
in $\mathcal C(a,b)$
for which
$\phi^{-1}\alpha$ is the curve of symmetry
which passes the points $\phi^{-1}(a)$ and $\phi^{-1}(b)$ on the unit circle.
Finally $\beta$ is chosen so that
$\phi^{-1}\beta$
is the curve of symmetry
which starts at the assgined point $\phi^{-1}(p)$ and
intersects $\phi^{-1}\alpha$ at a right angle.

\bigskip

\centerline{\bf{1.9 Existence of geodesic curves.}}
\medskip


\noindent
Let $\Omega$ be a connected domain in
${\bf{C}}$. it may have finite connectivity as well as
infinite connectivity.
let $u$ be a continuos and strictly subharmonic function in
$\Omega$,  i.e. $\Delta(u)$ 
is a positive function.
With $\lambda= e^u$ we define the $\lambda$-distance between a pair of points
$a,b$ by
\[
\ell(a,b)= \inf_{\gamma\in\mathcal C(a,b)}\, \ell(\gamma)
\]








 











\newpage




\centerline{\bf{XXX.  Beurling's conformal mapping theorem.}}
\bigskip


\noindent
{\bf Introduction.} 
Let $D$ be the open unit disc
$|z|<1$.
Denote by $\mathcal C$
the family 
of conformal maps $w=f(z)$ which map $D$ onto some
simply connected domain $\Omega_f$ which contains
the origin and satisfy:
\[ 
f(0)=0\, \quad\text{and}\quad f'(0)\,\,\text{is real and positive}\,.
\]


\noindent
Riemann's mapping theorem asserts that for every
simply connected subset $\Omega$ of ${\bf{C}}$ which is not equal to
${\bf{C}}$ there exists a unique $f\in\mathcal C$ such that
$\Omega_f=\Omega$.
We are going to construct a subfamily  of
$\mathcal C$.
Consider 
a positive and bounded continuous 
function a function $\Phi$ defined in the whole complex
$w$-plane.
\medskip

\noindent
{\bf 0.1 Definition.}
\emph{The set of all
$f\in \mathcal C$ such that}
\[ 
\lim_{r\to 1}\,\, 
\max_{0\leq\theta\leq 2\pi}\,\bigl[\bigl|f '(re^{i\theta})|-\Phi(f(re^{i\theta}))
\bigr]=0\tag{*}
\]
\emph{is denoted by $\mathcal C_\Phi$.}
\medskip

\noindent
{\bf Remark.}
Thus, when $f\in\mathcal C_\Phi$
then the difference of the absolute value
$|f'(z)|$ and $\Phi(f(z))$ tends uniformly to zero
as $|z|\to 1$.
Let $M$ be the upper bound of $\Phi$.
The maximum principle applied to the complex derivative
$f'(z)$ gives
\[
|f'(z)|\leq M\quad\colon\quad z\in D
\]
Hence $f(z)$ is a  continuous function in
the open disc $D$ whose Lipschitz norm is uniformly
bounded by $M$. This implies
that  $f$ extends to a continuous function in the closed disc, i.e.
$f$ belongs to the disc algebra
$A(D)$.
\bigskip


\noindent
{\bf 1. Theorem.}
\emph{Assume that
$\text{Log}\,\frac{1}{\Phi(w)}$ is subharmonic. Then
$\mathcal C_\Phi$ contains a unique function
$f^*$.}

\bigskip

\noindent
{\bf Remark.}
When
$\Phi(w)=\Phi(|w|)$
is a radial function and 
$\Phi(\rho)=\rho$ holds for some $\rho>0$
then 
the function $f(z)=\rho\cdot z$ belongs to
$\mathcal C_\Phi$. So for a radial $\Phi$-function
where different $\rho$-numbers exist  uniqueness fails for 
the family $\mathcal C_\Phi$.
The reader may verify that
a radial function $\Phi$ for which $\Phi(\rho)=\rho$ has more than one
solutions cannot satisfy the condition in
Theorem 1.
Next, let us give examples of $\Phi$-functions which satisfy the condition in
Theorem 1. Consider 
an arbitrary real-valued and non-negative $L^1$-function
$\rho(t,s)$ which has compact support.
Set
\[ 
\Phi(w)=\text{exp}\,\bigl[\int\,\text{log}\,\frac{1}{|w-t-is[}\cdot \rho(t,s)\cdot dtds\,\bigr]
\]
Here  
$\text{log}\,\frac{1}{\Phi}$ is subharmonic and 
Theorem 1 gives 
a unique simply connected domain
$\Omega$ such that the  normalised
conformal mapping function $f\colon\, D\to\Omega$
satisfies

\[
|f'(e^{i\theta})|=\Phi(f(e^{i\theta}))\quad\colon
\quad 0\leq \theta\leq 2\pi\,.
\]
\medskip

\noindent
The proof of Theorem 1 requires several steps
where  notble point is that we also estblish some
existence results  under the sole assumption
that $\Phi$ is continuous and positive.

\medskip




\noindent
{\bf 1.1 The family $\mathcal A_\Phi$}.
Let $\Phi$be continuous and positive.
Denote by $\mathcal A_\Phi$  the subfamily of all 
$f(z)\in \mathcal C$ such that
\[
\limsup_{|z|\to 1}\,\, |f'(z)|-\Phi(f(z))\leq 0\tag{1}
\]
\medskip
\noindent
{\bf{Remark.}} By the definition of  limes superior this means that 
for every $\epsilon>0$ there exists $\delta>0$ such that
\[
|f'(z)|\leq \Phi(f(z))+\epsilon\quad\colon\text{for all}\,\, 1-\delta<|z|<1\,.
\]
\medskip


\noindent
{\bf The maximal region
$\Omega^*(\Phi)$}. 
With $\Phi$ given we get  a bounded
open subset
in the complex plane as follows:
\[ 
\Omega^*(\Phi)=\cup\, f(D)\quad\colon\quad 
\text{union taken over all}\,\, f\in\mathcal A_\Phi\tag{1.2}
\]
\medskip

\noindent
{\bf 1.3  Theorem.}
\emph{The maximal region $\Omega^*(\Phi)$ is simply connected. Moreover, 
the
unique normalised
conformal mapping 
for which $f^*(D)=\Omega^*(\Phi)$ 
belongs to
$\mathcal C_\Phi$.}
\bigskip


\noindent
{\bf 1.4 The family $\mathcal B_\Phi$}.  It consists of all
$f\in\mathcal C$
such that
\medskip
\[
\liminf_{|z|\to 1}\,\, |f'(z)|-\Phi(f(z))\geq 0
\]
To this family we assign minimal region
\[ 
\Omega_*(\Phi)=\cap\, f(D)\quad\text{The intersection taken over all}
\,\, f\in \mathcal B_\Phi\tag{1.5}
\]
\medskip

\noindent
{\bf 1.6 Theorem.}
\emph{The set $\Omega_*(\Phi)$ is simply connected and the
unique $f_*\in\mathcal C$ for which
$f_*(D)=\Omega_*(\Phi)$ belongs to $\mathcal C_\Phi$.}
\medskip

\noindent
{\bf{Remark.}}
The constructions of the maximal and the minimal region give
\[ 
\Omega_*(\Phi)\subset\Omega^*(\Phi)\tag{1}
\]


\noindent
This inclusion  is in general strict as seen  by the example when
$\Phi$ is radial.
But when
$\text{Log}\,\frac{1}{|\Phi|}$ is subharmonic the uniqueness in
Theorem 1 asserts that one has 
the equality
$\Omega_*(\Phi)=\Omega^*(\Phi)$.
\medskip

\noindent
Before we enter the proofs of Theorem 1.4 and 1.6
we show  the
uniqueness part in
Theorem 1.
\bigskip

\centerline{\bf A. Proof of Theorem 1.}
\medskip

\noindent
Let $\Phi$ be as in Theorem 1. Admitting
Theorem 1.4 and 1.6  we get the two simply connected
domains
$\Omega^*(\Phi)$
and
$\Omega_*(\Phi)$. Keeping $\Phi$ fixed we set
$\Omega^*=\Omega^*(\Phi)$ and
$\Omega_*=\Omega_*(\Phi)$.
Let $f\colon D\to \Omega_*$ and
$g\colon D\to \Omega^*$ be the
corresponding conformal mappings.
Since $\Omega_*\subset \Omega^*$
Riemann's mapping theorem gives an inequality for
the first order derivative at $z=0$:
\[
f'(0)\leq g'(0)\tag{i}
\]
Set
\[ 
\Phi(w)= e^{U(w)}
\]
where $U(w)$ by assumption is super-harmonic.
Solving  the Dirichlet problem
with respect to the domain $\Omega^*$ we get 
the harmonic function $U^*$ in $\Omega^*$
where
\[ 
U^*(w)=U(w)\quad\, w\in\partial\Omega^*\,.
\]
Similarly we find the harmonic function $U_*$ in $\Omega_*$ such that
\[
U_*(w)=U(w)\quad\, w\in\partial\Omega_*\,.\tag{*}
\]
Next, since $g\in \mathcal C_\Phi$
we have
the equality
\[ 
\text{log}\, |g'(z)|=U(g(z))\quad |z|=1\tag{ii}
\]
Now 
$\text{log}\, |g'(z)|$ and $U^*(g(z))$ are harmonic in
$D$ and since $g$ is normalised so that $g'(0)$ is real and positive
it follows from (ii) that:
\[
\text{log}\, g'(0)= U^*(0)
\]
In a similar way we find that
\[ 
\text{log}\,f'(0)= U_*(0)
\]
\medskip


\noindent
Next, $U$ is super-harmonic in $\Omega^*$  since 
and $\partial\Omega_*$ is a closed subset of
$\bar\Omega^*$ one has:
\medskip
\[
U(w)\geq U^*(w)\quad w\in\partial\Omega_*
\]
Then (*) entails 
that $U_*\geq U^*$ holds in $\Omega_*$. In particular
\[
\text{log}\,f'(0)= U_*(0)\geq U^*(0)=\text{log}\,g'(0)
\]
Together with (i) we conclude that
$f'(0)= g'(0)$and by the uniqueness in
Riemann's mapping theorem it follos that 
$\Omega_*=\Omega^*$ which gives the uniqueness part in
Theorem 1.





\bigskip

\centerline{\bf B. Proof of Theorem 2.}



\medskip

\noindent
The first step in the proof is to construct a certain "union  map"
defined by a finite family $f_1,\ldots,f_n$
of functions  $\mathcal A_\Phi$.
Set 
\[ 
S_\nu=f_\nu(D)\quad\,\text{and}\,\,  S_*=\cup\, S_\nu\tag{*}
\]
\medskip

\noindent
So above $S_*$ is a union of Jordan domains
which in general can intersect each other in a rather arbitrary fashion.
\medskip

\noindent
{\bf B.1 Definition.}
\emph{The extended union denoted by $EU(S_*)$
is defined as follows:
A point $w$ belongs to the extended union
if there exists some closed Jordan curve
$\gamma\subset S_*$ and the Jordan domain bordered by
$\gamma$ contains
$w$}.
\medskip

\noindent
{\bf{Exercise.}} Verify that
the extended union is simply connected.
\medskip

\noindent
{\bf  B.2 Lemma }
\emph{Let $f_*$ be the unique normalised conformal map from
$D$ onto the extended union above. Then
$f_*\in\mathcal A_\Phi$.}
\bigskip

\noindent






\noindent
\emph{Proof.} 
First we  reduce the proof to the
case
when all the functions
$f_1,\ldots,f_n$  extend to be analytic in a neighborhood of
the closed disc
$\bar D$. 
In fact, with $r<1$ we set
$f_\nu^r(z)=f_\nu(rz)$
and get the image domains $S_\nu[r]= f_\nu^r(D)= f_\nu(D_r)$.
Put $S_*[r)=\cup\, S_\nu[r]$ and construct its
extended union which we denote by $S_{**}[r]$.
Next, let $\epsilon>0$
and consider the new function $\Psi(w)=\Phi(w)+\epsilon$.
Let $f_*[r]$ be the conformal map from $D$ onto $S_{**}[r]$.
If Lemma B.2 has been proved for the
$n$-tuple $\{f_\nu^r\}$
it follows by continuity that $f_*[r]$ belongs 
$\mathcal A_\Psi$ if $r$ is sufficently close to one.
Passing to the limit we see that
$f_*=\lim_{r\to 1}\, f_*[r]$
and we get $f_*\in\mathcal A_\Psi$. Since
$\epsilon>0$ is arbitrary we get
$f_*\in\mathcal A_\Phi$ as required.
\medskip

\noindent
After this preliminary reduction we consider the
case when each
$f$-function extends  analytically to a neighborhood of
the closed disc $|z|\leq 1$.
Then each $S_\nu$ is a closed real analytic Jordan curve
and
the boundary of $S_*$ is a finite union of
real analytic arcs and some corner points.
In particular we find the outer boundary which is a piecewise analytic and closed Jordan
curve
$\Gamma$
and  the extended union is the Jordan domain bordered by
$\Gamma$.
It is also clear that 
$\Gamma$ is the union of some connected
arcs $\gamma_1,\ldots,\gamma_N$ and a finite set of corner points
and for each $1\leq k\leq N$ there exists
$1\leq \nu(k)\leq n$
such that
\[ 
\gamma_k\subset \partial S_{\nu(k)}
\]



\noindent
Denote by  $\{F_\nu=f_\nu^{-1}\}$ and $F=f_*^{-1}$
the inverse functions and put:
\[ 
G=\text{Log}\, \frac{1}{|F|}\quad\colon
 G_\nu=\text{Log}\, \frac{1}{|F_\nu|}\quad\colon 1\leq\nu\leq n\,.
\]
\medskip

\noindent
With $1\leq\nu\leq n$ kept fixed we notice that
$G_\nu$ and $G$ are super-harmonic functions in
$S_\nu$ and the difference
\[ 
H=G-G_\nu
\] 
is superharmonic in $S_\nu$.
Next, consider a point  $p\in \partial S_\nu$. Then
$|F_\nu(p)|=1$
and hence
$G_\nu(p)=0$. At the same time
$p$ belongs to
$\partial S_*$ or the interior of $S_*$ so
$|F(p)|\leq 1$ and hence $G(p)\geq 0$.
This shows that
$H\geq 0$ on $\partial S_\nu$ and by the minimum principle for harmonic
functions we obtain:
\[
H(q)\geq 0\quad\text{for all}\,\, q\in S_\nu\tag{i}
\]
\medskip

\noindent
Let us then consider some boundary arc
$\gamma_k$  
where $\gamma\subset\partial S_\nu$, i.e.   here $\nu=\nu(k)$.
Now $H=0$ on $\gamma_k$ and since (i) holds it follows that
the \emph{outer normal derivative}:
\[
\frac{\partial H}{\partial n}(p)\leq 0\quad p\in\gamma_k\tag{ii}
\]


\noindent 
Since 
$|F|=|F_\nu|=1$ holds on
$\gamma_k$ and the gradient of $H$ is parallell to the normal
we also get:
\[ 
\frac{\partial G}{\partial n}(p)=
-|F'(w)|\quad\text{and}\quad\,\,
\frac{\partial G_\nu}{\partial n}(p)=
-|F_\nu'(w)|
\quad\colon w\in\gamma_k
\]
Hence (ii) above gives
\[
|F'(w)|\geq |F_\nu'(w)|\quad\text{when}\quad  w\in\gamma_k\tag{iii}
\]
Next, since $f_\nu\in \mathcal A_\Phi$
we have
\[
|f_\nu'(F_\nu(w))|\leq \Phi(w)\tag{iv}
\]
and since $F_\nu$ is the inverse of $f_\nu$
we get

\[ 1=f_\nu'(F_\nu(w))\cdot F'_\nu(w)
\]
Hence (iv) entails
\[ |F'_\nu(w)|\geq
\frac{1}{ \Phi(w)}\tag{v}
\]
We conclude from
(iii) that

\[ |F'(w)|\geq
\frac{1}{ \Phi(w)}\quad \colon\,\, w\in\gamma_k\tag{vi}
\]
This holds for all the sub-arcs
$\gamma_1,\dots,\gamma_n$ and hence
we have proved the inequality
\[
|F'(w)|\geq
\frac{1}{ \Phi(w)}\quad\text{ for all}\quad  w\in\Gamma\tag{*}
\]
except  at a
finite number of  corner points.
To settle the situation at corner points we notice that
Poisson's formula applied to the harmonic function
$
\text{log}\, |f_*'(z)|$ in the unit disc gives
\[
\text{log}\, |f_*'(z)|=
\frac{1}{2\pi}\cdot \int_0^{2\pi}\,
\frac{1-|z|^2}{|e^{i\theta}-z|^2}\cdot
\text{log}\, |f'(e^{i\theta})|
\cdot d\theta\,.\tag{vii}
\]
\medskip

\noindent
Next, since $F$ is the inverse of $f_*$ we have
\[
|f_*'(z)|\cdot |F'(f(z))|=1\quad\text{for all}\,\,|z|=1\,.
\]
Hence (vi) gives
\[ 
|f'(z)|\leq \Phi(f_*(z))\quad\text{for all}\,\,|z|=1\,.
\]
With $\Phi= e^U$
we therefore get
\[
\text{log}\, |f'_*(z)|\leq U(f(z))
\quad\text{for all}\,\,|z|=1\,.
\]

\noindent
From the Poisson integral (vii) it follows that
\[
\text{log}\, |f_*'(z)|\leq 
\frac{1}{2\pi}\cdot \int_0^{2\pi}\,
\frac{1-|z|^2}{|e^{i\theta}-z|^2}\cdot
\, U(f_*(e^{i\theta}))
\cdot d\theta\,.\quad\, z\in D
\]


\medskip

\noindent
{\bf{A passage to the limit.}}
I addition to the obvious equi-continuity the passage to the limit
requires some care which is exposed in
[Beurling: Lemma 1, page 122].
Passing to the limit as $|z|\to 1$
the continuity of $\Phi$ implies that
$f_*$ belongs to $\mathcal A_\Phi$ which proves Lemma B.2.

\newpage

\centerline{\bf B.3 The construction of $\Omega^*$}




\bigskip

\noindent
By the uniform bound for Lipschitz norms
the family $\mathcal A_\phi$
is equi-continuous. We can therefore find a denumerable dense subset
$\{h_\nu\}$. It means that to every
$f\in\mathcal A_\Phi$ and every $\epsilon>0$ there exists
some $h_\nu$ such that
the maximum norm
$|f-h_\nu|_D<\epsilon$. From this it is clear that
\[ 
\Omega^*=\cup\,\, h_\nu(D)\tag{i}
\]
Next, to every $n\geq 2$ we 
have the $n$-tuple $h_1,\ldots,h_n$
Lemma B. 2 gives  the function
$f_n$ where $f_n(D)$ is the extended union of
$\{h_\nu(D)\}$. In particular 
\[ 
h_\nu(D)\subset f_n(D)\quad\colon\,1\leq\nu\leq n
\]
The image domains $\{f_n(D)\}$ increase with $n$.
and (i)  gives
\[ 
\Omega^*=\cup\, f_n(D)\tag{ii}
\]


\noindent
Next, $\{f_n\}$ is a normal family of analytic functions
and since their image domains increase 
there exists the limit function
$f^*$ and it belongs to $\mathcal  C$  by the general results from Chapter VI.
Morover, (ii) entails that
\[
f^*(D)=\Omega^*
\]
There remains to prove 
that
\[ 
f^*\in \mathcal C_\Phi\tag{*}
\]
\medskip
To    establish  (*) we shall need
a  relation between
$\Phi$ and the maximal domain
$\Omega^*(\Phi)$.
\medskip

\noindent
{\bf B.4 Proposition.}
\emph{Let $\Psi$ be a positive continuous function which is equal to
$\Phi$ outside $\Omega^*(\Phi)$ while 
its restriction to
$\Omega^*(\Phi)$ is arbitrary. Then
one has the equality}
\[
\Omega^*(\Phi)=
\Omega^*(\Psi)
\]


\noindent
\emph{Proof.}
The assumption gives
\[
 \Psi(w)=\Phi(w)\quad\text{for all}\,\, w\in\partial\Omega^*(\Phi)\tag{i}
 \]

\medskip

\noindent
It follows that
 $f^*\in\mathcal A_\Psi$. Hence the
 equality $f^*(D)=\Omega^*(\Phi)$ and 
the construction of the maximal domain
 $\Omega^*(\Psi)$ give the inclusion
 \[
 \Omega^*(\Phi)\subset\Omega^*(\Psi)\tag{ii}
\]

\medskip

\noindent
Next, let  $h^*\colon D\to \Omega^*(\Psi)$ 
be the conformal mapping function associated to $\Psi$.
The equality (i) and the construction of the
maximal region $\Omega^*(\Phi)$ gives $h^*\in\mathcal A_\phi$
and then
\[
\Omega^*(\Psi)=h^*(D)\subset
 \Omega^*(\Phi)\tag{iii}
 \]
Hence (ii-iii)  give the requested equality in Proposition B.4.
\bigskip


\centerline {\bf B.5 A special choice of $\Psi$}.
\medskip

\noindent
Keeping $\Phi$ fixed we put
$\Omega^*(\Phi)=\Omega^*$ to simplify
the notations. We have the $U$-function such that
\[ 
\Phi(w)= e^{U(w)}\tag{B.5.i}
\]
Here
$U(w)$ is a continuous function on
$\partial\Omega^*$
and solving the Dirichlet problem we obtain the function $U_*(w)$
where $U_*=U$ outside $\Omega^*$, and in $\Omega^*$ 
the function $U_*$ is the harmonic extension of the boundary
function $U$ restricted to
$\partial\Omega^*$.
Set
\[
\Psi(w)= e^{U_*(w)}
\]
Proposition B.4 gives 
\[ 
f^*\in\mathcal A_\Psi\tag{B.5.ii}
\]
Next, consider  the function
in $D$ defined by:


\[ 
V(z)=\text{log}\, \bigl|\frac {d f^*(z)}{dz}\bigr|-U_*(f(z))
\] 
\medskip

\noindent
From the above 
$V(z)$ is either  identically zero in
$D$ or everywhere $<0$. It is also clear
that if $V=0$ then
$f^*\in\mathcal C_\Phi$ as required.
So there remains only to prove:
\medskip

\noindent
{\bf B.6 Lemma.} \emph{The function $V(z)$ is identically zero in $D$.}
\medskip

\noindent
\emph{Proof.}
Assume the contrary. So now
\[
 \bigl|\frac {d f^*(z)}{dz}\,\bigr|<e^{U_*(z)}\quad\text{for all}\,\,z\in D\,.\tag{i}
\]
Let $F(w)$ be the inverse of $f$ so that :
\[
F'(f^*(z))\cdot   \frac {d f^*(z)}{dz}=1\quad\, z\in D
\]
Then (i) gives:
\[ 
\bigl|F'(w)\,\bigr|> e^{-U_*(w)}\quad w\in \Omega^*\tag{ii}
\]


\noindent
Let $V(w)$ be the harmonic conjugate of $U_*(w)$ normalised so that
$V(0)=0$ and put
\[ 
H(w)=\int_0^w\,
e^{-U_*(\zeta)+iV(\zeta)}\cdot d\zeta\,.
\]
Then (ii) gives
\[
\bigl|H'(w)\bigr|<
\bigl|F'(w)\bigr|\quad w\in \Omega^*\tag{iii}
\]
Since $H(w((0))=F(w(0))=0$ it follows that
\[ 
\inf_{w\in\Omega^*}\,\frac{|H(w)|}{|F(w)|}=r_0<1\tag{iv}
\]
Now  $|F(w)|<1$ in $\Omega^*$
and  $|F(w)|\to 1$ as $w$ approaches
$\partial\Omega^*$. Hence  (iv) entails the domain
\[
R_0=\{ w\in \Omega^*\quad\colon\, |H(w)|<r_0\}\tag{v}
\]
has at least one boundary
point $w_*$ which also belongs to
$\partial\Omega^*$.
Next, the function $H(w)$ is analytic in $R_0$ and its derivative is everywhere
$\neq 0$ while $|H(w)|=1$ on $\partial R_0$. It follows
that $H$ gives a conformal map from $R_0$ onto the disc
$|z|<r_0$.
Let $h(z)$ be the inverse of this conformal mapping.
Now we get the 
analytic function in $D$ defined by
\[ 
g(z)= h(r_0z)
\] 
Next, let $|z|=1$ and put $w=h(r_0z)$.
Then 
\[ 
|g'(z)|= r_0\cdot |h'(r_0z)|=r_0\cdot \frac{1}{|H'(g(z))|}=
r_0\cdot e^{U_*(g(z))}=r_0\cdot\Psi(g(z))<\Psi(g(z))\tag{v}
\]
At the same time we have a common boundary point
\[ 
w_*\in\partial\Omega^*\,\cap\,\partial g(D)
\]


\noindent
Since the $g$-function extends to a continuous function on
$|z|\leq 1$ there exists a point
$e^{i\theta}$ such that
\[ 
g(e^{i\theta})= w_*
\]
Now we use that $r_0<1$ above.
The continuity of  $\Psi$
gives the existence of  $\epsilon>0$ such that
for any complex number $a$ which belongs to the disc
$|a-1|<\epsilon$, it follows that the function
\[
z\mapsto a\cdot g(z)
\]
belongs to $\mathcal A_\Psi$.
Finally, by  Proposition B.4  the maximal region for the $\Psi$-function is equal to
$\Omega^*$ and we conclude that
\[
ag(e^{i\theta})= aw_*\in \Omega^*\quad\, |a-1|<\epsilon
\]


\noindent
This would mean that
$w_*$ is an \emph{interior point} of
$\Omega^*$ which contradicts that $w_*\in\partial\Omega_*$
and
Lemma B.6 is proved.


\bigskip


\centerline{\bf C. Proof of Theorem 3.}
\bigskip

\noindent
First we have a companion to
Lemma B.2. Namely, let $g_1,\ldots,g_n$
be a finite set in $\mathcal B_\Phi$.
Set $S_\nu=g_\nu(D)$. Following [Beur: page
123] we give
\medskip

\noindent
{\bf C.1 Definition.}
\emph{The reduced intersection of the family
$\{S_\nu\}$ is defined as the set of these points
$w$
which can be joined with the origin by a Jordan arc
$\gamma$ contained in the intersection $\cap\, S_\nu$.
The resulting domain is denoted by
$RI\{S_\nu\}$.}
\medskip

\noindent
{\bf C.2 Proposition.}
\emph{The domain $RI\{S_\nu\}$ is simply connected and if
$g\in \mathcal C$ is the normalised conformal mapping onto
this domain, then
$g\in\mathcal B_\Phi$.}
\medskip

\noindent
The proof of this result can be carried out in a similar way as in
the proof of Lemma B.2 so we leave out the details.
Next, starting from a  dense sequence
$\{g_\nu\}$ in $\mathcal B_\Phi$
we find for each $n$ the function $f_n\in \mathcal B_\Phi$
where
\[ 
f_n(D)=RI\{S_\nu\}\quad\colon\, S_\nu=g_\nu(D)\,\colon\, 1\leq\nu\leq n\,.
\]
Here the simply connected domains
$\{f_n(D)\}$ decrease and there exists the limit function
$f_*\in\mathcal C$ where
\[
f_*(D)=\Omega_*
\]
There remains to prove
\medskip

\noindent
{\bf C.3 Proposition.}
\emph{One has $f_*\in\mathcal C_\Phi$.}
\medskip

\noindent
{\bf Remark.}
Proposition C.3  requires a quite involved proof 
as comared to the case of maximal regions.
The details are given in 
[Beur: page 127-130]. Let us 
just
sketch the strategy in the proof. Put
\[ 
m=\inf_{g\in\mathcal B_\Phi}\, g'(0)
\]
\medskip


\noindent
Next, $f_*$  belongs to
$\mathcal B_\Phi$ because we have the trivial inclusion
$\mathcal C_\Phi\subset \mathcal B_\Phi$ and using this Beurling  proved that
\[ 
m\geq \min_{w\in\Omega^*}\,\Phi(w)
\]
Next, starting with  Proposition C.2 above, Beurling introduces  a  normal family
and proves that
\[ 
f_*'(0)=m
\]
Thus, $f_*$ is a solution to an extremal problem which
Beurling used to   establish the inclusion
$f_*\in\mathcal C_\Phi$.
Let us remark that  this part of the proof 
relies upon
some some very interesting  set-theoretic constructions
where  the family of regions of the \emph{Schoenfliess' type}
are introduced in [Beur: page 121].
So the  whole proof  involves topological investigations of
independent interest.




























\newpage










\centerline{\bf\large{11.  Beurling's conformal mapping theorem.}}
\bigskip


\noindent
{\bf Introduction.} 
Let $D$ be the open unit disc
$|z|<1$.
Denote by $\mathcal C$
the family 
of conformal maps $w=f(z)$ which map $D$ onto some
simply connected domain $\Omega_f$ which contains
the origin and satisfy:
\[ 
f(0)=0\, \quad\text{and}\quad f'(0)\,\,\text{is real and positive}\,.
\]


\noindent
Riemann's mapping theorem asserts that for every
simply connected subset $\Omega$ of ${\bf{C}}$ which is not equal to
${\bf{C}}$ there exists a unique $f\in\mathcal C$ such that
$\Omega_f=\Omega$.
We are going to construct a subfamily  of
$\mathcal C$.
Consider 
a positive and bounded continuous 
function a function $\Phi$ defined in the whole complex
$w$-plane.
\medskip

\noindent
{\bf 0.1 Definition.}
\emph{The set of all
$f\in \mathcal C$ such that}
\[ 
\lim_{r\to 1}\,\, 
\max_{0\leq\theta\leq 2\pi}\,\bigl[\bigl|f '(re^{i\theta})|-\Phi(f(re^{i\theta}))
\bigr]=0\tag{*}
\]
\emph{is denoted by $\mathcal C_\Phi$.}
\medskip

\noindent
{\bf Remark.}
Thus, when $f\in\mathcal C_\Phi$
then the difference of the absolute value
$|f'(z)|$ and $\Phi(f(z))$ tends uniformly to zero
as $|z|\to 1$.
Let $M$ be the upper bound of $\Phi$.
The maximum principle applied to the complex derivative
$f'(z)$ gives
\[
|f'(z)|\leq M\quad\colon\quad z\in D
\]
Hence $f(z)$ is a  continuous function in
the open disc $D$ whose Lipschitz norm is uniformly
bounded by $M$. This implies
that  $f$ extends to a continuous function in the closed disc, i.e.
$f$ belongs to the disc algebra
$A(D)$.
Notice also that (*) implies that
the function $z\mapsto |f'(z)|$  extends to a continuous 
function on
$\bar D$.
\bigskip


\noindent
{\bf 1. Theorem.}
\emph{Assume that
$\text{Log}\,\frac{1}{\Phi(w)}$ is subharmonic. Then
$\mathcal C_\Phi$ contains a unique function
$f^*$.}

\bigskip

\noindent
{\bf Remark.}
In the special case when
$\Phi(w)=\Phi(|w|)$
is a radial function we notice that for every
$\rho>0$ such that
$\Phi(\rho)=\rho$ it follows that
the function $f(z)=\rho\cdot z$ belongs to
$\mathcal C_\Phi$. So for a radial $\Phi$-function
where different $\rho$-numbers exist one does not have uniqueness.
The reader may verify that
a radial function $\Phi$ for which $\Phi(\rho)=\rho$ has
several solutions cannot satisfy the condition in
Theorem 1.
Next, let us give examples of $\Phi$-functions which satisfy the condition in
Theorem 1. Consider 
an arbitrary real-valued and non-negative $L^1$-function
$\rho(t,s)$ which has compact support.
Set
\[ 
\Phi(w)=\text{exp}\,\bigl[\int\,\text{log}\,\frac{1}{|w-t-is[}\cdot \rho(t,s)\cdot dtds\,\bigr]
\]
Here  
$\text{log}\,\frac{1}{\Phi}$ is subharmonic and 
Theorem 1 asserts that there exists
a unique simply connected domain
$\Omega$ which contains the origin such that the  normalised
conformal mapping function $f\colon\, D\to\Omega$
satisfies
\[
|f'(e^{i\theta})|=\Phi(f(e^{i\theta}))\quad\colon
\quad 0\leq \theta\leq 2\pi\,.
\]
\medskip

\noindent
The proof of Theorem 1 relies upon
some  results where we only assume that
the $\Phi$-function is continuous and positive.

\medskip




\noindent
{\bf The family $\mathcal A_\Phi$}.
A conformal map
$f(z)$ in $\mathcal C$ belongs to
$\mathcal A_\Phi$ if
\[
\limsup_{|z|\to 1}\,\, |f'(z)|-\Phi(f(z))\leq 0\tag{1}
\]
\medskip
\noindent
{\bf{Remark.}} By the definition of  limes superior this means that 
for every $\epsilon>0$ there exists $\delta>0$ such that
\[
|f'(z)|\leq \Phi(f(z))+\epsilon\quad\colon\text{for all}\,\, 1-\delta<|z|<1\,.
\]
\medskip


\noindent
{\bf The maximal region
$\Omega^*(\Phi)$}. With $\Phi$ given we define a bounded
open subset
in the $w$-plane as follows:
\[ 
\Omega^*(\Phi)=\cup\, f(D)\quad\colon\quad \text{union taken over all}\,\, f\in\mathcal A_\Phi\,.
\]
With these notations we have
\medskip

\noindent
{\bf 2. Theorem.}
\emph{The maximal region $\Omega^*(\Phi)$ is simply connected. Moreover, 
there exists
a unique
conformal map
with $f^*(D)=\Omega^*(\Phi)$ which in addition
belongs to
$\mathcal C_\Phi$.}
\bigskip


\noindent
{\bf The family $\mathcal B_\Phi$}.  It consists of all
$f\in\mathcal C$
such that
\medskip

\[
 \text{Lim.inf.}\,_{|z|\to 1}\,\, |f'(z)|-\Phi(f(z))\geq 0
\]
To this family we assign minimal region

\[ 
\Omega_*(\Phi)=\cap\, f(D)\quad\text{The intersection taken over all}
\,\, f\in \mathcal B_\Phi
\]
\medskip

\noindent
{\bf 3. Theorem.}
\emph{The set $\Omega_*(\Phi)$ is simply connected and the
unique $f_*\in\mathcal C$ for which
$f_*(D)=\Omega_*(\Phi)$ belongs to $\mathcal C_\Phi$.}
\medskip

\noindent
The constructions of the maximal and the minimal region give
\[ 
\Omega_*(\Phi)\subset\Omega^*(\Phi)\tag{1}
\]


\noindent
In general this inclusion it is strict as seen  by the example when
$\Phi$ is radial.
But when
$\text{Log}\,\frac{1}{|\Phi|}$ is subharmonic the uniqueness in
Theorem 1 asserts that one has 
the equality
$\Omega_*(\Phi)=\Omega^*(\Phi)$.
\medskip

\noindent
{\bf Remark about  the proofs.}
Following Beurling's article [Beur] we shall give
the details of the proof of Theorem 2. Concerning Theorem 3
it is substantially harder
and for this part of the proof we
refer to 
[Beur: p. 127-130] for  details,
Before we enter the proof of Theorem 2
we show how Theorem 2 and 3 together give the
uniqueness in
Theorem 1.
\bigskip

\centerline{\bf A. Proof of Theorem 1.}
\medskip

\noindent
Let $\Phi$ be as in Theorem 1. Admitting
Theorem 2 and 3 we get the two simply connected
domains
$\Omega^*(\Phi)$
and
$\Omega_*(\Phi)$. Keeping $\Phi$ fixed we set
$\Omega^*=\Omega^*(\Phi)$ and
$\Omega_*=\Omega_*(\Phi)$.
Since $\Omega_*\subset \Omega^*$
Riemann's mapping theorem gives an inequality for
the first order derivative at $z=0$:
\[
f_*'(0)\leq (f^*)'(0)\tag{i}
\]
Next, we can write
\[ 
\Phi(w)= e^{U(w)}
\]
where $U(w)$ by assumption is super-harmonic.
We can solve the Dirichlet problem
with respect to the domain $\Omega^*$. This gives
the harmonic function $U^*$ in $\Omega^*$
where
\[ 
U^*(w)=U(w)\quad\, w\in\partial\Omega^*\,.
\]
Similarly we find the harmonic function $U_*$ in $\Omega_*$ such that
\[
U_*(w)=U(w)\quad\, w\in\partial\Omega_*\,.\tag{*}
\]
Next, since $f^*\in \mathcal C_\Phi$
we have
the equality
\[ 
\text{log}\, |(f^*)'(z)|=U(f(z))\quad |z|=1\tag{ii}
\]
Now 
$\text{log}\, |(f^*)'(z)|$ and $U^*(f(z))$ are harmonic in
$D$ and (ii) gives:
\[
\text{log}\, (f^*)'(0)= U^*(0)
\]
In a similar way we find that
\[ 
\text{log}\,f_*'(0)= U_*(0)
\]
Since $U$ is super-harmonic in $\Omega^*$ 
and $\partial\Omega_*$ is a closed subset of
$\bar\Omega^*$ we get:
\medskip
\[
U(w)\geq U^*(w)\quad w\in\partial\Omega_*
\]
From (*) it therefore
follows that $U_*\geq U^*$ holds in $\Omega_*$. So in particular
\[
\text{log}\,f_*'(0)= U_*(0)\geq U^*(0)=\text{log}\,(f^*)'(0)
\]
Together with (i) we conclude that
$f_*(0)= (f^*)'(0)$. Finally, the uniqueness in
Riemann's mapping theorem gives
$\Omega_*=\Omega^*$ and hence that $f_*=f^*$
which proves 
Theorem 1.





\bigskip

\centerline{\bf B. Proof of Theorem 2.}



\medskip

\noindent
The first step in the proof is to construct a certain "union  map"
defined by a finite family $f_1,\ldots,f_n$
of functions  $\mathcal A_\Phi$.
Set 
\[ 
S_\nu=f_\nu(D)\quad\,\text{and}\,\,  S_*=\cup\, S_\nu\tag{*}
\]
\medskip

\noindent
So above $S_*$ is a union of Jordan domains
which in general can intersect each other in a rather arbitrary fashion.
\medskip

\noindent
{\bf B.1 Definition.}
\emph{The extended union denoted by $EU(S_*)$
is defined as follows:
A point $w$ belongs to the extended union
if there exists some closed Jordan curve
$\gamma$ which contains $w$ in its interior domain
while $\gamma\subset S_*$.}
\medskip

\noindent
{\bf{Exercise.}} Verify that
the extended union is \emph{simply connected}.
\medskip

\noindent
{\bf  B.2 Lemma }
\emph{Let $f_*$ be the unique normalised conformal map from
$D$ onto the extended union above. Then
$f_*\in\mathcal A_\Phi$.}
\bigskip

\noindent






\noindent
\emph{Proof.} 
First we  reduce the proof to the
case
when all the functions
$f_1,\ldots,f_n$  extend to be analytic in a neighborhood of
the closed disc
$\bar D$. 
In fact, with $r<1$ we set
$f_\nu^r(z)=f_\nu(rz)$
and get the image domains $S_\nu[r]= f_\nu^r(D)= f_\nu(D_r)$.
Put $S_*[r)=\cup\, S_\nu[r]$ and construct its
extended union which we denote by $S_{**}[r]$.
Next, let $\epsilon>0$
and consider the new function $\Psi(w)=\Phi(w)+\epsilon$.
Let $f_*[r]$ be the conformal map from $D$ onto $S_{**}[r]$.
If Lemma B.2 has been proved for the
$n$-tuple $\{f_\nu^r\}$
it follows by continuity that $f_*[r]$ belongs 
$\mathcal A_\Psi$ if $r$ is sufficently close to one.
Passing to the limit we see that
$f_*=\lim_{r\to 1}\, f_*[r]$
and we get $f_*\in\mathcal A_\Psi$. Since
$\epsilon>0$ is arbitrary we get
$f_*\in\mathcal A_\Phi$ as required.
\medskip

\noindent
After this preliminary reduction we consider the
case when each
$f$-function extends  analytically to a neighborhood of
the closed disc $|z|\leq 1$.
Then each $S_\nu$ is a closed real analytic Jordan curve
and
the boundary of $S_*$ is a finite union of
real analytic arcs and some corner points.
In particular we find the outer boundary which is a piecewise analytic and closed Jordan
curve
$\Gamma$
and  the extended union is the Jordan domain bordered by
$\Gamma$.
It is also clear that 
$\Gamma$ is the union of some connected
arcs $\gamma_1,\ldots,\gamma_N$ and a finite set of corner points
and for each $1\leq k\leq N$ there exists
$1\leq \nu(k)\leq n$
such that
\[ 
\gamma_k\subset \partial S_{\nu(k)}
\]



\noindent
Denote by  $\{F_\nu=f_\nu^{-1}\}$ and $F=f_*^{-1}$
the inverse functions and put:
\[ 
G=\text{Log}\, \frac{1}{|F|}\quad\colon
 G_\nu=\text{Log}\, \frac{1}{|F_\nu|}\quad\colon 1\leq\nu\leq n\,.
\]
\medskip

\noindent
With $1\leq\nu\leq n$ kept fixed we notice that
$G_\nu$ and $G$ are super-harmonic functions in
$S_\nu$ and the difference
\[ 
H=G-G_\nu
\] 
is superharmonic in $S_\nu$.
Next, consider a point  $p\in \partial S_\nu$. Then
$|F_\nu(p)|=1$
and hence
$G_\nu(p)=0$. At the same time
$p$ belongs to
$\partial S_*$ or the interior of $S_*$ so
$|F(p)|\leq 1$ and hence $G(p)\geq 0$.
This shows that
$H\geq 0$ on $\partial S_\nu$ and by the minimum principle for harmonic
functions we obtain:
\[
H(q)\geq 0\quad\text{for all}\,\, q\in S_\nu\tag{i}
\]
\medskip

\noindent
Let us then consider some boundary arc
$\gamma_k$  
where $\gamma\subset\partial S_\nu$, i.e.   here $\nu=\nu(k)$.
Now $H=0$ on $\gamma_k$ and since (i) holds it follows that
the \emph{outer normal derivative}:
\[
\frac{\partial H}{\partial n}(p)\leq 0\quad p\in\gamma_k\tag{ii}
\]


\noindent 
Since 
$|F|=|F_\nu|=1$ holds on
$\gamma_k$ and the gradient of $H$ is parallell to the normal
we also get:
\[ 
\frac{\partial G}{\partial n}(p)=
-|F'(w)|\quad\text{and}\quad\,\,
\frac{\partial G_\nu}{\partial n}(p)=
-|F_\nu'(w)|
\quad\colon w\in\gamma_k
\]
Hence (ii) above gives
\[
|F'(w)|\geq |F_\nu'(w)|\quad\text{when}\quad  w\in\gamma_k\tag{iii}
\]
Next, since $f_\nu\in \mathcal A_\Phi$
we have
\[
|f_\nu'(F_\nu(w))|\leq \Phi(w)\tag{iv}
\]
and since $F_\nu$ is the inverse of $f_\nu$
we get

\[ 1=f_\nu'(F_\nu(w))\cdot F'_\nu(w)
\]
Hence (iv) entails
\[ |F'_\nu(w)|\geq
\frac{1}{ \Phi(w)}\tag{v}
\]
We conclude from
(iii) that

\[ |F'(w)|\geq
\frac{1}{ \Phi(w)}\quad \colon\,\, w\in\gamma_k\tag{vi}
\]
This holds for all the sub-arcs
$\gamma_1,\dots,\gamma_n$ and hence
we have proved the inequality
\[
|F'(w)|\geq
\frac{1}{ \Phi(w)}\quad\text{ for all}\quad  w\in\Gamma\tag{*}
\]
except  at a
finite number of  corner points.
To settle the situation at corner points we notice that
Poisson's formula applied to the harmonic function
$
\text{log}\, |f_*'(z)|$ in the unit disc gives
\[
\text{log}\, |f_*'(z)|=
\frac{1}{2\pi}\cdot \int_0^{2\pi}\,
\frac{1-|z|^2}{|e^{i\theta}-z|^2}\cdot
\text{log}\, |f'(e^{i\theta})|
\cdot d\theta\,.\tag{vii}
\]
\medskip

\noindent
Next, since $F$ is the inverse of $f_*$ we have
\[
|f_*'(z)|\cdot |F'(f(z))|=1\quad\text{for all}\,\,|z|=1\,.
\]
Hence (vi) gives
\[ 
|f'(z)|\leq \Phi(f_*(z))\quad\text{for all}\,\,|z|=1\,.
\]
With $\Phi= e^U$
we therefore get
\[
\text{log}\, |f'_*(z)|\leq U(f(z))
\quad\text{for all}\,\,|z|=1\,.
\]

\noindent
From the Poisson integral (vii) it follows that
\[
\text{log}\, |f_*'(z)|\leq 
\frac{1}{2\pi}\cdot \int_0^{2\pi}\,
\frac{1-|z|^2}{|e^{i\theta}-z|^2}\cdot
\, U(f_*(e^{i\theta}))
\cdot d\theta\,.\quad\, z\in D
\]


\medskip

\noindent
{\bf{A passage to the limit.}}
I addition to the obvious equi-continuity the passage to the limit
requires some care which is exposed in
[Beurling: Lemma 1, page 122].
Passing to the limit as $|z|\to 1$
the continuity of $\Phi$ implies that
$f_*$ belongs to $\mathcal A_\Phi$ which proves Lemma B.2.

\newpage

\centerline{\bf B.3 The construction of $f^*$}




\bigskip

\noindent
By the uniform bound for Lipschitz norms
the family $\mathcal A_\phi$
is equi-continuous. We can therefore find a denumerable dense subset
$\{h_\nu\}$. It means that to every
$f\in\mathcal A_\Phi$ and every $\epsilon>0$ there exists
some $h_\nu$ such that
the maximum norm
$|f-h_\nu|_D<\epsilon$.
It follows that
\[ 
\Omega^*=\cup\,\, h_\nu(D)
\]
Next, to every $n\geq 2$ we 
have the $n$-tuple $h_1,\ldots,h_n$
and
by Lemma B. 2 we construct the function
$f_n$ where we have the inclusions
\[ 
h_\nu(D)\subset f_n(D)\quad\colon\,1\leq\nu\leq n
\]
Moreover, the image domains $\{f_n(D)\}$ increase with $n$.
So (i) above gives
\[ 
\Omega^*=\cup\, f_n(D)\tag{*}
\]


\noindent
Next, $\{f_n\}$ is a normal family of analytic functions
and since their image domains increase it follows 
there exists the limit function
$f^*$ which belongs to $\mathcal  C$  and
(*) above gives the equality $f^*(D)=\Omega^*$.
There remains to prove that
$f^*$ also belongs to $\mathcal C_\Phi$. 
To get the inclusion
\[ 
f^*\in \mathcal C_\Phi
\]
\medskip
we   establish  a  relation between
$\Phi$ and the maximal domain
$\Omega^*(\Phi)$.
\medskip

\noindent
{\bf B.4 Proposition.}
\emph{Let $\Psi$ be a positive continuous function which is equal to
$\Phi$ outside $\Omega^*(\Phi)$ while 
its restriction to
$\Omega^*(\Phi)$ is arbitrary. Then
one has the equality}
\[
\Omega^*(\Phi)=
\Omega^*(\Psi)
\]


\noindent
\emph{Proof.}
The assumption gives
\[
 \Psi(w)=\Phi(w)\quad\text{for all}\,\, w\in\partial\Omega^*(\Phi)\tag{i}
 \]

\medskip

\noindent
It follows that
 $f^*\in\mathcal A_\Psi$. Hence the
 equality $f^*(D)=\Omega^*(\Phi)$ and 
the construction of
 $\Omega^*(\Psi)$ give the inclusion
 \[
 \Omega^*(\Phi)\subset\Omega^*(\Psi)\tag{ii}
\]

\medskip

\noindent
Next, let  $h^*$ be the mapping function associated to $\Psi$.
By the construction of the
maximal region $\Omega^*(\Phi$ we get:
\[
\Omega^*(\Psi)=h^*(D)\subset
 \Omega^*(\Phi)\tag{iv}
 \]
Hence (iii) and (iv) give the requested equality
\[
\Omega^*(\Psi)=
 \Omega^*(\Phi)\tag{v}
\] 

\bigskip


\centerline {\bf B.5 A special choice of $\Psi$}.
\medskip

\noindent
Keeping $\Phi$ fixed we put
$\Omega^*(\Phi)=\Omega^*$ to simplify
the notations. We have the $U$-function such that
\[ 
\Phi(w)= e^{-U(w)}\tag{vi}
\]
Now
$U(w)$ is a continuous function on
$\partial\Omega^*$
and solving the Dirichlet problem we obtain the function $U_*(w)$
where $U_*=U$ outside $\Omega^*$, and in $\Omega^*$ 
the function $U_*$ is the harmonic extension of the boundary
function $U$ restricted to
$\partial\Omega^*$.
Set
\[
\Psi(w)= e^{U_*(w)}
\]
Proposition B.4 gives 
\[ 
f^*\in\mathcal A_\Psi\tag{i}
\]
Next, consider  the function
in $D$ defined by:


\[ 
V(z)=\text{log}\, \bigl|\frac {d f^*(z)}{dz}\bigr|-U_*(f(z))
\] 
\medskip

\noindent
From (i) it follows that
$V(z)$ either is identically zero in
$D$ or everywhere $<0$. It is also clear
that if $V=0$ then
$f^*\in\mathcal C_\Phi$ as required.
So there remains only to prove:
\medskip

\noindent
{\bf B.6 Lemma.} \emph{The function $V(z)$ is identically zero in $D$.}
\medskip

\noindent
\emph{Proof.}
Assume the contrary. So now

\[
 \bigl|\frac {d f^*(z)}{dz}\,\bigr|<e^{U_*(z)}\quad\text{for all}\,\,z\in D\,.\tag{i}
\]
Let $F(w)$ be the inverse of $f$ so that :

\[
F'(f^*(z))\cdot   \frac {d f^*(z)}{dz}=1\quad\, z\in D
\]
Then (i) gives:
\[ 
\bigl|F'(w)\,\bigr|> e^{-U_*(w)}\quad w\in \Omega^*\tag{ii}
\]


\noindent
Next, let $V(w)$ be the harmonic conjugate of $U_*(w)$ normalised so that
$V(0)=0$ and set
\[ 
H(w)=\int_0^w\,
e^{-U_*(\zeta)+iV(\zeta)}\cdot d\zeta\,.
\]
Then (ii) gives
\[
\bigl|H'(w)\bigr|<
\bigl|F'(w)\bigr|\quad w\in \Omega^*\tag{iii}
\]
Since $H(w((0))=F(w(0))=0$ it follows that
\[ 
\inf_{w\in\Omega^*}\,\frac{|H(w)|}{|F(w)|}=r_0<1\tag{iv}
\]
Since $|F(w)|<1$ in $\Omega^*$
while $|F(w)|\to 1$ as $w$ approaches
$\partial\Omega^*$ we see that (iv) entails the domain
\[
R_0=\{ w\in \Omega^*\quad\colon\, |H(w)|<r_0\}\tag{v}
\]
has at least one boundary
point $w_*$ which also belongs to
$\partial\Omega^*$.
Next, the function $H(w)$ is analytic in $R_0$ and its derivative is everywhere
$\neq 0$ while $|H(w)|=1$ on $\partial R_0$. It follows
that $H$ gives a conformal map from $R_0$ onto the disc
$|z|<r_0$.
Let $h(z)$ be the inverse of this conformal mapping.
Now we get the 
analytic function in $D$ defined by
\[ 
g(z)= h(r_0z)
\] 
Next, let $|z|=1$ and put $w=h(r_0z)$.
Then 
\[ 
|g'(z)|= r_0\cdot |h'(r_0z)|=r_0\cdot \frac{1}{|H'(g(z))|}=
r_0\cdot e^{U_*(g(z))}=r_0\cdot\Psi(g(z))<\Psi(g(z))\tag{v}
\]
At the same time we have a common boundary point
\[ 
w_*\in\partial\Omega^*\,\cap\,\partial g(D)
\]


\noindent
Since the $g$-function extends to a continuous function on
$|z|\leq 1$ there exists a point
$e^{i\theta}$ such that
\[ 
g(e^{i\theta})= w_*
\]
Now we use that $r_0<1$ above.
The continuity of the $\Psi$
gives some $\epsilon>0$ such that
for any complex number $a$ which belongs to the disc
$|a-1|<\epsilon$, it follows that the function
\[
z\mapsto a\cdot g(z)
\]
belongs to $\mathcal A_\Psi$.
Finally, by  Proposition B.4  the maximal region for the $\Psi$-function is equal to
$\Omega^*$ and we conclude that
\[
ag(e^{i\theta})= aw_*\in \Omega^*\quad\, |a-1|<\epsilon
\]


\noindent
This would mean that
$w_*$ is an \emph{interior point} of
$\Omega^*$ which contradicts that $w_*\in\partial\Omega_*$.
Hence Lemma B.6 is proved.


\newpage


\centerline{\bf C. Proof of Theorem 3.}
\bigskip

\noindent
First we have a companion to
Lemma B.2. Namely, let $g_1,\ldots,g_n$
be a finite set in $\mathcal B_\Phi$.
Set $S_\nu=g_\nu(D)$. Following [Beur: page
123] we give
\medskip

\noindent
{\bf C.1 Definition.}
\emph{The reduced intersection of the family
$\{S_\nu\}$ is defined as the set of these points
$w$
which can be joined with the origin by a Jordan arc
$\gamma$ contained in the intersection $\cap\, S_\nu$.
The resulting domain is denoted by
$RI\{S_\nu\}$.}
\medskip

\noindent
{\bf C.2 Proposition.}
\emph{The domain $RI\{S_\nu\}$ is simply connected and if
$g\in \mathcal C$ is the normalised conformal mapping onto
this domain, then
$g\in\mathcal B_\Phi$.}
\medskip

\noindent
The proof of this result can be carried out in a similar way as in
the proof of Lemma B.2 so we leave out the details.
Next, starting from a  dense sequence
$\{g_\nu\}$ in $\mathcal B_\Phi$
we find for each $n$ the function $f_n\in \mathcal B_\Phi$
where
\[ 
f_n(D)=RI\{S_\nu\}\quad\colon\, S_\nu=g_\nu(D)\,\colon\, 1\leq\nu\leq n\,.
\]
Here the simply connected domains
$\{f_n(D)\}$ decrease and there exists the limit function
$f_*\in\mathcal C$ where
\[
f_*(D)=\Omega_*
\]
There remains to prove
\medskip

\noindent
{\bf C.3 Proposition.}
\emph{One has $f_*\in\mathcal C_\Phi$.}
\medskip

\noindent
{\bf Remark.}
Proposition C.3  requires a quite involved proof and is given in
[Beur: page 127-130].
We shall not try to present all the details and just
sketch the strategy in the proof. Put
\[ 
m=\inf_{g\in\mathcal B_\Phi}\, g'(0)
\]
\medskip


\noindent
Next, $f^*$  belongs to
$\mathcal B_\Phi$ because we have the trivial inclusion
$\mathcal C_\Phi\subset \mathcal B_\Phi$ and using this Beurling  proved that
\[ 
m\geq \min_{w\in\Omega^*}\,\Phi(w)
\]
Next, starting with  Proposition C.2 above, Beurling introduces  a  normal family
and proves that
\[ 
f_*'(0)=m
\]
Thus, $f_*$ is a solution to an extremal problem. This
is used  in the final part
of Beurling's  proof to establish the inclusion
$f_*\in\mathcal C_\Phi$.
Let us remark that  this part of the proof 
relies upon
some  subtle set-theoretic constructions
where  the family of regions of the \emph{Schoenfliess' type}
are introduced in [Beur: page 121].
The whole analysis involves topological investigations of
independent interest.


\newpage

\centerline{\bf{Conformal mapping onto comb domain}}
\bigskip

\noindent
{\bf{Introduction.}}
Let $\Omega$ be  a simply connected open set  in
${\bf{C}}$ with finite area and 
$\omega$  an open Jordan arc which appears as a relatively
open subset of
$\partial\Omega$. We say that $\omega$ has a convex
position in   $\Omega$ if the following hold: For each pair
of points $z\in\Omega$ and $a\in\gamma$ the
half-open  line segment
$[z,a)$ is contained in $\Omega$.
When this holds
we define a function
$\omega_*$ in $\Omega$ by
\[
\omega_*(z)=\inf_\gamma\, \int_\gamma\, |dz|
\]
where the infimum is taken over rectifiable Jordan
arcs
from $z$ with an end-point on $\omega$.
\medskip

\noindent
{\bf{Exercise}}\emph{Show that if  $\gamma$ has a convex position in
$\Omega$ then the  function $\omega_*$ is subharmonic.}
\medskip





\medskip

\noindent{Comb domains.} XXXX

\bigskip

\noindent
{\bf{Theorem.}}
\emph{Given the pair $\Omega,\omega$ there
exists a  comb domain $D$ and a
conformal mapping $f\colon\Omega\to D$ such that
$f(\gamma)$  is the base of $D$ and the following two inequalities hold:}

\[ 
\text{Area}(D)\leq 
\text{Area}(\Omega)\quad\colon\, 
\gamma_*(z)\leq \mathfrak{Re}(f(z))\quad\colon\, z\in \Omega
\]
\bigskip


\noindent
{\bf{The  conformal mapping $\kappa$}}.
Since $\omega$ is an aric in
$\partial\Omega$
there exists a conformal mapping $\kappa$
from $\Omega$ onto a domain $B$ in the right half-plane
such that
$\kappa(\omega)$ is the
imaginary axis, i.e. the line $\{x=0\}$.
In $B$ we get  the subharmonic function
\[ 
u_0^*\circ \kappa=\omega_*
\]





We are going to construct a conformal map
$\chi\colon B\to D$ where 
$D$ such that the composed conformal mapping
$f=\chi\circ\kappa$
gives (*) in the theorem.
To achieve this we shall perform certain constructions in
the strip domain $B$.
To begin with we have the subharmonic
function $u_0^*$ in $B$ where a notble fact is that

\[
\text{Area}(\Omega)=D(u_0^*)
\]
Same as the dirichlet integral !!!!!

\bigskip


\centerline{\bf{1. A study of $B$-domains.}}
\bigskip


\noindent
Denote by $\mathcal B$
the class of simply connected
domains  contained in the strip
$\{0<\mathfrak{Re}\, z<1\}$.
If $B\in\mathcal B$ a portion of its boundary
appears on the imaginary axis, i.e. we get
the closed set 
\[
B_*=\{y\colon\, iy\in\partial B\}
\]
This set may be infinite and is in general not connected.

\medskip


\noindent
{\bf{1.1 Proposition.}}
\emph{Let $u(x,y)$ be a harmonic function in $B$
which extends to a $C^1$-function on its closure.
Suppose also that $u(0,y)=0$ for all
$iy\in \partial B$ and that
the Dirichlet integral}
\[ 
D(u)=\iint_B\, (u_x^2+u_y^2)\, dxdy<\infty
\]
Then one has the equation
\[
 D(u)=2\cdot \iint_B\, u_x^2\, dxdy-\int_{B_*}\, u_x^2(0,y)\, dy
 \]
 

\medskip

\noindent
\emph{Proof.}
In general 
consider a $C^2$-function $f(x,y)$ and set
\[
I(x)= \int_{-\infty}^\infty\,[\, f_x^2(x,y)-f_y^2(x,y)]\, dy
\]
The derivative becomes
\[
\frac{dI}{dx}=
2\cdot \int_{-\infty}^\infty\,[f_xf_{xx}-f_yf_{xy}\, dy
\]
Next, a partial integration gives
\[
-\int_{-\infty}^\infty\,f_yf_{xy}\, dy
= -f_yf_x|xx +-\int_{-\infty}^\infty\,f_x\cdot f_{yy}\, dy
\]
Hence we obtain
\[
\frac{dI}{dx}=2\cdot \int_{-\infty}^\infty\,f_x\cdot \Delta f\, dy
\]
Taking the integral over $0\leq x\leq 1$ gives
\[
I(1)-I(0)= \iint_B\, f_x\cdot \Delta f\, dxdy
\]
\medskip

\noindent
{\bf{A special case.}}
Let $f=u$ where $u$ is harmonic and $u(0,y)=0$ for all $y$.
This implies that  $u_y(0,y)=0$ for all $y$
which shows that
\[
I(0)= \int_{-\infty}^\infty\, u^2_x(0,y)\, dy
\]
At the same time
(x) and $\Delta u=0$ show that
the function $x\to I(x)$ is constant which 
gives 
\[ 
I(0)=\int_0^1\, I(x)\,dx=\iint_B\, (u_x^2-u_y^2)\, dxdy
\]
From (xx) it follows that
the Dirichlet integral
\[
D(u)=\iint(u_x^2+u_y^2)\,dxdy= 2\cdot \iint\, u_x^2\,dxdy-
\int_{-\infty}^\infty\, u_x^2(0,y)\,dy\tag{*}
\]
\medskip


\noindent
{\bf{Exercise.}}
Let $\phi$ be subharmonic in $B$ where
$u^*(0,y)=0$ for all $y$. Use that
$\Delta u^*\geq 0$ and the same proof as above to deduce that
\[ 
D(\phi)\geq 2\cdot \iint\, \phi_x^2\,dxdy-\int_{-\infty}^\infty\, \phi_x^2(0,y)\,dy
\]

\medskip

\noindent
{\bf{Exrercise}}
In general, let $\phi(x,y)$ be a  
subharmonic function of class $C^2$ in
$B$ which extends continuously to $\bar B$. Define the function $\Phi$ by
\[ 
\Phi (x,y) \int_0^x\, |\phi_x(t,y)|\, dt
\]
Show that $\Phi$ is subharmonic and notice that
\[
\Phi^2_x=\phi^2_x
\]
Conclude from (*) and Exericce xx that
one gets the inequality
\[ 
D(\Phi)\geq D(\phi)
\]


\medskip


\noindent
Next, let $\phi$ be a subharmonic function
in $B$ with a finite Dirichlet integral.
Assume that $\phi(0,y)=0$ for all $y$
while $y\to \phi(1,y)$ is a continuous function.
Solving the Dirichlet problem we find
the harmonic function
$U_\phi$ which extends $\phi$.
By Dirchlet's principle in ¤ xx we have
\[
D(U_\phi)\leq D(\phi)
\]



\noindent
{\bf{A recursion.}}
Start with a subharmonic function $u^*_0$ in $B$ where
$u^*_0(0,y)=$.
Denote by $u_1$ the harmonic function which solves the
Dirichlet problem with $u^*_0$ as boundary value.
 Then we construct the subharmonic function
 \[
 u_1^*(x,y)= \int_0^x\, |(u^*_0)_x|(t,y)\, dt
\]
In the next stage $u_2$ is the harmonic function with
$u_1^*$ s boundary function. Inductively
we get a sequence
of such $u$ and $u^*$-functions. Here
\[ 
u^*_n\leq u_{n+1}\leq u_{n+1}^*\leq \ldots
\] 
hold for all $n$.  At the same time
(xx) above entails that the Dirichlet integrals decrease:
\[
D(u_0^*)\geq D(u_1)\geq D(u_1^*)\geq D(u_2)\geq \ldots
\]


\noindent
These two reversed sequences of inequalities and Harnacks Theorem
ential that there exists a limit function
\[
U=\lim\,u_n=\lim u^*_n
\]
Here $U$Êis harmonic in $B$ and by construction
the partial $x$-derivatives of the $u^*$-functions are all $\geq 0$ and hence
$U_x\geq 0$ in $B$. At the same time
$U(0,y)=0$ for all $y$. Now Theorem xx implies that
if $V$ is the conjugate harmonic function of $U$ then
$f=U+iV$ gives a conformal mapping
from $B$ onto a comb domain $\Omega$.
Moreover
the dewcrsing sequece of Dirichlet integrals entail that

\[
\text{Area}(\Omega)=
D(U)\leq D(u^*_0)
\]

LOGIC: We have started with a domain $D$
with a portion on boundary convex and
and first find $\kappa\colon D\to B$ sends portion to the $y$-axis
and $u_0^*$ becomes a subharmonic function
in $B$.
Starting from $u_0^*$ we perform the recursion above¬
and arrive at $U$ which eith $f=U+iV$ gives
a conformal map $B$ to comb domain.
The composed map $f\circ \kappa$ sends the given domin onte the
comb domsin where
area now shrinks why one has a stretched  in the other direction:

\[ 
[z,\alpha]\leq \mathfrak{Re}\,f(z)\quad z in domain
\]



\newpage


Let $0<b<1$ and consider the Mšbius transform
\[ 
T_b(z)= \frac{b-z}{1-bz}
\]
Notice that the composed map
\[ 
T_b\circ T_b(z)
 \frac{b- \frac{b-z}{1-bz}}{1- b\cdot  \frac{b-z}{1-bz}}=z
\] 
Next, if  
$w\in{\bf{C}}$ we have
$w=T_b(w)$ if
\[ 
w= \frac{b-w}{1-bw}\implies
2w=b+bw^2
\]
Thus can be rewritten as
\[ 
(w-\frac{1}{b})^2=\frac{1}{b^2}-1
\]
Thus, the fixed points of $T_b$ consists of the circle
of radius $\sqrt{b^{-2}-1}$ centered at $\frac{1}{b}$.
By a figure we see that it intersects the unit disc $|w|=1$ 
for all $0<b<1$ in a circular arc $\gamma_b$
intersects the real axis
at the point 
\[
u=\frac{1-\sqrt{1-b^2}}{b}
\]









\noindent






\end{document}






