

\documentclass{amsart}

\usepackage[applemac]{inputenc}

\addtolength{\hoffset}{-12mm}
\addtolength{\textwidth}{22mm}
\addtolength{\voffset}{-10mm}
\addtolength{\textheight}{20mm}

\def\uuu{_}

\def\vvv{-}

\begin{document}

\centerline{\bf\large{Functional analysis and operator theory}}

\bigskip




\centerline {\bf \large {8. Bounded self-adjoint operators.}}

\medskip

\noindent
{\bf Introduction.}
Let $\mathcal H$ be a complex Hilbert space.
A bounded linear operator $S$ on $\mathcal H$ is 
self-adjoint if $S=S^*$, or equivalently
\[ 
\langle x,Sy \rangle=\text{the complex conjugate of}\,\, 
\langle Sx, y\rangle\quad\colon\quad x,y\in \mathcal H\tag{*}
\]
If $S$ is self-adjoint we have the equality of operator norms:
\[ 
||S||^2=||S^2||\tag{1}
\]
To see this we notice that if $x\in\mathcal H$ has norm one then
\[
\langle Sx,Sx\rangle=
\langle x,S^*Sx\rangle=
\langle x,S^2x\rangle\tag{i}
\]
By the Cauchy-Schwarz inequality the last term
is $\leq ||x|\cdot ||S^2||$. Since (i) holds for
every $x$ of norm one we conclude that
\[
||S||^2\leq ||S^2||
\]
Now (1) follows
from the multiplicative inequality for operator norms.
Next, by induction over $n$ we get the
equalities
\[
||S||^{2n}=||S^n||^2\quad\,\colon\,\,n\geq 1
\]
Taking the $n$:th root and passing to the limit the spectral
radius formula gives
\[
||S||=\max_{z\in\sigma(S)}\, |z|\tag{*}
\]


\noindent
Next, we
consider the spectrum of self-adjoint operators.

\medskip

\noindent
{\bf{8.1 Theorem.}}
\emph{The spectrum of a bounded self-adjoint operator
is a compact real interval.}
\medskip

\noindent
\emph{Proof.}
Let $\lambda$ be a complex number 
and for a given $x$ we set
$y=\lambda x-Sx$.
It follows that
\[ 
||y||^2=|\lambda|^2\cdot ||x||^2+||Sx|^2+
\lambda\cdot \langle x,Sx\rangle+
\bar \lambda\cdot \langle Sx,x\rangle
\]
Since $S$ is self-adjoint
we get
\[
\lambda\cdot \langle x,Sx\rangle+
\bar \lambda\cdot \langle Sx,x\rangle=2\cdot \mathfrak{Re}(\lambda)\cdot
\langle Sx,x\rangle
\]
Now $|\langle Sx,x\rangle|\leq ||Sx||\cdot ||x||$
so the triangle inequality gives
\[
||y||^2\geq |\lambda|^2\cdot ||x||^2+||Sx|^2-2|\mathfrak{Re}(\lambda)||\cdot
||Sx||\cdot ||x||\tag{i}
\]
With $\lambda=a+ib$
the right hand side becomes
\[ 
b^2||x||^2+a^2||x||^2+||Sx||^2-2a\cdot ||Sx||\cdot ||x||\geq b^2||x||^2
\]
Hence we have proved that
\[ 
||\lambda x-Sx||^2\geq( \mathfrak{Im}\,\lambda)^2\cdot ||x||^2\tag{ii}
\]
This implies that
$\lambda E-S$ is invertible for every non-real $\lambda$
which proves Theorem 8.1. Notioce that the proof also gives 
\[
||(\lambda E-S)^{-1}||\leq \frac{1}{|\mathfrak{Im}\,\lambda|}\tag{iii}
\]





\medskip



\noindent
Theorem 8.1 together with
general results about uniform algebras in ¤ XX
 give the following:
\medskip


\noindent
{\bf{8.2 Theorem.}}
\emph{Denote by ${\bf{S}}$  the closed subalgebra of
$L(\mathcal H,\mathcal H)$ generated by $S$ and the identity
operator. Then ${\bf{S}}$ is 
a sup-norm algebra which is isomorphic to
the sup-norm algebra
$C^0(\sigma(S))$.}


\medskip


\noindent
{\bf{Exercise.}}
Let $T$ be an arbitary bounded opertor
on $\mathcal H$. Show that
the operator $A=T^*T$ is self-adjoint and that $\sigma(A)$
is a compact subset of $[0,+\infty)$,  i.e. every point in its spectrum os
real and non-negative.
A hint is to use the biduality formula $T= T^{**}$
and if $s$ is real the reader should verify that
\[
||sx+T^*T x||^2=s^2||x||^2+2s\cdot ||Tx||^2+||T^*T x||^2
\]

\newpage

\centerline{\bf{8.3 Normal operators.}}
\bigskip

\noindent
A bounded linear operator $A$ is normal if it commutes with its
adjoint $A^*$.
Let $A$ be normal and put $S=A^*A$ which yields a self-adjoint by  Exercise 8.2.
Here  (8.0.1) gives
\[
||S||^2= ||S^2||=||A^2\cdot A(^*)^2||\leq
||A^2||\cdot ||(A^*)^2||\tag{1}
\]
where we used the multiplicative inequality for operator norms.
Now $(A^*)^2$ is the adjoint of $A^2$
and we recall from ¤ xx that
the norms of an operator and its adjoint are equal. Hence
the right hand side in (1) is equal to $||A^2||^2$.
At the same time
\[
||S||= ||A^*A||= ||A||^2
\] 
and we conclude that (1) gives
\[
||A||^2\leq ||A^2||\tag{3}
\]
Exactly as in the self-adjoint case we can take higher powers
and obtain
the equality
\[
||A||=\max_{z\in\sigma(A)}\,|z|\tag{*}
\]
Since every polynomial in $A$ again is a normal operator
for which (*) holds we have proved the following:
\medskip

\noindent
{\bf{8.4 Theorem}}
\emph{Let $A$ be a normal operator.
Then the closed subalgebra ${\bf{A}}$ generated by
$A$ in  $L(\mathcal H,\mathcal H)$
is a sup-norm algebra.}
\medskip

\noindent
{\bf{Remark.}}
The spectrum $\sigma(A)$ is 
some compact subset of  ${\bf{C}}$ and in general analytic polynomials
restricted to $\sigma(A)$ do not generate a dense subalgebra of
$C^0(\sigma(A))$.
To get a more extensive algebra
we
consider the closed subalgebra $\mathcal B$
of
$L(\mathcal H,\mathcal H)$ which is generated by $A$ and $A^*$.
Since every  polynomial in $A$ and $A^*$ again is a normal operator
it follows that 
$\mathcal B$ is a sup-norm algebra and here 
the following holds:

\medskip
\noindent
{\bf{8.5 Theorem.}}
\emph{The sup-norm algebra $\mathcal B$ is via the Gelfand
transform isomorphic with $C^0(\sigma(A))$.}
\medskip

\noindent
\emph{Proof.}
Let $Q\in\mathcal B$
be arbitrary. Now $S=Q+Q^*$  is self-adjoint and 
Theorem 8.1 entails that its
Gelfand transform is real-valued, i.e. the function 
$\widehat Q(p)+\hat Q^*(p)$ is real. So if  
with $\widehat Q(p)= a+ib$ we must have $\hat Q^*=a_1-ib$ for some 
real number $a_1$. Next,  $QQ^*$ is also self-adjoint and hence
$(a+ib)(a_1-ib)$ is real. This gives $a=a_1$ and which shows that  
the Gelfand transform of $Q^*$ is the complex conjugate function of
$\widehat Q$. Hence the Gelfand transforms of $\mathcal B$-elements is 
a self-adjoint algebra and 
the Stone-Weierstrass theorem implies that
the Glefand transforms of $\mathcal B$-elements is 
equal to the whole algebra 
$C^0(\mathfrak{M}_\mathcal B$.
Finally, since $\widehat A^*$ is the complex conjugate function of 
$\widehat A$ it follows that the Gelfand transform
$\widehat A$  separates points on $\mathfrak{M}_\mathcal B$
which means that this maximal ideal space can be identified with
$\sigma(A)$.


\bigskip


\centerline {\bf{8.6 Spectral measures.}}
\medskip


\noindent
Let $A$ be a normal operator and  $\mathcal B$ is the
Banach algebra above.
Each   pair of vectors $x,y$
in
$\mathcal H$ yields
a linear functional on
$\mathcal B$ defined by 
\[ 
T\mapsto \langle Tx,y\rangle
\]
Identifying
$\mathcal B$ with $C^0(\sigma(A))$,
the Riesz representation formula gives 
a unique Riesz measure 
$\mu_{x,y}$ on $\sigma(A)$ such that
\[
\langle Tx,y\rangle=\int_{\sigma(A)}\, \widehat T(z)\cdot d\mu_{x,y}(z)\tag{8.6.1}
\] 
hold for every $T\in \mathcal B$.
Since $\widehat A(z)=z$ we have 
\[
\langle Ax,y\rangle=\int\, z\cdot d\mu_{x,y}(z)
\]
Similarly one has
\[
\langle A^*x,y\rangle=\int\, \bar z\cdot d\mu_{x,y}(z)
\]
\medskip

\noindent
{\bf{8.7 The operators $E(\delta)$}}.
Notice  that (8.6.1) implies that the map
from $\mathcal H\times\mathcal H$ into
the space of Riesz measures on $\sigma(A)$ is bi-linear.
We have for example:
\[
\mu_{x_1+x_2,y}=\mu_{x_1,y}+\mu_{x_2,y}
\]



\noindent
Moreover, since
$\mathcal B$ is the sup-norm algebra $C^0(\sigma(A))$
the total variations of the $\mu$-measures
satisfy the equations:
\[
||\mu_{x,y}||\leq\max_{T\in \mathcal B_*}|\langle Tx,y\rangle|\tag{8.7.1}
\]
where $\mathcal B_*$ is the unit ball in
$\mathcal B$. From this we obtain
\[
|| \mu_{x,y}||\leq ||x||\cdot ||y||\tag{8.7.2}
\]


\noindent
Next, let $\delta$ be a Borel subset of
$\sigma(A)$. Keeping $y$ fixed in $\mathcal H$
we obtain a linear functional on $\mathcal H$ defined by
\[ 
x\mapsto 
\int_\delta \,  d\mu_{x,y}(z)=\mu_{x,y}(\delta)
\]
By (8.7.2) it has norm $\leq ||y||$ and is represented by
a vector $E(\delta)x$ in $\mathcal H$. More precisely 
\[
\langle E(\delta)x,y\rangle= 
\int_\delta \,  d\mu_{x,y}(z)=\mu_{x,y}(\delta)\tag{8.7.3}
\]
\medskip

\noindent
{\bf{8.8 Exercise.}}
Show that $x\mapsto E(\delta)x$ is linear and that
the resulting linear operator
$E(\delta)$
commutes with all operators in $\mathcal B$. Moreover, show that 
it is a self-adjoint projection, i.e.
\[ 
E(\delta)^2=E(\delta)\quad\text{and}\quad
E(\delta)^*=E(\delta)
\]
Finally, show that
\[
E(\delta_1\cap\delta_2)=E(\delta_1)E(\delta_2)
\] 
holds for every pair of Borel subsets and with
$\delta=\sigma(A)$ one gets the identity operator.

\bigskip
\noindent
{\bf{8.9 Resolution of the identity.}}
If $\delta_1,\ldots,\delta_N$ is any finite family of disjoint 
Borel sets whose union is
$\sigma(A)$ then
\[
1= E(\delta_1)+\ldots +E(\delta_N)
\]
At the same tine we get a decomposition of the operator $A$:
\[
A=A_1+\ldots+A_N\quad\text{where}\quad
A_k=E(\delta_k)\cdot A
\]
For each $k$ the spectrum $\sigma(A_k)$ is equal to  the closure of
$\delta_k$. So the normal operator is represented by a sum of normal operators
where the individual operators have  small spectra when the
$\delta$-partition is fine.


\newpage

\centerline{\bf{9. Unbounded operators on Hilbert spaces}}
\bigskip


\noindent
Let $T$ be a densely
defined
linear operator on a complex Hilbert space $\mathcal H$.
We  suppose that 
$T$ is unbounded so that:
\[ 
\max_{x\in\mathcal D_*(T)}\, ||Tx||=+\infty
\quad \mathcal D_*(T)=\text{ the set of unit vectors in}\quad 
\mathcal D(T)
\]

\medskip

\noindent{\bf{9.1 The adjoint $T^*$.}}
If $y\in\mathcal H$  we get a linear functional on
$\mathcal D(T)$ defined by
\[
 x\mapsto \langle Tx,y\rangle\tag{i}
\]
If there exists a constant $C(y)$ such that
the absolute value of (i) is $\leq C(y)\cdot ||x||$ for every
$x\in\mathcal D(T)$, then  (i) extends to a continuous linear
functional on
$\mathcal H$.
The extension is unique because 
$\mathcal D(T)$ is dense and since   $\mathcal H$ 
is self-dual there exists 
a
unique vector
$T^*y$ such that
\[
\langle Tx,y\rangle=
\langle x,T^*y\rangle\quad\colon\quad x\in\mathcal D(T)
\tag{9.1.1}
\]
This gives  a linear operator $T^*$
where $\mathcal D(T^*)$ is characterised  as above.
Now we shall  describe the
graph of $T^*$. For this purpose 
we consider  the Hilbert space  $\mathcal H\times\mathcal H$
equipped with the  inner product
\[
\langle (x,y),(x_1,y_1)\rangle= 
\langle x,x_1\rangle+\langle y,y_1\rangle
\]
On $\mathcal H\times\mathcal H$ we define the linear operator
\[ 
J(x,y)= (-y,x)
\]


\noindent
{\bf{9.2 Proposition.}}
\emph{For every densely defined operator $T$
one has the equality}
\[ 
\Gamma(T^*)= J(\Gamma(T))^\perp
\]


\noindent
\emph{Proof.}
Let $(y,T^*y)$ be a vector in
$\Gamma(T^*)$. If $x\in\mathcal D(T)$  the equality (9.1.1)
and the construction of $J$ give
\[
\langle (y,-Tx\rangle + \langle  T^*y,x\rangle =0
\]
This proves  that $\Gamma(T^)*\perp
J(\Gamma(T))$. Conversely,  if 
$(y,z)\perp J(\Gamma(T))$
we have
\[
\langle y,-Tx\rangle + \langle  z,x\rangle=0
\quad\colon x\in\mathcal D(T)\tag{i}
\]
This shows that
$y\in\mathcal D(T^*)$ and  $z=T^*y$ which proves Proposition 9.2.
\medskip

\noindent
{\bf{9.3 Consequences.}}
The   orthogonal complement of
a subspace in a Hilbert space is  always
closed. Hence   Proposition 9.2 entails  that
$T^*$ has a closed graph. Passing to the closure of
$\Gamma(T)$
the decompostion of a Hilbert space
into a direct sum of a closed subpace and its orthogonal complement gives
\[
\mathcal H\times\mathcal H=
\overline{J(\Gamma(T))}\oplus \Gamma(T^*)
\tag{9.3.1}
\]


\noindent
Notice also that 
\[
\Gamma(T^*)^\perp=\overline{J(\Gamma(T))}\tag{9.3.2}
\]
\medskip

\noindent
{\bf{9.4 Closed extensions of operators.}}
A closed operator $S$ 
is called a
closed extension of $T$ if
\[
\Gamma(T)\subset\Gamma(S)
\]

\medskip

\noindent
{\bf{9.4.1 Exercise.}}
Show that 
if $S$ is a  closed extension of $T$ then
\[
S^*=T^*
\]



\noindent
{\bf{9.4.2 Theorem.}}
\emph{A densely defined operator $T$  has a closed extension if and only if
$\mathcal D(T^*)$ is dense.
Moreover, if $T$ is closed one has the biduality formula
$T=T^{**}$.}
\medskip

\noindent
\emph{Proof.}
Suppose first that $T$ has a closed extension. 
If $\mathcal D(T^*)$ is not dense 
there
exists a non-zero vector $0\neq h\perp \mathcal D(T^*)$ and
(9.3.2) gives
\[
(h,0)\in\Gamma(T^*)^\perp=J(\Gamma(T))\tag{ii}
\]
By the construction of $J$ this would give
$x\in\mathcal D(T)$ such that
$(h,0)=(-Tx,x)$ which cannot hold since
this equation first gives $x=0$ and then
$h=T(0)=0$.
Hence  closedness of $T$ implies that
$\mathcal D(T^*)$ is dense.
Conversely, assume that
$\mathcal D(T^*)$ is  dense. 
Starting from $T^*$  we 
construct its adjoint  $T^{**}$ and 
Proposition 9.3.2 applied with $T^*$  gives
\[
\Gamma(T^{**})= J(\Gamma(T^*)^\perp\tag{i}
\]
At the same time 
$J(\Gamma(T^*)^\perp$ is equal to the closure of
 $\Gamma(T)$ so (i) gives
\[
\overline{\Gamma(T)}=
\Gamma(T^{**})\tag{ii}
\]
which proves that $T^{**}$ is a closed extension of $T$.
\medskip

\noindent
{\bf{9.4.3 The biduality formula.}}
Let  $T$ be  closed. and  densely defined operator. from the above 
$T^*$ also is densely defined and closed. Hence its
dual exists. It 
is denoted by
$T^{**}$ and called the bi-dual of $T$. With these notations one has:
\[
T=T^{**}\tag{*}
\]
\medskip

\noindent
{\bf{9.4.4 Exercise.}} Prove the equality (*). 

\bigskip


\centerline {\bf{9.5 Inverse operators.}}.
\medskip

\noindent
Denote by
$\mathfrak I(\mathcal H)$ the set of
closed and densely defined operators $T$ such that
$T$ is injective on $\mathcal D(T)$ and the range $T(\mathcal D(T))$Êis dense in
$\mathcal H$.
If $T\in\mathfrak I(\mathcal H)$
there exists the densely defined operator $S$ where
$\mathcal D(S)$ is the range of  $T$ and
\[
S(Tx)= x\quad\colon\quad x\in\mathcal D(T)
\]
By this construction the range of $S$ is equal to
$\mathcal D(T)$. Next, 
 on $\mathcal H\times\mathcal H$
we have the isometry defined by
$I(x,y)= (y,x)$,  i.e we  interchange the pair of vectors.
The construction of $S$ gives 
\[ 
\Gamma(S)= I(\Gamma(T))\tag{i}
\]
Since $\Gamma(T)$ by hypothesis is closed it follows that
$S$ has a closed graph and we conclude that $S\in\mathfrak I(\mathcal H)$.
Moreover, since $I^2$ is the identity on
$\mathcal H\times \mathcal H$ we have
\[ 
\Gamma(T)= I(\Gamma(S))\tag{ii}
\]
We refer to $S$ is as the inverse of
$T$. It is denoted by $T^{-1}$
and  (ii) entails  that
$T$ is the inverse of $T^{-1}$, i.e. one has
\[ 
T=(T^ {-1})^{-1}\tag{*}
\]

\medskip

\noindent
{\bf{9.5.1 Exercise.}}
Let $T$ belong to
$\mathfrak I(\mathcal H)$.
Use the description of $\Gamma(T^*)$
in Proposition 9.3   to show that $T^*$  belongs to 
$\mathfrak I(\mathcal H)$  and the equality  
\[
(T^{-1})^*= (T^*)^{-1}\tag{**}
\]

\medskip


\centerline {\bf{9.6 The operator $T^*T$}}.
\medskip

\noindent
Each 
$h\in\mathcal H$ gives  the vector $(h,0)$ in
$\mathcal H\times\mathcal H$ and  (9.3.1) gives
a  pair  $x\in\mathcal D(T)$ and $y\in\mathcal D(T^*)$.
such that
\[
(h,0)= (x,Tx)+(-T^*y,y)=(x-T^*y, Tx+y)
\]
With $u=-y$ we get $Tx=u$ and obtain
\[
 h=x+T^*(Tx)\tag{9.6.1}
\]


\medskip

\noindent
{\bf{9.6.2  Proposition.}}
\emph{ The vector $x$ in (9.6.1) is uniquely determined by $h$.}

\medskip

\noindent
\emph{Proof.}
Uniqueness follows if we show that
\[
x+T^*(Tx)\implies x=0
\]
But this is clear since the construction
of $T^*$ gives
\[
0=\langle x,x)\rangle+ \langle x,T^*(Tx)\rangle=
\langle x,x)\rangle+ \langle Tx,Tx)\rangle\implies x=0
\] 
\medskip

\noindent
{\bf{9.7 The density of $\mathcal D(T^*T)$}}.
This is the subspace of $\mathcal D(T)$ where the extra
 condition for a vector $x\in\mathcal D(T)$ is that
$Tx\in\mathcal D(T^*)$.
To prove that
$\mathcal D(T^*T)$ is dense we consider some orthogonal vector $h$.
Proposition 9.6 gives some $x\in\mathcal D(T)$ such that
$h=x+T^*(Tx)$ and 
for every $g\in \mathcal D(T^*T)$ we have
\[
0=\langle x,g\rangle+\langle T^*Tx,g\rangle=
\langle x,g\rangle+\langle Tx,Tg\rangle=
\langle x,g\rangle+\langle x,T^*Tg\rangle
\tag{i}
\]
Here (i) hold for every $g\in\mathcal D(T^*T)$ and
by another application of Proposition 9.6 we  find $g$ so that
$x= g+T^*Tg$ and then (i) gives $\langle x,x\rangle =0$ so that
$x=0$.
But then we also have $h=0$ and the requested density follows.
\medskip

\noindent
{\bf{Conclusion.}}
Set $A=T^*T$.
From the above it is densely defined and
(9.6.1) entails that
the densely defined operator $E+A$ is injective. Moreover,   its range is
equal to $\mathcal H$.
Notice  that
\[
\langle x+Ax,x+Ax\rangle = c+ 
\langle x,Ax\rangle+\langle Ax,x\rangle
\]
Here
\[
\langle x,Ax\rangle=\langle x,T^*Tx\rangle=
\langle Tx,Tx\rangle= ||Tx||^2
\]
and from this
the reader can conclude that
\[
||x+Ax||^2= ||x||^2+||Ax||^2+2\cdot ||Tx||^2\quad\colon x\in \mathcal D(A)
\]
The right hand side is $\geq ||x||^2$ which
implies that
$E+A$ is invertible in Neumann's sense.

\medskip




\noindent
{\bf{9.8 The equality  $A^*=A$}}.
Recall the biduality
formula
$T= T^{**}$ and apply Proposition 9.6 starting with
$T^*$. It follows 
that
$\mathcal D(TT^*)$ also is dense and 
exactly as in (9.6.1) every $h\in\mathcal H$ has a unique
representation
\[ 
h= y+T(T^*y)
\]
\medskip

\noindent
{\bf{9.9. Exercise.}}
Verify from the above that $A$ is self-adjoint, i.e one has the equality $A=A^*$.



\bigskip




\centerline{\bf{9.10 Unbounded self-adjoint operators.}}
\bigskip

\noindent
A densely defined operator $A$ 
on the Hilbert space $\mathcal H$
for which $A=A^*$ is called self-adjoint. 


\medskip

\noindent
{\bf{9.11 Proposition}}
\emph{The spectrum of a self-adjoint operator
$A$ is contained in
the real line, and if
$\lambda$ is non-real  the resolvent
satisfies the norm inequality}
\[ 
||R_A(\lambda)||\leq \frac{1}{|\mathfrak{Im}\,\lambda|}
\]


\noindent
\emph{Proof.}
Set $\lambda=a+ib$ where $b\neq 0$.
If $x\in\mathcal D(A)$ and $y=\lambda x-Ax$ we have
\[
||y||^2=|\lambda|^2\cdot ||x||^2+||Ax||^2-2\cdot \mathfrak{Re}(\lambda)\cdot \langle x,Ax\rangle
\]

\noindent
The Cauchy-Schwarz inequality gives
\[
||y||^2\geq b^2||x||^2+ a^2||x||^2+||Ax||^2-2|a|\cdot ||Ax||\cdot ||x||
\geq
b^2||x||^2\tag{i}
\]

\noindent
This proves that  $x\to \lambda x-Ax$ is injective and
since
$A$ is closed  the range of
$\lambda\cdot E-A$ is closed.
Next, if $y$ is $\perp$ to this range we have
\[
0=\lambda \langle x,y\rangle -\langle Ax,y\rangle\quad\colon
x\in\mathcal D(A)
\]
From this we see that $y$ belongs to $\mathcal D(A^*)$ and since
$A$ is self-adjoint we get
\[
0=\lambda \langle x,y\rangle -\langle x,Ay\rangle
\]
This holds for all $x$ in the dense subspace $\mathcal D(A)$ which gives
$\lambda\cdot y=Ay$
Since $\lambda$ is non-real we have already seen that this entails that
$y=0$.
Hence the range of $\lambda\cdot E-A$ is equal to $\mathcal H$ and the inequality
(i) entails $R_A(\lambda)$
has norm
$\leq\frac{1}{|\mathfrak{Im}\lambda|}$.


\medskip

\noindent{\bf{9.12 A conjugation  formula.}}
Let $A$ be self-adjoint. For each complex number
$\lambda$  the hermitiain inner product on
$\mathcal H$ gives the equation
\[
\bar\lambda-A= (\lambda\cdot E-A)^*
\]
So when we take the complex conjugate of $\lambda$ it follows that
¤ 9.5 that 
\[
R_A(\lambda)^*= R_A(\bar\lambda)\tag{9.12.1}
\]

\noindent


\medskip

\noindent{\bf{9.13 Properties of resolvents.}}
Let $A$ be self-adjoint.
By Neumann's resolvent calculus 
the family $\{(R_A(\lambda)\}$ 
consists of pairwise commuting bounded operators
outside the spectrum of $A$. Since $\sigma(A)$ is real 
there exist  operator-valued analytic functions $\lambda\mapsto R_A(\lambda)$Ê
in the upper- respectively the lower half-plane.
Moreover, since Neumann's  resolvents  commute, it follows
from (9.12.1) that
$R_A(\lambda)$ commutes with its adjoint. Hence
every resolvent is a bounded normal operator.


\bigskip

\noindent
{\bf{9.14 A special resolvent operator.}}
Take $\lambda=i$ and set
$R=R_A(i)$. So here
\[ 
R(iE-A)(x)= x\quad\colon\quad x\in\mathcal D(A)
\]

\medskip

\noindent
{\bf{9.15 Theorem.}}
\emph{The spectrum $\sigma(R)$ is contained in the circle}
\[
C_*=\{|\lambda+i/2|= 1/2\}
\]


\noindent
\emph{Proof.}
Since $\sigma(A)$ is confined to the real line, it follows from
¤ 0.0. XX  that
points in $\sigma(R)$ have the form
\[
\lambda=\frac{1}{i-a}\quad\colon a\in {\bf{R}}
\]
This gives
\[
\lambda+i/2=\frac{1}{i-a}+i/2=
\frac{1}{2(i-a)}(2+i^2-ia)=
\frac{1-ia}{2i(1+ia)}
\]
and the last term has absolute value $1/2$ for every real $a$.




\bigskip



\centerline{\bf{9.B. The spectral theorem for unbounded 
self-adjoint operators.}}
\bigskip

\noindent
 The operational calculus in ¤ 8.3-8.6
applies to the bounded
normal operator $R$ in ¤ 9.14.
If $N$ is a positive integer we
set
\[
C_*(N)=\{\lambda\in C_*\,\colon\,\mathfrak {Im}(\lambda)
\leq - \frac{1}{N}\}\quad\text{and}\quad 
\Gamma_N=C_*(N)\cap \sigma(R)
\]
Let $\chi_{\Gamma_N}$ be the characterstic function of $\Gamma_N$.
Now
\[ 
g_N(\lambda)=\frac{1-i\lambda}{\lambda}\cdot \chi_{\Gamma_N}
\] 
is  Borel functionon
$\sigma(R)$ which by 
operational calculus in ¤ 8.xx 
gives a bounded and normal linear operator denoted by $G_N$.
On $\Gamma_N$ we have
 $\lambda=-i/2+\zeta$ where
$|\zeta|= 1/2$. This
gives
\[
\frac{1-i\lambda}{\lambda}=
\frac{1/2-i\zeta}{-i/2+\zeta}
=\frac{(1/2-i\zeta)(i/2+\bar\zeta)}{|\zeta-i/2|^2}
=\frac{\mathfrak{Re}\,\zeta}{|\zeta-i/2|^2}\tag{1}
\]
By  ¤ 8.x the spectrum of
$G_N$ is the range of the $g$-function on $\Gamma_N$ and  (1) 
entails that
$\sigma(G_N)$ is real. Since  $G_N$ also is normal it follows 
that it is self-adjoint.
Next, notice that
\[ 
\lambda\cdot (\frac{1-i\lambda}{\lambda}+i)=1\tag{2}
\]
holds on $\Gamma_N$.
Hence
operational calculus  gives the  equation
\[
R(G_N+i)=E(\Gamma_N)\tag{3}
\]
where $E(\Gamma_N)$
is a self-adjoint projection.
Notice also that
\[
R\cdot G_N=(E-iR)\cdot E(\Gamma_N)\tag{4}
\]
Hence (3-4) entail that
\[
E(\Gamma_N)-iRE(\Gamma_N)=(E-iR)\cdot E(\Gamma_N)\tag{5}
\]


\medskip

\noindent
Next, the equation $RA=E-iR$ gives
\[
RAE(\Gamma_N)=(E-iR)E(\Gamma_N)=R\cdot G_N\tag{*}
\]
\medskip

\noindent
{\bf{9.B.1 Exercise.}}
Conclude from the above that
\[
AE(\Gamma_N)= G_N\tag{*}
\] 
Show also that:
\[ 
\lim_{N\to\infty}\, AE(\Gamma_N)(x)= A(x)\quad
\text{for each}\quad x\in\mathcal D(A)\tag{**}
\]
\medskip

\noindent
{\bf{9.B.2 A general construction.}}
For  each bounded
Borel set $e$
 on the real line
we get a  Borel set 
$e_*\subset \sigma(R)$ 
given
by
\[ 
e_*=\sigma(R)\,\cap\, \{\frac{1}{i-a}\, a\in e\}
\]
The operational calculus  gives
the self-adjoint operator $G_e$ constructed via
$g\cdot \chi_{e_*}$.
We have also the operstor $E(e)$ given by
$ \chi_{e_*}$ and exactly as above we get
\[
AE(e)=G_e
\]
The bounded self-adjoint operators
$E(e)$ and $G_e$ commute with
$A$
and  $\sigma(G_e)$ is contained in the closure of 
the bounded Borel set $e$.
Moreover each $E(e)$ is a self-adjoint projection
and for each pair of bounded Borel sets we have
\[
E(e_1)E(e_2)= E(e_1\cap E(e_1)
\]
In particular the composed operators 
\[
E(e_1)\circ E(e_2)=0
\]
when the Borel  sets are disjoint.
\medskip


\noindent
{\bf{9.C The spectral measure.}}
Exactly as for bounded
self-adjoint operators the results above give
rise to a map from
$\mathcal H\times\mathcal H$ into the space of
Riesz measures:
\[ 
(x,y)\mapsto \mu_{x,y}
\]
For each real-valued
and bounded Borel function $\phi(t)$ on the real line with compact support
there exists a bounded self-adjoint operator
$\phi$ such that
\[
\langle \Phi(x),y\rangle=
\int\, g(t)\cdot  d\mu_{x,y}(t)
\]
All these $\Phi$ operators commute with
$A$.
If $x\in\mathcal D(A)$ and $y$ is a vector in
$\mathcal H$ one has
\[
\langle A(x),y\rangle=\lim_{M\to \infty}\,\int_{-M}^M\,
t\cdot d\mu_{x,y}(t)
\]









\newpage


\centerline{\bf{¤ 10.  Symmetric operators}}

\bigskip


\noindent
A densely defined and closed operator
$T$ on a Hilbert space $\mathcal H$
is  symmetric if
\[
\langle Tx,y\rangle=
\langle x,Ty\rangle\quad\text{hold for all pairs }\quad x,y\in\mathcal D(T)\tag{*}
\]


\noindent
The symmetry means  that
the adjoint 
$T^*$   extends $T$, i.e. 
\[
\Gamma(T)\subset \Gamma(T^*)
\]
Recall that adjoints always are closed operators.
Hence $\Gamma(T^*)$
is a closed subspace of $\mathcal H\times\mathcal H$ and  becomes
a Hilbert space equipped with
the inner product
\[
\{x,y\}=
\langle x,y\rangle+
\langle T^*x,T^*y\rangle
\]
Moreover, since
$T$  is closed. it follows that
$\Gamma(T)$ appears as a closed subspace of this Hilbert space.
Consider 
the  eigenspaces:
\[
\mathcal D_+=\{ x\in\mathcal D(T^*)\quad\colon T^*(x)=ix\}
\quad\text{and}\quad 
\mathcal D_-=\{ x\in\mathcal D(T^*)\quad\colon T^*(x)=-ix\}
\]


\medskip

\noindent {\bf{10.1 Proposition.}}
\emph{The following  orthogonal decomposition exists in
the Hilbert space $\Gamma(T^*)$:}
\[
\Gamma(T^*)=\Gamma(T)\oplus \mathcal D_+ \oplus\mathcal D_-
\tag{*}\]


\noindent
\emph{Proof.}
The verification that the three subspaces are pairwise orthogonal is
left to the reader.
To show  that the direct sum above
is equal to
$\Gamma(T^*)$ we use duality and  there remains only  to
prove that
\[ 
\Gamma(T)^\perp=
\mathcal D_+\oplus \mathcal D_-\tag{1}
\]

\noindent
To show (1) we pick a vector 
$y\in \Gamma(T)^\perp$. Here $(y,T^*y)\in\Gamma(T^*)$
and the definition of orthogonal complements gives:
\[
\langle x,y\rangle+ \langle Tx,T^*y\rangle=0
\quad\colon\quad x\in\mathcal D(T)
\]
From this we see that $T^*y\in\mathcal D(T^*)$ and obtain
\[
\langle x,y\rangle+ \langle x,T^*T^*y\rangle=0
\]
The density of $\mathcal D(T)$ entails that
\[ 
0=y+T^*T^*y=(T^*+iE)(T^*-iE)(y)\implies
\]
\[
\xi=T^*y-iy\in \mathcal D_-\quad\text{and}\quad
\eta=T^*y+iy\in \mathcal D_+\implies
\]
\[ 
y=\frac{1}{2i}(\eta-\xi)
\in \mathcal D_-\oplus \mathcal D_+
\]
which proves (1).


\medskip

\noindent
{\bf{10.2 The case 
$\dim(\mathcal D_+)= \dim(\mathcal D_-)$.}}
Suppose that $\mathcal D_+$ and $\mathcal D_-$  are finite dimensional
with equal  dimension $n\geq 1$. Then
self-adjoint extensions of $T$  are found as follows:
Let   $e_1,\ldots,e_n$ be an orthonormal  basis in $\mathcal D_+$ and
$f_1,\ldots,f_n$ a similar basis in $\mathcal D_-$.
For each $n$-tuple $e^{i\theta_1},\ldots, e^{i\theta_n}$
of complex numbers with absolute value one
we have  the subspace of $\mathcal H$
generated by $\mathcal D(T)$ and
the vectors
\[ 
\xi_k= e_k+ e^{i\theta_k}\cdot f_k\quad\colon\quad 1\leq k\leq n
\]

\medskip

\noindent
On this  subspace we define a linear operator $A_\theta $ where
$A_\theta =T$ on $\mathcal D(T)$
while
\[ 
A_\theta (\xi_k)=ie_k-i e^{i\theta_k}\cdot f_k
\]

\medskip

\noindent
{\bf{10.3 Exercise.}}
Verify 
that
$A_\theta $ is self-adjoint and  prove the converse, i.e. if
$A$ is an arbitrary self-adjoint operator such that
\[
\Gamma(T)\subset
\Gamma(A)\subset\Gamma(T^*)
\]
then there exists a unique $n$-tuple $\{e^{i\theta_\nu}\}$
such that
\[
A=A_\theta
\]







\bigskip
\noindent{\bf{10.4  Example.}}
Let $\mathcal H$ be the Hilbert space
$L^2[0,1]$ of  square-integrable functions 
on the unit interval $[0,1]$ with  the coordinate $t$.
A dense subspace $\mathcal H_*$ consists of  functions
$f(t)\in C^1[0,1]$
such that $f(0)=f(1)=0$.  On $\mathcal H_*$
we define the operator 
$T$ by
\[ 
T(f)=if'(t)
\]
A partial integration gives
\[ 
\langle T (f),g\rangle=
 i\int_0^1\, f'(t)\cdot\bar g(t)\cdot dt=\int_0^1\, \bar g'(t)\cdot f(t)dt=
 \langle f,T(g)\rangle
\] 
Hence $T$ is symmetric.
Next, an $L^2$-function $h$  belongs to $\mathcal D(T^*)$ if and only if there exists a constant $C(h)$ such that
\[
\bigl|\int_0^1\, if'(t)\cdot\bar h(t)dt\bigr|\leq
C(h)\cdot ||f||_2\quad\colon f\in \mathcal H_*
\] 
This means that
$\mathcal D(T^*)$ consists of all $L^2$-functions $h$ such that
the distribution derivative $\frac{dh}{dt}$ again belongs to $L^2$.
\medskip

\noindent
{\bf{Exercise.}}
Show that 
\[ 
\mathfrak{D}_+=\{h\in L^2\quad\colon\frac{dh}{dt}=ih\}
\] 
is a 1-dimensional vector space
generated by the $L^2$-function $e^{ix}$.
Similarly, $\mathcal D_-$ is 1-dimensional and generated
by $e^{-ix}$.
\medskip

\noindent
\emph {Self-adjoint extensions of $T$}.
For each  complex number
$e^{i\theta}$  we get the linear  space  
$\mathcal D_\theta$
of functions
$f(t)\in\mathcal D(T^*)$ such that
\[ 
f(1)= e^{i\theta}f(0)
\]


\noindent
{\bf{Exercise.}}
Verify
that one gets a  self-adjoint operator $T_\theta$
which extends $T$ where 
is   $\mathcal D(T_\theta)= \mathcal D_\theta$.
Conversely, show every  self-adjoint extension of
$T$ is equal to $T_\theta$
for some
$\theta$. Hence the family $\{T_\theta\}$
give all self-adjoint extensions of $T$ with their  graphs 
contained in  $\Gamma(T^*)$.


\bigskip

 
\centerline {\bf{10.5 Semi-bounded symmetric operators.}}
\bigskip

\noindent 
Let $T$ be  closed, densely defined and symmetric.
It is said to be bounded
below 
if there exists some positive constant $k$ such that
\[ 
\langle Tx,x\rangle \geq k\cdot ||x||^2\quad\colon\quad x\in\mathcal D(T)\tag{*}
\]

\medskip

\noindent
On $\mathcal D(T)$ we have the Hermitian bilinear form:
\[
\{x,y\}= \langle Tx,y\rangle \quad\text{where (*) entails that}\quad 
\{x,x\}\geq k\cdot ||x||^2\tag{1}
\]
In particular a Cauchy sequence with respect to this inner product is a
Caichy sequence in the given Hilbert space
$\mathcal H$. So if $\mathcal D_*$ is the completion of
$\mathcal D(T)$ with respect to the inner product above, then
it appears as a subspace of
$\mathcal H$.
Put
\[ 
\mathcal D_0=\mathcal D(T^*)\,\cap\, \mathcal D_*
\]

\noindent
{\bf{10.5.1 Proposition}}. \emph{One has the equality}
\[ 
T^*(\mathcal D_0)=\mathcal H\tag{*}
\]
\emph{Proof.}
A  vector $x\in\mathcal H$  gives
a  linear functional on $\mathcal D_*$ 
defined by
\[ 
y\mapsto \langle y,x\rangle
\]
We have
\[
|\langle y,x\rangle|\leq
||x|\cdot ||y||\leq ||x|||\cdot \frac{1}{\sqrt{k}}\cdot\sqrt{\{y,y\}}\tag{i}
\]
where we used (1) above.
The Hilbert space
$\mathcal D_*$
is self-dual. This   gives a  vector
$z\in\mathcal D_*$ such that
\[
\langle y,x\rangle=\{y,z\}=\langle Ty,z\rangle\tag{iii}
\]
Since $\mathcal D(T)\subset \mathcal D_*$
we have (iii)
for every vector 
$y\in\mathcal D(T)$, and  the construction of $T^*$
entails that  
$z\in  \mathcal D(T^*)$ so that  (iii) gives
\[
\langle y,x\rangle=\langle y,T^*(z)\rangle\tag{iv}
\]
The density of $\mathcal D_*$ in $\mathcal H$
implies that 
$x=T^*(z)$ and since $x\in\mathcal H$ was arbitrary we get
(*) in the proposition.
\bigskip


\noindent
{\bf{10.5.2 A self-adjoint extension.}}
Let $T_1$ be the restriction of $T^*$ to
$\mathcal D_0$. We leqve it to the reader to check that
$T_1$ is symmetric and 
has a closed graph.
Moroever, since $\mathcal D(T)\subset \mathcal D_0$ and 
$T^*$ is an extension of 
$T$ we have
\[ 
\Gamma(T)\subset \Gamma(T_1)
\]
Next, Proposition 11.2.1 gives
\[
 T_1(\mathcal D(T_1)= \mathcal H
\]
 i.e. the $T_1$Êis surjective.
But then $T_1$ is self-adjoint by   the general result below.

\bigskip
 
\noindent{\bf{10.5.3 Theorem }}.
\emph{Let $S$
be a  densely defined, closed and symmetric operator such that}
\[
S(\mathcal D(S))=\mathcal H\tag{*}
\]
\emph{Then $S$ is self-adjoint.}
\medskip



\noindent
\emph{Proof.}
Let $S^*$ be the adjoint of $S$.
When 
$y\in\mathcal D(S^*)$ we have by definition
\[
\langle Sx,y\rangle =\langle x,S^*y\rangle\quad\colon\quad x\in\mathcal D(S)
\]
If $S^*y=0$ this entails that
$\langle Sx,y\rangle=0$ for all $x\in\mathcal D(S)$ so 
the assumption that
$S(\mathcal D(S))=\mathcal H$ 
gives $y=0$ and hence  $S^*$ is injective.
Finally, if $x\in\mathcal D(S^*)$
the hypothesis (*) gives $\xi\in\mathcal D(S)$ such that
\[
S(\xi) =S^*(x)\tag{i}
\] 
Since $S$ is symmetric,
$S^*$ extends $S$ so that 
(i) gives  $S^*(x-\xi)=0$. Since we already proved that
$S^*$ is injective  we have
$x=\xi$. This proves that 
$\mathcal D(S)=\mathcal D(S^*)$ which means that   $S$ is self-adjoint.







\newpage














\centerline{\bf{¤ 11. Contractions and the Nagy-Szegš theorem}}
\bigskip


\noindent
A linear operator $A$ on the Hilbert space $\mathcal H$ is  a contraction if
its operator norm is $\leq 1$, i.e.
\[
 ||Ax||\leq ||x||\quad\colon\quad x\in\mathcal H\tag{1}
\] 
Let $E$ be the identity operator on $\mathcal H$.
Now $E-A^*A$ is a bounded self-adjoint operator and  (1) gives:
\[
\langle x-A^*Ax,x\rangle=||x||^2-||Ax||^2\geq 0
\]
From the result in ¤ 8.xx it follows that
this  non-negative self-adjoint operator has a square root:
\[ 
B_1=\sqrt{E-A^*A}
\]
Next,  the operator norms of $A$ and  $A^*$ are equal so
$A^*$ is  also a  contraction and the equation
$A^{**}=A$ gives the
self-adjoint operator
\[
B_2=\sqrt{E-AA^*}
\]
Since  $AA^*=A^*A$ is not assumed
the  self-adjoint operators
$B_1,B_2$ need not be equal.
However, the following hold:

\medskip

\noindent
{\bf{11.3.1 Propostion.}}
\emph{One has the equations}
\[ 
AB_1=B_2A\quad\text{and}\quad A^*B_2= B_1A^*
\]



\noindent
\emph{Proof.}
If $n$ is a positive integer we notice that
\[
A(A^*A)^n=(AA^*)^nA\tag{i}
\]
Now $A^*A$ is a self-adjoint operator whose compact spectrum is confined to
the closed unit interval $[0,1]$.
If $f\in C^0[0,1]$
is a real-valued continuous function it can be approximated uniformly
by a sequence of polynomials $\{p_n\}$
and the operational calculus from ¤ XX yields an operator
$f(A^*A)$ where
\[
\lim_{n\to\infty}\, ||p_n(A^*A)-f(A^*A)||=0
\]
Since the spectrum of $AA^*$ also is confined to $[0,1]$,
the same polynomial sequence
$\{p_n\}$ gives 
an operator $f(AA^*)$ where
\[
\lim\, ||p_n(AA^*)-f(AA^*)||=0
\]
Now (i) and the two limit formulas above give:
\[
A\circ f(A^*A)= f(AA^*)\circ A\tag{ii}
\]
In particular we can take 
$f(t)= \sqrt{1-t}$
and  Proposition 11.3.1 follows.
\bigskip

\noindent{\bf{11.2 The unitary operator $U_A$}}.
On the Hilbert space $\mathcal H\times \mathcal H$
we define a linear operator $U_A$ represented by the block matrix
\[
U_A=
\begin{pmatrix} A& B_2\\
B_1&-A^*
\end{pmatrix}\tag{*}
\]


\noindent
{\bf{11.3 Proposition.}}
\emph{$U_A$ is a unitary operator on
 $\mathcal H\times \mathcal H$}.
 
 \medskip
 
 \noindent
 \emph{Proof.}
 For a pair of vectors $x,y$ in $\mathcal H$
 we must prove the equality
\[
|| U_A(x\oplus y)||^2=||x||^2+||y||^2\tag{i}
\]
To get (i)  we notice that for every vector $h\in\mathcal H$ 
the self-adjointness of $B_1$ gives
\[
||B_1h||^2=\langle B_1h,B_1h\rangle=
\langle B_1^2h,h\rangle=\langle h-A^*Ah,h\rangle=
||h||^2-||Ah||^2\tag{ii}
\]
where  the last equality holds since we have
$\langle A^*Ah,h\rangle =\langle Ah,A^{**}h\rangle =||Ah||^2$
and the biduality formula $A=A^{**}$.
In the same way one has:
\[
||B_2h||^2=||h||^2-||A^*h||^2\tag{iii}
\]


\noindent
Next, by the construction of $U_A$ the left hand side in (i) becomes
\[
||Ax+B_2y||^2+||B_1x-A^*y||^2\tag{iv}
\]
Using (iii) we have
\[
||Ax+B_2y||^2=||Ax||^2+||y||^2-||A^*y||^2+
\langle Ax,B_2y\rangle+ \langle B_2 y,Ax\rangle
\]
Similarly,  (ii) gives
\[
||B_1x-A^*y||^2=||x||^2-||Ax||^2+||A^*y||^2-
\langle B_1x,A^*y\rangle- \langle A^*y,B_ x\rangle
\]
Adding these two equations  we 
conclude that (i) follows from the equality
\[
\langle Ax,B_2y\rangle+ 
\langle B_2 y,Ax\rangle=
\langle B_1x,A^*y\rangle+ \langle A^*y,B_ x\rangle\tag{v}
\]
To get (v) we use Proposition 11.5.1 which  gives
\[
\langle Ax,B_2y\rangle=
\langle x,A^*B_2y\rangle=
\langle x,B_1A^*y\rangle=
\langle B_1x,A^*y\rangle
\]
where the last equality used that $B_1$ is self-adjoint. In the same way one verifies that
\[
\langle B_2 y,Ax\rangle=
 \langle A^*y,B_ x\rangle
\]
and (v) follows.

\bigskip



\centerline{\bf{11.4 The Nagy-Szegš theorem.}}
\bigskip


\noindent
The constructions above were applied 
by 
Nagy and Szegš to give:
\medskip

\noindent
{\bf{11.4.1 Theorem}}
\emph{For every bounded linear operator $A$ on a Hilbert space
$\mathcal H$ there exists a Hilbert space
$\mathcal H^*$ which contains $\mathcal H$ and a unitary operator $U_A$
on $\mathcal H^*$ such that}
\[
A^n=\mathcal P\cdot U_A^n\quad\colon\quad n=1,2,\ldots
\]
\emph{where $\mathcal P\colon\mathcal H^* \to \mathcal H$
is the orthogonal  projection.}
\medskip


\noindent
\emph{Proof.}
On the product  $\mathcal H_1=\mathcal H\times\mathcal H$ we have the unitary
operator $U_A$ from (*) in 11.3.2. Let
$\mathcal P(x,y)= x$ be the projection onto the first
factor.
Then  (*) in (11.3.2) gives 
$A=\mathcal PU_A$ and  
the constructions from the proof of Propostion 11.3.4
imply that
$A^n=\mathcal P\cdot U^n$ hold for every $n\geq 1$ which finishes the proof.
\bigskip

\noindent
The Nagy-Szegš result has
an interesting consequence. 
Let $A$  be a contraction. If
$p(z)=
c_0+c_1<+\ldots+c_nz^n$ is an arbitrary polynomial with
complex coefficients
we get the 
operator $p(A)=\sum\,c_\nu A^\nu$ and 
with these notations one has:

\medskip

\noindent
{\bf{11.4.2 Theorem}}
\emph{For every pair $A,p(z)$ as above one has}
\[
||p(A)||\leq \max_{z\in D}\, |p(z)|
\] 
\emph{where the the maximum in the right hand side is taken on the unit disc.}
\medskip

\noindent
\emph{Proof.} Theorem 11.4.1  gives $p(A)= \mathcal P\cdot p(U_A)$.
Since the orthogonal $\mathcal P$-projection is norm decreasing we get
\[
||p(A)(\xi)||^2\leq ||p(U_A)(\xi,0)||^2
\]
Let $\xi$ be a unit vector such that
$||p(A)(\xi)||= ||p(A)||$.
The operational calculus in ¤ 7 XX  applied to the unitary operator
$U_A$  yields a
probablity measure $\mu_\xi$ on
the unit circle such that
\[
 ||p(U_A)(\xi,0)||^2=
 \int_0^{2\pi}\, |p(e^{i\theta})|^2\cdot d\mu_\xi(\theta)
 \]
The right hand side is majorized by $|p|_D^2$ and Theorem 11.4.2 follows.

\bigskip

\noindent
{\bf{11.4.3 An application.}}
Let $A(D)$ be the disc algebra. Since each $f\in A(D)$ can be 
uniformly approximated by analytic 
polynomials, Theorem 11.4.2  entails that if a linear operator $A$ 
on the Hilbert space $\mathcal H$ is a contraction
then each $f\in A(D)$
gives a 
bounded linear operator $f(A)$, i.e. we have norm-preserving map  from
the supnorm algebra $A(D)$ into the space of bounded linear operators on
$\mathcal H$.


\newpage

\centerline
{\bf{¤ 12 Miscellanous results}}
\bigskip


\noindent
Before Theorem 12.x is announced
we recall that the product formula for matrices in ¤ X  asserts the following.
Let $N\geq 2$  and $T$  is some $N\times N$-matrix whose
elements are complex numbers
which as usual is regarded as a linear operator on
the Hermitian space ${\bf{C}}^N$.
Then there 
exists the 
self-adjoint matrix $\sqrt{T^*T}$ whose eigenvalues are non-negative.
Notice that for every vector $x$ one has 
\[
||T^*T(x)||^||Tx||^2\implies ||\sqrt{T^*T}(x)||= ||Tx||\tag{i}
\] 


\noindent
and since
$\sqrt{T^*T}$ is self-adjoint
we have an orthogonal decomposition 
\[
\sqrt{T^*T}({\bf{C}}^N)\oplus
\text{Ker}(\sqrt{T^*T})= {\bf{C}}^N\tag{ii}
\]
where the self-adjointness gives the equality
\[
\text{Ker}(\sqrt{T^*T})=\sqrt{T^*T}({\bf{C}}^N)^\perp\tag{iii}
\]
\medskip

\noindent
{\bf{The partial isometry operator.}}
Show that 
there exists a unique linear operator $P$ such that
\[ 
T= P\cdot \sqrt{T^*T}\tag{*}
\]
where the $P$-kernel is
the orthogonal complement of the range of  $\sqrt{T^*T}$.
Moreover, from  (i) it follows that
\[
||P(y)||=||y||
\] 
for each vector in the range of
$\sqrt{T^*T}$.
One  refers to $P$ as a partial isometry attached to $T$.
\bigskip

\noindent
{\bf{Extension to operators on
Hilbert spaces.}}.
Let $T$ be a bounded opertor on
the Hilbert space
$\mathcal H$.
The spectral theorem for bounded
and self-adjoint operators
gives a similar equation as in (*) above
using
the non-negative and self-adjoint
operator $\sqrt{T^*T}$. More generally,
let $T$ be densely defined and closed.
From  ¤ XX  there exists the
densely defined self-adjoint operator $T^*T$
and we can also take its square root.

\medskip

\noindent
{\bf{12.1 Theorem.}}
\emph{There exists  a bounded partial isometry
$P$ such that}
\[ 
T= P\cdot \sqrt{T^*T}
\]



\medskip


\noindent
\emph{Proof.}
Since $T$ has closed graph we have the Hilbert space
$\Gamma(T)$.
For each $x\in\mathcal D(T)$ we get the vector
$x_*=(x,Tx)$ in $\Gamma(T)$.
Now
\[
(x_*.y_*)\mapsto \langle x,y\rangle
\] 
is a bounded Hermitiain bi-linear form on
the Hilbert space $\Gamma(T)$.
The self-duality of Hilbert spaces
gives  bounded and self-adjoint operator
$A$ on
$\Gamma(T)$ such that
\[
\langle x,y\rangle=\{ Ax_*,y_*\}
\]
where the right hand side is the inner product between vectors in
$\Gamma(T)$.
Let 
\[ 
j\colon (x,Tx)\mapsto x
\]
be  the projection from
$\Gamma(T)$ onto $\mathcal D(T)$ and for each
$x\in\mathcal D(T)$ we put
\[ 
Bx= j(Ax_*)
\]
Then $B$ is a linear operator from
$\mathcal D(T)$ into itself where
\[
\langle Bx,y\rangle =\{Ax_*,y_*\}= \{ x_*,Ay_*\}
=\langle x,By\rangle
\quad\colon\quad x,y\in
\mathcal D(T)
\tag{i}
\]
We have also
\[
\langle Bx,x\rangle=\{A^2x_*,x_*\}=\{Ax_*,Ax_*\}=
\langle Bx,Bx\rangle+\langle TBx,TBx\rangle\implies
\]
\[
||Bx||^2= \langle Bx,Bx\rangle\leq \langle Bx,x\rangle
\leq||Bx||\cdot ||x||
\] 

\noindent
where the Cauchy-Schwarz inequality was used in the last step.
Hence
\[
||Bx||\leq ||x||\quad\colon\quad x\in
\mathcal D(T)
\] 
This entails that that the densey defined operator $B$ 
extends uniquely to
$\mathcal H$ as  a bounded operator
of norm $\leq 1$.
 Moreover, since
(i) hold for pairs $x,y$ in the dense subspace
$\mathcal D(T)$, it follows that
$B$  is self-adjoint.
Next, consider a pair $x,y$ in $\mathcal D(T)$ which gives
\[ 
\langle x,y\rangle= \{Ax_*,y_*\}=
\{x_*,Ay_*\}=\langle x, By\rangle+\langle Tx,TBy\rangle
\]
Keeping $y$ fixed the linear functiional
\[ 
x\mapsto \langle Tx,TBy\rangle=\langle x,y\rangle-\langle x, By\rangle
\]
is bounded on $\mathcal D(T)$. By the construction of
$T^*$  it follows that
$TBy\in \mathcal D(T^*)$
and we also get the equality
\[
\langle x,y\rangle=
\langle x, By\rangle+\langle x,T^*TBy\rangle\tag{ii}
\]
\medskip


\noindent
Since (ii)  holds for all $x$ in the dense subspace $\mathcal D(T)$ we conclude that
\[
y=By+T^*TBy= (E+T^*T)(By)\quad\colon\quad y\in \mathcal D(T)\tag{iii}
\]
\medskip

\noindent
{\bf{Conclusion.}}
From the above we have 
the inclusion
\[ 
TB(\mathcal D(T))\subset
\mathcal D(T^*)
\]
Hence   $\mathcal D(T^*T)$
 contains
$B(\mathcal D(T))$ and (iii) 
means that
$B$ is a right inverse of $E+T^*T$
provided that the $y$-vectors are restricted to
$\mathcal D(T)$.
\bigskip


FINISH ..



\bigskip





\centerline{\bf{12.2 Positive operators on $C^0(S)$}}

\bigskip

\noindent
Let $S$ be a compact Hausdorff
space and $X$  the Banach space of continuous and
complex-valued functions on $S$.
A linear operator $T$ on $X$ is  positive if
it sends every non-negative and real-valued function $f$ to another  real-valued and
non-negative function.
Denote by $\mathcal F^+$ the family of positive operators
$T$ which satisfy the following: First
\[
\lim_{n\to\infty}\, \frac{1}{n}\cdot x^*(T^nx)=0\tag{1}
\] 
hold for all pairs $x\in X$ and $x^*\in X^*$.
The second condition is that
$\sigma(T)$ is the union of a compact set in a disc
$\{|\lambda|\leq r$ for some $r<1 $, and a 
finite set of points on the unit circle. 
The  final  condition is that
$R_T(\lambda)$
is meromorphic in the exterior disc
$\{|\lambda>r\}$, i.e. it has poles at
the spectral points on the unit circle.








\medskip

\noindent
{\bf{12.2.1. Theorem.}}
\emph{If $T\in\mathcal F^+$ 
then
each spectral value $e^{i\theta}\in \sigma(T)$ is a root of unity.}

\medskip


\noindent
\emph{Proof.}
Frist we prove that $R_T(\lambda)$  has a simple pole at
each  $e^{i\theta}\in \sigma(T)$.
Replacing 
$T$ by  $e^{-i\theta}\cdot T$
it suffices to prove this when
$e^{i\theta}=1$.
If $R_T(\lambda)$ has a pole of order $\geq 2$
at $\lambda=1 $ we know from ¤ XX that there exists $x\in X$ such that
\[ 
Tx\neq  x\quad\text{and}\quad
(E-T)^2\,x=0\tag{i}
\]
This gives  $T^2+x=2Tx$ and by an induction
\[
\frac{1}{n} \cdot T^n x=\frac{1}{n}\cdot x+(E-T)x\quad\colon n=1,2,\ldots\tag{ii}
\]
Condition (1) and (ii) give for each $x^*\in X^*$:
\[ 
0=\lim_{n\to\infty}\, \frac{1}{n}\cdot x^*( T^n x)=\lim_{n\to\infty}\,
x^*(\frac{1}{n}\cdot x+(E-T)x)
\] 
It follows that $x^*(E-T)(x)=0$ and since 
$x^*$ is arbitrary we get   $Tx=x$ which contradicts (i).
Hence
the pole must be simple.
\medskip


\noindent
Next, with $e^{i\theta}\in\sigma(T) $
we have seen that
$R_T$  has a simple pole.
By the general result in ¤ xx there exists
some    $f\in C^0(S)$ which is not identically zero and
\[ 
T(f)=e^{i\theta}\cdot f
\]
Multiplying $f$ with a complex scalar we may assume that
its  maximum norm on $S$ is one and there exists a point $s_0\in S$ such that
\[ 
f(s_0)=1
\]
For each $n\geq 1$ we have a linear functional on
$X$ defined by $g\mapsto T^n(g)(s_0)$ whuch gives a
Riesz measure $\mu_n$ such that
\[
\int_S\, g\cdot d\mu_n=T^n g(s_0)\quad\colon g\in C^0(S)
\]
Since $T^n$ is positive
the integrals in the left hand side are
$\geq 0$ when $g$ are real-valued and non-negative which entails that
the measures $\{\mu_n\}$ are real-valued and non-negative.
For each $n\geq 1 $ we put
\[ 
A_n=\{x\,\colon\, e^{-in\theta}\cdot f(x)\neq 1\}
\]
Since the sup-norm of $f$ is one we notice that
\[ 
A_n=
\{x\,\colon\, \mathfrak{Re}(e^{-in\theta}f(x))<1\}\tag{iii}
\]
Now
\[
0=f(s_0)- e^{-in\theta}\cdot T^n f(s_0)
=\int_S\,[1-e^{-in\theta}f(s)]\cdot  d\mu_n(s)\tag{iv}
\]
Taking real parts we get
\[
0=\int_S\,[1-\mathfrak{Re}(e^{-in\theta}f(s))]\cdot  d\mu_n(s)\tag{v}
\]
By (iii)  the integrand in (v)
is non-negative and since the whole 
integral is zero it follows that
\[
\mu_n(A_n)= \mu_n(\{\mathfrak{Re}(e^{-in\theta}<1\}=0\tag{vi}
\]
Suppose now that
there exists a pair $n\neq m$ such that
\[
(S\setminus A_n)\cap (S_m\setminus A_m)\neq \emptyset\tag{vii}
\] 
A point $s_*$ in this non-empty intersection
gives
\[
1=e^{in\theta}f(s_*)=e^{im\theta}\cdot f(s_*)\implies
e^{in\theta}=e^{im\theta}
\] 
and hence  $e^{i\theta}$ is a root of unity.
$m-n\neq 0$.
So the proof of Theorem 6.1  is finished if we have established the following

\medskip

\noindent
\emph{Sublemma.}
\emph{The sets $\{S\setminus A_n\}$ cannot be pairwise disjoint.}
\medskip

\noindent
\emph{Proof.}
First,  $f$ has maximum norm
and by the above:
\[ 
\int_S\, f\cdot d\mu_n=e^{in\theta}
\]
Hence the total mass $\mu_n(S)$ is at least one.
Next, 
for each $n\geq 2$ we set
\[
\pi_n=\frac{1}{n}\cdot (\mu_1+\ldots+\mu_n)
\]
Since 
$\mu_n(S)\geq 1$  for each $n$ we get 
$\pi_n(S)\geq 1$. Put
\[
\mathcal A=\bigcap\, A_n
\]
Above we proved that $\mu_n(A_n)=0$ hold for every $n$ which gives
\[ 
\pi_n(\mathcal A)=0\quad\colon\, n=1,2,\ldots\tag{*}
\]
Next, when
the sets $\{S\setminus A_k\}$ 
are pairwise disjoint one has 
the inclusions
\[
S\setminus A_k\subset A_\nu\quad\forall\,\nu\neq k
\]
Keeping $k$ fixed it follows that
$\pi_\nu(S\setminus A_k)=0$ for every $\nu\geq 0$.
So when $n$ is large while $k$ is kept fixed we obtain
\[ 
\pi_n(S\setminus A_k))= \frac{1}{n}\cdot \mu_k(S\setminus A_k))\implies
\lim_{n\to\infty}\, \pi_n(S\setminus A_k))=0
\quad\colon k=1,2,\ldots\tag{**}
\]
At this stage we use Lemma xx which shows that 
$R_T(\lambda)$ has at most a simple pole at $\lambda=1$.
With $\epsilon>0$
the Neumann series expansion gives
\[
E+\sum_{k=1}^\infty\,
\frac {T^k}{(1+\epsilon)^k}=
R_T(1+\epsilon))
=\frac{1}{\epsilon} \cdot Q+W(1+\epsilon))
\]
where $W(\lambda)$ is an operator-valued analytic function
in an open disc centered at $\lambda=1$ while $Q$ is a bounded
linear operator on $C^0(S)$.
Keeping $\epsilon>0$ fixed we apply both sides to the identity function
$1_S$ on $S$ and the construction of
the measures $\{\mu_n\}$ gives
\[
1+
\sum_{k=1}^\infty\,
\frac {\mu_k(S)}{(1+\epsilon)^k}=\frac{1}{\epsilon} \cdot Q(1_S)(s_0)+
W(1+\epsilon))(1_S)(s_0)
\]
If $n\geq 2$ is an integer and $\epsilon=\frac{1}{n}$
one gets the inequality
\[
\sum_{k=1}^{k=n}\,
\frac {\mu_k(S)}{(1+\frac{1}{n})^k}\leq
n\cdot |Q(1_S)(s_0)|+|W(1+1/n))(1_S)(s_0)|\leq
n\dot ||Q||+ ||W(1+1/n)||\implies
\]
\[
\frac{1}{n}\cdot\sum_{k=1}^{k=n}\,\mu_k(S)\leq
(1+\frac{1}{n})^n\cdot (||Q||+\frac{ ||W(1+1/n)||}{n}
\]
Since
Neper's constant $e\geq (1+\frac{1}{n})^n$ for every $n$
we find
a constant $C$ which is
independent of $n$ such that
\[
\frac{1}{n}\cdot\sum_{k=1}^{k=n}\,\mu_k(S)\leq C
\]
Hence the sequence $\{\pi_n(S)\}$ is  bounded
and we can pass to a subsequence
which converges weakly to a limit measure $\mu_*$.
For this $\sigma$-additive measure the limit formula in (**) above entails that
\[ 
\mu_*(S\setminus A_k)=0\quad\colon\, k=1,2,\ldots\tag{i}
\]
Moreover, by (*) we also have
\[
\pi_*(\mathcal A)=0\tag{ii}
\]
Now
$S= \mathcal A\cup\, A_k$ so (i-ii) give:
\[ 
\mu_*(S)=0
\]
But this is impossible for at the same time
we have already seen that
$\pi_n(S)\geq 1$ for each $n$ and hence also $\mu_*(S)\geq 1$.









\bigskip
Compact pertubations to finish Kakutani-Yosida !!!



\bigskip



\noindent 
In general, consider some complex Banch space
$X$ be a Banach space and
denote by $\mathcal F(X)$
the family of bounded liner operators  $T$ on $X$  
such that

\[ 
\lim_{n\to\infty}\, \frac{1}{n}\cdot x^*(T^nx)=0\tag{*}
\] 
hold for all pairs $x\in X$ and $x^*\in X^*$.
\medskip


\noindent
{\bf{1. Exercise.}} Apply the Banach-Steinhaus theorem to show that
if $T\in\mathcal F(X)$ then
there exists a constant $M$ such that the operator norms satisfy
\[ 
||T^n||\leq M\cdot n\quad\colon\, n=1,2,\ldots
\]


\noindent
Since the $n$:th root of $M\cdot n$ tends to one as $n\to+\infty$, 
the spectral radius formula entails that
the spectrum $\sigma(T)$ is contained in the closed unit disc
of the complex $\lambda$-plane.
So in the exterior disc
$\{|\lambda|>1\}$ there exists the
the resolvent 
\[ 
R_T(\lambda)= (\lambda\cdot E-T)^{-1}
\]



\noindent{\bf{2. The class $\mathcal F_*$}}.
It consists of those $T$ in $\mathcal F(X)$
for which there exists
some $\alpha<1$ such that
$R_T(\lambda)$ extends to a meromorphic function in
the exterior disc
$\{|\lambda|>\alpha\}$.
Since $\sigma(T)\subset
\{|\lambda|\leq 1\}$
it follows that when
$T\in\mathcal F_*$ then
the set of points in $\sigma(T)$ which belongs to the unit circle
in the complex $\lambda$-plane is empty or finite and
after we can always choose $\alpha<1$ such that
\[ 
\sigma(T)\cap \{\alpha<|\lambda|<1\}= \emptyset
\]

\medskip

\noindent
{\bf{3. Proposition.}}
\emph{If $T\in \mathcal F_*$ andÊ$e^{i\theta}\in \sigma(T)$
for some $\theta$, then Neumann's resolvent
$R_T(\lambda)$ 
has a simple pole at $e^{i\theta}$.}
 \medskip

\noindent
\emph{Proof.}
Replacing
$T$ by  $e^{-i\theta}\cdot T$
it suffices to prove the result when
$e^{i\theta}=1$.
If $R_T(\lambda)$ has a pole of order $\geq 2$
at $\lambda=1 $ we know from ¤ XX that there exists $x\in X$ such that
\[ 
Tx\neq  x\quad\text{and}\quad
(E-T)^2\,x=0\tag{i}
\]
The last equation means that $T^2+x=2Tx$ and an induction
over $n$ gives
\[
\frac{1}{n} \cdot T^n x=\frac{1}{n}\cdot x+(E-T)x\tag{ii}
\]
Since $T\in\mathcal F$ we have
\[ 
\lim_{n\to\infty}\, \frac{1}{n}\cdot x^*( T^n x)=0
\quad\colon\, \forall\\, x^*\in X^*\tag{iii}
\] 
Then (ii) entails that $x^*(E-T)(x)=0$. Since
$x^*$ is arbitrary we get  $Tx=x$ which contradicts (i) and hence
the pole is simple.
\medskip

\noindent
{\bf{4. Theorem.}}
\emph{Let $T\in \mathcal F(X)$ be such that   there exists a compact
operator $K$ where 
$||T+K||<1$. Then $T\in \mathcal F_*$ and
for every $e^{i\theta}\in\sigma(T)$
the eigenspace
$E_T(\theta)= \{ x\in X\,\colon\, Tx= e^{i\theta} x\}$ is finite dimensional.}

\medskip

\noindent
\emph{Proof.}
Set $S=T+K$ and for a complex number
$\lambda$ we write 
$\lambda\cdot E-T= \lambda\cdot E-T-K+K$. Outside $\sigma(S)$ we get
\[
R_S(\lambda)(\lambda\cdot E-T)=
E+R_S(\lambda)\cdot K\tag{i}
\]
The Neumann series for large absolute values
$|\lambda|$
applied to $R_S(\lambda)$ gives some $\rho>0$ and
\[
( E+R_S(\lambda)\cdot K)^{-1}= E+R_S(\lambda)\cdot K\dot
( E+R_S(\lambda)\cdot K)^{-1}\quad\colon\,|\lambda|>\rho\tag{ii}
\]

\noindent
Next, when
$|\lambda|$ is large
we notice that
(i) gives
\[
R_T(\lambda)=  ( E+R_S(\lambda)\cdot K)^{-1}\cdot R_S(\lambda)\tag{iii}
\]
Together with (ii) we obtain
\[
R_T(\lambda)=R_S(\lambda)+ 
R_S(\lambda)\cdot 
( E+R_S(\lambda)\cdot K)^{-1}\cdot R_S(\lambda)\tag{iv}
\]
Set $\alpha=||S||$ which by assumption is $<1$.
Now
$R_S(\lambda)$ is analytic in the exterior disc
$\{\lambda|>\alpha\}$ so in this exterior disc
$R_\lambda(T)$ differs from  the analytic function $R_\lambda(S)$ by
\[
\lambda\mapsto R_S(\lambda)\cdot 
( E+R_S(\lambda)\cdot K)^{-1}\cdot R_S(\lambda)\tag{v}
\]
Here $K$ is a compact operator so 
the
result in ¤ XX entails that this function extends to
be meromorphic  in $\{|\lambda|>\alpha\}$.
There remains to prove that
eigenspaces at spectral points on the unit circle are finite dimensional.
To prove this we use (iv). 
Let $e^{i\theta}\in\sigma(T)$. By Proposition 3 it is a simple pole
so we have a Laurent series expansion
\[
R_T(e^{i\theta}+z)= \frac{A_{-1}}{z}+ A_0+ A_1z+\ldots
\]
By the general results from ¤¤ there remains to show that 
$A_{-1}$ has finite dimensional range.
To see this we apply (iv) which gives the equation
\[
R_S(e^{i\theta}+z)+
R_S(e^{i\theta}+z)\cdot(E+
R_S(e^{i\theta}+z)\cdot K)^{-1}\cdot R_S(e^{i\theta}+z)
\]
To simplify notations we set $B(z)=R_S(e^{i\theta}+z)$
which by assumption is analytic in a neighborhood of $z=0$.
Moreover, the operator $B(0)$ is invertible.
So now one has
\[
 \frac{A_{-1}}{z}+ A_0+ A_1z+\ldots=
 B(z)+B(z)(E+B(z)\cdot K)^{-1}B(z)
 \]
Since $B(0)$ is invertible  we  have a Laurent series expansion
\[
(E+B(z)\cdot K)^{-1}= \frac{A^*_{-1}}{z}+A_0^*+A_1^*z+\ldots
\]
and identying the coefficient of $z^{-1}$ gives
\[
A_{-1}= B(0)A^*_{-1}B(0)
\]
Next, from (xx) one has

\[
E=(E+B(z)\cdot K)(\frac{A^*_{-1}}{z}+A_0^*+A_1^*z+\ldots)\implies
(E +B(0)\cdot K)A^*_{-1}=0
\]
Here $B(0)\cdot K$ is a compact operator and hence  Fredholm theory 
implies that $A^*_{-1}$ has a finite dimensional range. Since
$B(0)$ is invertible the same is true for $A_{-1}$ which finishes the proof
of 
Theorem 4.




\medskip

\noindent
{\bf{5. Proposition}}.
\emph{
If
$T\in\mathcal F$ is  such that
$T^N\in\mathcal F_*$ for some integer $N\geq 2$.
Then 
$T\in\mathcal F_*$.}
\medskip

\noindent
\emph{Proof.}
We have the algebraic equation
\[ 
\lambda^N\cdot E -T^N=(\lambda\cdot E-T)(
\lambda^{N-1}\cdot E+
\lambda^{N-2}\cdot T+\ldots+T^{N_1})
\]
It follows that
\[ R_T(\lambda)=
(\lambda^{N-1}\cdot E+
\lambda^{N-2}\cdot T+\ldots+T^{N_1})\cdot R_{T^N}(\lambda^N)
\]
Since $T^NB\in\mathcal F_*$ there exists
$\alpha<1$ such that
\[
\lambda\mapsto  R_{T^N}(\lambda^N)
\]
extends to be meromorphic in
$\{|\lambda|>\alpha\}$. At the same time
$(\lambda^{N-1}\cdot E+
\lambda^{N-2}\cdot T+\ldots+T^{N_1})$
is  a polynomial
and hence
$R_T(\lambda)$ also extends to be meromorphic
in this
exterior disc so that 
$T\in\mathcal F_*$.




\newpage




\centerline{\bf{12.3 Factorizations of non-symmetric kernels.}}


\bigskip

\noindent
Recall that
the Neumann-PoincarŽ kernel $K(p,q)$ of  a
plane $C^1$-curve $\mathcal C$
is given by
\[ 
K(p,q)= \frac{\langle p-q,{\bf{n}}_i(p)\rangle}{|p-q|}
\]
This kernel function gives the integral operator $\mathcal K$
defined on $C^0(\mathcal C)$ by
\[
\mathcal K_g(p)=\int_C\, K(p,q)\cdot g(q)\, ds(q)
\]
where $ds$ is the arc-length measure on $C$.
Let $M$ be a positive number which exceeds the diameter of 
$\mathcal C$
so that
$|p-q|<M\,\colon\, p,q\in\mathcal C$.
Set
\[
N(p,q)= \int_\mathcal C\, 
K(p,\xi )\cdot \log\,\frac{M}{|q-\xi|}\cdot ds(\xi)
\]



\noindent
{\bf{Exercise.}} Verify that
$N$ is symmetric, i.e. $N(p,q)= N(q,p)$
hold for all pairs $p,q$ in $\mathcal C$.
Moreover, 
\[ 
S(p,q)=\log\, \frac{M}{|p-q|}
\] 
is a symmetric and positive kernel function
and since $\mathcal C$ is of class $C^1$ the reader should verify that it gives a
Hilbert-Schmidt kernel, i.e.
\[ 
\iint_{\mathcal C\times\mathcal C}\,
S(p,q)^2\, ds(p)ds(q)<\infty
\]



\noindent
Hence the
Neuman-PoincarŽ operator  $\mathcal K$ appears in an
equation
\[ 
\mathcal N= \mathcal K\circ \mathcal S\tag{*}
\] 
where $\mathcal S$ is defined via a positive  symmetric Hilbert-Schmidt kernel and
$\mathcal N$ is symmetric.
Following  
[Carleman: ¤ 11 ] we give a procedure to determine 
the spectrum of $\mathcal K$.


\medskip

\centerline{\bf{12.3.1 Spectral properties of  non-symmetric kernels.}}
\bigskip


\noindent
In general,let  $K(x,y)$ be a continuous real-valued function on the closed unit square
$\square=\{0\leq x,y\leq 1\}$. We do not assume that  
$K$ is symmetric but 
there exists a positive definite
Hilbert-Schmidt kernel $S(x,y)$ such that
\[ 
N(x,y)=\int_0^1\, S(x,t) K(t,y)\, dy
\] 
yields a symmetric kernel function.
The Hilbert-Schmidt theory
gives
an orthonormal basis $\{\phi_n\}$ in
$L^2[0,1]$ formed by eigenfunctions to $\mathcal S$ where
\[ 
\mathcal S\phi_n=\kappa_n \phi_n\tag{1}
\] 
where the positive $\kappa$-numbers  tend to zero.
Moreover, each $u\in L^2[0,1]$
has a Fourier-Hilbert  expansion
\[ 
 u= \sum\,\alpha_n\cdot \phi_n\tag{2}
\]
We  seek 
eigenfunctions of  the integral operator $\mathcal K$.
Let  $u$ be  a function in $L^2[0,1]$
such that:
\[ 
u=\lambda\cdot \mathcal Ku\tag{3}
\]
where
$\lambda$ in general is a complex number. It follows that
\[
\lambda\cdot \int\, N(x,y)u(y)\, dy
=
\lambda\iint SA(x,t)K(t,y)u(y)\, dtdy=
\int S(x,t)u(t)\,dt\tag{4}
\]
Multiplying  with $\phi_p(x)$ an integration gives
\[
\lambda\cdot \int\, \phi_p(x)N(x,y)u(y)\, dx dy=
\iint \phi_p(x) S(x,t)u(t)\,dxdt=
\kappa_p\int \phi_p(t)u(t) \, dt\tag{5}
\]
Next, using  the expansion of $u$ from (2) we get
the equations:
\[
\sum_{q=1}^\infty \alpha_q\cdot 
\iint  \phi_q(x)\phi_p(x)N(x,y)\, dx dy=\kappa_p\alpha_p
\quad\colon\, p=1,2,\ldots\tag{6}
\]
Set
\[
c_{qp}=\iint  \phi_q(x)\phi_p(x)N(x,y)\, dx dy
\]
It follows that $\{\alpha_p\}$ satisfies the system
\[
\kappa_p\alpha_p=
\lambda\cdot \sum_{q=1}^\infty \, c_{qp}\alpha_q\tag{7}
\]
Since $N(x,y)= N(y,x)$ the
doubly indexed $c$-sequence is symmetric. Set
\[ 
\beta_p= \sqrt{\kappa_p}\cdot \alpha_p
\implies
\beta_p=\lambda\cdot \sum_{q=1}^\infty
\frac{c_{pq}}{\sqrt{\kappa_p}\cdot \sqrt{\kappa_q}}
\cdot \beta_q\tag{8}
\]



\noindent
Next, 
put
\[
k_{p,q}=\iint K(x,y)\phi_p(x)\phi_q(y)\, dxdy\tag{9}
\]
From  the above  the following hold for each pair $p,q$:

\[ c_{pq}= \iiint\,
\phi_q(x)\phi_p(y) S(x,t)K(t,y)\, dxdydt=
\kappa_qk_{p,q}=\kappa_pk_{q,p}\implies
\]
\[ 
\frac{c_{p,q}^2}{ \kappa_p\cdot \kappa_q}\leq
|k_{p,q}\cdot  k_{q,p}|
\leq \frac{1}{2}(k_{p,q}^2+k_{q,p}^2)\tag{10}
\]
Here $\{k_{p,q}\}$ are the Fourier-Hilbert coefficients of $K(x,y)$
which entails that
\[ 
\sum\sum\, k_{p,q}^2\leq
\iint K(x,y)^2\, dxdy
\]
Hence the symmetric and doubly indexed sequence
\[
\frac{c_{p,q}}{\sqrt{\kappa_p\cdot \kappa_q}}\tag{11}
\] 
is of Hilbert-Schmidt type.
\bigskip

\noindent
{\bf{11.6.2 Conclusion.}}
The eigenfunctions $u$ in $L^2[0,1]$
associated to the $\mathcal K$-kernel have Fourier-Hilbert expansions via
the $\{\phi_n\}$-basis  which are  determined by 
$\alpha$-sequences  satisfying the system (7)


\medskip

\noindent
{\bf{11.6.3 Remark.}}
When a plane curve
$\mathcal C$ has corner points the
Neumann-PoincarŽ kernel is
unbounded. Here
the reduction to the symmetric case is  more involved  and leads 
to
quite intricate results which appear in Part II from
[Carleman].
The interplay  between singularities
on boundaries in 
the Neumann-PoincarŽ equation
and the corresponding unbounded kernel functions 
illustrates  the 
general theory
densely defined self-adjoint operators.
Much analysis remains to be done and
open problems about
the Neumann-PoincarŽ equation 
remains to be settled in dimension three. So far  it appears that
only the 2-dimensional case 
is properly understood via 
results  in [Car:1916].
See also ¤ xx for a studiy of Neumann's boundary value problem
both in the plane and  ${\bf{R}}^3$.






\end{document}




\newpage


\centerline{\bf{12.4 Uniqueness results for the exterior
Laplace equation}}

\bigskip

\noindent
Let $\Omega$ be a bounded open set
in ${\bf{R}}^3$ whose boundary is a finite union of closed
surfaces of class $C^1$ at least.
Set $U={\bf{R}}^3\setminus \Omega$.
Denote by $\mathcal S(U)$ the class of real-valued $C^2$-functions
$f$ in $U$ which extend continuously to
the boundary of $U$ which of course is equal to
$\partial\Omega$. Moreover,  we assume that the 
the exterior normal derivaties
$\frac{df}{dn}$ taken along the boundary exist and
give a continuous function on
$\partial U$.
Consider large positive $R$-numbers  so that
the open ball $B(R)$ of radius $R$ centered at the origin
contains the closure of $\Omega$.
Set
\[ 
D(f)^2(x,y,z)=(\frac{\partial f}{\partial x})^2+
(\frac{\partial f}{\partial y})^2+(\frac{\partial f}{\partial z})^2
\]
Green's formula applied to the domain $B(R)\setminus\overline{\Omega}$
gives
\[
\int_{B(R)\setminus\overline{\Omega}}\,D(f)^2\, dp+
\int_{B(R)\setminus\overline{\Omega}}\,f\cdot \Delta(f)\, dp=
\int_{\partial U}\tag{1} 
\]
where $dp=dxdxydz$.
We shall use this to prove:

\bigskip

\noindent
{\bf{1. Theorem.}}
\emph{If $f$ and $\Delta(f)$ both belong to $L^2(U)$, it follows that}
\[
\int_U \,D(f)^2\, dp=\int_{\partial U}-
\int_U\,f\cdot \Delta(f)\, dp
\]
\medskip

\noindent
\emph{Proof}
Since $f$ and $\Delta(f)$ are square integrable, the Cauchy-Schwarz
inequality entails that
$f\cdot \Delta(f)$ is absolutely integrable over $U$.
Hence (1) gives the theorem if we prove the limit formula
\[
\liminf_{R\to \infty}\,\int_{\partial U}=0\tag{i}
\]
To prove (i) we consider the function
\[
\psi(R)=\int_{B(R)\setminus\overline{\Omega}}\, u^2\, dp 
\]
The derivative becomes
\[
\psi'(R)=\int_{S(R)} \, u^2\cdot d\omega
\]
where $S(R)$ is the sphere of radius $R$ and $d\omega$ its area measure.
Passing to the second derivative the reader should verify
the equation
\[
\psi''(R)=\frac{2}{R}\cdot \psi'(R)+
2\cdot \int_{S(R)} \, f\cdot\frac{\partial f}{\partial n}\, d\omega
\]
Hence (i) follows if 
\[
\liminf_{R\to \infty}\,\psi''(R)-\frac{2}{R}\cdot \psi'(R)=0\tag{ii}
\]
To obtain (ii)  we first notice that
$\Psi$ is non-decreasing and
since $f$ is square integrable it tends to a finite limit as $R\to+\infty$.
Hence the first order derivative cannot stay above a positive constant
for all large $R$.
So for the derivative  $\psi'$ two cases can occur. Either
it decreases in a monotone way to zero as $R\to+\infty$. In this case it is eveident that
there exists a striuctly increasing sequebce $\{r_n\}$ such that
$\psi''(r-n)\to 0$ and (ii) follows.
In the second case
the function $\psi'(R)$ attain a local minium at an infinite sequence
$\{r_n\}$ which again tend to zero.
Here $\psi''(r_n)=0$ and at the same time these local minimum values of
the first order derivative tend to zero. So again (ii) holds and
Theorem 1 is proved.
\bigskip



\centerline{\bf{A vanishing result.}}
\bigskip


\noindent
Let  $f$ satisfy the differential equation
\[
 \Delta(f)+\lambda\cdot f=0\tag{*}
 \] 
in $U$ for some real number $\lambda$.
In addition
we assume that
\[
\frac{df}{dn}(p)=0\quad\colon p\in \partial U\tag{**}
\]
\bigskip


\noindent
{\bf{2. Theorem. }}
\emph{If  $f$ satisfies (*-**) and  belongs to
$L^2(U)$, then $f$  is identically zero.}
 \bigskip


\noindent
\emph{Proof.}
Notice that Theorem 1 gives the equality
\[
\int_U \,D(f)^2\, dp=\lambda\cdot 
\int_U\,f^2\, dp
\]
So if $\lambda\leq 0$ the vanishing of $f$ is obvious.
From now on $\lambda>0$.
We shall work with polar coordinates, i.e. employ the Euler's  angular variables
$\phi$ and $\theta$ where
\[
0<\theta\quad\colon\, 0<\phi<2\pi
\]
The wellknown expression of $\Delta$Êin the variables $r,\theta,\phi$ 
shows that the equation (*) corresponds to
\[
xxxxx+xxxx=0\tag{i}
\]
Let $n\geq 1$ and $Y_n(\theta,\phi)$ some spherical function of
degree $n$ with a normalised $L^2$-integral  equal to one.
For each $r$ where $B(r)$ contains $\overline{\Omega}$
we set
\[
 Z(r)=\int_0^{2\pi}\int_0^\pi\, 
 Y_n(\theta,\phi)\cdot f(r,\theta,\phi)\, \sin(\theta)\, d\theta d\phi\tag{ii}
\]
The Cauchy-Schwarz inequality gives
\[
 Z(r)^2\leq \int_0^{2\pi}\int_0^\pi\, 
Y^2_n\cdot  \sin(\theta)\, d\theta d\phi\cdot 
\int_0^{2\pi}\int_0^\pi\, 
f^2(r,\theta,\phi)\cdot  \sin(\theta)\, d\theta d\phi
\]
Since the $L^2$-integral if $Y_n$ is normalised
the last product is reduced to
\[
J(r)=\int_0^{2\pi}\int_0^\pi\, 
f^2(r,\theta,\phi)\cdot  \sin(\theta)\, d\theta d\phi
\]
Now
\[
\int_{r_*}^\infty\, r^2\cdot J(r)\, dr
\]
is equal to the finite $L^2$-integral of $f$ in the exterior domain
taken outside a ball $B(r_*)$.
From (ii) we conclude that
\[
\int_{r_*}^\infty\, r^2\cdot Z(r)^2\, dr<\infty\tag{iii}
\]
\medskip


\noindent
{\bf{A differential equation.}}
Recall that a spherical function of degree $n$ satisfies
\[
\frac{1}{\sin \theta}
\frac{d}{d \theta}\bigl(\sin \theta\cdot
\frac{\partial Y_n}{\partial \theta}\bigr)+
\frac{1}{\sin^2 \theta}\frac{\partial^2 Y_n}{\partial \phi^2}+
(n+1)n\cdot Y_n=0
\tag{iv}
\]
\medskip

\noindent
{\bf{Exercise.}}
Show via suitable partial integrations that (i) and (iv) imply that
$Z(r)$ satisfies the differential equation
\[
\frac{1}{r^2}\cdot
\frac{d}{dr}(r^2\cdot \frac{dZ}{dr})+
(\lambda-\frac{n(n+1)}{r^2})Z=0\tag{v}
\]
\medskip

\noindent
The second order differential equation
has two linearly independent solutions of the form
\[
Z_1=\cos(\sqrt{\lambda} r)\cdot \bigl[\frac{1}{r}+
\frac{a_2}{r^2}+\ldots\bigr]
\]
\[
Z_2=\sin(\sqrt{\lambda} r)\cdot \bigl[\frac{1}{r}+
\frac{b_2}{r^2}+\ldots\bigr]
\]
It follows that there exist a pair of constants $c_1,c_2$ such that

\[
Z=c_1Z_1+c_2Z_2=\frac{c_1\cdot  \cos(\sqrt{\lambda} r)+
c_2\cdot  \sin(\sqrt{\lambda} r)}{r}+
\frac{B(r)}{r^2}\tag{vi}
\]
where $r\mapsto B(r)$ stays bounded as $r\to+\infty$.
\medskip

\noindent
{\bf{Exercise.}}
Show that the finite integral in (iii) and (vi) give 
$c_1=c_2=0$ and hence $Z(r)$
identically zero for large $r$.
Since this  hold for all spherical functions we conclude that 
$f$ is identically zero outside 
the closed ballÊ$B(r_*)$.
Finally, by assumption $U$Êis connected and the elliptic equation
(*) implies that $f$ is a real-analytic function in
$U$, So the vanishing outside a large ball entails that $f$ is identically zero in $U$
which finishes the proof of Theorem 2.
\bigskip

\noindent
\centerline {\bf{3. A result about absolute continuity.}}
\medskip

\noindent
We consider functions  depending upon a real parameter
$\mu$ which varies in an interval $[a,b]$. To each
$\mu$ we are given a function
$f(x,y,z;\mu)$
 which is square integrable $C^2$-function in $U$ and the normal derivative along
 $\partial U$ is zero, i.e just as in the class $\mathcal S$ above.
 Moreover, 
 the $L^2(U)$-valued function
 \[
\mu\mapsto f(x,y,z;\mu)\tag{i}
\]
has a finite total variation on $[a,b]$.
Next,  assume that for every sub-interval $\ell$ of $[a,b]$ one has
the equality
\[
\Delta \bigl(\int_\ell\, \frac{d } {d\mu}\,f(x,y,z;\mu)+
\int_\ell\, \mu\cdot \frac{d } {d\mu}\, f(x,y,z;\mu)=0
\]
where the integrals as usual are taken in the sense of Borel-Stieltjes.
\bigskip

\noindent
{\bf{Theorem.}} \emph{Every function
from (i) which satisfies the conditions above is 
absolutely continues with respect to $\mu$.}
\bigskip

\noindent
\emph{About the proof.}
Using similar methods as in the proof of Theorem 1
one reduces the proof to study
functions 
$g(r;\mu)$ where $r\mapsto g(r;\mu)$ is 
a $C^2$-function and square integrable on
the interval $[r_*,+\infty)$ for a given $r_*>0$
while $\mu$ as above varies in $[a,b]$.
Moreover one has 
\[ 
\max_\mu\, \int_{r_*}^\infty\, g(r;\mu)\,  dr<\infty
\] 
Next, for each sub-interval
$\ell=[\alpha,\beta]$ we set
\[
\delta_\ell(g(r,\mu)=g(r,\beta)-g(r,\alpha)
\]
With these notations we say that
$g(r;\mu)$ is absolutely continuous with respect to $\mu$
if there to each $\epsilon>0$ exists
$\delta>0$Êsuch that
\[
\sum\, \int_{r_*}\, |\delta_{\ell_\nu}((g(r,\mu)\bigr|^2\cdot r^2\,dr<\epsilon
\]
for every finite family of sub-intervals
$\{\ell_\nu\}$ when  the sum of their lengths is
$<\delta$.
\medskip

\noindent
{\bf{Theorem.}}
\emph{Assume in addition to the above that
the  equation below holds for each 
sub-interval $\ell$} 
\[
\frac{1}{r^2}
\frac{d}{dr} \bigl[\, r^2\frac{d}{dr}(\delta_\ell(g(r,\mu) \bigr]-
\frac{n(n+1)}{r^2}\cdot \delta_\ell(g(r,\mu)+
\int_\ell\, \mu\cdot \frac{d}{d\mu}(g(r,\mu)=0
\]
\emph{Then 
$g(r,\mu)$ is absolutely continuous with respect to $\mu$.}

\newpage


\medskip


\centerline {\bf{A first example: Moment problems.}}
\medskip

\noindent
In the  very impressive and highly original  article
\emph{Recherches sur les fractions continues}
[Ann.Fac. Sci. Toulouse. 1894], Stieltjes
studied    the moment problem on the non-negative real line. This
amounts to find
a non-negative Riesz measure $\mu$ on ${\bf{R}}^+$
with prescribed  moments
\[
 c_\nu=\int_0^\infty\, x^\nu d\mu(x)\quad\colon\nu=0,1,2,\ldots\tag{*}
\]
An obvious necessary condition for the existence of $\mu$
is that
the quadratic form
\[
J(x)=\sum_{p=1}^\infty\sum_{q=1}^ \infty\, c_{pq}x_px_q
\]
is positive definite when it is restricted to vectors
$x$-vectors where only  finitely many $x_p\neq 0$.
The moment problem is  determined with respect to
the given sequence $\{c_\nu\}$ if there exists a unique non-negative
measure $\mu$ such that (*) holds.
To prove  existence and  analyze
uniqueness, Stieltjes employed the  expansion in
continued fractions of the  $c$-sequence. 
Stieltjes' work was later reconsidered by Hamburger
in the article \emph{xxxx}[ 1922]
where one allows solutions by Riesz measures $\mu$ on the whole real line,
i.e. now integration takes place over
$(-\infty,+\infty)$.
In ¤ xx we explain that this (extended) moment problem
is closely related to
the class of linear operators defined by inifinite 
and symmetric matrices of the form
\[
xxx=xxx
\]
where $\{a_n\}$ is an arbitrary real sequence  while 
$\{b_n\}$ is a sequence of positive real numbers.
A  complete 
description of all solutions $\mu$ to 
a non-determined  moment problem
was established by Carleman in the article
\emph{Sur le problŽme des moments} [C.R.Acad. Sci. Paris. 1922],
and we shall expose this in ¤ xx.
\medskip

\noindent
Returning to the case treated by Stieltjes
the existence of non-determined moment problems,
leads to
a peculiar result for certain  densely defined
linear operators on the Hilbert space $\ell^2$.
Following Stieltjes we consider a positive sequence of real numbers
$\{b_n\}$
and regard the operator $S$ defined by
\[
S(x)= (-b_1x_2,-b_1x_1,-b_2x_4,-b_2x_3,\ldots)
\]
where $x=\{x_n\}$ is a vector in $\ell^2$.
It means that $S$ is represented by the infinite symmetric matrix
whose non-zero elements
only appear in position $(j,j+1)$ or $(j+1,j)$
for every integer $j\geq 1$.
Now there exists the  dense subspace
$\mathcal D(S)$  of vectors
$x\in \ell^2$ such that
$S(x)$ also belongs to $\ell^2$.
The question arises if
the symmetry of the $S$-matrix persists in the following
sense: Suppose that $x$ and $y$ both belong to
$\mathcal D(S)$. Does it follow that 
\[ 
\langle S(x),y\rangle=
\langle x,S(y)\rangle \tag{**}
\]
where we have used the Hermitian inner product on the complex Hilbert space
$\ell^2$. So above $x$ and $y$ can be complex vectors.
In the cited article above, Carleman proved that
(**) hold for
every pair in $\mathcal D(S)$ if and only if 
the corresponding moment problem is determined.
This means that in spite of 
the symmetry of the matrix which
represents $S$, the resulting densely defined linear operator can fail to be self-adjoint.
In ¤ xx we show
that whenever
this peculair phenomenon  occurs,
the series
\[
\sum_{n=1}^\infty\, \frac{1}{b_n}<\infty
\]
However, the converse is not true, i.e. 
there exist determine moment problems where
the series above is converges.
\medskip

\noindent
{\bf{A final remark.}}
The study of the Hamburger-Stieltjes moment problem offers
an instructive lesson about unbounded but densely defined liear operators on
Hilbert spaces.
At the same time the material in ¤xx will teach
that even if one starts with a problem expressed in terms of functional analysis,
it is often necesssty to 
employ both results and methods from other disciplines such as 
analytic function theory and
Fourier analysis.




 
\centerline{\bf{Moment problems.}}
\bigskip


\noindent
A great inspiration during the development of
unbounded symmetric operators on Hibert spaces
emerged from  Stieltjes' pioneering article
\emph{Recherches sur les fractions continues}
[Ann. Fac. Sci.  Toulouse. 1894].
The  moment problem
asks for conditions on a
sequence $\{c_0,c_1,\ldots\}$ of positive real numbers
such that there exists a non-negative Riesz measure
$\mu$ on the real line and
\[
c_\nu= \int_{-\infty}^\infty\, t^\nu\cdot d\mu(t)\tag{*}
\] 
hold for each $\nu\geq 0$.
One easily verifies that
if $\mu$ exists then
the Hankel determinants
\[
\begin{pmatrix}
c_0&c_1&\ldots&c_n\\
c_1&c_2&\ldots&c_{n+1}\\
\ldots&\ldots&\ldots&\ldots\\
c_n&c_{n+1}&\ldots&c_{2n}\\
\end{pmatrix}
\]
are $>0$ for every $n=0,1,\ldots$. 
For brevity we say that
$\{c_n\}$ is a positive
Hankel sequence when
the determinants above are $>0$.
It turns out that this confition also is sufficient.
\medskip


\noindent
{\bf{Theorem.}} \emph{For each 
positive Hankel sequence
there exists at least one non-negative Riesz measure such that
(*) holds.}
\medskip


\noindent
{\bf{Remark.}}
The result above is due to Hamburger who  extended Stieltjes' original  results 
which treated  the situation where 
one seeks non-negative measures supported by
$\{\geq 0\}$.
The moment problem for a positive Hankel sequence is 
said to be determined
if (*) has a unique  solution $\mu$.
Hamburger proved that the determined case holds
if and only if the
the associated continued fractions of $\{c_n\}$
is completely convergent.
See ¤ x below for an account about this convergence  condition.
A "drawback" in the Hamburger-Stieltjes theory
is that it is often  difficult to check
when the associated continued fraction of a positive Hankel sequence
is completely convergent.
So one is led to seek  sufficient conditions
in order that (*) has a unique solution $\mu$.
Such a sufficient condition
was established  in Carleman's  monograph
[Carleman 1923. Page 189-220] 
and goes as follows:




\noindent
{\bf{1. Theorem.}}
\emph{The moment problem of 
a positive Hankel sequence $\{c_n\}$ is determined if}
\[
\sum_{n=1}^\infty\,c_n^{-\frac{1}{n}}=+\infty
\]
\medskip

\noindent
{\bf{Another criterion for  determined moment problems.}}
Studies of continued fractions and
their associated quadratic forms 
go back to
work by Heine. See  [Handbuch der theorie
der Kugelfunktionen: Vol. 1. part 2]. An excellent account appears also
in the article \emph{Zur Einordnung der Kettenbruchentheorie
in die theorie der quadratischen Formen von
unendlichvielen VerŠnderlichen} [Crelle J. of math. 1914] by
Hellinger and Toeplitz.
A positive Hankel sequence $\{c_n\}$
 corresponds to a
 quadratic form
 in an infinite number of variables:
 \[
 J(x)=\sum_{p=1}^\infty a_px_p^2-
 2\cdot \sum_{p=1}^\infty b_px_px_{p+1}
\]
where $b_p\neq 0$ for every $p$.
More precisely, the
sequences $\{a_\nu\}$ and $\{b_\nu\}$
arise when
the series
\[
-\bigl[\frac{c_0}{\mu}+
\frac{c_1}{\mu^2}+\frac{c_2}{\mu^3}+\ldots\,\bigr]
\]
is formally expanded into a continuous fraction
\[
\frac{c_0}{a_1-\mu-\frac{b_1^2}{a_1-\mu-\frac{b_2^2}{a_2-\mu}} }
\]
Now there exists 
the infinite  matrix $A$
with diagonal elements $\alpha_{pp}=a_p$ while
\[
\alpha_{p,p+1}= \alpha_{p+1,p}= -b_p\quad\colon p=1,2,\ldots
\]
and all the other elements are zero.
The symmetric  $A$-matrix 
gives a densely defined linear operator on
the complex Hilbert space $\ell^2$.
The following result is proved
[Carleman:1923]:
\medskip

\noindent
{\bf{2. Theorem.}}
\emph{The densely defined operator $A$ on $\ell^2$ is self-adjoint if and only if
the moment problem for $\{c_n\}$ is determined.}
\bigskip


\centerline {\bf{3. A  study of $A$-operators.}}
\bigskip

\noindent
Ignoring the "source" of the pair of real sequences $\{a_p\}$ and $\{b_p\}$
we consider a matrix $A$ as above where the sole condition
is that $b_p> 0$ for every $p$.
If $\mu$ is a complex number
one seeks infinite vectors
$x=(x_1,x_2,\ldots)$ 
 such that
 \[ 
 Ax=\mu\cdot x\tag{i}
 \]
 It is clear that (i) holds if and only if
 the sequence $\{x_p\}$ satisfies the infinite system of linear equations
 \[
(a_1-\mu)x_1=b_1x_2
\]
\[ 
(a_p-\mu)x_p=b_{p-1}x_{p-1}+ b_px_{p+1}\quad\colon p\geq 2
\]
\medskip

\noindent
Since $b_p> 0$ for every $p$ we see  that
$x_1$ determines the sequence and 
$x_2,x_3,\ldots$ depend on $x_1$ and the parameter $\mu$.
Keeping $x_1$ fixed while $\mu$ varies
the reader can  verify that
\[ 
x_p=\psi_p(\mu)\quad\colon p\geq 2
\]
where $\psi_p(\mu)$ is a polynomial of degree $p-1$ for each $p\geq 2$.
These $\psi$-polynomials depend on the given
pair
of sequences
$\{a_p\}$ and $\{b_p\}$ and 
with the following
result is  proved in [ibid]:
\medskip


\noindent
{\bf{3.1 Theorem.}}
\emph{The densely defined operator $A$ on $\ell^2$ is self-adjoint if and only if}
\[
\sum_{p=1}^\infty\, \psi_p(\mu)=+\infty
\]
\emph{for every non-real complex number
$\mu$.}
\medskip


\noindent
{\bf{4. A  general result.}}
Let $\{c_\nu\}$ be a positive Hankel sequence,
determined or not.
Let  $\rho$ be a non-negative measure which solves the moment problem (*) and
set
\[
\widehat{\rho}(\mu) =\int\, \frac{d\rho(t)}{t-\mu}
\]
This yields  an analytic function in
the upper half-plane.
A major result in [Carleman]
gives a sharp inclusion for the values which can be attained
by
these $\widehat{\rho}$ functions while
$\rho$ varies in the family of  non-negative measures which
solve the moment problem.
It is expressed via constructions of discs in the upper half-plane which
arise via a nested limit of discs constructed from a certain family of
Mšbius transformations.
More precisely, to the given Hankel sequence
we have the pair of sequences $\{a_\nu\}$ and $\{b_\nu\}$.
For a fixed $\mu$ in the upper half-plane
we consider the maps:
\[ 
S_\nu(z)=\frac{b_\nu^2}{a_{\nu+1}-\mu-z}\quad\colon \nu=0,1,\ldots
\]
Notice that
\[ 
\mathfrak{Im}(S_\nu(z))=\frac{b_\nu^2\cdot \mathfrak{Im}(\mu+z)}
{|a_{\nu+1}-\mu-z|^2}>0
\]
It follows that $S_\nu$ maps the upper half-plane $U^+$ conformally onto a disc
placed in $U^+$.
\medskip

\noindent
{\bf{Exercise.}}
To each $n\geq 1$ we consider the composed map
\[ 
\Gamma_n=S_0\circ S_1\circ\ldots\circ S_{n-1}
\]
Show that the images $\{C_n(\nu)= \Gamma_n(U^+)\}$
form a decreasing sequence of discs and there exists a limit
\[ 
C(\mu)=\cap\, C_n(\mu)
\]
which either is reduced to a single point or is a closed disc
in $U^+$.
\bigskip

\noindent
{\bf{4.1 Theorem.}} \emph{For each $\mu\in U^+$
and every $\rho$-measure which solves the moment problem
one has the inclusion}
\[
\widehat{\rho}(\mu)\subset C(\mu)
\]
 \emph{Moreover, for each point $z$ in this disc there exists
 $\rho$ such that
 $\widehat{\rho}(\mu)=z$.}




\newpage

\centerline{\bf{¤ 12. Symmetric integral operators.}}
\bigskip


\noindent
Consider the domain $\square=\{0\leq x\leq 1\}\times\{0\leq y\leq 1\}$
in ${\bf{R}}^2$.
Let $K(x,y)$ be a real-valued and Lebesgue mesure function on
$\square$ such that
the integrals
\[ 
\int_0^1\, K(x,y)^2\, dy<\infty
\]
for all $x$ outside a null-set on $[0,1]$.
In addition we assume that $K$ is symmetric,  i.e.$K(x,y)= K(y,x)$.
The $K$-kernel is bounded in Hilbert's sense if there exists a constant
$C$ such that
\[ 
\iint_\square\, K(x,y) u(x)u(y)\, dxdy\leq C^2\cdot\int_0^1\, u(x)^2\, dx
\]
for each $u\in L^2[0,1]$. A special case occurs when
$K(x,y)$ satisfies
\[
\iint_\square\, |K(x,y)|^2\, dxdy<\infty
\]
Then $\mathcal K$ is called a Hilbert-Schmidt operator and a crucial fact is that
it yields a compact operator on the Hilbert space
$\mathcal H=L^2[0,1]$.
\medskip

\noindent
{\bf{Exercise.}}
Prove that Hilbert-.Schmidt operators are compact. Tne hint is that
Lebesgue theory to begin with entails that when (zz) holds then
there exists a seqience of symmwtric and continuous kernel
functions $\{K_n(,y)\}$
such that
\[
\iint_\square\, |K(x,y)-K(x,y)|^2\, dxdy=0
\]
Next, the Cauchy-Schwarz inequality gives 
\[
||\mathcal K-\mathcal K_n||\leq \iint_\square\, |K(x,y)-K(x,y)|^2\, dxdy
\] 
for each $n$, where the right hand side refers to operator norms.
Now one uses the general fact that a linear operator which can be approximated in the operator
norm by compact operators is itself compact.
Finally the reader should verify that
if $K(x,y)$ is contoinous then $\mathcal K$ is compact.



\medskip

\noindent
{\bf{Spectral functions.}}
Let $K$ be a  symmetric Hilbert-Schmidt operator.
A special case of Holbert's theorem from ¤ 8  and the general 
facts about spectera of compact operators
in ¤ xx, entail that
there exists a sequence $\{\phi_n\}$
of pairwise orthogonal functions in
$\mathcal H$ with $L^2$-norms equal to one, a
real eigenvalues
$\{\mu_n\}$ so that
\[
\mathcal K(\phi_n)=\mu_n\cdot \phi_n
\]
The eigenvalues  form a discrete set outside zero and
arranged so that $\mu_1\geq |\mu_2\geq \ldots$
and repeated according to multiplicities, i.e. when
the corresponding eigenspace has dimension $\geq 2$.
Set
\[
\lambda_n=\mu_n^{-1}
\]
For each  $\lambda>0$ we set
\[
\rho(x,y;\lambda)=\sum_{0<\lambda_\nu<\lambda}\, \phi_\nu(x)\phi_\nu(y)
\]
\[
\rho(x,y;-\lambda)\sum_{-\lambda <\lambda_\nu<0}\, \phi_\nu(x)\phi_\nu(y)
\]
Notice that  the $\lambda$-numbers in (x) stay
away from zero. Hence
function $\rho_N$
vanishes  in a neighborhood of zero.
The spectral theorem applied to symmetric Hilbert-Schmidt operators entails that
\[
\mathcal K(h)(y)=
\int_{-\infty}^\infty\, \frac{1}{\lambda}\cdot \frac{d}{d\lambda}\,
\rho(x,y;\lambda)\cdot h(y)\,  dy
\]
hold for each $h\in \mathcal H$.

\medskip

\noindent
{\bf{The $\Omega$-kernel.}}
If $h\in \mathcal H$ we have an expansion 

\[
h=\sum\, a_k\cdot\phi_k+h^*
\] 
where $h^*$ is $|perp$ to the subspace of
$\mathcal H$ generated by the eigenfunctions
and the reader should check that
 \[
\sqrt{\sum\, |a_k|^2}\leq ||h||_2 
\]
Apply (x) to a pair
$h,g$ in $L^2[0,1]$. Then the reader should check that
\[
 \bigl|\iint_\square\, \rho(x,y;\lambda)\cdot h(x)g(y)\, dxdy\bigr|\leq
 ||h||_2\cdot ||g||_2\tag{xx}
 \] 
hold for each $\lambda$ which may be taken to be positive or negative.
For each $\lambda$ we  set
\[
 \Omega(x,y;\lambda)=\int_a^x\int_a^y\, \rho(s,t;\lambda)\, dsdt
\]
 \medskip

\noindent
{\bf{Exercise.}}
Conclude from (xx)
that the function
\[
(x,y)\mapsto \Omega(x,y;\lambda)
\]
is  Hšlder continuous of order $1/2$.
More precisely, for each
$\lambda$ and every pair
$x_1<x_2$ and $y_1<y_2$ one has
\[
|\Omega(x_2,y_2;\lambda) -\Omega(x_1,y_1;\lambda)|
\leq \sqrt{(x_2-x_1)(y_2-y_1)}
\]
A crucial point is that (e.1) holds for all Hilbert-Schmidt kernels, i.e. independent
of the size of
the Hilbert-Schmidt norms.
\medskip

\noindent
{\bf{The $\psi$-functions.}}
With $\lambda$ and $0<x\leq 1$
kept fixed we set
\[
\psi(y;\lambda)=\int_0^x\, \rho(s,y;\lambda)\, ds
\]
We have the characteristic 
function $\chi(x)$ defined as one on $[0,x_*]$ and zero if
$x>x_*$.
Considered as a vector in $\mathcal H$ one has an expansion
\[
\chi(x)=
\sum\, a_k\phi_k(x)+\chi_*\quad\colon\,
a_k=\int_0^{x_*}\,\phi_k(s)\, ds
\]
At the same time the construction of the $\rho$-function
entails that
\[
\psi(y;\lambda)=\sum_*\, \int_0^{x_*}\,\phi_k(s)\cdot \phi_k(y)
\] 
with the sum restricited over those  $k$ for which
$0<\lambda_k<\lambda$.
Bessel's inequality gives
\[
\int_0^1\, \psi(y;\lambda)^2\, dy\leq
\bigl(\sum_*\, \int_0^{x_*}\,\phi_k(s)\bigr)^2
\]
In the last term we have taken a restricted sum which is majorsised by
the sum over all $k$ which again by Bessel's inequality is majorised by
the $L^2$-integral of $|chi$, i.e by $x^2$.
Hnece one has
the inequality
\[
\int_0^1\, \psi(y;\lambda)^2\, dy\leq x\quad\colon 0<x\leq 1
\]
\medskip

\noindent
{\bf{Exercise.}}
More generally, let
$E$ be a sum of disjoint intervals on the $x$-interval and put
\[ 
\psi_E(y;\lambda)=\int_E\, \rho(x,y;\lambda)\,dx
\]
Show that
\[
\int_0^1\, \psi_E(y;\lambda)^2\, dy\leq |E|_1
\]
where the last term is the Lebesgue measure of $E$.

\medskip

\noindent
{\bf{Weak limits.}}
Let us first notice that
the contruction of the $\psi$-function means that
\[
\frac{\partial \Omega(x,y;\lambda)}{\partial y}=
\psi_x(y;\lambda)
\]
So (xx) entails that
the Hšlder contionius $\Omega$-function has a partial $y$-derivative in
the sense of distributions which belongs to $L^2$ which moreover
is absolutely continuu as a fuinction of $x$ since
(xx) is constucted as a primitive function in the sense of
Lebesgue.
It follows that one also has
\[
\frac{\partial}{\partial x}(\frac{\partial \Omega(x,y;\lambda)}{\partial y})=
\rho(x,y;\lambda)
\]
\medskip


\noindent
Let us then consider a sequence of
Hilbert-Schmidt kernels $\{K_n\}$ and to
each of them we get the spectral function
$\rho_n(x,y;\lambda)$.
Now $\{\Omega_n(x,y;\lambda)$
is an equi-contonuous family of functions on
$\square$.
So by the Arzela-Ascli theorem
we find a subsequence which converges uniformly to a 
limit function
$\Omega_*(x,y;\lambda)$ for each fixed $\lambda$.
From (*)   $\Omega$ is again uniformly Hšlder continuous.
Moreover, the uniform bound for the
$L^2$-norms of $y\mapsto \psi_x(y;\lambda)$ entail that
the partial $y$-erivatives of $\Omega_*$ yield $L^2$-functions
which are absoutely continuous with respect to $x$. So there exists
an almost everywhere defined limit function
\[
\rho_*(x,y;\lambda)=
\frac{\partial}{\partial x}(\frac{\partial \Omega_*(x,y;\lambda)}{\partial y})
\]
for which the inequality (xx) holds.



\newpage







and
its first order partial derivatives are $L^2$-functions. Moreover, after the passage to
the limit one still
has Bessel's inequality which entails that
\[
\int_{-\infty}^\infty\, 
\frac{d}{d\lambda}\int_0^1 h(x)\cdot \bigl(\frac{\partial}{\partial x}
\int_0^1\, \frac{\partial\Omega(x,y;\lambda)}{\partial y}\cdot h(y))\,dy\bigr )\, dx
\leq \int_0^1\, h(x)^2\, dx
\]
for every $h\in L^2[0,1]$.



\newpage






In the monograph [Carelan 1923]
the condition (*) is imposed while (**) need not be valid.
Then we encounter an unbounded operator.
But notice that if
$u|in\mathcal H$ then (*9 and the CuachySchwarz inequality entails that
the functions
\[ 
y\mapsto K(x,y)u(y)
\] 
are absolutely integrable in Lebegue's sense 
for all $x$ outside the nullset $\mathcal N$ above.
Hence it makes sense to refer to $L^2$-functions $\phi$ on $[0,1]$
which
satisfy an eigenvalue equation
\[
\phi(x)= \lambda\cdot \int_0^1\, K(x,y)\phi(y)\, dy\tag{1}
\]
where $\lambda$ is a compkex number.
one is also led to consider the integral equation
\[
\phi(x)= \lambda\cdot \int_0^1\, K(x,y)\phi(y)\, dy+f(x)\tag{2}
\]
where $f\in\mathcal H$ is given and one seeks $\phi$.
It turns out that if $\mathfrak{Im}(\lambda)\neq 0$,
then the  inhomogenous equation 
(2) has at least one solution. 
Next,  consider the equation (1).
Let $\rho(\lambda)$ denote the number of linearly independent 
solution in (1). Carelan proived that
 the  $\rho$-function is constant 
when  $\lambda$ varies in
${\bf{C}}\setminus {\bf{R}}$.
Follwing Carelan one says that the kernel $(x,y)$ gives an operator $\mathcal K$ of Class I if
the $\rho$-function is zero. It means that
(2) has unique solutions
for every pair $\lambda,f)$
when $\lambda$ are non-real.
\medskip


\noindent
{\bf{A limit process.}}
Let $\{G_n(x,y)\}$ be a sequece of
symmetric kernel functions which are bounded in Hilbert's sense and
approximate $K$ in the sense that
\[
\lim_{n\to \infty} \int_0^1\, |K(x,y)-G_n(x,y)|^2\, dy=0
\]
for all $x$ outside
a null set. Fix some non-real $\lambda$.
Hilbert's theory entials that if
$f(x)$ is a continuous function, in general complex-valued, then
we find unqiue continuous functions $\{\phi_n\}$
which satisfy the integral equations
\[
\phi_n(x)= \lambda\cdot \int_0^1\, G_n(x,y)\phi(y)\, dy\tag{1}
\]
For a fixed $x$ we consider the complex numbers
$\{phi_n(x)\}$.
Now there exists the set $Z(x)$ of all cluster points, i.e.
a complex number
$z$ belongs to $Z(x)$ if there exists some
sequence $1\leq n_1<n_2<\ldots$ such that
\[
 z=\lim_{k\to\infty}\, \phi_{n_k}(x)
\]
\medskip

\noindent
{\bf{Theorem.}} \emph{For every approximating sequence $\{G_n\}$ as above
the sets $Z(x)$ are either reduced to points or circles in
the complex plane. Moreover, each $Z(x)$ is reduced to a siungleton set
when $\mathcal K$ is of class I.}
\medskip

\noindent
{\bf{Remark.}}
The result below was discovered by Weyl for some special unbounded operators
which arise during the study of second order
differential equations. See ¤ for a comment-.
If $\mathcal K$  is of Class I then
the theorem sbove shows that
each pair of a on-real $\lambda$
and some $f\in\mathcal H$ gives
a unique function $\phi(x)$
which satsfies (2) and
it can be found via a pointwise limit of solutions
$\{\phi_n\}$ to the equations (xx). In this sense the limit process
is robust because one can emply an arbitrary approximating
sequence $\{G_n\}$ under the sole condition that (xx) holds.
This already indficartes that the Case I leads to
a "consistent theory" even if $\mathcal K$ is unbounded.
To make this precise Carleman constructed a unique spectral function
when Case I holds.
More preciely, if
$K(x,y)$ is symmetric and 
Case I holds, then there exists a unique function
$\rho(x,y;\lambda)$ defined for
$(x,y)\in\square$ and every real $\lambda$ such that
\[
\mathcal K(h)(x)=\int_{-\infty}^\infty\, 
\,\frac{1}{\lambda}\cdot\frac{d}{d\lambda} \,
\int_0^1\, \theta(x,y;\lambda)\,h(y)\, dy
\] 
for all
$L^2$-functions $h$.
Concerning the spectral $\theta$-function, Carleman proved that  it
enjoys the same properties as Hilbert's spectral function for bounded 
operators.


\medskip

\noindent
{\bf{Remark.}}
For each fixed $\lambda>0$
one has a bounded self-adjoint operator
on $\mathcal H$ defined by
\[ 
\Theta_\lambda(h)(x)=\int_0^1\, \theta(x,y;\lambda)\,h(y)\, dy 
\]
Moreover, the operator-valued function
$\lambda\mapsto \Theta_\lambda$ has bounded variation over
each intervalÊ$\{a\leq \lambda\leq b\}$
when $0<a<b$.
It means that there exists a constant $C=C(a,b]$ such that
\[
\max\, \sum_{k=0}^M\, ||\Theta_{\lambda_{k+1}}-\Theta_{\lambda_k}||\leq C
\] 
for all partitions
$a=\lambda_0<\lambda_1<\ldots \lambda_{M+1}=b$ and
we have taken operator norms of the differences
$\Theta_{\lambda_{k+1}}-\Theta_{\lambda_k}$ in the sum above.
These bounded variations entail that one can compute the integrals in the right hand side
via the usual method  by Borel and Stieltjes.
\bigskip


\noindent
{\bf{The construction of  spectral functions.}}
When case I holds one constructs the $\rho$-function via a 
robust limit process.
Following [ibid:Chapitre 4] we expose this in ¤ xx.
The strategy is to
regard an approximating sequence $\{G_n\}$ of
Hilbert-Schmidt operator, i.e.
\[
 \iint_\square \, G_N(x,y)^2 \, dxdy<\infty
\]
hold for each $N$.
In this case $\{G_N\}$ are compact opertors.
With $N$ fixed
we get
a discrete sequence of non-zero real numbers
$\{\lambda\nu\}$
which are arragned with increasing avbsolute values and
an orthonormal  family of eigenfunctions $\{\phi_\nu^{(n)}\}$
where
\[
 G_N(\phi_\nu^{(N)})= \lambda\\nu\cdot \phi_\nu^{(N)}
 \] 
hold for each $\nu$.
Of course, the eigenvalues also depend on
$N$.
If $\lambda>0$ we set
\[
\rho_N(x,y;\lambda)=\sum_{0<\lambda_\nu<\lambda}\, \phi_\nu(x)\phi_\nu(y)
\]
\[
\rho_N(x,y;-\lambda)\sum_{-\lambda <\lambda_\nu<0}\, \phi_\nu(x)\phi_\nu(y)
\]
let us notice that for each fixed $n$, the $\lambda$-numbers in (x) stay
away from zero, i.e. there is a constant $c_N>0$ such that
$|\lambda_\nu\geq c_N$. So the function $\rho_N$
vanishes  in a neighborhood of zero.
The spectral theorem applied to symmetric Hilbert-Schmidt operators entails that
\[
\int_{-\infty}^\infty\, \frac{1}{\lambda}\cdot \frac{d}{d\lambda}\,
\rho_N(x,y;\lambda)\cdot h(y)\,  dy
\]
\medskip

\noindent
{\bf{The $\Omega$-kernels.}}
For each $N$ we introduce the function
\[
 \Omega_N(x,y;\lambda)=\int_a^x\int_a^y\, \rho_N(s,t;-\lambda)\, dsdt
\]
Let us notice that Bessel's inequality entails that
\[
 \bigl|\iint_\square\, \rho_N(x,y;\lambda)\cdot h(x)g(y)\, dxdy\bigr|\leq
 ||h||_2|cdot ||g|7_2
 \] 
 for each pair $h,g$ in $L^2[0,1]$.
 \medskip

\noindent
{\bf{Exercise.}}
Conclude from the above
that the variation of $\Omega$
over $[0,x]\times [0,y]$ is bounfed above by
\[
\sqrt{x\cdot y}
\] 
for every pair $0\leq x,y\leq 1$.
In partcular the functions
\[
(x,y)\mapsto \Omega(x,y;\lambda)
\]
are uniformly Hšlder continuous of order $1/2$
in $x$ and $y$ respectively.
\medskip


\noindent
Using the inequalities above
we elave it to the reader to check that there exists
at least one subsequence $\{N_k\}$ such that
the functions $\{\Omega_{N_k}(x,y;\lambda)$
converges uniformly with respect toÊ$x$ and $y$
while $\lambda$ stays in a bounded interval.
When Case I holds one proves that the limit is independent of the subsequence, i.e.
there exists a limit function
\[
\Omega(x,y;\lambda)=\lim_{N\to\infty}\,  
\Omega_N(x,y;\lambda)
\]
From the above the $\omega$-function is again uniformly Hšlder continuous
and
its first order partial derivatives are $L^2$-functions. Moreover, after the passage to
the limit one still
has Bessel's inequality which entails that
\[
\int_{-\infty}^\infty\, 
\frac{d}{d\lambda}\int_0^1 h(x)\cdot \bigl(\frac{\partial}{\partial x}
\int_0^1\, \frac{\partial\Omega(x,y;\lambda)}{\partial y}\cdot h(y))\,dy\bigr )\, dx
\leq \int_0^1\, h(x)^2\, dx
\]
for every $h\in L^2[0,1]$.
\medskip

\noindent
{\bf{Definition.}}
\emph{A Case 1 kernel $K(x,y)$ is closed if equality holds in (*).}
\medskip

\noindent
{\bf{Theorem.}} \emph{A Case I kernel $K(x,y)$ for which 
the equation}
\[ 
\int_0^1\, K(x,y)\cdot \phi(y)\ dy=0
 \] 
 \emph{has no non-zero $L^2$-solution $\phi$ is closed.}
\medskip

\noindent
{\bf{A representation  formula.}}
When (*) hols we can apply to to $h+g$ for every pair of
$L^2$-functiuons anbd since
the Hilbert space $L^2[0,1]$ is self-dual it follows that
for each $f\in L^2[0,1]$ one has the equality
\[
f(x)=\frac{d}{dx}\  
\int_{-\infty}^\infty\, 
\frac{d}{d\lambda}
\int_0^1\, \frac{\partial\Omega(x,y;\lambda)}{\partial y}\cdot f(y))\,dy
\]
almost everywhere with respect to $x$ on $[0,1]$.




{\bf{Remark.}} 
The 
formula (**) shows that it often is important to decide when a Case I kernel
is closed.
Theorem xx gives such a sufficent condition. However, it can
be extended to a quite geneeral result
where one for  can relax the passage to the limit via
suitable linear operators.
The reader may consult   [ibid; page 139-143]
for details. Here we are content to announce the conlsisive result ehich appear
in
[ibid;: page 142].
\medskip

\noindent
{\bf{The $\mathcal L$-family.}}
Let $\xi$ dentoe a paramter which in general depends on several variables, or
represents points in a manifold or  vectors in a normed linear space.
To each $\xi$ we are given  a linear operator
\[ 
L(\xi)\colon f\mapsto L(\xi)(f)
\]
from functions $f(x)$ on $[0,1]$ to new functions on $[0,1]$.
The linear map is weakly continuous, i.e. if
$\{f_\nu\}$ is a sequence in $L^2[0,1]$ which converges weakly to a init function $f$
in $L^2[0,1]$ then
\[ 
\lim L(\xi,f_\nu)\overset{w}\to L(\xi)(f)
\]
Next,
we are given $K(x,y)$ and
the second  condition for $L$ to be in  $\mathcal L$ is that
for each
pair  $\xi$ and $ 0\leq y\leq 1$ there exists
a constant $\gamma(\xi,y)$ which is independent of $\delta$ so that
\[
|L(\xi)(K_\delta(\cdot,y))(x)\leq  \gamma(\xi;y)
\]
where $K_\delta(x,y)$ is the truncated kernel function from (xx)
and in the left hand side we have applied $L(\xi$ to
the function $x\mapsto K_\delta(x,y)$ for each fixed $y$.
Moreover, we have
\[ 
\lim_{\delta\to 0}\, L(\xi)(K(\cdot,y))(x)\overset{w}\to 
\lim_{\delta\to 0}\, L(\xi)(K_\delta(\cdot,y))(x)
\]
where the convergence again holds weakly for
$L2$-functions on $[0,1]$.
Funally the equality below holds for every
$L^2$-function $\phi$:
\[
xxxx
\]








 
 













\bigskip

\centerline{\bf{Symmetric integral operators.}}
\bigskip


\noindent
Consider the domain $\square=\{0\leq x\leq 1\}\times\{0\leq y\leq 1\}$
in ${\bf{R}}^2$.
Let $K(x,y)$ be a real-vaued and Lebesgue mesure function on
$\square$ such that
the integrals
\[ 
\int_0^1\, K(x,y)^2\, dy<\infty
\]
for all $x$ outside a null-set on $[0,1]$.
In addition $K$ is symmetric,  i.e.$K(x,y)= K(y,x)$.
The $K$-kernel is bounded in Hilbert's sens if there exists a constant
$C$ such that
\[ 
\iint_\square\, K(x,y) u(x)u(y)\, dxdy\leq C^2\cdot\int_0^1\, u(x)^2\, dx
\]
for each $u\in L^2[0,1]$.
In the text-book |emph{Intyergralxxx}Ê[xxxx 1904],
Hilbert proved that
the linear operator on 
$L^2[0,1]$ defined by
\[ 
\mathcal K(u)(x)=\int_0^1\, K(x,y)u(y) dy
\]
is bounded and its operator norm is majorsied by $C$-Moreover
the spectrum is real and contained in $[-C,C]$ and
just as for symmetric real matrices
there exists a spectral resolution.
More precisely, set $\mathcal H= L^2[0,1]$.
Then there exists a
map
from $\mathcal H\times\mathcal H$
to the space of Riesz measures supported by
$[-C,C]$ which to every pair $u$ and $v$ in
$\mathcal H$ assigns a Riesz measure $\mu_{\{u,v\}}$
and $\mathcal K$ is recovered by the equation:
\[
\langle \mathcal K(u),v\rangle=\int_{-C}^C\,  t\cdot d\mu_{\{u,v\}}(t)
\]
where the left hand side
is the inner product
on the complex Hilbert space defined by
\[
\iint\, \mathcal K(u)(x)\cdot \overline{v}(x)\,dx
\]
In the monograph [Carelan 1923]
the condition (*) is imposed while (**) need not be valid.
Then we encounter an unbounded operator.
But notice that if
$u|in\mathcal H$ then (*9 and the CuachySchwarz inequality entails that
the functions
\[ 
y\mapsto K(x,y)u(y)
\] 
are absolutely integrable in Lebegue's sense 
for all $x$ outside the nullset $\mathcal N$ above.
Hence it makes sense to refer to $L^2$-functions $\phi$ on $[0,1]$
which
satisfy an eigenvalue equation
\[
\phi(x)= \lambda\cdot \int_0^1\, K(x,y)\phi(y)\, dy\tag{1}
\]
where $\lambda$ is a compkex number.
one is also led to consider the integral equation
\[
\phi(x)= \lambda\cdot \int_0^1\, K(x,y)\phi(y)\, dy+f(x)\tag{2}
\]
where $f\in\mathcal H$ is given and one seeks $\phi$.
It turns out that if $\mathfrak{Im}(\lambda)\neq 0$,
then the  inhomogenous equation 
(2) has at least one solution. 
Next,  consider the equation (1).
Let $\rho(\lambda)$ denote the number of linearly independent 
solution in (1). Carelan proived that
 the  $\rho$-function is constant 
when  $\lambda$ varies in
${\bf{C}}\setminus {\bf{R}}$.
Follwing Carelan one says that the kernel $(x,y)$ gives an operator $\mathcal K$ of Class I if
the $\rho$-function is zero. It means that
(2) has unique solutions
for every pair $\lambda,f)$
when $\lambda$ are non-real.
\medskip


\noindent
{\bf{A limit process.}}
Let $\{G_n(x,y)\}$ be a sequece of
symmetric kernel functions which are bounded in Hilbert's sense and
approximate $K$ in the sense that
\[
\lim_{n\to \infty} \int_0^1\, |K(x,y)-G_n(x,y)|^2\, dy=0
\]
for all $x$ outside
a null set. Fix some non-real $\lambda$.
Hilbert's theory entials that if
$f(x)$ is a continuous function, in general complex-valued, then
we find unqiue continuous functions $\{\phi_n\}$
which satisfy the integral equations
\[
\phi_n(x)= \lambda\cdot \int_0^1\, G_n(x,y)\phi(y)\, dy\tag{1}
\]
For a fixed $x$ we consider the complex numbers
$\{phi_n(x)\}$.
Now there exists the set $Z(x)$ of all cluster points, i.e.
a complex number
$z$ belongs to $Z(x)$ if there exists some
sequence $1\leq n_1<n_2<\ldots$ such that
\[
 z=\lim_{k\to\infty}\, \phi_{n_k}(x)
\]
\medskip

\noindent
{\bf{Theorem.}} \emph{For every approximating sequence $\{G_n\}$ as above
the sets $Z(x)$ are either reduced to points or circles in
the complex plane. Moreover, each $Z(x)$ is reduced to a siungleton set
when $\mathcal K$ is of class I.}
\medskip

\noindent
{\bf{Remark.}}
The result below was discovered by Weyl for some special unbounded operators
which arise during the study of second order
differential equations. See ¤ for a comment-.
If $\mathcal K$  is of Class I then
the theorem sbove shows that
each pair of a on-real $\lambda$
and some $f\in\mathcal H$ gives
a unique function $\phi(x)$
which satsfies (2) and
it can be found via a pointwise limit of solutions
$\{\phi_n\}$ to the equations (xx). In this sense the limit process
is robust because one can emply an arbitrary approximating
sequence $\{G_n\}$ under the sole condition that (xx) holds.
This already indficartes that the Case I leads to
a "consistent theory" even if $\mathcal K$ is unbounded.
To make this precise Carleman constructed a unique spectral function
when Case I holds.
More preciely, if
$K(x,y)$ is symmetric and 
Case I holds, then there exists a unique function
$\rho(x,y;\lambda)$ defined for
$(x,y)\in\square$ and every real $\lambda$ such that
\[
\mathcal K(h)(x)=\int_{-\infty}^\infty\, 
\,\frac{1}{\lambda}\cdot\frac{d}{d\lambda} \,
\int_0^1\, \theta(x,y;\lambda)\,h(y)\, dy
\] 
for all
$L^2$-functions $h$.
Concerning the spectral $\theta$-function, Carleman proved that  it
enjoys the same properties as Hilbert's spectral function for bounded 
operators.


\medskip

\noindent
{\bf{Remark.}}
For each fixed $\lambda>0$
one has a bounded self-adjoint operator
on $\mathcal H$ defined by
\[ 
\Theta_\lambda(h)(x)=\int_0^1\, \theta(x,y;\lambda)\,h(y)\, dy 
\]
Moreover, the operator-valued function
$\lambda\mapsto \Theta_\lambda$ has bounded variation over
each intervalÊ$\{a\leq \lambda\leq b\}$
when $0<a<b$.
It means that there exists a constant $C=C(a,b]$ such that
\[
\max\, \sum_{k=0}^M\, ||\Theta_{\lambda_{k+1}}-\Theta_{\lambda_k}||\leq C
\] 
for all partitions
$a=\lambda_0<\lambda_1<\ldots \lambda_{M+1}=b$ and
we have taken operator norms of the differences
$\Theta_{\lambda_{k+1}}-\Theta_{\lambda_k}$ in the sum above.
These bounded variations entail that one can compute the integrals in the right hand side
via the usual method  by Borel and Stieltjes.
\bigskip


\noindent
{\bf{The construction of  spectral functions.}}
When case I holds one constructs the $\rho$-function via a 
robust limit process.
Following [ibid:Chapitre 4] we expose this in ¤ xx.
The strategy is to
regard an approximating sequence $\{G_n\}$ of
Hilbert-Schmidt operator, i.e.
\[
 \iint_\square \, G_N(x,y)^2 \, dxdy<\infty
\]
hold for each $N$.
In this case $\{G_N\}$ are compact opertors.
With $N$ fixed
we get
a discrete sequence of non-zero real numbers
$\{\lambda\nu\}$
which are arragned with increasing avbsolute values and
an orthonormal  family of eigenfunctions $\{\phi_\nu^{(n)}\}$
where
\[
 G_N(\phi_\nu^{(N)})= \lambda\\nu\cdot \phi_\nu^{(N)}
 \] 
hold for each $\nu$.
Of course, the eigenvalues also depend on
$N$.
If $\lambda>0$ we set
\[
\rho_N(x,y;\lambda)=\sum_{0<\lambda_\nu<\lambda}\, \phi_\nu(x)\phi_\nu(y)
\]
\[
\rho_N(x,y;-\lambda)\sum_{-\lambda <\lambda_\nu<0}\, \phi_\nu(x)\phi_\nu(y)
\]
let us notice that for each fixed $n$, the $\lambda$-numbers in (x) stay
away from zero, i.e. there is a constant $c_N>0$ such that
$|\lambda_\nu\geq c_N$. So the function $\rho_N$
vanishes  in a neighborhood of zero.
The spectral theorem applied to symmetric Hilbert-Schmidt operators entails that
\[
\int_{-\infty}^\infty\, \frac{1}{\lambda}\cdot \frac{d}{d\lambda}\,
\rho_N(x,y;\lambda)\cdot h(y)\,  dy
\]
\medskip

\noindent
{\bf{The $\Omega$-kernels.}}
For each $N$ we introduce the function
\[
 \Omega_N(x,y;\lambda)=\int_a^x\int_a^y\, \rho_N(s,t;-\lambda)\, dsdt
\]
Let us notice that Bessel's inequality entails that
\[
 \bigl|\iint_\square\, \rho_N(x,y;\lambda)\cdot h(x)g(y)\, dxdy\bigr|\leq
 ||h||_2|cdot ||g|7_2
 \] 
 for each pair $h,g$ in $L^2[0,1]$.
 \medskip

\noindent
{\bf{Exercise.}}
Conclude from the above
that the variation of $\Omega$
over $[0,x]\times [0,y]$ is bounfed above by
\[
\sqrt{x\cdot y}
\] 
for every pair $0\leq x,y\leq 1$.
In partcular the functions
\[
(x,y)\mapsto \Omega(x,y;\lambda)
\]
are uniformly Hšlder continuous of order $1/2$
in $x$ and $y$ respectively.
\medskip


\noindent
Using the inequalities above
we elave it to the reader to check that there exists
at least one subsequence $\{N_k\}$ such that
the functions $\{\Omega_{N_k}(x,y;\lambda)$
converges uniformly with respect toÊ$x$ and $y$
while $\lambda$ stays in a bounded interval.
When Case I holds one proves that the limit is independent of the subsequence, i.e.
there exists a limit function
\[
\Omega(x,y;\lambda)=\lim_{N\to\infty}\,  
\Omega_N(x,y;\lambda)
\]
From the above the $\omega$-function is again uniformly Hšlder continuous
and
its first order partial derivatives are $L^2$-functions. Moreover, after the passage to
the limit one still
has Bessel's inequality which entails that
\[
\int_{-\infty}^\infty\, 
\frac{d}{d\lambda}\int_0^1 h(x)\cdot \bigl(\frac{\partial}{\partial x}
\int_0^1\, \frac{\partial\Omega(x,y;\lambda)}{\partial y}\cdot h(y))\,dy\bigr )\, dx
\leq \int_0^1\, h(x)^2\, dx
\]
for every $h\in L^2[0,1]$.
\medskip

\noindent
{\bf{Definition.}}
\emph{A Case 1 kernel $K(x,y)$ is closed if equality holds in (*).}
\medskip

\noindent
{\bf{Theorem.}} \emph{A Case I kernel $K(x,y)$ for which 
the equation}
\[ 
\int_0^1\, K(x,y)\cdot \phi(y)\ dy=0
 \] 
 \emph{has no non-zero $L^2$-solution $\phi$ is closed.}
\medskip

\noindent
{\bf{A representation  formula.}}
When (*) hols we can apply to to $h+g$ for every pair of
$L^2$-functiuons anbd since
the Hilbert space $L^2[0,1]$ is self-dual it follows that
for each $f\in L^2[0,1]$ one has the equality
\[
f(x)=\frac{d}{dx}\  
\int_{-\infty}^\infty\, 
\frac{d}{d\lambda}
\int_0^1\, \frac{\partial\Omega(x,y;\lambda)}{\partial y}\cdot f(y))\,dy
\]
almost everywhere with respect to $x$ on $[0,1]$.




{\bf{Remark.}} 
The 
formula (**) shows that it often is important to decide when a Case I kernel
is closed.
Theorem xx gives such a sufficent condition. However, it can
be extended to a quite geneeral result
where one for  can relax the passage to the limit via
suitable linear operators.
The reader may consult   [ibid; page 139-143]
for details. Here we are content to announce the conlsisive result ehich appear
in
[ibid;: page 142].
\medskip

\noindent
{\bf{The $\mathcal L$-family.}}
Let $\xi$ dentoe a paramter which in general depends on several variables, or
represents points in a manifold or  vectors in a normed linear space.
To each $\xi$ we are given  a linear operator
\[ 
L(\xi)\colon f\mapsto L(\xi)(f)
\]
from functions $f(x)$ on $[0,1]$ to new functions on $[0,1]$.
The linear map is weakly continuous, i.e. if
$\{f_\nu\}$ is a sequence in $L^2[0,1]$ which converges weakly to a init function $f$
in $L^2[0,1]$ then
\[ 
\lim L(\xi,f_\nu)\overset{w}\to L(\xi)(f)
\]
Next,
we are given $K(x,y)$ and
the second  condition for $L$ to be in  $\mathcal L$ is that
for each
pair  $\xi$ and $ 0\leq y\leq 1$ there exists
a constant $\gamma(\xi,y)$ which is independent of $\delta$ so that
\[
|L(\xi)(K_\delta(\cdot,y))(x)\leq  \gamma(\xi;y)
\]
where $K_\delta(x,y)$ is the truncated kernel function from (xx)
and in the left hand side we have applied $L(\xi$ to
the function $x\mapsto K_\delta(x,y)$ for each fixed $y$.
Moreover, we have
\[ 
\lim_{\delta\to 0}\, L(\xi)(K(\cdot,y))(x)\overset{w}\to 
\lim_{\delta\to 0}\, L(\xi)(K_\delta(\cdot,y))(x)
\]
where the convergence again holds weakly for
$L2$-functions on $[0,1]$.
Funally the equality below holds for every
$L^2$-function $\phi$:
\[
xxxx
\]








 
 
































































 



























\newpage







\centerline {\bf{11.5 Stones theorem.}}


\bigskip


\noindent

\noindent
{\bf{11.3.2 Unitary semi-groups.}}
Specialize the situation above to the case when
$B$ is a Hilbert space $\mathcal H$ and
$\{U_t\}$ are unitary
operators.
Set $T=\xi_*$ so that
\[ 
B(x)=
\lim_{t \to 0}\, \frac{U_tx-x}{t}\quad\colon\quad x\in\mathcal D(T)
\]
If  $x,y$ is a pair in $\mathcal D(B)$ we get
\[
\langle Bx,y\rangle=
\lim_{t \to 0}\, \langle \frac{U_tx- x}{t},U_ty\rangle
=\lim_{t \to 0}\, \frac{1}{t}\cdot \bigl( \langle U_tx,U_ty)\rangle-
 \langle x,U_ty)\rangle\,\bigr)
 \]
Since $U_t$ are unitary we have
$\langle U_tx,U_ty)\rangle=\langle x,y)\rangle$ for each$Êt$ and conclude that
the last term above  is equal to
\[
\lim_{t \to 0}\, \frac{\langle x,y-U_ty\rangle}{t}=-\langle x,By\rangle
\]

\noindent
Hence $B$ is anti-symmetric, i.e.
\[
\langle Bx,y\rangle=-
\langle x,By\rangle
\]
Set $A=i\cdot T$ which gives
\[
\langle Ax,y\rangle=
i\cdot \langle Tx,y\rangle=
-i\cdot \langle x,Ty\rangle=-\langle x,i\cdot Ty\rangle=
\langle x,Ay\rangle
\]
where  we used that the inner product is hermitian.
Hence $A$ is a densely defined and symmetric operator.
\medskip

\noindent
{\bf{Theorem.}}
\emph{A is self-adjoint, i.e. one has the equality $\mathcal D(A)= \mathcal D(A^*)$.}
\medskip

\noindent
\emph{Proof.}
It suffices to prove that
$\mathcal D(T)=|mathcal D(T^*)$. To btain this we take a vector
$y$ be a vector in $\mathcal D(T^*)$ which by definition gives
a constant $C(y)$ such that
\[
|\langle Tx,y\rangle||\leq C(y)\cdot ||x||
\quad\colon\, x\in\mathcal D(T)\tag{i}
\]
Now
$\langle Tx,y\rangle$ is equal to
\[
\lim_{t\to 0}\,\langle\frac{U_tx-x}{t}, U_ty\rangle
=-\lim_{t\to 0}\,\langle x,\frac{U_ty-y}{t}\rangle\tag{ii}
\]
So if
\[
 \eta_t=frac{U_ty-y}{t}
\]
it follows that there exists
\[
\lim_{t\to 0}\, ,\langle x,\eta_t\rangle=-\langle Tx,y\rangle
\]
for each $x\in\mathcal D(T)$.





\bigskip



The adjoint operators
$\{U^*_t\}$   give another  unitary semi-group with
infinitesmal generator  
$A_*$ where
\[ 
A_* (x)=
\lim_{t \to 0}\, \frac{U^*_tx-x}{t}\quad\colon\quad x\in\mathcal D(A_*)
\]
Since $U_t$ is the inverse operator of $U^*_t$ for each $t$ we get
\[
A_*(x)= \lim_{t\to 0}\, U_t(A_* x)= \lim_{t \to 0}\, \frac{x-U_t x}{t}\quad\colon\quad x\in\mathcal D(A_*)\tag{i}
\]
\medskip

\noindent
From (i) we see that
$\mathcal D(A)\subset
\mathcal D(A_*)$ and
one has the equation
\[
A_* x)=-A(x)\quad\colon\quad x\in\mathcal D(A_*)\tag{ii}
\]
Reversing the role the reader can check the equality
\[
\mathcal D(A)=
\mathcal D(A_*)\tag{iii}
\]
Next, let $x,y$ be a pair in $\mathcal D(A)$.
Then
\[
\langle Ax,y\rangle=
\lim_{t \to 0}\, \langle \frac{U_tx- x}{t},U_ty\rangle
=\lim_{t \to 0}\, \frac{1}{t}\cdot \bigl( \langle U_tx,U_ty)\rangle-
 \langle x,U_ty)\rangle\,\bigr)
 \]
Since $U_t$ are unitary we have
$\langle U_tx,U_ty)\rangle=\langle x,y)\rangle$ for each$Êt$ and conclude that
the last term in (xx) is equal to
\[
\lim_{t \to 0}\, \frac{\langle x,y-U_ty\rangle}{t}=-\langle x,Ay\rangle
\]

\noindent
Hence $A$ is anti-symmetric.
Set
\[ 
B=iA
\]

\bigskip









{\bf{Exercise.}}
Show that (i)  gives the equality
$\mathcal D(A_*)=\mathcal D(A)$ and that:
\[
 A_*(x)=-A(x)\quad\colon\quad x\in\mathcal D(A)
 \]
 
 

\[
 \langle Bx,y\rangle= -\langle x,By\rangle\quad\colon\quad
x,y\in\mathcal D(B)
\]


\noindent {\bf{Exercise.}}
Conclude from the above that the operator $iB$ is self-adjoint.

\medskip


\noindent
{\bf{Remark.}} The equations  above constitute Stones theorem
which was established in 1930.
It has a wide range of applications. See for example von Neumann's article \emph{Zur Operatorenmethode in der klassischen Mekanik}
and Maeda's article \emph{Unitary equivalence of self-adjoint
operators and constant motion}
from 1936.
\bigskip


\noindent
{\bf{11.3.3 A converse construction.}}
Let $A$ be a densely defined self-adjoint operator.
From ¤ 9.B  $A$ is approximated by a sequence of bounded
self-adjoint operators
$\{A_N\}$.
With $N$ kept fixed
we get a semi-group of unitary operators where
\[ 
U^{(N)}_t= e^{-it A_N}
\]
The reader may verify that the inifintesmal generator becomes
$-iA_N$.
Next, for each $x\in \mathcal D(A)$
and every fixed $t$ there exists the limit
\[ 
\lim_{N\to \infty}\, U^{(N)}_t(x)
\]
{\bf{Remark.}} This gives a densely defined linear operator $U_t$
whose operator norm is bounded by one which therefore
extends uniquely to 
a bounded linear operator $\mathcal H$ and it is clear
that this  extension 
becomes a unitary operator. In this way
we arrive at a semi-group $\{U_t\}$
and one verifies that its infinitesmal generator is equal to $-iA$.
However, it is not clear that
$\{U_t\}$ is strongly continuous and one may ask for 
conditions 
on the given self-adjoint operator $A$ which ensures that  $\{U_t\}$
is strongly continuous.








\newpage

\centerline{\bf{11.8 Transition probability functions.}}
\medskip


\noindent
Let $(\Omega,\mathcal B,\mu)$
be a probability space as defined in ¤ XX.
Consider a real-valued function
$P$ defined on the product set 
$\Omega\times\mathcal B$ with 
the following two properties:
\[ 
t\mapsto P(t,E)
\quad\text{is a bounded measurable function for each}\,\,\, E\in\mathcal B\tag{*}
\]
\[
E\mapsto P(t,E)
\quad\text{is a probability measure
for each fixed }\,\,\, t\in\Omega\tag{**}
\]
When (*-**) hold one refers to $P$ as a transition function.
Given  $P$ we define inductively the sequence $\{P^{(n)}\}$
by:
\[ 
P^{(n+1)}(t,E)=\int_\Omega\, P^{(n)}(s)\cdot dP(s,E)
\]
It is clear that 
$\{P^{(n)}\}$ yield  new transition  functions.
The probabilistic interpretation is that
one has a Markov chain
with independent increments.
More precisely,
if 
$E$ and $S$ are two sets in
$\mathcal B$ 
and 
$n\geq 1$.
then
\[
\int_S\, P^{(n)}(t;E)\cdot d\mu(t)
\]
is the probability that
the random walk which starts at some  point in $E$
has arrived to some  point in  $S$ after $n$ steps.
One says that the given
transition function $P$ yields a stationary
Markov process if
there exists a finite family of disjoint
subets $E_1,\ldots,E_m$ in $\mathcal B$
and some $\alpha<1$ and a constant $M$
such that the following hold:
First, for each $1\leq i\leq m$ one has:
\[ 
P(t,E_i)= 1 \quad\colon t\in E_i\tag{1}
\]
Next, if $\Delta= \Omega\setminus E_1\cup\ldots\cup E_m$ then
\[ 
\sup_{t\in S}\, P^{(n)}(t,\Delta)\leq M\cdot \alpha^n
\quad\colon \, n=1,2,\ldots\tag{2}
\]
\medskip

\noindent
{\bf{Remark.}}
One refers to $\Delta$ as the disippative part of $\Omega$
and $\{E_i\}$ are  the ergodic kernels of the process.
Since $\alpha<1$  in (2) the probabilistic  interpretation
of (2) is that as $n$ increase then
the disippative part is evacuated
with high probability while the Markov process 
stays inside every ergodic kernel.

\medskip


\centerline {\bf{11.9 The Kakutani-Yosida theorem.}}
\medskip

\noindent
A sufficient condition for a
Markov  process to be  stationary is as follows:
Denote by $X$ the Banach space of
complex-valued and bounded
$\mathcal B$-measurable
functions on the real $s$-line.
Now $P$ gives a 
linear operator $T$ which sends $f\in X$
to
the function
\[ 
T(f)(x)= \int_\Omega\ f(s)\cdot dPx,ds)
\]
Kakutani and Yosida  proved that 
the Markov process is stationary 
if there exists a 
triple $\alpha,n,K$
where $K$ is a compact
operator on $X$, $0<\alpha<1$ and $n$ some positive integer such that
the operator  norm
\[ 
||T+K||\leq \alpha\tag{*}
\]

\noindent
The proof relies upon some  general facts 
about
linear operators on Banach spaces.
First one identifies the Banach space
$X$ with
the space of continuous complex-valued functions on
the compact Hausdorff space $S$ given by the maximal ideal space of the
commutative Banach algebra $X$.
Then $T$ is a postive linear operator on $C^0(S)$ and in ¤ 11.xx    we
shall prove  that (*)
implies that
 the spectrum of $T$ consists of a finite set of points on
 the unit circle together with a compact subset
 in a disc of radius $<1$.
 Moreover, for each
 isolated point $e^{i\theta}\in \sigma(T)$
 the corresponding eigenspace is finite dimensional.
 Each  such eigenvalue corresponds to an ergodic kernel and when
the eigenspace has dimension $m\geq 2$, the
 corresponding ergodic kernel, say $E_1$, has a further decomposition into
 pairwise disjoint subsets $e_1,\ldots,e_m$
where  the process moves in a cyclic manner between these
sets, i.e. 
\[
\int_{e_{i+1}}\, P(s,e_i)=1\quad 
\colon 1\leq  i\leq m
\quad\text{where we put}\quad
 e_{m+1}= e_1
 \]
 

\medskip



\centerline {\bf{11.9.1 Some results about linear operators.}}
\medskip


\noindent 
The  Kakutani-Yosida  theorem  follows from 
some results about linear operators which we begin to expose.
Let $X$ be a Banach space and
denote by $\mathcal F$
the family of bounded liner operators  $T$ on $X$  
such that
\[ 
\lim_{n\to\infty}\, \frac{1}{n}\cdot x^*(T^nx)=0\tag{*}
\] 
hold for all pairs $x\in X$ and $x^*\in X^*$.
\medskip


\noindent
{\bf{1. Exercise.}} Apply the Banach-Steinhaus theorem to show that
if $T\in\mathcal F$ then
there exists a constant $M$ such that the operator norms satisfy
\[ 
||T^n||\leq M\cdot n\quad\colon\, n=1,2,\ldots
\]


\noindent
Since the $n$:th root of $M\cdot n$ tends to one as $n\to+\infty$, 
the spectral radius formula entails that
the spectrum $\sigma(T)$ is contained in the closed unit disc
of the complex $\lambda$-plane.
So in the exterior disc
$\{|\lambda|>1\}$ there exists the
the resolvent 
\[ 
R_T(\lambda)= (\lambda\cdot E-T)^{-1}
\]



\noindent{\bf{2. The class $\mathcal F_*$}}.
It consists of those $T$ in $\mathcal F$
for which there exists
some $\alpha<1$ such that
$R_T(\lambda)$ extends to a meromorphic function in
the exterior disc
$\{|\lambda|>\alpha\}$.
Since $\sigma(T)\subset
\{|\lambda|\leq 1\}$
it follows that when
$T\in\mathcal F_*$ then
the set of points in $\sigma(T)$ which belongs to the unit circle
in the complex $\lambda$-plane is empty or finite and
after we can always choose $\alpha<1$ such that
\[ 
\sigma(T)\cap \{\alpha<|\lambda|<1\}= \emptyset
\]

\medskip

\noindent
{\bf{3. Proposition.}}
\emph{If $T\in \mathcal F_*$ andÊ$e^{i\theta}\in \sigma(T)$
for some $\theta$, then
$R_T(\lambda)$ 
has a simple pole at $e^{i\theta}$.}
 \medskip

\noindent
\emph{Proof.}
Replacing
$T$ by  $e^{-i\theta}\cdot T$
it suffices to prove the result when
$e^{i\theta}=1$.
If $R_T(\lambda)$ has a pole of order $\geq 2$
at $\lambda=1 $ we know from ¤ XX that there exists $x\in X$ such that
\[ 
Tx\neq  x\quad\text{and}\quad
(E-T)^2\,x=0\tag{i}
\]
The last equation means that $T^2+x=2Tx$ and an induction
over $n$ gives
\[
\frac{1}{n} \cdot T^n x=\frac{1}{n}\cdot x+(E-T)x\tag{ii}
\]
Since $T\in\mathcal F$ we have
\[ 
\lim_{n\to\infty}\, \frac{1}{n}\cdot x^*( T^n x)=0
\quad\colon\, \forall\\, x^*\in X^*\tag{iii}
\] 
Then (ii) entails that $x^*(E-T)(x)=0$. Since
$x^*$ is arbitrary we get  $Tx=x$ which contradicts (i) and hence
the pole is simple.
\medskip

\noindent
{\bf{4. Theorem.}}
\emph{Let $T\in \mathcal F$ be such that   there exists a compact
operator $K$ where 
$||T+K||<1$. Then $T\in \mathcal F_*$ and
for every $e^{i\theta}\in\sigma(T)$
the eigenspace
$E_T(\theta)= \{ x\in X\,\colon\, Tx= e^{i\theta} x\}$ is finite dimensional.}

\medskip

\noindent
\emph{Proof.}
Set $S=T+K$ and for a complex number
$\lambda$ we write 
$\lambda\cdot E-T= \lambda\cdot E-T-K+K$. Outside $\sigma(S)$ we get
\[
R_S(\lambda)(\lambda\cdot E-T)=
E+R_S(\lambda)\cdot K\tag{i}
\]
The Neumann series for large absolute values
$|\lambda|$
applied to $R_S(\lambda)$ gives some $\rho>0$ and
\[
( E+R_S(\lambda)\cdot K)^{-1}= E+R_S(\lambda)\cdot K\dot
( E+R_S(\lambda)\cdot K)^{-1}\quad\colon\,|\lambda|>\rho\tag{ii}
\]

\noindent
Next, when
$|\lambda|$ is large
we notice that
(i) gives
\[
R_T(\lambda)=  ( E+R_S(\lambda)\cdot K)^{-1}\cdot R_S(\lambda)\tag{iii}
\]
Together with (ii) we obtain
\[
R_T(\lambda)=R_S(\lambda)+ 
R_S(\lambda)\cdot 
( E+R_S(\lambda)\cdot K)^{-1}\cdot R_S(\lambda)\tag{iv}
\]
Set $\alpha=||S||$ which by assumption is $<1$.
Now
$R_S(\lambda)$ is analytic in the exterior disc
$\{\lambda|>\alpha\}$ so in this exterior disc
$R_\lambda(T)$ differs from  the analytic function $R_\lambda(S)$ by
\[
\lambda\mapsto R_S(\lambda)\cdot 
( E+R_S(\lambda)\cdot K)^{-1}\cdot R_S(\lambda)\tag{v}
\]
Here $K$ is a compact operator so 
the
result in ¤ XX entails that this function extends to
be meromorphic  in $\{|\lambda|>\alpha\}$.
There remains to prove that
eigenspaces at spectral points on the unit circle are finite dimensional.
To prove this we use (iv). 
Let $e^{i\theta}\in\sigma(T)$. By Proposition 3 it is a simple pole
so we have a Laurent series expansion
\[
R_T(e^{i\theta}+z)= \frac{A_{-1}}{z}+ A_0+ A_1z+\ldots
\]
By the general results from ¤¤ there remains to show that 
$A_{-1}$ has finite dimensional range.
To see this we apply (iv) which gives the equation
\[
R_S(e^{i\theta}+z)+
R_S(e^{i\theta}+z)\cdot(E+
R_S(e^{i\theta}+z)\cdot K)^{-1}\cdot R_S(e^{i\theta}+z)
\]
To simplify notations we set $B(z)=R_S(e^{i\theta}+z)$
which by assumption is analytic in a neighborhood of $z=0$.
Moreover, the operator $B(0)$ is invertible.
So now one has
\[
 \frac{A_{-1}}{z}+ A_0+ A_1z+\ldots=
 B(z)+B(z)(E+B(z)\cdot K)^{-1}B(z)
 \]
Since $B(0)$ is invertible  we  have a Laurent series expansion
\[
(E+B(z)\cdot K)^{-1}= \frac{A^*_{-1}}{z}+A_0^*+A_1^*z+\ldots
\]
and identying the coefficient of $z^{-1}$ gives
\[
A_{-1}= B(0)A^*_{-1}B(0)
\]
Next, from (xx) one has

\[
E=(E+B(z)\cdot K)(\frac{A^*_{-1}}{z}+A_0^*+A_1^*z+\ldots)\implies
(E +B(0)\cdot K)A^*_{-1}=0
\]
Here $B(0)\cdot K$ is a compact operator and hence  Fredholm theory 
implies that $A^*_{-1}$ has a finite dimensional range. Since
$B(0)$ is invertible the same is true for $A_{-1}$ which finishes the proof
of 
Theorem 4.




\medskip

\noindent
{\bf{5. Proposition}}.
\emph{
If
$T\in\mathcal F$ is  such that
$T^N\in\mathcal F_*$ for some integer $N\geq 2$.
Then 
$T\in\mathcal F_*$.}
\medskip

\noindent
\emph{Proof.}
We have the algebraic equation
\[ 
\lambda^N\cdot E -T^N=(\lambda\cdot E-T)(
\lambda^{N-1}\cdot E+
\lambda^{N-2}\cdot T+\ldots+T^{N_1})
\]
It follows that
\[ R_T(\lambda)=
(\lambda^{N-1}\cdot E+
\lambda^{N-2}\cdot T+\ldots+T^{N_1})\cdot R_{T^N}(\lambda^N)
\]
Since $T^NB\in\mathcal F_*$ there exists
$\alpha<1$ such that
\[
\lambda\mapsto  R_{T^N}(\lambda^N)
\]
extends to be meromorphic in
$\{|\lambda|>\alpha\}$. At the same time
$(\lambda^{N-1}\cdot E+
\lambda^{N-2}\cdot T+\ldots+T^{N_1})$
is  a polynomial
and hence
$R_T(\lambda)$ also extends to be meromorphic
in this
exterior disc so that 
$T\in\mathcal F_*$.
\medskip

\centerline{\emph{A result about  positive operators.}}

\bigskip

\noindent
Let $S$ be a compact Hausdorff
space and $X$ is the Banach space of continuous and
complex-valued functions on $S$.
A linear operator $T$ on $X$ is  positive if
it sends every non-negative and real-valued function $f$ to another  real-valued and
non-negative function.
\medskip

\noindent
{\bf{6. Theorem.}}
\emph{If $T$ is positive and belongs to $\mathcal F_*$
then
each $e^{i\theta}\in \sigma(T)$ is a root of unity.}
\medskip

\noindent
\emph{Proof.}
The hypothesis gives   $f\in C^0(S)$ which is not identically zero and
\[ 
T(f)=e^{i\theta}\cdot f
\]
Multiplying $f$ with a complex scalar we may assume that
the maximum norm on $S$ is one and there exists $s_0\in S$ such that
\[ 
f(s_0)=1
\]
The dual space
$X^*$ consists of complex-valued Riesz measures on $X$.
If $n\geq 1$ we get the
measure
$\mu_n$
such that
the following hold 
for every  $g\in C^0(S)$:
\[
\int_S\, g\cdot d\mu_n=T^n g(s_0)\geq 0
\]
Since $T^n$ is positive
the integrals in the left hand side are
$\geq 0$ when $g$ are real-valued and non-negative. This
entails that
each $\mu_n$ is a real-valued and non-negative measure.
Next, for each $n$ we put
\[ 
A_n=\{e^{-in\theta}\cdot f\neq 1\}=\{\mathfrak{Re}(e^{-in\theta}f)<1\}\tag{6.0}
\]
where the last equality follows since
the sup-norm of $f$ is one.
Now
\[
0=f(s_0)- e^{-in\theta}\cdot T^n f(s_0)
=\int_S\,[1-e^{-in\theta}f(s)]\cdot  d\mu_n(s)\tag{6.1}
\]
Taking real parts we get
\[
0=\int_S\,[1-\mathfrak{Re}(e^{-in\theta}f(s))]\cdot  d\mu_n(s)
\]
By (6.0)  the integrand above
is non-negative and since the whole 
integral is zero it follows that
\[
\mu_n(A_n)= \mu_n(\{\mathfrak{Re}(e^{-in\theta}<1\}=0\tag{6.2}
\]
Hence (6.2) 
$A_n$ is a null set with respect to $\mu_n$.
Suppose now that
there exists a pair $n\neq m$ such that
\[
(S\setminus A_n)\cap (S_m\setminus A_m)\neq \emptyset
\] 
A point $s_*$ in this non-empty intersection
gives
\[
1=e^{in\theta}f(s_*)=e^{im\theta}\cdot f(s_*)\implies
e^{in\theta}=e^{im\theta}
\] 
and hence  $e^{i\theta}$ is a root of unity since
$m-n\neq 0$.
So the proof of Theorem 6.1  is finished if we have established the following

\medskip

\noindent
\emph{Sublemma.}
\emph{The sets $\{S\setminus A_n\}$ cannot be pairwise disjoint.}
\medskip

\noindent
\emph{Proof.}
First,  $f$ has maximum norm
and by the above:
\[ 
\int_S\, f\cdot d\mu_n=e^{in\theta}
\]
Hence the total mass $\mu_n(S)$ is at least one.
Next, 
for each $n\geq 2$ we set
\[
\pi_n=\frac{1}{n}\cdot (\mu_1+\ldots+\mu_n)
\]
Since 
$\mu_n(S)\geq 1$  for each $n$ we get 
$\pi_n(S)\geq 1$. Put
\[
\mathcal A=\bigcap\, A_n
\]
Above we proved that $\mu_n(A_n)=0$ hold for every $n$ which gives
\[ 
\pi_n(\mathcal A)=0\quad\colon\, n=1,2,\ldots\tag{*}
\]
Next, when
the sets $\{S\setminus A_k\}$ 
are pairwise disjoint one has 
the inclusions
\[
S\setminus A_k\subset A_\nu\quad\forall\,\nu\neq k
\]
Keeping $k$ fixed it follows that
$\pi_\nu(S\setminus A_k)=0$ for every $\nu\geq 0$.
So when $n$ is large while $k$ is kept fixed we obtain
\[ 
\pi_n(S\setminus A_k))= \frac{1}{n}\cdot \mu_k(S\setminus A_k))\implies
\lim_{n\to\infty}\, \pi_n(S\setminus A_k))=0
\quad\colon k=1,2,\ldots\tag{**}
\]
At this stage we use the hypothesis that
$T$ belongs to $\mathcal F_*$
which by Proposition XX entails that
the resolvent $R_T(\lambda)$ has at most a simple pole at $\lambda=1$.
With $\epsilon>0$
the Neumann series expansion gives
\[
E+\sum_{k=1}^\infty\,
\frac {T^k}{(1+\epsilon)^k}=
R_T(1+\epsilon))
=\frac{1}{\epsilon} \cdot Q+W(1+\epsilon))
\]
where $W(\lambda)$ is an operator-valued analytic function
in an open disc centered at $\lambda=1$ while $Q$ is a bounded
linear operator on $C^0(S)$.
Keeping $\epsilon>0$ fixed we apply both sides to the identity function
$1_S$ on $S$ and the construction of
the measures $\{\mu_n\}$ gives
\[
1+
\sum_{k=1}^\infty\,
\frac {\mu_k(S)}{(1+\epsilon)^k}=\frac{1}{\epsilon} \cdot Q(1_S)(s_0)+
W(1+\epsilon))(1_S)(s_0)
\]
If $n\geq 2$ is an integer and $\epsilon=\frac{1}{n}$
one gets the inequality
\[
\sum_{k=1}^{k=n}\,
\frac {\mu_k(S)}{(1+\frac{1}{n})^k}\leq
n\cdot |Q(1_S)(s_0)|+|W(1+1/n))(1_S)(s_0)|\leq
n\dot ||Q||+ ||W(1+1/n)||\implies
\]
\[
\frac{1}{n}\cdot\sum_{k=1}^{k=n}\,\mu_k(S)\leq
(1+\frac{1}{n})^n\cdot (||Q||+\frac{ ||W(1+1/n)||}{n}
\]
Since
Neper's constant $e\geq (1+\frac{1}{n})^n$ for every $n$
we find
a constant $C$ which is
independent of $n$ such that
\[
\frac{1}{n}\cdot\sum_{k=1}^{k=n}\,\mu_k(S)\leq C
\]
Hence the sequence $\{\pi_n(S)\}$ is  bounded
and we can pass to a subsequence
which converges weakly to a limit measure $\mu_*$.
For this $\sigma$-additive measure the limit formula in (**) above entails that
\[ 
\mu_*(S\setminus A_k)=0\quad\colon\, k=1,2,\ldots\tag{i}
\]
Moreover, by (*) we also have
\[
\pi_*(\mathcal A)=0\tag{ii}
\]
Now
$S= \mathcal A\cup\, A_k$ so (i-ii) give:
\[ 
\mu_*(S)=0
\]
But this is impossible for at the same time
we have already seen that
$\pi_n(S)\geq 1$ for each $n$ and hence also $\mu_*(S)\geq 1$.






















\centerline{\bf{Stone's theorem.}}
\medskip

\noindent
Here follows an
example where unbounded operators appear.
The reader has begun to master unbounded
operators and their spectral properties by learning  the  details which appear
during  
the proof of Stone's theorem below.
Let
$\mathcal H$ be a complex Hilbert space.
A strongly continuous semi-group of unitary operators
is a family
$\{U_t\,\colon t\geq 0\}$
where
each $U_t$ is unitary, i.e. they
preserve the Hermitian inner products:
\[
\langle U_tx,U_ty\rangle=
\langle x,y\rangle
\]
Moreover, $U_0$ is the identity operator $E$ and
$U_t\circ U_s=U_{t+s}$ hold for every pair of non-negative real numbers.
Finally, the strong continuity means that 
\[ 
\lim_{t\to 0}\, ||U_tx-x||=0
\] 
for every $x\in\mathcal H$.
Stone's theorem
asserts that there exists a densely defined and self-adjoint operator
$A$ on $\mathcal H$
which is called the infinitesmal generator. Its domain of defintion $\mathcal D(A)$
is a dense subspace of $\mathcal H$ which consists of vectors $x$ such that
there exists a limit
\[
\lim_{\delta\to 0}\, \frac{U_\delta(x)-x}{\delta}=y
\]
 and when it holds we set
\[ 
A(x)=iy
\] 
where $i$ is the imaginary unit.
The proof that such an inifintesmal generator
exists relies  upon Neumann's calculus in ¤ 0.0.
 Here follow the  crucial steps which 
lead to the construction of  $A$.
\medskip

\noindent
{\bf{The operators $R(\lambda)$.}}
When
$\lambda$ are complex numbers with positive real part
we obtain bounded linear operators
\[
R(\lambda)(x)=\int_0^\infty\, e^{-\lambda t}\cdot U_t(x)\, dt
\]
The integrals exists because of the strong continuity and
the convergence with respect to the norm in $\mathcal H$ is
evident since
$||U_t(x)|||\leq ||x||$ for each fixed vector $x$.
Approximating the integrals by Riemann sums
the bounded linear operator $R(\lambda)$ is found
by the limit equation
\[
R(\lambda)= \lim_{\delta\to 0}\, 
\delta^{-1}\cdot (E-e^{-\delta\lambda}U_\delta)^{-1}\tag{i}
\]
Notice that
$\mathfrak{Re}(\lambda)>0$ implies that
the operator norm
\[
||e^{-\delta\lambda}U_\delta)||= e^{-\mathfrak{Re}(\lambda)}<1
\]
and therefore linear operators
$E-e^{-\delta\lambda}U_\delta)$ are invertible which explains how one
proceeds to the  limit in the right hand side above.
A notable point is that
(i) enable us to describe the compact
spectra of the operators $R(\lambda)$.
Consider for example the case $\lambda=1$.
Since the spectrum of a unitary opertor is contained in
the unit circle it follows that
\[
\sigma(E-e^{-\delta}\cdot U_\delta)\subset
\{z\in{\bf{C}}\,\colon\, |z-1|=e^{-\delta}\}
\]
Next, 
general formulas for spectra of bounded operators
to be explained in ¤xx give
\[
\sigma(\delta^{-1}\cdot (E-e^{-\delta\lambda}U_\delta)^{-1})
\subset\{z\colon \, |z-\frac{\delta}{1-e^{-2\delta}}|=\frac{\delta}{1-e^{-\delta}}\}
\]
Passing to the limit as $\delta\to 0$ it follows that
\[ 
\sigma(R(1))\subset\{z\colon \, |z-1/2|=1/2\}\tag{ii}
\]
\medskip

\noindent
{\bf{The infinitesmal generator.}}
If  $h>0$ and $x\in\mathcal H$ then 
the semi-group equations $U_h\circ U_t= U_{h+t}$ give
\[ 
\frac{U_h-E}{h}\circ R(\lambda)(x)=
h^{-1}\cdot 
\int_0^\infty\, e^{-\lambda t}\cdot (U_{t+h}(x)-U_t(x))\, dt
\]
A variable substitution shows that the last term is equal to
\[
\frac{e^{\lambda h}-1}{h}\cdot 
\int_h^\infty\, e^{-\lambda t}\cdot U_t(x)\, dt-\frac{1}{h}\int_0^h\,
 e^{-\lambda t}\cdot U_t(x)\, dt \tag{iii}
\]
Passing to the limit as $h\to 0$ it is readily seen that
the vectors in (iii) converge in the norm topology on $\mathcal H$
to the vector
\[
\lambda\cdot R(\lambda)(x)-x
\]
The conclusion is that
if $y=R(\lambda)(x)$ then there exists
the limit
\[
\lim_{h\to 0}\, \frac{U_h(y)-y}{h}=
\lambda\cdot R(\lambda)(x)-x\tag{iv}
\]
This suggests that we regard the subspace
$\mathcal H_0$ of $\mathcal H$ which consists of vectors $y$ such that
there exists a limit vector $S(y)$ where
\[
\lim_{h\to 0}\, || \frac{U_h(y)-y}{h}-S(y)||=0
\]
It is clear that  $S\colon \mathcal H_0\to \mathcal H$
is a linear operator
and (iv) entails that
the range of $R(\lambda)$ is contained in
$\mathcal H_0$ when $\mathfrak{Re}(\lambda)>0$.
Moreover 
\[
S\circ R(\lambda)(x)= \lambda\cdot R(\lambda)(x)-x\quad\colon x\in \mathcal H
\tag{v}
\]
We can rewrite  (v)   and get
\[
(\lambda\cdot E-.S)\circ R(\lambda)(x)=x\quad\colon x\in \mathcal H
\]
In ¤ 0.0 we shall learn that this means that
$\{R(\lambda)\}$ appear as resolvent operators to
the densely defined linear operator $S$.
Applying the inclusion (ii) above
and the general result in (0.0.5.1) from Neumann's calculus, it
follows that 
$\sigma(S)$ consists of purely imaginary numbers.
Set
\[
 A=iS
\]
From the above $\sigma(A)\subset\mathfrak{R}$
and in ¤ xx we shall learn that $A$ is a densely defined and self-adjoint
operator which gives the requested  the infinitesmal generator of the
unitary semi-group $\{U_t\}$.


\medskip

\noindent
{\bf{Remark.}}
Stone's theorem has a wide range of applications, especially in ergodic theory.
For applications in quantum mechanics we refer to
the article \emph{xxxx} by J. von Neumann.
Let us also remark that
an analogue of Stone's theorem hold for a strongly continuous semi-group
$\{V_t\}$ satisfying
$V_t^*V_t=E$ for every $t$, but not necessarily
$V_tV_t^*=E$, i.e.  the $V$-operators need not be unitary.
In ¤ xx we also expose a result due to J. von Neumann
about
uniqueness of solutions to
a certain Schršdinger equation which arises via
the 
uncertainty   principle in quantum mechanics.
See also ¤ A:x for a "concrete version" of Stones theorem.
\bigskip



More precisely, in
the unbounded open complement
$U={\bf{R}}^3\setminus\overline{\Omega}$
there exists the symmetric Green's function $G(p,q)$
associated to Neumann's boundary value problem, i.e.
\[ 
G(p,q)= \frac{1}{4\pi\cdot |p-q|}+H(p,q)
\]
where $|p-q|$ is the euclidian distance between
a pair of points$p,q$ in $U$. Moreover,
$q\mapsto H(p,q)$ is harmonic as a function of $q$ for each fixed $p\in U$, and
for each $p\in U$ we have
\[
\frac{\partial G}{\partial n_q}(p,q)=0\quad\colon q\in \partial\Omega
\]
where $n_q$ is the outwards normal derivative.
Now $G$ gives a densely defined
operator on the Hilbert space $L^2(U)$ defined
by
\[
\mathcal G_f(p)= \int_U\, G(p,q)\cdot f(q)\, dq
\]
To be precise, the
volume integrals in the right hand side give
$L^2$-functions of $p$ for a dense subset of $L^2$-functions $f$ in $U$.
We shall learn that this unbounded and
densely defined operator 
has a spectrum in the sense of Neumann which is confined to the
non-negative real line. Moreover, there exists an associated
spectral function $\theta(p,q;\lambda)$
which for each $\lambda>0$ yields a bounded
integral operator on
$L^2(U$:
\[ 
\Theta(\lambda)_f(p) =\int_U\, \theta(p,q;\lambda)\cdot f(q)\, dq
\]
and here
\[
\mathcal G_f(p)= \lim_{\delta\to 0}\, \int_\delta^{1/\delta}\,
\lambda^{-1}\cdot \bigl[\int_U\,  \frac{d}{d\lambda}\theta(p,q;\lambda)\cdot f(q)\, dq
\bigr]\, d\lambda
\]
for those $L^2$-functions $f$ which belong to the domain of
definition of $\mathcal G$.
To learn about this construction and how one employs the spectral function to
fiond 
solutions to an assocaited wave equation can be regarded as 
one of the major goals  for this chapter.
As expected  measure theoretic considerations intervene, i.e.
"abstract functional analysis" is to a large extent
related to measure theory.
In the situation above one
also
considers the total variation of
operator norms for the
$\Theta$-operators, i.e. on a closed interval
$\{a\leq \lambda\leq b\}$ where $0<a<b$ we put
\[ 
\Theta^*[a,b]=
\max\, \sum\, || \Theta(\lambda_{\nu+1})-\Theta(\lambda_\nu)||
\]
with the maximum taken over all partitions 
$a=\lambda_0<\lambda_1<\ldots<\lambda_N=b$
and we have taken a sum of operator norms
for the corresponding difference of
the $\Theta$-operators which are parametrized with respect to $\lambda$.
It turns out that
the operator valued function $\lambda\mapsto \Theta(\lambda)$
is absolutely continuous. It means that for
every $\epsilon>0$ there exists $\delta>0$ such that
\[
\sum\, \Theta^*[a_j.b_j]<\epsilon
\]
for every finite familly of closed and disjoint intervals
$\{[a_j,b_j]\}$ arranged so that $b_j<a_{j+1}$ for each $j$.
To learn the proof which is presented in ¤ xx 
gives the reader a good
insight in spectral theory
since one arrives at a specific result in a concrete situation
which
therefore
consolidates the general  theory.



\noindent
Let $\Omega$ be a bounded open set in
${\bf{R}}^3$ whose boundary is a finite union of closed
surfaces of class $C^1$.
In the unbounded open complement
$U={\bf{R}}^3\setminus\overline{\Omega}$
there exists the symmetric Green's function $G(p,q)$
associated to Neumann's boundary value problem, i.e.
\[ 
G(p,q)= \frac{1}{4\pi\cdot |p-q|}+H(p,q)
\]
where $|p-q|$ is the euclidian distance between
a pair of points$p,q$ in $U$. Moreover,
$q\mapsto H(p,q)$ is harmonic as a function of $q$ for each fixed $p\in U$, and
for each $p\in U$ we have
\[
\frac{\partial G}{\partial n_q}(p,q)=0\quad\colon q\in \partial\Omega
\]
where $n_q$ is the outwards normal derivative.
Now $G$ gives a densely defined
operator on the Hilbert space $L^2(U)$ defined
by
\[
\mathcal G_f(p)= \int_U\, G(p,q)\cdot f(q)\, dq
\]
To be precise, the
volume integrals in the right hand side give
$L^2$-functions of $p$ for a dense subset of $L^2$-functions $f$ in $U$.
We shall learn that this unbounded and
densely defined operator 
has a spectrum in the sense of Neumann which is confined to the
non-negative real line. Moreover, there exists an associated
spectral function $\theta(p,q;\lambda)$
which for each $\lambda>0$ yields a bounded
integral operator on
$L^2(U$:
\[ 
\Theta(\lambda)_f(p) =\int_U\, \theta(p,q;\lambda)\cdot f(q)\, dq
\]
and here
\[
\mathcal G_f(p)= \lim_{\delta\to 0}\, \int_\delta^{1/\delta}\,
\lambda^{-1}\cdot \bigl[\int_U\,  \frac{d}{d\lambda}\theta(p,q;\lambda)\cdot f(q)\, dq
\bigr]\, d\lambda
\]
for those $L^2$-functions $f$ which belong to the domain of
definition of $\mathcal G$.
To learn about this construction and how one employs the spectral function to
fiond 
solutions to an assocaited wave equation can be regarded as 
one of the major goals  for this chapter.
As expected  measure theoretic considerations intervene, i.e.
"abstract functional analysis" is to a large extent
related to measure theory.
In the situation above one
also
considers the total variation of
operator norms for the
$\Theta$-operators, i.e. on a closed interval
$\{a\leq \lambda\leq b\}$ where $0<a<b$ we put
\[ 
\Theta^*[a,b]=
\max\, \sum\, || \Theta(\lambda_{\nu+1})-\Theta(\lambda_\nu)||
\]
with the maximum taken over all partitions 
$a=\lambda_0<\lambda_1<\ldots<\lambda_N=b$
and we have taken a sum of operator norms
for the corresponding difference of
the $\Theta$-operators which are parametrized with respect to $\lambda$.
It turns out that
the operator valued function $\lambda\mapsto \Theta(\lambda)$
is absolutely continuous. It means that for
every $\epsilon>0$ there exists $\delta>0$ such that
\[
\sum\, \Theta^*[a_j.b_j]<\epsilon
\]
for every finite familly of closed and disjoint intervals
$\{[a_j,b_j]\}$ arranged so that $b_j<a_{j+1}$ for each $j$.
To learn the proof which is presented in ¤ xx 
gives the reader a good
insight in spectral theory
since one arrives at a specific result in a concrete situation
which
therefore
consolidates the general  theory.



\noindent
{\bf{Unitary  groups.}}
There exists also a 1-1 correspondence 
exists between the family of self-adjoint operators
and unitary groups of transformations which
are strongly continuous on a dense subspace of
the given Hilbert space $\mathcal H$.
Moreo rpecisley, if $A$ is self-adjoint there exists for
each real number $t$ a unitary transformation $U_t$
such that
\[ 
U_t(x)= e^{itA(x)}
\]
hold
for a dense subspace of the domain of definition of $A$
and since $A$ is self-adnoint one eaily verifies the gruop law:
\[
U_{t+s}= U_t\circ U_s
\]
Conversly, let $\{U_t\}$ be a group of untary transformations
and assume that it is strongly continuos on a dense subapace 
$\mathcal H_*$
of
$\mathcal H$, i.e. for vectors in this subspace
one has
\[ 
\lim_{t\to 0}\, ||U_t(x)-x||=0
\]
When this holds one constructs opeprtator-valued Stieltjes integrals
for complex numbers in the open right half-plane. More precisely, 
each vector $x\in\mathcal H_*$ there exists the Stieltjes' integral 
\[
R(\lambda)(x)= \int_0^\infty\, e^{-\lambda t}\cdot U_t(x)\, dt
\]
One verifies that
\[
||R(\lambda(x)||\leq e^{-\mathfrak{Re}(\lambda)}\cdot ||x||\quad
\colon x\in\mathcal H_*
\]
It follows that $R(\lambda)$ extends in 
a unique fashion to a bounded linear operator.
We can specialize $\lambda$ and get the bounded operator
\[ 
R=R(1)
\]
Since $\{U_t\}$ is a unitary group an easy 
calculation to be given in
¤ xx entails that $R$ is normal
and one has  the inclusion
\[ 
\sigma(R)\subset
\]

















{\bf{Spectral functions.}}













In ¤ xx we show that under the sole condition 
(1), there exist a distinguished family of 
spectral functions $\theta(x,y;\lambda)$
assoc’ated toÊthe symmetric function $K(x,y)$.
For each spectral function,
$(x,y)\mapsto  \theta(x,y;\lambda)$ is 
symmetric and yields a bounded linear operarator on
$L^2[0,1]$ denoted by $\Theta(\lambda)$. Moreover,
the operator valued function
$\lambda\mapsto \Theta(\lambda)$ has a finite total  
variation with respect to $\lambda$ over
every bounded interval  the real $\lambda$-line
and the unbounded operator $\mathcal K$
is recaptured  from the spectral function
by the integral formula
\[ 
\mathcal K(h)= \int_{-\infty}^\infty\,
\frac{1}{\lambda}\cdot 
\frac{d\Theta} {\lambda}(h)
\] 
for every $L^2$-function $h$ in the domain of definition for $K$.
The precise calculus and constructions of operator valued integrals above
are exposed in ¤ xx. But let us briefly recall their construction.
Let $K$ satisfy (1).
Now we can approximate $\mathcal K$ in a weak sense by
sequences of Hilbert-Schmidt operators, i.e. linear operators on $L^2[0,1]$
of the form
\[ 
\mathcal G(f)(x)= \int_0^1\, G(x,y)\cdot f(y)\,dy
\] 
where $G$ are real-valued symmetric kernel functions such that
\[
\iint\, G(x,y)^2\, dxdy<\infty
\]
A sequece $\{G_n\}$ approximates $K$ weakly if
\[
\lim_{n\to \infty}\, \int_0^1\, |K(x,y)-G_n(x,y)|^2\, dy=0
\] 
hold outside a null set on the $x$-interval.
Next, if $\{G_n\}$ is an approximates $K$ as above one
constructs spectral $\theta$-functions as follows:
First, each fixed $G_n$ is compact and has therefore a discrete spectrum.
This gives  an
orthonormal family $\{\phi^{(n)}_\nu\}$
in $L^2[0,1$ and to each $n$ a non-zero real number
$\lambda^{(n)}_\nu$ such that
\[
\mathcal G_n(\phi)= \lambda^{(n)}_\nu\cdot \phi^{(n)}_\nu
\]
The $\lambda$-numbers are enumerated
with increasing absolute values.
For each $n$ and every $\lambda>0$ we set
\[
\rho_n(x,y;\lambda)= \sum_{0<\lambda_\nu^{(n)}<\lambda}\,
\phi^{(n)}_\nu(x)\phi^{(n)}_\nu(y)
\]
\[
\rho_n(x,y;-\lambda)= \sum_{-\lambda <\lambda_\nu^{(n)}<0}\,
\phi^{(n)}_\nu(x)\phi^{(n)}_\nu(y)
\]
Applying Bessel inequalities several times, it is proved in [ibid:Chapter 1-2]
that
one can always find subsequences
$\{\rho_{n_1},\rho_{n_2}\,\ldots\}$
which converge to a spectral $\rho$-function associated toÊ$K$
via the limit equation (xx).
So  every $K$-kernel which 
satisfies (1) has a non-empty family of associated
spectral 
$\rho$-functions.
The size of this $\rho$-family is
governed by Weyl's limit circles
which arise as follows: Let $f$ be a non-zero real-valued continuous
on $[0,1]$.
If $\{G_n\}$  approximates $K$
we find for each $n$ a unique function
$\phi_n$ which solves the integral equation
\[
\phi_n(x)=i\cdot \int_0^1\, G_n(x,y)\cdot \phi_n(y)\, dy+f(x)
\]
Here $\phi_n$ is automatically continuous.
Keeping $f$ and $x$ fixed
we get a sequence of complex numbers
$\{\phi_n(x)\}$.
Let $Z(x)$ be the closed set of cluster points of its closure.
It turns out that
the union of all such cluster sets 
as we take sequences $\{G_n\}$ as above,
is  a closed 
subset of ${\bf{C}}$
 which either is reduced to a single point or  equal to  a circle.
In the latter case the circle is denoted by by
$W_K(f:x)$ and called a Weyl circle associated to the triple $K,f,x$.
When Weyl circles appear it truns out that there exist many disctinct
spectral functions of $K$.

 
 






\medskip


\noindent
{\bf{The self-adjoint case.}}
Following [Carleman 1923]
one says that the 
$K(x,y)$ is of Class I if 
(*) has non non-trivial solution. In this case no Weyl circles appear and 
$\mathcal K$ is self-adjoint with  a unique spectral function.
Another fundamental result from  [Carleman 1923] asserts that
if
$K$ is such that
there does not exist a non-zero $\phi\in L^2[0,1]$ such that
$\mathcal K(\phi)=0$, then
every $L^2$-function $f$ on $[0,1]$ can be represented as a limit 
\[ 
f(x)=
\lim _{\ell\to +\infty}\, \int_{-\ell}^\ell\,
\frac{d}{d\lambda}(\int_0^1\, \theta(x,y;\lambda)\cdot h(y)\, dy)
\]
where  equality hold 
for all $x$ outside a nullset in $[0,1]$.
\medskip


\noindent
{\bf{Remark.}} The restriction to the unit interval is harmless, i.e
by a change of variables the theory holds verbatim for
$L^2$-spaces over domains in
${\bf{R}}^n$ for every positive integer $n$, and of course
also on manifolds equipped with some volume density.
Except for some minor technical points one can also extend
the whole study to cover case where infinite number of variables appear.
But to save notations we often prefer to work
with kernel functions on
intervals in ${\bf{R}}$.





Let us finally recall that
An alternative
proof of Carleman's  spectral theorem for unbounded operators on
Hilbert spaces was later given by  
J. von Neumann in     the article \emph{Eigenwerttheorie Hermitescher 
Funktionaloperatoren}[xxx: 1929].
 from 1929.
A merit in von Neumann's account 
is that 
some measure theoretic technicalities  
in  Carleman's proof
can be omitted 
and his proof  
covers the case for operators 
on
non-separable Hilbert spaces and von Neumann's 
more abstract version of the spectral theorem is presented in ¤ 9.
On the other hand 
it  is often necessary to establish
formulas of a measure theoretic character in order to apply
the spectral theorem. An example
is  Carleman's  solution to the 
Bohr-Schršdinger equation above which will be  exposed in ¤ xx.


\centerline {\bf{H. Neumann's resolvent operators}}.
\medskip

\noindent
The less experienced reader might prefer to start  with   ¤ 1-6
whose contents   "start from scratch".
However, it  is  essential to become
familiar with unbounded linear operators " as soon as possible"
since they
arise naturally in many applications.
So already
in
¤ 0.0 we introduce
Neumann's resolvent operators and the construction of spectral sets of
densely defined but unbounded linear operators.
Here analytic function theory plays a crucial role such as in the proof 
of 
Theorem 0.0.6.3
which enable us 
to construct bounded  linear operators  from
a given
densely defined  operator.
Let us also remark that Neumann's calculus for densely defined linear operators
extends 
several  results about 
matrices. 
For example, let $T\colon X\to X$ be a densely defined linear operator
on a Banach space
with a closed graph in $X\times X$ and  suppose also that the adjoint $T^*$  has 
a dense domain of definition. In ¤ xx   we  prove
the equality
\[
 \sigma(T)= \sigma(T^*)
\] 
under the extra assumption that the Banach space $X$ is reflexive.
Here $\sigma(T)$ is the spectrum of $T$ which will be constructed in
¤ 0.0. for each  densely defined and closed linear operator
on a Banach space.
In the case when
$\lambda_0$ is an isolated point in the spectrum of $T$
we  prove in ¤ 0.0.6 that there exists 
a bounded linear map $E(\lambda_0)$ which
commutes with $T$
and the spectrum of the operator $E(\lambda_0)T$
is reduced to the singleton set $\{\lambda_0\}$.
We remark that 
this extends the
classical constructions of
Cayley matrices in linear algebra.
\medskip

\noindent
{\bf{The operator $i\cdot \frac{d}{dx}$.}}
A "first lesson" about densely defined
linear operators
occurs 
when we consider
the densely defined derivation operator
$A=i\cdot \frac{d}{dx}$
acting on the Hilbert space of square integrable functions on
the real $x$-line. 
Using Fourier transforms  and
Parseval's equality we  prove in ¤ xx that
$A$ is self-adjoint.
The resder should keep this example in mind while the general theory
is exposed.
Another densely defined operator $B$ on
$L^2({\bf{R}})$
is given by multiplication with $-ix$. Here the domain of definition for
$B$ consists of $L^2$-functions $f(x)$ such that
$x\cdot f(x)$ also is square integrable.
The chain rule for derivatives 
and the equality $i^2=-1$
show that
if $f(x)$ is a test-function on
${\bf{R}}$ then
\[
A\circ B(f)-
B\circ A(f)= f\tag{*}
\]
One refers to (*) as Weyl's identity.
The equation (*)
appears in relation to the uncertainty principle in
quantum
mechanics.
in 1926 Schršdinger
discovered that when the pair above
are identified with
infinitesmal generators of unitary groups
on $L^2){\bf{R}})$, then one arrives at
an irreducible representation.
In ¤xx we expose von Neumann's 
uniqueness theorem which gives an affirmative answer
to a 
question which was  originally posed by Schršdinger.
Namely, 
that  every pair of densely defined
self-adjoint operators which satisfy (*) 
and as  infinitesmal generators of unitary groups
give riose to an irreducible
representation of
$L^2){\bf{R}})$, is equal to the special pair above up to a
unitary equivalence.



















\newpage

NEW TITLE FOR SCATTERED MATERIAL

\noindent
{\bf{A product formula.}}
Let us announce a theorem  due to Nagy and F. Riesz whose proof relies upon
results  in ¤ 8-9
and will be  proved in ¤ 11.xx.
Let $\mathcal H$ be a Hilbert space
and $T\colon\mathcal H\to \mathcal H$
a densely defined and closed linear operator.
Then we shall  prove that the adjoint $T^*$ also is densely
defined, as well as the composed operator $T T^*$.
Moreover, $TT^*$ is self-adjoint with a spectrum confined to the
non-negative real axis and we shall learn that 
there exists the densely defined self-adjoint operator
\[
A=\sqrt{TT^*}
\]
where  $A^2=TT^*$.
Next, a  bounded linear operator $P$ is called a partial isometry attached to $A$
if the norms
\[
||P(Ax)||= ||A(x)||\quad\colon x\in\mathcal D(A)
\]
while the $P$-kernel is the orthogonal complement 
to the range of $A$, i.e. if $y$ is a vector such that
$\langle Ax,y\rangle =0\colon\,x\in\mathcal D(A)$, then $P(y)=0$.
\medskip

\noindent
{\bf{Theorem.}}
\emph{For every densely defined and closed operator $T$
there exists a partial isometry $P$ attached to
$\sqrt{TT^*}$ such that}
\[
T(x)=P\circ\sqrt{TT^*}(x)
\quad\colon x\in\mathcal D(TT^*)
\]

\noindent
\emph{Summing up}, results as above
illustrate  the aim of this chapter 
which apart from presenting basic facts about normed
vector spaces  pays considerable attention to densely defined operators
on Hilbert spaces.






\medskip

\noindent
{\bf{Hellinger's integrals.}}
One 
often needs specific results from calculus, especially 
about  integrals where one encounters
both those of Lebesgue and  
integrals in the sense of Borel and Stieltjes.
Let us recall some 
constructions
and results due to Hellinger's in  
\emph{Die Orthogonalinvarianten quadratischer Formen von unendlichen
vielen Variabeln} [Dissertation. Gšttingen 1907].
Here 
Stieltjes' constructions are extended  to second order differences.
Fix a bounded and closed
interval  $J=[a,b]$.
For each subintervall $\ell=[\alpha,\beta]$
and  a continuous real-valued function $\phi $ on $J$ we set
\[
D_\ell(\phi )= \phi (\beta)-\phi(\alpha)
\]
Next,let
$g$ and $h$ be a pair of
continuous and non-decreasing 
functions which are kept fixed from now on.
Denote by $\mathcal S$ the class of
continuous functions $f$   such that
\[ 
(D_\ell(f))^2\leq D_\ell(g)\cdot D_\ell(h)\tag{*}
\] 
hold for
every subinterval $\ell$ as above.
Next, take some arbitrary  $u\in C^0(J)$
while $f\in\mathcal S$.
If $\{[\alpha_\nu,\beta_\nu]\}$ is a partition of
$[a,b]$ into an increasing sequence of intervals, i.e
$\alpha_{\nu+1}= \beta_\nu$ hold, 
we
define the upper respectively the lower sums

\[
S^*=\sum\, \max_{x\in\ell_\nu}u(x)\cdot \frac{(D_{\ell_\nu}(f))^2}{D_{\ell_\nu}(g)}\cdot \ell_\nu
\] 
\[
S_*= \sum\, \min_{x\in\ell_\nu}u(x)\cdot \frac{(D_{\ell_\nu}(f))^2}{D_{\ell_\nu}(g)}\cdot \ell_\nu
\] 
where $\ell_\nu=\beta_\nu-\alpha_\nu$.
If $\omega_u(\delta)=\max\{ |u(x)-u(x')|\,\colon |x-x'|\leq\delta\}$
is the modulos of continuity for $u$
we see that (*) gives
\[
S^*-S_*\leq \omega_u(\delta)\cdot (h(b)-h(a))|quad\colon
\delta= \max_\nu\, \beta_\nu-\alpha_\nu
\] 
From this the reader can deduce that
there exists a limit when the partitions get fine, i.e. the $\delta$-numbers
tend to zero in above. The result is Hellinger's integral
denoted by
\[ 
\int_a^b\, \frac{df^2}{dg}\tag{1}
\]
\medskip

\noindent
In a similar fashion the reader can verify that if $f_1,f_2$ is a oaiin 
$\mathcal S$, then there exists the integral
\[ 
\int_a^b\, \frac{df_1df_2}{dg}\tag{2}
\]
Next, with $ f\in\mathcal S$ 
and $u\in   C^0(J)$ we put
\[
S^*=\sum\, \max_{x\in\ell_\nu}u(x)\cdot D_{\ell_\nu}(f)\cdot \ell_\nu
\] 
\[
S_*= \sum\, \min_{x\in\ell_\nu}u(x)\cdot (D_{\ell_\nu}(f))\cdot\ell_\nu
\] 
Now
\[
|S^*-S_*|\leq \omega_u(\delta)\cdot
\sum\, |D_{\ell_\nu}(f)|\cdot \ell_\nu
\]
Using (*) and the Cauchy Schwartz inequality we see that
the last sum is majorised by
\[
\omega_u(\delta)\cdot \sqrt{(g(b)-g(a))(h(b)-h(a)}
\]
From this the reader can conclude that
there exists a welldefined integral
\[ 
\int_a^b\, u\cdot df\tag{3}
\]

\noindent
{\bf{Exercise.}}
Let $\phi$ and $\psi$ be some pair of continuous functions
while $f_1$ and $f-2$ belong to $\mathcal S$.
Put
\[ 
\Phi(x)=\int_a^x\, \phi\cdot df\quad\colon\,
\Psi(x)=\int_a^x\, \psi\cdot df
\]
Show the equality below for every $u\in C^0(J)$:
\[ 
\int_a^b\, u\cdot \frac{dF_1dF_2}{dg}=
\int_a^b\, u\phi\psi\cdot \frac{df_1df_2}{dg}
\]

\noindent
{\bf{Exercise.}}
Let $u$ and $v$ be a pair in $C^0(J)$ while $f_1,f_2$ belong to $\mathcal S$.
Show the equality
\[
\int_a^b\, v(x)\cdot (\int_a^x\, u\cdot \frac{df_1df_2}{dg})\, dx
\]























\medskip



\medskip



\centerline {\bf{Picard's equation.}}
\medskip


\noindent
Picard's   article \emph{Sur une Žquation intgrales singuliŽre} [Ann. Ecole, Norm. Sup.1911)
is devoted to the
integral equation
\[ 
\phi(x)=\lambda\cdot
 \int_{-\infty}^\infty\,e^{-|x-y|})\cdot\phi(y)\, dy+f(x)\tag{*}
\]
where $\lambda$ is a complex parameter.
To begin with one seeks solutions $\phi$ when
$f(x)$ is a $C^2$-function
on the real line with compact support and
requests that $\phi$ belongs to 
$L^2({\bf{R}})$.
By analyzing solutions to 
certain second order differential equations, Picard proved
that (*) has unique
$L^2$-solutions $\phi$ for each $f$ as above
when
the complex parameter
$\lambda$ stays
outside the real interval $[1/2,+\infty)$.
Moreover, the solution is given by
\[
\phi(x)= f(x)+\frac{\lambda}{\sqrt{1-2\lambda}}\cdot
 \int_{-\infty}^\infty\,e^{-|x-y|})\cdot f(y)\, dy
\]
where a single valued branch of
$\sqrt{1-2\lambda}$ in ${\bf{C}}\setminus [1/2,\infty)$
appears.
Let us express this via operators.
Picard's integral operator is defined by
\[ 
\mathcal K(f)(x)=\int_{-\infty}^\infty\, e^{-|x-y|}\cdot f(y)\, dy
\]
It is densely defined on the Hilbert space
$L^2(\bf{R}]$ and
Picard's uniqueness above  entails that when
$\lambda$ is not real, then
there does not exist a non-zero $L^2$-function $\phi$ such that
\[
\phi+\lambda\cdot \mathcal K(\phi)=0
\]
General results about densely defined and symmetric operators on
Hilbert spaces which are exposed later on, imply that
$\mathcal K$ is self-adjoint.


 and from the above
it follows that
if $E$ is the identity operator,. then
$E-\lambda\cdot \mathcal K$ is invertible in Neumann's sense
if $\lambda$ stays outside $[1/2,+\infty)$.









Starting from this, Carleman applied the general theory for symmetric and densely
defined operators and proved that
the densely defined operator $\mathcal K$ defined by
\[ 
\mathcal K_g(x)=\int_{-\infty}^\infty\, e^{-|x-y|}\cdot g(y)\, dy
\]
belongs to the favourable class I which means that
it is self-adjoint and 
the spectrum is $[1/2,+\infty)$.



we shall also give explicit formulas for the spectral function of Picard's operator.
More generally one can consider
densely defined operators
of the form
\[
\mathcal K_g(x)=
\int_{-\infty}^\infty\,\bigl(H_1(|x-y|)+ H_2(x+y)\bigr)\cdot g(y)\, dy
\]
where $H_1$ and $H_2$ is a pair of real-valued functions
such that the $L^2$-integrals
\[
\int_0^\infty\, H_1(s)^2\, ds\quad\colon
\int_{-\infty}^\infty\,H_2(s)^2\, ds
\] 
both exist.
Again one proves that
$\mathcal K$ is self-adjoint with a spectrum
confined to the real line.
See ¤ xx for further details., Let us remark
that
$\mathcal K$-operators as above
gives a gateway to analyse integral operators with kewrnel functions
\[ 
K(x,y)=\frac{1}{x}\Omega(\frac{x}{y})
\]
which are defined when
$x$ and $y$ both a $>0$ and
\[
\Omega(t)= t^{-1}\cdot \Omega(\frac{1}{t})
\]
Here $K$ is a kernel for a densely defined operator on
the Hilbert space 
$L^2({\bf{R}}^+)$ and we shall prove that it is
self-adjoint under the condition that
\[
\int_0^\infty\,\Omega(t)^2\, dt<\infty
\]










\bigskip

\centerline{\bf{Symmetric integral operators.}}
\bigskip


\noindent
Consider the domain $\square=\{0\leq x\leq 1\}\times\{0\leq y\leq 1\}$
in ${\bf{R}}^2$.
Let $K(x,y)$ be a real-vaued and Lebesgue mesure function on
$\square$ such that
the integrals
\[ 
\int_0^1\, K(x,y)^2\, dy<\infty
\]
for all $x$ outside a null-set on $[0,1]$.
In addition $K$ is symmetric,  i.e.$K(x,y)= K(y,x)$.
The $K$-kernel is bounded in Hilbert's sens if there exists a constant
$C$ such that
\[ 
\iint_\square\, K(x,y) u(x)u(y)\, dxdy\leq C^2\cdot\int_0^1\, u(x)^2\, dx
\]
for each $u\in L^2[0,1]$.
In the text-book |emph{Intyergralxxx}Ê[xxxx 1904],
Hilbert proved that
the linear operator on 
$L^2[0,1]$ defined by
\[ 
\mathcal K(u)(x)=\int_0^1\, K(x,y)u(y) dy
\]
is bounded and its operator norm is majorsied by $C$-Moreover
the spectrum is real and contained in $[-C,C]$ and
just as for symmetric real matrices
there exists a spectral resolution.
More precisely, set $\mathcal H= L^2[0,1]$.
Then there exists a
map
from $\mathcal H\times\mathcal H$
to the space of Riesz measures supported by
$[-C,C]$ which to every pair $u$ and $v$ in
$\mathcal H$ assigns a Riesz measure $\mu_{\{u,v\}}$
and $\mathcal K$ is recovered by the equation:
\[
\langle \mathcal K(u),v\rangle=\int_{-C}^C\,  t\cdot d\mu_{\{u,v\}}(t)
\]
where the left hand side
is the inner product
on the complex Hilbert space defined by
\[
\iint\, \mathcal K(u)(x)\cdot \overline{v}(x)\,dx
\]
In the monograph [Carelan 1923]
the condition (*) is imposed while (**) need not be valid.
Then we encounter an unbounded operator.
But notice that if
$u|in\mathcal H$ then (*9 and the CuachySchwarz inequality entails that
the functions
\[ 
y\mapsto K(x,y)u(y)
\] 
are absolutely integrable in Lebegue's sense 
for all $x$ outside the nullset $\mathcal N$ above.
Hence it makes sense to refer to $L^2$-functions $\phi$ on $[0,1]$
which
satisfy an eigenvalue equation
\[
\phi(x)= \lambda\cdot \int_0^1\, K(x,y)\phi(y)\, dy\tag{1}
\]
where $\lambda$ is a compkex number.
one is also led to consider the integral equation
\[
\phi(x)= \lambda\cdot \int_0^1\, K(x,y)\phi(y)\, dy+f(x)\tag{2}
\]
where $f\in\mathcal H$ is given and one seeks $\phi$.
It turns out that if $\mathfrak{Im}(\lambda)\neq 0$,
then the  inhomogenous equation 
(2) has at least one solution. 
Next,  consider the equation (1).
Let $\rho(\lambda)$ denote the number of linearly independent 
solution in (1). Carelan proived that
 the  $\rho$-function is constant 
when  $\lambda$ varies in
${\bf{C}}\setminus {\bf{R}}$.
Follwing Carelan one says that the kernel $(x,y)$ gives an operator $\mathcal K$ of Class I if
the $\rho$-function is zero. It means that
(2) has unique solutions
for every pair $\lambda,f)$
when $\lambda$ are non-real.
\medskip


\noindent
{\bf{A limit process.}}
Let $\{G_n(x,y)\}$ be a sequece of
symmetric kernel functions which are bounded in Hilbert's sense and
approximate $K$ in the sense that
\[
\lim_{n\to \infty} \int_0^1\, |K(x,y)-G_n(x,y)|^2\, dy=0
\]
for all $x$ outside
a null set. Fix some non-real $\lambda$.
Hilbert's theory entials that if
$f(x)$ is a continuous function, in general complex-valued, then
we find unqiue continuous functions $\{\phi_n\}$
which satisfy the integral equations
\[
\phi_n(x)= \lambda\cdot \int_0^1\, G_n(x,y)\phi(y)\, dy\tag{1}
\]
For a fixed $x$ we consider the complex numbers
$\{phi_n(x)\}$.
Now there exists the set $Z(x)$ of all cluster points, i.e.
a complex number
$z$ belongs to $Z(x)$ if there exists some
sequence $1\leq n_1<n_2<\ldots$ such that
\[
 z=\lim_{k\to\infty}\, \phi_{n_k}(x)
\]
\medskip

\noindent
{\bf{Theorem.}} \emph{For every approximating sequence $\{G_n\}$ as above
the sets $Z(x)$ are either reduced to points or circles in
the complex plane. Moreover, each $Z(x)$ is reduced to a siungleton set
when $\mathcal K$ is of class I.}
\medskip

\noindent
{\bf{Remark.}}
The result below was discovered by Weyl for some special unbounded operators
which arise during the study of second order
differential equations. See ¤ for a comment-.
If $\mathcal K$  is of Class I then
the theorem sbove shows that
each pair of a on-real $\lambda$
and some $f\in\mathcal H$ gives
a unique function $\phi(x)$
which satsfies (2) and
it can be found via a pointwise limit of solutions
$\{\phi_n\}$ to the equations (xx). In this sense the limit process
is robust because one can emply an arbitrary approximating
sequence $\{G_n\}$ under the sole condition that (xx) holds.
This already indficartes that the Case I leads to
a "consistent theory" even if $\mathcal K$ is unbounded.
To make this precise Carleman constructed a unique spectral function
when Case I holds.
More preciely, if
$K(x,y)$ is symmetric and 
Case I holds, then there exists a unique function
$\rho(x,y;\lambda)$ defined for
$(x,y)\in\square$ and every real $\lambda$ such that
\[
\mathcal K(h)(x)=\int_{-\infty}^\infty\, 
\,\frac{1}{\lambda}\cdot\frac{d}{d\lambda} \,
\int_0^1\, \theta(x,y;\lambda)\,h(y)\, dy
\] 
for all
$L^2$-functions $h$.
Concerning the spectral $\theta$-function, Carleman proved that  it
enjoys the same properties as Hilbert's spectral function for bounded 
operators.


\medskip

\noindent
{\bf{Remark.}}
For each fixed $\lambda>0$
one has a bounded self-adjoint operator
on $\mathcal H$ defined by
\[ 
\Theta_\lambda(h)(x)=\int_0^1\, \theta(x,y;\lambda)\,h(y)\, dy 
\]
Moreover, the operator-valued function
$\lambda\mapsto \Theta_\lambda$ has bounded variation over
each intervalÊ$\{a\leq \lambda\leq b\}$
when $0<a<b$.
It means that there exists a constant $C=C(a,b]$ such that
\[
\max\, \sum_{k=0}^M\, ||\Theta_{\lambda_{k+1}}-\Theta_{\lambda_k}||\leq C
\] 
for all partitions
$a=\lambda_0<\lambda_1<\ldots \lambda_{M+1}=b$ and
we have taken operator norms of the differences
$\Theta_{\lambda_{k+1}}-\Theta_{\lambda_k}$ in the sum above.
These bounded variations entail that one can compute the integrals in the right hand side
via the usual method  by Borel and Stieltjes.
\bigskip


\noindent
{\bf{The construction of  spectral functions.}}
When case I holds one constructs the $\rho$-function via a 
robust limit process.
Following [ibid:Chapitre 4] we expose this in ¤ xx.
The strategy is to
regard an approximating sequence $\{G_n\}$ of
Hilbert-Schmidt operator, i.e.
\[
 \iint_\square \, G_N(x,y)^2 \, dxdy<\infty
\]
hold for each $N$.
In this case $\{G_N\}$ are compact opertors.
With $N$ fixed
we get
a discrete sequence of non-zero real numbers
$\{\lambda\nu\}$
which are arragned with increasing avbsolute values and
an orthonormal  family of eigenfunctions $\{\phi_\nu^{(n)}\}$
where
\[
 G_N(\phi_\nu^{(N)})= \lambda\\nu\cdot \phi_\nu^{(N)}
 \] 
hold for each $\nu$.
Of course, the eigenvalues also depend on
$N$.
If $\lambda>0$ we set
\[
\rho_N(x,y;\lambda)=\sum_{0<\lambda_\nu<\lambda}\, \phi_\nu(x)\phi_\nu(y)
\]
\[
\rho_N(x,y;-\lambda)\sum_{-\lambda <\lambda_\nu<0}\, \phi_\nu(x)\phi_\nu(y)
\]
let us notice that for each fixed $n$, the $\lambda$-numbers in (x) stay
away from zero, i.e. there is a constant $c_N>0$ such that
$|\lambda_\nu\geq c_N$. So the function $\rho_N$
vanishes  in a neighborhood of zero.
The spectral theorem applied to symmetric Hilbert-Schmidt operators entails that
\[
\int_{-\infty}^\infty\, \frac{1}{\lambda}\cdot \frac{d}{d\lambda}\,
\rho_N(x,y;\lambda)\cdot h(y)\,  dy
\]
\medskip

\noindent
{\bf{The $\Omega$-kernels.}}
For each $N$ we introduce the function
\[
 \Omega_N(x,y;\lambda)=\int_a^x\int_a^y\, \rho_N(s,t;-\lambda)\, dsdt
\]
Let us notice that Bessel's inequality entails that
\[
 \bigl|\iint_\square\, \rho_N(x,y;\lambda)\cdot h(x)g(y)\, dxdy\bigr|\leq
 ||h||_2|cdot ||g|7_2
 \] 
 for each pair $h,g$ in $L^2[0,1]$.
 \medskip

\noindent
{\bf{Exercise.}}
Conclude from the above
that the variation of $\Omega$
over $[0,x]\times [0,y]$ is bounfed above by
\[
\sqrt{x\cdot y}
\] 
for every pair $0\leq x,y\leq 1$.
In partcular the functions
\[
(x,y)\mapsto \Omega(x,y;\lambda)
\]
are uniformly Hšlder continuous of order $1/2$
in $x$ and $y$ respectively.
\medskip


\noindent
Using the inequalities above
we elave it to the reader to check that there exists
at least one subsequence $\{N_k\}$ such that
the functions $\{\Omega_{N_k}(x,y;\lambda)$
converges uniformly with respect toÊ$x$ and $y$
while $\lambda$ stays in a bounded interval.
When Case I holds one proves that the limit is independent of the subsequence, i.e.
there exists a limit function
\[
\Omega(x,y;\lambda)=\lim_{N\to\infty}\,  
\Omega_N(x,y;\lambda)
\]
From the above the $\omega$-function is again uniformly Hšlder continuous
and
its first order partial derivatives are $L^2$-functions. Moreover, after the passage to
the limit one still
has Bessel's inequality which entails that
\[
\int_{-\infty}^\infty\, 
\frac{d}{d\lambda}\int_0^1 h(x)\cdot \bigl(\frac{\partial}{\partial x}
\int_0^1\, \frac{\partial\Omega(x,y;\lambda)}{\partial y}\cdot h(y))\,dy\bigr )\, dx
\leq \int_0^1\, h(x)^2\, dx
\]
for every $h\in L^2[0,1]$.
\medskip

\noindent
{\bf{Definition.}}
\emph{A Case 1 kernel $K(x,y)$ is closed if equality holds in (*).}
\medskip

\noindent
{\bf{Theorem.}} \emph{A Case I kernel $K(x,y)$ for which 
the equation}
\[ 
\int_0^1\, K(x,y)\cdot \phi(y)\ dy=0
 \] 
 \emph{has no non-zero $L^2$-solution $\phi$ is closed.}
\medskip

\noindent
{\bf{A representation  formula.}}
When (*) hols we can apply to to $h+g$ for every pair of
$L^2$-functiuons anbd since
the Hilbert space $L^2[0,1]$ is self-dual it follows that
for each $f\in L^2[0,1]$ one has the equality
\[
f(x)=\frac{d}{dx}\  
\int_{-\infty}^\infty\, 
\frac{d}{d\lambda}
\int_0^1\, \frac{\partial\Omega(x,y;\lambda)}{\partial y}\cdot f(y))\,dy
\]
almost everywhere with respect to $x$ on $[0,1]$.




{\bf{Remark.}} 
The 
formula (**) shows that it often is important to decide when a Case I kernel
is closed.
Theorem xx gives such a sufficent condition. However, it can
be extended to a quite geneeral result
where one for  can relax the passage to the limit via
suitable linear operators.
The reader may consult   [ibid; page 139-143]
for details. Here we are content to announce the conlsisive result ehich appear
in
[ibid;: page 142].
\medskip

\noindent
{\bf{The $\mathcal L$-family.}}
Let $\xi$ dentoe a paramter which in general depends on several variables, or
represents points in a manifold or  vectors in a normed linear space.
To each $\xi$ we are given  a linear operator
\[ 
L(\xi)\colon f\mapsto L(\xi)(f)
\]
from functions $f(x)$ on $[0,1]$ to new functions on $[0,1]$.
The linear map is weakly continuous, i.e. if
$\{f_\nu\}$ is a sequence in $L^2[0,1]$ which converges weakly to a init function $f$
in $L^2[0,1]$ then
\[ 
\lim L(\xi,f_\nu)\overset{w}\to L(\xi)(f)
\]
Next,
we are given $K(x,y)$ and
the second  condition for $L$ to be in  $\mathcal L$ is that
for each
pair  $\xi$ and $ 0\leq y\leq 1$ there exists
a constant $\gamma(\xi,y)$ which is independent of $\delta$ so that
\[
|L(\xi)(K_\delta(\cdot,y))(x)\leq  \gamma(\xi;y)
\]
where $K_\delta(x,y)$ is the truncated kernel function from (xx)
and in the left hand side we have applied $L(\xi$ to
the function $x\mapsto K_\delta(x,y)$ for each fixed $y$.
Moreover, we have
\[ 
\lim_{\delta\to 0}\, L(\xi)(K(\cdot,y))(x)\overset{w}\to 
\lim_{\delta\to 0}\, L(\xi)(K_\delta(\cdot,y))(x)
\]
where the convergence again holds weakly for
$L2$-functions on $[0,1]$.
Funally the equality below holds for every
$L^2$-function $\phi$:
\[
xxxx
\]








 
 





























 























\newpage







 









\newpage






\bigskip


\centerline{\bf{Moment problems.}}
\bigskip


\noindent
A great inspiration during the development of
unbounded symmetric operators on Hibert spaces
emerged from work by Stieltjes' pioneering article
\emph{Recherches sur les fractions continues}
[Ann. Fac. Sci.  Toulouse. 1894].
The  moment problem
asks for conditions on a
sequence $\{c_0,c_1,\ldots\}$ of positive real numbers
such that there exists a non-negative Riesz measure
$\mu$ on the real line and
\[
c_\nu= \int_{-\infty}^\infty\, t^\nu\cdot d\mu(t)\tag{*}
\] 
hold for each $\nu\geq 0$.
One easily verifies that
if $\mu$ exists then
the Hankel determinants
\[
\begin{pmatrix}
c_0&c_1&\ldots&c_n\\
c_1&c_2&\ldots&c_{n+1}\\
\ldots&\ldots&\ldots&\ldots\\
c_n&c_{n+1}&\ldots&c_{2n}\\
\end{pmatrix}
\]
are $>0$ for every $n=0,1,\ldots$. 
For brevity we say that
$\{c_n\}$ is a positive
Hankel sequence when
the determinants above are $>0$.
It turns out that this confition also is sufficient.
\medskip


\noindent
{\bf{Theorem.}} \emph{For each 
positive Hankel sequence
there exists at least one non-negative Riesz measure such that
(*) holds.}
\medskip


\noindent
{\bf{Remark.}}
The result above is due to Hamburger which extended Stieltjes' original  results where
one seeks non-negative measures supported by
$\{\geq 0\}$.
The moment problem for a positive Hankel sequence is 
said to be determined
if (*) has a unique  solution $\mu$.
Hamburger proved that the determined case holds
if and only if the
the associated continued fractions of $\{c_n\}$
is completely convergent.
See ¤ x below for an account about this convergence  condition.
A "drawback" in the Hamburger-Stieltjes theory
is that it is often  difficult to check
when the associated continued fraction of a positive Hankel sequence
is completely convergent.
So one is led to seek weaker,  but sufficient conditions
in order that (*) has a unique solution $\mu$.
Such a sufficient condition
was established  in Carleman's  monograph
[Carleman 1923. Page 189-220] 
and goes as follows:


\bigskip

\noindent
{\bf{Theorem.}}
\emph{The moment problem of 
a positive Hankel sequence $\{c_n\}$ is determined if}
\[
\sum_{n=1}^\infty\,c_n^{-\frac{1}{n}}=+\infty
\]
\medskip

\noindent
{\bf{Another criterion for  determined moment problems.}}
Constructions of continued fractions and
their associated quadratic forms 
go back to
work by Heine. See  [Handbuch der theorie
der Kugelfunktionen: Vol. 1. part 2]. An excellent account appears also
in the article \emph{Zur Einordnung der Kettenbruchentheorie
in die theorie der quadratischen Formen von
unendlichvielen VerŠnderlichen} [Crelle J. of math. 1914] by
Hellinger and Toeplitz.
Let us recall that a  positive Hankel sequence $\{c_n\}$
 corresponds to a
 quadratic form
 in an infinite number of variables:
 \[
 J(x)=\sum_{p=1}^\infty a_px_p^2-
 2\cdot \sum_{p=1}^\infty b_px_px_{p+1}
\]
where $b_p\neq 0$ for every $p$.
More precisely, the
sequences $\{a_\nu\}$ and $\{b_\nu\}$
arise when
the series
\[
-\bigl[\frac{c_0}{\mu}+
\frac{c_1}{\mu^2}+\frac{c_2}{\mu^3}+\ldots\,\bigr]
\]
is formally expanded into a continuous fraction
\[
\frac{c_0}{a_1-\mu-\frac{b_1^2}{a_1-\mu-\frac{b_2^2}{a_2-\mu}} }
\]
Now there exists 
the infinite  matrix $A$
with diagonal elements $\alpha_{pp}=a_p$ while
\[
\alpha_{p,p+1}= \alpha_{p+1,p}= -b_p\quad\colon p=1,2,\ldots
\]
and all the other elements are zero.
The symmetric  $A$-matrix 
gives a densely defined linear operator on
the complex Hilbert space $\ell^2$.
The following result is proved
[Carleman:1923]:
\medskip

\noindent
{\bf{Theorem.}}
\emph{The densely defined operator $A$ on $\ell^2$ is self-adjoint if and only if
the moment problem for $\{c_n\}$ is determined.}
\bigskip


\centerline {\bf{A general study of $A$-operators.}}
\bigskip

\noindent
Ignoring the "source" of the pair of real sequences $\{a_p\}$ and $\{b_p\}$
we consider a matrix $A$ as above where the sole condition
is that $b_p\neq 0$ for every $p$.
If $\mu$ is a complex number
one seeks infinite vectors
$x=(x_1,x_2,\ldots)$ 
 such that
 \[ 
 Ax=\mu\cdot x\tag{i}
 \]
 It is clear that (i) holds if and only if
 the sequence $\{x_p\}$ satisfies the infinite system of linear equations
 \[
(a_1-\mu)x_1=b_1x_2
\]
\[ 
(a_p-\mu)x_p=b_{p-1}x_{p-1}+ b_px_{p+1}\quad\colon p\geq 2
\]
\medskip

\noindent
Since $b_p\neq 0$ is assumed for every $p$ we see  that
$x_1$ determines the sequence. Here
$x_2,x_3,\ldots$ depend on $x_1$ and the parameter $\mu$.
Keeping $x_1$ fixed while $\mu$ varies
the reader can  verify that
\[ 
x_p=\psi_p(\mu)\quad\colon p\geq 2
\]
where $\psi_p(\mu)$ is a polynomial of degree $p-1$ for each $p\geq 2$.
These $\psi$-polynomials depend on the given
pair
of sequences
$\{a_p\}$ and $\{b_p\}$ and 
with these notations the following
results is  proved in [ibid]:
\medskip


\noindent
{\bf{2. Theorem.}}
\emph{The densely defined operator $A$ on $\ell^2$ is self-adjoint if and only if}
\[
\sum_{p=1}^\infty\, \psi_p(\mu)=+\infty
\]
\emph{for every non-real complex number
$\mu$.}
\medskip


\noindent
{\bf{A more general result.}}
Let $\{c_\nu\}$ be a positive Hankel sequence.
which is determined or not.
If $|rho$ is a non-negative measure which solves the moment problem (*)
we set
\[
\widehat{\rho}(\mu) =\int\, \frac{d\rho(t)}{t-\mu}
\]
It is defined outside the rell axis and yields in particular an analytic funcvtion in
the upper half-plane.
A major result in [Carleman]
gives a sharp inclusion for the values which can be attained
by
these $\widehat{\rho}$ functions while
$\rho$ are non-negative measures which
solve the moment problem.
It is expressed via constructions of discs in the upper half-plane which
arise via a nested limit of discs constructed from a certain family of
Mšbius transformations.
More precisely, to the given Hankel sequence
we have the pair of sequences $\{a_\nu\}$ and $\{b_\nu\}$.
For a fixed $\mu$ in the upper half-plane
we consider the maps:
\[ 
S_\nu(z)=\frac{b_\nu^2}{a_{\nu+1}-\mu-z}\quad\colon \nu=0,1,\ldots
\]
Notice that
\[ 
\mathfrak{Im}(S_\nu(z))=\frac{b_\nu^2\cdot \mathfrak{Im}(\mu+z)}
{|a_{\nu+1}-\mu-z|^2}>0
\]
It follows that $S_\nu$ maps the upper half-plane $U^+$ conformally onto a disc
placed in $U^+$.
\medskip

\noindent
{\bf{Exercise.}}
To each $n\geq 1$ we consider the composed map
\[ 
\Gamma_n=S_0\circ S_1\circ\ldots\circ S_{n-1}
\]
Show that the images $\{C_n(\nu)= \Gamma_n(U^+)\}$
form a decreasing sequence of discs and there exists a limit
\[ 
C(\mu)=\cap\, C_n(\mu)
\]
which either is reduced to a single point or is a closed disc
in $U^+$.
\bigskip

\noindent
{\bf{Theorem.}} \emph{For each $\mu\in U^+$
and every $\rho$-measure which solves the moment problem
one has the inclusion}
\[
\widehat{\rho}(\mu)\subset C(\mu)
\]





























\newpage



\centerline{\bf{The  Neumann-PoincarŽ kernel}}



\bigskip

\noindent
Operator theory was used  at an early stage by
Neumann and PoincarŽ.
So for historic reasons we  expose some facts about
a specific boundary value problem.
Let $\Omega$
be a bounded and connected open set in ${\bf{C}}$
of class $\mathcal D(C^1)$, i.e. the  boundary
$\mathcal C$ is the disjoint union of
closed and continuously differentiable Jordan curves.
To each $p\in\mathcal C$ there exists the inner normal 
${\bf{n}}_i(p)$
of unit length. Set
\[
K(p,q)=\frac{\langle p-q,{\bf{n}}_i(p)\rangle}{|p-q|}
\]
It is clear that the $C^1$-hypothesis entails that
$K$ is a continuous function on
$\mathcal C\times\mathcal C$.
Next, let $M$ be a positive real number.
If $u$ is a real-valued continuous function on
$\mathcal C$
there exists a harmonic function $U$ in
$\Omega$ defined by
\[
U(p)=\int_\mathcal C\, \log \frac{M}{|p-q|}\cdot u(q)\, ds(q)
\]
 where $ds$ is the arc-length measure on
$\mathcal C$.
We choose $M$ so large that it exceeds the diamater of
$\mathcal C$ defined by
$\max\, |q_1-q_2|\,\colon q_1,q-2\in\mathcal C$.
As explained in ¤xx the inner normal derivative of
$U$ is given by the equation
\[
\frac{\partial U}{\partial{\bf{n}}_i}(p)=
-\pi\cdot u(p)-
\int_\mathcal C\, K(p,q)\cdot u(q)\, ds(q)
\]
To solve the boundary  value problem (*)
from the introduction therefore 
amonunts
to find
$u$ which  satisfies the integral equation
\[
-\pi\cdot u(p)-
\int_\mathcal C\, K(p,q)\cdot u(q)\, ds(q)=
a(p)\cdot \int_\mathcal C\, \log \frac{M}{|p-q|}\cdot u(q)\, ds(q)+f(p)\tag{1}
\]
Following the device by Neumann and Poincare we choose $M$ so large that
that the function below defined on $\mathcal C\times\mathcal C$ is everywhere
positive:

\[ 
S(p,q)=a(p)\cdot  \log \frac{M}{|p-q|}+K(p,q)
\]
To $S$ one associaes the integral operator $\mathcal S$ which sends 
$u\in C^0(\mathcal C)$ into
\[ 
\mathcal S_u(p)=\int_\mathcal C\,S(p,q)\cdot u(q)\, ds(q)
\]
Now (1) amounts to find $u$ such that
\[
\mathcal S_u(p)+ \pi\cdot u(p)=-f(p)\tag{2}
\]
Since the kernel function $S$ is everywhere positive
one verifies easily that
the linear operator
on the Banach space 
$C^0(\mathcal C)$ defined by
$u\mapsto \mathcal S_u+\pi\cdot u$
is invertible, i.e. $-\pi$ does not belong to the spectrum of the bounded operator
$\mathcal S$.
Introducing the inverse operator
we solve (2) by
\[
u=-(\pi \cdot E+\mathcal S)^{-1}(f)\tag{3}
\]
\medskip

\noindent
{\bf{Remark.}}
From the above we have solved the boundary value problem
(*) in the introduction by operator
methods. Notice that the solution is found
without
using solutionds to the Dirichlet problem.
\medskip

\noindent
{\bf{A study of spectra.}}
The Neumann-PoincarŽ solution above
shows that the study of 
 the integral operator
$\mathcal K$ defined by
\[
\mathcal  K_u(p)=\int_\mathcal C\, K(p,q)\cdot u(q)\, ds(q)
\]
is crucial. In ¤ xx we shall learn that
$\mathcal K$ is a compact operator on the Hilbert space
$\mathcal H$ of square integrable functions on
$\mathcal C$ with respect to the arc-length measure.
Here one seeks real-valued eigenfunctions
$u$ which satisfy
\[
u(p)=\lambda\cdot \mathcal K_u(p)\tag{**}
\] 
for some real number $\lambda$.
An obstacle is  that
$K$ is not symmetric, i.e.
$K(p,q)\neq K(q,p)$.
Following a construction invented by
PoincarŽ one can find eigenvalues and eigenfunctions via a symmetric kernel function.

\medskip

\noindent
{\bf{The kernel $N(p,q)$.}}
Let $M$ be a positive number which as above
exceeds the diameter of 
$\mathcal C$.
Set
\[
N(p,q)= \int_\mathcal C\, 
K(p,\xi )\cdot \log\,\frac{M}{|q-\xi|}\cdot ds(\xi)
\]
Green's formula applied to a pair of harmonic functions $H_1,H_2$ in $\Omega$
with continuously differentiable boundary values gives the equlity
\[
\int_\mathcal C\,\frac{\partial H_1}{\partial{\bf{n}}_i}(p)\cdot H_2(p)\, ds(p)=
\int_\mathcal C\,\frac{\partial H_2}{\partial{\bf{n}}_i}(p)\cdot H_1(p)\, ds(p)
\]
From this it follows
that the the kernel function $N$ is symmetric, i.e.
$N(p,q)=N(q,p)$.
At the same time we have the operator
$\mathcal S$ defined by
\[
 \mathcal S(u)=\int_\mathcal C\, 
\log\,\frac{M}{|q-\xi|}\cdot u(\xi)\,ds(\xi)
\]
The construction of $N$ entails that its associated integral operator
$\mathcal N$ satisfies the equation
\[
\mathcal N=\mathcal S\circ \mathcal K
\]
This gives a gateway to find
eigenfuntions to the non-symmetric operator
$\mathcal K$.
To begin with $\mathcal S$
is special since the kernel
function $S(p,q)$ is both symmetric and positive.
In the Hilbert space $\mathcal H$ above
we shall learn  in ¤ x that there exists an   orthonormal basis
$\{\phi_n\}$ formed by eigenfunctions which satisfy
\[ 
\mathcal S\phi_n=\kappa_n \phi_n\tag{1}
\] 
where the positive $\kappa$-numbers  tend to zero.
Moreover, each $u\in \mathcal H$
has a Fourier-Hilbert  expansion
\[ 
 u= \sum\,\alpha_n\cdot \phi_n\tag{2}
\]
Next, the symmetric $N$-function yields a doubly indexed and symmtric sequence
$\{c_{jk}\}$ given by
\[
c_{jk}=\iint  \phi_j(p)\phi_k(q)N(p,q)\, ds(p)ds(q)
\]
\medskip

\noindent
{\bf{Theorem.}} \emph{A pair $(u,\lambda)$ solves (**)
if and only if $u$ has an expansion}
\[
u=\sum_{n=1}^\infty \, \alpha_n\cdot \phi_n(p)
\]
\emph{where the sequence $\{ \alpha_n\}$ satisfies the system of linear equations}
\[
\kappa_p\cdot \alpha_p=\lambda\cdot 
\sum_{q=1}^\infty \, c_{qp}\alpha_q\quad\colon p=1,2,\ldots
\]
\medskip


\noindent
{\bf{Remark.}}
The proof is given in ¤ xx where
a crucial step is to show
that
\[
\sum\sum \frac{c^2_{j,k}}{\kappa_j\cdot \kappa_k}<\infty
\] 


\noindent
{\bf{The case when $\mathcal C$ has corner points.}}
When 
$\mathcal C$ has corner points, for example if
$\partial\Omega$ is bordered by piecewise linear and closed Jordan
curves, then
the Neumann-PoincarŽ kernel is
unbounded. Here  
the reduction to the symmetric case is  more involved  and 
relies upon 
quite intricate results which appear in 
[Carleman : Part II: 1916].
Further  analysis remains to be done and
open problems about
the Neumann-PoincarŽ equation 
remains to be settled in dimension $\geq 3$.
So far  it appears that
only the 2-dimensional case 
is well understood by 
results  from  [Carleman :1916].

\newpage

\centerline{\bf{The self-adjoint operator $i\cdot \frac{d}{dx}$.}}

\medskip

\noindent
On the real $x$-line we have the Hilbert space
$\mathcal H= L^2({\bf{R}})$ of complex-valued and square integrable functions.
It contains  $C_0^\infty({\bf{R}})$ as a dense subspace on which
the operator
\[
\frac{d}{dx}\colon f\mapsto f'(x)
\] 
is defined where $f'(x)$ is the derivtive of $f$.
Set $A=i\cdot \frac{d}{dx}$. This gives a densely  defined
operator 
on $\mathcal H$ whose domain of defintion $\mathcal D(A)$
consists of all square-integerable functions $f$
for which the distribution derivative $f'$ again belongs to $\mathcal H$.
Let us remark that
every $f\in\mathcal D(A)$ therefore is locally the
primitive of an $L^1$-function and therefore
locally absolutely continuous.
So in particular $\mathcal D(A)\subset C^0({\bf{R}})$.
The graph of $A$ is the set of pairs $(f,if')\,\colon f\in\mathcal D(A)\}$.
Basic facts in distribution theory
show that  $\Gamma(A)$ is a closed subset of
$\mathcal H\times\mathcal H$. See ¤ xx for details.
Hence $A$ is densely defined
and closed.
Now we seek Neumann's spectrum $\sigma(A)$.
To begin with, if $\lambda$ is a complex number
and $A(f)= \lambda\cdot f$ for some
$f\in \mathcal H$ we have
\[
i\cdot f'=\lambda\cdot f
\]
Basic facts about ordinary differential equations entail that
$f$  is a constant times
$e^{-i\lambda x}$
and this exponential function has absolute value one
and cannot belong to $\mathcal H$. So if 
$E$ is the identity operator then
$\lambda\cdot E-A$ is injective for all complex numbers $\lambda$, i.e.
the  "point spectrum" of $A$ is empty.
However, the invertibility in Neumann's sense
requires more conditions on the densely defined operator
$\lambda\cdot E-A$, i.e its range must be  dense and there
exists a constant $c>0$ such that
\[
||\lambda\cdot f-if'||_2\geq c\cdot ||f||_2\quad\colon f\in\mathcal D(A)\tag{1}
\]
To analyze when these two conditions hold
we use the Fourier transform.
When $f\in C_0^\infty({\bf{R}})$ we have
the inversion formula
\[
i\cdot f'(x)=
-\frac{1}{2\pi}\cdot\int\, e^{ix\xi}\cdot \xi\cdot \widehat{f}(\xi)\, d\xi
\]
Fourier's inversion formula gives
\[
(\lambda\cdot E-A)(f)(x)=
\frac{1}{2\pi}\cdot\int\, e^{ix\xi}\cdot (\lambda+\xi)\cdot \widehat{f}(\xi)\, d\xi
\]
If $\lambda=a+ib$ with $b\neq 0$ we have
$|\lambda+\xi)|^2\geq b^2$ for all real $\xi$.
Applying Plancherel's equality we concludue that
\[
||\lambda\cdot f-if'||_2\geq b\cdot ||f||_2\colon f\in\mathcal D(A)
\]
Hence (1) hols for every non-real $\lambda$.
There remains to show that the range of
$(\lambda\cdot E-A)$ is dense in the Hilbert space $\mathcal H$
when $\mathfrak{m}(\lambda)\neq 0$.
If the density fails the orthogonal complement of the range is
non-zero and we find a non-zero function 
$g\in\mathcal H$ such that
\[ 
\langle \lambda\cdot f-if', g\rangle=
\int\,  (\lambda\cdot f-if')\cdot \bar g\, dx=0\quad\colon f\in\mathcal D(A)\tag{3}
\]
Thjs holds in particular when
$f$ are test-functions
and using thr notion of distribution derivatives
we see that (2) entails that
the $g$-function satisfies the equation
\[
\lambda\cdot g= i\cdot \frac{dg}{dx}
\]
From (xx) above it follows that   $g=0$ and hence the
range of
$(\lambda\cdot E-A)$ must be dense which finishes  the proof of the
inclusion
\[
 \sigma(A)\subset {\bf{R}}
\]
\medskip

\noindent
{\bf{The equality $A=A^*$.}}
By  (2) and Parseval's equality for $L^2$-norms under the Fourier transform
it follows that
$|mathcal D(A)$ consists of all $f\in L^2$ such that
$\xi\cdot \widehat{f}(\xi)$ is square integrable on the $\xi$-line.
Next, for a pair $f,g$ in $C_0^\infty$ a partial integration gives
the equality
\[
\langle Af, g\rangle=
\langle  f, Ag\rangle
\] 
which means that the densely defined operator $A$ is symmetric.
Next, by definition a function $g$ belongs to
$\mathcal D(A^*)$ if there exists a constant $C(g)$ such that
\[
|\langle Af, g\rangle\leq C(g)\cdot ||f||_2
\quad\colon f\in\mathcal D(A)
\]
Passing to the Fourier transform
and using Parseval's equality this is equivalent to the condition that
there exists a constant $C$ such that
\[
||\xi\cdot \widehat{f}\cdot\widehat{g}||_2\leq 
C\cdot ||\widehat{f}||_2\quad\colon f\in\mathcal D(A)
\]
Since the family
$\{\widehat{f}\,\colon f\in\mathcal D(A)$ is dense in
the $L^2$-space on the $\xi$-line this entails that
$\xi\cdot \widehat{g}$ is locally square integrable and hence
$g$ belongs to $\mathcal D(A)$.
Hence we have proved the equality
\[
\mathcal D(A)=
\mathcal D(A^*)
\]
which means that $A$ is a densely defined and self-adjoint operator
on $\mathcal H$.



\newpage

\centerline {\bf{Further examples.}}


\medskip

\noindent
{\bf{2. An ugly example}}.
Let $\{a_{pq}\}$
be a doubly-indexed and symmetric sequence of
real numbers,  i.e. 
$a_{pq}=a_{qp}$
hold for each pair of positive integers.
Moreover we assume that 
\[
 \sum_{q=1}^\infty\, a_{pq}^2<\infty
\quad\colon p=1,2,\ldots\tag{*}
\]
Consider the Hilbert space
$\ell^2$ whose vectors are complexes sequences
$\{\xi_p\}$ such that
\[
\sum_{q=1}^\infty\, |\xi_q|^2<\infty\tag{i}
\]
The Cauchy-Schwarz inequality entails that if
$\{\xi_p\}\in\ell^2$ then the series
\[
\sum_{q=1}^\infty\,a_{pq}\cdot \xi_q
\]
converges for each $p$.
However, the imposed conditions on
the $a$-sequence does in general not imply that
\[
\sum_{p=1}^\infty\, |\sum_{q=1}^\infty\,a_{pq}\cdot \xi_q|^2<\infty
\]
In an article from 1920,
Carleman  constructed 
a sequence $\{a_{pq}\}$ whch satisfies (*) and at the same time violates
the wellknown  fact in
linear algebra which asserts
that eigenvalues of a symmetric matrix with real elements are real.
Namely, in  Carleman's   sequence 
$\{a_{pq}\}$ there exists a complex  vector
$\xi\in\ell^2$ with norm one such that
\[
\xi_p=i\cdot \sum_{q=1}^\infty\,a_{pq}\cdot \xi_q\quad\colon p=1,2,\ldots\tag{ii}
\]
while the series (i) has value one.
We give the construction in ¤ xx and remark that
this example shows that  care must be taken when one
considers
linear
equations in an inifinite number of variables.
Namely, with the $\xi$-vector as in (ii)
we  have the limit formula:
\[
\lim_{N\to\infty}\, 
\sum_{p=1}^{p=N}\, |\xi_p|^2=1
\]
Next,  (ii)  entails that
\[
1=\lim_{N\to\infty}\, 
i\cdot \sum_{p=1}^{p=N}\sum_{q=1}^\infty\,
a_{pq}\xi_q\cdot\bar\xi_p=
i\cdot \sum_{q=1}^\infty\,\xi_q\cdot \sum_{p=1}^{p=N}a_{pq}\bar\xi_p
\]
For each $q$ we set
\[
\xi_q(N)=i\cdot  \sum_{p=1}^{p=N}a_{qp}\xi_p
\]
Since $\{a_{pq}\}$ is symmetric and real we have
\[
\sum_{p=1}^{p=N}a_{pq}\bar\xi_p=
i\cdot   \sum_{p=1}^{p=N}a_{qp}\bar\xi_p=-\bar\xi_q(N)
\]
and the equality $i^2=-1$ entails 
that
\[
-1=\lim_{N\to\infty}\, \sum_{q=1}^\infty\,\xi_q\cdot \bar \xi_q(N)\tag{iii}
\]
At the same time we have limit formulas:
\[
\lim_{N\to\infty}\,\bar \xi_q(N)=\bar \xi_q\quad\colon q=1,2,\ldots\tag{iv}
\]
But in spite of (iii) the results above give
\[
\lim_{N\to\infty}\,\xi_q\cdot (\bar \xi_q+\bar \xi_q(N)=0
\]
which at first sight seems to contradict
the limit formulas above. However,
the convergence in (iv)  holds  for each fixed
$q$, but not uniformly with respect to $q$.
This   is the reason why the 
"obscure limits" above appear when (ii) holds.
\medskip















\bigskip

\noindent
{\bf{3. The dual of $\ell^\infty$.}}
Consider
the Banach space
$\ell^1$ whose vectors are sequences of $\{x_n\}$
of complex numbersi indexed by positive integers
with the norm
$||x||=\sum\, |x_n|$.
The dual space  is $\ell^\infty$  which consists  of bounded vectors. It
contains the  subspace $\ell^\infty_0$ of  
sequences $\{\xi_n\}$ where only finitely many 
$\xi_n\neq 0$,
This is not a dense subspace for if
$\xi^*$ is the sequence with $\xi^*_n=1$ for every $n$ its distance to
$\ell_0^\infty$ is one.
On the other hand $\ell^\infty_0$ is dense in the
\emph{weak-star topology}
which by definition is the
weakest - or coarsest - topology on $\ell^\infty$ for which the functions
\[ 
\xi\mapsto\xi(x)= \sum\, \xi_nx_n
\] 
are continuous for every  $\ell^1$-vector $x$.
This leads us to consider
the dual space of $\ell^\infty$. It turns out that it consists 
of Riesz
measures on the compact space $\beta{\bf{Z}}$ 
obtained as the maximal ideal space of the 
Banach algebra $\ell^\infty$. One  refers to
$\beta{\bf{Z}}$
as the Stone-Cech compactification of the integers where
${\bf{Z}}$ appears as  a dense subset 
and at the same time there exist non-zero Riesz measurs $\mu$ on
$\beta{\bf{Z}}$ without any point mass at the integers.
Every such Riesz measure, regarded as an element in the dual 
of $\ell^\infty$ vanishes identically on the subspace
$\ell_0^\infty$.
The result is that the bi-dual
\[ 
(\ell^1)^{**}=\mathfrak{i}(\ell^1)\oplus
\mathfrak{M}(\beta{\bf{Z}}\setminus {\bf{Z}})
\]
where the last term is the space is Riesz measures on
the compact topoligical space
$\beta{\bf{Z}}\setminus {\bf{Z}})$.

\medskip

\noindent
{\bf{4. Domains of definition for
the Laplace operator.}}
Let $D$ be the unit disc in ${\bf{R}}^2$
and consider the Laplace operator $\Delta=\partial_x^2+\partial_y^2$.
In the Hilbert space
$L^2(D)$ of square-integrable complex valued functions
there exists
the  subspace $V$
of $L^2(D)$ with the property that for each
$\phi \in V$ its Laplacian taken in the distribution sense
belongs to $L^2(D)$. The necessary and sufficient condition for
this to hold is that there is a constant $C(\phi)$ such that
\[
|\iint_D\,\Delta(f)\cdot \phi \, dxdy|\leq C(\phi)\cdot ||f||_2
\quad\colon f\in C_0^\infty(D)\tag{1}
\]
where $||f||_2$ is the $L^2$-norm and as indicated 
$f$
are test-functions with compact support in
$D$.
In  fact, since Hilbert spaces are self-dual and $C_0^\infty(D)$ is dense in
$L^2(D)$ the inequality (1) gives a unique $\psi\in L^2(D)$ such that
\[
\iint_D\,\Delta(f)\cdot \phi \, dxdy=
\iint_D\,f\cdot\psi \, dxdy
\quad\colon f\in C_0^\infty(D)\tag{2}
\]
which  means that $\psi=\Delta(\phi)$ in the distribution sense.
Hence one has
a linear operator
\[
 T\colon \phi\mapsto \Delta(\phi)
\] 
The domain of definition $V=\mathcal D(T)$ contains test-functions and is therefore
dense in $L^2(D)$.
One easily verifies that the graph of $T$ taken in the product
$L^2(D)\times L^2(D)$ is closed.
Hence $T$ is a densely defined and closed
linear operator. The kernel consists of harmonic functions
in $D$ which  are square integrable.
So if one wants an injective and densely defined operator
it is necessary to shrink the domain of definition.
To achieve this we introduce the logarithmic
kernel
\[
L(z,\zeta)= \frac{1}{2\pi}\cdot \log\,\frac{|z-\zeta|}{|1-\bar\zeta z|}
\]
It gives the linear operator
$\mathcal L$
defined on $L^2(D)$ by:
\[
\mathcal L(\phi)(z)=\iint _D\,L(z,\zeta)
\cdot \phi(\zeta)\, d\xi d\eta
\tag{3}
\]
Here $L(z,\zeta)$ is square integrable on the product $D\times D$
which means that
$\mathcal L$ is a  Hilbert-Schmidt operator on
$L^2(D)$ and in particular compact.
Moreover, since
$L(z,\zeta)=0$ when $|z|=1$ and $|\zeta|<1$
one easily verifies that
$\mathcal L(\phi)$ is  a continuous function on
the closed disc with boundary values zero on the unit circle.
Moreover one has  the equality
\[
\Delta(\mathcal L(\phi))=\phi\quad\colon \phi\in 
L^2(D)\tag{4}
\]
Hence the composed operator $\Delta\circ \mathcal L$
is the identity on $L^2(D)$ and
 Stokes theorem gives
\[
f=\mathcal L(\Delta(f))\quad\colon f\in C_0^\infty(D)
\]
In particular the range of
$\mathcal L$ is a dense subspace of 
$\mathcal L(L^2(D))$ and from the above we see that if
$g=\mathcal L(\phi)$ for some
$\phi\in L^2(D)$ then
\[
\iint_D\,\Delta(f)\cdot g \, dxdy=
\iint_D\,f\cdot \phi\, dxdy
\quad\colon f\in C_0^\infty(D)
\]
We conclude that
$\mathcal L(L^2(D))$ is a subspace of
$\mathcal D(T)$ and we have the linear operator
\[
 \Delta\colon g\mapsto \Delta(g)\quad\colon
 g\in\mathcal L(L^2(D))
 \]
With this restricted domain of definition one has
\[
\mathcal L\circ\Delta(g)= g \quad\colon g\in\mathcal L(L^2(D))
\]
So here $\Delta$ becomes injective
and at the same time
(4) holds.
\medskip

\noindent
{\bf{The closure property.}}
There remains to show that
the chosen domain of definition  yields  a closed operator which
amounts
to show that
the graph
\[
\Gamma=\{
(g,\Delta(g))\,\colon g\in\mathcal L(L^2(D))\}
\]
The closed graph property relies upon the
following crucial result:

\medskip

\noindent
{\bf{4.1 Theorem.}}
\emph{An $L^2$-function $g$ belongs to
$\mathcal L(L^2(D))$ if and only if
there exists a constant $C(g)$ such that}
\[
|\iint_D\,\Delta(f)\cdot \phi \, dxdy|\leq C(g)\cdot ||f||_2
\quad\colon f\in C^\infty(\bar D)\tag{*}
\]
\medskip

\noindent
{\bf{Remark.}}
Notice the distinction from (1) where (*)
only is imposed when
$f$ have compact support in $D$. So  (*)  is more restrictive
and  the inclusion
$\mathcal L(L^2(D))\subset V$ is strict.
The theorem
above
will be  proved in
¤ xx and
entails that
$\Delta$ with the chosen domain of definition is 
an unbounded self-adjoint operator.


\medskip


\noindent
{\bf{5. The complex Hilbert transform}}.
Identify the complex $z$-plane with
the 2-dimensional real $(x,y)$-space.
Now we have the Hilbert space
$L^2({\bf{C}})$ whose vectors are complex-valued and
square integrable functions in the $(x,y)$-plane.
If $g$ is a continuously differentiable function with
compact support there exists a limit
\[
G(z)=\lim_{\epsilon\to 0}\, \iint_{|z-\zeta|>\epsilon}\, 
\frac{g(\zeta)}{(z-\zeta)^2}\, d\xi d\eta\tag{5.1}
\]
exists for every $z\in {\bf{C}}$.
In fact, using Stokes theorem we show in ¤ xx tht
\[
G(z)=\iint\,\frac{\frac{\partial g}{\partial \zeta}(\zeta)}{z-\zeta}
d\xi d\eta
\]
where the last integral exists since
$\frac{\partial g}{\partial \zeta}$ is a continuous function with compact support and
$(z-\zeta)^{-1}$
is locally integrable in the $(\xi,\eta)$-space
for each fixed $z$.
The complex Hilbert transform is defined by the linear operator:
\[ 
T_g(z)= \frac{1}{\pi}\, G(z)
\] 
It turns out that
$T$ is an isometry with respect to the $L^2$-norm, i.e. 
\[
\iint\, |T_g(z)|^2\, dxdy=
\iint\, |g(z)|^2\, dxdy\quad\colon g\in C_0^1({\bf{C}})\tag{5.2}
\]
There are several proofs of (5.2). One relies upon the Fourier transform
and Parseval's theorem which is exposed in ¤ xx.
Another proof employs an abstract reasoning and goes as follows:
Let
$\mathcal H$ be a Hilbert space
and $\Phi$ us a subset of vectors
with the property that
the subspace of vectors in
$\mathcal H$ of the form
\[
c_1\phi_1+\ldots+c_k\phi_k\quad\colon 
\langle\phi_j,\phi_i\rangle=0\colon j\neq i
\]
is dense
in $\mathcal H$. Thus, we assume that finite linear combinations of pairwise
orthogonal $\Phi$-vectors is dense.
Let us now
consider a 
linear operator
$T$ on
$\mathcal H$ 
such that the following   hold:
\[
||T(\phi)||= ||\phi||\quad\colon \phi\in \Phi\tag{*}
\]
\[
\langle\phi_1,\phi_2\rangle=0\implies
\langle T(\phi_1),T(\phi_2)\rangle=0
\quad\colon\, \phi_1,\phi_2\in \Phi
\tag{**}
\]

\medskip

\noindent
{\bf{Exercise}}
Show that (*)-(**) imply that $T$ is an isometry, i.e.
$||T(g)||= ||g||$  for every
$g\in\mathcal H$.

\medskip

\noindent
Apply the  result above  to the
complex Hilbert transform where
$\Phi$ is  the family of vectors in $L^2({\bf{C}})$
given
by characteristic functions of dics in
${\bf{C}}$. It  is clear that  this family satisfies
the density condition above.
Now we study the
action by the Hilbert transform on such  functions.
Let $z_0\in{\bf{C}}$ and $r_0>0$ be given and 
$\phi$  is the characteristic function
of the disc of radius $r_0$ centered at $z_0$.
\medskip

\noindent
{\bf{5.1 Proposition.}}
\emph{One has $T_\phi(z)=0$ when $|z-z_0|< r_0$ while}
\[
T_\phi(z)=\frac{r_0^2}{(z-z_0)^2}\quad \colon
|z-z_0|>r_0
\]

\medskip

\noindent
\emph{Proof.}
After a translation we can take $z_0=0$ and via a dilation of the scale
reduce the proof to the case $r_0=1$.
If $|z|>1$
we have
\[
T_\phi(z)=\frac{1}{\pi}\iint_D \, \frac{d\xi d\eta}{(z-\zeta)^2}
=\frac{1}{\pi z^2}\iint_D \frac{d\xi d\eta}{(1-\zeta/z)^2}
\]
Expand 
$(1-\zeta/z)^{-2}$ in a power series of $\zeta$ and notice that
\[
\iint_D \,\zeta^m\, d\xi d\eta=0\quad\colon m=1,2,\ldots
\]
Then we see that $T_\phi(z)= z^{-2}$.
There remains to show that
$|z|<1$ gives $T_\phi(z)=0$.
To prove this we use the differential 2-form
$d\zeta\wedge d\bar\zeta$ and there remains to show that
\[
\lim_{\epsilon\to 0}\, 
\iint_{D_\epsilon}\frac{d\zeta\wedge d\bar\zeta}{(z-\zeta)^2}=0\tag{i}
\]
where  $D_\epsilon= D\setminus \{|\zeta-z|\leq \epsilon\}$.
Now $\partial_\zeta((z-\zeta)^{-1})=(z-\zeta)^{-2}$
and Stokes theorem gives
(i) if
\[
\int_{|\zeta|=1}\, \frac{d\bar\zeta}{z-\zeta}-
\lim_{\epsilon\to 0}\, \int_{|\zeta-z|=\epsilon}\, \frac{d\bar\zeta}{z-\zeta}=0
\]
In the first integral we use the
series expansion 
$(z-\zeta)^{-1}=-\sum_{n=0}^\infty \, \zeta^{-n-1}\cdot z^n$
and get a vanishing since
\[
\int_{|\zeta|=1}\, \zeta^{-n-1}\, d\bar\zeta=0\quad\colon n=0,1,\dots
\]
The verification that the limit as $\epsilon\to 0$
in the second integral vanishes is left to the reader.


\medskip


\noindent
The Proposition  entails that
\[
||T(\phi)||^2=
r_0^4\cdot \iint_{|z|>r_0}\, \frac{dxdy}{|z|^4}=
r_0^4\cdot 2\pi\int_{r_0}^\infty \,\frac{dr}{r^3}=\pi\cdot r_0^2
\]
Since $||\phi||^2=\pi\cdot r_0^2$ we conclude that
$||T(\phi)||= ||\phi||$.
The verification that (**)  holds when
$\phi_1,\phi_2$ are characteristic functions of disjoint discs
is left as an exercise.






















\newpage

\centerline{\bf{A. Some results in functional analysis.}}

\bigskip

\noindent
The subsequent material  exposes some  results 
in functional analysis with special attention given to
linear operators on Hilbert spaces.
Proofs of some of the assertions below appear in ¤ 11.
\bigskip




\centerline{\bf{A.1 The Riezs-Nagy theorem.}}
\medskip

\noindent
Let $\mathcal H$ be a Hilbert space.
A linear operator $U\colon \mathcal H\to \mathcal H$
is  unitary if
\[
\langle Ux,Uy\rangle=
\langle x,y\rangle
\] 
hold for all pairs $x,y$ in
$\mathcal H$.
Next, a  
linear operator $A$ on  $\mathcal H$
of norm one is called a   contraction.
A family of contractions  arises as follows:
Let $\mathcal H_1$ be another Hibert space which contains
 $\mathcal H$ as a closed subspace.
 There exists the orthogonal projection $P$ from
 $\mathcal H_1$ onto $\mathcal H$ and
 if $U$ is a unitary operator on $\mathcal H_1$
 we get a linear operator on $\mathcal H$ defined by
 \[ 
 A=P\circ U
 \] 
 In other words, we take $x\in \mathcal H$
 and  apply $U$ to get $U(x)\in\mathcal H_1$ and
 $P$ projects this vector back to
 $\mathcal H$.
 Since the unitary operator $U$ preserves norms
 it follows that
 $A$ is a contraction.
 A  result due to F. Riesz and Nagy asserts that
 every contraction on $\mathcal H$ arises from
 a pair $U,P$ as above.
 Moreover, they proved that the pair can be chosen so that 
 \[
 p(A)=P\circ p(U)
 \] 
 hold for
 every polynomial in $A$.
 We prove this in ¤ 11.xx.
 
 



\bigskip


\centerline {\bf{A.2 The infinitesmal generator of a unitary semi-group}}.

\medskip

\noindent
A  result 
due to
M.H. Stone  about
strongly continuous semi-groups of unitary operators 
goes
as
follows:
There is given a doubly-index  sequence
of functions $\{c_{pq}(t)\}$, where $p,q$ are positive
integers and the $c$-functions are defined on $\{t\geq 0\}$
which satisfies the following:
First the Hermitian condition holds, i.e. 
$\bar c_{qp}(t)= c_{p,q}(t)$ for all pairs of integers.
In addition  
the following   hold
for all $s,t\geq 0$ and every pair $p,q$.
\[
\sum_{q=1}^\infty\, |c_{qp}(t)|^2=1\quad\colon\quad p=1,2,\ldots
\quad\text{and}\quad 
\sum_{q=1}^\infty\, c_{qp}(t)\cdot \overline {c_{qr}}(t)=0\quad\colon\quad p\neq r\tag{i}
\]
\[
c_{qp}(t+s)=
\sum_{j=1}^\infty\, c_{qj}(s)\cdot c_{jp}(t)\tag{ii}
\]
\[
\lim_{t\to 0}\, \sum_{q=1}^\infty\, \bigl|\, \xi_q- \sum_{p=1}^\infty\, c_{qp}(t)\xi_p
\,\bigr|^2=0\quad\text{for every}\quad \xi\in \ell^2\tag{iii}
\]
where $\ell^2$
is the Hilbert space
$\ell^2$ whose vectors are complex sequences
$\{\xi_p\}$ such that
$\sum\,| \xi_p|^2<\infty$.


\noindent
From now on Stone's condition hold.
For every 
pair of positive numbers $s.t$ and each $\xi\in \ell^2$ we set:
\[
D_\xi(s,t)=
\sum_{q=1}^\infty\, 
\bigl |\frac{1}{t}\cdot 
\sum_{p=1}^\infty\, c_{qp}(t)\xi_p-
\frac{1}{s}\cdot 
\sum_{p=1}^\infty\, c_{qp}(s)\xi_p+(\frac{1}{s}-\frac{1}{t})\xi_q\,\bigr |^2
\]
\newpage

\noindent
{\bf{Stones Theorem.}}
\emph{There exists a  dense subspace
$\mathcal H_*$ of the Hibert space $\ell^2$
such that}
\[
 \lim_{(s,t)\to (0,0)}\, D_\xi(s,t)=0\quad\colon\quad \xi\in\mathcal H_*
\]
 \emph{Moreover, to each $\xi\in\mathcal H_*$ we get the limit vector
 $\eta= \{\eta_q\}$ where}
 \[
 \eta_q=\lim_{t\to 0}\, \frac{1}{t}\,\cdot 
\bigl[\,  \sum_{p=1}^\infty c_{qp}(t)\xi_p- \xi_q\,\bigr]
\]
\emph{ Finally, the linear operator}
{\[
A(\xi)=i\cdot \eta
\]
\emph{is a densely defined
self-adjoint operator.}
\bigskip


\centerline {\bf{A.3 Unbounded self-adjoint operators.}}
\medskip

\noindent
Let  $\mathcal H$ be a Hilbert space
and consider a closed and densely defined 
linear operator $A$ which in general is unbounded.
One says that $A$  is  symmetric
if
\[ 
\langle Ax,y\rangle= \langle x,Ay\rangle
\quad\colon\,  x,y\in\mathcal D(A)\tag{0.1}
\]
Let $E$ be  the identity operator on
$\mathcal H$. 
If $x\in\mathcal D(A)$
and $\lambda$ is a complex number the symmetry gives:
\[
 ||(\lambda\dot E-A)(x)||^2=
 |\lambda|^2\cdot ||x||^2+||Ax||^2-
 2\cdot \mathfrak{Re}\,\lambda\cdot \langle x,Ax\rangle 
\] 
The Cauchy-Schwarz inequality gives:
\[
|\langle x,Ax\rangle|\leq ||x||\cdot ||Ax||\implies
||(\lambda\dot E-A)(x)||^2\geq |\mathfrak{Im}\,\lambda|^2\cdot ||x||^2\tag{0.2}
\]

\medskip

\noindent
Since $A$ has a closed graph
the inequality
(0.2) implies that if $\mathfrak{Im}\,\lambda\neq 0$ then
the operator $B=\lambda\cdot E-A$
sends $\mathcal D(A)$ into a closed subspace of $\mathcal H$.
Since Hilbert spaces are self-dual
the range $B(\mathcal D(A))$
is therefore $\neq \mathcal H$ if and only if its orthogonal complement is 
$\neq\emptyset$.
A  vector $y$ belongs  to $B(\mathcal D(A))^\perp$ if
\[
\lambda\cdot\langle x,y\rangle=
\langle Ax,y\rangle
\quad\,\colon\quad  x\in\mathcal D(A)\tag{*}
\]
So if 
(*) has no solutions $y\neq 0$  when
$\mathfrak{Im}\,\lambda\neq 0$  then 
$\lambda\cdot E-A$ is  surjective for every non-real complex number
and together with the inequality (0.2) we see that
$\lambda\cdot E-A$ is invertible in the sense of (0.0.1).
Hence it has a resolvent and
we find the operator
valued analytic function $R_A(\lambda)$
defined outside the real axis in the complex $\lambda$-plane.
\medskip

\noindent
{\bf{Remark.}}
In ¤ 9 we  study
symmetric and densely defined operators 
satisfying the above. 
A notable fact is that if (*) has no solution
$x\neq 0$ when
$\lambda$ is not real, then
the symmetric operator $A$ is equal to its adjoint $A^*$.
The detailed proofs appear in ¤ 9.







\bigskip


\centerline{\bf{A.4 Differential operators}}.
\medskip

\noindent
Pioneering work by  G.D. Birkhoff carried out around 1905
motivated and inspired  subsequent studies of unbounded
densely defined operators on Hibert spaces. Let
\[ 
P(t,\frac{d}{dt})=\sum_{j=0}^{j=m}\, a_j(t)\cdot \frac{d^j}{dt^j}
\] 
be a differential operator where we 
$\{a_j(t)\}$ are complex-valued polynomials.
The adjoint operator $P^*$ is defined by the equation
\[
\int\, P(f)\cdot \bar g\, dt=
\int\, f\cdot\overline {P^*( g)}\, dt
\] 
for each  pair of test-functions $f$ and $g$. 
If $P=P^*$ we say that $P$ is symmetric.
Assume this and consider some bounded interval $(a,b)$ which gives 
the Hilbert space
$L^2(a,b)$.
Now $P$ yields  a densely defined but unbounded operator on
this Hilbert space   denoted by $T_{ab}$.
We shall learn  that there exists
the adjoint operator $T_{ab}^*$ which also is densely defined
on $L^2(a,b)$.
However, the symmetry may be lost under this construction and
the search for  self-adjoint extensions of
$P$ on $L^2(a,b)$ leads to an involved theory.
Results concerned with
spectral theory of ordinary differential operators
are foremost due to Birkhoff,  
Weyl, Titschmarsh and Kodaira. These authors  also found
various boundary conditions  in
order to achieve self-adjoint extensions of
$P$. A notable fact is that when $P$ is a given symmetric ODe-operator,
then the  class of self-adjoint extensions to the Hilbert space $L^2(a,b)$ 
can  depend upon the interval $(a,b)$. We refrain from
a detailed discussion. The
reader may consult
chapter XIII from volume 2  in [Dunford-Schwartz] which offers an 
extensive account
about spectral theory for ordinary differential equations.


\bigskip





\newpage


 
 





\centerline {\bf{A.7 Moment problems.}}
\medskip

\noindent
In 1894 Stieltjes established
necessary and sufficient conditions for the existence of solutions
to the following equation: There is given a
sequence $\{c\uuu n\}$ of non-negative real numbers.
One asks if there exists a non-negative measure $\mu$ on
the real $x$-line such that
\[
\int_{-\infty}^\infty\, x^n\cdot d\mu(x)= c_n
\] 
hold for each $n=1,2,\ldots$.
No specific bound on $\{c_n\}$ is
imposed and Stieltjes solution relies upon properties 
of
continued fractions  associated to 
$\{c_n\}$.
The moment problem 
inspired
later studies
in operator theory.
Elegant results appear in  Stone's 
book  \emph{Linear operators on 
Hilbert spaces and their applications to analysis} (AMS: 1932).
For example, Stone proved a
uniqueness result which goes as follows: Denote by $\mathcal P_*$
the class of non-negative measures $\mu$ on the real line such 
\[
\int\, x^{2n}\cdot d\mu(x)<\infty\quad\colon\quad n=1,2,\ldots
\]
To each such measure $\mu$ one gets  a unique sequence of polynomials
$\{P_n(x)\}$, where  $P_n$ has degree $n$ and leading coefficient $>0$
while
\[
\int_{-\infty}^\infty\, P_n(x)P_m(x)\cdot d\mu(x)=0
\quad\colon\quad n\neq m
\]
A measure $\mu\in \mathcal P_*$ is of the Stone type if
\[
\sum_{n=0}^\infty\,|P_n(x+iy]^2=+\infty
\]
hold for every non-real complex number $z=x+iy$
with 
$y\neq 0$. Now Stone's uniqueness theorem asserts the following:
\medskip

\noindent
\emph{A pair
 $\mu,\nu$  of 
Stone type with equal   moments
for allÊ$n$ must be identical, i.e.  
$\mu=\nu$.}




\bigskip




\centerline {\bf{A.8 Optimal control theory.}}
\medskip



\noindent
Problems in the calculus of variation can
lead to severe doubts  about the existence of extremal solutions. This
was put forward by Weierstrass and a historic example is LamŽ's equation where
tentative  proofs of existence of solutions occured
in work by  Kovavelsky and Volterra but  
It was not until 1920
that
Zeilon settled the existence of solutions to LamŽ's equations
using advanced  Fourier analysis. In 
retrospect we mention that Zeilon's proof already used distribution-theoretic methods.
There also occur
optimization problems where
the control is restricted to vector-valued functions
with
range in a compact polyhedron  $\Pi$  in
${\bf{R}}^n$. In such problems
one often arrives at    
Bang-bang solutions where
the extremal control switches a finite number of times
between  extreme points of the polyhedron $\Pi$. In this pioneering work
which led to a general maximum principle in control problems,
Pontryagin
employed
functional analysis where one allows
competing families of control functions in  spaces  
of measurable functions.
The outcome is
a Bang-bang solution which is piecewise constant while its   existence
is   demonstrated  via a "detour into  larger spaces". So
functional analysis has  a wide range of applications
in optimization theory.







\bigskip



\centerline {\bf{A.10 $L^p$-inequalities.}}

\medskip


\noindent
Many results which originally  were 
constrained to  specific situations
can be extended  when
notions in
functional analysis are adopted. An  example
is  a theorem 
from the article [Hšrmander-1960]
where  singular integrals
are  treated  in a  general context.
Here is the set up: Let $B_1$ and $B_2$ be two Banach spaces
and $n$ some positive integer.
Let $K(x)$ be a function which for every 
$x\in{\bf{R}}^n$ assigns a vector 
in the Banach space
$L(B_1,B_2)$ of continuous linear operators from $B_1$ to $B_2$.
One only assumes that $K$ is a continuous function, i.e. it 
need not be linear.
If $f(x)$ is a continuous  $B_1$-valued function defined in
${\bf{R}}^n$ with compact support there exists
the convolution integral
\[
\mathcal Kf(x)= \int_{{\bf{R}}^n}\, K(x-y)(f(y))\, dy
\]
To be precise, with $x$ fixed in
${\bf{R}}^n$ the right hand side is
a welldefined $B_2$-valued integral which exists
because  $K(x-y)$ as a linear operator sends the
$B_1$-vector $f(y)$ into $B_2$, i.e. the integrand
in the right hand side is a $B_2$-valued function
\[ 
y\mapsto K(x-y)(f(y))
\] 
which can be integrated with respect to $y$ and the resulting
integral  yields
the $B_2$-vector in the left hand side. When $x$ varies,
$x\mapsto \mathcal Kf(x)$
becomes a $B_2$-valued function.
Following [ibid] we
impose two   conditions on $K$ where
norms on the three Banach spaces $L(B_1,B_2),B_1,B_2$ appear.
We say that $K$ satisfies the Hšrmander condition if there
exist positive constants $A$ and $C$ such that
the following hold for every real number $t>0$:
\[ 
\int_{|x|\geq 1}\, ||K(t(x-y))-K(tx)||\, dx\leq C\cdot t^{-n}
\quad\text{for all}\quad |y|\leq 1\tag{1}
\]
where the left hand side
employs 
the operator norms of $K$  defined for pairs of points  $tx$ and
$t(x-y)$ in ${\bf{R}}^n$. In addition to (1) we impose
the following $L^2$-inequality for every function $f$ with the 
same constant $C$ as above:
\[
\int_{{\bf{R}}^n}\, ||\mathcal Kf(x)||_2^2\, dx\leq
C^2\cdot \int_{{\bf{R}}^n}\,||f(x)||_1^2\, dx\tag{2}
\]
Here one has used norms on $B_1$ respectively $B_2$ during the integration.
Hšrmander  extended    Vitali's  Covering Lemma in ${\bf{R}}^n$
to a similar covering  principle on arbitrary normed spaces 
to prove the following weak-type inequality:
\medskip

\noindent
{\bf{Theorem.}}
\emph{There exists an absolute constant $C_n$ which depends on 
$n$ only such that for every
pair  of Banach spaces $B_1,B_2$ and every linear operator $K$
which satisfies (1-2), the following hold for every
$\alpha>0$:}
\[
\text{vol}_n(\{x\in{\bf{R}}^n\,\colon\,  ||\mathcal Kf(x)||_2 >\alpha\})\leq
\frac{C_n\cdot C}{\alpha}\cdot \int_{{\bf{R}}^n}\, ||f(x)||_1\, dx
\]


\noindent
{\bf{Remark.}}
This result 
has a wide range of applications
when it is combined  with
interpolation theorems  due to Markinkiewicz and Thorin.
For example, classical results which involve $L^p$-inequalties 
during the passage to Fourier transforms or other   kernel functions
can be put into a general  frame where one  employs
vector-valued functions rather than
scalar-valued functions. Typical examples occur when
$K$ sends real-valued functions
to vectors in a Hilbert space, i.e. here 
$B_1$ is  the 1-dimensional real line  and
$B_2=\ell^2$.
So Hšrmander's  result constitutes a veritable propagande for
learning  general notions in functional analysis. The
idea to regard vector-valued
functions
was of course  considered at an early stage. 
An  example is
a theorem due to Littlewood and Paley
which goes as follows: Let $f(x)$ be a function on the real line 
such that both $f$ and $f^2$ are integrable.
To each integer $n\geq 0$
we set
\[
f_n(x)=
\bigl|\int_{2^{n-1}}^{2^n}\, e^{ix\xi}\cdot \widehat f(\xi)\, d\xi\,\bigr|+
\bigl|\, \int_{-2^{-n}}^{-2^{n-1}}\, e^{ix\xi}\cdot \widehat f(\xi)\, d\xi\,\bigr|
\]
Then it is proved in [L-P] that for each
$1<p\leq 2$ there exists a constant $C_p\geq 1$ such that
\[
C_p^{-1}||f||_p\leq\cdot \int_{-\infty}^\infty\, \bigl(\sum_{n=0}^\infty\, f_n(x)^2\bigr)^{\frac{2}{p}}
\, dx\leq C_p\cdot ||f||_p\tag{*}
\]
where $||f||_p= \bigl(\int\, |f(x)|^p\, dx\bigr)^{\frac{1}{p}}$
is the $L^p$-norm of $f$.
Hšrmander's theorem can be used to  give an elegant proof of (*)
which has the merit that the use
a suitable vector-valued  operator during the proof
becomes
transparent. 




\bigskip









\centerline
{\bf B. Hilbert's  spectral theorem for bounded self-adjoint operators.}
\bigskip

\noindent
The  theory about integral equations
created  by Fredholm
led to 
Hilbert's   result from  1904 
which we  begin to describe.
Let $\mathcal H$ be a Hilbert space
and denote by 
$L(\mathcal H)$
the set of all bounded linear operators on $\mathcal H$.
Every $T\in L(\mathcal H)$ has its operator norm
\[
||T||=\max_x\,||T(x)||\quad
\text{maximum over vectors of norm}\,\,\,\leq 1
\]
Next, let $A$ be
a bounded
self-adjoint operator  on $\mathcal H$ whose compact spectrum is denoted by
$\sigma(A)$.
A crucial fact is that the self-adjointness implies that
\[
||A||^2=||A^2||
\]
and passing to higher powers it follows that
the operator norm
$||A||$ is equal to the spectral radius defined by
\[
\lim_{n\to\infty}\, ||A^n||^{\frac{1}{n}}
\]
Using this equality
the Operational Calculus in ¤ 7
will show that there exists
an algebra isomorphism from
the sup-norm algebra $C^0(\sigma(A))$
into a closed subalgebra $\mathcal A$ of $L(\mathcal H)$, i.e. 
each  continuous function $g$ on the compact spectrum
$\sigma(A)$ gives  a bounded linear operator $G$. 
Moreover, it is an
isometry which means that
\[ 
|g|_{\sigma(A)}= ||G||\tag{*}
\] 
where the left hand side is the maximum of $|g|$ over $\sigma(A)$.
Next, since  $A$ is self-adjoint  $\sigma(A)$
is a compact subset of the real line
where we use $t$ as the variable.
If $g(t)=c_0+c_1t+\ldots+c_mt^m$
is a polynomial, the operational calculus shows that
$G=E+c_1A+\ldots+c_mA^m$
where $E$ is the identity operator on
$\mathcal H$.
By Weierstrass' theorem the set of polynomials
a dense subalgebra of $C^0(\sigma(A))$
and hence $\mathcal A$ is the closure
in $L(\mathcal H)$ of the
algebra formed by all polynomials of $A$.
\medskip

\noindent
{\bf{B.1 The spectral measure.}}
The algebra isomorphism  gives
a map
from the product
$\mathcal H\times\mathcal H$ to the space of Riesz measures on
$\sigma(A)$ which to every
pair $(x,y)$ in $\mathcal H$ assigns a Riesz measure
$\mu_{x,y}$
such that
\[
\langle g(A)x,y\rangle=\int_{\sigma(A)}\,
g(t)\cdot d\mu_{x,y}(t)\tag{**}
\] 
holds for every $g\in C^0(\sigma(A))$.
The isometry  (*)   implies
that the total variation of $\mu_{x,y}$ is bounded by
$||x||\cdot ||y||$ for every pair $x,y$.
Now Borel's integrals give
a larger subalgebra of $L(\mathcal H)$. Namely, for
every bounded Borel function $g(t)$ on $\sigma(A)$
the integrals in the sense of Borel 
exist in the right hand side of (**) for each 
pair $x,y$ in $\mathcal H$.
In this way
the $g$-function
gives a
bounded linear operator $G$ such that
\[
\langle G(x),y\rangle=\int_{\sigma(A)}\,
g(t)\cdot d\mu_{x,y}(t)\quad\text{hold for all pairs}\quad
x,y\tag{***}
\] 


\noindent
This yields  an algebra isomorphism from
the algebra $\mathcal B^\infty(\sigma(A))$
of bounded Borel functions to a subalgebra of $L(\mathcal H)$ 
denoted by
$B(\mathcal A)$.
Again the map $g\mapsto G$ is an isometry
and in this extended algebra 
we can construct
an ample family of self-adjoint operators.
Namely, for every Borel subset $\gamma$
of $\sigma(A)$ we can take its characteristic function
and  get the bounded linear operator $\Gamma$.
By the Operational Calculus the
spectrum of $\Gamma$ is equal to the closure of $\gamma$.
Moreover, $\Gamma$ is a self-adjoint operator and  commutes with
$A$.
In particular we can consider  partitions of
$\sigma(A)$. Namely, choose $M>0$ so that
$\sigma(A)\subset [-M,M]$ and $M$ is outside $\sigma(A)$.
With a large integer $N$
we consider the half-open intervals
\[
\gamma_\nu=\bigl [-M+\frac{\nu}{N}\cdot M, -M+\frac{\nu+1}{N}\cdot M\bigr]
\quad\colon 0\leq \nu\leq 2N-1
\]
Then $\Gamma_0+\ldots+\Gamma_{2N-1}=E$ and
we also get the decomposition
\[
 A=A_0+\ldots+A_{2N-1}\quad
 \colon\,A_\nu=A\Gamma_\nu\tag{1}
\]
Above $\{\Gamma_\nu\}$ gives a  \emph{resolution of the identity}
where (1) means that $A$ is a sum of 
self-adjoint operators where every individual operator has a spectrum
confined to an interval of length
 $\leq \frac{1}{N}$. This 
constitutes 
Hilbert's Theorem for bounded self-adjoint operators.



\bigskip



\centerline {\bf C. Carleman's spectral theorem for unbounded self-adjoint operators}
\bigskip

\noindent
In a note from May 1920 [Comptes rendus], Carleman 
described  a procedure to handle unbounded symmetric
operators
expressed via integral kernels which fail to satisfy
Fredholm's  conditions. The  theory was presented
in the monograph 
\emph{Sur les Žquations singulires ˆ noyau
rel et symmŽtrique} from
1923 published by  Uppsala University.
In addition to [ibid]
the reader may also consult Carleman's plenary talk [Carleman]
at the Scandinavian
Congress held at Copenhagen in 1925
where the relation to
the new spectral theory with Fredholm's
pioneering discoveries is discussed and illuminated by
various examples.
For historic reasons  we give a citation from
the introduction  in [ibid]
where Carleman
expressed his admiration for Fredholm's work:
\emph{Peu du dŽcouvertes mathŽmatiques ont ŽtŽ donnŽes
par leur auteur sous une forme si achevŽe que la dŽcouverte
de la solution de l«Žquation intŽgrale}
\[ 
\phi(x)=\lambda\cdot \int_a^b\,K(x,y)\phi(y)\, dy+ f(x)
\]
\emph{par M. Fredholm. Les nombreuses application de cette thŽorie admirable
ont pourtant amŽnŽ un grand nombere 
de rechereches concerntant le cas —u le noyaue $K(x,y$ est non borneŽ.}

\bigskip




\noindent
{\bf{C.1 An ugly example.}}
Following 
in [Carleman 1923 ] we
give  an example which
illustrates that
new phenomena can occur for unbounded symmetric operators.
On the unit interval $[0,1]$ we have  an orthonormal family of
functions $\psi_0,\psi_1,\ldots$ where
$\psi_0=1$ is the identity and
$\psi_1(x)= -1$ on $(0,1/2)$Êand +1 on $(1/2,1)$. For each 
$n\geq 2$ we set:
\[
\psi_n(x)=-2^{\frac{n-1}[{2}} \,\colon\,
1-2^{-n+1}\leq x< 1-2^{-n}
\quad\text{and}\quad
\psi_n(x)=2^{\frac{n-1}{2}}\,\colon\, 1-2^{-n}<x<1
\]
while $\psi_n(x)=$ when $0<x< 1-2^{-n+1}$.
If $\{a_p\}$ is a sequence of real numbers we define
the kernel
function  on $[0,1)\times [0,1)$
by
\[
K(x,y)=\sum\, a_p\cdot \psi_p(x)\psi_q(x)\tag{i}
\]
It is clear that $K$
is symmetric and the associated operator 
\[
\mathcal K(u)(x)=\int_0^1\, K(x,y)u(y)\, dy
\]
is  defined on $L^2$-functions $u$ supported by
$0\leq x\leq x_*$ for every  $x_*<1$ and therefore  densely defined.
Choose a sequence $\{a_p\}$ such that
the positive series.
\[
\sum_{p=0}^\infty \, \frac{2^p}{1+a_p^2}<\infty\tag{ii}
\]
This convergence  means that
the sequence $\{a_p\}$ must have a high rate of growth so
the kernel function (i) becomes  turbulent when
$x$ and $y$ approach 1.
\medskip

\noindent
{\bf{Exercise.}}
Show that (ii) entails that there exists an $L^2$-function
$\phi(x)$ such that $\mathcal K(\phi)$ also is an $L^2$-function and
\[
\phi= i\cdot \mathcal K(\phi)
\]
If necessary, consult [ibid: page 62-66] for a demonstration. 



\bigskip


\centerline {\bf{A favourable case.}}
\bigskip

\noindent
We begin to 
expose Carleman's result for "wellbehaved"
integral operators.
Let $K(x,y)$ be a complex-valued function defined in
the open unit square$\{0 <x,y<1\}$
satisfying the hermitian condition
\[ 
K(y,x)= \bar K(x,y)
\]
Assume  that for all $x$ outside a nullset $\mathcal N$
one has a finite integral
\[ 
\int_0^1\, |K(x,y)|^2\, dy\tag{1}
\]
If $\phi(y)$ is an $L^2$-function, 
the Cauchy-Schwartz inequality gives:
\[
\int_0^1\, K(x,y)\phi(y)\, dy\quad\text{exists for all} 
\quad x\in (0,1)\setminus \mathcal N
\]


\medskip

\noindent
{\bf{C.2 Definition.}} \emph{The hermitian kernel $K$ is of type
I if
the homogeneous equation}
\[
\phi(x)=\lambda\cdot \int_0^1\, K(x,y)\phi(y)\, dy
\]
\emph{has no non-trivial $L^2$-solution $\phi(y)$ when
$\mathfrak{Im}\,\lambda\neq 0$.}


\newpage


\noindent
{\bf{C.3 Theorem.}}
\emph{If $K$ is of type I  the equation}
\[
\phi(x)=\lambda\cdot \int_0^1\, K(x,y)\phi(y)\, dy+f(x)\tag{*}
\]
\emph{has a unique $L^2$-solution $\phi$ for every
$f\in L^2$ and every non-real $\lambda$. Moreover
the $\phi$-solution satisfies:}
\[
\int_0^1\, |\phi(x)|^2\,dx\leq \frac{|\lambda|^2}{\mathfrak{Im}(\lambda)^2}
\cdot  \int_0^1\, |f(x)|^2\,dx\tag{**}
\]
\medskip

\noindent {\emph{Proof}}.
To get the existence we use the truncated kernels
$\{K_n(x,y)\}$
where $K_n(x,y)=K(x,y)$ when
$K(x,y)|\leq n$ and otherwise zero.
Given  $f(x)\in L^2[0,1]$ and a non-real
$\lambda$, the Hilbert-Schmidt theory from ¤ xx gives
a unique $\phi_n\in L^2$ such that
\[
\phi_n(x)=\lambda\cdot \int_0^1\, K_n(x,y)\phi_n(y)\, dy+f(x)\tag{i}
\]
Mutltiplying with $\bar\phi_n$ it follows that
\[
\frac{1}{\lambda}\, 
 \int_0^1\, \bar\phi_n(x)(\phi_n(x)-f(x))\, dx=
 \iint_\square \, K_n(x,y)\bar\phi_n(x)\phi_n(y)\, dxdy
\] 
Since $K_n$ is hermitian the right hand side is real  and taking imaginary
parts we obtain

\[
\bigl(\frac{1}{\lambda}-\frac{1}{\bar\lambda}\bigr)\cdot
 \int_0^1\, |\phi_n(x|^2\,dx)=
\frac{1}{\lambda}\cdot
 \int_0^1\, \bar \phi_n(x)f(x) dx)
 -\frac{1}{\bar \lambda}\cdot
 \int_0^1\, \phi_n(x)\bar f(x) dx)\tag{ii}
\] 
and the Cauchy-Schwarz inequality 
gives
\[
 \int_0^1\, |\phi_n(x)|^2\,dx\leq \frac{|\lambda|^2}{\mathfrak{Im}(\lambda)^2}
 \cdot  \int_0^1\, |f(x)|^2\,dx\tag{iii}
\]
Hence the $L^2$-norms of $\{\phi_n\}$ are uniformly bounded
and we can
find a subsequence which converges weakly to an
$L^2$-function $\phi$ whose $L^2$-norm again is bounded
by the right
hand side in (iii). 
Now the assumption that $K$ is of type I
entials that the weak limit is unique.
Hence the whole sequence $\{\phi_n\}$ is weakly convergent
and one verifies
that $\phi$ solves the inhomogeneous equation (*).



\bigskip










\noindent
{\bf{C.4 Spectral resolution.}}
Let $K(x,y)$ be a hermitian kernel of type I.
Hilbert's theorem applies to the bounded
kernels $\{K_n\}$
and give for each pair $f,g\in L^2[0,1]$
a Riesz measure
$\mu^n_{f,g}$ supported by the compact real spectrum of
the kernel operator defined by $K_n$.
In [Carleman]
it is  proved that
the sequence
$\{\mu_{f,g}^n\}$ converges weakly to a
Riesz-measure $\mu_{f,g}$ supported by the real line
and Hilbert's operational calculus applies when
one intergates continuous functions
$\phi(t)$ with compact support, i.e. every
such $\phi$ yields a bounded
linear operator
$\Phi$ on $L^2[0,1]$ such that
\[
\int_0^1\, \Phi(f)\cdot \bar g\, dx=
\int\, \phi(t)d\mu_{f,g}(t)
\]
hold for every pair $f,g$Êin $L^2[0,1]$.


\bigskip



\bigskip



\centerline {\bf{D. The Bohr-Schršdinger  equation.}}
\medskip

\noindent
In 1923 quantum mechanics had not yet appeared so
the studies in  [Carleman] were 
concerned with singular  integral equations, foremost
inspired from  work by Neumann, PoincarŽ,
Fredholm and Volterra.
The creation of quantum mechanics gave new challenges for
mathematicians.
The interested reader should   consult the
lecture held  by Niels Bohr at the Scandianavian congress in mathematics
held in Copenhagen 1925 where he
speaks  about  the   interplay between
the new physics and 
"pure" mathematics. 
Bohr's  lecture  presumably inspired Carleman when he
some years later resumed 
work from [Car 1923].
Recall that the fundamental point in Schršdinger's theory
is the hypothesis on energy levels which correspond to 
orbits in Bohr's theory of atoms. For a very good account about
the physical background
the reader may consult
Bohr's
plenary talk when 
he received the Nobel Prize in physics 1923.
Mathematically the Bohr-Schršdinger theory
leads to the  equation
\[ 
\Delta\phi+2m\cdot\bigl( E-U\bigr)\bigl(\frac{2\pi}{h}\bigr)^2\cdot \phi=0\tag{*}
\] 
Here $\Delta$ is the Laplace operator in the 3-dimensional $(x,y,z)$-space,
$m$ the mass of a particle and $h$  Planck's constant
while   $U(x,y,z)$ is a potential function.
Finally $E$ is a parameter and one seeks values on $E$
such that (*) has a solution $\phi$
which belongs to $L^2({\bf{R}}^3)$.
Let us   cite an excerpt   from Carlemans  lectures in Paris at 
Institut Henri PoincarŽ held in 1930:
\medskip

\noindent
\emph{Dans ces dernires annŽes l'’nteret de la question qui nous
occupe a considŽrablement augmentŽ.
C'est en effet
un instrument mathŽmatique 
indispensable pour development de la mechanique moderne crŽe par
M.M. de Brogile, Heisenberg et Schršdinger. Etude de l'Žquation
integrale:}
\[ 
\phi(x)= \lambda\cdot \int_a^b\, K(x,y)\phi(y)dy+f(x)
\quad\colon\lambda\in {\bf{C}}\setminus {\bf{R}}
\]
\medskip

\noindent
The theory from [Carleman :1923] applies  to the following
PDE-equations attached to a second order differential operator
\[ 
L=\Delta+c(x,y,z)\quad\colon
\Delta=\partial_x^2+\partial_y^2+\partial_z^2\tag{**}
\]
where $c(x,y,z)$ is a real-valued function.
The $L$-operator is  densely defined and  symmetric on the
dense subspace formed by
test-functions $u$ in
${\bf{R}}^3$. The problem is to find conditions on
the $c$-function in order that
the  Case I  from ¤ B  occurs.
The following
sufficiency result is proved in [ibid]:
\medskip

\noindent
{\bf{D.1 Theorem }}
\emph{Let $c(x,y,z)$ be a continuous and real-valued function
such that there is a constant $M$ for which}
\[
\limsup \uuu{x^2+y^2+z^2\to \infty}\, c(x,y,z)\leq M
\]
\emph{Then  Case I holds for the operator $\Delta+c(x,y,z)$.}
\medskip

\medskip

\noindent{{\bf{Example.}}
Considers a potential function:
\[ 
W(p)=\sum\,\frac{\alpha_k}{|p-q_k|}+\beta
\] 
where $\{q_k\}$ is a finite subset of
${\bf{R}}^3$ and the $\alpha$-numbers and $\beta$ are real and positive.
With $c=W$ we get Case I and hence
solutions to the Schršdinger equation can be established
via a robust limit process. See ¤¤ xx for details.

\bigskip


\noindent
{\bf{Further comments.}} The literature about
the Schršdinger equation and  other
equations which emerge from quantum mechanics is 
extensive. 
For the 
source of quantum mechanics
the reader should first of all consult 
the plenary talks by Heisenberg, Dirac and Shršdinger
when they received the Nobel prize in
physics. 
Apart from physical considerations the reader
will find
expositions where explanations
are given in a mathematical framework.
Actually Heisenberg was
sole winner 1931 while Dirac and Schršdinger shared the
prize in 1932. But they visited Stockholm together in
December 1932.
\medskip

\noindent
For  mathematician who wants to become acquainted with
quantum physics the eminent text-books by Lev Landau
are recommended. Especially 
\emph{Quantum mechanics: Non-relativistic theory}
in Vol. 3.
The
relativistic case  is treated in later volums of [L-L]. Here
one employs Heisenberg's matrix representation and
Dirac's  equations are used to study radiation phenomena.
In the introduction to
[ibid: Volume 3]
Landau inserts the following remark:
\emph{It is of interest to note
thst the complete mathematical formalisim
of quantum mechnaics was constructed by W. Heisenberg
and E. Schršdinger in 1925-26, before the discovery
of the uncertainty principle which revealed the physical
contents of this formalism.}
\medskip


\noindent
In the non-relativistic situation one studies
foremost 
wave equations of
Schršdinger's type. The  mathematical foundations
were laid in Schršdinger's article 
\emph{Quantizierung als Eigenwertproblem} from 1926
In ¤ XX from Special Topics we describe another of Schršdinger's equations which
led to a veritable challenge in the "world of mathematics"
which remains  quite open.
\bigskip

\noindent
{\bf{Final remark.}}
After [Carleman 1923] an alternative
proof of the spectral theorem for unbounded operators on
Hilbert spaces was given by  
J. von Neumann's   in the article \emph{Eigenwerttheorie Hermitescher 
Funktionaloperatoren} from 1929.
Neumann''s account seems  to have become
more fashion by  readers who prefer a  "formal style".
A merit in Neumann's work
is that 
some measure theoretic technicalities  
in  Carleman's proof
can be omitted. On the other hand 
it  is often necessary to establish
formulas of a measure theoretic character in order to apply
the spectral theorem. An example
is  Carleman's  solution to the 
Bohr-Schršdinger equation which he presented  during  lectures at Sorbonne
in 1930. Here
the Laplace operator  in
${\bf{R}}^3$ is transformed to a suitable integral operator. After this
estimates which lead to solutions
in $L^2){\bf{R}}^3)$ are obtain via
solutions to Neumann's boundary value problem in
increasing balls in
${\bf{R}}^3$.
Let us also remark
that
separable  Hilbert spaces  can be embedded into $L^2$-spaces.
So
the restriction to integral operators covers most applications.
In Chapter 1 from [Carleman] the reader may find a very general construction
of a family of 
spectral functions associated with Hermitian kernels which need not satisfy 
the condition from Definition B.2 above.


\medskip

\noindent
{\bf{Examples.}}
From a historic point of view we mention that various unbounded
symmetric operators
were studied in connecttion with differential operators
in work by
Birkhoff, Picard and Weyl around 1910.
Picard's equation was already described in
the introduction.
More generally one can consider kernel functions of the form
\[ 
K(x,y)=H_1(|x-y|)+ H_2(|x+y|)
\]

\noindent
which give linear operators on
$L^2({\bf{R}}$.
In [Carleman: Chapitre 4 ] it is proved that
$K$
is of class I when
\[
 \int_{-\infty}^\infty\, H_\nu(s)^2\,  ds<\infty\tag{i}
\] 
hold for $\nu=1,2$.
To prove this one seeks solutions to the integral equation
\[ 
\phi(x)=\lambda\cdot
 \int_{-\infty}^\infty\,K(x,y)\phi(y)\, dy+f(x)
\]
where $f$ is a given $L^2$-function on the real line
and $\lambda$ in genereal is a complex number.
In ¤ xx we shall expose material from [Carleman 1923] and construct
Neumann's sresolvent 
to the integral operator $K(x,y)$ which after
settles why 
(i) entails that it is self-adjoint.
We remark that in this construction
one employs specific solutions to
Picard's equation. 
The result above
can then be  applied  to analyze
integral operators in ${\bf{R}}^3$
defined by kernel functions
\[
S(p,q)= F(|p-q|)
\]
where
\[ 
\int_0^\infty\, F(r)^2 \cdot r\, dr<\infty 
\]
Another  interesting class of integral operators are given by
\[ 
K(x,y)=\frac{P(x,y)}{Q(x,y)}
\]
Here $P$ is a polynomial of some degree 
$m\geq 1$, and $Q(x,y)$ is homogeneous of degree $m+1$ which 
takes real and positive values when
$x$ and $y$  both are $>0$.
Already the special case when
\[
K(x,y)=\frac{1}{x+y}
\]
leads to some non-trivial conclusions.
In ¤ xx we prove that the spectrum
on the Hilbert space of square integrable functions
in the positive quadrant of
${\bf{R}}^2$ is the unbounded interval $[\pi^{-1},+\infty)$.





 
 








\newpage

\centerline{\bf{E. Application to a dynamical system.}}

\bigskip

\noindent
Using the spectral theorem
a rigorous proof of the Ergodic Hypothesis in
Statistical Mechanics
was given by Carleman
at seminars held at Institute Mittag-Leffler
in May 1931. Here is
the situation: There is given an $n$-tuple of
$C^1$-functions $A_1(x),\ldots,A_n(x)$ where
$x=(x_1,\ldots,x_n)$ are points in ${\bf{R}}^n$.
Let $t$ be a time variable and consider the differential system
\[
\frac{dx_k}{dt}= A_k(x_1(t),\ldots,x_n(t))\quad\colon\quad 1\leq k\leq n\tag{1}
\]
Assume that there exists a compact hypersurface
$S$ in ${\bf{R}}^n$
such that
if $p\in S$ and ${\bf{x}}_p(t)$ is the 
vector-valued solution to (1) with initial condition
${\bf{x}}_p(0)=p$, then
${\bf{x}}_p(t)$ stay in $S$ for every $t$.
The uniqueness for solutions to the differential systems above gives
for every $t$ a bijective map $p\mapsto {\bf{x}}_p(t)$ from $S$ onto itself. It is denoted by
$\mathcal T_t$ and we  notice that
\[
 \mathcal T_s\circ \mathcal T_t=\mathcal T_{s+t}
\]

\noindent
In addition to this we assume that there exists an invariant measure $\sigma$ on $S$
for the $\mathcal T$-maps. In other words, a non-negative measure
$\sigma$ such that
\[ 
\sigma(\mathcal T_t(A))=\sigma(A)
\] 
hold for every $\sigma$-measurable set. For the applications it suffices to consider the
case when $\sigma$ is absolutely continuos, i.e. a positive
continuous function times the area measure on $S$.
So now we have the Hilbert space $L^2(\sigma)$ of complex-valued
measurable functions $U$ on $S$ for which
\[ 
\int_S\, |U(p)|^2\cdot d\sigma(p)<\infty
\]
next, on the Hilbert space $L^2(\sigma)$ there exists
the following densely defined symmetric operator:
\[
U\mapsto i\cdot \sum_{\nu=1}^{\nu=n}\, A_\nu\cdot \frac{\partial U}{\partial x_\nu}\tag{*}
\]
It is easy to verify that \emph{Case 1} holds for this operator
and hence we can apply the spectral theorem.
In particular,  to each 
a pair of $L^2$-functions $U$ and $V$ we consider
the following mean-value integrals over time intervals $[0,T]$:
\[
J_T(U,V)=\frac{1}{T}\cdot \int_0^t\,
\bigl[U(\mathcal T_t(p))\cdot V(p)\cdot d\sigma(p)\bigr ]\cdot dt \tag{*}
\]

\medskip

\noindent
Using the spectral theorem from [Carleman 1923], the result below was
proved in 
[Carleman 1931]:
\medskip

\noindent
{\bf{Theorem.}}
\emph{Let $\{\omega\uuu\nu\}$
be an orthonormal basis in $\mathcal H$.
For each pair $U,V$ in $L^2(\sigma)$ one has the equality}
\[
\lim_{T\to\infty}\, J_T(U,V)=
\sum_{\nu=1}^\infty\, \langle \omega_\nu,U\rangle \cdot
 \langle \omega_\nu,V\rangle
 \]
\emph{where}
\[
 \langle \omega_\nu,U\rangle =\int_S\, \omega_\nu(p)\cdot U(p)\cdot d\sigma(p)
 \] 
\emph{and similarly with $U$ replaced with $V$.}
\bigskip

\noindent
{\bf{Remark.}}
Let $\mathcal H_*$ be the space  of $L^2(\sigma)$-functions
which are $\mathcal T$-invariant, i.e. $L^2$-functions $\omega$ satisfying
$\mathcal T_t(\omega)=\omega$  for all $t$.
When
$\mathcal H_*$ is reduced to the  
one-dimensional space of constant functions
the theorem above implies  that almost every trajectory 
comes close to every point in $S$ which confirms  the ergodic condition.
\medskip


\noindent
{\bf{Birkhoff's almost everywhere convergence result.}}
As pointed out  in [1932: page 80 ] where Carleman 
gave an affirmative answer to
a question raised by PoincarŽ in his  lecture
\emph{L'avŽnir dŽs mathematiques}
held at Rome in 1908,  the article [xxx] by Birkhoff published
in December 1931
contains    deeper results which establish  properties which hold  
almost everywhere.
For example, given a point $p_0\in S$
and a measurable subset  $\Omega\subset S$
one can study the
avergage time interval when the particle 
which starts at $p_0$ when $t=0$ visits $\Omega$.
Thus, for $T>0$ we denote by $\tau_{p_0;\Omega}(T)$
the total time of visits in $\Omega$
as $0\leq t\leq T$.
With these notations Birkhoff proved that
\[
 \lim_{T\to\infty}\frac{\tau_{p_0;\Omega} (T)}{T}\tag{*}
\] 
exists for almost all $p_0\in S$.
This impressive result was  the starting point for  extensive studies in
Ergodic Theory which has stayed as an 
active subject.
Many 
subtle problems dealing with almost everywhere convergence properties
have been established,.
Studies of
semi-groups of transformations which are
adapated to stochastic differential
equations is an extensive  subject where
the scenario is almost
"unlimited" since global considerations
occur while
a process  can be  governed by
many different differential systems.
A typical example from recent literature is the article
\emph{Ergodicity of the 2D Navier Stokes equations with degenerate
stochastic forcing} by Hairer and Mattingley.


\newpage




\newpage


\centerline{\bf{11.6 Numerical range.}}
\medskip


\noindent
Let $A$ be a closed and densely  defined linear operator on
the Hilbert space $\mathcal H$.
Its numerical range was introduced by Toeplitz and Hausdorff:

\medskip

\noindent
{\bf{11.6.1 Definition.}}
\emph{The numerical range is the subset of ${\bf{C}}$ defined by}
\[
\text{Num}(A)=\{ \langle Ax,x\rangle\quad\colon
x\quad\text{unit vector in}\quad\mathcal H\}
\]


\noindent
{\bf{11.6.2 Proposition.}}
\emph{The numerical range is  a convex set.}
\medskip

\noindent
\emph {Proof.}
If $\alpha,\beta$ are complex numbers and $B=\alpha A+\beta E$
it is clear that
$\text{Num}(B)$ is the image of 
$\text{Num}(A)$ under 
the linear map $z\mapsto \alpha z+\beta$.
So it siuffices to 
show that when 0 and 1 belong to 
$\text{Num}(A)$,
then the real interval $[0,1]$ stays in the numerical range.
So now we have two vectors $f,g$ for which
\[
\langle Af,f\rangle=0\quad\colon\quad  \langle Ag,g\rangle=1\tag{i}
\]
 To prove this we consider the family of vectors
 \[ 
 \xi= f+se^{i\theta}g
 \] 
where $s\geq 0$ is real and $0\leq\theta\leq 2\pi$.
It follows that
 \[
\langle A\xi,\xi\rangle =s^2+s\bigl
(e^{i\theta}
 \langle Ag,f\rangle+
e^{-i\theta}
 \langle Af,g\rangle\bigr)
 \]
\medskip


\noindent
Above we have the complex-valued function
\[
\theta\mapsto  
e^{i\theta}
 \langle Ag,f\rangle+
e^{-i\theta}
 \langle Af,g\rangle
\]
Since $e^{i\pi}=-1$ its value has opposed signs
at 0 and $\pi$ which  implies that
the imaginary part by the usual  mean-value theorem has some
zero $0\leq \theta_*\leq\pi$.
So with  $\xi_*=\xi= f+se^{i\theta_*}g$ it follows that
\[ 
\langle A\xi_*,\xi_*\rangle =s^2+s\cdot \rho
\quad\text{where}\quad \rho\in{\bf{R}}
\]
The right hand side is zero when $s=0$ and tends to $+\infty$ when
$s$ increases and hence this its range contains $[0,1]$ which give
$s$-values for which  $f+se^{i\theta_*} g$ and hence 
numerical values at every point in $[0,1]$.
\bigskip

\noindent
Next, let $A$ be a bounded linear operator. In this case it
is clear that $\text{Num}(A)$ is a bounded set.
However, it is in general not closed. See ¤ below for an example.
The following inclusions hold:

\medskip

\noindent
{\bf{11.6.3 Theorem.}} \emph{For every bounded operator $A$ one has}

\[
\sigma(A)\subset
\overline{\text{Num}(A)}\subset\widehat{\sigma(A)}
\]
\emph{where the right hand side is the convex hull of $\sigma(A)$.}
\bigskip

\noindent
\emph{Proof.}
TO BE GIVEN....











\centerline {\bf{11.5 Stones theorem.}}


\bigskip


\noindent

\noindent
{\bf{11.3.2 Unitary semi-groups.}}
Specialize the situation above to the case when
$B$ is a Hilbert space $\mathcal H$ and
$\{U_t\}$ are unitary
operators.
Set $T=\xi_*$ so that
\[ 
B(x)=
\lim_{t \to 0}\, \frac{U_tx-x}{t}\quad\colon\quad x\in\mathcal D(T)
\]
If  $x,y$ is a pair in $\mathcal D(B)$ we get
\[
\langle Bx,y\rangle=
\lim_{t \to 0}\, \langle \frac{U_tx- x}{t},U_ty\rangle
=\lim_{t \to 0}\, \frac{1}{t}\cdot \bigl( \langle U_tx,U_ty)\rangle-
 \langle x,U_ty)\rangle\,\bigr)
 \]
Since $U_t$ are unitary we have
$\langle U_tx,U_ty)\rangle=\langle x,y)\rangle$ for each$Êt$ and conclude that
the last term above  is equal to
\[
\lim_{t \to 0}\, \frac{\langle x,y-U_ty\rangle}{t}=-\langle x,By\rangle
\]

\noindent
Hence $B$ is anti-symmetric, i.e.
\[
\langle Bx,y\rangle=-
\langle x,By\rangle
\]
Set $A=i\cdot T$ which gives
\[
\langle Ax,y\rangle=
i\cdot \langle Tx,y\rangle=
-i\cdot \langle x,Ty\rangle=-\langle x,i\cdot Ty\rangle=
\langle x,Ay\rangle
\]
where  we used that the inner product is hermitian.
Hence $A$ is a densely defined and symmetric operator.
\medskip

\noindent
{\bf{Theorem.}}
\emph{A is self-adjoint, i.e. one has the equality $\mathcal D(A)= \mathcal D(A^*)$.}
\medskip

\noindent
\emph{Proof.}
It suffices to prove that
$\mathcal D(T)=|mathcal D(T^*)$. To btain this we take a vector
$y$ be a vector in $\mathcal D(T^*)$ which by definition gives
a constant $C(y)$ such that
\[
|\langle Tx,y\rangle||\leq C(y)\cdot ||x||
\quad\colon\, x\in\mathcal D(T)\tag{i}
\]
Now
$\langle Tx,y\rangle$ is equal to
\[
\lim_{t\to 0}\,\langle\frac{U_tx-x}{t}, U_ty\rangle
=-\lim_{t\to 0}\,\langle x,\frac{U_ty-y}{t}\rangle\tag{ii}
\]
So if
\[
 \eta_t=frac{U_ty-y}{t}
\]
it follows that there exists
\[
\lim_{t\to 0}\, ,\langle x,\eta_t\rangle=-\langle Tx,y\rangle
\]
for each $x\in\mathcal D(T)$.





\bigskip



The adjoint operators
$\{U^*_t\}$   give another  unitary semi-group with
infinitesmal generator  
$A_*$ where
\[ 
A_* (x)=
\lim_{t \to 0}\, \frac{U^*_tx-x}{t}\quad\colon\quad x\in\mathcal D(A_*)
\]
Since $U_t$ is the inverse operator of $U^*_t$ for each $t$ we get
\[
A_*(x)= \lim_{t\to 0}\, U_t(A_* x)= \lim_{t \to 0}\, \frac{x-U_t x}{t}\quad\colon\quad x\in\mathcal D(A_*)\tag{i}
\]
\medskip

\noindent
From (i) we see that
$\mathcal D(A)\subset
\mathcal D(A_*)$ and
one has the equation
\[
A_* x)=-A(x)\quad\colon\quad x\in\mathcal D(A_*)\tag{ii}
\]
Reversing the role the reader can check the equality
\[
\mathcal D(A)=
\mathcal D(A_*)\tag{iii}
\]
Next, let $x,y$ be a pair in $\mathcal D(A)$.
Then
\[
\langle Ax,y\rangle=
\lim_{t \to 0}\, \langle \frac{U_tx- x}{t},U_ty\rangle
=\lim_{t \to 0}\, \frac{1}{t}\cdot \bigl( \langle U_tx,U_ty)\rangle-
 \langle x,U_ty)\rangle\,\bigr)
 \]
Since $U_t$ are unitary we have
$\langle U_tx,U_ty)\rangle=\langle x,y)\rangle$ for each$Êt$ and conclude that
the last term in (xx) is equal to
\[
\lim_{t \to 0}\, \frac{\langle x,y-U_ty\rangle}{t}=-\langle x,Ay\rangle
\]

\noindent
Hence $A$ is anti-symmetric.
Set
\[ 
B=iA
\]

\bigskip









{\bf{Exercise.}}
Show that (i)  gives the equality
$\mathcal D(A_*)=\mathcal D(A)$ and that:
\[
 A_*(x)=-A(x)\quad\colon\quad x\in\mathcal D(A)
 \]
 
 

\[
 \langle Bx,y\rangle= -\langle x,By\rangle\quad\colon\quad
x,y\in\mathcal D(B)
\]


\noindent {\bf{Exercise.}}
Conclude from the above that the operator $iB$ is self-adjoint.

\medskip


\noindent
{\bf{Remark.}} The equations  above constitute Stones theorem
which was established in 1930.
It has a wide range of applications. See for example von Neumann's article \emph{Zur Operatorenmethode in der klassischen Mekanik}
and Maeda's article \emph{Unitary equivalence of self-adjoint
operators and constant motion}
from 1936.
\bigskip


\noindent
{\bf{11.3.3 A converse construction.}}
Let $A$ be a densely defined self-adjoint operator.
From ¤ 9.B  $A$ is approximated by a sequence of bounded
self-adjoint operators
$\{A_N\}$.
With $N$ kept fixed
we get a semi-group of unitary operators where
\[ 
U^{(N)}_t= e^{-it A_N}
\]
The reader may verify that the inifintesmal generator becomes
$-iA_N$.
Next, for each $x\in \mathcal D(A)$
and every fixed $t$ there exists the limit
\[ 
\lim_{N\to \infty}\, U^{(N)}_t(x)
\]
{\bf{Remark.}} This gives a densely defined linear operator $U_t$
whose operator norm is bounded by one which therefore
extends uniquely to 
a bounded linear operator $\mathcal H$ and it is clear
that this  extension 
becomes a unitary operator. In this way
we arrive at a semi-group $\{U_t\}$
and one verifies that its infinitesmal generator is equal to $-iA$.
However, it is not clear that
$\{U_t\}$ is strongly continuous and one may ask for 
conditions 
on the given self-adjoint operator $A$ which ensures that  $\{U_t\}$
is strongly continuous.



\newpage





\newpage

POSTPONE 

\noindent
{\bf{An exercise.}}
One often applies Newton's
decomposition of rational functions
and we shall employ his  formulas without hesitation.
Here is an example. Let 
$n\geq 2$ andÊ$t_1<\ldots<t_n$ is a strictly invreasing sequence of real numbers.
With a variable $z$ we consider
the rational function
\[
P(z)=\sum_{\nu=1}^{\nu=n}\, \frac{A_\nu}{t_\nu-z}
\]
where $\{A_\nu\}$ are positive real numbers.
Put $\mathcal A= \sum\, A_\nu$ and 
\[
a= \mathcal A^{-1}\cdot \sum\, A_\nu t_\nu
\]
Show that  $P(z)$ has $n-1$
simpe zeros
$\tau_1,\ldots,\tau_{n-1}$ where 
$t_1<\tau_1<t_2<\ldots <\tau_{n-1}<t_n$, and
there exist positive numbers
$B_1,\ldots,B_{n-1}$ such that
\[
P(z)=\frac{\mathcal A}{a-z-Q(z)}\quad\colon\,
\mathcal A= \sum\, A_\nu\quad\text{where}\quad
Q(z)=\sum_{\nu=1}^{\nu=n-1}\, 
\frac{B_\nu}{\tau_\nu-z}
\] 
Finally, use
residue calculus to prove that 
the $B$-numbers are given by the equations
\[
B_p^{-1}=
\mathcal A^{-1}\cdot \sum_{\nu=1}^{\nu=n}\,\frac{A_\nu}{(t_\nu-\tau_p)^2}
\]
\bigskip


\bigskip
\noindent
We discuss  two of the most  problems whose solutions inspired
later development of operator theory.
\medskip



\noindent
{\bf{The Dirichlet problem}}
Let
$\Omega$ be a bounded
domain in
${\bf{R}}^3$ whose boundary is a finite union of closed
$C^1$-surfaces. The Dirichlet  problem amounts
to find a harmonic extension $F$Êof each
$f\in C^0(\partial\Omega)$, i.e. here
$\Delta(F)=0$ in $\Omega$ while $F=f$ on the boundary.
The maximum principle for harmonic functions implies that 
the Dirichlet problem has a unique solution if it exists. Moreover
\[
\max_{p\in\overline{\Omega}} |F(p)|=
\max_{p\in\partial \Omega} \, |f(p)|\tag{*}
\]
It suffices to get solutions for a
dense subapace of
$C^0(\partial\Omega)$. 
For if $\{f_n\}$ is a sequence which convege uniformyl to a limit function
$f$ and  Dirichet's solutions $\{F_n\}$ exists, then
(*) entails that this sequence converges uniformly on
$\overline{\Omega}$ to a limit function $F$ which solves
the Dirichlet probelm for $f$.
To solve the Dirchlet problem for a dense set of boundary
value functions
one can proceed as follows:
Each real-vaued continuous boundary function
$\phi$ gives via Newton's potential a harmonic function in
$\Omega$:
\[
\Phi(p)=
\frac{1}{4\pi}\cdot \int_{\partial\Omega}\,
\frac{\phi(q)}{|p-q|}\, dA(q)
\]
where $dA$ is the area measure on the boundary.
If $\phi$ is of class $C^1$
on the $C^1$-manifold $\partial\Omega$ it is easily verified that
$\Phi$ extends continuously  to the closure. So if
$\phi_*=\Phi|\partial\Omega$ we obtain a continuous function
which has $\Phi$ as a harmonic extension, i.e. the
Dirichlet problem is solved for $\phi_*$.
Hence one is led to consider the linear operator 
defined by
\[ 
T(\phi)(p)=\frac{1}{4\pi}\cdot 
\int_{\partial\Omega}\,
\frac{\phi(q)}{|p-q|}\, dA(q)
\] 
where $p$  varies on
$\partial\Omega$. Since
\[
\max_{p\in\partial\Omega}\, 
\int_{\partial\Omega}\,
\frac{1}{|p-q|}\, dA(q)<\infty
\]
elementary measure theory  entails that
$T$ is a bounded linear operator on the Banach space
$C^0(\partial\Omega)$ and from the above
the Dirichlet problem is well-posed if
the range of
the linear operator $T$ is dense.
To prove this density  one uses
that the dual space of 
$C^0(\partial\Omega)$ consists of Riesz measures.
Baisc meaasure theory shows that for evety
such measure $\mu$ the function defined on the boundary by
\[
p\mapsto \int_{\partial\Omega}\,
\frac{1}{|p-q|}\, d\mu(q)
\]
is integrable in Lebegue's sense
with respect to the area measure $dA$.
The requested density of $T$ amounts to show that
this $L^1$-function cannot be zero unless $\mu=0$.
This can be proved in several ways. See ¤ xx for details.
Hence the Dirichlet problem can be settled in the spirit of
Neumann and PoincarŽ via operator methods.

























\end{document}
