
\documentclass[12pt]{amsart}


\usepackage[applemac]{inputenc}



\addtolength{\hoffset}{-12mm}
\addtolength{\textwidth}{22 mm}
\addtolength{\voffset}{-10mm}
\addtolength{\textheight}{20mm}

\def\uuu{_}

\def\vvv{-}

\begin{document}
\newpage
 




\centerline {\bf{Mathematics  by Arne Beurling.}}
\bigskip


\noindent
Let $X$ be a complex manifold of some dimension $n\geq 2$.
To each $0\leq k\leq n-1$ we denote by
$\mathcal V_k$ the family of analytic sets of pure
dimension $k$, i.e, the irreducible components are all $k$-dimensional.
If $V\in\mathcal V_k$ and $p=n-k$ there exists the 
temperate local cohomology sheaf
$\mathcal H^p_{[V]}(\mathcal O_X)$
and we recall, from basic $\mathcal D$-module theory that it is a regular holonomic
left $\mathcal D_X$-module.
Moreover, it can be identfied with the sheaf
$\text{CH}_V$ whose sections are Collef-Herrera currents of
bi-degree
$(0,p)$ with support on $V$.
Indeed, this can be expressed via the Dolbeault isomrphism and
the (non-trivial !) direct sum decomposition
\[
\text{ker}_{\bar\partial}(\mathcal C_V^{0,p})=\bar\partial(\mathcal C_V^{0,p-1})\oplus
\text{CH}_V
\]
Let us now consider some
$\phi\in\mathcal O(X)$ which  yields the holomorphic 1-form
$\partial(\phi)$.
If $\gamma\in\text{CH}_V$ we obtain the current
$\partial\phi\wedge \gamma$
of bi-degree $(1,p)$ acting on test-form
$\psi^{n-1,k}$ by
\[
\partial\phi\wedge \gamma(\psi^{n-1,k})=
\gamma(\partial\phi\wedge\psi^{n-1,k})
\]
Let $\mathcal J(\gamma)$ be the ideal in
$\mathcal O_X$ whose sections anihilate $\gamma$.
From the above it is clear that the annihilating ideal
of 
$\partial\phi\wedge \gamma$ is given by
\[
(\mathcal J(\gamma);\partial\phi)=\{
g\,\colon\,\text{Jac}(\phi)\cdot g\in \mathcal J(\gamma)\}
\]
where
$\text{Jac}(\phi)$ is the dieal in $\mathcal O_X$ generated by the first order
derivatives of $\phi$.
\medskip

\noindent
{\bf{A special case.}}
Let $T$ be a hypersurface in $X$ given as the zero set
$\phi^{-1}(0)$ where $\phi$ has no multiple factors.
Let $f_1,\ldots,f_{p-1}$
be holomprphic functions which form a complete intersection with
respect to $T$, i.e. the analytic set
\[
V= T\,\bigcap\, f_\nu^{-1}(0)
\] 
has codimension $p$.
In $\text{CH}_V$ we find the current $\gamma$
defined by the Coleff-Herrera product of the principal residue currents
given by $\phi.f_1,\ldots,f_{p-1}$.
A wellknown result due to Passare in [xx] asserts that
\[
\mathcal J(\gamma)=(\phi.f_1,\ldots,f_{p-1})
\]
Next, we get the ideal  from (x) which in general is strictly larger than
$\mathcal J(\gamma)$.
The question arises if this ideal can be described in some
way.
To begin with we recall that up to a constant
the cureent of bi-degree $(1,1)$ defined by
$\partial\phi\wedge \bar\partial(\phi^{-1})$
is equal to Lelong's integration current
$\square_T$.
Moreover, the $f$-functions 
can be restricted to
$T$ and one constructs the  current
\[
\rho=\square_T\,\bigwedge_{\nu=1}^{p-1}\bar\partial(f_\nu^{-1})
\]
Up to a constant one has the equality
\[
\rho=\partial\phi\wedge\gamma
\]


\newpage





\centerline {\bf{Mathematics  by Arne Beurling.}}



\[
\text{Notes by Jan-Erik Björk}
\]
\[
\text{Department of mathematics. Stockholm university. March 2010.}
\]



\centerline {\bf{Introduction.}}
\bigskip



\noindent
We    expose some results   by Beurling
which not only offer striking theorems but 
have the merit that the proofs are both highly original and instructive. 
We have not 
tried to include material from his  deepest work  which  appear
in joint articles  with Lars Ahlfors, P. Deny  and Paul Malliavin. 
For an account about his collected work
we refer 
to  [Beurling: Collected Works 1-2]
whose   foreword contains 
a very  informative text  written by 
Lars Ahlfors and Lennart Carleson.
A  feature in Beurling's work is the  mixture of
geometric constructions  and "hard calculus".
An example
is the notion 
of extremal distances which
he constructed   already  in 1929
and applied in  many different situations, foremost to
estimate harmonic measures.

\medskip


\centerline{\emph{Beurling's ph.d-students.}}
\medskip




\noindent
From 1937 until 1955 as professor at Uppsala University, Beurling
advised to many students who later
became eminent mathematicians, the most prominent 
was Lennart Carleson who presented his 
thesis in 1950 at the age of 22 years. In addition to
students  at Uppsala university, he inspired and gave
crucial ideas to visiting mathematicans like Helson, Hewitt and Wermer. 
In 1955 he  emigrated to United States  where he held a position at the Advanced Study in 
Princeton until his decease in 1989.
A topic which is not treated in these notes
is devoted to inverse spectral analysis of differential equations.
Göran Borg was one of Beurling's ph.d-students at Uppsala University. 
His dissertation was presented in May 1945
where  
many crucial ideas, apart from posing the problem  had
been given with great generosity by Beurling.
Let us recall that 
inverse spectral theory after became
a quite extensive subject.
See chapter xx in Volume 2 from
the text-book by Dunford and Schwartz for an account.
Another example of Beurling's
active role as advisor stems from his  first ph.d student
Karl Dagerholm who presented his thesis at Uppsala in 1938.
In § xx we expose a very elegant theorem which goes as follows:
One seeks a sequence of real numbers
$x_1,x_2,\ldots$ such that the additive series
\[
\sum_{p=1}^\infty\, \frac{x_p}{p}
\]
converges and
\[
\sum_{p\neq q}^\infty\, \frac{x_p}{p-q}=0
\quad\colon\, q=1,2,\ldots
\]
The result is that this system up to a multiple with a constant has a unique solution.
Dagerholm's proof relies upon  specific solutions to 
certain Wiener-Hopf equations which
had been suggested to him by Beurling.





\medskip





\noindent

\noindent{\emph{Early study years.}}
Like Torsten Carleman,  Beurling  studied
at Uppsala University, where Carleman entered in 1911 and Beurling in 1924.
During their years as students, the professors at Uppsala were
Erik  Holmgren and Anders Wiman.
The  major contents in Beurling's Ph.D-thesis
was  already carried out  in 1929, but not  presented  until  November 4 1933
with the title
\emph{Études sur un problème de majoration.}
At that time
 Carleman had   served during  five years as director at
Institute Mittag-Leffler.
In the period 1933-1937 
Beurling  attended Carleman's lectures at
the Mittag-Leffler institute and  got 
considerable  inspiration from this.
One can mention Carleman's lectures about the generalised Fourier transform in
1935 which contained
refined versions of Ikehara's theorem and 
some remarkable results about analytic extensions across linear boundaries.
A few years later 
Beurling   proved Tauberian theorems with
remainder terms. This work was never published
but  submitted in his
application for the chair  at Uppsala University when Beurling
replaced  Homgren after his retirement   in 1937.
Crucial idea from this manuscript
were  used and extended  by his former
ph.d-student  Sonja Lyttkens
whose articles contain  quite impressive Tauberian theorems with remaineder terms.
Preserved
letters between Carleman and Beurling
show that
they esteemed  each others work.
For example, in his thesis Beurling
inserted the following comments upon Carleman's
proof from 1933 of the Denjoy conjecture 
with a sharp bound $2n$ for entire functions of order
$n$:
\emph{Plus récemmment 
M. Carleman en perfectionnant sa méthode initiale 
est arrivé au resultat $\leq 2n$ d'une manière fort élegante}.
His own  proof from 1929
has like that by Carleman,  the merit
that it
can be adapted to other cases than
asymptotic values and relies upon the following
remarkable result from the thesis:

\medskip

\noindent
{\bf{Theorem}}
\emph{Let $f(z)$ be a bounded analytic function in
the half space
$\mathfrak{Re}\, z>0$. Set}
\[ 
\mu(r,f)= \min_
{-\pi/2<\theta<\pi/2}\ |f(re^{i\theta})|
\]
\emph{Then
$f$ converges uniformly to zero 
in
every sector $-\pi/2+\delta\leq\theta\leq \pi/2-\delta$
under the condition that}
\[
\lim_{r\to\infty}\ \mu(r,f)=0
\]






\newpage


\centerline{\bf{Contents.}}
\bigskip


\noindent
\emph{§ 0.0 Work in analytic function theory.}


\medskip
\noindent
\emph{§ 0.0 Work in harmonic analysis}


\medskip
\noindent{\bf{§ 1. Extremal distances and harmonic measure.}}
\medskip


\noindent
{\emph{A. The Milloux problem.}
\medskip


\noindent
\emph{B. Minimum modulus of analytic functions.}
\medskip


\noindent
\emph{C. Upper bounds for harminic measure.}

\medskip


\noindent
\emph{D. Regular points for the Dirichlet problem.}
 \medskip


\noindent
{\emph{E. Extremal length.}}
\medskip


\noindent
{\emph{F. General  extremal metrics.}}
\medskip


\noindent
{\emph{G. On quasi-analytic series.}



\medskip

\noindent
{\bf{Special sections.}}

\medskip

\noindent
\emph{0. Holmgren's uniqueness theorem and
the heat equation}

\medskip




\noindent
\emph{1. Radial limits of functions with finite Dirichlet integrals}

\medskip


\noindent
\emph{2. An automorphism on product measures.}




\medskip


\noindent
\emph{3. Beurling's criterion for the Riemann hypothesis.}



\medskip


\noindent
\emph{4. The Laplace operator and the Helmholtz equation.}


\medskip


\noindent
\emph{5. Beurling's conformal mapping theorem.}
\medskip


\noindent
\emph{6. The Riemann-Schwarz inequality for hyperbolic metrics.}

\medskip

\noindent
\emph{7. A uniqueness result for the $\zeta$-function.}


\medskip
\noindent
\emph{Part II: Some results about subharmonic functions.}
\medskip


\noindent
\emph{A. On zero sets of subharmonic functions.}


\medskip


\noindent
\emph{B. A subharmonic majorisation.}
\medskip


\noindent
\emph{C. Sjöberg's subharmonic minorants} 



\medskip


\noindent
\emph{D. An inequality for  subharmonic functions} 
\medskip


\noindent
\emph{E. Carleman's differential inequality
and the Denjoy conjecture.}



\medskip


\noindent
\emph{F. Ganelius'  inequality for conjugate harmonic functions.}

\medskip


\noindent
\emph{H. A minimum principle for subharmonic functions}.
\medskip


\noindent
\emph{I. An $L^1$-inequality for inverse Fourier transforms.}

\medskip


\noindent
\emph{J. On functions with spectral gaps}
\medskip


\noindent
\emph{L. A theorem about weak limits}

\medskip


\noindent
\emph{L. Dagerholm's  system of linear equations}

\medskip


\noindent
\emph{M. A theorem by Kjellberg.}
\medskip


\noindent
\emph{N. Carleson's interpolation theorem}




\bigskip











\centerline {\bf{Introduction.}}
\medskip



\noindent
 Familarity with measure theory and
basic results in functional analysis is assumed. Relevant background appears
in my notes devoted to analytic function theory of one complex variable.
The reader will recognize that
most of the results in these notes are concerned with inequalities which
in the present author's opinion is  the core of mathematical analysis.
To make these notes reasonably  self-contained we have included
an Appendix which reviews   facts about
Hardy spaces, and § A:2 treats convolution algebras on the real line
where major contributions are due to  Wiener and Beurling.
Let us start with a  comment about  § 0 in the Special Section 
devoted
to the heat equation.
In the  analytic case, diffusion equations are solved
by the usual heat kernel. But this simple device
does not apply for solutions which
increase considerably faster that
than $e^{x^2}$.
 So for parabolic equations where the initial value functions increase
 fast there arise  subtle problems about uniqueness. 
 This was  put forward  in work by Gevrey, Hadamard and Holmgren around 1900.
 A conclusive theorem was proved by Holmgren in 1924
 which
 is essentially sharp for the 1-dimensional heat-equation. 
\emph{So whether one likes it or not}, it is  necessary 
 to perform
constructions which involve rather tedious
 verifications of inequalities   to
 obtain non-analytic solutions of the heat-equation
 where Holmgren's  uniqueness result  applies.
 See § 0 for further details.
 \medskip
 


\noindent
{\bf{A first example.}}
To illustrate the flavour of these notes we
announce a result where the reader is supposed to
pursue the details.
Let $u(z)$ be a subharmonic 
function in  the open unit disc $D$.
Assume that it has continous boundary values on
the unit circle $T$ with the exception of the point 1
and
$u(e^{i\theta})\leq 0$ for each $0<\theta<2\pi$.
In addition  we assume that there exists some $0<\alpha<1$ such that
\[
u(z)\leq |1-z|^{-\alpha}
\]
for every $z\in D$.
Then  $u(z)\leq 0$ for all $z\in D$.
To prove this we take a small  $\epsilon>0$ and put
$D_\epsilon=D\cap \{ |z-1|\geq \epsilon\}$.
On the  boundary
$\partial D_\epsilon$ we define the function $h^*$ to be zero on
$T\cap \{ |z-1|\geq \epsilon\}$ while
$h^*$ is $\epsilon^{-\alpha}$ on the circular arc $\mathcal C_\epsilon$
of $\partial D_\epsilon$ which stays in $D$.
Then $h^*\geq u$ on $\partial D_\epsilon$. So if $h$ is its harmonic extension to
$D_\epsilon$ one has $u\leq h$ in this domain. 
For each $z\in D_\epsilon$ the principle of harmonic majorisation entails that
\[
 u(z)\leq\epsilon^{-\alpha}\cdot 
 \mathfrak{m}_{D_\epsilon}
(z_0;\mathcal C_\epsilon)
 \]
Now one uses an upper bound for the harmonic measure.
More precisely, with
$r<1$ kept fixed there exists a constant $C(r)$ such that
\[
\mathfrak{m}_{D_\epsilon}
(z_0;\mathcal C_\epsilon)\leq C(r)\cdot \epsilon
\]
hold when $|z_0|\leq r$ and $\epsilon \leq (1-r)/2$.
Since $\alpha<1$, a passage to the limit gives
$u(z)\leq 0$ in every disc $|z|\leq r$ which proves the
claim above.





 

\newpage

\noindent
{\bf{Some inequalities.}}
To illustrate material in the subsequent sections
we state some theorems by Beurling. 

\medskip



\centerline {\emph{0.1 A min-max inequality for polynomials.}}
\medskip

\noindent
Let $P(z)$ be a polynomial of some degree $n\geq 2$ where
$P(0)=1$.
To each pair $0<a<b<1$
we set
\[
\omega_P(a,b)= \max_{a\leq r\leq b}\, \min_\theta\, |P(re^{i\theta})|
\]
Thus, while the radius $r$ varies between
$a$ and $b$ we seek some $r$
such that the minimum modulus of $P$ on the circle
$|z|=r$ is as large as possible.
In his thesis
Beurling found
a lower bound hold for these $\omega$-functions.
\medskip


\noindent
{\bf{0.1.1.Theorem.}}
\emph{The following hold for
all pairs $0<a<b$ and each   polynomial $P$ as above with degree $n$:}
\[
 \omega_P(a,b)\geq \bigl(\frac{\sqrt{b}-\sqrt{a}}{\sqrt{b}+\sqrt{a}}\,\bigr)^n\tag{*}
\]
In § XX we  expose the proof
which
relies upon a study of
logarithmic potentials and
remark that (*)
becomes   sharp when $n$ increases.
\medskip



\centerline {\emph{0.2 The Riemann-Schwarz inequality.}}
\medskip


\noindent
Consider a Riemann surface $X$ whose universal 
covering space is the open unit disc equipped with a hyperbolic 
metric 
$\sigma$.
It means that the metric in a chart
with local coordinate $z$
is defined by
$e^{u(z)}\cdot |dz|$ where
$u(z)$ is  a  subharmonic function.
If $\gamma$ is
an arbitrary rectifiable curve in $X$
$\sigma$-length is denoted by
$\ell(\gamma)$.
To each  pair of points $p,q$ in $X$ we denote by 
$\mathcal C(p,q)$ the family of
curves in $x$ with end-points at $p$ and $q$. 
\medskip

\noindent
{\bf{0.2.1 Theorem.}}
\emph{For every pair
$\gamma_1,\gamma_2$ in  $\mathcal C(p,q)$
and
each point $\xi\in\gamma_1$,
there exist two other curves  curves $\alpha,\beta$ with
$\alpha\in\mathcal C(p,q)$, while the end-points of $\beta$ are
$\xi$ and some point on $\gamma_2$ such that}
\[
\ell(\alpha)^2+\ell(\beta)^2\leq
\frac{1}{2}\bigr (\ell(\gamma_1)^2+\ell(\gamma_2)^2\,\bigl )\tag{*}
\]

\noindent
This implies  the following: Let
\[
d(p,q)= \min_{\gamma\in\mathcal C(p,q)} \,\ell(\gamma)
\]
Then, if $\ell_1,\ell_2$ is pair in this family and $\epsilon>0$ are such that
such that
\[
\ell(\gamma_\nu)^2\leq d(p,q)^2+\epsilon^2
\]
It follows that the distance between
the two courves is majorised by $\sqrt{2\epsilon}$.
In § xx we give a proof due to Beurling.
Using the 
uniformisation theorem for Riemann surfaces, Beurling
reduced the 
proof to a   local result where $D$ is the open unit disc in which case the
following crucial result holds:
\newpage

\noindent
{\bf{0.2.2 Proposition.}}
\emph{To each
$0<\theta<\pi/2$ we denote by   
$C_\theta$ the unique circle which
contains
$e^{i\theta}$
and $e^{-i\theta}$ and intersects the unit circle at right angles at these points,
and 
$\gamma_\theta$ is  the circular subarc of $C_\theta$  contained in
$D$.
Then the following inequality holds for
every subharmonic function $u$ in $D$:}
\[
\bigl(\int_{-1}^1\, e^{u(x)}\, dx\bigr)^2+
\bigl(\int_{\gamma_\theta}\, e^{u(z)}\, |dz|\bigr)^2\leq
\frac{1}{4}\cdot\bigl( \int_0^{2\pi}\, e^{u(e^{i\phi})}\,d\phi\bigr)^2
\] 
\emph{and equality holds only for special
rhombic configurations as explained in § xx}.

\bigskip

\centerline{\emph{0.3 Duality on Hardy spaces.}}

\bigskip

\noindent
Tbe appendix devoted to Hardy spaces contains more than is needed as background
for the special sections. But it has been included because
the materail fits with
the spirit of these notes.
Here is a theorem from this appendix due to Fefferrman and Stein.
Denote by $H^1_0(T)$ the class of functions in the Hardy space 
on the unit circle whose analytic extensions to the disc $D$ vanish
at the origin.
Let $F$ be a function in $L^1(T)$ and denote by $H_F$ its harmonic extension
to $D$.
For each $0<r<1$ we get a linear functional on
$H^1_0(T)$
defined by
\[
L_r(g)=
\int_0^{2\pi}\, H_F(re^{i\theta})\cdot 
\mathfrak{Re}(g)(re^{i\theta})\,d\theta
\]
These functionals depend on $F$ and we set
\[
L^*(F)=\max_{rg}\, |L_r(g)|
\]
with the maximum taken over all pairs $0<r<1$ and
$H_0^1(T)$-functions $g$ for which
\[
\int_0^{2\pi}\, 
|\mathfrak{Re}(g)(re^{i\theta})|\,d\theta=1
\]
Recall also that $L^1(T)$ constains the subspace 
$\text{BMO}(T)$ of functions with a bounded mean 
oscillation in the sense of John and Nirenberg




\medskip

\noindent
{\bf{0.3.1 Theorem.}}
\emph{There exists an absolute constant $C$ such that}
\[
|L^*_F| \leq C\cdot ||F||_{\text{BMO}} \tag{1}
\]
\emph{for all $F\in\text{BMO}(T)$, and conversely
if $L^*(F)<\infty$ for some $F\in L^1(T)$, then
$F$ has bounded mean oscillation and}
\[
 ||F||_{\text{BMO}}\leq L^*(F) \tag{2}
 \]
 \medskip

\noindent
The  inequality (1) is proved in a rather straightforward way
while (2) requires considerably more work
based upon studies of Carleson measures.


\medskip





\newpage






\newpage


\centerline{\bf{A.  Beurling's work in analytic function theory.}}
\medskip


\noindent
\emph{Riemann's mapping theorem.}
Before Theorem A.1  is announced
announced
we recall the connection between
the conformal mappings  and
the equilibrium potential on plane curves.
Let $\Gamma$ be a closed Jordan
curve
of class $C^1$.
One seeks 
a positive density function
$\mu$ on 
$\Gamma$  with total mass one
such that
the logarithmic potential
\[
\int_\Gamma\,\log\,\frac{1}{|z-\zeta|}\cdot
\mu(\zeta)\cdot |d\zeta|\tag{*}
\]


\noindent
is constant as $z$ varies in $\Gamma$, where $|d\zeta|$ is the arc-length measure.
The existence of  $\mu$ is
expected since
$\mu$ corresponds to 
an equilibrium density for an electric
field. It turns out that
$\mu$ is found  via the conformal mapping
function $f$ from the exterior domain bordered by
$\Gamma$ onto the exterior of the unit disc. More precisely one has
\[
\mu(\zeta)=\frac{1}{|f'(\zeta)|}\tag{**}
\]
A proof of this classic result appears in Chapter VI from my 
notes in analytic function theory.
Beurling introduced a general set-up for conformal mappings as follows:
Denote by $\mathcal C$ the family of
analytic functions $f$ in the open unit disc $D$ such that
$f$ yields a conformal mapping onto some simply connected
domain and $f'(0)$ is real and positive.
For each
positive and bounded continuous 
function $\Phi$ defined in the whole complex
$w$-plane we get a subclass of $\mathcal C$  as follows:
\medskip

\noindent
{\bf Definition.}
\emph{The family  of all
$f\in \mathcal C$ such that}
\[ 
\lim_{r\to 1}\,\, 
\max_{0\leq\theta\leq 2\pi}\,\bigl|\,\bigl|f '(re^{i\theta})|-\Phi(f(re^{i\theta}))
\,\bigr|=0\tag{*}
\]
\emph{is denoted by $\mathcal C_\Phi$.}
\medskip

\noindent
Thus, when $f\in\mathcal C_\Phi$
the difference of the absolute values of 
$|f'(z)|$ and $\Phi(f(z))$ tends uniformly to zero
as $|z|\to 1$.
Let $M$ be the upper bound of $\Phi$.
The maximum principle applied to the complex derivative
$f'(z)$ gives
\[
|f'(z)|\leq M\quad\colon\quad z\in D
\]
Hence $f(z)$ is a  continuous function in
the open disc $D$ whose Lipschitz norm is uniformly
bounded by $M$. This implies
that  $f$ extends to a continuous function in the closed disc, i.e.
$f$ belongs to the disc algebra
$A(D)$.
\bigskip


\noindent
{\bf A.1 Theorem.}
\emph{If  
$\log\,\frac{1}{\Phi(w)}$ is subharmonic, it follows that
$\mathcal C_\Phi$ contains a unique function
$f^*$.}
\bigskip




\noindent
\emph{A.2. Invariant subspaces of $H^2(T)$.}
The Hilbert space $L^2(T)$ of square integrable functions on
the unit circle $T$  contains the closed subspace $H^2(T)$
whose elements are boundary values of analytic functions in
$D$.
Each  $f\in H^2(T)$
is expanded as
\[ 
\sum\uuu{n=0}^\infty\, a\uuu n\cdot e^{in\theta}
\]
and Parseval's theorem gives  the equality
\[
\sum\uuu{n=0}^\infty\, |a\uuu n|^2=\frac{1}{2\pi}\cdot
\int\uuu 0^{2\pi}\, 
|f(e^{i\theta})|^2 d\theta
\]
Moreover, in $D$ we get the analytic function
$f(z)=\sum\, a\uuu nz^n$ whose
radial limits
\[ 
\lim\uuu {r\to 1}\, f(re^{i\theta})= f(e^{i\theta})
\]
exist almost everywhere. In fact, this follows from 
the Brothers Riesz theorem established in 1916, and the inclusion 
$H^2(T)\subset  H^1(T)$.
Let us now consider
some $f\in H^2(T)$ whose analytic extension $f(z)$ is zero-free in $D$.
Then $\log f(z)$ exists as an analytic function in
$D$ and
the Brothers Riesz theorem gives
an absolutely continuous measure on $T$ via radial boundary values of
$\log |f(z|$. Put
\[
\mu=\log |f(e^{i\theta})|\quad\colon\, 
g_\mu(z)=
\frac{1}{2\pi}\int_0^{2\pi}\,
\frac{e^{i\theta}+z}{e^{i\theta}-z}\cdot d\mu(\theta)\tag{*}
\]
So  $g_\mu$    is  the  Herglotz
extension of the Riesz measure $\mu$.
Following Beurling one says that $f$
is of outer type if
\[ 
f(z)=e^{g\uuu\mu(z)}
\] 


\noindent
{\bf{A.2.1 Beurling's closure theorem.}}
\emph{Let  $f\in H^2(T)$ be of outer type .
Then the family
$\{ e^{in\theta}f(e^{i\theta})\,\colon n=0,1,2,\ldots\}$
generates a dense subspace of
$H^2(T)$}.

\medskip

\noindent
We prove this in § xx  where we also expose
applications of this closure theorem due to Helson and Szegö.
\bigskip



\noindent
\emph{A.3 Analytic extensions across a boundary.}}
Consider
the open square 
\[
\square=\{z=x+iy|,\colon -1<x,y<1\}
\]
The $x$-interval divides $\square$ into the upper
part
$\square^*=\square\cap\,\{ 0<y<1\}$.
and the  lower part $\square_*$ where $-1<y<0$.
Consider a pair  $f\in\mathcal O(\square^*)$ and $g\in \mathcal O(\square_*)$.
One seeks condition in order that they are analytic extensions of each other, i.e.
when there exists
$\phi\in\mathcal O(\square)$ whose restriction to $\square^*$ is $f$,
and  $\phi|\square_*=g$.
The following sufficiency results was established by Carleman in lectures at Mittag
Leffler in 1935:

\medskip

\noindent
{\bf{A.3.1 Theorem.}}
\emph{The analytic extension exists if}
\[
\lim_{\epsilon\to 0}\, \int_{-1}^1\,
|f(x+i\epsilon)-g(x-i\epsilon)|\, dx=0
\]
\medskip

\noindent
{\bf{Remark.}}
Notice that from the start no growth conditions are imposed on the functions
$f$ or $g$ as $z$ approaches the real  $x$-interval.
The proof by Carleman uses the subharmonic  property
of
the radius of convergence while one takes Taylor series of
$f$ and $g$ in discs which stay in the half-squares.
Inspired by this, Beurling established further results 
in the article
[Acta: xxx]. Here is one example:


\medskip

\noindent
\emph{A.3.2  An extension of Runge's theorem.}
Consider the open set $\Omega=
\square^*\cup\, \square_*$ and 
let  $\omega(y)$
be a continuus function on the closed square
$\overline{\square}$
which is $>0$ for $y\neq 0$ while $\omega(0)=0$.
Moreover,
$y\to \omega(y)$
decreases as $y$ tends to zero through positive or negative values.
Denote by $C_\omega(\square)$ the space of
complex-valued continuous functions
$f(z)$  in $\Omega$ 
such that the product $\omega(y)f(z)$ extends to a continuous function
on $\overline{\square}$
which is zero on   the real interval $[-1,1]$.
It becomes a Banach space under the  norm:
\[ 
||f||=\max_{x+iy\in \square}\, \omega(y) |f(x+iy)|
\]
Define
\[
A_\omega(\square)=\{ f\in 
C_\omega(\square)\,\colon\, f|\square\in\mathcal O(\square)\}
\]
We have also the larger subspace
$A_\omega^*(\square)$ of functions $f$ in
$C_\omega(\square)$ whose restrictions to $\Omega$ is 
analytic.
It is clear that
$A_\omega^*(\square)$  is a closed subspace of
$C_\omega(\square)$ and hence the closure of
$A_\omega(\square)$ is contained in
$A_\omega^*(\square)$. It turns out that
the equality depends upon
the $\omega$-function.

\medskip

\noindent
{\bf{A.3.3 Theorem.}} \emph{The
equality
$\overline{A_\omega(\square)}=A^*_\omega(\square)$
holds if and only if}
\[ 
\int_{-b}^b\, \log\log \frac{1}{\omega(y)}\, dy=-\infty\tag{*}
\]
\medskip

\noindent
We  remark that a crucial point in Beurling's proof
employs a
result by    Carleman from  1920 which asserts that if
$g(z)$ is an entire function of exponential type and
in addition bounded on the real $x$-line, then 
\[
\int_1^\infty\, \log^+\, \frac{1}{|g(x)|}\, dx<\infty
\]


\bigskip





\centerline{\bf{A.4 Gabriel's problem and interpolation.}}

\bigskip




\noindent
The  interpolation problem 
below  was posed and solved
in the joint  article  [N-P] by F. Nevanlinna and Pick.
To each    $n$-tuple  of distinct points
$E=\{\alpha_1,\ldots,\alpha_n\}$ in the open unit disc $D$ and some $n$-tuple
$w_1,\ldots,w_n$ of complex numbers we put:
\[
\rho(E;w(\cdot))= \min_{f\in\mathcal O(D)}\,
\,|f|_D\quad\colon\quad f(\alpha_\nu)=w_\nu\quad\colon\, 1\leq\nu\leq n\tag{*}
\]
Thus we seek to interpolate preassigned values on $E$
with an analytic
function $f(z)$ whose maximum norm is minimal.
Denote by $\mathfrak{B}_{n\vvv 1}$ 
the family of finite Blaschke products:
\[ 
f(z)=e^{i\theta}\cdot \prod_{\nu=1}^{\nu=n\vvv 1}
\,\frac{z-z_\nu}{1-\bar z_\nu\cdot z}\tag{**}
\]
where  $0\leq\theta\leq 2\pi$ and $(z_1,\ldots,z_{n\vvv 1})$ is some 
$(n\vvv 1)$-tuple of  points in $D$ which are not necessarily distinct.


\bigskip

\noindent {\bf A.4.1. Theorem}  \emph{For each pair  $E$
and $w(\cdot)$ as above 
there exists a unique function $f_*\in\mathfrak{B}_{n\vvv 1}$ 
such that
$\rho(E;w(\cdot))\cdot f_*(z)$ solves the
interpolation (*).}
\bigskip


\noindent
\emph{The interpolation bound}.
For each finite
set $E$ in $D$ with $n$ points we set
\[
\lambda(E)= \max_{w}\, \rho(E;w(\cdot))
\]
with the maximum taken over all $n$-tuples $w$ in $D$.
In the article [1986]
Beurling considered a mini-max problem which goes as follows:
For each $n$-tuple $E=\{\alpha_\nu\}$ of distinct
points in the unit disc we set
\[
\tau(E)= \min_{\phi\in\mathcal B_{n-1}}
\max_{\alpha\in E}\, |\phi(\alpha)|
\]
\medskip


\noindent
{\bf{A.4.2 Theorem.}}
\emph{Up to a multiple  with $e^{i\theta}$
the mini-max problem has a unique solution $\phi_E(z)$. Moreover,
one has the equality $\tau(E)= \lambda(E)^{-1}$ and}
\[
|\phi_E(\alpha)|=\tau(E)\quad \colon \alpha\in E
\]
\medskip

\noindent
{\bf{Remark.}}
For a given set $E$ the zeros of $\phi_E$ are in general not distinct.
Counted with eventual multiplicities the 
zero-set is denoted by $E^*$ and called the associated set of $E$ for the mini-max problem.
To prove this theorem, Beurling considered the following
Hilbert space problem:
Given the set $E$ we have the Blaschke product
\[
B_E(z)= \prod_{\nu=1}^{\nu=n}
\,\frac{z-\alpha_\nu}{1-\bar \alpha_\nu\cdot z}\tag{**}
\]
In the unit disc we introduce the positive discrete measure
\[
\mu= \sum_{\nu=1}^{\nu=n}\,\frac{1}{|B'_E(\alpha_\nu)|}
\cdot \delta_{\alpha_\nu}
\]
Now one has the extremal  problem
\[
\max_F\, \int_D\, |F(z)|^2\, d\mu(z)\tag{i}
\]
with the maximum taken over analytic functions $F$ for which
\[
\int _0^{2\pi}\, |F(e^{i\theta})|^2\, d\theta=1\tag{ii}
\]
Dividing with Blaschke products which do not affect
the $L^2$-norms in (ii), it follows that the extremal function $F^*$ is
zero-free and  unique when
we  require that $F^*(0)$ is real and positive.
Beurling proved that $F^*$ satisfies the folloeing two eqautions
\[
\int_D\, \frac{1-|z|^2}{|e^{i\theta}-z-|^2}\cdot [F(z)|^2|\, d\mu(z)=
||\mu||\cdot |F(e^{i\theta})|^2\quad\colon 0\leq \theta\leq 2\pi
\]
\[
\int_D\,\frac{F(z)}{1-\overline{\zeta}\cdot z}\, d\mu(z)=
||\mu||\cdot |F(\zeta)|^2\quad\colon |\zeta|>1/r
\]
where 
$r=\{\max\,\{\alpha_\nu\}$.
\bigskip


\noindent
From  the above one has found 
two criteria for extremal solutions. As expressed by  Beurling
it is this \emph{multiple  information that creates its usefulness}.
The results above were established in 1959, while the final part of the cited article
contains results which Beurling carried out in 1985,
where the major aim was to investigate
the behaviour of infinite Blaschke products.
So in [Beurling 1987]
appears one of his last 
contributions to mathematics.
The notion of Blascke products of the so called second kind appear
in the cited article, and Beurling proved that their zero sets
conicide with the family of discrete subsets of $D$ for which the bounded interpolation 
by analytic functions is solvable. Let us
recall that Carleson in a work from 1958
found necessary and sufficient conditions for discrete sets 
to have  the interpolation property expressed via
properties of th hyperboic distances between the points in 
the interpolating
sequence.
The analysis  in [1987] gives a new perspective upon this result.
Let us also remark
that the final part of Beurling's cited article contains a
quite exciting analysis where 
future research remains to be done.









\bigskip



\centerline{\bf{A.5 A uniqueness theorem for Riemann's $\zeta$-function.}}

\bigskip


\noindent
Let $\mathcal F$
be the family of all 
non\vvv decreasing  increasing sequence of
positive numbers $\lambda\uuu 1\leq \lambda\uuu 2\leq \ldots$ 
for which there exists some $\delta>0$ such that
\[ 
\lambda\uuu n\geq \delta\cdot n\tag{i}
\]
hold for every $n$ where $\delta$ can depend on the given sequence.
A result due to Hadamard  asserts that
the  product
\[ 
f(z)=\prod\, (1+\frac{z^2}{\lambda\uuu n^2})\tag{ii}
\]
is an entire  function in the class $\mathcal E$, i.e. there are constants
$C$ and $A$ such that
$|f(z)|\leq C\cdot e^{A|z|}$ for all $z$.
Next, we construct
the Dirichlet series
\[
\Lambda(s)=\sum_{n=1}^\infty \frac{1}{\lambda\uuu n^s}\tag{iii} 
\]
By (i) this gives
an analytic function in the half\vvv plane
$\mathfrak{Re}\, s>1$ and we recall that
$\Lambda(s)$ is obtained
from $f(z)$ by the formula
\[
\Lambda(s)= s\cdot \sin\,\frac{\pi s}{2}\cdot
\frac{1}{\pi}\cdot
\int\uuu 0^\infty\, \log f(x)\cdot \frac{dx}{x^{s+1}}\tag{iv}
\]
From this one gets:

\medskip

\noindent
{\bf{A.5.1 Theorem.}}
\emph{Every  $\Lambda$ \vvv function obtained from 
a seqence in $\mathcal F$
extends to a meromorphic function in
the complex $s$\vvv plane.}



\medskip

\noindent
{\bf{Example.}}
Riemann proved that
the associated $f$-function to the
Dirchlet series defining
$\zeta(s)$ is equal to
\[
f(z)=
\frac{e^{\pi z}\vvv e^{\vvv \pi z}}{2\pi z}
\]
Thus,  this choice of $f$ gives
$\zeta(s)$ in the left hand side from (iv).



\medskip


\noindent
\emph{An extremal property of  $\zeta(s)$.}
In a lecture at Harvard University in 1949, Beurling proved
that Riemann's  zeta\vvv function
has a distinguished  position in a class of
functions defined by Dirichlet series.
For each  positive number $k$
we denote by $\mathcal C\uuu k$
the class of 
series  $\Lambda(s)$ from (ii) 
with the properties:
\[
\Lambda(s)\vvv \frac{1}{s\vvv 1}\quad\text{is entire}\tag{a}
\]
\[
\Lambda(\vvv 2n)=0 \quad\text{for all positive integers}\tag{b}
\]
\[ 
\max\uuu {|s|=r}\, |\Lambda(s)|\leq
C\cdot \frac{\Gamma(r)}{(2\pi k)^r}\quad\text{hold for a constant}\quad
C\quad\text{and 
all}\quad r\geq 2\tag{c}
\]

\medskip

\noindent
Notice that the class $\mathcal C\uuu k$ becomes more
restrictive as $k$ increases.
Using Riemann's original work one verifies that
$\zeta(s)$ satisfies (a-b). By a more elaborate analysis Beurling proved
that
the zeta-function belongs to $\mathcal D_1$, i.e. (c) above hold with $k=1$
for a certain constant $C$.
Moreover one has

\medskip


\noindent
{\bf{A.5.2 Theorem.}}
\emph{If $k>1$ the class 
$\mathcal C_k$ is empty. Moreover, when $1/2<k\leq 1$, then
$\mathcal C\uuu k$ only consists of constants times
the zeta-function.}
\medskip


\noindent
{\bf{Remark.}}
Beurling's result illustrates the
special role of the
$\zeta$\vvv function. 
The proof requires several  steps.\medskip


\bigskip












\centerline{\bf{§ B Harmonic analysis}}
\medskip

\noindent
Beurling's work   devoted to harmonic analysis is  extensive. Here we
are content to  
decribe a few of his   results which will
be presented with detailed proofs in the subsequent sections.
\medskip

\noindent
{\bf{B.1 A result about weak limits.}}
The theorem below was
by Beurling in seminars at Uppsala university in 1942. 
On the real $x$-line we have the space of continuous functions
$f(x)$ whose Fourier transforms are Riesz measures  with a finite total
variation, i.e. 
\[
f(x)=\frac{1}{2\pi}\, \int e^{ix\xi} d\gamma(\xi)
\]
where $\gamma$ is a complex-valued Riesz measure
of finite total mass:
\[
 \int |d\gamma(\xi)|<\infty
\]
It is clear that every such $f$ is a
bounded and even uniformly continuous function on
the real $x$-line.
Its closure
taken in the Banach space $C^0({\bf{R}})$ equipped with 
the maximum norm is denoted
by $\mathcal A$.
Next, a sequence $\{\mu_n\}$ of Riesz measures
on the  $x$-line  converges weakly in Schauder's sense if
there is a constant $M$ such that
the total variations $||\mu_n||\leq M$, and the 
Fourier transforms converge pointwise to zero:
\[
\lim_{n\to\infty}\, \int\, e^{ix\xi}\, d\mu(x)=0
\]
for each real number $\xi$.
It is easily verified that when
$f\in \mathcal B$ and $\{\mu_n\}$ converge to zero in
Schauder's sense then
\[
\lim_{n\to\infty}\,\int \, f(x)\,  d\mu_n(x)=0\tag{*}
\]
Beurling proved that the  converse is true, i.e. if $f(x)$ is a uniformly
continuous and bounded function for which (*) holds whenever
$\mu_n\to 0$ in the sense of Schauder,  then $f\in\mathcal B$. 
Let us remark that in contrast to 
"soft results" in functional analysis derived   via
Baire's theorem, the proof  to be exposed in § xx
relies on a quite involved  variational problems whose
mere construction is not evident from the start.
\bigskip

\noindent
\emph{An $L^1$-inequality for
inverse Fourier transforms.}
Let $g(\xi)$ be a function defined on $\xi\geq 0$ where the 
inverse Fourier transform of $\xi g(\xi)$ is integrable, i.e.
the function defined on the $x$\vvv axis by
\[  
f(x)=\int_ 0^\infty e^{ix\xi}\cdot \xi g(\xi)\, d|xi\tag{*}
\]
belongs to $L^1({\bf{R}})$.
In §§ we show:
\medskip

\noindent
{\bf{B.2 Theorem.}}
\emph{When (*) holds it follows
that
$g$ is integrable and one has the inequality}
\[
\int\uuu 0^\infty\, |g(\xi)|\, d\xi\leq \frac{1}{2}
\int\uuu {\vvv \infty}^\infty\, |f(x)|\, dx
\]
\medskip


\noindent
\emph{Functions with spectral gap.}
A fore-runner to distribution theory 
appears in a
result  from a seminar
by Beurling at  at Uppsala University
in March 1942.
\medskip






\noindent
{\bf{B.3 Theorem.}}
\emph{Let $f(x)$ be a bounded and continuous function on
the real $x$\vvv line such that $\widehat{f}(\xi)$
is zero on
$\{-1\leq\xi\leq1\}$
and}
\[ 
f(x+h)\vvv f(x)\leq h
\] 
\emph{hold for all $h>0$ and every $x$. Then its maximum norm is
at most $\pi$.}
\medskip




\newpage

\centerline{\bf {§ C. Extremal distances and harmonic measure.}}

\bigskip

\noindent
Beurling's thesis \emph{Études sur un problème de majoration}
form Uppsala in 1933 contains many proofs which are
utmost  intstructive 
and  transparent. So 
[ibid] constitutes 
a veritable classic in
analytic function theory.
Here follow some
results from [ibid].


\bigskip


\centerline{\emph{C.1 The Milloux problem.}}



\medskip


\noindent
Here one studies the minimum modulus of analytic functions
and tries to
derive upper bounds for the maximum modulus. The following
result is proved in [ibid: p. xxx]:

\medskip

\noindent
{\bf{C.1.1 Theorem.}}
\emph{Let $f$ be
an analytic function $f(z)$ in the unit disc
where $|f(z)|<1$ for all $z$ and suppose there exist some
$\delta>0$ such that}
\[
 \min_\theta\, |f(re^{i\theta})|\leq \delta\quad\forall\,\ 0\leq r<1
\] 
\emph{Then it follows that}
\[
\max_\theta\, |f(re^{i\theta})|\leq \delta^{\frac{2}{\pi}\cdot
\arcsin\,\frac{1-r}{1+r}}
 \quad\colon\, 0<r<1 \tag {*}
\]

\noindent
{\bf{Remark.}}
Prior to this,
M.E  Schmidt had proved (*) under the constraint that
there exists a Jordan arc from the origin to the unit 
circle along which
$|f|$ is $\leq \delta$ in which case one  profits upon a suitable 
conformal mapping which in a simllar context had been used by Koebe.
To prove (*) in the general case
Beurling introduced   totally new ideas.

\bigskip


\centerline{\emph{C.2 Minimum modulus of analytic functions.}}
\medskip

\noindent
When $f(z)$ is analytic in a disc $\{|z|<R\}$
we set
\[
m_f(r)= \max_{|z|= r}\, |f(z)|\quad\colon\, \mu_f(r)=
 \min_{|z|= r}\, |f(z)\quad\colon 0<r<R
\]


\noindent
The following  is proved in [ibid: page 94]:

\medskip

\noindent
{\bf{C.2.1 Theorem.}}
\emph{Let $0<r_1<r_2<R$ and 
$\alpha>0$ satisfies 
$0<\alpha\leq m_f(r_1)$. Then}
\[
\int_{r_1}^{r_2}\, \chi(\{\mu_f\leq \alpha\} \cdot \log r\, dr \leq
\log 4+2 \int_{r_1}^{r_2} \,\log\log \frac{m_f(r)}{\alpha}\, dr\tag{**}
\]
\emph{where 
$\chi(\{\mu_f\leq \alpha\})$ is the characteristic function of the set
where $\mu_f(r)\leq\alpha$.}
\medskip


\noindent
{\bf{Remark.}}
In the article [xxx] from 1933
Nevanlinna found another proof of (*). 
Using  Nevanlinna's constructions , Beurling
demonstrated that
the inequality  (**) gets sharp when $\alpha$ tends to zero
which
is the interesting part of (**) above.
\bigskip

\centerline{\bf{C.3 Upper bounds for harmonic measures}}
\medskip

\noindent
 Let
$D$ be a simply connected domain and $\gamma\subset\partial D$
a subarc.
If $z\in D$ we denote by $r(z;\partial D)$, resp. $r(z,\gamma)$ the euclidian 
distance from $z$
to the boundary and to $\gamma$ respectively.
With these notations Theorem III : page 55 in [ibid] asserts that
\[
\mathfrak{m}(D,\gamma;z)\leq
\frac{4}{\pi} \cdot \arctan\,\sqrt{\frac{r(z,\partial D)}{r(z,\gamma)}}\tag{***}
\]
where the left hand side is the harmonic measure at $z$ with respect to
$\gamma$. Examples show that
this upper bound is sharp.

\bigskip


\centerline {\bf{C.4 Regular points for the Dirichlet problem.}}
\medskip

\noindent
Sections in [ibid:page 63-69]
are devoted to Dirichlet's problem. Let $\Omega$ be an open 
subset of
${\bf{C}}$.
If $f$ is a real-valued and continuous function on
$\partial\Omega$ it can be extended to some
$F\in C^0(\bar\partial\Omega)$.
Now $\Omega$ can be exhausted by an increasing sequence of subdomains
$\{\Omega_n\}$ for which the Dirichlet problem is solvable. Such exhaustions were
considered by Lebesgue
and explicit constructions
were given by de Vallé Poussin in 1910.
To each $n$ we find the harmonic function $H_n$ in $\Omega_n$
which solves the Dirichlet problem with boundary
values given by the restriction of $F$ to $\partial\Omega_n$.
Norbert  Wiener proved 
that the sequence $\{H_n\}$ converges to a unique  harmonic function
$W_f$ in $\Omega$ which is independent of the chosen
exhaustion. One refers to $W_f$ as Wiener's generalised solution.
A boundary point $z_0$ is called regular if
\[
\lim_{z\to z_0} W_f(z)= f(z_0)\quad\colon\forall\, f\in C^0(\partial\Omega)
\]
A criterion for
a boundary point to be
regular was established by 
Boulignad in 1923. Namely,
a boundary point $z_0$ is regular if and only if there
exists a positive harmonic function $V$ in $\Omega$ such that
\[
\lim_{z\to z_0} V(z)=0
\]
This condition is rather implicit
so one seeks geometric properties to
decide if a boundary point is regular or not.
In [ibid] Beurling established a sufficient regularity condition which 
goes as follows:
Let $z_0\in\partial \Omega$
and for a given $R>0$ we consider the
circular projection of
the closed complement of $\Omega$ onto the real interval $0<r<R$
defined by:
\[ 
E_\Omega(0,R)=\{ 0<r< R\,\colon\,\exists
\,\, z\in \{|z-z_0|=r\}\cap {\bf{C}}\setminus \Omega\}
\]
Following Beurling one
 says that $z_0$ is logarithmically dense  (Point
frontière de
condensation logarithmique)
if the integral
\[
\int_{E_\Omega(0,R)}\, \log \frac{1}{r}\, dr=+\infty\tag{1}
\]
Beurling proved that  (1) entails that 
then $z_0$ is a regular boundary point.
His  proof relies upon an inequality which has  independent interest.
Here is the situation considered in [ibid: page 64-66]:
Let $\Omega$ be an open set - not necessarily connected and
$R>0$ where $\Omega$ is general contains points of absolute value $\geq R$.
Consider a harmonic function $U$ in $\Omega$ with the following properties:
\[ 
\limsup_{z\to z_*}\, U(z)\leq 0\quad\colon \,
z_*\in \partial \Omega\cap \{|z|\leq R\}\tag{i}
\]
\[
U(z)\leq  M\quad\colon\, z\in \{|z|=R\}\,\cap D\tag{ii}
\]

\medskip
\noindent{\bf{C.4.1 Theorem.}}
\emph{When (i-ii) hold one has the inequality below for every
$0<r<R$}
\[
\max_{z}\, U(z)\leq 2M\cdot\, e^{-\frac{K}{2}}
\]
\emph{where the maximum in the left hand side
is taken over $\Omega\cap \{r<|z|<R\}$
and}
\[ 
K=\int_{E_\Omega(r,R)}\, \log r\, dr
\]





\bigskip





\centerline{\bf{D. Extremal length.}}
\medskip


\noindent
Let us first cite
Beurling
where he gives the following
attribute to original work
by Poincaré:
\emph{Rappelons que dans la 
théorie des fonctions analytiques, on a introduit
des élements géometriques non euclidiennes, invariants
par rapports a certaines transformation, et
cela surtout pour simplifier la thérie dont il s'agit}.
In his 
lecture at the Scandinavian Congress in
Copenhagen 1946, Beurling describes in more detail 
the  usefulness of
extremal
lengths.

\medskip

\noindent
\emph{In geometric function theory one often tries to
characterize or determine a certain mapping or quantity by
an extremal property. The method goes back to Riemann
who introduced variational methods in function theory in the form of
Dirichlet's principle. When you want to characterize
a function by an extremal property , then the class of competing functions
is very important. The wider you can make this class the more you can say
about the extremal function 
and the easier it becomes to find
good majorants or minorants, as the case may be.}




\medskip

\noindent
In his thesis
Beurling defined  an extremal distance between
pairs of points $z_0,z_1$ in  simply conected domains $\Omega$
with a finite area. The construction goes as follows:
First 
the interior distance 
is defined by
\[
\rho(z_0,z_1;\Omega)= \inf_\gamma\, \int_\gamma\, |dz|
\]
where the infimimum is taken over
rectifiable
Jordan arcs which
stay in $\Omega$ and join the two points.
Set
\[
\lambda_*(z_0,z_1;\Omega)=\sqrt{\frac{\pi}{\text{Area}(\Omega)}}|\cdot
\rho(z_0,z_1,\Omega)
\]
One refers to $\lambda_*$
as  the reduced distance. It is
not a conformal invariant and to  overcome this default
Beurling considered
the family of \emph{all triples} $(\Omega^*,z_0^*,z_1^*)$
which are conformally equivalent
to the given triple, i.e. 
there exists a conformal mapping $f\colon \Omega\to \Omega^*$
such that $f(z_\nu)= z_\nu^*$.
The \emph{extremal distance} is  defined by
\[
\lambda(z_0,z_1;\Omega)=
\sup\, \lambda_*(z^*_0,z^*_1;\Omega^*)
\]
with the supremum taken over all equivalent 
triples.
By this construction $\lambda$ yields a conformal invariant.
Next, consider
a 
triple $(z_0,z_1, \Omega)$
is the  Green's function $G(z_0,z_1;\Omega)$.
Recall that $G$ is a symmetric function of the pair $z_0,z_1$
and keeping $z_1$ fixed
\[ 
z\mapsto  G(z,z_1;\Omega)-\log\, \frac{1}{|z-z_1|}
\]
is a harmonic function
$\Omega$ which is zero on
$\partial\Omega$.
In [ibid: Théorème 1: page 29] the following fundamental result is proved:

\medskip

\noindent
{\bf{D.1 Theorem.}}
\emph{For each triple $(z_0,z_1;\Omega)$ one has the equality}
\[ 
e^{-2G}+e^{-\lambda^2}=1\tag{*}
\]


\noindent
\emph{About the proof.}
By conformal invariance it suffices to prove the equality 
for a triple $(0,a,D)$ where $D$ is the unit disc
where  the pair of points is the origin and a real point $0<a<1$.
In this case
\[
G=\log\,\frac{1}{a}
\]
Hence the theorem amounts to prove the equality
\[ 
e^{-\lambda^2}= 1-a^2
\]
or equivalently that
\[
\lambda^2=\log\,\frac{1}{1-a^2}\tag{*}
\]
We will show (*) in § XX.









\bigskip

\centerline{\bf{E. General extremal metrics.}}
\medskip

\noindent
Ten years later Beurling realised the need for a
more extensive class of extremal distances which
can be applied for domains  which are not 
simply connected. The  constructions below appear in 
the section  \emph{Extremal Distance and estimates for Harmonic Mesure}
[Collected work. Vol 1. page 361-385].


\medskip

\noindent
\emph{The numbers 
$\lambda(E,K;\Omega)(z_0).$}
Let  $\Omega$ be a connected  domain in the complex $z$-plane
whose boundary is a finite union of closed Jordan curves $\{\Gamma_\nu\}$.
Consider a pair of sets $E,K$
where
$E\subset \Gamma_\nu$
for one of the Jordan curves in $\partial \Omega$, while  $K$ is a compact subset
of $\Omega$. To a point 
$z_0\in\Omega\setminus K$
we introduce the family $\mathcal J(E,K;z_0)$ of  rectifiable Jordan
arcs $\gamma$ with the following properties:
Apart from its end-points 
$\gamma$ stays in
$\Omega\setminus K$ and  passes through  $z_0$. Moreover, the end-points
of $\gamma$ divides  the Jordan curve $\Gamma_\nu$
into a pair of closed intervals $\omega_1$ where
$E$
is contained in one  of these $\omega$-intervals.
Notice that neither $K$ or $E$
are assumed to be connected.
Next, let $\mathcal A$ be the family of positive and continuous
functions $\rho$ in $\Omega$ for which the squared area integral
\[ 
\iint_\Omega\, \rho^2(x,y)\,dxdy=1
\]
Put 
$\mathcal J= \mathcal J(E,K;z_0)$ and
for each  $\rho$-function above we set
\[
L(\rho)=\inf_{\gamma\in\mathcal J}\int\,  \,\rho(z)\,|dz|\tag{*}
\]
The extremal distance between
$E$ and $z_0$ taken in
$\Omega\setminus K$ is  defined by
\[ 
\lambda(E,K;\Omega)(z_0)= \sup_{\rho\in\mathcal A}
\,L(\rho)\tag{**}
\]


\noindent
These  $\lambda$-numbers are conformal invariants.
More precisely, let 
$(E^*,\Omega^*,K^*)$ be  another triple and 
$f\colon \Omega\setminus K\to \Omega^*\setminus K^*$
is  a conformal mapping
which extends 
continuously   to   the boundary and
gives a homeomorphism
between 
$\partial\Omega$ and $\partial\Omega^*$ where $E^*=f(E)$.
Then one has the equality
\[
\lambda(E,K;\Omega)(z_0)=\lambda(E^*,K^*;\Omega^*)(f(z_0))
\]




\noindent
Next, for each
triple $(E;\Omega,K)$ as above and every point
$z_0\in\Omega\setminus K$ there exists
the harmonic measure
$\mathfrak{m}(E;\Omega,K)(z_0)$. With these notstions 
Beurling proved the following:

\medskip

\noindent
{\bf{E.1 Theorem.}}
\emph{For every  triple $E;\Omega,K)$ and each
$z_0\in\Omega\setminus K$ 
where  $\lambda(E;\Omega,K)(z_0)\geq 2$ 
one has the inequality}
\[
\mathfrak{m}(E;\Omega,K)(z_0)\leq
3\pi\cdot e^{-\pi\cdot \lambda(E;\Omega,K)(z_0)}
\]


\noindent
This result  is often used to
estimate harmonic measures. The point is
that in the right hand side we can use
$\rho$-functions which need
not maximize the
$L$-functional in (**) and since $L(\rho)\leq\lambda(E;\Omega,K)(z_0)$
one has  in particular
\[
\mathfrak{m}(E;\Omega,K)(z_0)\leq
3\pi\cdot e^{-\pi\cdot L(\rho)}
\]
\medskip

\noindent
{\bf{E.2 The simply connected case.}}
Here $\Omega$ is  a Jordan domain 
and  $K=\emptyset$. Consider
a pair of closed subsets
$E$ and $F$ in $\partial\Omega$
which both are   a finite unions of closed subintervals.
Denote by  $\mathcal J(E,F)$  the family of
Jordan arcs $\gamma$ with
one end-point in $E$ and the other in $F$
while the interior stays in $\Omega$. Set
\[
\lambda(E;F:\Omega)=
\max_\rho\min_{\gamma\in\mathcal J}\,
\,\int_\gamma \, \rho\cdot d|z|\quad\colon\,\rho\in\mathcal A
\]
This yields  a conformal invariant which can
be determined under the extra condition that the sets
$E$ and $F$ are \emph{separated} which means
that
there exists a pair of points $p,q$ in $\partial \Omega\setminus E\cup F$
which divide $\partial \Omega$ in two intervals where $E$ belongs to one
and $F$ to the other.
Under this condition one has the equality
\[
\lambda(E;F:\Omega)=\mathcal{NS}(E;F:\Omega)\tag{1}
\]
Here  $\mathcal{NS}(E;F:\Omega)$ is  the Neumann-Schwarz number associated
to the triple $(E,F;\Omega)$ which is    found as follows:
Let $u$ be the 
harmonic function in
$\Omega$ with boundary values
$u=1$ on $E$ and 
zero on $F$ while the normal derivative
$\frac{\partial\phi}{\partial n}=0$ on $\partial\Omega\setminus E\,\cup F$.
If $v$ is the harmonic conjugate
then $v$ is increases on $E$ and decreases on $F$
and when  $v$ is normalised so that
the range $v(E)$ is an interval $[0,h]$ it follows that
$f=u+iv$ is a conformal mapping from
$\Omega$ onto a rectangular slit domain:
\[ 
\{0<x<1\}\times \{ 0<y<h\}\cup S_\nu 
\] 
where $\{S_\nu\}$ are horizontal intervals directed   into the rectangle
and with end-points on one of the vertical sides
$\{x=0\}$ or $\{y=0\}$. See  § XX for a figure.
The Neumann-Schwarz number is given by
\[
\mathcal{NS}(E,F;\Omega)=\frac{1}{\sqrt{h}}
\]
In § xx we prove that it is a conformal invariant which reduces
the proof of (1) to the case when
$\Omega$ is a rectangle as above with some removed
spikes while $E$ and $F$ are the opposed vertical lines.
If  $\rho^*$ is the constant function
$\frac{1}{\sqrt{h}}$ the fact that horisontal straight lines minimize
arc-lengths when we move from $E$ to $F$ imply that
\[ 
L(\rho^*)=\frac{1}{\sqrt{h}}\tag{2}
\]
On the other hand, let $\rho\in\mathcal A$ be non-constant.
Now
\[
0<\iint_\Omega\, (\rho-\frac{1}{\sqrt{h}})^2dxdy=2-\frac{2}{\sqrt{h}}\iint_\Omega \rho\, dxdy\implies
\iint_\Omega \rho\, dxdy<\sqrt{h}
\]
It follows that
\[
\min_{0\leq y\leq h}\, \int_0^1\,\rho(x,y)\,dx<\frac{1}{\sqrt{h}}
\]
In the left hand side appear competing $\gamma$-curves and hence
\[ 
L(\rho)<\frac{1}{\sqrt{h}}
\]
This proves that $\rho^*$ maximizes the $L$-function and 
the equality (2) entails (1).

\medskip







\noindent
{\bf{E.3 Another inequality.}}
Let $\Omega$
be a bounded and connected
domain whose boundary consists of a finite family of disjoint closed Jordan
curves $\{\Gamma_\nu\}$. Consider a pair $(z_0,\gamma)$
where $z_0\in\Omega$ and $\gamma$ is a Jordan arc
starting at $z_0$ and with
an end-point $p$ on one
boundary curve, say
$\Gamma_1$.
Next, let $K$ be a compact subset of
$\Gamma_1\setminus\{p\}$.
For each point $z\in \gamma$ we get the harmonic
measure
$\mathfrak{m}_K(z)$
which is the value at $z$ of the harmonic function in
$\Omega$ whose boundary values are one on $K$ and zero in
$\partial\Omega\setminus K$.
Set
\[ 
h^*(K,\gamma;z_0)= \max_{z\in\gamma}\, \mathfrak{m}_K(z)
\]
The  interpretation
is that one seeks a point $z\in\gamma$ where the probability for
the Browninan motion which starts at $z$
and escapes at some point in $K$
before it has reached points in
$\partial\Omega\setminus K$,
is as large as possible.
An upper bound
of $h^*$ is found using the notion of extremal length. Namely,
let
$\lambda(K;\gamma)$ be the extremal length for  the family of
curves in $\Omega$
with one end-point in $K$ and the other on
$\gamma$. Then Beurling proved that
\[
h^*(K,\gamma;z_0)\leq 5\cdot e^{-\pi\cdot \lambda(K;\gamma)}\tag{*}
\]
\medskip

\noindent
{\bf{Remark.}}
In  random walks under a Brownian motion the inequality above
shows that if $K$ is a  large obstacle
and $\gamma$ small, then the $h^*$-function
can be majorised if
some lower bound for
the extremal length can be proved. This is of interest
in configurations
with "narrow channels" when one seeks
paths  out to the boundary and 
illustrates a typical  application of extremal lengths.

\bigskip






\centerline{\emph{F. On quasianalytic series.}}
\medskip

\noindent
Let us finish with   a  result which
illustrates
Beurling's vigour in "hard analysis". The theorem below was presented
in a lecture  at the
Scandinvian congress in Helsinki 1938.
A closed subset
$E$ of ${\bf{C}}$ has positive    perimeter if 
there exists a positive constant $c$ such that
\[
\sum\ell(\gamma_\nu)\geq c
\] 
hold for every denumerable famly of
closed and rectifiable Jordan curves
$\{\gamma_\nu\}$
which surround $E$, i.e. $E$ is contained in the union of the
associated open Jordan domains.
Let $\{\alpha_k\}$ 
be a sequences of distinct complex numbers
and $\{A_k\}$  another sequence  sequence such that
\[
\sum\, |A_k|<\infty\tag{i}
\]
 Set
\[ 
F(z)= \sum\,\frac{A_k}{z-\alpha_k}\tag{*}
\]
To each $k$ we put $r_k= |A_1|+\ldots |A_k|$ and
define  $\mathcal E_f$ by
\[
 \mathcal E_f=\{ z\in{\bf{C}} \quad\colon\,
\sum_{k=2}^\infty\, \frac{A_k}{\sqrt{r_{k-1}}} \cdot \frac{1}{|z-\alpha_k|} <\infty\}
\]
It is easily seen that (i) entails that
the complement of $\mathcal E_f$ is a null set in
${\bf{C}}$. 
One says that
(*) is quasi-analytic if $F(z)$ cannot vanish 
on a closed subset $E$ of $\mathcal E_F$ with positive perimeter.
The following was proved in [ibid];
\medskip

\noindent
{\bf{F.1 Theorem.}}
\emph{The series (*) is quasi-analytic in the sense above if}
\[
\liminf_{n\to \infty}\,r_n^{\frac{1}{n}}<1
\]
In § XX we  expose some  steps in the proof based upon
some remarkable inequalities
for 
rational functions.




\newpage

\newpage


\centerline{\bf{§ 0. Holmgren's uniqueness theorem and
the heat equation.}}

\bigskip

\noindent
Given some 
$A>0$ we put
$\Omega=\{-\infty < x<+\infty\}\times
\{0<y<A\}$, and  consider a solution $u(x,y)$ to the heat equation
\[
\partial_x^2(u)= \partial_y(u)\tag{i}
\]
In addition we assume that
$u$ extends to $\{y=0\}$ and the question arises if
the 
function 
$x\mapsto u(x,0)$ determines the solution  in $\Omega$.
If $u$ satisfies the growth
condition
\[
|u(x,y)\leq e^{kx^2}\tag{ii}
\]
for some constant $k$, then
it is determined by its values on $\{y=0\}$ and
found via the usual heat kernel applied to
$u_0(x)= u(x,0)$.
Without any imposed growth condition
uniqeuness can fail. 
Such examples were known
by Hadamard  at an early stage around 1900.
In the article
\emph{Sur les solutions quasianalytiques de léquation
de la chaleur}[ Arkiv för matematik och fysik, Vol 18: 1926],
Holmgren proved that the uniqueness holds if there
exists a constant $k$ such that
\[
|u(x,y)\leq e^{kx^2\cdot \log(|x|+1)}\tag{*}
\]
That this result is essentially sharp was  demonstrated in work by Täcklund.
For example, if $\alpha>1$
there exist solutions whixh vanish identically on
a line $\{y=0\}$ while
\[
|u(x,y)\leq e^{kx^2\cdot (\log(|x|+1))^\alpha}
\]
\medskip

\noindent
{\bf{About Holmgren's proof}}.
To establish  the  uniquenss when (*) holds, the cited article starts with
constructions if suitable Greens functions
which are used
to estimate higher order derivaties of $u$.
More precisely, under the condition that
$x\mapsto u(x,0)=0$ and (*) hold, it is prived in [ibid] that 
there exists a constant
$C$
such that
\[
\frac{\partial^nu}{\partial y^n}(0,y)|\leq C^n\cdot (n\log(n+e))^n
\]
hold for every $y>0$ and
every positive integer $n$,
In addition the hypothesis that
$x\mapsto u(x,0)=0$ and the heat equation entail that
$y\mapsto u(0,y)$ is flat at $y=0$, i.e.
\[
|\frac{\partial^nu}{\partial y^n}(0,0)=0
\]
hold for every $n$.
At this stage Holmgren concludes that  $y\mapsto u(0,y)$ is the zero function
since (xx) means that it satisfies the Carleman-Denjoy inequality
which  means that we have a quasi-analytic function
of $y$  and henbce  (xx) implies that $u(0,y)=0$ for all $y$.
\medskip


\noindent
{\bf{Solutions by integral kernels.}}
The question arises if there exists a substitute for the heat kernel when
the relaxed growth condition (*) holds.
For a subclass of solutions satisfying (*) we shall construct
such a kernel function.
Denote by 
$\mathcal L$ the class of  solutions $u$  to the heat equations
for which there exists a function
$\rho(r)$ which tends to zero as $r\to+\infty$ and 
\[ 
|u(x,y)|\leq e^{\rho(|x|)x^2\cdot \log |x|}\tag{**}
\]
holds in $\Omega$.
\medskip

\noindent
{\bf{Main theorem.}}
\emph{Each $u\in \mathcal L$ is determined by $u_0(x)$.
Moreover there exists an explicit  kernel function which gives
an integral representation of
$u(x,y)$ for $0<y<A$.}
\medskip


\noindent
Following Beurling we shall contruct such  kernel
which cn be applied to solutions in the class $\mathcal L$.

\bigskip

\noindent
{\bf{1. Preliminary constructions.}}
Set
\[
\gamma(z)= (\log(z+e))^z
\quad\colon\quad
f(z)= \frac{\Gamma(z)}{\gamma(z+1/2)}
\]
where
$\Gamma(z)$ is the usual  gamma-function defined by
\[
\Gamma(z)= \int_0^\infty\, e^{-t}\cdot t^{z-1}\, dt
\]





\medskip

\noindent
{\bf{Some properties of $\gamma(z)$.}}
Let $z=1/2+iy$ and put  $a=e+1/2$.
Now
\[
\log \gamma(a+iy)=(a+iy\log\log\,(a+iy)
\]
When $y>0$ we have
\[
\log(a+iy)=\log\,|a+iy|+i\arg(a+iy)
\]
Hence the right hand side in (i) becomes
\[
(a+iy)\bigl(\log\log\,|a+iy|+i\arg(1+\frac{a+iy}{\log\,|a+iy|})\bigr)
\]
Set
\[
\rho(y)=\arg(1+\frac{a+iy}{\log\,|a+iy|})
\]
This entails that the real part in (i) becmoes
\[
a\cdot \log\log\,|a+iy|-y\cdot \rho(y)
\]
Hence
\[ 
|\gamma(a+iy)|=(\log\,|a+iy|)^a\cdot e^{-y\rho(y)}
\]
Notice that
\[ 
\lim_{y\to +\infty}\, \rho(y)= \frac{\pi}{2}
\]
So
\[
\frac{1}{\gamma(1/2+iy)|}\simeq \frac{1}{\log\,|a+iy|)^a} \cdot
e^{\pi y/2}
\] 
when $y$ is positive and large.
At the same time the functional equation for the $\Gamma$-function gives
\[
|\Gamma(1/2+iy)|^2=\frac{\pi}{\sin(\pi(1/2+iy)}
\]
This entails that
\[
|\Gamma(1/2+iy)|\simeq 2\pi\cdot e^{-\pi y/2}
\]
when $y>>0$.
So the factor $e^{pi y/2}$ which appears in (xx) is compensated by
the negative exponential for the $\Gamma$-function.
We can improve this because
$\rho(y)$ stys below $\pi/2$ for large $y$. In fact, when $y>>0$ we notice that
\[
\rho(y)\simeq \arctan\, \frac{y}{\log y}=
\pi/2-\int_{\frac{y}{\log y}}\, \frac{dt}{1+t^2}\simeq
\pi/2- \frac{\log y}{y}
\]
Hence
\[
 e^{y\rho(y)}\simeq e^{\pi y/2}\cdot y^{-1}
\]
From the above the reader can check that there exists a constant
$C$ such that
\[
\frac{|\Gamma(1/2+iy)|}{|\gamma(a+iy)|} 
\leq C\cdot \frac{1}{y\cdot \log\,|a+iy|)^a}
\quad\colon\, y\geq 1
\]
Here $a=e+1/2>1$ which entials that with $f$ as above one has an
absolutely convergent integral
\[
\int_0^\infty\, |f(1/2+iy)|\, dy
\]
In the same way the reader can check that
we get an absolutely convergent integral when
$-\infty <y\leq 0$.
\medskip


\noindent
{\bf{1.3 The function $W(z)$.}}
To begin with one applies Stirling's formula
and find that if
$-\pi/2<\theta<\pi/2$ then
\[
\log\, f(re^{i\theta})|=
\quad  \text{Check (23) on page 422 }\tag{1.3.1}
\]
Using this and
estimates as in (xx) the reader should verify that
there exists an analytic function  in the  half-plane 
$\mathfrak{Re}\, z>0$
defined by
\[ 
W(z)=\frac{1}{2\pi i}\cdot 
 \int_{\mathfrak{Re} \zeta=a}\, f(\zeta) \, z^{-\zeta}\quad\colon a>0
\tag{1.3.2}
\]
\medskip

\noindent
where
the integral in
(1.3.2) is independent of $a$. 
\medskip

\noindent
{\bf{1.4 Exercise.}}
Show that
there exists positive numbers $\alpha>0$ and $x_0>0$ such
that
\[
x>x_0\implies W(x)\leq e^{-\alpha x\log x}\tag{1.4.1}
\]
The hint is to
change the contour in (1.3.2) with respoect to $a$ in a suitable way
as $z$ is real and positive.
\medskip


\noindent
{\bf{2. The function $K(t)$.}} It is defined for real $t>0$ by
\[ 
K(t)=\frac{1}{2\pi i}\int_{\mathfrak{Re}\, z
=a}\, t^{-z}\gamma(z)\, dz=
\frac{1}{2\pi}\, \int_{-\infty}^\infty\, \gamma(a+iy)\cdot t^{-a-iy}\, dy
\tag{2.1}
\]
where $a>0$ and the reader should verify
that
(2.1) is independent of $a$. 

\medskip


\noindent
{\bf{2.2 Exercise.}} Apply the Fourier-Mellin inversion formula to show that
\[
\gamma(z)= \int_0^\infty\, t^{z-1}\, K(t)\, dt\tag{2.2.1}
\]
and shoiw via rules for convolutions under the Fourier transform that
\[
\int_0^\infty\, W(\frac{x}{t})\cdot \frac{K(t)}{\sqrt{t}}\, dt= e^{-x}\tag{2.2.2}
\]
(See page 422 for details of the proof.)
\medskip

\noindent
{\bf{2.3 Exercise.}}
Consider the ordinary heat kernel
\[
U(x,y)=e^{-x^2/y}\quad \colon y>0
\] 
and show the equality
\[ 
U(x,y)= \int_0^\infty\,
W(\frac{x^2}{4yt})\cdot \frac{K(t)}{\sqrt{t}}\,dt\tag{2.3.1}
\]




\bigskip


\noindent
{\bf{3. The function
$v(x,y)$}}. When $y>0$ we set
\[
V(x,y)=
\frac{W(\frac{x^2}{4y})}{\sqrt{y}}
\]
The previous estimates show that if
$u(x,y) $ belongs to $\mathcal L$ then
the there exists a function $v(x,y)$ defined for $y>0$ by
the convolution integral
\[
v(x,y)=\frac{1}{2\sqrt{\pi}}\cdot \int_{-\infty}^\infty\, V(x-\xi,y)\cdot u(\xi,0)\, d\xi\tag{3.1}
\]
\noindent
{\bf{4. Holmgren's integral formula.}}
With $v$ determined as above we set
\[ 
u^*(x,y)=\int_0^\infty\, v(x,yt)\cdot K(t)\, dt\tag{5-1}
\]
where the previous estimates entail that the integral conveges absolutely
for each
$0< y<A$. 
\medskip


\noindent
{\bf{4.1 Exercise.}}
Show via dominated convergence under the integrals above that
\[
\lim_{y\to 0}\,  u^*(x,y)= u(x,0)
\] 
hold for every $x$.
Moreover, use  (2.3.1) to show that
$u^*(x,y)$ satisfies the heat equation in
$\Omega$.
\medskip

\noindent
Finally, by  Holmgren's cited uniquenss theorem, it follows
that
the given solution $u$ in the class $\mathcal L$ is equal to $u^*$ and
hence (5.1) gives the requested
integral formula in the main theorem.















\newpage
































 
















\centerline{\bf{§ 1.  Radial limit of functions with  finite Dirichlet integral}}

\bigskip



\noindent
The article
\emph{Ensembles exceptionnels}
[Acta math. 1940] is devoted to
the study of functions
$f(\theta)$ on the unit circle $T$
whose harmonic extensions $H\uuu f$
to  $D$ have a finite Dirichlet integral.
A real\vvv valued functions $f(\theta)$  on the unit circle $T$
has a Fourier series:
\[
 f(\theta)=\frac{a\uuu 0}{2}+
\sum\uuu {n=1}^\infty\,a\uuu n\cdot \cos\,n\theta+
\sum\uuu {n=1}^\infty\,b\uuu n\cdot \sin\,n\theta
\]
We say that $f$ belongs to the class
$\mathcal D$ if
\[
\sum\uuu {n=1}^\infty\,n(a^2\uuu n+b^2\uuu n)<\infty\tag{*}
\]
The sum in (*) is denoted by $D(f)$
and  called the squared Dirichlet norm.
Denote by $\mathcal E\uuu f$ the set of all $\theta$ where the 
partial sums of the Fourier series of $f$ does not converge.

\medskip

\noindent
{\bf{0.1 Theorem.}}
\emph{For each $f\in \mathcal D$ 
the outer capacity of $\mathcal E\uuu f$ is zero.}
\medskip

\noindent
{\bf{Remark.}}
Recall from XXX that if $E\subset T$
then its outer capacity is defined by
\[ 
\text{Cap}^*(E)=\inf\uuu {E\subset U}\, \text{Cap}(U)
\]
with the infimum taken over open neighborhoods of $E$.
\medskip

\noindent
The proof of Theorem 0.1 relies upon
Theorem 0.2 and 0.3 below.
First, given some $f$ in the class $\mathcal D$ with constant term $a\uuu 0=0$
we obtain the harmonic
function
in the open disc defined by
 \[
 f(r,\theta)=
\sum\uuu {n=1}^\infty\,r^n(a\uuu n\cdot \cos\,n\theta+
b\uuu n\cdot \sin\,n\theta)
\]
The partial derivative with respect to $r$ becomes:
\[
 f'\uuu r(r,\theta)=\sum\uuu {n=1}^\infty\,n\
 \cdot r^{n\vvv 1}(a\uuu n\cdot \cos\,n\theta+
b\uuu n\cdot \sin\,n\theta)\tag{1}
\]
Define the function $F$ in $D$ by
\[
F(r,\theta)= \int\uuu 0^r\, |f'\uuu s(s,\theta)|\cdot ds\tag{2}
\]
Thus, for each $\theta$ we integrate
the absolute value of  (1) along a ray from the origin.
Now $r\mapsto F(r,\theta)$ is non\vvv decreasing 
for every fixed $\theta$.
Hence
there exists a limit
\[
\lim\uuu{r\to 1}\, F(r,\theta)=F^*(\theta)\tag{3}
\]
whcih can  be finite or $+\infty$.
It is clear that if (3) is finite then there exists the radial limit
\[
\lim\uuu{r\to 1}\, f(r,\theta)=f^*(\theta)\tag{4}
\]

\medskip

\noindent
Next, recall from the result in [Series]
that when the radial limit (4)
exists, then
Fourier's partial sums converge to  $f^*(\theta)$
which entails that
the following inclusion holds
for every $\rho>0$:
\[
\mathcal E\uuu f\subset \{ F^*(\theta)>\rho\}\tag{5}
\]


\noindent
We conclude that  
Theorem 0.1 follows if 
\[
\lim_{\rho\to+\infty}\,\text{Cap}\{F^*>\rho\}=0\tag{6}
\]
Here (6) follows from the following more precise result:

\medskip

\noindent
{\bf{0.2 Theorem.}}
\emph{Let $f\in\mathcal D$ where $a\uuu 0=0$
and $D(f)=1$. Then}
\[ 
\text{Cap}(\{F^*>\rho\})\leq e^{\vvv \rho^2}
\quad\text{hold for every}\,\,\,  \rho>0
\]

\medskip


\noindent
The essential step to get
Theorem 0.2 relies upon  the following
inequality:

\bigskip

\noindent{\bf{0.3 Theorem.}}
\emph{For each $f\in\mathcal D$ with $a\uuu 0=0$
one has   $F^*\in\mathcal D$ and}
\[ 
D(F^*)\leq D(f)
\]


\noindent
Theorem 0.3 is
proved in § 1 and
after we deduce
deduce 
Theorem 0.2 in § 2.
Before we proceed to § 1 we 
need some preliminary  results.
\medskip

\centerline{\bf{0.4 On logarithmic potentials.}}
\medskip


\noindent
Let $\mu$ be a probability measure on $T$ and put
\[
U\uuu \mu(z)=\int\ \log\,\frac{1}
{|z\vvv\zeta|}\cdot d\mu(\zeta)
\]
This is a harmonic function in $\{|z|<1\}$
and passing to its radial limits as $r\to 1$
the energy integral is defined by:
\[
J(\mu)=\lim\uuu{r\to 1}\,\int\, U\uuu \mu(r,\theta)\cdot d\mu(\theta)=
\int\, U\uuu \mu(\theta)\cdot d\mu(\theta)\tag{*}
\]
One says that $\mu$ has finite energy when (*) is finite.
To check when this holds
we use
polar coordinates
in $D$ and the   series expansion: 
\[ 
U\uuu\mu(r,\theta)=\sum\, \frac{r^n}{n}(
h\uuu n\cos\,n\theta+
k\uuu n\sin\,n\theta)
\]
where $\{h\uuu n\}$ and $\{k\uuu n\}$ are real 
numbers which will be determined in (2) below.
Then  $J(\mu)$ is 
the limit of the following expression as $r\to 1$:
\[
 \int \,U\uuu\mu(r,\phi)\cdot d\mu(\phi)
=\iint\, \log\, \frac{1}{|1\vvv re^{i(\phi\vvv\theta)}|}
d\mu(\phi)\cdot d\mu(\theta)\tag{1}
\]
To compute the right hand side we expand the
complex log\vvv function:
\[
\log\,\frac{1}{1\vvv re^{i(\phi\vvv\theta)}}
=\sum\uuu {n=1}^\infty \, \frac{r^n}{n}\cdot
e^{in(\phi\vvv\theta)}
\]
Taking real parts it follows that
(1) is equal to
\[
\sum\uuu {n=1}^\infty \, \frac{r^n}{n}\cdot
\cos\, n(\phi\vvv\theta)\cdot d\mu(\phi)\cdot d\mu(\theta)
\]
Now we use the trigonometric formula
\[
\cos\, n(\phi\vvv\theta)=\cos n\phi\cdot \cos n\theta+
\sin n\phi\cdot \sin n\theta
\]
Put 
\[ 
h\uuu n=\int\, \cos\,n\theta\cdot d\mu(\theta)\quad\text{and}\quad
k\uuu n=\int\, \sin\,n\theta\cdot d\mu(\theta)\tag{2}
\]
From the above it follows that
\[ 
J(\mu)= \sum \frac{1}{n}(h^2\uuu n+k\uuu n^2)\tag{3}
\]
\medskip

\noindent
Next, let   $g(\theta)\in\mathcal D$
with Fourier coefficients
$\{a\uuu n\}$ and $\{b\uuu n\}$ where $a\uuu 0=0$.
Then we have

\[
\int\, g\cdot d\mu=
\sum\, a\uuu n\cdot h\uuu n+b\uuu n\cdot k\uuu n
\]
and Cauchy\vvv Schwarz inequality gives:
\[
[\int\, g\cdot d\mu]^2\leq S(g)\cdot J(\mu)\tag{4}
\]

\medskip

\noindent
From the above we obtain the following:
\medskip


\noindent
{\bf{0.5 Theorem.}}
\emph{For each probability measure $\mu$ with finite energy and every
function $g(\theta)\in\mathcal D$  which is lower semi\vvv continuous
one has the 
inequality}

\[
\bigl[ \int\, g(\theta)\cdot d\mu(\theta)\bigr]^2\leq
S(g)\cdot J(\mu)
\]
\bigskip


\noindent
{\bf{Remark.}} Above the lower semi\vvv continuity is imposed in order to
ensure that the Borel integral of $g$ with respect to
$\mu$ is defined.









\bigskip





\noindent
\centerline{\bf{1. Proof of Theorem 0.3}}

\medskip

\noindent
To begin with one has

\medskip

\noindent
{\bf{1.1 Lemma.}} \emph{The function $F$ is subharmonic in $D$.}
\medskip

\noindent
For each fixed $0<\alpha<1$
we define the function $\phi\uuu\alpha$ in $D$ by
\[
\phi\uuu \alpha(x,y)= \frac{\partial}{\partial\alpha}\, f(\alpha x,\alpha y)
=x\cdot f'\uuu x(\alpha x,\alpha y)+y\cdot f'\uuu y(\alpha x,\alpha y)
\]
Notice
that the function $f\uuu\alpha(x,y)= f(\alpha x,\alpha y)$
is harmonic and (1) means that 
\[ 
\phi\uuu \alpha=(x\partial\uuu x+y\partial \uuu y)(f\uuu \alpha)
\] 
where
$\mathfrak{e}= x\partial\uuu x+y\partial \uuu y$ is the 
Euler field. As explained in XX this first order operator
satisfies the identity
\[ 
\Delta\circ \mathfrak{e}= \Delta+\mathfrak{e}\cdot \Delta
\]
in the ring of differential operators and hence
$\phi\uuu\alpha$ is harmonic.
Next, the absolute value of a harmonic function is subharmonic so
$\{|\phi\uuu\alpha|\}$  yield subharmonic functions and
a change of variables gives:
\[ 
F=\int\uuu 0^1\, |\phi\uuu\alpha|\cdot d\alpha
\]
This shows that $F$ is a Riemann integral of subharmonic functions
which in compact subsets of $D$ is uniformly approximated by 
finite sums 
\[
\frac{1}{N}\sum\uuu {k=1}^{k=N}  |\phi\uuu{k/N}|
\]
Lemma 1.1 follows since
a convex sum of subharmonic
functions again is subharmonic.
\bigskip

\noindent
{\bf{An inequality.}}
The function $F(r,\theta)$
is continuous and its derivative with respect to $r$
exists and equals $|f'\uuu r(r,\theta)|$.
But the partial derivative $\partial F/\partial\theta$ may have jump 
discontinuities 
along rays where the derivative  $f'\uuu r$ has a zero. However,
this cannot occur too  often so when $0<r<1$ is fixed there exists the integral
\[
I(r)= \int\uuu 0^{2\pi}\, (\frac{\partial F}{\partial\theta}(r,\theta))^2 \cdot d\theta
\]
\medskip

\noindent
We have proved that $F$ is subharmonic and by its construction
the partial derivative
$\partial F/\partial r$ is non\vvv negative.
The  result in Chapter V:B:xxx gives
 
\medskip
 
 \noindent
{\bf{1.2 Lemma.}} \emph{The inequality below holds for each $0<r<1$:}
\[ 
I(r)\leq 
r^2\cdot \int\uuu 0^{2\pi}\, 
\bigl(\frac{\partial F}{\partial r}(r,\theta)\bigr)^2 \cdot d\theta\tag{*}
\]







\medskip

\noindent
{\bf{1.3 Dirichlet integrals.}}
Let $f\in \mathcal D$ with $a\uuu 0=0$ and
construct the Dirichlet integral 
\[
\text{Dir}(f)=\frac{1}{\pi}\cdot \iiint\uuu D\,  
[(f'\uuu x)^2+(f'\uuu y)^2]\cdot dxdy
\]
Then one has the equality:
\[
\text{Dir}(f)=D(f)\tag{*}
\]
To see this we identify $f(r,\theta)$ with the real part of the analytic function

\[
G(z)=\sum\, (a\uuu n\vvv i\cdot b\uuu n)\cdot z^n
\]
The Cauchy\vvv Riemann equations give
\[
\text{Dir}(f)=\frac{1}{\pi}\cdot \iiint\uuu D\,  
|G'(z)|^2\cdot dxdy
\]
Now the reader can verify that the double integral above is equal to $D(f)$.
Notice that (*) identifies  $\mathcal D$ with the space
of real\vvv valued functions on $T$ whose harmonic extensions to $D$ have a finite Dirichlet
integral.
\medskip

\noindent
{\bf{1.4 Exercise.}}
Show that the Dirichlet integral 
of a function $g$ of class $C^2$ in $D$
also is given by the double integral
\[
\frac{1}{\pi}\cdot 
\int\uuu 0^1\int\uuu 0^{2\pi}\, 
\bigl[\, r^2\cdot \bigl(\frac{\partial g}{\partial r}\bigr)^2+
\frac{1}{r^2}\cdot\bigl(\frac{\partial g}{\partial \theta}\bigr)^2\,\bigr]
\cdot r\cdot d\theta dr\tag{i}
\]
Show also that if $g$ is harmonic then
\[
 \text{Dir}(g)= \frac{2}{\pi}\cdot 
\int\uuu 0^1\int\uuu 0^{2\pi}\, 
\bigl(\frac{\partial g}{\partial r}\bigr)^2
\cdot r\cdot d\theta dr\tag{ii}
\]

\bigskip


\centerline{\emph{1.5 Final part of the proof of Theorem 0.3}}
\bigskip

\noindent 
Apply (i) in 1.4 with $g=F$ where
the inequality in Lemma 1.2 and
an integration 
with respect
to $r$ give
\[ 
\text{Dir}(F)\leq \frac{2}{\pi}\cdot 
\int\uuu 0^1\int\uuu 0^{2\pi}\, 
\bigl(\frac{\partial F}{\partial r}\bigr)^2\cdot r\cdot d\theta dr\tag{1}
\]

\noindent
Next,  the construction of $F$ gives the equality
\[
(\frac{\partial F}{\partial r}\bigr)^2=
(\frac{\partial f}{\partial r}\bigr)^2
\] 
in the whole disc $D$.
Then (1) and the equality (ii) applied to the harmonic function
$f$ give:
\[
\text{Dir}(F)\leq \text{Dir}(f)=D(f)\tag{2}
\]
where the last equality used (*) in 1.3.
Next, construct the harmonic extension of 
the boundary function $F^*(\theta)$ which we denote by $H\uuu F$.
Here we have the equations
\[
D(F^*)= D(H\uuu F)\tag{3}
\]
Next, recall  that the Dirchlet integral is minimized when we take
a harmonic extension which entails that
\[
\text{Dir}(H\uuu F)\leq
\text{Dir}(F)\tag{4}
\]
Hence (2\vvv 4) give the requested inequality
\[
D(F^*)\leq D(f)
\]






\bigskip


\centerline{\bf{2. Proof of Theorem 0.2}}

\bigskip



\noindent
Let $\rho>0$ and
apply  Theorem 0.5  to the function $g=F^*$ and the equilibrium 
distribution $\mu$ assigned to the
set $E=\{F^*>\rho\}$. This   gives
\[ 
\rho^2\leq \bigl[\int F^*\cdot d\mu\,\bigr]^2\leq S(F^*)\cdot J(\mu)\tag{1}
\]
Now $D(F^*)\leq D(f)=1$ holds by Theorem 0.3
and hence we have:
\[
\rho^2\leq J(\mu)\tag{2}
\]
Next, recall from § XX that $J(\mu)$ is 
the the constant value $\gamma(E)$
of the potential function 
$U\uuu\mu$ restricted to $E$.
Hence (1) gives
\[
e^{\vvv\gamma(E)}\leq e^{\vvv \rho^2}\tag{3}
\]
By definition the left hand side is the capacity of $E$
which proves Theorem 0.2.



\bigskip

\centerline{\bf{3. An application}}
\bigskip


\noindent
Let $\Omega$ be a simply connected domain which contains
the origin in the complex $\zeta$\vvv plane and
$\partial\Omega$ contains a relatively open set given
by
an interval $\ell$ situated on the line
$\mathfrak{Re}\,\zeta=\rho$ for some $\rho>0$.
Consider the harmonic measure
$\mathfrak{m}\uuu 0^\Omega(\ell)$.
In other words, the value at the origin of the harmonic function
in $\Omega$ which is 1 on $\ell$ and zero on
$\partial\Omega\setminus\ell$.
We shall find an upper bound for (*) 
from the introduction in the family of simply connected domains
which contain the origin and $\ell$ and  have area $\pi$.
To attain this we
consider the conformal map $\phi$ from the unit disc onto
$\Omega$ with $\phi(0)=0$.
The invariance of harmonic measures gives:
\[
\mathfrak{m}\uuu 0^\Omega(\ell)=
\mathfrak{m}\uuu 0^D(\alpha)
\] 
where $\alpha$ is the interval on $T$ such that
$\phi(\alpha)=\ell$.
For an interval on the unit circle one has  the equality
\[
\text{Cap}(\alpha)= \sin\,\alpha/4
\]
At the same time
$\mathfrak{m}\uuu 0^D(\alpha)=\frac{\alpha}{2\pi}$ which entails that
\[
\mathfrak{m}\uuu 0^\Omega(\ell)=
\frac{2}{\pi}\,\arcsin\, \text{Cap}(\alpha)\tag{1}
\]


\noindent
There remains to estimate  last term above.
Put $u=\mathfrak{Re}\,\phi$.
The inclusion $\ell\subset\mathfrak{Re}\zeta=\rho$
means that $u=\rho$ on $\ell$.
So when $\phi$ is considered in the class $\mathcal S$
we have the inclusion
\[
\alpha\subset\{|\phi|>\rho\vvv \epsilon\}
\]
for each $\epsilon>0$.
Next, since the area of $\phi(D)=\pi$
we have $S(u)=1$
and Theorem 0.2 gives 
\[
\text{Cap}(\alpha)\leq e^{\vvv\rho^2}
\]
Hence we have proved the general inequality
\[
\mathfrak{m}\uuu 0^\Omega(\ell)\leq \frac{2}{\pi}\cdot \arcsin\,
e^{\vvv\rho^2}\tag{**}
\]
\medskip

\noindent
{\bf{Remark.}}
There exists
a special simply connected domain $\Omega$ for which equality holds
in (**).
See [Frostman: p. 39] : Potential theory.

\bigskip




\centerline{\bf{4. Sets of uniqueness for analytic functions in the unit disc.}}

\medskip

\noindent
When $E$ is a closed subset of the unit circle $T$
we get the function  $\phi_E(t)$ which to every $t>0$
is the linear measure of
the set of points on $T$ whose distance to $E$ is $\leq t$.
Denote by $\mathcal E$
the family of closed subsets in $T$ such that
\[ 
\int_0^1\,\frac{\phi_E(t)}{t}\, dt<\infty\tag{*}
\]
An equivalent condtion is that
\[
\sum\, \ell_\nu\cdot \log \ell_\nu<\infty\tag{**}
\]
where $\{\ell_\nu\}$ are the length of the open intecvals
in the complementary set $T\setminus E$. The proof of this equivalence is
easy and left as an exercise. See also my notes in measure theory for 
a proof. 
Next, for each positive integer  $m$
we denote by
 $A^m(D)$ the family of $m$-times continuously differentiable functions on
$T$ which extend to analytic functions in the unit disc.
 The following result is due to
Carleson and proved in the article  article [Acta-1952].

 
\medskip

\noindent

\noindent
{\bf{4.1 Theorem.}}
\emph{If  $E$ belongs to $\mathcal E$.
there exists for every positive integer $m$
a function $f\in A^m(D)$ such that $f=0$ on $E$
while $f$ is not identically zero.}
\medskip

\noindent
That  condition (*) is crucial for the existence of smooth functions in
the disc algebra which are zero on $E$ can be seen 
from a uniqueness result due to Beurling which
goes as follows:
\medskip

\noindent
{\bf{4.2 Theorem.}}
\emph{Let $E$ be a closed subset in $T$ outside the family
$\mathcal E$.
Then 
each $f\in A(D)$ which is Hölder continuous of some order
$\alpha>0$
which is zero on $E$ must vanish identically.}
\medskip


\noindent
Proofs of the results above are  given in § XXX.
Next we shall consider closed sets
$E$ with a positive logarithmic capacity which 
means that
there exists a probability  measure $\mu$ on $E$ whose energy intergal
\[
\iint\,\log\,\frac{1}{|e^{i\theta}-e^{i\phi}|}\,
d\mu(\theta)\cdot d\mu(\phi)<\infty
\]
\medskip

\noindent
Denote by $\mathcal D$ the class of analytic functions
$f$ in $D$ with a finite Dirichlet integral, i.e.
\[ 
\text{Dir}(f)=
\iint_D\, |f'(z)|^2\, dxdy<\infty
\]

In § XX from Special Tpoics we proved a result due to Beurling which
asserts that
if $f\in\mathcal D$
then the radial limits
\[
\lim_{r\to 1}\, f(re^{i\theta})\tag{1}
\]
exists for all $\theta$ outside a set whose logartihmic capacity is zero.
\medskip

\noindent
{\bf{4.3 The class $\mathcal D_E$.}}
Let $E$ be  a closed subset of $T$ with 
positive logarithmic capacity and belongd to $\mathcal E$.
If $f\in\mathcal D$ Beurling's result in Theorem 0.1 gives
a set
$\mathcal N_f$
of outer logarthmic capactiy zero such that
the radial limits exist in
$T\setminus \mathcal N_f$.
Now $\mathcal D_E$ is the family of functions $f\in\mathcal D$ 
for which the  set of non-zero Beurling limits in $E\setminus \mathcal N_f$
has outer logarithmic capacaity zero.
Notice that Theorem 4.1 implies that
$\mathcal D_E$  contains
functions which are not identically
zero.
Denote by  $\mathcal D_E^*$  the  functions $f$ 
in $\mathcal D_E$ which are normalised so that $f(0)=1$.
\medskip

\noindent
{\bf{4.3.1  Theorem.}}
\emph{Let  $E$ be  as above. Then 
the variational problem}
\[
\min_{f\in \mathcal D_E^*}\, \text{Dir}(f)
\]
\emph{has a unique solution. Moreover, the extremal function
$f_E$
extends to a continuous function in
$\bar D\setminus E$ without zeros and the complex derivative
$f'(z)$ extends to an analytic function in
${\bf{C}}\setminus E$.}
\bigskip

\noindent
{\bf{Remark.}} This is the major result in
Carleson's article [ibid].
That the variational problem has a unique solution
$f_E$ whose Dirichlet intergal is $>0$ is
fairly easy to establish. The remaining parts of the proof
involve several steps.
First Theorem 0.1 is used to
show that
$f_E$ extends continuously to $\bar D\setminus E$
and the boundary value function $f(e^{i\theta})$
is locally Lipschitz continuous on the open
set
$T\setminus E$.
Using this regularity  the next step is to show
that
$f_E$ has no zeros on $T\setminus E$.
To prove this one uses the extremal property which entails that
if $\tau(z)$ is an arbitrary function in
$A^2(D)$
which is zero at the origin, then
\[ 
t\mapsto D(f\cdot e^{t\tau})
\]
achieves its minimum when $t$ varies over real numbers.
The final step in  proof is to
show that
the previous facts imply that the derivative $f'$ extends to
be analytic in ${\bf{C}}\setminus E$.
We refer to § xx where material from [ibd] is exposed.
\bigskip

















\newpage

\centerline{\bf{§ 2. An automorphism on product measures}}

\bigskip


\noindent
{\bf{Introduction.}}
The  results is   expose material from
the article 
[Beurling]. Before  the   measure theoretic study starts 
we
insert comments from [Beurling] about 
the  significance of the main theorem in 0.§§ below.

\medskip


\noindent
{\bf{Schrödinger equations.}}
The article
\emph{Théorie relativiste de l'electron et l'interprétation
de la mécanique quantique} was published 1932. Here
Schrödinger raised a new and unorthodox question concerning Brownian motions
leading to new mathematical problems of considerable interest.
More precisely, consider a Brownian motion which takes place in a bounded
region $\Omega$ of some euclidian space
${\bf{R}}^d$ for some $d\geq 2$.
At time $t=0$
the densities of particles 
under observation is given by some
non\vvv negative function $f\uuu 0(x)$ 
defined on $\Omega$.
Classically the density at a later time $t>0$
is equal to
a function
$x\mapsto u(x,t)$ where
$u(x,t)$ solves the heat equation
\[
\frac{\partial u}{\partial t}= \Delta(u)
\] 
with boundary conditions 
\[
u(x,0)=f\uuu 0(x)\quad\text{and}\quad
\frac{\partial u}{\partial {\bf{n}}}(x,t)= 0
\quad\text{when }\quad x\in \partial\Omega\quad\text{and}\quad t>0\tag{1}
\]
Schrödinger took into the account
the reality of quantum physics which
means that in an  actual experiment
the observed density of particles at a time
$t\uuu 1>0$ does not coincide with $u(x,t\uuu 1)$.
He posed the problem to find the most probable development during the time
interval $[0,t\uuu 1)$ which leads to the state at time
$t\uuu 1$.
He concluded  that
the the requested density
function   which
substitutes the heat\vvv solution $u(x,t)$
should belong to a non\vvv linear class of functions formed by
products
\[ 
w(x,t)= u\uuu 0(x,t)\cdot u\uuu 1(x,t)\tag{*}
\]
where $u\uuu 0$ is a solution to (1) 
while $u\uuu 1(x,t)$ is a solution to an adjoint equation
\[
\frac{\partial u\uuu 1}{\partial t}= \vvv\Delta(u)
\quad\colon\quad
\frac{\partial u\uuu 1}{\partial {\bf{n}}}(x,t)= 0
\quad\text{on}\quad \partial\Omega\tag{2}
\] 
defined when $t<t\uuu 1$.
This leads to a new type of Cauchy problems
where one asks if there exists a  $w$\vvv function given by (*)
satisfying
\[ 
w(x,0)= f\uuu 0(x)\quad\colon\quad w(x,t\uuu 1)=f\uuu 1(x)
\]
where $f\uuu 0,f\uuu 1$ are non\vvv negative functions
such that
\[
\int\uuu\Omega\, f\uuu 0\cdot dx=
\int\uuu\Omega\, f\uuu 1\cdot dx
\]
\medskip

\noindent
The solvability of this non\vvv linear boundary value problem was left open
by Schrödinger and the search for  solutions has remained as an active field
in mathematical physics.
When $\Omega$ is a bounded set
and has a smooth boundary
one can use the Poisson\vvv Greens function for the
classical equation (*)  and 
rewrite Schrödinger's equation  to 
a system of non\vvv linear integral equations.
The interested reader should consult the talk by I.N. Bernstein a the IMU\vvv congress at Zürich 1932 for a first account about mathematical solutions to
Schrödinger equations.
Examples occur already  on the product
of two copies of the real line where Schrödinger's equations lead to
certain non\vvv linear equation for measures which goes as follows:
Consider the Gaussian density function


\[
g(x)=\frac{1}{\sqrt{2\pi}}\cdot e^{\vvv x^2/2}
\]

\medskip

\noindent
Next, consider the family $\mathcal S\uuu g^*$
of all non\vvv negative product measures
$\gamma\uuu 1\times\gamma\uuu 2 $ for which
\[
\iint g(x\uuu 1\vvv x\uuu 2)\cdot d\gamma\uuu 1(x\uuu 1)
\cdot d\gamma\uuu 2(x\uuu 2)=1\tag{i}
\]
The product measure gives another product measure 
\[
\mathcal T\uuu g(\gamma\uuu 1\times\gamma\uuu 2)=
\mu\uuu 1\times\mu\uuu 2
\]
where
\[
\mu\uuu 1(E\uuu 1)\cdot \mu\uuu 2(E\uuu 2)=
\iint \uuu {E\uuu 1\times E\uuu 2}\,
g(x\uuu 1\vvv x\uuu 2)\cdot d\gamma\uuu 1(x\uuu 1)
\cdot d\gamma\uuu 2(x\uuu 2)
\] 
hold for all pairs of bounded Borel sets.
Notice that $\mu\uuu 1\times \mu\uuu 2$
becomes a probability measure since (i) above holds.
With these notations one has

\medskip

\noindent
{\bf{0.1 Theorem.}}
\emph{For every product measure
$\mu\uuu1\times\mu\uuu2$ which in addition is a probability measure there exists
a unique $\gamma\uuu 1\times\gamma\uuu 2$ in $S^*\uuu g$
such that}
\[
\mathcal T\uuu g(\gamma\uuu 1\times\gamma\uuu 2)=\mu\uuu1\times\mu\uuu2
\]
\medskip


\noindent
In [Beurling]
a more general result is established
where the  $g$\vvv function can be replaced by
an arbitrary  non\vvv negative and bounded function $k(x\uuu 1,x\uuu 2)$
such that
\[
\iint\uuu{{\bf{R}}^2}\,\log \, k\cdot dx\uuu 1dx\uuu 2>\vvv \infty
\]
\bigskip
  

\centerline{\bf{1. The $\mathcal T$\vvv operator and
product measures}}

\bigskip


\noindent
Let $n\geq 2$ and consider an $n$\vvv tuple of
sample spaces $\{X\uuu\nu=(\Omega\uuu\nu,\mathcal B\uuu\nu)\}$.
We get the product space
\[ 
Y=\prod X\uuu\nu
\]
whose sample space is the set\vvv theoretic product
$\prod\,\Omega\uuu\nu$ and   Boolean $\sigma$\vvv algebra 
$\mathcal B$ generated by
$\{\mathcal  B\uuu \nu\}$.
\medskip


\noindent
{\bf{0.1 Product measures.}}
Let $\{\gamma\uuu\nu\}$ be an $n$\vvv tuple of signed measures on
$X\uuu 1,\ldots,X\uuu n$ where  each $\gamma\uuu\nu$
has a finite total variation. There exists a unique measure $\gamma^*$
on $Y$ such that
\[ 
\gamma^*(
E\uuu 1\times\ldots\times E\uuu n)=
\prod\,\gamma\uuu\nu(E\uuu\nu)
\]
hold for every $n$\vvv tuple of $\{\mathcal B\uuu\nu\}$\vvv measurable sets.
We refer to $\gamma^*$ as the product measure. It is
uniquely determined  because $\mathcal B$ is generated
by
product sets $E\uuu 1\times\ldots\times E\uuu n)$
with each $E\uuu\nu\in\mathcal B\uuu\nu$.
When no confusion is possible we put
\[
 \gamma^*=\prod\,\gamma\uuu\nu
\]

\noindent
The family of all such product measures is denoted by $\text{prod}(\mathcal M\uuu B)$.

\medskip

\noindent
{\bf{0.2 Remark.}}
The set of product measures is a proper non\vvv linear subset of the space
$\mathcal M\uuu B$ of all signed measures on $Y$.
This is already seen when $n=2$ with two discrete sample spaces, i.e.
$X\uuu 1$ and $X\uuu 2$  consists of $N$
points for some integer $N$. A
Every $N\times n$\vvv matrix with 
non\vvv negative elements $\{a\uuu{jk}\}$
give a probability measure $\mu$ on
$X\uuu 1\times X\uuu 2$
when the double sum $\sum\sum\, a\uuu{jk}=1$
The condition that $\mu$ is a product measure is tha there exist
$N$\vvv tuples $\{\alpha\uuu j$ and $\{\beta\uuu k\}$
such that $\sum\,\alpha\uuu \nu=\sum\,\beta\uuu k=1$
and 
$a\uuu{jk}=\alpha\uuu j\cdot \beta\uuu k$.
\bigskip

\noindent
{\bf{0.3 The space $\mathcal A$}}.
We have the linear space 
of functions on $Y$
whose elements are of the form
\[
a=g\uuu 1^*+\ldots+g\uuu n^*\tag{i}
\] 
where  $\{g\uuu\nu\} $  are functions on the separate
product factors
$\{X\uuu\nu\}$. It is clear that a pait of product measures
$\gamma$ and $\mu$ on $Y$ are equal if and only if
\[
\int\uuu Y\, a\cdot d\gamma=
\int\uuu Y\, a\cdot d\mu
\] 
hold for every $a\in\mathcal A$.
\medskip


\noindent
{\bf{0.4 The measure $e^a\cdot \gamma^*$}}
Let $a=\sum\, g^*\uuu\nu$ be as above.
Then we get the exponential function
\[
e^a=\prod \, e^{g^*\uuu\nu}
\]
If $\gamma^*=\prod\,\gamma\uuu\nu$ is some product measure
we get a new product measure defined by

\[
e^a\cdot \gamma\uuu *= \prod\, e^{g\uuu\nu}\cdot \gamma\uuu\nu
\]


\noindent
{\bf{0.5 The $\mathcal T$\vvv operators.}}
To every bounded
$\mathcal B$\vvv measurable function $k$ we shall construct a map $\mathcal T\uuu k$
from the space of product measures into itself.
First, let 
$1\leq\nu\leq n$ be given and  $g\uuu\nu $ is some
$\mathcal B\uuu\nu$\vvv measurable function. 
Then there exists the function $g\uuu\nu^*$
on the product space $Y$ defined by
\[
g\uuu\nu ^*(x\uuu 1,\ldots,x\uuu n)=g\uuu\nu (x\uuu \nu)
\]
Let us now consider a product measure
$\gamma$.  If $1\leq\nu\leq n$ we find a unique measure on $X\uuu \nu$
denoted by $(k\cdot\gamma)\uuu\nu$ such that
\[
\int\uuu Y\, g^*\uuu\nu\cdot k\cdot d\gamma=
\int\uuu{X\uuu\nu}\, g\uuu\nu\cdot d(k\cdot\gamma)\uuu\nu
\]
hold for every bounded
$\mathcal B\uuu\nu$\vvv measurable function $g\uuu\nu$ on $X\uuu\nu$.
Now we get
the product measure
\[ 
\mathcal T\uuu k(\gamma)=\prod\, (k\gamma)\uuu\nu\tag{*}
\]

\medskip

\noindent
{\bf{Remark.}}
In the the case when  
\[
k(x\uuu 1,\ldots,x\uuu n)=g^*\uuu 1\cdots g^*\uuu n
\]
we see that 
\[ 
\mathcal T\uuu k(\gamma)= \prod\, g\uuu\nu\cdot \gamma\nu
\]
\medskip

\noindent
{\bf{Exercise.}}
Consider the case $n=2$ where $X\uuu 1$ and $X\uuu 2$ both consist of two points, say
$a\uuu 1,a\uuu 2$ and $b\uuu 1,b\uuu 2$ respectively.
A measure $\gamma\in S^*\uuu 1$
is given by $\gamma\uuu 1\times\gamma\uuu 2$ and we can identify
this product measure by a $2\times 2$\vvv matrix
\[
XXX
\]
where $\alpha\uuu i\cdot \beta\uuu \nu$ is the mass of $\gamma$ at
the point $(a\uuu i,b\uuu \nu)$. Next, let $k$ be a positive function on
the product space which means that we assign four positive numbers
\[
k\uuu{i,\nu}=
k(a\uuu i,b\uuu\nu)
\]
Find the measure $\mathcal T\uuu k(\gamma)$ and
express it as above by a $2\times 2$\vvv matrix.



\bigskip





\noindent
Now we are prepared to announce the main result in
this section.
Consider a positive $\mathcal B$\vvv measurable function $k$
such that  $k$ and $k^{\vvv 1}$
both are bounded functions.
Denote by $\mathcal S^*\uuu k$ the family of non\vvv negative product measures
$\gamma$ on $Y$ such that
\[
\int\uuu Y\, k\cdot d\gamma=1
\]
We have also the set $\mathcal S^*\uuu 1$ 
of product measures $\mu$ which are non\vvv negative and have
total mass one, i.e.
\[
\int\uuu Y\, d\mu=1
\]


\noindent
It is easily seen   that $\mathcal T\uuu k$ yields
an injective
map from  $S^*\uuu k$ into $S^*\uuu 1$. It turns out that the map also
is surjective, i.e. the following hold:




\medskip

\noindent
{\bf{Main Theorem.}}
\emph{$\mathcal T\uuu k$ yields a homeomorphism between $S^*\uuu k$ and $S^*\uuu 1$}.

\bigskip

\noindent
{\bf{0.6 Remark.}}
Above we refer to  the norm topology on the space of measure, i.e.
if $\gamma\uuu 1$ and $\gamma\uuu 2$ are two  measures on
$Y$ then
the norm $||\gamma\uuu 1\vvv \gamma\uuu 2||$ is the total variation of
the signed measure $\gamma\uuu 1\vvv\gamma\uuu 2$.
The reader may verify that
$S^*\uuu k$ and $S^*\uuu 1$
both appear as closed subsets in the
normed space of all signed measures on $Y$.
Recall also from XX that the space of measures on $Y$
is complete under this norm.
In particular, let $\{\mu\uuu \nu\}$
be a Cauchy sequence with respect to the norm where
each $\mu\uuu\nu\in \mathcal S^*\uuu 1$. Then there exists a strong limit
$\mu^*$ where $\mu^*$ again belongs to $\mathcal S^*\uuu 1$
and
\[
||\mu\uuu\nu\vvv \mu^*||\to 0
\]
This completeness property will
be used in the subsequent proof.
We shall also need some inequalities
which are announced below.

\medskip

\noindent
{\bf{0.7 Some useful inequalities.}}
Let $\gamma\uuu 1$ and $\gamma\uuu 2$
be a pair of product measures 
such that
\[ 
\bigl|\int\uuu Y\, g^*\uuu \nu\cdot d\gamma\uuu 1\vvv
\int\uuu Y\, g^*\uuu \nu\cdot d\gamma\uuu 2\bigr |\leq\epsilon
\quad\colon\quad 1\leq\nu\leq n
\] 
hold for 
some $\epsilon>0$
and every function $g\uuu\nu$ on $X\uuu\nu$ with maximum norm
$\leq 1$. Then the norm
\[ 
||\gamma\uuu 1\vvv \gamma\uuu 2||\leq n\cdot \epsilon\tag{i}
\]


\noindent
The proof of (i) is  left to the reader
where the hint is to 
make repeated  use of  Fubini's theorem.
More generally, let
$k$ be a bounded measurable function on $Y$
and $\gamma,\mu$ is a pair of product measures.
Denote by $\mathcal A\uuu *$ the set of
$\mathcal A$\vvv functions $a$ with maximum norm
$\leq 1$. Then there exists a constant $C$ which only depends on $k$ and
$n$ such that




\[
||\mathcal T\uuu k(\mu)\vvv \gamma||\leq
\max\uuu {a\in A\uuu *}\, \bigl|\int\uuu Y\, a(kd\mu\vvv d\gamma)\,\bigr|\tag{*}
\]

\noindent
Again we leave the proof as an exercise.
\medskip










\noindent
{\bf{0.8 A variational problem.}}
Since we already have observed that
$\mathcal T\uuu k$ is injective there remains to
prove surjectivity.
For this we shall study a
a variational
problem which we begin to describe  before the proof is finished in 0.§§ X below.
We are given the function $k$ on $Y$ where both $k$ and $k^{\vvv 1}$
are bounded and the space
$\mathcal A$ was defined in 0.3.
For every pair  $\gamma\in \mathcal S^*\uuu 1$ and
$a\in \mathcal A$  we set
\[ 
W(a,\gamma)=\int\uuu Y\, (e^ak\vvv a)\cdot d\gamma 
\quad\text{and}\quad W\uuu *(\gamma)=
 \min\uuu{a\in\mathcal A}\,W(a,\gamma)
\]




\medskip

\noindent
{\bf{0.9 Proposition.}} \emph{Let $\{a\uuu \nu\}$ be a sequence in
$\mathcal A$ such that}
\[
\lim W(a\uuu\nu,\gamma)= W\uuu*(\gamma)
\]
\emph{Then the sequence  $\{e^{a\uuu \nu}\cdot \gamma\}$
converges to a   measure
$\mu\in S^*\uuu 1$ such that $\mathcal T\uuu k(\gamma)=\mu$.}




\medskip

\noindent
Before we enter the proof we insert a preliminary result which will
be used later on.
\medskip

\noindent
{\bf{0.10. Lemma.}} 
\emph{Let $\epsilon>0$ and $a\in\mathcal A$ be such that
$W(a)\leq W\uuu *(\gamma)+\epsilon$. Then it follows that}

\[
\int\, e^a\cdot k\cdot \gamma\leq 
\frac{1+\epsilon}{1\vvv e^{\vvv 1}}
\]

\noindent
\emph{Proof.}
For every real number $s$   the function $a\vvv s$
again belongs to $\mathcal A$ and by the hypothesis 
$W(a\vvv s)\geq W(a)\vvv \epsilon$. This entails that

\[
\int\, e^a k\cdot d\gamma\leq
\int\uuu Y\, e^{a\vvv s}\cdot kd\gamma+s\int\, k\cdot d\gamma+\epsilon
\implies
\]
\[
\int (1\vvv e^{\vvv s})\cdot e^a\cdot kd\gamma\leq s+\epsilon
\]
Lemma 0.10 follows if we take $s=1$.






\bigskip


\noindent
\emph{Proof of Proposition 0.9} Keeping $\gamma$ fixed we set
$W(a)= W(a,\gamma)$.
Let $0<\epsilon<1$ and consider a pair $a,b$ in $\mathcal A$ such that
$W(a)$ and $W(b)$ both are $\leq W\uuu *(\gamma)+ \epsilon$.
Since  $\frac{1}{2}(a+b)$
belongs to $\mathcal A$  we get
\[
2\cdot W(\frac{1}{2}(a+b))\geq 2\cdot W\uuu *(\gamma)
\geq W(a)+W(b)\vvv 2\epsilon\tag{i}
\]
Notice that
\[
W(a)+W(b)\vvv
2\cdot W(\frac{1}{2}(a+b))=
\int\uuu Y\, [e^a+e^b\vvv 2\cdot e^{\frac{1}{2}(a+b))}]\cdot kd\gamma\tag{ii}
\]
Next,  we have  the algebraic identity
\[
e^a+e^b\vvv 2\cdot e^{\frac{1}{2}(a+b))}]=(e^{a/2}\vvv e^{b/2})^2
\]
It follows from (i\vvv ii) that
\[
\int\uuu Y\, (e^{a/2}\vvv e^{b/2})^2\cdot k\cdot d\gamma \leq 2\epsilon\tag{iii}
\]
Next, the identity
$|e^a\vvv e^b)|=
(e^{a/2}+e^{b/2})\cdot |e^{a/2}\vvv e^{b/2}|$
and the Cauchy\vvv Schwarz inequality give:

\[
\bigl[\int\uuu Y\, |e^a\vvv e^b|\cdot k\cdot d\gamma\,\bigr ]^2\leq
2\epsilon\cdot \int\uuu Y\, (e^{a/2}+e^{b/2})\cdot k\cdot d\gamma\tag{iv}
\]
By Lemma 0.6  the last factor is bounded by
a fixed constant and hence (iv) gives a constant $C$ such that
\[
\int\uuu Y\, |e^a\vvv e^b|\cdot k\cdot d\gamma
\leq C\cdot \sqrt{\epsilon}\tag{v}
\]
Next, let $k\uuu *$ be the minimum value taken by
$k$ on $Y$ which by assumption is positive since
$k^{\vvv 1}$ is bounded.
Replacing $C$ by $C/k\uuu *$ where 
we get
\[
\int\uuu Y\, |e^a\vvv e^b|\cdot d\gamma
\leq C\cdot \sqrt{\epsilon}\tag{vi}
\] 


\noindent
Now (v) applies to pairs in the sequence $\{a\uuu\nu\}$
and shows that
$\{e^a\cdot d\gamma\}$ is a Cauchy sequence with respect 
to the norm of measures on $Y$. So from Remark 0.6
there exists a non\vvv negative measure $\mu$ such that
\[
\lim\uuu{\nu\to \infty}\, ||e^{a\uuu\nu}\cdot\gamma\vvv \mu||=0\tag{vii}
\]

\medskip


\noindent
\emph {The equality $\mathcal T\uuu k(\mu)=\gamma$}.
Consider the 
$a$\vvv functions in the minimizing sequence.
If $\rho\in \mathcal A$ is arbitrary we have
\[ 
W(a\uuu\nu+\rho)\geq W(a\uuu\nu)\vvv \epsilon\uuu\nu
\] 
where $\epsilon\uuu\nu\to 0$.
This gives
\[
\int\uuu Y\, [ke^{a\uuu\nu}(1\vvv e^\rho)+\rho]\cdot d\gamma\leq \epsilon\uuu\nu\tag{1}
\]
When the maximum norm
$|\rho|\uuu Y\leq 1$ we can write
\[
e^\rho=1+\rho+\rho\uuu 1\quad\text{where}\quad
 0\leq \rho\uuu 1\leq \rho^2\tag{2}
\]
Then we see that (1) gives
\[
\int\uuu Y\,(\rho\vvv ke^{a\uuu\nu}\cdot \rho)\cdot d\gamma\leq
\epsilon\uuu\nu +\int\,\rho\uuu 1\cdot \gamma\leq
\epsilon+||\rho||\uuu Y^2\tag{3}
\]
where the last inequality follows since
$\gamma$ is a probability measure and the inequality in (2) above.
The same inequality holds with $\rho$ replaced by $\vvv \rho$
which entails that
\[
\bigl|\int\uuu Y\,(ke^{a\uuu\nu}\vvv 1)\cdot \rho\cdot d\gamma\bigr|
\leq\epsilon\uuu\nu+||\rho||\uuu Y^2
\]

\noindent
Notice that Lemma 0.10 entails that
the sequence of functions
$\{ke^{a\uuu\nu}\}$ are uniformly bounded.
Now we apply the inequality (*) from 0.7
while we use
$\rho$\vvv functions in $\mathcal A$ of norm $\leq\sqrt{\epsilon\uuu\nu}$.
It follows
that there exists a constant $C$ which is independent of $\nu$
such that
the  following inequality for the total variation:
\[
||\mathcal T\uuu k(e^{a\uuu\nu}\cdot\gamma)\vvv \gamma||\leq C\cdot n
\cdot \frac{1}{\sqrt{\epsilon}}\cdot
(\epsilon\uuu\nu+\epsilon\uuu\nu)= 2\cdot Cn\cdot \sqrt{\epsilon\uuu\nu}
\]
Passing to the limit it follows from (vii) that we have
the equality
\[ 
\mathcal T\uuu k(\mu)=\gamma
\]

\noindent
Since $\gamma\in S^*\uuu1$ was arbitrary
we have proved that
the $\mathcal T\uuu k$ yields a surjective map from
$S^*\uuu k$ to $S^*\uuu 1$
which finishes the proof of the
Main Theorem.







\bigskip


\centerline {\bf{  0.11 The  singular case.}}
\bigskip

\noindent
We restrict to the case $n=2$ where
$k(x\uuu 1,x\uuu 2)$ is a bounded and strictly positive 
continuous function on
$Y= X\uuu 1\times X\uuu 2$. Let $\gamma\in S^*\uuu 1$ satisfy:
\[
\int\uuu Y\, \log k\cdot d\gamma>\vvv \infty\tag{1}
\]
Under this integrability condition the following hold:

\medskip

\noindent
{\bf{2. Theorem.}}
\emph{There exists a unique non\vvv negative 
product measure
$\mu$ on $Y$ such that
$\mathcal T\uuu k(\mu)=\gamma$.}
\medskip

\noindent
{\bf{Remark.}}
In general the measure $\mu$ need not have finite mass
but the proof shows that
$k$ belongs to $L^1(\mu)$, i.e.
\[
\int\uuu Y\, k\cdot d\mu<\infty
\]


\noindent
As pointed out by Beurling  Theorem 0.12
can be applied to the case $X\uuu 1=X\uuu 2={\bf{R}}$
both are copies of the real line and
\[
k(x\uuu1,x\uuu 2)=g(x\uuu 1\vvv x\uuu 2)
\] where $g$ is the density of a Gaussian distribution which after  a
normalisation  of
the variance is taken to be
\[
\frac{1}{\sqrt{2\pi}}\cdot e^{\vvv t^2/2}
\]
So the integrability condition for $\mu$  becomes

\[
\iint\, (x\uuu 1\vvv x\uuu 2)^2\cdot d\mu(x\uuu 1,x\uuu 2)<\infty
\] 
\medskip

\noindent
A proof of Theorem 0.12  is given on page 218\vvv 220
in [loc.cit] and relies upon similar but technically more involved
methods as in the Main Theorem.
Concerning higher dimensional cases,  i.e.
singular versions of the Main Theorem when
$n\geq 3$, 
Beurling gives the
following comments at the end of [ibid]
where the citation below has changed numbering of
the theorems as compared to [ibid]:
\medskip

\noindent
\emph{The proof of the Main Theorem 
relies heavily on the condition that $k\geq a$ for some
$a>0$.
If this lower bound condition is dropped
the individual equation $\mathcal K(\gamma)=\mu$ may still
be meaningful, but serious complications will
arise concerning the global uniqueness if $n\geq 3$
and the proof of Theorem 0.12  for the case $n\geq 3$ cannot be duplicated.}



\newpage

\centerline{\bf{§ 3. Beurlings criterion for the Riemann hypothesis.}}



\bigskip


\noindent
Let $\rho(x)$ be  the 1\vvv periodic function on the positive real $x$\vvv line
where $\rho(x)=x$ if $0<x<1$.
So if $\{x\}$ is the integral part of $x$ then
\[
\rho(x)= x\vvv\{x\}\quad\colon \, x>0
\]
To each $0<\theta<1$ we get the function
\[ 
\rho\uuu\theta(x)= \rho(\theta/x)
\]
whose  restriction   to $(0,1)$
gives a non\vvv negative function 
with  jumps at points in the discrete set
$\{ x= \frac{\theta}{k}\colon \, k=1,2,\ldots\}$.
Denote by $\mathcal D$
the linear space 
of functions on $(0,1)$ of the form
\[
f(x)=\sum\, c\uuu\nu\cdot \rho_{\theta_\nu}(x)
\]

\noindent
where $0<\theta\uuu 1<\ldots<\theta\uuu N<1$ is a finite set
and $\{c\uuu\nu\}$ are complex numbers such that
\[
\sum\, c\uuu\nu\cdot \theta\uuu\nu=0
\]


\noindent
{\bf{1.1 Theorem.}} \emph{The Riemann hypothesis is valid if and only if
the identity function  belongs to the closure of
$\mathcal D$ in
$L^2(0,1)$.}
\medskip

\noindent
The proof  uses the following formula:

\medskip

\noindent
{\bf{1.2 Proposition.}}
\emph{ For each $0<\theta<1$ one has the equality}
\[
 \int\uuu 0^1\,\rho(\theta/x)x^{s\vvv 1}\cdot dx=
 \frac{\theta}{s\vvv 1}\vvv 
 \frac{\theta^s\cdot \zeta(s)}{s}
\quad\text{when}\quad \mathfrak{Re}s >1\tag{*}
\]
\medskip
 
\noindent
\emph{Proof.}
The variable substitutions $x\to \theta/u$ 
identifies the left hand side with
\[
\theta^s\cdot 
\int\uuu\theta^\infty\,\rho(u)\cdot u^{\vvv s\vvv 1}\cdot du\tag{i}
\]
To evaluate (i) we  consider the integral
\[
\int\uuu1^\infty\,\rho(u)\cdot u^{\vvv s\vvv 1}\,du=
\sum\uuu{n=1}^\infty\, \int\uuu 0^1\,\frac{u}{(u+n)^{s+1}}\cdot du\tag{ii}
\]
where the last equation used the periodicity of $\rho$.
Integration by parts gives for each $n\geq 1$:
\[
\int\uuu 0^1\,\frac{u}{(u+n)^{s+1}}\cdot du=
\vvv \frac{1}{s}(n+1)^{\vvv s}+\frac{1}{s}\int\uuu 0^1\, \frac{du}{(n+u)^s}
\]
A summation over $n$ implies that  (ii) is equal to:
\[
\vvv \frac{\zeta(s)}{s}+\frac{1}{s}+\frac{1}{s}\int\uuu 1^\infty\, u^{\vvv s}\cdot du
=\vvv \frac{\zeta(s)}{s}+\frac{1}{s}+\frac{1}{s(s\vvv 1)}=
\vvv \frac{\zeta(s)}{s}+\frac{1}{s\vvv 1}\tag{iii}
\]
\medskip

\noindent
Next we have
\[
\theta^s\cdot \int_\theta^1\, \rho(u)\cdot u^{-s-1}\, du=\frac{\theta}{s-1}-
\frac{\theta^s}{s-1}
\tag{iv}
\]
Together (i-iv) give (*).




\bigskip

\centerline{\emph{1.3 The sufficiency part}}
\medskip


\noindent
Suppose that the identity function belongs to the
$L^2$-closure  of $\mathcal D$.
So if  $\epsilon>0$ there exists 
$f\in\mathcal D$ expressed by (*) above
such that the $L^2$\vvv norm
of $1+f$ is $<\epsilon$. 
Since $\sum\, c\uuu \nu\cdot\theta\uuu\nu =0$
Proposition 1.2 gives:
\[
\int\uuu 0^1\,(1+f(x))\cdot x^{s\vvv 1}\cdot dx=\frac{1}{s}+
\sum c_\nu\int_0^1\ \rho(\theta_\nu/x)\,dx=
\frac{1}{s}-\sum\, c_\nu\cdot \theta\uuu\nu ^s\cdot \frac{\zeta(s)}{s}\tag{i}
\]

\medskip

\noindent
With $s=\sigma+it$ and  $\sigma>1/2$
we have $x^{s\vvv 1}$ in $L^2$ and the Cauchy\vvv Schwarz inequality gives:
\[
\bigl|\int\uuu 0^1\,(1+f(x))\cdot x^{s\vvv 1}\cdot dx\,\bigr|\leq
||f||\uuu 2\cdot \sqrt{\int\uuu 0^1\, x^{2\sigma\vvv 2}\cdot dx}=
||f||\uuu 2\cdot \frac{1}{\sqrt{2\sigma\vvv 1}}\tag{ii}
\]
Hence we obtain
\[
|\frac{1}{s}
\vvv \frac{\zeta(s)}{s}\cdot \sum\, c\uuu\nu\cdot \theta\uuu\nu ^s|\leq
 \frac{\epsilon}{\sqrt{2\sigma\vvv 1}}\quad\colon\quad
 \sigma>1/2
\]
If $\zeta(s\uuu *)=0$  for some $s\uuu *=\sigma\uuu *+it\uuu *$
with $\sigma\uuu *>1/2$, 
the left hand side is reduced to $\frac{1}{|s\uuu *|}$. 
Since
we can find $f$ as above for every $\epsilon>0$ it would follow that
\[
\frac{1}{|s\uuu *|}\leq \epsilon\cdot 
\frac{\epsilon}{\sqrt{2\sigma\uuu *\vvv 1}}\quad\text{for every}\quad 
\epsilon>0
\]
But this is  impossible so
if 1 belongs to the $L^2$\vvv closure of $\mathcal D$ then
the Riemann\vvv Hypothesis is true.
\bigskip

\noindent
\centerline{\emph{1.4  Proof of necessity.}}
\medskip






\noindent
We shall need
a closure theorem   while the proof
of necessity is postponed until § 2.
In general, let  $f(x)$ be a complex-valued function in $L^2(0,1)$ which is
not identically close to $x=0$, i.e.
\[
\int\uuu 0^\delta\, |f(x)|\cdot dx>0\quad\colon\, \forall\,\,\delta >0\tag{*}
\]
For each $0<a<1$ we set
\[ 
f\uuu a(x)=f(ax)
\] 
We restrict each  $f\uuu a$ to  $(0,1)$
and let  $\mathcal C\uuu f$ be 
the linear space of functions on $(0,1)$
generated by $\{f\uuu a\,\colon\, 0<a<1\}$.
Thus, a function in $\mathcal C\uuu f$
is expressed as a finite sum
\[
\sum\, c\uuu k\cdot f\uuu{a\uuu k}(x)
\]
where $\{c\uuu k\}$ are complex numbers and 
$0<a\uuu 1<\ldots<a\uuu n<1$ some finite 
tuple  in $(0,1)$.
For every    $1<p<2$ we can consider
$\mathcal C\uuu f$ as  a subspace of
$L^p(0,1)$ whose   closure taken in the $L^p$-norm
is denoted by 
$\mathcal C\uuu f(p)$.

\medskip


\noindent
\emph{The function $F(s)$}. With $f$ as above we set
\[
F(s)=\int\uuu 0^1\, f(x)\cdot x^{s\vvv 1}\cdot ds\tag{1.4.1}
\]
Then $F$ is analytic
in  the
half\vvv plane 
$\mathfrak{Re}(s)>1/2$ for if
$\sigma= \mathfrak{Re}(s)>1/2$
the Cauchy\vvv Schwarz inequality gives
\[ 
|F(\sigma+it)|\leq
\sqrt{\int\uuu 0^1\, |f(x)|^2\cdot dx}\cdot
\sqrt{\int\uuu 0^1\, |x|^{2\sigma\vvv 2}\cdot dx}=||f||\uuu 2\cdot
\sqrt{\frac{1}{2\sigma\vvv 1}}\tag{1.4.2}
\]
\medskip


\noindent
{\bf{1.4.3 Theorem.}} \emph{If there exists some
$1<p<2$ such that
$\mathcal C\uuu f(p)$ is a proper subspace of
$L^p[0,1]$, then
$F(s)$ extends to a meromorphic function in the whole complex
$s$\vvv plane whose poles are confined to the open half\vvv plane
$\mathfrak{Re}(s)<1/2$. Moreover, for every  pole
$\lambda$ the function
$x^{\vvv\lambda}$ belongs to   $\mathcal C\uuu f(p)$.}

\medskip

\noindent
\emph{Proof.}
Set $\frac{1}{q}= 1\vvv \frac{1}{p}$ and
recall that $L^q(0,1)$ is the dual of $L^p(0,1)$.
The assumption that
$\mathcal C\uuu f(p)\neq L^p(0,1)$ gives 
a non\vvv zero $k(x)\in L^q(0,1)$ such that
\[
\int\uuu 0^1\, k(x) f(ax)\cdot dx=0
\quad\colon\quad 0<a<1\tag{1}
\]
To the $k$\vvv function we associate
the transform
\[
 K(s)= \int\uuu 0^1\, k(x)\cdot x^{\vvv s}\cdot dx\tag{2}
\]

\noindent
Hölder's inequality implies that
$K(s)$ is analytic in the half\vvv plane $\mathfrak{Re} s<\frac{1}{p}$.
Define a function $g(\xi)$ for every real $\xi>1$ by
\[
 g(\xi)=\int\uuu 0^1\, k(x)\cdot f(\xi x)\cdot dx
\]
Hölder's inequality gives
\[ 
|g(\xi)|\leq 
\bigl[\int\, |k(x)|^q\cdot dx\bigr]^{\frac{1}{q}}\cdot
\bigl[\int\uuu 0^{1/\xi}\, |f(\xi x)|^p\cdot dx\bigr]^{\frac{1}{p}}
\]
If $\xi>1$  a variable
substitution shows that the last factor
is equal to
$||f||\uuu p\cdot |\xi|^{\vvv 1/p}$. Hence
\[
|g(\xi)\leq ||k||\uuu q\cdot ||f||\uuu p\cdot \xi^{\vvv 1/p}\quad\colon\quad \xi>1\tag{3}
\]
Next, put
\[
G(s)= \int\uuu  1^\infty\, g(\xi)\cdot \xi^{s\vvv 1}\cdot d\xi\tag{4}
\]


\noindent
From (3) it follows that
$G(s)$ is analytic in the half\vvv space
$\mathfrak{Re}\, s<1/p$.
Consider  the strip domain:
\[
\square=1/2<\mathfrak{Re}\, s< 1/p
\]

\noindent
Variable substitutions of  double integrals show that the following holds
in $\square$:
\[
 G(s)= F(s)\cdot K(s)\tag{5}
\]
where $F(s)$ is defined as in (1.1.1).
\medskip

\noindent
\emph{Conclusion.}
Since $G(s)$ and $K(s)$ 
are meromorphic in $\mathfrak{Re}\, s<1/p$
and $F(s)$ from the start is holomorphic in
$\mathfrak{Re}\, s>1/2$, it follows that 
$F$ extends to a meromorphic function in the whole $s$\vvv plane.
The
inequality (1.1.2)  
shows that
no poles appear during the meromorphic continuation across 
$\mathfrak{Re}\, s=1/2$. Hence
$F$ either is an entire function or else  it has a
non\vvv empty set of
poles where each pole
$\lambda$ has  real part  $<1/2$.

\medskip




\noindent
\emph{Existence of at least one pole.}
We shall prove that
$F$ has at least one pole. To achieve this 
we argue by  contradiction and  suppose that
$F$  is  an entire function.
Fix some 
real number 
$1/2<\alpha<1/p$.
The construction of $F$ shows  that its
restriction to the half\vvv space
$\mathfrak{Re}\, s\geq \alpha$ is bounded.
Next,
in the half\vvv space 
$\mathfrak{Re}\,s\leq\alpha$
we have
\[
F=\frac{G}{K}
\]
where  $G$ and $K$ both are bounded analytic functions.
Moreover their constructions imply that
\[ 
\lim\uuu{\sigma\to \vvv \infty}\, G(\sigma+it)=0\quad
\lim\uuu{\sigma\to_\infty}\, K(\sigma+it)=0
\] 
A wellknown   result due to  F. and R. Nevanlinna 
gives some constant 
$M>0$ and  a real number  $c$ such that
\[
F(\sigma+it)|\leq M\cdot e^{c(\sigma\vvv \alpha})
\quad\text{holds when}\quad \sigma\leq \alpha\tag{6} 
\]


\noindent
If $c\geq 0$  
the entire function $F$ is bounded and hence reduced to a constant.
But then it is easily seen from (1.1.1) that $f$ is identically zero.
Next, if
$c<0$ we
put  $a=e^c$ 
so that $0<a<1$
and define the function:
\[ 
F\uuu 1(s)= \int_ 0^1\, f(ax)x^{s\vvv 1}\cdot ds=
a^s\bigl( F(s)\vvv
\int\uuu a^1\, f(x)x^{s\vvv 1}\cdot ds\bigr)\tag{7}
\]
From this expression
and the hypotheis that $F$ is entire it is easily seen that
$F\uuu 1(s)$ is a bounded entire function and hence constant
which entails that 
the function
$x\mapsto f(ax)$ is identically zero
on $(0,1)$.  This means  that
$f$ vanishes on the interval $[0,a)$ which was excluded 
from  by  (*) above.
Hence 
$F$ cannot be an entire function.

\medskip

\noindent
\emph{The case at pole.}
Suppose that $F$ as a pole at some
$\lambda$ with  real part  $<1/2$.
Since $G$ is analytic in $\mathfrak{Re}(s)<1/2$
the equality (5)
implies that $\lambda$ is  a zero of $K$ and
observe   that the
pole of $F$ at $\lambda$ is \emph{independent}
of the chosen 
$L^q$-function $k$
which is $\perp$ to $\mathcal C\uuu f(p)$. Hence the following 
implication holds:
\[
k\perp \mathcal C\uuu f(p)\implies 
K(\lambda)= \int\uuu 0^1\, k(x) x^{\vvv \lambda}\cdot dx=0
\]
The Hahn\vvv Banach theorem  entails
that
the $L^p$\vvv function $x^{\vvv\lambda}$ belongs to
$\mathcal C\uuu f(p)$ which proves  the last claim in
Theorem 1.2.


\bigskip

\centerline{\bf{§ 2. The necessity in Theorem 1.1.}}

\medskip

\noindent
We shall use
a family of linear operators $\{T\uuu a\}$
defined as follows:
If $0<a<1$ and $g(x)$ is a function on $(0,1)$
we set
\[ 
T\uuu a(g)(x)= g(x/a)\quad\colon\quad 0<x<a
\]
while $T\uuu a(g)=0$ when $x\geq a$.

\medskip


\noindent
Assume that the identity function  
$1$ is outside the $L^2$\vvv closure of $\mathcal D$.
Hence 
its orthogonal complement in the Hilbert space $L^2(0,1)$
is $\neq 0$ and we find
a non\vvv zero
$g\in L^2(0,1)$ such that
\[
\int\uuu 0^1\, f(x)\cdot g(x)\cdot dx=0
\quad\colon\quad f\in\mathcal D\tag{2.1}
\]
Since $\mathcal D$ is invariant under the $T$\vvv operators it follows that
if $0<a<1$ then we also have
\[
0=\int\uuu 0^a\, f(x/a)\cdot g(x)\cdot dx=
a\cdot \int\uuu 0^1\, f(x)\cdot g(ax)\cdot dx\tag{2.2}
\]


\noindent
Now  we show that the $g$\vvv function satisfies
the condition (*) above  Theorem 1.1.
For suppose that $g=0$ on some interval $(0,a)$ with $a>0$.
Choose  $b$ where
\[
a<b<\min (1,2a)
\]
Now $\mathcal D$ contains the function
$f(x)= b\rho(x/a)\vvv a\rho(x/b)$.
The reader may verify that $f(x)=0$ for $x>b$ 
and is equal to  $a$ on the interval $(a,b)$.
Hence  (2.1) applied to $f$ gives
\[
\int\uuu a^b\, g(x)\cdot dx=0
\]
This 
means that the primitive function
\[
 G(x)=\int\uuu 0^x\, g(u)\cdot du
 \]
has a vanishing derivative on the interval $(a,b)$. The derivative is also zero  on
$(0,a)$ where $g=0$.
We conclude that $G=0$ on the interval $(0,b)$ so the
$L^2$\vvv function $g$ is almost everywhere a constant on this interval
which in addition 
is zero since $g=0$ on $(0,a)$. Hence 
$g=0$ on the  interval $(0,b)$.
Repating this with $a$ replaced by $b$ it follows that 
$g$ also is zero on the interval
\[ 
0<x<\min(1,2b) =\min(1,4a)
\]
After a finite number of steps $2^m a\geq 1$ and 
hence $g$ would be identically zero on $(0,1)$ which is not the case.
\medskip

\noindent
Now   Theorem 1.4.3 applies to  $g$
and gives
some $\lambda\uuu *$ with $\mathfrak{Re}\, \lambda\uuu *<1/2$
such that one has the inclusion below for every $p<2$:
\[
x^{\vvv \lambda\uuu *}\in \mathcal C\uuu g(p)\tag{2.3}
\]
Next, for each $\theta>0$ we there exists 
the $\mathcal D$\vvv function
\[
x\mapsto \rho(1/x)\vvv \frac{1}{\theta}\cdot \rho(\theta/x)
\]
Since (2.1) holds for all $0<a<1$ it follows that
\[
\int\uuu 0^1\, [\rho(1/x)\vvv \frac{1}{\theta}
\cdot \rho(\theta/x)]\cdot x^{\vvv\lambda\uuu *}
\cdot dx=0\tag{2.4}
\]
Put
$s\uuu *=1\vvv\lambda\uuu *$.
The formula in Proposition 1.2 
shows  that the vanishing in
(2.4)  gives
\[
\frac{\theta^{s\uuu *}\vvv 1}{s\uuu *}\cdot \zeta(s\uuu *)=0
\]
This hold for every $0<\theta<1$ and    choosing $\theta$
so that
$\theta^{s\uuu *}\vvv 1\neq 0$ it follows that
$\zeta(s\uuu *)=0$. Here
$\mathfrak {Re}(s\uuu *)=1
\vvv \mathfrak {Re}(\lambda \uuu *)>1/2$
and hence the Riemann hypothesis is violated which proves the necessity in
Theorem 1.1.



\newpage

 










\centerline{\bf{§ 4. The Laplace operator and  the Helmholtz equation}}



\bigskip


\noindent
{\bf{Introduction.}}
Let $D$ be a domain in the $(x,y)$-plane where one has 
a stationary irrational flow of an ideal fluid
described a stream function $v(z)$ which  is harmonic in
$D$. The
gradient vector $\nabla(v)$
is the velocity vector of the flow and  assumed to be everywhere $\neq 0$.
In general $v$ is only defined in a subdomain $D_*$ of $D$.
and the part of $\partial D_*$. On each component of the full boundary
$\partial D_*$ we  assume  that $v$ is constant on every
connected component which means that these curves are streamlines of the flow.
In 1867  Helmoltz posed the problem
to find a pair
$(v,D_*)$ such that the length $|\nabla(v)|$ is constant on
$\partial D_*\cap D$.
More generally one can impose the condition that
the function
\[
 p\mapsto |\nabla(v)(p)|
\] 
agrees with a given positive and continuous function
$\Phi$ on $\partial D_*\cap D$.
This leads to a free boundary value problem 
which goes as follows: 

\medskip


\noindent
Let $D^*$
be the exterior disc $\{|z|>1\}$ in ${\bf{C}}$ and $\Phi(z)$ is a
given continuous and positive function in $D^*$.
Denote by $\mathcal J^*$ the family of closed
Jordan curves
$\gamma$ in $D^*$ which together with
$\{|z|=1\}$ borders an annulus.
For every such
$\gamma$ there exists the unique harmonic function
$v$  in the annulus bordered by
$\{|z|=1\}$ and $\gamma$, where
$v=1$ on  $\{|z|=1\}$ and   $v=0$ on $\gamma$.
One seek $\gamma$ so that
\[
 |\nabla(v)(p)|=\Phi(p)
 \quad\colon p\in
\gamma\tag{*}
\]

\medskip


\noindent
This problem is studied
in a series of articles by Beurling. Here we  expose
results  from
\emph{On free-boundary problems for the Laplace operator} 
[Princeton: Seminars analytic functions 1957].
To solve (*)
Beurling proceeds as follows.
Let us say that $\gamma$ is of type $\mathcal B(Q)$ if
\[ 
\limsup_{z\to p}\,  |\nabla(v)(z)|\leq \Phi(p) \quad\colon p\in
\gamma\tag{1}
\]
We consider also the class $\mathcal A(Q)$ where 
\[
\liminf_{z\to p}\,  |\nabla(v)(z)|\geq \Phi(p) \quad\colon p\in
\gamma\tag{2}
\]
If a curve
$ \gamma$ belongs to the intersection
$A(Q)\cap B(Q)$ then (*) holds.
There remains to  find conditions on $Q$ in order that
this intersection is non-empty and  the uniqueness amounts to show
that  this intersection
is reduced to a single curve in $\mathcal J^*$.
Following [ibid] we shall establish some sufficiency results for
existence as well as  uniqueness.
First  we impose a growth condition on $Q$ when
one approaches the unit circle:
\[
\lim_{|z|\to 1} \, \bigl[\log\frac{1}{|z|}\,\bigr]^{-1}\cdot
Q(z)=0\tag{3}
\]


\noindent
{\bf{Remark.}}
As explained in § XX
this condition is 
invariant under conformal mappings between our chosen annulus and
others.
From now on (3) is assumed. A first major result in [ibid]
is:

\medskip

\noindent
{\bf{Theorem.}}
\emph{If $\mathcal B(Q)\neq\emptyset$
then the  free boundary value problem has at least one solution}.
\medskip

\noindent
Next, we seek
conditions in order that
$B(Q)\neq\emptyset$. To each $a<1$ we
denote by $B_a(Q)$ the family of curves
$\gamma$ such that
\[ 
\limsup_{z\to p}\,  |\nabla(v)(z)|\leq a\cdot \Phi(p) \quad\colon p\in
\gamma\tag{i}
\]
Set
\[
\mathcal B_*(Q)=\bigcup_{a<1}\, B_a(Q)
\]



\noindent
{\bf{Theorem.}}
\emph{Suppose 
there exists a pair of curves
$\gamma\in \mathcal A(Q)$ and $\gamma_0\in \mathcal B(Q)$
such that $\gamma$ stays in the annulus bordered by
$\{|z|=1\}$ and $\gamma_0$. Then (*) has a solution
$\gamma_*$ where $\gamma_*$ is between 
$\gamma$ and $\gamma_0$.}



\bigskip



\centerline {\emph{Uniqueness.}}
\bigskip


\noindent
For each rectifiable and closed Jordan curve
$\gamma$ in the exterior disc with winding number one
we set
\[
\ell_\gamma(Q)= \int_\gamma\, Q\cdot |ds_\gamma|
\] 
where $ds_\gamma$ is the arc-length measure.
Set
\[ 
\ell_*(Q)=\inf_{\gamma}\, \ell_\gamma(Q)\tag{1}
\]


\medskip

\noindent
{\bf{Definition.}}
\emph{The circle
$\{|z|=1\}$ is said to be   convex
with respect to $Q$ if
the infimum in (1) can be achieved by a sequence of Jordan curves
$\gamma$ which tend to the circle.}

\medskip

\noindent 
Thus, convexity means that
for each
$\delta>0$ when we take the infimum over $\gamma$ curves which stay in the 
narrow annulus $1<|z|<1+\delta$ for arbitrary small  $\delta>0$, then
this infimum is $\geq \ell_*(Q)$.
\medskip

\noindent
{\bf{Theorem.}} 
\emph{
If $\{|z|= 1\}$ is $Q$-convex and
$\log\, Q$ is subharmonic  there cannot exist 
more than one solution to
(*).}
\medskip


\centerline {\emph{About the proofs.}}
\medskip

\noindent
They rely upon similar methods as in
Beurling's conformal mapping theorem to be presented in § III.B.
See also chapter VI: vol 2  [Collected work]
for further studies related to the free boundary value problem.








\newpage








\centerline{\bf{ 5.  Beurling's conformal mapping theorem.}}
\bigskip


\noindent
{\bf Introduction.} 
Let $D$ be the open unit disc
$|z|<1$.
Denote by $\mathcal C$
the family 
of conformal maps $w=f(z)$ which map $D$ onto some
simply connected domain $\Omega_f$ which contains
the origin and satisfy:
\[ 
f(0)=0\, \quad\text{and}\quad f'(0)\,\,\text{is real and positive}\,.
\]


\noindent
Riemann's mapping theorem asserts that for every
simply connected subset $\Omega$ of ${\bf{C}}$ which is not equal to
${\bf{C}}$ there exists a unique $f\in\mathcal C$ such that
$\Omega_f=\Omega$.
We are going to construct a subfamily  of
$\mathcal C$.
Consider 
a positive and bounded continuous 
function a function $\Phi$ defined in the whole complex
$w$-plane.
\medskip

\noindent
{\bf 0.1 Definition.}
\emph{The set of all
$f\in \mathcal C$ such that}
\[ 
\lim_{r\to 1}\,\, 
\max_{0\leq\theta\leq 2\pi}\,\bigl[\bigl|f '(re^{i\theta})|-\Phi(f(re^{i\theta}))
\bigr]=0\tag{*}
\]
\emph{is denoted by $\mathcal C_\Phi$.}
\medskip

\noindent
{\bf Remark.}
Thus, when $f\in\mathcal C_\Phi$
then the difference of the absolute value
$|f'(z)|$ and $\Phi(f(z))$ tends uniformly to zero
as $|z|\to 1$.
Let $M$ be the upper bound of $\Phi$.
The maximum principle applied to the complex derivative
$f'(z)$ gives
\[
|f'(z)|\leq M\quad\colon\quad z\in D
\]
Hence $f(z)$ is a  continuous function in
the open disc $D$ whose Lipschitz norm is uniformly
bounded by $M$. This implies
that  $f$ extends to a continuous function in the closed disc, i.e.
$f$ belongs to the disc algebra
$A(D)$.
\bigskip


\noindent
{\bf 1. Theorem.}
\emph{Assume that
$\text{Log}\,\frac{1}{\Phi(w)}$ is subharmonic. Then
$\mathcal C_\Phi$ contains a unique function
$f^*$.}

\bigskip

\noindent
{\bf Remark.}
When
$\Phi(w)=\Phi(|w|)$
is a radial function and 
$\Phi(\rho)=\rho$ holds for some $\rho>0$
then 
the function $f(z)=\rho\cdot z$ belongs to
$\mathcal C_\Phi$. So for a radial $\Phi$-function
where different $\rho$-numbers exist  uniqueness fails for 
the family $\mathcal C_\Phi$.
The reader may verify that
a radial function $\Phi$ for which $\Phi(\rho)=\rho$ has more than one
solutions cannot satisfy the condition in
Theorem 1.
Next, let us give examples of $\Phi$-functions which satisfy the condition in
Theorem 1. Consider 
an arbitrary real-valued and non-negative $L^1$-function
$\rho(t,s)$ which has compact support.
Set
\[ 
\Phi(w)=\text{exp}\,\bigl[\int\,\text{log}\,\frac{1}{|w-t-is[}\cdot \rho(t,s)\cdot dtds\,\bigr]
\]
Here  
$\text{log}\,\frac{1}{\Phi}$ is subharmonic and 
Theorem 1 gives 
a unique simply connected domain
$\Omega$ such that the  normalised
conformal mapping function $f\colon\, D\to\Omega$
satisfies

\[
|f'(e^{i\theta})|=\Phi(f(e^{i\theta}))\quad\colon
\quad 0\leq \theta\leq 2\pi\,.
\]
\medskip

\noindent
The proof of Theorem 1 requires several steps
where  notble point is that we also estblish some
existence results  under the sole assumption
that $\Phi$ is continuous and positive.

\medskip




\noindent
{\bf 1.1 The family $\mathcal A_\Phi$}.
Let $\Phi$be continuous and positive.
Denote by $\mathcal A_\Phi$  the subfamily of all 
$f(z)\in \mathcal C$ such that
\[
\limsup_{|z|\to 1}\,\, |f'(z)|-\Phi(f(z))\leq 0\tag{1}
\]
\medskip
\noindent
{\bf{Remark.}} By the definition of  limes superior this means that 
for every $\epsilon>0$ there exists $\delta>0$ such that
\[
|f'(z)|\leq \Phi(f(z))+\epsilon\quad\colon\text{for all}\,\, 1-\delta<|z|<1\,.
\]
\medskip


\noindent
{\bf The maximal region
$\Omega^*(\Phi)$}. 
With $\Phi$ given we get  a bounded
open subset
in the complex plane as follows:
\[ 
\Omega^*(\Phi)=\cup\, f(D)\quad\colon\quad 
\text{union taken over all}\,\, f\in\mathcal A_\Phi\tag{1.2}
\]
\medskip

\noindent
{\bf 1.3  Theorem.}
\emph{The maximal region $\Omega^*(\Phi)$ is simply connected. Moreover, 
the
unique normalised
conformal mapping 
for which $f^*(D)=\Omega^*(\Phi)$ 
belongs to
$\mathcal C_\Phi$.}
\bigskip


\noindent
{\bf 1.4 The family $\mathcal B_\Phi$}.  It consists of all
$f\in\mathcal C$
such that
\medskip
\[
\liminf_{|z|\to 1}\,\, |f'(z)|-\Phi(f(z))\geq 0
\]
To this family we assign minimal region
\[ 
\Omega_*(\Phi)=\cap\, f(D)\quad\text{The intersection taken over all}
\,\, f\in \mathcal B_\Phi\tag{1.5}
\]
\medskip

\noindent
{\bf 1.6 Theorem.}
\emph{The set $\Omega_*(\Phi)$ is simply connected and the
unique $f_*\in\mathcal C$ for which
$f_*(D)=\Omega_*(\Phi)$ belongs to $\mathcal C_\Phi$.}
\medskip

\noindent
{\bf{Remark.}}
The constructions of the maximal and the minimal region give
\[ 
\Omega_*(\Phi)\subset\Omega^*(\Phi)\tag{1}
\]


\noindent
This inclusion  is in general strict as seen  by the example when
$\Phi$ is radial.
But when
$\text{Log}\,\frac{1}{|\Phi|}$ is subharmonic the uniqueness in
Theorem 1 asserts that one has 
the equality
$\Omega_*(\Phi)=\Omega^*(\Phi)$.
\medskip

\noindent
Before we enter the proofs of Theorem 1.4 and 1.6
we show  the
uniqueness part in
Theorem 1.
\bigskip

\centerline{\bf A. Proof of Theorem 1.}
\medskip

\noindent
Let $\Phi$ be as in Theorem 1. Admitting
Theorem 1.4 and 1.6  we get the two simply connected
domains
$\Omega^*(\Phi)$
and
$\Omega_*(\Phi)$. Keeping $\Phi$ fixed we set
$\Omega^*=\Omega^*(\Phi)$ and
$\Omega_*=\Omega_*(\Phi)$.
Let $f\colon D\to \Omega_*$ and
$g\colon D\to \Omega^*$ be the
corresponding conformal mappings.
Since $\Omega_*\subset \Omega^*$
Riemann's mapping theorem gives an inequality for
the first order derivative at $z=0$:
\[
f'(0)\leq g'(0)\tag{i}
\]
Set
\[ 
\Phi(w)= e^{U(w)}
\]
where $U(w)$ by assumption is super-harmonic.
Solving  the Dirichlet problem
with respect to the domain $\Omega^*$ we get 
the harmonic function $U^*$ in $\Omega^*$
where
\[ 
U^*(w)=U(w)\quad\, w\in\partial\Omega^*\,.
\]
Similarly we find the harmonic function $U_*$ in $\Omega_*$ such that
\[
U_*(w)=U(w)\quad\, w\in\partial\Omega_*\,.\tag{*}
\]
Next, since $g\in \mathcal C_\Phi$
we have
the equality
\[ 
\text{log}\, |g'(z)|=U(g(z))\quad |z|=1\tag{ii}
\]
Now 
$\text{log}\, |g'(z)|$ and $U^*(g(z))$ are harmonic in
$D$ and since $g$ is normalised so that $g'(0)$ is real and positive
it follows from (ii) that:
\[
\text{log}\, g'(0)= U^*(0)
\]
In a similar way we find that
\[ 
\text{log}\,f'(0)= U_*(0)
\]
\medskip


\noindent
Next, $U$ is super-harmonic in $\Omega^*$  since 
and $\partial\Omega_*$ is a closed subset of
$\bar\Omega^*$ one has:
\medskip
\[
U(w)\geq U^*(w)\quad w\in\partial\Omega_*
\]
Then (*) entails 
that $U_*\geq U^*$ holds in $\Omega_*$. In particular
\[
\text{log}\,f'(0)= U_*(0)\geq U^*(0)=\text{log}\,g'(0)
\]
Together with (i) we conclude that
$f'(0)= g'(0)$and by the uniqueness in
Riemann's mapping theorem it follos that 
$\Omega_*=\Omega^*$ which gives the uniqueness part in
Theorem 1.





\bigskip

\centerline{\bf B. Proof of Theorem 2.}



\medskip

\noindent
The first step in the proof is to construct a certain "union  map"
defined by a finite family $f_1,\ldots,f_n$
of functions  $\mathcal A_\Phi$.
Set 
\[ 
S_\nu=f_\nu(D)\quad\,\text{and}\,\,  S_*=\cup\, S_\nu\tag{*}
\]
\medskip

\noindent
So above $S_*$ is a union of Jordan domains
which in general can intersect each other in a rather arbitrary fashion.
\medskip

\noindent
{\bf B.1 Definition.}
\emph{The extended union denoted by $EU(S_*)$
is defined as follows:
A point $w$ belongs to the extended union
if there exists some closed Jordan curve
$\gamma\subset S_*$ and the Jordan domain bordered by
$\gamma$ contains
$w$}.
\medskip

\noindent
{\bf{Exercise.}} Verify that
the extended union is simply connected.
\medskip

\noindent
{\bf  B.2 Lemma }
\emph{Let $f_*$ be the unique normalised conformal map from
$D$ onto the extended union above. Then
$f_*\in\mathcal A_\Phi$.}
\bigskip

\noindent






\noindent
\emph{Proof.} 
First we  reduce the proof to the
case
when all the functions
$f_1,\ldots,f_n$  extend to be analytic in a neighborhood of
the closed disc
$\bar D$. 
In fact, with $r<1$ we set
$f_\nu^r(z)=f_\nu(rz)$
and get the image domains $S_\nu[r]= f_\nu^r(D)= f_\nu(D_r)$.
Put $S_*[r)=\cup\, S_\nu[r]$ and construct its
extended union which we denote by $S_{**}[r]$.
Next, let $\epsilon>0$
and consider the new function $\Psi(w)=\Phi(w)+\epsilon$.
Let $f_*[r]$ be the conformal map from $D$ onto $S_{**}[r]$.
If Lemma B.2 has been proved for the
$n$-tuple $\{f_\nu^r\}$
it follows by continuity that $f_*[r]$ belongs 
$\mathcal A_\Psi$ if $r$ is sufficently close to one.
Passing to the limit we see that
$f_*=\lim_{r\to 1}\, f_*[r]$
and we get $f_*\in\mathcal A_\Psi$. Since
$\epsilon>0$ is arbitrary we get
$f_*\in\mathcal A_\Phi$ as required.
\medskip

\noindent
After this preliminary reduction we consider the
case when each
$f$-function extends  analytically to a neighborhood of
the closed disc $|z|\leq 1$.
Then each $S_\nu$ is a closed real analytic Jordan curve
and
the boundary of $S_*$ is a finite union of
real analytic arcs and some corner points.
In particular we find the outer boundary which is a piecewise analytic and closed Jordan
curve
$\Gamma$
and  the extended union is the Jordan domain bordered by
$\Gamma$.
It is also clear that 
$\Gamma$ is the union of some connected
arcs $\gamma_1,\ldots,\gamma_N$ and a finite set of corner points
and for each $1\leq k\leq N$ there exists
$1\leq \nu(k)\leq n$
such that
\[ 
\gamma_k\subset \partial S_{\nu(k)}
\]



\noindent
Denote by  $\{F_\nu=f_\nu^{-1}\}$ and $F=f_*^{-1}$
the inverse functions and put:
\[ 
G=\text{Log}\, \frac{1}{|F|}\quad\colon
 G_\nu=\text{Log}\, \frac{1}{|F_\nu|}\quad\colon 1\leq\nu\leq n\,.
\]
\medskip

\noindent
With $1\leq\nu\leq n$ kept fixed we notice that
$G_\nu$ and $G$ are super-harmonic functions in
$S_\nu$ and the difference
\[ 
H=G-G_\nu
\] 
is superharmonic in $S_\nu$.
Next, consider a point  $p\in \partial S_\nu$. Then
$|F_\nu(p)|=1$
and hence
$G_\nu(p)=0$. At the same time
$p$ belongs to
$\partial S_*$ or the interior of $S_*$ so
$|F(p)|\leq 1$ and hence $G(p)\geq 0$.
This shows that
$H\geq 0$ on $\partial S_\nu$ and by the minimum principle for harmonic
functions we obtain:
\[
H(q)\geq 0\quad\text{for all}\,\, q\in S_\nu\tag{i}
\]
\medskip

\noindent
Let us then consider some boundary arc
$\gamma_k$  
where $\gamma\subset\partial S_\nu$, i.e.   here $\nu=\nu(k)$.
Now $H=0$ on $\gamma_k$ and since (i) holds it follows that
the \emph{outer normal derivative}:
\[
\frac{\partial H}{\partial n}(p)\leq 0\quad p\in\gamma_k\tag{ii}
\]


\noindent 
Since 
$|F|=|F_\nu|=1$ holds on
$\gamma_k$ and the gradient of $H$ is parallell to the normal
we also get:
\[ 
\frac{\partial G}{\partial n}(p)=
-|F'(w)|\quad\text{and}\quad\,\,
\frac{\partial G_\nu}{\partial n}(p)=
-|F_\nu'(w)|
\quad\colon w\in\gamma_k
\]
Hence (ii) above gives
\[
|F'(w)|\geq |F_\nu'(w)|\quad\text{when}\quad  w\in\gamma_k\tag{iii}
\]
Next, since $f_\nu\in \mathcal A_\Phi$
we have
\[
|f_\nu'(F_\nu(w))|\leq \Phi(w)\tag{iv}
\]
and since $F_\nu$ is the inverse of $f_\nu$
we get

\[ 1=f_\nu'(F_\nu(w))\cdot F'_\nu(w)
\]
Hence (iv) entails
\[ |F'_\nu(w)|\geq
\frac{1}{ \Phi(w)}\tag{v}
\]
We conclude from
(iii) that

\[ |F'(w)|\geq
\frac{1}{ \Phi(w)}\quad \colon\,\, w\in\gamma_k\tag{vi}
\]
This holds for all the sub-arcs
$\gamma_1,\dots,\gamma_n$ and hence
we have proved the inequality
\[
|F'(w)|\geq
\frac{1}{ \Phi(w)}\quad\text{ for all}\quad  w\in\Gamma\tag{*}
\]
except  at a
finite number of  corner points.
To settle the situation at corner points we notice that
Poisson's formula applied to the harmonic function
$
\text{log}\, |f_*'(z)|$ in the unit disc gives
\[
\text{log}\, |f_*'(z)|=
\frac{1}{2\pi}\cdot \int_0^{2\pi}\,
\frac{1-|z|^2}{|e^{i\theta}-z|^2}\cdot
\text{log}\, |f'(e^{i\theta})|
\cdot d\theta\,.\tag{vii}
\]
\medskip

\noindent
Next, since $F$ is the inverse of $f_*$ we have
\[
|f_*'(z)|\cdot |F'(f(z))|=1\quad\text{for all}\,\,|z|=1\,.
\]
Hence (vi) gives
\[ 
|f'(z)|\leq \Phi(f_*(z))\quad\text{for all}\,\,|z|=1\,.
\]
With $\Phi= e^U$
we therefore get
\[
\text{log}\, |f'_*(z)|\leq U(f(z))
\quad\text{for all}\,\,|z|=1\,.
\]

\noindent
From the Poisson integral (vii) it follows that
\[
\text{log}\, |f_*'(z)|\leq 
\frac{1}{2\pi}\cdot \int_0^{2\pi}\,
\frac{1-|z|^2}{|e^{i\theta}-z|^2}\cdot
\, U(f_*(e^{i\theta}))
\cdot d\theta\,.\quad\, z\in D
\]


\medskip

\noindent
{\bf{A passage to the limit.}}
I addition to the obvious equi-continuity the passage to the limit
requires some care which is exposed in
[Beurling: Lemma 1, page 122].
Passing to the limit as $|z|\to 1$
the continuity of $\Phi$ implies that
$f_*$ belongs to $\mathcal A_\Phi$ which proves Lemma B.2.

\newpage

\centerline{\bf B.3 The construction of $\Omega^*$}




\bigskip

\noindent
By the uniform bound for Lipschitz norms
the family $\mathcal A_\phi$
is equi-continuous. We can therefore find a denumerable dense subset
$\{h_\nu\}$. It means that to every
$f\in\mathcal A_\Phi$ and every $\epsilon>0$ there exists
some $h_\nu$ such that
the maximum norm
$|f-h_\nu|_D<\epsilon$. From this it is clear that
\[ 
\Omega^*=\cup\,\, h_\nu(D)\tag{i}
\]
Next, to every $n\geq 2$ we 
have the $n$-tuple $h_1,\ldots,h_n$
Lemma B. 2 gives  the function
$f_n$ where $f_n(D)$ is the extended union of
$\{h_\nu(D)\}$. In particular 
\[ 
h_\nu(D)\subset f_n(D)\quad\colon\,1\leq\nu\leq n
\]
The image domains $\{f_n(D)\}$ increase with $n$.
and (i)  gives
\[ 
\Omega^*=\cup\, f_n(D)\tag{ii}
\]


\noindent
Next, $\{f_n\}$ is a normal family of analytic functions
and since their image domains increase 
there exists the limit function
$f^*$ and it belongs to $\mathcal  C$  by the general results from Chapter VI.
Morover, (ii) entails that
\[
f^*(D)=\Omega^*
\]
There remains to prove 
that
\[ 
f^*\in \mathcal C_\Phi\tag{*}
\]
\medskip
To    establish  (*) we shall need
a  relation between
$\Phi$ and the maximal domain
$\Omega^*(\Phi)$.
\medskip

\noindent
{\bf B.4 Proposition.}
\emph{Let $\Psi$ be a positive continuous function which is equal to
$\Phi$ outside $\Omega^*(\Phi)$ while 
its restriction to
$\Omega^*(\Phi)$ is arbitrary. Then
one has the equality}
\[
\Omega^*(\Phi)=
\Omega^*(\Psi)
\]


\noindent
\emph{Proof.}
The assumption gives
\[
 \Psi(w)=\Phi(w)\quad\text{for all}\,\, w\in\partial\Omega^*(\Phi)\tag{i}
 \]

\medskip

\noindent
It follows that
 $f^*\in\mathcal A_\Psi$. Hence the
 equality $f^*(D)=\Omega^*(\Phi)$ and 
the construction of the maximal domain
 $\Omega^*(\Psi)$ give the inclusion
 \[
 \Omega^*(\Phi)\subset\Omega^*(\Psi)\tag{ii}
\]

\medskip

\noindent
Next, let  $h^*\colon D\to \Omega^*(\Psi)$ 
be the conformal mapping function associated to $\Psi$.
The equality (i) and the construction of the
maximal region $\Omega^*(\Phi)$ gives $h^*\in\mathcal A_\phi$
and then
\[
\Omega^*(\Psi)=h^*(D)\subset
 \Omega^*(\Phi)\tag{iii}
 \]
Hence (ii-iii)  give the requested equality in Proposition B.4.
\bigskip


\centerline {\bf B.5 A special choice of $\Psi$}.
\medskip

\noindent
Keeping $\Phi$ fixed we put
$\Omega^*(\Phi)=\Omega^*$ to simplify
the notations. We have the $U$-function such that
\[ 
\Phi(w)= e^{U(w)}\tag{B.5.i}
\]
Here
$U(w)$ is a continuous function on
$\partial\Omega^*$
and solving the Dirichlet problem we obtain the function $U_*(w)$
where $U_*=U$ outside $\Omega^*$, and in $\Omega^*$ 
the function $U_*$ is the harmonic extension of the boundary
function $U$ restricted to
$\partial\Omega^*$.
Set
\[
\Psi(w)= e^{U_*(w)}
\]
Proposition B.4 gives 
\[ 
f^*\in\mathcal A_\Psi\tag{B.5.ii}
\]
Next, consider  the function
in $D$ defined by:


\[ 
V(z)=\text{log}\, \bigl|\frac {d f^*(z)}{dz}\bigr|-U_*(f(z))
\] 
\medskip

\noindent
From the above 
$V(z)$ is either  identically zero in
$D$ or everywhere $<0$. It is also clear
that if $V=0$ then
$f^*\in\mathcal C_\Phi$ as required.
So there remains only to prove:
\medskip

\noindent
{\bf B.6 Lemma.} \emph{The function $V(z)$ is identically zero in $D$.}
\medskip

\noindent
\emph{Proof.}
Assume the contrary. So now
\[
 \bigl|\frac {d f^*(z)}{dz}\,\bigr|<e^{U_*(z)}\quad\text{for all}\,\,z\in D\,.\tag{i}
\]
Let $F(w)$ be the inverse of $f$ so that :
\[
F'(f^*(z))\cdot   \frac {d f^*(z)}{dz}=1\quad\, z\in D
\]
Then (i) gives:
\[ 
\bigl|F'(w)\,\bigr|> e^{-U_*(w)}\quad w\in \Omega^*\tag{ii}
\]


\noindent
Let $V(w)$ be the harmonic conjugate of $U_*(w)$ normalised so that
$V(0)=0$ and put
\[ 
H(w)=\int_0^w\,
e^{-U_*(\zeta)+iV(\zeta)}\cdot d\zeta\,.
\]
Then (ii) gives
\[
\bigl|H'(w)\bigr|<
\bigl|F'(w)\bigr|\quad w\in \Omega^*\tag{iii}
\]
Since $H(w((0))=F(w(0))=0$ it follows that
\[ 
\inf_{w\in\Omega^*}\,\frac{|H(w)|}{|F(w)|}=r_0<1\tag{iv}
\]
Now  $|F(w)|<1$ in $\Omega^*$
and  $|F(w)|\to 1$ as $w$ approaches
$\partial\Omega^*$. Hence  (iv) entails the domain
\[
R_0=\{ w\in \Omega^*\quad\colon\, |H(w)|<r_0\}\tag{v}
\]
has at least one boundary
point $w_*$ which also belongs to
$\partial\Omega^*$.
Next, the function $H(w)$ is analytic in $R_0$ and its derivative is everywhere
$\neq 0$ while $|H(w)|=1$ on $\partial R_0$. It follows
that $H$ gives a conformal map from $R_0$ onto the disc
$|z|<r_0$.
Let $h(z)$ be the inverse of this conformal mapping.
Now we get the 
analytic function in $D$ defined by
\[ 
g(z)= h(r_0z)
\] 
Next, let $|z|=1$ and put $w=h(r_0z)$.
Then 
\[ 
|g'(z)|= r_0\cdot |h'(r_0z)|=r_0\cdot \frac{1}{|H'(g(z))|}=
r_0\cdot e^{U_*(g(z))}=r_0\cdot\Psi(g(z))<\Psi(g(z))\tag{v}
\]
At the same time we have a common boundary point
\[ 
w_*\in\partial\Omega^*\,\cap\,\partial g(D)
\]


\noindent
Since the $g$-function extends to a continuous function on
$|z|\leq 1$ there exists a point
$e^{i\theta}$ such that
\[ 
g(e^{i\theta})= w_*
\]
Now we use that $r_0<1$ above.
The continuity of  $\Psi$
gives the existence of  $\epsilon>0$ such that
for any complex number $a$ which belongs to the disc
$|a-1|<\epsilon$, it follows that the function
\[
z\mapsto a\cdot g(z)
\]
belongs to $\mathcal A_\Psi$.
Finally, by  Proposition B.4  the maximal region for the $\Psi$-function is equal to
$\Omega^*$ and we conclude that
\[
ag(e^{i\theta})= aw_*\in \Omega^*\quad\, |a-1|<\epsilon
\]


\noindent
This would mean that
$w_*$ is an \emph{interior point} of
$\Omega^*$ which contradicts that $w_*\in\partial\Omega_*$
and
Lemma B.6 is proved.


\bigskip


\centerline{\bf C. Proof of Theorem 3.}
\bigskip

\noindent
First we have a companion to
Lemma B.2. Namely, let $g_1,\ldots,g_n$
be a finite set in $\mathcal B_\Phi$.
Set $S_\nu=g_\nu(D)$. Following [Beur: page
123] we give
\medskip

\noindent
{\bf C.1 Definition.}
\emph{The reduced intersection of the family
$\{S_\nu\}$ is defined as the set of these points
$w$
which can be joined with the origin by a Jordan arc
$\gamma$ contained in the intersection $\cap\, S_\nu$.
The resulting domain is denoted by
$RI\{S_\nu\}$.}
\medskip

\noindent
{\bf C.2 Proposition.}
\emph{The domain $RI\{S_\nu\}$ is simply connected and if
$g\in \mathcal C$ is the normalised conformal mapping onto
this domain, then
$g\in\mathcal B_\Phi$.}
\medskip

\noindent
The proof of this result can be carried out in a similar way as in
the proof of Lemma B.2 so we leave out the details.
Next, starting from a  dense sequence
$\{g_\nu\}$ in $\mathcal B_\Phi$
we find for each $n$ the function $f_n\in \mathcal B_\Phi$
where
\[ 
f_n(D)=RI\{S_\nu\}\quad\colon\, S_\nu=g_\nu(D)\,\colon\, 1\leq\nu\leq n\,.
\]
Here the simply connected domains
$\{f_n(D)\}$ decrease and there exists the limit function
$f_*\in\mathcal C$ where
\[
f_*(D)=\Omega_*
\]
There remains to prove
\medskip

\noindent
{\bf C.3 Proposition.}
\emph{One has $f_*\in\mathcal C_\Phi$.}
\medskip

\noindent
{\bf Remark.}
Proposition C.3  requires a quite involved proof 
as comared to the case of maximal regions.
The details are given in 
[Beur: page 127-130]. Let us 
just
sketch the strategy in the proof. Put
\[ 
m=\inf_{g\in\mathcal B_\Phi}\, g'(0)
\]
\medskip


\noindent
Next, $f_*$  belongs to
$\mathcal B_\Phi$ because we have the trivial inclusion
$\mathcal C_\Phi\subset \mathcal B_\Phi$ and using this Beurling  proved that
\[ 
m\geq \min_{w\in\Omega^*}\,\Phi(w)
\]
Next, starting with  Proposition C.2 above, Beurling introduces  a  normal family
and proves that
\[ 
f_*'(0)=m
\]
Thus, $f_*$ is a solution to an extremal problem which
Beurling used to   establish the inclusion
$f_*\in\mathcal C_\Phi$.
Let us remark that  this part of the proof 
relies upon
some some very interesting  set-theoretic constructions
where  the family of regions of the \emph{Schoenfliess' type}
are introduced in [Beur: page 121].
So the  whole proof  involves topological investigations of
independent interest.

\newpage

\centerline{\bf{§ 6. The Riemann-Schwarz inequality.}}

\bigskip


\noindent
By the uniformisation theorem for Riemann surfaces it
suffices to prove the result in §§ when $X=D$ and
$u$ is a continuous and subharmonic function in $D$
where 
$\lambda(z)= e^{u(z)}$ which yields a metric.
Consider a pair of points $a,b$ in $D$ and a pair of rectifiable 
Jordan arcs
$\gamma_1,\gamma_2$ in $\mathcal C(a,b)$.
Suppose for the moment that
the intersection of
the $\gamma$-curves only contains the end-points $a$ and $b$.
Their union gives
a closed Jordan curve
$\Gamma$ which borders a Jordan domain
$\Omega$.
The inequality (*) in  Theorem XX amounts to
show that for every 
point $p\in\gamma_1$, there  exists
a Jordan arc
$\beta$ in $\Omega$ which joins $p$ with some 
$q\in\gamma_2$ and a
Jordan arc $\alpha$ in $\Omega$ which joins $a$ and $b$ such that
\[
\bigl(\int_\alpha\, \lambda(z)\, |dz|\bigr)^2+
\bigl(\int_\beta\, \lambda(z)\, |dz|\bigr)^2\leq
\frac{1}{2}\cdot\bigl[\,
\bigl(\int_{\gamma_1}\, \lambda(z)\, |dz|\bigr)^2+
\bigl(\int_{\gamma_2}\, \lambda(z)\, |dz|\bigr)^2\bigr ]\tag{1}
\]
To prove (1) we employ a conformal mapping
$\psi\colon D\to \Omega$ where $D$ is another unit disc with
the complex coordinate $w$. The   Koebe-Lindelöf theorem
entails 
that $\psi$ extends to a homeomorphism from $D$ onto the closed Jordan 
domain $\bar\Omega$ where the inverse images of  $\gamma_1$ and $\gamma_2$
is a pair of closed intervals on the unit circle $|w|=1$
which
instersect  at two points. Now
$\log\,\lambda\circ \psi$
is subharmonic in $D$ and 
if $\gamma$ is a rectifiable  arc in $\Omega$ one has the equation:
\[
\int_\gamma\, \lambda(z)\cdot  |dz|
=\int_{\psi(\gamma)}\, \lambda\circ \psi(w)\cdot\frac{|dw|}{|\psi'(w)|}
\]
Set
\[ 
\lambda^*(w)=\frac{1}{|\psi'(w)|}\cdot \lambda\circ \psi(w)
\]
Then
\[ 
\log \lambda^*=-\log |\psi'(w)| +\log  \lambda\circ \psi
\] 
Here 
$\log |\psi'(w)|$ is the real part of the analytic function $\log \psi'(w)$
in $D$ and hence harmonic  which entails that
$\log\lambda^*$ is subharmonic.
The proof of (1) is therefore  reduced to the case when
$\Omega$ is replaced by the unit $w$-disc and 
$\lambda$  by $\lambda^*$. If  $J_1$ and $J_2$
are intervals on $\{|w|=1\}$
whose union is the whole circle, then the
Cauchy-Schwarz inequality gives
\[
\bigl(\int_{J_1}\, \lambda^*(w)\, |dw|\bigr)^2+
\bigl(\int_{J_2}\, \lambda^*(w)\, |dw|\bigr)^2\leq
\frac{1}{2}\cdot  \bigl(\int_{|w|=1}\, \lambda^*(w)\, |dw|\bigr)^2
\]
Passin to the
$w$-disc with $\lambda^*$ as above there remains  to find
a pair of curves $\alpha^*$ and $\beta^*$
in the $w$-disc where
$\alpha^*$ joins
the two points $\{e^{i\theta_\nu}\}$
on the unit circle where
the boundary  arcs $\psi^{-1}(\gamma_1)$ and $\psi^{-1}(\gamma_2)$ intersect,
while 
the
$\beta^*$-curve
joins some point
$p\in \psi^{-1}(\gamma_1)$  with a point  $q\in  \psi^{-1}(\gamma_2)$. 
\medskip


\noindent
{\bf{The choice of
$\alpha^*$ and $\beta^*$.}}
Let  $\alpha^*$ be the circular arc
with end-points at $e^{i\theta_1}$ and $e^{i\theta_2}$
which intersects $\{|w|=1\}$ at right angles.
Next, given a point $p\in\psi^{-1}(\gamma_1)$ there exists the unique circular arc
$\beta^*$ which  intersects both
$\alpha^*$ and  $\{|w|=1\}$ at right angles. See figure § XX.
Togehter with the  inequality (xx) there remains to prove
that $\alpha^*$ snd $\beta^*$ can be chosen so that 
\[
\bigl(\int_{\alpha^*}\, \lambda^*(w)\cdot  |dw|\,\bigr)^2+
\bigl(\,\int_{\beta^*}\, \lambda^*(w)\cdot  |dw|\,\bigr)^2\leq
\frac{1}{4}\cdot \bigl(\int_{|w|= 1\}}
\, \lambda^*(w)\, |dw|\,\bigr)^2\tag{2}
\]

\medskip


\noindent
To prove
(2) we will use a symmetrisation of $\lambda^*$.
Namely, let $T_1$ be 
a Möbius transformation 
on the unit disc which is a reflection of $\alpha^*$, i.e.
it restricts to 
the identity map on $\alpha^*$ and the composed map
$T_1^2$ is the identity in $D$. Similarly we find the reflection $T_2$
of $\beta^*$. One easily verifies that
$T_2\circ T_1=T_1\circ T_1$.
Let $S_0(w)=w$ be the identity while 
\[
S_1=T_1\quad\&\quad S_2=T_2\quad\&\quad
S_3= T_2\circ T_1
\]
Set
\[ 
\lambda^{**}(w)=
\frac{1}{4}\cdot 
\sum_{\nu=0}^{\nu=3}
\, \lambda(S_\nu(w))\cdot |\frac{S_\nu(w)}{dw}|\tag{3}
\]
Notice that  $T_2$ maps $\alpha^*$ into itself, and similarly
$T_1$ maps $\beta^*$ into itself.
If follows  that 
the left hand side in (2) is unchanged when 
$\lambda^*$ is replaced by  $\lambda^{**}$, and
the right hand side is  unchanged 
since the  $S$-transformations 
map $\{|w|=1\}$ onto itself.
Hence it suffices to prove (2)  when
$\lambda^*$ from the start is invariant with respect to the 
$S$-transformations above.  In this situation 
we solve the Dirichlet problem
using the boundary value function $\log\lambda^*$ on $\{|w|\}$ so that
in the open disc
\[ 
\log \lambda^*=g+H
\]
where $H$ is harmonic
in $D$ while  $g$ is subharmonic and zero on
$\{|w|\}$.
The maximum principle entails that
$g\leq 0$ in $D$ which gives 
\[ 
\lambda^*= e^u\cdot e^H\leq e^H\tag{4}
\]
Since $g=0$ on $\{|w|=1\}$
the right hand side in (2) is does not change  while the left 
hand side is majorised when 
$\lambda^*$ is replaced by $e^H$.
Moroever, the reader csn check that the  $S$-invariance of $\lambda^*$ implies that
$H$ also is $S$-invariant. Next, we find 
an analytic function $g(w)$ in $D$ such that
\[
 e^{H(w)}= |g'(w)|
\]
where 
the map $w\mapsto g(w)$
sends $\alpha^*$ to a real interval $[-A,A]$ and $\beta^*$
to an imaginary interval $[-iB,iB]$. Hence (4) implies that
the left  hand side in (2) is majorized by
\[ 
\bigl(\int_\alpha\, |g'(w)|\ |dw|)^2+
\bigl(\int_\beta\, |g'(w)|\ |dw|\,\bigr)^2=
4A^2+4B^2\tag{5}
\]
Next, since
$\lambda^*=|g'|$ holds on $\{|w|\}$
the right hand side in (2) becomes
\[
\frac{1}{4}\cdot\bigl(
\int_{|w|= 1}\,
|g'(w)|\, |dw|\,\bigr)^2\tag{6}
\]
Finally, the  $S$-symmetry of $g$ entails that
$\int_{|w|= 1}\,
|g'(w)|\, |dw|$ is 4  times
the
integral taken along
a subarc of $T$ which joins
consequtive points where $\alpha^*$ and $\beta^*$ intersect.
Each  such integral is the euclidian length of
the image curve  under $g$ which by the above joins
the real point $A$ with $iB$. So its euclidian length is
$\geq \sqrt{A^2+B^2}$, i.e. since  the shortest
distance between a pair of points is a straight line, together with 
Pythagoras' theorem.
Hence (6)  majorizes 
\[ 
\frac{1}{4}\cdot \bigl (4\cdot \sqrt{A^2+B^2}\bigr)^2=4(A^2+B^2)\tag{7}
\]
Then (5) and (7) give the
requested inequality (2).









\newpage




\newpage

\centerline {\bf{§ 7. A uniqueness result for the $\zeta$\vvv function}}
\bigskip

\noindent
In §  0.5 from the introduction  we defined
a class $\mathcal D\uuu k$
of Dirichlet series for every $k>0$ and announced
Beurling's  result in Theorem § 0.5.1. Recall that
each  Dirichlet series $\Lambda (s)$ in the family $\mathcal D\uuu k$
gives an even and entire function of exponential type defined by 
an Hadamard product:
\[ 
f(z)=\prod\, (1+ \frac {z^2}{\lambda\uuu n^2})
\]
Using 
Phragmén\vvv Lindelöf inequalities together with
properties of the $\Gamma$\vvv function and Mellin's inversion formula,
we shall prove that for each $\epsilon>0$ there exists a constant
$C\uuu\epsilon$
such that the following hold for each real $x>0$:
\[ 
\bigl |f(x)\vvv ax^p\cdot e^{\pi x}\bigr | \leq
C\uuu\epsilon\cdot e^{\pi(1\vvv 2k+\epsilon)\cdot x}
\tag{*}
\] 
where
\[
a= e^{2\Lambda(0)}\quad\text{and}\quad  p=2\Lambda'(0)
\]


\noindent
When $k>1/2$ we can choose $\epsilon$ small so that
$1\vvv k+\epsilon=\vvv \delta$ for some $\delta>0$
which 
means that
$f(x) \vvv ax^p\cdot e^{\pi x}$ has exponential decay as $x\to+\infty$.
From this we shall deduce that $f(z)$ is of a 
special form in 1 7.1 below and after deduce Theorem § 0.5.1 
via an  inversion formula for Dirichlet series. 

 
\bigskip
\centerline{\bf{7.1  A  uniqueness result in $\mathcal E$}}.
\medskip

\noindent
Let $a$ and $\delta$ be positive real numbers and $p$ some real number.
Consider an even entire function $f(z)$ of exponential type
for which there exists a constant $C$ such that
\[ 
\bigl|f(x)\vvv ax^p\cdot e^{\pi x}\bigr|\leq Ce^{\vvv \delta x}
\quad\colon\,   x\geq 1\tag{*}
\] 

\medskip


\noindent
{\bf{7.1.1 Theorem.}} \emph{When (*) amd $f(0)=1$ it follows that
 $f$ is one of the following two functions:}
\[
f_1(z)=
\frac{e^{\pi z}+
e^{-\pi z}}{2}\quad\colon\quad 
f_2(z)= \frac{e^{\pi z}-
e^{-\pi z}}{2\pi z}
\]
\medskip


\noindent
\emph{Proof.}
In  the half-space $\mathfrak{Re}(z)>0$
we have the analytic  function
\[
h(z)= f(z)\vvv az^p\cdot e^{\pi z}\tag{i}
\]
where the branch of $z^p$ is taken so that $x^p>0$ when
$z=x$ is real and $>0$.
Consider  the domain
\[ 
\Omega=\{z=x+iy\quad y>0\quad\text{and}\quad x>1\}
\]
Since $f\in \mathcal E$ there is a  constant $A$ such that
$e^{\vvv A|z|}\cdot f(z)$ is bounded which gives
constants $C$ and  $B$ such that
\[
 |h(1+iy)|\leq C\cdot e^{By}\tag{ii}
 \] 
for all $y>0$.
At the same time (*) gives
\[
 |h(x)|\leq C\cdot e^{\vvv \delta x}\tag{iii}
\]
The Phragmén\vvv Lindelöf theorem applied to the quarter planer
$\Omega$ therefore gives a constant $C$ such that
\[ 
|h(x+iy)|\leq Ce^{Ay\vvv \delta x}\quad\text{for all}\quad
x+iy\in\Omega\tag{iv}
\]
In exactly the same way one proves (iv) with $y$ replaced by $\vvv y$
in the quarter\vvv plane where $x>0$ and $y<0$.
Let us then consider the strip domain
\[
S=\{ x+iy\quad |y|\leq 1\quad \text{and}\quad x>1\}
\]
Then we see that there is a constant such that
\[
 h(x+iy)|\leq C\cdot e^{\vvv \delta x}\quad\colon\quad  x+iy\in S\tag{v}
\]
If $n\geq 1$ we consider the complex derivative $h^{(n)}$
and when $x>2$,   Cauchy's inequality and (*)
give a constant $C\uuu n$ such that
\[ 
|h^{(n)}(x)|\leq C\uuu n\cdot e^{\vvv \delta x}\quad\colon x\geq 2\tag{vi}
\]
Next, consider the second order
differential operator
\[
L=x^2\partial\uuu x^2\vvv 2p\cdot x\partial\uuu x\vvv \pi^2x^2+
p(p+1)
\]
The  functions $x^pe^{\pi x}$ and $x^pe^{\vvv \pi x}$
are  solutions to
the homogeneous equation $L=0$ when $x> 0$ and hence 
\[ 
L(f)=L(h)
\]
holds on $x>0$.
Now $L$ also yields the holomorphic differential operator
where $\partial\uuu x$ is replaced by $\partial\uuu z$
and here  $g=L(f)$ is en entire function exponential type.
Now (*) above Theorem 7.1.1  and the estimates (vi) for $n=0,1,2$ give a constant
$C$ such that
\[
|g(x)|\leq  C(1+x^2)\cdot e^{\vvv \delta|x|}\quad x>0\tag{vii}
\]
Moreover, since $f$ is even it follows that
$g$
is so and hence (vii) hold for all real $x$.
Then the $\mathcal E$\vvv function $g$ is identically zero by a wellknown and easily verified
result.
Hence  $f$ satisfies the differential equation
\[ 
L(f)=0\tag{viii}
\]
The uniquenss for solutions of the  in ODE-equation
(viii) gives contants $c_1,c_2$ such that
\[
f(x)= 
c_1x^pe^{\pi x}+
c_2x^pe^{-\pi x}\quad x>0
\]
Since $f$ is an even entire  function it is clear that this entails that
$p$ must be an integer and if we moreover assume that
$f(0)=1$ then the reader may verify that
we have $p=0$ or $p=-1$
which yield corresponding
$f$-functions
\[
f_1(z)=
\frac{e^{\pi z}+
e^{-\pi z}}{2}\quad\colon\,\,
f_2(z)=\frac{e^{\pi z}-
e^{-\pi z}}{2\pi z}
\]











\bigskip

\centerline{\bf{B. Dirichlet series and their transforms.}}


\bigskip

\noindent
Let $0<\lambda\uuu 1\leq\lambda\uuu 2\leq\ldots$
be a non\vvv decreasing sequence of positive real numbers in the family $\mathcal F$
from § xx.
Then 
the
Dirichlet series
\[
\Lambda(s)=\sum_{n=1}^\infty \frac{1}{\lambda\uuu n^s}\tag{1} 
\]
is analytic in the half\vvv space
$\mathfrak{Re}\, s>1$, and we also have the entire
function 
\[ 
f(z)=\prod\, \bigl(1+\frac{z^2}{\lambda^2\uuu n}\bigr)\tag{2}
\] 
which is of exponential type.

\bigskip

\noindent
{\bf{B.1 Inversion formula.}} \emph{One has the equation}
\[
\int\uuu 0^\infty\log f(x)\cdot  \frac{dx}{x^{s+1}}= \frac{\pi\cdot \Lambda(s)}
{s\sin\,\frac{\pi s}{2}}\quad\colon\quad \mathfrak{Re}\, s>1\tag{B.1.}
\]
\medskip

\noindent
\emph{Proof.}
When $0<\mathfrak{Re}\, s<2$ and $a>0$ is real
the reader may verify the
equality:
\[
\int\uuu 0^\infty\, \log\,(1+\frac{x^2}{a^2})\cdot \frac{dx}{x^{s+1}}
=\frac{1}{a^s}\cdot \frac{\pi}{\cdot \sin\,\frac{\pi s}{2}}\tag{i}
\]
\medskip


\noindent
Apply (i) with 
$a=\lambda\uuu n$ and then (B.1) follows
after a summation over
$n$.
\medskip


\noindent
{\bf{B.2 Meromorphic extensions.}}
The inversion formula  (B.1) entails that
$\Lambda$ extends to a meromorphic function in the complex $s$-plane.
To see this we notice that if $x>0$ then the logartihmic derivative
\[
\frac{f'(x)}{f(x)}=\sum\, \frac{2x}{\lambda_n^2+x^2}\tag{i}
\]
Next, a   partial integration gives
\[
(s+1)\cdot
\int\uuu 0^\infty\, \log\,f(x)\cdot \frac{dx}{x^{s+1}}
=
\int\uuu 0^\infty\, \frac{f'(x)}{f(x)}\cdot 
\frac{dx}{x^s}\tag{ii}
\]
Since $\sum\, \lambda_n^{-2}$ is convergent,
the right hand side is analytic in
the half-space $\mathfrak{Re}\, s>0$
and by further integrations by parts the reader
may verify that it extends to
a meromorphic function in
the $s$-plane. Together with
the inversion for ua we conclude that
$\Lambda(s)$ extends to a meromorphic
function in the $s$-plane.


\bigskip




\centerline{\bf{The case when
$\Lambda\in\mathcal D_k$}}.
\medskip



\noindent 
Suppose this holds for some
$k>1/2$.
In particular $\Lambda(-2n)=0$ for every positive integer 
and then 
the right hand side in (B.1)
is a meromorphic function whose poles 
are confined to $s=0$ and $s=1$.
Denote this function with
$\Phi(s)$.
Now we shall  estimate  certain $L^1$\vvv integrals.
\medskip

\noindent
{\bf{B.3 Proposition.}}
\emph{There exists a constant $C$ such that}
\[
\int\uuu{\vvv\infty}^\infty\, 
|\Phi(\vvv \sigma+it)|\cdot dt\leq C\cdot
\frac{\sigma^3\cdot \Gamma(\sigma)}{(2\pi k)^\sigma}
 \quad\colon\quad \sigma\geq 2
 \]
 \medskip
 
 \noindent
\emph {Proof.}
Consider the function
\[ 
\psi\uuu *(s)=
(2\pi k)^s\cdot \Gamma(2\vvv s)
\]
The  series expression for 
$\Lambda (s)$ gives a constant $C$ such that
\[ 
\Lambda(3/2+it)|\leq C\quad\colon\quad \vvv \infty <t<+\infty\tag{i}
\] 
It follows that
\[ 
\bigl|\frac{\Phi(3/2+it)}{\psi\uuu *(3/2+it)}\bigr |
 \leq \frac{C\pi}{|3/2+it|}\cdot \frac{1}{2\pi k)^{3/2}} \cdot 
 \frac{1} { \sin\,(\pi(3/4+it/2)\cdot \Gamma(1/2\vvv it)}\tag{ii}
\]
\medskip

\noindent
The complex sine\vvv function increases along this
vertical line, i.e. there is  a constant $c>0$ such that
 \[
 |\sin\,(\pi(3/4+it/2)|\geq c\cdot e^{\pi |t|/2}\tag{iii}
\]
At the same time, a classic result about
the $\Gamma$-function
gives the lower bound
\[
| \Gamma(1/2\vvv it)|\geq \sqrt{\pi}\cdot e^{\vvv \pi|t|/2}\tag{iv}
\]
From (iii\vvv iv ) we conclude that
the function $\frac{\Phi}{\psi\uuu *}$ is bounded
on the line $\mathfrak{Re}(s)= 3/2$.
\medskip

\noindent
\emph{Sublemma 1.} \emph{The function
$\frac{\Phi}{\psi\uuu *}$ is a bounded function in the domain}
\[ 
\Omega=\{ \mathfrak{Re}(s)<3/2\}\cap\, \{|s| >2\}
\]

\medskip

\noindent\emph{Proof.}
Follows easily via
the Phragmén\vvv Lindelöf theorem and the bound above on
$\mathfrak{Re}(s)= 3/2$.

\medskip

\noindent
Next, Sublemma  1 gives a constant $C$ such that
\[ 
|\Phi(s)|\leq C\cdot \bigl|(2\pi k)^s\cdot \Gamma(2\vvv s)|
\quad\colon\quad s\in\Omega\tag{v}
\]

\medskip

\noindent
We shall  need another classic  inequality for the
$\Gamma$\vvv function which
asserts that there
exists a constant $C$ such that
\[
\int\uuu {\vvv \infty}^\infty\, 
 \bigl|\, \Gamma(\sigma+2+it)\,\bigr|\cdot dt\leq 
 C\cdot \sigma^3\cdot \Gamma(\sigma)
 \quad\colon\quad \sigma\geq 2\tag{vi}
 \]
\medskip

\noindent
The verification of (vi) is left to the reader. Together (v) and (vi)
give the inequality in Proposition B.3.

\bigskip




\centerline {\bf{B.4 Mellin's inversion formula.}}
\bigskip

\noindent
The integral inequality in Proposition B.3  enable us to apply
the Fourier\vvv Mellin inversion formula via (**) from XX. This gives
\[
\log f(x)= \frac{1}{2\pi i}\cdot
\int\uuu {c\vvv  i\infty }^{c+i\infty}\,
\Phi(s)\cdot x^s\cdot ds\quad\colon\quad 1<c<2
\]
\medskip

\noindent
Using Proposition B.3  we can shift the contour the left and perform
integrals over
lines
$\mathfrak{Re}\, s= \vvv c$ where $c>0$.
During such a shift we pass the poles of
$\Phi$ which appear at $s=0$ and $s=1$. Using condition (a) from (0.2)
in the introduction the
reader can deduce  the integral formula:
\[
\log f(x)\vvv \pi x\vvv
2\phi(0)\cdot \log x\vvv 2\phi'(0) = \frac{1}{2\pi i}\cdot
\int\uuu {\vvv c \vvv  i\infty}^{\vvv c+i\infty}\,
\Phi(s)\cdot x^s\cdot ds \quad \text{for all}\quad c>0\tag{*}
\]
\medskip

\noindent
{\bf{B.4.1 A clever estimate.}}
To profit upon (*)
we  adapt the  $c$\vvv values when $x$ are real and large.
With $x\geq 2$ we take $c=x$ and notice that
\[
|x^{(\vvv x+it)}|= x^{\vvv x}
\]
Proposition B.3  and the triangle inequality show that
the absolute value of the right hand side integral in (*)  is majorized by
\[
2\pi\cdot x^{\vvv x}\cdot C\cdot \frac{x^3\cdot \Gamma(x)}{(2\pi k)^x}
\quad\colon\quad x\geq 2\tag{**}
\]
\medskip

\noindent{\bf{B.4.2 Exercise.}}
Recall that $\Gamma(N)= N !$ for positive integers. Use this and
Stirling's formula to conclude that
for every $\epsilon>0$ there is a constant $C\uuu\epsilon$
such that (**)  is majorized by
\[
C\uuu\epsilon\cdot e^{\vvv 2\pi(k\vvv \epsilon)x}
\]


\noindent
{\bf{B.4.3 Consequences.}}
With $x\geq 2$, 
$p=2\phi(0)$ and $a=2\phi'(0)$ we obtain from above:

\[
\bigl|\log f(x)\vvv \pi x\vvv
p\cdot \log x\vvv a\bigr| \leq
C\uuu\epsilon\cdot e^{\vvv 2\pi(k\vvv \epsilon)x}
\]

\medskip

\noindent
Now
(B.4.3) gives
a constant
$C^*\uuu\epsilon$ such that
\[ 
|f(x)\vvv e^a\cdot x^p\cdot e^{\pi x}|\leq 
C^*\uuu\epsilon\cdot e^{\pi(1\vvv 2k+2\epsilon)\cdot x}
\quad\colon\quad x\geq 2\tag{B.4.4}
\]
\medskip

\noindent
Since $k>1/2$ and $\epsilon$ can be arbitrary small
we conclude the foillowing

\medskip

\noindent
{\bf{B.4.5 Theorem.}}
\emph{When $\Lambda\in \mathcal D_k$ for some $k>1/2$ there
exists $\delta>0$ and constants $a,p$ such that}
\[
|f(x)\vvv e^a\cdot x^p\cdot e^{\pi x}|\leq 
C^*\uuu\epsilon\cdot e^{-\delta\cdot x}
\quad\colon\quad x\geq 2
\]
\bigskip

\noindent
\emph{Final part of the proof.}
Together with Theorem 7.1.1   the reader can  check that this gives Beurling's
Theorem form the introduction.




\newpage


*




\newpage






\centerline{\bf{Part II. Some results about subharmonic functions.}}
\bigskip

\noindent
{\bf{Introduction.}}
Subharmonic functions in the complex plane
are used in many situations. Perron's solution to the Dirichlet problem is an
example and passing to several complex variables one
introduces pluri-subharmonic functions whose basis properties
rely upon subharmonic functions of a single complex variable.
In general, if $u(z)$ is subharmoic it is represented
by the Riesz formula over discs. For example, let
$u(z)$ be subharmonic in $D=\{|s|<1\}$
and assume that
$u(0)=0$ and that $u(z)<1$ for every $z\in D$.
Then one has the non-negative masure $\mu=\Delta(u)$
and there exists a harmonic function $H(z)$ in
$D$ 
such that the function
\[
H(z)= u(z)-\frac{1}{\pi}\int_D\, \log\,\bigl|\frac{z-\zeta}{1-\bar\zeta z}\bigr|
\cdot d\mu(z)
\]
is harmonic.
Since $u(0)=0$ it follows that
$H(0)=0$ and
the maximum principle entails that
$H(z)\leq 1$ for all $z\in D$.
It follows that $1-H$ is a non-negative harmonic function and
therefore given by the Poisson extension of
a non-negative Resz measure on $T$. Hence $H(z)$ is the Poisson extension of
a Riesz measure on $T$ with a finite total variation.
This representation formula
gives  a local control on a subharmonic function
$u(z)$ which 
in general is not continuous and may attain the value $-\infty$ at certain points.
However, $u$ cannot be "too negative too often".
This follows by an a priori inequality due to Rado which asserts
that for every $r<1$ there exists a constant $C_r$ such that 
for every subharmonic function $u$ as above one has the inequality
\[
\iint_{|z|\leq r} \, e^{-u(z)} \,dxdy\leq C_r
\]
\medskip

\noindent
The proof relies upon Harnack's inequality
and is given in § xx below.
We shall establish scattered  results about subharmonic functions in
the separate sections below.


\bigskip




\centerline{\bf{A.  On zero sets of subharmonic functions.}}

\medskip

\noindent
Let  $\Omega$ in ${\bf{C}}$ be a bounded open set and
denote by
$\text{SH}_0(\Omega)$
the set of  subharmonic functions in   $\Omega$
whose Laplacian is a Riesz measure supported by a 
compact null set. Every such function $v$ is locally a
logarithmic potential of $\Delta(v)$ plus a harmonic function
and 
can therefore be taken to be
upper
semi-continuous. Moreover,  the distribution
derivatives  $\partial v/\partial x$
and
$\partial v/\partial y$  belong to
$L^1_{\text{loc}}(\Omega)$.
Before  Theorem A.1 is announced 
we introduce a geometric construction.
If $U$ is an open subset of $\Omega$
we  construct
its forward star\vvv domain
as follows:
To each $\zeta\in U$
we find the largest $s(\zeta)>0$
such that the line segment
\[
\ell\uuu\zeta(U)=
\{ \zeta+x\,\colon \, 0\leq x<s(\zeta)\}\subset \Omega
\]
The forward star domain is defined by
\[ 
\mathfrak{s}(U)=\bigcup\uuu{\zeta\in U}\, 
\ell\uuu\zeta(U)\tag{*}
\]
\bigskip

\noindent{\bf{A.1 Theorem.}}
\emph{Let 
$V\in\text{SH}_0(\Omega)$ and put
$K=\text{Supp}(\Delta(V))$. Suppose that
$V=0$ in an open subset $U$ of $\Omega\setminus K$
and furthermore}
\[
\partial V/\partial x(z)<0,\quad\text{holds in}\quad 
\Omega
\setminus (K\cup U)\,.\tag{*}
\]
\emph{Then $V=0$ in $\mathfrak{s}(U)$.}
\medskip

\noindent
{\bf{Remark.}}
This result was proved by
Bergqvist and Rullgård in 
the article [Be\vvv Ru]
 under the assumption
that
the range of $V$ is a finite set. The crucial step  to attain
the more general result above  is
to regard
the complex log\vvv function from (2) in the 
subsequent proof and employ similar 
regularisations as  in [Be\vvv Ru].

\bigskip


\noindent
\emph{Proof.}
It is clear that it suffices to show the following:
Let $z_0\in U$ and consider a horisontal
line segment 
\[
\ell=\{z=z_0+s\,\colon\,
0\leq s\leq s_0\}
\]
which is contained in $\Omega$.
Then, if $0<\delta<\text{dist}(\ell,\partial\Omega)$
and the open disc $D_\delta(z_0)$ of radius $\delta$ centered at
$z_0$ is contained in $U$, it follows that $V$ vanishes in the open set
\[
\{z\,\colon\, \text{dist}(z,\ell)<\delta\}\tag{1}
\]



\noindent
Notice  that (1) is a relatively compact subset of $\Omega$.
Consider the complex derivative
\[
\partial V/\partial z=
\frac{1}{2}(\partial V/\partial x\vvv i
\partial V/\partial y)
\]
This yields a complex\vvv valued and locally integrable function
and since $V=0$ in $D\uuu\delta(z\uuu 0)$
it is clear that $V=0$ in the open set from (1) if we  prove that
$\partial V/\partial z=0$ holds almost everywhere in (1)
To prove this we take some  $\epsilon>0$ and put
\[
\Psi\uuu\epsilon (z)=\log \, (\partial V/\partial z\vvv\epsilon)
\tag{2}
\]
\medskip
where the single-valued branch of the complex Log-function
is chosen so that
\[
\pi/2<\mathfrak{Im}\,\Psi\uuu\epsilon <3\pi/2\tag{3}
\]
Hence we can write
\[
\Psi\uuu\epsilon (z)=\text{Log}|\epsilon-\partial V/\partial z|+i\tau(z)
\quad\,\colon\quad  \pi/2<\tau(z)<3\pi/2\tag{4}
\]


\noindent 
\emph{A regularisation.}
Choose a non-negative
test-function $\phi$ with compact support in
$|z|\leq \delta$ while  $\phi(z)>0$ if $|z|<\delta$
and $\iint \phi(z)dxdy=1$. We construct the
convolution $\sigma*\Psi\uuu\epsilon $ which is defined in the
subset of $\Omega$ whose points have distance 
$>\delta$ to $\partial\Omega$.
Rules for first order derivations of a convolution
give

\[
\bar\partial/\bar\partial\bar z\bigl(\phi \ast \Psi\uuu\epsilon \bigr )=
\frac{\phi\ast \bar\partial\partial (V)}{\partial V/\partial z)\vvv
\epsilon}=
\frac{1}{4}\cdot\frac{1}{\partial V/\partial z\vvv\epsilon}\cdot 
\phi\ast \Delta(V)
\]
Taking the real part we get 
\[
\mathfrak{Re}(\bar\partial/\bar\partial\bar z(\phi\ast \Psi\uuu\epsilon))=
\frac{\partial V/\partial x\vvv \epsilon}{4
|\epsilon-\partial V/\partial z|^2}\cdot\phi*\Delta(V)\tag{5}
\]


\medskip
\noindent
To simplify notations we set
\[
\sigma(z)=\text{Log}|\epsilon-\partial V/\partial z|\tag{6}
 \]


\medskip


\noindent
The definition
of the $\bar\partial$-derivative and the decomposition
$\Psi\uuu\epsilon =\sigma+i\cdot \tau$
together with the inequality (5) give
\[
\partial_x(\phi*\sigma)\leq\partial_y(\phi*\tau)\tag{7}
\]

\medskip

\noindent
In the right hand side we 
use the partial $y$\vvv derivative on $\phi$, i.e. we use the general formula:
\[
\partial_y(\phi*\tau)=
\partial_y(\phi)*\tau
\]
Since $\pi/2\leq \tau\leq 3\pi/2$ the absolute value of this function
is majorized by
\[
M=\frac{3\pi}{2}\cdot||\partial_y(\phi)||_1\tag{8}
\]
where
$||\partial_y(\phi)||_1$ denotes the $L^1$-norm.
Next,  
consider the function $s\mapsto \phi*\sigma(z\uuu 0+s)$
where $0\leq s\leq s_0$ whose  $s$-derivative becomes
$\partial_x(\phi*\sigma)(z+s)$. Hence (7\vvv 8) give:

\[
\frac{d}{ds}(\phi*\sigma(z+s))\leq M
\]
\[
\implies
\phi*\sigma(z\uuu 0+s\uuu 0)\leq\phi*\sigma(z\uuu 0)+M\cdot s_0\tag{9}
\]

\medskip 

\noindent 
From now on  $\epsilon<1$ so that $\log \epsilon<0$. 
Since $V=0$ in $D\uuu\delta(z\uuu 0)$
we also have $\partial V/\partial z=0$ in this disc
and conclude that
\[
\phi*\sigma(z\uuu 0)=\log\,\epsilon\tag{10}
\]
Next, we have
\[ 
\sigma=\log\,\epsilon+
\log\,|1\vvv \frac{\partial V/\partial z}{\epsilon}|
\]
Put
\[
f\uuu\epsilon=\log\,|1\vvv \frac{\partial V/\partial z}{\epsilon}|\tag{11}
\]
Then (9\vvv 10) give the inequality
\[
\phi\ast f\uuu\epsilon(z\uuu 0+s\uuu 0)\leq M\cdot s\uuu 0\tag{12}
\]
So from 
the construction of a convolution this means that
\[
\iint\uuu{|\zeta|\leq \delta }\,
f\uuu\epsilon (z\uuu 0+s\uuu 0+\zeta)\cdot \phi(\zeta)\cdot d\xi d\eta
\leq M\cdot s\uuu 0\tag{13}
\]





\medskip

\noindent
Next, we can write
\[
f\uuu\epsilon (z)= \frac{1}{2}\cdot \log\, \bigl(
(1\vvv \frac{\partial V/\partial x}{\epsilon})^2+
(\frac{\partial V/\partial y}{\epsilon})^2\bigr)\tag{14}
\]
Since $\partial V/\partial x\leq 0$ holds almost everywhere we have
$f\geq 0$ almost everywhere and 
at each point $z$ where $\partial V/\partial z\neq 0$
we have
\[ 
\lim\uuu{\epsilon\to 0}\, f\uuu\epsilon(z)=+\infty\tag{15}
\]
Since (13 holds for each $\epsilon>0$
and $\phi>0$ in the open disc $|\zeta|<\delta$
we conclude that
$\partial V/\partial z=0$ must hold almost everywhere
in the disc $D\uuu\delta(z\uuu 0+s\uuu 0)$.
Here we considered the largest $s$\vvv value 
along the horisontal line $\ell$.
Of course, we get a similar conclusion for each $0<s<s\uuu 0$
and hence $\partial V/\partial z=0$ holds almost everywhere in
the open set (1).
At the same time
$V=0$ in $D\uuu\delta(z\uuu 0)$ and we conclude that
$V=0$ in the open set from (1) as requested.
\bigskip

\noindent




\bigskip

\centerline{\bf{B. A subharmonic majorization.}}
\bigskip

\noindent
The result below appears in Carleman's book on quasi-analytic functions.
Let $\{0<\beta\uuu 1<\beta\uuu 2<\ldots\}$ be a sequence of positive real numbers.
Given $a>0$ we construct harmonic functions in the right half\vvv plane
$\Omega=\mathfrak{Re}\, z> a$ as follows: Set $q\uuu\nu=a+i\beta\uuu\nu$ and
To each $z\in\Omega $  we get  the triangle
with corner points at $z,eq_\nu,eq\uuu{\nu+1}$
where $e$ is Neper's constant.
Denote the angle at $z$ by $\theta\uuu\nu(z)$. Notice that 
$0<\theta_\nu(z)<\pi$.
As explained in
§ XX  $\theta_\nu(z)$ is a harmonic function
with the boundary value $\pi$  on $\mathfrak{Re}\, z=a$
when  $\beta\uuu\nu<y<\beta\uuu{\nu+1}$ 
while the boundary value is zero outside the closed 
$y$\vvv interval $[\beta\nu,\beta\uuu{\nu+1}]$.
If we instead consider the points $\{q^*\uuu\nu=a\vvv ie\beta\uuu\nu\}$
we get similar harmonic angle functions
$\{\theta\uuu\nu^*\}$
when we regard the angle at $z$ formed by the triangle
with corner points at $z \vvv eq\uuu\nu,\vvv eq\uuu{\nu+1}$.

\medskip

\noindent
{\bf{Exercise.}} Show by euclidian geometry that
if $b<0$ is real and positive then
\[ 
\sin\,\theta\uuu\nu(a+b)= \frac{eb(\beta\uuu{\nu+1}\vvv\beta\uuu\nu)}{
\sqrt{ (\beta\uuu\nu^2+b^2)(\beta\uuu{\nu+1}^2+b^2)}}\tag{1}
\]
Use also that $\beta\uuu \nu<\beta\uuu{\nu+1}$ and show
that (1) gives

\[
\theta\uuu\nu (a+b)> \frac{e b\beta\uuu 1^2\cdot (\beta\uuu{\nu+1} \vvv\beta\uuu\nu)}
{\beta\uuu{\nu+1}\cdot \beta\uuu\nu\cdot(e^2 \beta\uuu 1^2+b^2)}=
C(b,\beta\uuu 1)\cdot (\frac{1}{\beta\uuu\nu}\vvv\frac{1}{\beta\uuu{\nu+1}})
\quad\colon\quad
C(b,\beta\uuu 1)=\frac{e b\beta\uuu 1^2}{e^2 \beta\uuu 1^2+b^2}
\]

\medskip

\noindent
In addition to these $\theta\uuu\nu$\vvv functions we get the angle functions
$\{\theta^*\uuu n\}$ where we for each $n\geq 2$ consider the
harmonic extension to the half\vvv plane whose boundary
values are $\pi$  on $y>\beta\uuu n$ and zero when
$y<\beta\uuu n$.
This harmonic function is denoted by $\theta^*\uuu n(z)$
and here  $\theta^*\uuu n(z)$
and by a figure the reader can verify  that
\[
\sin\, \theta^*\uuu n(a+b)=\frac{b}{\beta\uuu n^2+b^2)}\implies
\theta^*\uuu n(a+b)>\frac{eb\beta\uuu 1^2}{e^2 \beta\uuu 1^2+b^2}
\cdot \frac{1}{\beta\uuu n}\tag{2}
 \]
 





\medskip

\noindent
{\bf{7.1 A class of harmonic functions.}}
Given the $\beta$\vvv sequence above we also consider a sequence
of positive real numbers
$\{\lambda\uuu\nu\}$. To each  $n\geq 2$ we get the harmonic function
$u\uuu n(x,y)$ in $\Omega$
defined by
\[
u\uuu n(x,y)=\frac{1}{\pi}\cdot \sum\uuu{\nu=1}^{\nu=n\vvv 1} \lambda\uuu\nu\cdot
(\theta\uuu\nu+\theta^*\uuu\nu)+
\lambda\uuu n\cdot (\theta\uuu n+\theta^*\uuu n)\tag{3}
\]
If $z=a+b$ is real with $b>0$ the inequalities in (1\vvv 2) give

\[
u\uuu n(a+b)\geq \frac{C(b,\beta\uuu 1)}{\pi}
\cdot
\bigl[\, \sum\uuu{\nu=1}^{\nu=n\vvv 1}\,
\lambda\uuu\nu(\frac{1}{\beta\uuu\nu}\vvv \frac{1}{\beta\uuu{\nu+1}})+
\frac{\lambda\uuu n}{\beta\uuu n}\,\bigr]\tag{4}
\]



\noindent
From the above we get:


\medskip

\noindent
{\bf{7.2 Proposition.}}
\emph{Let $\{\lambda\uuu\nu\}$ and $\{\beta\uuu\nu\}$ be such that}
\[ 
\lim\uuu{n\to\infty}\,
\bigl[\, \sum\uuu{\nu=1}^{\nu=n\vvv 1}\,
\lambda\uuu\nu(\frac{1}{\beta\uuu\nu}\vvv \frac{1}{\beta\uuu{\nu+1}})=+\infty\tag{*}
\]
\emph{Then the sequence $\{u\uuu n(a+b)\}$ increases to $+\infty$ for every $b>0$.}

\medskip

\noindent
{\bf{Remark.}} If  
the $\lambda$\vvv sequence  increases  a partial summation gives
\[
\sum\uuu{\nu=1}^{\nu=n}\, \frac{\lambda\uuu \nu\vvv\lambda\uuu{\nu\vvv 1}}
{\beta\uuu\nu}= \sum\uuu{\nu=1}^{\nu=n\vvv 1}\,
\lambda\uuu\nu(\frac{1}{\beta\uuu\nu}\vvv \frac{1}{\beta\uuu{\nu+1}})
\]
where we have put $\lambda\uuu 0=0$. Hence (*) is equivalent to the divergence of
the 
positive series 
\[
\sum\uuu{\nu=1}^\infty \, \frac{\lambda\uuu \nu\vvv\lambda\uuu{\nu\vvv 1}}
{\beta\uuu\nu}\tag{**}
\]
\medskip


\noindent
{\bf{7.3 An application.}}
Let $\{\beta\uuu\nu\}$
be a strictly increasing sequence and
$\{\lambda\uuu\nu\}$ a sequence of positive real numbers.
Consider an analytic function $\Phi(z)$ defined in
the half\vvv plane $\mathfrak{Re}\,z>a$ with continuous
boundary values on $\mathfrak{Re}\,z=a$ which satisfies the inequalities

\[
|\Phi(z)|\leq \bigl(\frac{\beta\uuu\nu}{|z|}\,\bigr )^{\lambda\uuu\nu}
\quad\colon\quad \nu=1,2,\ldots\tag{*}
\]
\medskip

\noindent
{\bf{7.4 Exercise.}}
Denote by $u\uuu *(z)$ the harmonic function in
the half\vvv plane whose boundary values are one on
$\vvv\beta\uuu 1<y<\beta\uuu 1$ and otherwise zero.
Show that   (*) 
gives the following inequality on
$\mathfrak{Re}\, z=a$ for every $n\geq 0$ and $-\infty<y<+\infty$
 \[
\log\,|\Phi(a+iy)|+u\uuu n(a+iy)\leq 
\log K\cdot u\uuu *(a+iy)\quad\colon\quad 
K=\max\uuu {\vvv\beta\uuu 1\leq  y\leq \beta\uuu 1}\, |\Phi(a+iy)|\tag{7.4.1}
\]

\medskip

\noindent
{\bf{ Conclusion.}}
Since $u\uuu n$ and $u\uuu *$ are  harmonic functions
while $\log\,|\Phi\,|$ is subharmonic, 
the principle of harmonic majorization implies that  (7.4.1) holds
in $\Omega$.
In particular, for every
real 
$b>0$ we have
\[
\log\,|\Phi(a+ib)|+u\uuu n(a+ib)\leq \log K\cdot u\uuu *(a+ib)\tag{7.4.2}
\]


\noindent
When $\Phi$ is not identically zero  we can  fix some
$b>0$ where
$\Phi(a+ib)\neq 0$ and (7.4.2) entails that
the sequence $\{u\uuu n(a+ib)\}$ is bounded.
Hence Proposition 7.2  gives

\medskip

\noindent
{\bf{7.5 Theorem.}} \emph{Assume there exists a non\vvv zero analytic function
$\Phi(z)$ in the half\vvv plane
$\mathfrak{Re}\, z>a$ such that (*) holds in (7.3)
that
$\{\lambda\uuu \nu\}$ is increasing.
Then}
\[
\sum\uuu{\nu=1}^\infty \, \frac{\lambda\uuu \nu\vvv\lambda\uuu{\nu\vvv 1}}
{\beta\uuu\nu}<\infty
\]
\medskip

\noindent
{\bf{Remark.}} We can rephrase the result above and get a 
vanishing principle. Namely, if the positive series in Theorem 7.5 is divergent
an analytic function $\Phi(z)$ in the half\vvv plane satisfying
(7.3) must be identically zero.
\medskip


\noindent
{\bf{7.6 Example.}}
Let $\{c\uuu n\}$ be a sequence of positive real numbers.
Suppose that $\Phi(z)$ is analytic in the half\vvv space
and satisfies
\[
|\Phi(z)|\leq \frac{c\uuu n}{|z|^n}\quad\colon\quad n=1,2,\ldots
\]
Then $\Phi$ must vanish identically if the series

\[
\sum\uuu{n=1}^\infty\, \frac{1}{c\uuu n^{\frac{1}{n}}}=+\infty
\]

\medskip
\newpage


\centerline{\bf{C.  Subharmonic minorant of a given function.}}
\bigskip


\noindent
{\bf{Introduction.}}
Let $\Omega$ be a bounded
open and connected subset of ${\bf{C}}$ and
$F$  a non-negative and upper semicontinuous function in
$\Omega$ which may take values $+\infty$ at some points. 
Denote by $\mathcal F_*$ the class of subharmonic functions $u$ in
$\Omega$ such that  $u(x)\leq F(x)$ hold for every
$x\in\Omega$.
Set
\[ 
\mathcal S_F(x)= \max_{u\in \mathcal F_*}\, u(x)
\]
We refer to $\mathcal S_F$ as Sjöberg's maximal function associated to
$F$.
Next, 
recall that every subharmonic function $u$ 
is upper semicontinuous and
for every compact subset $K$ of $\Omega$ there is a constant $C$
such that $u(x)\leq C$ on $K$.
It turns out that this is the sole obstruction in order
that $\mathcal S_F$ itself
subharmonic.
More precisely the following result  was proved by
Sjöberg in [1938; Scand. congress Helsinki]
\medskip

\noindent
{\bf{1. Theorem.}}
\emph{If  
$\mathcal S_F$ is bounded on  every compact subset of
$\Omega$ then it is subharmonic and gives therefore the largest subharmonic function
in the class
$\mathcal F_*$.}

\bigskip


\noindent
{\bf{Remark.}}
In addition to [Sjöberg[ we refer to Domar's article
\emph{Subharmonic minorants of a given function}
[Arkiv 1954] where Sjöberg's resuts is extended in a wider context
and a similar result is proved for subharmonic functions in
${\bf{R}}^k$ when $k\geq 3$.
One expects
that
if  $F(x)$
enjoys some finiteness condition then
Sjöberg's condition holds so that  $\mathcal S_F$  gives
the largest subharminic minorant to $F$.
The following sufficency
result was proved by  Beurling in [Beurling xx]:

\medskip

\noindent
{\bf{Theorem.}} \emph{The function $\mathcal S_F$ is subharmonic
if  there exists $\epsilon>0$ such that}
\[
\iint_\Omega\, \bigl[\log^+F(x,y)\,\bigr]^{1+\epsilon}<\infty\tag{*}
\]
\medskip

\noindent
\emph{Proof.}
Assume (*) and with $\epsilon$ kept fixed the
value of the finite integral is denoted by 
$J(F)$.
We shall prove that 
if $K$ is a compact subset of $\Omega$
then there exists an integer $n$
such that
\[
\max_{x\in K} u(x)\leq e^n\tag{1}
\]
hold for every $u\in\mathcal F_*$.
If this holds
then Sjöberg's result entails that
$\mathcal S_F$ is subharmonic.
To prove (1)
we  fix a positive integer $\lambda$ and
a positive constant $C$ such that
\[
\frac{e}{\pi C^2}+e^{-\lambda}\leq 1\tag{2}
\]
Let us then take some $u\in \mathcal F_*$ and to each integer $\nu$ we set
\[ 
U_\nu=\{ e^\nu\leq u<e^{\nu+1}\}\tag{3}
\]
Then $\{U_\nu\}$ is a family of disjoint sets whose union is
$\Omega$ and to each $\nu$ we denote by $\ell_\nu$ the area of $U_\nu$.
Next, suppose that for some integer  $n>\lambda $ 
there exists  a point $z_n\in \Omega$ 
such that 
\[
u(x_n)\geq e^n\quad\text{and}\quad 
\text{dist}(x_,\partial\Omega)>C\cdot \sqrt{\ell_{n-\lambda}+\cdot +\ell_n}\tag{4}
\]



\noindent
Consider the disc $D_n^*=\{|z-z_n|\leq 
C\cdot \sqrt{\ell_{n-\lambda}+\cdot +\ell_n}\}$.
\medskip

\noindent
\emph{Sublemma.}\emph{The inequality (4) entails that}
\[
\max_{z\in D_n^*}\, u(z)\geq e^{n+1}
\tag{5}
\]


\noindent
\emph{Proof.}
We 
argue by a contradiction. Set
\[
\rho=C\cdot \sqrt{\ell_{n-\lambda}+\cdot +\ell_n}
\]



\noindent
 (5) fails the upper semi-continuity of $u$ gives
some $\rho_*>\rho$
such that  the disc
$\Delta= \{|z-z_n|\leq\rho^*$ is  contained in $\Omega$
and
$u\leq e^{n+1}$ holds in $\Delta$.
The mean-value inequality gives
\[ 
e^n\leq u(z_n)\leq \frac{1}{\pi\rho_*^2}\,
\iint_\Delta\, u(x,y)\,dxdy\tag{6}
\]
Now $U_\nu\cap \Delta=\emptyset$ if $\nu>n$
and since the $U$-sets are disjoint 
the right
hand side in (6) is  majorised by
\[
\frac{1}{\pi\rho_*^2}\cdot 
e^{n+1}(\ell_n+\dots+\ell_{n-\lambda})+e^{n-\lambda}
=e^n\cdot \frac{\rho^2}{\rho_*^2}\cdot [
e\cdot\frac{\ell_n+\dots+\ell_{n-\lambda}}{\pi}+e^{-\lambda}]\tag{7}
\]
The last factor is $\frac{e}{\pi C^2}+ e^{-\lambda}$
which is $\leq 1$ by (2) above.
Hence  (6-7) would give
\[
e^n\leq  e^n\cdot \frac{\rho^2}{\rho_*^2}
\]
Thus is a contradiction since
$\rho_*>\rho$ and  
hence 
$(4)\implies(5)$ holds.

\medskip

\noindent
\emph{Proof continued.}
Next, given  $z_n\in \Omega$ where
$u(z_n)\geq e^n$ we set
\[ 
\xi(m)= C\cdot\sum_{\nu=n}^{\nu=m}\, 
\sqrt{\ell_{\nu-\lambda}+\ldots+\ell_\nu}\quad\colon\, \forall\, m>n
\]


\noindent
Repeated use of $(4)\implies (5)$
shows that when $m>n$ and 
the disc $\{|z-z_n|\leq\xi(m)\}$ stays in $\Omega$ then it contains a point $z_m$ 
where $u(z_m)\geq e^m$.
Since
$u$ is bounded over compact subsets of $\Omega$
we must have
\[
\text{dist}(z_n,\partial\Omega)\leq
C\cdot \sum_{\nu=n}^\infty\, 
\sqrt{\ell_{\nu-\lambda}+\ldots+\ell_\nu}\tag{*}
\]
\medskip

\noindent
Let us  majorize the right hand side in (*).
Since $\sqrt{a_1+\ldots+a_k}\leq \sqrt{a_1}+\ldots +\sqrt{a_k}$
hold for all tuples of positive numbers 
the right hand side in (*) is majorized
by
\[
C\cdot \sum _{\nu=n}^\infty\, 
[\sqrt{\lambda_{\nu-\lambda}+\ldots+\lambda_\nu}]\leq
C\cdot(\lambda+1)
\sum_{\nu=n-\lambda} ^\infty
\, \sqrt{\lambda_\nu}
\]
To estimate the sum of the square roots
we pick the positive $\epsilon$ in the Theorem and write
\[
\sum_{\nu=n-\lambda} ^\infty
\, \sqrt{\lambda_\nu}=
\sum_{\nu=n-\lambda} ^\infty
\,\nu^{-1/2-\epsilon/2}\cdot   \sqrt{\lambda_\nu}\cdot \nu^{1/2+\epsilon/2}\leq
\sqrt{\sum_{\nu=n-\lambda} ^\infty
\,\nu^{-1-\epsilon}}\cdot 
\sqrt{\sum_{\nu=n-\lambda}
\lambda_\nu\cdot \nu^{1+\epsilon}}
\]
where the Cauchy-Schwarz inequality was used.
Since $\epsilon>0$
the first factor 
is a function $n\mapsto \tau(n)$ given as a  square root of  tail sums
of a convergent series and hence $\tau(n)\to 0$ when
$n\to+\infty$.
Now (*) is majorised by
\[ 
C\cdot \tau(n)\cdot 
\sqrt{\sum_{\nu=n-\lambda}
\lambda_\nu\cdot \nu^{1+\epsilon}}\tag{**}
\]
Next, we have 
\[
\log^+\,u(z)\geq \nu\,\colon|, z\in U_\nu\}
\]
Since the sets $\{U_\nu\}$ are disjoint it follows that

\[
\sum_{\nu=n-\lambda}
\lambda_\nu\cdot \nu^{1+\epsilon}\leq
\iint_\Omega\, [\log^+\, u(x,y)|^{1+\epsilon}\, dxdy\leq J(F)
\]
where the last inequality follows since
$u\leq F$.
integral in the theorem whose value is denoted by $J(F)$. Hence (*) gives
\[ 
\text{dist}(z_n,\partial\Omega)\leq
C\cdot \sqrt{J(F)}\cdot \tau(n)
\]
\medskip

\noindent
Finally, if $K$ is a compact subset of $\Omega$ its distance to
$\partial\Omega$ is a positive number $a_K$
and since
$\tau(n)\to 0$ we find a large integer $N$
such that
$C\cdot \sqrt{J(F)}\cdot \tau(n)\leq a_K$ and by the above it follows that
$u\leq e^n$ holds on $K$. Since $u\in\mathcal F_*$ was arbitrary
we have proved that $\mathcal S_F$ is bounded on $K$ and Theorem 2 is proved.


\newpage

\centerline{\bf{D.  An inequality for harmonic functions.}}
\bigskip

\noindent
The result below appears in Beuling's article [xxx].
Denote by $U_+$ the upper half-plane $\{\mathfrak{Im}\, z>0\}$.




\medskip



\noindent
{\bf{13.4  Theorem.}}\emph{
For each positive harmonic  function $u(x,y)$  in $U_+$
we put}
\[
E_u=\{ x+iy\in U_+\quad\colon\, u(x,y)\geq y\}
\]
\emph{Then one has the implication}
\[
U_+\setminus E_u\neq\emptyset\implies
\int_{E_u}\,\frac{dxdy}{1+x^2+y^2}<\infty\tag{*}
\]
\medskip




\noindent{\emph{Proof}.
The impliction (*) is obvious
when
$u(x,y)=ay$ for some positive real number $a$, i.e.
regard the cases $a<1$ and $a\geq 1$ separately.
From now on we assume that
$u(x,y)$ is not a linear function of $y$ and the
wellknown Harnack-Hopf inequality  gives
the strict inequality
\[ 
\frac{\partial u}{\partial y}(x,y)<\frac{u(x,y)}{y}
\quad\colon\, (x,y)\in U_+\tag{1}
\]
\medskip

\noindent
Set $u_*=y-u$ which entails that
\[ 
\{u_*>0\}=U_+\setminus E_u\tag{2}
\]

\medskip

\noindent
\emph {3. A simply connected domain.}
We assume that the set $U_+\setminus E_u$ is non-emtpy and let
$\Omega$ be  some  connected component of this open set.
Replacing $u$ by the harmonic
function $u(x+a,y)$ for a suitable 
real $a$
we may assume that
$\Omega$ contains a point on the imaginary axis and after a scaling
that $i\in\Omega$.
Next, (1) gives
\[ 
\frac{\partial u_*}{\partial y}=1-\frac{\partial u}{\partial y}
>1-\frac{u}{y}\tag{4}
\]
Starting at a point $(x,y)\in\Omega$ it follows that
$s\mapsto u_*(x,y+is)$ increases strictly  on $\{s\geq 0\}$ and
hence the open set
$\Omega$ is placed above a graph, i.e. there exists an interval $(a,b)$
on the real $x$-axis and a non-negative 
continuous function $g(x)$ on $(a,b)$ such that
\[ 
\Omega=\{ (x,y)\,\colon a<x<b\,\,\colon\,\, y>g(x)\}\tag{5}
\]
In (5)
it  may occur that the interval $(a,b)$
is unbounded and may even be
the whole $x$-axis in which   case $\Omega$ is the sole component of
$U_+\setminus E_u$. In any case, since $i\in\Omega$
one has
$a<0<b$
and $\Omega$ contains
the the set $\{ai\colon\, a\geq 1\}$.
Next, for each $r>2$ we put
\[ 
C_r=U_+\cap \{|z+i|<r\}\tag{6}
\]
Notice that
$C_r$ contains the point $(r-1)i$
which also belongs to $\Omega$.
Denote by  $\gamma_r$ be the largest open interval on the
circle $\{|z+i|= r$ which contains 
$(r-1)i$ and at the same time is 
contained in $\partial\Omega$.
With the aid of a figure it is clear that the
set $\Omega _r= \Omega\cap C_r$ 
is simply connected where 
$\gamma_r$ is a part of
$\partial  D_r$ and   $u_*=0$ on
$\partial D_r\setminus \gamma_r$.
\medskip



\noindent{\emph{ The use of harmonic measure.}}
Let $h_r(z)$ be the harmonic function in
$\Omega_r$ which is 1 on
$\gamma_r$ and zero on the rest of the boundary.
By the above and the maximum principle for harmonic functions
we have the inequality
\[ 
u_*(i)\leq h_r(i)\cdot \max_{z\in\partial D_r} u_*(z)\leq r\tag{7}
\]
where the last inequality follows since
$u_*(x,y)\leq y\leq  r$.
To  estimate  the function $h_r(z)$ with resoect to both $r$ and $z$
we shall use
the harmonic function
\[
\Psi(z)= \log\, \bigl|\frac{z+i}{2i}\bigr |\implies
|\nabla(\Psi)|^2=\Psi_x^2+\Psi_y^2=\frac{1}{|z+i|^2}\tag{8}
\]
Set
\[ 
m(r)=
\frac{1}{\pi}\,  \iint_{E_u\cap C_r}\,|\nabla(\Psi)|^2\, dxdy=
\frac{1}{\pi}\,  \iint_{E_u\cap C_r}\,\frac{1}{|z+i|^2}|\, dxdy\tag{9}
\]
Notice  that
\[
\frac{1}{\pi}\,  \iint_{C_r}\,\frac{1}{|z+i|^2}|\, dxdy<\log r\tag{10}
\]
Together (9-10) give the inequality
\[
\frac{1}{\pi}\,  \iint_{\Omega_r}\,|\nabla(\Psi)|^2\, dxdy<
\log r-m(r)\tag{11}
\]


\noindent
Next, we notice that
 \[ 
 \Psi(z)= \log r-\log 2\quad\text{on}\quad \gamma_r\quad\text{and}\quad
 \Psi(i)=0\tag{12}
 \] 


\noindent
Now we can apply the general inequality from § XX in [Beurling-Special Topics]
and conclude that (11-12) 
give
the inequality
 \[ 
 h_r(i)\leq e^{-\frac{\pi L^2}{A}} \quad\text{where}\quad
 L=\log r-\log 2 \tag{13}
\]


\noindent
Next, the reader may verify
that there exists a constant $C$
which is independent of $r\geq 2$ such that
\[
 \frac{\pi L^2}{A}\geq \frac{\lg r-\log 2)^2}{\log r-\log m(r)}
 \geq \log r-2\log 2+m(r)\cdot \bigl[1-\frac{C}{\log r}]\tag{14}
 \]
 \medskip
 
 \noindent
Then (13-14)
gives a constant $C_1$ such that
\[
h_r(i)\leq  e^{-\frac{\pi L^2}{A}}\leq C_1\cdot \frac{1}{r}\cdot e^{-m(r)}
\quad\colon\, r\geq 2\tag{15}
\]

\noindent
Then (7) and  (15) give
\[ 
u_*(i)\leq C_1\cdot \cdot e^{-m(r)}\tag{*}
\]

\medskip

\noindent
This inequality hold for all $r>2$ and since
$u_*(i)>0$
there must exist a finite limit
\[ 
\lim_{r\to\infty} m(r)=m^*\tag{**}
\]
The requested implication in Theorem 15.2
follows since  (9)  this means that
\[
\iint_{E_u}\, \frac{1}{|z+i|^2}\, dxdy=\lim_{r\to\infty} m(r)
\]


\bigskip


\centerline{\bf{E.  Carleman's differential inequality and the
Denjoy conjecture}}

\bigskip

\noindent {\bf Introduction.}
Let $\rho$ be a positive integer and 
$f(z)$  is an entire function such that there exists some
$0<\epsilon<1/2 $  and a constant $A_\epsilon$ such that
\[
|f(z)|\leq A_\epsilon\cdot e^{|z|^{\rho+\epsilon}}\tag{0.1}
\]


\noindent
hold for every $z$. Then we say that 
$f$ has integral order $\leq\rho$.
Next, the entire function $f$ has an asymptotic value $a$
if there exists a Jordan curve
$\Gamma$ parametrized
by
$t\mapsto\gamma(t)$ for $t\geq 0$ such that
$|\gamma(t)|\to \infty$ as $t\to+\infty$ and
\[
\lim_{t\to+\infty}\, f(\gamma(t))=a\tag{0.2}
\]


\noindent
In 1907 Denjoy conjectured that
(0.1) implies that the entire function $f$ has at most
$2\rho$ many different asymptotic values. Examples show that
this upper bound is sharp. In an artice from 1920
Carelan proved that the number of asumptotic values cannot exceed
$5\cdot\rho$.
The sharp bound which
settled the Denjoy
conjecture was proved in 1929 by  Ahlfors in [Ahl] and
independently
by Beulring the same year while he
prepared his Ph.D  thesis.
A few years later T. Carleman found an alternative  proof based
upon a certain differential inequality which
has  applications beyond the proof of
the Denjoy conjecture
for estimates of
harmonic measures. See [Ga-Marsh].

\bigskip

\centerline{\bf A. The  differential inequality.}
\bigskip


\noindent
The conclusive result appears in Theorem XX below.
We begin to describe the geometric situation.
Let $\Omega$ be a connected open set in ${\bf{C}}$ whose
intersection $S\uuu x$ between
a  vertical line  $\{\mathfrak{Re}\, z=x\}$
is a bounded set
on the real $y$-line for every $x$.
When $S_x\neq\emptyset $ it is the disjoint union
of open
intervals $\{(a_\nu,b_\nu)\}$ and we set
\[ 
\ell(x)=\max\uuu \nu \,(b_\nu-a_\nu)\tag{*}
\]

\medskip


\noindent
Next, let
$u(x,y)$ be a positive harmonic   function
in $\Omega$ which 
extends to a continuous function on
the closure $\bar\Omega$  with the boundary values identical to zero.
Define the function $\phi$ by:
\[ 
\phi(x)=\int_{S_x}\,u^2(x,y)\cdot dy\tag{1}
\]
The Federer-Stokes theorem gives
the following  formula for the derivatives of $\phi$:
\[ 
\phi'(x)=2\int_{S_x}\,u_x\cdot u(x,y) dy\tag{2}
\]
\[
\phi''(x)=2\int_{S_x}\,u_{xx}\cdot u(x,y) dy+
2\int_{S_x}\,u^2_x\cdot dy\tag{3}
\]


\noindent
Since $\Delta(u)=0$ when $u>0$ we have
\[
2\int_{S_x}\,u_{xx}\cdot u(x,y) dy=-
2\int_{S_x}\,u_{yy}\cdot u(x,y) dy=
2\int u_y^2 dy\tag{4}
\]
The Cauchy-Schwarz inequality applied in (2) gives
\[
\phi'(x)^2\leq 4\cdot \int_{S_x}\,u^2_x\cdot\int_{S_x} u^2(x,y) dy
=4 \cdot \phi(x)\cdot \int_{S_x}u_x^2dy\tag{5}
\]
Hence (4) and (5) give:
\[ 
\phi''(x)\geq 2\int\uuu{S\uuu x} \,u^2_y(x,y)\cdot dy+\frac{1}{2}\cdot \frac{\phi'^2(x)}{\phi(x)}\tag{6}
\]
Next, since $u(x,y)=0$ at the end-points of all intervals of $S_x$,
\emph{Wirtinger's 
inequality}
and the definition of $\ell(x)$ give:
\[
\int\uuu{S\uuu x} u^2_y(x,y)\cdot dy\geq \frac{\pi^2}{\ell(x)^2}\cdot\phi(x)\tag{7}
\]


\noindent
Inserting (7) in (6) we have  proved
\medskip

\noindent
{\bf A.1 Proposition} \emph{The $\phi$-function satisfies the differential inequality}
\[
\phi''(x)\geq \frac{2\pi^2}{\ell(x)^2}\cdot\phi(x)+\frac{\phi'^2(x)}{2\phi(x)}
\]


\noindent
\emph{Proof continued.}
The maximum
principle for harmonic functions implies that the $\phi(x)>0$
when $x>0$ and hence there exists
a $\psi$-function where
$\phi(x)= e^{\psi(x)}$. It follows that

\[ 
\phi'=\psi' e^\psi\quad\text{and}\quad\,\phi''=
\psi''e^\psi+\psi'^2e^\psi
\]

\noindent
Now  Proposition A.1 gives
\[
 \psi''+\frac{\psi'^2}{2}\geq \frac{2\pi^2}{\ell(x)^2}\tag{*}
\]
\medskip


\noindent
{\bf {A.2 An integral inequality.}}
From (*) we obtain
\[
\frac{2\pi}{\ell(x)}\leq\sqrt{\psi'(x)^2+2\psi''(x)}\,\leq
\psi'(x)+\frac{\psi''(x)}{\psi'(x)}
\]
\medskip

\noindent
Taking the integral we get
\[ 
2\pi\cdot\int_0^x\,\frac{dt}{\ell(t)}\leq \psi(x)+\log\,\psi'(x)+O(1)
\leq \psi(x)+,\psi'(x)+O(1)\tag{**}
\]
where $O(1)$ is a remainder 
term which is bounded  independent of $x$. Taking the integral once more we 
obtain:
\medskip

\noindent
{\bf {A.3 Theorem.}}
\emph{The following inequality holds:}


\[
2\pi\cdot\int_0^x\, \frac{x-s}{\ell(s)}\cdot ds\leq
\int_0^x\,\psi(s)\cdot ds+\psi(x)+O(x)
\]
\emph{where the remainder term $O(x)$ is bounded by $Cx$ for 
a fixed constant.}

\newpage


\centerline {\bf B. Solution to the Denjoy conjecture}
\bigskip

\noindent
{\bf B.1 Theorem.}
\emph{Let $f(z)$ be entire of some integral order
$\rho\geq 1$. Then $f$ has at most $2\rho$ many different asymptotic values.}
\bigskip

\noindent
\emph{Proof.}
Suppose $f$ has $n$ different asymptotic values
$a_1,\ldots,a_n$.
To each  $a_\nu$ there exists a Jordan arc $\Gamma_\nu$ as described in the introduction.
Since the $a$-values are different the $n$-tuple of
$\Gamma$-arcs are separated from each other when
$|z|$ is large.
So we can find some $R$ such that
the arcs are disjoint in the exterior disc
$|z|>R$. We may also consider the tail of each arc, i.e. starting from
the last point on $\Gamma_\nu$ which intersects the circle
$|z|=R$. So now we have an $n$-tuple of disjoint Jordan
curves in $|z|\geq R$ where each curve intersects $|z|=R$ at some point $p_\nu$ and after the curves moves to the point at infinity. See figure.
Next, we take one of these curves, say $\Gamma_1$. Let
$D_R^*$ be the exterior disc $|\zeta |>R$.
In the domain
$\Omega={\bf{C}}\setminus \Gamma_1\cup\,D_R^*$ we can choose a single-valued
branch of $\log \zeta$ and with $z=\log\,\zeta $
the image of $\Omega$ is a simply connected domain 
$\Omega^*$
where
$S_x$ for each $x$ has length strictly less than
$2\pi$
The images of the $\Gamma$-curves
separate $\Omega^*$
into $n$ many disjoint connected
domains
denoted by $D_1,\ldots,D_n$ where
each $D_\nu$ is bordered by a pair of images of $\Gamma$-curves
and a portion of the vertical line $x=\log \,R$.

\medskip

\noindent
Let $\zeta=\xi+i\eta$ be the complex coordinate
in $\Omega^*$.
Here we get the analytic function
$F(\zeta)$ where
\[ F(\text{log}(z))= f(z)
\]
We notice that $F$ may have more growth than $f$. Indeed, we get
\[
|F(\xi+i\eta)|\leq \text{exp}\bigl(e^{(\rho+\epsilon)\xi}\bigr)\tag{1}
\]

\medskip

\noindent
With $u=\text{Log}^+\,|F|$ it follows that
\[ 
u(\xi,\eta)\leq e^{(\rho+\epsilon)\xi}\tag{2}
\]


\noindent
Hence the $\phi$-function constructed
during the proof of Theorem A.3  satisfies
\[
\phi(\xi)\leq e^{2(\rho+\epsilon)\xi}
\]
It follows that the $\psi$-function satisfies


\[ 
\psi(\xi)=2\cdot (\rho+\epsilon)\xi+O(1)\tag{3}
\]


\noindent Now we  apply Theorem A.3  in each region $D_\nu$
where we have a function
$\ell_\nu(\xi)$ constructed by (0) in section A. 
This gives the inequality
\[
2\pi\cdot \int_R^\xi\, \frac{\xi-s}{\ell_\nu(s)}\cdot ds\leq
\int_R^\xi\, (\rho+\epsilon)s\cdot ds+(\rho+\epsilon)\xi+O(1)\quad\colon\quad
1\leq \nu\leq n\tag{4}
\]
\medskip

\noindent
Next, recall the elementary inequality which asserts that if $a\uuu 1,\ldots,a\uuu n$
is an arbitrary $n$\vvv tuple of positive numbers then
\[
\sum\,a\uuu \nu\cdot \sum\, \frac{1}{a_\nu}\geq n^2
\tag{5}
\]
For each $s$ we apply this to the $n$\vvv tuple
$\{\ell\uuu \nu(s)\}$ where we also have
\[ 
\sum\,\ell\uuu \nu(s)\leq 2\pi
\] 
\noindent
So  a summation in (4) over $1\leq \nu\leq n$ gives
\[
n\cdot  \int_R^\xi\, (\xi-s)\cdot ds\leq
\int_R^\xi\, (\rho+\epsilon)s\cdot ds+(\rho+\epsilon)\xi+O(1)\tag{6}
\]
Another integration gives:
\[ 
n\cdot\frac{\xi^2}{2}\leq (\rho+\epsilon)\cdot \xi^2+O(\xi)\tag{7}
\]
\medskip

\noindent
This inequality can only hold for large $\xi$ if
$n\leq 2(\rho+\epsilon)$ and since  $\epsilon<1/2$ is assumed
it follows that 
$n\leq 2\rho$ which finishes the proof of the Denjoy conjecture.

\newpage



\centerline{\bf{F.  Ganelius' inequality for conjugate harmonic functions.}}
\bigskip


\noindent
{\bf{Introduction.}}
We   prove a result due to Ganelius from the article
\emph{Sequences of analytic functions and their zeros} Arkiv för matematik. Vol 3 (1953).
Here is the situation: Let $u$
be a harmonic function 
defined in some open neighborhood
of
the closed unit disc where 
$u(0)=0$. Its harmonic conjugate $v$
is normalised so that
$v(0)$. The constants  $H,K$ are defined by:
\[ 
\max_\theta\, u(e^{i\theta})=H\quad\colon\quad
\max_\theta\, \frac{\partial v}{\partial\theta}(e^{i\theta})=K\tag{*}
\]
where the maximum is taken over
$0\leq \theta\leq 2\pi$.


\noindent
{\bf{14.1 Theorem.}}
\emph{There exists an absolute constant $C$ such that}
\[ 
\max_{z\in D}\, |v(z)|\leq C\cdot \sqrt{HK}
\]

\medskip
\noindent
Before the proof starts 
we notice that the mean-value property  for harmonic functions
and the equality  $u(0)=0$  give
\[
\min_\theta\, u(e^{i\theta})=-\max_\theta\, u(e^{i\theta})
\]
Replacing $u$ by $-u$  it therefore suffices to
get an upper bound for
the maximum of $v$, and by a rotation it suffices to get
the inequality when
$\theta=0$, i.e. there remains to show that
\[
v(1)\leq C\cdot \sqrt{HK}
\]
where the subsequent proof will
provide the constant $C$.

\bigskip

\noindent{\emph{Proof}.
To each real $\lambda>1/2$ we put
\[ 
G_\lambda(z)= \log\, \bigl| \frac{1+z^\lambda}{1-z^\lambda}\bigr |
\]
which gives a harmonic function 
of $z$ in the sector 
of the open unit disc where
\[
-\frac{\pi}{2\lambda}<\arg z<\frac{\pi}{2\lambda}
\]
When
$z=e^{i\theta}$ we see that
\[
G_\lambda e^{i\theta})=
\,\log\,\frac{\cos(\lambda\theta/2)}{
|\sin(\lambda\theta/2)|} 
\]

\medskip

\noindent
{\bf{1. Exercise.}}
Apply  Green's formula  to domains
$S\cap \{|z-1|>\epsilon\}$ and  show that 
the equation
 below for each $0\leq \phi\leq 2\pi$:
 \[
2\lambda\cdot \int_0^1
\,  \frac{u(re^{i(\phi-\frac{\pi}{2\lambda})}+
u(re^{i(\phi+\frac{\pi}{2\lambda}})}{1+r^2}\,r^{\lambda-1}\, dr-\pi u(e^{i\phi})=
\]
\[
\int_ {\frac{\pi}{2\lambda}}^{-\frac{\pi}{2\lambda}}
\,\log\,\frac{\cos(\lambda\theta/2)}{
|\sin(\lambda\theta/2)|}\cdot 
\frac{\partial u}{\partial r}(
e^{i(\phi+\theta})\,d\theta\tag{1}
\]
\bigskip


\noindent
Next, the Cauchy-Riemann equations entail that
\[
\frac{\partial u}{\partial r}(
e^{i(\phi+\theta})= \frac{\partial v}{\partial\theta}(\phi+ \theta)
\]
Choose some
$0<\xi<\pi$
and integrate
(1) with respect to $\phi$ over $(-\xi,\xi)$.
The integral of the last term in (1) becomes
\[
\int_ {-\frac{\pi}{2\lambda}}^{\frac{\pi}{2\lambda}}
\,\log\,\frac{\cos(\lambda\theta/2)}{
\sin(\lambda\theta/2)}\cdot  \bigl[v(\xi+\theta)-v(-\xi+\theta)\bigr ]
\,d\theta\tag{2}
\]
\medskip

\noindent
{\bf{Exercise.}}
By assumption  $\frac{dv}{d\theta}\leq K$
holds for the
$\theta$-periodic $v$-function. Show via Rolle's theorem that  
\[
v(\xi+\theta)-v^*(-\xi+\theta)\leq
v(\xi-\frac{\pi}{2\lambda})-
v(-\xi+\frac{\pi}{2\lambda})+K\cdot \frac{\pi}{\lambda}
\quad\colon\quad 
 -\frac{\pi}{2\lambda}<\theta<\frac{\pi}{2\lambda}\tag{3}
\]
\medskip

\noindent
Set
\[
I(\lambda)=\int_ {-\frac{\pi}{2\lambda}}^{\frac{\pi}{2\lambda}}
\,\log\,\frac{\cos(\lambda\theta/2)}{
\sin(\lambda\theta/2)}\,d\theta\tag{4}
\]
Then (3) entails that  (2) is majorised by
\[
I(\lambda)\cdot [v(\xi-\frac{\pi}{2\lambda})-
v(-\xi+\frac{\pi}{2\lambda})+K\cdot \frac{\pi}{\lambda}]\tag{5}
\]


\noindent
{\bf{Exercise.}}
Show that
\[
I(\lambda)=\frac{4}{\lambda}\int_1^\infty\, \frac{\log t}{1+t^2}\, dt
= \frac{4}{\lambda}\cdot \mathcal C\quad\colon
\mathcal C= 1+ \sum_{m=1}^\infty\,(-1)^m\cdot \frac{1}{(m+1)^2} \simeq
0,916\ldots\tag{6}
\]
\medskip








\noindent
{\bf{7. A lower bound.}}
Recall that $u$ is harmonic with $u(0)=0$ and 
$-H\leq u(\theta)\leq H$ hold for all $\theta$.
This gives
\[ 
\int_a^b\, u(\theta)\,d\theta\geq  -2\pi H
\] 
for all intervals $(a,b)($ on the unit circle
and from this  the reader can check  that thr integral over
$-\xi<\phi<\xi)$ of the first two term in (1)
is bounded below by
$-4\pi H$ for each $0<\xi\leq \pi$.

\bigskip

\noindent
From the above
it follows that
\[
\frac{4}{\lambda}\cdot \mathcal C\bigl[v(\xi+\theta)-v(-\xi+\theta)\bigr ]
\geq -4\pi H-\frac{4K\pi\mathcal C}{\lambda^2})
\tag{8}
\]

\noindent
Since 
$v$ is $2\pi$-periodic we see that (8) gives
\[
v(2\kappa+\theta)-v( \theta)\geq
-\pi\cdot (\lambda\cdot H+
\frac{K\mathcal C}{\lambda})\quad\colon\,
0\leq\kappa\leq 2\pi
\tag{9}
\]
Next, since  $v(0)=0$ and $v$ is harmonic
the boundary value function $v(\theta)$ has at least one zero $\kappa$
and with $\theta=0$ in (9) we get
\[
v(1)\leq \pi\cdot (\lambda\cdot H+
\frac{K\mathcal C}{\lambda})\tag{11}
\]



\noindent
{\bf{12. The  choice of $\lambda$.}}
Above (11) hold for all $\lambda>1/2$.




and we choose $\lambda$ to minimize
\[
K\cdot \frac{\pi}{\lambda}+ \frac{4}{\lambda}\cdot k\cdot H
\]
It means that we take
$\lambda= \sqrt{\frac{Kk}{\pi H}}$ and
(7) gives the inequality
\[
v^*(\xi-\frac{\pi}{2\lambda})-
v^*(-\xi+\frac{\pi}{2\lambda})\geq
-2\pi\cdot \sqrt{\frac{\pi}{k}HK}\tag{8}
\]
\medskip

\noindent
Since  (8) hold for all $\xi$ and 
$v^*$ is $2\pi$-periodic we obtain
\[
v^*(2\kappa+\xi)-v^*( \xi)\geq
-2\pi\cdot \sqrt{\frac{\pi}{k}HK}\quad\forall\,\,
0\leq \xi,\kappa\leq 2\pi
\tag{9}
\]
Finally, since $v(0)=0$ and $v$ is harmonic
the boundary value function $v^*$ has at least one zero $\xi_0$
and we  can  choose $\kappa$ so that
\[
v^*(2\kappa+\xi_0)= \min_\theta\,V^*(\theta)
\]
 Then (9) implies that
 the minimum of $v^*$ is
 $\geq -2\pi\cdot \sqrt{\frac{\pi}{k}HK}$. In  the same way the
 reader can verify that the maximum of $v^*$ cannot exceed
 $2\pi\cdot \sqrt{\frac{\pi}{k}HK}$.
Hence (*) in Theorem 14.1 holds
with
\[
C=2\pi\cdot \sqrt{\frac{\pi}{k}}\tag{10}
\]
where $k$ is the constant from Exercise 4.


\bigskip




\centerline {\bf{14.2 Applications to zeros of polynomials.}}
\medskip




\noindent
Let $n\geq 1$ and consider a polynomial 
\[
p(z)=\prod\, (1-ze^{-i\theta_\nu})
\]
where $\{\theta_\nu\}$ is some $n$-tuple 
in the periodic  interval $[0,2\pi]$.
Let $(\alpha,\beta)$ be an interval on the unit circle.
Denote by $N(\alpha,\beta)$ the number
of $\theta_\nu$ satisfying
\[
\alpha<\theta_\nu<\beta
\]
and  $|p|_D$ is  the maximun norm of
$p$ over the unit disc.

\medskip

\noindent
{\bf{14.3 Theorem}}. \emph{With the same absolute constant as in Theorem 14.1 one has}
\[
\bigl[ \frac{N(\alpha,\beta)}{n}-\frac{\beta-\alpha}{2\pi}\bigr|\leq
C\cdot \sqrt{n\cdot \log |p|_D}
\]
\medskip


\noindent
\emph{Proof.}
Consider  the
harmonic function $u(z)$ in the unit disc defined by
\[
 u(z)=\frac{1}{\pi}\log\, |p(z)|=
 \frac{1}{\pi}\cdot \sum\, \log\,|1-ze^{-i\theta_\nu}|
\]
It follows that
the conjugate harmonic function becomes
\[ 
v(z)= \frac{1}{\pi}\cdot \sum\, \arg\,(1-z\cdot e^{-i\theta_\nu})
\]
From this the reader can verify  the inequality
\[
\frac{\partial v}{\partial\theta} (re^{i\theta})\leq
\frac{n}{2\pi}\quad\colon\, 0<r<1
\]

\noindent 
From the above  Theorem 14.1 gives
\[
 \max_\theta\, v(\theta) \leq C\sqrt{\frac{n}{2\pi}\cdot \log\, |p|_D}
 =
\sqrt{ \frac{2\pi}{k}}\cdot \sqrt{n\cdot  \log\, |p|_D}
\]
where $k$ is Catalani's constant from Exercise 4.
 
 
 \bigskip
 
 NOW DONE by generalformula !


\bigskip

\centerline {\bf{14.4 Schur's inequality.}}
\bigskip

 \noindent
 A  polynomial $P(z)$ of degree $n$ with constant term $a_0\neq 0$ can be written
as
\[ 
P(z)= a_0\cdot \prod\,(1-\frac{z}{\alpha_k})
\]
which entails that the absolute value of coefficient $a_n$ of $z^ n$ becomes
\[ 
|a_n|= \frac{|a_0|}{\prod\, |\alpha_k|}\tag{1}
\]
Put  $\alpha_k= \rho_k\cdot e^{i\theta_k}$
and set
\[ 
p(z)= \prod\, (1-e^{-i\theta_k}z)
\]
\medskip

\noindent
{\bf{14.5 Theorem.}}
\emph{One has the inequality}
\[
|p|_D\leq \frac{|P|_D}{\sqrt{|a_0a_n|}}
\]
\medskip

\noindent
\emph{Proof.}
For each $k$ one we set $|\alpha_k|= r_k$ and notice that
\[
r_k\cdot |1-\frac{e^{i\theta}}{\alpha_k}|^2=
r_k+\frac{1}{r_k}-2\cos(\theta-\theta_k)\geq 2-
2\cos(\theta-\theta_k)= |1-e^{i(\theta-\theta_k)}|^2
\]
This holds for each $\theta$
we choose $\theta$
where $|p|$ takes its maximum and conclude that
\[
|p|_D^2\leq \frac{\prod\, r_k}{|a_0|^2}\cdot |P|^2_D
\]
Taking the square root and using (1)  above we get Theorem 14.5
\bigskip


\noindent
{\bf{14.6 Carlson's formula.}}
Studies of zeros of polynomials, and more generally 
of analytic functions, in sectors
were  treated by F. Carlson in the article
\emph{Sur quelques suites de polynomes}.
We present a specific formula by Carlson.
Let $P(z)$ be a polynomial of some degree $n$
where  $P(x)\neq 0$ for every real $x\leq 0$.
The argument of each root $\alpha_\nu$ of $P$
is taken in the interval $(-\pi,\pi)$.
If $0<\phi<\pi$
we set
\[ 
J(\phi) =\sum\, (\phi-|\arg\alpha_\nu)|
\] 
where the sum is taken over roots of $P$ with their arguments in
$(-\phi,\phi)$. 

\medskip

\noindent
{\bf{14.6.1 Theorem.}}
\emph{For each $\phi$ one has the equality}

\[
J(\phi)= \frac{n\phi^2}{2\pi}+
 \frac{1}{2\pi}\int_0^\infty\,\frac{\log |P(re^{i\phi})|\cdot 
\log |P(re^{-i\phi})|}{|\log P(r)|^2}\, \frac{dr}{r}
\]
\medskip

\noindent
\emph{Proof}
By a factorisation of $P$
the proof is reduced to the case $n=1$ with
$P(z)=1-\frac{1}{\alpha}$ for some
non-zero complex number $\alpha$ and here the verification is left 
as an exercise to the reader.
\bigskip

\noindent
The formula above is  special and yet instructive.
Let us  finally mention
that 
one can study distributions of zeros for Dirichlet series and
exponential polynomials. This requires a further
analysis and will not be exposed here.
The reader may consult the cited
article by Ganelis for results about
complex zeros of
exponential polynomials.





\newpage

\centerline
{\bf{G. Beurling's  minimum principle for positive harmonic functions}}
\bigskip


\noindent
{\bf{Introduction.}}
We expose a result  from the article [Beurling:Ann.sci, Fennica].
 Let $\Omega$ be a simply connected
domain.
Let $g(z,\zeta)$ be the Green function for $\Omega$.
If
$p\in\partial\Omega$
a  Martin function with respect to $p$ 
is a positive harmonic function
$\phi$ in $\Omega$ such that
\[ 
\lim_{z\to q}\,\phi(z)=0\quad\colon\,\forall\,\, q\in\partial\Omega\setminus \{p\}
\]
The class of these Martin functions is denoted by
$\mathcal M(p)$.
Following  Beurling  we give

\medskip

\noindent
{\bf{15.0 Definition.}}
\emph{
A sequence $\mathcal S=\{ z_n\}$  in
$\Omega$ which convergs to the boundary point $p$
is an equivalence sequence 
at $p$ if the following implication
hold for every positive harmonic function $u$ in $D$,
every real $\lambda>0$ and each  $\phi\in \mathcal M(p)$}
\[
u-\lambda\cdot \phi\bigl| S\geq 0\implies u\geq \lambda\cdot \phi \quad\text{holds in the whole 
domain}\,\,\Omega
\]
\medskip



\noindent
{\bf{15.1 Theorem.}}
\emph{A sequence $\mathcal S=\{z_n\}$ which converges to $p$
is an equivalence at $p$
if and only if it constains a subsequence
$\{\xi_k= z_{n_k}\}$ such that}
\[
\sup_{k\neq j}\, g(\xi_j,\xi_k)<\infty\quad\text{and}\quad
\sum_{k=1}^\infty\, g(z,\xi_k)\cdot \phi(\xi_k)= +\infty
\quad\colon\, z\in\Omega
\]
\medskip


\noindent
{\bf{Remark.}}
The necessity in Theorem 15.1  proved rather easily. See § xx below.
From now on
we treat   the non-trivial part, i.e.we prove  that the two conditions in Theorem 15.1
entail that $\mathcal S$ is an equivalence at $p$.
By Riemann's mapping theorem it suffices to prove this sufficiency
when
$\Omega$ is the unit disc $D$.
Since every positive harmonic function $u$ in $D$
is the Poisson extension of a non-negative Riesz measure on $T$,
it follows 
that every  $\phi\in \mathcal M(p)$
is 
the
Poisson extension of the unit point mass at $p$ times a positive constant
$\lambda$, i.e. of the form
\[
\phi_\lambda(z)= \frac{\lambda}{2\pi}\cdot \frac{1-|z|^2}{|1-z|^2}
\]
where the mean-value property gives $\phi_\lambda (0)=\lambda$.
Moreover, if $u$
is a positive harmonic function
given by  the Poisson extension $P_\mu$ of some 
non-negative Riesz measure $\mu$ in $D$.
then 
the inequality $P_\mu\geq \phi_\lambda $
holds everywhere in   $D$ if and only if
the measure
$\mu$ has
an atom at $z=1$ of mass $\geq \lambda $.
Up to scaling it suffices to consider the
case $\lambda=1$ and hence
$\mathcal S$ is an equivalence sequence if 
and only if the following hold for 
every
non-negative Riesz measure on $T$:
\[
P_\mu(z_n)\geq \phi_1(z_n)\quad\colon\, n=1,2,\ldots\implies
\mu(\{1\})\geq 1\tag{* }
\]

\noindent
To prove (*) we  prefer to work in
the upper half-plane  where  $p$ is taken as $\infty$. Here we get 
Martin function $\phi(x,y)= y$ and 
Green's  function is
\[ 
g(\zeta,z)=\log\, \frac{|z-\bar\zeta|}{|z-\zeta)}
\]
When $z=re^{i\theta}$
where $r$ is large and $0<\theta<\pi$
one has
\[ 
\frac{|re^{i\theta}+i|^2}{|re^{i\theta}-i|^2}
=\frac{r^2+1+2r\sin\theta}{ r^2+1-2r\sin\theta}
\]
It follows that
\[
g(i,re^{i\theta})=
\frac{2\sin\,\theta}{r}+O(r^{-2})
\]

\noindent
in polar coordinates we write
$\{\zeta_k=r_ke^{i\theta_k}\}$ }
where $\{0<\theta_k=\arg \xi_k<\pi\}$
and from the above it is clear that
the  two conditions in Theorem 15.1 are  equivalent to
\[
\inf_{j\neq k}\, \frac{|\xi_j-\xi_k|}
{|\xi_j-\bar \xi_k|}
\quad\colon\quad 
\sum_{k=1}^\infty\, \sin^2\,\theta_k=+\infty \tag{**}
\]


\bigskip


\noindent
At this stage
we need a result  which has independent interest. 
In the final part of the proof of Theorem 15.2
below we
derive the
sufficiency in
Theorem 15.1.



\medskip



\noindent
{\bf{15.2 Theorem.}}\emph{
For each positive harmonic  function $u(x,y)$  in $U_+$
we put}
\[
E_u=\{ x+iy\in U_+\quad\colon\, u(x,y)\geq y\}
\]
\emph{Then one has the implication}
\[
U_+\setminus E_u\neq\emptyset\implies
\int_{E_u}\,\frac{dxdy}{1+x^2+y^2}<\infty\tag{15.2}
\]
\medskip




\noindent{\emph{Proof}.
The impliction (15.2) is obvious
when
$u(x,y)=ay$ for some positive real number $a$, i.e.
regard the cases $a<1$ and $a\geq 1$ separately.
From now on we assume that
$u(x,y)$ is not a linear function of $y$ and the
Harnack-Hopf inequality from § XX gives
the strict inequality
\[ 
\frac{\partial u}{\partial y}(x,y)<\frac{u(x,y)}{y}
\quad\colon\, (x,y)\in U_+\tag{1}
\]
\medskip

\noindent
Set $u_*=y-u$ which entails that
\[ 
\{u_*>0\}=U_+\setminus E_u\tag{2}
\]

\medskip

\noindent
\emph {3. A simply connected domain.}
Assume that the set $U_+\setminus E_u$ is non-emtpy and let
$\Omega$ be  a  connected component of this open set.
Replacing $u$ by the harmonic
function $u(x+a,y)$ for a suitable 
real $a$
we may assume that
$\Omega$ contains a point on the imaginary axis and after a scaling
that $i\in\Omega$.
Next, (1) gives
\[ 
\frac{\partial u_*}{\partial y}=1-\frac{\partial u}{\partial y}
>1-\frac{u}{y}\tag{4}
\]
Starting at a point $(x,y)\in\Omega$ it follows that
$s\mapsto u_*(x,y+is)$ increases strictly  on $\{s\geq 0\}$ and
hence the open set
$\Omega$ is placed above a graph, i.e. there exists an interval $(a,b)$
on the real $x$-axis and a non-negative 
continuous function $g(x)$ on $(a,b)$ such that
\[ 
\Omega=\{ (x,y)\,\colon a<x<b\,\,\colon\,\, y>g(x)\}\tag{5}
\]
In (5)
it  may occur that the interval $(a,b)$
is unbounded and may even be
the whole $x$-axis in which   case $\Omega$ is the sole component of
$U_+\setminus E_u$. In any case, since $i\in\Omega$
one has
$a<0<b$
and $\Omega$ contains
the the set $\{ai\colon\, a\geq 1\}$.
Next, for each $r>2$ we put
\[ 
C_r=U_+\cap \{|z+i|<r\}\tag{6}
\]
Notice that
$C_r$ contains the point $(r-1)i$
which also belongs to $\Omega$.
Denote by  $\gamma_r$ be the largest open interval on the
circle $\{|z+i|= r$ which contains 
$(r-1)i$ and at the same time is 
contained in $\partial\Omega$.
With the aid of a figure it is clear that the
set $\Omega _r= \Omega\cap C_r$ 
is simply connected where 
$\gamma_r$ is a part of
$\partial  D_r$ and   $u_*=0$ on
$\partial D_r\setminus \gamma_r$.
\medskip



\noindent{\emph{ The use of harmonic measure.}}
Let $h_r(z)$ be the harmonic function in
$\Omega_r$ which is 1 on
$\gamma_r$ and zero on the rest of the boundary.
By the above and the maximum principle for harmonic functions
we have the inequality
\[ 
u_*(i)\leq h_r(i)\cdot \max_{z\in\partial D_r} u_*(z)\leq r\tag{7}
\]
where the last inequality follows since
$u_*(x,y)\leq y\leq  r$.
To  estimate  the function $h_r(z)$ with respect to  $r$ and $z$
we  use
the harmonic function
\[
\Psi(z)= \log\, \bigl|\frac{z+i}{2i}\bigr |\implies
|\nabla(\Psi)|^2=\Psi_x^2+\Psi_y^2=\frac{1}{|z+i|^2}\tag{8}
\]
Set
\[ 
m(r)=
\frac{1}{\pi}\,  \iint_{E_u\cap C_r}\,|\nabla(\Psi)|^2\, dxdy=
\frac{1}{\pi}\,  \iint_{E_u\cap C_r}\,\frac{1}{|z+i|^2}|\, dxdy\tag{9}
\]
Notice  that
\[
\frac{1}{\pi}\,  \iint_{C_r}\,\frac{1}{|z+i|^2}|\, dxdy<\log r\tag{10}
\]
Together (9-10) give the inequality
\[
\frac{1}{\pi}\,  \iint_{\Omega_r}\,|\nabla(\Psi)|^2\, dxdy<
\log r-m(r)\tag{11}
\]


\noindent
Next, we notice that
 \[ 
 \Psi(z)= \log r-\log 2\quad\text{on}\quad \gamma_r\quad\text{and}\quad
 \Psi(i)=0\tag{12}
 \] 


\noindent
Now we can apply the general inequality from § XX in [Beurling-Special Topics]
and conclude that (11-12) 
give
the inequality
 \[ 
 h_r(i)\leq e^{-\frac{\pi L^2}{A}} \quad\text{where}\quad
 L=\log r-\log 2 \tag{13}
\]


\noindent
Next, the reader may verify
that there exists a constant $C$
which is independent of $r\geq 2$ such that
\[
 \frac{\pi L^2}{A}\geq \frac{\lg r-\log 2)^2}{\log r-\log m(r)}
 \geq \log r-2\log 2+m(r)\cdot \bigl[1-\frac{C}{\log r}]\tag{14}
 \]
 \medskip
 
 \noindent
Then (13-14)
gives a constant $C_1$ such that
\[
h_r(i)\leq  e^{-\frac{\pi L^2}{A}}\leq C_1\cdot \frac{1}{r}\cdot e^{-m(r)}
\quad\colon\, r\geq 2\tag{15}
\]

\noindent
Then (7) and  (15) give
\[ 
u_*(i)\leq C_1\cdot \cdot e^{-m(r)}\tag{*}
\]

\medskip

\noindent
This inequality hold for all $r>2$ and since
$u_*(i)>0$
there must exist a finite limit
\[ 
\lim_{r\to\infty} m(r)=m^*\tag{**}
\]
The requested implication in Theorem 15.2
follows since  (9)  this means that
\[
\iint_{E_u}\, \frac{1}{|z+i|^2}\, dxdy=\lim_{r\to\infty} m(r)
\]


\newpage

\centerline
{\bf{H. An $L^1$-inequality for
inverse Fourier transforms.}}

\bigskip

\noindent
Theorem 15.1 below is due to Beurling in [Beurling].
Let $g(t)$ be a function defined on $t\geq 0$
where the inverse Fourier transform of $tg(t)$ is integrable, i.e.
the function defined on the $x$\vvv axis by
\[  
f(x)=\int\uuu 0^\infty e^{itx}\cdot tg(t)\, dt\tag{*}
\]
belongs to $L^1({\bf{R}})$.
\medskip

\noindent
{\bf{15.1 Theorem.}}
\emph{When $f\in L^1({\bf{R}})$ it follows that
$g(t)$ is integrable and one has the inequality}
\[
\int\uuu 0^\infty\, |g(t)|\, dt\leq \frac{1}{2}
\int\uuu {\vvv \infty}^\infty\, |f(x)|\, dx
\]
\medskip

\noindent
\emph{Proof.}
Since (*) is taken over $t\geq 0$,
$f(x)$ is the boundary value function of
the analytic function
defined in $\mathfrak{Im}(z)>0$ by
\[
f(z)=\int\uuu 0^\infty e^{itz}\cdot tg(t)\cdot dt\tag{1}
\]
We  first prove the inequality in Theorem 15.1 when
$f(z)$ is zero-free in the upper halfplane
and consider the normalised situation where the $L^1$\vvv integral of $|f(x)|$ is one.
Now  the complex square root of $f(z)$  exists 
in $\mathfrak{Im}(z)>0$
and gives
an analytic function $F(z)$ such that   $F^2=f$.
Since  $|F(x)|^2=|f(x)|$ it follows that $F$ belongs to the
Hardy space $H^2({\bf{R}})$ and
Plancherel's theorem gives a function $h(t)$ on $t\geq 0$ where
\[ 
F(z)=\int\uuu 0^\infty \, e^{itz}\cdot h(t) dt\tag{2}
\]
Parseval's equality gives 
\[
1=\int\, |F(x)|^2\, dx=2\pi\cdot \int\uuu 0^\infty\, |h(t)|^2\, dt\tag{*}
\]
The Fourier transform of the convolution $h*h$
is equal to $F^2(x)= f(x)$. This gives
\[ 
t\cdot g(t)=\int\uuu 0^t\, h(t\vvv s)h(s)\, ds\implies
|t\cdot g(t)|\leq H(t)=\int\uuu 0^t\, |h(t\vvv s)|\cdot |h(s)|\, ds\tag{**}
\]
Put
\[ 
F\uuu *(x)=\int\uuu 0^\infty \, e^{itz}\cdot |h(t)| \,dt\tag{4}
\]
Parseval's formula applied to the pair $|h|$ and $F\uuu *$ gives
\[
\int\, |F^2(x)|\,dx=2\pi\cdot \int\uuu 0^\infty\, |h^2(t)|\, dt
\]
We conclude that the $L^2$\vvv norm of $F^*$ also is one
and here
\[
F\uuu *(x)^2= \int\uuu 0^\infty \, e^{itz}\cdot H(t)\, dt\tag{5}
\]
At this stage we use a result from XXX which shows that the function
\[ 
\theta\mapsto 
\log\, \bigl[\int\uuu 0^\infty\, |F\uuu*(re^{i\theta})|^2\cdot dr\,\bigr ]
\] 
is a convex function of $\theta$
where $\vvv \pi\leq\theta\leq 0$.
Apply this when
$\theta=\pi/2$ with   end\vvv values 0 and $\pi$.
This gives
\[
\int\uuu 0^\infty\, |F\uuu*(iy)|^2\cdot dy\leq
\sqrt{\int\uuu {\vvv\infty}^0\, |F\uuu*(x)|^2\cdot dx}
\cdot 
\sqrt{\int\uuu 0^\infty\, |F\uuu*(x)|^2\cdot dx}
\]
Since $x\mapsto |F\uuu *(x)|$ is an even function of
$x$ the equality in (*) entails
that the product above  is equal to one.
Hence we obtain:
\[
\int\uuu 0^\infty\,\bigl[\int\uuu 0^\infty\, e^{\vvv ty}\cdot H(t)\cdot dt\bigr ]
\cdot dy\leq \frac{1}{2}
\]
Integration by parts shows that
the left hand side is equal to 
\[
\int\uuu 0^\infty\, \frac{H(t)}{t}\cdot dt
\]
Finally, by (**) 
$|g(t)|\leq \frac{H(t)}{t}$ and hence  the $L^1$\vvv norm of
$g$ is bounded by $\frac{1}{2}$ as requested.
\bigskip

\noindent
\emph{Removing zeros.}
If $f$ is not zero\vvv free we let $B(z)$ be the Blaschke product of its zeros
and write
\[ 
f=B(z)\phi(z)
\] 
Here $\phi $ is zero\vvv free
and we do not change the $L^1$\vvv norm on the $x$\vvv line since
$|B(x)|=1$ holds almost everywhere.
Notice that we can write

\[ 
f=\phi\bigl(\frac{1+B}{2}\bigr)^2+
\phi\bigl(\frac{1\vvv B}{2}\bigr)^2=
F\uuu 1^2\vvv F\uuu 2^2
\]
where $F\uuu 1$ and $F\uuu 2$ as  above are zero\vvv free in
the Hardy space $H^2$.
Since we have
\[
\bigl|\frac{1+B}{2}\bigr|^2+
\bigl|\frac{1\vvv B}{2}\bigr|^2\leq 1
\]
it follows that
\[
|F\uuu1|^2+|F\uuu 2|^2\leq|\phi|
\]
Now the established  zero\vvv free case  gives
the inequality in
Theorem 15.1












\newpage


\centerline{\bf{I. On functions with spectral gap}}
\bigskip

\noindent
{\bf{Introduction.}}
A fore\vvv runner to distribution theory 
appears in work by Beurling
where spectral gaps
of functions $f$
on the real $x$\vvv line are analyzed.
We expose a result  from a seminar
by Beurling at  at Uppsala University
in March 1942.
\medskip





\medskip

\noindent
{\bf{16.1 Theorem.}}
\emph{Let $f(x)$ be a bounded and continuous function on
the real $x$\vvv line such that $\widehat{f}(\xi)$
is zero on
$\{-1\leq\xi\leq1\}$
and}
\[ 
f(x+h)\vvv f(x)\leq h
\] 
\emph{hold for all $h>0$ and every $x$. Then its maximum norm is
at most $\pi$.}
\medskip


\noindent
The proof is postponed until
§ 16.3. First we
establish some preliminary results where an essential ingredient
is the
entire function:
\[ 
2\cdot H(z)=\bigl(2\sin \frac{z}{2}\bigr)^2\cdot
\bigl[ \sum\uuu{n=1}^\infty\, \frac{1}{(z\vvv 2\pi n)^2}
\vvv \sum\uuu{n=0}^\infty\, \frac{1}{(z+ 2\pi n)^2}+ \frac{1}{\pi z}\bigr]
\]



\noindent
{\bf{A. Exercise.}}
Verify the identity
\[
\frac{1}{(2\sin \frac{z}{2}\bigr)^2}=
 \sum\uuu{\vvv \infty}^\infty\, \frac{1}{(z\vvv 2\pi n)^2}\tag{*}
\]
The hint is to consider the meromorphic function
\[
\phi(z)=\frac{\cos z/2}{2\sin z/2}
\]
It has simple poles at $\{2\pi n\}$ where $n$ runs over all integers
and we notice that
\[
\psi(z)= \phi(z)\vvv  \sum\uuu{\vvv \infty}^\infty\, \frac{1}{z\vvv 2\pi n}
\] 
is entire. Hence the  derivative 
$\psi'(z)$ is also entire. Since 
$\cos^2\,z/2+\sin^2\, z/2=1$ we get:
\[ 
\psi'(z)=\vvv \frac{1}{(2\sin \frac{z}{2}\bigr)^2}+
\sum\uuu{\vvv \infty}^\infty\, \frac{1}{(z\vvv 2\pi n)^2}
\]
At the same time the reader may verify that the right hand side is
bounded so this entire function must be identically zero which gives (*).

\bigskip

\noindent
{\bf{B. Exercise.}}
Use (*) to show that if $x>0$ then
\[
2H(x)=1\vvv  
\bigl (2\sin \frac{x}{2}\bigr)^2\cdot
\bigr[\sum\uuu{n=1}^\infty\, \frac{2}{(x+2\pi n)^2}+\frac{1}{x^2}\vvv
\frac{1}{\pi x}\bigr]
\]


\noindent
{\bf{The $\theta$\vvv function}}.
It is defined for all real $x$ by:
\[ 
\theta(x)=\frac{1}{2}\cdot \text{sign} (x)\vvv H(x)
\]
where
$\text{sign} (x)$ is $\vvv 1$ if $x<0$ and +1 if $x>0$.
\medskip

\noindent
{\bf{16.2 Proposition.}}
\emph{The $\theta$\vvv function is everywhere $\geq 0$ and}
\[
\int\uuu{\vvv\infty}^\infty \theta(x)\cdot dx=\pi\tag{*}
\]


\noindent
\emph{Proof.}
Exercise B gives for every $x>0$:
\[
\theta(x)=  \frac{1}{2}\bigl (2\sin \frac{x}{2}\bigr)^2\cdot
\bigr[\sum\uuu{n=1}^\infty\, \frac{2}{(x+2\pi n)^2}+ \frac{1}{x^2}\vvv
\frac{1}{\pi x}\bigr]
\]
Next,  notice the two inequalities
\[
\sum\uuu{n=1}^\infty\, \frac{2}{(x+2\pi n)^2}\leq
\int\uuu 0^\infty\,
\frac{2dt}{(x+2\pi t)^2}=\frac{1}{\pi x}\tag{1}
\]
\[
\sum\uuu{n=1}^\infty\, \frac{2}{(x+2\pi n)^2}+\frac{1}{x^2}\geq
\int\uuu 0^\infty\,
\frac{2dt}{(x+2\pi t)^2}=\frac{1}{\pi x}\tag{2}
\]
Here (2) entails that $\theta(x)\geq 0$ on $x>0$ and
(1) obviously implies that the integral
\[
\int\uuu 0^\infty\,\theta(x)\cdot dx<\infty\tag{3}
\]
We leave as an exercise to the reader to verify the similar result for 
$x<0$, i.e. that
$\theta(x)\geq 0$ hold for $x<0$ and that
its integral over $(\vvv \infty,0)$ is  finite.
To establish the equality
(*) in Proposition 16.2 we notice that
the function
\[
\text{sign}(x)
+(2\sin\frac{x}{2})^2\cdot \frac{1}{\pi x}
\]
is odd so its integral over the real line is zero.
The reader may also check the equation
\[ 
\int\uuu{\vvv \infty}\, 
\frac{(\sin \frac{x}{2})^2}{(x\vvv 2\pi n)^2}\cdot dx=
\int\uuu{\vvv \infty}\, 
\frac{(\sin \frac{x}{2})^2}{(x+2\pi n)^2}\cdot dx
\quad\text{for every}\quad  n\geq 1
\] 
and then verify the equality
\[
\int\uuu{\vvv\infty}^\infty \theta(x)\cdot dx=
\int\uuu 0^\infty\, 
\frac{(2\sin \frac{x}{2})^2}{x^2}\cdot dx
\]
where  residue calculus shows that the last integral is $\pi$.
\bigskip


\centerline{\emph{16.3 Proof of Theorem 16.1}}
\bigskip

\noindent
Let  $\mathcal H$ be the Heaviside function
which is one on $x>0$ and zero on
$\{(x\leq 0\}$.
Recall that the distribution derivative
$\partial_x(\mathcal H)=\delta_0$.
Regarding $f$ as a temperate distribution
this gives the equation
\[
f=\partial_x(f\ast( \mathcal H\vvv \frac{1}{2}))\tag{i}
\]
As explained in § XX the Fourier transform $\widehat H(\xi)$
is supported by $[\vvv 1,1]$.
Since the support of $\widehat f$
is disjoint from $[\vvv 1,1]$
it follows that $f\ast H=0$ and hence  the distribution derivative 
\[
\partial_x(f*H)=0\tag{ii}
\]
Next,
notice that
\[
\frac{1}{2}\cdot \text{sign}(x)=\mathcal H\vvv \frac{1}{2}\tag{iii}
\]

\noindent
The construction of $\theta$ in (B)
and (i-iii) therefore give 
\[
f=\partial_x(f\ast\theta)
\]
This  means that one has
the equation
\[ 
f(x)=\int\uuu{\vvv \infty}^\infty \, \theta(x\vvv y)\cdot f'(y)\cdot dy\tag{iv}
\]
By assumption $f'(y)\leq 1$ for all $y$
and since $\theta\geq 0$ 
the right hand side is bounded above by
\[
\int\uuu{\vvv \infty}^\infty \, \theta(x\vvv y)\cdot dy=\pi \implies
f(x)\leq \pi
\] 
To get $f(x)\geq \vvv \pi$ we consider the function
$g(x)=\vvv f(\vvv x)$ which
again is a bounded continuous function
and the reader easily verifies that $g(x+h)\vvv g(x)\leq h$
for all $h>0$. Moreover, $\widehat g(\xi)$ is minus the complex conjugate
of $\widehat f$ so $g$ has the same spectral gap as $f$ and just as above 
we get  the upper bound
$g(x)\leq \pi$ which entails
that $f(x)\geq \vvv \pi$ hold for all $x$. Hence  
its maximum norm is bounded by $\pi$ which finishes the proof of
Theorem 16.1
\medskip


\noindent
{\bf{16.4 Question.}}
Investigate if Theorem 16.1 is sharp, i.e. try to 
use the proof above in order to construct
$f$
whose   maximum norm is close to $\pi$.












\newpage


\centerline{\bf{J. A theorem about limits}}
\medskip

\noindent
The space of complex\vvv valued bounded and uniformly continuous functions
on the real $x$\vvv line is  
a Banach space $\mathcal C\uuu *$
where we use the maximum norm  over the whole line.
A subspace arises as follows: On the  $\xi$\vvv line we have the space
$\mathfrak{M}$
of complex Riesz measures $\gamma$ with a finite total variation
and 
to each $\gamma$ we get the function
\[
\mathcal F\uuu\gamma(x)=\int\uuu{\vvv \infty}^\infty\, e^{ix\xi}\cdot d\gamma(\xi)
\]
It is clear that $\mathcal F\uuu\mu$ belongs to $C\uuu *$.
Denote by $\mathcal A$ the subspace of $C\uuu *$
given by $\mathcal F\uuu\gamma$-functions as $\gamma $ varies over 
$\mathfrak{M}$.
Before we announce Theorem 17.1 below we recall the notion
of weak\vvv star limits in $\mathfrak{M}$.
Let $\{\mu\uuu n\}$ be a bounded sequence of Riesz measures, i.e. 
there exists a constant such that
\[ 
||\mu\uuu n||\leq M
\]
hold for all $n$.
The sequence $\{\mu\uuu n\}$
converges weakly to zero if
\[
\lim\uuu{n\to\infty}\,\int\, e^{ix\xi}\cdot d\mu\uuu n(x)=0
\] 
holds pointwise for every $\xi$.
\medskip

\noindent
{\bf{17.1 Theorem.}} \emph{A function $\psi\in C\uuu *$ belongs to the closure of
$\mathcal A$ if and only if}
\[
\lim\uuu{n\to\infty}\,\int\, \psi(x)\cdot d\mu\uuu n(x)=0\tag{*}
\] 
\emph{whenever $\{\mu\uuu n\}$ is a sequence in $\mathfrak{M}$
which converges weakly to zero.}
\medskip

\noindent
The sufficiency part is easy.
For suppose that $\psi$ belongs to the closure of $\mathcal A$
and let $\{\mu_n\}$ converge weakly to zero.
Since the total variations in this  weakly convergent sequence of measures 
is uniformly bounded, it suffices to show that
(*) holds when $\psi\in\mathcal A$.
So let $\psi=\mathcal F\uuu\gamma$ for some
$\gamma\in\mathfrak{M}$.
Since $\gamma$ and $\mu\uuu n$ both have a finite total variation
it is clear that
\[
 \int \psi(x)\cdot d\mu\uuu n(x)=
 \int\, \mathcal F\uuu{\mu\uuu n}(\xi)\cdot d\gamma(\xi)
 \]
Here $\{\mathcal F\uuu{\mu\uuu n}(\xi)\}$ is a sequence 
of uniformly bounded
continuous functions on the real $\xi$\vvv line which by assumption converges
pointwise to zero. Since the Riesz measure $\gamma$ has a finite total variation,
the Borel\vvv Riesz convergence result in [Measure] shows that
(*) tends to zero with $n$.
\bigskip

\centerline{\emph{Proof of necessity.}}
\medskip

\noindent
There remains to show that if $\psi\in C\uuu*$ is outside the closure of
$\mathcal A$, then there exists a
sequence $\{\mu\uuu n\}$ which converges weakly to zero while
$\{\int\,\psi\cdot d\mu\uuu n\}$ stay away from zero.
To attain this we shall consider a class of variational problem  and
extract a certain sequence of measures
which does the job.
\medskip

\noindent
{\bf{A class of  variational integrals.}}
Let $a,b,s$ be positive numbers and $q>2$.
With $p$ chosen so that
\[ 
\frac{1}{p}+\frac{1}{q}=1
\]
we have the space $L^p[\vvv a,a]$
where $[\vvv a,a]$ is an interval on the $\xi$\vvv line.
To each function $g(\xi)\in L^p[\vvv a,a]$
we get the function 
\[
 \mathcal F\uuu g(x)=
\int e^{ix\xi}\cdot g(\xi)\cdot d\xi
\]
This gives a continuous function which is  
restricted to $[\vvv b,b]$
and we set
\[
||\psi\vvv \mathcal F\uuu g||\uuu q^b=
\bigl[ \int\uuu {\vvv b}^b\,
[\psi(x)\vvv \mathcal F\uuu g(x)|^q\cdot dx\,\bigr]^{1/q}
\]
where the upper index $b$ indicates that we compute a $L^q$\vvv norm on
the bounded interval $[\vvv b,b]$.
To each $g\in L^p[\vvv a,a]$ we set
\[
\mathcal J(g;q,b,a,s)=||\psi\vvv \mathcal F\uuu g||\uuu q^b+||g||\uuu p\tag{*}
\] 


\noindent
where the last term is the $L^p$\vvv norm of $g$ taken over
$[\vvv a,a]$.
Since the Banach space $L^p[\vvv a,a]$ is strictly convex
one easily verifies:
\medskip

\noindent
{\bf{17.2 Proposition.}} \emph{The variational problem where
$\mathcal J$ is minimized
over $g$ while $a,b,s$ are fixed has a unique extremal solution.}
\medskip

\noindent
{\bf{17.3 Exercise.}} Regarding infinitesmal variations via the 
classic device due to Euler and Lagrange, the reader can verify that
there exists a unique
extremal solution $g$ which satisfies
\[
||g||\uuu p)^{1\vvv p}\cdot \frac{|g(\xi)|^p}{g(\xi)}=M^{\vvv 1/p}\cdot
\int\uuu {\vvv b}^b\, e^{i\xi x}\cdot 
\frac{|\psi(x)\vvv \mathcal F\uuu g(x)|^q}{|\psi(x)\vvv \mathcal F\uuu g(x)}
\cdot dx\tag{*}
\]
where we have put
\[ 
M=\int\uuu b^b\, |\psi\vvv \mathcal F\uuu g|^q\cdot dx
\]



\medskip

\noindent
Consider the absolutely continuous
measure  on the
$x$\vvv line defined by
the density
\[ 
d\mu=M^{\vvv 1/p}\cdot 
\frac{\psi(x)\vvv \mathcal F\uuu g(x)|^q}{|\psi(x)\vvv \mathcal F\uuu g(x)}
\quad\colon\quad \vvv b\leq x\leq b
\]


\noindent
This gives
\[
\int\uuu{\vvv b}^b\, 
|d\mu(x)|=M^{\vvv 1/p}\cdot\int\uuu{\vvv b}^{b} 
|\psi(x)\vvv \mathcal F\uuu g(x)|^{q\vvv 1}
\cdot dx
\]
Hölder's inequality applied to the pair of functions
$|\psi(x)\vvv \mathcal F\uuu g(x)|^{q\vvv 1}$ and 1 on $[\vvv b,b]$
gives the inequality below for the total variation:
\[
||\mu||\leq (2b)^{1/q}\tag{**}
\]




\medskip



\noindent
{\bf{17.4 Lemma.}}
\emph{The following two formulas hold:}
\[
\int\, \psi\cdot d\mu= \mathcal J(g; q,b,a,s)
\]
\[
\int\,\mathcal F\uuu g\cdot d\mu=s\cdot ||g||\uuu p
\]


\noindent
\emph{Proof.}
To begin with we have
\[
\int\, (\psi\vvv \mathcal F\uuu g)\cdot d\mu=
M^{\vvv 1/p}\cdot \int\uuu b^b \, |\psi\vvv \mathcal F\uuu g|\cdot dx
= M^{1\vvv 1/p}\cdot M=M^{1/q}
\]
\medskip

\noindent
Next Fubini's theorem gives

\[
\int\,\mathcal F\uuu g\cdot d\mu
=\int\uuu a^a\, [\int\, e^{ix\xi}\cdot \mu(x)\,]\cdot g(\xi)\cdot d\xi
=
s\cdot \int\uuu a^a\, 
||g||\uuu p)^{1\vvv p}\cdot \frac{|g(\xi)|^p}{g(\xi)}\cdot g(\xi) d\xi
=s\cdot ||g||\uuu p
\]
This proves formula (2) and (1) follows via (i) and the equality

\[
\mathcal J(g; q,b,a,s)=M+s\cdot ||g||\uuu p
\]
\medskip

\noindent {\bf{17.5 Passage to limits.}}
Following [Beurling] we now consider   certain limits where
we first let $q\to+\infty$ and after $b\to\infty$, and finally
use pairs $a=2^m$ and $s=2^{\vvv m}$ where 
$m$ will be large positive integers.
To begin with, the measure $\mu$ depends on $q,b,a,s$
and let us denote it by $\mu\uuu q(b,a,s)$.
The uniform bound (*) from Exercise 17.3
entails that while 
$a,b,s$ are kept fixed, then there is 
a sequence 
$\{q\uuu\nu\}$ which tends to $+\infty$
and give  a weak limit measure
\[
\mu\uuu *(b,a,s)=\lim\, \mu\uuu{q\uuu\nu}(b,a,s)
\]
The extremal $g$\vvv functions depend on $q$ and are denoted by $g\uuu q$.
Their $L^q$\vvv norms remain bounded
and passing to a subsequence we get
an $L^\infty$\vvv function $g\uuu *$ on $[\vvv a,a]$
where $g\uuu{q\uuu\nu}\to g\uuu *$. Here $g\uuu *$ depends on $b,a,s$ and is
therefore indexed as  
$g\uuu *(b,a,s)$.
We have also a limit:
\[ 
\lim_{\nu\to \infty}\, \mathcal J(g\uuu g;q\uuu\nu; b,a,s)=
\mathcal J\uuu *(g\uuu *(a,b,s))
\]
Moreover
\[
\mathcal J\uuu *(g\uuu *(a,b,s))=
\max\uuu{\vvv b\leq x\leq b}\, |\psi(x)\vvv \mathcal F\uuu{g\uuu *(b,a,s)}|
+s\cdot \int\uuu{\vvv a}^a |g\uuu *(b,a,s)(\xi)|\cdot d\xi
\]
\medskip

\noindent
At this stage we use the hypothesis that $\psi$ does not belong to the closure of
$\mathcal A$ which entails that with $a$ and $s$ fixed, then
here is a constant $\rho>0$ such that
\[ 
\liminf\uuu{b\to\infty}\, 
\max\uuu{\vvv b\leq x\leq b}\, |\psi(x)\vvv \mathcal F\uuu{g\uuu *(b,a,s)}|\geq \rho
\]

\bigskip

At this stage proof is easily FINISHED.


\newpage



\centerline{\bf L. Dagerholm's system of infinite linear equations.}

\bigskip
\noindent
{\bf Introduction.}
The main issue in this section is
the construction of a unique solution to
the system
\[ 
\sum\uuu{q\neq p}\,\frac{x\uuu q}{p\vvv q}=0\tag{*}
\] 
where (*) hold for all positive integers $p$ and
$\{x\uuu q\}$ is a sequence of real numbers for which the series
\[ 
\sum\uuu{q=1}^\infty\,\frac{x\uuu q}{q}\tag{**}
\] 
is convergent. The fact that (*) has a non\vvv trivial solution is
far from evident.
Before the study of (*)  in Section 1 we
discuss a  general situation  which was described
by Carleman in his major lecture at
the international congress in Zürich 1932.
A homogeneous system of linear equations with an inifinite number
of variables
takes the form
\[
\sum_{q=1}^\infty\, c_{pq}x_q=a_p
\quad\colon\quad p=1,2,\ldots\tag{***}
\]
where $\{c_{pq}\}$ is a matrix with an infinite number of elements.
A sequence $\{x_q\}$
of complex numbers
is a solution to (***) if
the sum  in the left hand side converges for each $p$ and has  value $a_p$.
Notice that one does not
require that the series are  absolutely convergent.

\medskip

\noindent
{\bf{The generic case.}}
To every $p\geq 1$
we have the linear form $L_p$
defined on finite sequences
$\{x_1,x_2,\ldots\} $, i.e. where  $x_q=0$ when $q>>0$ by:
\[ 
L_p(x_\bullet)=\sum_{q\geq 1}\, c_{pq}\cdot x_q
\]
Follownig Carleman the generic case occurs when
$c_{1q}\neq 0$ for every $q$ and
the linear forms
$\{L_p\}_1^\infty$ are linearly independent.
The last condition means that for every positive integer
$M$ there exists a strictly increasing sequence
$q_1<\ldots <q_M$ so that the
$M\times M$-matrix with elements
$a_{p\nu}= c_{pq_\nu}$ has a non-zero determinant.

\medskip

\noindent
{\bf{The $R$-functions.}}
Assume that the system (***) is generic.
Given a sequence $\{a_p\}$ 
we seek a solution $\{x_q\}$.
The necessary and sufficient condition for
its  existence  goes as follows:
Consider
$n$-tuples of positive integers $m_1,\ldots,m_n$
where $n\geq 2$. For every such  $n$-tuple and  $1\leq k\leq n-1$
we set
\[ 
\mathcal D(k)=
\{\nu\colon\, m_1+\ldots+m_k<\nu\leq m_1+\ldots+m_{k+1}\}
\]
Next, with $M=m_1+\ldots+m_N$ we denote by
$\mathcal F(m_1,\ldots,m_n)$ the family of sequences $(x_1,\ldots,x_M)$ such that
the following inequalities hold for every $1\leq k\leq n-1$:
\[
\bigl|\sum_{q=1}^{q=\nu}\, c_{pq}x_q-a_q\bigr|\leq
\frac{1}{k}\quad\colon\,\nu\in\mathcal D(k)\quad\text{and}\quad
1\leq p\leq k
\]


\noindent
The generic assumption implies that the set $\mathcal F(m_1,\ldots,m_n)$
is non-empty provided that we start with a sufficiently large $m_1$
and for
every  such $n$-tuple we set
\[
R(m_1,\ldots,m_n)=\min\sum_{\nu=1}^{m_1}\, x_\nu^2
\]
where  the minimum is taken
over
sequences $x_1,\ldots,x_{m_1}$ which give the starting terms of some
sequence 
$x_1,\ldots,x_M\in \mathcal F(m_1,\ldots,m_n)$.
\medskip






\noindent
{\bf Theorem.} \emph{The necessary and sufficient condition in order that
(***) has a least one  solution is that there exists
a constant $K$ and  an infinite
sequence of positive integers $\mu_1,\mu_2,\ldots$ such that }
\[
R(\mu_1,\mu_2,\ldots,\mu_r)\leq K\quad \text{hold for every $r$}
\]

\medskip

\noindent
{\bf Remark.}
The reader may consult [Carleman] for  further remarks
about this result  and also comments upon
the more involved
criterion for non-generic linear systems.
From now on we  study  linear systems which arise
as follows:
Consider a rational function of two variables $x,y$:
\[
f(x,y)=\frac{a_0(x)+a_1(x)y+\ldots a_n(x)y^n}
{b_0(x)+b_1(x)y+\ldots b_m(x)y^m}
\]
Here $n$ and $m$ are positive integers and
$a_\nu(x)$ and $b_j(x)$ polynomials in $x$.
No special assumptions are imposed on these polynomials except
that $b_m(x)$ and $a_n(x)$ are not identically zero.
For example, it is not neccesary that the degree of $b_m$ is
$\geq\text{deg}(b_j)$ for all $0\leq j\leq m-1$.
\medskip

\noindent
{\bf 0.1 Proposition }\emph{ Let $b_m^{-1}(0)$ be the finite set of zeros of $b_m$.
Let $\zeta_0\in {\bf{C}}\setminus b_m^{-1}(0)$ be such that}
\[
\sum_{j=0}^{j=m}\, b_j(\zeta_0)\cdot q^j=0
\]
\emph{holds for some finite set of
positive integers, say $1\leq q_1<\ldots<q_k$.
Then there exists $\delta>0$ such that }
\[ 
\sum_{j=0}^{j=m}\, b_j(\zeta)q^j\neq 0\quad\colon
\text{for all positive integers}\,\, q\, \quad\colon\quad 
0<|\zeta-\zeta_0|<\delta
\]



\noindent
{\bf{Exercise.}}
Prove this result.

\medskip

\noindent
Next, consider the sequence of polynomials
of the complex $\zeta$-variable given by:
\[ 
B_q(\zeta)=b_0(\zeta)+b_1(\zeta)q+\ldots+b_m(\zeta)q^m\,\quad\colon
q=1,2,\ldots
\]

\medskip

\noindent
{\bf 0.2 Proposition} \emph{Put}
\[ 
W=b_m^{-1}(0)\,\bigcup_{q\geq 1}\, B_q^{-1}(0)
\]
\emph{Then $W$ is a discrete subset of ${\bf{C}}$, 
i.e its intersection with any
bounded disc is finite.}
\medskip

\noindent
{\bf{Exercise.}}
Prove this result where a hint
is 
to apply Rouche's theorem.
\medskip

\noindent
Next, put  $W^*=W\cup a_n^{-1}(0)$, i.e. add the zeros of the polynomial $a_n$
to  $W$.
\bigskip

\noindent
{\bf 0.3 Proposition.}
\emph{Let $\zeta_0\in C\setminus W^*$
and suppose that $\{x_q\}$ is a sequence such that the series}
\[ 
\sum_{q=1}^\infty\,
f(\zeta_0,q)\cdot x_q\tag{i}
\] 
\emph{is convergent. 
Then  the series}
\[
\sum_{q=1}^\infty\,
f(\zeta,q)\cdot x_q\quad\text{converges for every}\,\,\zeta\in
C\setminus W^*\tag{ii}
\] 
\emph{Moreover, the series sum is a meromorphic function of $\zeta$
whose poles are contained in $W^*$.}

\medskip

\noindent 
{\bf Remark.}
Proposition 0.3 gives a procedure to find solutions 
$\{x_q\}$ which is not the trivial null solution to a homogeneous system:
\[ 
\sum_{q\neq p}\, f(p,q)\cdot x_q=0\quad\colon\quad
p=1,2,\ldots\tag{*}
\]


\noindent
More precisely, assume that the rational function
$f(x,y)$ is such that
$f(p,q)\neq 0$ when $p$ and $q$ are distinct positive integers.
To get a solution $\{x_q\}$ to (iii)
it suffices to begin with to verify (i) in Proposition 0.3  for some
$\zeta_0$ and  then also try to find
$\{ x_q\}$
so that the meromorphic
function
\[ 
\zeta\mapsto 
\sum_{q=1}^\infty x_q\cdot f(\zeta,q)\tag{**}
\]
has zeros at every positive integer. Using this criterium for
a solution we can show the following:
\medskip

\noindent
{\bf{Theorem.}} \emph{For every complex number
$a\in{\bf{C}}\setminus(-\infty,0\,]$ the system}
\[ 
\sum\uuu{q=1}^\infty \frac{x\uuu q}{p+aq}=0
\quad\colon\quad p=1,2,\ldots
\]
\emph{has no non\vvv trivial solution $\{x\uuu q\}$.}
\bigskip

\noindent
There remains to analyze the case
when $a$ is real and $<0$. In this case
complete answers about possible  
when $f$ is the  rational function were 
established by K. Dagerholm in  his
Ph.D-thesis at Uppsala University from  1938
with
Beurling as  supervisor.
The hardest case occurs when $a=1$
which will be studied in the next section.





\bigskip





\centerline{\bf 1. The Dagerholm series.}

\bigskip
\noindent
Let $\mathcal F$ be the family
of all sequences of
real numbers $x_1,x_2,\ldots$ such that the series
\[ 
\sum_{q=1}^\infty\,\frac{x_q}{q}<\infty\tag{i}
\]
We only require that the series is convergent, i.e. it need  not be
absolutely convergent. 
\bigskip

\noindent {\bf 1.1 Theorem.} \emph{Up to a multiple with a real constant
there exists a unique
sequence $\{x_q\}$ in $\mathcal F$ such that}
\[
\sum_{q\neq p}\, \frac{x_q}{p-q}=0\quad\colon\quad p=1,2,\ldots
\]
\medskip

\noindent
The proof of  uniquenss relies upon Jensen's formula and
the solution to  a specific Wiener-Hopf
equation.
We begin to describe the strategy  of the proof.
For each $\{x_q\}\in\mathcal F$
there exists
the  meromorphic function 
\[ 
h(z)=\sum_{q=1}^\infty\,\frac{x_q}{z-q}\tag {ii}
\]
To see  that $h(z)$ is defined
we notice that if
$s_*$ is the series sum in (i) then
\[
h(z)+s_*=\sum_{q=1}^\infty\,x_q\cdot [\frac{1}{z-q}+\frac{1}{q}]=
z\cdot \sum_{q=1}^\infty\frac{x_q}{q(z-q)}\tag{iii}
\]
It is clear that 
the right hand side
is 
a meromorphic function
with poles confined to  the set of positive integers. 
Hence we obtain the 
entire function:

\[ 
H(z)=\frac{1}{\pi}\cdot \text{sin}(\pi z)\cdot h(z)
\]
\medskip

\noindent
{\bf{1.2 Proposition.}}
\emph{The following hold for each positive integer:}
\[ 
H(p)= (\vvv 1)^p\cdot x\uuu p\quad\colon 
H'(p)= (\vvv 1)^q\cdot 
\sum_{q\neq p}\, \frac{x_q}{p-q}=0
\]


\medskip



\noindent 
\emph{Proof.}
Let $p\geq 1$ be an integer. With $\zeta$ small we have
\[
H(p+\zeta)=\frac{1}{\pi}\cdot\text{sin}(\,\pi p+\pi\zeta)\cdot 
\bigl [\frac{x_p}{\zeta}+
\sum_{q\neq p}\,\frac{x_q}{p+\zeta-q}\bigr ]
\]
A series expansion of the complex sine-function at
$\pi p$ gives
\[
\frac{1}{\pi}\cdot\text{sin}(\,\pi p+\pi\zeta)=
[\zeta\cdot \text{cos}(\pi p)+O(\zeta^3)]\cdot \bigl [\frac{x_p}{\zeta}+
\sum_{q\neq p}\,\frac{x_q}{p+\zeta-q}\bigr ]
\]
Proposition 1.2  follow since
$\text{cos}\,\pi p=(-1)^p$.


\bigskip

\noindent
{\bf{Remark.}}
Proposition 1.2 shows that
$\{x_p\}$ solves the homogeneous system in Theorem 1.1 
if the complex derivative of the  entire $H$-function
has zeros on all positive
integers. This observation is the gateway towards the
proof of Dagerholm's Theorem. But let us   first  establish the uniqueness.


\bigskip

\centerline{\bf 2. Proof of uniqueness}

\bigskip

\noindent
Let   $\{x_q\}$ be a
sequence in $\mathcal F$.
From the constructions in above
it is clear that the  meromorphic function
$h(z)$ satisfies the following in the left half-plane
$\mathfrak{Re}(z)\leq 0$:
\[
\lim_{x\to -\infty}\,h(x)=0
\colon\quad
|h(x+iy)|\leq C_*\quad\colon\,x\leq 0\tag{i}
\]
where $C_*$ is a constant.
Moreover, in the right half-plane there exists  a constant $C^*$ such that
\[
|h(x+iy)|\leq C^*\cdot \frac{|x|}{1+|y|}\quad\colon\, |x-q|\geq \frac{1}{2}\,\,
\text{for all positive integers}\tag{ii}
\]

\noindent
To $h(z)$ we get the entire function $H(z)$ 
and  (i-ii) above give the two
the estimates below in the right half-plane:
\[ 
|H(x+iy)|\leq Ce^{\pi|y|}\,\,\colon\, x\leq 0\quad\colon\,\quad
|H(x+iy)|\leq C\frac{|x|}{1+|y|}\cdot e^{\pi|y|}\tag{iii}
\]
Moreover, the first limit formula in (i) gives
\[
\lim_{x\to-\infty}\, H(x)=0\tag{iv}
\]


\noindent
It is easily seen that the same upper bounds hold
for the entire function $H'(z)$ and a straightforward application
of
the  Phragmén-Lindelöf theorem 
gives:
\medskip

\noindent
{\bf 2.1 Proposition.}
\emph{The complex derivative of
$H(z)$ 
satisfies the growth condition:}
\[
\lim_{r\to\infty}\,
e^{-\pi r\cdot |\text{sin}\,\phi|}\cdot |H'(re^{i\theta}\,|=0
\quad\colon\,\text{holds uniformly when}\,\,\, 0\leq\theta\leq 2\pi
\]
\medskip

\noindent
Now we are prepared to prove the uniqueness part in Theorem 0.1.
For suppose that we have two  sequences
$\{x_q\}$ and $\{x_q^*\}$ which both give solutions to 
(*) and are not equal up to a constant multiple of each other.
The two sequences  give entire functions $H\uuu 1$ and $H\uuu 2$. Since
both are constructed via real sequences 
their  Taylor coefficients  are real and there exists 
a  linear combination
\[
G=aH\uuu 1+bH\uuu 2
\] 
where $a,b$ are real numbers and
the complex derivative
$G'(0)=0$. The hypothesis that there exists
two ${\bf{R}}$-linearly independent solutions to (*)
leads to a contradiction once we have proved the following
\medskip

\noindent
{\bf{2.2 Lemma}} \emph{The entire function $G'(z)$ is identically zero.}
\medskip

\noindent
\emph{Proof.}
To simplify notations we set
$g(z)=G'(z)$ and
consider the series expansion
\[ 
g(z)= a_pz^p+a_{p+1}z^{p+1}+\ldots
\]
where $a_p$ ia the first non-vanishing coefficient. Since $g(0)=G'(0)=0$
we have $p\geq 1$ and since
the two $x$-sequences both are solutions to
(*), the second equation  in Proposition 0.2 gives
\[ 
g(p)=0\quad\colon\, p=1,2,\ldots\tag{i}
\]

\noindent
Next, $G$ is real-valued on the $x$-axis 
and since the $H$\vvv functions are zero for every integer $\leq 0$ the
same holds for $G$.
\emph{Rolle's theorem} implies
that for every $n\geq1 $
there exists
\[ 
-n<\lambda_n<-n+1\quad\colon\, g(\lambda_n)=0\tag{i}
\]


\noindent
So if $\mathcal N$ is the counting function for the
zeros of the entire $g$-function  one has
the inequality
\[ 
\mathcal N(r)\geq [2r]\tag{iii}
\]
where $[2r]$ is the largest integer $\leq 2r$.
Next, recall that  $a_p$ is the first non-zero term in the series
expansion of $g$. Hence Jensen's formula gives:


\[
\text{log}\,|a_p|+p\cdot\log\, r+
\int_0^r\,\frac{\mathcal N(t)\cdot dt}{t}=
\frac{1}{2\pi}\int_0^{2\pi}\, \text{Log}\, |g(re^{i\theta}\,|\,\cdot d\theta
\tag{*}
\]


\noindent
Proposition 2.1 applied to $g(z)$ gives:
\[
\int_0^{2\pi}\, \text{Log}\, |g(re^{i\theta}\,|\,\cdot d\theta
=2r-m(r)\quad\text{where}\,\lim_{r\to\infty}\, m(r)=+\infty\tag{iv}
\]


\noindent
At this stage we get the contradiction 
as follows. First (iii) gives
\[
\int_0^r\,\frac{\mathcal N(t)\cdot dt}{t}
\geq 2r-\text{Log}(r)-1
\]
Now (*) and   (iii) give the inequality
\[
\text{log}\,|a_p|+p\cdot\log\, r+2r-1-\text{log}\, r\leq
2r-m(r)\quad\colon\,r\geq 1\tag{vi}
\]


\noindent
Here $p\geq 1$ which therefore would give:
\[
\text{log}\,|a_p|-1+m(r)\leq 0
\]
But this is impossible since
we have seen that
$m(r)\to+\infty$.

\bigskip

\centerline{\bf 3. Proof of existence}
\bigskip

\noindent
We start with a general construction.
Let $\phi(z)$ be analytic in the unit disc $D$ which
extends to a continuous function on
$T$ except at the point $z=1$.
We also assume that
there exists some $0<\beta<2$ and a constant $C$ such that
\[ 
|\phi(\zeta)|\leq C|1-\zeta|^{-\beta}\tag{1}
\]
This implies that
the function
\[ 
\theta\mapsto \theta\cdot \phi(e^{i\theta})
\]
is integrable on the unit circle. Hence
there exists the entire function
\[
f(z)=\frac{-i}{2\pi}\int_{-\pi}^{\pi}
e^{-i\theta z}\cdot \theta\cdot \phi(e^{i\theta})\cdot d\theta\tag{2}
\]
\medskip

\noindent 
Next, with $\epsilon>0$ small we let $\gamma_\epsilon$ be the interval of
the circle $|z-1|=\epsilon$ with  end-points at the intersection with
$|z|=1$. So on $\gamma_\epsilon$ we have 
\[
z= 1+\epsilon\cdot e^{i\theta}\quad\colon\,
-\frac{\pi}{2}+\epsilon\uuu *<\theta<\frac{\pi}{2}-\epsilon\uuu *
\]
where $\epsilon_*$ is small with $\epsilon$.
We obtain
the entire function
\medskip
\[
F(z)=  \frac{1}{2\pi}\,\int_{\epsilon}^\pi
e^{-i\theta\cdot z}\cdot \phi(e^{i\theta})d\theta+
\frac{1}{2\pi}\, \int_{-\pi}^{-\epsilon}
e^{-i\theta\cdot z}\cdot \phi(e^{i\theta})d\theta+
\frac{1}{2\pi i}\int_{\gamma_\epsilon}\,
\frac{e^{-z\cdot\text{Log}\zeta}\cdot 
\phi(\zeta)d\zeta}{\zeta}
\]
\medskip

\noindent
If $z=n$ is an integer we
have 
\[
e^{-in\theta}=\zeta^{-n}\quad\colon\quad
e^{-n\cdot\text{Log}\zeta}=\zeta^{-n}
\]

\noindent 
Hence we get
\[
F(n)=\frac{1}{2\pi i}\cdot
\int_{\Gamma_\epsilon}\,\frac{\phi(\zeta)\cdot d\zeta}{\zeta^{n+1}}\tag{*}
\]
\medskip

\noindent
where $\Gamma_\epsilon$ is the closed curve
given as the union of $\gamma_\epsilon$ and the
interval of $T$ where
$|\theta|\geq\epsilon$.
Cauchy's formula applied to $\phi$ gives:

\medskip

\noindent {\bf 2.1 Proposition.} \emph{Let $\phi(\zeta)=\sum c_n\zeta^n$.
Then} 
\[
F(n)=c_n\quad\colon\,n\geq 0\quad\text{and}\quad  F(n)=0
\quad\, n\leq -1
\]


\noindent
Next, using (i) above we also have:
\medskip


\noindent 
{\bf 2.2 Proposition.} \emph{The complex derivative of $F$ is equal to $f$.}

\medskip

\noindent
\emph{Proof.}
With $\epsilon>0$ the derivative of the sum of first
two terms from the construction of $F(z)$ above
become
\[
\frac{1}{2\pi}\,\int_{|\theta|\geq\epsilon}\,
-i\theta\cdot e^{-iz\theta} \phi(e^{i\theta})d\theta\tag{i}
\]
\medskip

\noindent
In the last integral derivation with respect to $z$ gives
\[
-\frac{1}{2\pi i}\int_{\gamma_\epsilon}\,
\frac{e^{-z\cdot\text{Log}\zeta}\cdot\phi(\zeta)d\zeta}{\zeta}
 \tag{ii}
\]
Now $\zeta=1+\epsilon\cdot e^{i\theta}$ during the
integration along $\gamma_\epsilon$ which gives:
\[ 
|\text{Log}\,(1+\epsilon\cdot e^{i\theta})|\leq\epsilon
\]
At the same time the circle interval $\gamma_\epsilon$ has length
$\leq\epsilon$
and hence the growth condition  (i)
shows that the integral  (iii) tends to zero when
$\epsilon\to 0$.
Finally, since we assumed that 
the function $\theta\mapsto \theta\cdot\phi(e^{i\theta})$ 
is absoutely integrable on $T$ a passage to the limit as
$\epsilon\to 0$ gives $F'=f$ as requested.


\medskip

\noindent 
{\bf 2.3 Conclusion.}
If $n$ is a positive integer in Proposition 2.3 we have:
\[ 
F'(n)=
\frac{-i}{2\pi}\int_{-\pi}^{\pi}
e^{-in \theta }\cdot \theta\cdot \phi(e^{i\theta})\cdot d\theta\tag{**}
\]


\noindent
These integrals are zero for every
$n\geq 1$ if and only if
$\theta\cdot \phi(e^{i\theta})$ is the boundary value function of
some $\psi(z)$ which is analytic in the exterior disc
$|z|>1$. In 2.X we will show that
this is true for a specific $\phi$\vvv function 
satisfying the growth condition (1) above and in addition
the series

\[ 
\sum\uuu{n=1}^\infty\, (\vvv 1)^n\cdot \frac{c\uuu n}{n}
\]
converges.
\bigskip

\noindent
{\bf{2.4 How to deduce a solution $\{x\uuu p\}$.}}
Suppose we have found $\phi$ satisfying the conditions above
which gives the entire function $F(z)$
whose derivatives are zero for all $n\geq 1$.
Now we set

\[ 
x\uuu p=(\vvv 1)^p\cdot c\uuu p
\]
By (***) this sequence belongs to $\mathcal F$ and we construct the 
associated entire function $H(z)$.
From (i) in Proposition  0.1 and Proposition 2.1 we get

\[ 
H(p)=(\vvv 1)^p\cdot x\uuu p=c\uuu p=F(p)
\]
In addition both $H$ and $F$ have zeros at all integers $\leq 0$.
Next, by the construction of $F$ it is clear that this 
is an entire function of exponential
type and by the above the entire function $G=H\vvv F$
has zeros at all integers.
We leave as an exercise to the reader to show that
$G$ must be identically zero. The hint is to use similar
methods as in the proof of
the uniqueness.
It follows that
\[ 
H'(q)= F'(q)=0
\]
for all $q\geq 1$.
By (ii) in Proposition 0.2 this means precisely that
$\{x\uuu p\}$ is a solution to the requested equations in (*)
which gives the existence in Dagerholm's  Theorem.

\bigskip


\centerline {\bf{2.5 The construction of $\phi$.}}
\medskip


\noindent
There remains to find $\phi$ such that the conditions above hold.
To obtain $\phi$ we start with the integrable function
on $T$ defined by:
\[ 
u(\theta)=\frac{1}{2}\cdot \log \,\frac{1}{|\theta|}
\quad\colon\, -\pi<\theta<\pi
\]
We get the analytic function
\[ 
g(\zeta)=\frac{1}{2\pi}\int_{-\pi}^\pi\,
\frac{e^{i\theta}-\zeta}{e^{i\theta}+\zeta}\cdot
u(\theta)\cdot d\theta
\]


\noindent
In the exterior disc
we find the analytic function
\[
\psi(\zeta)=\text{exp}\,\, -\bar g(\frac{1}{\bar\zeta})
\]


\noindent
Let us also put
$\phi\uuu *(\zeta)=e^{g(\zeta)}$.
Now we have

\[
\log |\phi(e^{i\theta})|=\mathfrak{Re}\, g(e^{i\theta})=
u(\theta)
\]
In the same way we see that
\[
\log |\psi(e^{i\theta})|=\vvv \mathfrak{Re}\, g(e^{i\theta})=
\vvv u(\theta)
\]
Since $2u(\theta)= \vvv \log\,|\theta|$
it follows that
\[
\log\,|\theta|+\log |\phi\uuu *(e^{i\theta})|=\log |\psi(e^{i\theta})|
\]
Taking exponentials  we obtain
\[
|\theta|\cdot|\phi\uuu *(e^{i\theta})|= |\psi(e^{i\theta})|
\]
\medskip

\noindent
{\bf{Exercise.}}
Check also arguments and verify that
we can remove
absolute values in the last equality to attain
\[
|\theta|\cdot \phi\uuu *(e^{i\theta})= \psi(e^{i\theta})\tag{*}
\]

\medskip

\noindent
Here (*) is not precisely what we want since
our aim was to construct $\phi$ so that
$\theta|\cdot \phi(e^{i\theta})$ is equal to the boundary
value of an analytic function in
$|z|>1$.
So in order to get rid of the absolute value for $\theta$ in
(*) we modify $\phi\uuu *$ as follows: Set
\medskip

\noindent 
\[
\rho(\theta)=\frac{\pi i}{2}\cdot
\text{sign}\,\theta\cdot e^{-i\theta}\quad\colon 
-\pi<\theta<\pi
\]
\medskip

\noindent 
Next, consider the two analytic functions
in $D$, respectively in $|z|>1$ defined by:

\[ \phi\uuu 1(z)=
\frac{1}{\sqrt{1-z^2}}\quad\text{and}\quad \, \psi\uuu 1(z)=
\frac{1}{\sqrt{1-z^{-2}}}
\]
\medskip

\noindent {\bf {Exercise.}}
Show that one has the equality

\[
\rho(\theta)=\frac{\phi\uuu 1(e^{i\theta})}
{\psi\uuu 1(e^{i\theta})}
\] 
when $\vvv \pi<\theta <\pi$ and $\theta\neq 0$.

\medskip

\noindent
{\bf{The $\phi$\vvv function.}}
it is defined by
\[ 
\phi(z)=\frac{z}{\sqrt{1\vvv z^2}}\cdot \phi\uuu *(z)
\]
From (*) above and the construction of $\rho$
it follows that
\[ 
\theta\cdot \phi(e^{i\theta})=
\frac{\pi}{2}\cdot  \psi\uuu 1(e^{i\theta})\cdot\psi(e^{i\theta})
\]
The right hand side is the boundary function of an
analytic function in $|z|>1$ and hence $\phi$ satisfies (**) from
XX.
Consider its Taylor expansion
\[ 
\phi(z)=\sum\, c\uuu n\cdot z^n
\]
There remains to verify that the series (**) converges and
that $\phi$ satisfies the growth condition in XX.
To prove this
we begin to analyze the function
\[ 
\phi\uuu *(z)= e^{g(z)}\tag{i}
\]







\noindent
Rewrite the $u$ function as a sum
\[
u(\theta)=
\frac{1}{2}\log\,\bigl |\frac{1}{1-e^{i\theta}}\bigr |+
k(\theta)\quad\text{where}\quad \, k(\theta)=
\frac{1}{2}\log\,\bigl  |\frac{1-e^{i\theta}}{\theta}\bigr |\tag{ii}
\]


\noindent
When $\theta$ is small we have an expansion
\[
\frac{1-e^{i\theta}}{\theta}=-i+\theta/2+\ldots\tag{iii}
\] 
From this we conclude that the $k$-function is
at least twice differentiable as a function of $\theta$. So  the Fourier
coefficients in the expansion
\[ 
k(e^{i\theta})=\sum\, b_\nu e^{i\nu \theta}\tag{iv}
\]
have a good decay. For example, there is a constant $C$ such that
\[
 |b_\nu|\leq \frac{C}{\nu^2}\quad\colon\, \nu\neq 0\tag{v}
\]
This implies that the analytic function
\[
\mathcal{K}(z)=
\frac{1}{2\pi}\cdot\int_{-\pi}^{\pi}\,
\frac{e^{i\theta}+z}{e^{i\theta}-z}\cdot k(e^{i\theta})\cdot d\theta\tag{vi}
\]
yields a 
bounded analytic function in the unit disc.
Next, the construction of the $g$-function gives:

\[
g(z)= \frac{1}{2}\cdot \log\,\frac{1}{1-z}+
\sum\, b_\nu z^\nu\implies\tag{vii}
\]
\[ 
\phi\uuu *(z)=\frac{1}{\sqrt{1-z)}}\cdot e^{\mathcal K(z)}
\]
\medskip

\noindent
We conclude that

\[
\phi(z)= 
\frac{z}{1\vvv z}\cdot
\frac{1}{\sqrt{1+z)}}\cdot e^{\mathcal K(z)}
\]
Since $\mathcal K(z)$ extends to a continuous function on the closed disc
it follows that $\phi$ satisfies the growth condition (1) with $\beta=1$.
Moreover, the function $\theta\cdot \phi(e^{i\theta})$ belongs to $L^1(T)$
since
$\frac{1}{\sqrt{1+e^{i\theta}}}$ is integrable. 
There remains only to prove:

\medskip

\noindent
{\bf{Lemma.}} The series
\[
\sum\uuu{p=1}^\infty\, (\vvv 1)^n\cdot\frac{c\uuu n}{n}
\]
is convergent.
\medskip

\noindent
\emph{Proof.}
let us put

\[
A(z)= 
\frac{z}{\sqrt{1+z)}}\cdot e^{\mathcal K(z)}
\]
This gives

\[
\phi(z)=\frac{A(1)}{1\vvv z}+\frac{A(z)\vvv A(1)}{1\vvv z}
\]
From (v) it follows that $K(z)$, and hence also
$e^{K(z)}$ is differentiable at $z01$
which gives the existence of a constant $C$ such that

\[
\bigl|\frac{A(z)\vvv 1}{1\vvv z}\bigr|\leq
C\cdot \frac{1}{|\sqrt{1+z}|}
\]
Here the function $\theta\mapsto \frac{1}{|\sqrt{1+e^{i\theta}}|}$
belongs to $L^p(T)$ for each $p<2$ which by the  inequality for 
$L^p$\vvv norms between functions and their Fourier coefficients
in XX
for example implies that
if $\{c\uuu \nu^*\}$ give the Taylor series for
$\frac{A(z)\vvv 1}{1\vvv z}$ then
\[
\sum\, |c^*\uuu\nu|^3<\infty
\]
Now Hölder's inequality gives





\[
\sum\, \frac{|c^*_\nu|}{\nu}\leq \bigl(\sum\,|c_\nu^*|^3\bigr)^{\frac{1}{3}}\cdot
\bigl(\sum\,\nu^{-3/2}\bigr)^{\frac{2}{3}}<\infty\tag{8}
\]

\noindent
We conclude that the Taylor series for $\phi$ becomes


\[
A(1)\cdot(1+z+z^2+\ldots)+\sum c_\nu^*z^\nu
\]
Hence $c\uuu n=A(1)+c^*\uuu\nu$ and now
Lemma xx follows since the alternating series
$\sum\,(-1)^n\frac{1}{n}$ is convergent
and we have the absolute convergence in XX above.


\newpage

\centerline{\bf{§ M. A theorem by Kjellberg.}}
\bigskip


\noindent
{\bf{Introduction.}}
We  expose an article by Bo Kjellberg - former Ph.D-student of Beurling -
which deals with a
comparison between integrals and certain sums
of analytic functions of exponential type in a half-space.
Here is the situation: Let $f(z)$ be analytic in
the closed half-spae
$\mathfrak{Re}\, z\geq 0$.
Assume that the function $x\mapsto |f(x)|$ is bounded on the real $x$-axis
and there exists a positive real number
$c$ such that
\[
 \limsup_{|z|\to\infty}\, \frac{\log\,|f(z)|}{|z|}= c\tag{1}
\]
Next, let
$\phi(t)$ be a $C^2$-functionon $t\geq $ with $\phi(0)=0$ for which
\[
\phi'(t)\geq 0\quad\colon\quad  t\cdot \phi''(t)+\phi'(t)\geq 0
\]
Thus, $\phi$ is non-decreasing and the last inequality means that it is
convex
as a function of $\log t$.
\medskip

\noindent
{\bf{ Gap sequences.}}
A strictly increasing sequence $\{\lambda_n\}$ has gaps of order $\geq \delta$ 
if
\[
\lambda_{n+1}-\lambda_n\geq 2\cdot\delta\quad\colon\, n=1,2,\ldots
\]
\medskip

\noindent
{\bf{0.1 Theorem.}}
\emph{Let $f$ and $\phi$ be as above.
Then, for every $\delta>0$ and each
$\lambda$-sequence with gaps of order $\geq \delta$
one has the implication}

\[
\int_0^\infty\, \phi(|f(x)|)\, dx<\infty\implies
\sum_{n=1}^\infty\, \phi(e^{-\delta\cdot c}\cdot |f(\lambda_n)|)<\infty\tag{*}
\]
\medskip

\noindent
{\bf{Remark.}}
The result above gave an affirmative anser to a question posed by Boas
in the article \emph{Inequalities between
series and integrals involving entire functions}.
The proof of Theorem 0.1 has two ingredients. First one has 
a uniqueness result   which goes as follows:

\medskip

\noindent
{\bf{0.2 Theorem.}}
\emph{Let $f$ and $\phi$
be as above where (1) holds for $f$ and
the integral in the
left hand side of Theorem 0.1 is finite. Then, if}
\[
\int_0^{1/2}\, \frac{\phi(t)}{t\cdot \log\,\frac{1}{t}}\,dt=+\infty
\]
\emph{it follows that $f$ is identically zero.}


\medskip

\noindent
{\bf{Remark.}} We shall first prove Theorem 0.2 and notice that
it then is suffcient to prove Theorem 0.1 under the
\emph{additional assumption} that the integral in Theorem 0.2 is finite.
In both theorems the convexity of $\phi$ with respect to $\log t$
will
be used. More precisely we first notice that if
$H(x,y)$ is a harmonic function defined in some open
set in
${\bf{C}}$ then
\[
u(x,y)= \phi(e^{H(x,y)})
\] 
is subharmonic. Indeed , this follows since
\[
u_x= H_x\cdot e^H\cdot \phi'(e^H)\implies
u_{xx}=H_{xx}e^H\cdot \phi'(e^H)+
H_x^2e^H(e^H\cdot \phi''(e^H)+ \phi'(e^H))
\]
A similar equation holds for $u_{yy}$ and adding the result we use that
$\Delta(H)=0$ and
see that (2) above entails that
$\Delta(u)\geq 0$.
We shall need the following prelimninary result:
\medskip


\noindent
{\bf{1.1 Proposition.}}
\emph{Let $u(x)$ be a continuous and
non-negtive function on $x\geq 0$ where}
\[ 
\limsup_{x\to+\infty}\, u(x)=+\infty
\]
\emph{and 
$g$ is a stricty increasing function on $x>0$.
Then the implication below holds:}
\[
\int_0^\infty\, g(u(x))\, dx<\infty
\quad\text{and}\quad
\int_1^\infty\, \frac{g(u)}{u}\, du=+\infty
\implies
\int_1^\infty\, \frac{u(x)}{x^3}\, dx=+\infty
\]
\medskip

\noindent
\emph{Proof.}
Let $v(x)$ be the non-decreasing funftion which is equi-distributed with
$u$ as explained in §§. Then we have
\[
\int_1^\infty\, \frac{v(x)}{x^3}\, dx\leq
\int_1^\infty\, \frac{u(x)}{x^3}\, dx
\]
while the left and side integrals are unchanged when
$u$ is replaced by $v$. Hence it suffices to prove
the result for $v$, i.e. from now on we  assume
that $u$ is non-decreasing.
If $0<a<A$ a partial integration gives
\[
\int_a^A\, g(u(x))\, dx=
\quad\text{and}\quad
\]

Easy finish ....


\bigskip

\noindent
{\bf{1.2 Majorisations in quarter-planes.}}
We are given the constnst $c$ which implies that if $c'>c$ then there is a 
constant $B$ such that
the inequality below holds in the right half-plane:
\[ 
|f(x+iy)|\leq B\dot e^{c'\dot |y|}
\]
Let us then choose $c^*>c'$ snd set

\[ 
\psi(z)= \phi(e^{ic^*z}\cdot f(z)|)
\] 
By (xx) $\psi$
is a subharmonic function in the quarter plane
$U_*=\{x>0\}\times \{y>0\}$ and here
\[ 
\psi(x+iy)=\phi(e^{-c^*\cdot y}\cdot |f(x+iy)|)
\]
The subharmonicity of $\psi$ entails that
\[
\psi(z)\leq h_1(z)+h_2(z)
\] 
where
$h_1(z)$ is the harmonic extension of the boundary value function
which is
$\phi|f(x)|$ on the positive real axis and zero on
the positive $y$-axis, while $h_2(x,0)=0$ and
\[
h_2(0,y)= \phi(e^{-c^*\cdot y}\cdot |f(iy)|)
\]
Since $c^*>c'$ it follows from (xx) that $h_2(0,y)$ is bounded and 
tends to zero as $y\to\infty$
The growth properties of the two $h$-functions on
the boundsry of $U_*$ entail that
both are represented as in § XX.
Thus, one has

\[ 
h_1(x+iy)=\frac{1}{\pi}\int_0^\infty\,
y\cdot \psi(\xi)\cdot\bigl[\frac{1}{(\xi-x)^2+y^2}-
\frac{1}{(\xi+x)^2+y^2}\bigr]\, d\xi
\]

\[ 
h_2(x+iy)=\frac{1}{\pi}\int_0^\infty\,
x\cdot \psi(i\eta )\cdot\bigl[\frac{1}{(\xi-x)^2+y^2}-
\frac{1}{(\xi+x)^2+y^2}\bigr]\, d\eta
\]
From (i) we obtain
\[
\int_0^\infty\,h_1(x+iy)\,dx=
\frac{2}{\pi}\int_0^\infty\,
\psi(\xi)\cdot \arctan\,\frac{\xi}{y}\, d\xi\leq
\int_0^\infty\,\psi(\xi)\,d\xi\tag{1}
\]
For $h_2$ we obtain
\[
\int_0^\infty\,h_1(x+iy)\,dx=\frac{1}{\pi}\int_0^\infty\,
\psi(i\eta)\cdot \log\, \bigl|\frac{\eta+y}{\eta-y}\bigr|\, d\eta
\leq C+ A\cdot
\int_{2\delta}^\infty\,
\frac{\psi(i\eta)}{\eta}\, d\eta\tag{2}
\]
where $A$ and $C$ are two constants which the reader may derive from
(x-x) above,
Let us now estaimte the last integral in (2).
Since $\phi$ is non-decreasing we see that (xx) and (xx) give
have
\[ 
\psi(i\eta)\leq\phi(B\cdot e^{(c'-c^*)\eta})
\]
Consider the variable substitution
\[ 
t= B\cdot e^{(c'-c^*)\eta})\implies \frac{dt}{t}=-Bc^*\cdot d\eta
\]
Notice that it gives

\[
\eta=\frac{1}{c^*-c'}\cdot \log \frac{B}{t}
\]
It follows that
\[
\int_{2\delta}^\infty\,
\frac{\phi(B\cdot e^{(c'-c^*)\eta}}{\eta})\, d\eta=
(c^*-c')\cdot \int_{t_0}^\infty\, \frac{\phi(t)}{t\cdot \log\,\frac{B}{t}}\, dt
\]
\medskip


\noindent
{\bf{Conclusion.}}
Under the hypothesis that the integral (**) in Theorem 0.2 converges and 
integral in the left hand side in Theorem 0.1
also converges, it follows that for every $\delta>0$
there exis  constants $C_1,C_2$
which may depend upon $\delta$ such that
\[
\int_{C_1}^\infty\, (h_1(x+iy)+ h_2(x+iy))\, dy\leq C_2
\quad\colon\,\,\, 0\leq y\leq \delta
\]
Together with
the majorization in (xx) it follows that with another constant $C_3$ we have
\[ 
\iint_{\square_\delta}\, \psi(x+iy)\, dxdy\leq C_3
\]
where $\square_\delta= \{0<x<\infty\}\times \{0<y<\delta\}$.

\bigskip

NOW easy to finish the proof of theorems....

\newpage











\centerline{\bf § N.  Carleson's Interpolation Theorem}

\bigskip
\noindent
{\bf Introduction.}
Let $U=\mathfrak{Im}(z)>0$
be the upper half-plane. 
Denote by ${\bf{c}}_*$
the family of sequences of complex numbers 
$\{c_\nu\}$ where every
$|c_\nu|\leq 1$. 
A  sequence $z\uuu\bullet =\{z_\nu\}$
in $U$ has a finite interpolation norm
if there
exists a constant $K$ such that
for every 
sequence $\{c_\nu\}\in {\bf{c}}_*$ one can find    an analytic function $f(z)$ in $U$
such that
\medskip
\[
f(z_\nu)=c_\nu\quad\colon\quad\nu=1,2,\ldots\quad\text{and}\quad |f|_U\leq K\tag{*}
\]

\noindent
The smallest  constant
$K$  
for which (*) holds is denoted by
$\mathfrak{int}(z_\bullet)$.

\medskip


\noindent
{\bf 0.1 Theorem.}
\emph{A sequence $z_\bullet$ has a finite  interpolating norm if and only if }
\medskip
\[
\min\uuu \nu\, \prod_{k\neq\nu}\, |\frac{z_\nu-z_k}{z_\nu-\bar z_k}|>0\tag{1}
\]


\noindent
\emph{Moreover, if $\delta(z\uuu\bullet)$ denotes the minimum
above then}
\[ \mathfrak{int}(z_\bullet)\leq \frac{A}{\delta(z\uuu\bullet)}\cdot
\text{Log}
\,\frac{1}{\delta(z\uuu\bullet)}\,.\tag{2}
\]
\emph{where  $A$ is an absolute  constant.}

\medskip

\noindent
{\bf{Remark.}}
That the condition (1)  is
necessary
is easily verified and left to the reader as an exercise.
The proof of sufficieny is more involved.
In 
[Ca] the proof is carried out in the unit disc $D$
where (1) in
Theorem 0.1 means that a sequence 
$\{z\uuu\nu\}$ in $D$ should satisfy
\[
\min\uuu\nu \prod\uuu{k\neq \nu}\,
\frac{|z\uuu\nu\vvv z\uuu k|}{|1\vvv \bar z\uuu k\cdot z\uuu\nu|}>0
\tag{3}
\]
Carleson's result will be proved
in the upper half\vvv plane where  certain   constructions
become a bit more transparent  compared
to the unit disc.
Let $\{z\uuu\nu\}$ be a sequence in $U$ where (1) holds in Theorem 0.1.
Since a family  of analytic functions
in $U$ with a uniform upper bound for the maximum norm is a normal in Montel's sense,
it is sufficient to  prove the requested interpolation by bounded
functions
for every
finite subsequence of $\{z_\nu\}$.
The Nevanlinna-Pick theorem assigns   to each  finite
sequence $\{z_\nu\}$ and every sequence 
$\{c_\nu\}$  a unique interpolating analytic function
$F(z)$ with smallest maximum norm.
So Carleson's result  
gives a uniform bound in
the Nevannlinna-Pick interpolation expressed via the
numbers $\delta(z_\bullet)$.

\medskip

\noindent
From the above there remains to find an absolute constant
$A$ such that
(2) in Theorem 0.1 hold for every finite set
$E=\{z_1,\ldots,z_N\}$ in the upper half-plane. 
The proof has several ingredients.
We shall use the Hardy space $H^1({\bf{R}})$
and apply some fundamental  results due to Hardy and Littlewood concerned with
maximal functions.
In addition we use the Borthers Riesz theorem which
yields a describes the dual space of
$H^1({\bf{R}})$.
A crucial step  in Carleson's proof is
to
tge construction of a certain norm on
non-negative measures in the upper half-plane
and via the Hardy-Littlewood theory
one gets Theorem 0.1 after a duality argument.


\newpage





\centerline {\bf 0.1 Carleson measures.}
\medskip

\noindent
For every
$h>0$ we denote by
$\mathcal{S}(h)$
the family of squares of the form
\[ 
\square=\{(x,y)\quad\colon\quad x_0-h/2<x<x_0+h/2\quad\colon 0<y<h\}
\quad\colon\, x_0\in{\bf{R}}
\]

\noindent
{\bf 0.2. Definition.}
\emph{A non-negative measure $\mu$ in $U$ is called a Carleson measure if
there exists a constant $K$such that}
\[
\max_{\square\in\mathcal S(h)}\,\mu(\square)\leq K\cdot h
\]
\emph{hold for each $h>0$.
The least constant $K$ is denoted by
$\mathfrak{car}(\mu)$ and called the Carleson norm of
$\mu$.}
\medskip

\noindent
In § xx we  prove the following inequality:

\medskip

\noindent
{\bf 0.3 Theorem.}
\emph{For eqch finite set $\{z\uuu\nu\}$ 
in the upper half-plane one has}
\[
\mathfrak{car}\bigl (\, 
\sum_{\nu=1}^{\nu=\infty}\,
\mathfrak{Im}(z_\nu)\cdot \delta_{z_\nu}\bigr)\leq
(1+\frac{5}{2})\cdot\text{Log}\,\frac{1}{\delta(z_\bullet)}
\]
\emph{where $\{\delta\uuu{z\uuu\nu}\}$
denote  Dirac measures.}
\medskip

\noindent
{\bf {Use of duality.}}
We are  going to use the Hardy space
$H^1({\bf{R}})$. 
To each $h\in H^1({\bf{R}})$ we associate the
maximal function
$h^*$ as explained in § xx. 
\medskip

\noindent
{\bf 0.4 Theorem.}
\emph{For each  Carleson measure $\mu$ one has the inequality}
\[ 
\int_U\, |h(z)|\cdot d\mu(z)\leq
\mathfrak{car}(\mu)\cdot ||h^*||_1\quad\colon\, h\in H^1({\bf{R}})
\]
\medskip


\noindent
Armed with Theorems 0.3-0.4 we derive
Theorem 0.1 in
§ 3.

\bigskip


\centerline{\bf {1. Proof of Theorem 0.3}}
\medskip


\noindent
First we establish an inequality which is attributed to L. Hörmander.
\medskip



\noindent {\bf 1.1 Lemma}
\emph{Let
$z_1,\ldots,z_N$ be a finite sequence in $U$ and put $\delta=\delta(z\uuu\bullet)$.
Then}
\medskip
\[
\sum_{\nu\neq k}\, \mathfrak{Im}(z_k)\cdot
\frac{\mathfrak{Im}(z_\nu)}{|z_k-\bar z_\nu|^2}
\leq \frac{1}{2}\cdot
\log\,\frac{1}{\delta}\quad\colon\quad 1\leq k\leq N\tag{*}
\]


\noindent 
\emph{Proof.} The left hand side as well as
the $\delta$-norm of the
$z$-sequence are unchanged if we translate all points
to $z_\nu+a$ where $a$ is a real number. Similarly, the
$\delta$-norm and the left hand side in (*) are  unchanged when
the sequence is replaced by $\{A\cdot z_\nu\}$ for some $A>0$.
To prove (*) for a fixed $k$ which we may 
therefore take  $k=N$
and $z_N=i$.
Put $z_\nu=a_\nu+ib_\nu$ when $1\leq\nu\leq N-1$.
Then we must show
\[ 
\sum_{\nu=1}^{\nu=N-1}\,
\frac{b_\nu}{(1+b_\nu)^2+a_\nu^2}\leq \frac{1}{2}\cdot
\log\,\frac{1}{\delta}\tag{i}
\]

\noindent
To prove (i) we first notice that
\[
\frac{|i-\bar z_\nu|^2}{|i-z_\nu|^2}=
\frac{(1+b_\nu)^2+a_\nu^2}
{(1-b_\nu)^2+a_\nu^2}\tag{iii}
\]
By inverting the  $\delta=\delta(z_\bullet)$ we also have:
\[
 \prod\uuu{\nu=1}^{\nu=N\vvv 1}\,
\frac{(1+b_\nu)^2+a_\nu^2}
{(1-b_\nu)^2+a_\nu^2}\leq \delta^{\vvv 2}\implies
\sum_{\nu=1}^{\nu=N-1}\,
\log \bigl[\,\frac{(1+b_\nu)^2+a_\nu^2}
{(1-b_\nu)^2+a_\nu^2}\,\bigr]\leq 2\cdot\log\,\frac{1}{\delta}\tag{iii}
\]

\noindent
Next, for each $\nu$ we have the integral formula
\[
\log \, \frac{(1+b_\nu)^2+a_\nu^2}
{(1-b_\nu)^2+a_\nu^2}=\int\uuu{\vvv b\uuu\nu}^{b\uuu\nu}\,
\frac{2(1+ s)}{(1+ s)^2+a\uuu\nu^2}\, ds
\]

\noindent
Next, for every pair $(a,b)$ of real numbers with $b>0$
the reader may verify that
\[
\frac{b}{(1+b)^2+a^2}\leq
\frac{1}{2}\cdot \int_{-b}^b\, \frac{1+s}{(1+s)^2+a^2}\, ds\tag{iv}
\]
Now (iii-iv) and a summation over $\nu$ gives (i).





\bigskip






\centerline{\emph{Final part of the
proof of  Theorem 0.3}}
\medskip


\noindent
If $z_\bullet\in\mathcal S(\delta)$ and $a$ is a real number
the sequence $z_\bullet+a=\{z_\nu+a\}$
also belongs to
$\mathcal S(\delta)$. Since Theorem 0.3 asserts
an
a priori estimate we may  assume that
$\square$ is centered at $x=0$, i.e. 
\[
\square=\{(x,y)\,\colon\, -h/2<x<h/2\,\,\text{and}\,\, 0<y<h\}
\]
There remains to estimate
\[
\sum_{z_\nu\in \square}\, \mathfrak{Im}\, z_\nu\tag{i}
\]
Set
\[
y^*=\text{max}\,\{ \mathfrak{Im}(z_\nu)\,\colon\,z_\nu\in\square\}
\]

\noindent
Let $k$ give the equality $y^*=\mathfrak{Im}(z_k)$.
With $z_k=x_k+iy^*$ and $z_\nu=x_\nu+iy_\nu\in\square$
we  have
\[
|z_k-\bar z_\nu|^2=(x_k-x_\nu)^2+(y^*-y_\nu)^2
\leq h^2+(y^*)^2\implies
\]
\[
\frac{\mathfrak{Im}(z_k)}{|z_k-\bar z_\nu|^2}\geq
\frac{y^*}{h^2+(y^*)^2}\quad\colon\,\nu\neq k
\]

\noindent
Next, notice that 
\[
y^*\geq h/2\implies\frac{y^*}{h^2+(y^*)^2}\geq \frac{1}{5h}\,.
\]

\noindent
Lemma 1.1. applied with $\nu=k$
gives therefore
\[
\sum_{z_\nu\in \square}\, \mathfrak{Im}(z_\nu)
\leq y^*+\frac{5h}{ 2}\cdot\text{Log}\,\frac{1}{\delta}\leq
h\cdot\bigl (1+\frac{5}{ 2}\cdot\text{Log}\,\frac{1}{\delta}\bigr)
\tag{ii}
\]


\noindent
So if $y^*\geq h/2$ we are done.
Suppose now that  $y^*<h/2$ and
regard the cubes:
\[
\square_1=\{
-h/2<x<0\,\text{and}\,\, 0<y<h/2\}\quad
\square_2=\{
0<x<h/2\,\,\text{and}\,\, 0<y<h/2\}
\]


\noindent
We want to estimate
\[
S_1+S_2=\sum_{z_\nu\in\square_1}\,\mathfrak{Im}(z_\nu)+
\sum_{z_\nu\in\square_2}\,\mathfrak{Im}(z_\nu)
\]
We have also two sequences:
\[
\{z_\nu\,\colon\,z_\nu\in\square_1\}\quad\text{and}\quad
\{z_\nu\,\colon\,z_\nu\in\square_2\}
\] 
Since all factors defining the $\delta$-norm are $\leq 1$
these two smaller sequences both belong to $\mathcal S(\delta)$.
Suppose that:
\[
y_1^*=
\max_{z_\nu\in\square_1}\,
\mathfrak{Im}(z_\nu)\geq \frac {h}{4}
\]
When this holds we obtain via an obviouos scaling and the same argument
as above:
\[
S_1\leq \frac{h}{2}\cdot (1+\frac{5}{2}\cdot \text{Log}\, \frac{1}{\delta}
 \]
 
\noindent
If $y^*_1<\frac{h}{4}$ we continue to
split the cube $\square_1$. 
In a similar fashion we treat
the sequence which stays in $\square_2$.
After a finite number of steps  the requested  inequality in
Theorem 0.3 follows.


\bigskip


\centerline{\bf 2. Proof of Theorem 0.4}

\medskip


\noindent
Let $h\in H^1({\bf{R}})$ and  recall  that its maximal function is 
defined by
\[ 
h^*(t)=\max\, |h(x+iy)|\quad\colon\quad
|x-t|<y\tag{i}
\]

\noindent
To each  $\lambda>0$ we consider the open subset
on the real line defined by $\{h^*>\lambda\}$. It is some
union of disjoint intervals $\{(a_j,b_j)\}$ and
(i) gives the set-theoretic inclusion:
\[
\{|h(x+iy)|>\lambda\}\subset\,\cup \,\,T\uuu j
\quad\colon\tag{ii}
\]
where $T\uuu j$ is the  triangle side standing on the interval $(a_j,b_j)$
as explained in XXX.  (Hardy space). In particular we have
the inclusion:
\[ 
T\uuu j\subset
\square(a_j,b_j)=\{ x+iy\,\,\colon |x-\frac{a_j+b_j}{2}|< b_j-a_j\,\,
\colon\,\, 0<y< b_j-a_j\}\tag{iii}
\]

\noindent 
See figure XXX.
So if $\mu$ is a positive measure in $U$  we obtain:
\[
\mu(\{|h|>\lambda\})
\leq \sum \mu(T\uuu j)
\leq \sum \mu(\square(a_j,b_j))\tag{iv}
\]

\noindent 
If $\mu$ is a Carleson measure
the right hand side
is estimated by
\[
\mathfrak{car}(\mu)\cdot \sum\,(b_j-a_j)=
\mathfrak{car}(\mu)\cdot\mathfrak{m}(
\{h^*>\lambda\})\tag {v}
\]

\noindent
where  $\mathfrak{m}$
 refers to the 1-dimensional Lebesgue measure.
Here (v) holds for every $\lambda>0$ and  the general 
inequality for distribution functions from XXX gives:
\[
\int _U
|h|\cdot d\mu\leq \mathfrak{car}(\mu)\cdot||h^*||_1
\]
This finishes the proof of Theorem 0.4.

\bigskip



\centerline{\bf 3. Proof of Theorem 0.1.}
\bigskip

\noindent
As explained in § xx, the Banach space
$H^1({\bf{R}})$
contains a dense subspace denoted by $H_*^1$
of functions $h(z)$ with rapid  decay at infinity, i.e.
\[
|h(z)|\leq C_N\cdot (1+|z|)^{-N} 
\quad\colon\text{hold for some constant}\,\,\, C_N\quad\colon\, N=1,2,\ldots
\]
Consider a
finite sequence $z_1,\ldots,z_N$  in $U$
and
a finite sequence $c_1,\ldots,c_N$ in
${\bf{c}}_*$. Newton's interpolation
gives  a
unique  polynomial $P(z)$ of degree $N-1$ such that:
\[ 
P(z_k)=c_k\quad\colon\quad 1\leq k\leq N\tag{i}
\]

\noindent
Let $B(z)$ be  the Blascke product
associated to the $z$-sequence:
\[ 
B(z)=\prod_{\nu=1}^{\nu=N}\, \frac{z-z_\nu}{z-\bar z_\nu}\tag{ii}
\]

\noindent
For each $h\in H^1_*$
we have the absolutely convergent integral
\[ 
L(h)=\int_{-\infty}^\infty\,\frac{P(x)}{B(x)}\cdot h(x)\cdot dx
\]
Residue calculus gives the equation
\[
L(h)=2\pi i\cdot \sum_{k=1}^{k=N}\, \frac{c_k}{B'(z_k)}\cdot h(z_k)\tag{iii}
\]


\noindent
Next, for each  $1\leq k\leq N$ we notice that
\[ 
\frac{1}{B'(z_k)}=\prod_{\nu\neq k}\,
\frac{z_k-\bar z_\nu}{z_k-z_\nu}\cdot 2\cdot \mathfrak{Im}(z_k)\tag{iv}
\]
The definition of  $\delta(z_\bullet)$ and the triangle inequality give
\[
\bigl |\frac{1}{B'(z_k)}\bigr |\leq
\frac{2}{\delta(z\uuu\bullet)}\cdot \mathfrak{Im}(z_k)\tag{v}
\]

\medskip
\noindent
Since $\{c_\nu\}\in{\bf{c}}_*$ we see that (v) and the 
triangle inequality applied to (iii) give:

\[ 
\bigl |\int_{-\infty}^\infty\,\frac{P(x)}{B(x}\cdot h(x)\cdot dx
\,\bigr | \leq
\frac{4\pi}{\delta(z\uuu\bullet)}\cdot 
\sum_{k=1}^{k=N}| h(z_k)|
\cdot\mathfrak{Im}(z_k) \tag{vi}
\]
\medskip


\noindent 
Next, Theorem 0.4 gives the inequality
\[
\sum_{k=1}^{k=N}| h(z_k)|\cdot
\mathfrak{Im}(z_k)\leq\mathfrak{car}(\sum\,
\mathfrak{Im}(z\uuu\nu)\cdot \delta\uuu{z\uuu\nu})\cdot ||h^*||\uuu 1\tag{vii}
\]
Put
\[
C\uuu\delta =\frac{4\pi}{\delta(z\uuu\bullet)}\cdot 2\cdot \log\,\frac{1}{\delta(z\uuu\bullet)}
\]
Then (vi-vii) and Theorem 0.3
give
\[
\bigl |\int_{-\infty}^\infty\,\frac{P(x)}{B(x}\cdot h(x)\cdot dx
\,\bigr | \leq C_\delta\cdot ||h^*||\uuu 1\tag{*}
\]

\noindent
Next,  the Hardy-Littlewood inequality from §§
(Hardy Chapter ) gives an absolute constant $A$ such that
\[
||h^* ||_1\leq A\cdot ||h||_1
\]

\noindent
Hence the norm of the densely defined linear functional
\[
h\mapsto \int_{-\infty}^\infty\, \frac{P(x)}{B(x)}
\cdot h(x)\cdot dx
\] 
is $\leq C_\delta \cdot A$.
The Duality
Theorem from XXX  implies that if
$\epsilon>0$, then
there exists   $G(z)\in\mathcal O_*(U)$
such that
\[
\max_x\, \bigl |\frac{P(x)}{B(x)}-G(x)\bigr |<A\cdot C_\delta+\epsilon\tag{6}
\]
where the maximum is taken over all real $x$.
Since $B$ is a finite Blaschke product we have 
$|B(x)|=1$ for each real $x$ and hence
(6) gives:

\[
\max_x\,\bigl |P(x)-B(x)\cdot G(x)\,\bigr |<A\cdot C_\delta+\epsilon
\]

\medskip

\noindent
Set
\[
f(z)=P(z)-B(z)G(z)
\]
Since 
$B(z_\nu)=0$ for every $\nu$ we have
\[
f(z_\nu)=P(z_\nu)=c_\nu
\]
So 
the  analytic function $f(z)$ interpolates the $c$-values on the given finite set
$Z_\bullet$. Moreover, by (xx) and the maximum principle
from (*) for functions in $\mathcal O_*(U)$
it follows that
\[
|f|_U\leq A\cdot C_\delta+\epsilon
\]
Above 
$\epsilon>0$ can be arbitrary small
and since $c_1,\ldots,c_N$ was an arbitrary  sequence  in
${\bf{c}}_*$ we conclude that
the interpolation norm of the finite sequence $z_1,\ldots,z_N$ is at most
$A\cdot C_\delta$.  As observed in § xx this uniform estimate
finishes
the proof of Theorem 0.1.
\bigskip


\newpage



\newpage

*





\newpage


\centerline{\bf{Appendix 1: Invariant subspaces of $H^2(T)$}}
\bigskip


\noindent



\noindent
\emph{0. Introduction.}
\bigskip


\noindent
\emph{1. The Herglotz integral.}
\bigskip


\noindent
\emph{2. The class JN(D)}

\bigskip


\noindent
\emph{3. Blaschke products}


\bigskip


\noindent
\emph{4.  Invariant subspaces of $H^2(T)$}
\bigskip


\noindent
\emph{5.  Beurling's closure theorem}
\bigskip


\noindent
\emph{6 The Helson\vvv Szegö theorem.}



\bigskip


\centerline{\bf{Introduction.}}
\medskip

\noindent
A fundamental result was discovered by Jensen in 1899
which leads to the familiar
expression for counting numbers of zeros of analytic functions.
Together with factorisations with Blascke products
and Heglotz' integral formula 
which serves as the holomorphic version of th Poisson formula in discs,
one arrives at some powerful factorisation theorems
for analytic functions in the unit disc which belong to the
Jensen-Nevanlinna class which
is described below.
Starting from this Beuliung investigaged
decompositions
of
the boundary measure of analytic functions and
and defined inner, respectively outer factors.
Using these results  in  analytic function theory, he then
studied invarant subspaces of the Hardy space $H^2(T)$ where
the closure theorem in § 4 is fundamental.
It was later applied by Helson and Szegö and leads to certain 
results concerened with polynomial approximation which are exposed in § 5-6.
\medskip

\noindent
{\bf{Remark.}} For the reader's convenicnce the subsequent material is quite detailed and
essentially self-contained.
\bigskip


\centerline{\bf{§ 0. Poisson extensions.}}
\bigskip

\noindent
Let $\mu$ be a real Riesz measure on the unit circle $T$. It gives
the harmonic function in the unit disc $D$ defined by
\[
H\uuu\mu(z)=\frac{1}{2\pi}\int_0^{2\pi}\,
\frac{1\vvv |z|^2}{|e^{i\theta}-z|^2}\cdot d\mu(\theta)\tag{0.1}
\]
For each $0<r<1$ one has the inequality
\[
\int_0^{2\pi}\,\bigl | 
H_\mu(re^{i\theta})\bigr |\cdot d\theta\leq
||\mu||\tag{0.2}
\] 
where $||\mu||$ is the total variation of $\mu$.
Moreover, there exists  a weak limit, i.e. 
\[
\lim\uuu{r\to 1}\int_0^{2\pi}\, g(\theta)\cdot H_\mu(re^{i\theta})=
\int_0^{2\pi}\, g(\theta)\cdot d\mu(\theta)\tag{0.3}
\]
holds for every continuous function $g(\theta)$ on $T$.
Recall the converse result due to F. Riesz. Namely,
if $H(z)$ is a harmonic function in
$D$ for which there exists a constant $C$ such that
\[
\int_0^{2\pi}\,\bigl | 
H(re^{i\theta})\bigr |\cdot d\theta\leq C\tag{0.4}
\] 
hold for all $r<1$, then there exists a unique Riesz measure
$\mu$ on $T$ and $H=H\uuu \mu$.
In other words, there is a 1\vvv 1 correspondence between
the space of harmonic functions in $D$ satisfying (0.4) and the space of real Riesz measures on $T$.
Next, by a result due to Fatou
there  exist radial limits almost everywhere.
More precisely, define the
$\mu$\vvv primitive
function
\[
\psi(\theta)= \int\uuu 0^\theta\, d\mu(s)
\]

\noindent
Fatou's Theorem
asserts that for each Riesz measure $\mu$ there exists a radial limit
\[
H\uuu\mu^*(\theta)=\lim\uuu{r\to 1}\, H(re^{i\theta})\tag{0.5}
\]
for each $\theta$ where
$\psi$ has an ordinary derivative.
Since $\psi$ has a bounded variation this holds
almost everywhere by a famous result due to Lebesgue.
\medskip

\noindent
{\bf{0.6 The case when $\mu$ is singular.}}
If $\mu$ is singular 
the radial limit (0.5) is zero almost everywhere.
If the singular measure $\mu$ is non\vvv negative
with
total mass $2\pi$ we have
$H\uuu\mu(0)=1$ and  the mean\vvv value property for harmonic
functions gives:
\[
\int\uuu 0^{2\pi}\, H\uuu\mu(re^{i\theta})\cdot d\theta=1
\]
for all $0<r<1$.
At the same time the boundary function $H\uuu\mu^*(\theta)$ is almost everywhere zero
which means that one cannot have any kind of dominated convergence.
\medskip

\noindent
{\bf{0.7 Exercise.}}
Let $\mu$ be singular with
a Hahn\vvv decomposition
$\mu=\mu\uuu+ \vvv\mu\uuu \vvv$.
Assume that the positive part $\mu\uuu +(T)= a>0$.
Now there exists a closed null set $E$ such that
$\mu\uuu +(E)\geq a\vvv \epsilon$ while $\mu\uuu\vvv(E)=0$.
The last equation
gives a small $\delta>0$
such that if $E\uuu{2\delta}$ is the open
$2\delta$\vvv neighborhood of $E$ then
$\mu\uuu \vvv(E\uuu{2\delta})<\epsilon$.
Set


\[
H\uuu *(z) =
\frac{1}{2\pi}\int_E\,
\frac{1\vvv |z|^2}{|e^{i\theta}-z|^2}\cdot d\mu\uuu +(\theta)
\]
Since $\mu\uuu +(E)\geq a\vvv \epsilon$ we get
\[
\int\uuu 0^{2\pi}\, H\uuu *(re^{i\theta})\cdot d\theta \geq a\vvv \epsilon\tag{ii}
\]
Next, for each pair  $\phi\in E\uuu\delta$ and $e^{i\theta}\in T\setminus E\uuu{2\delta}$
we have:
\[
\frac{1\vvv r^2}{|e^{i\theta}-re^{i\phi}|^2}
\leq \frac{2(1\vvv r)}{1+r^2\vvv 2r\cos(\delta)}
\]
So with

\[
H\uuu\delta(z)=\frac{1}{2\pi}\int_{T\setminus E\uuu{2\delta}}\,
\frac{1\vvv |z|^2}{|e^{i\theta}-z|^2}\cdot d\mu\uuu (\theta)
\]
it follows that
\[
|H\uuu\delta(re^{i\phi})|\leq\frac{1}{2\pi}\cdot 
\frac{2(1\vvv r)}{1+r^2\vvv 2r\cos(\delta)}
\cdot \int\uuu{T\setminus E\uuu{2\delta}}\, |d\mu(\theta)|\tag{iii}
\]
for each $\phi\in E\uuu\delta$.
Since $H\uuu *$ is constructed via the
restriction of $\mu\uuu +$ to $E$, a similar reasoning gives:
\[
|H\uuu*(re^{i\phi})|\leq
\frac{1}{2\pi}\frac{2(1\vvv r)}{1+r^2\vvv 2r\cos(\delta)}
\cdot \mu\uuu +(E)\tag{iv}
\]
when $e^{i\phi}\in T\setminus E\uuu\delta$.
Next, by the constructions above we have

\[ 
H=H\uuu *+H\uuu \delta+H\uuu\nu
\]
where $\nu$ is the measure given by
the restriction of $\mu\uuu +$ to $E\uuu{2\delta}\setminus E$
minus $\mu\uuu \vvv$ restricted to
to $E\uuu{2\delta}$. So by the above the total variation
$||\nu||\leq 2\epsilon$ which gives

\[
\int\uuu 0^{2\pi}\, |H\uuu\nu(re^{i\theta})|\cdot d\theta
\leq 2\epsilon
\]


\medskip

\noindent
Deduce from the above that one has an inequality

\[
\int\uuu {E\uuu\delta}\, H(re^{i\phi})\cdot d\phi\geq
a\vvv \bigl[2\epsilon+\frac{1}{\pi}
\frac{2(1\vvv r)}{1+r^2\vvv 2r\cos(\delta)}
\cdot ||\mu||\bigl]\tag{*}
\]
Since $E$ is a null\vvv set, the
mean\vvv value integrals of $H$ behave in an "irregular fashion"
when $r\to 1$.









\bigskip



\centerline{\bf{1. The Herglotz integral }}

\bigskip

\noindent
Let $\mu$ be a real  Riesz measure on
the unit circle $T$.
Set
\[
g_\mu(z)=
\frac{1}{2\pi}\int_0^{2\pi}\,
\frac{e^{i\theta}+z}{e^{i\theta}-z}\cdot d\mu(\theta)\tag{*}
\]
This   analytic function is called the Herglotz
extension of the Riesz measure. 
Since $\mu$ is real it follows that
\[
\mathfrak{Re}\,g_\mu(z)=\frac{1}{2\pi}
\int_0^{2\pi}\,
\frac{1-|z[^2}{|e^{i\theta}-z|^2}\cdot d\mu(\theta)=H\uuu\mu(z)
\]
In particular the $L^1$\vvv norms from  (0.2) are uniformly bounded with
respect to $r$ when we integrate the absolute value of
$\mathfrak{Re}\,g\uuu\mu$.
But the conjugate harmonic function representing
$\mathfrak{Im}\, g\uuu\mu$ does not satisfy (0.2) in general.
However the following holds:

\medskip

\noindent
{\bf{1.1 Theorem.}}
\emph{For almost every $\theta$ there exists a radial limit}
\[
\lim\uuu{r\to 1} \,g_\mu(re^{i\theta})
\]
\medskip

\noindent
To prove Theorem 1.1 we shall use some tricks.
The Hahn\vvv decomposition
$\mu=\mu\uuu +\vvv \mu\uuu \vvv$
enables us to express $g\uuu\mu$ as a difference
$g\uuu 1\vvv g\uuu 2$ where  $g\uuu 1,g\uuu 2 $ both are
Herglotz extensions of
non\vvv negative Riesz measures and hence
$\mathfrak{Re}\,g\uuu\nu(z)>0$ in $D$.
Let us now discuss analytic functions with a positive real part.

\medskip

\noindent
{\bf{1.2 Exercise.}}
Let $f\in\mathcal O(D)$ where $\mathfrak{Re}\,f(z)>0$
and $\mathfrak{Im} f(0)=0$. Set $f=u+iv$ which gives
the analytic function
\[ 
\phi(z)=\log (1+u+iv)
\]
Here
\[ 
\mathfrak{Re}\,\phi=\log\,|1+u+iv|=
\frac{1}{2}\log [(1+u)^2+v^2]
\]
In particular $\mathfrak{Re}\,\phi>0$
so 
this  harmonic function has a radial limit almost everywhere.
We also know that $u$ has a radial limit almost everywhere
and from this the reader may conclude that there
almost everywhere exist
finite radial limits
\[
\lim\uuu{r\to 1}\, v^2(re^{i\theta})\tag{1}
\]
In order to determine the sign of these
radial limits we consider  the analytic function
\[ 
\psi= e^{\vvv u\vvv iv}
\]
Since $u>0$ we have
 $|\psi(z)|= e^{\vvv u(z)}\leq 1$
and hence $\psi(z)$ is a bounded analytic function in
$D$.
The Brothers
Riesz theorem shows that $\psi$ has a radial limit almost everywhere.
Finally, when we have a radial limit
\[
 \lim\uuu {r\to 1}\, e^{\vvv u(re^{i\theta})\vvv i v(re^{i\theta})}
\] 
and  in addition suppose that
$u$ has a radial limit, then it is clear that $v$ has a radial limit too.
\bigskip

\noindent
\emph {Proof of Theorem 1.1}
By the Hahn\vvv decomposition of $\mu$
the proof is reduced to the case $\mu\geq 0$ and 
Exercise 1.2 applies.

\bigskip

\noindent
{\bf{1.3 The case when $\mu$ is singular.}}
When this holds the radial limits of $\mathfrak{Re}\, g\uuu\mu$ are almost
everywhere zero.
With $v=\mathfrak{Im}\, g\uuu\mu$
there remains  to study  the almost 
everywhere defined function
\[ 
v^*(\theta)=\lim\uuu{r\to 1}\, v(re^{i\theta})
\]
It turns out that this  Lebesgue\vvv measurable function 
never is integrable when $\mu$ is singular.
In fact, the Brothers Riesz theorem
shows that if
there exists a constant $C$ such that

\[
\int\uuu 0^{2\pi}\, |v(re^{i\theta})|\cdot d\theta\leq C
\]
hold for all $r<1$, then the analytic function $g\uuu\mu$ belongs
to the Hardy space and its radial limits give an
$L^1$\vvv function $g^*(\theta)$ on the unit circle which
would entail that $\sigma$ is equal to the absolutely continuous
measure defined by $g^*$.
Thus,  for every singular measure $\mu$ one has

\[ 
\lim\uuu {r\to 1}\, \int\uuu 0^{2\pi}\,
\bigl| \,\mathfrak{Im} \,g\uuu\mu(re^{i\theta})\bigr | \cdot d\theta=+\infty\tag{*}
\]

\medskip

\noindent
{\bf{1.4 Example.}} Take the case where $\mu$ is 
$2\pi$ times the Dirac measure at $\theta=0$
which gives
the analytic function
\[ 
g(z)=\frac{1+z}{1\vvv z}
\]
It follows that
\[
v(re^{i\theta})= \vvv 2r\cdot \frac{\sin\theta}{1+r^2\vvv 2 r\cos\,\theta}
\]
and radial limits exist except for $\theta=\pi/2$ or $\vvv \pi/2$, i.e.

\[
v^*(\theta)=\vvv2\cdot \frac{\sin\theta}{2\vvv 2 \cos\,\theta}
\]
when $\theta$ is $\neq \pi/2$ and $\vvv \pi/2$.
At the same time
the reader may verify that $v^*(\theta)$ does not belong to $L^1(T)$
and  that
\[ 
\int\uuu 0^{2\pi}\, |v(re^{i\theta})|\cdot d\theta\simeq
\log\,\frac{1}{1\vvv r}
\] 
as $r\to 1$.
\medskip




\bigskip


\centerline{\bf{2. The Jensen\vvv Nevanlinna class}}



\bigskip

\noindent
Every Riesz measure $\mu$ on $T$
gives the zero\vvv free analytic function
\[ 
G\uuu\mu(z)=e^{g\uuu\mu(z)}\tag{*}
\]
Here 
$\log\,|G\uuu\mu (z)|=\mathfrak{Re}\,g\uuu\mu(z)$ which
gives the inequality

\[
\log^+|G\uuu\mu(z)|\leq \bigl|\mathfrak{Re}\,g\uuu\mu(z)\bigr|
\]
Applying  (0.2) we obtain:
\[
\int_0^{2\pi}\,\log^+|G\uuu\mu (re^{i\theta})|\cdot d\theta\leq ||\mu||\tag{**}
\]
for each $r<1$.
\medskip

\noindent{\bf{2.1 A converse.}}
Let $F(z)$ be a zero\vvv free analytic function in $D$ where
$F(0)=1$. Assume that there exists a constant $C$ such that
\[
\int_0^{2\pi}\,\log^+|F(re^{i\theta})|\cdot d\theta\leq C\tag{i}
\]
hold for each $r<1$.
The mean\vvv value property applied to the harmonic function
$H=\log\, |F|$
gives

\[
\int_0^{2\pi}\,|H(re^{i\theta})|\cdot d\theta=
2\cdot \int_0^{2\pi}\,\log^+|F(re^{i\theta})|\cdot d\theta\tag{ii}
\]
\medskip

\noindent
Hence (i) entails that $H$ satisfies (0.4)
and now the reader can settle the following:

\medskip

\noindent
{\bf{2.2 Exercise.}}
Show that (i) above entails that there exists a Riesz measure $\mu$ such that
$F=G\uuu\mu$ where the normalisation $F(0)=1$ gives
$\mu(T)=2\pi$.




\medskip

\noindent{\bf{2.3 Radial limits.}}
Whenever $g\uuu\mu$ has a radial limit for some
$\theta$ it is clear that $G\uuu\mu$ also has a radial limit in this
direction. So Theorem 1.1 implies that there
exists an almost everywhere defined boundary
function
\[
G^*\uuu\mu(\theta)=\lim\uuu{r\to 1}\,
G\uuu\mu(re^{i\theta})
\]







\noindent
The material above suggests the following:

\bigskip


\noindent {\bf 2.4 Definition.}
\emph{An analytic function $f$ in $D$
belongs to the Jensen-Nevanlinna class
if there exists a constant
$C$ such that}
\[
\int_0^{2\pi}\,\log^+|f(re^{i\theta})|\cdot d\theta\leq C
\] 
 \emph{hold for all $r<1$.
The family of Jensen-Nevannlina functions is denoted by
$\text{JN}(D)$.}
\medskip

\noindent
Above we described zero\vvv free functions in 
$\text{JN}(D)$.
Now we shall  study eventual    zeros of
functions in $\text{JN}(D)$.
Recall  that if $f\in\mathcal O(D)$ 
where $f(0)=1$ then  Jensen's formula gives:
\[
\sum_{|\alpha_\nu|<r}\,\text{Log}\,\frac{r}{|\alpha_\nu|}=
\frac{1}{2\pi}\int_0^{2\pi}\,
\log\,|f(re^{i\theta})\bigr|\cdot d\theta\quad\colon\quad 0<r<1\tag{*}
\]
where the left hand side is the sum of zeros of $f$ in the disc 
$D_r$.
\medskip

\noindent
{\bf{A notation.}}
If $f\in\mathcal O(D)$ and $r<1$ we set
\[
\mathcal T\uuu f(r)=\int_0^{2\pi}\,\log^+|f(re^{i\theta})|\cdot d\theta
\] 

\noindent
Since $\log\,|f(re^{i\theta})\bigr|\leq \log^+|f|$ it follows that
\[
\sum_{|\alpha_\nu|<r}\,\text{Log}\,\frac{r}{|\alpha_\nu|}\leq
\mathcal T_f(r)
\]
So if $f\in \text{JN}(D)$ we can pass to the limit 
as $r\to 1$ and conclude that the positive series
\[
\sum\,\text{Log}\,\frac{1}{|\alpha_\nu|}<\infty\tag{**}
\] 
where the sum is taken over all zeros  in $D$.
Next, recall form XX that the positive series  (**) converges
if and only if

\[
\sum\,(1-|\alpha_\nu|<\infty\tag{***}
\]
When (***) holds
we say that
the sequence $\{\alpha\uuu\nu\}$ satisfies the Blaschke condition.
Hence we have proved:

\medskip

\noindent
{\bf 2.5 Theorem.} \emph{Let $f$ be in  JN(D). Then 
its  zero set satisfies the Blaschke condition.}


\newpage



\centerline
{\bf 3. Blaschke products.}
\bigskip

\noindent
Consider an infinite sequence
$\{\alpha_\nu\}$ in $D$  which satisfies $|\alpha_1|\leq |\alpha_2|\leq\ldots$.
For every $N\geq 1$ we put:
\[ 
B\uuu N(z)=
\prod\uuu{\nu=1}^{\nu=N}\,\frac{|\alpha_\nu|}{\alpha_\nu}\cdot
\frac{\alpha_\nu-z}{1-\bar\alpha_\nu z}
\]
We are going to prove that the sequence of analytic function
$\{B\uuu N\}$ converge in $D$ to a limit function
$B(z)$ expressed by the infinite product

\[
B(z)=
\prod\uuu{\nu=1}^\infty\,
\frac{|\alpha_\nu|}{\alpha_\nu}\cdot
\frac{\alpha_\nu-z}{1-\bar\alpha_\nu z}
\]

\noindent
To prove this  we first analyze
the individual factors.
For each non\vvv zero $\alpha\in D$
we set
\[ 
B\uuu\alpha(z)=\frac{|\alpha|}{\alpha}\cdot
\frac{\alpha-z}{1-\bar\alpha z}
\]


\noindent
{\bf{Exercise.}}
Show that
\[
B_\alpha(z)=
|\alpha|\cdot\frac{1-z/\alpha}{1-\bar\alpha z}=
|\alpha|+\frac{|\alpha|^2-1}{1-\bar\alpha z}
\cdot\frac{|\alpha|}{\alpha}\cdot z\tag{i}
\]
and conclude that
\[
B_\alpha(z)\vvv 1=(|\alpha|-1)\cdot[1+\frac{|\alpha|+1}{1-\bar\alpha z}
\cdot\frac{|\alpha|}{\alpha}\cdot z]\tag{ii}
\]
Finally, use the triangle inequality to show the inequality
\[
\max_{|z|=r}\,|B_\alpha(z)-1|\leq (1-|\alpha|)\cdot
(1+\frac{2r}{1-r})=\frac{1+r}{1-r}\cdot (1-|\alpha|)\tag{iii}
\]


\noindent
{\bf{.1 The convergence of (**)}}
From (iii) and general results about product series
we get the requested convergence in (**).
In fact, when $|z|\leq r<1$ stays in a compact disc
the Blaschke condition and (iii) entail that
\[
\sum\uuu{\nu=1}^\infty \max_{|z|=r}\,|B_\alpha(z)-1|<\infty
\]
which implies that (**) converges uniformly on $|z|\leq r$ to an
analytic function and since
$r<1$ is arbitrary we get a limit function $B(z)\in\mathcal O(D)$.
\medskip

\noindent
{\bf{3.2 Exercise.}} The rate of convergence in $|z|\leq r$
 can be described as follows:
For each  $N\geq 1$ we set
\[ 
G_N(z)=
\prod_{\nu=N+1}^\infty\,
B_{\alpha_\nu}(z)\quad\colon\quad \Gamma_N=
\sum_{\nu=N+1}^\infty\,1-|\alpha_\nu|
\]

\noindent
With $r<1$ kept fixed
we choose $n$ so large that
\[
\frac{1+r}{1-r}\cdot (1-|\alpha_\nu|)\leq \frac{1}{2}\quad\colon\quad \nu>N
\]
Show that this gives:
\[
\max_{|z|=r}\,
|G_N(z)-1|\leq 8\cdot\frac{1+r}{1-r}\cdot \Gamma_N
\]

\medskip

\noindent
Since the Blaschke condition implies that
$\Gamma\uuu N\to 0$ as $N\to\infty$
this gives a control for the rate of convergence in
$|z|\leq r$.



\bigskip

\centerline {\bf 3.3 Radial limits of $B(z)$}
\bigskip

\noindent
When $z=e^{i\theta}$ the absolute value 
$|B\uuu\alpha(e^{i\theta}|=1$.
So $B(z)$ is the product of analytic functions where every
term has absolute value $\leq 1$ and hence
the maximum norm
\[ 
\max\uuu{z\in D}\, |B(z)|\leq 1
\]





\medskip


\noindent
Since the  analytic function $B(z)$ is bounded,
Fatou's Theorem from Section XX  gives
an almost everywhere defined  limit function
\[ 
B^*(e^{i\theta})=
\lim_{r\to 1}\, B(re^{i\theta})\tag{1}
\]
where the radial convergence holds almost everywhere.
Moreover, the Brothers Riesz theorem
gives:
\[
\lim_{r\to 1}\int_0^{2\pi}\,
|B^*(e^{i\theta})-B(re^{i\theta})|d\theta=0\tag{2}
\]

\medskip

\noindent
{\bf{3.4 Theorem.}}\emph{ The equality}
\[
|B^*(e^{i\theta})|=1\quad\text{holds almost everywhere}
\tag{*}
\] 
\medskip

\noindent
\emph{Proof.}
Since $|B^*|\leq 1$ it is clear that (*) follows if we have proved that
\[
\int\uuu 0^{2\pi}\,|B^*(e^{i\theta})|\cdot d\theta=1\tag{i}
\]
Using (2) above and the triangle inequality we get (i) if we prove the limit formula
\[
\lim\uuu {r\to 1}\,
\int\uuu 0^{2\pi}\,|B(re^{i\theta})|\cdot d\theta=1
\tag{ii}
\]
To show (ii) we will apply Jensen's formulas to $B(z)$ in discs
$|z|\leq r$. 
The convergent product which defines $B(z)$ gives

\[
B(0)=\prod\,\log\,|\alpha\uuu\nu|
\]
Next, for $0<r<1$ Jensen's formula gives
\[
\log B(0)=\sum\uuu{\nu=1}^{\rho(r)}\,\log\,\frac{|\alpha\uuu\nu|}{r}
+
\frac{1}{2\pi}\int\, \int\uuu 0^{2\pi}\,\log\,|B(re^{i\theta})|\cdot d\theta
\]
where $\rho(r)$ is the largest $\nu$ for which $|\alpha\uuu\nu|=r$.
It follows that
\[
\frac{1}{2\pi}\int\, \int\uuu 0^{2\pi}\,\log\,|B(re^{i\theta})|\cdot d\theta
\geq \sum\uuu{\nu=1}^{\rho(r)}\,\log\,\frac{r}{|\alpha\uuu\nu|}\vvv
\sum\uuu{\nu=1}^\infty \,\log\,\frac{1}{|\alpha\uuu\nu|}\tag{1}
\]
Next, with $\epsilon>0$ we find an integer $N$ such that
\[
\sum\uuu{\nu=1}^{\nu=N} \,\log\,\frac{1}{|\alpha\uuu\nu|}<\epsilon \tag{2}
\]
Since $|\alpha\uuu\nu|\to 1$
here exists $r\uuu*$ such that
\[ 
r\geq r\uuu *\implies \rho(r)\geq N\tag{3}
\]
When (3) holds it follows from (1\vvv 2) that
\[
\frac{1}{2\pi}\int\, \int\uuu 0^{2\pi}\,\log\,|B(re^{i\theta})|\cdot d\theta
\geq \sum\uuu{\nu=1}^{\rho(r)}\,\log\,\frac{r}{|\alpha\uuu\nu|}\vvv
\sum\uuu{\nu=1}^{\rho(r\uuu *)}\,\log\,\frac{1}{|\alpha\uuu\nu|}\vvv\epsilon\tag{4}
\]
In the first sum every term is $\geq 1$
so we get
a better inequality when the sum is restricted to $\nu\leq\rho(r\uuu *)$, i.e. we have
\[
\frac{1}{2\pi}\int\, \int\uuu 0^{2\pi}\,\log\,|B(re^{i\theta})|\cdot d\theta
\geq \sum\uuu{\nu=1}^{\rho(r\uuu *)}\,\log\,\frac{r}{\alpha\uuu\nu|}\vvv
\sum\uuu{\nu=1}^{\rho(r\uuu *)}\,\log\,\frac{1}{\alpha\uuu\nu|}\vvv\epsilon\tag{5}
\]
Here (5) hold for every $r\uuu *<r<1$ and a passing to the limit 
as $r\to 1$ where we only have a finite sum
$1\leq\nu\leq \rho(r\uuu *)$ above
we conclude that

\[
\lim\uuu{r\to 1}\, \frac{1}{2\pi}\int\, \int\uuu 0^{2\pi}\,\log\,|B(re^{i\theta})|\cdot d\theta
>\vvv \epsilon
\]
Since $\epsilon>0$ is arbitrary we have proved (ii) and hence also Theorem 3.54.





\bigskip


\centerline {\bf 3.5 Division  by Blaschke products.} 


\bigskip

\noindent
Let $F\in\mathcal O(D)$ and assume that  its zero set in
$D$ is a Blaschke sequence $\{\alpha_\nu\}$.
Then we obtain the analytic function
\[ 
G(z)=\frac{F(z)}{B(z)}
\]


\noindent
Here  $G$ has no zeros in $D$
and we can  construct the analytic function
$\text{Log}\,G(z)$.
Set
\[
\mathcal I^+_G(r)=\int_0^{2\pi}\,
\log^+|\,G(re^{i\theta})|\cdot d\theta
\]
Since $\log^+[ab|\leq \log^+|a|+\log^+|b|$ for 
every pair of complex numbers we get:

\[
\mathcal I^+_G(r)\leq
\mathcal I^+_F(r)+
\int_0^{2\pi}\,
\log^+\frac{1}{|\,B(re^{i\theta})|}\cdot d\theta\tag{1}
\]
The last nondecreasing function is
$\leq \log^+\frac{1}{|\,B(0)|}$ for every $r$ which gives 
\[
\mathcal I^+_G(r)\leq
\mathcal I^+_F(r)+\log^+\frac{1}{|\,B(0)|}\tag{2}
\] 
for every $r<1$.
When $F\in\text{JN}(D)$ this implies that
$G$ also belongs to $\text{JN}(D)$. Hence we have proved

\medskip
\noindent{\bf{3.6 Theorem.}}
\emph{For each $f\in\text{JN}(D)$
the function $\frac{f}{B\uuu f}$ also
belongs to $\text{JN}(D)$, where $B\uuu f(z)$ is the 
Blaschke product formed by zeros of $f$ outside the origin.}
\bigskip

\noindent{\bf{3.7 Conclusion.}}
Theorem 3.6 and the material in section 2 about zero\vvv free
Jensen\vvv Nevanlinna functions  give
the following factorisation  formula:

\medskip

\noindent{\bf{3.8 Theorem.}}
\emph{For each $f\in\text{JN}(D)$ there exists a unique
real Riesz measure $\mu$ on $T$ with $\mu(T)=0$
such that}
\[
f(z)=az^k\cdot B\uuu f(z)\cdot
e^{g\uuu\mu(z)}
\]
\emph{where $k\geq 0$ is the order of zero of $f$
at $z=0$ and $a\neq 0$ a constant. Moreover}
\[ 
\mu=\log\, |f(e^{i\theta})|\cdot d\theta+\sigma
\]
\emph{where $\sigma$ is the singular part of $\mu$.}

\medskip



\noindent
{\bf{3.9 Outer factors.}}
In Theorem 3.8 we get the analytic function
\[ 
\mathfrak{O}\uuu f(z)=e^{g\uuu{\log |f|}(z)}
\]
We refer to $\mathfrak O\uuu f$ as the outer part of $f$.
\medskip


\noindent
{\bf{3.10 A division result.}}
Consider a pair $f,h$ in $\text{JN}(D)$
which gives the analytic function in $D$ defined by

\[ 
k(z)= 
\frac{\mathfrak{O}\uuu h(z)}
{\mathfrak{ O}\uuu f(z)}
\]
By (2.3) there exists the almost everywhere defined quotient on $T$
\[ 
k^*(\theta)= \frac{\mathfrak{O}\uuu h^*(\theta)}
{\mathfrak{ O}\uuu f^*(\theta)}
\]

\medskip

\noindent
{\bf{3.11 Theorem.}}
\emph{Assume that $k^*\in L^1(T)$. Then 
$k^*$ belongs to the Hardy space $H^1(T)$.}
\medskip

\noindent
\emph{Proof.}
In $D$ there exists the harmonic  function
\[
k(z)=\log\,|\mathfrak{O}\uuu h(z)|\vvv\log\,\mathfrak |O\uuu f(z)|
\] 
The two harmonic functions in the right hasnd side
have by definition boundary functions in $L^1(T)$ and
Poisson's formula 
gives  for each point $z=re^{i\theta}$:

\[ 
\log |k(re^{i\theta})|=
\frac{1}{2\pi}\int\uuu 0^{2\pi}\, \frac{1\vvv r^2}{1+r^2\vvv
2r\cos(\phi\vvv \theta)}\cdot \log |k^*(\phi)|\cdot d\phi
\]
By the general mean\vvv value inequality
from (xx) the left hand side is majorized by:
\[ 
\leq \log
\bigl[\frac{1}{2\pi}\int\uuu 0^{2\pi}\, \frac{1\vvv r^2}{1+r^2\vvv
2r\cos(\phi\vvv \theta)}\cdot |k^*(\phi)|\cdot d\phi\bigr]
\]
Taking exponentials on both sides we get

\[
|k(re^{i\theta})|\leq 
\frac{1}{2\pi}\int\uuu 0^{2\pi}\, \frac{1\vvv r^2}{1+r^2\vvv
2r\cos(\phi\vvv \theta)}\cdot |k^*(\phi)|\cdot d\phi
\]
Now we integrate both sides with respect to $\theta$. Since
\[
\frac{1}{2\pi}\int\uuu 0^{2\pi}\, \frac{1\vvv r^2}{1+r^2\vvv
2r\cos(\phi\vvv \theta)}\cdot d\theta=1
\] 
for every $\phi$, it follows that
\[
\int\uuu 0^{2\pi}\, |k(re^{i\theta})|\cdot d\theta\leq
\int\uuu 0^{2\pi}\, |k^*(e^{i\phi})|\cdot d\phi
\]
This proves that the $L^1$\vvv norms of $\theta\to k(re^{i\theta})$
are bounded which means that $k$ belongs to $H^1(T)$.
Moreover, by the Brother's Riesz theorem
there exist radial limits almost everywhere
so we have also the equality
\[
\lim\uuu{r\to 1}\, k(re^{i\theta})= k^*(\theta)
\] 
almost everywhere. This proves that $k^*$ is the boundary value function of
the $H^1(T)$\vvv function $k$.
\medskip

\noindent
{\bf{3.12 Exercise.}}
Show by a similar technique that if we instead assume that
$k^*$ is square\vvv integrable, i.e. if $k^*\in L^2(T)$ then
$k(z)$ belongs to the Hardy space $H^2(T)$.
\bigskip

\noindent
{\bf{3.13 Inner functions.}}
If $\sigma$ is a non\vvv negative and singular measure on $T$
we get the bounded analytic function
\[
G\uuu{\vvv\sigma}(z)=
e^{\vvv g\uuu\sigma(z)}\tag{1}
\]
Keeping $\sigma$ fixed we denote this function with $f$.
Here 
\[
\lim\uuu{r\to 1}\, |f(re^{i\theta})|=1
\] 
holds almost everywhere.
So the boundary function $f^*(\theta)$ has absolute value almost
everywhere.
The class of analytic functions obtained via (1) is denoted by
$\mathfrak I\uuu *(D)$ and are called zero\vvv free inner functions.
In general a bounded analytic function $f$ in $D$
whose boundary values have absolute value almost everywhere
is called an inner function and this class is denoted by
$\mathfrak I(D)$.

\medskip

\noindent
{\bf{3.14 Exercise.}}. Use the factorisation in Theorem 3.8
to show that
every $f\in\mathfrak I(D)$ is a product

\[ 
f=B\uuu f\cdot f\uuu *
\] 
where $f\uuu *$ is a zero\vvv free inner function.
\medskip

\noindent
{\bf{3.15 The case of signed singular measures.}}
Let $\mu=\mu\uuu +\vvv \mu\uuu\vvv$ be a signed singular measure
where $\mu\uuu +\neq 0$.
We get the analytic function $G\uuu\mu$ and from the above we know that it
has radial limits almost everywhere and since $\mu$ is singular the boundary
function $G^*\uuu\mu$ has absolute value almost everywhere.
Here the presence of $\mu\uuu +$ implies that the analytic function
$G\uuu\mu$ is unbounded.
In fact, its maximum modules function 
\[
M(r)=\max\uuu{|z|=r|}\, |G\uuu\mu(z)|
\]
has a quite rapid growth as $r\to 1$.
Moreover one always has
\[
\lim\uuu{r\to 1}\, \int\uuu 0^{2\pi}\,
|G\uuu\mu(re^{i\theta})|\cdot d\theta=+\infty\tag{*}
\]
in other words, $G\uuu\mu$\vvv functions constructed by
signed measures with non\vvv zero negative part never belongs to
$H^1(T)$.
\medskip


\noindent
{\bf{3.16 Exercise.}} Prove (*) above using the divergence in (*) from 1.3.











\bigskip

\centerline{\bf{4. Invariant subspaces of $H^2(T)$}}
\bigskip


\noindent
The Hilbert space $L^2(T)$ of square integrable functions on
$T$  contains the closed subspace $H^2(T)$
whose elements are boundary values of analytic functions in
$D$.
If f $f\in H^2(T)$
it is expanded as
\[ 
\sum\uuu{n=0}^\infty\, a\uuu n\cdot e^{in\theta}
\]
and Parseval's theorem gives  the equality

\[
\sum\uuu{n=0}^\infty\, |a\uuu n|^2=\frac{1}{2\pi}\cdot
\int\uuu 0^{2\pi}\, 
|f(e^{i\theta})|^2 d\theta
\]
Moreover, in $D$ we get the analytic function
$f(z)=\sum\, a\uuu nz^n$ where
radial limits
\[ 
\lim\uuu {r\to 1}\, f(re^{i\theta})= f(e^{i\theta})
\]
exist almost everywhere.in fact, this follows via
the Brothers Riesz theorem and the inclusion 
$H^2(T)\subset  H^1(T)$.
We shall  study subspaces of $H^2(T)$
which are invariant under multiplication by
$e^{i\theta}$. 

\medskip

\noindent
{\bf{4.2 Definition.}}
\emph{A closed subspace $V$ of $H^2(T)$ is called invariant if
$e^{i\theta}V\subset V$.}
\bigskip




\noindent
{\bf{4.3 Theorem}}
\emph{Let $V$ be an invariant subspace of $H^2(T)$.
Then there exists
$w(\theta)\in H^2(T)$ 
whose absolute value is one almost everywhere
and}
\[ 
V=H^2(T)\cdot w
\]
\medskip


\noindent
\emph{Proof.}
First we show that that $e^{i\theta}V$ is a proper subspace of $V$.
For an equality $e^{i\theta}V=V$  gives
$e^{in\theta}V=V$ for every $n\geq 1$ which entails that if 
$0\neq f\in V$ then 
$f=e^{in\theta}\cdot g\uuu n$ for some $g\uuu n\in H^2(T)$. This  means
that the Taylor series of $f$ at $z=0$ starts with order $\geq n$
which  cannot
hold
for every $n$ unless $f$ is identically zero.
So now $e^{i\theta}V$ is a proper closed subspace of  $V$
which gives some $0\neq w\in V$
which is $\perp$ to $e^{i\theta}V$. It follows that

\[
\langle w,e^{in\theta} \cdot w\rangle
\int\uuu 0^{2\pi}\, w(e^{i\theta})\bar w(e^{i\theta})\cdot e^{\vvv in\theta}
\cdot d\theta=0
\]
hold for every $n\geq 1$.
Since $w\cdot \bar w=|w|^2$ is real\vvv valued we conclude that
this function is constant and we can normalize $w$ so that
$|w(\theta)|=1$ holds almost everywhere.
There remains to prove the equality
\[
V=H^2(T)\cdot w\tag{i}
\]
Since $|w|=1$ almost everywhere the right hand side is a closed subspace of
$V$. If it is proper we find
$0\neq u\in V$ where $u\perp H^2(T)w$ which gives

\[
\int\uuu 0^{2\pi}\, u(e^{i\theta})\bar w(e^{i\theta})\cdot e^{\vvv in\theta}
\cdot d\theta=0\quad\colon\quad n\geq 0\tag{ii}
\]
Taking complex conjugates we get

\[
\int\uuu 0^{2\pi}\, w(e^{i\theta})\bar u(e^{i\theta})\cdot e^{in\theta}
\cdot d\theta=0\quad\colon\quad n\geq 0\tag{iii}
\]
At the same time
$w\perp e^{i\theta}V$ which entails that
\[
\int\uuu 0^{2\pi}\, w(e^{i\theta})\bar u(e^{i\theta})\cdot e^{\vvv in\theta}
\cdot d\theta=0\quad\colon\quad n\geq 1\tag{iv}
\]
Together (iiii\vvv iv) imply that
$w\bar u$ has vanishing Fourier coefficients and is therefore identically zero which gives
$u=0$ and proves that $V=H^2(T)\cdot w$ must hold.
\bigskip

\noindent
{\bf{4.4 Examples.}}
Let $B(z)$ be a non\vvv constant Blaschke product.
Now $|B(e^{i\theta})|=1$  holds almost everywhere and
the presence of zeros of $B(z)$ in $D$ show that
$H^2(T)\cdot B$ is a proper 
and invariant subspace of $H^2(T)$.
Next, let
$\sigma$ be a singular Riesz measure on $T$
which is real and non\vvv negative.
We get the analytic function
\[ 
f(z)= e^{\vvv g\uuu\sigma(z)}
\]
Here
\[ 
|f(z)|= e^{\vvv H\uuu\sigma(z)}
\] 
and since $\sigma\geq 0$ we have $H\uuu \sigma(z)\geq 0$ and hence
$|f(z)|\leq 1$.
So $f$ is a bounded analytic function in $D$ and
in particular it belongs to $H^2(T)$. Moreover
we know from XX that the boundary function $f(e^{i\theta})$ has absolute
value one almost everywhere.
So $H^2(T)\cdot f$ is an invariant subspace of $H^2(T)$ and the
question arises if it is proper or not.
In contrast to the case for Blaschke functions $B$ above this is not obvious since
$f$ has no zeros in $D$.
However it turns out that one has

\medskip

\noindent
{\bf{4.5 Theorem.}} \emph{Let $\sigma$ be a 
singular and non\vvv negative 
Riesz measure which is not
identically zero. Then $H^2(T)\cdot e^{\vvv g\uuu\mu}$
is a proper subspace of $H^2(T)$.}
\medskip

\noindent
\emph{Proof.} 
Set $w(\theta)= e^{\vvv g\uuu\mu(e^{i\theta})}$. For the analytic function
$w(z)$ in the disc  its value at $z=0$ becomes
\[ 
w(0)=e^{\vvv g\uuu\mu(0}= e^{\vvv \sigma(T)/2\pi}
\]
Next, 
if $P(z)$ is a polynomial
we have
\[
\frac{1}{2\pi}\int\uuu 0^{2\pi}\, |P(\theta)w(\theta) \vvv 1|^2d\theta
=\frac{1}{2\pi}\int\uuu 0^{2\pi}\, |P(\theta)|^2\cdot d\theta
+1+2\mathfrak{Re}\,[\int
\frac{1}{2\pi}\int\uuu 0^{2\pi}\, P(\theta)\cdot w(\theta)\cdot d\theta]
\]
By Cauchy's formula the last term becomes
\[
2\mathfrak{Re}(P(0)w(0))= 2w(0)\cdot \mathfrak{Re}(P(0))
\]
By (i) we have $0<w(0)<1$ and if $||P||\uuu 2$ is the $L^2$\vvv norm of $P$
the right hand side majorizes
\[
||P||\uuu 2^2+1\vvv 2w(0)\cdot |P(0)|
\]
We have also the inequality
\[
|P(0)|\leq ||P||\uuu 2
\]
So if we set $\rho=||P||\uuu 2$
then we have shown that

\[
\frac{1}{2\pi}\int\uuu 0^{2\pi}\, |P(\theta)w(\theta) \vvv 1|^2d\theta
\geq \rho^2+1\vvv 2w(0)\cdot \rho
\]
Now we notice that the right hand side is $\geq 1\vvv w(0)^2$
for every $\rho$.
Since $P$ is an arbitrary polynomial we conclude that
the $L^2$\vvv distance of 1 to the subspace
$H^2(T)\cdot e^{\vvv g\uuu\mu}$
is at least
\[
1\vvv w(0)^2= 1\vvv e^{\vvv 2\sigma(T)}\tag{*}
\]








\bigskip

\centerline{\bf{5. Beurling's closure theorem.}}
\medskip

\noindent
A zero\vvv free  function $f\in H^2(T)$ is of outer type when
\[ 
f(z)=G\uuu\mu(z)
\] 
where $\mu$ is the absolutely continuous Riesz measure
$\log|f(e^{i\theta}|$.
The following result is due to Beurling in   [Beur]:
\medskip

\noindent
{\bf{5.1 Theorem.}}
\emph{For every nonzero $f\in H^2(T)$ of outer type 
the closed invariant subspace generated by analytic polynomials $P(z)$ times
$f$ is equal to $H^2(T)$.}
\medskip

\noindent
\emph{Proof.}
If the density fails we find
$0\neq g\in H^2(T)$ such that

\[
\int\uuu 0^{2\pi}\, e^{in\theta} f(e^{i\theta})\cdot \bar g(e^{i\theta}) \cdot d\theta=0
\tag{i}
\] 
for every $n\geq 0$.
By Cauchy\vvv Schwarz the product $f\cdot \bar g$
belongs to $L^1(T)$ and (i) implies that this function
is of the form $e^{i\theta}\cdot h(\theta)$ where
$h\in H^1(T)$.
So on $T$ we have almost everywhere:
\[ 
\bar g(e^{i\theta})=e^{i\theta}\cdot \frac{h(e^{i\theta})}{f(e^{i\theta})}\tag{ii}
\] 
Now we take the outer factor $\mathfrak{O}\uuu h$
whose absolute value is equal to $|k|$ almost everywhere on $T$. It follows that
\[
|g^*(\theta)|= 
 \frac{\mathfrak{O}\uuu h^*(\theta)}
{\mathfrak{ O}\uuu f^*(\theta)}\tag{iii}
\]
Since $g\in H^2(T)$ 
Exercise 3.12 shows that 
the quotient in (ii) is
the boundary value of an analytic  function in $H^2(T)$ which implies that
the conjugate function $\bar g$ also belongs to $H^2(T)$. But then
$g$ must be a constant and this constant is zero
because the factor $e^{i\theta}$ appears in (ii).
So $g$ must be zero which gives a contradiction and
the requested density is proved.

\bigskip

\centerline{\bf{5.2 Szegö's theorem.}}
\bigskip

\noindent
Let $w(\theta)$ be  real\vvv valued and non\vvv negative
function in $L^1(T)$ and  $\mathcal P\uuu 0$
is the space of analytic polynomials $P(z)$ where $P(0)=0$.
Put


\[ 
\rho(w)=\frac{1}{2\pi}\inf\uuu{P\in\mathcal P\uuu 0}\int\uuu 0^{2\pi}\,
\bigl| 1\vvv P(e^{i\theta})\bigr|\cdot w(\theta)\cdot d\theta
\]
\medskip

\noindent
{\bf{5.3 Theorem.}}
\emph{One has the equality}

\[ 
\rho(w)=\text{exp}\, [\frac{1}{2\pi}\int\uuu 0^{2\pi}\,  \log w(\theta)\cdot d\theta]
\]
\medskip

\noindent
\emph{Proof.} First we consider the case
when
$\log |w|\in L^1(T)$.
Multiplying $w$ with a positive constant we may assume that
\[
\int\uuu 0^{2\pi}\,\log w(\theta)\cdot d\theta=0\tag{i}
\]
Now we must show that
$\rho(w)=1$.
To prove this we use that $\log w\in L^1(T)$ and construct the analytic function
\[
f(z)=G\uuu {\log w(z)}
\]
So $f$ is an outer function where
on $T$ one has
\[ 
|f(e^{i\theta})|=e^{\log|w(\theta)|}=
w(\theta)\tag{ii}
\]
Hence $f\in H^1(T)$
and (1) gives  $f(0)=1$.
Let us now consider some $P(z)\in\mathcal P\uuu 0$
and set
\[
F(z)=(1\vvv P(z))f(z)
\]
Again $F(0)=1$ and $F\in H^1(T)$ which gives the inequality
\[
 1\leq\int\uuu 0^{2\pi}\, |F(e^{i\theta})|\cdot d\theta\tag{iii}
\]
By (ii) this means that
\[ 
1\leq \int\uuu 0^{2\pi}\, |1\vvv  P(e^{i\theta})|\cdot 
w(\theta) \cdot d\theta
\] Since this hold for every $P\in\mathcal P\uuu 0$ we have proved the inequality
\[
\rho(w)\geq 1\tag{iv}
\]
To prove the reverse inequality we
apply Beurling's theorem to the outer function $f$. This gives
a sequence of polynomials $\{Q\uuu n(z)\}$ such that
\[
\lim\uuu{n\to \infty}\, ||Q\uuu n\cdot f\vvv 1||\uuu 1=0\tag{v}
\] 
where we use the norm on $H^1(T)$.
Since $f(0)=1$ it follows that
$Q\uuu n(0)\to 1$ and we can normalize the approximating
sequence so that $Q\uuu n(0)=1$ for every $n$
and write $Q\uuu n=1\vvv P\uuu n$ with $P\uuu n\in\mathcal P\uuu 0$.
Finally using (ii) we get
\[
\lim\uuu{n\to\infty}\int\uuu 0^{2\pi}\, |1\vvv P(e^{i\theta})|\cdot w(\theta)\cdot d\theta=1
\]
This gives $\rho(w)\geq 1$ and Szegö's theorem is proved for the case A above.
\medskip

\noindent
\emph{B. The case when 
$\log^+\frac{1}{|w|}$
is not integrable}.
Here we must show 
that
$\rho(w)=0$ and the  proof of this is left as an exercise to the reader.




\bigskip

\centerline{\bf{6. The Helson\vvv Szegö theorem}}

\bigskip

\noindent
A trigonometric polynomial
on the unit circle is of the form
\[
P(\theta)=\sum\, a\uuu n\cdot e^{in\theta}
\]
where $\{a\uuu n\}$  are complex numbers and only
a finite family is $\neq 0$.
The conjugation operator $\mathcal C$ is defined by

\[
\mathcal C(P)=i\cdot \sum\uuu{n<0}\, a\uuu n\cdot e^{in\theta}\vvv
i\cdot \sum\uuu{n>0}\, a\uuu n\cdot e^{in\theta}\tag{*}
\]
Let $w(\theta)$ be a non\vvv negative function in
$L^1(T)$ and assume also that
$\bigl|\log\,|w|\,\bigr|\in L^1(T)$.
\medskip

\noindent
{\bf{6.1 Definition.}}
\emph{A $w$\vvv function 
as above is of Helson\vvv Szegö type if there exists a constant $C$ such that}
\[
\int\uuu 0^{2\pi}\, |\mathcal C(P)(e^{i\theta})|^2 \cdot w(\theta)\cdot d\theta
\leq C\cdot \int\uuu 0^{2\pi}\, |P(e^{i\theta})|^2\cdot w(\theta)\cdot d\theta
\tag{*}
\] 
\emph{hold for all trigonometric polynomials}.
\medskip

\noindent
Notice that if (*) holds for some $w$ then it holds for every function of the form 
$\rho\cdot w$ where
$0<c\uuu 0\leq \rho(\theta)\leq c\uuu 1$ for some pair of
positive constants. Or equivalently, with $w$ replaced by
$e^u\cdot w$ for some bounded function $u(\theta)$.
With this in mind we announce the result below which is due to Helson and Szegö in [HS]:

\medskip

\noindent
{\bf{6.2 Theorem.}}
\emph{A function $w(\theta)$ is of the Helson\vvv Szegö type if and only if
there exists a bounded function $u$ and 
a function $v(\theta)$ for which the maximum norm of $|v|$ over $T$ is $<1$
and}
\[ 
w(\theta)= e^{u(\theta)+ v^*(\theta)}
\] 
\emph{where $v^*$ is the harmonic conjugate of $v$.}
\bigskip

\noindent
The proof requires several steps. The first part is an exercise on
norms on the Hilbert space $L^2(w)$ which is left to the reader.
\medskip

\noindent
{\bf{Exercise.}}
Show that $w$ is of the Helson\vvv Szegö type if and only if there exists a constant
$\rho<1$ such that

\[
\bigl |\,\int\uuu 0^{2\pi}\,
P(\theta)\cdot e^{\vvv i\theta}\cdot Q(\theta)\cdot w(\theta)\cdot d\theta\,\bigr|
\leq \rho\cdot ||P||\uuu w\cdot ||Q||\uuu w\tag{*}
\]
hold for all pairs $P,Q$ in $\mathcal P\uuu 0$.
\medskip

\noindent
{\bf{6.3 The outer function $\phi$}}.
We define the analytic function $\phi(z)$ by

\[
\phi(z)=\text{exp}\bigl[\, \frac{1}{2\pi}\int\uuu 0^{2\pi}\,
\frac{e^{i\theta}+z}{e^{i\theta}\vvv z}\cdot 
\log 
(\sqrt{w(\theta)})\cdot d\theta\,\bigr]
\]
Since
$\log \,
\sqrt{w(\theta)}=
\frac{1}{2}\cdot \log\, 
w(\theta)$ is in $L^1(T)$ it means that
$\phi(z)$ is an outer function and
on the unit circle we have  the equality
\[ 
|\phi(\theta)|^2=w(\theta)\tag{1}
\]
Using (1) we find a 
real\vvv valued function $\gamma(\theta)$ such that
\[
w(\theta)= \phi^2(\theta)\cdot e^{i\gamma(\theta)}\tag{2}
\]


\noindent
Next,  (1) implies  that the weighted $L^2$\vvv norm $||P||\uuu w$
is equal to the standard $L^2$\vvv norm of $\phi\cdot P$ on
$T$. Hence (1) holds if and only if
\[
\bigl |\,\int\uuu 0^{2\pi}\,
\phi(\theta)P(\theta)\cdot e^{\vvv i\theta}\cdot 
\phi(\theta)Q(\theta)\cdot e^{i\gamma(\theta)}\cdot d\theta\,\bigr|
\leq \rho\cdot ||\phi\cdot P||\uuu 2 \cdot ||\phi\cdot Q||\uuu 2\tag{3}
\]
hold for all pairs $P,Q$ in $\mathcal P\uuu 0$.
Now we use that $\phi$ is outer which by Beurling's closure
theorem means that $\mathcal P\uuu 0\cdot \phi$ is dense in
$H\uuu 0^2(T)$.
Hence (3) is equivalent to 

\[
\bigl |\,\int\uuu 0^{2\pi}\,
F(\theta)\cdot e^{\vvv i\theta}\cdot G(\theta)
\cdot  e^{i\gamma(\theta)}
\cdot d\theta\,\bigr|
\leq \rho\cdot ||F||\uuu 2 \cdot ||G||\uuu 2\tag{4}
\]
for all pairs $F,G$ in $H^2\uuu 0(T)$.
\medskip

\noindent
Next, in XX we prove that every $f\in H^1\uuu 0(T)$
admits a factorization $f=F\cdot G\cdot e^{\vvv i\theta}$
for a pair $F,G$  where $||f||\uuu 1=||F||\uuu 2\cdot ||G||\uuu 2$.
So (4) is equivalent to 
\[
\bigl |\,\int\uuu 0^{2\pi}\,
f(\theta)\cdot e^{i\gamma(\theta)}
\cdot 
d\theta\,\bigr|
\leq \rho\cdot ||f||\uuu 1\tag{5}
\] 
for each $f\in H^1\uuu 0(T)$.
At this stage we use the duality between
$H^\infty(T)$ and $H^1\uuu 0(T)$ from 
Section XX. It follows that
(5) is equivalent to the following

\medskip

\noindent
{\bf{6.4 Approximation condition.}}
One has
\[ 
\min\uuu h\,||e^{i\gamma(\theta)}\vvv h(\theta)||\uuu\infty=\rho
\]
where the minimum is taken over $h$\vvv functions in $H^\infty(T)$.
\bigskip

\centerline{\emph {Final part of the proof.}}
\medskip


\noindent
Since $w\geq 0$ and $>0$ outside a set of measure zero, 
the approximation condition is equivalent with the existence of some
$h\in H^\infty(T)$ and some $\rho<1$ such that


\[ 
|w(\theta)\vvv \phi^2(\theta)\cdot h(\theta)|\leq \rho\cdot w(\theta)\tag{*}
\]
hold on $T$.
It remains to show that (*) is equivalent to the 
existence of a pair $u,v$ in Theorem 6.2.
Let us begin with

\medskip

\noindent
\emph{Proof that (*) gives the pair $u,v$}.
Since $\log w$ is in $L^1(T)$ we have $w>0$ almost everywhere
and (*) entails that
$\phi^2(\theta)\cdot h(\theta)$
stay in the sector
\[
Z=\{z\colon \vvv\pi/2+ \delta\leq \text{arg}(z)\leq
\pi/2\vvv \delta\}
\]
where we have put $\delta=\arccos(\rho)$.
This inclusion of the range of 
$\phi^2\cdot h$
implies that it is outer. See XX above.
Hence we can find a harmonic function
$V$ such that
\[
\phi^2\cdot h= e^{ia}\cdot e^{V+iV^*}
\]
where $a$ is some real constant.
The inclusion of the range implies that
\[
|a+V^*(\theta)|\leq \pi/2\vvv\delta
\]
Next, define the harmonic function
\[ 
v(\theta)= \vvv (a+ V^*(\theta))
\]
It follows that
\[
\phi^2(\theta)\cdot h(\theta)= e^{v(\theta)+iv^*(\theta)+c}
\]
for some constant $c$.
Finally, since $w=|\phi|^2$ we obtain
\[
w(\theta)= e^{v(\theta)}\cdot \frac{e^a}{|h(\theta)|}
\]
By (xx) above the last factor is  bounded both below and above and hence $e^u$ for some bounded function.
Together with the bound (xx) for the harmonic 
conjugate of $v$
we get the requested form for $w(\theta)$ in Theorem 6.2.
\medskip

\noindent
\emph{Proof that a pair $(u,v)$ gives (*)}.
Consider the special case when $w= e^v$ and 
\[
|v^*(\theta)|\leq 
\pi/2\vvv \epsilon
\] 
holds for 
some $\epsilon>0$.
It is clear that the corresponding $\phi$function obtained via (xx) above
satisfies


\[
\phi^2(\theta)= e^{v(\theta)+iv^*(\theta)}
\] 
This gives
\[
e^{i\gamma(\theta)}= e^{\vvv iv^*(\theta)}
\]
and we notice that if we take the constant function $h(\theta)=
\epsilon$ then the maximum norm
\[
||e^{i\gamma(\theta)}\vvv \epsilon||\uuu \infty<1
\]
which proves that (*) holds.


\newpage




\centerline{\bf {Appendix II: Beurling-Wiener  algebras}}

\bigskip

\noindent
\centerline{\emph{Contents}}
\bigskip

\noindent


\medskip

\noindent
A: Beurling-Wiener algebras on the real line.

\medskip

\noindent
B: A Tauberian theorem


\medskip

\noindent
C: Ikehara's theorem

\medskip
\noindent
D: The Gelfand space of $L^1({\bf{R}}^+)$.

\bigskip

\noindent {\bf{Introduction.}}
The results in this section are foremost due to Wiener and Beurling.
The cornerstone is Wiener's general Tauberian Theorem
which we  apply
a  class  called
Beurling\vvv Wiener algebras where the  convolution algebra
$L^1){\bf{R}}) $ is replaced by various weight algebras
introduced by Beurling in the article (Beurling: 1938].
Here follows the set\vvv up in this section.






\bigskip

\noindent
Consider
the Banach space $L^1({\bf{R}})$
of 
Lebesgue measurable and absolutely integrable functions whose
product is defined by  convolutions:
\[ 
f*g(x)=\int\, f(x-y)g(y)dy
\]

\medskip




\noindent {\bf A.1 The space $\mathcal F_0^\infty$.}
On the $\xi$-line we have the space $C_0^\infty$ 
of infintely differentiable functions with compact support.
Each $g(\xi)\in C_0^\infty$ yields an $L^1$-function on the real 
$x$-line defined by
\[ 
\mathcal F(g)(x)=\frac{1}{2\pi}\int\, e^{ix\xi}\, g(\xi)\cdot d\xi\tag{*}
\]
The resulting subspace of $L^1$ is denoted by
$\mathcal F_0^\infty$.

\medskip


\noindent {\bf A.2  Beurling-Wiener algebras.}
A subalgebra B of $L^1$
is called a Beurling-Wiener algebra - for short a 
$\mathcal B\mathcal W$-algebra - if the
following two conditions hold:
\medskip

\noindent
\emph{Condition 1.}
$B$ is
equipped with a complete norm
denoted by $||\cdot  ||_B$ such that 
\[
||f*g||_B\leq ||f||_B\cdot ||g||_B\quad\colon\quad f,g\in B\quad\text{and}\quad
||f||_1\leq ||f||_B
\]
\medskip

\noindent
\emph{ Condition 2.}
$\mathcal F_0^\infty$ is  a dense subalgebra of
$B$. 
\bigskip


\noindent {\bf A.3 Theorem} \emph{Let $B$ be a $\mathcal B\mathcal W$-algebra.
For each multiplicative and continuous functional $\lambda$ on $B$ 
which is not identically zero
there exists a unique $\xi\in\bf R$ such that}
\[
 \lambda(f)=\widehat f(\xi)\quad\colon\quad f\in B
\]

\medskip

\noindent 
\emph{Proof.}
Suppose that there exists some $\xi$ such that
\[
\lambda(f)=0
 \implies  \widehat f(\xi)=0\tag{i}
\]
This means that the linear
form $f\mapsto \widehat f(\xi)$
has the same kernel as $\lambda$ and hence there exists some
constant $c$ such that
\[
\lambda(f)=c\cdot \hat f(\xi)\quad\text{for all}\,\, f\in B\,.\tag{ii}
\]
Since  $\lambda$  is multiplicative it follows that
$c=c^n$ for every positive integer $n$ and then
$c=1$.
Next, since
$B$ contains $\mathcal F_0^\infty$ and test-functions on
the $\xi$-line separate points, it is clear that
$\xi$  is uniquely determined.
There remains to prove the existence
of some $\xi$ for which (i) holds.
\medskip

\noindent
To prove this we use the
density of $\mathcal F_0^\infty$ in $B$ which by the continuity of
$\lambda$ gives
some
$g\in\mathcal F_0^\infty$ such  that $\lambda(g)\neq 0$.
Let $K$ be the compact support of
the test-function $\widehat g(\xi)$ and
suppose that  
(i)  fails for each point  $\xi\in K$.
The density of
$\mathcal F_0^\infty$ gives
some $f_\xi \in\mathcal F_0^\infty$ such that
\[ 
 \widehat f(\xi)\neq 0\,\quad \text{and}\,\, \lambda(f)=0\tag{iii}
\]

\noindent
Heine-Borel's Lemma yields
a finite set of points $\xi_1,\ldots,\xi_N$ in $K$ such
that
family $\{ \widehat f_{\xi_k}\}$ have no common zero on $K$.
To simplify notations we set
$f_k=f_{\xi_k}$.
The complex conjugates 
of $\{\widehat f_k\}$ are again  test-functions. So for each $k$
we find
$h_k\in B$ such that $\widehat h_k$ is the s complex conjugate
of  $\widehat f_k$.
Set
\[ 
\phi (\xi)=
\sum_{k=1}^{k=N}\,\widehat h_k(\xi)\cdot \widehat f_k(\xi)
\]


\noindent
This test-function is $>0$ on the support of $\widehat g$ and hence there exists
the test-function
\[
Q(\xi)=\frac{\widehat g}{\phi}\tag{iv}
\]
By Condition 2, Q is  the Fourier transform of some $B$-element
$q$. Since $L^1({\bf{R}})$-functions are uniquely determined by their
Fourier transforms, it follows from (iv) that 
\[
\sum_{k=1}^{k=N}\, q*h_k*f_k=g\tag{v}
\]

\noindent
Now we get a contradiction since $\lambda(f_k)=0$ for each  $k$
while $\lambda(g)\neq 0$. 








\bigskip



\centerline {\bf  A.4 The algebra $B_a$.}
\medskip


\noindent 
Let $a>0$ be a positive real number.
Given a Beurling-Wiener algebra $ B$
we set
\[ 
J_a=\{ f\in B\quad\colon\, \widehat f(\xi)=0\,\,\text{for all}\,\,
-a\leq \xi\leq a\}
\]


\noindent
Condition 1 and the continuity of the Fourier transform on
$L^1$-functions imply
that $J_a$ is a closed ideal in $ B$. 
Hence we get the Banach algebra $\frac{B}{J_a}$ which we denote by
$B_a$. Let   $g\in \mathcal F_0^\infty$ be such that
$\widehat g(\xi)=1$ on $[-a,a]$. For every
$f\in B$ it  follows that
$g*f-f$ belongs to $J_a$ which  means that
the image of $f$ in $B_a$ is equal to the image of $g*f$. We conclude that
the $g$-image yields an identity in the algebra $B_a$ and  hence $B_a$
is a Banach algebra with a unit element.
\medskip

\noindent
{\bf A.5 Theorem.} \emph{The Gelfand space of
$B_a$ is equal to the compact interval $[-a,a]$.}
\medskip

\noindent
{\bf{A.6 Exercise.}} Prove this using Theorem A.3


\bigskip

\centerline{\bf {A.7. Examples of $\mathcal BW$-algebras}}
\medskip

\noindent
Let $B$ be the space of all continuous functions $f(x)$ 
on the real $x$-line such that the positive series below is convergent:
\[
\sum_{-\infty}^{\infty}\,||f||_{[\nu,\nu+1]}\tag{*}
\]


\noindent 
where
$||f||_{[\nu,\nu+1]}$ is the maximum norm of $f$ on the closed interval 
$[\nu.\nu+1]$ and the sum extends over all integers. The norm on $B$-elements
is defined by the sum of the series above.
It is obvious that this norm dominates the $L^1$-norm.
Moreover, one easily verifies that
\[
||f*g||_B\leq ||f|||\cdot ||g||_B\tag{i}
\]
for pairs in $B$.
Hence $B$ satisfies Condition 1 from B.
\medskip

\noindent
{\bf{Exercise.}}
Show that 
the Schwartz space $\mathcal S$
of rapidly decreasing functions
on the real $x$-line
is a dense subalgebra
of $B$.

\medskip

\noindent
Next, since  $\mathcal F_0^\infty\subset \mathcal S$ we have the inclusion
\[ 
\mathcal F_0^\infty\subset B\tag{ii}
\]
There remains to see why
$\mathcal F_0^\infty$ is dense in
$B$. To prove this we construct some special functions
on the $x$-line whose Fourier transforms have compact support.
If $b>0$
we set
\[ 
f_b(x)=\frac{1}{2\pi}
\int_{-b}^b\,e^{ix\xi}\cdot (1-\frac{|\xi|}{b})\cdot d\xi
\]
By Fourier's inversion formula this means that
\[ 
\widehat f_b(\xi)=1-\frac{|\xi|}{b}\quad\,-b\leq\xi\leq b\quad
\text{and zero if}\,\,|\xi|>b
\]
A computation which is left to the reader gives
\[
f_b(x)=\frac{1}{\pi}\cdot \frac{1-\text{cos}\, bx}{bx^2}
\]
From this expression it is clear that
$f_b(x)$ belongs to $B$ and we leave it to the reader to verify that
\[ 
\lim_{b\to+\infty}\, ||f_b*g-g||_B=0
\quad\text{for all}\,\, g\in B\tag{iii}
\]
\medskip

\noindent
Next,  the functions
$\widehat f_b(\xi)$ have compact support but they are not smooth, i.e.
they do not belong to $\mathcal F_0^\infty$.
However, we can perform a smoothing of these functions as follows:
Let $\phi(\xi)$  be an even and non-negative
$C_0^\infty$-function with support in
$-1\leq\xi\leq 1$  such that the integral
\[
\int\, \phi(\xi)\cdot d\xi=1
\]


\noindent
With $\delta>0$ we set
$\phi_\delta(\xi)= \frac{1}{\delta}\cdot \phi(\xi/\delta)$ and 
for each
pair $\delta,b$ we get the test-function on the $\xi$-line
defined by
\[
\psi_{\delta,b}(\xi)=
\int_{-b}^b\, \phi_\delta(\xi-\eta)\cdot (1-\frac{|\eta|}{b})\cdot d\eta
\]
The inverse Fourier transforms
\[ 
f_{\delta,b}(x)=\frac{1}{2\pi}\int
e^{ix\xi}\cdot \psi_{\delta,b}(\xi)\cdot d\xi
\]
yield functions in $\mathcal F_0^\infty$ for all pairs $\delta,b$.
Next, if $g\in B$ then 
the Fourier transform of the $B$-element $f_{\delta,b}*g$ is equal to the
\emph{convolution} of
$\phi_\delta(\xi)$ and the Fourier transform of
$f_b*g$.
This implies that
\[ 
f_{\delta,b}* g\in \mathcal F_0^\infty\,.
\]
At this stage we leave it to the reader to verify that
\[
\lim_{(\delta,b)\to (0,0)}\, f_{\delta,b}*g=g
\]
holds for every $g\in B$. Hence the required density of
$\mathcal F_0^\infty$ is proved and $B$ is a Beurling-Winer algebra.



\centerline{\bf A.8 Adding discrete measures}
\medskip

\noindent
Let $M_d({\bf{R}})$ be the Banach algebra of discrete measures
of finite total variation, i.e. measures of the form
\[ 
\mu=\sum\, c_\nu\cdot\delta_{x_\nu}\quad\colon\,
||\mu||=\sum\,|c_\nu|<\infty
\]
\medskip

\noindent
As explained in XX the Gelfand 
space is the compact
Bohr group $\mathfrak{B}$, where the real $\xi$-line via the Fourier
transform
appears as a dense subset.
Now we  adjoin some $\mathcal{BW}$\vvv algebra
$B$ and 
obtain a Banach algebra $B\uuu d$ which 
consists of measures of the form
\[ 
f+\mu\quad\colon\quad f\in B \,\,\text{and}\,\, \mu\in
M_d({\bf{R}})
\]
where the norm of $f+\mu$ is the sum of the $B$-norm of $f$
and the total variation of  $\mu$. Since $B$ is a subspace of
$L^1$ one easuly checks that this yields a complete norm.
next, by condition (2) in A.2 it follows that if
$f\in b$ and
$\mu\in M_d({\bf{R}})$ then the convolution
$f*\mu$ belongs to $B$.
This means that
$B$ appears as a closed ideal in $B\uuu d$.
\medskip

\noindent
{\bf A.9 The Gelfand space
$\mathcal M_{B\uuu d}$}.
Let  $\lambda$ is a multiplicative functional on
$B\uuu d$ which is not identically zero on
$B$. Theorem A.3 gives
a unique
$\xi$ such that
\[
\lambda(f)= \widehat f(\xi)\quad\,\colon\quad 
f\in B\tag{i}
\]
If $a$ is a real number then $\delta_a*f$ has the
Fourier transform
becomes $e^{ia\xi}\cdot \widehat f(\xi)$. It follows that
\[
\lambda(\delta_a)\cdot \widehat f(\xi)=
\lambda(\delta_a*f)= e^{-ia\xi}\cdot \widehat f(\xi)\tag{ii}
\]


\noindent
We conclude that $\lambda(\delta_a)=e^{-ia\xi}$ and hence  the restriction of
$\lambda$ 
is the evaluation of the Fourier transform  at $\xi$ on the whole algebra $B\uuu d$.
In this way the real $\xi$-line is embedded in
$\mathcal M_B$ where a point $\lambda\in\mathcal M_B$
belongs to this subset if and only if
$\lambda(f)\neq 0$ for some
$f\in B$.
The construction of the Gelfand 
topology shows  that
this copy of the real $\xi$-line appears as an \emph{open} subset of
$\mathcal M_{B\uuu d}$  denoted by
${\bf{R}}_\xi$.
\medskip

\noindent
{\bf A.10 The set $\mathcal M_{B\uuu d}\setminus {\bf{R}}_\xi$}.
If $\lambda$ belongs to this closed subset it is identically zero on
the ideal $B$ and its restriction to 
$M_d({\bf{R}})$ 
corresponds to a point $\gamma$ 
in the Bohr group
$\mathfrak{B}$. 
Conversely, every point in  $\mathfrak{B}$
yields a $\lambda\in
\mathcal M_{B\uuu d}\setminus {\bf{R}}_\xi$ 
since the quotient algebra
\[
\frac{B\uuu d}{B}\simeq
 M_d({\bf{R}})
\]
Hence we have the set\vvv theoretic equality
\[
\mathcal M\uuu{B\uuu d}= {\bf{R}}\uuu\xi
\cup\,\mathfrak{B}\tag{*}
\]




\medskip


\noindent
{\bf A.11  Proposition.} \emph{The open subset
${\bf{R}}_\xi$ is dense in $\mathcal M_B$.}
\medskip

\noindent\emph{Proof.}
Let $\lambda$ be a point in 
$\mathcal M_{B\uuu d}\setminus {\bf{R}}_\xi$ which therefore
corresponds to a point $\gamma\in\mathfrak{B}$.
By the result in XX we know that
for every finite set $\mu_1,\ldots,\mu_N$
of discrete measures, there exists a sequence $\{\xi_\nu\}$
such that
\[
\lim_{\nu\to\infty}
\widehat \mu_i(\xi_\nu)=\gamma(\mu_i)\quad\text{and}\,\,
|\xi_\nu|\to \infty
\]

\medskip

\noindent
At the same time
the Riemann-Lebesgue Lemma entails that

\[
\lim_{\nu\to\infty}\, \widehat f(\xi_\nu)=0
\]
for every
$f\in B$. Hence
the construction of the Gelfand topology on
$\mathcal M_{B\uuu d}$ gives the requested density
in Proposition A.11



\medskip

\noindent
{\bf A.12  An inversion formula.}
Let $f\in B $  and $\mu$ is some discrete measure.
Suppose that there exists $\delta>0$ such that
the Fourier transform of $f+\mu$ has absolute value 
$\geq\delta$ for all $\xi$.
Proposition A.11  implies that its Gelfand transform has no zeros and hence
this $B\uuu d$-element is invertible, i.e. there exist
$g\in B$ and a discrete measure $\gamma$ such that
\[
\delta_0=(f+\mu)*(g+\gamma)\tag{i}
\]
Notice  that the right hand side becomes
\[
f*g+ f*\gamma+g*\mu+\mu*\gamma
\]
Here $f*g+ f*\gamma+g*\mu$ belongs to $B$
while
$\mu*\gamma$ is a discrete measure. So (i) implies that
$\gamma$ must be the inverse of $\mu$ in
$M_d({\bf{R}})$
and hence (i) also gives the equality:
\[
f*g+f*\mu^{-1}+g*\mu=0\tag{ii}
\]
\bigskip














\noindent
\centerline {\bf B.  A Tauberian Theorem.}
\medskip

\noindent
Consider the Banach algebra $B$ above.
The dual space $B^*$ consists of  Riesz measures
$\mu$ on the real line for which there exists a constant $A$ such that
\[ 
\int_\nu^{\nu+1}\, |d\mu(x)|\leq A\quad\text{for all integers}\,\,\nu\,.
\] 

\noindent
The smallest $A$ above is  the norm of $\mu$ in $B^*$ and 
duality is expressed by:
\[ 
\mu(f)=\int\, f(x)\cdot d\mu(x)\,\quad\colon\quad f\in B\,\,\text{and}\,\, \mu\in B^*
\]
\noindent 
Let $f\in B$ be such that  $\widehat f(\xi)\neq 0$ for all
$\xi$. For each $a>0$ it follows from
Theorem A.5 that the $f$-image in $B_a$ generates the whole algebra.
Since this hold for every $a>0$
it follows that each
$\phi\in\mathcal F_0^\infty$
belongs to the principal ideal generated by $f$ in $B$, i.e. there exists some
$g\in B$ such that
\[
 \phi=g*f\tag{*}
\]
Since $\mathcal F_0^\infty$ is dense in $B$ we conclude that
$B\cdot f$ is dense in $B$.
Using this density we have:


\bigskip

\noindent 
{\bf B.1  Theorem} \emph{Let 
$\mu\in B^*$ be such that}
\[
\lim_{y\to+\infty}\, \int\, f(y-x)\cdot d\mu(x)=A\,\,\, \text{exists}.
\]
\emph{Then, for each $g\in B$ it follows that}
\[
\lim_{y\to+\infty}\, \int\, g(y-x)\cdot d\mu(x)=B
\quad\text{where}\quad B=A\cdot \frac{ \hat g(0)}{\hat f(0)}
\]

\medskip

\noindent \emph{Proof.} 
Let $g\in B$. If $\epsilon>0$ we find
$h_\epsilon\in B$ such that 
$||g-f*h_\epsilon||_B<\epsilon$. When  $y>0$ we get:
\[
\int\, (f*h_\epsilon)(y-x)\cdot d\mu(x)=\tag{i}
\]
\[
\int\, \bigl[f(y-s-x)h_\epsilon(s)\cdot ds\,\bigr] \cdot  d\mu(x)=
\int\, h_\epsilon(s)\cdot\bigl[\int \,f(y-s-x)\mu(x)\,\bigr]\cdot ds
\]
By the hypothesis the inner integral converges to $A$ when
$y\to+\infty$
every fixed $s$. Since
$h$ belongs to $B$ it follows easily that
the limit of (i) when $y\to+\infty$ is equal to
\[ 
A\cdot \int\, h_\epsilon(s)\cdot ds=A\cdot \widehat h_\epsilon(0)\tag{ii}
\]


\noindent
Next, since the $B$-norm is stronger than the $L^1$-norm it follows that
\[ 
|\widehat g(0)-\hat h_\epsilon(0)\cdot \widehat f(0)|<\epsilon\tag{iii}
\]
Moreover, since the $B$-norm is invariant under translations
we have
\[
\bigr |
 \int\, g(y-x)d\mu(x)-\int\, (f*h_\epsilon)(y-x)\cdot d\mu(x)\bigl|\leq
 \epsilon\cdot ||\mu||\quad\text{for all}\,\,y\tag{iv}
\]
where $||\mu||$ is the norm of $\mu$ in the dual space $B^*$.
Notice also that   (iii) gives:

\[
\lim_{\epsilon\to }\, \hat h_\epsilon(0)=\frac{\hat g(0)}{\hat f(0)}
\]
Finally, since $\epsilon>0$ is arbitrary we see that the limit formula for (i) when
$y\to+\infty$ expressed by
(ii)  and (iv) above together imply that


\[
\lim_{y\to+\infty}\, 
\int\, g(y-x)d\mu(x)=A\cdot \frac{\hat g(0)}{\hat f(0)}
\]
This finishes the proof of 
Theorem A.9

\bigskip




\centerline
{\bf B.2  The multiplicative version}
\medskip



\noindent 
Let ${\bf{ R}}^+$ be the multiplicative group of positive real numbers.
To each function $f(t)$ on ${\bf{R}}^+$
we get the function $E_f(x)= f(e^x)$ on the real $x$-line.
Since $dt=e^xdx$ under the exponential map we have
\[
\int_0^\infty\, f(t)\frac{dt}{t}=
\int_{-\infty}^\infty\, E_f(x)dx
\]
provided that $f$ is integrable.
On $\bf R^+$ we get the convolution algebra $L^1(\bf R^+)$ where
\[ 
f*g(t)=\int_0^\infty\, f(\frac{t}{s})\cdot g(s)\cdot \frac{ds}{s}
\]
This convolution commutes with the $E$ map from
$L^1({\bf {R}}^+$ into $L^1({\bf {R}}^1)$, i.e. 
\[
E_{f*g}= E_f*E_g
\]
Next, recall that the Fourier transform on $L^1({\bf{ R}}^+)$
is defined by
\[ 
\widehat f(\xi)=\int_0^\infty\,t^{-i\xi} \cdot f(t)\cdot \frac{dt}{t}
\]
\medskip









\noindent
{\bf B.3  The Banach algebra $B_m$.} The companion to $B$ on
${\bf {R}}^+$ consists of continuous functions $f(t)$ for which
\[ 
\sum\, ||f||_{[2^\nu,2^{\nu+1}]}<\infty
\]
where the is taken over all integers. Notice  that
with $\nu<0$ one takes small intervals approaching $t=0$.
Just as in Theorem A.9  we obtain a Tauberian Theorem for functions
$f\in B_m$ whose Fourier transform is everywhere $\neq 0$.
Here we  the dual space $B\uuu m^*$
consists of Riesz measures $\mu$ on ${\bf{R}}^+$
for which there exists a constant $C$ such that

\[
\int\uuu{2^m}^{2^{m+1}}\, |d\mu(t)|\leq C
\] 
for all integers $m$.



\bigskip



\bigskip


\centerline{\bf C. Ikehara's theorem.}
\bigskip


\noindent
Let
$\nu$ be a non-negative Riess measure supported on
$[1,+\infty)$ and assume that
\[
\int_1^\infty x^{-1-\delta}\cdot d\nu(x)<\infty\quad
\text{for all}\,\, \delta>0
\]
This gives
an analytic function
$f(s)$ of the complex variable $s$ defined in
the right half plane
$\mathfrak{Re}(s)>1$ by
\[ 
f(s)=\int_1^\infty x^{-s}\cdot d\nu(x)
\]
\medskip

\noindent
{\bf D.1 Theorem.}
\emph{Assume that there exists a constant
$A$ and a locally integrable  function
$G(u)$ defined on the real $u$-line such that}
\[
\lim_{\epsilon\to 0}\, \int_{-b}^b\, \bigl|
f(1+\epsilon+iu)-\frac{A}{1+\epsilon+iu}-G(u)\bigr|\cdot du=0\quad
\text{holds for each}\,\, b>0\tag{*}
\]
\medskip

\noindent
\emph{Then it follows that }
\[ 
\lim_{x\to+\infty}\,\frac{1}{x}\int_1^x\,d\nu(t)=A\tag{**}
\]
\medskip



\noindent
{\emph{Proof}.
Define the  measure $\nu^*$ on the non-negative real $\xi$-line by
\[
d\nu^*(\xi)= e^{-\xi}\cdot d\nu(e^\xi)-A\cdot d\xi\,\quad\colon\,\,\xi\geq 0\tag{1}
\]

\noindent
If $\eta>1$ we notice that
\[
\int_0^\eta\, e^{-\eta+\xi}\cdot d\nu^*(\xi)=
e^{-\eta}\int_0^\eta d\nu(e^\xi)-A(1-e^{-\eta})
=e^{-\eta}\int_0^{e^\eta} d\nu(t)-A(1-e^{-\eta})
\]
\medskip


\noindent
hence (**) holds if and only if
\[
\lim_{\eta\to\infty} \int_0^\eta\, e^{-\eta+\xi}\cdot d\nu^*(\xi)=0\tag{2}
\]

\noindent
It is also clear that condition (xx) for  $\nu$ entails that
\[ \int_0^\infty\, e^{-\delta\cdot \xi}\cdot d\nu^*(\xi)<\infty
\quad\text{for all}\,\,\delta>0\tag{3}
\]

\noindent
Moreover, a variable substitution gives
\[ 
f(s)-\frac{A}{s-1}=\int_0^\infty e^{(1-s)\xi}d\nu^*(\xi)\tag{4}
\]

\medskip
\centerline {\emph{C.1 A reformulation of Ikehara's theorem.}}


\medskip

\noindent
From (1-4)   we
can restate  Ikehara's theorem.
Let
$\nu^*$ be a non-negative measure on $0\leq\xi<+\infty$
such that 
\[ \int_0^\infty\, e^{-\delta\cdot \xi}\cdot d\nu^*(\xi)<\infty
\quad\text{for all}\,\,\delta>0\tag{1.1}
\]
\medskip

\noindent
Let $A>0$ be some positive constant and define the measure $\mu$ by
\[
d\mu(\xi)=d\nu^*(\xi)-A\cdot d\xi\tag{1.2}
\]
Then (1.1) gives
the analytic function
$g(s)$ defined in $\mathfrak{Re}(s)>0$ by
\[
g(s)=\int_0^\infty\, e^{-s\cdot\xi}\cdot d\mu(\xi)\tag{1.3}
\]
\medskip

\noindent
{\bf C.1.1. Definition.}
\emph{We say that the  measure $\mu$ is of the
Ikehara type if there exists a locally integrable function
$G(u)$ defined on the real $u$-line such that}
\[
\lim_{\epsilon\to 0}\, \int_{-b}^b\, \bigl|
g(\epsilon+iu)-G(u)\bigr|\cdot du=0\,\quad
\text{holds for each}\,\, b>0
\]
\medskip

\noindent
{\bf C.1.2. The space $\mathcal W$.}
Let $\mathcal W$ be the space of continuous functions
$\rho(\xi)$ defined on $\xi\geq 0$ which satisfy:
\[
\sum_{n\geq 0}\,||\rho||_n<\infty\,
\quad\text{where}\,\,||\rho||_n=\max_{n\leq u\leq n+1}\, |\rho(u)|
\]
The dual space
$\mathcal W^*$ consists of Riesz measures
$\gamma$ on $[0,+\infty)$ such that
\[ 
\max_{n\geq 0}\,\int_n^{n+1}\, |d\gamma(\xi)|<\infty
\]
With these notations we shall prove:
\bigskip

\noindent
{\bf C.1.3. Theorem.}
\emph{Let $\nu^*$ be a non-negative meausure
on $[0,+\infty)$ and $A\geq 0$ some constant
such that the measure $\mu=\nu^*-A\cdot d\xi$
is of Ikehara type.
Then $\mu\in \mathcal W^*$
and for every
function $\rho\in\mathcal W$ one has}
\[
\lim_{\eta\to+\infty}\, \int_0^\eta
\rho(\eta-\xi)\cdot d\mu(\xi)=0
\]
\medskip

\noindent
{\bf {C.1.4 Exercise.}} 
Use the material above to show that
Theorem C.1.3  gives Theorem C.0 where a
hint is to use the function $\rho(s)=e^{-s}$ above.

\medskip

\centerline {\emph{C.2 Proof of Theorem C.1.3.}}
\bigskip

\noindent
Let $b>0$ and define the function $\omega(u)$ by
\[
\omega(u)= 1-\frac{|u|}{b}\,,\quad
-b\leq u\leq b\,\,\quad\text{and}\,\,
\omega(u)=0\,\,\text{outside this interval}\tag{i}
\]


\noindent
Set
\[ J_b(\epsilon,\eta)=
\int_{-b}^b\, e^{i\eta u}\cdot g(\epsilon+iu)\cdot \omega(u)\cdot du\tag{ii}
\]
From Definition C.1.1 we have the $L^1_{\text{loc}}$-function $G(u)$
and since $\omega(u)$ is a continuous function on the compact
interval $[-b,b]$
we have
\[ 
\lim_{\epsilon\to 0}\, J_b(\epsilon,\eta)=J_b(0,\eta)=
\int_{-b}^b\, e^{i\eta u}\cdot G(u)\cdot \omega(u)\cdot du\tag{iii}
\]
With $b$ kept fixed  the right
hand side
is a Fourier transform of an
$L^1$-function. So  the Riemann-Lebesgue theorem gives:
\[
\lim_{\eta\to+\infty}\, J_b(0,\eta)=0\tag{iv}
\]
Moreover, the triangle inequality gives the inequality:
\[
|J_b(0,\eta)|\leq 
\int_{-b}^b\,\bigl| G(u)\bigr|\cdot du\tag{v}
\]
\medskip


\noindent{\bf Some integral formulas.}
From the above
it  is clear that
\[ J_b(\epsilon,\eta)=
\int_0^\infty\,
\bigl[\int_{-b}^b\, e^{i\eta u-i\xi u}\cdot \omega(u)\cdot du\bigr]
\cdot e^{-\epsilon\cdot\xi}\cdot d\mu(\xi)\tag{1}
\]


\noindent
Next, notice that
\[
\int_{-b}^b\, e^{i\eta u-i\xi u}\cdot \omega(u)\cdot du=
2\cdot\frac{1-\text{cos}\,b(\eta-\xi)}{b(\eta-\xi)^2}\tag{2}
\]
Hence we obtain
\[ J_b(\epsilon,\eta)=
2\cdot\int_0^\infty\, 
\frac{1-\text{cos}\,b(\eta-\xi)}{b(\eta-\xi)^2}\cdot e^{-\epsilon\xi}
\cdot d\mu(\xi)\tag{3}
\]

\noindent
From (iii) above it follows that  (3)
has a limit as $\epsilon\to 0$ which is equal to 
the integral in the right hand side in (iii) which is
denoted by $J_b(0,\eta)$. Next, it is 
easily seen that there exists the limit

\[
\lim_{\epsilon\to 0}\, 
2\cdot\int_0^\infty\, 
\frac{1-\text{cos}\,b(\eta-\xi)}{b(\eta-\xi)^2}\cdot e^{-\epsilon\xi}
\cdot Ad\xi=2\pi\cdot A\tag{4}
\]
\medskip

\noindent
Hence (3-4) imply that there exists the limit
\[
\lim_{\epsilon\to 0}\, 
2\cdot\int_0^\infty\, 
\frac{1-\text{cos}\,b(\eta-\xi)}{b(\eta-\xi)^2}\cdot e^{-\epsilon\xi}
\cdot d\nu^*(\xi)=J_b(0,\eta)+2\pi\cdot A\tag{5}
\]
\medskip

\noindent
Next, the measure  $\nu^*\geq 0$ and the function
$\frac{1-\text{cos}\,b(\eta-\xi)}{b(\eta-\xi)^2}\geq 0$
for all $\xi$. So the existence of a finite limit in (5) entails that there exists
the convergent integral 
\[
\int_0^\infty\, 
\frac{1-\text{cos}\,b(\eta-\xi)}{b(\eta-\xi)^2}
\cdot d\nu^*(\xi)=J_b(0,\eta)+2\pi\cdot A\tag{6}
\]



\medskip


\noindent
{\bf Proof that
$\mu\in\mathcal W^*$.}
Since $A\cdot d\xi$ obviously belongs to
$\mathcal W^*$ it suffices to show that
$\nu^*\in\mathcal W^*$.
To prove this we consider some integer $n\geq 0$ and with $b=1$
it is clear that
(6) gives
\[
\bigl|\int_n^{n+1}\, 
\frac{1-\text{cos}\,(\eta-\xi)}{(\eta-\xi)^2}
\cdot d\nu^*(\xi)\bigr|\leq |J_1(0,\eta)|+2\pi=
\int_{-1}^1\, |G(u)|\cdot du+2\pi\cdot A
\]
Apply this with
$\eta=n+1+\pi/2$ and notice that

\[
\frac{1-\text{cos}\,(n+1+\pi/2-\xi)}{(n+1+\pi/2-\xi)^2}
\geq a\quad\,\text{for all}\,\, n\leq\xi\leq n+1
\]
This gives a constant $K$ such that
\[
\int_n^{n+1}\, d\nu^*(\xi)\leq K\quad\, n=0,1,\ldots
\]
\medskip

\noindent
{\bf {Final part of the proof.}}
We have proved that
$\mu\in \mathcal W^*$. Moreover, from
(iv) above and the integral formula (6) we get
\[
\lim_{\eta\to+\infty}\, \int_0^\infty
\frac{1-\text{cos}\,b(\eta-\xi)}{b(\eta-\xi)^2}\cdot d\mu(\xi)=0
\quad\,\text{for all}\,\, b>0\tag{*}
\]
Next, for each fixed 
$b>0$ we notice that the function
\[
\rho_b(\xi)=2\cdot \frac{1-\text{cos}\,(b\xi)}{b\cdot \xi^2}
\]
belongs to $\mathcal W$ and its
Fourier is  $\omega_b(u)$.
Here $\omega_b(u)\neq 0$ when
$-b<u<b$.
So the family of these $\omega$-functions have no common
zero on the real $u$-line. By the Remark in XX this means that
the linear subspace of
$\mathcal W$ generated by
the translates of all $\rho_b$ -functions with
arbitrary large
$b$ is dense in $\mathcal W$. 
Hence (*) above implies
that
we get a zero limit as $\eta\to+\infty$ for every function
$\rho\in\mathcal W$. But this is precisely the
assertion in
Theorem C.1.3.


\bigskip


\centerline{\bf E. The algebra $L^1({\bf{R}}^+)$}

\bigskip

\noindent
Consider the  family
of $L^1$-functions on the real $x$-line which are
supported by the half-line $x\geq 0$.
This yields a closed subalgebra of $L^1({\bf{R}})$
denoted by
$L^1({\bf{R}}^+)$. 
Indeed, if $f(x)$ and $g(x)$ are  two such functions
in
$L^1({\bf{R}}^+)$.
the support of 
the convolution
$g*f$ stays in $[0,+\infty)$. 
Adding the unit point mass $\delta_0$ we obtain a commutative
Banach algebra
\[ 
B={\bf{C}}\cdot \delta_0+L^1({\bf{R}}^+)
\]


\noindent
{\bf 1. The Gelfand space
$\mathfrak{M}_B$}.
To obtain this space we consider some
$f(x)\in L^1({\bf{R}}^+)$
and set:
\[
\widehat f(\zeta)=\int_0^\infty\, e^{i\zeta x}\cdot f(x)\cdot dx,\quad\text{where}
\quad \mathfrak{Im}(\zeta)\geq 0
\]
With $\zeta=\xi+i\eta$ we get
\[
|\widehat f(\xi+i\eta)|\leq 
\int_0^\infty\, |e^{i\xi x-\eta x} |\cdot|f(x)|\cdot dx=
\int_0^\infty\, |e^{-\eta x}\cdot |f(x)|\cdot dx\leq ||f||_1
\]
We conclude that
for every point $\zeta=\xi+i\eta$ in the closed upper half-plane 
corresponds to a point
in $\zeta^*\in \mathfrak{M}_B$
defined by
\[ 
\zeta^*(f)=
\widehat f(\zeta)\,\quad\text{and}\quad \,\zeta^*(\delta_0)=1
\]
In addition to this 
 $L^1({\bf{R}}^+)$ is a maximal ideal in
 $B$ and there is the special point
 $\zeta^\infty\in \mathfrak{M}_B$ such that
 \[ 
 \zeta^\infty (f)=0\quad\text{for all}\,\, f\in
L^1({\bf{R}}^+ )
\]
\medskip

\noindent
{\bf 2. Theorem.} \emph{The Gelfand space
$\mathfrak{M}_B$ can be identified with
the union  of $\zeta^\infty $ and the closed upper half-plane.}
\medskip

\noindent
{\bf Remark.}
The theorem asserts that every multiplicative
functional on $B$ is either
$\zeta^\infty $ 
or determined by a point
$\zeta=\xi+i\eta$ where
$\eta\geq 0$.
Concerning the topological identification
$\zeta^\infty $ corresponds to the 
one point compactification of the closed
upper half-plane. Thus, whenever
$\{\zeta_\nu\}$ is a sequence in
$\mathfrak{Im}(\zeta)\geq 0$ such that
$|\zeta_\nu|\to\infty$ then $\{z_\nu^*\}$
converges to $\zeta^*$ in
$\mathfrak{M}_B$.
In fact, this follows via the Riemann-Lebegue Lemma which gives
\[ 
\lim_{|\zeta|\to\infty}\, \widehat f(\zeta)=0
\quad\text{for all}\,\, f\in L^1({\bf{R}}^+)
\]
\medskip

\noindent
By the general result in XX 
Theorem 2 holds  if we have
proved if   the following:

\medskip

\noindent
{\bf 3. Proposition.}
\emph{Let $\{g_\nu=\alpha_\nu\cdot\delta_0+f_\nu\}_1^k$
be a finite family in $B$ such that
the $k$-tuple $\{\hat g_\nu\}$
has no common zero in
$\bar U_+\cup\{\infty\}$.
Then the ideal in $B$ generated by this $k$-tuple is equal to
$B$.}

\medskip

\noindent
The proof requires some preliminary constructions.
We  use the conformal map from
the upper half-plane onto the unit disc defined by

\[
w=\frac{\zeta-i}{\zeta+i}
\]
So here $w$ is the complex coordinate in $D$.
Next, consider the disc algebra $A(D)$.
Via  the conformal map
each transform $\widehat f(\zeta)$ of a
function $f\in L^1(\bf{R}^+)$
yields an element of $A(D)$ defined by:

\[ 
F(w)=\widehat f(\frac{i+iw}{1-w})
\]
It is clear that
$F(w)\in A(D)$. Moreover, we notice that
\[
w\to 1\implies\, 
|\frac{i+iw)}{1-w}|\to\infty
\]
It follows that the $A(D)$-function $F(w)$ is zero at
$w=1$ and we can conlcude:
\medskip

\noindent
{\bf 4. Lemma.} \emph{By 
$f\mapsto F$ we have an algebra homomorphism
from $L^1({\bf{R}}^+)$ to functions in
$A(D)$ which are
zero at $w=1$.}
\medskip

\noindent
Next, let  $\mathcal H$ denote the algebra homomorphism in Lemma 4
and 
consider the function $1-w$ in $A(D)$.
We claim this it belongs to the image under $\mathcal H$.
To see this we consider the function
\[
f(x)= e^{-x}\quad\,x\geq 0\,\quad\text{and}\,\, f(x)=0
\quad\text{when}\,\, x<0
\]
Then we see that
\[
\hat f(\zeta)=\int_0^\infty \, e^{i\zeta x}\cdot e^{-x}\cdot dx=
\frac{1}{1-i\zeta}
\]
It follows that
\[ 
F(w)=\frac{1}{1-i(\frac{iw+i}{1-w})}=\frac{1-w}{1-w+w+1}=
\frac{1-w}{2}
\]
Using $2f$ we conclude that
$1-w$ belongs to the $\mathcal H$-image.
Next, the identity element $\delta_0$ is mapped to the constant function
on $D$. So via $\mathcal H$ we have an algebra homomorphism
from $B$ into a subalgebra of $A(D)$ which contains
$1-w$ and the identity function and hence all $w$-polynomials.
Returning to the special $B$-element $f$ we notice that the convolution

\[ 
f*f(x)= x\cdot e^{-x}
\]
We can continue and conclude that the subalgebra of $B$ 
generated by $f$ and $\delta_0$ contains 
$L^1$-functions of the form $p(x)\cdot e^{-x}$ where $p(x)$ are polynomials.
\medskip


\noindent
{\bf{5. Exercise.}}
Prove that the linear space ${\bf{C}}[x]\cdot e^{-x}$
is a dense subspace of $L^1({\bf{R}}^+)$.
\medskip

\noindent
From the result in  the exercise it follows that
the polynomial algebra ${\bf{C}}[w]$ appears as a dense subalgebra
of $\mathcal H(B)$ when it is equipped with the $B$-norm.
At this stage we are prepared to give:

\medskip

\noindent
{\bf{Proof of Proposition 3.}}
In $A(D)$ we have the functions $\{G_\nu=\mathcal H(g_\nu)\}$.
By assumption $\{G_\nu\}$ have no common zero in the closed disc $D$.
Since $D$ is the maximal ideal space of the disc algebra and
${\bf{C}}[w]$  a dense subalgebra, it follows that
for every $\epsilon>0$ there exist
polynomials $\{p_\nu(w)\}$ such that
the maximum norm
\[
|p_1\cdot G_1+\ldots+p_k\cdot G_k-1|_D<\epsilon|\tag{1}
\]
where 1 is the identity function.
Now $p_\nu=\mathcal H(\phi_\nu)$ for $B$-elements $\{\phi_\nu\}$.
So in $B$ we get the element
\[
\psi=\phi_1g_1+\ldots+\phi_k\cdot g_k\tag{2}
\] 
Moreover we have $|\mathcal H(\psi)-1|_D<\epsilon$ and here we can choose
$\epsilon<1/4$ and by the previous identifications it follows that
\[ 
|\widehat \psi(\xi)|\geq 1/4\quad\text{for all}\quad -\infty<\xi<\infty\tag{3}
\]
The proof of Proposition 3 is finished if we can show that (3) entails that
the $B$-element $\psi$ is invertible.
Multiplying $\psi$ with a non-zero scalar we may assume that
\[ 
\psi=\delta_0-g\quad\colon\quad g\in L^1({\bf{R}}^+)
\]
and  the Fourier transform $\widehat\psi(\xi)$
satisfies
\[
|\widehat\psi(\xi)-1|\leq 1/2
\]
for all $\xi$.
It means that $|\widehat g(\xi)|\leq 1/2$.
The spectral radius formula applied to $L^1$-functions shows that if
$N$ is a sufficiently large integer then
\[
||g^{(N)}||_1\leq (3/4)^N\tag{4}
\]
where $g^{(N)}$ is the $N$-fold convolution of $g$.
Now we have
\[
(1+g+\ldots+g^{N_1})\cdot \psi= 1-g^{(N)}\tag{5}
\]
By (4)  the norm of the $B$-element $g^{(N)}$ is strictly less than one
and hence the right hand side is invertible where the inverse is given
by a Neumann series, i.e. with $g_*=g^{(N)}$  the inverse is

\[ 
\delta_0+\sum_{\nu=1}^\infty\, g_*^\nu
\]
Since convolutions of $L^1({\bf{R}}^+)$-functions still are supported by
$x\geq 0$, it follows from the above that $\psi$ is invertible in $B$ and
Proposition 3 is proved.



\newpage





\centerline {\bf {Appendix  III. The Hardy space $H^1$}}



\bigskip


\noindent
\emph{0. Introduction.}\bigskip


\noindent
\emph{1. Zygmund's inequality}
\bigskip


\noindent
\emph{2. A weak type estimate.}
\bigskip


\noindent
\emph{3. Kolmogorov's inequality.}
\bigskip


\noindent
\emph{4. The dual space of $H^1(T)$}

\bigskip


\noindent
\emph{5. The class BMO}
\bigskip




\noindent
\emph{6. The dual of $\mathfrak{Re}\, H^1\uuu 0(T)$}
\bigskip




\noindent
\emph{7. Theorem of Gundy and Silver}
\bigskip

\noindent
\emph{8. The Hardy space on ${\bf{R}}$.}

\bigskip

\noindent
\emph{9. BMO and radial norms on measures in $D$}.


\bigskip






\centerline {\bf {0. Introduction.}}
\medskip


\noindent
At several occasions we have met the situation where
$F(z)\in\mathcal O(D)$
has bounded $L^1$-norms over circles of radius $r<1$.
The Brothers Riesz theorem in  section I
shows that
if there
is a constant $M$ such that
\[
\int_0^{2\pi}\, |F(re^{i\theta})|d\theta\leq M\quad\colon\quad
0<r<1
\]
then there exists an $L^1$-function $F(e^{i\theta})$
on the unit circle and
\[
\lim_{r\to 1}\, \int_0^{2\pi}\, 
|F(re^{i\theta})-F(e^{i\theta}|\cdot d\theta=0\tag{*}
\]

\noindent
The class of analytic functions $F$ with boundary function in
$L^1(T)$ is denoted by $H^1(T)$ and called the \emph{Hardy space}.
It is tempting to start with a real valued $L^1$-function
$u(\theta)$ on the unit circle and apply the
Herglotz integral formula  which  produces both
the harmonic extension of $u$ and  its conjugate
harmonic function by the equation:
\[
g\uuu\mu(z)=
\frac{1}{2\pi}
\int_0^{2\pi}\,\frac{e^{i\theta}+z}
{e^{i\theta}-z}\cdot u(\theta)d\theta\tag{**}
\]
\medskip

\noindent
It turns out that $g\uuu\mu$ in general does not belong to $H^1(T)$,
i.e. the condition that
$u\in L^1(T)$ does not imply that $g\uuu\mu\in H^1(T)$.
Theorem  0.1 below is due to Zygmund and
gives a necessary and sufficient condition for
the inclusion
$F\in L^1(T)$ when
$u$ is non-negative.
\medskip

\noindent
{\bf 0.1 Theorem.} \emph{Let $u(\theta)$ be a non-negative $L^1$-function on $T$.
Then  $g\uuu\mu(z)\in H^1(T)$ if and only if}

\[
\int_0^{2\pi}
\,u(\theta)\cdot\log^+\,|u(\theta)|\cdot d\theta<\infty
\]
\medskip

\noindent
{\bf Remark.}
That the condition is necessary is proved in section 1.
The proof of sufficiency relies upon  study of
linear operators satisfying 
weak type estimates where  a result due to  Kolmogorov is
the essential point. To profit upon 
Kolmogorov's result in section 3
we   need a weak-type estimate
for the harmonic
conjugation functor which is proved in section 2.
\medskip


\noindent
{\bf{0.2 The dual space of $H^1(T)$.}}
On the unit circle  the Banach space
$C^0(T)$ of continuous complex-valued functions
contains the closed subspace $A_*(D)$ which consists of
those continuous function $f(e^{i\theta})$
on $T$ which extend to analytic functions in the open
disc $|z|<1$ and vanish at $z=0$.
In Theorem 4.3 we prove that
$H^1(T)$ is the dual of the quotient space
\[
B=\frac{C^0(T)}{A_*(D)}
\]
The proof uses the Brothers Riesz theorem.
We shall also consider the subspace $H^1\uuu 0(T)$
of those functions in the Hardy space for which $f(0)=0$.
Here we find that
\[ 
H^1\uuu 0(T)\simeq \bigl[\frac{C^0(T)}{A(D}\bigr]^*\tag{1}
\]
Next,
we seek the dual space
of $H\uuu 0^1(T)$. Using the Brothers Riesz theorem
one finds that
\[ 
H\uuu 0^1(T)^*\simeq \frac{L^\infty(T)}{H^\infty(T)}\tag{2}
\]
where $H^\infty(T)$ is the space of 
boundary values of bounded analytic functions in $D$.

\medskip


\noindent
{\bf{0.3 The dual of $\mathfrak{Re}\, H^1\uuu 0(T)$.}}
The real part determine functions in
$H^1\uuu 0(T)$ which
means that we can identify $H^1\uuu 0(T)$ with a real subspace of
$L^1\uuu{{\bf{R}}}(T)$ whose elements consist of those real\vvv valued
and integrable functions $u(\theta)$ for which the
the Riesz transform also is integrable. Or equivalently,
if we take the harmonic extension
$H\uuu u$ then 
the harmonic conjugate has a boundary function in $L^1\uuu{{\bf{R}}}(T)$
which we denote by $u^*$.
The norm of such a $u$\vvv function 
is defined as

\[ 
||u||= ||u||\uuu 1+||u^*||\uuu 1\tag{*}
\]



\noindent
The norm in (3) is not equivalent to the $L^1$\vvv norm
so we cannot conclude that the dual space is reduced to
real\vvv valued functions in $L^\infty(T)$.
To exhibit elements in the dual space
we first consider some
real\vvv valued function
$F(\theta)$ on $T$.
Let $H\uuu F$ be its harmonic extension to $D$.
For each $0<r<1$
we define the linear functional on 
$\mathfrak{Re}\, H^1\uuu 0(T)$ by:
\[
u\mapsto \int\uuu 0^{2\pi}\, H\uuu F(re^{i\theta})\cdot u(\theta)\cdot d\theta\tag {**}
\]
If  the limit  (*) exists for every $u$
when $r\to 1$
and
the absolute value of this limit is $\leq C\cdot ||u||$ for a constant
$C$, then we have produced a continuous linear functional on
$\mathfrak{Re}\, H^1\uuu 0(T)$.
This leads to a description of the dual space which goes as follows.
The definition of the norm in (*) and the Hahn\vvv Banach theorem
yields for each $\Lambda$ in the dual space a pair
$(\phi,\psi)$ in $L^\infty(T)$ such that
when $f=u+iu^*$ is in $H^1\uuu 0(T)$ then
\[
\Lambda(u+iu^*)=
\int\uuu 0^{2\pi}\, u(\theta)\cdot \phi(\theta)\cdot d\theta+
\int\uuu 0^{2\pi}\, u^*(\theta)\cdot \psi(\theta)\cdot d\theta
\]
Let $\psi^*$ be the harmonic conjugate of $\psi$ which gives
the analytic function $H\uuu\psi+iH\uuu \psi^*$ in $D$.
Since $f=u+iu^*$ vanishes at $z=0$
we get
\[
\int\uuu 0^{2\pi}\, (u+iu^*)(\psi+i\psi^*)
\cdot d\theta=0
\]
Regarding the imaginary part it follows that
\[
\int\uuu 0^{2\pi}
u^*\cdot \psi\cdot d\theta=\vvv \int\uuu 0^{2\pi}\, u\cdot \psi^*\cdot d\theta
\]
We conclude that $\Lambda$ is expressed by
\[
\Lambda(u)= \lim\uuu{r\to 1}\int\uuu 0^{2\pi}\, H\uuu F(re^{i\theta})\cdot
u(\theta)\cdot d\theta
\]
where
\[ 
F(\theta)= \phi(\theta)\vvv \psi^*(\theta)\tag{***}
\]
\medskip

\noindent
Above $\psi^*$ is the harmonic conjugate of a bounded
$\psi$\vvv function where an arbitrary 
$\psi\in L^\infty(T)$ can be chosen.
Next,
recall from XXX that if $\psi\in L^\infty(T)$ then its conjugate
$\psi^*$ belongs to $\text{BMO}(T)$. Hence (***) identifies
the of
$\mathfrak{Re}\, H^1\uuu 0(T)$ with  a subspace of
$\text{BMO}(T)$.
It turns out that one has equality.
More precisely, Theorem 0.4 below which is 
due to C. Fefferman and E. Stein 
asserts that $F$ yields such a continuous linear form if and only if
$F$ has a bounded mean oscillation in the sense of F. John and L. Nirenberg.


\medskip

\noindent
{\bf{0.4 Theorem.}}
\emph{A real\vvv valued $L^1$\vvv function $F$
on $T$ yields a continuous linear functional on
$H^1\uuu 0(T)$ as above if and only if $F\in \text{BMO}(T)$.
Moreover, there exists an absolute constant $C$ such that}
\[
\bigl|\int\uuu 0^{2\pi}\, H\uuu F(re^{i\theta})\cdot u(\theta)\cdot d\theta\,\bigr|\leq
C\cdot ||F||\uuu{\text{BMO}}\cdot ||u||\uuu 1
\]
\emph{for all $r<1$ and $u\in H^1\uuu 0(T)$.}
\bigskip

\noindent
We refer to Section 6 for  details of the  proof which involves several steps
where the essential
step  is to exhibit
certain Carleson measures.
The space of real\vvv valued functions of bounded mean oscillation is
denoted by $\text{BMO}(T)$ and  studied in
Section 5 where
Theorem 5.5 is an important result which clarifies many properties
of functions in $\text{BMO}(T)$.

\medskip

\noindent
{\bf{0.5 The Hardy space on ${\bf{R}}$.}}
It consists of analytic functions $F(z)$ in the upper half\vvv plane
for which there exists a constant $C$ such that
\[ 
\int\uuu{\vvv\infty}^\infty\, |F(x+i\epsilon)\cdot dx\leq C\tag{*}
\] 
hold for every $\epsilon>0$.
This space is denoted by
$H^1({\bf{R}})$.
Let us remark that it differs from $H^1({\bf{T}})$ even if we
employ  the conformal map
\[
w=\frac{z\vvv i}{z+i}\tag{i}
\] 
onto the unit disc.
More precisely, with $F(z)$ given in the upper half\vvv plane
we set
\[ 
f(w)= 
F(\frac{i+iw}{1\vvv w})\tag{ii}
\]
Then the reader can verify that
\[
\lim\uuu{r\to 1}\int\uuu 0^{2\pi}\, |f(re^{i\theta})|\cdot d\theta=
\int\uuu{\vvv\infty}^\infty\, 
\frac{|F(x)|}{1+x^2}\cdot dx\tag{iii}
\]
where $F(x)$ is the almost everywhere defined limit of $F$
on the real $x$\vvv line which by (*)
identifies $F(x)$ with an element in
$H^1({\bf{R}})$.
Since
$\frac{1}{1+x^2}$ is bounded 
it follows that the right hand side is finite in (iii) and hence
$f$ belongs to $H^1({\bf{T}})$.
However, the map $F\to f$ is not bijective
because the convergence in (iii) need not imply that
(*) is finite.
In other words, the Hardy space on the real line is
more constrained and via $F\mapsto f$
it appears s a proper subspace
of $H^1({\bf{T}})$  and the corresponding norms are not equivalent.
\medskip

\noindent
Sections 7 and  9  study  $H^1({\bf{R}})$ and at the end of
section 9 we  introduce Carleson norms on
non\vvv negative Riesz measures in $\mathfrak{Im}(z)>0$
which will be used for interpolation of bounded analytic functions
in Chapter XXX.






\medskip


















\bigskip









\centerline {\bf 1. Zygmund's  inequality}


\bigskip


\noindent
Let
$u(\theta)$ be a non-negative real-valued function on
$T$ such that
\[
\frac{1}{2\pi}
\int_0^{2\pi}u(\theta)d\theta=1\tag{*}
\]
Put
\[
F(z)=
\frac{1}{2\pi}
\int_0^{2\pi}\,\frac{e^{i\theta}+z}
{e^{i\theta}-z}\cdot u(\theta)d\theta
\]
We write
\[ 
F=u+iv
\] 
where $u$ is the harmonic extension of
$u(\theta)$ from $T$ to $D$ and 
$v$ is the harmonic conjugate  which by the
Herglotz
formula is normalised so that $v(0)=0$
The
sufficency part in Zygmund's theorem
follows from the general inequality below:

 \medskip
 
 \noindent
{\bf 1.1 Theorem.} \emph{When   $u(\theta)$ is non-negative and (*) holds
we have}
\[
\int_0^{2\pi}
\,u(\theta)\cdot\text{Log}^+\,|u(\theta)|\cdot d\theta\leq
\frac{\pi}{2}\cdot
\int_0^{2\pi}
|v(\theta)|
\cdot d\theta+
\int_0^{2\pi}\,\text{Log}^+|F(e^{i\theta}]|\cdot d\theta\tag{*}
\]




\bigskip

\noindent \emph{Proof.}
Since $\mathfrak{Re}(F)>0$ holds in $D$
we can write
\[ 
\log \,F(z)=\log\,|F(z)|+i\gamma(z)\quad\colon\quad
-\pi/2<\gamma(z)<\pi/2\tag{i}
\]
Set $G(z)=F(z)\cdot\log\,F(z)$.
Since $F(0)=1$ we have
$G(0)=0$    and  the mean value formula for harmonic functions gives
\[
\int_0^{2\pi}
u(e^{i\theta})\cdot\text{Log}\,|F(e^{i\theta})|\cdot d\theta=
\int_0^{2\pi}
\gamma(e^{i\theta)})\cdot v(e^{i\theta})\cdot d\theta\tag{iii}
\]


\noindent
By (i) the absolute value of the right hand side is majorised by
\[
\frac{\pi}{2}\cdot
\int_0^{2\pi}
|v(\theta)|
\cdot d\theta\tag{iii}
\]

\noindent
Now we use the decomposition
\[
\log\,|F(e^{i\theta})|=
\text{Log}^+\,|F(e^{i\theta})|+\text{Log}^+\,\frac{1}{|F(e^{i\theta})|}
\]
Then (ii) and (iii) give
the inequality
\[
\int_0^{2\pi}
u(e^{i\theta})\cdot\text{Log}^+\,|F(e^{i\theta})|\cdot d\theta\leq
\]
\[\frac{\pi}{2}\cdot
\int_0^{2\pi}
|v(\theta)|
\cdot d\theta+
\int_0^{2\pi}
u(e^{i\theta})\cdot\text{Log}^+\frac{1}{\,|F(e^{i\theta})|}\cdot d\theta
\tag{iv}
\]

\noindent
Since
$\text{Log}^+\frac{1}{\,|F(e^{i\theta})|}\neq 0$
entails that $|F|\leq 1$ and hence also $u\leq 1$,
it follows that the last integral above is majorised by
\[
\int_0^{2\pi}
\text{Log}^+\frac{1}{\,|F(e^{i\theta})|}\cdot d\theta\tag{v}
\]
Next, $\log\,|F(z)|$ is a harmonic function whose value at $z=0$ is zero.
So the mean-value formula for harmonic functions in $D$ gives
the equality:
\[
\int_0^{2\pi}
\text{Log}^+\frac{1}{\,|F(e^{i\theta})|}\cdot d\theta=
\int_0^{2\pi}
\text{Log}^+\,|F(e^{i\theta})|\cdot d\theta\tag{vi}
\]
\medskip


\noindent
Using this and (iv) we get the requested inequality in
Theorem 1.1 since
we also have the trivial estimate
\[
\text{Log}^+\,u(e^{i\theta})\leq
\text{Log}^+\,|F(e^{i\theta})|\tag{vii}
\]

















\bigskip

\centerline
 {\bf 2. The weak type estimate.}
\bigskip

\noindent
Let $u(\theta)$ be non-negative and denote by $v(\theta)$ its harmonic conjugate
function which is obtained via Herglotz formula.If $E$ is a subset of $T$ we denote its
linear Lebesgue measure by
$\mathfrak{m}(E)$.
With these notations the following weak.type estimate hods:

\medskip

\noindent
{\bf 2.1 Theorem.} \emph{For each non-negative $u$-function on $T$
with mean-value one the following holds:}
\[
\mathfrak{m}(\{|v|)>\lambda\}\leq
\frac{ 4\pi}{1+\lambda}\quad\colon\quad \lambda>0
\]


\noindent
\emph{Proof.}
For a given $\lambda>0$ we set
\[ 
\phi(z)=1+\frac{F(z)-\lambda}{F(z)+\lambda}\tag{1}
\]
where $F(z)$  the analytic function constructed as in section 1.
Here $F(0)=u(0)=1$ which gives:
\[
\phi(0)=\frac{2}{\lambda+1}\tag{2}
\]
Next, since $\mathfrak{Re}\, F=u\geq 0$ it
follows that
\[
\bigl |\frac{F(z)-\lambda}{F(z)+\lambda}\bigr |\leq 1\tag{3}
\]

\medskip

\noindent
Hence (1)  gives $\mathfrak{Re}(\phi)\geq 0$ and
mean value formula for the harmonic function
$\mathfrak{Re}(\phi)$ gives:
\[
\frac{4\pi}{1+\lambda}=
\int_0^{2\pi}\,
\mathfrak{Re}\,\phi(e^{i\theta})\cdot d\theta\geq
\int_{\mathfrak{Re}\,\phi\geq 1}
\mathfrak{Re}\,\phi(e^{i\theta})\cdot d\theta\geq
\mathfrak{m}(\{\mathfrak{Re}\,\phi\geq 1\})\tag{4}
\]
Rewriting the last inequality we get:
\[
\mathfrak{m}(\{ \mathfrak{Re}\,\phi\geq 1\})\leq
\frac{4\pi}{1+\lambda}\tag{5}
\]


\noindent
Next,  the construction of
$\phi$ yields the following equality of sets:
\[
\{\mathfrak{Re}\,\phi(e^{i\theta})\geq 1\}=\{\mathfrak{Re}
\,\frac{F(e^{i\theta})-\lambda}
{F(e^{i\theta})+\lambda}\geq 0\}\tag{6}
\]


\noindent
Finally,  with $F(e^{i\theta})= u(\theta)+iv(\theta)$
one has
\[
\mathfrak{Re}\,[\,\frac{F(e^{i\theta})-\lambda}
{F(e^{i\theta})+\lambda}\,]=\frac{u^2+v^2-\lambda^2}{(u+\lambda)^2+v^2}
\]
The right hand side is $\geq 0$ when
$|v|\geq \lambda$ which  gives the
set-theoretic inclusion:
\[
\{|v|>\lambda\}\subset
\{\mathfrak{Re}\,\phi\geq 1\}).\tag{7}
\]
Then  (5) above gives Theorem 2.1.





\bigskip


\centerline{\bf 3. Kolmogorov's inequality}

\bigskip


\noindent {\bf 3.1 Notations.}
Consider a measure space equipped with a probability measure
$\mu$.
Let $f$ be a complex-valued and $\mu$-measurable 
function. For each  $\lambda>0$ we get
the $\mu$-measurable set $\{|f|>\lambda\}$ and then
\[ 
\lambda\mapsto \mu(\{|f|>\lambda\})
\] 
is a decreasing function. Construct
the differential function defined for every $\lambda>0$ by:
\[ 
d\rho_f(\lambda)=\lim_{\delta\to 0}\,
\frac{\mu(\{|f|>\lambda-\delta\})-\mu(\{|f|>\lambda\})}{\delta}\tag{*}
\]
For an arbitrary continuous function
$Q(\lambda)$ defined when $\lambda\geq 0$ 
the  formula in  XX gives the equality: 
\[
\int_0^\infty 
Q(|f|)d\mu=
\int_0^\infty\, Q(\lambda)\cdot d\rho_f(\lambda)\tag{**}
\]
Recall also from XX the formula
\[ 
\int_0^\infty \,
\mu[\{|f|>\lambda\}]\cdot d\lambda=\int\,|f|\cdot d\mu\tag{***}
\]

\medskip

\noindent
{\bf 3.2 Operators of Weak type (1,1).}
Let $\gamma$ be a probability measure on another sample space
and  $T$ is  some   linear map from
$\mu$-measurable functions into
$\gamma$-measurable functions.
\medskip

\noindent
{\bf 3.3 Definition. }\emph{We say that
$T$ satisfies a weak-type estimate of type (1,1)
if
there is a constant $K$ such that  the inequality below holds
for every $\lambda>0$:}
\[ 
\gamma(\{|Tf|>\lambda\}\,)\leq\frac{K}{\lambda}\cdot\int\,|f|\cdot d\mu
\quad\text{when}\quad f\,\,\,\text{is} \,\mu-\text{measurable}
\]

\medskip
\noindent
We can  also regard $L^2$-spaces. The operator
$T$ is $L^2$-continuous if there exists
a constant $K_2$ such that one has the inequality
\[
\int\,|T(f)|^2\cdot d\gamma\leq K_2^2\cdot
\int\,|f|^2\cdot d\mu
\]
Taking square roots it means that the $L^2$-norm
is $K_2$. 
\medskip

\noindent 
{\bf 3.4 Theorem.}
\emph{Let $T$ be a linear operator whose $L^2$-norm is 1 and with
finite weak-type norm $K$.
Then the following holds for each $\mu$-measurable function $f$:}
\[ 
\int\,
|T(f)|\cdot d\gamma\leq 1+4\cdot\int\,|f|\cdot d\mu+
2K\cdot \int\, |f|\cdot\text{Log}^+\,|f|\cdot d\mu
\]

\medskip

\noindent
\emph{Proof.} 
When $\lambda>0$ we decompose $f$
as follows:
\[
f=f_*+f^*\quad\colon
f_*=\chi_{\{|f|\leq\lambda\}}\cdot f\quad\colon\quad
f^*=\chi_{\{|f|>\lambda\}}\cdot f\tag{i}
\]

\noindent For the lower $f_*$-function we use that $T$ has
$L^2$-norm $\leq 1$ and get
\[
\gamma[\{|Tf_*|>\lambda/2\}\,]
\leq\frac{4}{\lambda^2}\int_0^\lambda\, s^2\cdot d\rho_f(s)\tag{ii}
\]

\noindent For $Tf^*$ we apply the weak-type estimate which gives 
\[
\gamma[\{|Tf^*|>\lambda/2\}\,]\leq
\frac{2K}{\lambda}\cdot\int_\lambda^\infty s\cdot d\rho_f(s)\tag{iii}
\]

\noindent 
where we used that
$\int_\lambda^\infty s\cdot d\rho_f(s)$ is the $L^1$-norm of $f^*$.
The set-theoretic inclusion 
\[
\{|Tf|>\lambda\}\subset
\{|Tf_*|>\lambda/2\}\cup\,\{|Tf^*|>\lambda/2\}\implies
\]
\[
\gamma[\{|Tf|>\lambda\}\,]\leq
\frac{4}{\lambda^2}
\int_0^\lambda\, s^2\cdot d\rho_f(s)+
\frac{2K}{\lambda}\cdot\int_\lambda^\infty sd\rho_f(s)\tag{iv}
\]
Next, since $\gamma$ has total mass one the  inequality:
\[ 
\int_0^\infty\,|Tf|\cdot d\gamma\leq 1+
\int_{\{|Tf|>1 \}}\,|Tf|\cdot d\gamma\tag{v}
\]


\noindent
Now (***) in (3.1) is applied to $Tf$ and the measure $\gamma$ which gives
\[
\int_{\{|Tf|>1 \}}\,|Tf|\cdot d\gamma=
\int_1^\infty\, \gamma[\{|Tf|>\lambda\}\cdot d\lambda
\]

\noindent 
By (iv) the
last integral in (v) is majorised by:
\[
4\cdot \int_1^\infty
\,\bigl[\frac{1}{\lambda^2}
\int_0^\lambda\, s^2\cdot d\rho_f(s)\bigr]\cdot d\lambda
+2K\int_1^\infty\, \frac{1}{\lambda}\cdot [\int_\lambda^\infty sd\rho_f(s)]\cdot d\lambda\tag{vi}
\]



\noindent
Next,  from (XX)  one has the equality:
\[
\int_0^\infty\,\bigl[\frac{1}{\lambda^2}
\int_0^\lambda\, s^2\cdot d\rho_f(s)\bigr]\cdot d\lambda=\int\,|f| \cdot d\mu\tag{vii}
\]
The left hand side is only smaller if the 
$\lambda$-integration starts at 1. It follows that the
first term in (vi) above is majorised by
$4\cdot \int\,|f| \cdot d\mu$ and together with (v) we
conclude that

\[
\int_0^\infty\,|Tf|d\gamma\leq 1+4\int\,|f|d\mu+
2K
\int_1^\infty\,[\frac{1}
{\lambda}\cdot\int_\lambda^\infty sd\rho_f(s)]\cdot d\lambda\tag{viii}
\]
Finally, 
\[
\int_1^\infty\,[\frac{1}
{\lambda}\cdot\int_\lambda^\infty sd\rho_f(s)]\cdot d\lambda=
\iint_{1\leq\lambda\leq s}\,
\frac{1}{\lambda}\cdot
s\rho_f(s) ds=\int_1^\infty s\cdot \text{Log}\, s\cdot d\rho_f(s)
\]
\medskip

\noindent
The last integral is equal to $\int \,f\cdot\text{Log}^+\,|f|\cdot d\mu$
by the general formula XX. 
Inserting this in (viii) we get  Theorem 3.4.

\bigskip

\centerline{\bf 3.5. Final part of  Theorem 0.1}
\bigskip

\noindent
There remains to show that if $u$ is non-negative and if 
$u\cdot \text{Log}^+u$ is integrable so is $v$.
To prove this we use $d\mu=d\gamma=\frac{d\theta}{2\pi}$
on the unit circle.
Theorem 2.1  which shows that the harmonic conjugation operator
$T\colon u\mapsto v$ is of weak-type (1,1) and it is
continuous on $L^2(T)$  by
Parseval's formula. Hence  Kolomogorv's Theorem gives
$v\in L^1(T)$ which proves the necessity in Theorem 0.1.


\bigskip

\noindent
{\bf Remark.} Notice that
Theorem 3.4 applies when we start from any
real-valued function  $u(\theta)$.
So have the following supplement to Theorem 0.1.

\bigskip

\noindent
{\bf 3.6 Theorem.} \emph{There exists an absolute constant $A$ such that}
\[
\int_0^{2\pi}\, |v(\theta)|\cdot d\theta\leq
A\cdot\bigr[\int_0^{2\pi}\, |u(\theta)|\cdot d\theta+
\int_0^{2\pi}\, |u(\theta)|\cdot \text{Log}^+|u(\theta)|\cdot  d\theta\,\bigr]
\]




\bigskip

\centerline{\bf 4. The Dual space of $H^1(T)$}
\medskip

\noindent
On the unit circle $T$
we have the Banach space
$L^1(T)$ 
where $H^1(T)$ is a closed subspace.
Next, let $C^0(T)$ be the Banach space of continuous
functions on $T$ equipped with the maximum norm.
It contains the closed subspace $A(D)$
whose functions can be extended as
analytic  functions in the open disc $D$.
We have also the subspace $A_*(D)$
which consists of  the functions in $A(D)$ whose analytic
extensions are zero at the origin.
As explained in XXX a continuous function $f$ on $T$
belongs to $A_*(D)$ if and only if
\medskip
\[
\int_0^{2\pi}\, e^{in\theta}\cdot f(e^{i\theta})\cdot d\theta=0
\quad\colon\quad n=0,1,\ldots
\tag{*}
\]


\noindent
From (*) it follows that
\[
\int_0^{2\pi}\,g(e^{i\theta})\cdot f(e^{i\theta})\cdot d\theta=0
\quad\colon\quad f\in A_*(D)\quad\text{and}\quad \, g\in H^1(T)\tag{**}
\]
Let us now regard the
Banach space
\[ 
B=\frac{C^0(T)}{A_*(D}
\]


\noindent
Riesz representation formula identifies the
dual space of $C^0(T)$ with Riesz measures on $T$.
Since $B$ is a quotient space its dual space becomes
\[ 
B^*=\{\,\mu\in M(T)\quad\colon\, \mu\perp A_*(D\,\}\tag{i}
\]


\noindent
Now a Riesz measure $\mu$ is $\perp A_*(D$
if and only if
\[
\int_0^{2\pi}\, e^{in\theta}\cdot d\mu(\theta)=0
\quad\colon\quad n=1,2\ldots\tag{ii}
\]


\noindent The Brothers Riesz theorem means
that  (ii) holds if and only if
$\mu$ is absolutely continuous, i.e. $\mu$
is given by some $L^1$-function $f$ which 
satisfies:
\[
\int_0^{2\pi}\, e^{in\theta}\cdot f(e^{i\theta})\cdot d\theta=0
\quad\colon\quad n=1,2\ldots\tag{iii}
\]
This is precisely the condition  that
$f\in H^1(T)$. Hence the whole discussion gives:
\bigskip

\noindent 
{\bf 4.1 Theorem.}
\emph{The Hardy space $H^1(T)$ is the dual of $B$.}
\bigskip

\noindent
{\bf 4.2 The dual of $H^1(T)$.}
Recall that $L^\infty(T)$ is the dual space of
$L^1(T)$.
So by a general formulafrom Appendix: Functional analysis
we get:

\[
H^1(T)^*=
\frac{L^\infty(T)}{H^1(T)^\perp}
\]


\noindent
Next, an $L^\infty$-function $f$ is $\perp H^1(T)$ if and only if
\[
\int_0^{2\pi}\, e^{in\theta}\cdot f(e^{i\theta})\cdot d\theta=0
\quad\colon\quad n=0,1,2\ldots
\]


\noindent
But this means precisely that $f$ is the boundary value of an analytic function
in $D$ which vanishes at the origin.
Let us identify  $H^\infty(D)$ with
a subalgebra of  $L^\infty(T)$
which is denoted by $H^\infty(T)$. Then we also get the subspace
$H_0^\infty(T)$ of those functions which are zero at
the origin.
Hence we have proved
\medskip

\noindent 
{\bf Theorem  4.3} \emph{The dual space of $H^1(T)$ is equal to the quotient
space}
\[ 
\frac{L^\infty(T)}{H^\infty_0(T)}
\]
\medskip



\centerline{\bf 5. BMO}


\bigskip


\noindent
{\bf Introduction.}
Functions of bounded mean oscillation were
introduced by F. John and L. Nirenberg in
[J-N].
This class of Lebesgue measurable functions
can be defined in $\bf R^n$ for every $n\geq 1$. Here we are content to
study the case $n=1$ and  restrict the attention to periodic functions
which is adapted to the class BMO on the unit circle. 
So let $F(x)$ be a locally integrable function on the real $x$-line
which is $2\pi$-periodic, i.e. 
$F(x+2\pi)=F(x)$.
If $J=(a,b)$ is an interval we  get the mean value
\[ 
F_J=\frac{1}{b-a}\cdot\int_a^b\, F(x)dx
\]
To every interval $J$ we put
\[
|F|_J^*=\int_J\,|F(x)-F_J|\cdot dx
\]
\medskip

\noindent 
{\bf 5.1 Definition.}
\emph{The function $F$ has a bounded mean oscillation if there exists a constant
$C$ such that
$|F|_J\leq C$ for all intervals $J$. When this holds the smallest constant
is denoted by $|F|_{\text{BMO}}$.}
\medskip

\bigskip

\noindent
{\bf 5.2 The case $n\geq 2$.}
Even though these notes are devoted to complex analysis in
dimension one, we cannot refrain from
mentioning a result which illustrates how the class BMO enters
in Fourier analysis. Namely, let $F(x)$ be an $L^1$-function with
compact support in $\bf R^n$. Assume 
that there exists a constant $C$ such that
its Fourier transform
$\hat F(\xi)$
satisfies the decay condition
\[ 
|\widehat F(\xi)\leq C\cdot(1+|\xi|)^{-n}\quad\colon\quad \xi\in\bf R^n\tag{*}
\]
This is not quite enough for $\widehat F$
to be integrable. So we cannot expect
that (*) implies that $F(x)$ is a bounded function.
However, its belongs to BM0 and more precisely one has:

\medskip

\noindent
{\bf{5.3 Theorem.}}
\emph{To each $M>0$ there exists a constant $C_M$ such that if $F(x)$
has support in the ball $\{|x|\leq M\}$
then}
\[ ||F||_{\text{BMO}}\leq C_M\cdot \max_\xi\,
\bigl[1+|\xi|)^n\cdot |\widehat F(\xi)|\bigr]
\]
For the proof we refer to [Björk]. See also  [Sjölin] for an
improved result
that $F$ belongs to BMO under less restrictive conditions expressed by
certain $L^2$-integrals of $\widehat F$ over   dyadic
grids. 
\bigskip

\centerline {\bf{5.4 The John-Nirenberg inequality.}}
\medskip


\noindent
Now we turn to the main topic in this section and prove
an 
inequality due to  F. John and L. Nirenberg  which is
presented for the 1\vvv dimensional periodic case.
See  [J-N] for
higher dimensional results.
\bigskip

\noindent







\noindent
{\bf 5.5 Theorem}
\emph{Let $F(x)$ be a $2\pi$-periodic function on
the real $x$-line which belongs to  BMO on $T$.  For every interval $J$ on
${\bf{R}}$ 
and every positive integer $n$ one has}
\[ 
\mathfrak{m}[\{ x\in J\,\colon\, \bigl|F(x)-F_J\bigr|\geq
4n\cdot |F|_{\text{BMO}}\}]\leq 2^{-n}\cdot |J|
\]
\medskip


\noindent
The proof requires several steps.
To begin with we make some trivial observations.
The BMO-norm of $F$ is unaffected when we add a constant to
$F$ and also 
under a translation, i.e. when we regard $F_a(x)=F(x+a)$ for some
real number $a$. Moreover, the BMO-norm is 
unchanged under dilations, i.e. when 
$t>0$ and $F_t(x)=F(tx)$.
Before we enter the proof we  need a preliminary result.
\medskip

\noindent {\bf 5.6 Lemma.}
\emph{Let $F$ belong to BMO. Let $I\subset J$ be two intervals with the same 
mid-point. Then}
\[
|F_J-F_I|\leq  2\cdot[\text{Log}_2\,\frac{|J|}{|I|}+1]\cdot |F|_\text{BMO}
\]

\medskip


\noindent{\bf{Exercise.}} Prove this result.

\bigskip



\noindent
\emph{Proof of Theorem 5.5}.
Replacing $F$ by $cF$ for some positive constant 
we may assume that its BMO-norm is 1/2.
and that $F_J=0$. Moreover, by the invariance under dilations
and translations  we may
assume that $J$ is the unit interval.
Thus, there remains to consider the set

\[ 
E_n=\{ x\in [0,1]\,\, \colon\,\, F(x)> 2n\}\tag{i}
\]
and  show that 
\[
\mathfrak{m}(E_n)\leq 2^{-n}\tag {ii}
\]

\noindent
Let us begin with the case $n=1$. 
For every $x\in E_1$ which is a Lebesgue point for $F$ we find the
unique largest dyadic interval $J(x)$ such that
\[
x\in J(x)\subset [0,1]\quad\colon\quad
\frac{1}{\mathfrak{m}(J(x))}\int_{J(x)}\, F(t)dt >1\tag{iii}
\]
Up to measure zero, i.e. ignoring the null set where
$F$ fails to have Lebesgue points, we have the inclusion 
\[ 
E_1\subset\,\cup_{x\in E_1}\, J(x)\tag{iv}
\]


\noindent 
Next, suppose we have a \emph{strict} inclusion $J(x)\subset J(y)$
for a pair of dyadic intervals in this family
which means that
$\mathfrak{m}(J(y))>\mathfrak{m}(J(x))$.
But this is impossible for then $x\in J(y)$ which contradicts 
the maximal choice of $J(x))$ as the dyadic interval of largest possible length containing $x$.
Hence the family $\{J(x_\nu)\}$ consists of dyadic intervals which either are equal or disjoint.
We can therefore pick a disjoint family where the corresponding $x$-points are
denoted by $x^*_\nu$
and obtain the set-theoretic inclusion
\[ 
E_1
\subset\,\cup\,\, (J(x^*_\nu)\tag{v}
\]
Next, put $\mathcal E=\cup\, J(x^*_\nu)$.
Since the mean value of $F$ over each $J(x^*_\nu)$ is 
$\geq 1$ we obtain
\[
\mathfrak{m}( \mathcal E)\leq
\sum\,\int_{J(x^*_\nu)}\,F(x)dx=
\int_{\mathcal E}\,F(x)dx\leq
\int_{\mathcal E}\,|F(x)|dx\leq\int_0^1\, |F(x)|dx
\leq |F|_{\text{BMO}}
\]
where the last inequality follows from the definition of the BMO-norm
and the condition that the mean-value of $F$ over the unit interval was zero.
Since the BMO-norm of $F$ was 1/2 the inclusion (v) gives:
\[
\mathfrak{m}( E_1)\leq\mathfrak{m}(\mathcal E)\leq 1/2\tag{*}
\] 


\noindent
This proves the case $n=1$ and  we proceed by an
induction over $n$.
Let us first regard one of the dyadic intervals $J(x^*_\nu)$
from the family covering $E_1$.
If $2^{-N}$ is the length of $J(x_\nu^*$
the
dyadic exhaustion of $[0,1]$ gives
a dyadic interval $J'$ of length $2^{-N+1}$
which contain $J(x_\nu^*)$.
The maximal choice of $J(x_\nu^*)$ gives:
\[
\frac{1}{\mathfrak{m}(J')}\int_{J'} F(t)dt\leq 1\tag{vi}
\]
Apply Proposition XX to the pair $J(x_\nu^*)$ and $J'$.
Since $|F|_{\text{BMO}}=1/2$ is assumed and $\text{Log}_2(2)=0$
we obtain
\[
F_{J(x_\nu^*)}=\frac{1}{\mathfrak{m}(J(x_\nu^*))}\int_{J(x_\nu^*)}\, F(t)dt \leq 2
\tag{vii}
\]
Let $n\geq 2$ and for every $\nu$ we set:
\[
E_n(\nu)=E_n\cap J(x_\nu^*)\tag{viii}
\]
Since $F(x)>2n$ holds on $E_n$ we  get
\[
F(x)-F_{J(x_\nu^*)}>2(n-1)\quad\colon\quad  x\in E_n(\nu)\tag{ix}
\]
 
 
 
\medskip

\noindent Hence we have the inclusion
\medskip
\[ 
E_n(\nu)\subset W_n(\nu)= \{
x\in J(x_\nu^*)\quad\colon\,
F(x)-F_{J(x_\nu^*)}>2(n-1)\}\tag{x}
\]



\noindent
By a change of scale we can use
the interval $J(x_\nu^*)$ instead of the unit interval 
and by an induction assume that the inequality in
Theorem xx holds for $n-1$. It follows that
the set in right hand side  in (x) is estimated by:
\medskip
\[ 
\mathfrak{m}(W_n(\nu))\leq 2^{-n+1}\cdot
\mathfrak{m}(J(x_\nu^*))\tag{xi}
\]


\noindent
The set-theoretic inclusion (x)
therefore gives
\[
\mathfrak{m}(E_n(\nu))\leq 2^{-n+1}\cdot
\mathfrak{m}(J(x_\nu^*))\tag{xii}
\]

\noindent
Finally, since $E_n\subset E_1$ and
we already have the inclusion (iv)
we obtain
\[ 
\mathfrak{m}(E_n)=
\sum\,
\mathfrak{m}(E_n(\nu))\leq 2^{-n+1}\cdot\sum\, 
\mathfrak{m}(J(x_\nu^*))=2^{-n+1}\mathfrak{m}(\mathcal E)
\leq2^{-n+1}\cdot\frac{1}{2}= 2^{-n}
\]
\medskip
This proves the induction step and Theorem 5.5 follows.
\bigskip

\centerline{\bf{5.7 An $L^2$\vvv inequality}}
\medskip


\noindent
Let $F\in\text{BMO}(T)$ be given.
Given some interval $J\subset T$
and $\lambda>0$ we set
\[
\mathfrak{m}\uuu J(\lambda)=
\{\theta\in J\,\colon\, |F(\theta)\vvv F\uuu J|>\lambda\}
\]
Consider the integral

\[ 
I=\frac{1}{|J|}\cdot\int\uuu 0^\infty\,\lambda\cdot \mathfrak{m}\uuu J(\lambda)\cdot d\lambda\tag{*}
\]
Set $A=4\cdot ||F||\uuu{\text{BMO}}$. 
Theorem 5.5. gives

\[
I=\frac{1}{|J|}\cdot \sum\uuu{n=0}^\infty\,
\int\uuu {nA}^{(n+1)A}\,\lambda\cdot \mathfrak{m}\uuu J(\lambda)\cdot d\lambda
\leq
\frac{1}{|J|}\cdot \sum\uuu{n=0}^\infty\,(n+1)A\cdot |J|\cdot \cdot 2^{\vvv n}=
C||F||\uuu{\text{BMO}}
\]
where $C= 4\cdot \sum\uuu{n=0}^\infty\,(n+1)\, 2^{\vvv n}$
is an absolute constant.
Next, by the general result in XX (*) is equal to
\[
\frac{1}{|J|}\cdot \int\uuu J\, |F(x)\vvv F\uuu J|^2\cdot dx\tag{**}
\]
So by the above  (**) is majorized by an absolute constant times
the BMO\vvv norm of $F$.




\newpage




\centerline{\bf{5.8 BMO and the Garsia norm.}}
\bigskip

\noindent
Using the $L^2$\vvv inequality in (5.7)
an elegant description of $\text{BMO}(T)$
was discovered by Garsia which we shall use in
Section 6. First we give:
\bigskip


\noindent
{\bf{5.9 Definition.}} \emph{To each real\vvv valued $u\in L^1(T)$
we define a function in $D$ by}

\[
\mathcal G\uuu u(z)=
\frac{1}{8\pi^2}
\cdot \iint\,\frac{(1\vvv |z|^2)^2}{|e^{i\theta}\vvv z|^2\cdot |e^{i\phi}\vvv z|^2}
\cdot
[u(\theta)\vvv u(\phi)]^2\cdot d\theta d\phi
\]
\medskip

\noindent
\emph{If this function is bounded  we set}
\[ 
\mathcal G(u)=\max\uuu{z\in D}\, \sqrt{\mathcal G\uuu u(z)}\tag{*}
\]
\emph{and say that $u$ has a finite Garsia norm.}

\medskip

\noindent
{\bf{Remark.}} Notice that constant functions have
zero\vvv norm. So just as for BMO the 
$\mathcal G$\vvv norm is defined on the quotient of functions modulu
constants.



\medskip

\noindent
{\bf{5.10 Exercise.}}
Expanding
the square $[u(\theta)\vvv u(\phi)]^2$
the reader can verify that
\[ 
\mathcal G\uuu u= H\uuu{u^2}\vvv H^2\uuu u\tag{*}
\] 
where $H\uuu {u^2}$ is the harmonic extension of $u^2$.
and $ H^2\uuu u$ the square of the harmonic extension $H\uuu u$.


\medskip

\noindent
{\bf{5.11 Theorem.}} 
\emph{An $L^1$\vvv function $u$ has finite Garsia norm if and only if
it belongs to BMO. Moreover, 
there exists a constant $C\geq 1$ such that}

\[ 
\frac{1}{C}\cdot 
||u||\uuu{\text{BMO}}\leq
\mathcal G(u)\leq 
C\cdot ||u||\uuu{\text{BMO}}
\]
\medskip

\noindent{\bf{5.12 Exercise.}}
The reader is invited to prove this result using
the previous facts about BMO and also
straightforward properties of the Poisson kernel.
if necessary, consult [Koosis  p. xxx\vvv xxx]
for details.
\bigskip


\noindent
{\bf{5.13  The Garsia norm and Carleson measures.}}
Let $f$ be a real\vvv valued continuous function on $T$.
We get the two harmonic functions $H\uuu f$ and $H\uuu{f^2}$ and recall from
(5.10) that
\[ 
\mathcal G\uuu f=H\uuu{f^2}\vvv(H\uuu f)^2
\]
In XX we  introduced the family of Carleson
sectors in $D$ and now we prove
an important inequality.


\medskip

\noindent
{\bf{5.14 Theorem.}}
\emph{For every Carleson sector $S\uuu h$ with $0<h<1/2$
and each $f\in C^0(T)$
one has the inequality}

\[
\frac{1}{h}\cdot \iint\uuu{S\uuu h}\, 
|z|\cdot \log\,\frac{1}{|z|}\cdot
\bigl |\nabla(H\uuu f)\bigr |^2\cdot dxdy\leq
96\cdot \mathcal G(f)^2
\]
\medskip


\noindent
\emph{Proof.}
We use the conformal map where $z=\frac{\zeta\vvv i}{\zeta+i}$.
If $\phi(z)$ is a function in $D$ we get the function
$\phi^*(\zeta)$  in the upper half\vvv plane where 
\[
\phi(\frac{\zeta\vvv i}{\zeta+i})=\phi^*(\zeta)
\]
One easily verifies that 
\[ 
(|z|\cdot \log\,\frac{1}{|z|})^*(\xi+i\eta)\leq
8\cdot \eta\tag{i}
\]
Set $w(\zeta)= H\uuu f^*(\zeta)$.
Then (i) implies that
the double integral which appears in the Theorem  5.14 is majorised by 
\[ 
J^*=8\cdot \iint\uuu{S\uuu h^*}\, \eta\cdot|\nabla(w)|^2 \cdot d\xi d\eta\tag{ii}
\]
where $S\uuu h^*$ is the image of $S\uuu h$ under the conformal map
and 
$|\nabla(w)|^2=w\uuu\xi^2+w\uuu\eta^2$.
Next, from (*) in Exercise 5.10 we have

\[
w^2=H\uuu{f^2}^*\vvv\mathcal G\uuu f^*
\]
Since $H^*\uuu{f^2}$ is harmonic  we obtain
\[
2\cdot |\nabla(w)|^2=\Delta(w^2)=\vvv\Delta(\mathcal G\uuu f^*)\tag{iii}
\]
where the first easy equality follows since $w$ is harmonic.
As explained by figure XX the set $S^*\uuu h$
is placed above an interval on the real $\xi$\vvv line and 
and since the subsequent estimates are invariant under the center of this interval
we therefore may take it as $\xi=0$.
Let us  introduce the half\vvv disc
\[
 D\uuu{2h}=\{|\zeta|<2h\}\cap \{\eta>0\}
 \]
Then a figure shows that
\[
S^*\uuu h\subset D\uuu{2h}\tag{iv}
\]
Next, consider the 
function $1\vvv\frac{|\zeta|}{2h}$ and notice that it is
$\geq 1/4$ in $D\uuu{2h}$.
Recall from the above that
\[
\Delta(\mathcal G\uuu f^*)=\vvv 2\cdot |\nabla(w)|^2\leq 0
\]
From the inclusion (iv) and taking the minus signs into the account
it follows from (ii) that
\[ 
J^*\leq \vvv 16\cdot \iint\uuu{D\uuu{2h}}
 \eta(1\vvv\frac{|\zeta|}{2h})\cdot\Delta (\mathcal G^*\uuu f) \cdot d\xi d\eta\tag{v}
\]
Apply Green's formula
to the pair $\mathcal G^*\uuu f$ and $\rho=\eta(1\vvv\frac{|\zeta|}{2h})$.
Here $\rho=0$ on the boundary of $D\uuu{2h}$
and it is easily checked that the outer normal 
$\partial\uuu n(\rho)\leq 0$. At the same time
$\mathcal G^*\uuu f\geq 0$ and from this it follows that
(v) gives:
\[ 
J^*\leq \vvv 16\cdot \iint\uuu{D\uuu{2h}}
 \Delta(\eta(1\vvv\frac{|\zeta|}{2h}))\cdot\mathcal G^*\uuu f
 \cdot d\xi d\eta\tag{iv}
\]
Next, using polar coordinates
$(r,\phi)$ an easy computation gives
\[
 \Delta(\eta(1\vvv\frac{|\zeta|}{2h}))=\vvv\frac{3}{2h}\cdot \sin\,\phi
 \]
It follows that
\[ 
J^*\leq  \frac{24}{h}\cdot 
\iint\uuu{D\uuu{2h}}
\mathcal G^*\uuu f\cdot \sin\,\phi\cdot rdr d\phi
\]
Finally, by definition  $\mathcal G(f)^2 $ is the maximum norm of 
$\mathcal G\uuu f$ in $D$ which is $\geq$ the maximum norm of
$\mathcal G^*\uuu f$ in $D\uuu{2h}$. So
the last integral is majorised by
\[
\frac{24 \mathcal G(f)^2}{h}\cdot 
\iint\uuu{D\uuu{2h}}
\sin\,\phi\cdot rdr d\phi=
96\cdot  \mathcal G(f)^2\cdot h
\]
After a division with $h$ we get Theorem 5.14.
\medskip

\noindent
{\bf{5.15 Remark.}}
Since $|z|\geq 1/2$ holds in sectors $S\uuu h$ with $0<h<1/2$
we can remove the factor $|z|$ and hence  Theorem 5.14
shows that
if $\mathcal G\uuu f(z)$ is  bounded  in $D$
then we obtain a Carleson measure in $D$ defined by
\[
\mu\uuu f=
\log\,\frac{1}{|z|}\cdot
\bigl |\nabla(H\uuu f)\bigr |^2\tag{*}
\]
Moreover, its Carleson norm is estimated via Theorem 5.11 and
Theorem 5.24 by an absolute constant times
$|F|\uuu{\text{BMO}}$.


\bigskip

\centerline{\bf{6. Proof of Theorem 0.4}}

\bigskip

\noindent
By the observations before Theorem 0.4 here remains to prove that if
$F\in\text{BMO}(T)$ then (*) holds in Theorem 0.4 for some
constant $C$. To obtain this we need some
preliminary results
derived via Green's formula.
\medskip

\noindent
{\bf{6.1 Some integral formulas.}}
To simplify notations we set
\[ 
\int\uuu0^{2\pi}\, g(e^{i\theta})\cdot d\theta= \int\uuu T\, g\cdot d\theta
\]
for integrals over the unit circle.
Now follow some results which are left as exercises and  proved by
Green's formula.
\medskip

\noindent
{\bf{A. Exercise.}}
For every $C^2$\vvv function
$W$ in the closed unit disc with $W(0)=0$
we have
\[
\int\uuu T\, W\cdot d\theta=\iint\uuu D\, \log\,\frac{1}{|z|}\cdot \Delta(W)\cdot dxdy\tag{1}
\]
Next, if
 \[
W= |z|\cdot W\uuu 1\tag{2}
\]
\medskip

\noindent
{\bf{B. Exercise.}}
Let $u,v$ is a pair of $C^2$\vvv functions which both are harmonic
in the open disc. Show that 
\[
\Delta(uv)=2\cdot \langle \nabla(u),\nabla(v)\rangle\tag{i}
\]
and use (A) to prove the equality
\[ 
\int\uuu T\, uv\cdot d\theta=\iint\uuu D\, \log\,\frac{1}{|z|}\cdot
\langle \nabla(u),\nabla(v)\rangle\cdot dxdy\tag{ii}
\]
\medskip

\noindent
{\bf{C. Exercise.}}
Let $f=u+iv$ be analytic in $D$. Verify that
\[
\Delta(|f|)=\frac{1}{|f|}\cdot |\nabla(u)|^2\tag{i}
\]
holds outside the zeros of $f$. Show also that
if 
\[ 
f=z\cdot g\tag{ii}
\] 
where $g$ is zero\vvv free in $D$ then
\[
\int\uuu T\, |f|\cdot d\theta=
\iint\uuu D\, \log\,\frac{1}{|z|}\cdot\frac{|\nabla(u)|^2}{|f|}\cdot dxdy\tag{iii}
\]

\noindent
Finally, let  $f$ be as in (ii) and $F$ a  real\vvv valued $C^2$\vvv function in
$D$. Show that
\[
\frac{1}{2}\int\uuu T\, u\cdot F\cdot d\theta=
\iint\uuu D\, \log\,\frac{1}{|z|}\cdot
\langle \nabla(u),\nabla H\uuu F\rangle\cdot dxdy\tag{iii}
\]






\bigskip

\centerline{\emph{6.2 Proof of Theorem 0.4}}
\bigskip

\noindent
Let $f\in H^1\uuu 0(T)$. Then one finds a Blaschke product
$B$ such that
\[
f(z)=z\cdot B(z)\cdot g(z)
\]
where $g$ is zero\vvv free in $D$.
It follows that
\[
2f=z(B+1)\cdot g+z(B\vvv 1)\cdot g=f\uuu 1+f\uuu 2
\]
where 
$||f\uuu\nu||\uuu 1\leq 2\cdot ||f||\uuu 1$ hold for each $\nu$.
Using this trick we conclude that
it suffices to estasblish 
Theorem 0.4 for $H^1(T)$\vvv functions
of the form
$f(z)= z\cdot g(z)$ with a
zero\vvv free function $g$ in $D$.
We write $f=u+iv$
and for each real\vvv valued $C^2$\vvv function $F(\theta)$ on $T$
we have by (iii) from Exercise C:

\[
\frac{1}{2}\cdot 
\int\uuu 0^{2\pi}\, F(\theta)\cdot u(\theta)\cdot d\theta=
\iint\uuu D\, \log\,\frac{1}{|z|}\cdot \langle \nabla(u),\nabla(H\uuu F)\rangle
\cdot dxdy\tag{1}
\]
Insert the factor $1=\sqrt{|f|}\cdot \frac{1}{\sqrt{|f|}}$
and apply the Cauchy\vvv Schwarz inequality which
estimates the absolute value of (i)
by

\[ 
J=\sqrt{
\iint\uuu D\, \log\,\frac{1}{|z|}\cdot \frac{|\nabla(u)|^2}{|f(z)|}
\cdot dxdy}\cdot
\sqrt{\iint\uuu D\, \log\,\frac{1}{|z|}\cdot |\nabla(H\uuu F)|^2\cdot |f(z)|}
\cdot dxdy\tag{2}
\]
The equality (iii) in Exercise C shows the first factor is equal to
$\sqrt{||f||\uuu 1}$.
In the second factor appears the density function 
$\log\,\frac{1}{|z|}\cdot |\nabla(H\uuu F)|^2$ in $D$.
\medskip

\noindent
Finally,  by
the  Remark in (5.15) 
the Carleson norm of the density
$\log\,\frac{1}{|z|}\cdot |\nabla(H\uuu F)|^2$
is bounded by an absolute constant
$C$ times the BMO\vvv norm of $F$.
Together with the result in XXX in Section XXX we get an absolute constant
$C$ such that the last factor in (2) above is bounded by
\[
C\cdot |F|\uuu{\text{BMO}}\cdot\sqrt{||f||\uuu 1}\tag{3}
\]
which finishes
the proof of
Theorem 0.4.












\bigskip

\centerline {\bf 7. A theorem by Gundy Silver}


\bigskip




\noindent
{\bf Introduction.}
Let $U(x)$ be in $L^1({\bf{R}})$ and construct its
harmonic extension  to the upper half plane:
\[
U(x+iy)=\frac{1}{\pi}\cdot \int\,\frac{y}{(x-t)^2+y^2}\cdot
U(t)\cdot dt
\]
\noindent
The  harmonic conjugate of $U(x+iy)$   is given by:
\[ 
V(x+iy)=\frac{y}{\pi}\int\,\frac
{U(t)\cdot dt}{(x-t)^2+y 2}\tag{0.1}
\]
\medskip


\noindent
Next, to each real  $x_0$  the Fatou sector in the upper half-plane is defined by
\[
\{x+iy)\quad\text{such that}\quad \,|x-x_0|\leq y\}\tag{0.2}
\]
and the maximal function $U^*$ over Fatou sectors 
is defined on the real $x$\vvv axis by
\[ 
U^*(x_0)=\max\, |U(x+iy)|\colon\quad\colon |x-x_0|\leq y\tag{0.3}
\]

\medskip

\noindent
In XXX we proved that if $V\in L^1(R)$
then $U^*(x)\in L^1({\bf{R}})$
and there exists
an absolute constant $C_0$ such that
\[ 
||U^*||_1\leq \int_{-\infty}^\infty\, \bigl(\,|U(x)|+|V(x)| \,\bigr)dx\tag{*}
\]


\noindent
A reverse inequality is due to
Burkholder, Gundy and Silverstein.

\medskip

\noindent {\bf Theorem 7.1.} \emph{One has the inequality}
\[ 
\int\,|V(x)|dx\leq  4\int\,U^*(x)dx
\]
\medskip


\noindent
{\bf Remark.}
Hence $U^*$ belongs to $L^1$ if and only if
the boundary value function $V(x)$ belongs to $L^1$.
The  original proof in [BGS] used 
probabilistic methods. Here we  give a proof
based upon
methods from [Feff-Stein].
Since we 
shall establish an \emph{a priori estimate}, it suffices to assume that
$U(x)$ from the start is a nice function. In particular
we may assume that both $U(x+iy)$ and $V(x+iy)$
have rapid decay when $y\to+\infty$ in the upper half-plane.
This assumption is used below to ensure that a certain complex line
integral is zero.

\bigskip



\centerline{\emph{Proof of Theorem 7.1}}
\medskip


\noindent
Given $\lambda>0$ we put
\[ 
J_\lambda=\{ x\colon U^*(x)>\lambda\}
\]
\medskip


\noindent
The closed complement
${\bf{R}}\setminus J_\lambda$ is denoted by $E$.
Let $\{(a_\nu,b_\nu)\}$ be the disjoint intervals of $J_\lambda$.
Construct the piecewise linear
$\Gamma$-curve
which stays on the real $x$-line on 
$E$ while it follows the two sides
of the triangle $T_\nu$
standing on $(a_\nu,b_\nu)$ for each $\nu$.
So  the  corner point of $T_\nu$ in the upper half-plane is:
\[
p_\nu=\frac{1}{2}(a_\nu+b_\nu)(1+i)
\]
Set $\partial T= \Gamma\setminus E$ and notice 
that the construction of Fatou sectors gives
\[ 
U^*(x)\leq \lambda\quad\colon\quad x\in T\tag {1}
\]

\noindent
In $\mathfrak{Im}(z)>0$
we have the
analytic function
$G(z)=(U+iV)^2$.
By hypothesis  $U$
$y\mapsto G(x+iy)$ decreases quite rapidly which gives
a vanishing complex line integral:
\[ 
\int_\Gamma\,G(z)dz=0
\] 



\noindent
Now $\Gamma$ is the union  of $E$
and the union of  of the broken lines which give the two sides
of the $T_\nu$-triangles.
Let $\partial T$ denote the union of these
broken lines. Since the complex differential $dz=dx+idy$
the real part of the complex line integral is zero which gives

\[
\int_E\, (U^2-V^2)\cdot dx+
\int_{\partial T}(U^2-V^2)\cdot dx-2\cdot 
\int_{\partial T}U\cdot Vdy\tag{2}
\]
On the sides of  the $T$-triangles
the slope is plus or minus $\pi/4$  and hence $|dy|=|dx|$
where $|dx|= dx$ is positive.
Hence the he inequality
$2ab\leq a^2+b^2$ for any pair of  non-negative numbers gives:
\[ 
2\cdot \bigl|\int_{\partial T}\,
 UV dy\,\bigr |\leq  \int_{\partial T}\, U^2\cdot dx+\int_{\partial T}\,V^2\cdot dx\tag{3}
\]


\noindent
Since (2) is zero we see that (3) and the triangle inequality
give:
\[
\int_E\, V^2\cdot dx\leq 
\int_E\, U^2\cdot dx+
2\cdot \int_{\partial  T}\, U^2\cdot dx
\tag{4}
\]

\medskip



\noindent
Next, put
\[
V^+_\lambda=\{x\,\colon |V(x)|>\lambda\}
\]
Then (4) gives:
\[
\mathfrak{m}(V^+_\lambda\cap E)\leq
\frac{1}{\lambda^2}\cdot
\int_E  V^2\cdot dx\leq
\frac{1}{\lambda^2}\cdot\int_E\, U^2\cdot dx+
\frac{2}{\lambda^2}\cdot\int_{\partial  T}\, U\cdot dx\tag{5}
\]


\medskip

\noindent
Next, 
Since the
integral  $\int_{T_\nu}dx=(b_\nu-a_\nu)$ for each $\nu$
and (1) holds we have
\[
\frac{2}{\lambda^2}\cdot
\int_{\partial T} U^2\cdot dx\leq 2\cdot \sum (b_\nu-a_\nu)=
2\cdot \mathfrak{m}(J_\lambda)\tag{6}
\]
Using the set-theoretic inclusion $V^+_\lambda\subset 
(V^+_\lambda
\cap E_\lambda)\,\cup
J_\lambda$ it follows after adding $\mathfrak{m}(J\uuu\lambda)$
on both sides in (5):
\[
\mathfrak{m}(V^+_\lambda)\leq 3\cdot\mathfrak{m}(J_\lambda)+
\frac{1}{\lambda^2}\cdot\int_E \,U^2\cdot dx\tag{6}
\]
Finally, $U\leq U^*$ holds on $E$
and since $E$ is the complement of $J\uuu\lambda$
we have $E=\{x\,\colon U^*(x)\leq\lambda\}$.
Now we apply general integral formulas which after integration over 
$\lambda\geq 0$
gives

\[
\int\,|V(x)\cdot dx=3\cdot \int\,U^*(x)\cdot dx+
\int\uuu 0^\infty\, \frac{1}{\lambda^2}\bigl [\int\uuu {(U^*\leq\lambda}\,(U^*)^2\cdot dx\,\bigr ]
\cdot d\lambda
\]
By the integral formula from XX the last term is equal to
$\int\,U^*(x)\cdot dx$ and Theorem 7.1 follows.




\bigskip


\centerline{\bf{8. The Hardy space on ${\bf{R}}$}}


\medskip

\noindent
Consider an analytic function $F(z)$ in the upper half\vvv plane
whose boundary value function $F(x)$ on the real line is integrable.
This class of analytic functions in $\mathfrak{Im}\,z>0$
is denoted by $H^1({\bf{R}})$.
To each such $F$ we introduce the
non\vvv tangential maximal function
\[ 
F^*(x)=\max\uuu {z\in\mathcal F(x)}
\, |F(z)|\tag{*}
\]
where $\mathcal F(x)$ is the Fatou sector of points
$z=\xi+i\eta$ for which $|\xi\vvv x|\leq \eta$.
With these notations one has

\medskip

\noindent{\bf{8.1 Theorem.}}
\emph{There exists an absolute constant $C$ such that}
\[
\int\uuu{\vvv\infty}^\infty |F^*(x)|\cdot dx\leq
C\cdot \int\uuu{\vvv\infty}^\infty |F(x)|\cdot dx
\]
\medskip


\noindent
To prove this we shall first study harmonic functions
and reduce the proof of Theorem 8.1 to a certain $L^2$\vvv inequality.
To begin with, let  $u(x)$ is a real\vvv valued function on
the $x$\vvv axis such that the integral
\[ 
\int\uuu{\vvv\infty}^\infty\, \frac{|u(x)|}{1+x^2}\cdot dx<\infty
\]
The harmonic extension to the upper half\vvv plane becomes:

\[
U(x+iy)=
\frac{1}{\pi}\cdot \int\uuu{\vvv\infty}^\infty\, \frac{y}{(x\vvv t)^2+y^2}
\cdot u(t)\cdot dt
\]
The non\vvv tangential maximal function is defined by:
\[
 U^*(x)=\max\uuu {z\in\mathcal F(x)}
\, |U(z)|\tag{*}
\]
When $u(x)$ belongs to $L^2({\bf{R}})$
it turns out that one there is an  $L^2$\vvv inequality.

\bigskip

\noindent{\bf{8.2 Theorem.}}
\emph{There exists an absolute constant $C$ such that}

\[
\int\uuu{\vvv\infty}^\infty\,(U^*(x))^2\cdot dx\leq
\int\uuu{\vvv\infty}^\infty\,u^2(x)\cdot dx
\]
\emph{for every $L^2$\vvv function on the $x$\vvv axis.}
\medskip

\noindent
In 8.X below   we show how Theorem 8.2 gives Theorem 8.1.
The proof of Theorem 8.2 relies upon a point\vvv wise estimate
of $U$ via the Hardy\vvv Littlewood maximal function of
$u$.
Let us first consider a function $u(x)$ supported by
$x\geq 0$ such that the function
\[
t\mapsto \frac{1}{t}\, \int\uuu 0^t\, |u(x)|\cdot dx
\]
is bounded on $(0,+\infty)$.
Let $u^M(0)$ denote this supremum over $t$.
Then one has

\medskip

\noindent
{\bf{8.3 Proposition.}}
\emph{For each $z=x+iy$ in the upper half\vvv plane one has}

\[
|U(x+iy)|\leq (1+\frac{|x|}{2y})\cdot u^M(0)
\]
\medskip

\noindent
\emph{Proof.}
Since the absolute values  $|U(x+iy)|$
increase when $u$ is replaced by $|u|$ we may assume that
$u\geq 0$ from the start. Put
\[ 
\Phi(t)=
\int\uuu 0^t\, u(x)\cdot dx
\]
which yields a primitive of $u$ and
a partial integration gives
\[
U(x+iy)= \lim\uuu {A\to \infty}
\frac{1}{\pi}
\cdot\bigr| \frac{y}{(x\vvv t)^2+y^2}
\cdot  \Phi(t)\bigl|  \uuu 0^A+
\lim\uuu {A\to \infty}
\frac{2}{\pi}\cdot\int\uuu 0^A\, \frac{y(t\vvv x)}{((x\vvv t)^2+y^2)^2}
\cdot \Phi(t)\cdot dt
\]
With $(x,y)$ kept fixed the finiteness of $u^M(0)$ entails that
$t^{\vvv 2}\cdot \Phi (t)$ tends  to zero 
with $A$ and there remains

\[
U(x+iy)=
\frac{2}{\pi}\cdot \int\uuu 0^\infty\, \frac{y(t\vvv x)}{((x\vvv t)^2+y^2)^2}
\cdot \Phi(t)\cdot dt
\]
Now $\Phi(t)\leq u^M(0)\cdot t$
gives the inequality

\[
U(x+iy)=\frac{2 u^M(0)}{\pi}\cdot \int\uuu 0^\infty\, 
\frac{y(t\vvv x)\cdot t}{((x\vvv t)^2+y^2)^2}\cdot dt
\]
To estimate the integrand we notice that it is equal to
\[
\frac{y}{((x\vvv t)^2+y^2)}+
\frac{y(t\vvv x)x}{((x\vvv t)^2+y^2)^2}
\]
The Cauchy\vvv Schwarz inequality gives
\[
|\frac{2y(t\vvv x)x}{((x\vvv t)^2+y^2)^2}|\leq
\frac{|x|}{(x\vvv t)^2+y^2}
\]
It follows that

\[ 
|U(x+iy)|\leq \frac{2u^M(0)}{\pi}\cdot 
\int\uuu 0^\infty\, \frac{y}{(x\vvv t)^2+y^2)}+\frac{u^M(0)\cdot |x|}{\pi}
\cdot 
\int\uuu 0^\infty\, \frac{1}{(x\vvv t)^2+y^2}\cdot dt
\]
The last sum of integrals is obviously
majorised by
$u^M(0)(1+\frac{|x|}{2y})$ and Proposition XX is proved.
\medskip


\noindent
{\bf{8.4 General cae.}}
If no constraint is imposed on the support of $u$
it is written as $ u\uuu 1+u\uuu 2$ where $u\uuu 1$ is supported by
$x\leq 0$ and $u\uuu 2$ b $x\geq 0$.
Here we consider the  maximal function
\[
u^M(0)=
\max\uuu t\, \frac{1}{2t}\int\uuu{\vvv t}^t\, |u(x)|\cdot dx
\]
Exactly as above the reader may verify that 
\[ 
|U(x,y)|\leq u^M(0)(2+\frac{|x|}{y})\tag{i}
\]


\noindent
In the Fatou sector at $x=0$ we have $x\leq |y|$
and hence (i) gives
\[
U^*(0)\leq \leq 3\cdot u^M(0)
\]
After a translation with respect to $x$ a similar inequality holds.
More precisely, put
\[ 
u^M(x)= \max\uuu t\, \frac{1}{2t}\int\uuu{\vvv t}^t\, |u(x+s)|\cdot ds
\]
for every $x$, Then we have
\[
U^*(x)\leq 3\dot u^M(x)
\]
\medskip

\noindent
Now we apply the Hardy\vvv Littlewood inequality from XX
for the $L^2$\vvv case and obtain the conclusive result:

\medskip

\noindent
{\bf{8.5 Theorem.}} \emph{There exists an absolute constant $C$ such that}

\[ 
\int\uuu{\vvv\infty>}^\infty\, U^*(x)^2\cdot dx\leq
C\cdot \int\uuu{\vvv\infty>}^\infty\, u^2(x)\cdot dx
\]
\emph{for every $L^2$\vvv function $u$ on the real line.}
\bigskip

\noindent
{\bf{8.6 Proof of  Theorem 8.1}}
We use a factorisation via Blaschke products which enable us to
write

\[
 F(z)= B(z)\cdot g^2(z)
 \]
 where $g(z)$ is a zero\vvv free analytic function in
 the upper half\vvv plane.
 Since $|B(z)|\leq 1$ holds in $\mathfrak{Im}(z)>0$
 we have trivially
 \[
 F^*(x)\leq g^*(x)^2
 \]
On the real axis we have $|F(x)|= |g(x)|^2$ almost everywhere so the 
$L^1$\vvv norm of $F$ is equal to the $L^2$\vvv norm of $g$.
Next, with $g=U+iV$
we have a pair of harmonic functions and since
$|g|^2= U^2+V^2$ we can apply Theorem 8.5 to each of 
these harmonic functions
and at this stage we leave it to the reader to confirm
the assertion in Theorem 8.1
\bigskip

\centerline{\bf{8.7 Carleson measures }}
\bigskip

\noindent
Let $F(z)$ be in the Hardy space $H^1({\bf{R}})$.
If $\lambda>0$ we put
\[
J\uuu\lambda= \{F^*(x)>\lambda\}
\]
We assume that the set is non\vvv empty and hence this open set
is a union of disjoint intervals $\{(a\uuu k,b\uuu k)\}$.
To each interval we construct the triangle $T\uuu k$
with corners at the points
$a\uuu k,b\uuu k$ and $p\uuu k=
\frac{1}{2}(a\uuu k+b\uuu k)+ \frac{i}{2}(b\uuu k\vvv a\uuu k)$.
Put
\[ 
\Omega=\cup\, T\uuu k
\]


\noindent{\bf{Exercise.}}
Use the construction of Fatou sectors 
and the definition of $F^*$ to show that
\[ 
\{|F(z)|>\lambda\} \subset \Omega\tag{1}
\]

\noindent
Let us now consider a non\vvv negative 
Riesz measure $\mu$ in the upper half\vvv plane.
For the moment we assume that $\mu$ has compact support
and that  $F(z)$ extends to a continuos function on
the closed upper half\vvv plane
This is to ensure that various integrals exists but 
does not affect the final a priori
inequality in Theorem X below.
General formulas for distribution functions give:
\[
\int\,|F(z)|\cdot d\mu(z)=
\int\uuu 0^\infty\, \lambda\cdot \mu( \{|F(z)|>\lambda\})\cdot d\lambda\tag{2}
\]


\noindent
To profit upon (1) we impose a certain norm  on $\mu$.
To each $x$ and every $h$ we construct the triangle $T\uuu x(a)$
standing on the interval $(x\vvv a/2,x+a/2]$.

\medskip

\noindent
{\bf{8.8 Definition.}}
\emph{The Carleson norm of $\mu$ is defined as
smallest constant $C$ such that}
\[
\mu(T\uuu x(a)\leq C\cdot a
\]
\emph{hold for all pairs $x\in{\bf{R}}$ and $a>0$ and is
denoted by $\mathfrak{car}(\mu)$}.
\medskip

\noindent{\bf{8.9 Application.}}
Given $\mu$ with its Carleson norm
the inclusion (1)  gives

\[
\mu( \{|F(z)|>\lambda\})\leq \sum\, \mu(T\uuu k)\leq
\mathfrak{car}(\mu)\cdot \sum\, (b\uuu k\vvv a\uuu k)\tag{i}
\]

\noindent
The last sum is the Lebesgue measure of $\{F^*>\lambda\}$
and hence the right hand side in (i) is estimated above by
\[
\mathfrak{car}(\mu)\cdot \int\uuu 0^\infty\, \lambda\cdot 
\mathfrak{m}(\mu( \{F^*>\lambda\})
\cdot
d\lambda= 
\mathfrak{car}(\mu)\cdot 
\int\uuu{\vvv \infty}^\infty\, F^*(x)\cdot dx\tag{ii}
\]
Together with Theorem 8.1 we arrive at the conclusive result:

\bigskip

\noindent
{\bf{8.10 Theorem.}}
\emph{There exists an absolute constant $C$ such that}
\[ 
\int\, |F(z)|\cdot d\mu(z)\leq C\cdot
\mathfrak{car}(\mu)\cdot 
\int\uuu{\vvv \infty}^\infty\, |F(x)|\cdot dx
\]
\emph{hold for each $F\in H^1({\bf{R}})$ and every 
non\vvv negative Riesz measure $\mu$ in the upper half\vvv plane.}










\bigskip

\centerline{\bf{9. BMO and radial norms of measures}}

\bigskip


\noindent
Theorem 0.4 together with the preceeding description of the dual space of
$\mathfrak{Re}\, H^1\uuu 0(T)$
implies that every BMO\vvv function $F$ can be written as a sum
\[
F=\phi+v^*\tag{i}
\]
where $\phi$ is bounded and $v^*$ is the harmonic conjugate of 
a bounded function.
However, this decomposition is not unique.
A \emph{constructive} procedure to find a pair $u,v$ in
for a given BMO\vvv function $F$
was given by P. Jones in [Jones].
See also the article [Carleson] from 1976.



 

\bigskip

\noindent
{\bf{9.1 Radial  norms on measures.}}
Let $D$ be the unit disc. An $L^1$-function $u(z)$ in
$D$ is radially bounded if there exists a constant $C$ such that
\[
\frac{1}{\pi}\cdot \iint_{S_h}\, |u(z)|\cdot dxdy\leq C\cdot h\tag{*}
\] 
for each sector
\[
S_h=\{z\colon \theta-h/2<\arg z\theta+h/2\}\quad\colon\quad h>0
\]

\medskip

\noindent
The smallest   $C$ for which (*) holds is denoted by $|u|^*$.
Notice that $|u|^*$ in general is strictly larger than
the $L^1$-norm over $D$ which
occurs when we take $h=\pi$ above.
If $u$ satisfies (*) we define a function $P_u$ on the unit circle by

\[
P_u(\theta)=
\frac{1}{\pi}\cdot \iint_D\, \frac{1-|z|^2}{|e^{i\theta}-z|^2}\cdot u(z)\cdot dxdxy
\]

\noindent
With these notations Fefferman proved:
\medskip


\noindent
{\bf{9.2 Theorem}} \emph{There exists an absolute constant $C$ such that}
\[
|P_u|_{\text{BMO}}\leq C\dot |u|^*
\]

\noindent
Thus, $u\mapsto P_u$ sends radially bounded
$L^1(D)$-functions to
$\text{BMO}(T)$.
The proof of Theorem 8.1  relies upon Theorem 0.4 and 
the following observation:

\medskip

\noindent
{\bf{9.3 Exercise.}}
Show that when $u$ is radially bounded and $H(z)$ is a harmonic function in
$D$ with continuous boundary values on $T$ then
\[
 \iint_D\, H(z)\cdot u(z)\cdot dxdy=
\int_0^{2\pi}\, H(e^{i\theta})\cdot P_u(\theta)\cdot d\theta
\]

\bigskip

\noindent
The following  result is also due to
Fefferman:

\medskip

\noindent
{\bf{9.4 Theorem.}}
\emph{Let $F(\theta)\in \text{BMO}(T)$. Then there exists a radially bounded
$L^1(D)$-function $u$ and some
$s(\theta)\in H^\infty(T)$ such that}
\[
 F(\theta)= s(\theta)+ P_u(\theta)
\]
For detailed proofs of the results above we refer to Chapter XX in [Koosis].









 
  









































\newpage











\centerline{Analytic extensions across a boundary.}}



\bigskip

\noindent
\emph{Proof.}
First we show that
the divergence in (*) entails that
$A_\omega(\square)$ is dense in $A^*_\omega(\square)$.
To prove this
we consider   a Riesz measure
$\mu$ supported by
$\overline{\square}$ where
$\omega(y)\cdot \mu$
is $\perp$ to
$A_\omega(\square)$. It remains to show that
\[
\int\,f\,d\mu=0\quad\colon f\in A_\omega^*(\square)\tag{1}
\]
To get  this we proceed as follows.
For each complex number $\zeta$ 
$e^{i\zeta z}\in A^*_\omega(\square)$. It follows that
\[
0=
\int_{y\geq 0}\, e^{i\zeta z}\cdot \omega(y)\,d\mu(z)+
\int_{y<0}\, e^{i\zeta z}\cdot \omega(y)\,d\mu(z)=F_+(\zeta)+F_-(\zeta)
\]
Here $F_+$ and $F_-$ are entire functions of exponential type.
If $\zeta=\xi$ is real and non-negative we have
\[ 
|F_+(\xi)|\leq 
\int_{y\geq 0}\, e^{-\xi y}\cdot \omega(y)\,|d\mu(z)|\leq
\max_{0\leq y\leq b}\,\omega(y)\cdot ||\mu||\tag{i}
\]
Hence $F_+(\xi)$ is bounded when
$\xi\geq 0$, and in the same way 
$F_-(\xi)$ is bounded when
$\xi\geq 0$.
Since $F_+(\xi)+F_-(\xi)=0$ for all real $\xi$
we conclude that
$F_+(\xi)$ is bounded on the whols real $\xi$-line.
Consider the function
\[
 h(y)=-\log \omega(y)\quad\colon y>0
\]
and introduce the lower Legendre envelope defined for $\xi>0$ by 
\[
k(\xi)=\min_{0<y\leq b}\, h(y)+\xi y
\]
Then we have
\[
e^{-\xi y}\cdot \omega(y)=
e^{-\xi y+\log \omega(y)}\leq e^{-k(\xi)}\quad\colon 0<y\leq 1\tag{ii}
\]
Hence (i) gives
\[
|F_+(\xi)\leq e^{-k(\xi)}\cdot ||\mu||\quad\colon \xi >0\tag{iii}
\]
At this stage we use a wellknown  general result about Legendre envelopes 
which  entails that
\[
\int_1^\infty\frac{k(\xi)}{\xi^2}\ d\xi=+\infty\tag{iv}
\]
Hence (iii) gives
\[
\log^+\frac{1}{|F_+(\xi)|}\geq
k(\xi)-\log \,||\mu||
\]
hence (ii) entials that
\[
\int_1^\infty\,\log^+\frac{1}{|F_+(\xi)|} \cdot \frac{d\xi}{\xi^2}=
+\infty\tag{iv}
\]
At the same time $F_+$ is an entire function of exponential type which is bounded
on the real axis and therefore  belongs to the Carleman class
$\mathcal N$ defined in § xx and Thoerem § xx implies that
 $F_+$ is identically zero.
This means that
the restriction of
$\omega(y)\cdot \mu$ to the closed rectangle $\overline{\square}_+$
is $\perp$ to functions of the form
$z\mapsto e^{i\zeta z}\colon\,\zeta\in {\bf{C}}$.
In the same way one verifies the restriction to
the lower rectangle has this property.
There remains to show  that this gives 
the vanishing in (1).
To achieve this
we consider first the upper triangle  and
when  $0<\epsilon <1 $ we define
\[
T_\epsilon(z)= -i/2+(1-\epsilon)(z-i/2)
\]
If $f\in A^*_\omega(\square)$, a picture shows that
$f(T_\epsilon(z)$ is analytic
in the closure of $\square_+$. By  Runge's theorem it
can be uniformly approximated by 
exponential polynomials
$\{e^{iz\zeta}\}$ on $\overline{\square^*}$
and the vanishing of $F_+$ entails that
\[
\int_{\square^*}\, 
f(T_\epsilon(z))\cdot \omega(y)\, d\mu(z)=0\tag{v}
\]
Next, we notice that 
there exists a constant
$C$ which is independent of $\epsilon$ such
that
\[
\max_{x+iy\in \square^*}\,\omega(y)\cdot |f(T_\epsilon(x+iy))|\leq C\cdot ||f||_\omega\tag{v}
\]
Finally,
\[
\lim_{\epsilon\to 0}\, 
 f(T_\epsilon(z))=f(z)
 \]
holds pointwise in the open square
$\square^*$, and by (v) we can apply dominated
convergence while we take  $\mu$-integrals. Hence
the vanishing integrals in (v) imply that
  \[
 \int_{\square^*}\, 
f(z))\cdot \omega(y)\, d\mu(z)\tag{vi}
\]
In the same way one proves that
the integral over
$\square_*$ is zero which proves (1).
\bigskip


\noindent
{\bf{The case when (*) is $>-\infty$.}}
There remains to show that when this holds, then
there exist
some
$f\in A_\omega^*(\square)$ which cannot be uniformly approximated by
functions from $A_\omega(\square)$.
CONTINUE proof ....



































\end{document}



