\documentclass{amsart}
\usepackage[applemac]{inputenc}


\addtolength{\hoffset}{-12mm}
\addtolength{\textwidth}{22mm}
\addtolength{\voffset}{-10mm}
\addtolength{\textheight}{20mm}
\def\uuu{_}

\def\vvv{-}

 
\begin{document}



\centerline{\bf\large{Compact Riemann surfaces}}

\bigskip



\centerline{\emph{Contents}}

\medskip

\noindent
\emph{Introduction}

\medskip

\noindent
\emph{0:1 Outline of the contents}

\medskip

\noindent
\emph{0:2 Elliptic functions}

\medskip

\noindent
\emph{A. The cohomology group $H^1(X,\mathcal O)$}

\medskip

\noindent
\emph{B. Divisors and the Riemann-Roch formula}





\medskip

\noindent
\emph{C. The duality theorem}

\medskip

\noindent
\emph{D. Harmonic forms}

\medskip

\noindent
\emph{E. Abels's theorem}
\medskip

\noindent
\emph{F. Weierstrass' points}
\medskip

\noindent
\emph{G. The Hurwitz-Riemann formula}.

\medskip

\noindent
\emph{H. Jacobi integrals and the Picard group.}
\medskip

\noindent
\emph{I. Riemann surfaces of algebraic function fields.}









\newpage

\centerline{\bf{Introduction.}}

\bigskip

\noindent
Before we present
a more detailed account of the contents in this chapter
we summarize some of the main
results  and 
describe some  tools which will be used in the proofs.
Geometry, algebra and analysis appear in a fruitful blend. 
during the   study of Riemann surfaces
which   therefore is an  instructive  subject 
since it teaches the  power  when 
methods and results from  different subjects  are combined.
The reader may turn directly to
the section entitled \emph{Algebraic function fields}
and after to the section devoted to Compact Riemann surfaces,
while the  material in this introduction
can be consulted later. But the
more experienced reader may prefer to study this 
expositary material directly.
An appendix covers general background including
shef theory and the construction of
cohomology of sheaves.
\medskip


\noindent
\emph{Algebraic function fields.}
In §  XX we 
start from
an irreducible polynomial $P(x,y)$ of two  variables
and construct its associated compact Riemann surface
$X$ which entails that
the field $\mathfrak{M}(X)$ 
of meromorphic functions on
$X$ is isomorphic to
the algebraic function field given by  the quotient field of
the integral domain
$\frac{{\bf{C}}[x,y]}{(P)}$
where $(P)$ denotes the principal ideal generated
by $P$ in the unique factorisation domain
${\bf{C}}[x,y]$.
Conversely, a result due to
 Weyl shows that every "abstract" compact
and 1-dimensional complex manifold  is
biholomorphic with
an algebraically defined Riemann surface as above.
Hence
there is a 
1-1 correspondence
between isomorphism classes of algebraic function fields in one
variable and compact Riemann surfaces, identified up to biholomorphic mappings.
A result from combinatorical topology 
will be taken for granted, namely that
every oriented
and compact 2-dimensional manifold $M$
is homeomorphic to
a sphere with
a finite number of handles attached. This  number is called the genus
of $X$ and  denoted by $g(X)$.
The case $g(X)=0$ means that 
$X$ is homeomorphic to
the unit sphere which is chosen as the Riemann sphere, or equivalently identified
with the projective line ${\bf{P}}^1$.
The
integer $g(X)$  determines $X$ as a topological space.
However, a pair of Riemann surfaces $X$ and $Y$ with equal genus are in general not
isomorphic in the sense above.  An exception is the case $g=0$, i.e. 
every compact Riemann surface $X$ for which $g(X)=0$ is isomorphic to
${\bf{P}}^1$ in the strong sense  which
means that
$\mathfrak{M}(X)$ is isomorphic to the field of rational functions on
one variable over
${\bf{C}}$.
When $g\geq 1$ the family of all compact Riemann surfaces
$X$ for which
$g(X)=g$
turns out to be quite an extensive family.
Riemann proved that
the  space $\mathcal M_g$
of all compact
Riemann surfaces with  presribed genus $g\geq 2 $
is parametrized by $3g-3$ many independent complex variables.
We shall not discuss the classification problem in detail since this 
would require a far more extensive account.
\medskip

\centerline {\emph{A first example}}.
\medskip

\noindent
Let $a$ be a complex number which differs from zero and 1
and consider the algebraic equation
\[
y^2=x(x-1)(x-a)\tag{i}
\]
Here $P=y^2-x(x-1)(x-a)$ is an irreducible polynomial in
${\bf{C}}[x,y]$
which gives the integral domain
$A=\frac{{\bf{C}}[x,y]}{(P)}$
where $(P)$ is the principal ideal generated by $P$.
The quotient field $K$ of $A$ is an example of an algebraic
function field. It contains the rational field 
${\bf{C}}(x)$ and $K$ is 
an algebraic exension of degree two where
(i) gives the equation  when
$y$ is adjoined to thid field.
A geometric object attched to the algebraic equation (i) arises when
we consider the curve $S$ in
the 2-dimensional complex $(x,y)$-space
defined by the zeros of $P(x,y)$.
Notice that  
the gradient vector
$\nabla(P)=(P'_x,P'_y)$ is non-zero at all points in $S$
which means that $S$ is non-singular, i.e. it appears as a 1-dimensional compl,ex submanifold of
${\bf{C}}^2$.
Next, ${\bf{C}}^2$
appears as an open subset of the projective space
${\bf{P}}^2$
whose homogeneuos coordinates are $(z,x,y)$
and points $(x,y)\in  {\bf{C}}^2$ are represented by
$(1,x,y)$.
When $(x,y)|\in S$ with $|x|$ large we see that
$|y|^2\simeq |x|^3$
which entails that the closure of $S$ in the compact metric space
${\bf{P}}^2$ contains one  extra point
$p^*=(0,0,1)$.
At this point one has local coordinates $(\xi,\eta)$
and points in ${\bf{C}}^2$  close to $p^*$ are
of the form
\[
(1,x,y)=
(y^{-1}, xy^{-1},1)=(\xi,\eta,1)
\]
\medskip

\noindent
The result is that
$S\cup \{p^*\}$
is a non-singular projective curve which
inherits a complex analytic structure from
${\bf{P}}^2$ and hence becomes a compact complex manifold of dimension one.
It is called the associated Riemann surface of the equation (1)
and let us denote it by $X$. Now there exists the field
$\mathfrak{M}(X)$ whose elements are meromorphic functions on
$X$.
One verifies that
it is isomorphic to the previous algebraic function field.
Here $x$ and $y$ are both identified with meromorphic functions on $X$.
We shall learn how local charts on the manifold $X$ are
adapted to the given equation and conclude that
the meromorphic function $y$ has a triple pole at $p^*$
and simple zeros at the points in
$(0,0),(1,0),(b,0)$ in $S$.
Similarly we shall learn that $x$ has a double pole at $p^*$
and a double zero at $(0,0)$ and  otherwise holomorphic and zero-free.
This gives
a globally defined holomiorphic 1-form
on $X$ given by
\[
\omega= \frac{dx}{y}
\]
One refer to $\omega$ as an abelian differential.
Its existence implies that
$X$ as a topological space is quite special, i.e. it is homeomorphic to
a torus $T^2$ which arises as the quotient space
\[
\frac{{\bf{C}}}{\Gamma}
\]
where $\Gamma$ is a lattice generated by a pair of
${\bf{R}}$-linearly independent vectors in the complex plane.
\medskip

\noindent
\emph{The moduli problem.}
The compact Riemann surface  was constructed via (1) 
and is therefore determined by $a$. So let us denote it by $X_a$.
If $b$ is another complex number
which is $\neq \{0,1\}$
we get the compact Riemann surface $X_b$
starting with
(1) where $b$ has replaced $a$.
As topological spaces $X_a$ and $X_b$ are homeomorphic but
this need not imply that they are biholomorphic as compact complex manifolds.
So one is led to analyze for which pairs $a,b$ one has
$X_a\simeq X_b$ where $\simeq$ indicates that the complex manifolds
are biholomorphic.
Here one encounters a crucial problem in
the study of Riemann surfaces.
More generally
one can consider equations of the form
\[
y^2=(x-a_1)\cdots (x-a_k)
\]
where $k\geq 4$ and $\{a_\nu\}$
are different complex numbers.
We get a non-singular projective curve
$X$ by the same procedure as above.
Here $y$ has simple zeros at the $a$-points and a pole of order
$k$
at $p^*$.
Here  the topological space $X$ need not be  a torus. But it is
homeomorphic to a compact manifold with
$g$ handles attached for some
integer  $g\geq 2$ 
which are  determined via $k$ as explained in § xx below.
Here $X=X(a_1,\ldots,a_k)$ depends on the $k$-tuple and
when
we consider the family of $k$-tuples of distinct numbers in
${\bf{C}}^k$ and 
one encounters a moduli problem
which was investigated
by Weierstrass after Riemann had
introduced the general notion of Reimann surfaces.
In these notes we shall  not try to expose this in detail since
this would require another  extensive chapter.
Let us only remark that
general moduli problems for compact Rieann surfaces
is a very rich subject which is an active field of reserach since
many delicate problems remain.
But the special case $k=3$ will
be treated in detail in these notes
and may be considered as
the first basic lesson about Riemann surfaces.
\bigskip





\centerline {\emph{An open problem.}}
\medskip


\noindent
The subsequent material deals foremost with results which
are classic and  established  more than a century ago.
But many problems
which  at a first sight appear to be quite modest remain open.
Let us give an example where one seeks solutions to
a certain variational problem.
Let $a,b,c,d$ be four distinct complex numbers
and consider the algebraic equation
\[
y^4=
\frac{1}{(x-a)(x-b)(x-c)(x-d)}\tag{1}
\]
Passing to the fourth root
we set
\[
 y^*(x)=\frac{1}{x}\cdot
[(1-a/x)(1-b/x)(1-c/x)(1-d/x)]^{-\frac{1}{4}}\tag{2}
\]
This  yields a single valued analytic function defined
in
the exterior disc
$\{|x|>R$ where $R$ is chosen so that
the four numbers
$a,b,c,d$ have absolute value $\leq R$.
When $|x|\to +\infty$ the function $y^*(x)$
is $\simeq x^{-1}$.
Denote by $\mathcal J$
the family of closed Jordan curves
which border Jordan domains containing $a,b,c,d$.
Residue calculus gives for each such Jordan curve
a unique Riesz measure
$\gamma$ supported by
$\Gamma$ such that
\[ 
y^*(z)=\int_\Gamma\, \frac{d\gamma(\zeta)}{z-\zeta}
\]
From (2) it follows that the mean-value
\[
\int_\Gamma\, d\gamma(\zeta)=1
\]
Hence the total variation of the Riesz measure
$\gamma$ is $\geq 1$ and we set
\[ 
\mathcal E(\Gamma)=
\int_\Gamma\, |d\gamma(\zeta)|\tag{3}
\]
\medskip

\noindent
{\bf{Question.}} Is it true that
\[
\min_{\Gamma\in\mathcal J}\, \mathcal E(\Gamma)=1\tag{1}
\]
Moreover, if (1) holds we ask if 
there exists a unique
compact set $\Gamma_*$ with the following properties:
It consists
of a finite union union of
simple and real-analytic Jordan arcs $\{\rho_\nu\}$
which in general need not be disjoint,
but each pair intersect at most in one point given
as a common boundary point of the two  arcs. Moreover,
there exists a probability measure
$\mu_*$ supported by
$\Gamma_*$ such that
$y^*(z)$ equals the Cauchy
transform
\[
\int_{\Gamma_*}\,\frac{ d\mu_*(\zeta)}{z-\zeta}\quad\colon
z\in {\bf{P}}^1\setminus \Gamma_*
\]
\medskip

\noindent
{\bf{Remark.}}
If $\Gamma_*$ exists the construction of
$\mu_*$ means that the compact Rieman surface
associated to the given algebraic equation (1)
can be equipped with  a special triangulation.
See § xx for further comments.
The question above 
is closely related to problems about asymptotic distributions of
zeros to eigenpolynomials of ordinary differential equations.
The case above where $a<b<c<d$ are real was treated in [B-S].
Here
the question was settled and it was proved that
$\Gamma_*$ is the disjoint union of the intervals $[a,b]$ and $[c,d]$. Moreover
the
measure $\mu_*$ was determined in this case. But when
$a,b,c,d$ do not belong to a common line
the existence and uniqueness of  $\Gamma_*$ remains open.
Similar  questions as above can of course be posed for
a more extensive class of Riemann surfaces attched to algebraic equations.
\medskip


\noindent
\emph{Another variational problem.}
It is tempting to   try to extend
results in   analytic function theory
on  the complex plane 
to Riemann surfaces.
Here is an example: Let $X$ be a compact Riemann surface
and $\sigma$ a metric whose curvatute is everywhere strictly negative
and  $\Phi$ is  a positive continuous function on
$X$
such that $\log\,\frac{1}{\Phi}$ is subharmonic.
Let $D$ be the unit disc and $f\colon  D\to X$
a bijective analytic function whose image
$f(D)$ is a Jordan domain in
$X$.
If $z\in D$ and $dz$ is small we
get the points $f(z)$ and $f(z+dz)$ in $X$ and can measure their
$\sigma$-distance. Put
\[
\rho_f(z)= \lim_{dz\to 0}\,
\frac{\sigma(f(z+dz),f(z))}{|dz|}
\]
When
one  deals with planar domains so that $w=f(z)$
and employ the euclidian metric on
the complex $w$-plane then
$\rho_f(z)$ is the absolute value of the complex derivative
$f'(z)$.
Inspired by Beurling's mapping theorem from § XX
one is led to study pairs $(\Phi,\sigma)$ and  seek 
bianalytic mappings
$f$ as above such that
\[
\lim_{r\to 1}\,\max_{0\leq \theta\leq 2\pi}\,
|\Phi(f(re^{i\theta})-\rho_f(re^{i\theta})|=0
\]
Recall  from § xx that the eventual existence of $f$
for a given pair $\Phi,\sigma$
relies upon a sophisticated
problem in the calculus of variation.
Here we shall not try to
discuss this problem in detail but mention
that special cases
are related to free boundary value problems in connection with
the Helmholtz equation. See § xx.







 

















\newpage



\centerline{\emph{0.1 Non-compact Riemann surfaces.}}

\medskip


\noindent
Let $X$ be a connected and 1-dimensional complex manifold
which means that
$X$ is covered by some family of charts
$\{U_\alpha,z_\alpha\}$ where every
$U_\alpha$ is a copy of the open unit disc in
the complex $z_\alpha$-plane and the glueing functions
in non-empty intersections 
$U_\alpha\cap U_\beta$ are  biholomorphic mappings.
In addition we assume that $X$ is not compact
and refer to $X$ as an open Riemann asurface.
A  theorem  due to Rado  
asserts
that every open Riemann surface
$X$ has  countable topology. This   means that
$X$ can be covered by  denumerable family of charts
which can be chosen to be locally finite. In particular 
the topology on
$X$ can be defined by
a metric
and   is also paracompact.
Moreover, 
by solving
the Dirichlet problem in subdomains one proves
that $X$ can be exhausted
by an increasing sequence of relatively compact Runge domains, i.e.
relatively compact open subsets $Y$ such that 
every connected component in the closed complement $X\setminus Y$
is non-compact.
Next, 
denote by
$\mathcal O$ the sheaf of holomorphic functions on
$X$. 
A result due to Behnke and Sstein
 asserts that 
the cohomology group
$H^1(X,\mathcal O)$ is zero. It is proved in the special section devoted to 
open Riemann surfaces.
Next, let $\mathcal O^*$ be the multiplicative sheaf
whose sections
are
zero-free holomorphic functions. 
In § XX we  also prove that
$H^1(X,\mathcal O^*)=0$ which means
that every holomorphic line bundle is 
holomorphically trivial.
An example of  a line bundle is the sheaf
$\Omega$ of holomorphic 1-forms. Its triviality entails  that
there exists a global section $\omega$ which is everywhere $\neq 0$.
This gives a "planar property" of a non-compact Riemann surface since
the holomorphic 1-form
$\omega$  serves like $dz$ for open domains in ${\bf{C}}$.
\medskip

\noindent
The vanishing results above have several consequences.
To begin with
there exists  an ample family of
globally defined meromorphic functions.
More preciely, let $\{p_k\}$ and $\{q_j\}$
be a pair of discrete subsets in $X$, i.e. every relatively compact 
set in $X$ contains at most a finite set of $p$-points or $q$-points.
Then, if $\{m_k\}$ and $\{n_j\}$ is an arbitrary pair of sequences
of positive integers there
exists
$f\in\mathfrak M(X)$
with poles of order
$m_k$ at $p_k$ for every $k$ while $f$ is holomorphic and
zero free
in $X\setminus\{p_k\}\cup\,\{q_j\}$
and
has a zero of order $n_j$ at every $q_j$. We prove this result in § XX.
Next, let $\Omega$ be the sheaf of holomorphic 1-forms.
In local charts every analytic function has a primitive which
gives an exact sequence of sheaves
\[
0\to {\bf{C}}_X\to \mathcal O\overset\partial\to \Omega\to 0
\]
where ${\bf{C}}_X$ is the sheaf whose sections are locally constant
complex-valued functions.
The vanishing of $H^1(X,\mathcal O)$ entails that one has an isomorphism
\[
H^1(X,{\bf{C}}_X)\simeq\frac{\Omega(X)}{\partial(\mathcal O(X))}\tag{*}
\]
A wellknown  fact in topology 
asserts that
$H^1(X,{\bf{C}}_X)$ is equal to the 
the complex vector space $G(X)$ 
of  group homomorphisms from
the fundamental
group $\pi_1(X)$ into the additive group 
of complex numbers. This leads
to
an
interpretation of (*).
Namely,  choose some
$x_*\in X$ and
identify
$\pi_1(X)$ with
homotopy classes of
differentiable and closed curves
$\gamma$ which have a common start- and endpoint at $x_*$.
Since a 1-form
$\omega\in \Omega(X)$ is closed 
elementary calculus implies that
the line integrals
\[ 
\gamma\mapsto  \int_\gamma\,\omega
\]
only depend upon the homotopy class of $\gamma$ and hence
 $\omega$ determines an element $G(\omega)\in G(X)$. If $G(\omega)=0$
we
get a single-valued holomorphic function $f$ on $X$ defined by
\[ 
f(x)= 
\int_{x_*}^x\omega
\] 
where the line integral is taken over some curve from $x_*$ to $x$
and  
$\omega=\partial(f)$.
On the other hand, (*) entails that if
a holomorphic 1-form $\omega$ is not $\partial$-exact then
the function $f$ above is multi-valued.
Its multi-valued behaviour reflects the image
$G(\omega)$.
\medskip

\noindent
{\bf{A result on 
compact Riemann surfaces.}}
Let $X$ be a compact Riemann surfacesd
and fix some point $p\in X$ and a local chart $\Delta$ centered
at $p$ where $z$ is a local coordinate.
Now $X\setminus\{p\}$ is an open Riemann surface
and hence $H^1(X\setminus\{p\},\mathcal O)=0$.
In the puntured disc
$\Delta\setminus \{z=0\}$
we consider an analytic function
\[
 \phi(z)= \sum_{\nu=1}^\infty\, c_kz^{-k}\tag{i}
\]
where $\{c_k\}$ are such that
$\sum\, |c_k|\cdot \delta^k<\infty$ for some
$\delta>0$.
Thus, we have taken a negative Laurent series.
The Behnke-Stein theoren entails that 
$H^1(X\setminus \{p\},\mathcal O)=0$.
From this a trvial sheaf-theoretic result entails that there exists
an injective map from
the space of all negative Laurent series (i) to the complex vector space
$H^1(X,\mathcal O)=0$.
As we shall see later on the last cohomology 
group is finite dimensional.
Moreover, a function $\phi$ is sent into zero in
$H^1(X,\mathcal O)=0$ if and only if there exists
$\Phi\in \mathcal O(X\setminus\{p\}$
such that the restriction of
$\Phi-\phi$ to the punctured disc extend to a holomorphic
function in
$\Delta$. In 
the special case when 
the negative Luarent series in (i) is finite it follows that
$\Phi$ is a globally defined meromorphic function on
$X$ with a single pole at $p$ whose
negative series expansion is given via (i).
In this way one gets a quite ample familly of meromorphic functions on
the compact Riemann surface.
Precise results will
be established later on where
ther material about Weiertrass points in § xx is an example.




\medskip

\noindent
{\bf{The vanishing of 
 $H^2(X,{\bf{Z}}_X)$}}.
 Let $X$ be an open Riemann surface.
 Since $H^1(X,\mathcal O^*)=0$  it follows 
that the
cohomology group $H^2(X,{\bf{Z}}_X)=0$.
To see this we regard
the exact sequence of sheaves
\[
0\to {\bf{Z}}_X\to \mathcal O\overset{exp}\to \mathcal O^*\to 0
\]
where the exponential map sends each
$f\in\mathcal O$ to $e^{2\pi if}$.
The long exact sequence for sheaf cohomology entails that
$H^2(X,{\bf{Z}}_X)=0$.
We remark that this vanishig
no longer holds when
$X$ is a compact Riemanbn surfce, i.e. the reader should
be aware of
the different topological properites in the compact versus the
non-compact case.









\bigskip


\centerline{\emph{0.2 The uniformisation  theorem and Fuchsian groups.}}
\medskip

\noindent
In § XX we prove
that if 
$X$ is a non-compact Riemann surface whose fundamental group $\pi_1(X)$ is 
zero then
$X$ is biholomorphic to the open unit disc $D$ or the complex plane
${\bf{C}}$.
If $X$ is a compact Riemann surface
it has a fundamental group $\pi_1(X)$
and there exists the universal covering space $\widehat X$
which yields another Riemann surface. One shows easily
that it  is non-compact unless
$X={\bf{P}}^1$. Ignoring this case
it follows that
$\widehat X$ is either $D$ or ${\bf{C}}$. We shall learn that
$\widehat X\simeq D$ when the genus of $X$ is $\geq 2$.
Here the  holomorphic map $\rho\colon\widehat X\to X$
is surjective and locally biholomorphic. Moreover,
every fiber
$\rho^{-1}(x)$ can be identified with $\pi_1(X)$ which
leads to 
constructions of  Fuchsian groups.
Namely, fix a point $x_*\in X$ and identify
$\pi_1(X)$ with homotopy classes of closed curves
at $x_*$. Now  $\widehat X=D$ and suppose that $x_*$ is chosen so that
$\rho(0)=x_*$, i.e, the origin in $D$ is mapped to $x_*$.
Let
$s\mapsto \gamma(s)$
be a closed parametrized curve
which starts and ends at $x_*$. It has a
unique lifting $\widehat \gamma$ to the open unit disc $D$ where
\[ 
\rho(\widehat{\gamma}(s)=\gamma(s)\quad\colon\, 0\leq s\leq 1
\]
and $\widehat{\gamma}(s)=0$.
The end-point $\widehat\gamma(1)$
depends only upon the homotopy class of $\gamma$ and
when $\gamma$ represent different elements
$\pi_1(X)$ these
end-points change.
In this way the set of end-points
$\{\widehat \gamma(1)\}$
identifies $\pi_1(X)$ with a discrete subset of $D$.
If $a= \widehat \gamma(1)$ for some
$\gamma$ one can associate the Möbius transform
\[
M_a(z)=\frac{z+a}{1+\bar a z}
\]
In this way $\pi_1(X)$ is identified with a group of Möbius transforms
and $\mathfrak{M}(X)$
with  automorphic functions, i.e.
meromorphic functions in $D$ which are invariant under the group
of Möbius transforms above.
In these notes
we shall not enter a detailed discussion sbout Fuchsian groups and
automorphic functions
which is an extensive subject.
It has the merit that
various compact Riemann surfaces 
arise via group theoretic constructions.













\newpage

\noindent
\centerline{\bf{0.3 Tools for the study of Riemann surfaces.}}
\medskip

\noindent
Sheaf theory is used without hesitation where relevant background is provided
in the appendix.
Now follows  some other basic constructions.

\medskip

\noindent
\emph{0.3.1 Puiseux expansions.}
The local ring
${\bf{C}}\{z\}$
of convergent power series is 
identified with the local ring of germs of analytic functions at
the origin.
Let $w$ be a new complex variable and consider a polynomial
\[ 
Q(z,w)= 
w^n+q_{n-1}(z)w^{n-1}+\ldots+ q_1(z)w+q_0(z)
\]
Here $n\geq 2$ and we assume that
this $w$-polynomial is irreducible in the unique factorisation
domain
${\bf{C}}\{z\}[w]$ and that
$q_\nu(0)=0$ for every $\nu$.
Under these conditions Puiseux proved that
with a new complex variable $\zeta$ there exists a unique 
holomorphic function $A(\zeta)$ defined in some
disc
$\{|\zeta|<r\}$ such that 
\[
Q(\zeta^n,A(\zeta))=
A(\zeta)^n+q_{n-1}(\zeta^n)A(\zeta)^{n-1}+\ldots+q_0(\zeta^n)=0
\]
This   is proved in § XX and will be  used to construct
the associated compact Riemann surface to an irreducible polynomial $P(x,y)$.
\medskip

\noindent
 \emph{0.3.2 Differential forms.}
Analysis on a general Riemann surface $X$ - compact or not -
is rather similar to the planar case.
The complex analytic structure implies that
$X$ is oriented and hence there exist
area integrals of test-forms of degree 2 and we often
employ its underlying structre as a $C^\infty$-manifold of dimension two.
Denote by $\mathcal E(X)$ the space of complex-valued $C^\infty$-functions on $X$
and $\mathcal E^1(X)$ is the space of
differential 1-forms wiith smooth coefficients. There exists the
exterior differential
map:
\[ 
d\colon \mathcal E(X)\to \mathcal E^1(X)
\] 
whose image consists   of exact 1-forms.
The complex analytic structure
on $X$ yields a direct sum decomposition
\[
\mathcal E^1(X)=\mathcal E^{1,0}(X)\oplus \mathcal E^{0,1}(X)
\]
To be precise, a differential 1-form
$\alpha$ is of bi-degree $(1,0)$ if it is expressed as $f\cdot dz$
in
every chart $(U,z)$ of $X$ where
$z$ is the local analytic coordinate
and $f\in C^\infty(U)$.
In a  chart
we also have the conjugate 1-forms
$d\bar z$ and
a 1-form $\beta$ is of bi-degree $(0,1)$ when
it is expressed as $g\cdot d\bar z$ in every chart
of $X$.
We have also the space
$\mathcal E^2(X)$ of differential 2-forms. In a chart
$(U,z)$ each 2-form is expressed as
$h\cdot d\bar z\wedge dz$
and we  prefer to write
$\mathcal E^2(X)= \mathcal E^{(1,1)}(X)$.
Here we have maps:
\[ 
\partial\colon \mathcal E^{0,1}(X)\to
\mathcal E^{(1,1)}(X)\quad\colon\quad
\bar \partial\colon \mathcal E^{1,0}(X)\to
\mathcal E^{(1,1)}(X)
\]

\medskip

\noindent
\emph{0.3.3 Stokes Theorem}.
Let $U$ be a bounded open subset
of a Riemann surface $x$ whose boundary $\partial U$
is some finite union of rectifiable  and closed curves.
Then
\[ 
\int_{\partial U}\, \alpha= \iint_U\, d\alpha
\] 
for
every $\alpha\in\mathcal E^1(X)$.
If $u$ is a real-valued $C^\infty$-function 
we  get the $(0,1)$-form $\partial u$ and
after we apply $\bar\partial$ which gives
\[ 
\int_{\partial U}\, \partial u= \iint_U\, \bar\partial\partial(u)
\] 
If $(U,z) $ is a chart in $X$ we recall from Chapter V that 
\[
\bar\partial\partial(u)(x+iy)=
\frac{i}{4}\cdot \Delta(u)\cdot dx\wedge dy
\]
If the Laplacian $\Delta(u)$ is a non-negative 
function in every chart one says that $u$ is a subharmonic function.
The condition is intrinsic because we know from Chapter 5
that subarmonicity is unchanged under local
conformal mappings.
This gives the class $\text{SH}(X)$
of real-valued $C^\infty$-functions $u$ on $X$  such that
\[
\iint_U\, \bar\partial\partial(u)
\]
is equal, to $i$ times a non-negative real number for every bounded
open set $U$.
If $\bar\partial\partial(u)$ 
vanishes  we say that $u$ is a harmonic function.
\medskip

\noindent \emph{0.3.4 The Dirichlet problem}.
Let $U$ be a bounded open set whose boundsry
$\partial U$ is as above
Perron's method to solve the Dirichlet problem in the planar
case extends verbatim  and shows that for
every real-valued and continuous function
$h\in C^0(\partial U)$ there exists a unique harmonic function $H$ in $U$
whose boundary values are equal to $h$.
\medskip

\noindent
\emph{0.3.5 A residue formula }
Let $U$ be a bounded domain as above and $\phi$ is
an analytic function in $U$ which extends to a continuous and zero-free
function
to the closure.
Then
$\frac{\partial\phi}{\phi}$ is a smooth 1-form on $\partial U$ and
there exists the line integral
\[
 \frac{1}{2\pi i}\cdot\int_{\partial U}\,
 \frac{\partial\phi}{\phi}\tag{*}
 \]
Let $\{q_k\}$ be the finite set of zeros of $\phi$ in $U$.
Around each $q_k$ we  choose a  chart
$D_k$ and the discs
$\{D_k\}$ are  pairwise disjoint.
Stokes Theorem applies to the open set $U_*=U\setminus\,\cup \bar D_k$.
Notice that
\[ 
d(\frac{\partial\phi}{\phi})=0
\] 
holds in  $U_*$. Hence (*) is equal to
\[
 \frac{1}{2\pi i}\cdot\ \sum\,\int_{\partial D_k}\,  \frac{\partial\phi}{\phi}
\]
The line integrals over the boundary
of the small discs 
are evaluated exactly as in the planar case and hence
(*) is equal to the number of zeros of $\phi$ 
in $u$ counted with multiplicities.
A special case occurs i
the absolute value $|\phi(x)|=1$ for every $x\in\partial U$.
Then, if  $a$ is a complex number with $|a|<1$ we consider
the analytic function $\phi(x)-a$ and by the above
\[
 \frac{1}{2\pi i}\cdot\int_{\partial U}\,
 \frac{\partial\phi}{\phi-a}\tag{*}
 \]
is an integer.
Since (*) depends continuously on $a$ this
integer is constant and hence the number of zeros of
$\phi-a$ is equal to that if $\phi$ in $U$.
When $\phi$ from the start has a simple zero
in $U$ it follows that
$x\mapsto \phi(x)$ yields a bijective map from $U$ onto the open unit
disc $D$ and it is therefore a conformal mapping.
In § xx  this is used
during the proof of the
uniformisation theorem.


\bigskip


\centerline {\emph{0.4 Currents.}}
\bigskip

\noindent
A distribution on $X$ is a continuous linear functional on
the topological space of test-forms of bi-degree 2.
An example is when
$f$ is an arbitrary 
$C^\infty$.function on $X$ which yields the distribution defined by
\[ 
\alpha\mapsto
\int_X\, f\cdot \alpha\quad\colon \alpha\in \mathcal E^{(1,1)}(X)
\]
In general, if $\{U_\nu\}$ is some locally finite covering of $X$ by charts
a distribution $\gamma$ on $X$ is
determined by its restriction to every chart. More precisely,
we first find a $C^\infty$-partition of the unity, i.e. a family
$\{\phi_\nu\in C0^\infty(U_\nu)\}$ such tht
$\sum\, \phi_nu(x)=1$ for all $x\in X$.
If $\nu$ is fixed and $\alpha_\nu$ is a smooth 2-form in
$U_\nu$ we set
\[
\gamma_\nu(\alpha_\nu)= \gamma(\phi_\nu\cdot \alpha_\nu)
\]
Working with local coordinates in 
$U_\nu$ it means that $\gamma_\nu$ yields an ordinary planar distribution
in $U_\nu$  expressed by  a finite sum of derivatives of Riesz measures as explained in 
§ XX. The distributions $\{\gamma_\nu\}$  recaputre $\gamma$ since
every test-form
$\alpha$ on $X$ is equal to $\sum\,\phi_\nu\cdot \alpha$.
An exampe of a non-smooth distribution on $X$ arises when
$U$ is an arbitrry open set and
the functional is given by
\[ 
\alpha\mapsto
\int_U\, \alpha
\]
Another case is when
$f$ is a globally defined meromorphic function on $X$.
If $f$ has a pole of some order $n\geq 1$ at a point $x_0$
we consider a chart
$(U,z9$ around $x_0$ where
$x_0$ is the origin and $f(z)= z^{-n}$.
In this chsrt the riniciapmvalue distribution $z^{-n}$ exists as exaplined in
§§ and by partitions of thr unity we get
a current on $X$ defined by
\[
\int_X\, f\cdot \alpha
\]
where the rule is that during the integration
one takes principal values   to avoid the discrete set of poles of $f$.
The space of distributions on $X$  is denoted by
$\mathfrak{Db}(X)$.
Next, we have the topological vector spaces
$\mathcal E^{0,1}(X)$ and
$\mathcal E^{1,0}(X)$. We set
\[ 
\mathfrak{c}^{1,0}(X)=\mathcal E^{0,1}(X)^*\quad\text{and}\quad
\mathfrak{c}^{0,1}(X)=\mathcal E^{1,0}(X)^*
\]
Here
$\mathfrak{c}^{1,0}(X)$ is the space of currents of bi-degree $(1,0)$.
An example occurs of $\alpha^{1,0}$ 
is a smooth form of bi-degree $(1,0)$
which yields the curent defined by
\[
 \beta^{0,1}\mapsto \int_X\alpha^{1,0}\wedge \beta^{0,1}
\]
Hence $\mathcal E^{1,0}$ is a subspace of
$\mathfrak{c}^{1,0}(X)$  and similarly
 $\mathcal E^{10,1}$ is  a subspace of
$\mathfrak{c}^{0,1}(X)$.  
If $\gamma\in\mathfrak{Db}(X)$
there exists the current $\partial\gamma$ defined by
\[
\partial(\gamma) (\beta^{0.1})=
-\gamma(\partial(\beta^{0,1})\tag{i}
\]
Indeed, this is so because
$\partial$ yields a continuous map from
the topological vector space
of test-forms of bi-degree $(0,1)$ to those of bi-degree $(1,1)$.
For example, let $\gamma$ be the distribution defined by
a $C\infty$-function $f$.
Stokes Theorem entails that
\[
0=\int_X\, d(f\cdot \beta^{0,1})=
\int_X\, \partial f\wedge \beta^{0,1})+
\int_X\, f\cdot \partial(\beta^{0,1})
\]
The sign rule in (i)  shows that
the current $\partial(f)$ is defined by the smooth $(1,0)$-form
$\partial f$.
In a similar way we get a differential map
\[
 \bar\partial \colon \mathfrak{Db}(X)\to
\mathfrak{c}^{0,1}(X)
\]


\noindent
Finally there exists the space
\[
\mathfrak{c}^{1,1}(X)=\mathcal E(X)^*
\]
Here $\mathcal E^{(1,1)}()$ appears as a subspace and
we leave it to the reader to
detect the mappings:
\[
 \bar\partial \colon \mathfrak{c}^{1,0}(X)\to
\mathfrak{c}^{1,1}(X)
\quad\text{and}\quad
 \partial \colon \mathfrak{c}^{0,1}(X)\to
\mathfrak{c}^{1,1}(X)
\]
\medskip


\noindent
Currents will
be used both to  study  compact as well as non-compact
Riemann surfaces.
A fundamental fact is   the elliptic propery of
the $\bar\partial$-map.
Fir example, if $\mu$ is a distribution such that
$\bar\partial(\mu)=0$ then
it is a holomorphic density function.
For compact Riemann surfaces
we shall use currents in § XX to prove 
the Hodge decomposition which asserts that if $X$ is a compact Riemann surface
then there exists a direct sum decomposition
\[ 
\mathcal E^1(X)= d(\mathcal E(X))+
\Omega(X)\oplus\bar\Omega(X)\tag{*}
\]
where
$\Omega(X)$ is the space of abelian differentials of the first kind, i.e.
globally defined holomorphic 1-forms, and
$\bar\Omega(X)$ is the conjugate space of differential
forms of bidegree $(0,1)$ which are $\partial$-closed.
\medskip

\noindent
{\bf{Remark.}}
The calculus based upon currents
is not only efficient but
enable us to give an operative meaning to 
geometric objects.
For example, an
oriented and $C^1$-parametrized curve $\gamma$
in a Riemann surface
$X$ yields a current of bi-degree $(1,0)$  
defined by
\[
\beta^{0,1}\mapsto \int_\gamma\,\beta^{0,1}
\]
and taking $(1,0)$-forms we get a current of bi-degree
$(0,1)$.
The proof of Abel's theorem in § E
is an  example where 
currents given by such integration chains
will be used.
\medskip

\noindent
\emph{0.4.1 Boundary value distributions.}
Let $X$ be a Riemann surface and
$\Omega$ some open and relatively compact subset.
Let $f(z)$ be a holomorphic function in
$\Omega$,  i.e. it belongs to $\mathcal O(\Omega)$.
If $p\in\partial\Omega$ we choose a local chart
$(U,z)$ around $p$
and impose the condition that
\[
\iint_{U\cap\Omega}\, |f(z)|\, dx dy<\infty
\] 
where $z=x+iy$. It is expressed by sying that
if $\chi_\Omega$ is the characteristic functuon of
$\Omega$ then
$f\cdot \chi_\Omega$ is a locally integrable function on.
Under this condition there exists
the current
\[
\rho=\bar\partial(f\cdot \chi_\Omega)
\]
The case when
$\partial\Omega$ is  recitifiable Jordan curve which may be simple or
closed is of special interest.
Let us give a simple example: First we have the
Riemann surface attched to the algebraic equation
$y^2=\frac{1}{x(x-1)}$.
Removing the unit interval $[0,1]$ from the complex
$x$-plane we can pick a single valued branch of the
root function and find the analytic function
\[
f(x)=
\frac{1}{\sqrt{x(x-1)}}
\]
where the branch is cohsen so that
$f(x)\simeq \frac{1}{x}$ when
$|x|>>0$.
To pbe precise, additing the point at inifintity one has the prpjective
line ${\bf{\P}}^1$ and $f$ extends to be analytic at
$x=\infty$ where $\zeta=x^{-1}$ is a new coordinate and
\[
 f(\zeta)= \frac{\zeta}{\sqrt{1-\zeta}}
 \]
Now we have the simply connectd set
$\Omega_*= {\bf{P}}^1\setminus [0,1]$
and $f\in\mathcal O(\Omega_*)$.
Here $\Omega_*$ corresponds to a  sheet 
$\Omega$ of the associated Riemann surface
$X$ to the given algebraic equation.
More precisely, one first identifies $x$ with a meromorphic function on
$X$ and as $p$
varies in $X$ we get points $x(p)\in {\bf{P}}^1$, i.e.
$x$ yields a holomorphic map from $X$ to the complex manifold
${\bf{P}}^1$.
Now the inverse image
$x^{-1}(\Omega_*)$ is a disjonit union of two sheets
on which single-valued branches of the root function
above are determined.
One of these sheets is denoted by $\Omega$ where
the specific function $f$ is given as above.
On $X$ the boundsry
$\partial\Omega$
has one realtively open part which is homeomorphic to
the open interval $(0,1)$.
In addition $\partial\Omega$ contains
the two points in $X$ above $\{x=0\}$ and $\{x=1\}$.
The local constructions of charts in 
the Riemann surface associated to an algebraic equation
will teach us that
$\zeta=y^{-1}$ serves as a local coordinate
at the point above
$\{x=0\}$ and
since $y=\zeta^{-1}$ is locally integrable in a disc
centered at $\{\zeta=0\}$
this entials that
when $f$ is lifted to the holomorphic function
$f^*$ on $\Omega$ then $f^*\cdot \chi_\Omega$
is locally integrable in the sense above.
The computation  of $\bar\partial f^*$
as a current on $X$
can be carried out by firt finding
the
usual $\bar\partial$-derivative of
$f$ in the complex $x$-plane.
In this way we
are led to calculus in analytic function theory.
As explained in §§ the result is that
the distribution derivative
$\bar\partial_x(f)$ is supported by 
the real interval $\{0\leq t\leq 1\}$ 
where $t=\mathfrak{Re}\,x$
and given 
by the $L^1$-density 
\[
\phi(t)=-2i\cdot \frac{1}{\sqrt{t(1-t)}}
\]
From this one derives that
$f(x)$ is given by a Cauchy transform in
${|bf{P}}^1\setminus [0,1]$, i.e. one has the
equation
\[ 
f(x)= \frac{1}{\pi}\cdot \int_0^1\, \frac{1}{\sqrt{t(1-t)}}\cdot
\frac{dt}{x-t}
\]
\medskip

\noindent
{\bf{Remark.}}
The discussion above shows that during the study of 
Riemann surfaces
basic material from analytic function theory
intervenes and it is also essential to be familiar with
basic facts in distribution theory, especially the
construction and prooperties
of boundary value distributions.




















\newpage


\centerline{\bf{Historic comments}}
\bigskip

\noindent
The theory  about
algebraic curves has foremost been created by
Abel  and 
Riemann.  
Abel's
article \emph{Remarques sur quelques propriétés génerales
d'une classe  de fonctions trancendantes} 
from 1826 and Riemann's thesis from 1851 
laid  the
table for
later generations. 
A high point in the theory is
Abel's 
addition theorem
which
gives a  bridge between  eliminations in
systems of algebraic equations  depending upon parameters and
evaluations of certain
integrals. It is exposed in § XX.

\bigskip


\centerline{\emph{Work by Jacobi and Puiseux.}}
\medskip


\noindent
Abel's pioneering ideas and results were  developed  further by Jacobi. His
main concern was to exhibit inversion formulas which arise via
abelian intergrals.
The  article \emph{Jacobi: Crelle 17 } from 18xx
studies meromorphic
functions of two independent  complex variables with
four periods which led to
inversion formulas  on hyperelliptic curves with genus two.
This work  inspired later studies
of
integrals which in general depend on several 
complex variables.
Of special interest is the  Jacobi residue
for a pair of irreducible 
polynomials in two variables which 
is used to define the intersection number between a pair of projective curves
even when the intersection is not transversal, i.e. the Jacobi residue gives
a consistent counting of multiplicities
when a pair of algebraic curves
do not intersect transversallly.
Important
contributions are also due to Puiseux.
His  monograph [§ p-p] from 1854 established
the  local uniformisation theorem which 
produces local charts in  
Riemann surfaces
associated to a given  algebraic
equation and  clarified the notion of  critical points
under maps with finite fibers.

\bigskip

\centerline{\emph{Work by Riemann}}
\bigskip


\noindent
Riemann 
gave the general construction of Riemann surfaces 
attached to an algebraic equation.
He    also developed  
differential calculus on manifolds which 
extend integral formulas by Cauchy in the complex plane.
Recall from § XX that if 
$U$ is a bounded domain with a boundary of class $C^1$
in ${\bf{C}}$ and $f=u+iv\in\mathcal O(U)$  extends to a $C^1$-function 
on the closure, then 
\[
\int_{\partial U}\, udv= \iint_U\, (u_x^2+u_y^2)\, dxdy\tag{1}
\]

\medskip

\noindent
Riemann established a similar  formula 
for pairs of analytic functions in  domains of a Riemann surface
which may have  several sheets above
the projective $x$-line and  used this  to
construct a canonical basis for the homology of  compact  surfaces where
a bilinear inequality for holomorphic 1-forms plays a central role.
In this way he clarified the
equality between the topologically defines genus number
$g(X)$ of a compact Riemann surfaces  
and the dimension of
the vector space of globally defined holomorphic 1-forms.
He also realised the crucial role  of solutions to the Dirichlet problem.
Riemann defined  a 1-dimensional  complex manifold
$X$ to be simply connected
if Jordan's  theorem holds, i.e. for  every
simple closed curve $\gamma$ in $X$ the open complement
$X\setminus\gamma$ has exactly two connected.
Solving the Dirichlet problem Riemann  proved that 
every simply connected Riemann surface is biholomorphic
to  the projective line ${\bf{P}}^1$, the complex plane or 
the open unit disc.
Riemann's original proof was a "bit  shaky" and it was not until
1907  that 
Koebe and Poincaré
gave the complete  proof.
But  the original ideas and
essential steps are   due to Riemann.

\medskip

\noindent
{\bf{The Riemann-Schwarz inequality.}}
If $\delta$ is a metric on a Riemann surface
$X$ and $(U,z)$ is   a chart,
the restriction of $\delta$ to
$U$ is expressed by a positive function
$\lambda(z)$.
It means that if $\gamma$ is a rectifiable Jordan
arc
in $U$ then its $\delta$-length is given
by
\[
\delta(\gamma)=\int_\gamma\, \lambda(z)\cdot |dz|
\]
In the chart we can find a real-valued function $u$ such that
\[ 
\lambda(z)= e^{u(z)}
\]
One says that $\delta$-metric has negative
curvature  if the Laplacian of 
$u$ is strictly positive,
i.e.  $\log\,\lambda$ is strictly  subharmonic.
\medskip

\noindent
{\bf{Theorem.}}
\emph{Let $\delta$  be a metric on $X$ whose curvature is
everywhere strictly negative. Then
each  pair of points $a,b$ on $X$
can be joined by a unique geodesic curve.}
\medskip

\noindent
The proof of this result relies upon
the Riemann-Schwarz  inequality which 
goes as follows:
Denote by $\mathcal C(a,b)$ the family of all recitifiable curves
$\gamma$ on $X$ which join $a$ and $b$.
Set
\[ 
\delta_*(a,b)= \min_\gamma\, \delta(\gamma)
\] 
with the minimum taken over
curves in $\mathcal C(a,b)$.
When $\gamma_1,\gamma_2$ is a pair in $\mathcal C(a,b)$
and  $p\in\gamma_1$
we set
\[ 
\delta(p,\gamma_2)= \inf_{q\in\gamma_2}\,
\delta_*(p,q)\quad\text{and}\quad
\text{dist}(\delta;\gamma_1,\gamma_2)=\sup_{p\in\gamma_1}\,
\delta(p,\gamma_2)
\]
\medskip


\noindent
{\bf{Theorem.}} \emph{For
each pair of points $a,b$ in $X$ and every pair
$\gamma_1,\gamma_2$ in $\mathcal C(a,b)$ one has
the inequality}
\[
\delta_*(a,b)^2+
\text{dist}(\delta;\gamma_1,\gamma_2)^2\leq
\frac{1}{2}\cdot \bigl(\delta(\gamma_1)^2+\delta(\gamma_2)^2\,\bigr)\tag{*}
\]
\medskip

\noindent
The proof is given in Chapter VI § XX.
We refer to the result above as the Riemann-Schwarz inequality since 
the  proof relies  upon
results due to them.
The general set-up was later put forward by Poincaré
who constructed metrics with
negative curvature on an extensive
class of Riemann surfaces.
\medskip

\noindent
{\emph{The Riemann-Hurwitz formula.}}.
Another important contribution by Riemann is  a
formula which computes the genus. His original result was 
later reconsidered by Hurwits so one
often adds his name this result.
Let us illustrate a specific case where
one considers 
consider Fermat's  algebraic equation
\[ 
y^p+x^p=1
\]
Here $p\geq 3$ is a prime number.
While $x$ varies in the complex plane and avoids
the  roots of unity for which $x^p=1$
one gets a $p$-tuple of corresponding $y$-values which
means that the Riemann surface $X$ has $p$ many sheets
above ${\bf{C}}\setminus \Sigma\}$ where
$\Sigma=\{e^{2\pi ik/p}\colon k=0,\ldots,(p-1)\}$.
The glueing of these sheets
gives a compact and connected complex manifold.
We shall learn that
the Riemann-Hurwitz formula
entails that the genus of $X$ is equal to $g=1+\frac{p(p-3)}{2}$, i.e
$X$ is homeomorphic to a sphere with $g$ attached handles.
The example illustrates the power of the abstract theory
since it is not easy to discover 
the genus in an intuitive fashion when the prime number $p$ is large.
To be precise, with $g$ as above
one has to 
construct
$2g$ many closed curves which have $(0,1)$ as commen start- and end-points
and give a basis of  the fundamental group of $X$ which is free of rank $2g$.
\medskip

\noindent{\emph{Triangulations and the Euler-Riemann
formula.}}
On a compact Riemann surface
$X$
there exist 
triangulations  where
$A$  vertex points, $B$ 
arcs and $C$  open triangles appear. Riemann proved that
for every
triangulation  on $X$ one has 
the equality
\[ 
2g(X)-2=B-A-C\tag{*}
\]
The reader may check this if $X=S^1$ is the simply connected sphere
and
construct  a triangulation where
$A=C=6$ while $B=10$ and as a result
\[ 
10-6-6=-2
\]
Let us remark that it is essential that $X$ is oriented in (*).
Starting from a  triangle  $\Delta_1$ one
introduces a positive orientation.
Now $\partial\Delta_1$ consists of
three arcs which get positive orientations via the rule of the thumb.
They determine orientations on the three triangles which
share an arc with
$\Delta_1$ and after their boundaries determine new
positive orientations on arcs. The process  continues and since
$X$ is assumed to be oriented and connected it gives a \emph{unique} orientation on
every arc and every open triangle.
Riemann's formula follows when
each triangle is idenified with 
a 2-simplex, each arc with a 1-simplex and vertices with 0-simplexes.
To see this
one  considers the  free abelian group of rank $C$
whose basis are the $C$-many triangles, and similarly the free
abelian group of rank $B$ whose basis consists of oriented arcs.
Finally we get the free abelian group of vertices. Now one has 
the complex
\[
0\to {\bf{Z}}^C\overset {d^0}\to {\bf{Z}}^B\overset{d^1}\to {\bf{Z}}^A\to 0
\]
It is easily seen that
an element $\sum_{\nu=1}^{\nu=C}\, k_\nu\cdot \Delta_\nu$
belongs to the $d^0$-kernel if and only if
all the integers $k_\nu$ are equal.
So the image of $d_0$ is an abelian group of  rank $C-1$.
Next, it is easily seen that the image of $d^1$
is the subgroup of elements 
$\sum_{\nu=1}^{\nu=A}\, k_\nu\cdot p_\nu$
for which
$\sum\,k_\nu=0$.
Hence the $d^1$-kernel has rank $B-A+1$.
It follows that
the quotient group
\[
\frac{\text{Ker}(d^1)}{\text{Im}(d^0)}
\]
has rank $B-A+1-C+1= B_A-C+2$.
This  quotient represents the homology group
$H_1(X;{\bf{Z}})$ which by 
the definition of $g$ is a free abelian group of rank $2g$ and 
Riemann's formula follows.
\medskip

\noindent                                 
{\bf{Remark.}}
The  reader may  consult Riemann's
article  \emph{Abelschen Funktionen}  from his collected work for
the construction of
canonical  triangulations of a sphere with $g$ handles
via $2g$ many closed curves.
A detailed account of his
constructions supplemented with instructive figures
appears  also  in 
[Appel-Goursat: chapter V].
Let us  recall that 
the existence of triangulations on differentiable manifolds in arbitrary dimension
$n\geq 2$ was  given by André Weil in [Weil].
\medskip







\bigskip


\centerline{\emph{Work by Weierstrass.}}
\bigskip


\noindent
In a series of articles 
starting from
the 
construction of doubly meromorphic
functions
associated to
curves of genus one,  
Weierstrass studied
meromorphic
functions of $n$ complex variables which
admit $2n$ periods and investigated their
relation to abelian integrals on compact Riemann surfaces of 
higher genus.
Articles such as \emph{Allgemeine untersuchungen über $2n$-fach
periodische functionen von $n$ veränderlichen} or
the inversion formulas in [Crelle: Bd 89]
go beyond the  material 
in this chapter.
Readers who want study
the interplay between analytic function theory and hyperelliptic curves should
consult original work by Weierstrass which contains a wealth of results and 
valuable  methods. See also the article
\emph{Der Weierstrassche Satz der algebraischen Abgängigkeit
von Abelschen Funktionen und seine Verallgemeinerungen}
by Thimm in [Weierstrass festschrift 1966].






\bigskip


\centerline{\emph{Work by Poincaré}}
\bigskip



\noindent
The article \emph{Mémoire sur les groupes fuchsiens } (Acta math. Vol 1)
gave a new perspective on Riemann surfaces, though one should also give 
credit to
Schwarz who  constructed
special classes of Riemann surfaces using Fuchsian groups
via his conformal mapping formulas between
polygons and the unit disc.
This inspired Poincaré to  investigate
more general classes than those treated by Schwarz.
Poincaré employed   Fuchsian groups
to construct 
Riemann surfaces and
studied  the inverse process
where
automorphic functions with respect to a group
serve as a field of meromorphic functions.
It would lead us too far
to enter
a serious discussion about Poincaré's work. Let us just  mention that
he generalised Abel's additivity  theorem to
algebraic surfaces and
paved the way towards the proof of the uniformisation theorem in its 
general form.
Important contributions are also due to Picard, foremost his
studies of  both linear and non-linear
systems of differential equations.
The interested reader should consult Poincaré's
account of the  historic development of
Fuchisan groups and algebraic functions
which appears in his collected work: [Poincaré vol. xxx].
Volume 2 in
\emph{Théorie des fonctions algébriques} by Appel and Goursat  covers 
Poincaré's
theory where a  text  covering
500 pages offers  a wealth of  examples and  instructive proofs
related to Poincaré's theory.
Properties of a compact Riemann surface  genus $g\geq 2$
related to its complex analytic structure 
leads to
many delicate results. One can  mention Picard's theorem which
asserts that on Riemann surface of genus $g\geq 2$ there exists at most
$84(g-1)$ many birational transformations
and that  every birational transformation has at most $2g+1$ many fixed points, where
equality only  hold for hyperelliptic curves.
\medskip


\noindent
{\bf{Remark.}}
Even though sheaf theory can be used to get simple proofs
the constructive nature
often becomes less transparent. So it is  valuable to
become familiar with
proofs of a more direct nature.
An example is  
Courant's proof of 
the uniformisation theorem
for Kleinian groups of the third kind. Here  the
details  are
considerably harder to follow than those which we are going  to
present but have the merit that
they are constructive when 
a Riemann surface is defined via
a Kleinian
group.





\medskip


\centerline {\bf{Literature on Riemann surfaces}}
\medskip

\noindent
A classic is 
\emph{Die Idée der Riemanschen Flächen} by Weyl from 1913.
Here it is proved    that every compact 1-dimensional complex manifold 
$X$ is defined via an algebraic equation which
amounts to
show
that
there exists an ample family of meromorphic
functions on $X$. The key point is
to use the
elliptic property
of the $\bar\partial$-operator.
Apart from  the 
use of sheaf-theoretic  
vocabulary the  proof in § XX that every compact 1-dimensional 
complex manifold is algebraic  
is  verbatim to
Weyl's original proof.
General results
about non-compact Riemann surfaces 
are of a more recent origin. The vanishing of $H^1(X,\mathcal L)$ when
$X$ is
a non-compact Riemann surface
and $\mathcal L$ an arbitrary holomorphic line bundle is due to Behnke and Stein in their joint article
\emph{Entwicklungen analytischer funktionen auf Riemannschen Flächen}
[Math. Ann. 120 (1948)].
Further results dealing with
Runge's approximation theorem
on Riemann surfaces were established in
the monograph \emph{Reguläre und meromorphe funktionen
auf nicht geschlossene Riemannschen Flächen} by Herta 
Florack [Münster 1848].
These articles have been quite influtential and together with Leray's
sheaf theory opened a veritable gateway to complex analysis on several variables
presented by Stein in the article
\emph{xxxx} from 1951.

\medskip

\noindent
The text-book \emph{Lectures on Riemann surfaces} by
Forster has inspired much of the subsequent material.
The
reader may also consult the  
text-books by Gunning which not only cover the basic theory about
compact  Riemann surfaces but also treat 
the Jacobi mapping and
holomorphic vector bundles over Riemann surfaces.
A concise and elegant
introduction to Riemann surfaces  is also given by 
Goenot and Narasimhan in [G-N].
At several places we also profit upon  material from
the classic \emph{Theorie des fonctions algebriques et leurs integrales}
by Appel and Goursat.
This text-book  contain many instructive
figures and a wealth of examples and detailed calculations of invariants
attached to a Riemann surface and
we follow [ibid]  while   proofs of Abel's resuts
are exposed in § XX.
Readers interested in applications of Riemann surfaces to geometry
should consult the last chapter in [ibid] which
describes many elegant applications such as Laguerre's directed curves
(courbes de directions).
Another  classic  which treats
the interplay between geometry and
Riemann surfaces is
Klein's book \emph{Theorie des Ikosaheder}. But it would
bring us too far to enter this  subject where
unexpected phenomena 
during topological constructions appear which are 
caused  by failure of differentiability.
Arithmetic problems where one for example seeks
rational points on projective curves will not be discussed.
This is a highly non-trivial issue  which is  illustrated by
the  Fermat curves
\[ 
y^p+x^p=1
\] 
where $p\geq 3 $ are prime numbers.
The \emph{non- existence}
of rational points on these curves is
equivalent  to the Fermat conjecture and  was settled by Wiles in 199X.
The proof  requires methods which go far
beyond the material  in this chapter.
For more advanced text-books devoted to non-compact Riemann surfaces
and related moduli probems the
reader may  consult the 
text-book [xxx] by Ahlfors and Sario 
while the book [xxx] by Netto and Sario goes quite far
and contains material which is still open for 
further  research. Below we add some comments about 
some
specific topics.



\newpage

\centerline{\bf{Specific topics.}}
\bigskip

\noindent
{\bf{1. A construction by R. Nevanlinna}}
Following
Nevanlinna's plenary talk 
\emph{Über die Riemannsche Fläche einer analytischen funktion}
held at the IMU-congress
at Zürich in 1932
we recall a  construction which Nevanlinna applied to
his  theory of value distribution of meromorphic functions
on non-compact Riemann surfaces.
\medskip

\noindent
Consider a polygon
$\Pi$ with $q$  corner points placed on the unit circle where
$q\geq 3$. As illustrated by figure XX each 
corner point has an angle 
angles $\frac{\pi}{m_\nu}$.
where  $m_\nu>1$ and $\Pi$ is chosen
so that
\[
\sum\, (1-\frac{1}{m_\nu})>2\tag{*}
\]
\medskip

\noindent
Next,
there exists the conformal
mapping $f$ from
the unit disc
$D$ onto $\Pi$ which 
extends to a bi-continuous map from  the unit circle
$T$ 
onto the boundary of $\Pi$.
The corner points on $\Pi$ correspond to
a $q$-tuple of points
$\{p_\nu= e^{i\theta_\nu}\}$
on $T$ and we have $q$ many  intervals 
$\ell_\nu=
(e^{i\theta_\nu},e^{i\theta_{\nu+1}}\}$.
Now $f$ maps every such circular interval onto line segment on
$\partial\Pi$. If we fix one such interval $\ell_\nu$
then   Schwarz' general reflection theorem 
implies that  $f$ extends analytically across
$\ell_ \nu$ and  
yields an analytic function
$f^*_\nu(z)$
defined in the  exterior disc
$\{|z|>1\}$.
Next,  $f^*_\nu$ can  be extended analytically across
another circular interval $\ell_k$ which yields 
an analytic function$f^{**}_{k,\nu}$  in  $D$.
The process can be continued and gives
a multi-valued  analytic function
$F$ defined in ${\bf{C}}\setminus\{p_1,\ldots,p_k\}$.
Since we have started from a conformal mapping
its complex derivative is everywhere $\neq 0$.
The full range of $F$ in the sense of Weierstrass
is determined via succesive applications of Schwarz' reflections.
Suppose for example that
we continue $f$ along
and arc $\ell_1$ where
$f(\ell_1)$ is a horisontal line segement of $\partial\Pi$.
In this case the analytic continuation
$f^*$ is obtained via complex 
conjugation so the range of $f^*$ on the
exterior unit disc
is equal to
the polygon
$\Pi(\ell_1)$ which is obtained by
reflecting $\Pi$ in $\ell_1$.
The reader is invited to contemplate upon the result after
a finite number of reflections or consult Nevanlinna's text-book
\emph{Uniformisation} for details and further comments about
the whole construction.
Let us remark that this  can be used to extend
Picard's  theorem to cases where an analytic functions exclude a finite set of
values. See again [ibid].
The constructions  above
also appear in the  theory about
automorphic functions and properties 
of elementary domains. In this context
analytic function theory
has initiated  
topics in combinatorical topology which  was
put forward by
Speiser in the influential article \emph{Probleme aus dem gebiet der ganzen
tranzendenten Funktionen} from 1929.




\bigskip

\noindent
{\bf{2. Algebraic function fields.}}
Every compact Riemann surface
arises from an algebraic function field.
The article \emph{Theorie der algebraischen functionen
einer verändelichen} by Dedekind and Weber from 1882
clarified this result 
which is used in arithmetical problems and has the merit that
it also applies 
in characteristic $p$.
Recall that
Weil has proved the Riemann hypothesis 
for fields of algebraic functions over finite fields. His book \emph{Sur les courbes algebriques}
treats  the $p$-adic case where the geometric and algebraic methods
are quite different from those we are going to expose 
when the groundfield is ${\bf{C}}$. 
Let us also recall that  Weil's influential article
\emph{Zur algebraischen Theorie der algebraischen Funktionen}
(Çrelle: 179: 1938)
gives  general constructions of differentials on function fields which
can be adapted in every characteristic.
So the reader should be aware of the fact that there are many
ways to enter studies of
Riemann surfaces, and more generally algebraic curves
over arbitrary fields.
A book which covers both the algebraic constructions
and the topology
on compact Riemann surfaces is Chevalley's 
book \emph{Introduction to the theory of algebraic functions in one
variable}. The text contains
many proofs  which
are useful to study before  
entering  deeper areas in algebraic geometry.







\medskip
\noindent
{\bf{3. Moduli problems.}}
The classification of
compact Riemann surfaces  with  prescribed genus is 
another central
issue. 
We shall not try to 
enter into a detailed account.
The interested reader should first of all consult  
the article
\emph{The complex analytic structure of the space of closed Riemann surfaces} 
by Ahlfors, who like Riemann has given many  important contributions to
the theory about Riemann surfaces, foremost in
the non-compact case. 
The moduli problem was already considered by Riemann
who proved that when $g\geq 2$ then
the number of independent parameters which are needed to classify
isomorphism
classes of Rieman surfaces with genus $g$ is equal to
$3g-3$. Riemann gave two proofs which  are exposed in 
Picard's the text-book
\emph{Traité d'Analyse} (Part II: page 482].
In the article [Teich]
Teichmüller  asked for
the realisation of a global complex analytic structure for the 
$3g-3$-dimensional moduli space.
The case $g=2$ is instructive
for if a Riemann surface
$X$ has genus 2 
there exist Weierstrass points on $X$ which means that one can
find
$f\in\mathfrak{M}(X)$ whose set of poles is confined to a single point where
$f$ has a double pole.
Hence the holomorphic map from
$X$ onto the projective
line which sends $p\in X$ into $f(p)$ is 2-sheeted. It follows
that  
$\mathfrak{M}(X)$ is an algebraic field extension of degree two over
the field of meromorphic functions generated by $f$.
As explained in § XX   this implies
that $X$ is the Riemann surface  associated to an algebraic
equation of the form
\[ 
y^2=P(x)
\] 
where $P(x)$ is a polynomial with simple zeros.
Moreover, since $g=2$ the Riemann-Hurwitz formula to be exposed in § xx
that $\deg P$ only can be five or six which 
comes quite  close to Riemann's
result that the moduli space for curves of genus two
is described via $3\cdot 2-3= 3$ many parameters. See § xx for a further discussion.
In connection with the moduli problem 
a theorem due to  Weber
in [Crelle: vol. LXXVI] 
asserts the following: \emph{Let $X$ and $Y$ be a
pair of Riemann surfaces with the same genus $g\geq 2$.
Then, if $\phi\colon X\to Y$ is a surjective holomorphic map
it follows that $\phi$ is biholomorphic.}.
We give the proof in § X  based upon constructions
of  adjoint curves.



\bigskip

\noindent
{\bf{4. Relation to algebraic geometry.}}
Results about compact Riemann surfaces 
have  inspired later studies in
algebraic geometry. Apart from facts  which already have been
mentioned and will be  covered in § A-H, we recall the
Reciprocity Law by
the Brill and Noether [Appel-Goursat: page 371-374].
This result was originally
announced  for compact Riemann surfaces
but
inspired more general considerations in
algebraic geometry where 
one encounters singular projective curves
which are not 
identfied in a direct way with a compact Riemann surfaces.
More precisely, 
let
$N\geq 2$ and consider the $N$-dimensional projective space
${\bf{P}}^N$ over the complex field.
It contains algebraic subsets which are irreducible and of dimension one
and  called
projective curves embedded in ${\bf{P}}^N$.
In general such a projective curve
$S$
is not regular so one needs to construct 
the associated Riemann surface. This is achieved by
local Puiseux-Riemann charts and gives
a unique 
compact Riemann surface
$X$
called the normalisation of $S$.
The map $\rho\colon X\to S$
is in general is not homeomorphic since
some singular points in $S$ may be surrounded by
more than one Puiseux-Riemann chart. This is explained in
§ XX.
We shall not  deal with more  extensive
material in algebraic geometry
and therefore not  study  embedded algebraic curves
in projective spaces  except for
intersection numbers between
irreducible algebraic curves
which is  treated in § XX.









\newpage


\centerline {\bf{§ 0. Specific examples.}}
\bigskip


POSTPONE





\noindent
The sections below serve to illustrate subsequent material.
The less experienced reader may prefer to
return to the material below later
except for the first
head-line:


\bigskip

\noindent
{\bf{The Riemann-Hurwitz formula.}}
We shall foremost consider  compact Riemann surfaces
$X$ which are  attached to an algebraic equation
$F(y,x)=0$. 
When this algebraic equation is given
there exists a procedure to find $g$ via
the duality theorem in § X. The method  is to
take a  meromorphic 1-form $w$  on $X$ and
determine  its zeros and poles which gives a divisor $D$ on $X$ such that
one has an isomorphism of sheaves:
\[ 
\mathcal O_D\cdot w\simeq \Omega\tag{*}
\] 
where $\Omega$ is  the sheaf of holomorphic 1-forms on $X$.
The divisor has a degree  and we shall learn that
\[ 
2g-2=\deg D
\] 
holds for every meromorphic 1-form $w$.
Using this  one can compute the genus 
for arbitrary given algebraic equations. 
We shall give many examples  to illustrate the  calculation of $g$
Consider for example
the case  when the equation is of the form
\[
y^m=Q(x)
\] 
where $m\geq 2$ and $Q(x)$ is a polynomial
of some
degree $n$ and  $y^m-Q(x)$ is irreducible in the unique factorisation domain
${\bf{C}}[x,y]$.
On the associated Riemann surface we 
have the meromorphic 1-form $\omega=dx$.
If the zeros of
$Q$ are all simple and the integers $m$ and $n$
are relatively prime  we shall learn
that the degree of the divisor which appears in (*)
satisfies
\[ 
\deg D= n(m-1)-m
\implies g=\frac{1}{2}(n-1)(m-1)
\]
More involved computations arise when
$Q$ has multiple zeros and the integers $m$ and $n$ are not prime.
More precisely, suppose that
$Q$ has $k$ distinct zeros $\alpha_1,\ldots \alpha_k$
where the zero at $\alpha_\nu$ has some order $e_\nu$.
So here $e_1+\ldots+e_k=n$.
The  positive contribution to  the divisor $D$
at
a zero $\alpha_\nu$  is found
as follows: 
Denote by $\rho_\nu$ the common divisor of $m$ and $e_\nu$.
So $\rho_\nu=1$ if and only if
$m$ and $e_\nu$ are relatively prime.
Then the  positive contribution at
$\alpha_\nu$  is  given by  
\[
m-\rho_\nu\tag{i}
\]
Next,  poles of $dx$ occur at points where $x=\infty$.
Another computation in local charts shows that if
$\rho_\infty$ is the common divisor of $n$ and $m$
then $D$ gets a negative contribution
$m+\rho_\infty$.
Hence 
\[
g=1+\frac{1}{2}\cdot \sum_{\nu=1}^{\nu=k}\, (m-\rho_\nu)
-\frac{1}{2}\cdot (m+\rho_\infty)\tag{ii}
\]


\noindent
{\bf{Example.}}
Consider the  equation where $a$ differs from  0 and 1 and
\[ 
y^4=x^2(x-1)^3(x-a)^3\tag{i}
\] 
So here $Q$ has degree 8 and  (*) gives
\[ 
g=1+\frac{1}{2}\cdot [(4-2)+(4-1)+(4-1)]-\frac{1}{2}\cdot(4+4)=1
\]



\noindent
The low $g$-number is not so obvious from the start
since (1) is an algebraic equation of degree 8.
Notice also that the $g$-number does not change in a continuous manner.
For example, if the right hand side is replaced by 
a monic polynomial $Q(x)$ of degree 8 with simple zeros
which  be arbitrary close to
the corresponding
multiple zeros
then 
\[ 
g=1+8\cdot 3-4=21
\]

\noindent
In general, if $n\geq 3$ and
$Q(x)$ is a polynomial of degree $n$ with simple zeros then the genus of
$X$ associated to the equation $y^n=Q(x)$ becomes
\[ 
g= 1+n(n-1)-n=(n-1)^2
\]




\bigskip



\noindent
The subsequent material    is
inserted to 
describe the flavour 
during the studies of  Riemann surfaces.
The reader may postpone § 0.1-0.8
until later and proceed directly to the headline
\emph{Outline of the Contents}.


\newpage






\centerline {\bf{0.1 Humbert's rosette.}}
\medskip


\noindent
Consider
the real $(x,y)$ plane where  $(r,\theta)$ are the polar coordinates
and the 
curve defined by the equation
\[ 
r^3=\cos\,3\theta\quad\colon\quad 0\leq \theta\leq 2\pi\tag{*}
\]
Drawing a picture the reader can recognize a rosette
denoted by $\mathfrak{R}$.
When 
$\pi/6\leq \theta\leq \pi/6+\pi/2$
we see from a figure that $\mathfrak{R}$
contains a simple closed curve which passes the origin and
for other $\theta$-intervals we get two other  simple curves and
the orgin is a common point to these.
Hence $\mathfrak{R}$   is a plane curve with a self-intersection
at the origin  and   oriented by
$\theta$.
With $z=x+iy$ we have $r^3\cos 3\theta=
\mathfrak{Re} z^3$ while $r^6=(x^2+y^2)^6$
so  (*) can be written in the form
\[
(x^2+y^2)^3=\mathfrak{Re}(x+iy)^3)= x^3-3xy^2
\]
Treating $x$ and $y$ as independent complex variable
we get the algebraic equation
\[ 
y^6+3x^2y^4+(3x^4+3x)y^2= x^3-x^6\tag{1}
\]
This is an irreducible equation which gives a compact
Riemann surface
$X$ whose  real points belong to $\mathfrak{R}$.
The equation (1) has degree six and looks rather complicated.
But it turns out that $X$ has genus one and is therefore homeomorphic
with a torus. To show this one  considers the  arc-length measure
$d\sigma $ which in polar coordinates
is given by
\[ 
d\sigma^2=dr^2+r^2d\theta^2
\] 
On  $\mathfrak{R}$ we have
$r^2dr=-\sin\, 3\theta\, d\theta$
and a  computation gives
\[
d\sigma = \frac{d\theta}{r^2}=\frac{1}{x^2+y^2}\cdot
d\arctan \frac{y}{x}=
\frac{xdy-ydx}{(x^2+y^2)^2}
\]
Hence the arc-length measure along  $\mathfrak{R}$
has a differential given by a rational function of $x$ and $y$.
Passing to the Riemann surface $X$ the right hand side
represents a differential 1-form and
in § X we show that  is everywhere holomorphic and $\neq 0$
which
explains why $X$ has genus one and  therefore   homeomorphic with a torus.
Let us now consider a circle $\mathcal C$
defined by an equation
\[ 
(x-\alpha)^2+(y+\beta)^2=\alpha^2+\beta^2
\]
where $\alpha,\beta$ are small positive constants. By a figure  the reader
can recognize that $\mathcal C$ intersects $\mathfrak{R}$
at three points $A_1,A_2,A_3$. Denote by $\ell(A_K)$ the arc-length
of the curve from the origin to $A_k$ taken along the corresponding
simple arc on  $\mathfrak{R}$.
Keeping trace of the orientation in  Figure XX 
it turns out that there exists a contant $C$ which is independent of the chosen
circle such that
\[
\ell(A_1)+\ell(A_2)-\ell(A_3)=C
\]
It is possible to show this after some
rather involved calculation but the  point is that
the existence of $C$ is an immediate consequence of Abel's Theorem
where one has used the fact that
$d\sigma$ yields a holomorphic 1-form
on the torus $X$, together weith some easy calculations which show that
when the equation for
$\mathcal C$ determines an algebraic curve in the 
2-dimensional complex projective $(x,y)$-space, then
this curve  has a triple intersection with
$X$ at the $(0,0)$ and 
six points intersect at infinity whose positions are independent of
the
chosen circle.
In addition we have  the three simple intersections
at the $A$-points.
This  reflects a general fact since
the circle is a curve of degree two while $\mathcal c$ has degree 6
and therefore the number of intersection points counted with multiplicities is 12.
We  explain this in § xx after  general results about
Riemann surfaces have been exposed. The example above
was treated by Humbert
in an article from 1887. It is  instructive since it shows  that
the  abstract theory about compact Riemann surfaces
has  concrete geometric applications.











\bigskip


\centerline {\bf{0.2 Currents and duality.}}
\medskip

\noindent
On a compact Riemann surface
$X$
there exist  the space
$\mathfrak{c}^{0,1}(X)$ of currents with bidegree $(0,1)$
which  is  the topological dual of the 
Frechet space $\mathcal E^{1,0}(X)$
of  differential
$C^\infty$-forms with bi-degre 
$(1,0)$.
The complex analytic structure gives  the
$\bar\partial$-operator which  sends $C^\infty$-functions $g$ to
smooth
(0,1)-forms
$\bar\partial(g)$. More generally $\bar\partial$ sends a distribution
$\mu$ on $X$ to the (0,1)-current $\bar\partial (u)$.
A fundamental fact is that the
$\bar\partial$-operator is elliptic which means that a distribution $\mu$ satisfying 
$\bar\partial(\mu)=0$ is a holomorphic function.
This was demonstrated and applied by
Hermann Weyl whose     book
\emph{The concept of a Riemann surface}
from 1913 contains the proof 
that
every compact 1-dimensional complex manifold
is given by an algebraic function field.
As we shall see later on currents  give
quick proofs 
of  central results about compact Riemann surfaces.
For example, the fact that
$\bar\partial$-closed $(0,1)$-currents are
holomorphic 1-forms easily entails that
\[ 
\Omega(X)\simeq
\bigl[\frac{\mathfrak{c}^{0,1}(X)}{
\bar\partial \mathfrak{c}(X)}\bigr]^*\tag{0.1}
\]
where the right hand side refers to the dual vector space.
At the same time Dolbeault resolutions will teach us that
\[
\frac{\mathfrak{c}^{0,1}(X)}{
\bar\partial \mathfrak{c}(X)}\simeq H^1(X,\mathcal O)
\tag{0.2}
\]


\bigskip


\noindent
Examples of  (0,1)-currents are  
integration cycles. Namely, let $\gamma$ be an oriented  and closed
Jordan curve in $X$  of class $C^1$. Every test-form
$\phi$ of bi-degree (1,0) can be integrated on
$\gamma$. Specializing
to holomorphic 1-forms
$w$
we get a ${\bf{C}}$-linear functional on
$\Omega(X)$ defined by
\[ 
w\mapsto \int_\gamma\,w
\]
One refers to this as  period integrals and (0.1) means
that
the integration current  $\gamma$ is $\bar\partial$-exact if and only if
the period integrals above are zero for every
holomorphic 1-form $w$.
If  these periodic integrals vanish for
every
$w\in\Omega(X)$ it turns out that the closed Jordan
curve
$\gamma$ is homotopic to zero, i.e. it can be retracted to
a single point which means that its image in the fundamental group $\pi_1(X)$
vanishes. This illustrates a flavour during the study of Riemann surfaces
where geometry and
analytic results often intervene with each other.
\medskip



\noindent
Next, consider
the cohomology group
$H^1(X,\Omega)$. In §xx we show that
the elliptic property of $\bar\partial$ entails that
the dual space 
\[
\bigl[ H^1(\Omega)\,\bigr]^*\simeq
\bigl[\frac{\mathcal E^{1,1}(X)}{\bar\partial \mathcal E^{1.0}}
\bigr]^*\simeq \mathcal O(X)={\bf{C}}\tag{i}
\]
Hence $H^1(\Omega)$ is 1-dimensional.
Next there exists  the following  exact sequence of sheaves
\[
0\to {\bf{ C}}^*_X\to \mathcal O^*\overset{\partial}\to \Omega\to 0
\] 
where
$\mathcal O^*$ is the  multiplicative sheaf of
holomorphic functions
without zeros.
Sheaf theory teaches that this gives an exact sequence of complex
vector spaces:
\[
0\to H^0(X;\Omega)\to H^1(X, {\bf{ C}}^*_X)
\to H^1(X,\mathcal O^*)\overset{\rho}\to 
H^1(X;\Omega)\to H^2(X, {\bf{ C}}^*_X)\to 0\tag{ii}
\]
In addition to this, a topological
result which we prove in § xx shows that
\[
H^2(X, {\bf{ C}}^*_X)\simeq \frac{H^2(X, {\bf{ C}}^*_X)}{
H^2(X, {\bf{ Z}}^*_X)}= \frac{\bf{ C}}{\bf{ Z}}\tag{iii}
\]
where ${\bf{ Z}}$ is the additive group of integers.
Together with (i) this implies that the image under the map
\[
\rho\colon H^1(X,\mathcal O^*)\to 
H^1(X;\Omega)
\] 
from (ii) is  reduced to the set of integers.
Apart from the "yoga"  based on diagram chasings, there remains to
understand what is really going on. To
grasp  the $\rho$-image one must
construct a cohomology class $\xi\in H^1(X,\mathcal O^*)$
whose $\rho$-image corresponds to the integer 1 in
the image and therefore is a generator of the abelian group of all integers.
This will be done in § xx where we also show that there exists a 1-1 correspondence
with isomorphism classes of twisted rings of
holomorphic differential operators.








\medskip

\noindent 
{\bf{Remark.}}
The calculus with currents
clarifies many constructions which otherwise
are not so easy to grasp. For example, let
$X$ be equipped with
a triangulation.
Each 2-simplex $\Delta$ appears as an open subset of $X$ where the identity function
gives a current of degree zero, i.e. one  integrates
2-forms on the oriented open subset $\Delta$.
Now there exists the (1,0)-current
$\partial(1_{\Delta}$ which is supported by the boundary arcs of
$\Delta$ and the  operative equation becomes:
\[
 \partial(1_{\Delta}(\phi^{0,1})=
- \int_{\Delta}\, \bar\partial (\phi^{0,1})=
-\int_{\partial \Delta}\, \phi^{0,1}
 \]
where the last equality follows from Stokes theorem and the
line integral is computed using the orientationon
$\partial\Delta$ derived via the rule of thumbs.
In the same way
there exists
the current (0,1)-current
$\bar\partial(1_{\Delta})$.

\bigskip


 
\centerline{\bf{0.3 Branch cuts on Riemann surfaces.}}
\medskip

\noindent
One  gets a picture of a Riemann surface
$X$ using the algebraic equation which defines it and 
the projection from $X$ onto the projective line.
Consider  an equation of the form
\[
 Q(x)y^n=1
\] 
where $n\geq 2$ and $Q(x)$ is a monic polynomial of degree $n$ with simple zeros $c_1,\dots,c_n$.
We shall learn that the meromorphic function $y$ has
simple poles at the points $\{c_k,0\}$ and
above $x=\infty$ there occur $n$ points and $y$ has a simple zero  at
each such point.
The map $\pi$ from $X$ onto the projective
$x$-line is $n$-sheeted and to find
single-valued sheaets one proceeds as
follows:
In the complex $x$-plane we can construct
compact sets $\Gamma$ which
are connected and given as a finite union of Jordan arics
while $\Omega= {\bf{P}}^1\setminus \Gamma$ is connected
and all the zeros $c_1,\cdots,c_n$ belong to $\Gamma$.
One refers to $\Gamma$ as a tree and since
$\Omega$
is simply connected
there exists
the $n$-root of $Q(z)$ which gives the analytic root function
\[
y_*(x)=Q(x)^{-1/n}
\] 
whose branch is chosen so that its Taylor series above $x=\infty$ 
starts with the linear term $\frac{1}{x}$.
By results from §§  there exists a unique Riesz measure
$\mu$ supported by
$\Gamma$ such that
\[
y_*(x)=\frac{1}{2\pi i} \int_\Gamma \,\frac{d\mu(\zeta)}{x-\zeta}
\]
Since $y_*(x)\simeq \frac{1}{x}$ at inifinity 
the mean-value
$\int_\Gamma \,d\mu(\zeta)=1$.
Hence the total variation of $\mu$ is at least one
which  suggests a 
variational problem. Namely,  try to find a tree $\Gamma$ such that
$\mu$ is a probability measure..
This
corresponds to a special branch cut of
the Riemann surface and the qurestion arises if $\Gamma$ exists and if it 
is unique.
An affirmative answer  was given in the article
[xxx] by Bergqvist and Rullgård which  shows 
that 
there exists a unique tree $\Gamma$ such that
$\mu$ is a probability measure.
The proof relies upon a study of
roots of eigenpolynomials to
differential equations and
will be exposed in § XX. 


\medskip

\centerline {\bf{0.4 The Cauchy  transform on Riemann surfaces.}}
\medskip

\noindent
A construction which 
extends  the Cauchy transform of Riesz measures with compact support in
the complex plane  goes as follows: Let $U$ be an open 
and connected subset of some compact  Riemann surface
$X$ and suppose that
$\partial U$ is a union of
a finite number of rectifiable Jordan arcs.
If  $\phi\in\mathcal O(U)$ has the property that it is
locally integrable over
sets $D\cap U$ when $D$ are small charts around boundary points, 
there exists a unique complex valued Riesz measure
$\mu$ supported by $\partial U$ such that
\[
\iint_U\, \phi\cdot
\partial\bar\partial(g)= \int_{\partial U}\, g\cdot  d\mu\tag{*}
\]
hold for every $g\in C^\infty(X)$.
Above the composed operator $\partial\circ\bar\partial$
sends every $C^\infty$-function $g$ on $X$ to a smooth
$(1,1)$-form 
$\partial\bar\partial(g)$ is 
and in the left hand side above its product wuth $\phi$ has been integrated
over
$U$ which is okay since the complex analytic structure on
$X$ yields a  positive orientation on its underlyng
real and 2-dimensional manifold.
In § XX we study special situations of this
construction where $\phi$ from the start is a meromorphic
function in $X$ and  discuss  variational problems of a similar nature as in
the case  above.

\newpage

\centerline
{\bf{0.5 Riemann's canonical basis for the singular holomlogy}}
\medskip

\noindent
Riemann surfaces
are constructed via  a
glueing of charts. 
There are many ways to achieve this and
at the same time 
Riemann surfaces with a prescribed genus $g$ are all homeomorphic
to a sphere with $g$ handles attached. So in principle it suffices
to perform suitable constructions for each $g$ but for a specific
surface $X$ with genus $g\geq 1$ one proceeds as follows:
Each oriented and closed Jordan curve
$\gamma$ on $X$ of class $C^1$ gives a 1-current which sends a test-form
$\phi$ to the line integral along $\gamma$:
\[
\mathfrak{c}_\gamma(\phi)=\int_\gamma \phi
\]
If $\phi=dg$ is exact where $g\in C^\infty(X)$ 
then the integral is zero since
$\gamma$ is closed.
Hence 
$\mathfrak{c}_\gamma$ gives a linear functional on the Dolbeault quotient
of closed modulu exact 1-forms which 
is a complex vector space of dimension $2g$ and dual to
the singular homology over $X$ in degree one.
There  exists the free abelian group
$H_1(X,{\bf{Z}})$ of rank $2g$ whose elements
represent group homomorphisms from the fundamental  group
$\pi_1(X)$ into the additive group of integers.
Here one has used the topological
fact that
$\pi_1(X)$ is a free group with $2g$ many generators.
If we choose some point  $p\in X$  and identify
$\pi_1(X)$  with homotopy classes of closed curves
which have $p$ as a common start- and end-point, then there exist
$2g$ many closed Jordan curves $\gamma_1,\ldots,\gamma_{2g}$
whose homotopy classes generate
$\pi_1(X)$.
The Dolbeault isomorphism gives
a $2g$-tuple of closed 1-forms
$\{\phi_\nu\}$ such that
\[
\int_{\gamma_k}\, \phi_j= \text{Kronecker's delta function}
\]
Since images of these 1-forms in the Dolbeault quotient are unique.
the integrals
\[
\int_X \phi_k\wedge\phi_j\tag{1}
\]
yield an anti-symmetric $2g\times 2g$-matrix whose elements 
only  depend on
the chosen $\gamma$-basis.
A simple matrix  arises of
of this kind is
a block matrix where
formed by $2\times 2$-matrices where +1 and -1 are the
non-diagonal elements.
One says that 
the closed curves $\{\gamma_\nu\}$ give a canonical basis
if (1) takes the value +1 when
for pairs $\{(j,j+g)\colon\, 1\leq j\leq g\}$
and   zero for all other pairs $k< j$.
\medskip

\noindent
{\bf{Remark.}} In the text-book [Appel-Goursat] one refers to
such a basis as a \emph{système canoniques des rétrosections}
and there it is explained how one constructs
such a basis after $g$ handles have been
removed from the sphere.
When  a Riemann surface
$X$ is defined by an algebraic
equation
one has a map from $X$ onto the projective $x$-line.
which can be  used to obtain
a canonical $\gamma$-basis.
However,  these   constructions can be quite involved
so the mere existence of a canonical $\gamma$-basis
via differential calculus is therefore a notable point if one wants to avoid
hard initial constructions when a Riemann surface is presented by an algebraic equation.
Riemann studied
integrals of holomorphic 1-forms
and their conjugate forms with respect to a canonical
$\gamma$-basis.
Riemann's \emph{Bilinear Inequality}
asserts that if $\{\gamma_\nu\}$ is a canonical
homology basis and $w$ an arbitrary holomorphic 1-form
with periods
\[
\int_{\gamma_j}\, w= \pi_j\quad\colon\quad 1\leq j\leq 2g
\] 
then 
\[
\frac{1}{2\pi i}\cdot \sum_{k=1}^{k=g}\, \bigl (\pi_{k+g}\cdot\bar \pi_k-
\pi_k\cdot \bar \pi_{k+g}\bigr)>0
\]



\noindent
We shall prove this result in § XX.


\medskip

\noindent
{\bf{An example.}}
Consider an irreducible algebraic equation of degree four:
\[ 
P(x,y)= y^4+q_1(x)y^3+q_2(x)y^2+q_3(x)y^3+x^4=0
\] 
where
$\{\deg q_\nu\leq \nu\}$ .
If the gradient vector
$(P'_x,P'_y)\neq (0,0)$ for all 
$(x,y)\in{\bf{C}}$ where $P(x,y)=0$ we shall learn in
§ xx that
the associated Riemann surface has genus 3 and
the $3$-dimensional vector space of
holomorphic 1-forms has a basis given by:
\[
\omega_1=
\frac{ax+b y+c}{P'_y}\cdot dx \quad\colon\, 
\omega_2=
\frac{x}{P'_y}\cdot dx \quad\colon\, 
\omega_3=
\frac{y}{P'_y}\cdot dx
\] 
then we have a basis for the complex vector space
$\Omega(X)$ and taking their conjugate (0,1)-forms
$\{\bar \omega_j\}$
we get 
the   Hermitian matrix with elements
\[
\rho_{kj}= \int _X \omega_k\wedge \bar \omega_j
\]
From this we can find a triple of holomorphic 1-forms
$\{\omega_k^*\}$ such that
\[ 
\int_X\omega_k\wedge \bar \omega_j^*= 
\text{Kronecker's delta function}
\]


\noindent
Now the material above gives the existence of a canonical basis
$\{\gamma_j\}$
for which the $\omega^*$-forms
satisfy (xx).
\medskip

\noindent
{\bf{Remark.}}
Notice that  this gives  an inverse process to attain a canonical basis
of homology.
It goes without saying that
the constructions for a general algebraic equation  is not easy to carry out.
In any case, Riemann's results give  theoretical foundations for
topological constructions.
\medskip


\noindent
{\bf{0.5.1 Glueing }}
To
grasp a compact Riemann surface one can
glue simply connected subsets across 
arcs. As an illustration we
consider an elliptic curve $X$ defined by the equation
\[
y^2=x(x-a)(x+b)
\] 
where $a$ and $b$ are positive real constants.
Remove the interval $[-b,a]$ from the complex $x$-plane.
In § XX we have explained that
there exists the  square root function
\[ 
y^*(x)= \sqrt{x(x-a)(x+b)}
\] 
which is holomorphic in the open set $U={\bf{C}}\setminus [-b,a]$
and takes positive real values  when $x$ is real and $>a$.
Next, the projection $\pi\colon {\bf{P}}^1$
onto the projective $x$-line is 2-sheeted an unramified
above $U$. So 
$\pi^{-1}(U)$ contains
two sheets $U^*$ and $U_*$
which are mapped biholomorphically onto $U$.
When $x=\infty$ we shall learn that
$\pi^{-1}(\infty)$ is reduced to a single point $p^*$
where the meromorphic function $y$ has a triple pole and $x$ a double pole.
So $U^*$ and $U_*$ have a common boundary point at $p^*$.
Their boundaries also share the points
$(0,0), (0,a),(0,-b)$.
The intervals $(-b,0)$ and $(0,a)$
appear as boundary arcs for the two sheets.
While one is crossing $(0,a)$ on the Riemann surface
the
meromorphic $y$-function on $X$ is denoted by  $y^*$ in $U^*$
moves to the holomorphic   function $y_*$ in $U_*$.
Now we  construct two simple closed $\gamma$-curves on $X$.
Choose first some simple Jordan arc
$J_1$ which joins 0 and $a$ and stays in the upper half-plane
of the $x$-plane. Via $\pi$ it is lifted to
a simple arc $J_1^*$ in $U^*$
with the  end-point  $(0,a)$ on $X$. Now we
can move in the reverse direction along $J_1$ but this time
its inverse $\pi$-image is taken in the sheet $U_*$ until one
arrives to the origin. This gives
a closed
Jordan curve $\gamma_1$ in $X$.
In a similar fashion we take a Jordan arc
$J_1$ from the origin to $(0,-b)$
which again moves in
$\mathfrak{Im}x)>0$
and construct a closed Jordan arc $\gamma_2$ in $X$
which first moves in $U^*$ until it turns into $U_*$ when
it passes $(0,-b)$.
Next, on $X$ we shall later on learn that the differential 1-form
$\frac{dx}{y}$ which a priori is meromorphic
actually is holomorphic on the whole of $X$
gives  a basis vector for the 1-dimensional complex vector space
$\Omega(X)$ of holomorphic 1-forms.


\medskip

\noindent
{\bf{Exercise.}} Show that one has the two equations:


\[ 
\int_{\gamma_1}\, \frac{dx}{y}= \frac{2}{i}\int_0^a\frac
{dx}{\sqrt{x(x+a)(x+b)}}\tag{i}
\]
\[ 
\int_{\gamma_2}\, \frac{dx}{y}= 2\cdot \int_0^b\frac
{dx}{\sqrt{x(x+a)(x+b)}}\tag{ii}
\]
Above one integral is purely imaginary and the other is real which
reflects the fact that the two $\gamma$-curves
is a canonical basis 
for the 2-dimensional integral homology group on $X$.
The two numbers which appear in the right hand side of (i-ii)
are called the periods of the 1-form $\frac{dx}{y}$.
Their siginificance
will be explained in § xx when we 
classify elliptic curves, i.e. the family of compact Riemann surfaces with genus one.
\medskip

\noindent
{\bf{0.5.2 The torus}}
The torus ${\bf{T}}^2$ can be 
identified
with
the quotient space
$\frac{{\bf{C}}}{\Gamma}$ where
$\Gamma$ is the lattice of Gaussian integers.
The open unit square
$\{0< x,y<1\}$ is a fundamental domain and 
the two line segments $\gamma_1=\{0\leq x\leq 1\}$ on the $x$-axis and  
$\gamma _2=\{0\leq  y\leq 1\}$ on the $y$-axis
give simple closed curves on the torus since
both $(1,0)$ and $(0,1)$ are identified with the origin.
A complex analytic structure  is 
derived from ${\bf{C}}$
and the holomorphic 1-form
$dz$ yields an abelian differential on
the torus, i.e.  a globally defined holomorphic 1-form.
With chosen orientations on $\gamma_1$ and $\gamma_2$ 
we have
\[ 
\int_{\gamma_1}\, dz=1\quad\colon\quad \int_{\gamma_2}\ dz=i
\]
These two periods are ${\bf{R}}$-linearly independent and we shall learn that
this reflects the topological fact that
the two $\gamma$-curves
generate
the singular homology group  which is a free abelian group of rank 
two.




\medskip



\centerline
{\bf{0.6 Automorphic functions.}}
\medskip


\noindent
Another  gateway to  study of Riemann surfaces
was created by Poincaré which  employs   Fuchsian groups
and their associated automorphic functions.
Hilbert
proved that
automorphic functions
can be found  via solutions to  integrals equations.
This has  an advantage 
when one seeks approximative solutions
numerically.
The fundamental equation  goes as follows:
Identify the unit circle with the $2\pi$-periodic $\theta$-interval.
Let
\[ 
\theta\mapsto \Psi(\theta)
\]
be an involutive  map form the unit circle
into itself, i.e.  
the composed map $\Psi\circ\Psi$ is the identity.
Examples of such $\theta$-maps occur when
the fundamental substitutions of a Fuchsian group
define the involutive
$\Psi$-map
The search of automorphic functions 
associated to the Fuchsian group
amounts therefore to find meromorphic
functions
$f(z)$ defined in ${\bf{C}}$ with
a finite number of poles in the disc
$\{|z|<1\}$ which  on the unit circle satisfy
\[
f(\Psi(\theta))= f(\theta)\tag{2}
\]
To get such  functions we start from 
a rational function $R(z)=\frac{Q(z))}{P(z)}$ where
the polynomial $Q$ has degree strictly less than $P$ and 
the zeros of $P$ belong to $\{|z|<1\}$.
Now one seeks $f$ as a solution to the integral equation
\[ 
f(z)=\frac{1}{2\pi }\cdot \int_0^{2\pi}
\, \bigl[\frac{1}{e^{i\theta}-z}-\frac{\Psi'(\theta)}{\Psi(\theta)-\Psi(z)}\,\bigr]
\cdot f(e^{i\theta})\cdot e^{i\theta}\cdot d\theta+R(z)+R(\Psi(z))\tag{*}
\]
which to begin with holds when $|z|=1$ and after 
$f$  extends  to a meromorphi functions with the same poles as $R$. 
The kernel function in (*) is  singular. But as explained in
Carleman's lecture at the IMU-congress in Zürich 1932,
see [xx- page 148-150],  one can
rewrite the integral equation and obtain
a kernel where Fredholm's theory applies and in this way
obtain    automorphic functions associated to a
discrete Fuchsian group.
The interested reader may consult [ibid:page 149] for  explicit
integral equations whose solutions produce
doubly periodic meromorphic functions
with prescribed periods.
With today's use of computers it appears that these integral equations can be used
to get accurate numerical solutions
to   extensive families of doubly periodic functions.
More could have been said about this approach 
to study Riemann surfaces. Let us only mention that 
studies of solutions to differential systems with prescribed monodromy
were  carried out  with great succes in work  by Plemelj
and readers interested in the theory of
fuchsian zeta-functions  should consult articles by Uhler. 

\bigskip

\noindent
{\bf{0.6.1 Fuchsian systems.}}
By elimination one shows that if
$y^n+q_1(x)y^{n-1}+\ldots+q_n(x)=0$ is an irreducible
algebraic equation where
$\{q_\nu(x)\}$  are rational functions of
$x$, then there exists a unique differential operator
\[ 
Q(x,\partial)= g_{n-1}(x)\partial^{n-1}+\ldots+g_1(x)\partial + g_0(x)\tag{*}
\]
where $\{g_\nu(x)\}$ are polynomials without a common factor and
the leading polynomial $g_{n-1}(x)$ is monic and 
every local branch $\alpha(x)$ of a
root to the algebraic equation 
satisfies the homogeneous equation $Q(x,\partial)(\alpha)=0$.
One refers to $Q$ as the associated Fuchsian operator.
In § xx we shall construct such $Q$-operators in some specific examples and
discuss how they can be used to investigate the multi-valuedness of the root
functions.
The operators in (*) belong to the Weyl algebra $A_1({\bf{C}})$
and are quite special because their generic solution spaces
consist of roots to an algebraic equation.
A more extensive class of differential operators appears
when integrals of algebraic root functions are constructed. To give
an example, suppose that
the algebraic equation above has a single-valued branch of a root
function $\alpha(x)$ defined in a neighborhood of the real interval $[0.1]$ in the complex $x$-plane.
Let $\zeta$ be a new complex variable and consider a function
\[ 
F(x,\zeta)= \zeta^m+p_1(\alpha(x))\cdot \zeta^{m-1}+\dots 
p_{m-1}(\alpha(x))\cdot \zeta+ p_m(\alpha(x))
\]
where $\{p_\nu(\alpha)\}$ are some polynomials.
 Suppose that $p_m(\alpha(x))\neq 0$ when $x$ belongs to
 the real interval $[0,1]$. Then there exists a small open disc $D$ centered at
 $\zeta=0$ and an anlytic function $g(\zeta)$ in this disc defined by
 \[
 g(\zeta)= \int_0^1\frac{dx}{ F(x,\zeta)}
 \]
It turns out that there exists a differential operator
$G(\zeta,\partial_\zeta)$ in the Weyl algebra
such that
$G(g)=0$ holds in $D$  and from this one can easily show  that
$g$ extends to a - in general multi-valued - analytic function
in an open complement of a finite subet of the projective
$\zeta$-line.
Moreover, the differential operator $G$ has a special form, i.e. it is
a Fuchsian operator  which is  used to investigage properties
of the multi-valued extension of the locally defined $g$-function.
 \bigskip
 

\centerline{\bf{0.7 Dynamical systems.}}
 \bigskip
 
\noindent
Riemann surfaces and algebraic function fields  appear in
systems of non-linear differential equations and lead to
dynamical considerations. This is an extensive subject
which will 
not be considered here.
Let us only   remark that 
Poincare's thesis from 1879 
opened a new era in mathematics.
An example is the article is \emph{Les fonctions
fuchsiennes et l'équation $\Delta(u)=e^u$}
where Poincaré proved that this non-linear second order differential equation has a 
subharmonic solution with prescribed
singularities on every closed Riemann surface attached to an algebraic equation, a
work which 
started  potential theoretic analysis
on complex manifolds.
Let us describe one
example of a differential system which
appears in
the article \emph{xxxx} by
Sonja Kovalevsky from 1889. Here
one encounters a differential system of six
independent functions real-valued functions which depend on the time variable $t$

\[
 xxxx
\]
In [ibid] it is proved that there exist four integrals to this system, i.e
there exist real  constants $x,x,x$ such that
the following four algebraic equations hold:
\[
xxx
\]
\medskip

\noindent
Starting from this Kovalevsky
proved that  the solution to the differential system
 are expressed by
$\theta$-functions of the second kind
which means that one has
constructed specific 
trancendental functions via integrals of algebraic functions
of two variables. To attain this Kovalevsky
uses the algebraic structure in the equations to
pass into the complex domain  where   the time variable $t$ takes
complex values.
The physical siginficance   is that the
equations above  determine the  motion for
a non-symmetric gyroscope which rotates around a fixed point in
${\bf{R}}^3$
where gravity is the sole external force.
A notable fact is that  Kovalevsky's gyroscope   
is the sole
non-symmetric example  where
the Euler equations of a rotating body in Newton's gravitational field
can be solved by quadrature.
The uniquess was proved by Lyapounov in 1892 and
the proof employs geometric constructions which ressemble those which
appear for Riemann surfaces.



\newpage



\centerline {\bf{0.8 Periods of abelian integrals.}}


\bigskip

\noindent
Let us finish this introduction by describing a specific result from
Abel's work which  has a geometric flavour.
Consider an equation of the form
\[ 
y^2=x(x-1)(x-\beta)
\] 
where the complex number
$\beta$ differs from 0 and 1.
This yields a Riemann surface
$X$
where $g=1$
and a global holomorphic 1-form is given
by
\[ 
\frac{dx}{y}
\]
Let $\gamma^*_1,\gamma^*_2$ be a canonical basis for the homology 
which gives the two period numbers
\[
w_k=\int_{\gamma^*_k}\,\frac{dx}{y}
\]


\noindent
Next,
consider a complex line $\ell$ in
the 2-dimensional complex $(x,y)$ space
defined by some equation
\[ 
\alpha x+\beta y+\gamma=0
\]
When  $\beta\neq 0$.
we see that $X\cap \ell$ consists of
three points whose $x$-coordinates
are roots of the cubic equation
\[
x(x-1)(x-\beta)=\frac{1}{\beta^2}(\alpha x+\gamma)^2\tag{1}
\]
One can solve this equation by Cardano's formula. But Abel took
another point of view to describe the three intersection points.
Suppose the line is chosen so that (1) has
three simple roots $\{x_\nu\}$ which
determine
three points $p_1,p_2,p_3$ on $X$ where
\[ 
p_\nu=(x_\nu,-\frac{1}{\beta}(\alpha x_\nu+\gamma)
\]
Next, starting at the point 
$p_*=(0,0)$ on $X$ we
choose simple curves
$\{\gamma_\nu\}$ which join  $p_*$ with $\{p_\nu\}$
and integrate $\omega$ along each such $\gamma$-curve.
With these notations the following  result is proved in [Abel]:

\medskip

\noindent
{\bf{Theorem.}}
\emph{There exists a constant $C$ which depends on $X$ only such that
for every line $\ell$ as above one has an equation}
\[
\sum_{\nu=1}^{\nu=3}\int_{\gamma_\nu}\, \frac{dx}{dy}= C+m_1\cdot w_1+m_2\cdot m_2
\tag{*}\]
\emph{where $m_1,m_2$ is a pair of integers.}
\medskip

\noindent
{\bf{Remark.}}
This equation implies that
two intersection points determine the third.
Let us for example see why
$p_3$ is determined by $p_1$ and $p_2$.
Choose the line $\ell^*$ which 
passes through $p_1$ and $p_2$ and let $p_3^*$ be the third point
in $\ell^*\cap XD$.
The equation applied to $\ell^*$ gives
a  pair of integers $m'_1,m'_2$
and an equation
\[
\sum_{\nu=1}^{\nu=2}\int_{\gamma_\nu}\, \frac{dx}{dy}
+\int_{\gamma}\,  \frac{dx}{dy}=C+m'_1+m'_2
\] 
where $\gamma$ is a curve from $(0,0)$ to $p^*_3$.
The composed curve
$\gamma_3^{-1}\circ \gamma$ joins $p_3$ with $p^*_3$
and subtracting the equations for the two lines
the constant $C$ disappears and we get
\[
\int_{p_3}^{p_3^*}\,  \frac{dx}{dy}=(m'_1-m_1)w_1+
(m'_2-m_2)w_2
\]
As explained in § xx this implies that $p_3^*=p_3$
which shows that two intersection points determine the third
via Abel's addition theorem.
 A notable fact is 
the equation (*) in the
Theorem  not only is necessary, but also gives a sufficient condition in order
that three given points on the elliptic curve stay on a line.
This 
could have been
established by
algebraic computations  based upon Cardano's formula
but Abel's method has a much wider range and
applies to  
intersection points of the 
elliptic curves with algebraic curves of arbitrary high degree.
The special case above has an 
obvious conceptual merit and
passing to algebraic curves of arbitrary degree $s\geq 3$ 
Abel proved the following result:


\medskip


\noindent
{\bf{Theorem.}}
\emph{Let $s\geq 3$ and 
$p_1,\dots,p_{3s}$ are $3s$  distinct points on the elliptic curve.
Then they all belong to an algebraic curve of degree
$s$ if and only if there exists a pair of integers $m_1,m_2$ such that}
\[
\sum_{\nu=1}^{\nu=3s}\int_{\gamma_\nu}\, \frac{dx}{dy}= 
C\cdot s+m_1\cdot w_1+m_2\cdot m_2
\tag{*}
\]
\emph{Where $\{\gamma_\nu\}$ are curves on $X$ 
which join $(0,0)$ to
$\{p_\nu\}$ and $C$ the constant of the preceeding theorem.}
\bigskip

\noindent
{\bf{A result about hyperelliptic curves.}}
Let $g\geq 1$ and consider a  Riemann surface $X$ defined by
\[
 y^2=p(x)
 \] 
where $p(x)$ is a monic polynomial of
degree $2g+2$
with simple zeros $\{c_\nu\}$.
As we shall explain later on 
$X$ has genus $g$ and 
a basis for $\Omega(X)$ consists of   the 1-forms
\[ 
\frac{x^kdx}{y}\quad\colon\quad 0\leq k\leq g-1
\]


\noindent
Let us now consider polynomials $Q(x)$ of the form
\[ 
Q(x)=x^{g+1}+ a_gx^g+\ldots+a_1x+a_0
\]
where $\{a_\nu\}$ is an arbitary $(g+1)$-tuple of complex numbers.
As will be explained in § x the number of intersection of the two curves
$\{Q=0\}$ and $\{u^2-p(x)=0\}$ when $x$ is finite 
consists of $2g+1$ points on $X$ counted with multplicity.
Next, let $\{\xi_\nu=(x_\nu,y_\nu)\}$
be some  $g+1$-tuple of points on
$X$ where the $x$-coordinates are finite. Above 
we dispose $g+1$ many $a$-parameters and they   can be choosen so that
the intersection above contains $\xi_1,\ldots,\xi_{g+1}$
together with another $p$-tuple of points $\{\xi_{g+2},\ldots,\xi_{2g+1}\}$ on $X$.
For the generic choice of the
first $(g+1)$-tuple of $\xi$-points the
$a$-tuple is unique  and the last
$g$-tuple
depends only upon  the assigned  $(g+1)$-tuple. Set
\[ 
\eta_j= \xi^*_{g+1+j}\quad\colon\quad 1\leq j\leq g
\] 
where the *-sign means that when
$\xi_{g+1+j}= (x,u)$ in ${\bf{C}}^2$ then
we take the *-marked point changes $u$ to $-u$, i.e.
the $\eta-$-point becomes $(x,-u)$.
With these notations Abel proved the following:

\medskip

\noindent
{\bf{Theorem.}}
\emph{There exists a constant $C$ such that the following hold for
each $\omega\in\Omega(X)$ and every
tuple
$(\xi_1,\ldots,\xi_{g+1})$} 
\[
\sum_{k=1}^{k=g+1}\,\int _{\xi_*}^{\xi_\nu}\, 
\omega=C+ \sum_{j=1}^{j=g}\int_{\xi_*}^{\eta_j}\omega
\]
\medskip

\noindent
{\bf{Remark.}}
As explained above
the $\eta$-points are algebraic functions of
$\xi_1,\ldots,\xi_{g+1}$
and since we have taken a sum of integrals in the right hand side
it is determined by the unordered $g$-tuple of $\eta$-points on $X$.
The theorem  constitutes an addition formula since it asserts 
that the sum of line integrals over a family of $g+1$ curves is equal to
a sum over
 $g$ curves.
When $g=1$  
the theorem above corresponds to an equation which  was
established by Euler and presumably inspired Abel while he
developed the theory of general hyperelliptic equations.
The case $g=2$ can solved
rather explicitly and the  reader may consult
[Appel-Goursat: page 423-425] for detailed formulas 
expressing Abel's addition theorem  for hyper-elliptic curves.

\bigskip




\centerline{\emph{Exercise.}}
\medskip



\noindent
We
pose the exercise below in two variables and  remark  that
Abel proved a similar     result for
any number of variables. By 
"contemporary
terminology"  it means that if $T\subset{\bf{C}}^n$
is a hypersurface with $k$ irreducible components defined by
irreducible polynomials $P_1,\dots,P_k$ in
${\bf{C}}[z_1,\dots,z_n]$,
then
the integral cohomology of order one over the  open
set
${\bf{C}}^N\setminus T)$ is a free abelian group
generated by
the $k$-tuple of $\partial$-closed 1-forms
$\{\frac{\partial P_\nu}{P_\nu}\}$.
Now we give the exercise:
Let $R(x,y)$ and $Q(x,y)$ be a pair of
rational functions in two variables.
Since the polynomial ring ${\bf{C}}[x,y]$ 
is a unique factorisation domain
each rational funtion is the quotient of two polynomials with no common factor.
Suppoose that the denomantors of $r$ and $W$ are non-zero at the origin in
${\bf{C}}^2$ and
set 
\[
\Phi(x,y) =
 \int_0^x\,R(\zeta,y)\,d\zeta+
 \int_0^y\,Q(x,\eta,y)\,d\eta+
 \] 
 which is defined when $(x,y)$ stays close to the originö
 Assume also that the differential 1-form
 $R dx+ Qdy$
 is exact which means that
 \[
\frac{\partial R}{\partial y}=
 \frac{\partial Q}{\partial x}
\]
Show that 
there exists a unique pair $F,P$ where
$P$ is a polynomial with $P(0,0)=1$ and
$F$ a rational function such that
\[
\Phi(x,y)= R(x,y)+\log P(x,y)
\]
holds in a neighborhood if the origin.



\bigskip

\centerline{\emph{Further comments on Abel's work.}}
\bigskip

\noindent
Prior to the cited article in the introduction 
we recall that 
Abel  proved that
the general algebraic  equations of order five cannot be solved by 
roots and radicals. The  proof uses
the symmetric group with 120 elements
and 
Abel also
introduced the general notion 
of field extensions  with
arbitrary degree of transcendency.
These revolutionary 
algebraic methods appear frequently 
in Abel's later work.
For an  expositions of  
Abel's contributions in mathematics the reader can consult
the book \emph{The  Abel Legacy} 
published at  the innaguration of the  Abel Prize which
since 2004 is considered as one the most prestigous prizes in mathematics.
In my article from [ibid]
comments are given on Abel's proof that the general algebraic equation
of degree 5 cannot be solved by roots and radicals
where an example is $x^5+x+1=0$. This was proved in 1823
and appears in the article [Abel] 
which was published shortly after his decease.
The demonstration is not via a 
"single example" but  derived from an explicit over-determined system of
linear equations which
exhibits  when a given algebraic equation of degree five cannot be solved by
roots and radicals.
For equations of higher order the
strategy in Abel's proof leads to
complicated
linear systems of high order
since the symmetric group of $n$ many elements increases very fast.
Two years after Abel's decease,
Galois discovered that
group theory
leads to criteria fror
non-solvability which is 
more transparent and Galois theory has therefore  become
a subject in many text-books. However, Abel's original proof has
the merit that today's use of computers can be applied
to analyze his linear systems and in this way
get decide when an specific algebraic equation has
solutions by roots and radicals in situations where the
its associated Galois group is not easy to handle.

























\newpage

\centerline{\bf{I. Algebraic functions and Riemann surfaces.}}

\bigskip

\noindent
In this section we 
demonstrate how algebraic function fields
determine a compact Riemann surface.
Before this is done in § 1.3 and § 1.4 we
discuss the genus and the degree of meromorphic functions on
a compact Riemann surface.


\bigskip





\centerline{\bf{1.1 The genus number.}}

\medskip

\noindent
Denote
by
$\mathfrak{M}(X)$ the field of meromorphic functions on $X$
on a compact one-dimensionsal complex manifold.
A major result
is that  $\mathfrak{M}(X)$ is
a finitely generated
field extension over $\bf{C}$
whose degree of trancendency is equal to one. 
To prove this  one must 
establish the existence of 
an ample family of meromorphic functions on an
"abstract" compact Riemann surface.
This is done in § 1 using  sheaf theory where
the
crucial result is
that
the cohomology space $H^1(X,\mathcal O)$ is a finite dimensional
complex vector space when
$\mathcal O$ is the sheaf of
holomorphic functions on $X$. 
This gives
the integer
\[ 
g=\dim_{\bf{C}}\,H^1(X,\mathcal O)\tag{*}
\]
It turns out that $g$
is  a topological
invariant of $X$. Namely, $X$ is  an oriented
compact manifold of real dimension two and 
a wellknown result in topology  asserts that
$X$ is homeomorphic to a sphere where
a finite number of handles attached.
Denote this number  by
$\text{gen}(X)$. With these  notations one has the 
equality:
\[ 
g=\text{gen}(X)\tag{**}
\]
The quickest proof is described in § xx using
an induction over $g$.
However, more insight is obtained by a
duality  result which shows that
$H^1(X,\Omega)$ in a canonical way is isomorphic to the dual
of the finite dimensional vector space
$H^0(X,\Omega_X)$ which consists of globally defined
holomorphic 1-forms, or as one says abelian differentials of the first kind on $X$.
The proof  is given in § 2.
If we admit this duality one  derives
(**) as follows: Let $\Omega_X$ denote the sheaf of holomorphic
functions. In local charts every holomorphic function $f$
has a primitive which gives  an
exact sequence of sheaves:
\[ 
0\to {\bf{C}}_X\to\mathcal O_X\overset{\partial}\to \Omega_X\to 0
\]
By the maximum principle a globally defined holomorphic function on
 the compact manifold $X$ is reduced to a constant which
means that $H^0(X,\mathcal O_X)$ is reduced to a
1-dimensional complex vector space. Hence
the  construction of
long exact sequences in   sheaf theory yields
an exact sequence of finite dimensional complex vector spaces:
\[
0\to H^0(X,\Omega_X)\to 
H^1(X,{\bf{C}}_X)\to H^1(X,\mathcal O_X)\to
H^1(X,\Omega_X)\to H^2(X,{\bf{C}}_X)\to 0\tag{***}
\]
Since $X$ is an oriented and compact real manifold of dimension
two, 
Poincaré duality shows that
$H^2(X,{\bf{C}}_X)$ is 1-dimensional. Moreover, the duality
in § XX will show that 
$H^1(X,\Omega_X)$ is isomorphic to the dual of
the  1-dimensional space $H^0(X,\mathcal O_X)$
and therefore also 1-dimensional.
Counting dimensions in (***) it follows that
\[
\dim(H^1(X,{\bf{C}}_X))=
 \dim(H^0(X,\Omega_X))+\dim(H^1(X,\mathcal O_X))\tag{1}
 \]
Next, by the duality above 
$\dim(H^0(X,\Omega_X))$ is isomorphic to  the dual vector space of
$H^1(X,\mathcal O_X)$ so (1) and the definition of $g$ gives the equality
\[
\dim(H^1(X,{\bf{C}}_X))=2\cdot g\tag{2}
\]
which  by  general topology  gives 
(**).




\medskip

\noindent 
{\bf{Remark.}} When  $X$ and $Y$ are two compact Riemann
surfaces with the
same genus  they are homeomorphic as manifolds.
But this does not imply that
they are biholomorphic as complex manifolds.
An exception is the case $g=0$
when $X$ always is biholomorphic with the projective line
${\bf{P}}^1$ which is identified with the Riemann sphere where
the point at infinity is added to the complex $z$-plane.
Here the field
$\mathfrak{M}({\bf{P}}^1)$
is equal to the field of rational functions of $z$.
If $g=1$
then  $X$ is 
homeomorphic to a torus
${\bf{T}}^2$ and in
§ XX  we
classify the conformal equivalence classes
of such compact Riemann
surfaces.


\bigskip



\centerline{\emph{A formula for $g$}}
\medskip


\noindent
The results above enable us
to compute
$g$ starting from  an arbitrary  non-constant meromorphic function $f$ on $X$.
Namely, let $p_1,\ldots,p_k$ be
the set of poles and denote by $\{\mu_f(p_\nu)\}$ the orders of
these poles.
Next, the
1-form $\partial f$  is holomorphic outside
the poles and let $n_+(\partial f)$ denote the number of zeros of $\partial f$ 
counted with their multiplicities.
With these notations one has the equality below referred to as 
the Riemann-Hurwitz formula:
\[ 
g=1+\frac{n_+(f)}{2}-\frac{1}{2}\cdot\sum_{\nu=1}^{\nu=k}(\mu_f(p_\nu)+1)
\tag{1.1}
\]
The proof is given in § X. As an illustration,
consider the
case when $X={\bf{P}}^1$ is the projective line.
Let $p(z)$ be a polynomial of degree $n\geq 1$. It is a meromorphic function 
on $X$ whose pole at the point at infinity has order $n+1$ and zeros of $\partial p$ correspond to zeros of the derivative 
$p'$ so that   $n_+(p)= n-1$. Now (i) gives $g=0$ which reflects  
that ${\bf{P}}^1$ has genus number zero.
A more involved case occurs if we consider the algebraic curve
defined by the equation
\[
y^3+x^3=1\tag{1.2}
\] 
where $x$ and $y$ are independent complex variables.
In § XX  we expain that its closure taken in
the 2-dimensional projective space
${\bf{P}}^2$ yields a non-singular projective curve
which therefore is a compact Riemann surface denoted by $X$.
Here $y$ is a meromorphic function with
three simple poles
and at the  three  points above  $x=0$ where $y$ is a third  root of unity,
one finds that $\partial y$ has zeros of order 2. From (1.1)
we deduce that
$g=1$ which means that $X$ is homeomorphic to a torus.
It is not easy to visualize this and the present author is unable to get
a  picture which  explain why $X$ is homeomorphic with
a torus.
So in the long run
it is essential to carry out calculations with the aid of
theoretical results.
In our example  
the 1-form
\[ 
\omega=\frac{dy}{x^2}
\]
is everywhere holomorphic and $\neq 0$
on $X$ and
in § XX we  construct a pair of simple closed curves
$\gamma_1,\gamma_2$ on $X$ such that  the two line integrals
\[ 
\int_{\gamma_\nu}\, \frac{dy}{x^2}
\] 
are
non-zero and yield a pair of ${\bf{R}}$-linearly independent complex numbers
which 
confirms that
$X$ is a torus.









\bigskip



\centerline {\bf{1.2 The degree of a meromorphic function.}}

\medskip

\noindent
With ${\bf{P}}^1$  considered as a compact complex manifold
a non\vvv constant
meromorphic function $f$ on a compact Riemann surface
$X$ yields
a holomorphic map from 
$X$ onto ${\bf{P}}^1$.
It turns out that
there exists a finite set of points
$a\uuu 1,\ldots,a\uuu k$ in ${\bf{P}}^1$
such that if $Y={\bf{P}}^1\setminus
(a\uuu 1,\ldots,a\uuu k)$, then $f$ yields a locally biholomorphic map from
$ f^{\vvv 1}(Y)$ onto 
$Y$ where each inverse fiber consists of $n$ points in $X$.
The integer $n$ called
the degree of $f$ and is denoted by $\text{deg}(f)$.
This integer is robust in the sense that for 
every complex number $c\in{\bf{P}}$
the  inverse fiber
$f^{-1}(c)$
consists of a finite number of points and counting multiplicities
this number is equal to $n$. To see this one employs the
meromorphic 1-form $\partial f$.
\medskip


\noindent
\emph{1.2.1 The use of Stokes Theorem.}
On a compact Riemann surface $X$
one can perform line integrals of differential 1-forms
in the same way as in open subsets of ${\bf{C}}$.
Let $f\in\mathfrak{M}(X)$
and 
$\{p\uuu k\}$ the finite set of poles.
If $c$ is a complex constant we consider
$g=f-c$ which has the same poies as $f$
and let  $\{ q_j\}$ be the zeros of $g$, i.e. points in $X$ where $f(q_j)=c$.
Around the zeros and the poles of $g$
we choose small charts which are biholomorphic 
to open discs
and take their union $U$.
The boundary $\partial U$
consists of a finite set of
disjoint closed curves where each  is a copy of a circle in a chart.
In $X\setminus \bar U$ there exists the 1\vvv form
\[
\frac{\partial g}{g}=
\frac{\partial f}{f-c}
\]
Since $g$  is holomorphic in $U$ this  1\vvv form is closed
and Stokes theorem gives
\[
\int\uuu{\partial U}\, \frac{\partial f}{f-c}=0\tag{1}
\]
In a chart with local coordinate $z$
around a zero of  $f-c$ with multiplicity $e$ we have
\[
\frac{\partial f}{f-c}=\frac{f'(z)}{f(z-c)}\cdot dz=
e\cdot \frac{dz}{z}+\quad\text{a holomorphic form}
\]
Hence the line integral along a small circle centered at $z=0$ has value $2\pi i\cdot e$.
Next, consider a chart around a pole of some order $e$.
Here
\[
\frac{\partial f}{f-c}=
\vvv e\cdot \frac{dz}{z}+\quad\text{a holomorphic form}
\]
where  the sign is reversed.
Now (1) implies that the number $n$ of zeros counted
with multiplicity is equal to the number of poles counted with their
order and by definition this common 
integer $n$ is  the degree of 
$f$. This confirms the
robustness of the degree.

\medskip 

\noindent
\emph{1.2.2 Weierstrass points.}
Let $X$ be a Riemann surface where $g\geq 2$.
Then there exists
a finite set of points on $X$
denoted by $\mathcal W(X)$ and for each $p\in \mathcal W(X)$
there exists a non-constant meromorphic function $f$ on $X$ 
which is holomorphic in
$X\setminus\{p\}$ and has a pole of order
$\leq g$ at $p$.
This result is due to Weierstrass and the proof is given in § XX.
The case $g=2$ is of special interest for then the meromorphic function
$f$ has degree two and yields a 2-sheeted covering map from
$x$ onto ${\bf{P}}^1$.


\medskip


\noindent
\emph{1.2.3 An algebraic equation.}
Let $f$ be meromorphic on $X$ with some degree $n$.
A complex number $c$ is called an $f$-critical value if
$\partial f(z)=0$ for some $z\in f^{-1}(z)$. The set of critical points is finite and we let
$\sigma_f$ be the union of these points and the
point at infinity, i,e. we avoid poles on $f$ when we take  the open set
$X\setminus f^{-1}(\sigma_f)$.
For each $z\in{\bf{P}}^1\setminus \sigma_f$
the inverse fiber $f^{\vvv 1}(z)$ is  an unordered $n$\vvv tuple
$x\uuu 1(z),\ldots x\uuu n(z)$ of points in $X$.
Next, 
consider another meromorphic function $\phi$ on $X$
and with a new variable $\lambda$ we set
\[
\Phi(\lambda)= \prod\uuu{k=1}^{k=n}\, 
(\lambda\vvv \phi(x\uuu k(z))
\]
\medskip

\noindent
When $z$ varies in
${\bf{P}}^1\setminus \sigma_f $
the coefficients of the $\lambda$-polynomial are symmetric 
polynomials of the $n$-tuple
$\{\phi(x_k(z))\}$  which entails that
\[ 
\phi(\lambda) =\lambda^n+r_{n-1}(z)\lambda^{n-1}+\ldots+ r_1(z)\lambda+r_0(z)
\] 
where
$\{r_j(z)\}$ are ordinary rational functions of the single complex variable
$z$. Returning to $X$ it follows that
\[
\phi^n+ r\uuu {n-1}(f)\cdot 
\phi^{n\vvv1}+\ldots+r_1(f)\phi+r_0 (f)\tag{1}
\] 
Since such an equation exists for every $\phi\in\mathfrak{M}(X)$ it follows 
from  
elementary algebra that the field 
$\mathfrak{M}(X)$ is an algebraic extension of the subfield
${\bf{C}}(f)$ formed by rational expressions of
the meromorphic function $f$ whose dimension as a complex vector space over
${\bf{C}}(f)$ is equal to
$\text{deg}(f)$.
Here
${\bf{C}}(f)$ can be identified with the standard field 
${\bf{C}}(z)$ of rational funtions of a single variable
and one says therefore that
$\mathfrak{M}(X)$ is an algebraic function field of one variable.





 









\bigskip


\centerline
{\bf{1.3 Algebraic function fields}}


\medskip

\noindent
An algebraic function field $K$ over ${\bf{C}}$ is an abstract field which contains
${\bf{C}}$ as a subfield with  
 degree of trancendency equal to  one and 
generated by a finite number of elements
 $k_1,\ldots,k_m$. This   means that
 every $k\in K$
 can be expressed as  quotient of polynomials in
 $k_1,\ldots,k_m$ with coefficients in
 ${\bf{C}}$. Elementary algebra teaches that when
 $K$ is such a field and 
 $\xi\in K\setminus {\bf{C}}$
then  there exists   $\eta\in K$
 such that
 $K$ is generated by $\eta$ and the field ${\bf{C}}(\xi)$ whose
 elements are rational functions in $\xi$ with complex coefficients.
 Here $\eta$ satisfies an equation
\[
 \eta^m+r_{m-1}(\xi)\eta^{m-1}+\ldots+ r_1(\xi)\eta+r_0(\xi)=0
 \]
 where $\{r_j(\xi)\}$ belong to ${\bf{C}}(\xi)$
 and each $k\in K$ can be written  as
 \[
  k=q_{m-1}(\xi)\eta^{m-1}+\ldots+ q_1(\xi\eta+q_0(\xi)=0
 \] 
 where $\{q_j(\xi)\}$ is a unique  $m$-tuple in
 ${\bf{C}}(\xi)$.
 Moreover, 
 the polynomial 
 in a new indeterminate variable $t$ given by
 \[
P(t,\xi)=t^m+r_{m-1}(\xi)t^{m-1}+\ldots+ r_1(\xi)+r_0(\xi)
 \]
 is irreducible in the polynomial ring
 of   $t$ over the field
 ${\bf{C}}(\xi)$.
This is  be expressed by saying that if
$K_*={\bf{C}}(z)$ is the standard field of rational functions in one
variable, then each algebraic function field
is isomorphic
to a field
\[ 
\frac{K_*[t]}{(P)}
\] 
where $(P)$ denotes the principal ideal generated by an irreducible polynomial in
$K_*[t]$. Here we  used  that 
$K_*[t]$ is an euclidian ring which 
implies that this $K_*$-algebra is a  unique factorisation  domain
and hence  onre has  a precise meaning for  a polynomial $P[t)$ to be  irreducible.
\medskip

\noindent
{\bf{Remark.}} When the algebraic function field $K$ is given
we can choose a  trancendental element $\xi$ in many ways.
Once $\xi$ is chosen we obtain the finite field extension
where ${\bf{C}}(\xi)$ appears as a subalgebra and $K$ regarded as a vector space over
this subfield has a finite dimension. More precisely one has the equality
\[
\dim_{{\bf{C}}(\xi)}\, (K)=
\text{deg}(\eta)
\] 
where $\eta$ is a primitive element whose minimal equation (*) has degree $m$.
Let us also remark that if a trancendental elment $\xi$ is chosen
then there is a whole family of primitive $\eta$-generators, i.e. for every
$\eta\in K$ whose minimal equation (1) has 
a degree which equals the dimension of $K$ as a vector space  over
${{\bf{C}}(\xi)}$ yields a primitive element 
in $K$ with respect to the chosen trancendental $\xi$-element.
Finally, two  algebraic function fields $K_1$ and $K_2$ 
are isomorphic if there exists a ${\bf{C}}$-algebra isomorphism
 between them.
With this kept in mind one has the following: 


 
 

\medskip

\noindent
{\bf{1.3.1 Theorem.}}
\emph{There is a 1-1 correspondence between the family of algebraic function fields in one variable and
the family of compact Riemann surfaces.}
\medskip

\noindent
Above a pair of 
Riemann surfaces are identified  when they are bi-holomorphic.
Several  steps are needed to prove (1.3.1).
 First Weyl's theorem shows that 
$\mathfrak{M}(X)$ is an algebraic function field for every
compact Riemann surface. Next, let $X_1,X_2$ be a pair of
biholomorphic Riemann surfaces and let 
$\rho\colon X_1\to X_2$ be a  biholomorphic mapping.
Then $\mathfrak{M}(X_1)\simeq \mathfrak{M}(X_2)$
since $\rho$ gives the algebra isomorphism which sends
$f\in \mathfrak{M}(X_2)$ to the meromorphic function on $X_1$ defined by
\[ 
f^*(x_1)= f(\rho(x_1)\quad\colon\quad x_1\in X_1
\]
There remains to show
show that
for every algebraic function field $K$ there exists a compact Riemann surface
$X$ such that $K\simeq\mathfrak{M}(X)$. 
Moreover we must show that if $X_1$ and $X_2$ are two Riemann surfaces where
the algebraic function fields 
$\mathfrak{M}(X_1)$ and $\mathfrak{M}(X_2)$ are isomorphic  then
$X_1$ and $X_2$ are
biholomorphic.
To prove we consider  an arbitrary 
algebraic function field $K$.
A valuation map on $K$ is
an injective algebra homomorphism
\[
\rho\colon\ K\to {\bf{C}}\{ t\}[t^{-1}]\tag{1}
\]
where the right hand side is the standard field of germs of meromorphic functions
at the origin with $t$ regarded as a complex variable. 
In addition one requires that $\rho$ is non-degenerated in the sense that there exists some 
$k\in K$ such that
\[
\rho(k)= t+\sum_{\nu=2}^\infty\, c_\nu \cdot t^\nu\tag{2}
\]
i.e. this germ is holomorphic and
its $t$-derivative is non-zero when $t=0$.
The  $\rho$-map defines a valuation on $K$ as follows:
Each 
non-zero element $k$ gives the meromorphic germ  $\rho(k)$ and we find
the unique integer $\rho_*(k)$ such that
\[
\rho(k)= t^{\rho_*(k)}\cdot \phi(t)
\] 
where $\phi(t)$ is a unit in the local ring
${\bf{C}}\{ t\}$, i.e its constant term is $\neq 0$.
Let $\mathcal V(K)$ denote the family of all valuations maps on $K$.
It turns out that $\mathcal V(K)$ corresponds to 
points in a compact Riemann surface $X$ and that
$K\simeq \mathfrak{M}(X)$
where
each point $x\in X$ yields
a valuation since
there exists  a local chart around $X$ with a coordinate $t$
so that
every  $f\in\mathfrak{M}$ has a series expansion at $x$ 
expressed by a an element in 
$\rho_f(t)\in{\bf{C}}\{ t\}[t^{-1}]$. By analyticity the map $f\to \rho_f(t)$ is injective which
clarifies the1-1  correspondence between points on $X$ and valuation maps on
$\mathfrak{M}(X)$.

\medskip

\noindent
So the main burden is to
prove  that there exists  
an ample family of valuations on a given  algebraic function field $K$ and 
explain how these 
valuations fabricate points on a Riemann surface.
This is done in § 1.4 below.



















\bigskip


\centerline{\bf{1.4 Algebraic curves.}}

\medskip

\noindent
Recall  that the polynomial ring
${\bf{C}}[x,y]$ in two variabes is a unique factorisation domain.
Let $n\geq 2$
and  consider an irreducible polynomial
\[ 
P(x,y)= y^n+q_1(x)y^{n\vvv 1}+\ldots+q_{n-1}(x)y+q_n(x)\tag{1}
\]
To $P$ corresponds the algebraic function field $K$ whose elements are 
\[ 
k=r_0(x)+r_1(x)y+\ldots+ r_{n-1}(x) y^{n-1}
\quad\text{where} \quad r_0,\ldots,r_{n-1}\in 
{\bf{C}}(x)\tag{2}
\]

\noindent
Next, we get  the algebraic curve $S$ in ${\bf{C}}^2$ defined by
$P=0$. 
It has a closure in
the projective space ${\bf{P}}^2$
whose homogeneous coordinates are $(\zeta_0,\zeta_1,\zeta_2)$.
Points in the $(x,y)$-space are represented by $(1,x,y)$.
The hyperplane at infinity is
$\{\zeta_0=0\}$
and points $(x,y)\in S$
converge to this hyperplane
when $|x|\to +\infty$ which yields the closure $\bar S$ in
the compact manifold
${\bf{P}}^2$.
Tbe boundary $\partial S=\bar S\setminus S$
is a finite set of at most 
$n$ points. As an example, suppose that $\deg q_\nu\leq \nu$
hold for the $q$-polynomials  in (1)
For each $1\leq \nu\leq n$
we denote by $c_\nu$  the coefficient of $x^\nu$ in $q_\nu(x)$.
Now
\[ 
P^*(x,y) = y^n+c_1xy^{n-1}+\ldots +c_{n-1}yx^{n-1}+ c_nx^n
\]
is a homogeneous polynomial and
the fundamental theorem of algebra entails that
\[ 
P^*(x,y)=\prod_{k=1}^{k=m}\, (y-\beta_k x)^{e_k}
\] 
where $\{\beta_k\}$ are distinct complex numbers and
$e_1+\ldots+e_m=n$.
Then
$\partial S$ consists of the $m$-tuple points 
$(0,1,\beta_1),\ldots,
(0,1,\beta_m)$.
The case where $\text{deg}(q_\nu)<n$ for each $\nu$ is not excluded in which case 
$P^*(y)=y^n$ and $\partial S$ is reduced to the single point
$(0,1,0)$.

\medskip

\noindent
{\bf{1.4.1 Regular points on $S$}}.
Let us restrict the attention to the affine curve $S$.
To analyze this affine curve we first consider the polynomial 
\[ 
P'_y(x,y)= ny^{n-1}+(n-1)q_1(x) y^{n-2}+\ldots+ q_{n-1}(x)
\]
and let us recall the following
from Euclides' algebra:
\medskip

\noindent
{\bf{1.4.2 The
discriminant polynomial.}}
By assumption $P$ is irreducible in
the polynomial ring
$K[y]$ in the single variable $y$ where
$k$ denotes the field ${\bf{C}}(x)$.
It follows by euclidian divisions that
there exists a unique pair $A(y),B(y)$ in $K[y]$ such that
\[ 
A(y)\dot P(x,y)+ B(y)\cdot P'_y(x,y)=1
\]
where the degree of the $y$-polynomial $A$ is at most $n-1$ and that of
$B$ at most $(n-2)$.
Next, we find a common factor for the denominstors in
the $K$-coefficients of these two $y$-polynomials whch yields
a unique monic polynomial $\delta(x)$
in ${\bf{C}}[x]$ such that
one has the equation
\[
A_*(x,y)\dot P(x,y)+ B_*(x,y)\cdot P'_y(x,y)=\delta(x)\tag{1.4.2}
\]
where $A_*$ and $B_*$ now are polynomials in $x$ and $y$
which both are primitive with respect to $x$. For example, one has
\[ 
A_*(x,y)= a_{n-2}(x)y^{n-2}+\ldots a_1(x(y+a_0(x)
\]
where the $x$-polynomials $\{a_k(x)\}$ have no common
factor.
We refer to $\delta(x)$ as the discriminant polynomial of $P$.
\medskip

\noindent{\bf{1.4.3 Root fiunctions.}}
For each fixed $n$ the fundamenntal theorem of algebra
yields an $n$-tuple of roots to the equation $P(y,x)=0$ and we can write
\[
P(y,x)= \prod_{k=1}^{k=n}\, (y-\alpha_k(x))
\]
From (1.4.2) we see that
the roots are all simle if and only if
$\delta(x)\neq 0$.
The finite set $\{\delta(x)=0\}$ is called the discriminant locus
so for each $z$ in the open and connected set
${\bf{C}}\setminus \delta^{-1}(0)$
we find the unordered $n$-tuple of simple roots.
As explained in § XX they give rise to germs of analytic functions of
$x$ and can be extended to multi-valued analytic functions in
${\bf{C}}\setminus \delta^{-1}(0)$.
By analyticity each new local bracnh is again a root.
For example, start at some point $x_0\in{\bf{C}}\setminus \delta^{-1}(0)$
and pick one root
$\alpha_1(x_0)$ which to begin with  gives an analytic function
$\alpha_1(z)$ in a small open disc centered at $z_0$.
It is now extended in the sense of Weierstrass
and the multi-valued function produces a finite set of local branches
at $z_0$.
The fact that $P$ from the start is irreducible entails that
the local branches under all possible the analytic continuations of
$\alpha_1$
along closed curves in
${\bf{C}}\setminus \delta^{-1}(0)$
which start and finish at $z_0$, will
produce local branches of all roots.
The conclusion is that
the set
\[ S_*= S\setminus \delta^{-1}(0)
\] 
is connected and the projection $\pi(x,y)=x$
restricts to an $n$-sheeted covering map from
$S_*$ onto ${\bf{C}}\setminus \delta^{-1}(0)$.
Moeover, since the root functions are analytic it follos that
$S_*$ appears as a 1-dimensional complex submanifold of
${\bf{C}}^2\setminus \delta^{-1}(0)$. Finally, by
continuity
of roots the closure of $S_*$ taken in
${\bf{C}}^2$ is equal to $S$.
\medskip

\noindent
{\bf{Remark.}}
The claims made above are classic and exposed in many text-books.
We remark only that this was the starting point for Riemann to construct
Riemann surfaces and that Weierstrass extended the
ressukt above to polynomials in $y$ which may depend upon
several $x$-variables. But in this case the discrimant locus is
a hypersurface in a multi-dimensional complex vector space
so
the properties of the algebraic hypersurface
$P^{-1}(0)$ when
$P= P(x_1,\ldots ,x_n,y)$ is an irreducible polynomial of $n+1$
many variables is more involved
and goes far beyond the material in these notes. Let us only mention that
the subsequet construction for curves were extended by
Zariski to the case of surfaces, i.e. when $n=2$
and
for arbitrary $n\geq 3$ a so called desingularisation of
the algebraic hypersurface
$P^{-1}(0)$ was established by Hironka in 
the article \emph{xxx} from 1962.
\medskip

\noindent
{\bf{1.4.4 The construction of local charts.}}
let  $p=(x_*,y_*)$ be a point in $S$.
Consider the local ring 
$\mathcal O={\bf{C}}\{x-x_*\}$
of germs of analytic functions in the complex $x$-variable at $x_*$.
Now $P(x,y)$ is an element in the polynomial ring
$\mathcal O[y]$ which by
elementary algebra is a so called unique factroisation domain.
it follows that there exists a unique factorisation
\[
P(y,x)= q_*(x,y)\cdot \prod_{k=1}^{k=r}\,\phi_k(x,y)
\]
where $q_*(x_*,y_*)\neq 0$
while $\{\phi_k\}$ are 
irreducible Weierstrass polynomials in $y$ with coefficients 
$\mathcal O$.
It means that each $\phi_k$ is of the form
\[
\phi_k(y,x)= y^{e_k}+\rho_{1,k}(x)\cdot y^{e_k-1}+\ldots+
\rho_{e_k,k}(x)
\]
where the $\rho$-functions belong to $\mathcal O$ and
all vanish at
$x=x_*$.
So in a neighborhood of $p=(x_*,y_*)$  the curve
$S$ is defined by common zeros of the $\phi$-functions.
\medskip


\noindent
{\bf{Puiseux charts.}}
Let us fix one $\phi$-polynomial say $\phi_1$.
In a small punctured disc centered at $x_*$ the $y$-polynomial $\phi_1(x,y)$
has $e_1$ many simple zeros
which occur among roots of $P(x,y)$.
As explained in § xx we introduce a new complex variable $\zeta$
and find
an analytic function $A_1(\zeta)$
in a disc of some radius $r_1>0$
centered at $\zeta=0$ such that
\[
q_1(x_*+\zeta^{e_1}, y_*+A_1(\zeta)=0\quad\colon\, |\zeta|<r_1
\]
Moreover, since $q_1$ was irreducible the Taylor series
\[
A_1(\zeta)= \sum_{\nu=1}^\infty  a_\nu\zeta^\nu
\]
is such that
the principal ideal in ${\bf{Z}}$
generated by those integers for which $a_\nu\neq 0$
does not contain any prime divisor of $e_1$.
This entails that the map
\[
\zeta\to  (x_*+\zeta^{e-1},y_*+A_1(\zeta))
\] 
is bijective,  i.e. the open $\zeta$-disc can be identified with
a subset of the given affine curve $S$
where $\zeta=0$ is mapped to $p=(x_*,y_*)$.
In this subset of $S$ we can wirte
\[ 
x=x_*+\zeta^{e_1}\quad\colon\, y=y_*+A_1(\zeta)
\]
It means that one can use $\zeta$ as a local coordinate
and
the image of the $\zeta$-disc constitues a chart in the Riemann surface
$X$  attached to the curve $S$.
We refer to this as a Puiseux chart. It can be constructed for
each $\phi$-function which appears in (1.4.4 *).
\medskip

\noindent
{\bf{1.4.5 Riemann's construction.}}
To get a Riemann surface $X$ associated to the curve
$S$
one must separate the Puiseux charts above. in orher words,
Riemann regarded  these charts as disjoint.
So if $r\geq 2$ then $X$ contains $r$ \emph{distinct}  points above
$(x_*,y_*)$.
In this way one gets a complex 1-dimensional manifold $X$
and a map $\rho\colon X\to S$
which is bijective except for those points $p=(x_*,y_*)$ in
$S$ where
more than one irreducible $\phi$-function appears in (1.4.3 *).
\medskip


\noindent
{\bf{1.4.6 Example.}}
Consider the irreducible polynomial
\[
P(x,y)= y^4-x^2(x+1)
\]
At the point $p=(0,0)$ on the curve
$S=P^{-1}(0)$ we get a factorisation
\[
P=\phi_1\cdot \phi_2
\] where
we choose a local bracnh of $\sqrt{1+x}$ so that
\[ 
\phi_1(x,y)= y^2-x\cdot \sqrt{1+x}\quad\colon
\phi_2(x,y)= y^2+x\cdot \sqrt{1+x}
\]
In this way we obtain teo distinct Puiseux-Riemann charts
so on $X$ the map $\rho\colon X\to S$ has an inverse fiber above
the origin which contains two points.
In our special case we notice that
$y$ serves as a local coordinate in each of these charts. Passing to
the Rieann surfsce it means that $y$ has a simple zero in
each of the two Puiseux-Riemann charts. In addition one
finds that $y$ has a simple zero above  $x=1$
and after we have constructed charts above $x0\infty$
we shall be abel to conclude that $y$ as a meromorphic funtion on
$X$ has three simple zeros and a triple pole at
the unique point on $X$ where $x=\infty$.
\medskip

\noindent
{\bf{Remark.}}
The reder shoud be aware of the spearated charts which occur when $r\geq 2$.
                                      one tries to "detect" a Riemann surface
by drawing pictures
the cases when such separated  charts appear
often cause visual problems. So in the long run it
is not only conventient but more or less necessary to perform
local calculations which lead to the
complete description of Puiseux-Riemann charts
above singular points on the affine curve $S$.
\bigskip


\noindent
{\bf{1.4.7  The passage to infinity.}}
There remains to construct charts around points in
$\partial S$. In § 1.4.x we explain how this
is reduced to the affine case above
where the strategy is to
perform a suitable transformation of
${\bf[P})^2$.
But let is first give some
examples to illustrate the calculations. 
Consider the polynomial 
\[ 
P(x,y)= y^3-x^6-1
\]
When  $|x|$ is large we have $|y|\simeq |x|^2$
which means that the $y$-coordinate tends faster to
infinity than the $x$-coordinate. So $\partial S$ 
is reduced to the single point $p^*=(0,0,1)$.
In ${\bf{P}}^2$ we have local coorfionstes
$(\zeta,\eta)$ around $p^*$ which corresponds to points
$(\zeta,\eta)$. When $\zeta\neq 0$ 
we are outside the hyplerplane at infinity and have
\[
 x=\frac{\eta}{\zeta}\quad\colon\, y=\frac{1}{\zeta}
\]
So the equation $P=0$ means that
\[
\zeta^{-3}=\frac{\eta^6}{\zeta^6}-1\implies
\zeta^3=\eta^6-\zeta^6
\]
The equation $\zeta^3+\zeta^6-\eta^6=0$
corrsspinds to a union of three zero sets
expressed by three functions $\phi_0,\phi_1,\phi_2$
where
\[ 
\phi_k(\zeta,\eta)=\zeta-b_k(\eta)
\]
and $b_k(\eta)$ has a Taylor series
of the form
\[ 
b_k(\eta)= e^{2\pi i k/3}\cdot \eta^2+\text{higher order terms}
\]
The conclusion is that there exists three Puiseux-Riemann charts
and in each chart
we can take $\eta$ as a local coordinate.
Since the  the $b$-functions
have zeros of order two it follos that $y$
gets a double pole in each chart.
Passing to the compact Riemann surface
¨$X$ itmeans that 
the meromorphic function $y$ gets three distinct double poles.
At thes same time we ntoice that in the finite affine part
the $y$-fuynction has six simple zeros which
appear when
$x$ solves the equation $x^6=1$.
So the number of poles counted with multiplicity is equal to the number of
zeros as it should be.
treating $x$ as a meromorphic function we see that it has simple poles in each of the three
Puiseux-Riemann charts arond $p*$.
At thes same time se cencounter three simple zeros ehich correspond to the points
$(0,j_\nu)$ where $j_\nu^3=1$
are 3rd-roots of unity.
Let us also consider the 1-form
\[ 
\omega=\frac{dx}{y}
\]
Since $y$ has a double pole and $x$ a simple pole in the charts around
$p^*$ we see that $\omega$ is holomorphic 
in these charts and also $\neq 0$.
Next, in the finite part $S$ we notice that
$dx=0$ can only occur when $y=0$ 
an this occurs at six points $\{j_\nu,0)\}$
where
$j_\nu^6 =1$. At each of these points$y$ is a local coordinste
and
$x$ has a zero of order three. Hence  the 1-form
$dx$ has a zero of order teo.
We conclude that $\omega$ has six simple zeros.
From this
the Hurwitz-Riemann formula implies that $X$ has   genus four.
\medskip

\noindent {\bf{1.4.8 The curve
$y^3=x(x-1)^2$}}.
Here $|y|^2\simeq |x|$ and this time
$\partial S$ contains three points:
\[ 
p^*_k=(0,1,e^{2\pi i k/3})\quad\colon\, k=0,1,2
\]
We leve it to the reder to verify that
around each $p_k^*$ we get a single Puiseux-Riemann chart and both $x$ and $y$
have simple poles at these three $p^*$-points.
Next, in the finite part
$x$ has a triple zero at $(0,0)$ where $y$ serves as a local coorfinste.
At $(1,0)$ we have a cusp-like sungularity and here
the Pusiuex-Riemann chart has a local coordinate $\zeta$ where
\[ 
x=1+\zeta^3
\quad\colon \quad y= A(\zeta)
\] 
where $A(\zeta)$ has a zero of order two.
Let us then consider the 1-form
\[ 
\omega=\frac{dx}{y^2}
\]
From the above it is holomorhic and $\neq 0$ at the $p^*$-points.
At $(0,0)$
$x$ has a triple zero so $dx$ has a double zero and since
$y$ has a simple zero we conclude that
$\omega$ is holomorphic and $\neq 0$ at $(0,0)$
At $(1,0)$
the reader may verify that
$\omega$ has a double pole.
The result is that the divisor $D$ for which $\mathcal O_D\cdot \omega=\Omega$
has degree
$-2$ and it follows from the Riemann-Hurwitz formula that the genus of $X$ is zero.
If we set
\[ f=\frac{x-1}{y}
\] then $∞f$ is a meromorphic function and
from the above
we see that it is holomophic and $\neq 0$ at the $p^*$-points
while it has a simple  pole at $(0,0)$ and a simple zero at $(1,0)$.
Therefore $\mathfrak{M}(X)$ is reduced to the field
${\bf{C}}(f)$ which means that both $x$ and $y$ can be expressed in this field.
That this holds is easily verified. The reader may for example show that
\[
 x= \frac{1}{1-f^3}
\]
\medskip

\noindent
{\bf{Remark.}}
The example above  illustrates
that even if one may be "lucky" to discover the existence of a
function like $f$, it is more systematic to proceed with a construction of charts in $X$ and
eventually discover $f$
via the positions of poles and zeros of $y$ and $x-1$.
\bigskip





\centerline{\bf{1.6 Intersection numbers.}}
\bigskip


\noindent
A pair of different irreducible polynomials $P(x,y)$ and $Q(x,y)$  give 
the two curves $\{P=0\}$ and $\{Q=0\}$ in
${\bf{P}}^2$.
We are going to assign 
an intersection number which  takes into the account
eventual multiplicities.
A "nice case" occurs if the
points of intersection
appear in the regular parts of the two curves
and  the gradient vectors of $p$ and $q$ are linearly
independent at every such point. Then one refers to
a simple transversal intersection and 
the intersection number is equal to 
the number of  transversal intersection points.
A general procedure to
assign an integer to the pair $P$ and $Q$ is the following:
Let $X$ be the Riemann surface associated to the projective curve defined
by $P$. Now $Q$ is a meromorphic function on $X$ and
we can  count its number of zeros with multiplicites which
yields an integer denoted by
${\bf{i}}(P;Q)$.
Reversing  the role and we take the Riemann surface $Y$ associated with
$\{Q=0\}$
and count the number of zeros for the meromorphic 
$P$-function on $Y$ which gives another integer
${\bf{i}}(Q;P)$. It turns out that one has  the equality
\[
{\bf{i}}(P;Q)={\bf{i}}(P;Q)\tag{*}
\]


\noindent
Keeping $P$ fixed the integer
${\bf{i}}(P;Q)$ is the degree of the meromorphic function $Q$ on $X$.
This entails that
the intersection number is unchanged
when $Q$ is replaced by $Q-\alpha$
for a complex number as long as $Q-\alpha$ is not reduced to
a constant function on $X$.
A similar invariance hold when we repace $P$ by $P-|beta$.
Si  intersection numbers enjoy
a robust property.
The proof of
(*)  uses  Jacobi's residue for the pair $P$ and $Q$
which we construct below in a local analytic context, i.e.
we shall work in small neighborhoods of
the points of intersection between the two projective curves.

\medskip

\medskip

\noindent
{\bf{1.6.1 Example.}}
Let $P(x,y)=x^2+a-y$ and $Q(x,y)= y^2-b-x^3$ where both
where $a$ and $b$ are complex numbers.
If $S$ is the closure of $\{P=0\}$ taken in
${\bf{P}}^2$ then
$\partial S$ is reduced to the single point
$(0,0,1)$  while 
the projective closure of $\{Q=0\}$
consists of $(0,1,0)$. Hence 
the curves only intersect in
${\bf{C}}^2$.
On the Riemann surface
$X$
attached to $\{P=0\}$
we see that the meromorphic $Q$-function becomes
\[
(x^2+a)^2-b-x^3
\] 
The number of zeros is 4 for all pairs $a,b$.
In the case $a=b=0$
we get $x^3(x-1)$ which means that a zero of order three occurs at
$(0,0)$ and geometrically
one verifies that the two curves $\{P=0\}$ and $\{Q=0\}$
do not intersect transversally at the origin but have a
contact of order three
while a transveral intersection occurs when $x=1$, i.e at the point
$(1,1-a)$ on $X$.
\[
x^2-a-y=0\quad\colon\quad y^2-b-x^3=0
\]
This gives
\[ 
(x^2+a)^2= b+x^3
\]
Let us reverse the role and with $b=0$ we consider the Riemann surface
$Y$ attached to $\{y^2-x^3\}$.
At the origin we get the local coordinate $\zeta$ with
\[
x=\zeta^2\quad\colon\quad y=\zeta^3
\]
Here 
$P=x^2-y=\zeta^4-\zeta^3$ has a zero of 
order three and at the point $(1,1)$ on $Y$ one verifies that
$P$ has a simple zero, i.e. the total number of zeros of
the meromorphic
function $P$ on $Y$ is equal to four as predicted by
Jacobi.

\medskip


\noindent
{\bf{1.6.2 Example.}}
Let $P(x,y)= y^2-x^2-1$ while $Q(x,y)= y^2-2x^2+L(x,y)$ where
$L(x,y)$ is some linear polynomial.
Here $\{P=0\}$ and
we notice that its boundary at infinity is reduced to the points
$(0,1,1)$ and $(0,1-1)$ while those of
$\{Q=0\}$ are $(0,1,\sqrt{2})$ and $(0,1,-\sqrt{2})$
To compute the number of zeros of $Q$ on the Riemann surface
$X$ we can equally well count the number of poles.
At the two points $p^*_1=(0,1,1)$ and $p^*_2=(0,1,-1)$
we notice that the meromorphic function $Q$ has poles of order two
and it follows that the number of zeros counted with multiplicities is equal to four.
\medskip


\noindent
{\bf{1.6.3 Example.}}
Let $P$ be as above but this time
$Q(x,y)= (y-x)(y-\alpha x)+ L(x,y)$ where
$\alpha$ differs from one and -1.
Again $Q$ has a double pole at $(0,1,-1)$ but 
at $(0,1,1)$
we must analyze the pole in more detail.
With $\zeta$ as a local coorniate on $X$ at $(0,1,1)$ we have

\[ 
x=\zeta^{-1}\quad\colon y=\zeta^{-1}\cdot \sqrt{1+\zeta^2}
\]
So with $L(x,y)= ax+by+c$ we get
\[ 
Q=(1- \sqrt{1+\zeta^2})\zeta^{-1}\cdot \zeta^{-1}(
\sqrt{1+\zeta^2}-\alpha)+a\zeta^{-1}+ b\zeta^{-1}\cdot \sqrt{1+\zeta^2}+c
\]
It follows that the coefficient of $\zeta^{-1}$ becomes
\[ 
(1-\alpha)+a+b\tag{i}
\]
So if this number is $\neq 0$ then $Q$ has a simple pole at
$(0,1,1)$ and if it is zero no pole at all.
This, if (i) is $\neq 0$ then the number of zeros is three and if (i)=0 then
$Q$ has two zeros on $X$.
\medskip

\noindent
{\bf{Exercise.}}
Find the equation which determines the three zeros of $Q$ when
(i) is $\neq 0$ and analyze under which conditions on
the numbers $\alpha,a,b,c$ we get three transversal intersection points.
Since the elimination to achieve these equations is rather cumbersome the
material above 
illustrates
the efficiency
of 
Jacobi's counting method for the number of intersection points.
















\bigskip

\centerline {\bf{ 1.7 Jacobi's residue}}
\medskip

\noindent
{\bf{Introduction.}}
The pioneering work by Jacobi  essentially covers the results below.
Extensions to more than two variables 
was given by Weil in the article \emph{L'Integrale
de Cauchy et les fonctions des plusieurs variables}.
Here we follow Weil's methods
applied to the  case of a pair of polynomials in two variables which
form a complete intersection.
The material in § A suffices to
get the requested facts about Intersection Numbers. 
In § B we include some
extra material which goes beyond our present
study of Riemann surfaces. It has been
inserted since it illustrates
calculus in
several complex variables and show
the usefulness of currents.
The reader may also consult the text-book [Griffiths-Harris] which 
has inspired the subsequent material.



\medskip

\centerline
{\bf{A.  The construction of residues.}}


\bigskip


\noindent
Let $P(x,y)$ 
and $Q(x,y)$ be a pair of polynomials.
We do not assume that they are irreducible and they may even have
multiple factors. But we suppose
that they have no common
factor in the unique factorisation domain
${\bf{C}}[x,y]$.
This entails that
the common zero set $\{P=0\}\cap \{Q=0\}$ is  a finite
subset of
${\bf{C}}^2$ and  one says that the pair $(P,Q)$ is a complete intersection.
We shall work close to the origin and
choose  some
$r>0$ such that
\[
\min_{(x,y)\in B(r)}\, |P(x,y)|^2+|Q(x,y)|^2=\rho>0
\]
where $B(r)= \{|x|^2+|y|^2\leq r^2\}$
is a closed ball centered at the origin and $\{P=0\}\cap \{Q=0\}\cap B(r)$
is reduced to the origin.
With $\rho$ and $r$ kept fixed
we  consider
pairs $\alpha,\beta$ such that
$|\alpha|^2+|\beta|^2<\rho$
and in the  common zero set
$\{P=\alpha\}\cap \{Q=\beta\}$
it is understood that we only 
pick points $(x,y)$ which belong to   ball $B(r)$.
Recall  from calculus that
the real-analytic function
$|P|^2$
only has a discrete set of critical values which entails that there exists
some $\epsilon^*>0$ such that the real hypersurfaces
$\{|P|^2=\epsilon\}$
are non-singular for every $0<\epsilon<\epsilon^*$.
One can therefore perform integrals on these.
With $x=u+iv$ and $y=\xi+i\eta$
we identify the 2-dimensional complex $(x,y)$-space with
the 4-dimensional real space where $(u,v,\xi,\eta)$ are coordinates.
One can integrate differential 3-forms
$\psi$   over
the
smooth hypersurfaces
$\{|P|^2=\epsilon\}$ which
are oriented in a natural way. See §§.
If $0<\delta_*<\delta^*$ we  set
\[
\square(\epsilon;\delta_*,\delta^*)=
\{|P|^2=\epsilon\}\cap\,
\{\delta_*<|Q|^2=\delta^*\}
\]
The Federer-Stokes Theorem from § xx gives:
\[
\iiint_{\square(\epsilon;\delta_*,\delta^*)}
d\phi=
 \iint _{\partial \square(\epsilon;\delta_*,\delta^*)}
\phi\tag{*}
\] 
for every test-form $\phi$ of degree two.
When  $g(x,y)$ is a polynomial
we apply this starting from the 2-form
\[ 
\phi=\frac{g(x,y)\cdot dx\wedge dy}{P(x,y)\cdot Q(x,y)}
\]
Here $\phi$ is $d$-closed since
we already have occupied the holomorphic 1-forms $dx$ and $dy$
while
the rational function $\frac{g}{P\cdot Q}$ is holomorphic in a neighborhood
of
$\square(\epsilon;\delta_*,\delta^*)$.
Hence (*) gives  the equality
 
 \[
 \iint _{\sigma(\epsilon;\delta_*)}\,\frac{g(x,y)\cdot dx\wedge dy}{P(x,y)\cdot Q(x,y)}
=
 \iint _{\sigma(\epsilon;\delta^*)}\,\frac{g(x,y)\cdot dx\wedge dy}{P(x,y)\cdot Q(x,y)}\tag{**}
\]
where  
\[
\sigma(\epsilon,\delta)= \{|P|^2=\epsilon\}\cap \{|Q|^2=\delta\}
\quad\colon\, \epsilon,\delta>0
\] 
To be precise this is okay provided that
the pair
$(\epsilon,\delta)$ are sufficiently small so that
integration only takes place over small compact sets close to the origin
in ${\bf{C}}^2$. One refers to
$\sigma(\epsilon,\delta)$ as integration chains of degree two.
In a similar fashion we can make a variation of  $\epsilon$ and
arrive at the following:

\bigskip


\noindent
{\bf{A.1. Proposition.}}
\emph{There exists a pair of positive numbers
$a,b$ such that
the integrals}

\[
 \iint _{\sigma(\epsilon;\delta)}\,\frac{g(x,y)\cdot dx\wedge dy}{P(x,y)\cdot Q(x,y)}
\quad\colon 0<\epsilon<a\,\colon\, 0<\delta<b
\]
\emph{are independent of $\epsilon,\delta$
while 
the 2-chain 
${\sigma(\epsilon;\delta)}$ stays in the ball $B(r)$. 
The common value is denoted by $\mathfrak{res}_{P,Q}(g)$
and  called the Jacobi residue of $g$ with respect to $P$ and $Q$.}
\medskip


\noindent
{\bf{Remark.}}
The residue depends on the ordering of $P$ and $Q$
because
we started from  the 
oriented real hypersurface
$\{|P|^2=\epsilon\}$ which  induces a positive orientation on
the  $\sigma$-chains which determines the sign of the integrals.
If the role is changed so that we start
with a hypersuface
$|Q|^2=\delta$  then
\[
\mathfrak{res}_{Q,P}(g)=-\mathfrak{res}_{P,Q}(g)
\]

\medskip

\noindent
{\bf{2. A continuity property.}}
Keeping $\epsilon,\delta$
fixed it is clear that
\[
\lim_{(\alpha,\beta)\to (0,0}\,
 \iint _{\sigma(\epsilon;\delta)}\,\frac{g(x,y)\cdot dx\wedge dy}{(P(x,y)-\alpha)
 \cdot (Q(x,y)-\beta)}
= \iint _{\sigma(\epsilon;\delta)}\,\frac{g(x,y)\cdot dx\wedge dy}{P(x,y)\cdot Q(x,y)}
\]
This entails that
\[
\lim_{(\alpha,\beta)\to (0,0}\,\mathfrak{res}_{P-\alpha,Q-\beta}(g)=
\mathfrak{res}_{P,Q}(g)\tag{2.1}
\]



\medskip

\noindent
{\bf{3. The Jacobian.}}
Given the pair $P,Q$ we set
\[ 
\mathcal J(x,y)=P'_x\cdot Q'_y-P'_y\cdot Q'_x
\]
This is a new polynomial.
As explained in § XX $\mathcal J$  is not
identically zero.
The curve
$\{\mathcal J=0\}$ is a sparse subset of
${\bf{C}}^2$
which entails that there exists many pairs of complex numbers
$\alpha$ and $\beta$ which both are close to zero such that
the finite set
$\{P=\alpha\}\cap \{Q=\beta\}$ 
stays outside
$\mathcal J^{-1}(0)$. When this holds we say that
the pair $(\alpha,\beta)$ is admissable.
Notice  that the Jacobian is unchanged when 
the pair $P,Q$ is replaced by  $P-\alpha$ and $Q-\beta$.
\medskip

\noindent
{\bf{4. Jacobi's residue formula.}}
Let $\alpha,\beta$ be a pair of small complex numbers such that
$\mathcal J\neq 0$ at the common zeros of $P-\alpha$
and $Q-\beta$ which are close to the origin in
${\bf{C}}^2$.
Repeated use of Cauchy's residue formula
from  § xx gives
\[
\mathfrak{res}_{P-\alpha,Q-\beta}(g)=(2\pi i)^2\cdot 
\sum\,\frac{g(p_k)}{\mathcal J(p_k)}
\] 

\medskip

\noindent
where
the sum extends over
the distinct points in
$\{P=\alpha\}\cap \{Q=\beta\}$.
which  belong to   $B(r)$.
\medskip

\noindent
{\bf{A.5. A special case.}}
Above we can take $g=\mathcal J$
in which case (2.1 ) is $-4\pi^2$ times an integer.
The continuity in § 2  shows that this integer
is constant as $\alpha,\beta$ varies
in the admissable set from § 3. Passing to the limit it follows that
\[ 
\mathfrak{res}_{P,Q}(\mathcal J)=K
\] 
where $K$ is the set of  points when $\{P-\alpha\}$ and $\{Q-\beta\}$
have
transversal intersections.
The absolute value
of $K$ is called the intersection number
and is denoted by
${\bf{i}}(P,Q)$.

\newpage



\centerline {\bf{B. Further results.}}
\bigskip


\noindent
Above we defined the integers
$\mathfrak{res}_{P,Q}(g)$ where $g$ are polynomials.
Keeping $P$ and $Q$ fixed
it means that one has a ${\bf{C}}$-linear map
\[ 
g\mapsto \mathfrak{res}_{P,Q}(g)
\]
\

\noindent
It turns out that it can be described in an algebraic fashion.
Namely, let $\mathcal O_2={\bf{C}}\{x,y\}$ 
be the local ring of convergent power series in two variables. 
Thus, the elements are germs of analytic functions in  $x$ and $y$.
Now $P$ and $Q$ are elements in $\mathcal O_2$ and generate an ideal denoted by
$(P,Q)$. Set
\[
\mathcal A=
\frac{\mathcal O_2}{(P,Q)}
\]
The assumption that the origin is an isolated
point in
the common seros of $P$ and $Q$ entails that
the ideal $(P,Q)$ contains a sufficiently high power of the maximal ideal 
$\mathfrak{m}$ of the local ring
$\mathcal O_2$. It follows that
$\mathcal A$ is a local and finite dimensional 
complex algebra.
In commutative algebra one refers to 
$\mathcal A$ as a local artinian ring.
If $g$ is a polynomial which belongs to the ideal $(P,Q)$ it follows easily from
Jacobi's residue formula in § 4  that
$\mathfrak{res}_{P,Q}(g)=0$.
Less obvious is the following:

\medskip

\noindent
{\bf{B.1 Theorem.}}
\emph{A polynomial $g$ belongs to the ideal $(P,Q)$ in
$\mathcal O_2$ if and only if}
\[
\mathfrak{res}_{P,Q}(h\cdot g)=0
\quad\text{hold for all polynomials}\,\, h
\]



\medskip

\noindent
{\bf{B.2 Noetherian operators.}}
Theorem B.1  entails that there exists  a ${\bf{C}}$-linear form
on the finite dimensional vector space
$\mathcal A$ defined by
\[ 
\bar g\mapsto 
\mathfrak{res}_{P,Q}(g)
\]
where $\bar g$ is the image in $\mathcal A$ of a polynomial $g$.
This linear functional can be expressed by a unique differential operator with
constant coefficients. More precisely, we have the polynomial ring
${\bf{C}}[\partial_x,\partial_y]$
of differential operators with constant coefficients
where
$\partial_x$ and $\partial_y$ are the holomorphic first order
operators defining partial derivatives with respect to $x$ and$ y$.
Then there exists a unique differential operator
$\mathcal N(\partial_x\partial_y)\in 
{\bf{C}}[\partial_x,\partial_y]$ such that
\[
\mathfrak{res}_{P,Q}(g)= \mathcal N(\partial_x,\partial_y)(g)(0)
\]
for every polynomial $g(x,y)$. Thus, in the right hand side one evaluates
the polynomial $\mathcal N(g)$ at the origin.
One refers to $\mathcal N$ as the noetherian operator attached to the pair $P,Q$. It
has the special property that
$\mathcal N(\phi)=0$ for every
$\phi$ in the ideal $(P,Q)$.
To avoid possible confusion we remark that
these differential operators were introduced by Max Noether, i.e. not by
his famous daughter Emmy whose name  is attributed to
the notion of noetherian rings
as well many other
deep results in algebra.




\medskip


\noindent
{\bf{B.2.1
The construction of Noetherian operators}}. They are  obtained
via  the localised Weyl algebra $A_2(*)$ whose elements
are
differential operators in whose  coefficients are rational functions with
no pole at the origin.
The crucial result is that if
${\bf{C}}[x,y]$ is identified with zero-order differential operators
then the right ideal in $A_2(*)$ generated by $P$ and $Q$ yields
a left  module
\[
\frac{A_2(*)}{A_2(*)\cdot P+A_2(*)\cdot Q}
\] 
which is isomorphic to $m$ copies of the simple
left $A_2$-module
\[
\frac{A_2(*)}{A_2(*)\cdot x+A_2(*)\cdot y}
\]
and $m$ is the integer which gives the Jordan-Hölder length of the artinian
local ring $\mathcal A$.
We shall not enter a discussion about this and remark only that the
result above belongs to  basic material in
$\mathcal D$-module theory.



\medskip

\noindent
{\bf{B.3 The Gorenstein property.}}
The local algebra $\mathcal A$ is special, i.e. it is a  local Gorenstein 
ring which means that
the 
socle defined as those elements $a\in\mathcal A$  which
are annihilated by the maximal ideal $\mathfrak{m}$ in $\mathcal O_2$
is a 1-dimensional complex vector space.
This  fact is easily proved via a diagram chasing in homological algebra
where one  uses the assumption that the pair $P,Q$ is a  complete
intersection.
The element in $\mathcal A$ which generates the
1-dimensional socle is  the image of $\mathcal J$. This is a consequence of
the following vanishing property of residue integrals:
\[
\mathfrak{res}(g\cdot \mathcal J)=0\quad\colon\forall\,\, g\in\mathfrak {m}
\]
The reader may notice that this is an
immediate consequence of Jacobi's residue formula in § A.4.




\bigskip


\noindent
{\bf{B.4 The trace map.}}
Let us introduce two new complex variables $w$ and $u$.
In the 4-dimensional complex $(x,y,w,u)$-space
one has the non-singular analytic surface
defined by the equation
\[ S=\{w=P(x,y)\} \cap \{ u=Q(x,y)\}
\]
Let $g(x,y)$ be a polynomial.
For every test-form
$\psi^{0,2}$ of bi-degree $(0,2)$
in the $(x,y,w,u)$-space
we set
\[ 
\iint_S\, g(x,y)\cdot dx\wedge\wedge \psi^{0,2}
\]
This gives a current in ${\bf{C}}^4$ 
denoted by $g\cdot \square_S$
Consider the projection $\pi(x,y,w,u)= (w,u)$.
The hypothesis that $P$ and $Q$ is a complete intersection entails that
$\pi$ restricts to a proper map  on $S$
and hence there exists a direct image current
defined by
\[ 
\phi^{0,2}\mapsto
\iint_S\, g(x,y)\cdot dx\wedge\wedge \pi^*(\phi^{0,2})\tag{1}
\]
where 
$\pi^*(\phi^{0,2})$ is the  pull-back of the test-form
$\phi^{0,2}$ in the $(w,u)$-space.
On $S$ one has the equality
\[
\pi^*(dw\wedge du)= \mathcal J\cdot dx\wedge dy
\]
Next, in the $(w,u)$-space there exists
the set of admissable points $(w,u)$ for which
$\mathcal J(x,y)\neq 0$ for all $(x,y)$ with
$P(x,y)=w$ and $Q(x,y)=u$.
We notice that this is the same as the image set
$\pi(S\cap \mathcal J^{-1}(0)$. Here
$S\cap \mathcal J^{-1}(0)$ is an algebraic hypersurface in
$S$ and since
$\pi$ restrict to a proper mapping with finite fibers, it
follows that the image set is
a hypersurface in the $(w,u)$-space which we denote by
$\Delta$ and refer to as a discriminant locus.
The direct image current (1) can be described
in
the open complement of $\Delta$.
Namely,
$\pi$ restricts to an unramified covering map from
$S\setminus \pi^{-1}(\Delta)$ onto the open complement of
$\Delta$ in 
the $(w,u)$-space,. Let  $K$ be the number of points in every fiber
which is given by
an unordered $k$-tuple
$p_k(w,u)= (x_k(w,u),y_k(w,u)\}$,
Here the coordinates $\{x_k(w,u)\}$ and $\{y_k(w,u)\}$ are local branches of
multi-valued analytic functions in
the open complement of $\Delta$.
If $h(u,w)$ is a test-function in
the $(w,u)$-space whose compact support 
does not intersect $\Delta$ and we take  $\phi^{0,2}= h(w,u)\cdot dw\wedge du$
then one has the equality
\[ 
\iint_S\, g(x,y)\cdot dx\wedge\wedge \pi^*(\phi^{0,2})=
\iint_{D^2}\, \mathfrak{Tr}(\frac{g}{\mathcal J})(w,u)\cdot h(w,u)\cdot dw\wedge du
\]
where
\[
 \mathfrak{Tr}(\frac{g}{\mathcal J}) (w,u)
=\sum_{k=1}^{k=K}\, \frac{g(p_k(w,u)}{\mathcal J(p_k(w,u))}\tag{*}
\]
\medskip


\noindent
We refer to (*) as a trace function of
$\frac{g}{\mathcal J}$.
Next,  recall that the passage to direct image currents commute
with
differentials. Since $g(x,y)$ is holomorphic
the current (1) is $\bar\partial$-closed. Indeed, Stokes theorem entails that
\[
\iint_S\, g(x,y)\cdot dx\wedge\wedge dy\wedge
\bar\partial(\psi^{0,1})=0
\] 
hold for every test-form $\psi^{0,1}$ with compact support in
the $(x,y,w,u)$-space.
\medskip

\noindent
{\bf{B.4.1 Conclusion.}}
Denote by $\gamma$
the direct image current
from (1). By (*) its restriction to
the open complement of $\Delta$ is  the density
expressed by the $(2,0)$-form
\[
\mathfrak{Tr}(\frac{g}{\mathcal J})(w,u)\cdot dw\wedge du
\]
Next, in (*) the trace function is constructed by
a sum over fibers which entails that it extends to a meromorphic function in
the $(w,u)$-space with eventual  poles  confined to $\Delta$.
Let $G$ denote this meromorphic function so that
\[
G(w,u)= \mathfrak{Tr}(\frac{g}{\mathcal J})(w,u)\tag{i}
\]
holds when $(w,u)$ are outside $\Delta$.
By the above the current $\gamma$ is $\bar\partial$-closed, i.e.
the $(2,0)$-current defined outside $\Delta$ by
$G\cdot dw\wedge du$ can be extends via $\gamma$ to a
$\bar\partial$-closed current in the $(w,u)$-space.
But this can only hold if the meromorphic function $G$ has no poles at all. 
In fact, this follows
from Hartogs' extension result in
§ XX. Hence we have proved:


\medskip

\noindent
{\bf{B.4.2 Theorem.}}
\emph{For every polynomial $g(x,y)$ 
the trace function
defined by (*)  in the
complement of $\Delta$ extends to 
a holomorphic function in the $(w,u)$-space.}

\bigskip
















\noindent
{\bf{C. The local algebra
${\bf{C}}\{P,Q\}$}}.
Given the pair $P,Q$ there exists
a subalgebra 
of $\mathcal O_2$
whose elements
are germs of analytic functions
which
can be expanded into a power series in $P$ and $Q$.
More precisely, denote by
${\bf{C}}[P,Q]$
the set of entire functions of the form
\[
\phi_n(x,y)=\sum\, c_{jk}\cdot P^j\cdot Q^k
\]
where 
$\{c_{jk}\}$ is a finite set of doubly-indexed complex numbers.
A  germ $g$ belongs to 
${\bf{C}}\{P,Q\}$ if and only if there exists a small polydisc $D^2$ 
centered at the origin in ${\bf{C}}^2$ such that
$g$ is holomorphic in $D^2$ and there exists a sequence
$\{\phi_n\}$ of $(P,Q)$-polynomials as 
above which converge uniformly to $g$ in $D^2$.
Concerning the algebra
${\bf{C}}\{P,Q\}$ a wellknown result in several complex variables 
shows that it is isomorphic to
the local ring of convergent power series in two variables, i.e. the polynomials 
considered as germs in $\mathcal O_2$ are analytically independent.
Moreover, $\mathcal O_2$ is a finitely generated
module over
its subring
${\bf{C}}\{P,Q\}$.






\bigskip



\noindent
{\bf{C.1 The algebraic  trace.}}
By the above the quotient field of $\mathcal O_2$ is a 
finite algebraic extension of the quotient field of
${\bf{C}}\{P,Q\}$. 
If $m$ is the dimension we can choose an $m$-tuple
$\phi_1,\ldots,\phi_m$ in the quotient field of $\mathcal O_2$ whose images in
$\mathcal A$ yields a basis
for this finite algebraic extension.
Let us then consider a polynomial $g$.
For each $1\leq \nu\leq m$
we can write
\[
g\cdot \phi_\nu=\sum_{j=1}^{j=m}\, \rho_{\nu,j}\cdot \phi_j
\]
where $\{\rho_{\nu,j}\}$ belong to the quotient field of
${\bf{C}}\{P,Q\}$.
As explained in §§ the trace defined by
\[
\mathfrak{Tr}(g)= \sum\,\rho_{\nu,\nu}
\]
does not  depend upon the chosen  $\phi$-basis.


\bigskip


\centerline
{\bf{D. More advanced results.}}
\bigskip


\noindent
Above we have treated Jacobi's residues where the
denominators are holomorphic functions.
More generally, when $P$ and $Q$ are in a complete intersection we can
still
define integral
\[
J_g(\epsilon,\delta)=
\]
when $g(x,y)$ is a test-function with compact support
close to the origin.
Here the integral is no longer independent of the pair
$(\epsilon,\delta)$ which  leads to a considerably more
involved  situation 
first studied by Miguel Herrera who proved
that there exists certain limits  provided  that
one pays attention while $\epsilon$ and $\delta$ tend to zero.
We shall not enter a detailed discussiona about multi-residue calculus
but
mention that a counter-example was discovered by Passare and Tsikh in
[P-T] which shows that
the   unrestricted limit of the integrals above in general does not exist.
In fact, these counter-examples are generic and the reader may consult my article
[Björk:Abel Legacy] for
further comments about the Passare-Tsikh example.
On the positive side there exists a remarkable result  due to  H. Samuelsson
in his Ph.d-thesis at Chalmers University 2005.
From an analytic point of view Theorem D.1 below is
quite useful. Instead of taking "ugly residues" as above one
considers regularisations. Namely, for the given polynomial $P$
there exists a smooth current
\[
\frac{\bar P}{|P|^2+\epsilon}
\] 
One can apply the $\bar\partial$-current and
get a smooth $(0,1)$-current
\[
\rho_P(\epsilon)=
\bar\partial(\frac{\bar P}{|P|^2+\epsilon})
\]
Similarly we construct smooth currents $\rho_\delta(Q)$.
With these notations Samuelson proved the following:

\medskip

\noindent
{\bf{D.1 Theorem.}} \emph{In the space of $(0,2)$-currents there exists an unrestricted limit}
\[
\gamma_{P,Q}=
\lim_{(\epsilon,\delta)\to (0,0)}\,
\rho_P(\epsilon)\wedge \rho_\delta(Q)
\]
\emph{Moreover, this current is of the Coleff-Herrera type which means
that}
\[
\gamma_{P,Q}(\phi^{2,0})=0
\]
\emph{for every test-form
$\phi^{2,0}$ given as $[\bar x\cdot g_1(x,y)+\bar y\cdot g_2(x,y)]\ddot d\wedge dy$
where $g_1,g_2$ is a pair of test-functions.}

























\newpage




















\bigskip

\centerline {\bf{ 1.8 Elliptic function fields.}}
\medskip


\noindent
Once the reader has studied the general theory in the subsequent sections
the
details which follow below become clear.
Let $y$ and $z$ be independent
and consider the algebraic equation
\[
y^2=(x-a)(x-b)(x-c)\tag {*}
\]
where $a,b,c$ are distinct complex numbers and all are $\neq 0$.
Set
\[
P(x,y)=y^2-(x-a)(x-b)(x-c)
\]
This is an irreducible polynomial
in ${\bf{C}}[x,y]$
and we get the algebraic function field
\[ 
K=\frac{{\bf{C}}[x,y]}{(P)}\tag{**}
\]
where $(P)$ is the principal ideal generated by $P$.
Let $X$ be the associated compact Riemann surface.
As a topological space we will show below
that
$X$ is homeomorphic to a torus, i.e. the sphere
with one attached handle. 
\medskip

\noindent
\emph{The construction of $X$}.
Consider the  algebraic curve
$S$
in 
$\bf{C}^2$ defined by the equation $P(x,y)=0$.
With 
$p(x)=(x-a)(x-b)(x-c)$
we get the complex gradient vector
\[ 
\nabla(P)=(P_x,P_y)=(p'(x),2y)
\]
The gradient vector is   $\neq 0$ if $y\neq 0$ and if $y=0$ while $p(x)=0$ we have
$p'(x)\neq 0$ since the $p$-roots are simple.
Hence $\nabla(P)\neq 0$ on $S$ which means  that
the curve $S$ is \emph{non-singular}, i.e. it appears as a
1-dimensional complex submanifold of
${\bf{C}}^2$ and
since the polynomial $P(x,y)$ is irreducible 
this manifold is \emph{connected}.
In algebraic geometry one refers to $S$ as a smooth and irreducible
affine curve.
\medskip

\noindent
\emph{A compactification.}
When $x$ tends to infinity on $S$ we notice that
\[
|y|^2\simeq |x|^3
\]
In other words, the absolute value of $y$ increases
considerably faster than
$x$.
Let us then
introduce the 2-dimensional projective space
$\bf{P}^2$ with coordinates
$\zeta_0,\zeta_1,\zeta_2$ and identify
$\bf{C}^2$
with the portion where
$\zeta_0\neq 0$ so that
$S$ is identified with the set
\[
(1,x,y)\quad\colon\, (x,y)\in S
\]
When $(x,y)\in S$ and $|x| >>0$
we can express the points by
\[
(\frac{1}{y},\frac{x}{y},1)
\]
Since $|y|>>|x|$ on $S$ 
we see these points converge to a unique point on
in ${\bf{P}}^2$  given by
$p^*=(0,0,1)$.
In a neighborhood of $p^*$ we have local coordinates
$w$ and $\tau$  which represent points close to $p^*$ by 
$(w,\tau,1)$. Outside the origin in the $(w,\tau)$ disc we get
\[
y=\frac{1}{w}\quad\text{\and}\quad x=\frac{\tau}{w}
\]

\noindent
Thus, a point  $p=(x,y)$ with 
$|x|$  large belongs to $S$
if and only if
the corresponding $(w,\tau)$-coordinates of $p$ satisfy:
\[
w^{-2}=(\frac{\tau}{w}-a)(\frac{\tau}{w}-b)(\frac{\tau}{w}-c)\implies
\]
\[ 
w=(\tau-aw)(\tau-bw)(\tau-cw)\tag{i}
\]
Here (i) determines
$w$ as an analytic function of $\tau$ given
by a convergent power series of the form:
\[ 
w= \tau^3+\sum_{\nu\geq 4}\, c_\nu\tau^4=b(\tau)
\]
Using the local coordinates   $(\tau,w)$ at  $p^*$ we conclude
that
$X=S\cup \,p^*$
appears a  non-singular submanifold of
$\bf{P}^2$ and is therefore  a compact Riemann surface. We conclude
that $\mathfrak{M}(X)$ is isomorphic to the
function field $K$ from (**)  above.
\medskip

\noindent
\emph{The genus of $X$}.
We have the meromorphic function $x$ on $X$.
At $p^*$ where $\tau$ is the local coordinate we have seen that
\[ 
x(\tau)=\frac{\tau}{\zeta}= \frac{\tau}{b(\tau)}
\] 
Since $b(\tau)$ has a zero of order 3 it follows that
$x$ has a double pole at $p^*$.
Next, zeros of $x$ occur when
\[
 y^2=-abc
\] 
Since $abc\neq 0$ we see that $x$ has two simple zeros on $X$.
Hence $x$ is
a meromorphic function whose degree is two and its  principal divisor is
given by:
\[
D(x)= 2\cdot p_*-(q_1+q_2)
\]
where $q_1,q_2$ are the points
on $S$ where $x=0$ and the $y$-coordinate is plus or minus
$\sqrt{abc}$. Next, consider the meromorphic function $y$.
Here we find three simple zeros at the points $(a,0),(b,0),(c,0)$ and at
$p^*$ we have seen that $y$ has a triple pole.
Now we consider the differential 1-form
\[ 
\omega=\frac{dx}{y}
\]
Zeros of $y$ occur at the points $(a,0),(b,0),(c,0)$
and at each of these $y$ serves as a local coordinate. 
Close to $(a,0)$ we have for example
\[ 
x= a+g(y)
\] 
where $g(y)$ has a zero of order two at $y=o$ which entails that
$dx$ is of the form $h(y)ydy$ and hence $\omega$ is holomorphic close to
$(a,0)$ and given by
\[ 
\omega=\alpha(y)\cdot dy
\quad\text{where}\quad  \alpha(0)\neq 0
\]
The same hold at $(b,0)$ and at $(c,0)$.
Next, at the point at infinity
we have the local coordinate $\tau$
and from the above one has

\[ 
x=\tau^{-2}(1+g(\tau))\quad\text{and}\quad
y(\tau)= \tau^{-3}(1+h(\tau))
\] 
where $g$ and $h$ are holomorphic
at $\tau=0$.
It follows that
\[ 
\omega= \frac{\tau^3}{(1+h(\tau)}\cdot(-2\tau^{-3}(1+g(\tau))+
\tau^{-2}g'(\tau)]\cdot d\tau
\]
which shows that $\omega$ also is holomorphic at $p^*$.


\bigskip





\noindent
{\bf{Exercise.}} Conclude from the above that
$\Omega$ not only is holomorphic but also $\neq 0$
everywhere and that the space 
$H^0(X,\Omega)$ of globally defined holomorphic 1-forms
is a 1-dimensional complex space generated by
$\omega$.
In § we shall learn that this entails that
$g=1$ and hence $X$ is homeomorphic to a torus.


\medskip


\noindent
{\bf{Remark.}}
Let us specify the three constants $a,b,c$ and take a curve
\[ 
y^2=x(x-1)(x-d)
\] 
where $d$ is a real number $>1$. Even in this case 
it is not easy to get a picture of $X$ and in a more naive  "discover" that
$X$ is a torus.
So the calculations which show
that $X\simeq T^2$
illustrate the power of
the general theory to
be exposed in the subsequent sections.



\bigskip




\noindent
\emph{1.5.1 The Jacobi map.}
Let $X$ be the elliptic curve assocaited to the curve (*) above.
Fix some point $p_0$ on $X$.
For every other point $p\in X$ we can choose a simple curve
$\gamma$ from $p_0$ to $p$ and construct the line integral of
$\omega$ along $\gamma$. This yields a function
\[
\phi_\gamma(p)=\int_\gamma\,\omega\tag{*}
\]
However, the $\phi$-function is not uniquely determined since there exist closoed curves
$\gamma$ along which the line integral is non-zero.
So values of the $\phi$-function are not well-defined.
To overcome
this we  consider the family of all closed curves
at $p_0$ and to every such curve $\gamma$ we assign 
the complex number
\[ 
\{\gamma\}=
\int_\gamma\,\omega\tag{1}
\] 
Above we have used the monodromy theorem
which shows
that the right hand side only  depends upon the homotopy class
of $\gamma$ in the family of closed curves at $p_0$.
In the left hand side $\{\gamma\}$ denotes this homotopy class
which is identfied with an
an element in the fundamental group $\pi_1(X)$.
The set of all complex numbers which are 
obtained via (1) as $\{\gamma\}$ varies is a subset of
${\bf{C}}$ which we denote by 
$\Gamma$.
In Section XX we shall prove
that $\Gamma $ is a discrete set
given as a ${\bf{Z}}$-lattice generated by a 
pair of ${\bf{R}}$-linearly independent vectors.
Now we obtain the torus
\[ 
T^2=\frac{{\bf{C}}}{\Gamma}
\]
From the above  the $\phi$-integral takes    well-defined values in
$T^2$ as $p$ varies in $X$.
Hence we obtain a map from $X$ into $T^2$. Since
$\omega\neq 0$ on the whole of $X$ it follows  this map
is  \emph{locally bi-holomorphic}. But then,  since $X$ is compact and
$T^2$ connected it follows from general toplogy  that
$\phi$ is  surjective and 
 \emph{Abel's theorem} will show    that
the map also is injective. 
In particular $\mathfrak{M}(X)$ can be identfied with the field
of $\Gamma$-periodic meromorphic functions
defined in the whole complex $z$-plane.
Above we found the special meromorphic function on $x$ given via $x$ which has one double pole and two simple zeros.
This led Weierstrass to
perform constructiuons in a reverse way, i.e. starting from a ${\bf{Z}}$-lattice
$\gamma$ the considered the field
$\mathcal P_\Gamma({\bf{C}})$ of all meromrphic functions which
are $\Gamma$-period, or as one says doubly-periodic with resepct to this lattice.
In § x we expose how to construct special double periodic functions
$\mathfrak{p}$ with a double pole at a lattice point
and two simple zeros in a  fundamental
domain. 







\medskip

\noindent
{\bf{1.5.2 A cubic equation.}}
Consider the algebraic equation
\[
y^3+x^3=1
\]
which gives the algebraic curve $S$ defined by the zero set of
$P= x^3+y^3\vvv 1$.
Here $\nabla(P)=(3x^2,3y^2)$ is non\vvv zero on $S$ and hence
the affine curve $S$ is non\vvv singular. Its closure
in ${\bf{P}}^2$
adds three points.
One is for example
\[ 
p\uuu 1^*=(0,1,\vvv 1)
\]
At $p\uuu 1^*$ we take local coordinates $(\zeta,\eta)$
representing the points 
$(\zeta,1,\vvv 1+\eta)$. When $\zeta\neq 0$
they correspond to points
\[ 
(1, \frac{1}{\zeta}, \frac{\vvv 1+\eta}{\zeta})
\]
in ${\bf{C}}^2$.
The defining equation for $\bar S$ close to $p\uuu 1^*$
becomes:

\[
\frac{(\vvv 1+\eta)^3}{\zeta^3})+\frac{1}{\zeta^3}=1\implies
(\vvv 1+\eta)^3+1=\zeta^3
\]
This gives $\zeta^3+\vvv 3\eta+3\eta^2\vvv \eta^3=0$
and  hence $\bar S$ is locally defined by an equation 
$\eta=\zeta^3\cdot g(\zeta)$ where $g(0)\neq 0$.
Set
$j_1=e^{2\pi i/3}$.
 A similar computation as above shows that $\bar S$ is non\vvv singular at
the  points $p^*\uuu 2=(0,1,j\uuu 1)$ and 
$p^*\uuu 3=(0,1,j\uuu 1^2)$.
Hence $\bar S$ is a nonsingular projective curve and is
identified with a Riemann surface  denoted by $X$.
\medskip

\noindent
{\bf{Exercise.}}
Show that when $y$ is identified with a meromorphic function then
it has simple poles at
the three  points $\{p^*\uuu\nu\}$
and simple zeros at 
$(1,0),(e^{2\pi i/3},0)$ and $e^{4\pi i/3},0)$
Similarly, $x$ has simple poles at $\{p^*\uuu\nu\}$
and a simple zeros at $(0,1),(0,e^{2\pi i/3})$ and $(0,e^{4\pi i/3})$.
Let us consider the point $(0,1)$
and with $x=1+\zeta)$ the local equation for $S$ becomes

\[
y^3+(1+\zeta)^3=1\implies y^3+3\zeta+\zeta^2+\zeta^3=0
\]
Hence $y$ serves as a local coordinate and $\zeta(y)=y^3\cdot g(y)$
with $g(0)\neq 0$.
\medskip

\noindent
{\bf{1.5.3 Conclusion.}}
Consider the meromorphic function
\[ 
f=\frac{y}{x\vvv 1}
\]
From the above 
$f$ has no poles at the boundary points and
$f(p^*\uuu\nu)\neq 0$ for each $\nu$.
At the point $(1,0)$ the
reader can  verify that
$f$ has a double pole and 
it has simple zeros  at
$(e^{2\pi i/3},0)$ and $e^{4\pi i/3},0)$.
Starting from the rational field ${\bf{C}}(f)$ it follows that 
$\mathfrak{M}(X)$ is a quadratic extension  
which shows  that $X$ is an elliptic curve.
So even if we start from a cubic eqaution it may happen that the resulting curve is 
elliptic !

\medskip


\noindent
{\bf{1.5.4 An exercise about period integrals.}}
Let $0<a<b$ be real and consider the  curve
\[
 y^2=x(x\vvv a)(x\vvv b)
\]
We have already seen that its closure in ${\bf{P}}^2$ is 
non\vvv singular and yields a
Riemann surface $X$ with genus $g=1$.
Moreover $\omega=\frac{dx}{y}$
is a holomorphic form without zeros.
We grasp this Riemann surface via the 2\vvv sheeted map given by
the meromorphic function $x$. If $z$ is the complex coordinate
in ${\bf{P}}^1$ then $\omega$ corresponds to the 1\vvv form
\[
\frac{dz}{\sqrt{z(z\vvv a)(z\vvv b)}}
\]
On $X$ there exists a closed curve starting at $(0,0)$
which first reaches $(a,0)$
along a simple curve on which $\mathfrak {Im} (y)>0$
and then returns
to the (0,0) along a simple curve 
starting at $(a,0)$ where $\mathfrak{Im}(y)<0$.
The resulting composed curve $\gamma$ is closed and
the reader should verify the equality

\[
\int\uuu \gamma\,\omega=
(1+i)\cdot \int\uuu 0^a\, \frac{dx}{\sqrt{x(a\vvv x)(b\vvv x)}}
\cdot dx\tag{i}
\]
Next, start at $(a,0)$ and construct a simple curve 
reaching $(b,0)$ along which $\mathfrak{Im}(y)>0$ and   return
after
along a simple curve 
where
$\mathfrak{Im}(y)<0$. This gives a closed curve
$\gamma\uuu 1$
which starts and ends at $(a,0)$.
here the reader should verify the equality

\[
\int\uuu {\gamma\uuu 1}\,\omega=
i\cdot (1+i)\cdot \int\uuu a^b\, \frac{dx}{\sqrt{x(x\vvv a)(b\vvv x)}}
\cdot dx\tag{ii}
\]

\medskip

\noindent
Using the material about doubly periodic functions
in § XX the isomorphism class
of the  elliptic curve
is governed by the quotient of the two real numbers which
compute the integrals above.
With $0<a<b$ and $\alpha=a/b$
the variable substitution $x\to as$ gives
the equality:
\[
\int\uuu 0^a\, \frac{dx}{\sqrt{x(a\vvv x)(b\vvv x)}}
\cdot dx=
\frac{1}{\sqrt{b}}\cdot \int\uuu 0^1\,
\frac{ds}{\sqrt{s(1\vvv s)(1\vvv \alpha s)}}\tag{iii}
\]
Similarly we find that
\[
\int\uuu a^b\, \frac{dx}{\sqrt{x(x\vvv a)(b\vvv x)}}
\cdot dx=
\frac{1}{\sqrt{b}}\cdot \int\uuu 1^{b/a}\,
\frac{ds}{\sqrt{s(1\vvv s)(1\vvv \alpha s)}}\tag{iv}
\]
So while $\alpha=a/b$ varies in $(0,1)$
we encounter the quotients

\[
\kappa(\alpha)= \frac{ \int\uuu 0^1\,
\frac{ds}{\sqrt{s(1\vvv s)(1\vvv \alpha s)}}}{
 \int\uuu 1^{1/\alpha}\,
\frac{ds}{\sqrt{s(1\vvv s)(1\vvv \alpha s)}}}
\]

\medskip

\noindent
{\bf{Exercise.}}
Analyze these quotients numerically as a functions of $\alpha$.
For example, do they take distinct values as $0<\alpha<1$ and draw conclusions from this concerning the eventual non\vvv isomorphism of the corresponding
elliptic curves $y^2=x(x\vvv a)(x\vvv b)$ when $a/b$ changes.
\bigskip

















\newpage


\centerline{\bf{1.9 Proof of Theorem § XX}}

\bigskip


\noindent
Let $u$ be a continuous and subharmonic function in
the unit disc $D$.
Set $\lambda(z)=e^{u(z)}$ which yields a metric $\delta$
with
non-positive curvature.
Consider a pair of points $a,b$ in $D$ and a pair of rectifiable 
Jordan arcs
$\gamma_1,\gamma_2$ in $\mathcal C(a,b)$.
Suppose for the moment that
the intersection of
the $\gamma$-curves only contains the end-points $a$ and $b$.
Their union gives
a closed Jordan curve
$\Gamma$ which borders a Jordan domain
$\Omega$.
The inequality (*) in  Theorem XX follows 
if there to each
point $p\in\gamma_1$ exist
a Jordan arc
$\beta$ in $\Omega$ which joins $p$ with some 
$q\in\gamma_2$ and a
Jordan arc $\alpha$ in $\Omega$ which joins $a$ and $b$ such that

\[
[\int_\alpha\, \lambda(z)\, |dz|]^2+
[\int_\beta\, \lambda(z)\, |dz|]^2\leq
\frac{1}{2}
\bigl([\int_{\gamma_1}\, \lambda(z)\, |dz|]^2+
[\int_{\gamma_2}\, \lambda(z)\, |dz|]^2\bigr )\tag{1}
\]
To prove (1) we employ a conformal mapping
$\psi\colon D\to \Omega$ where $D$ is another unit disc with
the complex coordinate $w$
and recall from § XX that$\psi$ extends to a homeomorphism from the closed Jordan 
domain $\bar\Omega$ where it sends $\gamma_1$ and $\gamma_2$
onto a pair of closed intervals on the unit circle which
instersect  at two points.
Next, 
there exists the composed function
$\lambda\circ \psi$ on $D$. By assumption $\lambda= e^u$ for some subharmonic
function $u$ in $\Omega$ and since
$u\circ\psi$ is subharmonic in $D$ it follows that $\log\,\lambda\circ \psi$
is subharmonic in $D$.
Notice that if $\gamma$ is a recitifable arcs in $\Omega$ then
\[
\int_\gamma\, \lambda(z)\cdot  |dz|
=\int_{\psi(\gamma)}\, \lambda\circ \psi(w)\cdot\frac{|dw|}{|\psi'(w)|}
\]
Set
\[ 
\lambda^*(w)=\frac{1}{|\psi'(w)|}\cdot \lambda\circ \psi(w)
\]
Then
\[ 
\log \lambda^*=-\log |\psi'(w)| +\log  \lambda\circ \psi
\] 
Here 
$\log |\psi'(w)|$ is the real part of the analytiuc function $\log \psi'(w)$
in $d$ and hence harmonic  which entails that
$\log\lambda^*$ is subharmonic.
The proof of (1) is now reduced to the case when
$\Omega$ is replaced by the unit $w$-disc where
$\lambda$ is replaced by $\lambda^*$.
Moreover, the Cauchy-Schearz inequality gives
\[
\frac{1}{2}
\bigl([\int_{\gamma_1}\, \lambda(z)\, |dz|]^2+
[\int_{\gamma_2}\, \lambda(z)\, |dz|]^2\bigr )\leq
\frac{1}{4}\cdot \bigl(\int_{\gamma_1\cup\gamma_2}\, \lambda(z)\, |dz|]^2\,\bigr)
= \frac{1}{4}\cdot \int_{|w|= 1\}}
\, \lambda^*(w)\, |dw|
\]
There remains only to find
a pair of curves $\alpha^*$ and $\beta^*$
in the $w$-disc where
$\alpha^*$ joins
the two points $\{e^{i\theta_\nu}\}$
on the unit circle where
the boundary  arcs $\psi(\gamma_1)$ and $\psi(\gamma_2)$ intersect
while
$\beta^*$ is a curve which joins some point
$p\in \psi(\gamma_1)$  with a point  $q\in  \psi(\gamma_2)$. 
\medskip


\noindent
{\bf{The choice of
$\alpha^*$ and $\beta^*$.}}
First $\alpha^*$ is the circular arc
with end-points at $e^{i\theta_1}$ and $e^{i\theta_2}$
and intersects $T$ at right angles.
Next, given a point $p\in\psi(\gamma_1)$ there exists the unique circular arc
$\beta^*$ which  intersects both
$\alpha^*$ and  $T$ at right angles. See figure § XX.
Now (1) follows if we have proved the inequality
\[
\bigl(\int_{\alpha^*}\, \lambda^*(w)\cdot  |dw|\,\bigr)^2+
\bigl(\,\int_{\beta^*}\, \lambda^*(w)\cdot  |dw|\,\bigr)^2\leq
= \frac{1}{4}\cdot \bigl(\int_{|w|= 1\}}
\, \lambda^*(w)\, |dw|\,\bigr)^2\tag{2}
\]

\medskip


\noindent
To prove
(2) we use a summetrisation of $\lambda^*$.
Recall from § xx that there
exists a Möbius transformation $T_1$
on the unit disc which is a reflection of $\alpha^*$, i.e.
it restricts to 
the identity map on $\alpha^*$ and the composed map
$T_1^2$ is the identity in $D$. Similarly we find the reflection $T_2$
of $\beta^*$.
As explained in § xx one has  $T_2\circ T_1=T_1\circ T_1$.
Let $S_0(w)=w$ be the identity while 
$S_1=T_1$, $S_2=T_2$
and $S_3= T_2\circ T_1$. Set
\[ 
\lambda^{**}(w)=
\frac{1}{4}\cdot 
\sum_{\nu=0}^{\nu=3}
\, \lambda(S_\nu(w))\cdot |\frac{S_\nu(w)}{dw}|\tag{3}
\]
Now $T_1$ maps $\alpha^*$ into itself, and similarly
$T_2$ maps $\beta^*$ into itself while the composed Möbius transformation 
$S_3=T_2\circ T_1$ interchanges the two curves. It follows 
that the left hand side in (2) is unchanged when 
replace $\lambda^*$ is replaced by  $\lambda^{**}$ and
the right hand side is also unchanged 
since the  $S$-transformations 
map $T$ onto itself.
Hence it suffices to prove (2)  when
$\lambda^*$ from the start is invariant with respect to the four
$S$-transformations. In this case
we solve the Dirichlet problem
using the boundary value function $\log\lambda^*$ on $T$ so that
\[ 
\log \lambda^*=u+H
\]
where $H$ is harmonic
in $D$ while  $u$ is subharmonic and zero on
$T$.
The maximum principle entails that
$u\leq 0$ in $D$ which gives 
\[ 
\lambda^*= e^u\cdot e^H\leq e^H\tag{4}
\]
Since $u=0$ the right hand side in (2) is unchagend while the left 
hand side is majorised when 
$\lambda^*$ is replaced by $e^H$.
The $S$-invariance of $\lambda^*$ implies that
$H$ also is $S$-invariant and as  explained
in §§ xx it follows that
there exists an analytic function $g(w)$ in $D$ such that
\[
 e^{H(w)}= |g'(w)|
\]
where 
the map $w\mapsto g(w)$
sends $\alpha^*$ to a real interval $[-A,A]$ and $\beta^*$
to an imaginary interval $[-iB,iB]$. Hence (4) implies that
the left  hand side in (2) is majorized by
\[ 
\bigl(\int_\alpha\, |g'(w)|\ |dw|)^2+
\bigl(\int_\beta\, |g'(w)|\ |dw|\,\bigr)^2=
4A^2+4B^2\tag{5}
\]
Next, since
$\lambda^*=|g'|$ holds on $T$
the right hand side in (2) becomes
\[
\frac{1}{4}\cdot\bigl(
\int_{|w|= 1}\,
|g'(w)|\, |dw|\,\bigr)^2\tag{6}
\]
The $S$-symmetry of $g$ entails thst
$\int_{|w|= 1}\,
|g'(w)|\, |dw|$ is four times
the
integral taken along
a subarc of $T$ which joins
consequtive points where $\alpha^*$ and $\beta^*$ intersect
and every suvh integral is the euclidian length of
the image curvr under $g$ which by the above joins
the real point $A$ with $iB$. So its euclidian length is
$\geq \sqrt{A^2+B^2}$, i.e. we have used that the shortest
distance between a pair of points is a straight line and then applied
Pythagoras' theorem.
Hence (6)  majorizes 
\[ 
\frac{1}{4}\cdot \bigl (4\cdot \sqrt{A^2+B^2}\bigr)^2=4(A^2+B^2)\tag{7}
\]
Then (5) and (7) give the
requested inequality (2).





\newpage

 

\centerline{\bf{Compact Riemann surfaces}}


\bigskip

\noindent
We assume that the reader is familiar with the notion
of  an abstract one-dimensional complex manifold 
$X$ and how
a covering by charts   defines the sheaf
$\mathcal O$ whose sections are holomorphic functions
and
basic
sheaf theory.
For the reader's convenience we have included appendices about sheaves and analysis
on two-dimensional manifolds.
From now on $X$ is a compact Riemann surface.


\medskip

\noindent
{\bf{Notations in § A-H.}}
Keeping  $X$ fixed we denote by
$\mathcal O$ the sheaf of holomorphic functions an $X$.
We have also the sheaf
$\Omega$ whose sections are holomorphic 1-forms.
Next, $\mathcal E$  denotes the sheaf of complex-valued $C^\infty$-functions
and passing to differential forms we have the two sheaves
$\mathcal E^{1,0}$ and $\mathcal E^{0,1}$.
The complex structure yields a decomposition 
\[ 
\mathcal E^1=\mathcal E^{1,0}\oplus \mathcal E^{0,1}
\]
and similarly 
the exterior differential  $d$ from $\mathcal E$ into $\mathcal E^1$
is decomposed as:
\[ 
d=\partial+\bar\partial
\]
Finally there exists the sheaf
$\mathcal E^{1,1}$ of differential forms
of maximal degree and  sheaf maps:
\[ 
\partial \colon  \mathcal E^{0,1}\to \mathcal E^{1,1}
\quad\colon\quad
\bar \partial \colon  \mathcal E^{1,0}\to\mathcal E^{1,1}
\]
We shall also employ currents. Denote by  
$\mathfrak{c}$ is the sheaf of currents whose sections 
over an open set $U$ in $X$
is the dual over the Frechet space
$\mathcal E^{1,1}(U)$. It means that $\mathfrak{c}(X)$ is the space of distributions on $X$
regarded as an oriented $C^\infty$-manifold.
We have also the sheaves
$\mathfrak{c}^{1,0}$ and
$\mathfrak{c}^{0,1}$ and 
passing to global sections one has
the inclusions
\[
\mathcal E(X)\subset\mathfrak{c}(X)
\quad\colon\,
\mathcal E^{1,0}(X)\subset\mathfrak{c}^{1,0}(X)
\quad\colon\, \mathcal E^{0,1}(X)\subset\mathfrak{c}^{0,1}(X)
\]
\medskip

\noindent
{\bf{The elliptic property of
$\bar\partial$.}}
If  $\gamma\in\mathcal E^{1,0}(X)$ is a 
$\bar\partial$-closed
the result from § XX entails that
it is a holomorphic 1-form, i.e in a chart $U$ where $x$ is a local coordinate
there exists $g\in\mathcal O(U)$ such that
\[ 
\gamma|U= g\cdot dx
\]
Passing to global sections we get the equality
\[ 
\Omega(X)= \text{ker}_{\bar\partial}( \mathcal E^{0,1}(X))\tag{*}
\]

\medskip

\noindent
{\bf{Divisors.}}
A divisor on $X$ is expressed by a finite sum:
\[ 
D=\sum\, k_\nu\cdot \delta(x_\nu)
\]
Here $\{x_\nu\}$ is a finite set of points in $X$ and
$\{k_\nu\}$ are integers.
The  set $\{x_\nu\}$ is called the support of
$D$ and the degree is  defined by:
\[ 
\text{deg}(D) = \sum k_\nu
\]
The class of divisors whose degree is zero is denoted by
$\mathfrak{D}_0$.
\medskip

\noindent{\bf{Principal divisors.}}
Denote by
$\mathcal M$  the sheaf of meromorphic  functions on
$X$.
If $f$ is a section over some open subset
$V$
it has an order at each
point in $V$. Namely, if
$a\in V$ we set
\[
\text{ord}_x(f)=k
\]
where $f(z)= z^k\cdot f_0(z)$ holds in some
chart $U$ which contains
$z$
while $U\subset V$ and  $f_0$ is holomorphic in
$U$ with
$f_0(a)\neq 0$. So here $k>0$ if $f$ has a zero of
multiplicity $k$ and $k<0$ when $f$ has a pole of order $-k$.
It is obvious that
set of points where the order is $\neq 0$ is a discrete subset
of $V$. When $f$ is a gobally defined meromorphic functions
the set of its poles and zeros are finite
and give the divisor
\[ 
D(f)= -\sum\, \text{ord}_{p_\nu}(f)\cdot \delta(p_\nu)-
\sum\, \text{ord}_{q_k} (f)\cdot \delta(q_k)
\] 
where the first sum is taken over the poles and the second over the zeros of $f$.
We refer to 
$D(f)$ as
the principal divisor 
associated to
$f$. Notice that the first minus sign aboe means that poles of $f$ 
yield positive integers in the sum which defines the degree of $D(f)$
The result from § 0. XX  shows that 
its degree is zero,  i.e. every principal
divisor belongs to $\mathfrak D_ 0$.



\medskip

\noindent
{\bf {The sheaves $\mathcal O_D$.}}
Let $D$ be a divisor on $X$.
Denote by $\mathcal O_D$  the subsheaf of
$\mathcal M$ whose sections
satisfy
\[
\text{ord}_a(f)\geq -D(a)
\]
for all points $a$ in the open set where
$f$ is defined as a meromorphic function.
\medskip

\noindent
{\bf Example.}
When  $p\in X$ and $n\geq 1$ is a positive integer we get
the divisor
$D=n\cdot p$. Here  $\mathcal O_D$ is the sheaf of meromorphic functions
whose sections have no poles outside $p$ 
while the order of the pole at $p$ is at most $n$.





\bigskip

\centerline{\bf{ Summary   about the material
in § A-H.}}

\medskip

\noindent {\bf{1. Divisors.}}
In § A we prove that 
the cohomology group
$H^1(X,\mathcal O_D)$
is a finite dimensional complex vector space and in § B the finite dimensionality is extended
to
the sheaves $\mathcal O_D$ where $D$ is an arbitrary divisor.
which gives the integer
\[ 
\chi(\mathcal O\uuu D)=
\text{dim}_{{\bf{C}}}[H^0(X,\mathcal O_D)]-
\text{dim}_{{\bf{C}}}[H^1(X,\mathcal O_D)]\tag{*}
\]


\medskip

\noindent The \emph{Riemann-Roch formula}  asserts that
\[
\chi(\mathcal O_D)=1-g+\text{deg}(D)\tag{**}
\] 
holds for every divisor $D$. This is
used to construct
non-constant
meromorphic functions on $X$. For example, let
$p\in X$ and consider the divisor $D=D_{(g+1)\cdot p}$ whose degree is $g+1$.
Then (**) gives
\[
\text{dim}_{{\bf{C}}}H^0(X,\mathcal O_D)=
1-g+(g+1)+\text{dim}_{{\bf{C}}}H^1(X,\mathcal O_D)\geq 2
\]
This shows that
there exists
a non-constant meromorphic function $f$ on $X$
which is holomorphic outside $p$ and has a pole 
at $p$
of
of order
$\leq g+1$ at most.






\medskip

\noindent
{\bf{2. The Dolbeault isomorphism.}}
By $C^\infty$\vvv partitions of the unity 
$\mathcal E$ is a  soft sheaf and has therefore
trivial cohomology.
The same holds for the sheaf
$\mathcal E^{0,1}$ whose sections are differential forms of
bidegree $(0,1)$.
Next, in every  chart of $X$ the 
inhomogeneous $\bar\partial$ equation has  a solution which
gives an exact sequence of sheaves:
\[
0\to \mathcal O\to \mathcal E
\overset{\bar\partial}\to \mathcal E^{0,1}\to 0
\]
This gives an exact sequence of complex vector spaces
\[
0\to \mathcal O(X)\to  \mathcal E(X)
\overset{\bar\partial}\to \mathcal E^{0,1}(X)\to H^1(X,\mathcal O)\to 0\implies
\]
\[
H^1(X,\mathcal O)
\simeq\frac{\mathcal E^{0,1}(X)}{\bar\partial(\mathcal E(X))}\tag {2*}
\]
If we consider the sheaf of all differential 1-forms
one has the isomorphism
\[
H^1(X,{\bf{C}})
\simeq\frac{\mathcal E^1(X)}{d(\mathcal E(X))}\tag{2**}
\]
The finite dimensionality of this topological cohomology group
follows from
existence of simplicial decompositions.
Next,
using (2*) we can exhibit the dual space of
$H^1(X,\mathcal O)$. Namely
the dual of the Frechet space
$\mathcal E^{0,1}(X)$ is $\mathfrak{c}^{(1,0)}$.
In a chart of $X$ where $z$ is a local coordinate a
current $\gamma\in \mathfrak{c}^{1,0}(X)$ is expressed by
\[ 
\gamma=\mu\cdot dz
\] 
where $\mu$ is a distribution in the chart.
Since
$H^1(X,\mathcal O)$ is finite dimensional, it follows from
(2*) that
$\bar\partial(\mathcal E(X))$ has finite codimension in
$\mathcal E^{0,1}(X)$ and is therefore a closed subspace.
A  current $\gamma\in \mathfrak{c}^{1,0}(X)$
vanishes on the subspace
$\bar\partial(\mathcal E(X))$ if and only if it is $\bar\partial$\vvv  closed.
In a chart where $\gamma$ is expressed as in (1) this means that
the distribution $\mu$ satisfies the equation
\[
\bar\partial(\mu)=0\tag{1}
\]
Since   the first order differential operator
$\bar\partial$ is elliptic the distribution
$\mu$ is a holomorphic density. Hence
the $\bar\partial$-closed current $\gamma$ is
a holomorphic 1 \vvv  form on $X$, i.e. a global section of the sheaf
$\Omega$.
Hence
there exists
a surjective  ${\bf{C}}$ \vvv linear map
\[
\Omega(X)\mapsto \text{Hom} \uuu {{\bf{C}}}(
\frac{\mathcal E^{0,1}(X)}{\bar\partial(\mathcal E(X)}),{\bf{C}})\tag{*}
\]


\medskip

\noindent
{\bf{The injectivity in (*)}}.
If 
$\omega\in \Omega(X)$ is not identically zero
we can construct the conjugate
(0,1)\vvv form $\bar \omega$ and find that
\[
 \int  \uuu X\,\omega\wedge\bar\omega>0
\]
We conclude that (*) also is injective which proves
that (*) is a duality isimorphism. In particular we get 
the equality
\[ 
g= \dim_{\bf{C}}(\Omega(X))
\]
\medskip

\noindent
{\bf{3. Another duality.}}
Starting from the sheaf $\Omega$ we have the exact sequence
\[ 
\Omega\to \mathcal E^{1,0}\overset{\bar\partial}\to
\mathcal E^{1,1}\to 0
\]
It follows that
\[ 
H^1(X,\Omega)\simeq
\frac{\mathcal E^{1,1}(X)}{\bar\partial(\mathcal E^{1,0}(X))}
\]
Hence the dual space
of 
$H^1(X,\Omega)$ can be identified with the space of
$C^\infty$-functions $f$ on $X$
such that
\[
 \int_X\, f\cdot \bar\partial(\gamma^{1,0})=0
 \] 
 for every test-form of bi-degree $(0,1)$.
 Stokes theorem  entails that
 \[
 0=\int_X\, \bar\partial(f)\,\wedge \gamma^{1,0})
 \quad\text{for all}\quad \gamma^{1,0}\in\mathcal E^{1,0}(X)
\] 
 We conclude that $f$ is holomorphic and hence one has  the isomorphism
 \[
 [H^1(X,\Omega)]^*\simeq \mathcal O(X)
 \] 
 which shows that
 the cohomology group
 $H^1(X,\Omega)$ is 1-dimensional.











\bigskip


\noindent
{\bf{4. The general duality theorem.}}
The duality in  (*) 
extends to
an arbitrary divisor $D$
and goes as follows.
We have the sheaf $\mathcal O\uuu D$
and introduce the sheaf
\[ 
\mathcal E\uuu D=
\mathcal O\uuu D\otimes\uuu \mathcal O\,\mathcal E\tag{1}
\]
Similarly we get the sheaves
$\mathcal E\uuu D^{(0,1)}$
and
$\mathcal E\uuu D^{(1,0)}$
which all become soft sheaves. Let
$\vvv D$ be the opposite divisor and put
\[ 
\Omega\uuu {\vvv D}=
\mathcal O\uuu {\vvv D}\otimes\uuu \mathcal O\,\mathcal E\tag{2}
\]
Then every global section  $\omega\in \Omega\uuu {\vvv D}(X)$ 
defines a continuous linear form on
$\mathcal E\uuu D^{(0,1)}(X)$ by
\[
\phi\mapsto \int\uuu X\, \omega\wedge \phi
\]
Exactly as in   the case of the trivial divisor one gets the isomorphism
\[
 \Omega\uuu {\vvv D}(X)\simeq \text{Hom}\uuu{{\bf{C}}}(
 \frac{\mathcal E\uuu D^{(0,1)}(X)}
{\bar\partial(\mathcal E\uuu D(X)}, {\bf{C}})\tag{***}
\]
We refer to (***) as the general duality theorem for compact Riemann surfaces
and the proof is given in § XX.
\medskip

\noindent
{\bf{5. A consequence of the duality.}}
To each divisor $D$ there exists the sheaf
$\Omega\uuu D$ whose 
Euler characteristic is defined by:
\[
\chi(\Omega\uuu D)=
\text{dim}_{{\bf{C}}}[H^0(X,\Omega_D)]-
\text{dim}_{{\bf{C}}}[H^1(X,\Omega_D)]\tag{1}
\]
Using the scyscraper sheaf associated to a divisor one finds
the formula
\[
\chi(\Omega\uuu D)=\chi(\Omega)+|D|\tag{2}
\]
\medskip

\noindent
From (*) and the duality in (C.4) we have in partcular:
$\chi(\Omega_X)=1\vvv g$ and hence that:
\[
\chi(\Omega\uuu D)=1-g+|D|\tag{3}
\]

 






\bigskip



\noindent{\bf{6. Abel's theorem.}}
Let 
$\mathfrak{D}_0$ be the family of divisors on
$X$ of degree zero.
If $f$ is a globally defined meromorphic function
we associate its principal divisor $D(f)$ 
where we assign positve integers at poles and negative integers at zeros.
In §  (0.2) we have seen that the degree 
$|D(f)|=0$.
The question arises when a divisor $D$ of degree zero is principal.
Let $D$ be such a divisor whose support 
consists of a family of points
points $q_1,\ldots,q_m$ whose $k$-numbers are $<0$ and 
another family of points
$p_1,\ldots,p_m$ whose $k$-numbers are $>0$.
Let $M=\sum^+\,k_\nu$ with the sum extended over
those $k_\nu$ which are $>0$.
Since $D$ has degree zero we can
pick $M$ many simple curves $\gamma_1,\ldots,\gamma_M$
where the end-points of  $\gamma_j$ consists of one $p$-point and one $q$-point.
Let $\omega_1,\ldots,\omega_g$ be a basis of the complex
vector space
$H^0(X,\Omega)$.
To each $1\leq j\leq g$ we assign the complex number
\[
\rho_j=\sum_{\nu=1}^{\nu=M}\, \int_{\gamma_\nu}\, \omega_j
\]
\emph{Abel's theorem}
asserts that all these $\rho$-numbers are zero if and only
if
the divisor $D$ is principal.
This   result is proved in § E
and leads to  interesting conclusions in § H relating
the Jacobi map with   the Picard group.










 






\newpage










\centerline{\bf{A. The cohomology group $H^1(X,\mathcal O)$}}

\bigskip

\noindent
Let $X$ be a compact Riemann surface and 
$\mathfrak U=\{U_\nu\}$ is
a finite covering of charts which gives 
the Cech complex
\[
0\to C^0(\mathfrak U,\mathcal O)\overset\delta\to
C^1(\mathfrak U,\mathcal O)\overset\delta \to
C^2(\mathfrak U,\mathcal O)\to\ldots
\]
where the arrows are the usual co-boundary 
maps. Above
\[
C^0(\mathfrak U,\mathcal O)=\oplus\,\mathcal O(U_\nu)
\quad\text{and}\quad
C^1(\mathfrak U,\mathcal O)=\oplus\,\mathcal O(U_\nu\cap U_j)
\]
A 1-cochain is an alternating  family
$\{ f_{\nu,j}\in \mathcal O(U_\nu\cap U_j)\}$, i.e.
$f_{\nu,j}= -f_{j,\nu}$ hold for all pairs $\nu,j,$.
The $\delta$-map from
$C^0(\mathfrak U,\mathcal O)$ into
$C^1(\mathfrak U,\mathcal O)$ is defined by
\[
\delta(\oplus f_j)=\{f_{\nu,j}= f_\nu-f_j\}
\]
Next, we have
$1$-cocycles
\[
Z^1(\mathfrak U,\mathcal O)=\{f_{\nu,j}\in
\mathcal O(U_\nu\cap U_j)\quad\text{such that}\quad
f_{\nu j}+f_{jk}+f_{k\nu}=0\}
\]
where the last equality holds whenever
the open set
$U_\nu\cap U_j \cap U_k\neq\emptyset$.
The  Cech cohomology group with respect to the covering
$\mathfrak{U}$
is defined by:
\[
H^1(\mathfrak U;\mathcal O)=
\frac{Z^1(\mathfrak U,\mathcal O)}{
\delta(C^0(\mathfrak U,\mathcal O))}\tag{*}
\]


\noindent
{\bf{A.1 Dolbeault formulas.}} 
Recall from § XX that the inhomogenous $\bar\partial$-equation
is solvable in every open subdomain of
${\bf{C}}$.
If $\mathfrak{U}$ is a  finite covering by charts
every intersection in this family
is
biholomorphic with a domain in
${\bf{C}}$. It follows
that for each $p\geq 0$ there is an exact sequence:
\[
0 \to C^p(\mathfrak U,\mathcal O)
\to C^p(\mathfrak U,\mathcal E)\overset{\bar\partial}\to
 C^p(\mathfrak U,\mathcal E^{0,1})\to 0\tag{i}
\]
Recall from § xx that $C^\infty$-partitions
of the soft sheaves
$\mathcal E$ and $\mathcal E^{0,1}$ entail that
\[
H^p(\mathfrak U;\mathcal \mathcal E)=
H^p(\mathfrak U;\mathcal \mathcal E^{0,1})\quad\colon\quad p\geq 1\tag{ii}
\]
Then  (ii) and the general result in
§ xx give
an exact sequence:
\[
H^0(\mathfrak U;\mathcal O)\to
H^0(\mathfrak U;\mathcal E)\to
H^0(\mathfrak U;\mathcal \mathcal E^{0,1})\to 
H^1(\mathfrak U;\mathcal O)\to 0\tag{iii}
\]
Moreover, 
the long exact sequence from § xx and the vanishing of higher cohomology
in (ii) give:
\[
H^p(\mathfrak U;\mathcal \mathcal O)=0)\quad\colon\quad p\geq 2\tag{iv}
\]



\noindent
Next, by definition 
\[
H^0(\mathfrak U;\mathcal \mathcal E^{0,1})=
Z^0(\mathfrak U;\mathcal \mathcal E^{0,1})=\mathcal E^{0,1}(X)
\]
Similarly $H^0(\mathfrak U;\mathcal E)=\mathcal E(X)$
and from 
(iii) we get:


\medskip

\noindent
{\bf{A.2 Theorem.}} \emph{For every finite covering by charts one has
an isomorphism:}
\[
H^1(\mathfrak U;\mathcal \mathcal O)\simeq
\frac{\mathcal E^{0,1}(X)}{\bar\partial(\mathcal E(X))}\tag{*}
\]
\medskip


\noindent
{\bf{A.3 The finite dimensionality of
$H^1(X,\mathcal O)$.}}
Every finite chart covering $\mathfrak{U}$
is acyclic with respect to
the sheaf $\mathcal O$. Hence
Leray's theorem in §§ implies that
the cohomology group
$H^1(X;\mathcal O)$ is equal to
the Cech cohomlogy 
$H^1(\mathfrak U;\mathcal \mathcal O)$.
To  see  that the complex vector space
$H^1(X;\mathcal O)$  has finite dimension 
we can argue as follows:
Let $\mathfrak{U_*}$
be another covering of charts which is refinement of
$\mathfrak{U}$ as explained in § xx.
This gives a map
\[
H^1(\mathfrak {U};\mathcal O)\to H^1(\mathfrak {U_*};\mathcal O)\tag{1.3.i}
\]
Recall  Montel's theorem  which asserts that 
when $V$ is a relatively compact subset of a domain $U$ in
${\bf{C}}$ then
the restriction map
$\mathcal O(U)\to \mathcal O(V)$ is compact. Since the map (1.3.i) is
an isomrphism it follows
from 
the general result from [functional analysis in  xx]  applied to the Frechet spaces defined
by sections of $\mathcal O$ over open sets)
that the common cohomology groups above have finite dimension.


\newpage

\centerline{\bf{B. The Riemann-Roch theorem}}
\bigskip


\noindent
Let $D$ be a positive divisor, i.e. the  integers $\{k_\nu\}$
in 
(1.2.0 )  are positive.
Now $\mathcal O$ is a subsheaf of $\mathcal O_D$ which gives
an exact sequence of sheaves:
\[
 0\to\mathcal O\to\mathcal O_D\to\mathcal S_D\to 0
 \] 
 where $\mathcal S_D$ is the scyscraper sheaf of $D$.
For the scyscraper sheaf $\mathcal S_D$
 one has 
 $H^1(X,\mathcal S_D)=0$ which gives
an
 exact sequence of
complex vector spaces:
 \[ 
 0\to H^0(X,\mathcal O)\to
  0\to H^0(X,\mathcal O_D)\to H^0(X,\mathcal S)\to 
  H^1(X,\mathcal O)\to
 H^1(X,\mathcal O_D)\to 0\tag{i}
\]
Recall from
§ xx that the higher cohomology groups
$H^p(X,\mathcal O)$ are zero if $p\geq 2$.
Set
\[ 
\chi(\mathcal O_D)=\dim_{\bf{C}}\, H^0(X,\mathcal O_D)-
\dim_{\bf{C}}\, H^1(X,\mathcal O_D)
\]
The exact sequence (i)  gives
the equality
\[
\chi(\mathcal O_D)= \chi(\mathcal O)+
\text{deg}(D)=1-g+\text{deg}(D)
\tag{ii}
\]




\medskip



\noindent
Above $D$ was a positive divisor. In general a divisor $D$ is
the difference of two positive divisors, i.e. $D=D_1-D_2$.
Here one has    the inclusion
\[ 
\mathcal O_{-D_2}\subset \mathcal O_D
\]
and exactly as above we have:
\[
 \chi(\mathcal O_D)=\chi(\mathcal O_{-D_2})+\text{deg}(D_1)
\]
The inclusion $\mathcal O_{-D_2}\subset\mathcal O$ gives
\[
 \chi(\mathcal O)=\chi(\mathcal O_{-D_2})+\text{deg}(D_2)
\]
Adding this two equations we obtain

\medskip

\noindent
{\bf{B.1 Theorem.}}
\emph{For every divisor $D$ one has the equality:}
\[
 \chi(\mathcal O_D)= \chi(\mathcal O)+\text{deg}(D_1)-\text{deg}(D_2)
= 1-g+\text{deg}(D)\tag{*}
\]


\bigskip



\noindent
{\bf B.2  Existence of meromorphic functions.}
Let $p\in X$  and 
consider the divisor $D=(g+1)\cdot p$. So here
$\mathcal O_D$ is the sheaf of meromorphic functions
with a pole of order
$\leq g+1$ at $p$ and otherwise it is holomorphic.
The Riemann-Roch formula gives
\[
\text{dim}_{\bf C}\,(H^0(X,\mathcal O_D))=
\text{dim}_{\bf C}\,(H^1(X,\mathcal O_D))+1-g+(g+1)
\geq 2\tag{i}
\]
This proves that 
$H^0(X,\mathcal O_D)$  contains a non-constant meromorphic function.
Hence there exists a non-constant meromorphic function
$f$ with a pole at $p$ of order $ g+1$ at most   and otherwise $f$  is holomorphic.





\bigskip

\centerline{\bf{C. The duality theorem}}
\medskip

\noindent
Denote by  $\Omega$  the sheaf of holomorphic 1-forms.
A section $\omega$ 
defined in some open set $V$ is given as follows:
If $U\subset V$ is a chart where
$z$ is the 
local coordinate then
\[ 
\omega|U= f(z)\cdot dz\quad\text{where}\quad f\in\mathcal O(U)\tag{1}
\]


\noindent
Let $\omega\in\Omega(X)$ be a global section.
For every globally defined differential form
$\sigma\in\mathcal E^{0,1}(X)$
we can integrate the 2-form
$\omega\wedge\sigma$ over 
$X$ and get the map:
\[ 
\sigma\to \int_X\,\omega\wedge\sigma\tag{2}
\]
If $\sigma$ is $\bar\partial$-exact,  i.e. if
$\sigma=\bar\partial(g)$ for some $C^\infty$-function we have:
\[ 
d(g\omega)=\bar\partial(g\omega)=
\bar\partial(g)\wedge \omega=-\omega\wedge\sigma
\]
By Stokes Theorem the integral
\[
\int_X\, d(g\omega)=0\tag{3}
\]

\noindent
We conclude that $\omega$ yields a linear functional on the quotient space
\[
\frac{\mathcal E^{0,1}(X)}{\bar\partial(C^\infty(X))}\tag{4}
\]
which by § XX is isomorphic to $H^1(X,\mathcal O)$. Hence we have found a 
linear map:
\[
L\colon\, \Omega(X)\mapsto H^1(X,\mathcal O)^*\tag{5}
\]


\noindent
{\bf{C.1 Theorem.}}
\emph{The $L$-map is an isomorphism}.
\bigskip


\noindent
\emph{Proof.} Recall that $\mathfrak{c}^{1,0}(X)$ is the dual of
$\mathcal E^{0,1}(X)$ and when a $(1,0)$-current 
$\gamma$ is zero on
the subspace $\bar\partial(C^\infty(X))$ it is $\bar\partial$-closed
which by the elliptic property means that
$\gamma$ is a holomorphic 1-form.
This shows that
$L$ is surjective. To see that
$L$ is injective we take some
non-zero $\omega\in\Omega(X)$ and construct the conjugate
$(0,1)$-form $\bar\omega$ and by the result in § xx one has 
\[ 
\int_X\, \omega\wedge \bar\omega=i\cdot A
\] 
where $A$ is a positive real number.
This shows that $L(\omega)$ is not identically zero and the proof is finished.

\medskip


\noindent
{\bf{C.2 A more  general duality theorem.}}
Let $D$ be a divisor and define the sheaf:
\[ 
\mathcal E_D=\mathcal O_D\otimes_{\mathcal O}\, 
\mathcal E
\]
Similarly we get the sheaf $\mathcal E_D^{0,1}$ and passing to the opposed sheaf
$-D$ we get the two sheaves
\[
\mathcal E_{-D}\quad\text{and}\quad \mathcal E_{-D}^{1,0}
\]
If $\phi\in \mathcal E_{-D}^{1,0}(X)$ and $\psi\in \mathcal E_D^{0,1}(X)$
the reader may check that there exists an integral
\[
 \int_X\, \phi\wedge\,\psi\tag{i}
\]
The Dolbeault isomorphism gives:
\[ 
H^1(X;\mathcal O_D)\simeq
\frac{\mathcal E_D^{0,1}(X)}{\mathcal E_D^(X))}\tag{ii}
\]
Next, we have the sheaf
\[
\Omega_{-D}= \mathcal O_{-D}\otimes_{\mathcal O}\,\Omega
\]
Now (i-ii) gives a canonical map
\[
 L_D\colon \Omega_{-D}(X)\to H^1(X;\mathcal O_D)^*\tag{iii}
\]


\noindent
{\bf{Exercise.}} Repeat the proof  from
the case when $D=0$ to show that $L_D$ is an isomorphism.





\bigskip

\noindent
{\bf{C.3 Another duality.}}
We have the exact sheaf sequence
\[
0\to\Omega\to \mathcal E^{1,0}\overset{\bar\partial}\to \mathcal E^{1,1}\to 0
\]
This gives
\[
H^1(X;\Omega)\simeq\frac{ \mathcal E^{1,1(X)}}{\bar\partial( \mathcal E^{1,0})}\tag{i}
\]
The dual space
$ \mathcal E^{1,1}(X)^*=C^\infty(X)$ and a 
$C^\infty$-function $f$
vanishes on the subspace
$\bar\partial(\mathcal E^{1,0})$ if and only if $\bar\partial(f)=0$,i.e. if
$f\in\mathcal O(X)$. Hence we have
\[
H^1(X;\Omega)^*\simeq\mathcal O(X)={\bf{C}}\tag{ii}
\]
it follows that
\[ 
\chi(\Omega)=g-1\tag{*}
\]


\newpage









\centerline{\bf{D. The Hodge decomposition.}}


\medskip

\noindent
The duality from § C implies that
\[ 
\dim_{\bf{C}}\,\Omega(X)=\dim_{\bf{C}}
\frac{\mathcal E^{0,1}(X)}{\bar\partial(\mathcal E(X))}\tag{1}
\]
Denote by $\bar\Omega(X)$ be the space of $\partial$-closed
$(0,1)$-forms, i.e they arise as conjugates of holomorphic 1-forms.
The map
\[
 \omega\to \bar\omega
\] 
is a ${\bf{C}}$-linear isomorphism and
from this the reader can conclude that we also have the equality
\[
\dim_{\bf{C}}\,\bar \Omega(X)=\dim_{\bf{C}}
\frac{\mathcal E^{1,0}(X)}{\partial(\mathcal E(X))}\tag{2}
\]
\medskip


\noindent
{\bf{D.1 Theorem.}} \emph{One has the two direct sum decompositions}

\[
\mathcal E^{1,0}(X)=\partial(\mathcal E(X))\oplus\Omega(X)
\quad\colon\quad
\mathcal E^{0,1}(X)=\bar \partial(\mathcal E(X))\oplus\bar \Omega(X)
\]


\noindent
{\bf{Exercise.}} Prove this result. The hint is to count dimensions via (1-2) above.
\medskip


\noindent
Next, $\Omega(X)$ and $\bar\Omega(X)$
both appear as subspaces of
$\mathcal E^1(X)$ and here we get another decomposition:

\bigskip

\noindent
{\bf{D.2 Theorem.}} \emph{One has }
\[
\mathcal E^1(X)=d(\mathcal E(X))\oplus \Omega(X)\oplus \bar\Omega(X)\tag{*}
\]


\noindent
\emph{Proof.}
Since $\mathcal E^1(X)=\mathcal E^{0,1}(X)\oplus \mathcal E^{0,1}(X)$
it is clear that the right hand side is equal to $\mathcal E^1(X)$.
There remains to show that one has a direct sum, i.e. suppose that
\[
dg+\omega_1+\bar\omega_2=0
\] 
where $g\in\mathcal E$ and $\omega_1,\omega_2$ is a pair of holomorphic
1-forms.
Write $dg=\partial g+\bar\partial g$ which gives
\[ 
\partial(g)= \omega_1\implies
\bar\partial(\partial(g))=0
\]
As explained in §§ x this means that $g$ is a harmonic function 
and by the maximum principle
reduced to a constant so that
$dg=0$. It follows that $\omega_1=\omega_2=0$
and the requested direct sum decomposition follows.



\bigskip


\noindent
{\bf D.3 A basis for $H^1(X,{\bf{C}})$}.
This  cohomology group is obtained via the ordinary $d$-complex, i.e.
we have the exact sequence of sheaves:
\[ 
0\to {\bf{C}}_X\to 
\mathcal E
\overset{d}\to \mathcal E^1
\overset{d}\to \mathcal E^2\to 0
\]
Using $C^\infty$-partitions of the unity it follows that:
\[
H^1(X,{\bf{C}})=\frac{\text{Ker}_d(\mathcal E^1(X))}{d(\mathcal E(X)}\tag{1}
\]
Theorem D.2 entails that

\[
H^1(X,{\bf{C}})\simeq \Omega(X)\oplus \bar\Omega(X)
\]


\noindent
So if  $\omega_1,\ldots,\omega_g$ is a basis for the $g$-dimensional vector space
$\Omega(X)$ then
$H^1(X,{\bf{C}})$ is $2g$-dimensional where a basis is given
by
this $g$-tuple of holomorphic forms and
the corresponding $g$-tuple $\{\bar\omega_\nu\}$.


\newpage




\centerline{\bf{E.  The Riemann\vvv Hurwitz formula.}}

\medskip

\noindent
Let $\omega$ be a non-zero global section in
$\Omega(X)$.
At each point $p$ we have a local chart
$U$ with coordinate $z$ and write
$\omega|U= g(z)\cdot dz$ where
the holomorphic function $g$ may have a zero of some order
$\geq 1$ at $p$. Such zeros can  occur at a finite set of points
and gives a positive divisor $D_\omega $ which assigns
positive integers at those $p\in X$ where
$\omega$ has a zero of some order $k\geq 1$.
It is clear that one has an equality of sheaves:
\[
\Omega=
\mathcal O_{D_\omega}\cdot \omega
\]
The left hand side is isomorphic to the sheaf
$\mathcal O_{D_\omega}$ so the Riemann-Roch theorem gives
\[ 
g-1=\chi(\Omega)
=1-g+\text {deg}D_\omega )\tag{1}
\]
Hence we have proved

\medskip

\noindent
{\bf{E.1 Theorem.}}
\emph{For every non-zero holomorphic 1-form the number of 
zeros counted with multiplicity
is
equal to $2g-2$.}
 
\medskip

\noindent
{\bf{E.2 The case of meromorphic forms.}}
If $\Omega$ is a meromorphic 1-form
we also encounter poles and get an associated
divisor
$D_\omega $ whose negative part
comes from poles counted by their order and from the above one has
\[ 
2g-2= \text{deg}(D_\omega)\tag{*}
\]
\medskip

\noindent 
This applies in particular when
$f$ is a meromorphic function and $\omega=\partial f$.
The divisor $D_{\partial f}$
has a negative part caused by poles of $f$. 
Notice that if $f$ has a pole of order $k$ at some
point $p\in X$ then
\[ 
\partial f=d(z^{-k}g)= -kz^{-k-1}\cdot dz+z^{-k}\cdot \partial g
\] 
which entails that
$\partial f$ has a pole of order $k+1$.
It follows that
if $\{p_\nu\}$
are the poles of $f$ with multiplicities
$\{k_\nu\}$ then
the negtive part of
$D_{\partial f}$ has degree
\[
\sum\, (k_\nu+1)
\]

\medskip

\noindent
{\bf{E.3  Zeros of $\partial f$.}}
If
$\zeta$ is a local coordinate at a point 
$q$ where $f$ has no pole write
\[ 
f(\zeta)= f(q)+ a\zeta^k+\text{higher order terms}
\implies df= ak\zeta^{k\vvv 1}+\text{higher order terms}
\]
If $k\geq 2$  we assign the positive one-point divisor $(k-1)\delta( q)$.
Taking the sum over all these  one-point divisors
we get the positive part of
the divisor $D_{\partial f}$.

\medskip

\noindent
{\bf{E.4 Example.}}
Suppose that the meromorphic function $f$ has degree $n\geq 2$.
Zeros of $df$ outside the poles
correspond to critical points under the holomorphic map
$f\colon X\to {\bf{P}}^1$. Their
images  are called critical values of the map.
If $\alpha$ is  a critical value the  inverse fiber
$f^{\vvv 1}(\alpha)$ consists of  strictly less than $n$ 
many points, say $q_1,\ldots,q_m$ where 
$df(q_j)=0$ for at least one $j$ and when this holds we refer to $q_j$
as a branch point under the mapping $f\colon X\to {\bf{P}}^1$.
In this way we get a finite set of branch points
$q_1,\dots,q_m$ and
let $\rho(q_j)$ be the order of the zero of $df$ at each $q_j$.
Hence
\[
\sum\, (\rho(q_j)-1)\cdot \delta(q_j)
\]
gives positive part of the divisor $D_{\partial f}$. 
In the case when all poles of $f$ are simpke each pole
contributes with degree 2 and as a result one has 
the degree formua
\[
2g-2= \text{deg}(D_{\partial f}= \sum\, (\rho(q_j)-1)-2n\tag{*}
\]


\bigskip


\noindent
{\bf{E.5 Calculations of some $g$-numbers}}
Consider an irreducible equation of the form
\[ 
y^m-Q(x)=0
\] 
where $Q(x)$ is a polynomial with simple zeros of some
degree $n$ and  $m\geq 2$.
Now 
\[ 
my^{m-1}dy =Q'(x)dx
\] 
It follows that
$dy$ has simple zeros when
$Q'(x)=0$ and counting multiplicities and
recalling that one has an $m$-sheeted covering
from the Riemann surface $X$ onto the projective $x$-line
the positive part of tthe divisor $D_{dy}$
has degree
\[ 
m(n-1)
\]
Next, above $x=\infty$ the meromorphic function $y$ has poles.
If the integers $m$ and $n$
are relatively prime wr recall from § § that there is a unique point above
$x=\infty$
and 
a local coordinate $t$ where $y=t^{-n}$. So the
degree of the negative
part of
$D_{dy}$ becomes $-(n+1)$.
From this  we get the genus formula:
\[ 
g=1+\frac{(m(n-1)}{2}-\frac{n+1}{2}\tag{1}
\]
\medskip

\noindent
When $n$ and $m$ have a common factor we write
$n=kn_*$ and $m=km_*$ where $n_*$ and $m_*$ are relatively prime.
In this case we get $k$ many charts above $x=\infty$ where $y$ has a pole of order
$n_*$ in each chart.
The result is that
\[
g=1+\frac{(m(n-1)}{2}-k\cdot \frac{n_*+1}{2}\tag{2}
\]
\medskip

\noindent
For  example, consider the equation
\[ 
y^4= x^2+x+1
\]
Here (xx) gives $g= 1+2-2\cdot 2=1$ so  $X$ is a torus.
\medskip


\noindent
{\bf{Exercise.}} Verify that in the example above
the 1-form
$\frac{dx}{y}$ is
holomorphic and $\neq 0$ on $X$ which
clarifies why $g=1$.

\newpage




\centerline{\bf{F. Weierstrass' points}}
\bigskip

\noindent
Let $X$ be a Riemann surface of some genus $g\geq 2$
Given  a point $p\in X$ we  ask  if there exists a
meromorphic
function $f$ on $X$  which is holomorphic in
$X\setminus\{p\}$
and the order of the pole at $p$ is $\leq g$.
If such a meromorphic function exists we say that
$p$ is a Weierstrass point and denote this set by 
$\mathcal W(X)$.
We shall prove that this is a non-empty subset of $X$  when
$g\geq 2$.
To achieve this 
we 
take  a basis $\omega_1,\ldots,\omega_g$ in the complex vector space
$\Omega(X)$.
\medskip

\noindent
{\bf {F.1. Wronskian  determinants.}}
Let $p\in X$ and choose a chart
$U_0$  around $p$ where $p$ is the origin and $z$
the local coordinate.
We get the $g$-tuple of holomorphic functions 
$\{f_\nu\}$
in $U_0$
defined by
\[ 
\omega_\nu|U_0=f_\nu(z)\cdot dz
\]
In the chart we  take higher order derivatives
with respect 
$\partial=\partial/\partial z$ and get 
the following $m\times m$-matrix
with elements in $\mathcal O(U_0)$:
\[ 
\phi_{m\nu}(z)= \frac{\partial^{m-1}(f_\nu)(z)}{(m-1)!}
\quad 1\leq m,\nu\leq g
\]
Set
\[ 
W(z)=\text{det}(
\phi_{m\nu}(z))\tag{i}
\]


\noindent
Since $f_1,\ldots,f_g$ are ${\bf{C}}$-linearly independent in the chart
$U_0$,  the general result in § XX shows that
$W(z)$ is not identically zero.
Next, let $\mathfrak U=\{U_i\}$ be a finite covering of $X$ by charts.
In each chart $U_i$ we choose a local coordinate
$z_i$ and construct the Wronskian
$W_i\in\mathcal O(U_i)$.
Consider a pair of charts where
$U_i\cap U_k\neq \emptyset $.
In the interesction we have
$z_k=z_k(z_i)$ and get the non-vanishing holomorphic function
\[
\frac{dz_k}{dz_i}\tag{ii}
\]
The transition formula from § XX gives:
\medskip

\noindent
{\bf F.2. Lemma.}
\emph{In each non-empty intersection
 $U_i\cap U_k$  we have}
\[ 
W_k=(\frac{dz_k}{dz_i})^N\cdot W_i\quad\colon\quad N=\frac{g(g+1)}{2}
\]
\medskip

\noindent
This gives a well defined finite subset
$\Sigma$ in $X$ such that for each chart $U_i$ one has
\[ 
\Sigma\cap U_i= W_i^{-1}(0)\tag{*}
\]



\noindent
{\bf{F.3. Theorem.}} \emph{Every $p\in  \Sigma$ is
a Weierstrass point.}
\medskip


\noindent
\emph{Proof.}
Let $(U,z)$ be a chart around $p$ and for each $1\leq\nu\leq g$
the restriction $\omega_\nu|U$ is of the form
$f_\nu(z)dz$ where $\{f_\nu\}$ in $\mathcal O(U)$.
Every $f_\nu$ has a Taylor expansion
\[
f_\nu(z)= a_{0,\nu}+ a_{1,\nu}z+\ldots+a_{g-1,\nu}z^{g-1}+
\quad\text{higher order terms}
\]
The hypotesis that the local Wronskian is zero at $p$
implies that the determinant of the  $g\times g$-matrix 
formed by the doubly-indexed $a$-coefficients is zero.
Hence there exists a non-zero $g$-tuple
$(c_1,\ldots,c_g)$ such that
\[
\sum_{j=0}^{j=g-1}\,  a_{j,\nu}\cdot c_j
=0\quad\colon\quad 1\leq\nu\leq g\tag{1}
\]
Next, in $U_0$ we consider the meromorphic function
\[
h(z)=\frac{c_1}{z}+\ldots+\frac{c_g}{z^g}\tag{2}
\]
It follows from (1) that
\[ 
\mathfrak{res}(\omega_\nu(h))=0 \quad\colon\quad 1\leq\nu\leq g\tag{3}
\]
Since $\omega_1,\ldots,\omega_g$
is a basis for $\Omega(X)$  the general result in
§ XX gives a globally defined meromorphic
function $H$ which is holomorphic in $X\setminus\{p\}$
whose polar expansion at $p$ is    $h$. In particular
$H$ has a pole of order $\leq g$ at $p$ and since no other poles occur we have
$p\in\mathcal W(X)$.


\bigskip

\noindent
{\bf {The divisor $\mathfrak{w}$}}.
The functions $\frac{dz_k}{dz_i}$ from (ii) are $\neq 0$
in each pair of overlapping charts. Hence there exists
a non-negative  divisor $\mathfrak{w}$ on $X$
where one for each chart $U_i$ has:
\[ 
\mathfrak {w}(x)=\text{ord}_x(W_i)\quad
x\in U_i
\]
\medskip

\noindent
{\bf F.4. Proposition.} \emph{One has the equality}
\[ 
|\mathfrak w|=g(g+1)(g-1)
\]

\noindent
\emph{Proof.}
Let $\omega\in\Omega(X)$
be a non-zero holomorphic 1-form. In each  chart we can write
\[ 
\omega|U_i=h_i(z)\cdot dz_i
\]
where the holomorphic $h$-functions satisfy
\[
h_k=\frac{dz_i}{dz_k}\cdot h_i\quad\text{ in}\,\, U_k\cap U_i
\]
It follows that
\[ 
h_k^{-N}= (\frac{dz_k}{dz_i})^N \cdot h_i^{-N}
\]
Hence 
$\{h_k^{-N}\}$ satisfies the same transition
formulas as the $W$-functions which gives
a globally defined meromorphic function
$F$ on $X$ such that
\[ 
F|U_i=W_i\cdot h_i^{-N}\tag{1}
\]
Next, the holomorphic
1-form
$\omega$ has its divisor $D_\omega$ whose degree becomes:
\[ 
|D_\omega|= 2(g-2)\tag{2}
\]
At the same time the principal divisor of
$F$ has degree zero and then (1-2) entail that
\[
|\mathfrak{w}|= N|D_\omega|= 2N(g-2)=g(g+1)(g-1)
\] 
where the last equality follows from Lemma F.2.


\medskip

\noindent
{\bf{F.5 Conclusion.}}
With  $g\geq 2$  the number of Weierstrass points is at   least
$g(g+1)(g-1)$.



\newpage










\centerline{\bf{G. Abel's theorem.}}
\medskip

\noindent
In § X
we have shown 
that if $f\in\mathcal M(X)$
then its principal divisor 
$D(f)$
has degree zero. Hence
we get a subset of
$\mathcal D_0$ given by
\[ 
\mathcal P_0=\{
D(f)\quad\colon\, f\in\mathcal M(X)\}
\]
We shall find a necessary and sufficient condition in order
that
a  divisor
$D\in\mathcal D_0$ belongs to $\mathcal P_0$.
To attain this
we shall 
represent divisors in $\mathcal D_0$ by chains.
Denote by
$\mathcal C$ the family of 
$C^1$-curves in $X$:
\[ 
t\mapsto  x(t)\quad\colon\,0\leq t\leq 1\tag{i}
\]
from the closed unit interval into $X$.
The curve in (i) has two end-points $p,q$ in $X$
and if $g$ is any $C^\infty$-function on $X$ we have
\[ 
g(q)-g(p)=\int_0^1\, g(x(t))\cdot \dot x(t)\, dt\tag{ii}
\]
Recall from calculus that (ii) does not depend upon the special parametrization
of the curve so we prefer to write (ii) as
$\int_c\, dg$
and $c$ is  called an elementary  1-chain whose boundary
$\partial(c)$ consists of the two points $q$ and $p$   reflected by the equations
\[ 
g(q)-g(p)=\int_c \, dg\quad\colon\quad g\in \mathcal E(X)\tag{ii}
\]
More generally, consider a finite family of
such curves $\{c_k\}$.  The sum
yields a 1-chain ${\bf{c}}$ where
\[
\int_{{\bf{c}}} \, dg=
\sum\, \int_{c_k}\,dg= \sum\, g(q_k)- \sum g(p_k)\tag{iii}
\]
where $\{(p_k,q_k)\}$ are the end-points of the individual $c$-curves
in the chain ${\bf{c}}$.
Since the manifold $X$ is connected
it is clear that if $N$ is a positive integer and
$\{p_k\}$ and $\{q_k\}$  an arbitrary pair of
$N$-tuples of points in $X$, then there exists a 1-chain
${\bf{c}}$ which consists of $N$ curves $c_1,\ldots,c_N$
where $c_k$ is a curve from  $p_k$ to  $q_k$
so that (iii) holds. 
Every divisor $D$ in $\mathcal D_0$ is represented by a pair of such
$N$-tuples $\{q_k\}$ and $\{p_k\}$ and we say that
a 1-chain ${\bf{c}}$ represents $D$ if
\[
\int_{{\bf{c}}} \, dg=\sum\, g(q_k)- \sum g(p_k)\quad\colon\, g\in\mathcal E(X)
\tag{*}
\] 
\medskip



\noindent
{\bf {G.1 Theorem.}}
\emph{A divisor $D$ in $\mathcal D_0$
belongs to $\mathcal P_0$ if and only it can be represented by an oriented 
1-chain ${\bf{c}}$ 
such that }
\[
\int_c\,\omega=0\quad\text{for all}\,\,\omega\in\Omega(X)\tag{*}
\]



\medskip

\noindent
First we carry out some general constructions.
If $c$ is an
elementary and oriented
1-chain then
an arbitrary 1-form $\gamma$ can be integrated along 
$c$ and in this way 
$c$ is identified with a current of degree one.
More generally, a chain expressed by a sum of
elementary chains yields 1-current.
Moreover, when an elementary
1-chain $c$ is defined
by a map $t\to x(t)$ as in (i) above we can
take a partition of the interval $[0,1]$ and express
$c$ as a sum of elementary chains where
$t\to x(t)$ in each small partition is such that
the range stays in a chart of $X$.
Hence every 1-chain $c$ is a finite sum of
elementary 1-chains $\{c_\alpha\}$ where each single $c_\alpha$ is
contained - or rather supported as a current - by a  chart in
$U_\alpha$ in $x$ which in local coordinates
can be taken as an open disc.
\medskip

\noindent
{\bf{The currents $\frac{d\Phi}{\Phi}$.}}
Let $U$ be a chart which in local coordinates
is an open disc
centered at  $z=0$.
In this chart
there exists a  function
\[ 
\phi(z)=\frac{z}{z-z_0}\cdot a(z)
\]
where $z_0\neq 0$ in the disc while
$a\in C^\infty(X)$
is zero-free
and 
chosen so that $\phi$ is identicallly one outside a compact 
subset of $U$.
Now there exists the current of degree one in $X$ which has a compact support contained
in $U$ and in the chart
it is given by
\[
\frac{d\phi}{\phi}=\frac{da}{a}+\frac{dz}{z}-\frac{dz}{z-z_0}\tag{1}
\]
\medskip


\noindent
{\bf{Exercise.}}
Above we have a 1-current which can be
decomposed into a sum of currents of bi-degree
$(0,1$ and $(1,0)$. Show that
the component of bi-degree $(0,1)$ is 
the smooth current
\[
a^{-1}\cdot \bar\partial a
\]
Apply also Cauchy's residue formula 
in the chart and show  that if $g\in\mathcal E(X)$
then
\[
\int_X\,\frac{d\phi}{\phi}\wedge dg
= 2\pi i(g(q)-g(p))
\] 
where $p\in X$  corresponds 
to $z=0$ and  $q$  to $z_0$ in the chart.
The reader should make a figure to check that
the signs are okay because  Stokes Theorem is applied
in exterior domains in the complement of
 small punctured discs at $z=0$ and $z=z_0$.
\medskip


\noindent
Next,
let $c$ be a 1-chain and perform a decomposition so that
$c=\sum c_j$ where every $c_j$ is an elementary chain
with compact support in a chart $U_j$. We can carry out the construction above to
each $j$ and obtain
the current
\[ 
\rho=
\sum\,\frac{d\phi_j}{\phi_j}
\]
Next, let $\gamma$ be a closed 1-form in $X$. 
Its restriction to
a chart $U_j$ is exact and if $K_j$ is a compact subset of $U_J$
whose interior contains
the union of the support of the elementary 1-chain and the support of
the current $\rho_j$, then we can find
$g\in\mathcal E(X)$ such that
\[ 
\gamma= dg+\gamma^*
\]
where the support of the 1-form
$\gamma^*$ is disjoint from $K_j$.
It follows that
\[
\rho_j(\gamma)= \rho_j(dg)= \int_c\, dg= \int_c\,\gamma\tag{1}
\] 
where the last equality follows since
the support of $c$ does not intersect the support of $\gamma^*$.
Next, with $c=\sum\, c_j$ we associate the current
\[
\rho= \frac{1}{2\pi i}\cdot \sum\, \frac{d\phi_j}{\phi_j}
\]
A summation over $j$ gives the equation below for
every closed 1-form $\gamma$:
\[
\int_c\,\gamma= \rho(\gamma)\tag{*}
\]


\medskip

\centerline{\emph{Proof of sufficiency}}
\medskip

\noindent
Suppose the divisor $D$ is represented by a 1-chain $c$
for which (*) holds in Theorem G.1.
Construct the current $\rho$ as above. 
Each $\omega\in\Omega(X)$ is closed
and hence (*) above  entails that
\[
0=\rho(\omega)=0
\]
Since $\omega$ is a test-form of bi-degree $(1,0)$
we apply the $(0,1)$-part of $\rho$
which by (xx)  is a
smooth current 
given by
\[ 
\rho^{0,1}= \frac{1}{2\pi i}\cdot \sum\,a_j^{-1}\cdot \bar\partial a_j
\]
Since $\rho^{0,1}$
applied to every $\omega\in\omega(X)$ gives zero, the duality result in
§ XX implies that it is
$\bar\partial$-exact. Hence there 
exists $G\in C^\infty(X)$ such that
\[ 
\bar\partial(G)=\rho^{0,1}
\]
Outside the
the union of the finite set of pairs
$\{p_j,q_j\}$ there exists the function
\[ 
\Psi= e^{-G}\cdot \prod\,\phi_j
\]
Here (xx) and (xx)  give 
$\bar\partial(\Psi)=0$
outside the finite union above
and by  
the local constructions of the $\phi$-functions
in the charts
we see that
$\Psi$ has at most simple poles at $\{p_j\}$
and yields a  globally defined meromorphic function on $X$.
Next, we also have the equation 

\[ 
\frac{d\Psi}{\Psi}=
\frac{d\Phi}{\Phi}-dG
\]
If $g\in\mathcal E(X)$ it follows that
\[
\int_X\, \frac{d\Psi}{\Psi}\wedge dg=
\int_X\, \frac{dF}{F}\wedge dg=\int_c\,dg
\]
Since the 1-chain $c$ represents the given divisor  $D$ it follows
that the principal divisor $D(\Psi)= D$
which proves the sufficiency in Theorem G.1.

\bigskip

\centerline{\emph{G.2 Proof of necessity}}.
\medskip

\noindent
We must  prove that  when $f\in\mathfrak{M}(X)$ and 
$D=\text{div}(f)$ 
then (*) holds in Theorem G.1. To begin with $f$ yields a holomorphic map from
$X$ onto ${\bf{P}}^1$.
So if $\gamma$ is a smooth 1\vvv form on ${\bf{P}}^1$ there exists the pull\vvv back
$f^*(\gamma)\in\mathcal E^1(X)$. If $\omega\in\Omega(X)$
we therefore obtain a 1\vvv current $f\uuu *(\omega)$ on
${\bf{P}}^1$ defined by
\[
\langle f\uuu *(\omega),\gamma\rangle =\int\uuu X\, \omega\wedge f^*(\gamma)
\quad\colon\quad \gamma \in \mathcal E^1({\bf{P}}^1)
\tag{1}
\]

\medskip

\noindent
Let us now consider some
function 
$g\in C^\infty({\bf{P}}^1)$.
Since $f\colon X\to {\bf{P}}^1$ is a holomorphic mapping it follows that
$g\circ f\in C^\infty(X)$ and since $\omega$ is a holomorphic 1-form
Stokes Theorem gives
\[ 
\int_X\,\omega\wedge \bar\partial(g\circ f)=0
\]
Recall from § XX that $f_*$ commutes with differentials which entails that
the $(1,1)$-current $\bar\partial(f_*(\omega))$ on ${\bf{P}}^1$
satisfies
\[
\langle\bar\partial(f_*(\omega)),g\rangle =
\langle f_*(\omega),\bar\partial(g)\rangle=
\int_X\,\omega\wedge \bar\partial(g\circ f)=0
\]
Since this vanishing hold for every
$g\in C^\infty({\bf{P}}^1$
it follows that
$\bar\partial(f_*(\omega))=0$, i.e. the $(1,0)$-current
$f_*(\omega)$ is $\bar\partial$-closed.
Now $\bar\partial$ is elliptic and therefore
$f_*(\omega)$  belongs to $\Omega({\bf{P}}^1)$.
But on the projective line there do not exist non-zero holomorphic
1-forms by the result in § XX.
We conclude that
$f_*(\omega)=0$, i.e. we have proved the following:
\medskip

\noindent
{\bf{G.3 Proposition.}}
\emph{For each pair $f\in\mathfrak{M}(X)$ and 
$\omega\in\Omega(X)$ the direct image current
$f_*(\omega)$ is zero.}


\medskip


\noindent
There remains to see why Proposition G.3
enable us  to construct a 1-chain ${\bf{c}}\in\text{rep}(D(f))$ 
such that (*) holds in Theorem G.1.
Let us first consider the case when
the meromorphic function $f$ has some degree $n$ with
$n$  simple zeros $p_1,\dots,p_n$ and 
$n$  simple poles $q_1,\dots,q_n$.
On ${\bf{P}}^1$
we have the finite set $\xi_1,\dots,\xi_k$ which yield critical
values of the mapping
$f\colon X\to {\bf{P}}^1$. Let $\Sigma$ denote the  set
$\xi_1,\dots,\xi_k$ and put
\[ 
X_*= X\setminus \cup\, f^{-1}(\Sigma)
\]
Now  $f\colon X_*\to  {\bf{P}}^1\setminus \Sigma$
is an $n$-sheeted unbranched covering map which
in addition is locally biholomorphic.
Let $c_*$ be a simple closed curve which joins
the origin in
${\bf{P}}^1$ with the point at infinity and avoids the set $\Sigma$.
Then 
$f^{-1}(c_*)$ consists of $n$ pairwise disjoint
simple curves $c_1,\dots,c_n$ where $c_k$ joins some zero $p_k$ with a pole 
indexed to be $q_k$.
Hence the 1-chain
\[ 
{\bf{c}}= c_1+\ldots+c_n
\] 
represents $D(f)$.
Finally, since
$f\colon X_*\to {\bf{P}} 1$
is locally biholomorphic  the general result in
§ XX gives:
\[
\int_{{\bf{c}}}\,\omega= \langle f_*(\omega),c_*\rangle
\] 
The right  hand side is  zero by Proposition G.3
and since this hold for every $\Omega\in\omega(X)$
the representing 1-chain ${\bf{c}}$ satisfies (*) in
Theorem G.1 and the  necessity is proved.



\bigskip


\newpage

\centerline{\bf{H. Jacobi integrals.}}
\bigskip

\noindent
Let $X$ be a Riemann surface with genus $g\geq 1$.
The manifold $X$ has a fundamental group $\pi_1(X)$ whose
elements can be identified with homotopy classes of closed curves
of class $C^1$ at any given point in $X$.
Fix $p\in X$
and for each closed
$C^1$-curve $\gamma$ which has $p$ as commen start- and end-point
its homotopy class in this family of closed curves in denoted by $\{\gamma\}$.
If $\omega\in\omega(X)$
we get integrals
\[ 
\int_\gamma\,\omega
\]
Since $\omega$ is a closed 1-form 
the general result in § XX shows that this integral only depends upon
$\{\gamma\}$. Hence there exists   a complex-valued function on
$\pi_1(X)$ defined by
\[ 
\{\gamma\}\mapsto \int_\gamma\,\omega\tag{i}
\]
If $\gamma_1,\gamma_2$ are two closed curves
at $p$
the homotopy class of  the composed curve
$\gamma_2\circ\gamma_1$
is the product $\{\gamma_2\}\cdot \{\gamma_2\}$
in  $\pi_1(X)$ and we have the additive formula:
\[
\int_{\gamma_2\circ\gamma_1}\,\omega=
\int_{\gamma_2}
\,\omega+\int_{\gamma_1}
\,\omega
\]
Hence (i)  is a group homomorphism from
$\pi_1(X)$ into the additive group of complex numbers.
\medskip


\noindent
Next, let $\omega_1,\ldots,\omega_g$ be a basis in $\Omega(X)$.
Then we obtain an additive map from
$\pi_1(X)$ into the $g$-dimensional complex vector space
defined by
\[
\{\gamma\}\mapsto (\int_{\gamma}\,\omega_1,\ldots
\int_{\gamma}\,\omega_g)\tag{*}
\]
Its image yields an additive subgroup of ${\bf{C}}^g$  denoted by
$\Gamma$ and called  the period group associated to
the given basis $\omega_1,\ldots,\omega_g$ in $\Omega(X)$.
\medskip

\noindent
{\bf{Exercise.}}
Show that $\Gamma$ only depends on
 $\omega_1,\ldots,\omega_g$. More precisely, let  $q\in X$ be another point
 where
 $\pi_1(X)$ is represented by closed curves which start and end
 at $q$. Then the resulting $\Gamma$-group is the same, i.e. the chosen
 base point $p\in X$ does not affect the position of $\Gamma$.
\medskip

\noindent
 An additive subgroup
 $G$ in ${\bf{C}}^g$ is called a ${\bf{Z}}$-lattice if it
 is a free abelian group of rank $2g$
 whose basis vectors are ${\bf{R}}$-linearly independent
 vectors in ${\bf{C}}^g$ which can be identified with
 a real vector space of dimension $2g$. 
  \medskip

\noindent
{\bf{H.1 Theorem.}}\emph{ The period group $\Gamma$ is a lattic in
${\bf{C}}^g$.}
\medskip


\noindent
The proof requires some preliminaries.
To begin with, with a chosen base point $p$
we  study $C^1$-curves 
which in general are non-closed  starting at $p$
and with varying end-points in $X$. If
$\omega\in\Omega(X)$
and $c_x$ denotes  a curve from $p$ to a point $x\in X$
we get the line integral
\[
\int_{c_x}\, \omega
\]
If $c_x$ and $d_x$ are two such curves 
the composed  curve
$\gamma= d_x^{-1}\circ c_x$ is closed
which entails that the difference
\[
\int_{d_x}\, \omega-\int_{c_x}\, \omega=
\int_\gamma\, \omega
\]
We conclude that
there exists a mapping $\mathcal J_p$ from
$X$ into the quotient group $\frac{{\bf{C}}^g}{\Gamma}$ defined by
\[
\mathcal J_p(x)=\sum_{k=1}^{k=g}\,\overline{
\int_{c_x}\, \omega_1,\ldots\int_{c_x}\, \omega_g)}
\]
where $c_x$ is an arbitrary $C^1$-curve $c_x$ from $p$ to $x$.
and we have taken the image of the complex $g$-vector in
the quotient group above.
We refer to $\mathcal J_p$ as a Jacobi map at the base point $p$.

\newpage

\noindent
Choose $g$  different base points
$p_1,\ldots,p_g$ and 
and for every  $g$-tuple of points $x_1,\ldots,x_g$ in $X$ we
put
\[ 
F(x_1,\ldots,x_g)=\sum_{j=1}^{j=g}\, \mathcal J_{p_j}(x_j)
\]
Hence $F$ is a map from the $g$-fold product $X^g$ into
$\frac{{\bf{C^g}}}{\Gamma}$.
\medskip

\noindent
{\bf{H.2 A local study of $F$.}}
Around each $p_j$ we choose a chart $U_j$ where
$z_j$ is a local coordinate
so when $(z_1,\ldots,z_g)$ is close to the origin in the
$g$-dimensional $z$-space we  the ${\bf{C}}^g$-valued function
\[
\Phi(z)= F(p_1+z_1,\ldots,p_1+z_g)
\]
where  $\Phi=(\phi_1,\ldots \phi_g)$ and
\[
\phi_k(z_1,\ldots,z_g) = \sum_{j=1}^{j=k}\, \int_0^{z_j}\, \omega_k
\]
At $z=0$ we
get the $g\times g$-matrix
with elements
\[ 
\rho_{jk}= \frac{\partial \phi_k}{\partial z_j}(0)
\]
To find the $\rho$-numbers we express the 1-forms
$\{\omega_k\}$ in each chart, i.e.  write
\[ 
\omega_k|U_j= f_{kj}(z)\cdot dz_j
\]
Then it is clear that
\[
\frac{\partial \phi_k}{\partial z_j}(0)=f_{kj}(0)
\] 
hold for all pairs $j,k$.
Hence the Jacobian of $\Phi$ at $z=0$ is the $g\times g$-matrix
with elements $\{f_{kj}(0)\}$.

\medskip

\noindent
{\bf{H.3 A favourable choice of $p_1,\ldots,p_g$}}.
The matrix $\{f_{kj}(0)\}$ depends 
on the chosen $g$-tuple $p_1,\dots,p_g$.
We will prove
that for a suitable choice of this $g$-tuple
the matrix is non-singular.
To see this we notice that if
the matrix is singular there exists a non-zero $g$-tuple of complex numbers
$\alpha_1,\ldots,\alpha_g$ such that
\[
\sum\, \alpha_k\cdot f_{kj}(0)=0\quad\colon\quad 1\leq j\leq g\tag{i}
\]
Now we consider the holomorphic 1-form
\[ 
\omega= \alpha_1\omega_1+\ldots+\alpha_g\omega_g\tag{ii}
\]
The vanishing in (i) shows that
$\omega$ has a zero at every $p_j$.
The next result shows that this cannot  occur for suitable $g$-tuples of $p$-points.
\medskip

\noindent
{\bf{H.4 Lemma.}}
\emph{There exists a $g$-tuple $p_1,\ldots,p_g$ in $X$ with the property that
a holomorphic 1-form $\omega$ which is zero at each $p_j$
must be identically zero.}
\medskip

\noindent
\emph{Proof.}
To each $p\in X$ we set
\[
H_p=\{ \omega\in\Omega(X(\,\colon\ \omega(p)=0\}
\]
Each $H_p$ is either $\Omega(X)$ or a hyperplane and
at the same time
\[ 
\bigcap_{p\in X}\, H_p=\{0\}
\]
Since the vector space
$\Omega(X)$ is $g$-dimensional it follows by elementary geometry
that
there exists some $g$-tuple $p_1,\ldots,p_g$ such that
\[ 
H_{p_1}\cap\ldots\cap H_{p_g}= \{0\}
\]
Clearly every such $g$-tuple does the job in Lemma H.4.
\medskip

\noindent
{\bf{H.5 Conclusion.}}
We can always find some $g$-tuple $p_1,\ldots,p_g$ such that
the Jacobian  of the $\Phi$-function above is $\neq 0$ at $z=0$.
This entails that
if the charts $U_1,\dots,U_g$ are taken as small discs
then
$F$ yields a bijective map from the polydisc  $U_1\times\ldots U_g$
onto an open neighborhood $V$ of the origin in ${\bf{C}}^g$.
In fact, it is even a biholomorphic mapping.
Using this local result one has:

\medskip

\noindent
{\bf{H.6 Proposition.}}
\emph{The intersection $\Gamma\cap V$ is reduced to the origin in
${\bf{C}}^g$.}
\medskip

\noindent
\emph{Proof.} Via Abel EASY ...

\bigskip

\noindent
{{\bf{H.7 The Picard group.}}
Every $f\in\mathfrak{M}(X)$ yields a principal divisor $D(f)$ which belongs to
$\mathcal D_0$. These principal divisors give  an additive subgroup
denoted by $\mathcal P_0$ and we obtain
the quotient group
\[ 
\text{Pic}(X) =\frac{\mathcal D_0}{\mathcal P_0}\tag{*}
\]
If $D\in\mathcal D_0$ we choose a representing 1-chain $c$
and assign the point in $\frac{{\bf{C}}^g}{\Gamma}$ given by

\[
\overline{\bigl(\int_c\omega_1,\dots,\int_c\,\omega_g\bigr)}\tag{i}
\]
Its image in
$\frac{{\bf{C}}^g}{\Gamma}$
is unique since two different one-chains $c$ and $d$
for which $D=\partial(c)=\partial(d)$
yield the 
a closed chain $c-d$.
Moreover,
Abel's theorem shows that
$D=D(f)$ for a meromorphic function $f$ if and only if 
is a principal  divisor  if and only if (i) is zero in the quotient group.
From this one
concludes the following:
\medskip


\noindent
{\bf{H.8 Theorem.}}
\emph{By (i) above we have an injective mapping from
$\text{Pic}(X)$ into
$\frac{{\bf{C}}^g}{\Gamma}$.}
\bigskip


\noindent
{\bf{H.9 Remark.}}
Since $\Gamma$ is a lattice in
${\bf{C}}^g$ the complex analytic structure on the affine space induces a complex analytic structure on the quotient which therefore becomes
 a compact complex analytic manifold of  dimension $g$. One refers to
 $\frac{{\bf{C}}^g}{\Gamma}$ as a $g$-dimensional complex torus.
One  can say more about the map in Theorem H.8:

 
 \medskip
 
 \noindent
 {\bf{H.10 Theorem.}}
 \emph{The  map in Theorem H.8  is also surjective and hence one has
 a set-theoretic bijection}
 
 \[ 
 \text{Pic}(X)\simeq
 \frac{{\bf{C}}^g}{\Gamma}
\]
\bigskip

Proof EASY by previous locally conformal mapping...

\bigskip

\noindent
{\bf{H.11 Additive representations of $\pi_1(X)$}}
Suppose that $\psi\colon\,\pi_1(X)\to {\bf{C}}$ is
a group homomorphism where
${\bf{C}}$  the additive group of complex numbers and hence an
abelian group.
If $g$ is the genus of $S$ topology teaches that
the fundamental group is free of rank $2g$ and generated
by $2g$ many simply closed curves
$\gamma1,\ldots,\gamma_{2g}$ 
which issue from some chosen point $p\in X$ and
surround the $g$ many handles in a suitable fashion
An arbitary  additive representation is 
therefore determined by a $2g$-tuple of complex numbers
$\{c_\nu\}$. If it  is induced via integrals of some 
$w\in\Omega(X)$
one has
\[ 
\int_{\gamma_\nu}\, w= c_\nu
\]
Here $1\leq\nu\leq 2g$
and since
$\Omega(X)$ is $g$-dimensional it is in general not possibe to find
$w$, i.e. only special $2g$-tuples $\{c_\nu\}$
give the existence of $w$.



\newpage





\centerline{\bf{I. Non-compact Riemann surfaces}}



\bigskip

\noindent
{\bf{Introduction.}}
Sheaves and currents will be used in the subsequent proofs.
The crucial result in this chapter are  the following vanishing theorems.

\medskip

\noindent
{\bf{0.1 Theorem.}}
\emph{For every non-compact Remann surface one
has
 $H^1(X,\mathcal O)=0$.}
\bigskip

\noindent
Next, let $\mathcal O^*$ be the multiplicative sheaf whose sections
are zero-free holomorphic functions.

\medskip


\noindent
{\bf{0.2 Theorem.}}
\emph{The cohomology group $H^1(X,\mathcal O^*)=0$.}
\medskip

\noindent
A locally free sheaf of $\mathcal O$-modules of rank one is called
a holomorphic line bundle
As explained in § xx the family of holomorphic line bundles
correspond to elements in
$H^1(X,\mathcal O^*)=0$. So Theorem 0.2 means that
every holomorphic line bundle $\mathcal L$
is holomorphically trivial
and as a sheaf  therefore isomorphic to
$\mathcal O$ which by Theorem 0.1 entails that
\[
H^1(X;\mathcal L)=0\tag{*}
\]


\noindent
However, to  prove Theorem 0.2 we shall  need 
(*) and we shall later on explain how
(*) can be established in a similar way as in the special case
$\mathcal L=\mathcal O$.
\medskip

\noindent
{\bf{0.3 Some  cohomology groups.}}
The sheaf $\Omega$ is a locally free sheaf of $\mathcal O$-modules of rank one
and there is  the exact sequence of sheaves:
\[ 
0\to {\bf{C}}_X\to \mathcal O\overset\partial\to \Omega\to 0
\]
Passing the the long exact sequence of cohomology
the vanishing in
(*)  entails that
\[ 
H^2(X,{\bf{C}}_X)=0
\]
From this
it follows trivially - see § xx - that
if the complex field ${\bf{C}}$ is replaced by the field of rational numbers
then
\[
H^2(X,Q_X)=0\tag{i}
\]
Next,   the exponential map
which sends a holomorphic function $f$ to
the zero-free function $e^{2\pi i f}$
gives an exact sequence of sheaves:
\[
0\to {\bf{Z}}_X\to \mathcal O\overset{\text{exp}}\to \mathcal O^*\to 0
\]
Passing to the long exact sequence of cohomology  we get
\[
H^1(X,\mathcal O^*)\simeq
H^2(X,{\bf{Z}}_X
\]
So Theorem 0.2 anounts to show that
the last cohomology group is zero.
We have already  (i) so 
Theroem 0.2 is
"almost" derived from 
(*).
However, extra arguments will be needed to 
get Theorem 0.2 which we begin to explain.
Let  $\mathcal L$
ibea holomorphic line bundle.
By definton it is trivial, i.e. isomorphic to $\mathcal O$ if and only if it
has a global generating section.
Suppose to begin with that one has found
a non-constant global section $\xi\in \mathcal L$.
The zeros of $\xi$ is some (possibly empty) discrete set in $xX$.
Let $\{q_\nu\}$ be these zeros and $\xi$ vanishes of some
order $k_\nu$ at $q_\nu$.
Suppose we have
found
a meromorphic function $g$ in $X$
with poles of order $k_\nu$ at every
 $q_\nu$ while $g$ is a zero-free holomorphic function outside this
 discrete set.
 Then $g\cdot \xi\in\mathcal L(X)$ is 
 a global section which gives the requested
trivialisation so that
 $\mathcal L\simeq \mathcal O$.
 So in order to get Theorem 0.2 we need to 
 prove the existence of globally defined meromorphic functions
 with prescribed
 poles on  discrete subsets  of  $X$.
The whole discussion has shown that Theorem 0.2 follows if we in addition to
Theorem 01 and its extension in  (*) have established the following:
\medskip

\noindent
{\bf{0.4 Theorem.}}
\emph{Every divisor $D$ on $X$ is principal, i.e.
equal to $D(f)$ for some
$f\in\mathfrak {M}(X)$.}

 
 
\bigskip


\noindent
{\bf{0.5 Runge's theorem.}}
Recall from § xx that an open subset $Y$ in $X$ is a Runge domain if
every connectd component of the closed complemnet $X\setminus y$
is non-compact. The following result will
be used to prove Theorem 0.1 and  has also independent interest:

\medskip

\noindent
{\bf{0.6 Theorem.}}
\emph{Let $Y\subset X$ be a Runge domain.
Then
the restriction map $\mathcal O(X)\to \mathcal O(Y)$ has a dense image.}
\bigskip

\noindent
The results above constitute the
major facts in this section.
To prove Theorem 0.1  we first establish  seeemingly weaker results
and after 
finish the proofs of the the other  results.
\medskip

\centerline{\bf{§ 1. A finiteness result.}}

\medskip

\noindent
Consider
an connected open subset $Y$ 
which is relatively compact in
$X$. The boundary
$\partial Y$
is  compact but in general it need not be connected.
It can for example consist of a finite number of pairwise disjoint
and closed Jordan curves
together with some Jordan arcs and
some isolated points, like an annulus where
a finite set of points in the open annulus have been
removed.
If $\partial Y$
is "nice", for example piecewise analytic
then
tthe cohomology group
$H^1(Y,{\bf{C}})$ is a finite dimensional complex vector space.
Recall also from § xx that one has
the isomorphism
\[
\frac{\mathcal E^1(Y)}{d(\mathcal E(Y))} \simeq
H^1(Y,{\bf{C}})
\]
and
as explained in § xx there exists   an injective map
\[
\frac{\mathcal E^{0,1}Y)}{\bar\partial(\mathcal E(Y))}\to
H^1(Y,{\bf{C}})
\]
Moreover, Dolbeault's Theorem   identifies
right hand side with
$H^1(Y,\mathcal O)$ and hence
this cohomology group is finite dimensional
for every $Y$ as above with a nice compact boundary.
The finite-dimensionality
enable us to construct non-constant meromorphic functions on
$Y$.
Namely, if $p\in Y$ is fixed we
take a positive integer $N$ and
the sheaf $\mathcal O_D$ where $D$ is the divisor
$N\cdot p$ which means that one allows a pole of order
$\leq N$ at $p$.
Exactly as in the compact case from § xx one has an exact sequence
\[ 
0\to \mathcal O(Y)\to \mathcal O_D(Y)
\to {\bf{C}}^N\to H^1(Y,\mathcal O)\to H^1(Y,\mathcal O_D)\to
0
\]
If $N$ is strictly larger than
the dimension of
$H^1(Y,\mathcal O)$ we  get a non-zero
section of  $\mathcal O_D$, i.e. a meromorphic
function
in $Y$
with a pole of order
$\leq N$ at $p$ and otherwise  holomorphic.


\bigskip


\centerline{\bf{ § 2. A vanishing lemma.}}
\medskip

\noindent
Consider a pair  $Y\subset Y_1$ 
where $Y$ is relatively compact in $Y_1$.
As explained in § xx one has  the restriction map

\[
\mathcal L\colon H^1(Y_1,\mathcal O)\to 
H^1(Y,\mathcal O)\tag{2.1}
\]
\medskip

\noindent
{\bf{2.2 Proposition.}}
\emph{If $H^1(Y;\mathcal O)$ is finite dimensional
the $\mathcal L$-image in (2.1) is zero}
\medskip

\noindent
\emph{Proof.}
Choose $\xi_1,\ldots,\xi_K$ in  
$H^1(Y_1,\mathcal O)$ such that
$\{\mathcal L(\xi_k)\}$
gives a basis for the  $\mathcal L$-image
in the finite dimensional vector space
$H^1(Y;\mathcal O)$.
Next, we can find
a 
relatively compact set
$Y_2$ in $X$ where $Y_1<< Y_2$
and $\partial Y_2$ is "nice" so that
$H^1(Y_2,\mathcal O)$ is finite dimensional.
Fix a point $p\in Y_2\setminus Y_1$ and from § 1 we 
find
a meromorphic function
$f$
in $Y_2$ 
which restricts to a holomorphic funtion in
$Y_1$
which is not constant  on the connected components of this set.
Now we get the vectors
$\{f\cdot \xi_k\}$  in $H^1(Y_1,\mathcal O)$
and take  their $\mathcal L$-images.
Since we have chosen a basis above 
there is an $N\times n$-matrix $B$ with complex
elements such that

\[ 
\mathcal L(f\cdot \xi_k)=\sum_{j=1}^{j=N}\,
b_{kj}\cdot \mathcal L(\xi_j)\tag{i}
\]
Let us now consider
the holomorphic function in $Y_1$ defined by 
\[ 
F=\det(f\cdot E_N-B)
\]
Then (i) and Cramer's rule entail that
\[
\mathcal L(F\cdot \xi_k)=0\quad\colon\, 1\leq k\leq N\tag{ii}
\] 
Above $F$ is meromorphic in $Y_2$ with no poles
in the relatively compact subset $Y_1$.
We can therefore cover $Y_1$ with a finite number of charts
$\mathfrak{U}= \{U_\alpha\}$
such that
$F$ has no zeros in
non-empty intersections $U_\alpha\cap U_\beta$ when
$\alpha\neq \beta$.
Let us then take some $\eta\in H^1(Y_1,\mathcal O)$ which by 
Lerays theorem is represented by a cocycle
$\{\phi_{\alpha,\beta}\}$
in $Z^1(\mathfrak{U},\mathcal O)$.
Since $F\neq 0$ on each non-empty intersection we get  the cocycle
$\{\psi_{\alpha,\beta}= F^{-1}\cdot \phi_{\alpha,\beta}\}$
which represents a vector in $H^1(Y_1,\mathcal O)$ denoted by
$\eta^*$.
From  these  constructions we get
\[ 
\mathcal L(\eta)=\mathcal L(F\cdot \eta^*)
\] 
By (ii) the last term is zero and since
$\eta\in H^1(Y_1,\mathcal O)$ was arbitrary Proposition 2.2 is proved.

\medskip

\noindent
{\bf{2.3 A $\bar\partial$-equation.}}
Consider a pair $Y<< Y_1$ as above.
Dolbeault's theorem and Proposition 2.2  imply
that every  $\phi\in \mathcal E^{0,1}(Y_1)$
restricts to a $\bar\partial$-exact form on $Y$, i.e.
there exsits $g\in \mathcal E(Y)$ such that
\[ 
\bar\partial g=\phi|Y\tag{2.3.1}
\]
\medskip

\noindent
Now we can establish  a density result:

\medskip

\noindent
{\bf{2.4 Proposition.}}
\emph{Let $Y$ be 
a relatively compact
Runge domain in $X$. Then, for every $Y_1$
sich that $Y< Y_1$ and $H^1(Y_1,\mathcal O)$ is finite dimensional
it follows that  the restriction map from 
$\mathcal O(Y_1)$ to $\mathcal O(Y)$ has a dense image.}
\bigskip


\noindent
\emph{Proof.}
By the Hahn-Banach Theorem it suffices to show that 
for every (1,1)-current $\gamma$ with  some compact support $K$  in $Y$
one has the implication
\[ 
\gamma(f|Y)=0\quad\forall \,\, f\in \mathcal O(Y_1)\implies
\gamma|\,\mathcal O(Y)=0\tag{i}
\]
Consider a current $\gamma$ as above which vanishes on
each restricition of $f\in\mathcal O(Y_1)$
to $Y$ and let  $k$ be its compact support in $Y$.
Next,  choose an open set $Y_2$
where $Y_1<< Y_2$ and (2.3.1)
holds for this pair. So when
$\phi\in \mathcal E^{0,1}(X)$
there exists
$g\in \mathcal E(Y_1)$ such that
\[
\bar\partial g=\phi|Y_1
\]
Above $g$ is unique up to a
function in $\mathcal O(Y_1)$ and since
$\gamma$  vanishes on
$\mathcal O(Y_1)|Y$ 
the evaluation $\gamma(g)$ only depends upon $\phi$.
Hence there exists a current $S$ on $X$
defined by
the process above, i.e.
\[
S(\phi)= \gamma(g|Y)\quad\colon\,\bar\partial g=\phi|Y_1
\]
If $h\in C_0^\infty(X\setminus K)$
we get the $(0,1)$-form
$\bar\partial(h)$ and by the constructions above
\[ 
S(\bar\partial h)= \gamma(h|Y)=0
\] 
where the last equality follows since
$\gamma$ is supported by $K$.
This means that the current $S$ is $\bar\partial$-closed in
$X\setminus K$ and since $\bar\partial$ is elliptic
the restricttion of $S$
 to $X\setminus K$ is expressed by a holomorphic 1-form
$\sigma\in \Omega(X\setminus K)$.
So far we have not used the assumption that $Y$ is Runge.
To profit upon this we consider
the compact hull
$\mathfrak{h}(K)$ from § XX.
If
$y\in Y\setminus \mathfrak{H}(K)$  
the connected component $V$
in
$X\setminus  K$ which contains $y$ is non-compact.
Since the current $S$ has  compact support it follows that
\[ 
V\setminus \bigl(\text{Supp}(S)\cup K\bigr)\neq \emptyset\tag{ii}
\]
Now $\sigma$ respresents $S$ outside $K$
and  therefore it must vanishes in
the open set (ii).
By analyticity $\sigma$ vanishes in the whole connected
set $V$ and hence in a neighborhood of $y$.
Since $y$ was arbitrary we conclude that 
$\sigma$ vanishes identically in
$Y\setminus \mathfrak{h}(K)$.
Let us now consider some
$f\in \mathcal O(Y)$ and 
take
$g\in C_0^\infty(Y)$ where
$g=f$  in an open neighborhood of
$\mathfrak{h}(K)$.
It follows that
\[ 
S(\bar\partial(g))=\gamma(g|Y)= \gamma(f)
\] 
where the last equality holds since
$K$ is the support of $\gamma$.
Finally, since
$f$ is holomorphic we have $\bar\partial g=0$ in a neighborhood of
$\mathfrak{H}(k)$
and since $\sigma$ is supported by $\mathfrak{h}(K)$ it follows that
$S(\bar\partial(g))=0$. Hence 
$\gamma(f)=0$ for every $f\in \mathcal O(Y)$
which proves the requested implication (i)
above and hence the density in
Proposition 2.4.



\medskip

\noindent
{\bf{Remark.}}
 The
 proof above
 is attributed to Malgrange and  we  followed
 the presentation in  [Forster: page xx-xx].
 \bigskip
 
\noindent
{\bf{2.5 The case of locally free $\mathcal O$-modules.}}
If $\mathcal L$ is 
a locally free sheaf of $\mathcal O$-modules with rank one
similar results as above hold. Theproofs are more or less verbatim.
More precisely we first have some locally finite covering
$\mathfrak{U}=\{U_\alpha\}$ by simply connected charts
and $\mathcal L|U_\alpha$ are trvial for every $\alpha$, i.e.
there exists a section $\rho_\alpha\in\mathcal L(U_\alpha)$
such that the restricted sheaf
$\mathcal L|U_\alpha$ is the free
$\mathcal O_{U_\alpha}$-module 
generated by $\rho_\alpha$.
Shrinking $\mathfrak{U}$ if necessary we may assume that
the transistion functions which give
\[
\rho_\beta= \phi_{\beta\alpha}\cdot \rho_\alpha
\]
 in each non-empty intersection $U_\beta\cap U_\alpha$ yiled bounded
 holomrphic functions, i.e. the maximum norms
 \[
 || \phi_{\beta\alpha}||_{U_\beta\cap U_\alpha}<\infty
\]
When
this holds it is meaningful to speak about convergence for $\mathcal L$-valued sections.
More precisely, let 
$Y<< Y_1$ and $\{\rho_\nu\in\mathcal (Y_1)\}$
be given. If $\rho_*\in \mathcal L(Y)$ and $K$ is a compact subset
of
$Y$ we leave it to the reader to
clarify the condition that $\{\rho_\nu|K$ converges in a uniform way to
$\rho|K$, i.e. u
Thus, in Propostion 22and 2.4 we can replace $\mathcal O$ by
any $\mathcal L$. Concerning (2,3,1) we ntocie that
there exists the sheaf
\[
 \mathcal E_\mathcal L= 
 \mathcal O_\mathcal L\otimes_\mathcal O\,\mathcal E
\]
and
a well  defined map
\[
\bar\partial\colon\mathcal E_\mathcal L\to \mathcal E^{(0,1)}_\mathcal L
\]
So now (2,3,1) means that if $\phi\in \mathcal E^{(0,1)}_\mathcal L(Y_1)$
then there exists
$g\in \mathcal E_\mathcal L(Y)$ such that
\[
\bar\partial(g)=\phi|Y
\]





\centerline{\bf{2.5 Proof of Theorem 0.1}}
\medskip

\noindent
By  § XX we  exhaust $X$ by an increasing sequence of Runge domains
$\{Y_n\}$
where $Y_n<<Y_{n+1}$ and $\{H^1(Y_n,\mathcal O)\}$ are finite dimensional.
Consider
some $\phi\in \mathcal E^{0,1}(X)$. Now (2.3.1) applies to each
piar $Y_n<< Y_{n+1}$ and since $\phi$ restricts to 
$\mathcal E^{(0,1)}(Y_{n+1}$
there exists
$f_n\in \mathcal E(Y_n)$
such that 
\[
 \bar\partial f_n=\phi|Y_n
\]
It follows that
the restriction to $Y_n$ of $f_{n+1}-f_n$ is holomorphic.
Now $Y_{n-1}<< Y_n$ and
Proposition 2.4 entails that
this restricted holomorphic function can be uniformly approximated on
$Y_{n-1}$ by functions from $\mathcal O(Y_{n+1}$.
In particular we find
$g_{n+1}\in \mathcal O(Y_{n+1})$
such that the maximum norm
\[
||f_{n+1}+g_{n+1}-f_n||_{Y_{n-1}}<2^{-n}
\]
With $f^*_{n+1}= f_{n+1}+g_{n+1}$
we still have
\[
\bar\partial f^*_{n+1}=\phi|Y_{n+1}
\]
Pwerforibng these modfifications inductively we get
anew sequence $\{f^*_n\}$ where  (xx) hold for every $n$
while
\[
||f^*_{n+1}-f^*_n||_{Y_{n-1}}<2^{-n}
\quad\colon \, n=1,2,\ldots
\]
It follows that $\{f_n^*\}$ converge uniformly on $X$ to a continuous function
$F$.
This entials that
the distributuons
$\\bar\partial f_n^*\}$ converge to the distribution derivative
$\bar\partial (F)$ and by (xx) it is clear that
the following hold on the whole of $X$:
\[ 
\bar\partial(F)=\phi
\]
Now $\phi$ is a smooth form and the elliptic property of
$\bar\partial$ implies that
$F$ is a $C^\infty$-function. Hence the mapping
\[ 
\bar\partial\colon \mathcal E(X)\to \mathcal E^{(0,1)}(X)
\]
is surjective.
Dolbeaualt's theorem gives  $H^1(X,\mathcal O)=0$
and Theorem 0.1 is proved.
\medskip

\noindent
{\bf{2.7 Exercise.}}
Use the remarks from § 25.5
and repeat the methods above to show that
\[
H^1(X,\mathcal L)=0
\] 
for every locally free sheaf of $\mathcal O$-modules with rank one.



\newpage




 




 
















\newpage

\centerline{\bf{Sheaf theory.}}

\bigskip

\noindent
{\bf{Introduction.}}
Sheaf theory  was created by Leray 
during  the years 1943-45. A historic account about 
 sheaves and their cohomology is presented by Houzel in 
[xxx].
A merit of  sheaves is that
triangulations on topological spaces is not
needed to define cohomology. But  specific 
triangulations are of  course be  helpful
to calculate cohomology of specific topological spaces.
The fact that 
cohomology groups are  defined for arbitrary sheaves
has many  advantages.
One reason is that the family of all sheaves on a given topological space
is  ample  enough to produce  suitable resolutions of a given
sheaf by     sheaves whose cohomology are
easy to find.
For example,
on a  compact Riemann surface one starts  with the sheaf
$\mathcal O_X$ whose first cohomology group
$H^1(X,\mathcal O_X)$ is not found directly.
But there exists the  $\bar\partial$-resolution of $\mathcal O(X)$ 
where the  local solvability of inhomogenous $\bar\partial$-equation gives
 an exact sequence of sheaves
\[
\mathcal O_X\to\mathcal E_X\overset{\bar\partial}\to \mathcal E_X^{0,1}\to 0
\]
In § xx we explain why
the existence of $C^\infty$-partitions of the unity
implies  that
cohomology groups in positive degree
of 
$\mathcal E_X$ and
$\mathcal E_X^{0,1}$ are zero. Together with a general long exact sequence for sheaf cohomology
one arrives at the Dolbeault isomorphism expressed by the equality
\[
 H^1(X,\mathcal O(X)\simeq
\frac{\mathcal E_X^{0,1}(X)}{\bar\partial(\mathcal E_X^{0,1}(X))}
\]
\medskip

\noindent
We  shall expose  material which go further than what is needed for
compact Riemann surfaces. But  for those results which will be used 
to study compact Riemann surfaces
detailed proofs are given.
In the long run it is essential to become familiar with
general constructions in sheaf theory, and foremost with
cohomology which can be defined not only for a single sheaf but even
for a complex of sheaves where one encounters  hypercohomology.
To determine  the  cohomology of
complexes of sheaves one  employs spectral sequences which
is another major contribution due to
Leray in  the famous article
\emph{L'anneau spectral et anneau filtré d'homologie
d'un espace localement compact} from 1950.
 The construction of
spectral sequences of filtered complexes is presented  in § XX.

\medskip

\noindent
{\bf{Remark.}}
For  students in complex analysis
spectral sequences and their use
should  belong to common knowledge just as 
Stokes theorem. It suffices to
spend a week-end
to learn
the  rather  trivial constructions of  the derived category associated to
an arbitrary abelian category.
This  "yoga" is 
applied to construct 
cohomology for complexes of sheaves
and at the same time 
standard homological functors over
associative rings. After this one considers
derived functors on ringed spaces where 
sheaf cohomology and
homological functors  appear at the same time.
Recall  that if $\mathcal A$ is an abelian category with a finite
homological dimension if
there exists an integer $\mu$ such that
each object
in $\mathcal A$ has an injective resolution of length
$\mu$ at most. When this holds 
the derived category $D^b(\mathcal A)$ whose objects are bounded
complexes is equivalent to the triangulated category
$K^b(i(\mathcal A))$ whose objects are bounded
complexes of injectice objects and
morphisms between them are identified up to homotopy.
If $X$ is a manifold of some
real dimension $n$ and $\mathcal A$ the abelian category of sheaves
whose sections are complex vector spaces, then $i(\mathcal A)$ consists of flabby
sheaves
and one verifies easily that
its homological dimension is $\dim(X)+1$.
If $U$ is an open subset of such a manifold $X$
and $\mathcal F^\bullet$ is a bounded sheaf complex one
takes an injective resolution $\mathcal J^\bullet$ and  gets the
complex $\mathcal J^\bullet(U)$.
In this complex of vector spaces 
the cohomolgy groups are intrinsically defined, i.e. independent of the
chosen injective resolution of $\mathcal F$
and one writes
\[ 
H^k(U;\mathcal F^\bullet)= H^k(\mathcal J^\bullet(U))
\]
In addition  there exists Leray's spectral sequence whose
second table are  doubly indexed vector spaces
\[ 
E_2^{p,q}=H^p(U;h^q(\mathcal  F^\bullet))
\]
where $\{h^q(\mathcal F^\bullet)\}$ are the cohomology sheaves of
$\mathcal F^\bullet$.
See also § 0.1 for some further comments in the case of sheaves.


\medskip



\noindent
{\bf{ The genus of Riemann surfaces.}}
The equality between the dimension of $H^1(X,\mathcal O_X)$ and the topological genus
is easily proved by sheaves.
Let us for example consider a compact 
Riemann surface $X$ which is homeomorphic to a sphere
with two handles. We may assume
that they are
placed close 
to the 
northern respectively 
the southern pole. Choose a pair of open sets
$U_1,U_2$ whose union cover $X$ while $U_1\cap U_2$ is an
annulus around the equator circle. Here the handle at the northern pole 
is contained in $U_1$, and the handle at the south pole in $U_2$,
Since $U_1\cap U_2$ is biholomorphic with a planar domain 
we have $H^1(U_1\cap U_2,\mathcal O_X)=0$.
At the same time
the cohomology over $U_1$ and $U_2$ are equal to that over the torus which
is known to be of dimension one. Hence
$H^1(U_\nu,\mathcal O_X)$ are 1-dimensional for $\nu=1,2$.
In § xx we explain why 
$H^1(X,\mathcal O_X)$ is a direct sum of these cohomology groups and hence
of dimension two  which gives the
requested equality. By an induction over $g$ the 
equality is proved by similar elementary sheaf theoretic arguments.


\medskip

\noindent
{\bf{0.1 Flabby sheaves and categorical cohomology.}}
A sheaf $\mathcal J$ on a topological space is flabby
if
the restriction maps $\mathcal J(X)\to \mathcal J(U)$ are surjective for
every open subset $U$.
Denote by $M({\bf{C}}_X)$ 
the abelian category of sheaves whose sections are complex vector spaces.
It turns out that injective objects in this category consist of flabby sheaves
and to compute cohomology of a 
sheaf $\mathcal F$ one can therefore use a flabby resolution

\[
 0\to \mathcal F\to\mathcal J^0\to 
\mathcal J^1\to\ldots
\]
Passing to global sections one gets a complex
\[
0\to \mathcal J^0(X)\to \mathcal J^1(X)\to\ldots
\]
By a general result about injective resolutions in an arbitrary
abelian category one shows that
the cohomology of this complex  does not depend upon the chosen
flabby resolutionof $\mathcal F$ and in this way one gets
intrinsically defined cohomology groups
\[ 
H^p(X;\mathcal F)= H^p(J^\bullet(X))\tag{*}
\]
A fundamental fact is that these cohomology groups are equal to the
Cech cohomoogy groups when
$X$ is paracompact, i.e. when every open covering has  a locally finite
subcovering. This rather weak condition holds in
most applications so 
one can study cohomology via flabby resolutions which
has the merit that many long exact sequences are easier to
discover.
One can also go further and study ringed spaces where
homological algebra intervense with sheaf cohomology.
This systematic approach was put forward by Grothendieck in the article 
\emph{Sur quelques points d'algèbre homologiques} from 1957
which has been very influential.
We shall not give a full account about
sheaf theory.
 So we refrain from
discussing direct and inverse image sheaves and
their higher direct images as well as local cohomology.
Excellent material 
which covers most of the   essential  results
in advanced sheaf theory appear  in the text-book
\emph{Sheaves on Manifolds} by Kashiwara and Schapira.

\bigskip






\noindent
{\bf{0.2 Mittag-Leffler's theorem.}}
In [ibid] Grothendieck proved a   result with wide a range of applications. 
It is called the Mittag-Leffler theorem since the essential
ingredient in the proof is to
succesively
modify
sections by a similar procedure  as in  
Mittag-Leffler's constructions 
of 
meromorphic functions with
prescribed  poles in
${\bf{C}}$.
For
simplicity we announce the result  below for a single sheaf but mention that
it is valid for complexes of sheaves where
single cohomology groups  are replaced by
derived cohomology groups.
Here is the situation: Let $X$ be a topological 
space which is Hausdorff and paracompact. A family of open set
$\{\Omega_t$ indexed by real numbers
$0\leq t\leq 1$ is called a Mittag-Leffler family if 
it is increasing, i.e  $t<s\implies \Omega_t\subset \Omega_s$
and satisfies:

\[
\bigcup_{t< s}\, \Omega_t=\Omega_s\quad\colon\quad  0<s\leq 1
\quad\text{and}\quad 
\bigcup_{t> s}\, \Omega_t=\bar\Omega_s \quad\colon\quad 0\leq s<1
\]
Consider a sheaf $\mathcal F$. The inclusion
$\Omega_0\subset \Omega_1$ gives for each $p\geq 1$
a restriction map
\[
H^p(\Omega_1,\mathcal F)\to H^p(\Omega_0,\mathcal F)\tag{*}
\]
In many applications one wants to decide when these maps are
isomorphisms. The following sufficient condition was
proved in [ibid]:

\medskip

\noindent
{\bf{Theorem.}} \emph{The restriction maps in (*) are isomorphisms if
the following hold for each $p\geq 1$:}
\[
\lim_{U\to\{x_0\}} \,H^p(U\cap \Omega_t)=0
  \quad 0<t<1\,\colon\ x_0\in\partial\Omega_t\tag{i}
\]
\[
\mathcal H^0_{X\setminus \Omega_t}(\mathcal F(x_0)=0
\quad\colon\quad x_0\in\partial\Omega_t\tag{ii}
\]

\medskip

\noindent
Above condition (ii)  means that 
if $\xi$ is a non-zero element
in   the stalk $\mathcal F(x_0)$, then its support
cannot be contained in the closed complement of
$\Omega_t$.

\medskip

\noindent
{\bf{0.3 Multiplicative sheaves.}}
There occur also sheaves whose 
sections over open set no longer
are
complex vector spaces.
If $X$ is compact Riemann surface one has the sheaf
$\mathfrak{M}^*$ whose sections are
meromorphic
functions which are not identically zero
and for such a pair $f,g$ one can take the product $fg$.
With this rule the  sections
$\mathfrak{M}^*(U)$ over an open set is an abelian group whose identity is the
constant function which is everywhere one.
There is also
the subsheaf
$\mathcal O^*$ whose sections are holomorphic functions with no zeros.
The determination of the local cohomology group
$H^1(X,\mathcal O^*)$
is given in § XX. 
The exponential map $f\to e^{2\pi i f}$
yields a surjective sheaf morphism from
$\mathcal O$ onto $\mathcal O^*$ whose kernel consists of
functions which are locally constant and integer-valued.
This sheaf is denoted by ${\bf{Z}}_X$
where each stalk is a copy of the abelian group of integers.
The exact sequence
\[
0\to {\bf{Z}}_X\to \mathcal O\to \mathcal O^*\to 0\tag{*}
\] 
gives a 
long exact sequence of cohomology.
Since $\mathcal O(X)={\bf{C}}$ and $\mathcal O^*(X)= {\bf{C}}^*$
one gets an exact sequence
\[ 
0\to H^1(X, {\bf{Z}}_X)\to H^1(X,\mathcal O)\to
 H^1(X,\mathcal O^*)\to H^2(X, {\bf{Z}}_X)\to 0
 \]
\medskip
 
 \noindent
 In § xx we show that
$H^2(X, {\bf{Z}}_X)$ is reduced to the group of integers which means that
to each  cohomology class
$\xi\in  H^1(X,\mathcal O^*)$ one assigns an integer
denoted by $\text{ch}(\xi)$ and called the Chern class of $\xi$.
In (*) we have also the inclusion
$H^1(X, {\bf{Z}}_X)\subset  H^1(X,\mathcal O)$. Topology teaches that
$H^1(X, {\bf{Z}}_X)$ is a free abelian group of rank $2g$
where a basis is given by $2g$ many cycles
$\gamma_1,\ldots,\gamma_{2g}$ as described in § XX.
Recall  that
the dual of 
$H^1(X,\mathcal O)$ is $\Omega(X)$. So every
$w\in \Omega(X)$ restricts to an additive map
\[ 
w\colon H^1(X, {\bf{Z}}_X)\to {\bf{C}}
\]
It turns out that this map is given by
period integrals: 
\[ 
w(\gamma_k)= \int_{\gamma_k}\, w
\quad\colon\quad 1\leq k\leq  2g
\]
where $\{\gamma_k\}$ is a
 a canonical basis 
for the integer homology in Riemann's sense.
If $\Gamma$ denotes the image of
$H^1(X, {\bf{Z}}_X)$ in 
$H^1(X,\mathcal O)$ we get the $g$-dimensional torus
\[
T^g=\frac{H^1(X,\mathcal O)}{H^1(X, {\bf{Z}}_X)}
\]
By the above there remains an exact sequence
\[ 
0\to T^g\to H^1(X,\mathcal O^*)\to {\bf{Z}}\tag{**}
\]
At the same time we recall the Jacobi-Picard theorem
from § xx which asserts that
\[
T^q\simeq \frac{\mathcal D_0}{\mathcal P_0}\tag{***}
\]
In § we shall how (**) can be used to recover
(***) in an elegant fashion.
The basic point is that
$H^1(X,\mathcal O^*)$ can be identified with
isomorphism classes of holomorphic line bundles over $X$
which 
correspond to locally free sheaves of $\mathcal O$-modules of rank one.
If $\mathcal L$ is such a sheaf
we prove in § xx via
results from § x that
its meromorphic
extension has global sections and
that every such global sections assigns a unique divisor
$D(\mathcal L)$ on $X$. Its the degree is  $\neq 0$ 
precisely when the corresponding cohomology class
$\{\mathcal L\}\in H^1(X,\mathcal O)$
is sent to a non-zero integer in (**) above.
The class of holomorphic line bundle $\mathcal L$
for which
$D(\mathcal  L)=0$
is therefore identified with the torus $T^q$
which gives 
another realisation of the Jacobi-Picard torus.





\newpage

\centerline{\bf{1. Leray's spectral sequence.}}
\medskip


\noindent
{\bf{Introduction.}} 
A complex of abelian groups consists of an indexed family $\{A_k;d^k\}$
where $k$ run over the set of integers and 
each $A^k$ is an abelian group. Moreover, to each $k$ there is an additive map
\[
 d^k\colon A^k\to A^{k+1}
\]
where the 
composed maps are zero, i.e. 
$d^{k+1}\circ d^k=0$.
This gives   a complex
\[
\ldots A^{k-1}\overset{d^{k-1}}\to 
\ldots A^k\overset{d^k}\to \ldots A^{k+1}\to\ldots\tag{*}
\]
It is denoted by $A^\bullet$ and 
for  each integer $k$ there exists the cohomology group
\[ 
H^k(A^\bullet)=\frac{\text{ker}(d^k)}{\text{im}(d^{k-1})}
\]
If all  these cohomology groups are zero one says that
(*) is an exact complex.
\medskip

\noindent
{\bf{Homotopy.}}
Let $\mathcal C(A^\bullet)$ be a complex.
Supoose we have a family of additive maps
\[
\rho^k\colon\ A^k\mapsto A^{k-1}
\]
which satisfy
\[
d^{k-1}\circ\rho^k-\rho^{k+1}\circ d^k= 1_{A^k}
\] 
for every integer $k$ where $1_{A^k}$ is the identity map on $A^k$.
Then the complex is exact. For if $k$ is an integer and
$\xi\in \text{ker}(d^k)$ one has:
\[ 
\xi= d^{k-1}\circ\rho^k(\xi)-\rho^{k+1}\circ d^k(\xi)=
d^{k-1}(\eta)\quad\colon\quad \eta= \rho^k(\xi)
\]
Hence  the cohomology class of $\xi$ is zero.
The existence of $\rho$-maps  yields a sufficient condition for
exactness only but we remark  that  there exist exact complexes where
such a family of $\rho$-maps does not exist.
\medskip

\noindent
{\bf{Example.}} Let $\mathcal O={\bf{C}}\{z\}$ be the local ring of germ
of holomprihic functions at the origin. We consider the abelian catrgory of
$\mathcal O$-modues andnow one has an exact sequence
\[
0\to \mathcal O\to \mathcal O  [z^{-1}]\to \mathcal P\to 0
\] 
where
$\mathcal P$ is thr module of polar parts of germs of holomorphic
functions. Now the reader can verify that there
cannot exist non-zero
$\mathcal O$-linear maps from $\mathcal P\to \mathcal O[t^{-1}]$ or
from
 $\mathcal O  [z^{-1}]$ into $\mathcal O$.

\medskip

\noindent
Next, let $A^\bullet$ and $B^\bullet$
be  complexes. A
morphism
from  $A^\bullet $  into  $B^\bullet $ consists of a family of
additive maps
$\phi^k\colon\ A^k\to B^k$ such that
\[ 
d_B^k\circ \phi^k=
\phi^{k+1}\circ d_A^k
\quad\text{hold for all integers}\quad  k
\]


\noindent
{\bf{1. Exercise}}.
Show that if $\phi^\bullet$ is a morphism  then
there exist  additive maps
\[
H^k(\phi^\bullet)\colon H^k(A^\bullet)\to H^k(A^\bullet)
\]
for all $k$.
One refers to $\{H^k(\phi^\bullet)\}$ as the associated cohomology maps.

\medskip

\noindent
{\bf{Homotopy of morphisms.}}
Let 
$\phi^\bullet$ and $\psi^\bullet$ be a pair of morphisms.
They are homotopic if there
exists a family of additive $\rho$-maps
$\rho^k\colon A^k\to B^{k-1}$
such that
\[
\psi^k-\phi^k=d_B^{k-1}\circ\rho^k-\rho^{k+1}\circ d_A^k
\]

\medskip

\noindent
{\bf{2. Exercise.}} Show that if $\phi^\bullet$ and $\psi^\bullet$ are homotopic then
$H^k(\phi^\bullet)=H^k(\psi^\bullet)$  for all $k$.
\medskip

\noindent
{\bf{A long exact sequence.}}
Let $\{A_\nu^\bullet\}$ 
be three complexes and consider a pair of morphisms
\[
\phi^\bullet_\nu\colon\,  
A_\nu^\bullet\to 
A_{\nu+1}^\bullet\quad\colon\quad \nu=1,2
\]
For each integer $k$ we get a complex
\[
0\to A_1^k\overset{\phi_1^k}\to  A_2^k\overset{\phi_1^k}\to A_3^k\to 0\tag{i}
\]
If (i) are eact for every integer $k$
we say that the pair $\phi_1^\bullet,\phi_2^\bullet$
yield an exact sequence of the three given complexes.
Now there exist the cohomology maps:
\[ 
H^k(\phi_1^\bullet)\colon H^k(A_1^\bullet)\to
H^k(A_2^\bullet)
\quad\text{and}\quad
H^k(\phi_2^\bullet)\colon H^k(A_2^\bullet)\to
H^k(A_3^\bullet)
\]
\medskip

\noindent
{\bf{The connecting morphisms on cohomology.}}
Consider
an exact sequence of complexes.
Let $\xi\in \text{ker}(d^k_3)$ and
denote its  cohomoogy class in $H^k(A_3^\bullet)$  by
$\{\xi\}$.
The exactness gives
$\eta\in A_2^k$ such that
\[ 
\phi^k_2(\eta)=\xi\tag{i}\implies
\]
\[
0=d_3^k(\xi)= d_3^k\circ \phi_2^k(\eta)=
\phi_2^{k+1}\cdot d_2^k(\eta) \tag{ii}
\]
Hence $d^2_k(\eta)$ belongs to the kernel of $\phi_2^{k+1}$ and by exactness
we find
$\gamma\in A_1^{k+1}$ such that
\[
\phi_1^{k+1}(\gamma)= d^2_k(\eta)\tag{iii}
\]


\noindent
Notice that (iii) entail that
\[ 
\phi_1^{k+2}\circ d_1^{k+1}(\gamma)=
d_2^{k+1}\circ \phi_1^{k+1}(\gamma)=
d_2^{k+1}\circ d^2_k(\eta)=0\tag{iii}
\]
The last equality holds since  
$d_2^{k+1}\circ d_2^k=0$.
Hence $d_1^{k+1}(\eta)\in\text{ker}(\phi_1^{k+1})$.
Exactness  entails that $\phi^{k+1}_1$ is injective and hence
 $d_1^{k+1}(\eta)=0$ which means that $\eta$
 yields a cohomology class $\{\eta\}\in H^{k+1}(A_1^\bullet)$.
 


\medskip

\noindent
{\bf{3. Exercise.}}
Show that 
the cohomology class $\{\eta\}$  only depends upon
$\{\xi\}$ and gives an
additive map
\[ 
\rho^k\colon H^k(A_3^\bullet)\to H^{k+1}(A_1^\bullet)
\]
Show also  that these
$\rho$ maps yield a long exact sequence
\[
 \ldots 
 H^k(A_1^\bullet)\overset
 {H^k(\phi_1^\bullet)}\to
  H^k(A_2^\bullet)\overset
 {H^k(\phi_2^\bullet)}\to
  H^k(A_3^\bullet)\overset{\rho^k}\to 
 H^{k+1}(A_1^\bullet)\overset{H^{k+1}(\phi_1^\bullet)} \to
 \ldots\tag{*}
 \]


\noindent
One refers to 
(*) as the  long exact sequence of cohomology.
\bigskip



\centerline
{\bf{Double complexes.}}
\medskip

\noindent
Let $A^{k\nu}$ be a doubly indexed family of abelian groups where
$k,\nu$ are non-negative integers.
For each pair we are also given  additive mappings:
\[ 
\partial^{k,\nu} \colon A^{k\nu}\to A^{k,\nu+1}
\quad\colon\quad 
\delta^{k,\nu} \colon A^{k\nu}\to A^{k+1,\nu}
\]
where the  composed maps below are  zero:
\[ 
d^{k,\nu+1}\circ \partial ^{k,\nu}= 
\partial^{k+1,\nu}\circ \delta^{k,\nu}=0\tag{i}
\]
It means that each single row and each single column is a complex.
In addition the double complex is commutative which means that
\[
\partial^{k+1,\nu}\circ \delta^{k,\nu}=
\delta^{k,\nu+1}\circ \partial^{k,\nu}\tag{ii}
\]
For each $m\geq 0$ we set
$\Delta^0=A^{0,0}$ and 
\[ 
\Delta^m=A^{0,m}\oplus A^{1.m-1}\oplus\dots\oplus A^{m,0}\,\colon\, m\geq 1
\]
Now there exist  maps $\{d^m\}$ from $\Delta^m$ into $\Delta^{m+1}$
defined for  each pair $j,k$ with $j+k=m$ by:
\[
d^m(a_{k,j})= \partial(a_{k,j})+(-1)^j\cdot \delta(a_{k,j})
\]
\medskip

\noindent
From  (i-ii)  the
composed maps $d^{m+1}\circ d^m=0$ and refer to 
$\{\delta^\bullet; d^\bullet\}$ as the diagonal complex.
Now we have  the 
diagonal cohomology groups $\{ H^m(\delta^\bullet)\}$.
Each  cohomology group can be  equipped with
two filtrations, the \emph{First}  and the
\emph{ Second}. Both consist
of a non-decreasing sequence of subspaces
with  at most $m$ strict inclusions.


\bigskip

\noindent
{\bf{The First filtration.}}
To each  $m$ we set
\[
\mathcal F_\nu(\Delta^m)=A^{m,0}\oplus\ldots\oplus A^{\nu,m-\nu}
\quad\colon\quad 0\leq\nu\leq m
\]
Then
$d^m$ maps $F_\nu(\delta^m)$ into $F_{\nu+1}(\Delta^{m+1})$ for all pairs 
$\nu,m$ and 
in this way the $\Delta^\bullet$-complex is equipped with a 
filtration where the differentials increase the
degree with one unit for every $m$. This yields a filtration  on the diagonal 
cohomology groups as follows: Put 

\[
 Z_\nu^m=\mathcal F_\nu(\Delta^m)\,\cap \text{Ker}(d^m)
 \]
 Then $H^m(\Delta^\bullet)$ is filtered by the increasing sequence
 \[
 \mathcal F _\nu(H^m(\Delta^\bullet))=
\frac{Z_\nu^m+\text{Im}(d^{m-1})} {\text{Im}(d^{m-1})}\simeq
\frac{Z_\nu^m}{Z_\nu^m\cap\,\text{Im}(d^{m-1})}
 \] 
 where the last equality comes via  Noether's isomorphism.
 So for each $m$ we have a non-decreasing sequence
\[ 
 0\subset \mathcal F^{(1)} _0(H^m(\Delta^\bullet))\subset
\mathcal F^{(1)} _1(H^m(\Delta^\bullet))
\subset\ldots\subset \mathcal F^{(1)} _m(H^m(\delta^\bullet))\tag{*}
\]
To simplify notations we set
\[
\mathcal F^\nu((H^m(\Delta^\bullet))= \mathcal F_\nu(m)
\]



\noindent
and associate the graded cohomology group
\[
\text{gr}(H^m(\Delta^\bullet)= \oplus
\frac{\mathcal F_\nu(m)}{\mathcal F_{\nu-1}(m)}
\]

\medskip

\noindent
{\bf{The spectral sequence.}}
To each $m$ we have the graded group
\[
\text{gr}(\Delta^m)=\oplus\frac{ \mathcal F_\nu(\Delta^m)}{
\mathcal F_{\nu-1}(\Delta^m)}
 \]
 The $d$-differentials are homogenoeous of degree +1
 and we notice that 
the $\delta$-maps preserve the first filtration. Hence the  
$\partial$-maps  alone determine the cohomology of the associated graded complex
which by the construction of $\{d^m\}$ means that we for each fixed
$m$ consider
the $\partial$-cohomology of the complex
\[ 
0\to A^{m,0}\overset{\partial}\to A^{m,1}\overset{\partial}\to \ldots
\]
Let $H^\nu(A^{m,\bullet})$ denote
the cohomology of degree $\nu$ of this complex and define
the
graded group
\[ 
\mathcal E^m_1=H^0(A^{m,\bullet})\oplus\dots H^m(A^{0,\bullet})
\]
\medskip

\noindent 
Next, using Noether's isomorphism one shows that 
there exist graded maps

\[
\rho_2^m\colon \mathcal E^m_1\to \mathcal E_1^{m+1}
\]
which are homogenous of
degree $-1$ which means that
\[ 
\rho_1^m\colon H^\nu(A^{m-\nu,\bullet})\to
H^{\nu-2}(A^{m+1-\nu,\bullet})
\quad\text{hold for all pairs }\quad \nu,m
\]


\noindent
Moreover, these $\rho$-maps appear in a complex
\[ 
\ldots \to\mathcal E_1^{m-1}\overset{\rho_1^{m-1}}\to
\mathcal E_1^m\overset{\rho_1^m}\to 
\mathcal E_1^{m+1}\overset{\rho_1^{m+1}}\to \ldots
\]
As a result the cohomology yield graded 
groups $\{\mathcal E_2^m\}$
where
\[
 \mathcal E_2^m=\frac{\text{Ker}(\rho_1^m)}{\text{Im}(\rho_1^{m-1})}
 \]
 This  construction can be  continued, i.e. there exists  for each  $r\geq 2$ 
a family of  graded groups $\{\mathcal E^m_r\}$ which arise as cohomology groups via
 graded $\rho$-differentials on a complex formed by
 $\{\mathcal E_{r-1}^m\}$.
 After a finite number of steps the construction terminante
 and for each integer $m$ one has
 \[ 
 \mathcal E^m_m\simeq\text{gr}(H^m(\Delta^\bullet))\tag{*}
 \]
 This is  expressed by saying that the spectral sequence abuts to
 the graded cohomology.
 \bigskip
 
 
 \noindent
 {\bf{Remark.}}
 Many text-books expose the construction above and 
 are often supplied
 by diagrams which  help to visulize the 
higher order differentials.
The Second filtration is constructed in a similar fashion and the details are left to 
the reader who may  consult the literature
for details.
A good reference is the text-book \emph{xxx} by Bott.



\medskip


\centerline {\bf{A general construction.}}
\medskip

\noindent
The construction above is a special case of
the spectral sequence associated to a general filtered complex.
Let $\{F^\nu\}$ be a family of abelian groups indexed by integers where
$\nu$ can be negative and infinitely many $F^\nu\neq 0$.
Suppose   each $F^\nu$ is equipped with
a filtration $\{F^\nu(j)\}$ where $F^\nu(j)\subset F^\nu(j+1)$
and every
$F^\nu(j)$ is an additive subgroup. Next, suppose there are  additive maps
\[ 
d^\nu\colon F^\nu\to F^{\nu+1}
\] 
where each $d^\nu$ is filter preserving and $d^{\nu+1}\circ d^\nu=0$.
The cohomology of $F^\bullet$
is filtered by
\[ 
H^\nu(j)=
\frac{\text{Ker}(d^\nu)\cap F^\nu(j)+\text{Im}(d^{\nu-1})}
{\text{Im}(d^{\nu-1})}
\]
For each fixed $\nu$ we obtain the graded group
\[
\text{gr}(H^\nu)=\oplus\frac{H^\nu(j)}{H^\nu(j-1)}\tag{1}
\]



\noindent
Now we construct a sequence of graded complexes whose graded cohomology groups
approximate the graded cohomology (1).
To obtain this we set for each triple $j,k,\nu$ with $k\geq 0$:
\[ 
Z_j^\nu(k)=\{u\in F ^\nu(j)\,\colon\,d^\nu(u)\in F^{\nu+1}(j-k) \}
\] 
\[
B_j^\nu(k)=F^\nu(j)\cap\, d^{\nu-1}(F^{\nu-1}(j+k-1)
\]
\medskip

\noindent
Notice that $Z_j^\nu(0)=F^\nu(j)$ and that
$\{Z_j^\nu(k)\}$ decrease with $k$ for each fixed pair $j,\nu$.
The $B$-groups increase with $k$
and since $d^\nu\circ d^{\nu-1}=0$ we have the inclusions
\[
B_j^\nu(k)\subset Z_j^\nu(k)
\]


\noindent
It follows that there exist graded groups
\[ 
E_k^\nu=\oplus_j\, E_k(j)\quad\colon\quad
E_k(j)=\frac{Z_j^\nu(k)+ F^\nu(j-1)}{
B_j^\nu(k)+ F^\nu(j-1)}
\]


\noindent
{\bf{Exercise.}}
Noether's isomorphism gives
\[
E_k(j)=\frac{Z_j^\nu(k)}{
B_j^\nu(k)+ Z_j^\nu(k\cap\,  F^\nu(j-1)}\tag{i}
\]
The construction of the $Z$-groups entail that
\[
d^\nu(Z_j^\nu(k))\subset Z_{j-k}^{\nu+1}(k)
\quad\, \colon
d(Z_j^\nu(k\cap\,  F^\nu(j-1))\subset  B^{\nu+1}_{j-\nu}(k)
\tag{ii}
\] 
Show that (i-ii) give
additive maps
\[ 
E^\nu_k(j)\mapsto E_k^{\nu+1}(j-k)
\]
and taking the direct sum over $j$ we obtain a graded additive map
\[
\delta_k^\nu\colon  E_k^\nu\to E_k^{\nu+1}
\] 
which
is homogeneous of degre $-k$ where  the constructions above entail that
\[
\delta_k^{\nu+1}\circ \delta_k^\nu=0
\]
So for each fixed $k$,
$E_k^\bullet$ 
is a complex of graded groups whose differentials are of degree $-k$.
\medskip

\noindent
Finally, show that
Noether's isomorphism gives the following:

\medskip

\noindent
{\bf{Proposition.}} \emph{For each $k$ the cohomology of
$E_k^\bullet$ are isomorphic
to the graded groups in $E_{k+1}^\bullet$, i.e}

\[ 
H^\nu(E_k^\bullet)\simeq E_{k+1}^\nu\quad\colon \, \nu,k\geq 0
\]
\medskip

\noindent
{\bf{Convergence of the spectral sequence.}}
The constructions of the $Z$-groups show that
when $k$ increases then
$Z_j(k)$ gets close to the $d^\nu$-kernel on $F^\nu(j)$
and similarly $B_j(k)$ increase to
\[ 
B_j(\infty)=F^\nu(j)\cap \text{Im}(d^{\nu-1})
\]
So one expects that the graded groups $E_k^\nu$ 
approximate the graded cohomology groups in (1).
A sufficient condition for this goes as follows:


\medskip

\noindent
{\bf{Theorem.}}
\emph{Let $w$ be a non-negative integer such that}
\[ 
F^\nu(j)\cap \text{Im}(d^{\nu-1})\subset
d^{\nu-1}(F^{\nu-1}(j+w))
\] 
\emph{hold for all pairs $j,\nu$. Then it follows that}
\[
E_w^\bullet\simeq \text{gr}(H^\bullet)
\]


\noindent
{\bf{Remark.}} The isomorphism above
holds in the category of graded groups, i.e for
each $\nu$ one has the isomorphism
\[ 
E_w^\nu\simeq \text{gr}(H^\nu)
\]

\noindent The proof  of Theorem xx is left 
as an exercise.
When it holds one says that the spectral sequence abuts to the graded cohomology.
Notice that the conditions in Theorem xx are satisfied if we start 
from a  complex $F^\bullet$ for which there exist an  integer $j^*$ such that
\[
F_\nu(j)\neq 0\implies -j^*\leq j\leq j^*
\]
In other words, when the filtrations on the given complex $F^\bullet$
are uniformly bounded the spectral sequence
abuts to the graded cohomology.
This applies in particular to the first, respectively the second filtration of a bounded
double complex.



  





\newpage

\centerline{\bf{Sheaf theory.}}

\bigskip

\noindent
Let $X$ be a topological space. No special assumptions are made. For example, $X$ need
not be a Haussdorff space. 
We restrict the study to sheaves whose sections are complex vector spaces.
Such a sheaf $\mathcal F$ on $X$ assigns to every open subset
$U$ a 
complex vector space
$\mathcal F(U)$ and  to each pair
$V\subset U$ a ${\bf{C}}$-linear map
\[ 
\rho_{V,U}\colon \mathcal F(U)\to\mathcal F(V)\tag{i}
\]
where the   $\rho$-maps satisfy
\[ 
\rho_{W,U}= \rho_{W,V}\circ \rho_{V,U}\tag{ii}
\] 
for every triple $W\subset V\subset U$.
Finally the following two axioms hold:
First, let $U$ be open  and
$\{V_\alpha\}$  a family of open  subsets
of $U$ such that $\cup\, V_\alpha=U$. Then the map
\[ 
\mathcal F(U)\mapsto \prod\, \mathcal F(V_\alpha)
\] 
is injective.
It means that if a section $\xi\in\mathcal F(U)$ under the restriction maps is zero in
$V_\alpha$ for every $\alpha$, then $\xi$ is the zero vector in
$\mathcal F(U)$. Finally the  the glueing axiom holds.
It means that if $\{V_\alpha\}$ as above is covering of $U$ and
$\{\xi_\alpha\in\mathcal F(V_\alpha)\}$ is a family of sections such that
\[ 
\rho_{V_\beta\cap V_\alpha,V_\alpha}(\xi_\alpha)=
\rho_{V_\beta\cap V_\alpha,V_\beta}(\xi_\beta)
\] 
hold for all pairs of $V$-sets with an non-empty intersection, then
there exists a section $\xi\in \mathcal F(U)$ such that
\[ 
\rho_{V_\alpha,U}(\xi)=\xi_\alpha
\] 
for every $\alpha$.
Notice that $\xi$ is unique by the first axiom.
\medskip

\noindent
{\bf{1. Sheaf maps}}
The family of sheaves on $X$ whose sections are complex vector spaces
is denoted by
$\mathcal{S}({\bf{C}}_X)$.
If $\mathcal F$ and $\mathcal G$ is a pair of sheaves
a morphism - or a sheaf map -  from
$\mathcal F$ into $\mathcal G$
consists of a family of
${\bf{C}}$-linear maps
\[
\gamma_U\colon\mathcal F(U)\to \mathcal G(U)
\] 
where $U$ run over all open  sets and
the $\gamma$-maps which commute with the restriction maps of the two sheaves.
\medskip

\noindent
{\bf{2. Stalks of sheaves.}}
Let $\mathcal F$ be a sheaf on $X$. To
each  $x_0\in X$ the vector space
$\mathcal F(x_0)$
is inductive limit of
the vector spaces
$\{\mathcal F(U)\}$ where
$U$ run over open neighborhoods of $x_0$.
It means that for every open
set $U$ which contains $x_0$ one has a ${\bf{C}}$-linear map
\[
\gamma_U(x_0)\colon \mathcal F(U)\to \mathcal F(x_0)
\]
A vector $\xi_U\in\mathcal F(U)$ belongs to the $\gamma_U$-kernel if and only if
there exists some smaller open set $V\subset U$ with $x_0\in V$
and $\rho_{V,U}(\xi_U)=0$.
\medskip

\noindent
Finally, every vector $\xi\in\mathcal F(x_0)$ is the
$\gamma$-image for some open neighborhood of $x_0$.
Let us remark that  it suffices to use small open neighborhoods of
$x_0$ and choosing a chart around $x_0$ given by some open disc
$D$ in the complex $z$-plane we can use the decreasing sequence of open
discs $\{U_n=\{|z|<1/n\}$ and then
$\mathcal F(x_=)$ is identified with
the inductive limit of the
denumerable family of vector spaces
$\{\mathcal F(U_n)\}$.
\bigskip

\noindent
{\bf{3. Induced stalk maps.}}
Consider a pair  of sheaves $\mathcal F,\mathcal G$
and a sheaf map
\[
\phi\colon \mathcal F\to\mathcal G
\]
So for every open  set $U$ one has  ${\bf{C}}$-linear map $\alpha_U$
and these maps commute with the $\rho$-maps on the two given sheaves.
\medskip

\noindent
{\bf{3.1 Exercise.}}
Explain how one for each $x_0\in X$ constructs a ${\bf{C}}$-linear map
\[ 
\phi(x_0)\colon \mathcal F(x_0)\to\mathcal G(x_0)
\]
It is called the induced stalk-map at $x_0$ of the  sheaf map.
\medskip

\noindent
Next, to each open set $U$
we have the linear map  $\phi_U$ whose kernel is a
complex subspace of 
$\mathcal F(U)$. We can restrict the
$\rho$-maps which define $\mathcal F$ to these subspaces and
the reader may verify that we obtain a sheaf via the data:
\[ 
U\mapsto \ker \phi_U
\]
The resulting sheaf is denoted by
$\emph{ker}\,(\phi)$. 
\medskip

\noindent
{\bf{3.2 Exercise.}}
Prove that for every $x_0\in X$ there exists a natural ${\bf{C}}$-linear map
from the stalk at $x_0$ of the sheaf
$\ker\phi$ to the
kernel $\phi(x_0)$.
Hence the following isomorphism of complex vector spaces holds:
\[
\emph{ker}\, (\phi)(x_0)= \ker(\phi(x_0))\tag{*}
\]



\medskip

\noindent
{\bf{3.3 Image sheaves.}}
Given $\phi$ we get
image spaces
and the resulting map
\[ 
U\mapsto \text{Im}(\phi_U)
\]
The $\rho$-maps on $\mathcal G$ induce $\rho$-maps
\[
 \rho_{V,U}\colon\, \text{Im}(\phi_U)\to \text{Im}(\phi_V)
\] 
for each pair $V\subset U$ and 
they satisfy (ii) from 0.1.
Since the vector spaces
$\text {Im}(\phi_U)\}$ appear as subspaces of
vector spaces defining the sheaf $\mathcal G$, the first
sheaf axiom for $\mathcal G$ is inherited.
There remains to study the glueing condition. 
So now $U$ is an open set and $\{V_\alpha\}$ some open covering of $U$.
We are given
a family $\{\xi_\alpha\in\mathcal F(V_\alpha)\}$
such that
\[ 
\phi(\xi_\alpha)|V_\alpha\cap V_\beta=
\phi(\xi_\beta)|V_\alpha\cap V_\beta
\] 
hold for all pairs $\alpha,\beta$.
It means  that there exist sections
$\{\eta_{\alpha,\beta}\in \emph{ker}\,(\phi)(V_\alpha\cap V_\beta)\}$
such that
the restricted difference
\[ 
\xi_\alpha-\xi_\beta|V_\alpha\cap V_\beta=\eta_{\alpha,\beta}
\]
At this stage we encounter an "ugly obstruction".
Namely, we seek $\xi_U\in\mathcal F(U)$
such that
\[
\phi(\xi_U)|V_\alpha= \phi(\xi_\alpha)
\] 
hold for each $\alpha$.
This cannot be achieved in general
so
we have not found a sheaf above.
To compensate for this we enlarge
space of sections over open sets.
This, when $U$ is open we
denote by $\emph{Im}\,\phi)(U)$
the vector space
whose elements are of the form
$\{\phi(\xi_\alpha)\}$
for some open covering
$\{V_\alpha\}$ of $U$.
If $\{W_\beta\}$
is another open covering for which we assign
a vector $\{\phi(\xi^*_\beta)\,\colon\, \xi^*_\alpha\in
\mathcal F(U\,\cap W_\beta)\}$, we declare  that
the two vectors are equal if all the restrictions
\[ 
\phi(\xi_\alpha)-\phi(\xi^*_\beta \,\bigl| V_\alpha\,\cap W_\beta=0
\]
In this way we obtain a sheaf
denoted by $\emph{Im}\,\phi$ and called the sheaf-theoretic image of
$\phi$.
\medskip

\noindent
{\bf{3.4 Quotient sheaves.}}
SAY Defintion ....





\bigskip

\noindent
{\bf{3.5 Remark.}} The results above can be summarized
by saying that $\mathcal S(X)$ is an abelian catergory.
A short exact sequence in this category isd given by
\[
0\to \mathcal F_0\to
 \mathcal F_1\to  \mathcal F_2\to 0
 \]
 where $\mathcal F_0$ is a subsheaf of $\mathcal F_1$ and
 $\mathcal F_2$ the quotient
 sheaf
 $\frac{ \mathcal F_1}{  \mathcal F_2}$.





\newpage

\noindent
\centerline {\bf{3.6 Cohomology.}}
\bigskip

\noindent
Let 
$\mathfrak {U}$ be an open covering which  means that one has an index set
$A$ and for each $\alpha\in A$ an open set
$U_\alpha$. The sole condition is that
their union is equal to $X$.
Next, let $\mathcal F$ be a sheaf on $X$.
A zero-cochain with values in $\mathcal F$ consists of a family
\[
\{\xi_\alpha\in\mathcal F(U_\alpha)\,\colon\,\alpha\in A\}
\]
The family of zero-cochains is denoted by
$C^0(\mathfrak U,\mathcal F)$ which as  a vector space becomes the direct product:
\[
 C^0(\mathfrak U,\mathcal F)=\prod_{\alpha\in A}
 \, \mathcal F(U_\alpha)\tag{1}
\]
Next, we introduce the
vector space of alternating 1-cochains
given by
\[
 C^1(\mathfrak U,\mathcal F)=\prod^*\, \mathcal F(U_\alpha\cap U_\beta)
\] 
where (*) indicates  the alternating rule which means that
\[
\xi_{\beta,\alpha}=-\xi_{\alpha,\beta}\quad\text{for each pair}\quad 
\alpha, \beta
\]
hold for every index pair.
In particular  $\xi_{\alpha,\alpha}=0$ for every  $\alpha$.
\medskip

\noindent
{\bf{3.6.1. The coboundary map
$\delta^0$}}.
Let $\{\xi_\alpha\}$ in $C^0((\mathfrak U,\mathcal F)$.
For each pair of open sets $U_\alpha,U_\beta$
we can restrict  $\xi_\alpha$ and $\xi_\beta$ to the intersection
$U_\alpha\cap U_\beta$ and
obtain the alternating
1-chain
represented by
the sections
\[
\xi_{\alpha,\beta}=
\xi_\alpha-\xi_\beta|U_\alpha\cap U_\beta
\]
This 1-cochain is denoted by $\delta^0(\{\xi_\alpha\})$
and called the coboundary image of the 0-cochain.
This yields  a ${\bf{C}}$-linear map
\[ 
\delta^0\colon C^0(\mathfrak U,\mathcal F)\to C^1(\mathfrak U,\mathcal F)
\]


\noindent
{\bf{The vector space $C^2(\mathfrak U,\mathcal F)$.}}
This tine we consider intersection of triples in
$\mathfrak{U}$ and define the vector space
\[
 C^2(\mathfrak U,\mathcal F)=\prod^*
 \, \mathcal F(U_\alpha\cap U_\beta\cap U_\gamma)
\]
where (*) again indicates that
the sections satify the alternating rule.
It means that whenever a triple of $\mathfrak {U}$-sets have a non-empty
intersection then:

\[
\xi_{\alpha,\beta,\gamma}=-\xi_{\gamma,\alpha,\beta}=
\xi_{\beta,\gamma,\alpha}
\]
Now there exists a cobuondary map
\[ 
\delta^1\colon   C^1(\mathfrak U,\mathcal F) \to C^2(\mathfrak U,\mathcal F)
\]
Namely, let $\{\xi_{\alpha,\beta}\}$ be a 1-cochain.
 If $U_\alpha\cap U\beta\cap U_\gamma\neq \emptyset$ we 
 take restrictions of sections and put
 
 \[
 \xi_{\alpha,\beta,\gamma}=\xi_{\alpha,\beta}-\xi_{\alpha,\gamma}+
 \xi_{\beta,\gamma}
 \]
 \medskip
 
 \noindent
 {\bf{Exercise.}}
Show that (xx) satsifies the alternating rules
As a result we obtain a ${\bf{C}}$-linear map
\[
\delta^1\colon C^1(\mathfrak U,\mathcal F)\to
 C^2(\mathfrak U,\mathcal F)
 \]

\noindent
{\bf{The case $p\geq 3$.}}
In general we define the vector space
of alternating $p$-cochains by
\[
 C^p(\mathfrak U,\mathcal F)= \prod^*
 \, \mathcal F(U_{\alpha_0}\cap \ldots\cap U_{\alpha_p})
\] 
So here $p+1$-fold intersections of open sets occur and the
alternating conditions means that for every permutation  $\sigma(0),\ldots,\sigma(p)$
of $0,1,\ldots,p$ one has:
\[
 \xi_{\alpha_{\sigma(0)},\ldots ,\alpha_{\sigma(p)}}=
 \text{sign}(\sigma)\cdot
 \xi_{\alpha_0,\ldots ,\alpha_p)}
\]
 where 
$\text{sign}(\sigma)$ is the signature of the permutation.
\medskip

\noindent
{\bf{Exercise.}} 
 Show that to every $p$ there exists a map
 \[ 
 \delta^p\colon\, C^p(\mathfrak U,\mathcal F)\to 
 C^{p+1}(\mathfrak U,\mathcal F)
 \] 
 and verify that the composed maps
 \[
 \delta^{+1}\circ \delta^p =0
 \] 
 for all $p$.
 
 \medskip


\centerline {\bf{3.7 Cech cohomology groups.}}
  \medskip

\noindent
From the above
we obtain the complex
 $C^\bullet(\mathfrak{U},\mathcal F)$.
To each $p\geq 0$ we get the cohomology group
 \[ 
 H^p(\mathfrak{U},\mathcal F)=\frac
 {\text{Ker}(\delta^p)}{\text{Im}(\delta^{p-1})}
 \]
 \medskip
 
 \noindent
{\bf{3.7.1 Subcoverings.}}
Let $\mathfrak U$ and
$\mathfrak V$ be a pair of open coverings.
We write $\mathfrak{V}\leq \mathfrak{U}$ if there
exists an index map
$\tau$ which such that
\[ 
V_\beta\subset U_{\tau(\beta)}
\]
for all $\beta$ in the index set $B$ for $\mathfrak{V}$ while
$\{\tau(\beta)\}$
belong to the index set $A$ for $\mathfrak{U}$.
When this hold we can restrict sections  which
for each $p$ yields a map
\[ 
\tau ^p\colon 
C^p(\mathfrak{U},\mathcal F)\to C^p(\mathfrak{V},\mathcal F) 
\]
For example, consider some
vector $\xi\in C^1(\mathfrak{U},\mathcal F)$.
To each pair $\beta_1,\beta_2$ in $B$
we get the section over $V_{\beta_1}\cap V_{\beta_2}$ defined by 
\[
\eta_{\beta_1,\beta_2} =  \xi_{\tau(\beta_1),\tau(\beta_2)}|
V_{\beta_1}\cap V_{\beta_2}
\]
\medskip

\noindent
The construction  of $\tau^p$ for $p\geq 2$ is similar way and we leave it to the
reader to check
that  $\{\tau^p\}$ commute with the coboundary differentials. Hence
$\tau^\bullet=\{\tau^p\}$
is a morphism from
the complex $C^\bullet( \mathfrak{U},\mathcal F)$ into
$C^\bullet( \mathfrak{V},\mathcal F)$ which give
induced maps on cohomology
\[ 
H^p(\tau)\colon\  H^p( \mathfrak{U},\mathcal F)\to
 H^p( \mathfrak{V},\mathcal F)
 \]
 \medskip
 
 \noindent
 {\bf{3.7.2 Theorem.}}
 \emph{The cohomology maps $\{H^p(\tau)\}$ are intrinsic in 
 the sense that they do not depend upon
 the
 chosen index-map from $A$ to $B$.}
\medskip

\noindent
\emph{Proof when $p=1$.}
Let u$\mu\colon A\to B$ be another index map and we must show that
$H^1(\tau)=H^1(\mu)$. 
We orefer to use latin letters for the sets in $\mathfrak {V}$, i.e. 
now we have open sets $\{V_j\}$.
Let $\{\xi_{\alpha,\beta}\}$ be a 1-cocycle in
$C^1(\mathfrak {U},\mathcal F)$.
The index map $\tau$ gives the cochain
\[
g_{jk}= \xi_{\tau(j),\tau(k)}
\]
Similarly $\mu$ gives the cochain
\[
g^*_{jk}= \xi_{\mu(j),\mu(k)}
\] 
For each $V_k$ the open sets
$U_{\tau(k)}$ and $U_{\mu(k)}$ contain $V_k$ which enable us to define
\[
h_k=  \xi_{\tau(k),\mu(k)}
\]
$\{\xi_{\alpha,\beta}\}$
Now we use that
$\{\xi_{\alpha,\beta}\}$ is a 1-cycycle which 
applied to the triple $\tau(j),\tau(k),\mu(j)$ in $A$
entails that

\[
\xi_{\tau(j),\tau(k)}= \xi_{\tau(j),\mu(j)}+
\xi_{\tau(k),\mu(j)}
\]
From this the reader may confirm the equality:
\[ 
g_{jk}-g^*_{j,k}=\bigl(\xi_{\tau(j),\mu(j)}+\xi_{\tau(k),\mu(j)}\bigr)-
\bigl(\xi_{\mu(j),\mu(k)}+\xi_{\tau(k),\mu(j)}\bigr)=h_j-h_k
\]
Since $\{h_j\in\mathcal F(V_j)\}$ this gives the requiested equality between
the cohomology classes of $g$ and $g^*$.



\medskip


\noindent 
{\bf{Exercise.}}
Use a similar  device as above to prove Theorem XX for every $p\geq 2$.


\newpage


\noindent
{\bf{3.7.3. An injective map.}}
\medskip

\noindent
Let $\tau$ be an index map as above.
With $p=1$ we have the map

\[
H^1(\tau)\colon H^1(\mathfrak{U},\mathcal F)\to H^1(\mathfrak{V},\mathcal F) 
\]
\medskip


\noindent
It turns out that this map always is injective.
\medskip

\noindent
\emph{Proof.}} GIVE IT

\bigskip

{\bf{3.7.4
A surjective map.}}
Now we impose the condition that
\[ 
H^1(U_\alpha \cap \mathfrak {V},\mathcal F)=0\tag{*}
\]
holds for every open set in $\mathfrak{U}$.
Under this condition we  prove that $H^1(\tau)$ is surjective.
Let $\{\eta_{j,k}\}$ be a
cocycle in $C^1(\mathfrak{V},\mathcal F)$.
For each $U_\alpha$ in $\mathfrak{U}$
we can consider  restrictions to the open sets
$U_\alpha \cap V_k\cap V_j$.
In this way
the $\eta$-cocylce yields a co-cycle in $C^1(U\cap\mathfrak{V},\mathcal F)$
which by assumption is a coboundary which means 
that there exist sections 
\[
\gamma^\alpha_k\in\mathcal F(U_\alpha\cap V_k)
\]
such that
\[
\eta_{k,j}|U_\alpha\cap V_k\cap V_j
=\gamma^\alpha_k-\gamma^\alpha_j
\tag{i}
\]


\noindent
Next, consider some pair $\alpha_1,\alpha_2$ in $A$.
For every $m\in B$ we have the section
\[
\gamma^{\alpha_1}_m-\gamma^{\alpha_2}_m
\in\mathcal F(U_{\alpha_1}\cap U_{\alpha_2}\cap V_m)
\]
and (i) gives
\[
\gamma^{\alpha_1}_k-\gamma^{\alpha_2}_k=
\gamma^{\alpha_1}_j-\gamma^{\alpha_2}_j
\]
\medskip

\noindent
Since this hold for all pairs $\beta_1,\beta_2$.
the glueing condition is satisifed while 
$\mathfrak {V}$ induces an open covering of $U_{\alpha_1}\cap U_{\alpha_2}$.
Hence the sheaf axiom gives a section
\[
\xi_{\alpha_1,\alpha_2}\in \mathcal F(U_{\alpha_1}\cap U_{\alpha_2})
\]
such that
\[
\xi_{\alpha_1,\alpha_2}|U_{\alpha_1}\cap U_{\alpha_2}\cap V_m=
\gamma^{\alpha_1}_m-\gamma^{\alpha_2}_m
\quad\text{hold for all}\quad  m\in B
\]


\noindent
It is clear that this entails that
these $\xi$-sections gives a cocycle in $C^1(\mathfrak{U},\mathcal F)$
and hence it has an image in $H^1(\mathfrak{U},\mathcal F)$.
Its image under $H^1(\tau)$
is represented by 
\[
\eta^*_{k,j}=\xi_{\tau(k),\tau(j)}=
\gamma^{\tau(k}_k-\gamma^{\tau(j)}_j
\]
Now $U_{\tau(j)}$ and $U_{\tau(k)}$ both contain
$V_k\cap V_j$ and therefore (*) above
together with
(**) imply that
the equality below in $\mathcal F(V_k\cap V_j)$:
\[
\eta^*_{k,j}=\eta_{k,j}
\]
which finshes the proof that $H^1(\tau)$ is surjective



\newpage

\centerline
{\bf{3.8 Leray's Theorem.}}
\medskip

\noindent
Let $\mathcal F$ be a sheaf on $X$. To each open covering
$\mathfrak{U}$ we have constructed the Cech cohomlogy groups.
Passing to subcoverings one can employ the intrinsically 
maps in Theorem 3.7.2 which after a  passage to  the limit give
canonical maps for every $p$:
\[
\rho^p_{\mathfrak{U}}\colon
H^p(\mathfrak{U},\mathcal F)\to H^p(X,\mathcal F)
\]

\noindent
Following Leray we shall exhibit a condition that
a $\rho$-map is an isomorphism in a given degree $p$.
We say
that $\mathcal F$ satisfies Leray's $p$-condition 
if the following hold:

\[ 
H^{q-k}(U_{\alpha_1}\cap\ldots U{\alpha_k})=0
\quad\colon\ 
q+k=p\quad\text{ and}\quad  1\leq q\leq p\tag{i}
\]
\[
H^\nu(U_{\alpha_1}\cap\ldots U{\alpha_k}\})=0
\quad\colon\quad
q+\nu=p-2\quad\text{and}\quad  1\leq q\leq p-2\tag{ii}
\]


\medskip




\noindent
{\bf{3.8.1 Theorem.}}
\emph{If Leray's $p$-condition holds for a given $p$ then
 $\rho^p_{\mathfrak{U}}$ is an isomorphism.}
\bigskip

\noindent
{\bf{3.8.2 Example.}} When $p=1$ Leray's condition means that
$H^1(U_\alpha,\mathcal F)=0$ for each $U_\alpha$ which is
a useful criterion for 
$\rho^p_{\mathfrak{U}}$ to be an isomorphism.
\bigskip

\noindent
To prove of Theorem 3.8.1 we take  a flabby resolution
$\mathcal J^\bullet$ and identify
the cohomology groups of $\mathcal F$ with those in the complex $\mathcal J^\bullet$
as explained in § xx.
Next, when $\mathfrak{U}$ is an open covering
we obtain a double complex
where

\[ 
A^{p,\nu}=C^p(\mathfrak{U}, \mathcal J^\nu)
\]
Let us first consider
the
$\delta$-maps which means that with
$\nu$ fixed we regard the
cochain complex $C^\bullet(\mathfrak{U}, \mathcal J^\nu)$. Since
$\mathcal J^\nu$is flabby it is exact in every degree except 
zero where the kernel 
becomees $J^\nu(X)$.
It means that the spectral sequence of the Second Filtration degenerates
and as explained in § xx this entials that the diagonal cohomology of
the double complex are equal to those of the complex $\mathcal J^\bullet(X)$
which by defintion are
the cohomology groups
$\{ H^p(X,\mathcal F)\}$.
\medskip

\noindent
Next  we consider the First Filtration where we start with
$\partial$-maps.
This time 
the $\partial$-cohomology
gives the double complex:
\[
E_1^{k,\nu}=\oplus\, H^\nu(U_{\alpha_0}\cap\ldots U_{\alpha_k},\mathcal F)
\]
where the direct sum is taken over
stictly increasing sequences
$\alpha_0<\ldots<\alpha_k$ in the totally ordered and finite index-set
$A$.
If $p\geq 1$ and Leray's $p$-condition holds
only one $E_1$-term remains on the diagonal $k+\nu=p$, i.e.
\[ 
E_1^{p,0}=C^p(\mathfrak{U},\mathcal F)
\] 
Next, passing to
the $E_2$-term leary's condition entails tht nocoboundsry terms
appear in position $(p,0)$ where
we also have the $\delta$-map. So  by inspecting the diagram (*) it follows that:


\[ 
H^p(\Delta^\bullet)\simeq
E_2^{p,0}\simeq H^p(\mathfrak{U},\mathcal F)
\]
Since we already have seen that
$H^p(\Delta^\bullet)\simeq H^p(X,\mathcal F)$
Leray's theorem follows.

\bigskip

\noindent{\bf{3.8.3 Example.}}
Let us consider the case $p=1$ but this time we do no assume
that $H^1(U\alpha,\mathcal F)$ are all zero.
When we take the Second Filtration
we  encounter
a table
where

\[
 E_2^{1.0}= H^1(\mathfrak{U},\mathcal F)
\]
But we may have also a contribution from
$E_2^{0,1}$. In general the Second Filtration induces
a fikltrationon $H^1(\delta^\bullet)$ which entails that there is an exact seuence

\[ 
0\to H^1(\mathfrak{U},\mathcal F)\to
 H^1(X,\mathcal F)\to E_2^{0,1}\tag{*}
\]
where the klast arrow in general is not surjective.
To analyze $E_2^{0,1}$ we  recall that
\[ 
E_1^{0,1}= \oplus \, H^1(U_\nu\mathcal F)
\]
Let us now assume that
\[
H^1(U_k\cap\, U_\nu,\mathcal F)=0
\quad\text{for all pairs}\quad k\leq\nu
\]
Then the $\delta$-map on $E_1^{0,1}$
is identically zero so that
\[
E_2^{0,1}=  \oplus \, H^1(U_\nu\mathcal F)
\]
Next, the spectral sequence gives a canonical apping
\[
E_2^{0,1}\to H^2(\mathfrak{U},\mathcal F)
\]
Let $\mathcal K$ be the kernel of this map
which gives

\[
E_3^{0,1}=\mathcal K
\] 
Nothing more happens in this position since
the next differential has bi-degree $(-2,3)$ and no entries in
the double complex occur when the first index is negative.
So in general we have an exact sequence

\[
0\to H^1(\mathfrak{U},\mathcal F)\to
 H^1(X,\mathcal F)\to \mathcal K\tag{*}
\] 
where
$\mathcal K$ is the kernel under the canonical map
\[
\oplus\, H^1(U_\nu,\mathcal F)\to H^2(\mathfrak{U},\mathcal F)
\]
\bigskip

\noindent{\bf{Remark}}
The computations above illustrate the "yoga" which appears while one
investigates the specrtral sequences of a double complex.
A specific case occurs if
$X$ is a compact Riemann surface and $\mathcal F=\mathcal O$.
We can consider finite coverings $\mathfrak{U}$ where
some of the Cech cohomology groups
$H^1(U_\nu,\mathcal O)\neq 0$
and when this  occurs the exact sequence above
shows that
the CFech cohomology
$H^1(\mathfrak{U},\mathcal O)$ in general does not recover
the cohomology.  Take as an example the case when
$X$ has genus 2 and let us imagine that
$H^1(\mathfrak{U},\mathcal F)$ is 1-dimensional.
while
$H^1(U_\nu,\mathcal O)\neq 0$ for every $\nu$
and that $m\geq 2 $ is the number of sets in the covering.
Now $\mathcal K$ has dimension one so the
kernel of the map (*) is $m-1$-dimensional.
The reader is invited to
find examples where a situation as above occurs.
with $m\geq 3$.
























 


\newpage

\centerline{\bf{Analysis on compact Riemann surfaces.}}
\medskip


\noindent
Each  compact Riemann surface $X$ has an
underlying real-analytic structure which is   an oriented compact real manifold
of dimension two  denoted by $X_{\bf{R}}$.
For a while we ignore
the complex analytic structure.
There exists the sheaf
$\mathcal E$ whose sections are complex-valued
$C^\infty$-functions and 
the sheaf $\mathcal E^1$ of differential 1-forms with
$C^\infty$-coefficients. For brevity we refer to smooth 1-forms.
Finally there is the sheaf $\mathcal E^2$ of smooth 2-forms.
Since $X$ is oriented and compact smooth 2-forms
$\sigma$ can be integrated
over $X$ and we write
\[ 
\int_X\, \sigma
\] 
If $\alpha$ is a smooth 1-form its exterior differential $d\alpha$ belongs to
$\mathcal E^2(X)$ and Stokes Theorem gives
\[
\int_X d\alpha=0
\] 
It  means that the integral of an
exact 2-form over $X$ is zero.
A non-trivial fact is the converse
whose proof is given in § xx below.

\medskip


\noindent
{\bf{1.Theorem.}} \emph{A smooth 2-form is exact 
if and only if its integral over $X$ is zero.}
\bigskip


\noindent
{\bf{Currents.}}
A current of degree zero is a continuous linear form on
the Frechet space $\mathcal E^2(X)$ and we
set
\[
\mathfrak{c}^0(X)=
\mathcal E^2(X)^*
\]
Let us remark that $\mathfrak{c}^0(X)$ corresponds to the space of 
distributions on $X$, i.e. 
\[
\mathfrak{c}^0(X)=\mathfrak{Db}(X)
\]


\noindent
The dual  $\mathcal E^1(X)^*$
is denoted by $\mathfrak{c}^1(X)$ 
whose elements are
called 1-currents. Finally, the dual of $\mathcal E(X)$ is denoted by
$\mathfrak{c}^2(X)$ and its elements are called
2-currents.
\medskip

\noindent{\bf{Example.}}
A function $f\in \mathcal E(X)$   defines a zero-current
via the linear form
\[ 
\sigma\mapsto \int_X f\cdot \sigma
\quad\colon\quad \sigma\in \mathcal E ^2(X)
\]
In this way $\mathcal E(X)$ appears as a subspace of $\mathfrak{c}^0(X)$ and such currents 
are called smooth.
In the same way we get an inclusion $\mathcal E^1(X)\subset\mathfrak{c}^1(X)$
where $\phi\in\mathcal E^1(X)$ yields a continuous linear functional on
$\mathcal E^1(X)$ defined by
\[
w\mapsto \int_X \phi\wedge w
\quad\colon\quad w\in \mathcal E ^1(X)
\]
Exterior differential maps on smooth forms
 extend  to currents. If $w\in\mathcal E^1(X)$
is a smooth 1-current then
$dw$ is the 2-current defined by
\[
f\mapsto \int_X\ f\cdot dw\quad\colon\quad f\in \mathcal E (X)
\]
Stokes theorem gives:
\[
0=\int_X\, d(fw)=\int_X f\cdot dw+
\int_X\ df\wedge  w
\]
Since $df\wedge w=-w\wedge df$ we get
\[
\int_X\ f\cdot dw=\int_X\ w\wedge  df
\]

\medskip
\noindent
This leads to the construction of 
exterior differentials of 1-currents. Namely, if
$\gamma\in\mathfrak{c}^1(X)$
then the  2-current $d\gamma$ is 
defined by
\[
f\mapsto \gamma(df)\quad\colon\quad f\in \mathcal E (X)
\]
By the above 
it follows that
if $w\in \mathcal E^1(X)$ is regarded as a smooth
1-current then its current differential $dw$ is the smooth 2-current
expressed by the differential 2-form $dw$.
Thus, the exterior differentials on smooth forms extend to
currents and one has a complex
\[
0\to \mathfrak{c}^0(X)\overset{d}\to 
 \mathfrak{c}^1(X)\overset{d}\to  \mathfrak{c}^2(X)\to 0
 \]


\noindent
{\bf{2. $d$-closed zero currents.}}
A 
current $\gamma$ of order zero is $d$-closed if and only if
\[
d\gamma(w)= \gamma(dw)=0\quad\colon\quad w\in \mathcal E^1 (X)\tag{2.1}
\]
To grasp this condition we consider a chart $U$ in $X$ 
taken as an open disc in the  $(x,y)$-plane.
If $f(x,y)\in C_0^\infty(U)$
we have the 1-form $f\cdot dx$ and get $d(fdx)= f'_y\cdot dy\wedge dx$.
Hence
(2.i) means that
\[ 
\gamma(f'_y\cdot dy\wedge dx)= 0\quad\colon\quad f\in C_0^\infty(U)\tag{2.2}
\]
The restriction of $\gamma$ to $U$
 is a distribution in the sense of § X and
(i)
means that the distribution derivative $\frac{\partial\gamma}{\partial y}$
vanishes in $U$.
Similarly, if we start with a 1-form $gdx$ where $g\in C_0^\infty(U)$
we find that
$\frac{\partial\gamma}{\partial x}=0$
in $U$. It follows that the distribution $\gamma$ 
restricts to a constant density
function in $U$.
The conclusion is that the $d$-kernel on
$ \mathfrak{c}^0(X)$ is reduced to constant functions, i.e.
\[ 
\text{ker}_d( \mathfrak{c}^0(X))={\bf{C}}\tag{2.3}
\]
\medskip

\noindent
{\bf{3. Inverse and direct images under mappings.}}
Let $X,Y$ be a 
pair of oriented compact two-dimensional manifolds and $F\colon X\to Y$
a real-analytic map. Assume that $F$ is surjective, i.e.
$F(X)=Y$ and that the mapping is finite which means  that
there exists an integer $n$
such that the inverse finber
$F^{-1}(\{y\}$ contains at most $n$ points in $X$ for 
every $y\in Y$. Now
we  construct inverse images of smooth forms on $Y$.
First, if $g\in \mathcal E(Y)$ the composed function $g\circ F$ belongs to $\mathcal E(X)$.
Next, let $w$ be a smooth 1-form on $Y$. Using local coordinates
one verifies that
there exists a pull-back denoted by $F^*(w)$ which yields a smooth
1-form on $X$.
More precisely, let $p\in X$ be a given point and
$U$ is some chart around $p$ while $V$ is a chart around
$F(p)$.
Let $(\xi,\eta)$ be local coordinates in the chart $V$ and
$(x,y)$ are local coordinates in $U$.
Then
\[ 
w|V= g\cdot d\xi+ h\cdot d\eta
\quad\colon\quad g,h\in \mathcal E (V)\tag{i}
\]
In $U$ we get the $C^\infty$-functions
$\xi\circ F$ and $\eta\circ F$
whose exterior differentials give smooth 1-forms in $U$
denoted by $F^*(\xi)$ and $F^*(d\eta)$.
Now
\[
F^*(w)=g\circ F\cdot F^*(d\xi)+ h\circ F\cdot F^*(d\eta)
\]
\medskip

\noindent
{\bf{Exercise.}} Verify that
the 1-form $F^*(w)$  does not depend upon the chosen local coordinates
in the two charts. Conclude that
if $w\in \mathcal E^1(Y)$ then there exists a smooth
1-form
$F^*(w)$ on $X$ obtained in local charts as above. Hence there exists a pull-back map:
\[ 
w\mapsto F^*(w)
\]
In the same way one constructs the pull-back of each smooth 2-form on $Y$.
A notable fact is that
these pull-back mappings commute with
exterior differentials.
One has for example
\[ 
d(F^*(w))= F^*(dw) \quad\colon\quad w\in \mathcal E^1 (Y)
\]


\noindent We leave out the detailed verifications which are exposed in text-books
devoted to differential geometry.

\bigskip

\noindent
{\bf{4. Direct images of currents.}}
Tbe construction of the $F^*$-mappings of smooth forms
give by duality  $F_*$-mappings on currents.
More precisely, let $\gamma\in \mathfrak{c}^\nu(X)$ for some
$0\leq\nu\leq 2$.
The direct image current
$F_*(\gamma)$ is defined by
\[
F_*(\gamma)(w)=
\gamma(F^*(w))\quad\colon\quad w\in \mathcal E^\nu (Y)
\]
By this construction  the passage to direct images of currents 
commute with exterior differentials. For example, let
$\gamma$ be a 1-current on $X$. Then
\[
d_Y(F_*(\gamma))= F_*(d_X(\gamma))
\]
where we for convenience introduced a sub-index to indicate on which
manifold one has performed an exterior differential.
In particular $F_*$ sends $d$-closed currents on $X$ to $d$-closed currents on $Y$.
\medskip





\noindent
{\bf{5. Integration chains and 1-currents.}}
Let $c$ be an oriented $C ^1$-curve on $X$
which means that $c$ is defined via
a $C^1$-mapping $t\to x(t)$
from
a closed $t$-interval $[0,T]$ into $X$.
Each smooth 1-form
$\gamma$ in $X$ can  be integrated along $c$
and the map
\[
\gamma\mapsto \int_c\,\gamma
\] 
yields a 1-current
denoted by $\int_c$.
More generally we can take a finite sum of such integration currents, i.e.
every chain $c$ of class $C^1$
gives
a current
$\int_c$ which belongs to $\mathfrak{c}^1(X)$.
By definition the exterior differential $d\int_c$ is the 2-current defined by
\[
g\mapsto  \int_c\, dg\quad\colon\quad g\in \mathcal E (X)
\]
The resulting current is denoted by $\partial c$. In simplicial topology one
refers to $\partial c$ as the boundary of the 1-chain $c$.
Here it has been given an operative definition.
If $c$ is an elementary chain defined by a single 
oriented $C^1$-curve with end-points
$a$ and $b$, then
the 2-current
$\partial c$ is a  current
supported by the end-points $a$ and $b$.
In general $\partial c$ is a sum of Dirac measures assigned at a finite set of points, i.e.
\[
d\int_c= \sum\, k_\nu\cdot \delta(x_\nu)
\] 
where  $\{k_\nu\}$ are integers
and $\sum\, k_\nu=0$.
\medskip

\noindent
{\bf{6. Critical values of a map $F$.}}
Let $F\colon X\to Y$ be a surjective mapping with finite fibers.
One says that $F$ is smooth at a point $p\in X$
if the following hold when
a pair of local charts $U$ and $V$ have been chosen as in § XX:
The 1-forms $F^*(d\xi)$ and $F^*(d\eta)$ are non-zero and 
${\bf{R}}$-linearly independent.
Next, a point $q\in Y$
non-critical if $F$ is smooth at each $p\in F^{-1}(\{q\})$.
The complement is denoted by $\text{Crit}(F)$
and is called the set of the critical values.
A welknown fact - called Sard's Lemma - asserts that
the set of $F$-critical values is a (possibly empty) finite subset of $Y$.
Since $X$ and $Y$ both are connected
it follows that when $q\in Y\setminus \text{Crit}(F)$
then the number of points in
the inverse fiber
$F^{-1}(\{q\})$ does not depend upon $q$. This integer $n$ is called the degree of the 
mapping $F$ and  denoted by $\text{deg}(F)$.
Put $X_*= X\setminus F^{-1}(\text{Crit}(F)$. In topology one says that the
restricted mapping
\[ 
F\colon X_*\to Y\setminus \text{Crit}(F)
\]
is an unbranched covering map of degree $n$.
If $\Omega\subset Y\setminus \text{Crit}(F)$ is open and simply connected one proves that
the inverse image $F^{-1}(\Omega)$ consists of pairwise disjoint open subsets 
$U_1,\ldots,U_n$ and
$F\colon U_k\to \Omega$
is a diffeomorphism  for each $k$. One refers to
$\{U_k\}$ as the sheets above $\Omega$.
\bigskip

\noindent
{\bf{7. Direct images of integration currents.}}
Let $F$ be as above and consider a 1-current $\int_c$ on $X$ given by an
oriented 1-chain $c$.
Now there exists the direct image current $F_*(\int_c)$.
To describe this 1-current on $Y$
we proceed as follows.
To begin with $c$ is a sum of small 1-chains $\{c_k\}$ where
each $c_k$ is a single $C ^1$-curve
and we can also choose  $c_k$ so that
its parametrized curve
$t\to x(t)$  stays in a small
subset of $X$. So $a=x(0)$ and $b=x(T)$ are close to each other and
the whole curve $c_k$ stays inside a chart  $U$ in $X$ where
$a$ is the origin in $U$ and we may also assume that
$F(U)$ stays in a chart $V$ around $F(a)$.
\medskip

\noindent
Let $(\xi,\eta)$ be local coordinates in
$F(U)$.
If $g(\xi,\eta)\in C_0^\infty(F(U))$
we get the differential 1-form
$g\cdot d\xi$
whose  pull-back
can be integrated on the chain $c_k$.
This gives a linear functional
\[
 g\mapsto \int_{c_k}\,F^*(g\cdot \xi)
\]
A similar linear functional arises when
we instead use the 1-form $d\eta$.
\medskip

\noindent
{\bf{Exercise.}}
Conclude from the above that there exists the direct image current
$F_*(\int_{c_k})$
which has a compact support in
$F(U)$ and is given by
a 1-current of the form
\[ 
\mu_1\cdot d\xi+\mu_2\cdot d\eta
\]
where $\mu_1,\mu_2$ are two
Riesz measures with compact support in
$U$.
It means that the direct image current has order zero.
But unless $F\colon U\to F(U)$ is a diffeomorphism the direct image current
is in general not given by integration along a 1-chain.
Funally, by additivity one has
\[ 
F_*(\int_c)=\sum\, 
F_*(\int_{c_k})
\]
\bigskip


\noindent
{\bf{9. Further results.}}
Let $F\colon X\to Y$ be as above.
A special current on $X$ is the 2-current $\square_X$
 defined by
 \[ 
 \omega^2\mapsto \int_X\,\omega^2
 \]
i.e. one integrates 2-forms over $X$.
If $\phi$ is a bounded Borel function on $X$, or more generally
an $L^1$-function on $x$ in Lebegue's sense, then
there exists the 2-current defined by
\[ 
 \omega^2\mapsto \int_X\,\phi \cdot \omega^2
\]
It is denoted by $\phi \cdot \square_X$.
\bigskip


\noindent
{\bf{9.1 Exercise.}}
Let $F\colon X\to Y$ where
$F(X)=Y$ and $F$ is finite but may have some critical values.
Show that there exists a Borel function $\phi$ on $Y$ such that
\[
F_*(\square_X)= \phi\cdot \square_Y
\]
and  describe the $\phi$-function via some sort of Jacobian of $F$.
The case when $X$ is a compact Riemann  surface and $Y={\bf{P}}^1$
while $F$ is a meromorphic function on $X$ is of special interest.





 
 












\newpage


\centerline{\bf{II. The case when $X$ is a
Riemann surfaces.}}
\bigskip

\noindent 
On a  compact Riemann surface $X$
the complex analytic structure gives a
decomposition:
\[ 
\mathcal E^1(X)= \mathcal E^{1,0}(X)\oplus
\mathcal E^{0,1}(X)
\]
The exterior differential on $X$  is decomposed into
a sum $d=\partial+\bar\partial $ and when
$f\in\mathcal E(X)$ one gets  the 1-forms
\[
\partial f\in \mathcal E^{1,0}(X) \quad\text{and}\quad\bar\partial f \in 
\mathcal E^{0,1}(X)
\]
This gives  two complexes
\[
0\to \mathcal E(X)\overset{\partial}\to
\mathcal E^{1,0}(X)\overset{\bar \partial}\to
\mathcal E^{1,1}(X)\to 0
\]
\[
0\to \mathcal E(X)\overset{\bar \partial}\to
\mathcal E^{0,1}(X)\overset{\partial}\to
\mathcal E^{1,1}(X)\to 0
\]
\medskip

\noindent
where we remark that
$\mathcal E^{1,1}(X)= \mathcal E^2(X)$.
Since $\bar\partial$ is elliptic a current 
$\gamma\in \mathfrak {c}^0(X)$ is $\bar\partial$-closed if
it is a holomorphic function, i.e. 
\[
\text{Ker}_{\bar\partial}( \mathfrak {c}^0(X))=\mathcal O(X)={\bf{C}}
\] 
where the last equality follows since holomorphic functions on
the compact Riemann surface are  constant.

\medskip

\noindent
{\bf{2.1 Principal value distributions.}}
Let $f\in\mathfrak {M}(X)$.
It defines a distribution  $\text{VP}(f)$ as follows: When
$\sigma$ is a smooth 2-form on $X$ we avoid poles of $f$
and consider the limit integrals:
\[ 
\lim_{\epsilon\to 0}\, \int_{X_f(\epsilon)}\,f\cdot\sigma\tag{*}
\]
where $X_f(\epsilon)$ is the open complement of
small removed $\epsilon$-discs centered at the finite set of poles of $f$.
The existence of this limit was explained in §§,  i.e. in local coordinates
it amounts to show that there exist limits
\[
\int_{|z|>\epsilon},\frac{\phi(x,y)dxdy}{z^k}
\] 
for every positive integer $k$ and 
each test-function $\phi(x,y)$ in ${\bf{C}}$.
Next,  construct the current
\[
R_f=\bar\partial(\text{VP}(f))
\]
It is called the residue current of the meromorphic function $f$.
Since $f$ is holomorphic outside the poles
the (0,1)-current $R_f$
is supported by the discrete set of poles. In fact, Stokes Theorem gives
\[ 
R_f(\gamma)=
\lim_{\epsilon\to 0}\, \int_{X_f[\epsilon]}\,f\cdot\gamma\tag{**}
\]
where $X_f[\epsilon]$
consists of disjoint small circles centered at the poles
$p_1,\dots,p_k$ of $f$.

\medskip



\noindent
{\bf{2.2 The current $\frac{\partial f}{f}$}}.
Let $f\in\mathfrak {M}(X)$. 
Now 
$\frac{\partial f}{f}$ is a $(1,0)$-current.
Let  $U$ be  a chart around a zero $q$ of $f$ of some order $e$
so that $f= z^e\phi(z)$ where $\phi\neq 0$ holds in the chart.
Then 
\[
\frac{\partial f}{f}|U=\frac{\partial \phi}{\phi}+
e\cdot \frac{dz}{z}
\]
If $V$ instead is a chart around a pole
of some order $e$ we have $f= z^{-e}\phi(z)$ and obtain
\[
\frac{\partial f}{f}|V=\frac{\partial \phi}{\phi}-
e\cdot \frac{dz}{z}
\]


\medskip

\noindent
{\bf{2.3 Exercise.}}
Show that
if $g\in\mathcal E(X)$ then
\[
\frac{\partial f}{f}(dg)=2\pi i\cdot \bigl[\sum e_k\cdot g(p_k)- \sum\ e_j\cdot g(q_j)\,\bigr]
\]
where $\{p_k\}$ are the poles and $\{q_k\}$ the zeros of $f$
and $\{e_k\}$ the order of poles, respectively 
the multiplicities at the zeros of $f$.
\bigskip


{\bf{2.4 A special  direct images.}}
Let $w\in \Omega(X)$ be an abelian differential.
It yields a smooth
current
and there exists the dirct image current
$F_*(\omega)$.
Since the passage to direct images commute with differentials we have
\[ 
\bar\partial_y(F_*(\omega))=0
\]
Hence  the direct image current belongs to
$\Omega(Y)$.
If $Y={\bf{P}}^1$ 
there are no non-zero holomorphic forms so when 
$f\colon X\to {\bf{P}}^1$ is
given via some $f\in\mathfrak{M}(X)$ then
$f_*(\omega)=0$.
The vanishing of this direct image current means that
for every  $\beta\in\mathcal E^{0,1}({\bf{P}}^1)$ one has

\[
\int_X\, w\wedge f^*(\beta)=0\tag{2.4.1}
\]
\medskip

\noindent
{\bf{2.4.2 Exercise.}}
Verify (2.4.1) directly. The hint is to use partitions of the unity and
reduce the proof to the case when
the test-form
$\beta$ has a small support.
The sole local difficulty occurs when the support
contains some critical value under the mapping $f$.




\newpage





\centerline {\bf{III. Holomorphic line bundles.}}
\medskip


\noindent
Let $X$ be a compact Riemann surface. If $U$ is an open set we denote by
$\mathcal O^*(U)$ the family of
holomorphic functions  with no zeros in $U$.
For each pair $f,g$ in $\mathcal O^*(U)$ the product $fg$
is also holomorphic without zeros. In this way
$\mathcal O^*(U)$
is an abelian group whose zero-element corresponds to
the constant function in $U$ which is everywhere one.
One verifies easily that
\[ 
U\mapsto \mathcal O^*(U)
\] 
satisfies the sheaf axioms and the resulting sheaf is denoted by
$\mathcal O^*$.
Next, if $g\in\mathcal O(U)$ the exponential function
$e^{2\pi i g}$ yields a section in
$\mathcal O^*(U)$
which is the zero-element in this multiplicative abelian group if and only if
$g$ is a locally constant and integer-valued function on $U$.
In simply connected charts
the exist logarithms of $\mathcal O^*$-valued sections
which gives an exact sheaf complex:
\[
0\to {\bf{Z}}_X\to \mathcal O_X\overset
{\text{exp}}\to \mathcal O^*\to 0
\]
\medskip

\noindent
where ${\bf{Z}}_X$ is the abelian sheaf of 
locally constant integer-valued funtions. 
Hence there is a long exact sequence of cohomology where we
notice that $\mathcal O^*(X)$ is reduced to 
the multiplicative group of non-zero complex numbers
and the kernel of the exponential map on
${\bf{C}}$ is the additive group of integers . This gives an
exact sequence
\[
0\to H^1({\bf{Z}}_X)\to 
\to H^1(X,\mathcal O)\to  H^1(X,\mathcal O^*)\to
H^2({\bf{Z}}_X)\to 0\tag{1}
\]
where the last arrow comes from  $H^2(X,\mathcal O)=0$.
A wellknown result in topology asserts that 
$H^2({\bf{Z}}_X)$ is reduced to the group of integers.
So the last arrow in the exact squence above gives an additive map
\[
H^1(X,\mathcal O^*)\to{\bf{Z}}
\]
To investigate this map
we use Cech cohomology to describe
$H^1(X,\mathcal O^*)$.
Let $\mathfrak {U}$ be a finite covering by charts. 
As explained in § xx this gives:
\[
 H^1(\mathfrak{U},\mathcal O)\simeq H^1(X,\mathcal O)
\]
Next, for the   sheaf
${\bf{Z}}_X$ 
topology teaches that
\[
H^\nu(\mathfrak{U},{\bf{Z}}_X)\simeq H^\nu(X,{\bf{Z}}_X)
\quad\colon\quad 1\leq \nu\leq 2
\] 
hold when non-empty intersections of pairs or triples in
$\mathfrak{U}$ are simply connected.
So when $\mathfrak{U}$ 
is a simply connected covering
in the sense of § XX then (1) gives the exact sequence
\[ 
0\to H^1(\mathfrak{U}, {\bf{Z}}_X)
\to H^1\mathfrak{U},(X,\mathcal O)\to  H^1(\mathfrak{U},\mathcal O^*)\to
H^2(\mathfrak{U},{\bf{Z}}_X)\to 0\tag{2}
\]
Moreover one has the isomorphism
\[
H^1(\mathfrak{U}, X,\mathcal O^*)\simeq H^1(X,\mathcal O^*)\tag{3}
\]
\medskip

\noindent
{\bf{3.1 Conclusion.}}
The last isomorphism entails that
each  cohomology class in $ H^1(X,\mathcal O^*)$ is represented by
a Cech cocycle $\{f_{\beta\alpha}\}$
in $C^1(\mathfrak{U},\mathcal O^*)$ where
the multiplicative cocycle condition means that 
for every triple $U_\alpha,U_\beta,U_\gamma$ with
non-empty intersection it holds that
\[
f_{\gamma \alpha}=f_{\gamma,\beta}\cdot
f_{\beta, \alpha}\tag{3.1.i}
\]
\medskip

\noindent
{\bf{3.2 Associated locally free $\mathcal O$-modules.}}
Let $\xi= \{f_{\beta\alpha}\}$ be an element in
$C^1(\mathfrak{U},\mathcal O^*)$.
Then there exists a sheaf $\mathcal F$
whose sections  are given as follows: If
$V$ is an open set one has
\[ 
\mathcal F(V)=\prod^*\,\mathcal O(U_\alpha\cap V)
\]
where (*) indicates that a family 
$\{\phi_\alpha\in\mathcal O(V\cap U_\alpha)\}$
yields an element in the (*)-marked product if and only if
\[
\phi_\beta(x)=f_{\beta,\alpha}(x)\cdot \phi_\alpha(x)
\quad\colon\quad x\in V\cap U_\beta\cap U_\alpha
\]

\medskip

\noindent
If  $V=U_{\alpha_*}$ for a given index we see that
$\mathcal F(U_{\alpha_*})$ is a copy of
$\mathcal O_{U_{\alpha_*}}$. For if
$g_*\in \mathcal O(V)$ with
$V\subset {U_{\alpha_*}}$
we get an $\mathcal F$-valued section over
$V$ where
\[ 
g_\alpha= f_{\alpha,\alpha_*}\cdot g_*
\]


\noindent
Hence $\mathcal F$ is a locally free sheaf of
$\mathcal O$-modules with rank one.
Such sheaves are also called holomorphic vector bundles.
\medskip


\noindent
{\bf{3.3 Exercise.}} Show that conversely each locally free
sheaf of $\mathcal O$-modules with rank one comes from
some $\xi\in H^1(X,\mathcal O^*)$.
Show also that if
$\xi\neq \eta$ in $H^1(X,\mathcal O^*)$ then their associated holomorphic
vector bundles are non-isomorphic.



\medskip




\noindent
{\bf{3.4 Cohomology of  holomorphic vector bundles.}}
Given a Cech cocycle
$\xi=\{f_{\beta, \alpha}\}$ in 
$H^1(\mathfrak{U}, \mathcal O^*)$
we denote the associated holomorphic vector bundle with
$\mathcal O_\xi$.
We can also introduce the $C^\infty$-bundle $\mathcal E_\xi$
whose sections are $C^\infty$-functions satisfying the glueing conditions
in 3.2  and similarly  the sheaf of such sections in
$\mathcal E ^{0,1}$. Since the transition functions 
$f_{\beta,\alpha}$ are
holomorphic we get an exact sheaf complex
\[
\mathcal O_\xi \to \mathcal E_\xi \overset{\bar\partial}\to
 \mathcal E^{0,1}_\xi\to 0
\]


\noindent
It follows that
\[ 
H^1(X,\mathcal O_\xi)\simeq\frac{ \mathcal E^{0,1}_\xi(X)}{
 \bar\partial(\mathcal E_\xi(X))}
 \]
 \medskip
 
 
 \noindent
 {\bf{Exercise.}} Prove that
 the cohomlogy groups
 $H^0(X,\mathcal O_\xi)$ and $H^1(X,\mathcal O_\xi)$
are finite dimensional complex vectorspaces.
The  hint is to pass to subcoverings and use Leray's Theorem.

 \medskip
 
 
 \noindent
{\bf{3.5 Meromorphic sheaves.}}
We can  consider meromorphic
sections and introduce the sheaf
\[
\mathfrak{M}_\xi= \mathfrak{M}\otimes_\mathcal O\, \mathcal O_\xi
\]
If $D$ is a divisor we get the sheaf
\[ 
\mathcal O_D\otimes_\mathcal O\, \mathcal O_\xi\tag{1}
\]
It  is denoted by $\mathcal O_\xi[D]$.
Since  $\mathcal O_D$ is a subsheaf of $\mathfrak{M}$
it follows that  $\mathcal O_\xi[D]$ is a subsheaf of
$\mathfrak{M}_\xi$.
Next, if  $D$ is a positive divisor we get the exact sheaf sequence
\[
0\to \mathcal O_\xi\to \mathcal O_\xi[D]\to
\mathcal S_D\to 0
\] 
where $\mathcal S_D$ is the scysraper sheaf of the divisor.
Ecxactly as in § Xx we get the equality below for the Euler characteristics:
\[
\chi(\mathcal O_\xi[D])=
\chi(\mathcal O_\xi)+|D|
\]
So if $|D|$ is sufficiently large then
$H^0(X,\mathcal O_\xi[D])$ 
has a positive dimension which gives
a non-zero global section in
$\mathcal O_\xi[D]$ and hence also in the larger sheaf
$\mathfrak{M}_\xi$.
\bigskip

\noindent
{\bf{3.6 The divisor of meromorphic sections.}}
Keeping $\xi$ fixed we consider a global section
$\phi$ in $\mathfrak{M}_\xi$. It means that
there is a family
$\{g_\alpha\in\mathfrak {M}(U_\alpha)\}$
such that
\[ 
g_\beta= f_{\beta,\alpha}\cdot g_\alpha
\]
in every non-empty intersection $U_\alpha\cap U_\beta$.
Since the $f$-functions are zero-free
the divisors of the $g$-functions are matching and  
produce  a divisor on $X$ denoted by $D(g_\bullet)$.
Let $\{h_\alpha\}$ be another global meromorphic
section.
Then there exists a meromorphic function
$\psi$ on $X$ such that
\[ 
\psi|U_\alpha= \frac{h_\alpha}{g_\alpha}
\]
It follows that
\[ 
D(h_\bullet)=D(g_\bullet)+ D(h)
\]
So the images in the quotient t space
$\frac{\mathcal D}{\mathcal P_0}$
are equal and we have proved
\medskip

\noindent
{\bf{3.7 Proposition.}}
\emph{The holomorphic line  bundle defined by $\xi$
yields a unique element in
$\frac{\mathcal D}{\mathcal P_0}$ which we denote by
$\mathfrak{D}(\xi)$}.
\medskip


\noindent
The degree of
$\mathfrak{D}(\xi)$ can be non-zero. See §§ for a specific example.
To find those $\xi$ for which the degree is zero so that
$\mathfrak{D}(\xi)$ belongs to the Jacobi-Picard torus
$\frac{\mathcal D_0}{\mathcal P_0}$
we  employ the  exact sequence of sheaves. from (1).
Recall from
XX that
\[
\frac{H^1(\mathcal O)}{ H^1(X,{\bf{Z}}_X)}
\] 
is equal to the Jacobi-Picard torus $\text{Pic}(X)$ and (1)
and (1) gives the exact sequence
\[ 
0\to \text{Pic}(X)\to H^1(X,\mathcal O^*)
\overset{\rho}\to {\bf{Z}}\to 0
\]
\medskip


\noindent
{\bf{3.8 Proposition.}}
\emph{For each $\xi\in H^1(X,\mathcal O^*)$
one has the equality}
\[
\rho(\xi)=|\mathfrak{D}(\xi)|
\]
\emph{Hence the degree of $\mathfrak{D}(\xi)$ is zero if and only if
$\xi$ belongs to the
image of $H^1(X,\mathcal O)$ from the sequence on (1).}
\medskip

\noindent
{\bf{Exercise.}} Prove this result.
The hint is that when
$\xi$  is represented by  $\{f_{\beta,\alpha}\}$
then we can pick bracnhes of the log-functions
and since we have a muyltilicative co-cycle it follows that
we get a Cech cocycle  in $Z^2(\mathfrak{U},{\bf{Z}}_X)$
where a triple intersection has  the integer

\[
\log f_{\gamma,\beta}+\log f_{\beta,\alpha}-
\log f_{\gamma,\alpha}
\]

\medskip

\noindent
This cocycle represents an integer in
$H^2(X,{\bf{Z}}_X))$ and the reader should verify that it is equal
to $\rho(\xi)$ and after this show that if
the cocycle (i) is $\delta$-exact in the Cech complex of
${\bf{Z}}_X$ then $\xi$ belongs to the $H^1(X,\mathcal O) $-image.








\newpage

\centerline{\bf{4. Differential operators.}}

\bigskip

\noindent
On a given Ruemann surface $X$
we have the sheaf of ring
$\mathcal D$ whose sections are holomorphic differential operators which is
filtered by $\{\mathcal D(m)\}$.
See § xx for further details. Next, denote by
$\mathfrak{g}_X$ the sheaf of holomorphic vector fields
which yields the subsheaf of first order differential operators in
$\mathcal D$.
Recall from § XX   that $\mathcal D(0)$ is a copy of $\mathcal O$
and the associated graded sheaf

\[
\text{gr}(\mathcal D)=\mathcal D(0)\oplus
\frac{\mathcal D(1)}{\mathcal D(0)}\oplus 
\frac{\mathcal D(2)}{\mathcal D(1)}\oplus\ldots
\]
is a commutative graded sheaf of rings which in local charts
is isomorphic to the polynomial sheaf in one variable over
$\mathcal O$.
\medskip

\noindent
{\bf{4.1 Twisted rings of differential operators}}.
Consider a sheaf $\mathcal A$ of rings which is filtered where
$\mathcal A(0)= \mathcal O_X$ and the associated graded ring
\[
\text{gr}(\mathcal A)=\mathcal A(0)\oplus
\frac{\mathcal A(1)}{\mathcal A(0)}\oplus 
\frac{\mathcal A(2)}{\mathcal A(1)}\oplus\ldots
\]
is locally isomorphic to
is isomorphic to the polynomial sheaf in one variable over
$\mathcal O$.

\medskip

\noindent
{\bf{Definition.}}
When $\mathcal A$ is as above itis called a twised ring of differential operators
if there exists an $\mathcal OX$-linear sheaf map
$\rho$ which gives an exact sequence
\[
0\to \mathcal A_0\to\frac{\mathcal A_1}{\mathcal A_0}\overset
\rho\to \mathfrak g_X\to 0\tag{*}
\]
\medskip

\noindent
Since 
$ \mathfrak g_X$ is a locally free $\mathcal O_X$-moduke it follows that
(*) is locally split exact. So when $\{U_\alpha\}$
is a covering by charts
there exists for each $\alpha$ some
$\mathcal O_X$-linear map
\[
\gamma_\alpha \colon\,  \mathfrak g_X\to\mathcal A_1
\] 
defined in $U_\alpha$ where
$\rho\circ\gamma_\alpha $ is the identity on the restriction of 
$\mathfrak{g}_X$ to $U_\alpha$.
So if $\delta\in \mathfrak{g}(U_\alpha\cap U_\beta)$
we obtain
\[
\gamma_\alpha(\delta)-\gamma_\beta(\delta)=f_{\alpha,\beta}\tag{1}
\]

\medskip

\noindent
where $\{f_{\alpha,\beta}\}$. The assignment of these $f$-functions 
give an $\mathcal O_X$-linear map from
$\mathfrak{g}_X| U_\alpha\,\cap U_\beta$.
Hence there is a holomorphic 1-form
$w_{\alpha,\beta}\in \Omega(  U_\alpha\,\cap U_\beta)$
such that

\[
w_{\alpha,\beta}(\delta)=\gamma_\alpha(\delta)-\gamma_\beta(\delta)
\]
It is clear that $\{w_{\alpha,\beta}\}\in Z^1(\mathfrak{U},\Omega)$
so this cocycle gives a cohomoogy class in
$H^1(X,\Omega)$.
Hence every twisted ring of 
differential operators produces an
element in $H^1(X,\Omega)$.

\medskip

\noindent
{\bf{A converse construction.}}
Let $\{w_{\alpha,\beta}\}\in Z^1(\mathfrak{U},\Omega)$
be given.
On $\mathcal D$
we construct an isomorphism
on the restriction to    $U_\alpha\cap\,U_\beta$ 
which is the identity on
$\mathcal D(0)$ while
\[ 
\delta\mapsto  \delta-w_{\beta,\alpha}(\delta
\]
when $\delta\in\mathfrak{g}_X|U_\alpha\cap\,U_\beta$.

\medskip

\noindent
{\bf{Exercise.}} Show that these isomorphisms yield a twisted  ring
of differential operators
 whose isomorphism class in the category $XX$ above
only depends upon the cohomology class of the cocycle.
Conclude that there exists a 1-1 correspondence with
elements in $H^1(X,\Omega)$ and isomorphismclasses in $XX$.




\medskip

\noindent
{\bf{An exact sequence.}}
If $f\in\mathcal O^*$ we 
obtain the holomorphic 1-form
$\frac{\partial f}{f}$.
The reader can verify that thisyields an exact sequence of sheaves

\[
0\to {\bf{C}}_X^*\to \mathcal O^*\overset{d\log}\to
\Omega\to 0
\]
Passing to cohomology there is a long exact sequence:

\[ 
0\to H^0(X,\Omega)\to H^1({\bf{C}}_X^*)\overset{\rho} \to 
H^1(X:\mathcal O^*)\to H^1(X,\Omega)\to H^1({\bf{C}}_X^*)\to 0
\]

\medskip

\noindent 
Recall from § XX that
$ H^1(X,\Omega)$ is one dimensional
and as explained in
§ xx one has

\[
H^1({\bf{C}}_X^*)\simeq
\frac{{\bf{C}}}{{\bf{Z}}}
\]
\medskip

\noindent
We conclude from (x)nthat the image of the $\rho$-map above is reduced to
the additive group of integers. So this image is a sparse subset of the complex vector space
$H^1(X,\Omega)$
and  there is a family of twisted rings of differential operators
indexed by integers which arise via the $\rho$-image.

\bigskip

\noindent{\bf{The construction of $\mathcal A_*$}}.
We shall find the special tweisted ring $\mathcal A_*$ 
which
belongs to  the $\rho$-image and corresponds to the integer 1.





\newpage



\centerline{\bf{Cauchy measures on Riemann surfaces.}}
\bigskip

\noindent
Let $U$ be an open and connected subset of $X$ whose boundary
$\partial U$ has the following properties:
It is  a finite union of rectifiable 
Jordan arcs $\gamma_1,\ldots,\gamma_N$. 
Each $\gamma$-arc
is a bijective image of a function from
[0,1] into $X$ with bounded variation whose  interior part is  the image of
$(,1)$ is denoted by $\gamma^*$ and we add the condition
that  interior
arcs are disjoint, i.e.  
$\gamma_j^* \cap \gamma^*_k=\emptyset$ when $j\neq k$.
Next, let  $k\geq 2$.
and $p\in\partial U$ is a common boundary point of
$k$ many $\gamma$-curves, say
$\gamma_1,\ldots,\gamma_k$.
In a small chart
centered at $p$ which we can take as a disc
where $p$ is the origin and $\gamma_\nu\cap D$ is 
an arc with one end-point at the origin and the other
on the circle $\partial D$. The complement
in $D$ f these $k$ curves
consists of $k$  disjoint open sectors
$W_1,\ldots,W_k$ which is  illustrated by a figure.
For each $W$-sector t holds that
$U\cap W_j=W_j$
or that this intersection is empty.
\medskip


\noindent
Next, let $\phi\in\mathcal U$ and assume that
$\phi$ is locally integrable at every boundary point, i.e.
if $\chi_U$ is the characteristic function of $U$ we assume that
$\chi_U\cdot \phi$ belongs to $L^1(X)$.
This $L^1$-function is considered as a distribution on $X$
and applying the $\bar\partial$-operator we
get
the $(0,1)$-current $\bar\partial(\chi_U\cdot \phi)$ which
is supported by $\partial U$.
Under these conditions on $U$ and $\phi$, the
local constructions of boundary values of analytic functions
from § XX entail
this current has order zero and we can conclude:

\bigskip

\noindent
{\bf{Theorem.}} \emph{With $U$ and $\phi$ as above there exists a unique
Riesz measure $\mu$ supported by $\partial U$ such that
the following hold for every $g\in C^\infty(X)$:}
\[
\int_U\, \phi\cdot \bar\partial\partial\,g= \int\, g\cdot d\mu
\]

\noindent
{\bf{Example.}}
Let $X$ be the Riemann surface associated to an equation
\[ 
y^n+q_1(x)y^{n-1}+\ldots +q_n(x)=0
\]
\medskip


\noindent
We have the map $\pi\colon X\to {\bf{P}}^1$ where
$x$ is the coordinate on the projective line.
Above the point at infinity we suppose that there
is
an unbranched point $p_*$ which means that
$\zeta= \frac{1}{x}$ serves as a local coordinare at $p_*$.
Moreover, we suppose that 
the meromorphic function
$y$ has a simple zero at $p_*$ where the Taylor expansion
is  $y(x)= \frac{a}{x}+\sum_{j=2}^\infty c_j x^{-j}$
with $a$ real and positive.
Denote by $\mathcal F$   the family of open and connected  domains
$U$ in $X$ which contain $p_*$ and whose 
boundary consists of a finite union of Jordan arcs.
in addition $\pi$ restricts to a biholomorphic map from
$U$ onto an open domain in ${\bf{P}}^1$ and
the meromorphic
function
$y$ in $U$
has no poles.

\medskip

\noindent
{\bf{Tbe $L^1$-condition.}}
Suppose that
the order of poles of the  rational function $q_\nu(x)$
at points $x\in{\bf{C}}$ is $\leq\nu$ for each
$1\leq\nu\leq n-1$.
 Then we leave it to the reader to check that
 $y\in L^1(U)$ 
for each  domain  in the family $\mathcal F$
Hence  
each $U\in\mathcal F$ gives a Riesz- measure
$\mu_U$ supported by $\partial U$ for which
(*) holds in Theorem XX.
Put  $U_*=\pi(U)$
and when $g\in C^\infty(X)$
we get the funtion $g_*$ in
$U_*$ where
$g_*= g\circ \pi^{-1}$.
Similarly, we get the holomorphic function $y_*$ in $U_*$ where
$y_*= y\circ \pi^{-1}$.
The complex variable $x$ is written as $t+is$ and with
these notations we get
\[
\int_U\, y\cdot \bar\partial\partial g=
\int_{U_*}\, y_*(x) \cdot \bar\partial_x(g_*\cdot dx)
\]



\noindent
If $\mu_*=\pi_*(\mu)$ is the direct image measure
it follows that
when $h(x)$ is a $C^2$-function in
$U_*$ with continuous boundary values 
then
\[
\int_{U_*}\, y_*(x) \cdot \bar\partial_x(h\cdot dx)
=\int\, h\cdot d\mu_*
\]





\noindent
The construction above is foremost of interest when
$U$ is so large that
$\pi(\partial U)$ is a compact subset of the complex
$x$-plane without interior points.
Next, (xx) means that
the Laplacian of $y_*$ taken in the dsistribution sense is
the Riesz measure $4\cdot \mu_*$ and   from § xx we have
\[ 
y_*(x)=\frac{1}{2\pi i}\int\frac{d\mu_*(\zeta)}{x-\zeta}
\]
\medskip










\noindent
{\bf{Conjecture}}
Given a  local branch 
for $y$ as above, we ask if $\mathcal F$ contains a  domain
$U$ such that ${\bf{P}}^1\setminus
\pi(U)$ has no interior points and 
the measure $\mu_U$ is real and positive.


\medskip


\noindent
{\bf{Example.}}
Consider the Riemann surface $X$ associated to the equation
\[ 
y^2= \frac{1}{x(x-1)(x-2)(x-a)}
\]
where $a>2$ is real.
Above $x=\infty$ we have the point $p$ where
the local series of $y= \frac{1}{x}+ c_2x^{-2}+\ldots$.
Put
\[ 
U_*={\bf{P}}^1\setminus [0,1]\cup[2,a]
\]
Then there exists $U\in\mathcal F$ with $\pi(U)= U_*$
and here one finds that the Ruesz easure $\mu_U$
is real and positive.
The verification is left as an exercise to the reader where
material from § X in [Distributions] can be used.
On the Riemann surface $X$ we remark that
$\partial U$ is the union of two pairwse disjoint and closed Jordan curves.



 \newpage
 
\centerline{\bf{Some specific calculations.}}
\medskip


\noindent
 Consider the equation
\[
 y^2+y=\frac{1}{x}
 \]
 Here we can solve out $x$ in $y$, i.e
 \[
 x= \frac{1}{y+y^2}
 \] 
 So the Riemann surface $X$ is  ${\bf{P}}^1$.
 But we have also  the 2-sheeted map $\pi\colon X\to {\bf{P}}^1$
 where
 ${\bf{P}}^1$ is the projective $x$-space.
When $x\neq 0$ is stays in the complex plane
we write
\[ 
(y+1/2)^2=\frac{1}{x}+ 1/4
\]
Hence we get a pair of simple roots except when
$x=-4$ where a double root
appears and $y$ takes the value $-1/2$.
When $x=\infty$
$\zeta=\frac{1}{x}$ is a local coordinate
and the equation
$(y+1/2)^2=1/4+\zeta$  yields
a pair of  roots functions
\[ 
\alpha_1(\zeta)=\sqrt{1/4+\zeta}-1/4
\quad\colon\quad \alpha_2(\zeta)=-\sqrt{1/4+\zeta}-1/4
\]
Let us now remove the line interval $[-4,0]$ from the complex $x$-plane. Then
$U_*= {\bf{P}}^1\setminus [-4,0]$ is simply connected and 
homeomorphic to the open unit disc.
In $U_*$ there exist  single-valued branches of the root functions.
In particular we find the holomorphic function
$\alpha^*(x)$ in  where $\alpha^*(\infty)=0$.
When $x$ is close to the origin and stays outside the removed interval
we see that
\[ 
|\alpha^*(x)|\simeq |x|^{-\frac{1}{2}}
\]
Hence $\alpha^*$ is a locally integrable function close to
the origin
and regarding $\alpha^*$ as a distribution 
we get the distribution derivative
\[ 
\frac{\bar\partial }{\bar \partial \bar z}(\alpha^*)\tag{1}
\]
which is  supported by $[-4,0]$.
To find this distribution we consider
the behaviour of $\alpha^*$ above and below 
the open real interval $(-4,0)$.
If $0<t<4$ and $\epsilon>0$ is small 
we have

\[ 
\alpha_1(-t+i\epsilon)=i\cdot \sqrt{\frac{4-t-4i\epsilon t}{4t}}-1/4
\quad\colon\quad 
\alpha_2(-t-i\epsilon)=-i\cdot \sqrt{\frac{4-t+4i\epsilon t}{4t}}-1/4
\]
It follows that
\[
\lim_{\epsilon\to 0}\, \alpha_1(-t+i\epsilon)-\alpha_1(-t-i\epsilon)
=2i\cdot \sqrt{\frac{4-t}{4t}}
\]
By the results in § XX this entails that the distribution derivative in (1)
is equal to the density
on $[-4,0]$ expressed by 
\[
t\mapsto 2i\cdot \sqrt{\frac{4+t}{-4t}}=\rho(t)\quad \colon\quad
-4<t<0
\]
Now the general  formula for Cauchy transforms in § xx gives
\[
 \alpha^*(x)=\frac{1}{2\pi i} \int_{-4}^0\, \frac{1}{x-t}\cdot
\rho(t)\, dt\tag{xx}
\]
Above the $\rho$-function is purely imaginary and 
division with $i$ gives:
\[
\alpha^*(x)=
\frac{1}{2\pi } \int_{-4}^0
\,\frac{1}{x-t}\cdot \sqrt{\frac{4+t}{-4t}}\,dt
\]

\medskip

\noindent
Hence $\alpha^*(x)$ is the Cauchy transform of a positive measure supported by
$[-4,0]$.
\medskip

\noindent
{\bf{Remark.}}
After the variable substitution $u=-t$
we have

\[
\frac{1}{2\pi }\cdot  \int_{-4}^0
\, \sqrt{\frac{4+t}{-4t}}\,dt=
\frac{1}{2\pi }\cdot  \int_0^4
\, \sqrt{\frac{4-u}{u}}\,du=\frac{4}{2\pi }
\cdot\int_0^1 \, \sqrt{\frac{1-s}{s}}\, ds=1
\]
where the reader can check the last equality.

\newpage


\noindent
{\bf{The curve $y^3=\frac{1}{x(x-1)(x-i)}$.}}
Let $X$ be the associated Remann surface and $\pi$ the projection from
$X$ onto the projective $x$-line.
Above 0,1 and $i$
the fiber is reduced to a single point and at of these points the meromorphic
function $y$ has a simple pole and above $x=\infty$ we encounter three
simple zeros.
Consider a tree
$\Gamma$ in the complex $x$-plane which consists of
three Jordan arcs $\gamma_0,\gamma_1,\gamma_3$ which have one
common boundary pount $p\in{\bf{C}}\setminus\{0,1,i\}$
and 0,1 and $i$ appear as end-points of
this triple of Jordan arcs. See figure XX:
Now $U_*= {\bf{P}}^1\setminus \Gamma$ is simply connected
and  $\pi^{-1}(U_*)$ consists of three sheets
$U_1,U_2,U_3$. The sheet $U_1$ is chosen so that
the meromorphic function $y$ has the local Taylor series
$\frac{1}{x}$ plus higher order terms when $x=\infty$.
The $L^1$–function $y|U_1$ produces  a 
Riesz measure and we take its image under $\pi$
which  gives a Riesz meassure $\mu$ supported by
$\Gamma$ such that the chosen single valued branch
\[ 
y^*(x)= \int_\Gamma\, \frac{d\mu(\zeta)}{x-\zeta}
\]
The expansion of the chosen branch at $x=\infty$ entails that
the mean-value integral
\[
\int_\Gamma\, d\mu(\zeta)=1
\]
In particular the total variation of $\mu$ is always $\geq 1$. This total variation
is minimized if by a tree $\Gamma$ for which 
$\mu$ is real and positive.
So one is led to a variational problem. 
In the article [Bergquist-Rullgård]
it is proved
that there exists
a unique $\Gamma$-tree such that
the associated $\mu$-measure is real and positive.
Moreover, the branch point $p$ in 
$\Gamma$ where the three $\gamma$-curves
meet each other is contained in the 
open triangle with
with corner points at 0,1 and $i$.




 



 
\newpage



\centerline{\bf{Examples and Exercise.}}
\bigskip



\noindent
{\bf{Binomial curves.}}
This is the class of Riemann surfaces defined by an equation of the form
\[ 
y^m=R(x)
\] 
where $R(x)$ is a rational function and $m\geq 2$
Notice that when
$x\in{\bf{C}}$ and $R$ neither has a zero or a pole at $x$, then$y$ takes $m$
values which differ by roots if the unity.
If  $R$ has a zero or a pole it is locally like $z^q$ for some
integer $q$
and when $m$ and $q$ are prime we get a chart where
$y= t^q$ for the chosen local coordinte.
\medskip

\noindent
{\bf{1. Example.}}
Suppose that $R=\frac{P}{Q}$ where $P$ and $Q$ are polynomials 
with equal degree $k$ and each has
simple roots.
Now the reader can varify that
$y$ has simple zeros at the zeros of $P$ and simple poles at zero of $Q$.
So the degree of the map from $X$ onto the projective $x$-line is $k$.
Above $x=\infty$ we have $k$ distinct points, i.e. here $\pi$ is unramified.
Hence the sole ramification points on the projective $x$-line
occur at zeros of $P$ or of $Q$.
\medskip

\noindent
{\bf{Exercise.}} Show that
the meromorphic function $x$ has zeros of order
$m$
at the $(a_k,0)$ and also at $(b_k,0)$. So the posotove psrt of the
principal divisor $D(x)$ has degree
$2mq$.
An interesting conclusion is that
when $x=\infty$ then $m$ points are above
where $y$ is a local coordiante and now $x$ 
should have a plle of order
$2q$ at all these points.


CLASSIFY ....














Finally, at $\infty$ the function $x$
has a pole of order 2 so here $dx$ has a pole of order 3.
Starting from this, Abel considered
curves defined by
\[ 
u= \frac{R(x)}{Q(x)}\tag{1}
\]
where $R$ and $Q$ are polynomials of degree $m$ with no common zero
and 
$m$ is an arbitrary  positive integer.
The points of intersection between
$X$ and such a curve
have $x$-coordinates which satisfy
\[
Q^2(x)p(x)-R^2(x)=0
\]
This is a polynomial of degree $2m+2g+1$ whose zeros
via (1) determines the
$u$-coordinates. So the intersections of the two curves
consists of 
$2m+2g+1$ points
$\{\xi_\nu\}$ in $X$. here eventual multiple points may appear and
then we just repeat some of the $\xi$-points.
Let us for brevity write 
\[ 
M= 2g+2m+1
\]
Next, let $q(x)$ be a polynomial  where
$\deg q\leq g-1$.
Following Abel we set
\[ 
J=\sum_{\nu=1}^{\nu=M}\, \int_{p_*}^{\xi_\nu}\,
\frac{\phi(x) dx}{y}
\] 
where $p_*$ is some fixed point on $X$
and curves joining $p$ with the 
$\xi$-points are chosen for each
$\nu$.
By the construction the $\xi$-points depend upon the
chosen pair $P,Q$. A first remarkable fact
from [Abel] is that
the  sum of integrals in (*) 
alwaysis  zero ! 
The proof is given in § XX and constitutes a veritable  high point
in the theory of Riemann surfaces.
The vanishing was then used by Abel to
prove a fundamental
result which for the present hyperelliptic curve
goes as follows:
Assume for simplicity
that the polynomials $P$ and $Q$ are monic of some dgree $m$.
But lower order terms can be arbitrary. Following Abel we
consider  $2m$ independent variables
$(a_0,\ldots,a_{m-1}, b_0,\ldots,b_{m1})$ and write 
\[ 
R(x)= x^m+\sum_{k=0}^{m-1}a_kx^k\quad\colon\quad
Q(x)= x^m+\sum_{k=0}^{m-1}b_kx^k
\]
\medskip

\noindent
We consider the case when $2m\geq g+1$
and let $m_*$ be some integer such that
\[
g+1\leq m_*\leq 2m
\]
Now the $\xi$-points above depend both on $x$ and






hyperelliptic curves it gives
Abel's addition theorem which Abel himself  considered as an extension 
addition formulas for trigonometric
functions.
Concerning  the genus number
of a Riemann surface, where Abel of course   referred to algebraic functions
to interpretate
the
genus number, he was led 
count points of intersection between a  given curve
and whoe families of   curves with some arbitrary assigned degree.



{\bf{Specific examples.}} To digest 
general and often rather abstract results 
one should first
consider some 
specific Riemann surfaces.
As a first example we consider the algebraic equation
\[ 
y^2=x(x-1)
\]
When the absolute value $|x|\to +\infty$ we notice that
$\frac{y}{x}$ converges to +1 or -1.
From this we shall learn that the equation
yields a projective and non-singular curve
$S$ which is embedded in ${\bf{P}}^2$
and gives the associated compact Riemann surface.
On $S$ the meromorphic function
$y$ has two simple poles
and simple zeros at the points $(0,0)$ and $(1,0)$.
The meromorphic function $x$ has also two simple poles and 
a zero of multiplicity two at $(0,0)$.
We shall later on learn that the assertions above
are immediate consequences
of the construction of charts in $S$.
Next, consider   the meromorphic function $\phi=\frac{y}{x}$. From the above
it has a sole simple pole at $(0,0)$ and 
also a  simple zero at $(1,0)$. The conclusion is that
$S$ is isomorphic to the projective $\phi$-line
and
every meromorphic function
on $S$ is a rational function of $\phi$. Of course, this can be seen directly since
\[ 
\phi^2=\frac{y^2}{x^2}= \frac{x(x-1)}{x^2}
 =\frac{(x-1)}{x}\implies x= \frac{1}{1-\phi^2}
 \]
And the reader can also confirm that
$y= \frac{\phi}{1-\phi^2}$.
But the example is  instructive since it was not obvious from the start
that the quotient $\frac{y}{x}$ can be used to identify
$S$ with a projective line.
A more involved case
appears in § 0.X where we take the curve
\[
 y^4= x(x-1)^3
\] 
It turns out that it  also
is a projective line where 
$\phi= \frac{y}{x-1}$ is  used.
Riemann surfaces with a more complicated
 topology 
arise via 
algebraic equations of the form
\[ 
y^m=q(x)\tag{i}
\] 
where $m\geq 2$ and $q(x)$ is a polynomial with simple zeros of some
degree
$n\geq 3$ and 
$y^m-q(x)$ is irreducible in the unique factorization domain
${\bf{C}}[x,y]$
The genus of the associated
Riemann surface is calculated via the Hurwitz-Riemann formula
which is presented in § XX. If $m$ and $n$ are relatively prime
the genus is given by:
\[
1+\frac{m(n-1)}{2}-\frac{n+1}{2}=\frac{(m-1)(n-1)}{2}
\]
Notice that the last term is an integer since
the hypothesis means that not both $n$ and $m$ are even integers.
The formula shows that
the genus $g$ increases quite rapidly. For example, if
$m=4$ and $n=5$  we find that $g=6$ which means that
the Riemann surface is homeomorphic with a sphere with 6 handles attached.
The special case in (i) above with
$m=2$ and $n=3$
lead to elliptic 
Riemann surfaces which will be  treated in § XX.
\medskip





 \medskip
 
 \noindent
 {\bf{0.1 Abelian differentials.}}
The notions which appear below will
be explained in detail later on.
Let $P(x,y)=0$ 
be an irreducible algebraic equation which defines
a Riemann surface $X$ of some genus $g\geq 1$ and  $m$ is
the degree of $P$.
Consider also a globally defined holomorphic 1-form
$\omega$ on $X$ and
fix some point $p_*\in X$.
Given $X$ and $\omega$
one constructs
functions which in general depend upon several complex variables.
Following Abel the  procedure is  as follows.
Let $N\geq 2$ be a positive integer and
$x,y,a_1,\ldots,a_k$ are $k+2$ independent complex variables.
Consider a polynomial of the form
\[
 Q(x,y;a_\bullet)=q_N(x,y)+\sum\, g_{k,j}(a_1,\ldots a_m)
\cdot x^jy^k
\]
where the last sum extends over
pairs $j.k$ with  $j+k\leq N-1$ while $q_N(x,y)$
is a polynomial of degree $N$ and the doubly-indexed $g$-functions 
belong to the polynomial ring
${\bf{C}}[a_1,\ldots,a_k]$.
For  each $a_\bullet \in {\bf{C}}^k$
the intersection between  $X$ and $Q(x,y;a_\bullet)$ consists of $mN$ points
on
$X$  denoted by
$\{\xi_j(a_\bullet)\,\colon 1\leq j\leq mN\}$. 
Here
eventual multiple points are repeated
according to their multiplicities.
Notice that this $mN$-tuple of points on $X$
is unordered.
Continuity gives for each point $a_\bullet$ in ${\bf{C}}^k$
an unordered $mN$-tuple of arcs  
$\{\gamma_j(a_\bullet)\}$ where
each $\gamma_j(a_\bullet)$ joins $p_*$ with
$\xi_j(a_\bullet)$ and in this way we get a function defined on ${\bf{C}}^k$ by:
\[
J(a_\bullet)= \sum_{j=1}^{j=nM}\, 
\int_{\gamma_j(a_\bullet)}\, \omega\tag{1}
\] 
Abel's first result is that
$J$ is
a constant
function 
in ${\bf{C}}^k$. 
More generally we take a 
meromorphic 1-form $\omega$ on $X$.
Then a major result in [loc.cit]
is that the function
\[
J(a_\bullet)=r(a_\bullet)+\log  p(a_\bullet)
\]
where $r$ is a rational function of
$a_\bullet$ and $p$ a polynomial.
This  means that
the $J$-function in general is multivalued and must
be restricted to the complement of an algebraic hypersurface
in ${\bf{C}}^k$ which is natrual since
one must avoid poles of $\omega$ when we take intersections between
$X$ and the varying $Q$-curves parametrized by $a_\bullet$.
From the results above
Abel deduced an addition theorem which we 
describe locally as follows:
Given a point $p\in X$ we stay in a small chart
$\Delta$ around $x$ which
can be identified with the open unit disc
in a complex plane.
Let $\mu$
be an arbitrary integer which is strictly greater than the genus $g$.
Let $\omega$ be a holomorphic 1-form on $x$.
For each $\mu$-tuple $x_1,\ldots,x_\mu$ of points in
$\Delta$ we choose simple curves $\{\gamma_j\}$
which stay in
$\Delta$ with end-points at $p_*$ and $\{x_j\}$.
Then we get a complex-valued function defined in the
$\mu$-fold product  of  $\Delta$ by
\[ 
J(x_1,\ldots,x_\mu)=
\sum_{j=1}^{j=\mu}\, 
\int_{\gamma_j}\,\omega
\] 
Let  $z$ be the local coordinte in $\Delta$ 
which identifies $\Delta$  with the open unit disc
$D= \{|z|<1\}$
and here
$p$ corresponds to the origin.
$x_\mu=p+z_\nu$  where $\{x_\mu\}$
is a $\mu$-tuple of points in  $D$
so the $J$-function above is a function in
the polydisc $D^\mu$.
It is special because we have taken a sum
so that $J$ is invariant under permutations of
$z_1,\ldots,z_\mu$, i.e. the $J$-function is symmetric.
Abel's addition theorem expressed locally asserts that
in the situation above there exists
a $g$-tuple of analytic functions
$\{\phi_k(z_1,\ldots,z_\mu)\}$
such that
\[
J(x_1,\ldots,x_\mu)=
\sum_{j=1}^{j=g}\, 
\int_0^{\phi_k(z_\bullet)}
\,\omega
\]
in other words, the
symmetric $J$-function which a priori depends upon
$\mu$ many independent variables can be expressed by
a sum of $g$ integrals which means that if
$\{w_k=\phi_k(z_\bullet)\}$ then
$J$ only depends on $g$ many independent variables.
Abel expressed this by saying that
the $J$-function above has a degree of trancendency given by 
the genus of $X$.
Let us remark that the local equation above extends 
when the $J$-function is constructed on the
symmetric product of $\mu$ copies of $X$ and
where the $\phi$-functions
extend to rational functions on $X^\mu$.
A precise description of this
global result requires conceots from 
analytic function theory in several variables and
in this chapter
we shall be content to expose consequences of Abel's addition theorem in
specific cases.





\medskip


\noindent
\emph{About Abel's proof.}
The results above
constitute in the present author's opinion the
high point for the material in this chapter. As expected the proofs 
require a considerable amount of preparations.
 Abel employed
differentials in a similar fashion  
as Lagrange when he
derived the equations of motion in
an arbitrary
particle system with a finite degree of freedom
which obeys
Newton's Law of Forces while    external time dependent
outer forces can be arbitrary. Recall  that the d'Alembert-Lagrange 
equations
are valid
in non-conservative systems and can therefore be applied 
in many applied situations.
The equations constitute 
a cornerstone in optimization theory
and are for example used in optimal control theory as long as
the solutions are not of Bang-bang character.
A modified version  of Lagrange's proof was given by Pontryagin in 1949
adpated to problems where control variables are restricted
to bounded sets.
It is well documented
that Abel as a young student
studied mechanics.  So it is 
no surprise that he got much inspiration from
from  Lagrange's  text-book in mechanics from
1780. Let us also recall 
that  one of Abel's  first publications was devoted to mechanics where
an inversion formula was established  which makes it possible to recover
a potential field in an oscillating system after
experiments have determined
the periods  as a function of varying amplitudes.
Concerning Abel's  results above we mention that
extensions to higher dimensions 
were achieved by Nils Nilsson in the impressive article [Nils] from 1965
which  has led to the notion of Nilsson class functions in 
several complex variables.




\noindent
{\bf{Jacobi's residue.}}
An elegatn analytic formua to obtain intersection numbners
was given by Jacobi based upon residue calculus.
Let $P$ and $Q$ be a pair of irreducible polynomials and supose that
their projective curves do not intersect at infinity.
If $(x_*,y_*)$ is a point in
the intersection of $\{P=0\}$ and $\{Q=0\}$
a local intersection number
is defined by
\[
{\bf{i}}(P;Q; (x_0,y_0))=-\frac{1}{4\pi^2}\cdot 
\lim_{(\epsilon,\delta)\to (0,0)}\, \iint\, \frac{\partial P}{P}\wedge \frac{\partial Q}{Q}
\]
where the integration takes place over
the
2-dimensional surface defined by
\[ 
\{|P|=\epsilon\}\cap
\{|Q|=\delta\}
\]
Following Jacobi this yields
an integer which deends upon the ordering of $P$ and $Q$
and is called the local intersection number of the two curves
at $(x_0,y_0)$.
It turns out that this construction gives
intersection numbers which enjoy continuity.
Let us first compute Jacobi's number for the pair $P=x^2-y$ and $Q=y^2-x^3$.
Using Stokes Theorem as explained in § xx
the limit in
(*) can be performed while
$\epsilon$ tends much faster than
$\delta$ to zero.
During such a limit we set $y=x^2 +\epsilon\cdot e^{i\theta}$
to get points on $|P|=\epsilon$.
Jacobis integral becomes
\[
-\frac{1}{4\pi^2}\cdot \int_0^{2\pi}[\int_{|Q(x,x^2+
\epsilon\cdot e^{i\theta}|=\delta}\, \frac{\partial Q}{Q}]\cdot i\cdot d\theta
\]
We notice that
\[
\partial P\wedge\partial Q= 2x dx\wedge 2y dy-dy\wedge -3x^2dx
=(4xy-3x^2)\cdot dx\wedge dy
\]
Thus the inner integral is taken over the curve in the $x$-plane defined by
\[
|(x^2+\epsilon e^{i\theta})^2-x^3|=\delta
\]
and the limit when $\epsilon <<\delta$ becomes
\[
-\frac{1}{4\pi^2}\cdot 2\pi i\cdot\,\int_{|x^3-x^4|=\delta}\,
\frac{dx^4-dx^3}{x^3-x^4}
\]
Notice that
the curve
$|x^3-x^4|=\delta$  is approximately the circle
when $\delta$is small.
Moreover
\[
\frac{dx^4-dx^3}{x^3-x^4}=\frac{(4x-3)dx}{x(1-x)}
\]
By Cauchy's residue formula this nmber is equal to $2\pi i\dot 3$
and hence Jacobi's limit becomes
\[
-\frac{1}{4\pi^2}\cdot 2\pi i\cdot 2\pi i\cdot 3= 3
\]
Thus, we have found the previous intersection number.
\medskip

\noindent
{\bf{A general case.}}









To $P$ we have associated a Riemann surface $X$
where $x$ and $y$ become meromorphic functions.
Hence $Q(x,y)$,  being a polynomial of the two meromorphic functions
$x$ and $y$ on $X$, belongs to  $\mathfrak{M}(S)$.
This meromorphic function has some degree $N$
whose  zeros correspond  to points in
the intersection between $S$ and the curve $\{Q=0\}$ in
the projective space ${\bf{P}}^2$.

\medskip

\noindent
{\bf{Proposition.}}
\emph{The degree of the meromorphic $Q$-function on $S$ is equal to
the product $\deg P\cdot \deg Q$ of the given polynomials.}

\medskip

\noindent
How can we prove this result ?
A first observation is that the assertion
is invariant under a linear change of coordinates
in the $(x,y)$-space
which reduces the proof to the case when
$P(x,y)$ is of the form
\[ 
y^n+p_1(x)y^{n-1}+\ldots +p_n(x)
\] 
where $\deg p_k\leq k$ hold for the $q$-polynomials.
Let us assume
that
we do not encounter singular points above $x=\infty$.
A s explained in § XX it means that the leading $n$-homogeneous polynomial in
(1) is of the form
$\prod\, (y-\alpha_kx)$ where
$\alpha_1,\ldots,\alpha_n$ are distinct complex numbers.
The degree of the meromorphic function $Q$ can be found
by regarding its 
poles on $X$ which only can occur at points above $x=\infty$.
Supoose that we also have:
\[ 
Q(x,y)= y^m+q_1(x)y^{n-1}+\ldots +q_m(x)
\] 
where $\deg q_k\leq k$ for $1\leq k\leq m$.
On $X$ we have the ponits
\[ 
p_k=(0,1,\alpha_k)\quad\colon\quad 1\leq k\leq n
\]
At each of these points the meromorphic functions $y$ and $x$ have simple poles.
Now we can find a condition in order
that the meromorphic function $Q$ has a pole of order $m$
at each $p_k$. 
Namely, 
the leading $m$-homogeneous polynomial $Q^*$ of $Q$
is of the form
\[ 
Q^*(x,y)=\prod\, (y-\beta_\nu\cdot x) 
\]
If each $\beta-\nu$ differes from the $\alpha$-values it is clear that
$Q$ has a pole of order $m$ at every $p_k$
and conclude that
the degree of the meromorphic function $Q$ is equal to $nm$ which confirms
Proposition 1.6.1.
There reamins to decribe the
zeros of $Q$. In contrast to the poles there may occur
multiple zeros, i.e. the set-theoretic intersection between the 
projective curves $\{P=0\}$
and $\{Q=0\}$ may consist of fewer than  $mn$ many points.
So the intersection number $mn$ takes into the account multiple points when
$S$ and $\{Q=0\}$ intersect at points $(x,y)$
in ${\bf{C}}^2$.
\medskip





To $P$ one associates the gradient vector
\[
\nabla(P)= (P'_x,P'_y)
\]
A point $s=(x_*,y_*)\in S$ is called regular if
$\nabla(P)(s)\neq 0$.
If  $P'_y(s)\neq 0$ there exists a local factorisation:
\[
P(x,y)=(y-a(x))\cdot Q(y,x)
\]
where $a(x)$ is a holomorphic function of $x$ defined in some disc centered
at $x_*$ and $a(x_*)= y_*$.
This means geometrically that
$s$ is surrounded by a chart defined by a copy of
a disc $\{|x-x_*|<\delta$ where the points on $S$ are
$(x,a(x)$ and gives a chart on $S$ where
one says that
$x-x_*$ gives a local coordinate in the chart.
Regarding $S$ as a subset of ${\bf{P}}^2$
this  means that
$S$ appears as  locally a 1-dimensional complex
submanifold in an open neighbrhood of $(1,x_*,y_*)$.
If we instead have $P'_y(x_*,y_*)$ we find in a similar way that
$y$ is a local coordinate. This
time one has a local factorisation
\[ 
P(x,y)= (x-b(y))\cdot R(x,y)
\] 
where $b(y)$ is holomorphic in disc centered at $y_*$.
Put
\[ 
\text{reg}(S)= \{ (x,y)\in S\,\colon\, \nabla(P)(x,y)\neq (0,0)\}
\]
A first  fact is:

\medskip

\noindent
{\bf{1.4.2  Proposition.}}
\emph{$\text{reg}(S)$ is a connected and dense open subset of $\bar S$.}
\medskip

\noindent
The density is clear while the connectivity is not
so obvious from the start. But it follows from the hypothesis that
the  polynomial $P$ is irreducible. 
See § xx below for details. It follows that
$\text{reg}(S)$ is a connected complex manifold and the question arises 
if the complex analytic structure can
be extended to $\bar S$.
This turns out to be "almost true". More precisely one has

\medskip

\noindent
{\bf{1.4.3  Theorem.}} \emph{There exists a unique 
compact Riemann surface $X$ where $\text{reg}(S)$ can be identfied
with a dense open subset of $X$ and we have a surjective map
$\rho\colon X\to \bar S$
where the inverse fiber
of each $p\in S\setminus \text{reg}(S)$ is a finite set.}
\medskip


\noindent
This result is known as the normalisation theorem for projective curves.
It appears that no precise source of this result is known, but  was most likely 
understood by Abel since his work [Abel] contains
the requested constructions of complex analytic structures for elliptic curves.
The subsequent proof  shows that 
the $\rho$-map  often is bijective which means that the  topological spaces
$X$ and $\bar S$ are the same.


\medskip

\centerline{\emph{Proof of Theorem 1.4.3.}}
\medskip

\noindent
Let $s_*=(x_*,y_*)\in S $ where $\nabla(P)(s_*)=0$.
With $z=x-x_*$ and $\eta=y-y_*$ we 
set
\[ 
p(z,\eta)= P(x_*+z,y_*+\eta)
\] 
It follows that
\[
p(z,\eta)= \eta^n+r_1(z)\eta^{n-1}+\ldots+r_{n-1}(z)\eta+r_n(z)
\]
where $\{r_j(z)\}$ are polynomials in $z$.
Since $p(0,0)= P(x_*,y_*)=0$ we have $r_n(0)=0$ and we  notice that
$P'_y(x_*,y_*)=0$ 
also gives  $r_{n-1}(0)=0$. Hence there exists
an integer $2\leq k\leq n$ such that 
\[
p(0,\eta)=\eta^k\cdot p_*(\eta)\quad\colon\quad p_*(0)\neq 0
\]
As explained in § xx where we even treated  $\eta$-polynomials 
with coefficients in
${\bf{C}}\{z\}$ 
there exists  a factoriasation
\[ 
p_*(z,\eta)=\bigl(\eta^k+\rho_1(z)\eta^{k-1}+\ldots+\rho_k(z)\bigr)
Q(z,\eta)
\] 
where $Q(0,0)\neq 0$ and
$\rho_j(0)=0$ for every $1\leq  j\leq k$.
Set
\[ 
w(y,z)=\eta^k+\rho_1(z)\eta^{k-1}+\ldots+\rho_k(z)
\] 
By the above
$\rho_\nu(0)=0$ for every $\nu$
which means that $w$
is a Weierstrass polynomial.
Zeros of $w$ close to the origin correspond to points on $s$ close to $s_*$. From
§ xx  it follows that there exists some
$\delta>0$
such that if $0<|z|<\delta$ then the roots of the $\eta$-polynomial above
are simple and distinct which by §§ means that
$w$ has no multiple  factors
and is therefore a product
\[ 
w(z,y)= w_1(z,y)\cdots w_r(z,y)
\] 
where $\{w_j\}$ are irreducible
Weierstrass polynomials.
Next,  the local  construction in
§ xx shows that every  irreducible factor
$w_j$ produces an analytic disc.
More precisely, for a fixed $1\leq j\leq r$ we let
$e$ denote  the
$\eta$-degree of $w_j$. When $e\geq 2$ the material from 
§§ gives
an analytic function $A(\zeta)$ defined of  a new complex variable
$\zeta$  in a disc $\{|\zeta|<\delta\}$
such
that
\[
w_j(\zeta^e, A(\zeta))=0\quad\colon\quad 
0\leq\nu\leq e-1
\]
Moreover, in the Taylor expansion of $A$
there does not exist an integer $e_*\geq 2$ which is a factor of $e$
such that
$A(\zeta)= A_1(\zeta^{e_*})$ for some analytic function $A_1$.
Thus implies
that the map from the punctured disc
$\dot D=\{0<|\zeta|<\delta\} $ which sends  $\zeta$ to $(\zeta^e,A(\zeta)$
is injective for a sufficiently small $\delta$
and the image is a relatively open set in
$\text{reg}(S)$.
The origin $\zeta=0$ is mapped to $s_*$
and the local geometric
picture is as follows:
There exists  an open neighborhood $U$ of $s_*$ in
 $S$ such that
\[
U\setminus\{s_*\}= U_1\cup\ldots, \cup\, U_r
\]
and to each $U_j$ we have a biholomorphic mapping from
a punctured $\zeta$-disc which sends $\zeta\neq 0$ to
$(\zeta^{e_j}, A_j(\zeta)$ where $e_j$ is the degree of 
the $j$:th Weierstrass polynomial $w_j$ in the factorisation of $w$ above.
The sets $\{U_j\}$ are disjoint  open subsets 
$\text{reg}(S)$
and have $s_*$ as a common boundary point.
\medskip

\noindent
{\bf{Remark.}}
A favourable case occurs when
$w$ from the start is irreducible.
Then we get   an open neighborhood
$U$ of $s_*$ where the map
\[ 
\zeta\to (\zeta^e,A(\zeta))
\] 
yields a bijective mapping between the open $\zeta$-disc
and $U$.
Moreover, the map is holomorphic in the sense that if
for every rational function 
\[ 
k(x,y) =q_0(x)+q_1(x)y+\ldots+q_{n-1}(x)y^{n-1}
\] 
where $\{q_j(x)\}$ belong to ${\bf{C}}[x)$, it follows that
$k\circ \rho=k^*(\zeta)$ are meromorphic functions in the $\zeta$-disc.
So when  the local Weierstrass polynomials $w$ are irreducible for all $s_*\in
S\setminus \text{reg}(S)$
we have prodiced local charts at all points in $S$ which 
give a an atlas of a complex manifold $X_0$
which as a point set coincides with $S$.
\bigskip

\noindent
If $w$ has several irreducible factors we
get $r$ many charts where the origin in each chart has to be speatted from the others.
So here  one is obliged   to consider $r$  disjoint $\zeta$-discs 
$D_1,\ldots,D_r$ where the punctured discs are  mapped into 
disjoint sets $U_1,\dots,U_r$ as above while the origin in
each $D_j$ is mapped into $s_*$. In the Riemann surface
$X_0$ we therefore  find $r$ distinct points above $s_*$, i.e.
the map $X_0\to S$ is no longer bijective.
But it is bijective outside the singular points and 
every rational function $k(x,y)$ has
a pull-back to a meromorphic function on $X_0$.

\medskip


\noindent
\emph{Passage to infinity.}
Above we studied $\alpha$-roots while $x$ stays in ${\bf{C}}$.
Passing to $\infty$ we replace $x$ by $\zeta= \frac{1}{x}$
and corresponding $\alpha$-roots
are solutions to 
\[ 
P^*(\zeta,y)=
y^n+q\uuu {n-1}(\zeta^{-1})y^{n\vvv 1}+\ldots+q\uuu 0(\zeta^{-1})
\]
Again the local uniformisation theorem is used to construct
a local $t$-coordinates if multiple roots occur
and in this way a finite set of points is added to $X_0$ which yields 
a compact Riemann surface $X$ where we have a surjective map
$\rho\colon X\to \bar S$ which is  only fails to be bijective
at a finite (possibly empty) set of points.



\medskip







\centerline {\bf{1.5 Examples.}}
\medskip


\noindent
Consider the  curve $S$ defined by the equation $y^2=x^2+1$.
With $P=y^2-x^2-1$ we have
$\nabla(P)(x,y)= (-2x,2y)\neq 0$ on  
$S$.
The projective closure contains two points
$p_1=(0,1,1)$ and $p_2=(0,1,-1)$.
Close to $p_1$ we have local coordinates
$(\zeta,\eta)$ where
\[
(\zeta,1,1+\eta)\simeq
(1,\frac{1}{\zeta},\frac{1+\eta}{\zeta})\quad\colon\quad \zeta\neq 0
\]
The equation for $\bar S$ close to $p_1$ becomes
\[
\frac{(1+\eta)^2}{\zeta^2}=\frac{1}{\zeta^2}+1\implies
\]
\[
2\eta+\eta^2=-\zeta^2
\]
Hence $\zeta$ yields a local coordinate and $p_1$ is a non-singular point. 
In the same way one verifies that $p_2$ is 
a regular point. Hence
 $\bar S$ is a smooth projective curve and can therefore be identified with
a compact Riemann surface.






\medskip

\noindent {\bf{The curve
$y^4=x(x\vvv 1)^3$}}.
At  $(0,0)$ we can take $y$ as a local coordinate
on $S$ and then  $x$ has a zero of order 4 at this point.
At the point $p=(1,0)$  $S$ is locally a
cusp\vvv like curve where a local coordinate $t$ on the associated Riemann surface
$X$ is found such that:
\[
x=1+t^4\quad\text{and}\quad y= (1+t^4)^{\frac{1}{3}}\cdot t^3
\]
So at $p$
the meromorphic function $y$ has a zero of
order three while it has a simple zero at $(0,0)$
since here $y$ itself serves as a local coordinate.
Next, as $|x|\to+\infty$ we notice that 
\[ 
y^4=x^4(1-x^{-1})3\simeq x^4
\]
Gometrically it means that the curve $S$ regarded as a subset of
the 2-.dimensional complex $(x,y)$-space
has four asymptotic lines
of the form
\[ 
\ell_\nu=
\{ y= e^{2\pi i \nu/4}x\,\colon\, 0\leq\nu\leq 3\}
\]
From this it follows that above
$x=\infty$ there occur four points in $X$
and at each of these the meromorphic
functions
$x$ and $y$ both have simple poles.
\medskip

\noindent
From the above the reader can recognize that
the degree of the meromorphic function $y$ is four.
Similarly, $x$ has a multiple zero of order four at 
$p=(0,0)$ and four simple poles. So it has also degree four.
Next, consider the meromorphic function
\[ 
\phi=\frac{y}{x\vvv 1}
\]
Then $\phi$ has a simple zero at $(0,0)$ and at $(1,0)$
we recall that  $x\vvv 1= t^4$ while $y$ has a zero of order 3 
and hence  $\phi$ has a simple pole here.
At the boundary points at infinity we see that
$\phi$ has no poles and is $\neq 0$.
The conclusion is that the map defined by $\phi$ from
$X$ onto ${\bf{P}}^1$ is \emph{biholomorphic} which means that
$X\simeq {\bf{P}}^1$ and the associated algebraic function field $K$
is therefore isomorphic to the standard field of rational functions in one
variable.
The theory therefore predicts that
\[ 
K={\bf{C}}(\phi)
\]
which means that both $x$ and $y$ can be expressed as rational functions of
$\phi$.
Of course, this can be seen directly, i.e. the reader may verify that
\[ 
x=\frac{\phi^4}{\phi^4-1}\quad\colon\quad 
y=\frac{2\phi^4-\phi^5}{\phi^4-1}
\]
\medskip

\noindent
{\bf{Remark.}}
The example is instructive since it teaches how to find
the $\phi$-function in a  systematic way since
a mere guessing starting from the algebraic equation (*)
is not obvious.
\bigskip














\end{document}


