
\documentclass{amsart}

\usepackage[applemac]{inputenc}

\addtolength{\hoffset}{-12mm}
\addtolength{\textwidth}{22mm}
\addtolength{\voffset}{-10mm}
\addtolength{\textheight}{20mm}

\def\uuu{_}

\def\vvv{-}

\begin{document}

\centerline{\bf\large{Functional analysis and operator theory}}

\bigskip


\centerline{\bf{Contents.}}

\bigskip

\noindent
{\bf{0. Introduction}}
\bigskip

\noindent
\emph{Four specific  examples:}

\medskip

\noindent
\emph{a. Toeplitz matrices.}
\medskip

\noindent
\emph{b. The moment problem}
\medskip

\noindent
\emph{c. The Picard operator}
\bigskip






\noindent
\emph{0.1: Historic comments}

\bigskip



\noindent
\emph{0.0.1: Infinite systems of linear equations}

\bigskip
\noindent
\emph{0.0.2: Maxwell's equations in electrodynamics}


\bigskip

\noindent
\emph{0.0.3: Position of spectra and an inequality by Toeplitz}





\bigskip
\noindent
\emph{0.0.4 : Postive quadratic forms and a result by Beurling}


\bigskip
\noindent
\emph{0.0.5: Self-adjoint operators on Hilbert spaces}

\bigskip
\noindent
\emph{0.0.6: The Cayley transform}


\bigskip
\noindent
\emph{0.0.6 Spectral functions  }


\bigskip
\noindent
\emph{0.0.7 Unitary groups}

\bigskip
\noindent
\emph{0.0.8 An ugly example}


\bigskip
\noindent
\emph{0.0.9 Two examples from PDE-theory}

\medskip
\noindent
\emph{0.0.9.1 Propagation of sound}

\medskip
\noindent
\emph{0.0.9.2 The Bohr-Schršdinger equation}
\bigskip

\noindent
{\bf{Some special examples}}
\medskip

\noindent
\emph{1.  A linear system in infinitely many unknowns}

\medskip

\noindent
\emph{1.  A linear system in infinitely many unknowns}
\medskip

\noindent
\emph{1.  A linear system in infinitely many unknowns}
\medskip

\noindent
\emph{1.  A linear system in infinitely many unknowns}
\medskip

\noindent
\emph{2.  A singular integral}
\medskip

\noindent
\emph{3.  Carelson-Kronecker sets}

\medskip

\noindent
\emph{4.  $L^p$-inequalities}
\medskip

\noindent
\emph{5.  The complex Hilbert transform}
\medskip

\noindent
\emph{6.  The Kakutani-Yosida theorem}

\bigskip

\noindent{\bf{Basic facts in functional analysis}}

\medskip
\noindent
\emph{A. Three basic principles}


\medskip

\noindent
\emph{B.  Dual spaces and weak topologies}
\medskip

\noindent
\emph{C.  Compact metric spaces.}

\medskip

\noindent
\emph{D.  Support functions of convex sets}


\medskip

\noindent
\emph{E.  Non-linear calculus in Banach spaces}

\medskip

\noindent
\emph{F.  The logarithmic potential}
\medskip

\noindent
\emph{G.  A result about spectral values}

\newpage


\centerline{\bf{Special chapters}}
\bigskip

\noindent
\emph{Introduction.}
\medskip



\noindent 
\emph{ 0.0. Neumann's resolvent operators}



\medskip

\noindent
\emph{0.1: Locally convex topologies and Frechet spaces}
\medskip


\noindent
\emph{1. Normed spaces}

\medskip

\noindent
\emph{2. Banach spaces}


\medskip

\noindent
\emph{3. Linear operators}

\medskip

\noindent
\emph{4. Hilbert spaces}

\medskip

\noindent
\emph{4. B: Eigenvalues of matrices}
\medskip


\noindent
\emph{5. Dual spaces and locally convex spaces}

\medskip


\noindent
\emph{6. Fredholm theory}

\medskip

\noindent
\emph{7. Calculus on Banach spaces}
\medskip

\noindent
\emph{8. Bounded self-adjoint operators}
\medskip

\noindent
\emph{9. Unbounded self-adjoint operators}

\medskip

\noindent
\emph{10. Commutative Banach algebras.}


\medskip

\noindent
\emph{11. Exercises and further results.}


\bigskip


\centerline{\bf{Introduction.}}
\bigskip


\noindent
Basic  facts about normed vector spaces and bounded linear operators
appear in
¤ 1-6 under the headline Special Chapters.
The  less experienced reader may prefer to start directly with ¤ 1-6
and postpone the reading of earlier  text until
later.
However, a  survey 
appears under the headline
\emph{Some basic  facts in functional analysis} and 
a glimpse upon   this introductory 
section is  helpful as a guidance for the material in the special chapters.
In addition to ¤ 1-6, section  7  contains
material  which is  needed 
in
¤ 8-9 where we treat    
the spectral theorem for both bounded and unbounded
self-adjoint operators in Hilbert spaces.
Basic facts about
commutative Banach algebras are established  in
¤ 10 and ¤ 11 treats scatterred  results which foremost deal with
operators on
Hilbert spaces. 
\medskip


\noindent
{\bf{Differential operators.}} In addition to
general theory devoted to topological vector spaces and their linear operators,
Chapter xx is devoted to partial differential operators.
An instructive lesson appears in ¤ xx where  we construct
fundamental solutions to second order elliptic
operatars with variable coefficients which in general need not be symmetric.
As we shall see this is achieved via
Newton's classical formula
for 
fundamental solutions of second order elliptic operators
with constant coefficients,  together with
extensive use of Neumann series which are used to   solve  integral equations.
The reward is that  fundamental solutions and  
Greens' functions, are found in
a canonical fashion with  accurate estimates.
Another example is the solution to
first order differential equations of hyperbolic type in ¤ xx
where
the crucial step to get solutions
employs 
unbounded operators on Hilbert spaces of the Sobolev type.
A veritable challenge appears during the study of
the time-dependent Schršdinger equation
\[
i\cdot \frac{\partial f}{\partial t}=
-\Delta(f)+V(x)f
\]
where $\Delta$ is the Laplace operaror in
${\bf{R}}^n$ for some positive integer $n$ and
$V(x)$ a real-valued potential function.
One seks solutions $f(x,t)$ where $x$ belongs to
some domain $\Omega$ which may be bounded or unbounded, whike $t\geq 0$.
In addition one has some intial conditions and eventual boundary conditions to
ensure that the solution is unique,
It goes without saying that this leads to quite delicate problems.
In ¤ xx we  discuss certain situations where
the equation above occurs. Let us mention that already
when $n=1$ leads to a quite rich theory.
\medskip

\noindent
{\bf{Remark.}}
It is a matter of taste if one should regard all this as a topic 
within functional analysis or not.
Personally I think the general theory
only becomes interesting when constructions of this nature are performed.
So in that perspective ¤ xx is an essential and "rewarding" section for the  whole text.


\medskip

\noindent
{\bf{The spectrum of a linear operator.}}
The passage to infinite dimension
leads to phenomena which
do not occur in the finite dimensional case.
Consider as an example the Hilbert space
$\ell^2$ whose vectors are sequences of complex numbers
$x_0,x_1,x_2,\dots$ where $\sum\, |x_k|^2<\infty$.
Now there exists the forward shift operator
$S$ defined by $S(x_0,x_1,x_2,\dots)=(x_1,x_2,x_3,\dots)$ 
It is clear that $S$ is surjective, i.e. its range is $\ell^2$
while the kernel is the 1-dimensional  subspace generated
by
$e_0=(1,0,0,\ldots)$.
On the other hand, linear algebra teaches that if
$A\colon V\to V$ is a linear and operator on a finite dimensional 
vector space whose range is
$V$, then $A$ is injective.
The spectrum of the linear operator $S$ is 
consists of the set of complex numbers
$\lambda$ for which $\lambda\cdot E-S$ is
not invertible, where $E$ is the identity on $\ell^2$.
It turns out that this is a compact set in the complex
$\lambda$-plane which we denote by $\sigma(S)$.
In the infinite dimensional case there does not exist
a direct substitute for determinants which
are used to descibe spectra of linear operators
acting on finite dimensional vector spaces.
To find $\sigma(S)$ one must therefore
perform a special study.
if $\lambda|<1$  there exists a non-zero
vector $x$ such that $S(x)=\lambda\cdot x$.
In fact, this follows when we take
$x=(1,-\lambda,-\lambda^2,\ldots$. Hence $\lambda\cdot E-S$
has a non-zero kernel  and we conclude that the open unit disc
$D$ is contained in $\sigma(S)$.
If $\lambda= e^{i\theta}$ 
the situation is different. Here one checks that
no eigenvectors exist, i.e. the operator $e^{i\theta}\cdot E-S$
is injective.
But it is not invertible. The reason is that
the range of $e^{i\theta}\cdot E-T$
is a dense subspace of $\ell^2$, but not equal to the whole space.
To see this one can use another model of $\ell^2$
given by the Hardy space $H^2(T)$ whose vectors are
square integrable functions on the unit circle $T$.
which are boundsty values of analytic functions in the unit disc.
Every such function has a Fourier series expansion
\[ 
f(e^{i\theta})= \sum_{n=0}^\infty\, a_n\cdot e^{in\theta}
\]
which yield the analytic extension via the series
$f(z)=\sum_{n=0}^\infty\, a_n\cdot  z^n$.
Then $S$ can be expressed by
\[
S(f)= \frac{f(z)-f(0)}{z}
\]
With $\theta=0$ 
and some $q\in H^2(T)$
we seek $f$ so that
\[
f-S(f)= q(z)
\]
which means thar
\[
(z+1)f= zq(z)+f(0)
\]
Set $f=f(0)+ zg(z)$ and now $g$ must satisfy
\[
(z+1)zg+zf(0)=zq(z)\implies (z+1)g=q(z)-f(0)
\]
Above we are free to chose $f(0)$.
If $q(-1)=a$ we try $f(0)=a$, and if $q$ is continuous on $T$
one may expect that $g$ exists.
However, even with this choice of $f(0)$
one can constrcut continuuos $q$-functions where
no $g\in H^2(T)$ solves (xx).
See ¤ for further details.
\medskip

\noindent
{\bf{Remark.}}
The example above is a first example of
a bounded linear operator which spectrum fills up a show disc
and for spectral poinits which belong to the boundary
$T$ there do not exist non-zero eigenvectors.




\medskip

\noindent
{\bf{Adjoint operators.}}
In general, let $A\colon X\to X$ be a bounded inear operstor
from a Banach space $X$ into itself.
We shall learn how to construct the dual space $X^*$ and
the adjoint operator
$A^*\colon X^*\to X^*$.
A basic result asserts that $A$ is invertible if and only if
$A^*$ is so which entails that
$\sigma(A)= \sigma(A^*$.
We prove this in ¤ xx.
\medskip

\noindent
{\bf{Unbounded linear operators}}.
They arise from
pairs $(A,\mathcal D(A)$ where
$\mathcal D(A)$ is a dense subspace of a Banach space $X$ and
$A\colon \mathcal D(A)\to X$ a linear map.
The graph
\[
\Gamma(A)=\{(x,A(x)\,\colon x\in \mathcal D(A)\}\tag{i}
\]
is a subspace of $X\times X$ and one says that
$A$ is closed when (i)
is a closed subspace. The study of densely defined
and closed linear operators
is  a natural subject  because one encounters many examples in applications.
A crucial point is that one can associate a well-defined
spectrum $\sigma(A)$
of every densely defined and closed
linear operator.
But in contrast to bounded operators, the spectrum is in general not a 
compact set of the complex 
$\lambda$-plane.
\medskip


\noindent
{\bf{Example.}}
We have the Hilbert space
$L^2({\bf{R}})$ of complex-valued and square integrable functions on
the real $x$-line.
Consider a differential operator $P$ with polynomial coefficients:
\[
P(x,\frac{d}{dx})=p_0(x)+p_1(x)\frac{d}{dx}+
\ldots p_m(x)\frac{d^m}{dx^m}+
\]
So above $m\geq 1$ and $\{p_k(x)\}$ are polynomials 
with complex coefficients.
Since test-functions belong to $\mathcal D(P)$,
it follows that
$P$ is densely defined and 
in ¤ xx we shall learn that it has a closed graph.
The determination of $\sigma(P)$
is not at all clear, and it is only in the case when
$P$ has constant coefficients that one can
perform a precise analysis.
Namely, using Fourier's inversin formula and Parseval's equality
this amounts to study linear operators on square integrable functions on
the real $\xi$-line defined by
$f(\xi)\mapsto p(\xi)\cdot f(\xi)$ where
$P(\xi)$ is a polynomial
We shall discuss this in ¤ xx and here we only mention that if
\[
P(x,\frac{d}{dx})=\frac{d^2}{dx^2}
\]
then the spectrum of $P$ is the unbounded real interval
$[0,+\infty)$.


\noindent
{\bf{Schšdinger operators on the real line}}
With
$X=L^2({\bf{R}})$ we there exists a densely defined operator
\[
 A(f)(x)= -\frac{d^2 f}{dx^2}+ V(x)f(x)
\]
when $V(x)$ is some  complex-valued function which at least is
locally square integrable on the real $x$-line.
Here the spectral analysis becomes quite involved.
An account appears in ¤ xx where we treat  the case when
$V(x)$ is 
integrable, i.e. the $L^1$-norm
\[
||V||_1=\int_{-\infty}^\infty\, |V(x)|\, dx<\infty
\]
Here  one can search eventual eigenvalues $\lambda$ outside
$[0,+\infty)$ for which
there exists a non-zero
$f\in L^2({\bf{R}})$ such that
\[
-\frac{d^2 f}{dx^2}+ V(x)f(x)=\lambda\cdot f(x)
\]
In ¤ xx we show that the absolute value
of every such eigenvalue
$\lambda$  satisfies
\[
|\lambda|\leq \frac{1}{4}\cdot ||V||_1^2
\]
The proof relies upon
Neumann's equations for resolvents
and a  pertubation argument using 
properties of the function 
\[
P_V(s)=\max_x\, \int\, e^{-s|x-y|}\,v(y)|\, dy
\]

\medskip



\noindent
{\bf{Remark.}}
We could continue by listing further examples and results
about spectral properties of
unbounded operators  of the Schršdinger type, i.e. arising via second order 
elliptic
 operators. Already 
the 1-dimensional case contains a wealth of
results and
many problems for current research remain open.
The interested reader should consult the final chapters in the text-book
\emph{Linear Operators and their spectra} by E. Brian Davies
which in addition to its excellent presentation
of quite recent discoveries
contains an extensive list of literature covering
work up to 2006.

\bigskip

\noindent
{\bf{Fredholm operators.}}
Let $A\colon X\to Y$ be a bounded linear operator from one Banach space into 
another. It is called Fredholm if both the 
kernel $\text{Ker}(A)= \{ x\,\colon \, A(x)=0\}$ and
$\text{Coker}(A)=\frac{Y}{A(X)}$
are finite dimensional vector spaces.
The index of a Fredholm operator is defined by
\[
\text{ind}(A)= \dim(\text{Ker}(A)-
\dim( \text{Coker}(A))
\]
In ¤ xx we shall learn that if
$T\colon X\to X$ is a compact operator on a
Banach space $X$, then
$A=E+T$ is Fredholm and
has index zero.
Next, to each 
linear operator $A\colon X\to X$ on a complex Banach space
its \emph{essential spectrum} is defined as
the set of complex numbers
$\lambda$ for which $\lambda\cdot E-A$ is not a Fredholm operator.
It is denoted by $\sigma_{\text{ess}}(A)$
and we shall learn that it is a compact subset of
${\bf{C}}$.
The full spectrum $\sigma(A)$ is the disjoint union of
its essential spectrum and
a (possibly empty)  set of 
spectral values $\{\lambda_k\}$ where
$\lambda_k\cdot E-A$ are Fredholm.
If $T\colon X\to X$ is compact, then a result which goes back to
Fredholm, and for operators on general 
Banach spaces was put forward by 
F. Riesz around 1910, asserts that
$\sigma_{\text{ess}}(T)$ is reduced to $\{0\}$.
\medskip


\noindent
{\bf{Toeplitz' operators on $H^2(T)$}}
We consider the Hardy space from ¤ xx.
 Analytic function theory shows 
that an $L^2$-function $g$ on $T$ belong to
$H^2(T)$ if and only if
\[
\int_0^{2\pi}\, e^{in\theta}\cdot g(e^{i\theta})\, d\theta=0
\quad \colon\, n=1,2,\ldots
\]
There exists the bounded projection operator
$\Pi\,\colon L^2(T)\to H^2(T)$. More precisely, each
$f\in L2(T)$ has a unique Fourier expansion
\[
f(e^{i\theta})= \sum\, a_n\cdot e^{in\theta}
\]
where the sum extends over all integers
and $\sum\, |a_n|^2<\infty$. Now
\[
\Pi(f)(e^{i\theta})=\sum_{n=0}^\infty\, a_n\cdot e^{in\theta}
\]
Next, let  $a(\theta)$ 
belong to $L^\infty(T)$, i.e. it is a bounded measurable function in
the sense of Lebesgue. The Toeplitz operator
$T_a$ on $H^2(T)$ is defined by
\[
T_a(f)= \Pi(af)
\]
Thus one multiplies functions  $f\in H^2(T)$ with $a$ and
after they are  projected to the Hardy space.
The determination of
the essential spectrum of
$T_a$ is quite delicate and is an active area for research up to the present date.
Only the case hen
$a$ is a continuous function is easy. In ¤ x we show that
$\text{ess}(\sigma(T)$ is equal to the range $a(T)$.
But already the case when $a$ is piecewise continuous leads to
situations where
no such simple formula exists.
\bigskip



\noindent
{\bf{The Dirichlet problem.}}
Let $\Omega$ be a bounded and connected open set in
${\bf{R}}^n$ for some $n\geq 3$.
We assume that the boundary
$\partial\Omega$ is a finite union of
closed surfaces of class $C^1$ which implies that
a well-defined area measure $d\omega$.
By a result
which goes back to Newton
each continuuos boundary function $g\in C^0(\partial\Omega)$
yields a harmonic function $G$ in $\Omega$ defined by
\[
G(p)= \int_{\partial\Omega}\, 
|p-q|^{-n+2}\cdot g(q)\, d\omega(q)
\]
Moreover, the $C^1$-hypothesis and elementary calculus entail that
$G$ extends to a continuous function 
on the closure of $\Omega$. In particular there exists
the boundary function $g^*=G|\partial\Omega$ which 
by Newton's construction has $G$ as its harmonic extension.
Now
\[
T\colon g\mapsto g^*
\]
is a linear operator from
$C^0(\partial\Omega)$ into itself.
In ¤ xx we explain how the
maximum principle for harmonic functions
implies that the Dirichlet problem has a solution for
every continuous boundary function if the range of the linear operator
$T$ is dense.
At this stage one profits upon general functional analysis. Namely,
the dual of 
$C^0(\partial\Omega)$ consists of Riesz measures on
the boundary, so if the range is not dense there
exists a non-zero Riesz measure $\mu$ on
$\partial\Omega$ with the property that
\[
\int_{\partial\Omega}\,\bigl[\,  
|p-q|^{-n+2}\cdot g(q)\, d\omega(q)\,\bigr]\, d\mu(p)=0
\]
for every $g\in C^0(\partial\Omega)$.
In ¤ xx we explain why this vanishing entials that
the harmonic function defined in the complement of
$\partial\Omega$
by
\[
U_\mu(x)=\int_{\partial\Omega}\,\bigl[\,  
|p-x|^{-n+2}\, d\mu(p)
\]
vanishes identically and from this one can deduce that
$\mu=0$ which gives a contradiction and  proves
that the Dirchlet problem always can be solved for
every
$g\in C^0(\partial\Omega)$.
\bigskip


\noindent
{\bf{The Riemann hypothesis.}}
One does not need "sophisticated theoretical concepts"
to arrive at
deep problems.
An outstanding   challenge  is to
prove (or disprove) the famous Riemann hypothesis 
about zeros of the $\zeta$-function.
Beurling has proved
that this hypothesis is equivalent to a certain closure
result which at first sight appears to be "elementary" and
goes as follows: 
To each positive real number $x$ we denote by $\{x\}$ the unique
largest integer
such that $0\leq x-\{x\}<1$.
If $M$ is a positive integer we
define functions $\rho_1(x),\ldots,\rho_M(x)$ 
on the open unit interval $(0,1)$ by
\[
\rho_j(x)=\frac{j}{Mx}-\{\frac{j}{Mx}\}
\]
Set
\[
\beta(M)=
\min\,\int_0^1\, (c_1\cdot \rho_1(x)+\ldots c_M\cdot \rho_M(x)-1)^2\, dx
\]
with the minimum taken over $M$-tuples of real numbers
$\{c_j\}$ which satisfy
\[
\sum_{j=1}^{j=M}\,jc_j=0\tag{i}
\]
Beurling proved that Riemann's hypothesis is true if and only if
\[
\lim_{M\to\infty}\, \beta(M)=0\tag{*}
\]
In spite of the  appearantly simple assertion
one is left with 
an outstanding open question. Notice
that each $\beta(M)$ is
given as the minimum of a quadratic form
of the $M$-tuple $c_1,\ldots,c_M$ satisfying the linear
equation (i).The difficulty to check if (*) holds or not
is that
the $\rho$-functions become quite irregular as $M$ increases, and 
they hide
subtle arithmetic  properties which is the reason why
the Riemann conjecture remains open.






\medskip

\noindent
{\bf{A result by Hardy and Littlewood}}.
For students who enter the study of functional analysis, a device is to
first perform some serious studies about additive series
and
learn about  such beautiful results as the
Tauberian theorem by Hardy and Littlewood which 
asserts the following:
Let $\{a_n\}$ be a sequence of non-negative real numbers such that there exists
the limit
\[
A=\lim_{r\to 1}\,  (1-r)\cdot a_nr^n
\]
Then it follows that
\[
\lim_{N\to \infty}\,\frac{a_1+\ldots+a_N}{N}
\] 
also  exist and its limit value is equal to $A$.
The proof offers an instructive lesson about
how to handle  inequalities which is the core in functional analysis.
It is given in Chapter 1 from my notes in analytic function theory.
Let me    remark
that the result above 
cannot be deduced from
"soft methods" which rely upon Baire's category theorem.
So the Hardy-Littelwood theorem is not covered by the material in this chapter.
\medskip

\noindent
{\bf{A result by Beurling.}}
We shall learn about the construction of dual spaces and
the notion of weak convergence.
An example of a Banach space consists of
bounded continuous functions $f(x)$ on the real line equipped with
the maximum norm.
A subspace arises via the inverse
Fourier transform, i.e. for every Riesz measure
$\gamma$ on the real $\xi$-line with a finite total variation we get
the bounded continuous function
\[
f(x)= \int\, e^{ix\xi}\, d\gamma(\xi)
\]
Let $\mathcal A$ be its closure taken in the Banch space
$C^0_b({\bf{R}})$.
Next, a sequence $\{\mu_n\}$ of Riesz measures
on the real $x$-line is said to converge weakly in Beurling's sence if there
exists a constant $M$ such that the total variations
$||\mu_n||\leq M$ for each $n$, and
\[
\lim_{n\to\infty}\, \int\, e^{ix\xi}\, d\mu_n(x)
=0
\] 
hold for each fixed $\xi$.
It is easily seen that if $f\in\mathcal A$ then
\[
\lim_{n\to\infty}\, \int\, f(x)\, d\mu_n(\xi)
=0
\]
for every sequence
$\{\mu_n\}$ which converges to zero in
Beurling's sense.
In ¤ xx we prove thst  the converse holds,  i.e.
the convergence property above for a given
bounded continuous functionÊ$f$ entails that
$f\in\mathcal A$.
In contrast to proofs of  general
nature which are derived via Baire's theorem, the result by
Beurling requires a quite involved proof.
So the reader should be aware of the fact that
the general theory is helpful  but not always sufficent to
attain more refined results.



\newpage

\centerline{\bf{Historic comments.}}

\bigskip

\noindent
The need for 
functional analysis in
a general set-up was recognized
after Weierstrass had found cases where 
"obscure phenomena"  appear  in the
calculus of variation, starting from 
the study of minimal surfaces with fixed boundaries in
${\bf{R}}^3$ which leads to
some
peculiar situations which were 
discovered by Hermann Schwarz in 1866 while he
considered surfaces with vanishing mean curvature.
To overcome these obstacles  new
methods 
were invented by Carl  Neumann
in his  pioneering work \emph{Untersuchungen Ÿber das logarithmische
und Newtonsche Potential}[Teuber. Leipzig. 1877].
Here  
elliptic boundary value problems
were solved by operator methods which at that time
was a revolutionary idea.
Neumann's constructions of
bounded  resolvent operators is fundamental. In 
¤ 0.0 we expose  Neumann's spectral theory for unbounded
densely defined operators
which 
leads to an operational calculus with a wide range of
applications.
\medskip

\noindent
Results   which settled  Neumann's boundary
value problem in non-convex domains
were established
by
PoincarŽ  in the article \emph{La mŽthode de Neumann et
le problme de Dirichlet}
from 1897. His analysis is 
based upon solutions to certain variational problems where
a crucial step  was to use a symmetrization of
the Neumann kernel $K(p,q)$ which is defined on the boundary
$S$ of a  domain in ${\bf{R}}^3$
of class $C^2$.
In ¤ xx below we
discuss  two
famous value problems
whose solutions have inspired later work.

\medskip

\noindent
More extensive classes of integral operators
than those defined by the Newton potential  
were introduced by   
Fredholm whose  article 
\emph{ Sur une classe d'Žquationes fonctionnelles} [Acta math. 1903]
has been very
influential during the early development of  functional analysis.
Fredholm's studies of integral equations
inspired Hilbert to create  an abstract theory
which led to the notion of
infinite dimensional Hilbert spaces. His book
\emph{Integralgleichungen} from 1904 
gave  the first
general account of 
linear operators and contains
the spectral theorem for bounded self-adjoint operators
on Hilbert spaces. After the contributions
by Fredholm and Hilbert, 
spectral properties  of  operators on Hilbert spaces
were investigated by many authors.
An example
is a result due to Jentsch
from 1912 concerned with
symmetric integral operators with  positive kernels.
His theorem asserts that for every such operator
there exists a positive real eigenvalue $\lambda_*$ whose eigenspace is
one-dimensional and generated by a positive function, while the
remaining eigenvalues all have absolute value $\geq \lambda_*$.
This should be compared with
earlier results due to Perron and Frobenius about
positive matrices where we
recall  that if
$A=\{a_pq\}$ is an $N\times N$-matrix whose elements are real and positive numbers,
then the characteristic polynomial $P_A(\lambda)$ has a simple real root
$s^*>0$   and
$|\alpha|<s^*$ hold for every other root.






\medskip

\noindent
The need for a  spectral theory of  unbounded linear operators
was put forward   by Birkhoff
and Weyl  around 1910 while they studied differential operators.
Consider for example
a second order ODE-equations 
\[
P(u)= \frac{d^2 u}{dx^2}+ q(x)\cdot u
\]
where $q(x)$ is a real-valued continuous function on the real $x$-line.
Given a bounded interval $[0,\ell]$ one seeks solutions
$u$ to the equation
\[
P(u)+\lambda\cdot u=0\tag{*}
\]
which satisfy the boundary conditions $u(0)=u(\ell)=0$.
Here it is easy to show
that the set of real numbers $\lambda$ for which (*) has a non-trivial
solution
 form an infinite discrete sequence of real numbers.
Passing to  an infinite interval $[0\leq x<+\infty)$
the situation becomes  more involved.
Here one seeks solutions
$u$ of (*) such that $u(0)=0$ and
\[
\int_0^\infty\, u(x)^2\, dx<\infty
\]
In contrast to the case of bounded intervals non-real 
$\lambda$ can occur in (*).
Following Weyl one says that
the "Grenzpunktfall" occurs if (*) has no non-trivial solutions
$u\in L^2{\bf{R}})$ when $\lambda$ is non-real.
The significance of this condition
can  be understood after one has  constructed
spectral resolutions of unbounded 
self-adjoint  operators. A crucial fact is that
when Weyl's
"Grenzpunktfall" occurs, then there exists a unique spectral function
of the given ODE-operator $P$.
Extension to  
elliptic PDE-equations was undertaken by Carleman
and we give further comments and examples in the subsection below about
self-adjoint operators on
Hilbert spaces.
\bigskip


\noindent
{\bf{A personal remark.}}
The reader will recognize that many results are
attributed to Torsten Carleman (1892-1949).
This is motivated by his extensive contributions to the general theory during
the years 1916-1923.
Starting from
pioneering work by C. Neumann, PoincarŽ, Hadamard, Fredholm and Hilbert, 
followed by some further  contributions by  Schmidt, Weyl
and Toeplitz whose articles at an early stage
treated various   unbounded operators,
Carleman established 
the spectral   theory for unbounded self-adjoint operators on 
separable Hilbert spaces in 1923.
He also 
proved several
fundamental  inequalites which  lead
to quite precise estimates for resolvent operators and can be used to obtain
asymptotic formulas for
eigenvalues of elliptic PDE-operators. 











\bigskip










\noindent
Next follow some  comments  which
point out some of the major issues
and expose some basic facts which are used frequently in functional analysis.


\medskip


\centerline{\bf{Matrices and determinants}}.
\medskip

\noindent
A separate section 
is devoted to    finite dimensional  constructions which
are essential to study linear operators on
normed vector spaces of infinite dimension.
We expose the Cayley-Hamilton
calculus for matrices which
is helpful as a start before Neumann's resolvents are studied for
operators on infinite dimensional spaces.
In ¤ xx  we describe some 
results  from
 Hilbert's
text-book \emph{Integralgleichungen} 
about the construction of
Fredholm's determinants 
which are used to  express
the resolvents of 
integral operators. Here is 
an important outcome of
the Fredholm-Hilbert theory.
Let $\Omega$
an  open set in ${\bf{R}}^n$ and
$K(x,y)$ a real-valued and square integrable function
in $\Omega\times\Omega$.
In general $K(x,y)\neq K(y,x)$
so the integral operator on
the Hilbert space $L^2(\Omega)$ defined by
\[
\mathcal K(f)(x)=\int_\Omega\, K(x,y)\cdot f(y)\, dy
\]
is not self-adjoint and its spectrum needs not be real.
A major fact in the Fredholm-Hilbert theory asserts  that the kernels 
$\Gamma(x,y,\lambda)$
of
the resolvent operators
$R_K(\lambda)= (\lambda\cdot E-\mathcal K)^{-1}$
are operator-valued  meromorphic functions
of the complex variable $\lambda$ whose
poles are controlled via Fredholm's resolvent determinant 
$\mathcal D_K(\lambda)$ which makes the operator valued function
$\lambda\mapsto \mathcal D(\lambda)\cdot R_K(\lambda)$  entire.
In ¤¤ we prove a result due to Carleman which
asserts that if $\{\lambda_n\}$ is the sequence of complex numbers
where
$\{\frac{1}{\lambda_n\}}$ give the non-zero spectral
values  of the compact operator
$\mathcal K$, then
\[
\mathcal D_K(\lambda)=\prod\,  (1-\frac{\lambda}{\lambda_n})\cdot e^{\frac{
\lambda}{\lambda_n}}
\]
where the right hand side is the convergent Hadamard product
of an entire function of exponential type.
We have announced this  to underline that
more delicate inequalities   in operator theory
often rely heavily upon 
analytic function theory or Fourier analysis.
So the reader should be aware of the fact that
functional analysis is not
"an independent subject", i.e. the results in the general theory
serve as a guidance while
one often needs  specific computations from other disciplines to attain sharp
inequalities.
Another example where analytic function theory is used appears
in Thorin's  theorem. The proof is given in ¤ xx
using
Hadamard's convexity theorem
for maximum norms
of analytic functions in strip domains.





\medskip


\noindent
\emph{Hadamard's radius formula.}
A veritable "high-point" appears in   ¤¤ XX.
One starts with
a local Taylor  series $\sum\, c_nz^n$ 
which converges and gives an analytic function in some disc
centered at the origin.
In his thesis from 1894, Hadamard
found
necessary and sufficient conditions in order that
$f$ extends to a meromorphic function to larger discs,
expressed  via properties of 
the recursive Hankel determinants defined by  
the Taylor  sequence $\{c_n\}$.
Moreover,  Hadamard's  precise
analysis of determinants, give insight about
absolute values of the poles which
occur while $f$ extends to a meromorphic function.

\bigskip

\noindent
\centerline{\bf{2. Measure theory.}}
\medskip

\noindent
We assume that 
the reader is already  familiar with
Lebesgue theory, as well as  Borel-Stieltjes integrals and
the description of the dual space of continuous functions on
a compact space via the representation theorem by F. Riesz.
Relevant background 
appears
in the appendix of my notes devoted to measure theory.
An exception is the construction of integrals in the sense of
Hellinger where quadratic  differences appear while  
the construction of  Stieltjes'
integrals is extended.
In ¤ xx we expose  results from
his work \emph{Die Orthogonalinvarianten quadratischer Formen von unendlichen
vielen Variabeln} [Dissertation. Gšttingen 1907].
Let us   remark that the construction of Borel-Stieltjes  integrals  of 
complex-valued functions extends  verbatim to  vector-valued
functions.
For example, let $X$ be a Banach space
and
consider a function
\[
s\mapsto x(s)\tag{i}
\]
defined on a real interval $\{a\leq s\leq b\}$.
Introducing the norm on $X$
we  consider  variations with respect to partitions of
$[a,b]$, i.e. when
$a=s_0<s_1<\ldots<s_M=b$
we set
\[
V= \sum_{\nu=0}^{M-1}\, ||x(s_{\nu+1})-x(s_\nu)||
\]
If there exists a constant $C$ such that
$V\leq C$ for all partitions as above
one says that
the vector-valued function  (i)  has a bounded total
variation.
The same construction as for complex-valued functions
give Borel-Stieltjes  integrals
\[
\int_a^b\, g(s)\cdot \frac{dx}{ds}
\]
for every $g\in C^0([a,b])$
with values in  $X$.
More precisely, the integral  is a limit of Borel-Stieltjes sums:
\[
\sum_{\nu=0}^{M-1}\, g(s_\nu)\cdot (x(s_{\nu+1})-x(s_\nu))
\] 
taken over partitions where $\{\max\,s_{\nu+1}-s_\nu\}$
tend to zero.
The function in  (i) is  absolutely continuous if there
to  each $\epsilon>0$  exists
$\delta$ such that
\[
\sum\, ||x(s_\nu-x(t_\nu)||<\epsilon
\]
whenever $\{[t_\nu,s_\nu]\}$ is a finite family of
of subintervals of $[a,b]$ arranged so that
$s_\nu\leq t_{\nu+1}<s_{\nu+1}$
and
$\sum\,(s_\nu-t_\nu)<\delta$.
So many constructions
which appear in ordinary calculus and measure theory
extend while one regards vector-valued integrals.

\medskip


\noindent
{\bf{2.1 Weak limits of $L^2$-functions.}}
Let us recall some  fundamental   results 
established by F. Riesz in the article \emph{Memoire Ÿber Systeme integrierabarer
Funktionen} [Math. Ann. 1910 ].
Without essential loss of generality we
expose his results for functions in the Hilbert space
$L^2[0,1]$
where $0\leq x\leq 1$ is the unit interval.
Following Riesz, a sequence $\{f_n\}$ of Lebesgue measurable and
square integrable functions 
converges weakly to an $L^2$-function $f$ if there exists a constant
$M$ such that the $L^2$-norms 
$\{||f_n||_2\leq M\}$ for every $n$ and
\[
\lim_{n\to\infty}\int_0^x\, f_n(s)\, ds=\int_0^x\, f(s)\, ds
\] 
hold for every $x$.
A first result  is that this weak convergence entails that
\[
\lim_{n\to\infty}\int_0^1\, f_n(s)\cdot \phi(s)\, ds=\int_0^1\, f(s)\cdot \phi(s)\, ds
\] 
hold for every $L^2$-function $\phi$.
Next, let
$\{g_n\}$ be   another sequence of $L^2$-functions which 
under dominated converge to a limit function $g$.
It means that there exists some non-negative $L^2$-function $\gamma(x)$ such that
\[
|g_n(x)|\leq \gamma(x)
\]
for all $n$, and
$\lim_{n\to\infty}\, g_n(x)= g(x)$ holds almost everywhere on $[0,1]$.
Under this assumptions, Riesz proved that
$g$ is an $L^2$-function and one has the limit formula
\[
\lim_{n\to\infty}\int_0^1\, f_n(s)\cdot g_n(s)\, ds=\int_0^1\, f(s)\cdot g(s)\, ds\tag{*}
\] 
This ressembles the Lebesgue theorem for dominated convergence in
$L^1[0,1]$.
A proof of Riesz'  result in $L^2$ is  given in ¤ xx.
Another  useful fact by Riesz  goes as follows:
Let $\{f_n\}$
be a sequence in $L^2$ such that
\[
\lim_{n\to\infty}\int_0^1\, f_n(s)\cdot \phi(s)\, ds=0
\] 
hold for every $L^2$-function $\phi$. Then  there exists a constant $M$
such that
\[
||f_n||_2\leq M
\]
for all $n$, i.e. the sequence is automatically bounded in the $L^2$-norm.,
Moreover,
there exists 
a sequence of convex combinations 
\[
s_N=\sum_{k= 0}^{M}c_0^{(N)}f_N+\ldots+c_M^{(N)}\, f_{N+M}
\]
where each sum is taken over a finite set of integers
and 
the $c$-coefficients are non-negative while 
$c_0^{N}+\ldots c_0^{N}=1$ hold for all $N$ and one has the strong limit
\[
\lim_{N\to\infty}\,||S_N||_2=0
\]
Thus, by taking convex combinations from 
$\{f_n\}$ we obtain a  sequence of $s$-functions 
which tend to zero in the $L^2$-norm.


\bigskip



\centerline{\bf{3. Weak limits in separable Hilbert spaces.}}

\medskip


\noindent
Every separable Hilbert space is
isomorphic to $\ell^2$ whose vectors a sequenes of complex numbers
$x=\{x_p\}$ with a finite norm
\[ 
||x||= \sqrt{\sum_{p=1}^\infty\, |x_p|^2}
\]
In spite of this elementary definition, the geometry in
$\ell^2$ is very rich.
A crucial fact is that if
$\Pi$ is a closed subspace in
$\ell^2$ then
its complement
\[
\Pi^\perp=\{y\in\ell^2\,\colon\,\langle x,y\rangle=0\}\tag{i}
\]
is a new subspace and
\[
\ell^2=\Pi\oplus\Pi^\perp
\]
Next, consider
a sequence of closed subspaces $\{\Pi_1,\Pi_2,\ldots\}$.
Each vector $x$
in $\ell^2$ is decomposed via (i) to give
\[ 
x=
\pi_n(x)+\pi_n^\perp(x)\tag{ii}
\]
One says that the sequence $\{\Pi_n\}$
converges weakly to a closed
subspace $\Pi$  if the following hold: 
\[
\lim_{n\to \infty}\, ||\pi_n(x)-x||=0\quad\colon x\in \Pi\tag{1}
\]
\[
\lim_{n\to \infty}\, ||\pi^\perp_n(x)-x||=0\quad\colon x\in \Pi^\perp\tag{2}
\]
It turns out
that
every sequence $\{\Pi_n\}$ of closed subspaces contains
at least one convergent subsequence which tends weakly to a limit space
$\Pi$.
We prove this in ¤ xx.
The result is  remarkable since
the Hilbert space $\ell^2$ 
has infinite dimension. while the assertion  above gives a
"weak compactness property" for 
the family of closed subspaces.
\medskip

\noindent
{\bf{3.1. Kernel functions.}}
Let us consider  take $L^2[0,1]$ as a model for a separable Hilbert space.
Thus, the vectors are complex-valued and square integrable functions in
the sense of Lebesgue.
If $\Pi$ is a closed subspace there exists an orthonormal basis 
$\phi_n(x)\}$, where
each $\phi$-function has $L^2$-norm equal to one and
\[
\int_0^1\, \phi_n(x)\cdot \overline{\phi_k}(x)\,dx=0
\quad\colon k\neq n
\]
We associate the kernel function
\[
\phi(x,y)=
\sum\, \phi_n(x)\cdot \overline{\phi_n}(y) 
\]
Now there exists the linear operator
which sends each
$h\in L^2[0,1]$ to
\[
\Phi(h)(x)= \int_0^1\,\phi(x,y)\cdot h(y)\, dy
\]
Then one easily verifes that
$\Phi$ is the orthogonal projection onto the subspace
$\Pi$. 

\medskip

\noindent{\bf{3.2.The general Bessel inequality}}.
It asserts that for every pair
$h,g$ in
$L^2[0,1]$ one has:
\[
\bigl|\iint\, g(x)\phi(x,y)h(y)\, dxdy\,\bigr|\leq ||g||_2\cdot ||h||_2\tag{2.1}
\]
with equality if and only if both $h$ and $g$ belong to $\Pi$.
The proof of (2.1) is easy but we shall supply details in ¤ xx.
\medskip

\noindent
{\bf{3.3. Weak limits of  operators}}
Let $[a,b]$ be a bounded real interval where $0<a<b$.
Given a subspace $\Pi$ and an orthonormal famly
$\{\phi_n\}$ as above  we  consider a kernel function of the form
\[
\rho(x,y)=\sum\, \mu_n\cdot \phi_n(x)\cdot \overline{\phi_n}(y) 
\]
where $0\leq \mu_n\leq b$ hold for each $n$.
In this case one has the Bessel inequality
\[
\bigl|\iint\, g(x)\rho(x,y)h(y)\, dxdy\,\bigr|\leq b\cdot ||g||_2\cdot ||h||_2
\]
Again a weak compactness principle holds.
 More precisely, let $\{\rho_1,\rho_2,\ldots\}$ be a sequence
 of kernel functions constructed as above via
pairs of an orthonormal famliy of $\phi$-functions and
a $\mu$-sequence.
Then there exists at least one subsequence 
$\{\rho_{n_k}\}$
which converges weakly to
a bounded linear operator $A$ which
means that:
\[
\lim_{k\to \infty}\, \int_0^1\, \rho_{n_k}(x,y)\cdot h(y)\, dy=
A(h)(x)\tag{3.1}
\]
hold for every $h\in L^2[0,1]$.


\bigskip




\centerline {\bf{4. Symmetric operators}} 
\medskip



\noindent
Much attention will be given
to the spectral theorem for unbounded self-adjoint operators
on a separable Hilbert space. 
So let us already in this  introduction 
give a brief exposition 
to
illustrates our major theme.
Consider a doubly indexed and symmetric
sequence of real numbers
$\{a_{pq}\}$,  i.e. 
$a_{pq}=a_{qp}$ hold for all pairs of positive integers.
The sequence is said to be 
of the Hilbert-Schmidt type if
\[
\sum\sum \, a_{pq}^2<\infty\tag{*}
\]
When (*) holds we get a linear operator
$A$ on $\ell^2$ which sends a vector $x$ to a vector
$y=\{y_p\}$
where
\[ 
y_p=\sum_{q=1}^\infty\, a_{pq}x_q
\]
The spectral theorem for symmetric matrices in the finite dimensional case
was extended by Hilbert to  bounded and symmetric linear operators on
$\ell^2$.
This fundamental result is exposed in ¤  8 from special chapters.
Applied to a Hilbert-Schmidt operator it gives
a sequece $\{\phi_n\}$ of pairwise orthogonal eigenvectors
of unit norm in $\ell^2$ with non-zero real eigenvalues $\{\lambda_n\}$, i.e. 
\[
A(\phi_n)=\lambda_n\cdot \phi_n
\] 
hold for each $n$.
Let $V= \oplus\, {\bf{C}}\cdot \phi_n$
be the closed subspace of
$\ell^2$ generated by these eigenvectors. Then 
the kernel of $A$ is  the orthogonal complement
\[ 
V^\perp=\{ y\,\colon\langle y,V\rangle =0\}
\]
and one has the direct sum decomposition
\[
\ell^2=V\oplus V^\perp
\] 
If  
$\{\psi_k\}$ is an
orthonormal basis in $V^\perp$, then 
$\{\phi_n\}$ and $\{\psi_k\}$  give an ON-basis in $\ell^2$ and there exists
a unitary matrix $U$
which sends the standard $e$-basis  to the ON-basis given by the pair
$\{\phi_n\}$ and $\{\psi_k\}$. It follows that
\[
A= U^*\circ B\circ U
\]
where $B$ is the linear operator expressed  by  a diagonal matrix
where the eigenvalues $\{\lambda_n\}$ appear.
\medskip

\noindent
{\bf{4.1 Unbounded symmetric matrices.}}
Consider a real and symmetric doubly indexed sequence
$\{\alpha_{pq}\}$ such that
\[
\sum_{q=1}^\infty \, \alpha_{pq}^2<\infty\tag{1}
\]
hold for each $p$.
This yields
a densely defined linear operator
$A$ on $\ell^2$ whose domain of definition
$\mathcal D(A)$ consists of $\ell^2$-vectors $x$ 
such that
\[
\sum_{p=1}^\infty\,\bigl|
\sum_{q=1}^\infty \, \alpha_{pq}\cdot x_q\bigr|^2<\infty\tag{2}
\]
A sequence  of Hilbert-Schmidt operators $\{A_n\}$
defined by the double indexed sequences
$\{a_{pq}^{(n)}\}$ of real numbers
converges weakly to $A$ if
\[
\lim_{n\to \infty}\, \sum_{q=1}^\infty \, (a_{pq}^{(n)}-\alpha_{pq})^2=0\tag{3}
\] 
hold for every positive integer $p$, and in addition there exists a constant $M$ such that
\[
\sum_{q=1}^\infty \, (a_{pq}^{(n)})^2\leq
\sum_{q=1}^\infty \, \alpha_{pq}^2\tag{4}
\]
for each $p$.
The question arises if (3-4) entails that
\[
\lim_{n\to \infty}\, A_n(x) =A(x)\tag{5}
\]
hold for each vector $x\in\mathcal D(A)$, where
the limit means that the $\ell^2$-norms of
$\{A_n(x) -A(x)\}$ tend to zero.
It turns out that in general (5) fails.
This leads us to the following: Denote by $\mathcal S$ the family of symmetric
sequences for which (1) hold.

\medskip

\noindent
{\bf{4.2 Definition.}}
\emph{An operator in $\mathcal S$
is of 
Class I if
(5) hold for every weak approximation by Hilbert-Schmidt operators.}
\medskip

\noindent
{\bf{4.3 Carleman's criterion.}}
We shall learn  that  a necessary and sufficient condition for
an operator $A$ in 
$\mathcal S$ to be of Class I is that there does not exist a non-zero
vector $\phi\in\mathcal D(A)$
such that
\[
A(\phi)= i\cdot \phi
\]
where $i$ is the imaginary unit.
If $A\in\mathcal S$ is not of Class I it is said to be of Class II.
We will also give examples of Class II-operators $A$
and  mention that
they include Stieltjes' 
symmetric matrices
for which
\[
a_{p,p+1}= a_{p+1,p}=b_p\quad\colon p=1,2,\ldots \tag{i} 
\] 
where $\{b_p\}$ is a sequence of positive real numbers, while
$a_{p,q}=0$ for all other pairs.
The condition that  a Stieltjes matrix $A$ is of class I
is expressed by Stieltjes' criterion for determined 
moment problems which amounts to 
check if the infinite continued fractions associated to
a given  $b$-sequence converges or not.
Let us remark that growth conditions on $\{b_p\}$
alone do not give criteria for
the convergence of its associated continued fractions.
This illustrates that in general one cannot expect
"easy criteria " in order that  a  matrix  in
$\mathcal S$ is of Class I or not.
However, the following "positive result" is
proved in ¤ XX:
If the series
\[
 \sum_{p=1}^\infty\, \frac{1}{b_p}=+\infty
\]
then the Stieltjes   matrix in (i) is of Class I.
However,  this sufficient condition is not
 necessary,  i.e. there exist Case I-operators for which
 the series above is convergent.
\medskip

\noindent
{\bf{4.4  Weyl's example.}}
In most applications one is  given a separable  complex Hilbert space
$\mathcal H$ and a densely defined symmetric operator $A$
where a denumerable   orthonormal basis in $\mathcal H$ which
represents $A$ by an inifinite  matrix 
is not given in advance.
Here one often needs  extra work in order to decide if
$A$ is a Case I operator or not.
Of special interest are densely defined operators
given by symmetric PDE-operators acting on 
Hibert spaces $L^2(\Omega)$ where
$\Omega$ is an open set in some euclidian space
${\bf{R}}^n$ with $n\geq 1$.
Already the case $n=1$ leads to involved
situations which were  treated
by Weyl in an article from 1908
while he studied second  order differential operators acting
on the Hilbert space $\mathcal H$ of square integrable functions
on the non-negative real line $[0,+\infty)$.
If  $q(x)$ is a real-valued continuous function on
$[0,+\infty)$ there exists the symmetric and densely defined operator
\[
P=\frac{d^2}{dx^2}+ q(x)
\]
By Carleman's criterion in (4.3)
$P$  
yields a self-adjoint  operator if and only if
there
does not exist any non-zero  $L^2$-function $\phi(x)$ such that
\[
\phi''(x)+q(x)\cdot \phi(x)=i\cdot \phi(x)\tag{i}
\]
Weyl gave exampes of $q$-functions for which (i)
has non-trivial solutions which means that
$P$ fails to be a Case I-operator. We discuss this further in ¤ xx.


\bigskip


\centerline{\bf{5. Neumann's resolvent operators}}.
\medskip


\noindent
The reader should at an early stage become familiar with the construction of
spectra of  densely defined unbounded operators, and 
series expansions of their 
resolvents outside the spectrum.
The
construction and properties of Neumann's resolvent operators
which can be defined for every densely defined operator on a
Banach space  is presented in ¤ 0.0.
The power of the Neumann  calculus  is 
illustrated in
¤ xx where we construct fundamental  solutions to elliptic
second order differential operators in a canonical way, starting
from Newton's explicit solutions 
for
PDE-operators with constant coefficients which already appear
in 
his famous text-books from 1666.
Another example where 
Neumann's resolvent operators occur appears  in the study of  
strongly continuous semi-groups
of bounded operators on a Banach space.
In ¤ xx we prove a  result due to Hille, Phillips and Yosida  which
gives a criterion
for a closed and densely  defined linear operator $T$
on a Banach space to be  the infinitesmal generator of a strongly 
continuous semi-group $\{S(t)\}$.
The Hille-Phillips-Yosida theorem
asserts that
the necessary and sufficient
condition for $T$ to be an infinitesmal generator 
is that the spectrum $\sigma(T)$ is contained in a half-plane
$\mathfrak{Re}(\lambda)\leq a$ for some real number $a$, and there
exists a constant $K$ and some positive real number $a^*>a$
such that
the operator norms of the resolvents $R_T(\lambda)$
for real values of $\lambda$  satisfy
\[
||R_T(\lambda)||\leq \frac{K}{\lambda}\quad\colon\,\lambda\geq a^*
\] 
where the left hand side means that we take  operator norms of Neumann's resolvents.






\bigskip



\centerline {\bf{6. Geometry of normed vector spaces.}}
\bigskip

\noindent
This topic is treated rather scarcely. 
For example, we shall not discuss in detail
more advanced facts about 
extreme points of a convex sets and
barycentric representations which
includes the notion of the Choquet boundary.
But we  expose  some
results which occur rather frequently  in applications. 
The notion of convex subsets in a  vector space
$X$  over
the real field is fundamental.
A convex set $K$ which contains the origin is absorbing if
every sufficiently dilated vector belongs to $K$. It means that
for every $x\in X$ there exists some
$a>0$ such that $x$ belongs to
$aK=\{a\xi\,\colon \xi\in K\}$.
When it holds the support function
$\mathfrak{k}_K$ is defined for every $x\in X$ by
\[
\mathfrak{k}_K(x)= \inf_{a>0}\, x\in aK\tag{i}
\]
The tangent functional of $K$
assigns  a number
for each pair of vectors $x,y$ in $X$ by:
\[
\mathfrak{T}_K(x,y)=\lim_{a\to 0^+}\,\frac{1}{a}(
\mathfrak{k}_K(x+ay)-\mathfrak{k}_K(x)\tag{ii}
\]
The proof that (ii) exists  is easy. See ¤ xx for details.
Above no topology has been  introduced, i.e. 
one deals with pure geometry related to the convex set $K$.
When $X$ is a normed vector space
further notions are introduced.
The support function
of a convex set $K$ is strongly differentiable at a point $x\in X$ if
\[
\lim_{||y||\to 0}\, \frac{1}{||y||}\bigl ( \mathfrak{k}(x+y)-
\mathfrak{k}(x)-\mathfrak{T}_K(x,y)\bigr )=0\tag{iii}
\]
where $||y||$ denotes  norms 
during the passage to the limit.
This definition, as well as several  notions of differentiable with respect to
other topologies than that defined by the norm, were
investigated in a series of articles by Smulian around 1938.
In ¤ xx we prove one of his results which gives
criteria for stong differentiability.
Let  $X$ be a normed vector space
and $B$ 
the closed unit ball, i.e. vectors of norm
$\leq 1$. Then  the following hold
where $X^*$ is the dual of $X$ and  $B^*$ its  unit ball.



\bigskip

\noindent
{\bf{6.1 Smulian's criterion.}}
\emph{A necessary and sufficient condition that
(iii) holds with $K=B$
for a non-zero vector $x$, is that
there exists a unique $x^*\in X^*$ with norm one 
such that
$x^*(x)=||x||$ with the additional property
that  whenever $\{x^*_n\}$ is a sequence 
in $B^*$ such that $x^*_n(x)\to 1$, it follows that
$||x^*_n-x^*||\to 0$.}
\medskip

\noindent
{\bf{6.2 Further results.}}
In ¤ xx we  prove a result due to Mazur which asserts that
when $X=L^p(\mu)$ for some $1<p<\infty$ with respect to a measure
space, then
strong differentiability with respect to the norm hold for
all
$x\in X$.
In ¤¤ we 
prove a  theorem by 
Hšrmander in ¤ xx which describes support functions on convex
sets
in locally convex topological vector spaces, and
a non-linear
functional appear in a theorem due to
Beurling and Lorch
in ¤ xx.
\medskip


\centerline {\bf{7. Fixed point theorems.}}
\medskip

\noindent
A compact topological space $S$ has the fixed point property
if every continuous map $T\colon S\to S$
has at least one fixed point.
An example is the closed unit ball in ${\bf{R}}^n$ whose  fixed-point
property is an immediate  consequenc of Stokes Theorem. See ¤ xxx for details.
More generally, consider
a locally convex vector space $X$.
In ¤ xx we explain the construction of its dual space $X^*$ whose vectors
are continuous linear functionals on $X$.
Now one equips $X$  with the weak
topology whose open sets are generated
by pairs
$x^*\in X^*$ and positive numbers
$\delta)$ of the form:
\[
B_\delta(x^*)= \{ x\in X\,\colon\, |x^*(x)|\leq \delta\}
\]
Denote by $\mathcal K(X)$   the family of
convex subsets  of $X$ which are
compact
with respect to
the $X^*$-topology. In ¤ xx we prove the following two results.

\medskip

\noindent
{\bf{7.1 The Schauder-Tychonoff fixed point theorem.}}\emph{
Each $K$ in $\mathcal K(X)$ has the fixed point property.}

\medskip

\noindent
The merit of this result is of course that one allows
non-linear maps. The next
result is  due to Kakutani and  goes as follows:
By a group of linear transformations
$\bf{G}$ on $X$ we mean a family of bijective linear maps
$g\colon X\to X$ such that composed maps $g_2\circ g_1$
again belong to the group as well as  the inverse of every $g$.
\medskip

\noindent
{\bf{7.2 Kakutani's theorem.}} \emph{Let $K\in\mathcal K(X)$ be 
$\bf {G}$-invariant,  i.e. $g(K)\subset K$ hold for every
$g\in{\bf {G}}$. 
Assume in addition that the family of the restricted
${\bf{G}}$-maps to $K$ is equicontinuous.
Then there exists at least some
vector $k\in K$ such that $g(k)=k$ for every
$g\in{\bf{G}}$.}
\medskip

\noindent
{\bf{Remark.}}
The equicontinuous assumption means that to each pair
every $(x^*,\epsilon)$ with $x^*\in X^*$ and $\epsilon>0$ , there exists a finite
family $x^*_1,\ldots,x^*_M$ and some $\delta>0$
such
that the following hold: If
$p$ and $q$ is a pair of points in $K$ such that
$p-q$ belongs to $\cap\, B_\delta(x^*_\nu)$, then
\[
g(p)-g(q)\in B_\epsilon(x^*)
\] 
hold for all $g\in {\bf{G}}$.
\medskip

\noindent
{\bf{7.3 Haar measures.}}
Let $G$ be a compact topological group which
means that the  group is equipped with a Hausdorff topology where
the group operations are continuous, i.e the map from
$G\times G$ into $G$ which sends a pair of group elements $g,h$ to
the product $gh$ is continuous, and  the inverse map $g\mapsto g^{-1}$
is bi-continuous.
Now there exists  the  Banach apace
$C^0(G)$ of continuous real-valued functions on $G$.
Recall from basic measure theory that
the dual space
consists of Riesz measures. Denote by $P(G)$ the family of non-negative measures with
total mass one, i.e. probability measures onÊ$G$.
If $\phi\in C^0(G)$
and $g\in G$ we get the new continuous function
$S_g(\phi)$ defined by
\[ 
S_g(\phi)(h)=\phi(gh)\quad\colon h\in G
\]
Next, if  $\mu\in P(G)$ we get the new probability measure
$T_g(\mu)$ given by the linear functional
\[
\phi\mapsto \int_G\, S_g(\phi)\, d\mu
\]
In this way $G$ is identified with a group of
transformations on $P(G)$.
Next,  $P(G)$ is equipped with the weak-star topology
where  open neighborhoods of
a given $\mu\in P(G)$ consists of
finite intersections of sets
$\{\gamma\in P(G)\,\colon |\gamma(\phi)-\mu(\phi)|<\delta\}$
for pairs $\delta>0$ and $\phi\in C^0(G)$.
The  uniform continuity of every $\phi \in C^0(G)$
entails that
that the group action on
$P(G)$ is equi-continuous on $P(G)$
with respect to the weak-star topology.
As explained in ¤ xx, Kakutani's theorem also applies 
in this situation which yields
a fixed point. Hence  there is a probability measure
$\mu$ such that
\[
\int_G\, \phi(gh)\, d\mu(h)=\int_G\,\phi(h)\, d\mu(h)\tag{*}
\] 
hold for every pair $g\in G$ and
$\phi \in C^0(G)$.
In ¤ xx we show
that $\mu$ is uniquely determined by (*), i.e.
only one probability measure enjoys the invariance above.
Moreover,  starting with the operators
\[ 
S^*_g(\phi)(h)=\phi(hg)\quad\colon h\in G
\]
one finds a probability measure $\mu^*$ such that
\[
\int_G\,\phi(hg)\, d\mu(h)=\int_G\,\phi(h)\, d\mu(h)\tag{**}
\] 
hold for every pair $g\in G$ and
$\phi \in C^0(G)$.
In ¤ xx we prove that $\mu=\mu^*$ which 
means that the unique Haar measure
is both left and right invariant.


\bigskip



\centerline {\bf{8. The approximation property.}}
\medskip


\noindent
Normed vector  spaces can be quite   involved.
This is best  illustrated
by  Enflo's example of
a separable Banach space on  which there exists a compact operator
which cannot be approximated by operators with finite dimensional range.
Enflo's  ingenious  construction was presented  in a seminar at Stockholm University in 
1972 
which after led to an intense study where one seeks to
determine when a given separable Banach space $X$  has
the approximation property in the sense that
every compact operator on $X$ can be approximated in the strong operator norm
by operators with finite dimensional range.
Fortunately most Banach spaces  encountered in applications enjoy this
property.
For example, if $S$ is a compact metric space which
contains a denumerable  dense subset, then
the Arzela-Ascoli theorem for equi-continuous functions
entails that
the Banach space $C^0(S)$ has the approximation property.
See ¤ xxx for the proof.
Let us also remark that if the approximation property hold for
the family of compact operators in a  separable Banach space
then there exists a Schauder basis. See
¤ xx for further comments.







 \newpage





\centerline {\bf{Preliminary  examples.}}
\medskip

\noindent
While entering the study of a general theory it is
useful to
consider special situations. 
So we  describe some results which from  a historic  perspective
inspired
later studies of operators on Hilbert spaces.
We begin with an example which in a histriic perspective
inspired the 
theory about linear operstors.
\bigskip


\bigskip




\centerline {\bf{Neumann's boundary value problem.}}
\medskip

\noindent
Consider a domain
$\Omega$ in ${\bf{R}}^2$ whose boundary is the union of a finite family
of closed Jordan curves of class $C^1$.
Given a pair of real-valued continuous functions $a$ and $f$ on
$\partial\Omega$ one seeks a harmonic function $U$ in
$\Omega$ which extends continuously to the boundary. In addition
the inner normal derivatives along the boundary  
exist where they satisfy the equation
\[
\frac{\partial U}{\partial n_*}(p)=a(p)\cdot U(p)+ f(p)\quad\colon
p\in \partial\Omega\tag{1}
\]
Above  the left hand side refers to inner normal derivatives.
Here the situation is more involved since neither uniqueness nor
existence are automatic.
However, if $a$ is a positive function then it turns out that
the equation has a unique solution $U$.
To prove this one regards a  positive number
$M$ which  exceeds the diameter
of $\partial\Omega$, i.e. $M>|p-q|$ for every pair of points
on the boundary.
Now there exist the linear operator on
$C^0(\partial \Omega)$ defined by
\[
\mathcal L(u)(p)=\int_{\partial\Omega}\,
\log\, \frac{M}{|p-q|}\cdot u(q)\, ds(q)\tag{2}
\] 
where $ds$ is the arc-length measure on the boundary.
Since the function $(x,y)\mapsto \log\, \sqrt {x^2+y^2}$
is harmonic outside the origin, it follows
that
(2) defines a harmonic function $U$
in
$\Omega$ when $p$ varies in this domain.
To solve (1)  is therefore equivalent to
find $u\in C^0(\partial\Omega)$ such that
\[
\frac{\partial \mathcal L(u)}{\partial n_*} (p)=a(p)\cdot \mathcal L(u)(p)+ f(p)\quad\colon
p\in \partial\Omega\tag{3}
\]
This is  the gateway to settle Neumann's boundary value problem.
The crucial point that the composed operator
\[
u\mapsto \frac{\partial}{\partial n_*}\circ \mathcal L(u)
\]
acting on $C^0(\partial\Omega)$ is expressed by
the linear operator
\[
\mathcal S(u)(p)=-\pi\cdot u(p)+
\int_{\partial\Omega}\,
\frac{\langle n_*(p),q-p\rangle}{|q-p|^2}\cdot u(q)\, ds(q)\tag{iv}
\]
The verifiction of (iv) relies on calculus and 
given in ¤ xx.
Next, the  assumption that $\partial\Omega$ is of class $C^1$ gives
a constant $C$ such that
\[
\max_{p,q}\,\bigl|\,\frac{\langle n_*(p),q-p\rangle}{|q-p|^2}\bigr|\leq C\tag{v}
\]
with the maximum taken over all pairs $p,q$ on the boundary,
We shall learn that this entails that
the linear operator on $C^0(\partial\Omega)$ defined by
\[
\mathcal K(u)(p)=\int_{\partial\Omega}\,
\frac{\langle n_*(p),q-p\rangle}{|q-p|^2}\cdot u(q)\, ds(q)
\] 
is compact.
Neumann's operator  is defined by 
\[
\mathcal N(u)(p)=a(p)\cdot \mathcal L(u)(p)-
\mathcal K(u)(p)\tag{vi}
\]
As  explained in ¤ xx, Lebesgue theory and the Arzela-Ascoli theorem
entail that the  operator
\[
u\mapsto a(p)\cdot \mathcal L(u)(p)
\]
also  is compact. Hence
Neumann's operator is 
compact  and we
shall learn that it has a discrete spectrum.  Next, for each $M$ chosen as above
we set
\[
\rho(M)=\min_{p,q}\, a(p)\cdot \log\, \frac{M}{|p-q|}-C
\]
Let $E$ be the identity operator.
If $\rho(M)>0$ one easily verifies that
the  operator 
\[
u\mapsto s\cdot u+\mathcal N(u)
\]
is invertible for all real numbers $s$ such that
\[
s+\rho(M)>0
\]
Next,  notice that (1) can be written as
\[
\pi\cdot u+\mathcal N(u)=-f
\]
When $\rho(M)>-\pi$ it follows from the above
that there exists the bounded inverse operator
\[
(\pi\cdot E+\mathcal N)^{-1}
\]
and (1) is solved by
\[
u=-(\pi\cdot E+\mathcal N)^{-1}(f)
\]

\medskip

\noindent
{\bf{The case when the boundary is not smooth.}}
Let $\Omega$ be a bounded domain in
${\bf{R}}^2$ such that 
$\partial\Omega$ is sufficiently smooth in order
Stokes formula is valid as explained in
Chapter 2 from my notes in analytic function theory.
Let $\text{reg}(\partial\Omega)$
denote the regular part of the boundary.
Given a pair $a,f$ in $C^0(\partial\Omega$ one now asks for
a harmonic function $U$ in $\Omega$
which together with its inner normal derivatives extend
to be continuous on
$\text{reg}(\partial\Omega)$ and
\[
\frac{\partial U}{\partial n_*}(p)=a(p)\cdot U(p)+ f(p)\quad\colon
p\in \text{reg}(\partial\Omega)\tag{1}
\]
Again one tries to solve this via suitable linear operators.
Since our assumption
in particular means that the 2-dimensional area of
 $\text{reg}(\partial\Omega)$ is finite, it follows
$\mathcal L$-operator is still
defined, where the integral in (1) is taken over
the regular part of
$\partial\Omega$.
Next, 
let us impose the condition that there exists a constant $C$ such that
\[
\max_{p\in \text{reg}(\partial\Omega)}
\int_{\text{reg}(\partial\Omega)}\,
\bigl|\, \frac{\langle n_*(p),p-q\rangle}{|p-q|^2}\,\bigr|\, ds(q)\leq C\tag{2}
\]
Then  
each $u\in C^0(\partial\Omega)$
yields a function on
the regular part of
the boundary defined by  
\[
\mathcal K(u)(p)= 
\int_{\text{reg}(\partial\Omega)}\,
\frac{\langle n_*(p),p-q\rangle}{|p-q|^2}\cdot u(q)\, ds(q)\tag{3}
\]
where
$\mathcal K$
becomes  a  linear operator
from the Banach space $C^0(\partial\Omega)$ into the
Banach space of bounded and continuous functions on
$\text{reg}(\partial\Omega)$ whose operator norm is majorized by $C$.
Hence there also exists the Neumann operator
$\mathcal N$
given as the sum of the 
$\mathcal L$-operator minus the bounded operator
$\mathcal K$.
The
question rises if we can produce bounded inverse operators 
similar to   the smooth
case 
for sufficiently large $M$.
To achieve this we
suppose in addition to (2) that
there exists a constant $C^*$ such that
\[
\max_{p\in \text{reg}(\partial\Omega)}
\int_{\text{reg}(\partial\Omega)}\,
\, \frac{M}{\log |p-q|}\, ds(q)\leq C^*\tag{4}
\]
Basic measure theory entails that
$\mathcal L$ now becomes a compact operator whose spectrum depends on $M$.
The whole discussion has shown that
the essential point is to analyze the spectrum of
Neumann's operator
defined as in (vi) frome the smooth case while
$p$ stays in $\text{reg}(\partial\Omega)$.
We shall treat this in ¤ xx and settle Neumann's boundary
value problem for domains where (2) and (4) hold.









\medskip

\noindent
{\bf{A non-linear   boundary value problem.}}
In his lecture \emph{L'avenir des mathŽmatiques}
at the international congress at Rome in 1908,
PoincarŽ
pointed out the significance
of regarding infinite systems of linear equations which
can be used to treat non-linear equations.
His proposed strategy was used by Carleman
in an article from 1921 to establish the result below.
Let $\Omega$ be as above and fix a point $q_*\in\Omega$.
Consider
functions of the form
\[
u(p)= \frac{1}{4\pi}\cdot \frac{1}{|p-q_*|}+H(p)\tag{i}
\]
where $H$ is harmonic in $\Omega$.
Let $F(s,p)$ be a real-valued continuous function defined on
$\{s\geq 0\}\times \partial\Omega$ such  that
$s\mapsto F(s,p)$ is strictly decreasing on $[0,+\infty)$ with
$F(0,p)=0$ for each $p\in\partial\Omega$.
\medskip

\noindent
{\bf{Theorem.}}\emph{There exists a unique function
$u$ from (i) such that
its inner normal derivative along
$\partial\Omega$ satisfies the equation}
\[
\frac{\partial u}{\partial n}(p)=F(u(p),p)
\]
We shall prove this result in ¤ xx where
an essential ingredient is the systematic use of Neumann series of linear operators.
\newpage


\noindent
\centerline{\bf{a. Toeplitz' operators.}}
\medskip

\noindent
Let $\{a_p\}$ be a Hermitian sequence of complex numbers 
indexed over all integers where
\[
\sum_{-\infty }^\infty\, |a_p|^2<\infty\tag{*}
\]
The hermitian condition means that
\[ 
a_{-p}= \overline{a}_p\quad\colon p=1,2,\ldots
\]
In an article  [Gšttingen Nachrichten: 1907], Toeplitz 
studied  quadratic forms of  infinitely many   variables:
\[
J(x)= \sum_{p=1}^\infty\sum_{q=1}^\infty\,a_{p-q}x_qx_p
\]
which arise from
sequences satisfying (*).
If $\lambda$ is a complex number
with $\mathfrak{Im}(\lambda)\neq 0$
and $\{c_p\}$ is a vector such that
$\sum_{-\infty }^\infty\, |c_p|^2<\infty$, then Toeplitz proved
that there
exists
a unique vector  $\{x_p\}$ 
which again satisfies (*) and
\[
x_p=\lambda\cdot 
\sum_{q=-\infty }^\infty\, a_{p-q}x_q=c_p\quad\colon\, p\in {\bf{Z}}\tag{1}
\]
In ¤ xx we prove an  integral version which gives 
Toeplitz'  result as a special case and includes   an inversion formula which
represents the solution vector $\{x_p\}$ for each
given $c$-vector.
It goes without saying that the discoveries above  by Toeplitz inspired  later
studies of  linear operators.
An example occurs in  the moment problem of
Stieltjes and its extended version by Hamburger.
Here the starting point is the close interplay between
expansions in continued fractions of a sequence of real numbers
$\{c_1,c_2,\ldots\}$ with the property that
the quadratic form
\[ 
\mathcal C(x)= \sum\sum\, c_{p+q}x_px_q
\]
is positive, i.e. the value is $>0$ for every $x$-vector where
only finitely  many $x_p\neq 0$.
The article \emph{Zur Einordnung der Kettenbruchtheorie in die
Theorie der quadratischen Formen von
unendlichvielen verŠnderlichen} [Crelle J. fŸr Math. 1914]
by Hellinger and Toeplitz
led to a new perspective
of Stieltjes' original solutions to
the moment problem. 
Conclusive  results which cover both determined and undetermined
moment problems were attained by Carleman in the article
\emph {Sur le problme des moments}
[ C.R. Acad. Sci. Paris 1922]
which we expose in ¤ xx. 
A first acount about this is given in the next subsection.



\medskip










\noindent
\centerline {\bf{b. The moment problem.}}
\medskip

\noindent
We shall briefly resume some results  and refer to ¤ xx for further details.
Consider a pair of sequences of real numbers
$\{a_p\}$Êand $\{b_p\}$,  indexed by  integers $p\geq 1$.
We assume that every $b_p>0$ while no conditions are imposed 
on the $a$-sequence. It can for example occur that
$a_p=0$ for every $p$. To each $n\geq 2$ we get the symmetric
$n\times n$-matrix

\[
A_n=\begin{pmatrix}
a\uuu 1&-b_1&0&\ldots &0& 0\\
-b_1&a_2&-b_2&\ldots &0& 0\\
0&-b_2&a_3&\ldots&\ldots\\
\ldots&\ldots&\ldots&\ldots&\ldots\\
0&0&\ldots &a\uuu{n-1}& -b_{n-1}\\
0&0&\ldots &-b_{n-1}& a_n\\
\end{pmatrix}
\]
Let  $\mu$ be a complex number with
$\mathfrak{Im}(\mu)>0$. Then
there exists a unique complex $n$-vector
$\Phi(\mu)$
which solves the equation
\[
A_n(\Phi(\mu))= \mu\cdot \Phi(\mu)+e_1\tag{i} 
\]
where $e_1=(1,0,\ldots 0)$.
Indeed, we see that (i) holds if and only if
\[
a_1\phi_1(\mu)-b_1\phi_2(\mu)=\mu\phi_1(\mu)+1
\]
\[
-b_{k-1}\phi_{k-1}(\mu)+a_k\phi_k(\mu)-b_k\phi_{k+1}(\mu)=0
\quad\colon 2\leq k\leq n-1
\]
\[
b_{n-1}\phi_{n-1}(\mu)= a_n\phi_n(\mu)
\]
From this it is clear that
$\phi_1(\mu)$ determines the remaining
components and treating $\mu$ as an indeterminate. In ¤ xx we show that
\[ 
\phi_1(\mu)=\frac{P_n(\mu)}{Q_n(\mu)}
\]
where $Q_n(\mu)$ is a polynomial  of degree $n$ while $P_{n-1}$ 
has degree $(n-1)$
Moreover, since the solution exists for every
non-real $\mu$ it follows that the zeros of
$Q_n$ are real and since
$\phi_1(\mu)\neq 0$ for non-real $\mu$, the zeros of $P_{n-1}$ are also real.
Finally one shows that
the polynomials satisfy the recursive equations
\[
\frac{P_{n+1}(\mu)}{Q_{n+1}(\mu)}=
\frac{P_n(\mu)}{Q_n(\mu)}+
\frac{b_1^2\cdots b_n^2}{Q_n(\mu)\cdot Q_{n+1}(\mu)}
\]
Since the degree of the polynomial
$Q_n(\mu)\cdot Q_{n+1}(\mu)$ is $\geq 2n+1$ for every $n$, it
follows that when
one takes the Laurent series expansions of the rational $g$-functions at
$\mu=+\infty$, then the
coefficients in negative $\mu$-powers up to degree $2n$ are the same
for
$g_n(\mu)$ and $g_{n+1}(\mu)$.
This gives
a unique asymptotic series
\[
-\sum_{k=1}^\infty\, \frac{c_k}{\mu^{k+1}}\tag{1}
\]
whose series expansion up to order $2n$ is matching that of $g_n(\mu)$
for every positive integer $n$.
As explained in ¤ xx, the series (1) corresponds 
to the expansion in continued fractions 
attached to the two 
sequences $\{a_k\}$ and $\{b_k\}$. 
In ¤¤ we also show that there exists a probability measure $\rho_n$ on the real $t$-line such that
\[
\frac{P_n(\mu)}{Q_n(\mu)}=\int_{-\infty}^\infty\, \frac{d\rho_n(t)}{t-\mu}\tag{2}
\]
\medskip

\noindent
{\bf{b.1 Passage to a limit.}}
From (2) it follows that the functions $\{g_n(\mu)=\frac{P_n(\mu)}{Q_n(\mu)}\}$
are analytic in
the upper half-plane and satisfy
\[
|g_n(\mu)|\leq \frac{1}{\mathfrak{Im}(\mu)}
\]
Montel's theorem entails that
$\{g_n\}$ is a normal family of analytic functions in
the upper half-plane.
Denote by $\mathcal G$ the familly of all analytic functions
$g(\mu) $ in the upper half-plane which
are limits from a subsequence 
$g_{n_1},g_{n_2},\ldots$, i.e.
\[
\lim_{k\to\infty}\,  g_{n_k}(\mu)= g(\mu)
\]
where the convergence holds uniformly over compact
subsets of the upper half-plane.
By weak-star compactenss of Riesz measures and the compatibility
between the Laurent series of the $g$-functions, it follows that
for each  $g\in\mathcal G$, there exists
a  probability measure $\rho$ such that
\[
g(\mu)=\int_{-\infty}^\infty\, \frac{d\rho(t)}{t-\mu}
\]
and the moments of the $\rho$-measure satisfy
\[
\int\, t^\nu\cdot d\rho(t)= c_\nu\quad\colon \nu=1,2,\ldots\tag{3}
\]
Above 
the $c$-sequence is quite special since
Cauchy-Schwarz inequality entails 
that the quadratic form
in an infinite number of variables $x_1,x_2,\ldots$ defined by
\[
 J(x)= \sum\sum\, c_{p+q}x_px_q\tag{4}
\]
is positive definite. One 
refers to $\{c_n\}$ as a Hankel sequence.
This termionology stems from the fact that
$J$  is positive definite if and only if the recursive Hankel determinants of
the $c$-sequence are all positive. See the section about matrices for details.


\medskip

\noindent
{\bf{b.2 The determined case.}}
If
$\mathcal G$ is reduced to a single function one says that the moment problem is
determined which by the above means that there exists a unique probability measure
$\rho$ for which (3) holds.
Necessary and sufficient conditions 
on the sequence $\{c_n\}$ in order that the moment problem is determined
is not known. It appears as a very  hard (and perhaps even unolvable)
problem However, the
following sufficiency  result by Carleman holds:
\medskip

\noindent
{\bf{B.2.1 Theorem.}}
\emph{A Hankel sequence
 $\{c_n\}$ yields a derermined moment problem if}
 \[
 \int_1^\infty\, \log\, \bigl[\, \sum_{n=0}^\infty\, \frac{r^{2n}}{C_{2n}^2}\,\bigr]
 \, \frac{dr}{r^2}=+\infty
 \]
 \medskip
 
 
 \noindent
 The proof of this result goes beyond the scope of the present chapter since
 it is based upon quite involved analysis   where
 estimates for harmonic measures and constructions of suitable subharmonc
 functions are needed.
In the case of  a non-determined moment problem
 the following is proved in ¤ xx:
For each complex number $\mu$ in the open upper half-plane we set
\[
\mathcal R(\mu)=\{g(\mu)\,\colon\,  g\in\mathcal G\}
\]
\medskip

\noindent
{\bf{B.2.2 Theorem.}} \emph{In a non-determined moment problem
each set $\mathcal R(\mu)$ is a compact disc with positive radius placed in
the upper half-plane.}
\noindent

\bigskip


\centerline {\bf{c. Picard's operator.}}
\bigskip

\noindent
Consider the Hilbert space $L^2({\bf{R}})$ whose vectors are square integrable complex
valued functions on the real line.
For each $f\in L^2{\bf{R}})$ we get a function 
\[ 
x\mapsto P_f(x)= \int_0^\infty\, e^{-[x-y|}\cdot f(y)\, dy
\]
The Cauchy-Schwarz inequality shows that
when $x$ is fixed, then the integral in the right hand side
is absolutely convergent which gives   a well-defined function
$P_f(x)$ on the real $x$-line.
In ¤ xx 
we use
Fourier's inversion formula to calculate
the spectral function
$\theta(x,y;\lambda)$ of Picard's operator.
 More precisely,  it  is zero  on the interval  $(-\infty,1/2]$, and
when $\lambda>1/2$ one has
\[
\theta(x,y;\lambda)=\int_{\frac{1}{2}}\,
\frac{\sin\,(\sqrt{2s-1}\cdot (x-y))}{x-y}\, ds
\]
From this explicit equation for the spectral function
we shall demonstrate in ¤ xx how classic formulas in
Fourier analysis can be interpretated via Carleman 's 
general results  about
their spectral functions.
In our present situation  one
recaptures
the Fourier-Parseval  equation 
\[
\int_{-\infty}^\infty\,  f(x)g(x)\,dx=
\frac{1}{\pi}\cdot
\int_{-\infty}^\infty\,\frac{d}{d\lambda}\bigl(
\iint 
\frac{\sin\,(\sqrt{2\lambda -1}\cdot (x-y))} {x-y}\cdot f(x)g(y)\, dxdy\bigr)\,d\lambda\tag{*}
\]
for each  pair of $L^2$-functions $f$ and $g$.
More generally one considers operators on $L^2({\bf{R}})$ defined by
\[
\mathcal H(f)(x)= \int_0^\infty\, H_1(|x-y|)\cdot f(y)\,dy
 +\int_0^\infty\, H_2(x+y)\cdot f(y)\,dy
\]
where the $H$-functions satisfy
\[
\int_0^\infty\, H_\nu(s)^2\,ds<\infty
\]
Again one computes the spectral function of this self-adjoint operator
which is used to obtain equations  similar to (*)





\newpage



\centerline {\bf{d. Inequalities via spectra.}}
\bigskip


\noindent
An inequality  which goes back to early work by Hilbert and Schur
 asserts that for every sequence $x_1,x_2,\ldots$ of real numbers
 one has the inequality
 \[
\bigl|\,  \sum_{p,q}\,\frac{x_px_q}{p+q}\bigr |\leq \pi\cdot \sum_{p=1}^\infty\, x_p^2
\]
where the double sum is extended over all pairs of non-negative integers.
The integral version asserts that if $f(x)$ is a square-integrable function on
$\{x\geq 0\}$
then
\[ 
\iint\,\frac{1}{x+y}\, f(x)f(y)\, dxdy\leq\pi\cdot
\int_0^\infty\, f(x)^2\, dx\tag{d.1}
\]
where the double integral is taken over $\{x,y\geq 0\}$.
To prove this one considers  the linear operator
$T$ defined by
\[
T(f)(x)=\int_0^\infty\, \frac{1}{x+y}\cdot f(y)\, dy\tag{i}
\]
It is clear that (d.1) follows if 
the linear operator 
$T$ on the Hilbert space
$L^2({\bf{R}}^+$ has norm $\leq \pi$.
To prove this we shall use variable substitutions.
For each
square integrable function $g$ on the non-negative $y$-line we set
Set $g_*(s)=g(e^s)$, and notice that
\[
\int_{-\infty}^\infty\, g_*(s)^2\cdot e^s\, ds=
\int_0^\infty\, g(y)^2\, dy\tag{ii}
\]
Using a similar transformation $t\mapsto e^t=x$ we  define the linear operator
$T_*$ on
$L^2({\bf{R}})$ by
\[
T_*(f_*)(t)=\int_{-\infty}^\infty\, \frac{e^{\frac{t}{2}+\frac{s}{2}}
}{e^t+e^s}\cdot f_*(s)\, ds\tag{iii}
\]
From (ii) the reader can check that the operator norms of
$T_*$ and $T$ are the same.
Define the function
\[
K(u)= \frac{1}{e^{\frac{u}{2}}+e^{-\frac{u}{2}}}\tag{iv}
\]
Then it is clear that 
\[
T_*(f_*)(t)=\int_{-\infty}^\infty\,K(t-s)\cdot f_*(s)\,ds\tag{v}
\]
Hence $T_*$ is defined via a convolution and Fourier's inversion formula entails that
\[
T_*(f_*)(t)=\frac{1}{2\pi}\cdot \int\, e^{-it\xi}
\cdot \widehat {K}(\xi)\cdot
\widehat {f}(\xi)\,d\xi
\]
Next, the Fourier transform of
$K$ is given by
\[
\int_{-\infty}^\infty\, e^{-iu\xi}\cdot \frac{1}{e^{\frac{u}{2}-\frac{u}{2}}}\, du
\]
\medskip

\noindent
{\bf{Exercise.}}
Use residue calculus to show that the Fourier transform
\[
\widehat {K}(\xi)=\int_{-\infty}^\infty\, e^{-iu\xi}\cdot \frac{1}
{e^{\frac{u}{2}-\frac{u}{2}}}\, du=\frac{2\pi}
{e^\xi+e^{-\xi}}
\]
\medskip

\noindent
Finally, Parseval's equality and the observation that
\[
\min_\xi\,  {e^\xi+e^{-\xi}}=2
\]
imply that the operator norm of $T_*$ is at most $\pi$.
Moreover, one has equality since
we
can take
$L^2$-function $f(t)$ where the Fourier transform is
the characteristic function of a small intervalÊ$[-\delta,\delta]$ on the
real $\xi$-line in which case
\[
||T_*(f)||^2\geq \pi^2\cdot \frac{4}{(e^\delta+e^{-\delta})^2}\cdot ||f||^2
\]
Since 
$\frac{4}{(e^\delta+e^{-\delta})^2}\simeq 1$ when
$\delta$ is small we conclude that
the operator norm of $T$ is $\pi$.
Hence 
(d.1) is sharp and  notice that equality cannot be attained for
a single $f$-function, i.e. one must pass to the infimum  while the operator norm
of $T$ is determined.







\bigskip


\centerline {\bf{e. Infinite systems of linear equations.}}
\bigskip

\noindent
In functional analysis one usually imposes constraints 
on infinite vectors. 
One may also study linear systems of equations under the sole condition  that
solutions are expressed by
convergent additive series.
Thus, let $\mathcal C=\{c_{pq}\}$ be an infinite matrix
where
the doubly-indexed elements are compex numbers.
Given a complex sequence $\{a_p\}$ one studies the system:
\[ 
\sum_{q=1}^\infty\, c_{pq}\cdot x_q=a_p\quad\colon p=1,2,\ldots
\]
The infinite $x$-vector is a solution when the additive 
series in the left hand side converges 
for each fixed $p$ with a sum equal toÊ$a_p$.
A necessary and sufficient condition for the existence of at least
one $x$-solution is described in Carleman's  
lecture from  the IMU-congress  at ZŸrich in 1932.
As expected the criterion is  involved and  relies upon
solutions with bounds to a recursively  constructed
family of variational problems. 
A special case occurs when
$\{c_{pq}\} $ are given  via evaluations at pairs of integers of
rational funtions of two variables. Here follows an example.
\medskip

\noindent
{\bf{The Dagerholm series.}}
Consider the homogeneous system
\[
\sum_{q\neq p}\, \frac{x_q}{p-q}=0\quad\colon p=1,2,\ldots
\]
It means that we seek vectors $x=(x_1,x_2,\ldots$
such that the left hand side above converges for each fixed positive integer
$p$
and the series sum is zero. Without loss of generality we only ask for 
real $x$-vectors.
It turns out that the system has a unique 
non-trivial solution up to a multiple with a constant.
This result is due to Dagerholm and a proof is  exposed in a section from
\emph{Special Topics} from  my notes devoted to analytic function theory.
It goes without saying that
the proof is considerably more demanding compared to
situations in normed vector spaces where existence and uniqueness properties
are controlled via imposed norms.




\bigskip


\centerline
{\bf{f. Maxwell's equations in electrodynamics}}.
\medskip

\noindent
Consider the following triple of
$3\times 3$-matrices
\medskip

\[
A_1=\begin{pmatrix} 0&0&0\\ 0&0&-i\\ 0&i&0 \end{pmatrix}
\quad\colon\, 
A_2=\begin{pmatrix} 0&0&i\\ 0&0&0\\ -i&0&0 \end{pmatrix}\quad\colon
A_3=\begin{pmatrix} 0&-i&0\\ i&0&0\\ 0&0&0 \end{pmatrix}
\]
One seeks a vector valued function 
$f= (f_1(x_1,x_2,x_3,t),f_2(x_1,x_2,x_3,t),(f_3(x_1,x_2,x_3,t)$
which satisfies  the differential system
\[
\frac{\partial}{\partial t}
\begin{pmatrix} f_1\\f_2\\f_3\end{pmatrix}=
\sum_{j=1}^{j=3}\, A_j\circ 
\frac{\partial }{\partial x_j}\begin{pmatrix} f_1\\f_2\\f_3\end{pmatrix}\tag{*}
\]
and the initial conditions $\{f_\nu(x,0)= g_\nu(x)\}$ where
$g_1,g_2,g_3$ are given real-valued $C^\infty$-functions in
${\bf{R}}^3$.
This turns out to be a well-posed
Cauchy problem, i.e. for every
triple of $g$-functions there exists a unique solution
$f$ to (*) with the boundary conditions as above.

\medskip

\noindent
A veritable propagande for operator theory
appears during the proof of this result which actuslly extends  
to symmetric hyperbolic systems. They   arise as follows.
Let $x=(x_1,\ldots,x_n)$ be  space variables 
for some  positive integer $n$.
Next, let
$m$ be another positive integer
and 
\[
(x,t)\mapsto A_\nu(x,t)\quad\colon 1\leq \nu\leq n
\]
is an $n$-tuple of maps from
${\bf{R}}^n\times\{t\geq 0\}$ into the space 
$m\times m$-matrices where
the
elements of these $A$-matrices are
complex-valued $C^\infty$-functions
defined on ${\bf{R}}^n\times\{t\geq 0\}$.
In addition we consider
another matrix-valued function
$B(x,t)$ whose $m^2$-many elements again are
$C^\infty$-functions.
Now one seeks vector-valued functions
$f=(f_1(x,t),\ldots,f_m(x,t)$ which satisfy the differential system
\[
\frac{\partial}{\partial t}
\begin{pmatrix} f_1\\...\\f_m\end{pmatrix}=
\sum_{j=1}^{j=n}\, A_j(x,t)\cdot 
\frac{\partial }{\partial x_j}\begin{pmatrix} f_1\\...\\f_m\end{pmatrix}+
B(x,t)\begin{pmatrix} f_1\\...\\f_m\end{pmatrix}\tag{**}
\]
and the boundary value conditions
\[
f_\nu(x,0)= g_\nu(x)\quad\colon 1\leq\nu\leq m
\]
where 
$\{g_\nu(x)\}$ is an $m$-tuple in $C^\infty({\bf{R}}^n)$.
\medskip



\noindent
{\bf{The symmetric case.}}
If
the $n\times n$-matrices 
$\{A_1(x,s),\ldots, A_m(x,t)\}$ are Hermitian for each
fixed pair $(x,t)$
one says that the system (**) is symmetric.
No
special condition is imposed on $B$, except that its elements  are
complex-valued $C^\infty$-functions.
Notice that  the $A$-matrices
in Maxwell's equations are Hermitian so (*) is an example of a symmetric system.
The existence and uniqueness of
solution to Maxwell's equations is a special case of
the result below  proved by Friedrichs in the article 
\emph{Symmetric hyperbolic differential systems} 
[Comm. pure.appl.math.
Vol 7. 1954].


\medskip

\noindent
{\bf{0.1 Theorem.}}
\emph {Assume that the system (**) is symmetric
and that
the matrix elements of $A_1,\ldots,A_n$ and of $B$ are
bounded functions in ${\bf{R}}^{n+1}$.
Then Cauchy's boundary value problem has a unique $C^\infty$solution
$f=(f_1,\ldots,f_m)$ for every $m$ tuple
$g=(g_1,\ldots,g_m)$ of $C^\infty$-functions in the $n$-dimensional $x$-space.}

\medskip


\noindent
{\bf{Remark.}}
The proof is given in ¤ xx. 
It  involves a number of steps where
unbounded operators on
suitable Hilbert spaces which emerge from Sobolev
spaces appear.
So the  proof relies heavily upon operator theory
and gives therefore
 a good motivation for learning material to be exposed later on.



\bigskip



\centerline {\bf{g. Positive definite quadratic forms}}
\bigskip


\noindent
Inequalities play a major role in functional analysis.
They are often established via geometric considerations. Let us  illustrate
this
by 
some remarkable results  presented by Beurling
during seminars at Uppsala university in 1935.
See  \emph{Collected work} [ vol. xx p. xx-xx].
The theorem   below 
can for example be used to establish  the 
existence of certain spectral measures which arise in
ergodic processes.
Let $f$ and $g$ be a pair of square integrable functions on
the real line.
For each real number $t$ we set
\[
\psi(t)=\int\uuu{\vvv \infty}^\infty\, 
[f(t+s)\vvv g(s)|^2\cdot ds
\]
\medskip

\noindent
{\bf{g.1 Theorem.}}
\emph{There exists a measure $\mu$ 
on the real line whose  total variation 
$\leq 2\sqrt{||f||_2\cdot ||g||_2}$
such that}
\[ 
\psi(t)=||f||\uuu2+||g||\uuu 2+\int\uuu{\vvv \infty}^\infty\,
e^{ix t}\cdot d\mu(x)
\]
\bigskip


\noindent
The proof of this theorem  relies upon
a study of certain bi-linear forms in euclidian spaces
which we describe in detail to illiustrate
the usefulness of geometric considerations  while
objects such as quadratic forms are studied.
Let $m\geq 2$ and denote $m$\vvv vectors in
${\bf{R}}^m$
with  capital letters, i.e. $X=(x\uuu 1,\ldots,x\uuu m)$.
Let $N\geq 2 $ be some positive integer 
and $X\uuu 1,\ldots,X\uuu N$
an $N$\vvv tuple of real $m$\vvv vectors.
To each pair $j\neq k$
we set
\[
b\uuu{ij}= ||X\uuu j||+X\uuu k||\vvv 
||X\uuu j\vvv X\uuu k||
\]
where $||\cdot ||$ is 
the usual euclidian length in ${\bf{R}}^m$ and consider
the 
quadratic form
\[ 
H(\xi\uuu 1,\ldots,\xi\uuu N)=
\sum\sum\, b\uuu{ij}\cdot \xi\uuu i\cdot \xi\uuu j
\]
\medskip

\noindent
{\bf{g.2. Theorem.}}
\emph{If the
$X$\vvv vectors are all different then
$H$ is positive definite.}
\medskip

\noindent
The proof relies upon an integral  formula which determines 
the length of a vector in ${\bf{R}}^m$.
\medskip

\noindent
{\bf{g.3. Lemma }}\emph{There exists a constant
$C\uuu m$
such that}
\[
||X||=C\uuu m\cdot  
\int\uuu{{\bf{R}}^m}\,
\frac{1\vvv \cos\,\langle X,Y\rangle }{||Y||^{m+1}}\cdot dY\tag{*}
\]
\emph{hold for every $m$\vvv vector $X$}.  
\medskip

\noindent
\emph{Proof.}
We use polar
coordinates. Denote by $dA$  the area measure on the unit sphere
$S^{m\vvv 1}$ and
$\omega=(\omega\uuu 1,\ldots,\omega\uuu m)$
are  points on the unit sphere
$S^{m\vvv 1}$.
Notice that the integrals 
\[
\int\uuu{S^{m\vvv 1}}\, 
(1\vvv \cos\,\langle X,\omega\rangle)\cdot dA
\]
only depend upon $||X||$. Hence it suffices to prove Lemma 2.xx  when
$X=(R,\ldots,0)$ where $R=||X||$.
It is clear that
\[
\int\uuu{{\bf{R}}^m}\,
\frac{1\vvv \cos\,\langle X,Y\rangle }{||Y||^{m+1}}\cdot dY=
\int\uuu 0^\infty\, \bigl[\,
\int\uuu{S^{m\vvv 2}}\, (1\vvv\cos Rr\omega\uuu 1)\cdot dA\uuu{m\vvv 1}
\,\bigr]\cdot \frac{dr}{r^2}\tag{i}
\] 
where $dA\uuu{m\vvv 1}$ is the area measure on $S^{m\vvv 2}$.
Set 
\[
B(R,\omega\uuu 1)=
\int\uuu 0^\infty\, (1\vvv\cos Rr\omega\uuu 1)\cdot \frac{dr}{r^2}
\]
for each   $\vvv 1<\omega\uuu 1<1$. The variable substitution $r\to s/R$
gives
\[
B(R,\omega\uuu 1)=
R\cdot 
\int\uuu 0^\infty\, \frac{1\vvv\cos s\omega\uuu 1}{s^2}\cdot ds
=R\cdot B\uuu *(\omega\uuu 1)
\]
With these notations  the right hand side in (i) is equal to 
\[ 
R\cdot\int\uuu{S^{m\vvv 2}}\,B\uuu *(\omega\uuu 1)\cdot dA\uuu{m\vvv 2}\tag{1}
\]
Above $||X||=R$ and
Lemma 2.xx follows with
\[
C\uuu m=
\bigl(\int\uuu 0^\infty\, \frac{1\vvv\cos s\omega\uuu 1}{s^2}\cdot ds\,\bigr)^{-1}
\]




\medskip

\noindent
\emph{Proof of Theorem g.2. }
For a given pair $1\leq i,j\leq N $ the addition formula for the cosine\vvv function gives:
\[
1\vvv\cos\, \langle X\uuu i,Y\rangle+
1\vvv\cos\, \langle X\uuu j,Y\rangle+
\cos\, \langle (X\uuu i\vvv X\uuu j ),Y\rangle=
\]
\[
(1\vvv\cos\, \langle X\uuu i,Y\rangle)\cdot 
(1\vvv\cos\, \langle X\uuu i,Y\rangle)+\sin\,\langle X\uuu i,Y\rangle\cdot
\sin\,\langle X\uuu j,Y\rangle\tag{1}
\]
It follows that the matrix element $b\uuu{ij}$
is given by

\[
C\uuu m\cdot \int\uuu{{\bf{R}}^m}\,
\frac{(1\vvv\cos\, \langle X\uuu i,Y\rangle)\cdot 
(1\vvv\cos\, \langle X\uuu j,Y\rangle)+\sin\,\langle X\uuu i,Y\rangle\cdot
\sin\,\langle X\uuu j,Y\rangle}{||Y||^{m+1}}\cdot dY\tag{3}
\]
From this we see that
\[
H(\xi)= C\uuu m\cdot
\int\uuu{{\bf{R}}^m}
\,\bigl([\sum\, (\xi\uuu k\cdot(1\vvv \cos\langle X\uuu k,Y\rangle) \,]^2
+[\sum\, (\xi\uuu k\cdot(\sin\langle X\uuu k,Y\rangle) \,]^2\bigr) \cdot 
\frac{dY}{||Y||^{m+1}}\tag{3}
\]
Since the vectors $\{X_k\}$ are different it is clear that
\[
\,\bigl([\sum\, (\xi\uuu k\cdot(1\vvv \cos\langle X\uuu k,Y\rangle) \,]^2
+[\sum\, (\xi\uuu k\cdot(\sin\langle X\uuu k,Y\rangle) \,]^2\bigr) \neq 0\tag{4}
\]
for all non-zero $m$-vectors $Y$.
of norm $\geq 1$.
By continuity this gives for example a positive coinstant
$\rho$ such that (4) is
$\geq \rho^*\cdot ||\xi||^2$ for all vectors $Y$ with norm between
$2^{-1}$ and $2$ and from this  the reader can conclude that
$H$ is positive definite.

\bigskip

\noindent
{\bf{g.4. Exercise.}}
Prove more generally that for every $1<p<2$ that the  quadratic form
\[
H_p(\xi)= \bigl(||X\uuu j||^p+X\uuu k||^p\vvv 
||X\uuu j\vvv X\uuu k||^p\bigr)\cdot \xi_j\cdot \xi_k
\]
again is positive when the $X$-vectors are all different.
Show also the following: Let 
$z\uuu 1,\ldots,z\uuu N$ be an $N$\vvv tuple of distinct and non-zero
zero complex numbers and  put 
\[
b\uuu {ij}= \{\frac{z\uuu i}{z\uuu j}\}
\]
Show that the Hermitian matrix $B=\{b\uuu{ij}\}$ is  positive definite.







\newpage



\centerline
{\bf{Self-adjoint operators on Hilbert spaces.}}



\bigskip


\noindent
The spectral theory for 
unbounded   self-adjoint operators was developed
by Carleman in the
monograph \emph{Sur les Žquations singulires ˆ noyau
rel et symmŽtrique} [Uppsala University. 1923].
An account of this work appears in 
Carleman's lecture from [Comptes rendus du $VI^e$  CongrŽs des
MathŽmatiques Scandinavies. Copenhagen 1925].
Let us remark that
[ibid] was preceeded by his earlier studies of
singular integral operators. For example, kernels associated to
the Neumann's boundary value problem whose
boundary has corner points, produce operators whose
spectra contain closed sets with interor points, a situation which in 1916
was quite new.
 
\medskip


\noindent
Hundreds of  text-books and thousands of articles
treat 
spectral theory for unbounded
self-adjoint operators.
But the basic material is  covered in Carleman's original work
and to this 
I would like to add a personal comment. Even though
"abstract methods" in mathematics 
often are  useful, one only becomes truly familiar
with the "source" of a subject
after  executing 
explicit computations. From this point of view [ibid]
appears as an outstanding text about
unbounded linear operators on Hilbert spaces which in addition to
 theoretic results
contain several 
concrete applications   exposed with  
detailed and   very  elegant  proofs.
At the same time specific situations illustrate how to perform the 
pasage to limits which are taken in various weak topologies.
Let us brielfy
describe the major results from [ibid] which will
be
exposed in more detail in ¤ xx.
\medskip

\noindent
{\bf{1. Densely defined hermitian operators.}}
Let $A$ be a linear operator on a separable Hilbert space
$\mathcal H$ whose domain of definition $\mathcal D(A)$ is
dense and satisfies the hermitian equation:
\[
\langle Ax,y\rangle=
\langle x,Ay\rangle
\] 
for each pair $x,y$
in
$\mathcal D(A)$.
A first result in [ibid]
asserts  that the inhomogenous equation
\[
x=\lambda\cdot A(x)+\xi\tag{*}
\]
has at least one solution $x\in\mathcal D(A)$ for every vector $\xi\in\mathcal H$
and non-real complex number $\lambda$.
To prove this  Carleman  used weak approximations of $A$ by
hermitian Hilbert-Schmidt operators.
Using the material from  ¤ xx
it follows that
every solution in (*) satisfies
\[
||x||\leq |\mathfrak{Im}(\lambda)|^{-1}\cdot ||\xi||\tag{**}
\]
If (*) has a unique solution for some 
$\lambda_*$ whose imaginary part is $>0$, then
it is proved in [ibid] that  (*) has unique  solutions for
all $\lambda$ in the upper half-plane which gives
an operator-valued function
$\lambda\mapsto T(\lambda)$ where
\[ 
T(\lambda)(\xi)=x(\lambda)
\]
when $x(\lambda)$ is the unique solution to (*) for the pair
$\xi$ and $\lambda$.
In the same way one can consider (*) when
$\lambda$ varies in the lower half-plane. If uniqueness
again holds, then the  operator-valued function above is defined
in the complement of the real axis.
We shall learn that the uniquness above hold
for non-real $\lambda$ if and only if
$A$ is self-adjoint which means that $A$Êis equal to its adjoint $A^*$.
\medskip

\noindent
{\bf{2. A criterion for existence of self-adjoint extensions.}}
Suppose that the solution space in
(*) has a  common finite dimension $N^*$ 
for each non-real
$\lambda_*$.
Then there exist
a distinguished family of
self-adjoint operators whose
graphs contain that of $A$. More precisely, this family 
is parametrized by points on an $N^*$-dimensional torus.
Details appear in ¤ xx.

\medskip

\noindent
{\bf{3. The case of integral operators.}}
Here one starts with a real-valued function $K(x,y)$ defined in
a product $\Omega\times\Omega$ where
$\Omega$ is an open set in
${\bf{R}}^n$ for some $n\geq 1$.
Assume the symmetry  $K(x,y)= K(y,x)$ and that there exists a nullset
$\mathcal N$ in $\Omega$ such that
\[
\int_\Omega\, K(x,y)^2\, dy<\infty
\quad\colon x\in \Omega\setminus \mathcal N
\]
Let $f(x)$ is a continuous  and square integrable function
in $\Omega$. Now there exist  the non-empty family of
$L^2$-functions $\phi$ which satisfy
\[
\phi(x)=\lambda\cdot  \int_\Omega\, K(x,y)\cdot \phi(y)\, dy+f(x)\tag{3.1}
\]
To begin with
this equality hold for almost every 
$x\in \Omega$, i.e. outside a null-set
which in general  contains
$\mathcal N$.
Suppose that $E$ is a compact subset of
$\Omega\setminus \mathcal N$
such that
\[
\max_{|x_1|-x_2|\leq\delta}\, \int_\Omega\, (K(x_1,y)-K(x_2,y))^2\,dy
\]
tends to zero as $\delta\to 0$ while $x_1,x_2$ stay in  $E$.
Then it is easily seen that
each $\phi$-function is continuous on $E$ and one is led to introduce the sets
\[
\mathcal D(x:\lambda)= \bigcup\, \phi(x)
\]
with the union taken over all solutions to (3.1).
Properties of these sets are studied in [ibid] and 
in the section devoted to the monent problem we shall
give some precise results.
\bigskip


\centerline {\bf{4. The spectral function of a self-adjoint operator.}}
\medskip

\noindent
A major result in Carleman's cited monograph 
asserts the following:
Let $A$ be  a densely defined self-adjoint operator on a separable Hilbert space
$\mathcal H$. Then 
there exists an operator valued function
\[
\lambda\mapsto \Theta(\lambda)\tag{*}
\]
of finite total variation with respect to the operator norms on
the Banach space of bounded linear operators on $\mathcal H$ 
with the following properties.
First, a  vector  $x\in\mathcal H$ belongs to
$\mathcal D(A)$ if and only if 
\[
\lim_{\delta\to 0}\,\bigl[\, \int_{-1/\delta}^{-\delta}\,
|\lambda|^{-1}\cdot ||\frac{d}{d\lambda}( \Theta(\lambda)(x))||+
 \int_{\delta}^{1/\delta}\,
|\lambda|^{-1}\cdot ||\frac{d}{d\lambda}( \Theta(\lambda)(x))||\,\bigr]
< \infty\tag{**}
\]
and when this holds
\[
A(x)=
\lim_{\delta\to 0}\bigl[
\, \int_{-1/\delta}^{-\delta}\,
\lambda^{-1}\cdot \frac{d}{d\lambda}(\Theta(\lambda)(x))
+\, \int_{\delta}^{1/\delta}\,
\lambda^{-1}\cdot \frac{d}{d\lambda}(\Theta(\lambda)(x))\,\bigr]
\tag{***}
\] 
Above the  integrals are  taken in the sense of Stieltjes.
For example, the finiteness of
the last integral in (**)  means that
if $\delta=\lambda_0<\ldots<\lambda_1<\lambda_N=1/\delta$ is
a partition of the interval $[\delta,1/\delta]$, then
\[
\sum_{\nu=1}^{\nu=N-1}\,\lambda_\nu^{-1} \cdot  
||\Theta(\lambda_\nu)(x))- ||\Theta(\lambda_{\nu-1})(x))||\leq C
\]
for a constant which is independent  of $\delta$ and the chosen   partitions of
the corresponding interval.
One refers to (*) as the spectral  operator-valued function  attached to $A$.
In addition to the above the operators which arise via (*) have the
property that
whenver $[a,b]$ and $[c,d]$ are pairwise disjoint intervals on the real
$\lambda$-line then the composed opertor
\[
(\Theta(b)-\Theta(a))\circ
(\Theta(d)-\Theta(c))=0
\]
and $E_{a,b}=(\Theta(b)-\Theta(a))$ is a self-adjoint projection
for every interval $[a,b]$ which  are zero when
the interval $[a,b]$ is disjoint from $\sigma(A)$.
Finally,  for every vector $x\in\mathcal H$ one has the Bessel inequality
\[
\int_{-\infty}^\infty\,||\frac{d}{d\lambda}( \Theta(\lambda)(x)||\leq ||x||
\]
\medskip

\noindent
{\bf{4.1 The construction of $\Theta$.}}
It will be given in ¤ xx and here we ony remark that
the spectral resolution of $A$ is found via a passage to the limit where
one approximates
$A$ by bounded self-adjoint operators.
By this procedure one  gets  insigh about
the $\Theta$-function in (*). 



\medskip

\noindent
{\bf{4.2 The closure property.}}
When $A$ is a self-adjoint operator one can impose
the condition that its kernel is zero, i.e.
$A\colon\mathcal D(A)\to\mathcal H$ is injective.
In [Carleman: Chapire 4]
it is proved  that when this holds, then every
every vector $x\in\mathcal H$
satisfies
the equation:
\[
x=\lim_{\delta\to 0}\, \bigl[
\, \int_{-1/\delta}^{-\delta}\,\frac{d}{d\lambda}(\Theta(x))+
\, \int_{\delta}^{1/\delta}\,\frac{d}{d\lambda}(\Theta(x))\,\bigr]\tag{****}
\]
Following [ibid. page 136] one says that the self-adjoint operator $A$ has the 
closure property when
(****) holds. In the case where  $A$ is presented  as an integral operator
a more refined sufficient  
condition for $A$ to have the closure property is
established in [Carleman: page 138-142] which is 
expressed by the existence of certain weak approximations of
$A$.

 
\bigskip






\centerline{\bf{5. Unitary groups.}}
\bigskip





\noindent
Starting from (*) above one constructs a unitary group
$\{U_t\}$ indexed by real numbers where
\[
U_t(x)=i\cdot \int_{-\infty}^\infty\, e^{i\frac{t}{\lambda}}\cdot
\frac{d}{d\lambda}(\Theta(\lambda)(x))\quad\colon\, x\in\mathcal H
\]
Taylor's limit   formula gives
\[
i\cdot \lim_{t\to 0}\, t^{-1}(e^{i\frac{t}{\lambda}}-1)=
\lambda^{-1}\quad\colon\,\lambda\neq 0
\] 
Then (***)  entails that 
$A$ is the infinitesmal generator  of
$\{U_t\}$ to be defined in ¤ xx.
The  converse  was
proved by Stone and  exposed
in the section devoted to the
Hille-Phillips-Yosida theorem.
Together, the results  by
Carleman and Stone
give a
1-1 corespondence between  the family of strongly continuous
unitary groups and
the family of self-adjoint operators.
\medskip



\noindent
{\bf{5.1 Example.}}
In ${\bf{R}}^3$
the Laplace operator $\Delta$ yields a 
densely defined linear operstor on
the Hilbert space $\mathcal H=L^2({\bf{R}}^3)$.
Introducing the Fourier transform, Parseval's equality gives
the unitary group
$\{U_t\}$
where
\[ 
U_t(f)(x)=
i\cdot (2\pi)^{-3}\cdot \int_{{\bf{R}}^3}
e^{i\langle  x,\xi\rangle}
\cdot  e^{\frac{it}{|\xi|^2}} \cdot\widehat{f}(\xi)\, d\xi
\]
When $f$ is such that
$\widehat{f}(\xi)\in C_0^\infty({\bf{R}}^3)$ we have
\[
\lim_{t\to 0}\,\frac{U_t(f)-f}{t}=
 -(2\pi)^{-3}\cdot \int_{{\bf{R}}^3} \,|\xi|^{-2}\cdot
 e^{i\langle  x,\xi\rangle}\cdot \widehat{f} (\xi)\, d\xi
=\Delta(f)(x)
 \]



\noindent
It follows that the infinitesmal generator of
$\{U_t\}$ is the self-adjoint operator $A$
where $\mathcal D(A)$
consists of $L^2$-functions $f$ for which
$\Delta(f)$ taken in the sense of distribution theory is square integrable.
To find $\Theta(\lambda)$
one  employs Fourier's
inversion formula 
to Gaussian $L^2$-functions of the form
$e^{-a|x|^2}$ where  $a$ 
are real and positive numbers.
The spectrum of $A$ is $(-\infty,0]$. Indeed, this follows
since  Fourier's inversion formula  gives
\[
R_A(\lambda)(f)(x)=
-(2\pi)^{-3}\cdot \int_{{\bf{R}}^3}\,
\frac{e^{i\langle  x,\xi\rangle}}{\lambda+|\xi|^2}\cdot
\widehat{f}(\xi)\, d\xi
\]
Parseval's equality entails  that this gives  a bounded linear operator when
$\lambda$ is outside
${\bf{C}}\setminus (-\infty,0]$.










\bigskip



\centerline {\bf{6. The case of non-separable Hilbert spaces.}}
\bigskip


\noindent
Carleman's studies 
were restricted to
separable Hilbert spaces which means that densely 
defined and symmetric operators
are represented
by   infinite hermitian matrices indexed
by pairs of non-negative integers.
Using the Cayley transform and Hilbert's spectral theorem for bounded
normal operators one can establish 
the spectral theorem for
densely defined self-adjoint operators on non-separable 
Hilbert spaces.
This was carried out in
J. von Neumann's  article  \emph{Allgemeine Eigenwerttheorie Hermitscher
Funktionaloperatoren} [Math. Annalen, vol. 102 (1929)].
See the next section for a brief account and ¤ 9 in
Special Chapters for details.
During  the search of self-adjoint extensions of
densely defined symmetric operators we remark that 
the notion of hypermaximality   introduced by Schmidt
is useful. It
stems
from Schmidt's 
early contributions in  the article \emph{Auflšsing der allgemeinen linearen Integralgleichung}
[Math. Annalen, vol. 64 (1907].  
\medskip

\noindent
Non-separable Hilbert spaces arise in many situations. An example
is the Hilbert space of square integrable functions on
the compact Bohr group which by definition is the dual of
the discrete abelian group of real numbers.
The theory   of almost periodic functions was created by Harald Bohr
(brother to the  phycisist  Niels Bohr) and   presented in the articles
\emph{Zur Theorie  der fastperiodischen Funktionen I-III } [ Acta. Math. vol
45-47 (1925-26]. This led  in
a natural way to  consider  of operators
on
non-separable Hilbert spaces and   motivated a
more
"abstract account"  where unbounded operators
are not  described via infinite matrices indexed by pairs of integers.
Other examples emerge  from quantum mechanics. 
The uncertainty principle led to 
questions concerned with
actions by pairs of non-commutating densely defined
operators on a Hilbert space.
In 1928 this was   reformulated by Weyl to
specific problems about non-commuting families   of unitary groups.
See ¤  for further details where we present 
von Neumann's proof  of a 
result
which settled  original problems posed by
de Broigle, Heisenberg and Schršdinger.


\bigskip




\centerline{\bf{6.1 The Cayley transform.}}

\medskip


\noindent
Recall a classic result about
matrices
which goes back to work by
Cayley and Hamilton.
If $N\geq 2$ is an integer we have the family
$\mathfrak{h}(N)$
of Hermitian  $N\times N$-matrices.
Next, a
matrix $R$ is normal if it commutes
with
the  adjoint matrixÊ$R^*$.
The Cayley transform sends
a Hermitian matrix
$A$ to the normal matrix   
\[
R_A=(iE_N-A)^{-1}
\]
where $E_N$ is the identity matrix in $M_N({\bf{C}})$.
If   $\{\alpha_\nu\}$ is the real spectrum of $A$
it is readily seen that
\[ 
\sigma(R_A)=\{\frac{1}{i-\alpha_\nu}\}
\]
Next, when $a$ is a real number we notice that
\[
\frac{1}{i-a}+\frac{i}{2}=\frac{1}{2(i-a)}(2+i^2-ia)=\frac{1-ai}{2i(1+ai)}
\]
The last quotient  is a complex number with absolute value 1/2. Hence
$\sigma(R_A)$ is contained in the circle
\[
\mathcal C=\{|\lambda+\frac{i}{2}|= \frac{1}{2}\}
\]
Conversely, let  $R$ be a normal operator such that
$\sigma(R)$ is contained in
$\mathcal C$ and does not contain
the origin. Now  there exists the inverse operator $R^{-1}$
and 
\[ 
A=iE_N-R^{-1}\tag{i}
\]
is a normal operator whose spectrum
$\sigma(A)$ is real,  and since $A$  also is normal it follows that it is
Hermitian. Notice also that $R=R_A$ in (i).
\emph{Summing up},  the Cayley transform gives
a bijective map between
Hermitian matrices and the family of invertible
normal operators
whose spectra are contained in $\mathcal C$.

\medskip

\noindent
{\bf{The passage to Hilbert spaces.}}
Consider a complex Hilbert space
$\mathcal H$ and denote by  $\mathcal N$  the family of bounded
normal operators $R$ with the property that
$\sigma(R)$ is contained in the circle $\mathcal C$, and in addition 
$R$ is injective and has a dense range.
To each such $R$ we find a densely defined operator
$S_R$ on $\mathcal H$
which for each $y=R(x)$ in the dense range 
assigns the vector $x$,  i.e. the composed operator
$S_R\circ R=E$, where $E$ is the identity on $\mathcal H$.
Now there also exists the densely defined operator
\[
A= iE-S_R\tag{*}
\] 
We shall learn that the densely operator $A$
is self-adjoint, and 
conversely every
densely defined and self-adjoint operator $A$
is of the form (*)  for
a unique
$R$ in $\mathcal C$.
So this gives
1-1 correspondence which extends the previous result for matrices.
Let us remark that 
bounded self-adjoint operators appear
in (*)  when the normal operator $R$ is    invertible.


\bigskip



\centerline {\bf{7. An ugly example.}}
\bigskip


\noindent
Following [Carleman -  page 62-66]
we  give  examples which show that
the existence of self-adjoint extensions
of  densely defined symmetric operator
is not automatic.
Every separable Hilbert space can be
identified with $L^2[0,1]$ whose vectors are complex-valued square integrable functions.
Let us then consider a real-valued
Lebegue measurable function $K(x,y)$ defined on the square
$\{0\leq x\leq 1\}\times\{0\leq y\leq 1\}$ which is symmetric, i.e.
$K(y,x)= K(x,y)$.
Assume that there exists a null set $\mathcal N$ such that
\[
\int_0^1\, K(x,y)^2\, dy<\infty\quad\colon x\in [0,1]\setminus\mathcal N\tag{1}
\]
If $f\in L^2[0,1]$
the Cauchy-Schwarz inequality entails that
$y\mapsto K(x,y)\cdot f(y)$
is absolutely integrable when $x$ is outside $\mathcal N$.
Hence there exists the almost everywhere defined function
\[
\mathcal K(f)(x)=\int_0^1\, K(x,y)\cdot f(y)\, dy\tag{2}
\]
However,
(1) does not imply that
$\mathcal K(f)$ is square integrable.
So we  consider the subspace
$\mathcal D$ of $L^2[0.1]$
where $f\in \mathcal D$ gives
$\mathcal K(f)$ in
$L^2[0.1]$.
To analyze this subspace
we consider
positive integers $N$ and denote by $E_N$
the subset 
of the unit $x$-interval such that
\[
\int_0^1\, K(x,y)^2\, dy\leq N\quad\colon x\in E_N\tag{3}
\]
If $f\in L^2[0,1]$ is supported by $E_N$
and $g$ is another $L^2$-function, the symmetry of $K$ and Fubini's theorem give
\[
\int_0^1\, g(x)\mathcal K(f)(x)\, dx=
\int_0^1\, g(x)\cdot (\int\, K(x,y)f(y)\, dy)\, dx=
\int_0^1\, f(x)\cdot (\int\, K(x,y)g(y)\, dy)\, dx
\]
The Cauchy-Schwartz inequality and (3) entail that
the absolute value of the last term is majorised by
\[
\sqrt{N}\cdot ||g||_2\cdot \int_{E_N}\, |f(x)|\,dx\leq
\sqrt{N}\cdot ||g||_2\cdot ||f||_2
 \]
Since this hold for every $L^2$-function $g$, 
a wellknown fact from integration theory implies
that
$\mathcal K(f)$ is square integrable and its $L^2$-norm is majorised by
$\sqrt{N}\cdot ||f||_2$.
Hence $\mathcal D$ contains every $L^2$-function supported by
$E_N$. Since $\cup\, E_N=[0,1]\setminus\mathcal N$
it follows that $\mathcal D$ is a dense subspace.
The question arises if there exists some
complex-valued function $\phi\in\mathcal D$ 
which satisfies the eigenvalue equation
\[
\phi=i\cdot \mathcal K(\phi)\tag{*}
\]
When
$\mathcal K$ is a bounded linear operator on
the Hilbert space
$L^2[0,1]$ such non-zero solutions do not exist. In
fact, this
follows from Hilbert's theorem for
bounded symmetric operators.
So if a non-trivial solution to (*) exists, then
$\mathcal K$ must be unbounded.
To exhibit examples of such
"ugly operators", Carleman introduced the
an orthonormal basis for
$L^2[0,1]$ given by a sequence $\{\psi_n\}$ where
$\psi_0(x)=1$ and 
$\psi_1(x)= -1$ on $(0,1/2)$Êand +1 on $(1/2,1)$. 
Finally, for each $n\geq 2$ we set
\[
\psi_n(x)=-2^{\frac{n-1}[{2}} \,\colon\,
1-2^{-n+1}\leq x< 1-2^{-n}
\quad\text{and}\quad
\psi_n(x)=2^{\frac{n-1}{2}}\,\colon\, 1-2^{-n}<x<1
\]
while
\[
\psi_n(x)=0\quad\colon\, 0<x<1-2^{-n+1}
\]
It is easily seen that this gives an orthonormal basis.
Next, for every
sequece $\{a_p\}$  of real numbers we define
the kernel
function  on $[0,1)\times [0,1)$
by
\[
K(x,y)=\sum\, a_p\cdot \psi_p(x)\psi_q(x)\tag{i}
\]
To this symetric function
we associate
the  operator 
\[
\mathcal K(u)(x)=\int_0^1\, K(x,y)u(y)\, dy
\]
The construction of the $\psi$-functions
show that $\mathcal D$ contains
$L^2$-functions $u$ supported by
$0\leq x\leq x_*$ for every   $x_*<1$. In ¤ xx we shall prove the following:

\medskip

\noindent
{\bf{Theorem.}}
\emph{The equation (*) has a non-trivial $L^2$-solution if and only if}
\[
\sum_{p=0}^\infty \, \frac{2^p}{1+a_p^2}<\infty
\]


\bigskip


\centerline{\bf{8. Two examples from PDE-theory.}}

\medskip


\noindent
The study of unbounded self-adjoint
operators is especially relevant while one regards PDE-operators.
We present  two examples below.
\medskip


\noindent
{\bf{1. Propagation of sound}}.
With $(x,y,z)$ as space variables in
${\bf{R}}^3$ and a time variable $t$, the 
propagation of sound
in the infinite  open complement $U={\bf{R}}^3\setminus \overline{\Omega}$
of a bounded open subset $\Omega$ is governed by
 solutions $u(x,y,z,t)$ to the wave equation
 \[ 
 \frac{\partial^2 u}{\partial t^2}= \Delta u\tag{1}
 \] 
 where 
 $\Delta$ is the Laplace operator in $x,y,z$.
So here (1) holds when
$p=(x,y,z)\in U$
and $t\geq  0$. We  assume that
$\partial\Omega$ is of class $C^1$, i.e. given as  a union of pairwise disjoint
closed surfaces of class $C^1$ along which normal vectors are defined.
A well-posed Cauchy problem arises when we seek solutions 
such that
$p\mapsto u(p,t)$ belong to $L^2(U)$ for each $t$,
and the outer normal derivatives
taken along $\partial\Omega$ are zero,  i.e. for every $t$ 
\[
\frac{\partial u}{\partial n}(p,t)=0\quad\colon p\in \partial \Omega\tag{2}
\]
Initial conditions are expressed by  a pair of $C^2$-functions
$f_1x,y,z)$ and $f_2(x,y,z)$ defined in $U$ such that
$f_1,f_2$  together with
$\Delta(f_1$ and $\Delta(f_2)$ belong to $L^2(U)$,
and their outer normal derivatives along $\partial\Omega$ are zero.
Then there exists a unique solution $u$ which satisfies
(1-2) and the initial conditions
$u(p,0)= f_0(p)$Êand $\frac{\partial u}{\partial t}(p,0)= f_1(p)$.
A proof of  existence and uniqueness relies upon the construction
of a 
time-independent self-adjoint operator $A$ acting on 
$L^2(U)$ whose kernel is
expressed via a Green's function
which is found by Neumann's standard elliptic boundary value problem
in the domain $U$.
After this has been done one
gets
an integral representation of the solution $u$ 
expressed via the pair $f_0,f_1$ and the spectral function associated to $A$.
For physical  reaons one expects that
if $u$ is a solution, then the first order partial derivatives of
$u(p,t)$ with respect to the space variables tend to zero as
$t\to+\infty$.
In [Carleman 1923] this is proved by analyzing the spectral function
associated with $A$
where the crucial point is that its associated spectral function is
absolutely continuous with respect to
the $\lambda$-parameter.
In ¤¤ we show
that this absolute continuity is derived from  a
general result which goes as follows:

\medskip

\noindent
Let $\{a\leq s\leq b\}$ be a 
compact interval on the real $s$-line and
$s\mapsto G_s$ is  a function with values in the Hilbert space
$L^2(U)$ which  is 
continuous in the sense that 
\[
\lim_{s\to s_0}\, ||G_s-G_{s_0}||_2=0
\]
hold for each $s_0$, where we  introduced the $L^2$-norms.
The function has a finite total variation if 
there exists a constant $M$ such that
\[
\sum\, ||G_{s_{\nu+1}}-G_{s_\nu}||_2\leq M
\] 
hold for every partition $a=s_0<s_1<\ldots<s_M=b$.
When this holds one  construct Stieltjes integrals
and 
for every subinterval $[\alpha,\beta]$
there exists
the $L^2$-function in $U$ 
\[
\Phi_{[\alpha,\beta]}= \int_\alpha^\beta\, s\cdot \frac{dG_s}{ds}
\]
We impose the extra conditions that the normal deriviatives
$ \frac{\partial G_s}{\partial n}$ exist  and vanish 
$\partial\Omega$ for every $a\leq s\leq b$
and the following differential equation
holds for
every sub-interval $[\alpha,\beta]$ of $[a,b]$:
\[
\Delta(G_\beta-G_\alpha)+\Phi_{[\alpha,\beta]}=0
\] 
\medskip

\noindent
{\bf{Theorem.}}
\emph{The equations  above imply that
$s\mapsto G_s$ is absolutely continuous.}
\medskip

\noindent
{\bf{Remark.}}
The absolute continuity of 
$s\mapsto G_s$Êmeans that 
whenever $\{\ell_1,\ldots,\ell_M\}$ a finite family of disjoint
intervals in $[a,b]$ where the sum of their lengths is $<\delta$,
then the sum of
the total variations over these intervals is
bounded by $\rho(\delta)$ where
$\rho$ is a function of $\delta$ which tends to zero as $\delta\to 0$.
We refer to ¤ xx for an account of the proof of this result.

\bigskip


\medskip






\centerline
{\bf{2. The Bohr-Schršdinger  equation.}}
\bigskip




\noindent
In 1923 quantum mechanics had not yet appeared so
the studies in  [Carleman: 1923] were 
concerned with singular  integral equations, foremost 
inspired from  previous work by Fredholm, Hilbert,
Weyl  and Volterra.
The creation of quantum mechanics gave new challenges for the
mathematical community,.
The interested reader should   consult the
lecture held  by Niels Bohr at the Scandianavian congress in mathematics
in Copenhagen 1925 where he
speaks  about  the   interplay between
the new physics and 
mathematics. 
Bohr's  lecture  presumably inspired Carleman when he
some years later resumed 
work from [Car 1923].
Recall that the fundamental point in Schršdinger's theory
is the hypothesis on energy levels which correspond to 
orbits in Bohr's theory of atoms. For an account about
the physical background
the reader may consult
Bohr's
plenary talk when 
he received the Nobel Prize in physics 1923.
Mathematically the Bohr-Schršdinger theory
leads to the  equation
\[ 
\Delta\phi+2m\cdot\bigl( E-U\bigr)\bigl(\frac{2\pi}{h}\bigr)^2\cdot \phi=0\tag{*}
\] 
Here $\Delta$ is the Laplace operator in the 3-dimensional $(x,y,z)$-space,
$m$ the mass of a particle and $h$  Planck's constant
while   $U(x,y,z)$ is a potential function.
Finally $E$ is a parameter and one seeks values on $E$
such that (*) has a solution $\phi$
which belongs to $L^2({\bf{R}}^3)$.
Let us   cite an excerpt   from Carlemans  lectures in Paris at 
Institut Henri PoincarŽ held in 1930:
\medskip

\noindent
\emph{Dans ces dernires annŽes l'’nteret de la question qui nous
occupe a considŽrablement augmentŽ.
C'est en effet
un instrument mathŽmatique 
indispensable pour development de la mechanique moderne crŽe par
M.M. de Brogile, Heisenberg et Schršdinger. Etude de l'Žquation
integrale:}
\[ 
\phi(x)= \lambda\cdot \int_a^b\, K(x,y)\phi(y)dy+f(x)
\quad\colon\lambda\in {\bf{C}}\setminus {\bf{R}}
\]
\medskip

\noindent
The theory from [Carleman:1923] applies  to the following
PDE-equations attached to a second order differential operator
\[ 
L=\Delta+c(x,y,z)\quad\colon
\Delta=\partial_x^2+\partial_y^2+\partial_z^2\tag{**}
\]
where $c(x,y,z)$ is a real-valued function.
The $L$-operator is  densely defined and  symmetric on the
subspace of
test-functions  in
${\bf{R}}^3$. The problem is to find conditions on
the $c$-function in order that $L$ is self-adjoint on
the Hilbert space $L^2({\bf{R}}^3)$
with a real spectrum confined to $[a,+\infty)$ for some real number $a$.
The following
sufficiency result was presented by
Carleman's  
during  his lectures at Sorbonne
in the spring 1930:
\medskip

\noindent
{\bf{Theorem }}
\emph{Let $c(x,y,z)$ be a continuous and real-valued function
such that there is a constant $M$ for which}
\[
\limsup \uuu{x^2+y^2+z^2\to \infty}\, c(x,y,z)\leq M
\]
\emph{Then $\Delta+c(x,y,z)$ is self-adjoint.}
\medskip

\medskip

\noindent{{\bf{Example.}}
The result applies when $c$ is given
by a potential function:
\[ 
W(p)=\sum\,\frac{\alpha_k}{|p-q_k|}+\beta
\] 
where $\{q_k\}$ is a finite subset of
${\bf{R}}^3$ and the $\alpha$-numbers and $\beta$ are real and positive.
Here the requested self-adjointness is  easy to prove
and solutions
to the Bohr-Schršdinger equation
are found
via  robust limit formulas.
See ¤¤ xx for details.

\bigskip


\noindent
{\bf{Further comments.}} The literature about
the Schršdinger equation and  other
equations which emerge from quantum mechanics is 
extensive. 
For the 
source of quantum mechanics
the reader should first of all consult 
the plenary talks by Heisenberg, Dirac and Shršdinger
when they received the Nobel prize in
physics. 
Apart from physical considerations the reader
will find
expositions where explanations
are given in a mathematical framework.
Actually Heisenberg was
sole winner 1931 while Dirac and Schršdinger shared the
prize in 1932. But they visited Stockholm together in
December 1932.
\medskip

\noindent
For  mathematician who wants to become acquainted with
quantum physics the eminent text-books by Lev Landau
are recommended. Especially 
\emph{Quantum mechanics: Non-relativistic theory}
in Vol. 3.
Here Landau exposes
Heisenberg's matrix representation and
Dirac's  equations are used to study radiation phenomena.
In the introduction to
[ibid: Volume 3]
Landau inserts the following remark:
\emph{It is of interest to note
that the complete mathematical formalisim
of quantum mechanics was constructed by W. Heisenberg
and E. Schršdinger in 1925-26, before the discovery
of the uncertainty principle which revealed the physical
contents of this formalism.}

\bigskip



\centerline {\bf{Schršdinger's non-linear Cauchy problem}}
\medskip


\noindent
The  mathematical foundations
in non-relativistic quantum mechanics
rely upon studies of wave-equations. This    was  put
forward in Schršdinger's article 
\emph{Quantizierung als Eigenwertproblem} from 1926.
In the  article
\emph{ThŽorie relativiste de l'electron et l'interprŽtation
de la mŽcanique quantique} [xxx 1932],
 Schršdinger raised a new and unorthodox question concerned with  Brownian motions 
leading to new mathematical problems of considerable interest
which up to the present date remain open.
Consider a Brownian motion which takes place in a bounded
region $\Omega$ of some euclidian space
${\bf{R}}^d$ for some $d\geq 2$.
At time $t=0$
the densities of particles 
under observation is given by some
non\vvv negative function $f\uuu 0(x)$ 
defined on $\Omega$.
Classically the density at a later time $t>0$
is equal to
a function
$x\mapsto u(x,t)$ which satisfies
the heat equation
\[
\frac{\partial u}{\partial t}= \Delta(u)
\] 
with boundary conditions 
\[
u(x,0)=f\uuu 0(x)\quad\text{and}\quad
\frac{\partial u}{\partial {\bf{n}}}(x,t)= 0
\quad\text{when }\quad x\in \partial\Omega\quad\text{and}\quad t>0\tag{1}
\]
Schršdinger took into the account
the reality of quantum physics which
means that in an  actual experiment
the observed density of particles at a time
$t\uuu 1>0$ does not coincide with $u(x,t\uuu 1)$.
He posed the problem to find the most probable development during the time
interval $[0,t\uuu 1)$ which leads to the state at time
$t\uuu 1$, and
concluded  that
the  requested density
function   which
substitutes the heat\vvv solution $u(x,t)$
belongs to a non\vvv linear class of functions formed by
products
\[ 
w(x,t)= u\uuu 0(x,t)\cdot u\uuu 1(x,t)\tag{*}
\]
where $u\uuu 0$ is a solution to (1) 
while $u\uuu 1(x,t)$ is a solution to an adjoint equation
\[
\frac{\partial u\uuu 1}{\partial t}= \vvv\Delta(u)
\quad\colon\quad
\frac{\partial u\uuu 1}{\partial {\bf{n}}}(x,t)= 0
\quad\text{on}\quad \partial\Omega\tag{2}
\] 
defined when $t<t\uuu 1$.
This leads to a new type of Cauchy problems
where one asks if there exists a  $w$\vvv function in  (*)
satisfying
\[ 
w(x,0)= f\uuu 0(x)\quad\colon\quad w(x,t\uuu 1)=f\uuu 1(x)
\]
whenever $f\uuu 0,f\uuu 1$ are non\vvv negative functions
such that
\[
\int\uuu\Omega\, f\uuu 0\cdot dx=
\int\uuu\Omega\, f\uuu 1\cdot dx
\]
\medskip

\noindent
The solvability of this non\vvv linear boundary value problem was left open
by Schršdinger.
When $\Omega$ is a bounded set
with  a smooth boundary
one can use the Poisson\vvv Greens function for the
classical equation (*)  and 
rewrite Schršdinger's equation  to 
a system of non\vvv linear integral equations.
The  reader should consult the talk by I.N. Bernstein a the IMU\vvv congress at ZŸrich 1932 
for a first account about eventual  solutions to the
Schršdinger equation above.
Non-trivial examples occur already  on the product
of two copies of the real line where solutions to Schršdinger's equation 
is equivalent to find solutions 
of non\vvv linear equationa expressed via
measures. More precisely,
consider the Gaussian density function
\[
g(x)=\frac{1}{\sqrt{2\pi}}\cdot e^{\vvv x^2/2}
\]
on the real $x$-line.
Denote by the family $\mathcal S\uuu g^*$
of all non\vvv negative product measures
$\gamma\uuu 1\times\gamma\uuu 2 $
for which
\[
\iint g(x\uuu 1\vvv x\uuu 2)\cdot d\gamma\uuu 1(x\uuu 1)
\cdot d\gamma\uuu 2(x\uuu 2)=1\tag{i}
\]
Next,  $\gamma\uuu 1\times\gamma\uuu 2 $ gives a new  product measure 
\[
\mathcal T\uuu g(\gamma\uuu 1\times\gamma\uuu 2)=
\mu\uuu 1\times\mu\uuu 2
\]
such that 
\[
\mu\uuu 1(E\uuu 1)\cdot \mu\uuu 2(E\uuu 2)=
\iint \uuu {E\uuu 1\times E\uuu 2}\,
g(x\uuu 1\vvv x\uuu 2)\cdot d\gamma\uuu 1(x\uuu 1)
\cdot d\gamma\uuu 2(x\uuu 2)
\] 
hold for all pairs of bounded Borel sets.
Notice that $\mu\uuu 1\times \mu\uuu 2$
becomes a probability measure since (i) above holds.
With these notations the following result was proved by
Beuling in the article \emph{xxx}[ xxx]:

\medskip

\noindent
{\bf{Theorem.}}
\emph{For every product measure
$\mu\uuu1\times\mu\uuu2$ with total mass one
there exists
a unique $\gamma\uuu 1\times\gamma\uuu 2$ in $S^*\uuu g$
such that}
\[
\mathcal T\uuu g(\gamma\uuu 1\times\gamma\uuu 2)=\mu\uuu1\times\mu\uuu2
\]
\medskip

\noindent
{\bf{Remark.}}
Beurling's proof  relies upon
an  involved variational problem and goes beyond the scope of
the present chapter. 
But see ¤ xxx in my notes
\emph{Special Topics}
for an account of Beurling's studies related to Schršdinger's 
"unorthodox" Cauchy problem.






\newpage



\centerline {\bf{Some special  examples.}}

\bigskip

\noindent
It  is  
valuable to become familiar with various "concrete examples"
in order to appreciate the general theory
about normed spaces and their operators.
At the same time 
we remark that many problems which from the start are put in the context of
"pure functional analysis" can only be solved
by analytic function theory or other disciplines.
Here follows  some examples which  illustrates this.
 The less experienced reader may neglect the present section
for a while since
 the subsequent material is independent of the general theory in the  chapters.
 

\bigskip


\centerline {\bf{1. A linear system in infinitely many unknowns}}
\medskip

\noindent
Let $\{b_q\}$ be an infinite sequence of complex numbers
indexed by positive integers. We 
assume it is separated which means that there
exists $c>0$ such that
\[
|b_q-b_p|\geq c\quad\colon p\neq q\tag{i}
\]
Let
$\{a_q\}$ be another sequence of complex numbers
where $a_q\neq b_p$ for all pairs $p,q$.
We do not assume that
$\{a_q\}$ is separated but it is a discrete subset
of ${\bf{C}}$.
Denote by $\ell^2$ the linear space of sequences
of complex numbers $\{x_n\}$ for which
$\sum\, |x_n|^2<\infty$.
To each vector 
$\{x_n\}\in\ell^2$ we get the sequence
\[
\xi_p=\sum_{q=1}^\infty\, \frac{x_q}{a_p-b_q}\tag{ii}
\] 
It is easily seen that (i) entails that
\[
\sum_{q=1}^\infty\, \frac{1}{|a_p-b_q|^2}<\infty
\quad\colon p=1,2,\ldots
\]
The Cauchy-Schwarz inequality gives
$\{\xi_p\}\in \ell^2$ and hence  (ii) becomes  a linear operator from
$\ell^2$ into itself.
The question arises when this operator is injective, i.e.
if the system
\[
\sum_{q=1}^\infty\, \frac{x_q}{a_p-b_q}=0
\quad\colon p=1,2,\ldots
\]
only has the trivial null solution.
Put in this generality one cannot
give an answer.
However, certain conclusions are available if 
the two sequences  have angular distributions.
More precisely,  suppose that
none of the sequences contain zero. 
To each $p$ we get the poinit $\beta_p=|b_p|^{-1}b_p$ on the
unit circleÊ$T$. 
 If $r\geq 1 $ we get  the disctete measure
 $\mu_b(r)$ on $T$  defined by
 \[
 \mu_b(r)=\frac{1}{r}\cdot \sum\, \delta(\beta_p)
 \] 
 where the sum extends over integers $p$ such that
 $|b_p|\leq r$ and
 $\delta(\beta_p)$ assign unit point masses at the $\beta$-points.
 One says that $\{b_p\}$ has an angular distribution if
 there exists
 a non-negative Riess measure $\mu_b$ of finite
 mass such that
 \[
 \lim_{r\to\infty}\, \mu_b(r)= \mu_b
 \]
 holds in the weak-star topology of Riesz measures on $T$.
 In the same way we   impose the condition that
 $\{a_p\}$  has an angular distribution and let
 $\mu_a$ be the resulting limit measure.
 Now we consider  the support functions
 \[
 h_b(\theta)= \int_0^{2\pi}\, \cos^+(\theta-\phi)\, d\mu_b(\phi)
 \quad\colon\, h_a(\theta)= \int_0^{2\pi}\, \cos^+(\theta-\phi)\, d\mu_a(\phi)
\]
They define closed convex
sets
\[ 
C_b=\{re^{i\theta}\,\colon\, 0\leq r\leq h_b(\theta)\}
\quad\colon\,
C_a=\{re^{i\theta}\,\colon\, 0\leq r\leq h_a(\theta)\}
\] 

\medskip

\noindent
{\bf{1.1 Theorem.}}
\emph{If $C_b\setminus C_a\neq\emptyset$ the system (*)
only has the trivial null solution. Conversely, if
$C_b$ is contained in the interior of $C_a$ there exists
non-trivial solutions to (*).}
\medskip

\noindent
{\bf{Remark.}}
The proof of this result relies upon analytic function theory and cannot 
be derived via  general considerations in functional analysis, even if the
question is posed in the Hibert space $\ell^2$.
So the result above illustrates that in many
 "concrete situations" the general theory  serves as a guidance
only, while the 
solutions  require  a more delicate analysis.
We refer to ¤ xx in special Topics for
an account of the proof of the theorem above 
and remark  that
equations of thid nature  were studied in the thesis 
\emph{Sur une classe de systmes d'Žquations lineaires
ˆ une infinitŽ d'innconnues} by K. Dagerholm at   Uppsala
in 1938.
\bigskip




\centerline {\bf{2. A singular integral.}}
\bigskip

\noindent
Given a real-valued and continuous
function $a(x)$ defined on  $[-1,1]$
we consider the operator
\[
\mathcal K_u(x)=a(x)u(x)-\int_{-1}^1\, \frac{u(x)-u(y)}{x-y}\, dx
\]
Here some care must be taken, i.e. the $u$-functions should be
sufficiently  regular in order that
the integral above exists. A sufficient condition is that
$u$ is Hšlder continuous of some order $>0$, i.e. 
\[
|u(x)-u(y)|\leq C\cdot |x-y|^\delta
\] 
hold for a constant $C$ and some $\delta>0$.
Consider the inhomogeneous equation
\[ 
\mathcal K(u)=f\tag{*}
\] 
where $f$ is a given function.
When $a$ is identically 
the following uniqueness result holds:
\medskip

\noindent
{\bf{Theorem. }} \emph{If $u(x)$ is Hšlder continuous of some order
$>0$ on the unit interval $[0,1]$ and satisfies}
\[
\int_0^1\, \frac{u(x)-u(y)}{x-y}\, dx=0\quad\colon 0<x<1
\]
\emph{then $u$ is a constant.}
\medskip

\noindent
Let us now turn to the equation (*).
If the function $a(x)$ is real-analytic
it turns out that (*) has a solution $u$ for every
real-analytic function $f$.
Moreover, $u$ is found by the inversion formula:
\[
u(x)=\frac{a(x)}{a(x)^2+\pi^2}\cdot f(x)+
\frac{e^{\omega(x)}}{\sqrt{a(x)^2+\pi^2}}\cdot
\int_{-1}^1\, 
 \frac{e^{-\omega(s)}f(s)}{\sqrt{a(s)^2+\pi^2}} \cdot \frac{1}{s-x}\, ds
\]
where the $\omega$-function is defined by
\[
\omega(x)=\int_{-1}^1\,  \frac{\theta(s)}{s-x}\, ds
\quad\colon\,
\theta(s)= \frac{1}{2\pi i}\cdot \log\, \frac{a(x)+\pi i}{a(x)-\pi i}
\]
and the argument of the complex log-function has been chosen above so that
$0<\theta(x)<1$ hold for each $-1<x<1$.
\medskip


\noindent
{\bf{Renark.}}
The results above appear in Carleman's article
\emph{Sur la rŽsolution de certaines Žquations intgrales}
[Arkiv fšr matematik, fysik och astronomi: Vol 16].
It goes without saying that the proof of the inversion formula relies
heavily upon analytic function theory.
So the here the 
solutions 
are  not found by "abstract reasoning" or via calculus of variation.
Instead one employs residue calculus and
integral formulas taken from analytic function theory
where
mutli-valued branches of the complex log-function play
an essential role.


\bigskip


\centerline{\bf{3. Carleson-Kronecker sets.}}
\medskip

\noindent
Let us begin with  a  result  due to F. Riesz.
Consider  a doubly indexed sequence
$\{c\uuu{\nu.n}\}$ of complex numbers 
where $(\nu,n)$ are pairs of non\vvv negative integers.
Suppose
there exists a strictly increasing sequence of positive numbers
$\{A\uuu n\}$ which tends to $+\infty$ such that

\[ 
|c\uuu{\nu.n}|\leq \frac{1}{A\uuu n}\quad\text{hold for all pairs}\quad \nu,n
\]
Under this assumption we study the inhomogeneous system of linear equations
\[
\sum\uuu{n=1}^\infty\, c\uuu{n,\nu}\cdot x\uuu n=y\uuu \nu\tag{*}
\]
where $\{y\uuu \nu\}$ is a bounded sequence of complex numbers.
The equation is said to be  solvable in $\ell^1$ if there exists a sequence
$\{x\uuu n\}$ such that
$\sum\, |x\uuu n|<\infty$.
The following result was proved by Riesz:

\medskip

\noindent
{\bf{Theorem.}}
\emph{Let $\{c\uuu{n,\nu}\}$ and $\{y\uuu \nu\}$ be such that
for every finite sequence 
$\lambda\uuu 0,\ldots,\lambda\uuu r$ it holds that}
\[
|\sum\uuu{\nu=0}^{\nu=r}\, \lambda\uuu \nu\cdot y\uuu\nu|
\leq \,\sup\uuu {n\geq 0}\, |\sum\uuu{\nu=0}^{\nu=r}\, 
\lambda\uuu \nu\cdot c\uuu{n\nu}|
\]
\emph{Then (*) has an $\ell^1$\vvv solution such that
$\sum\, |x\uuu n|\leq 1$.}
\medskip

\noindent
Let us give an example where
Riesz' theorem is applied. 
Let $E$ be a compact subset
of the unit circle $T$ and denote by   $C^0(E)$ 
the Banach space of complex\vvv valued 
continuous functions on $E$ equipped with the maximum norm.
 Measure theory teaches that
the dual space consists of Riesz measures $\mu$ of finite total variation on $E$.
Let $M(E)$ denote this set of measures.
To every $\mu\in M(E)$  and each non\vvv negative integer we set

\[
\widehat \mu(n)=\int\uuu E\, e^{in\theta}\cdot d\mu(\theta)
\]
We say that $E$ is of the Carleson\vvv Kronecker set
if there exists $0<p(E)\leq 1$ such that
\[
||\mu||\leq \frac{1}{p(E)}\cdot \sup\uuu{n\geq 0}\, 
|\widehat \mu(n)|\quad\text{hold for all}\quad \mu\in M(E)
\]

\medskip

\noindent
With these notations the result below
is proved in  ¤ XX from  \emph{Special Topics}.
\medskip


\noindent
{\bf{Theorem.}}
\emph{Let $E$ be  a Carleson\vvv Kronecker set. Then, for each
$\phi\in C^0(E)$ there exists 
an absolutely convergent sequence
$\{x\uuu n\}$ 
such that}
\[ 
\phi(e^{i\theta})= \sum\uuu{n\geq 0} \, x\uuu n\cdot e^{in\theta}
\quad \text{holds on}\quad E
\]
\bigskip


\centerline {\bf{4. $L^p$-inequalities.}}

\medskip


\noindent
Many results which originally  were 
constrained to  specific situations
can be extended  when
notions in
functional analysis are adopted. An  example
is  a theorem 
from the article [Hšrmander-1960]
where  singular integrals
are  treated  in a  general context.
Here is the set up: Let $B_1$ and $B_2$ be  Banach spaces
and $n$ a positive integer.
Let $x\mapsto K(x)$ be a function which for every 
$x\in{\bf{R}}^n$ assigns a vector  $K(x)$
in the Banach space
$L(B_1,B_2)$ of continuous linear operators from $B_1$ to $B_2$.
One only assumes that $K$ is a continuous function, i.e. it 
need not be linear.
If $f(x)$ is a continuous  $B_1$-valued function defined in
${\bf{R}}^n$ with compact support there exists
the convolution integral
\[
\mathcal Kf(x)= \int_{{\bf{R}}^n}\, K(x-y)(f(y))\, dy\tag{1}
\]
To be precise, with $x$ fixed in
${\bf{R}}^n$ the right hand side is
a well-defined $B_2$-valued integral which exists
because  the linear operator $K(x-y)$  sends the
$B_1$-vector $f(y)$ into $B_2$, i.e. the integrand
in the right hand side is a $B_2$-valued function
\[ 
y\mapsto K(x-y)(f(y))
\] 
whose Borel-Stieltjes integral   with respect to $y$ exists.
The resulting value of this integral
yields
the $B_2$-vector in the left hand side in (1). When $x$ varies,
$x\mapsto \mathcal Kf(x)$
becomes a $B_2$-valued function.

\medskip

\noindent
{\bf{The Hšrmander conditions}}.
Following [ibid] we
impose two   conditions on $K$ where
norms on the three Banach spaces $L(B_1,B_2),B_1,B_2$ appear.
The first is
that there
exist a constant $C_K$ such that
the following hold for every real number $t>0$:
\[ 
\int_{|x|\geq 1}\, ||K(t(x-y))-K(tx)||\, dx\leq C_K\cdot t^{-n}
\quad\text{for all}\quad |y|\leq 1\tag{1}
\]
where the left hand side
employs 
the operator norms of $K$  defined for pairs of points  $tx$ and
$t(x-y)$ in ${\bf{R}}^n$. The second is
the following $L^2$-inequality for every function $f$ where we employ the 
same constant $C_K$ as above:
\[
\int_{{\bf{R}}^n}\, ||\mathcal Kf(x)||^2\, dx\leq
C_K^2\cdot \int_{{\bf{R}}^n}\,||f(x)||^2\, dx\tag{2}
\]
where one has used norms on $B_1$ respectively $B_2$ during the integration.


\medskip

\noindent
Using an extension of Vitali's covering lemma
to a similar covering  principle on arbitrary normed spaces,
the following result is proved in [ibid]:
 

\bigskip

\noindent
{\bf{4.1 Theorem.}}
\emph{There exists an absolute constant $C_n$ which depends on 
$n$ only such that for every
pair  of Banach spaces $B_1,B_2$ and every linear operator $K$
which satisfies (1-2), the following hold for every
$\alpha>0$:}
\[
\text{vol}_n(\{x\in{\bf{R}}^n\,\colon\,  ||\mathcal Kf(x)||_2 >\alpha\})\leq
\frac{C_n\cdot C_K}{\alpha}\cdot \int_{{\bf{R}}^n}\, ||f(x)||_1\, dx
\]


\noindent
{\bf{Remark.}}
This result 
has a wide range of applications
when it is combined  with
interpolation theorems  by  Markinkiewicz and Thorin.
For example, classical results which involve $L^p$-inequalties 
during the passage to Fourier transforms or other   kernel functions
can be put into a general  frame where one  employs
vector-valued functions rather than
scalar-valued functions. Typical examples occur when
$K$ sends real-valued functions
to vectors in a Hilbert space, i.e.  
$B_1$ is  the 1-dimensional real line  and
$B_2=\ell^2$.
So Hšrmander's  theorem  constitutes a veritable propagande for
learning  general notions in functional analysis. The
idea to regard vector-valued
functions
was of course  considered at an early stage. 
An  example is
a theorem due to Littlewood and Paley
which goes as follows: Let $f(x)$ be a function on the real line 
such that both $f$ and $f^2$ are integrable.
To each integer $n\geq 0$
we set
\[
f_n(x)=
\bigl|\int_{2^{n-1}}^{2^n}\, e^{ix\xi}\cdot \widehat f(\xi)\, d\xi\,\bigr|+
\bigl|\, \int_{-2^{-n}}^{-2^{n-1}}\, e^{ix\xi}\cdot \widehat f(\xi)\, d\xi\,\bigr|
\]
Then it is proved in [L-P] that for each
$1<p\leq 2$ there exists a constant $C_p\geq 1$ such that
\[
C_p^{-1}||f||_p\leq\cdot \int_{-\infty}^\infty\, \bigl(\sum_{n=0}^\infty\, f_n(x)^2\bigr)^{\frac{2}{p}}
\, dx\leq C_p\cdot ||f||_p\tag{*}
\]
where $||f||_p= \bigl(\int\, |f(x)|^p\, dx\bigr)^{\frac{1}{p}}$
is the $L^p$-norm of $f$.
Hšrmander's theorem can applied to get  (*)
which has the merit that the use
a suitable vector-valued  operator during the proof
becomes
transparent. 
\medskip


\noindent
{\bf{The class BMO.}}
The space of functions with bounded mean oscillation  was
introduced by
F. John and Nirenberg. It can be used to establish various estimates for
singular integrals.
A fundamental  discovery due to C. Fefferman and E.M. Stein
is the duality between
$\text{BMO}({\bf{R}}^n)$ and
the Hardy space $H^1({\bf{R}}^n)$.
See their joint article \emph[xxxx} [Acta mathematica. xx 19xx]
and also Fefferman's article \emph{xxxx} [ibid. xxx 19xx].
In addition we refer to the excellent 
text-books by E.M Stein.
A merit to use 
$\text{BMO}({\bf{R}}^n)$ is that one
often can  establish requested inequalities within this space, and in this
way
ignore the study of so called weak-type estimates.
Here is an example of a result due to the present author in
the article \emph{xxx}[Math. Scand. xxx 1973]:
Let $n\geq 1$ and for a given positive number $M$ we denote by
$\mathfrak{Db}_M({\bf{R}}^n)$
the family of all distributions in
${\bf{R}}^n$ with  compact support in the ball
$\{|x||\leq M\}$ whose Fourier transform satisfy the decay condition
\[
|\widehat{\mu}(\xi)|\leq (1+|\xi|)^{-n}\tag{*}
\]
\medskip

\noindent
{\bf{Theorem.}}
\emph{For each $n$ there exists a constant $C_n$ such that
every $\mu\in \mathfrak{Db}_M({\bf{R}}^n)$ has bounded mean oscillation and
its BMO-norm is bounded by $C_n\cdot ??$.}
\medskip

\noindent
Improvements of this result were later given by P. Sjšlin. For example, he showed that
(*) can be relaxed to the condition 
\[
\sum\, xxxx<\infty
\]
{\bf{A final remark.}}
For   results where translation invariant 
convolution operators are replaced by kernels of pseudo-differential
operators  we refer to volume 3 in Hšrmander's eminent text-book series  on
linear PDE theory.












\bigskip


\centerline{\bf{4.2 Sobolev inequalities}}


\bigskip



\noindent
Sobolev's article
\emph{On a theorem of functional analysis} [Mat. Sbornik. Vol 4 (1938)]
established  inequalities where
integrability assumptions on derivative of a function
lead to various regularity properties of the function itself.
For functions of one or two variables
such  results were established earlier by Landau,  
Hardy  and
Littlewoood.
The results in  [Sob] 
rely upon  integral  formulas 
which recover $f$
from  first order partial derivatives
when  $f$ is  defined in some half-space of
 ${\bf{R}}^n$, or more generally in
 a domain with
smooth boundary. We present this in ¤ xx. Let us  remark that
Sobolev's averaged Taylor formula was
inspired by the methods used by Hardy and Littlewood
in the proof of Theorem xx below.
For $L^2$-norms
Sobolev  inequalites were a
well understood by Hermann Weyl at an early stage who
used them  to
solve the Dirichlet problemand more general elliptic
boundary value problems.
Thanks to the general interpolation results
by Markinsiewiz and Thorin 
one arrives at quite sharp estimates of the Sobolev type
where
one often profits upon  weak-type estimates. Finally, 
using 
the Fefferman-Stein 
duality between functions of bounded mean oscillation in
${\bf{R}}^n$ and the Hardy space $H^1({\bf{R}}^n)$
one gets inequalities which go beyond
those in Sobolev's original work.
Since the literature dealing with inequalities of the Sobolev type is very
extensive we
shall refrain fgrom a more detailed discussion.
But we shal, expose  some crucial results, foreost restricted
to  functions of two variables since already here the general 
methods to attain Sobolev inequalities appear.



\medskip

\noindent
{\bf{The Hardy-Littelwood theorem}}.
Let $f$ be 
a real-valued function 
defined in the open  half-plane $\{x>0\}$
in ${\bf{R}}^2$ with a  bounded support, i.e. say that 
$f=0$ when  $x^2+y^2\geq 1$.
Assume that  $f$ has first order dervatives
in the open  half-disc $D^+$ where $x>0$ and $x^2+y^2<1$
and impose the condition that
\[
\iint_{D^+}\, \bigl[\,|\frac{\partial f}{\partial x}(x,y)|^p+
 |\frac{\partial f}{\partial y}(x,y)|^p\,\bigr]\cdot\, dxdy<\infty
\]
holds for some $p\geq 1$,
i.e. the  partial derivatives belongs to
$L^p(D^+)$. 


\medskip

\noindent
{\bf{4.2.1 Theorem.}}
\emph{If
the first order derivatives of $f$ belong to 
$L^p(D^+)$ for some $1<p<2$, then}
\[
\iint_{D_+}\, |f(x,y)|^{p_*}<\infty
\quad\text{where}\quad \frac{1}{p_*}= \frac{1}{p}-\frac{1}{2}
\]
\medskip

\noindent
{\bf{4.2.2 The case $p=2$}}.
Before we give the proof we notice that
$p=2$ means that
$p_*=+\infty$. The question arises
if  square integrability
of the partial derivatives imply that
$f$ is a bounded function.
The answer is negative.
To see this we apply
Riemann's Mapping Theorem.
Namely, consider a simply connected unbounded open
set
$\Omega$ in ${\bf{C}}$ which has finite area while $\mathfrak{Re}(z)$ can 
become arbitrary large in the unbounded domain.
Let $f\colon D\to \Omega$ be the conformal mapping.
Now one has the equality
\[ 
\text{area}(\Omega)=
\iint \, |f'(z)|^2\cdot dxdy
\]
So with  $u=\mathfrak{Re}\, f$
the first order derivatives of $u$ are square integrable while $\Omega$
while the choice of $\Omega$ entails that
the harmonic function  
$u$ is unbounded in $D$.







\newpage

\centerline{\bf{Proof of Theorem 4.2.1}}
\bigskip

\noindent
Let $b(r)$ be a smooth function defined on $r\geq 0$
where $b(r)=1$ if $0\leq r\leq 2$ and $b(r)=0$ if
$r\geq 3$. Next, let $a(\theta)$ be a smooth and non-negative function on
the periodic $\theta$-interval where
\[ 
\int_0^{2\pi}\, a(\theta)\, d\theta=1
\]
We also assume that the support of $a$ stays close to the point 1
on the unit circle, say that
$a(\theta)=$ if
$|e^{i\theta}-1|\geq 1/10$.
Set:
\[ 
F(x,y)=
\iint\, \frac{\partial}{\partial_r}(f(x+r\cos\theta,y+r\sin\theta)
\cdot b(r)\cdot a(\theta)\, drd\theta
\]
where the double integral is  over
${\bf{R^+}}\times T$.
Partial integration with respect to $r$ gives:
\[
F(x,y)= f(x,y)-\iint\, f(x+r\cos\theta,y+r\sin\theta)
\cdot b'(r)\cdot a(\theta)\, drd\theta
\]
Here   $b'(r)=0$ when
$r$ is outside $[2,3]$ so the constraints on
the supports of $f$ and $a$ imply that
the last integral vanishes when  $x^2+y^2\leq 1$.
In the half-disc $D_+$ we therefore have $F=f$.
At the same time
rules of differentation give
\[
\frac{\partial}{\partial_r}(f(x+r\cos\theta,y+r\sin\theta)=
\]
\[
\frac{\partial}{\partial_x}f(x+r\cos\theta,y+r\sin\theta))\cdot \cos\theta+
\frac{\partial}{\partial_y}f(x+r\cos\theta,y+r\sin\theta))\cdot \sin\theta
\]
\medskip

\noindent
Define the functions
\[ 
h(r,\theta)=\frac{\cos\theta\cdot b(r)\cdot a(\theta)}{r}
\quad\colon\quad
g(r,\theta)=\frac{\sin\theta\cdot b(r)\cdot a(\theta)}{r}
\]
From the above we get
\[ 
F(x,y)=\iint_{\bf{R^2}}\,\bigl[
\frac{\partial}{\partial_x}f(x+t,y+s)\cdot h(s,t)+
\frac{\partial}{\partial_y}f(x+t,y+s)\cdot g(s,t)\,\bigr]\cdot dsdt
\]
\medskip

\noindent
Hence $F$ is the sum of two convolution integrals.
The hypothesis
in Theorem 0.1 means that each term is the convolution given by
a compactly supported $L^p$-function and $h$, respectively $g$.
Ths reduces the proof to
an inequality for
convolution integrals. More precisely, Theorem 4.2.1 follows
we have proved:

\medskip

\noindent
{\bf{4.2.3 Lemma.}}
\emph{To
each $1<p<2$ there exists a constant
$C_p$ such that}
\[
||\phi*h||_{p_*}\leq C_p\cdot ||\phi||_p
\]
\emph{ hold for each $L^p$-function $\phi(x,y)$ supported by the compact
half-disc $\overline{D^+}$, and with a similar result when
$h$ is replaced by $g$.}
\medskip


\centerline {\bf{4.2.4 How to prove Lemma 4.2.3}}.
\medskip

\noindent
In their  original proof, Hardy and Littlewood used
weak-type estimates to analyze the two extreme cases when
$p=1$Êor $p=2$,  and prior to the Fefferman-Stein
theory 
text-books have exposed the Hardy-Littelwood theorem via
interpolation results due to 
Markinzievich and Thorin.
A more precise
study when  $p=2$ is available which 
gives a proof of Lemma 4.2.3 via the general interpolation
results from |Fef-Stein].
Namely,  the constructions of 
$h$ and $g$ entail that both
have Fourier transforms 
which
decay like $|\xi|^{-1}$ with
$\xi=(\xi_1,\xi_2)$. This leads us to
consider the following set-up:
\medskip


\noindent
To each $R\geq 1$ we denote by
$D_R$  the closed disc of radius $R$
centered at the origin in the $(x,y)$-space. Next, 
$\mathfrak{Db}_*(R)$ is 
the family of distributions $\mu$ with compact support in
in $D_R$ whose Fourier transforms satisfy
\[
|\widehat{\mu}(\xi)|\leq (1+|\xi|)^{-1}\tag{i}
\]
for all $\xi$.
Each such distribution
gives the convolution operator
$T_\mu$ which to begin with is defined on test-functions
$f(x,y)$ by
\[
T_\mu(f)=
f*\mu
\] 

\medskip

\noindent
{\bf{4.2.5 Theorem.}}
\emph{To each $R\geq 1$ there exists a constant $C_R$
such that the inequality below hold when 
$f$ is a test-function
with support in $D_R$ and
$\mu\in \mathfrak{Db}_*(R)$}
\[
||f*\mu||_{\text{BMO}}\leq C_R\cdot ||f||_2
\]
\emph{where the right hand side refers to the norm in the John-Nirenberg space of
functions havnig bounded mean oscillation.}
\medskip

\noindent
{\bf{Remark.}}
This result appears nowadays as a standard result from
the theory of singular integrals.
The reader may consult my cited article [Bjšrk] for the
methods which give the theorem above, or text-books
by E.M. Stein et. al.
\medskip

\noindent
{\bf{4.2.6 Use of interpolation.}}
Theorem 4.2.5   can be spplied with
$\mu$ equal to $h$ or $g$.
Notice that these functions also are integrable and recall that
convolution of $L^1$-functions again belongs to
$L^1$, where 
\[
||f*\mu||_1|\leq ||\mu||_1\cdot ||f||_1
\]
hold for all test-funtions and  no constraint on their support is needed.
Together with the general interpolation
result from the work by Fefferman and Stein, it follows that
Theorem 4.2.5 gives the result below where
$\mathfrak{Db}_{**}(R)$ denotes the class if distributions
$\mu\in \mathfrak{Db}_{**}(R)$ which in addition are $L^1$-densities with
norms
$||\mu||_1\leq 1$.
\medskip


\noindent
{\bf{Theorem.}}
\emph{If 
$\mu\in \mathfrak{Db}_{**}(R)$ and $f$ has support in
$D_R$, the following hold for each $1<p<2$:}
\[
||f*\mu||_{p_*}\leq  
\]







\bigskip



\centerline {\bf{4.2.7 Regularity up to the boundary.}}
\bigskip


\noindent
Consider
the open rectangle
\[
\square=\{0<x<1\}\times\{-1<y<1\}
\]
Let $F(x,y)$ be a function in
$\square$Êwith the additional property that
the first  order derivatives belong to $L^2(\square)$.
Now one may ask
if there exists the  limit function
\[
f(y)=\lim_{x\to 0}\, F(x,y)\tag{i}
\]
and if it yields   a continous function of $y$.
This  turns out that to be  a  subtle question. 
Consider the special case when
$f$ is a harmonic function in $\square$.
Then 
the limit exist for all $y$ outside a set whose outer logarithmic capacity is zero.
This result (which is  sharp)
was proved by   Beurling in the article
\emph{xxxx} [Acta math. 1940].
The  proof goes beyond the scope of the present chapter
since it would require a rather extensive detour into the 
theory about subharmonic functions
and properties of logarithmic potential functions in the complex plane.
For   open cubes in
${\bf{R}}^3$ where $y=(y_1,y_2)$
the situation becomes  more involved and it appears
that no definite answers are known about the
properties of the limit function $f$ under the condition that
the first order derivatives of $F$ belong to
$L^2(\square)$.
So apart from cases  where standard estimates from 
the theory about singular integrals are available,
questions of a more refined nature related to Sobolev inequalities remain to
be investigated.
\medskip

\noindent
{\bf{4.2.8 Easier cases.}}
Avoiding the  case $p=2$ we impose the condition that
the first order derivatives of $F$ belong to $L^p$ for some $p>2$.
In that case the proof of Hardy and Littewood entails that
a continuous limit function $f$ exists in (i).
In fact, this follows from the observation that the  functions
$h$ and $g$ belong to $L^r$ for each $r<2$.
With $p>2$ we can take
$r$ such that
\[
r^{-1}+p^{-1}=1
\]
and Hšlder's inequality entails that
\[
||F*h||_\infty\leq ||F||_p\cdot ||h||_r
\]
Approximating $F$ by a sequence of
test-functions whose $L^p$-norms are uniformly bounded by that of
$F$
the reader should verify that
$F$ extends to a continuous function
along $x=0$ in (i). Moreover, 
the maximum norm
of $f(y)$ is bounded by a constant times
the sum of the $L^p$-norms of the first order derivatives of
$F$.




\bigskip


\centerline {\bf{4.2.9 Sobolev's integral formula.}}
\bigskip

\noindent
Here follows a  crucial  construction from Sobolev's original work.
Let $n\geq 2$ and consider a real-valued function $F(x)=F(x_1,\ldots,x_n)$
in ${\bf{R}}^n$ which is zero outside a
ball of radius $K/2 $ centered at the origin for some positive number $K$.
We shall perform some constructions which
lead to
a certain integral formula for $F$ in (*) below.
\medskip

\noindent
Choose a $C^\infty$-function
$b(r)$ on the real line where
$b(r)=1$ if $0\leq r\leq 2K$ and zero if $r> 3K$.
Let $\omega$ denote points on the unit sphere $S^{n-1}$.
For each fixed $\omega$ we set
\[ 
F_\omega(x)=
\int_0^\infty\, \frac{\partial}{\partial r}(
F(x-r\omega)\cdot b(r)\, dr
\]
A partial integration shows that the right hand side becomes
\[ 
F(x)+\int_0^\infty\, 
F(x-r\omega)\cdot b'(r)\, dr
\]
Now $b'(r)\neq 0$ only occurs if $2K<r<3K$ so if
$|x|\leq K/2$ it is clear that the last integral is zero because $F$
vanishes when
$|x|>K/2$.
Hence the following hold for
each $\omega\in S^{n-1}$:
\[
F_\omega(x)= F(x)\quad\colon |x|\leq K/2\tag{1}
\]
Notice that
\[
 \frac{\partial}{\partial r}(
F(x-r\omega)=\sum_{j=1}^{j=n}\, \omega_j\cdot 
\frac{\partial}{\partial x_j}( F(x-rw)\tag{i}
\]
Hence (1)  entails that
\[
F(x)=\frac{1}{|S^{n-1}|}\cdot 
\sum_{j=1}^{j=n}\int_{S^{n-1}}\int_0^\infty\, 
\,\omega_j\cdot \frac{\partial}{\partial x_j}( F(x-rw)
\cdot b(r)\, dr d\omega\quad\colon\, |x|\leq K/2
\]
where the volume of the unit sphere was introduced.
Define the functions $h_1,\ldots,h_n$ in
${\bf{R}}^n$ expressed in polar coordinates $r,\omega$ by
\[ 
h_j(r\omega)=\frac{1}{|S^{n-1}|}\cdot \frac{b(r)\cdot \omega_j }{r^{n-1}}
\]
With $y=r\omega$ as a variable in
${\bf{R}}^n$ it follows that
\[
F(x)= \sum_{j=1}^{j=n}\int\, \frac{\partial}{\partial x_j}( F(x-y)\cdot h_j(y)\,dy
\quad\colon\, |x|\leq K/2\tag{*}
\]
\medskip

\noindent
{\bf{Remark.}}
Above (*) which can be regarded as an "averaged Taylor formula", and
since the right hand side is a sum
of convolution integrals one can apply 
results about singular integrals.
Notice that
the right hand side in (xx) entails that
that the  restrictions of the $h$-functions
to every sphere
$\{y|=\delta\}$
have mean-value zero. 
The $h$-functions have by construction compact support and
are $C^\infty$ outside the origin.
The denominator $r^{n-1}$ which appears in (x) causes singularities.
However,  the $h$-functions  are integrable
and behave better  than  Riesz kernel where
$r^n$ appears in the denominator.
Let us finally remark  that it
is a "matter of taste" how to 
describe regularity of $F$ 
when the partial derivatives belong to $L^p$ for some $p>1$.
Hšlder continuity of some order $\alpha>0$
is one possibility. Another is to express regularity via
properties of the Fourier transform of $F$ which often is used
in PDE-theory.
More precsely, let
$\{\phi_j(\xi)\}$ be the Fourier transforms of the partial derivatives.
Fourier's inversion formula entails that
the convolution integrals which appear in (*) are given by
\[
x\mapsto (\frac{1}{(2\pi)^n}\cdot \int \, e^{\{i\langle x,\xi\rangle}\cdot
\phi_j(\xi)\cdot \widehat{h}_j(\xi)\,  d\xi
\]
\medskip

\noindent
{\bf{4.2.10 Passage to higher order derivatives.}}
Passing to second order derivatives of $F$
one gets similar averaged Taylor formulas as in (*). For example, one finds
doubly indexed functions $\{h_{jk}\}$
such that
\[
F(x)= \sum\sum\,\int\, \frac{\partial^2}{\partial x_j\partial x_k}( F(x-y)\cdot h_{jk}(y)\,dy
\]
This time the compactly supported $h$-functions
are of the form
\[
\frac{\rho(x)}{|x|^{n-2}}
\]
where $\rho$ are test-functions. Moreover, the Fourier transforms
of the doubly indexed $h$-functions
decay like $\xi|^{-2}$ as $|\xi|\to +\infty$.
Passing to the case of $n$:th order derivatives
it follows that $F$ is represented as a sum of convolution integrals
of
$n$:th order partial derivtives times
compactly supported distributions whose Fourier transforms
decay like
$|\xi|^{-n}$.
Applying the cited result in (¤ 4.1. xx) one arrives at the following:
\medskip

\noindent
{\bf{4.2.11 Theorem.}}
\emph{Let $\square$ be a fixed bounded cube in
${\bf{R}}^n$. Then there exists a constant
$C$ whuch only depends on the size of
$\square$Ê and $n$ such that the following hold for
$n$-times differentiable functions supported by
$\square$:}
\[
||F||_{\text{BMO}}\leq \sum \, ||\frac{\partial^\alpha (F)}{\partial x^\alpha}||_1
\]
\emph{with the sum extened over multi-indices of length $\leq n$.}
\medskip


\noindent
{\bf{4.2.11 Smooth extensions to  boundaries.}}
Consider a bounded open set
$\Omega$  in
${\bf{R}}^n$ with a smooth boundary, i.e. of class
$C^\infty$. Let $p\geq 1$ and $k$ is a positive integer
which yields the largest integer $m$ such that
\[ 
\frac{1}{m}<k-\frac{n}{p}
\]

\medskip
CHECK


\medskip

\noindent
{\bf{4.2.3 Theorem.}}
\emph{Let $F(x)$ be a function in $\Omega$
whose partial derivatives up to order $k$
belong to $L^p(\Omega)$.
Then every derivative of order $\leq m$ exists and extends to a
continuous function  on the closure of $\Omega$.}
\medskip









\bigskip














\centerline {\bf{5. The complex Hilbert transform}}.
\medskip


\noindent
Identify the complex $z$-plane with
the 2-dimensional real $(x,y)$-space.
Now we have the Hilbert space
$L^2({\bf{C}})$ whose vectors are complex-valued and
square integrable functions in the $(x,y)$-plane.
If $g$ is a continuously differentiable function with
compact support there exists a limit
\[
G(z)=\lim_{\epsilon\to 0}\, \iint_{|z-\zeta|>\epsilon}\, 
\frac{g(\zeta)}{(z-\zeta)^2}\, d\xi d\eta\tag{5.1}
\]
for every $z\in {\bf{C}}$.
In fact, using Stokes theorem one has
\[
G(z)=\iint\,\frac{\frac{\partial g}{\partial \zeta}(\zeta)}{z-\zeta}
d\xi d\eta
\]
where the last integral exists since
$\frac{\partial g}{\partial \zeta}$ is a continuous function with compact support and
$(z-\zeta)^{-1}$
is locally integrable in the $(\xi,\eta)$-space
for each fixed $z$.
The complex Hilbert transform is defined by the linear operator:
\[ 
T_g(z)= \frac{1}{\pi}\, G(z)
\] 
It turns out that
$T$ is an isometry with respect to the $L^2$-norm, i.e. 
\[
\iint\, |T_g(z)|^2\, dxdy=
\iint\, |g(z)|^2\, dxdy\quad\colon g\in C_0^1({\bf{C}})\tag{5.2}
\]
There are several proofs of (5.2). One relies upon the Fourier transform
and Parseval's theorem which is exposed in ¤ xx.
Another proof employs an abstract reasoning and goes as follows:
Let
$\mathcal H$ be a Hilbert space
and $\Phi$ us a subset of vectors
with the property that
the subspace of vectors in
$\mathcal H$ of the form
\[
c_1\phi_1+\ldots+c_k\phi_k\quad\colon 
\langle\phi_j,\phi_i\rangle=0\colon j\neq i
\]
is dense
in $\mathcal H$. Thus, we assume that finite linear combinations of pairwise
orthogonal $\Phi$-vectors is dense.
Let us now
consider a 
linear operator
$T$ on
$\mathcal H$ 
such that the following   hold:
\[
||T(\phi)||= ||\phi||\quad\colon \phi\in \Phi\tag{*}
\]
\[
\langle\phi_1,\phi_2\rangle=0\implies
\langle T(\phi_1),T(\phi_2)\rangle=0
\quad\colon\, \phi_1,\phi_2\in \Phi
\tag{**}
\]

\medskip

\noindent
{\bf{Exercise}}
Show that (*)-(**) imply that $T$ is an isometry, i.e.
$||T(g)||= ||g||$  for every
$g\in\mathcal H$.

\medskip

\noindent
Apply the  result above  to the
complex Hilbert transform where
$\Phi$ is  the family of vectors in $L^2({\bf{C}})$
given
by characteristic functions of dics in
${\bf{C}}$. It  is clear that  this family satisfies
the density condition above.
Now we study the
action by the Hilbert transform on such  functions.
Let $z_0\in{\bf{C}}$ and $r_0>0$ be given and 
$\phi$  is the characteristic function
of the disc of radius $r_0$ centered at $z_0$.
\medskip

\noindent
{\bf{5.1 Proposition.}}
\emph{One has $T_\phi(z)=0$ when $|z-z_0|< r_0$ while}
\[
T_\phi(z)=\frac{r_0^2}{(z-z_0)^2}\quad \colon
|z-z_0|>r_0
\]

\medskip

\noindent
\emph{Proof.}
After a translation we can take $z_0=0$ and via a dilation of the scale
reduce the proof to the case $r_0=1$.
If $|z|>1$
we have
\[
T_\phi(z)=\frac{1}{\pi}\iint_D \, \frac{d\xi d\eta}{(z-\zeta)^2}
=\frac{1}{\pi z^2}\iint_D \frac{d\xi d\eta}{(1-\zeta/z)^2}
\]
Expand 
$(1-\zeta/z)^{-2}$ in a power series of $\zeta$ and notice that
\[
\iint_D \,\zeta^m\, d\xi d\eta=0\quad\colon m=1,2,\ldots
\]
Then we see that $T_\phi(z)= z^{-2}$.
There remains to show that
$|z|<1$ gives $T_\phi(z)=0$.
To prove this we use the differential 2-form
$d\zeta\wedge d\bar\zeta$ and there remains to show that
\[
\lim_{\epsilon\to 0}\, 
\iint_{D_\epsilon}\frac{d\zeta\wedge d\bar\zeta}{(z-\zeta)^2}=0\tag{i}
\]
where  $D_\epsilon= D\setminus \{|\zeta-z|\leq \epsilon\}$.
Now $\partial_\zeta((z-\zeta)^{-1})=(z-\zeta)^{-2}$
and Stokes theorem gives
(i) if
\[
\int_{|\zeta|=1}\, \frac{d\bar\zeta}{z-\zeta}-
\lim_{\epsilon\to 0}\, \int_{|\zeta-z|=\epsilon}\, \frac{d\bar\zeta}{z-\zeta}=0
\]
In the first integral we use the
series expansion 
$(z-\zeta)^{-1}=-\sum_{n=0}^\infty \, \zeta^{-n-1}\cdot z^n$
and get a vanishing since
\[
\int_{|\zeta|=1}\, \zeta^{-n-1}\, d\bar\zeta=0\quad\colon n=0,1,\dots
\]
The verification that the limit as $\epsilon\to 0$
in the second integral vanishes is left to the reader.


\medskip


\noindent
The Proposition  entails that
\[
||T(\phi)||^2=
r_0^4\cdot \iint_{|z|>r_0}\, \frac{dxdy}{|z|^4}=
r_0^4\cdot 2\pi\int_{r_0}^\infty \,\frac{dr}{r^3}=\pi\cdot r_0^2
\]
Since $||\phi||^2=\pi\cdot r_0^2$ we conclude that
$||T(\phi)||= ||\phi||$.
The verification that (**)  holds when
$\phi_1,\phi_2$ are characteristic functions of disjoint discs
is left as an exercise.

\bigskip

\centerline {\bf{6. The Kakutani-Yosida theorem.}}
\bigskip

\noindent


\noindent
Let $(\Omega,\mathcal B,\mu)$
be a probability space  defined in [Appendix: Measure theory].
Consider a real-valued function
$P$ defined on the product set 
$\Omega\times\mathcal B$ with 
the following two properties:
\[ 
t\mapsto P(t,E)
\quad\text{is a bounded measurable function for each}\,\,\, E\in\mathcal B\tag{*}
\]
\[
E\mapsto P(t,E)
\quad\text{is a probability measure
for each fixed }\,\,\, t\in\Omega\tag{**}
\]
When (*-**) hold one refers to $P$ as a transition function.
Inductively we get the sequence $\{P^{(n)}\}$:
\[ 
P^{(n+1)}(t,E)=\int_\Omega\, P^{(n)}(s)\cdot dP(s,E)
\]
It is clear that 
$\{P^{(n)}\}$ yield  new transition  functions.
The probabilistic interpretation is that
one has a Markov chain
with independent increments.
More precisely,
if 
$E$ and $S$ are two sets in
$\mathcal B$ 
and 
$n\geq 1$.
then
\[
\int_S\, P^{(n)}(t;E)\cdot d\mu(t)
\]
is the probability that
the random walk which starts at some  point in $E$
has arrived to some  point in  $S$ after $n$ steps.
One says that the 
transition function $P$ yields a stationary
Markov process if
there exists a finite family of disjoint
subets $E_1,\ldots,E_m$ in $\mathcal B$
and some $\alpha<1$ and a constant $M$
such that the following hold:
First, for each $1\leq i\leq m$ one has:
\[ 
P(t,E_i)= 1 \quad\colon t\in E_i\tag{1}
\]
Next, if $\Delta= \Omega\setminus E_1\cup\ldots\cup E_m$ then
\[ 
\sup_{t\in S}\, P^{(n)}(t,\Delta)\leq M\cdot \alpha^n
\quad\colon \, n=1,2,\ldots\tag{2}
\]
\medskip

\noindent
{\bf{Remark.}}
One refers to $\Delta$ as the disippative part of $\Omega$
and $\{E_i\}$ are  the ergodic kernels of the process.
Since $\alpha<1$  in (2) the probabilistic  interpretation
of (2) is that as $n$ increase then
the disippative part is evacuated
with high probability while the Markov process 
stays inside every ergodic kernel.
A sufficient condition for a
Markov  process to be  stationary is as follows:
Denote by $\mathfrak{B}$ the Banach space of
complex-valued and bounded
$\mathcal B$-measurable
functions on the real $s$-line.
Now $P$ gives a 
linear operator $T$ which sends $f\in \mathfrak{B}$
to
the function
\[ 
T(f)(x)= \int_\Omega\ f(s)\cdot dPx,ds)
\]
\medskip

\noindent
{\bf{Theorem.}}
\emph{The Markov process is stationary 
if there exists a 
triple $\alpha,n,K$
where $K$ is a compact
operator on $\mathfrak{B}$, $0<\alpha<1$ and $n$ some positive integer such that
the operator  norm}
\[ 
||T^n+K||\leq \alpha\tag{*}
\]
\medskip

\noindent
{\bf{Remark.}}
The proof relies upon   general facts 
about
linear operators on Banach spaces. 
First $\mathfrak{B}$ is a commutative Banach algebra with
a maximal ideal space
denoted by $S$ and  the Gelfand transform enable us to identify
$\mathfrak{B}$ with
the space of continuous complex-valued functions on
the compact Hausdorff space $S$, Now 
$T$ can be regarded as  a positive linear operator on $C^0(S)$.
The  crucial step in the proof is to show that (*)
entails that
the spectrum of $T$ consists of a finite set of points on
 the unit circle together with a compact subset
 in a disc of radius $<1$.
 Moreover, for  each
 isolated point $e^{i\theta}\in \sigma(T)$
 the corresponding eigenspace is finite dimensional.
 Each  such eigenvalue corresponds to an ergodic kernel and when
the eigenspace has dimension $m\geq 2$, the
 corresponding ergodic kernel, say $E_1$, has a further decomposition into
 pairwise disjoint subsets $e_1,\ldots,e_m$
where  the process moves in a cyclic manner between these
sets, i.e. 
\[
\int_{e_{i+1}}\, P(s,e_i)=1\quad 
\colon 1\leq  i\leq m
\quad\text{where we put}\quad
 e_{m+1}= e_1
 \]
 

\medskip

\noindent 
Above we desfribed the probabilistic consequences of
the theorem. 
The proof 
is given in ¤ xx after we have
introduced Neumann's resolvent operators and 
establish a result about positive operators on
Banach spaces of continuous functions on compact topological
spaces which gives the theorem above as a special case.





\newpage

\centerline{\bf{Basic facts in functional analysis.}}

\bigskip


\noindent
Baire's category theorem for complete metric spaces
is used in several proofs below. The detailed proofs
of the results below are  given in ¤ xx.


\medskip

\centerline{\bf{A. Three basic principles.}}


\bigskip

\noindent
{\bf{A.1 The Banach-Steinhaus Theorem.}}
\emph{Let $X$ be a vector space equipped with a complete norm
$||\cdot||^*$. Then, every stronger norm is equivalent to
the complete norm, i.e. if
$||\cdot||$ is a norm for which there is a constant $C$ such that}
\[
||x||^*||\leq C\cdot ||x||
\]
\emph{hold for all vectors $x\in X$, then there is a constant $C_1$ such that}
\[
||x||\leq C_1\cdot ||x||^*
\]


\noindent
{\bf{A.2 The Open Mapping theorem.}}
Let $T\colon X\to Y$ be a bounded linear operator
where $Y$ is a Banach space and $X$ some normed space.
Assume that $T$ is surjective, i.e.  $T(X)=Y$.
If $y\in Y$ we set
\[
||y||=\min_{x\in X}\, ||x||\,\colon y=Tx\tag{i}
\]
 It is easily seen that this gives a norm on $Y$.
 Let $||\cdot ||^*$ be the complete norm
 on $Y$.
 The construction in (i) gives
 \[
 ||y||^*\leq ||T||\cdot ||y||
 \]
where
$||T||$ is the operator norm of $T$.
Now the Banach-Steinhaus theoren gives a constant $C_1$
such that every vector $y$ in $Y$ norm $<1$ is 
the image of a vector $x$ in $X$ with norm 
$\leq C_1$.
In particular $T$  maps the open unit ball in $X$ to an open set in $Y$
which
is convex and contains the origin,


\bigskip

 





\noindent
{\bf{A.3 The Hahn-Banach theorem.}}
Let $X$ be a real vector space.
A function $\rho\colon X\to {\bf{R}}^+$ is
subadditive and positively homogeneous
if the following hold for
each pair $x_1,x_2$ in $X$ and every non-negative real number $s$:
\[
\rho(x_1+x_2)\leq 
\rho(x_1)+
\rho(x_2)\quad\colon \rho(sx_1)= s\cdot \rho(x_1)
\] 
Using the axiom of choice one verifies that
if $X_0$ is a subspace and
$\lambda_0\colon  X_0\to {\bf{R}}$ is
a linear functional  such that
\[
\lambda_0(x_0)\leq \rho(x_0)\quad\colon x_0\in X_0
\] 
then there exists a 
linear functional
$\lambda$ on $X$ which extends $\lambda_0$ and
\[
\lambda(x)\leq \rho(x)\quad\colon x\in X
\] 







\medskip

\noindent
{\bf{A.4 Example.}}
One is often confronted with severe 
difficulties in specific cases. Consider for example a positive integer 
$N$ and let $\mathcal P_N$ denote  the $(N+1)$-dimensional
real vector space of polynomials  $P(t)$ of degree $\leq N$.
Define a linear functional  $\lambda_0$ on $\mathcal P_N$
by
\[
\lambda_0(P)=\sum_{\nu=1}^{\nu=M} \, c_\nu\cdot P(t_\nu)\tag{i}
\]
where $\{t_\nu\}$ and
$\{c_\nu\}$ are real numbers.
We can identify $\mathcal P_N$ with a subspace of
$X=C^0[0,1]$ where
$C^0[0,1]$ is the vector space of real-valued and continuous functions on
the unit interval $\{0\leq t\leq 1\}$.
On $X$ we get a $\rho$-function via the maximum norm, i.e.
\[ 
\rho(f)= \max_{0\leq x\leq 1}\, |f(x)|
\]
Next, there exists a unique smallest constant $C>0$ such that
\[
|\lambda_0(P)|\leq C\cdot \rho(P)\quad\colon P\in  \mathcal P_N
\]
Notice that $C$ exists even in the case when some
of the $t$-points in (i) are outside $[0,1]$.
By the result above we can extend $\lambda_0$ to a linear functional
$\lambda$ on $X$ and  the Riesz representation theorem  gives
a real-valued Riesz measure $\mu$ on $[0,1]$ such that
\[
\lambda_0(P)=\int_0^1\, P(t)\cdot d\mu(t)
\quad\colon P\in \mathcal P_N
\]
and at the same time the total variation of $\mu$ 
is equal to the constant $C$ above.
However, to determine $C$ and to find
$\mu$ requires a further analysis which leads to a
rather delicate problem in optimization thoery.
Already a case when
$M=1$ and we take $t_1=2$ and $c_1=1$
is highly non-trivial. Here we find a constant $C_N$ for each
$N\geq 2$ such that
\[ 
|P(2)|\leq C_N\cdot \rho(P)\quad
\quad\colon P\in \mathcal P_N
\]
I do not know how to determine $C_N$ and how to find
a Riesz measure $\mu_N$ whose total variation is $C_N$ while
\[
P(2)=\int_0^1\, P(t)\cdot d\mu_N(t)\quad\colon P\in \mathcal P_N
\]
\bigskip

\noindent
{\bf{A.5 Separating hyperplanes.}}
The Hahn-Banach theorem employs the axiom of choice
and is therefore not very constructive.
So one often asks for more explicit proofs.
An example is the separation of a pair of disjoint closed and convex
sets $K$ and $K_1$ in a normed vector space. So here 
there exists some $\delta>0$ such that
\[
\min_{x,y}\,||x-y||=\delta\tag{i}
\]
where the minimum is taken over pairs $x\in K$ and $y\in K_1$.
Using the Hahn-Banach theorem one verifies that
there exists a continuous linear functional
$x^*$ of norm one such that
\[
\max_{x\in K}\, x^*(x)+\delta\leq \min_{x\in K_1}\, x^*(x)\tag{ii}
\]
In specific situations one often wants to find $x^*$ in some constructive manner.
When
$X={\bf{R}}^n$ is an euclidian space we 
can get $x^*$ as follows.
By a translation we may assume that the origin belongs to $K$
and let us for a moment also assume that $K$ contains a small open ball
of radius $\delta$ centered at $x=0$.
In this case the convexity of $K$ easily entails that the interior is
a dense open set. In fact, if
$p\in\partial K$ and $0<s<1$ the convexity 
implies that $K$ contains the open ball of radius 
$(1-s)\delta$ centered at $sx$. Since $||x-sx||= (1-s)||x||$
tends to zero as $s\to 1$ we conclude that the interior is dense.
Next, let $p\in\partial K$ and denote by $\mathcal H(p)$ the family 
of  hyperplanes $\pi$ in $X$ such that 
$K$ is placed in one of the closed half-spaces
separated by the affine hyperplane $\{p\}+\pi$.
\medskip

\noindent
{\bf{Exercise.}}
Show with the aid of a figure that the hyperplane
\[
\{p\} ^\perp=\{ x\in X\,\colon \langle x,p\rangle=0\}
\]
belongs to $\mathcal H(p)$.
\medskip

\noindent
Next, let $K_1$ be another closed convex set
which gives the positve $\delta$ in (i).
Since bounded sets in $X$ are relatively compact, 
there exists a point $p\in K$ such that
\[
\delta=\min_{y\in K_1}\, ||p-y||
\]
\medskip

\noindent
{\bf{Exercise.}}
With $p$ as above we 
define $x^*$ by
\[
x^*(x)= -\frac{1}{||p||}\cdot \langle x,p\rangle
\]
Then $x^*$ has  unit norm and we leave it to the reader to check that
(ii) holds for this linear functional which by construction has unit norm.
Finally, show also how to get $x^*$ in (ii) when
the two convex sets are not fat.


















\newpage


\centerline{\bf{B. Dual spaces and weak topologies.}}
\medskip

\noindent
Let  $X$ be a normed
complex vector space.
The dual $X^*$ consists of ${\bf{C}}$-linear
maps $x^*\colon X\to {\bf{C}}$ which
satisfy
\[ 
|x^*(x)|\leq C\cdot ||x||
\]
for a constant $C$ which depends on the given
linear functional $x^*$.
The smallest $C$ is the norm of $x^*$ and in this way
$X^*$ becomes a normed vector space.
The Hahn-Banach theorem
entails that
\[
||x||=\max_{x^*\in S^*}\, |x^*(x)|
\] 
where  $S^*$ is the family of vectors in 
$X^*$ with unit norm.
Now we introduce other topologies on $X$.
To begin with a  Banach space
$X$ is equipped with the weak topology. Here
a sequence
$\{x_n\}$ converges weakly to a limit vector
$x$ if
\[
\lim_{n\to\infty}\, x^*(x_n)= x^*(x)\quad\colon\, x^*\in X^*
\]
To indicate weak convergnce we use $w$ as a subscript and write
\[
\lim_{n\to\infty}\, x_n\overset{w}\to x
\]
 {\bf{B.0 The weak-star topology on $X^*$}}.
It is
defined by the family of semi-norms
$\{\rho_X\colon\, x\in X\}$ where
\[ 
\rho_x(x^*)= |x^*(x)|
\] 
for each pair $\in X$ and $x^*\in X^*$.
Equipped with  the weak-star topology,  $X^*$ becomes  a locally convex vector space.
Recall Tychonoff's  theoremt in topology
which asserts that the product of compact spaces is compact.
It follows  that if $S^*$ is the unit sphere in $X^*$, 
then 
the weak-star topology restricted to $S^*$ gives 
a compact topological  space.
Next, starting from the normed space $X^*$ one constructs 
the bi-dual $X^{**}$ which by definiton is the dual of $X^*$.
If $x\in X$ we get the vector $\mathfrak{i}_X(x)\in X^{**}$ defined by
\[
\mathfrak{i}_X(x)(x^*)= x^*(x)\quad\colon\, x^*\in X^*
\]
The Hahn-Banach theorem entails that
the mapÊ$x\to \mathfrak{i}_X(x)$
is an isometry, i.e. 
\[ 
||x||= ||\mathfrak{i}_X(x)||
\]
 One refers to $\mathfrak{i}_X\colon X\to X^{**}$ as the bi-dual embedding.
A Banach space $X$ is reflexive if
$\mathfrak{i}_X$ is surjective 
In ¤ xx we prove that
 $X$Êis reflexive if and only if the unit sphere
 $S$ in $X$ is compact
 with respect to the weak topology which was defined above.
 An example of a reflexive Banach space is
 $\ell^p$ where $1<p<\infty$.
 The vectors are sequences of complex numbers
 $x_1,x_2,\ldots$ for which
 \[
 ||x||_p= \bigl(\sum_{\nu=1}^\infty\, |x_\nu|^p\bigr)^{\frac{1}{p}}<\infty
 \]
Hšlder's inequality entails
 that   the dual space of $\ell^p$ is $\ell^q$ where
$q= \frac{p-1}{p}$, and
from which it is clear that
$\ell^p$ is reflexive.
An example of a non-reflexive Banach space is
${\bf{c}}_0$
whose vectors are complex sequences $\{x_n\}$ for which
$x_n\to 0$, and
the norm is defined by
\[
||x||=\max_n\, |x_n|
\]
Here the dual space is $\ell^1$ and the bi-dual
${\bf{c}}_0^{**}=\ell^\infty$ 
where $\ell^\infty$ is the Banach space whose
vectors consist of
bounded sequences of complex numbers.
\bigskip


\noindent
{\bf{B.1 The Krein-Smulian theorem.}}
Articles by these authors
from the years around 1940 contain
a wealth of results.
A major theorem
from their work goes as follows.
Let $X$ be a Banach space and
$X^*$ its dual.
Each $x\in X$ gives a linear function
$\widehat {x}$ on $X^*$ defined by
\[
\widehat{x}(x^*)= x^*(x)
\]
By definition the weak-star topology
on $X^*$ is  the weakest topology so that 
$\widehat{x}$ becomes a continuous function for every
vector $x\in X$.
It means that a fundamental  system of open neighborhoods of
the origin in $X^*$ consists of
sets
\[
U(x_1,\ldots,x_N;\delta)=
\{x^*\colon\, |x^*(x_\nu)|<\delta\}
\]
Next we construct the 
\emph{bounded weak-star topology}
on $X^*$. Here one takes the open unit
ball $S^*$ of vectors in $X^*$ with norm
$<1$. If $n$ is a positive integer we get
the ball $nS^*$ of vectors with norm $<n$.
A subset $V$ of  $X^*$ is open in the bounded weak-star
topology if and only
if
the interesections $V\cap nS^*$ are weak-star open
for every positive integer $n$.
In this way we get a locally convex topology on $X^*$
whose corresponding
topological vector space is denoted 
by
$X^*_{bw}$,  while $X^*_w$ denotes
the locally convex vector space when
$X^*$ is equipped with the weak topology.
Notice that the family of open sets in
$X^*_{bw}$
contains the open sets in
$X^*_w$, i.e. the bounded weak-star topology is stronger.
Examples show that the topologies in general are not equal.
Next, let 
$\lambda$ be  a linear functional on $X^*$ which is continuous with
respect to the weak-star  topology.
This gives by
definition  a finite set
$x_1,\ldots,x_M$ in $X$ such that
if $|x^*(x_\nu)|<1$ for each $\nu$, then
$\lambda(x^*)|<1$.
This  implies that the 
subspace of $X^*$ given by
the common kernels of
$\widehat{x}_1,\ldots\widehat{x}_M$
contains the $\lambda$-kernel and   linear algebra gives
an $M$-tuple of complex numbers
such that
\[
\lambda=\sum\, c_\nu\cdot \widehat{x}_\nu
\]
We can express this by saying that 
the dual space of $X^*_w$
is equal to $\widehat{X}$, i.e. every linear functional on $X^*$ which is continuous 
with respect to the
weak-star topology is of the form
$\widehat{x}$ for a unique $x\in X$.
Less obvious is the following:

\medskip

\noindent
{\bf{B.1.1. Theorem.}}
\emph{The dual of $X^*_{bw}$ is equal to $\widehat{X}$.}
\medskip

\noindent
We prove this in ¤ x.
For the moment we only remark that an essential ingredient in the proof
employs a 
result due to Stefan Banach which goes as follows:
Consider the Banach space
${\bf{c}}_0$ whose vectors consist of
sequences $\{x_1,x_2,\ldots\}$ of complex numbers
where $x_n\to 0$ as $n\to \infty$
and the norm 
\[
||x||= \max_{n\geq 1}\, |x_n|
\]
Banach proved that the dual space
${\bf{c}}^*_0$ is $\ell^1$ whose vectors
are complex sequences $\{y_n\}$ where
$\sum\, |y_n|<\infty$.
\bigskip


\noindent
{\bf{B.2 Bounded operators  with closed range.}}
Consider  a bounded linear operator
$T\colon X\to Y$ where $X$ and $Y$ are Banach spaces.
Then there
exists  the adjoint linear operator
\[ 
T^*\colon Y^*\to X^*
\]
where a continuous linear functional
$y^*$ on $Y^*$ is mapped into the vector 
\[
T^*(y^*)(x)= y^*(Tx)\quad\colon x\in X
\]
\noindent
{\bf{B.2.1. Theorem.}}
\emph{$T$ has closed range if and only if $T^*$ has a closed range.}

\medskip

\noindent
{\bf{Remark.}}
Thus, the subspace $T(X)$ is closed in $Y$ if and only if
$T^*(Y^*)$ is closed in $X^*$.
We prove  this result in ¤¤¤ using the Krein-Smulian theorem.


\medskip

\noindent
{\bf{B.3 A result by Pietsch }}.
The  result below 
illustrates the usefulness of
regarding various weak topologies.
Let $T$
be a bounded linear operator on a Banach space $X$ and
$\{p_n(z)\}$ is  a sequence of polynomials
with complex coefficients
where $p_n(1)=1$  for each $n$. We get the bounded operators
\[
 A_n=p_n(T)\quad\colon\, n=1,2,\ldots
\]
Suppose that
\[
\lim_{n\to \infty}\, A_n(x)- A_n(T(x)) \overset{w}\to 0\tag{i}
\]
hold for every $x\in X$
where the superscript $w$ mens that we regard weak convergence.
In addition to (i) we assume that
for every $x\in X$, the sequence $\{A_n(x)\}$
is relatively compact with respect to the weak topology.
Under these two assumptions  one has:
\medskip


\noindent
{\bf{B.3.1 Theorem.}}
\emph{For every $x\in X$ the sequence
$\{A_n(x)\}$ converges weakly to a limit vector
$B(x)$ where $B$ is a bounded linear operator on $X$. Moreover
$B$ is an idempotent, i.e. $B=B^2$
and one has a direct sum decomposition}
\[ 
X=\overline{(E-T)(X)}\, \oplus  \ker(E-T)
\]
\emph{where $E$ is the identity operator on $X$
and 
$\overline{(E-T)(X)}$ is the closure taken in the norm topology of
the range of $E-T$. Finally,
$\ker(E-T)$ is equal to the range $B(X)$ while
$\ker(B)=\overline{(E-T)(X)}$.}

\medskip
\noindent
The proof  in ¤ xx and gives an instructive lesson of
"duality methods" while infinite dimensional normed spaces are
considered.






\bigskip

\centerline{\bf{C. Compact metric spaces.}}
\medskip

\noindent
To avoid possible confusion we
recall the notion of  compactness on a metric space
which goes back to Heine and Bolzano.
Let $S$ be a metric  space where $d$ is the distance function.
A closed subset $K$ is totally bounded in  Heine's sense
if there to every $\epsilon>0$ exists
a finite subset
$\{x_1,\ldots,x_N\}$ in $K$ such that
$K$ is covered by the union of the open balls
$B_\epsilon(x_k)= \{ x\colon\, d(x,x_k)<\epsilon\}$.
A wellknown fact  whose verification is left
to the reader asserts that a
closed subset $K$ is totally bounded
if and only if it is compact in the sense of Bolzano, i.e.
every sequence $\{x_n\}$ in $K$ contains at least one convergent subsequence.
\medskip

\noindent
{\bf{C.1 On finite dimensional normed spaces.}}
Let $E$ be a finite dimensional subspace of some
dimension $n$ with a basis $e_1,\ldots,e_n$ and let
$||\cdot||$
be  a norm on $E$. On the unit sphere $S^{n-1}$ in
${\bf{R}}^n$ we get the continuous function
\[
\phi(x_1,\ldots,x_n)=
||x_1e_1+\ldots+x_ne_n||
\] 
Since it is everywhere positive there exist    constants
$0<a<A$ such that the range
$\phi( S^{n-1})$ is contained in $[a,A]$.
From this we conclude that
\[
a\cdot \sqrt{\sum\, |x_k|^2}\leq
||x_1e_1+\ldots+x_ne_n||\leq
A\cdot \sqrt{\sum\, |x_k|^2}
\]
Hence the induced norm-topology on $E$ is equivalent to
the euclidian topology  expressed via  a chosen basis in $E$.
It means that
on a finite dimensional vector space
every pair of norms are equivalent  in the sense that they
are compared as above by some constant as above.
\medskip



\noindent
{\bf{A special construction.}}
Let $X$ be a vector space of  infinite dimension
equipped with a norm
and
consider an infinite sequence
$\{x_1,x_2,\ldots\}$
of linearly independent vectors in $X$.
To each $n\geq 1$ we get the $n$-dimensional subspaces
\[
 E_n=\{x_1,\ldots,x_n\}
 \]
generated by the first $n$ vectors.
 For a fixed $n$ 
and every vector  $y\in X\setminus E_n$ we set
 \[
 d(y;E_n)= \min_{x\in E_n}\, ||y-x||
 \]
 

\noindent
{\bf{C.2  Exercise.}}
Use (C. 1) to show that
there exists at least one vector $x_*\in E_n$ such that
\[
d(y;E_n)= ||y-x_*||
\]
Next, construct via an induction over
$n$ a sequence of vectors $\{y_n\}$ where
each
$||y_n||=1$ with the following properties. For every
$n$ one has
\[
E_n=\{y_1,\ldots,y_n\}\quad\colon\,
d(y_{n+1},E_n)= 1
\]
In particular $||y_n-y_m||=1$ when $n\neq m$ which entails that
the 
sequence $\{y_n\}$ cannot contain a convergent subsequence and
hence the unit ball in $X$ is non-compact.
Thus, only finite dimensional normed spaces have a unit ball which is compact with
respect to the metric defined by the norm.
\medskip

\noindent
{\bf{C.3 A direct sum decomposition.}}
Let $X$ be a normed space and $V$ some finite dimensional subspace
of dimension $n$. Choose a basis $v_1,\ldots,v_n$ in $V$ and
via the Hahn-Banach theorem we find an $n$-tuple $x_1^*,\ldots,x_n^*$
such that
$x_j^*(v_k)$ is Kronecker's delta-function.
Set
\[ 
W=\{x\in X\,\colon x_\nu^*(x)=0\, \colon\,1\leq\nu\leq n\}
\]
Then $W$ is a closed subspace of $X$ and we have a direct sum decompotion
\[
X=W\oplus\, V
\]
Thus, every finite dimensional subspace of a normed space $X$ has 
a closed complement.
On the other hand a  closed infinite dimensional subspace
$X_0$ has in general not  closed complenent.

\bigskip



\centerline{\bf{D.  Locally convex topologies and Frechet spaces.}}

\bigskip


\noindent
A pseudo-norm on a complex vector space $X$ is  a map $\rho$ from $X$ into
the non-negative real numbers
with the properties
\[
\rho(\alpha\cdot x)= |\alpha|\cdot \rho(x)
\quad\colon
\rho(x_1+x_2)\leq \rho(x_1)+\rho(x_2)\tag{D.1}
\]
where $x,x_1,x_2$ are vectors in
$X$ and $\alpha\in {\bf{C}}$. If 
 $X$ is a real vector space  the left hand side  equality is only required
 for real scalars $\alpha$.
 Notice that (0.0.1) entails that
 the kernel of  $\rho$
 is a subspace of $X$ denoted by  $\text{Ker}(\rho)$.
 If it is reduced  to  the zero vector one says that 
$\rho$ is a  norm.
Next, a subset $K$ in $X$ is convex
if $x_1,x_2$ in $K$ implies 
that the line segment
\[
[x_1,x_2]= \{ sx_1+(1-s)x-2\,\colon 0\leq s\leq 1\}\subset K
\]
If $\rho$ is a pseudo-norm
we put
\[ 
\mathcal B_\rho=\{ x\,\colon\, \rho(x)\leq 1\}
\]
This is  a convex set  with
the property that
\[
x\in \mathcal B_\rho\implies
e^{i\theta}\cdot x\in \mathcal B_\rho\quad\colon\, 0\leq\theta\leq 2\pi\tag{i}
\]
Moreover
$\mathcal B_\rho$ 
is absorbing which 
means that for
every
vector $x\in X$ there exists some
real $s>0$ such that
$s\cdot x\in  \mathcal B_\rho$.
\medskip

\noindent
{\bf{D.2 A converse result.}}
Denote by $\mathcal K_X$
the family of convex, symmetric 
and absorbing subsets $K$   with the property that 
\[
K=e^{i\theta}\cdot K\quad\colon
0\leq \theta\leq 2\pi\tag{ii}
\]
For a real vector space one only imposes  symmetry with respect to the origin, i.e.
that $K=-K$.
\medskip

\noindent
{\bf{Exercise.}}
Show that (ii) gives 
a pseudo-norm
$\rho$
defined by
\[ 
\rho(x)=\inf_{s>0} \, x\in s\cdot K\tag{iii}
\]
and verify the inclusions
\[  
s\cdot \mathcal B_{\rho}\subset K\subset
B_\rho
\quad\colon\, \forall\, \,\,0<s<1
\]



\noindent
{\bf{D.3 Locally convex topologies.}}
Let $\{\rho_\alpha\}$ be a family of semi-norms on
$X$
such that
\[
\bigcap\, \text{Ker}(\rho_\alpha)\, =\{0\}\tag{i}
\]
One defines a topology 
whose   open
neighborhoods of
the origin are of the form:
\[
U=\cap \,\,\{\rho_\alpha<\epsilon\}\tag{ii}
\] 
where
$\epsilon>0$ are arbitrary small and
the intersection is taken over a finite set $\alpha$-indices.
Finally, a set $\Omega$ in $X$ is open if there
for every $x\in \Omega$ exists some finite
$\rho$-family and $\epsilon>0$ such that
$x+U\subset \Omega$ with $U$ as in (ii).
One refers to a
locally convex topology defined by the
$\rho$-family. Notice that   (i) implies that the topology is
Haussdorf.
\medskip

\noindent
{\bf{D.4 Frechet spaces.}}
Let
 $\{\rho_n\}$ be a denumerable sequence of pseudo-norms
where (i)  holds above. Put
\[ 
d (x,y)=\sum_{n=1}^\infty\, 2^{-n}\cdot 
\frac{\rho_n(x-y)}{1+\rho_n(x-y)}\tag{iii}
\]
It is clear $d$
is a metric which
defines the
$\{\rho_n\} $-topology. If 
every Cauchy-sequence with respect to $d $ converges to a vector in
$X$ one refers to   
$X$ as a Frechet space 
\medskip

\noindent
{\bf{D.5 Theorem.}}
\emph{Let $X$ be a Frechet space 
with the Frechet metric $d$.
Then every 
$d$-closed convex set $K$ in the family $\mathcal K_X$
contains an open neighborhood of the origin.}
\medskip

\noindent
\emph{Proof.}
To each integer $N\geq 1$ we have the closed set
$F_N= N\cdot K$.
Since $K$ is absorbing
the union of these $F$-sets is equal to $X$.
Baire's theorem applied to the complete metric space
$(X,d)$ yields some $N$ and $\epsilon>0$ such
that $F_N$ contains
an open ball of radius $\epsilon$ centered at some
$x_0\in F_N$. If $d(x)<\epsilon$ we write
\[ 
x=\frac{x_0+x}{2}-\frac{x_0-x}{2}
\]
Now $F_N$ contains $x_0+x$ and $x_0-x$. By symmetry it also contains
$-(x_0-x)$ and the convexity entails that
$x\in F_N$.
Hence one has  the implication
\[
d(x,0)<\epsilon\implies x\in N\cdot K
\]
Now the $d$-metric is defined by 
a sequence of pseudo-norms
$\{\rho_n\}$. Choose an integer $M$ where $2^{-M}<\epsilon/2$.
The construction of $d$  shows that
if
$\rho_n(x)<\frac{\epsilon}{2M}$ hold for $1\leq n\leq M$, then
$d_\rho(x)<\epsilon$. Hence (i) gives
\[ 
\max_{1\leq n\leq M}\, \rho_n(x)<
\frac{\epsilon}{2M}\implies x\in N\cdot K
\]
After a  scaling one has
\[
\max_{1\leq n\leq M}\, \rho_n(x)<
\frac{\epsilon}{2M N}\implies x\in K
\]
The reader can check that there exists $\epsilon_*>0$ such that
\[
d(x,0)<\epsilon_*\implies
\max_{1\leq n\leq M}\, \rho_n(x)<
\frac{\epsilon}{2M N}
\]
and conclude that  $K$ contains an
open neighborhood of  the origin.


\medskip

\noindent
{\bf{D.6 The open mapping theorem.}}
Consider  a pair of
Frechet spaces $X$ and $Y$ and let
\[
u\colon X\to Y
\]
be  a continuous linear and surjective map.
Then $u$ is an open mapping, i.e.
for every $\epsilon>0$
the $u$-image of the $\epsilon$-ball with respect to
the Frechet metric on $X$ contains
an open neighborhood of the origin in $Y$.
The proof is left as an exercise to the reader
where the hint is to employ Baire's theorem
and similar arguments as in the proof of Theorem 0.1.5.

\medskip


\noindent
{\bf{D.7 Closed Graph Theorem.}}
Let $X$ and $Y$ be Frechet spaces and 
$u\colon X\to Y$ is 
a linear map. Set
\[ 
\Gamma(u)=\{ (x,u(x)\}
\]
and suppose it is a closed subspace of the Frechet space $X\times Y$.
Under this hypothesis it follows that
$u$ is continuous.
\medskip

\noindent
{\bf{D.8  Exercise.}}
Verify the closed graph theorem. A hint is that
one has  the bijective linear map
from $X$ onto $\Gamma(u)$ defined by
$x\mapsto  (x,u(x))$.
Since $\Gamma(u)$ is closed in
$X\times Y$ it is a Frechet
space so the  mapping above
is open and from this one easily checks 
that $u$ is continuous.
\medskip



\centerline
{\bf{Dual spaces.}}
\medskip


\noindent
Let 
$X$ be a locally convex  real vector space
where $\{\rho_\alpha\}$ is a family  of pseudo-norms  defining the topology
on $X$. 
The
dual space $X^*$ consists of  continuous linear forms
on $X$.
The continuity  for  a vector $x^*\in X^*$
means that there exist
a finite family of pseudo-norms
$\{\rho_\alpha\}$ and a constant $C$
such that
\[
|x^*(x)|\leq C\cdot \sum\, \rho_\alpha(x)\quad\colon\, x\in X
\]
If  $x^*\in X^*$ and $a$Êis a real number
one gets the closed
half-space
 \[
 H(x^*;a)= \{x\colon\, x^*(x)\leq a\}
 \]


\noindent
The result below appears in 
the article
\emph{La dualitŽ dans les espaces vectorielles} [Ann. Ecoles Sup. 1942]
by DieudonnŽ.

 \medskip

\noindent
 {\bf{D.9  Theorem.}}
 \emph{Every  closed and convex
 subset $K$ in  $X$ which is not equal toÊ$X$
 is the intersection of closed half-spaces.}
 \medskip
 
 
 \noindent
 \emph{Proof.} 
Clearly it suffieces to prove the result when
$K$ contains the origin.
If $\xi\in X\setminus K$ the closedness gives an open set
$U$  and some $0<s<1$ such that
$K\,\cap \, \{s\cdot \xi\}+U=\emptyset$. By translations this entails that
the convex set $\widehat{K}= K+U$ does not contain $s\cdot \xi$.
To this convex set we construct the associated
function $\rho$ as in (ii) from (D.2) and (iii) entials that
\[
\rho(s\cdot \xi)\geq 1\implies \rho(\xi)= s^{-1}>1
\]
Next,
the Hahn-Banach theorem    gives
a linear funtional $\lambda$ on $X$ such that
$\lambda(\xi)=s^{-1}$ while
$|\lambda(x)\leq \rho(x)$ for each $x\in \widehat{K}$. Since
the open set $u$ is contained in
$\widehat{K}$ it follows that
the functional $\lambda$ is continuous and
from the above $K$ is contained in the half-space
$H(\lambda:1)$ while $\xi$ is outside this half-space. Since
$\xi\in X\setminus K$ was arbitrary the proof is finished.



















\bigskip





\centerline{\bf{D.10  Support functions of convex sets.}}
\medskip


\noindent
In ¤¤ we prove
a theorem  due to Hšrmander  
which describes
support functions of closed and convex subsets in a  locally convex
vector space. Hšrmander's result   goes as follows.
Let $X$ be a real vector space, i.e.
the elements are vectors and
each $x\in X$ yields vectors $s\cdot x$ for every real number
$s$.
A  pseudo-norm on $X$ is a sub-additive real-valued map  $\rho$
such that
$\rho(s\cdot x)=|s|\cdot \rho(x))$
hold for every real number $s$ and every $x\in X$.
Let $\mathcal F=\{\rho_\alpha\}$ be a family of
pseudo-norms indexed by a set which may be finite or infinite.
One associates the space
$X^*_\mathcal F$ of  linear functionals $\lambda$ on $X$
for which there exists some finite family
$\{\rho_{\alpha_1},\ldots,\rho_{\alpha_n}\}$ in $\mathcal F$ 
and a constant $C$ such that
\[
 |\lambda(x)|\leq C\cdot \sum_{\nu=1}^{\nu=n}\,
 \rho_{\alpha_\nu}(x)
\]
for every $x\in X$.
To each pseudo-norm $\rho_\alpha$ 
in the family and $\epsilon>0$ we put
\[ 
U(\alpha;\epsilon)=
\{\lambda\in X_\mathcal F^*\,\colon
|\lambda(x)|<\epsilon\cdot \rho_\alpha(x)\, x\in X\}
\]
The weak-star topology on  $X^*_\mathcal F$
arises as follows: A subset $\Omega$ in $X^*_\mathcal F$ 
is weak-star open if there for each $\lambda_0\in \Omega$ exists
a finite family of pseudo-norms
$\{\rho_{\alpha_\nu}\}$  and some $\epsilon>0$ such that
\[
\lambda_0+\cap\, U(\alpha_\nu;\epsilon)\subset\Omega
\]
Next, denote by
$\mathcal S(X^*_\mathcal F)$ the family of functions
$g$ on $X^*_\mathcal F$ with values in $(-\infty,+\infty]$
such that the following hold for
each pair $\lambda_1,\lambda_2$ in $X_\mathcal F^*$ and every real $s>0$:
\[ 
g(\lambda_1+\lambda_2)\leq 
g(\lambda_1)+g(\lambda_2)
\quad\colon\, 
g(s\lambda)=s\cdot g(\lambda)
\]
where the rule is that 
$+\infty+a=+\infty$ for every real number $a$.
It is easily seen that
every convex subset $K$ in $X$ gives rise to such a $g$-function
defined by
\[
\mathcal H_K(\lambda)=
\max_{x\in K}\, \lambda(x)
\]
With these notations one has:

\medskip

\noindent
{\bf{D.11 Theorem.}}
\emph{Let $g$ be a function in
$\mathcal S(X^*_\mathcal F)$ which
is lower semi-contoinuous in the weak-star topology,  i.e. the sets
$\{\lambda\,\colon g(\lambda)>a\}$ are
weak-star open for every real $s$. Then there exists a convex set
$K$ such that
$g=\mathcal H_K$.}



\bigskip



\centerline
{\bf{E. Non-linear calculus on Banach spaces.}}
\bigskip

\noindent
Ordinary differential calculus in ${\bf{R}}^n$  can be extended to
Banach spaces. We present 
some results 
due to Clarkson, 
Beurling and Lorch.
Let $X$ be a
Banach space $X$ and 
to each $\epsilon>0$ we
denote by $\mathcal F(\epsilon)$ 
the set of
of pairs of unit vectors $x,y$ in $X$ such that
\[
||x+y||\geq 2-\epsilon
\]
Following  Clarkson's article \emph{Uniformly convex spaces} in
[ Trans. Amer.Soc. 40: 1936]
we give
\medskip

\noindent
{\bf{E.1 Definition.}}
\emph{A Banach space $X$ is uniformly convex
if}
\[ 
\lim_{\epsilon\to 0}\, \max_{x,y\in \mathcal F(\epsilon)}\,||x-y||=0
\]
Next, 
a uniformly  convex
Banach space
$X$ is differentiable if
\[
\lim_{a\to 0}\, \frac{||p+ax||-||p||}{a}
\]
exists for evey pair of non-zero vectors $x,p$ in $X$.
During the passage to the
limit
$a$ can be both $>0$ or $<0$.
From now on 
$X$ is uniformly convex and differentiable.
Let $S$ be the unit sphere in $X$, i.e. the set of vectors of unit norm. 
Similarly, $S^*$ is the unit sphere
in $X^*$.
With  $p\in X$  kept fixed the differentiablity gives a map
from $X$ into ${\bf{R}}$ defined by
\[ 
x\mapsto D_p(x)=\lim_{a\to 0}\, \frac{||p+ax||- ||p||}{a}\tag{i}
\]
With these notations the following result was proved by Clarkson in
the cited article:

\medskip

\noindent
{\bf{E.2 Theorem.}}
\emph{For each $p\in S$ the 
function $x\mapsto D_p(x)$ is a linear functional of unit norm and
$p\mapsto D_p$ is a bijective map between
$S$ and $S^*$. Finally, $D_p(p)=1$ and for
every
$x^*\in S^*\setminus\{D_p\}$ one has}
\[
|x^*(p)|<1
\]
\medskip

\noindent
{\bf{E.3  Non-linear duality.}}
Clarkson's result is proved in ¤ xx
and  can be  used to construct non-linear duality maps.
Consider
a continuous and strictly increasing function
$\phi(r)$ defined on $\{r\geq 0\}$ where
$\phi(0)=0$ and $\phi(r)\to +\infty$ as $r\to \infty$.
Each $p\in S$ gives the Clarkson  vector $D_p\in S^*$.
For each non-zero vector  $x\in X$ we put 
\[ 
\mathcal D_\phi (x)=\phi(||x||)\cdot D_{||x||^{-1}\cdot x}
\]
Next, if $V\subset X$ is a closed subspace we set
\[
V^\perp=\{x^*\in X^*\,\colon x^*(V)=0\}
\]
\medskip

\noindent
{\bf{E.4 The Beurling-Lorch Theorem.}}
\emph{For each closed subspace $V$ of $X$ which is not equal to the whole 
space $X$,
and every pair of vectors  $x\in X$ and $y\in X^*$ the intersection}
\[
\mathcal D_\phi(V+x)\,\cap\, (C^\perp+y)
\] 
\emph{consists of a  single vector in $X^*$.}
\medskip


\noindent
The result above is  proved in ¤ xx. 
 
\bigskip

\centerline {\bf{F. The logarithmic potential.}}

\medskip




\noindent
General results in functional analysis 
are not always
sufficient for more precise conclusions.
A typical problem is to describe the range of
a bounded linear operator $T\colon X\to Y$
from a Banach space into another.
A favourable case is when
$T(X)$ is a closed subspace of $Y$. But in general one
encounters situations where the closedness fails to hold.
Consider as an example the Banach space $C^0[0,1]$
of complex-valued
and continuous functions on the closd unit interval and 
the bounded linear operator
 \[
 L_g(x)= \int_0^1\, \log\, \frac{1}{|x-t|}\cdot g(t)\, dt
 \]
whose  operator norm  is bounded above by
 \[
 \max_{0\leq x\leq 1}\,\int_0^1\, \log \frac{1}{|x-t|}\, dt
 \]
Lebesgue  theory teaches that
\[
\lim_{\delta\to 0}\,\max_{x_1,x_2}\,
,\int_0^1\, \bigl[\log\, \frac{1}{|x_1-t|}-
 \frac{1}{|x_2-t|}\bigr| \, dt=0
 \] 
 where the maximum for each $\delta>0$ is taken over
 pairs of points in $[0,1]$ for which $|x_1-x_2|\leq\delta$.
 This entails that $L$ maps the unit ball in
 $C^0[0,1$ to 
 an equi-continuous family of functions.  
 The Arzela-Ascoli theorem implies that $L$ is
 a compact operator.
 It turns out that $L$ is injective and has a 
dense range. 
See ¤ xx for the proof  which includes an inversion formula for $L$
which therefore 
describes the range of $L$.
But as we shall see this description is rather involved.
It turns out that the range contains all $C^2$-functions and is therefore
dense in
$C^0[0,1]$ but its precise description is not easy
to
give.
Next,
 general results about compact operators imply  that
the spectrum of $L$ is discrete.
Here $\sigma(L)$ contains the origin
and outside the origin
the spectrum is a discrete subset of
${\bf{C}}$
with a sole cluster point at zero.
Moreover. general facts  from 
Fredholm's theory sbout integral equations show that the spectrum is
real and since the kernel function 
$\frac{1}{|x-t|}$ is everywhere postive, each
eigenvalue $\mu$ for 
which there exists a non-trivial eigenfunction $g$ satisfying
\[
L_g(x)= 
\mu\cdot g(x)
\]
is $>0$.
One often prefers to replace the $\mu$-numbers by
$\mu^{-1}$ which gives
a discrete non-decreasing
sequence of eigenvalues 
$0<\lambda_1\leq \lambda_2\leq \ldots$
and associated eigenfunctions $\{g_n\}$
such that
\[
L_{g_n}(x)=\lambda^{-1}_n\cdot g_n(x)
\]
\medskip


\centerline {\bf{G. A result about spectral values.}}
\bigskip

\noindent
Consider
a linear operator $\mathcal K$ defined by
\[
\mathcal K_g(x)=\int_0^1\, \frac{K(x,y)}{|x-y|^\alpha}\cdot g(y)\, dy
\]
where $0<\alpha<1$ and
$K(x,y)$ is continuous and symmetric, i.e.
$K(x,y)= K(y,x)$ hold when  $\{0\leq x,y\leq 1\}$.
We  regard $\mathcal K$ as a linear operator on
the Hilbert space $L^2[0,1]$. The Cauchy-Schwartz inequality shows
that it is a bounded operator whose
operator norm is estimated above by:
\[
||\mathcal K||\leq \max_{0\leq x\leq 1}\, \int_0^1\, \frac{|K(x,y)|}{|x-y|^\alpha}\, dy
\]
If $0<\alpha<1/2$
the kernel function
$K(x,y)= \frac{K(x,y)}{|x-y|^\alpha}$ is square integrable over
the unit square $\{0\leq x,y\leq 1\}$
which means that
$\mathcal K$ is a Hilbert-Schmidt operator.
In this case Hilbert proved in his text-book from 1904
that
the eigenvalues are real, and  the eigenfunctions
normalised with $L^2$-integrals of unit norm 
give an orthonormal basis for $L^2(0,1]$.
 The extension to the case
 $1/2\leq \alpha<1$ was treated  by Carleman in his thesis from 1916, and again
the spectrum  consists real numbers with a sole cluster point at
 zero. Moreover,  the eigenfunctions give an orthonormal basis
 in $L^2[0,1]$.
It turns
out that the set of
eigenvalues, which  are repeated when the eigenspaces have
dimension $\geq 2$
is a quite ample set.
One has for example:

\medskip

\noindent
{\bf{G.1 Theorem.}}
\emph{If there exists some interval $(a,b)$ in
$[0.1]$ such that
$K(x,x)>0$ when $a<x<b$, then}
\[
\sum\, \bigl(\frac{1}{\lambda_n^+}\bigr)^{\frac{1}{1-\alpha}}=+\infty
\]
\emph{where the sum is taken over positive eigenvalues.}

\medskip

\noindent
{\bf{Remark.}}
This theorem appears
in Carleman's  article
\emph{Sur la distribution des valeurs singuliŽrs
d'une classe des noyaux infinis} [Arkiv fšr matematik, astronomi och fysik. Vol. 12]
and a 
proof is given in ¤ xx.

 
\newpage








\centerline {\bf{¤ 0. Neumann's  resolvent operators}}
\medskip



\noindent
{\bf{Introduction.}}
The less expericenced reader may prefer to first
study basic material in the special chapters.
But is it essential to become familiar with unbounded densely defined linear operators
and their bounded resolvent operators.
So we expose the crucial facts about this and remark that the
major result appears in Theorem 0.xxx
where analytic function theory is used to
perform an operational calculus using resolvent operators.
\medskip


\noindent
{\bf{0.1 The class $\mathcal I(X)$.}}
Let $X$ be a Banach space.
Denote by
$\mathcal I(X)$ the classs of bounded linear operators
$R$ on $X$ with the property that
$R$ is injective and the range
$R(X)$ is a dense subspace of $X$.
We do not exclude the possibility that
$R$ is surjective.
Each such operator
$R$ gives  a densely defined
operator $T$ whose domain of defintion
$\mathcal D(T)= R(X)$.
Namely, if $x\in R(X)$ the injectivity of $R$ gives a unique
vector
$\xi\in X$ such that
$R(\xi)=x$ and we set
\[
T(x)=\xi\tag{i}
\]
It means that the composed operator $T\circ R=E$, where
$E$ is the identity operator on $X$.
It is also clear that
\[ 
R\circ T(x)=x\quad\colon x\in\mathcal D(T)
\]
Next, the bounded operator $R$ has a finite operator norm
$||R||$ and (i) entails that
\[
||x|||\leq ||R||\cdot ||T(x)||\tag{ii}
\]
Thus, with $c= ||R||^{-1}$ one has
\[
||T(x)||\geq c\cdot ||x|||\quad\colon x\in\mathcal D(T)\tag{iii}
\]
\medskip

\noindent
{\bf{The graph $\Gamma(T)$}}.
It is by definition the subset of $X\times X$ given by
$\{(x,Tx)\,\colon x\in\mathcal D(T)\}$.
The construction of $T$ gives
\[
\Gamma(T)=\{(Rx,x)\colon x\in X\}
\]
Since
$R$ is a bounded inear operator it is clear  that
the last set os closed in $X\times X$, i.e.
$\Gamma(T)$ is closed which we express by saying that
$T$ is a densely defined and closed
linear operator on $X$.
The inequality (iii) shows that $T$ is injective and
since
\[ 
T(Rx))=x\quad\colon x\in X
\]
the range of $T$ is equal to $X$.
\medskip


\noindent
{\bf{A converse result.}}
Assume that $T$ is a densely defined and closed operator
such that
(iii) holds and in addition the range of $T$ is dense in $X$.
It turns out that this gives the equality
\[
T(\mathcal D(T))=X\tag{1}
\]
For if $y\in X$ the density of the range  gives
a sequence
$\{x_n\}$ in $\mathcal D(T)$ such that
\[
\lim_{n\to \infty}\, ||T(x_n)-y||=0\tag{2}
\]
Now
\[
||x_n-x_m||\leq c^{-1}\cdot ||T(x_n)-T(x_m)||
\] 
and (2) entails that
$\{T(x_n)\}$ is a Cauchy sequence. Since $X$ is a Banach space
it follows that
$\{x_n\}$ converges to a limit vector $x$.
Now $\Gamma(T)$ is closed which implies that 
$(x,y)$ belongs to the graph, i.e. $x\mathcal D(T)$ and $T(x)=y$
which proves (1).
\medskip


\noindent
{\bf{Exercise.}}
Let $T$ be densely defined and closed where
(xx) holds and $T(\mathcal D(T))=X$. 
Show that there exists a unique bounded operator
$R\in\mathcal I(X)$
such that $T$ is the attached operator in ¤ xx.

\bigskip





\centerline
{\bf{0.2 Spectra of densely defined operators.}}
\medskip




\noindent
Let $T$ be a densely defined and closed linear operator.
Each complex number
$\lambda$ gives  the densely defined
operator $\lambda\cdot E-T$.
We say that
$\lambda$ is a resolvent value of $T$
if
$\lambda\cdot E-T$ is injective and there exists 
a positive constant $c$ such that
\[
||\lambda\cdot x-T(x)||\geq c\cdot ||x||
\]
The set of resolvent values is denoted by
$\rho(T)$.
Put
\[
\sigma(T)={\bf{C}}\setminus \rho(T)
\]
which by definition
is  the spectrum of $T$. 
Next,  each
$\lambda\in\rho (T)$ the construction in (0.1)  gives a unique bounded operator
$R_T(\lambda)\in\mathcal I(X)$. So here
\[
(\lambda\cdot E-T)\circ R_T(\lambda)(x)=x
\] 
and since $\mathcal D(T)= \mathcal D(\lambda\cdot E-T)$
it follows that the range of $R_T(\lambda)$ is equal to $\mathcal D(T)$
for every resolvent value.
\medskip


\noindent
{\bf{0.2.1 Definition.}}
\emph{Tbe bounded operators
$\{R_T(\lambda)\,\colon\,\lambda\in \rho(T)\}$
are called Neumann's resolvent operators of $T$.}

\medskip

\noindent
{\bf{An example.}}
Let $X$ be the Hilbert space $\ell^2$ whose vectors are  complex sequences
$\{c_1,c_2,\ldots\}$ for which $\sum\ |c_n|^2<\infty$.
We have  the dense subspace $\ell^2_*$ vectors such that
$c_n\neq 0$ only occurs for finitely many integers $n$.
If $\{\xi_n\}$ is an arbitrary sequence of complex numbers
there exists the densely defined operator $T$ on $\ell^2$
which
sends every sequence  vector $\{c_n\}\in \ell_*^2$ to
the vector $\{\xi_n\cdot c_n\}$.
If $\lambda$ is a complex number 
the reader may check that
(i) holds in (0.0.1) if and only if
there exists a  constant $C$ such that
\[
|\lambda-\xi_n|\geq C\quad\colon n=1,2,\ldots\tag{v}
\]
Thus, $\lambda\cdot E-T$ has a bounded left inverse if and ony if
$\lambda$ belongs to the open complement of the closure of the
set
$\{\xi_n\}$ taken in the complex plane.
Moreover,   if (v) holds then
$R_T(\lambda)$ is the bounded
linear operator on $\ell^2$
which sends $\{c_n\}$ to 
$\{\frac{1}{\lambda-\xi_n}\cdot c_n\}$.
Since
every closed subset of ${\bf{C}}$
is equal to the closure of a denumerable set of points our
construction  shows that the spectrum of a 
densely defined
operator $\sigma(T)$ can be an arbitrary closed set in
${\bf{C}}$. 

\medskip


\noindent
\centerline{\bf{0.3 Neumann's equation.}}

\medskip


\noindent
Lwet $T$ be closed and  densely defined.
Assume that
$\rho(T)\neq\emptyset$.
The fundamental equation below
was discovered by  Neumann:
\medskip


\noindent
\emph{For each pair 
$\lambda\neq\mu$  in $\rho(T)$ the operators 
$R_T(\lambda)$ and $R_T(\mu)$ commute
and}
\[
R_T(\mu)R_T(\lambda)=\frac{R_T(\mu)-R_T(\lambda)}{\lambda-\mu}\tag{*}
\]


\noindent
\emph{Proof.}
Notice that
\[
(\mu\cdot E-T)\cdot \frac{R_T(\mu)-R_T(\lambda)} {\lambda-\mu}
=
\]
\[
\frac{E}{\lambda-\mu}-(\mu-\lambda)\cdot\frac{R_T(\lambda)}{\lambda-\mu}-
(\lambda\cdot E-T)\cdot \frac{R_T(\lambda)}{\lambda-\mu}=R_T(\lambda)\tag{i}
\]
Multiplying to the left by
$R_T(\mu)$
gives (*) and at the same time this proves
that the resolvent operators commute.

\medskip


\centerline {\bf{0.4 Neumann series.}}
\medskip


\noindent
If  $\lambda_0\in\rho(T)$  we
construct the operator valued series
\[
S(\zeta)= R_T(\lambda_0)+ \sum_{n=1}^\infty
(-1)^n\cdot \zeta^n\cdot R_T(\lambda_0)^{n+1}\tag{1}
\]
It is clear that (1)
converges in the Banach space of bounded linear operators when
\[
|\zeta|<\frac{1}{||R_T(\lambda_0)||}
\]
Moreover we see that
\[ 
(\lambda_0+\zeta-T)\cdot S(\zeta)=
(\lambda_0-T)\cdot S(\zeta)+\zeta S(\zeta)=E\tag{2}
\]
where the last equality follows via the series expansion (1).
Hence
\[
S(\zeta)=R_T(\lambda_0+\zeta)
\] 
give resolvent operators.
Thjs oroves that
the set $\rho(T)$ is open. Moreover, the
 operator-valued  function
$\lambda\mapsto R_T(\lambda)$ is an
analytic function of the complex varaible $\lambda$ in
defined in $\rho(T)$.
If $\lambda\in \rho(T)$ we can pass to therimit as 
$\mu\to \lambda$ in Neumann's equation
and conclude that the complex derivative is given by
\[
\frac{d}{d\lambda}(R_T(\lambda)=-R^2_T(\lambda)\tag{**}
\]
Thus, Neumann's resolvent operator satisfies a specifiic differential equation for
every densely defined and closed operator $T$
with a non-empty resolvent set.

\medskip



\noindent
{\bf{0.5 The position of $\sigma(T)$.}}
Assume that $\rho(T)\neq\emptyset$.
For a oair of resolvent values of $T$ we
can  write Neumann's equation in the form
\[
R_T(\lambda)(E+(\lambda-\mu)R_T(\mu))= R_T(\mu)\tag{1}
\]
Keeping $\mu$ fixed we conclude that
$R_T(\lambda)$ exists if and only if
$E+(\lambda-\mu)R_T(\mu))$ is invertible. This gives 
the set-theoretic equality
\[
 \sigma(T)= \{\lambda\,\colon \frac{1}{\mu-\lambda}\in
\sigma(R_T(\mu))\} \tag{0.5.1}
 \]

 
 \noindent
Hence one  recovers $\sigma(T)$ via the spectrum of
any given  resolvent operator. Notice that (0.5.1) holds  even
when
the open component
of $\sigma(T)$ has several connected components.

\medskip

\noindent
{\bf{0.5.2 Example.}}
Suppose that $\mu=i$ and that 
$\sigma(R_T(i))$ is contained in a circle
$\{|\lambda+i/2|=1/2\}$.
If $\lambda\in\sigma(T)$ the inclusion (0.0.5.1) gives some
$0\leq\theta\leq 2\pi$ such that 
\[
\frac{1}{i-\lambda}=-i/2+ 1/2\cdot e^{i\theta}\implies
1-i\cdot e^{i\theta}=\lambda(e^{i\theta}-i)
\]
The last equation entails that
\[
\lambda=\frac{2\cdot \cos \theta}{|e^{i\theta}-i|^2}
\]
and hence $\lambda$ is real.
\medskip

\noindent
{\bf{0.5.3 The case when resolvent operators are compact.}}
Let $T$ be such that
$R_T(\lambda_0)$ is a compact operator for some
resolvent value. We assume of course that
the Banach space $X$ is not finite dimensional.
In ¤¤ we shall learn that the spectrum of a compact operator
always contains zero and outside the origin the spectrum is a discrete set
with a sole cluster point at the origin.
From (xxx) it follows that
$\sigma(T)$ is a discrete set in
${\bf{C}}$, i.e. its intersection with
every disc
$\{|\lambda|\leq R\}$ is finite.
\bigskip

\noindent
{\bf{0.5.4 Exercise.}}
In ¤ xx we shall learn that if $S$ is a compact operator
then $S\circ  U$ and $U\circ S$ are compact for every bounded
operator $U$.
Apply this in Neumann's equation (xx) to conclude that
if one resolvent operator
$R_T(\lambda_0)$ is  compact, then all resolvent operators of $T$ are compact.
 
\bigskip



\centerline{\bf{0.5.5 Adjoint operators and closed extensions.}}
\medskip


\noindent
Let $T$ be densely defined. 
But for the monent we do not assune that its is closed.
In the dual space $X^*$ we have   the family 
of  vectors $y$ for which   there exists a constant
$C(y)$ such that
\[
|y(Tx)|\leq C(y)\cdot ||x||\quad\colon x\in\mathcal D(T)\tag{i}
\]
It is clear that the set of such $y$-vectors is a subspace of $X^*$.
Moreover, when (i) holds the density of $\mathcal D(T)$
gives  a unique vector 
$T^*(y)$ in $X^*$ 
such that
\[
y(Tx)= T^*(y)(x)\quad\colon x\in\mathcal D(T)\tag{ii}
\]
One refers to $T^*$ as the adjoint operator of $T$ whose
domain of definition is denoted by
$\mathcal D(T^*)$.







\medskip


\noindent
{\bf{Exercise.}}
Show that the graph of $T^*$ is closed in
$X^*\times X^*$.
However,
$\mathcal D^*(T)$
is in general not a dense subspace of $X^*$.
See ¤ xx for an example.



\bigskip

\noindent
{\bf{ Closed extensions.}}
Let $T$ be  densely defined.
There may exist  closed operators $S$
with the property that
\[
\Gamma(T)\subset \Gamma(S)
\]
When this holds
we refer to
$S$ as  a closed extension of $T$. Notice that
the inclusion above is strict if and only if
$\mathcal D(S)$ is strictly larger than
$\mathcal D(T)$.

\medskip

\noindent
{\bf{Exercise.}}
Use the density of
$\mathcal D(T)$ to show that 
\[ 
T^*= S^*
\]
hold for every closed extension $S$ of $T$.
\medskip

\noindent
{\bf{The case when
$\mathcal D(T^*)$ is dense.}}
Let $T$ be densely defined and assume that its adjoint has a dense domain of definition.
In this situation the following holds:


\medskip




\noindent
{\bf{0.5.6 Theorem.}}
\emph{If $\mathcal D(T^*)$ is dense then there exists
a closed operator $\widehat{T}$ whose graph is the closure of
$\Gamma(T)$.}
\medskip

\noindent
\emph{Proof.}
Consider the graph 
 $\Gamma(T)$
and let 
$\{x_n\}$ and $\{\xi_n\}$
be two sequences in $\mathcal D(T)$ which both converge to a point
$p\in X$ while 
$T(x_n)\to y_1$ and $T(\xi_n)\to y_2$ hold 
for some pair $y_1,y_2$. We must rove that $y_1=y_2$.
To achieve this we take some
$x^*\in \mathcal D(T^*)$ which gives
\[
x^*(y_1)= \lim \,x^*(Tx_n)= \lim\,T^*(x^*)(x_n)= T^*(x^*)(p)
\]
In the same way we get $x^*(y_2)=T^*(x^*)(p)$. 
Now the density of $\mathcal D(T^*)$ gives $y_1=y_2$
which proves that
the closure of $\Gamma(T)$ is a graphic subset of $X\times X$
and gives the closed   operator $\widehat{T}$
with 
\[
\Gamma(\widehat{T})=
\overline{\Gamma(T)}
\]
\bigskip


\noindent
{\bf{ The case when $X$ is reflexive.}}
Assume this and
let $T$ be densely defined and closed and suppose in addition
that $T^*$ also is  densely defined. 
Now we can construct the adjoint of $T^*$ which is denoted by $T^{**}$.
Since $X$ is reflexive it follows that $T^{**}$ is a 
closed and densely  defined operator on $X$.
If $x\in\mathcal D(T)$ and $y\in\mathcal D(T^*)$
we have the vector $\widehat{x}\in X^{**}$
and
\[
\widehat{x}(T^*(y))=T^*(y)(x)= y(T(x))
\]
From this it is clear that
$\widehat{x}\in\mathcal D(T^{**})$
and one has the equality
\[
T^{**}(\widehat{x})= T(x)
\]
Hence 
the graph of $T$ is contained in that of $T^{**}$, i.e.
$T^{**}$ is a closed extension of $T$.

\bigskip

\noindent
{\bf{0.5.7 The spectrum of $T^*$.}}
Let $X$ and $T$ be as above. Then
one has the inclusion
\[
 \rho(T) \subset \rho(T^*)\tag{*}
\]
\medskip

\noindent
\emph{Proof.}
By translations it suffices to show that if
the origin beongs to $\rho(T)$ then it also belongs to
$\rho(T^*)$. So now  the resolvent 
$R_T(0)$ exists which means  that
$T$ is surjective
and there is a constant $c>0$ such that
\[
||x||\leq c^{-1}\cdot ||Tx||\quad\colon x\in\mathcal D(T)\tag{i}
\]
Consider some
$y\in\mathcal D(T^*)$ of unit norm. Since $T$ is surjective
we find 
$x\in\mathcal D(T)$ with 
$||Tx||=1$ and
\[ 
|y(Tx)|\geq 1/2\tag{ii}
\]
Now
\[ 
y(Tx)= T^*(y)(x)\tag{iii}
\]
and from (i) we have
\[
||x||\leq c^{-1}\cdot ||Tx||= c^{-1}\tag{iv}
\]
Then (ii) and (iv) entail that 
\[ 
||T^*(y)||\geq c/2
\]
This proves that
\[ 
||T^*(y)||\geq  c/2\cdot ||y||\quad\colon y\in\mathcal D(T^*)\tag{v}
\]
Hence the origin belongs to $\rho(T^*)$ if we prove that
$T^*$ has a dense range.
If the density  fails  there exists a non-zero linear functional
$\xi\in X^{**}$ such that
\[
\xi(T^*(y))=0\quad\colon y\in\mathcal D(T^*)
\]
Since $X$ is reflexive we have $\xi=\mathfrak{i}_X(x)$ for some
vector $x$ and obtain
\[
y(Tx)=0\quad\colon y\in\mathcal D(T^*)
\]
The density of $\mathcal D(T^*)$ gives $Tx=0$ which contradicts the hypothesis that
$T$ is injective and (*) follows.
\medskip

\noindent
{\bf{The case when $X$ is a Hilbert space.}}
In this case we shall prove that
when both $T$ and $T^*$ are closed and densely defined, then one has the euality
\[
\sigma(T)\subset\sigma(T^*)
\]
We refer to  ¤ xx for the proof.

\bigskip







\centerline{\bf{0..6 Operational calculus.}}
\medskip


\noindent
Let $T$ be a densely defined and closed operator on a Banach apace $X$.
To each pair $(\gamma,f)$ where
$\gamma$ is a rectifiable Jordan
arc contained in
${\bf{C}}\setminus \sigma(T)$
and $f\in C^0(\gamma)$, there exists the bounded linear operator
\[ 
T_{(\gamma,f)}=\int_\gamma\, f(z)R_T(z)\, dz\tag{0.6.1}
\]
The integral is calculated
via a Riemann sum
where the integrand has values in the Banach space of bounded
linear operators on $X$. 
More precisely, let $s\mapsto z(s)$ be a parametrisation with respec to
arc-length. If $L$ is the arc-length of $\gamma$ we 
get Riemann sums
\[
\sum_{k=0}^{k=N-1} \, f(z(s_k))\cdot (z(s_{k+1})-z(s_k))\cdot 
(s_{k+1}-s_k)\cdot R_T(z(s_k))
\]
where $0=s_0<s_1<\ldots s_N=L$ is a partition of
$[0,L]$.
These Riemann sums converge
to a limit when
$\{\max\, (s_{k+1}-s_k\}\to 0$ with respect to the operator norm
and give the $T$-operator in (0.6.1). The triagle inequality entials that
\[
T_{(\gamma,f)}\leq L\cdot |f|_\gamma\cdot \max_{z\in\gamma}\, ||R_T(z)||
\]
where $|f|_\gamma$ is the maximum norm of $f$ on $\gamma$..
\medskip

\noindent
Neumann's equation in (0.3)
entails that
$R_T(z_1)$ and $R_T(z_2)$
commute for all pairs $z_1,z-2$ on $\gamma$. It follows that
if 
$g$ is another function in
 $C^0((\gamma)$
then  the operators $T_{f,\gamma}$
and $T_{g,\gamma}$
commute. Moreover, for each $f\in C^0(\gamma)$
the reader may verify that
the closedeness of $T$
implies that
the range of
$T_{f,\gamma}$ is contained in
$\mathcal D(T)$ and one has
\[
T_{f,\gamma}\circ T(x)= T\circ T_{f,\gamma}(x)
\quad\colon x\in \mathcal D(T)
\]


 

\medskip

\noindent
Next, let $\Omega$ be an open set of class $\mathcal D(C^1)$, i.e.
$\partial\Omega$ is a finite union of
closed differentiable Jordan curves. 
When
$\partial\Omega\,\cap \sigma(T)=\emptyset$
we construct line integrals as in (0.6.1)
for continuous functions on
the boundary.
Consider the algebra $\mathcal A(\Omega)$
of analytic functions in
$\Omega$ which extend to be continuous on the closure.
Each $f\in \mathcal A(\Omega)$
gives the operator
\[ 
T_f=
\int_{\partial\Omega}\, f(z)R_T(z)\, dz\tag{0.6.2}
\]
\medskip

\noindent
{\bf{0.6.3 Theorem.}}
\emph{The map $f\mapsto T_f$ is an algebra homomorphism from
$\mathcal A(\Omega)$ into a commutative algebra of bounded
linear operators on $X$ whose  image is  a commutative algebra of 
bounded linear operators
denoted by $T(\Omega)$.}

\medskip

\noindent
{\emph{Proof.}}
Let $f,g$ be a pair in $\mathcal A(\Omega)$.
To show that
$T_{gf}= T_f\circ T_g$
we consider a slightly  smaller open
set $\Omega_*$ which again is of class $\mathcal D(C^1)$
and each of it  bounding Jordan curve is close to one 
boundary curve in
$\partial\Omega$ and $\Omega\setminus \Omega_*$ does not
intersect $\sigma(T)$.
By Cauchy's theorem we can shift the integration to
$\partial\Omega_*$ and get
\[
T_g=
\int_{\partial\Omega_*}\, g(z)R_T(z_*)\, dz_*\tag{i}
\]
where we use  $z_*$ to indicate that integration takes place
along
$\partial\Omega_*$. Now
\[
T_f\circ T_g=
\iint_{\partial\Omega_*\times\partial\Omega}\, f(z)g(z_*)R_T(z)\circ
R_T(z_*)\, dz_*dz\tag{ii}
\]
Neumann's equation
(*) from  (0.0.3) entails that  the right hand side in
(ii) becomes
\[
\iint_{\partial\Omega_*\times\partial\Omega}\, \frac{f(z)g(z_*)R_T(z_*)}{z-z_*}
\, dz_*dz+
\iint_{\partial\Omega_*\times\partial\Omega}\, \frac{f(z)g(z_*)R_T(z)}{z-z_*}
\, dz_*dz=A+B
\tag{iii}
\]
\medskip

\noindent
Here $A$ is  evaluated
by first integrating with respect to $z$ and 
Cauchy's theorem gives
\[
f(z_*)=\frac{1}{2\pi i}\cdot 
\iint_{\partial\Omega }\frac{f(z)}{z-z_*}\quad\colon z_*\in\partial\Omega_*
\, dz
\]
It follows that
\[ 
A=\frac{1}{2\pi i}\cdot
\iint_{\partial\Omega_*\times\partial\Omega}\, f(z_*)g(z_*)R_T(z_*)\, dz_*
=T_{fg}
\]
Next, $B$ is evaluated when we first integrate with respect to $z_*$. Here
\[
\iint_{\partial\Omega}\frac{g(z_*)}{z-z_*}\quad\colon z\in\partial\Omega
\]
which entails that $B=0$ and the theorem  follows.
\medskip

\noindent

\noindent
{\bf{Spectral gap sets.}}
Let
$K$ be a compact subset
of $\sigma(T)$ 
such that
$\sigma(T)\setminus K$ is a closed
set in ${\bf{C}}$.
This implies that if $V$ is an open  neighborhood of $K$, then
there exists a relatively compact subdomain
$U\in \mathcal D(C^1)$ which contains
$K$ as a compact subset.
To every such domain $\Omega$ we can apply Theorem 0.0.6.3.
If $U_*\subset U$ for a pair of such domains
we can restrict functions in
$\mathcal A(U)$ to $U_*$
which  yields an algebra homomorphism
\[
\mathcal T(U)\to \mathcal T(U_*)
\]
Next, denote by
$\mathcal O(K)$ the algebra of germs of analytic functions
on $K$.
So each $f\in \mathcal O(K)$ 
comes from
some analytic function in a domain $U$ as above.
The resulting operator $T_U(f)$ depends on the germ $f$ only.
In fact, this follows because if
$f\in \mathcal A(U)$ and
$U_*\subset U$ is a similar 
$\mathcal D(C^1)$-domain which again contains
$K$, then
Cauchy's vanishing theorem from ¤ xxx is applied
to $f(z)R_T(z)$ in $U\setminus \bar U_*$ and entails that
\[
\int_{\partial U_*}\, f(z)R_T(z)\, dz=
\int_{\partial U}\, f(z)R_T(z)\, dz
\]
Hence there exists an algebra homorphism
from $\mathcal O(K)$ into
bounded linear operators on $X$
whose image is denoted by $\mathcal T(K)$.
The identity in $\mathcal T_K$
is denoted
by $E_K$ and called 
the spectral projection operator
attached to the compact set $K$ in
$\sigma(T)$. By this construction one has
\[
E_K=\frac{1}{2\pi i}\cdot \int_{\partial U}\, z\cdot R_T(z)\, dz
\] 
for every open domain $U$ around $K$ as above.


\medskip

\noindent
{\bf{0.0.6.4 The operator $T_K$.}} When $K$ is a compact spectral gap set of $T$
we set
\[
 T_K=TE_K
\]
This   bounded linear operator is given
by
\[
\frac{1}{2\pi i}\cdot \int_{\partial U}\, z\cdot R_T(z)\, dz
\] 
where $U$ is a domain as above containing $K$.
\medskip

\noindent
{\bf{0.0.6.4.1}} \emph{Identify
$T_K$ with a densely defined operator on
the space $E_K(X)$. Then one has the equality}
\[
\sigma(T_K)=K
\]
\emph{Proof.}
If $\lambda_0$ is outside $K$ we can choose
$U$ so that $\lambda_0$ is outside $\bar U$
and construct the operator
\[
S=\frac{1}{2\pi i}\cdot \int_{\partial U}\, \frac{1}{\lambda_0-z}\cdot R_T(z)\, dz
\]
The operational calculus gives
\[
S(\lambda_0 E_K-T)= E_K
\]
here $E_K$ is the identity operator on
$E_K(X)$ which shows that
$\sigma(T_K)\subset K$.


\bigskip


\noindent
{\bf{0.0.6.5  Discrete spectra.}}
Consider 
a spectral set  reduced to a singleton set
$\{\lambda_0\}$, i.e.
$\lambda_0$ is an isolated point in
$\sigma(T)$. The associated spectral projection is denoted by
$E_T(\lambda_0)$ and
expressed 
\[
E_T(\lambda_0)=
\frac{1}{2\pi i}\cdot \int_{|\lambda-\lambda_0|=\epsilon}\,
R(\lambda)\, d\lambda
\]
for all sufficiently small $\epsilon$.
Now
$R_T(\lambda)$ is an analytic function defined
in some punctured disc
$\{0<\lambda-\lambda_0|<\delta\}$
with  a Laurent expansion
\[
R_T(\lambda)=\sum_{-\infty}^\infty\, 
(\lambda-\lambda_0)^k\cdot B_k
\]
where $\{B_k\}$ are bounded linear operators
obtained  by residue formulas:
\[
B_k= \frac{1}{2\pi i}\cdot
\int_{|\lambda|=\epsilon}\,  
\frac{R_T(\lambda)}{(\lambda-\lambda_0)^{k+1}}\, d\lambda
\quad\colon\,\epsilon<\delta
\]

\noindent
{\bf{Exercise.}}
Show
that
$R_T(\lambda)$ is meromorphic, i.e. 
$B_k=0$ hold when $k<<0$,
if and only if there
exists a constant $C$ and some integer $M\geq 0$ such that
the operator norms satisfy
\[
||R_T(\lambda)||\leq C\cdot |\lambda-\lambda_0)^{-M}
\]
\medskip

\noindent
Suppose now that
$R_T$ has a pole of some order $M\geq 1$ which gives
an  expansion
\[
R_T(\lambda)=\sum_1^M\,
\frac{B_{-k}}{(\lambda-\lambda_0)^k}+
\sum_0^\infty\, 
(\lambda-\lambda_0)^k\cdot B_k
\]
Here $B_{-1}=E_T(\lambda_0)$ and if $M\geq 2$
the negative indexed operators satisfy
\[
B_{-k}= B_{-k}E_T(\lambda_0)\quad 2\leq k\leq M
\]
In the case of a simple pole, i.e.
when $M=1$ the operational calculus gives
\[
(\lambda_0E-T)E_T(\lambda_0)=
\lim_{\epsilon\to 0}
\frac{1}{2\pi i}\cdot \int_{|\lambda-\lambda_0|=\epsilon}\,
(\lambda_0-\lambda)R(\lambda)\, d\lambda=0
\]
which implies
hat the range of the projection operator
$E_T(\lambda_0)$ is equal to the kernel of
$\lambda_0\cdot E-T$.
\medskip

\noindent
{\bf{0.0.6.6 The case $M\geq 2$}}.
Now one has 
a
a non-decreasing family of subspaces
\[
N_k(\lambda_0)= \{ x\colon (\lambda_0E-T)^k(x)=0\}
\quad\colon 1\leq k\leq M
\]


\noindent
Let us analyzie the special case
when the range of 
$E_T(\lambda_0)$ has   finite dimension.
Here  the operator $T(\lambda_0)= TE_T(\lambda_0)$
acts on this finite dimensional vector space 
and the $B$-matrices with negative indices can be expressed 
as in linear algebra via 
a Jordan decomposition of $T(\lambda_0)$.
More precisely Jordan blocks of size
$>1$ may occur which
occurs of the smallest positive integer $m$ such that
\[
(\lambda_0E-T)^m(x)= \quad\colon
x\in E_T(\lambda_0)(X)
\]
is strictly larger than one.
Moreover, $E-E_T(\lambda_0)$ is a projection operator
and
one has a direct sum decompostion
\[
X=E_T(\lambda_0)(X)\oplus E-E_T(\lambda_0)
\]
Here $V=E-E_T(\lambda_0)$ is a closed subspace of $X$
which is invariant under $T$ and  there exists
some $c>0$ such that
\[
||\lambda_0-Tx||\geq ||x||\quad x\in V\cap \mathcal D(T)
\]
\medskip

\noindent
{\bf{Remark.}}
In applications it is often an important issue to decide when
$E_T(\lambda_0)$ has a finite dimensional range for
an isolated point in $\sigma(T)$.
The Kakutani-Yosida theorem 
in ¤ 11.9 is an example where
this finite dimensionality will
be established for certain
operators $T$.


\newpage

\noindent
\centerline {\bf{¤ 0.0.7 Semi-groups and infinitesmal generators.}}
\bigskip


\noindent
We give details of proofs of
a result due to Hille, Phillips and Yosida.
It has been inserted at this early stage to illustrate Neumann's theory about resolvents.
The less expericence dreader may consult the subsequent proof after studies of
basic material in the apecial chapters.
Let $X$ be a Banach space.
A family of bounded operators $\{T_t\}$ indexed by non-negative real numbers
is a semi-group if $T_0=E$ is the identity and
\[
T_{t+s}= T_s\circ T_t
\]
for all pairs of non-negative real numbers. In particular the $T$-operators commute.
The semi-group is said to be strongly continuous
if the vector-valued functions
\[ 
x\mapsto T_t(x)
\] 
are continuous with respect to the norm in $X$ for each
$x\in X$.
\medskip

\noindent
{\bf{1. Proposition.}}
\emph{Let $\{T_t\}$ be a strongly continuous semi-group
and set}
\[
\omega=\log| ||T_1||
\]
\emph{Then
the operator norms satisfy}
\[
||T_t||\leq e^{\omega t}\quad\colon t\geq 0
\]
\medskip

\noindent
{\bf{Exercise.}} Prove this using calculus applied to sub-multiplicative functions.
\medskip

\noindent
With $\omega$  as above
we consider the open half-plane
\[
U= \{\mathfrak{Re}(\lambda)>\omega \}
\]
Let  $\lambda\in  U$
and $x$ is a vector in $X$.
The Borel-Stieltjes  construction of
integrals with values in a Banach space gives 
the $X$-valued integral
\[
\int_0^\infty\, e^{-\lambda t}\cdot T_t(x)\, dt\tag{1.1}
\]
whose value is   denoted by
$\mathcal T(\lambda)(x)$.
It is clear that
\[ 
x\mapsto \mathcal T(\lambda)(x)
\] 
is linear and
the triangle inequality gives
\[
||\mathcal T(\lambda)(x)||\leq 
\int_0^\infty\, e^{-\mathfrak{Re}\lambda t} \cdot e^{\omega t}\, dt
\cdot ||x||=\frac{1}{\mathfrak{Re}\,\lambda -\omega}\cdot ||x||\tag{1.2}
\]

\medskip
\noindent
{\bf{2. Infinitesmal generators.}}
Let $\{T_t\}$ be a a strongly continuous semi-group.
Then there exists a densely defined and closed operator which is 
called its infinitesmal generator and obtained as follows:
\medskip

\noindent
{\bf{2.1 Theorem.}}
\emph{There exists a dense subspace $\mathcal D$ in $X$ such that
there exist}
\[
A(x)=\lim_{h\to 0}\, \frac{T_h(x)-x}{h}\quad\colon x\in\mathcal D
\] 
\emph{Here  the densely defined operator
$A$Êis closed and}
\[
\sigma(A\subset \{\mathfrak{Re}\,\lambda\leq\omega\}\tag{i}
\]
\emph{Moreover,  in the open half-space $U$ one has the equality}
\[
R_A(\lambda)=\mathcal T(\lambda)\tag{ii}
\]
\bigskip

\noindent
{\bf{3. The Hille-Phillips-Yosida theorem.}}
Theorem 2.1   produces infinitesmal generators of
strongly continuous semi-groups.
This specific  class of  densely defined and closed operators
can be described via properties of their spectra and
behavious of the resolvent operators.
Denote by $\mathcal{HPY}$ the family of densely defined
and closed linear operators $A$ with the property that 
$\sigma(A)$ is contained in a half-space
$\{\mathfrak{Re}\,\lambda\leq a\}$Ê
for some real number $a$, and
if $a^*>a$ there exists a constant $M$ such that
\[
||R_A(\lambda)||\leq
M\cdot \frac{1}{\mathfrak{Re}\,\lambda -\omega}\quad\colon 
\mathfrak{Re}\,\lambda\geq a^*
\]
\medskip

\noindent
{\bf{3.1 Theorem.}}
\emph{Each $A\in\mathcal{HPY}$ is the infinitesmal generator of a 
 uniquely determined strongly continuous
 semi-group.}
\medskip

\noindent
{\bf{Remark.}}
Notice that (iii) in Theorem 2.1 together with
(1.2) imply that
the infinitesmal generator of a strongly 
continuous semi-group
belongs to
$\mathcal{HPY}$. 
Hence Theorem 3.1  this  gives 
a 1-1 correspondence between
$\mathcal{HPY}$
and the family of strongly contionuous semi-groups.
\medskip

\noindent
{\bf{4. The case of bounded operators.}}
Before we give the proofs of the two theorems above
we consider  bounded operators. If
$B$ is a bounded linear operator on $X$
there exists the strongly continuous semi-group
where
\[
 T_t= e^{tB}= 1+\sum_{n=1}^\infty\, \frac{t^n}{n !}\cdot B^n
\]
If $h>0$ 
and $x\in X$ we have
\[
||\lim_{h\to 0}\, \frac{T_h(x)-x}{h}-B(x)||
=||\sum_{n=2}^\infty|\, \frac{h^n}{n !}\cdot B^n(x)||
\]
The triangle inequality entails that the last term is majorised by
\[
\frac{h^2}{2}\cdot e^{||B(x)||}
\]
We conclude that $B$ is the infinitesmal generator of
the semi-group. $\mathcal T= \{T_t\}$.
Next, if $\omega=||B||$
then $\sigma(B)$ is contained in the disc of radius $\omega$ and hence
in the half-plane $U=\{\mathfrak{Re}\,\lambda\leq\omega\}$.
If
$\lambda\in U$
the operator-valued integral 
\[
\int_0^\infty\, e^{-\lambda t}\cdot e^{Bt}\,dt=\frac{1}{\lambda}\cdot E+
\sum_{n=1}^\infty\, \bigl(\int_0^\infty\, e^{-\lambda t}\cdot t^n\,dt\,\bigr)\cdot \frac{B^n}{n !}
\]
Evaluating the integrals the right hand side becomes
\[
\frac{1}{\lambda}\cdot E+
\sum_{n=1}^\infty\, \frac{B^n}{\lambda^{n+1}}
\]
The last sum is equal to the Neumann series for
$R_B(\lambda)$ from ¤ xx. which gives the equation
\[ 
R_B(\lambda)= \mathcal T(\lambda)
\]
Hence Theorem 3.1 is confirmed for bounded operators.
\medskip

\noindent
{\bf{4.1 Uniformly
continuous semi-groups.}}
The semi-group
$\{e^{tB}\}$ has the additional property that 
\[ 
t\mapsto e^{tB}
\] 
is continuous with respect to  operator norms.
In fact, by v the triangle inequality the reader can check that
each pair $0\leq t<s$ gives
\[
||e^{sB}-e^{tB}||=||e^{tB}||\cdot ||e^{(s-t)B}-E||
\leq ||e^{tB}||\cdot ||B||\cdot ||e^{(s-t)||B||}\cdot (s-t)\tag{4.2}
\]
\medskip

\noindent
{\bf{4.3 A converse result.}}
A semi-group  $\{T_t\}$ is uniformly continuous if
\[
\lim_{t\to 0}| ||T_t-E||=0\tag{i}
\]
\medskip

\noindent
When (i)
holds
the operators $T_t$ are invertible when $t\simeq 0$
and if $h_*$ is chosen so that
\[
||T_t-E||\leq 1/2\quad\colon\, 0\leq t\leq h_*
\]
there exist bounded operators 
$\{S_t\,\colon\, 0\leq t\leq h_*\}$
such that
\[ 
T_t=e^{S_t}
\]
This entails that
if $0<h\leq h_*$ then
\[
\frac{T_h-E}{h} =\frac{S_h}{h}+\sum_{n=2}^\infty\,
\frac{h^{n-1}}{n !}\cdot  S_h^n
\]

\medskip

\noindent
{\bf{4.4 Exercise.}}
Verify that the semi-group equations entail that if $N$ is a positive integer and
$h$ so small that $Nh\leq h_*$ gives the equation
\[
\frac{S_{Nh}}{N}=S_h\tag{4.4.1}
\] 
\medskip

\noindent
Next,  $h\simeq 0$ we choose the
largest positive integer $N_h$ such that $N_h\cdot h\leq h_*$.
So here
\[
\frac{h_*}{N_h+1}< h\leq\frac{h_*}{N_h}
\]
With this choice of $N_h$ we apply (4.4.1) and get
\[
\frac{S_h}{h}=\frac{1}{N_h\cdot h}\cdot S_{N_h\cdot h}
 \]
Passing to the imit as $h\to 0$ the reader can check 
the limit equation
\[
\lim_{h\to 0}\, \frac{S_h}{h}=
h_*\cdot S(h_*)
\]
\medskip

\noindent
{\bf{4.5 Exercise.}}
Show from the above that
\[
\lim_{h\to 0}\, \frac{T_h-E}{h} =
h_*\cdot S(h_*)
\]
which
means that the infinitesmal generator of
$\{T_t\}$ is given by the bounded operator
$h_*\cdot S(h_*)$.
\medskip

\noindent
{\bf{4.6 Conclusion.}}
There exists a 1-1 correspondence between uniformly continuous 
semi-groups and bounded linear operators on $X$.
\bigskip


\centerline{\bf{5. Proofs in the unbounded case.}}
\bigskip

\medskip
First we prove Theorem 2.1. 
If $x\in X$ and $\delta>0$ we put
\[
x_\delta=\int_0^\delta\, T_t(x)\, dt
\]
For every  $h>0$ the semi-group equation gives
\[
\frac{T_h(x_\delta)-x_\delta}{h}=
\frac{1}{h}\cdot \int_\delta^{\delta+h}\, T_t(x)\, dt
\] 
By strong contoinuity
the limit in the right hand side exists as $h\to 0$ and gives a vector
$T_\delta(x)$. Hence the space $\mathcal D$ contains $x_\delta$.
The continuity of $t\mapsto T_t(x)$ at $t=0$ implies that 
$||x_\delta-x||\to 0$ which  proves that
$\mathcal D$ is dense and  the construction of the infinitesmal generator
$A$ gives
\[
A(x_\delta)= T_\delta(x)\tag{5.1}
\]
for every $\delta>0$.
\medskip


\noindent
Next, consider some vector  $x\in\mathcal D(A)$. 
Now  there exists the integral which defines
$\mathcal T(\lambda)(Ax)$ when $\lambda$ belongs to the half-plane $U$.
If $\lambda$ is real  and $h>0$ a variable substitution
gives
\[
\mathcal T(\lambda)(T_h(x))=
\int_0^\infty\, e^{-\lambda t}\cdot T_{t+h}(x)\, dt=
e^{\lambda h}\cdot 
\int_h^\infty e^{-\lambda s}T_s(x)\, ds
\]
It follows that

\[
\mathcal T(\lambda)(\frac{T_h(x))-x}{h})
=
\frac{e^{\lambda h}-1}{h}\cdot 
\int_h^\infty e^{-\lambda s}T_s(x)\, ds-
\frac{1}{h}\cdot 
\int_0^h e^{-\lambda s}T_s(x)\, ds
\]
Passing to the limit as $h\to 0$ the reader can check that
the right hand side becomes
\[
\lambda\cdot\mathcal T(\lambda)(x)-x
\]
So with $x\in\mathcal D(A)$ we have the equation
\[
\mathcal T(\lambda)(A(x))=
\lambda\cdot\mathcal T(\lambda)(x)-x
\]
which can be written
as
\[
\mathcal T(\lambda)( \lambda\cdot E-A)(x)=x
\]
\medskip

\noindent
{\bf{Exercise.}}
Conclude from the above that
\[ 
\mathcal T(\lambda)= R_A(\lambda)
\]
and deduce Theorem 2.1.





\medskip

\centerline{\bf{5.2 proof of Theorem 3.1}}

\medskip

\noindent
Let $A$ belong to $\mathcal{HPY}$. So here  
$\sigma(A)$ is contained in 
$\{\mathfrak{Re}(\lambda)\leq a\}$ for some real number $a$, and
when
$\lambda$ varies  in the open half-plane $U=\{\mathfrak{Re}(\lambda)\leq a\}$
there exist the resolvents $R(\lambda)$ where the subscript $A$ is deleted while 
we consider a fixed operator $A$.
By assumption there
exists a constant $K$ and some $a^*\geq a$ such that
\[
 ||R(\lambda)||\leq \frac{K}{\lambda}\tag{5.2.0}
\] 
when $\mathfrak{Re}(\lambda\geq a^*$.
\medskip

\noindent
{\bf{The operators
$B_\lambda$.}}
For each  $\lambda\in U$ we set
\[ 
B_\lambda=
\lambda^2\cdot R(\lambda)-\lambda\cdot E\tag{ii}
\]
Notice  that (5.2.0) gives
\[
||B_\lambda||\leq (K+1)|\lambda|\tag{iv}
\]
Consider a vector $x\in\mathcal D(A)$.
Now
\[
B_\lambda(x)=
\lambda\cdot(\lambda R(\lambda)(x)-x)=
\lambda \cdot R(\lambda)(Ax)
\]
We have also
\[
\lambda \cdot R(\lambda)(Ax)-R(\lambda(A(x))=A(x)
\]
Hence
\[
B_\lambda(x)-A(x)=R(\lambda)(A(x))
\]
Hence (5.2.0) gives
\[
||B_\lambda(x)-A(x)||\leq \frac{K}{\lambda}\cdot ||A(x)||
\]
Hence we have  the limit
formula
\[ 
\lim_{\lambda \to \infty}\,||B_\lambda(x)-A(x)||=0
\quad\colon x\in\mathcal D(A)
\]








\medskip


\noindent
{\bf{The semi-groups
$\mathcal S_\lambda=\{ e^{tB_\lambda}\,\colon\,  t\geq 0\}$.}}
To each $t\geq 0$ and $\lambda\in U$
we set
\[
S_\lambda(t)=e^{tB_\lambda}=E+
\sum_{n=1}^\infty\,
 \frac{t^n}{n !}\cdot B_\lambda^n\tag{5.2.1}
\]
By (iv) the series converges and
with $t$ fixed
termwise differentiation with respect to $\lambda$ gives
\[
\frac{d}{d\lambda}(S_\lambda(t))=t\cdot \frac{d}{d\lambda}(B_\lambda)\cdot S_t(\lambda)
=-t\cdot S_\lambda(t)+t\cdot(\lambda\cdot R(\lambda)^2-R(\lambda))\cdot S_\lambda(t)
\]


\noindent
Keeping $t$ fixed  we get after an integration
\[
S_\mu(t)-S_\lambda(t)=
t\cdot \int_\lambda^\mu\, (\xi\cdot R(\xi)^2-R(\xi))
S_\xi(t)\, ds
\quad\colon \mu>\lambda\geq a^*\tag{5.2.2}
\]
\medskip

\noindent
Next, we notice that (5.2.0) gives
\[
\lim_{\xi\to\infty}\, ||(\xi\cdot R(\xi)^2-R(\xi)||=0\tag{5.2.3}
\]
Together with  the general differential inequality from (xx) we
conclude that if $t$ stays in a bounded interval $[0,T)$
and  $\epsilon>0$, then  there exists some
large $\xi^*$ such that for every $0\leq t \leq T$
the operator norms satisfy
\[
||S_\mu(t)-S_\lambda(t)||<\epsilon\quad\colon \mu\geq \lambda\geq \xi^*\tag{5.2.4}
\] 
\medskip


\noindent
{\bf{5.2.5 The semi-group $\{S(t)\}$.}}
Since the  bounded operators on $X$ is 
a Banach space, it follows from the above
that each $t$ gives a bounded operator
$S(t)$ given by 
\[ 
\lim_{\lambda\to +\infty}\, S_\lambda(t)= S(t)
\]
where the limit is taken in the operator norm and
the convergence holds
uniformly  when $t$ stays in a bounded interval.
Since $t\mapsto S_\lambda(t)$ is a semi-group for each large
$\lambda$, the same holds for the family $\{S(t)\}$. Moreover, the
convergence properties entail that the semi-group
$\{S(t)\}$ 
is strongly continuous.
\medskip
Neumann's differential equation from (¤ 0.x) gives
\[
\frac{d}{d\lambda}(B_\lambda)=R(\lambda)-E-\lambda\cdot R(\lambda)^2\tag{iii}
\]


\noindent
{\bf{The infinitesmal generator of $\{S(t)\}$.}}
Returning to the series (5.2.1) it is clear that 
\[
\frac{d}{dt}(S_\lambda(t)=S_\lambda(t)\cdot B_\lambda\tag{5.2.6}
\] 
An integration and the equality 
$S_\lambda(0)= E$ give for every $t>0$ and each vector $x\in X$:
\[
S_\lambda(t)(x)-x=\int_0^t\, S_\lambda(\xi)\circ B_\lambda(\xi)(x)\, d\xi\tag{5.2.7}
\]
\medskip




\noindent

\noindent
When $x\in\mathcal D(A)$ we have the limit formula (xx) and together with
the limit which produces the semi-group $\{S(t)\}$ we conclude that
\[
S(t)(x)-x=\int_0^t\, S(\xi)\circ A(x)\, d\xi\quad\colon x\in\mathcal D(A)
\]
We can take a limit as $t\to 0$
where the strong continuity of 
the semi-group $\{S(t)\}$ applies to
vectors $A(x)\,\colon x\in\mathcal D(A)\}$.
Hence 
\[
\lim_{t\to 0}\,
\frac{S(t)(x)-x}{t}=A(x)\quad\colon x\in\mathcal D(A)
 \]
 \medskip
 
\noindent
 So if $\widehat{A}$ is the infinitesmal generator of the semi-group
 $\{S(t)\}$ then its graph contains that of $A$, i.e.
 $\widehat{A}$ is an extension of 
 the densely defined and closed operator $A$.
However, we have equality because $\widehat{A}$ being  an inifinitesmal generator of a 
strongly continuous semi-group
has its spectrum confined to a half-space
$\{\mathfrak{Re}(\lambda)\leq b\}$
for some real number $b$, i.e. here we used theorem 2.1.
In particular 
there exist points outside the union of $\sigma(A)$ and $\sigma(\widehat{A})$
and 
the equality
$A=\widehat{A}$ 
follows from the general result in ¤ xx.
Hence  $A$ is an infinitesmal generator of a semi-group
which
finishes the proof of Theorem 3.1.



 
\newpage














\newpage

\centerline{\bf{Special Chapters}}

\bigskip


\noindent
\emph{Summary of the contents.}
¤ 1  studies normed vector spaces
over the complex field
${\bf{C}}$ or the real field
${\bf{R}}$. 
We
explain how each norm  is defined
by a convex subset of $V$ with 
special properties.
If  $X$ is a normed vector space
such that every
Cauchy sequence with respect to the norm $||\cdot||$
converges to some vector in $X$ one
says that the norm is complete and refer to
the pair $(X,||\cdot||)$ as a Banach space. 

\medskip





\noindent 
{\bf Dual spaces.}
When
$X$ is a normed linear space one constructs the  linear
space $X^*$ whose elements are continuous linear functionals
on $X$.
The Hahn-Banach Theorem 
identifies norms of vectors in
$X$ via evaluations by $X^*$-elements. More precisely, denote by
$S^*$ the unit sphere in
$X^*$, i.e. 
linear functionals
$x^*$  of unit norm.
Then
one has the equality
\[
 ||x||=\max_{x^*\in S^*}\, |x^*(x)|\quad \,\text{for all}\,\, x\in X\,.\tag{i}
\]

\noindent
The determination of
$X^*$  is  often an important issue. An example
is the dual of the normed space
$X=H^\infty(T)$ of bounded Lebesgue measurable functions on the unit circle
which are boundary values of bounded analytic functions in
the open disc $D$. A portion of its dual space
is given by the  quotient space:
\[ 
Y=\frac{L^1(T)}{H\uuu 0^1(T)}\tag{ii}
\]
where $H\uuu 0^1(T)$ is the closed subspace of
$L^1(T)$ whose functions are boundary values of analytic functions in
$D$ which vanish at $z=0$. However, the dual
$X^*$ is considerably larger. In fact, we shall learn that
$H^\infty(T)$ is an example of a commutative Banach algebra
to which we can assign the maximal ideal space
$\mathfrak{M}\uuu X$
and now $X^*$ is the space of Riesz measures on this 
compact space.
But a concrete description of
$\mathfrak{M}\uuu X$ is not known.
Via point evaluations in $D$
it is  clear that $D$ appears as a  subset
of $\mathfrak{M}\uuu X$. 
Its position in 
$\mathfrak{M}\uuu X$ was an open question for
some time, until
Carleson in an article from 1957 proved that
$D$ is a dense  subset. This result is known as the
Corona Theorem whose  proof requires
a deep  analysis 
based upon geometric constructions such as Carleson measures.


 \medskip

\noindent{\bf{Reflexive spaces.}}
Starting from a Banach space $X$ we get $X^*$ 
whose  dual 
is  denoted by $X^{**}$ and called the bi\vvv dual of $X$.
There is  a natural injective map $\mathfrak{i}_X\colon X\to X^{**}$
and (i) above shows thatit  is an isometry, i.e.
the norms $||x||$ and $||\mathfrak{i}_X(x)||$ are equal.
But in general the bi-dual embedding map
is nor surjective.
If it is  is surjective so that
$X=X^{**}$ one says that $X$ is reflexive.
 \medskip

\noindent{\bf{Compact operators.}}
Let $X$ and $Y$ be a pair of Banach spaces.
A bounded linear operator $T\colon X\to Y$
is compact if the image of the unit ball in $X$ is relatively compact in
$Y$.
In applications one often encounters compact operators.
The case when the target space $Y= C^0(S)$
for a compact metric space
is of special interest.
Let  $B$ denote  the unit ball in $X$.
A classic result due to
Arzela and Vitali asserts that $T(B)$ is relatively compact if and only
if this family is equi-continuous, i.e. to each $\epsilon>0$ there
exists $\delta>0$ such that
\[
\max_{x\in B}\,\omega_{Tx}(\delta)\leq\epsilon
\]
where we introduced the modulus of continuity, i.e if
$f\in C^0(S)$ and $\delta>0$ then
\[
\omega_f(\delta)=\max\, |f(y_1)-f(y_2)|\quad \colon
\, d(y_1,y_2)<\epsilon
\]
In ¤ xx we prove that if $T\colon X\to Y$
is a compact operator between a pair of Banach spaces, then
its adjoint $T^*\colon X^*\to Y^*$ is also compact.
With
$Y= C^0(S)$ we recall that Riesz' representation theorem  gives
the equality   $Y^*=\mathfrak{M}(S)$
where 
$\mathfrak{M}(S)$ is the space of Riesz measures on $S$ with a finite total mass.
Let  us then consider a sequence
$\{\mu_n\}$  in the unit ball of
$\mathfrak{M}(S)$ which converges in the weak star topology 
to a limit measure $\mu$.
When $T^*$ is compact there exists at least one  subsequence
$\{\mu_{n_k}\}$
such that
$\{T(\mu_{n_k})\}$ converges in the norm 
topology to some
$x^*\in X^*$.
We leave as an exercise to the reader to show that
$x^*$ is independentof the chosen subsequence. In other words, one has
the following:
\medskip

\noindent
{\bf{Theorem.}} \emph{Let  $T\colon X\to C^0(S)$ be a compact operator
and $\{\mu_n\}$ a sequence in the unit ball of
$\mathfrak{M}(S)$ which converges in the weak star topology to a limit
measure $\mu$. Then it follows that}
\[
\lim_{n\to\infty}\, ||T^*(\mu_n)-T^*(\mu)||=0
\]
\medskip

\noindent
The result as above illustrates why general theory has a 
great merit since
we can apply the theorem in many different situations.














\medskip

\noindent
{\bf Calculus on Banach spaces.}
Let $X$ and $Y$ be two Banach spaces.
In ¤ 7  we define
the differential of a $C^1$-map $g\colon\,X\to Y$ where
$g$ in general is non-linear.
Here the 
differential of $g$ at a  point
$x_0\in X$ is a bounded linear operator from
$X$ into $Y$. This extends the construction of
the Jacobian  for a $C^1$-map from
${\bf{R}}^n$ into ${\bf{R}}^m$
expressed by an $m\times n$-matrix.
More generally one constructs higher order differentials and 
refer to $C^\infty$-maps from one Banach space into another.
We shall review this 
in ¤ 7.  Let us  remark that 
Baire's category theorem together with the Hahn-Banach theorem
show that if $S$ is an arbitrary  compact metric  space and
$\phi$ is a continuous function on $S$ with values
in a normed space
$X$, then $\phi$ is \emph{uniformly continuous}, i.e. to
every
$\epsilon>0$ there exists $\delta>0$ such that
\[
d_K(p,q)\leq\delta\implies
||\phi(p)-\phi(q)||\leq\epsilon
\]
where $d_S$ is the distance function on
the metric space $S$
and in 
the right hand side we have taken the norm in $X$.
Next,  there exists  class
of differentiable Banach spaces.
By definition a Banach space $X$ is differentiable at a point $x$
if there exists a linear functional $\mathcal D\uuu x$ on $X$
such that
\[
\mathcal D\uuu x(y)=
||x+\zeta\cdot y||\vvv ||x||=\mathfrak{Re}\, (\zeta\cdot
\mathcal D\uuu x(y))+\text{small ordo}(|\zeta|)\tag{*}
\]
hold for every $y\in X$ where the limit is taken over complex
$\zeta$ which tend to zero.
One says that $X$ is differentiable if $\mathcal D\uuu x$ exist
for every $x\in X$.
In ¤ XX  
we expose a result due to Beurling and Lorch
concerned with certain non-linear duality maps
on uniformly  convex and differentiable Banach spaces.








\medskip

\noindent
{\bf Analytic functions.} Let $X$ be a Banach space
and 
consider a power series with coefficients in $X$:
\[ 
f(z)=\sum_{\nu=0}^\infty\, b_\nu\cdot z^\nu\quad\, b_0,b_1,\ldots
\,\,\text{is a sequence in}\,\,  X\,.\tag{i}
\]
Let $R>0$ and suppose there exists
a constant $C$ such that
\[ 
||b_\nu||\leq C\cdot R^\nu\quad\colon\,\nu=0,1,\ldots\tag{ii}
\]
Then the series (i) converges when $|z|<R$ and 
$f(z)$ is called an $X$-valued analytic function in the open disc
$|z|<R$.
More generally, let $\Omega$ be an open set in
${\bf{C}}$. An $X$-valued function $f(z)$
is analytic if there to every
$z_0\in\Omega$
exists an open disc $D$ centered at $z_0$ 
such that the restriction of $f$ to $D$ is represented by
a convergent power series
\[ 
f(z)=\sum\, b_\nu(z-z_0)^\nu
\] 
Using the dual space
$X^*$
results about ordinary analytic functions
extend to $X$-valued analytic functions.
Namely, for each fixed
$x^*\in X^*$
the complex valued function
\[ 
z\mapsto x^*(f(z))
\]
is analytic in $\Omega$.
From this one recovers the Cauchy formula.
For example, let $\Omega$ be a domain in the class
$\mathcal D(C^1)$ and  $f(z)$  is an analytic $X$-valued function in
$\Omega$ which extends to a continuous $X$-valued function on
$\bar\Omega$.
If $z_0\in\Omega$ there exists the complex line integral
\[ \int_{\partial\Omega}\, \frac{f(z)dz}{z-z_0}
\]
It is evaluated by  sums just as for a  Riemann integral
of  complex-valued functions. One simply 
replaces  absolute
values of complex valued functions by
the norm on $X$  in  approximating sums which converge to the
Riemann integral. This gives  Cauchy's integral formula
\[
f(z_0)= \int_{\partial\Omega}\, \frac{f(z)dz}{z-z_0}\,.
\]

\medskip

\noindent
{\bf{Borel-Stieltjes integrals.}}
Let  $\mu$
be  a Riesz measure on the unit interval $[0,1]$ and 
$f$  an $X$-valued function, which to every
$0\leq t\leq 1$ assigns a vector $f(t)$ in $X$. Suppose 
there exists a constant $M$ such that
\[
 \max_{0\leq t\leq 1}\,||f(t)||=M
\]
Assume in addition that
the complex-valued functions
$t\mapsto x^*(f(t))$ are Borel functions on $[0,1]$ 
for every $x^*\in X^*$.
Then there exist the Borel-Stieltjes integral
\[ 
J(x^*)= \int_0^1\, x^*(f(t))\dot dt
\] 
for every $x^*$.
The boundedness of $f$ implies that
$x^*\mapsto J(x^*)$ is a continuous linear functional on
$X^*$. This  gives
a vector $\xi(f)$ in the bi\vvv dual $X^{**}$
such that
\[
\xi(f)(x^*)= J(x^*)\quad\colon\quad x^*\in X^*\tag{1}
\]
When $X$ is reflexive
the  $f$-integral yields a vector in $\mu_f\in X$
which computes (1), i.e.
\[
x^*(\mu_f)= \int_0^1\, x^*(f(t))\dot dt\quad\colon
x^*\in X
\]
This map  applies in particular if $X$ is a Hilbert space
since they are reflexive. 


\bigskip





\noindent
{\bf Operational calculus}.
Commutative Banach algebras are  defined and studied in 
¤ 10.
If $B$ is a semi-simple Banach algebra with a unit element $e$
and
$x\in B$, then the spectrum
$\sigma(x)$ is  a compact subset of
${\bf{C}}$ and 
one gets the vector-valued resolvent map:
\[
\lambda\mapsto R_x(\lambda)= (\lambda\cdot e-x)^{-1}\quad\colon\quad
\lambda\in{\bf{C}}\setminus\sigma(x)\tag{i}
\]
If
$\lambda_0\in {\bf{C}}\setminus\sigma(x)$
there exists a local Neumann series which
represents $R_x(\lambda)$
when $\lambda$ stays in the open disc of
radius $\text{dist}(\lambda_0,\sigma(x))$.
It follows that $R_x(\lambda)$ is a $B$-valued
analytic function of the complex variable $\lambda$ defined in the open 
complement of
$\sigma(x)$.
Starting from this, Cauchy's formula gives
vectors  in $B$ for every   analytic function
$f(\lambda)$ which is defined in some open neighborhood of
$\sigma(x)$.
More precisely, denote by
$\mathcal O(\sigma(x))$ the algebra of 
germs of analytic functions on the compact set
$\sigma(x)$.
In ¤ 10 we prove
that there exists
an algebra homomorphism
from $\mathcal O(\sigma(x))$ into $X$ which sends
$f\in \mathcal O(\sigma(x))$ into an element $f(x)\in X$.
Moreover,
the \emph{Gelfand transform} of $f(x)$
is related to that of $x$ by the formula
\[
\widehat f(x)(\xi)= f(\widehat x(\xi))\quad\colon\quad
\xi\in\mathfrak{M}_B\tag{*}
\]
This general result  is used in many applications. A crucial case occurs
when $B$
is the Banach algebra generated 
by a single bounded linear operator on a Hilbert space.





\medskip


\noindent
{\bf Hilbert spaces.}
An non-degenerate inner product on a complex vector space
$\mathcal H$
is a complex valued function on
the product set
$\mathcal H\times\mathcal H$ which
sends each pair $(x,y)$
into a complex number
$\langle x,y\rangle$  satisfying the following 
three conditions:
\[
x\mapsto\langle x,y\rangle\,\,\text{is a linear form on}\,\,\mathcal H
\,\,\text{for each fixed}\,\, y\in\mathcal H\tag{1}
\]
\[
\langle y,x\rangle=\overline{\langle x,y\rangle}
\quad\colon 
x,y\in\mathcal H\tag{2}
\]
\[
\langle x,x\rangle>0\,\,\text{for all}\,\, x\neq 0\tag{3}
\]


\noindent
Here  (1-3)
imply
that
$\mathcal H$ is equipped with a norm
defined
by
$||x||=\sqrt{\langle x,x\rangle}$ and one easiy verfies that
it satisfies
\[
||x-y||^2+||x+y||^2=
2||x||^2+2||y||^2\tag{*}
\]
Conversely, if (*) holds for a norm
then
it is defined by an inner product where
\[
2\cdot \mathfrak{Re}\,\langle x,y\rangle=
||x+y||^2-||x||^2-||y||^2
\quad\colon
2\cdot \mathfrak{Im}\,\langle x,y\rangle=
||ix+y||^2-||x||^2-||y||^2
\]


\noindent
If a norm given via an inner product
is complete one says that
$\mathcal H$ is a Hilbert space.
A fundamental fact is that  Hilbert spaces are  
\emph{self-dual}. This means that if
$\gamma$ is an element in the dual $\mathcal H^*$, then there exists
a unique vector $y\in\mathcal H$ such that
\[ 
\gamma(x)=\langle x,y\rangle\,\quad\text{for all}\,\, x\in\mathcal H\,.
\]
We prove this in the section devoted to Hilbert spaces.
\bigskip


\noindent
{\bf{Orthonormal bases.}}
If $\mathcal H$ is separable, i.e. contains a denumerable dense subset, then
it is isomorphic to the  Hilbert space
$\ell^2$ whose elements are sequences of complex numbers
$\{c_0,c_1,\ldots\}$ for which
$\sum\, |c_n|^2<\infty$.
However, this does not mean that one has a clear  picture of a Hilbert space
which is given  without a specified orthonormal basis.
So even if all separable Hiolbert spaces are isomorphic one often
needs considerable work to exhibit a sequence" of pairwise
orthogonal vectors to exhibit that $\mathcal H\simeq \ell^2$.
An example occurs when $\mathcal H$ is the Hilbert space of square integrable analytic functions
in a bounded domain in ${\bf{C}}$.
Here one defines Bergman's kernel  function and for simply connected
domains an orthonormal bases given by polynomials was found
by Faber which has consequences in analytic function theory. See
¤ X in Chapter VI for an account.










\newpage

\centerline {\bf \large 1. Normed spaces.}

\bigskip

\noindent
A norm on  a complex vector space
$X$  is 
a map
from $X$ into ${\bf{R}}^+$ satisfying:
\[
||x+y||\leq
||x||+||y||\quad\text{and}\quad 
||\lambda\cdot x||=|\lambda\cdot
||x||\quad\colon\quad x,y\in X\quad\colon\,\,\lambda\in{\bf{C}}\tag{*}
\]
Moreover  $||x||>0$ holds for every $x\neq 0$.
A norm gives a topology on $X$ defined by the distance function
\[ d(x,y)=||x-y||\tag{**}
\]


\noindent
{\bf 1.1 Real versus complex  norms.}
The real numbers appear as a subfield of
${\bf{C}}$. Hence every complex vector space
has an underlying structure as a vector space over
${\bf{R}}$.
A norm on a  real vector space
$Y$
is a function $y\mapsto ||y||$
where (*)
holds for real numbers $\lambda$.
Next, let  $X$ be a complex vector space
with a norm $||\cdot ||$.
Since we can take $\lambda\in{\bf{R}}$ in (*)
the complex norm induces a
real norm on the underlying
real vector space of $X$.
Complex norms are  more special than real norms.
For example, consider the 1-dimensional complex vector space
given by
${\bf{C}}$.  When the point 1 has norm one there is no choice
for the norm of any complex vector $z=a+ib$,  i.e. its norm
becomes the usual absolute value. On the other hand we can define
many norms on
the underlying real $(x,y)$-space. For example, we may
take the norm defined by
\[ 
||(x,y)||=|x|+|y|\tag{i}
\]
It fails to satisfy
(*) under complex multiplication. For example,
with
$\lambda=e^{\pi i/4}$ we send $(1,0)$ to
$p=(\frac{1}{\sqrt{2}},
\frac{1}{\sqrt{2}})$ whose norm from (i) becomes
$\sqrt 2$
while it should remain with norm one if
(*) holds.



\medskip

\noindent
{\bf 1.2 Convex sets.} We shall work on
real vector spaces for a while.
Let $Y$ be a real vector space.
A subset $K$  is convex if
the line segment formed by a pair of points in $K$
stay in $K$, i.e.
\[ 
y_1,y_2\in K\implies s\cdot y_2+(1-s)\cdot y_1\in K\quad\colon\quad
0\leq s\leq 1\tag{i}
\]
Let ${\bf{o}}$ denote the origin in $Y$.
Let $K$ be a convex set which
contains ${\bf{o}}$  and is symmetric with respect to
${\bf{o}}$:
\[ 
y\in K\implies -y\in K
\]
The symmetric convex set $K$ is called  \emph{absorbing} if there to every
$y\in Y$ exists some $t>0$ such that $ty\in K$.
Suppose that $K$ is symmetric and absorbing.
To every $s>0$ we set
\[ 
sK=\{ sx\,\colon\,\, x\in K\}
\]
Since ${\bf{o}}\in K$ and $K$ is convex  these
sets increase with $s$ and since
$K$ is absorbing we  have:
\[
\bigcup_{s>0}\, sK=Y\tag{ii}
\]
Next, we impose  the condition that $K$ does not contain
any 1-dimensional subspace, i.e. whenever
$y\neq 0$ is a non-zero vector
there exists  some large $t^*$ such that $t^*\cdot y$ does not
belong to $K$. The condition is equivalent with
\[ 
\bigcap_{s>0}\, 
s\cdot K={\bf{o}} \tag{iii}
\]



\noindent {\bf 1.3 The norm $\rho_K$.}
Let $K$ be convex and 
symmetric and assume that  (ii-iii) hold. To each $y\neq 0$
we set
\[
\rho_K(y)=\min_{t>0}\,\frac{1}{t}\quad\colon\, t\cdot y\in K\tag{*}
\]
Notice that if $y\in K$ then
$t=1$ is competing when we seek the minimum and hence
$\rho_K(y)\leq 1$. On the other hand, if $y$ is "far away" from $K$
we need small $t$-values to get $t\cdot y\in K$
and therefore
$\rho_K(y)$ is large. It is also clear that
\[
\rho_K(ay)=a\cdot\rho_K(y)\quad\colon\ a\,\,\text{real and positive}\tag{i}
\]
Finally , since $K$ is symmetric we have $\rho_K(y)=\rho_K(-y)$  and hence (i) gives
\[
\rho_K(ay)=|a|\cdot\rho_K(y)\quad\colon\ a\,\,\text{any real number}\tag{ii}
\]

\medskip


\noindent
{\bf 1.4 Proposition.}
\emph{By (*) we get a norm which is called the $K$-norm defined by
the convex set $K$.}
\bigskip

\noindent
\emph{Proof.} The verification of the triangle inequality:
\[ 
\rho_K(y_1+y_2)\leq \rho_K(y_1)+\rho_K(y_2)
\]
is left as an exercise. The hint is to use the convexity of $K$.
\medskip

\noindent
{\bf 1.5 A converse.} Let $||\cdot||$ be a norm
on $Y$ which gives the  convex set
\[ 
K^*=\{ y\in Y\quad\colon\,||y|\leq 1\}
\]
It is clear that $\rho_{K^*}(y)=||y||$ holds, i.e. the given
norm is recaptured by the norm defined by $K^*$.
We can also regard the set
\[
K_*=y\in Y\quad\colon\,||y|< 1\}
\]
Here $K_*\subset K^*$
but the reader should notice
the equality
\[
\rho_{K_*}(y)=\rho_{K^*}(y)
\]
Thus, the two convex sets define the same norm
even if the set-theoretic inclusion
$K_*\subset K^*$ may be strict.
In general, a pair of convex sets $K_1,K_2$
satisfying (i-ii) above are
equivalent if they define the same norm.
Starting from this norm we get $K_*$ and $K^*$ and then
the reader may verify that
\[
K_*\subset K_\nu\subset K^*\quad\colon \nu=1,2
\]


\noindent
\emph{Summing up} we have described all norms
on $Y$ and   they are in a 1-1 correspondence with
equivalence classes in the family
$\mathcal K$  of  convex
sets which are symmetric, absorbing and satisfy (iii) above, i.e.
when $K\in\mathcal K$ then
$K$ does not contain any 1-dimensional subspace.
For each specific norm on $Y$
we can assign the largest convex set $K^*$ in the corresponding
equivalence class.
\bigskip

\noindent
{\bf 1.6 Equivalent norms.}
Two norms $||\cdot||_1$ and $||\cdot||_2$ are equivalent if there
exists a constant $C\geq 1$ such that
\[
\frac{1}{C}\cdot ||y||_1\leq ||y||_2\leq C\cdot ||y||_1\quad\colon\quad\tag{0.6}
y\in Y
\]
Notice that if the norms are defined by convex
sets $K_1$ and $K_2$ respectively, then 
(0.6) means that there exists some $0<t<1$ such that
\[ 
tK_1\subset K_2\subset t^{-1}K_1
\]
\medskip


\noindent{\bf The case $Y={\bf{R}}^n$}.
If $Y$ is finite dimensional all norms are equivalent. To
see this we consider  the euclidian basis $e_1,\ldots, e_n$.
To begin with we have  the \emph{euclidian norm}
which  measures the euclidian length
from a vector $y$ to the origin:
\[
||y||_e=\sqrt{\,\sum_{\nu=1}^{\nu=n}\,|a_\nu|^2}\quad\colon\quad
y=a_1e_1+\ldots+a_ne_n\tag{i}
\]
The reader should verify that (i)
satisfies the triangle inequality
\[
||y_1+y_2||_e\leq ||y_1||_e+||y_2||_e
\]
which  amounts to verify the Cauchy-Schwartz inequality.
We have also  the norm $||\cdot ||^*$ defined by
\[ 
||y||^*=\sum_{\nu=1}^{\nu=n}\,|a_\nu|\quad\colon\quad
y=a_1e_1+\ldots+a_ne_n\tag{ii}
\]
This norm is equivalent to the euclidian norm. More precisely
the reader may verify the inequality
\[
\frac{1}{\sqrt{n}}\cdot ||y||_e\leq
||y||^*\leq\sqrt{n}\cdot ||y||_e\tag{iii}
\]
\medskip

\noindent
Next, let 
$||\cdot||$ be some arbitrary norm. Put
\[ 
C=\max_{1\leq \nu\leq n}\, ||e_\nu||\tag{iv}
\]
Then (ii) and the triangle inequality for the norm
$||\cdot||$ gives
\[ 
||y||\leq C\cdot ||y||^*\tag{v}
\]
\medskip

\noindent
By the equivalence (iii) the norm topology defined by
$||\cdot||^*$ is the same as the usual euclidian topology in
$Y={\bf{R}}^n$.
Next, notice  that (v) implies that the sets
\[ 
U_N=\{ y\in Y\quad\colon\quad ||y||<\frac{1}{N}\}\quad\colon\quad
N=1,2,\ldots
\]
are \emph{open} sets when  $Y$ is equipped with its usual euclidian topology.
Now $\{U_N\}$ is an increasing sequence of open sets
and their union is obviously equal t o$Y$.
in particular this union covers the compact
unit sphere $S^{n-1}$. This gives an integer $N$ such that
\[ 
S^{n-1}\subset U_N
\]
This inclusion gives
\[ 
||y||_e\leq N\cdot ||y||
\]
Together with (iii) and (v) we conclude that
$||\cdot||$is equivalent with $||\cdot||_e$.
Hence we have proved
\medskip

\noindent 
{\bf 1.7 Theorem.}
\emph{On a finite dimensional vector space all norms
are equivalent.}

\bigskip

\noindent{\bf 1.8 The complex case.}
If $X$ is a complex vector space
we obtain complex norms via
convex
sets $K$ which not only are symmetric with
respect to scalar multiplication with
real numbers, but is also invariant under multiplication
with complex numbers
$e^{i\theta}$ which  entails that
\[ 
\rho_K(\lambda\cdot x)= \lambda\cdot \rho_K(x)
\] 
hold for every complex number
$\lambda$, i.e. we get a norm on the complex vector space.

\bigskip


\noindent
\centerline {\bf{1.9 Non-linear convexity.}}
\medskip


\noindent
Let $f(x)$ be a real-valued function in
${\bf{R}}^n$ of class $C^2$.
To every point $x$ we assign the Hessian
$H_f(x)$ which is the symmetric matrix with elements
$\{\partial^2f/\partial x_j\partial x_k\}$.
The function is called strictly convex if $H_f(x)$ is positive for all $x$, i.e. if
the eigenvalues  are all $>0$.
Assume in addition that
\[
 \lim_{|x|\to+\infty}\, f(x)=+\infty\tag{1}
\]
Under these conditions one has the  results
below:

\medskip

\noindent
{\bf{1.10 Theorem.}}
\emph{The function takes its minimum at a unique point in
${\bf{R}}^n$
and the vector valued function}
\[
x\mapsto \nabla_f(x)
\]
\emph{bijective,  i.e. $\nabla_f(p)\neq \nabla_f(q)$
hold for all pairs $p\neq q$ in ${\bf{R}}^n$.}

 \medskip
 
 \noindent
 {\bf{Exercise.}}
 Prove this classical result  which is due to
 Lagrange and Legendre.
 \medskip
 
 \noindent
 With $f$ as in the theorem
 we can  move origin 
 and assume that $f$ takes its mimium at $x=0$.
 Replacing $f$ by $f(x)-f(0)$  the  minimum value is zero.
 To each positive real number
  $s$ we put
 \[
 K_s=\{f\leq s\}
 \] 
 Then $\{K_s\}$ is an increasing sequence of convex
 and compact sets whose boundaries
$\{\partial K_s\}$ are  $C^1$-submanifolds in
${\bf{R}}^n$.
The reader is invited to analyze the ray functions where one for each
point $\omega$ on the unit sphere $S^{n-1}$
studies the function
\[ 
\rho_\omega (s)=r\quad\colon r\cdot \omega\in \partial K_s
\]
For each fixed $\omega$ the reader should verify that
this  yields a strictly increasing function of
$s$ and we leave it to the reader to
plot level sets $\{f=a\}$
when $a>0$ for some different $f$-functions as above.



\noindent
{\bf{1.11 On cones in ${\bf{R}}^n$}}.
A subset $\Gamma$ is  a cone if 
$x\in\Gamma $ implies that the  half-ray
${\bf{R}}^+\cdot x\subset\Gamma$.
Suppose that $\Gamma$ is a closed set in
${\bf{R}}^n$. Let  $S^{n-1}$ be the 
euclidian  unit sphere and put
\[
\Gamma_*=\Gamma\cap S^{n-1}
\]
We say that $\Gamma$ is \emph{fat} if
$\Gamma_*$ has a non-empty interior in $S^{n-1}$
and
$\Gamma$ is \emph{proper} if 
\[
\Gamma_*\cap -\Gamma_*=\emptyset
\]
The reader may verify that
this is equivalent with the condition that
$\Gamma$ does not contain any 1-dimensional subspace.
\medskip

\noindent
{\bf{1.12 Exercise.}} Show that a cone
$\Gamma$ is proper if and only if
$\widehat{\Gamma}$ is fat.
\medskip

\noindent
{\bf{1.13 Dual cones.}}
The \emph{dual cone} is defined by
\[
 \widehat\Gamma=\{x\quad\colon\langle x,\Gamma\rangle\leq 0\}
\]


\noindent
{\bf{1.14 Exercise.}} Show the biduality formula, i.e.
tha t $\Gamma$ is equal to the dual cone of $\widehat\Gamma$.


 \bigskip
 
 


\centerline {\bf 2. Banach spaces.}
\medskip


\noindent
Let $X$ be a normed space over ${\bf{C}}$ or over
${\bf{R}}$.
A sequence of vectors
$\{x_n\}$
is called a Cauchy sequence if
\[ 
\lim_{n,m\to\infty}\, ||x_n-x_m||=0\tag{*}
\]
We obtain a vector space
$\widehat X$ whose vectors are defined as equivalence classes of Cauchy sequences.
The norm of a Cauchy sequence $\hat x=\{x_n\}$ is defined by
\[
||\hat x||=\lim_{n\to\infty}\,||x_n||
\]


\noindent
One says that the  norm on $X$
is complete if every
Cauchy sequence converges, or equivalently $X=\widehat X$.
A complete normed space is  called a \emph{Banach space}
as an  attribution to Stefan Banach whose
article [Ban] introduced the general concept of
normed vector spaces.


\medskip

\noindent
{\bf 2.1 The Banach-Steinhaus theorem.}
\emph{Let $X$ be a Banach space equipped with the complete
norm
$||\cdot||^*$. Then 
for every other complete norm
$||\cdot||$ there exists a constant $C$ such that}
\[
C^{-1}\cdot ||x||^*\leq ||x||\leq C\cdot ||x||^*\quad\colon\quad x\in X
\]



\medskip

\noindent
{\bf Remark.}
Thus,
if
$||\cdot||_1$ and $||\cdot||_2$ are two complete norms on the
same vector space then they are equivalent.
The proof of Theorem 2.1 relies upon a result due to
Baire which we recall below.

\medskip

\noindent
{\bf The Baire category theorem.}
Let
$X$ be a metric space whose metric $d$ is complete, i.e.
every Cauchy sequence with respect to the distance function
$d$ converges. 
\medskip

\noindent
{\bf 2.2 Theorem.}
\emph{Let $\{F_n\}$ is an increasing  sequence of
closed subsets of $X$ where each $F_n$ has empty interior. Then
the union $F^*=\cup\, F_n$ is meager, i.e.
$F^*$ does not contain any open
set.}


\medskip

\noindent
\emph{Proof.} Let $x_0\in X$ and $\epsilon>0$ be given.
It suffices to show that
$B_\epsilon(x_0)$ contains a point $x_*$ outside
$F^*$ for every $\epsilon>0$.
To show this we first use that $F_1$ has empty interior which gives
some $x_1\in B_{\epsilon/2}(x_0)\setminus F_1$
and we choose $\delta_1<\epsilon/2$ so that
\[
B_{\delta_1}(x_1)\cap F_1=\emptyset\tag{i}
\]
Now $B_{\delta_1/2}(x_1)$ is not contained in
$F_2$ and we find a pair $x_2$ and $\delta_2<\delta_1/2$
such that
\[
B_{\delta_2}(x_2)\cap F_2=\emptyset\tag{ii}
\]
We can continue in this way and to every $n$ find a pair $x_n,\delta_n$ such that
\[
B_{\delta_n}(x_n)\cap F_n=\emptyset
\quad\colon\quad x_n\in B_{\delta_{n-1}}(x_{n-1})\quad\colon\quad
\delta_n<\delta_{n-1}/2\tag{iii}
\]
Since $X$ by assumption is complete and
$\{x_n\}$ by the construction  is a Cauchy 
sequence there exists a limit $x_n\to x^*$.
The rapid decrease of the $\delta$-numbers gives
$x^*\in B_\epsilon(x_0)$ and  the
inductive construction shows that
$x^*$ does not belong to the union
$F^*$.






\bigskip

\noindent
{\bf {2.3 Exercise.}}
Prove Theorem 2.1 using Baire's result.


\bigskip

\noindent
{\bf 2.4 Separable Banach spaces.}
A Banach space $X$ which
which contain a denumerable and dense subset $\{x_n\}$
is called separable.
If this holds we get for each
$n$ the finite dimensional subapce
$X_n$ generated by
$x_1,\ldots,x_n$
By a wellknown procedure from  Linear algebra we can
construct a basis in each $X_n$ and
construct
a denumarable sequence of linearly independent vectors
$e_1,e_2,\ldots$ such that the increasing sequence of subspaces
$\{X_n\}$ are  contained in
the vector space
\[
X_*= \oplus \,\bf{R}\cdot e_n\tag{i}
\]
Then  $X_*$ is a dense subspace of $X$.
Of course, there are many ways to construct a denumerable
sequence of linearly independent vectors which 
give a dense subspace of $X$.
One may ask if it is possible to choose
a sequence $\{e_n\}$ as above such that
every $x\in X$ can be expanded  as follows:
\medskip


\noindent
{\bf {2.5 Definition.}}
\emph{A denumerable sequence $\{e_n\}$
of ${\bf{C}}$-linearly independent vectors
in a complex vector space $X$
is called a Schauder basis 
if there to each $x\in X$
exists a unique sequence of complex  numbers
$c_1(x),c_2(x),\ldots$ such that}
\[
\lim_{N\to \infty}\,
||x-\sum_{n=1}^{n=N}\, c_\nu(x)\cdot e_\nu||=0
\]
\medskip

\noindent
{\bf 2.6 Enflo's example.}
The existence of a Schauder basis in every separable Banach space
appears to be natural and 
Schauder constructed such a basis in 
the Banach space
${\bf{C}}^0[0,1]$ of continuous functions on the closed unit interval 
equipped with the maximum norm.
For several decades the question of existence of a Schauder basis in
every separable Banach space was open until
Per Enflo at seminars in Stockholm University
during  the autumn in   1972 presented an
example where a Schauder basis does not exist.
For the  construction
we refer to the   article [Enflo-Acta Mathematica]. Let us  remark  that
the essential ingredient in Enflo's construction relies upon
a study of Fourier series where one
has  \emph{Rudin-Schapiro} polynomials
which consist of trigonometric polynomials
\[ 
P_N(x)=\epsilon_0+\epsilon_1e^{ix}+\ldots+\epsilon_N\cdot e^{iNx}\tag{*}
\]
where each $\epsilon_\nu$ is +1 or -1.
For any such sequence  Plancherel's equality gives
\[ 
\frac{1}{2\pi}\int_=^{2\pi}\, |P_n(x)|^2\cdot dx= 2^{N+1}
\]
This implies that
the maximum norm of
$|P(x)|$ is at least $2^{\frac{N+1}{2}}$.
In [Ru-Sch] it is shown  that
there exists a fixed constant
$C$ such that to every $N\geq 1$ there exists at least one
choice of
signs of the $\epsilon_\bullet$-sequence so that
\[
\max_{0\leq x\leq2\pi}\, |P_N(x)|\leq C\cdot
2^{\frac{N+1}{2}}
\]
\medskip

\noindent
{\bf Remark.}
After  [Enflo]
it became a veritable industry to
verify that various concrete Banach spaces $Y$
do have a Schauder basis and perhaps more important, also enjoy the
approximation property , i.e. that 
the class of linear operators on $Y$ with
finite dimensional range is dense in the linear
space of all compact
operators on $Y$. Fortunately most Banach spaces 
do have a Schauder basis. But the construction of a specific Schauder basis
is 
often non-trivial. It requires for example considerable work to exhibit a 
Schauder basis in the disc algebra 
$A(D)$ of continuous functions on the closed unit disc which
are analytic in the interior.





\newpage

\centerline {\bf 3. Bounded linear operators.}
\medskip

\noindent
Let $X$ and $Y$ be two normed spaces and 
$T\colon\,X\to Y$  a linear operator. We say that
$T$ is continuous if there exists a constant $C$ such that
\[ 
||T(x)||\leq C\cdot ||x||
\]
where the norms on $X$ respectively $Y$ appear.
Denote by $\mathcal{L}(X,Y)$ the set of all continuous linear operators
from $X$ into $Y$.
This yields a vector space  equipped with
the norm:
\[
||T||=\max_{||x||=1}\, ||T(x)||\quad\colon\,
T\in\mathcal{L}(X,Y)
\tag{*}
\]
Above  $X$ and $Y$ are not necessarily Banach spaces.
But one verifies easily that if
$\widehat X$ and $\widehat Y$ are their completitions, then
every $T\in\mathcal{L}(X,Y)$ extends in a unique way
to a continuous linear operator
$\hat T$ from $\hat X$ into $\hat Y$. Moreover, if $Y$ from the start is a Banach space
and $T\in\mathcal L(X,Y)$ then it extends in a unique way to a
bounded 
linear operator from
$\widehat X$ into $\widehat Y$.
Finally the reader may verify the following:

\medskip

\noindent
{\bf 3.1 Proposition.}
\emph{If $Y$ is a Banach space then
the  norm on
$\mathcal {L}(X,Y)$ is complete, i.e. this
normed vector space is a Banach space.}
\medskip

\noindent
{\bf {3.2 Null spaces and the range.}}
Let $X$ and $Y$ be two Banach spaces and
$T\in\mathcal{L}(X,Y)$. In $X$ we get the subspace
\[
\mathcal{N}(T)=\{ x\colon\, T(x)=0\}
\]
Since $T$ is continuous 
the kernel is a closed subspace of $X$ and we
get the quotient space
\[
\bar X=\frac{X}{\mathcal{N}(T)}
\]
It is clear  that $T$ yields a linear operator
$\bar T$ from $\bar X$ into $Y$ which by the construction of
the quotient norm on $\bar X$ has the same norm as
$T$.
Next, consider the range  $T(X)$ and notice the equality
\[ 
T(X)=\bar T(\bar X)\tag {i}
\]
One says that $T$ has  \emph{closed range} if the linear subspace
$T(X)$ of $Y$ is closed. When this holds
the complete norm on $Y$ induces a complete
norm on  $T(X)$. 
In addition,
$T(X)$is equipped with
the norm defined by
\[
||y||_*=||\bar x||\quad\colon\quad y=\bar T(\bar x)
\]
It is clear that
\[
||y||_*\leq ||\bar T||\cdot ||y||=
 ||T|||\cdot ||y||
 \]
 Ths, up to a constant the complete norm majorises then
 norm in (xx). The
Banach-Steinhaus theorem applies and gives a constant
$C$ such that
\[
||y||\leq C\cdot ||y||_*
\]


\noindent
This means that
if $y\in T(X)$ 
, then there exists
$x\in X$ such that
\[
y=T(x)\quad\colon\quad ||x||\leq C\cdot ||y||\tag{*}
\]
\medskip

\noindent 
{\bf Remark.}
The inequality (*) implies that
if $\epsilon>0$ and $B_X(\epsilon)= \{||x||<\epsilon\}$, then
$T(B_X(\epsilon)$ is an open neighborhood of
the origin in the Banach space $T(X)$.
Thus, (*) gives the so called  \emph{Open Mapping Theorem}. 
\bigskip

\noindent
{\bf 3.4 The closed graph theorem }
Let $X$ and $Y$ be Banach spaces and let $T$ be a linear
operator from $X$ into $Y$. For the moment we do not assume that it is bounded.
In the product space $X\times Y$ we get the graph
\[
\Gamma_T=\{(x,T(x))\quad\colon\, x\in X\}
\]

\noindent
{\bf 3.5 Theorem.}
\emph{Let $T$ be a linear operator from one Banach space $X$ into another 
Banach space $Y$
with a closed graph $\Gamma_T$. Then $T$ is continuous.}
\medskip


\noindent
\emph{Proof.}
Notice that
\[
\mathcal{N}(T)=
\{ x\colon\, (x,0)\in\Gamma_T\}\tag{i}
\]
The hypothesis that
$\Gamma_T$ is a closed subset of $X\times Y$
obviously implies that
$\mathcal{N}(T)$ is a closed subspace of $X$ which gives
the Banach space $X_*=\frac{X}{\mathcal{N}(T)}$ and
a \emph{bijective} linear map:
\[ 
\mathfrak{i}\colon\,\bar x\mapsto (\bar x,T(\bar x))\tag{ii}
\]
from $X_*$ into $\Gamma_T$.
A complete norm on 
the closed graph $\Gamma_T$ is defined by
\[
||(\bar x,T(\bar x)||=||\bar x||+||T(\bar x)||\tag{ii}
\]
Theorem 3.3 XX  applies
to $\mathfrak{i}$
and proves that the inverse map is continuos. This gives a constant
$C$ such that
\[
||\bar x||+||T(\bar x]||\leq C\cdot ||\bar x||\implies
||T(\bar x]||\leq C\cdot ||\bar x||\tag{iii}
\]
By the observation in XX this implies that
$T$ is  bounded with  an operator norm $\leq C$.

\bigskip

\centerline {\bf 3.6 Densely defined and closed operators.}
\medskip

\noindent
Let $X_*\subset X$ be a dense subspace and
$T\colon\, X_*\to Y$
a linear operator where  $Y$ is a Banach space. As above we construct the graph
\[
\Gamma_T=\{(x,y)\colon\quad x\in X_*\,\colon\, y=T(x)\}
\]
If $\Gamma_T$ is a closed subspace of $X\times Y$.
we say that the densely defined operator
$T$  also is  closed. 
\medskip

\noindent
{\bf 3.7 Example.}
Let $X=C^0_*[0,1]$
be Banach space whose elements are continuous functions
$f(x)$ on the closed interval $[0,1]$ with $f(0)=0$.
The space $X_*=C^1_*[0,1]$ of continuously differentiable functions
appears as a dense subspace of $X$.
Let $Y=L^1[0,1]$ which gives
a linear map $T\colon\, X_*\to Y$ defined by
\[ 
T(f)=f'\quad\colon\quad f\in C^1_*[0,1]\tag{i}
\]
Now $T$ has a graph
\[ 
\Gamma(T)=\{ (f,f')\quad\colon\, f\in C^1_*[0,1]\}
\tag{ii}
\]
\medskip

\noindent
Let $\overline{\Gamma(T)}$ denote the closure taken in the Banach space
$X\times Y$.
By definition a pair $(f,g)$ belongs to $\overline{\Gamma(T)}$
if and only if
\[
\exists \,\, \{f_n\}\in C^1_*[0,1]\quad\colon
\max_{0\leq x\leq 1}\, |f(x)-f_n(x)|\to 0\quad\colon \int_0^1\, |f'_n(t)-g(t)|\cdot dt=0
\]
The last limit means that
the derivatives
$f'_n$ converge to an $L^1$-function $g$.
Since $f_n(0)=0$ hold for each $n$
we have
\[
f_n(x)=\int_0^x\, f'_n(t\cdot dt\to \int_0^x\, g(t)\cdot dt
\]
Hence the  limit function $f$ is a
primitive integral
\[ 
f(x)=\int_0^x\, g(t)\cdot dt\tag{iii}
\]
\medskip

\noindent
{\bf 3.8 Conclusion}. The linear space $\overline{\Gamma(T)}$
consists of pairs
$(f,g)$ with $g\in L^1[0,T)$ and $f$ is the $g$-primitive defined by
(iii).
In this way we obtain a linear operator $\widehat{T}$ with a closed graph.
More precisely, $\mathcal D(\widehat{T})$ 
consists of  functions $f(x)$
which are primitives of $L^1$-functions. 
Lebesgue theory this means  that that the domain of definition of
$\widehat{T}$ consists of \emph{absolutely continuous functions}.
Thus, by enlarging the domain of definition the 
linear operator $T$ is extended to a densely defined and closed
linear operator.



\medskip

\noindent
{\bf{3.9 Remark.}}
The example above is typical for many constructions where one starts
with some densely defined linear operator $T$
and finds an extension $\widehat{T}$ whose graph is the
closure of $\Gamma(T)$.
The reader should  notice that the choice of the target space
$Y$ affects the construction of closed extensions.
For example, replace above
$L^1[0,1]$ with the Banach space
$L^2[0,1]$
of square integrable functions on $[0,1]$.
In this case we find a closed graph extension
$S$ whose  domain of definition  consists of
continuous functions $f(x)$ which are primitives of
$L^2$-functions.
Since the inclusion $L^1[0,1]\subset L^2[0,1]$
is strict the domain of definition for
$S$  is a proper subspace of the linear space of all
absolutely continuous functions. 
In
PDE-theory  one  starts from a
differential operator
\[
P(x,\partial)=\sum\, p_\alpha(x)\cdot\partial^\alpha\tag{*}
\]
where  $x=(x_1,\ldots,x_n)$
are coordinates in ${\bf{R}}^n$
and $\partial^\alpha$ denote the higher order differential operators
expressed by products of 
the first order operators
$\{\partial_\nu=\partial/\partial x_\nu\}$.
The coefficients $p_\alpha(x)$ are in general only 
continuous functions defined in some open subset
$\Omega$ of ${\bf{R}}^n$, though the case when
$p_\alpha$ are $C^\infty$-functions is the most frequent.
Depending upon the situation one
takes various target spaces $Y$.
For example we let $Y$ be the 
Hilbert space $L^2(\Omega)$.
To begin with
one restricts $P(x,\partial)$ to the
linear space $C_0^\infty(\Omega)$ of test-functions in
$\Omega$ and constructs the corresponding graph.
With $Y=L^2(\Omega)$
we construct a closed extension as bove.
This device is often used in PDE-theory and was
used by Weyl in  pioneering work which
for example gave existence theorems for elliptic boundary value problems.
In later work the systematic use
of "abstract functional analysis" has been used with great succes.
A result of this nature is 
\emph{GŒrding's inequality} established by
Lars GŒrding in [GŒ] and later 
extended to the so called sharp GŒrding inequality by
L. Hšrmander in [Hš]. This  illustrates the usefulness of
functional analysis, though one must not forget that
delicate parts in the  proofs rely upon "hard analysis".
See also ¤ xx for further comments related to PDE-theory.









\newpage

\centerline{\bf 4. Hilbert spaces.}
\bigskip

\noindent
{\bf Introduction.}
Euclidian geometry teaches   that if
$A$ is some  invertible $n\times n$-matrix whose elements are real
numbers and $A$ is regarded  as a linear map from
${\bf{R}}^n$ into itself, then the image of the euclidian unit sphere
$S^{n-1}$ is an ellipsoid $\mathcal E_A$. Conversely  if
$\mathcal {E}$ is an ellipsoid   there exists an invertible matrix
$A$ such that $\mathcal{E}=\mathcal{E_A}$.
\medskip

\noindent
{\bf 4.1 The case $n=2$}. 
Let $(x,y)$ be the coordinates in
${\bf{R}}^2$ and  $A$  the linear map
\[ 
(x,y)\mapsto  (x+y,y)\tag{0.1}
\]
To get the image of the unit circle  $x^2+y^2=1$ 
we use polar coordinates and write
$x=\text{cos}\,\phi$ and $y=\text{sin}\,\phi$.
This gives the closed image curve
\[ 
\phi\mapsto (\text{cos}\phi+\text{sin}\phi\,;\,\text{sin}\phi)
\quad\colon|\quad 0\leq\phi\leq 2\pi\tag{i}
\]
It is not obvious  how to  determine the principal axes of
this ellipse. The gateway is to consider the
\emph{symmetric} $2\times 2$-matrix $B=A^*A$.
If $u,v$ is a pair of vectors in ${\bf{R}}^2$ we have
\[
\langle Bu,v\rangle=\langle Au,Av\rangle\tag{ii}
\]
It follows that $\langle Bu,u\rangle>0$ for all $u\neq 0$. By
a wellknown result in elementary geometry it means that the symmetric matrix
$B$ is positive, i.e. the eigenvalues arising from zeros of
the characteristic polynomial $\text{det}(\lambda E_2-B)$
are both positive.
Moreover, the {\emph{spectral theorem} for symmetric matrices
shows that there exists an orthonormal basis in
${\bf{R}}^2$ given by a pair of eigenvectors for $B$ denoted by
$u_*$ and $v_*$. So here

\[ 
B(u_*)=\lambda_1\cdot u_*\quad\colon\quad
B(v_*)=\lambda_2\cdot v_*
\]
Next, since $(u_*,v_*)$ is an orthonormal basis in
${\bf{R}}^2$ points on the unit circle are
of the form
\[
\xi=
\text{cos}\phi\cdot u_*+
\text{sin}\phi\cdot v_*
\]
Then we get
\[
|A(\xi)|^2=
\langle A(\xi).A(\xi)\rangle=\langle B(\xi),\xi)=
\text{cos}^2\phi\cdot \lambda_1+
\text{sin}^2\phi\cdot \lambda_2
\]
From this we see that the ellipse $\mathcal E_A$ has $u_*$ and
$v_*$ as principal axes. It is a circle if and only if
$\lambda_1=\lambda_2$. If $\lambda_1>\lambda_2$
the largest principal axis has length $2\sqrt{\lambda_1}$ 
and the smallest has length $2\sqrt{\lambda_2}$. The reader should
now compute the specific example (*) and find
$\mathcal E_A$. 
\medskip

\noindent
{\bf 4.2 A Historic Remark.}
The fact that $\mathcal E_A$ is an ellipsoid was  wellknown in
the Ancient Greek mathematics when $n=2$ and $n=3$.
 After  general matrices and their determinants were introduced,
the spectral theorem for symmetric matrices was 
established by A. Cauchy in
1810 under the assumption that the eigenvalues are different. Later
Weierstrass found the proof in the general case, and independently Gram
and Weierstrass  found a method to
produce an  
orthonormal basis of eigenvectors for
a given symmetric $n\times n$-matrix $B$. To find an  eigenvector with
largest eigenvalue one studies the extremal problem
\[ 
\max_x\,\langle Bx,x\rangle\quad\colon\quad||x||=1\tag{1}
\]
If a unit vector $x_*$ maximises
(1) then it is an eigenvector, i.e.
\[ 
Bx_*=a_1x_*
\] 
holds for a real number $a$.
In the next stage one takes the orthogonal complement $x_*^\perp$
and proceed to  the restricted extremal problem
where $x$ say in this orthogonal complement which gives  an eigenvector
whose eigenvalue $a_2\leq a_1$. After $n$ steps we obtain an
$n$-tuple of pairwise orthogonal eigenvectors to $B$.
In the orthonormal basis given by this $n$-tuple the linear operator of $B$ is
represented by a diagonal matrix.

\medskip

\noindent
{\bf{Singular values.}}
\emph{Mathematica} has implemented programs which for every
invertible $n\times n$-matrix $A$ determines the
ellipsoid $\mathcal E_A$ numerically. This is presented under the headline
\emph{singular values for matrices}. In general
the $A$-matrix  is not symmetric but  the spectral theorem
is applied to the symmetric matrix $A^*A$ 
which  determines
the ellipsoid $\mathcal E_A$ and whose principal axis
are pairwise disjoint.


\bigskip

\noindent{\bf 4.3 Rotating bodies.}
The spectral theorem in dimension $n=3$ is
best illustrated by regarding a rotating body.
Consider a bounded
3-dimensional body
$K$ in which some distribution of mass is given.
The body is placed i ${\bf{R}}^3$ where
$(x_1,x_2,x_3)$ are the coordinates and the distribution of mass
is expressed by a positive function
$\rho(x,y,z)$ defined in $K$.
The \emph{center of gravity} in $K$ is the point
$(\bar x_1,\bar x_2,\bar x_3)$ where
\[ 
\bar x_\nu=\iiint_K\,x_\nu\cdot \rho(x_1,x_2,x_3)\cdot dx_1dx_2dx_3\tag{i}
\quad\colon\, 1\leq\nu\leq 3
\]
After a translation we may assume that 
the center of mass is the
origin.
Now we imagine that  a rigid bar
which stays on a  line $\ell$ is attached to $K$ with its two endpoints 
$p$ and $q$, i.e. if $\gamma$ is the unit vector
in ${\bf{R}}^3$ which determines the line
then
\[
p= A\cdot\gamma\quad\colon\quad q=-A\cdot\gamma
\]
where $A$ is so large that
$p$ and $q$ are outside $K$.
The mechanical experiment is to rotate
around $\ell$ with some constant
angular velocity $\omega$ while
the two points $p$ and $q$ are kept fixed.
The question arises if such an imposed rotation
of $K$ around $\ell$
implies that  external forces
at $p$ and $q$ are needed to prevent these to points from moving.
It turns out that there exist
so called free axes where no such forces are needed, i.e. for certain directions of
$\ell$ the body rotates nicely around
the axis with constant angular velocity.
The free axes are found from the spectral theorem.
More precisely, one introduces the symmetric 
$3\times 3$-matrix $A$ whose elements are
\[
a_{pq}=
\bar x_\nu=\iiint_K\,x_p\cdot x_q\cdot \rho(x_1,x_2,x_3)\cdot dx_1dx_2dx_3\tag{i}
\]
Using the expression for the centrifugal force
by C. Huyghen's one has the  \emph{Law of Momentum}
which in the present case shows that
the body has a free rotation along the
lines which correspond to eigenvectors of
the symmetric matrix $A$ above.
In view of the historic importance of this example we present the proof of this
in a separate section even though 
some readers may
refer to this as a subject in classical mechanics rather
than linear algebra.
Hence   the spectral theorem becomes evident by
this mechanical experiment, i.e. just as Stokes Theorem 
the spectral theorem  for symmetric matrices
is rather a Law
of Nature than a mathematical discovery.



\bigskip
\centerline {\bf 4.4 Inner product norms}
\medskip

\noindent
Let $A$ be an invertible $n\times n$-matrix.
The ellipsoid $\mathcal{E}_A$ defines a norm on
${\bf{R}}^n$ by the general construction in XX.
This norm has a special property. For if $B=A^*A$
and $x,y$ is a pair of $n$-vectors, then
\[
||x+y||^2=\langle B(x+y),B(x+y)\rangle
=||x||^2+||y||^2+2\cdot B(x,y)\tag{i}
\]
It means that the map
\[ (x,y)\mapsto 
||x+y||^2-||x||^2-||y||^2\tag{ii}
\]
is linear both with respect to $x$ and to $y$, i.e. it is a
bilinear map given by
\[
(x,y)\mapsto 2\cdot B(x,y)\tag{iii}
\]
We leave as an exercise for the reader to prove that if
$K$ is a symmetric convex set in
${\bf{R}}^n$
defining the $\rho_K$-norm as in xx, then this norm
satisfies the bi-linearity (ii) if and only if
$K$ is an ellipsoid and therefore  equal to  $\mathcal{E}_A$
for an invertible $n\times n$-matrix $A$.
Following Hilbert we refer to a norm
defined by some bilinear form $B(x,y)$ as an
\emph{inner product norm.}
The spectral theorem asserts that there exists
an orthonormal basis in ${\bf{R}}^n$ with respect to this norm.
\medskip

\noindent
{\bf 4.5 The complex case.}
Consider a  Hermitian matrix
$A$,  i.e an $n\times n$-matrix with complex elements
satisfying
\[ 
a_{qp}=\bar a_{pq}\quad\colon\quad 1\leq p,q\leq n\tag{*}
\]
Consider the $n$-dimensional complex vector space
${\bf{C}}^n$
with the basis $e_1,\ldots,e_n$.
An inner product is defined by
\[
\langle x,y\rangle=x_1\bar y_1+\ldots+x_n\bar y_n\tag{**}
\]
where 
$x_\bullet=\sum x_\nu\cdot e_\nu$
and
$y_\bullet=\sum y_\nu\cdot e_\nu$
is a pair of complex $n$-vectors.
If $A$ as above is a Hermitian matrix we obtain
\[
\langle Ax,y\rangle=\sum \sum a_{pq}x_q\cdot \bar y_p
\sum \sum \, x_p\cdot \bar a_{qp}\bar y_q=
\langle x,Ay\rangle\tag{***}
\]
\medskip

\noindent
Let us consider the characteristic polynomial
$\text{det}(\lambda\cdot E_n-A)$. If
$\lambda$ is a root there exists a non-zero eigenvector
$x$ such that
$Ax=\lambda\cdot x$. Now (***) entails that
\[
\lambda\cdot ||x||^2=
\langle Ax,x\rangle=
\langle x, Ax\rangle=\bar \lambda\cdot ||x||^2
\]
It follows that $\lambda$ is \emph{real}, i.e. the roots of the
characteristic polynomial of a Hermitian matrix are always
real numbers.
If all  roots are $>0$ one say that
the Hermitiain matrix is \emph{positive}.
\medskip

\noindent
\emph {4.6 Unitary matrices.}
An $n\times n$-matrix $U$ is called unitary if
\[
\langle Ux,Ux\rangle=\langle x,x\rangle
\]
hold for all $x\in{\bf{C}}^n$.
The spectral theorem for Hermitian  matrices asserts that if
$A$ is Hermitian then there exists a unitary
matrix $U$ such that
\[ 
UAU^*=\Lambda
\] 
where $\Lambda$ is a diagonal matrix whose elements are real.




\bigskip

\centerline{\bf  4.7 The passage to infinite dimension.}
\medskip

\noindent
Around 1900 the need for a spectral theorem in infinite dimensions
became  urgent.
In his article \emph{Sur une nouvelle mŽthode pour la resolution
du problme de Dirichlet} from 1900,
Ivar Fredholm extended earlier construction by Volterra and
studied  
systems of linear equations in an infinite number
of variables with certain bounds.
In Fredholm's investiagations one starts
with a sequence of matrices $A_1,A_2,\ldots$ where
$A_n$ is an $n\times n$-matrix and an infinite dimensional vector space
\[ 
V=
{\bf{R}}e_1+
{\bf{R}}e_2+\ldots
\]
To each $N\geq 1$ we get the finite dimensional subspace
$V_N={\bf{R}}e_1+\ldots
{\bf{R}}e_N$.
Now $A_N$ is regarded as a linear operator on $V_N$ and we assume that
the $A$-sequence is matching , i.e. if $M>N$ then
the restriction of $A_M$ to $V_N$ is equal to $A_N$.
This means   that we take  any infinite matrix $A_\infty$ with elements 
$\{a_{ik}\}$ and here $A_N$ is the $N\times N$-matrix
which appears as an upper block with $N^2$-elements
$a_{ik}\,\colon\,1\leq i,k\leq N$.
To each $N$ 
the ellipsoid $\mathcal {E}_N=\mathcal{E}_{A_N}$ on $V_N$ where 
defines a norm.
As $N$ increases the norms are matching
and hence  $V$ is equipped with a norm
which for every $N\geq 1$ restricts to the norm defined by $\mathcal E_N$
on the finite dimensional subspace $V_N$. Notice that
the norm of any vector $\xi\in V$
is finite  since $\xi$ belongs to $V_N$ for some $N$, i.e. by
definition any vector in $V$ is a finite
${\bf{R}}$-linear combination of the basis vectors
$\{e_\nu\}$.
Moreover, the norm on $V$ satisfies the
bilinear rule from (0.3), i.e. on $V\times V$
there exists a bilinear form $B$ such that
\[ 
||x+y||^2-||x||^2-||y||^2=2B(x,y)\quad\colon\quad
x,y\in V\tag{*}
\]
\medskip

\noindent
{\bf Remark.}
Inequalities for determinants
due to Hadamard play an important role in
Fredholm's work and since the Hadamard inequalities are used
in many other situations we 
announce some of his results, leaving proofs as an exercise or
consult the literature where an  excellent source is the introduction to integral equations by
the former professor at Harvard University
Maxime Bochner [Cambridge University Press: 1914):
\medskip

\noindent
{\bf 4.8 Two inequalities.} Let
$n\geq 2$ and $A=\{a_{ij}\}$  some
$n\times n$-matrix whose elements are real numbers.
Show that if
\[ a_{i1}^2+\ldots+a_{in}^2=1\quad\colon\quad 1\leq i\leq n
\]
then the determinant of $A$ has absolute value $\leq 1$.
Next, assume that there is a constant $M$ such that the absolute values
$|a_{ij|}|\leq M$ 
hold for all pairs $i,j$. Show that this gives
\[ 
\bigl|\text{det}(A)\bigr |\leq \sqrt{n^n}\cdot M^n
\]
 



\medskip

\noindent
{\bf 4.9 The Hilbert space $\mathcal{H}_V$}.
This is the completition of the normed space $V$.
That is, exactly as when the field of rational numbers is
completed to the real number system one regards Cauchy sequences for the norm
of vectors in $V$ and in this way we get  a  normed
vector space denoted by $\mathcal{H}_V$ where the norm topology is complete.
Under this process the bi-linearity is preserved, i.e.
on $\mathcal{H}_V$ there exists  a bilinear form $B_{\mathcal{H}}$ such that
(*) above holds for pairs $x,y\in\mathcal {H}_V$.
Following Hilbert we refer to
$B_{\mathcal{H}}$ as the  \emph{inner product}
attached to the norm.
Having performed this construction starting from any
infinite matrix $A_\infty$ it is tempting to make a further abstraction. 
This is precisely
what Hilbert did, i.e. he ignored the "source" of a matrix $A_\infty$
and defined a complete normed vector space over
${\bf{R}}$ to be  a real Hilbert space if the there exists a bilinear form
$B$ on $V\times V$ such that (*) holds. 
\medskip

\noindent
{\bf {Remark.}}
If $V$ is a "abstract"  Hilbert space the restriction of the norm to
any finite dimensional subspace $W$ is determined by
an ellipsoid and  exactly as in linear algebra  one constructs an orthonormal basis
on $W$.
By the Gram-Schmidt 
construction there exists
an orthonormal sequence $\{e_n\}$ in $V$.
However, in order to be sure that it suffices to take a
\emph{denumerable} orthonormal basis it is necessary and sufficient that
the normed space $V$ is \emph{separable}.
Assuming this  every $v\in V$ has a unique
representation
\[ 
v=\sum\, c_n\cdot e_n\quad\colon\, \sum\, |c_n|^2=||v||^2\tag{i}
\]
\medskip

\noindent
The existence of this orthonormal family  means that every
separable Hilbert space is isomorphic to
the standard space $\ell^2$ whose vectors are infinite sequences
$\{c_n\}$ where the square sum $\sum\, c_n^2<\infty$.
So in order to prove general results about separable Hilbert spaces
it is  sufficient to regard
$\ell^2$. However,  the abstract notion of a Hilbert space
is useful since inner products on 
specific linear spaces
appear in many different situations. 
For example, in complex analysis  an
example occurs when  we regard the space
of analytic functions which are square 
integrable on a domain or
whose boundary values are square integrable.
Here  the inner product
is given in advance but it can be  a highly non-trivial affair to exhibit
an orthonormal basis.

\medskip

\noindent
{\bf 4.10 Linear operators on $\ell^2$.}
A bounded linear operator
$T$ from the complex Hilbert space $\ell^2$ into itself is
described by an infinite matrix
$\{a_{p,q}\}$ whose elements are complex numbers. Namely, 
for each $p\geq 1$ we set
\[ T(e_p)=\sum_{q=1}^\infty\, a_{pq}\cdot e_q\tag{i}
\]
For each fixed $p$ we get
\[
||T(e_p)||^2=\sum_{q=1}^\infty\, |a_{pq}[^2\tag{ii}
\]


\noindent
Next,
let $x=\sum\,\alpha_\nu\cdot e_\nu$
and $y=\sum\,\beta_\nu\cdot e_\nu$ be two vectors in
$\ell^2$. Then we get
\[
||x+y||^2=\sum\, |\alpha_\nu+\beta_\nu|^2\cdot e_\nu
\]
For each $\nu$ we have the pair of complex numbers
$\alpha_\nu,\beta_\nu$ and here
we have the inequality
\[
|\alpha_\nu+\beta_\nu|^2\leq  2\cdot |\alpha_\nu|^2+2\cdot |\beta_\nu|^2
\]
It follows that
\[
||x+y||^2\leq 2\cdot ||x||^2+2\cdot||y||^2\tag{iii}
\]


\noindent
In (iii) equality holds if and only if the
two vectors $x$ and $y$ are linearly dependent, i.e. if there
exists some complex number $\lambda$ such that
$y=\lambda\cdot x$.
Let us now return to the linear operator $T$.
In (ii) we get an expression for
the norm of the $T$-images of the orthonormal basis
vectors. So when $T$ is bounded with  operator norm
$M$ then the sum of the squared absolute values in each row
of the matrix $A=\{a_{p,q}\}$ is $\leq M^2$.
However, this condition along is not sufficient to
guarantee that
$T$ is a bounded linear operator. For example, suppose that
the row vectors in $T$ are all equal to a given
vector in $\ell^2$, i.e. $a_{p,q}=\alpha_q$ hold for all pairs where
$\sum,|\alpha_q|^2=1$.
Then
\[ 
T(e_1+\ldots+e_N)=N\cdot v\quad\colon\quad
v=\sum\,\alpha_q\cdot e_q
\]
The norm in the right hand side is $N$ while the norm
of $e-1+\ldots+e_n$ is $\sqrt{N}$. Since
$N>>\sqrt{N}$ when $N$ increases this shows that
$T$ cannot be bounded. So the condition on
the matrix $A$ in order that
$T$ is bounded is more subtle.
In fact, given a vector $x=\sum\,\alpha_\nu\cdot e_\nu$ as above with
$||x||=1$ we have
\[ 
||T(x)||^2=\sum_{p=1}^\infty\, 
\sum_q\sum_k\, a_{p,q}\cdot\alpha_q\cdot\bar a_{pk}\cdot\bar \alpha_k\tag{*}
\]


\noindent
So we encounter an involved triple sum.
Notice also that for each fixed $p$ we get a \emph{non-negative}
term 
\[ 
\rho_p=
\sum_q\sum_k\, a_{p,q}\cdot\alpha_q\cdot\bar a_{pk}\cdot\bar \alpha_k=
\bigl| \sum_{q=1}^\infty\, a_{pq}\cdot\alpha_q\,\bigr|^2
\]
\medskip

\noindent
{\bf Final remark.}
Thus, the description of the Banach space
$L(\ell^2,\ell^2)$ of all bounded
linear operators on
$\ell^2$ is not easy to grasp. In fact, no
"comprehensible" description exists of this space.






\bigskip

\centerline {\bf 4.11 General  results on Hilbert spaces.}
\medskip

\noindent
Let $\mathcal H$  be  a real Hilbert space.
The construction of the inner product norm entails  that
\[
||x+y||^2+||x-y||^2=
2\cdot ||x||^2+2\cdot ||y||^2\tag{*}
\]
for every pair $x,y$ in $\mathcal H$.
Using this one solves an extremal problem.
For every  closed convex subset $K$ of
$\mathcal H$ and if $\xi\in \mathcal H\setminus K$  there exists a unique
$k_*\in K$ such that
\[
\min_{k\in K}\,||\xi-k||=||\xi-k_*||\tag{**}
\]
To prove (**) 
we let
$\rho$ denote  the minimal distance.
We find a sequence $\{k_n\}$ in $K$ such that
$||\xi-k_n||\to\rho$. Now we show that 
$\{k_n\}$ is a Cauchy sequence. For let 
$\epsilon>0$ which gives some integer  $N_*$ such that
\[
||\xi-k_n||<\rho+\epsilon\quad\colon\quad n\geq N_*\tag{i}
\]
The convexity of $K$ implies that
if $n,m\geq N_*$ then $\frac{k_n+k_m}{2}\in K$. 
Hence 
\[
\rho^2\leq ||\xi-\frac{k_n+k_m}{2}||^2\implies
4\rho^2\leq ||(\xi-k_n)+(\xi-k_m]||^2\tag{ii}
\]
By the identity (*) the right hand side is
\[
2||\xi-k_n||^2+2||\xi-k_m||^2-||k_n-k_m||^2\tag{iii}
\]
It follows from (i-iii) that
\[
||k_n-k_m||^2\leq 4(\rho+\epsilon)^2-4\rho^2=
8\rho\cdot\epsilon+4\epsilon^2
\]
Since $\epsilon$ can be made arbitrary small
$\{k_n\}$ is a Cauchy sequence and hence 
there exists a limit $k_n\to k_*$ where $k_*\in K$
since $K$ is closed.
Finally, the  uniqueness of $k_*$ 
follows from the equality
\[
||\xi-k_1||^2+||\xi-k_2||^2=
2\cdot ||\xi-\frac{k_1+k_2}{2}||^2+\frac{1}{2}\cdot ||k_1-k_2||^2
\]
for every pair $k_1,k_2$ in $K$. In fact, this equality entails that if
$\epsilon>0$ and 
$k_1,k_2$ is a pair such that
\[
||\xi-k_\nu||\leq \rho^2+\epsilon\quad\colon\, \nu=1,2
\]
then we have
\[
||k_1-k_2||^2\leq 4\epsilon
\]
from which the uniquness of $k_*$ follows.

\bigskip

\noindent
{\bf 4.12 The decomposition theorem.}
Let $V$ be a closed subspace of $H$.
Its orthogonal complement is defined by
\[ 
V^\perp=\{x\in H\quad\colon\,\langle x,V\rangle=0\}\tag{i}
\]
It is obvious that $V^\perp$ is a closed subspace of $H$
and that $V\cap V^\perp=0$.
There remains to prove the equality
\[ 
H=V\oplus\, V^\perp\tag{ii}
\]
To see this we take some $\xi\in H\setminus V$. 
Now $V$ is a closed convex set so we find $v_*$ such that
\[ 
\rho=||\xi-v_*||=\min_{v\in V}\,||\xi-v||\tag{iii}
\]
If we prove that $\xi-v_*\in V^\perp$ we get (ii).
To show this we consider  some $\eta\in V$. If
$\epsilon>0$ we have
\[
\rho^2\leq ||\xi-v_*+\epsilon\cdot\eta||^2=
||\xi-v_*||^2+\epsilon^2 \cdot||\eta||^2+
\epsilon\langle \xi-v_*,\eta\rangle
\]
Since $||\xi-v_*||^2=\rho^2$ and $\epsilon>0$ it follows that
\[
\langle \xi-v_*,\eta\rangle+\epsilon \cdot||\eta||^2\geq 0
\]
here $\epsilon$ can be arbitrary small and we conclude that
$\langle \xi-v_*,\eta\rangle\geq 0$. Using 
$-\eta$ instead we get the 
opposed inequality and hence
$\langle \xi-v_*,\eta\rangle=0$ as required.

\bigskip

\noindent
{\bf 4.13 Complex Hilbert spaces.}
On a complex vector space  similar results as above hold
provided that 
we regard convex sets which
are ${\bf{C}}$-invariant. We leave details to the reader
and refer to the literature  for a more detailed account about
general properties on Hilbert spaces.
See for example the text-book [Hal] by P. Halmos - a former student to
J. von Neumann - which in addition to theoretical
results contains
many interesting exercises.
\newpage

\centerline{\bf{4:B. Eigenvalues of matrices.}}

\bigskip

\noindent
Using  the Hermitian inner product on ${\bf{C}}^n$
we study
eigenvalues of an $n\times n$-matrices $A$ with complex elements.
The  spectrum $\sigma(A)$ is the $n$-tuple of roots
$\lambda_1,\ldots,\lambda_n$ of the characteristic polynomial
$P_A(\lambda)=\text{det}(\lambda\cdot E_n-A)$,
where eventual multiple eigenvalues are
repeated.
\medskip


\noindent
{\bf{4:B.1 Polarisation.}}
Let $A$ be an arbitrary $n\times n$-matrix.
Then there exists a unitary matrix
$U$ such that the matrix 
$U^*AU$ is upper triangular. To prove this
we first use the wellknown fact that there exists
a basis
$\xi_1,\ldots,\xi_n$ in ${\bf{C}}^n$
in which $A$ is upper triangular, i.e. 
\[ 
A(\xi_k)= a_{1k}\xi_1+\ldots a_{kk}\xi_k\quad\colon\,,1\leq k\leq n
\]
The \emph{Gram-Schmidt orthogonalisation}
gives
an orthonormal basis $e_1,\ldots,e_n$ where
\[ 
\xi_k=c_{1k}\cdot e_1+\ldots c_{kk}\cdot e_k\quad\text{for each}
\quad 1\leq k\leq n
\]
Let $U$ be  the unitary matrix which sends the standard basis in
${\bf{C}}^n$ to the $\xi$-basis. Now the
reader can  verify that the linear operator 
$U^*AU$ is  represented by an upper triangular matrix in the $\xi$-basis.





\medskip


\noindent
\emph{A theorem by H. Weyl.}
Let $\{\lambda_k\}$ be the spectrum of $A$ where the $\lambda$-sequence is
chosen with non-increasing absolute values, i.e. 
$|\lambda_1|\geq \ldots\geq |\lambda_n|$. 
We  have also the Hermitian matrix $A^*A$ which is non-negative so that
$\sigma(A^*A)$ consists of non-negative real numbers
$\mu_1\geq \mu_2\geq\ldots\geq \mu_n$. 
In particular one has 
\[ 
\mu_1=\max_{|x|=1}\, \langle Ax,Ax\rangle\tag{1}
\]
\medskip



\noindent
{\bf{4:B.2 Theorem.}}
\emph{For every $1\leq p\leq n$ one has the inequality}
\[
|\lambda_1\cdots\lambda_p|\leq \sqrt{\mu_1\cdots \mu_p}
\]
\emph{where $\{\mu_k\}$ are the eigenvalues of $A^*A$}


\medskip


\noindent
First
we consider the  case $p=1$ and prove the inequality
\[ 
|\lambda_1| \leq \sqrt{\mu_1}\tag{i}
\]


\noindent
Since $\lambda_1$ is an eigenvalue there exists
a vector $x_*$ with $|x_*|=1$ so that
$A(x_*)=\lambda_1\cdot x_*$. It follows from (1) above
that
\[
\mu_1\geq \langle A(x_*),A(x_*)\rangle=|\lambda_1|^2
\]

\medskip

\noindent
{\bf{Remark.}}
The inequality is in general strict.
Consider the $2\times 2$-matrix
\[ 
A= 
\begin{pmatrix}
1& a\\ 0&b
\end{pmatrix}
\]
where $0<b<1$  and $a\neq 0$ some complex number
which gives
\[ 
A^*A= \begin{pmatrix}
1& a\\ a&a^2+b^2
\end{pmatrix}
\]
Here $\lambda\uuu 1=1$ and the eigenvector $x\uuu *=e\uuu
1$ and we see that
$\langle A(x_*),A(x_*)\rangle=1+|a|^2$.


\bigskip

\noindent
\emph{Proof when $p\geq 2$}
We employ a construction of independent interest.
Let $e_1,\ldots,e_n$ be some orthonormal basis in
${\bf{C}}^n$. For   every $p\geq 2$ we get 
the inner product space $V^{p}$ whose vectors are
\[ 
v=\sum\, c_{i_1,\ldots,i_p}\cdot e_{i_1}\wedge\ldots\wedge e_{i_p}
\]
where the sum extends over $p$-tuples $1\leq i_1<\ldots<i_p$.
This is an inner product   space of dimension $\binom{n}{p}$
where $\{e_{i_1}\wedge\ldots\wedge e_{i_p}\}$ is an orthonormal basis.
Consider a linear operator $A$ on ${\bf{C}}^n$
which in the $e$-basis is represented by a matrix
with elements
\[ 
a_{ik}=\langle Ae_i,e_k\rangle
\]
If $p\geq 1$ we define the linear operaror $A^{(p)}$
on $V^{(p)}$ by
\[ 
A^{(p)}(e_{i_1}\wedge\ldots\wedge e_{i_p})=
A(e_{i_1})\wedge\ldots\wedge A(e_{i_p})=
\sum\, a_{j_1i_1}\cdots a_{j_pi_p}\cdot
e_{j_1}\wedge\ldots\wedge e_{j_p}
\]
with the sum extended over all $1\leq j_1<\ldots<j_p$.
\medskip

\noindent
\emph{Sublemma.} \emph{The eigenvalues of $A^{(p)}$
consists of the $\binom{n}{p}$-tuple given by the products}
\[ 
\lambda_{i_1}\cdots \lambda_{i_m}\quad\colon\quad
1\leq i_1<\ldots<i_p\leq n\tag{*}
\]

\medskip

\noindent
\emph{Proof.} The eigenvalues above are independent of the chosen
orthonormal basis $e_1,\ldots,e_n$ since a change of this basis gives
another orthonormal basis in $V^{(p)}$ which does not affect
the eigenvalues of $A^{(p)}$.
Using  a   polarisation from 4:B.1 we may  assume 
from the start that
$A$ is an upper  triangular matrix and   then reader can
verify (*) in the sublemma.
\bigskip

\noindent
\emph{Final part of the proof.}
If  $p\geq 2$ it is clear that  one has the equality

\[
(A^{(p)})^*\cdot A^{(p)}=(A^*\cdot A)^{(p)}\tag{i}
\]
If $\lambda_1,\ldots\lambda_p$ is the
large $p$-tuple in Weyl's Theorem the product appears
as an eigenvalue of
$A^{(p)}$ and using the case $p=1$
one gets Weyl's inequality
since
the product $\mu_1\cdots\mu_p$
appears as an eigenvalue of
$(A^*\cdot A)^{(p)}$.

\bigskip


\centerline {\emph{4.B.3 An inequality by Pick.}}
\bigskip

\noindent
Let $C=\{c_{ik}\}$ be a skew-symmetric $n\times n$-matrix, i.e. 
$c_{ik}= -c_{ki}$ hold for all pairs $i,k$.
Denote  by $g$  the maximum of the absolute values of
the matrix  elements of $C$. 

\medskip

\noindent
{\bf{4:B.4 Theorem.}} \emph{One
has the inequality}
\[
\max_{|x|=1}\, \bigl|\langle Cx,x\rangle\bigr|
\leq g\cdot \text{cot}(\frac{\pi}{2n})\cdot 
\sqrt{n(n-1)/2}\tag{*}
\]



\noindent
\emph{Proof.}
Since $g$ is unchanged if we permute the columns of the given
$C$-matrix it suffices to prove (*) for a vector $x$ of unit length such that
\[
\mathfrak{Im}(x_k\bar x_i-x_i\bar x_k)\geq 0
\quad\colon\quad 1\leq i<k\leq n\tag{1}
\]



\noindent
Now one has
\[
\langle Cx,x\rangle=
\sum\sum\, c_{ik}x_k\bar x_i=
\sum_{i<k}\, c_{ik}x_k\bar x_i+
\sum_{i>k}\,c_{ik} x_k\bar x_i=
\sum_{i<k}\, c_{ik}(x_k\bar x_i-\bar x_k x_i)
\tag{3}
\]
where the last equality follows since
$C$ is skew-symmetric. Put
\[
\gamma_{ik}=\mathfrak{Im}\,( x_k\bar x_i-\bar x_k x_i)
\]

\noindent
Then (1) and the triangle
inequality give
\[
|\langle Cx,x\rangle|\leq \sum_{i<k}\, |c_{ik}|\cdot \gamma_{ik}
\leq g\cdot \sum_{i<k}\,  \gamma_{ik}
\]
Hence there only  remains to show that
\[
\sum_{i<k}\,  \gamma_{ik}\leq 
\text{cot}(\frac{\pi}{2n})\cdot 
\sqrt{n(n-1)/2}\tag{4}
\]
To prove this we write $x_k= \alpha_k+i\beta_k$
and the reader can verify that (4) follows from the inequality
\[
\sum_{i\neq k}\, a_kb_i\leq \text{cot}(\frac{\pi}{2n})\cdot 
\sqrt{n(n-1)/2}\tag{5}
\] 
whenever $\{a_k\}$ and $\{b_i\}$ are $n$-tuples of non-negative real numbers 
for which
$\sum_{k=1}^{k=n}\, a_k^2+b_k^2=1$.
Finally, 
(4) follows when one
applies Lagrange's multiplier for extremals of a quadratic form.





\newpage


\centerline {\emph{4.B.4 Results  by A. Brauer.}}
\bigskip

\noindent
Let $A$ be an  $n\times n$-matrix. To each
$1\leq k\leq n$ we set

\[ r_k=\text{min}\,[\,\sum_{j\neq k}\, |a_{jk}|\,\colon\,
\sum_{j\neq k}\, |a_{kj}\,\bigr]
\]

\medskip
\noindent
{\bf{4:B.5 Theorem.}}
\emph{Denote by $C_k$ the closed  disc of 
of radius $r_k$ centered at the diagonal element $a_{kk}$.
Then one has the inclusion:}
\[
\sigma(A)\subset C_1\cup\ldots\cup C_n\tag{*}
\]


\noindent 
\emph{Proof.}  Consider some eigenvalue $\lambda$ so that
$Ax=\lambda\cdot x$ for a non-zero eigenvector.
It means that
\[
\sum_{j=1}^
 {j=n}\, a_{j\nu}\cdot x_\nu=\,\lambda\cdot x_j
 \quad\colon\quad 1\leq j\leq n
 \]
Choose $k$ so that $|x_k|\geq |x_j|$ for all $j$.
Now we have
\[ 
(\lambda-a_{kk})\cdot x_k=  \sum_{j\neq k}\, a_{j\nu}\cdot x_\nu\implies
|\lambda-a_{kk}|\leq \sum_{j\neq k}\, |a_{kj}|\tag{1}
\]
At the same time the adjoint $A^*$ satisfies
$A^*(x)=\bar\lambda\cdot x$ which gives
\[
\sum_{j=1}^
 {j=n}\, \bar a_{\nu,j}\cdot x_\nu=\,\bar \lambda\cdot x_j
 \quad\colon\quad 1\leq j\leq n
\] 
Exactly as above we get
\[
|\lambda- a_{kk}|=
|\bar \lambda-\bar a_{kk}|\leq \sum_{j\neq k}\, |a_{jk}|\tag{2}
\]
Hence (1-2) give the inclusion
$\lambda\in C_k$.
\medskip


\noindent
{\bf{4:B.6 Theorem.}} \emph{Assume that the closed discs $C_1,\ldots,C_n$ are disjoint.
Then the eigenvalues of $A$ are simple and for every
$k$ there is a unique $\lambda_k\in C_k$.}
\medskip


\noindent
\emph{Proof.} 
Let $D$ be the diagonal matrix where $d_{kk}=a_{kk}$.
For ever $0<s<1$ we consider the matrix

\[ 
B_s=sA+(1-s)D
\]
Here $b_{kk}=a_{kk}$ for every $k$ and the associated discs
of the $B$-matrix are $C_1(s),\ldots,C_b(s)$ where
$C_k(s)$ is again centered at $a_{kk}$ while the radius is $s\cdot r_k$.
When $s\simeq 0$ the matrix $B\simeq D$ and then it is clear that
the previous theorem implies that
$B_s$ has simple eigenvalues $\{\lambda_k(s)\}$ where
$\lambda_k(s)\in C_k(s)$  for every $k$.
Next, since the "large discs" $C_1,\ldots,C_n$ are disjoint, it follows by
continuity that these inclusions  holds for every $s$ and with $s=1$ we get
the theorem. 
\medskip

\noindent
{\bf{Exercise.}} Assume that the elements of $A$ are all real and
the discs above are disjoint. Show that the eigenvalues of $A$ are all real.

\bigskip


\centerline {\emph{ Results  by Perron and Frobenius}}
\medskip

\noindent
Let $A=\{a_{pq}\}$ be a matrix where all elements are 
real and positive.
Denote by $\Delta^n_+$ the standard simplex of $n$-tuples
$(x_1,\ldots,x_n)$ where
$x_1+\ldots+x_n=1$ and every $x_k\geq 0$.
The following result was  established by Perron in [xx]:

\medskip

\noindent
{\bf{4:B.7  Theorem.}} \emph{There exists a unique ${\bf{x}}^*\in\Delta_+^n$
which is an eigenvector for $A$ with an eigenvalue $s^*$. Moreover.
$|\lambda|<s^*$ holds for every other eigenvalue}.
\medskip


\noindent
We leave the proof as an exercise to the reader.
In [Frob] 
the following addendum to
Theorem 4:B.7 is proved.
\medskip

\noindent
{\bf{4:B.8  Theorem.}} \emph{Let $A$ as above be a positive matrix
which gives the eigenvalue $s^*$. For every complex
$n\times n$-matrix
$B=\{b_{pq}\}$ such that $|b_{pq}|\leq a_{pq}$
hold for all pairs $p,q$, it follows that
every root of $P_B(\lambda)$ has absolute value $\leq s^*$
and equality holds if and only if $B=A$.}

\bigskip


\noindent
{\bf{4:B.9 The case of probability matrices.}}
Let $A$ have positive elements and assume that the sum in every column 
is one. In this case $s^*=1$ for with ${\bf{x}}^*=(x_1^*,\ldots,x_n^*)$ we have
\[
s^*= s^*\cdot \sum\, x^*_p= \sum\sum a_{pq}\cdot x^*_q=
\sum\, x^*_q=1
\]
\medskip

\noindent
The components of the
Perron vector ${\bf{x}}^*$
yields the probabilities to arrive at a station $q$ after many
independent motions in an associated stationary Markov chain where
the $A$-matrix defines the transition probabilities.
\medskip


\noindent
{\bf{Example.}} Let $n=2$ and 
take  $a_{11}=3/4$ and $a_{21}= 1/4$, while $a_{12}=a_{22}= 1/2$.
A computation gives $s^*=2/3$ which in probabilistic terms means that the
asymptotic probability  to arrive
at station 1 after many steps is $2/3$ while that of station 2 is $1/3$.
Here we notice that the second eigenvalue is
$s_*=1/4$ and an associated eigenvector is
$(1,-2)$.
\bigskip

\noindent
{\bf{4.B.10  Extension to infinite dimensions.}}
The Perron-Forbenius result was
extended to positive operstors on Hilbert spaces by
Pietsch in the article [1912].
We refer to ¤ xx the proof.
















\newpage


\centerline {\bf\large 5. Dual vector spaces}
\medskip

\noindent
Let $X$ be a normed space over the complex field. A continuous linear form on
$X$ is a ${\bf{C}}$-linear map $\gamma$ from $X$ into ${\bf{C}}$
such that there exists a constant $C$ with:
\[
\max_{||x||=1}\,|\gamma(x)|\leq C
\]
The set of these continuous linear forms is denoted by $X^*$.
It is obvious that $X^*$ is a vector space and  the smallest constant $C$ above is 
the norm of $\gamma$. In this way $X^*$ is a normed space.
Since Cauchy-sequences of complex numbers
converge it follows easily that
$X^*$ is a Banach space.  Notice that this is true  even
if $X$ from the start is not complete.
Next, let $Y$ be a subspace of $X$.
Every $\gamma\in X^*$ can be restricted to $Y$ and gives
an element of $Y^*$, i.e. one has  the restriction map
\[ 
\mathfrak{res}_Y\colon X^*\to Y^*\tag{i}
\]
Since a restricted linear form cannot increase the norm  one has
the  inequality
\[ 
|| \mathfrak{res}_Y(\gamma)|\leq ||\gamma||\quad\colon\quad
\gamma\in X^*
\]


\noindent
{\bf The kernel  of
$\mathfrak{res}_Y$}.
The kernel is by definition the set of
$X^*$-elements which are zero on $Y$.This
gives a subspace of $X^*$ denoted by $Y^\perp$.
It can 
be identfied with the dual of
a new normed space. Namely,  consider the 
quotient space
\[
Z= \frac{X}{Y}
\]
Vectors  in $Z$ are images of vectors $x\in X$ where  a pair of 
$x_1$ and $x_2$ give the same vector in $Z$ if and only if
$x_2-x_1\in Y$.
Let $\pi_Y(x)$ denote the image of $x\in X$. Now $Z$ is 
is equipped with a norm defined by
\[
||z||=
\min_x\,||x||\quad\colon\quad z=\pi_Y(x)
\]
From the constructions above the reader can verify
tht one has  a canonical isomorphism
\[
Z^*\simeq \text{Ker}(\mathfrak{res}_y)=Y^\perp
\]
\bigskip

\noindent
{\bf 5.1 The Hahn-Banch Theorem.}
Every continuous linear form $\gamma$
on a subspace $Y$
of $X$ has a \emph{norm preserving extension}
to a linear form on $X$.
Thus, if $\gamma$  has some norm $C$,  there
exists $\gamma^*\in X$ with norm $C$ such that
\[ 
\mathfrak{res}_Y(\gamma^*)=\gamma
\]
One refers to $\gamma^*$ as a norm-preserving extension of
$\gamma$.
\medskip

\noindent
{\bf{5.2 Exercise.}} Consult a text-book for the proof or
find  the details using the following hint.
Given the pair $(Y,\gamma_*)$ we consider all pairs
$(Z,\rho)$ where $Y\subset Z\subset X$
and $\rho\in Z^*$
is such that its norm is $C$ and $\rho|Y=\gamma_*$.Thus, 
$\rho$ is a norm preserving extension of
$\gamma_*$ to $Z$.
By \emph{Zorn's Lemma} there exists a maximal pair
$(Z,\rho)$ in this family.
There remains only to show that $Z=X$ for then $\rho$ gives
the required norm-preserving extension. To prove that
$Z=X$ one argues by contradiction. Namely, suppose
$Z\neq X$ and choose a vector $x_0\in X\setminus Z$ of norm one.
Next, if  $\alpha$ is a complex number we get a
linear form on
$Z^*=Z+{\bf{C}}\cdot x_0$ defined by
\[ 
\rho_\alpha(ax_0+z)= a\cdot\alpha+\rho(z)
\]
where $a\in{\bf{C}}$ and $z\in Z$ are arbitrary.
The  contradiction follows if we can find
$\alpha$ so that the norm of $\rho_\alpha$
again is $\leq C$.
It is clear that $\rho_\alpha||\leq C$ holds if and only if
\[
|\alpha+\rho(z)|\leq C\cdot ||x_0+z||
\quad\text{hold for all}\,\, z\in Z\tag{*}
\]
At this stage the reader should be able to finish the proof.
\bigskip

\noindent
{\bf{5.3 An exact sequence}}.
Let $Y\subset X$  be a closed subspace and put
$Z=\frac{X}{Y}$.
The Hahn-Banach Theorem identifies
$Z^*$ with $Y^\perp$ and gives
an exact sequence
\[
0\to Z^*\to X
^*\to Y^*\to 0
\]
where the restriction map $X^*\to Y^*$
sends the unit ball in $X^*$ onto the unit ball of 
$Y^*$.
\bigskip

\noindent
{\bf 5.3.1 Example}
Let $X=L^1(T)$ be the normed
space of integrable functions on the unit circle.
Recall from measure theory that the dual space  $X^*=L^\infty(T)$.
Next, we have the subspace
$H^\infty(T)$ of $X^*$ of those Lebesgue measurable and bounded functions on
$T$ which are boundary values to analytic functions in
the unit disc $D$.
We have also the subspace
$Y=H^1_0(T)$ of $L^1$-functions which are boundary 
values of analytic functions which are zero at the origin. 
As explained in XXX expansions in Fourier series show that if $g\in L^\infty(T)$ then
\[
\int_0^{2\pi}\, g\cdot h\cdot d\theta=0
\quad\text{for all}\quad f\in H^1_0
\]
holds if and only if $g\in H^\infty(T)$.
This means  that
\[
H^\infty(T)=\text{Ker}(\mathfrak{res}_Y)\quad\colon\, Y=H_0^1(T)\subset
L^1(T)=X
\]
In other words
\[
H^\infty(T)\simeq\frac{L^\infty(T)}{H^1_0(T)}\tag{*}
\]

\medskip

\noindent
Consider now some $g\in L^\infty(T)$ and put
\[
C=\max_{h}|\int_0^{2\pi}\, g\cdot h\cdot d\theta\quad\colon\quad
h\in H_0^1(T)\,\,\text{and}\,\, ||h||_1=1
\]
The Hahn-Banach theorem
 gives some
$h\in H^\infty(T)$ such that
the $L^\infty$-norm  norm $||g-h||_\infty=C$. Thus, we can write
\[ 
g=h+f\tag{1}
\] 
where $h\in H^\infty$ and the $L^\infty$-function $f$
has norm $C$.
The function  $h$
is not determined because there exist 
several decompositions in (1). However, in
¤ XX we shall find a specific decompositions
of $g$ in certain cases.


\bigskip


\centerline{\bf 5.4 Weak Convergence.}

\medskip

\noindent
Let $X$ be a normed space. On the dual $X^*$ there exists a
topology where 
a fundamental system of open neighborhood of
the origin in the vector space $X^*$ is given by
\[
U(x_1,\ldots,x_N;\epsilon)=\{\gamma\in X^*\quad\colon\, |\gamma(x_\nu)|<\epsilon\quad\colon
x_1,\ldots,x_N\,\,\,\text{finite set}\}\tag{*}
\]
\medskip

\noindent
Notice that each such $U$-set is a convex subset of
$X^*$. 
Let  $Y$ be the finite dimensional subspace of
$X$ generated by $x_1,\ldots,x_n$. It is clear that the kernel of
$\mathfrak{res}_Y)$ is contained in the $U$-set above.
\medskip

\noindent
Let $k$ be the dimension of the vector space generated
by $x_1,\ldots,x_n$.
By Linear Algebra 
the kernel of $\mathfrak{res}_Y)$ has codimension $k$ in $X$.
So the $U$-set in (*) contains a subspace of $X^*$ with
finite codimension, i.e. 
the open $U$-sets in (*) are quite large
when $X$ has inifinite dimension.
One refers to the \emph{weak-star}  topology on $X^*$.
\medskip

\noindent
{\bf 5.5 The case when
$X$ is separable.}
Assume this and let
$x_1,x_2,\ldots $ be a dense   subset of $X$.
Let $B(X^*)$ denote the unit ball in
$X^*$, i.e. elements $\gamma\in X^*$ of norm
$\leq 1$.
On this unit ball we define a metric by
\medskip

\[ d(\gamma_1,\gamma_2)= \sum_{n=1}^\infty\,
2^{-n}\cdot 2^{-n}\cdot 
\frac{\bigl|\gamma_1(x_n)-\gamma_2(x_n)\bigr|}
{1+\bigl|\gamma_1(x_n)-\gamma_2(x_n)\bigr|}
\tag{5.5.1}
\]
\medskip


\noindent
{\bf{Exercise.}} Verify that the weak-start topology induces
a topology $B(X^*)$ which is equal to the
topology defined by the metric above.
So in particular the topology defined by the metric in
(5.5.1) does not depend upon the chosen dense subsequence in $X$.


\medskip


\noindent
{\bf{5.6 Theorem.}}
\emph{The metric space $B(X^*)$ is compact.}
\medskip

\noindent
\emph{Proof.} 
Let $\{\gamma_k\}$ be a sequence in
$B(X^*)$.
To every $j$ we get the bounded sequence of complex numbers
$\{\gamma_k(x_j)\}$.
By the wellknown diagonal construction there exists
a strictly increasing sequence $k_1<k_2<\ldots$ such that
if $\rho_\nu=\gamma_{k_\nu}$
then
\[
\lim_{\nu\to\infty}\, \rho_\nu(x_j)\tag{*}
\]
exists for every $j$.
Since every $\rho_j$ has norm $\leq 1$ and $\{x_j\}$ is dense in $X$
it follows that
\[
\lim_{\nu\to\infty}\, \rho_\nu(x)\quad\text{exist for all}\,\, x\in X
\]
This gives some $\rho\in X^*$ such that $\rho(x)$ is the limit value
above for every $x$. It is  clear that the norm of
$\rho$ is $\leq 1$ and by the construction of the
distance function on $B(X^*)$ we have:
\[
 \lim_{\nu\to\infty}\, d(\rho_\nu,\rho)=0
\]
This proves that the given $\gamma$-sequence contains a convergent
subsequence. So by the definition of compact metric spaces
Theorem 5.6  follows.


\bigskip

\noindent
{\bf 5.7 Weak hulls in $X^*$.}
Let $X$  be
separable and choose a denumerable and dense subset
$\{x_n\}$. Examples show that in general the dual space
$X^*$ is no longer separable in its norm topology.
However,  there always exists a denumerable sequences
$\{\gamma_k\}$ in $X^*$ which is dense in the weak-star  topology.
\medskip

\noindent
{\bf{5.8 Exercise.}}
For every $N\geq 1$ we let  $V_N$
be the finite dimensional space generated by
$x_1,\ldots,x_N$.
It has dimension $N$ at most.
Applying the Hahn-Banch theorem
the reader should construct
a sequence $\gamma_1,\gamma_2,\ldots$
in $X^*$ such that for every $N$ the restricted linear
forms
\[
\gamma_\nu|V_N\quad 1\leq \nu\leq N
\]
generate the dual vector space $V_N^*$.
Next, let $Q$ be the field of rational numbers.
Show  that if $\Gamma$ is the subset of $X^*$ formed
by all finite $Q$-linear combinations 
of the sequence $\{\gamma_\nu\}$
then this denumerable set is dense in $X^*$ with respect to the
weak-star  topology.

\medskip


\noindent
{\bf 5.9 Another exercise.}
Let $X$ be a separable Banach space and let $E$ be a subspace of
$X^*$. We say that
$E$ point separating if 
there to every $0\neq x\in X$ exists some
$e\in E$ such that
$e(x)\neq 0$. Show first that every such point-separating subspace of
$X^*$ is dense with respect to the weak topology.
This is the easy part of the exercise. The second part is
less obvious. Namely, put
\[ 
B(E)=B(X^*)\cap E
\] 
Prove now that $B(E)$ is a dense   $B(X^*)$.
Thus, if $\gamma\in B(X^*)$ then there exists a sequence
$\{e_k\}$ in $B(E)$ such that
\[
lim_{k\to\infty}\, e_k(x)=\gamma(x)
\] 
hold for all $x\in X$.





\medskip

\noindent
{\bf 5.10 An example from integration theory.}
An example of a separable Banach space is
$X=L^1({\bf{R}})$ whose elements are
Lebesgue measurable functions
$f(x)$ for which the $L^1$-norm
\[ 
\int_{-\infty}^\infty\, |f(x)|\cdot dx<\infty
\]
If $g(x)$ is a bounded continuous functions on
${\bf{R}}$, i.e. there is a constant
$M$ such that
$|g(x)|\leq M$ for all $x$, then we get a linear
functional on $X$ defined by
\[ 
g^*(f)=\int_{-\infty}^\infty\, g(x)\cdot f(x)\cdot dx<\infty
\]
Let $E$ be the
linear space of all bounded
and continuous functions. By the previous exercise it
is a dense subspace of $X^*$ with respect to the weak topology.
Moreover, by the second part of the exercise
it follows
that if $\gamma\in X^*$ has norm one, then there exists a sequence 
of continuous functions
$\{g_n\}$ of norm one at most such that
$g_\nu\to\gamma$ holds weakly.
Let us now find   $\gamma$.
For this purpose we define the functions
\[
G_n(x)=\int_0^x\, g_n(t)\cdot dt\quad\colon\quad x\geq 0\tag{i}
\]
These primitive functions are continuous and enjoy
a further property. Namely, since the maximum norm of every
$g$-function is $\leq 1$ we see that
\[ 
|G_n(x)-G_n(x')|\leq |x-x'|\quad\colon\quad x,x'\geq 0\tag{ii}
\]
This is means that whenever $a>0$ is fixed, then the
sequence $\{G_n\}$ restricts to an
\emph{equi-continuous} family of functions on the compact
interval $[0,a]$.
Moreover, for each $0<x\leq a$
since we can take $f\in L^1({\bf{R}})$ to be
the characteristic function on the interval $[0,x]$, the
weak convergence of the $g$-sequence implies that
there exists the limit
\[
\lim_{n\to\infty}\, G_n(x)=G_*(x)\tag{iii}
\]
Next, the equi-continuity in (ii) enable us to apply the classic result due to
C. ArzŽla in his paper
\emph{Intorno alla continua della somma di infinite
funzioni contionue}
from 1883 and conclude that the point-wise limit in
(iii) is uniform. Hence   the limit function
$G_*(x)$ is continuous on $[0,a]$ and it is clear
that
$G_*$ also satisfies (ii), i.e. it is Lipschitz continuous of norm
$\leq 1$. Since the passae to the limit can be carried out 
for every $a>0$ we conclude that $G_*$ is defined on $[0,+\infty>)$.
In the same way we find
$G_*$ on $(-\infty,0]$.
Next, 
by the result in [XX-measure] there exists
the Radon-Nikodym derivative
$G_*(x)$ which is  a bounded measurable function
$g_*(x)$ whose maximum norm is   $\leq 1$.
So then
\[ G_*(x)=
\int_0^x\,g_*(t)\cdot dt=
\lim_{n\to\infty}\, G_n(x)=
\lim_{n\to\infty}\, \int_0^x\, g_n(t)\cdot dt
\]
holds for all $x$. 
Since finite ${\bf{C}}$-linear sums of characteristic functions
is dense in $L^1({\bf{R}})$ we conclude that
the limit functional $\gamma$ is determined by
the $L^\infty$-function $g_*$.
So this shows the equality
\[
L^1({\bf{R}})^*=L^\infty({\bf{R}})
\]

\medskip

\noindent
{\bf Remark.}
The result above is of course wellknown. But it is interesting to see how the
last duality formula is derived  from  studies of 
the Lebesgue integral.

\bigskip



\centerline {\bf{5.11 The weak topology on $X$}}.
\medskip


\noindent
Let $X$  be a  Banach space.
Here we do not assume that $X$ is separable.
A sequence $\{x_k\}$ in $X$ converges weakly to a limit vector $x$
if
\[ 
\lim_{k\to\infty}\,
x^*(x_k)= x^*(x)\quad\text{hold for all}\,\, x^*\in X^*
\]


\noindent
{\bf{Exercise.}}
Apply Biare's theorem and
show that a weakly convergent
sequence  $\{x_k\}$ is 
bounded, i.e. there exists a constant $C$ such that
\[ 
||x_k||\leq C
\quad\colon\, k=1,2,\ldots
\]

\medskip

\noindent
{\bf{5.12 Weak versus strong convergence.}}
A weakly convergent sequence need not be strongly convergent.
An example is when
$X=C^0[0,1]$ is the Banach space of continuous
functions on the closed unit interval.
By the Riesz representation theorem the dual space
$X^*$ consists of Riesz measures.
A sequence $\{x_n(t)\}$ of continuous functions
converge weakly to zero if
\[ 
\lim_{n\to\infty}\, \int_0^1\, x_n(t)\cdot d\mu(t)=0
\quad\text{hold for every Riesz measure}\quad  \mu
\]

\newpage


\noindent
By the result from [Measure] this holds if and only if
the maximum norms of the $x$-functions are uniformly bounded
and
the sequence converges pointwise to zero.
One can construct many such pointwise convergent sequences which
fail to converge in the maximum norm.
\medskip

\noindent
{\bf{5.13 Remark.}}
If $X$ is an arbitrary
infinite dimensional Banach space  the norm-topology is always strictly stronger
than the weak topology.
To prove this we argue as follows.
By the construction  of the weak topology on $X$ its equality
with the norm topology gives
a finite subset $x^*_1,\ldots,x^*_N$ of $X^*$ 
and a constant $C$ such that
one has the implication
\[ 
\max_\nu |x_\nu^*(x)|<C\implies ||x||<1
\quad\colon  x\in X
\] 
But then it is clear that the
Hahn-Banach theorem implies that the complex vector space
$X^*$  is
generated by the $n$-tuple $x^*_1,\ldots,x^*_N$ which entails that
$X$ has dimension $N$ at most and  contradicts the assumption that
$X$ has infinite dimension.





\medskip


\noindent
{\bf{5.14 The bidual  $X^{**}$ and reflexive spaces.}} 
A \emph{reflexive} Banach space $X$ is reflexive if
the canonical map from
$X$ into its bi-dual $X^{**}$ is surjective.
For such spaces one
often profits upon the existence of weak convergence.
In general, let $X$ be  a Banach space and $A$ is some bounded
subsets.
One says
that $A$ is 
\emph{weakly sequentially compact}
if every sequence $x_1,x-2,\ldots$ of points from $A$ contains at least
one subsequence $\{x_{n_k}\}$
such that $\{\xi_k\}$ converges weakly to a limit $x_*$, i.e.
\[
\lim_{k\to \infty}\gamma(x_{n_k})\, =\gamma(x_*)
\] 
hold for every $\gamma\in X^*$.
In a reflexive space every bounded subset is weakly sequentially compact.
This is often used to get certain existence results when the reflexive
condition holds.
A remarkable result due to Eberlein and Smulian goes as follows:

\medskip

\noindent
{\bf{5.13 Theorem.}}
\emph{Let $X$ be a Banach space and $A$ a bounded subset. Then
$A$ is weakly sequentially conpact if and only if the closure of $A$ taken 
in the weak topology on $X$ is compact.}
\medskip

\noindent
{\bf{Remark.}}
For the proof we refer to [D-S. Vol 1: page 490-492].
The theorem above is non-trivial since
general toplogy gives examples of
spaces $Y$  which are non-compact while every
denumerable sequence in $Y$ has a convergent subsequence.
The main difficulty in the proof of Theorem 5.13
appears when the weak topology on $X$  is 
not metrisable which occurs
when  $X^*$  is non-separable.
The Krein-Smulian result is for example very useful
when we take the Banach space $L^1(\mu)$ of integrable functions with
respect to some $\sigma$-additive measure $\mu$.


\newpage



\centerline {\bf{5.14 A theorem by Pietsch}}.
\medskip


\noindent
We prove a result which will be used in ¤ 11.xx in relation to
ergodic theorems.
Let $T$ be a bounded linear operator on a Banach space $X$ and
$\{p_n(\lambda)\}$  a sequence of polynomial
with complex coefficients  which give the linear operators
\[ 
A_n=p_n(T)
\]
Assume that $p_n(1)=1$ for every $n$
and impose the following two extra conditions for each vector $x\in X$
where $E$  denotes the identity operator on $X$:
\[ 
A_n(E-T)(x) \overset w\to 0\tag{i}
\]
\[
\{A_n(x)\}\quad\text{ is a weakly compact sequence}\tag{ii} 
\]
In $X$ we define the closed subspaces:
\[
X_1=\overline{(E-T)(X)}\quad\text{and}\quad X_2=
\text{Ker}(E-T)\tag{iii}
\]
\medskip


\noindent
{\bf{Theorem.}} \emph{When (i-ii) hold
it follows
that  $\{A_n\}$ converge weakly to a bounded operator $B$ where 
is a projection whose kernel is $X_1$ while $B$ restricts to the 
identity on $X_2$ and one has the direct sum decomposition}
\[ 
X= X_1\oplus X_2
\]
\medskip


\noindent
\emph{Proof.}
To begin with the result in ¤ XX  and
the hypothesis (ii)
give a constant $M$ such that the operator norms
\[
||A_n||\leq M\tag{1}
\]
 for all $n$.
Next, if $\xi=(E-T)(x)= x-T(x)$
for some
$x\in X$, then (i) entails that
\[
\lim_{n\to \infty}A_n(\xi)\overset{w}\to 0\tag{2}
\]
Together  with (1)
(2) also holds for  each vector  in the closure of
$(E-T)(X)$, i.e. for each  $\xi\in X_1$.
Next, we prove that there exists a  bounded operator $B$ such that
\[
\lim_{n\to \infty}A_n(x)\overset{w}\to  Bx\tag{3}
\]
hold for every $x\in X$.
To begin with (1)
implies that if the sequenes $\{A_n(x)\}$ converge weakly for
every $x$, then
we get a bounded linear operator $B$ in (3).
To prove that these weak limits exist we argue by a contradiction, 
i.e. let $x\in X$ and suppose there are two subsequences
of integers $\{n_k\}$ and $\{m_k\}$ such that
\[
\lim_{k\to \infty}\, A_{n_k}(x)= \xi
\quad\colon
\lim_{k\to \infty}\, A_{m_k}(x)= \eta
\]
where $\xi\neq \eta$.
At the same time (2) entails that
\[
0=\lim_{k\to \infty}\, (E-T)A_{n_k}(x)= \xi-T(\xi)
\]
and in the same way we get
$T(\eta)=\eta$.
In particular
\[
T(\xi-\eta)= \xi-\eta
\]
Since $p_n(1)=1$ for every $n$ this entails that
\[
A_n(\xi-\eta)= \xi-\eta\quad\colon n=1,2,\ldots
\]
In particular the non-zero
vector
$\xi-\eta$  does not belong to the closed subspace $X_1$. The Hahn-Banach theorem gives
some
$x^*\in X^*$ such that
\[
x^*\in X_1^\perp\quad\colon x^*(\xi-\eta)\neq 0\tag{4}
\]
Consider the adjoint operator $T^*$.
The inclusion $x^*\in X_1\perp$ 
means that
\[
x^*(x-Tx)=
x^*(x)- T^*x^*(x)=0\tag{5}
\]
hold for every $x\in X$ and hence $T^*(x^*)= x^*$.
Next, passing the adjoints of $\{A_n\}$
it follows that
\[ 
A_n^*(x^*)=p_n(T^*)(x^*)= x^*\quad\colon\, n=1,2,\ldots
\]
where we again used that
$p_n(1)=1$ for every $n$,
This gives
\[
x^*(\xi)= \lim \, x^*(A_{n_k}(x))=
\lim\, A_{n_k}^*(x^*)(x)=x^*(x)\tag{6}
\]
in the same way we find that
$x^*(\eta)=x^*(x)$
which would give
$x^*(\xi-\eta)=0$ and
contradict (4) above.
\medskip

\noindent
We have proved (2) which
give the bounded operator $B$.
If $\xi=(E-T)(x)$ is vector in the range of $E-T$, then
(i) entails that
$A_n(\xi)\overset{w}\to 0$
which gives $B(\xi)=0$. Passing to the closure we conclude that
\[
X_1\subset \text{Ker}(B)\tag{7}
\]
Next, if
$x^*\in X_1^\perp$ we have 
$T^*(x^*)=x^*$
which  entails that
$A_n^*(x^*)= x^*$  for every $n$.
It follows that
\[
B^*(x^*)=x^*
\]
i.e. the adjoint operator $B^*$ restricts to the identity on
the subspace $X_1^\perp$ in the dual space $X^*$.
Together with (7)  this gives
a direct sum decomposition
\[
X=X_1\oplus\, X_2\tag{8}
\]
where $B$ restricts to the identity on $X_2$.
Thus, if $x_2\in X_2$ we have
$B(x_2)=x_2$. At the same time
\[
(E-T)(A_n(x_2))\overset{w}\to 0
\]
which entals that
\[
(E-T)(Bx_2)= x_2-T(x_2)=0
\] 
Hence $X_2$ is the kernel  of $E-T$ which together 
with the direct sum in (8) finishes the proof of the theorem.







  


























\newpage

\centerline {\bf {5.B Locally convex spaces}}
\bigskip


\noindent
Let $E$ be a real vector space.
Denote by $\mathcal C_E$ the family of convex
and symmetric subsets $U$ which contain the origin
and are absorbing in the sense that
for every $x\in E$ there exists some
real $s>0$ such that
$s\cdot \in U$.
The symmetry means that $U=-U$.
If $U\in \mathcal C_E$ 
and $x$ is a vector in $E$ it may occur that
the whole line
${\bf{R}}x$ is contained in $U$
in which case we say that $x$ is fully absorbed by $U$.
The convexity of $U$ entails that
the set of absorbed vectors is a linear subspace of $E$ which we denote by
$\mathcal L_U$.
\medskip


\noindent
{\bf{5.B.1 The pseudo-norm
$\rho_U$.}}
For each non-absorbed vector $x$ we get a positive number
\[
\mu(x)=\max\{ s\,\colon sx\in U\}
\]
If $x$ is absorbed we put $\mu(x)=+\infty$ and
for every non-zero vector $x$
we set
\[ 
\rho_U(x)=\frac{1}{\mu(x)}
\]
We leave it to the reader to verify that
the convexity of $U$ entails that
$\rho_U$ satisfies the triangle inequlity
\[
\rho_U(x_1+x_2)\leq \rho_U(x_1)+\rho_U(x_2)\tag{i}
\]
for every pair in $X$. Moreover,
$\rho_U(x)=0$ if and only if
$x$ beongs to
$\mathcal L_U$ and $\rho_U$ is positively homogeneous, i.e.
the equality below holds when $a$ is real and positive:
\[
\rho_U(ax)= a\rho_U(x)\quad\colon a>0\tag{ii}
\]
Finally, the symmetry of $U$ entails that
$\rho_U(x)= \rho_U(-x)$ for every $x$.
\medskip

\noindent
{\bf{Exercise.}}
Conversely, let $\rho\colon X\to {\bf{R}}^+$
satisfiy (i-ii) and the symmetry
$\rho (x)=\rho(-x)$.
Set
\[ 
U=\{ x\colon\, \rho(x)<1\}
\]
Show that 
$U$ belongs to $\mathcal C_E$ and that $\rho_U=\rho$.
\medskip


\noindent
{\bf{5.B.2 Locally convex topologies.}}
A topology on the real vector space
$X$ is said to be locally convex
and separated
if there exists a family
$\mathfrak{U}= \{U_\alpha\}$ in $\mathcal C_E$ such that
the intersection $\mathcal L_{U_\alpha}\}$
is reduced to the zero vector. A bais for open
neighborhoods of the origin in $X$
consists of sets defined by
\[
\{x\colon \rho_{U_i}(x)<\epsilon\}
\] 
where $\epsilon>0$ and $\{\alpha_1,\ldots,\alpha_k\}$ is a finite set
of indices defining the  $U$-family.





 \medskip
 
 \noindent
 {\bf{Remark.}}
 The locally convex topology above depends upon the family
 $\mathfrak{U}$-toplogy. Its topology  is not changed if we enlarge 
 the family to consist of all finite intersection of its
 convex subsets. When this has been done
 we notice that if $U_1,\ldots, U_n$ is a finite family in
 $\mathfrak{U}$ then the norm defined by
 $U=U_1|\cap\ldots\,\cap U_n$ is stronger than
 the individual $\rho_{U_i}$-norms. Hence
 a fundamental system of neighborhoods 
 consists of single $\rho$-balls:
  \[
 \Omega=\{\rho_U<\epsilon \}    \quad\colon U\in\mathfrak {U}
 \]
 
 \medskip
 
 \noindent
 {\bf{5.B.3 The dual space $E^*$}}.
Let $E$ be equipped with a locally convex $\mathfrak{U}$-topology.
A linear functional  $\phi$ is $\mathfrak{U}$-continuous if and only if there
exists some
$U\in\mathfrak{U}$ such that $\phi$ is continuous with
respect to the
$\rho_U$-norm, i.e  there is a constant $C$ such that
\[
|\phi(x)||\leq C\cdot \rho_U(x)
\]

\noindent
To each pair 
$\phi\in E^*$ and a real number $a$ one assigns the
closed half-space
\[
H=\{x\in X\,\colon\, \phi(x)\leq a\}
\]
The next result
is due to
 DieudonnŽ from the 
 article 
 \emph{La dualitŽ dans les
espaces vectorielles} (Ann.Ecol. Norm.Sup. 1942).

\medskip

\noindent
{\bf{5.B.4. Theorem.}}
\emph{Each closed convex set $K$ in $E$ is the intersection of closed half-spaces.}


 \medskip
 
 \noindent
 Tbe proof is left as an exercise. A hint is that
  $K$ to begin with is closed with
 respect to the
 $\rho_U$-toplogy for
 every $U$ which  this gives
 a real number $a_U$ such that
 \[ 
 K+\mathcal L_U=\{\rho_U\leq a_U\}
\]
 
\medskip



\centerline {\bf{5.C Support functions of convex sets.}}
\medskip


\noindent
From now on $E$ is a locally convex space.
Denote by
$\mathcal S(E)$ the family of real-valued 
functions $G$ on $E^*$ which  are
subadditive and positively
homogeneous, i.e. for each  real $t>0$ and all pairs
$y_1,y_2$ in $E^*$ one has:
\[ 
G(y_1+y_2)\leq G(y_1)+G(y_2)\quad\colon\quad G(ty)=tG(y)\tag{*}
\]
To each closed and convex subset $K$ 
we define a function $\mathcal H_K$ on the dual $E^*$ by:
\[ 
\mathcal H_K(y)=\sup_{x\in K}\,y(x)
\]


\noindent
Notice that these $\mathcal H$-functions
take values in $(-\infty,+\infty]$, i.e. it may be $+\infty$ 
for some vectors $y\in E^*$.


\noindent
{\bf{5.C.1 Exercise.}}
Show that $\mathcal H_K\in\mathcal S(E)$  for every closed convex set $K$.

\medskip

\noindent
Next,  in  the weak-star topology on $E^*$
a basis for open neighborhoods of
the origin consists of open sets
\[
U(x_1,\ldots,x_N;\epsilon)=
\{ y\in E^*\,\colon\, |y(x_k)|<\epsilon \,\colon\, 1\leq k\leq N\}
\]
where $x_1,\ldots,x_N$ are finite subsets of $E$ and $\epsilon>0$.
DieudonnŽ's theorem shows that
if $K$ is a closed convex set then
$H_K$
is an upper semi-continuous function with respect to the weak-star topology.
Indeed, this is so because the $y\mapsto y(x)$ is weak-star
continuous for every fixed $x\in E$ and the supremum
of an arbitrary family of weak-star continuoes functions is upper
semi-continuous.
Less obvious is the converse which was proved by   Hšrmander 
in the article
\emph{Sur la fonction d'appui des ensembles convexes dans un espaces
localementt convexe} [Arkiv fšr mat. Vol 3: 1954].

 
\medskip

\noindent
{\bf{5.C.2. Theorem.}}
\emph{Each $G\in\mathcal S(E)$
which is upper semi-continuous with
respect to the weak-star topology is of the form
$\mathcal H_K$ for a unique closed convex subset $K$ in $E$.}
\medskip

\noindent
{\bf{Remark.}}
As pointed out by Hšrmander in [ibid] 
Theorem 5.C.2  is closely related to  earlier studies by
Fenchel in the article \emph{On conjugate convex functions}
Canadian Journ. of math. Vol 1 p. 73-77) 
where  Legendre transforms are
studied in infinite dimensional topological vector spaces.
The novely in Theorem 5.C.2 is the generality and we
remark that various separation theorems 
in text-books dealing with notions of convexity
are easy consequences of Theorem 5.C.2.


\bigskip


\noindent{\emph{Proof of Theorem 5.C.2}}
Put $F=E\oplus{\bf{R}}$ which is a new vector space where
the 1-dimensional real line is added. Here $F^*=E^*\oplus
{\bf{R}}^*$
and for each vector $(y,\eta)$ in $F^*$ we declare that
\[ 
(y\oplus t)(x,t)= y(x)-\eta t\tag{1}
\]
Notice the minus sign in the right hand side.
 Next,  each  closed and convex set $K$
 in $E$
gives the  convex cone in $F$ defined by
\[ 
C_K=\{(tx,t)\,\colon\, t\geq 0\}\tag{1}
\]
It is in general not closed  but is closure is again a convex
cone denoted by $\overline{C_K}$ and the reader may notice that
\[ 
\overline{C_K}\setminus C_K\subset E\oplus\{0\}
\]
\medskip

\noindent
{\bf{Exercise.}}
Show that $K\mapsto \overline{C_K}$
yields 1-1 correpondence between
closed convex sets $K$ in $E$ 
which contain at least one point outside the origin and
the family of closed cones in $F$  contained
in $\{t\geq 0\}$ 
but not entirely in the hyperplane
$\{t=0\}$.
\medskip


\noindent
Next, when  $K\subset E$ is a closed convex set we get a cone in
$F^*$ defined by:
\[ 
C_K^*=\{(y,t)\,\colon\, y(x)- t\geq 0\,\colon\, (x,t)\in \bar C_K
\quad\text{and}\quad s\geq 0\}\tag{2}
\]
This means that
$(y,s)\in C_K^*$ if and only if $y(x)\leq t$ for
each $(x,t)\in \bar C_K$, or equivalently that
$\mathcal H_K(y)\leq t$.
\medskip

\noindent
After these preliminary observations we begin to
study a function
$G$ on $E^*$ which satisfies the conditions in
Theorem 5.B.2
Put
\[
G_*=\{(y,\eta)\in F^*\quad\colon, G(y)\leq \eta\}\tag{i}
\]
Condition in (*) entails that $G_H$ is a convex cone
in $F^*$ and the semi-continuous hypothesis on $G$
implies that  $G_*$ is closed with respect to the weak-star toplogy on $F^*$.
Since $G(0)=0$ we have
\[
(0,\eta)\in G_*\implies \eta\geq 0\tag{ii}
\]
Next, in $F$ we define the cone
\[ 
G_{**}=\{(x,t)\,\colon\, y(x)-\eta t\leq 0\,\colon\, (y,\eta)\in G_*\}\tag{ii}
\]
Since $\eta\geq 0$ for every vector $(y,\eta)\in G_*$
we see that $G_{**}$ is contained in the half-space 
$t\geq 0$.
Moreover it is obviously  closed in $F$
Next, let  $\widehat C$ be the  cone in $F^*$
defined by
\[
\widehat C=\{(y,\eta)\,\colon\, y(x)-\eta t\leq 0\,\colon\,(x,t)\in 
G_{**}\}\tag{iii}
\]
It is clear that $G_*\subset \widehat C$
and if equality holds the construction  $G_*$ in (i) and  the
remarks at the beginning of the proof
entail that $G=\mathcal H_K$ for  closed convex cone $K$ in $E$.
Hence there only
remains to prove that  inclusion below is not strict:

\[
G_*\subset \widehat C\tag{*}
\]
To prove this we use Theorem 5.B.0.
Namely, since
the two sets above are weak-star closed a strict inequality
gives a separating
vector $(x_*,t_*)\in E$, i.e.  there exists $(y_*,\eta_*)\in \widehat C$
and a real number $\alpha$ such that 
\[
y_*(x_*)-\eta _* t_*>\alpha
\quad\text{and}\quad (y,\eta)\in D_K\implies y(x_*)-\eta t_*\leq \alpha\tag{iv}
\]
Since $G_*$ contains $(0,0$ we must have $\alpha\leq 0$.
and since it also is a cone the implication above gives
$(x_*,t_*)\in G_{**}$ and then
the construction of $\widehat{C}$ in (iii) contradicts the strict inequality in
the left hand side of (iv).
Hence there cannot exist
a separating vector and the proof of Theorem 5.C.2 is finished.

\bigskip

\noindent
{\bf{5.C.3 The case of normed spaces.}}
If $X$ is a normed vector space Theorem 5.C.2
leads to a certain isomorphism of two families.
Denote by $\mathcal K$ the family of all convex
subsets of $E$ which are closed with respect to the norm topology.
A topology on $\mathcal K$ is defined
when we for each $K_0\in\mathcal K$ and $\epsilon>0$
declare an open neighborhod
\[ 
U_\epsilon(K_0)=\{ K\in\mathcal K\,\colon\,
\text{dist}(K,K_0)<\epsilon\}
\] 
where the norm defines the distance between
$K$ and $K_0$ in the usual way.
Denote by $\mathfrak{H}$ the family of all
functions $G$ on $E^*$ which satisfy (*) in 5.B.1 and are continuous
with respect to the norm topology on $E^*$.
A subset $M$ of $\mathfrak{H}$ is equi-continuous if there
to
each $\epsilon>0$ exists $\delta>0$ such that
\[
||y_2-y_1||<\delta \implies ||G(y_2)-G(y_1)||<\epsilon
\] 
for every $G\in M$ and 
all pairs $y_1,y_2$ in $E^*$.
The topology on $\mathfrak{H}$ is  defined
by  uniform convergence on equi-continuous subsets.

\medskip




\noindent
{\bf{5.C.4 Theorem.}}
\emph{If $E$ is a normed vector space
the set-theoretic bijective map $K\to \mathcal H_K$ is
a homeomorphism when
$\mathcal K$ and
$\mathfrak {H}$ are equipped with the described topologies.}
\medskip

\noindent
{\bf{5.C.5 Exercise.}} Deduce this  result 
from     Theorem C.5.2.
\bigskip


\centerline
{\bf{5.D The Krein-Smulian theorem.}}
\bigskip


\noindent
Let $X$ be a Banach space and $X^*$ its dual.
The weak-star topology on $X^*$ was defined in ¤ 5.4.
We have also the bounded weak-star topology desrcibed in ¤ xx from
the introduction.
So now we have a pair of  locally convex spaces 
$X^*_w$ and $X^*_{bw}$.
Open sets in the weak-star topology are
by defintion also open in
the bounded weak-star topology, i.e. the latter topology 
contains more open sets and is therefore strongethan the ordinary weak-star topology.
Hence  there is a natural inclusion of   dual spaces:
\[
(X_w^*)^*\subset
(X_{bw}^*)^*\tag{*}
\]
The Krein-Smulian theoren assers that eqaulity holds in (*).
To prove this we 
first study the bounded weak-star topology on $X^*$.
In general, if $A$ is a finte set in $X$ we put
\[ 
A^0=\{x^*\,\colon\, \max_{x\in A}\,|x^*(x)|\leq 1\}
\]
Let $U$ be an open set in $X^*_{bw}$
which cointains the origin
and $S^*$ is the closed unit ball in
$X^*$.
The defintion of the bounded weak-star topology gives
a finite set $A_1$ in $X$ such that
\[
S^*\,\cap A_1^0\subset U\tag{i}
\]
Next, let $n\geq 1$ and suppose we have constructed
a finite set $A_n$ with
\[
nS^*\,\cap A_n^0\subset U\tag{ii}
\]
To each finite set $B$ of vectors 
in $X$ with norm $\leq n^{-1}$
we notice that   $(A_n\cup\, B)^0$
contains $A_n^0$.
Let $U^c=X^*\setminus U$ and put
\[
 F(B)=(n+1)S^*\cap (A_n\cup\, B)^0 \,\cap U^c
\]
Each such set if weak-star closed.
If they are non.empty for
every finite set $B$ as above, it follows by
the weak-star compactness of $(n+1)S^*$
 that the whole intersection is non-empty. So we find
 $x^*$
 in this intersection.
In particular $x^*\in B^0$ for every finite set of vectors
in $X$ of norm $\leq n^{-1}$. It means that
$|x^*(x)|\leq 1$ when $||x|\leq 1$ and hence
the norm
$||x^*||\leq n$. This gives the inclusion
\[
 x^*\in nS^*\cap A:n^0\cap U^c\tag{ii}
\]
But this contradicts (ii) and hence
$F(B)=\emptyset$ for some finite set $B$ if $X$-vectors of norm $\leq n^{1}$.
\medskip

\noindent
From the above it is clear that an induction over $n$ gives
a sequence of sets $\{A_n\}$ for which (ii) hold
for each $n$ and
\[ 
A_{n+1}=A_n\,\cup B_n\tag{iii}
\]
where
$B_n$ is a finite set of vectors of norm
$\leq n^{-1}$.
\bigskip

\centerline{\emph{Proof of the Krein-Smulian theorem.}}

\bigskip

\noindent
Let $\theta$ be a linear functional on $X^*$ which is
continuous with respect to the bounded weak-star topology.
This gives an open neighborhood
$U$ in
$X^*_{bw}$ such that
\[
|\theta(x^*)\leq 1\quad\colon\,  x^*\in U\tag{i}
\]
To the set $U$
we find a sequence $\{A_n\}$ as above.
Let us enumerate the vectors in this sequence iof finite sets by
$x_1,x_2,\ldots$, i.e.
start with the finite string of vectors in $A_1$, and so on.
In particular $||x_n||\to 0$ as $n\to \infty$.
If $x^*$ is a vector in $X^*$ we 
associate the complex sequence
\[
\rho(x^*)= \{x^*(x_n)\}
\]
which tends to zero since
$||x_n||\to 0$ as $n\to \infty$.
Then
\[ 
x^*\mapsto \rho(x^*)
\]
is a linear map from $X^*$ into the 
Banach space ${\bf{c}}_0$.
If the norm 
\[
||\rho(x^*)||=\max_n\, |x^*(x_n)|\leq 1
\]
we have by defintion $x^*\in A_n^0$ for each $n$.
Choose  $n$ so large that $||x^*||\leq n$. Thus entails that
\[
x^*\in nS^*\cap A_n^0
\]
and hence $x^*\in U$
which by (i) gives
$\theta(x^*)|\leq 1$.
We conclude that $\theta$ yields
a linear functional on
on the image space of $\rho$ with norm one at most.
The 
Hahn-Banach theoren gives
$\lambda\in{\bf{c}}_0^*$
of norm one at most such that
\[
\theta(x^*)= \lambda(\rho(x^*))
\]
Next,  a wellknown result due to
Banach gives a sequence $\{\alpha_n\}$ in $\ell^1$ such that
\[
\theta(x^*)= \sum\,\alpha_n\cdot x^*(x_n)
\]
In $X$ we find the vector $x=\sum\, \alpha_n\cdot x_n$
and conclude that
$\theta=\widehat{x}$ which proves the Krein-Smulian theorem.
\bigskip



\centerline{\bf{5.E Fixed point theorems.}}
\bigskip


\medskip
\noindent
A topological space $S$ has the fixed-point property if every
continuous map $f\colon S\to S$ has at least one fixed point.
To begin with we  apply
Stokes theorem to prove the classical  result:
\medskip


\noindent
{\bf{1. Theorem.}}
\emph{The closed unit ball in ${\bf{R}}^n$ has the fixed point property.}


\medskip


\noindent
\emph{Proof.}
By Weierstrass approximation theorem
every continuous map from $B$ into itself can be approxiated unifomly by
a $C^\infty$-map. Together with the compactness of $B$ the reader
should conclude that it suffices to prove every $C^\infty$-map, 
$\phi\colon B\to B$  has at least one fixed point.
We are going to derive argue by  contradiction, i.e suppose that
$\phi(x)\neq x$ for all $x\in B$.
Each  $x\in B$ gives the quadratic equation  in the variable $a$
\[
1= |x+a(x-\phi(x)|^2=|x|^2+2a(1-\langle x,\phi(x)\rangle )+a^2|x-\phi(x)|^2\tag{i}
\]


\noindent
{\bf{Exercise 1.}}
Use that $\phi(x)\neq x$,
to check that
(i) has two simpe roots for
each $x\in S$, and if $a(x)$ is the larger, then
the function $x\mapsto a(x)$
belongs to $C^\infty(B)$. Moreover
\[
a(x)=0\quad\colon x\in S\tag{E.1}
\]


\medskip


\noindent
Next,  for each real number $t$ we set
\[
f(x,t)= x+ta(x)(x-\phi(x))
\]
This is a vector-valued function of the $n+1$ variables $t,x_1,\dots,x_n$
where $x$ varies in $B$.
With $f=(f_1,\ldots,f_n)$ we  set
\[
g_i(x)=a(x)(x_i-\phi_i(x)
\]
Taking partial derivatives
with respect to $x$ we get
\[
\frac{\partial f_i}{\partial x_k}= e_{ik}+t\frac{\partial g_i}{\partial x_k}\tag{ii}
\]
where $e_{ii}=1$ and $e_{ik}=0$ if $i\neq k$.
Let $D(x;t)$ be the determinant of the $n\times n$-matrix
whose elements are the partial derivatives in (ii) and put
\[ 
J(t)=\int_B\, D(x;t)\, dx\tag{iii}
\]
When $t=0$ we notice that the $n\times n$-matrix above
is the identy matrix and hence
$D(x;0)$ has constant value one so that  $J(0)$ is the volume of $B$.
Next, (i) entails that 
$x\mapsto f(x;1)$ satisfies the functional equation
\[
|f(x;1)|^2=1
\]
which implies  that $x\mapsto D(x;1)$ is identically zero
and hence $J(1)=0$.
The requested contradiction follows if 
$t\mapsto J(t)$
is  a constant function of $t$. To attain  this we shall need:
\medskip

\noindent
{\bf{2. Exercise.}}
Use Leibniz's rule and that determinants of matrices with
two equal columns are zero to conclude that
\[
\frac{d}{dt}(D(x;t)= \sum\sum\, (-1)^{j+k}\cdot
\frac{\partial g_i}{\partial x_k}\tag{E.2}
\] 
where the double sum extends over all pairs $\leq j,k\leq n$.
\medskip

\noindent
Next, for all pairs $i.k$, Stokes theorem gives
\[
\int_B\, \frac{\partial g_i}{\partial x_k}\, dx=
\int_S\, g_i\cdot {\bf{n}}_k\, d\omega\tag{iv}
\]
where $\omega$ is the area measure on the unit sphere.
From (E.1)  we have $g_i=0$ on $S$ for each $i$.
Hence (E.2) and (iv)  imply that
\[
\frac{dJ}{dt}=\int_B\, \frac{d}{dt}(D(x;t)\, dx=0
\]
So $t\mapsto J(t)$ is constant which is impossible  because
$J(0)=1$ and $J(1)=0$ which  finishes  the proof.

\bigskip


\noindent
{\bf{The Hilbert cube $\mathcal C$}}.
In the Hilbert space $\ell^2$ we have the closed subset
$\mathcal C$ which consists of vectors $x=(x_1,x_2,\ldots)$ such that
$|x_k|\leq 1/k$ for each $k$.
\medskip



\noindent
{\bf{2. Proposition.}}
\emph{Every closed and convex subset of
$\mathcal C$ has the fixed point property.}
\medskip

\noindent
{\bf{Exercise.}} Deduce this result from Theorem 1.

\bigskip

\noindent
Next, let $X$ be a locally convex vector space and $X^*$ its dual.
Consider the family $\mathcal K(X)$ of convex subsets 
which are compact with respect to the  weak topology. 
Let $K\in \mathcal K(X)$ and $T\colon K\to K$
a continuous map in the weak topology.
For each fixed  $f\in X^*$,  it follows from our assumptions that 
the complex-valued function on $K$ defined by
\[
p\mapsto f(T(p))
\]
is uniformly contnuus with respect to the weak topology.
So for each positive integer $n$ there exists a finite set
$G_n=(x^*_1,\ldots,x^*_N)$ and some $\delta>0$
such that the following implication holds for each pair of points
$p,q$  in $K$:
\[
p-q\in\cap \, B_\delta(x^*_\nu)\implies 
|f(T(p))-f(T(q))|\leq n^{-1}\tag{i}
\]
We can attain this for each positive integer  $n$ and get a denumerable set
\[
G=\,\cup \, G_n
\]
From (i)  it is clear that if
$p,q$ is a pair in $K$ and $g(p)=g(q)$ hold for every $g\in G$, then
$x^*(T(p))=x^*(T(q)$.
We refer to $G$ as a determining set for the map $T$.
In a similar way we find a denumerable
determining set
$G^{1)}$
for $g_1$, By a standard "diagonal argument" the
reader may verify the following:
\medskip


\noindent
{\bf{3. Proposition.}}
\emph{There exists a denumerable subset
$G$ in $X^*$ which contains $f$ and  is self-determining in the sense that
it determines each of its vectors as above}.

\bigskip


\noindent
{\bf{4. An embedding into the Hilbert cube.}}
During the construction of the finite $G_m$-sets which
give (i), we can choose small $\delta$-numbers and
take $\{x^*_\nu\}$  such that the maximum values
\[
\max_{p\in K}\, |x^*_\nu(p)|
\] 
are small.
From this observation the reader should confirm that
in Proposition 3 we can construct 
the sequence
 $G=(g_1,g_2,\ldots)$  in such a way that
 \[
 \max_{p\in K}\, |g_n(p)|\leq n^{-1}
\]
hold for every $n$.
Hence each $p\in K$ gives the vector
$\xi(p)=(g_1(p),g_2(p),\ldots)$ in the Hilbert cube
and now 
\[
K_*=\{\xi(p)\,\colon\, p\in K\}
\]
yields a convex subset of $\mathcal C$.
Since $G$ is self-determininig we have
$T(p)=T(q)$ whenever $\xi(p)=\xi(q)$. Hence
there exists a  map from
$K_*$ into itself defined by
\[
T_*(\xi(p))= \xi(T(p)\tag{4.1}
\]
\medskip

\noindent
{\bf{5. Exercise.}}
Use the compact property of $K$ to show that
$K_*$ is closed in the Hibert cube and that
$T_*$ is a continuous map with respect to the induced 
strong norm topology on $K_*$ derived from the
complete norm on $\ell^2$.
\medskip

\noindent
{\bf{6. Consequence.}}
Suppose from the start that
we are given a pair of points $p_1,p_2$  in $K$ and some
$f\in X^*$ where $f(p_1)\neq f(p_2)$.
From the above $f$ appears in the $G$-sequence and put
\[
K_0=\{p\in K\colon\, \xi(p)=\xi (p_1)\}
\]
Then $K_0$ is a 
convex subset of $K$, and since
$f$ appears in the $G$-sequence it follows that
$p_2$ does not belong to $K_0$.
Moreover, since $G$ is self-determining with respect to $T$ it 
is clear that 
\[
T(K_0)\subset K_0
\]
Hence we have proved:

\medskip

\noindent
{\bf{6.1 Proposition.}} \emph{For each pair
$K$ and $T$  as above where $K$ is not reduced to a single point, there
exists a proper and $X^*$-closed convex subset $K_0$ of $K$ such that
$T(K_0)\subset K_0$.}
\bigskip


\centerline {\bf{7. Proof of the Schauder-Tychonoff theorem.}}
\bigskip

\noindent
Let $T\colon K\to K$
be a continuous map where $K$ belongs to $\mathcal K(X)$.
Consider the family  $\mathcal F$
of all closed and convex subsets
which are $T$-invariant. It is clear that
intersections of such sets enjoy the same property. So we find
the minimal set
\[
K_*= \bigcap\, K_0
\]
given by the intersection of all sets $K_0$
in
$\mathcal F$.
If $K_*$ is not reduced to a single point then Proposition  6.1
gives a proper closed subset which again belongs to
$\mathcal F$. This is contradicts the minimal property.
Hence $K_*=\{p\}$ is a singleton set and $p$ 
gives the requested fixed point for $T$.
\bigskip


\centerline{\bf{5.F Proof of Kakutani's theorem.}}
\bigskip

\noindent
With the notations from the introduction we are given a group
${\bf{G}}$ where each element $g$ preserves the convex set
$K$ in $\mathcal K(X)$.
Zorn's lemma gives a minimal 
closed and convex subset $K_*$ of $K$ which again is invariant under the group.
Kakutani's theorem follows if $K_*$ is a singleton set.
To prove that this indeed is the case we  argue by contradiction.
For  $K_*$ is not a singleton set then
\[
K_*-K_*=\{p-q\colon p,q\in K_*\}
\] 
contains points outside the origin, and we find  
a convex open neighborhood $V$ of the origin such that
\[
(K_*-K_*)\setminus\overline{V}\neq\emptyset\tag{i}
\]
Since
${\bf{G}}$ is equicontinuous on $K$ and hence also on $K_*$ there
exists an open convex neighborhood $U$ of the origin such that
whenever $k_1,k_2$ is a pair in $K_*$
such that $k_1-k_2\in U$, then  the  orbit
\[
{\bf{G}}(k_1-k_2)\subset V\tag{ii}
\]
Set
\[
U^*=\text{convex hull of }\,\,{\bf{G}}(U)
\]
Since the ${\bf{G}}$-maps are linear, the set 
$U^*$ is invariant and  continuity entails  the equality
\[
{\bf{G}}\overline{U^*})=\overline{U^*}\tag{iii}
\]
We find the unique positive number $\delta$ such that
the following hold for every $\epsilon>0$:
\[
K_*-K_*\subset (1+\epsilon)\cdot U^*
\quad\colon\, (K_*-K_*)\setminus (1-\epsilon)\cdot \delta\cdot\overline{U^*}\neq\emptyset\tag{iv}
\]
Next,  $\{k+\frac{\delta}{2}\cdot U\colon\, k\in K_*\}$ 
is an open covering of the compact set $K_*$.
Hence Heine-Borel's Lemma gives 
 a finite set 
$k_1,\ldots,k_n$ in $K_*$ such that
\[
K_*\subset\ \cup\, (k_\nu+\frac{\delta}{2}\cdot U)\tag{v}
\]
Put
\[
K_{**}= K_*\cap\, \bigcup_{k\in K_*}
(k+(1-1/4n)\delta\cdot \overline{U})\tag{vi}
\]
Since
 $\overline{U}$ is 
${\bf{G}}$-invariant and the intersection above is taken over all $k$ in the
invariant  set $K_*$, we see that 
$K_{**}$ is  a closed convex  and ${\bf{G}}$-invariant set.
The requested contradiction follows if we prove that
$K_{**}$ is non-empty
and
is strictly contained in $K_*$.
To get the  strict inclusion follows  we take some
$0< \epsilon<1/4n$. Then   (iv)  gives
a pair $k_1,k_2$ in $K_*$ such that
$k_1-k_2$ does not belong to
$(1-\epsilon) \delta\cdot\overline{U^*}$.
At the same time the inclusion $k_1\in K_{**}$ entails that
\[
k_1\in (k_2+(1-1/4n)\delta\cdot \overline{U})
\implies k_1-k_2\in  (1-1/4n)\delta\cdot \overline{U}\tag{v}
\]
which cannot hold since   $1-1/4n<1-\epsilon$.
The proof of Kakutani's theorem is therefore finished if we have shown that
\[
p\in K_{**}\tag{vi}
\]
To see this
we take an arbitrary $k\in K_*$.
From (v) we find some $1\leq i\leq n$ such that
\[
k_i-k\in \frac{\delta}{2}\cdot U\tag{vii}
\]
Without loss of generality we can assume that $i=1$
and get  a vector $u\in U$ such that
\[
k_1= k+\frac{\delta}{2}\cdot u\tag {viii}
\]
It follows that
\[
p=\frac{k_1+\ldots+k_n}{n}=k+\frac{\delta}{2n}\cdot u+
\sum_{i=2}^{i=n}\, \frac{1}{n}(k_i-k)\tag {ix}
\]
Next, for  each $\epsilon>0$ the left hand inclusion in (iv) and the 
convexity of $U$ give
\[
\sum_{i=2}^{i=n}\, \frac{1}{n}(k_i-k)\subset
\frac{n-1}{n}(1+\epsilon)\cdot \delta \cdot U\tag{x}
\]
It follows   that
\[
\frac{\delta}{2n}\cdot u+
\sum_{i=2}^{i=n}\, \frac{1}{n}(k_i-k)\in
(\frac{n-1}{n}(1+\epsilon)\delta +\frac{\delta}{2n})\cdot U\tag{xi}
\]
Above we can choose $\epsilon $ so small that
\[
\frac{n-1}{n}(1+\epsilon)+\frac{1}{2n})<1-1/4n
\]
and then we see that
\[
p\in k+(1-1/4n)\delta\cdot \overline{U}
\]
Since $k\in K_*$ was arbitrary the requested inclusion
$p\in K_{**}$ follows.











\newpage

\centerline {\bf 6. Fredholm theory.}

\bigskip
\noindent
{\bf Introduction.} A major  result in this section is Theorem 6.6.1
which  is due to Fredholm in the article [Fredholm: 1901].
The  original result was stated for integral operators
but the  proof adapted to bounded linear operators on Banach spaces 
is verbatim the same.
From now on
$X$ and $Y$ are Banach spaces with
dual spaces 
$X^*$ and $Y^*$.
\medskip

\noindent
{\bf 6.1 Adjoint operators.}
Let $u\colon X\to Y$
be a bounded linear operator . The adjoint $u^*$ is the linear operator
from $Y^*$ to $X^*$ defined by
\[
u^*(y^*)
\colon\, x\mapsto y^*(u(x))\quad\colon\quad y^*\in Y\quad\colon x\in X\tag{1}
\]



\noindent
{\bf{Exercise.}} Show that 
the Hahn-Banach theorem gives the equality of operator norms:
\[
||u||=||u^*||
\]
\medskip






\noindent
{\bf 6.2 The operator $\bar u$.} Let $u\colon X\to Y$ 
be a bounded linear operator which gives
the 
closed null space
$N_u$ in $X$. On the
Banach space
$\frac{X}{N_u}$  there exists   the
induced linear operator
\[ 
\bar u\colon\,\frac{X}{N_u}\to Y\tag{6.2.1}
\]


\noindent
By construction $\bar u$
is an \emph{injective} linear operator with 
the same range as $u$:
\[
 u(X)=\bar u(\frac{X}{N_u})\tag{6.2.2}
 \]
\medskip

\noindent
{\bf 6.3 The image of $u^*$}. In the dual space $X^*$ we get
the subspace
\[ 
N_u^\perp=\{x^*\in X^*\quad\colon\, x^*(N_u)=0\}\tag{i}
\]


\noindent
Consider a pair 
$y^*\in Y^*$ and
If $x\in N_u$. Then
\[
u^*(y^*)(x)= y^*(u(x))=0
\]
The proves the inclusiuon
\[
u^*(Y^*)\subset N_u^\perp\tag{ii}
\]

\noindent
Next, the Hahn-Banach theorem gives
the canonical isomorphism
\[
\bigl[\frac{X}{N_u}\bigr]^*\simeq N_u^\perp\tag{iii}
\]
\medskip

\noindent Now we consider the linear operator $\bar u$ 
from (6.2.1)
whose adjoint
$\bar u^*$ maps $Y^*$ into
the dual of $\frac{X}{N_u}$. The canonical isomorphism
(iii) gives a linear map
\[ 
\bar u^*\colon\, Y^*\mapsto N_u^\perp\tag{iv}
\]

\noindent
From this and (ii) we get the equality
\[
\text{Im}(\bar u^*)=\text{Im}(u^*)\tag{6.3.1}
\]
where both sides appear as subspaces of $N_u^\perp$.

\medskip


\centerline {\bf 6.4 The closed range property}
\medskip

\noindent
A bounded linear operator
$u\colon X\to Y$ is said to have
closed range if
$u(X)$ 
is a closed subspace of $Y$.
When this holds 
\[
\bar u\colon \frac{X}{N_u}\to u(X) 
\]
is  a bijective map between
Banach spaces and the  The Open Mapping Theorem 
implies that this is an isomorphism of Banach spaces.
We use this to prove:

\medskip

\noindent
{\bf 6.4.1 Proposition}. \emph{If  $u$ has closed range then $u^*$ has closed range
and
one has the equality}
\[ 
\text{Im}(u^*)= N^\perp_u
\]
\medskip


\noindent
\emph{Proof.}
Using (6.3.1) we can replace $u$ by $\bar u$ and hence assume
that $u\colon X\to Y$ from the start is injective.
It means that $N_u^\perp=Y^*$
so there remains to show
that
$u^*$ is surjective, i.e. that
\[ 
u^*(Y^*)=X^*\tag{i}
\]

To prove (i) this the assumption that 
 $u$ has closed range and the Open Mapping theorem gives
a constant $c>0$ such that
\[ 
||u(x)||\geq c\cdot ||x||\quad\colon\, x\in X\tag{ii}
\]
If $x^*$ the injectivity of $u$ gives
a linear functional
$\xi$ on  $u(X)$ defined by
\[
\xi(u(x))= x^*(x)\tag{iii}
\]
Now (ii) entails that
$\xi$ belong to $u(X)^*$ with norm
$\leq c\cdot ||x^*||$.
The Hahn-Banach theorem applied to
the subspace 
$u(X)$ of $Y$ gives a
norm preserving extension $y^*\in Y^*$ where (iii) entails that
\[ 
u^*(y^*)(x)= y^*(u(x))= x^*(x)
\]
This means  that
$u^*(y^*)= x^*$ and the requested surjectivity follows.









\bigskip

\noindent
{\bf {The  converse result.}}
Let $u\colon X\to Y$ be a bounded linear operator and
assume that $u^*$ has closed range. Then we shall prove that
$u$ has closed range. 
To begin with we reduce the proof to the case when
$u$ is injective.
For if
$X_0=\frac{X}{\ker(u)}$
we have the induced linear operator
\[
u_0\colon X_0\to Y
\]
where $u_0(X_0)= u(X)$
and at the same time
\[
u_0^*\colon Y\to X_0^*
\] 
where we recall that
\[ 
X_0^*=\ker(u)^\perp=\{x^*\in X^*\colon x^*(\ker (u))=0\}
\]
Here $u_0^*(Y^*)$ can be identified with the closed subspace $u^*(Y)$
in $X_0^*$ which entails that
we reduce the proof to the case when $u$ is injective.
\medskip

\noindent
From now on $u$ is injective
and consider
the image space $u(X)$
whose  closure yields a Banach space $\overline{u(X)}$. Here
\[ 
u\colon X\to \overline{u(X)}
\] 
is a linear operator whose range is dense.
Let us denote this operator with
$T$. The adjoint
\[ 
T^*\colon\, \overline{u(X)}\to X^*
\]
and we have seen that
\[
 \overline{u(X)}=\frac{Y^*}{\ker (u^*)}
 \]
In particular the $T^*$-image is equal to $u^*(Y^*)$
and hence $T^*$ has a closed range.
The requuested closedness of $u(X)$ follows if we show that
\[ 
T\colon X\to \overline{u(X)}
\] 
is surjective.
Hence, we have reduced the proof of to the following:
\medskip

\noindent
{\bf{6.4.2 Proposition.}} \emph{Let $T\colon X\to Y$ be injective
where $T(X)$
is dense in $Y$ and $T^*$ has closed range. Then $T(X)=Y$.}
\medskip

\noindent
\emph{Proof}.
Let $y$ 
be a non-zero vector in $Y$
and put
\[ 
\{y\}^\perp=\{y^*\in Y^*\colon\,y^*(y)=0\}
\]
Consider the image
\[
V=T^*(\{y\}^\perp)
\]
Let us first notice that $V\neq X^*$.
To see this we choose
$y^*$ in $Y^*$ such that $y^*(y)=1$ and get the vector
$T^*(y^*)$. If 
$V=X^*$ this gives some $\eta\in \{y\}^\perp$
such that
$T^*(y)= T^*(\eta)$. This means
that
\[
y^*(Tx)= \eta(Tx)\quad\colon x\in X
\]
The density of $T(X)$ implies that $y^*=\eta$
which is a contradiction since
$\eta(y)=0$.
\medskip

\noindent
Next we show
that
$V$ is closed in the weak-star topology on $X^*$.
By the Krein-Smulian theorem the weak-star closedness follows
if $V$ is closed in $X^*_{bw}$.
So let $S$ be the unit ball in $X$
and $\{\xi_n\}$ is  a sequence in
$V\cap nS^*$ where $\xi_n\overset{w}\to  x^*$
for some
limit vector $x^*$.
The Open Mapping Theorem applies to
the operator $T^*\colon \{y\}^\perp\to X^*$
and gives 
a 
constant $C$ and a sequence $\{y_n^*\in  \{y\}^\perp$
such that $||y_n^*||\leq C$  and 
$T^*(y_n)=\xi_n$.
By weak-star compactness for bounded sets in $ \{y\}^\perp$ we can pass to a 
subsequence and assume that
$y_n^*$ converge in $\{y\}^\perp_w$
to 
a limit vector $y^*$.
If $x\in X$ we get
\[
T^*(y^*)(x)= y^*(Tx)=\lim y^*_n(Tx)=\lim T^*(y_n)(x)=\lim\xi_n(x)=x^*(x)
\]
Hence  $x^*=T^*(y^*)$ which proves that $V$ is weak-star closed
in $X^*$.
\medskip

\noindent
We have proved that
 $V$ is closed in the weak-star topology on $X^*$
and not equal to the whole of $X^*$.
This gives   a non-zero vector
$x\in X$ such that $\widehat{x}(V)=0$ which
gives the implication
\[ 
y^*(y)=0\implies \widehat{x}(T^*(y^*))=
y^*(Tx)=0\quad\colon\ y^*\in Y^*
\tag{i}
\]
Since $T$ is injective we have $Tx\neq 0$ and
(i) gives by linear algebra 
a complex number
$\alpha$ such that $y=\alpha\cdot T(x)$, i.e. the vector $y$ belongs toÊ$T(X)$
as requested.
 

\bigskip

\noindent
{\bf{6.4.3 Operators with finite dimensional  range.}}
The range of $u$ is the image space $u(X)$.
Suppose the range has a  finite dimension $N$ and 
choose 
an $N$-tuple $x_1,\ldots,x_N$ in $X$ such that
$\{u(x_k)\}$ is a basis for
$u(X)$. Consider the
$N$-dimensional subspace of $X$ :
\[
 V={\bf{C}}x_1+\ldots+{\bf{C}}x_N
 \]
The $u$-kernel  is given by:
\[ 
N_u=\{ x\quad\colon\, u(x)=0\}
\] 
It is clear that there exists a direct sum:
\[ 
X=N_u\oplus V
\] 
Next, consider the adjoint operator $u^*$.
In $Y^*$ we can find an $N$-tuple
$y_1^*,\ldots,y_N^*$
such that 
\[
j\neq k\implies y_j^*(u(x_k))=0\quad\text{and}\quad
y_j^*(u(x_j))=1
\]
If $N_{u^*}$ is the kernel of $u^*$ the reader may verify that
\[
Y^*=N_{u^*}\oplus {\bf{C}}y_1^*+\ldots+{\bf{C}}y_N^*
\]
and
conclude  that
the range of $u^*$  is   $N$-dimensional.

\bigskip



\centerline{\bf 6.5 Compact operators.}
\medskip

\noindent
A linear operator
$T\colon X\to Y$ is compact if
the the image under $T$ of the unit ball in
$X$ is relatively compact in $Y$.
By the general result about compact metric spaces in ¤ xx
an equivalent  condition for $T$ to be compact
is that if
$\{x_k\}$ is an arbitrary sequence in the unit ball $B(X)$ then there exists a subsequence of $\{T(x_k)\}$ which converges to some $y\in Y$.
\medskip

\noindent
{\bf{6.5.1 Exercise.}}
Let  $\{T_n\}$
be  a sequence of compact operators
which converge to another operator $T$, i.e. 
\[ 
\lim_{n\to \infty}\, ||T_n-T||=0
\]
where we employ the operator norm on the Banach space
$L(X,Y)$.
Verify that $T$ also is a compact operator.



\medskip



\noindent
{\bf 6.5.2  Theorem.} \emph{A bounded linear operator
$T$ is  compact if and only if its
adjoint $T^*$ is  compact.}

\medskip
\noindent
\emph{Proof.}
Assume first that $T$ is compact and
let $B$ be the unit ball in $X$.
From the material
in ¤ xx this entails that for each
postive integer $N$ there exists
a finite set $F_N$ in $B$
which is $N^{-1}$-dense in $T(B)$, i.e. for
each $y\in T(B)$ there exists
$x\in F_N$ and
\[
||T(x)-y||<N^{-1}\tag{i}
\]
Let us then consider a sequence $\{y_n^*\}$ in the unit ball of
$Y^*$.
By the standard diagonal procedure we find a subsequence
$\{\xi_j=y^*_{n_j}\}$
such that
\[
\lim_{j\to\infty}\, \xi_j(Tx)\quad\colon \, x\in \bigcup_{N\geq 1}\, F_N\tag{ii}
\]
Next, if $x\in B$ and $\epsilon>0$ we  choose $N$ so large
that
$N^{-1}<\epsilon/3$.
Since
(i) hold for the finite set of points in $F_N$
there exists an integer $w$ such that
\[
 |\xi_j(Tx) -\xi_i(Tx)|<\epsilon/3 \quad\colon j,i\geq w\tag{iii}
 \]
hold for each $x\in F_N$. 
Since the $\xi$-vectors have unit norm it follows from
(i) and the triangle inequality  that
(iii) hold for each $x\in B$.
Above $\epsilon>0$ is arbitrary small which entials that
 $\{\xi_j(Tx)\}$ is a Cauchy seqence of complex numbers
for every $x\in B$ and then the same hold for
each $x\in X$. Since  Cauchy sequences of complex numbers converge
there exist limits:
 \[
 \lim_{j\to\infty}\, \xi_j(Tx)\quad\colon x\in X\tag{iv}
 \]
 It is clear that these
 limits values are
 linear with respect to $x$. So by
 the construction of $T^*$
 there exist the pointwise limits
 \[
\lim_{j\to\infty}\, T^*\xi_j(x)\quad\colon x\in X\tag{v}
\]
which means that there exists
$x^*\in X^*$ such that
 \[
x^*(x)=\lim_{j\to\infty}\, T^*\xi_j(x)\quad\colon\in x\in X\tag{vi}
\]
The requested compactness of $T^*$ follows if we have proved that
the pointwise convergence in (vi) is uniformwhen $x$ stays in $B$, i.e.
that
\[
\lim_{j\to\infty}\, ||T^*\xi_j-x^*||=0\tag{vii}
\]
To prove that (vi) gives (viii)
we apply  the Arzela-Ascoli theorem which
shows that pointwise convergence on the relatively compact
set $T(B)$ of the equicontinuous family of functions
$\{\xi_j\}$
gives the uniform convergence in (vii).
\medskip

\noindent
Above we proved that if $T$ is compact, so is $T^*$.
To prove the  the opposed  implication
we employ the bi-dual space
$X^{**}$. From the above the compactness of 
$T^*$ implies that 
$T^{**}$ is compact.
By the construction the restriction of
 $T^{**}$ to the
 the closed subspace $j(X)$ of $X^{**}$ under the bi-dual embedding is compact
which entails  that $T$ is compact.





 

 









\bigskip

\noindent
{\bf{6.5.3 Enflo's example.}}
Denote by
 $\mathcal F(X,Y)$ the family of linear operator from $X into $Y
  with a finte dimensional range and $\mathcal C(X,Y)$
the family of compact operators.
 The question arises if $\mathcal F(X,Y)$ is a dense subspace
of $\mathcal C(X,Y)$.
This was an open problem for many decades until Per Enflo
during  a spectacular seminar at Stockholm University in 1972
constructed an example of a separable Banach space
$X$ and a compact operator $T\in\mathcal C(X,X)$ which
cannot be approximated by operators from
$\mathcal F(X,X)$.
Enflo's counter-example
has led to a veritable industry where one
seeks to determine "good pairs" of Banach spaces
$X$ and $Y$ for which
$\mathcal F(X,Y)$ is dense in $\mathcal C(X,Y)$.
We shall not dwell upon this but remark only that
for most of the "familiar" Banach spaces one has the density
which therefore means that a compact operator can be approximated
in the operator norm by
operators having finite dimensional range.
\bigskip


\centerline {\bf 6.6 Compact pertubations.}
\medskip

\noindent
The main result goes as follows:


\medskip

\noindent 
{\bf 6.6.1 Theorem.}
\emph{Let $u\colon X\to Y$
be an injective operator with closed range and $T\colon\, X\to Y$
a compact operator. Then  the kernel of $u+T$ is finite dimensional
and $u+T$ has closed range.}

\medskip

\noindent
Before we enter the proof we recal from ¤ xx
that the hypothesis on $u$ via the
Open Mppaing Theorem gives $c>0$ such that
\[
||u(x)||\geq c\cdot ||x||\tag {i}
\]






\medskip

\noindent
\emph{ Proof.}
First we show that $N_{u+T}$ is finite dimensional.
By the  result in ¤ xx it suffices to show that the set
below is relatively compact:
\[ 
B=\{x\in N_{u+T}\quad\colon\,||x|\leq 1\}
\]
Let $\{x_n\}$ be a sequence in $B$. Since
$T$ is compact there is a subsequence $\{\xi_j=x_{n_j}\}$
and some vector $y$ such that
$\lim\, T{\xi_j}= y$. Since
$u(\xi_j)=-T(\xi_j)$
it follows that $\{u(\xi_j)\}$ is a Cauchy sequence and then
(i) entails that $\{\xi_j\}$ is a Cauchy sequence and hence has a limit vector.
This proves that
$B$ is relatively compact.
\medskip

\noindent
{\emph {The closedness of $\text{Im}(u+T)$}}.
Since $N_{u+T}$ is finite dimensional the result in  ¤ xx gives
a direct sum decomposition
\[ 
X= N_{u+T}\oplus X_*
\]
Here
$(u+T)(X)= (u+T)(X_*)$ so it suffices that the last image is closed and 
we can restrict both $u$ and $T$ to $X_*$ where  
$T_*$ again is compact. Hence we may assume that
the operator $u+T$ is \emph{injective}.
Next, let
$y$ be in the closure of
$\text{Im}(u+T)$. It means that there is a sequence
$\xi_n$ in $X$ such that
\[ \lim\, (u+T)(x_n)=y\tag{i}
\]
Suppose first that
the norms of $\{x_n\}$ are unbounded. Passing to a subsequence if necessary
we may assume that $||x_n||\to\infty$.
With $x^*_n=\frac{x_n}{||x_n||}$
it follows that
\[ \lim\, u(x_n^*)+T(x_n^*)=0\tag{ii}
\]
Now $\{x_n^*\}$ is bounded and since $T$ is compact we can pass to
another subsequence and assume that 
$T(x_n^*)\to y$ holds for some $y\in Y$. But then
(x) entails that
$u(x_n^*)$ also has a limit and since
$u$ is ionjective it follows as above that
$\{x^*_n\}$ is convergent. It $x_n^*\to x_*$. Here
$x^*\neq 0$ since
$||x_n^*||=1$ for all $n$.
We see that (xx) entails that
$u(x_*)+T(x_*)=0$ and this is contradiction since
$N_{u+T}$ is assumed to be the null space.
\medskip

\noindent So in (i) we now have that
the sequence $\{x_n\}$ is bounded.
Since $T$ is compact we can pass to a subsequence and assume that
$T(x_n)\to \xi$ holds for some
$\xi\in Y$.
But then (i)  entails that
the sequence
$\{u(x_n)\}$ converges to $y-\xi$. Now $u$ is 
injective so the Open Mapping Theorem
implies that
$\{x_n\}$ is a Cauchy sequence in $X$ and hence converges to some
$x^*$. 
Passing to the limit in (i) we 
get
\[ 
u(x_*)+T(x_*)=y
\]
Hence $y$ belongs to $\text{Im}(u+T)$ and Theorem 6.6.1 is proved.











\bigskip

\centerline{\bf{6.7 Spectra and resolvents of compact operators.}}

\medskip

\noindent
Let $T\colon X\to X$ be a compact operator.
For each complex number $\lambda\neq 0$ we set
\[
\mathcal N(\lambda)= \{ x\colon Tx=\lambda\cdot x\}
\]


\noindent
{\bf{6.7.1 Theorem.}} \emph{
The set of non-zero $\lambda$ for which
$N(\lambda)$ contains a non-zero vector is discrete.}
\medskip

\noindent
{\emph{Proof.}}
Suppose that there exists a non-zero cluster point $\lambda_0\neq 0$, i.e.
a sequence $\{\lambda_n\}$ where $\lambda_n\to \lambda_0$ and for
each $n$  a non-zero vector
$x_n\in \mathcal N(\lambda_n)$.
Since the numbers $\{\lambda_n\}$ are distinct and
$T(x_n)= \lambda_n\cdot x_n$ hold one easily verifies
that the vectors 
$\{x_n\}$ are linearly independent.
By the result in ¤ xx we find
a sequence of unit vectors $\{y_n\}$ satisfying the separation in
Theorem ¤ xx and 
\[
\{x_1,\ldots,x_n\}=
\{y_1,\ldots,y_n\}
\] 
hold for each $n$.
Now 
\[
T(\lambda_n^{-1}y_n)-\lambda_m^{-1}T(y_m)=y_n-y_m\in \{y_1,\ldots,y_{n-1}\}
\quad\colon n>m\tag{i}
\]
At the same time the separation  gives
\[
||y_n-y_m||\geq 1
\quad\colon n>m\tag{ii}
\]
Since $\lambda_n$ converge to the non-zero number
$\lambda_0$ this entails that $\{\lambda_n^{-1}y_n\}$
is a bounded sequence and from
(i-ii) we see that
$\{T(\lambda_n^{-1}y_n)\}$ cannot contain a convergent subsequence.
This  contradiction  proves Theorem 6.7.1

\medskip

\noindent
{\bf{6.7.2 Theorem.}}\emph{The spectrum of a compact operator
$T$ is discrete outside the origin.}

 \medskip
 
 \noindent
\emph{Proof.}
Consider a non-zero $\lambda_0\in\sigma(T)$.
By Schauder's result in (xx) the adjoint $T^*$ is also compact.
Hence Theorem 6.7.1 applies to $T$ and  $T^*$ which  gives
 a small punctured disc $\{0<|\lambda-\lambda_0|<\delta\}$
 such that  $\lambda\cdot E-T$ and $\lambda\cdot E^*-T^*$ 
both  are injective
when $\lambda$ belongs to the punctured disc.
 Next,  
 $\lambda\cdot E-T$ has a closed range by Theorem 5.X.
 If it is a proper subspace of $X$  find a non-zero
 $x^*\in X^*$ which vanishes on this range. The construction of
 $T^*$ entails that
 $T^*(x^*)=\lambda\cdot x^*$. But this was not the case and hence
 $\lambda\cdot E-T$ is surjective which shows that
 $\lambda$ is outside $\sigma(T)$ and  finishes the proof of
 Theorem 6.7.2.
 \medskip
 
\noindent
{\bf{6.7.3 Spectral projections}}.
Let $\lambda_0$ be non-zero in
$\sigma(T)$.
By Theorem 6.7.2 it is an isolated poiunt in
$\sigma(T)$ which gives
 the spectral projection
$E_T(\lambda_0)$ where we recal, from ¤ xx that this
operator commutes with $T$.
So if Ê$V=E_T(\lambda_0)(X)$ then
$T$ restricts to a bounded linear operator on $V$
denoted by $T_V$ where we recall from ¤ xx that
the spectrum of $T_V$ is reduced to the singleton set
$\{\lambda_0\}$.
Since $\lambda_0\neq 0$ it means that
$T_V$
is an invertible and compact operator on
$V$. So by
the result in ¤ xx 
$V$ is finite dimensional. 
Ths finiteness and linear algebra applied to
$T_V$ gives an integer $m\geq 1$ such that
\[
(Tx-\lambda_0 x)^m=0\quad \colon x\in V\tag{6.7.3.1}
\]

\bigskip

\centerline{\bf{6.8 Fredholm operators.}}
\medskip

\noindent
A bounded linear operator
 $u\colon X\to Y$ 
is called a  Fredholm operator 
if it has closed range and 
the kernel and the cokernel of $u$ are both  finite dimensional.
When $u$ is  
Fredholm  its index is defined by:
\[ 
\mathfrak{ind}(u)=
\text{dim}\, N_u-\text{dim}\bigl[\frac{Y}{u(X)}\bigr]
\]
\medskip

\noindent
{\bf 6.8.1  Theorem.} \emph{Let $u$ be of Fredholm type  and
$T\colon X\to Y$ a compact operator. Then
$u+T$ is Fredholm and one has the equality}
\[
\mathfrak{ind}(u)=
\mathfrak{ind}(u+T)
\]

\bigskip


\noindent
The proof requires several steps
where the crucial point is to regard 
the case $X=Y$ and a compact pertubation of the
identity operator. Thus we begin with:
\medskip


\noindent
{\bf 6.8.2  Theorem.} \emph{Let $T\colon X\to X$ be compact.
Then $E-T$ is Fredholm and has index zero.}

\medskip

\noindent
\emph{Proof.}
Apply (6.7.3) with $\lambda_0=1$ which gives
the decompostion
\[
X= E_T(1)(X)\oplus
(E-E_T(1))(X)\tag{i}
\]
Theorem 6.6.1 implies that
$E-T$ has closed range.
Next, from the spectral decomposition in (6.7.3)
it follows that 
 $E-T$ restricts to a bijective operator on
$(E-E_T(1))(X)$ which by (i)
entails that
the codimension of $(E-T)(X)$ is at most
the dimension of the finite dimensional vector space
$V=E_T(1)(X)$. Moreover, 
the kernel of $E-T$ is  finite dimensional by Theorem 6.6.1.
\medskip

\noindent
Hence we have proved that
$E-T$ is a Fredholm operator and there reamins to show
that its index is zero.
To obtain this we notice again that
the decomposition
(i) impies that this index is equal to that of
the restricted operator
$E-T$ to the finite dimensional vector space
$V$. Finally,  recall from linear algebra that
the index of a linear operator on a finite dimensional vector space always is zero
which
finishes the proof.
\medskip


\noindent
{\bf{6.8.3 The general case.}}
Consider first the case when the kernel of the Fredholm operstor
$u$ is zero.
Now there exists a finite dimensional subspace $W$ of $Y$ such that
\[
Y= u(X)\oplus W
\]
and here $u\colon X\to u(X)$ is
an isomorphisn between the  Banach spaces $X$ and $u(X)$
which gives the existence of a bounded inverse operator
\[
\phi\colon u(X)\to X
\]
So here $\phi\circ u$ is the identity on $X$.
Next, given a compact operator $T$
we consider the projection operator
$\pi\colon Y\to  u(X)$ whose kernel is
$W$ and notice that $\pi\circ T$ is a compact operator.
Now we can regard the operator
\[ 
u+\pi\circ T\colon X\to u(X)
\]
From the above and Theorem 6.8.2 the reader can verify that
this Fredholm operator has index zero.
Next, we notice that
\[
\mathfrak{ind}(u)=-\dim W\tag{1}
\]
We have also the operator
\[ 
T_*=(E_Y-\pi)\circ T\colon X\to W
\]
The direct sum decomposition (xx) entails that
\[
\ker(u+T)= \ker(u+\pi\circ T\colon X)\cap\, \ker T_*\tag{2}
 \]
\[
\frac{Y}{(u+T)(X)}=
\frac{Y}{(u+\pi\circ T)(X)}\oplus\frac{W}{T_*(X)}\tag{3}
\]
From (1-3) we leave it as an exercise
to show that
the index of $u+T$ is equal to that if $u$
given by (1).
\medskip

\noindent
Above we treated the case when $u$ is injective.
Since $N_u$ is finite dimensional we  have a decompostion
\[ 
X= N_u\oplus X_*
\]
and now the restricted operator $u\colon X_*\to Y$ is injective.
For a given compact operator
$T$ we consider the restrcited compact operator
$T_*|colon X_*\to Y$
and form the previous special case we have
\[
 \mathfrak{ind}(u_*+T_*)= \mathfrak{ind}(u_*)
\]
Next, let  $\pi\colon X\to N_u$ be the projection with kernel $X_*$
which gives
\[ 
T=T_*+T\circ \pi
\] 
At this stage we leave it as an exercise to verify that
(x) gives the requested index formula 
\[
 \mathfrak{ind}(u+T)= 
 \mathfrak{ind}(u)
\]
\medskip

\noindent
{\bf{Remark.}} 
There are more "sophisticated proofs"
which employ suitable diagram chasings
and Theorem xx can be extended to compact pertubations of 
Fredholm operators between Frechet spaces. For 
elegant proofs and conclusive results the reader may consult 
the  lecture by Serre from the Cartan seminars. See
[Cartan-xxxx].



















 















\newpage



\newpage

\centerline {\bf{7. Calculus on Banach spaces.}}

\bigskip

\noindent
Let $X$ and $Y$ be two Banach spaces and
$g\colon\,X\to Y$ some map. Here $g$ is not assumed
to be linear and 
we suppose that
the Banach spaces are real so  the dual space
$Y^*$ consists of continuous ${\bf{R}}$-linear maps from
$Y$ into ${\bf{R}}$.
Every 
$y^*\in Y^*$ yields the real-valued function
$y^*\circ g$ on $X$.
With $x_0$ kept fixed
we can impose the condition that
there exist limits
\[
\lim_{\epsilon\to 0}\,  \frac{y^*\circ g(x_0+\epsilon\cdot x)-
y^*(g(x_0))}{\epsilon}\tag{1}
\]
for each vector $x\in X$.
These limits resemble directional derivatives in calculus and
we can impose the extra condition that
the limits above depend linearly upon $x$.
Thus, assume  that each $y^*\in Y$
yields a linear form $\chi(y^*)$ on $X$ such that
(1) is equal to 
$\chi(y^*)(x)$ for every $x\in X$.
When this holds it is clear that
\[ 
y^*\mapsto \chi(y^*)\tag{2}
\] 
is a linear mapping from $Y^*$ into $X^*$.
When both $Y$ and $X$ are finite dimensional real vector spaces
this linear operator corresponds to the usual Jacobian
in calculus.
In the infinite-dimensional case
it is not always true that
(2) is continuous with respect to the norms
on the dual spaces.
As an extra condition for differentaiblity at $x_0$ we impose the condition that
there exists a constant $C$ such that
\[
||\chi(y^*)||\leq C\cdot ||y^*||\tag{3}
\]
When (3) holds
we have a bounded linear operator $\chi\colon Y^*\to X^*$
associated to $g$ and the given point $x_0\in X$.
It may occur that $\chi$ is the adjoint of a bounded linear operator
from $X$ into $Y$ which 
means that there exists a bounded linear operator $L\colon X\to Y$
such that
\[
\lim_{\epsilon\to 0}\, 
\frac {||g(x_0+\epsilon\cdot x)-g(x_0)-\epsilon\cdot L(x)||}{\epsilon}=0\tag{*}
\]
\medskip

\noindent
Concerning the passage to the limit
the weakest condition is that it holds pointwise, i.e.
(*) holds for every vector $x$.
A stronger condition is to impose that
the limits above hold uniformly which means that
\[
\lim_{\epsilon\to 0}\, \max_{x\in B(X)}\, 
\frac {||g(x_0+\epsilon\cdot x)-g(x_0)-\epsilon\cdot L(x)||}{\epsilon}=0\tag{**}
\]
where the maximum is taken over 
$X$-vectors with norm $\leq 1$.
In applications the
the condition (**) is often taken as a definition for
$g$ to be differentiable at $x_0$ and the uniquely determined linear map 
$L$ above is denoted by $D_g(x_0)$ and called the differential of $g$ at $x_0$.
If $g$ is a map from some open subset
$\Omega$ of $X$ with values in
$Y$ we can impose the condition that
$g$ is differentiable at each $x_0\in \Omega$ and  add the 
condition that
$x\mapsto D_g(x)$ is continuous in $\Omega$ where the values are
taken in
the Banach space of continuous linear maps from $X$ into $Y$.
When this holds we get another map
$x\to D_g(x)$ from $\Omega$ into $\mathcal L(X,Y)$
and can impose the condition that it also is differentiable in the strong sense above.
This leads  to the notion of $k$-times continuosly differentiable maps from
a Banach space into another for every positive integer $k$.
\medskip

\noindent
{\bf{Remark.}} We shall not dwell upon a general study of differentiable maps between 
Banach spaces which is best illustrated by
various examples. For a concise
treatment we refer to Chapter 1 in Hšrmander's text-book
[PDE:1]
which 
contains a proof of the implicit function theorem
for
differentiable maps between Banach spaces
in its most general set-up.

\bigskip

\noindent
\centerline {\bf 7.1 Line integrals}
\medskip

\noindent
Let  $Y$ be a Banach space. Consider a
continuous map $g$ from  some open set
$\Omega$ in ${\bf{C}}$ with values in $Y$.
Let  $t\mapsto \gamma(t)$ be a parametrized $C^1$-curve
whose image is a compact subset of $\Omega$.
Then there exists  the $Y$-valued line integral
\[
\int_\gamma\, g\cdot dz
=\int_0^T\, g(\gamma(t))\cdot \dot\gamma(t)\cdot dt \tag{*}
\]
The evaluation is performed exactly as for ordinary
Riemann integrals, Namely, one uses the fact that
the
$Y$-valued function
\[ t\mapsto g(\gamma(t))
\] 
is uniformly continuous with respect to the norm on
$Y$, i.e. the Bolzano-Weierstrass theorem gives:
\[
\lim_{\epsilon\to 0}
\,\max_{|t-t'|\leq\epsilon}\,||g(t)-g(t')||=0
\]
Then (*) is approximated by Riemann sums and since
$Y$ is complete this gives
a unique limit vector in $ Y$.


\bigskip

\centerline{\bf 7.2 Analytic functions.}
\medskip

\noindent
Let $g(z)$ be a continuous map from
the open  set $\Omega$ into the Banach space $Y$.
We say that  $g(z)$ is analytic  a point $z_0\in\Omega$
if there exists some $\delta>0$    and a 
convergent power series expansion
\[
g(z)=g(z_0)+\sum (z-z_0)^\nu\cdot y_\nu
\colon\quad\, \sum\, ||y_\nu||\cdot \delta^\nu<\infty\tag{*}
\]
The last condition implies that the power series
$\sum (z-z_0)^\nu\cdot y_\nu$ converges in the Banach space $Y$
when $z\in D_\delta(z_0)$.
Notice that if $\gamma\in Y^*$
then (*) gives an ordinary 
complex-valued analytic function
\[
\gamma(g)(z)=\gamma(g(z_0)+
\sum c_\nu\cdot (z-z_0)^\nu
\colon\quad\, c_\nu=\gamma(y_\nu)\tag{**}
\]
Since elements  $y$ in 
$Y$ are determined when we know 
$\gamma(y)$ for every 
$\gamma\in Y^*$ we see that (**) entails that the 
sequence $\{y_\nu\}$ in (*) is unique, i.e. $Y$-valued analytic functions have
unique power series expansions.
Moreover, using (**) the reader may verify the following
Banach-space version of Cauchy's theorem.
\bigskip

\noindent
{\bf 7.3 Theorem.}
\emph{Let $\Omega\in\mathcal D^1({\bf{C}})$ and
$g(z)$ is an $Y$-valued function which is analytic in
$\Omega$ and extends to a continuous function on
$\bar\Omega$. 
Then}
\[
g(z_0)=\int_{\partial\Omega}\, \frac{g(\zeta)\,d\zeta}{\zeta-z_0}\quad\colon\quad
z_0\in\Omega
\]
\medskip

\noindent 
\emph{Moreover, 
we have the vanishing integral}
\[
\int_{\partial\Omega}\, 
g(\zeta)\, d\zeta=0
\]

\medskip

\noindent
{{\bf Exercise.}}
Let $g(z)$ be as above and suppose that
$\phi(z)$ is a complex-valued analytic function
in
$\Omega$ which extends to a continuous  function on its closure.
Multiplying the $Y$-vectors $g(z)$ with the complex scalars
$\phi(z)$ we get the $Y$-valued funtion
$z\mapsto \phi(z)g(z)$.
Show that this $Y$-valued function is analytic and
verify also the Cauchy formula
\[
\phi(z_0)g(z_0)=\int_{\partial\Omega}\, \frac{
\phi(\zeta)g(\zeta)\,d\zeta}{\zeta-z_0}\quad\colon\quad
z_0\in\Omega
\]







\medskip


\centerline{\bf 7.4 Resolvent operators}
\bigskip

\noindent
Let $A$ be a continuous linear operator on a
Banach space $X$.
In XX we defined the spectrum $\sigma(A)$ and proved that
the  resolvent function
\[
R_A(z)=(z\cdot E-A)^{-1}\quad\colon\quad
z\in {\bf{C}}\setminus\sigma(A)\tag{i}
\]


\noindent 
is an analytic function, i.e. the local Neumann series from XX
show that
$R_A(z)$ is an analytic function with values in the
Banach space $Y=\mathcal{L}(X,X)$.
Let us now consider a connected
bounded domain $\Omega\in\mathcal{D}^1({\bf{C}})$
whose boundary $\partial\Omega$ is a union of smooth and closed Jordan curves
$\Gamma_1,\ldots,\Gamma_p$.
Let $f(z)$ be an analytic function in
$\Omega$ which extends to a continuous function on
$\bar\Omega$.
We impose the condition
\[ 
\partial\Omega\cap\sigma(A)=\emptyset\tag{ii}
\]


\noindent
Then we can construct the line integral
\[
\int_{\partial\Omega}\,f(\zeta)\cdot 
R_A(\zeta)\cdot d\zeta\tag{*}
\]
This yields an element of $Y$ denoted by $f(A)$.
Thus, if $\mathcal A(\Omega)$ is the space of analytic functions
with continuous extension to $\bar\Omega$
then (*) gives a map
\[
T_A\colon\,\mathcal{A}(\Omega)\to Y\tag{**}
\]
Let us put
\[ 
\delta=\min\,\{|z-\zeta|\quad\colon\,
\zeta\in\partial\Omega\,\colon\, z\in\sigma(A)\}
\]
By the result in XX there is a constant $C$
which depends on $A$ only such that
the operator norms:
\[
||R_A(\zeta)||\leq \frac{C}{\delta}\quad\colon\quad \zeta\in
\partial\Omega\tag{***}
\]
\medskip

\noindent
From (***) and the construction in (*) we conclude that
the linear operators $T_A(f)$ have norms which are estimated by
\[ 
||T_A(f)||\leq  \frac{C}{\delta}\cdot\ell(\partial\Omega)\cdot
|f|_{\partial\Omega}
\]
where 
$\ell(\partial\Omega)$ is the total arc-length of the boundary.
Hence we have proved:
\medskip

\noindent
{\bf 7.5 Theorem.}
\emph{With $\Omega$ as above there exists  a continuos linear map
$f\mapsto f(A)$ from the Banach space
$\mathcal A(\Omega)$ into $Y$ and one has the norm inequality}
\[
||f(A)||\leq
\frac{C}{\delta}\cdot\ell(\partial\Omega)\cdot |f|_{\partial\Omega}
\]

\medskip

\noindent
Recall  that
the resolvent operators
$R_A(z)$ commute with $A$ in the algebra of linear
operators on $X$.
Since $f(A)$ is obtained by a Riemann sum of 
resolvent operators, it follows that
$f(A)$ commutes with $A$ for every
$f\in\mathcal A(\Omega)$.
At the same time
$\mathcal A(\Omega)$ is a \emph{commutative Banach algebra}.
It turns out that one has a multiplicative formula for 
the operator $T_A\colon f\mapsto f(A)$.
\bigskip

\noindent
{\bf 7.6 Theorem.}
\emph{$T_A$ yields an algebra homomorphism from
$\mathcal A(\Omega)$ into a commutative subalgebra of
$Y$, i.e.}
\[
T_Afg)= T_A(f)\cdot T_A(g)\quad\colon f,g\in\mathcal A(\Omega)
\]


\medskip


\noindent
\emph{Proof.}
In addition to the given domain
$\Omega$ we  construct a slightly smaller domain
$\Omega_*$ which also is bordered by
$p$ many disjoint and closed Jordan curves
$\Gamma^*_1,\ldots,\Gamma^*_p$ where each single
$\Gamma_\nu^*$
is close to
$\Gamma_\nu$ and
$\partial\Omega^*$ stays so close to
$\partial\Omega$ that 
$\bar\Omega\setminus \Omega_*$
does not intersect $\sigma(A)$.
Consider 
pair $f,g$ in $\mathcal A(\Omega)$.
The careful choice of $\Omega_*$
and Cauchy's integral formula
give the equality
\[
g(A)= \int_{\partial \Omega_*}\, g(\zeta_*)\cdot R_A(\zeta_*)\cdot d\zeta_*\tag{i}
\]
where we use $\zeta_*$ as a variable to distinguish from the subsequent integration
along $\partial\Omega$.
To compute $f(A)$ we keep integration on $\partial\Omega$
and obtain
\[
g(A)\cdot f(A)=
\int_{\partial\Omega_*}\int
_{\partial\Omega}\,g(\zeta_*)\cdot f(\zeta)\cdot
R_A(\zeta_*)\cdot R(\zeta)\cdot d\zeta_*d\zeta\tag{ii}
\]
Next we use the Nemann's  equation
\[
R_A(\zeta_*)\cdot R(\zeta)=
\frac{R(\zeta_*)-R(\zeta)}
{\zeta-\zeta_*}\tag{ii}
\]
The double integral in (ii)  becomes a sum of two integrals
\[
C_1=\int_{\partial\Omega_*}\int
_{\partial\Omega}\, g(\zeta_*)\cdot f(\zeta)
\frac{R(\zeta_*)}
{\zeta-\zeta_*}\cdot d\zeta_*d\zeta
\]
\[
C_2=-\int_{\partial\Omega_*}\int
_{\partial\Omega}\, g(\zeta_*)\cdot f(\zeta)
\frac{R(\zeta)}
{\zeta-\zeta_*}\cdot d\zeta_*d\zeta
\]
To find $C_1$ we first perform integration with
respect to
$\zeta$. Since every $\zeta_*$ from
the inner boundary
$\partial\Omega_*$ belongs 
to the domain $\Omega$
Cauchy's formula applied to the analytic function $f$ gives:
\[
f(\zeta_*)=\frac{1}{2\pi i}\int_{\partial\Omega}\,\frac{f(\zeta)d\zeta}{\zeta-\zeta_*}
\]
Inserting this in the double integral defining $C_1$ we get
\[ 
C_1=\frac{1}{2\pi i}
\int_{\partial\Omega_*}
\int_{\partial\Omega_*}\,
f(\zeta_*)g(\zeta_*)\cdot 
R(\zeta_*)\cdot d\zeta_*=T_A(fg)\tag{iii}
\]
\medskip

\noindent
To evaluate $C_2$ we first perform integration along
$\partial\Omega_*$, i.e. we regard:
\[
\int_{\partial\Omega_*}
\frac{g(\zeta_*)}{\zeta-\zeta_*}\cdot d\zeta_*
\]
Here  $\zeta$ stays \emph{outside} the domain
$\Omega_*$ and hence (iv) is zero by Cauchy's vanishing theorem.
So $C_2=0$ and  (iii) gives the equality in
Theorem 7.6.
\bigskip


\noindent
{\bf{7.7 The Banach algebra $\mathcal A$.}}
This is the closed subagebra of $Y$
generated by
$A$ and all the resolvent operators
$R_A(z)$ as $z$ moves outside $\sigma(A)$.
Let $\mathfrak{M}_A$ denote its 
Gelfand space.
\medskip

\noindent
{\bf 7.8 Proposition} \emph{The Gelfand space
$\mathfrak M_A$
can be identified with the compact set
$\sigma(A)$.}
\medskip

\noindent
\emph{Proof.} 
As explained in ¤ XX the points in
$\mathfrak{M}_A$ correspond to
multiplicative
and linear forms on
$\mathcal A$.
Let
$\gamma$ be such a multiplicative
linear functional.
If $\gamma(A)=z_*$ for some complex number
$z_*$
then the $\gamma$-values are determined on all resolvents. In
fact,
this holds since
\[
1=\gamma((\lambda\cdot E-A)R_A(\lambda))=
(\lambda-z_*)\cdot \gamma(R_A(\lambda))
\]
hold when
$\lambda\in{\bf{C}}\setminus \sigma(A)$
Notce that this also entails that
$z_*$ must belong to $\sigma(A)$.
There remains  to show that
for each point $z_*\in\sigma(A)$ there exists
some $\gamma$ such that $\gamma(A)= z_*$.
To prove this we notice that the hypothesis on $z_*$ means that
the operator $z_*\cdot E-A$ is not inverible on $X$.
If $z_*$ is outside the range of the Gelfand transform of $A$ in the
Banach algebra $\mathcal A$, then
$z_*\cdot E-A)$ would be invertible in $\mathcal A$ whuch
gives a contradiction and finishes the proof of
Proposition 7.8.



\bigskip

\noindent
{\bf 7.9 The sup-norm case.}
Suppose that 
$\mathcal A $ is a sup-norm algebra and put $K=\sigma(A)$.
Let $\Omega$
be an open set
$\Omega$ which contains  $K$.
The operational calculus 
gives
an algebra homomorphism
\[
T_A\colon\,\mathcal O(\Omega)\to \mathcal A
\]


\noindent
Let $f\in A(\Omega$.
The spectrum of the $\mathcal A$-element
$f(A) $ is
equal to $f(\sigma(A))$. 
When $\mathcal A$
is  a sup-norm
algebra it follows that
\[
\max_{z\in K}\, |f(z)|=||f(A)||\tag{*}
\]
Above  $\Omega$ is an arbitrary open neighborhood of $K$.
Since $\mathcal A$ is a Banach algebra we can therefore perform
a limit as the open sets $\Omega$ shrink to $K$
and obtain 
an algebra homomorphism  as follows:
We have the sup-norm algebra
$\mathcal H(K)$ which consists of continuous functions on
$K$ which an be uniformly approximated 
on $K$
by analytic functions defined in small open
neighborhoods.
Then (*) yields  an algebra homomorphism
\[ 
T_A\colon\, f\mapsto f(A) \quad\colon\quad f\in\mathcal A(K)
\]
Moreover it is an isometry, i.e.
\[
\max_{z\in K}\, |f(z)|= ||f(A)||
\]
In this way the Banach algebra $\mathcal A$ is identified with
the sup-norm algebra $\mathcal H(K)$.
\bigskip

\noindent
{\bf 7.10 A special  case.}
If $K$ is "thin" one has the equality
\[
\mathcal H(K)=C^0(K)\tag{*}
\]
For example,  Theorem ¤¤ in chapter XX shows that
if the 2-dimensional Lebesgue measure of $K$ is zero then
all continuous functions on $K$ can be uniformly approximated
by rational functions with poles outside $K$ and then (*) holds.
If we also assume that ${\bf{C}}\setminus K$
is connected then Runge's Theorem from ¤¤ XX
shows that
$C^0(K)$ is equal to the closure of analytic polynomials
$P(z)$. So in this case
polynomials in  $A$ generate
a dense subalgebra of $\mathcal A$.
\bigskip

\centerline{\bf{7.11 Uniformly convex    Banach spaces.}}
\medskip

\noindent
A Banach space $X$ is uniformly  convex if there corresponds to each 
$0<\epsilon<1$ some $\delta(\epsilon)$ tending to zero with
$\epsilon$  such that

\[ 
\frac{||x+y||}{2}\geq 1-\epsilon\implies
||x-y||\leq \delta(\epsilon)
\]
for all pair of vectors of norm one at most.
This condition   was introduced by Clarkson
in the article [Clarkson] from
1936. 
\medskip

\noindent
{\bf{Exercise.}}
Show  that in a uniformly convex Banach space
each closed convex set contains a unique vector of minimal norm.

\medskip

\noindent
Next, let $p$ be a non-zero vector in $X$.
If $x\neq 0$ is another vector
we get the function of a real variable $a$ defined by:
\[
a\mapsto ||p+ax||-||p||
\]
We say that $X$ has directional $x$-derivative at $p$ if there exists the limit
\[
\lim_{a\to 0}\,\frac{||p+ax||- ||p||}{a}=
D_p(x)
\]
Notice that in this limit $a$ can tend to zero both from
the negative and the positive side.
The following result is due to Clarkson:




\medskip

\noindent
{\bf{Theorem}} \emph{Let $p$ be a non-zero vector in
$X$ such that the directional derivatives above exist for every
$x|n X$. Then $x\mapsto D-p(x)$ is linear and 
the vector $D_p\in X^*$ has norm one with
$D_p(p)=1$.}

\medskip

\noindent
{\bf{Exercise.}} Prove Clarkson's result.



\medskip

\noindent
{\bf{7.11.2 Conjugate vectors.}}
For brevity we say that
$X$ is differentiable if the directional derivatives above exist for all pairs $p,x$.
Let $S$ be the unit sphere in $X$ and $S^*$ the unit sphere in
$X^*$. A pair $x\in S$ and $x^*\in S^*$ are said to be conjugate if
\[ 
x^*(x)=1
\]


\noindent
{\bf{7.11.3  Theorem.}} \emph{Let $X$ be uniformly convex and 
differentiable. Then every $x\in S$ has a unique conjugate
given by $x^*=D_x(x)$ 
and  the map $x\to x^*$ from $S$ to
$S^*$ is bijective.}



\medskip

\noindent
{\bf{Exercise.}}
Prove this result or consult
Clarkson's article or some text-book.


\medskip

\noindent
{\bf{7.11.4  Duality maps.}}
Let
$X$ be uniformly convex and differentiable and
$\phi(r)$ is  a strictly increasing and continuous function on
$r\geq 0$ where $\phi(0)=0$ and $\phi(r)\to +\infty$ 
when $r\to +\infty$.  
Each verctor in
$X$ is of the form
$r\cdot x$ with $x|in S$ while $r\geq 0$.
The duality map above yields a function
$\mathcal D_\phi$ from $X$ into $X^*$ defined by
\[ 
\mathcal D_\phi (rx)= \phi(r)\cdot x^*
\quad\text{when}\quad  x\in S\quad\text{and}\quad  r\geq 0
\]
If $C$ is a closed subspace in $X$ we put:
\[ 
C^\perp=\{\xi\in X^*\quad \colon\quad \xi(C)=0\}
\]



\noindent
{\bf{7.14 Theorem.}}
\emph{For each closed 
and proper subspace $C\neq X$  the following hold:
For 
every pair of vectors $x_*\in X$ and $y^*\in X^*$
the intersection}
\[ 
\mathcal D_\phi(C+x_*)\cap \{C^\perp+y*\}
\]
\emph{is non\vvv empty and consists of a single point in $X^*$.}


\medskip

\noindent
\emph{Proof.} Introduce the function
\[ 
\Phi(r)= \int_0^r\,\phi(s)\, ds
\]
Since $\phi$ is strictly increasing,
$\Phi$ is a strictly convex function
and since $\phi(r)\to +\infty$ we have
$\frac{\Phi(r)}{r}\to +\infty$.
Consider the functional defined on $C+x_*$
by

\[ 
F(x)= \Phi(||x||)-y^*(x)
\]
If $||x||= r$ we have
\[ 
F(x)\geq \Phi(r)-r||y^*||
\]
The right hand side is a strictly convex function of $r$
which tends to $+\infty$ and is therefore bounded below. Hence
there exists  a number
\[ 
\delta =\inf_{x\in C+x_*}\, F(x)
\]
Let $\{x_n\}$ be a minimizing sequence for $F$.
The strict convexity of $\Phi$ entails that
the norms $\{||x_n||\}$ converge to some finite limit $\alpha$.
Since the set $C+x_*$ is convex we have
\[ 
F(\frac{x_n+x_m}{2})\geq \delta
\]
Next, the convexity of $\phi$ entails that
\[
0\leq \frac{1}{2}\bigl[ \Phi(||x_n||)+
\Phi(||x_m||)-\Phi(||\frac{x_n+x_m}{2}||)=
\]
\[
 \frac{1}{2}\bigl(F(x_n)+F(x_m))-
 F(\frac{x_n+x_m}{2})
 \]
Since $\{x_n\}$ is $F$-minimizing the last terms tend to zero when
$n$ and $m$ increase which gives
\[
\lim_{n,m\to \infty}\, \Phi(||\frac{x_n+x_m}{2}||)=\Phi(\alpha) \tag{1}
\]
where we recall that
\[ 
\alpha=\lim_{n\to\infty}\, ||x_n||
\]
Now (1) and the strict convexity of $\Phi$ gives
\[
\lim_{n,m\to \infty}\, ||\frac{x_n+x_m}{2}||)=\alpha 
\]
The unifom convexity entails  that
$\{x_n\}$ is a Cauchy sequence which gives  a limit
point $p$ where $F(p)= \delta $ and consequently
\[ 
F(p+tx)-F(p)\geq 0\quad\colon\quad
x\in C\tag{2}
\]
Since $p$ belongs to $C+x_*$ the existence part in Theorem
7.14 follows if we have proved the inclusion
\[
\mathcal D_\phi(p)\in C^\perp+y^*\tag{3}
\]

\medskip

\noindent
To get (3) we use that the Banach space is differentiable
and since the $\Phi$-function as a primitive of a continuous function is of class $C^1$
one has

\[
\Phi(||p+tx||)-\Phi(||p||)=
\Phi'(||p||)\cdot \mathfrak{Re}\, tD_p(x) +o(|t|)=
\phi(\alpha)\cdot \mathfrak{Re}\, tD_p(x)+o(|t|)
\]
where $t$ is a small real or complex number.
Together with (2) this gives
\[
\phi(\alpha)\cdot \mathfrak{Re}\, tD_p(x)+o(|t|)\geq
\mathfrak{Re}\, y^*(tx)\quad\colon\quad x\in C
\]
By linearity it is clear that this implies that
\[
\phi(\alpha)\cdot D_p(x)= y^*(x)
\]
This means precisely that
the linear functional $y^*-\phi(\alpha)\cdot D_p$ belongs to $C^\perp$,
or equivalently that
\[ 
\phi(||p||)\cdot D_p\in C^\perp+y^*
\] 
Finally we recall from (7.13) 
that  
\[
\mathcal D_\phi(p)=\phi(||p||)\cdot D_p(p)
\]
and  the requested inclusion (3) is proved.
\medskip

\noindent
\emph{The uniqueness part.}
Above we proved the existence of at least one point in
the intersection from Theorem 7.12. The verification that
this set is reduced to a single point is left as an exercise to the reader.










\newpage


\centerline {\bf \large {8. Bounded self-adjoint operators.}}

\medskip

\noindent
{\bf Introduction.}
Let $\mathcal H$ be a complex Hilbert space.
A bounded linear operator $S$ on $\mathcal H$ is 
self-adjoint if $S=S^*$, or equivalently
\[ 
\langle x,Sy \rangle=\text{the complex conjugate of}\,\, 
\langle Sx, y\rangle\quad\colon\quad x,y\in \mathcal H\tag{*}
\]
If $S$ is self-adjoint we have the equality of operator norms:
\[ 
||S||^2=||S^2||\tag{1}
\]
To see this we notice that if $x\in\mathcal H$ has norm one then
\[
\langle Sx,Sx\rangle=
\langle x,S^*Sx\rangle=
\langle x,S^2x\rangle\tag{i}
\]
By the Cauchy-Schwarz inequality the last term
is $\leq ||x|\cdot ||S^2||$. Since (i) holds for
every $x$ of norm one we conclude that
\[
||S||^2\leq ||S^2||
\]
Now (1) follows
from the multiplicative inequality for operator norms.
Next, by induction over $n$ we get the
equalities
\[
||S||^{2n}=||S^n||^2\quad\,\colon\,\,n\geq 1
\]
Taking the $n$:th root and passing to the limit the spectral
radius formula gives
\[
||S||=\max_{z\in\sigma(S)}\, |z|\tag{*}
\]


\noindent
Next, we
consider the spectrum of self-adjoint operators.

\medskip

\noindent
{\bf{8.1 Theorem.}}
\emph{The spectrum of a bounded self-adjoint operator
is a compact real interval.}
\medskip

\noindent
\emph{Proof.}
Let $\lambda$ be a complex number 
and for a given $x$ we set
$y=\lambda x-Sx$.
It follows that
\[ 
||y||^2=|\lambda|^2\cdot ||x||^2+||Sx|^2+
\lambda\cdot \langle x,Sx\rangle+
\bar \lambda\cdot \langle Sx,x\rangle
\]
Since $S$ is self-adjoint
we get
\[
\lambda\cdot \langle x,Sx\rangle+
\bar \lambda\cdot \langle Sx,x\rangle=2\cdot \mathfrak{Re}(\lambda)\cdot
\langle Sx,x\rangle
\]
Now $|\langle Sx,x\rangle|\leq ||Sx||\cdot ||x||$
so the triangle inequality gives
\[
||y||^2\geq |\lambda|^2\cdot ||x||^2+||Sx|^2-2|\mathfrak{Re}(\lambda)||\cdot
||Sx||\cdot ||x||\tag{i}
\]
With $\lambda=a+ib$
the right hand side becomes
\[ 
b^2||x||^2+a^2||x||^2+||Sx||^2-2a\cdot ||Sx||\cdot ||x||\geq b^2||x||^2
\]
Hence we have proved that
\[ 
||\lambda x-Sx||^2\geq( \mathfrak{Im}\,\lambda)^2\cdot ||x||^2\tag{ii}
\]
This implies that
$\lambda E-S||$ is invertible for every non-real $\lambda$
which proves Theorem 8.1.





\medskip



\noindent
Theorem 8.1 together with
the general result from 7.XX gives the following:
Denote by ${\bf{S}}$  the closed subalgebra of
$L(\mathcal H,\mathcal H)$ generated by $S$ and the identity
operator. Then ${\bf{S}}$ is 
a sup-norm algebra which is isomorphic to
the sup-norm algebra
$C^0(\sigma(S))$.


\medskip


\noindent
{\bf{8.2 Exercise.}}
Let $T$ be an arbitary bounded opertor
on $\mathcal H$. Show that
the operator $A=T^*T$ is self-adjoint and that $\sigma(A)$
is a compact subset of $[0,+\infty)$,  i.e. every point in its spectrum os
real and non-negative.
A hint is to use the biduality formula $T= T^{**}$
and if $s$ is real the reader should verify that
\[
||sx+T^*T x||^2=s^2||x||^2+2s\cdot ||Tx||^2+||T^*T x||^2
\]

\bigskip

\centerline{\bf{8.3 Normal operators.}}
\bigskip

\noindent
A bounded linear operator $A$ is normal if it commutes with its
adjoint $A^*$.
Let $A$ be normal and put $S=A^*A$ which yields a self-adjoint by  Exercise 8.2.
Here  (8.0.1) gives
\[
||S||^2= ||S^2||=||A^2\cdot A(^*)^2||\leq
||A^2||\ddot ||(A^*)^2||\tag{1}
\]
where we used the multiplicative inequality for operator norms.
Now $(A^*)^2$ is the adjoint of $A^2$
and we recall from ¤ xx that
thr norms of an operator and its adjoint are equal. Hence
the right hand side in (1) is equal to $||A^2||^2$.
At the same time
\[
||S||= ||A^*A||= ||A||^2
\] 
and we conclude that (1) gives
\[
||A||^2\leq ||A^2||\tag{3}
\]
Exactly as in the self-adjoint case we can take higher powers
and obtain
the equality
\[
||A||=\max_{z\in\sigma(A)}\,|z|\tag{*}
\]
Since every polynomial in $A$ again is a normal operator
for which (*) holds we have proved the following:
\medskip

\noindent
{\bf{8.4 Theorem}}
\emph{Let $A$ be a normal operator.
Then the closed subalgebra ${\bf{A}}$ generated by
$A$ in  $L(\mathcal H,\mathcal H)$
is a sup-norm algebra.}
\medskip

\noindent
{\bf{Remark.}}
The spectrum $\sigma(A)$ is 
some compact subset of  ${\bf{C}}$ and in general analytic polynomials
restricted to $\sigma(A)$ do not generate a dense subalgebra of
$C^0(\sigma(A))$.
To get a more extensive algebra
we
consider the closed subalgebra $\mathcal B$
of
$L(\mathcal H,\mathcal H)$ which is generated by $A$ and $A^*$.
Since every  polynomial in $A$ and $A^*$ again is a normal operator
it follows that 
$\mathcal B$ is a sup-norm algebra and here 
the following holds:

\medskip
\noindent
{\bf{8.5 Theorem.}}
\emph{The sup-norm algebra $\mathcal B$ is via the Gelfand
transform isomorphic with $C^0(\sigma(A))$.}
\medskip

\noindent
\emph{Proof.}
If $S\in\mathcal B$ is self-adjoint then we know from the previous section that its
Gelfand transform is real-valued. Next, let $Q\in\mathcal B$
be arbitrary. Now $S=Q+Q^*$  is self-adjoint.
So if $p\in\mathfrak{M}_\mathcal B$
it first follows that the gelfand transform $\widehat Q(p)+\hat Q^*(p)$ is real, i.e. 
with $\widehat Q(p)= a+ib$ we must have $\hat Q^*=a_1-ib$ for some 
real number $a_1$. Next,  $QQ^*$ is also self-adjoint and hence
$(a+ib)(a_1-ib)$ is real. This gives $a=a_1$ and hence we have proved that
the Gelfand transform of $Q^*$ is the complex conjugate function of
$\widehat Q$. Hence the Gelfand transforms of $\mathcal B$-elements is 
a self-adjoint algebra and 
the Stone-Weierstrass theorem implies that
the Glefand transforms of $\mathcal B$-elements is 
equal to the whole algebra 
$C^0(\mathfrak{M}_\mathcal B$.
Finally, since $\widehat A^*$ is the complex conjugate function of 
$\widehat A$ it follows that the Gelfand transform
$\widehat A$  separates points on $\mathfrak{M}_\mathcal B$
which means that this maximal ideal space can be identified with
$\sigma(A)$.


\bigskip


\centerline {\bf{8.6 Spectral measures.}}
\medskip


\noindent
Given $\mathcal B$ and $\sigma(A)$ as above
we  construct certain Riesz measures on
$\sigma(A)$.
Namely, each   pair of vectors $x,y$
in
$\mathcal H$ yields
a linear functional on
$\mathcal B$ defined by 
\[ 
T\mapsto \langle Tx,y\rangle
\]
The Riesz representation formula gives 
a unique Riesz measure 
$\mu_{x,y}$ on $\sigma(A)$ such that
\[
\langle Tx,y\rangle=\int_{\sigma(A)}\, \hat T(z)\cdot d\mu_{x,y}(z)\tag{8.6 *}
\] 
hold for every $T\in \mathcal B$.
Since $\widehat A(z)=z$ we have 
\[
\langle Ax,y\rangle=\int\, z\cdot d\mu_{x,y}(z)
\]
Similarly one has
\[
\langle A^*x,y\rangle=\int\, \bar z\cdot d\mu_{x,y}(z)
\]
\medskip

\noindent
{\bf{8.7 The operators $E(\delta)$}}.
Notice  that (8.6 *) implies that the map
from $\mathcal H\times\mathcal H$ into
the space of Riesz measures on $\sigma(A)$ is bi-linear.
We have for example:
\[
\mu_{x_1+x_2,y}=\mu_{x_1,y}+\mu_{x_2,y}
\]



\noindent
Moreover, since
$\mathcal B$ is the sup-norm algebra $C^0(\sigma(A))$
the total variations of the $\mu$-measures
satisfy the equations:
\[
||\mu_{x,y}||\leq\max_{T\in \mathcal B_*}|\langle Tx,y\rangle|\tag{8.7.1}
\]
where $\mathcal B_*$ is the unit ball in
$\mathcal B$. From this we obtain
\[
|| \mu_{x,y}||\leq ||x||\cdot ||y||\tag{8.7.2}
\]


\noindent
Next, let $\delta$ be a Borel subset of
$\sigma(A)$. Keeping $y$ fixed in $\mathcal H$
we obtain a linear functional on $\mathcal H$ defined by
\[ 
x\mapsto 
\int_\delta \,  d\mu_{x,y}(z)=\mu_{x,y}(\delta)
\]
By (8.7.2) it has norm $\leq ||y||$ and is represented by
a vector $E(\delta)x$ in $\mathcal H$. More precisely 
\[
\langle E(\delta)x,y\rangle= 
\int_\delta \,  d\mu_{x,y}(z)=\mu_{x,y}(\delta)\tag{8.7.3}
\]
\medskip

\noindent
{\bf{8.8 Exercise.}}
Show that $x\mapsto E(\delta)x$ is linear and that
the resulting linear operator
$E(\delta)$
commutes with all operators in $\mathcal B$. Moreover, show that 
it is a self-adjoint projection, i.e.
\[ 
E(\delta)^2=E\delta)\quad\text{and}\quad
E(\delta)^*=E(\delta)
\]
Finally, show that
\[
E(\delta_1\cap\delta_2)=E(\delta_1)E(\delta_2)
\] 
holds for every pair of Borel subsets and with
$\delta=\sigma(A)$ one gets the identity operator.

\bigskip
\noindent
{\bf{8.9 Resolution of the identity.}}
If $\delta_1,\ldots,\delta_N$ is any finite family of disjoint 
Borel sets whose union is
$\sigma(A)$ then
\[
1= E(\delta_1)+\ldots +E(\delta_N)
\]
At the same tine we get a decomposition of the operator $A$:
\[
A=A_1+\ldots+A_N\quad\text{where}\quad
A_k=E(\delta_k)\cdot A
\]
For each $k$ the spectrum $\sigma(A_k)$ is equal to  the closure of
$\delta_k$. So the normal operator is represented by a sum of normal operators
where the individual operators have  small spectra when the
$\delta$-partition is fine.


\newpage

\centerline{\bf{9. Unbounded operators on Hilbert spaces}}
\bigskip


\noindent
Let $T$ be a densely
defined
linear operator on a complex Hilbert space $\mathcal H$.
We  suppose that 
$T$ is unbounded so that:
\[ 
\max_{x\in\mathcal D_*(T)}\, ||Tx||=+\infty
\quad \mathcal D_*(T)=\text{ the set of unit vectors in}\quad 
\mathcal D(T)
\]

\medskip

\noindent{\bf{9.1 The adjoint $T^*$.}}
If $y\in\mathcal H$  we get a linear functional on
$\mathcal D(T)$ defined by
\[
 x\mapsto \langle Tx,y\rangle\tag{i}
\]
If there exists a constant $C(y)$ such that
the absolute value of (i) is $\leq C(y)\cdot ||x||$ for every
$x\in\mathcal D(T)$, then  (i) extends to a continuous linear
functional on
$\mathcal H$.
The extension is unique because 
$\mathcal D(T)$ is dense and since   $\mathcal H$ 
is self-dual there exists 
a
unique vector
$T^*y$ such that
\[
\langle Tx,y\rangle=
\langle x,T^*y\rangle\quad\colon\quad x\in\mathcal D(T)
\tag{9.1.1}
\]
This gives  a linear operator $T^*$
where $\mathcal D(T^*)$ is characterised  as above,
To describe the
graph of $T^*$ 
we consider  the Hilbert space  $\mathcal H\times\mathcal H$
equipped with the  inner product
\[
\langle (x,y),(x_1,y_1)\rangle= 
\langle x,x_1\rangle+\langle y,y_1\rangle
\]
On $\mathcal H\times\mathcal H$ we define the linear operator
\[ 
J(x,y)= (-y,x)
\]


\noindent
{\bf{9.2 Proposition.}}
\emph{For every densely defined operator $T$
one has the equality}
\[ 
\Gamma(T^*)= J(\Gamma(T))^\perp
\]


\noindent
\emph{Proof.}
Let $(y,T^*y)$ be a vector in
$\Gamma(T^*)$. If $x\in\mathcal D(T)$  the equality (9.1.1)
and the construction of $J$ give
\[
\langle (y,-Tx\rangle + \langle  T^*y,x\rangle =0
\]
This proves  that $\Gamma(T^)*\perp
J(\Gamma(T))$. Conversely,  if 
$(y,z)\perp J(\Gamma(T))$
we have
\[
\langle y,-Tx\rangle + \langle  z,x\rangle=0
\quad\colon x\in\mathcal D(T)\tag{i}
\]
This shows that
$y\in\mathcal D(T^*)$ and  $z=T^*y$ which proves Proposition 9.2.
\medskip

\noindent
{\bf{9.3 Consequences.}}
The   orthogonal complement of
a subspace in a Hilbert space is  always
closed. Hence   Proposition 9.2 entails  that
$T^*$ has a closed graph. Passing to the closure of
$\Gamma(T)$
the decompostion of a Hilbert space
into a direct sum of a closed subpace and its orthogonal complement gives
\[
\mathcal H\times\mathcal H=
\overline{J(\Gamma(T))}\oplus \Gamma(T^*)
\tag{9.3.1}
\]


\noindent
Notice also that 
\[
\Gamma(T^*)^\perp=\overline{J(\Gamma(T))}\tag{9.3.2}
\]
\medskip

\noindent
{\bf{9.4 Closed extensions of operators.}}
A closed operator $S$ 
is called a
closed extension of $T$ if
\[
\Gamma(T)\subset\Gamma(S)
\]

\medskip

\noindent
{\bf{9.4.1 Exercise.}}
Show that 
if $S$ is a  closed extension of $T$ then
\[
S^*=T^*
\]



\noindent
{\bf{9.4.2 Theorem.}}
\emph{A densely defined operator $T$  has a closed extension if and only if
$\mathcal D(T^*)$ is dense.
Moreover, if $T$ is closed one has the biduality formula
$T=T^{**}$.}
\medskip

\noindent
\emph{Proof.}
Suppose first that $T$ has a closed extension. 
If $\mathcal D(T^*)$ is not dense 
there
exists a non-zero vector $0\neq h\perp \mathcal D(T^*)$ and
(9.3.2) gives
\[
(h,0)\in\Gamma(T^*)^\perp=J(\Gamma(T))\tag{ii}
\]
By the construction of $J$ this would give
$x\in\mathcal D(T)$ such that
$(h,0)=(-Tx,x)$ which cannot hold since
this equation first gives $x=0$ and then
$h=T(0)=0$.
Hence  closedness of $T$ implies that
$\mathcal D(T^*)$ is dense.
Conversely, assume that
$\mathcal D(T^*)$ is  dense. 
Starting from $T^*$  we 
construct its adjoint  $T^{**}$ and 
Proposition 9.3.2 applied with $T^*$  gives
\[
\Gamma(T^{**})= J(\Gamma(T^*)^\perp\tag{i}
\]
At the same time 
$J(\Gamma(T^*)^\perp$ is equal to the closure of
 $\Gamma(T)$ so (i) gives
\[
\overline{\Gamma(T)}=
\Gamma(T^{**})\tag{ii}
\]
which proves that $T^{**}$ is a closed extension of $T$.
\medskip

\noindent
{\bf{9.4.3 The biduality formula.}}
Assume that the densely defined operator $T$ is closed.
We constrict $T^*$ which by the above is densely defined and therefored its dual exists.
It is denoted by
$T^{**}$ and called the bi-dual of $T$. With these notations one has:
\[
T=T^{**}\tag{*}
\]
\medskip

\noindent
{\bf{9.4.4 Exercise.}} Prove the equality (*). 

\bigskip


\centerline {\bf{9.5 Inverse operators.}}.
\medskip

\noindent
Denote by
$\mathfrak I(\mathcal H)$ the set of
closed and densely defined operators $T$ such that
$T$ is injective on $\mathcal D(T)$ and the range $T(\mathcal D(T))$Êis dense in
$\mathcal H$.
If $T\in\mathfrak I(\mathcal H)$
there exists the densely defined operator $S$ where
$\mathcal D(S)$ is the range of  $T$ and
\[
S(Tx)= x\quad\colon\quad x\in\mathcal D(T)
\]
By this construction the range of $S$ is equal to
$\mathcal D(T)$. Next, 
 on $\mathcal H\times\mathcal H$
we have the isometry defined by
$I(x,y)= (y,x)$,  i.e we  interchange the pair of vectors.
The construction of $S$ gives 
\[ 
\Gamma(S)= I(\Gamma(T))\tag{i}
\]
Since $\Gamma(T)$ by hypothesis is closed it follows that
$S$ has a closed graph and we conclude that $S\in\mathfrak I(\mathcal H)$.
Moreover, since $I^2$ is the identity on
$\mathcal H\times \mathcal H$ we have
\[ 
\Gamma(T)= I(\Gamma(S))\tag{ii}
\]
We refer to $S$ is as the inverse of
$T$. It is denoted by $T^{-1}$
and  (ii) entails  that
$T$ is the inverse of $T^{-1}$, i.e one has
\[ 
T=(T^ {-1})^{-1}
\]

\medskip

\noindent
{\bf{9.5.1 Exercise.}}
Let $T$ belong to
$\mathfrak I(\mathcal H)$.
Use the description of $\Gamma(T^*)$
in Proposition 9.3   to show that $T^*$  belongs to 
$\mathfrak I(\mathcal H)$  and the equality  
\[
(T^{-1})^*= (T^*)^{-1}\tag{*}
\]


\noindent
{\bf{9.6 The operator $T^*T$}}.
Each 
$h\in\mathcal H$ gives  the vector $(h,0)$ in
$\mathcal H\times\mathcal H$ and  (9.3.1) gives
a  pair  $x\in\mathcal D(T)$ and $y\in\mathcal D(T^*)$.
such that
\[
(h,0)= (x,Tx)+(-T^*y,y)=(x-T^*y, Tx+y)
\]
With $u=-y$ we get $Tx=u$ and obtain
\[
 h=x+T^*(Tx)\tag{9.6.1}
\]


\medskip

\noindent
{\bf{9.6.2  Proposition.}}
\emph{ The vector $x$ in (9.6.1) is uniquely determined by $h$.}

\medskip

\noindent
\emph{Proof.}
Uniqueness follows if we show that
\[
x+T^*(Tx)\implies x=0
\]
But this is clear since the construction
of $T^*$ gives
\[
0=\langle x,x)\rangle+ \langle x,T^*(Tx)\rangle=
\langle x,x)\rangle+ \langle Tx,Tx)\rangle\implies x=0
\] 
\medskip

\noindent
{\bf{9.7 The density of $\mathcal D(T^*T)$}}.
This is the subspace of $\mathcal D(T)$ where the extra
 condition for a vector $x\in\mathcal D(T)$ is that
$Tx\in\mathcal D(T^*)$.
To prove that
$\mathcal D(T^*T)$ is dense we consider some orthogonal vector $h$.
Proposition 9.6 gives some $x\in\mathcal D(T)$ such that
$h=x+T^*(Tx)$ and 
for every $g\in \mathcal D(T^*T)$ we have
\[
0=\langle x,g\rangle+\langle T^*Tx,g\rangle=
\langle x,g\rangle+\langle Tx,Tg\rangle=
\langle x,g\rangle+\langle x,T^*Tg\rangle
\tag{i}
\]
Here (i) hold for every $g\in\mathcal D(T^*T)$ and
by another application of Proposition 9.6 we  find $g$ so that
$x= g+T^*Tg$ and then (i) gives $\langle x,x\rangle =0$ so that
$x=0$.
But then we also have $h=0$ and the requested density follows.
\medskip

\noindent
{\bf{Conclusion.}}
Set $A=T^*T$.
From the above it is densely defined and
(9.6.1) entails that
the densely defined operator $E+A$ is injective. Moreover,   its range is
equal to $\mathcal H$.
Notice  that
\[
\langle x+Ax,x+Ax\rangle = c+ 
\langle x,Ax\rangle+\langle Ax,x\rangle
\]
Here
\[
\langle x,Ax\rangle=\langle x,T^*Tx\rangle=
\langle Tx,Tx\rangle= ||Tx||^2
\]
and from this
the reader can conclude that
\[
||x+Ax||^2= ||x||^2+||Ax||^2+2\cdot ||Tx||^2\quad\colon x\in \mathcal D(A)
\]
The right hand side is $\geq ||x||^2$ which
implies that
$E+A$ is invertible in Neumann's sense.

\medskip




\noindent
{\bf{9.8 The equality  $A^*=A$}}.
Recall the biduality
formula
$T= T^{**}$ and apply Proposition 9.6 starting with
$T^*$. It follows 
that
$\mathcal D(TT^*)$ also is dense and 
exactly as in (9.6.1) every $h\in\mathcal H$ has a unique
representation
\[ 
h= y+T(T^*y)
\]
\medskip

\noindent
{\bf{9.9. Exercise.}}
Verify from the above that $A$ is self-adjoint, i.e one has the equality $A=A^*$.



\bigskip




\centerline{\bf{9.10 Unbounded self-adjoint operators.}}
\bigskip

\noindent
A densely defined operator $A$ 
on the Hilbert space $\mathcal H$
for which $A=A^*$ is called self-adjoint. 


\medskip

\noindent
{\bf{9.11 Proposition}}
\emph{The spectrum of a self-adjoint operator
$A$ is contained in
the real line, and if
$\lambda$ is non-real  the resolvent
satisfies the norm inequality}
\[ 
||R_A(\lambda)||\leq \frac{1}{|\mathfrak{Im}\,\lambda|}
\]


\noindent
\emph{Proof.}
Set $\lambda=a+ib$ where $b\neq 0$.
If $x\in\mathcal D(A)$ and $y=\lambda x-Ax$ we have
\[
||y||^2=|\lambda|^2\cdot ||x||^2+||Ax||^2-2\cdot \mathfrak{Re}(\lambda)\cdot \langle x,Ax\rangle
\]

\noindent
The Cauchy-Schwarz inequality gives
\[
||y||^2\geq b^2||x||^2+ a^2||x||^2+||Ax||^2-2|a|\cdot ||Ax||\cdot ||x||
\geq
b^2||x||^2\tag{i}
\]

\noindent
This proves that  $x\to \lambda x-Ax$ is injective and
since
$A$ is closed  the range of
$\lambda\cdot E-A$ is closed.
Next, if $y$ is $\perp$ to this range we have
\[
0=\lambda \langle x,y\rangle -\langle Ax,y\rangle\quad\colon
x\in\mathcal D(A)
\]
From this we see that $y$ belongs to $\mathcal D(A^*)$ and since
$A$ is self-adjoint we get
\[
0=\lambda \langle x,y\rangle -\langle x,Ay\rangle
\]
This holds for all $x$ in the dense subspace $\mathcal D(A)$ which gives
$\lambda\cdot y=Ay$
Since $\lambda$ is non-real we have already seen that this entails that
$y=0$.
Hence the range of $\lambda\cdot E-A$ is equal to $\mathcal H$ and the inequality
(i) entails $R_A(\lambda)$
has norm
$\leq\frac{1}{|\mathfrak{Im}\lambda|}$.


\medskip

\noindent{\bf{9.12 An conjugation  formula.}}
Let $A$ be self-adjoint. For each complex number
$\lambda$  the hermitiain inner product on
$\mathcal H$ gives the equation
\[
\bar\lambda-A= (\lambda\cdot E-A)^*
\]
So when we take the complex conjugate of $\lambda$ it follows that
¤ 9.5 that 
\[
R_A(\lambda)^*= R_A(\bar\lambda)\tag{9.12.1}
\]

\noindent


\medskip

\noindent{\bf{9.13 Properties of resolvents.}}
Let $A$ be self-adjoint.
By Neumann's resolvent calculus 
the family $\{(R_A(\lambda)\}$ 
consists of pairwise commuting bounded operators
outside the spectrum of $A$. Since $\sigma(SA)$ is real 
there exist  operator-valued analytic functions $\lambda\mapsto R_A(\lambda)$Ê
in the upper- respectively the lower half-plane.
Moreover, since Neumann's  resolvents  commute, it follows
from (9.12.1) that
$R_A(\lambda)$ commutes with its adjoint. Hence
every resolvent is a bounded normal operator.


\bigskip

\noindent
{\bf{9.14 A special resolvent operator.}}
Take $\lambda=i$ and set
$R=R_A(i)$. So here
\[ 
R(iE-A)(x)= x\quad\colon\quad x\in\mathcal D(A)
\]

\medskip

\noindent
{\bf{9.15 Theorem.}}
\emph{The spectrum $\sigma(R)$ is contained in the circle}
\[
C_*=\{|\lambda+i/2|= 1/2\}
\]


\noindent
\emph{Proof.}
Since $\sigma(A)$ is confined to the real line, it follows from
¤ 0.0.5.1 that
points in $\sigma(R)$ have the form
\[
\lambda=\frac{1}{i-a}\quad\colon a\in {\bf{R}}
\]
This gives
\[
\lambda+i/2=\frac{1}{i-a}+i/2=
\frac{1}{2(i-a)}(2+i^2-ia)=
\frac{1-ia}{2i(1+ia)}
\]
and the last term has absolute value $1/2$ for every real $a$.




\bigskip



\centerline{\bf{9.B. The spectral theorem for unbounded 
self-adjoint operators.}}
\bigskip

\noindent
 The operational calculus in ¤ 8.3-8.6
applies to the bounded
normal operator $R$ in ¤ 9.14.
If $N$ is a positive integer we
set
\[
C_*(N)=\{\lambda\in C_*\,\colon\,\mathfrak {Im}(\lambda)
\leq - \frac{1}{N}\}\quad\text{and}\quad 
\Gamma_N=C_*(N)\cap \sigma(R)
\]
Let $\chi_{\Gamma_N}$ be the characterstic function of $\Gamma_N$.
Now
\[ 
g_N(\lambda)=\frac{1-i\lambda}{\lambda}\cdot \chi_{\Gamma_N}
\] 
is  Borel functionon
$\sigma(R)$ which by 
operational calculus in ¤ 8.xx 
gives a bounded and normal linear operator denoted by $G_N$.
On $\Gamma_N$ we have
 $\lambda=-i/2+\zeta$ where
$|\zeta|= 1/2$. This
gives
\[
\frac{1-i\lambda}{\lambda}=
\frac{1/2-i\zeta}{-i/2+\zeta}
=\frac{(1/2-i\zeta)(i/2+\bar\zeta)}{|\zeta-i/2|^2}
=\frac{\mathfrak{Re}\,\zeta}{|\zeta-i/2|^2}\tag{1}
\]
By  ¤ 8.x the spectrum of
$G_N$ is the range of the $g$-function on $\Gamma_N$ and  (1) 
entails that
$\sigma(G_N)$ is real. Since  $G_N$ also is normal it follows 
that it is self-adjoint.
Next, notice that
\[ 
\lambda\cdot (\frac{1-i\lambda}{\lambda}+i)=1\tag{2}
\]
holds on $\Gamma_N$.
Hence
operational calculus  gives the  equation
\[
R(G_N+i)=E(\Gamma_N)\tag{3}
\]
where $E(\Gamma_N)$
is a self-adjoint projection.
Notice also that
\[
R\cdot G_N=(E-iR)\cdot E(\Gamma_N)\tag{4}
\]
Hence (3-4) entail that
\[
E(\Gamma_N)-iRE(\Gamma_N)=(E-iR)\cdot E(\Gamma_N)\tag{5}
\]


\medskip

\noindent
Next, the equation $RA=E-iR$ gives
\[
RAE(\Gamma_N)=(E-iR)E(\Gamma_N)=R\cdot G_N\tag{*}
\]
\medskip

\noindent
{\bf{9.B.1 Exercise.}}
Conclude from the above that
\[
AE(\Gamma_N)= G_N\tag{*}
\] 
Show also that:
\[ 
\lim_{N\to\infty}\, AE(\Gamma_N)(x)= A(x)\quad
\text{for each}\quad x\in\mathcal D(A)\tag{**}
\]
\medskip

\noindent
{\bf{9.B.2 A general construction.}}
For  each bounded
Borel set $e$
 on the real line
we get a  Borel set 
$e_*\subset \sigma(R)$ 
given
by
\[ 
e_*=\sigma(R)\,\cap\, \{\frac{1}{i-a}\, a\in e\}
\]
The operational calculus  gives
the self-adjoint operator $G_e$ constructed via
$g\cdot \chi_{e_*}$.
We have also the operstor $E(e)$ given by
$ \chi_{e_*}$ and exactly as above we get
\[
AE(e)=G_e
\]
The bounded self-adjoint operators
$E(e)$ and $G_e$ commute with
$A$
and  $\sigma(G_e)$ is contained in the closure of 
the bounded Borel set $e$.
Moreover each $E(e)$ is a self-adjoint projection
and for each pair of bounded Borel sets we have
\[
E(e_1)E(e_2)= E(e_1\cap E(e_1)
\]
In particular the composed operators 
\[
E(e_1)\circ E(e_2)=0
\]
when the Borel  sets are disjoint.
\medskip


\noindent
{\bf{9.C The spectral measure.}}
Exactly as for bounded
self-adjoint operators the results above give
rise to a map from
$\mathcal H\times\mathcal H$ into the space of
Riesz measures:
\[ 
(x,y)\mapsto \mu_{x,y}
\]
For each real-valued
and bounded Borel function $\phi(t)$ on the real line with compact support
there exists a bounded self-adjoint operator
$\phi$ such that
\[
\langle \Phi(x),y\rangle=
\int\, g(t)\cdot  d\mu_{x,y}(t)
\]
All these $\Phi$ operators commute with
$A$.
If $x\in\mathcal D(A)$ and $y$ is a vector in
$\mathcal H$ one has
\[
\langle A(x),y\rangle=\lim_{M\to \infty}\,\int_{-M}^M\,
t\cdot d\mu_{x,y}(t)
\]
\medskip


\noindent
{\bf{9.D Remark.}}
To digest the results above
one should regard specific examples.
For exasmpše, consider
$A$-opertors which arise via integral 
kernels on $L^2$-spaces.
Then $\mu$-measures above 
are related  to the spectral functions
constructed in ¤ xx
by approximating of the unbounded self-adjoint operator $AS$ by 
a sequence of bounded self-adjoint operators.







 




\newpage






\centerline{\bf 10. Commutative Banch algebras}
\bigskip

\centerline{\emph{Contents}}


\bigskip

\noindent
0. Introduction

\bigskip

\noindent
0.1: Operator algebras
\bigskip

\noindent
0.2: Measure algebras 

\bigskip

\noindent
A: Neumann series and resolvents

\bigskip

\noindent
B: The Gelfand transform


\bigskip



\noindent{\bf Introduction}
Let $B$ be
a complex Banach space 
equipped with 
a commutative product whose norm
satisfies the multiplicative inequality
\[ 
||xy||\leq ||x||\cdot ||y||\quad\,\colon\, x,y\in B\tag{*}
\]
We  also assume that $B$ has a multiplicative unit element $e$
where  
$ex=xe$ hold for all $x\in B$ and   $||e||=1$. 
When this holds we refer to $B$ as a commutative Banach algebra with 
a multiplicative unit.
A  ${\bf{C}}$-linear form $\lambda$ on $B$
is  multiplicative if:
\[
\lambda(xy)=\lambda(x)\cdot \lambda(y)
\quad\text{for all pairs}\quad x,y\in B\tag{**}
\]
When  $\lambda$ satisfies (**) and is not identically zero it is clear that
$\lambda(e)=1$.

\bigskip


\noindent
{\bf{0.1 Theorem.}}
\emph{Every multiplicative functional $\lambda$
on $B$ is automatically continuous, i.e.
an element in the normed dual space $B^*$ and its norm is equal to one.}

\bigskip

\noindent
The proof in A.1 below uses
analytic function theory via  Neumann series.
The  crucial point
is that when $x\in B$ has a norm strictly less than one, then
$e-x$ is invertible in $B$ whose inverse is  the
$B$-valued power series
\[
(e-x)^{-1}= e+x+x^2+\ldots\tag{1}
\]

\medskip

\noindent
{\bf{The spectral radius formula.}}
Given  $ x\in B$ we  can take its powers and for each $n$ set
\[ 
\rho_n(x)=||x^n||^{\frac{1}{n}}
\]
In XX  we show that
these $\rho$-numbers have a limit as $n\to\infty$, i.e. there exists
\[
\rho(x)= \lim_{n\to\infty}\, \rho_n(x)
\]


\noindent
One refers to the limit $\rho(x)$ as the spectral radius of
$x$
which reflects the inequality below.
\medskip

\noindent
{\bf{0.2 Theorem.}}
\emph{For each $x\in B$ one has the equality}
\[ 
\rho(x)= \max_
{\lambda\in\mathcal M(B)}\, |\lambda(x)|
\]
\emph{where $\mathcal M(B)$ denotes the set of all multiplicative functionals on $B$.}

\medskip


\noindent
{\bf{0.3 The Gelfand transform.}}
Keeping  an element $x\in B$ fixed we get
the complex-valued function  on $\mathcal M(B)$ defined by:
\[ 
\lambda\mapsto \lambda(x)
\]
The resulting function is denoted by $\widehat x$ 
and  called the Gelfand transform.
Since
$\mathcal M(B)$ is a subset of 
the dual space
$B^*$ it is equipped with the
weak\vvv star  topology.
By
definition this is the  weakest topology
on $\mathcal M(B)$ 
for which every Gelfand transform
$\widehat x$ becomes a continuous function.
Hence there exists
an algebra homomorphism
from $B$ into the commutative algebra $C^0(\mathcal M(B))$:
\[ 
x\mapsto \widehat x\tag{*}
\]


\noindent
{\bf{0.4 Semi-simple algebras.}}
The spectral radius formula shows that $\widehat x$ is the zero function if and only if
$\rho(x)=0$. One says that the Banach algebra $B$ is
\emph{semi-simple} if
(*)  is injective. An equivalent condition is that
\[
0\neq x\implies \rho(x)>0
\]
\medskip


\noindent
{\bf{0.5 Uniform algebras.}}
If $B$ is  semi-simple the Gelfand transform
identifies $B$ with a subalgebra of $C^0(\mathcal M(B))$.
In general
this subalgebra is not closed. The reason is that
there can exist $B$-elements of norm one while
the $\rho$-numbers can be arbitrarily small.
If the equality below holds for every $x\in B$:
\[
||x||=\rho(x)= |\widehat x|_{\mathcal M(B)}\tag{*}
\]
one says that $B$ is a uniform  algebra.
\bigskip

\noindent
{\bf{Remark.}}
Multiplicative functionals
on specific Banach algebras were used  by Norbert Wiener  and Arne Beurling
where
the focus was on 
Banach algebras which arise via the 
Fourier transforms.
Later  Gelfand, Shilov and Raikow established the  abstract theory which 
has the merit that it applies to quite general situations such
as Banach algebras generated by   linear operators on a
normed space. Moreover,  
Shilov  applied results from the theory
of 
analytic functions in several complex
to construct
\emph{joint spectra} of several elements
in a commutative Banach algebra.
See [Ge-Raikov-Shilov] for  a
study of commutative Banach algebras which include
results about joint spectra.
One should also mention  the   work by J. Taylor who used
integral formulas in
several complex variables  to analyze the topology
of Gelfand spaces
which arise  from 
the Banach
algebra of  Riesz measures with total bounded variation on
the real line, and more generally on arbitrary locally compact abelian groups.

\bigskip




\centerline {\bf A. Neumann series and resolvents }
\medskip


\noindent
Let $B$ be a commutative Banach algebra with the  identity element  $e$.
The set of elements $x$ whose norms have absolute value $<1$ is denoted by
$\mathfrak B$ and  called the open unit ball in $B$.

\medskip

\noindent
{\bf A.1 Neumann series.}
Let us  prove that $e-x$ is invertible for
every $x\in\mathfrak B$. We have
$||x||=\delta<1$ and the multiplicative inequality for the norm
gives:
\[ 
||x^n||\leq ||x||^n=\delta^n\quad\colon\quad n=1,2,\ldots\tag{1}
\]

\noindent
If $N\geq 1$ we set:
\[ 
S_N(x)= e+x+\ldots+ x^N\tag{2}
\]


\noindent
For each pair $M>N$  the triangle inequality for norms gives:
\[
||S_M(x)-S_N(x)||\leq ||x^{N+1}||+\ldots+||x^M||\leq \delta^{N+1}+\ldots+\delta^M\tag{3}
\]
It follows that
\[
||S_M(x)-S_N(x)||\leq \frac{\delta^{N+1}}{1-\delta}\quad\colon M>N\geq 1
\]
Hence $\{S_N(x)\}$ is a Cauchy sequence and is therefore
convergent in the Banach space. For each $N\geq 1$ we notice that
\[
(e-x)S_N(x)= e-x^{N+1}
\]
Since $x^{N+1}\to 0$ we conclude that if $S_*(x)$ is the limit of
$\{S_N(x)\}$ then
\[ 
(e-x)S_*(x)= e\tag{*}
\]
This proves that
$e-x$ is an invertible element in
$B$ whose inverse is the convergent $B$-valued series
\[ 
S_*(x)= e+\sum_{k=1}^\infty\, x^k\tag{**}
\]

\noindent
More generally, let $0\neq x\in B$
and consider some $\lambda$ such that
$|\lambda|>||x||$. Now $\lambda^{-1}\cdot x\in \mathfrak B$
and from (**) we conclude that
$\lambda\cdot e-x=\lambda(e-\lambda^{-1}\cdot x)$ is invertible
where
\[
(\lambda\cdot e-x)^{-1}=\lambda^{-1}\cdot
\bigl[\,e+\sum_{k=1}^\infty\, \lambda^{-k}\cdot x^k\,\bigr]\tag{***}
\]

\medskip

\noindent {\bf{Exercise.}}
Deduce from (***) that one has the inequality
\[
||(\lambda\cdot e-x)^{-1}||\leq
\frac{1}{|\lambda|-||x||}
\]

\medskip






\noindent
{\bf {A.2. Local Neumann series expansions}}.
To each $x\in B$ we define the set
\[ 
\gamma(x)=\{\lambda\,\colon \,e-x\quad\text{is invertible}\}
\]
Let $\lambda_0\in\gamma(x)$
and put
\[
\delta=||(\lambda_0\cdot e-x)^{-1}||\tag{1}
\]
To each complex number $\lambda$ we set
\[ 
y(\lambda) =(\lambda_0-\lambda)\cdot (\lambda_0\cdot e-x)^{-1}\tag{2}
\]

\noindent
If $|\lambda-\lambda_0|<\delta$ we see that $y(\lambda)\in\mathfrak B$
and hence $e-y(\lambda)$ is invertible with an  inverse  given by the Neumann series:
\[
(e-y(\lambda))^{-1}=
e+\sum_{\nu=1}^\infty\, (\lambda_0-\lambda)^\nu\cdot
(\lambda_0\cdot e-x)^{-\nu}\tag{3}
\]


\noindent
Next,  for each complex number $\lambda$ we notice that
\[
(\lambda\cdot e-x)\cdot (\lambda_0\cdot e-x)^{-1}=
\]
\[
\bigl[(\lambda_0\cdot e-x)+(\lambda-\lambda_0)\cdot e\bigr]
(\lambda_0\cdot e-x)^{-1}
=e-y(\lambda)\implies 
\]
\[
(\lambda\cdot e-x)=(\lambda_0\cdot e-x)^{-1}\cdot (e-y(\lambda))\tag{4}
\]

\noindent
So if $|\lambda-\lambda_0|<\delta$ it follows that
$(\lambda\cdot e-x)$ is a product of two invertible elements and hence invertible. 
Moreover,  the series expansion from (3) gives:
\[
(\lambda\cdot e-x)^{-1}= (\lambda_0\cdot e-x)\cdot [\,
e+\sum_{\nu=1}^\infty\, (\lambda_0-\lambda)^\nu\cdot
(\lambda_0\cdot e-x)^{-\nu}\,]\tag{A.2.1}
\]

 

\medskip

\noindent
We refer to (A.2.1 ) as a local Neumann series.
The triangle inequality gives the norm inequality:
\[
||(\lambda\cdot e-x)^{-1}||\leq
||(\lambda_0\cdot e-x)||\cdot \bigl[1+\sum_{\nu=1}^\infty\,
|\lambda-\lambda_0|^\nu\cdot \delta^\nu\,\bigr]=
\]
\[
||(\lambda_0\cdot e-x)||\cdot\frac{1}{
1-|\lambda-\lambda_0|\cdot \delta}\tag{A.2.2}
\]
\medskip


\noindent
{\bf A.3. The analytic function $R_x(\lambda)$}.
From the above 
$\gamma(x)$ is an open subset of
${\bf{C}}$. Put:
\[ 
R_x(\lambda)=(\lambda\cdot e-x)^{-1}\quad\colon\, \lambda\in\gamma(x)
\]
The local Neumann series (A.2.1) 
shows that
$\lambda\mapsto R_x(\lambda)$ is a $B$-valued analytic function in
the open set $\gamma(x)$. We use this analyticity to prove:
\medskip


\noindent
{\bf A.4 Theorem.}
\emph{The set 
${\bf{C}}\setminus\gamma(x)\neq\emptyset$.}
\medskip

\noindent
\emph{Proof.}
If $\gamma(x)$ is the whole complex plane the
function $R_x(\lambda)$ is entire.
When
$\lambda|>||x||$ we have seen that 
the norm of
$R_x(\lambda)$ is $\leq \frac{1}{|\lambda|-||x||}$
which tends to zero as
$\lambda\to \infty$.
So if  $\xi$ is an element in the dual space
$B^*$
then the entire function
\[ 
\lambda\mapsto \xi(R_x(\lambda))
\]
is bounded and tends to zero and hence identically zero by
the Liouville theorem for entire functions.
This would hold  for every
$\xi\in B^*$ which clearly is impossible and hence
$\gamma(x)$ cannot be the whole complex plane.
\bigskip

\noindent
{\bf{A.5 Definition}}
\emph{The  complement ${\bf{C}}\setminus \gamma(x)$ 
is denoted by $\sigma(x)$ and called the spectrum of $x$.}


\bigskip

\noindent
{\bf{A.6 Exercise.}}
Let $\lambda_*$ be a point in $\sigma_B(x)$.
Show the following inequality for each
$\lambda\in\gamma(x)$:
\[
||(\lambda\cdot e-x)^{-1}||\geq
\frac{1}{|\lambda-\lambda_*|}
\]
The hint is to use local Neumann series from A.2.

\bigskip


\centerline {\bf B. The Gelfand transform}
\bigskip

\noindent
Put
\[
\mathfrak{r}(x)=\max_{\lambda\in\sigma(x)}\,|\lambda|\tag{*}
\]


\noindent
We refer to $\mathfrak{r}(x)$ as the spectral radius of $x$. Notice
that it gives  the radius of the smallest closed disc which contains
$\sigma(x)$.
The next result shows that
the spectral radius is found via  a limit of certain norms.


\medskip


\noindent
{\bf B.1 Theorem.}
\emph{For each $x\in B$ there exists the 
limit $\lim_{n\to\infty}\, ||x^||^{\frac{1}{n}}$
and it is equal to
$\mathfrak{r}(x)$.}
\medskip

\noindent
\emph{Proof.}
Put 
\[
\xi(n)=||x^n||^{\frac{1}{n}}\quad\, n\geq 1\,.
\]
The multiplicative inequality for the norm gives
\[
\log\,\xi(n+k)\leq
\frac{n}{n+k}\cdot \log\,\xi(n)+
\frac{k}{n+k}\cdot \log\,\xi(k)\,\quad\text{for all pairs}\,\, n,k\geq 1\,.
\]
Using this convexity it is an easy exercise to verify that there exists the
limit
\[
\lim_{n\to\infty}\, \xi(n)=\xi_*\tag{i}
\]


\noindent
There remains to prove the equality
\[ 
\xi_*=\mathfrak{r}(x)\,.\tag{ii}
\]
To prove (ii) we use
the Neumann series
expansion for $R_x(\lambda)$.
With $z=\frac{1}{\lambda}$ this gives the
$B$-valued analytic function
\[
g(z)=z\cdot e+\cdot \sum_{\nu=1}^\infty\, 
z^\nu\cdot x^\nu
\]
which  is analytic in the disc $|z|<\frac{1}{\mathfrak{rad}(x)}$.
The general result about analytic functions in
a Banach space from XX therefore implies  that when
$\epsilon>0$  there exists a constant $C_0$ such that
\[ 
||x^n||\leq C_0\cdot (\mathfrak{r}(x)+\epsilon)^n\quad\, n=1,2,\ldots\implies 
\xi(n)\leq
C_0^{\frac{1}{n}}\cdot(\mathfrak{r}(x)+\epsilon))
\]
Since
$C_0^{\frac{1}{\nu}}\to 1$ we conclude that
\[
\limsup_{n\to\infty}\,
\xi(n)\leq \mathfrak{r}(x)+\epsilon)
\]
Since $\epsilon>0$ is arbitrary and the limit  (i) exists we get
\[ 
\xi_*\leq  \mathfrak{r}(x)\tag{iii}
\]


\noindent
To prove the opposite inequality we use the definition of
the spectral radius which to begin with shows that
the $B$-valued analytic function $g(z)$ above cannot converge
in a disc of radius
$>\frac {1}{\mathfrak{r}(x)}$.
Hence Hadamard's  limit formula for  power series
with values on a Banach space  in XX gives
\[ 
\limsup_{n\to\infty}\,
\xi(n)\geq\mathfrak{r}(x)-\epsilon\quad\,\text{for every}\,\,\epsilon>0\,.
\]
Since the limit in (i)  exists we conclude that
$\xi_*\geq\mathfrak{r}(x)$ and together with (iii) above we have proved 
Theorem B.1.
\newpage


\centerline
{\bf B.2 The Gelfand space $\mathcal M_B$}.

\medskip

\noindent
Let $B$  be a commutative Banach algebra with a unit element $e$.
As a commutative ring we can refer to its \emph{maximal ideals}. Thus, 
a maximal ideal
$\mathfrak{m}$ 
is  $\neq B$ and not contained in any
strictly larger ideal.
The maximality means that
every non-zero element in the quotient ring
$\frac{B}{\mathfrak{m}}$ is invertible, i.e.
this quotient ring is a \emph{commutative field}.
Since the maximal ideal $\mathfrak{m}$
cannot contain an invertible element it follows from A.1
that
\[
x\in\mathfrak{m}\implies
||e-x||\geq 1\tag{i}
\]


\noindent
Hence the closure of $\mathfrak{m}$ 
in the Banach space is 
$\neq B$. So by  maximality 
$\mathfrak{m}$ is a \emph{closed subspace} of $B$
and hence there exists 
the Banach space
$\frac{B}{\mathfrak{m}}$.
Moreover, the  multiplication on $B$ induces a product on this quotient space and in this
way
$\frac{B}{\mathfrak{m}}$ becomes a new Banach algebra.
Since
$\mathfrak{m}$ is maximal this  Banach algebra cannot contain
any non-trivial maximal ideal which
means  that when
$\xi$ is any non-zero element in
$\frac{B}{\mathfrak{m}}$ then the principal ideal generated
by $\xi$ must be equal to
$\frac{B}{\mathfrak{m}}$. In other words, every non-zero element in
$\frac{B}{\mathfrak{m}}$ is \emph{invertible}. Using this we get
the following result.

\medskip


\noindent
{\bf B.3 Theorem.} \emph{The Banach algebra $\frac{B}{\mathfrak{m}}={\bf{C}}$, i.e. it
is reduced to the complex field.}


\medskip

\noindent
\emph{Proof.}
Let $e$ denote the identity in $\frac{B}{\mathfrak{m}}$.
Let $\xi$ be an element in $\frac{B}{\mathfrak{m}}$
and suppose that

\[
\lambda\cdot e-\xi\neq 0\quad\text{ for all}\quad \lambda\in{\bf{C}}\tag{i}
\]

\noindent
Now all non-zero elements in
$\frac{B}{\mathfrak{m}}$ are invertible so (i) would entail that
the spectrum of $\xi$ is empty which contradicts
Theorem 3.1.
We conclude that for each element $\xi\in\frac{B}{\mathfrak{m}}$ 
there exists a complex number $\lambda$ such that
$\lambda\cdot e=\xi$. It is clear that $\lambda$ is unique and
that this means precisely that
$\frac{B}{\mathfrak{m}}$ is a 1-dimensional complex vector space generated by
$e$.
\bigskip

\noindent
{\bf {B.4 The continuity of multiplicative functionals.}}
Let $\lambda\colon B\to {\bf{C}}$ be a multiplicative
functional. Since ${\bf{C}}$ is a field it follows that the
$\lambda$-kerenl is a maximal ideal in $B$ and hence closed.
Recall from XX that every linear functional on
a Banach space whose kernel is a closed subspace is automatically
in the continuous dual $B^*$.
This proves that every multiplicative functional is continuous
and as a consequence its norm in $B^*$ is equal to one.



\bigskip

\noindent
{\bf B.5 The Gelfand transform.}
Denote by $\mathcal M_B$ the set of all maximal ideals in
$B$.
For each
$\mathfrak{m}\in\mathcal  M_B$ we have proved that
$\frac{B}{\mathfrak{m}}$ is reduced to the complex field.
This enable us to construct complex-valued functions on $\mathcal M_B$. 
Namely, to each element 
$x\in B$ we get a complex-valued function on
$\mathcal  M_B$ defined by:
\medskip
\[
\hat x(\mathfrak{m})=
\,\text{the unique complex number for which}\,\, 
x-\hat x(\mathfrak{m})\cdot e\in\mathfrak{m}
\]


\noindent 
One refers to $\hat x$ as the Gelfand transform
of $x$.
Now we can    equip $\mathcal M_B$ with the \emph{weakest topology} such that the functions
$\hat x$ become continuous. 
\medskip

\noindent{\bf B.6 Exercise.}
Show that with the topology  it follows
that $\mathcal M_B$ is a compact Hausdorff space.
\bigskip



\noindent {\bf B.7 Semi-simple algebras.} 
The definition of $\sigma(x)$ shows that
this compact set is equal to the range of
$\hat x$, i.e. one has the equality
\[
\sigma(x)=\hat x(\mathcal M_B)\tag{*}
\]
Hence Theorem 4.1  gives the equality:

\[
\lim_{n\to\infty}\, ||x^n||^{\frac{1}{n}}=
\max_{\mathfrak{m}}\,\hat x(\mathfrak{m})=|\hat x|_{\mathcal M_B}\tag{**}
\]


\noindent
where the right hand side is the maximum norm of the Gelfand transform.
It may occur that the spectral radius is zero which 
by (**)  means that the Gelfand transform $\hat x$ is identically zero.
This eventual possibility leads to:
\medskip

\noindent
{\bf B.8 Definition.}
\emph{A Banach algebra $B$ is called semi-simple if
$\mathfrak{r}(x)>0$ for every non-zero element.}

\bigskip

\noindent
{\bf{B.9 Remark.}} So when $B$ is semi-simple then the Gelfand map 
$x\mapsto \widehat x$
from $B$ into $C^0(\mathcal M_B)$ is injective. In this way $B$ is
identified with a subalgebra of all continuous and complex-valued functions on the compact 
Hausdorff space $\mathcal M_B$. Moreover one has the inequality
\[
|\widehat x|_{\mathcal M_B}\leq ||x||\tag{*}
\]
It is in general strict. 
When equality holds one says that
$B$ is a \emph{uniform algebra}.
In this case the Gelfand transform identifies $B$ with a closed
subalgebra of $C^0(\mathcal M_B)$.
For an extensive study of uniform algebras
we refer to the books [Gamelin] and [Wermer].


\bigskip


\centerline{\bf{C. Examples of Banach algebras.}}



\medskip

\noindent
Below we illustrate the general theory by some examples.
Let us start with:
\medskip

\noindent
{\bf{1. Operator algebras.}}
Let $B$ be a Banach space and 
$T$ is a bounded linear operator on
$B$.
Together with the identity operator  we construct the subalgebra of $\mathcal L(B)$
expressed  by polynomials in $T$ and  take the closure of this polynomial 
$T$-algebra in the Banach space $\mathcal L(B)$.
In this way
we obtain
a Banach algebra $\mathcal L(T)$
So if $S\in\mathcal L(T)$ then $||S||$ is the operator norm taken in
$\mathcal L(B)$.
Here the Gelfand space of $\mathcal L(T)$ is identified with a compact
subset of ${\bf{C}}$ which is the spectrum of $T$
denoted by $\sigma(T)$. By definition $\sigma(T)$
consists of those complex numbers
$\lambda$ such that the operator
$\lambda\cdot E-T$ fails to be invertible in $\mathcal L(T)$.

\medskip

\noindent
{\bf{1.0 Permanent spectrum.}}
Above $\sigma(T)$ refers to the spectrum in the Banach algebra $\mathcal L(T)$.
But it can occur that $\lambda\cdot e-T$ is an invertible linear operator on
$B$ even when
$\lambda\in\sigma(T)$. To see an example we let $B=C^0(T)$
be the Banach space of continuous functions on the unit circle.
Let $T$ be the linear operator on $B$ defined by the multiplication with
$z$, i.e.
when $f(\theta)$ is some $2\pi$-periodic function we set

\[ 
T(f)(\theta)= e^{i\theta}\cdot f(e^{i\theta})
\]
If $\lambda$ belongs to the open unit disc
we notice that for any polynomial $Q(\lambda)$ one has

\[
|Q(\lambda)|\leq \max_\theta\, |Q(e^{i\theta})|=||Q(T)||
\]
It follows that the spectrum of $T$ in $\mathcal L(T)$ is identified with
the closed unit disc $\{|\lambda|\leq 1\}$.
For example, $\lambda=0$ belongs to this spectrum. On the other hand
$T$ is invertible as a linear operator on $B$ where $T^{-1}$ is
the operator defined by
\[ 
T^{-1}(f)(\theta)= e^{-i\theta}\cdot f(e^{i\theta})
\]
So in this example the spectrum of $T$ taken in the
space of all continuous linear operators on $B$ is reduced to the unit circle
$\{|\lambda|=1\}$.
\medskip

\noindent
In general, let $B$ be a commutative Banach algebra which appears as a closed 
subalgebra of a larger Banach algebra $B^*$.
If $x\in B$ we have its spectrum $\sigma_B(x)$ relative $B$ and 
the spectrum $\sigma_{B^*}(x)$ relative the larger algebra.
The following inclusion is obvious:
\[
\sigma_{B^*}(x)\subset \sigma_B(x)\tag{1}
\]
The example above shows that this inclusion in general is strict.
However, one has the opposite inclusion
\[
\partial(\sigma_B(x))\subset \sigma_{B^*}(x)\tag{2}
\]
In other words, if $\lambda$ belongs to the boundary of $\sigma_B(x)$ then
$\lambda\cdot e-x$ cannot be inverted in any larger Banach algebra. It means that
$\lambda$ is a permanent spectral value for $x$.
The proof of (2) is given in XX using  Neumann series.



\bigskip






\noindent
{\bf{2.  Finitely generated Banach algebras.}}
A Banach algebra $B$ is finitely generated if there exists a finite subset
$x_1,\ldots,x_k$ such that every $B$-element can be approximated in the norm
by polynomials of this $k$-tuple.
Since every multiplicative functional 
$\lambda$ is continuous it is determined by its values on
$x_1,\ldots,x_k$. It means that we have an injective map from
$\mathcal M(B)$ into the $k$-dimensional complex vector space
${\bf{C}}^k$
defined by
\[
\lambda\mapsto (\lambda(x_1),\ldots\lambda(x_k))\tag{1}
\]
Since the Gelfand topology is compact
the image under (1) yields a compact
subset of ${\bf{C}}^k$  denoted by $\sigma(x_\bullet)$.
This construction was introduced by Shilov and one refers to
$\sigma(x_\bullet)$ as the joint spectrum of the $k$-tuple
$\{x_\nu\}$.
It turns out that such joint spectra are 
special. More precisely, they are polynomially convex subsets of
${\bf{C}}^k$.
Namely, let $z_1,\ldots,z_k$ be the complex coordinates
in
${\bf{C}}^k$. If $z_*$ is a point outside
$\sigma(x_\bullet)$ there exists for every $\epsilon>0$ some polynomial 
$Q[z_1,\ldots,z_k]$ such that $Q(z_*)=1$ while the maximum norm of
$Q$ over $\sigma(x_\bullet)$ is $\epsilon$.
To see this one argues by a contradiction, i.e. if
this fails there exists a constant $M$ such that
\[
|Q(z^*)|\leq M\cdot|Q|_{\sigma(x_\bullet)}
\]
for all polynomials $Q$.
Then the reader may verify that we obtain a multiplicative
functional $\lambda^*$ on $B$ for which
\[
\lambda^*(x_\nu)=z^*_\nu\quad\colon\, 1\leq\nu\leq k
\]
By definition this would entail that
$z^*\in\sigma(x_\bullet)$.
\medskip

\noindent
{\bf{Remark.}}
Above we encounter a topic in several complex variables.
In contrast to the case $n=1$
it is not
easy to describe conditions on a compact subset
$K$ of ${\bf{C}}^k$ in order that it is polynomially convex,
which by definition means that whenever $z^*$ is a point in
${\bf{C}}^k$ such that
\[ 
|Q(z^*)|\leq |Q|_K
\] 
then $z^*\in K$.

\bigskip


\centerline {\bf{3. Examples from harmonic analysis.}}
\medskip

\noindent
{\bf{The measure algebra $M({\bf{R}}^n)$}}.
The elements are Riesz measures in ${\bf{R}}^n$ of finite total mass and the product defined by
convolution. The identity is the Dirac measure at the origin.
Set $B= M({\bf{R}}^n)$. The Fourier transform identifies the
$n$-dimensional $\xi$-space with a subset of
$\mathcal M(B)$. In fact, this follows since
the Fourier transform of a convolution
$\mu*\nu$ is the product $\widehat\mu(\xi)\cdot \widehat\nu(\xi)$.
In this way we have an embedding of ${\bf{R}}^n_\xi$ into $\mathcal M(B)$.
However, the resulting subset is not dense in
$\mathcal M(B)$.
It means that there exist Riesz measures $\mu$ such that 
$|\widehat\mu(\xi)|\geq \delta >0$ 
hold for all $\xi$, and yet $\mu$ is not invertible in $B$.
An example of such a measure was
discovered by Wiener and Pitt and one therefore refers to
the \emph{Wiener-Pitt phenomenon} in $B$.
Further examples occur in [Gelfand et. all].
The idea is to construct Riesz measurs $\mu$ with independent powers, i.e. measures $\mu$ such that the norm of a $\mu$-polynomial
\[ 
c_0\cdot \delta_0+c_1\cdot \mu+\ldots+c_k\cdot \mu^ k
\] 
is roughly equal
to $\sum\,|c_k|$ while $||\mu||=1$.
In this way one can construct measurs $\mu$ for which
the spectrum in $B$ is the unit disc while the range of the
Fourier transform is a real interval.
Studies of $\mathcal M(B)$
occur in work by J. Taylor who established
topological properties of
$\mathcal M(B)$. The proofs rely upon several complex variables and
we shall not try to expose material from Taylor's deep work.
Let us only mention one result from Taylor's work
in the case $n=1$.
Denote by $i(B)$ the multiplicative group of invertible measures in 
$B$ where $B=\mathcal M(B)$ on the real line.
If $\nu\in B$
we  construct the exponential sum
\[
 e^\nu=\delta_0+\sum_{k=1}^\infty\, \frac{\nu^k}{k !}
\]
In this way $e^B$ appears as a subgroup of $i(B)$.
Taylor proved that the quotient group
\[
\frac{i(B)}{e^B}\simeq {\bf{Z}}
\] 
where
the right hand side is the additive group of integers.
More precisely one finds an explicit 
invertible measure $\mu_*$ which does not belong to $e^B$ and for 
any $\mu\in i(B)$ there exists a unique integer $m$ and some
$\nu\in B$ such that

\[ 
\mu=e^\nu*\mu_*^k\tag{*}
\]
The measure $\mu_*$ is given by
\[ 
\mu_*=\delta_0+f
\] 

CONTINUE...


\medskip

\noindent{\bf{3.1 Wiener algebras.}}
We can ask for  subalgebras of $M({\bf{R}}^n)$ where the Wiener-Pitt phenomenon does not occur, i.e. subalgebras $B$ where the Fourier transform gives a dense embedding of
${\bf{R}}^n_\xi$ into $\mathcal M(B)$.
A first example goes as follows:
Let $n\geq 1$ and consider the Banach space
$L^1({\bf{R}}^n)$ where convolutions of $L^1$-functions
is defined.
Adding the unit point mass $\delta_0$ at 
the origin we get the commutative Banach algebra 
\[
B={\bf{C}}\cdot \delta_0+L^1({\bf{R}}^n)
\]
Here the Fourier transform  describes $\mathcal M(B)$.
More precisely, if $\lambda$ is a multiplicative functional on $B$ whose
restriction to  $L^1({\bf{R}}^n)$ is not identically zero, then
one proves that  there exists
a unique point $\xi\in {\bf{R}}^n$ such that
\[
\lambda(f)=\widehat f(\xi)\quad\colon\quad 
f\in L^1({\bf{R}}^n)
\]
In this way the $n$-dimensional $\xi$-space is identified with a subset of
$\mathcal M(B)$. An extra point $\lambda^*$ appears in
$\mathcal M(B)$ where $\lambda^*(\delta_0)=1$ while its restriction to
$L^1({\bf{R}}^n)$ vanishes.
Hence
the compact Gelfand space $\mathcal M(B)$ 
corresponds to the  one-point compactification of
the $\xi$-space. Here the continuity of Fourier transforms of $L^1$-functions 
correspond to the  fact that their Gelfand transforms are continuous.
An important consequence
of this is that when
$f(x)\in L^1({\bf{R}}^n)$ is such that $\widehat f(\xi)\neq 1$ for every
$\xi$, then the $B$-element $\delta_0-f$ is invertible,  i.e. there
exists another $L^1$-function $g$ such that
\[
\delta_0=(\delta_0-f)*(\delta_0+g)\implies f=g-f*g
\]
The equality
\[ 
\mathcal M(B)= {\bf{R}}^n_\xi\cup\{\lambda^*\}\tag{*}
\]
was originally put forward by Wiener prior to the general theory about Banach algebras.
Another  Banach algebra 
is $M_d({\bf{R})^n}$
whose elements are discrete measures with a finite total variation.
Thus, the elements are measures

\[ 
\mu=\sum\, c_\nu\cdot \delta(p_\nu)
\]


\noindent
where $\{p_\nu\}$ is a sequence of points in ${\bf{R}}^n$
and
$\{c_\nu\}$ a sequence of complex numbers such that
$\sum\,|c_\nu|<\infty$.
Here the Gelfand space is more involved. To begin with
the Fourier transform identifies ${\bf{R}}^n_\xi$ with a subset of
$\mathcal M(B)$.
But the compact space $\mathcal M(B)$ is considerably and given
by a compact abelian group which is  called the Bohr group after
Harald Bohr whose studies of
almost periodic functions led to
the description of $\mathcal M(B)$. However one has the following result:


\medskip

\noindent
{\bf{3.2 Bohr's Theorem.}}
\emph{The subset ${\bf{R}}^n_\xi$ is dense in $\mathcal M(B)$.}
\medskip

\noindent
{\bf{Remark.}}
See XX for an account about almost periodic functions 
which proves Bohr's theorem
in the case $n=1$.

\medskip


\noindent
{\bf{3.3 Beurling's density theorem}}.
Consider  the Banach algebra $B$ generated
by
$M_d({\bf{R}}^n)$ and $L^1({\bf{R}}^n)$.
So its elements are measures of the form
\[
\mu=\mu_d+f
\] 
where $\mu_d$ is discrete and $f$ is absolutely continuous.
Here 
the Fourier transform identifies ${\bf{R}}^n_\xi$ with an open subset
of $\mathcal M(B)$. More precisely, a multiplicative
functional $\lambda$ on $B$ belongs to the open set
${\bf{R}}^n_\xi$ if and only if $\lambda(f)\neq 0$
for at least some $f\in L^1({\bf{R}}$.
The remaining part
$\mathcal M(B)\setminus{\bf{R}}^n_\xi$  is equal to the Bohr group above..
It means
that when
$\lambda$ is an arbitrary multiplicative functional on
$B$ then there exists $\lambda_*\in\mathcal M(B)$ such that
$\lambda_*$ vanishes on $L^1({\bf{R}}^n$ while $\lambda_*(\mu)=\lambda(\mu)$
for every discrete measure.
The density of ${\bf{R}}\uuu\xi^n$
follows via Bohr's theorem and the fact that
Fourier transforms of $L^1$\vvv functions
tend to zero as $|\xi|\to +\infty$.






\medskip

\noindent
{\bf{3.4  Varopoulos'  density theorem}}.
For each  linear subspace $\Pi$ of
arbitrary dimension $1\leq d\leq n$ we get the space
$L^1(\Pi)$ of absolutely continuous measures supported by
$\Pi$ and of finite total mass.
Thus, we identify $L^1(\Pi)$ with a subspace of $M({\bf{R}}^n)$.
We get the closed subalgebra of 
 $M({\bf{R}}^n)$  generated by
all these $L^1$-spaces and the discrete measures. It is denoted by
$\mathcal V({\bf{R}}^n)$ and  called the Varopoulos 
measure algebra in ${\bf{R}}^n$.
In [Var] it is proved that
the Fourier
transform identifies
${\bf{R}}^n_\xi$ with a dense subset of
$\mathcal M( \mathcal V({\bf{R}}^n))$.
\medskip

\noindent
{\bf{3.5 The extended $\mathcal V$-algebra.}}
In ${\bf{R}}^n$
we can consider  semi-analytic strata which consist of locally closed
real-analytic submanifolds $S$ whose closure $\bar S$ is compact and
the relative boundary $\partial S=\bar S\setminus S$
is equal to the zero set of a real analytic function.
On each such stratum we  construct measures which are absolutely continuous with
respect to the area measure of $S$.
Here the dimension of $S$ is between 1 and $n-1$ and now
each  measure in  $L^1(S)$ is 
identified with a Riesz measure in
${\bf{R}}^n$ which happens to be supported by $S$,
One can easily prove
that every $\mu\in L^1(S)$ has a power which 
belongs to the
Varopolulos algebra and from  this deduce
that if $\mathcal V^*$ 
is the closed subalgebra of $M({\bf{R}}^n)$
generated by the family $\{L^1(S)\}$ and
$V({\bf{R}}^n))$ then one gets a new
Wiener algebra.
\medskip

\noindent{\bf{3.6 Olofsson's example.}}
Above real analytic strata were used to obtain $\mathcal V^*$. That real-analyticity
is essential was demonstrated  by Olofsson in [Olof]. For example, 
he found a $C^\infty$-function $\phi(x)$ on $[0,1]$ such that if
$\mu$ is the measure in ${\bf{R}}^2$ defined by
\[ 
\mu(f)=\int_0^1\, f(x,\phi(x))\cdot dx
\] 
then $\mu$ has independent powers and it cannot belong  
to any Wiener subalgebra of $M({\bf{R}}^n)$.
Actually [Olofson] constructs further examples as above
on curves defined by
$C^\infty$-functions outside the
Carleman
class of quasi-anaytic functions.













\newpage


\centerline{\bf{11.  Miscellaneous results.}}

\bigskip


\noindent
{\bf{Introduction.}}
The subsequent sections treat  topics related  to the material in
¤ 8 and 9.

\bigskip




\centerline{\bf{11.1. Symmetric operators.}}



\bigskip

\noindent
A densely defined and closed operator
$T$ on a Hilbert space $\mathcal H$
is  symmetric if
\[
\langle Tx,y\rangle=
\langle x,Ty\rangle\quad\text{hold for all pairs }\quad x,y\in\mathcal D(T)\tag{*}
\]


\noindent
The symmetry means  that
the adjoint 
$T^*$   extends $T$, i.e. 
\[
\Gamma(T)\subset \Gamma(T^*)
\]
Recall that adjoints always are closed operators.
Hence $\Gamma(T^*)$
is a closed subspace of $\mathcal H\times\mathcal H$ and  becomes
a Hilbert space equipped with
the inner product
\[
\{x,y\}=
\langle x,y\rangle+
\langle T^*x,T^*y\rangle
\]
Moreover, since
$T$ also is closed. it follows that
$\Gamma(T)$ appears as a closed subspace of this Hilbert space.
Consider 
the  eigenspaces:
\[
\mathcal D_+=\{ x\in\mathcal D(T^*)\quad\colon T^*(x)=ix\}
\quad\text{and}\quad 
\mathcal D_-=\{ x\in\mathcal D(T^*)\quad\colon T^*(x)=-ix\}
\]


\medskip

\noindent {\bf{11.1.1 Proposition.}}
\emph{The following  orthogonal decomposition exists in
the Hilbert space $\Gamma(T^*)$:}
\[
\Gamma(T^*)=\Gamma(T)\oplus \mathcal D_+ \oplus\mathcal D_-
\tag{*}\]


\noindent
\emph{Proof.}
The verification that the three subspaces are pairwise orthogonal is
left to the reader.
To show  that the direct sum above
is equal to
$\Gamma(T^*)$ we use duality and  there remains only  to
prove that
\[ 
\Gamma(T)^\perp=
\mathcal D_+\oplus \mathcal D_-\tag{1}
\]

\noindent
To show (1) we pick a vector 
$y\in \Gamma(T)^\perp$. Here $(y,T^*y)\in\Gamma(T^*)$
and the definition of orthogonal complements gives:
\[
\langle x,y\rangle+ \langle Tx,T^*y\rangle=0
\quad\colon\quad x\in\mathcal D(T)
\]
From this we see that $T^*y\in\mathcal D(T^*)$ and obtain
\[
\langle x,y\rangle+ \langle x,T^*T^*y\rangle=0
\]
The density of $\mathcal D(T)$ entails that
\[ 
0=y+T^*T^*y=(T^*+iE)(T^*-iE)(y)\implies
\]
\[
\xi=T^*y-iy\in \mathcal D_-\quad\text{and}\quad
\eta=T^*y+iy\in \mathcal D_+\implies
\]
\[ 
y=\frac{1}{2i}(\eta-\xi)
\in \mathcal D_-\oplus \mathcal D_+
\]
which proves (1).


\medskip

\noindent
{\bf{11.1.2 The case 
$\dim(\mathcal D_+)= \dim(\mathcal D_-)$.}}
Suppose they   are finite dimensional
with equal  dimension $n\geq 1$. Then
self-adjoint extensions of $T$  are found as follows:
Let   $e_1,\ldots,e_n$ be an orthonormal  basis in $\mathcal D_+$ and
$f_1,\ldots,f_n$ a similar basis in $\mathcal D_-$.
For each $n$-tuple $e^{i\theta_1},\ldots, e^{i\theta_n}$
of complex numbers with absolute value one
we have  the subspace of $\mathcal H$
generated by $\mathcal D(T)$ and
the vectors
\[ 
\xi_k= e_k+ e^{i\theta_k}\cdot f_k\quad\colon\quad 1\leq k\leq n
\]

\medskip

\noindent
On this  subspace we define a linear operator $A_\theta $ where
$A_\theta =T$ on $\mathcal D(T)$
while
\[ 
A_\theta (\xi_k)=ie_k-i e^{i\theta_k}\cdot f_k
\]

\medskip

\noindent
{\bf{11.1.3 Exercise.}}
Verify 
that
$A_\theta $ is self-adjoint and  prove the converse, i.e. if
$A$ is an arbitrary self-adjoint operator such that
\[
\Gamma(T)\subset
\Gamma(A)\subset\Gamma(T^*)
\]
then there exists a unique $n$-tuple $\{e^{i\theta_\nu}\}$
such that
\[
A=A_\theta
\]







\bigskip
\noindent{\bf{11.1.4  Example.}}
Let $\mathcal H$ be the Hilbert space
$L^2[0,1]$ of  square-integrable functions 
on the unit interval $[0,1]$ with  the coordinate $t$.
A dense subspace $\mathcal H_*$ consists of  functions
$f(t)\in C^1[0,1]$
such that $f(0)=f(1)=0$.  On $\mathcal H_*$
we define the operator 
$T$ by
\[ 
T(f)=if'(t)
\]
A partial integration gives
\[ 
\langle T (f),g\rangle=
 i\int_0^1\, f'(t)\cdot\bar g(t)\cdot dt=\int_0^1\, \bar g'(t)\cdot f(t)dt=
 \langle f,T(g)\rangle
\] 
Hence $T$ is symmetric.
Next, an $L^2$-function $h$  belongs to $\mathcal D(T^*)$ if and only if there exists a constant $C(h)$ such that
\[
\bigl|\int_0^1\, if'(t)\cdot\bar h(t)dt\bigr|\leq
C(h)\cdot ||f||_2\quad\colon f\in \mathcal H_*
\] 
This means that
$\mathcal D(T^*)$ consists of all $L^2$-functions $h$ such that
the distribution derivative $\frac{dh}{dt}$ again belongs to $L^2$.
\medskip

\noindent
{\bf{Exercise.}}
Show that 
\[ 
\mathfrak{D}_+=\{h\in L^2\quad\colon\frac{dh}{dt}=ih\}
\] 
is a 1-dimensional vector space
generated by the $L^2$-function $e^{ix}$.
Similarly, $\mathcal D_-$ is 1-dimensional and generated
by $e^{-ix}$.
\medskip

\noindent
\emph {Self-adjoint extensions of $T$}.
For each  complex number
$e^{i\theta}$  we get the linear  space  
$\mathcal D_\theta$
of functions
$f(t)\in\mathcal D(T^*)$ such that
\[ 
f(1)= e^{i\theta}f(0)
\]


\noindent
{\bf{Exercise.}}
Verify
that one gets a  self-adjoint operator $T_\theta$
which extends $T$ where 
is   $\mathcal D(T_\theta)= \mathcal D_\theta$.
Conversely, show every  self-adjoint extension of
$T$ is equal to $T_\theta$
for some
$\theta$. Hence the family $\{T_\theta\}$
give all self-adjoint extensions of $T$ with their  graphs 
contained in  $\Gamma(T^*)$.


\bigskip

 
\centerline {\bf{11.2 Semi-bounded symmetric operators.}}
\bigskip

\noindent 
Let $T$ be  closed, densely defined and symmetric.
It is said to be bounded
below 
if there exists some positive constant $k$ such that
\[ 
\langle Tx,x\rangle \geq k\cdot ||x||^2\quad\colon\quad x\in\mathcal D(T)\tag{*}
\]

\medskip

\noindent
On $\mathcal D(T)$ we have the Hermitian bilinear form:
\[
\{x,y\}= \langle Tx,y\rangle \quad\text{where (*) entails that}\quad 
\{x,x\}\geq k\cdot ||x||^2\tag{1}
\]
In particular a Cauchy sequence with respect to this inner product is a
Caichy sequence in the given Hilbert space
$\mathcal H$. So if $\mathcal D_*$ is the completion of
$\mathcal D(T)$ with respect to the inner product above, then
it appears as a subspace of
$\mathcal H$.
Put
\[ 
\mathcal D_0=\mathcal D(T^*)\,\cap\, \mathcal D_*
\]

\noindent
{\bf{11.2.1 Proposition}}. \emph{One has the equality}
\[ 
T^*(\mathcal D_0)=\mathcal H\tag{*}
\]
\emph{Proof.}
A  vector $x\in\mathcal H$  gives
a  linear functional on $\mathcal D_*$ 
defined by
\[ 
y\mapsto \langle y,x\rangle
\]
We have
\[
|\langle y,x\rangle|\leq
||x|\cdot ||y||\leq ||x|||\cdot \frac{1}{\sqrt{k}}\cdot\sqrt{\{y,y\}}\tag{i}
\]
where we used (1) above.
The Hilbert space
$\mathcal D_*$
is self-dual. This   gives a  vector
$z\in\mathcal D_*$ such that
\[
\langle y,x\rangle=\{y,z\}=\langle Ty,z\rangle\tag{iii}
\]
Since $\mathcal D(T)\subset \mathcal D_*$
we have (iii)
for every vector 
$y\in\mathcal D(T)$, and  the construction of $T^*$
entails that  
$z\in  \mathcal D(T^*)$ so that  (iii) gives
\[
\langle y,x\rangle=\langle y,T^*(z)\rangle\tag{iv}
\]
The density of $\mathcal D_*$ in $\mathcal H$
implies that 
$x=T^*(z)$ and since $x\in\mathcal H$ was arbitrary we get
(*) in the proposition.
\bigskip


\noindent
{\bf{11.2.2 A self-adjoint extension.}}
Let $T_1$ be the restriction of $T^*$ to
$\mathcal D_0$. We leqve it to the reader to check that
$T_1$ is symmetric and 
has a closed graph.
Moroever, since $\mathcal D(T)\subset \mathcal D_0$ and 
$T^*$ is an extension of 
$T$ we have
\[ 
\Gamma(T)\subset \Gamma(T_1)
\]
Next, Proposition 11.2.1 gives
\[
 T_1(\mathcal D(T_1)= \mathcal H
\]
 i.e. the $T_1$Êis surjective.
But then $T_1$ is self-adjoint by   the general result below.

\bigskip
 
\noindent{\bf{11.2.3 Theorem }}.
\emph{Let $S$
be a  densely defined, closed and symmetric operator such that}
\[
S(\mathcal D(S))=\mathcal H\tag{*}
\]
\emph{Then $S$ is self-adjoint.}
\medskip



\noindent
\emph{Proof.}
Let $S^*$ be the adjoint of $S$.
When 
$y\in\mathcal D(S^*)$ we have by definition
\[
\langle Sx,y\rangle =\langle x,S^*y\rangle\quad\colon\quad x\in\mathcal D(S)
\]
If $S^*y=0$ this entails that
$\langle Sx,y\rangle=0$ for all $x\in\mathcal D(S)$ so 
the assumption that
$S(\mathcal D(S))=\mathcal H$ 
gives $y=0$ and hence  $S^*$ is injective.
Finally, if $x\in\mathcal D(S^*)$
the hypothesis (*) gives $\xi\in\mathcal D(S)$ such that
\[
S(\xi) =S^*(x)\tag{i}
\] 
Since $S$ is symmetric,
$S^*$ extends $S$ so that 
(i) gives  $S^*(x-\xi)=0$. Since we already proved that
$S^*$ is injective  we have
$x=\xi$. This proves that 
$\mathcal D(S)=\mathcal D(S^*)$ which means that   $S$ is self-adjoint.
\bigskip









\bigskip







\centerline{\bf{11.3 Contractions}}
\bigskip


\noindent
A linear operator $A$ on the Hilbert space $\mathcal H$ is  a contraction if
its operator norm is $\leq 1$, i.e.
\[
 ||Ax||\leq ||x||\quad\colon\quad x\in\mathcal H\tag{1}
\] 
Let $E$ be the identity operator on $\mathcal H$.
Now $E-A^*A$ is a bounded self-adjoint operator and  (1) gives:
\[
\langle x-A^*Ax,x\rangle=||x||^2-||Ax||^2\geq 0
\]
From the result in ¤ 8.xx it follows that
this  non-negative self-adjoint operator has a square root:
\[ 
B_1=\sqrt{E-A^*A}
\]
Next,  the operator norms of $A$ and  $A^*$ are equal so
$A^*$ is  also a  contraction and the equation
$A^{**}=A$ gives the
self-adjoint operator
\[
B_2=\sqrt{E-AA^*}
\]
Since  $AA^*=A^*A$ is not assumed
the  self-adjoint operators
$B_1,B_2$ need not be equal.
However, the following hold:

\medskip

\noindent
{\bf{11.3.1 Propostion.}}
\emph{One has the equations}
\[ 
AB_1=B_2A\quad\text{and}\quad A^*B_2= B_1A^*
\]



\noindent
\emph{Proof.}
If $n$ is a positive integer we notice that
\[
A(A^*A)^n=(AA^*)^nA\tag{i}
\]
Now $A^*A$ is a self-adjoint operator whose compact spectrum is confined to
the closed unit interval $[0,1]$.
If $f\in C^0[0,1]$
is a real-valued continuous function it can be approximated uniformly
by a sequence of polynomials $\{p_n\}$
and the operational calculus from ¤ XX yields an operator
$f(A^*A)$ where
\[
\lim_{n\to\infty}\, ||p_n(A^*A)-f(A^*A)||=0
\]
Since the spectrum of $AA^*$ also is confined to $[0,1]$,
the same polynomial sequence
$\{p_n\}$ gives 
an operator $f(AA^*)$ where
\[
\lim\, ||p_n(AA^*)-f(AA^*)||=0
\]
Now (i) and the two limit formulas above give:
\[
A\circ f(A^*A)= f(AA^*)\circ A\tag{ii}
\]
In particular we can take 
$f(t)= \sqrt{1-t}$
and  Proposition 11.3.1 follows.
\bigskip

\noindent{\bf{11.3.2 The unitary operator $U_A$}}.
On the Hilbert space $\mathcal H\times \mathcal H$
we define a linear operator $U_A$ represented by the block matrix
\[
U_A=
\begin{pmatrix} A& B_2\\
B_1&-A^*
\end{pmatrix}\tag{*}
\]


\noindent
{\bf{11.3.3 Proposition.}}
\emph{$U_A$ is a unitary operator on
 $\mathcal H\times \mathcal H$}.
 
 \medskip
 
 \noindent
 \emph{Proof.}
 For a pair of vectors $x,y$ in $\mathcal H$
 we must prove the equality
\[
|| U_A(x\oplus y)||^2=||x||^2+||y||^2\tag{i}
\]
To get (i)  we notice that for every vector $h\in\mathcal H$ 
the self-adjointness of $B_1$ gives
\[
||B_1h||^2=\langle B_1h,B_1h\rangle=
\langle B_1^2h,h\rangle=\langle h-A^*Ah,h\rangle=
||h||^2-||Ah||^2\tag{ii}
\]
where  the last equality holds since we have
$\langle A^*Ah,h\rangle =\langle Ah,A^{**}h\rangle =||Ah||^2$
and the biduality formula $A=A^{**}$.
In the same way one has:
\[
||B_2h||^2=||h||^2-||A^*h||^2\tag{iii}
\]


\noindent
Next, by the construction of $U_A$ the left hand side in (i) becomes
\[
||Ax+B_2y||^2+||B_1x-A^*y||^2\tag{iv}
\]
Using (iii) we have
\[
||Ax+B_2y||^2=||Ax||^2+||y||^2-||A^*y||^2+
\langle Ax,B_2y\rangle+ \langle B_2 y,Ax\rangle
\]
Similarly,  (ii) gives
\[
||B_1x-A^*y||^2=||x||^2-||Ax||^2+||A^*y||^2-
\langle B_1x,A^*y\rangle- \langle A^*y,B_ x\rangle
\]
Adding these two equations  we 
conclude that (i) follows from the equality
\[
\langle Ax,B_2y\rangle+ 
\langle B_2 y,Ax\rangle=
\langle B_1x,A^*y\rangle+ \langle A^*y,B_ x\rangle\tag{v}
\]
To get (v) we use Proposition 11.5.1 which  gives
\[
\langle Ax,B_2y\rangle=
\langle x,A^*B_2y\rangle=
\langle x,B_1A^*y\rangle=
\langle B_1x,A^*y\rangle
\]
where the last equality used that $B_1$ is self-adjoint. In the same way one verifies that
\[
\langle B_2 y,Ax\rangle=
 \langle A^*y,B_ x\rangle
\]
and (v) follows.

\newpage



\centerline{\bf{11.3.4 The Nagy-Szegš theorem.}}
\bigskip


\noindent
The constructions above were applied 
by 
Nagy and Szegš to give:
\medskip

\noindent
{\bf{11.3.5 Theorem}}
\emph{For every bounded linear operator $A$ on a Hilbert space
$\mathcal H$ there exists a Hilbert space
$\mathcal H^*$ which contains $\mathcal H$ and a unitary operator $U_A$
on $\mathcal H^*$ such that}
\[
A^n=\mathcal P\cdot U_A^n\quad\colon\quad n=1,2,\ldots
\]
\emph{where $\mathcal P\colon\mathcal H^* \to \mathcal H$
is the orthogonal  projection.}
\medskip


\noindent
\emph{Proof.}
On the product  $\mathcal H_1=\mathcal H\times\mathcal H$ we have the unitary
operator $U_A$ from (*) in 11.3.2. Let
$\mathcal P(x,y)= x$ be the projection onto the first
factor.
Then  (*) in (11.3.2) gives 
$A=\mathcal PU_A$ and  
the constructions from the proof of Propostion 11.3.4
imply that
$A^n=\mathcal P\cdot U^n$ hold for every $n\geq 1$ which finishes the proof.
\bigskip

\noindent
\emph {11.3.6 A  norm inequality.}
The Nagy-Szegš result has
an interesting consequence. 
Let $A$  be a contraction. If
$p(z)=
c_0+c_1<+\ldots+c_nz^n$ is an arbitrary polynomial with
complex coefficients
we get the 
operator $p(A)=\sum\,c_\nu A^\nu$ and 
with these notations one has:

\medskip

\noindent
{\bf{11.3.7 Theorem}}
\emph{For every pair $A,p(z)$ as above one has}
\[
||p(A)||\leq \max_{z\in D}\, |p(z)|
\] 
\emph{where the the maximum in the right hand side is taken on the unit disc.}
\medskip

\noindent
\emph{Proof.} Theorem 11.3.5  gives $p(A)= \mathcal P\cdot p(U_A)$.
Since the orthogonal $\mathcal P$-projection is norm decreasing we get
\[
||p(A)(\xi)||^2\leq ||p(U_A)(\xi,0)||^2
\]
Let $\xi$ be a unit vector such that
$||p(A)(\xi)||= ||p(A)||$.
The operational calculus in ¤ 7 XX  applied to the unitary operator
$U_A$  yields a
probablity measure $\mu_\xi$ on
the unit circle such that
\[
 ||p(U_A)(\xi,0)||^2=
 \int_0^{2\pi}\, |p(e^{i\theta})|^2\cdot d\mu_\xi(\theta)
 \]
The right hand side is majorized by $|p|_D^2$ and Theorem 11.3.7 follows.

\bigskip

\noindent
{\bf{11.3.8 An application.}}
Let $A(D)$ be the disc algebra. Since each $f\in A(D)$ can be 
uniformly approximated by analytic 
polynomials, Theorem 11.3.7 entails that if $A$ is a contraction
then each $f\in A(D)$
gives a 
bounded linear operator $f(A)$, i.e. we have a map from
$A(D)$ into the space of bounded linear operators on
$\mathcal H$.


\newpage

\centerline
{\bf{11.4 A product formula}}
\bigskip


\noindent
The product formula for matrices in ¤ X  asserts the following.
Let $N\geq 2$  and $T$  is some $N\times N$-matrix whose
elements are complex numbers
which as usual is regarded as a linear operator on
the Hermitian space ${\bf{C}}^N$.
Recall that there 
exists the 
self-adjoint matrix $\sqrt{T^*T}$ whose eigenvalues are non-negative.
Notice that for every vector $x$ one has 
\[
||T^*T(x)||^||Tx||^2\implies ||\sqrt{T^*T}(x)||= ||Tx||\tag{i}
\] 
Since
$\sqrt{T^*T}$ is self-adjoint
we have an orthogonal decomposition 
\[
\sqrt{T^*T}({\bf{C}}^N)\oplus
\text{Ker}(\sqrt{T^*T})= {\bf{C}}^N\tag{ii}
\]
where the self-adjointness gives the equality
\[
\text{Ker}(\sqrt{T^*T})=\sqrt{T^*T}({\bf{C}}^N)^\perp
\]
\medskip

\noindent
{\bf{The partial isometry operator.}}
Show that 
there exists a unique linear operator $P$ such that
\[ 
T= P\cdot \sqrt{T^*T}\tag{*}
\]
where the $P$-kernel is
the orthogonal complement of the range of  $\sqrt{T^*T}$.
Moreover, from  (i) it follows that
\[
||P(y)||=||y||
\] 
for each vector in the range of
$\sqrt{T^*T}$.
One  refers to $P$ as a partial isometry attached to $T$.
\bigskip

\noindent
Hilbert's the spectral theorem for bounded
and self-adjoint operators
on a Hilbert space $\mathcal H$ gives a similar equation as in (*) above
using
the non-negative and self-adjoint
operator $\sqrt{T^*T}$. More generally,
let $T$ be densely defined and closed.
From  ¤ XX  there exists the
densely defined self-adjoint operator $T^*T$
and we can also take its square root.

\medskip

\noindent
{\bf{11.4.1 Theorem.}}
\emph{There exists  a bounded partial isometry
$P$ such that}
\[ 
T= P\cdot \sqrt{T^*T}
\]



\bigskip


\noindent
{\bf{11.4.2 The construction of $P$.}}
Since $T$ has closed graph we have the Hilbert space
$\Gamma(T)$.
For each $x\in\mathcal D(T)$ we get the vector
$x_*=(x,Tx)$ in $\Gamma(T)$.
Now
\[
(x_*.y_*)\mapsto \langle x,y\rangle
\] 
is a bounded Hermitiain bi-linear form on
the Hilbert space $\Gamma(T)$.
The self-duality of Hilbert spaces
gives  bounded and self-adjoint operator
$A$ on
$\Gamma(T)$ such that
\[
\langle x,y\rangle=\{ Ax_*,y_*\}
\]
where the right hand side is the inner product between vectors in
$\Gamma(T)$.
Let 
\[ 
j\colon (x,Tx)\mapsto x
\]
be  the projection from
$\Gamma(T)$ onto $\mathcal D(T)$ and for each
$x\in\mathcal D(T)$ we put
\[ 
Bx= j(Ax_*)
\]
Then $B$ is a linear operator from
$\mathcal D(T)$ into itself where
\[
\langle Bx,y\rangle =\{Ax_*,y_*\}= \{ x_*,Ay_*\}
=\langle x,By\rangle
\quad\colon\quad x,y\in
\mathcal D(T)
\tag{i}
\]
We have also
\[
\langle Bx,x\rangle=\{A^2x_*,x_*\}=\{Ax_*,Ax_*\}=
\langle Bx,Bx\rangle+\langle TBx,TBx\rangle\implies
\]
\[
||Bx||^2= \langle Bx,Bx\rangle\leq \langle Bx,x\rangle
\leq||Bx||\cdot ||x||
\] 

\noindent
where the Cauchy-Schwarz inequality was used in the last step.
Hence
\[
||Bx||\leq ||x||\quad\colon\quad x\in
\mathcal D(T)
\] 
This entails that that the densey defined operator $B$ 
extends uniquely to
$\mathcal H$ as  a bounded operator
of norm $\leq 1$.
 Moreover, since
(i) hold for pairs $x,y$ in the dense subspace
$\mathcal D(T)$, it follows that
$B$  is self-adjoint.
Next, consider a pair $x,y$ in $\mathcal D(T)$ which gives
\[ 
\langle x,y\rangle= \{Ax_*,y_*\}=
\{x_*,Ay_*\}=\langle x, By\rangle+\langle Tx,TBy\rangle
\]
Keeping $y$ fixed the linear functiional
\[ 
x\mapsto \langle Tx,TBy\rangle=\langle x,y\rangle-\langle x, By\rangle
\]
is bounded on $\mathcal D(T)$. By the construction of
$T^*$  it follows that
$TBy\in \mathcal D(T^*)$
and we also get the equality
\[
\langle x,y\rangle=
\langle x, By\rangle+\langle x,T^*TBy\rangle\tag{ii}
\]
\medskip


\noindent
Since (ii)  holds for all $x$ in the dense subspace $\mathcal D(T)$ we conclude that
\[
y=By+T^*TBy= (E+T^*T)(By)\quad\colon\quad y\in \mathcal D(T)\tag{iii}
\]
\medskip

\noindent
{\bf{Conclusion.}}
From the above we have 
the inclusion
\[ 
TB(\mathcal D(T))\subset
\mathcal D(T^*)
\]
Hence   $\mathcal D(T^*T)$
 contains
$B(\mathcal D(T))$ and (iii) 
means that
$B$ is a right inverse of $E+T^*T$
provided that the $y$-vectors are restricted to
$\mathcal D(T)$.
\bigskip


FINISH ..



\newpage





\centerline{\bf{11.5 A result about  positive operators.}}

\bigskip

\noindent
Let $S$ be a compact Hausdorff
space and $X$  the Banach space of continuous and
complex-valued functions on $S$.
A linear operator $T$ on $X$ is  positive if
it sends every non-negative and real-valued function $f$ to another  real-valued and
non-negative function.
Denote by $\mathcal F^+$ the family of positive operators
$T$ which satisfy the following: First
\[
\lim_{n\to\infty}\, \frac{1}{n}\cdot x^*(T^nx)=0\tag{1}
\] 
hold for all pairs $x\in X$ and $x^*\in X^*$.
The second condition is that
$\sigma(T)$ is the union of a compact set in a disc
$\{|\lambda|\leq r$ for some $r<1 $, and a 
finite set of points on the unit circle. 
The  final  condition is that
$R_T(\lambda)$
is meromorphic in the exterior disc
$\{|\lambda>r\}$, i.e. it has poles at
the spectral points on the unit circle.








\medskip

\noindent
{\bf{6. Theorem.}}
\emph{If $T\in\mathcal F^+$ 
then
each spectral value $e^{i\theta}\in \sigma(T)$ is a root of unity.}

\medskip


\noindent
\emph{Proof.}
Frist we prove that $R_T(\lambda)$  has a simple pole at
each  $e^{i\theta}\in \sigma(T)$.
Replacing 
$T$ by  $e^{-i\theta}\cdot T$
it suffices to prove this when
$e^{i\theta}=1$.
If $R_T(\lambda)$ has a pole of order $\geq 2$
at $\lambda=1 $ we know from ¤ XX that there exists $x\in X$ such that
\[ 
Tx\neq  x\quad\text{and}\quad
(E-T)^2\,x=0\tag{i}
\]
This gives  $T^2+x=2Tx$ and by an induction
\[
\frac{1}{n} \cdot T^n x=\frac{1}{n}\cdot x+(E-T)x\quad\colon n=1,2,\ldots\tag{ii}
\]
Condition (1) and (ii) give for each $x^*\in X^*$:
\[ 
0=\lim_{n\to\infty}\, \frac{1}{n}\cdot x^*( T^n x)=\lim_{n\to\infty}\,
x^*(\frac{1}{n}\cdot x+(E-T)x)
\] 
It follows that $x^*(E-T)(x)=0$ and since 
$x^*$ is arbitrary we get   $Tx=x$ which contradicts (i).
Hence
the pole must be simple.
\medskip


\noindent
Next, with $e^{i\theta}\in\sigma(T) $
we have seen that
$R_T$  has a simple pole.
By the general result in ¤ xx there exists
some    $f\in C^0(S)$ which is not identically zero and
\[ 
T(f)=e^{i\theta}\cdot f
\]
Multiplying $f$ with a complex scalar we may assume that
its  maximum norm on $S$ is one and there exists a point $s_0\in S$ such that
\[ 
f(s_0)=1
\]
For each $n\geq 1$ we have a linear functional on
$X$ defined by $g\mapsto T^n(g)(s_0)$ whuch gives a
Riesz measure $\mu_n$ such that
\[
\int_S\, g\cdot d\mu_n=T^n g(s_0)\quad\colon g\in C^0(S)
\]
Since $T^n$ is positive
the integrals in the left hand side are
$\geq 0$ when $g$ are real-valued and non-negative which entails that
the measures $\{\mu_n\}$ are real-valued and non-negative.
For each $n\geq 1 $ we put
\[ 
A_n=\{x\,\colon\, e^{-in\theta}\cdot f(x)\neq 1\}
\]
Since the sup-norm of $f$ is one we notice that
\[ 
A_n=
\{x\,\colon\, \mathfrak{Re}(e^{-in\theta}f(x))<1\}\tag{iii}
\]
Now
\[
0=f(s_0)- e^{-in\theta}\cdot T^n f(s_0)
=\int_S\,[1-e^{-in\theta}f(s)]\cdot  d\mu_n(s)\tag{iv}
\]
Taking real parts we get
\[
0=\int_S\,[1-\mathfrak{Re}(e^{-in\theta}f(s))]\cdot  d\mu_n(s)\tag{v}
\]
By (iii)  the integrand in (v)
is non-negative and since the whole 
integral is zero it follows that
\[
\mu_n(A_n)= \mu_n(\{\mathfrak{Re}(e^{-in\theta}<1\}=0\tag{vi}
\]
Suppose now that
there exists a pair $n\neq m$ such that
\[
(S\setminus A_n)\cap (S_m\setminus A_m)\neq \emptyset\tag{vii}
\] 
A point $s_*$ in this non-empty intersection
gives
\[
1=e^{in\theta}f(s_*)=e^{im\theta}\cdot f(s_*)\implies
e^{in\theta}=e^{im\theta}
\] 
and hence  $e^{i\theta}$ is a root of unity.
$m-n\neq 0$.
So the proof of Theorem 6.1  is finished if we have established the following

\medskip

\noindent
\emph{Sublemma.}
\emph{The sets $\{S\setminus A_n\}$ cannot be pairwise disjoint.}
\medskip

\noindent
\emph{Proof.}
First,  $f$ has maximum norm
and by the above:
\[ 
\int_S\, f\cdot d\mu_n=e^{in\theta}
\]
Hence the total mass $\mu_n(S)$ is at least one.
Next, 
for each $n\geq 2$ we set
\[
\pi_n=\frac{1}{n}\cdot (\mu_1+\ldots+\mu_n)
\]
Since 
$\mu_n(S)\geq 1$  for each $n$ we get 
$\pi_n(S)\geq 1$. Put
\[
\mathcal A=\bigcap\, A_n
\]
Above we proved that $\mu_n(A_n)=0$ hold for every $n$ which gives
\[ 
\pi_n(\mathcal A)=0\quad\colon\, n=1,2,\ldots\tag{*}
\]
Next, when
the sets $\{S\setminus A_k\}$ 
are pairwise disjoint one has 
the inclusions
\[
S\setminus A_k\subset A_\nu\quad\forall\,\nu\neq k
\]
Keeping $k$ fixed it follows that
$\pi_\nu(S\setminus A_k)=0$ for every $\nu\geq 0$.
So when $n$ is large while $k$ is kept fixed we obtain
\[ 
\pi_n(S\setminus A_k))= \frac{1}{n}\cdot \mu_k(S\setminus A_k))\implies
\lim_{n\to\infty}\, \pi_n(S\setminus A_k))=0
\quad\colon k=1,2,\ldots\tag{**}
\]
At this stage we use Lemma xx which shows that 
$R_T(\lambda)$ has at most a simple pole at $\lambda=1$.
With $\epsilon>0$
the Neumann series expansion gives
\[
E+\sum_{k=1}^\infty\,
\frac {T^k}{(1+\epsilon)^k}=
R_T(1+\epsilon))
=\frac{1}{\epsilon} \cdot Q+W(1+\epsilon))
\]
where $W(\lambda)$ is an operator-valued analytic function
in an open disc centered at $\lambda=1$ while $Q$ is a bounded
linear operator on $C^0(S)$.
Keeping $\epsilon>0$ fixed we apply both sides to the identity function
$1_S$ on $S$ and the construction of
the measures $\{\mu_n\}$ gives
\[
1+
\sum_{k=1}^\infty\,
\frac {\mu_k(S)}{(1+\epsilon)^k}=\frac{1}{\epsilon} \cdot Q(1_S)(s_0)+
W(1+\epsilon))(1_S)(s_0)
\]
If $n\geq 2$ is an integer and $\epsilon=\frac{1}{n}$
one gets the inequality
\[
\sum_{k=1}^{k=n}\,
\frac {\mu_k(S)}{(1+\frac{1}{n})^k}\leq
n\cdot |Q(1_S)(s_0)|+|W(1+1/n))(1_S)(s_0)|\leq
n\dot ||Q||+ ||W(1+1/n)||\implies
\]
\[
\frac{1}{n}\cdot\sum_{k=1}^{k=n}\,\mu_k(S)\leq
(1+\frac{1}{n})^n\cdot (||Q||+\frac{ ||W(1+1/n)||}{n}
\]
Since
Neper's constant $e\geq (1+\frac{1}{n})^n$ for every $n$
we find
a constant $C$ which is
independent of $n$ such that
\[
\frac{1}{n}\cdot\sum_{k=1}^{k=n}\,\mu_k(S)\leq C
\]
Hence the sequence $\{\pi_n(S)\}$ is  bounded
and we can pass to a subsequence
which converges weakly to a limit measure $\mu_*$.
For this $\sigma$-additive measure the limit formula in (**) above entails that
\[ 
\mu_*(S\setminus A_k)=0\quad\colon\, k=1,2,\ldots\tag{i}
\]
Moreover, by (*) we also have
\[
\pi_*(\mathcal A)=0\tag{ii}
\]
Now
$S= \mathcal A\cup\, A_k$ so (i-ii) give:
\[ 
\mu_*(S)=0
\]
But this is impossible for at the same time
we have already seen that
$\pi_n(S)\geq 1$ for each $n$ and hence also $\mu_*(S)\geq 1$.









\bigskip
Compact pertubations to finish Kakutani-Yosida !!!



\bigskip



\noindent 
In general, consider some complex Banch space
$X$ be a Banach space and
denote by $\mathcal F(X)$
the family of bounded liner operators  $T$ on $X$  
such that

\[ 
\lim_{n\to\infty}\, \frac{1}{n}\cdot x^*(T^nx)=0\tag{*}
\] 
hold for all pairs $x\in X$ and $x^*\in X^*$.
\medskip


\noindent
{\bf{1. Exercise.}} Apply the Banach-Steinhaus theorem to show that
if $T\in\mathcal F(X)$ then
there exists a constant $M$ such that the operator norms satisfy
\[ 
||T^n||\leq M\cdot n\quad\colon\, n=1,2,\ldots
\]


\noindent
Since the $n$:th root of $M\cdot n$ tends to one as $n\to+\infty$, 
the spectral radius formula entails that
the spectrum $\sigma(T)$ is contained in the closed unit disc
of the complex $\lambda$-plane.
So in the exterior disc
$\{|\lambda|>1\}$ there exists the
the resolvent 
\[ 
R_T(\lambda)= (\lambda\cdot E-T)^{-1}
\]



\noindent{\bf{2. The class $\mathcal F_*$}}.
It consists of those $T$ in $\mathcal F(X)$
for which there exists
some $\alpha<1$ such that
$R_T(\lambda)$ extends to a meromorphic function in
the exterior disc
$\{|\lambda|>\alpha\}$.
Since $\sigma(T)\subset
\{|\lambda|\leq 1\}$
it follows that when
$T\in\mathcal F_*$ then
the set of points in $\sigma(T)$ which belongs to the unit circle
in the complex $\lambda$-plane is empty or finite and
after we can always choose $\alpha<1$ such that
\[ 
\sigma(T)\cap \{\alpha<|\lambda|<1\}= \emptyset
\]

\medskip

\noindent
{\bf{3. Proposition.}}
\emph{If $T\in \mathcal F_*$ andÊ$e^{i\theta}\in \sigma(T)$
for some $\theta$, then Neumann's resolvent
$R_T(\lambda)$ 
has a simple pole at $e^{i\theta}$.}
 \medskip

\noindent
\emph{Proof.}
Replacing
$T$ by  $e^{-i\theta}\cdot T$
it suffices to prove the result when
$e^{i\theta}=1$.
If $R_T(\lambda)$ has a pole of order $\geq 2$
at $\lambda=1 $ we know from ¤ XX that there exists $x\in X$ such that
\[ 
Tx\neq  x\quad\text{and}\quad
(E-T)^2\,x=0\tag{i}
\]
The last equation means that $T^2+x=2Tx$ and an induction
over $n$ gives
\[
\frac{1}{n} \cdot T^n x=\frac{1}{n}\cdot x+(E-T)x\tag{ii}
\]
Since $T\in\mathcal F$ we have
\[ 
\lim_{n\to\infty}\, \frac{1}{n}\cdot x^*( T^n x)=0
\quad\colon\, \forall\\, x^*\in X^*\tag{iii}
\] 
Then (ii) entails that $x^*(E-T)(x)=0$. Since
$x^*$ is arbitrary we get  $Tx=x$ which contradicts (i) and hence
the pole is simple.
\medskip

\noindent
{\bf{4. Theorem.}}
\emph{Let $T\in \mathcal F(X)$ be such that   there exists a compact
operator $K$ where 
$||T+K||<1$. Then $T\in \mathcal F_*$ and
for every $e^{i\theta}\in\sigma(T)$
the eigenspace
$E_T(\theta)= \{ x\in X\,\colon\, Tx= e^{i\theta} x\}$ is finite dimensional.}

\medskip

\noindent
\emph{Proof.}
Set $S=T+K$ and for a complex number
$\lambda$ we write 
$\lambda\cdot E-T= \lambda\cdot E-T-K+K$. Outside $\sigma(S)$ we get
\[
R_S(\lambda)(\lambda\cdot E-T)=
E+R_S(\lambda)\cdot K\tag{i}
\]
The Neumann series for large absolute values
$|\lambda|$
applied to $R_S(\lambda)$ gives some $\rho>0$ and
\[
( E+R_S(\lambda)\cdot K)^{-1}= E+R_S(\lambda)\cdot K\dot
( E+R_S(\lambda)\cdot K)^{-1}\quad\colon\,|\lambda|>\rho\tag{ii}
\]

\noindent
Next, when
$|\lambda|$ is large
we notice that
(i) gives
\[
R_T(\lambda)=  ( E+R_S(\lambda)\cdot K)^{-1}\cdot R_S(\lambda)\tag{iii}
\]
Together with (ii) we obtain
\[
R_T(\lambda)=R_S(\lambda)+ 
R_S(\lambda)\cdot 
( E+R_S(\lambda)\cdot K)^{-1}\cdot R_S(\lambda)\tag{iv}
\]
Set $\alpha=||S||$ which by assumption is $<1$.
Now
$R_S(\lambda)$ is analytic in the exterior disc
$\{\lambda|>\alpha\}$ so in this exterior disc
$R_\lambda(T)$ differs from  the analytic function $R_\lambda(S)$ by
\[
\lambda\mapsto R_S(\lambda)\cdot 
( E+R_S(\lambda)\cdot K)^{-1}\cdot R_S(\lambda)\tag{v}
\]
Here $K$ is a compact operator so 
the
result in ¤ XX entails that this function extends to
be meromorphic  in $\{|\lambda|>\alpha\}$.
There remains to prove that
eigenspaces at spectral points on the unit circle are finite dimensional.
To prove this we use (iv). 
Let $e^{i\theta}\in\sigma(T)$. By Proposition 3 it is a simple pole
so we have a Laurent series expansion
\[
R_T(e^{i\theta}+z)= \frac{A_{-1}}{z}+ A_0+ A_1z+\ldots
\]
By the general results from ¤¤ there remains to show that 
$A_{-1}$ has finite dimensional range.
To see this we apply (iv) which gives the equation
\[
R_S(e^{i\theta}+z)+
R_S(e^{i\theta}+z)\cdot(E+
R_S(e^{i\theta}+z)\cdot K)^{-1}\cdot R_S(e^{i\theta}+z)
\]
To simplify notations we set $B(z)=R_S(e^{i\theta}+z)$
which by assumption is analytic in a neighborhood of $z=0$.
Moreover, the operator $B(0)$ is invertible.
So now one has
\[
 \frac{A_{-1}}{z}+ A_0+ A_1z+\ldots=
 B(z)+B(z)(E+B(z)\cdot K)^{-1}B(z)
 \]
Since $B(0)$ is invertible  we  have a Laurent series expansion
\[
(E+B(z)\cdot K)^{-1}= \frac{A^*_{-1}}{z}+A_0^*+A_1^*z+\ldots
\]
and identying the coefficient of $z^{-1}$ gives
\[
A_{-1}= B(0)A^*_{-1}B(0)
\]
Next, from (xx) one has

\[
E=(E+B(z)\cdot K)(\frac{A^*_{-1}}{z}+A_0^*+A_1^*z+\ldots)\implies
(E +B(0)\cdot K)A^*_{-1}=0
\]
Here $B(0)\cdot K$ is a compact operator and hence  Fredholm theory 
implies that $A^*_{-1}$ has a finite dimensional range. Since
$B(0)$ is invertible the same is true for $A_{-1}$ which finishes the proof
of 
Theorem 4.




\medskip

\noindent
{\bf{5. Proposition}}.
\emph{
If
$T\in\mathcal F$ is  such that
$T^N\in\mathcal F_*$ for some integer $N\geq 2$.
Then 
$T\in\mathcal F_*$.}
\medskip

\noindent
\emph{Proof.}
We have the algebraic equation
\[ 
\lambda^N\cdot E -T^N=(\lambda\cdot E-T)(
\lambda^{N-1}\cdot E+
\lambda^{N-2}\cdot T+\ldots+T^{N_1})
\]
It follows that
\[ R_T(\lambda)=
(\lambda^{N-1}\cdot E+
\lambda^{N-2}\cdot T+\ldots+T^{N_1})\cdot R_{T^N}(\lambda^N)
\]
Since $T^NB\in\mathcal F_*$ there exists
$\alpha<1$ such that
\[
\lambda\mapsto  R_{T^N}(\lambda^N)
\]
extends to be meromorphic in
$\{|\lambda|>\alpha\}$. At the same time
$(\lambda^{N-1}\cdot E+
\lambda^{N-2}\cdot T+\ldots+T^{N_1})$
is  a polynomial
and hence
$R_T(\lambda)$ also extends to be meromorphic
in this
exterior disc so that 
$T\in\mathcal F_*$.




\newpage




\centerline{\bf{11.6 Factorizations of non-symmetric kernels.}}


\bigskip

\noindent
Recall that
the Neumann-PoincarŽ kernel $K(p,q)$ of  a
plane $C^1$-curve $\mathcal C$
is given by
\[ 
K(p,q)= \frac{\langle p-q,{\bf{n}}_i(p)\rangle}{|p-q|}
\]
This kernel function gives the integral operator $\mathcal K$
defined on $C^0(\mathcal C)$ by
\[
\mathcal K_g(p)=\int_C\, K(p,q)\cdot g(q)\, ds(q)
\]
where $ds$ is the arc-length measure on $C$.
Let $M$ be a positive number which exceeds the diameter of 
$\mathcal C$
so that
$|p-q|<M\,\colon\, p,q\in\mathcal C$.
Set
\[
N(p,q)= \int_\mathcal C\, 
K(p,\xi )\cdot \log\,\frac{M}{|q-\xi|}\cdot ds(\xi)
\]



\noindent
{\bf{Exercise.}} Verify that
$N$ is symmetric, i.e. $N(p,q)= N(q,p)$
hold for all pairs $p,q$ in $\mathcal C$.
Moreover, 
\[ 
S(p,q)=\log\, \frac{M}{|p-q|}
\] 
is a symmetric and positive kernel function
and since $\mathcal C$ is of class $C^1$ the reader should verify that it gives a
Hilbert-Schmidt kernel, i.e.
\[ 
\iint_{\mathcal C\times\mathcal C}\,
S(p,q)^2\, ds(p)ds(q)<\infty
\]



\noindent
Hence the
Neuman-PoincarŽ operator  $\mathcal K$ appears in an
equation
\[ 
\mathcal N= \mathcal K\circ \mathcal S\tag{*}
\] 
where $\mathcal S$ is defined via a positive  symmetric Hilbert-Schmidt kernel and
$\mathcal N$ is symmetric.
Following  
[Carleman: ¤ 11 ] we give a procedure to determine 
the spectrum of $\mathcal K$.


\medskip

\centerline{\bf{11.6.1 Spectral properties of  non-symmetric kernels.}}
\bigskip


\noindent
In general,let  $K(x,y)$ be a continuous real-valued function on the closed unit square
$\square=\{0\leq x,y\leq 1\}$. We do not assume that  
$K$ is symmetric but 
there exists a positive definite
Hilbert-Schmidt kernel $S(x,y)$ such that
\[ 
N(x,y)=\int_0^1\, S(x,t) K(t,y)\, dy
\] 
yields a symmetric kernel function.
The Hilbert-Schmidt theory
gives
an orthonormal basis $\{\phi_n\}$ in
$L^2[0,1]$ formed by eigenfunctions to $\mathcal S$ where
\[ 
\mathcal S\phi_n=\kappa_n \phi_n\tag{1}
\] 
where the positive $\kappa$-numbers  tend to zero.
Moreover, each $u\in L^2[0,1]$
has a Fourier-Hilbert  expansion
\[ 
 u= \sum\,\alpha_n\cdot \phi_n\tag{2}
\]
We  seek 
eigenfunctions of  the integral operator $\mathcal K$.
Let  $u$ be  a function in $L^2[0,1]$
such that:
\[ 
u=\lambda\cdot \mathcal Ku\tag{3}
\]
where
$\lambda$ in general is a complex number. It follows that
\[
\lambda\cdot \int\, N(x,y)u(y)\, dy
=
\lambda\iint SA(x,t)K(t,y)u(y)\, dtdy=
\int S(x,t)u(t)\,dt\tag{4}
\]
Multiplying  with $\phi_p(x)$ an integration gives
\[
\lambda\cdot \int\, \phi_p(x)N(x,y)u(y)\, dx dy=
\iint \phi_p(x) S(x,t)u(t)\,dxdt=
\kappa_p\int \phi_p(t)u(t) \, dt\tag{5}
\]
Next, using  the expansion of $u$ from (2) we get
the equations:
\[
\sum_{q=1}^\infty \alpha_q\cdot 
\iint  \phi_q(x)\phi_p(x)N(x,y)\, dx dy=\kappa_p\alpha_p
\quad\colon\, p=1,2,\ldots\tag{6}
\]
Set
\[
c_{qp}=\iint  \phi_q(x)\phi_p(x)N(x,y)\, dx dy
\]
It follows that $\{\alpha_p\}$ satisfies the system
\[
\kappa_p\alpha_p=
\lambda\cdot \sum_{q=1}^\infty \, c_{qp}\alpha_q\tag{7}
\]
Since $N(x,y)= N(y,x)$ the
doubly indexed $c$-sequence is symmetric. Set
\[ 
\beta_p= \sqrt{\kappa_p}\cdot \alpha_p
\implies
\beta_p=\lambda\cdot \sum_{q=1}^\infty
\frac{c_{pq}}{\sqrt{\kappa_p}\cdot \sqrt{\kappa_q}}
\cdot \beta_q\tag{8}
\]



\noindent
Next, 
put
\[
k_{p,q}=\iint K(x,y)\phi_p(x)\phi_q(y)\, dxdy\tag{9}
\]
From  the above  the following hold for each pair $p,q$:

\[ c_{pq}= \iiint\,
\phi_q(x)\phi_p(y) S(x,t)K(t,y)\, dxdydt=
\kappa_qk_{p,q}=\kappa_pk_{q,p}\implies
\]
\[ 
\frac{c_{p,q}^2}{ \kappa_p\cdot \kappa_q}\leq
|k_{p,q}\cdot  k_{q,p}|
\leq \frac{1}{2}(k_{p,q}^2+k_{q,p}^2)\tag{10}
\]
Here $\{k_{p,q}\}$ are the Fourier-Hilbert coefficients of $K(x,y)$
which entails that
\[ 
\sum\sum\, k_{p,q}^2\leq
\iint K(x,y)^2\, dxdy
\]
Hence the symmetric and doubly indexed sequence
\[
\frac{c_{p,q}}{\sqrt{\kappa_p\cdot \kappa_q}}\tag{11}
\] 
is of Hilbert-Schmidt type.
\bigskip

\noindent
{\bf{11.6.2 Conclusion.}}
The eigenfunctions $u$ in $L^2[0,1]$
associated to the $\mathcal K$-kernel have Fourier-Hilbert expansions via
the $\{\phi_n\}$-basis  which are  determined by 
$\alpha$-sequences  satisfying the system (7)


\medskip

\noindent
{\bf{11.6.3 Remark.}}
When a plane curve
$\mathcal C$ has corner points the
Neumann-PoincarŽ kernel is
unbounded. Here
the reduction to the symmetric case is  more involved  and leads 
to
quite intricate results which appear in Part II from
[Carleman].
The interplay  between singularities
on boundaries in 
the Neumann-PoincarŽ equation
and the corresponding unbounded kernel functions 
illustrates  the 
general theory
densely defined self-adjoint operators.
Much analysis remains to be done and
open problems about
the Neumann-PoincarŽ equation 
remains to be settled in dimension three. So far  it appears that
only the 2-dimensional case 
is properly understood via 
results  in [Car:1916].
See also ¤ xx for a studiy of Neumann's boundary value problem
both in the plane and  ${\bf{R}}^3$.


\newpage


\centerline{\bf{Uniqueness results for the exterior
Laplace equation}}

\bigskip

\noindent
Let $\Omega$ be a bounded open set
in ${\bf{R}}^3$ whose boundary is a finite union of closed
surfaces of class $C^1$ at least.
Set $U={\bf{R}}^3\setminus \Omega$.
Denote by $\mathcal S(U)$ the class of real-valued $C^2$-functions
$f$ in $U$ which extend continuously to
the boundary of $U$ which of course is equal to
$\partial\Omega$. Moreover,  we assume that the 
the exterior normal derivaties
$\frac{df}{dn}$ taken along the boundary exist and
give a continuous function on
$\partial U$.
Consider large positive $R$-numbers  so that
the open ball $B(R)$ of radius $R$ centered at the origin
contains the closure of $\Omega$.
Set
\[ 
D(f)^2(x,y,z)=(\frac{\partial f}{\partial x})^2+
(\frac{\partial f}{\partial y})^2+(\frac{\partial f}{\partial z})^2
\]
Green's formula applied to the domain $B(R)\setminus\overline{\Omega}$
gives
\[
\int_{B(R)\setminus\overline{\Omega}}\,D(f)^2\, dp+
\int_{B(R)\setminus\overline{\Omega}}\,f\cdot \Delta(f)\, dp=
\int_{\partial U}\tag{1} 
\]
where $dp=dxdxydz$.
We shall use this to prove:

\bigskip

\noindent
{\bf{1. Theorem.}}
\emph{If $f$ and $\Delta(f)$ both belong to $L^2(U)$, it follows that}
\[
\int_U \,D(f)^2\, dp=\int_{\partial U}-
\int_U\,f\cdot \Delta(f)\, dp
\]
\medskip

\noindent
\emph{Proof}
Since $f$ and $\Delta(f)$ are square integrable, the Cauchy-Schwarz
inequality entails that
$f\cdot \Delta(f)$ is absolutely integrable over $U$.
Hence (1) gives the theorem if we prove the limit formula
\[
\liminf_{R\to \infty}\,\int_{\partial U}=0\tag{i}
\]
To prove (i) we consider the function
\[
\psi(R)=\int_{B(R)\setminus\overline{\Omega}}\, u^2\, dp 
\]
The derivative becomes
\[
\psi'(R)=\int_{S(R)} \, u^2\cdot d\omega
\]
where $S(R)$ is the sphere of radius $R$ and $d\omega$ its area measure.
Passing to the second derivative the reader should verify
the equation
\[
\psi''(R)=\frac{2}{R}\cdot \psi'(R)+
2\cdot \int_{S(R)} \, f\cdot\frac{\partial f}{\partial n}\, d\omega
\]
Hence (i) follows if 
\[
\liminf_{R\to \infty}\,\psi''(R)-\frac{2}{R}\cdot \psi'(R)=0\tag{ii}
\]
To obtain (ii)  we first notice that
$\Psi$ is non-decreasing and
since $f$ is square integrable it tends to a finite limit as $R\to+\infty$.
Hence the first order derivative cannot stay above a positive constant
for all large $R$.
So for the derivative  $\psi'$ two cases can occur. Either
it decreases in a monotone way to zero as $R\to+\infty$. In this case it is eveident that
there exists a striuctly increasing sequebce $\{r_n\}$ such that
$\psi''(r-n)\to 0$ and (ii) follows.
In the second case
the function $\psi'(R)$ attain a local minium at an infinite sequence
$\{r_n\}$ which again tend to zero.
Here $\psi''(r_n)=0$ and at the same time these local minimum values of
the first order derivative tend to zero. So again (ii) holds and
Theorem 1 is proved.
\bigskip



\centerline{\bf{A vanishing result.}}
\bigskip


\noindent
Let  $f$ satisfy the differential equation
\[
 \Delta(f)+\lambda\cdot f=0\tag{*}
 \] 
in $U$ for some real number $\lambda$.
In addition
we assume that
\[
\frac{df}{dn}(p)=0\quad\colon p\in \partial U\tag{**}
\]
\bigskip


\noindent
{\bf{2. Theorem. }}
\emph{If  $f$ satisfies (*-**) and  belongs to
$L^2(U)$, then $f$  is identically zero.}
 \bigskip


\noindent
\emph{Proof.}
Notice that Theorem 1 gives the equality
\[
\int_U \,D(f)^2\, dp=\lambda\cdot 
\int_U\,f^2\, dp
\]
So if $\lambda\leq 0$ the vanishing of $f$ is obvious.
From now on $\lambda>0$.
We shall work with polar coordinates, i.e. employ the Euler's  angular variables
$\phi$ and $\theta$ where
\[
0<\theta\quad\colon\, 0<\phi<2\pi
\]
The wellknown expression of $\Delta$Êin the variables $r,\theta,\phi$ 
shows that the equation (*) corresponds to
\[
xxxxx+xxxx=0\tag{i}
\]
Let $n\geq 1$ and $Y_n(\theta,\phi)$ some spherical function of
degree $n$ with a normalised $L^2$-integral  equal to one.
For each $r$ where $B(r)$ contains $\overline{\Omega}$
we set
\[
 Z(r)=\int_0^{2\pi}\int_0^\pi\, 
 Y_n(\theta,\phi)\cdot f(r,\theta,\phi)\, \sin(\theta)\, d\theta d\phi\tag{ii}
\]
The Cauchy-Schwarz inequality gives
\[
 Z(r)^2\leq \int_0^{2\pi}\int_0^\pi\, 
Y^2_n\cdot  \sin(\theta)\, d\theta d\phi\cdot 
\int_0^{2\pi}\int_0^\pi\, 
f^2(r,\theta,\phi)\cdot  \sin(\theta)\, d\theta d\phi
\]
Since the $L^2$-integral if $Y_n$ is normalised
the last product is reduced to
\[
J(r)=\int_0^{2\pi}\int_0^\pi\, 
f^2(r,\theta,\phi)\cdot  \sin(\theta)\, d\theta d\phi
\]
Now
\[
\int_{r_*}^\infty\, r^2\cdot J(r)\, dr
\]
is equal to the finite $L^2$-integral of $f$ in the exterior domain
taken outside a ball $B(r_*)$.
From (ii) we conclude that
\[
\int_{r_*}^\infty\, r^2\cdot Z(r)^2\, dr<\infty\tag{iii}
\]
\medskip


\noindent
{\bf{A differential equation.}}
Recall that a spherical function of degree $n$ satisfies
\[
\frac{1}{\sin \theta}
\frac{d}{d \theta}\bigl(\sin \theta\cdot
\frac{\partial Y_n}{\partial \theta}\bigr)+
\frac{1}{\sin^2 \theta}\frac{\partial^2 Y_n}{\partial \phi^2}+
(n+1)n\cdot Y_n=0
\tag{iv}
\]
\medskip

\noindent
{\bf{Exercise.}}
Show via suitable partial integrations that (i) and (iv) imply that
$Z(r)$ satisfies the differential equation
\[
\frac{1}{r^2}\cdot
\frac{d}{dr}(r^2\cdot \frac{dZ}{dr})+
(\lambda-\frac{n(n+1)}{r^2})Z=0\tag{v}
\]
\medskip

\noindent
The second order differential equation
has two linearly independent solutions of the form
\[
Z_1=\cos(\sqrt{\lambda} r)\cdot \bigl[\frac{1}{r}+
\frac{a_2}{r^2}+\ldots\bigr]
\]
\[
Z_2=\sin(\sqrt{\lambda} r)\cdot \bigl[\frac{1}{r}+
\frac{b_2}{r^2}+\ldots\bigr]
\]
It follows that there exist a pair of constants $c_1,c_2$ such that

\[
Z=c_1Z_1+c_2Z_2=\frac{c_1\cdot  \cos(\sqrt{\lambda} r)+
c_2\cdot  \sin(\sqrt{\lambda} r)}{r}+
\frac{B(r)}{r^2}\tag{vi}
\]
where $r\mapsto B(r)$ stays bounded as $r\to+\infty$.
\medskip

\noindent
{\bf{Exercise.}}
Show that the finite integral in (iii) and (vi) give 
$c_1=c_2=0$ and hence $Z(r)$
identically zero for large $r$.
Since this  hold for all spherical functions we conclude that 
$f$ is identically zero outside 
the closed ballÊ$B(r_*)$.
Finally, by assumption $U$Êis connected and the elliptic equation
(*) implies that $f$ is a real-analytic function in
$U$, So the vanishing outside a large ball entails that $f$ is identically zero in $U$
which finishes the proof of Theorem 2.
\bigskip

\noindent
\centerline {\bf{3. A result about absolute continuity.}}
\medskip

\noindent
We consider functions  depending upon a real parameter
$\mu$ which varies in an interval $[a,b]$. To each
$\mu$ we are given a function
$f(x,y,z;\mu)$
 which is square integrable $C^2$-function in $U$ and the normal derivative along
 $\partial U$ is zero, i.e just as in the class $\mathcal S$ above.
 Moreover, 
 the $L^2(U)$-valued function
 \[
\mu\mapsto f(x,y,z;\mu)\tag{i}
\]
has a finite total variation on $[a,b]$.
Next,  assume that for every sub-interval $\ell$ of $[a,b]$ one has
the equality
\[
\Delta \bigl(\int_\ell\, \frac{d } {d\mu}\,f(x,y,z;\mu)+
\int_\ell\, \mu\cdot \frac{d } {d\mu}\, f(x,y,z;\mu)=0
\]
where the integrals as usual are taken in the sense of Borel-Stieltjes.
\bigskip

\noindent
{\bf{Theorem.}} \emph{Every function
from (i) which satisfies the conditions above is 
absolutely continues with respect to $\mu$.}
\bigskip

\noindent
\emph{About the proof.}
Using similar methods as in the proof of Theorem 1
one reduces the proof to study
functions 
$g(r;\mu)$ where $r\mapsto g(r;\mu)$ is 
a $C^2$-function and square integrable on
the interval $[r_*,+\infty)$ for a given $r_*>0$
while $\mu$ as above varies in $[a,b]$.
Moreover one has 
\[ 
\max_\mu\, \int_{r_*}^\infty\, g(r;\mu)\,  dr<\infty
\] 
Next, for each sub-interval
$\ell=[\alpha,\beta]$ we set
\[
\delta_\ell(g(r,\mu)=g(r,\beta)-g(r,\alpha)
\]
With these notations we say that
$g(r;\mu)$ is absolutely continuous with respect to $\mu$
if there to each $\epsilon>0$ exists
$\delta>0$Êsuch that
\[
\sum\, \int_{r_*}\, |\delta_{\ell_\nu}((g(r,\mu)\bigr|^2\cdot r^2\,dr<\epsilon
\]
for every finite family of sub-intervals
$\{\ell_\nu\}$ when  the sum of their lengths is
$<\delta$.
\medskip

\noindent
{\bf{Theorem.}}
\emph{Assume in addition to the above that
the  equation below holds for each 
sub-interval $\ell$} 
\[
\frac{1}{r^2}
\frac{d}{dr} \bigl[\, r^2\frac{d}{dr}(\delta_\ell(g(r,\mu) \bigr]-
\frac{n(n+1)}{r^2}\cdot \delta_\ell(g(r,\mu)+
\int_\ell\, \mu\cdot \frac{d}{d\mu}(g(r,\mu)=0
\]
\emph{Then 
$g(r,\mu)$ is absolutely continuous with respect to $\mu$.}

\newpage


\medskip


\centerline {\bf{A first example: Moment problems.}}
\medskip

\noindent
In the  very impressive and highly original  article
\emph{Recherches sur les fractions continues}
[Ann.Fac. Sci. Toulouse. 1894], Stieltjes
studied    the moment problem on the non-negative real line. This
amounts to find
a non-negative Riesz measure $\mu$ on ${\bf{R}}^+$
with prescribed  moments
\[
 c_\nu=\int_0^\infty\, x^\nu d\mu(x)\quad\colon\nu=0,1,2,\ldots\tag{*}
\]
An obvious necessary condition for the existence of $\mu$
is that
the quadratic form
\[
J(x)=\sum_{p=1}^\infty\sum_{q=1}^ \infty\, c_{pq}x_px_q
\]
is positive definite when it is restricted to vectors
$x$-vectors where only  finitely many $x_p\neq 0$.
The moment problem is  determined with respect to
the given sequence $\{c_\nu\}$ if there exists a unique non-negative
measure $\mu$ such that (*) holds.
To prove  existence and  analyze
uniqueness, Stieltjes employed the  expansion in
continued fractions of the  $c$-sequence. 
Stieltjes' work was later reconsidered by Hamburger
in the article \emph{xxxx}[ 1922]
where one allows solutions by Riesz measures $\mu$ on the whole real line,
i.e. now integration takes place over
$(-\infty,+\infty)$.
In ¤ xx we explain that this (extended) moment problem
is closely related to
the class of linear operators defined by inifinite 
and symmetric matrices of the form
\[
xxx=xxx
\]
where $\{a_n\}$ is an arbitrary real sequence  while 
$\{b_n\}$ is a sequence of positive real numbers.
A  complete 
description of all solutions $\mu$ to 
a non-determined  moment problem
was established by Carleman in the article
\emph{Sur le problŽme des moments} [C.R.Acad. Sci. Paris. 1922],
and we shall expose this in ¤ xx.
\medskip

\noindent
Returning to the case treated by Stieltjes
the existence of non-determined moment problems,
leads to
a peculiar result for certain  densely defined
linear operators on the Hilbert space $\ell^2$.
Following Stieltjes we consider a positive sequence of real numbers
$\{b_n\}$
and regard the operator $S$ defined by
\[
S(x)= (-b_1x_2,-b_1x_1,-b_2x_4,-b_2x_3,\ldots)
\]
where $x=\{x_n\}$ is a vector in $\ell^2$.
It means that $S$ is represented by the infinite symmetric matrix
whose non-zero elements
only appear in position $(j,j+1)$ or $(j+1,j)$
for every integer $j\geq 1$.
Now there exists the  dense subspace
$\mathcal D(S)$  of vectors
$x\in \ell^2$ such that
$S(x)$ also belongs to $\ell^2$.
The question arises if
the symmetry of the $S$-matrix persists in the following
sense: Suppose that $x$ and $y$ both belong to
$\mathcal D(S)$. Does it follow that 
\[ 
\langle S(x),y\rangle=
\langle x,S(y)\rangle \tag{**}
\]
where we have used the Hermitian inner product on the complex Hilbert space
$\ell^2$. So above $x$ and $y$ can be complex vectors.
In the cited article above, Carleman proved that
(**) hold for
every pair in $\mathcal D(S)$ if and only if 
the corresponding moment problem is determined.
This means that in spite of 
the symmetry of the matrix which
represents $S$, the resulting densely defined linear operator can fail to be self-adjoint.
In ¤ xx we show
that whenever
this peculair phenomenon  occurs,
the series
\[
\sum_{n=1}^\infty\, \frac{1}{b_n}<\infty
\]
However, the converse is not true, i.e. 
there exist determine moment problems where
the series above is converges.
\medskip

\noindent
{\bf{A final remark.}}
The study of the Hamburger-Stieltjes moment problem offers
an instructive lesson about unbounded but densely defined liear operators on
Hilbert spaces.
At the same time the material in ¤xx will teach
that even if one starts with a problem expressed in terms of functional analysis,
it is often necesssty to 
employ both results and methods from other disciplines such as 
analytic function theory and
Fourier analysis.




 
\centerline{\bf{Moment problems.}}
\bigskip


\noindent
A great inspiration during the development of
unbounded symmetric operators on Hibert spaces
emerged from  Stieltjes' pioneering article
\emph{Recherches sur les fractions continues}
[Ann. Fac. Sci.  Toulouse. 1894].
The  moment problem
asks for conditions on a
sequence $\{c_0,c_1,\ldots\}$ of positive real numbers
such that there exists a non-negative Riesz measure
$\mu$ on the real line and
\[
c_\nu= \int_{-\infty}^\infty\, t^\nu\cdot d\mu(t)\tag{*}
\] 
hold for each $\nu\geq 0$.
One easily verifies that
if $\mu$ exists then
the Hankel determinants
\[
\begin{pmatrix}
c_0&c_1&\ldots&c_n\\
c_1&c_2&\ldots&c_{n+1}\\
\ldots&\ldots&\ldots&\ldots\\
c_n&c_{n+1}&\ldots&c_{2n}\\
\end{pmatrix}
\]
are $>0$ for every $n=0,1,\ldots$. 
For brevity we say that
$\{c_n\}$ is a positive
Hankel sequence when
the determinants above are $>0$.
It turns out that this confition also is sufficient.
\medskip


\noindent
{\bf{Theorem.}} \emph{For each 
positive Hankel sequence
there exists at least one non-negative Riesz measure such that
(*) holds.}
\medskip


\noindent
{\bf{Remark.}}
The result above is due to Hamburger who  extended Stieltjes' original  results 
which treated  the situation where 
one seeks non-negative measures supported by
$\{\geq 0\}$.
The moment problem for a positive Hankel sequence is 
said to be determined
if (*) has a unique  solution $\mu$.
Hamburger proved that the determined case holds
if and only if the
the associated continued fractions of $\{c_n\}$
is completely convergent.
See ¤ x below for an account about this convergence  condition.
A "drawback" in the Hamburger-Stieltjes theory
is that it is often  difficult to check
when the associated continued fraction of a positive Hankel sequence
is completely convergent.
So one is led to seek  sufficient conditions
in order that (*) has a unique solution $\mu$.
Such a sufficient condition
was established  in Carleman's  monograph
[Carleman 1923. Page 189-220] 
and goes as follows:




\noindent
{\bf{1. Theorem.}}
\emph{The moment problem of 
a positive Hankel sequence $\{c_n\}$ is determined if}
\[
\sum_{n=1}^\infty\,c_n^{-\frac{1}{n}}=+\infty
\]
\medskip

\noindent
{\bf{Another criterion for  determined moment problems.}}
Studies of continued fractions and
their associated quadratic forms 
go back to
work by Heine. See  [Handbuch der theorie
der Kugelfunktionen: Vol. 1. part 2]. An excellent account appears also
in the article \emph{Zur Einordnung der Kettenbruchentheorie
in die theorie der quadratischen Formen von
unendlichvielen VerŠnderlichen} [Crelle J. of math. 1914] by
Hellinger and Toeplitz.
A positive Hankel sequence $\{c_n\}$
 corresponds to a
 quadratic form
 in an infinite number of variables:
 \[
 J(x)=\sum_{p=1}^\infty a_px_p^2-
 2\cdot \sum_{p=1}^\infty b_px_px_{p+1}
\]
where $b_p\neq 0$ for every $p$.
More precisely, the
sequences $\{a_\nu\}$ and $\{b_\nu\}$
arise when
the series
\[
-\bigl[\frac{c_0}{\mu}+
\frac{c_1}{\mu^2}+\frac{c_2}{\mu^3}+\ldots\,\bigr]
\]
is formally expanded into a continuous fraction
\[
\frac{c_0}{a_1-\mu-\frac{b_1^2}{a_1-\mu-\frac{b_2^2}{a_2-\mu}} }
\]
Now there exists 
the infinite  matrix $A$
with diagonal elements $\alpha_{pp}=a_p$ while
\[
\alpha_{p,p+1}= \alpha_{p+1,p}= -b_p\quad\colon p=1,2,\ldots
\]
and all the other elements are zero.
The symmetric  $A$-matrix 
gives a densely defined linear operator on
the complex Hilbert space $\ell^2$.
The following result is proved
[Carleman:1923]:
\medskip

\noindent
{\bf{2. Theorem.}}
\emph{The densely defined operator $A$ on $\ell^2$ is self-adjoint if and only if
the moment problem for $\{c_n\}$ is determined.}
\bigskip


\centerline {\bf{3. A  study of $A$-operators.}}
\bigskip

\noindent
Ignoring the "source" of the pair of real sequences $\{a_p\}$ and $\{b_p\}$
we consider a matrix $A$ as above where the sole condition
is that $b_p> 0$ for every $p$.
If $\mu$ is a complex number
one seeks infinite vectors
$x=(x_1,x_2,\ldots)$ 
 such that
 \[ 
 Ax=\mu\cdot x\tag{i}
 \]
 It is clear that (i) holds if and only if
 the sequence $\{x_p\}$ satisfies the infinite system of linear equations
 \[
(a_1-\mu)x_1=b_1x_2
\]
\[ 
(a_p-\mu)x_p=b_{p-1}x_{p-1}+ b_px_{p+1}\quad\colon p\geq 2
\]
\medskip

\noindent
Since $b_p> 0$ for every $p$ we see  that
$x_1$ determines the sequence and 
$x_2,x_3,\ldots$ depend on $x_1$ and the parameter $\mu$.
Keeping $x_1$ fixed while $\mu$ varies
the reader can  verify that
\[ 
x_p=\psi_p(\mu)\quad\colon p\geq 2
\]
where $\psi_p(\mu)$ is a polynomial of degree $p-1$ for each $p\geq 2$.
These $\psi$-polynomials depend on the given
pair
of sequences
$\{a_p\}$ and $\{b_p\}$ and 
with the following
result is  proved in [ibid]:
\medskip


\noindent
{\bf{3.1 Theorem.}}
\emph{The densely defined operator $A$ on $\ell^2$ is self-adjoint if and only if}
\[
\sum_{p=1}^\infty\, \psi_p(\mu)=+\infty
\]
\emph{for every non-real complex number
$\mu$.}
\medskip


\noindent
{\bf{4. A  general result.}}
Let $\{c_\nu\}$ be a positive Hankel sequence,
determined or not.
Let  $\rho$ be a non-negative measure which solves the moment problem (*) and
set
\[
\widehat{\rho}(\mu) =\int\, \frac{d\rho(t)}{t-\mu}
\]
This yields  an analytic function in
the upper half-plane.
A major result in [Carleman]
gives a sharp inclusion for the values which can be attained
by
these $\widehat{\rho}$ functions while
$\rho$ varies in the family of  non-negative measures which
solve the moment problem.
It is expressed via constructions of discs in the upper half-plane which
arise via a nested limit of discs constructed from a certain family of
Mšbius transformations.
More precisely, to the given Hankel sequence
we have the pair of sequences $\{a_\nu\}$ and $\{b_\nu\}$.
For a fixed $\mu$ in the upper half-plane
we consider the maps:
\[ 
S_\nu(z)=\frac{b_\nu^2}{a_{\nu+1}-\mu-z}\quad\colon \nu=0,1,\ldots
\]
Notice that
\[ 
\mathfrak{Im}(S_\nu(z))=\frac{b_\nu^2\cdot \mathfrak{Im}(\mu+z)}
{|a_{\nu+1}-\mu-z|^2}>0
\]
It follows that $S_\nu$ maps the upper half-plane $U^+$ conformally onto a disc
placed in $U^+$.
\medskip

\noindent
{\bf{Exercise.}}
To each $n\geq 1$ we consider the composed map
\[ 
\Gamma_n=S_0\circ S_1\circ\ldots\circ S_{n-1}
\]
Show that the images $\{C_n(\nu)= \Gamma_n(U^+)\}$
form a decreasing sequence of discs and there exists a limit
\[ 
C(\mu)=\cap\, C_n(\mu)
\]
which either is reduced to a single point or is a closed disc
in $U^+$.
\bigskip

\noindent
{\bf{4.1 Theorem.}} \emph{For each $\mu\in U^+$
and every $\rho$-measure which solves the moment problem
one has the inclusion}
\[
\widehat{\rho}(\mu)\subset C(\mu)
\]
 \emph{Moreover, for each point $z$ in this disc there exists
 $\rho$ such that
 $\widehat{\rho}(\mu)=z$.}




\newpage

\centerline{\bf{¤ 12. Symmetric integral operators.}}
\bigskip


\noindent
Consider the domain $\square=\{0\leq x\leq 1\}\times\{0\leq y\leq 1\}$
in ${\bf{R}}^2$.
Let $K(x,y)$ be a real-valued and Lebesgue mesure function on
$\square$ such that
the integrals
\[ 
\int_0^1\, K(x,y)^2\, dy<\infty
\]
for all $x$ outside a null-set on $[0,1]$.
In addition we assume that $K$ is symmetric,  i.e.$K(x,y)= K(y,x)$.
The $K$-kernel is bounded in Hilbert's sense if there exists a constant
$C$ such that
\[ 
\iint_\square\, K(x,y) u(x)u(y)\, dxdy\leq C^2\cdot\int_0^1\, u(x)^2\, dx
\]
for each $u\in L^2[0,1]$. A special case occurs when
$K(x,y)$ satisfies
\[
\iint_\square\, |K(x,y)|^2\, dxdy<\infty
\]
Then $\mathcal K$ is called a Hilbert-Schmidt operator and a crucial fact is that
it yields a compact operator on the Hilbert space
$\mathcal H=L^2[0,1]$.
\medskip

\noindent
{\bf{Exercise.}}
Prove that Hilbert-.Schmidt operators are compact. Tne hint is that
Lebesgue theory to begin with entails that when (zz) holds then
there exists a seqience of symmwtric and continuous kernel
functions $\{K_n(,y)\}$
such that
\[
\iint_\square\, |K(x,y)-K(x,y)|^2\, dxdy=0
\]
Next, the Cauchy-Schwarz inequality gives 
\[
||\mathcal K-\mathcal K_n||\leq \iint_\square\, |K(x,y)-K(x,y)|^2\, dxdy
\] 
for each $n$, where the right hand side refers to operator norms.
Now one uses the general fact that a linear operator which can be approximated in the operator
norm by compact operators is itself compact.
Finally the reader should verify that
if $K(x,y)$ is contoinous then $\mathcal K$ is compact.



\medskip

\noindent
{\bf{Spectral functions.}}
Let $K$ be a  symmetric Hilbert-Schmidt operator.
A special case of Holbert's theorem from ¤ 8  and the general 
facts about spectera of compact operators
in ¤ xx, entail that
there exists a sequence $\{\phi_n\}$
of pairwise orthogonal functions in
$\mathcal H$ with $L^2$-norms equal to one, a
real eigenvalues
$\{\mu_n\}$ so that
\[
\mathcal K(\phi_n)=\mu_n\cdot \phi_n
\]
The eigenvalues  form a discrete set outside zero and
arranged so that $\mu_1\geq |\mu_2\geq \ldots$
and repeated according to multiplicities, i.e. when
the corresponding eigenspace has dimension $\geq 2$.
Set
\[
\lambda_n=\mu_n^{-1}
\]
For each  $\lambda>0$ we set
\[
\rho(x,y;\lambda)=\sum_{0<\lambda_\nu<\lambda}\, \phi_\nu(x)\phi_\nu(y)
\]
\[
\rho(x,y;-\lambda)\sum_{-\lambda <\lambda_\nu<0}\, \phi_\nu(x)\phi_\nu(y)
\]
Notice that  the $\lambda$-numbers in (x) stay
away from zero. Hence
function $\rho_N$
vanishes  in a neighborhood of zero.
The spectral theorem applied to symmetric Hilbert-Schmidt operators entails that
\[
\mathcal K(h)(y)=
\int_{-\infty}^\infty\, \frac{1}{\lambda}\cdot \frac{d}{d\lambda}\,
\rho(x,y;\lambda)\cdot h(y)\,  dy
\]
hold for each $h\in \mathcal H$.

\medskip

\noindent
{\bf{The $\Omega$-kernel.}}
If $h\in \mathcal H$ we have an expansion 

\[
h=\sum\, a_k\cdot\phi_k+h^*
\] 
where $h^*$ is $|perp$ to the subspace of
$\mathcal H$ generated by the eigenfunctions
and the reader should check that
 \[
\sqrt{\sum\, |a_k|^2}\leq ||h||_2 
\]
Apply (x) to a pair
$h,g$ in $L^2[0,1]$. Then the reader should check that
\[
 \bigl|\iint_\square\, \rho(x,y;\lambda)\cdot h(x)g(y)\, dxdy\bigr|\leq
 ||h||_2\cdot ||g||_2\tag{xx}
 \] 
hold for each $\lambda$ which may be taken to be positive or negative.
For each $\lambda$ we  set
\[
 \Omega(x,y;\lambda)=\int_a^x\int_a^y\, \rho(s,t;\lambda)\, dsdt
\]
 \medskip

\noindent
{\bf{Exercise.}}
Conclude from (xx)
that the function
\[
(x,y)\mapsto \Omega(x,y;\lambda)
\]
is  Hšlder continuous of order $1/2$.
More precisely, for each
$\lambda$ and every pair
$x_1<x_2$ and $y_1<y_2$ one has
\[
|\Omega(x_2,y_2;\lambda) -\Omega(x_1,y_1;\lambda)|
\leq \sqrt{(x_2-x_1)(y_2-y_1)}
\]
A crucial point is that (e.1) holds for all Hilbert-Schmidt kernels, i.e. independent
of the size of
the Hilbert-Schmidt norms.
\medskip

\noindent
{\bf{The $\psi$-functions.}}
With $\lambda$ and $0<x\leq 1$
kept fixed we set
\[
\psi(y;\lambda)=\int_0^x\, \rho(s,y;\lambda)\, ds
\]
We have the characteristic 
function $\chi(x)$ defined as one on $[0,x_*]$ and zero if
$x>x_*$.
Considered as a vector in $\mathcal H$ one has an expansion
\[
\chi(x)=
\sum\, a_k\phi_k(x)+\chi_*\quad\colon\,
a_k=\int_0^{x_*}\,\phi_k(s)\, ds
\]
At the same time the construction of the $\rho$-function
entails that
\[
\psi(y;\lambda)=\sum_*\, \int_0^{x_*}\,\phi_k(s)\cdot \phi_k(y)
\] 
with the sum restricited over those  $k$ for which
$0<\lambda_k<\lambda$.
Bessel's inequality gives
\[
\int_0^1\, \psi(y;\lambda)^2\, dy\leq
\bigl(\sum_*\, \int_0^{x_*}\,\phi_k(s)\bigr)^2
\]
In the last term we have taken a restricted sum which is majorsised by
the sum over all $k$ which again by Bessel's inequality is majorised by
the $L^2$-integral of $|chi$, i.e by $x^2$.
Hnece one has
the inequality
\[
\int_0^1\, \psi(y;\lambda)^2\, dy\leq x\quad\colon 0<x\leq 1
\]
\medskip

\noindent
{\bf{Exercise.}}
More generally, let
$E$ be a sum of disjoint intervals on the $x$-interval and put
\[ 
\psi_E(y;\lambda)=\int_E\, \rho(x,y;\lambda)\,dx
\]
Show that
\[
\int_0^1\, \psi_E(y;\lambda)^2\, dy\leq |E|_1
\]
where the last term is the Lebesgue measure of $E$.

\medskip

\noindent
{\bf{Weak limits.}}
Let us first notice that
the contruction of the $\psi$-function means that
\[
\frac{\partial \Omega(x,y;\lambda)}{\partial y}=
\psi_x(y;\lambda)
\]
So (xx) entails that
the Hšlder contionius $\Omega$-function has a partial $y$-derivative in
the sense of distributions which belongs to $L^2$ which moreover
is absolutely continuu as a fuinction of $x$ since
(xx) is constucted as a primitive function in the sense of
Lebesgue.
It follows that one also has
\[
\frac{\partial}{\partial x}(\frac{\partial \Omega(x,y;\lambda)}{\partial y})=
\rho(x,y;\lambda)
\]
\medskip


\noindent
Let us then consider a sequence of
Hilbert-Schmidt kernels $\{K_n\}$ and to
each of them we get the spectral function
$\rho_n(x,y;\lambda)$.
Now $\{\Omega_n(x,y;\lambda)$
is an equi-contonuous family of functions on
$\square$.
So by the Arzela-Ascli theorem
we find a subsequence which converges uniformly to a 
limit function
$\Omega_*(x,y;\lambda)$ for each fixed $\lambda$.
From (*)   $\Omega$ is again uniformly Hšlder continuous.
Moreover, the uniform bound for the
$L^2$-norms of $y\mapsto \psi_x(y;\lambda)$ entail that
the partial $y$-erivatives of $\Omega_*$ yield $L^2$-functions
which are absoutely continuous with respect to $x$. So there exists
an almost everywhere defined limit function
\[
\rho_*(x,y;\lambda)=
\frac{\partial}{\partial x}(\frac{\partial \Omega_*(x,y;\lambda)}{\partial y})
\]
for which the inequality (xx) holds.



\newpage







and
its first order partial derivatives are $L^2$-functions. Moreover, after the passage to
the limit one still
has Bessel's inequality which entails that
\[
\int_{-\infty}^\infty\, 
\frac{d}{d\lambda}\int_0^1 h(x)\cdot \bigl(\frac{\partial}{\partial x}
\int_0^1\, \frac{\partial\Omega(x,y;\lambda)}{\partial y}\cdot h(y))\,dy\bigr )\, dx
\leq \int_0^1\, h(x)^2\, dx
\]
for every $h\in L^2[0,1]$.



\newpage






In the monograph [Carelan 1923]
the condition (*) is imposed while (**) need not be valid.
Then we encounter an unbounded operator.
But notice that if
$u|in\mathcal H$ then (*9 and the CuachySchwarz inequality entails that
the functions
\[ 
y\mapsto K(x,y)u(y)
\] 
are absolutely integrable in Lebegue's sense 
for all $x$ outside the nullset $\mathcal N$ above.
Hence it makes sense to refer to $L^2$-functions $\phi$ on $[0,1]$
which
satisfy an eigenvalue equation
\[
\phi(x)= \lambda\cdot \int_0^1\, K(x,y)\phi(y)\, dy\tag{1}
\]
where $\lambda$ is a compkex number.
one is also led to consider the integral equation
\[
\phi(x)= \lambda\cdot \int_0^1\, K(x,y)\phi(y)\, dy+f(x)\tag{2}
\]
where $f\in\mathcal H$ is given and one seeks $\phi$.
It turns out that if $\mathfrak{Im}(\lambda)\neq 0$,
then the  inhomogenous equation 
(2) has at least one solution. 
Next,  consider the equation (1).
Let $\rho(\lambda)$ denote the number of linearly independent 
solution in (1). Carelan proived that
 the  $\rho$-function is constant 
when  $\lambda$ varies in
${\bf{C}}\setminus {\bf{R}}$.
Follwing Carelan one says that the kernel $(x,y)$ gives an operator $\mathcal K$ of Class I if
the $\rho$-function is zero. It means that
(2) has unique solutions
for every pair $\lambda,f)$
when $\lambda$ are non-real.
\medskip


\noindent
{\bf{A limit process.}}
Let $\{G_n(x,y)\}$ be a sequece of
symmetric kernel functions which are bounded in Hilbert's sense and
approximate $K$ in the sense that
\[
\lim_{n\to \infty} \int_0^1\, |K(x,y)-G_n(x,y)|^2\, dy=0
\]
for all $x$ outside
a null set. Fix some non-real $\lambda$.
Hilbert's theory entials that if
$f(x)$ is a continuous function, in general complex-valued, then
we find unqiue continuous functions $\{\phi_n\}$
which satisfy the integral equations
\[
\phi_n(x)= \lambda\cdot \int_0^1\, G_n(x,y)\phi(y)\, dy\tag{1}
\]
For a fixed $x$ we consider the complex numbers
$\{phi_n(x)\}$.
Now there exists the set $Z(x)$ of all cluster points, i.e.
a complex number
$z$ belongs to $Z(x)$ if there exists some
sequence $1\leq n_1<n_2<\ldots$ such that
\[
 z=\lim_{k\to\infty}\, \phi_{n_k}(x)
\]
\medskip

\noindent
{\bf{Theorem.}} \emph{For every approximating sequence $\{G_n\}$ as above
the sets $Z(x)$ are either reduced to points or circles in
the complex plane. Moreover, each $Z(x)$ is reduced to a siungleton set
when $\mathcal K$ is of class I.}
\medskip

\noindent
{\bf{Remark.}}
The result below was discovered by Weyl for some special unbounded operators
which arise during the study of second order
differential equations. See ¤ for a comment-.
If $\mathcal K$  is of Class I then
the theorem sbove shows that
each pair of a on-real $\lambda$
and some $f\in\mathcal H$ gives
a unique function $\phi(x)$
which satsfies (2) and
it can be found via a pointwise limit of solutions
$\{\phi_n\}$ to the equations (xx). In this sense the limit process
is robust because one can emply an arbitrary approximating
sequence $\{G_n\}$ under the sole condition that (xx) holds.
This already indficartes that the Case I leads to
a "consistent theory" even if $\mathcal K$ is unbounded.
To make this precise Carleman constructed a unique spectral function
when Case I holds.
More preciely, if
$K(x,y)$ is symmetric and 
Case I holds, then there exists a unique function
$\rho(x,y;\lambda)$ defined for
$(x,y)\in\square$ and every real $\lambda$ such that
\[
\mathcal K(h)(x)=\int_{-\infty}^\infty\, 
\,\frac{1}{\lambda}\cdot\frac{d}{d\lambda} \,
\int_0^1\, \theta(x,y;\lambda)\,h(y)\, dy
\] 
for all
$L^2$-functions $h$.
Concerning the spectral $\theta$-function, Carleman proved that  it
enjoys the same properties as Hilbert's spectral function for bounded 
operators.


\medskip

\noindent
{\bf{Remark.}}
For each fixed $\lambda>0$
one has a bounded self-adjoint operator
on $\mathcal H$ defined by
\[ 
\Theta_\lambda(h)(x)=\int_0^1\, \theta(x,y;\lambda)\,h(y)\, dy 
\]
Moreover, the operator-valued function
$\lambda\mapsto \Theta_\lambda$ has bounded variation over
each intervalÊ$\{a\leq \lambda\leq b\}$
when $0<a<b$.
It means that there exists a constant $C=C(a,b]$ such that
\[
\max\, \sum_{k=0}^M\, ||\Theta_{\lambda_{k+1}}-\Theta_{\lambda_k}||\leq C
\] 
for all partitions
$a=\lambda_0<\lambda_1<\ldots \lambda_{M+1}=b$ and
we have taken operator norms of the differences
$\Theta_{\lambda_{k+1}}-\Theta_{\lambda_k}$ in the sum above.
These bounded variations entail that one can compute the integrals in the right hand side
via the usual method  by Borel and Stieltjes.
\bigskip


\noindent
{\bf{The construction of  spectral functions.}}
When case I holds one constructs the $\rho$-function via a 
robust limit process.
Following [ibid:Chapitre 4] we expose this in ¤ xx.
The strategy is to
regard an approximating sequence $\{G_n\}$ of
Hilbert-Schmidt operator, i.e.
\[
 \iint_\square \, G_N(x,y)^2 \, dxdy<\infty
\]
hold for each $N$.
In this case $\{G_N\}$ are compact opertors.
With $N$ fixed
we get
a discrete sequence of non-zero real numbers
$\{\lambda\nu\}$
which are arragned with increasing avbsolute values and
an orthonormal  family of eigenfunctions $\{\phi_\nu^{(n)}\}$
where
\[
 G_N(\phi_\nu^{(N)})= \lambda\\nu\cdot \phi_\nu^{(N)}
 \] 
hold for each $\nu$.
Of course, the eigenvalues also depend on
$N$.
If $\lambda>0$ we set
\[
\rho_N(x,y;\lambda)=\sum_{0<\lambda_\nu<\lambda}\, \phi_\nu(x)\phi_\nu(y)
\]
\[
\rho_N(x,y;-\lambda)\sum_{-\lambda <\lambda_\nu<0}\, \phi_\nu(x)\phi_\nu(y)
\]
let us notice that for each fixed $n$, the $\lambda$-numbers in (x) stay
away from zero, i.e. there is a constant $c_N>0$ such that
$|\lambda_\nu\geq c_N$. So the function $\rho_N$
vanishes  in a neighborhood of zero.
The spectral theorem applied to symmetric Hilbert-Schmidt operators entails that
\[
\int_{-\infty}^\infty\, \frac{1}{\lambda}\cdot \frac{d}{d\lambda}\,
\rho_N(x,y;\lambda)\cdot h(y)\,  dy
\]
\medskip

\noindent
{\bf{The $\Omega$-kernels.}}
For each $N$ we introduce the function
\[
 \Omega_N(x,y;\lambda)=\int_a^x\int_a^y\, \rho_N(s,t;-\lambda)\, dsdt
\]
Let us notice that Bessel's inequality entails that
\[
 \bigl|\iint_\square\, \rho_N(x,y;\lambda)\cdot h(x)g(y)\, dxdy\bigr|\leq
 ||h||_2|cdot ||g|7_2
 \] 
 for each pair $h,g$ in $L^2[0,1]$.
 \medskip

\noindent
{\bf{Exercise.}}
Conclude from the above
that the variation of $\Omega$
over $[0,x]\times [0,y]$ is bounfed above by
\[
\sqrt{x\cdot y}
\] 
for every pair $0\leq x,y\leq 1$.
In partcular the functions
\[
(x,y)\mapsto \Omega(x,y;\lambda)
\]
are uniformly Hšlder continuous of order $1/2$
in $x$ and $y$ respectively.
\medskip


\noindent
Using the inequalities above
we elave it to the reader to check that there exists
at least one subsequence $\{N_k\}$ such that
the functions $\{\Omega_{N_k}(x,y;\lambda)$
converges uniformly with respect toÊ$x$ and $y$
while $\lambda$ stays in a bounded interval.
When Case I holds one proves that the limit is independent of the subsequence, i.e.
there exists a limit function
\[
\Omega(x,y;\lambda)=\lim_{N\to\infty}\,  
\Omega_N(x,y;\lambda)
\]
From the above the $\omega$-function is again uniformly Hšlder continuous
and
its first order partial derivatives are $L^2$-functions. Moreover, after the passage to
the limit one still
has Bessel's inequality which entails that
\[
\int_{-\infty}^\infty\, 
\frac{d}{d\lambda}\int_0^1 h(x)\cdot \bigl(\frac{\partial}{\partial x}
\int_0^1\, \frac{\partial\Omega(x,y;\lambda)}{\partial y}\cdot h(y))\,dy\bigr )\, dx
\leq \int_0^1\, h(x)^2\, dx
\]
for every $h\in L^2[0,1]$.
\medskip

\noindent
{\bf{Definition.}}
\emph{A Case 1 kernel $K(x,y)$ is closed if equality holds in (*).}
\medskip

\noindent
{\bf{Theorem.}} \emph{A Case I kernel $K(x,y)$ for which 
the equation}
\[ 
\int_0^1\, K(x,y)\cdot \phi(y)\ dy=0
 \] 
 \emph{has no non-zero $L^2$-solution $\phi$ is closed.}
\medskip

\noindent
{\bf{A representation  formula.}}
When (*) hols we can apply to to $h+g$ for every pair of
$L^2$-functiuons anbd since
the Hilbert space $L^2[0,1]$ is self-dual it follows that
for each $f\in L^2[0,1]$ one has the equality
\[
f(x)=\frac{d}{dx}\  
\int_{-\infty}^\infty\, 
\frac{d}{d\lambda}
\int_0^1\, \frac{\partial\Omega(x,y;\lambda)}{\partial y}\cdot f(y))\,dy
\]
almost everywhere with respect to $x$ on $[0,1]$.




{\bf{Remark.}} 
The 
formula (**) shows that it often is important to decide when a Case I kernel
is closed.
Theorem xx gives such a sufficent condition. However, it can
be extended to a quite geneeral result
where one for  can relax the passage to the limit via
suitable linear operators.
The reader may consult   [ibid; page 139-143]
for details. Here we are content to announce the conlsisive result ehich appear
in
[ibid;: page 142].
\medskip

\noindent
{\bf{The $\mathcal L$-family.}}
Let $\xi$ dentoe a paramter which in general depends on several variables, or
represents points in a manifold or  vectors in a normed linear space.
To each $\xi$ we are given  a linear operator
\[ 
L(\xi)\colon f\mapsto L(\xi)(f)
\]
from functions $f(x)$ on $[0,1]$ to new functions on $[0,1]$.
The linear map is weakly continuous, i.e. if
$\{f_\nu\}$ is a sequence in $L^2[0,1]$ which converges weakly to a init function $f$
in $L^2[0,1]$ then
\[ 
\lim L(\xi,f_\nu)\overset{w}\to L(\xi)(f)
\]
Next,
we are given $K(x,y)$ and
the second  condition for $L$ to be in  $\mathcal L$ is that
for each
pair  $\xi$ and $ 0\leq y\leq 1$ there exists
a constant $\gamma(\xi,y)$ which is independent of $\delta$ so that
\[
|L(\xi)(K_\delta(\cdot,y))(x)\leq  \gamma(\xi;y)
\]
where $K_\delta(x,y)$ is the truncated kernel function from (xx)
and in the left hand side we have applied $L(\xi$ to
the function $x\mapsto K_\delta(x,y)$ for each fixed $y$.
Moreover, we have
\[ 
\lim_{\delta\to 0}\, L(\xi)(K(\cdot,y))(x)\overset{w}\to 
\lim_{\delta\to 0}\, L(\xi)(K_\delta(\cdot,y))(x)
\]
where the convergence again holds weakly for
$L2$-functions on $[0,1]$.
Funally the equality below holds for every
$L^2$-function $\phi$:
\[
xxxx
\]








 
 













\bigskip

\centerline{\bf{Symmetric integral operators.}}
\bigskip


\noindent
Consider the domain $\square=\{0\leq x\leq 1\}\times\{0\leq y\leq 1\}$
in ${\bf{R}}^2$.
Let $K(x,y)$ be a real-vaued and Lebesgue mesure function on
$\square$ such that
the integrals
\[ 
\int_0^1\, K(x,y)^2\, dy<\infty
\]
for all $x$ outside a null-set on $[0,1]$.
In addition $K$ is symmetric,  i.e.$K(x,y)= K(y,x)$.
The $K$-kernel is bounded in Hilbert's sens if there exists a constant
$C$ such that
\[ 
\iint_\square\, K(x,y) u(x)u(y)\, dxdy\leq C^2\cdot\int_0^1\, u(x)^2\, dx
\]
for each $u\in L^2[0,1]$.
In the text-book |emph{Intyergralxxx}Ê[xxxx 1904],
Hilbert proved that
the linear operator on 
$L^2[0,1]$ defined by
\[ 
\mathcal K(u)(x)=\int_0^1\, K(x,y)u(y) dy
\]
is bounded and its operator norm is majorsied by $C$-Moreover
the spectrum is real and contained in $[-C,C]$ and
just as for symmetric real matrices
there exists a spectral resolution.
More precisely, set $\mathcal H= L^2[0,1]$.
Then there exists a
map
from $\mathcal H\times\mathcal H$
to the space of Riesz measures supported by
$[-C,C]$ which to every pair $u$ and $v$ in
$\mathcal H$ assigns a Riesz measure $\mu_{\{u,v\}}$
and $\mathcal K$ is recovered by the equation:
\[
\langle \mathcal K(u),v\rangle=\int_{-C}^C\,  t\cdot d\mu_{\{u,v\}}(t)
\]
where the left hand side
is the inner product
on the complex Hilbert space defined by
\[
\iint\, \mathcal K(u)(x)\cdot \overline{v}(x)\,dx
\]
In the monograph [Carelan 1923]
the condition (*) is imposed while (**) need not be valid.
Then we encounter an unbounded operator.
But notice that if
$u|in\mathcal H$ then (*9 and the CuachySchwarz inequality entails that
the functions
\[ 
y\mapsto K(x,y)u(y)
\] 
are absolutely integrable in Lebegue's sense 
for all $x$ outside the nullset $\mathcal N$ above.
Hence it makes sense to refer to $L^2$-functions $\phi$ on $[0,1]$
which
satisfy an eigenvalue equation
\[
\phi(x)= \lambda\cdot \int_0^1\, K(x,y)\phi(y)\, dy\tag{1}
\]
where $\lambda$ is a compkex number.
one is also led to consider the integral equation
\[
\phi(x)= \lambda\cdot \int_0^1\, K(x,y)\phi(y)\, dy+f(x)\tag{2}
\]
where $f\in\mathcal H$ is given and one seeks $\phi$.
It turns out that if $\mathfrak{Im}(\lambda)\neq 0$,
then the  inhomogenous equation 
(2) has at least one solution. 
Next,  consider the equation (1).
Let $\rho(\lambda)$ denote the number of linearly independent 
solution in (1). Carelan proived that
 the  $\rho$-function is constant 
when  $\lambda$ varies in
${\bf{C}}\setminus {\bf{R}}$.
Follwing Carelan one says that the kernel $(x,y)$ gives an operator $\mathcal K$ of Class I if
the $\rho$-function is zero. It means that
(2) has unique solutions
for every pair $\lambda,f)$
when $\lambda$ are non-real.
\medskip


\noindent
{\bf{A limit process.}}
Let $\{G_n(x,y)\}$ be a sequece of
symmetric kernel functions which are bounded in Hilbert's sense and
approximate $K$ in the sense that
\[
\lim_{n\to \infty} \int_0^1\, |K(x,y)-G_n(x,y)|^2\, dy=0
\]
for all $x$ outside
a null set. Fix some non-real $\lambda$.
Hilbert's theory entials that if
$f(x)$ is a continuous function, in general complex-valued, then
we find unqiue continuous functions $\{\phi_n\}$
which satisfy the integral equations
\[
\phi_n(x)= \lambda\cdot \int_0^1\, G_n(x,y)\phi(y)\, dy\tag{1}
\]
For a fixed $x$ we consider the complex numbers
$\{phi_n(x)\}$.
Now there exists the set $Z(x)$ of all cluster points, i.e.
a complex number
$z$ belongs to $Z(x)$ if there exists some
sequence $1\leq n_1<n_2<\ldots$ such that
\[
 z=\lim_{k\to\infty}\, \phi_{n_k}(x)
\]
\medskip

\noindent
{\bf{Theorem.}} \emph{For every approximating sequence $\{G_n\}$ as above
the sets $Z(x)$ are either reduced to points or circles in
the complex plane. Moreover, each $Z(x)$ is reduced to a siungleton set
when $\mathcal K$ is of class I.}
\medskip

\noindent
{\bf{Remark.}}
The result below was discovered by Weyl for some special unbounded operators
which arise during the study of second order
differential equations. See ¤ for a comment-.
If $\mathcal K$  is of Class I then
the theorem sbove shows that
each pair of a on-real $\lambda$
and some $f\in\mathcal H$ gives
a unique function $\phi(x)$
which satsfies (2) and
it can be found via a pointwise limit of solutions
$\{\phi_n\}$ to the equations (xx). In this sense the limit process
is robust because one can emply an arbitrary approximating
sequence $\{G_n\}$ under the sole condition that (xx) holds.
This already indficartes that the Case I leads to
a "consistent theory" even if $\mathcal K$ is unbounded.
To make this precise Carleman constructed a unique spectral function
when Case I holds.
More preciely, if
$K(x,y)$ is symmetric and 
Case I holds, then there exists a unique function
$\rho(x,y;\lambda)$ defined for
$(x,y)\in\square$ and every real $\lambda$ such that
\[
\mathcal K(h)(x)=\int_{-\infty}^\infty\, 
\,\frac{1}{\lambda}\cdot\frac{d}{d\lambda} \,
\int_0^1\, \theta(x,y;\lambda)\,h(y)\, dy
\] 
for all
$L^2$-functions $h$.
Concerning the spectral $\theta$-function, Carleman proved that  it
enjoys the same properties as Hilbert's spectral function for bounded 
operators.


\medskip

\noindent
{\bf{Remark.}}
For each fixed $\lambda>0$
one has a bounded self-adjoint operator
on $\mathcal H$ defined by
\[ 
\Theta_\lambda(h)(x)=\int_0^1\, \theta(x,y;\lambda)\,h(y)\, dy 
\]
Moreover, the operator-valued function
$\lambda\mapsto \Theta_\lambda$ has bounded variation over
each intervalÊ$\{a\leq \lambda\leq b\}$
when $0<a<b$.
It means that there exists a constant $C=C(a,b]$ such that
\[
\max\, \sum_{k=0}^M\, ||\Theta_{\lambda_{k+1}}-\Theta_{\lambda_k}||\leq C
\] 
for all partitions
$a=\lambda_0<\lambda_1<\ldots \lambda_{M+1}=b$ and
we have taken operator norms of the differences
$\Theta_{\lambda_{k+1}}-\Theta_{\lambda_k}$ in the sum above.
These bounded variations entail that one can compute the integrals in the right hand side
via the usual method  by Borel and Stieltjes.
\bigskip


\noindent
{\bf{The construction of  spectral functions.}}
When case I holds one constructs the $\rho$-function via a 
robust limit process.
Following [ibid:Chapitre 4] we expose this in ¤ xx.
The strategy is to
regard an approximating sequence $\{G_n\}$ of
Hilbert-Schmidt operator, i.e.
\[
 \iint_\square \, G_N(x,y)^2 \, dxdy<\infty
\]
hold for each $N$.
In this case $\{G_N\}$ are compact opertors.
With $N$ fixed
we get
a discrete sequence of non-zero real numbers
$\{\lambda\nu\}$
which are arragned with increasing avbsolute values and
an orthonormal  family of eigenfunctions $\{\phi_\nu^{(n)}\}$
where
\[
 G_N(\phi_\nu^{(N)})= \lambda\\nu\cdot \phi_\nu^{(N)}
 \] 
hold for each $\nu$.
Of course, the eigenvalues also depend on
$N$.
If $\lambda>0$ we set
\[
\rho_N(x,y;\lambda)=\sum_{0<\lambda_\nu<\lambda}\, \phi_\nu(x)\phi_\nu(y)
\]
\[
\rho_N(x,y;-\lambda)\sum_{-\lambda <\lambda_\nu<0}\, \phi_\nu(x)\phi_\nu(y)
\]
let us notice that for each fixed $n$, the $\lambda$-numbers in (x) stay
away from zero, i.e. there is a constant $c_N>0$ such that
$|\lambda_\nu\geq c_N$. So the function $\rho_N$
vanishes  in a neighborhood of zero.
The spectral theorem applied to symmetric Hilbert-Schmidt operators entails that
\[
\int_{-\infty}^\infty\, \frac{1}{\lambda}\cdot \frac{d}{d\lambda}\,
\rho_N(x,y;\lambda)\cdot h(y)\,  dy
\]
\medskip

\noindent
{\bf{The $\Omega$-kernels.}}
For each $N$ we introduce the function
\[
 \Omega_N(x,y;\lambda)=\int_a^x\int_a^y\, \rho_N(s,t;-\lambda)\, dsdt
\]
Let us notice that Bessel's inequality entails that
\[
 \bigl|\iint_\square\, \rho_N(x,y;\lambda)\cdot h(x)g(y)\, dxdy\bigr|\leq
 ||h||_2|cdot ||g|7_2
 \] 
 for each pair $h,g$ in $L^2[0,1]$.
 \medskip

\noindent
{\bf{Exercise.}}
Conclude from the above
that the variation of $\Omega$
over $[0,x]\times [0,y]$ is bounfed above by
\[
\sqrt{x\cdot y}
\] 
for every pair $0\leq x,y\leq 1$.
In partcular the functions
\[
(x,y)\mapsto \Omega(x,y;\lambda)
\]
are uniformly Hšlder continuous of order $1/2$
in $x$ and $y$ respectively.
\medskip


\noindent
Using the inequalities above
we elave it to the reader to check that there exists
at least one subsequence $\{N_k\}$ such that
the functions $\{\Omega_{N_k}(x,y;\lambda)$
converges uniformly with respect toÊ$x$ and $y$
while $\lambda$ stays in a bounded interval.
When Case I holds one proves that the limit is independent of the subsequence, i.e.
there exists a limit function
\[
\Omega(x,y;\lambda)=\lim_{N\to\infty}\,  
\Omega_N(x,y;\lambda)
\]
From the above the $\omega$-function is again uniformly Hšlder continuous
and
its first order partial derivatives are $L^2$-functions. Moreover, after the passage to
the limit one still
has Bessel's inequality which entails that
\[
\int_{-\infty}^\infty\, 
\frac{d}{d\lambda}\int_0^1 h(x)\cdot \bigl(\frac{\partial}{\partial x}
\int_0^1\, \frac{\partial\Omega(x,y;\lambda)}{\partial y}\cdot h(y))\,dy\bigr )\, dx
\leq \int_0^1\, h(x)^2\, dx
\]
for every $h\in L^2[0,1]$.
\medskip

\noindent
{\bf{Definition.}}
\emph{A Case 1 kernel $K(x,y)$ is closed if equality holds in (*).}
\medskip

\noindent
{\bf{Theorem.}} \emph{A Case I kernel $K(x,y)$ for which 
the equation}
\[ 
\int_0^1\, K(x,y)\cdot \phi(y)\ dy=0
 \] 
 \emph{has no non-zero $L^2$-solution $\phi$ is closed.}
\medskip

\noindent
{\bf{A representation  formula.}}
When (*) hols we can apply to to $h+g$ for every pair of
$L^2$-functiuons anbd since
the Hilbert space $L^2[0,1]$ is self-dual it follows that
for each $f\in L^2[0,1]$ one has the equality
\[
f(x)=\frac{d}{dx}\  
\int_{-\infty}^\infty\, 
\frac{d}{d\lambda}
\int_0^1\, \frac{\partial\Omega(x,y;\lambda)}{\partial y}\cdot f(y))\,dy
\]
almost everywhere with respect to $x$ on $[0,1]$.




{\bf{Remark.}} 
The 
formula (**) shows that it often is important to decide when a Case I kernel
is closed.
Theorem xx gives such a sufficent condition. However, it can
be extended to a quite geneeral result
where one for  can relax the passage to the limit via
suitable linear operators.
The reader may consult   [ibid; page 139-143]
for details. Here we are content to announce the conlsisive result ehich appear
in
[ibid;: page 142].
\medskip

\noindent
{\bf{The $\mathcal L$-family.}}
Let $\xi$ dentoe a paramter which in general depends on several variables, or
represents points in a manifold or  vectors in a normed linear space.
To each $\xi$ we are given  a linear operator
\[ 
L(\xi)\colon f\mapsto L(\xi)(f)
\]
from functions $f(x)$ on $[0,1]$ to new functions on $[0,1]$.
The linear map is weakly continuous, i.e. if
$\{f_\nu\}$ is a sequence in $L^2[0,1]$ which converges weakly to a init function $f$
in $L^2[0,1]$ then
\[ 
\lim L(\xi,f_\nu)\overset{w}\to L(\xi)(f)
\]
Next,
we are given $K(x,y)$ and
the second  condition for $L$ to be in  $\mathcal L$ is that
for each
pair  $\xi$ and $ 0\leq y\leq 1$ there exists
a constant $\gamma(\xi,y)$ which is independent of $\delta$ so that
\[
|L(\xi)(K_\delta(\cdot,y))(x)\leq  \gamma(\xi;y)
\]
where $K_\delta(x,y)$ is the truncated kernel function from (xx)
and in the left hand side we have applied $L(\xi$ to
the function $x\mapsto K_\delta(x,y)$ for each fixed $y$.
Moreover, we have
\[ 
\lim_{\delta\to 0}\, L(\xi)(K(\cdot,y))(x)\overset{w}\to 
\lim_{\delta\to 0}\, L(\xi)(K_\delta(\cdot,y))(x)
\]
where the convergence again holds weakly for
$L2$-functions on $[0,1]$.
Funally the equality below holds for every
$L^2$-function $\phi$:
\[
xxxx
\]








 
 
































































 



























\newpage







\centerline {\bf{11.5 Stones theorem.}}


\bigskip


\noindent

\noindent
{\bf{11.3.2 Unitary semi-groups.}}
Specialize the situation above to the case when
$B$ is a Hilbert space $\mathcal H$ and
$\{U_t\}$ are unitary
operators.
Set $T=\xi_*$ so that
\[ 
B(x)=
\lim_{t \to 0}\, \frac{U_tx-x}{t}\quad\colon\quad x\in\mathcal D(T)
\]
If  $x,y$ is a pair in $\mathcal D(B)$ we get
\[
\langle Bx,y\rangle=
\lim_{t \to 0}\, \langle \frac{U_tx- x}{t},U_ty\rangle
=\lim_{t \to 0}\, \frac{1}{t}\cdot \bigl( \langle U_tx,U_ty)\rangle-
 \langle x,U_ty)\rangle\,\bigr)
 \]
Since $U_t$ are unitary we have
$\langle U_tx,U_ty)\rangle=\langle x,y)\rangle$ for each$Êt$ and conclude that
the last term above  is equal to
\[
\lim_{t \to 0}\, \frac{\langle x,y-U_ty\rangle}{t}=-\langle x,By\rangle
\]

\noindent
Hence $B$ is anti-symmetric, i.e.
\[
\langle Bx,y\rangle=-
\langle x,By\rangle
\]
Set $A=i\cdot T$ which gives
\[
\langle Ax,y\rangle=
i\cdot \langle Tx,y\rangle=
-i\cdot \langle x,Ty\rangle=-\langle x,i\cdot Ty\rangle=
\langle x,Ay\rangle
\]
where  we used that the inner product is hermitian.
Hence $A$ is a densely defined and symmetric operator.
\medskip

\noindent
{\bf{Theorem.}}
\emph{A is self-adjoint, i.e. one has the equality $\mathcal D(A)= \mathcal D(A^*)$.}
\medskip

\noindent
\emph{Proof.}
It suffices to prove that
$\mathcal D(T)=|mathcal D(T^*)$. To btain this we take a vector
$y$ be a vector in $\mathcal D(T^*)$ which by definition gives
a constant $C(y)$ such that
\[
|\langle Tx,y\rangle||\leq C(y)\cdot ||x||
\quad\colon\, x\in\mathcal D(T)\tag{i}
\]
Now
$\langle Tx,y\rangle$ is equal to
\[
\lim_{t\to 0}\,\langle\frac{U_tx-x}{t}, U_ty\rangle
=-\lim_{t\to 0}\,\langle x,\frac{U_ty-y}{t}\rangle\tag{ii}
\]
So if
\[
 \eta_t=frac{U_ty-y}{t}
\]
it follows that there exists
\[
\lim_{t\to 0}\, ,\langle x,\eta_t\rangle=-\langle Tx,y\rangle
\]
for each $x\in\mathcal D(T)$.





\bigskip



The adjoint operators
$\{U^*_t\}$   give another  unitary semi-group with
infinitesmal generator  
$A_*$ where
\[ 
A_* (x)=
\lim_{t \to 0}\, \frac{U^*_tx-x}{t}\quad\colon\quad x\in\mathcal D(A_*)
\]
Since $U_t$ is the inverse operator of $U^*_t$ for each $t$ we get
\[
A_*(x)= \lim_{t\to 0}\, U_t(A_* x)= \lim_{t \to 0}\, \frac{x-U_t x}{t}\quad\colon\quad x\in\mathcal D(A_*)\tag{i}
\]
\medskip

\noindent
From (i) we see that
$\mathcal D(A)\subset
\mathcal D(A_*)$ and
one has the equation
\[
A_* x)=-A(x)\quad\colon\quad x\in\mathcal D(A_*)\tag{ii}
\]
Reversing the role the reader can check the equality
\[
\mathcal D(A)=
\mathcal D(A_*)\tag{iii}
\]
Next, let $x,y$ be a pair in $\mathcal D(A)$.
Then
\[
\langle Ax,y\rangle=
\lim_{t \to 0}\, \langle \frac{U_tx- x}{t},U_ty\rangle
=\lim_{t \to 0}\, \frac{1}{t}\cdot \bigl( \langle U_tx,U_ty)\rangle-
 \langle x,U_ty)\rangle\,\bigr)
 \]
Since $U_t$ are unitary we have
$\langle U_tx,U_ty)\rangle=\langle x,y)\rangle$ for each$Êt$ and conclude that
the last term in (xx) is equal to
\[
\lim_{t \to 0}\, \frac{\langle x,y-U_ty\rangle}{t}=-\langle x,Ay\rangle
\]

\noindent
Hence $A$ is anti-symmetric.
Set
\[ 
B=iA
\]

\bigskip









{\bf{Exercise.}}
Show that (i)  gives the equality
$\mathcal D(A_*)=\mathcal D(A)$ and that:
\[
 A_*(x)=-A(x)\quad\colon\quad x\in\mathcal D(A)
 \]
 
 

\[
 \langle Bx,y\rangle= -\langle x,By\rangle\quad\colon\quad
x,y\in\mathcal D(B)
\]


\noindent {\bf{Exercise.}}
Conclude from the above that the operator $iB$ is self-adjoint.

\medskip


\noindent
{\bf{Remark.}} The equations  above constitute Stones theorem
which was established in 1930.
It has a wide range of applications. See for example von Neumann's article \emph{Zur Operatorenmethode in der klassischen Mekanik}
and Maeda's article \emph{Unitary equivalence of self-adjoint
operators and constant motion}
from 1936.
\bigskip


\noindent
{\bf{11.3.3 A converse construction.}}
Let $A$ be a densely defined self-adjoint operator.
From ¤ 9.B  $A$ is approximated by a sequence of bounded
self-adjoint operators
$\{A_N\}$.
With $N$ kept fixed
we get a semi-group of unitary operators where
\[ 
U^{(N)}_t= e^{-it A_N}
\]
The reader may verify that the inifintesmal generator becomes
$-iA_N$.
Next, for each $x\in \mathcal D(A)$
and every fixed $t$ there exists the limit
\[ 
\lim_{N\to \infty}\, U^{(N)}_t(x)
\]
{\bf{Remark.}} This gives a densely defined linear operator $U_t$
whose operator norm is bounded by one which therefore
extends uniquely to 
a bounded linear operator $\mathcal H$ and it is clear
that this  extension 
becomes a unitary operator. In this way
we arrive at a semi-group $\{U_t\}$
and one verifies that its infinitesmal generator is equal to $-iA$.
However, it is not clear that
$\{U_t\}$ is strongly continuous and one may ask for 
conditions 
on the given self-adjoint operator $A$ which ensures that  $\{U_t\}$
is strongly continuous.








\newpage

\centerline{\bf{11.8 Transition probability functions.}}
\medskip


\noindent
Let $(\Omega,\mathcal B,\mu)$
be a probability space as defined in ¤ XX.
Consider a real-valued function
$P$ defined on the product set 
$\Omega\times\mathcal B$ with 
the following two properties:
\[ 
t\mapsto P(t,E)
\quad\text{is a bounded measurable function for each}\,\,\, E\in\mathcal B\tag{*}
\]
\[
E\mapsto P(t,E)
\quad\text{is a probability measure
for each fixed }\,\,\, t\in\Omega\tag{**}
\]
When (*-**) hold one refers to $P$ as a transition function.
Given  $P$ we define inductively the sequence $\{P^{(n)}\}$
by:
\[ 
P^{(n+1)}(t,E)=\int_\Omega\, P^{(n)}(s)\cdot dP(s,E)
\]
It is clear that 
$\{P^{(n)}\}$ yield  new transition  functions.
The probabilistic interpretation is that
one has a Markov chain
with independent increments.
More precisely,
if 
$E$ and $S$ are two sets in
$\mathcal B$ 
and 
$n\geq 1$.
then
\[
\int_S\, P^{(n)}(t;E)\cdot d\mu(t)
\]
is the probability that
the random walk which starts at some  point in $E$
has arrived to some  point in  $S$ after $n$ steps.
One says that the given
transition function $P$ yields a stationary
Markov process if
there exists a finite family of disjoint
subets $E_1,\ldots,E_m$ in $\mathcal B$
and some $\alpha<1$ and a constant $M$
such that the following hold:
First, for each $1\leq i\leq m$ one has:
\[ 
P(t,E_i)= 1 \quad\colon t\in E_i\tag{1}
\]
Next, if $\Delta= \Omega\setminus E_1\cup\ldots\cup E_m$ then
\[ 
\sup_{t\in S}\, P^{(n)}(t,\Delta)\leq M\cdot \alpha^n
\quad\colon \, n=1,2,\ldots\tag{2}
\]
\medskip

\noindent
{\bf{Remark.}}
One refers to $\Delta$ as the disippative part of $\Omega$
and $\{E_i\}$ are  the ergodic kernels of the process.
Since $\alpha<1$  in (2) the probabilistic  interpretation
of (2) is that as $n$ increase then
the disippative part is evacuated
with high probability while the Markov process 
stays inside every ergodic kernel.

\medskip


\centerline {\bf{11.9 The Kakutani-Yosida theorem.}}
\medskip

\noindent
A sufficient condition for a
Markov  process to be  stationary is as follows:
Denote by $X$ the Banach space of
complex-valued and bounded
$\mathcal B$-measurable
functions on the real $s$-line.
Now $P$ gives a 
linear operator $T$ which sends $f\in X$
to
the function
\[ 
T(f)(x)= \int_\Omega\ f(s)\cdot dPx,ds)
\]
Kakutani and Yosida  proved that 
the Markov process is stationary 
if there exists a 
triple $\alpha,n,K$
where $K$ is a compact
operator on $X$, $0<\alpha<1$ and $n$ some positive integer such that
the operator  norm
\[ 
||T+K||\leq \alpha\tag{*}
\]

\noindent
The proof relies upon some  general facts 
about
linear operators on Banach spaces.
First one identifies the Banach space
$X$ with
the space of continuous complex-valued functions on
the compact Hausdorff space $S$ given by the maximal ideal space of the
commutative Banach algebra $X$.
Then $T$ is a postive linear operator on $C^0(S)$ and in ¤ 11.xx    we
shall prove  that (*)
implies that
 the spectrum of $T$ consists of a finite set of points on
 the unit circle together with a compact subset
 in a disc of radius $<1$.
 Moreover, for each
 isolated point $e^{i\theta}\in \sigma(T)$
 the corresponding eigenspace is finite dimensional.
 Each  such eigenvalue corresponds to an ergodic kernel and when
the eigenspace has dimension $m\geq 2$, the
 corresponding ergodic kernel, say $E_1$, has a further decomposition into
 pairwise disjoint subsets $e_1,\ldots,e_m$
where  the process moves in a cyclic manner between these
sets, i.e. 
\[
\int_{e_{i+1}}\, P(s,e_i)=1\quad 
\colon 1\leq  i\leq m
\quad\text{where we put}\quad
 e_{m+1}= e_1
 \]
 

\medskip



\centerline {\bf{11.9.1 Some results about linear operators.}}
\medskip


\noindent 
The  Kakutani-Yosida  theorem  follows from 
some results about linear operators which we begin to expose.
Let $X$ be a Banach space and
denote by $\mathcal F$
the family of bounded liner operators  $T$ on $X$  
such that
\[ 
\lim_{n\to\infty}\, \frac{1}{n}\cdot x^*(T^nx)=0\tag{*}
\] 
hold for all pairs $x\in X$ and $x^*\in X^*$.
\medskip


\noindent
{\bf{1. Exercise.}} Apply the Banach-Steinhaus theorem to show that
if $T\in\mathcal F$ then
there exists a constant $M$ such that the operator norms satisfy
\[ 
||T^n||\leq M\cdot n\quad\colon\, n=1,2,\ldots
\]


\noindent
Since the $n$:th root of $M\cdot n$ tends to one as $n\to+\infty$, 
the spectral radius formula entails that
the spectrum $\sigma(T)$ is contained in the closed unit disc
of the complex $\lambda$-plane.
So in the exterior disc
$\{|\lambda|>1\}$ there exists the
the resolvent 
\[ 
R_T(\lambda)= (\lambda\cdot E-T)^{-1}
\]



\noindent{\bf{2. The class $\mathcal F_*$}}.
It consists of those $T$ in $\mathcal F$
for which there exists
some $\alpha<1$ such that
$R_T(\lambda)$ extends to a meromorphic function in
the exterior disc
$\{|\lambda|>\alpha\}$.
Since $\sigma(T)\subset
\{|\lambda|\leq 1\}$
it follows that when
$T\in\mathcal F_*$ then
the set of points in $\sigma(T)$ which belongs to the unit circle
in the complex $\lambda$-plane is empty or finite and
after we can always choose $\alpha<1$ such that
\[ 
\sigma(T)\cap \{\alpha<|\lambda|<1\}= \emptyset
\]

\medskip

\noindent
{\bf{3. Proposition.}}
\emph{If $T\in \mathcal F_*$ andÊ$e^{i\theta}\in \sigma(T)$
for some $\theta$, then
$R_T(\lambda)$ 
has a simple pole at $e^{i\theta}$.}
 \medskip

\noindent
\emph{Proof.}
Replacing
$T$ by  $e^{-i\theta}\cdot T$
it suffices to prove the result when
$e^{i\theta}=1$.
If $R_T(\lambda)$ has a pole of order $\geq 2$
at $\lambda=1 $ we know from ¤ XX that there exists $x\in X$ such that
\[ 
Tx\neq  x\quad\text{and}\quad
(E-T)^2\,x=0\tag{i}
\]
The last equation means that $T^2+x=2Tx$ and an induction
over $n$ gives
\[
\frac{1}{n} \cdot T^n x=\frac{1}{n}\cdot x+(E-T)x\tag{ii}
\]
Since $T\in\mathcal F$ we have
\[ 
\lim_{n\to\infty}\, \frac{1}{n}\cdot x^*( T^n x)=0
\quad\colon\, \forall\\, x^*\in X^*\tag{iii}
\] 
Then (ii) entails that $x^*(E-T)(x)=0$. Since
$x^*$ is arbitrary we get  $Tx=x$ which contradicts (i) and hence
the pole is simple.
\medskip

\noindent
{\bf{4. Theorem.}}
\emph{Let $T\in \mathcal F$ be such that   there exists a compact
operator $K$ where 
$||T+K||<1$. Then $T\in \mathcal F_*$ and
for every $e^{i\theta}\in\sigma(T)$
the eigenspace
$E_T(\theta)= \{ x\in X\,\colon\, Tx= e^{i\theta} x\}$ is finite dimensional.}

\medskip

\noindent
\emph{Proof.}
Set $S=T+K$ and for a complex number
$\lambda$ we write 
$\lambda\cdot E-T= \lambda\cdot E-T-K+K$. Outside $\sigma(S)$ we get
\[
R_S(\lambda)(\lambda\cdot E-T)=
E+R_S(\lambda)\cdot K\tag{i}
\]
The Neumann series for large absolute values
$|\lambda|$
applied to $R_S(\lambda)$ gives some $\rho>0$ and
\[
( E+R_S(\lambda)\cdot K)^{-1}= E+R_S(\lambda)\cdot K\dot
( E+R_S(\lambda)\cdot K)^{-1}\quad\colon\,|\lambda|>\rho\tag{ii}
\]

\noindent
Next, when
$|\lambda|$ is large
we notice that
(i) gives
\[
R_T(\lambda)=  ( E+R_S(\lambda)\cdot K)^{-1}\cdot R_S(\lambda)\tag{iii}
\]
Together with (ii) we obtain
\[
R_T(\lambda)=R_S(\lambda)+ 
R_S(\lambda)\cdot 
( E+R_S(\lambda)\cdot K)^{-1}\cdot R_S(\lambda)\tag{iv}
\]
Set $\alpha=||S||$ which by assumption is $<1$.
Now
$R_S(\lambda)$ is analytic in the exterior disc
$\{\lambda|>\alpha\}$ so in this exterior disc
$R_\lambda(T)$ differs from  the analytic function $R_\lambda(S)$ by
\[
\lambda\mapsto R_S(\lambda)\cdot 
( E+R_S(\lambda)\cdot K)^{-1}\cdot R_S(\lambda)\tag{v}
\]
Here $K$ is a compact operator so 
the
result in ¤ XX entails that this function extends to
be meromorphic  in $\{|\lambda|>\alpha\}$.
There remains to prove that
eigenspaces at spectral points on the unit circle are finite dimensional.
To prove this we use (iv). 
Let $e^{i\theta}\in\sigma(T)$. By Proposition 3 it is a simple pole
so we have a Laurent series expansion
\[
R_T(e^{i\theta}+z)= \frac{A_{-1}}{z}+ A_0+ A_1z+\ldots
\]
By the general results from ¤¤ there remains to show that 
$A_{-1}$ has finite dimensional range.
To see this we apply (iv) which gives the equation
\[
R_S(e^{i\theta}+z)+
R_S(e^{i\theta}+z)\cdot(E+
R_S(e^{i\theta}+z)\cdot K)^{-1}\cdot R_S(e^{i\theta}+z)
\]
To simplify notations we set $B(z)=R_S(e^{i\theta}+z)$
which by assumption is analytic in a neighborhood of $z=0$.
Moreover, the operator $B(0)$ is invertible.
So now one has
\[
 \frac{A_{-1}}{z}+ A_0+ A_1z+\ldots=
 B(z)+B(z)(E+B(z)\cdot K)^{-1}B(z)
 \]
Since $B(0)$ is invertible  we  have a Laurent series expansion
\[
(E+B(z)\cdot K)^{-1}= \frac{A^*_{-1}}{z}+A_0^*+A_1^*z+\ldots
\]
and identying the coefficient of $z^{-1}$ gives
\[
A_{-1}= B(0)A^*_{-1}B(0)
\]
Next, from (xx) one has

\[
E=(E+B(z)\cdot K)(\frac{A^*_{-1}}{z}+A_0^*+A_1^*z+\ldots)\implies
(E +B(0)\cdot K)A^*_{-1}=0
\]
Here $B(0)\cdot K$ is a compact operator and hence  Fredholm theory 
implies that $A^*_{-1}$ has a finite dimensional range. Since
$B(0)$ is invertible the same is true for $A_{-1}$ which finishes the proof
of 
Theorem 4.




\medskip

\noindent
{\bf{5. Proposition}}.
\emph{
If
$T\in\mathcal F$ is  such that
$T^N\in\mathcal F_*$ for some integer $N\geq 2$.
Then 
$T\in\mathcal F_*$.}
\medskip

\noindent
\emph{Proof.}
We have the algebraic equation
\[ 
\lambda^N\cdot E -T^N=(\lambda\cdot E-T)(
\lambda^{N-1}\cdot E+
\lambda^{N-2}\cdot T+\ldots+T^{N_1})
\]
It follows that
\[ R_T(\lambda)=
(\lambda^{N-1}\cdot E+
\lambda^{N-2}\cdot T+\ldots+T^{N_1})\cdot R_{T^N}(\lambda^N)
\]
Since $T^NB\in\mathcal F_*$ there exists
$\alpha<1$ such that
\[
\lambda\mapsto  R_{T^N}(\lambda^N)
\]
extends to be meromorphic in
$\{|\lambda|>\alpha\}$. At the same time
$(\lambda^{N-1}\cdot E+
\lambda^{N-2}\cdot T+\ldots+T^{N_1})$
is  a polynomial
and hence
$R_T(\lambda)$ also extends to be meromorphic
in this
exterior disc so that 
$T\in\mathcal F_*$.
\medskip

\centerline{\emph{A result about  positive operators.}}

\bigskip

\noindent
Let $S$ be a compact Hausdorff
space and $X$ is the Banach space of continuous and
complex-valued functions on $S$.
A linear operator $T$ on $X$ is  positive if
it sends every non-negative and real-valued function $f$ to another  real-valued and
non-negative function.
\medskip

\noindent
{\bf{6. Theorem.}}
\emph{If $T$ is positive and belongs to $\mathcal F_*$
then
each $e^{i\theta}\in \sigma(T)$ is a root of unity.}
\medskip

\noindent
\emph{Proof.}
The hypothesis gives   $f\in C^0(S)$ which is not identically zero and
\[ 
T(f)=e^{i\theta}\cdot f
\]
Multiplying $f$ with a complex scalar we may assume that
the maximum norm on $S$ is one and there exists $s_0\in S$ such that
\[ 
f(s_0)=1
\]
The dual space
$X^*$ consists of complex-valued Riesz measures on $X$.
If $n\geq 1$ we get the
measure
$\mu_n$
such that
the following hold 
for every  $g\in C^0(S)$:
\[
\int_S\, g\cdot d\mu_n=T^n g(s_0)\geq 0
\]
Since $T^n$ is positive
the integrals in the left hand side are
$\geq 0$ when $g$ are real-valued and non-negative. This
entails that
each $\mu_n$ is a real-valued and non-negative measure.
Next, for each $n$ we put
\[ 
A_n=\{e^{-in\theta}\cdot f\neq 1\}=\{\mathfrak{Re}(e^{-in\theta}f)<1\}\tag{6.0}
\]
where the last equality follows since
the sup-norm of $f$ is one.
Now
\[
0=f(s_0)- e^{-in\theta}\cdot T^n f(s_0)
=\int_S\,[1-e^{-in\theta}f(s)]\cdot  d\mu_n(s)\tag{6.1}
\]
Taking real parts we get
\[
0=\int_S\,[1-\mathfrak{Re}(e^{-in\theta}f(s))]\cdot  d\mu_n(s)
\]
By (6.0)  the integrand above
is non-negative and since the whole 
integral is zero it follows that
\[
\mu_n(A_n)= \mu_n(\{\mathfrak{Re}(e^{-in\theta}<1\}=0\tag{6.2}
\]
Hence (6.2) 
$A_n$ is a null set with respect to $\mu_n$.
Suppose now that
there exists a pair $n\neq m$ such that
\[
(S\setminus A_n)\cap (S_m\setminus A_m)\neq \emptyset
\] 
A point $s_*$ in this non-empty intersection
gives
\[
1=e^{in\theta}f(s_*)=e^{im\theta}\cdot f(s_*)\implies
e^{in\theta}=e^{im\theta}
\] 
and hence  $e^{i\theta}$ is a root of unity since
$m-n\neq 0$.
So the proof of Theorem 6.1  is finished if we have established the following

\medskip

\noindent
\emph{Sublemma.}
\emph{The sets $\{S\setminus A_n\}$ cannot be pairwise disjoint.}
\medskip

\noindent
\emph{Proof.}
First,  $f$ has maximum norm
and by the above:
\[ 
\int_S\, f\cdot d\mu_n=e^{in\theta}
\]
Hence the total mass $\mu_n(S)$ is at least one.
Next, 
for each $n\geq 2$ we set
\[
\pi_n=\frac{1}{n}\cdot (\mu_1+\ldots+\mu_n)
\]
Since 
$\mu_n(S)\geq 1$  for each $n$ we get 
$\pi_n(S)\geq 1$. Put
\[
\mathcal A=\bigcap\, A_n
\]
Above we proved that $\mu_n(A_n)=0$ hold for every $n$ which gives
\[ 
\pi_n(\mathcal A)=0\quad\colon\, n=1,2,\ldots\tag{*}
\]
Next, when
the sets $\{S\setminus A_k\}$ 
are pairwise disjoint one has 
the inclusions
\[
S\setminus A_k\subset A_\nu\quad\forall\,\nu\neq k
\]
Keeping $k$ fixed it follows that
$\pi_\nu(S\setminus A_k)=0$ for every $\nu\geq 0$.
So when $n$ is large while $k$ is kept fixed we obtain
\[ 
\pi_n(S\setminus A_k))= \frac{1}{n}\cdot \mu_k(S\setminus A_k))\implies
\lim_{n\to\infty}\, \pi_n(S\setminus A_k))=0
\quad\colon k=1,2,\ldots\tag{**}
\]
At this stage we use the hypothesis that
$T$ belongs to $\mathcal F_*$
which by Proposition XX entails that
the resolvent $R_T(\lambda)$ has at most a simple pole at $\lambda=1$.
With $\epsilon>0$
the Neumann series expansion gives
\[
E+\sum_{k=1}^\infty\,
\frac {T^k}{(1+\epsilon)^k}=
R_T(1+\epsilon))
=\frac{1}{\epsilon} \cdot Q+W(1+\epsilon))
\]
where $W(\lambda)$ is an operator-valued analytic function
in an open disc centered at $\lambda=1$ while $Q$ is a bounded
linear operator on $C^0(S)$.
Keeping $\epsilon>0$ fixed we apply both sides to the identity function
$1_S$ on $S$ and the construction of
the measures $\{\mu_n\}$ gives
\[
1+
\sum_{k=1}^\infty\,
\frac {\mu_k(S)}{(1+\epsilon)^k}=\frac{1}{\epsilon} \cdot Q(1_S)(s_0)+
W(1+\epsilon))(1_S)(s_0)
\]
If $n\geq 2$ is an integer and $\epsilon=\frac{1}{n}$
one gets the inequality
\[
\sum_{k=1}^{k=n}\,
\frac {\mu_k(S)}{(1+\frac{1}{n})^k}\leq
n\cdot |Q(1_S)(s_0)|+|W(1+1/n))(1_S)(s_0)|\leq
n\dot ||Q||+ ||W(1+1/n)||\implies
\]
\[
\frac{1}{n}\cdot\sum_{k=1}^{k=n}\,\mu_k(S)\leq
(1+\frac{1}{n})^n\cdot (||Q||+\frac{ ||W(1+1/n)||}{n}
\]
Since
Neper's constant $e\geq (1+\frac{1}{n})^n$ for every $n$
we find
a constant $C$ which is
independent of $n$ such that
\[
\frac{1}{n}\cdot\sum_{k=1}^{k=n}\,\mu_k(S)\leq C
\]
Hence the sequence $\{\pi_n(S)\}$ is  bounded
and we can pass to a subsequence
which converges weakly to a limit measure $\mu_*$.
For this $\sigma$-additive measure the limit formula in (**) above entails that
\[ 
\mu_*(S\setminus A_k)=0\quad\colon\, k=1,2,\ldots\tag{i}
\]
Moreover, by (*) we also have
\[
\pi_*(\mathcal A)=0\tag{ii}
\]
Now
$S= \mathcal A\cup\, A_k$ so (i-ii) give:
\[ 
\mu_*(S)=0
\]
But this is impossible for at the same time
we have already seen that
$\pi_n(S)\geq 1$ for each $n$ and hence also $\mu_*(S)\geq 1$.









\end{document}













\centerline{\bf{Stone's theorem.}}
\medskip

\noindent
Here follows an
example where unbounded operators appear.
The reader has begun to master unbounded
operators and their spectral properties by learning  the  details which appear
during  
the proof of Stone's theorem below.
Let
$\mathcal H$ be a complex Hilbert space.
A strongly continuous semi-group of unitary operators
is a family
$\{U_t\,\colon t\geq 0\}$
where
each $U_t$ is unitary, i.e. they
preserve the Hermitian inner products:
\[
\langle U_tx,U_ty\rangle=
\langle x,y\rangle
\]
Moreover, $U_0$ is the identity operator $E$ and
$U_t\circ U_s=U_{t+s}$ hold for every pair of non-negative real numbers.
Finally, the strong continuity means that 
\[ 
\lim_{t\to 0}\, ||U_tx-x||=0
\] 
for every $x\in\mathcal H$.
Stone's theorem
asserts that there exists a densely defined and self-adjoint operator
$A$ on $\mathcal H$
which is called the infinitesmal generator. Its domain of defintion $\mathcal D(A)$
is a dense subspace of $\mathcal H$ which consists of vectors $x$ such that
there exists a limit
\[
\lim_{\delta\to 0}\, \frac{U_\delta(x)-x}{\delta}=y
\]
 and when it holds we set
\[ 
A(x)=iy
\] 
where $i$ is the imaginary unit.
The proof that such an inifintesmal generator
exists relies  upon Neumann's calculus in ¤ 0.0.
 Here follow the  crucial steps which 
lead to the construction of  $A$.
\medskip

\noindent
{\bf{The operators $R(\lambda)$.}}
When
$\lambda$ are complex numbers with positive real part
we obtain bounded linear operators
\[
R(\lambda)(x)=\int_0^\infty\, e^{-\lambda t}\cdot U_t(x)\, dt
\]
The integrals exists because of the strong continuity and
the convergence with respect to the norm in $\mathcal H$ is
evident since
$||U_t(x)|||\leq ||x||$ for each fixed vector $x$.
Approximating the integrals by Riemann sums
the bounded linear operator $R(\lambda)$ is found
by the limit equation
\[
R(\lambda)= \lim_{\delta\to 0}\, 
\delta^{-1}\cdot (E-e^{-\delta\lambda}U_\delta)^{-1}\tag{i}
\]
Notice that
$\mathfrak{Re}(\lambda)>0$ implies that
the operator norm
\[
||e^{-\delta\lambda}U_\delta)||= e^{-\mathfrak{Re}(\lambda)}<1
\]
and therefore linear operators
$E-e^{-\delta\lambda}U_\delta)$ are invertible which explains how one
proceeds to the  limit in the right hand side above.
A notable point is that
(i) enable us to describe the compact
spectra of the operators $R(\lambda)$.
Consider for example the case $\lambda=1$.
Since the spectrum of a unitary opertor is contained in
the unit circle it follows that
\[
\sigma(E-e^{-\delta}\cdot U_\delta)\subset
\{z\in{\bf{C}}\,\colon\, |z-1|=e^{-\delta}\}
\]
Next, 
general formulas for spectra of bounded operators
to be explained in ¤xx give
\[
\sigma(\delta^{-1}\cdot (E-e^{-\delta\lambda}U_\delta)^{-1})
\subset\{z\colon \, |z-\frac{\delta}{1-e^{-2\delta}}|=\frac{\delta}{1-e^{-\delta}}\}
\]
Passing to the limit as $\delta\to 0$ it follows that
\[ 
\sigma(R(1))\subset\{z\colon \, |z-1/2|=1/2\}\tag{ii}
\]
\medskip

\noindent
{\bf{The infinitesmal generator.}}
If  $h>0$ and $x\in\mathcal H$ then 
the semi-group equations $U_h\circ U_t= U_{h+t}$ give
\[ 
\frac{U_h-E}{h}\circ R(\lambda)(x)=
h^{-1}\cdot 
\int_0^\infty\, e^{-\lambda t}\cdot (U_{t+h}(x)-U_t(x))\, dt
\]
A variable substitution shows that the last term is equal to
\[
\frac{e^{\lambda h}-1}{h}\cdot 
\int_h^\infty\, e^{-\lambda t}\cdot U_t(x)\, dt-\frac{1}{h}\int_0^h\,
 e^{-\lambda t}\cdot U_t(x)\, dt \tag{iii}
\]
Passing to the limit as $h\to 0$ it is readily seen that
the vectors in (iii) converge in the norm topology on $\mathcal H$
to the vector
\[
\lambda\cdot R(\lambda)(x)-x
\]
The conclusion is that
if $y=R(\lambda)(x)$ then there exists
the limit
\[
\lim_{h\to 0}\, \frac{U_h(y)-y}{h}=
\lambda\cdot R(\lambda)(x)-x\tag{iv}
\]
This suggests that we regard the subspace
$\mathcal H_0$ of $\mathcal H$ which consists of vectors $y$ such that
there exists a limit vector $S(y)$ where
\[
\lim_{h\to 0}\, || \frac{U_h(y)-y}{h}-S(y)||=0
\]
It is clear that  $S\colon \mathcal H_0\to \mathcal H$
is a linear operator
and (iv) entails that
the range of $R(\lambda)$ is contained in
$\mathcal H_0$ when $\mathfrak{Re}(\lambda)>0$.
Moreover 
\[
S\circ R(\lambda)(x)= \lambda\cdot R(\lambda)(x)-x\quad\colon x\in \mathcal H
\tag{v}
\]
We can rewrite  (v)   and get
\[
(\lambda\cdot E-.S)\circ R(\lambda)(x)=x\quad\colon x\in \mathcal H
\]
In ¤ 0.0 we shall learn that this means that
$\{R(\lambda)\}$ appear as resolvent operators to
the densely defined linear operator $S$.
Applying the inclusion (ii) above
and the general result in (0.0.5.1) from Neumann's calculus, it
follows that 
$\sigma(S)$ consists of purely imaginary numbers.
Set
\[
 A=iS
\]
From the above $\sigma(A)\subset\mathfrak{R}$
and in ¤ xx we shall learn that $A$ is a densely defined and self-adjoint
operator which gives the requested  the infinitesmal generator of the
unitary semi-group $\{U_t\}$.


\medskip

\noindent
{\bf{Remark.}}
Stone's theorem has a wide range of applications, especially in ergodic theory.
For applications in quantum mechanics we refer to
the article \emph{xxxx} by J. von Neumann.
Let us also remark that
an analogue of Stone's theorem hold for a strongly continuous semi-group
$\{V_t\}$ satisfying
$V_t^*V_t=E$ for every $t$, but not necessarily
$V_tV_t^*=E$, i.e.  the $V$-operators need not be unitary.
In ¤ xx we also expose a result due to J. von Neumann
about
uniqueness of solutions to
a certain Schršdinger equation which arises via
the 
uncertainty   principle in quantum mechanics.
See also ¤ A:x for a "concrete version" of Stones theorem.
\bigskip



More precisely, in
the unbounded open complement
$U={\bf{R}}^3\setminus\overline{\Omega}$
there exists the symmetric Green's function $G(p,q)$
associated to Neumann's boundary value problem, i.e.
\[ 
G(p,q)= \frac{1}{4\pi\cdot |p-q|}+H(p,q)
\]
where $|p-q|$ is the euclidian distance between
a pair of points$p,q$ in $U$. Moreover,
$q\mapsto H(p,q)$ is harmonic as a function of $q$ for each fixed $p\in U$, and
for each $p\in U$ we have
\[
\frac{\partial G}{\partial n_q}(p,q)=0\quad\colon q\in \partial\Omega
\]
where $n_q$ is the outwards normal derivative.
Now $G$ gives a densely defined
operator on the Hilbert space $L^2(U)$ defined
by
\[
\mathcal G_f(p)= \int_U\, G(p,q)\cdot f(q)\, dq
\]
To be precise, the
volume integrals in the right hand side give
$L^2$-functions of $p$ for a dense subset of $L^2$-functions $f$ in $U$.
We shall learn that this unbounded and
densely defined operator 
has a spectrum in the sense of Neumann which is confined to the
non-negative real line. Moreover, there exists an associated
spectral function $\theta(p,q;\lambda)$
which for each $\lambda>0$ yields a bounded
integral operator on
$L^2(U$:
\[ 
\Theta(\lambda)_f(p) =\int_U\, \theta(p,q;\lambda)\cdot f(q)\, dq
\]
and here
\[
\mathcal G_f(p)= \lim_{\delta\to 0}\, \int_\delta^{1/\delta}\,
\lambda^{-1}\cdot \bigl[\int_U\,  \frac{d}{d\lambda}\theta(p,q;\lambda)\cdot f(q)\, dq
\bigr]\, d\lambda
\]
for those $L^2$-functions $f$ which belong to the domain of
definition of $\mathcal G$.
To learn about this construction and how one employs the spectral function to
fiond 
solutions to an assocaited wave equation can be regarded as 
one of the major goals  for this chapter.
As expected  measure theoretic considerations intervene, i.e.
"abstract functional analysis" is to a large extent
related to measure theory.
In the situation above one
also
considers the total variation of
operator norms for the
$\Theta$-operators, i.e. on a closed interval
$\{a\leq \lambda\leq b\}$ where $0<a<b$ we put
\[ 
\Theta^*[a,b]=
\max\, \sum\, || \Theta(\lambda_{\nu+1})-\Theta(\lambda_\nu)||
\]
with the maximum taken over all partitions 
$a=\lambda_0<\lambda_1<\ldots<\lambda_N=b$
and we have taken a sum of operator norms
for the corresponding difference of
the $\Theta$-operators which are parametrized with respect to $\lambda$.
It turns out that
the operator valued function $\lambda\mapsto \Theta(\lambda)$
is absolutely continuous. It means that for
every $\epsilon>0$ there exists $\delta>0$ such that
\[
\sum\, \Theta^*[a_j.b_j]<\epsilon
\]
for every finite familly of closed and disjoint intervals
$\{[a_j,b_j]\}$ arranged so that $b_j<a_{j+1}$ for each $j$.
To learn the proof which is presented in ¤ xx 
gives the reader a good
insight in spectral theory
since one arrives at a specific result in a concrete situation
which
therefore
consolidates the general  theory.



\noindent
Let $\Omega$ be a bounded open set in
${\bf{R}}^3$ whose boundary is a finite union of closed
surfaces of class $C^1$.
In the unbounded open complement
$U={\bf{R}}^3\setminus\overline{\Omega}$
there exists the symmetric Green's function $G(p,q)$
associated to Neumann's boundary value problem, i.e.
\[ 
G(p,q)= \frac{1}{4\pi\cdot |p-q|}+H(p,q)
\]
where $|p-q|$ is the euclidian distance between
a pair of points$p,q$ in $U$. Moreover,
$q\mapsto H(p,q)$ is harmonic as a function of $q$ for each fixed $p\in U$, and
for each $p\in U$ we have
\[
\frac{\partial G}{\partial n_q}(p,q)=0\quad\colon q\in \partial\Omega
\]
where $n_q$ is the outwards normal derivative.
Now $G$ gives a densely defined
operator on the Hilbert space $L^2(U)$ defined
by
\[
\mathcal G_f(p)= \int_U\, G(p,q)\cdot f(q)\, dq
\]
To be precise, the
volume integrals in the right hand side give
$L^2$-functions of $p$ for a dense subset of $L^2$-functions $f$ in $U$.
We shall learn that this unbounded and
densely defined operator 
has a spectrum in the sense of Neumann which is confined to the
non-negative real line. Moreover, there exists an associated
spectral function $\theta(p,q;\lambda)$
which for each $\lambda>0$ yields a bounded
integral operator on
$L^2(U$:
\[ 
\Theta(\lambda)_f(p) =\int_U\, \theta(p,q;\lambda)\cdot f(q)\, dq
\]
and here
\[
\mathcal G_f(p)= \lim_{\delta\to 0}\, \int_\delta^{1/\delta}\,
\lambda^{-1}\cdot \bigl[\int_U\,  \frac{d}{d\lambda}\theta(p,q;\lambda)\cdot f(q)\, dq
\bigr]\, d\lambda
\]
for those $L^2$-functions $f$ which belong to the domain of
definition of $\mathcal G$.
To learn about this construction and how one employs the spectral function to
fiond 
solutions to an assocaited wave equation can be regarded as 
one of the major goals  for this chapter.
As expected  measure theoretic considerations intervene, i.e.
"abstract functional analysis" is to a large extent
related to measure theory.
In the situation above one
also
considers the total variation of
operator norms for the
$\Theta$-operators, i.e. on a closed interval
$\{a\leq \lambda\leq b\}$ where $0<a<b$ we put
\[ 
\Theta^*[a,b]=
\max\, \sum\, || \Theta(\lambda_{\nu+1})-\Theta(\lambda_\nu)||
\]
with the maximum taken over all partitions 
$a=\lambda_0<\lambda_1<\ldots<\lambda_N=b$
and we have taken a sum of operator norms
for the corresponding difference of
the $\Theta$-operators which are parametrized with respect to $\lambda$.
It turns out that
the operator valued function $\lambda\mapsto \Theta(\lambda)$
is absolutely continuous. It means that for
every $\epsilon>0$ there exists $\delta>0$ such that
\[
\sum\, \Theta^*[a_j.b_j]<\epsilon
\]
for every finite familly of closed and disjoint intervals
$\{[a_j,b_j]\}$ arranged so that $b_j<a_{j+1}$ for each $j$.
To learn the proof which is presented in ¤ xx 
gives the reader a good
insight in spectral theory
since one arrives at a specific result in a concrete situation
which
therefore
consolidates the general  theory.



\noindent
{\bf{Unitary  groups.}}
There exists also a 1-1 correspondence 
exists between the family of self-adjoint operators
and unitary groups of transformations which
are strongly continuous on a dense subspace of
the given Hilbert space $\mathcal H$.
Moreo rpecisley, if $A$ is self-adjoint there exists for
each real number $t$ a unitary transformation $U_t$
such that
\[ 
U_t(x)= e^{itA(x)}
\]
hold
for a dense subspace of the domain of definition of $A$
and since $A$ is self-adnoint one eaily verifies the gruop law:
\[
U_{t+s}= U_t\circ U_s
\]
Conversly, let $\{U_t\}$ be a group of untary transformations
and assume that it is strongly continuos on a dense subapace 
$\mathcal H_*$
of
$\mathcal H$, i.e. for vectors in this subspace
one has
\[ 
\lim_{t\to 0}\, ||U_t(x)-x||=0
\]
When this holds one constructs opeprtator-valued Stieltjes integrals
for complex numbers in the open right half-plane. More precisely, 
each vector $x\in\mathcal H_*$ there exists the Stieltjes' integral 
\[
R(\lambda)(x)= \int_0^\infty\, e^{-\lambda t}\cdot U_t(x)\, dt
\]
One verifies that
\[
||R(\lambda(x)||\leq e^{-\mathfrak{Re}(\lambda)}\cdot ||x||\quad
\colon x\in\mathcal H_*
\]
It follows that $R(\lambda)$ extends in 
a unique fashion to a bounded linear operator.
We can specialize $\lambda$ and get the bounded operator
\[ 
R=R(1)
\]
Since $\{U_t\}$ is a unitary group an easy 
calculation to be given in
¤ xx entails that $R$ is normal
and one has  the inclusion
\[ 
\sigma(R)\subset
\]

















{\bf{Spectral functions.}}













In ¤ xx we show that under the sole condition 
(1), there exist a distinguished family of 
spectral functions $\theta(x,y;\lambda)$
assoc’ated toÊthe symmetric function $K(x,y)$.
For each spectral function,
$(x,y)\mapsto  \theta(x,y;\lambda)$ is 
symmetric and yields a bounded linear operarator on
$L^2[0,1]$ denoted by $\Theta(\lambda)$. Moreover,
the operator valued function
$\lambda\mapsto \Theta(\lambda)$ has a finite total  
variation with respect to $\lambda$ over
every bounded interval  the real $\lambda$-line
and the unbounded operator $\mathcal K$
is recaptured  from the spectral function
by the integral formula
\[ 
\mathcal K(h)= \int_{-\infty}^\infty\,
\frac{1}{\lambda}\cdot 
\frac{d\Theta} {\lambda}(h)
\] 
for every $L^2$-function $h$ in the domain of definition for $K$.
The precise calculus and constructions of operator valued integrals above
are exposed in ¤ xx. But let us briefly recall their construction.
Let $K$ satisfy (1).
Now we can approximate $\mathcal K$ in a weak sense by
sequences of Hilbert-Schmidt operators, i.e. linear operators on $L^2[0,1]$
of the form
\[ 
\mathcal G(f)(x)= \int_0^1\, G(x,y)\cdot f(y)\,dy
\] 
where $G$ are real-valued symmetric kernel functions such that
\[
\iint\, G(x,y)^2\, dxdy<\infty
\]
A sequece $\{G_n\}$ approximates $K$ weakly if
\[
\lim_{n\to \infty}\, \int_0^1\, |K(x,y)-G_n(x,y)|^2\, dy=0
\] 
hold outside a null set on the $x$-interval.
Next, if $\{G_n\}$ is an approximates $K$ as above one
constructs spectral $\theta$-functions as follows:
First, each fixed $G_n$ is compact and has therefore a discrete spectrum.
This gives  an
orthonormal family $\{\phi^{(n)}_\nu\}$
in $L^2[0,1$ and to each $n$ a non-zero real number
$\lambda^{(n)}_\nu$ such that
\[
\mathcal G_n(\phi)= \lambda^{(n)}_\nu\cdot \phi^{(n)}_\nu
\]
The $\lambda$-numbers are enumerated
with increasing absolute values.
For each $n$ and every $\lambda>0$ we set
\[
\rho_n(x,y;\lambda)= \sum_{0<\lambda_\nu^{(n)}<\lambda}\,
\phi^{(n)}_\nu(x)\phi^{(n)}_\nu(y)
\]
\[
\rho_n(x,y;-\lambda)= \sum_{-\lambda <\lambda_\nu^{(n)}<0}\,
\phi^{(n)}_\nu(x)\phi^{(n)}_\nu(y)
\]
Applying Bessel inequalities several times, it is proved in [ibid:Chapter 1-2]
that
one can always find subsequences
$\{\rho_{n_1},\rho_{n_2}\,\ldots\}$
which converge to a spectral $\rho$-function associated toÊ$K$
via the limit equation (xx).
So  every $K$-kernel which 
satisfies (1) has a non-empty family of associated
spectral 
$\rho$-functions.
The size of this $\rho$-family is
governed by Weyl's limit circles
which arise as follows: Let $f$ be a non-zero real-valued continuous
on $[0,1]$.
If $\{G_n\}$  approximates $K$
we find for each $n$ a unique function
$\phi_n$ which solves the integral equation
\[
\phi_n(x)=i\cdot \int_0^1\, G_n(x,y)\cdot \phi_n(y)\, dy+f(x)
\]
Here $\phi_n$ is automatically continuous.
Keeping $f$ and $x$ fixed
we get a sequence of complex numbers
$\{\phi_n(x)\}$.
Let $Z(x)$ be the closed set of cluster points of its closure.
It turns out that
the union of all such cluster sets 
as we take sequences $\{G_n\}$ as above,
is  a closed 
subset of ${\bf{C}}$
 which either is reduced to a single point or  equal to  a circle.
In the latter case the circle is denoted by by
$W_K(f:x)$ and called a Weyl circle associated to the triple $K,f,x$.
When Weyl circles appear it truns out that there exist many disctinct
spectral functions of $K$.

 
 






\medskip


\noindent
{\bf{The self-adjoint case.}}
Following [Carleman 1923]
one says that the 
$K(x,y)$ is of Class I if 
(*) has non non-trivial solution. In this case no Weyl circles appear and 
$\mathcal K$ is self-adjoint with  a unique spectral function.
Another fundamental result from  [Carleman 1923] asserts that
if
$K$ is such that
there does not exist a non-zero $\phi\in L^2[0,1]$ such that
$\mathcal K(\phi)=0$, then
every $L^2$-function $f$ on $[0,1]$ can be represented as a limit 
\[ 
f(x)=
\lim _{\ell\to +\infty}\, \int_{-\ell}^\ell\,
\frac{d}{d\lambda}(\int_0^1\, \theta(x,y;\lambda)\cdot h(y)\, dy)
\]
where  equality hold 
for all $x$ outside a nullset in $[0,1]$.
\medskip


\noindent
{\bf{Remark.}} The restriction to the unit interval is harmless, i.e
by a change of variables the theory holds verbatim for
$L^2$-spaces over domains in
${\bf{R}}^n$ for every positive integer $n$, and of course
also on manifolds equipped with some volume density.
Except for some minor technical points one can also extend
the whole study to cover case where infinite number of variables appear.
But to save notations we often prefer to work
with kernel functions on
intervals in ${\bf{R}}$.





Let us finally recall that
An alternative
proof of Carleman's  spectral theorem for unbounded operators on
Hilbert spaces was later given by  
J. von Neumann in     the article \emph{Eigenwerttheorie Hermitescher 
Funktionaloperatoren}[xxx: 1929].
 from 1929.
A merit in von Neumann's account 
is that 
some measure theoretic technicalities  
in  Carleman's proof
can be omitted 
and his proof  
covers the case for operators 
on
non-separable Hilbert spaces and von Neumann's 
more abstract version of the spectral theorem is presented in ¤ 9.
On the other hand 
it  is often necessary to establish
formulas of a measure theoretic character in order to apply
the spectral theorem. An example
is  Carleman's  solution to the 
Bohr-Schršdinger equation above which will be  exposed in ¤ xx.


\centerline {\bf{H. Neumann's resolvent operators}}.
\medskip

\noindent
The less experienced reader might prefer to start  with   ¤ 1-6
whose contents   "start from scratch".
However, it  is  essential to become
familiar with unbounded linear operators " as soon as possible"
since they
arise naturally in many applications.
So already
in
¤ 0.0 we introduce
Neumann's resolvent operators and the construction of spectral sets of
densely defined but unbounded linear operators.
Here analytic function theory plays a crucial role such as in the proof 
of 
Theorem 0.0.6.3
which enable us 
to construct bounded  linear operators  from
a given
densely defined  operator.
Let us also remark that Neumann's calculus for densely defined linear operators
extends 
several  results about 
matrices. 
For example, let $T\colon X\to X$ be a densely defined linear operator
on a Banach space
with a closed graph in $X\times X$ and  suppose also that the adjoint $T^*$  has 
a dense domain of definition. In ¤ xx   we  prove
the equality
\[
 \sigma(T)= \sigma(T^*)
\] 
under the extra assumption that the Banach space $X$ is reflexive.
Here $\sigma(T)$ is the spectrum of $T$ which will be constructed in
¤ 0.0. for each  densely defined and closed linear operator
on a Banach space.
In the case when
$\lambda_0$ is an isolated point in the spectrum of $T$
we  prove in ¤ 0.0.6 that there exists 
a bounded linear map $E(\lambda_0)$ which
commutes with $T$
and the spectrum of the operator $E(\lambda_0)T$
is reduced to the singleton set $\{\lambda_0\}$.
We remark that 
this extends the
classical constructions of
Cayley matrices in linear algebra.
\medskip

\noindent
{\bf{The operator $i\cdot \frac{d}{dx}$.}}
A "first lesson" about densely defined
linear operators
occurs 
when we consider
the densely defined derivation operator
$A=i\cdot \frac{d}{dx}$
acting on the Hilbert space of square integrable functions on
the real $x$-line. 
Using Fourier transforms  and
Parseval's equality we  prove in ¤ xx that
$A$ is self-adjoint.
The resder should keep this example in mind while the general theory
is exposed.
Another densely defined operator $B$ on
$L^2({\bf{R}})$
is given by multiplication with $-ix$. Here the domain of definition for
$B$ consists of $L^2$-functions $f(x)$ such that
$x\cdot f(x)$ also is square integrable.
The chain rule for derivatives 
and the equality $i^2=-1$
show that
if $f(x)$ is a test-function on
${\bf{R}}$ then
\[
A\circ B(f)-
B\circ A(f)= f\tag{*}
\]
One refers to (*) as Weyl's identity.
The equation (*)
appears in relation to the uncertainty principle in
quantum
mechanics.
in 1926 Schršdinger
discovered that when the pair above
are identified with
infinitesmal generators of unitary groups
on $L^2){\bf{R}})$, then one arrives at
an irreducible representation.
In ¤xx we expose von Neumann's 
uniqueness theorem which gives an affirmative answer
to a 
question which was  originally posed by Schršdinger.
Namely, 
that  every pair of densely defined
self-adjoint operators which satisfy (*) 
and as  infinitesmal generators of unitary groups
give riose to an irreducible
representation of
$L^2){\bf{R}})$, is equal to the special pair above up to a
unitary equivalence.



















\newpage

NEW TITLE FOR SCATTERED MATERIAL

\noindent
{\bf{A product formula.}}
Let us announce a theorem  due to Nagy and F. Riesz whose proof relies upon
results  in ¤ 8-9
and will be  proved in ¤ 11.xx.
Let $\mathcal H$ be a Hilbert space
and $T\colon\mathcal H\to \mathcal H$
a densely defined and closed linear operator.
Then we shall  prove that the adjoint $T^*$ also is densely
defined, as well as the composed operator $T T^*$.
Moreover, $TT^*$ is self-adjoint with a spectrum confined to the
non-negative real axis and we shall learn that 
there exists the densely defined self-adjoint operator
\[
A=\sqrt{TT^*}
\]
where  $A^2=TT^*$.
Next, a  bounded linear operator $P$ is called a partial isometry attached to $A$
if the norms
\[
||P(Ax)||= ||A(x)||\quad\colon x\in\mathcal D(A)
\]
while the $P$-kernel is the orthogonal complement 
to the range of $A$, i.e. if $y$ is a vector such that
$\langle Ax,y\rangle =0\colon\,x\in\mathcal D(A)$, then $P(y)=0$.
\medskip

\noindent
{\bf{Theorem.}}
\emph{For every densely defined and closed operator $T$
there exists a partial isometry $P$ attached to
$\sqrt{TT^*}$ such that}
\[
T(x)=P\circ\sqrt{TT^*}(x)
\quad\colon x\in\mathcal D(TT^*)
\]

\noindent
\emph{Summing up}, results as above
illustrate  the aim of this chapter 
which apart from presenting basic facts about normed
vector spaces  pays considerable attention to densely defined operators
on Hilbert spaces.






\medskip

\noindent
{\bf{Hellinger's integrals.}}
One 
often needs specific results from calculus, especially 
about  integrals where one encounters
both those of Lebesgue and  
integrals in the sense of Borel and Stieltjes.
Let us recall some 
constructions
and results due to Hellinger's in  
\emph{Die Orthogonalinvarianten quadratischer Formen von unendlichen
vielen Variabeln} [Dissertation. Gšttingen 1907].
Here 
Stieltjes' constructions are extended  to second order differences.
Fix a bounded and closed
interval  $J=[a,b]$.
For each subintervall $\ell=[\alpha,\beta]$
and  a continuous real-valued function $\phi $ on $J$ we set
\[
D_\ell(\phi )= \phi (\beta)-\phi(\alpha)
\]
Next,let
$g$ and $h$ be a pair of
continuous and non-decreasing 
functions which are kept fixed from now on.
Denote by $\mathcal S$ the class of
continuous functions $f$   such that
\[ 
(D_\ell(f))^2\leq D_\ell(g)\cdot D_\ell(h)\tag{*}
\] 
hold for
every subinterval $\ell$ as above.
Next, take some arbitrary  $u\in C^0(J)$
while $f\in\mathcal S$.
If $\{[\alpha_\nu,\beta_\nu]\}$ is a partition of
$[a,b]$ into an increasing sequence of intervals, i.e
$\alpha_{\nu+1}= \beta_\nu$ hold, 
we
define the upper respectively the lower sums

\[
S^*=\sum\, \max_{x\in\ell_\nu}u(x)\cdot \frac{(D_{\ell_\nu}(f))^2}{D_{\ell_\nu}(g)}\cdot \ell_\nu
\] 
\[
S_*= \sum\, \min_{x\in\ell_\nu}u(x)\cdot \frac{(D_{\ell_\nu}(f))^2}{D_{\ell_\nu}(g)}\cdot \ell_\nu
\] 
where $\ell_\nu=\beta_\nu-\alpha_\nu$.
If $\omega_u(\delta)=\max\{ |u(x)-u(x')|\,\colon |x-x'|\leq\delta\}$
is the modulos of continuity for $u$
we see that (*) gives
\[
S^*-S_*\leq \omega_u(\delta)\cdot (h(b)-h(a))|quad\colon
\delta= \max_\nu\, \beta_\nu-\alpha_\nu
\] 
From this the reader can deduce that
there exists a limit when the partitions get fine, i.e. the $\delta$-numbers
tend to zero in above. The result is Hellinger's integral
denoted by
\[ 
\int_a^b\, \frac{df^2}{dg}\tag{1}
\]
\medskip

\noindent
In a similar fashion the reader can verify that if $f_1,f_2$ is a oaiin 
$\mathcal S$, then there exists the integral
\[ 
\int_a^b\, \frac{df_1df_2}{dg}\tag{2}
\]
Next, with $ f\in\mathcal S$ 
and $u\in   C^0(J)$ we put
\[
S^*=\sum\, \max_{x\in\ell_\nu}u(x)\cdot D_{\ell_\nu}(f)\cdot \ell_\nu
\] 
\[
S_*= \sum\, \min_{x\in\ell_\nu}u(x)\cdot (D_{\ell_\nu}(f))\cdot\ell_\nu
\] 
Now
\[
|S^*-S_*|\leq \omega_u(\delta)\cdot
\sum\, |D_{\ell_\nu}(f)|\cdot \ell_\nu
\]
Using (*) and the Cauchy Schwartz inequality we see that
the last sum is majorised by
\[
\omega_u(\delta)\cdot \sqrt{(g(b)-g(a))(h(b)-h(a)}
\]
From this the reader can conclude that
there exists a welldefined integral
\[ 
\int_a^b\, u\cdot df\tag{3}
\]

\noindent
{\bf{Exercise.}}
Let $\phi$ and $\psi$ be some pair of continuous functions
while $f_1$ and $f-2$ belong to $\mathcal S$.
Put
\[ 
\Phi(x)=\int_a^x\, \phi\cdot df\quad\colon\,
\Psi(x)=\int_a^x\, \psi\cdot df
\]
Show the equality below for every $u\in C^0(J)$:
\[ 
\int_a^b\, u\cdot \frac{dF_1dF_2}{dg}=
\int_a^b\, u\phi\psi\cdot \frac{df_1df_2}{dg}
\]

\noindent
{\bf{Exercise.}}
Let $u$ and $v$ be a pair in $C^0(J)$ while $f_1,f_2$ belong to $\mathcal S$.
Show the equality
\[
\int_a^b\, v(x)\cdot (\int_a^x\, u\cdot \frac{df_1df_2}{dg})\, dx
\]























\medskip



\medskip



\centerline {\bf{Picard's equation.}}
\medskip


\noindent
Picard's   article \emph{Sur une Žquation intgrales singuliŽre} [Ann. Ecole, Norm. Sup.1911)
is devoted to the
integral equation
\[ 
\phi(x)=\lambda\cdot
 \int_{-\infty}^\infty\,e^{-|x-y|})\cdot\phi(y)\, dy+f(x)\tag{*}
\]
where $\lambda$ is a complex parameter.
To begin with one seeks solutions $\phi$ when
$f(x)$ is a $C^2$-function
on the real line with compact support and
requests that $\phi$ belongs to 
$L^2({\bf{R}})$.
By analyzing solutions to 
certain second order differential equations, Picard proved
that (*) has unique
$L^2$-solutions $\phi$ for each $f$ as above
when
the complex parameter
$\lambda$ stays
outside the real interval $[1/2,+\infty)$.
Moreover, the solution is given by
\[
\phi(x)= f(x)+\frac{\lambda}{\sqrt{1-2\lambda}}\cdot
 \int_{-\infty}^\infty\,e^{-|x-y|})\cdot f(y)\, dy
\]
where a single valued branch of
$\sqrt{1-2\lambda}$ in ${\bf{C}}\setminus [1/2,\infty)$
appears.
Let us express this via operators.
Picard's integral operator is defined by
\[ 
\mathcal K(f)(x)=\int_{-\infty}^\infty\, e^{-|x-y|}\cdot f(y)\, dy
\]
It is densely defined on the Hilbert space
$L^2(\bf{R}]$ and
Picard's uniqueness above  entails that when
$\lambda$ is not real, then
there does not exist a non-zero $L^2$-function $\phi$ such that
\[
\phi+\lambda\cdot \mathcal K(\phi)=0
\]
General results about densely defined and symmetric operators on
Hilbert spaces which are exposed later on, imply that
$\mathcal K$ is self-adjoint.


 and from the above
it follows that
if $E$ is the identity operator,. then
$E-\lambda\cdot \mathcal K$ is invertible in Neumann's sense
if $\lambda$ stays outside $[1/2,+\infty)$.









Starting from this, Carleman applied the general theory for symmetric and densely
defined operators and proved that
the densely defined operator $\mathcal K$ defined by
\[ 
\mathcal K_g(x)=\int_{-\infty}^\infty\, e^{-|x-y|}\cdot g(y)\, dy
\]
belongs to the favourable class I which means that
it is self-adjoint and 
the spectrum is $[1/2,+\infty)$.



we shall also give explicit formulas for the spectral function of Picard's operator.
More generally one can consider
densely defined operators
of the form
\[
\mathcal K_g(x)=
\int_{-\infty}^\infty\,\bigl(H_1(|x-y|)+ H_2(x+y)\bigr)\cdot g(y)\, dy
\]
where $H_1$ and $H_2$ is a pair of real-valued functions
such that the $L^2$-integrals
\[
\int_0^\infty\, H_1(s)^2\, ds\quad\colon
\int_{-\infty}^\infty\,H_2(s)^2\, ds
\] 
both exist.
Again one proves that
$\mathcal K$ is self-adjoint with a spectrum
confined to the real line.
See ¤ xx for further details., Let us remark
that
$\mathcal K$-operators as above
gives a gateway to analyse integral operators with kewrnel functions
\[ 
K(x,y)=\frac{1}{x}\Omega(\frac{x}{y})
\]
which are defined when
$x$ and $y$ both a $>0$ and
\[
\Omega(t)= t^{-1}\cdot \Omega(\frac{1}{t})
\]
Here $K$ is a kernel for a densely defined operator on
the Hilbert space 
$L^2({\bf{R}}^+)$ and we shall prove that it is
self-adjoint under the condition that
\[
\int_0^\infty\,\Omega(t)^2\, dt<\infty
\]










\bigskip

\centerline{\bf{Symmetric integral operators.}}
\bigskip


\noindent
Consider the domain $\square=\{0\leq x\leq 1\}\times\{0\leq y\leq 1\}$
in ${\bf{R}}^2$.
Let $K(x,y)$ be a real-vaued and Lebesgue mesure function on
$\square$ such that
the integrals
\[ 
\int_0^1\, K(x,y)^2\, dy<\infty
\]
for all $x$ outside a null-set on $[0,1]$.
In addition $K$ is symmetric,  i.e.$K(x,y)= K(y,x)$.
The $K$-kernel is bounded in Hilbert's sens if there exists a constant
$C$ such that
\[ 
\iint_\square\, K(x,y) u(x)u(y)\, dxdy\leq C^2\cdot\int_0^1\, u(x)^2\, dx
\]
for each $u\in L^2[0,1]$.
In the text-book |emph{Intyergralxxx}Ê[xxxx 1904],
Hilbert proved that
the linear operator on 
$L^2[0,1]$ defined by
\[ 
\mathcal K(u)(x)=\int_0^1\, K(x,y)u(y) dy
\]
is bounded and its operator norm is majorsied by $C$-Moreover
the spectrum is real and contained in $[-C,C]$ and
just as for symmetric real matrices
there exists a spectral resolution.
More precisely, set $\mathcal H= L^2[0,1]$.
Then there exists a
map
from $\mathcal H\times\mathcal H$
to the space of Riesz measures supported by
$[-C,C]$ which to every pair $u$ and $v$ in
$\mathcal H$ assigns a Riesz measure $\mu_{\{u,v\}}$
and $\mathcal K$ is recovered by the equation:
\[
\langle \mathcal K(u),v\rangle=\int_{-C}^C\,  t\cdot d\mu_{\{u,v\}}(t)
\]
where the left hand side
is the inner product
on the complex Hilbert space defined by
\[
\iint\, \mathcal K(u)(x)\cdot \overline{v}(x)\,dx
\]
In the monograph [Carelan 1923]
the condition (*) is imposed while (**) need not be valid.
Then we encounter an unbounded operator.
But notice that if
$u|in\mathcal H$ then (*9 and the CuachySchwarz inequality entails that
the functions
\[ 
y\mapsto K(x,y)u(y)
\] 
are absolutely integrable in Lebegue's sense 
for all $x$ outside the nullset $\mathcal N$ above.
Hence it makes sense to refer to $L^2$-functions $\phi$ on $[0,1]$
which
satisfy an eigenvalue equation
\[
\phi(x)= \lambda\cdot \int_0^1\, K(x,y)\phi(y)\, dy\tag{1}
\]
where $\lambda$ is a compkex number.
one is also led to consider the integral equation
\[
\phi(x)= \lambda\cdot \int_0^1\, K(x,y)\phi(y)\, dy+f(x)\tag{2}
\]
where $f\in\mathcal H$ is given and one seeks $\phi$.
It turns out that if $\mathfrak{Im}(\lambda)\neq 0$,
then the  inhomogenous equation 
(2) has at least one solution. 
Next,  consider the equation (1).
Let $\rho(\lambda)$ denote the number of linearly independent 
solution in (1). Carelan proived that
 the  $\rho$-function is constant 
when  $\lambda$ varies in
${\bf{C}}\setminus {\bf{R}}$.
Follwing Carelan one says that the kernel $(x,y)$ gives an operator $\mathcal K$ of Class I if
the $\rho$-function is zero. It means that
(2) has unique solutions
for every pair $\lambda,f)$
when $\lambda$ are non-real.
\medskip


\noindent
{\bf{A limit process.}}
Let $\{G_n(x,y)\}$ be a sequece of
symmetric kernel functions which are bounded in Hilbert's sense and
approximate $K$ in the sense that
\[
\lim_{n\to \infty} \int_0^1\, |K(x,y)-G_n(x,y)|^2\, dy=0
\]
for all $x$ outside
a null set. Fix some non-real $\lambda$.
Hilbert's theory entials that if
$f(x)$ is a continuous function, in general complex-valued, then
we find unqiue continuous functions $\{\phi_n\}$
which satisfy the integral equations
\[
\phi_n(x)= \lambda\cdot \int_0^1\, G_n(x,y)\phi(y)\, dy\tag{1}
\]
For a fixed $x$ we consider the complex numbers
$\{phi_n(x)\}$.
Now there exists the set $Z(x)$ of all cluster points, i.e.
a complex number
$z$ belongs to $Z(x)$ if there exists some
sequence $1\leq n_1<n_2<\ldots$ such that
\[
 z=\lim_{k\to\infty}\, \phi_{n_k}(x)
\]
\medskip

\noindent
{\bf{Theorem.}} \emph{For every approximating sequence $\{G_n\}$ as above
the sets $Z(x)$ are either reduced to points or circles in
the complex plane. Moreover, each $Z(x)$ is reduced to a siungleton set
when $\mathcal K$ is of class I.}
\medskip

\noindent
{\bf{Remark.}}
The result below was discovered by Weyl for some special unbounded operators
which arise during the study of second order
differential equations. See ¤ for a comment-.
If $\mathcal K$  is of Class I then
the theorem sbove shows that
each pair of a on-real $\lambda$
and some $f\in\mathcal H$ gives
a unique function $\phi(x)$
which satsfies (2) and
it can be found via a pointwise limit of solutions
$\{\phi_n\}$ to the equations (xx). In this sense the limit process
is robust because one can emply an arbitrary approximating
sequence $\{G_n\}$ under the sole condition that (xx) holds.
This already indficartes that the Case I leads to
a "consistent theory" even if $\mathcal K$ is unbounded.
To make this precise Carleman constructed a unique spectral function
when Case I holds.
More preciely, if
$K(x,y)$ is symmetric and 
Case I holds, then there exists a unique function
$\rho(x,y;\lambda)$ defined for
$(x,y)\in\square$ and every real $\lambda$ such that
\[
\mathcal K(h)(x)=\int_{-\infty}^\infty\, 
\,\frac{1}{\lambda}\cdot\frac{d}{d\lambda} \,
\int_0^1\, \theta(x,y;\lambda)\,h(y)\, dy
\] 
for all
$L^2$-functions $h$.
Concerning the spectral $\theta$-function, Carleman proved that  it
enjoys the same properties as Hilbert's spectral function for bounded 
operators.


\medskip

\noindent
{\bf{Remark.}}
For each fixed $\lambda>0$
one has a bounded self-adjoint operator
on $\mathcal H$ defined by
\[ 
\Theta_\lambda(h)(x)=\int_0^1\, \theta(x,y;\lambda)\,h(y)\, dy 
\]
Moreover, the operator-valued function
$\lambda\mapsto \Theta_\lambda$ has bounded variation over
each intervalÊ$\{a\leq \lambda\leq b\}$
when $0<a<b$.
It means that there exists a constant $C=C(a,b]$ such that
\[
\max\, \sum_{k=0}^M\, ||\Theta_{\lambda_{k+1}}-\Theta_{\lambda_k}||\leq C
\] 
for all partitions
$a=\lambda_0<\lambda_1<\ldots \lambda_{M+1}=b$ and
we have taken operator norms of the differences
$\Theta_{\lambda_{k+1}}-\Theta_{\lambda_k}$ in the sum above.
These bounded variations entail that one can compute the integrals in the right hand side
via the usual method  by Borel and Stieltjes.
\bigskip


\noindent
{\bf{The construction of  spectral functions.}}
When case I holds one constructs the $\rho$-function via a 
robust limit process.
Following [ibid:Chapitre 4] we expose this in ¤ xx.
The strategy is to
regard an approximating sequence $\{G_n\}$ of
Hilbert-Schmidt operator, i.e.
\[
 \iint_\square \, G_N(x,y)^2 \, dxdy<\infty
\]
hold for each $N$.
In this case $\{G_N\}$ are compact opertors.
With $N$ fixed
we get
a discrete sequence of non-zero real numbers
$\{\lambda\nu\}$
which are arragned with increasing avbsolute values and
an orthonormal  family of eigenfunctions $\{\phi_\nu^{(n)}\}$
where
\[
 G_N(\phi_\nu^{(N)})= \lambda\\nu\cdot \phi_\nu^{(N)}
 \] 
hold for each $\nu$.
Of course, the eigenvalues also depend on
$N$.
If $\lambda>0$ we set
\[
\rho_N(x,y;\lambda)=\sum_{0<\lambda_\nu<\lambda}\, \phi_\nu(x)\phi_\nu(y)
\]
\[
\rho_N(x,y;-\lambda)\sum_{-\lambda <\lambda_\nu<0}\, \phi_\nu(x)\phi_\nu(y)
\]
let us notice that for each fixed $n$, the $\lambda$-numbers in (x) stay
away from zero, i.e. there is a constant $c_N>0$ such that
$|\lambda_\nu\geq c_N$. So the function $\rho_N$
vanishes  in a neighborhood of zero.
The spectral theorem applied to symmetric Hilbert-Schmidt operators entails that
\[
\int_{-\infty}^\infty\, \frac{1}{\lambda}\cdot \frac{d}{d\lambda}\,
\rho_N(x,y;\lambda)\cdot h(y)\,  dy
\]
\medskip

\noindent
{\bf{The $\Omega$-kernels.}}
For each $N$ we introduce the function
\[
 \Omega_N(x,y;\lambda)=\int_a^x\int_a^y\, \rho_N(s,t;-\lambda)\, dsdt
\]
Let us notice that Bessel's inequality entails that
\[
 \bigl|\iint_\square\, \rho_N(x,y;\lambda)\cdot h(x)g(y)\, dxdy\bigr|\leq
 ||h||_2|cdot ||g|7_2
 \] 
 for each pair $h,g$ in $L^2[0,1]$.
 \medskip

\noindent
{\bf{Exercise.}}
Conclude from the above
that the variation of $\Omega$
over $[0,x]\times [0,y]$ is bounfed above by
\[
\sqrt{x\cdot y}
\] 
for every pair $0\leq x,y\leq 1$.
In partcular the functions
\[
(x,y)\mapsto \Omega(x,y;\lambda)
\]
are uniformly Hšlder continuous of order $1/2$
in $x$ and $y$ respectively.
\medskip


\noindent
Using the inequalities above
we elave it to the reader to check that there exists
at least one subsequence $\{N_k\}$ such that
the functions $\{\Omega_{N_k}(x,y;\lambda)$
converges uniformly with respect toÊ$x$ and $y$
while $\lambda$ stays in a bounded interval.
When Case I holds one proves that the limit is independent of the subsequence, i.e.
there exists a limit function
\[
\Omega(x,y;\lambda)=\lim_{N\to\infty}\,  
\Omega_N(x,y;\lambda)
\]
From the above the $\omega$-function is again uniformly Hšlder continuous
and
its first order partial derivatives are $L^2$-functions. Moreover, after the passage to
the limit one still
has Bessel's inequality which entails that
\[
\int_{-\infty}^\infty\, 
\frac{d}{d\lambda}\int_0^1 h(x)\cdot \bigl(\frac{\partial}{\partial x}
\int_0^1\, \frac{\partial\Omega(x,y;\lambda)}{\partial y}\cdot h(y))\,dy\bigr )\, dx
\leq \int_0^1\, h(x)^2\, dx
\]
for every $h\in L^2[0,1]$.
\medskip

\noindent
{\bf{Definition.}}
\emph{A Case 1 kernel $K(x,y)$ is closed if equality holds in (*).}
\medskip

\noindent
{\bf{Theorem.}} \emph{A Case I kernel $K(x,y)$ for which 
the equation}
\[ 
\int_0^1\, K(x,y)\cdot \phi(y)\ dy=0
 \] 
 \emph{has no non-zero $L^2$-solution $\phi$ is closed.}
\medskip

\noindent
{\bf{A representation  formula.}}
When (*) hols we can apply to to $h+g$ for every pair of
$L^2$-functiuons anbd since
the Hilbert space $L^2[0,1]$ is self-dual it follows that
for each $f\in L^2[0,1]$ one has the equality
\[
f(x)=\frac{d}{dx}\  
\int_{-\infty}^\infty\, 
\frac{d}{d\lambda}
\int_0^1\, \frac{\partial\Omega(x,y;\lambda)}{\partial y}\cdot f(y))\,dy
\]
almost everywhere with respect to $x$ on $[0,1]$.




{\bf{Remark.}} 
The 
formula (**) shows that it often is important to decide when a Case I kernel
is closed.
Theorem xx gives such a sufficent condition. However, it can
be extended to a quite geneeral result
where one for  can relax the passage to the limit via
suitable linear operators.
The reader may consult   [ibid; page 139-143]
for details. Here we are content to announce the conlsisive result ehich appear
in
[ibid;: page 142].
\medskip

\noindent
{\bf{The $\mathcal L$-family.}}
Let $\xi$ dentoe a paramter which in general depends on several variables, or
represents points in a manifold or  vectors in a normed linear space.
To each $\xi$ we are given  a linear operator
\[ 
L(\xi)\colon f\mapsto L(\xi)(f)
\]
from functions $f(x)$ on $[0,1]$ to new functions on $[0,1]$.
The linear map is weakly continuous, i.e. if
$\{f_\nu\}$ is a sequence in $L^2[0,1]$ which converges weakly to a init function $f$
in $L^2[0,1]$ then
\[ 
\lim L(\xi,f_\nu)\overset{w}\to L(\xi)(f)
\]
Next,
we are given $K(x,y)$ and
the second  condition for $L$ to be in  $\mathcal L$ is that
for each
pair  $\xi$ and $ 0\leq y\leq 1$ there exists
a constant $\gamma(\xi,y)$ which is independent of $\delta$ so that
\[
|L(\xi)(K_\delta(\cdot,y))(x)\leq  \gamma(\xi;y)
\]
where $K_\delta(x,y)$ is the truncated kernel function from (xx)
and in the left hand side we have applied $L(\xi$ to
the function $x\mapsto K_\delta(x,y)$ for each fixed $y$.
Moreover, we have
\[ 
\lim_{\delta\to 0}\, L(\xi)(K(\cdot,y))(x)\overset{w}\to 
\lim_{\delta\to 0}\, L(\xi)(K_\delta(\cdot,y))(x)
\]
where the convergence again holds weakly for
$L2$-functions on $[0,1]$.
Funally the equality below holds for every
$L^2$-function $\phi$:
\[
xxxx
\]








 
 





























 























\newpage







 









\newpage






\bigskip


\centerline{\bf{Moment problems.}}
\bigskip


\noindent
A great inspiration during the development of
unbounded symmetric operators on Hibert spaces
emerged from work by Stieltjes' pioneering article
\emph{Recherches sur les fractions continues}
[Ann. Fac. Sci.  Toulouse. 1894].
The  moment problem
asks for conditions on a
sequence $\{c_0,c_1,\ldots\}$ of positive real numbers
such that there exists a non-negative Riesz measure
$\mu$ on the real line and
\[
c_\nu= \int_{-\infty}^\infty\, t^\nu\cdot d\mu(t)\tag{*}
\] 
hold for each $\nu\geq 0$.
One easily verifies that
if $\mu$ exists then
the Hankel determinants
\[
\begin{pmatrix}
c_0&c_1&\ldots&c_n\\
c_1&c_2&\ldots&c_{n+1}\\
\ldots&\ldots&\ldots&\ldots\\
c_n&c_{n+1}&\ldots&c_{2n}\\
\end{pmatrix}
\]
are $>0$ for every $n=0,1,\ldots$. 
For brevity we say that
$\{c_n\}$ is a positive
Hankel sequence when
the determinants above are $>0$.
It turns out that this confition also is sufficient.
\medskip


\noindent
{\bf{Theorem.}} \emph{For each 
positive Hankel sequence
there exists at least one non-negative Riesz measure such that
(*) holds.}
\medskip


\noindent
{\bf{Remark.}}
The result above is due to Hamburger which extended Stieltjes' original  results where
one seeks non-negative measures supported by
$\{\geq 0\}$.
The moment problem for a positive Hankel sequence is 
said to be determined
if (*) has a unique  solution $\mu$.
Hamburger proved that the determined case holds
if and only if the
the associated continued fractions of $\{c_n\}$
is completely convergent.
See ¤ x below for an account about this convergence  condition.
A "drawback" in the Hamburger-Stieltjes theory
is that it is often  difficult to check
when the associated continued fraction of a positive Hankel sequence
is completely convergent.
So one is led to seek weaker,  but sufficient conditions
in order that (*) has a unique solution $\mu$.
Such a sufficient condition
was established  in Carleman's  monograph
[Carleman 1923. Page 189-220] 
and goes as follows:


\bigskip

\noindent
{\bf{Theorem.}}
\emph{The moment problem of 
a positive Hankel sequence $\{c_n\}$ is determined if}
\[
\sum_{n=1}^\infty\,c_n^{-\frac{1}{n}}=+\infty
\]
\medskip

\noindent
{\bf{Another criterion for  determined moment problems.}}
Constructions of continued fractions and
their associated quadratic forms 
go back to
work by Heine. See  [Handbuch der theorie
der Kugelfunktionen: Vol. 1. part 2]. An excellent account appears also
in the article \emph{Zur Einordnung der Kettenbruchentheorie
in die theorie der quadratischen Formen von
unendlichvielen VerŠnderlichen} [Crelle J. of math. 1914] by
Hellinger and Toeplitz.
Let us recall that a  positive Hankel sequence $\{c_n\}$
 corresponds to a
 quadratic form
 in an infinite number of variables:
 \[
 J(x)=\sum_{p=1}^\infty a_px_p^2-
 2\cdot \sum_{p=1}^\infty b_px_px_{p+1}
\]
where $b_p\neq 0$ for every $p$.
More precisely, the
sequences $\{a_\nu\}$ and $\{b_\nu\}$
arise when
the series
\[
-\bigl[\frac{c_0}{\mu}+
\frac{c_1}{\mu^2}+\frac{c_2}{\mu^3}+\ldots\,\bigr]
\]
is formally expanded into a continuous fraction
\[
\frac{c_0}{a_1-\mu-\frac{b_1^2}{a_1-\mu-\frac{b_2^2}{a_2-\mu}} }
\]
Now there exists 
the infinite  matrix $A$
with diagonal elements $\alpha_{pp}=a_p$ while
\[
\alpha_{p,p+1}= \alpha_{p+1,p}= -b_p\quad\colon p=1,2,\ldots
\]
and all the other elements are zero.
The symmetric  $A$-matrix 
gives a densely defined linear operator on
the complex Hilbert space $\ell^2$.
The following result is proved
[Carleman:1923]:
\medskip

\noindent
{\bf{Theorem.}}
\emph{The densely defined operator $A$ on $\ell^2$ is self-adjoint if and only if
the moment problem for $\{c_n\}$ is determined.}
\bigskip


\centerline {\bf{A general study of $A$-operators.}}
\bigskip

\noindent
Ignoring the "source" of the pair of real sequences $\{a_p\}$ and $\{b_p\}$
we consider a matrix $A$ as above where the sole condition
is that $b_p\neq 0$ for every $p$.
If $\mu$ is a complex number
one seeks infinite vectors
$x=(x_1,x_2,\ldots)$ 
 such that
 \[ 
 Ax=\mu\cdot x\tag{i}
 \]
 It is clear that (i) holds if and only if
 the sequence $\{x_p\}$ satisfies the infinite system of linear equations
 \[
(a_1-\mu)x_1=b_1x_2
\]
\[ 
(a_p-\mu)x_p=b_{p-1}x_{p-1}+ b_px_{p+1}\quad\colon p\geq 2
\]
\medskip

\noindent
Since $b_p\neq 0$ is assumed for every $p$ we see  that
$x_1$ determines the sequence. Here
$x_2,x_3,\ldots$ depend on $x_1$ and the parameter $\mu$.
Keeping $x_1$ fixed while $\mu$ varies
the reader can  verify that
\[ 
x_p=\psi_p(\mu)\quad\colon p\geq 2
\]
where $\psi_p(\mu)$ is a polynomial of degree $p-1$ for each $p\geq 2$.
These $\psi$-polynomials depend on the given
pair
of sequences
$\{a_p\}$ and $\{b_p\}$ and 
with these notations the following
results is  proved in [ibid]:
\medskip


\noindent
{\bf{2. Theorem.}}
\emph{The densely defined operator $A$ on $\ell^2$ is self-adjoint if and only if}
\[
\sum_{p=1}^\infty\, \psi_p(\mu)=+\infty
\]
\emph{for every non-real complex number
$\mu$.}
\medskip


\noindent
{\bf{A more general result.}}
Let $\{c_\nu\}$ be a positive Hankel sequence.
which is determined or not.
If $|rho$ is a non-negative measure which solves the moment problem (*)
we set
\[
\widehat{\rho}(\mu) =\int\, \frac{d\rho(t)}{t-\mu}
\]
It is defined outside the rell axis and yields in particular an analytic funcvtion in
the upper half-plane.
A major result in [Carleman]
gives a sharp inclusion for the values which can be attained
by
these $\widehat{\rho}$ functions while
$\rho$ are non-negative measures which
solve the moment problem.
It is expressed via constructions of discs in the upper half-plane which
arise via a nested limit of discs constructed from a certain family of
Mšbius transformations.
More precisely, to the given Hankel sequence
we have the pair of sequences $\{a_\nu\}$ and $\{b_\nu\}$.
For a fixed $\mu$ in the upper half-plane
we consider the maps:
\[ 
S_\nu(z)=\frac{b_\nu^2}{a_{\nu+1}-\mu-z}\quad\colon \nu=0,1,\ldots
\]
Notice that
\[ 
\mathfrak{Im}(S_\nu(z))=\frac{b_\nu^2\cdot \mathfrak{Im}(\mu+z)}
{|a_{\nu+1}-\mu-z|^2}>0
\]
It follows that $S_\nu$ maps the upper half-plane $U^+$ conformally onto a disc
placed in $U^+$.
\medskip

\noindent
{\bf{Exercise.}}
To each $n\geq 1$ we consider the composed map
\[ 
\Gamma_n=S_0\circ S_1\circ\ldots\circ S_{n-1}
\]
Show that the images $\{C_n(\nu)= \Gamma_n(U^+)\}$
form a decreasing sequence of discs and there exists a limit
\[ 
C(\mu)=\cap\, C_n(\mu)
\]
which either is reduced to a single point or is a closed disc
in $U^+$.
\bigskip

\noindent
{\bf{Theorem.}} \emph{For each $\mu\in U^+$
and every $\rho$-measure which solves the moment problem
one has the inclusion}
\[
\widehat{\rho}(\mu)\subset C(\mu)
\]





























\newpage



\centerline{\bf{The  Neumann-PoincarŽ kernel}}



\bigskip

\noindent
Operator theory was used  at an early stage by
Neumann and PoincarŽ.
So for historic reasons we  expose some facts about
a specific boundary value problem.
Let $\Omega$
be a bounded and connected open set in ${\bf{C}}$
of class $\mathcal D(C^1)$, i.e. the  boundary
$\mathcal C$ is the disjoint union of
closed and continuously differentiable Jordan curves.
To each $p\in\mathcal C$ there exists the inner normal 
${\bf{n}}_i(p)$
of unit length. Set
\[
K(p,q)=\frac{\langle p-q,{\bf{n}}_i(p)\rangle}{|p-q|}
\]
It is clear that the $C^1$-hypothesis entails that
$K$ is a continuous function on
$\mathcal C\times\mathcal C$.
Next, let $M$ be a positive real number.
If $u$ is a real-valued continuous function on
$\mathcal C$
there exists a harmonic function $U$ in
$\Omega$ defined by
\[
U(p)=\int_\mathcal C\, \log \frac{M}{|p-q|}\cdot u(q)\, ds(q)
\]
 where $ds$ is the arc-length measure on
$\mathcal C$.
We choose $M$ so large that it exceeds the diamater of
$\mathcal C$ defined by
$\max\, |q_1-q_2|\,\colon q_1,q-2\in\mathcal C$.
As explained in ¤xx the inner normal derivative of
$U$ is given by the equation
\[
\frac{\partial U}{\partial{\bf{n}}_i}(p)=
-\pi\cdot u(p)-
\int_\mathcal C\, K(p,q)\cdot u(q)\, ds(q)
\]
To solve the boundary  value problem (*)
from the introduction therefore 
amonunts
to find
$u$ which  satisfies the integral equation
\[
-\pi\cdot u(p)-
\int_\mathcal C\, K(p,q)\cdot u(q)\, ds(q)=
a(p)\cdot \int_\mathcal C\, \log \frac{M}{|p-q|}\cdot u(q)\, ds(q)+f(p)\tag{1}
\]
Following the device by Neumann and Poincare we choose $M$ so large that
that the function below defined on $\mathcal C\times\mathcal C$ is everywhere
positive:

\[ 
S(p,q)=a(p)\cdot  \log \frac{M}{|p-q|}+K(p,q)
\]
To $S$ one associaes the integral operator $\mathcal S$ which sends 
$u\in C^0(\mathcal C)$ into
\[ 
\mathcal S_u(p)=\int_\mathcal C\,S(p,q)\cdot u(q)\, ds(q)
\]
Now (1) amounts to find $u$ such that
\[
\mathcal S_u(p)+ \pi\cdot u(p)=-f(p)\tag{2}
\]
Since the kernel function $S$ is everywhere positive
one verifies easily that
the linear operator
on the Banach space 
$C^0(\mathcal C)$ defined by
$u\mapsto \mathcal S_u+\pi\cdot u$
is invertible, i.e. $-\pi$ does not belong to the spectrum of the bounded operator
$\mathcal S$.
Introducing the inverse operator
we solve (2) by
\[
u=-(\pi \cdot E+\mathcal S)^{-1}(f)\tag{3}
\]
\medskip

\noindent
{\bf{Remark.}}
From the above we have solved the boundary value problem
(*) in the introduction by operator
methods. Notice that the solution is found
without
using solutionds to the Dirichlet problem.
\medskip

\noindent
{\bf{A study of spectra.}}
The Neumann-PoincarŽ solution above
shows that the study of 
 the integral operator
$\mathcal K$ defined by
\[
\mathcal  K_u(p)=\int_\mathcal C\, K(p,q)\cdot u(q)\, ds(q)
\]
is crucial. In ¤ xx we shall learn that
$\mathcal K$ is a compact operator on the Hilbert space
$\mathcal H$ of square integrable functions on
$\mathcal C$ with respect to the arc-length measure.
Here one seeks real-valued eigenfunctions
$u$ which satisfy
\[
u(p)=\lambda\cdot \mathcal K_u(p)\tag{**}
\] 
for some real number $\lambda$.
An obstacle is  that
$K$ is not symmetric, i.e.
$K(p,q)\neq K(q,p)$.
Following a construction invented by
PoincarŽ one can find eigenvalues and eigenfunctions via a symmetric kernel function.

\medskip

\noindent
{\bf{The kernel $N(p,q)$.}}
Let $M$ be a positive number which as above
exceeds the diameter of 
$\mathcal C$.
Set
\[
N(p,q)= \int_\mathcal C\, 
K(p,\xi )\cdot \log\,\frac{M}{|q-\xi|}\cdot ds(\xi)
\]
Green's formula applied to a pair of harmonic functions $H_1,H_2$ in $\Omega$
with continuously differentiable boundary values gives the equlity
\[
\int_\mathcal C\,\frac{\partial H_1}{\partial{\bf{n}}_i}(p)\cdot H_2(p)\, ds(p)=
\int_\mathcal C\,\frac{\partial H_2}{\partial{\bf{n}}_i}(p)\cdot H_1(p)\, ds(p)
\]
From this it follows
that the the kernel function $N$ is symmetric, i.e.
$N(p,q)=N(q,p)$.
At the same time we have the operator
$\mathcal S$ defined by
\[
 \mathcal S(u)=\int_\mathcal C\, 
\log\,\frac{M}{|q-\xi|}\cdot u(\xi)\,ds(\xi)
\]
The construction of $N$ entails that its associated integral operator
$\mathcal N$ satisfies the equation
\[
\mathcal N=\mathcal S\circ \mathcal K
\]
This gives a gateway to find
eigenfuntions to the non-symmetric operator
$\mathcal K$.
To begin with $\mathcal S$
is special since the kernel
function $S(p,q)$ is both symmetric and positive.
In the Hilbert space $\mathcal H$ above
we shall learn  in ¤ x that there exists an   orthonormal basis
$\{\phi_n\}$ formed by eigenfunctions which satisfy
\[ 
\mathcal S\phi_n=\kappa_n \phi_n\tag{1}
\] 
where the positive $\kappa$-numbers  tend to zero.
Moreover, each $u\in \mathcal H$
has a Fourier-Hilbert  expansion
\[ 
 u= \sum\,\alpha_n\cdot \phi_n\tag{2}
\]
Next, the symmetric $N$-function yields a doubly indexed and symmtric sequence
$\{c_{jk}\}$ given by
\[
c_{jk}=\iint  \phi_j(p)\phi_k(q)N(p,q)\, ds(p)ds(q)
\]
\medskip

\noindent
{\bf{Theorem.}} \emph{A pair $(u,\lambda)$ solves (**)
if and only if $u$ has an expansion}
\[
u=\sum_{n=1}^\infty \, \alpha_n\cdot \phi_n(p)
\]
\emph{where the sequence $\{ \alpha_n\}$ satisfies the system of linear equations}
\[
\kappa_p\cdot \alpha_p=\lambda\cdot 
\sum_{q=1}^\infty \, c_{qp}\alpha_q\quad\colon p=1,2,\ldots
\]
\medskip


\noindent
{\bf{Remark.}}
The proof is given in ¤ xx where
a crucial step is to show
that
\[
\sum\sum \frac{c^2_{j,k}}{\kappa_j\cdot \kappa_k}<\infty
\] 


\noindent
{\bf{The case when $\mathcal C$ has corner points.}}
When 
$\mathcal C$ has corner points, for example if
$\partial\Omega$ is bordered by piecewise linear and closed Jordan
curves, then
the Neumann-PoincarŽ kernel is
unbounded. Here  
the reduction to the symmetric case is  more involved  and 
relies upon 
quite intricate results which appear in 
[Carleman : Part II: 1916].
Further  analysis remains to be done and
open problems about
the Neumann-PoincarŽ equation 
remains to be settled in dimension $\geq 3$.
So far  it appears that
only the 2-dimensional case 
is well understood by 
results  from  [Carleman :1916].

\newpage

\centerline{\bf{The self-adjoint operator $i\cdot \frac{d}{dx}$.}}

\medskip

\noindent
On the real $x$-line we have the Hilbert space
$\mathcal H= L^2({\bf{R}})$ of complex-valued and square integrable functions.
It contains  $C_0^\infty({\bf{R}})$ as a dense subspace on which
the operator
\[
\frac{d}{dx}\colon f\mapsto f'(x)
\] 
is defined where $f'(x)$ is the derivtive of $f$.
Set $A=i\cdot \frac{d}{dx}$. This gives a densely  defined
operator 
on $\mathcal H$ whose domain of defintion $\mathcal D(A)$
consists of all square-integerable functions $f$
for which the distribution derivative $f'$ again belongs to $\mathcal H$.
Let us remark that
every $f\in\mathcal D(A)$ therefore is locally the
primitive of an $L^1$-function and therefore
locally absolutely continuous.
So in particular $\mathcal D(A)\subset C^0({\bf{R}})$.
The graph of $A$ is the set of pairs $(f,if')\,\colon f\in\mathcal D(A)\}$.
Basic facts in distribution theory
show that  $\Gamma(A)$ is a closed subset of
$\mathcal H\times\mathcal H$. See ¤ xx for details.
Hence $A$ is densely defined
and closed.
Now we seek Neumann's spectrum $\sigma(A)$.
To begin with, if $\lambda$ is a complex number
and $A(f)= \lambda\cdot f$ for some
$f\in \mathcal H$ we have
\[
i\cdot f'=\lambda\cdot f
\]
Basic facts about ordinary differential equations entail that
$f$  is a constant times
$e^{-i\lambda x}$
and this exponential function has absolute value one
and cannot belong to $\mathcal H$. So if 
$E$ is the identity operator then
$\lambda\cdot E-A$ is injective for all complex numbers $\lambda$, i.e.
the  "point spectrum" of $A$ is empty.
However, the invertibility in Neumann's sense
requires more conditions on the densely defined operator
$\lambda\cdot E-A$, i.e its range must be  dense and there
exists a constant $c>0$ such that
\[
||\lambda\cdot f-if'||_2\geq c\cdot ||f||_2\quad\colon f\in\mathcal D(A)\tag{1}
\]
To analyze when these two conditions hold
we use the Fourier transform.
When $f\in C_0^\infty({\bf{R}})$ we have
the inversion formula
\[
i\cdot f'(x)=
-\frac{1}{2\pi}\cdot\int\, e^{ix\xi}\cdot \xi\cdot \widehat{f}(\xi)\, d\xi
\]
Fourier's inversion formula gives
\[
(\lambda\cdot E-A)(f)(x)=
\frac{1}{2\pi}\cdot\int\, e^{ix\xi}\cdot (\lambda+\xi)\cdot \widehat{f}(\xi)\, d\xi
\]
If $\lambda=a+ib$ with $b\neq 0$ we have
$|\lambda+\xi)|^2\geq b^2$ for all real $\xi$.
Applying Plancherel's equality we concludue that
\[
||\lambda\cdot f-if'||_2\geq b\cdot ||f||_2\colon f\in\mathcal D(A)
\]
Hence (1) hols for every non-real $\lambda$.
There remains to show that the range of
$(\lambda\cdot E-A)$ is dense in the Hilbert space $\mathcal H$
when $\mathfrak{m}(\lambda)\neq 0$.
If the density fails the orthogonal complement of the range is
non-zero and we find a non-zero function 
$g\in\mathcal H$ such that
\[ 
\langle \lambda\cdot f-if', g\rangle=
\int\,  (\lambda\cdot f-if')\cdot \bar g\, dx=0\quad\colon f\in\mathcal D(A)\tag{3}
\]
Thjs holds in particular when
$f$ are test-functions
and using thr notion of distribution derivatives
we see that (2) entails that
the $g$-function satisfies the equation
\[
\lambda\cdot g= i\cdot \frac{dg}{dx}
\]
From (xx) above it follows that   $g=0$ and hence the
range of
$(\lambda\cdot E-A)$ must be dense which finishes  the proof of the
inclusion
\[
 \sigma(A)\subset {\bf{R}}
\]
\medskip

\noindent
{\bf{The equality $A=A^*$.}}
By  (2) and Parseval's equality for $L^2$-norms under the Fourier transform
it follows that
$|mathcal D(A)$ consists of all $f\in L^2$ such that
$\xi\cdot \widehat{f}(\xi)$ is square integrable on the $\xi$-line.
Next, for a pair $f,g$ in $C_0^\infty$ a partial integration gives
the equality
\[
\langle Af, g\rangle=
\langle  f, Ag\rangle
\] 
which means that the densely defined operator $A$ is symmetric.
Next, by definition a function $g$ belongs to
$\mathcal D(A^*)$ if there exists a constant $C(g)$ such that
\[
|\langle Af, g\rangle\leq C(g)\cdot ||f||_2
\quad\colon f\in\mathcal D(A)
\]
Passing to the Fourier transform
and using Parseval's equality this is equivalent to the condition that
there exists a constant $C$ such that
\[
||\xi\cdot \widehat{f}\cdot\widehat{g}||_2\leq 
C\cdot ||\widehat{f}||_2\quad\colon f\in\mathcal D(A)
\]
Since the family
$\{\widehat{f}\,\colon f\in\mathcal D(A)$ is dense in
the $L^2$-space on the $\xi$-line this entails that
$\xi\cdot \widehat{g}$ is locally square integrable and hence
$g$ belongs to $\mathcal D(A)$.
Hence we have proved the equality
\[
\mathcal D(A)=
\mathcal D(A^*)
\]
which means that $A$ is a densely defined and self-adjoint operator
on $\mathcal H$.



\newpage

\centerline {\bf{Further examples.}}


\medskip

\noindent
{\bf{2. An ugly example}}.
Let $\{a_{pq}\}$
be a doubly-indexed and symmetric sequence of
real numbers,  i.e. 
$a_{pq}=a_{qp}$
hold for each pair of positive integers.
Moreover we assume that 
\[
 \sum_{q=1}^\infty\, a_{pq}^2<\infty
\quad\colon p=1,2,\ldots\tag{*}
\]
Consider the Hilbert space
$\ell^2$ whose vectors are complexes sequences
$\{\xi_p\}$ such that
\[
\sum_{q=1}^\infty\, |\xi_q|^2<\infty\tag{i}
\]
The Cauchy-Schwarz inequality entails that if
$\{\xi_p\}\in\ell^2$ then the series
\[
\sum_{q=1}^\infty\,a_{pq}\cdot \xi_q
\]
converges for each $p$.
However, the imposed conditions on
the $a$-sequence does in general not imply that
\[
\sum_{p=1}^\infty\, |\sum_{q=1}^\infty\,a_{pq}\cdot \xi_q|^2<\infty
\]
In an article from 1920,
Carleman  constructed 
a sequence $\{a_{pq}\}$ whch satisfies (*) and at the same time violates
the wellknown  fact in
linear algebra which asserts
that eigenvalues of a symmetric matrix with real elements are real.
Namely, in  Carleman's   sequence 
$\{a_{pq}\}$ there exists a complex  vector
$\xi\in\ell^2$ with norm one such that
\[
\xi_p=i\cdot \sum_{q=1}^\infty\,a_{pq}\cdot \xi_q\quad\colon p=1,2,\ldots\tag{ii}
\]
while the series (i) has value one.
We give the construction in ¤ xx and remark that
this example shows that  care must be taken when one
considers
linear
equations in an inifinite number of variables.
Namely, with the $\xi$-vector as in (ii)
we  have the limit formula:
\[
\lim_{N\to\infty}\, 
\sum_{p=1}^{p=N}\, |\xi_p|^2=1
\]
Next,  (ii)  entails that
\[
1=\lim_{N\to\infty}\, 
i\cdot \sum_{p=1}^{p=N}\sum_{q=1}^\infty\,
a_{pq}\xi_q\cdot\bar\xi_p=
i\cdot \sum_{q=1}^\infty\,\xi_q\cdot \sum_{p=1}^{p=N}a_{pq}\bar\xi_p
\]
For each $q$ we set
\[
\xi_q(N)=i\cdot  \sum_{p=1}^{p=N}a_{qp}\xi_p
\]
Since $\{a_{pq}\}$ is symmetric and real we have
\[
\sum_{p=1}^{p=N}a_{pq}\bar\xi_p=
i\cdot   \sum_{p=1}^{p=N}a_{qp}\bar\xi_p=-\bar\xi_q(N)
\]
and the equality $i^2=-1$ entails 
that
\[
-1=\lim_{N\to\infty}\, \sum_{q=1}^\infty\,\xi_q\cdot \bar \xi_q(N)\tag{iii}
\]
At the same time we have limit formulas:
\[
\lim_{N\to\infty}\,\bar \xi_q(N)=\bar \xi_q\quad\colon q=1,2,\ldots\tag{iv}
\]
But in spite of (iii) the results above give
\[
\lim_{N\to\infty}\,\xi_q\cdot (\bar \xi_q+\bar \xi_q(N)=0
\]
which at first sight seems to contradict
the limit formulas above. However,
the convergence in (iv)  holds  for each fixed
$q$, but not uniformly with respect to $q$.
This   is the reason why the 
"obscure limits" above appear when (ii) holds.
\medskip















\bigskip

\noindent
{\bf{3. The dual of $\ell^\infty$.}}
Consider
the Banach space
$\ell^1$ whose vectors are sequences of $\{x_n\}$
of complex numbersi indexed by positive integers
with the norm
$||x||=\sum\, |x_n|$.
The dual space  is $\ell^\infty$  which consists  of bounded vectors. It
contains the  subspace $\ell^\infty_0$ of  
sequences $\{\xi_n\}$ where only finitely many 
$\xi_n\neq 0$,
This is not a dense subspace for if
$\xi^*$ is the sequence with $\xi^*_n=1$ for every $n$ its distance to
$\ell_0^\infty$ is one.
On the other hand $\ell^\infty_0$ is dense in the
\emph{weak-star topology}
which by definition is the
weakest - or coarsest - topology on $\ell^\infty$ for which the functions
\[ 
\xi\mapsto\xi(x)= \sum\, \xi_nx_n
\] 
are continuous for every  $\ell^1$-vector $x$.
This leads us to consider
the dual space of $\ell^\infty$. It turns out that it consists 
of Riesz
measures on the compact space $\beta{\bf{Z}}$ 
obtained as the maximal ideal space of the 
Banach algebra $\ell^\infty$. One  refers to
$\beta{\bf{Z}}$
as the Stone-Cech compactification of the integers where
${\bf{Z}}$ appears as  a dense subset 
and at the same time there exist non-zero Riesz measurs $\mu$ on
$\beta{\bf{Z}}$ without any point mass at the integers.
Every such Riesz measure, regarded as an element in the dual 
of $\ell^\infty$ vanishes identically on the subspace
$\ell_0^\infty$.
The result is that the bi-dual
\[ 
(\ell^1)^{**}=\mathfrak{i}(\ell^1)\oplus
\mathfrak{M}(\beta{\bf{Z}}\setminus {\bf{Z}})
\]
where the last term is the space is Riesz measures on
the compact topoligical space
$\beta{\bf{Z}}\setminus {\bf{Z}})$.

\medskip

\noindent
{\bf{4. Domains of definition for
the Laplace operator.}}
Let $D$ be the unit disc in ${\bf{R}}^2$
and consider the Laplace operator $\Delta=\partial_x^2+\partial_y^2$.
In the Hilbert space
$L^2(D)$ of square-integrable complex valued functions
there exists
the  subspace $V$
of $L^2(D)$ with the property that for each
$\phi \in V$ its Laplacian taken in the distribution sense
belongs to $L^2(D)$. The necessary and sufficient condition for
this to hold is that there is a constant $C(\phi)$ such that
\[
|\iint_D\,\Delta(f)\cdot \phi \, dxdy|\leq C(\phi)\cdot ||f||_2
\quad\colon f\in C_0^\infty(D)\tag{1}
\]
where $||f||_2$ is the $L^2$-norm and as indicated 
$f$
are test-functions with compact support in
$D$.
In  fact, since Hilbert spaces are self-dual and $C_0^\infty(D)$ is dense in
$L^2(D)$ the inequality (1) gives a unique $\psi\in L^2(D)$ such that
\[
\iint_D\,\Delta(f)\cdot \phi \, dxdy=
\iint_D\,f\cdot\psi \, dxdy
\quad\colon f\in C_0^\infty(D)\tag{2}
\]
which  means that $\psi=\Delta(\phi)$ in the distribution sense.
Hence one has
a linear operator
\[
 T\colon \phi\mapsto \Delta(\phi)
\] 
The domain of definition $V=\mathcal D(T)$ contains test-functions and is therefore
dense in $L^2(D)$.
One easily verifies that the graph of $T$ taken in the product
$L^2(D)\times L^2(D)$ is closed.
Hence $T$ is a densely defined and closed
linear operator. The kernel consists of harmonic functions
in $D$ which  are square integrable.
So if one wants an injective and densely defined operator
it is necessary to shrink the domain of definition.
To achieve this we introduce the logarithmic
kernel
\[
L(z,\zeta)= \frac{1}{2\pi}\cdot \log\,\frac{|z-\zeta|}{|1-\bar\zeta z|}
\]
It gives the linear operator
$\mathcal L$
defined on $L^2(D)$ by:
\[
\mathcal L(\phi)(z)=\iint _D\,L(z,\zeta)
\cdot \phi(\zeta)\, d\xi d\eta
\tag{3}
\]
Here $L(z,\zeta)$ is square integrable on the product $D\times D$
which means that
$\mathcal L$ is a  Hilbert-Schmidt operator on
$L^2(D)$ and in particular compact.
Moreover, since
$L(z,\zeta)=0$ when $|z|=1$ and $|\zeta|<1$
one easily verifies that
$\mathcal L(\phi)$ is  a continuous function on
the closed disc with boundary values zero on the unit circle.
Moreover one has  the equality
\[
\Delta(\mathcal L(\phi))=\phi\quad\colon \phi\in 
L^2(D)\tag{4}
\]
Hence the composed operator $\Delta\circ \mathcal L$
is the identity on $L^2(D)$ and
 Stokes theorem gives
\[
f=\mathcal L(\Delta(f))\quad\colon f\in C_0^\infty(D)
\]
In particular the range of
$\mathcal L$ is a dense subspace of 
$\mathcal L(L^2(D))$ and from the above we see that if
$g=\mathcal L(\phi)$ for some
$\phi\in L^2(D)$ then
\[
\iint_D\,\Delta(f)\cdot g \, dxdy=
\iint_D\,f\cdot \phi\, dxdy
\quad\colon f\in C_0^\infty(D)
\]
We conclude that
$\mathcal L(L^2(D))$ is a subspace of
$\mathcal D(T)$ and we have the linear operator
\[
 \Delta\colon g\mapsto \Delta(g)\quad\colon
 g\in\mathcal L(L^2(D))
 \]
With this restricted domain of definition one has
\[
\mathcal L\circ\Delta(g)= g \quad\colon g\in\mathcal L(L^2(D))
\]
So here $\Delta$ becomes injective
and at the same time
(4) holds.
\medskip

\noindent
{\bf{The closure property.}}
There remains to show that
the chosen domain of definition  yields  a closed operator which
amounts
to show that
the graph
\[
\Gamma=\{
(g,\Delta(g))\,\colon g\in\mathcal L(L^2(D))\}
\]
The closed graph property relies upon the
following crucial result:

\medskip

\noindent
{\bf{4.1 Theorem.}}
\emph{An $L^2$-function $g$ belongs to
$\mathcal L(L^2(D))$ if and only if
there exists a constant $C(g)$ such that}
\[
|\iint_D\,\Delta(f)\cdot \phi \, dxdy|\leq C(g)\cdot ||f||_2
\quad\colon f\in C^\infty(\bar D)\tag{*}
\]
\medskip

\noindent
{\bf{Remark.}}
Notice the distinction from (1) where (*)
only is imposed when
$f$ have compact support in $D$. So  (*)  is more restrictive
and  the inclusion
$\mathcal L(L^2(D))\subset V$ is strict.
The theorem
above
will be  proved in
¤ xx and
entails that
$\Delta$ with the chosen domain of definition is 
an unbounded self-adjoint operator.


\medskip


\noindent
{\bf{5. The complex Hilbert transform}}.
Identify the complex $z$-plane with
the 2-dimensional real $(x,y)$-space.
Now we have the Hilbert space
$L^2({\bf{C}})$ whose vectors are complex-valued and
square integrable functions in the $(x,y)$-plane.
If $g$ is a continuously differentiable function with
compact support there exists a limit
\[
G(z)=\lim_{\epsilon\to 0}\, \iint_{|z-\zeta|>\epsilon}\, 
\frac{g(\zeta)}{(z-\zeta)^2}\, d\xi d\eta\tag{5.1}
\]
exists for every $z\in {\bf{C}}$.
In fact, using Stokes theorem we show in ¤ xx tht
\[
G(z)=\iint\,\frac{\frac{\partial g}{\partial \zeta}(\zeta)}{z-\zeta}
d\xi d\eta
\]
where the last integral exists since
$\frac{\partial g}{\partial \zeta}$ is a continuous function with compact support and
$(z-\zeta)^{-1}$
is locally integrable in the $(\xi,\eta)$-space
for each fixed $z$.
The complex Hilbert transform is defined by the linear operator:
\[ 
T_g(z)= \frac{1}{\pi}\, G(z)
\] 
It turns out that
$T$ is an isometry with respect to the $L^2$-norm, i.e. 
\[
\iint\, |T_g(z)|^2\, dxdy=
\iint\, |g(z)|^2\, dxdy\quad\colon g\in C_0^1({\bf{C}})\tag{5.2}
\]
There are several proofs of (5.2). One relies upon the Fourier transform
and Parseval's theorem which is exposed in ¤ xx.
Another proof employs an abstract reasoning and goes as follows:
Let
$\mathcal H$ be a Hilbert space
and $\Phi$ us a subset of vectors
with the property that
the subspace of vectors in
$\mathcal H$ of the form
\[
c_1\phi_1+\ldots+c_k\phi_k\quad\colon 
\langle\phi_j,\phi_i\rangle=0\colon j\neq i
\]
is dense
in $\mathcal H$. Thus, we assume that finite linear combinations of pairwise
orthogonal $\Phi$-vectors is dense.
Let us now
consider a 
linear operator
$T$ on
$\mathcal H$ 
such that the following   hold:
\[
||T(\phi)||= ||\phi||\quad\colon \phi\in \Phi\tag{*}
\]
\[
\langle\phi_1,\phi_2\rangle=0\implies
\langle T(\phi_1),T(\phi_2)\rangle=0
\quad\colon\, \phi_1,\phi_2\in \Phi
\tag{**}
\]

\medskip

\noindent
{\bf{Exercise}}
Show that (*)-(**) imply that $T$ is an isometry, i.e.
$||T(g)||= ||g||$  for every
$g\in\mathcal H$.

\medskip

\noindent
Apply the  result above  to the
complex Hilbert transform where
$\Phi$ is  the family of vectors in $L^2({\bf{C}})$
given
by characteristic functions of dics in
${\bf{C}}$. It  is clear that  this family satisfies
the density condition above.
Now we study the
action by the Hilbert transform on such  functions.
Let $z_0\in{\bf{C}}$ and $r_0>0$ be given and 
$\phi$  is the characteristic function
of the disc of radius $r_0$ centered at $z_0$.
\medskip

\noindent
{\bf{5.1 Proposition.}}
\emph{One has $T_\phi(z)=0$ when $|z-z_0|< r_0$ while}
\[
T_\phi(z)=\frac{r_0^2}{(z-z_0)^2}\quad \colon
|z-z_0|>r_0
\]

\medskip

\noindent
\emph{Proof.}
After a translation we can take $z_0=0$ and via a dilation of the scale
reduce the proof to the case $r_0=1$.
If $|z|>1$
we have
\[
T_\phi(z)=\frac{1}{\pi}\iint_D \, \frac{d\xi d\eta}{(z-\zeta)^2}
=\frac{1}{\pi z^2}\iint_D \frac{d\xi d\eta}{(1-\zeta/z)^2}
\]
Expand 
$(1-\zeta/z)^{-2}$ in a power series of $\zeta$ and notice that
\[
\iint_D \,\zeta^m\, d\xi d\eta=0\quad\colon m=1,2,\ldots
\]
Then we see that $T_\phi(z)= z^{-2}$.
There remains to show that
$|z|<1$ gives $T_\phi(z)=0$.
To prove this we use the differential 2-form
$d\zeta\wedge d\bar\zeta$ and there remains to show that
\[
\lim_{\epsilon\to 0}\, 
\iint_{D_\epsilon}\frac{d\zeta\wedge d\bar\zeta}{(z-\zeta)^2}=0\tag{i}
\]
where  $D_\epsilon= D\setminus \{|\zeta-z|\leq \epsilon\}$.
Now $\partial_\zeta((z-\zeta)^{-1})=(z-\zeta)^{-2}$
and Stokes theorem gives
(i) if
\[
\int_{|\zeta|=1}\, \frac{d\bar\zeta}{z-\zeta}-
\lim_{\epsilon\to 0}\, \int_{|\zeta-z|=\epsilon}\, \frac{d\bar\zeta}{z-\zeta}=0
\]
In the first integral we use the
series expansion 
$(z-\zeta)^{-1}=-\sum_{n=0}^\infty \, \zeta^{-n-1}\cdot z^n$
and get a vanishing since
\[
\int_{|\zeta|=1}\, \zeta^{-n-1}\, d\bar\zeta=0\quad\colon n=0,1,\dots
\]
The verification that the limit as $\epsilon\to 0$
in the second integral vanishes is left to the reader.


\medskip


\noindent
The Proposition  entails that
\[
||T(\phi)||^2=
r_0^4\cdot \iint_{|z|>r_0}\, \frac{dxdy}{|z|^4}=
r_0^4\cdot 2\pi\int_{r_0}^\infty \,\frac{dr}{r^3}=\pi\cdot r_0^2
\]
Since $||\phi||^2=\pi\cdot r_0^2$ we conclude that
$||T(\phi)||= ||\phi||$.
The verification that (**)  holds when
$\phi_1,\phi_2$ are characteristic functions of disjoint discs
is left as an exercise.






















\newpage

\centerline{\bf{A. Some results in functional analysis.}}

\bigskip

\noindent
The subsequent material  exposes some  results 
in functional analysis with special attention given to
linear operators on Hilbert spaces.
Proofs of some of the assertions below appear in ¤ 11.
\bigskip




\centerline{\bf{A.1 The Riezs-Nagy theorem.}}
\medskip

\noindent
Let $\mathcal H$ be a Hilbert space.
A linear operator $U\colon \mathcal H\to \mathcal H$
is  unitary if
\[
\langle Ux,Uy\rangle=
\langle x,y\rangle
\] 
hold for all pairs $x,y$ in
$\mathcal H$.
Next, a  
linear operator $A$ on  $\mathcal H$
of norm one is called a   contraction.
A family of contractions  arises as follows:
Let $\mathcal H_1$ be another Hibert space which contains
 $\mathcal H$ as a closed subspace.
 There exists the orthogonal projection $P$ from
 $\mathcal H_1$ onto $\mathcal H$ and
 if $U$ is a unitary operator on $\mathcal H_1$
 we get a linear operator on $\mathcal H$ defined by
 \[ 
 A=P\circ U
 \] 
 In other words, we take $x\in \mathcal H$
 and  apply $U$ to get $U(x)\in\mathcal H_1$ and
 $P$ projects this vector back to
 $\mathcal H$.
 Since the unitary operator $U$ preserves norms
 it follows that
 $A$ is a contraction.
 A  result due to F. Riesz and Nagy asserts that
 every contraction on $\mathcal H$ arises from
 a pair $U,P$ as above.
 Moreover, they proved that the pair can be chosen so that 
 \[
 p(A)=P\circ p(U)
 \] 
 hold for
 every polynomial in $A$.
 We prove this in ¤ 11.xx.
 
 



\bigskip


\centerline {\bf{A.2 The infinitesmal generator of a unitary semi-group}}.

\medskip

\noindent
A  result 
due to
M.H. Stone  about
strongly continuous semi-groups of unitary operators 
goes
as
follows:
There is given a doubly-index  sequence
of functions $\{c_{pq}(t)\}$, where $p,q$ are positive
integers and the $c$-functions are defined on $\{t\geq 0\}$
which satisfies the following:
First the Hermitian condition holds, i.e. 
$\bar c_{qp}(t)= c_{p,q}(t)$ for all pairs of integers.
In addition  
the following   hold
for all $s,t\geq 0$ and every pair $p,q$.
\[
\sum_{q=1}^\infty\, |c_{qp}(t)|^2=1\quad\colon\quad p=1,2,\ldots
\quad\text{and}\quad 
\sum_{q=1}^\infty\, c_{qp}(t)\cdot \overline {c_{qr}}(t)=0\quad\colon\quad p\neq r\tag{i}
\]
\[
c_{qp}(t+s)=
\sum_{j=1}^\infty\, c_{qj}(s)\cdot c_{jp}(t)\tag{ii}
\]
\[
\lim_{t\to 0}\, \sum_{q=1}^\infty\, \bigl|\, \xi_q- \sum_{p=1}^\infty\, c_{qp}(t)\xi_p
\,\bigr|^2=0\quad\text{for every}\quad \xi\in \ell^2\tag{iii}
\]
where $\ell^2$
is the Hilbert space
$\ell^2$ whose vectors are complex sequences
$\{\xi_p\}$ such that
$\sum\,| \xi_p|^2<\infty$.


\noindent
From now on Stone's condition hold.
For every 
pair of positive numbers $s.t$ and each $\xi\in \ell^2$ we set:
\[
D_\xi(s,t)=
\sum_{q=1}^\infty\, 
\bigl |\frac{1}{t}\cdot 
\sum_{p=1}^\infty\, c_{qp}(t)\xi_p-
\frac{1}{s}\cdot 
\sum_{p=1}^\infty\, c_{qp}(s)\xi_p+(\frac{1}{s}-\frac{1}{t})\xi_q\,\bigr |^2
\]
\newpage

\noindent
{\bf{Stones Theorem.}}
\emph{There exists a  dense subspace
$\mathcal H_*$ of the Hibert space $\ell^2$
such that}
\[
 \lim_{(s,t)\to (0,0)}\, D_\xi(s,t)=0\quad\colon\quad \xi\in\mathcal H_*
\]
 \emph{Moreover, to each $\xi\in\mathcal H_*$ we get the limit vector
 $\eta= \{\eta_q\}$ where}
 \[
 \eta_q=\lim_{t\to 0}\, \frac{1}{t}\,\cdot 
\bigl[\,  \sum_{p=1}^\infty c_{qp}(t)\xi_p- \xi_q\,\bigr]
\]
\emph{ Finally, the linear operator}
{\[
A(\xi)=i\cdot \eta
\]
\emph{is a densely defined
self-adjoint operator.}
\bigskip


\centerline {\bf{A.3 Unbounded self-adjoint operators.}}
\medskip

\noindent
Let  $\mathcal H$ be a Hilbert space
and consider a closed and densely defined 
linear operator $A$ which in general is unbounded.
One says that $A$  is  symmetric
if
\[ 
\langle Ax,y\rangle= \langle x,Ay\rangle
\quad\colon\,  x,y\in\mathcal D(A)\tag{0.1}
\]
Let $E$ be  the identity operator on
$\mathcal H$. 
If $x\in\mathcal D(A)$
and $\lambda$ is a complex number the symmetry gives:
\[
 ||(\lambda\dot E-A)(x)||^2=
 |\lambda|^2\cdot ||x||^2+||Ax||^2-
 2\cdot \mathfrak{Re}\,\lambda\cdot \langle x,Ax\rangle 
\] 
The Cauchy-Schwarz inequality gives:
\[
|\langle x,Ax\rangle|\leq ||x||\cdot ||Ax||\implies
||(\lambda\dot E-A)(x)||^2\geq |\mathfrak{Im}\,\lambda|^2\cdot ||x||^2\tag{0.2}
\]

\medskip

\noindent
Since $A$ has a closed graph
the inequality
(0.2) implies that if $\mathfrak{Im}\,\lambda\neq 0$ then
the operator $B=\lambda\cdot E-A$
sends $\mathcal D(A)$ into a closed subspace of $\mathcal H$.
Since Hilbert spaces are self-dual
the range $B(\mathcal D(A))$
is therefore $\neq \mathcal H$ if and only if its orthogonal complement is 
$\neq\emptyset$.
A  vector $y$ belongs  to $B(\mathcal D(A))^\perp$ if
\[
\lambda\cdot\langle x,y\rangle=
\langle Ax,y\rangle
\quad\,\colon\quad  x\in\mathcal D(A)\tag{*}
\]
So if 
(*) has no solutions $y\neq 0$  when
$\mathfrak{Im}\,\lambda\neq 0$  then 
$\lambda\cdot E-A$ is  surjective for every non-real complex number
and together with the inequality (0.2) we see that
$\lambda\cdot E-A$ is invertible in the sense of (0.0.1).
Hence it has a resolvent and
we find the operator
valued analytic function $R_A(\lambda)$
defined outside the real axis in the complex $\lambda$-plane.
\medskip

\noindent
{\bf{Remark.}}
In ¤ 9 we  study
symmetric and densely defined operators 
satisfying the above. 
A notable fact is that if (*) has no solution
$x\neq 0$ when
$\lambda$ is not real, then
the symmetric operator $A$ is equal to its adjoint $A^*$.
The detailed proofs appear in ¤ 9.







\bigskip


\centerline{\bf{A.4 Differential operators}}.
\medskip

\noindent
Pioneering work by  G.D. Birkhoff carried out around 1905
motivated and inspired  subsequent studies of unbounded
densely defined operators on Hibert spaces. Let
\[ 
P(t,\frac{d}{dt})=\sum_{j=0}^{j=m}\, a_j(t)\cdot \frac{d^j}{dt^j}
\] 
be a differential operator where we 
$\{a_j(t)\}$ are complex-valued polynomials.
The adjoint operator $P^*$ is defined by the equation
\[
\int\, P(f)\cdot \bar g\, dt=
\int\, f\cdot\overline {P^*( g)}\, dt
\] 
for each  pair of test-functions $f$ and $g$. 
If $P=P^*$ we say that $P$ is symmetric.
Assume this and consider some bounded interval $(a,b)$ which gives 
the Hilbert space
$L^2(a,b)$.
Now $P$ yields  a densely defined but unbounded operator on
this Hilbert space   denoted by $T_{ab}$.
We shall learn  that there exists
the adjoint operator $T_{ab}^*$ which also is densely defined
on $L^2(a,b)$.
However, the symmetry may be lost under this construction and
the search for  self-adjoint extensions of
$P$ on $L^2(a,b)$ leads to an involved theory.
Results concerned with
spectral theory of ordinary differential operators
are foremost due to Birkhoff,  
Weyl, Titschmarsh and Kodaira. These authors  also found
various boundary conditions  in
order to achieve self-adjoint extensions of
$P$. A notable fact is that when $P$ is a given symmetric ODe-operator,
then the  class of self-adjoint extensions to the Hilbert space $L^2(a,b)$ 
can  depend upon the interval $(a,b)$. We refrain from
a detailed discussion. The
reader may consult
chapter XIII from volume 2  in [Dunford-Schwartz] which offers an 
extensive account
about spectral theory for ordinary differential equations.


\bigskip





\newpage


 
 





\centerline {\bf{A.7 Moment problems.}}
\medskip

\noindent
In 1894 Stieltjes established
necessary and sufficient conditions for the existence of solutions
to the following equation: There is given a
sequence $\{c\uuu n\}$ of non-negative real numbers.
One asks if there exists a non-negative measure $\mu$ on
the real $x$-line such that
\[
\int_{-\infty}^\infty\, x^n\cdot d\mu(x)= c_n
\] 
hold for each $n=1,2,\ldots$.
No specific bound on $\{c_n\}$ is
imposed and Stieltjes solution relies upon properties 
of
continued fractions  associated to 
$\{c_n\}$.
The moment problem 
inspired
later studies
in operator theory.
Elegant results appear in  Stone's 
book  \emph{Linear operators on 
Hilbert spaces and their applications to analysis} (AMS: 1932).
For example, Stone proved a
uniqueness result which goes as follows: Denote by $\mathcal P_*$
the class of non-negative measures $\mu$ on the real line such 
\[
\int\, x^{2n}\cdot d\mu(x)<\infty\quad\colon\quad n=1,2,\ldots
\]
To each such measure $\mu$ one gets  a unique sequence of polynomials
$\{P_n(x)\}$, where  $P_n$ has degree $n$ and leading coefficient $>0$
while
\[
\int_{-\infty}^\infty\, P_n(x)P_m(x)\cdot d\mu(x)=0
\quad\colon\quad n\neq m
\]
A measure $\mu\in \mathcal P_*$ is of the Stone type if
\[
\sum_{n=0}^\infty\,|P_n(x+iy]^2=+\infty
\]
hold for every non-real complex number $z=x+iy$
with 
$y\neq 0$. Now Stone's uniqueness theorem asserts the following:
\medskip

\noindent
\emph{A pair
 $\mu,\nu$  of 
Stone type with equal   moments
for allÊ$n$ must be identical, i.e.  
$\mu=\nu$.}




\bigskip




\centerline {\bf{A.8 Optimal control theory.}}
\medskip



\noindent
Problems in the calculus of variation can
lead to severe doubts  about the existence of extremal solutions. This
was put forward by Weierstrass and a historic example is LamŽ's equation where
tentative  proofs of existence of solutions occured
in work by  Kovavelsky and Volterra but  
It was not until 1920
that
Zeilon settled the existence of solutions to LamŽ's equations
using advanced  Fourier analysis. In 
retrospect we mention that Zeilon's proof already used distribution-theoretic methods.
There also occur
optimization problems where
the control is restricted to vector-valued functions
with
range in a compact polyhedron  $\Pi$  in
${\bf{R}}^n$. In such problems
one often arrives at    
Bang-bang solutions where
the extremal control switches a finite number of times
between  extreme points of the polyhedron $\Pi$. In this pioneering work
which led to a general maximum principle in control problems,
Pontryagin
employed
functional analysis where one allows
competing families of control functions in  spaces  
of measurable functions.
The outcome is
a Bang-bang solution which is piecewise constant while its   existence
is   demonstrated  via a "detour into  larger spaces". So
functional analysis has  a wide range of applications
in optimization theory.







\bigskip



\centerline {\bf{A.10 $L^p$-inequalities.}}

\medskip


\noindent
Many results which originally  were 
constrained to  specific situations
can be extended  when
notions in
functional analysis are adopted. An  example
is  a theorem 
from the article [Hšrmander-1960]
where  singular integrals
are  treated  in a  general context.
Here is the set up: Let $B_1$ and $B_2$ be two Banach spaces
and $n$ some positive integer.
Let $K(x)$ be a function which for every 
$x\in{\bf{R}}^n$ assigns a vector 
in the Banach space
$L(B_1,B_2)$ of continuous linear operators from $B_1$ to $B_2$.
One only assumes that $K$ is a continuous function, i.e. it 
need not be linear.
If $f(x)$ is a continuous  $B_1$-valued function defined in
${\bf{R}}^n$ with compact support there exists
the convolution integral
\[
\mathcal Kf(x)= \int_{{\bf{R}}^n}\, K(x-y)(f(y))\, dy
\]
To be precise, with $x$ fixed in
${\bf{R}}^n$ the right hand side is
a welldefined $B_2$-valued integral which exists
because  $K(x-y)$ as a linear operator sends the
$B_1$-vector $f(y)$ into $B_2$, i.e. the integrand
in the right hand side is a $B_2$-valued function
\[ 
y\mapsto K(x-y)(f(y))
\] 
which can be integrated with respect to $y$ and the resulting
integral  yields
the $B_2$-vector in the left hand side. When $x$ varies,
$x\mapsto \mathcal Kf(x)$
becomes a $B_2$-valued function.
Following [ibid] we
impose two   conditions on $K$ where
norms on the three Banach spaces $L(B_1,B_2),B_1,B_2$ appear.
We say that $K$ satisfies the Hšrmander condition if there
exist positive constants $A$ and $C$ such that
the following hold for every real number $t>0$:
\[ 
\int_{|x|\geq 1}\, ||K(t(x-y))-K(tx)||\, dx\leq C\cdot t^{-n}
\quad\text{for all}\quad |y|\leq 1\tag{1}
\]
where the left hand side
employs 
the operator norms of $K$  defined for pairs of points  $tx$ and
$t(x-y)$ in ${\bf{R}}^n$. In addition to (1) we impose
the following $L^2$-inequality for every function $f$ with the 
same constant $C$ as above:
\[
\int_{{\bf{R}}^n}\, ||\mathcal Kf(x)||_2^2\, dx\leq
C^2\cdot \int_{{\bf{R}}^n}\,||f(x)||_1^2\, dx\tag{2}
\]
Here one has used norms on $B_1$ respectively $B_2$ during the integration.
Hšrmander  extended    Vitali's  Covering Lemma in ${\bf{R}}^n$
to a similar covering  principle on arbitrary normed spaces 
to prove the following weak-type inequality:
\medskip

\noindent
{\bf{Theorem.}}
\emph{There exists an absolute constant $C_n$ which depends on 
$n$ only such that for every
pair  of Banach spaces $B_1,B_2$ and every linear operator $K$
which satisfies (1-2), the following hold for every
$\alpha>0$:}
\[
\text{vol}_n(\{x\in{\bf{R}}^n\,\colon\,  ||\mathcal Kf(x)||_2 >\alpha\})\leq
\frac{C_n\cdot C}{\alpha}\cdot \int_{{\bf{R}}^n}\, ||f(x)||_1\, dx
\]


\noindent
{\bf{Remark.}}
This result 
has a wide range of applications
when it is combined  with
interpolation theorems  due to Markinkiewicz and Thorin.
For example, classical results which involve $L^p$-inequalties 
during the passage to Fourier transforms or other   kernel functions
can be put into a general  frame where one  employs
vector-valued functions rather than
scalar-valued functions. Typical examples occur when
$K$ sends real-valued functions
to vectors in a Hilbert space, i.e. here 
$B_1$ is  the 1-dimensional real line  and
$B_2=\ell^2$.
So Hšrmander's  result constitutes a veritable propagande for
learning  general notions in functional analysis. The
idea to regard vector-valued
functions
was of course  considered at an early stage. 
An  example is
a theorem due to Littlewood and Paley
which goes as follows: Let $f(x)$ be a function on the real line 
such that both $f$ and $f^2$ are integrable.
To each integer $n\geq 0$
we set
\[
f_n(x)=
\bigl|\int_{2^{n-1}}^{2^n}\, e^{ix\xi}\cdot \widehat f(\xi)\, d\xi\,\bigr|+
\bigl|\, \int_{-2^{-n}}^{-2^{n-1}}\, e^{ix\xi}\cdot \widehat f(\xi)\, d\xi\,\bigr|
\]
Then it is proved in [L-P] that for each
$1<p\leq 2$ there exists a constant $C_p\geq 1$ such that
\[
C_p^{-1}||f||_p\leq\cdot \int_{-\infty}^\infty\, \bigl(\sum_{n=0}^\infty\, f_n(x)^2\bigr)^{\frac{2}{p}}
\, dx\leq C_p\cdot ||f||_p\tag{*}
\]
where $||f||_p= \bigl(\int\, |f(x)|^p\, dx\bigr)^{\frac{1}{p}}$
is the $L^p$-norm of $f$.
Hšrmander's theorem can be used to  give an elegant proof of (*)
which has the merit that the use
a suitable vector-valued  operator during the proof
becomes
transparent. 




\bigskip









\centerline
{\bf B. Hilbert's  spectral theorem for bounded self-adjoint operators.}
\bigskip

\noindent
The  theory about integral equations
created  by Fredholm
led to 
Hilbert's   result from  1904 
which we  begin to describe.
Let $\mathcal H$ be a Hilbert space
and denote by 
$L(\mathcal H)$
the set of all bounded linear operators on $\mathcal H$.
Every $T\in L(\mathcal H)$ has its operator norm
\[
||T||=\max_x\,||T(x)||\quad
\text{maximum over vectors of norm}\,\,\,\leq 1
\]
Next, let $A$ be
a bounded
self-adjoint operator  on $\mathcal H$ whose compact spectrum is denoted by
$\sigma(A)$.
A crucial fact is that the self-adjointness implies that
\[
||A||^2=||A^2||
\]
and passing to higher powers it follows that
the operator norm
$||A||$ is equal to the spectral radius defined by
\[
\lim_{n\to\infty}\, ||A^n||^{\frac{1}{n}}
\]
Using this equality
the Operational Calculus in ¤ 7
will show that there exists
an algebra isomorphism from
the sup-norm algebra $C^0(\sigma(A))$
into a closed subalgebra $\mathcal A$ of $L(\mathcal H)$, i.e. 
each  continuous function $g$ on the compact spectrum
$\sigma(A)$ gives  a bounded linear operator $G$. 
Moreover, it is an
isometry which means that
\[ 
|g|_{\sigma(A)}= ||G||\tag{*}
\] 
where the left hand side is the maximum of $|g|$ over $\sigma(A)$.
Next, since  $A$ is self-adjoint  $\sigma(A)$
is a compact subset of the real line
where we use $t$ as the variable.
If $g(t)=c_0+c_1t+\ldots+c_mt^m$
is a polynomial, the operational calculus shows that
$G=E+c_1A+\ldots+c_mA^m$
where $E$ is the identity operator on
$\mathcal H$.
By Weierstrass' theorem the set of polynomials
a dense subalgebra of $C^0(\sigma(A))$
and hence $\mathcal A$ is the closure
in $L(\mathcal H)$ of the
algebra formed by all polynomials of $A$.
\medskip

\noindent
{\bf{B.1 The spectral measure.}}
The algebra isomorphism  gives
a map
from the product
$\mathcal H\times\mathcal H$ to the space of Riesz measures on
$\sigma(A)$ which to every
pair $(x,y)$ in $\mathcal H$ assigns a Riesz measure
$\mu_{x,y}$
such that
\[
\langle g(A)x,y\rangle=\int_{\sigma(A)}\,
g(t)\cdot d\mu_{x,y}(t)\tag{**}
\] 
holds for every $g\in C^0(\sigma(A))$.
The isometry  (*)   implies
that the total variation of $\mu_{x,y}$ is bounded by
$||x||\cdot ||y||$ for every pair $x,y$.
Now Borel's integrals give
a larger subalgebra of $L(\mathcal H)$. Namely, for
every bounded Borel function $g(t)$ on $\sigma(A)$
the integrals in the sense of Borel 
exist in the right hand side of (**) for each 
pair $x,y$ in $\mathcal H$.
In this way
the $g$-function
gives a
bounded linear operator $G$ such that
\[
\langle G(x),y\rangle=\int_{\sigma(A)}\,
g(t)\cdot d\mu_{x,y}(t)\quad\text{hold for all pairs}\quad
x,y\tag{***}
\] 


\noindent
This yields  an algebra isomorphism from
the algebra $\mathcal B^\infty(\sigma(A))$
of bounded Borel functions to a subalgebra of $L(\mathcal H)$ 
denoted by
$B(\mathcal A)$.
Again the map $g\mapsto G$ is an isometry
and in this extended algebra 
we can construct
an ample family of self-adjoint operators.
Namely, for every Borel subset $\gamma$
of $\sigma(A)$ we can take its characteristic function
and  get the bounded linear operator $\Gamma$.
By the Operational Calculus the
spectrum of $\Gamma$ is equal to the closure of $\gamma$.
Moreover, $\Gamma$ is a self-adjoint operator and  commutes with
$A$.
In particular we can consider  partitions of
$\sigma(A)$. Namely, choose $M>0$ so that
$\sigma(A)\subset [-M,M]$ and $M$ is outside $\sigma(A)$.
With a large integer $N$
we consider the half-open intervals
\[
\gamma_\nu=\bigl [-M+\frac{\nu}{N}\cdot M, -M+\frac{\nu+1}{N}\cdot M\bigr]
\quad\colon 0\leq \nu\leq 2N-1
\]
Then $\Gamma_0+\ldots+\Gamma_{2N-1}=E$ and
we also get the decomposition
\[
 A=A_0+\ldots+A_{2N-1}\quad
 \colon\,A_\nu=A\Gamma_\nu\tag{1}
\]
Above $\{\Gamma_\nu\}$ gives a  \emph{resolution of the identity}
where (1) means that $A$ is a sum of 
self-adjoint operators where every individual operator has a spectrum
confined to an interval of length
 $\leq \frac{1}{N}$. This 
constitutes 
Hilbert's Theorem for bounded self-adjoint operators.



\bigskip



\centerline {\bf C. Carleman's spectral theorem for unbounded self-adjoint operators}
\bigskip

\noindent
In a note from May 1920 [Comptes rendus], Carleman 
described  a procedure to handle unbounded symmetric
operators
expressed via integral kernels which fail to satisfy
Fredholm's  conditions. The  theory was presented
in the monograph 
\emph{Sur les Žquations singulires ˆ noyau
rel et symmŽtrique} from
1923 published by  Uppsala University.
In addition to [ibid]
the reader may also consult Carleman's plenary talk [Carleman]
at the Scandinavian
Congress held at Copenhagen in 1925
where the relation to
the new spectral theory with Fredholm's
pioneering discoveries is discussed and illuminated by
various examples.
For historic reasons  we give a citation from
the introduction  in [ibid]
where Carleman
expressed his admiration for Fredholm's work:
\emph{Peu du dŽcouvertes mathŽmatiques ont ŽtŽ donnŽes
par leur auteur sous une forme si achevŽe que la dŽcouverte
de la solution de l«Žquation intŽgrale}
\[ 
\phi(x)=\lambda\cdot \int_a^b\,K(x,y)\phi(y)\, dy+ f(x)
\]
\emph{par M. Fredholm. Les nombreuses application de cette thŽorie admirable
ont pourtant amŽnŽ un grand nombere 
de rechereches concerntant le cas —u le noyaue $K(x,y$ est non borneŽ.}

\bigskip




\noindent
{\bf{C.1 An ugly example.}}
Following 
in [Carleman 1923 ] we
give  an example which
illustrates that
new phenomena can occur for unbounded symmetric operators.
On the unit interval $[0,1]$ we have  an orthonormal family of
functions $\psi_0,\psi_1,\ldots$ where
$\psi_0=1$ is the identity and
$\psi_1(x)= -1$ on $(0,1/2)$Êand +1 on $(1/2,1)$. For each 
$n\geq 2$ we set:
\[
\psi_n(x)=-2^{\frac{n-1}[{2}} \,\colon\,
1-2^{-n+1}\leq x< 1-2^{-n}
\quad\text{and}\quad
\psi_n(x)=2^{\frac{n-1}{2}}\,\colon\, 1-2^{-n}<x<1
\]
while $\psi_n(x)=$ when $0<x< 1-2^{-n+1}$.
If $\{a_p\}$ is a sequence of real numbers we define
the kernel
function  on $[0,1)\times [0,1)$
by
\[
K(x,y)=\sum\, a_p\cdot \psi_p(x)\psi_q(x)\tag{i}
\]
It is clear that $K$
is symmetric and the associated operator 
\[
\mathcal K(u)(x)=\int_0^1\, K(x,y)u(y)\, dy
\]
is  defined on $L^2$-functions $u$ supported by
$0\leq x\leq x_*$ for every  $x_*<1$ and therefore  densely defined.
Choose a sequence $\{a_p\}$ such that
the positive series.
\[
\sum_{p=0}^\infty \, \frac{2^p}{1+a_p^2}<\infty\tag{ii}
\]
This convergence  means that
the sequence $\{a_p\}$ must have a high rate of growth so
the kernel function (i) becomes  turbulent when
$x$ and $y$ approach 1.
\medskip

\noindent
{\bf{Exercise.}}
Show that (ii) entails that there exists an $L^2$-function
$\phi(x)$ such that $\mathcal K(\phi)$ also is an $L^2$-function and
\[
\phi= i\cdot \mathcal K(\phi)
\]
If necessary, consult [ibid: page 62-66] for a demonstration. 



\bigskip


\centerline {\bf{A favourable case.}}
\bigskip

\noindent
We begin to 
expose Carleman's result for "wellbehaved"
integral operators.
Let $K(x,y)$ be a complex-valued function defined in
the open unit square$\{0 <x,y<1\}$
satisfying the hermitian condition
\[ 
K(y,x)= \bar K(x,y)
\]
Assume  that for all $x$ outside a nullset $\mathcal N$
one has a finite integral
\[ 
\int_0^1\, |K(x,y)|^2\, dy\tag{1}
\]
If $\phi(y)$ is an $L^2$-function, 
the Cauchy-Schwartz inequality gives:
\[
\int_0^1\, K(x,y)\phi(y)\, dy\quad\text{exists for all} 
\quad x\in (0,1)\setminus \mathcal N
\]


\medskip

\noindent
{\bf{C.2 Definition.}} \emph{The hermitian kernel $K$ is of type
I if
the homogeneous equation}
\[
\phi(x)=\lambda\cdot \int_0^1\, K(x,y)\phi(y)\, dy
\]
\emph{has no non-trivial $L^2$-solution $\phi(y)$ when
$\mathfrak{Im}\,\lambda\neq 0$.}


\newpage


\noindent
{\bf{C.3 Theorem.}}
\emph{If $K$ is of type I  the equation}
\[
\phi(x)=\lambda\cdot \int_0^1\, K(x,y)\phi(y)\, dy+f(x)\tag{*}
\]
\emph{has a unique $L^2$-solution $\phi$ for every
$f\in L^2$ and every non-real $\lambda$. Moreover
the $\phi$-solution satisfies:}
\[
\int_0^1\, |\phi(x)|^2\,dx\leq \frac{|\lambda|^2}{\mathfrak{Im}(\lambda)^2}
\cdot  \int_0^1\, |f(x)|^2\,dx\tag{**}
\]
\medskip

\noindent {\emph{Proof}}.
To get the existence we use the truncated kernels
$\{K_n(x,y)\}$
where $K_n(x,y)=K(x,y)$ when
$K(x,y)|\leq n$ and otherwise zero.
Given  $f(x)\in L^2[0,1]$ and a non-real
$\lambda$, the Hilbert-Schmidt theory from ¤ xx gives
a unique $\phi_n\in L^2$ such that
\[
\phi_n(x)=\lambda\cdot \int_0^1\, K_n(x,y)\phi_n(y)\, dy+f(x)\tag{i}
\]
Mutltiplying with $\bar\phi_n$ it follows that
\[
\frac{1}{\lambda}\, 
 \int_0^1\, \bar\phi_n(x)(\phi_n(x)-f(x))\, dx=
 \iint_\square \, K_n(x,y)\bar\phi_n(x)\phi_n(y)\, dxdy
\] 
Since $K_n$ is hermitian the right hand side is real  and taking imaginary
parts we obtain

\[
\bigl(\frac{1}{\lambda}-\frac{1}{\bar\lambda}\bigr)\cdot
 \int_0^1\, |\phi_n(x|^2\,dx)=
\frac{1}{\lambda}\cdot
 \int_0^1\, \bar \phi_n(x)f(x) dx)
 -\frac{1}{\bar \lambda}\cdot
 \int_0^1\, \phi_n(x)\bar f(x) dx)\tag{ii}
\] 
and the Cauchy-Schwarz inequality 
gives
\[
 \int_0^1\, |\phi_n(x)|^2\,dx\leq \frac{|\lambda|^2}{\mathfrak{Im}(\lambda)^2}
 \cdot  \int_0^1\, |f(x)|^2\,dx\tag{iii}
\]
Hence the $L^2$-norms of $\{\phi_n\}$ are uniformly bounded
and we can
find a subsequence which converges weakly to an
$L^2$-function $\phi$ whose $L^2$-norm again is bounded
by the right
hand side in (iii). 
Now the assumption that $K$ is of type I
entials that the weak limit is unique.
Hence the whole sequence $\{\phi_n\}$ is weakly convergent
and one verifies
that $\phi$ solves the inhomogeneous equation (*).



\bigskip










\noindent
{\bf{C.4 Spectral resolution.}}
Let $K(x,y)$ be a hermitian kernel of type I.
Hilbert's theorem applies to the bounded
kernels $\{K_n\}$
and give for each pair $f,g\in L^2[0,1]$
a Riesz measure
$\mu^n_{f,g}$ supported by the compact real spectrum of
the kernel operator defined by $K_n$.
In [Carleman]
it is  proved that
the sequence
$\{\mu_{f,g}^n\}$ converges weakly to a
Riesz-measure $\mu_{f,g}$ supported by the real line
and Hilbert's operational calculus applies when
one intergates continuous functions
$\phi(t)$ with compact support, i.e. every
such $\phi$ yields a bounded
linear operator
$\Phi$ on $L^2[0,1]$ such that
\[
\int_0^1\, \Phi(f)\cdot \bar g\, dx=
\int\, \phi(t)d\mu_{f,g}(t)
\]
hold for every pair $f,g$Êin $L^2[0,1]$.


\bigskip



\bigskip



\centerline {\bf{D. The Bohr-Schršdinger  equation.}}
\medskip

\noindent
In 1923 quantum mechanics had not yet appeared so
the studies in  [Carleman] were 
concerned with singular  integral equations, foremost
inspired from  work by Neumann, PoincarŽ,
Fredholm and Volterra.
The creation of quantum mechanics gave new challenges for
mathematicians.
The interested reader should   consult the
lecture held  by Niels Bohr at the Scandianavian congress in mathematics
held in Copenhagen 1925 where he
speaks  about  the   interplay between
the new physics and 
"pure" mathematics. 
Bohr's  lecture  presumably inspired Carleman when he
some years later resumed 
work from [Car 1923].
Recall that the fundamental point in Schršdinger's theory
is the hypothesis on energy levels which correspond to 
orbits in Bohr's theory of atoms. For a very good account about
the physical background
the reader may consult
Bohr's
plenary talk when 
he received the Nobel Prize in physics 1923.
Mathematically the Bohr-Schršdinger theory
leads to the  equation
\[ 
\Delta\phi+2m\cdot\bigl( E-U\bigr)\bigl(\frac{2\pi}{h}\bigr)^2\cdot \phi=0\tag{*}
\] 
Here $\Delta$ is the Laplace operator in the 3-dimensional $(x,y,z)$-space,
$m$ the mass of a particle and $h$  Planck's constant
while   $U(x,y,z)$ is a potential function.
Finally $E$ is a parameter and one seeks values on $E$
such that (*) has a solution $\phi$
which belongs to $L^2({\bf{R}}^3)$.
Let us   cite an excerpt   from Carlemans  lectures in Paris at 
Institut Henri PoincarŽ held in 1930:
\medskip

\noindent
\emph{Dans ces dernires annŽes l'’nteret de la question qui nous
occupe a considŽrablement augmentŽ.
C'est en effet
un instrument mathŽmatique 
indispensable pour development de la mechanique moderne crŽe par
M.M. de Brogile, Heisenberg et Schršdinger. Etude de l'Žquation
integrale:}
\[ 
\phi(x)= \lambda\cdot \int_a^b\, K(x,y)\phi(y)dy+f(x)
\quad\colon\lambda\in {\bf{C}}\setminus {\bf{R}}
\]
\medskip

\noindent
The theory from [Carleman :1923] applies  to the following
PDE-equations attached to a second order differential operator
\[ 
L=\Delta+c(x,y,z)\quad\colon
\Delta=\partial_x^2+\partial_y^2+\partial_z^2\tag{**}
\]
where $c(x,y,z)$ is a real-valued function.
The $L$-operator is  densely defined and  symmetric on the
dense subspace formed by
test-functions $u$ in
${\bf{R}}^3$. The problem is to find conditions on
the $c$-function in order that
the  Case I  from ¤ B  occurs.
The following
sufficiency result is proved in [ibid]:
\medskip

\noindent
{\bf{D.1 Theorem }}
\emph{Let $c(x,y,z)$ be a continuous and real-valued function
such that there is a constant $M$ for which}
\[
\limsup \uuu{x^2+y^2+z^2\to \infty}\, c(x,y,z)\leq M
\]
\emph{Then  Case I holds for the operator $\Delta+c(x,y,z)$.}
\medskip

\medskip

\noindent{{\bf{Example.}}
Considers a potential function:
\[ 
W(p)=\sum\,\frac{\alpha_k}{|p-q_k|}+\beta
\] 
where $\{q_k\}$ is a finite subset of
${\bf{R}}^3$ and the $\alpha$-numbers and $\beta$ are real and positive.
With $c=W$ we get Case I and hence
solutions to the Schršdinger equation can be established
via a robust limit process. See ¤¤ xx for details.

\bigskip


\noindent
{\bf{Further comments.}} The literature about
the Schršdinger equation and  other
equations which emerge from quantum mechanics is 
extensive. 
For the 
source of quantum mechanics
the reader should first of all consult 
the plenary talks by Heisenberg, Dirac and Shršdinger
when they received the Nobel prize in
physics. 
Apart from physical considerations the reader
will find
expositions where explanations
are given in a mathematical framework.
Actually Heisenberg was
sole winner 1931 while Dirac and Schršdinger shared the
prize in 1932. But they visited Stockholm together in
December 1932.
\medskip

\noindent
For  mathematician who wants to become acquainted with
quantum physics the eminent text-books by Lev Landau
are recommended. Especially 
\emph{Quantum mechanics: Non-relativistic theory}
in Vol. 3.
The
relativistic case  is treated in later volums of [L-L]. Here
one employs Heisenberg's matrix representation and
Dirac's  equations are used to study radiation phenomena.
In the introduction to
[ibid: Volume 3]
Landau inserts the following remark:
\emph{It is of interest to note
thst the complete mathematical formalisim
of quantum mechnaics was constructed by W. Heisenberg
and E. Schršdinger in 1925-26, before the discovery
of the uncertainty principle which revealed the physical
contents of this formalism.}
\medskip


\noindent
In the non-relativistic situation one studies
foremost 
wave equations of
Schršdinger's type. The  mathematical foundations
were laid in Schršdinger's article 
\emph{Quantizierung als Eigenwertproblem} from 1926
In ¤ XX from Special Topics we describe another of Schršdinger's equations which
led to a veritable challenge in the "world of mathematics"
which remains  quite open.
\bigskip

\noindent
{\bf{Final remark.}}
After [Carleman 1923] an alternative
proof of the spectral theorem for unbounded operators on
Hilbert spaces was given by  
J. von Neumann's   in the article \emph{Eigenwerttheorie Hermitescher 
Funktionaloperatoren} from 1929.
Neumann''s account seems  to have become
more fashion by  readers who prefer a  "formal style".
A merit in Neumann's work
is that 
some measure theoretic technicalities  
in  Carleman's proof
can be omitted. On the other hand 
it  is often necessary to establish
formulas of a measure theoretic character in order to apply
the spectral theorem. An example
is  Carleman's  solution to the 
Bohr-Schršdinger equation which he presented  during  lectures at Sorbonne
in 1930. Here
the Laplace operator  in
${\bf{R}}^3$ is transformed to a suitable integral operator. After this
estimates which lead to solutions
in $L^2){\bf{R}}^3)$ are obtain via
solutions to Neumann's boundary value problem in
increasing balls in
${\bf{R}}^3$.
Let us also remark
that
separable  Hilbert spaces  can be embedded into $L^2$-spaces.
So
the restriction to integral operators covers most applications.
In Chapter 1 from [Carleman] the reader may find a very general construction
of a family of 
spectral functions associated with Hermitian kernels which need not satisfy 
the condition from Definition B.2 above.


\medskip

\noindent
{\bf{Examples.}}
From a historic point of view we mention that various unbounded
symmetric operators
were studied in connecttion with differential operators
in work by
Birkhoff, Picard and Weyl around 1910.
Picard's equation was already described in
the introduction.
More generally one can consider kernel functions of the form
\[ 
K(x,y)=H_1(|x-y|)+ H_2(|x+y|)
\]

\noindent
which give linear operators on
$L^2({\bf{R}}$.
In [Carleman: Chapitre 4 ] it is proved that
$K$
is of class I when
\[
 \int_{-\infty}^\infty\, H_\nu(s)^2\,  ds<\infty\tag{i}
\] 
hold for $\nu=1,2$.
To prove this one seeks solutions to the integral equation
\[ 
\phi(x)=\lambda\cdot
 \int_{-\infty}^\infty\,K(x,y)\phi(y)\, dy+f(x)
\]
where $f$ is a given $L^2$-function on the real line
and $\lambda$ in genereal is a complex number.
In ¤ xx we shall expose material from [Carleman 1923] and construct
Neumann's sresolvent 
to the integral operator $K(x,y)$ which after
settles why 
(i) entails that it is self-adjoint.
We remark that in this construction
one employs specific solutions to
Picard's equation. 
The result above
can then be  applied  to analyze
integral operators in ${\bf{R}}^3$
defined by kernel functions
\[
S(p,q)= F(|p-q|)
\]
where
\[ 
\int_0^\infty\, F(r)^2 \cdot r\, dr<\infty 
\]
Another  interesting class of integral operators are given by
\[ 
K(x,y)=\frac{P(x,y)}{Q(x,y)}
\]
Here $P$ is a polynomial of some degree 
$m\geq 1$, and $Q(x,y)$ is homogeneous of degree $m+1$ which 
takes real and positive values when
$x$ and $y$  both are $>0$.
Already the special case when
\[
K(x,y)=\frac{1}{x+y}
\]
leads to some non-trivial conclusions.
In ¤ xx we prove that the spectrum
on the Hilbert space of square integrable functions
in the positive quadrant of
${\bf{R}}^2$ is the unbounded interval $[\pi^{-1},+\infty)$.





 
 








\newpage

\centerline{\bf{E. Application to a dynamical system.}}

\bigskip

\noindent
Using the spectral theorem
a rigorous proof of the Ergodic Hypothesis in
Statistical Mechanics
was given by Carleman
at seminars held at Institute Mittag-Leffler
in May 1931. Here is
the situation: There is given an $n$-tuple of
$C^1$-functions $A_1(x),\ldots,A_n(x)$ where
$x=(x_1,\ldots,x_n)$ are points in ${\bf{R}}^n$.
Let $t$ be a time variable and consider the differential system
\[
\frac{dx_k}{dt}= A_k(x_1(t),\ldots,x_n(t))\quad\colon\quad 1\leq k\leq n\tag{1}
\]
Assume that there exists a compact hypersurface
$S$ in ${\bf{R}}^n$
such that
if $p\in S$ and ${\bf{x}}_p(t)$ is the 
vector-valued solution to (1) with initial condition
${\bf{x}}_p(0)=p$, then
${\bf{x}}_p(t)$ stay in $S$ for every $t$.
The uniqueness for solutions to the differential systems above gives
for every $t$ a bijective map $p\mapsto {\bf{x}}_p(t)$ from $S$ onto itself. It is denoted by
$\mathcal T_t$ and we  notice that
\[
 \mathcal T_s\circ \mathcal T_t=\mathcal T_{s+t}
\]

\noindent
In addition to this we assume that there exists an invariant measure $\sigma$ on $S$
for the $\mathcal T$-maps. In other words, a non-negative measure
$\sigma$ such that
\[ 
\sigma(\mathcal T_t(A))=\sigma(A)
\] 
hold for every $\sigma$-measurable set. For the applications it suffices to consider the
case when $\sigma$ is absolutely continuos, i.e. a positive
continuous function times the area measure on $S$.
So now we have the Hilbert space $L^2(\sigma)$ of complex-valued
measurable functions $U$ on $S$ for which
\[ 
\int_S\, |U(p)|^2\cdot d\sigma(p)<\infty
\]
next, on the Hilbert space $L^2(\sigma)$ there exists
the following densely defined symmetric operator:
\[
U\mapsto i\cdot \sum_{\nu=1}^{\nu=n}\, A_\nu\cdot \frac{\partial U}{\partial x_\nu}\tag{*}
\]
It is easy to verify that \emph{Case 1} holds for this operator
and hence we can apply the spectral theorem.
In particular,  to each 
a pair of $L^2$-functions $U$ and $V$ we consider
the following mean-value integrals over time intervals $[0,T]$:
\[
J_T(U,V)=\frac{1}{T}\cdot \int_0^t\,
\bigl[U(\mathcal T_t(p))\cdot V(p)\cdot d\sigma(p)\bigr ]\cdot dt \tag{*}
\]

\medskip

\noindent
Using the spectral theorem from [Carleman 1923], the result below was
proved in 
[Carleman 1931]:
\medskip

\noindent
{\bf{Theorem.}}
\emph{Let $\{\omega\uuu\nu\}$
be an orthonormal basis in $\mathcal H$.
For each pair $U,V$ in $L^2(\sigma)$ one has the equality}
\[
\lim_{T\to\infty}\, J_T(U,V)=
\sum_{\nu=1}^\infty\, \langle \omega_\nu,U\rangle \cdot
 \langle \omega_\nu,V\rangle
 \]
\emph{where}
\[
 \langle \omega_\nu,U\rangle =\int_S\, \omega_\nu(p)\cdot U(p)\cdot d\sigma(p)
 \] 
\emph{and similarly with $U$ replaced with $V$.}
\bigskip

\noindent
{\bf{Remark.}}
Let $\mathcal H_*$ be the space  of $L^2(\sigma)$-functions
which are $\mathcal T$-invariant, i.e. $L^2$-functions $\omega$ satisfying
$\mathcal T_t(\omega)=\omega$  for all $t$.
When
$\mathcal H_*$ is reduced to the  
one-dimensional space of constant functions
the theorem above implies  that almost every trajectory 
comes close to every point in $S$ which confirms  the ergodic condition.
\medskip


\noindent
{\bf{Birkhoff's almost everywhere convergence result.}}
As pointed out  in [1932: page 80 ] where Carleman 
gave an affirmative answer to
a question raised by PoincarŽ in his  lecture
\emph{L'avŽnir dŽs mathematiques}
held at Rome in 1908,  the article [xxx] by Birkhoff published
in December 1931
contains    deeper results which establish  properties which hold  
almost everywhere.
For example, given a point $p_0\in S$
and a measurable subset  $\Omega\subset S$
one can study the
avergage time interval when the particle 
which starts at $p_0$ when $t=0$ visits $\Omega$.
Thus, for $T>0$ we denote by $\tau_{p_0;\Omega}(T)$
the total time of visits in $\Omega$
as $0\leq t\leq T$.
With these notations Birkhoff proved that
\[
 \lim_{T\to\infty}\frac{\tau_{p_0;\Omega} (T)}{T}\tag{*}
\] 
exists for almost all $p_0\in S$.
This impressive result was  the starting point for  extensive studies in
Ergodic Theory which has stayed as an 
active subject.
Many 
subtle problems dealing with almost everywhere convergence properties
have been established,.
Studies of
semi-groups of transformations which are
adapated to stochastic differential
equations is an extensive  subject where
the scenario is almost
"unlimited" since global considerations
occur while
a process  can be  governed by
many different differential systems.
A typical example from recent literature is the article
\emph{Ergodicity of the 2D Navier Stokes equations with degenerate
stochastic forcing} by Hairer and Mattingley.


\newpage




\newpage


\centerline{\bf{11.6 Numerical range.}}
\medskip


\noindent
Let $A$ be a closed and densely  defined linear operator on
the Hilbert space $\mathcal H$.
Its numerical range was introduced by Toeplitz and Hausdorff:

\medskip

\noindent
{\bf{11.6.1 Definition.}}
\emph{The numerical range is the subset of ${\bf{C}}$ defined by}
\[
\text{Num}(A)=\{ \langle Ax,x\rangle\quad\colon
x\quad\text{unit vector in}\quad\mathcal H\}
\]


\noindent
{\bf{11.6.2 Proposition.}}
\emph{The numerical range is  a convex set.}
\medskip

\noindent
\emph {Proof.}
If $\alpha,\beta$ are complex numbers and $B=\alpha A+\beta E$
it is clear that
$\text{Num}(B)$ is the image of 
$\text{Num}(A)$ under 
the linear map $z\mapsto \alpha z+\beta$.
So it siuffices to 
show that when 0 and 1 belong to 
$\text{Num}(A)$,
then the real interval $[0,1]$ stays in the numerical range.
So now we have two vectors $f,g$ for which
\[
\langle Af,f\rangle=0\quad\colon\quad  \langle Ag,g\rangle=1\tag{i}
\]
 To prove this we consider the family of vectors
 \[ 
 \xi= f+se^{i\theta}g
 \] 
where $s\geq 0$ is real and $0\leq\theta\leq 2\pi$.
It follows that
 \[
\langle A\xi,\xi\rangle =s^2+s\bigl
(e^{i\theta}
 \langle Ag,f\rangle+
e^{-i\theta}
 \langle Af,g\rangle\bigr)
 \]
\medskip


\noindent
Above we have the complex-valued function
\[
\theta\mapsto  
e^{i\theta}
 \langle Ag,f\rangle+
e^{-i\theta}
 \langle Af,g\rangle
\]
Since $e^{i\pi}=-1$ its value has opposed signs
at 0 and $\pi$ which  implies that
the imaginary part by the usual  mean-value theorem has some
zero $0\leq \theta_*\leq\pi$.
So with  $\xi_*=\xi= f+se^{i\theta_*}g$ it follows that
\[ 
\langle A\xi_*,\xi_*\rangle =s^2+s\cdot \rho
\quad\text{where}\quad \rho\in{\bf{R}}
\]
The right hand side is zero when $s=0$ and tends to $+\infty$ when
$s$ increases and hence this its range contains $[0,1]$ which give
$s$-values for which  $f+se^{i\theta_*} g$ and hence 
numerical values at every point in $[0,1]$.
\bigskip

\noindent
Next, let $A$ be a bounded linear operator. In this case it
is clear that $\text{Num}(A)$ is a bounded set.
However, it is in general not closed. See ¤ below for an example.
The following inclusions hold:

\medskip

\noindent
{\bf{11.6.3 Theorem.}} \emph{For every bounded operator $A$ one has}

\[
\sigma(A)\subset
\overline{\text{Num}(A)}\subset\widehat{\sigma(A)}
\]
\emph{where the right hand side is the convex hull of $\sigma(A)$.}
\bigskip

\noindent
\emph{Proof.}
TO BE GIVEN....











\centerline {\bf{11.5 Stones theorem.}}


\bigskip


\noindent

\noindent
{\bf{11.3.2 Unitary semi-groups.}}
Specialize the situation above to the case when
$B$ is a Hilbert space $\mathcal H$ and
$\{U_t\}$ are unitary
operators.
Set $T=\xi_*$ so that
\[ 
B(x)=
\lim_{t \to 0}\, \frac{U_tx-x}{t}\quad\colon\quad x\in\mathcal D(T)
\]
If  $x,y$ is a pair in $\mathcal D(B)$ we get
\[
\langle Bx,y\rangle=
\lim_{t \to 0}\, \langle \frac{U_tx- x}{t},U_ty\rangle
=\lim_{t \to 0}\, \frac{1}{t}\cdot \bigl( \langle U_tx,U_ty)\rangle-
 \langle x,U_ty)\rangle\,\bigr)
 \]
Since $U_t$ are unitary we have
$\langle U_tx,U_ty)\rangle=\langle x,y)\rangle$ for each$Êt$ and conclude that
the last term above  is equal to
\[
\lim_{t \to 0}\, \frac{\langle x,y-U_ty\rangle}{t}=-\langle x,By\rangle
\]

\noindent
Hence $B$ is anti-symmetric, i.e.
\[
\langle Bx,y\rangle=-
\langle x,By\rangle
\]
Set $A=i\cdot T$ which gives
\[
\langle Ax,y\rangle=
i\cdot \langle Tx,y\rangle=
-i\cdot \langle x,Ty\rangle=-\langle x,i\cdot Ty\rangle=
\langle x,Ay\rangle
\]
where  we used that the inner product is hermitian.
Hence $A$ is a densely defined and symmetric operator.
\medskip

\noindent
{\bf{Theorem.}}
\emph{A is self-adjoint, i.e. one has the equality $\mathcal D(A)= \mathcal D(A^*)$.}
\medskip

\noindent
\emph{Proof.}
It suffices to prove that
$\mathcal D(T)=|mathcal D(T^*)$. To btain this we take a vector
$y$ be a vector in $\mathcal D(T^*)$ which by definition gives
a constant $C(y)$ such that
\[
|\langle Tx,y\rangle||\leq C(y)\cdot ||x||
\quad\colon\, x\in\mathcal D(T)\tag{i}
\]
Now
$\langle Tx,y\rangle$ is equal to
\[
\lim_{t\to 0}\,\langle\frac{U_tx-x}{t}, U_ty\rangle
=-\lim_{t\to 0}\,\langle x,\frac{U_ty-y}{t}\rangle\tag{ii}
\]
So if
\[
 \eta_t=frac{U_ty-y}{t}
\]
it follows that there exists
\[
\lim_{t\to 0}\, ,\langle x,\eta_t\rangle=-\langle Tx,y\rangle
\]
for each $x\in\mathcal D(T)$.





\bigskip



The adjoint operators
$\{U^*_t\}$   give another  unitary semi-group with
infinitesmal generator  
$A_*$ where
\[ 
A_* (x)=
\lim_{t \to 0}\, \frac{U^*_tx-x}{t}\quad\colon\quad x\in\mathcal D(A_*)
\]
Since $U_t$ is the inverse operator of $U^*_t$ for each $t$ we get
\[
A_*(x)= \lim_{t\to 0}\, U_t(A_* x)= \lim_{t \to 0}\, \frac{x-U_t x}{t}\quad\colon\quad x\in\mathcal D(A_*)\tag{i}
\]
\medskip

\noindent
From (i) we see that
$\mathcal D(A)\subset
\mathcal D(A_*)$ and
one has the equation
\[
A_* x)=-A(x)\quad\colon\quad x\in\mathcal D(A_*)\tag{ii}
\]
Reversing the role the reader can check the equality
\[
\mathcal D(A)=
\mathcal D(A_*)\tag{iii}
\]
Next, let $x,y$ be a pair in $\mathcal D(A)$.
Then
\[
\langle Ax,y\rangle=
\lim_{t \to 0}\, \langle \frac{U_tx- x}{t},U_ty\rangle
=\lim_{t \to 0}\, \frac{1}{t}\cdot \bigl( \langle U_tx,U_ty)\rangle-
 \langle x,U_ty)\rangle\,\bigr)
 \]
Since $U_t$ are unitary we have
$\langle U_tx,U_ty)\rangle=\langle x,y)\rangle$ for each$Êt$ and conclude that
the last term in (xx) is equal to
\[
\lim_{t \to 0}\, \frac{\langle x,y-U_ty\rangle}{t}=-\langle x,Ay\rangle
\]

\noindent
Hence $A$ is anti-symmetric.
Set
\[ 
B=iA
\]

\bigskip









{\bf{Exercise.}}
Show that (i)  gives the equality
$\mathcal D(A_*)=\mathcal D(A)$ and that:
\[
 A_*(x)=-A(x)\quad\colon\quad x\in\mathcal D(A)
 \]
 
 

\[
 \langle Bx,y\rangle= -\langle x,By\rangle\quad\colon\quad
x,y\in\mathcal D(B)
\]


\noindent {\bf{Exercise.}}
Conclude from the above that the operator $iB$ is self-adjoint.

\medskip


\noindent
{\bf{Remark.}} The equations  above constitute Stones theorem
which was established in 1930.
It has a wide range of applications. See for example von Neumann's article \emph{Zur Operatorenmethode in der klassischen Mekanik}
and Maeda's article \emph{Unitary equivalence of self-adjoint
operators and constant motion}
from 1936.
\bigskip


\noindent
{\bf{11.3.3 A converse construction.}}
Let $A$ be a densely defined self-adjoint operator.
From ¤ 9.B  $A$ is approximated by a sequence of bounded
self-adjoint operators
$\{A_N\}$.
With $N$ kept fixed
we get a semi-group of unitary operators where
\[ 
U^{(N)}_t= e^{-it A_N}
\]
The reader may verify that the inifintesmal generator becomes
$-iA_N$.
Next, for each $x\in \mathcal D(A)$
and every fixed $t$ there exists the limit
\[ 
\lim_{N\to \infty}\, U^{(N)}_t(x)
\]
{\bf{Remark.}} This gives a densely defined linear operator $U_t$
whose operator norm is bounded by one which therefore
extends uniquely to 
a bounded linear operator $\mathcal H$ and it is clear
that this  extension 
becomes a unitary operator. In this way
we arrive at a semi-group $\{U_t\}$
and one verifies that its infinitesmal generator is equal to $-iA$.
However, it is not clear that
$\{U_t\}$ is strongly continuous and one may ask for 
conditions 
on the given self-adjoint operator $A$ which ensures that  $\{U_t\}$
is strongly continuous.



\newpage





\newpage

POSTPONE 

\noindent
{\bf{An exercise.}}
One often applies Newton's
decomposition of rational functions
and we shall employ his  formulas without hesitation.
Here is an example. Let 
$n\geq 2$ andÊ$t_1<\ldots<t_n$ is a strictly invreasing sequence of real numbers.
With a variable $z$ we consider
the rational function
\[
P(z)=\sum_{\nu=1}^{\nu=n}\, \frac{A_\nu}{t_\nu-z}
\]
where $\{A_\nu\}$ are positive real numbers.
Put $\mathcal A= \sum\, A_\nu$ and 
\[
a= \mathcal A^{-1}\cdot \sum\, A_\nu t_\nu
\]
Show that  $P(z)$ has $n-1$
simpe zeros
$\tau_1,\ldots,\tau_{n-1}$ where 
$t_1<\tau_1<t_2<\ldots <\tau_{n-1}<t_n$, and
there exist positive numbers
$B_1,\ldots,B_{n-1}$ such that
\[
P(z)=\frac{\mathcal A}{a-z-Q(z)}\quad\colon\,
\mathcal A= \sum\, A_\nu\quad\text{where}\quad
Q(z)=\sum_{\nu=1}^{\nu=n-1}\, 
\frac{B_\nu}{\tau_\nu-z}
\] 
Finally, use
residue calculus to prove that 
the $B$-numbers are given by the equations
\[
B_p^{-1}=
\mathcal A^{-1}\cdot \sum_{\nu=1}^{\nu=n}\,\frac{A_\nu}{(t_\nu-\tau_p)^2}
\]
\bigskip


\bigskip
\noindent
We discuss  two of the most  problems whose solutions inspired
later development of operator theory.
\medskip



\noindent
{\bf{The Dirichlet problem}}
Let
$\Omega$ be a bounded
domain in
${\bf{R}}^3$ whose boundary is a finite union of closed
$C^1$-surfaces. The Dirichlet  problem amounts
to find a harmonic extension $F$Êof each
$f\in C^0(\partial\Omega)$, i.e. here
$\Delta(F)=0$ in $\Omega$ while $F=f$ on the boundary.
The maximum principle for harmonic functions implies that 
the Dirichlet problem has a unique solution if it exists. Moreover
\[
\max_{p\in\overline{\Omega}} |F(p)|=
\max_{p\in\partial \Omega} \, |f(p)|\tag{*}
\]
It suffices to get solutions for a
dense subapace of
$C^0(\partial\Omega)$. 
For if $\{f_n\}$ is a sequence which convege uniformyl to a limit function
$f$ and  Dirichet's solutions $\{F_n\}$ exists, then
(*) entails that this sequence converges uniformly on
$\overline{\Omega}$ to a limit function $F$ which solves
the Dirichlet probelm for $f$.
To solve the Dirchlet problem for a dense set of boundary
value functions
one can proceed as follows:
Each real-vaued continuous boundary function
$\phi$ gives via Newton's potential a harmonic function in
$\Omega$:
\[
\Phi(p)=
\frac{1}{4\pi}\cdot \int_{\partial\Omega}\,
\frac{\phi(q)}{|p-q|}\, dA(q)
\]
where $dA$ is the area measure on the boundary.
If $\phi$ is of class $C^1$
on the $C^1$-manifold $\partial\Omega$ it is easily verified that
$\Phi$ extends continuously  to the closure. So if
$\phi_*=\Phi|\partial\Omega$ we obtain a continuous function
which has $\Phi$ as a harmonic extension, i.e. the
Dirichlet problem is solved for $\phi_*$.
Hence one is led to consider the linear operator 
defined by
\[ 
T(\phi)(p)=\frac{1}{4\pi}\cdot 
\int_{\partial\Omega}\,
\frac{\phi(q)}{|p-q|}\, dA(q)
\] 
where $p$  varies on
$\partial\Omega$. Since
\[
\max_{p\in\partial\Omega}\, 
\int_{\partial\Omega}\,
\frac{1}{|p-q|}\, dA(q)<\infty
\]
elementary measure theory  entails that
$T$ is a bounded linear operator on the Banach space
$C^0(\partial\Omega)$ and from the above
the Dirichlet problem is well-posed if
the range of
the linear operator $T$ is dense.
To prove this density  one uses
that the dual space of 
$C^0(\partial\Omega)$ consists of Riesz measures.
Baisc meaasure theory shows that for evety
such measure $\mu$ the function defined on the boundary by
\[
p\mapsto \int_{\partial\Omega}\,
\frac{1}{|p-q|}\, d\mu(q)
\]
is integrable in Lebegue's sense
with respect to the area measure $dA$.
The requested density of $T$ amounts to show that
this $L^1$-function cannot be zero unless $\mu=0$.
This can be proved in several ways. See ¤ xx for details.
Hence the Dirichlet problem can be settled in the spirit of
Neumann and PoincarŽ via operator methods.

























\end{document}
